### 2019-01-31 supCLT.tex
supCLT.tex: inital

\documentclass{article}

\usepackage{cite}
\usepackage[utf8]{inputenc}
\usepackage{hyperref,amsmath,amssymb,amscd}
\usepackage{amsthm}
\usepackage{color}
\usepackage{bbm}
\usepackage{appendix} 
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\newtheorem{remark}{Remark}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{notation}{Notation}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{conjecture}{Conjecture}[section]

\title{Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching}
\author{Jianjie Zhao }

\begin{document}
%%给公式前加章节编号
\makeatletter
\@addtoreset{equation}{section}
\makeatother
\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}

\maketitle

\section{Introduction}
\subsection{Model}

We first fix our notation, for a vector $x\in \mathbb{R}^d$, we denote by $|x|$  its Euclidean norm. Let $\xi=\{\xi_t : t\geq 0\}$ be an Ornstein-Uhlenbeck prcess, short for OU process, on $\mathbb{R}^d$, with infinitesimal generator $L$. For any $f \in C^2(\mathbb{R}^d)$,
\begin{equation}\label{generatior}
Lf(x)= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x))   
\end{equation}
where $\sigma>0$ is the diffusion parameter, $b>0$ is the drift parameters. What's more, we respectively use $\Delta$ and $\nabla$ to express the Laplace operator and gradient operator as usual.

For any $x\in \mathbb{R}^d$, We denote by $\Pi_x$ the law of $\xi$ starting from $x$. The semigroup of $\xi$ will be denoted by $\{T_t: t\geq 0\}$.

In this paper, we consider a branching mechanism of the form  
\begin{equation}\label{mechanism}
\psi(\lambda)=-\alpha \lambda + \lambda^{(1+\beta)}, \lambda \geq 0
\end{equation}
Where $\alpha = -\psi'(0+)>0$ and $\beta \in (0,1) $.

Let $\mathcal{M}(\mathbb{R}^d)$ be the space of finite measures on $\mathbb{R}^d$. We say a $\mathcal{M}(\mathbb{R}^d)$-value branching Markov process $X=\{(X_t)_{t\geq 0},\mathbb{P}_{\mu}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for any $t \geq 0$, positive bounded measurable functions $f$ on $\mathbb{R}^d$ and any $\mu \in \mathcal{M}(\mathbb{R}^d)$, we have 
\begin{equation} \label{super}
    \mathbb{P}_{\mu}(e^{-\langle f,X_t \rangle})=e^{-\langle u_f(\cdot , t), \mu \rangle},
\end{equation}
where  $u_f(\cdot , t)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
     u_f(x , t) + \Pi_x \left( \int_0^t\psi(u_f(\xi_s,t-s))~ds\right) =\Pi_x [f(\xi_t)],
\end{equation}
According to \cite[section 2]{ZL}, is equivalent to
\begin{equation}\label{eq2}
     u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
\end{equation}

In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$. Put $\|\mu\|=\langle 1,\mu\rangle$. We assume that the parameter $\alpha$ in branching mechanism $\psi$ is larger than zero, i.e. $X$ is  supercritical.

 The existence of such superprocesses is well known, see \cite{EB} for instance. Let $||X_t||=\langle 1, X_t \rangle$ be the total mass of the process $X$ at time $t$, then $\{\|X_t\|; t \geq 0\}$ is a continuous-state branching process with branching mechanism $\psi$.  The fact $\psi(\infty)=\infty$ implies that the probability of extinction event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see, for example,  \cite[section 10.2.2]{AK}. Let $\alpha^{\ast}$ be the larger root of $\psi=0$, we have
$$\mathbb{P}_{\mu}\left(\lim_{t\rightarrow \infty}\|X_t\|=0\right)=e^{-\alpha^{\ast}\|\mu\|}.$$

For any $f \in \mathcal{P}$, define the {\em Feyman-Kac semigroup} 
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x) := \Pi_x [e^{\alpha t}f(\xi_t)], \quad x\in \mathbb{R}^d,t\geq 0,
\end{equation}
which is konwn as the {\em mean semigroup} of the superprocess $X$, in the sense that
\begin{equation}\label{meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle] = \langle T_t^{\alpha t}f, \mu \rangle.
\end{equation}
see \cite[Proposition 2.27]{ZL}.  Notice that $T^{\alpha}_t f =e^{\alpha t}T_t f$.

The purpose of this paper is to establish some spatial central limit theorems for the super OU-process with stable branching \eqref{mechanism}. More precisely, consider the limit of 
$$\frac{\langle f,X_t\rangle-\|X_t\|\langle f, \varphi \rangle}{F_t},$$
we want to find $(F_t)_{t\geq0}$, for suitable test functions $f$, such that the former formula convergence to some non-degenerate random variable as $t\rightarrow \infty$.

\subsection{OU semigroup and Eigenfunctions}

Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
\begin{equation}\label{invariantdensity}
    \varphi (x) =\left (\frac{b}{\pi \sigma^2}\right )^{\frac{d}{2}}\exp \left(-\frac{b}{\sigma^2}|x|^2 \right ),\quad x\in \mathbb{R}^d.
\end{equation}
Let $L^2(\varphi):= \left\{ h: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
$$\langle f_1, f_2 \rangle_{\varphi} = \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).$$

For $p=(p_1,p_2,...,p_d) \in \mathbb{Z}_+^{d}$, let $|p|=p_1+...+p_d$, $p!=p_1 \cdot ... \cdot p_n$ and $\partial x^p =\partial x_1^{p_1} \cdot ... \cdot \partial x_d^{p_d}$. We recall the Hermite polynomials $H_p$ in $\mathbb{R}^d$

$$H_p(x):=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{|p|}}{\partial x^p} \left ( e^{-|x|^2} \right ).$$
It is known that, see \cite{GD} as an example, the eigenvalues of $L$ are $\{-bk: k =0,1,2,...\}$ and the eigenspace $A_k$ corresponding to $-bk$ is
$$A_k = {\rm Span} \{\phi_p : |p|=k\},$$
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)= \frac{1}{\sqrt{p!2^{|p|}}}H_p \left(\frac{\sqrt{b}}{\sigma}x \right ),\quad x\in \mathbb{R}^d, p\in \mathbb{Z}_+^d.
\end{equation}
 The function $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-b|p|$, and satisfies 
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)=e^{-b|p|t}\phi_p(x),\quad x\in \mathbb{R}^d.
\end{equation}
Moreover, The polynomials $\{\phi_p(x)\}_{p \in \mathbb{Z}_+^d}$ form a complete orthonormal basis of $L^2(\varphi)$. Thus, for any $f\in L^2(\varphi)$, we have
\begin{align}
    f=\sum_{k=0}^{\infty}\sum_{|p|=k}a_p \varphi_p \quad {\rm in~} L^2(\varphi), \label{semicomp1}
\end{align}
where $a_p=\langle f, \phi_p \rangle_{\varphi}$. Let
\begin{equation}\label{order}
    \kappa(f):=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  a_p \neq 0\right \}
\end{equation}
denote the order of function $f$ in $L^2(\varphi)$. Then $ \kappa(f)\geq 0$, in particular, the order of constant functions is zero.

In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
\begin{align*}
     \mathcal{P}:=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C, n>0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}
\end{align*}

It is easy to see that $\mathcal{P} \subset L^2(\phi)$. What's more, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$
\begin{equation}\label{semigroupineq}
    |T_tf(x)| \leq e^{-\kappa(f)bt}R(x) 
\end{equation}

That is to say the rate of decay of the semigroup depending on $\kappa(f)$. The readers can find the prove in \cite[Fact 1.2]{MM}.

\subsection{Characteristic functions}
 Let $X$ be a super OU-process with initial configuration $\mu$. For any $f \in \mathcal{P}$,
replace $f$ by $-i\theta f$ in equations of \eqref{super} and \eqref{eq2}, we obtain that
\begin{equation}\label{characteristic}
    \mathbb{P}_{\mu}\left[\exp(i\theta \langle  f,X_t\rangle)\right]=e^{\langle w_f(\cdot,t,\theta),\mu\rangle}
\end{equation}
where $w_f(x,t,\theta)=\log \mathbb{P}_{\delta_x}e^{i\theta\langle f,X_t\rangle}$ satisfying the equation that
\begin{equation}\label{charequation}
    w_f(x,t,\theta)-\int_0^t T_{t-s} \left(\psi (-w_f(\cdot,s,\theta))\right)(x)ds=i\theta T_tf(x)
\end{equation}

Recall the branching mechanism $\psi$ and Feynman-Kac semigroup $T^{\alpha}_t$, and apply \cite[Proposition 2.9]{ZL} to \eqref{charequation}, we have that
\begin{equation}\label{chareq2}
        w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x)
\end{equation}

\subsection{Main Result}

In this subsection, we will give the main results of this paper. In the remainder of this paper,whenever we deal with an initial configuration $\mu \in \mathcal{M}(\mathbb{R}^d)$, we are implicitly assuming that it has a compact support.
\subsubsection{Large Branching Rate}

For each $p\in \mathbb{Z}_+^d$, we define 
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
 We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0\leq\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{theorem}\label{Theorem11}
     If $g \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(g)b(1+\beta)$, then as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa(g)b)t}\langle g, X_t\rangle \rightarrow\sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
     for any $0\leq\gamma<\beta$.

     Moreover, if $g$ is twice differentiable and its twice derivative $D^2 g$ satisfies $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure. 
 \end{theorem}
For any $t>0$, let $W_t:=e^{-\alpha t}\|X_t\|$, then $W_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $W_{\infty}:=\lim_{t\rightarrow\infty}W_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.  
 \begin{remark}
    If $\kappa(g)=0$, $\langle g, \phi_{\kappa(g)}\rangle_{\varphi}$ reduces to $\langle g,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
     $$e^{-\alpha t}\langle g, X_t\rangle \rightarrow \langle g, \varphi\rangle W_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    for any $0\leq\gamma<\beta$.

    Moreover, if $g$ is twice differentiable and $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure. 
 \end{remark}

\subsubsection{Critical Branching Rate}
For $g\in \mathcal{P}$, define 
$$\tilde{m}[g]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
{\color{red}where} 
$$\phi(x)=\sum_{|p|=\kappa(g)}\langle g,\phi_p\rangle\phi_p(x).$$
See Lemma \ref{lemma210} for more details about $\tilde{m}[g]$.
\begin{theorem}\label{Theorem12}
Let $g\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
$$\frac{\langle g,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by 
$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[g]).$$
\end{theorem}

\subsubsection{Small Branching Rate}

For $g\in \mathcal{P}$, define
$$m[g]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx$$
In Lemma \ref{lemma211}, we will prove that $|m[g]|<\infty$.
\begin{theorem}\label{Theorem13}
    If $g\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
    $$\frac{\langle g,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
    where $\eta_2$ is a $(1+\beta)$-stable random variable with characteristic function given by 
    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(\theta^{1+\beta}m[g]).$$
\end{theorem}

\section{Preliminaries}
In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in [0,\beta)$. Fix $g\in \mathcal{P}$ and for notational convenience we omit it in formulations of most of lemmas below.

Consider a incremental decomposition of $\langle g,X_t \rangle$. Denote by $\{\mathcal{F}_t:t\geq 0\}$ the filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$. For $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$. For each $t-k\geq 1$, according to \eqref{meanformula}, define
\begin{align*}
    M_k^t[g]:&=\langle g_k, X_{t-k}\rangle-\mathbb{P}_{\mu}(\langle g_k,X_{t-k}\rangle|\mathcal{F}_{t-k-1})\\
    &=\langle g_k, X_{t-k}\rangle-\langle T_1^{\alpha}g_{k},X_{t-k-1}\rangle\\
    &=\langle g_k, X_{t-k}\rangle-\langle g_{k+1},X_{t-k-1}\rangle.
\end{align*}
If $k=t$, let $M_t^t[g]:=\langle g_t,\mu\rangle$, where $\mu $ is the initial configuration. From now on, we assume $t$ is a positive integer, for simplicity. Thus
\begin{equation}\label{decomposition}
    \langle g,X_t\rangle=\sum_{k=0}^{t}M_k^t[g]
\end{equation}

{\color{red} We have to emphasize that, if $t\notin \mathbb{N}$, there will appear an additional term corresponding to the interval $[\lfloor t \rfloor,t]$, which can be handled with the same techniques.}
\subsection{Approximate expansion of characteristic function}

In this subsection, we will estimate the characteristic function of $M_k^t[g]$ near $0$. First, we will prove the following inequality which controls $w_{g_k}(x,s,\theta)$.
\begin{lemma}\label{lemma1}
There exists $R \in \mathcal{P}$, such that for any $k \in \mathbb{N}$, $x\in\mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
$$e^{-(\alpha-\kappa(g)b) s}|w_{g_k}(x,s,\theta)|\leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), \quad s\geq 0.$$
\end{lemma}
Recall some result about the Kuznestov measures of $\{X_t, t\geq 0\}$. Let $\mathbb{D}$ be the collection of $\mathcal{M}(\mathbb{R}^d)$-valued right continuous functions $t\rightarrow \omega_t$ on $(0,\infty)$ having zero as a trap. Denote by $\{\omega_t, t\geq0\}$ the coordinate process of $\mathbb{D}$ and
 $(\mathcal{C},\mathcal{C}_t)$ the natural $\sigma$-algebras on $\mathbb{D}$ generated by the coordinate process.

It's known by \cite[section 8.4]{ZL} that  one can associate with $\{\mathbb{P}_{\delta_x}:x\in\mathbb{R}^d\}$ a family of $\sigma$-finite measures $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ defined on $(\mathbb{D},\mathcal{C})$ such that $\mathbb{N}_x\{0\}=0$, 
\begin{equation}\label{Nmeasure}
   \int_{\mathbb{D}}(1-e^{-\langle f,\omega_t\rangle})\mathbb{N}_x(d\omega)=-\log \mathbb{P}_{\delta_x}(e^{-\langle f, X_t \rangle}), \quad f \in \mathcal{B}_b^+(\mathbb{R}^d), t>0,
\end{equation}
and, for $0<t_2<...<t_n<\infty$, and nonzero $\mu_1,...,\mu_n \in \mathcal{M}(\mathbb{R}^d)$,
\begin{align*}
    \mathbb{N}_x&\left(\omega_1\in d \mu_1,...,\omega_n \in d\mu_n\right)=\mathbb{N}_x(\omega_1\in d\mu_1)\mathbb{P}_{\mu_1}\left(X_{t_2-t_1}\in d \mu_2\right)...\\
    &\mathbb{P}_{\mu_{n-1}}\left(X_{t_n-t_{n-1}}\in d \mu_n\right).
\end{align*}
We refer $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ as {\em Kuznestov measures} of $X$. For more general definition and further properties of such measures, we refer our readers to \cite{ZL,DK}.

For any $\mu \in \mathcal{M}(\mathbb{R}^d)$, if $\mathcal{N}$ is a Poisson random measure defined in some probability space with intensity $\mathbb{N}_{\mu}(\cdot):=\int_{\mathbb{R}^d}\mathbb{N}_x(\cdot)~\mu(dx)$, then the super OU-process $\{X;\mathbb{P}_{\mu}\}$ can be realized by $\tilde{X}_t(\cdot)=\mu$ and
\begin{align*}
    \tilde{X}_t(\cdot):=\int_{\mathbb{D}}\omega_t(\cdot)\mathcal{N}(d\omega), \quad t\geq 0.
\end{align*}
See \cite[Theorem 8.24]{ZL} for a proof.

What's more, if $\mathbb{P}_{\delta_x}|\langle f, X_t\rangle|<\infty$, then
\begin{equation}\label{Nmean}
    \mathbb{N}_x(\langle f,\omega_t \rangle) = \mathbb{P}_{\delta_x}(\langle f, X_t\rangle)=T^{\alpha}_t f(x).
\end{equation}
See \cite[Lemma 3.3]{RSS} for example.

\begin{proof}[Proof of Lemma \ref{lemma1}]

Recall that $w_{g_k}(x,s,\theta)=\log\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
Replace $f$ by $-i\theta g_k$ in equation \eqref{Nmeasure},\eqref{Nmean}, we obtain that $w_{g_k}(x,s,\theta)=\mathbb{N}_x\left(e^{i\theta\langle g_k,w_s\rangle}-1\right)$.
Therefore,by the element inequality $|e^{i\theta}-1|\leq|\theta|$ for $\theta \in \mathbb{R}$, we have 
$$|w_{g_k}(x,s,\theta)|=|\mathbb{N}_x(e^{i\theta\langle g_{k},\omega_s \rangle}-1)|\leq |\theta|\mathbb{N}_x(\langle|g_k|,\omega_s\rangle)\leq|\theta|T_{s+k}^{\alpha}|g|$$
At last, by \eqref{semigroupineq}, we get the desired result.
\end{proof}
 For any $k \in \{0,1,...,t\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$, by the Markov property of $X$, we have
 \begin{align*}
      \mathbb{P}_{\mu}(e^{i\theta M_k^t[g]}|\mathcal{F}_{t-k-1}) &=\mathbb{P_{\mu}}\left [\mathbb{P}_{\nu}\left(e^{i\theta(\langle g_k,X_1\rangle-\langle T_1^{\alpha}g_k,\nu\rangle)}\right)|_{\nu=X_{t-k-1}}\right]   \\
      &=\mathbb{P}_{\mu}\left[ e^{\langle w_{g_k}(\cdot,1,\theta),X_{t-k-1}\rangle -i \theta\langle T_1^{\alpha}g_k,X_{t-k-1}\rangle}\right].
 \end{align*}
Hence, it is important to estimate the function $w_{g_k}(x,1,\theta)$. For any $f \in \mathcal{P}$, let 
\begin{equation}\label{w2function}
    \tilde{w}_{f}(x,t,\theta)=i\theta T^{\alpha}_t f(x) + \int_0^t T^{\alpha}_{t-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds
\end{equation}

\begin{lemma}\label{lemma2}
There exists $R \in \mathcal{P}$ and $p_1 >1+\beta$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have 
$$|w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_1}R(x),\quad x\in \mathbb{R}^d,\theta\in \mathbb{R}.$$
\end{lemma}
\begin{proof}
 Using the fact that 
 \begin{align}
      |x^{1+\beta}-y^{1+\beta}|\leq C (|x|^{\beta}+|y|^{\beta})|x-y|\label{element}
 \end{align}
for $x,y \in \mathbb{C}$ such that ${\rm Re~} x \geq 0, {\rm Re~} y\geq 0$, we have
\begin{align*}
   |w_{g_k}(x,s,\theta)-&\tilde{w}_{g_k}(x,s,\theta)|\\
   \leq &\int_0^s T_{s-v}^{\alpha}\left(|(-w_{g_k}(\cdot,v,\theta))^{1+\beta}-(-i\theta T_v^{\alpha}g_k)^{1+\beta}|\right)(x)~dv\\
   \leq &\int_0^s T_{s-v}^{\alpha}\left( |w_{g_k}-i\theta T_v^{\alpha}g_{k}|\left(|w_{g_k}|^{\beta}+|i\theta T_v^{\alpha}g_k|^{\beta}\right)\right)(x)~dv, 
\end{align*}
as $\exp({\rm Re~}w_{g_k})=|\exp(w_{g_k})|=\left|\mathbb{P}_{\delta_x}\exp(i\theta \langle  g_k,X_t\rangle)\right|\leq 1$, this is to say ${\rm Re~}(-w_{g_k})\geq0$.

Notice that, for $0\leq v \leq 1$, $x\in \mathbb{R}^d$ and $\theta \in \mathbb{R}$, by Lemma \ref{lemma1} and \eqref{semigroupineq}, there exists $R_1,R_2\in \mathcal{P}$ such that
\begin{align*}
    |w_{g_{k}}(x,v,\theta)|\leq &|\theta|e^{(\alpha-\kappa(g)b)k}R_1(x),\\
    |i\theta T_v^{\alpha}g_k(x)|\leq & |\theta|e^{(\alpha-\kappa(g)b)k}R_1(x),
\end{align*}
and
\begin{align}
   |w_{g_{k}}(x,v,\theta)-i\theta T_v^{\alpha}g_k(x)|=&\left| \int_0^v T^{\alpha}_{v-u}(-w_{g_k}(\cdot,u,\theta))^{1+\beta}(x)du\right| \nonumber\\ 
   \leq & \int_0^1 T_{1-u}^{\alpha}(|w_{g_k}(\cdot,u,\theta)|^{1+\beta})(x)du \nonumber \\
   \leq & |\theta e^{(\alpha-\kappa(g)b)k}|^{1+\beta}R_2(x). \label{Zineq}
\end{align}
In consequence, take $p_1=2+\beta$, we obtain the desired result.
\end{proof}
For $f\in \mathcal{R}$, define 
$$Z_f(x,\theta):=\int_0^1 T^{\alpha}_{1-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds ,$$
and let $Z_f(x)=Z_f(x,1)$. We observe that
\begin{equation}\label{zfunction}
    Z_f(x,\theta)=\theta^{1+\beta}Z_f(x).
\end{equation}

\begin{corollary}\label{corollary2}
  There exists $R \in \mathcal{P}$ such that for any $k\in\{0,1,...,t\}$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have 
  \begin{align}
       &|Z_{g_k}(x,\theta)|\leq |\theta|^{1+\beta}e^{(\alpha-\kappa(g)b)(1+\beta)k}R(x) \label{zineq1},\\
       &|Z_{g_k}(x)|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}R(x). \label{zineq2}
  \end{align}
  \end{corollary}

\begin{proof}
     By \eqref{semigroupineq}, we have
   $$|Z_{g_k}(x)|\leq \int_0^1 T_{1-s}^{\alpha}(|T_s^{\alpha}g_k|^{1+\beta})(x)ds\leq  e^{(\alpha-\kappa(g)b)(1+\beta)k}R(x), \quad x\in \mathbb{R}^d,$$
   for some $R\in \mathcal{P}$. The proof of \eqref{zineq1} is similar with \eqref{zineq2}.
\end{proof}

\begin{corollary}\label{corollary1}
There exists $R \in \mathcal{P}$ and $p_2 >1+\beta$ such that for any $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, we have 
$$\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}=1+\langle Z_{g_k}(\cdot,\theta),\mu\rangle+\langle err(\cdot,\theta),\mu\rangle$$
where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R(\cdot)$.
\end{corollary}

\begin{proof}
    Let $ w_f(x,\theta)=w_f(x,1,\theta)$, $\tilde{w}_f(x,\theta)=\tilde{w}_f(x,1,\theta)$ for short, and denote
\begin{align}\label{charfirst}
    \varphi_{\mu}(\theta)=\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}=e^{(\langle w_{g_k}(\cdot,\theta),\mu \rangle-i\theta \langle T_1^{\alpha} g_k, \mu \rangle)},
\end{align}
 we have
\begin{align*}
    |\varphi_{\mu}(\theta)-1-& \langle Z_{g_k}(\cdot, \theta),\mu\rangle|\\
    &\leq|\varphi_{\mu}(\theta)-1-\left( \langle w_{g_k}(\cdot,\theta), \mu \rangle-i\theta \langle T_1^{\alpha}g_k,\mu\rangle\right)|\\
    &+|\langle w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta),\mu \rangle|.
\end{align*}
Using Lemma \ref{lemma2}, \eqref{Zineq} and the fact that if $ {\rm Re~} z\leq 0$, $|e^z-1-z|\leq|z|^2$,   we get, for any $\theta \in \mathbb{R}$, there exists $R\in \mathcal{P}$ such that 
\begin{align*}
    |\varphi_{\mu}(\theta)-1-& \langle Z_{g_k}(\cdot, \theta),\mu\rangle|\\
    &\leq 2|\langle w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k, \mu \rangle|^2 + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle\\
    &\leq |\theta_{k}|^{2(1+\beta)}\langle R,\mu\rangle + |\theta_{k}|^{2+\beta}\langle R,\mu\rangle,
\end{align*}
where $\theta_k=\theta e^{(\alpha-\kappa(g)b)k}$. By implicitly assuming that $|\theta_k|\leq 1$, and taking $p_2=\min \{2(1+\beta), 2+\beta\}$, we get the desired result.
\end{proof}  
\begin{remark}\label{remark1}
   For $0<s\leq 1$, let 
   $$Z_f(x,s,\theta):=\int_0^s T^{\alpha}_{s-u}(-i\theta T_u^{\alpha}f)^{1+\beta}(x)du ,$$
   which has the same estimation with \eqref{zineq1}. moreover, the decomposition in Corollary \ref{corollary1} is also hold for $\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)$, this is to say,
   $$\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}=1+\langle Z_{g_k}(\cdot,s,\theta),\mu\rangle+\langle err(\cdot,\theta),\mu\rangle$$
   where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R(\cdot)$, for some $R\in \mathcal{P}, p>1+\beta$.
\end{remark}

\subsection{Moment}

 In this subsection, for any $\gamma \in [0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle $ by an exponential function depending on $\kappa(g)$.
\begin{lemma}\label{lemma23}
For any $0\leq \gamma < \beta$ there exists a constant $C>0$ such that
$$\|M_k^t[g]\|_{1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k},$$
for any $k \in \{0,...,t\}$.
\end{lemma}

\begin{proof}
    Let $C_k=e^{(\alpha-\kappa(g)b)k}$, and, for convenience, define $A:=\{|M_t^k[g]|>C_k\}$, $A_{\mu}:=\{|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\mu\rangle|>C_k\}$.
$$\mathbb{P}_{\mu}|M_k^t[g]|^{1+\gamma}=\mathbb{P}_{\mu}|M_k^t[g]\mathbbm{1}_{A^c}|^{1+\gamma}+\mathbb{P}_{\mu}|M_k^t[g]\mathbbm{1}_{A}|^{1+\gamma}=I+II.$$
For the first part,
\begin{align*}
    I\leq C_k^{1+\gamma}=&e^{(\alpha-\kappa(g)b)k(1+\gamma)}=e^{-\alpha(t-k)}e^{\alpha t}e^{(\gamma \alpha-\kappa(g)(1+\gamma)b)k}\\
    \leq &e^{\alpha t}e^{(\gamma \alpha-\kappa(g)(1+\gamma)b)k},
\end{align*}
as $k\leq t$.

For the second part, recall that $M_k^t[g]=\langle T_k^{\alpha}g, X_{t-k}\rangle-\langle T_{k+1}^{\alpha}g,X_{t-k-1}\rangle$,
under the condition of $\sigma$-algebra $\mathcal{F}_{t-k-1}$, by the Markov property of $X$, we have
\begin{align*}
    II=\mathbb{P}_{\mu}\left[\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\mathbbm{1}_{A_{\nu}}\right]|_{\nu=X_{t-k-1}}\right]
\end{align*}
Observe that, for any $\nu \in \mathcal{M}(\mathbb{R}^d)$
\begin{align}
    &\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\right] \label{temp1}\\ 
    &=(1+\gamma)\int_0^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|\mathbbm{1}_{A_{\nu}}>\lambda\right)d\lambda \nonumber\\
    &\leq (1+\gamma)\int_{C_{k}}^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\right)d\lambda.\nonumber
\end{align}
Using the element inequality $\mathbb{P}(|Y|>2/u)\leq u^{-1}\int_{-u}^{u}(1-\varphi(t))dt$, see,\cite[Chaper 3]{DR}, for example, where $Y$ is a random variable corresponding to characteristic function $\varphi(t)$, $u\geq 0$, we have

$$\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\right)\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1-\varphi_{\nu}(\theta))d\theta,$$
where $\varphi_{\nu}(\theta))$ has been defined in Corollary \eqref{corollary1}. What's more, as $g_k=T_k^{\alpha}g$, by Corollary \eqref{corollary1} and Corollary \eqref{corollary2}, we get, for any $\theta\in\mathbb{R}$, there exists $R_1,R_2 \in \mathcal{P}$ and $p>\beta$, such that 
\begin{align*}
    |1-\varphi_{\nu}(\theta)|&\leq|\langle Z_{g_k}(\cdot,\theta),\nu \rangle|+|\langle err(\cdot,\theta),\nu \rangle|\\
    &\leq|\theta_k|^{1+\beta}\langle R_1,\nu\rangle+|\theta_k|^{1+p}\langle R_1, \nu \rangle\\
    &\leq (|\theta_k|^{1+\beta}+|\theta_k|^{1+p})\langle R_2, \nu \rangle.
\end{align*}
Therefore,
\begin{align*}
    &\mathbb{P}_{\nu}\big(|\langle T_k^{\alpha}g, X_1 \rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\big)\\
    &\leq\lambda\int_0^{2/\lambda}(|\theta_k|^{1+\beta}+|\theta_k|^{1+p})\langle R_2, \nu \rangle d\theta\\
    &\leq C_1(e^{(\alpha-\kappa(g)b)k(1+\beta)}\lambda^{-(1+\beta)}+e^{(\alpha-\kappa(g)b)k(1+p)}\lambda^{-(1+p)})\langle R_2,\nu \rangle,
\end{align*}
Where $C_1=\max\{\frac{2^{1+\beta}}{2+\beta}, \frac{2^{2+p}}{2+p}\}$ is a constant real number. Then by calculating the integral in formula \eqref{temp1}, we get
\begin{align*}
    &\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma} \right] \\
    &\leq C_2\left(e^{(\alpha-\kappa(g)b)k(1+\beta)}C_k^{\gamma-\beta}+e^{(\alpha-\kappa(g)b)k(1+p)}C_k^{\gamma-p}\right)\langle R_2,\nu\rangle\\
    &\leq C_2 e^{(\alpha-\kappa(g)b)k(1+\gamma)}\langle R_2,\nu\rangle,
\end{align*}
for some $C_2>0$. At last, using the mean formula \eqref{meanformula} and \eqref{semigroupineq}, we get
\begin{align*}
    II &\leq C_2e^{(\alpha-\kappa(g)b)k(1+\gamma)}\mathbb{P}_{\mu}\left[\langle R_3,X_{t-k-1}\rangle\right]\\
       &\leq C_3e^{\alpha t}e^{(\gamma\alpha-\kappa(g)b(1+\gamma))k},
\end{align*}
for some $C_3>0$. Combining with the result of $I$ and $II$, we complete the proof.
\end{proof}
\begin{remark}\label{remark2}
   When $t\notin \mathbb{N}$, on the interval $[\lfloor t \rfloor , t]$, similar with $M_k^t[g]$, we can define 
   $$M_{t,\lfloor t \rfloor}[g]:=\langle g,X_t\rangle-\langle T^{\alpha}_{t-\lfloor t \rfloor}g,X_{\lfloor t \rfloor}\rangle,$$
   which satisfies 
   $$\|M_{t,\lfloor t \rfloor}[g]\|_{1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t},$$
   For some $C>0$. This can be proved by using Remark \ref{remark1} and following the same method in Lemma \ref{lemma23}.
\end{remark}

Recall that,$\langle g,X_t\rangle$ is the sum of $M_k^{t}[g], k=0,1,...,t$. We obtain the following lemma.

\begin{lemma}\label{lemma24}
For any $0\leq \gamma < \beta$ there exists a constant $C>0$, we have the result:

i) When $\alpha\gamma > \kappa(g)(1+\gamma)b$,
$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C e^{(\alpha-\kappa(g)b)t}.$$

ii) When  $\alpha\gamma = \kappa(g)(1+\gamma)b$,
$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}.$$

iii) When $\alpha\gamma < \kappa(g)(1+\gamma)b$,
$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}.$$

\end{lemma}
\begin{proof}
Using the triangle inequality and Lemma \eqref{lemma23}, for some $C_1>0$
$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq \sum_{k=0}^{t}\|M_k^t[g]\|_{1+\gamma}\leq C_1 e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^t e^{\frac{\gamma\alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}.$$
By calculating the sum on the right, we easily get the result. 
\end{proof}

\begin{remark}
    The Lemma \eqref{lemma24} offers insights how to guess $\{F_t, t\geq0\}$ raised in Introduction. indeed

    Large branching rate: when $\alpha\gamma > \kappa(g)(1+\gamma)b$, $F_t\approx e^{(\alpha-\kappa(g)b)t} $;

    Critical branching rate: when when  $\alpha\gamma = \kappa(g)(1+\gamma)b$, $F_t\approx (te^{\alpha t})^{\frac{1}{1+\beta}}\approx(t\|X_t\|)^{\frac{1}{1+\beta}}$;

    Small branching rate: when $\alpha\gamma < \kappa(g)(1+\gamma)b$, $F_t\approx e^{\frac{\alpha t}{1+\beta}}\approx \|X_t\|^{\frac{1}{1+\beta}}$.
\end{remark}
\subsection{Martingales}

In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales, for $0\leq\gamma<\beta$. Recall that $L$ is the infinitesimal generator of OU-process. Let $a\in \mathbb{R}$ and $f\in \mathcal{P}$ such that $Lf \in \mathcal{P}$ ,we define that
$$M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle \bar{f}, X_s\rangle~ ds$$
Where $\bar{f}=(L+ab)f$. The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathcal{F}_t\}_{t\geq 0}$.
\begin{lemma}\label{lemma25}
For any $a \in \mathbb{R}$ and $f\in\mathcal{P}$ such that $L f\in\mathcal{P}$, Then $\{M_t^{f,a},\mathcal{F}_t:t\geq 0\}$ is a martingale.
\end{lemma}

\begin{proof} 
For any $0\leq s\leq t$,
\begin{align}
    \mathbb{P}_{\mu}\left[M_t^{f,a}|\mathcal{F}_s\right] &=e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\left[\int_0^t e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du|\mathcal{F}_s\right]\nonumber\\
    &=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du\nonumber\\
    &-\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_u\rangle~ du.\label{martingale1}
\end{align}

Observe that $\frac{d}{du}\left(e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha}f,X_s\rangle\right)=e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha}\bar{f},X_s\rangle$, we get
$$\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_u\rangle~ du=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f,X_s\rangle-e^{-(\alpha-ab)s}\langle f,X_s\rangle.$$
Take it to the \eqref{martingale1}, we obtain the desired result.
\end{proof}

Let $p=(p_1,...,p_d)\in \mathbb{Z}_+^d$, recall that $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$. Define
$$H_t^p:=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.$$

\begin{lemma}\label{lemma26}
$\{H_t^p: t\geq0\}$ is a martingale with respect to $\mathcal{F}_t$. If $\alpha\beta>|p|b(1+\beta)$, then for any $0\leq \gamma<\beta$, we have $\sup_t\|H_t^p\|_{1+\gamma}< \infty$. Thus the limit
$$H_{\infty}^p:=\lim_{t\rightarrow \infty}H_t^p$$
exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
\end{lemma}
\begin{proof}
    By taking $a=|p|$ and $f=\phi_p$ in Lemma \ref{lemma25}, we get $\{H_t^p, \mathcal{F}_t:t\geq 0\}$ is a martingale.

    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that $\alpha\gamma_0>|p|(1+\gamma_0)b$. Using  Lemma \eqref{lemma24} and the fact $\kappa(\phi_p)=|p|$, we get that
    $$\|H_t^p\|_{1+\gamma_0}\leq Ce^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C,$$
    where $C$ is a constant. For any $0\leq\gamma<\gamma_0$, by the concave of function $h(x)=x^{(1+\gamma)/(1+\gamma_0)}$, 
    $$\mathbb{P}_{\mu}|H_t^p|^{1+\gamma}\leq(\mathbb{P}_{\mu}|H_t^p|^{1+\gamma_0})^{\frac{1+\gamma}{1+\gamma_0}}<\infty.$$
    Hence the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicate the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ an almost sure.
\end{proof}

Recall that $\|X_t\|=\langle 1,X_t\rangle$. By Lemma \eqref{lemma26}, it is not to hard to prove that, under $\mathbb{P}_{\mu}$, the process $W_t=e^{-\alpha t}\|X_t\|$ is a positive martingale satisfying
$$\lim_{t\rightarrow \infty} W_t= W_{\infty}$$
$\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. So $W_{\infty}$ is non-degenerate and the $(1+\gamma)$-th moment is finite. Moreover, we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D$ which is the extinction event.
\begin{lemma}\label{lemma27}
 For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have 
 $$\|W_t-W_s\|_{1+\gamma}\leq C e^{-\alpha s/2},$$
 for some C just depending on $\gamma$.
\end{lemma}

\begin{proof}
    Let $n\in \mathbb{N}$, in Lemma \eqref{lemma23}, we take $t=n+k,g=1$, then $\kappa(g)=0$, moreover, the following inequality holds.
    $$ \mathbb{P}_{\mu}\left|e^{\alpha k}\|X_n\|-e^{\alpha(k+1)}\|X_{n-1}\|\right|^{1+\gamma}\leq C_1 e^{\alpha(n+k)}e^{\alpha\gamma k}.$$
    Dividing both sides by $e^{\alpha(n+k)(1+\gamma)}$, we get
    $$\mathbb{P}_{\mu}\left|W_n-W_{n-1}\right|^{1+\gamma}\leq C_1 e^{-\alpha \gamma n}.$$
    For any $m\in \mathbb{N}$ and $m<n$, 
    $$\|W_n-W_m\|_{1+\gamma}\leq \sum_{k=m}^{n-1}\|W_{k+1}-W_k\|_{1+\gamma}\leq C_1\sum_{k=m}^{n-1}e^{-\frac{\alpha\gamma(k+1)}{1+\gamma}}\leq C e^{-\frac{\alpha\gamma m}{1+\gamma}}\leq C e^{-\frac{\alpha m}{2}}.$$
    Where $C,C_1$ are constant just depending $\gamma$.
 When we take any $0\leq s\leq t$,there will appear two terms corresponding to the interval $[s,[s]+1]$ and $[[t],t]$, which are  handled by using Remark \ref{remark2} with the same method, then we complete our proof.
\end{proof}

\begin{lemma}\label{lemma28}
  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C>0$ and $\delta>0$ such that 
  $$\mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq C e^{-\delta t},\quad t\geq 0.$$
\end{lemma}

\begin{proof}
    First, for any $\delta_1>0$, using Markov inequality, we get
    $$\mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\delta_1)t})\leq e^{-\delta_1 t}.$$ 
    For another side, let $\{(Z_t)_{t\geq 0}, \mathbb{P}^{\ast}_{\mu}\}$ be the backbone process of $X$. we know that $Z$ is a branching OU-process with initial configuration $\mu$. in which individuals, from the moment of birth, live for an independent and exponentially distributed period of time with parameter $\beta^{\ast}=\psi'(\alpha^{\ast})>0$ during which they move according to the OU-process issued from their position of birth and at death the give birth at the same position to an independent number of offspring with generator $F(s)=(1/\alpha^{\ast})\psi(\alpha^{\ast}(1-s))$ (see \cite{BAM} for further information about backbone decomposition.)

    Using \cite[Fact 1.8]{MM}, we have
    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq\mathbb{P}^{\ast}_{\mu}\left(\|Z_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right) \leq C_1 e^{-\delta_2\epsilon t}, $$
   For some $C,\delta_2>0$.  We get the desired result.
\end{proof}

\subsection{Parameter $m_k[g]$}
 In this subsection, we will introduce an important parameter $m_k[g]$ which is a parameter of $(1+\beta)$-stable distribution. Recall the definition of $Z_f(x)$
 $$Z_f(x)=\int_0^1 T^{\alpha}_{1-s}(-iT_s^{\alpha}f)^{1+\beta}(x)~ds,$$
 Let
 \begin{align}
      m_k[g]:=e^{-\alpha(k+1)}\langle Z_{g_k},\varphi\rangle.
 \end{align}
\begin{lemma}\label{mgineq1}
There exists $R\in \mathcal{P}$ and constant $C>0$ such that for any $k\in \{0,1,...,t\}$, we have 
$$|m_k[g]|\leq C e^{(\alpha\beta-\kappa(g)b(1+\beta))k}.$$
\end{lemma}
\begin{proof}
    By \eqref{zineq2} and simply calculating, we obtain the result.
\end{proof}

$m_k[g]$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Notice that, 
$$m_k[g]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}(-iT_{s+k}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx.$$
Using Fubini's Theorem and the fact $\varphi(x)$ is an invariant measure of $T$, we get  
\begin{align}
    m_k[g]&=\int_{\mathbb{R}^d}\int_0^1 e^{-\alpha(k+s)}(-iT_{s+k}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx\nonumber\\
    &=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx.\label{mkeq}
\end{align}

Next, we describe the parameter of limiting distribution in the critical case. Let 
$$\phi(x)=\sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle\phi_p(x)$$
i.e. $\phi$ is the projection of $g$ onto the $\kappa(g)$-eigenspace.
\begin{lemma}\label{lemma210}
Let $g \in \mathcal{P}$, $\kappa(g)\geq 1$ and $\alpha\beta=\kappa(g)b(1+\beta)$, then the following limit exists:
\begin{align}
    \tilde{m}[g]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{t}m_k[g]=\langle(-i\phi)^{1+\beta},\varphi\rangle.
\end{align}
\end{lemma}

\begin{proof}
    We want to show the gap between $m_k[g]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$, 
    $$|m_k[g]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}\left|(-i T^{\alpha}_s g)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
    As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(g)bt}$,  $\kappa(g)=\kappa(\phi)$ and $\kappa(g-\phi)\geq \kappa(g)+1$. The inequality \eqref{semigroupineq} yields that for some $R_1\in\mathcal{P}$ we have
    \begin{align*}
        &|T_s^{\alpha}g|\leq e^{(\alpha-\kappa(g)b)s}R_1(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(g)b)s}R_1(x), \\ 
        &|T_s^{\alpha}(g-\phi)|\leq e^{(\alpha-(\kappa(g)+1)b)s}R_1(x), \quad s\geq0.
    \end{align*}
  Using the element inequality \eqref{element} and the condition $\alpha\beta=\kappa(g)b(1+\beta)$, we get
    $$|m_k[g]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R(x)~ds~\varphi(x)~dx\leq C e^{-bk},$$
    for some $R\in\mathcal{P}$ and constant $C$.

    Therefore, the limits of $(1/t)\sum_{k=0}^tm_k[g]$ is the same with that of $(1/t)\sum_{k=0}^tm_k[\phi]$. What's more
    \begin{align*}
        m_k[\phi]&=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}\phi)^{1+\beta}(x)~ds~\varphi(x)~dx\\
        &=\int_{\mathbb{R}^d}(-i\phi(x))^{1+\beta}\varphi (x)~dx=\langle (-i\phi)^{1+\beta},\varphi\rangle.
    \end{align*}
    The second equality holds as $T_s\phi=e^{-\kappa(g)bs}\phi$. Hence
    $$\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{t}m_k[g]=\langle(-i\phi)^{1+\beta},\varphi\rangle.$$
\end{proof}

For the small branching rate case: $\alpha\beta<\kappa(g)b(1+\beta)$.
\begin{lemma}\label{lemma211}
Assume $\alpha\beta<\kappa(g)b(1+\beta)$, if $\kappa(g)\geq 1$, the series $\sum_{k=0}^{\infty}m_k[g]$ is absolutely convergent, hence we can define
\begin{align}
    m[g]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)ds\varphi(x)dx \label{msmallcase}
\end{align}
\end{lemma}
\begin{proof}
    By Lemma \ref{mgineq1}, we have $|m_k[g]|\leq C e^{(\alpha\beta-\kappa(g)b(1+\beta))k}$, for some $C>0$, which implies $\sum_{k=0}^{\infty}|m_k[g]|<\infty$ as $\alpha\beta<\kappa(g)b(1+\beta)$. Hence
    $$m[g]:=\sum_{k=0}^{\infty}m_k[g]=\sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)ds\varphi(x)dx$$
     Moreover, the right side series are also absolutely convergence, since $|e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)|\leq e^{(\alpha\beta-\kappa(g)b(1+\beta))s}R(x)$ for some $R \in \mathcal{P}$.

     Those means the equation \eqref{msmallcase} hold.
\end{proof}

\section{Proof of main results}

In this section, we will prove the main results of this paper. Let $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
 \begin{lemma}\label{lemma31}
 Assume that $\alpha\beta\leq \kappa(g)b(1+\beta)$, let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}}$, then for any  $k\in\mathbb{N}$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
 \begin{align}
      \frac{M_k^t[g]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{align}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[g]\right].$$
 \end{lemma}
\begin{proof}
    Recall that $w_{g_k}(x,\theta)=w_{g_k}(x,1,\theta),\tilde{w}_{g_k}(x,\theta)=\tilde{w}_{g_k}(x,1,\theta)$. For any $k\in\mathbb{N}$ and $t>k$, we have
    \begin{align*}
        \mathbb{\tilde{P}}_{\mu}&[\exp(i\theta\frac {M_k^t[g]}{F_k(X_{t-k-1})})]\\
        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[g]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\nu}\left[\exp\left(i\frac{\theta}{F_k(v)}(\langle T_k^{\alpha}g,X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle)\right)\right]_{\nu=X_{t-k-1}}\right]\\
        &=\mathbb{\tilde{P}}_{\mu}\left[\exp\left(\langle w_{g_k}(\cdot,\frac{\theta}{F_k(X_{t-k-1})}),X_{t-k-1}\rangle-i\frac{\theta}{F_k(X_{t-k-1})}\langle T_{k+1}^{\alpha}g, X_{t-k-1}\rangle\right)\right].
    \end{align*}
    Our aim now is showing that the on the event $\mathcal{A}_{t-k-1}$, the characteristic functions of random variables on both sides in \eqref{limitdistribution1} are much the same. Let $c=|\theta e^{\alpha}m_k[g]|$, $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. Then
    \begin{align*}
        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right|\\
        &=\bigg|\big(\mathbb{\tilde{P}}_{\mu}\exp(\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\\
        &-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\big)\mathbbm{1}_{\mathcal{A}_{t-k-1}}\bigg|\\
        &\leq e^c\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]\\
        &+e^c\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]=I+II.
    \end{align*}
    The first equation holds because that $w_{g_k}-i\theta T_1^{\alpha}g_k=w_{g_k}-\tilde{w}_{g_k}+Z_{g_k}$. the inequality holds by mean value theorem and triangular inequality.

    Using the Lemma \ref{lemma2}, there exists $p>1+\beta$ and $R \in \mathcal{P}$ such that, for any $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}$, we have 
    \begin{align*}
        I&\leq \left(\frac{|\theta|e^{(\alpha-\kappa(g)b)k}}{(e^{\alpha k}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\right)^p\mathbb{\tilde{P}}_{\mu}\langle R,X_{t-k-1}\rangle\\
        &\leq C |\theta|^p e^{-\frac{p\alpha(t-k-1)}{1+\beta}}e^{\frac{p\epsilon(t-k-1)}{1+\beta}}\mathbb{\tilde{P}}_{\mu}\langle R,X_{t-k-1}\rangle\\
        &\leq C |\theta|^p e^{\alpha(t-k-1)}e^{-\frac{p\alpha(t-k-1)}{1+\beta}}e^{\frac{p\epsilon(t-k-1)}{1+\beta}},\quad \theta\in \mathbb{R},
    \end{align*}
    for some constant $C$. Since $\alpha(\frac{p}{1+\beta}-1)>0$, we can chose $\epsilon>0$ such that there exists $C_1,\delta_1>0$ satisfying  
    \begin{align}
        I\leq C_1|\theta|^p e^{-\delta_1(t-k)}, \quad k\in \mathbb{N}, t>k, \theta \in \mathbb{R}.\label{lemma31q}
    \end{align}

    For part $II$, notice that $\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle=\theta^{1+\beta}e^{-\alpha k}\frac{\langle Z_{g_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|} \rangle$ and $\theta^{1+\beta}e^{\alpha}m_k[g]=\theta^{1+\beta}e^{-\alpha k}\langle Z_{g_k},\varphi\rangle$. Therefore,
\begin{align}
    II&=e^c|\theta|^{1+\beta}e^{-\alpha k}\mathbb{\tilde{P}}_{\mu}\left[\left|\frac{\langle Z_{g_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{g_k},\varphi\rangle\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]\nonumber\\
    &\leq e^c|\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}\mathbb{\tilde{P}}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
\end{align}
    where $h_k=Z_{g_k}-\langle Z_{g_k}, \varphi\rangle$. To estimate $h_k$, we claim that for any $f \in \mathcal{P}$, $T_t f$ is differential and $\frac{\partial (T_t f)}{\partial x_i} \in \mathcal{P}, i=1,...,d$. We firstly admit the claim and continue our proof.
    \begin{align*}
        h_k(x)&=\int_{\mathbb{R}^d}(Z_{g_k}(x)-Z_{g_k}(y))\varphi(y)~dy\\
        &\leq\int_{\mathbb{R}^d} \sup|\nabla Z_{g_k}(z)||x-y|\varphi(y)~dy.
    \end{align*}

    Let $\tilde{g}=T_1^{\alpha}g $, then $\tilde{g}$ differentiable. For any $i \in \{1,...,d\}$,
    $$\frac{\partial}{\partial x_i}Z_{g_k}(x)=\int_0^1 T^{\alpha}_{1-s}\left(\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha} \tilde{g})^{1+\beta}\right)(x)~ds$$
    Using the inequality \eqref{semigroupineq} and the fact $\kappa\left(\frac{\partial \tilde{g}}{\partial x_i}\right)\geq \kappa(\tilde{g})-1$, see \cite[Lemma 2.3]{RSZ}, we get that there exists $R_1 \in \mathcal{P}$ such that, for any $k\in \mathbb{N}$,
    \begin{align*}
        \left|\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha}\tilde{g})^{\beta}\right|&=\left|(1+\beta)(-i T_{s+k-1}^{\alpha}\tilde{g})^{\beta}(-i e^{-b(s+k-1)}T_{s+k-1}^{\alpha}\left(\frac{\partial \tilde{g}}{\partial x_i}\right))\right|\\
        &\leq e^{(\alpha-\kappa(\tilde{g})b)(s+k-1)(1+\beta)}R_1(x).
    \end{align*}

    What's more, $T_1 g(x)=\sum_{|p|\geq\kappa(g)}\langle g,\phi_p\rangle e^{-b|p|}\phi_p$, thus $\kappa(\tilde{g})=\kappa(g)$. Therefore, there exists $R_2 \in \mathcal{P}$ such that for any $k\in \mathbb{N}$,
    $$\left|\frac{\partial}{\partial x_i}Z_{g_k}(x)\right|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}R_2(x),\quad x\in \mathbb{R}^d. $$
    Hence
\begin{align}
    |h_k(x)|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}(R_2(x)(|x|+C)),\quad  x\in \mathbb{R}^d, k\in\mathbb{N},
\end{align}

for some constant $C$. Denote $R_3=R_2(x)(|x|+C)$, we notice that $\kappa(R_3)=\kappa(R_2(x)(|x|+C))\geq1$. Therefore, for $\theta\in \mathbb{R}^d$, $k\in\mathbb{N}$ and $t>k$,
\begin{align*}
  \mathbb{\tilde{P}}_{\mu}\left[|\langle h_k,X_{t-k-1}\rangle\right|]&\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}\langle T_{t-k-1}^{\alpha}R_3,\mu\rangle\\
  &\leq C_1|\theta|^{1+\beta} e^{(\alpha-\kappa(g)b)(1+\beta)k}e^{(\alpha-b)(t-k-1)}.
\end{align*}
 The last inequality holds as \eqref{semigroupineq}. Now combine with \eqref{II1}, we can chose $\epsilon$ just depending $b$ such that, 
\begin{align}
    II\leq C_2|\theta|^{1+\beta} e^{-(b-\epsilon)(t-k)}\leq C_2e^{-\delta_2(t-k)},\quad k\in\mathbb{N},t>k,\theta\in\mathbb{R}\label{lemma32q}
\end{align}
for some $C_2,\delta_2>0$.

At last, Using Lemma \ref{lemma28}, on the event $\mathcal{A}^c_{t-k-1}$, we get

\begin{align}
    \left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbbm{1}_{\mathcal{A}^c_{t-k-1}}\right|&\leq C_3\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})\nonumber\\
    &\leq C_3 e^{-\delta_3(t-k)},\label{lemma33q}
\end{align}
Combine with \eqref{lemma31q},\eqref{lemma32q} and \eqref{lemma33q}, by letting $t \rightarrow \infty$, We obtain the desired result. 
\end{proof}

Now we will prove the claim mentioned in Lemma \ref{lemma31}.

\begin{proof}[Proof of claim:] Let $\sigma_t^2=\sigma^2(1-e^{-2bt})$, then we get
\begin{align*}
    T_t f(x)= \int_{\mathbb{R}^d}f(y)\left(\frac{b}{\pi \sigma_t^2}\right)^{\frac{d}{2}} \exp\left(-\frac{b}{\sigma_t^2}(y-xe^{-bt})^2\right)dy=f\ast\varphi_t(xe^{-bt})
\end{align*}
where $\varphi_t(x)=\left(\frac{b}{\pi \sigma_t^2}\right)^{\frac{d}{2}} \exp\left(-\frac{b}{\sigma_t^2}x^2\right)$, which is belong to $C^{\infty}$. Hence $  T_t f(x)$ also belong to $C^{\infty}$. On the other hand, by calculating, we get
\begin{align*}
    \frac{\partial}{\partial x_i}T_t f(x)&=\int_{\mathbb{R}^d}f(y)\frac{\partial}{\partial x_i}\left(\varphi_t(xe^{-bt}-y)\right)dy\\
    &=e^{-bt}\int_{\mathbb{R}^d}\frac{\partial \varphi_t}{\partial x_i}(y)f(xe^{-bt}-y)dy\\
    &=\frac{-2bx_i}{\sigma_t^2}e^{-bt}T_t f(x)\in \mathcal{P}.
\end{align*}
\end{proof}
\begin{remark}
   i) For any $k\in\mathbb{N}$, $e^{\theta^{1+\beta}e^{\alpha}m_k[g]}$ is the characteristic function of some $1+\beta$-stable distribution, hence $|e^{\theta^{1+\beta}e^{\alpha}m_k[g]}|\leq 1$.

   ii) the parameters $\delta_1,\delta_2, \delta_3$ in Lemma \ref{lemma31} are just depending on $b,\beta$.
\end{remark}

\begin{corollary}\label{corollary31}
Let $\Theta>0$, assume that $\alpha\beta\leq\kappa(g)b(1+\beta)$. There exists $C,\delta>0$ such that for any $n \in \{0,...,t\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
\begin{align*}
    \left|\mathbb{\tilde{P}}_{\mu}\left(\prod_{k=0}^n\exp(i\theta_k \frac {M_k^t[g]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}})-\prod_{k=0}^n\exp(\theta_k^{1+\beta}e^{\alpha}m_k[g])\right)\right|\leq Ce^{-\delta(t-n)}
\end{align*}
\end{corollary}
\begin{proof}
    Denote $\gamma_{t,k}=\frac {M_k^t[g]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}} $, we define 
    $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[g]\right)\mathbb{\tilde{P}}_{\mu}\left(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\right)$$
    for $k\in\{-1,...,n\}$, if $k=-1$, the product is one. Then Conditioning with $\mathcal{F}_{t-k-1}$ we get
    \begin{align*}
        \varphi^{k-1}_t(\theta_0,...,\theta_n)-&\varphi^{k}_t(\theta_0,...,\theta_n)=\prod_{l=0}^{k-1}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[g]\right)\\
        &\mathbb{\tilde{P}}_{\mu}\left[\left(\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[g]}\right)\prod_{l=k+1}^n\exp(i\theta_l \gamma_{t,l})\right]
    \end{align*}
    Hence,
    \begin{align*}
        \left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| \leq \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[g]}\right|.
    \end{align*}
    If we have proved that there exists $C,\delta>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,t\}$,
    \begin{align}
        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\leq C e^{-\delta(t-k)},
    \end{align}
    we completed our proof, as the left side of thesis of the lemma is equal to $\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|$.

    Recall that 
    $$\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)=\exp(\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle).$$
    In Lemma \ref{lemma31}, we have proved that (see \eqref{lemma31q} and \eqref{lemma32q}), if $|\theta|\leq\Theta$ and $k\in\{0,...,t\}$,
    \begin{align*}
        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_1 e^{-\delta_1 (t-k)}\\
        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_1 e^{-\delta_1(t-k)}
    \end{align*}
for some $C_1,\delta_1>0$. Define 
\begin{align*}
    \mathcal{B}_{t-k-1}:=\left\{\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\leq C_1 e^{-\frac{\delta_1}{2}(t-k)}\right\}.
\end{align*}
Applying Markov's inequality, we get $\mathbb{\tilde{P}}_{\mu}(\mathcal{B}_{t-k-1})\geq 1- e^{-\frac{\delta_1}{2}(t-k)}$. Similarly, define
\begin{align*}
    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\leq C_1 e^{-\frac{\delta_1}{2}(t-k)}\right\},
\end{align*}
 which satisfies  $\mathbb{\tilde{P}}_{\mu}(\mathcal{C}_{t-k-1})\geq 1- e^{-\frac{\delta_1}{2}(t-k)}$.

Hence, for any $k\in\{0,...,t\}$, on the event $\mathcal{A}_{t-k-1}\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1}$, we get
\begin{align*}
   &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\\
   &\leq \left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|
   +\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\\
   &\leq 2C_1 e^{-\frac{\delta_1}{2}(t-k)},
\end{align*}
on the event $(\mathcal{A}_{t-k-1}\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1})^c$, we get
\begin{align*}
    &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\\
    &\leq 2(\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1}))\\
    &\leq C e^{-\delta(t-k)},
\end{align*}
for some $C_2,\delta_2>0$.
\end{proof}

In next three subsection, we just use $C$ as a constant positive real number, which may be different in different formula.
\subsection{Proof of Theorem \ref{Theorem12}}

    Recall that $\langle g,X_t\rangle=\sum_{k=0}^t M_k^t[g]$, we write
    \begin{align*}
        (t\|X_t\|)^{-\frac{1}{1+\beta}}\langle g,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} (t\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[g]+\sum_{\lceil t-\ln t \rceil}^t (t\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[g]\\
        &=I_t+J_t.
    \end{align*}
    Denote
    $$\tilde{I}_t=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{M_k^t[g]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
    Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get
    \begin{align*}
        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}-\exp\left(\theta^{1+\beta}\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[g]\right)\right|\leq C \frac{1}{t^{\delta}},
    \end{align*}
    for some $C,\delta>0$. Hence we obtain that $\tilde{I}_t\rightarrow\eta_1$ as $t\rightarrow \infty$, by using Lemma \ref{lemma210}.

    Therefore, to prove this theorem ,we just to prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\rightarrow 0$ and $J_t\rightarrow^d 0$.

    Denote
    \begin{align*}
        Y_{t,k}=\exp\left(i\theta\frac{M_k^t[g]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{M_k^t[g]}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
    \end{align*}

    Using the element inequality $|\prod x_i-\prod y_i|\leq\sum |x_i-y_i|$ for $x_i,y_i \in \mathbb{C}$ with $|x_i|,|y_i|\leq 1$, we get
    \begin{align*}
        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}|Y_{t,k}|.
    \end{align*}
    Recall Lemma \ref{lemma27}, define
    \begin{align*}
        \mathcal{D}_{t,k}:=\left\{|W_t-W_{t-k-1}|\leq C e^{-\frac{\alpha}{4}(t-k-1)}, W_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\},
    \end{align*}
    then follow Lemma \ref{lemma27} and Lemma \ref{lemma28}, we get
    \begin{align*}
        \mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)&\leq \mathbb{\tilde{P}}_{\mu}(|W_t-W_{t-k-1}|\geq C e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(W_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),\\
        &\leq C e^{-\delta(t-k-1)}
    \end{align*}
    for some $C,\delta>0$. Hence
    \begin{align}
        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbbm{1}_{\mathcal{D}^c_{t,k}}\leq 2 C e^{-\delta(t-k-1)}.\label{thm121}
    \end{align}

    Using the element inequality $|e^{ix}-e^{iy}|\leq|x-y|$,
    \begin{align*}
        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbbm{1}_{\mathcal{D}_{t,k}}&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\left|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\right|\mathbbm{1}_{\mathcal{D}_{t,k}}\\
        &\leq|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbbm{1}_{\mathcal{D}_{t,k}}.
    \end{align*}
    When $t$ is large enough, $t^{-\frac{1}{1+\beta}}\leq 1$. What's more, by Lemma \ref{lemma23}
    $$\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k},$$
for some constant $C \geq 0$ and any $0\leq\gamma<\beta$.
We denote
$$K_{t,k}:=\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbbm{1}_{\mathcal{D}_{t,k}}.$$
 On the event $\mathcal{D}_{t,k}$, by mean value theorem of integrals, we get
 \begin{align*}
     \left|W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}\right|\leq \max \left\{W_t^{-\frac{\beta}{1+\beta}},W_{t-k-1}^{-\frac{\beta}{1+\beta}}\right\}\left|W_t-W_{t-k-1}\right|,
 \end{align*}
 what's more, 
 \begin{align*}
     W_t\geq W_{t-k-1}-C e^{-\frac{\alpha}{4}(t-k-1)}&\geq\min\{\|\mu\|,C\}\left(e^{-\frac{\alpha}{32}(t-k-1)}-e^{-\frac{\alpha}{4}(t-k-1)}\right)\\
     &\geq C e^{-\frac{\alpha}{16}(t-k-1)}.
 \end{align*}
Hence, 
\begin{align*}
    \left|W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}\right|&\leq C \max\left\{e^{\frac{\alpha}{16}(t-k-1)}, e^{\frac{\alpha}{32}(t-k-1)}\right\}e^{-\frac{\alpha}{4}(t-k-1)}\\
    &\leq C e^{-\frac{3\alpha}{16}(t-k-1)},
\end{align*}
\begin{align*}
    \left|W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}\right|\geq C e^{-\frac{3\alpha}{32}(t-k-1)}.
\end{align*}
This is to say on the event $\mathcal{D}_{t,k}$, we get $K_{t,k}\leq C e^{-\frac{3\alpha}{32}(t-k-1)}$. Moreover, recall that $\alpha\beta=\kappa(g)(1+\beta)b$, we get
\begin{align}
    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbbm{1}_{\mathcal{D}_{t,k}}&\leq C e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
    &\leq C e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}.\nonumber
\end{align}

Now we take $\gamma$ so close to $\beta$ such that $\frac{1}{1+\gamma}-\frac{1}{1+\beta}<\frac{1}{32}$, then 
\begin{align}
     \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbbm{1}_{\mathcal{D}_{t,k}}\leq  e^{-\frac{\alpha}{16}(t-k)}.\label{thm122}
\end{align}
At last, combining \eqref{thm121} and \eqref{thm122}, we get 
$$\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\leq C t^{-\delta},$$
for some $C,\delta>0$, which tend to zero, as $t\rightarrow \infty$.

Next, we will prove $J_t \rightarrow^d 0$ as $t\rightarrow \infty$, this is to say
\begin{align*}
    \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\rightarrow 0.
\end{align*}

Let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|t^{-1/2}e^{\alpha t}\}$. Recall that branching OU-process $\{Z,\mathbb{P}^{\ast}\}$ is the backbone process corresponding to $X$. Therefore, by using the fact 1.8 in \cite{MM}
\begin{align}
    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq\mathbb{P}^{\ast}(\|Z_t\|\leq\|\mu\|t^{-1/2}e^{\alpha t})\leq C t^{-\delta}, \quad t\geq0,\label{Theorem123}
\end{align}
for some $C,\delta>0$. Hence $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\mathbbm{1}_{\mathcal{E}^c_{t,k}}\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ct^{-\delta}$.

On the event $\mathcal{E}_t$, by using the element inequality $|e^{i z}-1|\leq |z|$,
\begin{align*}
    \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|&\leq|\theta| \mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t \left(t\|X_t\|\right)^{-\frac{1}{1+\beta}}M_k^t[g]\right|\\
    &\leq t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t M_k^t[g]\right|.
\end{align*}
By the triangle inequality and Lemma \ref{lemma23}, for any $\gamma\in[0,\beta)$, we know that
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t M_k^t[g]\right|&\leq \sum_{k=\lceil t-\ln t \rceil}^t \|M_k^t[g]\|_{1+\gamma}\leq\sum_{k=\lceil t-\ln t \rceil}^t C_{\gamma}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}\\
    &=\sum_{k=\lceil t-\ln t \rceil}^t C_{\gamma}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}\leq C_{\gamma}e^{\frac{\alpha}{1+\beta}}t^{-\alpha(\frac{1}{1+\beta}-\frac{1}{1+\gamma})}.
\end{align*}
Hence, on the event $\mathcal{E}_t$
\begin{align*}
    \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\leq C_{\gamma}t^{-\alpha(\frac{1}{1+\beta}-\frac{1}{1+\gamma})} t^{-\frac{1}{2(1+\beta)}}
\end{align*}
We take $\gamma$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})$ smaller than $\frac{1}{2(1+\beta)}$ and combine with \eqref{Theorem123}, we proved that $J_t \rightarrow^d 0$ as $t\rightarrow \infty$.

\subsection{Proof of Theorem \ref{Theorem11}}
For any $g\in \mathcal{P}$, $g=\sum_{|p|\geq \kappa(g)}\langle g,\phi_p\rangle_\varphi \phi_p$. Therefore, we have the decomposition.
\begin{align*}
    &e^{-(\alpha-\kappa(g)b)t}\langle g,X_t\rangle=I_t+J_t\\
    &=e^{-(\alpha-\kappa(g)b)t}\sum_{|p|= \kappa(g)}\langle g,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle+e^{-(\alpha-\kappa(g)b)t}\sum_{|p|> \kappa(g)}\langle g,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle
\end{align*}
By Lemma \ref{lemma26}, we easily get that 
\begin{align*}
    I_t \rightarrow \sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle_{\varphi} H_{\infty}^p  \quad as~ t\rightarrow \infty
\end{align*}
$\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for any $0\leq \gamma<\beta$. Thus, we just prove that $J_t$ tend to zero by this two ways.

{\em Convergence in $L^{1+\gamma}(\mathbb{P}_{\mu})$}:
Let
\begin{align*}
    \tilde{g}=\sum_{|p|> \kappa(g)}\langle g,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle
\end{align*}
By the definition of $\kappa(g)$, we know that $\kappa(\tilde{g})\geq \kappa(g)+1$. What's more, $J_t=e^{-(\alpha-\kappa(g)b)t}\langle \tilde{g},X_t\rangle$. 
Using Lemma\ref{lemma24}, for some constant $C$, we get

1) when $\alpha\gamma>\kappa(\tilde{g})(1+\gamma)b$
\begin{align*}
    \|J_t\|_{1+\gamma}\leq C e^{-(\alpha-\kappa(g)b)t}e^{(\alpha-\kappa(\tilde{g})b)t}\leq C  e^{-(\alpha-\kappa(g)b)t}e^{(\alpha-(\kappa(g)+1)b)t}=C e^{-bt}
\end{align*}

2) when $\alpha\gamma=\kappa(\tilde{g})(1+\gamma)b\geq (\kappa(g)+1)(1+\gamma)b$
\begin{align*}
     \|J_t\|_{1+\gamma}\leq C t e^{-(\alpha-\kappa(g)b)t}e^{\frac{\alpha}{1+\gamma}t}\leq C t e^{-bt}
\end{align*}

3) when $\alpha\gamma>\kappa(\tilde{g})(1+\gamma)b\geq (\kappa(g)+1)(1+\gamma)b$
\begin{align*}
    \|J_t\|_{1+\gamma}\leq C e^{-(\alpha-\kappa(g)b)t}e^{\frac{\alpha}{1+\gamma}t}\leq C e^{-bt}
\end{align*}
In conclusion, $\lim_{t\rightarrow \infty}\|J_t\|=0$.

{\em Almost sure convergence}: We recall the martingale defined in Lemma \ref{lemma25}. Let 
$$L_t^{f,a}:=\int_0^t e^{-(\alpha-ab)s}\langle \bar{f},X_s\rangle ds.$$
We take $a=\kappa(g)+\frac{1}{2}$ and $f=\tilde{g}$ into this martingale and get
\begin{align*}
    J_t=e^{-\frac{1}{2}}M_t^{\tilde{g},a}+e^{-\frac{1}{2}}L_t^{\tilde{g},a}.
\end{align*}
Equivalently, we will prove that
\begin{align*}
    e^{-\frac{1}{2}bt}M_t^{\tilde{g},a}\rightarrow 0, \quad e^{-\frac{1}{2}bt}L_t^{\tilde{g},a}\rightarrow 0 \quad as~t\rightarrow \infty
\end{align*}
$\mathbb{P}_{\mu}$-as.
We notice that $\kappa(L\tilde{g})=\kappa(\tilde{g})$, this is to say $\kappa(L\tilde{g}+ab\tilde{g})=\kappa(\tilde{g})\geq \kappa(g)+1$. Following the similar way to prove the case $L^{1+\gamma}(\mathbb{P}_{\mu})$-convergence, we get there exists some $C, \delta>0$ such that
\begin{align*}
    \|e^{-(\alpha-ab)t}\langle \tilde{g},X_t\rangle)\|_{1+\gamma}\leq C e^{-\delta t},\quad \|e^{-(\alpha-ab)t}\langle L\tilde{g}+ab\tilde{g},X_t\rangle\|_{1+\gamma}\leq C e^{-\delta t}.
\end{align*}
Therefore, $|L_t^{\tilde{g},a}|\leq Y_t^{\tilde{g},a}:=\int_0^t e^{-(\alpha-ab)s}|\langle L\tilde{g}+ab\tilde{g},X_s\rangle|ds$ satisfying
\begin{align*}
    \|L_t^{\tilde{g},a}\|_{1+\gamma}\leq\|Y_t^{\tilde{g},a}\|_{1+\gamma}\leq \int_0^t \|e^{-(\alpha-ab)s}\langle L\tilde{g}+ab\tilde{g},X_s\rangle\|_{1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
\end{align*}
As $Y_t^{\tilde{g},a}$ is positive increasing, we get that it convergence some random variable $Y_{\infty}^{\tilde{g},a}$ almost sure and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. This is to say
\begin{align*}
    \lim_{t\rightarrow \infty}e^{-\frac{1}{2}bt}|L_t^{\tilde{g},a}|\leq  \lim_{t\rightarrow \infty}e^{-\frac{1}{2}bt}|Y_t^{\tilde{g},a}|=0.
\end{align*}
On the other hand, the martingale $M_t^{\tilde{g},a}$ satisfies
\begin{align*}
    \|M_t^{\tilde{g},a}\|_{1+\gamma}\leq  \|e^{-(\alpha-ab)t}\langle \tilde{g},X_t\rangle)\|_{1+\gamma}+\|L_t^{\tilde{g},a}\|_{1+\gamma}\leq C
\end{align*}
for some constant $C$, which implies that $\lim_{t\rightarrow\infty} e^{-\frac{1}{2}bt}M_t^{\tilde{g},a}=0$. we complete our proof.
\subsection{Proof of Theorem \ref{Theorem13}}
The proof of Theorem \ref{Theorem13} is similar with that of Theorem \ref{Theorem12} or much easier. 
     We write
    \begin{align*}
        (\|X_t\|)^{-\frac{1}{1+\beta}}\langle g,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} (\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[g]+\sum_{\lceil t-\ln t \rceil}^t (\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[g]\\
        &=I_t+J_t.
    \end{align*}
    We denote
    $$\tilde{I}_t=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{M_k^t[g]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
    Taking $\theta_k=( e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, then we get
    \begin{align*}
        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}-\exp\left(\theta^{1+\beta}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[g]\right)\right|\leq C \frac{1}{t^{\delta}},
    \end{align*}
    for some $C,\delta>0$. Hence We obtain that $\tilde{I}_t\rightarrow\eta_2$ as $t\rightarrow \infty$, by using  \eqref{msmallcase}.

    Therefore, to prove the theorem ,we just to prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\rightarrow 0$ and $J_t\rightarrow^d 0$.

    We denote
    \begin{align*}
        Y_{t,k}:=\exp\left(i\theta\frac{M_k^t[g]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{M_k^t[g]}{\left(\|X_t\|\right)^{\frac{1}{1+\beta}}}\right)
    \end{align*}
With completely same method before \eqref{thm125} in the proof of Theorem \ref{Theorem12}, we can prove that
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C_1 e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}+C_2 e^{-\delta(t-k-1)}
\end{align*}
Moreover, on the case $\alpha\beta<\kappa(g)(1+\beta)b$,  $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}< - \frac{\alpha\gamma-\kappa(g)(1+\gamma)b}{1+\gamma}$, this is to say,
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C e^{-(t-k)}
\end{align*}
Then we can prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\rightarrow 0$, by following the lines of the proof in the critical case.

To prove $J_t\rightarrow^d 0$, We let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon )t}\}$ instead, for any $\epsilon>0$, we know that, see Lemma \ref{lemma28}, there exists
$C,\delta >0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal{E}_t^c)\leq C e^{-\delta t}$. What's more, for any $0\leq \gamma <\beta$, we let $p=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa(g)(1+\gamma)b}{1+\gamma}>0$, then by Lemma \ref{lemma23}, we have
\begin{align*}
    \|M_k^t[g]\|\leq \|M_k^t[g]\|_{1+\gamma}\leq C_{\gamma} e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}\leq C_{\gamma} e^{-pk}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}
\end{align*}
Then we get $  \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\rightarrow 0$ as $ t\rightarrow \infty$, by following the similar way in critical case.

\begin{thebibliography} {10}

\bibitem{EB}
Dynkin,~E.B. 
\newblock {\em Superprocesses and partial differential equations}, Ann. Probab (1993): 1185-1262.

\bibitem{AK}
Kyprianou,~A.E. 
\newblock {\em Introductory Lectures on Fluctuations of Levy Processes with Application}, Springer, Berlin(2006)

\bibitem{ZL}
Z.~Li,
\newblock {\em Measure-valued branching Markov processes}, Probability and its Applications (New York), Springer, Heidelberg, 2011. MR 2060602

\bibitem{GD}
Metafune,~G., Pallara,D.
\newblock {\em Specturm of Ornstein-Uhlenbeck operators in $\mathcal{L}^p$ space with respect to invariant measures}. J. Funct. Anal. 196, 40-60(2002)

\bibitem{RSZ}
Y.-X.Ren, R. Song, R. Zhang,
\newblock {\em Central limit theorems for super Ornstein-Uhlenbeck processes}, Acta Appl. Math. 130(2014)9-49.

\bibitem{MM}
R.Marks, P.Mil\'{o}s
\newblock {\em CLT for supercritical branching processes with heavy-tailed branching law}. arXiv preprint arXiv:1803.05491, 2018.

\bibitem{DK}
E.B.Dynkin, S.E. Kuznetsov,
\newblock {\em $\mathbb{N}$-measure  for branching exit Markov system and their applications to differential equations}, Probab. Theory Related Fields 130(2004) 135-150

\bibitem{DR}
Durrett, Rick.
\newblock {\em Probability: theory and examples}. Cambridge university press, 2010.

\bibitem{BAM}
Berestycki, J., Kyrianou, A.E., Murillo-Salas, A
\newblock{\em The prolific backbone for supercritical superprocesses}. Stoch. Proc. Appl. 121, 1315-1331(2011)

\bibitem{RSS}
Y.-X.Ren, R. Song, Z. Sun,
\newblock{\em Spine decompositions and limit theorems for a class of critical superpeocesses,} arXiv preprint arXiv:1711.09188(2017).

\end{thebibliography}

\end{document}

### 2019-01-31 supCLT.tex
supCLT.tex: version 1

@@
-\documentclass{article}
-
-\usepackage{cite}
+%%%----Versions-----------------------------
+% supCLT1.tex 2018/6/24 by Zhenyao
+% supCLT.tex 2018/6/29 by Jianjie
+%---The preamble----------------------
+\documentclass[12pt, a4paper]{amsart}
+\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
 \usepackage[utf8]{inputenc}
-\usepackage{hyperref,amsmath,amssymb,amscd}
-\usepackage{amsthm}
+\usepackage{hyperref}
+\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
+\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
+\usepackage{mathrsfs}
+\usepackage{bbm}
+\usepackage{mathtools}
+\mathtoolsset{showonlyrefs}
+\usepackage{stackrel}
 \usepackage{color}
-\usepackage{bbm}
-\usepackage{appendix} 
-\newtheorem{proposition}{Proposition}
-\newtheorem{assumption}{Assumption}
-
-\newtheorem{remark}{Remark}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{notation}{Notation}[section]
-\newtheorem{definition}{Definition}[section]
-\newtheorem{conjecture}{Conjecture}[section]
-
-\title{Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching}
-\author{Jianjie Zhao }
-
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{conj}[thm]{Conjecture}
+\theoremstyle{definition}
+\newtheorem{rem}[thm]{Remark}
+\newtheorem{exa}[thm]{Example}
+\newtheorem{asp}{Assumption}
+\numberwithin{equation}{section}
+\allowdisplaybreaks
+%---Top matter------------------------------
 \begin{document}
-%%给公式前加章节编号
-\makeatletter
-\@addtoreset{equation}{section}
-\makeatother
-\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
-
+\title
+    %{\large Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching}
+    [CLT for Super-OU processes]
+    {CLT for Super-OU Processes with stable Branching}
+\author
+    [Y.-X. Ren, Z. Sun and J. Zhao]
+    {Yan-Xia Ren, Zhenyao Sun and Jianjie Zhao}
+%---Yan-Xia Ren
+\address
+    {Yan-Xia Ren\\
+    School of Mathematical Sciences\\
+    Peking University\\
+    Beijing, P. R. China, 100871}
+\email{yxren@math.pku.edu.cn}
+\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
+%---Zhenyao Sun
+\address
+    {Zhenyao Sun\\
+    School of Mathematical Sciences\\
+    Peking University\\
+    Beijing, P. R. China, 100871}
+\email{zhenyao.sun@pku.edu.cn}
+%---Jianjie Zhao
+\address
+    {Jianjie Zhao\\
+    School of Mathematical Sciences\\
+    Peking University\\
+    Beijing, P. R. China, 100871}
+\email{???@pku.edu.cn}
+%\begin{abstract}
+%\end{abstract}
+%\subjclass[2010]{60J80, 60F05}
+%\keywords{}
+%\date{}
 \maketitle
-
+%---Contents-----------------------
 \section{Introduction}
 \subsection{Model}
-
-We first fix our notation, for a vector $x\in \mathbb{R}^d$, we denote by $|x|$  its Euclidean norm.
+%We first fix our notation, for a vector $x\in \mathbb{R}^d$, we denote by $|x|$  its Euclidean norm.
 Let $\xi=\{\xi_t : t\geq 0\}$ be an Ornstein-Uhlenbeck prcess, short for OU process, on $\mathbb{R}^d$, with infinitesimal generator $L$.
 For any $f \in C^2(\mathbb{R}^d)$,
+%\begin{equation}\label{generatior}
+%Lf(x)= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x))   
+%\end{equation}
+%where $\sigma>0$ is the diffusion parameter, $b>0$ is the drift parameters. What's more, we respectively use $\Delta$ and $\nabla$ to express the Laplace operator and gradient operator as usual.
+Let $d \in \mathbb N:= \{1,2,\dots\}$.
+For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm. 
+Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
 \begin{equation}\label{generatior}
-Lf(x)= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x))   
-\end{equation}
-where $\sigma>0$ is the diffusion parameter, $b>0$ is the drift parameters. What's more, we respectively use $\Delta$ and $\nabla$ to express the Laplace operator and gradient operator as usual.
-
-For any $x\in \mathbb{R}^d$, We denote by $\Pi_x$ the law of $\xi$ starting from $x$. The semigroup of $\xi$ will be denoted by $\{T_t: t\geq 0\}$.
-
-In this paper, we consider a branching mechanism of the form  
+    Lf(x)
+    %= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x)), 
+    = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x), 
+    \quad f \in C^2(\mathbb{R}^d), 
+\end{equation}
+where $\sigma>0$ and $b>0$. 
+%For any $x\in \mathbb{R}^d$, We denote by $\Pi_x$ the law of $\xi$ starting from $x$. The semigroup of $\xi$ will be denoted by $\{T_t: t\geq 0\}$.
+Denoted by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
+%In this paper, we consider a branching mechanism of the form  
+%\begin{equation}\label{mechanism}
+%\psi(\lambda)=-\alpha \lambda + \lambda^{(1+\beta)}, \lambda \geq 0
+%\end{equation}
+%Where $\alpha = -\psi'(0+)>0$ and $\beta \in (0,1) $.
+Let $\psi$ be a function on $\mathbb C_+:= \{x+iy: x\in [0,\infty), y\in \mathbb R\}$ with
 \begin{equation}\label{mechanism}
-\psi(\lambda)=-\alpha \lambda + \lambda^{(1+\beta)}, \lambda \geq 0
-\end{equation}
-Where $\alpha = -\psi'(0+)>0$ and $\beta \in (0,1) $.
-
-Let $\mathcal{M}(\mathbb{R}^d)$ be the space of finite measures on $\mathbb{R}^d$.
-We say a $\mathcal{M}(\mathbb{R}^d)$-value branching Markov process $X=\{(X_t)_{t\geq 0},\mathbb{P}_{\mu}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for any $t \geq 0$, positive bounded measurable functions $f$ on $\mathbb{R}^d$ and any $\mu \in \mathcal{M}(\mathbb{R}^d)$, we have
-\begin{equation} \label{super}
-    \mathbb{P}_{\mu}(e^{-\langle f,X_t \rangle})=e^{-\langle u_f(\cdot , t), \mu \rangle},
-\end{equation}
-where  $u_f(\cdot , t)$ is the unique locally bounded positive solution to the equation
-\begin{equation}\label{eq1}
-     u_f(x , t) + \Pi_x \left( \int_0^t\psi(u_f(\xi_s,t-s))~ds\right) =\Pi_x [f(\xi_t)],
-\end{equation}
-According to \cite[section 2]{ZL}, is equivalent to
-\begin{equation}\label{eq2}
-     u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
-\end{equation}
-
-In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$.
+    \psi(z)
+    := - \alpha z + z^{1+\beta}, 
+    \quad z \in \mathbb C_+,
+\end{equation}
+where $\alpha > 0$ and $\beta \in (0,1) $.
+%Let $\mathcal{M}(\mathbb{R}^d)$ be the space of finite measures on $\mathbb{R}^d$. 
+Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of finite measures on $\mathbb{R}^d$.
+%We say a $\mathcal{M}(\mathbb{R}^d)$-value branching Markov process $X=\{(X_t)_{t\geq 0},\mathbb{P}_{\mu}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for any $t \geq 0$, positive bounded measurable functions $f$ on $\mathbb{R}^d$ and any $\mu \in \mathcal{M}(\mathbb{R}^d)$, we have
+%\begin{equation} \label{super}
+%    \mathbb{P}_{\mu}(e^{-\langle f,X_t \rangle})=e^{-\langle u_f(\cdot , t), \mu \rangle},
+%\end{equation}
+%where  $u_f(\cdot , t)$ is the unique locally bounded positive solution to the equation
+%\begin{equation}\label{eq1}
+%     u_f(x , t) + \Pi_x \left( \int_0^t\psi(u_f(\xi_s,t-s))~ds\right) =\Pi_x [f(\xi_t)],
+%\end{equation}
+%In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$.
 Put $\|\mu\|=\langle 1,\mu\rangle$.
@@
 $X$ is  supercritical.
+In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$. Put $\|\mu\|=\langle 1,\mu\rangle$.
+We say a $\mathcal{M}(\mathbb{R}^d)$-value Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
+\begin{equation} \label{super}
+    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
+    = e^{-\langle u_f(\cdot , t), \mu \rangle}, 
+    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
+\end{equation}
+where $(x,t) \mapsto u_f(x, t)$ is the unique locally bounded positive solution to the equation
+\begin{equation}\label{eq1}
+     u_f(x , t) + \Pi_x \Big[ \int_0^t\psi\big(u_f(\xi_s,t-s)\big)~ds\Big] 
+     = \Pi_x [f(\xi_t)],
+     \quad x\in \mathbb R^d, t\geq 0.
+\end{equation}
+
+%According to \cite[section 2]{Li2011Measure}, is equivalent to
+According to \cite[section 2]{Li2011Measure}, the above is equivalent to
+\begin{equation}\label{eq2}
+     u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
+\end{equation}
 
     The existence of such superprocesses is well known, see \cite{EB} for instance. 
-Let $||X_t||=\langle 1, X_t \rangle$ be the total mass of the process $X$ at time $t$, then $\{\|X_t\|; t \geq 0\}$ is a continuous-state branching process with branching mechanism $\psi$.
-The fact $\psi(\infty)=\infty$ implies that the probability of extinction event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see, for example,  \cite[section 10.2.2]{AK}.
-Let $\alpha^{\ast}$ be the larger root of $\psi=0$, we have
-$$\mathbb{P}_{\mu}\left(\lim_{t\rightarrow \infty}\|X_t\|=0\right)=e^{-\alpha^{\ast}\|\mu\|}.$$
-
-For any $f \in \mathcal{P}$, define the {\em Feyman-Kac semigroup} 
+    %Let $||X_t||=\langle 1, X_t \rangle$ be the total mass of the process $X$ at time $t$, then $\{\|X_t\|; t \geq 0\}$ is a continuous-state branching process with branching mechanism $\psi$.  
+    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. 
+    %The fact $\psi(\infty)=\infty$ implies that the probability of extinction event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see, for example,  \cite[section 10.2.2]{Kyprianou2014Fluctuations}.
+    The fact $\psi(\infty)=\infty$ implies that the probability of extinguish event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see \cite[Theorem 12.7]{Kyprianou2014Fluctuations} for example.
+    %Let $\alpha^{\ast}$ be the larger root of $\psi=0$, we have $$\mathbb{P}_{\mu}\left(\lim_{t\rightarrow \infty}\|X_t\|=0\right)=e^{-\alpha^{\ast}\|\mu\|}.$$
+    In fact, 
+\begin{equation}
+    \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
+    = e^{-\alpha^* \|\mu\|},
+\end{equation}
+    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
+
+%For any $f \in \mathcal{P}$, define the {\em Feyman-Kac semigroup}
+    Define the \emph{Fenyman-Kac semigroup} by  
 \begin{equation}\label{meansemigroup}
-    T^{\alpha}_t f(x) := \Pi_x [e^{\alpha t}f(\xi_t)], \quad x\in \mathbb{R}^d,t\geq 0,
-\end{equation}
-which is konwn as the {\em mean semigroup} of the superprocess $X$, in the sense that
+    T^{\alpha}_t f(x) 
+    := \Pi_x [e^{\alpha t}f(\xi_t)],
+    %\quad x\in \mathbb{R}^d,t\geq 0, 
+    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
+\end{equation}
+%which is konwn as the {\em mean semigroup} of the superprocess $X$, in the sense that
+    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
 \begin{equation}\label{meanformula}
-    \mathbb{P}_{\mu}[\langle f, X_t \rangle] = \langle T_t^{\alpha t}f, \mu \rangle.
-\end{equation}
-see \cite[Proposition 2.27]{ZL}.  Notice that $T^{\alpha}_t f =e^{\alpha t}T_t f$.
-
-The purpose of this paper is to establish some spatial central limit theorems for the super OU-process with stable branching \eqref{mechanism}. More precisely, consider the limit of 
-$$\frac{\langle f,X_t\rangle-\|X_t\|\langle f, \varphi \rangle}{F_t},$$
-we want to find $(F_t)_{t\geq0}$, for suitable test functions $f$, such that the former formula convergence to some non-degenerate random variable as $t\rightarrow \infty$.
-
-\subsection{OU semigroup and Eigenfunctions}
-
+    \mathbb{P}_{\mu}[\langle f, X_t \rangle] 
+    = \langle T_t^\alpha f, \mu \rangle,
+%new
+    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
+%end new
+\end{equation}
+%see \cite[Proposition 2.27]{Li2011Measure}. 
+%Notice that $T^{\alpha}_t f =e^{\alpha t}T_t f$.
+Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.
+
+%The purpose of this paper is to establish some spatial central limit theorems for the super OU-process with stable branching \eqref{mechanism}. More precisely, consider the limit of 
+%$$\frac{\langle f,X_t\rangle-\|X_t\|\langle f, \varphi \rangle}{F_t},$$
+%we want to find $(F_t)_{t\geq0}$, for suitable test functions $f$, such that the former formula convergence to some non-degenerate random variable as $t\rightarrow \infty$.
+
+%\subsection{OU semigroup and Eigenfunctions}
+\subsection{OU semigroup}
+({\bf Do we have a good reference about those following result about the OU semigroup?})
 Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
 \begin{equation}\label{invariantdensity}
-    \varphi (x) =\left (\frac{b}{\pi \sigma^2}\right )^{\frac{d}{2}}\exp \left(-\frac{b}{\sigma^2}|x|^2 \right ),\quad x\in \mathbb{R}^d.
+    \varphi (x) 
+    =\Big (\frac{b}{\pi \sigma^2}\Big )^{\frac{d}{2}}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big),\quad x\in \mathbb{R}^d.
 \end{equation}
 Let $L^2(\varphi):= \left\{ h: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
-$$\langle f_1, f_2 \rangle_{\varphi} = \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).$$
-
-For $p=(p_1,p_2,...,p_d) \in \mathbb{Z}_+^{d}$, let $|p|=p_1+...+p_d$, $p!=p_1 \cdot ...
+\begin{equation}
+\langle f_1, f_2 \rangle_{\varphi} 
+%= 
+:=
+\int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
+\end{equation}
+
+    %For $p=(p_1,p_2,...,p_d) \in \mathbb{Z}_+^{d}$, let $|p|=p_1+...+p_d$, $p!=p_1 \cdot ...
 \cdot p_n$ and $\partial x^p =\partial x_1^{p_1} \cdot ...
@@
 We recall the Hermite polynomials $H_p$ in $\mathbb{R}^d$
-
-$$H_p(x):=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{|p|}}{\partial x^p} \left ( e^{-|x|^2} \right ).$$
-It is known that, see \cite{GD} as an example, the eigenvalues of $L$ are $\{-bk: k =0,1,2,...\}$ and the eigenspace $A_k$ corresponding to $-bk$ is
-$$A_k = {\rm Span} \{\phi_p : |p|=k\},$$
+    For each $p = (p_k)_{k = 1\dots d} \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$. 
+    The Hermite polynomials are defined by
+\begin{equation}
+    H_p(x)
+    %:=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{|p|}}{\partial x^p} \left ( e^{-|x|^2} \right ).
+    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
+    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
+\end{equation}
+%It is known that, see \cite{GD} as an example, the eigenvalues of $L$ are $\{-bk: k =0,1,2,...\}$ and the eigenspace $A_k$ corresponding to $-bk$ is
+%$$A_k = {\rm Span} \{\phi_p : |p|=k\},$$
+It is known that, see \cite{GD} for example, the generator $L$ of OU process $\xi$ can be viewed as an operator 
+%on $L^2(\phi)$ 
+on $L^2(\varphi)$ 
+with eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
+For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ of this operator is
+\begin{equation}
+    A_k 
+    %= \operatorname{Span} \{\phi_p : |p|=k\},
+    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
+\end{equation}
 where
 \begin{equation}\label{eigenfunction}
-    \phi_p(x)= \frac{1}{\sqrt{p!2^{|p|}}}H_p \left(\frac{\sqrt{b}}{\sigma}x \right ),\quad x\in \mathbb{R}^d, p\in \mathbb{Z}_+^d.
-\end{equation}
- The function $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-b|p|$, and satisfies 
+	\phi_p(x) 
+    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
+    %\quad x\in \mathbb{R}^d, p\in \mathbb{Z}_+^d.
+    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
+\end{equation}
+ %The function $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-b|p|$, and satisfies 
+ It is known that 
 \begin{equation}\label{semigroupformula}
-    T_t\phi_p(x)=e^{-b|p|t}\phi_p(x),\quad x\in \mathbb{R}^d.
-\end{equation}
-Moreover, The polynomials $\{\phi_p(x)\}_{p \in \mathbb{Z}_+^d}$ form a complete orthonormal basis of $L^2(\varphi)$. Thus, for any $f\in L^2(\varphi)$, we have
-\begin{align}
-    f=\sum_{k=0}^{\infty}\sum_{|p|=k}a_p \varphi_p \quad {\rm in~} L^2(\varphi), \label{semicomp1}
-\end{align}
-where $a_p=\langle f, \phi_p \rangle_{\varphi}$. Let
+    T_t\phi_p(x)
+    =e^{-b|p|t}\phi_p(x),
+    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
+\end{equation}
+%Moreover, The polynomials $\{\phi_p(x)\}_{p \in \mathbb{Z}_+^d}$ form a complete orthonormal basis of $L^2(\varphi)$. Thus, for any $f\in L^2(\varphi)$, we have
+Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$. 
+Therefore, for each $f\in L^2(\varphi)$, 
+\begin{equation}\label{semicomp1}
+    f
+    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p, 
+    \quad \text{in~} L^2(\varphi).
+\end{equation}
+%where $a_p=\langle f, \phi_p \rangle_{\varphi}$. 
+Let
 \begin{equation}\label{order}
-    \kappa(f):=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  a_p \neq 0\right \}
+    \kappa(f)
+    %:=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  a_p \neq 0\right \}
+    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
 \end{equation}
@@
 In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
-\begin{align*}
-     \mathcal{P}:=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C, n>0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}
-\end{align*}
-
-It is easy to see that $\mathcal{P} \subset L^2(\phi)$. What's more, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$
+\begin{equation}
+     \mathcal{P}
+     %:=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C, n>0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+     :=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+\end{equation}
+%It is easy to see that $\mathcal{P} \subset L^2(\phi)$. 
+It is easy to see that $\mathcal{P} \subset L^2(\varphi)$. 
+%What's more, 
+According to \cite[Fact 1.2]{MM},
+for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
 \begin{equation}\label{semigroupineq}
-    |T_tf(x)| \leq e^{-\kappa(f)bt}R(x) 
-\end{equation}
-
-That is to say the rate of decay of the semigroup depending on $\kappa(f)$. The readers can find the prove in \cite[Fact 1.2]{MM}.
+    |T_tf(x)| \leq e^{-\kappa(f)bt}R(x).
+\end{equation}
+%That is to say the rate of decay of the semigroup depending on $\kappa(f)$. 
+%The readers can find the prove in \cite[Fact 1.2]{MM}.
 
@@
 
-Recall the branching mechanism $\psi$ and Feynman-Kac semigroup $T^{\alpha}_t$, and apply \cite[Proposition 2.9]{ZL} to \eqref{charequation}, we have that
+Recall the branching mechanism $\psi$ and Feynman-Kac semigroup $T^{\alpha}_t$, and apply \cite[Proposition 2.9]{Li2011Measure} to \eqref{charequation}, we have that
 \begin{equation}\label{chareq2}
@@
  We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0\leq\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
- \begin{theorem}\label{Theorem11}
+ \begin{thm}\label{Theorem11}
      If $g \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(g)b(1+\beta)$, then as $t\rightarrow \infty$,
@@
      Moreover, if $g$ is twice differentiable and its twice derivative $D^2 g$ satisfies $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure. 
- \end{theorem}
+ \end{thm}
 For any $t>0$, let $W_t:=e^{-\alpha t}\|X_t\|$, then $W_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $W_{\infty}:=\lim_{t\rightarrow\infty}W_t$,  $\mathbb{P}_{\mu}$-a.s.
 and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
- \begin{remark}
+ \begin{rem}
     If $\kappa(g)=0$, $\langle g, \phi_{\kappa(g)}\rangle_{\varphi}$ reduces to $\langle g,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
@@
     Moreover, if $g$ is twice differentiable and $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure. 
- \end{remark}
+ \end{rem}
 
@@
 See Lemma \ref{lemma210} for more details about $\tilde{m}[g]$.
-\begin{theorem}\label{Theorem12}
+\begin{thm}\label{Theorem12}
 Let $g\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
@@
 $$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[g]).$$
-\end{theorem}
+\end{thm}
 
@@
 In Lemma \ref{lemma211}, we will prove that $|m[g]|<\infty$.
-\begin{theorem}\label{Theorem13}
+\begin{thm}\label{Theorem13}
     If $g\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
@@
     $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(\theta^{1+\beta}m[g]).$$
-\end{theorem}
+\end{thm}
 
@@
 In this subsection, we will estimate the characteristic function of $M_k^t[g]$ near $0$. First, we will prove the following inequality which controls $w_{g_k}(x,s,\theta)$.
-\begin{lemma}\label{lemma1}
+\begin{lem}\label{lemma1}
 There exists $R \in \mathcal{P}$, such that for any $k \in \mathbb{N}$, $x\in\mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
 $$e^{-(\alpha-\kappa(g)b) s}|w_{g_k}(x,s,\theta)|\leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), \quad s\geq 0.$$
-\end{lemma}
+\end{lem}
 Recall some result about the Kuznestov measures of $\{X_t, t\geq 0\}$.
@@
 
-It's known by \cite[section 8.4]{ZL} that  one can associate with $\{\mathbb{P}_{\delta_x}:x\in\mathbb{R}^d\}$ a family of $\sigma$-finite measures $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ defined on $(\mathbb{D},\mathcal{C})$ such that $\mathbb{N}_x\{0\}=0$,
+It's known by \cite[section 8.4]{Li2011Measure} that  one can associate with $\{\mathbb{P}_{\delta_x}:x\in\mathbb{R}^d\}$ a family of $\sigma$-finite measures $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ defined on $(\mathbb{D},\mathcal{C})$ such that $\mathbb{N}_x\{0\}=0$,
 \begin{equation}\label{Nmeasure}
@@
 \end{align*}
-See \cite[Theorem 8.24]{ZL} for a proof.
+See \cite[Theorem 8.24]{Li2011Measure} for a proof.
 
@@
 \end{equation}
-See \cite[Lemma 3.3]{RSS} for example.
+See \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
 
@@
 
-\begin{lemma}\label{lemma2}
+\begin{lem}\label{lemma2}
 There exists $R \in \mathcal{P}$ and $p_1 >1+\beta$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have 
 $$|w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_1}R(x),\quad x\in \mathbb{R}^d,\theta\in \mathbb{R}.$$
-\end{lemma}
+\end{lem}
 \begin{proof}
@@
 
-\begin{corollary}\label{corollary2}
+\begin{cor}\label{corollary2}
   There exists $R \in \mathcal{P}$ such that for any $k\in\{0,1,...,t\}$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have 
@@
   \end{align}
-  \end{corollary}
+  \end{cor}
 
@@
 
-\begin{corollary}\label{corollary1}
+\begin{cor}\label{corollary1}
 There exists $R \in \mathcal{P}$ and $p_2 >1+\beta$ such that for any $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, we have 
@@
 where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R(\cdot)$.
-\end{corollary}
+\end{cor}
 
@@
 \end{proof}  
-\begin{remark}\label{remark1}
+\begin{rem}\label{remark1}
    For $0<s\leq 1$, let 
@@
    where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R(\cdot)$, for some $R\in \mathcal{P}, p>1+\beta$.
-\end{remark}
+\end{rem}
 
@@
  In this subsection, for any $\gamma \in [0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle $ by an exponential function depending on $\kappa(g)$.
-\begin{lemma}\label{lemma23}
+\begin{lem}\label{lemma23}
 For any $0\leq \gamma < \beta$ there exists a constant $C>0$ such that
@@
 for any $k \in \{0,...,t\}$.
-\end{lemma}
+\end{lem}
 
@@
     Let $C_k=e^{(\alpha-\kappa(g)b)k}$, and, for convenience, define $A:=\{|M_t^k[g]|>C_k\}$, $A_{\mu}:=\{|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\mu\rangle|>C_k\}$.
-$$\mathbb{P}_{\mu}|M_k^t[g]|^{1+\gamma}=\mathbb{P}_{\mu}|M_k^t[g]\mathbbm{1}_{A^c}|^{1+\gamma}+\mathbb{P}_{\mu}|M_k^t[g]\mathbbm{1}_{A}|^{1+\gamma}=I+II.$$
+$$\mathbb{P}_{\mu}|M_k^t[g]|^{1+\gamma}=\mathbb{P}_{\mu}|M_k^t[g]\mathbf{1}_{A^c}|^{1+\gamma}+\mathbb{P}_{\mu}|M_k^t[g]\mathbf{1}_{A}|^{1+\gamma}=I+II.$$
 For the first part,
@@
 \begin{align*}
-    II=\mathbb{P}_{\mu}\left[\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\mathbbm{1}_{A_{\nu}}\right]|_{\nu=X_{t-k-1}}\right]
+    II=\mathbb{P}_{\mu}\left[\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\mathbf{1}_{A_{\nu}}\right]|_{\nu=X_{t-k-1}}\right]
 \end{align*}
@@
     &\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\right] \label{temp1}\\ 
-    &=(1+\gamma)\int_0^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|\mathbbm{1}_{A_{\nu}}>\lambda\right)d\lambda \nonumber\\
+    &=(1+\gamma)\int_0^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|\mathbf{1}_{A_{\nu}}>\lambda\right)d\lambda \nonumber\\
     &\leq (1+\gamma)\int_{C_{k}}^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\right)d\lambda.\nonumber
 \end{align}
-Using the element inequality $\mathbb{P}(|Y|>2/u)\leq u^{-1}\int_{-u}^{u}(1-\varphi(t))dt$, see,\cite[Chaper 3]{DR}, for example, where $Y$ is a random variable corresponding to characteristic function $\varphi(t)$, $u\geq 0$, we have
+Using the element inequality $\mathbb{P}(|Y|>2/u)\leq u^{-1}\int_{-u}^{u}(1-\varphi(t))dt$, see,\cite[Chaper 3]{Durrett2010Probability}, for example, where $Y$ is a random variable corresponding to characteristic function $\varphi(t)$, $u\geq 0$, we have
 
@@
 \end{proof}
-\begin{remark}\label{remark2}
+\begin{rem}\label{remark2}
    When $t\notin \mathbb{N}$, on the interval $[\lfloor t \rfloor , t]$, similar with $M_k^t[g]$, we can define 
@@
    For some $C>0$. This can be proved by using Remark \ref{remark1} and following the same method in Lemma \ref{lemma23}.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{lemma}\label{lemma24}
+\begin{lem}\label{lemma24}
 For any $0\leq \gamma < \beta$ there exists a constant $C>0$, we have the result:
@@
 
-\end{lemma}
+\end{lem}
 \begin{proof}
@@
 
-\begin{remark}
+\begin{rem}
     The Lemma \eqref{lemma24} offers insights how to guess $\{F_t, t\geq0\}$ raised in Introduction. indeed
@@
     Small branching rate: when $\alpha\gamma < \kappa(g)(1+\gamma)b$, $F_t\approx e^{\frac{\alpha t}{1+\beta}}\approx \|X_t\|^{\frac{1}{1+\beta}}$.
-\end{remark}
+\end{rem}
 \subsection{Martingales}
@@
 Where $\bar{f}=(L+ab)f$. The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathcal{F}_t\}_{t\geq 0}$.
-\begin{lemma}\label{lemma25}
+\begin{lem}\label{lemma25}
 For any $a \in \mathbb{R}$ and $f\in\mathcal{P}$ such that $L f\in\mathcal{P}$, Then $\{M_t^{f,a},\mathcal{F}_t:t\geq 0\}$ is a martingale.
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{lemma}\label{lemma26}
+\begin{lem}\label{lemma26}
 $\{H_t^p: t\geq0\}$ is a martingale with respect to $\mathcal{F}_t$. If $\alpha\beta>|p|b(1+\beta)$, then for any $0\leq \gamma<\beta$, we have $\sup_t\|H_t^p\|_{1+\gamma}< \infty$. Thus the limit
@@
 exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
-\end{lemma}
+\end{lem}
 \begin{proof}
@@
 Moreover, we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D$ which is the extinction event.
-\begin{lemma}\label{lemma27}
+\begin{lem}\label{lemma27}
  For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have 
@@
  for some C just depending on $\gamma$.
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{lemma}\label{lemma28}
+\begin{lem}\label{lemma28}
   For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C>0$ and $\delta>0$ such that 
   $$\mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq C e^{-\delta t},\quad t\geq 0.$$
-\end{lemma}
+\end{lem}
 
@@
 
-\subsection{Parameter $m_k[g]$}
+%\subsection{Parameter $m_k[g]$}
+\subsection{Parameters}
  In this subsection, we will introduce an important parameter $m_k[g]$ which is a parameter of $(1+\beta)$-stable distribution. Recall the definition of $Z_f(x)$
@@
  \end{align}
-\begin{lemma}\label{mgineq1}
+\begin{lem}\label{mgineq1}
 There exists $R\in \mathcal{P}$ and constant $C>0$ such that for any $k\in \{0,1,...,t\}$, we have 
 $$|m_k[g]|\leq C e^{(\alpha\beta-\kappa(g)b(1+\beta))k}.$$
-\end{lemma}
+\end{lem}
 \begin{proof}
@@
 i.e. $\phi$ is the projection of $g$ onto the $\kappa(g)$-eigenspace.
-\begin{lemma}\label{lemma210}
+\begin{lem}\label{lemma210}
 Let $g \in \mathcal{P}$, $\kappa(g)\geq 1$ and $\alpha\beta=\kappa(g)b(1+\beta)$, then the following limit exists:
@@
 \end{align}
-\end{lemma}
+\end{lem}
 
@@
 For the small branching rate case: $\alpha\beta<\kappa(g)b(1+\beta)$.
-\begin{lemma}\label{lemma211}
+\begin{lem}\label{lemma211}
 Assume $\alpha\beta<\kappa(g)b(1+\beta)$, if $\kappa(g)\geq 1$, the series $\sum_{k=0}^{\infty}m_k[g]$ is absolutely convergent, hence we can define
@@
 \end{align}
-\end{lemma}
+\end{lem}
 \begin{proof}
@@
 In this section, we will prove the main results of this paper. Let $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
- \begin{lemma}\label{lemma31}
+ \begin{lem}\label{lemma31}
  Assume that $\alpha\beta\leq \kappa(g)b(1+\beta)$, let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}}$, then for any  $k\in\mathbb{N}$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
@@
  $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[g]\right].$$
- \end{lemma}
+ \end{lem}
 \begin{proof}
@@
     \begin{align*}
-        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right|\\
+        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}}\right|\\
         &=\bigg|\big(\mathbb{\tilde{P}}_{\mu}\exp(\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\\
-        &-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\big)\mathbbm{1}_{\mathcal{A}_{t-k-1}}\bigg|\\
-        &\leq e^c\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]\\
-        &+e^c\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]=I+II.
+        &-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}}\bigg|\\
+        &\leq e^c\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\\
+        &+e^c\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]=I+II.
     \end{align*}
@@
 \begin{align}
-    II&=e^c|\theta|^{1+\beta}e^{-\alpha k}\mathbb{\tilde{P}}_{\mu}\left[\left|\frac{\langle Z_{g_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{g_k},\varphi\rangle\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]\nonumber\\
+    II&=e^c|\theta|^{1+\beta}e^{-\alpha k}\mathbb{\tilde{P}}_{\mu}\left[\left|\frac{\langle Z_{g_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{g_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\nonumber\\
     &\leq e^c|\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}\mathbb{\tilde{P}}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
@@
 \begin{align}
-    \left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbbm{1}_{\mathcal{A}^c_{t-k-1}}\right|&\leq C_3\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})\nonumber\\
+    \left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbf{1}_{\mathcal{A}^c_{t-k-1}}\right|&\leq C_3\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})\nonumber\\
     &\leq C_3 e^{-\delta_3(t-k)},\label{lemma33q}
@@
 \end{proof}
-\begin{remark}
+\begin{rem}
    i) For any $k\in\mathbb{N}$, $e^{\theta^{1+\beta}e^{\alpha}m_k[g]}$ is the characteristic function of some $1+\beta$-stable distribution, hence $|e^{\theta^{1+\beta}e^{\alpha}m_k[g]}|\leq 1$.
@@
    ii) the parameters $\delta_1,\delta_2, \delta_3$ in Lemma \ref{lemma31} are just depending on $b,\beta$.
-\end{remark}
-
-\begin{corollary}\label{corollary31}
+\end{rem}
+
+\begin{cor}\label{corollary31}
 Let $\Theta>0$, assume that $\alpha\beta\leq\kappa(g)b(1+\beta)$.
@@
 \end{align*}
-\end{corollary}
+\end{cor}
 \begin{proof}
@@
     \begin{align*}
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_1 e^{-\delta_1 (t-k)}\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_1 e^{-\delta_1(t-k)}
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_1 e^{-\delta_1 (t-k)}\\
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_1 e^{-\delta_1(t-k)}
     \end{align*}
@@
 \begin{align*}
-    \mathcal{B}_{t-k-1}:=\left\{\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\leq C_1 e^{-\frac{\delta_1}{2}(t-k)}\right\}.
+    \mathcal{B}_{t-k-1}:=\left\{\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\leq C_1 e^{-\frac{\delta_1}{2}(t-k)}\right\}.
 \end{align*}
@@
 \begin{align*}
-    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbbm{1}_{\mathcal{A}_{t-k-1}}\leq C_1 e^{-\frac{\delta_1}{2}(t-k)}\right\},
+    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\leq C_1 e^{-\frac{\delta_1}{2}(t-k)}\right\},
 \end{align*}
@@
     \begin{align}
-        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbbm{1}_{\mathcal{D}^c_{t,k}}\leq 2 C e^{-\delta(t-k-1)}.\label{thm121}
+        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\leq 2 C e^{-\delta(t-k-1)}.\label{thm121}
     \end{align}
@@
     \begin{align*}
-        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbbm{1}_{\mathcal{D}_{t,k}}&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\left|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\right|\mathbbm{1}_{\mathcal{D}_{t,k}}\\
-        &\leq|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbbm{1}_{\mathcal{D}_{t,k}}.
+        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\left|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}\\
+        &\leq|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}.
     \end{align*}
@@
 We denote
-$$K_{t,k}:=\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbbm{1}_{\mathcal{D}_{t,k}}.$$
+$$K_{t,k}:=\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}.$$
  On the event $\mathcal{D}_{t,k}$, by mean value theorem of integrals, we get
@@
 \begin{align}
-    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbbm{1}_{\mathcal{D}_{t,k}}&\leq C e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
+    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}&\leq C e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
     &\leq C e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}.\nonumber
@@
 \begin{align}
-     \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbbm{1}_{\mathcal{D}_{t,k}}\leq  e^{-\frac{\alpha}{16}(t-k)}.\label{thm122}
+     \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\leq  e^{-\frac{\alpha}{16}(t-k)}.\label{thm122}
 \end{align}
@@
 \end{align}
-for some $C,\delta>0$. Hence $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\mathbbm{1}_{\mathcal{E}^c_{t,k}}\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ct^{-\delta}$.
+    for some $C,\delta>0$. Hence $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\mathbf{1}_{\mathcal{E}^c_{t,k}}\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ct^{-\delta}$.
 
@@
 
+%new added
+\section{Appendix}
+
+\subsection{}
+    We first present two analytic results which are useful.
+\begin{lem}
+\label{lem: estimate of exponential remaining}
+	Suppose that $z\in \mathbb C_+:= \{x+iy: x \in [0,\infty), y \in \mathbb R\}$. Then
+\begin{equation}
+\label{eq: estimate of exponential remaining}
+	\Big|e^{-z} - \sum_{k=0}^n \frac{(-z)^k}{k!} \Big| 
+	\leq \frac{|z|^{n+1}}{(n+1)!} \wedge \frac{2|z|^{n}}{n!}, \quad n\in \mathbb N_0.
+\end{equation}
+\end{lem}
+\begin{proof}
+	Notice that $|e^{-z}| = e^{- \operatorname{Re} z} \leq 1$. 
+	Therefore, according to \cite[Theorem 7.20.]{Rudin1987Real},
+\begin{equation}
+	|e^{-z} - 1| = \Big| \int_0^1 e^{-\theta z} z d\theta\Big|
+	\leq |z|. 
+\end{equation}
+	Also, notice that $|e^{-z} - 1| \leq |e^{-z}|+1 \leq 2$.
+	So we have \eqref{eq: estimate of exponential remaining} is true when $n = 0$.
+	Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb N_0$.
+	According to \cite[Theorem 7.20.]{Rudin1987Real},
+\begin{align}
+	&\Big|e^{-z} - \sum_{k=0}^{m+1} \frac{(-z)^k}{k!}\Big|
+	= \Big| \int_0^1\Big(e^{-\theta z} - \sum_{k=0}^m \frac{(-\theta z)^k}{k!} \Big) z d\theta \Big|
+	\\&\quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} z d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} z d\theta\Big)
+	= \frac{|z|^{m+2}}{(m+2)!} \wedge \frac{2|z|^{m+1}}{(m+1)!},
+\end{align}
+	which says that \eqref{eq: estimate of exponential remaining} is true for $n = m + 1$.
+	Finally, use induction.
+\end{proof}
+
+\begin{lem}
+\label{lem: extension lemma for branching mechanism}
+	Suppose that  $\nu$ is a measure on $(0,\infty)$ such that $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$. Then the following function $h: \mathbb C_+ \to \mathbb C$ is well defined:
+\begin{equation}
+	h (z) = \int_{(0,\infty)} (e^{-zu} - 1 + zu) \nu(du), \quad z \in \mathbb C_+.
+\end{equation}
+	Moreover, $h$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}$ with deriavative
+\begin{equation}
+\label{eq: deriavetive of the Poission part}
+	h'(z) = \int_{(0,\infty)}(1- e^{-uz})u \nu(du).
+\end{equation}
+\end{lem}
+\begin{proof}
+	From Lemma \ref{lem: estimate of exponential remaining}, we know that $h$ is well defined on $\mathbb C_+$.
+	According to \cite[Theorem 3.2.
+\& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, \eqref{eq: deriavetive of the Poission part} defines a continuous function $h'$ on $\mathbb C_+$ which is holomorphic on $\mathbb C_+^0$.
+	Let $z_0, z \in \mathbb C_+$. 
+	Let $\gamma: [0,1]\mapsto \mathbb C_+$ be a $C^1$ path with $\gamma(0) = z_0$ and $\gamma(1) = z$.
+	Notice that, according to Lemma \ref{lem: estimate of exponential remaining},
+\begin{align}
+	&\int_0^1 \int_0^\infty |1-e^{-u\gamma(\theta)}|u~\nu(du)~d\theta
+	\\ &= \int_0^1~d\theta~ \Big( \int_0^1 |1-e^{-u\gamma(\theta)}|u~\nu(du) + \int_1^\infty |1-e^{-u\gamma(\theta)}|u~\nu(du) \Big)
+	\\ &\leq \int_0^1~d\theta~ \Big( |\gamma(\theta)|\int_0^1 u^2~\nu(du) + 2\int_1^\infty u~\nu(du) \Big) 
+	< \infty.
+\end{align}
+	Therefore, according to Fubini's theorem,
+\begin{align}
+\label{eq: path integration representation of h}
+	\int_\gamma h'(z)dz
+	&=\int_0^1 h'(\gamma(\theta))\gamma'(\theta) ~d\theta 
+	= \int_0^1 \int_0^\infty (1-e^{-u\gamma(
+	\theta)}) u~\nu(du)~ \gamma'(\theta) ~d\theta
+	\\&= \int_0^\infty \int_0^1 (1-e^{-u\gamma(
+	\theta)})~ \gamma'(\theta) u ~d\theta~ \nu(du)
+	= h(z) - h(z_0).
+\end{align}
+	The rest of the proof follows the arguement in \cite[Section 10.14]{Rudin1987Real}.
+\end{proof}
+
+\subsection{}
+\label{seq: complex Feynman-Kac transform}
+	Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact seperable metric space $E$. 
+	For brevity, for each $0< s< t< \infty$ and each bounded complex valued measurable function $\rho$ on $[0,\infty) \times E$, we write
+\begin{equation}
+	H^{(\rho)}_{(s,t)}:= \exp\Big\{\int_s^t \rho(u,\xi_u) du\Big\}.
+\end{equation}
+	Notice that
+\begin{equation}
+\label{eq: crucial for Feynman-Kac}
+	\frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
+	\quad s> 0.
+\end{equation}
+	Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,\infty) \times E$; $F$ is a complex valued bounded measurable function on $E$.
+    Fix a time $t >0$.  
+	Define
+\begin{equation}
+	g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\beta+\rho)} F(\xi_t)],\quad r \in [0,t], x\in E.
+\end{equation}
+    Notice that
+\begin{align}
+    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} F(\xi_t)| ~ds \Big] 
+    \leq  \int_r^t e^{(t-r)\|\beta\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|F\|_\infty ~ds 
+    < \infty.
+\end{align}
+	Therefore, from the Markov property of $\xi$, \eqref{eq: crucial for Feynman-Kac}, Fubini's theorem and above, we can verify that
+\begin{align}
+	&\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\beta)}~(\rho g)(s,\xi_s)~ds \Big]
+	=\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\beta)}\rho(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\beta+\rho)} F(\xi_t)]~ds \Big]
+	\\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} F(\xi_t) ~ds \Big]
+	= \Pi_{r,x} [ H_{(r,t)}^{(\beta)}F(\xi_t)(H_{(r,t)}^{(\rho)} - 1)]
+	\\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\beta)} F(\xi_t)].
+\end{align}
+
+\subsection{}
+\label{sec: definition of characteristic exponent}
+	According to Levy-Khintchine formula \cite[Theorem 8.1]{Sato1990Levy}, an $\mathbb R$-valued random variable $\{Y; P\}$ is infinitely divisible if and only if
+\begin{equation}
+\label{eq: characteristic function of an infinitely divisible random variable}
+	P[e^{i\theta Y}] 
+	= \exp\Big( ia \theta - \frac{1}{2}\sigma^2 \theta^2 + \int_{\mathbb R}(e^{i\theta x} - 1 - i \theta x\mathbf 1_{|x|< 1}) \nu(dx)\Big),
+    \quad \theta \in \mathbb R,
+\end{equation}
+	where $a\in \mathbb R$, $\sigma \in \mathbb R$ and $\nu$ is a measure on $\mathbb R\setminus\{0\}$ with $\int_{\mathbb R}(1\wedge x^2) \nu(dx)< \infty$.
+	Suppose that $\{Y;P\}$ is an infinitely divisible random variable with characteristic function \eqref{eq: characteristic function of an infinitely divisible random variable}, then
+\begin{equation}
+\label{eq: Characteristic exponent}
+	h(\theta) 
+	:= ia \theta - \frac{1}{2}\sigma^2 \theta^2 + \int_{\mathbb R}(e^{i\theta x} - 1 - i \theta x\mathbf 1_{|x|< 1}) \nu(dx),
+	\quad \theta \in \mathbb R, 
+\end{equation}
+    is a continuous function.
+    In fact, for any compact $K \subset \mathbb R$, since due to Lemma \ref{lem: estimate of exponential remaining},
+\begin{equation}
+\int_{\mathbb R}\sup_{\theta \in K} |e^{i\theta x} - 1 - i \theta x\mathbf 1_{|x|< 1}|~\nu(dx)
+\leq (\sup_{\theta \in K} \theta^2)\int_{[0,1)} | x|^2 \nu(dx) + 2 \int_{[1,\infty)} \nu(dx) < \infty,
+\end{equation}
+    we can verify the continuity of $h$ from the dominant convergence theorem.
+    Now, according to \cite[Proposition 1.9.1.]{Linde1986Probability}, 
+	$h$ is the unique continuous function from $\mathbb R$ to $\mathbb C$ with $h(0) = 0$ and $P[e^{i\theta Y}] = \exp\big(h(\theta)\big)$.
+	We refer to function $h$ the characteristic exponent of random variable $Y$ and write $\operatorname{Log} P[e^{i\theta Y}] = h(\theta)$.
+
+\subsection{}
+
+	Suppose that $\{Y;P\}$ is an infinitely divisible random variable with characteristic exponent \eqref{eq: Characteristic exponent}.
+	Suppose that $P[|Y|]< \infty$.
+	According to \cite[Corollary 25.8.]{Sato1990Levy}, $\int_{|x|>1} |x|\nu(dx) < \infty$.
+
+	We claim that, $h$ is differentiable on $\mathbb R$.
+	In fact, according to Lemma \ref{lem: estimate of exponential remaining}, we have for any compact $K \subset \mathbb R$,
+\begin{align}
+	&\int_{\mathbb R} \sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta}(e^{i\theta x} - 1 - i \theta x\mathbf 1_{|x|< 1})\Big| \nu(dx) 
+    = \int_{\mathbb R} \sup_{\theta \in K} | e^{
+    i\theta x} ix - ix \mathbf 1_{|x|< 1} | \nu(dx)
+    \\&\leq(\sup_{\theta \in K}|\theta|) \int_{[0,1)}|x^2| \nu(dx)+\int_{[1,\infty)} |x|  \nu(dx)
+    < \infty,
+    \quad \epsilon > 0.
+\end{align}
+	Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability},
+	we have that $h$ is differentiable on $\mathbb R$ with derivative
+\begin{equation}
+	h'(\theta) = ia - \sigma^2 \theta + i \int_{\mathbb R} (xe^{i\theta x} - x\mathbf 1_{|x|<1}) \nu(dx).
+\end{equation}
+
+	Therefore, according to \cite[Theorem 3.2.4.]{Cuppens1975Decomposition}, we have that map $\theta \mapsto \mathbf P[e^{i\theta Y}]$ from $\mathbb R$ to $\mathbb C$ is differentiable with
+\begin{equation}
+\label{eq: derivative of characteristic exponent}
+	iP[Y e^{i\theta Y}]
+	=\frac{d}{d \theta} P[e^{i\theta Y}] 
+	= P[e^{i\theta Y}] \frac{d}{d \theta} h(\theta),
+	\quad \theta \in \mathbb R.
+\end{equation}
+
+\subsection{}
+\label{sec: definition of superprocess}
+	We say $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a $(\xi,\psi)$-superprocess if
+\begin{itemize}
+\item
+	The sample space $E$ is a locally compact separable metric space. 
+	Denote by $\mathcal M_E^1$ the collection of all the finite measures on $E$ equipped with weak topology.
+\item
+	The spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$.
+\item
+	the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by 
+\begin{equation}
+\label{eq: branching mechanism}
+	\psi(x,z)=
+	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
+\end{equation}
+	where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+\item
+	$X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is an $\mathcal M^1_E$-valued Hunt process with is transition probability determined by
+\begin{align}
+	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(u_f(t,\cdot))},
+	\quad t\geq 0, \mu \in \mathcal M_E^1, f\in \mathscr B^+_b(E),
+\end{align}
+	where the function $u_f:(t,x) \mapsto u_f(t,x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
+\begin{align}\label{eq:FKPP_in_definition}
+	u_f(t,x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi \big(\xi_s,u_f(t-s,\xi_s)\big) ds \Big]
+	= \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
+	\quad t \geq 0, x \in E.
+\end{align}
+\end{itemize}
+	We refer our reader to \cite{Li2011Measure} for more discussion about the definition and the existence of superprocesses.
+    To avoid triviality, we assume that $\psi(x,z)\neq -\beta(x)z$ for some $x \in E$ and $z \geq 0$; and that $\Pi_x(\zeta>t)>0$ for each $x \in E$ and $t \geq 0$.
+
+\subsection{}
+\label{sec: extension of branching mechanism}
+    Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.	
+	Notice that, the branching mechanism $\psi$ can be extended as a map from $E \times \mathbb C_+$ to $\mathbb C$ using \eqref{eq: branching mechanism}.
+	Define
+\begin{equation}
+	\psi'(x,z):= - \beta(x) + 2\alpha(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
+	\quad x\in E, z\in \mathbb C_+.
+\end{equation}
+	Then according to Lemma \ref{lem: extension lemma for branching mechanism}, for each $x \in E$, $z \mapsto \psi(x,z)$ is a holomorphic function on $\mathbb C_+^0$ with deriavetive $z \mapsto \psi'(x,z)$.
+	Define $\psi_0(x,z) := \psi(x,z)+ \beta(x)z $ and $\psi'_0(x,z) := \psi'(x,z) + \beta(x)$.
+
+\subsection{}
+	Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.
+	Denote by $\mathbb W$ the space of $\mathcal M_E^1$-valued c\`{a}dl\`{a}g paths whis its conanical path denoted by $(W_t)_{t\geq 0}$.
+	We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
+	Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure},
+	there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
+\begin{itemize}
+\item
+	$\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$;
+\item
+	$\mathbb N_x(\|W_0 \|\neq 0) = 0$;
+\item
+	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure defined on some probability space
+	with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
+	then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
+\end{itemize}
+	We refer to $(\mathbb N_x)_{x\in E}$ the Kuznetsov measures of $X$.
+\subsection{}
+\label{sec: definition of vf}
+	Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.
+	Define the mean semigroup
+\begin{equation}
+	P_t^\beta f(x)
+	:= \Pi_{x}[e^{\int_0^t \beta(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
+	\quad t\geq 0, x\in E, f\in b\mathscr B^+_E. 
+\end{equation}
+	It is know from \cite[Proposition 2.27]{Li2011Measure} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for any $t > 0$, $\mu \in \mathcal M_E^1$ and $f\in b\mathscr B^+_E$,
+\begin{equation}
+\label{eq: mean formula for superprocesses}
+    \mathbb N_{\mu}[W_t(f)]
+    =\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_t f).
+\end{equation}
+	Define 
+\begin{align}
+    L_1(\xi)
+    &:= \{f\in \mathscr B_E: \forall x\in E, t\geq 0, \quad \Pi_x[|f(\xi_t)|]< \infty\},
+	\\L_2(\xi)
+    &:= \{f \in \mathscr B_E: |f|^2 \in L_1(\xi)\}.
+\end{align}
+	Let $f\in L_1(\xi), t >0$ and $x\in E$.
+    Evaluating \eqref{eq: mean formula for superprocesses} by monotonicity and linearity, we have
+\begin{equation}
+    \mathbb N_x[W_t(f)]
+    =\mathbf P_{\delta_x}[X_t(f)]=P^\beta_t f(x) \in \mathbb R.
+\end{equation}
+	Notice that, from the branching property of the superprocess $X$, $\{X_t(f); \mathbf P_{\delta_x}\}$ is an infinitely divisible random variable with finite moment. 
+	Denote by $v_f(t,x,\theta) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i\theta X_t(f)}]$ the charateristic exponent of random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
+	Assume that the superprocess $X$ is non-presistent with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
+	According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, for each $\theta \in \mathbb R$,
+$	\mathbf P_{\delta_x} [e^{i\theta X_t(f)}] 
+	= \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]).
+$
+	Notice that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function. 
+	Also notice that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$.
+	Therefore, according to the discussion in Subsection \ref{sec: definition of characteristic exponent}, we have 
+\begin{equation}
+\label{eq: N and characteristic exponent}
+	v_f(t,x,\theta) = \mathbb N_x[e^{i\theta W_t(f)} - 1],
+	\quad \theta \in \mathbb R.
+\end{equation}
+
+\subsection{}
+    Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}. 
+    Fix $t > 0,x\in E$ and $f\in L^1(\xi)$.
+	Noticing that
+\[
+	e^{\operatorname{Re} v_f(t,x,\theta)} = |e^{v_f(t,x,\theta)}|
+	= |\mathbf P_{\delta_x}[e^{i\theta X_t(f)}]| \leq 1,
+	\quad \theta\in \mathbb R,
+\]
+    we have
+\begin{equation}
+\label{eq: v has positive real part}
+	\operatorname{Re} v_f(t,x,\theta) \geq 0,\quad \theta \in \mathbb R.
+\end{equation}
+	According to Lemma \ref{lem: estimate of exponential remaining}, we have that
+\begin{equation}
+	|v_f(t,x,\theta)| \leq \mathbb N_x[|e^{i\theta W_t(f)} - 1|]
+	\leq \mathbb N_x[|i\theta W_t(f)|]
+	\leq |\theta| ~(P^\beta_t |f|)(x),
+	\quad \theta \in \mathbb R.
+\end{equation}
+	Notice that, for any compact $K \subset \mathbb R$, 
+\begin{equation}
+\label{eq: estimate of deriavetive of v(theta)}
+	\mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
+	\leq \mathbb N_x[|W_t(f)|] \leq (P^\beta_t |f|)(x) < \infty.
+\end{equation}
+	Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability},
+	$v_f(t,x,\theta)$ is differentiable in $\theta \in \mathbb R$ with
+\[
+	\frac{\partial}{\partial \theta} v_f(t,x,\theta)
+	= i\mathbb N_x[W_t(f)e^{i\theta W_t(f)}],
+	\quad \theta \in \mathbb R.
+\]
+	Moreover, from the above, it is clear that
+\begin{equation}
+\label{eq: upper bounded for derivative of v(theta)}
+	\sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta} v_f(t,x,\theta)\Big|\leq ( P^\beta_t |f|)(x),
+    \quad \theta \in \mathbb R.
+\end{equation}
+    From \eqref{eq: estimate of deriavetive of v(theta)} and the dominate convergence theorem, we can verify that $(\partial/\partial \theta)v_f(t,x,\theta)$ is continuous in $\theta$.
+    In another words, $\theta \to v_f(t,x,\theta)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
+    According to this and \eqref{eq: path integration representation of h}, we can write
+\begin{equation}
+\label{eq: path integration representation of psi(v)}
+    \psi(x,v_f(t,x,\theta_0)) = \int_0^{\theta_0} \psi'(x,v_f(t,x,\theta)) \frac{\partial}{\partial \theta} v_f(t,x,\theta)~d\theta,
+    \quad \theta_0 \in \mathbb R.
+\end{equation}
+    Notice that
+\begin{align}
+\label{eq: upper bound of psi'(v)}
+    &\big|\psi'\big(x, v_f(t,x,\theta)\big)\big| 
+    \\&= \Big| -\beta(x)+ 2\alpha(x) v_f(t-s,x,\theta) 
+    + \int_{(0,\infty)} y (e^{-y v_f(t-s,x,\theta)} - 1) \pi(x,dy)\Big|
+    \\&= \Big| - \beta(x)+ 2\alpha(x)\mathbb N_x(e^{i\theta W_{t}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[e^{i\theta W_{t}(f)} - 1] \pi(x,dy) \Big|
+\\ &\leq \|\beta\|_\infty + 2\alpha(x)\mathbb N_x[|\theta| W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}\big[2\wedge\big(|\theta| W_t(|f|)\big)\big] \pi(x,dy)
+\\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty  |\theta|~ (P^\beta_t |f|)(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~ |\theta| ~(P^\beta_t |f|)(x) 
+\\ & \qquad + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
+\\ &= c_0 +c_1 |\theta| ~(P^\beta_t |f|)(x),
+\quad \theta \in \mathbb R.
+\end{align}
+    where $c_0,c_1 \geq 0$ are constants not dependent on $f,x,t$ and $\theta$.
+    Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have
+\begin{align}
+\label{eq: upper bound of psi(v)}
+    \big|\psi\big(x,v_f(t,x,\theta)\big)\big| 
+    \leq c_0|\theta|~(P^\beta_t |f|)(x)+c_1 |\theta|^2 ~(P^\beta_t |f|)(x)^2,
+    \quad \theta \in \mathbb R.
+\end{align}
+
+    Assume that $f \in L_2(\xi) \subset L_1(\xi)$.
+    Then, using Jensen's inequality and the above, we have that 
+\begin{align}
+\label{eq: domination of psi(v)}
+    &\Pi_x\Big[\int_0^t |\psi(\xi_s,v_f(t-s,\xi_s,\theta))|ds\Big] 
+\\&\leq \Pi_x\Big[\int_0^t \big(c_0|\theta| (P_{t-s}^\beta|f|)(\xi_s)+c_1|\theta|^2(P_{t-s}^\beta|f|)(\xi_s)^2\big)ds\Big]
+\\ &\leq \int_0^t \big(c_0|\theta|e^{t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+c_1|\theta|^2e^{2t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
+\\ &\leq \int_0^t (c_0|\theta|e^{t\|\beta\|}\Pi_x [ |f(\xi_{t})|]+c_1|\theta|^2e^{2t\|\beta\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
+\end{align}
+    As a consequence, expectation
+\[
+    \Pi_x\Big[\int_0^t \psi(\xi_s,v_f(t-s,\xi_s,\theta))ds\Big]
+    \in \mathbb C
+\]
+    is well defined for all $f\in L_2(\xi)$.
+\subsection{}
+	Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
+	Let $f\in b\mathscr B_E^{++}$, $T >0$ and $x\in E$.
+	The fact that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^\beta_T f(x) \in (0,\infty)$ allows us to define the following probability transforms:
+\begin{equation}
+	d\mathbf P_{\delta_x}^{X_T(f)}
+	:= \frac{X_T(f)}{T_t^\beta f(x)} d\mathbf P_{\delta_x};
+	\quad d\mathbb N_x^{W_T(f)}
+	:=  \frac{W_T(f)}{T_t^\beta f(x)} d\mathbb N_x.
+\end{equation}
+	Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{W_T(f)}$ if
+\begin{itemize}
+\item
+    The spine process $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$, 
+    where
+\begin{equation}
+    d\Pi_x^{(f,T)} := \frac{f(\xi_T)e^{\int_0^T \beta(\xi_s)ds}}{P^\beta_T f(x)} d \Pi_x;
+\end{equation}
+\item
+    Given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure $\{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
+\begin{align}
+    \mathbf m(\xi,ds,dw)
+    := 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
+\end{align}
+\item
+    $\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M^1_E$-valued process defined by
+\begin{align}
+    Y_t
+    := \int_{(0,t] \times \mathbb W} w_{t-s} \mathbf n(\xi,ds,dw),
+    \quad 0 \leq t\leq T.
+\end{align}
+\end{itemize}
+	According to the spine decomposition theorem \cite{RenSongSun2017Spine}, we have that
+\begin{align}
+\label{eq: Spine decomposition 1}
+	\{(X_s)_{s \geq 0};\mathbf P_{\delta_x}^{X_T(f)}\}
+	\overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{W_T(f)} \}
+\end{align}
+    and
+\begin{align}
+\label{eq: Spine decomposition 2}
+    \{(W_s)_{0\leq s\leq T};\mathbb N_x^{W_T(f)}\}
+    \overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
+\end{align}
+\subsection{}
+    Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
+\begin{prop}
+	Let $f\in L_2(\xi)$. Then for each $t\geq 0$, $x\in E$ and $\theta \in \mathbb R$,
+\begin{equation}
+\label{eq: complex FKPP-equation}
+	v_f(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s,v_f(t-s,\xi_s,\theta)\big) ds \Big]
+	\\= i\theta \Pi_{x} [f(\xi_t)].
+\end{equation}
+\end{prop}
+\begin{proof}
+    Assume that $f\in b\mathscr B_E$.
+	Set $t>0, r\in [0,t), x\in E, \theta \in \mathbb R$ and $g\in b\mathscr B_E^{++}$.
+	Denoted by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
+    Given $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$.
+    Denote by $\Pi_{r,x}$ the probability of Hunt process $\{\xi; \Pi\}$ initiated at time $r$ and position $x$.
+    From Lemma \ref{lem: estimate of exponential remaining}, we have $\mathbf Q^{(g,t)}_{x}$-a.s.ly
+\begin{align}
+&\int_{[0,t]\times \mathbb W}|e^{i\theta w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
+    \leq \int_{[0,t]\times \mathbb W}\big(|\theta w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
+    \\&\leq \int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}\big(|\theta | W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[|\theta| X_{t-s}(|f|)] \pi(\xi_s,dy) 
+    \\&\qquad\qquad+ 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
+     \\&\leq \int_0^t |\theta|(P_{t-s}^\beta |f|)(\xi_s)\Big(2\alpha(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+    \\&\leq \Big(2\|\alpha\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t |\theta| e^{t\|\beta\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+    < \infty.
+\end{align}
+    According to this, Fubini's theorem, \eqref{eq: N and characteristic exponent}, \eqref{eq: v has positive real part} and the argument in Subsection \ref{sec: extension of branching mechanism}, we have $\mathbf Q^{(g,t)}_{x}$-a.s.ly,
+\begin{align}
+	&\int_{[0,t]\times \mathbb N}(e^{i\theta w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
+	\\&=\int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}(e^{i\theta W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i\theta W_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
+	\\&=\int_0^t \Big( 2\alpha(\xi_s) v_f(t-s,\xi_s,\theta) 
+	+ \int_{(0,\infty)} y (e^{-y v_f(t-s,\xi_s,\theta)} - 1) \pi(\xi_s,dy) \Big) ds
+	\\&= \int_0^t \psi'_0\big(\xi_s, v_f(t-s,\xi_s,\theta)\big)ds.
+\end{align}
+	Therefore, according to \eqref{eq: Spine decomposition 2}, Campbell's formula and above, we have that 
+\begin{align}
+\label{eq: N to Pi}
+	\mathbb N_x^{W_t(g)}[e^{i\theta W_t(f)}]
+	&=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i\theta w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
+	\\&= \Pi_x^{(g,t)} [e^{\int_0^t \psi'_0(\xi_s, v_f(t-s,\xi_s,\theta))ds}]
+	\\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta))ds} ].
+\end{align}
+    Let $\epsilon >0$.
+    Define $f^+ = (f \vee 0) + \epsilon$ and $f^- = (-f) \vee 0 + \epsilon$, then $f^\pm \in b\mathscr B^{++}_E$ and $f = f^+ - f^-$. 
+    According to \eqref{eq: Spine decomposition 1}, we have that
+\begin{equation}
+    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i\theta X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]} 
+    = \mathbf P_{\delta_x}[e^{i\theta X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i\theta X_t(f)}].
+\end{equation}
+    Using \eqref{eq: N to Pi} and above, we have
+\begin{align}
+	\frac{\mathbf P_{\delta_x}[X_t(f)e^{i\theta X_t(f)}] }{\mathbf P_{\delta_x}[e^{i\theta X_t(f)}]} 
+	&= \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i\theta X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i\theta X_t(f)}]
+	\\& = \Pi_x[ f(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta)) ds}  ].
+\end{align}
+	Therefore, according to \eqref{eq: derivative of characteristic exponent} and above, we have
+\begin{align}
+	\frac{\partial}{\partial \theta} v_f(t, x, \theta)
+	= \Pi_x[ if(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta)) ds} ].
+\end{align}
+	Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
+\begin{align}
+	&\frac{\partial}{\partial \theta} v_f(t - r, x, \theta)
+	= \Pi_x[ if(\xi_{t-r}) e^{\int_0^{t-r} \psi'(\xi_s, v_f(t-r-s,\xi_s,\theta)) ds} ]
+	\\&= \Pi_{r,x}[if(\xi_t)e^{\int_0^{t-r} \psi'(\xi_{r+s}, v_f(t-r-s,\xi_{r+s},\theta)) ds} ]
+	= \Pi_{r,x}[if(\xi_t)e^{\int_r^t \psi'(\xi_{s}, v_f(t-s,\xi_{s},\theta)) ds} ].
+\end{align}
+    From \eqref{eq: upper bound of psi'(v)}, we know that for each fixed $\theta \in \mathbb R$, $(t,x) \mapsto |\psi'(x,v_f(t,x,\theta))|$ is bounded above.
+	Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
+\begin{equation}
+	\frac{\partial}{\partial \theta} v_f(t-r, x, \theta) - \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s, v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
+	= \Pi_{r,x} [i f(\xi_t)].
+\end{equation}
+	Integrating the above with respect to $\theta$, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we have
+\begin{equation}
+	v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
+	\\= i\theta \Pi_{r,x} [f(\xi_t)].
+\end{equation}
+    Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} is true if $f\in b\mathscr B_E$.
+
+    Now assume that $f\in L_2(\xi)$. Set $n \in \mathbb N$.
+    Writing $f_n := (f^+ \wedge n) - (f^- \wedge n)$, then $f_n \xrightarrow[n\to \infty]{} f$ pointwisely. 
+    From what we have proved, 
+\begin{equation}
+\label{eq: complex FKPP-equation for fn}
+    v_{(f_n)}(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta)\big) ~ds\Big]
+    \\= i\theta \Pi_{x} [f_n(\xi_t)].
+\end{equation}
+    Notice the following:
+\begin{itemize}
+\item
+    It is clear that $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$.
+\item
+    $v_{(f_n)}(t,x,\theta) \xrightarrow[n\to \infty]{} v_f(t,x,\theta)$ due to \eqref{eq: N and characteristic exponent}, dominated convergence theorem and the fact that
+\[
+    |e^{i\theta W_t(f_n)} - 1| \leq |\theta| W_t(|f|);
+    \quad \mathbb N_x[W_t(|f|)] = (P_t^\beta |f|)(x) < \infty.
+\]
+\item
+    $\Pi_{x} [\int_0^t \psi(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta))ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,v_{f}(t-s,\xi_s,\theta))ds]$ due to donimated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
+\begin{align}
+    \big|\psi\big(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta)\big)\big|
+    \leq c_0|\theta|~(P^\beta_{t-s} |f|)(\xi_s)+c_1 |\theta|^2 ~(P^\beta_{t-s} |f|)(\xi_s)^2.
+\end{align}
+\end{itemize}
+    Using the above arguements, letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
+\end{proof}
+%end new add
+
 \begin{thebibliography} {10}
+
+\bibitem{BAM}
+Berestycki, J., Kyrianou, A.E., Murillo-Salas, A
+\newblock{\em The prolific backbone for supercritical superprocesses}. Stoch. Proc. Appl. 121, 1315-1331(2011)
+
+\bibitem{Cuppens1975Decomposition}
+Cuppens, R.:
+\emph{Decomposition of multivariate probabilities.}
+Probability and Mathematical Statistics, Vol. 29. Academic Press [Harcourt Brace Jovanovich, Publishers], New York-London, 1975.
+\MR{0517412}
+
+\bibitem{Durrett2010Probability}
+Durrett, R.:
+\emph{Probability: theory and examples.}
+Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
+\MR{2722836}
 
@@
 
-\bibitem{AK}
-Kyprianou,~A.E. 
-\newblock {\em Introductory Lectures on Fluctuations of Levy Processes with Application}, Springer, Berlin(2006)
-
-\bibitem{ZL}
-Z.~Li,
-\newblock {\em Measure-valued branching Markov processes}, Probability and its Applications (New York), Springer, Heidelberg, 2011. MR 2060602
+\bibitem{DK}
+Dynkin, E. B., Kuznetsov, S. E.: 
+\newblock {\em $\mathbb{N}$-measure  for branching exit Markov system and their applications to differential equations}, Probab. Theory Related Fields 130(2004) 135-150
+
+\bibitem{Kyprianou2014Fluctuations}
+Kyprianou, A. E.: 
+\emph{Fluctuations of L\'{e}vy processes with applications.}
+Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
+\MR{3155252}
+
+\bibitem{Li2011Measure}
+Li, Z.:
+\emph{Measure-valued branching Markov processes.} 
+Probability and its Applications (New York), Springer, Heidelberg, 2011. 
+\MR{2060602}
+
+\bibitem{Linde1986Probability}
+Linde, W.:
+\emph{Probability in Banach spaces—stable and infinitely divisible distributions.}
+Second edition. A Wiley-Interscience Publication. John Wiley \& Sons, Ltd., Chichester, 1986.
+
+\bibitem{MM}
+Marks, R., Mil\'{o}s, P.:
+\newblock {\em CLT for supercritical branching processes with heavy-tailed branching law}. 
+\ARXIV{1803.05491}
 
@@
 \bibitem{RSZ}
-Y.-X.Ren, R. Song, R. Zhang,
+Ren, Y.-X., Song, R., Zhang, R.:
 \newblock {\em Central limit theorems for super Ornstein-Uhlenbeck processes}, Acta Appl. Math. 130(2014)9-49.
 
-\bibitem{MM}
-R.Marks, P.Mil\'{o}s
-\newblock {\em CLT for supercritical branching processes with heavy-tailed branching law}. arXiv preprint arXiv:1803.05491, 2018.
-
-\bibitem{DK}
-E.B.Dynkin, S.E. Kuznetsov,
-\newblock {\em $\mathbb{N}$-measure  for branching exit Markov system and their applications to differential equations}, Probab. Theory Related Fields 130(2004) 135-150
-
-\bibitem{DR}
-Durrett, Rick.
-\newblock {\em Probability: theory and examples}. Cambridge university press, 2010.
-
-\bibitem{BAM}
-Berestycki, J., Kyrianou, A.E., Murillo-Salas, A
-\newblock{\em The prolific backbone for supercritical superprocesses}. Stoch. Proc. Appl. 121, 1315-1331(2011)
-
-\bibitem{RSS}
-Y.-X.Ren, R. Song, Z. Sun,
+\bibitem{RenSongSun2017Spine}
+Ren, Y.-X., Song, R., Sun, Z.:
 \newblock{\em Spine decompositions and limit theorems for a class of critical superpeocesses,} arXiv preprint arXiv:1711.09188(2017).
 
+\bibitem{Rudin1987Real}
+Rudin, W.:
+\emph{Real and complex analysis.}
+Third edition. McGraw-Hill Book Co., New York, 1987.
+\MR{0924157}
+
+\bibitem{SchillingSongVondracek2010Bernstein}
+Schilling, R., Song, R., Vondra\v{c}ek, Z.:
+\emph{Bernstein functions. Theory and applications.} 
+De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2010.
+\MR{2598208}
+
+\bibitem{Sato1990Levy}
+Sato, K.:
+\emph{Lévy processes and infinitely divisible distributions.}
+Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.
+
 \end{thebibliography}

### 2019-01-31 supCLT.tex
supCLT.tex: version 3

@@
 %%%----Versions-----------------------------
-% supCLT1.tex 2018/6/24 by Zhenyao
+% supCLT3.tex 2018/8/25 by Zhenyao
+% supCLT2.tex 2018/8/13 by Jianjie
+% supCLT1.tex 2018/7/24 by Zhenyao
 % supCLT.tex 2018/6/29 by Jianjie
@@
 \usepackage{bbm}
+\usepackage{comment}
 \usepackage{mathtools}
@@
     Beijing, P. R. China, 100871}
-\email{???@pku.edu.cn}
+\email{zhaojianjie@pku.edu.cn}
 %\begin{abstract}
@@
 \subsection{Model}
-%We first fix our notation, for a vector $x\in \mathbb{R}^d$, we denote by $|x|$  its Euclidean norm.
-Let $\xi=\{\xi_t : t\geq 0\}$ be an Ornstein-Uhlenbeck prcess, short for OU process, on $\mathbb{R}^d$, with infinitesimal generator $L$.
-For any $f \in C^2(\mathbb{R}^d)$,
-%\begin{equation}\label{generatior}
-%Lf(x)= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x))   
-%\end{equation}
-%where $\sigma>0$ is the diffusion parameter, $b>0$ is the drift parameters. What's more, we respectively use $\Delta$ and $\nabla$ to express the Laplace operator and gradient operator as usual.
 Let $d \in \mathbb N:= \{1,2,\dots\}$.
@@
 Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
-\begin{equation}\label{generatior}
+\begin{equation}
+\label{eq: OU generator}
     Lf(x)
-    %= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x)), 
     = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
@@
 where $\sigma>0$ and $b>0$.
-%For any $x\in \mathbb{R}^d$, We denote by $\Pi_x$ the law of $\xi$ starting from $x$. The semigroup of $\xi$ will be denoted by $\{T_t: t\geq 0\}$.
-Denoted by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
-%In this paper, we consider a branching mechanism of the form  
-%\begin{equation}\label{mechanism}
-%\psi(\lambda)=-\alpha \lambda + \lambda^{(1+\beta)}, \lambda \geq 0
-%\end{equation}
-%Where $\alpha = -\psi'(0+)>0$ and $\beta \in (0,1) $.
-Let $\psi$ be a function on $\mathbb C_+:= \{x+iy: x\in [0,\infty), y\in \mathbb R\}$ with
+Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
+%Let $\psi$ be a function on $\mathbb C_+:= \{x+iy: x\in [0,\infty), y\in \mathbb R\}$ with
+Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
 \begin{equation}\label{mechanism}
@@
     := - \alpha z + z^{1+\beta},
-    \quad z \in \mathbb C_+,
+    %\quad z \in \mathbb C_+,
+    \quad z \in \mathbb R_+,
 \end{equation}
 where $\alpha > 0$ and $\beta \in (0,1) $.
-%Let $\mathcal{M}(\mathbb{R}^d)$ be the space of finite measures on $\mathbb{R}^d$. 
 Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of finite measures on $\mathbb{R}^d$.
-%We say a $\mathcal{M}(\mathbb{R}^d)$-value branching Markov process $X=\{(X_t)_{t\geq 0},\mathbb{P}_{\mu}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for any $t \geq 0$, positive bounded measurable functions $f$ on $\mathbb{R}^d$ and any $\mu \in \mathcal{M}(\mathbb{R}^d)$, we have
-%\begin{equation} \label{super}
-%    \mathbb{P}_{\mu}(e^{-\langle f,X_t \rangle})=e^{-\langle u_f(\cdot , t), \mu \rangle},
-%\end{equation}
-%where  $u_f(\cdot , t)$ is the unique locally bounded positive solution to the equation
-%\begin{equation}\label{eq1}
-%     u_f(x , t) + \Pi_x \left( \int_0^t\psi(u_f(\xi_s,t-s))~ds\right) =\Pi_x [f(\xi_t)],
-%\end{equation}
-%In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$.
-Put $\|\mu\|=\langle 1,\mu\rangle$.
-We assume that the parameter $\alpha$ in branching mechanism $\psi$ is larger than zero, i.e.
-$X$ is  supercritical.
 In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$. Put $\|\mu\|=\langle 1,\mu\rangle$.
-We say a $\mathcal{M}(\mathbb{R}^d)$-value Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
+We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
 \begin{equation} \label{super}
@@
 \end{equation}
-
-%According to \cite[section 2]{Li2011Measure}, is equivalent to
-According to \cite[section 2]{Li2011Measure}, the above is equivalent to
-\begin{equation}\label{eq2}
-     u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
-\end{equation}
+%deleted
+%According to \cite[section 2]{Li2011Measure-valued}, the above is equivalent to
+%\begin{equation}\label{eq2}
+     %u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
+%\end{equation}
+%end deleted
 
     The existence of such superprocesses is well known, see \cite{EB} for instance.
-    %Let $||X_t||=\langle 1, X_t \rangle$ be the total mass of the process $X$ at time $t$, then $\{\|X_t\|; t \geq 0\}$ is a continuous-state branching process with branching mechanism $\psi$.  
     Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
-    %The fact $\psi(\infty)=\infty$ implies that the probability of extinction event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see, for example,  \cite[section 10.2.2]{Kyprianou2014Fluctuations}.
     The fact $\psi(\infty)=\infty$ implies that the probability of extinguish event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see \cite[Theorem 12.7]{Kyprianou2014Fluctuations} for example.
-    %Let $\alpha^{\ast}$ be the larger root of $\psi=0$, we have $$\mathbb{P}_{\mu}\left(\lim_{t\rightarrow \infty}\|X_t\|=0\right)=e^{-\alpha^{\ast}\|\mu\|}.$$
     In fact,
@@
     where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
-
-%For any $f \in \mathcal{P}$, define the {\em Feyman-Kac semigroup}
+%comment
+    {\bf (Zhenyao: We should use \cite[Theorem 12.5]{Kyprianou2014Fluctuations} and talk about the probability of $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$.
+Because we want to emphsis that our superprocess is non-presistent.)}
+%end comment
+
     Define the \emph{Fenyman-Kac semigroup} by
@@
     := \Pi_x [e^{\alpha t}f(\xi_t)],
-    %\quad x\in \mathbb{R}^d,t\geq 0, 
     \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
 \end{equation}
-%which is konwn as the {\em mean semigroup} of the superprocess $X$, in the sense that
-    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
-\begin{equation}\label{meanformula}
+    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
+\begin{equation}\label{eq:meanformula}
     \mathbb{P}_{\mu}[\langle f, X_t \rangle]
     = \langle T_t^\alpha f, \mu \rangle,
-%new
     \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
-%end new
-\end{equation}
-%see \cite[Proposition 2.27]{Li2011Measure}. 
-%Notice that $T^{\alpha}_t f =e^{\alpha t}T_t f$.
+\end{equation}
 Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.
 
-%The purpose of this paper is to establish some spatial central limit theorems for the super OU-process with stable branching \eqref{mechanism}. More precisely, consider the limit of 
-%$$\frac{\langle f,X_t\rangle-\|X_t\|\langle f, \varphi \rangle}{F_t},$$
-%we want to find $(F_t)_{t\geq0}$, for suitable test functions $f$, such that the former formula convergence to some non-degenerate random variable as $t\rightarrow \infty$.
-
-%\subsection{OU semigroup and Eigenfunctions}
 \subsection{OU semigroup}
-({\bf Do we have a good reference about those following result about the OU semigroup?})
-Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
-\begin{equation}\label{invariantdensity}
-    \varphi (x) 
-    =\Big (\frac{b}{\pi \sigma^2}\Big )^{\frac{d}{2}}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big),\quad x\in \mathbb{R}^d.
+%moved and modified from below
+    In tihs subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
+%end moved and modified from below
+    %Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
+    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}. 
+    %It is known that $\xi$ has an invariant density
+    It is known that $\xi$ has an invariant measure
+\begin{equation}
+\label{invariantdensity}
+    %\varphi (x)
+    \varphi(x)dx
+    %=\Big (\frac{b}{\pi \sigma^2}\Big )^{\frac{d}{2}}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big),\quad x\in \mathbb{R}^d.
+    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
+    \quad x\in \mathbb{R}^d.
 \end{equation}
@@
     \langle f_1, f_2 \rangle_{\varphi}
-%= 
-:=
-\int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
-\end{equation}
-
-    %For $p=(p_1,p_2,...,p_d) \in \mathbb{Z}_+^{d}$, let $|p|=p_1+...+p_d$, $p!=p_1 \cdot ...
-\cdot p_n$ and $\partial x^p =\partial x_1^{p_1} \cdot ...
-\cdot \partial x_d^{p_d}$.
-We recall the Hermite polynomials $H_p$ in $\mathbb{R}^d$
-    For each $p = (p_k)_{k = 1\dots d} \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$. 
+    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
+\end{equation}
+%moved to above
+    %In tihs subsection, we recall some results on the spectrum in $L^2(\varphi)$ of the operator $L$, more details can be found in \cite{GD}.
+%end moved to above
+    %For each $p = (p_k)_{k = 1\dots d} \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$.
+    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$.
     The Hermite polynomials are defined by
@@
     H_p(x)
-    %:=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{|p|}}{\partial x^p} \left ( e^{-|x|^2} \right ).
     :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
@@
 \end{equation}
-%It is known that, see \cite{GD} as an example, the eigenvalues of $L$ are $\{-bk: k =0,1,2,...\}$ and the eigenspace $A_k$ corresponding to $-bk$ is
-%$$A_k = {\rm Span} \{\phi_p : |p|=k\},$$
-It is known that, see \cite{GD} for example, the generator $L$ of OU process $\xi$ can be viewed as an operator 
-%on $L^2(\phi)$ 
-on $L^2(\varphi)$ 
-with eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
-For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ of this operator is
+    It is known that the generator $L$ of OU process $\xi$ can be viewed as an operator on $L^2(\varphi)$ with eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
+    %For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ of this operator is
+    For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ is
 \begin{equation}
@@
 \end{equation}
-%Moreover, The polynomials $\{\phi_p(x)\}_{p \in \mathbb{Z}_+^d}$ form a complete orthonormal basis of $L^2(\varphi)$. Thus, for any $f\in L^2(\varphi)$, we have
-Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$. 
-Therefore, for each $f\in L^2(\varphi)$, 
+    %Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
+    Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
+    %Therefore, for each $f\in L^2(\varphi)$,
+    That is, for each $f\in L^2(\varphi)$,
 \begin{equation}\label{semicomp1}
@@
 \end{equation}
-%where $a_p=\langle f, \phi_p \rangle_{\varphi}$. 
-Let
+%Let
+    Denote
 \begin{equation}\label{order}
     \kappa(f)
-    %:=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  a_p \neq 0\right \}
     :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
 \end{equation}
-denote the order of function $f$ in $L^2(\varphi)$. Then $ \kappa(f)\geq 0$, in particular, the order of constant functions is zero.
-
-In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
+    %denote the order of function $f$ in $L^2(\varphi)$. Then $ \kappa(f)\geq 0$, in particular, the order of constant functions is zero.
+    the order of function $f$ in $L^2(\varphi)$. 
+    Then $ \kappa(f)\geq 0$. 
+    In particular, the order of any constant function is zero.
+
+    %In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
+    In this paper, we consider the class of functions of ploynomial growth $\mathcal{P}$ defined by
 \begin{equation}
     \mathcal{P}
-     %:=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C, n>0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
     :=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
 \end{equation}
-%It is easy to see that $\mathcal{P} \subset L^2(\phi)$. 
     It is easy to see that $\mathcal{P} \subset L^2(\varphi)$.
-%What's more, 
-According to \cite[Fact 1.2]{MM},
-for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
-\begin{equation}\label{semigroupineq}
-    |T_tf(x)| \leq e^{-\kappa(f)bt}R(x).
-\end{equation}
-%That is to say the rate of decay of the semigroup depending on $\kappa(f)$. 
-%The readers can find the prove in \cite[Fact 1.2]{MM}.
+    %According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
+    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that,
+\begin{equation}
+\label{eq:semigroupineq}
+    |T_tf(x)| 
+    \leq e^{-\kappa(f)bt} R(x),
+    \quad t\geq 0, x\in \mathbb R^d.
+\end{equation}
 
 \subsection{Characteristic functions}
- Let $X$ be a super OU-process with initial configuration $\mu$. For any $f \in \mathcal{P}$,
-replace $f$ by $-i\theta f$ in equations of \eqref{super} and \eqref{eq2}, we obtain that
-\begin{equation}\label{characteristic}
-    \mathbb{P}_{\mu}\left[\exp(i\theta \langle  f,X_t\rangle)\right]=e^{\langle w_f(\cdot,t,\theta),\mu\rangle}
-\end{equation}
-where $w_f(x,t,\theta)=\log \mathbb{P}_{\delta_x}e^{i\theta\langle f,X_t\rangle}$ satisfying the equation that
-\begin{equation}\label{charequation}
-    w_f(x,t,\theta)-\int_0^t T_{t-s} \left(\psi (-w_f(\cdot,s,\theta))\right)(x)ds=i\theta T_tf(x)
-\end{equation}
-
-Recall the branching mechanism $\psi$ and Feynman-Kac semigroup $T^{\alpha}_t$, and apply \cite[Proposition 2.9]{Li2011Measure} to \eqref{charequation}, we have that
-\begin{equation}\label{chareq2}
-        w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x)
-\end{equation}
+    %Let $X$ be a super OU-process with initial configuration $\mu$. 
+%new added
+    Let the Gamma function $\Gamma$ be defined by
+\begin{equation}
+    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt, 
+    \quad x>0,
+\end{equation}
+and
+\begin{align}
+\label{eq: definition of Gamma function}
+    \Gamma(x)
+    := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
+    \quad -n< x< -n+1, n\in \mathbb N.
+\end{align}
+    Then it is elementary to verify that
+\begin{equation}
+    \Gamma(x+1) = x\Gamma(x),
+    \quad x>0~\text{or}~-n< x< -n+1, n\in \mathbb N.
+\end{equation}
+
+    Fix a $\beta \in (0,1)$.
+    According to \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that the following function:
+\begin{equation}
+    z
+    \mapsto z^{\beta}
+    := \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}, 
+    \quad z\in \mathbb C_+,
+\end{equation}
+\begin{itemize}
+\item
+    is an extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
+\item
+    is continuous in $\mathbb C_+$;
+\item 
+    is holomorphic in $\mathbb C_+^0$.
+\end{itemize}
+    According to Lemma \ref{lem: extension lemma for branching mechanism} in the Appendix, we can verify that the following function:
+\begin{equation}
+\label{eq: stable branching on C+}
+    z\mapsto 
+    z^{1+\beta} 
+    := \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
+    \quad z\in \mathbb C_+,
+\end{equation}
+\begin{itemize}
+\item
+    is an extension of the real function $x\mapsto x^{1+\beta}$ on $[0,\infty)$;
+\item
+    is continuous in $\mathbb C_+$;
+\item 
+    is holomorphic in $\mathbb C_+^0$.
+\end{itemize}
+    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\mapsto \mathbb C_+$,
+\begin{align}
+\label{eq: integration formula for 1+beta-th power of z}
+    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta} 
+    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
+    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}} 
+    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
+\end{align}
+    This indicates that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
+\begin{lem}
+\label{lem: Lip of power function}
+    There is a constant $C_0 > 0$ such that for any $z_0,z_1 \in \mathbb C_+$,
+\[
+    |z_0^{1+\beta} - z_1^{1+\beta}| 
+    \leq C_0(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
+\]
+\end{lem}
+\begin{proof}
+    Notice that
+\begin{align}
+\label{eq: upper bound for beta power of z}
+    &|z^{\beta}|
+    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big| 
+    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
+    \\&= \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c_0 |z|^{\beta},
+    \quad z\in \mathbb C_+.
+\end{align}
+    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
+\[
+    \gamma(\theta) 
+    = z_0 (1-\theta) + \theta z_1,
+    \quad \theta \in [0,1].
+\]
+    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
+\begin{align}
+    |z_0^{1+\beta} - z_1^{1+\beta}| 
+    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
+    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
+    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
+    \qedhere
+\end{align}
+\end{proof}
+
+    Let $X$ be the super OU-process discussed in the previous subsections.
+    Its branching mechanism $\psi$ can be extended in the following way: $\psi(z) := -\alpha z + z^{1+\beta}$ for $z\in \mathbb C_+$. 
+    Then according to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}$ with derivative
+\begin{equation}
+\label{eq: deriavetive of the Poission part}
+    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
+    \quad z\in \mathbb C_+.
+\end{equation}
+Write $\psi_0(z) = \psi(z) + \alpha z$ and $\psi'_0(z) = \psi'(z) + \alpha$.
+%end new added
+    %For any $f \in \mathcal{P}$, replace $f$ by $-i\theta f$ in equations of \eqref{super} and \eqref{eq2}, we obtain that
+%\begin{equation}\label{characteristic}
+    %\mathbb{P}_{\mu}\left[\exp(i\theta \langle  f,X_t\rangle)\right]=e^{\langle w_f(\cdot,t,\theta),\mu\rangle}
+%\end{equation}
+%where $w_f(x,t,\theta)=\log \mathbb{P}_{\delta_x}e^{i\theta\langle f,X_t\rangle}$ satisfying the equation that
+%\begin{equation}\label{charequation}
+    %w_f(x,t,\theta)-\int_0^t T_{t-s} \left(\psi (-w_f(\cdot,s,\theta))\right)(x)ds=i\theta T_tf(x)
+%\end{equation}
+    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, denote by $w_f(x,t,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]$ the characteristic exponent of $\{X_t(f); \mathbb P_{\delta_x}\}$
+    (For percise definition, see the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
+    From \eqref{eq: -v has positive real part}, we know that $- w_f(x,t,\theta)$ taks values in $\mathbb C_+$.
+    Furthermore, we know from Proposition \ref{sec: definition of characteristic exponent} that
+%delete
+%\begin{equation}\label{characteristic}
+    %\mathbb{P}_{\mu}[e^{i\theta X_t(f)}]
+    %=e^{\langle w_f(\cdot,t,\theta),\mu\rangle},
+    %\quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
+%\end{equation}
+    %where $w_f(x,t,\theta)$ satisfies the equation
+\begin{align}\label{charequation}
+    w_f(x,t,\theta)-\int_0^t T_{t-s} \psi \big(-w_f(\cdot,s,\theta)\big)(x)ds
+    =i\theta T_tf(x),
+    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
+\end{align}
+and
+\begin{align}
+\label{eq:chareq2}
+    %w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x),
+    w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \psi_0(-w_f(\cdot,s,\theta))(x)ds=i\theta T^{\alpha}_t f(x),
+    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
+\end{align}
+%new added
+%end new added
+%begin comments
+    {\bf Zhenyao: There are notation inconsistency in the Appendix and other suctions. Mainly on the branching mechanism: In the appendix, we use
+\[
+    \psi(x,z)= -\beta(x)z+\alpha(x)z^2 + \int_0^t \dots;
+\]
+    But in other subsections we use
+\[
+    \psi(z) = - \alpha z + z^{1+\beta}.
+\]
+    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.
+
+    Another inconsistency is the notation for the characteristic exponent $\operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]$.
+In the appendix we use $v_f(t,x,\theta)$, but in other subsection we use $w_f(x,t,\theta)$.
+I recommended to use $v_f$ because I would like that $w$ be reserved for representing canonical element in some measurable spaces.
+Also, I would like to use $(t,x)$ instead of $(x,t)$ because it make more sense to put the ``time parameter t" first.
+($(t,x)$ and $(x,t)$ are both used by different authors.)
+
+    Though I recommended all those changes, I did not try to make them in this version (in order to not mess things up).
+I would like Jianjie to decide which set of notations is better.
+Overall, I am fine with any set of notations as long as they are consistent with each other and don't raise any confusions.}
+%end comments
 
@@
 In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in [0,\beta)$. 
-Fix $g\in \mathcal{P}$ and for notational convenience we omit it in formulations of most of lemmas below.
-
-Consider a incremental decomposition of $\langle g,X_t \rangle$.
-Denote by $\{\mathcal{F}_t:t\geq 0\}$ the filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$.
-For $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$.
-For each $t-k\geq 1$, according to \eqref{meanformula}, define
+%For notational convenience, we always fix $g\in \mathcal{P}$ in the following sections, correspondingly, there exists $R\in\mathcal{P}$ such that 
+    In this section, we fix a $g\in \mathcal{P}$. 
+    According to \eqref{eq:semigroupineq}, there exists an $R_0\in\mathcal{P}$ such that 
+\begin{align}
+     %|T_tg|\leq T_t|g|\leq e^{-\kappa(g)bt}R.
+     |T_tg|(x)
+     \leq e^{-\kappa(g)bt}R_0(x),
+     \quad t\geq 0,x\in E.
+\end{align}
+%new added
+Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R \in \mathcal P$ such that
+\begin{align}
+\label{eq:gcontrol}
+    T_s|T_t g|(x) 
+    \leq e^{-\kappa(g)bt} R(x), 
+    \quad t\geq 0,s\geq 0,x\in E.
+\end{align}
+%end new added
+
+Consider an incremental decomposition of $\langle g,X_t \rangle$. 
+    %Denote by $\{\mathcal{F}_t:t\geq 0\}$ the filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$. 
+    For each $t\geq 0$, denote by $\{\mathcal{F}_t:t\geq 0\}$ the natrual filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$. 
+    %For $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$. 
+    For each $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$. 
+    %For each $t-k\geq 1$, according to \eqref{eq:meanformula}, write
+    For each $k \in \mathbb N$ and $t\geq k+1$, according to \eqref{eq:meanformula}, write
 \begin{align*}
@@
 \end{align*}
-If $k=t$, let $M_t^t[g]:=\langle g_t,\mu\rangle$, where $\mu $ is the initial configuration. From now on, we assume $t$ is a positive integer, for simplicity. Thus
+    %If $k=t$, let $M_t^t[g]:=\langle g_t,\mu\rangle$, where $\mu $ is the initial configuration. 
+    For each $t\geq 0$, let $M_t^t[g]:=\langle g_t,\mu\rangle$ under $\mathbb P_\mu$, where $\mu $ is the initial configuration. 
+    From now on, we assume $t$ is a positive integer, for simplicity. Thus
 \begin{equation}\label{decomposition}
-    \langle g,X_t\rangle=\sum_{k=0}^{t}M_k^t[g]
-\end{equation}
-
-{\color{red} We have to emphasize that, if $t\notin \mathbb{N}$, there will appear an additional term corresponding to the interval $[\lfloor t \rfloor,t]$, which can be handled with the same techniques.}
+    \langle g,X_t\rangle
+    =\sum_{k=0}^{t}M_k^t[g]
+%new added
+    , \quad t \in \mathbb N.
+%end new added
+\end{equation}
+
+{\bf Jianjie: We have to emphasize that, if $t\notin \mathbb{N}$, there will appear an additional term corresponding to the interval $[\lfloor t \rfloor,t]$, which can be handled with the same techniques.
+}
 \subsection{Approximate expansion of characteristic function}
@@
 \begin{lem}\label{lemma1}
-There exists $R \in \mathcal{P}$, such that for any $k \in \mathbb{N}$, $x\in\mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
-$$e^{-(\alpha-\kappa(g)b) s}|w_{g_k}(x,s,\theta)|\leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), \quad s\geq 0.$$
+%For any $k \in \mathbb{N}$, $x\in\mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
+    Let $R \in \mathcal P$ be the control function in \eqref{eq:gcontrol}, then
+%$$e^{-(\alpha-\kappa(g)b) s}|w_{g_k}(x,s,\theta)|\leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), \quad s\geq 0.$$
+\begin{equation}
+    e^{-\alpha s}|w_{g_k}(x,s,\theta)|
+    \leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), 
+    \quad k\in \mathbb N, x\in \mathbb R^d, \theta \in \mathbb R, s\geq 0.
+\end{equation}
 \end{lem}
-Recall some result about the Kuznestov measures of $\{X_t, t\geq 0\}$.
+%comment
+    {\bf Zhenyao: The statement of the above Lemma is changed. I think the old version is not correct. I'm not sure how this influence the rest of the paper.
+
+    Also, there are some paragraphs below I deleted which are duplicated with the appendix.}
+%end comment
+%delete
+    %Recall some result about the Kuznestov measures of $\{X_t, t\geq 0\}$.
 Let $\mathbb{D}$ be the collection of $\mathcal{M}(\mathbb{R}^d)$-valued right continuous functions $t\rightarrow \omega_t$ on $(0,\infty)$ having zero as a trap.
-Denote by $\{\omega_t, t\geq0\}$ the coordinate process of $\mathbb{D}$ and
- $(\mathcal{C},\mathcal{C}_t)$ the natural $\sigma$-algebras on $\mathbb{D}$ generated by the coordinate process.
-
-It's known by \cite[section 8.4]{Li2011Measure} that  one can associate with $\{\mathbb{P}_{\delta_x}:x\in\mathbb{R}^d\}$ a family of $\sigma$-finite measures $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ defined on $(\mathbb{D},\mathcal{C})$ such that $\mathbb{N}_x\{0\}=0$,
-\begin{equation}\label{Nmeasure}
-   \int_{\mathbb{D}}(1-e^{-\langle f,\omega_t\rangle})\mathbb{N}_x(d\omega)=-\log \mathbb{P}_{\delta_x}(e^{-\langle f, X_t \rangle}), \quad f \in \mathcal{B}_b^+(\mathbb{R}^d), t>0,
-\end{equation}
-and, for $0<t_2<...<t_n<\infty$, and nonzero $\mu_1,...,\mu_n \in \mathcal{M}(\mathbb{R}^d)$,
-\begin{align*}
-    \mathbb{N}_x&\left(\omega_1\in d \mu_1,...,\omega_n \in d\mu_n\right)=\mathbb{N}_x(\omega_1\in d\mu_1)\mathbb{P}_{\mu_1}\left(X_{t_2-t_1}\in d \mu_2\right)...\\
-    &\mathbb{P}_{\mu_{n-1}}\left(X_{t_n-t_{n-1}}\in d \mu_n\right).
-\end{align*}
-We refer $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ as {\em Kuznestov measures} of $X$. For more general definition and further properties of such measures, we refer our readers to \cite{ZL,DK}.
-
-For any $\mu \in \mathcal{M}(\mathbb{R}^d)$, if $\mathcal{N}$ is a Poisson random measure defined in some probability space with intensity $\mathbb{N}_{\mu}(\cdot):=\int_{\mathbb{R}^d}\mathbb{N}_x(\cdot)~\mu(dx)$, then the super OU-process $\{X;\mathbb{P}_{\mu}\}$ can be realized by $\tilde{X}_t(\cdot)=\mu$ and
-\begin{align*}
-    \tilde{X}_t(\cdot):=\int_{\mathbb{D}}\omega_t(\cdot)\mathcal{N}(d\omega), \quad t\geq 0.
-\end{align*}
-See \cite[Theorem 8.24]{Li2011Measure} for a proof.
-
-What's more, if $\mathbb{P}_{\delta_x}|\langle f, X_t\rangle|<\infty$, then
-\begin{equation}\label{Nmean}
-    \mathbb{N}_x(\langle f,\omega_t \rangle) = \mathbb{P}_{\delta_x}(\langle f, X_t\rangle)=T^{\alpha}_t f(x).
-\end{equation}
-See \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
-
-\begin{proof}[Proof of Lemma \ref{lemma1}]
-
-Recall that $w_{g_k}(x,s,\theta)=\log\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
-Replace $f$ by $-i\theta g_k$ in equation \eqref{Nmeasure},\eqref{Nmean}, we obtain that $w_{g_k}(x,s,\theta)=\mathbb{N}_x\left(e^{i\theta\langle g_k,w_s\rangle}-1\right)$.
-Therefore,by the element inequality $|e^{i\theta}-1|\leq|\theta|$ for $\theta \in \mathbb{R}$, we have 
-$$|w_{g_k}(x,s,\theta)|=|\mathbb{N}_x(e^{i\theta\langle g_{k},\omega_s \rangle}-1)|\leq |\theta|\mathbb{N}_x(\langle|g_k|,\omega_s\rangle)\leq|\theta|T_{s+k}^{\alpha}|g|$$
-At last, by \eqref{semigroupineq}, we get the desired result.
+Denote by $\{\omega_t, t\geq0\}$ the coordinate process of $\mathbb{D}$ and $(\mathcal{C},\mathcal{C}_t)$ the natural $\sigma$-algebras on $\mathbb{D}$ generated by the coordinate process.
+
+    %It's known by \cite[section 8.4]{Li2011Measure-valued} that  one can associate with $\{\mathbb{P}_{\delta_x}:x\in\mathbb{R}^d\}$ a family of $\sigma$-finite measures $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ defined on $(\mathbb{D},\mathcal{C})$ such that $\mathbb{N}_x\{0\}=0$,
+%\begin{equation}\label{Nmeasure}
+   %\int_{\mathbb{D}}(1-e^{-\langle f,\omega_t\rangle})\mathbb{N}_x(d\omega)=-\log \mathbb{P}_{\delta_x}(e^{-\langle f, X_t \rangle}), \quad f \in \mathcal{B}_b^+(\mathbb{R}^d), t>0,
+%\end{equation}
+%and, for $0<t_2<...<t_n<\infty$, and nonzero $\mu_1,...,\mu_n \in \mathcal{M}(\mathbb{R}^d)$,
+%\begin{align*}
+    %\mathbb{N}_x&\left(\omega_1\in d \mu_1,...,\omega_n \in d\mu_n\right)=\mathbb{N}_x(\omega_1\in d\mu_1)\mathbb{P}_{\mu_1}\left(X_{t_2-t_1}\in d \mu_2\right)...\\
+    %&\mathbb{P}_{\mu_{n-1}}\left(X_{t_n-t_{n-1}}\in d \mu_n\right).
+%\end{align*}
+    %We refer $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ as {\em Kuznestov measures} of $X$.
+For more general definition and further properties of such measures, we refer our readers to \cite{Li2011Measure,DK}.
+
+    %For any $\mu \in \mathcal{M}(\mathbb{R}^d)$, if $\mathcal{N}$ is a Poisson random measure defined in some probability space with intensity $\mathbb{N}_{\mu}(\cdot):=\int_{\mathbb{R}^d}\mathbb{N}_x(\cdot)~\mu(dx)$, then the super OU-process $\{X;\mathbb{P}_{\mu}\}$ can be realized by $\tilde{X}_t(\cdot)=\mu$ and
+%\begin{align*}
+    %\tilde{X}_t(\cdot):=\int_{\mathbb{D}}\omega_t(\cdot)\mathcal{N}(d\omega), \quad t\geq 0.
+%\end{align*}
+    %See \cite[Theorem 8.24]{Li2011Measure-valued} for a proof.
+
+    %What's more, if $\mathbb{P}_{\delta_x}|\langle f, X_t\rangle|<\infty$, then
+%\begin{equation}\label{Nmean}
+    %\mathbb{N}_x(\langle f,\omega_t \rangle) = \mathbb{P}_{\delta_x}(\langle f, X_t\rangle)=T^{\alpha}_t f(x).
+%\end{equation}
+    %See \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
+%end delete
+
+%\begin{proof}[Proof of Lemma \ref{lemma1}]
+\begin{proof}
+%Recall that $w_{g_k}(x,s,\theta)=\log\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
+    Recall that $w_{g_k}(x,s,\theta)=\operatorname{Log}\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
+    %Replace $f$ by $-i\theta g_k$ in equation \eqref{Nmeasure},\eqref{Nmean}, we obtain that $w_{g_k}(x,s,\theta)=\mathbb{N}_x\left(e^{i\theta\langle g_k,w_s\rangle}-1\right)$.
+    %Therefore,by the element inequality $|e^{i\theta}-1|\leq|\theta|$ for $\theta \in \mathbb{R}$, we have
+    %$$|w_{g_k}(x,s,\theta)|=|\mathbb{N}_x(e^{i\theta\langle g_{k},\omega_s \rangle}-1)|\leq |\theta|\mathbb{N}_x(\langle|g_k|,\omega_s\rangle)\leq|\theta|T_{s+k}^{\alpha}|g|$$
+    Let $R \in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
+    From \eqref{eq: upper bound for vf} in the appendix, we have for each $k \in \mathbb{N}$, $x\in\mathbb{R}^d$, $\theta\in \mathbb{R}$ and $s\geq 0$,
+\begin{equation}
+    w_{g_k}(x,s,\theta) 
+    \leq |\theta| (T_s^\alpha |g_k|) (x) 
+    = |\theta| (T_{s}^\alpha |T^\alpha_k g|) (x)
+    \leq |\theta| e^{\alpha(s+k)}e^{-\kappa(g)bk}R(x).
+    \qedhere
+\end{equation}
 \end{proof}
- For any $k \in \{0,1,...,t\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$, by the Markov property of $X$, we have
- \begin{align*}
-      \mathbb{P}_{\mu}(e^{i\theta M_k^t[g]}|\mathcal{F}_{t-k-1}) &=\mathbb{P_{\mu}}\left [\mathbb{P}_{\nu}\left(e^{i\theta(\langle g_k,X_1\rangle-\langle T_1^{\alpha}g_k,\nu\rangle)}\right)|_{\nu=X_{t-k-1}}\right]   \\
-      &=\mathbb{P}_{\mu}\left[ e^{\langle w_{g_k}(\cdot,1,\theta),X_{t-k-1}\rangle -i \theta\langle T_1^{\alpha}g_k,X_{t-k-1}\rangle}\right].
+    %For any $k \in \{0,1,...,t\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$, by the Markov property of $X$, we have
+    For each $t \in \mathbb N$ and $k \in \{0,1,...,t-1\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$.
+    By the Markov property of $X$, we have
+ \begin{align*}
+    &\mathbb{P}_{\mu}(e^{i\theta M_k^t[g]}|\mathcal{F}_{t-k-1}) 
+    %&=\mathbb{P_{\mu}}\left [\mathbb{P}_{\nu}\left(e^{i\theta(\langle g_k,X_1\rangle-\langle T_1^{\alpha}g_k,\nu\rangle)}\right)|_{\nu=X_{t-k-1}}\right]   \\
+    =\mathbb{P}_{\mu}(e^{i\theta (\langle X_{t-k},g_k\rangle - \langle X_{t-(k+1)},g_{k+1}\rangle)}|\mathcal{F}_{t-k-1}) 
+    %\\&=\mathbb P_\mu \big [\mathbb P_{X_{t-k-1}} [e^{i\theta(\langle g_k,X_1\rangle)}]e^{-i\theta \langle T_1^{\alpha}g_k,X_{t-k-1}\rangle}\big]
+    \\&=\mathbb P_{X_{t-k-1}} [e^{i\theta(\langle g_k,X_1\rangle)}]e^{-i\theta \langle T_1^{\alpha}g_k,X_{t-k-1}\rangle}   
+    \\&= e^{\langle w_{g_k}(\cdot,1,\theta),X_{t-k-1}\rangle -i \theta\langle T_1^{\alpha}g_k,X_{t-k-1}\rangle},
+%new added
+    \quad \mu \in \mathcal M(\mathbb R^d), \theta \in \mathbb R.
+%end added
 \end{align*}
@@
 \begin{equation}\label{w2function}
-    \tilde{w}_{f}(x,t,\theta)=i\theta T^{\alpha}_t f(x) + \int_0^t T^{\alpha}_{t-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds
+    %\tilde{w}_{f}(x,t,\theta)=i\theta T^{\alpha}_t f(x) + \int_0^t T^{\alpha}_{t-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds
+    \tilde{w}_{f}(x,t,\theta)
+    := i\theta T^{\alpha}_t f(x) + \int_0^t T^{\alpha}_{t-s}\psi_0(-i\theta T_s^{\alpha}f(\cdot))(x)ds,
+    \quad x\in \mathbb R^d,t\geq 0, \theta \in \mathbb R.
 \end{equation}
@@
 \begin{lem}\label{lemma2}
-There exists $R \in \mathcal{P}$ and $p_1 >1+\beta$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have 
-$$|w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_1}R(x),\quad x\in \mathbb{R}^d,\theta\in \mathbb{R}.$$
+%There exists $R_1 \in \mathcal{P}$ and $p_1 >1+\beta$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have
+There exists $R_1 \in \mathcal{P}$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have
+\begin{align}
+    |w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|
+    \leq |\theta e^{(\alpha-\kappa(g)b)k}|^{1+2\beta}R_1(x),
+    \quad x\in \mathbb{R}^d,\theta\in \mathbb{R}.
+\end{align}
+
 \end{lem}
 \begin{proof}
- Using the fact that 
- \begin{align}
-      |x^{1+\beta}-y^{1+\beta}|\leq C (|x|^{\beta}+|y|^{\beta})|x-y|\label{element}
- \end{align}
-for $x,y \in \mathbb{C}$ such that ${\rm Re~} x \geq 0, {\rm Re~} y\geq 0$, we have
-\begin{align*}
-   |w_{g_k}(x,s,\theta)-&\tilde{w}_{g_k}(x,s,\theta)|\\
-   \leq &\int_0^s T_{s-v}^{\alpha}\left(|(-w_{g_k}(\cdot,v,\theta))^{1+\beta}-(-i\theta T_v^{\alpha}g_k)^{1+\beta}|\right)(x)~dv\\
-   \leq &\int_0^s T_{s-v}^{\alpha}\left( |w_{g_k}-i\theta T_v^{\alpha}g_{k}|\left(|w_{g_k}|^{\beta}+|i\theta T_v^{\alpha}g_k|^{\beta}\right)\right)(x)~dv, 
-\end{align*}
-as $\exp({\rm Re~}w_{g_k})=|\exp(w_{g_k})|=\left|\mathbb{P}_{\delta_x}\exp(i\theta \langle  g_k,X_t\rangle)\right|\leq 1$, this is to say ${\rm Re~}(-w_{g_k})\geq0$.
-
-Notice that, for $0\leq v \leq 1$, $x\in \mathbb{R}^d$ and $\theta \in \mathbb{R}$, by Lemma \ref{lemma1} and \eqref{semigroupineq}, there exists $R_1,R_2\in \mathcal{P}$ such that
-\begin{align*}
-    |w_{g_{k}}(x,v,\theta)|\leq &|\theta|e^{(\alpha-\kappa(g)b)k}R_1(x),\\
-    |i\theta T_v^{\alpha}g_k(x)|\leq & |\theta|e^{(\alpha-\kappa(g)b)k}R_1(x),
-\end{align*}
-and
-\begin{align}
-   |w_{g_{k}}(x,v,\theta)-i\theta T_v^{\alpha}g_k(x)|=&\left| \int_0^v T^{\alpha}_{v-u}(-w_{g_k}(\cdot,u,\theta))^{1+\beta}(x)du\right| \nonumber\\ 
-   \leq & \int_0^1 T_{1-u}^{\alpha}(|w_{g_k}(\cdot,u,\theta)|^{1+\beta})(x)du \nonumber \\
-   \leq & |\theta e^{(\alpha-\kappa(g)b)k}|^{1+\beta}R_2(x). \label{Zineq}
-\end{align}
-In consequence, take $p_1=2+\beta$, we obtain the desired result.
+%As $\exp({\rm Re~}w_{g_k})=|\exp(w_{g_k})|=\left|\mathbb{P}_{\delta_x}\exp(i\theta \langle  g_k,X_t\rangle)\right|\leq 1$ implying ${\rm Re~}(-w_{g_k})\geq0$,
+From \eqref{eq: -v has positive real part} we know that $\operatorname{Re}(-w_{g_k})\geq 0$.
+%we use the fact that
+%\begin{align}
+    %|x^{1+\beta}-y^{1+\beta}|
+    %\leq C (|x|^{\beta}+|y|^{\beta})|x-y|\label{element},
+%\end{align}
+    %for $x,y \in \mathbb{C}$ such that ${\rm Re~} x \geq 0, {\rm Re~} y\geq 0$ to get
+    Let $C_0>0$ be the constant in Lemma \ref{lem: Lip of power function}, then from \eqref{eq:chareq2}, we have
+\begin{align}
+\label{eq: estimate of wgk}
+   &|w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|
+   \\&\leq \int_0^s T_{s-v}^{\alpha}\left(|(-w_{g_k}(\cdot,v,\theta))^{1+\beta}-(-i\theta T_v^{\alpha}g_k)^{1+\beta}|\right)(x)~dv
+   \\&\leq C_0\int_0^s T_{s-v}^{\alpha}\left( |w_{g_k}(\cdot,v,\theta)-i\theta T_v^{\alpha}g_{k}|\left(|w_{g_k}(\cdot,v,\theta)|^{\beta}+|i\theta T_v^{\alpha}g_k|^{\beta}\right)\right)(x)~dv.
+\end{align}
+%Notice that, for $0\leq v \leq 1$, $x\in \mathbb{R}^d$ and $\theta \in \mathbb{R}$, by Lemma \ref{lemma1} and \eqref{eq:gcontrol}, we have
+   Let $R\in \mathcal P$ be the control function in both \eqref{eq:gcontrol} and Lemma \ref{lemma1}, then for $0\leq v \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
+\begin{align}
+\label{eq: upper bound of wgk}
+    %|w_{g_{k}}(x,v,\theta)|\leq &|\theta|e^{(\alpha-\kappa(g)b)k}(e^{(\alpha-\kappa(g)b)v}R(x))\leq|\theta|e^{(\alpha-\kappa(g)b)k}(C_1R(x)),
+    |w_{g_{k}}(x,v,\theta)|
+    &\leq |\theta|e^{(\alpha-\kappa(g)b)k+\alpha}R(x),
+    \\
+    |i\theta T_v^{\alpha}g_k(x)|
+    &\leq |\theta| e^{\alpha(k+1)}T_v|T_k g|(x)
+    \leq |\theta|e^{(\alpha-\kappa(g)b)k+\alpha}R(x).
+\end{align}
+%deleted
+    %where $C_1=\max\{1,e^{(\alpha-\kappa(g)b)}\}$.
+%end deleted
+%new added
+    Observe that $R^{1+\beta}\in \mathcal P$. 
+    According to \eqref{eq:semigroupineq}, there exists an $\tilde R_0 \in \mathcal P$ such that
+\begin{align}
+\label{eq: tilde R0}
+    |T_t (R^{1+\beta})(x)| 
+    \leq \tilde R_0(x),
+    \quad t\geq0, x\in E.
+\end{align}
+    According \eqref{eq:chareq2}, \eqref{eq: upper bound of wgk} and above, for $0\leq v \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
+%end new
+\begin{align}
+\label{eq: Zineq}
+   &|w_{g_{k}}(x,v,\theta)-i\theta T_v^{\alpha}g_k(x)|
+   =\Big| \int_0^v T^{\alpha}_{v-u}(-w_{g_k}(\cdot,u,\theta))^{1+\beta}(x)du\Big| 
+   %\\\leq & \int_0^1 T_{1-u}^{\alpha}(|w_{g_k}(\cdot,u,\theta)|^{1+\beta})(x)du \nonumber \\
+   \\&\leq \int_0^v T_{v-u}^{\alpha}(|w_{g_k}(\cdot,u,\theta)|^{1+\beta})(x)du
+   \leq  |\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+\beta}\int_0^v (T_{v-u}^{\alpha}R^{1+\beta})(x)du
+   %\\\leq &C_1^{1+\beta}e^{\alpha}|\theta e^{(\alpha-\kappa(g)b)k}|^{1+\beta}R^{1+\beta}(x)\nonumber\\
+   \\&\leq e^{\alpha}|\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+\beta}\tilde R(x).
+%deleted
+   %\\= & |\theta e^{(\alpha-\kappa(g)b)k}|^{1+\beta}R_2(x),
+%end deleted
+\end{align}
+%where $R_2(x)=C_1^{1+\beta}e^{\alpha}R^{1+\beta}(x)$.
+    According to \eqref{eq:semigroupineq}, since $\tilde RR^{\beta} \in \mathcal P$, there exists an $\tilde R_1\in \mathcal P$ such that
+\[
+    |T_t(\tilde RR^{\beta})(x)| 
+    \leq \tilde R_1(x),
+    \quad t\geq0, x\in E.
+\]
+%In consequence, 
+As a consecuence of \eqref{eq: estimate of wgk}, \eqref{eq: Zineq}, \eqref{eq: upper bound of wgk} and the above, for $k \in \mathbb{N}$, $0\leq s \leq 1$, $x\in E$ and $\theta \in \mathbb R$, we have
+\begin{align}
+    &|w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|
+%new added
+    \\&\leq C_0e^{\alpha}|\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta} \int_0^s T_{s-v}^{\alpha}( \tilde RR^{\beta})(x)~dv
+%end new added
+    %\\&\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{2+\beta}\cdot 2CC_1e^{\alpha}R(x)R_2(x).
+    \\&\leq C_0e^{2\alpha}|\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta}\tilde R_1(x).
+    \qedhere
+\end{align}
+%delete
+    %Take $p_1=2+\beta$ and $R_1(x)=2CC_1e^{\alpha}R(x)R_2(x)$, we obtain the desired result.
+%end delete
 \end{proof}
-For $f\in \mathcal{R}$, define 
-$$Z_f(x,\theta):=\int_0^1 T^{\alpha}_{1-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds ,$$
-and let $Z_f(x)=Z_f(x,1)$. We observe that
+
+%new added
+    It can be verified from its definition that $(\rho z)^{1+\beta} = \rho^{1+\beta}z^{1+\beta}$ for all $\rho \in [0,\infty)$ and $z\in \mathbb C_+$.
+%end new
+%For each $f\in \mathcal{R}$, define
+For each $f\in \mathcal{P}$, define
+\[
+    Z_f(x,\theta)
+    %:=\int_0^1 T^{\alpha}_{1-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds ,
+    :=\int_0^1 T^{\alpha}_{1-s}\big((-i\theta T_s^{\alpha}f)^{1+\beta}\big)(x)ds ,
+%new
+    \quad x\in E, \theta \in \mathbb R.
+%end new
+\]
+and let $Z_f(x)=Z_f(x,1)$. 
+%Observe that
+Then we have
 \begin{equation}\label{zfunction}
-    Z_f(x,\theta)=\theta^{1+\beta}Z_f(x).
-\end{equation}
-
-\begin{cor}\label{corollary2}
-  There exists $R \in \mathcal{P}$ such that for any $k\in\{0,1,...,t\}$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have 
-  \begin{align}
-       &|Z_{g_k}(x,\theta)|\leq |\theta|^{1+\beta}e^{(\alpha-\kappa(g)b)(1+\beta)k}R(x) \label{zineq1},\\
-       &|Z_{g_k}(x)|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}R(x). \label{zineq2}
+    Z_f(x,\theta)=\theta^{1+\beta}Z_f(x),
+%new
+    \quad x\in E, \theta \in \mathbb R.
+%end new
+\end{equation}
+
+\begin{cor}
+\label{cor: corollary2}
+    %For any $k\in\{0,1,...,t\}$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
+    There exists $R_2\in \mathcal P$ such that for each $k\in\mathbb N$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
+\begin{align}
+\label{zineq2}
+    |Z_{g_k}(x)|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}R_2(x),
+\end{align}
+    and consequently,
+\begin{align}
+    |Z_{g_k}(x,\theta)|\leq |\theta|^{1+\beta}e^{(\alpha-\kappa(g)b)(1+\beta)k}R_2(x). \label{zineq1}
 \end{align}
@@
 \begin{proof}
-     By \eqref{semigroupineq}, we have
-   $$|Z_{g_k}(x)|\leq \int_0^1 T_{1-s}^{\alpha}(|T_s^{\alpha}g_k|^{1+\beta})(x)ds\leq  e^{(\alpha-\kappa(g)b)(1+\beta)k}R(x), \quad x\in \mathbb{R}^d,$$
-   for some $R\in \mathcal{P}$. The proof of \eqref{zineq1} is similar with \eqref{zineq2}.
+%new
+    Let $c_0 > 0$ be the constant in \eqref{eq: upper bound for beta power of z}.
+%end new
+    %By \eqref{eq:gcontrol}, we have
+    Let $R\in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
+    Let $\tilde R_0 \in \mathcal P$ be the control function in \eqref{eq: tilde R0}.
+    Now, we have for each $k\in\mathbb N$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$,
+\begin{align}
+    |Z_{g_k}(x)|
+    %&\leq \int_0^1 T_{1-s}^{\alpha}(|T_s^{\alpha}g_k|^{1+\beta})(x)ds \leq\int_0^t T_{1-s}^{\alpha}\left(|C_1 e^{(\alpha-\kappa(g)b)k}|R(x)\right )^{1+\beta}
+    &\leq c_0\int_0^1 T_{1-s}^{\alpha}(|T_s^{\alpha}g_k|^{1+\beta})(x)ds 
+    \leq c_0 \int_0^1 T_{1-s}^{\alpha}\Big(\big(e^{(\alpha-\kappa(g)b)k+\alpha}R\big)^{1+\beta}\Big)(x)
+    \\&\leq c_0e^{\alpha(2+\beta)} e^{(\alpha-\kappa(g)b)(1+\beta)k}\tilde R_2(x). 
+\qedhere
+\end{align}
+%delete
+    %The proof of \eqref{zineq1} is similar with \eqref{zineq2}.
+%end delete
 \end{proof}
 
-\begin{cor}\label{corollary1}
-There exists $R \in \mathcal{P}$ and $p_2 >1+\beta$ such that for any $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, we have 
-$$\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}=1+\langle Z_{g_k}(\cdot,\theta),\mu\rangle+\langle err(\cdot,\theta),\mu\rangle$$
-where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R(\cdot)$.
+%comments
+    {\bf Zhenyao: I don't think the following corollary in the old version is accurate. Here is what I think the correct form should be.}
+%end comment
+\begin{cor}
+\label{cor: corollary1}
+%There exists $R_3 \in \mathcal{P}$ and $p_2 >1+\beta$ such that for any $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, we have
+There exists an $R_3 \in \mathcal{P}$ such that for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, we have
+\[
+    %\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}
+    \mathbb P_{\mu}[e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}]
+    %=1+\langle Z_{g_k}(\cdot,\theta),\mu\rangle+\langle err(\cdot,\theta),\mu\rangle
+    =1+\langle Z_{g_k}(\cdot,\theta),\mu\rangle+ err(k,\mu,\theta),
+\]
+    %where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R_3(\cdot)$.
+    where $|err(k,\mu,\theta)| \leq (|\theta e^{(\alpha-\kappa(g)b)k}|^{2+2\beta} + |\theta e^{(\alpha-\kappa(g)b)k}|^{1+2\beta} )\langle R_3,\mu\rangle$.
 \end{cor}
@@
 \begin{proof}
-    Let $ w_f(x,\theta)=w_f(x,1,\theta)$, $\tilde{w}_f(x,\theta)=\tilde{w}_f(x,1,\theta)$ for short, and denote
-\begin{align}\label{charfirst}
-    \varphi_{\mu}(\theta)=\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}=e^{(\langle w_{g_k}(\cdot,\theta),\mu \rangle-i\theta \langle T_1^{\alpha} g_k, \mu \rangle)},
-\end{align}
- we have
-\begin{align*}
-    |\varphi_{\mu}(\theta)-1-& \langle Z_{g_k}(\cdot, \theta),\mu\rangle|\\
-    &\leq|\varphi_{\mu}(\theta)-1-\left( \langle w_{g_k}(\cdot,\theta), \mu \rangle-i\theta \langle T_1^{\alpha}g_k,\mu\rangle\right)|\\
-    &+|\langle w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta),\mu \rangle|.
-\end{align*}
-Using Lemma \ref{lemma2}, \eqref{Zineq} and the fact that if $ {\rm Re~} z\leq 0$, $|e^z-1-z|\leq|z|^2$,   we get, for any $\theta \in \mathbb{R}$, there exists $R\in \mathcal{P}$ such that 
-\begin{align*}
-    |\varphi_{\mu}(\theta)-1-& \langle Z_{g_k}(\cdot, \theta),\mu\rangle|\\
-    &\leq 2|\langle w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k, \mu \rangle|^2 + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle\\
-    &\leq |\theta_{k}|^{2(1+\beta)}\langle R,\mu\rangle + |\theta_{k}|^{2+\beta}\langle R,\mu\rangle,
-\end{align*}
-where $\theta_k=\theta e^{(\alpha-\kappa(g)b)k}$. By implicitly assuming that $|\theta_k|\leq 1$, and taking $p_2=\min \{2(1+\beta), 2+\beta\}$, we get the desired result.
+    Let $ w_f(x,\theta)=w_f(x,1,\theta)$, $\tilde{w}_f(x,\theta)=\tilde{w}_f(x,1,\theta)$ for short, and write
+\begin{align}
+\label{eq: definition of varphi-mu-k-theta}
+    %\varphi_{\mu}(\theta)
+    \varphi_{k,\mu}(\theta)
+    %=\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}
+    =\mathbb{P}_{\mu}[e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}]
+    =e^{(\langle w_{g_k}(\cdot,\theta),\mu \rangle-i\theta \langle T_1^{\alpha} g_k, \mu \rangle)},
+    \quad \theta \in \mathbb R.
+\end{align}
+    Then we have
+\begin{align*}
+    &|\varphi_{k,\mu}(\theta)-1-\langle Z_{g_k}(\cdot, \theta),\mu\rangle|\\
+    &\leq|\varphi_{\mu,k}(\theta)-1-\left( \langle w_{g_k}(\cdot,\theta), \mu \rangle-i\theta \langle T_1^{\alpha}g_k,\mu\rangle\right)| + |\langle w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta),\mu \rangle|.
+\end{align*}
+%Using Lemma \ref{lemma2}, \eqref{eq: Zineq} and the fact that if $ {\rm Re~} z\leq 0$, $|e^z-1-z|\leq|z|^2$,   we get, for any $\theta \in \mathbb{R}$ and $k\in \mathbb{N}$, 
+    Let $R_1\in \mathcal P$ be the control function in Lemma \ref{lemma2}. 
+    Let $\tilde R$ be the control function in \eqref{eq: Zineq}. 
+    Notice that
+$
+    \operatorname{Re} \big(w_{g_k}(x,\theta) - i\theta T_1^\alpha g_k(x)\big)
+    = \operatorname{Re} w_{g_k}(x,\theta)
+    \leq 0,
+$
+    (see \eqref{eq: -v has positive real part} in the appendix); and if $ \operatorname{Re} z\leq 0$, we have $|e^z-1-z|\leq |z|^2$, (see Lemma \ref{lem: estimate of exponential remaining} in the appendix).
+    Therefore, for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, using Jensen's inequality,
+\begin{align*}
+    &|\varphi_{k,\mu}(\theta)-1- \langle Z_{g_k}(\cdot, \theta),\mu\rangle|\\
+    %&\leq 2|\langle w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k, \mu \rangle|^2 + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle\\
+    &\leq |\langle w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k, \mu \rangle|^2 + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle
+%new added
+    \\&\leq \langle |w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k|^2, \mu \rangle + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle
+%end new
+    %\\&\leq |\theta_{k}|^{2(1+\beta)}\langle R_2,\mu\rangle + |\theta_{k}|^{2+\beta}\langle R_1,\mu\rangle,
+    \\&\leq e^{2\alpha}|\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{2+2\beta}\langle \tilde R^2,\mu\rangle + |\theta e^{(\alpha-\kappa(g)b)k}|^{1+2\beta}\langle R_1,\mu\rangle.
+    \qedhere
+\end{align*}
+%deleted
+    %where $\theta_k=\theta e^{(\alpha-\kappa(g)b)k}$. By implicitly assuming that $|\theta_k|\leq 1$, and taking $p_2=\min \{2(1+\beta), 2+\beta\}$ and $R_3=R_1+R_2$, we get the desired result.
+%end deleted
 \end{proof}
-\begin{rem}\label{remark1}
+%comment
+    {\bf Zhenyao: Again, I think the following remark is not accurate. Even if it is accurate, it should be proved with more details.}
+%comment
+\begin{rem}
+\label{remark1}
    For $0<s\leq 1$, let
@@
    which has the same estimation with \eqref{zineq1}.
-moreover, the decomposition in Corollary \ref{corollary1} is also hold for $\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)$, this is to say,
+moreover, the decomposition in Corollary \ref{cor: corollary1} is also hold for $\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)$, this is to say,
    $$\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}=1+\langle Z_{g_k}(\cdot,s,\theta),\mu\rangle+\langle err(\cdot,\theta),\mu\rangle$$
-   where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R(\cdot)$, for some $R\in \mathcal{P}, p>1+\beta$.
+   where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R_3(\cdot)$.
 \end{rem}
@@
  In this subsection, for any $\gamma \in [0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle $ by an exponential function depending on $\kappa(g)$.
-\begin{lem}\label{lemma23}
-For any $0\leq \gamma < \beta$ there exists a constant $C>0$ such that
-$$\|M_k^t[g]\|_{1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k},$$
+ %comment
+    {\bf Zhenyao: I changed the statement and the proof of the following Lemma. I think the old version has too many mistakes.}
+%end comment
+%deleted
+\begin{comment}
+\begin{lem}\label{lem: lemma23}
+For any $0\leq \gamma < \beta$ there exists a constant $C_2>0$ such that
+$$\|M_k^t[g]\|_{1+\gamma}\leq C_2 e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k},$$
 for any $k \in \{0,...,t\}$.
 \end{lem}
-
 \begin{proof}
-    Let $C_k=e^{(\alpha-\kappa(g)b)k}$, and, for convenience, define $A:=\{|M_t^k[g]|>C_k\}$, $A_{\mu}:=\{|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\mu\rangle|>C_k\}$.
-$$\mathbb{P}_{\mu}|M_k^t[g]|^{1+\gamma}=\mathbb{P}_{\mu}|M_k^t[g]\mathbf{1}_{A^c}|^{1+\gamma}+\mathbb{P}_{\mu}|M_k^t[g]\mathbf{1}_{A}|^{1+\gamma}=I+II.$$
+    %Let $C(k)=e^{(\alpha-\kappa(g)b)k}$, and, for convenience, define $A:=\{|M_t^k[g]|>C(k)\}$, $A_{\mu}:=\{|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\mu\rangle|>C(k)\}$.
+    Let $C(k)=e^{(\alpha-\kappa(g)b)k}$.
+    Define events $A:=\{|M_t^k[g]|>C(k)\}$ and $A_{k,\mu}:=\{|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\mu\rangle|>C(k)\}$ for each $k \in \mathbb N$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support.
+    Notice that
+\[
+    \mathbb{P}_{\mu}[|M_k^t[g]|^{1+\gamma}]
+    =\mathbb{P}_{\mu}[|M_k^t[g]\mathbf{1}_{A^c}|^{1+\gamma}]+\mathbb{P}_{\mu}[|M_k^t[g]\mathbf{1}_{A}|^{1+\gamma}]
+    =:I+II.
+\]
     For the first part,
 \begin{align*}
-    I\leq C_k^{1+\gamma}=&e^{(\alpha-\kappa(g)b)k(1+\gamma)}=e^{-\alpha(t-k)}e^{\alpha t}e^{(\gamma \alpha-\kappa(g)(1+\gamma)b)k}\\
-    \leq &e^{\alpha t}e^{(\gamma \alpha-\kappa(g)(1+\gamma)b)k},
-\end{align*}
-as $k\leq t$.
+    I\leq C(k)^{1+\gamma}
+    =e^{(\alpha-\kappa(g)b)k(1+\gamma)}
+    \leq e^{\alpha t}e^{(\gamma \alpha-\kappa(g)(1+\gamma)b)k},
+\end{align*}
+    since $k\leq t$.
 
@@
 \begin{align*}
-    II=\mathbb{P}_{\mu}\left[\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\mathbf{1}_{A_{\nu}}\right]|_{\nu=X_{t-k-1}}\right]
-\end{align*}
-Observe that, for any $\nu \in \mathcal{M}(\mathbb{R}^d)$
-\begin{align}
-    &\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\right] \label{temp1}\\ 
-    &=(1+\gamma)\int_0^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|\mathbf{1}_{A_{\nu}}>\lambda\right)d\lambda \nonumber\\
-    &\leq (1+\gamma)\int_{C_{k}}^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\right)d\lambda.\nonumber
-\end{align}
+    II
+    %=\mathbb{P}_{\mu}\left[\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\mathbf{1}_{A_{\nu}}\right]|_{\nu=X_{t-k-1}}\right]
+    =\mathbb{P}_{\mu}\big[\mathbb{P}_{\nu}[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\mathbf{1}_{A_{k,\nu}}]|_{\nu=X_{t-k-1}}\big].
+\end{align*}
+%comment
+{\bf Zhenyao: Just wondering why $X$ has compact support a.s.ly.}
+%end comment
+%Observe that, for any $\nu \in \mathcal{M}(\mathbb{R}^d)$
+Observe that, for any $\nu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, from Fubini's theorem,
+\begin{align}
+    %&\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\right] \label{temp1}\\
+    &\mathbb{P}_{\nu}[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma} \mathbf 1_{A_{k,\nu}}] \label{temp1}\\
+    %&=(1+\gamma)\int_0^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|\mathbf{1}_{A_{\nu}}>\lambda\right)d\lambda \nonumber\\
+    &=(1+\gamma)\int_0^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|\mathbf{1}_{A_{k,\nu}}>\lambda)d\lambda \\
+    &\leq (1+\gamma)\int_{C(k)}^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\right)d\lambda.\nonumber
+\end{align}
+%comment
+    {\bf Zhenyao: Why the above inequality is true?}
+%end comment
 Using the element inequality $\mathbb{P}(|Y|>2/u)\leq u^{-1}\int_{-u}^{u}(1-\varphi(t))dt$, see,\cite[Chaper 3]{Durrett2010Probability}, for example, where $Y$ is a random variable corresponding to characteristic function $\varphi(t)$, $u\geq 0$, we have
@@
 $$\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\right)\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1-\varphi_{\nu}(\theta))d\theta,$$
-where $\varphi_{\nu}(\theta))$ has been defined in Corollary \eqref{corollary1}.
-What's more, as $g_k=T_k^{\alpha}g$, by Corollary \eqref{corollary1} and Corollary \eqref{corollary2}, we get, for any $\theta\in\mathbb{R}$, there exists $R_1,R_2 \in \mathcal{P}$ and $p>\beta$, such that
+where $\varphi_{\nu}(\theta))$ has been defined in Corollary \eqref{cor: corollary1}.
+What's more, as $g_k=T_k^{\alpha}g$, by Corollary \eqref{cor: corollary1} and Corollary \eqref{cor: corollary2}, we get, for any $\theta\in\mathbb{R}$, there exists $p>\beta$ (actually, we just take $p=p_2-1$ ), such that
 \begin{align*}
     |1-\varphi_{\nu}(\theta)|&\leq|\langle Z_{g_k}(\cdot,\theta),\nu \rangle|+|\langle err(\cdot,\theta),\nu \rangle|\\
-    &\leq|\theta_k|^{1+\beta}\langle R_1,\nu\rangle+|\theta_k|^{1+p}\langle R_1, \nu \rangle\\
-    &\leq (|\theta_k|^{1+\beta}+|\theta_k|^{1+p})\langle R_2, \nu \rangle.
+    &\leq|\theta_k|^{1+\beta}\langle R_2,\nu\rangle+|\theta_k|^{1+p}\langle R_3, \nu \rangle\\
+    &\leq (|\theta_k|^{1+\beta}+|\theta_k|^{1+p})\langle R_2+R_3, \nu \rangle.
 \end{align*}
@@
     &\mathbb{P}_{\nu}\big(|\langle T_k^{\alpha}g, X_1 \rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\big)\\
-    &\leq\lambda\int_0^{2/\lambda}(|\theta_k|^{1+\beta}+|\theta_k|^{1+p})\langle R_2, \nu \rangle d\theta\\
-    &\leq C_1(e^{(\alpha-\kappa(g)b)k(1+\beta)}\lambda^{-(1+\beta)}+e^{(\alpha-\kappa(g)b)k(1+p)}\lambda^{-(1+p)})\langle R_2,\nu \rangle,
-\end{align*}
-Where $C_1=\max\{\frac{2^{1+\beta}}{2+\beta}, \frac{2^{2+p}}{2+p}\}$ is a constant real number. Then by calculating the integral in formula \eqref{temp1}, we get
+    &\leq\lambda\int_0^{2/\lambda}(|\theta_k|^{1+\beta}+|\theta_k|^{1+p})\langle R_2+R_3, \nu \rangle d\theta\\
+    &= \frac{2^{2+\beta}}{2+\beta}e^{(\alpha-\kappa(g)b)k(1+\beta)}\lambda^{-(1+\beta)}+ \frac{2^{2+p}}{2+p}e^{(\alpha-\kappa(g)b)k(1+p)}\lambda^{-(1+p)})\langle R_2+R_3,\nu \rangle,
+\end{align*}
+ Then by calculating the integral in formula \eqref{temp1}, we get
 \begin{align*}
     &\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma} \right] \\
-    &\leq C_2\left(e^{(\alpha-\kappa(g)b)k(1+\beta)}C_k^{\gamma-\beta}+e^{(\alpha-\kappa(g)b)k(1+p)}C_k^{\gamma-p}\right)\langle R_2,\nu\rangle\\
-    &\leq C_2 e^{(\alpha-\kappa(g)b)k(1+\gamma)}\langle R_2,\nu\rangle,
-\end{align*}
-for some $C_2>0$. At last, using the mean formula \eqref{meanformula} and \eqref{semigroupineq}, we get
-\begin{align*}
-    II &\leq C_2e^{(\alpha-\kappa(g)b)k(1+\gamma)}\mathbb{P}_{\mu}\left[\langle R_3,X_{t-k-1}\rangle\right]\\
-       &\leq C_3e^{\alpha t}e^{(\gamma\alpha-\kappa(g)b(1+\gamma))k},
-\end{align*}
-for some $C_3>0$. Combining with the result of $I$ and $II$, we complete the proof.
+    &\leq C_3\left(e^{(\alpha-\kappa(g)b)k(1+\beta)}C(k)^{\gamma-\beta}+e^{(\alpha-\kappa(g)b)k(1+p)}C(k)^{\gamma-p}\right)\langle R_2+R_3,\nu\rangle\\
+    &= C_3 e^{(\alpha-\kappa(g)b)k(1+\gamma)}\langle R_2+R_3,\nu\rangle,
+\end{align*}
+where $C_3=(1+\gamma)\cdot\max\{ \frac{2^{2+\beta}}{(\beta-\gamma)(2+\beta)}, \frac{2^{2+p}}{(2+p)(p-\gamma)}\}$. At last, using the mean formula \eqref{eq:meanformula}, we get
+\begin{align*}
+    II &\leq C_3e^{(\alpha-\kappa(g)b)k(1+\gamma)}\mathbb{P}_{\mu}\left[\langle R_2+R_3,X_{t-k-1}\rangle\right]\\
+       &=C_3e^{-\alpha}\langle T_{t-k-1}(R_2+R_3),\mu \rangle e^{\alpha t}e^{(\gamma\alpha-\kappa(g)b(1+\gamma))k}\\
+       &\leq C_4e^{\alpha t}e^{(\gamma\alpha-\kappa(g)b(1+\gamma))k}.
+\end{align*}
+ By \eqref{eq:semigroupineq}, there exists $R_4\in \mathcal{P}$, such that $T_t(R_2+R_3)\leq R_4$, we take $C_4=C_3 e^{-\alpha}\langle R_4, \mu\rangle$.
+Combining with the result of $I$ and $II$, we complete the proof by taking $C_2=(1+C_4)^{\frac{1}{1+\gamma}}$.
 \end{proof}
+\end{comment}
+%end deleted
+%new added
+\begin{lem}\label{lem: lemma23}
+For each $0\leq \gamma < \beta$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_1>0$ such that, for each $t\in \mathbb N$ and $k \in \{0,\dots,t\}$, we have
+\begin{align}
+\label{eq: upper bound of 1+gamma moment of Mktg}
+    \mathbb P_\mu\big[|M_k^t[g]|^{1+\gamma}\big]
+    \leq C_1 e^{\alpha t}e^{(\alpha \gamma - \kappa(g)b(1+\gamma))k}.
+\end{align}
+\end{lem}
+\begin{proof}
+    Let $R$ be the control function in \eqref{eq:gcontrol}.
+    Then for each $\mu\in \mathcal M(\mathbb R^d)$ with compact support and $t\in \mathbb N$, we have
+\begin{align}
+    \mathbb P_\mu\big[|M_t^t[g]|^{1+\gamma}\big]
+    = |\langle T_t^\alpha g, \mu\rangle|^{1+\gamma}
+    \leq \langle e^{\alpha t} |T_tg|, \mu\rangle^{1+\gamma}
+    \leq  \langle R,\mu\rangle^{1+\gamma} e^{\alpha t} e^{(\alpha\gamma- \kappa(g)b(1+\gamma))t}.
+\end{align}
+    This proves the Lemma in the case that $k = t$.
+    So we only have to consider the case when $k \in \{0,\dots,t-1\}$.
+    Let $c_k=e^{(\alpha-\kappa(g)b)k}$.
+    For each $\nu \in \mathcal M(\mathbb R^d)$ with compact support, denote by $\varphi_{k,\nu}$ the characteristic function of $\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle$.
+
+    Step 1. We will show that there exeists an $\tilde R_2 \in \mathcal P$ such that for each $\nu \in \mathcal M(\mathbb R^d)$ with compact support and $\lambda > c_k$ we have
+\begin{align} 
+    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda)
+    \leq \langle \tilde R_2,\nu\rangle \Big(\frac{c_k}{\lambda}\Big)^{1+\beta}.
+\end{align}
+    In fact, using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, letting $R_2 \in \mathcal P$ and $R_3 \in \mathcal P$ be the control functions in Corollary \ref{cor: corollary2} and Corollary \ref{cor: corollary1}, we have
+\begin{align} 
+    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda)
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1-\varphi_{k,\nu}(\theta))d\theta
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\langle Z_{g_k}(\cdot,\theta),\nu\rangle|+|err(k,\nu,\theta)|\big)d\theta
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\theta c_k|^{1+\beta}+|\theta c_k|^{1+2\beta}+ |\theta c_k|^{2+2\beta}\big)d\theta \times \langle R_2+R_3,\nu\rangle
+    \\& = \bigg(\frac{2^{2+\beta}}{2+\beta}\Big(\frac{c_k}{\lambda}\Big)^{1+\beta}+\frac{2^{2+2\beta}}{2+2\beta}\Big(\frac{c_k}{\lambda}\Big)^{1+2\beta} + \frac{2^{3+2\beta}}{3+2\beta}\Big(\frac{c_k}{\lambda}\Big)^{2+2\beta}\bigg) \langle R_2+R_3,\nu\rangle.
+\end{align}
+    This implies the desired result in Step 1.
+
+    Step 2.
+Let $\tilde R_3\in \mathcal P$ be the control function in Step 1, we will show that for each $\nu\in \mathcal M(\mathbb R^d)$ with compact support, $k\in \mathbb N$ and $\gamma \in [0,\beta)$,
+\[
+    \int_{c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda) d\lambda
+    \leq \frac{1}{\beta-\gamma} \langle \tilde R_3,\nu\rangle c_k^{1+\gamma}.
+\]
+    In fact, a direct application of Step 1 shows that
+\begin{align}      
+    &\int_{c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda) d\lambda
+    \\&\leq \langle \tilde R_3,\nu \rangle c_k^{1+\beta}\int_{c_k}^\infty \lambda^{\gamma-1-\beta}d\lambda
+    = \frac{1}{\beta-\gamma}\langle \tilde R_3,\nu \rangle c_k^{1+\gamma}.
+\end{align}
+
+    Step 3. 
+    Let $\tilde R_3\in \mathcal P$ be the control function in Step 1 and 2. According to \eqref{eq:semigroupineq}, there exists an $\tilde R_4\in \mathcal P$ such that
+$
+    |T_t(\tilde R_3)(x)| 
+    \leq \tilde R_4(x),
+$
+    for each $t\geq 0$ and $x\in E$.
+    Therefore, for each $\mu \in \mathcal M(\mathbb R^d)$ with compact support, $t\in \mathbb N$ and $k \in \{1,\dots,t-1\}$, we have
+\begin{align}
+    &\mathbb P_\mu\big[|M_k^t[g]|^{1+\gamma}\big] = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|M_k^t[g]|>\lambda) d\lambda
+    \\&\leq c_k^{1+\gamma}+(1+\gamma)\int_{c_k}^\infty \lambda^{\gamma}\mathbb P_\mu(|M_k^t[g]|> \lambda) d\lambda
+    \\&\leq c_k^{1+\gamma}+(1+\gamma)\int_{c_k}^\infty \lambda^{\gamma}\mathbb P_\mu \big[\mathbb P_\mu\big(|M_k^t[g]|> \lambda\big| \mathscr F_{t-k-1}\big)\big] d\lambda
+    \\&\leq c_k^{1+\gamma}+(1+\gamma)\int_{c_k}^\infty \lambda^{\gamma}\mathbb P_\mu \big[\mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda)\big|_{\nu=X_{t-k-1}}\big] d\lambda
+    \\&\leq c_k^{1+\gamma}+\mathbb P_\mu\Big[(1+\gamma)\int_{c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda) d\lambda\Big|_{\nu=X_{t-k-1}}\Big]
+    \\&\leq c_k^{1+\gamma}+\mathbb P_\mu\Big[\frac{1+\gamma}{\beta- \gamma}\langle \tilde R_3,X_{t-k-1}\rangle c_k^{1+\gamma}\Big]
+    = c_k^{1+\gamma}+\frac{1+\gamma}{\beta- \gamma}c_k^{1+\gamma} \langle T_{t-k-1}^{\alpha}\tilde R_3,\mu\rangle
+    \\&\leq \Big(1+ \frac{1+\gamma}{\beta - \gamma} \langle \tilde R_4,\mu\rangle\Big) e^{\alpha(t-k-1)}c_k^{1+\gamma}
+    \\&= \Big(1+ \frac{1+\gamma}{\beta - \gamma} \langle \tilde R_4,\mu\rangle\Big)e^{-\alpha} e^{\alpha t}e^{(\alpha \gamma - \kappa(g)b(1+\gamma))k}.
+\qedhere
+\end{align}
+\end{proof}
+%comment
+    {\bf Zhenyao: Even if the following remark is correct, I would like to see it been proved.}
+%end comment
 \begin{rem}\label{remark2}
@@
    which satisfies
-   $$\|M_{t,\lfloor t \rfloor}[g]\|_{1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t},$$
-   For some $C>0$. This can be proved by using Remark \ref{remark1} and following the same method in Lemma \ref{lemma23}.
+   $$\|M_{t,\lfloor t \rfloor}[g]\|_{1+\gamma}\leq C_2 e^{\frac{\alpha}{1+\gamma}t},$$
+This can be proved by using Remark \ref{remark1} and following the same method in Lemma \ref{lem: lemma23}.
 \end{rem}
@@
 \begin{lem}\label{lemma24}
-For any $0\leq \gamma < \beta$ there exists a constant $C>0$, we have the result:
-
-i) When $\alpha\gamma > \kappa(g)(1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C e^{(\alpha-\kappa(g)b)t}.$$
-
-ii) When  $\alpha\gamma = \kappa(g)(1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}.$$
-
-iii) When $\alpha\gamma < \kappa(g)(1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}.$$
+%For each $0\leq \gamma < \beta$ there exists a constant $C_5>0$, we have the result:
+For each $0\leq \gamma < \beta$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_5>0$, such that for each $t\in \mathbb N$:
+
+i) If $\alpha\gamma > \kappa(g)(1+\gamma)b$,
+$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C_5 e^{(\alpha-\kappa(g)b)t}.$$
+
+ii) If  $\alpha\gamma = \kappa(g)(1+\gamma)b$,
+$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C_5 te^{\frac{\alpha}{1+\gamma}t}.$$
+
+iii) If $\alpha\gamma < \kappa(g)(1+\gamma)b$,
+$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C_5 e^{\frac{\alpha}{1+\gamma}t}.$$
 
@@
 \begin{proof}
-Using the triangle inequality and Lemma \eqref{lemma23}, for some $C_1>0$
-$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq \sum_{k=0}^{t}\|M_k^t[g]\|_{1+\gamma}\leq C_1 e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^t e^{\frac{\gamma\alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}.$$
+    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support.
+    Let $C_1$ be the constant in Lemma \ref{lem: lemma23}.
+    Using the triangle inequality, 
+\begin{align}
+    \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+    \leq \sum_{k=0}^{t}\|M_k^t[g]\|_{\mathbb P_\mu;1+\gamma}
+    \leq C_1 e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^{t} e^{\frac{\gamma\alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}.
+\end{align}
 By calculating the sum on the right, we easily get the result.
@@
 \begin{lem}\label{lemma25}
-For any $a \in \mathbb{R}$ and $f\in\mathcal{P}$ such that $L f\in\mathcal{P}$, Then $\{M_t^{f,a},\mathcal{F}_t:t\geq 0\}$ is a martingale.
+%For any $a \in \mathbb{R}$ and $f\in\mathcal{P}$ such that $L f\in\mathcal{P}$, Then $\{M_t^{f,a},\mathcal{F}_t:t\geq 0\}$ is a martingale.
+For any $a \in \mathbb{R}$ and $f\in\mathcal{P}$ such that $L f\in\mathcal{P}$, $\{M_t^{f,a},\mathcal{F}_t:t\geq 0\}$ is a martingale.
 \end{lem}
@@
 \begin{align}
-    \mathbb{P}_{\mu}\left[M_t^{f,a}|\mathcal{F}_s\right] &=e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\left[\int_0^t e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du|\mathcal{F}_s\right]\nonumber\\
-    &=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du\nonumber\\
-    &-\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_u\rangle~ du.\label{martingale1}
+\label{martingale1}
+    %\mathbb{P}_{\mu}\left[M_t^{f,a}|\mathcal{F}_s\right] &=e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\left[\int_0^t e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du|\mathcal{F}_s\right]\nonumber\\
+    &\mathbb{P}_{\mu}\left[M_t^{f,a}|\mathcal{F}_s\right] 
+    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\left[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du|\mathcal{F}_s\right]
+    %\\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du\nonumber\\
+    %\\&-\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_u\rangle~ du.\label{martingale1}
+    \\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du -\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
 \end{align}
@@
 \end{proof}
+%comment
+{\bf Zhenyao: I think the above Lemma is not accurate.
+I think we need condition that $f\in C^2(\mathbb R^d) \cap \mathcal P$.
+Also in the proof we better use \cite[Theorem A.55]{Li2011Measure-valued} and Fubini's theorem.}
+%end comment
 
@@
 
-    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that $\alpha\gamma_0>|p|(1+\gamma_0)b$. Using  Lemma \eqref{lemma24} and the fact $\kappa(\phi_p)=|p|$, we get that
-    $$\|H_t^p\|_{1+\gamma_0}\leq Ce^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C,$$
-    where $C$ is a constant. For any $0\leq\gamma<\gamma_0$, by the concave of function $h(x)=x^{(1+\gamma)/(1+\gamma_0)}$, 
+    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that $\alpha\gamma_0>|p|(1+\gamma_0)b$.
+Using  Lemma \eqref{lemma24} and the fact $\kappa(\phi_p)=|p|$, we get that, for any $\gamma_0\leq\gamma<\beta$
+    $$\|H_t^p\|_{1+\gamma}\leq C_5e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C_5,$$
+ For any $0\leq\gamma<\gamma_0$, by the concave of function $h(x)=x^{(1+\gamma)/(1+\gamma_0)}$,
     $$\mathbb{P}_{\mu}|H_t^p|^{1+\gamma}\leq(\mathbb{P}_{\mu}|H_t^p|^{1+\gamma_0})^{\frac{1+\gamma}{1+\gamma_0}}<\infty.$$
-    Hence the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicate the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ an almost sure.
+    Hence the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicate the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ an almost sure,
+%added
+    according to \cite[Theorem 5.4.5]{Durrett2010Probability}.
+%end added
 \end{proof}
@@
     Recall that $\|X_t\|=\langle 1,X_t\rangle$. 
-By Lemma \eqref{lemma26}, it is not to hard to prove that, under $\mathbb{P}_{\mu}$, the process $W_t=e^{-\alpha t}\|X_t\|$ is a positive martingale satisfying
+    By Lemma \ref{lemma26}, 
+    %it is not to hard to prove that, 
+    it is clear that,
+    under $\mathbb{P}_{\mu}$, the process $W_t=e^{-\alpha t}\|X_t\|$ is a positive martingale satisfying
 $$\lim_{t\rightarrow \infty} W_t= W_{\infty}$$
@@
 Moreover, we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D$ which is the extinction event.
+%comment
+    {\bf Zhenyao: we need references for the last assertion.}
+%end comment
 \begin{lem}\label{lemma27}
- For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have 
- $$\|W_t-W_s\|_{1+\gamma}\leq C e^{-\alpha s/2},$$
- for some C just depending on $\gamma$.
+ %For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have
+ For any $\gamma\in [0,\beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a $C_6> 0$ such that for each $0\leq s<t$,
+ $$\|W_t-W_s\|_{1+\gamma}\leq C_6 e^{-\alpha s/2}.$$
 \end{lem}
@@
 \begin{proof}
-    Let $n\in \mathbb{N}$, in Lemma \eqref{lemma23}, we take $t=n+k,g=1$, then $\kappa(g)=0$, moreover, the following inequality holds.
-    $$ \mathbb{P}_{\mu}\left|e^{\alpha k}\|X_n\|-e^{\alpha(k+1)}\|X_{n-1}\|\right|^{1+\gamma}\leq C_1 e^{\alpha(n+k)}e^{\alpha\gamma k}.$$
+%new added
+    Fix $\gamma \in [0,\beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support. 
+    According to Lemma \ref{lem: lemma23}, for each $n \in \mathbb N$, we have
+%end new added
+%delete
+    %Let $n\in \mathbb{N}$, in Lemma \eqref{lem: lemma23}, we take $t=n+k,g=1$, then $\kappa(g)=0$, moreover, the following inequality holds.
+%end delete
+    $$ \mathbb{P}_{\mu}[|e^{\alpha k}\|X_n\|-e^{\alpha(k+1)}\|X_{n-1}\||^{1+\gamma}]
+    = \mathbb P_\mu [|M^{n+k}_k[1]|^{1+\gamma}]
+    \leq C_1 e^{\alpha(n+k)}e^{\alpha\gamma k}.$$
     Dividing both sides by $e^{\alpha(n+k)(1+\gamma)}$, we get
@@
     For any $m\in \mathbb{N}$ and $m<n$,
-    $$\|W_n-W_m\|_{1+\gamma}\leq \sum_{k=m}^{n-1}\|W_{k+1}-W_k\|_{1+\gamma}\leq C_1\sum_{k=m}^{n-1}e^{-\frac{\alpha\gamma(k+1)}{1+\gamma}}\leq C e^{-\frac{\alpha\gamma m}{1+\gamma}}\leq C e^{-\frac{\alpha m}{2}}.$$
-    Where $C,C_1$ are constant just depending $\gamma$.
+    $$\|W_n-W_m\|_{1+\gamma}\leq \sum_{k=m}^{n-1}\|W_{k+1}-W_k\|_{1+\gamma}\leq C_2\sum_{k=m}^{n-1}e^{-\frac{\alpha\gamma(k+1)}{1+\gamma}}\leq C_6 e^{-\frac{\alpha\gamma m}{1+\gamma}}\leq C_6 e^{-\frac{\alpha m}{2}}.$$
+    Where we can take $C_6=\frac{C_2}{1-e^{-\frac{\alpha \gamma}{1+\gamma}}}$
  When we take any $0\leq s\leq t$,there will appear two terms corresponding to the interval $[s,[s]+1]$ and $[[t],t]$, which are  handled by using Remark \ref{remark2} with the same method, then we complete our proof.
 \end{proof}
-
+Recall that $\|X_t\|$ is an continuous state branching process with initial mass $\|\mu\|$.
+for any $\lambda>0$, $\|X_t\|$ satisfies, see \cite[Chapter 3]{Li2011Measure-valued}, for example.
+\begin{align}\label{CSBP}
+    \mathbb{P}_{\mu}e^{-\lambda\|X_t\|}=e^{-\|\mu\|v_t(\lambda)}
+\end{align}
+where $v_t(\lambda)$ is the unique local bounded solution to the equation 
+\begin{align*}
+    \frac{\partial}{\partial t}v_t(\lambda)=-\psi(v_t(\lambda)), \quad  v_0(\lambda)=\lambda.
+\end{align*}
+
+In this paper, for any $\beta\in (0,1)$, $v_t(\lambda)$ has explicit expression \cite[Example 3.1]{Li2011Measure-valued}
+\begin{align*}
+    v_t(\lambda)=\frac{e^{\alpha t} \lambda}{[1+\frac{1}{\alpha}(e^{\alpha \beta t}-1)\lambda^{\beta}]^{1/\beta}}=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0,
+\end{align*}
+If we fix $t>0$, $v_t(\lambda)$ is increasing corresponding to $\lambda$.
+
+Recall that the superprocess $X$'s extinction probability $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
+Denote $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$, by equation (3.48) in\cite{Li2011Measure-valued} and formula \eqref{CSBP}, we easily get
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}\nonumber\\
+        &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right| \label{laplaceexpress} 
+\end{align}
+
+We want to prove the following Lemma
+\begin{lem}\label{lemma2_13}
+Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function such that $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$. Then there exist $C_7>0$ such that for any $t\geq 0$, there is
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_7 \exp(\beta(\ln f(t)-\alpha t))
+\end{align}
+\end{lem}
+\begin{proof}
+ Without loss of generality, we assume that $\|\mu\|=1$, By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get 
+\begin{align*}
+    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|)}]\\
+    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
+\end{align*}
+Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t},~ t\geq 0,\lambda\geq0$, $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
+\begin{align*}
+    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\cdot\left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right|\\
+    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t}\\
+    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}
+\end{align*}
+Therefore, 
+\begin{align*}
+    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}\cdot \frac{1}{1-e^{-\alpha^*}} e^{\lambda f(t)}.
+\end{align*}
+Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
+\begin{align*}
+    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\cdot\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}\exp(\beta(\ln f(t)-\alpha t))
+\end{align*}
+Notice that 
+\begin{align*}
+    w_t(s)^{-1/\beta-1}&\leq \frac{1}{(\alpha s^{-\beta}e^{-\alpha \beta t})^{1/
+    \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
+    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}. 
+\end{align*}
+This is to say
+\begin{align*}
+    \sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}&\leq\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
+    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}
+\end{align*}
+We conclude the lemma by taking $C_7= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
+\end{proof}
 \begin{lem}\label{lemma28}
-  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C>0$ and $\delta>0$ such that 
-  $$\mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq C e^{-\delta t},\quad t\geq 0.$$
+  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C_8>0$ and $\delta_1>0$ such that
+  $$\mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq C_8 e^{-\delta_1 t},\quad t\geq 0.$$
 \end{lem}
@@
 \begin{proof}
-    First, for any $\delta_1>0$, using Markov inequality, we get
-    $$\mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\delta_1)t})\leq e^{-\delta_1 t}.$$ 
-    For another side, let $\{(Z_t)_{t\geq 0}, \mathbb{P}^{\ast}_{\mu}\}$ be the backbone process of $X$.
-we know that $Z$ is a branching OU-process with initial configuration $\mu$.
-in which individuals, from the moment of birth, live for an independent and exponentially distributed period of time with parameter $\beta^{\ast}=\psi'(\alpha^{\ast})>0$ during which they move according to the OU-process issued from their position of birth and at death the give birth at the same position to an independent number of offspring with generator $F(s)=(1/\alpha^{\ast})\psi(\alpha^{\ast}(1-s))$ (see \cite{BAM} for further information about backbone decomposition.)
-
-    Using \cite[Fact 1.8]{MM}, we have
-    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq\mathbb{P}^{\ast}_{\mu}\left(\|Z_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right) \leq C_1 e^{-\delta_2\epsilon t}, $$
-   For some $C,\delta_2>0$.  We get the desired result.
+    First, for any $\epsilon>0$, using Markov inequality, we get
+    $$\mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)\leq e^{-\epsilon t}.$$
+    For another side, using Lemma \ref{lemma2_13}, we have
+    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq C_7 e^{-\beta\epsilon t}, $$
+Therefore,
+\begin{align*}
+    \mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq \mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq(C_7+1)e^{-\beta \epsilon t }
+\end{align*}
 \end{proof}
@@
  \begin{align}
-      m_k[g]:=e^{-\alpha(k+1)}\langle Z_{g_k},\varphi\rangle.
+      m_k[g]:=e^{-\alpha(k+1)}\langle Z_{g_k},\psi\rangle.
  \end{align}
 \begin{lem}\label{mgineq1}
-There exists $R\in \mathcal{P}$ and constant $C>0$ such that for any $k\in \{0,1,...,t\}$, we have 
-$$|m_k[g]|\leq C e^{(\alpha\beta-\kappa(g)b(1+\beta))k}.$$
+There exists constant $C_9>0$ such that for any $k\in \{0,1,...,t\}$, we have
+$$|m_k[g]|\leq C_9 e^{(\alpha\beta-\kappa(g)b(1+\beta))k}.$$
 \end{lem}
 \begin{proof}
-    By \eqref{zineq2} and simply calculating, we obtain the result.
+    By \eqref{zineq2} and simply calculating, we obtain the result by  taking $C_9=e^{-\alpha}\langle R_2,\phi\rangle$.
 \end{proof}
@@
     As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(g)bt}$,  $\kappa(g)=\kappa(\phi)$ and $\kappa(g-\phi)\geq \kappa(g)+1$.
-The inequality \eqref{semigroupineq} yields that for some $R_1\in\mathcal{P}$ we have
-    \begin{align*}
-        &|T_s^{\alpha}g|\leq e^{(\alpha-\kappa(g)b)s}R_1(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(g)b)s}R_1(x), \\ 
-        &|T_s^{\alpha}(g-\phi)|\leq e^{(\alpha-(\kappa(g)+1)b)s}R_1(x), \quad s\geq0.
+The inequality \eqref{eq:semigroupineq} yields that for some $R_5\in\mathcal{P}$ we have
+    \begin{align*}
+        &|T_s^{\alpha}g|\leq e^{(\alpha-\kappa(g)b)s}R_5(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(g)b)s}R_5(x), \\
+        &|T_s^{\alpha}(g-\phi)|\leq e^{(\alpha-(\kappa(g)+1)b)s}R_5(x), \quad s\geq0.
     \end{align*}
   Using the element inequality \eqref{element} and the condition $\alpha\beta=\kappa(g)b(1+\beta)$, we get
-    $$|m_k[g]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R(x)~ds~\varphi(x)~dx\leq C e^{-bk},$$
-    for some $R\in\mathcal{P}$ and constant $C$.
+    $$|m_k[g]-m_k[\phi]|\leq2C\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R_5^{1+\beta}(x)~ds~\varphi(x)~dx\leq \frac{2C}{b}\langle R_5^{1+\beta},\varphi\rangle e^{-bk},$$
 
@@
 \begin{proof}
-    By Lemma \ref{mgineq1}, we have $|m_k[g]|\leq C e^{(\alpha\beta-\kappa(g)b(1+\beta))k}$, for some $C>0$, which implies $\sum_{k=0}^{\infty}|m_k[g]|<\infty$ as $\alpha\beta<\kappa(g)b(1+\beta)$.
-Hence
+    By Lemma \ref{mgineq1}, we have $|m_k[g]|\leq C_9 e^{(\alpha\beta-\kappa(g)b(1+\beta))k}$, which implies $\sum_{k=0}^{\infty}|m_k[g]|<\infty$ as $\alpha\beta<\kappa(g)b(1+\beta)$. Hence
     $$m[g]:=\sum_{k=0}^{\infty}m_k[g]=\sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)ds\varphi(x)dx$$
-     Moreover, the right side series are also absolutely convergence, since $|e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)|\leq e^{(\alpha\beta-\kappa(g)b(1+\beta))s}R(x)$ for some $R \in \mathcal{P}$.
+     Moreover, the right side series are also absolutely convergence, since $|e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)|\leq e^{(\alpha\beta-\kappa(g)b(1+\beta))s}R(x)$.
 
@@
 
-In this section, we will prove the main results of this paper. Let $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
  \begin{lem}\label{lemma31}
@@
 
-    Using the Lemma \ref{lemma2}, there exists $p>1+\beta$ and $R \in \mathcal{P}$ such that, for any $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}$, we have 
-    \begin{align*}
-        I&\leq \left(\frac{|\theta|e^{(\alpha-\kappa(g)b)k}}{(e^{\alpha k}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\right)^p\mathbb{\tilde{P}}_{\mu}\langle R,X_{t-k-1}\rangle\\
-        &\leq C |\theta|^p e^{-\frac{p\alpha(t-k-1)}{1+\beta}}e^{\frac{p\epsilon(t-k-1)}{1+\beta}}\mathbb{\tilde{P}}_{\mu}\langle R,X_{t-k-1}\rangle\\
-        &\leq C |\theta|^p e^{\alpha(t-k-1)}e^{-\frac{p\alpha(t-k-1)}{1+\beta}}e^{\frac{p\epsilon(t-k-1)}{1+\beta}},\quad \theta\in \mathbb{R},
-    \end{align*}
-    for some constant $C$. Since $\alpha(\frac{p}{1+\beta}-1)>0$, we can chose $\epsilon>0$ such that there exists $C_1,\delta_1>0$ satisfying  
-    \begin{align}
-        I\leq C_1|\theta|^p e^{-\delta_1(t-k)}, \quad k\in \mathbb{N}, t>k, \theta \in \mathbb{R}.\label{lemma31q}
+    Using the Lemma \ref{lemma2}, for any $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}$, we have
+    \begin{align*}
+        I&\leq e^c\left(\frac{|\theta|e^{(\alpha-\kappa(g)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\right)^{p_1}\mathbb{\tilde{P}}_{\mu}\langle R_1,X_{t-k-1}\rangle\\
+        &=\frac{e^c}{\|\mu\|^{p_1/(1+\beta)}}\langle T_{t-k-1} R_1,\mu\rangle|\theta|^{p_1}e^{\alpha(t-k-1)} e^{-\frac{p_1\alpha(t-k-1)}{1+\beta}}e^{\frac{p_1\epsilon(t-k-1)}{1+\beta}}\\
+        &\leq C_{10} |\theta|^{p_1} e^{\alpha(t-k-1)}e^{-\frac{p_1\alpha(t-k-1)}{1+\beta}}e^{\frac{p_1\epsilon(t-k-1)}{1+\beta}},\quad \theta\in \mathbb{R},
+    \end{align*}
+    for some constant $C_{10}$. Since $\alpha(\frac{p_1}{1+\beta}-1)>0$, we can chose $\epsilon>0$ such that there exists $C_{11},\delta_2>0$ satisfying
+    \begin{align}
+        I\leq C_{11}|\theta|^{p_1} e^{-\delta_2(t-k)}, \quad k\in \mathbb{N}, t>k, \theta \in \mathbb{R}.\label{lemma31q}
     \end{align}
@@
     $$\frac{\partial}{\partial x_i}Z_{g_k}(x)=\int_0^1 T^{\alpha}_{1-s}\left(\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha} \tilde{g})^{1+\beta}\right)(x)~ds$$
-    Using the inequality \eqref{semigroupineq} and the fact $\kappa\left(\frac{\partial \tilde{g}}{\partial x_i}\right)\geq \kappa(\tilde{g})-1$, see \cite[Lemma 2.3]{RSZ}, we get that there exists $R_1 \in \mathcal{P}$ such that, for any $k\in \mathbb{N}$,
+    Using the inequality \eqref{eq:semigroupineq} and the fact $\kappa\left(\frac{\partial \tilde{g}}{\partial x_i}\right)\geq \kappa(\tilde{g})-1$, see \cite[Lemma 2.3]{RSZ}, we get that there exists $R_7 \in \mathcal{P}$ such that, for any $k\in \mathbb{N}$,
     \begin{align*}
         \left|\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha}\tilde{g})^{\beta}\right|&=\left|(1+\beta)(-i T_{s+k-1}^{\alpha}\tilde{g})^{\beta}(-i e^{-b(s+k-1)}T_{s+k-1}^{\alpha}\left(\frac{\partial \tilde{g}}{\partial x_i}\right))\right|\\
-        &\leq e^{(\alpha-\kappa(\tilde{g})b)(s+k-1)(1+\beta)}R_1(x).
-    \end{align*}
-
-    What's more, $T_1 g(x)=\sum_{|p|\geq\kappa(g)}\langle g,\phi_p\rangle e^{-b|p|}\phi_p$, thus $\kappa(\tilde{g})=\kappa(g)$.
-Therefore, there exists $R_2 \in \mathcal{P}$ such that for any $k\in \mathbb{N}$,
-    $$\left|\frac{\partial}{\partial x_i}Z_{g_k}(x)\right|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}R_2(x),\quad x\in \mathbb{R}^d. $$
+        &\leq e^{(\alpha-\kappa(\tilde{g})b)(s+k-1)(1+\beta)}R_7(x).
+    \end{align*}
+
+    What's more, $T_1 g(x)=\sum_{|p|\geq\kappa(g)}\langle g,\phi_p\rangle e^{-b|p|}\phi_p(x)$, thus $\kappa(\tilde{g})=\kappa(g)$.
+Therefore, there exists $R_8 \in \mathcal{P}$ such that for any $k\in \mathbb{N}$,
+    $$\left|\frac{\partial}{\partial x_i}Z_{g_k}(x)\right|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}R_8(x),\quad x\in \mathbb{R}^d. $$
     Hence
 \begin{align}
-    |h_k(x)|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}(R_2(x)(|x|+C)),\quad  x\in \mathbb{R}^d, k\in\mathbb{N},
-\end{align}
-
-for some constant $C$. Denote $R_3=R_2(x)(|x|+C)$, we notice that $\kappa(R_3)=\kappa(R_2(x)(|x|+C))\geq1$. Therefore, for $\theta\in \mathbb{R}^d$, $k\in\mathbb{N}$ and $t>k$,
-\begin{align*}
-  \mathbb{\tilde{P}}_{\mu}\left[|\langle h_k,X_{t-k-1}\rangle\right|]&\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}\langle T_{t-k-1}^{\alpha}R_3,\mu\rangle\\
-  &\leq C_1|\theta|^{1+\beta} e^{(\alpha-\kappa(g)b)(1+\beta)k}e^{(\alpha-b)(t-k-1)}.
-\end{align*}
- The last inequality holds as \eqref{semigroupineq}. Now combine with \eqref{II1}, we can chose $\epsilon$ just depending $b$ such that, 
-\begin{align}
-    II\leq C_2|\theta|^{1+\beta} e^{-(b-\epsilon)(t-k)}\leq C_2e^{-\delta_2(t-k)},\quad k\in\mathbb{N},t>k,\theta\in\mathbb{R}\label{lemma32q}
-\end{align}
-for some $C_2,\delta_2>0$.
+    |h_k(x)|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}(R_8(x)(|x|+\int_{\mathbb{R}^d}|y|\varphi(y)~dy)),\quad  x\in \mathbb{R}^d, k\in\mathbb{N},
+\end{align}
+
+Denote $R_9=R_8(x)(|x|+\int_{\mathbb{R}^d}|y|\varphi(y)~dy)$, we notice that $\kappa(R_9)\geq1$. Therefore, for $\theta\in \mathbb{R}^d$, $k\in\mathbb{N}$ and $t>k$,
+\begin{align*}
+  \mathbb{\tilde{P}}_{\mu}\left[|\langle h_k,X_{t-k-1}\rangle\right|]&\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}\langle T_{t-k-1}^{\alpha}R_9,\mu\rangle\\
+  &\leq C_{12} e^{(\alpha-\kappa(g)b)(1+\beta)k}e^{(\alpha-b)(t-k-1)}.
+\end{align*}
+ The last inequality holds as \eqref{eq:semigroupineq}. Now combine with \eqref{II1}, we can chose $\epsilon$ just depending $b$ such that,
+\begin{align}
+    II\leq C_{12} e^c|\theta|^{1+\beta} e^{-(b-\epsilon)(t-k-1)}\leq C_{13}|\theta|^{1+\beta}e^{-\delta_3(t-k)},\quad k\in\mathbb{N},t>k,\theta\in\mathbb{R}\label{lemma32q}
+\end{align}
+for some $C_{13},\delta_3>0$.
 
@@
 \begin{align}
-    \left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbf{1}_{\mathcal{A}^c_{t-k-1}}\right|&\leq C_3\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})\nonumber\\
-    &\leq C_3 e^{-\delta_3(t-k)},\label{lemma33q}
+    \left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbf{1}_{\mathcal{A}^c_{t-k-1}}\right|&\leq e^c\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})\nonumber\\
+    &\leq C_{14} e^{-\delta_1(t-k)},\label{lemma33q}
 \end{align}
@@
    i) For any $k\in\mathbb{N}$, $e^{\theta^{1+\beta}e^{\alpha}m_k[g]}$ is the characteristic function of some $1+\beta$-stable distribution, hence $|e^{\theta^{1+\beta}e^{\alpha}m_k[g]}|\leq 1$.
-
-   ii) the parameters $\delta_1,\delta_2, \delta_3$ in Lemma \ref{lemma31} are just depending on $b,\beta$.
 \end{rem}
@@
 Let $\Theta>0$, assume that $\alpha\beta\leq\kappa(g)b(1+\beta)$.
-There exists $C,\delta>0$ such that for any $n \in \{0,...,t\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
-\begin{align*}
-    \left|\mathbb{\tilde{P}}_{\mu}\left(\prod_{k=0}^n\exp(i\theta_k \frac {M_k^t[g]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}})-\prod_{k=0}^n\exp(\theta_k^{1+\beta}e^{\alpha}m_k[g])\right)\right|\leq Ce^{-\delta(t-n)}
+There exists $C_{15},\delta_4>0$ such that for any $n \in \{0,...,t\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
+\begin{align*}
+    \left|\mathbb{\tilde{P}}_{\mu}\left(\prod_{k=0}^n\exp(i\theta_k \frac {M_k^t[g]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}})-\prod_{k=0}^n\exp(\theta_k^{1+\beta}e^{\alpha}m_k[g])\right)\right|\leq C_{15}e^{-\delta_4(t-n)}
 \end{align*}
@@
     \end{align*}
-    If we have proved that there exists $C,\delta>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,t\}$,
-    \begin{align}
-        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\leq C e^{-\delta(t-k)},
+    If we have proved that there exists $C_{16},\delta_5>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,t\}$,
+    \begin{align}
+        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\leq C_{16} e^{-\delta_5(t-k)},
     \end{align}
@@
     \begin{align*}
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_1 e^{-\delta_1 (t-k)}\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_1 e^{-\delta_1(t-k)}
-    \end{align*}
-for some $C_1,\delta_1>0$. Define 
-\begin{align*}
-    \mathcal{B}_{t-k-1}:=\left\{\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\leq C_1 e^{-\frac{\delta_1}{2}(t-k)}\right\}.
-\end{align*}
-Applying Markov's inequality, we get $\mathbb{\tilde{P}}_{\mu}(\mathcal{B}_{t-k-1})\geq 1- e^{-\frac{\delta_1}{2}(t-k)}$. Similarly, define
-\begin{align*}
-    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\leq C_1 e^{-\frac{\delta_1}{2}(t-k)}\right\},
-\end{align*}
- which satisfies  $\mathbb{\tilde{P}}_{\mu}(\mathcal{C}_{t-k-1})\geq 1- e^{-\frac{\delta_1}{2}(t-k)}$.
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_{11}|\theta|^{p_1} e^{-\delta_2 (t-k)}\\
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_{13}|\theta|^{1+\beta} e^{-\delta_3(t-k)}
+    \end{align*}
+ Define
+\begin{align*}
+    \mathcal{B}_{t-k-1}:=\left\{\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\leq C_{11}|\theta|^{p_1} e^{-\frac{\delta_2}{2}(t-k)}\right\}.
+\end{align*}
+Applying Markov's inequality, we get $\mathbb{\tilde{P}}_{\mu}(\mathcal{B}_{t-k-1})\geq 1- e^{-\frac{\delta_2}{2}(t-k)}$. Similarly, define
+\begin{align*}
+    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\leq C_{13}|\theta|^{1+\beta} e^{-\frac{\delta_3}{2}(t-k)}\right\},
+\end{align*}
+ which satisfies  $\mathbb{\tilde{P}}_{\mu}(\mathcal{C}_{t-k-1})\geq 1- e^{-\frac{\delta_3}{2}(t-k)}$.
 
@@
    +\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\\
-   &\leq 2C_1 e^{-\frac{\delta_1}{2}(t-k)},
+   &\leq (C_{11}|\Theta|^{p_1}+C_{13}|\Theta|^{1+\beta}) e^{-\frac{\min\{\delta_2,\delta_3\}}{2}(t-k)},
 \end{align*}
@@
     &\leq 2(\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1}))\\
-    &\leq C e^{-\delta(t-k)},
-\end{align*}
-for some $C_2,\delta_2>0$.
+    &\leq 6e^{-\min\{\delta_1,\frac{\delta_2}{2},\frac{\delta_3}{2}\}(t-k)},
+\end{align*}
 \end{proof}
 
-In next three subsection, we just use $C$ as a constant positive real number, which may be different in different formula.
+In next three subsection, we just use $C$ and $\delta$ as a constant positive real number, which may be different in different formula.
 \subsection{Proof of Theorem \ref{Theorem12}}
@@
     \begin{align*}
-        \mathcal{D}_{t,k}:=\left\{|W_t-W_{t-k-1}|\leq C e^{-\frac{\alpha}{4}(t-k-1)}, W_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\},
+        \mathcal{D}_{t,k}:=\left\{|W_t-W_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, W_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\},
     \end{align*}
@@
     \begin{align*}
-        \mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)&\leq \mathbb{\tilde{P}}_{\mu}(|W_t-W_{t-k-1}|\geq C e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(W_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),\\
+        \mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)&\leq \mathbb{\tilde{P}}_{\mu}(|W_t-W_{t-k-1}|\geq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(W_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),\\
         &\leq C e^{-\delta(t-k-1)}
@@
     \end{align*}
-    When $t$ is large enough, $t^{-\frac{1}{1+\beta}}\leq 1$. What's more, by Lemma \ref{lemma23}
+    When $t$ is large enough, $t^{-\frac{1}{1+\beta}}\leq 1$. What's more, by Lemma \ref{lem: lemma23}
     $$\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k},$$
@@
  \begin{align*}
-     W_t\geq W_{t-k-1}-C e^{-\frac{\alpha}{4}(t-k-1)}&\geq\min\{\|\mu\|,C\}\left(e^{-\frac{\alpha}{32}(t-k-1)}-e^{-\frac{\alpha}{4}(t-k-1)}\right)\\
-     &\geq C e^{-\frac{\alpha}{16}(t-k-1)}.
+     W_t\geq W_{t-k-1}-\|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}&\geq\|\mu\|\left(e^{-\frac{\alpha}{32}(t-k-1)}-e^{-\frac{\alpha}{4}(t-k-1)}\right)\\
+     &\geq \|\mu\| e^{-\frac{\alpha}{16}(t-k-1)}.
  \end{align*}
@@
 
-Let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|t^{-1/2}e^{\alpha t}\}$.
-Recall that branching OU-process $\{Z,\mathbb{P}^{\ast}\}$ is the backbone process corresponding to $X$.
-Therefore, by using the fact 1.8 in \cite{MM}
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq\mathbb{P}^{\ast}(\|Z_t\|\leq\|\mu\|t^{-1/2}e^{\alpha t})\leq C t^{-\delta}, \quad t\geq0,\label{Theorem123}
+Let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|t^{-1/2}e^{\alpha t}\}$. Using Lemma \eqref{lemma2_13}, we get
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C t^{-\delta}, \quad t\geq0,\label{Theorem123}
 \end{align}
@@
 \end{align*}
-By the triangle inequality and Lemma \ref{lemma23}, for any $\gamma\in[0,\beta)$, we know that
+By the triangle inequality and Lemma \ref{lem: lemma23}, for any $\gamma\in[0,\beta)$, we know that
 \begin{align*}
@@
 $C,\delta >0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal{E}_t^c)\leq C e^{-\delta t}$.
-What's more, for any $0\leq \gamma <\beta$, we let $p=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa(g)(1+\gamma)b}{1+\gamma}>0$, then by Lemma \ref{lemma23}, we have
+What's more, for any $0\leq \gamma <\beta$, we let $p=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa(g)(1+\gamma)b}{1+\gamma}>0$, then by Lemma \ref{lem: lemma23}, we have
 \begin{align*}
@@
 	= \Big| \int_0^1\Big(e^{-\theta z} - \sum_{k=0}^m \frac{(-\theta z)^k}{k!} \Big) z d\theta \Big|
-	\\&\quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} z d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} z d\theta\Big)
+	%\\&\quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} z d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} z d\theta\Big)
+    \\&\quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} |z| d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} |z| d\theta\Big)
 	= \frac{|z|^{m+2}}{(m+2)!} \wedge \frac{2|z|^{m+1}}{(m+1)!},
@@
 \label{seq: complex Feynman-Kac transform}
+%new added
+    In this subsection we give a version of the Feynman-Kac formula with complex values.
+%end new added
 	Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact seperable metric space $E$.
-	For brevity, for each $0< s< t< \infty$ and each bounded complex valued measurable function $\rho$ on $[0,\infty) \times E$, we write
+	%For brevity, for each $0< s< t< \infty$ and each bounded complex valued measurable function $\rho$ on $[0,\infty) \times E$, we write
+    Fix a time $t >0$.
+    For each $0< s< t$ and each bounded complex valued measurable function $\rho$ on $[0,t) \times E$, we write
 \begin{equation}
@@
 	\frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
-	\quad s> 0.
-\end{equation}
-	Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,\infty) \times E$; $F$ is a complex valued bounded measurable function on $E$.
-    Fix a time $t >0$.  
+	%\quad s> 0.
+    \quad s\in (0,t).
+\end{equation}
+	%Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,\infty) \times E$; $F$ is a complex valued bounded measurable function on $E$.
+    Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,t) \times E$; $F$ is a complex valued bounded measurable function on $E$.
+%delete
+    %Fix a time $t >0$.
+%end delete
 	Define
 \begin{equation}
-	g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\beta+\rho)} F(\xi_t)],\quad r \in [0,t], x\in E.
+	g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\beta+\rho)} F(\xi_t)],\quad r \in [0,t), x\in E.
 \end{equation}
@@
     is a continuous function.
-    In fact, for any compact $K \subset \mathbb R$, since due to Lemma \ref{lem: estimate of exponential remaining},
+    %In fact, for any compact $K \subset \mathbb R$, since due to Lemma \ref{lem: estimate of exponential remaining},
+    In fact, for any compact $K \subset \mathbb R$, due to Lemma \ref{lem: estimate of exponential remaining},
 \begin{equation}
@@
     \\&\leq(\sup_{\theta \in K}|\theta|) \int_{[0,1)}|x^2| \nu(dx)+\int_{[1,\infty)} |x|  \nu(dx)
-    < \infty,
-    \quad \epsilon > 0.
+    %< \infty,
+    %\quad \epsilon > 0.
+    < \infty.
 \end{align}
@@
 \end{equation}
-
-	Therefore, according to \cite[Theorem 3.2.4.]{Cuppens1975Decomposition}, we have that map $\theta \mapsto \mathbf P[e^{i\theta Y}]$ from $\mathbb R$ to $\mathbb C$ is differentiable with
+	%Therefore, according to \cite[Theorem 3.2.4.]{Cuppens1975Decomposition}, we have that map $\theta \mapsto \mathbf P[e^{i\theta Y}]$ from $\mathbb R$ to $\mathbb C$ is differentiable with
+    Now, according to \cite[Theorem 3.2.4.]{Cuppens1975Decomposition}, we have that map $\theta \mapsto \mathbf P[e^{i\theta Y}]$ from $\mathbb R$ to $\mathbb C$ is differentiable with
 \begin{equation}
@@
 \item
-	the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by 
+	%the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
+    The branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
 \begin{equation}
@@
 \end{itemize}
-	We refer our reader to \cite{Li2011Measure} for more discussion about the definition and the existence of superprocesses.
+	We refer our reader to \cite{Li2011Measure-valued} for more discussion about the definition and the existence of superprocesses.
     To avoid triviality, we assume that $\psi(x,z)\neq -\beta(x)z$ for some $x \in E$ and $z \geq 0$; and that $\Pi_x(\zeta>t)>0$ for each $x \in E$ and $t \geq 0$.
@@
 	Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.
-	Denote by $\mathbb W$ the space of $\mathcal M_E^1$-valued c\`{a}dl\`{a}g paths whis its conanical path denoted by $(W_t)_{t\geq 0}$.
+	%Denote by $\mathbb W$ the space of $\mathcal M_E^1$-valued c\`{a}dl\`{a}g paths whis its conanical path denoted by $(W_t)_{t\geq 0}$.
+    Denote by $\mathbb W$ the space of $\mathcal M_E^1$-valued c\`{a}dl\`{a}g paths with its conanical path denoted by $(W_t)_{t\geq 0}$.
 	We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
-	Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure},
+	Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued},
 	there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
@@
 \end{equation}
-	It is know from \cite[Proposition 2.27]{Li2011Measure} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for any $t > 0$, $\mu \in \mathcal M_E^1$ and $f\in b\mathscr B^+_E$,
+    Assume that the superprocess $X$ is non-presistent with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
+	It is know from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for any $t > 0$, $\mu \in \mathcal M_E^1$ and $f\in b\mathscr B^+_E$,
 \begin{equation}
@@
 	Denote by $v_f(t,x,\theta) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i\theta X_t(f)}]$ the charateristic exponent of random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
-	Assume that the superprocess $X$ is non-presistent with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
 	According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, for each $\theta \in \mathbb R$,
@@
 \begin{equation}
-\label{eq: v has positive real part}
-	\operatorname{Re} v_f(t,x,\theta) \geq 0,\quad \theta \in \mathbb R.
-\end{equation}
+\label{eq: -v has positive real part}
+	\operatorname{Re} v_f(t,x,\theta) \leq 0,\quad \theta \in \mathbb R.
+\end{equation}
+%new added
+    Therefore, it is legal to talk about $\psi(x,-v_f(t,x,\theta))$ since in $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
+%end new added
 	According to Lemma \ref{lem: estimate of exponential remaining}, we have that
 \begin{equation}
+\label{eq: upper bound for vf}
 	|v_f(t,x,\theta)| \leq \mathbb N_x[|e^{i\theta W_t(f)} - 1|]
@@
     From \eqref{eq: estimate of deriavetive of v(theta)} and the dominate convergence theorem, we can verify that $(\partial/\partial \theta)v_f(t,x,\theta)$ is continuous in $\theta$.
-    In another words, $\theta \to v_f(t,x,\theta)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
+    %In another words, $\theta \to v_f(t,x,\theta)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
+    In another words, $\theta \mapsto -v_f(t,x,\theta)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
     According to this and \eqref{eq: path integration representation of h}, we can write
@@
 \label{eq: path integration representation of psi(v)}
-    \psi(x,v_f(t,x,\theta_0)) = \int_0^{\theta_0} \psi'(x,v_f(t,x,\theta)) \frac{\partial}{\partial \theta} v_f(t,x,\theta)~d\theta,
+    %\psi(x,v_f(t,x,\theta_0)) = \int_0^{\theta_0} \psi'(x,v_f(t,x,\theta)) \frac{\partial}{\partial \theta} v_f(t,x,\theta)~d\theta,
+    \psi(x,-v_f(t,x,\theta_0)) = -\int_0^{\theta_0} \psi'(x,-v_f(t,x,\theta)) \frac{\partial}{\partial \theta} v_f(t,x,\theta)~d\theta,
     \quad \theta_0 \in \mathbb R.
@@
 \label{eq: upper bound of psi'(v)}
-    &\big|\psi'\big(x, v_f(t,x,\theta)\big)\big| 
-    \\&= \Big| -\beta(x)+ 2\alpha(x) v_f(t-s,x,\theta) 
-    + \int_{(0,\infty)} y (e^{-y v_f(t-s,x,\theta)} - 1) \pi(x,dy)\Big|
-    \\&= \Big| - \beta(x)+ 2\alpha(x)\mathbb N_x(e^{i\theta W_{t}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[e^{i\theta W_{t}(f)} - 1] \pi(x,dy) \Big|
+    %&\big|\psi'\big(x, v_f(t,x,\theta)\big)\big|
+    &\big|\psi'\big(x, -v_f(t,x,\theta)\big)\big|
+    %\\&= \Big| -\beta(x)+ 2\alpha(x) v_f(t-s,x,\theta) + \int_{(0,\infty)} y (e^{-y v_f(t-s,x,\theta)} - 1) \pi(x,dy)\Big|
+    \\&= \Big| -\beta(x)- 2\alpha(x) v_f(t-s,x,\theta) + \int_{(0,\infty)} y (1- e^{y v_f(t-s,x,\theta)} ) \pi(x,dy)\Big|
+    %\\&= \Big| - \beta(x)+ 2\alpha(x)\mathbb N_x(e^{i\theta W_{t}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[e^{i\theta W_{t}(f)} - 1] \pi(x,dy) \Big|
+    \\&= \Big| - \beta(x)- 2\alpha(x)\mathbb N_x(e^{i\theta W_{t}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i\theta X_{t}(f)}] \pi(x,dy) \Big|
 \\ &\leq \|\beta\|_\infty + 2\alpha(x)\mathbb N_x[|\theta| W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}\big[2\wedge\big(|\theta| W_t(|f|)\big)\big] \pi(x,dy)
@@
 \label{eq: upper bound of psi(v)}
-    \big|\psi\big(x,v_f(t,x,\theta)\big)\big| 
+    %\big|\psi\big(x,v_f(t,x,\theta)\big)\big|
+    \big|\psi\big(x,-v_f(t,x,\theta)\big)\big|
     \leq c_0|\theta|~(P^\beta_t |f|)(x)+c_1 |\theta|^2 ~(P^\beta_t |f|)(x)^2,
@@
 \label{eq: domination of psi(v)}
-    &\Pi_x\Big[\int_0^t |\psi(\xi_s,v_f(t-s,\xi_s,\theta))|ds\Big] 
+    %&\Pi_x\Big[\int_0^t |\psi(\xi_s,v_f(t-s,\xi_s,\theta))|ds\Big]
+    &\Pi_x\Big[\int_0^t |\psi(\xi_s,-v_f(t-s,\xi_s,\theta))|ds\Big]
 \\&\leq \Pi_x\Big[\int_0^t \big(c_0|\theta| (P_{t-s}^\beta|f|)(\xi_s)+c_1|\theta|^2(P_{t-s}^\beta|f|)(\xi_s)^2\big)ds\Big]
@@
 \[
-    \Pi_x\Big[\int_0^t \psi(\xi_s,v_f(t-s,\xi_s,\theta))ds\Big]
+    %\Pi_x\Big[\int_0^t \psi(\xi_s,v_f(t-s,\xi_s,\theta))ds\Big]
+    \Pi_x\Big[\int_0^t \psi(\xi_s,-v_f(t-s,\xi_s,\theta))ds\Big]
     \in \mathbb C
@@
     \mathbf m(\xi,ds,dw)
-    := 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
+    %:= 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
+    := 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
 \end{align}
@@
 \begin{prop}
+\label{prop: complex FKPP-equation}
 	Let $f\in L_2(\xi)$. Then for each $t\geq 0$, $x\in E$ and $\theta \in \mathbb R$,
@@
 \label{eq: complex FKPP-equation}
-	v_f(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s,v_f(t-s,\xi_s,\theta)\big) ds \Big]
-	\\= i\theta \Pi_{x} [f(\xi_t)].
-\end{equation}
+	v_f(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s, - v_f(t-s,\xi_s,\theta)\big) ds \Big]
+	\\= i\theta \Pi_{x} [f(\xi_t)],
+\end{equation}
+%new
+and
+\begin{equation}
+\label{eq: complex FKPP-equation with FK-transform}
+    v_f(t,x,\theta) -  \int_0^t P_{t-s}^{\beta} \psi_0\big(\cdot,-v_f(s,\cdot,\theta)\big) (x)~ds
+    \\= i\theta P_t^\beta f(x).
+\end{equation}
+%end new
 \end{prop}
@@
 	Denoted by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
-    Given $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$.
+    %Given $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$.
+    Conditioned on $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$.
     Denote by $\Pi_{r,x}$ the probability of Hunt process $\{\xi; \Pi\}$ initiated at time $r$ and position $x$.
@@
 \end{align}
-    According to this, Fubini's theorem, \eqref{eq: N and characteristic exponent}, \eqref{eq: v has positive real part} and the argument in Subsection \ref{sec: extension of branching mechanism}, we have $\mathbf Q^{(g,t)}_{x}$-a.s.ly,
+    According to this, Fubini's theorem, \eqref{eq: N and characteristic exponent}, \eqref{eq: -v has positive real part} and the argument in Subsection \ref{sec: extension of branching mechanism}, we have $\mathbf Q^{(g,t)}_{x}$-a.s.ly,
 \begin{align}
 	&\int_{[0,t]\times \mathbb N}(e^{i\theta w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
-	\\&=\int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}(e^{i\theta W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i\theta W_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
-	\\&=\int_0^t \Big( 2\alpha(\xi_s) v_f(t-s,\xi_s,\theta) 
-	+ \int_{(0,\infty)} y (e^{-y v_f(t-s,\xi_s,\theta)} - 1) \pi(\xi_s,dy) \Big) ds
-	\\&= \int_0^t \psi'_0\big(\xi_s, v_f(t-s,\xi_s,\theta)\big)ds.
+	\\&=\int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}(e^{i\theta W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i\theta X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
+	%\\&=\int_0^t \Big( 2\alpha(\xi_s) v_f(t-s,\xi_s,\theta) + \int_{(0,\infty)} y (e^{-y v_f(t-s,\xi_s,\theta)} - 1) \pi(\xi_s,dy) \Big) ds
+    \\&=\int_0^t \Big( 2\alpha(\xi_s) v_f(t-s,\xi_s,\theta) + \int_{(0,\infty)} y (e^{y v_f(t-s,\xi_s,\theta)} - 1) \pi(\xi_s,dy) \Big) ds
+	%\\&= \int_0^t \psi'_0\big(\xi_s, v_f(t-s,\xi_s,\theta)\big)ds.
+    \\&= -\int_0^t \psi'_0 \big(\xi_s, -v_f(t-s,\xi_s,\theta)\big)ds.
 \end{align}
@@
 	&=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i\theta w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
-	\\&= \Pi_x^{(g,t)} [e^{\int_0^t \psi'_0(\xi_s, v_f(t-s,\xi_s,\theta))ds}]
-	\\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta))ds} ].
+	%\\&= \Pi_x^{(g,t)} [e^{\int_0^t \psi'_0(\xi_s, v_f(t-s,\xi_s,\theta))ds}]
+    \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -v_f(t-s,\xi_s,\theta))ds}]
+	%\\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta))ds} ].
+    \\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta))ds} ].
 \end{align}
@@
 	&= \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i\theta X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i\theta X_t(f)}]
-	\\& = \Pi_x[ f(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta)) ds}  ].
+	%\\& = \Pi_x[ f(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta)) ds}  ].
+    \\& = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta)) ds}  ].
 \end{align}
@@
 	\frac{\partial}{\partial \theta} v_f(t, x, \theta)
-	= \Pi_x[ if(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta)) ds} ].
+	%= \Pi_x[ if(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta)) ds} ].
+    = \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta)) ds} ].
 \end{align}
@@
 	&\frac{\partial}{\partial \theta} v_f(t - r, x, \theta)
-	= \Pi_x[ if(\xi_{t-r}) e^{\int_0^{t-r} \psi'(\xi_s, v_f(t-r-s,\xi_s,\theta)) ds} ]
-	\\&= \Pi_{r,x}[if(\xi_t)e^{\int_0^{t-r} \psi'(\xi_{r+s}, v_f(t-r-s,\xi_{r+s},\theta)) ds} ]
-	= \Pi_{r,x}[if(\xi_t)e^{\int_r^t \psi'(\xi_{s}, v_f(t-s,\xi_{s},\theta)) ds} ].
-\end{align}
-    From \eqref{eq: upper bound of psi'(v)}, we know that for each fixed $\theta \in \mathbb R$, $(t,x) \mapsto |\psi'(x,v_f(t,x,\theta))|$ is bounded above.
+	%= \Pi_x[ if(\xi_{t-r}) e^{\int_0^{t-r} \psi'(\xi_s, v_f(t-r-s,\xi_s,\theta)) ds} ]
+	%\\&= \Pi_{r,x}[if(\xi_t)e^{\int_0^{t-r} \psi'(\xi_{r+s}, v_f(t-r-s,\xi_{r+s},\theta)) ds} ]
+	%= \Pi_{r,x}[if(\xi_t)e^{\int_r^t \psi'(\xi_{s}, v_f(t-s,\xi_{s},\theta)) ds} ].
+    = \Pi_x[ if(\xi_{t-r}) e^{-\int_0^{t-r} \psi'(\xi_s, -v_f(t-r-s,\xi_s,\theta)) ds} ]
+    \\&= \Pi_{r,x}[if(\xi_t)e^{-\int_0^{t-r} \psi'(\xi_{r+s}, -v_f(t-r-s,\xi_{r+s},\theta)) ds} ]
+    = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -v_f(t-s,\xi_{s},\theta)) ds} ].
+\end{align}
+    %From \eqref{eq: upper bound of psi'(v)}, we know that for each fixed $\theta \in \mathbb R$, $(t,x) \mapsto |\psi'(x,v_f(t,x,\theta))|$ is bounded above.
+    From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-v_f(t,x,\theta))|$ is locally bounded (i.e.
+bounded on $[0,T]\times E$ for each $T \geq 0$).
 	Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
 \begin{equation}
-	\frac{\partial}{\partial \theta} v_f(t-r, x, \theta) - \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s, v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
-	= \Pi_{r,x} [i f(\xi_t)].
-\end{equation}
-	Integrating the above with respect to $\theta$, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we have
-\begin{equation}
-	v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
-	\\= i\theta \Pi_{r,x} [f(\xi_t)].
-\end{equation}
-    Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} is true if $f\in b\mathscr B_E$.
-
-    Now assume that $f\in L_2(\xi)$. Set $n \in \mathbb N$.
+	%\frac{\partial}{\partial \theta} v_f(t-r, x, \theta) - \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s, v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
+    \frac{\partial}{\partial \theta} v_f(t-r, x, \theta) + \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s,- v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
+	= \Pi_{r,x} [i f(\xi_t)],
+\end{equation}
+%new added
+    and
+\begin{align}
+    &\frac{\partial}{\partial \theta} v_f(t-r, x, \theta) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du}\psi_0'\big(\xi_s,- v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
+    \\&= \Pi_{r,x} [i e^{\int_r^t \beta(\xi_s)ds}f(\xi_t)].
+\end{align}
+%end added
+	Integrating the aboves with respect to $\theta$, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we have
+\begin{equation}
+	%v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
+    v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
+	\\= i\theta \Pi_{r,x} [f(\xi_t)],
+\end{equation}
+%new added
+    and similarly,
+\begin{equation}
+    v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du} \psi_0\big(\xi_s,-v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
+    \\= i\theta \Pi_{r,x} [e^{\int_r^t\beta(\xi_u)du}f(\xi_t)].
+\end{equation}
+%end added
+    %Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} is true if $f\in b\mathscr B_E$.
+    Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} is true if $f\in b\mathscr B_E$.
+
+    %Now assume that $f\in L_2(\xi)$.
+    The rest of the proof is to evaluate \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} for all $f\in L_2(\xi)$.
+We only do this for \eqref{eq: complex FKPP-equation} since the argument for \eqref{eq: complex FKPP-equation with FK-transform} is similar.
+    Set $n \in \mathbb N$.
     Writing $f_n := (f^+ \wedge n) - (f^- \wedge n)$, then $f_n \xrightarrow[n\to \infty]{} f$ pointwisely.
-    From what we have proved, 
+    From what we have proved, we have
 \begin{equation}
@@
 
-\bibitem{Li2011Measure}
+\bibitem{Li2011Measure-valued}
 Li, Z.:

### 2019-01-31 supCLT.tex
supCLT.tex: 0926

@@
     \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
-    = e^{-\langle u_f(\cdot , t), \mu \rangle},
+    = e^{-\langle u_f(t,\cdot), \mu \rangle},
     \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
 \end{equation}
-where $(x,t) \mapsto u_f(x, t)$ is the unique locally bounded positive solution to the equation
+where $(t,x) \mapsto u_f(t,x)$ is the unique locally bounded positive solution to the equation
 \begin{equation}\label{eq1}
-     u_f(x , t) + \Pi_x \Big[ \int_0^t\psi\big(u_f(\xi_s,t-s)\big)~ds\Big]
+     u_f(t,x) + \Pi_x \Big[ \int_0^t\psi\big(u_f(t-s, \xi_s)\big)~ds\Big]
      = \Pi_x [f(\xi_t)],
@@
     Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
-    The fact $\psi(\infty)=\infty$ implies that the probability of extinguish event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see \cite[Theorem 12.7]{Kyprianou2014Fluctuations} for example.
+    The fact $\psi(\infty)=\infty$  and $\int^{\infty}\frac{1}{\psi(z)}~dz<\infty$ implies that the probability of extinguish event $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ is contained in $(0,1)$, which means that our superprocess is non-persistent.
     In fact,
 \begin{equation}
-    \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
+    \mathbb{P}_{\mu}(D)= \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
     = e^{-\alpha^* \|\mu\|},
 \end{equation}
-    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
+    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$. See \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations} for a example.
 %comment
-    {\bf (Zhenyao: We should use \cite[Theorem 12.5]{Kyprianou2014Fluctuations} and talk about the probability of $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$.
+   % {\bf (Zhenyao: We should use \cite[Theorem 12.5]{Kyprianou2014Fluctuations} and talk about the probability of $D:= \{\exists t\geq %0,~\text{s.t.}~\|X_t\|=0\}$.
 Because we want to emphsis that our superprocess is non-presistent.)}
 %end comment
-
+%comment
+    {\bf (Jianjie: I rewrite this part to emphsis that our superprocess is non-presistent.)}
+%end comment
     Define the \emph{Fenyman-Kac semigroup} by
@@
     %According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
-    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that,
+    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R_0 \in \mathcal{P}$ such that,
 \begin{equation}
@@
     |T_tf(x)|
-    \leq e^{-\kappa(f)bt} R(x),
+    \leq e^{-\kappa(f)bt} R_0(x),
     \quad t\geq 0, x\in \mathbb R^d.
@@
 %\end{equation}
-    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, denote by $w_f(x,t,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]$ the characteristic exponent of $\{X_t(f); \mathbb P_{\delta_x}\}$
+    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, denote by $v_f(t,x,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]$ the characteristic exponent of $\{\langle f,X_t \rangle; \mathbb P_{\delta_x}\}$
     (For percise definition, see the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
-    From \eqref{eq: -v has positive real part}, we know that $- w_f(x,t,\theta)$ taks values in $\mathbb C_+$.
+    From \eqref{eq: -v has positive real part}, we know that $- v_f(t,x,\theta)$ taks values in $\mathbb C_+$.
     Furthermore, we know from Proposition \ref{sec: definition of characteristic exponent} that
@@
 \begin{align}\label{charequation}
-    w_f(x,t,\theta)-\int_0^t T_{t-s} \psi \big(-w_f(\cdot,s,\theta)\big)(x)ds
+    v_f(t,x,\theta)-\int_0^t T_{t-s} \psi \big(-v_f(s,\cdot,\theta)\big)(x)ds
     =i\theta T_tf(x),
@@
     %w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x),
-    w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \psi_0(-w_f(\cdot,s,\theta))(x)ds=i\theta T^{\alpha}_t f(x),
+    v_f(t,x,\theta)-\int_0^t T^{\alpha}_{t-s} \psi_0(-v_f(s,\cdot,\theta))(x)ds=i\theta T^{\alpha}_t f(x),
     \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
@@
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
- We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0\leq\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+ We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0<\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  \begin{thm}\label{Theorem11}
-     If $g \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(g)b(1+\beta)$, then as $t\rightarrow \infty$,
-     $$e^{-(\alpha-\kappa(g)b)t}\langle g, X_t\rangle \rightarrow\sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
-     for any $0\leq\gamma<\beta$.
-
-     Moreover, if $g$ is twice differentiable and its twice derivative $D^2 g$ satisfies $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure.
+     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then as $t\rightarrow \infty$,
+     $$e^{-(\alpha-\kappa(f)b)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa(f)}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
+     for any $0<\gamma<\beta$.
+
+     Moreover, if $f$ is twice differentiable and its twice derivative $D^2 f$ satisfies $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
  \end{thm}
@@
  \begin{rem}
-    If $\kappa(g)=0$, $\langle g, \phi_{\kappa(g)}\rangle_{\varphi}$ reduces to $\langle g,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
-     $$e^{-\alpha t}\langle g, X_t\rangle \rightarrow \langle g, \varphi\rangle W_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
-    for any $0\leq\gamma<\beta$.
-
-    Moreover, if $g$ is twice differentiable and $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure.
+    If $\kappa(f)=0$, $\langle f, \phi_{\kappa(f)}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
+     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle W_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
+    for any $0<\gamma<\beta$.
+
+    Moreover, if $f$ is twice differentiable and $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
  \end{rem}
@@
 \subsubsection{Critical Branching Rate}
-For $g\in \mathcal{P}$, define
-$$\tilde{m}[g]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
-{\color{red}where}
-$$\phi(x)=\sum_{|p|=\kappa(g)}\langle g,\phi_p\rangle\phi_p(x).$$
-See Lemma \ref{lemma210} for more details about $\tilde{m}[g]$.
+For $f\in \mathcal{P}$, define
+$$\tilde{m}[f]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
+where
+$$\phi(x)=\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).$$
+See Lemma \ref{lemma210} for more details about $\tilde{m}[f]$.
 \begin{thm}\label{Theorem12}
-Let $g\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-$$\frac{\langle g,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
+Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(f)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+$$\frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
 where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by
-$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[g]).$$
+$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[f]).$$
 \end{thm}
@@
 
-For $g\in \mathcal{P}$, define
-$$m[g]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx$$
-In Lemma \ref{lemma211}, we will prove that $|m[g]|<\infty$.
+For $f\in \mathcal{P}$, define
+$$m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx$$
+In Lemma \ref{lemma211}, we will prove that $|m[f]|<\infty$.
 \begin{thm}\label{Theorem13}
-    If $g\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-    $$\frac{\langle g,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
+    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa(f)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
     where $\eta_2$ is a $(1+\beta)$-stable random variable with characteristic function given by
-    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(\theta^{1+\beta}m[g]).$$
+    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(\theta^{1+\beta}m[f]).$$
 \end{thm}
@@
 \section{Preliminaries}
-In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in [0,\beta)$. 
+In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
 %For notational convenience, we always fix $g\in \mathcal{P}$ in the following sections, correspondingly, there exists $R\in\mathcal{P}$ such that
-    In this section, we fix a $g\in \mathcal{P}$. 
-    According to \eqref{eq:semigroupineq}, there exists an $R_0\in\mathcal{P}$ such that 
-\begin{align}
-     %|T_tg|\leq T_t|g|\leq e^{-\kappa(g)bt}R.
+    In this section, we assume a function $g$ satisfying that there exists $C_h, \kappa>0$ and $R^g_0\in \mathcal{P}$
+    such that
+\begin{align}
+\label{eq:gcontrol1}
      |T_tg|(x)
-     \leq e^{-\kappa(g)bt}R_0(x),
-     \quad t\geq 0,x\in E.
+     \leq C_g e^{-\kappa bt}R^g_0(x),
+     \quad t\geq 0,x\in \mathbb{R}^d.
 \end{align}
 %new added
-Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R \in \mathcal P$ such that
+Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R^g \in \mathcal P$ such that
 \begin{align}
@@
     T_s|T_t g|(x)
-    \leq e^{-\kappa(g)bt} R(x), 
-    \quad t\geq 0,s\geq 0,x\in E.
+    \leq C_g e^{-\kappa bt} R^g(x),
+    \quad t\geq 0,s\geq 0,x\in \mathbb{R}^d.
 \end{align}
@@
     %For $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$.
-    For each $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$. 
+    For each $f\in\mathcal{P}$ and $k \in \mathbb{N}$, let $f_k=T^{\alpha}_k f$.
     %For each $t-k\geq 1$, according to \eqref{eq:meanformula}, write
-    For each $k \in \mathbb N$ and $t\geq k+1$, according to \eqref{eq:meanformula}, write
+    %For each $k \in \mathbb N$ and $t\geq k+1$, 
+    According to \eqref{eq:meanformula}, write
 \begin{align*}
@@
     &=\langle g_k, X_{t-k}\rangle-\langle T_1^{\alpha}g_{k},X_{t-k-1}\rangle\\
-    &=\langle g_k, X_{t-k}\rangle-\langle g_{k+1},X_{t-k-1}\rangle.
+    &=\langle g_k, X_{t-k}\rangle-\langle g_{k+1},X_{t-k-1}\rangle, \quad t\geq k+1.
 \end{align*}
     %If $k=t$, let $M_t^t[g]:=\langle g_t,\mu\rangle$, where $\mu $ is the initial configuration.
-    For each $t\geq 0$, let $M_t^t[g]:=\langle g_t,\mu\rangle$ under $\mathbb P_\mu$, where $\mu $ is the initial configuration. 
-    From now on, we assume $t$ is a positive integer, for simplicity. Thus
+    What's more, we denote $M_{\lfloor t\rfloor}^t[g]:=\langle g_{\lfloor t \rfloor},X_{t-\lfloor t\rfloor}\rangle-\langle g_t, \mu\rangle$ and $M_t^t[g]:=\langle g_t,\mu\rangle$ under $\mathbb P_\mu$, where $\mu $ is the initial configuration.
+Thus
 \begin{equation}\label{decomposition}
-    \langle g,X_t\rangle
-    =\sum_{k=0}^{t}M_k^t[g]
+    \langle g,X_t\rangle-M_t^t[g]
+    =\sum_{k=0}^{\lfloor t\rfloor}M_k^t[g]
 %new added
-    , \quad t \in \mathbb N.
+    , \quad t \geq 0.
 %end new added
@@
 
-{\bf Jianjie: We have to emphasize that, if $t\notin \mathbb{N}$, there will appear an additional term corresponding to the interval $[\lfloor t \rfloor,t]$, which can be handled with the same techniques.
-}
+%{\bf Jianjie: We have to emphasize that, if $t\notin \mathbb{N}$, there will appear an additional term corresponding to the interval $[\lfloor t %\rfloor,t]$, which can be handled with the same techniques.
+%}
 \subsection{Approximate expansion of characteristic function}
 
-In this subsection, we will estimate the characteristic function of $M_k^t[g]$ near $0$. First, we will prove the following inequality which controls $w_{g_k}(x,s,\theta)$.
+In this subsection, we will estimate the characteristic function of $M_k^t[g]$ near $0$. First, we will prove the following inequality which controls $v_{g_k}(s,x,\theta)$.
 \begin{lem}\label{lemma1}
 %For any $k \in \mathbb{N}$, $x\in\mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
-    Let $R \in \mathcal P$ be the control function in \eqref{eq:gcontrol}, then
+    Let $R^g \in \mathcal P$ be the control function in \eqref{eq:gcontrol}, then
 %$$e^{-(\alpha-\kappa(g)b) s}|w_{g_k}(x,s,\theta)|\leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), \quad s\geq 0.$$
 \begin{equation}
-    e^{-\alpha s}|w_{g_k}(x,s,\theta)|
-    \leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), 
+    e^{-\alpha s}|v_{g_k}(s,x,\theta)|
+    \leq C_g|\theta|e^{(\alpha-\kappa b)k} R^g(x),
     \quad k\in \mathbb N, x\in \mathbb R^d, \theta \in \mathbb R, s\geq 0.
@@
 %comment
-    {\bf Zhenyao: The statement of the above Lemma is changed. I think the old version is not correct. I'm not sure how this influence the rest of the paper.
-
-    Also, there are some paragraphs below I deleted which are duplicated with the appendix.}
+   % {\bf Zhenyao: The statement of the above Lemma is changed. I think the old version is not correct. I'm not sure how this influence the rest of the paper.
+
+    % Also, there are some paragraphs below I deleted which are duplicated with the appendix.}
 %end comment
@@
 %Recall that $w_{g_k}(x,s,\theta)=\log\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
-    Recall that $w_{g_k}(x,s,\theta)=\operatorname{Log}\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
+    Recall that $v_{g_k}(s,x,\theta)=\operatorname{Log}\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
     %Replace $f$ by $-i\theta g_k$ in equation \eqref{Nmeasure},\eqref{Nmean}, we obtain that $w_{g_k}(x,s,\theta)=\mathbb{N}_x\left(e^{i\theta\langle g_k,w_s\rangle}-1\right)$.
@@
     %$$|w_{g_k}(x,s,\theta)|=|\mathbb{N}_x(e^{i\theta\langle g_{k},\omega_s \rangle}-1)|\leq |\theta|\mathbb{N}_x(\langle|g_k|,\omega_s\rangle)\leq|\theta|T_{s+k}^{\alpha}|g|$$
-    Let $R \in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
+    Let $R^g \in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
     From \eqref{eq: upper bound for vf} in the appendix, we have for each $k \in \mathbb{N}$, $x\in\mathbb{R}^d$, $\theta\in \mathbb{R}$ and $s\geq 0$,
 \begin{equation}
-    w_{g_k}(x,s,\theta) 
+    v_{g_k}(s,x,\theta)
     \leq |\theta| (T_s^\alpha |g_k|) (x)
     = |\theta| (T_{s}^\alpha |T^\alpha_k g|) (x)
-    \leq |\theta| e^{\alpha(s+k)}e^{-\kappa(g)bk}R(x).
+    \leq C_g|\theta| e^{\alpha(s+k)}e^{-\kappa bk}R^g(x).
     \qedhere
@@
     %For any $k \in \{0,1,...,t\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$, by the Markov property of $X$, we have
-    For each $t \in \mathbb N$ and $k \in \{0,1,...,t-1\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$.
+    For each $t \geq 0 $ and $k \in \{0,1,...,\lfloor t \rfloor-1\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$.
     By the Markov property of $X$, we have
@@
     \\&=\mathbb P_{X_{t-k-1}} [e^{i\theta(\langle g_k,X_1\rangle)}]e^{-i\theta \langle T_1^{\alpha}g_k,X_{t-k-1}\rangle}
-    \\&= e^{\langle w_{g_k}(\cdot,1,\theta),X_{t-k-1}\rangle -i \theta\langle T_1^{\alpha}g_k,X_{t-k-1}\rangle},
+    \\&= e^{\langle v_{g_k}(1,\cdot,\theta),X_{t-k-1}\rangle -i \theta\langle T_1^{\alpha}g_k,X_{t-k-1}\rangle},
 %new added
@@
 \end{align*}
-Hence, it is important to estimate the function $w_{g_k}(x,1,\theta)$. For any $f \in \mathcal{P}$, let
+Hence, it is important to estimate the function $v_{g_k}(1,x,\theta)$. For any $f \in \mathcal{P}$, let
 \begin{equation}\label{w2function}
     %\tilde{w}_{f}(x,t,\theta)=i\theta T^{\alpha}_t f(x) + \int_0^t T^{\alpha}_{t-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds
-    \tilde{w}_{f}(x,t,\theta)
+    \tilde{v}_{f}(t,x,\theta)
     := i\theta T^{\alpha}_t f(x) + \int_0^t T^{\alpha}_{t-s}\psi_0(-i\theta T_s^{\alpha}f(\cdot))(x)ds,
@@
 %There exists $R_1 \in \mathcal{P}$ and $p_1 >1+\beta$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have
-There exists $R_1 \in \mathcal{P}$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have
-\begin{align}
-    |w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|
-    \leq |\theta e^{(\alpha-\kappa(g)b)k}|^{1+2\beta}R_1(x),
+There exists $R^g_1 \in \mathcal{P}$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have
+\begin{align}
+    |v_{g_k}(s,x,\theta)-\tilde{v}_{g_k}(s,x,\theta)|
+    \leq |C_g\theta e^{(\alpha-\kappa b)k}|^{1+2\beta}R^g_1(x),
     \quad x\in \mathbb{R}^d,\theta\in \mathbb{R}.
@@
 %As $\exp({\rm Re~}w_{g_k})=|\exp(w_{g_k})|=\left|\mathbb{P}_{\delta_x}\exp(i\theta \langle  g_k,X_t\rangle)\right|\leq 1$ implying ${\rm Re~}(-w_{g_k})\geq0$,
-From \eqref{eq: -v has positive real part} we know that $\operatorname{Re}(-w_{g_k})\geq 0$.
+From \eqref{eq: -v has positive real part} we know that $\operatorname{Re}(-v_{g_k})\geq 0$.
 %we use the fact that
@@
 \label{eq: estimate of wgk}
-   &|w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|
-   \\&\leq \int_0^s T_{s-v}^{\alpha}\left(|(-w_{g_k}(\cdot,v,\theta))^{1+\beta}-(-i\theta T_v^{\alpha}g_k)^{1+\beta}|\right)(x)~dv
-   \\&\leq C_0\int_0^s T_{s-v}^{\alpha}\left( |w_{g_k}(\cdot,v,\theta)-i\theta T_v^{\alpha}g_{k}|\left(|w_{g_k}(\cdot,v,\theta)|^{\beta}+|i\theta T_v^{\alpha}g_k|^{\beta}\right)\right)(x)~dv.
+   &|v_{g_k}(s,x,\theta)-\tilde{v}_{g_k}(s,x,\theta)|
+   \\&\leq \int_0^s T_{s-u}^{\alpha}\left(|(-v_{g_k}(u,\cdot,\theta))^{1+\beta}-(-i\theta T_u^{\alpha}g_k)^{1+\beta}|\right)(x)~du
+   \\&\leq C_0\int_0^s T_{s-u}^{\alpha}\left( |v_{g_k}(u,\cdot,\theta)-i\theta T_u^{\alpha}g_{k}|\left(|v_{g_k}(u,\cdot,\theta)|^{\beta}+|i\theta T_u^{\alpha}g_k|^{\beta}\right)\right)(x)~du.
 \end{align}
 %Notice that, for $0\leq v \leq 1$, $x\in \mathbb{R}^d$ and $\theta \in \mathbb{R}$, by Lemma \ref{lemma1} and \eqref{eq:gcontrol}, we have
-   Let $R\in \mathcal P$ be the control function in both \eqref{eq:gcontrol} and Lemma \ref{lemma1}, then for $0\leq v \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
+   Let $R^g\in \mathcal P$ be the control function in both \eqref{eq:gcontrol} and Lemma \ref{lemma1}, then for $0\leq u \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
 \begin{align}
@@
     %|w_{g_{k}}(x,v,\theta)|\leq &|\theta|e^{(\alpha-\kappa(g)b)k}(e^{(\alpha-\kappa(g)b)v}R(x))\leq|\theta|e^{(\alpha-\kappa(g)b)k}(C_1R(x)),
-    |w_{g_{k}}(x,v,\theta)|
-    &\leq |\theta|e^{(\alpha-\kappa(g)b)k+\alpha}R(x),
+    |v_{g_{k}}(u,x,\theta)|
+    &\leq C_g|\theta|e^{(\alpha-\kappa b)k+\alpha}R^g(x),
     \\
-    |i\theta T_v^{\alpha}g_k(x)|
-    &\leq |\theta| e^{\alpha(k+1)}T_v|T_k g|(x)
-    \leq |\theta|e^{(\alpha-\kappa(g)b)k+\alpha}R(x).
+    |i\theta T_u^{\alpha}g_k(x)|
+    &\leq |\theta| e^{\alpha(k+1)}T_u|T_k g|(x)
+    \leq C_g|\theta|e^{(\alpha-\kappa b)k+\alpha}R^g(x).
 \end{align}
@@
 %new added
-    Observe that $R^{1+\beta}\in \mathcal P$. 
-    According to \eqref{eq:semigroupineq}, there exists an $\tilde R_0 \in \mathcal P$ such that
+    Observe that $(R^g)^{1+\beta}\in \mathcal P$.
+    According to \eqref{eq:semigroupineq}, there exists an $\tilde R^g_0 \in \mathcal P$ such that
 \begin{align}
 \label{eq: tilde R0}
-    |T_t (R^{1+\beta})(x)| 
-    \leq \tilde R_0(x),
-    \quad t\geq0, x\in E.
-\end{align}
-    According \eqref{eq:chareq2}, \eqref{eq: upper bound of wgk} and above, for $0\leq v \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
+    |T_t ((R^g)^{1+\beta})(x)|
+    \leq \tilde R^g_0(x),
+    \quad t\geq0, x\in \mathbb{R}^d.
+\end{align}
+    According \eqref{eq:chareq2}, \eqref{eq: upper bound of wgk} and above, for $0\leq u \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
 %end new
@@
 \label{eq: Zineq}
-   &|w_{g_{k}}(x,v,\theta)-i\theta T_v^{\alpha}g_k(x)|
-   =\Big| \int_0^v T^{\alpha}_{v-u}(-w_{g_k}(\cdot,u,\theta))^{1+\beta}(x)du\Big| 
+   &|v_{g_{k}}(u,x,\theta)-i\theta T_u^{\alpha}g_k(x)|
+   =\Big| \int_0^u T^{\alpha}_{u-t}(-v_{g_k}(t,\cdot,\theta))^{1+\beta}(x)dt\Big|
    %\\\leq & \int_0^1 T_{1-u}^{\alpha}(|w_{g_k}(\cdot,u,\theta)|^{1+\beta})(x)du \nonumber \\
-   \\&\leq \int_0^v T_{v-u}^{\alpha}(|w_{g_k}(\cdot,u,\theta)|^{1+\beta})(x)du
-   \leq  |\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+\beta}\int_0^v (T_{v-u}^{\alpha}R^{1+\beta})(x)du
+   \\&\leq \int_0^u T_{u-t}^{\alpha}(|v_{g_k}(t,\cdot,\theta)|^{1+\beta})(x)dt
+   \leq  |C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{1+\beta}\int_0^u (T_{u-t}^{\alpha}(R^g)^{1+\beta})(x)dt
    %\\\leq &C_1^{1+\beta}e^{\alpha}|\theta e^{(\alpha-\kappa(g)b)k}|^{1+\beta}R^{1+\beta}(x)\nonumber\\
-   \\&\leq e^{\alpha}|\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+\beta}\tilde R(x).
+   \\&\leq e^{\alpha}|C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{1+\beta}\tilde R^g_0(x).
 %deleted
@@
 %where $R_2(x)=C_1^{1+\beta}e^{\alpha}R^{1+\beta}(x)$.
-    According to \eqref{eq:semigroupineq}, since $\tilde RR^{\beta} \in \mathcal P$, there exists an $\tilde R_1\in \mathcal P$ such that
+    According to \eqref{eq:semigroupineq}, since $\tilde R^g_0(R^g)^{\beta} \in \mathcal P$, there exists an $\tilde R^g_1\in \mathcal P$ such that
 \[
-    |T_t(\tilde RR^{\beta})(x)| 
-    \leq \tilde R_1(x),
-    \quad t\geq0, x\in E.
+    |T_t(\tilde R^g_0(R^g)^{\beta})(x)|
+    \leq \tilde R^g_1(x),
+    \quad t\geq0, x\in \mathbb{R}^d.
 \]
 %In consequence,
-As a consecuence of \eqref{eq: estimate of wgk}, \eqref{eq: Zineq}, \eqref{eq: upper bound of wgk} and the above, for $k \in \mathbb{N}$, $0\leq s \leq 1$, $x\in E$ and $\theta \in \mathbb R$, we have
-\begin{align}
-    &|w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|
+As a consecuence of \eqref{eq: estimate of wgk}, \eqref{eq: Zineq}, \eqref{eq: upper bound of wgk} and the above, for $k \in \mathbb{N}$, $0\leq s \leq 1$, $x\in \mathbb{R}^d$ and $\theta \in \mathbb R$, we have
+\begin{align}
+    &|v_{g_k}(s,x,\theta)-\tilde{v}_{g_k}(s,x,\theta)|
 %new added
-    \\&\leq C_0e^{\alpha}|\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta} \int_0^s T_{s-v}^{\alpha}( \tilde RR^{\beta})(x)~dv
+    \\&\leq C_0e^{\alpha}|C_g\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta} \int_0^s T_{s-u}^{\alpha}( \tilde R^g_0(R^g)^{\beta})(x)~du
 %end new added
     %\\&\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{2+\beta}\cdot 2CC_1e^{\alpha}R(x)R_2(x).
-    \\&\leq C_0e^{2\alpha}|\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta}\tilde R_1(x).
+    \\&\leq C_0e^{2\alpha}|C_g\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta}\tilde R^g_1(x).
     \qedhere
@@
 \[
-    Z_f(x,\theta)
+    Z_f(s,x,\theta)
     %:=\int_0^1 T^{\alpha}_{1-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds ,
-    :=\int_0^1 T^{\alpha}_{1-s}\big((-i\theta T_s^{\alpha}f)^{1+\beta}\big)(x)ds ,
+    :=\int_0^s T^{\alpha}_{s-u}\big((-i\theta T_u^{\alpha}f)^{1+\beta}\big)(x)du ,
 %new
-    \quad x\in E, \theta \in \mathbb R.
+    \quad s\geq 0, x\in E, \theta \in \mathbb R.
 %end new
 \]
-and let $Z_f(x)=Z_f(x,1)$. 
+and let $Z_f(s,x)=Z_f(s,x,1)$.
 %Observe that
@@
 \begin{equation}\label{zfunction}
-    Z_f(x,\theta)=\theta^{1+\beta}Z_f(x),
+    Z_f(s,x,\theta)=\theta^{1+\beta}Z_f(s,x),
 %new
-    \quad x\in E, \theta \in \mathbb R.
+    \quad s\geq 0, x\in E, \theta \in \mathbb R.
 %end new
@@
     %For any $k\in\{0,1,...,t\}$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
-    There exists $R_2\in \mathcal P$ such that for each $k\in\mathbb N$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
+    There exists $R^g_2\in \mathcal P$ such that for each $k\in\mathbb N$ and $0\leq s\leq1$, we have
 \begin{align}
 \label{zineq2}
-    |Z_{g_k}(x)|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}R_2(x),
+    |Z_{g_k}(s,x)|\leq C_g^{1+\beta}e^{(\alpha-\kappa b)(1+\beta)k}R^g_2(x), \quad x\in \mathbb{R}^d,
 \end{align}
@@
 \begin{align}
-    |Z_{g_k}(x,\theta)|\leq |\theta|^{1+\beta}e^{(\alpha-\kappa(g)b)(1+\beta)k}R_2(x). \label{zineq1}
+    |Z_{g_k}(s,x,\theta)|\leq C_g^{1+\beta}|\theta|^{1+\beta}e^{(\alpha-\kappa b)(1+\beta)k}R^g_2(x), \quad x\in \mathbb{R}^d,\theta\in \mathbb{R}. \label{zineq1}
 \end{align}
@@
     %By \eqref{eq:gcontrol}, we have
-    Let $R\in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
-    Let $\tilde R_0 \in \mathcal P$ be the control function in \eqref{eq: tilde R0}.
+    Let $R^g\in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
+    Let $\tilde R^g_0 \in \mathcal P$ be the control function in \eqref{eq: tilde R0}.
     Now, we have for each $k\in\mathbb N$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$,
 \begin{align}
-    |Z_{g_k}(x)|
+    |Z_{g_k}(s,x)|
     %&\leq \int_0^1 T_{1-s}^{\alpha}(|T_s^{\alpha}g_k|^{1+\beta})(x)ds \leq\int_0^t T_{1-s}^{\alpha}\left(|C_1 e^{(\alpha-\kappa(g)b)k}|R(x)\right )^{1+\beta}
-    &\leq c_0\int_0^1 T_{1-s}^{\alpha}(|T_s^{\alpha}g_k|^{1+\beta})(x)ds 
-    \leq c_0 \int_0^1 T_{1-s}^{\alpha}\Big(\big(e^{(\alpha-\kappa(g)b)k+\alpha}R\big)^{1+\beta}\Big)(x)
-    \\&\leq c_0e^{\alpha(2+\beta)} e^{(\alpha-\kappa(g)b)(1+\beta)k}\tilde R_2(x). 
+    &\leq c_0\int_0^s T_{s-u}^{\alpha}(|T_u^{\alpha}g_k|^{1+\beta})(x)du
+    \leq c_0 \int_0^s T_{s-u}^{\alpha}\Big(\big(e^{(\alpha-\kappa b)k+\alpha}R\big)^{1+\beta}\Big)(x)~du
+    \\&\leq c_0e^{\alpha(2+\beta)} C_g^{1+\beta}e^{(\alpha-\kappa b)(1+\beta)k}\tilde R^g_2(x).
 \qedhere
@@
 %comments
-    {\bf Zhenyao: I don't think the following corollary in the old version is accurate. Here is what I think the correct form should be.}
+   % {\bf Zhenyao: I don't think the following corollary in the old version is accurate. Here is what I think the correct form should be.}
 %end comment
@@
 %There exists $R_3 \in \mathcal{P}$ and $p_2 >1+\beta$ such that for any $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, we have
-There exists an $R_3 \in \mathcal{P}$ such that for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, we have
+There exists an $R^g_3 \in \mathcal{P}$ such that for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$,$\theta \in \mathbb{R}$ and $0\leq s\leq 1$, we have
 \[
     %\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}
-    \mathbb P_{\mu}[e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}]
+    \mathbb P_{\mu}[e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}]
     %=1+\langle Z_{g_k}(\cdot,\theta),\mu\rangle+\langle err(\cdot,\theta),\mu\rangle
-    =1+\langle Z_{g_k}(\cdot,\theta),\mu\rangle+ err(k,\mu,\theta),
+    =1+\langle Z_{g_k}(s,\cdot,\theta),\mu\rangle+ err(k,\mu,\theta),
 \]
     %where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R_3(\cdot)$.
-    where $|err(k,\mu,\theta)| \leq (|\theta e^{(\alpha-\kappa(g)b)k}|^{2+2\beta} + |\theta e^{(\alpha-\kappa(g)b)k}|^{1+2\beta} )\langle R_3,\mu\rangle$.
+    where $|err(k,\mu,\theta)| \leq (C_g|\theta e^{(\alpha-\kappa b)k}|^{2+2\beta} + C_g|\theta e^{(\alpha-\kappa b)k}|^{1+2\beta} )\langle R^g_3,\mu\rangle$.
 \end{cor}
@@
 \begin{proof}
-    Let $ w_f(x,\theta)=w_f(x,1,\theta)$, $\tilde{w}_f(x,\theta)=\tilde{w}_f(x,1,\theta)$ for short, and write
+    Let 
+    % $ w_f(x,\theta)=w_f(x,1,\theta)$, $\tilde{w}_f(x,\theta)=\tilde{w}_f(x,1,\theta)$ for short, and write
 \begin{align}
@@
     %\varphi_{\mu}(\theta)
-    \varphi_{k,\mu}(\theta)
+    \varphi_{k,\mu,s}(\theta)
     %=\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}
-    =\mathbb{P}_{\mu}[e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}]
-    =e^{(\langle w_{g_k}(\cdot,\theta),\mu \rangle-i\theta \langle T_1^{\alpha} g_k, \mu \rangle)},
+    =\mathbb{P}_{\mu}[e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}]
+    =e^{(\langle v_{g_k}(s,\cdot,\theta),\mu \rangle-i\theta \langle T_s^{\alpha} g_k, \mu \rangle)},
     \quad \theta \in \mathbb R.
@@
 \begin{align*}
-    &|\varphi_{k,\mu}(\theta)-1-\langle Z_{g_k}(\cdot, \theta),\mu\rangle|\\
-    &\leq|\varphi_{\mu,k}(\theta)-1-\left( \langle w_{g_k}(\cdot,\theta), \mu \rangle-i\theta \langle T_1^{\alpha}g_k,\mu\rangle\right)| + |\langle w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta),\mu \rangle|.
+    &|\varphi_{k,\mu,s}(\theta)-1-\langle Z_{g_k}(s,\cdot, \theta),\mu\rangle|\\
+    &\leq|\varphi_{\mu,k,s}(\theta)-1-\left( \langle v_{g_k}(s,\cdot,\theta), \mu \rangle-i\theta \langle T_s^{\alpha}g_k,\mu\rangle\right)| + |\langle v_{g_k}(s,\cdot,\theta)-\tilde{v}_{g_k}(s,\cdot,\theta),\mu \rangle|.
 \end{align*}
 %Using Lemma \ref{lemma2}, \eqref{eq: Zineq} and the fact that if $ {\rm Re~} z\leq 0$, $|e^z-1-z|\leq|z|^2$,   we get, for any $\theta \in \mathbb{R}$ and $k\in \mathbb{N}$,
-    Let $R_1\in \mathcal P$ be the control function in Lemma \ref{lemma2}. 
-    Let $\tilde R$ be the control function in \eqref{eq: Zineq}. 
+    Let $R^g_1\in \mathcal P$ be the control function in Lemma \ref{lemma2}.
+    Let $\tilde R^g$ be the control function in \eqref{eq: Zineq}.
     Notice that
 $
-    \operatorname{Re} \big(w_{g_k}(x,\theta) - i\theta T_1^\alpha g_k(x)\big)
-    = \operatorname{Re} w_{g_k}(x,\theta)
+    \operatorname{Re} \big(v_{g_k}(s,x,\theta) - i\theta T_s^\alpha g_k(x)\big)
+    = \operatorname{Re} v_{g_k}(s,x,\theta)
     \leq 0,
@@
     (see \eqref{eq: -v has positive real part} in the appendix); and if $ \operatorname{Re} z\leq 0$, we have $|e^z-1-z|\leq |z|^2$, (see Lemma \ref{lem: estimate of exponential remaining} in the appendix).
-    Therefore, for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, using Jensen's inequality,
-\begin{align*}
-    &|\varphi_{k,\mu}(\theta)-1- \langle Z_{g_k}(\cdot, \theta),\mu\rangle|\\
+    Therefore, for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$, $\theta \in \mathbb{R}$ and $0\leq s\leq1$, using Jensen's inequality,
+\begin{align*}
+    &|\varphi_{k,\mu,s}(\theta)-1- \langle Z_{g_k}(s,\cdot, \theta),\mu\rangle|\\
     %&\leq 2|\langle w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k, \mu \rangle|^2 + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle\\
-    &\leq |\langle w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k, \mu \rangle|^2 + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle
+    &\leq |\langle v_{g_k}(s,\cdot,\theta)-i\theta T_s^{\alpha}g_k, \mu \rangle|^2 + \langle |v_{g_k}(s,\cdot,\theta)-\tilde{v}_{g_k}(s,\cdot,\theta)|, \mu \rangle
 %new added
-    \\&\leq \langle |w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k|^2, \mu \rangle + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle
+    \\&\leq \langle |v_{g_k}(s,\cdot,\theta)-i\theta T_s^{\alpha}g_k|^2, \mu \rangle + \langle |v_{g_k}(s,\cdot,\theta)-\tilde{v}_{g_k}(s,\cdot,\theta)|, \mu \rangle
 %end new
     %\\&\leq |\theta_{k}|^{2(1+\beta)}\langle R_2,\mu\rangle + |\theta_{k}|^{2+\beta}\langle R_1,\mu\rangle,
-    \\&\leq e^{2\alpha}|\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{2+2\beta}\langle \tilde R^2,\mu\rangle + |\theta e^{(\alpha-\kappa(g)b)k}|^{1+2\beta}\langle R_1,\mu\rangle.
+    \\&\leq e^{2\alpha}|C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{2+2\beta}\langle (\tilde R^g)^2,\mu\rangle + |C_g\theta e^{(\alpha-\kappa b)k}|^{1+2\beta}\langle R^g_1,\mu\rangle.
     \qedhere
@@
 \end{proof}
+
+\subsection{Moment}
+
+ In this subsection, for any $\gamma \in (0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle $ by an exponential function depending on $\kappa$.
  %comment
-    {\bf Zhenyao: Again, I think the following remark is not accurate. Even if it is accurate, it should be proved with more details.}
-%comment
-\begin{rem}
-\label{remark1}
-   For $0<s\leq 1$, let
-   $$Z_f(x,s,\theta):=\int_0^s T^{\alpha}_{s-u}(-i\theta T_u^{\alpha}f)^{1+\beta}(x)du ,$$
-   which has the same estimation with \eqref{zineq1}.
-moreover, the decomposition in Corollary \ref{cor: corollary1} is also hold for $\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)$, this is to say,
-   $$\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}=1+\langle Z_{g_k}(\cdot,s,\theta),\mu\rangle+\langle err(\cdot,\theta),\mu\rangle$$
-   where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R_3(\cdot)$.
-\end{rem}
-
-\subsection{Moment}
-
- In this subsection, for any $\gamma \in [0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle $ by an exponential function depending on $\kappa(g)$.
- %comment
-    {\bf Zhenyao: I changed the statement and the proof of the following Lemma. I think the old version has too many mistakes.}
+   % {\bf Zhenyao: I changed the statement and the proof of the following Lemma. I think the old version has too many mistakes.}
 %end comment
@@
 \begin{lem}\label{lem: lemma23}
-For any $0\leq \gamma < \beta$ there exists a constant $C_2>0$ such that
+For any $0< \gamma < \beta$ there exists a constant $C_2>0$ such that
 $$\|M_k^t[g]\|_{1+\gamma}\leq C_2 e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k},$$
-for any $k \in \{0,...,t\}$.
+for any $k \in \{0,...,t \}$.
 \end{lem}
@@
 \begin{lem}\label{lem: lemma23}
-For each $0\leq \gamma < \beta$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_1>0$ such that, for each $t\in \mathbb N$ and $k \in \{0,\dots,t\}$, we have
+For each $0< \gamma < \beta$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_1>0$ such that, for each $t >0$ and $k \in \{0,\dots,\lfloor t \rfloor\}$, we have
 \begin{align}
@@
     \mathbb P_\mu\big[|M_k^t[g]|^{1+\gamma}\big]
-    \leq C_1 e^{\alpha t}e^{(\alpha \gamma - \kappa(g)b(1+\gamma))k}.
+    \leq C_1 C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))k}.
+\end{align}
+and
+\begin{align}
+    \mathbb P_\mu\big[|M_t^t[g]|^{1+\gamma}\big]
+    \leq C_1 C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))t}.
 \end{align}
@@
 \begin{proof}
-    Let $R$ be the control function in \eqref{eq:gcontrol}.
-    Then for each $\mu\in \mathcal M(\mathbb R^d)$ with compact support and $t\in \mathbb N$, we have
+    Let $R^g$ be the control function in \eqref{eq:gcontrol}.
+    Then for each $\mu\in \mathcal M(\mathbb R^d)$ with compact support and $t\geq 0$, we have
 \begin{align}
@@
     \leq \langle e^{\alpha t} |T_tg|, \mu\rangle^{1+\gamma}
-    \leq  \langle R,\mu\rangle^{1+\gamma} e^{\alpha t} e^{(\alpha\gamma- \kappa(g)b(1+\gamma))t}.
-\end{align}
-    This proves the Lemma in the case that $k = t$.
-    So we only have to consider the case when $k \in \{0,\dots,t-1\}$.
-    Let $c_k=e^{(\alpha-\kappa(g)b)k}$.
-    For each $\nu \in \mathcal M(\mathbb R^d)$ with compact support, denote by $\varphi_{k,\nu}$ the characteristic function of $\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle$.
-
-    Step 1. We will show that there exeists an $\tilde R_2 \in \mathcal P$ such that for each $\nu \in \mathcal M(\mathbb R^d)$ with compact support and $\lambda > c_k$ we have
-\begin{align} 
-    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda)
-    \leq \langle \tilde R_2,\nu\rangle \Big(\frac{c_k}{\lambda}\Big)^{1+\beta}.
-\end{align}
-    In fact, using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, letting $R_2 \in \mathcal P$ and $R_3 \in \mathcal P$ be the control functions in Corollary \ref{cor: corollary2} and Corollary \ref{cor: corollary1}, we have
-\begin{align} 
-    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda)
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1-\varphi_{k,\nu}(\theta))d\theta
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\langle Z_{g_k}(\cdot,\theta),\nu\rangle|+|err(k,\nu,\theta)|\big)d\theta
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\theta c_k|^{1+\beta}+|\theta c_k|^{1+2\beta}+ |\theta c_k|^{2+2\beta}\big)d\theta \times \langle R_2+R_3,\nu\rangle
-    \\& = \bigg(\frac{2^{2+\beta}}{2+\beta}\Big(\frac{c_k}{\lambda}\Big)^{1+\beta}+\frac{2^{2+2\beta}}{2+2\beta}\Big(\frac{c_k}{\lambda}\Big)^{1+2\beta} + \frac{2^{3+2\beta}}{3+2\beta}\Big(\frac{c_k}{\lambda}\Big)^{2+2\beta}\bigg) \langle R_2+R_3,\nu\rangle.
+    \leq  \langle R^g,\mu\rangle^{1+\gamma} C_h^{1+\gamma}e^{\alpha t} e^{(\alpha\gamma- \kappa(g)b(1+\gamma))t}.
+\end{align}
+    This proves the Lemma in the case that $M_t^t[g]$.
+    So we only have to consider the case when $k \in \{0,\dots,\lfloor t \rfloor\}$.
+    Let $c_k=e^{(\alpha-\kappa b)k}$.
+    For each $\nu \in \mathcal M(\mathbb R^d)$ with compact support and $0\leq s\leq 1$, denote by $\varphi_{k,\nu,s}$ the characteristic function of $\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle$.
+
+    Step 1. We will show that there exeists an $\tilde R^g_3 \in \mathcal P$ such that for each $\nu \in \mathcal M(\mathbb R^d)$ with compact support and $\lambda > C_g c_k$ we have
+\begin{align}
+    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle|>\lambda)
+    \leq \langle \tilde R^g_3,\nu\rangle \Big(\frac{C_g c_k}{\lambda}\Big)^{1+\beta}, \quad 0\leq s \leq 1.
+\end{align}
+    In fact, using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, letting $R^g_2 \in \mathcal P$ and $R^g_3 \in \mathcal P$ be the control functions in Corollary \ref{cor: corollary2} and Corollary \ref{cor: corollary1}, we have
+\begin{align}
+    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle|>\lambda)
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1-\varphi_{k,\nu,s}(\theta))d\theta
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\langle Z_{g_k}(s,\cdot,\theta),\nu\rangle|+|err(k,\nu,\theta)|\big)d\theta
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\theta C_g c_k|^{1+\beta}+|\theta C_g c_k|^{1+2\beta}+ |\theta C_g c_k|^{2+2\beta}\big)d\theta \times \langle R^g_2+R^g_3,\nu\rangle
+    \\& = \bigg(\frac{2^{2+\beta}}{2+\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{1+\beta}+\frac{2^{2+2\beta}}{2+2\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{1+2\beta} + \frac{2^{3+2\beta}}{3+2\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{2+2\beta}\bigg) \langle R^g_2+R^g_3,\nu\rangle.
 \end{align}
@@
     Step 2.
-Let $\tilde R_3\in \mathcal P$ be the control function in Step 1, we will show that for each $\nu\in \mathcal M(\mathbb R^d)$ with compact support, $k\in \mathbb N$ and $\gamma \in [0,\beta)$,
+Let $\tilde R^g_3\in \mathcal P$ be the control function in Step 1, we will show that for each $\nu\in \mathcal M(\mathbb R^d)$ with compact support, $k\in \mathbb N$, $\gamma \in (0,\beta)$ and $0\leq s \leq 1$,
 \[
-    \int_{c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda) d\lambda
-    \leq \frac{1}{\beta-\gamma} \langle \tilde R_3,\nu\rangle c_k^{1+\gamma}.
+    \int_{C_g c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_s\rangle - \langle T_{k+s}^\alpha g, \nu\rangle|> \lambda) d\lambda
+    \leq \frac{1}{\beta-\gamma} \langle \tilde R^g_3,\nu\rangle (C_g c_k)^{1+\gamma}.
 \]
@@
 \begin{align}
-    &\int_{c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda) d\lambda
-    \\&\leq \langle \tilde R_3,\nu \rangle c_k^{1+\beta}\int_{c_k}^\infty \lambda^{\gamma-1-\beta}d\lambda
-    = \frac{1}{\beta-\gamma}\langle \tilde R_3,\nu \rangle c_k^{1+\gamma}.
+    &\int_{C_g c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_s\rangle - \langle T_{k+s}^\alpha g, \nu\rangle|> \lambda) d\lambda
+    \\&\leq \langle \tilde R^g_3,\nu \rangle (C_g c_k)^{1+\beta}\int_{C_g c_k}^\infty \lambda^{\gamma-1-\beta}d\lambda
+    = \frac{1}{\beta-\gamma}\langle \tilde R^g_3,\nu \rangle (C_g c_k)^{1+\gamma}.
 \end{align}
@@
     Step 3.
-    Let $\tilde R_3\in \mathcal P$ be the control function in Step 1 and 2. According to \eqref{eq:semigroupineq}, there exists an $\tilde R_4\in \mathcal P$ such that
+    Let $\tilde R^g_3\in \mathcal P$ be the control function in Step 1 and 2. According to \eqref{eq:semigroupineq}, there exists an $\tilde R^g_4\in \mathcal P$ such that
 $
-    |T_t(\tilde R_3)(x)| 
-    \leq \tilde R_4(x),
+    |T_t(\tilde R^g_3)(x)|
+    \leq \tilde R^g_4(x),
 $
-    for each $t\geq 0$ and $x\in E$.
-    Therefore, for each $\mu \in \mathcal M(\mathbb R^d)$ with compact support, $t\in \mathbb N$ and $k \in \{1,\dots,t-1\}$, we have
+    for each $t\geq 0$ and $x\in \mathbb{R}^d$.
+    Therefore, for each $\mu \in \mathcal M(\mathbb R^d)$ with compact support, $t\geq 0$ and $k \in \{1,\dots,\lfloor t \rfloor-1\}$, we have
 \begin{align}
     &\mathbb P_\mu\big[|M_k^t[g]|^{1+\gamma}\big] = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|M_k^t[g]|>\lambda) d\lambda
-    \\&\leq c_k^{1+\gamma}+(1+\gamma)\int_{c_k}^\infty \lambda^{\gamma}\mathbb P_\mu(|M_k^t[g]|> \lambda) d\lambda
-    \\&\leq c_k^{1+\gamma}+(1+\gamma)\int_{c_k}^\infty \lambda^{\gamma}\mathbb P_\mu \big[\mathbb P_\mu\big(|M_k^t[g]|> \lambda\big| \mathscr F_{t-k-1}\big)\big] d\lambda
-    \\&\leq c_k^{1+\gamma}+(1+\gamma)\int_{c_k}^\infty \lambda^{\gamma}\mathbb P_\mu \big[\mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda)\big|_{\nu=X_{t-k-1}}\big] d\lambda
-    \\&\leq c_k^{1+\gamma}+\mathbb P_\mu\Big[(1+\gamma)\int_{c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda) d\lambda\Big|_{\nu=X_{t-k-1}}\Big]
-    \\&\leq c_k^{1+\gamma}+\mathbb P_\mu\Big[\frac{1+\gamma}{\beta- \gamma}\langle \tilde R_3,X_{t-k-1}\rangle c_k^{1+\gamma}\Big]
-    = c_k^{1+\gamma}+\frac{1+\gamma}{\beta- \gamma}c_k^{1+\gamma} \langle T_{t-k-1}^{\alpha}\tilde R_3,\mu\rangle
-    \\&\leq \Big(1+ \frac{1+\gamma}{\beta - \gamma} \langle \tilde R_4,\mu\rangle\Big) e^{\alpha(t-k-1)}c_k^{1+\gamma}
-    \\&= \Big(1+ \frac{1+\gamma}{\beta - \gamma} \langle \tilde R_4,\mu\rangle\Big)e^{-\alpha} e^{\alpha t}e^{(\alpha \gamma - \kappa(g)b(1+\gamma))k}.
+    \\&\leq (C_g c_k)^{1+\gamma}+(1+\gamma)\int_{C_g c_k}^\infty \lambda^{\gamma}\mathbb P_\mu(|M_k^t[g]|> \lambda) d\lambda
+    \\&\leq (C_g c_k)^{1+\gamma}+(1+\gamma)\int_{C_g c_k}^\infty \lambda^{\gamma}\mathbb P_\mu \big[\mathbb P_\mu\big(|M_k^t[g]|> \lambda\big| \mathscr F_{t-k-1}\big)\big] d\lambda
+    \\&\leq (C_g c_k)^{1+\gamma}+(1+\gamma)\int_{C_g c_k}^\infty \lambda^{\gamma}\mathbb P_\mu \big[\mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda)\big|_{\nu=X_{t-k-1}}\big] d\lambda
+    \\&\leq (C_g c_k)^{1+\gamma}+\mathbb P_\mu\Big[(1+\gamma)\int_{C_g c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda) d\lambda\Big|_{\nu=X_{t-k-1}}\Big]
+    \\&\leq (C_g c_k)^{1+\gamma}+\mathbb P_\mu\Big[\frac{1+\gamma}{\beta- \gamma}\langle \tilde R^g_3,X_{t-k-1}\rangle (C_g c_k)^{1+\gamma}\Big]
+    \\&= (C_g c_k)^{1+\gamma}+\frac{1+\gamma}{\beta- \gamma}(C_g c_k)^{1+\gamma} \langle T_{t-k-1}^{\alpha}\tilde R^g_3,\mu\rangle
+    \\&\leq \Big(1+ \frac{1+\gamma}{\beta - \gamma} \langle \tilde R^g_4,\mu\rangle\Big) e^{\alpha(t-k-1)}(C_g c_k)^{1+\gamma}
+    \\&\leq \Big(1+ \frac{1+\gamma}{\beta - \gamma} \langle \tilde R^g_4,\mu\rangle\Big) C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))k}.
+\end{align}
+On the case $k=\lfloor t \rfloor$, also we have
+\begin{align}
+     &\mathbb P_\mu\big[|M_{\lfloor t \rfloor}^t[g]|^{1+\gamma}\big]\leq (C_g c_{\lfloor t \rfloor})^{1+\gamma}+(1+\gamma)\int_{C_g c_{\lfloor t \rfloor}}^\infty \lambda^{\gamma}\mathbb P_\mu(|M_{\lfloor t \rfloor}^t[g]|> \lambda) d\lambda
+     \\ & = (C_g c_{\lfloor t \rfloor})^{1+\gamma}+(1+\gamma)\int_{C_g c_{\lfloor t \rfloor}}^\infty \lambda^{\gamma}\mathbb P_\mu(|\langle T^{\alpha}_{\lfloor t \rfloor}g,X_{t-\lfloor t\rfloor}\rangle-\langle T^{\alpha}_t g, \mu\rangle|> \lambda) d\lambda
+     \\ &\leq \Big(1+\frac{1+\gamma}{\beta-\gamma}\langle \tilde{R}^g_3, \mu\rangle\Big) (C_g c_{\lfloor t \rfloor})^{1+\gamma}\leq \Big(1+\frac{1+\gamma}{\beta-\gamma}\langle \tilde{R}^g_3, \mu\rangle\Big) C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))\lfloor t \rfloor}.
  \qedhere
@@
 \end{proof}
-%comment
-    {\bf Zhenyao: Even if the following remark is correct, I would like to see it been proved.}
-%end comment
-\begin{rem}\label{remark2}
-   When $t\notin \mathbb{N}$, on the interval $[\lfloor t \rfloor , t]$, similar with $M_k^t[g]$, we can define
-   $$M_{t,\lfloor t \rfloor}[g]:=\langle g,X_t\rangle-\langle T^{\alpha}_{t-\lfloor t \rfloor}g,X_{\lfloor t \rfloor}\rangle,$$
-   which satisfies
-   $$\|M_{t,\lfloor t \rfloor}[g]\|_{1+\gamma}\leq C_2 e^{\frac{\alpha}{1+\gamma}t},$$
-This can be proved by using Remark \ref{remark1} and following the same method in Lemma \ref{lem: lemma23}.
-\end{rem}
-
-Recall that,$\langle g,X_t\rangle$ is the sum of $M_k^{t}[g], k=0,1,...,t$. We obtain the following lemma.
+
+As $\langle g,X_t\rangle$ is the sum of $M_k^{t}[g], k=0,1,...,\lfloor t\rfloor$ and $M_t^t[g]$. We obtain the following lemma.
 
@@
 %For each $0\leq \gamma < \beta$ there exists a constant $C_5>0$, we have the result:
-For each $0\leq \gamma < \beta$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_5>0$, such that for each $t\in \mathbb N$:
-
-i) If $\alpha\gamma > \kappa(g)(1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C_5 e^{(\alpha-\kappa(g)b)t}.$$
-
-ii) If  $\alpha\gamma = \kappa(g)(1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C_5 te^{\frac{\alpha}{1+\gamma}t}.$$
-
-iii) If $\alpha\gamma < \kappa(g)(1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{1+\gamma}\leq C_5 e^{\frac{\alpha}{1+\gamma}t}.$$
+For each $0 < \gamma < \beta$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_2>0$, such that for each $t\geq 0$:
+
+i) If $\alpha\gamma > \kappa (1+\gamma)b$,
+$$\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C_2 C_g e^{(\alpha-\kappa b)t}.$$
+
+ii) If  $\alpha\gamma = \kappa (1+\gamma)b$,
+$$\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C_2 C_g te^{\frac{\alpha}{1+\gamma}t}.$$
+
+iii) If $\alpha\gamma < \kappa (1+\gamma)b$,
+$$\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C_2 C_g e^{\frac{\alpha}{1+\gamma}t}.$$
 
@@
     \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    \leq \sum_{k=0}^{t}\|M_k^t[g]\|_{\mathbb P_\mu;1+\gamma}
-    \leq C_1 e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^{t} e^{\frac{\gamma\alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}.
+    &\leq \sum_{k=0}^{\lfloor t\rfloor}\|M_k^t[g]\|_{\mathbb P_\mu;1+\gamma}+\|M_t^t[g]\|_{\mathbb P_\mu;1+\gamma}
+    \\ &\leq C_1 C_g e^{\frac{\alpha}{1+\gamma}t}\Big(\sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma}k}+e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma}t}\Big).
 \end{align}
@@
 \end{proof}
+According to \eqref{eq:semigroupineq}, each $f \in \mathcal{P}$ satisfies \eqref{eq:gcontrol1} with $C_f=1$, $\kappa=\kappa(f)$ and $R_0^f=R_0$. Thus 
+\begin{cor}\label{cor27}
+Let $0< \gamma < \beta$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, for each $f\in \mathcal{P}$, there exist constants $\tilde{C}_1,\tilde{C}_2>0$ such that, for each $t>0$ and $k \in \{0,\dots,\lfloor t \rfloor\}$, we have
+\begin{align}
+\label{eq: upper bound of 1+gamma moment of Mktf}
+    \|M_k^t[f]\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq \tilde{C}_1 e^{\frac{\alpha t}{1+\gamma}}e^{(\alpha \gamma - \kappa(f)b)k}.
+\end{align}
+and
+\begin{align}
+    \|M_t^t[f]\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq \tilde{C}_1 e^{\frac{\alpha t}{1+\gamma}}e^{(\alpha \gamma - \kappa(f)b)t}.
+\end{align}
+Moreover,
+\begin{itemize}
+    \item If $\alpha\gamma > \kappa(f)(1+\gamma)b$,\quad $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq \tilde{C}_2 e^{(\alpha-\kappa b)t}.$
+    \item If  $\alpha\gamma = \kappa(f)(1+\gamma)b$,\quad $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq \tilde{C}_2 te^{\frac{\alpha}{1+\gamma}t}.$
+    \item If $\alpha\gamma < \kappa(f)(1+\gamma)b$,\quad$\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq \tilde{C}_2 e^{\frac{\alpha}{1+\gamma}t}.$
+\end{itemize}
+\end{cor}
+\begin{comment}
 
@@
     The Lemma \eqref{lemma24} offers insights how to guess $\{F_t, t\geq0\}$ raised in Introduction. indeed
-
-    Large branching rate: when $\alpha\gamma > \kappa(g)(1+\gamma)b$, $F_t\approx e^{(\alpha-\kappa(g)b)t} $;
-
-    Critical branching rate: when when  $\alpha\gamma = \kappa(g)(1+\gamma)b$, $F_t\approx (te^{\alpha t})^{\frac{1}{1+\beta}}\approx(t\|X_t\|)^{\frac{1}{1+\beta}}$;
-
-    Small branching rate: when $\alpha\gamma < \kappa(g)(1+\gamma)b$, $F_t\approx e^{\frac{\alpha t}{1+\beta}}\approx \|X_t\|^{\frac{1}{1+\beta}}$.
+    \begin{itemize}
+        \item  Large branching rate: when $\alpha\gamma > \kappa(g)(1+\gamma)b$, $F_t\approx e^{(\alpha-\kappa(g)b)t} $;
+        \item  Critical branching rate: when $\alpha\gamma = \kappa(g)(1+\gamma)b$, $F_t\approx (te^{\alpha               t})^{\frac{1}{1+\beta}}\approx(t\|X_t\|)^{\frac{1}{1+\beta}}$;
+        \item  Small branching rate: when $\alpha\gamma < \kappa(g)(1+\gamma)b$, $F_t\approx e^{\frac{\alpha t}{1+\beta}}\approx \|X_t\|^{\frac{1}{1+\beta}}$.
+    \end{itemize}
 \end{rem}
+{\bf (Jianjie: We do not mention $F_t$ in Introduction, But we possibly need this mark in the future, so I decide to keep this part for now.)}
+\end{comment}
 \subsection{Martingales}
-
-In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales, for $0\leq\gamma<\beta$.
+In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales, for $0<\gamma<\beta$.
 Recall that $L$ is the infinitesimal generator of OU-process.
-Let $a\in \mathbb{R}$ and $f\in \mathcal{P}$ such that $Lf \in \mathcal{P}$ ,we define that
-$$M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle \bar{f}, X_s\rangle~ ds$$
+Let $a\in \mathbb{R}$ and $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$ ,we define that
+\begin{align}
+\label{defmartingale}
+  M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle \bar{f}, X_s\rangle~ ds
+\end{align}
 Where $\bar{f}=(L+ab)f$. The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathcal{F}_t\}_{t\geq 0}$.
 \begin{lem}\label{lemma25}
-%For any $a \in \mathbb{R}$ and $f\in\mathcal{P}$ such that $L f\in\mathcal{P}$, Then $\{M_t^{f,a},\mathcal{F}_t:t\geq 0\}$ is a martingale.
-For any $a \in \mathbb{R}$ and $f\in\mathcal{P}$ such that $L f\in\mathcal{P}$, $\{M_t^{f,a},\mathcal{F}_t:t\geq 0\}$ is a martingale.
+Let $a\in \mathbb{R}$ and $h\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$. Then the process $\left\{M_t^{f,a}, \mathcal{F}_t:t\geq 0\right\}$ is an martingale.
 \end{lem}
-
 \begin{proof}
-For any $0\leq s\leq t$,
+For any $a\in \mathbb{R},x\in \mathbb{R}^d$, take $\pi_tf(x)=T_t^{ab}f(x)$ into \cite[Theorem A.55]{Li2011Measure-valued}, we have
+\begin{align}\label{Theorem55}
+    T_t^{ab}f(x)= f(x)+\int_0^t T_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb{R}^d.
+\end{align}
+Let $0\leq s\leq t$,
 \begin{align}
@@
 \end{align}
-
-Observe that $\frac{d}{du}\left(e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha}f,X_s\rangle\right)=e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha}\bar{f},X_s\rangle$, we get
-$$\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_u\rangle~ du=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f,X_s\rangle-e^{-(\alpha-ab)s}\langle f,X_s\rangle.$$
-Take it to the \eqref{martingale1}, we obtain the desired result.
+By using \eqref{Theorem55}and Fubini's theorem , further we get
+\begin{align}
+    &\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle T_{u-s}^{ab}\bar{f},X_s\rangle~du\\
+    &=e^{-(\alpha-ab)s}\langle\int_0^{t-s}T_{u}^{ab}\bar{f}~du,X_s\rangle=e^{-(\alpha-ab)s}\left(\langle T_{t-s}^{ab}f,X_s\rangle-\langle
+    f,X_s\rangle\right)\\
+    &=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-e^{-(\alpha-ab)s}\langle
+    f,X_s\rangle
+\end{align}
+Take it to \eqref{martingale1}, we get the desired result.
 \end{proof}
+{\bf (Jianjie: Please check this above lemma. )}
 %comment
-{\bf Zhenyao: I think the above Lemma is not accurate.
+%{\bf Zhenyao: I think the above Lemma is not accurate.
 I think we need condition that $f\in C^2(\mathbb R^d) \cap \mathcal P$.
-Also in the proof we better use \cite[Theorem A.55]{Li2011Measure-valued} and Fubini's theorem.}
+Also in the proof we %better use \cite[Theorem A.55]{Li2011Measure-valued} and Fubini's theorem.}
 %end comment
@@
 \begin{lem}\label{lemma26}
-$\{H_t^p: t\geq0\}$ is a martingale with respect to $\mathcal{F}_t$. If $\alpha\beta>|p|b(1+\beta)$, then for any $0\leq \gamma<\beta$, we have $\sup_t\|H_t^p\|_{1+\gamma}< \infty$. Thus the limit
+$\{H_t^p: t\geq0\}$ is a martingale with respect to $\mathcal{F}_t$.
+If $\alpha\beta>|p|b(1+\beta)$, then for any $0< \gamma<\beta$ and $\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, we have $\sup_{t\geq 0}\|H_t^p\|_{1+\gamma}< \infty$.
+Thus the limit
 $$H_{\infty}^p:=\lim_{t\rightarrow \infty}H_t^p$$
@@
     There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that $\alpha\gamma_0>|p|(1+\gamma_0)b$.
-Using  Lemma \eqref{lemma24} and the fact $\kappa(\phi_p)=|p|$, we get that, for any $\gamma_0\leq\gamma<\beta$
-    $$\|H_t^p\|_{1+\gamma}\leq C_5e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C_5,$$
+Using  Lemma \ref{lemma24} and the fact $\kappa(\phi_p)=|p|$, we get that, for any $\gamma_0\leq\gamma<\beta$
+    $$\|H_t^p\|_{1+\gamma}\leq C_2e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C_2,$$
  For any $0\leq\gamma<\gamma_0$, by the concave of function $h(x)=x^{(1+\gamma)/(1+\gamma_0)}$,
@@
  %For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have
- For any $\gamma\in [0,\beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a $C_6> 0$ such that for each $0\leq s<t$,
- $$\|W_t-W_s\|_{1+\gamma}\leq C_6 e^{-\alpha s/2}.$$
+ For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a $C_3> 0$ such that for each $0\leq s<t$,
+ $$\|W_t-W_s\|_{1+\gamma}\leq C_3 e^{-\alpha s/2}.$$
 \end{lem}
@@
 %new added
-    Fix $\gamma \in [0,\beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support. 
+    Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support.
     According to Lemma \ref{lem: lemma23}, for each $n \in \mathbb N$, we have
@@
     For any $m\in \mathbb{N}$ and $m<n$,
-    $$\|W_n-W_m\|_{1+\gamma}\leq \sum_{k=m}^{n-1}\|W_{k+1}-W_k\|_{1+\gamma}\leq C_2\sum_{k=m}^{n-1}e^{-\frac{\alpha\gamma(k+1)}{1+\gamma}}\leq C_6 e^{-\frac{\alpha\gamma m}{1+\gamma}}\leq C_6 e^{-\frac{\alpha m}{2}}.$$
-    Where we can take $C_6=\frac{C_2}{1-e^{-\frac{\alpha \gamma}{1+\gamma}}}$
- When we take any $0\leq s\leq t$,there will appear two terms corresponding to the interval $[s,[s]+1]$ and $[[t],t]$, which are  handled by using Remark \ref{remark2} with the same method, then we complete our proof.
+    $$\|W_n-W_m\|_{1+\gamma}\leq \sum_{k=m}^{n-1}\|W_{k+1}-W_k\|_{1+\gamma}\leq C_1^{\frac{1}{1+\gamma}}\sum_{k=m}^{n-1}e^{-\frac{\alpha\gamma(k+1)}{1+\gamma}}\leq C_3 e^{-\frac{\alpha m}{2}}.$$
+ When we take any $0\leq s\leq t$, there will appear two terms corresponding to the interval $[s,[s]+1]$ and $[[t],t]$, which are  handled by using Lemma \ref{lem: lemma23} with the same method, then we complete our proof.
 \end{proof}
-Recall that $\|X_t\|$ is an continuous state branching process with initial mass $\|\mu\|$.
+As $\|X_t\|$ is an continuous state branching process with initial mass $\|\mu\|$.
 for any $\lambda>0$, $\|X_t\|$ satisfies, see \cite[Chapter 3]{Li2011Measure-valued}, for example.
@@
 \begin{align*}
-    \frac{\partial}{\partial t}v_t(\lambda)=-\psi(v_t(\lambda)), \quad  v_0(\lambda)=\lambda.
+    \frac{\partial}{\partial t}v_t(\lambda)=-\psi(v_t(\lambda)), \quad  v_0(\lambda)=\lambda,  \quad \lambda>0, t\geq 0.
 \end{align*}
@@
 \begin{align*}
-    v_t(\lambda)=\frac{e^{\alpha t} \lambda}{[1+\frac{1}{\alpha}(e^{\alpha \beta t}-1)\lambda^{\beta}]^{1/\beta}}=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0,
+    v_t(\lambda)=\frac{e^{\alpha t} \lambda}{[1+\frac{1}{\alpha}(e^{\alpha \beta t}-1)\lambda^{\beta}]^{1/\beta}}=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
 \end{align*}
@@
 \begin{lem}\label{lemma2_13}
-Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function such that $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$. Then there exist $C_7>0$ such that for any $t\geq 0$, there is
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_7 \exp(\beta(\ln f(t)-\alpha t))
+Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function such that $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$ Then for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exist $C_4>0$ such that there is
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_4 \exp(\beta(\ln f(t)-\alpha t)), \quad t\geq 0.
 \end{align}
@@
 \end{align*}
-We conclude the lemma by taking $C_7= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
+We conclude the lemma by taking $C_4= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
 \end{proof}
 \begin{lem}\label{lemma28}
-  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C_8>0$ and $\delta_1>0$ such that
-  $$\mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq C_8 e^{-\delta_1 t},\quad t\geq 0.$$
+  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C_5>0$ and $\delta_1>0$ such that
+  $$\mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq C_5 e^{-\delta_1 t},\quad t\geq 0.$$
 \end{lem}
@@
     For another side, using Lemma \ref{lemma2_13}, we have
-    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq C_7 e^{-\beta\epsilon t}, $$
+    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq C_4 e^{-\beta\epsilon t}, $$
 Therefore,
 \begin{align*}
-    \mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq \mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq(C_7+1)e^{-\beta \epsilon t }
+    \mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq \mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq(C_4+1)e^{-\beta \epsilon t }
 \end{align*}
@@
 %\subsection{Parameter $m_k[g]$}
+{\bf (Jianjie: Can I add the condition $t\in \mathbb{N}$ above this subsection and omit the case $t \notin \mathbb{N}$.)}
 \subsection{Parameters}
- In this subsection, we will introduce an important parameter $m_k[g]$ which is a parameter of $(1+\beta)$-stable distribution. Recall the definition of $Z_f(x)$
+ In this subsection, we will introduce an important parameter $m_k[f],~f\in\mathcal{P}$, which is a parameter of $(1+\beta)$-stable distribution. Let $Z_f(x)=Z_f(1,x)$, thus
  $$Z_f(x)=\int_0^1 T^{\alpha}_{1-s}(-iT_s^{\alpha}f)^{1+\beta}(x)~ds,$$
@@
  \begin{align}
-      m_k[g]:=e^{-\alpha(k+1)}\langle Z_{g_k},\psi\rangle.
+      m_k[f]:=e^{-\alpha(k+1)}\langle Z_{f_k},\varphi\rangle.
  \end{align}
 \begin{lem}\label{mgineq1}
-There exists constant $C_9>0$ such that for any $k\in \{0,1,...,t\}$, we have
-$$|m_k[g]|\leq C_9 e^{(\alpha\beta-\kappa(g)b(1+\beta))k}.$$
+Let $f\in\mathcal{P}$, there exists constant $C_6>0$ such that for any $k\in \{0,1,...,t\}$, we have
+$$|m_k[f]|\leq C_6 e^{(\alpha\beta-\kappa(f)b(1+\beta))k}.$$
 \end{lem}
 \begin{proof}
-    By \eqref{zineq2} and simply calculating, we obtain the result by  taking $C_9=e^{-\alpha}\langle R_2,\phi\rangle$.
+Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
+\begin{align}
+    |Z_{f_k}(x)|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_2^f(x), \quad x\in \mathbb{R}^d, k\in\mathbb{N}.
+\end{align}
+This implies the result by simply calculating.
 \end{proof}
 
-$m_k[g]$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Notice that,
-$$m_k[g]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}(-iT_{s+k}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx.$$
+$m_k[f],~f\in \mathcal{P}$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Notice that,
+$$m_k[f]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}(-iT_{s+k}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx.$$
 Using Fubini's Theorem and the fact $\varphi(x)$ is an invariant measure of $T$, we get
 \begin{align}
-    m_k[g]&=\int_{\mathbb{R}^d}\int_0^1 e^{-\alpha(k+s)}(-iT_{s+k}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx\nonumber\\
-    &=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx.\label{mkeq}
+    m_k[f]&=\int_{\mathbb{R}^d}\int_0^1 e^{-\alpha(k+s)}(-iT_{s+k}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx\nonumber\\
+    &=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx.\label{mkeq}
 \end{align}
@@
 Next, we describe the parameter of limiting distribution in the critical case. Let
-$$\phi(x)=\sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle\phi_p(x)$$
-i.e. $\phi$ is the projection of $g$ onto the $\kappa(g)$-eigenspace.
+$$\phi(x)=\sum_{|p|=\kappa(f)}\langle f, \phi_p\rangle\phi_p(x)$$
+i.e. $\phi$ is the projection of $f$ onto the $\kappa(f)$-eigenspace.
 \begin{lem}\label{lemma210}
-Let $g \in \mathcal{P}$, $\kappa(g)\geq 1$ and $\alpha\beta=\kappa(g)b(1+\beta)$, then the following limit exists:
-\begin{align}
-    \tilde{m}[g]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{t}m_k[g]=\langle(-i\phi)^{1+\beta},\varphi\rangle.
+Let $f \in \mathcal{P}$, $\kappa(f)\geq 1$ and $\alpha\beta=\kappa(f)b(1+\beta)$, then the following limit exists:
+\begin{align}
+    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{t}m_k[f]=\langle(-i\phi)^{1+\beta},\varphi\rangle.
 \end{align}
@@
 \begin{proof}
-    We want to show the gap between $m_k[g]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$,
-    $$|m_k[g]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}\left|(-i T^{\alpha}_s g)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
-    As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(g)bt}$,  $\kappa(g)=\kappa(\phi)$ and $\kappa(g-\phi)\geq \kappa(g)+1$.
+    We want to show the gap between $m_k[f]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$,
+    $$|m_k[f]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}\left|(-i T^{\alpha}_s f)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
+    As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(f)bt}$,  $\kappa(f)=\kappa(\phi)$ and $\kappa(f-\phi)\geq \kappa(f)+1$.
 The inequality \eqref{eq:semigroupineq} yields that for some $R_5\in\mathcal{P}$ we have
     \begin{align*}
-        &|T_s^{\alpha}g|\leq e^{(\alpha-\kappa(g)b)s}R_5(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(g)b)s}R_5(x), \\
-        &|T_s^{\alpha}(g-\phi)|\leq e^{(\alpha-(\kappa(g)+1)b)s}R_5(x), \quad s\geq0.
-    \end{align*}
-  Using the element inequality \eqref{element} and the condition $\alpha\beta=\kappa(g)b(1+\beta)$, we get
-    $$|m_k[g]-m_k[\phi]|\leq2C\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R_5^{1+\beta}(x)~ds~\varphi(x)~dx\leq \frac{2C}{b}\langle R_5^{1+\beta},\varphi\rangle e^{-bk},$$
-
-    Therefore, the limits of $(1/t)\sum_{k=0}^tm_k[g]$ is the same with that of $(1/t)\sum_{k=0}^tm_k[\phi]$. What's more
+        &|T_s^{\alpha}f|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \\
+        &|T_s^{\alpha}(f-\phi)|\leq e^{(\alpha-(\kappa(f)+1)b)s}R_5(x), \quad s\geq0.
+    \end{align*}
+  Using Lemma \ref{lem: Lip of power function} and the condition $\alpha\beta=\kappa(f)b(1+\beta)$, we get
+    $$|m_k[f]-m_k[\phi]|\leq2C_0\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R_5^{1+\beta}(x)~ds~\varphi(x)~dx\leq \frac{2C_0}{b}\langle R_5^{1+\beta},\varphi\rangle e^{-bk},$$
+
+    Therefore, the limits of $(1/t)\sum_{k=0}^tm_k[f]$ is the same with that of $(1/t)\sum_{k=0}^tm_k[\phi]$. What's more
     \begin{align*}
@@
     The second equality holds as $T_s\phi=e^{-\kappa(g)bs}\phi$. Hence
-    $$\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{t}m_k[g]=\langle(-i\phi)^{1+\beta},\varphi\rangle.$$
+    $$\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{t}m_k[f]=\langle(-i\phi)^{1+\beta},\varphi\rangle.$$
 \end{proof}
 
-For the small branching rate case: $\alpha\beta<\kappa(g)b(1+\beta)$.
+For the small branching rate case: $\alpha\beta<\kappa(f)b(1+\beta)$.
 \begin{lem}\label{lemma211}
-Assume $\alpha\beta<\kappa(g)b(1+\beta)$, if $\kappa(g)\geq 1$, the series $\sum_{k=0}^{\infty}m_k[g]$ is absolutely convergent, hence we can define
-\begin{align}
-    m[g]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)ds\varphi(x)dx \label{msmallcase}
+Let $f\in \mathcal{P}$, assume $\alpha\beta<\kappa(f)b(1+\beta)$, if $\kappa(f)\geq 1$, the series $\sum_{k=0}^{\infty}m_k[f]$ is absolutely convergent, hence we can define
+\begin{align}
+    m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)ds\varphi(x)dx \label{msmallcase}
 \end{align}
@@
 \begin{proof}
-    By Lemma \ref{mgineq1}, we have $|m_k[g]|\leq C_9 e^{(\alpha\beta-\kappa(g)b(1+\beta))k}$, which implies $\sum_{k=0}^{\infty}|m_k[g]|<\infty$ as $\alpha\beta<\kappa(g)b(1+\beta)$. Hence
-    $$m[g]:=\sum_{k=0}^{\infty}m_k[g]=\sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)ds\varphi(x)dx$$
-     Moreover, the right side series are also absolutely convergence, since $|e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)|\leq e^{(\alpha\beta-\kappa(g)b(1+\beta))s}R(x)$.
+    By Lemma \ref{mgineq1}, we have $|m_k[f]|\leq C_6 e^{(\alpha\beta-\kappa(g)b(1+\beta))k}$, which implies $\sum_{k=0}^{\infty}|m_k[f]|<\infty$ as $\alpha\beta<\kappa(f)b(1+\beta)$. Hence
+    $$m[f]:=\sum_{k=0}^{\infty}m_k[f]=\sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)ds\varphi(x)dx$$
+     Moreover, the right side series are also absolutely convergence, since $|e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)|\leq e^{(\alpha\beta-\kappa(f)b(1+\beta))s}R_0^{1+\beta}(x)$.
 
@@
 
-In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+In this section, we will prove the main results of this paper.
+Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.
  \begin{lem}\label{lemma31}
- Assume that $\alpha\beta\leq \kappa(g)b(1+\beta)$, let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}}$, then for any  $k\in\mathbb{N}$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
- \begin{align}
-      \frac{M_k^t[g]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
+ Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(R^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+ \begin{align}
+      \frac{M_k^t[f]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
  \end{align}
  where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
- $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[g]\right].$$
+ $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[f]\right].$$
  \end{lem}
 \begin{proof}
-    Recall that $w_{g_k}(x,\theta)=w_{g_k}(x,1,\theta),\tilde{w}_{g_k}(x,\theta)=\tilde{w}_{g_k}(x,1,\theta)$. For any $k\in\mathbb{N}$ and $t>k$, we have
-    \begin{align*}
-        \mathbb{\tilde{P}}_{\mu}&[\exp(i\theta\frac {M_k^t[g]}{F_k(X_{t-k-1})})]\\
-        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[g]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
-        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\nu}\left[\exp\left(i\frac{\theta}{F_k(v)}(\langle T_k^{\alpha}g,X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle)\right)\right]_{\nu=X_{t-k-1}}\right]\\
-        &=\mathbb{\tilde{P}}_{\mu}\left[\exp\left(\langle w_{g_k}(\cdot,\frac{\theta}{F_k(X_{t-k-1})}),X_{t-k-1}\rangle-i\frac{\theta}{F_k(X_{t-k-1})}\langle T_{k+1}^{\alpha}g, X_{t-k-1}\rangle\right)\right].
-    \end{align*}
-    Our aim now is showing that the on the event $\mathcal{A}_{t-k-1}$, the characteristic functions of random variables on both sides in \eqref{limitdistribution1} are much the same.
-Let $c=|\theta e^{\alpha}m_k[g]|$, $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$.
+Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and Let $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$, by Lemma \ref{lemma28}, there exists $\delta_1>0$ and $C_5>0$ such that
+    \begin{align}
+    \label{eq:31step0}
+        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right|
+        \\ &\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1}(\epsilon_0))
+        \leq 2C_5e^{-\delta_1(t-k-1)},\quad k\in \mathbb{N}, t>k.\label{lemma33q}
+    \end{align}
+
+    Let $v_{f_k}(x,\theta)=v_{f_k}(1,x,\theta),\tilde{v}_{f_k}(x,\theta)=\tilde{v}_{f_k}(1,x,\theta)$ for short. For any $k\in\mathbb{N}$ and $t>k$, we have
+    \begin{align*}
+        &\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})]\\
+        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
+        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\nu}\left[\exp\left(i\frac{\theta}{F_k(v)}(\langle T_k^{\alpha}f,X_1\rangle-\langle T_{k+1}^{\alpha}f,\nu\rangle)\right)\right]_{\nu=X_{t-k-1}}\right]\\
+        &=\mathbb{\tilde{P}}_{\mu}\left[\exp\left(\langle v_{f_k}(\cdot,\frac{\theta}{F_k(X_{t-k-1})}),X_{t-k-1}\rangle-i\frac{\theta}{F_k(X_{t-k-1})}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\right)\right].
+    \end{align*}
+
+    Next, our aim now is showing that the on the event $\mathcal{A}_{t-k-1}(\epsilon_0)$, the characteristic functions of random variables on both sides in \eqref{limitdistribution1} are much the same.
+Let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$.
 Then
     \begin{align*}
-        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}}\right|\\
-        &=\bigg|\big(\mathbb{\tilde{P}}_{\mu}\exp(\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\\
-        &-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}}\bigg|\\
-        &\leq e^c\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\\
-        &+e^c\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]=I+II.
-    \end{align*}
-    The first equation holds because that $w_{g_k}-i\theta T_1^{\alpha}g_k=w_{g_k}-\tilde{w}_{g_k}+Z_{g_k}$. the inequality holds by mean value theorem and triangular inequality.
-
-    Using the Lemma \ref{lemma2}, for any $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}$, we have
-    \begin{align*}
-        I&\leq e^c\left(\frac{|\theta|e^{(\alpha-\kappa(g)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\right)^{p_1}\mathbb{\tilde{P}}_{\mu}\langle R_1,X_{t-k-1}\rangle\\
-        &=\frac{e^c}{\|\mu\|^{p_1/(1+\beta)}}\langle T_{t-k-1} R_1,\mu\rangle|\theta|^{p_1}e^{\alpha(t-k-1)} e^{-\frac{p_1\alpha(t-k-1)}{1+\beta}}e^{\frac{p_1\epsilon(t-k-1)}{1+\beta}}\\
-        &\leq C_{10} |\theta|^{p_1} e^{\alpha(t-k-1)}e^{-\frac{p_1\alpha(t-k-1)}{1+\beta}}e^{\frac{p_1\epsilon(t-k-1)}{1+\beta}},\quad \theta\in \mathbb{R},
-    \end{align*}
-    for some constant $C_{10}$. Since $\alpha(\frac{p_1}{1+\beta}-1)>0$, we can chose $\epsilon>0$ such that there exists $C_{11},\delta_2>0$ satisfying
-    \begin{align}
-        I\leq C_{11}|\theta|^{p_1} e^{-\delta_2(t-k)}, \quad k\in \mathbb{N}, t>k, \theta \in \mathbb{R}.\label{lemma31q}
-    \end{align}
-
-    For part $II$, notice that $\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle=\theta^{1+\beta}e^{-\alpha k}\frac{\langle Z_{g_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|} \rangle$ and $\theta^{1+\beta}e^{\alpha}m_k[g]=\theta^{1+\beta}e^{-\alpha k}\langle Z_{g_k},\varphi\rangle$.
+        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right|\\
+        &=\bigg|\big(\mathbb{\tilde{P}}_{\mu}\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\\
+        &-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}}(\epsilon_0)\bigg|\\
+        &\leq \mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
+        &+\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right].
+    \end{align*}
+    The first equation holds because that $v_{f_k}-i\theta T_1^{\alpha}f_k=v_{f_k}-\tilde{v}_{f_k}+Z_{f_k}$. the inequality holds by triangular inequality.
+
+Step 1.  We will show that for each $\mu \in\mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_6>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k$,
+    \begin{align}
+    \label{lemma31q}  
+        \mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{g_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
+    \end{align}
+Combining with \eqref{eq:semigroupineq}, \eqref{eq:gcontrol1} and Lemma \ref{lemma2}, there exist $R_1^f,R_6>0$ such that
+\begin{align}
+    & |v_{f_k}(x,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(x,\tilde{\theta}_{t,k})|\leq |\tilde{\theta}_{t,k} e^{(\alpha-\kappa(f) b)k}|^{1+2\beta}R^f_1(x),\\
+    & |T_t (R^f_1)(x)|\leq R_6(x), \quad x\in \mathbb{R}^d,t\geq 0, \theta \in \mathbb{R}.
+\end{align}
+%Let $R_1$ be the control function in Lemma \ref{lemma2}.
+According to \eqref{eq:semigroupineq}, there exists $R_6\in \mathcal{P}$, satisfying $|T_t %(R_1)(x)|\leq R_6(x)$, for each $t>0$ and $x\in \mathbb{R}^d$.
+
+For any $\theta\in \mathbb{R}$, $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}$, we have
+    \begin{align*}
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
+        \\ &\leq \left(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\right)^{1+2\beta}\mathbb{\tilde{P}}_{\mu}\langle R^f_1,X_{t-k-1}\rangle\\
+        &\leq\frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle R_6,\mu\rangle|\theta|^{1+2\beta}e^{\alpha(t-k-1)} e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}\\
+        &\leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle R_6,\mu\rangle|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
+    \end{align*}
+ Step 2.
+Let $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.We will show that there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
+ \begin{align}
+ \label{eq:31step2}
+     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa(f)b)(1+\beta)k}R_7(x).
+ \end{align}
+ Let $\tilde{f}=T_1^{\alpha}f$, then $\kappa(\tilde{f})=\kappa(f)$.
+It is easy to show that $\tilde{f}\in C^{\infty}$ and $\tilde{f}^{(p)}\in\mathcal{P},~p\in\mathbb{Z}_+^d$, thus by the inequality \eqref{eq:semigroupineq} and the fact $\kappa\left(\frac{\partial \tilde{f}}{\partial x_i}\right)\geq \kappa(\tilde{f})-1$, see \cite[Lemma 2.3]{RSZ}, we get there exists $\tilde{R}_7\in \mathcal{P}$ such that for each $i=1,...,d$
+ \begin{align}
+ \label{ineq-temp}
+     \left|T_t\big(\frac{\partial\tilde{f}}{\partial x_i}\big)(x)\right|\leq e^{(\alpha-(\kappa(f)-1)b)t}\tilde{R}_7(x), \quad x\in \mathbb {R}^d, t\geq 0.
+ \end{align}
+ As $\langle h_k,\varphi\rangle=0$,
+ \begin{align}
+     &T_s h_k(x)= T_s [h_k(\cdot+xe^{-bs})] (0)-\langle h_k,\varphi\rangle
+     \\ &= \int_{\mathbb{R}^d}\big(h_k(xe^{-bs}+y\sqrt{1-e^{-2bs}})-h_k(y)\big)\varphi (y)~dy
+     \\ &\leq \int_{\mathbb{R}^d}|\nabla h_k(z)||xe^{-bs}+y\sqrt{1-e^{-2bs}}-y|\varphi (y)~dy.
+  \end{align}
+ Where $z$ is a point on the line segment connecting $y$ and $xe^{-bs}+y\sqrt{1-e^{-2bs}}$. For each $i=1,...,d$
+ \begin{align}
+     \frac{\partial h_k}{\partial x_i}(x)=\frac{\partial Z_{g_k}}{\partial x_i}(x)=\int_0^1 T^{\alpha}_{1-s}\left(\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha} \tilde{f})^{1+\beta}\right)(x)~ds.
+ \end{align}
+  Let $R_0$ be the control function in \eqref{eq:semigroupineq},
+      \begin{align}
+        \left|\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha}\tilde{f})^{\beta}\right|&=\left|(1+\beta)(-i T_{s+k-1}^{\alpha}\tilde{f})^{\beta}(-i e^{-b(s+k-1)}T_{s+k-1}^{\alpha}\left(\frac{\partial \tilde{f}}{\partial x_i}\right))\right|\\
+        &\leq e^{(\alpha-\kappa(\tilde{f})b)(s+k-1)(1+\beta)}\cdot (1+\beta)e^{(\alpha-\kappa(f)b)\beta}R_0^{\beta}(x)\tilde{R}_7(x).
+    \end{align}
+Thus there exists $R_8\in \mathcal{P}$,
+\begin{align}
+\label{eq:31temp }
+    \left|\frac{\partial}{\partial x_i}h_k(x)\right|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_8(x),\quad x\in \mathbb{R}^d, k\in \mathbb{N}.
+\end{align}
+By \eqref{eq:31temp } and the fact $|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y|\leq e^{-bs}(|x|+|y|)$,
+\begin{align}
+    |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa(f)b)(1+\beta)k}R_8(x)(|x|+\int_{\mathbb{R}^d}|y|\varphi(y)~dy).
+\end{align}
+
+Step 3, for any $\mu \in \mathcal{M}(\mathbb{R}^d)$ and $\theta\in \mathbb{R}$, we will show that there exists $C_7>0$ such that
+\begin{align}
+\label{eq:31step3}
+    \mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_7|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)},\quad k\in \mathbb{N}, t\geq k.
+\end{align}
+    Notice that $\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]=\theta^{1+\beta}e^{-\alpha k}(\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|} \rangle-\langle Z_{f_k},\varphi\rangle)$.
 Therefore,
-\begin{align}
-    II&=e^c|\theta|^{1+\beta}e^{-\alpha k}\mathbb{\tilde{P}}_{\mu}\left[\left|\frac{\langle Z_{g_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{g_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\nonumber\\
-    &\leq e^c|\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}\mathbb{\tilde{P}}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
-\end{align}
+    %and $\theta^{1+\beta}e^{\alpha}m_k[f]=\theta^{1+\beta}e^{-\alpha k}\langle Z_{f_k},\varphi\rangle$. 
+\begin{align}
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
+    &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{\tilde{P}}_{\mu}\left[\left|\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{f_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\nonumber\\
+    &\leq |\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon_0)(t-k-1)}\mathbb{\tilde{P}}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
+\end{align}
+As $h_k$ satisfies \eqref{eq:gcontrol1} with $C_{h_k}=e^{(\alpha-\kappa(f))(1+\beta)k}$, $\kappa=1$ and $R_0^{h_k}(x)=R_7(x)$, fix some $\gamma_0\in(0,\beta)$, according to Lemma \ref{lemma24}, there exist $C_8>0$,
+\begin{align}
+    &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right]\leq \|\langle h_k, X_{t-k-1}\rangle\|_{\mathbb{P}_{\mu,1+\gamma_0}}\\
+    &\leq C_8 e^{(\alpha-\kappa(f)b)(1+\beta)k}
+    \begin{cases}
+    e^{(\alpha-b)(t-k-1)}\quad &\alpha\gamma_0>(1+\gamma_0)b\\
+    e^{(\alpha-\frac{\gamma_0}{2(1+\gamma_0)}\alpha)(t-k-1)}\quad &\alpha\gamma_0=(1+\gamma_0)b\\
+    e^{(\alpha-\frac{\gamma_0}{(1+\gamma_0)}\alpha)(t-k-1)}\quad &\alpha\gamma_0<(1+\gamma_0)b\\
+    \end{cases}
+    \\& \leq C_8 e^{(\alpha-\kappa(f)b)(1+\beta)k}e^{(\alpha-p)(t-k-1)}, \quad k\in \mathbb{N}, t\geq k,
+\end{align}
+We want to emphasize that, on the case $\alpha\gamma_0=(1+\gamma_0)b$, the second equation holds when $t$ is large enough. Thus
+\begin{align}
+    &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
+    \\ & \leq C_8 |\theta|^{1+\beta}e^{(\alpha\beta-\kappa(f)b(1+\beta))k}e^{-(p-\epsilon_0)(t-k-1)} \leq C_8 |\theta|^{1+\beta}e^{-\frac{p}{2}(t-k-1)}.
+\end{align}
+
+At last, combine \eqref{eq:31step0},\eqref{lemma31q} and \eqref{eq:31step3} and let $t\rightarrow\infty$, we get the result.
+\end{proof}
+\begin{comment}
     where $h_k=Z_{g_k}-\langle Z_{g_k}, \varphi\rangle$.
@@
 Combine with \eqref{lemma31q},\eqref{lemma32q} and \eqref{lemma33q}, by letting $t \rightarrow \infty$, We obtain the desired result.
-\end{proof}
+
+\end{comment}
+\begin{comment}
 
 Now we will prove the claim mentioned in Lemma \ref{lemma31}.
-
 \begin{proof}[Proof of claim:] Let $\sigma_t^2=\sigma^2(1-e^{-2bt})$, then we get
@@
 \end{proof}
+
 \begin{rem}
@@
 
+\end{comment}
 \begin{cor}\label{corollary31}
-Let $\Theta>0$, assume that $\alpha\beta\leq\kappa(g)b(1+\beta)$.
-There exists $C_{15},\delta_4>0$ such that for any $n \in \{0,...,t\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
-\begin{align*}
-    \left|\mathbb{\tilde{P}}_{\mu}\left(\prod_{k=0}^n\exp(i\theta_k \frac {M_k^t[g]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}})-\prod_{k=0}^n\exp(\theta_k^{1+\beta}e^{\alpha}m_k[g])\right)\right|\leq C_{15}e^{-\delta_4(t-n)}
-\end{align*}
+Let$f\in \mathcal{P}$ and $\Theta>0$, assume that $\alpha\beta\leq\kappa(f)b(1+\beta)$.
+There exists $C_9,\delta_2>0$ such that for any $n \in \{0,...,t\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
+\begin{align}
+\label{32corollary}
+    \left|\mathbb{\tilde{P}}_{\mu}\left(\prod_{k=0}^n\exp(i\theta_k \frac {M_k^t[f]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}})-\prod_{k=0}^n\exp(\theta_k^{1+\beta}e^{\alpha}m_k[f])\right)\right|\leq C_9 e^{-\delta_2(t-n)}
+\end{align}
 \end{cor}
 \begin{proof}
-    Denote $\gamma_{t,k}=\frac {M_k^t[g]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}} $, we define
-    $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[g]\right)\mathbb{\tilde{P}}_{\mu}\left(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\right)$$
+    Denote $\gamma_{t,k}=\frac {M_k^t[f]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}} $, we define
+    $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[f]\right)\mathbb{\tilde{P}}_{\mu}\left(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\right)$$
     for $k\in\{-1,...,n\}$, if $k=-1$, the product is one. Then Conditioning with $\mathcal{F}_{t-k-1}$ we get
     \begin{align*}
-        \varphi^{k-1}_t(\theta_0,...,\theta_n)-&\varphi^{k}_t(\theta_0,...,\theta_n)=\prod_{l=0}^{k-1}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[g]\right)\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left(\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[g]}\right)\prod_{l=k+1}^n\exp(i\theta_l \gamma_{t,l})\right]
+        \varphi^{k-1}_t(\theta_0,...,\theta_n)-&\varphi^{k}_t(\theta_0,...,\theta_n)=\prod_{l=0}^{k-1}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[f]\right)\\
+        &\mathbb{\tilde{P}}_{\mu}\left[\left(\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[f]}\right)\prod_{l=k+1}^n\exp(i\theta_l \gamma_{t,l})\right]
     \end{align*}
@@
     \begin{align*}
-        \left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| \leq \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[g]}\right|.
-    \end{align*}
-    If we have proved that there exists $C_{16},\delta_5>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,t\}$,
-    \begin{align}
-        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\leq C_{16} e^{-\delta_5(t-k)},
-    \end{align}
-    we completed our proof, as the left side of thesis of the lemma is equal to $\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|$.
+        \left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| \leq \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[f]}\right|.
+    \end{align*}
+    Step 1, we will prove that there exists $C_{10},\delta_3>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,t\}$,
+    \begin{align}
+    \label{eq:32step1}
+        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\leq C_{10} e^{-\delta_3(t-k-1)}.
+    \end{align}
+    %we completed our proof, as the left side of thesis of the lemma is equal to %$\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|$.
 
     Recall that
-    $$\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)=\exp(\langle w_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{w}_{g_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{g_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle).$$
-    In Lemma \ref{lemma31}, we have proved that (see \eqref{lemma31q} and \eqref{lemma32q}), if $|\theta|\leq\Theta$ and $k\in\{0,...,t\}$,
-    \begin{align*}
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_{11}|\theta|^{p_1} e^{-\delta_2 (t-k)}\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\right]\leq C_{13}|\theta|^{1+\beta} e^{-\delta_3(t-k)}
+    $$\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)=\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle).$$
+    In Lemma \ref{lemma31}, we have proved that (see \eqref{lemma31q} and \eqref{eq:31step3}), if $|\theta|\leq\Theta$ and $k\in\{0,...,t\}$,
+    \begin{align*}
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_{6}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}\\
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_7|\Theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)}.
     \end{align*}
@@
 \begin{align*}
-    \mathcal{B}_{t-k-1}:=\left\{\left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\leq C_{11}|\theta|^{p_1} e^{-\frac{\delta_2}{2}(t-k)}\right\}.
-\end{align*}
-Applying Markov's inequality, we get $\mathbb{\tilde{P}}_{\mu}(\mathcal{B}_{t-k-1})\geq 1- e^{-\frac{\delta_2}{2}(t-k)}$. Similarly, define
-\begin{align*}
-    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}}\leq C_{13}|\theta|^{1+\beta} e^{-\frac{\delta_3}{2}(t-k)}\right\},
-\end{align*}
- which satisfies  $\mathbb{\tilde{P}}_{\mu}(\mathcal{C}_{t-k-1})\geq 1- e^{-\frac{\delta_3}{2}(t-k)}$.
-
-Hence, for any $k\in\{0,...,t\}$, on the event $\mathcal{A}_{t-k-1}\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1}$, we get
-\begin{align*}
-   &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\\
-   &\leq \left|\langle w_{g_k}(\cdot,\tilde{\theta}_k)-\tilde{w}_{g_k}(\cdot,\tilde{\theta}_k), X_{t-k-1}\rangle\right|
-   +\left|\langle Z_{g_k}(\cdot,\tilde{\theta}_k),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[g]\right|\\
-   &\leq (C_{11}|\Theta|^{p_1}+C_{13}|\Theta|^{1+\beta}) e^{-\frac{\min\{\delta_2,\delta_3\}}{2}(t-k)},
-\end{align*}
-on the event $(\mathcal{A}_{t-k-1}\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1})^c$, we get
-\begin{align*}
-    &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\\
-    &\leq 2(\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1}))\\
-    &\leq 6e^{-\min\{\delta_1,\frac{\delta_2}{2},\frac{\delta_3}{2}\}(t-k)},
-\end{align*}
+    \mathcal{B}_{t-k-1}:=\left\{\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq C_6|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{4(1+\beta)}(t-k-1)}\right\}.
+\end{align*}
+Applying Markov's inequality, we get $\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})\leq e^{-\frac{\alpha\beta}{4(1+\beta)}(t-k-1)}$. Similarly, define
+\begin{align*}
+    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq C_7|\Theta|^{1+\beta} e^{-\frac{p}{4}(t-k-1)}\right\},
+\end{align*}
+ which satisfies  $\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1})\leq e^{-\frac{p}{4}(t-k-1)}$.
+
+Hence, for any $k\in\{0,...,t\}$, on the event $\mathcal{A}_{t-k-1}(\epsilon_0)\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1}$, we get
+\begin{align*}
+   &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[f]}\right|\\
+   &\leq \left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|
+   +\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\\
+   &\leq (C_6|\Theta|^{1+2\beta}+C_7|\Theta|^{1+\beta}) e^{-\min\{\frac{\alpha\beta}{4(1+\beta)},\frac{p}{4}\}(t-k-1)}.
+\end{align*}
+On the event $(\mathcal{A}_{t-k-1}(\epsilon_0)\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1})^c$, we get
+\begin{align*}
+    &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[f]}\right|\\
+    &\leq 2(\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1}(\epsilon_0))+\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1}))\\
+    &\leq 6e^{-\min\{\delta_1,\frac{\alpha\beta}{2(1+\beta)},\frac{p}{4}\}(t-k-1)}.
+\end{align*}
+
+Step 2, notice that the left side of \eqref{32corollary} is equal to $\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|$, moreover,
+\begin{align}
+    &\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|
+    \\&\leq\sum_{k=0}^n\left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right|
+    \\&\leq \sum_{k=0}^n C_{10} e^{-\delta_3(t-k-1)}.
+\end{align}
+Thus, we complete our proof.
 \end{proof}
 
-In next three subsection, we just use $C$ and $\delta$ as a constant positive real number, which may be different in different formula.
+In next three subsections, we just use $C$ and $\delta$ as a constant positive real number, which may be different in different formula.
 \subsection{Proof of Theorem \ref{Theorem12}}
 
-    Recall that $\langle g,X_t\rangle=\sum_{k=0}^t M_k^t[g]$, we write
-    \begin{align*}
-        (t\|X_t\|)^{-\frac{1}{1+\beta}}\langle g,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} (t\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[g]+\sum_{\lceil t-\ln t \rceil}^t (t\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[g]\\
+    For any $f\in\mathcal{P}$, we write
+    \begin{align*}
+        (t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} (t\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[f]+\sum_{k=\lceil t-\ln t \rceil}^t (t\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[f]\\
         &=I_t+J_t.
@@
     Denote
-    $$\tilde{I}_t=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{M_k^t[g]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
+    $$\tilde{I}_t=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{M_k^t[f]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
     Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get
     \begin{align*}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}-\exp\left(\theta^{1+\beta}\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[g]\right)\right|\leq C \frac{1}{t^{\delta}},
+        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}-\exp\left(\theta^{1+\beta}\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[f]\right)\right|\leq C \frac{1}{t^{\delta}},
     \end{align*}
@@
     \begin{align*}
-        Y_{t,k}=\exp\left(i\theta\frac{M_k^t[g]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{M_k^t[g]}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
+        Y_{t,k}=\exp\left(i\theta\frac{M_k^t[f]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{M_k^t[f]}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
     \end{align*}
@@
     \begin{align*}
-        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\left|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}\\
-        &\leq|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}.
-    \end{align*}
-    When $t$ is large enough, $t^{-\frac{1}{1+\beta}}\leq 1$. What's more, by Lemma \ref{lem: lemma23}
-    $$\mathbb{\tilde{P}}_{\mu}|M_k^t[g]|\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k},$$
-for some constant $C \geq 0$ and any $0\leq\gamma<\beta$.
+        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}|M_k^t[f]|\left|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}\\
+        &\leq|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}|M_k^t[f]|\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}.
+    \end{align*}
+    When $t$ is large enough, $t^{-\frac{1}{1+\beta}}\leq 1$. What's more, by Corollary \ref{cor27}
+    $$\mathbb{\tilde{P}}_{\mu}|M_k^t[f]|\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k},$$
+for some constant $C \geq 0$ and any $0<\gamma<\beta$.
 We denote
@@
  \end{align*}
- what's more,
+ what's more, when $t$ is sufficiently large,
  \begin{align*}
@@
 \end{align*}
-This is to say on the event $\mathcal{D}_{t,k}$, we get $K_{t,k}\leq C e^{-\frac{3\alpha}{32}(t-k-1)}$. Moreover, recall that $\alpha\beta=\kappa(g)(1+\beta)b$, we get
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}&\leq C e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
+This is to say on the event $\mathcal{D}_{t,k}$, we get $K_{t,k}\leq C e^{-\frac{3\alpha}{32}(t-k-1)}$. Moreover, recall that $\alpha\beta=\kappa(f)(1+\beta)b$, we get
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}&\leq C e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
     &\leq C e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}.\nonumber
@@
 
-Let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|t^{-1/2}e^{\alpha t}\}$. Using Lemma \eqref{lemma2_13}, we get
+Let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|t^{-1/2}e^{\alpha t}\}$. Using Lemma \ref{lemma2_13}, we get
 \begin{align}
@@
 \begin{align*}
-    \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|&\leq|\theta| \mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t \left(t\|X_t\|\right)^{-\frac{1}{1+\beta}}M_k^t[g]\right|\\
-    &\leq t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t M_k^t[g]\right|.
-\end{align*}
-By the triangle inequality and Lemma \ref{lem: lemma23}, for any $\gamma\in[0,\beta)$, we know that
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t M_k^t[g]\right|&\leq \sum_{k=\lceil t-\ln t \rceil}^t \|M_k^t[g]\|_{1+\gamma}\leq\sum_{k=\lceil t-\ln t \rceil}^t C_{\gamma}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}\\
+    \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|&\leq|\theta| \mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t \left(t\|X_t\|\right)^{-\frac{1}{1+\beta}}M_k^t[f]\right|\\
+    &\leq t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t M_k^t[f]\right|.
+\end{align*}
+By the triangle inequality and Corollary \ref{cor27}, for any $\gamma\in(0,\beta)$, we know that
+\begin{align*}
+    \mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t M_k^t[f]\right|&\leq \sum_{k=\lceil t-\ln t \rceil}^t \|M_k^t[f]\|_{1+\gamma}\leq\sum_{k=\lceil t-\ln t \rceil}^t C_{\gamma}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k}\\
     &=\sum_{k=\lceil t-\ln t \rceil}^t C_{\gamma}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}\leq C_{\gamma}e^{\frac{\alpha}{1+\beta}}t^{-\alpha(\frac{1}{1+\beta}-\frac{1}{1+\gamma})}.
@@
 \subsection{Proof of Theorem \ref{Theorem11}}
-For any $g\in \mathcal{P}$, $g=\sum_{|p|\geq \kappa(g)}\langle g,\phi_p\rangle_\varphi \phi_p$. Therefore, we have the decomposition.
-\begin{align*}
-    &e^{-(\alpha-\kappa(g)b)t}\langle g,X_t\rangle=I_t+J_t\\
-    &=e^{-(\alpha-\kappa(g)b)t}\sum_{|p|= \kappa(g)}\langle g,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle+e^{-(\alpha-\kappa(g)b)t}\sum_{|p|> \kappa(g)}\langle g,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle
+For any $f\in \mathcal{P}$, $f=\sum_{|p|\geq \kappa(f)}\langle f,\phi_p\rangle_\varphi \phi_p$. Therefore, we have the decomposition.
+\begin{align*}
+    &e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle=I_t+J_t\\
+    &=e^{-(\alpha-\kappa(f)b)t}\sum_{|p|= \kappa(f)}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle+e^{-(\alpha-\kappa(f)b)t}\sum_{|p|> \kappa(f)}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle
 \end{align*}
@@
 \begin{align*}
-    I_t \rightarrow \sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle_{\varphi} H_{\infty}^p  \quad as~ t\rightarrow \infty
-\end{align*}
-$\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for any $0\leq \gamma<\beta$. Thus, we just prove that $J_t$ tend to zero by this two ways.
+    I_t \rightarrow \sum_{|p|=\kappa(f)}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p  \quad as~ t\rightarrow \infty
+\end{align*}
+$\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for any $0< \gamma<\beta$. Thus, we just prove that $J_t$ tend to zero by this two ways.
 
@@
 \begin{align*}
-    \tilde{g}=\sum_{|p|> \kappa(g)}\langle g,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle
-\end{align*}
-By the definition of $\kappa(g)$, we know that $\kappa(\tilde{g})\geq \kappa(g)+1$. What's more, $J_t=e^{-(\alpha-\kappa(g)b)t}\langle \tilde{g},X_t\rangle$.
-Using Lemma\ref{lemma24}, for some constant $C$, we get
-
-1) when $\alpha\gamma>\kappa(\tilde{g})(1+\gamma)b$
-\begin{align*}
-    \|J_t\|_{1+\gamma}\leq C e^{-(\alpha-\kappa(g)b)t}e^{(\alpha-\kappa(\tilde{g})b)t}\leq C  e^{-(\alpha-\kappa(g)b)t}e^{(\alpha-(\kappa(g)+1)b)t}=C e^{-bt}
-\end{align*}
-
-2) when $\alpha\gamma=\kappa(\tilde{g})(1+\gamma)b\geq (\kappa(g)+1)(1+\gamma)b$
-\begin{align*}
-     \|J_t\|_{1+\gamma}\leq C t e^{-(\alpha-\kappa(g)b)t}e^{\frac{\alpha}{1+\gamma}t}\leq C t e^{-bt}
+    \tilde{f}=\sum_{|p|> \kappa(f)}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle
+\end{align*}
+By the definition of $\kappa(f)$, we know that $\kappa(\tilde{f})\geq \kappa(f)+1$. What's more, $J_t=e^{-(\alpha-\kappa(f)b)t}\langle \tilde{f},X_t\rangle$.
+Using Corollary \ref{cor27}, for some constant $C$, we get
+
+1) when $\alpha\gamma>\kappa(\tilde{f})(1+\gamma)b$
+\begin{align*}
+    \|J_t\|_{1+\gamma}\leq C e^{-(\alpha-\kappa(f)b)t}e^{(\alpha-\kappa(\tilde{f})b)t}\leq C  e^{-(\alpha-\kappa(f)b)t}e^{(\alpha-(\kappa(f)+1)b)t}=C e^{-bt}
+\end{align*}
+
+2) when $\alpha\gamma=\kappa(\tilde{f})(1+\gamma)b\geq (\kappa(f)+1)(1+\gamma)b$
+\begin{align*}
+     \|J_t\|_{1+\gamma}\leq C t e^{-(\alpha-\kappa(f)b)t}e^{\frac{\alpha}{1+\gamma}t}\leq C t e^{-bt}
 \end{align*}
@@
 
-{\em Almost sure convergence}: We recall the martingale defined in Lemma \ref{lemma25}. Let
+{\em Almost sure convergence}: For each $a\in \mathbb{R}$, let $\{M_t^{f,a},t\geq0\}$ be the martingale in \eqref{defmartingale} and let
 $$L_t^{f,a}:=\int_0^t e^{-(\alpha-ab)s}\langle \bar{f},X_s\rangle ds.$$
-We take $a=\kappa(g)+\frac{1}{2}$ and $f=\tilde{g}$ into this martingale and get
-\begin{align*}
-    J_t=e^{-\frac{1}{2}}M_t^{\tilde{g},a}+e^{-\frac{1}{2}}L_t^{\tilde{g},a}.
+Thus, $M_t^{\tilde{f},a}=e^{-(\alpha-ab)t}\langle \tilde{f}, X_t\rangle-L_t^{\tilde{f},a}$. When take $\alpha=\kappa(f)+\frac{1}{2}$, we get
+
+%We take $a=\kappa(g)+\frac{1}{2}$ and $f=\tilde{g}$ into this martingale and get
+\begin{align*}
+    J_t=e^{-\frac{1}{2}}M_t^{\tilde{f},a}+e^{-\frac{1}{2}}L_t^{\tilde{f},a}.
 \end{align*}
@@
 \begin{align*}
-    e^{-\frac{1}{2}bt}M_t^{\tilde{g},a}\rightarrow 0, \quad e^{-\frac{1}{2}bt}L_t^{\tilde{g},a}\rightarrow 0 \quad as~t\rightarrow \infty
+    e^{-\frac{1}{2}bt}M_t^{\tilde{f},a}\rightarrow 0, \quad e^{-\frac{1}{2}bt}L_t^{\tilde{f},a}\rightarrow 0 \quad as~t\rightarrow \infty
 \end{align*}
 $\mathbb{P}_{\mu}$-as.
-We notice that $\kappa(L\tilde{g})=\kappa(\tilde{g})$, this is to say $\kappa(L\tilde{g}+ab\tilde{g})=\kappa(\tilde{g})\geq \kappa(g)+1$.
-Following the similar way to prove the case $L^{1+\gamma}(\mathbb{P}_{\mu})$-convergence, we get there exists some $C, \delta>0$ such that
-\begin{align*}
-    \|e^{-(\alpha-ab)t}\langle \tilde{g},X_t\rangle)\|_{1+\gamma}\leq C e^{-\delta t},\quad \|e^{-(\alpha-ab)t}\langle L\tilde{g}+ab\tilde{g},X_t\rangle\|_{1+\gamma}\leq C e^{-\delta t}.
-\end{align*}
-Therefore, $|L_t^{\tilde{g},a}|\leq Y_t^{\tilde{g},a}:=\int_0^t e^{-(\alpha-ab)s}|\langle L\tilde{g}+ab\tilde{g},X_s\rangle|ds$ satisfying
-\begin{align*}
-    \|L_t^{\tilde{g},a}\|_{1+\gamma}\leq\|Y_t^{\tilde{g},a}\|_{1+\gamma}\leq \int_0^t \|e^{-(\alpha-ab)s}\langle L\tilde{g}+ab\tilde{g},X_s\rangle\|_{1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
-\end{align*}
-As $Y_t^{\tilde{g},a}$ is positive increasing, we get that it convergence some random variable $Y_{\infty}^{\tilde{g},a}$ almost sure and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. This is to say
-\begin{align*}
-    \lim_{t\rightarrow \infty}e^{-\frac{1}{2}bt}|L_t^{\tilde{g},a}|\leq  \lim_{t\rightarrow \infty}e^{-\frac{1}{2}bt}|Y_t^{\tilde{g},a}|=0.
-\end{align*}
-On the other hand, the martingale $M_t^{\tilde{g},a}$ satisfies
-\begin{align*}
-    \|M_t^{\tilde{g},a}\|_{1+\gamma}\leq  \|e^{-(\alpha-ab)t}\langle \tilde{g},X_t\rangle)\|_{1+\gamma}+\|L_t^{\tilde{g},a}\|_{1+\gamma}\leq C
-\end{align*}
-for some constant $C$, which implies that $\lim_{t\rightarrow\infty} e^{-\frac{1}{2}bt}M_t^{\tilde{g},a}=0$. we complete our proof.
+As $\kappa(L\tilde{f}+ab\tilde{f})=\kappa(\tilde{f})\geq \kappa(f)+1$, following the similar way to prove the case $L^{1+\gamma}(\mathbb{P}_{\mu})$-convergence, we get there exists some $C, \delta>0$ such that for any $t\geq 0$
+\begin{align*}
+    \|e^{-(\alpha-ab)t}\langle \tilde{f},X_t\rangle)\|_{1+\gamma}\leq C e^{-\delta t},\quad \|e^{-(\alpha-ab)t}\langle L\tilde{f}+ab\tilde{f},X_t\rangle\|_{1+\gamma}\leq C e^{-\delta t}.
+\end{align*}
+Therefore, $|L_t^{\tilde{f},a}|\leq Y_t^{\tilde{f},a}:=\int_0^t e^{-(\alpha-ab)s}|\langle L\tilde{f}+ab\tilde{f},X_s\rangle|ds$ satisfying that, for ant $t\geq 0$,
+\begin{align*}
+    \|L_t^{\tilde{f},a}\|_{1+\gamma}\leq\|Y_t^{\tilde{f},a}\|_{1+\gamma}\leq \int_0^t \|e^{-(\alpha-ab)s}\langle L\tilde{f}+ab\tilde{f},X_s\rangle\|_{1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
+\end{align*}
+As $Y_t^{\tilde{f},a}$ is positive increasing, we get that it convergence some random variable $Y_{\infty}^{\tilde{f},a}$ almost sure and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. This is to say
+\begin{align*}
+    \lim_{t\rightarrow \infty}e^{-\frac{1}{2}bt}|L_t^{\tilde{f},a}|\leq  \lim_{t\rightarrow \infty}e^{-\frac{1}{2}bt}|Y_t^{\tilde{f},a}|=0.
+\end{align*}
+On the other hand, the martingale $M_t^{\tilde{f},a}$ satisfies
+\begin{align*}
+    \|M_t^{\tilde{f},a}\|_{1+\gamma}\leq  \|e^{-(\alpha-ab)t}\langle \tilde{f},X_t\rangle)\|_{1+\gamma}+\|L_t^{\tilde{f},a}\|_{1+\gamma}\leq C,\quad t\geq 0.
+\end{align*}
+for some constant $C$, which implies that $\lim_{t\rightarrow\infty} e^{-\frac{1}{2}bt}M_t^{\tilde{f},a}=0$. we complete our proof.
 \subsection{Proof of Theorem \ref{Theorem13}}
 The proof of Theorem \ref{Theorem13} is similar with that of Theorem \ref{Theorem12} or much easier.
-     We write
-    \begin{align*}
-        (\|X_t\|)^{-\frac{1}{1+\beta}}\langle g,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} (\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[g]+\sum_{\lceil t-\ln t \rceil}^t (\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[g]\\
+     For each $f\in \mathcal{P}$, we write
+    \begin{align*}
+        (\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} (\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[f]+\sum_{\lceil t-\ln t \rceil}^t (\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[f]\\
         &=I_t+J_t.
@@
     We denote
-    $$\tilde{I}_t=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{M_k^t[g]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
+    $$\tilde{I}_t=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{M_k^t[f]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
     Taking $\theta_k=( e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, then we get
     \begin{align*}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}-\exp\left(\theta^{1+\beta}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[g]\right)\right|\leq C \frac{1}{t^{\delta}},
+        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}-\exp\left(\theta^{1+\beta}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[f]\right)\right|\leq C \frac{1}{t^{\delta}},
     \end{align*}
@@
     \begin{align*}
-        Y_{t,k}:=\exp\left(i\theta\frac{M_k^t[g]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{M_k^t[g]}{\left(\|X_t\|\right)^{\frac{1}{1+\beta}}}\right)
+        Y_{t,k}:=\exp\left(i\theta\frac{M_k^t[f]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{M_k^t[f]}{\left(\|X_t\|\right)^{\frac{1}{1+\beta}}}\right)
     \end{align*}
@@
 \begin{align*}
-    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C_1 e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}+C_2 e^{-\delta(t-k-1)}
-\end{align*}
-Moreover, on the case $\alpha\beta<\kappa(g)(1+\beta)b$,  $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}< - \frac{\alpha\gamma-\kappa(g)(1+\gamma)b}{1+\gamma}$, this is to say,
+    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}+ e^{-\delta(t-k-1)}), \quad t\geq 0.
+\end{align*}
+Moreover, on the case $\alpha\beta<\kappa(f)(1+\beta)b$,  $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}< - \frac{\alpha\gamma-\kappa(f)(1+\gamma)b}{1+\gamma}$, this is to say,
 \begin{align*}
@@
 $C,\delta >0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal{E}_t^c)\leq C e^{-\delta t}$.
-What's more, for any $0\leq \gamma <\beta$, we let $p=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa(g)(1+\gamma)b}{1+\gamma}>0$, then by Lemma \ref{lem: lemma23}, we have
-\begin{align*}
-    \|M_k^t[g]\|\leq \|M_k^t[g]\|_{1+\gamma}\leq C_{\gamma} e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k}\leq C_{\gamma} e^{-pk}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}
+What's more, for any $0< \gamma <\beta$, we let $q=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa(f)(1+\gamma)b}{1+\gamma}>0$, then by Corollary \ref{cor27}, we have
+\begin{align*}
+    \|M_k^t[f]\|\leq \|M_k^t[f]\|_{1+\gamma}\leq \tilde{C}_1 e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k}\leq \tilde{C}_1 e^{-qk}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}
 \end{align*}

### 2019-01-31 supCLT.tex
supCLT.tex: 1029

@@
 %%%----Versions-----------------------------
+% supCLT4.tex ......... by Jianjie
 % supCLT3.tex 2018/8/25 by Zhenyao
@@
 %---The preamble----------------------
-\documentclass[12pt, a4paper]{amsart}
-\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
+\documentclass[12pt,oneside,english]{amsart}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage{hyperref}
+\usepackage{geometry}
+\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
+\usepackage{mathtools}
+\mathtoolsset{showonlyrefs}
+\usepackage{amsthm}
+\usepackage{stackrel}
+\usepackage[backref=section]{hyperref}
 \def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
@@
 \usepackage{mathrsfs}
-\usepackage{bbm}
+\usepackage{color}
 \usepackage{comment}
-\usepackage{mathtools}
-\mathtoolsset{showonlyrefs}
-\usepackage{stackrel}
-\usepackage{color}
+\theoremstyle{plain}
 \newtheorem{thm}{Theorem}[section]
@@
 \theoremstyle{definition}
+\newtheorem{defi}[thm]{Definition}
 \newtheorem{rem}[thm]{Remark}
@@
 \allowdisplaybreaks
+\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
+%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}
+
 %---Top matter------------------------------
@@
 \title
-    %{\large Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching}
     [CLT for Super-OU processes]
@@
 \author
-    [Y.-X. Ren, Z. Sun and J. Zhao]
-    {Yan-Xia Ren, Zhenyao Sun and Jianjie Zhao}
-%---Yan-Xia Ren
+    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
+    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
 \address
@@
 \thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
-%---Zhenyao Sun
 \address
@@
 \email{zhenyao.sun@pku.edu.cn}
-%---Jianjie Zhao
 \address
@@
     Let $d \in \mathbb N:= \{1,2,\dots\}$.
-For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.
+    \deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
     Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
@@
         = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
-    \quad f \in C^2(\mathbb{R}^d),
+        \quad \added{ x\in \mathbb R^d,}
+        f \in C^2(\mathbb{R}^d),
 \end{equation}
@@
     Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
-%Let $\psi$ be a function on $\mathbb C_+:= \{x+iy: x\in [0,\infty), y\in \mathbb R\}$ with
     Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
@@
         := - \alpha z + z^{1+\beta},
-    %\quad z \in \mathbb C_+,
         \quad z \in \mathbb R_+,
@@
         where $\alpha > 0$ and $\beta \in (0,1) $.
-Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of finite measures on $\mathbb{R}^d$.
-In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$. Put $\|\mu\|=\langle 1,\mu\rangle$.
+    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of \added{ all} finite measures on $\mathbb{R}^d$.
+    For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
+    Put $\|\mu\|=\langle 1,\mu\rangle$. 
     We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
@@
 \end{equation}
-%deleted
-%According to \cite[section 2]{Li2011Measure-valued}, the above is equivalent to
-%\begin{equation}\label{eq2}
-     %u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
-%\end{equation}
-%end deleted
 
@@
     Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
+\added{
+    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
+}\deleted{
     The fact $\psi(\infty)=\infty$ and $\int^{\infty}\frac{1}{\psi(z)}~dz<\infty$ implies that the probability of extinguish event $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ is contained in $(0,1)$, which means that our superprocess is non-persistent.
     In fact,
-\begin{equation}
-    \mathbb{P}_{\mu}(D)= \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
+}
+\begin{equation}
+\added{
+    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
     = e^{-\alpha^* \|\mu\|}, 
-\end{equation}
-    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$. See \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations} for a example.
-%comment
-   % {\bf (Zhenyao: We should use \cite[Theorem 12.5]{Kyprianou2014Fluctuations} and talk about the probability of $D:= \{\exists t\geq %0,~\text{s.t.}~\|X_t\|=0\}$.
-Because we want to emphsis that our superprocess is non-presistent.)}
-%end comment
-%comment
-    {\bf (Jianjie: I rewrite this part to emphsis that our superprocess is non-presistent.)}
-%end comment
+}\deleted{
+    \mathbb{P}_{\mu}(D)
+    = \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
+    = e^{-\alpha^* \|\mu\|},
+}
+\end{equation} 
+    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
+\deleted{ 
+    See {\cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations} }for a example.
+    }
+
     Define the \emph{Fenyman-Kac semigroup} by
@@
     T^{\alpha}_t f(x)
-    := \Pi_x [e^{\alpha t}f(\xi_t)],
+    :=
+\added{ e^{\alpha t} T_t f(x) =}
+    \Pi_x [e^{\alpha t}f(\xi_t)],
     \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
@@
 \end{equation}
-Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.
+\deleted{Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.}
 
 \subsection{OU semigroup}
-%moved and modified from below
-    In tihs subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
-%end moved and modified from below
-    %Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
+    In this subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
     Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
-    %It is known that $\xi$ has an invariant density
     It is known that $\xi$ has an invariant measure
@@
 \label{invariantdensity}
-    %\varphi (x)
     \varphi(x)dx
-    %=\Big (\frac{b}{\pi \sigma^2}\Big )^{\frac{d}{2}}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big),\quad x\in \mathbb{R}^d.
     =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
@@
 \end{equation}
-    Let $L^2(\varphi):= \left\{ h: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
+    Let $L^2(\varphi):= \left\{ h \added{ \in \mathscr B(\mathbb R^d)}: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
 \begin{equation}
@@
 \end{equation}
-%moved to above
-    %In tihs subsection, we recall some results on the spectrum in $L^2(\varphi)$ of the operator $L$, more details can be found in \cite{GD}.
-%end moved to above
-    %For each $p = (p_k)_{k = 1\dots d} \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$.
-    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$.
+    \added{ Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.}
+    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p! \added{ :}= \prod_{k= 1}^d p_k !$ and $\partial x^p \added{ :}= \prod_{k = 1}^d\partial x_k^{p_k}$.
     The Hermite polynomials are defined by
@@
 \end{equation}
-    It is known that the generator $L$ of OU process $\xi$ can be viewed as an operator on $L^2(\varphi)$ with eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
-    %For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ of this operator is
-    For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ is
+    It is known that \added{ $(T_t)$ is a strong continuous semigroup }\deleted{ the generator $L$ of OU process $\xi$ can be viewed as an operator} on $L^2(\varphi)$ \added{ and its generator $L$ has }\deleted{ with} eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
+    For each $k \in \mathbb N_0$, \added{denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then}\deleted{the eigenspace $A_k$ corresponding to eigenvalue $-bk$ is}
 \begin{equation}
     A_k
-    %= \operatorname{Span} \{\phi_p : |p|=k\},
     = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
@@
     := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
-    %\quad x\in \mathbb{R}^d, p\in \mathbb{Z}_+^d.
     \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
 \end{equation}
- %The function $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-b|p|$, and satisfies
     It is known that
@@
 \end{equation}
-    %Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
-    Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
-    %Therefore, for each $f\in L^2(\varphi)$,
+    Moreover, \deleted{it is known that} $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
     That is, for each $f\in L^2(\varphi)$,
@@
 \end{equation}
-%Let
-    Denote
+    Denote by
 \begin{equation}\label{order}
     \kappa(f)
-    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
-\end{equation}
-    %denote the order of function $f$ in $L^2(\varphi)$. Then $ \kappa(f)\geq 0$, in particular, the order of constant functions is zero.
+    :=\inf \left \{k\geq 0: \exists ~ p\in \added{ \mathbb N_0^d }\deleted{ \mathbb{Z}_+^d},{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
+\end{equation}
     the order of function $f$ in $L^2(\varphi)$.
-    Then $ \kappa(f)\geq 0$.
+    \added{ Note that }\deleted{ Then} $ \kappa(f)\geq 0$.
     In particular, the order of any constant function is zero.
 
-    %In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
+\added{
+\subsection{} 
+    Let $(\Omega, \mathscr F)$ be a measurable space.
+    Let $\mathcal F$ be a linear subspace of real valued measurable functions on $\Omega$.
+\begin{defi}
+\label{def: alpha-positive operator}
+    We say an operator $A: \mathcal F \to \mathcal F$ is $\alpha$-scalable for some $\alpha \in \mathbb R$ if for each $\lambda \in \mathbb R$ and $h \in \mathcal F$ we have $A (\lambda h) = |\lambda|^\alpha~ Ah$.
+\end{defi}
+
+    Suppose that $\alpha, \beta \in \mathbb R$. 
+    Let $A_\alpha$ and $A_\beta$ be an $\alpha$-scalable and a $\beta$-scalable operator on $\mathcal F$. 
+    Then it is clear that $A_\alpha A_\beta$ is an $(\alpha\beta)$-scalable operator.
+}
+\added{
+    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ defined by
+}
+\deleted{
     In this paper, we consider the class of functions of ploynomial growth $\mathcal{P}$ defined by
+}
 \begin{equation}
     \mathcal{P}
-    :=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
-\end{equation}
-    It is easy to see that $\mathcal{P} \subset L^2(\varphi)$.
-    %According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
+    :=\big \{f\in \added{ \mathscr B}\deleted{ \mathcal{B}}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+\end{equation}
+    It is \added{clear} \deleted{easy to see} that $\mathcal{P} \subset L^2(\varphi)$.
+    \added{ For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.}
+\added{
+    According to \cite[Fact 1.2]{MM}, $Q$ is an $1$-scalable operator on $\mathcal P$.
+}
+\deleted{
     According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R_0 \in \mathcal{P}$ such that,
@@
 \end{equation}
-
-\subsection{Characteristic functions}
-    %Let $X$ be a super OU-process with initial configuration $\mu$.
-%new added
-    Let the Gamma function $\Gamma$ be defined by
+}
+
+\subsection{}
+    \added{Recall $\Gamma$} \deleted{Let} the Gamma function \deleted{$\Gamma$ be} defined by
 \begin{equation}
@@
 \end{align}
-    Then it is elementary to verify that
+    \added{ It is known that }\deleted{ Then it is elementary to verify that}
 \begin{equation}
@@
 \item
-    is continuous in $\mathbb C_+$;
+    is continuous \added{ on }\deleted{ in} $\mathbb C_+\added{ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}}$;
 \item
-    is holomorphic in $\mathbb C_+^0$.
+    is holomorphic \added{ on }\deleted{ in} $\mathbb C_+^0\added{ := \{x+iy:x\in (0,\infty), y\in \mathbb R\}}$.
 \end{itemize}
@@
 \item
-    is continuous in $\mathbb C_+$;
+    is continuous \added{ on }\deleted{ in} $\mathbb C_+$;
 \item
-    is holomorphic in $\mathbb C_+^0$.
+    is holomorphic \added{ on }\deleted{ in} $\mathbb C_+^0$.
 \end{itemize}
-    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\mapsto \mathbb C_+$,
+    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path \added{ $\gamma:[0,1]\to \mathbb C_+$ }\deleted{ $\gamma:[0,1]\mapsto \mathbb C_+$},
 \begin{align}
@@
 \label{lem: Lip of power function}
-    There is a constant $C_0 > 0$ such that for any $z_0,z_1 \in \mathbb C_+$,
-\[
+    There is a constant $\added{ C_{\ref{lem: Lip of power function}} } \deleted{ C_0} > 0$ such that for any $z_0,z_1 \in \mathbb C_+$,
+\begin{equation}
+\label{eq: Lip of power function}
     |z_0^{1+\beta} - z_1^{1+\beta}|
-    \leq C_0(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
-\]
+    \leq \added{ C_{\ref{lem: Lip of power function}} }\deleted{ C_0}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
+\end{equation}
+\added{
+    In particular, for each $z\in \mathbb C$, we have
+$
+    |z^{1+\beta}|
+    \leq  C_{\ref{lem: Lip of power function}} |z|^{1+\beta}.
+$
+}
 \end{lem}
@@
     \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
-    \\&= \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c_0 |z|^{\beta},
+    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
     \quad z\in \mathbb C_+.
@@
 \end{proof}
-
+\subsection{}
     Let $X$ be the super OU-process discussed in the previous subsections.
-    Its branching mechanism $\psi$ can be extended in the following way: $\psi(z) := -\alpha z + z^{1+\beta}$ for $z\in \mathbb C_+$.
-    Then according to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}$ with derivative
+    Its branching mechanism $\psi$ can be extended \added{ on $\mathbb C_+$ by }\deleted{ in the following way: } $\psi(z) := -\alpha z + z^{1+\beta}$ for \added{ each} $z\in \mathbb C_+$.
+    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0\deleted{:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}}$ with derivative
 \begin{equation}
@@
 \end{equation}
-Write $\psi_0(z) = \psi(z) + \alpha z$ and $\psi'_0(z) = \psi'(z) + \alpha$.
-%end new added
-    %For any $f \in \mathcal{P}$, replace $f$ by $-i\theta f$ in equations of \eqref{super} and \eqref{eq2}, we obtain that
-%\begin{equation}\label{characteristic}
-    %\mathbb{P}_{\mu}\left[\exp(i\theta \langle  f,X_t\rangle)\right]=e^{\langle w_f(\cdot,t,\theta),\mu\rangle}
-%\end{equation}
-%where $w_f(x,t,\theta)=\log \mathbb{P}_{\delta_x}e^{i\theta\langle f,X_t\rangle}$ satisfying the equation that
-%\begin{equation}\label{charequation}
-    %w_f(x,t,\theta)-\int_0^t T_{t-s} \left(\psi (-w_f(\cdot,s,\theta))\right)(x)ds=i\theta T_tf(x)
-%\end{equation}
-    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, denote by $v_f(t,x,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]$ the characteristic exponent of $\{\langle f,X_t \rangle; \mathbb P_{\delta_x}\}$
-    (For percise definition, see the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
-    From \eqref{eq: -v has positive real part}, we know that $- v_f(t,x,\theta)$ taks values in $\mathbb C_+$.
-    Furthermore, we know from Proposition \ref{sec: definition of characteristic exponent} that
-%delete
-%\begin{equation}\label{characteristic}
-    %\mathbb{P}_{\mu}[e^{i\theta X_t(f)}]
-    %=e^{\langle w_f(\cdot,t,\theta),\mu\rangle},
-    %\quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
-%\end{equation}
-    %where $w_f(x,t,\theta)$ satisfies the equation
-\begin{align}\label{charequation}
+    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
+\added{
+    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in E$, define $\Psi_0f(x) := \psi_0(x,f(x))$ and $\Psi'_0 f(x) := \psi'_0(x,f(x))$.
+}
+    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, \added{define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$} \deleted{ denote by $v_f(t,x,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]$ the characteristic exponent of $\{\langle f,X_t \rangle; \mathbb P_{\delta_x}\}$}
+    (\added{ See }\deleted{ For percise definition, see} the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
+    From \eqref{eq: -v has positive real part}, we know that \added{$-U_tf(x)$} \deleted{$- v_f(t,x,\theta)$} taks values in $\mathbb C_+$.
+    Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
+\deleted{
+\begin{align}
+\label{charequation}
     v_f(t,x,\theta)-\int_0^t T_{t-s} \psi \big(-v_f(s,\cdot,\theta)\big)(x)ds
@@
     and
+}
+\added{
 \begin{align}
 \label{eq:chareq2}
-    %w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x),
+    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
+    =i T^{\alpha}_t f(x),
+    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
+\end{align}
+}
+\deleted{
+\begin{align}
+\label{eq:chareq2}
     v_f(t,x,\theta)-\int_0^t T^{\alpha}_{t-s} \psi_0(-v_f(s,\cdot,\theta))(x)ds=i\theta T^{\alpha}_t f(x),
@@
 \end{align}
+}
 %new added
@@
 %begin comments
-    {\bf Zhenyao: There are notation inconsistency in the Appendix and other suctions. Mainly on the branching mechanism: In the appendix, we use
+    {\bf Zhenyao: There are notation inconsistency in the Appendix and other sections. Mainly on the branching mechanism: In the appendix, we use
 \[
@@
     Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.
-
-    Another inconsistency is the notation for the characteristic exponent $\operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]$.
-In the appendix we use $v_f(t,x,\theta)$, but in other subsection we use $w_f(x,t,\theta)$.
-I recommended to use $v_f$ because I would like that $w$ be reserved for representing canonical element in some measurable spaces.
-Also, I would like to use $(t,x)$ instead of $(x,t)$ because it make more sense to put the ``time parameter t" first.
-($(t,x)$ and $(x,t)$ are both used by different authors.)
 
@@
     In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
-%For notational convenience, we always fix $g\in \mathcal{P}$ in the following sections, correspondingly, there exists $R\in\mathcal{P}$ such that
-    In this section, we assume a function $g$ satisfying that there exists $C_h, \kappa>0$ and $R^g_0\in \mathcal{P}$
-    such that
-\begin{align}
-\label{eq:gcontrol1}
+    \deleted{In this section, we assume a function $g$ satisfying that there exists $C_h, \kappa>0$ and $R^g_0\in \mathcal{P}$
+    such that}
+\deleted{\begin{align}\label{eq:gcontrol1}
     |T_tg|(x)
@@
     \quad t\geq 0,x\in \mathbb{R}^d.
-\end{align}
-%new added
-Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R^g \in \mathcal P$ such that
-\begin{align}
-\label{eq:gcontrol}
+\end{align}}
+\deleted{Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R^g \in \mathcal P$ such that}
+\deleted{\begin{align}\label{eq:gcontrol}
     T_s|T_t g|(x)
@@
     \quad t\geq 0,s\geq 0,x\in \mathbb{R}^d.
-\end{align}
-%end new added
-
+\end{align}}
+\added{
     Consider an incremental decomposition of $\langle g,X_t \rangle$.
-    %Denote by $\{\mathcal{F}_t:t\geq 0\}$ the filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$.
+    For each $t\geq 0$, denote by $\{\mathcal{F}_t:t\geq 0\}$ the natrual filtration of $X$.
+    For each $g\in \mathcal P$ and $0 \leq a \leq b \leq t <\infty$, define random variable
+\[
+    M_{r,s}\langle g,X_t\rangle   
+    := \mathbb P[\langle g,X_t\rangle|\mathscr F_s] - \mathbb P[\langle g,X_t\rangle|\mathscr F_r]
+    \langle T_{t-b}^\alpha g, X_b\rangle - \langle T_{t-a}^\alpha g, X_a\rangle.
+\]
+    Thus, we have
+\begin{align}
+    M^t_g(0,t)
+    = \sum_{k = 0}^{\lfloor t \rfloor - 1} M^t_g(k,k+1) + M^t_g(\lfloor t \rfloor, t).
+\end{align}
+    Note that 
+\begin{align}
+    M_g^t(a,b) = M_{(T_{t-b}^\alpha g)}^b (a,b).
+\end{align}
+}
+\deleted{
+    Consider an incremental decomposition of $\langle g,X_t \rangle$.
     For each $t\geq 0$, denote by $\{\mathcal{F}_t:t\geq 0\}$ the natrual filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$.
-    %For $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$.
     For each $f\in\mathcal{P}$ and $k \in \mathbb{N}$, let $f_k=T^{\alpha}_k f$.
-    %For each $t-k\geq 1$, according to \eqref{eq:meanformula}, write
-    %For each $k \in \mathbb N$ and $t\geq k+1$, 
-    According to \eqref{eq:meanformula}, write
-\begin{align*}
-    M_k^t[g]:&=\langle g_k, X_{t-k}\rangle-\mathbb{P}_{\mu}(\langle g_k,X_{t-k}\rangle|\mathcal{F}_{t-k-1})\\
-    &=\langle g_k, X_{t-k}\rangle-\langle T_1^{\alpha}g_{k},X_{t-k-1}\rangle\\
-    &=\langle g_k, X_{t-k}\rangle-\langle g_{k+1},X_{t-k-1}\rangle, \quad t\geq k+1.
-\end{align*}
-    %If $k=t$, let $M_t^t[g]:=\langle g_t,\mu\rangle$, where $\mu $ is the initial configuration.
-    What's more, we denote $M_{\lfloor t\rfloor}^t[g]:=\langle g_{\lfloor t \rfloor},X_{t-\lfloor t\rfloor}\rangle-\langle g_t, \mu\rangle$ and $M_t^t[g]:=\langle g_t,\mu\rangle$ under $\mathbb P_\mu$, where $\mu $ is the initial configuration.
-Thus
+    According to \eqref{eq:meanformula}, write}
+\begin{align*}
+    \deleted{M_k^t[g]}:&
+    \deleted{=\langle g_k, X_{t-k}\rangle-\mathbb{P}_{\mu}(\langle g_k,X_{t-k}\rangle|\mathcal{F}_{t-k-1})}\\
+    &\deleted{=\langle g_k, X_{t-k}\rangle-\langle T_1^{\alpha}g_{k},X_{t-k-1}\rangle}\\
+    &\deleted{=\langle g_k, X_{t-k}\rangle-\langle g_{k+1},X_{t-k-1}\rangle, \quad t\geq k+1.}
+\end{align*}
+    \deleted{What's more, we denote $M_{\lfloor t\rfloor}^t[g]:=\langle g_{\lfloor t \rfloor},X_{t-\lfloor t\rfloor}\rangle-\langle g_t, \mu\rangle$ and $M_t^t[g]:=\langle g_t,\mu\rangle$ under $\mathbb P_\mu$, where $\mu $ is the initial configuration.
+Thus}
 \begin{equation}\label{decomposition}
-    \langle g,X_t\rangle-M_t^t[g]
+    \deleted{\langle g,X_t\rangle-M_t^t[g]
     =\sum_{k=0}^{\lfloor t\rfloor}M_k^t[g]
-%new added
-    , \quad t \geq 0.
-%end new added
-\end{equation}
-
-%{\bf Jianjie: We have to emphasize that, if $t\notin \mathbb{N}$, there will appear an additional term corresponding to the interval $[\lfloor t %\rfloor,t]$, which can be handled with the same techniques.
-%}
-\subsection{Approximate expansion of characteristic function}
-
-In this subsection, we will estimate the characteristic function of $M_k^t[g]$ near $0$. First, we will prove the following inequality which controls $v_{g_k}(s,x,\theta)$.
-\begin{lem}\label{lemma1}
-%For any $k \in \mathbb{N}$, $x\in\mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
+    , \quad t \geq 0.}
+\end{equation}
+
+\added{
+\subsection{}
+    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R^+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
+    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Tf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
+    We say $R$ is a monotonic operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for each $f, g \in \mathcal P^+$ with $f\leq g$. 
+    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P$.
+    We say an operator $A$ is $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^+$ if $A: \mathcal D \to \mathcal P^*$ and there exits a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
+    In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
+    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$ if there exits a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(M, S)$ on $\mathcal D$ for each $s\in \Lambda$.
+}
+\added{
+    The first reason for considering $\gamma$-controllable operators is the following:
+\begin{lem}
+    Suppose that operators $(A_\lambda)_{\lambda\in \Lambda}$ are uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$.
+    Then there exists a $\gamma$-scalable operator $S$ such that
+\[
+    |A_\lambda T_t^\alpha f|
+    \leq e^{\gamma t (\alpha  - \kappa_f b)} SQf,
+    \quad \lambda \in \Lambda, t\geq 0, f\in \mathcal D.
+\]
+\end{lem}
+}
+\added{
+\begin{proof}
+    Let $(R,S)$ be the $\gamma$-control-pair for $(A_\lambda)_{\lambda\in \Lambda}$. 
+    Then
+\[
+    |A_\lambda T_t^\alpha f| \leq R|T_t^\alpha f|
+    \leq R (e^{\alpha t  - \kappa_f bt}Qf)
+    \leq S (e^{\alpha t  - \kappa_f bt}Qf)
+    \leq e^{\gamma t (\alpha  - \kappa_f b)} SQf.
+    \qedhere
+\]
+\end{proof}
+}
+\added{
+    For two operators $A$ and $B$ defined on same domain $\mathcal D\subset \mathcal P^*$, write $(A\times B)f (x):= Af(x) \times Bf(x)$. 
+    Let $a \in \mathbb R$, write $A^{\times a}f(x):= (Af(x))^a$ as long as it is well defined for all .
+    The second reason for considering $\gamma$-controllable operators is that they have good algebra properties: 
+\begin{lem}
+\label{lem: property of controllable operators}
+    Let operators $(A_\lambda)_{\lambda\in \Lambda}$ be uniformly $\gamma$-controllable on $\mathcal D$ from some $\gamma \in \mathbb R$ and $\mathcal D\subset \mathcal P^*$:
+\begin{itemize}
+\item[(1)]
+    Suppose that $(\Lambda, \mathscr F)$ is a measurable space.
+    Also suppose that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
+    For each probability measure $\mu$ on $(\Lambda, \mathscr F)$ write
+\[
+    A_\mu f(x):= \int_{\Lambda} A_\lambda f (x)~\mu(d\lambda), \quad f\in \mathcal D, x\in \mathbb R^d.
+\]
+    Then operators $\{A_\mu: \mu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ are uniformly $\gamma$-controllable on $\mathcal D$.
+\item[(2)]
+    Suppose that operators $(B_\theta)_{\theta\in \Theta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$. 
+    Also suppose that for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
+    Then operators $(B_\theta A_\lambda)_{\theta\in \Theta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
+\item[(3)]
+    Suppose that operators $(B_\theta)_{\theta \in \Theta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta\in \mathbb R$.
+    Then operators $(B_\theta\times A_\lambda)_{\theta \in \Theta, \lambda \in \Lambda}$ are uniformly $(\gamma+\beta)$-controllable.
+\item[(4)]
+    Let $a\in \mathbb R$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
+    Then operators $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ are uniformly $(a\gamma)$-controllable.
+\end{itemize}
+\end{lem}
+\begin{proof}
+    ......
+\end{proof}
+}
+
+\subsection{}
+\added{
+    For each $f \in \mathcal{P}$, $x\in E$ and $t\geq 0$, define
+\begin{align}
+\label{eq: def of Zf}
+    \tilde U_t f(x)
+    &:= i T^\alpha_t f(x) + \int_0^t T^\alpha_{t-s} \Psi_0(-i T_s^{\alpha}f)(x)ds
+    \\Z_t f (x)
+    &:= \int_0^t T^\alpha_{t-s} \Psi_0(-i T_s^{\alpha}f)(x)ds.
+\end{align}
+}
+\added{
+\begin{lem}
+\label{lem: upper bound for usgx} 
+$~$
+\begin{itemize}
+\item[(1)]
+    Operators $(-U_t)_{0\leq t\leq 1}$ are uniformly $1$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$. 
+\item[(2)]
+    Operators $(T^\alpha_t)_{0\leq t\leq 1}$ are uniformly $1$-controllable on $\mathcal P$.
+\item[(3)]
+    Operator $\Psi_0$ is $(1+\beta)$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
+\item[(4)]
+    Operators $(U_t- iT_t^{\alpha})_{0\leq t\leq 1}$ are uniformly $(1+\beta)$-controllable on $\mathcal P$.
+\item[(5)]
+    Operators $\{\Psi_0(-U_t) - \Psi_0(-iT_t^\alpha): 0\leq t\leq 1\}$ are uniformly $(1+2\beta)$-controllable on $\mathcal P$.
+\item[(6)]
+    Operator $(U_t-\tilde U_t)_{0\leq t\leq 1}$ are uniformly $(1+2\beta)$-controllable on $\mathcal P$.
+\item[(7)]
+    Operators $(Z_t)_{0\leq t\leq 1}$ are uniformly $(1+\beta)$-controallable on $\mathcal P$.
+\end{itemize}
+\end{lem}
+}
+\added{
+\begin{proof}
+    Proof of (1): From \eqref{eq: upper bound for vf} in the appendix, we have for each $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in E$,
+\[
+    |U_t g(x)|
+    \leq \sup_{0\leq u\leq 1}T_u^\alpha |g| (x).
+\]
+    Note that $f\mapsto\sup_{0\leq u\leq 1}T_u|f|$ is monotonic and $1$-scalable.
+
+    Proof of (2): Similar to the Proof of (1).
+
+    Proof of (3): According to Lemma \ref{lem: Lip of power function}, for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
+\[
+    |\Psi_0 f(x)| = |f(x)^{1+\beta}| \leq C_{\ref{lem: Lip of power function}} |f(x)|^{1+\beta}.
+\]
+    Also note that $f\mapsto |f|^{1+\beta}$ is monotonic and $(1+\beta)$-scalable.
+
+    Proof of (4): From (1), (2), (3) and Lemma \ref{lem: property of controllable operators}(2) we know that operators
+\[
+    f
+    \mapsto T^{\alpha}_{t-s}\Psi_0(-U_sf)(x),
+    \quad 0\leq s\leq t\leq 1
+\]
+    are uniformly $(1+\beta)$-controllable.
+    From Lemma \ref{lem: property of controllable operators}(1) and above we get the desired result.
+
+    Proof of (5): Notice that from Lemma \ref{lem: Lip of power function},
+\[
+    |\Psi_0(-U_t f) - \Psi_0(-iT_t^\alpha f) |
+    \leq  C_{\ref{lem: Lip of power function}} |U_u f-iT_u^{\alpha}f|(|U_u f|^{\beta}+|i T_u^{\alpha}f|^{\beta}).
+\]
+    From (1), (2), (4) and Lemma \ref{lem: property of controllable operators} (3,4) we get the desired result.
+
+    Proof of (6): Note that 
+\[
+    U_sf - \tilde U_sf
+    = \int_0^s T_{s-u}^{\alpha}\big(\Psi_0(-U_t f)-\Psi_0(-i T_t^{\alpha}f)\big)~du.
+\]
+    Then from (2), (5) and Lemma \ref{lem: property of controllable operators}(1,2) we get the desired result.
+
+    Proof of (7): Similar to the proof of (4).
+\end{proof}
+}
+\deleted{
+\begin{lem}
+\label{lemma1}    
     Let $R^g \in \mathcal P$ be the control function in \eqref{eq:gcontrol}, then
-%$$e^{-(\alpha-\kappa(g)b) s}|w_{g_k}(x,s,\theta)|\leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), \quad s\geq 0.$$
 \begin{equation}
@@
 \end{lem}
-%comment
-   % {\bf Zhenyao: The statement of the above Lemma is changed. I think the old version is not correct. I'm not sure how this influence the rest of the paper.
-
-    % Also, there are some paragraphs below I deleted which are duplicated with the appendix.}
-%end comment
-%delete
-    %Recall some result about the Kuznestov measures of $\{X_t, t\geq 0\}$.
-Let $\mathbb{D}$ be the collection of $\mathcal{M}(\mathbb{R}^d)$-valued right continuous functions $t\rightarrow \omega_t$ on $(0,\infty)$ having zero as a trap.
-Denote by $\{\omega_t, t\geq0\}$ the coordinate process of $\mathbb{D}$ and $(\mathcal{C},\mathcal{C}_t)$ the natural $\sigma$-algebras on $\mathbb{D}$ generated by the coordinate process.
-
-    %It's known by \cite[section 8.4]{Li2011Measure-valued} that  one can associate with $\{\mathbb{P}_{\delta_x}:x\in\mathbb{R}^d\}$ a family of $\sigma$-finite measures $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ defined on $(\mathbb{D},\mathcal{C})$ such that $\mathbb{N}_x\{0\}=0$,
-%\begin{equation}\label{Nmeasure}
-   %\int_{\mathbb{D}}(1-e^{-\langle f,\omega_t\rangle})\mathbb{N}_x(d\omega)=-\log \mathbb{P}_{\delta_x}(e^{-\langle f, X_t \rangle}), \quad f \in \mathcal{B}_b^+(\mathbb{R}^d), t>0,
-%\end{equation}
-%and, for $0<t_2<...<t_n<\infty$, and nonzero $\mu_1,...,\mu_n \in \mathcal{M}(\mathbb{R}^d)$,
-%\begin{align*}
-    %\mathbb{N}_x&\left(\omega_1\in d \mu_1,...,\omega_n \in d\mu_n\right)=\mathbb{N}_x(\omega_1\in d\mu_1)\mathbb{P}_{\mu_1}\left(X_{t_2-t_1}\in d \mu_2\right)...\\
-    %&\mathbb{P}_{\mu_{n-1}}\left(X_{t_n-t_{n-1}}\in d \mu_n\right).
-%\end{align*}
-    %We refer $\{\mathbb{N}_x:x \in \mathbb{R}^d\}$ as {\em Kuznestov measures} of $X$.
-For more general definition and further properties of such measures, we refer our readers to \cite{Li2011Measure,DK}.
-
-    %For any $\mu \in \mathcal{M}(\mathbb{R}^d)$, if $\mathcal{N}$ is a Poisson random measure defined in some probability space with intensity $\mathbb{N}_{\mu}(\cdot):=\int_{\mathbb{R}^d}\mathbb{N}_x(\cdot)~\mu(dx)$, then the super OU-process $\{X;\mathbb{P}_{\mu}\}$ can be realized by $\tilde{X}_t(\cdot)=\mu$ and
-%\begin{align*}
-    %\tilde{X}_t(\cdot):=\int_{\mathbb{D}}\omega_t(\cdot)\mathcal{N}(d\omega), \quad t\geq 0.
-%\end{align*}
-    %See \cite[Theorem 8.24]{Li2011Measure-valued} for a proof.
-
-    %What's more, if $\mathbb{P}_{\delta_x}|\langle f, X_t\rangle|<\infty$, then
-%\begin{equation}\label{Nmean}
-    %\mathbb{N}_x(\langle f,\omega_t \rangle) = \mathbb{P}_{\delta_x}(\langle f, X_t\rangle)=T^{\alpha}_t f(x).
-%\end{equation}
-    %See \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
-%end delete
-
-%\begin{proof}[Proof of Lemma \ref{lemma1}]
-\begin{proof}
-%Recall that $w_{g_k}(x,s,\theta)=\log\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
+\begin{proof}
     Recall that $v_{g_k}(s,x,\theta)=\operatorname{Log}\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
-    %Replace $f$ by $-i\theta g_k$ in equation \eqref{Nmeasure},\eqref{Nmean}, we obtain that $w_{g_k}(x,s,\theta)=\mathbb{N}_x\left(e^{i\theta\langle g_k,w_s\rangle}-1\right)$.
-    %Therefore,by the element inequality $|e^{i\theta}-1|\leq|\theta|$ for $\theta \in \mathbb{R}$, we have
-    %$$|w_{g_k}(x,s,\theta)|=|\mathbb{N}_x(e^{i\theta\langle g_{k},\omega_s \rangle}-1)|\leq |\theta|\mathbb{N}_x(\langle|g_k|,\omega_s\rangle)\leq|\theta|T_{s+k}^{\alpha}|g|$$
     Let $R^g \in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
@@
 \end{proof}
-    %For any $k \in \{0,1,...,t\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$, by the Markov property of $X$, we have
     For each $t \geq 0 $ and $k \in \{0,1,...,\lfloor t \rfloor-1\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$.
@@
     &\mathbb{P}_{\mu}(e^{i\theta M_k^t[g]}|\mathcal{F}_{t-k-1})
-    %&=\mathbb{P_{\mu}}\left [\mathbb{P}_{\nu}\left(e^{i\theta(\langle g_k,X_1\rangle-\langle T_1^{\alpha}g_k,\nu\rangle)}\right)|_{\nu=X_{t-k-1}}\right]   \\
     =\mathbb{P}_{\mu}(e^{i\theta (\langle X_{t-k},g_k\rangle - \langle X_{t-(k+1)},g_{k+1}\rangle)}|\mathcal{F}_{t-k-1})
-    %\\&=\mathbb P_\mu \big [\mathbb P_{X_{t-k-1}} [e^{i\theta(\langle g_k,X_1\rangle)}]e^{-i\theta \langle T_1^{\alpha}g_k,X_{t-k-1}\rangle}\big]
     \\&=\mathbb P_{X_{t-k-1}} [e^{i\theta(\langle g_k,X_1\rangle)}]e^{-i\theta \langle T_1^{\alpha}g_k,X_{t-k-1}\rangle}
     \\&= e^{\langle v_{g_k}(1,\cdot,\theta),X_{t-k-1}\rangle -i \theta\langle T_1^{\alpha}g_k,X_{t-k-1}\rangle},
-%new added
     \quad \mu \in \mathcal M(\mathbb R^d), \theta \in \mathbb R.
-%end added
-\end{align*}
-Hence, it is important to estimate the function $v_{g_k}(1,x,\theta)$. For any $f \in \mathcal{P}$, let
-\begin{equation}\label{w2function}
-    %\tilde{w}_{f}(x,t,\theta)=i\theta T^{\alpha}_t f(x) + \int_0^t T^{\alpha}_{t-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds
+\end{align*}
+    Hence, it is important to estimate the function $v_{g_k}(1,x,\theta)$.
+    For any $f \in \mathcal{P}$, let
+\begin{equation}
+\label{w2function}
     \tilde{v}_{f}(t,x,\theta)
@@
 \end{equation}
-
+}
+\deleted{
 \begin{lem}\label{lemma2}
-%There exists $R_1 \in \mathcal{P}$ and $p_1 >1+\beta$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have
     There exists $R^g_1 \in \mathcal{P}$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have
@@
 \end{align}
-
 \end{lem}
-\begin{proof}
-%As $\exp({\rm Re~}w_{g_k})=|\exp(w_{g_k})|=\left|\mathbb{P}_{\delta_x}\exp(i\theta \langle  g_k,X_t\rangle)\right|\leq 1$ implying ${\rm Re~}(-w_{g_k})\geq0$,
+}
+\deleted{
+\begin{proof}
     From \eqref{eq: -v has positive real part} we know that $\operatorname{Re}(-v_{g_k})\geq 0$.
-%we use the fact that
-%\begin{align}
-    %|x^{1+\beta}-y^{1+\beta}|
-    %\leq C (|x|^{\beta}+|y|^{\beta})|x-y|\label{element},
-%\end{align}
-    %for $x,y \in \mathbb{C}$ such that ${\rm Re~} x \geq 0, {\rm Re~} y\geq 0$ to get
     Let $C_0>0$ be the constant in Lemma \ref{lem: Lip of power function}, then from \eqref{eq:chareq2}, we have
@@
 \end{align}
-%Notice that, for $0\leq v \leq 1$, $x\in \mathbb{R}^d$ and $\theta \in \mathbb{R}$, by Lemma \ref{lemma1} and \eqref{eq:gcontrol}, we have
    Let $R^g\in \mathcal P$ be the control function in both \eqref{eq:gcontrol} and Lemma \ref{lemma1}, then for $0\leq u \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
@@
 \label{eq: upper bound of wgk}
-    %|w_{g_{k}}(x,v,\theta)|\leq &|\theta|e^{(\alpha-\kappa(g)b)k}(e^{(\alpha-\kappa(g)b)v}R(x))\leq|\theta|e^{(\alpha-\kappa(g)b)k}(C_1R(x)),
     |v_{g_{k}}(u,x,\theta)|
@@
 \end{align}
-%deleted
-    %where $C_1=\max\{1,e^{(\alpha-\kappa(g)b)}\}$.
-%end deleted
-%new added
     Observe that $(R^g)^{1+\beta}\in \mathcal P$.
@@
     According \eqref{eq:chareq2}, \eqref{eq: upper bound of wgk} and above, for $0\leq u \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
-%end new
 \begin{align}
@@
    =\Big| \int_0^u T^{\alpha}_{u-t}(-v_{g_k}(t,\cdot,\theta))^{1+\beta}(x)dt\Big|
-   %\\\leq & \int_0^1 T_{1-u}^{\alpha}(|w_{g_k}(\cdot,u,\theta)|^{1+\beta})(x)du \nonumber \\
    \\&\leq \int_0^u T_{u-t}^{\alpha}(|v_{g_k}(t,\cdot,\theta)|^{1+\beta})(x)dt
    \leq  |C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{1+\beta}\int_0^u (T_{u-t}^{\alpha}(R^g)^{1+\beta})(x)dt
-   %\\\leq &C_1^{1+\beta}e^{\alpha}|\theta e^{(\alpha-\kappa(g)b)k}|^{1+\beta}R^{1+\beta}(x)\nonumber\\
    \\&\leq e^{\alpha}|C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{1+\beta}\tilde R^g_0(x).
-%deleted
-   %\\= & |\theta e^{(\alpha-\kappa(g)b)k}|^{1+\beta}R_2(x),
-%end deleted
-\end{align}
-%where $R_2(x)=C_1^{1+\beta}e^{\alpha}R^{1+\beta}(x)$.
+\end{align}
     According to \eqref{eq:semigroupineq}, since $\tilde R^g_0(R^g)^{\beta} \in \mathcal P$, there exists an $\tilde R^g_1\in \mathcal P$ such that
@@
 \]
-%In consequence,
 As a consecuence of \eqref{eq: estimate of wgk}, \eqref{eq: Zineq}, \eqref{eq: upper bound of wgk} and the above, for $k \in \mathbb{N}$, $0\leq s \leq 1$, $x\in \mathbb{R}^d$ and $\theta \in \mathbb R$, we have
@@
     &|v_{g_k}(s,x,\theta)-\tilde{v}_{g_k}(s,x,\theta)|
-%new added
     \\&\leq C_0e^{\alpha}|C_g\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta} \int_0^s T_{s-u}^{\alpha}( \tilde R^g_0(R^g)^{\beta})(x)~du
-%end new added
-    %\\&\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{2+\beta}\cdot 2CC_1e^{\alpha}R(x)R_2(x).
     \\&\leq C_0e^{2\alpha}|C_g\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta}\tilde R^g_1(x).
@@
 \end{align}
-%delete
-    %Take $p_1=2+\beta$ and $R_1(x)=2CC_1e^{\alpha}R(x)R_2(x)$, we obtain the desired result.
-%end delete
-\end{proof}
-
-%new added
+\end{proof}
+}
+\deleted{
     It can be verified from its definition that $(\rho z)^{1+\beta} = \rho^{1+\beta}z^{1+\beta}$ for all $\rho \in [0,\infty)$ and $z\in \mathbb C_+$.
-%end new
-%For each $f\in \mathcal{R}$, define
     For each $f\in \mathcal{P}$, define
-\[
+\begin{equation}
+\label{eq: def of Zf}
     Z_f(s,x,\theta)
-    %:=\int_0^1 T^{\alpha}_{1-s}(-i\theta T_s^{\alpha}f)^{1+\beta}(x)ds ,
     :=\int_0^s T^{\alpha}_{s-u}\big((-i\theta T_u^{\alpha}f)^{1+\beta}\big)(x)du ,
-%new
     \quad s\geq 0, x\in E, \theta \in \mathbb R.
-%end new
-\]
+\end{equation}
 and let $Z_f(s,x)=Z_f(s,x,1)$.
-%Observe that
-Then we have
+\deleted{Then we have}
 \begin{equation}\label{zfunction}
-    Z_f(s,x,\theta)=\theta^{1+\beta}Z_f(s,x),
-%new
-    \quad s\geq 0, x\in E, \theta \in \mathbb R.
-%end new
-\end{equation}
-
+    \deleted{Z_f(s,x,\theta)=\theta^{1+\beta}Z_f(s,x),
+    \quad s\geq 0, x\in E, \theta \in \mathbb R.}
+\end{equation}
+}
+\deleted{
 \begin{cor}
 \label{cor: corollary2}
-    %For any $k\in\{0,1,...,t\}$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
     There exists $R^g_2\in \mathcal P$ such that for each $k\in\mathbb N$ and $0\leq s\leq1$, we have
 \begin{align}
-\label{zineq2}
     |Z_{g_k}(s,x)|\leq C_g^{1+\beta}e^{(\alpha-\kappa b)(1+\beta)k}R^g_2(x), \quad x\in \mathbb{R}^d,
@@
 \end{cor}
-
-\begin{proof}
-%new
+}
+\deleted{
+\begin{proof}
     Let $c_0 > 0$ be the constant in \eqref{eq: upper bound for beta power of z}.
-%end new
-    %By \eqref{eq:gcontrol}, we have
     Let $R^g\in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
@@
     |Z_{g_k}(s,x)|
-    %&\leq \int_0^1 T_{1-s}^{\alpha}(|T_s^{\alpha}g_k|^{1+\beta})(x)ds \leq\int_0^t T_{1-s}^{\alpha}\left(|C_1 e^{(\alpha-\kappa(g)b)k}|R(x)\right )^{1+\beta}
-    &\leq c_0\int_0^s T_{s-u}^{\alpha}(|T_u^{\alpha}g_k|^{1+\beta})(x)du
+    &\leq C_{}\int_0^s T_{s-u}^{\alpha}(|T_u^{\alpha}g_k|^{1+\beta})(x)du
     \leq c_0 \int_0^s T_{s-u}^{\alpha}\Big(\big(e^{(\alpha-\kappa b)k+\alpha}R\big)^{1+\beta}\Big)(x)~du
@@
 \end{align}
-%delete
-    %The proof of \eqref{zineq1} is similar with \eqref{zineq2}.
-%end delete
-\end{proof}
-
-%comments
-   % {\bf Zhenyao: I don't think the following corollary in the old version is accurate. Here is what I think the correct form should be.}
-%end comment
+\end{proof}
+}
+\textbf{ Zhenyao: I think the following Corollary is incorrect.
+In its proof, we seems used Jensen's inequality assuming $\mu$ is a probability measure (which is not the case).
+At first, I think I may find a way to fix this.
+But then I realize we don't really need this Corrollary to calculate $\|X_t(g)\|_{1+\gamma}$.
+So I didn't touch it.
+Yet, I'm not sure if this Corrollary is needed somewhere else in section 3.}
+
 \begin{cor}
 \label{cor: corollary1}
-%There exists $R_3 \in \mathcal{P}$ and $p_2 >1+\beta$ such that for any $k \in \mathbb{N}$ and $\theta \in \mathbb{R}$, we have
     There exists an $R^g_3 \in \mathcal{P}$ such that for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$,$\theta \in \mathbb{R}$ and $0\leq s\leq 1$, we have
 \[
-    %\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}
     \mathbb P_{\mu}[e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}]
-    %=1+\langle Z_{g_k}(\cdot,\theta),\mu\rangle+\langle err(\cdot,\theta),\mu\rangle
     =1+\langle Z_{g_k}(s,\cdot,\theta),\mu\rangle+ err(k,\mu,\theta),
 \]
-    %where $err(\cdot,\theta)\leq |\theta e^{(\alpha-\kappa(g)b)k}|^{p_2}R_3(\cdot)$.
     where $|err(k,\mu,\theta)| \leq (C_g|\theta e^{(\alpha-\kappa b)k}|^{2+2\beta} + C_g|\theta e^{(\alpha-\kappa b)k}|^{1+2\beta} )\langle R^g_3,\mu\rangle$.
 \end{cor}
-
 \begin{proof}
     Let 
-    % $ w_f(x,\theta)=w_f(x,1,\theta)$, $\tilde{w}_f(x,\theta)=\tilde{w}_f(x,1,\theta)$ for short, and write
 \begin{align}
 \label{eq: definition of varphi-mu-k-theta}
-    %\varphi_{\mu}(\theta)
     \varphi_{k,\mu,s}(\theta)
-    %=\mathbb{P}_{\mu}e^{i\theta(\langle g_k, X_1\rangle-\langle T_1^{\alpha}g_k,\mu \rangle)}
     =\mathbb{P}_{\mu}[e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}]
@@
 \end{align*}
-%Using Lemma \ref{lemma2}, \eqref{eq: Zineq} and the fact that if $ {\rm Re~} z\leq 0$, $|e^z-1-z|\leq|z|^2$,   we get, for any $\theta \in \mathbb{R}$ and $k\in \mathbb{N}$,
     Let $R^g_1\in \mathcal P$ be the control function in Lemma \ref{lemma2}.
@@
     &|\varphi_{k,\mu,s}(\theta)-1- \langle Z_{g_k}(s,\cdot, \theta),\mu\rangle|\\
-    %&\leq 2|\langle w_{g_k}(\cdot,\theta)-i\theta T_1^{\alpha}g_k, \mu \rangle|^2 + \langle |w_{g_k}(\cdot,\theta)-\tilde{w}_{g_k}(\cdot,\theta)|, \mu \rangle\\
     &\leq |\langle v_{g_k}(s,\cdot,\theta)-i\theta T_s^{\alpha}g_k, \mu \rangle|^2 + \langle |v_{g_k}(s,\cdot,\theta)-\tilde{v}_{g_k}(s,\cdot,\theta)|, \mu \rangle
-%new added
     \\&\leq \langle |v_{g_k}(s,\cdot,\theta)-i\theta T_s^{\alpha}g_k|^2, \mu \rangle + \langle |v_{g_k}(s,\cdot,\theta)-\tilde{v}_{g_k}(s,\cdot,\theta)|, \mu \rangle
-%end new
-    %\\&\leq |\theta_{k}|^{2(1+\beta)}\langle R_2,\mu\rangle + |\theta_{k}|^{2+\beta}\langle R_1,\mu\rangle,
     \\&\leq e^{2\alpha}|C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{2+2\beta}\langle (\tilde R^g)^2,\mu\rangle + |C_g\theta e^{(\alpha-\kappa b)k}|^{1+2\beta}\langle R^g_1,\mu\rangle.
@@
 \end{align*}
-%deleted
-    %where $\theta_k=\theta e^{(\alpha-\kappa(g)b)k}$. By implicitly assuming that $|\theta_k|\leq 1$, and taking $p_2=\min \{2(1+\beta), 2+\beta\}$ and $R_3=R_1+R_2$, we get the desired result.
-%end deleted
-\end{proof}
-
-\subsection{Moment}
-
- In this subsection, for any $\gamma \in (0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle $ by an exponential function depending on $\kappa$.
- %comment
-   % {\bf Zhenyao: I changed the statement and the proof of the following Lemma. I think the old version has too many mistakes.}
-%end comment
-%deleted
-\begin{comment}
-\begin{lem}\label{lem: lemma23}
-For any $0< \gamma < \beta$ there exists a constant $C_2>0$ such that
-$$\|M_k^t[g]\|_{1+\gamma}\leq C_2 e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(g)(1+\gamma)b}{1+\gamma}k},$$
-for any $k \in \{0,...,t \}$.
+\end{proof}
+
+\subsection{}
+
+ In this subsection, for any $\gamma \in (0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ \deleted{by an exponential function depending on $\kappa$}.
+
+\added{
+\begin{lem}
+\label{lem: control pair for P(M>lambda)}
+    There is an $(1+\beta)$-control-pair $(R,S)$ such that for each $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$ we have
+\[
+    \mathbb P_\mu (|M^t_g(0,t)| > \lambda) 
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\nu\rangle d\theta    
+    \leq \langle S| g|,\nu\rangle \frac{1}{\lambda^{1+\beta}}.
+\]
 \end{lem}
-\begin{proof}
-    %Let $C(k)=e^{(\alpha-\kappa(g)b)k}$, and, for convenience, define $A:=\{|M_t^k[g]|>C(k)\}$, $A_{\mu}:=\{|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\mu\rangle|>C(k)\}$.
-    Let $C(k)=e^{(\alpha-\kappa(g)b)k}$.
-    Define events $A:=\{|M_t^k[g]|>C(k)\}$ and $A_{k,\mu}:=\{|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\mu\rangle|>C(k)\}$ for each $k \in \mathbb N$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support.
-    Notice that
+}
+\added{
+\begin{proof}
+    Denote by $(R_0,S_0)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for U-iT}.
+    Using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability} and Lemma \ref{cor: corollary1} we have
+\begin{align}
+    &\mathbb P_\mu (|M^t_g(0,t)| > \lambda) 
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{i\theta M_g^t(0,t)}]\Big)d\theta
+    = \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{iM_{(\theta g)}^t(0,t)}]\Big)d\theta
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle 3|U_t(\theta g) - iT_t^\alpha(\theta g)|,\nu\rangle d\theta
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle 3R_0|\theta g|,\nu\rangle d\theta
+    \\& \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle 3S_0|\theta g|,\nu\rangle d\theta
+\end{align}
+    To finish the proof we write $R=3R_0$ and $S= 3S_0$.
+\end{proof}
+}
+\added{
+\begin{lem}
+    There is an $(1+\beta)$-scalable operator $S$ such that for each $g\in \mathcal P$, $\lambda >0$, $\mu\in \mathcal M_c(\mathbb R^d)$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
 \[
-    \mathbb{P}_{\mu}[|M_k^t[g]|^{1+\gamma}]
-    =\mathbb{P}_{\mu}[|M_k^t[g]\mathbf{1}_{A^c}|^{1+\gamma}]+\mathbb{P}_{\mu}[|M_k^t[g]\mathbf{1}_{A}|^{1+\gamma}]
-    =:I+II.
+    \mathbb P_{\mu}(|M^t_g(r,s)|>\lambda) 
+    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle Sg,\mu\rangle  
 \]
-    For the first part,
-\begin{align*}
-    I\leq C(k)^{1+\gamma}
-    =e^{(\alpha-\kappa(g)b)k(1+\gamma)}
-    \leq e^{\alpha t}e^{(\gamma \alpha-\kappa(g)(1+\gamma)b)k},
-\end{align*}
-    since $k\leq t$.
-
-For the second part, recall that $M_k^t[g]=\langle T_k^{\alpha}g, X_{t-k}\rangle-\langle T_{k+1}^{\alpha}g,X_{t-k-1}\rangle$,
-under the condition of $\sigma$-algebra $\mathcal{F}_{t-k-1}$, by the Markov property of $X$, we have
-\begin{align*}
-    II
-    %=\mathbb{P}_{\mu}\left[\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\mathbf{1}_{A_{\nu}}\right]|_{\nu=X_{t-k-1}}\right]
-    =\mathbb{P}_{\mu}\big[\mathbb{P}_{\nu}[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\mathbf{1}_{A_{k,\nu}}]|_{\nu=X_{t-k-1}}\big].
-\end{align*}
-%comment
-{\bf Zhenyao: Just wondering why $X$ has compact support a.s.ly.}
-%end comment
-%Observe that, for any $\nu \in \mathcal{M}(\mathbb{R}^d)$
-Observe that, for any $\nu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, from Fubini's theorem,
-\begin{align}
-    %&\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma}\right] \label{temp1}\\
-    &\mathbb{P}_{\nu}[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma} \mathbf 1_{A_{k,\nu}}] \label{temp1}\\
-    %&=(1+\gamma)\int_0^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|\mathbf{1}_{A_{\nu}}>\lambda\right)d\lambda \nonumber\\
-    &=(1+\gamma)\int_0^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|\mathbf{1}_{A_{k,\nu}}>\lambda)d\lambda \\
-    &\leq (1+\gamma)\int_{C(k)}^{\infty}\lambda^{\gamma}\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\right)d\lambda.\nonumber
-\end{align}
-%comment
-    {\bf Zhenyao: Why the above inequality is true?}
-%end comment
-Using the element inequality $\mathbb{P}(|Y|>2/u)\leq u^{-1}\int_{-u}^{u}(1-\varphi(t))dt$, see,\cite[Chaper 3]{Durrett2010Probability}, for example, where $Y$ is a random variable corresponding to characteristic function $\varphi(t)$, $u\geq 0$, we have
-
-$$\mathbb{P}_{\nu}\left(|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\right)\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1-\varphi_{\nu}(\theta))d\theta,$$
-where $\varphi_{\nu}(\theta))$ has been defined in Corollary \eqref{cor: corollary1}.
-What's more, as $g_k=T_k^{\alpha}g$, by Corollary \eqref{cor: corollary1} and Corollary \eqref{cor: corollary2}, we get, for any $\theta\in\mathbb{R}$, there exists $p>\beta$ (actually, we just take $p=p_2-1$ ), such that
-\begin{align*}
-    |1-\varphi_{\nu}(\theta)|&\leq|\langle Z_{g_k}(\cdot,\theta),\nu \rangle|+|\langle err(\cdot,\theta),\nu \rangle|\\
-    &\leq|\theta_k|^{1+\beta}\langle R_2,\nu\rangle+|\theta_k|^{1+p}\langle R_3, \nu \rangle\\
-    &\leq (|\theta_k|^{1+\beta}+|\theta_k|^{1+p})\langle R_2+R_3, \nu \rangle.
-\end{align*}
-Therefore,
-\begin{align*}
-    &\mathbb{P}_{\nu}\big(|\langle T_k^{\alpha}g, X_1 \rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|>\lambda\big)\\
-    &\leq\lambda\int_0^{2/\lambda}(|\theta_k|^{1+\beta}+|\theta_k|^{1+p})\langle R_2+R_3, \nu \rangle d\theta\\
-    &= \frac{2^{2+\beta}}{2+\beta}e^{(\alpha-\kappa(g)b)k(1+\beta)}\lambda^{-(1+\beta)}+ \frac{2^{2+p}}{2+p}e^{(\alpha-\kappa(g)b)k(1+p)}\lambda^{-(1+p)})\langle R_2+R_3,\nu \rangle,
-\end{align*}
- Then by calculating the integral in formula \eqref{temp1}, we get
-\begin{align*}
-    &\mathbb{P}_{\nu}\left[|\langle T_k^{\alpha}g, X_1\rangle-\langle T_{k+1}^{\alpha}g,\nu\rangle|^{1+\gamma} \right] \\
-    &\leq C_3\left(e^{(\alpha-\kappa(g)b)k(1+\beta)}C(k)^{\gamma-\beta}+e^{(\alpha-\kappa(g)b)k(1+p)}C(k)^{\gamma-p}\right)\langle R_2+R_3,\nu\rangle\\
-    &= C_3 e^{(\alpha-\kappa(g)b)k(1+\gamma)}\langle R_2+R_3,\nu\rangle,
-\end{align*}
-where $C_3=(1+\gamma)\cdot\max\{ \frac{2^{2+\beta}}{(\beta-\gamma)(2+\beta)}, \frac{2^{2+p}}{(2+p)(p-\gamma)}\}$. At last, using the mean formula \eqref{eq:meanformula}, we get
-\begin{align*}
-    II &\leq C_3e^{(\alpha-\kappa(g)b)k(1+\gamma)}\mathbb{P}_{\mu}\left[\langle R_2+R_3,X_{t-k-1}\rangle\right]\\
-       &=C_3e^{-\alpha}\langle T_{t-k-1}(R_2+R_3),\mu \rangle e^{\alpha t}e^{(\gamma\alpha-\kappa(g)b(1+\gamma))k}\\
-       &\leq C_4e^{\alpha t}e^{(\gamma\alpha-\kappa(g)b(1+\gamma))k}.
-\end{align*}
- By \eqref{eq:semigroupineq}, there exists $R_4\in \mathcal{P}$, such that $T_t(R_2+R_3)\leq R_4$, we take $C_4=C_3 e^{-\alpha}\langle R_4, \mu\rangle$.
-Combining with the result of $I$ and $II$, we complete the proof by taking $C_2=(1+C_4)^{\frac{1}{1+\gamma}}$.
-\end{proof}
-\end{comment}
-%end deleted
-%new added
+\end{lem}
+}
+
+\added{
+\begin{proof}
+    Denote by $(R_0,S_0)$ the $(1+\beta)$-control-pair in Lemma \ref{lem: control pair for P(M>lambda)}. 
+    Then using Markovian property of $(X_t)$ we get
+\begin{align}
+    &\mathbb P_{\mu}(|M^t_g(r,s)|>\lambda) 
+    = \mathbb P_\mu \big[\mathbb P_\mu\big(|M_g^t(r,s)|> \lambda\big| \mathscr F_r\big)\big]
+    = \mathbb P_\mu \big[\mathbb P_{X_r}(|M^{t-r}_g(0,s-r)|> \lambda)\big] 
+    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|M^{s-r}_{T^\alpha_{t-s}g}(0,s-r)|> \lambda)\big]
+    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
+    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big] 
+    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big] 
+    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \mathbb P_\mu [ \langle S_0Qg,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
+    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \langle T_r^\alpha S_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
+    \leq e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle QS_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}.
+\end{align}
+    Note that
+\[
+    S := \frac{2^{2+\beta}}{2+\beta}QS_0Q 
+\]
+    is an $(1+\beta)$-scalable operator which is independent of the choice of $g,\mu, \lambda, r, s$ and $t$.
+\end{proof}
+}
+\added{
+\begin{lem}
+    For each $g\in \mathcal P$, $\mu \in \mathcal M_c$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
+\[
+    \mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big] 
+    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb)}.
+\]
+\end{lem}
+}
+\added{
+\begin{proof}
+    For each $c>0$ we have
+\begin{align}
+    &\mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big] 
+    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|M^t_g(r,s)|>\lambda) d\lambda
+    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|M^t_g(r,s)|> \lambda) d\lambda
+    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle Sg,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
+    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle Sg,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
+\end{align}
+    Taking $c = e^{(t-s)(\alpha- \kappa_gb)}$ we have
+\begin{align}
+    &\mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big] 
+    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa_gb)} e^{\alpha r}\Big(1+ \langle Sg,\mu\rangle \frac{1+\gamma}{\beta - \gamma}\Big).
+\end{align}
+    Note that
+\[
+    (1+\gamma)(t-s)(\alpha- \kappa_gb) + \alpha r
+    \leq t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb).
+    \qedhere
+\]
+\end{proof}
+}
+
+\deleted{
 \begin{lem}\label{lem: lemma23}
@@
 \begin{proof}
-    Let $R^g$ be the control function in \eqref{eq:gcontrol}.
-    Then for each $\mu\in \mathcal M(\mathbb R^d)$ with compact support and $t\geq 0$, we have
+    For each $g \in \mathcal P$, $t\geq 0$, $\gamma \in (0,\beta)$ and $\mu$ with compact support:
 \begin{align}
     \mathbb P_\mu\big[|M_t^t[g]|^{1+\gamma}\big]
-    = |\langle T_t^\alpha g, \mu\rangle|^{1+\gamma}
+    = |\langle g_t, \mu\rangle|^{1+\gamma}
     \leq \langle e^{\alpha t} |T_tg|, \mu\rangle^{1+\gamma}
-    \leq  \langle R^g,\mu\rangle^{1+\gamma} C_h^{1+\gamma}e^{\alpha t} e^{(\alpha\gamma- \kappa(g)b(1+\gamma))t}.
+    \leq \langle e^{\alpha t}e^{-\kappa(g)bt}Q[g],\mu\rangle^{1+\gamma}
+\leq (e^{\alpha t}e^{-\kappa(g)bt})^{1+\gamma}\langle Q[g],\mu\rangle^{1+\gamma}.
 \end{align}
@@
 \end{proof}
-
+}
     As $\langle g,X_t\rangle$ is the sum of $M_k^{t}[g], k=0,1,...,\lfloor t\rfloor$ and $M_t^t[g]$. We obtain the following lemma.
-
-\begin{lem}\label{lemma24}
-%For each $0\leq \gamma < \beta$ there exists a constant $C_5>0$, we have the result:
+\added{
+\begin{lem}
+\label{lemma24}
+    For each $0 < \gamma < \beta$ and $\mu\in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$ there exists a constant $C>0$ such that for each $t\geq 0$:
+\begin{itemize}
+\item[(1)]
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$.
+\item[(2)]
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$.
+\item[(3)]
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
+\end{itemize}
+\end{lem}
+\begin{proof}
+    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$.
+    Let $C$ be the constant in Lemma \ref{lem: lemma23}.
+    Using the triangle inequality,
+\begin{align}
+    \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\| M_g^t(t-k-1,t-k)\|_{\mathbb P_\mu;1+\gamma}+\|M_g^t(0, t-\lfloor t \rfloor)\|_{\mathbb P_\mu;1+\gamma}
+    \\ &\leq C e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa_g (1+\gamma)b}{1+\gamma} k} .
+\end{align}
+    By calculating the sum on the right, we get the desired result.
+\end{proof}
+}
+\deleted{
+\begin{lem}%\label{lemma24}
 For each $0 < \gamma < \beta$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_2>0$, such that for each $t\geq 0$:
@@
 \end{proof}
+}
+\deleted{
 According to \eqref{eq:semigroupineq}, each $f \in \mathcal{P}$ satisfies \eqref{eq:gcontrol1} with $C_f=1$, $\kappa=\kappa(f)$ and $R_0^f=R_0$. Thus 
@@
 \end{cor}
-\begin{comment}
-
-\begin{rem}
-    The Lemma \eqref{lemma24} offers insights how to guess $\{F_t, t\geq0\}$ raised in Introduction. indeed
-    \begin{itemize}
-        \item  Large branching rate: when $\alpha\gamma > \kappa(g)(1+\gamma)b$, $F_t\approx e^{(\alpha-\kappa(g)b)t} $;
-        \item  Critical branching rate: when $\alpha\gamma = \kappa(g)(1+\gamma)b$, $F_t\approx (te^{\alpha               t})^{\frac{1}{1+\beta}}\approx(t\|X_t\|)^{\frac{1}{1+\beta}}$;
-        \item  Small branching rate: when $\alpha\gamma < \kappa(g)(1+\gamma)b$, $F_t\approx e^{\frac{\alpha t}{1+\beta}}\approx \|X_t\|^{\frac{1}{1+\beta}}$.
-    \end{itemize}
-\end{rem}
-{\bf (Jianjie: We do not mention $F_t$ in Introduction, But we possibly need this mark in the future, so I decide to keep this part for now.)}
-\end{comment}
+}
 \subsection{Martingales}
-In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales, for $0<\gamma<\beta$.
+    In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales with $0<\gamma<\beta$.
 Recall that $L$ is the infinitesimal generator of OU-process.
@@
 \label{defmartingale}
-  M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle \bar{f}, X_s\rangle~ ds
-\end{align}
-Where $\bar{f}=(L+ab)f$. The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathcal{F}_t\}_{t\geq 0}$.
-\begin{lem}\label{lemma25}
-Let $a\in \mathbb{R}$ and $h\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$. Then the process $\left\{M_t^{f,a}, \mathcal{F}_t:t\geq 0\right\}$ is an martingale.
+    M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds
+\end{align}
+    \deleted{Where $\bar{f}=(L+ab)f$.} 
+    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathcal{F}_t\}_{t\geq 0}$.
+\begin{lem}
+\label{lemma25}
+    Let $a\in \mathbb R$ and $\added{f} \deleted{h}\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$.
+Then the process \added{$(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.} \deleted{$\left\{M_t^{f,a}, \mathcal{F}_t:t\geq 0\right\}$ is an martingale.}
 \end{lem}
 \begin{proof}
-For any $a\in \mathbb{R},x\in \mathbb{R}^d$, take $\pi_tf(x)=T_t^{ab}f(x)$ into \cite[Theorem A.55]{Li2011Measure-valued}, we have
+    \added{Write $\bar{f}=(L+ab)f$.} \deleted{For any $ a\in \mathbb{R},x\in \mathbb{R}^d$, take $\pi_tf(x)=T_t^{ab}f(x)$} \added{According to} \deleted{into} \cite[Theorem A.55]{Li2011Measure-valued}, we have
 \begin{align}\label{Theorem55}
@@
 \label{martingale1}
-    %\mathbb{P}_{\mu}\left[M_t^{f,a}|\mathcal{F}_s\right] &=e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\left[\int_0^t e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du|\mathcal{F}_s\right]\nonumber\\
-    &\mathbb{P}_{\mu}\left[M_t^{f,a}|\mathcal{F}_s\right]
-    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\left[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du|\mathcal{F}_s\right]
+    &\mathbb{P}_{\mu}[M_t^{f,a}|\mathcal{F}_s]
+    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathcal{F}_s\big]
     %\\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du\nonumber\\
@@
 \end{align}
-By using \eqref{Theorem55}and Fubini's theorem , further we get
+    \added{Using \eqref{Theorem55} and Fubini's theorem, we have}
+    \deleted{By using \eqref{Theorem55} and Fubini's theorem , further we get}
 \begin{align}
@@
     &=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-e^{-(\alpha-ab)s}\langle
-    f,X_s\rangle
-\end{align}
-Take it to \eqref{martingale1}, we get the desired result.
-\end{proof}
-{\bf (Jianjie: Please check this above lemma. )}
-%comment
-%{\bf Zhenyao: I think the above Lemma is not accurate.
-I think we need condition that $f\in C^2(\mathbb R^d) \cap \mathcal P$.
-Also in the proof we %better use \cite[Theorem A.55]{Li2011Measure-valued} and Fubini's theorem.}
-%end comment
-
-Let $p=(p_1,...,p_d)\in \mathbb{Z}_+^d$, recall that $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$. Define
+    f,X_s\rangle.
+\end{align}
+    \deleted{Take it to} \added{Using this and} \eqref{martingale1}, we get the desired result.
+\end{proof}
+
+    Let $p=(p_1,...,p_d)\in \added{\mathbb N_0^d} \deleted{\mathbb{Z}_+^d}$, recall that $\phi_p$ is \added{one of the} \deleted{an} eigenfunction\added{s} of $L$ corresponding to the eigenvalue $-|p|b$.
+Define
 $$H_t^p:=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.$$
@@
 \begin{lem}\label{lemma26}
-$\{H_t^p: t\geq0\}$ is a martingale with respect to $\mathcal{F}_t$.
-If $\alpha\beta>|p|b(1+\beta)$, then for any $0< \gamma<\beta$ and $\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, we have $\sup_{t\geq 0}\|H_t^p\|_{1+\gamma}< \infty$.
-Thus the limit
+    \added{$(H^p_t)_{t\geq 0}$} \deleted{$\{H_t^p: t\geq0\}$} is a martingale with respect to \added{filtration $(\mathscr F_t)$} \deleted{$\mathcal{F}_t$}. 
+    \deleted{If} \added{Moreover, if} $\alpha\beta>|p|b(1+\beta)$, then for any $0< \gamma<\beta$ and \added{$\mu \in \mathcal M_c(\mathbb R^d)$} \deleted{$\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support}, we have $\sup_{t\geq 0}\|H_t^p\|_{\added{\mathbb P_\mu;}1+\gamma}< \infty$ \added{and}\deleted{.
+Thus the limit}
 $$H_{\infty}^p:=\lim_{t\rightarrow \infty}H_t^p$$
@@
 \begin{proof}
-    By taking $a=|p|$ and $f=\phi_p$ in Lemma \ref{lemma25}, we get $\{H_t^p, \mathcal{F}_t:t\geq 0\}$ is a martingale.
-
-    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that $\alpha\gamma_0>|p|(1+\gamma_0)b$.
-Using  Lemma \ref{lemma24} and the fact $\kappa(\phi_p)=|p|$, we get that, for any $\gamma_0\leq\gamma<\beta$
-    $$\|H_t^p\|_{1+\gamma}\leq C_2e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C_2,$$
- For any $0\leq\gamma<\gamma_0$, by the concave of function $h(x)=x^{(1+\gamma)/(1+\gamma_0)}$,
+    \deleted{By taking $a=|p|$ and $f=\phi_p$ in} \added{According to} Lemma \ref{lemma25}, we get \added{$(H_t^p)_{t\geq 0}$} \deleted{$\{H_t^p, \mathcal{F}_t:t\geq 0\}$} is a martingale.
+
+    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that \deleted{$\alpha\gamma_0>|p|(1+\gamma_0)b$} \added{for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$}. 
+    Using  Lemma \ref{lemma24} and the fact $\kappa(\phi_p)=|p|$, we get that, for any $\gamma_0\leq\gamma<\beta$\added{, there exists a constant $C$ such that}
+    $$\|H_t^p\|_{1+\gamma}\leq Ce^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C.$$
+    For any $0\leq\gamma<\gamma_0$, \deleted{by the concave of function $h(x)=x^{(1+\gamma)/(1+\gamma_0)}$,} \added{consider the concave function $x\mapsto x^{(1+\gamma)/(1+\gamma_0)}$ on $[0,\infty)$, using Jensen's inequality, we have}
     $$\mathbb{P}_{\mu}|H_t^p|^{1+\gamma}\leq(\mathbb{P}_{\mu}|H_t^p|^{1+\gamma_0})^{\frac{1+\gamma}{1+\gamma_0}}<\infty.$$
@@
 \begin{proof}
-Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
+Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{eq: zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
 \begin{align}
@@
 \end{proof}
-\begin{comment}
-    where $h_k=Z_{g_k}-\langle Z_{g_k}, \varphi\rangle$.
-To estimate $h_k$, we claim that for any $f \in \mathcal{P}$, $T_t f$ is differential and $\frac{\partial (T_t f)}{\partial x_i} \in \mathcal{P}, i=1,...,d$.
-We firstly admit the claim and continue our proof.
-    \begin{align*}
-        h_k(x)&=\int_{\mathbb{R}^d}(Z_{g_k}(x)-Z_{g_k}(y))\varphi(y)~dy\\
-        &\leq\int_{\mathbb{R}^d} \sup|\nabla Z_{g_k}(z)||x-y|\varphi(y)~dy.
-    \end{align*}
-
-    Let $\tilde{g}=T_1^{\alpha}g $, then $\tilde{g}$ differentiable. For any $i \in \{1,...,d\}$,
-    $$\frac{\partial}{\partial x_i}Z_{g_k}(x)=\int_0^1 T^{\alpha}_{1-s}\left(\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha} \tilde{g})^{1+\beta}\right)(x)~ds$$
-    Using the inequality \eqref{eq:semigroupineq} and the fact $\kappa\left(\frac{\partial \tilde{g}}{\partial x_i}\right)\geq \kappa(\tilde{g})-1$, see \cite[Lemma 2.3]{RSZ}, we get that there exists $R_7 \in \mathcal{P}$ such that, for any $k\in \mathbb{N}$,
-    \begin{align*}
-        \left|\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha}\tilde{g})^{\beta}\right|&=\left|(1+\beta)(-i T_{s+k-1}^{\alpha}\tilde{g})^{\beta}(-i e^{-b(s+k-1)}T_{s+k-1}^{\alpha}\left(\frac{\partial \tilde{g}}{\partial x_i}\right))\right|\\
-        &\leq e^{(\alpha-\kappa(\tilde{g})b)(s+k-1)(1+\beta)}R_7(x).
-    \end{align*}
-
-    What's more, $T_1 g(x)=\sum_{|p|\geq\kappa(g)}\langle g,\phi_p\rangle e^{-b|p|}\phi_p(x)$, thus $\kappa(\tilde{g})=\kappa(g)$.
-Therefore, there exists $R_8 \in \mathcal{P}$ such that for any $k\in \mathbb{N}$,
-    $$\left|\frac{\partial}{\partial x_i}Z_{g_k}(x)\right|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}R_8(x),\quad x\in \mathbb{R}^d. $$
-    Hence
-\begin{align}
-    |h_k(x)|\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}(R_8(x)(|x|+\int_{\mathbb{R}^d}|y|\varphi(y)~dy)),\quad  x\in \mathbb{R}^d, k\in\mathbb{N},
-\end{align}
-
-Denote $R_9=R_8(x)(|x|+\int_{\mathbb{R}^d}|y|\varphi(y)~dy)$, we notice that $\kappa(R_9)\geq1$. Therefore, for $\theta\in \mathbb{R}^d$, $k\in\mathbb{N}$ and $t>k$,
-\begin{align*}
-  \mathbb{\tilde{P}}_{\mu}\left[|\langle h_k,X_{t-k-1}\rangle\right|]&\leq e^{(\alpha-\kappa(g)b)(1+\beta)k}\langle T_{t-k-1}^{\alpha}R_9,\mu\rangle\\
-  &\leq C_{12} e^{(\alpha-\kappa(g)b)(1+\beta)k}e^{(\alpha-b)(t-k-1)}.
-\end{align*}
- The last inequality holds as \eqref{eq:semigroupineq}. Now combine with \eqref{II1}, we can chose $\epsilon$ just depending $b$ such that,
-\begin{align}
-    II\leq C_{12} e^c|\theta|^{1+\beta} e^{-(b-\epsilon)(t-k-1)}\leq C_{13}|\theta|^{1+\beta}e^{-\delta_3(t-k)},\quad k\in\mathbb{N},t>k,\theta\in\mathbb{R}\label{lemma32q}
-\end{align}
-for some $C_{13},\delta_3>0$.
-
-At last, Using Lemma \ref{lemma28}, on the event $\mathcal{A}^c_{t-k-1}$, we get
-
-\begin{align}
-    \left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[g]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[g])\right)\mathbf{1}_{\mathcal{A}^c_{t-k-1}}\right|&\leq e^c\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1})\nonumber\\
-    &\leq C_{14} e^{-\delta_1(t-k)},\label{lemma33q}
-\end{align}
-Combine with \eqref{lemma31q},\eqref{lemma32q} and \eqref{lemma33q}, by letting $t \rightarrow \infty$, We obtain the desired result.
-
-\end{comment}
-\begin{comment}
-
-Now we will prove the claim mentioned in Lemma \ref{lemma31}.
-\begin{proof}[Proof of claim:] Let $\sigma_t^2=\sigma^2(1-e^{-2bt})$, then we get
-\begin{align*}
-    T_t f(x)= \int_{\mathbb{R}^d}f(y)\left(\frac{b}{\pi \sigma_t^2}\right)^{\frac{d}{2}} \exp\left(-\frac{b}{\sigma_t^2}(y-xe^{-bt})^2\right)dy=f\ast\varphi_t(xe^{-bt})
-\end{align*}
-where $\varphi_t(x)=\left(\frac{b}{\pi \sigma_t^2}\right)^{\frac{d}{2}} \exp\left(-\frac{b}{\sigma_t^2}x^2\right)$, which is belong to $C^{\infty}$.
-Hence $  T_t f(x)$ also belong to $C^{\infty}$.
-On the other hand, by calculating, we get
-\begin{align*}
-    \frac{\partial}{\partial x_i}T_t f(x)&=\int_{\mathbb{R}^d}f(y)\frac{\partial}{\partial x_i}\left(\varphi_t(xe^{-bt}-y)\right)dy\\
-    &=e^{-bt}\int_{\mathbb{R}^d}\frac{\partial \varphi_t}{\partial x_i}(y)f(xe^{-bt}-y)dy\\
-    &=\frac{-2bx_i}{\sigma_t^2}e^{-bt}T_t f(x)\in \mathcal{P}.
-\end{align*}
-\end{proof}
-
-\begin{rem}
-   i) For any $k\in\mathbb{N}$, $e^{\theta^{1+\beta}e^{\alpha}m_k[g]}$ is the characteristic function of some $1+\beta$-stable distribution, hence $|e^{\theta^{1+\beta}e^{\alpha}m_k[g]}|\leq 1$.
-\end{rem}
-
-\end{comment}
 \begin{cor}\label{corollary31}
@@
 
-%new added
-\section{Appendix}
+\appendix
+\section{}
 
 \subsection{}
-    We first present two analytic results which are useful.
+    \added{ In this subsection, we }\deleted{ We first} present two analytic results which are useful.
 \begin{lem}
@@
 \begin{align}
-	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(u_f(t,\cdot))},
+    \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(\added{ V_tf}\deleted{ u_f(t,\cdot)})},
     \quad t\geq 0, \mu \in \mathcal M_E^1, f\in \mathscr B^+_b(E),
 \end{align}
-	where the function $u_f:(t,x) \mapsto u_f(t,x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
+    where \added{ for each $f\in b\mathscr B_E$,} the function \added{ $(t,x)\mapsto V_tf(x)$}\deleted{ $u_f:(t,x) \mapsto u_f(t,x)$} on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
 \begin{align}\label{eq:FKPP_in_definition}
-	u_f(t,x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi \big(\xi_s,u_f(t-s,\xi_s)\big) ds \Big]
+    V_tf(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi(\xi_s,V_{t-s}f)ds \Big]
     = \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
     \quad t \geq 0, x \in E.
+    \\
+    \deleted{u_f(t,x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi \big(\xi_s,u_f(t-s,\xi_s)\big) ds \Big]
+    = \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
+    \quad t \geq 0, x \in E.}
 \end{align}
@@
     Notice that, from the branching property of the superprocess $X$, $\{X_t(f); \mathbf P_{\delta_x}\}$ is an infinitely divisible random variable with finite moment.
-	Denote by $v_f(t,x,\theta) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i\theta X_t(f)}]$ the charateristic exponent of random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
+    \added{ Denote by $U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}]$ }\deleted{ Denote by $v_f(t,x,\theta) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i\theta X_t(f)}]$} the charateristic exponent of random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
     According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, for each $\theta \in \mathbb R$,
@@
 \label{eq: N and characteristic exponent}
-	v_f(t,x,\theta) = \mathbb N_x[e^{i\theta W_t(f)} - 1],
+    \added{ U_tf(x)}\deleted{ v_f(t,x,\theta)} = \added{ \mathbb N_x[e^{i W_t(f)} - 1]}
+    \deleted{ \mathbb N_x[e^{i\theta W_t(f)} - 1]},
     \quad \theta \in \mathbb R.
@@
 \subsection{}
+\deleted{
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
-    Fix $t > 0,x\in E$ and $f\in L^1(\xi)$.
+    In this subsection, we want to show that if $f\in L^2(\xi)$ then the following expectation
+\[
+    \Pi_x\Big[\int_0^t \psi(\xi_s,- U_{t-s}f)ds\Big]
+    \in \mathbb C
+\]
+    is well defined.
+}
+
+    Firstly, fix $t > 0,x\in E$ and $f\in L^1(\xi)$.
     Noticing that
 \[
-	e^{\operatorname{Re} v_f(t,x,\theta)} = |e^{v_f(t,x,\theta)}|
-	= |\mathbf P_{\delta_x}[e^{i\theta X_t(f)}]| \leq 1,
+    \added{ e^{\operatorname{Re} U_tf(x)}}
+    \deleted{ e^{\operatorname{Re} v_f(t,x,\theta)}} 
+    = \added{|e^{U_tf(x)}|}
+    \deleted{ |e^{v_f(t,x,\theta)}|}
+    = \added{|\mathbf P_{\delta_x}[e^{i X_t(f)}]|}
+    \deleted{|\mathbf P_{\delta_x}[e^{i\theta X_t(f)}]|}
+    \leq 1,
     \quad \theta\in \mathbb R,
@@
 \label{eq: -v has positive real part}
-	\operatorname{Re} v_f(t,x,\theta) \leq 0,\quad \theta \in \mathbb R.
+    \added{ \operatorname{Re} U_tf(x)}
+    \deleted{ \operatorname{Re} v_f(t,x,\theta)} 
+    \leq 0.
+    \deleted{\quad \theta \in \mathbb R.}
 \end{equation}
 %new added
-    Therefore, it is legal to talk about $\psi(x,-v_f(t,x,\theta))$ since in $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
-%end new added
+    Therefore, it is legal to talk about \added{$\psi(x,-U_tf)$}\deleted{$\psi(x,-v_f(t,x,\theta))$} since \deleted{in} $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
     According to Lemma \ref{lem: estimate of exponential remaining}, we have that
@@
 \label{eq: upper bound for vf}
-	|v_f(t,x,\theta)| \leq \mathbb N_x[|e^{i\theta W_t(f)} - 1|]
-	\leq \mathbb N_x[|i\theta W_t(f)|]
-	\leq |\theta| ~(P^\beta_t |f|)(x),
+    |\deleted{U_tf(x)}\added{ v_f(t,x)}| \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
+    \leq \mathbb N_x[|i W_t(f)|]
+    \leq (P^\beta_t |f|)(x),
     \quad \theta \in \mathbb R.
@@
     Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability},
-	$v_f(t,x,\theta)$ is differentiable in $\theta \in \mathbb R$ with
+    \added{$U_t(\theta f)(x)$}\deleted{$v_f(t,x,\theta)$} is differentiable in $\theta \in \mathbb R$ with
 \[
-	\frac{\partial}{\partial \theta} v_f(t,x,\theta)
+    \added{\frac{\partial}{\partial \theta} U_t(\theta f)(x)}
+    \deleted{\frac{\partial}{\partial \theta} v_f(t,x,\theta)}
     = i\mathbb N_x[W_t(f)e^{i\theta W_t(f)}],
@@
 \label{eq: upper bounded for derivative of v(theta)}
-	\sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta} v_f(t,x,\theta)\Big|\leq ( P^\beta_t |f|)(x),
+    \added{\sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|}
+    \deleted{\sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta} v_f(t,x,\theta)\Big|}
+    \leq ( P^\beta_t |f|)(x),
     \quad \theta \in \mathbb R.
 \end{equation}
-    From \eqref{eq: estimate of deriavetive of v(theta)} and the dominate convergence theorem, we can verify that $(\partial/\partial \theta)v_f(t,x,\theta)$ is continuous in $\theta$.
-    %In another words, $\theta \to v_f(t,x,\theta)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
-    In another words, $\theta \mapsto -v_f(t,x,\theta)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
+    From \deleted{\eqref{eq: estimate of deriavetive of v(theta)} and} the dominate convergence theorem, we can verify that \added{$(\partial/\partial \theta)U_tf(x)$}\deleted{$(\partial/\partial \theta)v_f(t,x,\theta)$} is continuous in $\theta$.
+    In another words, \added{$\theta \mapsto -U_t(\theta f)(x)$}\deleted{$\theta \mapsto -v_f(t,x,\theta)$} is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
     According to this and \eqref{eq: path integration representation of h}, we can write
+\deleted{
 \begin{equation}
 \label{eq: path integration representation of psi(v)}
-    %\psi(x,v_f(t,x,\theta_0)) = \int_0^{\theta_0} \psi'(x,v_f(t,x,\theta)) \frac{\partial}{\partial \theta} v_f(t,x,\theta)~d\theta,
-    \psi(x,-v_f(t,x,\theta_0)) = -\int_0^{\theta_0} \psi'(x,-v_f(t,x,\theta)) \frac{\partial}{\partial \theta} v_f(t,x,\theta)~d\theta,
-    \quad \theta_0 \in \mathbb R.
+    \psi(x,-U_tf) = -\int_0^1 \psi'\big(x,-U_t(\theta f)\big) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
+\end{equation}
+}
+\begin{equation}
+%\label{eq: path integration representation of psi(v)}
+    \deleted{\psi(x,-v_f(t,x,\theta_0)) = -\int_0^{\theta_0} \psi'(x,-v_f(t,x,\theta)) \frac{\partial}{\partial \theta} v_f(t,x,\theta)~d\theta,
+    \quad \theta_0 \in \mathbb R.}
 \end{equation}
     Notice that
-\begin{align}
+\deleted{
+\begin{equation}
 \label{eq: upper bound of psi'(v)}
-    %&\big|\psi'\big(x, v_f(t,x,\theta)\big)\big|
-    &\big|\psi'\big(x, -v_f(t,x,\theta)\big)\big|
-    %\\&= \Big| -\beta(x)+ 2\alpha(x) v_f(t-s,x,\theta) + \int_{(0,\infty)} y (e^{-y v_f(t-s,x,\theta)} - 1) \pi(x,dy)\Big|
-    \\&= \Big| -\beta(x)- 2\alpha(x) v_f(t-s,x,\theta) + \int_{(0,\infty)} y (1- e^{y v_f(t-s,x,\theta)} ) \pi(x,dy)\Big|
-    %\\&= \Big| - \beta(x)+ 2\alpha(x)\mathbb N_x(e^{i\theta W_{t}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[e^{i\theta W_{t}(f)} - 1] \pi(x,dy) \Big|
-    \\&= \Big| - \beta(x)- 2\alpha(x)\mathbb N_x(e^{i\theta W_{t}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i\theta X_{t}(f)}] \pi(x,dy) \Big|
-\\ &\leq \|\beta\|_\infty + 2\alpha(x)\mathbb N_x[|\theta| W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}\big[2\wedge\big(|\theta| W_t(|f|)\big)\big] \pi(x,dy)
-\\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty  |\theta|~ (P^\beta_t |f|)(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~ |\theta| ~(P^\beta_t |f|)(x)
-\\ & \qquad + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
-\\ &= c_0 +c_1 |\theta| ~(P^\beta_t |f|)(x),
-\quad \theta \in \mathbb R.
-\end{align}
-    where $c_0,c_1 \geq 0$ are constants not dependent on $f,x,t$ and $\theta$.
+\begin{split}
+    &|\psi'(x, -U_tf)|
+    \\&= \Big| -\beta(x)- 2\alpha(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
+    \\&= \Big| - \beta(x)- 2\alpha(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi(x,dy) \Big|
+\\ &\leq \|\beta\|_\infty + 2\alpha(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
+\\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty  P^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\beta_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
+\\ &=: C_{\ref{eq: upper bound of psi'(v)}.1} + C_{\ref{eq: upper bound of psi'(v)}.2}(P^\beta_t |f|)(x).
+\end{split}
+\end{equation}
+}
+\begin{equation}
+\deleted{ \textbf{The old equation is deleted and marked by \%}}
+\end{equation}
+    where \added{$C_{\ref{eq: upper bound of psi'(v)}.1}, C_{\ref{eq: upper bound of psi'(v)}.2}$}\deleted{$c_0,c_1$} are constants not dependent on \added{$f,x$ and $t$}\deleted{$f,x,t$ and $\theta$}.
     Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have
+\deleted{
 \begin{align}
 \label{eq: upper bound of psi(v)}
-    %\big|\psi\big(x,v_f(t,x,\theta)\big)\big|
-    \big|\psi\big(x,-v_f(t,x,\theta)\big)\big|
+    \big|\psi\big(x,-U_tf\big)\big|
+    \leq C_{\ref{eq: upper bound of psi'(v)}.1} P^\beta_t |f|(x)+C_{\ref{eq: upper bound of psi'(v)}.2} P^\beta_t |f| (x)^2.
+    \\ \deleted{\big|\psi\big(x,-v_f(t,x,\theta)\big)\big|
     \leq c_0|\theta|~(P^\beta_t |f|)(x)+c_1 |\theta|^2 ~(P^\beta_t |f|)(x)^2,
-    \quad \theta \in \mathbb R.
-\end{align}
-
-    Assume that $f \in L_2(\xi) \subset L_1(\xi)$.
+    \quad \theta \in \mathbb R.}
+\end{align}
+}
+
+    Now assume that $f \in L_2(\xi) \subset L_1(\xi)$.
     Then, using Jensen's inequality and the above, we have that
+\deleted{
 \begin{align}
 \label{eq: domination of psi(v)}
-    %&\Pi_x\Big[\int_0^t |\psi(\xi_s,v_f(t-s,\xi_s,\theta))|ds\Big]
-    &\Pi_x\Big[\int_0^t |\psi(\xi_s,-v_f(t-s,\xi_s,\theta))|ds\Big]
-\\&\leq \Pi_x\Big[\int_0^t \big(c_0|\theta| (P_{t-s}^\beta|f|)(\xi_s)+c_1|\theta|^2(P_{t-s}^\beta|f|)(\xi_s)^2\big)ds\Big]
-\\ &\leq \int_0^t \big(c_0|\theta|e^{t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+c_1|\theta|^2e^{2t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
-\\ &\leq \int_0^t (c_0|\theta|e^{t\|\beta\|}\Pi_x [ |f(\xi_{t})|]+c_1|\theta|^2e^{2t\|\beta\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
+    &\Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
+    \\&\leq \Pi_x\Big[\int_0^t \big(C_{\ref{eq: upper bound of psi'(v)}.1} P_{t-s}^\beta|f|(\xi_s)+C_{\ref{eq: upper bound of psi'(v)}.2} P_{t-s}^\beta|f|(\xi_s)^2\big)ds\Big]
+    \\ &\leq \int_0^t \big(C_{\ref{eq: upper bound of psi'(v)}.1} e^{t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_{\ref{eq: upper bound of psi'(v)}.2} e^{2t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
+    \\ &\leq \int_0^t (C_{\ref{eq: upper bound of psi'(v)}.1} e^{t\|\beta\|}\Pi_x [ |f(\xi_{t})|]+C_{\ref{eq: upper bound of psi'(v)}.2}e^{2t\|\beta\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
+\end{align}
+}
+\begin{align}
+    \added{ \textbf{The old equation is deleted and marked by \%}}
+    %\label{eq: domination of psi(v)}
+    %&\Pi_x\Big[\int_0^t |\psi(\xi_s,-v_f(t-s,\xi_s,\theta))|ds\Big]
+    %\\&\leq \Pi_x\Big[\int_0^t \big(c_0|\theta| (P_{t-s}^\beta|f|)(\xi_s)+c_1|\theta|^2(P_{t-s}^\beta|f|)(\xi_s)^2\big)ds\Big]
+    %\\ &\leq \int_0^t \big(c_0|\theta|e^{t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+c_1|\theta|^2e^{2t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
+    %\\ &\leq \int_0^t (c_0|\theta|e^{t\|\beta\|}\Pi_x [ |f(\xi_{t})|]+c_1|\theta|^2e^{2t\|\beta\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
 \end{align}
@@
 \[
-    %\Pi_x\Big[\int_0^t \psi(\xi_s,v_f(t-s,\xi_s,\theta))ds\Big]
-    \Pi_x\Big[\int_0^t \psi(\xi_s,-v_f(t-s,\xi_s,\theta))ds\Big]
+    \added{ \Pi_x\Big[\int_0^t \psi(\xi_s,-U_{t-s}f)ds\Big]}
+    \deleted{\Pi_x\Big[\int_0^t \psi(\xi_s,-v_f(t-s,\xi_s,\theta))ds\Big]}
     \in \mathbb C
@@
 \subsection{}
+    \added{ In this subsection, we recall the generalized spine decomposition theorem for the superprocesses.}
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
@@
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
+\added{
 \begin{prop}
 \label{prop: complex FKPP-equation}
+    Let $f\in L_2(\xi)$. Then for each $t\geq 0$ and $x\in E$,
+\begin{equation}
+\label{eq: complex FKPP-equation}
+    U_tf(x) - \Pi_x \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f\big) ds \Big]
+    \\= i \Pi_x [f(\xi_t)],
+\end{equation}
+and
+\begin{equation}
+\label{eq: complex FKPP-equation with FK-transform}
+    U_tf(x) -  \int_0^t P_{t-s}^{\beta} \psi_0\big(\cdot,-U_sf\big) (x)~ds
+    \\= iP_t^\beta f(x).
+\end{equation}
+\end{prop}
+}
+\deleted{
+\begin{prop}
+%\label{prop: complex FKPP-equation}
     Let $f\in L_2(\xi)$. Then for each $t\geq 0$, $x\in E$ and $\theta \in \mathbb R$,
 \begin{equation}
-\label{eq: complex FKPP-equation}
+%\label{eq: complex FKPP-equation}
     v_f(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s, - v_f(t-s,\xi_s,\theta)\big) ds \Big]
@@
 \end{equation}
-%new
     and
 \begin{equation}
-\label{eq: complex FKPP-equation with FK-transform}
+%\label{eq: complex FKPP-equation with FK-transform}
     v_f(t,x,\theta) -  \int_0^t P_{t-s}^{\beta} \psi_0\big(\cdot,-v_f(s,\cdot,\theta)\big) (x)~ds
@@
 \end{equation}
-%end new
 \end{prop}
+}
 \begin{proof}
     Assume that $f\in b\mathscr B_E$.
-	Set $t>0, r\in [0,t), x\in E, \theta \in \mathbb R$ and $g\in b\mathscr B_E^{++}$.
+    Set $t>0, r\in [0,t), x\in E\deleted{, \theta \in \mathbb R}$ and $g\in b\mathscr B_E^{++}$.
     Denoted by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
@@
 \begin{align}
-&\int_{[0,t]\times \mathbb W}|e^{i\theta w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
-    \leq \int_{[0,t]\times \mathbb W}\big(|\theta w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
-    \\&\leq \int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}\big(|\theta | W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[|\theta| X_{t-s}(|f|)] \pi(\xi_s,dy)
+&\int_{[0,t]\times \mathbb W}|e^{i \deleted{\theta} w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
+    \leq \int_{[0,t]\times \mathbb W}\big(|\deleted{\theta} w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
+    \\&\leq \int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}\big(\deleted{|\theta |} W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[\deleted{|\theta|} X_{t-s}(|f|)] \pi(\xi_s,dy)
     \\&\qquad\qquad+ 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
-     \\&\leq \int_0^t |\theta|(P_{t-s}^\beta |f|)(\xi_s)\Big(2\alpha(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
-    \\&\leq \Big(2\|\alpha\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t |\theta| e^{t\|\beta\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+     \\&\leq \int_0^t \deleted{|\theta|}(P_{t-s}^\beta |f|)(\xi_s)\Big(2\alpha(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+    \\&\leq \Big(2\|\alpha\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t \deleted{|\theta|} e^{t\|\beta\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
     < \infty.
@@
 \begin{align}
-	&\int_{[0,t]\times \mathbb N}(e^{i\theta w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
-	\\&=\int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}(e^{i\theta W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i\theta X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
-	%\\&=\int_0^t \Big( 2\alpha(\xi_s) v_f(t-s,\xi_s,\theta) + \int_{(0,\infty)} y (e^{-y v_f(t-s,\xi_s,\theta)} - 1) \pi(\xi_s,dy) \Big) ds
-    \\&=\int_0^t \Big( 2\alpha(\xi_s) v_f(t-s,\xi_s,\theta) + \int_{(0,\infty)} y (e^{y v_f(t-s,\xi_s,\theta)} - 1) \pi(\xi_s,dy) \Big) ds
-	%\\&= \int_0^t \psi'_0\big(\xi_s, v_f(t-s,\xi_s,\theta)\big)ds.
-    \\&= -\int_0^t \psi'_0 \big(\xi_s, -v_f(t-s,\xi_s,\theta)\big)ds.
+    &\int_{[0,t]\times \mathbb N}(e^{i\deleted{\theta} w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
+    \\&=\int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}(e^{i\deleted{\theta} W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i\deleted{\theta} X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
+    \\&=\int_0^t \Big( 2\alpha(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
+    \\&\deleted{=\int_0^t \Big( 2\alpha(\xi_s) v_f(t-s,\xi_s,\theta) + \int_{(0,\infty)} y (e^{y v_f(t-s,\xi_s,\theta)} - 1) \pi(\xi_s,dy) \Big) ds}
+    \\&= -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
+    \\&\deleted{= -\int_0^t \psi'_0 \big(\xi_s, -v_f(t-s,\xi_s,\theta)\big)ds.}
 \end{align}
@@
 \label{eq: N to Pi}
-	\mathbb N_x^{W_t(g)}[e^{i\theta W_t(f)}]
-	&=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i\theta w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
-	%\\&= \Pi_x^{(g,t)} [e^{\int_0^t \psi'_0(\xi_s, v_f(t-s,\xi_s,\theta))ds}]
-    \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -v_f(t-s,\xi_s,\theta))ds}]
-	%\\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta))ds} ].
-    \\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta))ds} ].
+    \mathbb N_x^{W_t(g)}[e^{i\deleted{\theta} W_t(f)}]
+    &=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i\deleted{\theta} w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
+    \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
+    \\&\deleted{= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -v_f(t-s,\xi_s,\theta))ds}]}
+    \\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
+    \\&\deleted{= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta))ds} ].}
 \end{align}
@@
 \begin{equation}
-    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i\theta X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]}
-    = \mathbf P_{\delta_x}[e^{i\theta X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i\theta X_t(f)}].
+    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i\deleted{\theta} X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]}
+    = \mathbf P_{\delta_x}[e^{i\deleted{\theta} X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i\deleted{\theta} X_t(f)}].
 \end{equation}
@@
 \begin{align}
-	\frac{\mathbf P_{\delta_x}[X_t(f)e^{i\theta X_t(f)}] }{\mathbf P_{\delta_x}[e^{i\theta X_t(f)}]}
-	&= \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i\theta X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i\theta X_t(f)}]
-	%\\& = \Pi_x[ f(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta)) ds}  ].
-    \\& = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta)) ds}  ].
+    \frac{\mathbf P_{\delta_x}[X_t(f)e^{i \deleted{\theta} X_t(f)}] }{\mathbf P_{\delta_x}[e^{i\deleted{\theta} X_t(f)}]}
+    &= \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i\deleted{\theta} X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i\deleted{\theta} X_t(f)}]
+    \\& = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
+    \\& \deleted{= \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta)) ds}  ].}
 \end{align}
@@
 \begin{align}
-	\frac{\partial}{\partial \theta} v_f(t, x, \theta)
-	%= \Pi_x[ if(\xi_t) e^{\int_0^t \psi'(\xi_s, v_f(t-s,\xi_s,\theta)) ds} ].
-    = \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta)) ds} ].
+    \frac{\partial}{\partial \theta} \added{U_t(\theta f)(x)}\deleted{v_f(t, x, \theta) }   
+    = \added{ \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ]}\deleted{ \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta)) ds} ]}.
 \end{align}
     Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
+\deleted{
+\begin{align}
+    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)( x)
+    = \Pi_x[ i f(\xi_{t-r}) e^{-\int_0^{t-r} \psi'(\xi_s, -U_{t-r-s}(\theta f)) ds} ]
+    \\&= \Pi_{r,x}[i f(\xi_t)e^{-\int_0^{t-r} \psi'(\xi_{r+s}, -U_{t-r-s}(\theta f)) ds} ]
+    = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -U_{t-s}(\theta f)) ds} ].
+\end{align}}
+\deleted{
 \begin{align}
     &\frac{\partial}{\partial \theta} v_f(t - r, x, \theta)
-	%= \Pi_x[ if(\xi_{t-r}) e^{\int_0^{t-r} \psi'(\xi_s, v_f(t-r-s,\xi_s,\theta)) ds} ]
-	%\\&= \Pi_{r,x}[if(\xi_t)e^{\int_0^{t-r} \psi'(\xi_{r+s}, v_f(t-r-s,\xi_{r+s},\theta)) ds} ]
-	%= \Pi_{r,x}[if(\xi_t)e^{\int_r^t \psi'(\xi_{s}, v_f(t-s,\xi_{s},\theta)) ds} ].
     = \Pi_x[ if(\xi_{t-r}) e^{-\int_0^{t-r} \psi'(\xi_s, -v_f(t-r-s,\xi_s,\theta)) ds} ]
@@
 \end{align}
-    %From \eqref{eq: upper bound of psi'(v)}, we know that for each fixed $\theta \in \mathbb R$, $(t,x) \mapsto |\psi'(x,v_f(t,x,\theta))|$ is bounded above.
-    From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-v_f(t,x,\theta))|$ is locally bounded (i.e.
+}
+    From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, \added{$(t,x) \mapsto |\psi'(x,-U_tf(x))|$}\deleted{$(t,x) \mapsto |\psi'(x,-v_f(t,x,\theta))|$} is locally bounded (i.e.
 bounded on $[0,T]\times E$ for each $T \geq 0$).
     Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
-\begin{equation}
-	%\frac{\partial}{\partial \theta} v_f(t-r, x, \theta) - \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s, v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
-    \frac{\partial}{\partial \theta} v_f(t-r, x, \theta) + \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s,- v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
+\deleted{
+\[
+    \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]
     = \Pi_{r,x} [i f(\xi_t)],
-\end{equation}
-%new added
+\]}
+\begin{equation}
+    \deleted{\frac{\partial}{\partial \theta} v_f(t-r, x, \theta) + \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s,- v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
+    = \Pi_{r,x} [i f(\xi_t)],}
+\end{equation}
     and
+\deleted{
+\begin{align}
+    \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]
+    = \Pi_{r,x} [i e^{\int_r^t \beta(\xi_s)ds}f(\xi_t)].
+\end{align}}
+\deleted{
 \begin{align}
@@
 \end{align}
-%end added
-	Integrating the aboves with respect to $\theta$, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we have
-\begin{equation}
-	%v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
-    v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
-	\\= i\theta \Pi_{r,x} [f(\xi_t)],
-\end{equation}
-%new added
+}
+    Integrating the aboves with respect to $\theta$ \added{ on [0,1]}, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we have
+\deleted{
+\begin{equation}
+    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-U_{t-s}f\big) ~ds\Big]
+    = i\theta \Pi_{r,x} [f(\xi_t)],
+\end{equation}}
+\begin{equation}
+    \deleted{v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
+    = i\theta \Pi_{r,x} [f(\xi_t)],}
+\end{equation}
     and similarly,
-\begin{equation}
-    v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du} \psi_0\big(\xi_s,-v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
-    \\= i\theta \Pi_{r,x} [e^{\int_r^t\beta(\xi_u)du}f(\xi_t)].
-\end{equation}
-%end added
-    %Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} is true if $f\in b\mathscr B_E$.
+\deleted{
+\begin{equation}
+    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
+    = i\Pi_{r,x} [e^{\int_r^t\beta(\xi_u)du}f(\xi_t)].
+\end{equation}}
+\begin{equation}
+    \deleted{v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du} \psi_0\big(\xi_s,-v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
+    = i\theta \Pi_{r,x} [e^{\int_r^t\beta(\xi_u)du}f(\xi_t)].}
+\end{equation}
     Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} is true if $f\in b\mathscr B_E$.
@@
     From what we have proved, we have
+\deleted{
 \begin{equation}
 \label{eq: complex FKPP-equation for fn}
-    v_{(f_n)}(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta)\big) ~ds\Big]
-    \\= i\theta \Pi_{x} [f_n(\xi_t)].
+    U_tf_n(x) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f_n\big) ~ds\Big]
+    = i \Pi_{x} [f_n(\xi_t)].
+\end{equation}}
+\begin{equation}
+%\label{eq: complex FKPP-equation for fn}
+    \deleted{v_{(f_n)}(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta)\big) ~ds\Big]
+    = i\theta \Pi_{x} [f_n(\xi_t)].}
 \end{equation}
@@
 \item
-    $v_{(f_n)}(t,x,\theta) \xrightarrow[n\to \infty]{} v_f(t,x,\theta)$ due to \eqref{eq: N and characteristic exponent}, dominated convergence theorem and the fact that
+    \added{ $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$}\deleted{ $v_{(f_n)}(t,x,\theta) \xrightarrow[n\to \infty]{} v_f(t,x,\theta)$} due to \eqref{eq: N and characteristic exponent}, dominated convergence theorem and the fact that
 \[
-    |e^{i\theta W_t(f_n)} - 1| \leq |\theta| W_t(|f|);
+    |e^{i\deleted{\theta} W_t(f_n)} - 1| \leq \deleted{|\theta|} W_t(|f|);
     \quad \mathbb N_x[W_t(|f|)] = (P_t^\beta |f|)(x) < \infty.
@@
 \item
-    $\Pi_{x} [\int_0^t \psi(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta))ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,v_{f}(t-s,\xi_s,\theta))ds]$ due to donimated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
+    \added{ $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$}\deleted{ $\Pi_{x} [\int_0^t \psi(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta))ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,v_{f}(t-s,\xi_s,\theta))ds]$} due to donimated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
+\added{
+\begin{align}
+    \big|\psi(\xi_s,- U_{t-s}f_n)\big|
+    \leq C_{\ref{eq: upper bound of psi'(v)}.1} P_{t-s}^\beta|f|(\xi_s)+C_{\ref{eq: upper bound of psi'(v)}.2} P_{t-s}^\beta|f|(\xi_s)^2.
+\end{align}}
+\deleted{
 \begin{align}
@@
 \end{align}
+}
 \end{itemize}

### 2019-01-31 supCLT.tex
supCLT.tex: 1031

@@
   For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C_5>0$ and $\delta_1>0$ such that
-  $$\mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq C_5 e^{-\delta_1 t},\quad t\geq 0.$$
+  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_5 e^{-\delta_1 t},\quad t\geq 0.$$
 \end{lem}
@@
     First, for any $\epsilon>0$, using Markov inequality, we get
-    $$\mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)\leq e^{-\epsilon t}.$$
+    $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq e^{-\epsilon t}.$$
     For another side, using Lemma \ref{lemma2_13}, we have
@@
     We want to show the gap between $m_k[f]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$,
-    $$|m_k[f]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}\left|(-i T^{\alpha}_s f)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
+    $$|m_k[f]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-\alpha s}\left|(-i T^{\alpha}_s f)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
     As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(f)bt}$,  $\kappa(f)=\kappa(\phi)$ and $\kappa(f-\phi)\geq \kappa(f)+1$.
@@
 Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.
+
+{\bf In Milos' paper, he says $e^{\theta^{1+\beta}e^{\alpha}m_k[f]}$ is a characteristic function, but no explanation.}
+\begin{lem}
+For any $x,y\in \mathbb{C}$, $|e^x-e^y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|$.
+\begin{proof}
+let $z=Re(y)+Im(x)$,
+\begin{align}\label{estim}
+    |e^x-e^y|\leq|e^x-e^z|+|e^z-e^y|\leq |e^{Re(x)}-e^{Re(y)}|+e^{Re(y)}|x-y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|.
+\end{align}
+\end{proof}
+\end{lem}
 \begin{lem}\label{lemma31}
+
  Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(R^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
@@
  \end{lem}
-\begin{proof}
-Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and Let $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$, by Lemma \ref{lemma28}, there exists $\delta_1>0$ and $C_5>0$ such that
-    \begin{align}
-    \label{eq:31step0}
-        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right|
-        \\ &\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1}(\epsilon_0))
-        \leq 2C_5e^{-\delta_1(t-k-1)},\quad k\in \mathbb{N}, t>k.\label{lemma33q}
-    \end{align}
-
-    Let $v_{f_k}(x,\theta)=v_{f_k}(1,x,\theta),\tilde{v}_{f_k}(x,\theta)=\tilde{v}_{f_k}(1,x,\theta)$ for short. For any $k\in\mathbb{N}$ and $t>k$, we have
-    \begin{align*}
-        &\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})]\\
-        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
-        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\nu}\left[\exp\left(i\frac{\theta}{F_k(v)}(\langle T_k^{\alpha}f,X_1\rangle-\langle T_{k+1}^{\alpha}f,\nu\rangle)\right)\right]_{\nu=X_{t-k-1}}\right]\\
-        &=\mathbb{\tilde{P}}_{\mu}\left[\exp\left(\langle v_{f_k}(\cdot,\frac{\theta}{F_k(X_{t-k-1})}),X_{t-k-1}\rangle-i\frac{\theta}{F_k(X_{t-k-1})}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\right)\right].
-    \end{align*}
-
-    Next, our aim now is showing that the on the event $\mathcal{A}_{t-k-1}(\epsilon_0)$, the characteristic functions of random variables on both sides in \eqref{limitdistribution1} are much the same.
-Let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$.
-Then
-    \begin{align*}
-        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right|\\
-        &=\bigg|\big(\mathbb{\tilde{P}}_{\mu}\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\\
-        &-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}}(\epsilon_0)\bigg|\\
-        &\leq \mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
-        &+\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right].
-    \end{align*}
-    The first equation holds because that $v_{f_k}-i\theta T_1^{\alpha}f_k=v_{f_k}-\tilde{v}_{f_k}+Z_{f_k}$. the inequality holds by triangular inequality.
-
+
+ \begin{proof}
+     Let $v_{f_k}(x,\theta)=v_{f_k}(1,x,\theta),\tilde{v}_{f_k}(x,\theta)=\tilde{v}_{f_k}(1,x,\theta)$ and $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$.
+For any $k\in\mathbb{N}$ and $t>k$, we have
+         \begin{align}
+        &\mathbb{P}_{\mu}[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})]\\
+        &=\mathbb{P}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
+        &=\mathbb{P}_{\mu}\left[\exp\left(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\right)\right].\\
+        \label{condition mean}
+        &=\mathbb{P}_{\mu}\left[\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\right]\\
+       \end{align}
+       To get the conclusion of Lemma \ref{lemma31}, it suffices to show that
+       \begin{align}
+           \mathbb{P}_{\mu}\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\right)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(\theta^{1+\beta}e^{\alpha}m_k[f]).
+       \end{align}
+       Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and Let $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
+        Recall that $\mathcal{A}_t(\epsilon_0)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\}$.
+        \begin{align}
+        &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c}\right]\right| \\
+        &\leq\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\right|\\
+        &+\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right|
+        \end{align}
+         Let $c=|\theta^{1+\beta}e^{\alpha}m_k[f]|$. By lemma \ref{lemm28}, there exists $\delta_1>0$ and $C_5>0$ such that
+       \begin{align}
+            &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right| \\
+            &\leq \mathbb{P}_{\mu}(D^c)\mathbb{\tilde{P}}_{\mu}(\mathcal{A}_{t-k-1})\leq (1+e^c)C_5\mathbb{P}_{\mu}(D^c)e^{-\delta_1(t-k-1)}.
+       \end{align}
+       On the other hand, by formula \eqref{condition mean} and Lemma \ref{estim}
+    \begin{align}
+        &\left|\mathbb{P}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right|\\
+        &\leq e^c\mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
+        \label{ineqinlem31}
+        &+e^c\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right].
+    \end{align}
 Step 1.  We will show that for each $\mu \in\mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_6>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k$,
@@
     \label{lemma31q}
-        \mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{g_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
+        \mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
     \end{align}
@@
     \begin{align*}
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
+        &\mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
         \\ &\leq \left(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\right)^{1+2\beta}\mathbb{\tilde{P}}_{\mu}\langle R^f_1,X_{t-k-1}\rangle\\
@@
  Step 2.
-Let $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.We will show that there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
+Let $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.to prove inequality \eqref{ineqinlem31}, We will first show that there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
  \begin{align}
@@
 \end{align}
-
 Step 3, for any $\mu \in \mathcal{M}(\mathbb{R}^d)$ and $\theta\in \mathbb{R}$, we will show that there exists $C_7>0$ such that
@@
 \label{eq:31step3}
-    \mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_7|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)},\quad k\in \mathbb{N}, t\geq k.
+    &\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
+    &\leq C_7|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)},\quad k\in \mathbb{N}, t\geq k.
 \end{align}
@@
 \begin{align}
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
-    &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{\tilde{P}}_{\mu}\left[\left|\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{f_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\nonumber\\
+        &\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
+    &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{P}_{\mu}\left[\left|\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{f_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\nonumber\\
     &\leq |\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon_0)(t-k-1)}\mathbb{\tilde{P}}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
@@
 \begin{align}
-    &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right]\leq \|\langle h_k, X_{t-k-1}\rangle\|_{\mathbb{P}_{\mu,1+\gamma_0}}\\
+    &\mathbb{P}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right]\leq \|\langle h_k, X_{t-k-1}\rangle\|_{\mathbb{P}_{\mu,1+\gamma_0}}\\
     &\leq C_8 e^{(\alpha-\kappa(f)b)(1+\beta)k}
@@
 \begin{align}
-    &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
+    &\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
     \\ & \leq C_8 |\theta|^{1+\beta}e^{(\alpha\beta-\kappa(f)b(1+\beta))k}e^{-(p-\epsilon_0)(t-k-1)} \leq C_8 |\theta|^{1+\beta}e^{-\frac{p}{2}(t-k-1)}.

### 2019-01-31 supCLT.tex
supCLT.tex: 1101

@@
 \end{proof}
+Define $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\},\quad \epsilon,t>0$.
 \begin{lem}\label{lemma28}
-  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C_5>0$ and $\delta_1>0$ such that
-  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_5 e^{-\delta_1 t},\quad t\geq 0.$$
+  For any $\epsilon>0$, $t>0$ and $\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_5>0$ and $\delta_1>0$ such that
+  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_5 e^{-\delta_1 t}.$$
 \end{lem}
@@
     First, for any $\epsilon>0$, using Markov inequality, we get
-    $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq e^{-\epsilon t}.$$
+    $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.$$
     For another side, using Lemma \ref{lemma2_13}, we have
-    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq C_4 e^{-\beta\epsilon t}, $$
+    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_4 e^{-\beta\epsilon t}, $$
 Therefore,
 \begin{align*}
-    \mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq \mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq(C_4+1)e^{-\beta \epsilon t }
+    \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq(C_4+\frac{1}{\mathbb{P}_{\mu}(D^c)})e^{-\beta \epsilon t }
 \end{align*}
@@
  Let
- \begin{align}
+ \begin{align}\label{parameter_mk}
       m_k[f]:=e^{-\alpha(k+1)}\langle Z_{f_k},\varphi\rangle.
@@
 {\bf In Milos' paper, he says $e^{\theta^{1+\beta}e^{\alpha}m_k[f]}$ is a characteristic function, but no explanation.}
-\begin{lem}
+\begin{lem}\label{lemma31}
 For any $x,y\in \mathbb{C}$, $|e^x-e^y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|$.
-\begin{proof}
-let $z=Re(y)+Im(x)$,
+\end{lem}
+\begin{proof}
+let $z=Re(y)+iIm(x)$,
 \begin{align}\label{estim}
@@
 \end{proof}
+\begin{lem}\label{lemma32}
+Recall $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\},~\epsilon,t>0$, then for any $t>0$, we have
+\begin{align}
+    \lim_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=D^c
+\end{align}
 \end{lem}
-\begin{lem}\label{lemma31}
-
- Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(R^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+\begin{proof}
+    We just need to prove 
+    \begin{align}
+        D^c \subset \liminf_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c.
+    \end{align}
+    for any $\omega\in D$, there exists $S>0$, such that $\|X_t(\omega)\|=0,~t\geq T$.
+Thus $\omega \notin \cup_{t\geq S}\mathcal{A}_t(\epsilon)$ and $\omega\notin  \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon):=\cap_{S\geq 0}\cup_{t\geq S}\mathcal{A}_t(\epsilon)$ imply that $\limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c$.
+
+    For any $\omega \in D^c$, there exists $\delta>0$ such that $W_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$,\deleted{$~\mathbb{P}_{\mu}$-a.s}.
+As $W_t$ converges to $W_{\infty}$ $\mathbb{P}_{\mu}$-a.s, there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq W_t(\omega)\leq 2\delta,$\deleted{$~\mathbb{P}_{\mu}$-a.s}.
+Taking $S_2>0$ such that for any $t>S_2$, $\|\mu\|e^{-\epsilon t}<\frac{\delta}{2}$ and $\|\mu\|e^{-\epsilon t}>2\delta$, then $\omega\in \mathcal{A}_t(\epsilon),~t>S:=\max\{S_1,S_2\}$ implies $\omega \in \liminf_{t\rightarrow \infty}\mathcal{A}_t(\epsilon):=\cup_{S>0}\cap_{t\geq S}\mathcal{A}_t(\epsilon)$.
+\end{proof}
+
+\begin{lem}
+For any $f\in \mathcal{P}$ and $k\in \mathbb{N}$, let $m_k[f]$ be the parameter defined in \eqref{parameter_mk}, then the function $\theta\mapsto \exp(\theta^{1+\beta}e^{\alpha}m_k[f])$ defined on $\theta\in(0,\infty)$ is a characteristic function of some $(1+\beta)$-stable random variable.
+\end{lem}
+\begin{proof}
+    Let $J=\langle\int_0^1 T_{1-s}^{\alpha}(-T^{\alpha}_s f)^{1+\beta}(\cdot)ds,\varphi\rangle$, then 
+    \begin{align}
+        m_k[f]=J e^{-\alpha(k+1)}\cdot i^{1+\beta}=J e^{-\alpha(k+1)}\cos\frac{(1+\beta)\pi}{2}\big(1+i\tan\frac{(1+\beta)\pi}{2}\big).
+    \end{align}
+Thus
+\begin{align}
+    \exp(\theta^{1+\beta}e^{\alpha}m_k[f])=\exp\big(J e^{-\alpha k}\cos\frac{(1+\beta)\pi}{2}\cdot\theta^{1+\beta}\big(1+i\tan\frac{(1+\beta)\pi}{2}\big)\big)
+\end{align}
+B \cite[Theorem 14.15]{Sato1990Levy}, we get the result.
+\end{proof}
+{\bf Jianjie: I think the proof has some problem, as we are not sure $J$ is negative or not,}
+\begin{lem}\label{lemma33}
+
+ Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
  \begin{align}
@@
          \begin{align}
-        &\mathbb{P}_{\mu}[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})]\\
-        &=\mathbb{P}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
-        &=\mathbb{P}_{\mu}\left[\exp\left(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\right)\right].\\
+        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})\big|\mathcal{F}_{t-k-1}\big]\\
+        &=\exp\big(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
         \label{condition mean}
-        &=\mathbb{P}_{\mu}\left[\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\right]\\
-       \end{align}
-       To get the conclusion of Lemma \ref{lemma31}, it suffices to show that
-       \begin{align}
-           \mathbb{P}_{\mu}\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\right)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(\theta^{1+\beta}e^{\alpha}m_k[f]).
-       \end{align}
-       Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and Let $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
-        Recall that $\mathcal{A}_t(\epsilon_0)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\}$.
+        &=\exp\big(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle\big)\\
+       \end{align}
+         Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
+       To get the conclusion of Lemma \ref{lemma33}, it suffices to show that
+       \begin{align}
+           \mathbb{P}_{\mu}\Big(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\Big)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(\theta^{1+\beta}e^{\alpha}m_k[f]).
+       \end{align}
+\deleted{
         \begin{align}
@@
        \end{align}
-       On the other hand, by formula \eqref{condition mean} and Lemma \ref{estim}
-    \begin{align}
-        &\left|\mathbb{P}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right|\\
-        &\leq e^c\mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
+       }
+     Equivalently, by Lemma \ref{lemma32}， we just need to prove
+     \begin{align}
+        \Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\xrightarrow{t\rightarrow\infty} 0.
+    \end{align}
+
+      \deleted{ On the other hand, by formula \eqref{condition mean} and Lemma \ref{estim}}
+      By formula \eqref{condition mean} and lemma \ref{lemma31},
+    \begin{align}
+        &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
+        &=\Big|\mathbb{P}_{\mu}\Big[\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathcal{F}_{t-k-1}\Big)\Big]\Big|\\
+        &\leq e^c\mathbb{P}_{\mu}\big[\big|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
         \label{ineqinlem31}
-        &+e^c\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right].
+        &+e^c\mathbb{P}_{\mu}\big[\big|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big].
     \end{align}
@@
     \label{lemma31q}
-        \mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
+        \mathbb{P}_{\mu}\big[\big|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
     \end{align}
@@
 
-For any $\theta\in \mathbb{R}$, $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}$, we have
-    \begin{align*}
-        &\mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
-        \\ &\leq \left(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\right)^{1+2\beta}\mathbb{\tilde{P}}_{\mu}\langle R^f_1,X_{t-k-1}\rangle\\
+For any $\theta\in \mathbb{R}$, $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}(\epsilon_0)$, we have
+    \begin{align*}
+        &\mathbb{P}_{\mu}\big[\big|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]
+        \\ &\leq \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+2\beta}\mathbb{\tilde{P}}_{\mu}\langle R^f_1,X_{t-k-1}\rangle\\
         &\leq\frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle R_6,\mu\rangle|\theta|^{1+2\beta}e^{\alpha(t-k-1)} e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}\\
@@
  Let $\tilde{f}=T_1^{\alpha}f$, then $\kappa(\tilde{f})=\kappa(f)$.
-It is easy to show that $\tilde{f}\in C^{\infty}$ and $\tilde{f}^{(p)}\in\mathcal{P},~p\in\mathbb{Z}_+^d$, thus by the inequality \eqref{eq:semigroupineq} and the fact $\kappa\left(\frac{\partial \tilde{f}}{\partial x_i}\right)\geq \kappa(\tilde{f})-1$, see \cite[Lemma 2.3]{RSZ}, we get there exists $\tilde{R}_7\in \mathcal{P}$ such that for each $i=1,...,d$
+It is easy to show that $\tilde{f}\in C^{\infty}$ and $\tilde{f}^{(p)}\in\mathcal{P},~p\in\mathbb{Z}_+^d$, thus by the inequality \eqref{eq:semigroupineq} and the fact $\kappa\big(\frac{\partial \tilde{f}}{\partial x_i}\big)\geq \kappa(\tilde{f})-1$, see \cite[Lemma 2.3]{RSZ}, we get there exists $\tilde{R}_7\in \mathcal{P}$ such that for each $i=1,...,d$
  \begin{align}
  \label{ineq-temp}
-     \left|T_t\big(\frac{\partial\tilde{f}}{\partial x_i}\big)(x)\right|\leq e^{(\alpha-(\kappa(f)-1)b)t}\tilde{R}_7(x), \quad x\in \mathbb {R}^d, t\geq 0.
+     \Big|T_t\big(\frac{\partial\tilde{f}}{\partial x_i}\big)(x)\Big|\leq e^{(\alpha-(\kappa(f)-1)b)t}\tilde{R}_7(x), \quad x\in \mathbb {R}^d, t\geq 0.
  \end{align}
@@
  \begin{align}
-     \frac{\partial h_k}{\partial x_i}(x)=\frac{\partial Z_{g_k}}{\partial x_i}(x)=\int_0^1 T^{\alpha}_{1-s}\left(\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha} \tilde{f})^{1+\beta}\right)(x)~ds.
+     \frac{\partial h_k}{\partial x_i}(x)=\frac{\partial Z_{g_k}}{\partial x_i}(x)=\int_0^1 T^{\alpha}_{1-s}\Big(\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha} \tilde{f})^{1+\beta}\Big)(x)~ds.
  \end{align}
@@
       \begin{align}
-        \left|\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha}\tilde{f})^{\beta}\right|&=\left|(1+\beta)(-i T_{s+k-1}^{\alpha}\tilde{f})^{\beta}(-i e^{-b(s+k-1)}T_{s+k-1}^{\alpha}\left(\frac{\partial \tilde{f}}{\partial x_i}\right))\right|\\
+        \Big|\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha}\tilde{f})^{\beta}\Big|&=\Big|(1+\beta)(-i T_{s+k-1}^{\alpha}\tilde{f})^{\beta}(-i e^{-b(s+k-1)}T_{s+k-1}^{\alpha}\big(\frac{\partial \tilde{f}}{\partial x_i}\big))\Big|\\
         &\leq e^{(\alpha-\kappa(\tilde{f})b)(s+k-1)(1+\beta)}\cdot (1+\beta)e^{(\alpha-\kappa(f)b)\beta}R_0^{\beta}(x)\tilde{R}_7(x).
@@
 \label{eq:31temp }
-    \left|\frac{\partial}{\partial x_i}h_k(x)\right|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_8(x),\quad x\in \mathbb{R}^d, k\in \mathbb{N}.
+    \Big|\frac{\partial}{\partial x_i}h_k(x)\Big|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_8(x),\quad x\in \mathbb{R}^d, k\in \mathbb{N}.
 \end{align}
@@
 \label{eq:31step3}
-    &\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
+    &\mathbb{P}_{\mu}\big[\big|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
     &\leq C_7|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)},\quad k\in \mathbb{N}, t\geq k.
@@
     &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{P}_{\mu}\left[\left|\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{f_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\nonumber\\
-    &\leq |\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon_0)(t-k-1)}\mathbb{\tilde{P}}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
+    &\leq |\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon_0)(t-k-1)}\mathbb{P}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
 \end{align}
@@
 
-At last, combine \eqref{eq:31step0},\eqref{lemma31q} and \eqref{eq:31step3} and let $t\rightarrow\infty$, we get the result.
+At last, combine \eqref{lemma31q} and \eqref{eq:31step3} and let $t\rightarrow\infty$, we get the result.
 \end{proof}
 \begin{cor}\label{corollary31}
-Let$f\in \mathcal{P}$ and $\Theta>0$, assume that $\alpha\beta\leq\kappa(f)b(1+\beta)$.
+Let $f\in \mathcal{P}$ and $\Theta>0$, assume that $\alpha\beta\leq\kappa(f)b(1+\beta)$.
 There exists $C_9,\delta_2>0$ such that for any $n \in \{0,...,t\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
@@
     $$\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)=\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle).$$
-    In Lemma \ref{lemma31}, we have proved that (see \eqref{lemma31q} and \eqref{eq:31step3}), if $|\theta|\leq\Theta$ and $k\in\{0,...,t\}$,
-    \begin{align*}
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_{6}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_7|\Theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)}.
+ By \eqref{lemma31q} and \eqref{eq:31step3}, we easily get, if $|\theta|\leq\Theta$ and $k\in\{0,...,t\}$,
+    \begin{align*}
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq \frac{C_{6}}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}\\
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq \frac{C_{7}}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)}.
     \end{align*}
@@
 \begin{align*}
-    \mathcal{B}_{t-k-1}:=\left\{\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq C_6|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{4(1+\beta)}(t-k-1)}\right\}.
+    \mathcal{B}_{t-k-1}:=\left\{\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq\frac{C_{6}}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{4(1+\beta)}(t-k-1)}\right\}.
 \end{align*}
@@
 \begin{align*}
-    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq C_7|\Theta|^{1+\beta} e^{-\frac{p}{4}(t-k-1)}\right\},
+    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq \frac{C_{7}}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+\beta} e^{-\frac{p}{4}(t-k-1)}\right\},
 \end{align*}
@@
    +\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\\
-   &\leq (C_6|\Theta|^{1+2\beta}+C_7|\Theta|^{1+\beta}) e^{-\min\{\frac{\alpha\beta}{4(1+\beta)},\frac{p}{4}\}(t-k-1)}.
+   &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}(C_6|\Theta|^{1+2\beta}+C_7|\Theta|^{1+\beta}) e^{-\min\{\frac{\alpha\beta}{4(1+\beta)},\frac{p}{4}\}(t-k-1)}.
 \end{align*}
@@
     When $t$ is large enough, $t^{-\frac{1}{1+\beta}}\leq 1$. What's more, by Corollary \ref{cor27}
-    $$\mathbb{\tilde{P}}_{\mu}|M_k^t[f]|\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k},$$
+    $$\mathbb{\tilde{P}}_{\mu}|M_k^t[f]|\leq \frac{\mathbb{P}_{\mu}(|M_k^t[f]|)}{\mathbb{P}(D^c)}\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k},$$
 for some constant $C \geq 0$ and any $0<\gamma<\beta$.

### 2019-01-31 supCLT.tex
supCLT.tex: 1108

@@
 \subsection{Model}
-    Let $d \in \mathbb N:= \{1,2,\dots\}$.
-    \deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
-    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
+    Let $d \in \mathbb N:= \{1,2,\dots\}$ and
+    %\deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
+    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
 \begin{equation}
@@
         = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
-        \quad \added{ x\in \mathbb R^d,}
+        \quad  x\in \mathbb R^d,
         f \in C^2(\mathbb{R}^d),
@@
         where $\alpha > 0$ and $\beta \in (0,1) $.
-    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of \added{ all} finite measures on $\mathbb{R}^d$.
+    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite measures on $\mathbb{R}^d$.
     For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
@@
     Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
-\added{
     According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
-}\deleted{
-    The fact $\psi(\infty)=\infty$ and $\int^{\infty}\frac{1}{\psi(z)}~dz<\infty$ implies that the probability of extinguish event $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ is contained in $(0,1)$, which means that our superprocess is non-persistent.
-    In fact,
-}
-\begin{equation}
-\added{
+\begin{equation}
     \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
     = e^{-\alpha^* \|\mu\|},
-}\deleted{
-    \mathbb{P}_{\mu}(D)
-    = \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
-    = e^{-\alpha^* \|\mu\|},
-}
 \end{equation}
     where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
-\deleted{
-    See {\cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations} }for a example.
-    }
 
@@
     :=
-\added{ e^{\alpha t} T_t f(x) =}
+    e^{\alpha t} T_t f(x) =
     \Pi_x [e^{\alpha t}f(\xi_t)],
@@
 \end{equation}
-\deleted{Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.}
 
@@
 \end{equation}
-    Let $L^2(\varphi):= \left\{ h \added{ \in \mathscr B(\mathbb R^d)}: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
+    Let $L^2(\varphi):= \left\{ h  \in \mathscr B(\mathbb R^d): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
 \begin{equation}
@@
 \end{equation}
-    \added{ Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.}
-    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p! \added{ :}= \prod_{k= 1}^d p_k !$ and $\partial x^p \added{ :}= \prod_{k = 1}^d\partial x_k^{p_k}$.
+     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.
+    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
     The Hermite polynomials are defined by
@@
 \end{equation}
-    It is known that \added{ $(T_t)$ is a strong continuous semigroup }\deleted{ the generator $L$ of OU process $\xi$ can be viewed as an operator} on $L^2(\varphi)$ \added{ and its generator $L$ has }\deleted{ with} eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
-    For each $k \in \mathbb N_0$, \added{denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then}\deleted{the eigenspace $A_k$ corresponding to eigenvalue $-bk$ is}
+    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
+    For each $k \in \mathbb N_0$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
 \begin{equation}
@@
 \end{equation}
-    Moreover, \deleted{it is known that} $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
+    Moreover, $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
     That is, for each $f\in L^2(\varphi)$,
@@
 \begin{equation}\label{order}
-    \kappa(f)
-    :=\inf \left \{k\geq 0: \exists ~ p\in \added{ \mathbb N_0^d }\deleted{ \mathbb{Z}_+^d},{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
+    \added{\kappa_f}\deleted{\kappa(f)}
+    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb N_0^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
 \end{equation}
     the order of function $f$ in $L^2(\varphi)$.
-    \added{ Note that }\deleted{ Then} $ \kappa(f)\geq 0$.
+    Note that $ \kappa_f\geq 0$.
     In particular, the order of any constant function is zero.
 
-\added{
 \subsection{}
@@
     Then it is clear that $A_\alpha A_\beta$ is an $(\alpha\beta)$-scalable operator.
-}
-\added{
     Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ defined by
-}
-\deleted{
-    In this paper, we consider the class of functions of ploynomial growth $\mathcal{P}$ defined by
-}
 \begin{equation}
     \mathcal{P}
-    :=\big \{f\in \added{ \mathscr B}\deleted{ \mathcal{B}}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
-\end{equation}
-    It is \added{clear} \deleted{easy to see} that $\mathcal{P} \subset L^2(\varphi)$.
+    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+\end{equation}
+    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
     \added{ For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.}
@@
 \subsection{}
-    \added{Recall $\Gamma$} \deleted{Let} the Gamma function \deleted{$\Gamma$ be} defined by
+    Recall $\Gamma$ the Gamma function be defined by
 \begin{equation}
@@
 \end{align}
-    \added{ It is known that }\deleted{ Then it is elementary to verify that}
+    It is known that
 \begin{equation}
@@
 \item
-    is continuous \added{ on }\deleted{ in} $\mathbb C_+\added{ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}}$;
+    is continuous on $\mathbb C_+ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}$;
 \item
-    is holomorphic \added{ on }\deleted{ in} $\mathbb C_+^0\added{ := \{x+iy:x\in (0,\infty), y\in \mathbb R\}}$.
+    is holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$.
 \end{itemize}
@@
 \item
-    is continuous \added{ on }\deleted{ in} $\mathbb C_+$;
+    is continuous on $\mathbb C_+$;
 \item
-    is holomorphic \added{ on }\deleted{ in} $\mathbb C_+^0$.
+    is holomorphic on $\mathbb C_+^0$.
 \end{itemize}
-    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path \added{ $\gamma:[0,1]\to \mathbb C_+$ }\deleted{ $\gamma:[0,1]\mapsto \mathbb C_+$},
+    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\to \mathbb C_+$ ,
 \begin{align}
@@
 \label{lem: Lip of power function}
-    There is a constant $\added{ C_{\ref{lem: Lip of power function}} } \deleted{ C_0} > 0$ such that for any $z_0,z_1 \in \mathbb C_+$,
+    There is a constant $C_{\ref{lem: Lip of power function}}$ such that for any $z_0,z_1 \in \mathbb C_+$,
 \begin{equation}
@@
     |z_0^{1+\beta} - z_1^{1+\beta}|
-    \leq \added{ C_{\ref{lem: Lip of power function}} }\deleted{ C_0}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
-\end{equation}
-\added{
+    \leq C_{\ref{lem: Lip of power function}}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
+\end{equation}
     In particular, for each $z\in \mathbb C$, we have
@@
 $
-}
+
 \end{lem}
@@
     Let $X$ be the super OU-process discussed in the previous subsections.
-    Its branching mechanism $\psi$ can be extended \added{ on $\mathbb C_+$ by }\deleted{ in the following way: } $\psi(z) := -\alpha z + z^{1+\beta}$ for \added{ each} $z\in \mathbb C_+$.
-    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0\deleted{:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}}$ with derivative
+    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
+    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
 \begin{equation}
@@
     Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
-\added{
     For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in E$, define $\Psi_0f(x) := \psi_0(x,f(x))$ and $\Psi'_0 f(x) := \psi'_0(x,f(x))$.
-}
-    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, \added{define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$} \deleted{ denote by $v_f(t,x,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]$ the characteristic exponent of $\{\langle f,X_t \rangle; \mathbb P_{\delta_x}\}$}
-    (\added{ See }\deleted{ For percise definition, see} the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
-    From \eqref{eq: -v has positive real part}, we know that \added{$-U_tf(x)$} \deleted{$- v_f(t,x,\theta)$} taks values in $\mathbb C_+$.
-    Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
-\deleted{
-\begin{align}
-\label{charequation}
-    v_f(t,x,\theta)-\int_0^t T_{t-s} \psi \big(-v_f(s,\cdot,\theta)\big)(x)ds
-    =i\theta T_tf(x),
-    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
-\end{align}
-    and
-}
-\added{
+    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
+    (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
+    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ taks values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
 \begin{align}
@@
 \end{align}
-}
-\deleted{
-\begin{align}
-\label{eq:chareq2}
-    v_f(t,x,\theta)-\int_0^t T^{\alpha}_{t-s} \psi_0(-v_f(s,\cdot,\theta))(x)ds=i\theta T^{\alpha}_t f(x),
-    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
-\end{align}
-}
+
 %new added
@@
     In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
-    \deleted{In this section, we assume a function $g$ satisfying that there exists $C_h, \kappa>0$ and $R^g_0\in \mathcal{P}$
-    such that}
-\deleted{\begin{align}\label{eq:gcontrol1}
-    |T_tg|(x)
-    \leq C_g e^{-\kappa bt}R^g_0(x),
-    \quad t\geq 0,x\in \mathbb{R}^d.
-\end{align}}
-\deleted{Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R^g \in \mathcal P$ such that}
-\deleted{\begin{align}\label{eq:gcontrol}
-    T_s|T_t g|(x)
-    \leq C_g e^{-\kappa bt} R^g(x),
-    \quad t\geq 0,s\geq 0,x\in \mathbb{R}^d.
-\end{align}}
-\added{
+
     Consider an incremental decomposition of $\langle g,X_t \rangle$.
-    For each $t\geq 0$, denote by $\{\mathcal{F}_t:t\geq 0\}$ the natrual filtration of $X$.
+    For each $t\geq 0$, denote by $\{\mathscr{F}_t:t\geq 0\}$ the natrual filtration of $X$.
     For each $g\in \mathcal P$ and $0 \leq a \leq b \leq t <\infty$, define random variable
-\[
-    M_{r,s}\langle g,X_t\rangle
-    := \mathbb P[\langle g,X_t\rangle|\mathscr F_s] - \mathbb P[\langle g,X_t\rangle|\mathscr F_r]
-    \langle T_{t-b}^\alpha g, X_b\rangle - \langle T_{t-a}^\alpha g, X_a\rangle.
-\]
+
+\[
+   \deleted{ M_{r,s}\langle g,X_t\rangle} \added{M_g^t(a,b)}
+    := \mathbb P_{\mu}[\langle g,X_t\rangle|\mathscr F_b] - \mathbb P_{\mu}[\langle g,X_t\rangle|\mathscr F_a]
+    =\langle T_{t-b}^\alpha g, X_b\rangle - \langle T_{t-a}^\alpha g, X_a\rangle.
+\]
+
     Thus, we have
@@
 \end{align}
-}
-\deleted{
-    Consider an incremental decomposition of $\langle g,X_t \rangle$.
-    For each $t\geq 0$, denote by $\{\mathcal{F}_t:t\geq 0\}$ the natrual filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$.
-    For each $f\in\mathcal{P}$ and $k \in \mathbb{N}$, let $f_k=T^{\alpha}_k f$.
-    According to \eqref{eq:meanformula}, write}
-\begin{align*}
-    \deleted{M_k^t[g]}:&
-    \deleted{=\langle g_k, X_{t-k}\rangle-\mathbb{P}_{\mu}(\langle g_k,X_{t-k}\rangle|\mathcal{F}_{t-k-1})}\\
-    &\deleted{=\langle g_k, X_{t-k}\rangle-\langle T_1^{\alpha}g_{k},X_{t-k-1}\rangle}\\
-    &\deleted{=\langle g_k, X_{t-k}\rangle-\langle g_{k+1},X_{t-k-1}\rangle, \quad t\geq k+1.}
-\end{align*}
-    \deleted{What's more, we denote $M_{\lfloor t\rfloor}^t[g]:=\langle g_{\lfloor t \rfloor},X_{t-\lfloor t\rfloor}\rangle-\langle g_t, \mu\rangle$ and $M_t^t[g]:=\langle g_t,\mu\rangle$ under $\mathbb P_\mu$, where $\mu $ is the initial configuration.
-Thus}
-\begin{equation}\label{decomposition}
-    \deleted{\langle g,X_t\rangle-M_t^t[g]
-    =\sum_{k=0}^{\lfloor t\rfloor}M_k^t[g]
-    , \quad t \geq 0.}
-\end{equation}
-
-\added{
+
 \subsection{}
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R^+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
-    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Tf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
+    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
     We say $R$ is a monotonic operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for each $f, g \in \mathcal P^+$ with $f\leq g$.
-    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P$.
-    We say an operator $A$ is $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^+$ if $A: \mathcal D \to \mathcal P^*$ and there exits a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
+    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P^+$.
+    We say an operator $A$ is $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and \added{$\mathcal D \subset \mathcal P^*$}\deleted{$\mathcal D \subset \mathcal P$} if $A: \mathcal D \to \mathcal P^*$ and there exits a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
     In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
-    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$ if there exits a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(M, S)$ on $\mathcal D$ for each $s\in \Lambda$.
-}
+    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$ if there exits a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(\added{R}\deleted{M}, S)$ on $\mathcal D$ for each $s\in \Lambda$.
+
+    The first reason for considering $\gamma$-controllable operators is the following:
 \added{
-    The first reason for considering $\gamma$-controllable operators is the following:
 \begin{lem}
@@
 }
-\added{
     For two operators $A$ and $B$ defined on same domain $\mathcal D\subset \mathcal P^*$, write $(A\times B)f (x):= Af(x) \times Bf(x)$.
@@
 \item[(2)]
-    Suppose that operators $(B_\theta)_{\theta\in \Theta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$.
+    Suppose that operators $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$.
     Also suppose that for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
-    Then operators $(B_\theta A_\lambda)_{\theta\in \Theta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
+    Then operators $(B_\delta A_\lambda)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
 \item[(3)]
-    Suppose that operators $(B_\theta)_{\theta \in \Theta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta\in \mathbb R$.
-    Then operators $(B_\theta\times A_\lambda)_{\theta \in \Theta, \lambda \in \Lambda}$ are uniformly $(\gamma+\beta)$-controllable.
+    Suppose that operators $(B_\delta)_{\delta \in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta\in \mathbb R$.
+    Then operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ are uniformly $(\gamma+\beta)$-controllable.
 \item[(4)]
@@
 \end{lem}
-\begin{proof}
-    ......
+\added{
+\begin{proof}
+    Proof of (1): Let $(R,S)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$.
+For each $f \in \mathcal{D}$ and $\mu$ the probability measure on $(\Lambda, \mathscr F)$.
+\[
+   |A_{\mu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\mu(d\lambda) \leq \int_{\Lambda}R|f|(x)\mu(d\lambda) \leq R|f|(x).
+\]
+
+   Proof of (2): Let $(R_A, S_A)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$ and $(R_B, S_B)$ be the $\beta$-control-pair of $(B_{\delta})_{\delta\in\Delta}$ on $\mathcal{D}_0$.
+
+   For each $f\in \mathcal{P}^+$ and $\theta \geq 0$, $S_BS_A(\theta f)=S_b(\theta^{\gamma}S_Af)=\theta^{\beta\gamma}S_BS_Af$.
+
+   For each $f,g \in \mathcal P^+$ with $f\leq g$, $R_B(R_A f)\leq R_B(R_A g)$ and $R_B (R_A f)\leq R_B(S_A f)\leq S_BS_A f$.
+
+   For each $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|,~~\delta\in \Delta, \lambda\in\Lambda$.
+
+   Thus $(R_BR_A,S_BS_A)$ is a $\beta\gamma$-control-pair of operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$.
+
+   Proof of (3) and (4): Similar to the Proof of (2).
 \end{proof}
 }
-
 \subsection{}
-\added{
     For each $f \in \mathcal{P}$, $x\in E$ and $t\geq 0$, define
@@
 \end{align}
-}
-\added{
+
 \begin{lem}
@@
 \end{lem}
-}
-\added{
+
 \begin{proof}
@@
 \end{proof}
-}
-\deleted{
-\begin{lem}
-\label{lemma1}
-    Let $R^g \in \mathcal P$ be the control function in \eqref{eq:gcontrol}, then
-\begin{equation}
-    e^{-\alpha s}|v_{g_k}(s,x,\theta)|
-    \leq C_g|\theta|e^{(\alpha-\kappa b)k} R^g(x),
-    \quad k\in \mathbb N, x\in \mathbb R^d, \theta \in \mathbb R, s\geq 0.
-\end{equation}
-\end{lem}
-\begin{proof}
-    Recall that $v_{g_k}(s,x,\theta)=\operatorname{Log}\mathbb{P}_{\delta_x}(e^{i\theta \langle g_k, X_s \rangle})$.
-    Let $R^g \in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
-    From \eqref{eq: upper bound for vf} in the appendix, we have for each $k \in \mathbb{N}$, $x\in\mathbb{R}^d$, $\theta\in \mathbb{R}$ and $s\geq 0$,
-\begin{equation}
-    v_{g_k}(s,x,\theta)
-    \leq |\theta| (T_s^\alpha |g_k|) (x)
-    = |\theta| (T_{s}^\alpha |T^\alpha_k g|) (x)
-    \leq C_g|\theta| e^{\alpha(s+k)}e^{-\kappa bk}R^g(x).
-    \qedhere
-\end{equation}
-\end{proof}
-    For each $t \geq 0 $ and $k \in \{0,1,...,\lfloor t \rfloor-1\}$, consider the characteristic function of $M^t_k[g]$ conditioned on $\mathcal{F}_{t-k-1}$.
-    By the Markov property of $X$, we have
- \begin{align*}
-    &\mathbb{P}_{\mu}(e^{i\theta M_k^t[g]}|\mathcal{F}_{t-k-1})
-    =\mathbb{P}_{\mu}(e^{i\theta (\langle X_{t-k},g_k\rangle - \langle X_{t-(k+1)},g_{k+1}\rangle)}|\mathcal{F}_{t-k-1})
-    \\&=\mathbb P_{X_{t-k-1}} [e^{i\theta(\langle g_k,X_1\rangle)}]e^{-i\theta \langle T_1^{\alpha}g_k,X_{t-k-1}\rangle}
-    \\&= e^{\langle v_{g_k}(1,\cdot,\theta),X_{t-k-1}\rangle -i \theta\langle T_1^{\alpha}g_k,X_{t-k-1}\rangle},
-    \quad \mu \in \mathcal M(\mathbb R^d), \theta \in \mathbb R.
-\end{align*}
-    Hence, it is important to estimate the function $v_{g_k}(1,x,\theta)$.
-    For any $f \in \mathcal{P}$, let
-\begin{equation}
-\label{w2function}
-    \tilde{v}_{f}(t,x,\theta)
-    := i\theta T^{\alpha}_t f(x) + \int_0^t T^{\alpha}_{t-s}\psi_0(-i\theta T_s^{\alpha}f(\cdot))(x)ds,
-    \quad x\in \mathbb R^d,t\geq 0, \theta \in \mathbb R.
-\end{equation}
-}
-\deleted{
-\begin{lem}\label{lemma2}
-    There exists $R^g_1 \in \mathcal{P}$ such that for any $k \in \mathbb{N}$ and $0\leq s \leq 1$, we have
-\begin{align}
-    |v_{g_k}(s,x,\theta)-\tilde{v}_{g_k}(s,x,\theta)|
-    \leq |C_g\theta e^{(\alpha-\kappa b)k}|^{1+2\beta}R^g_1(x),
-    \quad x\in \mathbb{R}^d,\theta\in \mathbb{R}.
-\end{align}
-\end{lem}
-}
-\deleted{
-\begin{proof}
-    From \eqref{eq: -v has positive real part} we know that $\operatorname{Re}(-v_{g_k})\geq 0$.
-    Let $C_0>0$ be the constant in Lemma \ref{lem: Lip of power function}, then from \eqref{eq:chareq2}, we have
-\begin{align}
-\label{eq: estimate of wgk}
-   &|v_{g_k}(s,x,\theta)-\tilde{v}_{g_k}(s,x,\theta)|
-   \\&\leq \int_0^s T_{s-u}^{\alpha}\left(|(-v_{g_k}(u,\cdot,\theta))^{1+\beta}-(-i\theta T_u^{\alpha}g_k)^{1+\beta}|\right)(x)~du
-   \\&\leq C_0\int_0^s T_{s-u}^{\alpha}\left( |v_{g_k}(u,\cdot,\theta)-i\theta T_u^{\alpha}g_{k}|\left(|v_{g_k}(u,\cdot,\theta)|^{\beta}+|i\theta T_u^{\alpha}g_k|^{\beta}\right)\right)(x)~du.
-\end{align}
-   Let $R^g\in \mathcal P$ be the control function in both \eqref{eq:gcontrol} and Lemma \ref{lemma1}, then for $0\leq u \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
-\begin{align}
-\label{eq: upper bound of wgk}
-    |v_{g_{k}}(u,x,\theta)|
-    &\leq C_g|\theta|e^{(\alpha-\kappa b)k+\alpha}R^g(x),
-    \\
-    |i\theta T_u^{\alpha}g_k(x)|
-    &\leq |\theta| e^{\alpha(k+1)}T_u|T_k g|(x)
-    \leq C_g|\theta|e^{(\alpha-\kappa b)k+\alpha}R^g(x).
-\end{align}
-    Observe that $(R^g)^{1+\beta}\in \mathcal P$.
-    According to \eqref{eq:semigroupineq}, there exists an $\tilde R^g_0 \in \mathcal P$ such that
-\begin{align}
-\label{eq: tilde R0}
-    |T_t ((R^g)^{1+\beta})(x)|
-    \leq \tilde R^g_0(x),
-    \quad t\geq0, x\in \mathbb{R}^d.
-\end{align}
-    According \eqref{eq:chareq2}, \eqref{eq: upper bound of wgk} and above, for $0\leq u \leq 1$, $x\in \mathbb{R}^d$, $\theta \in \mathbb{R}$ and $k \in \mathbb N$,
-\begin{align}
-\label{eq: Zineq}
-   &|v_{g_{k}}(u,x,\theta)-i\theta T_u^{\alpha}g_k(x)|
-   =\Big| \int_0^u T^{\alpha}_{u-t}(-v_{g_k}(t,\cdot,\theta))^{1+\beta}(x)dt\Big|
-   \\&\leq \int_0^u T_{u-t}^{\alpha}(|v_{g_k}(t,\cdot,\theta)|^{1+\beta})(x)dt
-   \leq  |C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{1+\beta}\int_0^u (T_{u-t}^{\alpha}(R^g)^{1+\beta})(x)dt
-   \\&\leq e^{\alpha}|C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{1+\beta}\tilde R^g_0(x).
-\end{align}
-    According to \eqref{eq:semigroupineq}, since $\tilde R^g_0(R^g)^{\beta} \in \mathcal P$, there exists an $\tilde R^g_1\in \mathcal P$ such that
-\[
-    |T_t(\tilde R^g_0(R^g)^{\beta})(x)|
-    \leq \tilde R^g_1(x),
-    \quad t\geq0, x\in \mathbb{R}^d.
-\]
-As a consecuence of \eqref{eq: estimate of wgk}, \eqref{eq: Zineq}, \eqref{eq: upper bound of wgk} and the above, for $k \in \mathbb{N}$, $0\leq s \leq 1$, $x\in \mathbb{R}^d$ and $\theta \in \mathbb R$, we have
-\begin{align}
-    &|v_{g_k}(s,x,\theta)-\tilde{v}_{g_k}(s,x,\theta)|
-    \\&\leq C_0e^{\alpha}|C_g\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta} \int_0^s T_{s-u}^{\alpha}( \tilde R^g_0(R^g)^{\beta})(x)~du
-    \\&\leq C_0e^{2\alpha}|C_g\theta e^{(\alpha-\kappa(g)b)k+\alpha}|^{1+2\beta}\tilde R^g_1(x).
-    \qedhere
-\end{align}
-\end{proof}
-}
-\deleted{
-    It can be verified from its definition that $(\rho z)^{1+\beta} = \rho^{1+\beta}z^{1+\beta}$ for all $\rho \in [0,\infty)$ and $z\in \mathbb C_+$.
-    For each $f\in \mathcal{P}$, define
-\begin{equation}
-\label{eq: def of Zf}
-    Z_f(s,x,\theta)
-    :=\int_0^s T^{\alpha}_{s-u}\big((-i\theta T_u^{\alpha}f)^{1+\beta}\big)(x)du ,
-    \quad s\geq 0, x\in E, \theta \in \mathbb R.
-\end{equation}
-and let $Z_f(s,x)=Z_f(s,x,1)$.
-\deleted{Then we have}
-\begin{equation}\label{zfunction}
-    \deleted{Z_f(s,x,\theta)=\theta^{1+\beta}Z_f(s,x),
-    \quad s\geq 0, x\in E, \theta \in \mathbb R.}
-\end{equation}
-}
-\deleted{
-\begin{cor}
-\label{cor: corollary2}
-    There exists $R^g_2\in \mathcal P$ such that for each $k\in\mathbb N$ and $0\leq s\leq1$, we have
-\begin{align}
-    |Z_{g_k}(s,x)|\leq C_g^{1+\beta}e^{(\alpha-\kappa b)(1+\beta)k}R^g_2(x), \quad x\in \mathbb{R}^d,
-\end{align}
-    and consequently,
-\begin{align}
-    |Z_{g_k}(s,x,\theta)|\leq C_g^{1+\beta}|\theta|^{1+\beta}e^{(\alpha-\kappa b)(1+\beta)k}R^g_2(x), \quad x\in \mathbb{R}^d,\theta\in \mathbb{R}. \label{zineq1}
-\end{align}
-\end{cor}
-}
-\deleted{
-\begin{proof}
-    Let $c_0 > 0$ be the constant in \eqref{eq: upper bound for beta power of z}.
-    Let $R^g\in \mathcal P$ be the control function in \eqref{eq:gcontrol}.
-    Let $\tilde R^g_0 \in \mathcal P$ be the control function in \eqref{eq: tilde R0}.
-    Now, we have for each $k\in\mathbb N$, $x\in \mathbb{R}^d$ and $\theta\in \mathbb{R}$,
-\begin{align}
-    |Z_{g_k}(s,x)|
-    &\leq C_{}\int_0^s T_{s-u}^{\alpha}(|T_u^{\alpha}g_k|^{1+\beta})(x)du
-    \leq c_0 \int_0^s T_{s-u}^{\alpha}\Big(\big(e^{(\alpha-\kappa b)k+\alpha}R\big)^{1+\beta}\Big)(x)~du
-    \\&\leq c_0e^{\alpha(2+\beta)} C_g^{1+\beta}e^{(\alpha-\kappa b)(1+\beta)k}\tilde R^g_2(x).
-\qedhere
-\end{align}
-\end{proof}
-}
+\begin{comment}
 \textbf{ Zhenyao: I think the following Corollary is incorrect.
@@
 \end{proof}
+\end{comment}
 
@@
 
- In this subsection, for any $\gamma \in (0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ \deleted{by an exponential function depending on $\kappa$}.
-
-\added{
+ In this subsection, for any $\gamma \in (0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$.
+Denote $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite measures on $\mathbb{R}^d$ with compact support.
 \begin{lem}
@@
     \mathbb P_\mu (|M^t_g(0,t)| > \lambda)
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\nu\rangle d\theta
-    \leq \langle S| g|,\nu\rangle \frac{1}{\lambda^{1+\beta}}.
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta
+    \leq \langle S| g|,\mu\rangle \frac{1}{\lambda^{1+\beta}}.
 \]
 \end{lem}
-}
-\added{
-\begin{proof}
-    Denote by $(R_0,S_0)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for U-iT}.
-    Using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability} and Lemma \ref{cor: corollary1} we have
+
+\begin{proof}
+    Denote by $(R_0,S_0)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}.
+    Using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, we have
 \begin{align}
@@
     = \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{iM_{(\theta g)}^t(0,t)}]\Big)d\theta
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle 3|U_t(\theta g) - iT_t^\alpha(\theta g)|,\nu\rangle d\theta
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle 3R_0|\theta g|,\nu\rangle d\theta
-    \\& \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle 3S_0|\theta g|,\nu\rangle d\theta
-\end{align}
-    To finish the proof we write $R=3R_0$ and $S= 3S_0$.
-\end{proof}
-}
-\added{
+    \\&= \added{\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}\Big) d\theta}
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iT_t^\alpha(\theta g)|,\mu\rangle d\theta
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta g|,\mu\rangle d\theta
+      \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta g|,\mu\rangle d\theta
+\end{align}
+    To finish the proof we write $R=R_0$ and $S= S_0$.
+\end{proof}
+
 \begin{lem}
@@
 \end{lem}
-}
-
-\added{
+
 \begin{proof}
     Denote by $(R_0,S_0)$ the $(1+\beta)$-control-pair in Lemma \ref{lem: control pair for P(M>lambda)}.
-    Then using Markovian property of $(X_t)$ we get
+    Then using Markovian property of $(X_t)_{t\geq 0}$ we get
 \begin{align}
@@
 \end{proof}
-}
-\added{
-\begin{lem}
-    For each $g\in \mathcal P$, $\mu \in \mathcal M_c$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
+
+\begin{lem}\label{lem: control of mgtrs}
+    For each $g\in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
 \[
@@
 \end{proof}
-}
-
+\begin{comment}
 \deleted{
@@
 }
-    As $\langle g,X_t\rangle$ is the sum of $M_k^{t}[g], k=0,1,...,\lfloor t\rfloor$ and $M_t^t[g]$. We obtain the following lemma.
-\added{
+\end{comment}
+    As $\langle g,X_t\rangle,~g\in \mathcal{P}$ is the sum of $M_g^t(k,k+1), k=0,1,...,\lfloor t\rfloor$ and $M_g^t(\lfloor t\rfloor, t)$. We obtain the following lemma.
+
 \begin{lem}
@@
 \item[(1)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$.
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa_g b)t}$ provided $\alpha\gamma > \kappa_g (1+\gamma)b$.
 \item[(2)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$.
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa_g (1+\gamma)b$.
 \item[(3)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa_g (1+\gamma)b$.
 \end{itemize}
@@
     Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$.
-    Let $C$ be the constant in Lemma \ref{lem: lemma23}.
+    Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
     Using the triangle inequality,
@@
 \end{proof}
-}
-\deleted{
-\begin{lem}%\label{lemma24}
-For each $0 < \gamma < \beta$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_2>0$, such that for each $t\geq 0$:
-
-i) If $\alpha\gamma > \kappa (1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C_2 C_g e^{(\alpha-\kappa b)t}.$$
-
-ii) If  $\alpha\gamma = \kappa (1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C_2 C_g te^{\frac{\alpha}{1+\gamma}t}.$$
-
-iii) If $\alpha\gamma < \kappa (1+\gamma)b$,
-$$\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C_2 C_g e^{\frac{\alpha}{1+\gamma}t}.$$
-
-\end{lem}
-\begin{proof}
-    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support.
-    Let $C_1$ be the constant in Lemma \ref{lem: lemma23}.
-    Using the triangle inequality,
-\begin{align}
-    \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    &\leq \sum_{k=0}^{\lfloor t\rfloor}\|M_k^t[g]\|_{\mathbb P_\mu;1+\gamma}+\|M_t^t[g]\|_{\mathbb P_\mu;1+\gamma}
-    \\ &\leq C_1 C_g e^{\frac{\alpha}{1+\gamma}t}\Big(\sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma}k}+e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma}t}\Big).
-\end{align}
-By calculating the sum on the right, we easily get the result.
-\end{proof}
-}
-\deleted{
-According to \eqref{eq:semigroupineq}, each $f \in \mathcal{P}$ satisfies \eqref{eq:gcontrol1} with $C_f=1$, $\kappa=\kappa(f)$ and $R_0^f=R_0$. Thus
-\begin{cor}\label{cor27}
-Let $0< \gamma < \beta$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, for each $f\in \mathcal{P}$, there exist constants $\tilde{C}_1,\tilde{C}_2>0$ such that, for each $t>0$ and $k \in \{0,\dots,\lfloor t \rfloor\}$, we have
-\begin{align}
-\label{eq: upper bound of 1+gamma moment of Mktf}
-    \|M_k^t[f]\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq \tilde{C}_1 e^{\frac{\alpha t}{1+\gamma}}e^{(\alpha \gamma - \kappa(f)b)k}.
-\end{align}
-and
-\begin{align}
-    \|M_t^t[f]\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq \tilde{C}_1 e^{\frac{\alpha t}{1+\gamma}}e^{(\alpha \gamma - \kappa(f)b)t}.
-\end{align}
-Moreover,
-\begin{itemize}
-    \item If $\alpha\gamma > \kappa(f)(1+\gamma)b$,\quad $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq \tilde{C}_2 e^{(\alpha-\kappa b)t}.$
-    \item If  $\alpha\gamma = \kappa(f)(1+\gamma)b$,\quad $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq \tilde{C}_2 te^{\frac{\alpha}{1+\gamma}t}.$
-    \item If $\alpha\gamma < \kappa(f)(1+\gamma)b$,\quad$\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq \tilde{C}_2 e^{\frac{\alpha}{1+\gamma}t}.$
-\end{itemize}
-\end{cor}
-}
+
 \subsection{Martingales}
@@
 \end{align}
-    \deleted{Where $\bar{f}=(L+ab)f$.}
     The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathcal{F}_t\}_{t\geq 0}$.
@@
 \label{lemma25}
-    Let $a\in \mathbb R$ and $\added{f} \deleted{h}\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$.
-Then the process \added{$(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.} \deleted{$\left\{M_t^{f,a}, \mathcal{F}_t:t\geq 0\right\}$ is an martingale.}
+    Let $a\in \mathbb R$ and $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$. Then the process $(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.
 \end{lem}
 \begin{proof}
-    \added{Write $\bar{f}=(L+ab)f$.} \deleted{For any $ a\in \mathbb{R},x\in \mathbb{R}^d$, take $\pi_tf(x)=T_t^{ab}f(x)$} \added{According to} \deleted{into} \cite[Theorem A.55]{Li2011Measure-valued}, we have
+    Write $\bar{f}=(L+ab)f$. According to \cite[Theorem A.55]{Li2011Measure-valued}, we have
 \begin{align}\label{Theorem55}
@@
     =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathcal{F}_s\big]
-    %\\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)s}\langle \bar{f}, X_u\rangle~ du\nonumber\\
-    %\\&-\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_u\rangle~ du.\label{martingale1}
     \\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du -\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
 \end{align}
-    \added{Using \eqref{Theorem55} and Fubini's theorem, we have}
-    \deleted{By using \eqref{Theorem55} and Fubini's theorem , further we get}
+    Using \eqref{Theorem55} and Fubini's theorem, we have
 \begin{align}
@@
 \end{align}
-    \deleted{Take it to} \added{Using this and} \eqref{martingale1}, we get the desired result.
-\end{proof}
-
-    Let $p=(p_1,...,p_d)\in \added{\mathbb N_0^d} \deleted{\mathbb{Z}_+^d}$, recall that $\phi_p$ is \added{one of the} \deleted{an} eigenfunction\added{s} of $L$ corresponding to the eigenvalue $-|p|b$.
-Define
+   Using this and \eqref{martingale1}, we get the desired result.
+\end{proof}
+
+    Let $p=(p_1,...,p_d)\in \mathbb N_0^d$, recall that $\phi_p$ is one of the eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
 $$H_t^p:=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.$$
@@
 \begin{lem}\label{lemma26}
-    \added{$(H^p_t)_{t\geq 0}$} \deleted{$\{H_t^p: t\geq0\}$} is a martingale with respect to \added{filtration $(\mathscr F_t)$} \deleted{$\mathcal{F}_t$}.
-    \deleted{If} \added{Moreover, if} $\alpha\beta>|p|b(1+\beta)$, then for any $0< \gamma<\beta$ and \added{$\mu \in \mathcal M_c(\mathbb R^d)$} \deleted{$\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support}, we have $\sup_{t\geq 0}\|H_t^p\|_{\added{\mathbb P_\mu;}1+\gamma}< \infty$ \added{and}\deleted{.
-Thus the limit}
+    $(H^p_t)_{t\geq 0}$ is a martingale with respect to filtration $(\mathscr F_t)$.
+    Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $0< \gamma<\beta$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
 $$H_{\infty}^p:=\lim_{t\rightarrow \infty}H_t^p$$
@@
 \begin{proof}
-    \deleted{By taking $a=|p|$ and $f=\phi_p$ in} \added{According to} Lemma \ref{lemma25}, we get \added{$(H_t^p)_{t\geq 0}$} \deleted{$\{H_t^p, \mathcal{F}_t:t\geq 0\}$} is a martingale.
-
-    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that \deleted{$\alpha\gamma_0>|p|(1+\gamma_0)b$} \added{for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$}.
-    Using  Lemma \ref{lemma24} and the fact $\kappa(\phi_p)=|p|$, we get that, for any $\gamma_0\leq\gamma<\beta$\added{, there exists a constant $C$ such that}
+    According to Lemma \ref{lemma25}, we get $(H_t^p)_{t\geq 0}$ is a martingale.
+
+    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$.
+    Using  Lemma \ref{lemma24} and the fact $\kappa_{\phi_p}=|p|$, we get that, for any $\gamma_0\leq\gamma<\beta$, there exists a constant $C$ such that
     $$\|H_t^p\|_{1+\gamma}\leq Ce^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C.$$
-    For any $0\leq\gamma<\gamma_0$, \deleted{by the concave of function $h(x)=x^{(1+\gamma)/(1+\gamma_0)}$,} \added{consider the concave function $x\mapsto x^{(1+\gamma)/(1+\gamma_0)}$ on $[0,\infty)$, using Jensen's inequality, we have}
+    For any $0\leq\gamma<\gamma_0$, consider the concave function $x\mapsto x^{(1+\gamma)/(1+\gamma_0)}$ on $[0,\infty)$, using Jensen's inequality, we have
     $$\mathbb{P}_{\mu}|H_t^p|^{1+\gamma}\leq(\mathbb{P}_{\mu}|H_t^p|^{1+\gamma_0})^{\frac{1+\gamma}{1+\gamma_0}}<\infty.$$
@@
 %end comment
-\begin{lem}\label{lemma27}
+\begin{lem}\label{lem: control of Wt}
  %For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have
- For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exists a $C_3> 0$ such that for each $0\leq s<t$,
- $$\|W_t-W_s\|_{1+\gamma}\leq C_3 e^{-\alpha s/2}.$$
+ For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C_{\ref{lem: control of Wt}}> 0$ such that for each $0\leq s<t$,
+ $$\|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq C_3 e^{-\alpha s/2}.$$
 \end{lem}
@@
 %new added
-    Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support.
-    According to Lemma \ref{lem: lemma23}, for each $n \in \mathbb N$, we have
-%end new added
-%delete
-    %Let $n\in \mathbb{N}$, in Lemma \eqref{lem: lemma23}, we take $t=n+k,g=1$, then $\kappa(g)=0$, moreover, the following inequality holds.
-%end delete
-    $$ \mathbb{P}_{\mu}[|e^{\alpha k}\|X_n\|-e^{\alpha(k+1)}\|X_{n-1}\||^{1+\gamma}]
-    = \mathbb P_\mu [|M^{n+k}_k[1]|^{1+\gamma}]
-    \leq C_1 e^{\alpha(n+k)}e^{\alpha\gamma k}.$$
-    Dividing both sides by $e^{\alpha(n+k)(1+\gamma)}$, we get
-    $$\mathbb{P}_{\mu}\left|W_n-W_{n-1}\right|^{1+\gamma}\leq C_1 e^{-\alpha \gamma n}.$$
-    For any $m\in \mathbb{N}$ and $m<n$,
-    $$\|W_n-W_m\|_{1+\gamma}\leq \sum_{k=m}^{n-1}\|W_{k+1}-W_k\|_{1+\gamma}\leq C_1^{\frac{1}{1+\gamma}}\sum_{k=m}^{n-1}e^{-\frac{\alpha\gamma(k+1)}{1+\gamma}}\leq C_3 e^{-\frac{\alpha m}{2}}.$$
- When we take any $0\leq s\leq t$, there will appear two terms corresponding to the interval $[s,[s]+1]$ and $[[t],t]$, which are  handled by using Lemma \ref{lem: lemma23} with the same method, then we complete our proof.
+    Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
+    According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
+    \begin{align}
+        \mathbb{P}_{\mu}[|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\||^{1+\gamma}]=\mathbb{P}_{\mu}[|M_1^t(r,s)|^{1+\gamma}]\leq Ce^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)b)}.
+    \end{align}
+    Dividing both sides by $e^{\alpha t(1+\gamma)}$, we get
+    \begin{align}
+        \mathbb{P}_{\mu}\left|W_s-W_r\right|^{1+\gamma}\leq  C e^{-\alpha \gamma s}.
+    \end{align}
+    Then for any $0\leq s<t$,
+    \begin{align}
+       & \|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq \|W_{\lfloor s \rfloor +1}-W_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+2}^{\lfloor t \rfloor}\|W_k-W_{k-1}\|_{\mathbb{P}_{\mu};1+\gamma}+\|W_t-W_{\lfloor t \rfloor}\|_{\mathbb{P}_{\mu};1+\gamma}
+       \\&\leq C_{\ref{lem: control of Wt}}e^{-\frac{\alpha \gamma}{1+\gamma}s}\leq C_{\ref{lem: control of Wt}}e^{-\frac{\alpha}{2}s}.
+    \end{align}
 \end{proof}
@@
 Recall that the superprocess $X$'s extinction probability $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
-Denote $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$, by equation (3.48) in\cite{Li2011Measure-valued} and formula \eqref{CSBP}, we easily get
+Denote $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$, by equation (3.48) in \cite{Li2011Measure-valued} and formula \eqref{CSBP}, we easily get
 \begin{align}
     \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}\nonumber\\
-        &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right| \label{laplaceexpress}
+        &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|. \label{laplaceexpress}
 \end{align}
@@
 We want to prove the following Lemma
-\begin{lem}\label{lemma2_13}
-Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function such that $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$ Then for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exist $C_4>0$ such that there is
+\begin{lem}\label{lem: control of XT}
+Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function satisfying $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$, Then for any $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C_{\ref{lem: control of XT}}>0$ such that
 \begin{align}
@@
     \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|)}]\\
-    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
+    &\leq \frac{1}{1-e^{-\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
 \end{align*}
@@
 \end{align*}
-We conclude the lemma by taking $C_4= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
+We conclude the lemma by taking $C_{\ref{lem: control of XT}}= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
 \end{proof}
 Define $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\},\quad \epsilon,t>0$.
-\begin{lem}\label{lemma28}
-  For any $\epsilon>0$, $t>0$ and $\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_5>0$ and $\delta_1>0$ such that
-  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_5 e^{-\delta_1 t}.$$
+\begin{lem}\label{lem: control of AT}
+  For any $\epsilon,t>0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exists $C_{\ref{lem: control of AT}}>0$ and $\delta_{\ref{lem: control of AT}}>0$ such that
+  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_{\ref{lem: control of AT}} e^{-\delta_{\ref{lem: control of AT}} t}.$$
 \end{lem}
@@
     $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.$$
-    For another side, using Lemma \ref{lemma2_13}, we have
-    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_4 e^{-\beta\epsilon t}, $$
-Therefore,
+    For another side, using Lemma \ref{lem: control of XT}, we have
+    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_{\ref{lem: control of XT}} e^{-\beta\epsilon t}, $$
+To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.
+\begin{comment}
 \begin{align*}
@@
 \end{align*}
+\end{comment}
 \end{proof}
@@
 %\subsection{Parameter $m_k[g]$}
-{\bf (Jianjie: Can I add the condition $t\in \mathbb{N}$ above this subsection and omit the case $t \notin \mathbb{N}$.)}
 \subsection{Parameters}
- In this subsection, we will introduce an important parameter $m_k[f],~f\in\mathcal{P}$, which is a parameter of $(1+\beta)$-stable distribution. Let $Z_f(x)=Z_f(1,x)$, thus
- $$Z_f(x)=\int_0^1 T^{\alpha}_{1-s}(-iT_s^{\alpha}f)^{1+\beta}(x)~ds,$$
+\added{
+ In this subsection, we will introduce an important parameter of $(1+\beta)$-stable distribution: $m_k[f],~~f\in \mathcal{P}$.
+
+ Let $Zf(x)=Z_1f(x),~x\in\mathbb{R}^d$ and 
+ \begin{align}\label{parameter_mk}
+      m_k[f]:=e^{-\alpha(k+1)}\langle Z(T_k^{\alpha}f),\varphi\rangle,\quad k\in \mathbb{N}.
+ \end{align}
+ }
+\begin{lem}\label{lem: control of mk}
+For each $f\in\mathcal{P}$, there exists constant $C_{\ref{lem: control of mk}}>0$ such that for any $k\in \{0,1,...,\lfloor t\rfloor\}$, we have
+$$|m_k[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))k}.$$
+\end{lem}
+\begin{proof}
+\added{
+According to Lemma \ref{lem: upper bound for usgx}, there exists an $(1+\beta)$-control-pair $(R,S)$ suct that for each $k\in\mathbb{N}$,
+\begin{align}
+    |Z(T^{\alpha}_k f)|\leq R|T^{\alpha}_k|\leq R (e^{(\alpha-\kappa_fb)k}Qf)\leq S(e^{(\alpha-\kappa_fb)k}Qf)=e^{(\alpha-\kappa_fb)(1+\beta)k}SQf.
+    \end{align}
+}
+\deleted{
+Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{eq: zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
+\begin{align}
+    |Z_{f_k}(x)|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_2^f(x), \quad x\in \mathbb{R}^d, k\in\mathbb{N}.
+\end{align}
+}
+This implies the result by simply calculating.
+\end{proof}
+
+$m_k[f],~f\in \mathcal{P}$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Note that,
+\begin{align}
+    m_k[f]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}\Psi_0(-iT_{s+k}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in\mathbb{N}.
+\end{align}
+
+Using Fubini's Theorem and the fact $\varphi(x)$ is an invariant measure of $(T)_{t\geq 0}$, we get
+\begin{align}
+    m_k[f]=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in \mathbb{N}.\label{mkeq}
+\end{align}
+
+\deleted {Next, we will introduce a parameter of limiting distribution in the critical case.}
 Let
- \begin{align}\label{parameter_mk}
-      m_k[f]:=e^{-\alpha(k+1)}\langle Z_{f_k},\varphi\rangle.
- \end{align}
-\begin{lem}\label{mgineq1}
-Let $f\in\mathcal{P}$, there exists constant $C_6>0$ such that for any $k\in \{0,1,...,t\}$, we have
-$$|m_k[f]|\leq C_6 e^{(\alpha\beta-\kappa(f)b(1+\beta))k}.$$
+\begin{align}
+    \phi(x)=\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p(x),~x\in \mathbb{R}^d, p \in\mathbb{N}_0^d.
+\end{align}
+i.e. $\phi$ is the projection of $f$ onto the $\kappa_f$-eigenspace. Easily we get $\kappa_f=\kappa_{\phi}$ and $\kappa_{f-\phi}\geq \kappa_f+1$.
+\begin{lem}\label{lemma210}
+Let $f \in \mathcal{P}$, $\kappa_f\geq 1$ and $\alpha\beta=\kappa(f)b(1+\beta)$, then the following limit exists:
+\begin{align}
+    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\added{\lfloor t \rfloor}}m_k[f]=\langle\Psi_0(-i\phi),\varphi\rangle.
+\end{align}
 \end{lem}
-\begin{proof}
-Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{eq: zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
-\begin{align}
-    |Z_{f_k}(x)|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_2^f(x), \quad x\in \mathbb{R}^d, k\in\mathbb{N}.
-\end{align}
-This implies the result by simply calculating.
-\end{proof}
-
-$m_k[f],~f\in \mathcal{P}$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Notice that,
-$$m_k[f]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}(-iT_{s+k}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx.$$
-Using Fubini's Theorem and the fact $\varphi(x)$ is an invariant measure of $T$, we get
-\begin{align}
-    m_k[f]&=\int_{\mathbb{R}^d}\int_0^1 e^{-\alpha(k+s)}(-iT_{s+k}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx\nonumber\\
-    &=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx.\label{mkeq}
-\end{align}
-
-Next, we describe the parameter of limiting distribution in the critical case. Let
-$$\phi(x)=\sum_{|p|=\kappa(f)}\langle f, \phi_p\rangle\phi_p(x)$$
-i.e. $\phi$ is the projection of $f$ onto the $\kappa(f)$-eigenspace.
-\begin{lem}\label{lemma210}
-Let $f \in \mathcal{P}$, $\kappa(f)\geq 1$ and $\alpha\beta=\kappa(f)b(1+\beta)$, then the following limit exists:
-\begin{align}
-    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{t}m_k[f]=\langle(-i\phi)^{1+\beta},\varphi\rangle.
-\end{align}
-\end{lem}
-
-\begin{proof}
+
+\begin{proof}
+\deleted{
     We want to show the gap between $m_k[f]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$,
     $$|m_k[f]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-\alpha s}\left|(-i T^{\alpha}_s f)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
+    }
+    \added{
+    Notice that
+        \begin{align}\label{parameter of mkphi}
+        m_k[\phi]&=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}\phi)(x)~ds~\varphi(x)~dx\\
+        &=\int_{\mathbb{R}^d}\Psi_0(-i\phi(x))\varphi (x)~dx=\langle \Psi_0(-i\phi),\varphi\rangle.
+    \end{align}
+    }
+    \deleted{
     As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(f)bt}$,  $\kappa(f)=\kappa(\phi)$ and $\kappa(f-\phi)\geq \kappa(f)+1$.
@@
     $$|m_k[f]-m_k[\phi]|\leq2C_0\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R_5^{1+\beta}(x)~ds~\varphi(x)~dx\leq \frac{2C_0}{b}\langle R_5^{1+\beta},\varphi\rangle e^{-bk},$$
-
-    Therefore, the limits of $(1/t)\sum_{k=0}^tm_k[f]$ is the same with that of $(1/t)\sum_{k=0}^tm_k[\phi]$. What's more
+    }
+    \added{
+    According to Lemma \ref{lem: Lip of power function}, for any $s\geq 0$,
+    \begin{align}
+        &\Big|\Psi_0(-iT^{\alpha}_s f)-\Psi_0(-iT^{\alpha}_s\phi)\Big|\leq C_{\ref{lem: Lip of power function}}(|T^{\alpha}_sf|^{\beta}+|T^{\alpha}_s\phi|^{\beta})|T^{\alpha}_s(f-\phi)|
+        \\& \leq C_{\ref{lem: Lip of power function}}e^{(\alpha-\kappa_f b)(1+\beta)s}e^{-bs}\big((Qf)^{\beta}+(Q\phi)^{\beta}\big)Q(f-\phi).
+    \end{align}
+    Therefore, by the condition $\alpha\beta=\kappa_fb(1+\beta)$,
+    \begin{align}
+        |m_k[f]-m_k[\phi]|&\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-\alpha s}\Big|\Psi_0(-iT^{\alpha}_s f)-\Psi_0(-iT^{\alpha}_s\phi)\Big|(x)~ds~\varphi(x)~ds.
+        \\&\leq C_{\ref{lem: Lip of power function}}\int_{\mathbb{R}^d}\int_{k}^{k+1} e^{-bs}\big((Qf)^{\beta}+(Q\phi)^{\beta}\big)Q(f-\phi)~ds~ \varphi(x)~dx.
+        \\&\leq C_{\ref{lem: Lip of power function}}\langle((Qf)^{\beta}+(Q\phi)^{\beta})Q(f-\phi), \varphi\rangle e^{-bk},\quad k \in \mathbb{N}.
+    \end{align}
+    Therefore, the limits of $(1/t)\sum_{k=0}^tm_k[f]$ is the same with that of $(1/t)\sum_{k=0}^tm_k[\phi]$.
+    }
+
+    \deleted{
+    What's more
     \begin{align*}
@@
     \end{align*}
-    The second equality holds as $T_s\phi=e^{-\kappa(g)bs}\phi$. Hence
-    $$\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{t}m_k[f]=\langle(-i\phi)^{1+\beta},\varphi\rangle.$$
-\end{proof}
-
-For the small branching rate case: $\alpha\beta<\kappa(f)b(1+\beta)$.
+    The second equality holds as $T_s\phi=e^{-\kappa(g)bs}\phi$.
+    }
+
+    From \eqref{parameter of mkphi}, for any $k\in \mathbb{N}$,
+    \begin{align}
+        \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t\rfloor}m_k[f]=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[\phi]=\langle\Psi_0(-i\phi),\varphi\rangle.
+    \end{align}
+
+\end{proof}
+
+\deleted {For the small branching rate case: $\alpha\beta<\kappa(f)b(1+\beta)$.}
 \begin{lem}\label{lemma211}
-Let $f\in \mathcal{P}$, assume $\alpha\beta<\kappa(f)b(1+\beta)$, if $\kappa(f)\geq 1$, the series $\sum_{k=0}^{\infty}m_k[f]$ is absolutely convergent, hence we can define
-\begin{align}
-    m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)ds\varphi(x)dx \label{msmallcase}
+Let $f\in \mathcal{P}$, assume $\alpha\beta<\kappa_fb(1+\beta)$, if $\kappa_f\geq 1$, the series $\sum_{k=0}^{\infty}m_k[f]$ is absolutely convergent, hence we can define
+\begin{align}
+    m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx \label{msmallcase}
 \end{align}
@@
 \begin{proof}
-    By Lemma \ref{mgineq1}, we have $|m_k[f]|\leq C_6 e^{(\alpha\beta-\kappa(g)b(1+\beta))k}$, which implies $\sum_{k=0}^{\infty}|m_k[f]|<\infty$ as $\alpha\beta<\kappa(f)b(1+\beta)$. Hence
-    $$m[f]:=\sum_{k=0}^{\infty}m_k[f]=\sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)ds\varphi(x)dx$$
-     Moreover, the right side series are also absolutely convergence, since $|e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)|\leq e^{(\alpha\beta-\kappa(f)b(1+\beta))s}R_0^{1+\beta}(x)$.
-
-     Those means the equation \eqref{msmallcase} hold.
+\added{
+    By Lemma \ref{lem: control of mk}, we have $|m_k[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))k},~k\in\mathbb{N}$, which implies $\sum_{k=0}^{\infty}|m_k[f]|<\infty$.
+
+    On the other hand, denote by $(R,S)$ the $(1+\beta)$-control-pair for Lemma \ref{lem: upper bound for usgx}(3), for any $s\geq 0$,
+    \begin{align}
+        |e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)|\leq e^{-\alpha s}R|T^{\alpha]_s}f|\leq e^{-\alpha s}R(e^{(\alpha-\kappa_fb)s}Qf)=e^{(\alpha\beta-\kappa_fb(1+\beta))s}RQf.
+    \end{align}
+    This implies 
+    \begin{align}
+        \sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)ds\varphi(x)dx< \infty.
+    \end{align}
+    and
+    \begin{align}
+            m[f]:=\sum_{k=0}^{\infty}m_k[f]=\sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)ds\varphi(x)dx
+    \end{align}
+    is well defined.
+    }
 \end{proof}
@@
 \begin{lem}\label{lemma32}
-Recall $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\},~\epsilon,t>0$, then for any $t>0$, we have
-\begin{align}
-    \lim_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=D^c
+Recall $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\},~\epsilon,t>0$, then for any $\epsilon>0$, we have
+\begin{align}
+    \lim_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=D^c, ~~\mathbb{P}_{\mu}\text{-}{\rm a.s}.
 \end{align}
@@
     \begin{align}
-        D^c \subset \liminf_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c.
+        D^c \subset \liminf_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c,~~\mathbb{P}_{\mu}\text{-}{\rm a.s}.
     \end{align}
@@
 \subsection{}
-    \added{ In this subsection, we }\deleted{ We first} present two analytic results which are useful.
+    In this subsection, we present two analytic results which are useful.
 \begin{lem}
@@
 \begin{align}
-    \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(\added{ V_tf}\deleted{ u_f(t,\cdot)})},
+    \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
     \quad t\geq 0, \mu \in \mathcal M_E^1, f\in \mathscr B^+_b(E),
 \end{align}
-    where \added{ for each $f\in b\mathscr B_E$,} the function \added{ $(t,x)\mapsto V_tf(x)$}\deleted{ $u_f:(t,x) \mapsto u_f(t,x)$} on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
+    where for each $f\in b\mathscr B_E$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
 \begin{align}\label{eq:FKPP_in_definition}
@@
     \quad t \geq 0, x \in E.
-    \\
-    \deleted{u_f(t,x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi \big(\xi_s,u_f(t-s,\xi_s)\big) ds \Big]
-    = \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
-    \quad t \geq 0, x \in E.}
 \end{align}
@@
     Notice that, from the branching property of the superprocess $X$, $\{X_t(f); \mathbf P_{\delta_x}\}$ is an infinitely divisible random variable with finite moment.
-    \added{ Denote by $U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}]$ }\deleted{ Denote by $v_f(t,x,\theta) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i\theta X_t(f)}]$} the charateristic exponent of random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
+    Denote by $U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}]$  the charateristic exponent of random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
     According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, for each $\theta \in \mathbb R$,
@@
 \label{eq: N and characteristic exponent}
-    \added{ U_tf(x)}\deleted{ v_f(t,x,\theta)} = \added{ \mathbb N_x[e^{i W_t(f)} - 1]}
-    \deleted{ \mathbb N_x[e^{i\theta W_t(f)} - 1]},
-    \quad \theta \in \mathbb R.
+    U_tf(x) = \mathbb N_x[e^{i W_t(f)} - 1]
+    \quad t \geq 0.
 \end{equation}
@@
 \subsection{}
-\deleted{
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
@@
     is well defined.
-}
 
@@
 \[
-    \added{ e^{\operatorname{Re} U_tf(x)}}
-    \deleted{ e^{\operatorname{Re} v_f(t,x,\theta)}}
-    = \added{|e^{U_tf(x)}|}
-    \deleted{ |e^{v_f(t,x,\theta)}|}
-    = \added{|\mathbf P_{\delta_x}[e^{i X_t(f)}]|}
-    \deleted{|\mathbf P_{\delta_x}[e^{i\theta X_t(f)}]|}
+     e^{\operatorname{Re} U_tf(x)}
+    = |e^{U_tf(x)}|
+    = |\mathbf P_{\delta_x}[e^{i X_t(f)}]|
     \leq 1,
-    \quad \theta\in \mathbb R,
 \]
@@
 \label{eq: -v has positive real part}
-    \added{ \operatorname{Re} U_tf(x)}
-    \deleted{ \operatorname{Re} v_f(t,x,\theta)}
+ \operatorname{Re} U_tf(x)
     \leq 0.
-    \deleted{\quad \theta \in \mathbb R.}
 \end{equation}
 %new added
-    Therefore, it is legal to talk about \added{$\psi(x,-U_tf)$}\deleted{$\psi(x,-v_f(t,x,\theta))$} since \deleted{in} $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
+    Therefore, it is legal to talk about $\psi(x,-U_tf)$since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
     According to Lemma \ref{lem: estimate of exponential remaining}, we have that
@@
 \label{eq: upper bound for vf}
-    |\deleted{U_tf(x)}\added{ v_f(t,x)}| \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
+    |U_tf(x)| \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
     \leq \mathbb N_x[|i W_t(f)|]
-    \leq (P^\beta_t |f|)(x),
-    \quad \theta \in \mathbb R.
+    \leq (P^\beta_t |f|)(x).
 \end{equation}
@@
     Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability},
-    \added{$U_t(\theta f)(x)$}\deleted{$v_f(t,x,\theta)$} is differentiable in $\theta \in \mathbb R$ with
-\[
-    \added{\frac{\partial}{\partial \theta} U_t(\theta f)(x)}
-    \deleted{\frac{\partial}{\partial \theta} v_f(t,x,\theta)}
+    $U_t(\theta f)(x)$ is differentiable in $\theta \in \mathbb R$ with
+\[
+    \frac{\partial}{\partial \theta} U_t(\theta f)(x)
     = i\mathbb N_x[W_t(f)e^{i\theta W_t(f)}],
@@
 \label{eq: upper bounded for derivative of v(theta)}
-    \added{\sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|}
-    \deleted{\sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta} v_f(t,x,\theta)\Big|}
-    \leq ( P^\beta_t |f|)(x),
-    \quad \theta \in \mathbb R.
-\end{equation}
-    From \deleted{\eqref{eq: estimate of deriavetive of v(theta)} and} the dominate convergence theorem, we can verify that \added{$(\partial/\partial \theta)U_tf(x)$}\deleted{$(\partial/\partial \theta)v_f(t,x,\theta)$} is continuous in $\theta$.
-    In another words, \added{$\theta \mapsto -U_t(\theta f)(x)$}\deleted{$\theta \mapsto -v_f(t,x,\theta)$} is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
+    \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
+    \leq ( P^\beta_t |f|)(x).
+\end{equation}
+    From the dominate convergence theorem, we can verify that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
+    In another words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
     According to this and \eqref{eq: path integration representation of h}, we can write
-\deleted{
 \begin{equation}
@@
 \end{equation}
-}
-\begin{equation}
-%\label{eq: path integration representation of psi(v)}
-    \deleted{\psi(x,-v_f(t,x,\theta_0)) = -\int_0^{\theta_0} \psi'(x,-v_f(t,x,\theta)) \frac{\partial}{\partial \theta} v_f(t,x,\theta)~d\theta,
-    \quad \theta_0 \in \mathbb R.}
-\end{equation}
     Notice that
-\deleted{
 \begin{equation}
@@
 \end{equation}
-}
-\begin{equation}
-\deleted{ \textbf{The old equation is deleted and marked by \%}}
-\end{equation}
-    where \added{$C_{\ref{eq: upper bound of psi'(v)}.1}, C_{\ref{eq: upper bound of psi'(v)}.2}$}\deleted{$c_0,c_1$} are constants not dependent on \added{$f,x$ and $t$}\deleted{$f,x,t$ and $\theta$}.
+    where $C_{\ref{eq: upper bound of psi'(v)}.1}, C_{\ref{eq: upper bound of psi'(v)}.2}$ are constants not dependent on $f,x$ and $t$.
     Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have
-\deleted{
+
 \begin{align}
@@
     \leq C_{\ref{eq: upper bound of psi'(v)}.1} P^\beta_t |f|(x)+C_{\ref{eq: upper bound of psi'(v)}.2} P^\beta_t |f| (x)^2.
-    \\ \deleted{\big|\psi\big(x,-v_f(t,x,\theta)\big)\big|
-    \leq c_0|\theta|~(P^\beta_t |f|)(x)+c_1 |\theta|^2 ~(P^\beta_t |f|)(x)^2,
-    \quad \theta \in \mathbb R.}
-\end{align}
-}
-
+\end{align}
     Now assume that $f \in L_2(\xi) \subset L_1(\xi)$.
     Then, using Jensen's inequality and the above, we have that
-\deleted{
 \begin{align}
@@
 \end{align}
-}
-\begin{align}
-    \added{ \textbf{The old equation is deleted and marked by \%}}
-    %\label{eq: domination of psi(v)}
-    %&\Pi_x\Big[\int_0^t |\psi(\xi_s,-v_f(t-s,\xi_s,\theta))|ds\Big]
-    %\\&\leq \Pi_x\Big[\int_0^t \big(c_0|\theta| (P_{t-s}^\beta|f|)(\xi_s)+c_1|\theta|^2(P_{t-s}^\beta|f|)(\xi_s)^2\big)ds\Big]
-    %\\ &\leq \int_0^t \big(c_0|\theta|e^{t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+c_1|\theta|^2e^{2t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
-    %\\ &\leq \int_0^t (c_0|\theta|e^{t\|\beta\|}\Pi_x [ |f(\xi_{t})|]+c_1|\theta|^2e^{2t\|\beta\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
-\end{align}
+
     As a consequence, expectation
 \[
-    \added{ \Pi_x\Big[\int_0^t \psi(\xi_s,-U_{t-s}f)ds\Big]}
-    \deleted{\Pi_x\Big[\int_0^t \psi(\xi_s,-v_f(t-s,\xi_s,\theta))ds\Big]}
+     \Pi_x\Big[\int_0^t \psi(\xi_s,-U_{t-s}f)ds\Big]
     \in \mathbb C
@@
 \subsection{}
-    \added{ In this subsection, we recall the generalized spine decomposition theorem for the superprocesses.}
+     In this subsection, we recall the generalized spine decomposition theorem for the superprocesses.
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
@@
     d\mathbf P_{\delta_x}^{X_T(f)}
-    := \frac{X_T(f)}{T_t^\beta f(x)} d\mathbf P_{\delta_x};
+    := \frac{X_T(f)}{P_T^\beta f(x)} d\mathbf P_{\delta_x};
     \quad d\mathbb N_x^{W_T(f)}
-    :=  \frac{W_T(f)}{T_t^\beta f(x)} d\mathbb N_x.
+    :=  \frac{W_T(f)}{P_T^\beta f(x)} d\mathbb N_x.
 \end{equation}
@@
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
-\added{
+
 \begin{prop}
@@
 \end{prop}
-}
-\deleted{
-\begin{prop}
-%\label{prop: complex FKPP-equation}
-    Let $f\in L_2(\xi)$. Then for each $t\geq 0$, $x\in E$ and $\theta \in \mathbb R$,
-\begin{equation}
-%\label{eq: complex FKPP-equation}
-    v_f(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s, - v_f(t-s,\xi_s,\theta)\big) ds \Big]
-    \\= i\theta \Pi_{x} [f(\xi_t)],
-\end{equation}
-    and
-\begin{equation}
-%\label{eq: complex FKPP-equation with FK-transform}
-    v_f(t,x,\theta) -  \int_0^t P_{t-s}^{\beta} \psi_0\big(\cdot,-v_f(s,\cdot,\theta)\big) (x)~ds
-    \\= i\theta P_t^\beta f(x).
-\end{equation}
-\end{prop}
-}
+
 \begin{proof}
     Assume that $f\in b\mathscr B_E$.
-    Set $t>0, r\in [0,t), x\in E\deleted{, \theta \in \mathbb R}$ and $g\in b\mathscr B_E^{++}$.
+    Set $t>0, r\in [0,t), x\in E$ and $g\in b\mathscr B_E^{++}$.
     Denoted by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
@@
 \begin{align}
-&\int_{[0,t]\times \mathbb W}|e^{i \deleted{\theta} w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
-    \leq \int_{[0,t]\times \mathbb W}\big(|\deleted{\theta} w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
-    \\&\leq \int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}\big(\deleted{|\theta |} W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[\deleted{|\theta|} X_{t-s}(|f|)] \pi(\xi_s,dy)
+&\int_{[0,t]\times \mathbb W}|e^{i w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
+    \leq \int_{[0,t]\times \mathbb W}\big(| w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
+    \\&\leq \int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[ X_{t-s}(|f|)] \pi(\xi_s,dy)
     \\&\qquad\qquad+ 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
-     \\&\leq \int_0^t \deleted{|\theta|}(P_{t-s}^\beta |f|)(\xi_s)\Big(2\alpha(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
-    \\&\leq \Big(2\|\alpha\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t \deleted{|\theta|} e^{t\|\beta\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+     \\&\leq \int_0^t (P_{t-s}^\beta |f|)(\xi_s)\Big(2\alpha(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+    \\&\leq \Big(2\|\alpha\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\beta\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
     < \infty.
@@
 \begin{align}
-    &\int_{[0,t]\times \mathbb N}(e^{i\deleted{\theta} w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
-    \\&=\int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}(e^{i\deleted{\theta} W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i\deleted{\theta} X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
+    &\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
+    \\&=\int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
     \\&=\int_0^t \Big( 2\alpha(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
-    \\&\deleted{=\int_0^t \Big( 2\alpha(\xi_s) v_f(t-s,\xi_s,\theta) + \int_{(0,\infty)} y (e^{y v_f(t-s,\xi_s,\theta)} - 1) \pi(\xi_s,dy) \Big) ds}
     \\&= -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
-    \\&\deleted{= -\int_0^t \psi'_0 \big(\xi_s, -v_f(t-s,\xi_s,\theta)\big)ds.}
 \end{align}
@@
 \label{eq: N to Pi}
-    \mathbb N_x^{W_t(g)}[e^{i\deleted{\theta} W_t(f)}]
-    &=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i\deleted{\theta} w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
+    \mathbb N_x^{W_t(g)}[e^{i W_t(f)}]
+    &=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
     \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
-    \\&\deleted{= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -v_f(t-s,\xi_s,\theta))ds}]}
     \\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
-    \\&\deleted{= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta))ds} ].}
 \end{align}
@@
 \begin{equation}
-    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i\deleted{\theta} X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]}
-    = \mathbf P_{\delta_x}[e^{i\deleted{\theta} X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i\deleted{\theta} X_t(f)}].
+    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]}
+    = \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i X_t(f)}].
 \end{equation}
@@
 \begin{align}
-    \frac{\mathbf P_{\delta_x}[X_t(f)e^{i \deleted{\theta} X_t(f)}] }{\mathbf P_{\delta_x}[e^{i\deleted{\theta} X_t(f)}]}
-    &= \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i\deleted{\theta} X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i\deleted{\theta} X_t(f)}]
+    \frac{\mathbf P_{\delta_x}[X_t(f)e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
+    &= \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i X_t(f)}]
     \\& = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
-    \\& \deleted{= \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta)) ds}  ].}
 \end{align}
@@
 \begin{align}
-    \frac{\partial}{\partial \theta} \added{U_t(\theta f)(x)}\deleted{v_f(t, x, \theta) }
-    = \added{ \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ]}\deleted{ \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -v_f(t-s,\xi_s,\theta)) ds} ]}.
+    \frac{\partial}{\partial \theta} {U_t(\theta f)(x)} 
+    =  \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ]
 \end{align}
     Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
-\deleted{
+
 \begin{align}
@@
     = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -U_{t-s}(\theta f)) ds} ].
-\end{align}}
-\deleted{
-\begin{align}
-    &\frac{\partial}{\partial \theta} v_f(t - r, x, \theta)
-    = \Pi_x[ if(\xi_{t-r}) e^{-\int_0^{t-r} \psi'(\xi_s, -v_f(t-r-s,\xi_s,\theta)) ds} ]
-    \\&= \Pi_{r,x}[if(\xi_t)e^{-\int_0^{t-r} \psi'(\xi_{r+s}, -v_f(t-r-s,\xi_{r+s},\theta)) ds} ]
-    = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -v_f(t-s,\xi_{s},\theta)) ds} ].
-\end{align}
-}
-    From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, \added{$(t,x) \mapsto |\psi'(x,-U_tf(x))|$}\deleted{$(t,x) \mapsto |\psi'(x,-v_f(t,x,\theta))|$} is locally bounded (i.e.
-bounded on $[0,T]\times E$ for each $T \geq 0$).
+\end{align}
+
+    From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
     Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
-\deleted{
+
 \[
@@
     = \Pi_{r,x} [i f(\xi_t)],
-\]}
-\begin{equation}
-    \deleted{\frac{\partial}{\partial \theta} v_f(t-r, x, \theta) + \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s,- v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
-    = \Pi_{r,x} [i f(\xi_t)],}
-\end{equation}
+\]
     and
-\deleted{
 \begin{align}
@@
     = \Pi_{r,x} [i e^{\int_r^t \beta(\xi_s)ds}f(\xi_t)].
-\end{align}}
-\deleted{
-\begin{align}
-    &\frac{\partial}{\partial \theta} v_f(t-r, x, \theta) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du}\psi_0'\big(\xi_s,- v_f(t-s,\xi_s,\theta)\big)\frac{\partial}{\partial \theta} v_f(t-s, \xi_s, \theta)~ds\Big]
-    \\&= \Pi_{r,x} [i e^{\int_r^t \beta(\xi_s)ds}f(\xi_t)].
-\end{align}
-}
-    Integrating the aboves with respect to $\theta$ \added{ on [0,1]}, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we have
-\deleted{
+\end{align}
+    Integrating the aboves with respect to $\theta$  on [0,1], using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we have
+
 \begin{equation}
@@
     = i\theta \Pi_{r,x} [f(\xi_t)],
-\end{equation}}
-\begin{equation}
-    \deleted{v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
-    = i\theta \Pi_{r,x} [f(\xi_t)],}
 \end{equation}
     and similarly,
-\deleted{
 \begin{equation}
@@
     = i\Pi_{r,x} [e^{\int_r^t\beta(\xi_u)du}f(\xi_t)].
-\end{equation}}
-\begin{equation}
-    \deleted{v_f(t-r,x,\theta) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du} \psi_0\big(\xi_s,-v_f(t-s,\xi_s,\theta)\big) ~ds\Big]
-    = i\theta \Pi_{r,x} [e^{\int_r^t\beta(\xi_u)du}f(\xi_t)].}
 \end{equation}
@@
     From what we have proved, we have
-\deleted{
 \begin{equation}
@@
     = i \Pi_{x} [f_n(\xi_t)].
-\end{equation}}
-\begin{equation}
-%\label{eq: complex FKPP-equation for fn}
-    \deleted{v_{(f_n)}(t,x,\theta) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta)\big) ~ds\Big]
-    = i\theta \Pi_{x} [f_n(\xi_t)].}
 \end{equation}
@@
 \item
-    \added{ $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$}\deleted{ $v_{(f_n)}(t,x,\theta) \xrightarrow[n\to \infty]{} v_f(t,x,\theta)$} due to \eqref{eq: N and characteristic exponent}, dominated convergence theorem and the fact that
-\[
-    |e^{i\deleted{\theta} W_t(f_n)} - 1| \leq \deleted{|\theta|} W_t(|f|);
+     $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$ due to \eqref{eq: N and characteristic exponent}, dominated convergence theorem and the fact that
+\[
+    |e^{i W_t(f_n)} - 1| \leq W_t(|f|);
     \quad \mathbb N_x[W_t(|f|)] = (P_t^\beta |f|)(x) < \infty.
@@
 \item
-    \added{ $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$}\deleted{ $\Pi_{x} [\int_0^t \psi(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta))ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,v_{f}(t-s,\xi_s,\theta))ds]$} due to donimated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
-\added{
+     $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to donimated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
 \begin{align}
@@
     \leq C_{\ref{eq: upper bound of psi'(v)}.1} P_{t-s}^\beta|f|(\xi_s)+C_{\ref{eq: upper bound of psi'(v)}.2} P_{t-s}^\beta|f|(\xi_s)^2.
-\end{align}}
-\deleted{
-\begin{align}
-    \big|\psi\big(\xi_s,v_{(f_n)}(t-s,\xi_s,\theta)\big)\big|
-    \leq c_0|\theta|~(P^\beta_{t-s} |f|)(\xi_s)+c_1 |\theta|^2 ~(P^\beta_{t-s} |f|)(\xi_s)^2.
-\end{align}
-}
+\end{align}
 \end{itemize}

### 2019-01-31 SuperCLT.tex
supCLT.tex: 1118

--- 2019-01-31 supCLT.tex
@@
 %%%----Versions-----------------------------
+% supCLT5.tex ......... by Zhenyao
 % supCLT4.tex ......... by Jianjie
@@
     Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
-    Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
+    Let $\psi$ be a function on \added{$\mathbb R^d \times \mathbb R_+$}\deleted{$\mathbb R_+:= [0,\infty)$} with
+\deleted{
 \begin{equation}\label{mechanism}
@@
 \end{equation}
+}
+\added{
+\begin{equation}\label{mechanism}
+    \psi(x, z)
+    := - \alpha z + z^{1+\beta},
+    \quad x\in \mathbb R^d, z \in \mathbb R_+,
+\end{equation}
+}
         where $\alpha > 0$ and $\beta \in (0,1) $.
@@
     For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
-    Put $\|\mu\|=\langle 1,\mu\rangle$.
+    Put $\|\mu\|=\langle 1,\mu\rangle$ \added{if it is well defined}.
     We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
+\deleted{
 \begin{equation} \label{super}
@@
 \end{equation}
-        where $(t,x) \mapsto u_f(t,x)$ is the unique locally bounded positive solution to the equation
+}
+\added{
+\begin{equation} \label{super}
+    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
+    = e^{-\langle V_tf, \mu \rangle},
+    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
+\end{equation}
+}
+    where \deleted{$(t,x) \mapsto u_f(t,x)$} \added{$(t,x) \mapsto V_tf(x)$} is the unique locally bounded positive solution to the equation
+\deleted{
 \begin{equation}\label{eq1}
@@
 \end{equation}
-
+}
+\added{
+\begin{equation}\label{eq1}
+	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
+	= \Pi_x [f(\xi_t)],
+    \quad x\in \mathbb R^d, t\geq 0.
+\end{equation}	
+}
+
+\deleted{
 	The existence of such superprocesses is well known, see \cite{EB} for instance.
+}
+\added{
+	The existence of superprocesses are well known, see \cite{EB} for instance.
+}
     Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
@@
     = \langle T_t^\alpha f, \mu \rangle,
-    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
+    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d)\added{, \mu \in \mathcal M(\mathbb R^d)}.
 \end{equation}
@@
 \begin{equation}\label{order}
-    \added{\kappa_f}\deleted{\kappa(f)}
+    \kappa_f
     :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb N_0^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
@@
     In particular, the order of any constant function is zero.
-
+{
+    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ with
+\begin{equation}
+    \mathcal{P}
+    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+\end{equation}
+    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
+    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that,
+\begin{equation}
+\label{eq:semigroupineq}
+    |T_tf(x)|
+    \leq e^{-\kappa_f bt} R(x),
+    \quad t\geq 0, x\in \mathbb R^d.
+\end{equation}
+	For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$. 
+	Then $Q$ is an operator form $\mathcal P$ to $\mathcal P \cap \mathscr B
+	(\mathbb R^d,\mathbb R_+)$.
+}
+\deleted{
 \subsection{}
@@
 \end{defi}
-
     Suppose that $\alpha, \beta \in \mathbb R$.
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-    \added{ For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.}
-\added{
+    For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.
     According to \cite[Fact 1.2]{MM}, $Q$ is an $1$-scalable operator on $\mathcal P$.
-}
-\deleted{
     According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R_0 \in \mathcal{P}$ such that,
@@
 }
-
+{\bf Zhenyao: I moved the next subsection in the appendix.}
+\deleted{
 \subsection{}
@@
 \end{proof}
+}
 \subsection{}
-    Let $X$ be the super OU-process discussed in the previous subsections.
-    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
-    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
+    Let $X$ be the super OU-process discussed in the \deleted{previous subsections} \added{first subsection}.
+    Its branching mechanism $\psi$ can be extended on \deleted{$\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$} \added{$\mathbb R^d\times \mathbb C_+$ by $\psi(x, z) := -\alpha z + z^{1+\beta}$ for each $x\in \mathbb R^d$ and $z\in \mathbb C_+$}.
+    According to the above analysis, \added{for each $x\in \mathbb R^d$}, $\psi\added{(x,\cdot)}$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
 \begin{equation}
 \label{eq: deriavetive of the Poission part}
-    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
-    \quad z\in \mathbb C_+.
-\end{equation}
-    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
-    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in E$, define $\Psi_0f(x) := \psi_0(x,f(x))$ and $\Psi'_0 f(x) := \psi'_0(x,f(x))$.
+    \psi'(\added{x,}z) := -\alpha + (1+\beta)z^{\beta},
+    \quad \added{x\in \mathbb R^d}, z\in \mathbb C_+.
+\end{equation}
+    Write $\psi_0(\added{x,}z) := \psi(\added{x,}z) + \alpha z$ and $\psi'_0(\added{x,}z) := \psi'(\added{x,}z) + \alpha$.
+    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in \deleted{E}\added{\mathbb R^d}$, define $\Psi_0f(x) := \psi_0(x,f(x))$ and $\Psi'_0 f(x) := \psi'_0(x,f(x))$.
     For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
     (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
-    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ taks values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
+    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ take values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
 \begin{align}
@@
 
-%new added
-%end new added
-%begin comments
     {\bf Zhenyao: There are notation inconsistency in the Appendix and other sections. Mainly on the branching mechanism: In the appendix, we use
@@
 \]
-    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.
-
-    Though I recommended all those changes, I did not try to make them in this version (in order to not mess things up).
-I would like Jianjie to decide which set of notations is better.
-Overall, I am fine with any set of notations as long as they are consistent with each other and don't raise any confusions.}
-%end comments
+    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.}
 
@@
     In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
-
+\deleted{
     Consider an incremental decomposition of $\langle g,X_t \rangle$.
@@
     For each $g\in \mathcal P$ and $0 \leq a \leq b \leq t <\infty$, define random variable
-
-\[
-   \deleted{ M_{r,s}\langle g,X_t\rangle} \added{M_g^t(a,b)}
+\[
+   	M_g^t(a,b)
     := \mathbb P_{\mu}[\langle g,X_t\rangle|\mathscr F_b] - \mathbb P_{\mu}[\langle g,X_t\rangle|\mathscr F_a]
@@
 \]
-
     Thus, we have
@@
 \end{align}
-    Note that
+    Note that $I_a^b[\langle g,X_t \rangle] = I_a^b[\langle g,X_t\rangle]$
 \begin{align}
@@
 \end{align}
-
-\subsection{}
-    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R^+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
+}
+
+\added{
+	For each $0 \leq a \leq b <\infty$ and  random variable $Y$ with finite mean, define random variable
+$
+   	I_a^b[Y]
+    := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
+$
+	Then we have an nature incremental decomposition of $Y$:
+\begin{align}
+    I_0^t[Y]
+    = \sum_{k = 0}^{\lfloor t \rfloor - 1} I_k^{k+1}[Y] + I_{\lfloor t \rfloor}^t[Y],
+    \quad t\geq 0.
+\end{align}
+	The random variable we are interested in is $Y:= \langle g,X_t\rangle$. 
+	In this case we have
+\begin{align}
+    I_a^b[\langle g,X_t\rangle] 
+    = I_a^b\big[\mathbb P[\langle g,X_t\rangle|\mathscr F_b]\big]
+    = I_a^b[ \langle T_{t-b}^\alpha g, X_b \rangle ].
+\end{align}
+}
+
+    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
     We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
@@
     We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P^+$.
-    We say an operator $A$ is $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and \added{$\mathcal D \subset \mathcal P^*$}\deleted{$\mathcal D \subset \mathcal P$} if $A: \mathcal D \to \mathcal P^*$ and there exits a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
+    We say an operator $A$ is $\gamma$-controllable on $\mathcal D \added{\subset \mathcal P^*}$ for some $\gamma \in \mathbb R$ \deleted{and $\mathcal D \subset \mathcal P^*$} if $A: \mathcal D \to \mathcal P^*$ and there \deleted{exits} \added{is} a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
     In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
-    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$ if there exits a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(\added{R}\deleted{M}, S)$ on $\mathcal D$ for each $s\in \Lambda$.
+    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\added{\subset \mathcal P^*}$ for some $\gamma \in \mathbb R$ \deleted{and $\mathcal D \subset \mathcal P^*$} if there \deleted{exits} \added{is} a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(\added{R}\deleted{M}, S)$ on $\mathcal D$, for each $s\in \Lambda$.
 
@@
 }
+\deleted{
     For two operators $A$ and $B$ defined on same domain $\mathcal D\subset \mathcal P^*$, write $(A\times B)f (x):= Af(x) \times Bf(x)$.
     Let $a \in \mathbb R$, write $A^{\times a}f(x):= (Af(x))^a$ as long as it is well defined for all .
+}
+\added{
+	For two operators $A: \mathcal D_A \to \mathcal P^*$ and $B: \mathcal D_B \to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for each $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
+    Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for each $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
+}
     The second reason for considering $\gamma$-controllable operators is that they have good algebra properties:
@@
 \item[(2)]
-    Suppose that operators $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$.
+    Suppose that operators $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$ \added{for some $\beta \in \mathbb R$}.
     Also suppose that for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
@@
 \item[(4)]
-    Let $a\in \mathbb R$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
+    Let \deleted{$a\in \mathbb R$} \added{$a>0$}. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
     Then operators $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ are uniformly $(a\gamma)$-controllable.
@@
 \end{lem}
-\added{
 \begin{proof}
@@
    	Proof of (2): Let $(R_A, S_A)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$ and $(R_B, S_B)$ be the $\beta$-control-pair of $(B_{\delta})_{\delta\in\Delta}$ on $\mathcal{D}_0$.
-
-   For each $f\in \mathcal{P}^+$ and $\theta \geq 0$, $S_BS_A(\theta f)=S_b(\theta^{\gamma}S_Af)=\theta^{\beta\gamma}S_BS_Af$.
-
-   For each $f,g \in \mathcal P^+$ with $f\leq g$, $R_B(R_A f)\leq R_B(R_A g)$ and $R_B (R_A f)\leq R_B(S_A f)\leq S_BS_A f$.
-
-   For each $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|,~~\delta\in \Delta, \lambda\in\Lambda$.
-
-   Thus $(R_BR_A,S_BS_A)$ is a $\beta\gamma$-control-pair of operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$.
+\added{ 
+	Note that $(R_BR_A, S_BS_A)$ is a $\beta \gamma$-control-pair. 
+	In fact:
+\begin{itemize}
+\item
+	For each $f,g \in \mathcal P^+$ with $f\leq g$, since $R_Af \leq R_A g$ we have $R_B(R_A f)\leq R_B(R_A g)$.
+\item
+	For each $f\in \mathcal{P}^+$ and $\theta \geq 0$, we have $S_BS_A(\theta f)=S_B(\theta^{\gamma}S_Af)=\theta^{\beta\gamma}S_BS_Af$.
+\item
+	For each $f,g \in \mathcal P^+$ with $f\leq g$, we have $R_B R_A f \leq R_B S_A f \leq S_BS_A f$. 
+\end{itemize}
+	Finally, note that for each $\delta\in \Delta, \lambda\in\Lambda$ and $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|$ which says that operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ are uniformly $(\beta\gamma)$-controlled by $(R_BR_A,S_BS_A)$.
+}
 
@@
 \end{proof}
-}
 \subsection{}
@@
 \label{lem: upper bound for usgx}
-$~$
+\added{The following statements are true for the super-OU process considered in the first subsection:}
 \begin{itemize}
@@
 \]
-    Note that $f\mapsto\sup_{0\leq u\leq 1}T_u|f|$ is monotonic and $1$-scalable.
+    Note that $f\mapsto\sup_{0\leq u\leq 1}T^{\added{\alpha}}_u|f|$ is monotonic and $1$-scalable. 
+    \added{Combine this with \eqref{eq: -v has positive real part}, we get the desired result.}
 
@@
     are uniformly $(1+\beta)$-controllable.
-    From Lemma \ref{lem: property of controllable operators}(1) and above we get the desired result.
+    From \added{\eqref{eq:chareq2},} Lemma \ref{lem: property of controllable operators}(1) and this we get the desired result.
 
@@
 \[
-    \mathbb P_\mu (|M^t_g(0,t)| > \lambda)
+    \mathbb P_\mu (|\deleted{M^t_g(0,t)} \added{I_0^t[\langle g,X_t\rangle]}| > \lambda)
     \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta
-    \leq \langle S| g|,\mu\rangle \frac{1}{\lambda^{1+\beta}}.
+    \deleted{\leq \langle S| g|,\mu\rangle \frac{2^{2+\beta/(2+\beta)}}{\lambda^{1+\beta}}}.
 \]
 \end{lem}
-
-\begin{proof}
-    Denote by $(R_0,S_0)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}.
-    Using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, we have
-\begin{align}
-    &\mathbb P_\mu (|M^t_g(0,t)| > \lambda)
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{i\theta M_g^t(0,t)}]\Big)d\theta
-    = \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{iM_{(\theta g)}^t(0,t)}]\Big)d\theta
-    \\&= \added{\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}\Big) d\theta}
+\added{
+\begin{proof}
+    Denote by $(R,S)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}(4).
+    Using Lemma \ref{lem: estimate of exponential remaining} and the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, we have
+\begin{align}
+    &\big|\mathbb P_\mu (|I_0^t[\langle g,X_t\rangle]| > \lambda)\big|
+    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta I_0^t[\langle g,X_t\rangle]}])d\theta\Big|
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}|d\theta
     \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iT_t^\alpha(\theta g)|,\mu\rangle d\theta
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta g|,\mu\rangle d\theta
-      \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta g|,\mu\rangle d\theta
-\end{align}
-    To finish the proof we write $R=R_0$ and $S= S_0$.
-\end{proof}
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
+      \qedhere
+\end{align}
+\end{proof}
+}
+
+{\bf Zhenyao: I will change $M_g^t(a,b)$ to $I_a^b[\langle g,X_t\rangle]$ without mention. Here ``I'' means incremental.}
 
@@
 \[
-    \mathbb P_{\mu}(|M^t_g(r,s)|>\lambda)
-    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle Sg,\mu\rangle
+    \mathbb P_{\mu}(|\added{I_r^s[\langle g, X_t\rangle]}|>\lambda)
+    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle S\added{Q}g,\mu\rangle.
 \]
@@
     Then using Markovian property of $(X_t)_{t\geq 0}$ we get
-\begin{align}
-    &\mathbb P_{\mu}(|M^t_g(r,s)|>\lambda)
-    = \mathbb P_\mu \big[\mathbb P_\mu\big(|M_g^t(r,s)|> \lambda\big| \mathscr F_r\big)\big]
-    = \mathbb P_\mu \big[\mathbb P_{X_r}(|M^{t-r}_g(0,s-r)|> \lambda)\big]
-    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|M^{s-r}_{T^\alpha_{t-s}g}(0,s-r)|> \lambda)\big]
-    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
-    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
-    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
-    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \mathbb P_\mu [ \langle S_0Qg,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
+\added{
+\begin{align}
+    &\mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda)
+    = \mathbb P_\mu \big[\mathbb P_\mu[|\langle T_{t-s}^\alpha g, X_{s}\rangle - \langle T_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r]\big]
+    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle T_{t-s}^\alpha g, X_{s-r}\rangle - \langle T_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
+    = \mathbb P_\mu \big[\mathbb P_{X_r}(|I_0^{s-r}[\langle T_{t-s}^\alpha g, X_{s-r}\rangle] |> \lambda)\big]
+    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
+    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
+	\\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
+    = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \mathbb P_\mu [ \langle S_0Qg,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
     \\& = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \langle T_r^\alpha S_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
@@
 \end{align}
+}
     Note that
 \[
-    S := \frac{2^{2+\beta}}{2+\beta}QS_0Q
+    S := \frac{2^{2+\beta}}{2+\beta}QS_0\deleted{Q}
 \]
@@
 \[
-    \mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big]
+    \mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
     \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb)}.
@@
 \begin{proof}
+	\added{Let $S$ be the $(1+\beta)$-scalable operator in the previous Lemma.}
     For each $c>0$ we have
 \begin{align}
-    &\mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big]
-    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|M^t_g(r,s)|>\lambda) d\lambda
-    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|M^t_g(r,s)|> \lambda) d\lambda
-    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle Sg,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
-    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle Sg,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
+    &\mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
+    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda) d\lambda
+    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|I_r^s[\langle g, X_t\rangle]|> \lambda) d\lambda
+    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle S\added{Q}g,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
+    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle S\added{Q}g,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
 \end{align}
@@
 \begin{align}
-    &\mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big]
-    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa_gb)} e^{\alpha r}\Big(1+ \langle Sg,\mu\rangle \frac{1+\gamma}{\beta - \gamma}\Big).
+    &\mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
+    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa_gb)} e^{\alpha r}\Big(1+ \langle SQg,\mu\rangle \frac{1+\gamma}{\beta - \gamma}\Big).
 \end{align}
@@
 \begin{comment}
-\deleted{
-\begin{lem}\label{lem: lemma23}
-For each $0< \gamma < \beta$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_1>0$ such that, for each $t >0$ and $k \in \{0,\dots,\lfloor t \rfloor\}$, we have
-\begin{align}
-\label{eq: upper bound of 1+gamma moment of Mktg}
-    \mathbb P_\mu\big[|M_k^t[g]|^{1+\gamma}\big]
-    \leq C_1 C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))k}.
-\end{align}
-and
-\begin{align}
-    \mathbb P_\mu\big[|M_t^t[g]|^{1+\gamma}\big]
-    \leq C_1 C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))t}.
-\end{align}
-\end{lem}
-\begin{proof}
-    For each $g \in \mathcal P$, $t\geq 0$, $\gamma \in (0,\beta)$ and $\mu$ with compact support:
-\begin{align}
-    \mathbb P_\mu\big[|M_t^t[g]|^{1+\gamma}\big]
-    = |\langle g_t, \mu\rangle|^{1+\gamma}
-    \leq \langle e^{\alpha t} |T_tg|, \mu\rangle^{1+\gamma}
-    \leq \langle e^{\alpha t}e^{-\kappa(g)bt}Q[g],\mu\rangle^{1+\gamma}
-\leq (e^{\alpha t}e^{-\kappa(g)bt})^{1+\gamma}\langle Q[g],\mu\rangle^{1+\gamma}.
-\end{align}
-    This proves the Lemma in the case that $M_t^t[g]$.
-    So we only have to consider the case when $k \in \{0,\dots,\lfloor t \rfloor\}$.
-    Let $c_k=e^{(\alpha-\kappa b)k}$.
-    For each $\nu \in \mathcal M(\mathbb R^d)$ with compact support and $0\leq s\leq 1$, denote by $\varphi_{k,\nu,s}$ the characteristic function of $\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle$.
-
-    Step 1. We will show that there exeists an $\tilde R^g_3 \in \mathcal P$ such that for each $\nu \in \mathcal M(\mathbb R^d)$ with compact support and $\lambda > C_g c_k$ we have
-\begin{align}
-    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle|>\lambda)
-    \leq \langle \tilde R^g_3,\nu\rangle \Big(\frac{C_g c_k}{\lambda}\Big)^{1+\beta}, \quad 0\leq s \leq 1.
-\end{align}
-    In fact, using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, letting $R^g_2 \in \mathcal P$ and $R^g_3 \in \mathcal P$ be the control functions in Corollary \ref{cor: corollary2} and Corollary \ref{cor: corollary1}, we have
-\begin{align}
-    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle|>\lambda)
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1-\varphi_{k,\nu,s}(\theta))d\theta
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\langle Z_{g_k}(s,\cdot,\theta),\nu\rangle|+|err(k,\nu,\theta)|\big)d\theta
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\theta C_g c_k|^{1+\beta}+|\theta C_g c_k|^{1+2\beta}+ |\theta C_g c_k|^{2+2\beta}\big)d\theta \times \langle R^g_2+R^g_3,\nu\rangle
-    \\& = \bigg(\frac{2^{2+\beta}}{2+\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{1+\beta}+\frac{2^{2+2\beta}}{2+2\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{1+2\beta} + \frac{2^{3+2\beta}}{3+2\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{2+2\beta}\bigg) \langle R^g_2+R^g_3,\nu\rangle.
-\end{align}
-    This implies the desired result in Step 1.
-
-    Step 2.
-Let $\tilde R^g_3\in \mathcal P$ be the control function in Step 1, we will show that for each $\nu\in \mathcal M(\mathbb R^d)$ with compact support, $k\in \mathbb N$, $\gamma \in (0,\beta)$ and $0\leq s \leq 1$,
-\[
-    \int_{C_g c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_s\rangle - \langle T_{k+s}^\alpha g, \nu\rangle|> \lambda) d\lambda
-    \leq \frac{1}{\beta-\gamma} \langle \tilde R^g_3,\nu\rangle (C_g c_k)^{1+\gamma}.
-\]
-    In fact, a direct application of Step 1 shows that
-\begin{align}
-    &\int_{C_g c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_s\rangle - \langle T_{k+s}^\alpha g, \nu\rangle|> \lambda) d\lambda
-    \\&\leq \langle \tilde R^g_3,\nu \rangle (C_g c_k)^{1+\beta}\int_{C_g c_k}^\infty \lambda^{\gamma-1-\beta}d\lambda
-    = \frac{1}{\beta-\gamma}\langle \tilde R^g_3,\nu \rangle (C_g c_k)^{1+\gamma}.
-\end{align}
-
-    Step 3.
-    Let $\tilde R^g_3\in \mathcal P$ be the control function in Step 1 and 2. According to \eqref{eq:semigroupineq}, there exists an $\tilde R^g_4\in \mathcal P$ such that
-$
-    |T_t(\tilde R^g_3)(x)|
-    \leq \tilde R^g_4(x),
-$
-    for each $t\geq 0$ and $x\in \mathbb{R}^d$.
-    Therefore, for each $\mu \in \mathcal M(\mathbb R^d)$ with compact support, $t\geq 0$ and $k \in \{1,\dots,\lfloor t \rfloor-1\}$, we have
-\begin{align}
-    &\mathbb P_\mu\big[|M_k^t[g]|^{1+\gamma}\big] = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|M_k^t[g]|>\lambda) d\lambda
-    \\&\leq (C_g c_k)^{1+\gamma}+(1+\gamma)\int_{C_g c_k}^\infty \lambda^{\gamma}\mathbb P_\mu(|M_k^t[g]|> \lambda) d\lambda
-    \\&\leq (C_g c_k)^{1+\gamma}+(1+\gamma)\int_{C_g c_k}^\infty \lambda^{\gamma}\mathbb P_\mu \big[\mathbb P_\mu\big(|M_k^t[g]|> \lambda\big| \mathscr F_{t-k-1}\big)\big] d\lambda
-    \\&\leq (C_g c_k)^{1+\gamma}+(1+\gamma)\int_{C_g c_k}^\infty \lambda^{\gamma}\mathbb P_\mu \big[\mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda)\big|_{\nu=X_{t-k-1}}\big] d\lambda
-    \\&\leq (C_g c_k)^{1+\gamma}+\mathbb P_\mu\Big[(1+\gamma)\int_{C_g c_k}^\infty \lambda^{\gamma} \mathbb P_\nu(|\langle T_k^\alpha g,X_1\rangle - \langle T_{k+1}^\alpha g, \nu\rangle|> \lambda) d\lambda\Big|_{\nu=X_{t-k-1}}\Big]
-    \\&\leq (C_g c_k)^{1+\gamma}+\mathbb P_\mu\Big[\frac{1+\gamma}{\beta- \gamma}\langle \tilde R^g_3,X_{t-k-1}\rangle (C_g c_k)^{1+\gamma}\Big]
-    \\&= (C_g c_k)^{1+\gamma}+\frac{1+\gamma}{\beta- \gamma}(C_g c_k)^{1+\gamma} \langle T_{t-k-1}^{\alpha}\tilde R^g_3,\mu\rangle
-    \\&\leq \Big(1+ \frac{1+\gamma}{\beta - \gamma} \langle \tilde R^g_4,\mu\rangle\Big) e^{\alpha(t-k-1)}(C_g c_k)^{1+\gamma}
-    \\&\leq \Big(1+ \frac{1+\gamma}{\beta - \gamma} \langle \tilde R^g_4,\mu\rangle\Big) C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))k}.
-\end{align}
-On the case $k=\lfloor t \rfloor$, also we have
-\begin{align}
-     &\mathbb P_\mu\big[|M_{\lfloor t \rfloor}^t[g]|^{1+\gamma}\big]\leq (C_g c_{\lfloor t \rfloor})^{1+\gamma}+(1+\gamma)\int_{C_g c_{\lfloor t \rfloor}}^\infty \lambda^{\gamma}\mathbb P_\mu(|M_{\lfloor t \rfloor}^t[g]|> \lambda) d\lambda
-     \\ & = (C_g c_{\lfloor t \rfloor})^{1+\gamma}+(1+\gamma)\int_{C_g c_{\lfloor t \rfloor}}^\infty \lambda^{\gamma}\mathbb P_\mu(|\langle T^{\alpha}_{\lfloor t \rfloor}g,X_{t-\lfloor t\rfloor}\rangle-\langle T^{\alpha}_t g, \mu\rangle|> \lambda) d\lambda
-     \\ &\leq \Big(1+\frac{1+\gamma}{\beta-\gamma}\langle \tilde{R}^g_3, \mu\rangle\Big) (C_g c_{\lfloor t \rfloor})^{1+\gamma}\leq \Big(1+\frac{1+\gamma}{\beta-\gamma}\langle \tilde{R}^g_3, \mu\rangle\Big) C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))\lfloor t \rfloor}.
- \qedhere
-\end{align}
-\end{proof}
-}
 \end{comment}
-    As $\langle g,X_t\rangle,~g\in \mathcal{P}$ is the sum of $M_g^t(k,k+1), k=0,1,...,\lfloor t\rfloor$ and $M_g^t(\lfloor t\rfloor, t)$. We obtain the following lemma.
+    \deleted{As $\langle g,X_t\rangle,~g\in \mathcal{P}$ is the sum of $M_g^t(k,k+1), k=0,1,...,\lfloor t\rfloor$ and $M_g^t(\lfloor t\rfloor, t)$. We obtain the following lemma.}
 
@@
     \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\| M_g^t(t-k-1,t-k)\|_{\mathbb P_\mu;1+\gamma}+\|M_g^t(0, t-\lfloor t \rfloor)\|_{\mathbb P_\mu;1+\gamma}
+    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| I_{t-k-1}^{t-k}[\langle g,X_t\rangle] \big\|_{\mathbb P_\mu;1+\gamma}+\big\| I_{0}^{t-\lfloor t \rfloor}[\langle g,X_t\rangle]  \big\|_{\mathbb P_\mu;1+\gamma}
     \\ &\leq C e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa_g (1+\gamma)b}{1+\gamma} k} .
@@
 \label{defmartingale}
-    M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds
-\end{align}
-    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathcal{F}_t\}_{t\geq 0}$.
+    M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds.
+\end{align}
+{\bf Zhenyao: we should show that it is well defined.}
+    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra \added{$\{\mathscr{F}_t\}_{t\geq 0}$}.
+{\bf Zhenyao: I changed all $\mathcal F$ to $\mathscr F$ without mention below. I want to use mathscr for $\sigma$-fields and mathcal for function classes.}
 \begin{lem}
@@
 \label{martingale1}
-    &\mathbb{P}_{\mu}[M_t^{f,a}|\mathcal{F}_s]
-    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathcal{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathcal{F}_s\big]
+    &\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
+    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
     \\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du -\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
@@
     &\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle T_{u-s}^{ab}\bar{f},X_s\rangle~du\\
-    &=e^{-(\alpha-ab)s}\langle\int_0^{t-s}T_{u}^{ab}\bar{f}~du,X_s\rangle=e^{-(\alpha-ab)s}\left(\langle T_{t-s}^{ab}f,X_s\rangle-\langle
+    &=e^{-(\alpha-ab)s}\Big\langle\int_0^{t-s}T_{u}^{ab}\bar{f}~du,X_s\Big\rangle=e^{-(\alpha-ab)s}\left(\langle T_{t-s}^{ab}f,X_s\rangle-\langle
     f,X_s\rangle\right)\\
@@
     There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$.
-    Using  Lemma \ref{lemma24} and the fact $\kappa_{\phi_p}=|p|$, we get that, for any $\gamma_0\leq\gamma<\beta$, there exists a constant $C$ such that
-    $$\|H_t^p\|_{1+\gamma}\leq Ce^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}=C.$$
-    For any $0\leq\gamma<\gamma_0$, consider the concave function $x\mapsto x^{(1+\gamma)/(1+\gamma_0)}$ on $[0,\infty)$, using Jensen's inequality, we have
-    $$\mathbb{P}_{\mu}|H_t^p|^{1+\gamma}\leq(\mathbb{P}_{\mu}|H_t^p|^{1+\gamma_0})^{\frac{1+\gamma}{1+\gamma_0}}<\infty.$$
-    Hence the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicate the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ an almost sure,
+    Using  Lemma \ref{lemma24} and the fact $\kappa_{\phi_p}=|p|$, we get that, \deleted{for any $\gamma_0\leq\gamma<\beta$,} there exists a constant $C_{\gamma, \mu, p} \added{>0}$ \added{(which depends on the choice of $\gamma$, $\mu$ and $p$)}  such that
+ \added{
+ $$
+ 	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
+    \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
+    =C_{\gamma, \mu, p}, \quad t\geq 0.
+ $$
+ }
+    For any $0\leq\gamma<\gamma_0$, \deleted{consider the concave function $x\mapsto x^{(1+\gamma)/(1+\gamma_0)}$ on $[0,\infty)$, using Jensen's inequality, we have} \added{note that}
+\added{
+$$
+	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
+	\leq\|H_t^p\|_{\mathbb P_\mu;1+\gamma_0}
+	<C_{\gamma_0, \mu, p},
+	\quad t\geq 0.
+$$
+}
+
+    Hence \added{, for each $\gamma \in (0,\beta)$,} the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicate\added{s} the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ and almost sure,
 %added
@@
     under $\mathbb{P}_{\mu}$, the process $W_t=e^{-\alpha t}\|X_t\|$ is a positive martingale satisfying
-$$\lim_{t\rightarrow \infty} W_t= W_{\infty}$$
+$\lim_{t\rightarrow \infty} W_t= W_{\infty},$
 $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 So $W_{\infty}$ is non-degenerate and the $(1+\gamma)$-th moment is finite.
-Moreover,  we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D$ which is the extinction event.
+Moreover,  we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D,$ \added{$\mathbb{P}_{\mu}$-a.s} \deleted{which is the extinction event}.
 %comment
-    {\bf Zhenyao: we need references for the last assertion.}
+    {\bf Zhenyao: we need references for the last assertion. Also, we used three different notation $M, H$ and $W$ to denote one martingale. This is unnessary.}
 %end comment
@@
  %For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have
- For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C_{\ref{lem: control of Wt}}> 0$ such that for each $0\leq s<t$,
- $$\|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq C_3 e^{-\alpha s/2}.$$
+ For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a \added{$C> 0$} such that for each $0\leq s<t$,
+ $$\|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq \added{C} e^{-\alpha s/2}.$$
 \end{lem}
@@
     Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-    According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
-    \begin{align}
-        \mathbb{P}_{\mu}[|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\||^{1+\gamma}]=\mathbb{P}_{\mu}[|M_1^t(r,s)|^{1+\gamma}]\leq Ce^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)b)}.
+    According to Lemma \ref{lem: control of mgtrs}, there exists a constant \added{$C_0>0$}, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
+    \begin{align}
+        \mathbb{P}_{\mu}\big[\big|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\|\big|^{1+\gamma}\big]
+        \deleted{=\mathbb{P}_{\mu}[|M_1^t(r,s)|^{1+\gamma}]}
+        \leq \added{C_0}e^{\alpha t+(t-s)\deleted{(}\alpha\gamma\deleted{-(1+\gamma)b)}}.
     \end{align}
@@
     \begin{align}
-        \mathbb{P}_{\mu}\left|W_s-W_r\right|^{1+\gamma}\leq  C e^{-\alpha \gamma s}.
-    \end{align}
-    Then for any $0\leq s<t$,
+        \mathbb{P}_{\mu}\left|W_s-W_r\right|^{1+\gamma}\leq  \added{C_0} e^{-\alpha \gamma s}.
+    \end{align}
+    Then \added{there is a $C>0$,} for any $0\leq s<t$,
+\deleted{
     \begin{align}
@@
     \end{align}
+}
+\added{
+\begin{align}
+	& \|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}
+	\leq \|W_{\lfloor s \rfloor+1}-W_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|W_{k+1}-W_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|W_t-W_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
+	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
+	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
+\end{align}	
+}
 \end{proof}
@@
 We want to prove the following Lemma
+\added{
 \begin{lem}\label{lem: control of XT}
-Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function satisfying $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$, Then for any $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C_{\ref{lem: control of XT}}>0$ such that
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_4 \exp(\beta(\ln f(t)-\alpha t)), \quad t\geq 0.
+	For each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for each function $f:[0,\infty)\to [1,\infty)$ and each $t\geq 0$ we have
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)\leq C \Big(\frac{f(t)}{e^{\alpha t}}\Big)^{\beta}.
 \end{align}
 \end{lem}
-\begin{proof}
- Without loss of generality, we assume that $\|\mu\|=1$, By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|)}]\\
-    &\leq \frac{1}{1-e^{-\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
-\end{align*}
-Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t},~ t\geq 0,\lambda\geq0$, $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
-\begin{align*}
-    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\cdot\left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right|\\
-    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t}\\
-    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}
-\end{align*}
-Therefore,
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}\cdot \frac{1}{1-e^{-\alpha^*}} e^{\lambda f(t)}.
-\end{align*}
+}
+\begin{proof}
+ \deleted{Without loss of generality, we assume that $\|\mu\|=1$,} By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
+\added{
+\begin{align*}
+    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]\\
+    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
+\end{align*}
+}
+	Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t}$ where $t\geq 0,\lambda\geq0$ then $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
+\added{Note that}
+\begin{align*}
+    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta} \left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right| \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
+    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
+    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
+\end{align*}
+Therefore, \added{for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for each non-negative function $f$ on $[0,\infty),$ each $\lambda \geq 0$ and each $t\geq 0$ we have }
+\begin{align}
+\label{eq: inequality before take lambda}
+    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)
+    \leq C_0e^{\lambda f(t)}\frac{1}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
+\end{align}
+\deleted{
 Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
@@
 \end{align*}
+}
 Notice that
@@
     \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
-    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.
-\end{align*}
-This is to say
-\begin{align*}
-    \sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}&\leq\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
-    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}
-\end{align*}
-We conclude the lemma by taking $C_{\ref{lem: control of XT}}= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
-\end{proof}
-Define $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\},\quad \epsilon,t>0$.
+    &\added{\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.}
+\end{align*}
+This is to say \added{for each $\lambda \in [0,1]$,
+\begin{align*}
+    \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}
+    &\leq\sup_{s\in [\lambda,\lambda+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
+    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}} =: C_1.
+\end{align*}
+}
+\added{Finally, taking $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.}
+\end{proof}
+	Define $\mathcal{A}_t(\epsilon):=\{ \|X_t\|\in \|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\}$ where $\epsilon,t>0$.
+\deleted{
 \begin{lem}\label{lem: control of AT}
-  For any $\epsilon,t>0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exists $C_{\ref{lem: control of AT}}>0$ and $\delta_{\ref{lem: control of AT}}>0$ such that
-  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_{\ref{lem: control of AT}} e^{-\delta_{\ref{lem: control of AT}} t}.$$
+  For any $\epsilon,t>0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$ and $\delta>0$ such that
+  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\delta t}.$$
 \end{lem}
-
-\begin{proof}
-    First, for any $\epsilon>0$, using Markov inequality, we get
-    $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.$$
+}
+\added{
+\begin{lem}\label{lem: control of AT}
+  For each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ there exists $C>0$ such that for each $t\geq 0$ we have
+  $
+  \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\beta\epsilon t}.
+  $
+\end{lem}
+}
+
+\begin{proof}
+    First, for any $\epsilon>0$, using Markov inequality, \added{we get for each $\epsilon>0$ and $t\geq 0$,}
+\added{
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})
+    \leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}
+	= \frac{\mathbb P_\mu[\|X_t\|\mathbf 1_{D^c}]}{\mathbb P_\mu(D^c)\|\mu\|e^{(\alpha+\epsilon)t}}
+    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.
+\end{align}
+}
     For another side, using Lemma \ref{lem: control of XT}, we have
-    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_{\ref{lem: control of XT}} e^{-\beta\epsilon t}, $$
-To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.
+    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_0 e^{-\beta\epsilon t}, $$
+    \added{for some constant $C_0>0$ not related to $\epsilon>0$ and $t\geq 0$.}
+\deleted{To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.}
 \begin{comment}
@@
 \subsection{Parameters}
+\deleted{ In this subsection, we will introduce an important parameter of $(1+\beta)$-stable distribution: $m_k[f],~~f\in \mathcal{P}$.}
 \added{ 
- In this subsection, we will introduce an important parameter of $(1+\beta)$-stable distribution: $m_k[f],~~f\in \mathcal{P}$.
-
- Let $Zf(x)=Z_1f(x),~x\in\mathbb{R}^d$ and 
+ Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}, define 
  \begin{align}\label{parameter_mk}
-      m_k[f]:=e^{-\alpha(k+1)}\langle Z(T_k^{\alpha}f),\varphi\rangle,\quad k\in \mathbb{N}.
- \end{align}
- }
+      m_t[f]:=e^{-\alpha (t+1)}\int_{\mathbb R^d} (Z_1T_t^{\alpha}f)(x)\varphi(x)dx,\quad t\geq 0, f\in \mathcal P.
+ \end{align}
+ }
+\added{
 \begin{lem}\label{lem: control of mk}
-For each $f\in\mathcal{P}$, there exists constant $C_{\ref{lem: control of mk}}>0$ such that for any $k\in \{0,1,...,\lfloor t\rfloor\}$, we have
-$$|m_k[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))k}.$$
+For each $f\in\mathcal{P}$, there is a constant $C>0$ such that for each $t\geq 0$, we have
+$$|m_t[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))t}.$$
 \end{lem}
+}
+{\bf Zhenyao: It seems to me that the definition of $m_k[f]$ is exactly the same as in Milos' paper. Why we prove its properties again?}
 \begin{proof}
 \added{
-According to Lemma \ref{lem: upper bound for usgx}, there exists an $(1+\beta)$-control-pair $(R,S)$ suct that for each $k\in\mathbb{N}$,
-\begin{align}
-    |Z(T^{\alpha}_k f)|\leq R|T^{\alpha}_k|\leq R (e^{(\alpha-\kappa_fb)k}Qf)\leq S(e^{(\alpha-\kappa_fb)k}Qf)=e^{(\alpha-\kappa_fb)(1+\beta)k}SQf.
-    \end{align}
-}
-\deleted{
-Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{eq: zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
-\begin{align}
-    |Z_{f_k}(x)|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_2^f(x), \quad x\in \mathbb{R}^d, k\in\mathbb{N}.
-\end{align}
-}
-This implies the result by simply calculating.
+	Let $(R,S)$ be the $(1+\beta)$-control-pair corresponding to \ref{lem: upper bound for usgx}(7). 
+	For each $t\geq 0$,
+\begin{align}
+    |Z_1(T^{\alpha}_t f)|
+    \leq R|T^{\alpha}_tf|
+    \leq R (e^{(\alpha-\kappa_fb)t}Qf)
+    \leq S(e^{(\alpha-\kappa_fb)t}Qf)
+    =e^{(\alpha-\kappa_fb)(1+\beta)t}SQf.
+    \end{align}
+Therefore,
+\[
+	|m_t[f]|\leq e^{-\alpha}e^{-\alpha t}e^{(\alpha-\kappa_fb)(1+\beta)t}\int_{\mathbb R^d}SQf(x)\varphi(x)dx.
+	\qedhere
+\]
+}
 \end{proof}
@@
 
-\deleted {Next, we will introduce a parameter of limiting distribution in the critical case.}
 Let
@@
 \begin{proof}
-\deleted{
-    We want to show the gap between $m_k[f]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$,
-    $$|m_k[f]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-\alpha s}\left|(-i T^{\alpha}_s f)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
-    }
     \added{
@@
     }
-    \deleted{
-    As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(f)bt}$,  $\kappa(f)=\kappa(\phi)$ and $\kappa(f-\phi)\geq \kappa(f)+1$.
-The inequality \eqref{eq:semigroupineq} yields that for some $R_5\in\mathcal{P}$ we have
-    \begin{align*}
-        &|T_s^{\alpha}f|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \\
-        &|T_s^{\alpha}(f-\phi)|\leq e^{(\alpha-(\kappa(f)+1)b)s}R_5(x), \quad s\geq0.
-    \end{align*}
-  Using Lemma \ref{lem: Lip of power function} and the condition $\alpha\beta=\kappa(f)b(1+\beta)$, we get
-    $$|m_k[f]-m_k[\phi]|\leq2C_0\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R_5^{1+\beta}(x)~ds~\varphi(x)~dx\leq \frac{2C_0}{b}\langle R_5^{1+\beta},\varphi\rangle e^{-bk},$$
-    }
+    {\bf Zhenyao: Give more details about the above equality.}
     \added{
@@
          \begin{align}
-        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})\big|\mathcal{F}_{t-k-1}\big]\\
+        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})\big|\mathscr{F}_{t-k-1}\big]\\
         &=\exp\big(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
@@
        }
-     Equivalently, by Lemma \ref{lemma32}， we just need to prove
+     Equivalently, by Lemma \ref{lemma32}, we just need to prove
      \begin{align}
@@
         &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
-        &=\Big|\mathbb{P}_{\mu}\Big[\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathcal{F}_{t-k-1}\Big)\Big]\Big|\\
+        &=\Big|\mathbb{P}_{\mu}\Big[\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big]\Big|\\
         &\leq e^c\mathbb{P}_{\mu}\big[\big|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
@@
     $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[f]\right)\mathbb{\tilde{P}}_{\mu}\left(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\right)$$
-    for $k\in\{-1,...,n\}$, if $k=-1$, the product is one. Then Conditioning with $\mathcal{F}_{t-k-1}$ we get
+    for $k\in\{-1,...,n\}$, if $k=-1$, the product is one. Then Conditioning with $\mathscr{F}_{t-k-1}$ we get
     \begin{align*}
         \varphi^{k-1}_t(\theta_0,...,\theta_n)-&\varphi^{k}_t(\theta_0,...,\theta_n)=\prod_{l=0}^{k-1}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[f]\right)\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left(\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[f]}\right)\prod_{l=k+1}^n\exp(i\theta_l \gamma_{t,l})\right]
+        &\mathbb{\tilde{P}}_{\mu}\left[\left(\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[f]}\right)\prod_{l=k+1}^n\exp(i\theta_l \gamma_{t,l})\right]
     \end{align*}
@@
     \begin{align*}
-        \left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| \leq \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[f]}\right|.
+        \left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| \leq \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[f]}\right|.
     \end{align*}
@@
     \label{eq:32step1}
-        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\leq C_{10} e^{-\delta_3(t-k-1)}.
+        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\leq C_{10} e^{-\delta_3(t-k-1)}.
     \end{align}
@@
     Recall that
-    $$\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)=\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle).$$
+    $$\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)=\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle).$$
  By \eqref{lemma31q} and \eqref{eq:31step3}, we easily get, if $|\theta|\leq\Theta$ and $k\in\{0,...,t\}$,
@@
 \begin{align*}
-   &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[f]}\right|\\
+   &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[f]}\right|\\
    &\leq \left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|
@@
 \begin{align*}
-    &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathcal{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[f]}\right|\\
+    &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[f]}\right|\\
     &\leq 2(\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1}(\epsilon_0))+\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1}))\\
@@
 \end{proof}
+
+\added{
+\subsection{}
+	In this subsection, we give more analytic results that will be used in this paper.
+	For each $z\in \mathbb C\setminus (-\infty,0]$ define 
+\[
+	\log z := \log |z| + i \arg z
+\] 
+	where $\arg z \in (-\pi,\pi)$ is uniquely determined by
+\[
+	z = |z|e^{i \arg z}.
+\] 	
+	For each $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$ define
+\[
+	z^\gamma := e^{\gamma \log z}.
+\]
+	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, $z\mapsto \log z$ is holomophic on $\mathbb C\setminus (-\infty,0]$.
+	Therefore, so is $z\mapsto z^\gamma$, for each $\gamma \in \mathbb C$.
+	For convention, define $0^\gamma := \mathbf 1_{\gamma = 0}$ for each $\gamma \in \mathbb C$.
+
+    Recall $\Gamma$ the Gamma function defined by
+\begin{equation}
+    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
+    \quad x>0.
+\end{equation}
+	It is known, see \cite[Theorem 6.1.3 and its following remark]{SteinShakarchi2003Complex} for example, function $\Gamma$ has an unique analytic extension on $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
+\[
+	\Gamma(z+1) = z \Gamma(z),\quad z\in \mathbb C\setminus\{0, -1,-2,\dots\}.
+\]
+	Using this recursively, one can verify that
+\begin{align}
+\label{eq: definition of Gamma function}
+    \Gamma(x)
+    := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
+    \quad -n< x< -n+1, n\in \mathbb N.
+\end{align}
+    It is known that
+\begin{equation}
+    \Gamma(x+1) = x\Gamma(x),
+    \quad x>0~\text{or}~-n< x< -n+1, n\in \mathbb N.
+\end{equation}
+
+    Fix a $\beta \in (0,1)$.
+    We can verify that
+\begin{equation}
+    z^{\beta}
+	= \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}},
+    \quad z\in \mathbb C_+,
+\end{equation}
+	by observing that the both sides 
+\begin{itemize}
+\item
+    are extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
+\item
+    are holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$ (For the right side, use \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein});
+\item
+    are continuous on $\mathbb C_+ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}$.
+\end{itemize}
+    Similarly, using Lemma \ref{lem: extension lemma for branching mechanism} in the Appendix, we can verify that
+\begin{equation}
+\label{eq: stable branching on C+}
+    z^{1+\beta}
+    = \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
+    \quad z\in \mathbb C_+.
+\end{equation}
+    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\to \mathbb C_+$ ,
+\begin{align}
+\label{eq: integration formula for 1+beta-th power of z}
+    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta}
+    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
+    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}}
+    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
+\end{align}
+    This indicates that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
+\begin{lem}
+\label{lem: Lip of power function}
+    There is a constant $C_{\ref{lem: Lip of power function}}$ such that for any $z_0,z_1 \in \mathbb C_+$,
+\begin{equation}
+\label{eq: Lip of power function}
+    |z_0^{1+\beta} - z_1^{1+\beta}|
+    \leq C_{\ref{lem: Lip of power function}}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
+\end{equation}
+    In particular, for each $z\in \mathbb C_+$, we have
+$
+    |z^{1+\beta}|
+    \leq  C_{\ref{lem: Lip of power function}} |z|^{1+\beta}.
+$
+
+\end{lem}
+\begin{proof}
+    Notice that
+\begin{align}
+\label{eq: upper bound for beta power of z}
+    &|z^{\beta}|
+    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big|
+    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
+    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
+    \quad z\in \mathbb C_+.
+\end{align}
+    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
+\[
+    \gamma(\theta)
+    = z_0 (1-\theta) + \theta z_1,
+    \quad \theta \in [0,1].
+\]
+    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
+\begin{align}
+    |z_0^{1+\beta} - z_1^{1+\beta}|
+    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
+    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
+    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
+    \qedhere
+\end{align}
+\end{proof}
+}
 
@@
 
+\bibitem{SteinShakarchi2003Complex}
+Stein, E. M. and Shakarchi, Rami:
+\emph{Complex analysis.} 
+Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.
+
 \end{thebibliography}

### 2019-01-31 supCLT.tex
supCLT.tex: 1113

@@
     In particular, the order of any constant function is zero.
-
+{
+    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ with
+\begin{equation}
+    \mathcal{P}
+    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+\end{equation}
+    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
+    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that,
+\begin{equation}
+\label{eq:semigroupineq}
+    |T_tf(x)|
+    \leq e^{-\kappa_f bt} R(x),
+    \quad t\geq 0, x\in \mathbb R^d.
+\end{equation}
+	For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.
+	Then $Q$ is an operator form $\mathcal P$ to $\mathcal P \cap \mathscr B
+	(\mathbb R^d,\mathbb R_+)$.
+}
+\deleted{
 \subsection{}
@@
 \end{align}
-
-\subsection{}
-    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R^+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
+}
+
+\added{
+	For each $0 \leq a \leq b <\infty$ and  random variable $Y$ with finite mean, define random variable
+$
+   	I_a^b[Y]
+    := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
+$
+	Then we have an nature incremental decomposition of $Y$:
+\begin{align}
+    I_0^t[Y]
+    = \sum_{k = 0}^{\lfloor t \rfloor - 1} I_k^{k+1}[Y] + I_{\lfloor t \rfloor}^t[Y],
+    \quad t\geq 0.
+\end{align}
+	The random variable we are interested in is $Y:= \langle g,X_t\rangle$.
+	In this case we have
+\begin{align}
+    I_a^b[\langle g,X_t\rangle]
+    = I_a^b\big[\mathbb P[\langle g,X_t\rangle|\mathscr F_b]\big]
+    = I_a^b[ \langle T_{t-b}^\alpha g, X_b \rangle ].
+\end{align}
+}
+
+    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
     We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
@@
    	Proof of (2): Let $(R_A, S_A)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$ and $(R_B, S_B)$ be the $\beta$-control-pair of $(B_{\delta})_{\delta\in\Delta}$ on $\mathcal{D}_0$.
-
-   For each $f\in \mathcal{P}^+$ and $\theta \geq 0$, $S_BS_A(\theta f)=S_b(\theta^{\gamma}S_Af)=\theta^{\beta\gamma}S_BS_Af$.
-
-   For each $f,g \in \mathcal P^+$ with $f\leq g$, $R_B(R_A f)\leq R_B(R_A g)$ and $R_B (R_A f)\leq R_B(S_A f)\leq S_BS_A f$.
-
-   For each $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|,~~\delta\in \Delta, \lambda\in\Lambda$.
-
-   Thus $(R_BR_A,S_BS_A)$ is a $\beta\gamma$-control-pair of operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$.
+\added{
+	Note that $(R_BR_A, S_BS_A)$ is a $\beta \gamma$-control-pair.
+	In fact:
+\begin{itemize}
+\item
+	For each $f,g \in \mathcal P^+$ with $f\leq g$, since $R_Af \leq R_A g$ we have $R_B(R_A f)\leq R_B(R_A g)$.
+\item
+	For each $f\in \mathcal{P}^+$ and $\theta \geq 0$, we have $S_BS_A(\theta f)=S_B(\theta^{\gamma}S_Af)=\theta^{\beta\gamma}S_BS_Af$.
+\item
+	For each $f,g \in \mathcal P^+$ with $f\leq g$, we have $R_B R_A f \leq R_B S_A f \leq S_BS_A f$.
+\end{itemize}
+	Finally, note that for each $\delta\in \Delta, \lambda\in\Lambda$ and $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|$ which says that operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ are uniformly $(\beta\gamma)$-controlled by $(R_BR_A,S_BS_A)$.
+}
 
@@
 \]
-    Note that $f\mapsto\sup_{0\leq u\leq 1}T_u|f|$ is monotonic and $1$-scalable.
+    Note that $f\mapsto\sup_{0\leq u\leq 1}T^{\added{\alpha}}_u|f|$ is monotonic and $1$-scalable.
+    \added{Combine this with \eqref{eq: -v has positive real part}, we get the desired result.}
 
@@
 \[
-    \mathbb P_\mu (|M^t_g(0,t)| > \lambda)
+    \mathbb P_\mu (|\deleted{M^t_g(0,t)} \added{I_0^t[\langle g,X_t\rangle]}| > \lambda)
     \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta
-    \leq \langle S| g|,\mu\rangle \frac{1}{\lambda^{1+\beta}}.
+    \deleted{\leq \langle S| g|,\mu\rangle \frac{2^{2+\beta/(2+\beta)}}{\lambda^{1+\beta}}}.
 \]
 \end{lem}
-
+\added{
 \begin{proof}
-    Denote by $(R_0,S_0)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}.
-    Using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, we have
-\begin{align}
-    &\mathbb P_\mu (|M^t_g(0,t)| > \lambda)
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{i\theta M_g^t(0,t)}]\Big)d\theta
-    = \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{iM_{(\theta g)}^t(0,t)}]\Big)d\theta
-    \\&= \added{\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}\Big) d\theta}
+    Denote by $(R,S)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}(4).
+    Using Lemma \ref{lem: estimate of exponential remaining} and the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, we have
+\begin{align}
+    &\big|\mathbb P_\mu (|I_0^t[\langle g,X_t\rangle]| > \lambda)\big|
+    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta I_0^t[\langle g,X_t\rangle]}])d\theta\Big|
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}|d\theta
     \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iT_t^\alpha(\theta g)|,\mu\rangle d\theta
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta g|,\mu\rangle d\theta
-      \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta g|,\mu\rangle d\theta
-\end{align}
-    To finish the proof we write $R=R_0$ and $S= S_0$.
-\end{proof}
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
+      \qedhere
+\end{align}
+\end{proof}
+}
+
+{\bf Zhenyao: I will change $M_g^t(a,b)$ to $I_a^b[\langle g,X_t\rangle]$ without mention. Here ``I'' means incremental.}
 
@@
 We want to prove the following Lemma
+\added{
 \begin{lem}\label{lem: control of XT}
-Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function satisfying $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$, Then for any $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C_{\ref{lem: control of XT}}>0$ such that
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_4 \exp(\beta(\ln f(t)-\alpha t)), \quad t\geq 0.
+	For each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for each function $f:[0,\infty)\to [1,\infty)$ and each $t\geq 0$ we have
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)\leq C \Big(\frac{f(t)}{e^{\alpha t}}\Big)^{\beta}.
 \end{align}
 \end{lem}
+}
 \begin{proof}
- Without loss of generality, we assume that $\|\mu\|=1$, By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|)}]\\
-    &\leq \frac{1}{1-e^{-\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
-\end{align*}
-Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t},~ t\geq 0,\lambda\geq0$, $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
-\begin{align*}
-    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\cdot\left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right|\\
-    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t}\\
-    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}
-\end{align*}
-Therefore,
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}\cdot \frac{1}{1-e^{-\alpha^*}} e^{\lambda f(t)}.
-\end{align*}
+ \deleted{Without loss of generality, we assume that $\|\mu\|=1$,} By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
+\added{
+\begin{align*}
+    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]\\
+    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
+\end{align*}
+}
+	Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t}$ where $t\geq 0,\lambda\geq0$ then $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
+\added{Note that}
+\begin{align*}
+    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta} \left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right| \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
+    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
+    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
+\end{align*}
+Therefore, \added{for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for each non-negative function $f$ on $[0,\infty),$ each $\lambda \geq 0$ and each $t\geq 0$ we have }
+\begin{align}
+\label{eq: inequality before take lambda}
+    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)
+    \leq C_0e^{\lambda f(t)}\frac{1}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
+\end{align}
+\deleted{
 Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
@@
     \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
-    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.
-\end{align*}
-This is to say
-\begin{align*}
-    \sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}&\leq\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
-    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}
-\end{align*}
-We conclude the lemma by taking $C_{\ref{lem: control of XT}}= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
-\end{proof}
-Define $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\},\quad \epsilon,t>0$.
+    &\added{\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.}
+\end{align*}
+This is to say \added{for each $\lambda \in [0,1]$,
+\begin{align*}
+    \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}
+    &\leq\sup_{s\in [\lambda,\lambda+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
+    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}} =: C_1.
+\end{align*}
+}
+\added{Finally, taking $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.}
+\end{proof}
+	Define $\mathcal{A}_t(\epsilon):=\{ \|X_t\|\in \|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\}$ where $\epsilon,t>0$.
+\deleted{
 \begin{lem}\label{lem: control of AT}
-  For any $\epsilon,t>0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exists $C_{\ref{lem: control of AT}}>0$ and $\delta_{\ref{lem: control of AT}}>0$ such that
-  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_{\ref{lem: control of AT}} e^{-\delta_{\ref{lem: control of AT}} t}.$$
+  For any $\epsilon,t>0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$ and $\delta>0$ such that
+  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\delta t}.$$
 \end{lem}
+}
+\added{
+\begin{lem}\label{lem: control of AT}
+  For each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ there exists $C>0$ such that for each $t\geq 0$ we have
+  $
+  \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\beta\epsilon t}.
+  $
+\end{lem}
+}
 
 \begin{proof}
-    First, for any $\epsilon>0$, using Markov inequality, we get
-    $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.$$
+    First, for any $\epsilon>0$, using Markov inequality, \added{we get for each $\epsilon>0$ and $t\geq 0$,}
+\added{
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})
+    \leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}
+	= \frac{\mathbb P_\mu[\|X_t\|\mathbf 1_{D^c}]}{\mathbb P_\mu(D^c)\|\mu\|e^{(\alpha+\epsilon)t}}
+    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.
+\end{align}
+}
     For another side, using Lemma \ref{lem: control of XT}, we have
-    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_{\ref{lem: control of XT}} e^{-\beta\epsilon t}, $$
-To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.
+    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_0 e^{-\beta\epsilon t}, $$
+    \added{for some constant $C_0>0$ not related to $\epsilon>0$ and $t\geq 0$.}
+\deleted{To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.}
 \begin{comment}
@@
 \added{
- In this subsection, we will introduce an important parameter of $(1+\beta)$-stable distribution: $m_k[f],~~f\in \mathcal{P}$.
-
- Let $Zf(x)=Z_1f(x),~x\in\mathbb{R}^d$ and 
+ Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}, define
  \begin{align}\label{parameter_mk}
-      m_k[f]:=e^{-\alpha(k+1)}\langle Z(T_k^{\alpha}f),\varphi\rangle,\quad k\in \mathbb{N}.
- \end{align}
- }
+      m_t[f]:=e^{-\alpha (t+1)}\int_{\mathbb R^d} (Z_1T_t^{\alpha}f)(x)\varphi(x)dx,\quad t\geq 0, f\in \mathcal P.
+ \end{align}
+ }
+ \added{
+ Using the same argument as in the proof of \cite[Lemma2.7, Lemma4.2 \& Lemma 5.1]{MM}, we can show that
  \begin{lem}\label{lem: control of mk}
-For each $f\in\mathcal{P}$, there exists constant $C_{\ref{lem: control of mk}}>0$ such that for any $k\in \{0,1,...,\lfloor t\rfloor\}$, we have
-$$|m_k[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))k}.$$
+For each $f\in\mathcal{P}$, there is a constant $C>0$ such that for each $t\geq 0$, we have
+$$|m_t[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))t}.$$
+Therefore, $m_t[f]$ is well-defined.
 \end{lem}
-\begin{proof}
-\added{
-According to Lemma \ref{lem: upper bound for usgx}, there exists an $(1+\beta)$-control-pair $(R,S)$ suct that for each $k\in\mathbb{N}$,
-\begin{align}
-    |Z(T^{\alpha}_k f)|\leq R|T^{\alpha}_k|\leq R (e^{(\alpha-\kappa_fb)k}Qf)\leq S(e^{(\alpha-\kappa_fb)k}Qf)=e^{(\alpha-\kappa_fb)(1+\beta)k}SQf.
-    \end{align}
-}
-\deleted{
-Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{eq: zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
-\begin{align}
-    |Z_{f_k}(x)|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_2^f(x), \quad x\in \mathbb{R}^d, k\in\mathbb{N}.
-\end{align}
-}
-This implies the result by simply calculating.
-\end{proof}
-
-$m_k[f],~f\in \mathcal{P}$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Note that,
-\begin{align}
-    m_k[f]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}\Psi_0(-iT_{s+k}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in\mathbb{N}.
-\end{align}
-
-Using Fubini's Theorem and the fact $\varphi(x)$ is an invariant measure of $(T)_{t\geq 0}$, we get
-\begin{align}
-    m_k[f]=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in \mathbb{N}.\label{mkeq}
-\end{align}
-
-\deleted {Next, we will introduce a parameter of limiting distribution in the critical case.}
 Let
@@
 \end{align}
-i.e. $\phi$ is the projection of $f$ onto the $\kappa_f$-eigenspace. Easily we get $\kappa_f=\kappa_{\phi}$ and $\kappa_{f-\phi}\geq \kappa_f+1$.
+i.e. $\phi$ is the projection of $f$ onto the $\kappa_f$-eigenspace.
 \begin{lem}\label{lemma210}
@@
 
-\begin{proof}
+\begin{lem}\label{lemma211}
+Let $f\in \mathcal{P}$, assume $\alpha\beta<\kappa_fb(1+\beta)$, if $\kappa_f\geq 1$, the series $\sum_{k=0}^{\infty}m_k[f]$ is absolutely convergent, hence we can define
+\begin{align}
+    m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx \label{msmallcase}
+\end{align}
+\end{lem}
+ }
 \deleted{
-    We want to show the gap between $m_k[f]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$,
-    $$|m_k[f]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-\alpha s}\left|(-i T^{\alpha}_s f)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
-    }
-    \added{
+\begin{proof}[proof of Lemma 2.14]
+
+	Let $(R,S)$ be the $(1+\beta)$-control-pair corresponding to \ref{lem: upper bound for usgx}(7).
+	For each $t\geq 0$,
+\begin{align}
+    |Z_1(T^{\alpha}_t f)|
+    \leq R|T^{\alpha}_tf|
+    \leq R (e^{(\alpha-\kappa_fb)t}Qf)
+    \leq S(e^{(\alpha-\kappa_fb)t}Qf)
+    =e^{(\alpha-\kappa_fb)(1+\beta)t}SQf.
+    \end{align}
+Therefore,
+\[
+	|m_t[f]|\leq e^{-\alpha}e^{-\alpha t}e^{(\alpha-\kappa_fb)(1+\beta)t}\int_{\mathbb R^d}SQf(x)\varphi(x)dx.
+	\qedhere
+\]
+
+\end{proof}
+
+$m_k[f],~f\in \mathcal{P}$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Note that,
+\begin{align}
+    m_k[f]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}\Psi_0(-iT_{s+k}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in\mathbb{N}.
+\end{align}
+
+Using Fubini's Theorem and the fact $\varphi(x)$ is an invariant measure of $(T)_{t\geq 0}$, we get
+\begin{align}
+    m_k[f]=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in \mathbb{N}.\label{mkeq}
+\end{align}
+
+Let
+\begin{align}
+    \phi(x)=\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p(x),~x\in \mathbb{R}^d, p \in\mathbb{N}_0^d.
+\end{align}
+i.e. $\phi$ is the projection of $f$ onto the $\kappa_f$-eigenspace. Easily we get $\kappa_f=\kappa_{\phi}$ and $\kappa_{f-\phi}\geq \kappa_f+1$.
+
+\begin{proof}[Proof of Lemma 2.15]
+
     Notice that
@@
     \end{align}
-    }
-    \deleted{
-    As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(f)bt}$,  $\kappa(f)=\kappa(\phi)$ and $\kappa(f-\phi)\geq \kappa(f)+1$.
-The inequality \eqref{eq:semigroupineq} yields that for some $R_5\in\mathcal{P}$ we have
-    \begin{align*}
-        &|T_s^{\alpha}f|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \\
-        &|T_s^{\alpha}(f-\phi)|\leq e^{(\alpha-(\kappa(f)+1)b)s}R_5(x), \quad s\geq0.
-    \end{align*}
-  Using Lemma \ref{lem: Lip of power function} and the condition $\alpha\beta=\kappa(f)b(1+\beta)$, we get
-    $$|m_k[f]-m_k[\phi]|\leq2C_0\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R_5^{1+\beta}(x)~ds~\varphi(x)~dx\leq \frac{2C_0}{b}\langle R_5^{1+\beta},\varphi\rangle e^{-bk},$$
-    }
-    \added{
+
     According to Lemma \ref{lem: Lip of power function}, for any $s\geq 0$,
@@
     Therefore, the limits of $(1/t)\sum_{k=0}^tm_k[f]$ is the same with that of $(1/t)\sum_{k=0}^tm_k[\phi]$.
-    }
-
-    \deleted{
-    What's more
-    \begin{align*}
-        m_k[\phi]&=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}(-iT_{s}^{\alpha}\phi)^{1+\beta}(x)~ds~\varphi(x)~dx\\
-        &=\int_{\mathbb{R}^d}(-i\phi(x))^{1+\beta}\varphi (x)~dx=\langle (-i\phi)^{1+\beta},\varphi\rangle.
-    \end{align*}
-    The second equality holds as $T_s\phi=e^{-\kappa(g)bs}\phi$.
-    }
 
@@
     \end{align}
-
-\end{proof}
-
-\deleted {For the small branching rate case: $\alpha\beta<\kappa(f)b(1+\beta)$.}
-\begin{lem}\label{lemma211}
-Let $f\in \mathcal{P}$, assume $\alpha\beta<\kappa_fb(1+\beta)$, if $\kappa_f\geq 1$, the series $\sum_{k=0}^{\infty}m_k[f]$ is absolutely convergent, hence we can define
-\begin{align}
-    m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx \label{msmallcase}
-\end{align}
-\end{lem}
-\begin{proof}
-\added{
+\end{proof}
+
+\begin{proof}[Proof of Lemma 2.16]
+
     By Lemma \ref{lem: control of mk}, we have $|m_k[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))k},~k\in\mathbb{N}$, which implies $\sum_{k=0}^{\infty}|m_k[f]|<\infty$.
@@
     is well defined.
-    }
-\end{proof}
-
+\end{proof}
+}
 \section{Proof of main results}
@@
     \end{align*}
+     \deleted{
  Step 2.
-Let $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.to prove inequality \eqref{ineqinlem31}, We will first show that there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
+Let $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.According to \cite[Lemma 2.8]{MM}, there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
  \begin{align}
@@
  \end{align}
+
  Let $\tilde{f}=T_1^{\alpha}f$, then $\kappa(\tilde{f})=\kappa(f)$.
@@
 \end{align}
-Step 3, for any $\mu \in \mathcal{M}(\mathbb{R}^d)$ and $\theta\in \mathbb{R}$, we will show that there exists $C_7>0$ such that
+}
+Step 2, for any $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ and $\theta\in \mathbb{R}$, we will show that there exists $C_7>0$ such that
 \begin{align}
@@
 \end{align}
-As $h_k$ satisfies \eqref{eq:gcontrol1} with $C_{h_k}=e^{(\alpha-\kappa(f))(1+\beta)k}$, $\kappa=1$ and $R_0^{h_k}(x)=R_7(x)$, fix some $\gamma_0\in(0,\beta)$, according to Lemma \ref{lemma24}, there exist $C_8>0$,
+\added{
+where $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.According to \cite[Lemma 2.8]{MM}, there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
+ \begin{align}
+ \label{eq:31step2}
+     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa(f)b)(1+\beta)k}R_7(x).
+ \end{align}
+}
+Thus $h_k$ satisfies \eqref{eq:gcontrol1} with $C_{h_k}=e^{(\alpha-\kappa(f))(1+\beta)k}$, $\kappa=1$ and $R_0^{h_k}(x)=R_7(x)$, fix some $\gamma_0\in(0,\beta)$, according to Lemma \ref{lemma24}, there exist $C_8>0$,
 \begin{align}
@@
 \end{proof}
+
+\added{
+\subsection{}
+	In this subsection, we give more analytic results that will be used in this paper.
+	For each $z\in \mathbb C\setminus (-\infty,0]$ define
+\[
+	\log z := \log |z| + i \arg z
+\]
+	where $\arg z \in (-\pi,\pi)$ is uniquely determined by
+\[
+	z = |z|e^{i \arg z}.
+\] 	
+	For each $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$ define
+\[
+	z^\gamma := e^{\gamma \log z}.
+\]
+	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, $z\mapsto \log z$ is holomophic on $\mathbb C\setminus (-\infty,0]$.
+	Therefore, so is $z\mapsto z^\gamma$, for each $\gamma \in \mathbb C$.
+	For convention, define $0^\gamma := \mathbf 1_{\gamma = 0}$ for each $\gamma \in \mathbb C$.
+
+    Recall $\Gamma$ the Gamma function defined by
+\begin{equation}
+    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
+    \quad x>0.
+\end{equation}
+	It is known, see \cite[Theorem 6.1.3 and its following remark]{SteinShakarchi2003Complex} for example, function $\Gamma$ has an unique analytic extension on $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
+\[
+	\Gamma(z+1) = z \Gamma(z),\quad z\in \mathbb C\setminus\{0, -1,-2,\dots\}.
+\]
+	Using this recursively, one can verify that
+\begin{align}
+\label{eq: definition of Gamma function}
+    \Gamma(x)
+    := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
+    \quad -n< x< -n+1, n\in \mathbb N.
+\end{align}
+    It is known that
+\begin{equation}
+    \Gamma(x+1) = x\Gamma(x),
+    \quad x>0~\text{or}~-n< x< -n+1, n\in \mathbb N.
+\end{equation}
+
+    Fix a $\beta \in (0,1)$.
+    We can verify that
+\begin{equation}
+    z^{\beta}
+	= \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}},
+    \quad z\in \mathbb C_+,
+\end{equation}
+	by observing that the both sides
+\begin{itemize}
+\item
+    are extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
+\item
+    are holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$ (For the right side, use \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein});
+\item
+    are continuous on $\mathbb C_+ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}$.
+\end{itemize}
+    Similarly, using Lemma \ref{lem: extension lemma for branching mechanism} in the Appendix, we can verify that
+\begin{equation}
+\label{eq: stable branching on C+}
+    z^{1+\beta}
+    = \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
+    \quad z\in \mathbb C_+.
+\end{equation}
+    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\to \mathbb C_+$ ,
+\begin{align}
+\label{eq: integration formula for 1+beta-th power of z}
+    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta}
+    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
+    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}}
+    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
+\end{align}
+    This indicates that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
+\begin{lem}
+\label{lem: Lip of power function}
+    There is a constant $C_{\ref{lem: Lip of power function}}$ such that for any $z_0,z_1 \in \mathbb C_+$,
+\begin{equation}
+\label{eq: Lip of power function}
+    |z_0^{1+\beta} - z_1^{1+\beta}|
+    \leq C_{\ref{lem: Lip of power function}}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
+\end{equation}
+    In particular, for each $z\in \mathbb C_+$, we have
+$
+    |z^{1+\beta}|
+    \leq  C_{\ref{lem: Lip of power function}} |z|^{1+\beta}.
+$
+
+\end{lem}
+\begin{proof}
+    Notice that
+\begin{align}
+\label{eq: upper bound for beta power of z}
+    &|z^{\beta}|
+    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big|
+    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
+    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
+    \quad z\in \mathbb C_+.
+\end{align}
+    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
+\[
+    \gamma(\theta)
+    = z_0 (1-\theta) + \theta z_1,
+    \quad \theta \in [0,1].
+\]
+    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
+\begin{align}
+    |z_0^{1+\beta} - z_1^{1+\beta}|
+    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
+    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
+    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
+    \qedhere
+\end{align}
+\end{proof}
+}
 
@@
 
+\bibitem{SteinShakarchi2003Complex}
+Stein, E. M. and Shakarchi, Rami:
+\emph{Complex analysis.}
+Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.
+
 \end{thebibliography}

### 2019-01-31 supCLT.tex
supCLT.tex: 1114

@@
 \end{proof}
+
+\deleted{
 As $\|X_t\|$ is an continuous state branching process with initial mass $\|\mu\|$.
@@
 If we fix $t>0$, $v_t(\lambda)$ is increasing corresponding to $\lambda$.
-
-Recall that the superprocess $X$'s extinction probability $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
-Denote $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$, by equation (3.48) in \cite{Li2011Measure-valued} and formula \eqref{CSBP}, we easily get
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}\nonumber\\
-        &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|. \label{laplaceexpress}
-\end{align}
-
-We want to prove the following Lemma
+}
+\added{
+    According to \cite[Example 3.1]{Li2011Measure-valued}, we have
+\begin{align}\label{CSBP}
+    \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
+    =e^{-\|\mu\|v_t(\lambda)},
+    \quad \lambda \geq 0, t\geq 0,
+\end{align}
+    where
+\[
+    v_t(\lambda)=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
+\]
+}
+
+    Recall that the \deleted{superprocess $X$'s} extinction probability \added{of the superprocess is} $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
+    Denote \added{by} $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$. 
+    \added{According to \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and 
+    $t\geq 0$,}
+\added{
+\begin{align}
+    \label{laplaceexpress}
+    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]
+    &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
+    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\alpha^*\|X_t\|})] }{\mathbb P_\mu(D^c)}
+    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}
+    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|. 
+\end{align}
+}
+    \deleted{We want to prove the following Lemma}
 \added{
@@
 \end{align*}
-This is to say \added{for each $\lambda \in [0,1]$,
+\added{Therefore, for each $\lambda \in [0,1]$,
 \begin{align*}
@@
 \deleted{To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.}
-\begin{comment}
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq(C_4+\frac{1}{\mathbb{P}_{\mu}(D^c)})e^{-\beta \epsilon t }
-\end{align*}
-\end{comment}
 \end{proof}
 
-%\subsection{Parameter $m_k[g]$}
 \subsection{Parameters}
-\added{
  Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}, define
@@
  \end{align}
- }
+ \deleted{Using the same argument as in the proof of \cite[Lemma2.7, Lemma4.2 \& Lemma 5.1]{MM}, we can show that}
+\added{According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that 
+\[
+    |m_t[f]|
+    \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
+    \quad t\geq 0.
+\]
+}
+\deleted{Therefore, $m_t[f]$ is well-defined.}
+
 \added{
- Using the same argument as in the proof of \cite[Lemma2.7, Lemma4.2 \& Lemma 5.1]{MM}, we can show that
- \begin{lem}\label{lem: control of mk}
-For each $f\in\mathcal{P}$, there is a constant $C>0$ such that for each $t\geq 0$, we have
-$$|m_t[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))t}.$$
-Therefore, $m_t[f]$ is well-defined.
+    Let $f \in \mathcal{P}$.
+    Suppose that $\kappa_f\geq 1$ and $\alpha\beta=\kappa_f b(1+\beta)$.
+    Denote by
+\[
+    \phi(x)
+    =\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p(x),
+    \quad x\in \mathbb{R}^d, p \in\mathbb Z_+^d,
+\]
+    the projection of $f$ onto the $\kappa_f$-eigenspace.
+    Then accodting to \cite[Lemma 4.2]{MM} the following limit exists:
+\begin{align}
+\label{lemma210}
+    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\Psi_0(-i\phi),\varphi\rangle.
+\end{align}
+
+    Let $f\in \mathcal{P}$.
+    Suppose that $\kappa_f\geq 1$ and $\alpha\beta<\kappa_fb(1+\beta)$. Then, according to \cite[Lemma 5.1]{MM}, the following series and integral absolutely convergence:
+\begin{align}
+    m[f]
+    :=e^{-\alpha}\sum_{k=0}^\infty m_k[f]
+    =\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx. \label{msmallcase}
+\end{align}
+}
+
+\added{
+    Note that $m_t[\theta f]$ can be rewritten as follows:
+\[
+    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 T_{1-s}^\alpha (-i\theta T_{s+t}^\alpha f)^{1+\beta}(x)~ds,
+    \quad \theta \in \mathbb R.
+\]
+    The following Lemma says that function $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+\begin{lem}
+    Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$. 
+    Then $$\theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\}$$
+    is the characteristic function of a $(1+\beta)$-stable random variable.
 \end{lem}
-Let
-\begin{align}
-    \phi(x)=\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p(x),~x\in \mathbb{R}^d, p \in\mathbb{N}_0^d.
-\end{align}
-i.e. $\phi$ is the projection of $f$ onto the $\kappa_f$-eigenspace.
-\begin{lem}\label{lemma210}
-Let $f \in \mathcal{P}$, $\kappa_f\geq 1$ and $\alpha\beta=\kappa(f)b(1+\beta)$, then the following limit exists:
-\begin{align}
-    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\added{\lfloor t \rfloor}}m_k[f]=\langle\Psi_0(-i\phi),\varphi\rangle.
-\end{align}
-\end{lem}
-
-\begin{lem}\label{lemma211}
-Let $f\in \mathcal{P}$, assume $\alpha\beta<\kappa_fb(1+\beta)$, if $\kappa_f\geq 1$, the series $\sum_{k=0}^{\infty}m_k[f]$ is absolutely convergent, hence we can define
-\begin{align}
-    m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx \label{msmallcase}
-\end{align}
-\end{lem}
- }
-\deleted{
-\begin{proof}[proof of Lemma 2.14]
-
-	Let $(R,S)$ be the $(1+\beta)$-control-pair corresponding to \ref{lem: upper bound for usgx}(7).
-	For each $t\geq 0$,
-\begin{align}
-    |Z_1(T^{\alpha}_t f)|
-    \leq R|T^{\alpha}_tf|
-    \leq R (e^{(\alpha-\kappa_fb)t}Qf)
-    \leq S(e^{(\alpha-\kappa_fb)t}Qf)
-    =e^{(\alpha-\kappa_fb)(1+\beta)t}SQf.
-    \end{align}
-Therefore,
-\[
-	|m_t[f]|\leq e^{-\alpha}e^{-\alpha t}e^{(\alpha-\kappa_fb)(1+\beta)t}\int_{\mathbb R^d}SQf(x)\varphi(x)dx.
+\begin{proof}
+    From the measure theory, there is a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that 
+\[
+    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \int_{\mathbb R^+} f(\xi t)k(\xi,dt) \lambda(d\xi),\quad 
+    f\in \mathscr B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+\]
+    Define another measure $\lambda_0$ on $S$ by
+\[
+    \lambda_0(d\xi) := \frac{1}{\Gamma(-1-\beta)} \int_0^\infty t^{1+\beta}k(\xi,dt) \lambda (d\xi).
+\]
+    Then $\lambda_0$ is a non-zero finite measure, since
+\[
+    \lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt) \lambda (d\xi)
+    = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
+\]
+    Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
+\[
+    \int_{\mathbb R^d/\{0\}}f(x)\nu(dx)= \int_{S} \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} \lambda_0(d\xi).
+\]
+    Then, according to \cite[Remark 14.4]{Sato1999Levy}, $\nu$ is the L\`evy measure of an $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is \[\hat \mu(\theta)=\exp\Big\{\int_{\mathbb R^d/\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\}.\]
+    The final step, we verify that
+\begin{align}
+    &\int_{\mathbb R^d/\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
+    = \int_S \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}\lambda_0(d\xi)
+\\&\quad = \int_S \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt) \lambda (d\xi)
+\\&\quad = \int_S (i\theta\cdot \xi)^{1+\beta} \int_0^\infty t^{1+\beta} k(\xi,dt) \lambda (d\xi)
+= \int_S \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)\lambda(d\xi)
+\\&\quad = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
 \qedhere
-\]
-
-\end{proof}
-
-$m_k[f],~f\in \mathcal{P}$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Note that,
-\begin{align}
-    m_k[f]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}\Psi_0(-iT_{s+k}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in\mathbb{N}.
-\end{align}
-
-Using Fubini's Theorem and the fact $\varphi(x)$ is an invariant measure of $(T)_{t\geq 0}$, we get
-\begin{align}
-    m_k[f]=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in \mathbb{N}.\label{mkeq}
-\end{align}
-
-Let
-\begin{align}
-    \phi(x)=\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p(x),~x\in \mathbb{R}^d, p \in\mathbb{N}_0^d.
-\end{align}
-i.e. $\phi$ is the projection of $f$ onto the $\kappa_f$-eigenspace. Easily we get $\kappa_f=\kappa_{\phi}$ and $\kappa_{f-\phi}\geq \kappa_f+1$.
-
-\begin{proof}[Proof of Lemma 2.15]
-
-    Notice that
-        \begin{align}\label{parameter of mkphi}
-        m_k[\phi]&=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}\phi)(x)~ds~\varphi(x)~dx\\
-        &=\int_{\mathbb{R}^d}\Psi_0(-i\phi(x))\varphi (x)~dx=\langle \Psi_0(-i\phi),\varphi\rangle.
-    \end{align}
-
-    According to Lemma \ref{lem: Lip of power function}, for any $s\geq 0$,
-    \begin{align}
-        &\Big|\Psi_0(-iT^{\alpha}_s f)-\Psi_0(-iT^{\alpha}_s\phi)\Big|\leq C_{\ref{lem: Lip of power function}}(|T^{\alpha}_sf|^{\beta}+|T^{\alpha}_s\phi|^{\beta})|T^{\alpha}_s(f-\phi)|
-        \\& \leq C_{\ref{lem: Lip of power function}}e^{(\alpha-\kappa_f b)(1+\beta)s}e^{-bs}\big((Qf)^{\beta}+(Q\phi)^{\beta}\big)Q(f-\phi).
-    \end{align}
-    Therefore, by the condition $\alpha\beta=\kappa_fb(1+\beta)$,
-    \begin{align}
-        |m_k[f]-m_k[\phi]|&\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-\alpha s}\Big|\Psi_0(-iT^{\alpha}_s f)-\Psi_0(-iT^{\alpha}_s\phi)\Big|(x)~ds~\varphi(x)~ds.
-        \\&\leq C_{\ref{lem: Lip of power function}}\int_{\mathbb{R}^d}\int_{k}^{k+1} e^{-bs}\big((Qf)^{\beta}+(Q\phi)^{\beta}\big)Q(f-\phi)~ds~ \varphi(x)~dx.
-        \\&\leq C_{\ref{lem: Lip of power function}}\langle((Qf)^{\beta}+(Q\phi)^{\beta})Q(f-\phi), \varphi\rangle e^{-bk},\quad k \in \mathbb{N}.
-    \end{align}
-    Therefore, the limits of $(1/t)\sum_{k=0}^tm_k[f]$ is the same with that of $(1/t)\sum_{k=0}^tm_k[\phi]$.
-
-   From \eqref{parameter of mkphi}, for any $k\in \mathbb{N}$,
-    \begin{align}
-        \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t\rfloor}m_k[f]=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[\phi]=\langle\Psi_0(-i\phi),\varphi\rangle.
-    \end{align}
-\end{proof}
-
-\begin{proof}[Proof of Lemma 2.16]
-
-    By Lemma \ref{lem: control of mk}, we have $|m_k[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))k},~k\in\mathbb{N}$, which implies $\sum_{k=0}^{\infty}|m_k[f]|<\infty$.
-
-    On the other hand, denote by $(R,S)$ the $(1+\beta)$-control-pair for Lemma \ref{lem: upper bound for usgx}(3), for any $s\geq 0$,
-    \begin{align}
-        |e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)|\leq e^{-\alpha s}R|T^{\alpha]_s}f|\leq e^{-\alpha s}R(e^{(\alpha-\kappa_fb)s}Qf)=e^{(\alpha\beta-\kappa_fb(1+\beta))s}RQf.
-    \end{align}
-    This implies
-    \begin{align}
-        \sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)ds\varphi(x)dx< \infty.
-    \end{align}
-    and
-    \begin{align}
-            m[f]:=\sum_{k=0}^{\infty}m_k[f]=\sum_{k=0}^{\infty}\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)ds\varphi(x)dx
-    \end{align}
-    is well defined.
+\end{align}
 \end{proof}
@@
 
-{\bf In Milos' paper, he says $e^{\theta^{1+\beta}e^{\alpha}m_k[f]}$ is a characteristic function, but no explanation.}
 \begin{lem}\label{lemma31}
@@
 \end{proof}
+{\bf Zhenyao: The proof of the above lemma is not right. The proof of the following lemma is not accurate.}
 \begin{lem}\label{lemma32}
@@
 \end{proof}
-
+\deleted{
 \begin{lem}
@@
 \end{align}
-B \cite[Theorem 14.15]{Sato1990Levy}, we get the result.
+B \cite[Theorem 14.15]{Sato1999Levy}, we get the result.
 \end{proof}
-{\bf Jianjie: I think the proof has some problem, as we are not sure $J$ is negative or not,}
+}
 \begin{lem}\label{lemma33}
@@
 
-\added{
+{ \color{blue}
 \subsection{}
-	In this subsection, we give more analytic results that will be used in this paper.
+	In this subsection, we give some analytical facts that will be used in this paper.
 	For each $z\in \mathbb C\setminus (-\infty,0]$ define
@@
 	For convention, define $0^\gamma := \mathbf 1_{\gamma = 0}$ for each $\gamma \in \mathbb C$.
+    From this definition we can verify that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
 
@@
 \end{align}
-    It is known that
-\begin{equation}
-    \Gamma(x+1) = x\Gamma(x),
-    \quad x>0~\text{or}~-n< x< -n+1, n\in \mathbb N.
-\end{equation}
 
     Fix a $\beta \in (0,1)$.
-    We can verify that
+    Using \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that
 \begin{equation}
@@
 \end{equation}
-	by observing that the both sides
+	by showing that the both sides
 \begin{itemize}
@@
 \item
-    are holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$ (For the right side, use \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein});
+    are holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$;
 \item
@@
 \label{sec: definition of characteristic exponent}
-    According to Levy-Khintchine formula \cite[Theorem 8.1]{Sato1990Levy}, an $\mathbb R$-valued random variable $\{Y; P\}$ is infinitely divisible if and only if
+    According to Levy-Khintchine formula \cite[Theorem 8.1]{Sato1999Levy}, an $\mathbb R$-valued random variable $\{Y; P\}$ is infinitely divisible if and only if
 \begin{equation}
@@
     Suppose that $P[|Y|]< \infty$.
-    According to \cite[Corollary 25.8.]{Sato1990Levy}, $\int_{|x|>1} |x|\nu(dx) < \infty$.
+    According to \cite[Corollary 25.8.]{Sato1999Levy}, $\int_{|x|>1} |x|\nu(dx) < \infty$.
 
@@
 
-\bibitem{Sato1990Levy}
+\bibitem{Sato1999Levy}
 Sato, K.:

### 2019-01-31 supCLT.tex
supCLT.tex: 1115

@@
     Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
-    Let $\psi$ be a function on \added{$\mathbb R^d \times \mathbb R_+$}\deleted{$\mathbb R_+:= [0,\infty)$} with
-\deleted{
+    Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
 \begin{equation}\label{mechanism}
@@
 \end{equation}
-}
-\added{
-\begin{equation}\label{mechanism}
-    \psi(x, z)
-    := - \alpha z + z^{1+\beta},
-    \quad x\in \mathbb R^d, z \in \mathbb R_+,
-\end{equation}
-}
+
         where $\alpha > 0$ and $\beta \in (0,1) $.
@@
     For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
-    Put $\|\mu\|=\langle 1,\mu\rangle$ \added{if it is well defined}.
+    Put $\|\mu\|=\langle 1,\mu\rangle$ if it is well defined.
     We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
-\deleted{
-\begin{equation} \label{super}
-    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
-        = e^{-\langle u_f(t,\cdot), \mu \rangle},
-        \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
-\end{equation}
-}
-\added{
 \begin{equation} \label{super}
@@
 \end{equation}
-}
-    where \deleted{$(t,x) \mapsto u_f(t,x)$} \added{$(t,x) \mapsto V_tf(x)$} is the unique locally bounded positive solution to the equation
-\deleted{
-\begin{equation}\label{eq1}
-	u_f(t,x) + \Pi_x \Big[ \int_0^t\psi\big(u_f(t-s, \xi_s)\big)~ds\Big]
-	= \Pi_x [f(\xi_t)],
-	\quad x\in \mathbb R^d, t\geq 0.
-\end{equation}
-}
-\added{
+
+    where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
 \begin{equation}\label{eq1}
@@
 \end{equation}
-}
-
-\deleted{
-	The existence of such superprocesses is well known, see \cite{EB} for instance.
-}
-\added{
+
 	The existence of superprocesses are well known, see \cite{EB} for instance.
-}
-    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
+    \deleted {Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.}
     According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
@@
     where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
-
     Define the \emph{Fenyman-Kac semigroup} by
@@
     = \langle T_t^\alpha f, \mu \rangle,
-    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d)\added{, \mu \in \mathcal M(\mathbb R^d)}.
+    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d), \mu \in \mathcal M(\mathbb R^d).
 \end{equation}
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that,
+    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $\deleted{R} \in \mathcal{P}$ such that,
+
+    {\bf Jianjie: we repeatedly use $R$ as both a function and a operator.}
 \begin{equation}
@@
 \end{equation}
-	For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.
+	For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa_f bt} |T_tf(x)|$.
 	Then $Q$ is an operator form $\mathcal P$ to $\mathcal P \cap \mathscr B
@@
 }
-\deleted{
+
 \subsection{}
-    Let $(\Omega, \mathscr F)$ be a measurable space.
-    Let $\mathcal F$ be a linear subspace of real valued measurable functions on $\Omega$.
-\begin{defi}
-\label{def: alpha-positive operator}
-    We say an operator $A: \mathcal F \to \mathcal F$ is $\alpha$-scalable for some $\alpha \in \mathbb R$ if for each $\lambda \in \mathbb R$ and $h \in \mathcal F$ we have $A (\lambda h) = |\lambda|^\alpha~ Ah$.
-\end{defi}
-    Suppose that $\alpha, \beta \in \mathbb R$.
-    Let $A_\alpha$ and $A_\beta$ be an $\alpha$-scalable and a $\beta$-scalable operator on $\mathcal F$.
-    Then it is clear that $A_\alpha A_\beta$ is an $(\alpha\beta)$-scalable operator.
-    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ defined by
-\begin{equation}
-    \mathcal{P}
-    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
-\end{equation}
-    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-    For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.
-    According to \cite[Fact 1.2]{MM}, $Q$ is an $1$-scalable operator on $\mathcal P$.
-    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R_0 \in \mathcal{P}$ such that,
-\begin{equation}
-\label{eq:semigroupineq}
-    |T_tf(x)|
-    \leq e^{-\kappa(f)bt} R_0(x),
-    \quad t\geq 0, x\in \mathbb R^d.
-\end{equation}
-}
-{\bf Zhenyao: I moved the next subsection in the appendix.}
-\deleted{
-\subsection{}
-    Recall $\Gamma$ the Gamma function be defined by
-\begin{equation}
-    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
-    \quad x>0,
-\end{equation}
-and
-\begin{align}
-\label{eq: definition of Gamma function}
-    \Gamma(x)
-    := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
-    \quad -n< x< -n+1, n\in \mathbb N.
-\end{align}
-    It is known that
-\begin{equation}
-    \Gamma(x+1) = x\Gamma(x),
-    \quad x>0~\text{or}~-n< x< -n+1, n\in \mathbb N.
-\end{equation}
-
-    Fix a $\beta \in (0,1)$.
-    According to \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that the following function:
-\begin{equation}
-    z
-    \mapsto z^{\beta}
-    := \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}},
-    \quad z\in \mathbb C_+,
-\end{equation}
-\begin{itemize}
-\item
-    is an extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
-\item
-    is continuous on $\mathbb C_+ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}$;
-\item
-    is holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$.
-\end{itemize}
-    According to Lemma \ref{lem: extension lemma for branching mechanism} in the Appendix, we can verify that the following function:
-\begin{equation}
-\label{eq: stable branching on C+}
-    z\mapsto
-    z^{1+\beta}
-    := \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
-    \quad z\in \mathbb C_+,
-\end{equation}
-\begin{itemize}
-\item
-    is an extension of the real function $x\mapsto x^{1+\beta}$ on $[0,\infty)$;
-\item
-    is continuous on $\mathbb C_+$;
-\item
-    is holomorphic on $\mathbb C_+^0$.
-\end{itemize}
-    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\to \mathbb C_+$ ,
-\begin{align}
-\label{eq: integration formula for 1+beta-th power of z}
-    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta}
-    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
-    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}}
-    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
-\end{align}
-    This indicates that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
-\begin{lem}
-\label{lem: Lip of power function}
-    There is a constant $C_{\ref{lem: Lip of power function}}$ such that for any $z_0,z_1 \in \mathbb C_+$,
-\begin{equation}
-\label{eq: Lip of power function}
-    |z_0^{1+\beta} - z_1^{1+\beta}|
-    \leq C_{\ref{lem: Lip of power function}}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
-\end{equation}
-    In particular, for each $z\in \mathbb C$, we have
-$
-    |z^{1+\beta}|
-    \leq  C_{\ref{lem: Lip of power function}} |z|^{1+\beta}.
-$
-
-\end{lem}
-\begin{proof}
-    Notice that
-\begin{align}
-\label{eq: upper bound for beta power of z}
-    &|z^{\beta}|
-    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big|
-    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
-    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
+    Let $X$ be the super OU-process discussed in the first subsection.
+    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
+    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
+\begin{equation}
+\label{eq: deriavetive of the Poission part}
+    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
     \quad z\in \mathbb C_+.
-\end{align}
-    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
-\[
-    \gamma(\theta)
-    = z_0 (1-\theta) + \theta z_1,
-    \quad \theta \in [0,1].
-\]
-    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
-\begin{align}
-    |z_0^{1+\beta} - z_1^{1+\beta}|
-    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
-    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
-    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
-    \qedhere
-\end{align}
-\end{proof}
-}
-\subsection{}
-    Let $X$ be the super OU-process discussed in the \deleted{previous subsections} \added{first subsection}.
-    Its branching mechanism $\psi$ can be extended on \deleted{$\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$} \added{$\mathbb R^d\times \mathbb C_+$ by $\psi(x, z) := -\alpha z + z^{1+\beta}$ for each $x\in \mathbb R^d$ and $z\in \mathbb C_+$}.
-    According to the above analysis, \added{for each $x\in \mathbb R^d$}, $\psi\added{(x,\cdot)}$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
-\begin{equation}
-\label{eq: deriavetive of the Poission part}
-    \psi'(\added{x,}z) := -\alpha + (1+\beta)z^{\beta},
-    \quad \added{x\in \mathbb R^d}, z\in \mathbb C_+.
-\end{equation}
-    Write $\psi_0(\added{x,}z) := \psi(\added{x,}z) + \alpha z$ and $\psi'_0(\added{x,}z) := \psi'(\added{x,}z) + \alpha$.
-    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in \deleted{E}\added{\mathbb R^d}$, define $\Psi_0f(x) := \psi_0(x,f(x))$ and $\Psi'_0 f(x) := \psi'_0(x,f(x))$.
-    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
+\end{equation}
+    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
+    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(\deleted {x,}f(x))$ and $\Psi'_0 f(x) := \psi'_0(\deleted {x,}f(x))$.
+    For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
     (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
@@
  \end{thm}
-For any $t>0$, let $W_t:=e^{-\alpha t}\|X_t\|$, then $W_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $W_{\infty}:=\lim_{t\rightarrow\infty}W_t$,  $\mathbb{P}_{\mu}$-a.s.
+For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s.
 and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  \begin{rem}
-    If $\kappa(f)=0$, $\langle f, \phi_{\kappa(f)}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
-     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle W_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
+    If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
+     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
     for any $0<\gamma<\beta$.
@@
 See Lemma \ref{lemma210} for more details about $\tilde{m}[f]$.
+Denote by $D$ the extinction event of super process.
 \begin{thm}\label{Theorem12}
@@
     In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
-\deleted{
-    Consider an incremental decomposition of $\langle g,X_t \rangle$.
-    For each $t\geq 0$, denote by $\{\mathscr{F}_t:t\geq 0\}$ the natrual filtration of $X$.
-    For each $g\in \mathcal P$ and $0 \leq a \leq b \leq t <\infty$, define random variable
-\[
-   	M_g^t(a,b)
-    := \mathbb P_{\mu}[\langle g,X_t\rangle|\mathscr F_b] - \mathbb P_{\mu}[\langle g,X_t\rangle|\mathscr F_a]
-    =\langle T_{t-b}^\alpha g, X_b\rangle - \langle T_{t-a}^\alpha g, X_a\rangle.
-\]
-    Thus, we have
-\begin{align}
-    M^t_g(0,t)
-    = \sum_{k = 0}^{\lfloor t \rfloor - 1} M^t_g(k,k+1) + M^t_g(\lfloor t \rfloor, t).
-\end{align}
-    Note that $I_a^b[\langle g,X_t \rangle] = I_a^b[\langle g,X_t\rangle]$
-\begin{align}
-    M_g^t(a,b) = M_{(T_{t-b}^\alpha g)}^b (a,b).
-\end{align}
-}
-
-\added{
 	For each $0 \leq a \leq b <\infty$ and  random variable $Y$ with finite mean, define random variable
@@
 \end{align}
-}
-
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
@@
     We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P^+$.
-    We say an operator $A$ is $\gamma$-controllable on $\mathcal D \added{\subset \mathcal P^*}$ for some $\gamma \in \mathbb R$ \deleted{and $\mathcal D \subset \mathcal P^*$} if $A: \mathcal D \to \mathcal P^*$ and there \deleted{exits} \added{is} a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
+    We say an operator $A$ is $\gamma$-controllable on $\mathcal D $ for some $\gamma \in \mathbb R$ if $A: \mathcal D \to \mathcal P^*$ and there  is a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
     In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
-    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\added{\subset \mathcal P^*}$ for some $\gamma \in \mathbb R$ \deleted{and $\mathcal D \subset \mathcal P^*$} if there \deleted{exits} \added{is} a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(\added{R}\deleted{M}, S)$ on $\mathcal D$, for each $s\in \Lambda$.
+    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$, for each $s\in \Lambda$.
 
     The first reason for considering $\gamma$-controllable operators is the following:
-\added{
 \begin{lem}
@@
 \end{proof}
-}
-\deleted{
-    For two operators $A$ and $B$ defined on same domain $\mathcal D\subset \mathcal P^*$, write $(A\times B)f (x):= Af(x) \times Bf(x)$.
-    Let $a \in \mathbb R$, write $A^{\times a}f(x):= (Af(x))^a$ as long as it is well defined for all .
-}
-\added{
 	For two operators $A: \mathcal D_A \to \mathcal P^*$ and $B: \mathcal D_B \to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for each $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
     Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for each $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
-}
     The second reason for considering $\gamma$-controllable operators is that they have good algebra properties:
@@
 \item[(2)]
-    Suppose that operators $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$ \added{for some $\beta \in \mathbb R$}.
+    Suppose that operators $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$ for some $\beta \in \mathbb R$.
     Also suppose that for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
@@
 \item[(4)]
-    Let \deleted{$a\in \mathbb R$} \added{$a>0$}. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
+    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
     Then operators $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ are uniformly $(a\gamma)$-controllable.
@@
    	Proof of (2): Let $(R_A, S_A)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$ and $(R_B, S_B)$ be the $\beta$-control-pair of $(B_{\delta})_{\delta\in\Delta}$ on $\mathcal{D}_0$.
-\added{
 	Note that $(R_BR_A, S_BS_A)$ is a $\beta \gamma$-control-pair.
@@
 	Finally, note that for each $\delta\in \Delta, \lambda\in\Lambda$ and $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|$ which says that operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ are uniformly $(\beta\gamma)$-controlled by $(R_BR_A,S_BS_A)$.
-}
 
@@
 \label{lem: upper bound for usgx}
-\added{The following statements are true for the super-OU process considered in the first subsection:}
+The following statements are true for the super-OU process considered in the first subsection:
 \begin{itemize}
@@
 \]
-    Note that $f\mapsto\sup_{0\leq u\leq 1}T^{\added{\alpha}}_u|f|$ is monotonic and $1$-scalable.
-    \added{Combine this with \eqref{eq: -v has positive real part}, we get the desired result.}
+    Note that $f\mapsto\sup_{0\leq u\leq 1}T^{\alpha}_u|f|$ is monotonic and $1$-scalable.
+    Combine this with \eqref{eq: -v has positive real part, we get the desired result.}
 
@@
     are uniformly $(1+\beta)$-controllable.
-    From \added{\eqref{eq:chareq2},} Lemma \ref{lem: property of controllable operators}(1) and this we get the desired result.
+    From \eqref{eq:chareq2}, Lemma \ref{lem: property of controllable operators}(1) and this we get the desired result.
 
@@
 \[
-    \mathbb P_\mu (|\deleted{M^t_g(0,t)} \added{I_0^t[\langle g,X_t\rangle]}| > \lambda)
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta
-    \deleted{\leq \langle S| g|,\mu\rangle \frac{2^{2+\beta/(2+\beta)}}{\lambda^{1+\beta}}}.
+    \mathbb P_\mu ( |I_0^t[\langle g,X_t\rangle]| > \lambda)
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
 \]
 \end{lem}
-\added{
+
 \begin{proof}
@@
 \end{proof}
-}
-
-{\bf Zhenyao: I will change $M_g^t(a,b)$ to $I_a^b[\langle g,X_t\rangle]$ without mention. Here ``I'' means incremental.}
-
 \begin{lem}
@@
 \[
-    \mathbb P_{\mu}(|\added{I_r^s[\langle g, X_t\rangle]}|>\lambda)
-    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle S\added{Q}g,\mu\rangle.
+    \mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda)
+    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle SQg,\mu\rangle.
 \]
 \end{lem}
-
 \begin{proof}
@@
     Then using Markovian property of $(X_t)_{t\geq 0}$ we get
-\added{
 \begin{align}
@@
 \end{align}
-}
     Note that
 \[
-    S := \frac{2^{2+\beta}}{2+\beta}QS_0\deleted{Q}
+    S := \frac{2^{2+\beta}}{2+\beta}QS_0
 \]
@@
 \begin{proof}
-	\added{Let $S$ be the $(1+\beta)$-scalable operator in the previous Lemma.}
+Let $S$ be the $(1+\beta)$-scalable operator in the previous Lemma.
     For each $c>0$ we have
@@
     \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|I_r^s[\langle g, X_t\rangle]|> \lambda) d\lambda
-    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle S\added{Q}g,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
-    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle S\added{Q}g,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
+    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle SQg,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
+    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle SQg,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
 \end{align}
@@
 \end{proof}
-\begin{comment}
-\end{comment}
-    \deleted{As $\langle g,X_t\rangle,~g\in \mathcal{P}$ is the sum of $M_g^t(k,k+1), k=0,1,...,\lfloor t\rfloor$ and $M_g^t(\lfloor t\rfloor, t)$. We obtain the following lemma.}
-
 \begin{lem}
-\label{lemma24}
+\label{lem: control moment}
     For each $0 < \gamma < \beta$ and $\mu\in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$ there exists a constant $C>0$ such that for each $t\geq 0$:
@@
 \end{align}
-{\bf Zhenyao: we should show that it is well defined.}
-    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra \added{$\{\mathscr{F}_t\}_{t\geq 0}$}.
-{\bf Zhenyao: I changed all $\mathcal F$ to $\mathscr F$ without mention below. I want to use mathscr for $\sigma$-fields and mathcal for function classes.}
+\added{{\bf Zhenyao: we should show that it is well defined.}}
+    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathscr{F}_t\}_{t\geq 0}$.
 \begin{lem}
@@
     There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$.
-    Using  Lemma \ref{lemma24} and the fact $\kappa_{\phi_p}=|p|$, we get that, \deleted{for any $\gamma_0\leq\gamma<\beta$,} there exists a constant $C_{\gamma, \mu, p} \added{>0}$ \added{(which depends on the choice of $\gamma$, $\mu$ and $p$)}  such that
- \added{
+    Using  Lemma \ref{lemma24} and the fact $\kappa_{\phi_p}=|p|$, we get that, there exists a constant $C_{\gamma, \mu, p}>0$ (which depends on the choice of $\gamma$, $\mu$ and $p$)  such that
  $$
@@
  $$
- }
-    For any $0\leq\gamma<\gamma_0$, \deleted{consider the concave function $x\mapsto x^{(1+\gamma)/(1+\gamma_0)}$ on $[0,\infty)$, using Jensen's inequality, we have} \added{note that}
-\added{
+    For any $0\leq\gamma<\gamma_0$, note that
 $$
@@
 $$
-}
-
-    Hence \added{, for each $\gamma \in (0,\beta)$,} the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicate\added{s} the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ and almost sure,
+
+    Hence, for each $\gamma \in (0,\beta)$, the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicates the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ and almost sure,
 %added
@@
 
+\deleted{
     Recall that $\|X_t\|=\langle 1,X_t\rangle$.
@@
 So $W_{\infty}$ is non-degenerate and the $(1+\gamma)$-th moment is finite.
-Moreover,  we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D,$ \added{$\mathbb{P}_{\mu}$-a.s} \deleted{which is the extinction event}.
+Moreover,  we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D,$ $\mathbb{P}_{\mu}$-a.s.
+
 %comment
     {\bf Zhenyao: we need references for the last assertion. Also, we used three different notation $M, H$ and $W$ to denote one martingale. This is unnessary.}
+    }
 %end comment
+\added{
+In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ convergences to $H_{\infty}$ $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.}
 \begin{lem}\label{lem: control of Wt}
  %For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have
- For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a \added{$C> 0$} such that for each $0\leq s<t$,
- $$\|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq \added{C} e^{-\alpha s/2}.$$
+ For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for each $0\leq s<t$,
+ $$\|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-\alpha s/2}.$$
 \end{lem}
@@
      Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-    According to Lemma \ref{lem: control of mgtrs}, there exists a constant \added{$C_0>0$}, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
+    According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C_0>0$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
     \begin{align}
         \mathbb{P}_{\mu}\big[\big|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\|\big|^{1+\gamma}\big]
-        \deleted{=\mathbb{P}_{\mu}[|M_1^t(r,s)|^{1+\gamma}]}
-        \leq \added{C_0}e^{\alpha t+(t-s)\deleted{(}\alpha\gamma\deleted{-(1+\gamma)b)}}.
+        \leq C_0e^{\alpha t+(t-s)\alpha\gamma}.
     \end{align}
@@
     \begin{align}
-        \mathbb{P}_{\mu}\left|W_s-W_r\right|^{1+\gamma}\leq  \added{C_0} e^{-\alpha \gamma s}.
-    \end{align}
-    Then \added{there is a $C>0$,} for any $0\leq s<t$,
-\deleted{
-    \begin{align}
-       & \|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq \|W_{\lfloor s \rfloor +1}-W_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+2}^{\lfloor t \rfloor}\|W_k-W_{k-1}\|_{\mathbb{P}_{\mu};1+\gamma}+\|W_t-W_{\lfloor t \rfloor}\|_{\mathbb{P}_{\mu};1+\gamma}
-       \\&\leq C_{\ref{lem: control of Wt}}e^{-\frac{\alpha \gamma}{1+\gamma}s}\leq C_{\ref{lem: control of Wt}}e^{-\frac{\alpha}{2}s}.
-    \end{align}
-}
-\added{
-\begin{align}
-	& \|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}
-	\leq \|W_{\lfloor s \rfloor+1}-W_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|W_{k+1}-W_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|W_t-W_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
+        \mathbb{P}_{\mu}\left|H_s-H_r\right|^{1+\gamma}\leq  C_0 e^{-\alpha \gamma s}.
+    \end{align}
+    Then there is a $C>0$, for any $0\leq s<t$,
+\begin{align}
+	& \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}
+	\leq \|H_{\lfloor s \rfloor+1}-H_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H_{k+1}-H_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H_t-H_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
 	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
@@
 \end{align}	
-}
-\end{proof}
-
-\deleted{
-As $\|X_t\|$ is an continuous state branching process with initial mass $\|\mu\|$.
-for any $\lambda>0$, $\|X_t\|$ satisfies, see \cite[Chapter 3]{Li2011Measure-valued}, for example.
-\begin{align}\label{CSBP}
-    \mathbb{P}_{\mu}e^{-\lambda\|X_t\|}=e^{-\|\mu\|v_t(\lambda)}
-\end{align}
-where $v_t(\lambda)$ is the unique local bounded solution to the equation
-\begin{align*}
-    \frac{\partial}{\partial t}v_t(\lambda)=-\psi(v_t(\lambda)), \quad  v_0(\lambda)=\lambda,  \quad \lambda>0, t\geq 0.
-\end{align*}
-
-In this paper, for any $\beta\in (0,1)$, $v_t(\lambda)$ has explicit expression \cite[Example 3.1]{Li2011Measure-valued}
-\begin{align*}
-    v_t(\lambda)=\frac{e^{\alpha t} \lambda}{[1+\frac{1}{\alpha}(e^{\alpha \beta t}-1)\lambda^{\beta}]^{1/\beta}}=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
-\end{align*}
-If we fix $t>0$, $v_t(\lambda)$ is increasing corresponding to $\lambda$.
-}
-\added{
-    According to \cite[Example 3.1]{Li2011Measure-valued}, we have
+\end{proof}
+
+\added{Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
 \begin{align}\label{CSBP}
@@
 \]
-}
-
-    Recall that the \deleted{superprocess $X$'s} extinction probability \added{of the superprocess is} $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
-    Denote \added{by} $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$. 
-    \added{According to \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and 
-    $t\geq 0$,}
-\added{
+
+     Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$}.
+    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+    By \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
+    $t\geq 0$,
+
 \begin{align}
@@
 \end{align}
-}
-    \deleted{We want to prove the following Lemma}
-\added{
+
 \begin{lem}\label{lem: control of XT}
@@
 \end{lem}
-}
-\begin{proof}
- \deleted{Without loss of generality, we assume that $\|\mu\|=1$,} By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
-\added{
+
+\begin{proof}
+ By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
+
 \begin{align*}
@@
 \end{align*}
-}
 	Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t}$ where $t\geq 0,\lambda\geq0$ then $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
-\added{Note that}
+Note that
 \begin{align*}
@@
 \end{align*}
-Therefore, \added{for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for each non-negative function $f$ on $[0,\infty),$ each $\lambda \geq 0$ and each $t\geq 0$ we have }
+Therefore, for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for each non-negative function $f$ on $[0,\infty),$ each $\lambda \geq 0$ and each $t\geq 0$ we have 
 \begin{align}
@@
 \end{align}
-\deleted{
-Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\cdot\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}\exp(\beta(\ln f(t)-\alpha t))
-\end{align*}
-}
+
 Notice that
@@
     \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
-    &\added{\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.}
-\end{align*}
-\added{Therefore, for each $\lambda \in [0,1]$,
+    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.
+\end{align*}
+Therefore, for each $\lambda \in [0,1]$,
 \begin{align*}
@@
 \end{align*}
-}
-\added{Finally, taking $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.}
+Finally, taking $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.
 \end{proof}
 	Define $\mathcal{A}_t(\epsilon):=\{ \|X_t\|\in \|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\}$ where $\epsilon,t>0$.
-\deleted{
-\begin{lem}\label{lem: control of AT}
-  For any $\epsilon,t>0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$ and $\delta>0$ such that
-  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\delta t}.$$
-\end{lem}
-}
-\added{
+
 \begin{lem}\label{lem: control of AT}
@@
 \end{lem}
-}
-
-\begin{proof}
-    First, for any $\epsilon>0$, using Markov inequality, \added{we get for each $\epsilon>0$ and $t\geq 0$,}
-\added{
+
+\begin{proof}
+    First, for any $\epsilon>0$, using Markov inequality, we get for each $\epsilon>0$ and $t\geq 0$,
 \begin{align}
@@
 \end{align}
-}
+
     For another side, using Lemma \ref{lem: control of XT}, we have
     $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_0 e^{-\beta\epsilon t}, $$
-    \added{for some constant $C_0>0$ not related to $\epsilon>0$ and $t\geq 0$.}
-\deleted{To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.}
+     for some constant $C_0>0$ not related to $\epsilon>0$ and $t\geq 0$.
 \end{proof}
@@
  \end{align}
- \deleted{Using the same argument as in the proof of \cite[Lemma2.7, Lemma4.2 \& Lemma 5.1]{MM}, we can show that}
-\added{According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that 
+According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
 \[
@@
 \]
-}
-\deleted{Therefore, $m_t[f]$ is well-defined.}
-
-\added{
+
     Let $f \in \mathcal{P}$.
@@
 \end{align}
-}
-
-\added{
+
     Note that $m_t[\theta f]$ can be rewritten as follows:
@@
 \end{proof}
-}
+
 \section{Proof of main results}
@@
 Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.
-
+\begin{comment}
 \begin{lem}\label{lemma31}
@@
 \end{proof}
-{\bf Zhenyao: The proof of the above lemma is not right. The proof of the following lemma is not accurate.}
+\end{comment}
+
 \begin{lem}\label{lemma32}
-Recall $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\},~\epsilon,t>0$, then for any $\epsilon>0$, we have
+Recall $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\},~\epsilon,t>0$, then for any $\epsilon>0$, we have
 \begin{align}
@@
 \end{lem}
+\added{
 \begin{proof}
@@
 
-    For any $\omega \in D^c$, there exists $\delta>0$ such that $W_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$,\deleted{$~\mathbb{P}_{\mu}$-a.s}.
-As $W_t$ converges to $W_{\infty}$ $\mathbb{P}_{\mu}$-a.s, there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq W_t(\omega)\leq 2\delta,$\deleted{$~\mathbb{P}_{\mu}$-a.s}.
+    For any $\omega \in \{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}$, there exists $\delta>0$ such that $H_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$ and there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq H_t(\omega)\leq 2\delta,$.
 Taking $S_2>0$ such that for any $t>S_2$, $\|\mu\|e^{-\epsilon t}<\frac{\delta}{2}$ and $\|\mu\|e^{-\epsilon t}>2\delta$, then $\omega\in \mathcal{A}_t(\epsilon),~t>S:=\max\{S_1,S_2\}$ implies $\omega \in \liminf_{t\rightarrow \infty}\mathcal{A}_t(\epsilon):=\cup_{S>0}\cap_{t\geq S}\mathcal{A}_t(\epsilon)$.
-\end{proof}
-\deleted{
-\begin{lem}
-For any $f\in \mathcal{P}$ and $k\in \mathbb{N}$, let $m_k[f]$ be the parameter defined in \eqref{parameter_mk}, then the function $\theta\mapsto \exp(\theta^{1+\beta}e^{\alpha}m_k[f])$ defined on $\theta\in(0,\infty)$ is a characteristic function of some $(1+\beta)$-stable random variable.
-\end{lem}
-\begin{proof}
-    Let $J=\langle\int_0^1 T_{1-s}^{\alpha}(-T^{\alpha}_s f)^{1+\beta}(\cdot)ds,\varphi\rangle$, then
-    \begin{align}
-        m_k[f]=J e^{-\alpha(k+1)}\cdot i^{1+\beta}=J e^{-\alpha(k+1)}\cos\frac{(1+\beta)\pi}{2}\big(1+i\tan\frac{(1+\beta)\pi}{2}\big).
-    \end{align}
-Thus
-\begin{align}
-    \exp(\theta^{1+\beta}e^{\alpha}m_k[f])=\exp\big(J e^{-\alpha k}\cos\frac{(1+\beta)\pi}{2}\cdot\theta^{1+\beta}\big(1+i\tan\frac{(1+\beta)\pi}{2}\big)\big)
-\end{align}
-B \cite[Theorem 14.15]{Sato1999Levy}, we get the result.
+
+    According to \cite{LSR}, $D^c=\{H_{\infty}>0\}~ \mathbb{P}_{\mu}$-a.s, combining with the fact $\lim_{t\rightarrow \infty}H_t=H_{\infty}~\mathbb{P}_{\mu}$-a.s, we get the result.
 \end{proof}
@@
 
- Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
- \begin{align}
-      \frac{M_k^t[f]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
+ Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa_fb(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+ \begin{align}
+      \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
  \end{align}
  where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
- $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[f]\right].$$
+ $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[e^{\alpha}m_k[\theta f]\right].$$
  \end{lem}
@@
  \begin{proof}
-     Let $v_{f_k}(x,\theta)=v_{f_k}(1,x,\theta),\tilde{v}_{f_k}(x,\theta)=\tilde{v}_{f_k}(1,x,\theta)$ and $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$.
-For any $k\in\mathbb{N}$ and $t>k$, we have
-         \begin{align}
-        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})\big|\mathscr{F}_{t-k-1}\big]\\
-        &=\exp\big(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
+For each $\theta \in \mathbb{R}$, let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any $k\in\mathbb{N}$ and $t>k+1$, we have
+         \begin{align}
+        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})\big|\mathscr{F}_{t-k-1}\big]\\
+        &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
         \label{condition mean}
-        &=\exp\big(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle\big)\\
+        &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle+\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle\big)\\
        \end{align}
@@
        \begin{align}
-           \mathbb{P}_{\mu}\Big(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\Big)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(\theta^{1+\beta}e^{\alpha}m_k[f]).
+           \mathbb{P}_{\mu}\Big(\exp(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\Big)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[\theta f]).
+       \end{align}
+     Equivalently, by Lemma \ref{lemma32}, we just need to prove
+     \begin{align}
+        \Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\xrightarrow{t\rightarrow\infty} 0.
+    \end{align}
+      According to \eqref{condition mean},
+    \begin{align}
+        &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
+        &=\Big|\mathbb{P}_{\mu}\Big[\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big]\Big|\\
+        &\leq \mathbb{P}_{\mu}\big[\big|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
+        \label{ineqinlem31}
+        &+\mathbb{P}_{\mu}\big[\big|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big].
+    \end{align}
+Step 1.  We will show that for each $\mu \in\mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k+1$,
+    \begin{align}
+    \label{lemma31q}
+        \mathbb{P}_{\mu}\big[\big|\langle  U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\leq C|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
+    \end{align}
+Let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6). For any $\theta\in\mathbb{R}$, $k \in \mathbb N$ and $t>k+1$, we have
+\begin{align}
+   & \big|U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq R\big(|\tilde{\theta}_{t,k}T_k^{\alpha}f|\big)\leq R \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
+   \\& \leq S \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big) 
+   \leq \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+2\beta}SQf
+   \\&=\frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}SQf.
+\end{align}
+Thus,
+\begin{align}
+     &\mathbb{P}_{\mu}\big[\big|\langle  U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
+     &\leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}\mathbb{P}_{\mu}[\langle SQf,X_{t-k-1}\rangle]\\
+     & \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}e^{-\alpha(t-k-1)}\langle QSQf, \mu \rangle\\
+     & \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle QSQf,\mu\rangle|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
+\end{align}
+Step 2, for any $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ and $\theta\in \mathbb{R}$, we will show that there exists $C>0$ such that
+\begin{align}
+\label{eq:31step3}
+    &\mathbb{P}_{\mu}\big[\big|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
+    &\leq C|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)},\quad k\in \mathbb{N}, t\geq k+1.
+\end{align}
+    Notice that $\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]=\theta^{1+\beta}e^{-\alpha k}(\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|} \rangle-\langle Z_{f_k},\varphi\rangle)$.
+Therefore,
+
+\begin{align}
+        &\mathbb{P}_{\mu}\left[\left|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
+    &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{P}_{\mu}\left[\left|\frac{\langle Z_1(T^{\alpha}_k f),X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1(T^{\alpha}_k f)Z_{f_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\nonumber\\
+    &\leq |\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon_0)(t-k-1)}\mathbb{P}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
+\end{align}
+where $h_k(x):= Z_1(T^{\alpha}_k f)(x)-\langle  Z_1(T^{\alpha}_k f),\varphi\rangle,~x\in\mathbb{R}^d$.
+According to \cite[Lemma 2.8]{MM}, there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
+ \begin{align}
+ \label{eq:31step2}
+     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa_fb)(1+\beta)k}R_7(x).
  \end{align}
 \deleted{
-        \begin{align}
-        &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c}\right]\right| \\
-        &\leq\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\right|\\
-        &+\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right|
-        \end{align}
-         Let $c=|\theta^{1+\beta}e^{\alpha}m_k[f]|$. By lemma \ref{lemm28}, there exists $\delta_1>0$ and $C_5>0$ such that
-       \begin{align}
-            &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right| \\
-            &\leq \mathbb{P}_{\mu}(D^c)\mathbb{\tilde{P}}_{\mu}(\mathcal{A}_{t-k-1})\leq (1+e^c)C_5\mathbb{P}_{\mu}(D^c)e^{-\delta_1(t-k-1)}.
-       \end{align}
-       }
-     Equivalently, by Lemma \ref{lemma32}, we just need to prove
-     \begin{align}
-        \Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\xrightarrow{t\rightarrow\infty} 0.
-    \end{align}
-
-      \deleted{ On the other hand, by formula \eqref{condition mean} and Lemma \ref{estim}}
-      By formula \eqref{condition mean} and lemma \ref{lemma31},
-    \begin{align}
-        &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
-        &=\Big|\mathbb{P}_{\mu}\Big[\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big]\Big|\\
-        &\leq e^c\mathbb{P}_{\mu}\big[\big|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
-        \label{ineqinlem31}
-        &+e^c\mathbb{P}_{\mu}\big[\big|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big].
-    \end{align}
-Step 1.  We will show that for each $\mu \in\mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_6>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k$,
-    \begin{align}
-    \label{lemma31q}
-        \mathbb{P}_{\mu}\big[\big|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
-    \end{align}
-Combining with \eqref{eq:semigroupineq}, \eqref{eq:gcontrol1} and Lemma \ref{lemma2}, there exist $R_1^f,R_6>0$ such that
-\begin{align}
-    & |v_{f_k}(x,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(x,\tilde{\theta}_{t,k})|\leq |\tilde{\theta}_{t,k} e^{(\alpha-\kappa(f) b)k}|^{1+2\beta}R^f_1(x),\\
-    & |T_t (R^f_1)(x)|\leq R_6(x), \quad x\in \mathbb{R}^d,t\geq 0, \theta \in \mathbb{R}.
-\end{align}
-%Let $R_1$ be the control function in Lemma \ref{lemma2}.
-According to \eqref{eq:semigroupineq}, there exists $R_6\in \mathcal{P}$, satisfying $|T_t %(R_1)(x)|\leq R_6(x)$, for each $t>0$ and $x\in \mathbb{R}^d$.
-
-For any $\theta\in \mathbb{R}$, $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}(\epsilon_0)$, we have
-    \begin{align*}
-        &\mathbb{P}_{\mu}\big[\big|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]
-        \\ &\leq \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+2\beta}\mathbb{\tilde{P}}_{\mu}\langle R^f_1,X_{t-k-1}\rangle\\
-        &\leq\frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle R_6,\mu\rangle|\theta|^{1+2\beta}e^{\alpha(t-k-1)} e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}\\
-        &\leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle R_6,\mu\rangle|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
-    \end{align*}
-     \deleted{
- Step 2.
-Let $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.According to \cite[Lemma 2.8]{MM}, there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
- \begin{align}
- \label{eq:31step2}
-     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa(f)b)(1+\beta)k}R_7(x).
- \end{align}
-
- Let $\tilde{f}=T_1^{\alpha}f$, then $\kappa(\tilde{f})=\kappa(f)$.
-It is easy to show that $\tilde{f}\in C^{\infty}$ and $\tilde{f}^{(p)}\in\mathcal{P},~p\in\mathbb{Z}_+^d$, thus by the inequality \eqref{eq:semigroupineq} and the fact $\kappa\big(\frac{\partial \tilde{f}}{\partial x_i}\big)\geq \kappa(\tilde{f})-1$, see \cite[Lemma 2.3]{RSZ}, we get there exists $\tilde{R}_7\in \mathcal{P}$ such that for each $i=1,...,d$
- \begin{align}
- \label{ineq-temp}
-     \Big|T_t\big(\frac{\partial\tilde{f}}{\partial x_i}\big)(x)\Big|\leq e^{(\alpha-(\kappa(f)-1)b)t}\tilde{R}_7(x), \quad x\in \mathbb {R}^d, t\geq 0.
- \end{align}
- As $\langle h_k,\varphi\rangle=0$,
- \begin{align}
-     &T_s h_k(x)= T_s [h_k(\cdot+xe^{-bs})] (0)-\langle h_k,\varphi\rangle
-     \\ &= \int_{\mathbb{R}^d}\big(h_k(xe^{-bs}+y\sqrt{1-e^{-2bs}})-h_k(y)\big)\varphi (y)~dy
-     \\ &\leq \int_{\mathbb{R}^d}|\nabla h_k(z)||xe^{-bs}+y\sqrt{1-e^{-2bs}}-y|\varphi (y)~dy.
-  \end{align}
- Where $z$ is a point on the line segment connecting $y$ and $xe^{-bs}+y\sqrt{1-e^{-2bs}}$. For each $i=1,...,d$
- \begin{align}
-     \frac{\partial h_k}{\partial x_i}(x)=\frac{\partial Z_{g_k}}{\partial x_i}(x)=\int_0^1 T^{\alpha}_{1-s}\Big(\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha} \tilde{f})^{1+\beta}\Big)(x)~ds.
- \end{align}
-  Let $R_0$ be the control function in \eqref{eq:semigroupineq},
-      \begin{align}
-        \Big|\frac{\partial}{\partial x_i}(-i T_{s+k-1}^{\alpha}\tilde{f})^{\beta}\Big|&=\Big|(1+\beta)(-i T_{s+k-1}^{\alpha}\tilde{f})^{\beta}(-i e^{-b(s+k-1)}T_{s+k-1}^{\alpha}\big(\frac{\partial \tilde{f}}{\partial x_i}\big))\Big|\\
-        &\leq e^{(\alpha-\kappa(\tilde{f})b)(s+k-1)(1+\beta)}\cdot (1+\beta)e^{(\alpha-\kappa(f)b)\beta}R_0^{\beta}(x)\tilde{R}_7(x).
-    \end{align}
-Thus there exists $R_8\in \mathcal{P}$,
-\begin{align}
-\label{eq:31temp }
-    \Big|\frac{\partial}{\partial x_i}h_k(x)\Big|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_8(x),\quad x\in \mathbb{R}^d, k\in \mathbb{N}.
-\end{align}
-By \eqref{eq:31temp } and the fact $|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y|\leq e^{-bs}(|x|+|y|)$,
-\begin{align}
-    |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa(f)b)(1+\beta)k}R_8(x)(|x|+\int_{\mathbb{R}^d}|y|\varphi(y)~dy).
-\end{align}
-}
-Step 2, for any $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ and $\theta\in \mathbb{R}$, we will show that there exists $C_7>0$ such that
-\begin{align}
-\label{eq:31step3}
-    &\mathbb{P}_{\mu}\big[\big|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
-    &\leq C_7|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)},\quad k\in \mathbb{N}, t\geq k.
-\end{align}
-    Notice that $\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]=\theta^{1+\beta}e^{-\alpha k}(\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|} \rangle-\langle Z_{f_k},\varphi\rangle)$.
-Therefore,
-    %and $\theta^{1+\beta}e^{\alpha}m_k[f]=\theta^{1+\beta}e^{-\alpha k}\langle Z_{f_k},\varphi\rangle$.
-\begin{align}
-        &\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
-    &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{P}_{\mu}\left[\left|\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle Z_{f_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\nonumber\\
-    &\leq |\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon_0)(t-k-1)}\mathbb{P}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
-\end{align}
-\added{
-where $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.According to \cite[Lemma 2.8]{MM}, there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
- \begin{align}
- \label{eq:31step2}
-     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa(f)b)(1+\beta)k}R_7(x).
- \end{align}
-}
 Thus $h_k$ satisfies \eqref{eq:gcontrol1} with $C_{h_k}=e^{(\alpha-\kappa(f))(1+\beta)k}$, $\kappa=1$ and $R_0^{h_k}(x)=R_7(x)$, fix some $\gamma_0\in(0,\beta)$, according to Lemma \ref{lemma24}, there exist $C_8>0$,
@@
 \end{align}
+}
+{\bf Jianjie: I think we should change the condition of Lemma \ref{lem: control moment} }
 We want to emphasize that, on the case $\alpha\gamma_0=(1+\gamma_0)b$, the second equation holds when $t$ is large enough. Thus
@@
 Let $f\in \mathcal{P}$ and $\Theta>0$, assume that $\alpha\beta\leq\kappa(f)b(1+\beta)$.
-There exists $C_9,\delta_2>0$ such that for any $n \in \{0,...,t\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
+There exists $C,\delta>0$ such that for any $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
 \begin{align}
 \label{32corollary}
-    \left|\mathbb{\tilde{P}}_{\mu}\left(\prod_{k=0}^n\exp(i\theta_k \frac {M_k^t[f]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}})-\prod_{k=0}^n\exp(\theta_k^{1+\beta}e^{\alpha}m_k[f])\right)\right|\leq C_9 e^{-\delta_2(t-n)}
+    \left|\mathbb{\tilde{P}}_{\mu}\left(\prod_{k=0}^n\exp(i\theta_k \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}})-\prod_{k=0}^n\exp(e^{\alpha}m_k[\theta_k f])\right)\right|\leq C e^{-\delta(t-n)}
 \end{align}
@@
 \begin{proof}
-    Denote $\gamma_{t,k}=\frac {M_k^t[f]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}} $, we define
-    $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[f]\right)\mathbb{\tilde{P}}_{\mu}\left(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\right)$$
+    Denote $\gamma_{t,k}=\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}} $, we define
+    $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp\left(e^{\alpha}m_l[\theta_lf]\right)\mathbb{\tilde{P}}_{\mu}\left(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\right)$$
     for $k\in\{-1,...,n\}$, if $k=-1$, the product is one. Then Conditioning with $\mathscr{F}_{t-k-1}$ we get
     \begin{align*}
-        \varphi^{k-1}_t(\theta_0,...,\theta_n)-&\varphi^{k}_t(\theta_0,...,\theta_n)=\prod_{l=0}^{k-1}\exp\left(\theta_l^{1+\beta}e^{\alpha}m_l[f]\right)\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left(\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[f]}\right)\prod_{l=k+1}^n\exp(i\theta_l \gamma_{t,l})\right]
+        \varphi^{k-1}_t(\theta_0,...,\theta_n)-&\varphi^{k}_t(\theta_0,...,\theta_n)=\prod_{l=0}^{k-1}\exp\left(e^{\alpha}m_l[\theta_l f]\right)\\
+        &\mathbb{\tilde{P}}_{\mu}\left[\left(\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta_kf]}\right)\prod_{l=k+1}^n\exp(i\theta_l \gamma_{t,l})\right]
     \end{align*}
@@
     \begin{align*}
-        \left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| \leq \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta_k^{1+\beta}e^{\alpha}m_k[f]}\right|.
-    \end{align*}
-    Step 1, we will prove that there exists $C_{10},\delta_3>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,t\}$,
+        \left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| \leq \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta_kf]}\right|.
+    \end{align*}
+    Step 1, we will prove that there exists $C,\delta>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,\lfloor t\rfloor\}$,
     \begin{align}
     \label{eq:32step1}
-        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[g]}\right|\leq C_{10} e^{-\delta_3(t-k-1)}.
-    \end{align}
-    %we completed our proof, as the left side of thesis of the lemma is equal to %$\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|$.
-
-    Recall that
-    $$\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)=\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle).$$
- By \eqref{lemma31q} and \eqref{eq:31step3}, we easily get, if $|\theta|\leq\Theta$ and $k\in\{0,...,t\}$,
-    \begin{align*}
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq \frac{C_{6}}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq \frac{C_{7}}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)}.
+        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta f]}\right|\leq C e^{-\delta(t-k-1)}.
+    \end{align}
+
+ By \eqref{lemma31q} and \eqref{eq:31step3}, we easily get, if $|\theta|\leq\Theta$ and $k\in\{0,...,\lfloor t\rfloor\}$,
+    \begin{align*}
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle  U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}\\
+        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)}.
     \end{align*}
@@
 \begin{align*}
-    \mathcal{B}_{t-k-1}:=\left\{\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq\frac{C_{6}}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{4(1+\beta)}(t-k-1)}\right\}.
+    \mathcal{B}_{t-k-1}:=\left\{\left|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq\frac{C}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{4(1+\beta)}(t-k-1)}\right\}.
 \end{align*}
@@
 \begin{align*}
-    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq \frac{C_{7}}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+\beta} e^{-\frac{p}{4}(t-k-1)}\right\},
+    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+\beta} e^{-\frac{p}{4}(t-k-1)}\right\},
 \end{align*}
@@
 
-Hence, for any $k\in\{0,...,t\}$, on the event $\mathcal{A}_{t-k-1}(\epsilon_0)\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1}$, we get
-\begin{align*}
-   &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[f]}\right|\\
-   &\leq \left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|
-   +\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\\
-   &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}(C_6|\Theta|^{1+2\beta}+C_7|\Theta|^{1+\beta}) e^{-\min\{\frac{\alpha\beta}{4(1+\beta)},\frac{p}{4}\}(t-k-1)}.
+Hence, for any $k\in\{0,...,\lfloor t\rfloor\}$, on the event $\mathcal{A}_{t-k-1}(\epsilon_0)\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1}$, we get
+\begin{align*}
+   &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta f]}\right|\\
+   &\leq \left|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\right|
+   +\left|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\right|\\
+   &\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}(|\Theta|^{1+2\beta}+|\Theta|^{1+\beta}) e^{-\min\{\frac{\alpha\beta}{4(1+\beta)},\frac{p}{4}\}(t-k-1)}.
 \end{align*}
@@
 \begin{align*}
-    &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{\theta^{1+\beta}e^{\alpha}m_k[f]}\right|\\
+    &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta f]}\right|\\
     &\leq 2(\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1}(\epsilon_0))+\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1}))\\
@@
     \\&\leq\sum_{k=0}^n\left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right|
-    \\&\leq \sum_{k=0}^n C_{10} e^{-\delta_3(t-k-1)}.
+    \\&\leq \sum_{k=0}^n C e^{-\delta_3(t-k-1)}.
 \end{align}
@@
 
-In next three subsections, we just use $C$ and $\delta$ as a constant positive real number, which may be different in different formula.
 \subsection{Proof of Theorem \ref{Theorem12}}
@@
 
-{ \color{blue}
 \subsection{}
@@
 \end{proof}
-}
 
@@
 
+\bibitem{LSR}
+Liu, R.,  Ren, Y.-X., Song, R.:
+\emph{ L Log L Criterion for a Class of Superdiffusions.}
+Journal of Applied Probability, 46(2), 479-496. 2009.
+
 \end{thebibliography}

### 2019-01-31 supCLT.tex
supCLT.tex: 1115b

@@
     There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$.
-    Using  Lemma \ref{lemma24} and the fact $\kappa_{\phi_p}=|p|$, we get that, there exists a constant $C_{\gamma, \mu, p}>0$ (which depends on the choice of $\gamma$, $\mu$ and $p$)  such that
+    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that, there exists a constant $C_{\gamma, \mu, p}>0$ (which depends on the choice of $\gamma$, $\mu$ and $p$)  such that
  $$
@@
     Hence, for each $\gamma \in (0,\beta)$, the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicates the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ and almost sure,
-%added
     according to \cite[Theorem 5.4.5]{Durrett2010Probability}.
-%end added
 \end{proof}
 
-\deleted{
-    Recall that $\|X_t\|=\langle 1,X_t\rangle$.
-    By Lemma \ref{lemma26},
-    %it is not to hard to prove that,
-    it is clear that,
-    under $\mathbb{P}_{\mu}$, the process $W_t=e^{-\alpha t}\|X_t\|$ is a positive martingale satisfying
-$\lim_{t\rightarrow \infty} W_t= W_{\infty},$
-$\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-So $W_{\infty}$ is non-degenerate and the $(1+\gamma)$-th moment is finite.
-Moreover,  we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D,$ $\mathbb{P}_{\mu}$-a.s.
-
-%comment
-    {\bf Zhenyao: we need references for the last assertion. Also, we used three different notation $M, H$ and $W$ to denote one martingale. This is unnessary.}
-    }
-%end comment
-\added{
-In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ convergences to $H_{\infty}$ $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.}
+In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ convergences to $H_{\infty}$, $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{lem}\label{lem: control of Wt}
@@
 	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
+    \qedhere
 \end{align}	
@@
 
-\added{Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
+\deleted{
+Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
 \begin{align}\label{CSBP}
@@
 \]
-
-     Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$}.
+    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
     Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
@@
 \end{align}
+}
+
+\added{Write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.}
 
@@
 \begin{proof}
+\added{
+    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
+\begin{align}\label{CSBP}
+    \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
+    =e^{-\|\mu\|v_t(\lambda)},
+    \quad \lambda \geq 0, t\geq 0,
+\end{align}
+    where
+\[
+    v_t(\lambda)=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
+\]
+    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
+    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+    By \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
+    $t\geq 0$,
+
+\begin{align}
+    \label{laplaceexpress}
+    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]
+    &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
+    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\alpha^*\|X_t\|})] }{\mathbb P_\mu(D^c)}
+    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}
+    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
+\end{align}
+}
+
 By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
@@
 Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.
-\begin{comment}
-\begin{lem}\label{lemma31}
-For any $x,y\in \mathbb{C}$, $|e^x-e^y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|$.
-\end{lem}
-\begin{proof}
-let $z=Re(y)+iIm(x)$,
-\begin{align}\label{estim}
-    |e^x-e^y|\leq|e^x-e^z|+|e^z-e^y|\leq |e^{Re(x)}-e^{Re(y)}|+e^{Re(y)}|x-y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|.
-\end{align}
-\end{proof}
-\end{comment}
 
 \begin{lem}\label{lemma32}
-Recall $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\},~\epsilon,t>0$, then for any $\epsilon>0$, we have
+    \deleted{Recall} \added{Write} $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\},$ for each $\epsilon,t>0$. 
+    Then for any $\epsilon>0$, we have
 \begin{align}
@@
     \end{align}
-    for any $\omega\in D$, there exists $S>0$, such that $\|X_t(\omega)\|=0,~t\geq T$.
-Thus $\omega \notin \cup_{t\geq S}\mathcal{A}_t(\epsilon)$ and $\omega\notin  \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon):=\cap_{S\geq 0}\cup_{t\geq S}\mathcal{A}_t(\epsilon)$ imply that $\limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c$.
-
-    For any $\omega \in \{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}$, there exists $\delta>0$ such that $H_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$ and there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq H_t(\omega)\leq 2\delta,$.
-Taking $S_2>0$ such that for any $t>S_2$, $\|\mu\|e^{-\epsilon t}<\frac{\delta}{2}$ and $\|\mu\|e^{-\epsilon t}>2\delta$, then $\omega\in \mathcal{A}_t(\epsilon),~t>S:=\max\{S_1,S_2\}$ implies $\omega \in \liminf_{t\rightarrow \infty}\mathcal{A}_t(\epsilon):=\cup_{S>0}\cap_{t\geq S}\mathcal{A}_t(\epsilon)$.
-
-    According to \cite{LSR}, $D^c=\{H_{\infty}>0\}~ \mathbb{P}_{\mu}$-a.s, combining with the fact $\lim_{t\rightarrow \infty}H_t=H_{\infty}~\mathbb{P}_{\mu}$-a.s, we get the result.
+
+    On one hand, let $\omega\in D$. Then there exists $T(\omega)>0$, such that $\|X_t(\omega)\|=0,$ for each $t\geq T(\omega)$. 
+    Thus $\omega\notin  \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=\cap_{s\geq 0}\cup_{t\geq s}\mathcal{A}_t(\epsilon)$.
+    This implies that $\limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c$.
+
+    On the other hand, let $\omega \in \{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}$. 
+    Then, there exists $\delta>0$ such that $H_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$ and there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq H_t(\omega)\leq 2\delta$.
+    Taking $S_2>0$ such that for any $t>S_2$, $\|\mu\|e^{-\epsilon t}<\frac{\delta}{2}$ and $\|\mu\|e^{\epsilon t}>2\delta$.
+    Then $\omega\in \mathcal{A}_t(\epsilon),$ for each $t>S:=\max\{S_1,S_2\}$. 
+    This implies that $\omega \in \liminf_{t\rightarrow \infty}\mathcal{A}_t(\epsilon):=\cup_{s>0}\cap_{t\geq s}\mathcal{A}_t(\epsilon)$. 
+    According to \cite{LSR}, $D^c=\{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}, \mathbb{P}_{\mu}$-a.s.. Using this we get the desired result.
 \end{proof}
@@
 
- Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa_fb(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+Let $f\in \mathcal{P}$. 
+Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
+Then for any  \deleted{$k\in\mathbb{N}$} \added{$k\geq 0$} and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
  \begin{align}
@@
  where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
- $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[e^{\alpha}m_k[\theta f]\right].$$
+ $$\mathbb{E}(e^{i\theta\zeta_k})=\exp(e^{\alpha}m_k[\theta f]),\quad \theta \in \mathbb R.$$
  \end{lem}
@@
  \begin{proof}
-For each $\theta \in \mathbb{R}$, let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any $k\in\mathbb{N}$ and $t>k+1$, we have
+For each $\theta \in \mathbb{R}$, let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any \deleted{$k\in\mathbb{N}$} \added{$k\geq 0$} and $t>k+1$, we have
+{\bf Zhenyao: Could you change $k\in \mathbb N$ to $k>0$ universilly?}
          \begin{align}
         &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})\big|\mathscr{F}_{t-k-1}\big]\\
+        &\added{ = ...}\\
         &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
@@
     \end{align}
+    {\bf Zhenyao: Give more detail about the above assertion. For example, We used the fact that $\exp(e^{\alpha}m_k[\theta f])$ is bounded.}
+
       According to \eqref{condition mean},
@@
     \end{align}
-Step 1.  We will show that for each $\mu \in\mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k+1$,
+{\bf Zhenyao: I think the last inequality for the above assertion needs more details. It seems that it use the result that $|e^x-e^y|\leq (|e^x|\wedge |e^y|)|x-y|$ for $x,y\in \mathbb C$.  }
+
+Step 1.  We will show that for each $\mu \in\mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$, such that for any $\theta\in \mathbb{R}$, \added{$k\geq 0$} and $t>k+1$,
     \begin{align}
@@
     \end{align}
-Let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6). For any $\theta\in\mathbb{R}$, $k \in \mathbb N$ and $t>k+1$, we have
-\begin{align}
-   & \big|U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq R\big(|\tilde{\theta}_{t,k}T_k^{\alpha}f|\big)\leq R \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
+    \added{In fact,} let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6). For any $\theta\in\mathbb{R}$, $k \in \mathbb N$ and $t>k+1$, we have
+\begin{align}
+   & \big|U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}
+   \leq R\big(|\tilde{\theta}_{t,k}T_k^{\alpha}f|\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}
+   \\&\leq R \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
    \\& \leq S \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big) 
@@
 \end{align}
+{\bf Zhenyao: I can't see the last step. It seems that you used the definition of $\epsilon_0$. Could you please explain more? Espicially, how $\kappa_f$ vanished, and how this is an equality?}
+
 Thus,
@@
 \end{align}
+{\bf Zhenyao: I can't see the last step either. It seems that you used the definition of $\epsilon_0$. Could you please explain more?}
+
 Step 2, for any $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ and $\theta\in \mathbb{R}$, we will show that there exists $C>0$ such that
@@
     Notice that $\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]=\theta^{1+\beta}e^{-\alpha k}(\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|} \rangle-\langle Z_{f_k},\varphi\rangle)$.
+
+    {\bf Zhenyao: The above assertion is not right.
+$\theta^\beta$ has no meaning if $\theta < 0$.
+And we don't use notation $Z_f$ anymore.
+It seems to me that $m_t[\theta f] = |\theta|^{1+\beta}m_t[f\operatorname{sgn}\theta]$.}
+
     Therefore,
@@
  \end{align}
-\deleted{
+\added{
 Thus $h_k$ satisfies \eqref{eq:gcontrol1} with $C_{h_k}=e^{(\alpha-\kappa(f))(1+\beta)k}$, $\kappa=1$ and $R_0^{h_k}(x)=R_7(x)$, fix some $\gamma_0\in(0,\beta)$, according to Lemma \ref{lemma24}, there exist $C_8>0$,
@@
 {\bf Jianjie: I think we should change the condition of Lemma \ref{lem: control moment} }
-We want to emphasize that, on the case $\alpha\gamma_0=(1+\gamma_0)b$, the second equation holds when $t$ is large enough. Thus
+We want to emphasize that, on the case $\alpha\gamma_0=(1+\gamma_0)b$, the second equation holds when $t$ is large enough. 
+Thus
 \begin{align}

### 2019-01-31 supCLT.tex
supCLT.tex: 1122

@@
 	The existence of superprocesses are well known, see \cite{EB} for instance.
-    \deleted {Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.}
     According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
@@
     In particular, the order of any constant function is zero.
-{
     Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ with
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $\deleted{R} \in \mathcal{P}$ such that,
-
-    {\bf Jianjie: we repeatedly use $R$ as both a function and a operator.}
+    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exist $C>0$  and $n\in \mathbb{N}$ such that,
+
 \begin{equation}
@@
     |T_tf(x)|
-    \leq e^{-\kappa_f bt} R(x),
+    \leq e^{-\kappa_f bt} C(1+|x|)^n,
     \quad t\geq 0, x\in \mathbb R^d.
 \end{equation}
-	For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa_f bt} |T_tf(x)|$.
-	Then $Q$ is an operator form $\mathcal P$ to $\mathcal P \cap \mathscr B
-	(\mathbb R^d,\mathbb R_+)$.
+	\added{
+	For each $\kappa\geq0$, define $\mathcal{P}_{\kappa}$ by 
+	\begin{align}
+	     \mathcal{P}_{\kappa}
+    :=\big \{f\in \mathcal{P}:\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ \sup_{t\geq0}e^{\kappa b t}|T_tf(x)|\leq C(1+|x|)^n\big\}.
+	\end{align}
+	and an operator $Q_{\kappa}:\mathcal{P}_{\kappa}\mapsto\mathcal{P}\cap\mathscr{B}(\mathbb{R}^d,\mathbb{R}_+)$ by $Q_{\kappa}f=\sup_{t\geq0}e^{\kappa b t}|T_tf|$.
+	Then
+	\begin{itemize}
+	    \item For each $\kappa_1\geq \kappa_2$, $\mathcal{P}_{\kappa_1}\subset\mathcal{P}_{\kappa_2}$, and $\mathcal{P}=\cup_{\kappa\geq 0}\mathcal{P}_{\kappa}$.
+	    \item for each $f\in \mathcal{P}$, then $f\in \mathcal{P}_{\kappa_f}$, and $Q_{\kappa}f\leq Qf:=Q_{\kappa_f}f$, $\kappa\leq \kappa_f$.
+
+	\end{itemize}
 	}
-
 \subsection{}
@@
     Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
-    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(\deleted {x,}f(x))$ and $\Psi'_0 f(x) := \psi'_0(\deleted {x,}f(x))$.
+    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
     For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
@@
 
-For each $p\in \mathbb{Z}_+^d$, we define
+For each $p\in \mathbb{N}_+^d$, we define
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
- We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0<\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+  For any $0<\gamma<\beta$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  \begin{thm}\label{Theorem11}
      If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then as $t\rightarrow \infty$,
-     $$e^{-(\alpha-\kappa(f)b)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa(f)}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
+     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
      for any $0<\gamma<\beta$.
@@
 $$\phi(x)=\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).$$
-See Lemma \ref{lemma210} for more details about $\tilde{m}[f]$.
 Denote by $D$ the extinction event of super process.
 \begin{thm}\label{Theorem12}
-Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(f)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
 $$\frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
 where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by
-$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[f]).$$
+$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\tilde{m}[\theta f]).$$
 \end{thm}
@@
 $$m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx$$
-In Lemma \ref{lemma211}, we will prove that $|m[f]|<\infty$.
 \begin{thm}\label{Theorem13}
-    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa(f)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
     $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
     where $\eta_2$ is a $(1+\beta)$-stable random variable with characteristic function given by
-    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(\theta^{1+\beta}m[f]).$$
+    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(m[\theta f]).$$
 \end{thm}
@@
     Suppose that operators $(A_\lambda)_{\lambda\in \Lambda}$ are uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$.
-    Then there exists a $\gamma$-scalable operator $S$ such that
+    Then \added{for each $\kappa\geq0$,} there exists a $\gamma$-scalable operator $S$ such that
 \[
     |A_\lambda T_t^\alpha f|
-    \leq e^{\gamma t (\alpha  - \kappa_f b)} SQf,
-    \quad \lambda \in \Lambda, t\geq 0, f\in \mathcal D.
+    \leq e^{\gamma t (\alpha  - \added{\kappa} b)} S\added{Q_{\kappa}}f,
+    \quad \lambda \in \Lambda, t\geq 0, f\in \added{ \mathcal{D}\cap\mathcal{P}_{\kappa}}.
 \]
@@
     |A_\lambda T_t^\alpha f| \leq R|T_t^\alpha f|
-    \leq R (e^{\alpha t  - \kappa_f bt}Qf)
-    \leq S (e^{\alpha t  - \kappa_f bt}Qf)
-    \leq e^{\gamma t (\alpha  - \kappa_f b)} SQf.
+    \leq R (e^{\alpha t  - \kappa bt}Q_{\kappa}f)
+    \leq S (e^{\alpha t  - \kappa bt}Q_{\kappa}f)
+    \leq e^{\gamma t (\alpha  - \kappa b)} SQ_{\kappa}f.
     \qedhere
@@
 \subsection{}
-    For each $f \in \mathcal{P}$, $x\in E$ and $t\geq 0$, define
+    For each $f \in \mathcal{P}$, $x\in \mathbb{R}^d$ and $t\geq 0$, define
 \begin{align}
@@
 \begin{proof}
-    Proof of (1): From \eqref{eq: upper bound for vf} in the appendix, we have for each $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in E$,
+    Proof of (1): From \eqref{eq: upper bound for vf} in the appendix, we have for each $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
 \[
@@
 \end{proof}
-\begin{lem}
-    There is an $(1+\beta)$-scalable operator $S$ such that for each $g\in \mathcal P$, $\lambda >0$, $\mu\in \mathcal M_c(\mathbb R^d)$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
+\begin{lem}\label{lem: temp}
+    There is an $(1+\beta)$-scalable operator $S$ such that for each \added{$g\in \mathcal P_{\kappa}$ with $\kappa\geq 0$}, $\lambda >0$, $\mu\in \mathcal M_c(\mathbb R^d)$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
 \[
     \mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda)
-    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle SQg,\mu\rangle.
+    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r} \langle SQ_{\kappa}g,\mu\rangle.
 \]
@@
     \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
-    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
-	\\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
-    = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \mathbb P_\mu [ \langle S_0Qg,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
-    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \langle T_r^\alpha S_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
-    \leq e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle QS_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}.
+    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta e^{(t-s)(\alpha- \kappa b)}Q_{\kappa}g|,X_r\rangle d\theta \Big]
+	\\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta e^{(t-s)(\alpha- \kappa b)}Q_{\kappa}g|,X_r\rangle d\theta \Big]
+    = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \mathbb P_\mu [ \langle S_0Q_{\kappa}g,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
+    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \langle T_r^\alpha S_0Q_{\kappa}g,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
+    \leq e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r} \langle QS_0Q_{\kappa}g,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}.
 \end{align}
@@
 \begin{lem}\label{lem: control of mgtrs}
-    For each $g\in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
+    \added{Let $g$ be the function in lemma \ref{lem: temp}.}
+    For each $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
 \[
     \mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
-    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb)}.
+    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b)}.
 \]
@@
     \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|I_r^s[\langle g, X_t\rangle]|> \lambda) d\lambda
-    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle SQg,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
-    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle SQg,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
-\end{align}
-    Taking $c = e^{(t-s)(\alpha- \kappa_gb)}$ we have
+    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r} \langle SQ_{\kappa}g,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
+    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r} \langle SQ_{\kappa}g,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
+\end{align}
+    Taking $c = e^{(t-s)(\alpha- \kappa b)}$ we have
 \begin{align}
     &\mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
-    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa_gb)} e^{\alpha r}\Big(1+ \langle SQg,\mu\rangle \frac{1+\gamma}{\beta - \gamma}\Big).
+    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ \langle SQ_{\kappa}g,\mu\rangle \frac{1+\gamma}{\beta - \gamma}\Big).
 \end{align}
@@
 \[
-    (1+\gamma)(t-s)(\alpha- \kappa_gb) + \alpha r
-    \leq t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb).
+    (1+\gamma)(t-s)(\alpha- \kappa b) + \alpha r
+    \leq t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b).
     \qedhere
@@
 \label{lem: control moment}
-    For each $0 < \gamma < \beta$ and $\mu\in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$ there exists a constant $C>0$ such that for each $t\geq 0$:
+    \added{Let $g$ be the function in Lemma \ref{lem: control of mgtrs}.}
+    For each $0 < \gamma < \beta$ and $\mu\in \mathcal M_c(\mathbb R^d)$ there exists a constant $C>0$ such that for each $t\geq 0$:
+\begin{itemize}
+\item[(1)]
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$.
+\item[(2)]
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$.
+\item[(3)]
+    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
+\end{itemize}
+\end{lem}
+\begin{proof}
+    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$.
+    Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
+    Using the triangle inequality,
+\begin{align}
+    \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| I_{t-k-1}^{t-k}[\langle g,X_t\rangle] \big\|_{\mathbb P_\mu;1+\gamma}+\big\| I_{0}^{t-\lfloor t \rfloor}[\langle g,X_t\rangle]  \big\|_{\mathbb P_\mu;1+\gamma}
+    \\ &\leq C e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} k} .
+\end{align}
+    By calculating the sum on the right, we get the desired result.
+\end{proof}
+\added{
+\begin{cor}\label{cor: control of moment}
+   For each $g\in\mathcal{P}$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
+    \[
+    \mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
+    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_g b)}.
+    \]
+    Moreover,
     \begin{itemize}
@@
 \end{itemize}
-\end{lem}
-\begin{proof}
-    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$.
-    Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
-    Using the triangle inequality,
-\begin{align}
-    \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| I_{t-k-1}^{t-k}[\langle g,X_t\rangle] \big\|_{\mathbb P_\mu;1+\gamma}+\big\| I_{0}^{t-\lfloor t \rfloor}[\langle g,X_t\rangle]  \big\|_{\mathbb P_\mu;1+\gamma}
-    \\ &\leq C e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa_g (1+\gamma)b}{1+\gamma} k} .
-\end{align}
-    By calculating the sum on the right, we get the desired result.
-\end{proof}
-
+\end{cor}
+\begin{proof}
+    As $g\in\mathcal{P}$, $g\in\mathcal{P}_{\kappa_g}$. We get the detail result by taking $\kappa=\kappa_g$ in Lemma \ref{lem: control of mgtrs} and Lemma \ref{lem: control moment}.
+\end{proof}
+}
 \subsection{Martingales}
@@
 \end{align}
-\added{{\bf Zhenyao: we should show that it is well defined.}}
     The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathscr{F}_t\}_{t\geq 0}$.
@@
      Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-    According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C_0>0$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
+   \added{ According to Corollary \ref{cor: control of moment}}, there exists a constant $C_0>0$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
     \begin{align}
@@
 
-\deleted{
+Write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+\begin{lem}\label{lem: control of XT}
+	For each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for each function $f:[0,\infty)\to [1,\infty)$ and each $t\geq 0$ we have
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)\leq C \Big(\frac{f(t)}{e^{\alpha t}}\Big)^{\beta}.
+\end{align}
+\end{lem}
+
+\begin{proof}
     Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
@@
 \end{align}
-}
-
-\added{Write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.}
-
-\begin{lem}\label{lem: control of XT}
-	For each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for each function $f:[0,\infty)\to [1,\infty)$ and each $t\geq 0$ we have
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)\leq C \Big(\frac{f(t)}{e^{\alpha t}}\Big)^{\beta}.
-\end{align}
-\end{lem}
-
-\begin{proof}
-\added{
-    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
-\begin{align}\label{CSBP}
-    \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
-    =e^{-\|\mu\|v_t(\lambda)},
-    \quad \lambda \geq 0, t\geq 0,
-\end{align}
-    where
-\[
-    v_t(\lambda)=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
-\]
-    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
-    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
-    By \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
-    $t\geq 0$,
-
-\begin{align}
-    \label{laplaceexpress}
-    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]
-    &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
-    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\alpha^*\|X_t\|})] }{\mathbb P_\mu(D^c)}
-    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}
-    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
-\end{align}
-}
 
@@
 \end{proof}
-
+\added{
+\begin{lem}\label{lem: control of A&D}
+For each $\mu\in \mathcal{M}_c(\mathbb{R}^d)$ and $0<\epsilon<\alpha$, there exist $C,\delta\geq 0$ such that for each $t>0$, we have $\mathbb{P}_{\mu}(\mathcal{A}_t(\epsilon)\Delta D^c)\leq Ce^{-\delta t}$.
+\end{lem}
+\begin{proof}
+    According to Lemma \ref{lem: control of AT}, we know
+    \begin{align}
+            \mathbb{P}_{\mu}(\mathcal{A}_t(\epsilon)^c\cap D^c)=\mathbb{P}_{\mu}(D^c)\mathbb{\tilde{P}}_{\mu}(\mathcal{A}_t(\epsilon)^c)\leq C\mathbb{P}_{\mu}(D^c)e^{-\beta \epsilon t}.
+    \end{align}
+    On the other hand,
+    \begin{align}
+        \mathbb{P}_{\mu}(\mathcal{A}_t(\epsilon)\cap D)=\mathbb{P}_{\mu}\big[\mathcal{A}_t(\epsilon)\mathbb{P}_{\mu}(D|\mathscr{F}_t)\big]=\mathbb{P}_{\mu}\big[\mathbf{1}_{\mathcal{A}_t(\epsilon)}e^{-\alpha^* \|X_t\|}\big]\leq \exp\big(e^{-\alpha^*\|\mu\|e^{(\alpha-\epsilon)t}}\big).
+    \end{align}
+\end{proof}
+}
 \subsection{Parameters}
@@
 \begin{align}
-\label{lemma210}
+\label{para: critical case}
     \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\Psi_0(-i\phi),\varphi\rangle.
@@
     The following Lemma says that function $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\begin{lem}
+\begin{lem}\label{lem: charactreisticfunction}
     Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
@@
 
-In this section, we will prove the main results of this paper.
-Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.
-
+In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+\begin{comment}
 \begin{lem}\label{lemma32}
-    \deleted{Recall} \added{Write} $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\},$ for each $\epsilon,t>0$. 
+    Write $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\},$ for each $\epsilon,t>0$.
     Then for any $\epsilon>0$, we have
@@
 \end{proof}
-}
-\begin{lem}\label{lemma33}
+\end{comment}
+\begin{lem}\label{lem: mainlemma}
 
@@
 Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
-Then for any  \deleted{$k\in\mathbb{N}$} \added{$k\geq 0$} and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
- \begin{align}
-      \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
+Then for any $k\geq 0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+ \begin{align}
+      \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
  \end{align}
@@
  \begin{proof}
-For each $\theta \in \mathbb{R}$, let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any \deleted{$k\in\mathbb{N}$} \added{$k\geq 0$} and $t>k+1$, we have
-{\bf Zhenyao: Could you change $k\in \mathbb N$ to $k>0$ universilly?}
-         \begin{align}
-        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})\big|\mathscr{F}_{t-k-1}\big]\\
-        &\added{ = ...}\\
+Fix $\theta \in \mathbb{R}$, let $\tilde{\theta}_{t,k}=\frac{\theta}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}$. For any $k\geq 0$ and $t>k+1$, we have
+\begin{align}
+    &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k((e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}})\big|\mathscr{F}_{t-k-1}\big]\\
+    &=\mathbb{P}_{\mu}\big[\exp(i\tilde{\theta}\langle T_k^{\alpha}f,X_{t-k}\rangle-i\tilde{\theta}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle)\big|\mathscr{F}_{t-k-1}\big] \\
         &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
@@
        \end{align}
-         Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
-       To get the conclusion of Lemma \ref{lemma33}, it suffices to show that
+         Fix $\gamma_0\in (0,\beta)$, let $p=\min\{\frac{b}{2},\frac{\alpha\gamma_0}{1+\gamma_0}\}$ and $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
+       To get the conclusion of Lemma \ref{lem: mainlemma}, it suffices to show that
        \begin{align}
@@
        \end{align}
-     Equivalently, by Lemma \ref{lemma32}, we just need to prove
-     \begin{align}
-        \Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\xrightarrow{t\rightarrow\infty} 0.
-    \end{align}
-    {\bf Zhenyao: Give more detail about the above assertion. For example, We used the fact that $\exp(e^{\alpha}m_k[\theta f])$ is bounded.}
-
-      According to \eqref{condition mean},
-    \begin{align}
-        &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
-        &=\Big|\mathbb{P}_{\mu}\Big[\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big]\Big|\\
+
+      According to Lemma \ref{lem: charactreisticfunction}, \eqref{condition mean} and the element inequality, for any $x,y\in \mathbb{C}_{+}$, $|e^{-x}-e^{-y}|\leq |x-y|$.
+    \begin{align}
+        %&\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha %k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
+        &\mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big|\Big]\\
         &\leq \mathbb{P}_{\mu}\big[\big|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
         \label{ineqinlem31}
-        &+\mathbb{P}_{\mu}\big[\big|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big].
-    \end{align}
-{\bf Zhenyao: I think the last inequality for the above assertion needs more details. It seems that it use the result that $|e^x-e^y|\leq (|e^x|\wedge |e^y|)|x-y|$ for $x,y\in \mathbb C$.  }
-
-Step 1.  We will show that for each $\mu \in\mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$, such that for any $\theta\in \mathbb{R}$, \added{$k\geq 0$} and $t>k+1$,
+        &+\mathbb{P}_{\mu}\big[\big|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]:=J_1(\theta,k,t)+J_2(\theta,k,t).
+    \end{align}
+Therefore, according to the fact $|e^{-z}|\leq1,~z\in \mathbb{C}_+$
+\begin{align}
+    &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{D^c}\Big]\Big|
+    \\& \leq \mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{D^c}\Big|\mathscr{F}_{t-k-1}\Big)\Big|\Big]
+    \label{ineq: used in next corollary}
+    \\ & \leq\mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big|\Big]
+    \\&+ 2\mathbb{P}_{\mu}(\mathcal{A}_{t-k-1}(\epsilon_0)\Delta D^c)\\
+    &\leq J_1(\theta,k,t)+J_2(\theta,k,t)+J_3(k,t),
+\end{align}
+where $J_3(k,t)=2\mathbb{P}_{\mu}(\mathcal{A}_{t-k-1}(\epsilon_0)\Delta D^c)$.
+
+Step 1.  We will show that for each $\mu \in\mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$, such that for any $\theta\in \mathbb{R}$, $k\geq 0$ and $t>k+1$,
     \begin{align}
     \label{lemma31q}
-        \mathbb{P}_{\mu}\big[\big|\langle  U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\leq C|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
-    \end{align}
-    \added{In fact,} let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6). For any $\theta\in\mathbb{R}$, $k \in \mathbb N$ and $t>k+1$, we have
+      J_1(\theta,k,t)\leq C|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
+    \end{align}
+In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6). For any $\theta\in\mathbb{R}$, $k \geq 0$ and $t>k+1$, we have
 \begin{align}
@@
    \leq R\big(|\tilde{\theta}_{t,k}T_k^{\alpha}f|\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}
-   \\&\leq R \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
-   \\& \leq S \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big) 
-   \leq \Big(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+2\beta}SQf
-   \\&=\frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}SQf.
-\end{align}
-{\bf Zhenyao: I can't see the last step. It seems that you used the definition of $\epsilon_0$. Could you please explain more? Espicially, how $\kappa_f$ vanished, and how this is an equality?}
-
-Thus,
-\begin{align}
-     &\mathbb{P}_{\mu}\big[\big|\langle  U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
-     &\leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}\mathbb{P}_{\mu}[\langle SQf,X_{t-k-1}\rangle]\\
-     & \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}e^{-\alpha(t-k-1)}\langle QSQf, \mu \rangle\\
+   \\&\leq R \Big(\frac{|\theta|e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon_0)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
+    \leq S \Big(\frac{|\theta|e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon_0)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
+   \\&\leq \Big(\frac{|\theta|e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon_0)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+2\beta}SQf
+   \\&=\frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{\frac{1+2\beta}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta)k)}e^{-\frac{(\alpha-\epsilon_0)(1+2\beta)(t-k-1)}{1+\beta}}SQf.
+   \\&\leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{(\alpha-\epsilon_0)(1+2\beta)(t-k-1)}{1+\beta}}SQf
+\end{align}
+Note that $\epsilon_0\leq \frac{\alpha\beta}{2(1+2\beta)}$, thus
+\begin{align}
+     J_1(\theta,k,t)&
+     \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{(\alpha-\epsilon_0)(1+2\beta)(t-k-1)}{1+\beta}}\mathbb{P}_{\mu}[\langle SQf,X_{t-k-1}\rangle]\\
+     & \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}e^{\alpha(t-k-1)}\langle QSQf, \mu \rangle\\
      & \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle QSQf,\mu\rangle|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
 \end{align}
-{\bf Zhenyao: I can't see the last step either. It seems that you used the definition of $\epsilon_0$. Could you please explain more?}
-
-Step 2, for any $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ and $\theta\in \mathbb{R}$, we will show that there exists $C>0$ such that
+Step 2, for any $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, we will show that there exists $C>0$ such that for any $\theta\in \mathbb{R}$, $k\geq 0$ and $t\geq k+1$, 
 \begin{align}
 \label{eq:31step3}
-    &\mathbb{P}_{\mu}\big[\big|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
-    &\leq C|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)},\quad k\in \mathbb{N}, t\geq k+1.
-\end{align}
-    Notice that $\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]=\theta^{1+\beta}e^{-\alpha k}(\frac{\langle Z_{f_k},X_{t-k-1}\rangle}{\|X_{t-k-1}\|} \rangle-\langle Z_{f_k},\varphi\rangle)$.
-
-    {\bf Zhenyao: The above assertion is not right.
-$\theta^\beta$ has no meaning if $\theta < 0$.
-And we don't use notation $Z_f$ anymore.
-It seems to me that $m_t[\theta f] = |\theta|^{1+\beta}m_t[f\operatorname{sgn}\theta]$.}
-
-    Therefore,
-
-\begin{align}
-        &\mathbb{P}_{\mu}\left[\left|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
-    &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{P}_{\mu}\left[\left|\frac{\langle Z_1(T^{\alpha}_k f),X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1(T^{\alpha}_k f)Z_{f_k},\varphi\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\nonumber\\
+    J_2(\theta,k,t)\leq C|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)}.
+\end{align}
+    Notice that
+    \begin{align}
+          &\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]
+          \\&=|\theta|^{1+\beta}e^{-\alpha k}\Big(\frac{\langle Z_1(T_k^{\alpha}(f \operatorname{sgn} \theta)),X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1(T_k^{\alpha}(f \operatorname{sgn} \theta)),\varphi\rangle\Big).
+    \end{align}
+For convenience, we first assume that $\theta>0$. Therefore, for any $k\geq 0$ and $t\geq k+1$,
+\begin{align}
+J_2(\theta,k,t)
+    &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{P}_{\mu}\Big[\Big|\frac{\langle Z_1(T^{\alpha}_k f),X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1(T^{\alpha}_k f)Z_{f_k},\varphi\rangle\Big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\nonumber\\
     &\leq |\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon_0)(t-k-1)}\mathbb{P}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
 \end{align}
-where $h_k(x):= Z_1(T^{\alpha}_k f)(x)-\langle  Z_1(T^{\alpha}_k f),\varphi\rangle,~x\in\mathbb{R}^d$.
-According to \cite[Lemma 2.8]{MM}, there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
+where $h_k:= Z_1(T^{\alpha}_k f)-\langle  Z_1(T^{\alpha}_k f),\varphi\rangle$.
+According to \cite[Lemma 2.8]{MM}, there exists $C>0$ and $n\in\mathbb{N}$, such that for any $k\geq 0$, $x\in \mathbb{R}^d$ and $s\geq 0$,
  \begin{align}
  \label{eq:31step2}
-     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa_fb)(1+\beta)k}R_7(x).
+     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa_fb)(1+\beta)k}C(1+|x|)^n.
  \end{align}
 \added{
-Thus $h_k$ satisfies \eqref{eq:gcontrol1} with $C_{h_k}=e^{(\alpha-\kappa(f))(1+\beta)k}$, $\kappa=1$ and $R_0^{h_k}(x)=R_7(x)$, fix some $\gamma_0\in(0,\beta)$, according to Lemma \ref{lemma24}, there exist $C_8>0$,
+Thus $\frac{h_k}{C_{h_k}} \in \mathcal{P}_{1}$ with $C_{h_k}=e^{(\alpha-\kappa_f)(1+\beta)k}$ (Actually, we rewrite $h_k(x)=\text{Re}~h_k(x)+i \text{Im} ~h_k(x)$ and $\frac{\text{Re}~h_k}{C_{h_k}},\frac{\text{Im}~h_k}{C_{h_k}}\in \mathcal{P}_1$).
+Recall that $\gamma_0\in(0,\beta)$ and $p=\min\{\frac{b}{2},\frac{\alpha\gamma_0}{1+\gamma_0}\}$, according to Lemma \ref{lem: control moment}, there exist $C>0$,
 \begin{align}
     &\mathbb{P}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right]\leq \|\langle h_k, X_{t-k-1}\rangle\|_{\mathbb{P}_{\mu,1+\gamma_0}}\\
-    &\leq C_8 e^{(\alpha-\kappa(f)b)(1+\beta)k}
+    &\leq C e^{(\alpha-\kappa_fb)(1+\beta)k}
     \begin{cases}
     e^{(\alpha-b)(t-k-1)}\quad &\alpha\gamma_0>(1+\gamma_0)b\\
-    e^{(\alpha-\frac{\gamma_0}{2(1+\gamma_0)}\alpha)(t-k-1)}\quad &\alpha\gamma_0=(1+\gamma_0)b\\
-    e^{(\alpha-\frac{\gamma_0}{(1+\gamma_0)}\alpha)(t-k-1)}\quad &\alpha\gamma_0<(1+\gamma_0)b\\
+    (t-k-1)e^{(\alpha-b)(t-k-1)}\quad &\alpha\gamma_0=(1+\gamma_0)b\\
+    e^{(\alpha-\frac{\alpha\gamma_0}{1+\gamma_0})(t-k-1)}\quad &\alpha\gamma_0<(1+\gamma_0)b\\
     \end{cases}
-    \\& \leq C_8 e^{(\alpha-\kappa(f)b)(1+\beta)k}e^{(\alpha-p)(t-k-1)}, \quad k\in \mathbb{N}, t\geq k,
+    \\& \leq C^{'}e^{(\alpha-\kappa_f b)(1+\beta)k}e^{(\alpha-p)(t-k-1)}, \quad k\geq 0, t\geq k+1.
 \end{align}
 }
-{\bf Jianjie: I think we should change the condition of Lemma \ref{lem: control moment} }
-We want to emphasize that, on the case $\alpha\gamma_0=(1+\gamma_0)b$, the second equation holds when $t$ is large enough. 
-Thus
-\begin{align}
-    &\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
-    \\ & \leq C_8 |\theta|^{1+\beta}e^{(\alpha\beta-\kappa(f)b(1+\beta))k}e^{-(p-\epsilon_0)(t-k-1)} \leq C_8 |\theta|^{1+\beta}e^{-\frac{p}{2}(t-k-1)}.
-\end{align}
-
-At last, combine \eqref{lemma31q} and \eqref{eq:31step3} and let $t\rightarrow\infty$, we get the result.
+Therefore, for each $\theta>0$, $ k\geq 0$ and $t\geq k+1$, we have
+\begin{align}
+J_2(\theta,k,t)\leq C^{'} |\theta|^{1+\beta}e^{(\alpha\beta-\kappa_fb(1+\beta))k}e^{-(p-\epsilon_0)(t-k-1)} \leq C^{'} |\theta|^{1+\beta}e^{-\frac{p}{2}(t-k-1)}.
+\end{align}
+When $\theta\leq 0$, we obtain the inequality the same way as above but replacing $f$ by $-f$.
+
+Step 3, As $\epsilon_0\leq \alpha$, according to Lemma \ref{lem: control of A&D}, for any $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that 
+\begin{align}\label{ineq: control of J3}
+    J_3(k,t)\leq 2Ce^{-\delta (t-k-1)}\quad k\geq0, t\geq k+1.
+\end{align}
+At last, combine \eqref{lemma31q}, \eqref{eq:31step3} and \eqref{ineq: control of J3}, let $t\rightarrow\infty$, we get the result.
+\end{proof}
+
+\begin{cor}\label{cor: used in next corollary}
+Under condition in Lemma \ref{lem: mainlemma}, for each $\theta\in \mathbb{R}$ satisfying $|\theta|<\Theta$, there exist $C,\delta>0$ such for any $k\geq0$ and $t\geq k+1$,
+\begin{align}
+    \mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\big[\big(\exp{(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{D^c}\big|\mathscr{F}_{t-k-1}\big]\Big|\Big]\leq Ce^{-\delta(t-k-1)}.
+\end{align}
+\end{cor}
+\begin{proof}
+    Conclusion implied by  \eqref{ineq: used in next corollary}-\eqref{ineq: control of J3} and the condition $|\theta|\leq \Theta$.
 \end{proof}
 \begin{cor}\label{corollary31}
-Let $f\in \mathcal{P}$ and $\Theta>0$, assume that $\alpha\beta\leq\kappa(f)b(1+\beta)$.
+Let $f\in \mathcal{P}$ and $\Theta>0$, assume that $\alpha\beta\leq\kappa_fb(1+\beta)$.
 There exists $C,\delta>0$ such that for any $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
@@
 \begin{proof}
-    Denote $\gamma_{t,k}=\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}} $, we define
-    $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp\left(e^{\alpha}m_l[\theta_lf]\right)\mathbb{\tilde{P}}_{\mu}\left(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\right)$$
-    for $k\in\{-1,...,n\}$, if $k=-1$, the product is one. Then Conditioning with $\mathscr{F}_{t-k-1}$ we get
-    \begin{align*}
-        \varphi^{k-1}_t(\theta_0,...,\theta_n)-&\varphi^{k}_t(\theta_0,...,\theta_n)=\prod_{l=0}^{k-1}\exp\left(e^{\alpha}m_l[\theta_l f]\right)\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left(\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta_kf]}\right)\prod_{l=k+1}^n\exp(i\theta_l \gamma_{t,l})\right]
-    \end{align*}
-    Hence,
-    \begin{align*}
-        \left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| \leq \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta_k \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta_kf]}\right|.
-    \end{align*}
+    Denote $\gamma_{t,k}=\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}} $. For $k\in\{-1,...,n\}$, we define
+    $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),\quad |\theta_l|\leq \Theta,$$
+     where by convention the product is $1$ for $l=-1$. Then Conditioning with $\mathscr{F}_{t-k-1}$ we get
+    \begin{align*}
+        &\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)
+        %\\&=\prod_{l=0}^{k-1}\exp(e^{\alpha}m_l[\theta_l %f])\mathbb{\tilde{P}}_{\mu}\Big[\prod_{l=k}^{n}\exp(i\theta_{l}\gamma_{t,l})-\exp(e^{\alpha}m_k[\theta_k %f])\prod_{l=k+1}^n\exp(i\theta_{l}\gamma_{t,l})\Big]
+        \\&=\frac{1}{\mathbb{P}_{\mu}(D^c)}\prod_{l=0}^{k-1}\exp(e^{\alpha}m_l[\theta_l f])\mathbb{P}_{\mu}\Big[\Big(\prod_{l=k}^{n}\exp(i\theta_{l}\gamma_{t,l})-\exp(e^{\alpha}m_k[\theta_k f])\prod_{l=k+1}^n\exp(i\theta_{l}\gamma_{t,l})\Big)\mathbf{1}_{D^c}\Big]
+        \\&=\frac{1}{\mathbb{P}_{\mu}(D^c)}\prod_{l=0}^{k-1}\exp(e^{\alpha}m_l[\theta_l f])\mathbb{P}_{\mu}\Big[\prod_{l=k+1}^{n}\exp(i\theta_{l}\gamma_{t,l})\mathbb{P}_{\mu}\big[\big(\exp(i\theta_k\gamma_{t,k})-\exp(e^{\alpha}m_k[\theta_k f])\big)\mathbf{1}_{D^c}\big|\mathscr{F}_{t-k-1}\big]\Big]
+    \end{align*}
+    According to  the element inequality $|e^{iz}|\leq 1$, Lemma \ref{lem: charactreisticfunction} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$, $t>n$ and $|\theta_l|\leq \Theta,~l=1,...,n$, we have
+    \begin{align*}
+        &\left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| 
+        \\&\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\big[\big(\exp(i\theta_k\gamma_{t,k})-\exp(e^{\alpha}m_k[\theta_k f])\big)\mathbf{1}_{D^c}\big|\mathscr{F}_{t-k-1}\big]\Big|\Big]
+        \\& \leq C e^{-\delta(t-k-1)}.
+    \end{align*}
+    \begin{comment}
+
     Step 1, we will prove that there exists $C,\delta>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,\lfloor t\rfloor\}$,
@@
     \label{eq:32step1}
-        \left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta f]}\right|\leq C e^{-\delta(t-k-1)}.
+        \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta f]}\right|\leq C e^{-\delta(t-k-1)}.
     \end{align}
@@
 \end{align*}
-
-Step 2, notice that the left side of \eqref{32corollary} is equal to $\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|$, moreover,
-\begin{align}
-    &\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|
+\end{comment}
+Therefore, 
+\begin{align}
+    \text{LHS of \eqref{32corollary}}= &\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|
     \\&\leq\sum_{k=0}^n\left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right|
-    \\&\leq \sum_{k=0}^n C e^{-\delta_3(t-k-1)}.
-\end{align}
+    \\&\leq \sum_{k=0}^n C e^{-\delta(t-k-1)}.
+\end{align}
+
 Thus, we complete our proof.
@@
     \begin{align*}
-        (t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} (t\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[f]+\sum_{k=\lceil t-\ln t \rceil}^t (t\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[f]\\
-        &=I_t+J_t.
+        (t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{I_0^{t-\lfloor t \rfloor}[\langle f ,X_t\rangle]}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\\
+        &:=I_1(t)+I_2(t)+I_3(t).
     \end{align*}
     Denote
-    $$\tilde{I}_t=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{M_k^t[f]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
-    Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get
-    \begin{align*}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}-\exp\left(\theta^{1+\beta}\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[f]\right)\right|\leq C \frac{1}{t^{\delta}},
-    \end{align*}
-    for some $C,\delta>0$. Hence we obtain that $\tilde{I}_t\rightarrow\eta_1$ as $t\rightarrow \infty$, by using Lemma \ref{lemma210}.
-
-    Therefore, to prove this theorem ,we just to prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\rightarrow 0$ and $J_t\rightarrow^d 0$.
-
+    $$\tilde{I}_1(t):=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
+    Fix $\theta\in \mathbb{R}$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get
+    \begin{align*}
+        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}-\exp\left(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\right)\right|\leq C \frac{1}{t^{\delta}},
+    \end{align*}
+    for some $C,\delta>0$. According to \eqref{para: critical case}, we obtain that $\tilde{I}_1(t)\xrightarrow{d}\eta_1$ as $t\rightarrow \infty$.
+    Therefore, to end this proof, we just to prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\rightarrow 0$ and $I_i(t)\xrightarrow{d} 0,~i=2,3$.
+
+    Step 1, Fix $\mu\in \mathcal{M}_c(\mathbb{R}^d)$ and $\theta\in \mathbb R$, we show that
+    \begin{align}
+        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\rightarrow 0,\quad t\rightarrow \infty.
+    \end{align}
     Denote
     \begin{align*}
-        Y_{t,k}=\exp\left(i\theta\frac{M_k^t[f]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{M_k^t[f]}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
-    \end{align*}
-
-    Using the element inequality $|\prod x_i-\prod y_i|\leq\sum |x_i-y_i|$ for $x_i,y_i \in \mathbb{C}$ with $|x_i|,|y_i|\leq 1$, we get
-    \begin{align*}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}|Y_{t,k}|.
-    \end{align*}
-    Recall Lemma \ref{lemma27}, define
-    \begin{align*}
-        \mathcal{D}_{t,k}:=\left\{|W_t-W_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, W_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\},
-    \end{align*}
-    then follow Lemma \ref{lemma27} and Lemma \ref{lemma28}, we get
-    \begin{align*}
-        \mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)&\leq \mathbb{\tilde{P}}_{\mu}(|W_t-W_{t-k-1}|\geq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(W_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),\\
-        &\leq C e^{-\delta(t-k-1)}
-    \end{align*}
-    for some $C,\delta>0$. Hence
-    \begin{align}
-        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\leq 2 C e^{-\delta(t-k-1)}.\label{thm121}
+        Y_{t,k}:=\exp\left(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
+    \end{align*}
+
+    Using the element inequality: for $x_i,y_i \in \mathbb{C}$ with $|x_i|,|y_i|\leq 1$, $|\prod x_i-\prod y_i|\leq\sum |x_i-y_i|$ , we get
+    \begin{align}\label{ineq: control of I1t}
+        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}|Y_{t,k}|.
+    \end{align}
+    For $t>1$ and $k\in \{0,...,\lfloor t-\ln t \rfloor\}$, define
+    \begin{align*}
+        \mathcal{D}_{t,k}:=\left\{|H_t-H_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, H_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\}.
+    \end{align*}
+    Then according to Lemma \ref{lem: control of Wt} and Lemma \ref{lem: control of AT}, there exist $C,\delta>0$, such that
+    \begin{align*}
+        \mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}|\geq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),\\
+        &\leq C e^{-\delta(t-k-1)}, \quad t>1, k\in \{0,...,\lfloor t-\ln t \rfloor\}.
+    \end{align*}
+  Therefore, for each $t>1$ and $k\in \{0,...,\lfloor t-\ln t \rfloor\}$,
+    \begin{align}
+        \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\big]\leq 2 C e^{-\delta(t-k-1)}.\label{thm121}
     \end{align}
@@
     Using the element inequality $|e^{ix}-e^{iy}|\leq|x-y|$,
-    \begin{align*}
-        \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}|M_k^t[f]|\left|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}\\
-        &\leq|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}|M_k^t[f]|\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}.
-    \end{align*}
-    When $t$ is large enough, $t^{-\frac{1}{1+\beta}}\leq 1$. What's more, by Corollary \ref{cor27}
-    $$\mathbb{\tilde{P}}_{\mu}|M_k^t[f]|\leq \frac{\mathbb{P}_{\mu}(|M_k^t[f]|)}{\mathbb{P}(D^c)}\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k},$$
-for some constant $C \geq 0$ and any $0<\gamma<\beta$.
-We denote
-$$K_{t,k}:=\left|\frac{W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}}{W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}.$$
- On the event $\mathcal{D}_{t,k}$, by mean value theorem of integrals, we get
- \begin{align*}
-     \left|W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}\right|\leq \max \left\{W_t^{-\frac{\beta}{1+\beta}},W_{t-k-1}^{-\frac{\beta}{1+\beta}}\right\}\left|W_t-W_{t-k-1}\right|,
- \end{align*}
- what's more, when $t$ is sufficiently large,
- \begin{align*}
-     W_t\geq W_{t-k-1}-\|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}&\geq\|\mu\|\left(e^{-\frac{\alpha}{32}(t-k-1)}-e^{-\frac{\alpha}{4}(t-k-1)}\right)\\
+    \begin{align}
+        \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}\Big[\big|I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]\big|\cdot\Big|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\Big]\\
+        \label{ineq: control of Ykt}
+        &=|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\Big[\big|I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]\big|\cdot\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\Big].
+    \end{align}
+Denote
+$$K_{t,k}:=\left|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}.\quad t>1, k\in \{0,...,\lfloor t-\ln t\rfloor\}.$$
+ On the event $\mathcal{D}_{t,k}$, when $t$ is sufficiently large,
+ \begin{align*}
+     H_t\geq H_{t-k-1}-\|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}&\geq\|\mu\|\left(e^{-\frac{\alpha}{32}(t-k-1)}-e^{-\frac{\alpha}{4}(t-k-1)}\right)\\
      &\geq \|\mu\| e^{-\frac{\alpha}{16}(t-k-1)}.
  \end{align*}
-Hence,
-\begin{align*}
-    \left|W_t^{\frac{1}{1+\beta}}-W_{t-k-1}^{\frac{1}{1+\beta}}\right|&\leq C \max\left\{e^{\frac{\alpha}{16}(t-k-1)}, e^{\frac{\alpha}{32}(t-k-1)}\right\}e^{-\frac{\alpha}{4}(t-k-1)}\\
-    &\leq C e^{-\frac{3\alpha}{16}(t-k-1)},
-\end{align*}
-\begin{align*}
-    \left|W_t^{\frac{1}{1+\beta}}W_{t-k-1}^{\frac{1}{1+\beta}}\right|\geq C e^{-\frac{3\alpha}{32}(t-k-1)}.
-\end{align*}
-This is to say on the event $\mathcal{D}_{t,k}$, we get $K_{t,k}\leq C e^{-\frac{3\alpha}{32}(t-k-1)}$. Moreover, recall that $\alpha\beta=\kappa(f)(1+\beta)b$, we get
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}&\leq C e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
-    &\leq C e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}.\nonumber
-\end{align}
-
+ For sufficiently large $t$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$, we get
+ \begin{align*}
+     \left|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\right|
+     &\leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
+    \\&\leq \frac{1}{1+\beta}\|\mu\|^{\frac{2+\beta}{1+\beta}} \max\left\{e^{\frac{\alpha}{16}(t-k-1)}, e^{\frac{\alpha}{32}(t-k-1)}\right\}e^{-\frac{\alpha}{4}(t-k-1)}\\
+    &\leq\frac{1}{1+\beta}\|\mu\|^{\frac{2+\beta}{1+\beta}}  e^{-\frac{3\alpha}{16}(t-k-1)}.
+\end{align*}
+Similarly, we easily get 
+\begin{align*}
+    \left|H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}\right|\geq \|\mu\|^{\frac{2}{1+\beta}} e^{-\frac{3\alpha}{32}(t-k-1)}.
+\end{align*}
+Thus, for sufficiently large  $t$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$, there is a constant $C\geq 0$ such that
+\begin{align}\label{ineq: control of Kkt}
+     K_{t,k}\leq C e^{-\frac{3\alpha}{32}(t-k-1)}.
+\end{align}
+ According to Corollary \ref{cor: control of moment}, \eqref{ineq: control of Ykt}, \eqref{ineq: control of Kkt} and the condition $\alpha\beta=\kappa_f(1+\beta)b$, for any $\gamma\in (0, \beta)$, there exists $C,C'>0$, such that for any  sufficiently large  $t$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$,
+\begin{align}
+    &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
+    \leq C|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|I_{t-k-1}^{t-k}[\langle f,X_t\rangle]|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
+    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|I_{t-k-1}^{t-k}[\langle f,X_t\rangle]|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
+    \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
+    &\leq C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}.\nonumber
+\end{align}
+The last inequality hold as $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}=-\frac{\alpha \gamma-\kappa
+_f(1+\gamma)b}{1+\gamma}$.
 Now we take $\gamma$ so close to $\beta$ such that $\frac{1}{1+\gamma}-\frac{1}{1+\beta}<\frac{1}{32}$, then
 \begin{align}
-     \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\leq  e^{-\frac{\alpha}{16}(t-k)}.\label{thm122}
-\end{align}
-At last, combining \eqref{thm121} and \eqref{thm122}, we get
-$$\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\leq C t^{-\delta},$$
-for some $C,\delta>0$, which tend to zero, as $t\rightarrow \infty$.
-
-Next, we will prove $J_t \rightarrow^d 0$ as $t\rightarrow \infty$, this is to say
-\begin{align*}
-    \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\rightarrow 0.
-\end{align*}
-
-Let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|t^{-1/2}e^{\alpha t}\}$. Using Lemma \ref{lemma2_13}, we get
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C t^{-\delta}, \quad t\geq0,\label{Theorem123}
-\end{align}
-    for some $C,\delta>0$. Hence $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\mathbf{1}_{\mathcal{E}^c_{t,k}}\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ct^{-\delta}$.
-
-On the event $\mathcal{E}_t$, by using the element inequality $|e^{i z}-1|\leq |z|$,
-\begin{align*}
-    \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|&\leq|\theta| \mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t \left(t\|X_t\|\right)^{-\frac{1}{1+\beta}}M_k^t[f]\right|\\
-    &\leq t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t M_k^t[f]\right|.
-\end{align*}
-By the triangle inequality and Corollary \ref{cor27}, for any $\gamma\in(0,\beta)$, we know that
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}\left|\sum_{k=\lceil t-\ln t \rceil}^t M_k^t[f]\right|&\leq \sum_{k=\lceil t-\ln t \rceil}^t \|M_k^t[f]\|_{1+\gamma}\leq\sum_{k=\lceil t-\ln t \rceil}^t C_{\gamma}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k}\\
-    &=\sum_{k=\lceil t-\ln t \rceil}^t C_{\gamma}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}\leq C_{\gamma}e^{\frac{\alpha}{1+\beta}}t^{-\alpha(\frac{1}{1+\beta}-\frac{1}{1+\gamma})}.
-\end{align*}
-Hence, on the event $\mathcal{E}_t$
-\begin{align*}
-    \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\leq C_{\gamma}t^{-\alpha(\frac{1}{1+\beta}-\frac{1}{1+\gamma})} t^{-\frac{1}{2(1+\beta)}}
-\end{align*}
-We take $\gamma$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})$ smaller than $\frac{1}{2(1+\beta)}$ and combine with \eqref{Theorem123}, we proved that $J_t \rightarrow^d 0$ as $t\rightarrow \infty$.
+     \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]\leq  C' e^{-\frac{\alpha}{16}(t-k)}.\label{thm122}
+\end{align}
+At last, combining\eqref{ineq: control of I1t}, \eqref{thm121} and \eqref{thm122}, we get, there exists $C,\delta>0$ such that 
+$$\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\leq C t^{-\delta}, t ~\text{sufficiently large}.$$
+We complete step 1 by letting $t\rightarrow \infty$.
+
+Step 2. Fix $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, we will show that as $t\rightarrow \infty$, $I_2(t) \xrightarrow{d} 0$.
+
+Let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|t^{-1/2}e^{\alpha t}\}$. According to Lemma \ref{lem: control of XT}, there exists $C>0$
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C t^{-\frac{\beta}{2}}, \quad t\geq0.
+\end{align}
+    Therefore, for any $t\geq 0$ and $\theta\in \mathbb{R}$,
+    \begin{align}\label{Theorem123}
+        \left|\mathbb{\tilde{P}}_{\mu}\big [\big(e^{i\theta I_2(t)}-1\big)\mathbf{1}_{\mathcal{E}^c_t}\big]\right|\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq 2Ct^{-\frac{\beta}{2}}.
+    \end{align}
+On the event $\mathcal{E}_t$, according to Corollary \ref{cor: control of moment} and the element inequality $|e^{i z}-1|\leq |z|$, for each $\gamma\in (0,\beta)$, there exist $C,C'>0$, such that for any $t>0$ and $\theta \in \mathbb{R}$,
+\begin{align*}
+    &\left|\mathbb{\tilde{P}}_{\mu}\big[\big(e^{i\theta I_2(t)}-1\big)\mathbf{1}_{\mathcal{E}_t}\big]\right|
+    \leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}\mathbb{\tilde{P}}_{\mu}\big| I_{t-k-1}^{t-k}[\langle f,X_t\rangle]\big|.\\
+    &\leq C |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    &= C |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{(\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma})k}\\
+    &\leq C'|\theta|t^{-\frac{1}{2(1+\beta)}}t^{-\alpha(\frac{1}{1+\beta}-\frac{1}{1+\gamma})}.
+\end{align*}
+ Take $\gamma$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})$ smaller than $\frac{1}{2(1+\beta)}$ and combine with \eqref{Theorem123}, we proved that $J_t \rightarrow^d 0$ as $t\rightarrow \infty$.
+
+Step 3. Fix $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, we will show that as $t\rightarrow \infty$, $I_3(t) \xrightarrow{d} 0$.
+
+Similar to the proof of Stop 2.
 
 \subsection{Proof of Theorem \ref{Theorem11}}
-For any $f\in \mathcal{P}$, $f=\sum_{|p|\geq \kappa(f)}\langle f,\phi_p\rangle_\varphi \phi_p$. Therefore, we have the decomposition.
-\begin{align*}
-    &e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle=I_t+J_t\\
-    &=e^{-(\alpha-\kappa(f)b)t}\sum_{|p|= \kappa(f)}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle+e^{-(\alpha-\kappa(f)b)t}\sum_{|p|> \kappa(f)}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle
-\end{align*}
-By Lemma \ref{lemma26}, we easily get that
-\begin{align*}
-    I_t \rightarrow \sum_{|p|=\kappa(f)}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p  \quad as~ t\rightarrow \infty
-\end{align*}
-$\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for any $0< \gamma<\beta$. Thus, we just prove that $J_t$ tend to zero by this two ways.
+For any $f\in \mathcal{P}$, we rewrite 
+\begin{align}
+    f=\sum_{|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p=\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f},
+\end{align}
+where $\tilde{f}=\sum_{|p|> \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p$. Therefore
+\begin{align*}
+    &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
+    e^{-(\alpha-\kappa_fb)t}\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle.
+\end{align*}
+According to Lemma \ref{lemma26}, we easily get that,  for any $0< \gamma<\beta$,
+\begin{align}\label{as convergence}
+     e^{-(\alpha-\kappa_fb)t}\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle \rightarrow \sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,  \quad  t\rightarrow \infty,
+\end{align}
+$\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. Let
+\begin{align}
+    J_t=e^{-(\alpha-\kappa_fb)t}\langle \tilde{f},X_t\rangle.
+\end{align}
+It suffices to show that $\lim_{t\rightarrow \infty}J_t=0$, $\mathbb{P}_{\mu}$ and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
 
 {\em Convergence in $L^{1+\gamma}(\mathbb{P}_{\mu})$}:
-Let
-\begin{align*}
-    \tilde{f}=\sum_{|p|> \kappa(f)}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle
-\end{align*}
-By the definition of $\kappa(f)$, we know that $\kappa(\tilde{f})\geq \kappa(f)+1$. What's more, $J_t=e^{-(\alpha-\kappa(f)b)t}\langle \tilde{f},X_t\rangle$.
-Using Corollary \ref{cor27}, for some constant $C$, we get
-
-1) when $\alpha\gamma>\kappa(\tilde{f})(1+\gamma)b$
-\begin{align*}
-    \|J_t\|_{1+\gamma}\leq C e^{-(\alpha-\kappa(f)b)t}e^{(\alpha-\kappa(\tilde{f})b)t}\leq C  e^{-(\alpha-\kappa(f)b)t}e^{(\alpha-(\kappa(f)+1)b)t}=C e^{-bt}
-\end{align*}
-
-2) when $\alpha\gamma=\kappa(\tilde{f})(1+\gamma)b\geq (\kappa(f)+1)(1+\gamma)b$
-\begin{align*}
-     \|J_t\|_{1+\gamma}\leq C t e^{-(\alpha-\kappa(f)b)t}e^{\frac{\alpha}{1+\gamma}t}\leq C t e^{-bt}
-\end{align*}
-
-3) when $\alpha\gamma>\kappa(\tilde{g})(1+\gamma)b\geq (\kappa(g)+1)(1+\gamma)b$
-\begin{align*}
-    \|J_t\|_{1+\gamma}\leq C e^{-(\alpha-\kappa(g)b)t}e^{\frac{\alpha}{1+\gamma}t}\leq C e^{-bt}
-\end{align*}
-In conclusion, $\lim_{t\rightarrow \infty}\|J_t\|=0$.
-
-{\em Almost sure convergence}: For each $a\in \mathbb{R}$, let $\{M_t^{f,a},t\geq0\}$ be the martingale in \eqref{defmartingale} and let
-$$L_t^{f,a}:=\int_0^t e^{-(\alpha-ab)s}\langle \bar{f},X_s\rangle ds.$$
-Thus, $M_t^{\tilde{f},a}=e^{-(\alpha-ab)t}\langle \tilde{f}, X_t\rangle-L_t^{\tilde{f},a}$. When take $\alpha=\kappa(f)+\frac{1}{2}$, we get
-
-%We take $a=\kappa(g)+\frac{1}{2}$ and $f=\tilde{g}$ into this martingale and get
-\begin{align*}
-    J_t=e^{-\frac{1}{2}}M_t^{\tilde{f},a}+e^{-\frac{1}{2}}L_t^{\tilde{f},a}.
-\end{align*}
-Equivalently, we will prove that
-\begin{align*}
-    e^{-\frac{1}{2}bt}M_t^{\tilde{f},a}\rightarrow 0, \quad e^{-\frac{1}{2}bt}L_t^{\tilde{f},a}\rightarrow 0 \quad as~t\rightarrow \infty
-\end{align*}
-$\mathbb{P}_{\mu}$-as.
-As $\kappa(L\tilde{f}+ab\tilde{f})=\kappa(\tilde{f})\geq \kappa(f)+1$, following the similar way to prove the case $L^{1+\gamma}(\mathbb{P}_{\mu})$-convergence, we get there exists some $C, \delta>0$ such that for any $t\geq 0$
-\begin{align*}
-    \|e^{-(\alpha-ab)t}\langle \tilde{f},X_t\rangle)\|_{1+\gamma}\leq C e^{-\delta t},\quad \|e^{-(\alpha-ab)t}\langle L\tilde{f}+ab\tilde{f},X_t\rangle\|_{1+\gamma}\leq C e^{-\delta t}.
-\end{align*}
-Therefore, $|L_t^{\tilde{f},a}|\leq Y_t^{\tilde{f},a}:=\int_0^t e^{-(\alpha-ab)s}|\langle L\tilde{f}+ab\tilde{f},X_s\rangle|ds$ satisfying that, for ant $t\geq 0$,
-\begin{align*}
-    \|L_t^{\tilde{f},a}\|_{1+\gamma}\leq\|Y_t^{\tilde{f},a}\|_{1+\gamma}\leq \int_0^t \|e^{-(\alpha-ab)s}\langle L\tilde{f}+ab\tilde{f},X_s\rangle\|_{1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
-\end{align*}
-As $Y_t^{\tilde{f},a}$ is positive increasing, we get that it convergence some random variable $Y_{\infty}^{\tilde{f},a}$ almost sure and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. This is to say
+
+According to  Corollary \ref{cor: control of moment} and the fact $\kappa_{\tilde{f}}\geq \kappa_f+1$, for each $\gamma\in(0,\beta)$, there exists $C>0$ such that 
+\begin{itemize}
+    \item [1)] When $\alpha\gamma>\kappa_{\tilde{f}}(1+\gamma)b$
+\begin{align*}
+    \|J_t\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-(\alpha-\kappa_fb)t}e^{(\alpha-\kappa_{\tilde{f}})bt}\leq C  e^{-(\alpha-\kappa_fb)t}e^{(\alpha-(\kappa_f+1)b)t}=C e^{-bt};
+\end{align*}
+     \item[2)] When $\alpha\gamma=\kappa_{\tilde{f}}(1+\gamma)b\geq (\kappa_f+1)(1+\gamma)b$
+\begin{align*}
+     \|J_t\|_{\mathbb{P}_{\mu};1+\gamma}\leq C t e^{-(\alpha-\kappa_fb)t}e^{\frac{\alpha}{1+\gamma}t}\leq C t e^{-bt}.
+\end{align*}
+     \item[3)] When $\alpha\gamma>\kappa_{\tilde{g}}(1+\gamma)b\geq (\kappa_f+1)(1+\gamma)b$
+\begin{align*}
+    \|J_t\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-(\alpha-\kappa_fb)t}e^{\frac{\alpha}{1+\gamma}t}\leq C e^{-bt}.
+\end{align*}
+\end{itemize}
+In conclusion, $\lim_{t\rightarrow \infty}\|J_t\|_{\mathbb{P}_{\mu};1+\gamma}=0$.
+
+{\em Almost sure convergence}: For each $a\in \mathbb{R}$ and $f\in \mathcal{P}$, let
+\begin{align}
+L_t^{f,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f,X_s\rangle ds \quad t\geq 0.
+\end{align}
+and 
+\begin{align}
+    Y_t^{f,a}:=\int_0^t e^{-(\alpha-ab)s}|\langle Lf+abf,X_s\rangle|ds, \quad t\geq0.
+\end{align}
+ Take $a=\kappa_{\tilde{f}}+\frac{1}{2}$ into the martingale defined in \eqref{defmartingale}, we easily get
+
+\begin{align*}
+    J_t=e^{-\frac{1}{2}bt} M_t^{\tilde{f},a}+e^{-\frac{1}{2}bt}L_t^{\tilde{f},a}.
+\end{align*}
+Equivalently, we just show that, as $t\rightarrow \infty$,
+\begin{align*}
+    e^{-\frac{1}{2}bt}M_t^{\tilde{f},a}\rightarrow 0, \quad e^{-\frac{1}{2}bt}L_t^{\tilde{f},a}\rightarrow 0 \quad \mathbb{P}_{\mu}\text{-a.s.}
+\end{align*}
+As $\kappa_{(L+ab)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1$, following the similar way to prove the case $L^{1+\gamma}(\mathbb{P}_{\mu})$-convergence, we get, for each $\gamma\in (0,\beta)$ there exists some $C, \delta>0$ such that for any $t\geq 0$,
+\begin{align}
+    \|e^{-(\alpha-ab)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-\delta t},\quad \|e^{-(\alpha-ab)t}\langle L\tilde{f}+ab\tilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-\delta t}.
+\end{align}
+Therefore, by triangle inequality, for any $t\geq 0$,
+\begin{align*}
+    \|L_t^{\tilde{f},a}\|_{\mathbb{P}_{\mu};1+\gamma}\leq\|Y_t^{\tilde{f},a}\|_{\mathbb{P}_{\mu};1+\gamma}\leq \int_0^t \|e^{-(\alpha-ab)s}\langle L\tilde{f}+ab\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
+\end{align*}
+Note that $Y_t^{\tilde{f},a}$ is positive increasing about $t$, we conclude that it converges to some random variable $Y_{\infty}^{\tilde{f},a}$ almost sure and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. 
+Therefore,
 \begin{align*}
@@
 \begin{align*}
-    \|M_t^{\tilde{f},a}\|_{1+\gamma}\leq  \|e^{-(\alpha-ab)t}\langle \tilde{f},X_t\rangle)\|_{1+\gamma}+\|L_t^{\tilde{f},a}\|_{1+\gamma}\leq C,\quad t\geq 0.
-\end{align*}
-for some constant $C$, which implies that $\lim_{t\rightarrow\infty} e^{-\frac{1}{2}bt}M_t^{\tilde{f},a}=0$. we complete our proof.
+    \|M_t^{\tilde{f},a}\|_{\mathbb{P}_{\mu};1+\gamma}\leq  \|e^{-(\alpha-ab)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),\quad t\geq 0.
+\end{align*}
+which implies that $\lim_{t\rightarrow\infty} e^{-\frac{1}{2}bt}M_t^{\tilde{f},a}=0$. we complete our proof.
 \subsection{Proof of Theorem \ref{Theorem13}}
@@
     \begin{align*}
-        (\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} (\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[f]+\sum_{\lceil t-\ln t \rceil}^t (\|X_t\|)^{-\frac{1}{1+\beta}}M_k^t[f]\\
-        &=I_t+J_t.
-    \end{align*}
+        (\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(\|X_t\|)^{\frac{1}{1+\beta}}}+\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{I_0^{t-\lfloor t \rfloor}[\langle f ,X_t\rangle]}{(\|X_t\|)^{\frac{1}{1+\beta}}}\\
+        &:=I_1(t)+I_2(t)+I_3(t).
+    \end{align*}
+ Denote
+    $$\tilde{I}_1(t):=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
+    Fix $\theta\in \mathbb{R}$. Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get
+    \begin{align*}
+        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}-\exp\left(\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\right)\right|\leq C \frac{1}{t^{\delta}},
+    \end{align*}
+    for some $C,\delta>0$. Hence, according to \eqref{msmallcase}, as $t\rightarrow \infty$, We obtain that $\tilde{I}_1(t)\xrightarrow{d}\eta_2$.
+
+    Therefore, to prove the theorem ,we just to prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\rightarrow 0$ and $I_i(t)\xrightarrow{d} 0,~i=1,2$.
+
     We denote
-    $$\tilde{I}_t=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{M_k^t[f]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
-    Taking $\theta_k=( e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, then we get
-    \begin{align*}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}-\exp\left(\theta^{1+\beta}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[f]\right)\right|\leq C \frac{1}{t^{\delta}},
-    \end{align*}
-    for some $C,\delta>0$. Hence We obtain that $\tilde{I}_t\rightarrow\eta_2$ as $t\rightarrow \infty$, by using  \eqref{msmallcase}.
-
-    Therefore, to prove the theorem ,we just to prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\rightarrow 0$ and $J_t\rightarrow^d 0$.
-
-    We denote
-    \begin{align*}
-        Y_{t,k}:=\exp\left(i\theta\frac{M_k^t[f]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{M_k^t[f]}{\left(\|X_t\|\right)^{\frac{1}{1+\beta}}}\right)
-    \end{align*}
-With completely same method before \eqref{thm125} in the proof of Theorem \ref{Theorem12}, we can prove that
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}+ e^{-\delta(t-k-1)}), \quad t\geq 0.
-\end{align*}
-Moreover, on the case $\alpha\beta<\kappa(f)(1+\beta)b$,  $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}< - \frac{\alpha\gamma-\kappa(f)(1+\gamma)b}{1+\gamma}$, this is to say,
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C e^{-(t-k)}
-\end{align*}
-Then we can prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_t}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_t}\right|\rightarrow 0$, by following the lines of the proof in the critical case.
-
-To prove $J_t\rightarrow^d 0$, We let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon )t}\}$ instead, for any $\epsilon>0$, we know that, see Lemma \ref{lemma28}, there exists
-$C,\delta >0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal{E}_t^c)\leq C e^{-\delta t}$.
-What's more, for any $0< \gamma <\beta$, we let $q=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa(f)(1+\gamma)b}{1+\gamma}>0$, then by Corollary \ref{cor27}, we have
-\begin{align*}
-    \|M_k^t[f]\|\leq \|M_k^t[f]\|_{1+\gamma}\leq \tilde{C}_1 e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa(f)(1+\gamma)b}{1+\gamma}k}\leq \tilde{C}_1 e^{-qk}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}
-\end{align*}
-Then we get $  \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta J_t}-1\right|\rightarrow 0$ as $ t\rightarrow \infty$, by following the similar way in critical case.
+    \begin{align*}
+        Y_{t,k}:=\exp\left(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{\left(\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
+    \end{align*}
+With completely same method of Step 1 in the proof of Theorem \ref{Theorem12}, we can prove that, for each $\gamma\in (0,\beta)$, there exist $C,\delta>0$, such that for any $t\geq1$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$,
+\begin{align*}
+    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}+ e^{-\delta(t-k-1)}).
+\end{align*}
+Moreover, on the case $\alpha\beta<\kappa_f(1+\beta)b$,  $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}< - \frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}$, therefore,
+\begin{align}
+    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C (e^{-\frac{3\alpha}{32}(t-k-1)}+e^{-\delta(t-k-1)}).
+\end{align}
+Then we can prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\rightarrow 0$, by following the lines of the proof in the critical case.
+
+To prove $I_2(t)\xrightarrow{d} 0$, We let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon )t}\},~\epsilon>0$, instead. According to Lemma \ref{lem: control of AT}, there exists
+$C>0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal{E}_t^c)\leq C e^{-\epsilon \beta t},~t\geq 0$.
+
+According to Corollary \ref{cor: control of moment}, for any $0< \gamma <\beta$, let $q=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}>0$, there exists $C>0$ such that
+\begin{align}
+    \|I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]\|\leq \|I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}\leq C e^{-qk}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}.
+\end{align}
+Then we get $  \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_2(t)}-1\right|\rightarrow 0$ as $ t\rightarrow \infty$, by following the similar way in critical case.
+
+The method to prove $I_3(t)\xrightarrow{d}0$ is similar to that of $I_3(t)$.
 

### 2019-01-31 supCLT.tex
supCLT.tex: 1129

@@
 %%%----Versions-----------------------------
+% supCLT6.tex 2018/11/29 by Zhenyao
 % supCLT5.tex ......... by Zhenyao
@@
 \end{equation}
-
 	where $\alpha > 0$ and $\beta \in (0,1) $.
@@
 \end{equation}
-
 	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
@@
     \Pi_x [e^{\alpha t}f(\xi_t)],
-    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
+    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
 \end{equation}
@@
     = \langle T_t^\alpha f, \mu \rangle,
-    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d), \mu \in \mathcal M(\mathbb R^d).
+    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
 \end{equation}
@@
 \end{equation}
-    Let $L^2(\varphi):= \left\{ h  \in \mathscr B(\mathbb R^d): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
+    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
 \begin{equation}
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exist $C>0$  and $n\in \mathbb{N}$ such that,
-
-\begin{equation}
-\label{eq:semigroupineq}
-    |T_tf(x)|
-    \leq e^{-\kappa_f bt} C(1+|x|)^n,
-    \quad t\geq 0, x\in \mathbb R^d.
-\end{equation}
 \added{
+    For each $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
+$
+	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
+$
+and
+$
+	Q f:= Q_{\kappa_f}f.
+$
+    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
+}
+	\deleted{
 	For each $\kappa\geq0$, define $\mathcal{P}_{\kappa}$ by 
@@
     Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
-    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
+    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
     For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
@@
 \end{align}
-
-    {\bf Zhenyao: There are notation inconsistency in the Appendix and other sections. Mainly on the branching mechanism: In the appendix, we use
-\[
-    \psi(x,z)= -\beta(x)z+\alpha(x)z^2 + \int_0^t \dots;
-\]
-    But in other subsections we use
-\[
-    \psi(z) = - \alpha z + z^{1+\beta}.
-\]
-    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.}
 
@@
 $
-   	I_a^b[Y]
+   	\mathcal I_a^b Y
     := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
@@
 \begin{align}
-    I_0^t[Y]
-    = \sum_{k = 0}^{\lfloor t \rfloor - 1} I_k^{k+1}[Y] + I_{\lfloor t \rfloor}^t[Y],
+    \mathcal I_0^t Y
+    = \sum_{k = 0}^{\lfloor t \rfloor - 1} \mathcal I_k^{k+1}Y + \mathcal I_{\lfloor t \rfloor}^t Y,
     \quad t\geq 0.
@@
 	The random variable we are interested in is $Y:= \langle g,X_t\rangle$.
+\deleted{	
 	In this case we have
@@
 \end{align}
+}
+
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
@@
     We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$, for each $s\in \Lambda$.
-
+\deleted{
     The first reason for considering $\gamma$-controllable operators is the following:
@@
 \end{proof}
+}
 	For two operators $A: \mathcal D_A \to \mathcal P^*$ and $B: \mathcal D_B \to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for each $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
     Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for each $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
-    The second reason for considering $\gamma$-controllable operators is that they have good algebra properties:
+    The reason for considering $\gamma$-controllable operators is that they have good algebra properties:
 \begin{lem}
@@
 \label{lem: upper bound for usgx}
-The following statements are true for the super-OU process considered in the first subsection:
+The following statements are true for the super-OU process considered in this paper:
 \begin{itemize}
@@
     Note that $f\mapsto\sup_{0\leq u\leq 1}T^{\alpha}_u|f|$ is monotonic and $1$-scalable.
-    Combine this with \eqref{eq: -v has positive real part, we get the desired result.}
 
@@
 \end{proof}
+\added{
 \begin{lem}\label{lem: temp}
-    There is an $(1+\beta)$-scalable operator $S$ such that for each \added{$g\in \mathcal P_{\kappa}$ with $\kappa\geq 0$}, $\lambda >0$, $\mu\in \mathcal M_c(\mathbb R^d)$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
-\[
-    \mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda)
-    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r} \langle SQ_{\kappa}g,\mu\rangle.
+	For each $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb{R}^d)$ there exist a constant $C \geq 0$ such that for each $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
+\[
+    \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
+    \leq \frac{ C}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r}.
 \]
@@
 \begin{proof}
-    Denote by $(R_0,S_0)$ the $(1+\beta)$-control-pair in Lemma \ref{lem: control pair for P(M>lambda)}.
-    Then using Markovian property of $(X_t)_{t\geq 0}$ we get
-\begin{align}
-    &\mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda)
+    Denote by $(R,S)$ the $(1+\beta)$-control-pair in Lemma \ref{lem: control pair for P(M>lambda)}.
+    Let $h \in \mathcal P^+$, $\mu \in \mathcal M_c(\mathbb{R}^d)$, $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t$ with $s-r \leq 1$. 
+    Suppose that $g\in \mathcal P$ satisfies $Q_\kappa g \leq h$.
+    Using Markovian property of $(X_t)_{t\geq 0}$ we get
+\begin{align}
+    &\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
     = \mathbb P_\mu \big[\mathbb P_\mu[|\langle T_{t-s}^\alpha g, X_{s}\rangle - \langle T_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r]\big]
     \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle T_{t-s}^\alpha g, X_{s-r}\rangle - \langle T_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
-    = \mathbb P_\mu \big[\mathbb P_{X_r}(|I_0^{s-r}[\langle T_{t-s}^\alpha g, X_{s-r}\rangle] |> \lambda)\big]
-    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
-    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta e^{(t-s)(\alpha- \kappa b)}Q_{\kappa}g|,X_r\rangle d\theta \Big]
-	\\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta e^{(t-s)(\alpha- \kappa b)}Q_{\kappa}g|,X_r\rangle d\theta \Big]
-    = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \mathbb P_\mu [ \langle S_0Q_{\kappa}g,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
-    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \langle T_r^\alpha S_0Q_{\kappa}g,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
-    \leq e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r} \langle QS_0Q_{\kappa}g,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}.
-\end{align}
-    Note that
-\[
-    S := \frac{2^{2+\beta}}{2+\beta}QS_0
-\]
-    is an $(1+\beta)$-scalable operator which is independent of the choice of $g,\mu, \lambda, r, s$ and $t$.
-\end{proof}
-
+    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle T_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
+    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
+    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
+	\\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
+    \\&= e^{(1+\beta)(t-s)(\alpha- \kappa b)} \mathbb P_\mu [ \langle Sh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
+    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \langle T_r^\alpha Sh,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
+    \\&\leq e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r} \langle Q_0 Sh,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}.
+\end{align}
+    Therefore the desired result is true with 
+\[
+    C := \frac{2^{2+\beta}}{2+\beta}\langle Q_0Sh, \mu\rangle.
+    \qedhere
+\]
+\end{proof}
+}
+\added{
 \begin{lem}\label{lem: control of mgtrs}
-    \added{Let $g$ be the function in lemma \ref{lem: temp}.}
-    For each $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
-\[
-    \mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
+	For each $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exist a constant $C > 0$, such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
+\[
+    \sup_{g \in \mathcal P: Q_\kappa g\leq h} \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
     \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b)}.
@@
 \begin{proof}
-Let $S$ be the $(1+\beta)$-scalable operator in the previous Lemma.
-    For each $c>0$ we have
-\begin{align}
-    &\mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
-    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda) d\lambda
-    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|I_r^s[\langle g, X_t\rangle]|> \lambda) d\lambda
-    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r} \langle SQ_{\kappa}g,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
-    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r} \langle SQ_{\kappa}g,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
+	Fix $h \in \mathcal P$ and $\mu \in \mathcal M_c(\mathbb R^d)$. Let $C_0$ be the constant in the previous Lemma.
+    For each $\kappa \in \mathbb Z_+$, each $0\leq r\leq s\leq t$ with $s-r \leq 1$, each $g\in \mathcal P$ with $Q_k g \leq h$ and each $c>0$, we have
+\begin{align}
+    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
+    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda) d\lambda
+    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^s\langle g, X_t\rangle|> \lambda) d\lambda
+    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r} C_0  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
+    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r} C_0   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
 \end{align}
@@
 \begin{align}
-    &\mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
-    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ \langle SQ_{\kappa}g,\mu\rangle \frac{1+\gamma}{\beta - \gamma}\Big).
+    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
+    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}\Big).
 \end{align}
@@
     \leq t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b).
+\]
+	So the desired result is true with 
+\[
+	C := \Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}\Big).
 	\qedhere
@@
 \end{proof}
+}
+\added{
 \begin{lem}
 \label{lem: control moment}
-    \added{Let $g$ be the function in Lemma \ref{lem: control of mgtrs}.}
-    For each $0 < \gamma < \beta$ and $\mu\in \mathcal M_c(\mathbb R^d)$ there exists a constant $C>0$ such that for each $t\geq 0$:
+	For each $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$, $0<\gamma < \beta$ and $\kappa \in \mathbb Z_+$, there exist a constant $C > 0$, such that for each $t\geq 0$, we have
 \begin{itemize}
 \item[(1)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$.
+    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$;
 \item[(2)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$.
+    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$;
 \item[(3)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
+    $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
 \end{itemize}
@@
 \begin{proof}
-    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$.
+    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
     Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
-    Using the triangle inequality,
+    Using the triangle inequality, for each $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$ we have
 \begin{align}
@@
     &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| I_{t-k-1}^{t-k}[\langle g,X_t\rangle] \big\|_{\mathbb P_\mu;1+\gamma}+\big\| I_{0}^{t-\lfloor t \rfloor}[\langle g,X_t\rangle]  \big\|_{\mathbb P_\mu;1+\gamma}
-    \\ &\leq C e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} k} .
+    \\ &\leq C_0^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} k} 
 \end{align}
@@
 \end{proof}
-\added{
+}
+\deleted{
 \begin{cor}\label{cor: control of moment}
@@
     \[
-    \mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
+    \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
     \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_g b)}.
@@
 \end{proof}
-\added{
+\deleted{
 \begin{lem}\label{lem: control of A&D}
@@
 \end{align}
-
+\deleted{
     Note that $m_t[\theta f]$ can be rewritten as follows:
@@
     The following Lemma says that function $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\begin{lem}\label{lem: charactreisticfunction}
+}
+\begin{lem}
+\label{lem: charactreisticfunction}
     Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
@@
 \[
-    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \int_{\mathbb R^+} f(\xi t)k(\xi,dt) \lambda(d\xi),\quad
-    f\in \mathscr B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
+    f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
 \]
@@
 \[
-    \lambda_0(d\xi) := \frac{1}{\Gamma(-1-\beta)} \int_0^\infty t^{1+\beta}k(\xi,dt) \lambda (d\xi).
+    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi)
 \]
@@
 \[
-    \lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt) \lambda (d\xi)
+    \lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt)
     = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
@@
 \[
-    \int_{\mathbb R^d/\{0\}}f(x)\nu(dx)= \int_{S} \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} \lambda_0(d\xi).
+    \int_{\mathbb R^d/\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
 \]
@@
     &\int_{\mathbb R^d/\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
-    = \int_S \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}\lambda_0(d\xi)
-\\&\quad = \int_S \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt) \lambda (d\xi)
-\\&\quad = \int_S (i\theta\cdot \xi)^{1+\beta} \int_0^\infty t^{1+\beta} k(\xi,dt) \lambda (d\xi)
-= \int_S \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)\lambda(d\xi)
+    = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}
+\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt) 
+\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt) 
+= \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)
 \\&\quad = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
@@
 \end{proof}
+\added{
+\begin{cor}
+\label{cor: alpha stable rv}
+	For any $t\geq 0$ and $f\in \mathcal P$, function $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+\end{cor}
+\begin{proof}
+	Fix $t\geq 0$ and $f\in \mathcal P$.
+	Note that $m_t[\theta f]$ can be rewritten as follows:
+\[
+    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 T_{1-s}^\alpha (-i\theta T_{s+t}^\alpha f)^{1+\beta}(x)~ds,
+    \quad \theta \in \mathbb R.
+\]
+	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only have to show that
+\begin{equation}
+\label{eq: what I want to proof}
+	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 T_{1-s}^\alpha (|T_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
+\end{equation}
+	According to Lemma \ref{lem: upper bound for usgx}(2) and Lemma \ref{lem: property of controllable operators}(1,2,4) we know that 
+$
+	g \mapsto \int_0^1 T_{1-s}^\alpha (|T_{s}^\alpha g|^{1+\beta})~ds
+$
+	is an $(1+\beta)$-controallable operator on $\mathcal P$.
+	This implies that $x \mapsto \int_0^1 T_{1-s}^\alpha (|T_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
+	Therefore \eqref{eq: what I want to proof} is true.
+\end{proof}
+}
 
@@
  \begin{align}
-      \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
+      \gamma_{t,k}:=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
  \end{align}
@@
  \end{lem}
-
- \begin{proof}
-Fix $\theta \in \mathbb{R}$, let $\tilde{\theta}_{t,k}=\frac{\theta}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}$. For any $k\geq 0$ and $t>k+1$, we have
-\begin{align}
-    &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k((e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}})\big|\mathscr{F}_{t-k-1}\big]\\
-    &=\mathbb{P}_{\mu}\big[\exp(i\tilde{\theta}\langle T_k^{\alpha}f,X_{t-k}\rangle-i\tilde{\theta}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle)\big|\mathscr{F}_{t-k-1}\big] \\
-        &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
-        \label{condition mean}
-        &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle+\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle\big)\\
-       \end{align}
-         Fix $\gamma_0\in (0,\beta)$, let $p=\min\{\frac{b}{2},\frac{\alpha\gamma_0}{1+\gamma_0}\}$ and $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
-       To get the conclusion of Lemma \ref{lem: mainlemma}, it suffices to show that
-       \begin{align}
-           \mathbb{P}_{\mu}\Big(\exp(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\Big)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[\theta f]).
-       \end{align}
-
-      According to Lemma \ref{lem: charactreisticfunction}, \eqref{condition mean} and the element inequality, for any $x,y\in \mathbb{C}_{+}$, $|e^{-x}-e^{-y}|\leq |x-y|$.
-    \begin{align}
-        %&\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha %k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
-        &\mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big|\Big]\\
-        &\leq \mathbb{P}_{\mu}\big[\big|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
-        \label{ineqinlem31}
-        &+\mathbb{P}_{\mu}\big[\big|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]:=J_1(\theta,k,t)+J_2(\theta,k,t).
-    \end{align}
-Therefore, according to the fact $|e^{-z}|\leq1,~z\in \mathbb{C}_+$
-\begin{align}
-    &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{D^c}\Big]\Big|
-    \\& \leq \mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{D^c}\Big|\mathscr{F}_{t-k-1}\Big)\Big|\Big]
-    \label{ineq: used in next corollary}
-    \\ & \leq\mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big|\Big]
-    \\&+ 2\mathbb{P}_{\mu}(\mathcal{A}_{t-k-1}(\epsilon_0)\Delta D^c)\\
-    &\leq J_1(\theta,k,t)+J_2(\theta,k,t)+J_3(k,t),
-\end{align}
-where $J_3(k,t)=2\mathbb{P}_{\mu}(\mathcal{A}_{t-k-1}(\epsilon_0)\Delta D^c)$.
-
-Step 1.  We will show that for each $\mu \in\mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$, such that for any $\theta\in \mathbb{R}$, $k\geq 0$ and $t>k+1$,
+\added{
+ \begin{proof}
+	We only have to show that 
+\begin{align}
+    \mathbb{P}_{\mu}[\exp(i\gamma_{t,k}); D^c]
+    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[f]),
+    \quad \mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0.
+\end{align}
+	In fact, once we proved this, we can replace $f$ with $\theta f$ where $\theta \in \mathbb R$ is arbitrary and get the desired result.
+	In the rest of the proof we fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and an $f\in \mathcal P$.
+	Define events
+\[
+	A_t(\epsilon):=\{ \|X_t\| \geq \|\mu\|e^{(\alpha - \epsilon)t} \},\quad t\geq 0, \epsilon > 0.
+\]
+
+	Step 1. We will show that for each $\epsilon > 0, k\geq 0$, and $t>k+1$ we have
+\begin{align}
+    \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
+    \leq J_1(t,k,\epsilon)+J_2(t,k,\epsilon)+J_3(t,k,\epsilon)
+\end{align}
+	where
+\begin{align}
+\label{eq: Def of Ji}
+	\theta_{t,k}
+	&:= (e^{\alpha k}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}},
+	\\ J_1(t,k,\epsilon) 
+	&:= \mathbb{P}_{\mu}\big[|\langle U_1(\theta_{t,k}T_k^{\alpha}f)-\tilde U_1(\theta_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big]
+	\\ J_2(t,k,\epsilon)
+	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|; A_{t-k-1}(\epsilon)\big]
+	\\ J_3(t,k, \epsilon)
+	&:=2\mathbb{P}_{\mu}(A_{t-k-1}(\epsilon)\Delta D^c).
+\end{align}
+In fact, from the definition of $U_1, \tilde U_1$ and $Z_1$, we have
+\begin{align}
+\label{eq: need1}
+    &\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}|\mathscr{F}_{t-k-1}]
+    =\mathbb{P}_{\mu}[e^{i\theta_{t,k}\langle T_k^{\alpha}f,X_{t-k}\rangle-i\theta_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle}|\mathscr{F}_{t-k-1}] 
+    \\&=e^{\langle (U_1 - iT_{1}^{\alpha}) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle}
+    \\&=e^{\langle (U_1 - \tilde U_1+Z_1) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle},
+    \quad k\geq 0, t\geq k+1.
+\end{align}
+	From Corollary \ref{cor: alpha stable rv}, we have
+\begin{equation}
+\label{eq: need2}
+	\operatorname {Re} m_t[f] < 0.
+\end{equation}
+    According to the definition of $\tilde U_1$ and $Z_1$, \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
+\[
+	|e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+, 
+\]
+	we verify that
+\begin{align}
+\label{eq: inequality that will used later}
+    &\big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
+    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; A_{t-k-1}(\epsilon)| \mathscr F_{t-k-1}]\big| + 2\mathbb P_\mu(A_{t-k-1}(\epsilon) \Delta D^c| \mathscr F_{t-k-1})\Big]
+    \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{e^{\alpha}m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon)
+    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (U_1 - iT_{1}^{\alpha}) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    \\& \leq \mathbb{P}_{\mu}\big[|\langle (U_1 - i T_1^\alpha)(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    \\&\leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon),
+    \quad k\geq 0, t\geq k+1, \epsilon> 0.
+\end{align}
+
+Step 2.  We will show that there exists a $C>0$, such that,
     \begin{align}
     \label{lemma31q}
-      J_1(\theta,k,t)\leq C|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
-    \end{align}
-In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6). For any $\theta\in\mathbb{R}$, $k \geq 0$ and $t>k+1$, we have
-\begin{align}
-   & \big|U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}
-   \leq R\big(|\tilde{\theta}_{t,k}T_k^{\alpha}f|\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}
-   \\&\leq R \Big(\frac{|\theta|e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon_0)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
-    \leq S \Big(\frac{|\theta|e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon_0)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
-   \\&\leq \Big(\frac{|\theta|e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon_0)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+2\beta}SQf
-   \\&=\frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{\frac{1+2\beta}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta)k)}e^{-\frac{(\alpha-\epsilon_0)(1+2\beta)(t-k-1)}{1+\beta}}SQf.
-   \\&\leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{(\alpha-\epsilon_0)(1+2\beta)(t-k-1)}{1+\beta}}SQf
-\end{align}
-Note that $\epsilon_0\leq \frac{\alpha\beta}{2(1+2\beta)}$, thus
-\begin{align}
-     J_1(\theta,k,t)&
-     \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{(\alpha-\epsilon_0)(1+2\beta)(t-k-1)}{1+\beta}}\mathbb{P}_{\mu}[\langle SQf,X_{t-k-1}\rangle]\\
-     & \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}|\theta|^{1+2\beta}e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}e^{\alpha(t-k-1)}\langle QSQf, \mu \rangle\\
-     & \leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle QSQf,\mu\rangle|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
-\end{align}
-Step 2, for any $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, we will show that there exists $C>0$ such that for any $\theta\in \mathbb{R}$, $k\geq 0$ and $t\geq k+1$, 
+      J_1(k,t,\epsilon)\leq C\exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
+      \quad k \geq 0, t\geq k+1, \epsilon > 0.
+    \end{align}
+	In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6). 
+	Then, we can verify that
+\begin{align}
+   & |(U_1 - \tilde U_1)(\theta_{t,k}T_k^{\alpha}f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
+   \leq R(|\theta_{t,k}T_k^{\alpha}f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
+   \\&\leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
+    \leq S \Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
+   \\&\leq \Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+2\beta}SQf
+   \\&=\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}}e^{\frac{1+2\beta}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf
+   \\&\leq\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf,
+   \quad k\geq 0, t\geq k+1, \epsilon > 0.
+\end{align}
+Thus
+\begin{align}
+\label{eq: estimate of J1}
+     J_1(k,t,\epsilon)&
+     \leq \|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}\mathbb{P}_{\mu}[\langle SQf,X_{t-k-1}\rangle]\\
+     & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
+     \\ &\qquad k\geq 0, t\geq k+1, \epsilon > 0.
+\end{align}
+	Step 3.
+	Fix a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
+	Then there exists a constant $C > 0$ such that
 \begin{align}
 \label{eq:31step3}
-    J_2(\theta,k,t)\leq C|\theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)}.
-\end{align}
-    Notice that
-    \begin{align}
-          &\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]
-          \\&=|\theta|^{1+\beta}e^{-\alpha k}\Big(\frac{\langle Z_1(T_k^{\alpha}(f \operatorname{sgn} \theta)),X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1(T_k^{\alpha}(f \operatorname{sgn} \theta)),\varphi\rangle\Big).
-    \end{align}
-For convenience, we first assume that $\theta>0$. Therefore, for any $k\geq 0$ and $t\geq k+1$,
-\begin{align}
-J_2(\theta,k,t)
-    &=|\theta|^{1+\beta}e^{-\alpha k}\mathbb{P}_{\mu}\Big[\Big|\frac{\langle Z_1(T^{\alpha}_k f),X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1(T^{\alpha}_k f)Z_{f_k},\varphi\rangle\Big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\nonumber\\
-    &\leq |\theta|^{1+\beta}e^{-\alpha k}e^{-(\alpha-\epsilon_0)(t-k-1)}\mathbb{P}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right],\label{II1}
-\end{align}
-where $h_k:= Z_1(T^{\alpha}_k f)-\langle  Z_1(T^{\alpha}_k f),\varphi\rangle$.
-According to \cite[Lemma 2.8]{MM}, there exists $C>0$ and $n\in\mathbb{N}$, such that for any $k\geq 0$, $x\in \mathbb{R}^d$ and $s\geq 0$,
- \begin{align}
- \label{eq:31step2}
-     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa_fb)(1+\beta)k}C(1+|x|)^n.
- \end{align}
+    J_2(t,k,\epsilon)
+    \leq C \exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big),
+    \quad k\geq 0, t\geq k+1, \epsilon >0.
+\end{align}
+    In fact, according to the definition of $Z_1$ and $m_t$ we have
+    \begin{align}
+          &\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]
+          \\&= \theta_{t,k}^{1+\beta} \langle Z_1T_k^{\alpha}f,X_{t-k-1}\rangle - e^{-\alpha k}\langle  Z_1T_k^{\alpha}f,\varphi\rangle
+          \\&=e^{-\alpha k}\Big(\frac{\langle Z_1T_k^{\alpha}f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1T_k^{\alpha}f ,\varphi\rangle\Big),
+          \quad k\in \mathbb Z_+, t\geq k+1.
+    \end{align}
+Therefore,
+\begin{align}
+\label{eq: prevJ2}
+&J_2(k,t,\epsilon)
+	\\&= \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]
+    \\&=e^{-\alpha k}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1T^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1T^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
+    &\leq \|\mu\|^{-1} e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
+    \\&\qquad\qquad k\in \mathbb Z_+, t\geq k+1, \epsilon > 0,
+\end{align}
+where 
+\[ 
+g_k
+	:= \frac{Z_1 T^{\alpha}_k f-\langle  Z_1T^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)k}},
+	\quad k \in \mathbb Z_+.
+\]
+According to \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$, such that
+\[
+     |T_t g_k|\leq e^{-bt}h,
+     \quad k\geq 0,t\geq 0.
+\]
+ 	This implies that,
+ \[
+ 	Q_1 (\operatorname{Re} g_k) \leq h
+ 	\text{ and } Q_1 (\operatorname{Im} g_k)\leq h,
+ 	\quad k \geq 0.
+ \]
+	Recall that $\gamma\in(0,\beta)$ is chosen small enough such that $\alpha \gamma < b < (1+\gamma)b$. 
+	According to Lemma \ref{lem: control moment} (3) (with $\kappa$ being $1$), there exist $C>0$ such that
+\begin{align}
+    &\mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t}\rangle\right|\right]
+    \leq \|\langle \operatorname{Re} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}}
+    \\& \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma}
+    \\&\leq C e^{\frac{\alpha t}{1+\gamma}},\quad k \in \mathbb Z_+, t\geq 0.
+\end{align}
+Therefore, according to \eqref{eq: prevJ2}, we have
+\begin{align}
+	&J_2(k,t,\epsilon)
+	\leq  \|\mu\|^{-1}e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
+	\\&\leq \|\mu\|^{-1}C e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)}
+	\\&= \|\mu\|^{-1}C e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
+	\\&\leq \|\mu\|^{-1}C e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}, \quad k \in \mathbb Z_+, t\geq k+1, \epsilon > 0,
+\end{align}
+	as desired.
+
+	Step 4. We will show that for each $\epsilon\leq \alpha$ there exist $C,\delta>0$ such that 
+\begin{align}\label{ineq: control of J3}
+    J_3(k,t,\epsilon)\leq Ce^{-\delta (t-k-1)}\quad k\geq0, t\geq k+1.
+\end{align}
+	In fact, we have
+\begin{align}
+	&\mathbb P_{\mu}(A_{t}(\epsilon), D) = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)] 
+	\\&= \mathbb P_\mu[e^{-\alpha^*\|X_t\|};A_t(\epsilon)]
+	\leq \exp({-\alpha^* e^{(\alpha - \epsilon)t}}),\quad t\geq 0, \epsilon >0,
+\end{align}
+	and, according to Lemma \ref{lem: control of XT}, there is a constant $C>0$ such that
+\begin{align}
+	\mathbb P_\mu(A_t(\epsilon)^c,D^c) = \mathbb P_\mu(D^c) \tilde{\mathbb P}_\mu(\|X_t\|\leq e^{(\alpha - \epsilon) t}) \leq \mathbb P_\mu(D^c)C e^{-\epsilon \beta t},\quad t\geq 0, \epsilon >0.
+\end{align}
+	Combine those we get the desired result in step 4.
+
+	Final step, combine the result in Step 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ convergence to $0$ exponentially fast while $t\rightarrow\infty$. 
+	This gives the desired result.
+\end{proof}
+}
+	It turns out that we need to evaluate the previous Lemma into the following:
 \added{
-Thus $\frac{h_k}{C_{h_k}} \in \mathcal{P}_{1}$ with $C_{h_k}=e^{(\alpha-\kappa_f)(1+\beta)k}$ (Actually, we rewrite $h_k(x)=\text{Re}~h_k(x)+i \text{Im} ~h_k(x)$ and $\frac{\text{Re}~h_k}{C_{h_k}},\frac{\text{Im}~h_k}{C_{h_k}}\in \mathcal{P}_1$).
-Recall that $\gamma_0\in(0,\beta)$ and $p=\min\{\frac{b}{2},\frac{\alpha\gamma_0}{1+\gamma_0}\}$, according to Lemma \ref{lem: control moment}, there exist $C>0$,
-\begin{align}
-    &\mathbb{P}_{\mu}\left[\left|\langle h_k,X_{t-k-1}\rangle\right|\right]\leq \|\langle h_k, X_{t-k-1}\rangle\|_{\mathbb{P}_{\mu,1+\gamma_0}}\\
-    &\leq C e^{(\alpha-\kappa_fb)(1+\beta)k}
-    \begin{cases}
-    e^{(\alpha-b)(t-k-1)}\quad &\alpha\gamma_0>(1+\gamma_0)b\\
-    (t-k-1)e^{(\alpha-b)(t-k-1)}\quad &\alpha\gamma_0=(1+\gamma_0)b\\
-    e^{(\alpha-\frac{\alpha\gamma_0}{1+\gamma_0})(t-k-1)}\quad &\alpha\gamma_0<(1+\gamma_0)b\\
-    \end{cases}
-    \\& \leq C^{'}e^{(\alpha-\kappa_f b)(1+\beta)k}e^{(\alpha-p)(t-k-1)}, \quad k\geq 0, t\geq k+1.
-\end{align}
+\begin{cor}\label{cor: used in next corollary}
+Let $f\in \mathcal{P}$ and $\Theta >0$.
+Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
+Then there exist $C>0$ and $\delta>0$ such that for each $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
+\begin{align}
+    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]\leq Ce^{-\delta(t-k-1)}.
+\end{align}
+\end{cor}
+\begin{proof}
+	Define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as $J_1, J_2$ and $J_3$ in \eqref{eq: Def of Ji}.
+	Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal P$.
+    According to \eqref{eq: inequality that will used later} we have
+\begin{align}
+    &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+    \\&\leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon),
+    \quad \theta\in \mathbb R, k\geq 0, t\geq k+1, \epsilon> 0.
+\end{align}
+	According to \eqref{eq: estimate of J1}, we have
+\begin{align}
+	J^{\theta f}_1(k,t,\epsilon)
+     & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQ (\theta f), \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\}
+     \\& = |\theta|^{1+2\beta} \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
+     \\ &\qquad \theta \in \mathbb R^d, k\geq 0, t\geq k+1, \epsilon > 0,
+\end{align}
+	where $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6).
+	From the definition of $Z_1$ and $m_t$ we can verify that
+\[
+	Z_1( \pm \theta g) = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[g],\quad g\in \mathcal P, \theta \geq 0, t\geq 0. 
+\]
+	Therefore, we have
+\[
+J^{\pm \theta f}_2(t,k,\epsilon)
+	:= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon), \quad \theta >0, k \geq 0, t\geq k+1, \epsilon > 0.
+\]
+	According to this and the Step 3 in the proof of the previous Lemma, we have that there exists a constant $C > 0$ such that
+\begin{align}
+\label{eq:31step3}
+    J^{\theta f}_2(t,k,\epsilon)
+    \leq C |\theta|^{1+\beta}\exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big),
+    \quad \theta \in \mathbb R, k\geq 0, t\geq k+1, \epsilon >0.
+\end{align}
+	Finally, according to those estimation of $J^{\theta f}_{i}, i = 1,2$ and the estimation of $J_3$ in the Step 4 of the proof of the previous Lemma, we get the desired result by chosing $\epsilon$ small enough.
+\end{proof}
 }
-Therefore, for each $\theta>0$, $ k\geq 0$ and $t\geq k+1$, we have
-\begin{align}
-J_2(\theta,k,t)\leq C^{'} |\theta|^{1+\beta}e^{(\alpha\beta-\kappa_fb(1+\beta))k}e^{-(p-\epsilon_0)(t-k-1)} \leq C^{'} |\theta|^{1+\beta}e^{-\frac{p}{2}(t-k-1)}.
-\end{align}
-When $\theta\leq 0$, we obtain the inequality the same way as above but replacing $f$ by $-f$.
-
-Step 3, As $\epsilon_0\leq \alpha$, according to Lemma \ref{lem: control of A&D}, for any $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that 
-\begin{align}\label{ineq: control of J3}
-    J_3(k,t)\leq 2Ce^{-\delta (t-k-1)}\quad k\geq0, t\geq k+1.
-\end{align}
-At last, combine \eqref{lemma31q}, \eqref{eq:31step3} and \eqref{ineq: control of J3}, let $t\rightarrow\infty$, we get the result.
-\end{proof}
-
-\begin{cor}\label{cor: used in next corollary}
-Under condition in Lemma \ref{lem: mainlemma}, for each $\theta\in \mathbb{R}$ satisfying $|\theta|<\Theta$, there exist $C,\delta>0$ such for any $k\geq0$ and $t\geq k+1$,
-\begin{align}
-    \mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\big[\big(\exp{(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{D^c}\big|\mathscr{F}_{t-k-1}\big]\Big|\Big]\leq Ce^{-\delta(t-k-1)}.
-\end{align}
-\end{cor}
-\begin{proof}
-    Conclusion implied by  \eqref{ineq: used in next corollary}-\eqref{ineq: control of J3} and the condition $|\theta|\leq \Theta$.
-\end{proof}
-\begin{cor}\label{corollary31}
-Let $f\in \mathcal{P}$ and $\Theta>0$, assume that $\alpha\beta\leq\kappa_fb(1+\beta)$.
-There exists $C,\delta>0$ such that for any $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
+\begin{prop}\label{corollary31}
+Let $f\in \mathcal{P}$ and $\Theta>0$.
+Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$.
+Then there exists $C,\delta>0$ such that for any $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
 \begin{align}
 \label{32corollary}
-    \left|\mathbb{\tilde{P}}_{\mu}\left(\prod_{k=0}^n\exp(i\theta_k \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}})-\prod_{k=0}^n\exp(e^{\alpha}m_k[\theta_k f])\right)\right|\leq C e^{-\delta(t-n)}
-\end{align}
-\end{cor}
-\begin{proof}
-    Denote $\gamma_{t,k}=\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}} $. For $k\in\{-1,...,n\}$, we define
-    $$\varphi^k_t(\theta_0,...,\theta_n):=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),\quad |\theta_l|\leq \Theta,$$
-     where by convention the product is $1$ for $l=-1$. Then Conditioning with $\mathscr{F}_{t-k-1}$ we get
-    \begin{align*}
-        &\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)
-        %\\&=\prod_{l=0}^{k-1}\exp(e^{\alpha}m_l[\theta_l %f])\mathbb{\tilde{P}}_{\mu}\Big[\prod_{l=k}^{n}\exp(i\theta_{l}\gamma_{t,l})-\exp(e^{\alpha}m_k[\theta_k %f])\prod_{l=k+1}^n\exp(i\theta_{l}\gamma_{t,l})\Big]
-        \\&=\frac{1}{\mathbb{P}_{\mu}(D^c)}\prod_{l=0}^{k-1}\exp(e^{\alpha}m_l[\theta_l f])\mathbb{P}_{\mu}\Big[\Big(\prod_{l=k}^{n}\exp(i\theta_{l}\gamma_{t,l})-\exp(e^{\alpha}m_k[\theta_k f])\prod_{l=k+1}^n\exp(i\theta_{l}\gamma_{t,l})\Big)\mathbf{1}_{D^c}\Big]
-        \\&=\frac{1}{\mathbb{P}_{\mu}(D^c)}\prod_{l=0}^{k-1}\exp(e^{\alpha}m_l[\theta_l f])\mathbb{P}_{\mu}\Big[\prod_{l=k+1}^{n}\exp(i\theta_{l}\gamma_{t,l})\mathbb{P}_{\mu}\big[\big(\exp(i\theta_k\gamma_{t,k})-\exp(e^{\alpha}m_k[\theta_k f])\big)\mathbf{1}_{D^c}\big|\mathscr{F}_{t-k-1}\big]\Big]
-    \end{align*}
-    According to  the element inequality $|e^{iz}|\leq 1$, Lemma \ref{lem: charactreisticfunction} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$, $t>n$ and $|\theta_l|\leq \Theta,~l=1,...,n$, we have
-    \begin{align*}
-        &\left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right| 
-        \\&\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\Big|\mathbb{P}_{\mu}\big[\big(\exp(i\theta_k\gamma_{t,k})-\exp(e^{\alpha}m_k[\theta_k f])\big)\mathbf{1}_{D^c}\big|\mathscr{F}_{t-k-1}\big]\Big|\Big]
+    \Big|\mathbb{\tilde{P}}_{\mu}\Big[\prod_{k=0}^n\exp\Big(i\theta_k \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}}\Big)-\prod_{k=0}^n\exp(e^{\alpha}m_k[\theta_k f])\Big]\Big|\leq C e^{-\delta(t-n)}.
+\end{align}
+\end{prop}
+\begin{proof}
+	Let $C,\delta > 0$ be the constant in Corollary \ref{cor: used in next corollary}.
+    Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \] 
+    Fix $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$.
+    For each $k\in\{-1,...,n\}$, we define
+    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big).\]
+     where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
+    \begin{align*}
+        &a_{k-1} - a_k
+        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
+        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big]
+    \end{align*}
+    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$, we have
+    \begin{align*}
+        &|a_{k-1}- a_k| 
+        \\&\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
         \\& \leq C e^{-\delta(t-k-1)}.
     \end{align*}
-    \begin{comment}
-
-    Step 1, we will prove that there exists $C,\delta>0$ such that for any $|\theta|<\Theta$ and $k\in \{0,...,\lfloor t\rfloor\}$,
-    \begin{align}
-    \label{eq:32step1}
-        \mathbb{\tilde{P}}_{\mu}\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta f]}\right|\leq C e^{-\delta(t-k-1)}.
-    \end{align}
-
- By \eqref{lemma31q} and \eqref{eq:31step3}, we easily get, if $|\theta|\leq\Theta$ and $k\in\{0,...,\lfloor t\rfloor\}$,
-    \begin{align*}
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle  U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}\\
-        &\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+\beta} e^{-\frac{p}{2}(t-k-1)}.
-    \end{align*}
- Define
-\begin{align*}
-    \mathcal{B}_{t-k-1}:=\left\{\left|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq\frac{C}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+2\beta} e^{-\frac{\alpha\beta}{4(1+\beta)}(t-k-1)}\right\}.
-\end{align*}
-Applying Markov's inequality, we get $\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})\leq e^{-\frac{\alpha\beta}{4(1+\beta)}(t-k-1)}$. Similarly, define
-\begin{align*}
-    \mathcal{C}_{t-k-1}:=\left\{\left|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\Theta|^{1+\beta} e^{-\frac{p}{4}(t-k-1)}\right\},
-\end{align*}
- which satisfies  $\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1})\leq e^{-\frac{p}{4}(t-k-1)}$.
-
-Hence, for any $k\in\{0,...,\lfloor t\rfloor\}$, on the event $\mathcal{A}_{t-k-1}(\epsilon_0)\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1}$, we get
-\begin{align*}
-   &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta f]}\right|\\
-   &\leq \left|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\right|
-   +\left|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\right|\\
-   &\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}(|\Theta|^{1+2\beta}+|\Theta|^{1+\beta}) e^{-\min\{\frac{\alpha\beta}{4(1+\beta)},\frac{p}{4}\}(t-k-1)}.
-\end{align*}
-On the event $(\mathcal{A}_{t-k-1}(\epsilon_0)\cap\mathcal{B}_{t-k-1}\cap\mathcal{C}_{t-k-1})^c$, we get
-\begin{align*}
-    &\left|\mathbb{\tilde{P}}_{\mu}\left(e^{i\theta \gamma_{t,k}}|\mathscr{F}_{t-k-1}\right)-e^{e^{\alpha}m_k[\theta f]}\right|\\
-    &\leq 2(\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1}(\epsilon_0))+\mathbb{\tilde{P}}_{\mu}(\mathcal{B}^c_{t-k-1})+\mathbb{\tilde{P}}_{\mu}(\mathcal{C}^c_{t-k-1}))\\
-    &\leq 6e^{-\min\{\delta_1,\frac{\alpha\beta}{2(1+\beta)},\frac{p}{4}\}(t-k-1)}.
-\end{align*}
-\end{comment}
 Therefore, 
 \begin{align}
-    \text{LHS of \eqref{32corollary}}= &\left|\varphi^{-1}_t(\theta_0,...,\theta_n)-\varphi^{n}_t(\theta_0,...,\theta_n)\right|
-    \\&\leq\sum_{k=0}^n\left|\varphi^{k-1}_t(\theta_0,...,\theta_n)-\varphi^{k}_t(\theta_0,...,\theta_n)\right|
-    \\&\leq \sum_{k=0}^n C e^{-\delta(t-k-1)}.
-\end{align}
-
-Thus, we complete our proof.
-\end{proof}
-
+    \text{LHS of \eqref{32corollary}}&= \left|a_{-1}-a_n\right|
+    \leq\sum_{k=0}^n\left|a_{k-1}-a_k\right|
+    \leq \sum_{k=0}^n C e^{-\delta(t-k-1)}.
+\end{align}
+	Recall that $C, \delta>0$ are independent of the choice of $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ with $|\theta_i|\leq \Theta$.
+\end{proof}
 \subsection{Proof of Theorem \ref{Theorem12}}
 
-    For any $f\in\mathcal{P}$, we write
-    \begin{align*}
-        (t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{I_0^{t-\lfloor t \rfloor}[\langle f ,X_t\rangle]}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\\
-        &:=I_1(t)+I_2(t)+I_3(t).
+    Fix a $f\in\mathcal{P}$. Write
+    \begin{align*}
+        (t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle
+        &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\\
+        &:=I_1(t)+I_2(t)+I_3(t), \quad t\geq 1.
     \end{align*}
     Denote
-    $$\tilde{I}_1(t):=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
-    Fix $\theta\in \mathbb{R}$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get
-    \begin{align*}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}-\exp\left(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\right)\right|\leq C \frac{1}{t^{\delta}},
-    \end{align*}
-    for some $C,\delta>0$. According to \eqref{para: critical case}, we obtain that $\tilde{I}_1(t)\xrightarrow{d}\eta_1$ as $t\rightarrow \infty$.
-    Therefore, to end this proof, we just to prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\rightarrow 0$ and $I_i(t)\xrightarrow{d} 0,~i=2,3$.
-
-    Step 1, Fix $\mu\in \mathcal{M}_c(\mathbb{R}^d)$ and $\theta\in \mathbb R$, we show that
-    \begin{align}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\rightarrow 0,\quad t\rightarrow \infty.
+    $$\tilde{I}_1(t):=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}, \quad t\geq 1.$$
+    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb{R}$.
+Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we have that there exists $C,\delta>0$ such that for each $t > 1$,
+    \begin{align*}
+        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}-\exp\left(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\right)\right|\leq C \frac{1}{t^{\delta}}.
+    \end{align*}
+    According to \eqref{para: critical case}, we obtain that $\tilde{I}_1(t)\xrightarrow{d}\eta_1$ as $t\rightarrow \infty$.
+    Therefore, to end this proof, we just need to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\rightarrow 0$ and $I_i(t)\xrightarrow{d} 0,~i=2,3$.
+
+    Step 1. We will show that
+    \begin{align}
+        |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\rightarrow 0,\quad t\rightarrow \infty.
     \end{align}
@@
     \begin{align*}
-        Y_{t,k}:=\exp\left(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
-    \end{align*}
-
-    Using the element inequality: for $x_i,y_i \in \mathbb{C}$ with $|x_i|,|y_i|\leq 1$, $|\prod x_i-\prod y_i|\leq\sum |x_i-y_i|$ , we get
+        Y_{t,k}:=\exp\left(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
+    \end{align*}
+    Using the elementary inequality: $|\prod_{i=1}^n x_i-\prod_{i=1}^n y_i|\leq\sum_{i=1}^n |x_i-y_i|$ for any $x_i,y_i \in \mathbb{C}$ with $|x_i|,|y_i|\leq 1$, we get
     \begin{align}\label{ineq: control of I1t}
@@
     \end{align*}
-    Then according to Lemma \ref{lem: control of Wt} and Lemma \ref{lem: control of AT}, there exist $C,\delta>0$, such that
+    Then according to Lemma \ref{lem: control of Wt} and Lemma \ref{lem: control of AT}, there exist $C,\delta>0$, such that (\added{\bf Zhenyao: I dont get this, why not use Lemma 2.5?})
     \begin{align*}
@@
     \begin{align}
-        \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}\Big[\big|I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]\big|\cdot\Big|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\Big]\\
+        \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}\Big[\big|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle\big|\cdot\Big|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\Big]\\
         \label{ineq: control of Ykt}
-        &=|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\Big[\big|I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]\big|\cdot\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\Big].
+        &=|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\Big[\big|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle\big|\cdot\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\Big].
     \end{align}
@@
     \begin{align*}
-        (\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(\|X_t\|)^{\frac{1}{1+\beta}}}+\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{(\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{I_0^{t-\lfloor t \rfloor}[\langle f ,X_t\rangle]}{(\|X_t\|)^{\frac{1}{1+\beta}}}\\
+        (\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(\|X_t\|)^{\frac{1}{1+\beta}}}+\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(\|X_t\|)^{\frac{1}{1+\beta}}}\\
         &:=I_1(t)+I_2(t)+I_3(t).
@@
  Denote
-    $$\tilde{I}_1(t):=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
+    $$\tilde{I}_1(t):=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
     Fix $\theta\in \mathbb{R}$. Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get
@@
     \begin{align*}
-        Y_{t,k}:=\exp\left(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{\left(\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
+        Y_{t,k}:=\exp\left(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\left(\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
     \end{align*}
@@
 \begin{align}
-    \|I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]\|\leq \|I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}\leq C e^{-qk}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}.
+    \|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle\|\leq \|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}\leq C e^{-qk}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}.
 \end{align}

### 2019-01-31 supCLT.tex
supCLT.tex: 1130

@@
 %---Contents-----------------------
+\begin{abstract}
+    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$.
+For each testing function $f$ with polynomial growth, denote by $\kappa_f$ the order of $f$ in term of the spectral decomposition of $f$ with respect to the mean semigroup of $X$.
+Conditioned on no-extinction, we establish some spatial central limit theorem for $\langle f, X_t \rangle$ under three different regimes: In the small branching case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ convergences weakly.
+In the critical branching case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ convergences weakly.
+In the large branching case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ convergences a.s and in $L^{1+\gamma}$, with $\gamma \in (0,\beta)$.
+\end{abstract}
 \section{Introduction}
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-\added{
     For each $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
@@
     Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
-}
+\begin{comment}
+
 	\deleted{
@@
 	}
+\end{comment}
 \subsection{}
@@
 	The random variable we are interested in is $Y:= \langle g,X_t\rangle$.
+\begin{comment}
+
 \deleted{	
@@
 }
-
+\end{comment}
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
@@
     We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$, for each $s\in \Lambda$.
+    \begin{comment}
+
 \deleted{
@@
 }
+\end{comment}
 	For two operators $A: \mathcal D_A \to \mathcal P^*$ and $B: \mathcal D_B \to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for each $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
@@
 \[
-    \mathbb P_\mu ( |I_0^t[\langle g,X_t\rangle]| > \lambda)
+    \mathbb P_\mu ( |\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)
     \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
@@
 \begin{align}
-    &\big|\mathbb P_\mu (|I_0^t[\langle g,X_t\rangle]| > \lambda)\big|
-    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta I_0^t[\langle g,X_t\rangle]}])d\theta\Big|
+    &\big|\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)\big|
+    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^t\langle g,X_t\rangle]})d\theta\Big|
     \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}|d\theta
@@
 \end{proof}
-\added{
+
 \begin{lem}\label{lem: temp}
@@
     \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle T_{t-s}^\alpha g, X_{s-r}\rangle - \langle T_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
-    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle T_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
+    = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle T_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
     \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
-    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
+    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
 	\\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
-    \\&= e^{(1+\beta)(t-s)(\alpha- \kappa b)} \mathbb P_\mu [ \langle Sh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
+    = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \mathbb P_\mu [ \langle Sh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
     \\& = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \langle T_r^\alpha Sh,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
@@
 \end{proof}
-}
-\added{
+
 \begin{lem}\label{lem: control of mgtrs}
@@
 	Fix $h \in \mathcal P$ and $\mu \in \mathcal M_c(\mathbb R^d)$. Let $C_0$ be the constant in the previous Lemma.
-    For each $\kappa \in \mathbb Z_+$, each $0\leq r\leq s\leq t$ with $s-r \leq 1$, each $g\in \mathcal P$ with $Q_k g \leq h$ and each $c>0$, we have
+    For each $\kappa \in \mathbb Z_+$, each $0\leq r\leq s\leq t$ with $s-r \leq 1$, each $g\in \mathcal P$ with $Q_{\kappa} g \leq h$ and each $c>0$, we have
 \begin{align}
@@
 \end{proof}
-}
-\added{
+
 \begin{lem}
@@
     \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| I_{t-k-1}^{t-k}[\langle g,X_t\rangle] \big\|_{\mathbb P_\mu;1+\gamma}+\big\| I_{0}^{t-\lfloor t \rfloor}[\langle g,X_t\rangle]  \big\|_{\mathbb P_\mu;1+\gamma}
+    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-k-1}^{t-k}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
     \\ &\leq C_0^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} k}
@@
 \end{proof}
-}
-\deleted{
-\begin{cor}\label{cor: control of moment}
-   For each $g\in\mathcal{P}$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
-    \[
-    \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
-    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_g b)}.
-    \]
-    Moreover,
-    \begin{itemize}
-    \item[(1)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa_g b)t}$ provided $\alpha\gamma > \kappa_g (1+\gamma)b$.
-    \item[(2)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa_g (1+\gamma)b$.
-    \item[(3)]
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa_g (1+\gamma)b$.
-\end{itemize}
-\end{cor}
-\begin{proof}
-    As $g\in\mathcal{P}$, $g\in\mathcal{P}_{\kappa_g}$. We get the detail result by taking $\kappa=\kappa_g$ in Lemma \ref{lem: control of mgtrs} and Lemma \ref{lem: control moment}.
-\end{proof}
-}
+
 \subsection{Martingales}
@@
      Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-   \added{ According to Corollary \ref{cor: control of moment}}, there exists a constant $C_0>0$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
+ According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C_0>0$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
     \begin{align}
@@
 \end{proof}
+\added{
 	Define $\mathcal{A}_t(\epsilon):=\{ \|X_t\|\in \|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\}$ where $\epsilon,t>0$.
@@
 \end{proof}
-\deleted{
-\begin{lem}\label{lem: control of A&D}
-For each $\mu\in \mathcal{M}_c(\mathbb{R}^d)$ and $0<\epsilon<\alpha$, there exist $C,\delta\geq 0$ such that for each $t>0$, we have $\mathbb{P}_{\mu}(\mathcal{A}_t(\epsilon)\Delta D^c)\leq Ce^{-\delta t}$.
-\end{lem}
-\begin{proof}
-    According to Lemma \ref{lem: control of AT}, we know
-    \begin{align}
-            \mathbb{P}_{\mu}(\mathcal{A}_t(\epsilon)^c\cap D^c)=\mathbb{P}_{\mu}(D^c)\mathbb{\tilde{P}}_{\mu}(\mathcal{A}_t(\epsilon)^c)\leq C\mathbb{P}_{\mu}(D^c)e^{-\beta \epsilon t}.
-    \end{align}
-    On the other hand,
-    \begin{align}
-        \mathbb{P}_{\mu}(\mathcal{A}_t(\epsilon)\cap D)=\mathbb{P}_{\mu}\big[\mathcal{A}_t(\epsilon)\mathbb{P}_{\mu}(D|\mathscr{F}_t)\big]=\mathbb{P}_{\mu}\big[\mathbf{1}_{\mathcal{A}_t(\epsilon)}e^{-\alpha^* \|X_t\|}\big]\leq \exp\big(e^{-\alpha^*\|\mu\|e^{(\alpha-\epsilon)t}}\big).
-    \end{align}
-\end{proof}
 }
@@
 \end{align}
-\deleted{
-    Note that $m_t[\theta f]$ can be rewritten as follows:
-\[
-    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 T_{1-s}^\alpha (-i\theta T_{s+t}^\alpha f)^{1+\beta}(x)~ds,
-    \quad \theta \in \mathbb R.
-\]
-    The following Lemma says that function $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-}
 \begin{lem}
@@
 \end{proof}
-\added{
+
 \begin{cor}
@@
  \end{lem}
-\added{
  \begin{proof}
@@
 \end{proof}
-}
+
 	It turns out that we need to evaluate the previous Lemma into the following:
-\added{
+
 \begin{cor}\label{cor: used in next corollary}
@@
 \end{proof}
-}
+
 \begin{prop}\label{corollary31}
@@
     \end{align*}
-    Then according to Lemma \ref{lem: control of Wt} and Lemma \ref{lem: control of AT}, there exist $C,\delta>0$, such that (\added{\bf Zhenyao: I dont get this, why not use Lemma 2.5?})
+    Let $C_1,C_2$ be the control constant in  Lemma \ref{lem: control of Wt} and Lemma \ref{lem: control of XT} respectively, by Chebyshev inequality,
+     there exist $C>0$, such that
+    \added{
     \begin{align*}
         \mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}|\geq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),\\
-        &\leq C e^{-\delta(t-k-1)}, \quad t>1, k\in \{0,...,\lfloor t-\ln t \rfloor\}.
-    \end{align*}
+        &\leq \frac{\|\mu\|}{\mathbb{P}_{\mu}(D^c)}e^{\frac{\alpha}{4}(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]+\mathbb{\tilde{P}}(H_{t-k-1}\leq\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)})
+        \\&\leq C_1  \frac{\|\mu\|}{\mathbb{P}_{\mu}(D^c)}e^{-\frac{\alpha}{4}(t-k-1)}+C_2\|\mu\|^{\beta}e^{-\frac{\alpha\beta}{32}(t-k-1)}
+        \\&\leq Ce^{-\frac{\alpha\beta}{32}(t-k-1)},\quad t>1, k\in \{0,...,\lfloor t-\ln t \rfloor\}.
+    \end{align*}
+    }
   Therefore, for each $t>1$ and $k\in \{0,...,\lfloor t-\ln t \rfloor\}$,
     \begin{align}
-        \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\big]\leq 2 C e^{-\delta(t-k-1)}.\label{thm121}
+        \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\big]\leq 2 C e^{-\frac{\alpha\beta}{32}(t-k-1)}.\label{thm121}
     \end{align}
@@
 \end{align}
- According to Corollary \ref{cor: control of moment}, \eqref{ineq: control of Ykt}, \eqref{ineq: control of Kkt} and the condition $\alpha\beta=\kappa_f(1+\beta)b$, for any $\gamma\in (0, \beta)$, there exists $C,C'>0$, such that for any  sufficiently large  $t$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$,
+ According to Lemma \ref{lem: control moment}, \eqref{ineq: control of Ykt}, \eqref{ineq: control of Kkt} and the condition $\alpha\beta=\kappa_f(1+\beta)b$, for any $\gamma\in (0, \beta)$, there exists $C,C'>0$, such that for any  sufficiently large  $t$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$,
 \begin{align}
     &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \leq C|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|I_{t-k-1}^{t-k}[\langle f,X_t\rangle]|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
-    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|I_{t-k-1}^{t-k}[\langle f,X_t\rangle]|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
+    \leq C|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
+    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
     \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
@@
     \end{align}
-On the event $\mathcal{E}_t$, according to Corollary \ref{cor: control of moment} and the element inequality $|e^{i z}-1|\leq |z|$, for each $\gamma\in (0,\beta)$, there exist $C,C'>0$, such that for any $t>0$ and $\theta \in \mathbb{R}$,
+On the event $\mathcal{E}_t$, according to Lemma \ref{lem: control moment} and the element inequality $|e^{i z}-1|\leq |z|$, for each $\gamma\in (0,\beta)$, there exist $C,C'>0$, such that for any $t>0$ and $\theta \in \mathbb{R}$,
 \begin{align*}
     &\left|\mathbb{\tilde{P}}_{\mu}\big[\big(e^{i\theta I_2(t)}-1\big)\mathbf{1}_{\mathcal{E}_t}\big]\right|
-    \leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}\mathbb{\tilde{P}}_{\mu}\big| I_{t-k-1}^{t-k}[\langle f,X_t\rangle]\big|.\\
+    \leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}\mathbb{\tilde{P}}_{\mu}\big| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\big|.\\
     &\leq C |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
@@
 \end{align}
-It suffices to show that $\lim_{t\rightarrow \infty}J_t=0$, $\mathbb{P}_{\mu}$ and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
+It suffices to show that $\lim_{t\rightarrow \infty}J_t=0$, $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
 
@@
 
-According to  Corollary \ref{cor: control of moment} and the fact $\kappa_{\tilde{f}}\geq \kappa_f+1$, for each $\gamma\in(0,\beta)$, there exists $C>0$ such that 
+According to  Lemma \ref{lem: control moment} and the fact $\kappa_{\tilde{f}}\geq \kappa_f+1$, for each $\gamma\in(0,\beta)$, there exists $C>0$ such that
 \begin{itemize}
@@
 \end{align*}
-     \item[3)] When $\alpha\gamma>\kappa_{\tilde{g}}(1+\gamma)b\geq (\kappa_f+1)(1+\gamma)b$
+     \item[3)] When $\alpha\gamma>\kappa_{\tilde{f}}(1+\gamma)b\geq (\kappa_f+1)(1+\gamma)b$
 \begin{align*}
@@
 
-According to Corollary \ref{cor: control of moment}, for any $0< \gamma <\beta$, let $q=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}>0$, there exists $C>0$ such that
+According to Lemma \ref{lem: control moment}, for any $0< \gamma <\beta$, let $q=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}>0$, there exists $C>0$ such that
 \begin{align}

### 2019-01-31 supCLT.tex
supCLT.tex: 1204
Dear Prof. Ren and Song,

Jianjie and I were working on the CLT for superprocesses with stable branching.
In this newest version, under the simplest setting ( super OU-process with simple stable branching), we were finally able to walk through every proofs and details. 
Please take a look.

Best,
Zhenyao

@@
 %%%----Versions-----------------------------
-% supCLT6.tex 2018/11/29 by Zhenyao
+% supCLT1204.tex 2018/12/04 by Zhenyao
+% supCLT1130.tex 2018/11/30 by Jianjie
+% supCLT1124.tex 2018/11/24 by Zhenyao
+% supCLT1115.tex 2018/11/15 by Jianjie
+% supCLT9.tex ......... by Zhenyao
+% supCLT8.tex ......... by Jianjie
+% supCLT7.tex ......... by Zhenyao
+% supCLT6.tex ......... by Jianjie
 % supCLT5.tex ......... by Zhenyao
@@
 %---The preamble----------------------
-\documentclass[12pt,oneside,english]{amsart}
-\usepackage[T1]{fontenc}
+\documentclass[12pt]{amsart}
 \usepackage[utf8]{inputenc}
@@
     where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
-    Define the \emph{Fenyman-Kac semigroup} by
+    Define 
 \begin{equation}\label{meansemigroup}
@@
 \end{equation}
-     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.
+     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
     For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
@@
 \end{equation}
-    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
-    For each $k \in \mathbb N_0$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
+    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
+    For each $k \in \mathbb Z_+$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
 \begin{equation}
     A_k
-    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
+    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
 \end{equation}
@@
     := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
-    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
+    \quad x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
 \end{equation}
@@
     =e^{-b|p|t}\phi_p(x),
-    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
-\end{equation}
-    Moreover, $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
+    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
+\end{equation}
+    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
     That is, for each $f\in L^2(\varphi)$,
@@
     \kappa_f
-    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb N_0^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
+    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
 \end{equation}
@@
     \mathcal{P}
-    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
 \end{equation}
@@
 	     \mathcal{P}_{\kappa}
-    :=\big \{f\in \mathcal{P}:\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ \sup_{t\geq0}e^{\kappa b t}|T_tf(x)|\leq C(1+|x|)^n\big\}.
+    :=\big \{f\in \mathcal{P}:\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ \sup_{t\geq0}e^{\kappa b t}|T_tf(x)|\leq C(1+|x|)^n\big\}.
 	\end{align}
@@
     For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
-    For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
-    (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
+    For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$ the value of the L\'evy exponent of infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
     From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ take values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
@@
 
-In this subsection, we will give the main results of this paper.
-In the remainder of this paper,whenever we deal with an initial configuration $\mu \in \mathcal{M}(\mathbb{R}^d)$, we are implicitly assuming that it has a compact support.
+In this subsection, we will give the main results of this paper. Let $\mu\in \mathcal M_c(\mathbb R_d)$ be a finite measure on $\mathbb R_d$ with compact support.
 \subsubsection{Large Branching Rate}
@@
      $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
-    for any $0<\gamma<\beta$.
-
-    Moreover, if $f$ is twice differentiable and $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
+    for any $0<\gamma<\beta$. Moreover, if $f$ is twice differentiable and $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
  \end{rem}
@@
 $$\phi(x)=\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).$$
-Denote by $D$ the extinction event of super process.
+Denote by $D$ the extinction event of the super OU-process.
 \begin{thm}\label{Theorem12}
-Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
 $$\frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
@@
 \section{Preliminaries}
-    In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
-	For each $0 \leq a \leq b <\infty$ and  random variable $Y$ with finite mean, define random variable
-$
-   	\mathcal I_a^b Y
-    := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
-$
-	Then we have an nature incremental decomposition of $Y$:
-\begin{align}
-    \mathcal I_0^t Y
-    = \sum_{k = 0}^{\lfloor t \rfloor - 1} \mathcal I_k^{k+1}Y + \mathcal I_{\lfloor t \rfloor}^t Y,
-    \quad t\geq 0.
-\end{align}
-	The random variable we are interested in is $Y:= \langle g,X_t\rangle$.
 \begin{comment}
@@
 \end{comment}
-    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
+
+    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
     We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
@@
     In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
-    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$, for each $s\in \Lambda$.
+    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that, for each $s\in \Lambda$, $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$.
     \begin{comment}
@@
     Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for each $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
-    The reason for considering $\gamma$-controllable operators is that they have good algebra properties:
+    One of the reason for considering $\gamma$-controllable operators is that they have good algebra properties:
 \begin{lem}
 \label{lem: property of controllable operators}
-    Let operators $(A_\lambda)_{\lambda\in \Lambda}$ be uniformly $\gamma$-controllable on $\mathcal D$ from some $\gamma \in \mathbb R$ and $\mathcal D\subset \mathcal P^*$:
+    Let operators $(A_\lambda)_{\lambda\in \Lambda}$ be uniformly $\gamma$-controllable on $\mathcal D \subset \mathcal P^*$:
 \begin{itemize}
@@
 \[
-    |\Psi_0 f(x)| = |f(x)^{1+\beta}| \leq C_{\ref{lem: Lip of power function}} |f(x)|^{1+\beta}.
+    |\Psi_0 f(x)| = |f(x)^{1+\beta}| = |f(x)|^{1+\beta}.
 \]
@@
     |\Psi_0(-U_t f) - \Psi_0(-iT_t^\alpha f) |
-    \leq  C_{\ref{lem: Lip of power function}} |U_u f-iT_u^{\alpha}f|(|U_u f|^{\beta}+|i T_u^{\alpha}f|^{\beta}).
+    \leq  (1+\beta) |U_u f-iT_u^{\alpha}f|(|U_u f|^{\beta}+|i T_u^{\alpha}f|^{\beta}).
 \]
@@
 Denote $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite measures on $\mathbb{R}^d$ with compact support.
+	For each $0 \leq a \leq b <\infty$ and  random variable $Y \in$ with finite mean, define random variable
+$
+   	\mathcal I_a^b Y
+    := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
+$
 \begin{lem}
@@
 
-\begin{lem}\label{lem: control of mgtrs}
+\begin{lem}
+\label{lem: control of mgtrs}
 	For each $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exist a constant $C > 0$, such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
@@
 \begin{align}
-    \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-k-1}^{t-k}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
-    \\ &\leq C_0^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} k}
+    &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+    \\ &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-k-1}^{t-k}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
+    + |\langle T^\alpha_t g,\mu\rangle|
+    \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} k} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle. 
 \end{align}
@@
 
-    Let $p=(p_1,...,p_d)\in \mathbb N_0^d$, recall that $\phi_p$ is one of the eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
+    Let $p=(p_1,...,p_d)\in \mathbb Z_+^d$, recall that $\phi_p$ is one of the eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
 $$H_t^p:=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.$$
@@
     \begin{align}
-        \mathbb{P}_{\mu}\left|H_s-H_r\right|^{1+\gamma}\leq  C_0 e^{-\alpha \gamma s}.
+        \mathbb{P}_{\mu}\big[|H_s-H_r|^{1+\gamma}\big]\leq  C_0 e^{-\alpha \gamma s}.
     \end{align}
@@
 	& \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}
-	\leq \|H_{\lfloor s \rfloor+1}-H_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H_{k+1}-H_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H_t-H_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
+	\\&\leq \|H_{\lfloor s \rfloor+1}-H_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H_{k+1}-H_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H_t-H_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
 	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
@@
 Write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
-\begin{lem}\label{lem: control of XT}
+\begin{lem}
+\label{lem: control of XT}
 	For each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for each function $f:[0,\infty)\to [1,\infty)$ and each $t\geq 0$ we have
@@
 \end{proof}
-\added{
-	Define $\mathcal{A}_t(\epsilon):=\{ \|X_t\|\in \|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\}$ where $\epsilon,t>0$.
-
-\begin{lem}\label{lem: control of AT}
-  For each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ there exists $C>0$ such that for each $t\geq 0$ we have
-  $
-  \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\beta\epsilon t}.
-  $
-\end{lem}
-
-\begin{proof}
-    First, for any $\epsilon>0$, using Markov inequality, we get for each $\epsilon>0$ and $t\geq 0$,
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})
-    \leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}
-	= \frac{\mathbb P_\mu[\|X_t\|\mathbf 1_{D^c}]}{\mathbb P_\mu(D^c)\|\mu\|e^{(\alpha+\epsilon)t}}
-    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.
-\end{align}
-
-    For another side, using Lemma \ref{lem: control of XT}, we have
-    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_0 e^{-\beta\epsilon t}, $$
-     for some constant $C_0>0$ not related to $\epsilon>0$ and $t\geq 0$.
-\end{proof}
-}
+
 \subsection{Parameters}
- Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}, define
- \begin{align}\label{parameter_mk}
-      m_t[f]:=e^{-\alpha (t+1)}\int_{\mathbb R^d} (Z_1T_t^{\alpha}f)(x)\varphi(x)dx,\quad t\geq 0, f\in \mathcal P.
+    Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}.
+    Define
+ \begin{align}
+ \label{parameter_mk}
+      m_t[f]
+      :=e^{-\alpha (t+1)}\int_{\mathbb R^d} (Z_1T_t^{\alpha}f)(x)\varphi(x)dx,\quad t\geq 0, f\in \mathcal P.
  \end{align}
@@
 \]
-
-    Let $f \in \mathcal{P}$.
-    Suppose that $\kappa_f\geq 1$ and $\alpha\beta=\kappa_f b(1+\beta)$.
-    Denote by
-\[
-    \phi(x)
-    =\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p(x),
-    \quad x\in \mathbb{R}^d, p \in\mathbb Z_+^d,
-\]
-    the projection of $f$ onto the $\kappa_f$-eigenspace.
-    Then accodting to \cite[Lemma 4.2]{MM} the following limit exists:
+    Accodting to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies that $\alpha\beta=\kappa_f b(1+\beta)$ then the following limit exists:
 \begin{align}
 \label{para: critical case}
-    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\Psi_0(-i\phi),\varphi\rangle.
-\end{align}
-
-    Let $f\in \mathcal{P}$.
-    Suppose that $\kappa_f\geq 1$ and $\alpha\beta<\kappa_fb(1+\beta)$. Then, according to \cite[Lemma 5.1]{MM}, the following series and integral absolutely convergence:
+    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\Psi_0(-i\phi),\varphi\rangle,
+\end{align}
+    where
+\[
+    \phi
+    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
+\]
+    According to \cite[Lemma 5.1]{MM}, if $f\in \mathcal{P}$ satisfies that $\alpha\beta<\kappa_fb(1+\beta)$, then we have that the following summation and integration are equal and absolutely convergence:
 \begin{align}
     m[f]
-    :=e^{-\alpha}\sum_{k=0}^\infty m_k[f]
-    =\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx. \label{msmallcase}
+    :=\sum_{k=0}^\infty m_k[f]
+    =\alpha e^{\alpha}\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx. \label{msmallcase}
 \end{align}
@@
 \label{cor: alpha stable rv}
-	For any $t\geq 0$ and $f\in \mathcal P$, function $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+	For each $t\geq 0$ and $f\in \mathcal P$, 
+\begin{enumerate}
+\item 
+\label{it: first stable}
+    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of an $(1+\beta)$-stable random variable.
+\item 
+\label{it: second stable}
+    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$.
+\item 
+\label{it: third stable}
+    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
+\end{enumerate}
 \end{cor}
 \begin{proof}
+    Proof of \eqref{it: first stable}: 
 	Fix $t\geq 0$ and $f\in \mathcal P$.
@@
 	Therefore \eqref{eq: what I want to proof} is true.
+
+    Proof of \eqref{it: second stable} and \eqref{it: third stable}: Similar to the proof of \eqref{it: first stable}.
 \end{proof}
@@
 \label{eq: Def of Ji}
-	\theta_{t,k}
-	&:= (e^{\alpha k}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}},
-	\\ J_1(t,k,\epsilon)
+	J_1(t,k,\epsilon)
 	&:= \mathbb{P}_{\mu}\big[|\langle U_1(\theta_{t,k}T_k^{\alpha}f)-\tilde U_1(\theta_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big]
@@
 	\\ J_3(t,k, \epsilon)
-	&:=2\mathbb{P}_{\mu}(A_{t-k-1}(\epsilon)\Delta D^c).
+	&:=2\mathbb{P}_{\mu}(A_{t-k-1}(\epsilon)\Delta D^c),
+	\\\theta_{t,k}
+	&:= (e^{\alpha k}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
 \end{align}
@@
      & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
-     \\ &\qquad k\geq 0, t\geq k+1, \epsilon > 0.
+     \\ &&\mathllap {k\geq 0, t\geq k+1, \epsilon > 0.}
 \end{align}
@@
     &\leq \|\mu\|^{-1} e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
-    \\&\qquad\qquad k\in \mathbb Z_+, t\geq k+1, \epsilon > 0,
+    \\& &\mathllap{k\in \mathbb Z_+, t\geq k+1, \epsilon > 0,}
 \end{align}
@@
 \[
-	Z_1( \pm \theta g) = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[g],\quad g\in \mathcal P, \theta \geq 0, t\geq 0.
+	Z_1( \pm \theta g) = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[\pm g],\quad g\in \mathcal P, \theta \geq 0, t\geq 0.
 \]
@@
 Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$.
-Then there exists $C,\delta>0$ such that for any $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
+Then there exists $C,\delta>0$ such that for any $T\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
 \begin{align}
@@
     For each $k\in\{-1,...,n\}$, we define
-    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big).\]
+    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big)\]
      where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
@@
 \subsection{Proof of Theorem \ref{Theorem12}}
-
-    Fix a $f\in\mathcal{P}$. Write
-    \begin{align*}
-        (t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle
-        &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\\
-        &:=I_1(t)+I_2(t)+I_3(t), \quad t\geq 1.
-    \end{align*}
-    Denote
-    $$\tilde{I}_1(t):=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}, \quad t\geq 1.$$
+\label{sec: proof of thm 1.3}
+    Fix an $f\in\mathcal{P}$. 
+    Chose a $t_0 > 0$ large enough such that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
+    Write
+    \begin{align*}
+        &(t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle
+        \\ &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big) + \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
+        \\&=:I_1(t)+I_2(t) + I_3(t), 
+        \quad t\geq t_0.
+    \end{align*}
+    Denote by
+\[
+    \tilde I_1(t)
+    :=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}, 
+    \quad t\geq t_0.
+\]
     Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb{R}$.
-Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we have that there exists $C,\delta>0$ such that for each $t > 1$,
-    \begin{align*}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}-\exp\left(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\right)\right|\leq C \frac{1}{t^{\delta}}.
-    \end{align*}
-    According to \eqref{para: critical case}, we obtain that $\tilde{I}_1(t)\xrightarrow{d}\eta_1$ as $t\rightarrow \infty$.
-    Therefore, to end this proof, we just need to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\rightarrow 0$ and $I_i(t)\xrightarrow{d} 0,~i=2,3$.
-
-    Step 1. We will show that
-    \begin{align}
-        |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\rightarrow 0,\quad t\rightarrow \infty.
-    \end{align}
-    Denote
-    \begin{align*}
-        Y_{t,k}:=\exp\left(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
-    \end{align*}
-    Using the elementary inequality: $|\prod_{i=1}^n x_i-\prod_{i=1}^n y_i|\leq\sum_{i=1}^n |x_i-y_i|$ for any $x_i,y_i \in \mathbb{C}$ with $|x_i|,|y_i|\leq 1$, we get
+Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we have that there exists $C,\delta>0$ such that,
+\begin{align*}
+        \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq C \frac{1}{t^{\delta}},
+        \quad t\geq t_0.
+\end{align*}
+    According to \eqref{para: critical case}, we obtain that $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\eta_1$ with respect to $\tilde {\mathbb P}_\mu$.
+    Therefore, we only need to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I_i(t)\xrightarrow[t\to \infty]{d} 0$ for $i = 2,3$ with respect to $\tilde {\mathbb P}_\mu$.
+
+    In order to show
+\begin{align}
+    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
+    \xrightarrow[t\to \infty]{} 0,
+\end{align}
+	we use \cite[Lemma 3.4.3.]{Durrett2010Probability} and get that
 \begin{align}\label{ineq: control of I1t}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}|Y_{t,k}|.
-    \end{align}
-    For $t>1$ and $k\in \{0,...,\lfloor t-\ln t \rfloor\}$, define
-    \begin{align*}
-        \mathcal{D}_{t,k}:=\left\{|H_t-H_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, H_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\}.
-    \end{align*}
-    Let $C_1,C_2$ be the control constant in  Lemma \ref{lem: control of Wt} and Lemma \ref{lem: control of XT} respectively, by Chebyshev inequality,
-     there exist $C>0$, such that
-    \added{
-    \begin{align*}
-        \mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}|\geq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),\\
-        &\leq \frac{\|\mu\|}{\mathbb{P}_{\mu}(D^c)}e^{\frac{\alpha}{4}(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]+\mathbb{\tilde{P}}(H_{t-k-1}\leq\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)})
-        \\&\leq C_1  \frac{\|\mu\|}{\mathbb{P}_{\mu}(D^c)}e^{-\frac{\alpha}{4}(t-k-1)}+C_2\|\mu\|^{\beta}e^{-\frac{\alpha\beta}{32}(t-k-1)}
-        \\&\leq Ce^{-\frac{\alpha\beta}{32}(t-k-1)},\quad t>1, k\in \{0,...,\lfloor t-\ln t \rfloor\}.
-    \end{align*}
-    }
-  Therefore, for each $t>1$ and $k\in \{0,...,\lfloor t-\ln t \rfloor\}$,
-    \begin{align}
-        \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\big]\leq 2 C e^{-\frac{\alpha\beta}{32}(t-k-1)}.\label{thm121}
-    \end{align}
-
-    Using the element inequality $|e^{ix}-e^{iy}|\leq|x-y|$,
-    \begin{align}
-        \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]&\leq|\theta|t^{-\frac{1}{1+\beta}}\mathbb{\tilde{P}}_{\mu}\Big[\big|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle\big|\cdot\Big|\frac{1}{\left(e^{\alpha(k+1)\|X_{t-k-1}\|}\right)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\Big]\\
-        \label{ineq: control of Ykt}
-        &=|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\Big[\big|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle\big|\cdot\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\Big].
-    \end{align}
-Denote
-$$K_{t,k}:=\left|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\right|\mathbf{1}_{\mathcal{D}_{t,k}}.\quad t>1, k\in \{0,...,\lfloor t-\ln t\rfloor\}.$$
- On the event $\mathcal{D}_{t,k}$, when $t$ is sufficiently large,
- \begin{align*}
-     H_t\geq H_{t-k-1}-\|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}&\geq\|\mu\|\left(e^{-\frac{\alpha}{32}(t-k-1)}-e^{-\frac{\alpha}{4}(t-k-1)}\right)\\
-     &\geq \|\mu\| e^{-\frac{\alpha}{16}(t-k-1)}.
- \end{align*}
- For sufficiently large $t$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$, we get
+    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]|
+    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\big],
+    \quad t\geq t_0,
+\end{align}
+    where
+\begin{align*}
+    Y_{t,k}
+    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big),
+    \quad k \geq 0 , t\geq k+1.
+\end{align*}
+    Define
+\begin{align}
+\label{def: Dtk}
+    \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, H_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\},
+    \\ &&\mathllap{ k\geq 0, t\geq k+1.}
+\end{align}
+
+    Step 1. We will show that there exists a $C>0$ such that,
+\begin{align}
+\label{thm121}
+    \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\big]
+    \leq C e^{-\frac{\alpha\beta}{32}(t-k-1)},
+    \quad k\geq 0, t\geq k+1.
+\end{align}
+    Fix a $\gamma \in (0,\beta)$.
+    Let $C_1$ be the constant in  Lemma \ref{lem: control of Wt} corresponding to this $\gamma_0$ and $C_2$ be the constant in Lemma \ref{lem: control of XT}. 
+    By Chebyshev inequality, there exist $C>0$, such that
+\begin{align}
+\label{eq: prob of Dtkc}
+    &\mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
+    \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}|\geq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),
+    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}\|\mu\|^{-1}e^{\frac{\alpha}{4}(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]+\mathbb{\tilde{P}}(H_{t-k-1}\leq\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)})
+    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1} \|\mu\|^{-1} e^{\frac{\alpha}{4}(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}+\mathbb{\tilde{P}}(H_{t-k-1}\leq\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)})
+    \\&\leq C_1  \mathbb{P}_{\mu}(D^c)^{-1} \|\mu\|^{-1} e^{-\frac{\alpha}{4}(t-k-1)}+C_2\|\mu\|^{\beta}e^{-\frac{\alpha\beta}{32}(t-k-1)}
+    \\&\leq Ce^{-\frac{\alpha\beta}{32}(t-k-1)},
+    \quad k\geq 0, t\geq k+1.
+\end{align}
+    This implies the desired result in Step 1.
+
+    Step 2. We will show that there exists constant $C > 0$ such that
+\begin{align}
+\label{thm122}
+     \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
+     \leq  C e^{-\frac{\alpha}{16}(t-k)}, \quad 0\leq k\leq t-\ln t, t\text{ large enough.}
+\end{align}
+    In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for each $x,y\in \mathbb R$, we have
+\begin{align}
+\label{eq: control of Ykt}
+        &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
+        \\&\leq|\theta|t^{-\frac{1}{1+\beta}} \mathbb{\tilde{P}}_{\mu}\bigg[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot\Big|\frac{1}{(e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\bigg]
+        \\&=|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
+        \quad k\geq 0, t\geq k+1,
+\end{align}
+    where
+\begin{equation}
+\label{def: Ktk}
+    K_{t,k}
+    :=\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}},
+    \quad k\geq 0, t\geq k+1.
+\end{equation}
+    Note that for each $0 < x< y$, we have
+\[
+    1-e^{-(y-x)t} 
+    \geq e^{-xt},
+    \quad t \text{ large enough,}
+\]
+    since the left side converges to $1$ and the right side converges to $0$.
+    Therefore, by taking $x= \frac{\alpha}{32}$ and $y= \frac{\alpha}{4}$, we have 
+\[
+    e^{-\frac{\alpha t}{32} } - e^{-\frac{\alpha t}{4}}
+    \geq e^{- \frac{\alpha t}{32}}(1 - e^{-(\frac{1}{4} - \frac{1}{32})\alpha t})
+    \geq e^{- \frac{\alpha t}{16}},
+    \quad t \text{ large enough.}
+\]
+    We can then verify that
+\begin{align*}
+    H_t
+    &\geq H_{t-k-1}-\|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}
+    \geq\|\mu\|\left(e^{-\frac{\alpha}{32}(t-k-1)}-e^{-\frac{\alpha}{4}(t-k-1)}\right)
+    \\&\geq \|\mu\| e^{-\frac{\alpha}{16}(t-k-1)},
+    \quad \text{ on } \mathcal D_{t,k}, 
+    \quad 0 \leq k \leq t - \ln t, t \text{ large enough}.
+\end{align*}
+    Therefore,
 \begin{align*}
@@
      &\leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
-    \\&\leq \frac{1}{1+\beta}\|\mu\|^{\frac{2+\beta}{1+\beta}} \max\left\{e^{\frac{\alpha}{16}(t-k-1)}, e^{\frac{\alpha}{32}(t-k-1)}\right\}e^{-\frac{\alpha}{4}(t-k-1)}\\
-    &\leq\frac{1}{1+\beta}\|\mu\|^{\frac{2+\beta}{1+\beta}}  e^{-\frac{3\alpha}{16}(t-k-1)}.
-\end{align*}
-Similarly, we easily get
-\begin{align*}
-    \left|H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}\right|\geq \|\mu\|^{\frac{2}{1+\beta}} e^{-\frac{3\alpha}{32}(t-k-1)}.
-\end{align*}
-Thus, for sufficiently large  $t$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$, there is a constant $C\geq 0$ such that
-\begin{align}\label{ineq: control of Kkt}
-     K_{t,k}\leq C e^{-\frac{3\alpha}{32}(t-k-1)}.
-\end{align}
- According to Lemma \ref{lem: control moment}, \eqref{ineq: control of Ykt}, \eqref{ineq: control of Kkt} and the condition $\alpha\beta=\kappa_f(1+\beta)b$, for any $\gamma\in (0, \beta)$, there exists $C,C'>0$, such that for any  sufficiently large  $t$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$,
-\begin{align}
+    \\&\leq \frac{1}{1+\beta}\|\mu\|^{\frac{1}{1+\beta}} \max\left\{e^{\frac{\alpha}{16}(t-k-1)}, e^{\frac{\alpha}{32}(t-k-1)}\right\}e^{-\frac{\alpha}{4}(t-k-1)}\\
+    &=\frac{1}{1+\beta}\|\mu\|^{\frac{1}{1+\beta}}  e^{-\frac{3\alpha}{16}(t-k-1)},
+    \\ && \mathllap{ \text{ on } \mathcal D_{t,k}, \quad 0 \leq k \leq t - \ln t, t \text{ large enouph,} }
+\end{align*}
+    and
+\begin{align*}
+    |H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}|
+    \geq \|\mu\|^{\frac{2}{1+\beta}} e^{-\frac{3\alpha}{32}(t-k-1)},
+    \\ && \mathllap{ \text{ on } \mathcal D_{t,k}, \quad 0 \leq k \leq t - \ln t, t \text{ large enouph.} }
+\end{align*}
+    Thus, there is a constant $C\geq 0$ such that 
+\begin{align}
+\label{ineq: control of Kkt}
+     K_{t,k}
+     \leq C e^{-\frac{3\alpha}{32}(t-k-1)},
+    \quad 0 \leq k \leq t - \ln t, t \text{ large enouph.} 
+\end{align}
+    Now fix a $\gamma \in (0, \beta)$ close enough to $\beta$ such that 
+\[
+    \frac{1}{1+\gamma} - \frac{1}{1+\beta} 
+    \leq \frac{1}{32}.
+\]
+    From the condition $\alpha\beta=\kappa_f(1+\beta)b$, we can verify that 
+\begin{align}
+    &\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}
+    = -\alpha(1-\frac{1}{1+\gamma}) + \alpha(1-\frac{1}{1+\beta})
+    \\&= -\frac{\gamma \alpha}{1+\gamma} + k_f b
+    =-\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
+\end{align}
+    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt}, \eqref{ineq: control of Kkt} and the above, there exists constants $C,C'>0$, such that
+\begin{align}
+\label{eq: Y in D}
     &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
@@
     \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
-    \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}\label{thm125}\\
-    &\leq C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}.\nonumber
-\end{align}
-The last inequality hold as $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}=-\frac{\alpha \gamma-\kappa
-_f(1+\gamma)b}{1+\gamma}$.
-Now we take $\gamma$ so close to $\beta$ such that $\frac{1}{1+\gamma}-\frac{1}{1+\beta}<\frac{1}{32}$, then
-\begin{align}
-     \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]\leq  C' e^{-\frac{\alpha}{16}(t-k)}.\label{thm122}
-\end{align}
-At last, combining\eqref{ineq: control of I1t}, \eqref{thm121} and \eqref{thm122}, we get, there exists $C,\delta>0$ such that
-$$\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\leq C t^{-\delta}, t ~\text{sufficiently large}.$$
-We complete step 1 by letting $t\rightarrow \infty$.
-
-Step 2. Fix $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, we will show that as $t\rightarrow \infty$, $I_2(t) \xrightarrow{d} 0$.
-
-Let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|t^{-1/2}e^{\alpha t}\}$. According to Lemma \ref{lem: control of XT}, there exists $C>0$
+    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-\frac{3\alpha}{32}(t-k)}
+    \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k)}\\&= C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}
+    \\&\leq C' e^{-\frac{\alpha}{16}(t-k)},
+    \quad 0\leq k\leq t-\ln t, t\text{ large enough,}
+\end{align}
+    as required in Step 2.
+
+    Step 3. We will show that there exists $C, \delta> 0$ such that
+\[
+    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
+    \leq C t^{-\delta}, 
+    \quad t \text{ large enough}.
+\]
+    In fact, according to \eqref{thm121} and \eqref{thm122}, there exists $C,\delta > 0$ such that
+\[
+    \tilde{\mathbb P}_\mu\big[|Y_{t,k}|\big] 
+    \leq C e^{-\delta(t-k)},
+    \quad 0\leq k\leq t-\ln t, t\text{ large enough.}
+\]
+    Therefore, there exists $C, \delta > 0$ and $C'$ such that 
+\begin{align}
+    &\sum_{k=0}^{\lfloor t-\ln t \rfloor} \tilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
+    \leq C\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{-\delta(t-k)}
+    = C e^{-\delta t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta k} 
+    \\&\leq C' e^{-\delta t}e^{\delta (t-\ln t)} 
+    = C'\frac{1}{t^{\delta}},
+    \quad t \text{ large enough,}
+\end{align}
+    as required in Step 3.
+
+    Step 4. We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$.
+    In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Lemma \ref{lem: control of XT}, there exists $C>0$ such that
 \begin{align}
@@
 \end{align}
-    Therefore, for any $t\geq 0$ and $\theta\in \mathbb{R}$,
+    Therefore, there exists $C>0$ such that
 \begin{align}\label{Theorem123}
-        \left|\mathbb{\tilde{P}}_{\mu}\big [\big(e^{i\theta I_2(t)}-1\big)\mathbf{1}_{\mathcal{E}^c_t}\big]\right|\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq 2Ct^{-\frac{\beta}{2}}.
-    \end{align}
-On the event $\mathcal{E}_t$, according to Lemma \ref{lem: control moment} and the element inequality $|e^{i z}-1|\leq |z|$, for each $\gamma\in (0,\beta)$, there exist $C,C'>0$, such that for any $t>0$ and $\theta \in \mathbb{R}$,
-\begin{align*}
-    &\left|\mathbb{\tilde{P}}_{\mu}\big[\big(e^{i\theta I_2(t)}-1\big)\mathbf{1}_{\mathcal{E}_t}\big]\right|
-    \leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}\mathbb{\tilde{P}}_{\mu}\big| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\big|.\\
-    &\leq C |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    &= C |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{(\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma})k}\\
-    &\leq C'|\theta|t^{-\frac{1}{2(1+\beta)}}t^{-\alpha(\frac{1}{1+\beta}-\frac{1}{1+\gamma})}.
-\end{align*}
- Take $\gamma$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})$ smaller than $\frac{1}{2(1+\beta)}$ and combine with \eqref{Theorem123}, we proved that $J_t \rightarrow^d 0$ as $t\rightarrow \infty$.
-
-Step 3. Fix $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, we will show that as $t\rightarrow \infty$, $I_3(t) \xrightarrow{d} 0$.
-
-Similar to the proof of Stop 2.
+    |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
+    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ct^{-\frac{\beta}{2}},
+    \quad t\geq t_0.
+\end{align}
+    Chose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})\leq \frac{1}{2(1+\beta)}$.
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that
+\begin{align*}
+    &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
+    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
+    \\&\leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
+    \\& \leq C |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
+    \\ &\leq C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    &= C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})k}\\
+    &\leq C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})j}\\
+    &\leq C''|\theta| t^{-\frac{1}{2(1+\beta)}}t^{(\frac{\alpha}{1+\gamma}- \frac{\alpha}{1+\beta})},
+    \quad t\geq t_0.
+\end{align*}
+	From this and \eqref{Theorem123}, we get the required result in Step 4.
+
+	Step 5. We will show that $I_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$. 
+	In fact, we can write
+\begin{align}
+	&|I_3(t)| 
+	\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
+	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(te^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
+	\\& = t^{-\frac{1}{1+\beta}} e^{\frac{\beta \alpha t}{1+\beta} - k_fbt} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
+	\\& = t^{-\frac{1}{1+\beta}} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
+	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
+\end{align}
+
+	Finally, according to Step 3,4 and 5, we complete the proof of Theorem \ref{Theorem12}.
 
 \subsection{Proof of Theorem \ref{Theorem11}}
-For any $f\in \mathcal{P}$, we rewrite
-\begin{align}
-    f=\sum_{|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p=\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f},
-\end{align}
-where $\tilde{f}=\sum_{|p|> \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p$. Therefore
+	%For any $f\in \mathcal{P}$, we rewrite
+	Fix a $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$.
+	Fix $\mu \in \mathcal M_c(\mathbb R^d)$.
+	Write
+\begin{align}
+    f
+    =\sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
+    %=
+    =:
+    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f}.
+\end{align}
+%	where $\tilde{f}=\sum_{|p|> \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p$. 
+	Therefore
 \begin{align*}
     &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
-    e^{-(\alpha-\kappa_fb)t}\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle.
-\end{align*}
-According to Lemma \ref{lemma26}, we easily get that,  for any $0< \gamma<\beta$,
-\begin{align}\label{as convergence}
-     e^{-(\alpha-\kappa_fb)t}\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle \rightarrow \sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,  \quad  t\rightarrow \infty,
-\end{align}
-$\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. Let
-\begin{align}
-    J_t=e^{-(\alpha-\kappa_fb)t}\langle \tilde{f},X_t\rangle.
-\end{align}
-It suffices to show that $\lim_{t\rightarrow \infty}J_t=0$, $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
-
-{\em Convergence in $L^{1+\gamma}(\mathbb{P}_{\mu})$}:
-
-According to  Lemma \ref{lem: control moment} and the fact $\kappa_{\tilde{f}}\geq \kappa_f+1$, for each $\gamma\in(0,\beta)$, there exists $C>0$ such that
-\begin{itemize}
-    \item [1)] When $\alpha\gamma>\kappa_{\tilde{f}}(1+\gamma)b$
-\begin{align*}
-    \|J_t\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-(\alpha-\kappa_fb)t}e^{(\alpha-\kappa_{\tilde{f}})bt}\leq C  e^{-(\alpha-\kappa_fb)t}e^{(\alpha-(\kappa_f+1)b)t}=C e^{-bt};
-\end{align*}
-     \item[2)] When $\alpha\gamma=\kappa_{\tilde{f}}(1+\gamma)b\geq (\kappa_f+1)(1+\gamma)b$
-\begin{align*}
-     \|J_t\|_{\mathbb{P}_{\mu};1+\gamma}\leq C t e^{-(\alpha-\kappa_fb)t}e^{\frac{\alpha}{1+\gamma}t}\leq C t e^{-bt}.
-\end{align*}
-     \item[3)] When $\alpha\gamma>\kappa_{\tilde{f}}(1+\gamma)b\geq (\kappa_f+1)(1+\gamma)b$
-\begin{align*}
-    \|J_t\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-(\alpha-\kappa_fb)t}e^{\frac{\alpha}{1+\gamma}t}\leq C e^{-bt}.
-\end{align*}
-\end{itemize}
-In conclusion, $\lim_{t\rightarrow \infty}\|J_t\|_{\mathbb{P}_{\mu};1+\gamma}=0$.
-
-{\em Almost sure convergence}: For each $a\in \mathbb{R}$ and $f\in \mathcal{P}$, let
-\begin{align}
-L_t^{f,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f,X_s\rangle ds \quad t\geq 0.
+    %e^{-(\alpha-\kappa_fb)t}\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle.
+    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle,
+    \quad t\geq 0.
+\end{align*}
+	According to Lemma \ref{lemma26}, 
+	%we easily get that,  for any $0< \gamma<\beta$,
+	we have
+\begin{align}
+\label{as convergence}
+     %e^{-(\alpha-\kappa_fb)t}\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle 
+     \sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p
+     %\rightarrow \sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,  \quad  t\rightarrow \infty,
+     \xrightarrow[t\to \infty]{} \sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
+\end{align}
+	in $\mathbb{P}_{\mu}$-a.s. and in $L_{1+\gamma}(\mathbb{P}_{\mu})$ with arbitrary $\gamma\in(0,\beta)$.
+%	$\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. 
+	Therefore, it is suffice to show that
+\begin{align}
+    J_t
+    :=e^{-(\alpha-\kappa_fb)t}\langle \tilde{f},X_t\rangle,
+    \quad t\geq 0,
+\end{align}
+	%It suffices to show that $\lim_{t\rightarrow \infty}J_t=0$, $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
+	convergence in $L_{1+\gamma}(\mathbb{P}_{\mu})$ with arbitrary $\gamma\in(0,\beta)$, and convergence a.s.ly provided $f\in C^2(\mathbb R^d)$.
+
+	Step 1. Let $g\in \mathcal P$. 
+	Let $a > 0$ satisfies that $a< \kappa_g$ and $a < \frac{\alpha \beta}{b(1+\beta)}$. 
+	We will show that for each $\gamma\in (0,\beta)$ there exists constants $C,\delta > 0$ such that
+\[
+	\|e^{-(\alpha - ab)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma} 
+	\leq C e^{-\delta t},
+	\quad t\geq 0.
+\] 
+	In order to do this, we choice a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, for each $\gamma \in [\gamma_0, \beta)$, we have $a < \frac{\alpha\gamma}{b(1+\gamma)}$.
+	Then, according to Lemma \ref{lem: control moment}, we verify that, for each $\gamma \in (0,\beta)$,
+\begin{enumerate}
+\item 
+	%When $\alpha\gamma>\kappa_{\tilde{f}}(1+\gamma)b$
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
+\[
+    \|e^{-(\alpha - ab)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+    \leq C e^{-(\alpha-ab)t}e^{(\alpha-\kappa_g b)t}
+    \leq C  e^{-(\kappa_g - a)bt},
+    \quad t\geq 0.
+\]
+\item 
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C>0$ such that
+\[
+     \|e^{-(\alpha - ab)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+     \leq C t e^{-(\alpha - a b)t}e^{\frac{\alpha}{1+\gamma}t}
+     = C t e^{-(\frac{\alpha \gamma}{1+\gamma} - ab)t},
+     \quad t\geq 0.
+\]
+\item 
+	%When $\alpha\gamma>\kappa_{\tilde{f}}(1+\gamma)b\geq (\kappa_f+1)(1+\gamma)b$
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
+\[
+    \|J_t\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C  e^{-(\alpha - a b)t}e^{\frac{\alpha}{1+\gamma}t}
+     = C  e^{-(\frac{\alpha \gamma}{1+\gamma} - ab)t},
+     \quad t\geq 0.
+\]
+\item
+	if $\gamma \in (0,\gamma_0)$ then, thanks to the above (1-3), and the fact that $\|J_t\|_{\mathbb{P}_{\mu};1+\gamma} 
+	\leq \|J_t\|_{\mathbb{P}_{\mu};1+\gamma_0}$, there exists $C, \delta >0$ such that
+\[
+	\|J_t\|_{\mathbb{P}_{\mu};1+\gamma} 
+	\leq Ce^{-\delta t},
+	\quad t\geq 0.
+\]
+\end{enumerate}
+	Thus, we get the desired conclusion in Step 1. 
+	In particular, by taking $g = \tilde f$ and $a = \kappa_f$, this implies that $J_t$ convergence to $0$ in $L_{1+\gamma}(\mathbb{P}_{\mu})$ with arbitrary $\gamma\in(0,\beta)$.
+
+	Step 2.
+	Further assume that $f\in C^2(\mathbb R^d)$, we will show that $J_t$ convergence to $0$ as surely.
+	Define
+\begin{align}
+	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,
+	\quad g\in \mathcal P\cap C^2(\mathbb R^d), a \geq 0, t\geq 0,
 \end{align}
@@
 \begin{align}
-    Y_t^{f,a}:=\int_0^t e^{-(\alpha-ab)s}|\langle Lf+abf,X_s\rangle|ds, \quad t\geq0.
-\end{align}
- Take $a=\kappa_{\tilde{f}}+\frac{1}{2}$ into the martingale defined in \eqref{defmartingale}, we easily get
-
-\begin{align*}
-    J_t=e^{-\frac{1}{2}bt} M_t^{\tilde{f},a}+e^{-\frac{1}{2}bt}L_t^{\tilde{f},a}.
-\end{align*}
-Equivalently, we just show that, as $t\rightarrow \infty$,
-\begin{align*}
-    e^{-\frac{1}{2}bt}M_t^{\tilde{f},a}\rightarrow 0, \quad e^{-\frac{1}{2}bt}L_t^{\tilde{f},a}\rightarrow 0 \quad \mathbb{P}_{\mu}\text{-a.s.}
-\end{align*}
-As $\kappa_{(L+ab)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1$, following the similar way to prove the case $L^{1+\gamma}(\mathbb{P}_{\mu})$-convergence, we get, for each $\gamma\in (0,\beta)$ there exists some $C, \delta>0$ such that for any $t\geq 0$,
-\begin{align}
-    \|e^{-(\alpha-ab)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-\delta t},\quad \|e^{-(\alpha-ab)t}\langle L\tilde{f}+ab\tilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-\delta t}.
-\end{align}
-Therefore, by triangle inequality, for any $t\geq 0$,
-\begin{align*}
-    \|L_t^{\tilde{f},a}\|_{\mathbb{P}_{\mu};1+\gamma}\leq\|Y_t^{\tilde{f},a}\|_{\mathbb{P}_{\mu};1+\gamma}\leq \int_0^t \|e^{-(\alpha-ab)s}\langle L\tilde{f}+ab\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
-\end{align*}
-Note that $Y_t^{\tilde{f},a}$ is positive increasing about $t$, we conclude that it converges to some random variable $Y_{\infty}^{\tilde{f},a}$ almost sure and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-Therefore,
-\begin{align*}
-    \lim_{t\rightarrow \infty}e^{-\frac{1}{2}bt}|L_t^{\tilde{f},a}|\leq  \lim_{t\rightarrow \infty}e^{-\frac{1}{2}bt}|Y_t^{\tilde{f},a}|=0.
+    Y_t^{g,a}
+    :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds, 
+    \quad g\in \mathcal P\cap C^2(\mathbb R^d), a \geq 0, t\geq 0.
+\end{align}
+	Now choice $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enouph to $\kappa_f$ such that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$. 
+	According to \eqref{defmartingale}, we have
+\begin{align*}
+    J_t
+    =e^{-(a_0-\kappa_f)bt} (M_t^{\tilde{f}, a_0}+L_t^{\tilde{f}, a_0}),
+    \quad t\geq 0.
+\end{align*}
+	So we only have to show that
+\begin{align*}
+    e^{-(a_0-\kappa_f)b t}M_t^{\tilde{f},a_0}
+    \xrightarrow[t\to \infty]{} 0, 
+    \quad e^{-(a_0-\kappa_f)b t}L_t^{\tilde{f},a_0}
+    \xrightarrow[t\to \infty]{} 0 
+    \quad \mathbb{P}_{\mu}\text{-a.s.}
+\end{align*}
+	Notice that $\kappa_{(L+a_0 b)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
+	So according to Step 1, for an arbitrary fixed $\gamma\in (0,\beta)$, there exists $C, \delta>0$ such that for each $t\geq 0$,
+\begin{align}
+    \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C e^{-\delta t},
+    \quad \|e^{-(\alpha-a_0 b)t}\langle L\tilde{f}+a_0 b\tilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C e^{-\delta t}.
+\end{align}
+	Now, by triangle inequality, for each $t\geq 0$,
+\begin{align*}
+    &\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq\|Y_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\tilde{f}+a_0 b\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
+\end{align*}
+	Noticing that $Y_t^{\tilde{f},a_0}$ is increasing with $t$, so it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+	As a consequence, as surely we have
+\begin{align*}
+    \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\tilde{f},a_0}|
+    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\tilde{f},a_0}|=0.
 \end{align*}
@@
 \begin{align*}
-    \|M_t^{\tilde{f},a}\|_{\mathbb{P}_{\mu};1+\gamma}\leq  \|e^{-(\alpha-ab)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),\quad t\geq 0.
-\end{align*}
-which implies that $\lim_{t\rightarrow\infty} e^{-\frac{1}{2}bt}M_t^{\tilde{f},a}=0$. we complete our proof.
+    \|M_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),\quad t\geq 0.
+\end{align*}
+	This implies that the martingale convergence as surely. 
+	As a consequence, 
+\[
+	\lim_{t\rightarrow\infty} e^{-(a_0-\kappa_f)bt}M_t^{\tilde{f},a}
+	=0,
+	\quad \mathbb P_\mu\text{-a.s.}
+\]
+
+	The proof is completed.
 \subsection{Proof of Theorem \ref{Theorem13}}
-The proof of Theorem \ref{Theorem13} is similar with that of Theorem \ref{Theorem12} or much easier.
-     For each $f\in \mathcal{P}$, we write
-    \begin{align*}
-        (\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(\|X_t\|)^{\frac{1}{1+\beta}}}+\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(\|X_t\|)^{\frac{1}{1+\beta}}}\\
-        &:=I_1(t)+I_2(t)+I_3(t).
-    \end{align*}
- Denote
-    $$\tilde{I}_1(t):=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}.$$
-    Fix $\theta\in \mathbb{R}$. Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get
-    \begin{align*}
-        \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}-\exp\left(\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\right)\right|\leq C \frac{1}{t^{\delta}},
-    \end{align*}
-    for some $C,\delta>0$. Hence, according to \eqref{msmallcase}, as $t\rightarrow \infty$, We obtain that $\tilde{I}_1(t)\xrightarrow{d}\eta_2$.
-
-    Therefore, to prove the theorem ,we just to prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\rightarrow 0$ and $I_i(t)\xrightarrow{d} 0,~i=1,2$.
-
-    We denote
-    \begin{align*}
-        Y_{t,k}:=\exp\left(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\right)-\exp\left(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\left(\|X_t\|\right)^{\frac{1}{1+\beta}}}\right).
-    \end{align*}
-With completely same method of Step 1 in the proof of Theorem \ref{Theorem12}, we can prove that, for each $\gamma\in (0,\beta)$, there exist $C,\delta>0$, such that for any $t\geq1$ and $k\in \{0,...,\lfloor t-\ln t\rfloor\}$,
-\begin{align*}
-    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k-1)}+ e^{-\delta(t-k-1)}).
-\end{align*}
-Moreover, on the case $\alpha\beta<\kappa_f(1+\beta)b$,  $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}< - \frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}$, therefore,
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}|Y_{t,k}|\leq C (e^{-\frac{3\alpha}{32}(t-k-1)}+e^{-\delta(t-k-1)}).
-\end{align}
-Then we can prove $\left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_1(t)}-\mathbb{\tilde{P}}_{\mu}e^{i\theta\tilde{I}_1(t)}\right|\rightarrow 0$, by following the lines of the proof in the critical case.
-
-To prove $I_2(t)\xrightarrow{d} 0$, We let $\mathcal{E}_t:=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon )t}\},~\epsilon>0$, instead. According to Lemma \ref{lem: control of AT}, there exists
-$C>0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal{E}_t^c)\leq C e^{-\epsilon \beta t},~t\geq 0$.
-
-According to Lemma \ref{lem: control moment}, for any $0< \gamma <\beta$, let $q=\frac{\alpha}{1+\beta}-\frac{\alpha}{1+\gamma} - \frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}>0$, there exists $C>0$ such that
-\begin{align}
-    \|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle\|\leq \|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}\leq C e^{-qk}e^{\frac{\alpha}{1+\gamma}(t-k)}e^{\frac{\alpha}{1+\beta}k}.
-\end{align}
-Then we get $  \left|\mathbb{\tilde{P}}_{\mu}e^{i\theta I_2(t)}-1\right|\rightarrow 0$ as $ t\rightarrow \infty$, by following the similar way in critical case.
-
-The method to prove $I_3(t)\xrightarrow{d}0$ is similar to that of $I_3(t)$.
+	Let $f\in \mathcal P$ satisfy that $\alpha \beta < \kappa_f b(1+\beta)$. 
+	Let $t_0 > 1$ be large enough such that 
+\[
+	\lceil t - \ln t\rceil 
+	\leq \lfloor t \rfloor - 1,
+	\quad t\geq t_0.
+\]
+	Write
+\begin{align*}
+	&\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+	\\&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+ \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big) + \frac{\langle P_t^\alpha f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+	\\&=:I'_1(t)+I'_2(t)+I'_3(t),
+	\quad t\geq t_0.
+\end{align*}
+	Define
+ \[
+ 	\tilde I'_1(t)
+ 	:=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
+ 	\quad t > t_0,
+ \]
+    Let $\theta\in \mathbb{R}$. 
+    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get that there exists $C,\delta > 0$ such that
+\begin{align*}
+    \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde I'_1(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|
+    \leq C e^{-\delta(t - \lfloor t - \ln t\rfloor)}
+    \leq C \frac{1}{t^{\delta}},
+    \quad t\geq 0.
+\end{align*}
+    Hence, according to \eqref{msmallcase}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \eta_2$ with respect to $\tilde {\mathbb P}_\mu$.
+    So we only have to prove that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3$ with respect to $\tilde {\mathbb P}_\mu$.
+
+    Step 1. We will show that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
+    Define
+\begin{align*}
+    Y'_{t,k}
+    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big),
+    \quad k\geq 0, t\geq k+1.
+\end{align*}
+	Then we have 
+\begin{align}
+\label{ineq: control of I1t}
+    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}] - \mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}'_1(t)}]|
+    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big],
+    \quad t\geq t_0,
+\end{align}
+	Let $\gamma\in (0,\beta)$ be close enouph to $\beta$ such that
+\[
+	\frac{1}{1+\gamma} - \frac{1}{1+\beta} \leq \frac{1}{32}.
+\]
+	Define $\mathcal D_{t,k}$ and $K_{t,k}$ using \eqref{def: Dtk} and \eqref{def: Ktk} respectively.
+	According to \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and the similar arguement in \eqref{eq: control of Ykt} we have that there exists $C,C'>0$ such that
+\begin{align*}
+    &\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
+    = \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}\big] + \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}^c \big]
+    \\& \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\tilde{P}}_{\mu}( \mathcal D_{t,k}^c )
+    \\& \leq C e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-\frac{3\alpha}{32}(t-k)} + Ce^{-\frac{\alpha \beta}{32}(t-k)}
+    \\& \leq C'( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)}),
+    \\&& \mathllap{\quad 0 \leq k \leq t - \ln t, t \text{ large enough}.}
+\end{align*}
+	Note that $\alpha\beta<\kappa_f(1+\beta)b$, so we have  
+\begin{align}
+\label{eq: condition for supercritical}
+	&-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})
+    = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta})
+    \\&> \frac{\gamma \alpha}{1+\gamma} - k_f b
+    =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
+\end{align}
+	Using this, we have that there exists $C > 0$ such that
+\begin{align*}
+    &\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
+    \\& \leq C( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)})
+    \\& \leq C( e^{-\frac{\alpha}{16}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)}),
+    \quad 0 \leq k \leq t - \ln t, t \text{ large enough}.
+\end{align*}
+	Then we can prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ using same arguement in the Step 3 in Section \ref{sec: proof of thm 1.3}.
+
+	Step 2. 
+	We will show that $I'_2(t)\xrightarrow[t\to \infty]{d} 0$. 
+	Let $\gamma \in (0,\beta)$.
+	According to \eqref{eq: condition for supercritical}, we can choice $\epsilon > 0$ small enough such that
+\[
+	q:= - \frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma} 
+	> \frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta} + \frac{2\epsilon}{1+\beta} > 0.
+\]
+	Let 
+\[
+	\mathcal E_t
+	:=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon )t}\},
+	\quad t\geq 0.
+\]
+	According to Lemma \ref{lem: control of XT}, there exists
+	$C>0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal E_t^c)\leq C e^{-\epsilon \beta t},~t\geq 0$.
+	Therefore, there exists $C>0$ such that
+\begin{align}
+    |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{\mathcal{E}^{c}_t}]|
+    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ce^{-\epsilon \beta t},
+    \quad t\geq t_0.
+\end{align}
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that
+\begin{align*}
+    &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
+    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
+    \\&\leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
+    \\& \leq C  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
+    \\ &\leq C'  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta} + \frac{2\epsilon}{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{qt} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-qk}\\
+    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\\
+    &\leq C'' e^{-\frac{\epsilon}{1+\beta} t} t^q,
+    \quad t\geq t_0.
+\end{align*}
+	Therefore, we get the required result in Step 2.
+
+	Step 3. We will show that $I'_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$. 
+	In fact, we can write
+\begin{align}
+	&|I'_3(t)| 
+	\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
+	\\& = e^{(\frac{\beta \alpha }{1+\beta} - k_fb)t} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
+	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
+\end{align}
+	The proof is compeleted.
 
@@
 \subsection{}
-    In this subsection, we present two analytic results which are useful.
+    In this subsection, we present some analytic fasts that will be useful.
 \begin{lem}
@@
     \Big|e^{-z} - \sum_{k=0}^n \frac{(-z)^k}{k!} \Big|
-    \leq \frac{|z|^{n+1}}{(n+1)!} \wedge \frac{2|z|^{n}}{n!}, \quad n\in \mathbb N_0.
+    \leq \frac{|z|^{n+1}}{(n+1)!} \wedge \frac{2|z|^{n}}{n!}, \quad n\in \mathbb Z_+.
 \end{equation}
@@
     So we have \eqref{eq: estimate of exponential remaining} is true when $n = 0$.
-    Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb N_0$.
+    Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb Z_+$.
     According to \cite[Theorem 7.20.]{Rudin1987Real},
@@
 \end{align}
-    Therefore, according to Fubini's theorem,
+    Therefore, according to Fubini's theorem and \cite[Theorem 7.20.]{Rudin1987Real},
 \begin{align}
@@
 
-\subsection{}
-	In this subsection, we give some analytical facts that will be used in this paper.
 	For each $z\in \mathbb C\setminus (-\infty,0]$ define
@@
     Fix a $\beta \in (0,1)$.
-    Using \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that
+    Using the uniqueness of holomorphic extension and \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that
 \begin{equation}
@@
 \end{align}
-    This indicates that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
+    This also verifies that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
 \begin{lem}
 \label{lem: Lip of power function}
-    There is a constant $C_{\ref{lem: Lip of power function}}$ such that for any $z_0,z_1 \in \mathbb C_+$,
+    There is a constant $(1+\beta)$ such that for any $z_0,z_1 \in \mathbb C_+$,
 \begin{equation}
@@
     |z_0^{1+\beta} - z_1^{1+\beta}|
-    \leq C_{\ref{lem: Lip of power function}}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
-\end{equation}
-    In particular, for each $z\in \mathbb C_+$, we have
-$
-    |z^{1+\beta}|
-    \leq  C_{\ref{lem: Lip of power function}} |z|^{1+\beta}.
-$
+    \leq (1+\beta)(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
+\end{equation}
 
@@
 \label{eq: upper bound for beta power of z}
-    &|z^{\beta}|
-    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big|
-    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
-    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
-    \quad z\in \mathbb C_+.
+	|z^\beta| 
+	= |e^{\beta \log |z| +i\beta \operatorname {arg}z}| = e^{\beta \log |z|} = |z|^\beta,
+	\quad z \in \mathbb C\setminus (-\infty, 0].
 \end{align}
@@
     &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
-    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
-    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
+    \leq (1+\beta)  \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
+    \\&\leq (1+\beta)  ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
     \qedhere
@@
 \end{proof}
+
+	Suppose that $\varphi(\theta)$ is a continuous function from $\mathbb R$ into $\mathbb C$ such that $\varphi(0) = 1$ and $\varphi(\theta) \neq 0$ for all $\theta \in \mathbb R$. 
+	Then according to \cite[Lemma 7.6]{Sato1999Levy}, there is a unique continuous function $f(\theta)$ from $\mathbb R$ into $\mathbb C$ such that $f(0) = 0$ and $e^{f(\theta)} = \varphi(\theta)$. 
+	Such function $f$ is called the distinguished logarithm of function $\varphi$ and is denoted as $\operatorname{Log} \varphi(\theta)$.
+	In particular, let $\varphi$ be the characteristic function of an infinitely divisible random variable $Y$, then $h$ is called the Levy exponent of $Y$. 
+	This distinguished logarithm should not be confused with the $\log$ function defined on $\mathbb C\setminus (-\infty, 0]$.
 
@@
 \end{align}
-    Therefore, from the Markov property of $\xi$, \eqref{eq: crucial for Feynman-Kac}, Fubini's theorem and above, we can verify that
+    Therefore, from the Markov property of $\xi$ and Fubini's theorem we can verify that
 \begin{align}
@@
 \subsection{}
-\label{sec: definition of characteristic exponent}
-    According to Levy-Khintchine formula \cite[Theorem 8.1]{Sato1999Levy}, an $\mathbb R$-valued random variable $\{Y; P\}$ is infinitely divisible if and only if
-\begin{equation}
-\label{eq: characteristic function of an infinitely divisible random variable}
-    P[e^{i\theta Y}]
-    = \exp\Big( ia \theta - \frac{1}{2}\sigma^2 \theta^2 + \int_{\mathbb R}(e^{i\theta x} - 1 - i \theta x\mathbf 1_{|x|< 1}) \nu(dx)\Big),
-    \quad \theta \in \mathbb R,
-\end{equation}
-    where $a\in \mathbb R$, $\sigma \in \mathbb R$ and $\nu$ is a measure on $\mathbb R\setminus\{0\}$ with $\int_{\mathbb R}(1\wedge x^2) \nu(dx)< \infty$.
-    Suppose that $\{Y;P\}$ is an infinitely divisible random variable with characteristic function \eqref{eq: characteristic function of an infinitely divisible random variable}, then
-\begin{equation}
-\label{eq: Characteristic exponent}
-    h(\theta)
-    := ia \theta - \frac{1}{2}\sigma^2 \theta^2 + \int_{\mathbb R}(e^{i\theta x} - 1 - i \theta x\mathbf 1_{|x|< 1}) \nu(dx),
-    \quad \theta \in \mathbb R,
-\end{equation}
-    is a continuous function.
-    %In fact, for any compact $K \subset \mathbb R$, since due to Lemma \ref{lem: estimate of exponential remaining},
-    In fact, for any compact $K \subset \mathbb R$, due to Lemma \ref{lem: estimate of exponential remaining},
-\begin{equation}
-\int_{\mathbb R}\sup_{\theta \in K} |e^{i\theta x} - 1 - i \theta x\mathbf 1_{|x|< 1}|~\nu(dx)
-\leq (\sup_{\theta \in K} \theta^2)\int_{[0,1)} | x|^2 \nu(dx) + 2 \int_{[1,\infty)} \nu(dx) < \infty,
-\end{equation}
-    we can verify the continuity of $h$ from the dominant convergence theorem.
-    Now, according to \cite[Proposition 1.9.1.]{Linde1986Probability},
-    $h$ is the unique continuous function from $\mathbb R$ to $\mathbb C$ with $h(0) = 0$ and $P[e^{i\theta Y}] = \exp\big(h(\theta)\big)$.
-    We refer to function $h$ the characteristic exponent of random variable $Y$ and write $\operatorname{Log} P[e^{i\theta Y}] = h(\theta)$.
-
-\subsection{}
-
-    Suppose that $\{Y;P\}$ is an infinitely divisible random variable with characteristic exponent \eqref{eq: Characteristic exponent}.
-    Suppose that $P[|Y|]< \infty$.
-    According to \cite[Corollary 25.8.]{Sato1999Levy}, $\int_{|x|>1} |x|\nu(dx) < \infty$.
-
-    We claim that, $h$ is differentiable on $\mathbb R$.
-    In fact, according to Lemma \ref{lem: estimate of exponential remaining}, we have for any compact $K \subset \mathbb R$,
-\begin{align}
-    &\int_{\mathbb R} \sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta}(e^{i\theta x} - 1 - i \theta x\mathbf 1_{|x|< 1})\Big| \nu(dx)
-    = \int_{\mathbb R} \sup_{\theta \in K} | e^{
-    i\theta x} ix - ix \mathbf 1_{|x|< 1} | \nu(dx)
-    \\&\leq(\sup_{\theta \in K}|\theta|) \int_{[0,1)}|x^2| \nu(dx)+\int_{[1,\infty)} |x|  \nu(dx)
-    %< \infty,
-    %\quad \epsilon > 0.
-    < \infty.
-\end{align}
-    Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability},
-    we have that $h$ is differentiable on $\mathbb R$ with derivative
-\begin{equation}
-    h'(\theta) = ia - \sigma^2 \theta + i \int_{\mathbb R} (xe^{i\theta x} - x\mathbf 1_{|x|<1}) \nu(dx).
-\end{equation}
-    %Therefore, according to \cite[Theorem 3.2.4.]{Cuppens1975Decomposition}, we have that map $\theta \mapsto \mathbf P[e^{i\theta Y}]$ from $\mathbb R$ to $\mathbb C$ is differentiable with
-    Now, according to \cite[Theorem 3.2.4.]{Cuppens1975Decomposition}, we have that map $\theta \mapsto \mathbf P[e^{i\theta Y}]$ from $\mathbb R$ to $\mathbb C$ is differentiable with
-\begin{equation}
-\label{eq: derivative of characteristic exponent}
-    iP[Y e^{i\theta Y}]
-    =\frac{d}{d \theta} P[e^{i\theta Y}]
-    = P[e^{i\theta Y}] \frac{d}{d \theta} h(\theta),
-    \quad \theta \in \mathbb R.
-\end{equation}
-
-\subsection{}
 \label{sec: definition of superprocess}
@@
 \end{equation}
-    where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+    where $\beta \in \mathcal B_b(E)$, $\alpha \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
 \item
@@
     We refer our reader to \cite{Li2011Measure-valued} for more discussion about the definition and the existence of superprocesses.
-    To avoid triviality, we assume that $\psi(x,z)\neq -\beta(x)z$ for some $x \in E$ and $z \geq 0$; and that $\Pi_x(\zeta>t)>0$ for each $x \in E$ and $t \geq 0$.
-
-\subsection{}
-\label{sec: extension of branching mechanism}
-    Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.
+    To avoid triviality, we assume that $\psi(x,z)\neq -\beta(x)z$ for some $x \in E$ and $z \geq 0$.
+
     Notice that, the branching mechanism $\psi$ can be extended as a map from $E \times \mathbb C_+$ to $\mathbb C$ using \eqref{eq: branching mechanism}.
@@
 
-\subsection{}
-    Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.
-    %Denote by $\mathbb W$ the space of $\mathcal M_E^1$-valued c\`{a}dl\`{a}g paths whis its conanical path denoted by $(W_t)_{t\geq 0}$.
     Denote by $\mathbb W$ the space of $\mathcal M_E^1$-valued c\`{a}dl\`{a}g paths with its conanical path denoted by $(W_t)_{t\geq 0}$.
@@
     Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued},
-    there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
+    there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
 \begin{itemize}
@@
     Also notice that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$.
-    Therefore, according to the discussion in Subsection \ref{sec: definition of characteristic exponent}, we have
+    Therefore, according to \cite[Lemma 7.6]{Sato1999Levy}, we have
 \begin{equation}
@@
 
-\subsection{}
-    Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
-    In this subsection, we want to show that if $f\in L^2(\xi)$ then the following expectation
+    We claim that if $f\in L^2(\xi)$ then the following expectation
 \[
@@
 \]
-    is well defined.
-
-    Firstly, fix $t > 0,x\in E$ and $f\in L^1(\xi)$.
+    is well defined. Firstly, we only assume that $f\in L^1(\xi)$.
     Noticing that
@@
 \\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty  P^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\beta_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
-\\ &=: C_{\ref{eq: upper bound of psi'(v)}.1} + C_{\ref{eq: upper bound of psi'(v)}.2}(P^\beta_t |f|)(x).
+\\ &=: C_1 + C_2(P^\beta_t |f|)(x).
 \end{split}
 \end{equation}
-    where $C_{\ref{eq: upper bound of psi'(v)}.1}, C_{\ref{eq: upper bound of psi'(v)}.2}$ are constants not dependent on $f,x$ and $t$.
+    where $C_1, C_2$ are constants not dependent on $f,x$ and $t$.
     Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have
@@
     \big|\psi\big(x,-U_tf\big)\big|
-    \leq C_{\ref{eq: upper bound of psi'(v)}.1} P^\beta_t |f|(x)+C_{\ref{eq: upper bound of psi'(v)}.2} P^\beta_t |f| (x)^2.
+    \leq C_1 P^\beta_t |f|(x)+C_2 P^\beta_t |f| (x)^2.
 \end{align}
@@
     &\Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
-    \\&\leq \Pi_x\Big[\int_0^t \big(C_{\ref{eq: upper bound of psi'(v)}.1} P_{t-s}^\beta|f|(\xi_s)+C_{\ref{eq: upper bound of psi'(v)}.2} P_{t-s}^\beta|f|(\xi_s)^2\big)ds\Big]
-    \\ &\leq \int_0^t \big(C_{\ref{eq: upper bound of psi'(v)}.1} e^{t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_{\ref{eq: upper bound of psi'(v)}.2} e^{2t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
-    \\ &\leq \int_0^t (C_{\ref{eq: upper bound of psi'(v)}.1} e^{t\|\beta\|}\Pi_x [ |f(\xi_{t})|]+C_{\ref{eq: upper bound of psi'(v)}.2}e^{2t\|\beta\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
-\end{align}
-
+    \\&\leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^\beta|f|(\xi_s)+C_2 P_{t-s}^\beta|f|(\xi_s)^2\big)ds\Big]
+    \\ &\leq \int_0^t \big(C_1 e^{t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
+    \\ &\leq \int_0^t (C_1 e^{t\|\beta\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\beta\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
+\end{align}
 	As a consequence, expectation
@@
     is well defined for all $f\in L_2(\xi)$.
+
 \subsection{}
-     In this subsection, we recall the generalized spine decomposition theorem for the superprocesses.
+	Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}. 
+	In this subsection, we will proof the following:
+	\begin{prop}
+\label{prop: complex FKPP-equation}
+    Let $f\in L_2(\xi)$. Then for each $t\geq 0$ and $x\in E$,
+\begin{equation}
+\label{eq: complex FKPP-equation}
+    U_tf(x) - \Pi_x \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f\big) ds \Big]
+    \\= i \Pi_x [f(\xi_t)],
+\end{equation}
+and
+\begin{equation}
+\label{eq: complex FKPP-equation with FK-transform}
+    U_tf(x) -  \int_0^t P_{t-s}^{\beta} \psi_0\big(\cdot,-U_sf\big) (x)~ds
+    \\= iP_t^\beta f(x).
+\end{equation}
+\end{prop}
+
+    To do this, we will need the generalized spine decomposition theorem for the superprocesses \cite{RenSongSun2017Spine} which we now recall.
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
@@
 \begin{align}
+\label{eq: conditional intensity}
     \mathbf m(\xi,ds,dw)
@@
 \end{align}
-\subsection{}
-    Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
-
-\begin{prop}
-\label{prop: complex FKPP-equation}
-    Let $f\in L_2(\xi)$. Then for each $t\geq 0$ and $x\in E$,
-\begin{equation}
-\label{eq: complex FKPP-equation}
-    U_tf(x) - \Pi_x \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f\big) ds \Big]
-    \\= i \Pi_x [f(\xi_t)],
-\end{equation}
-and
-\begin{equation}
-\label{eq: complex FKPP-equation with FK-transform}
-    U_tf(x) -  \int_0^t P_{t-s}^{\beta} \psi_0\big(\cdot,-U_sf\big) (x)~ds
-    \\= iP_t^\beta f(x).
-\end{equation}
-\end{prop}
-
-\begin{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop: complex FKPP-equation}]
     Assume that $f\in b\mathscr B_E$.
@@
     %Given $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$.
-    Conditioned on $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$.
+    Conditioned on $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$ in \eqref{eq: conditional intensity}.
     Denote by $\Pi_{r,x}$ the probability of Hunt process $\{\xi; \Pi\}$ initiated at time $r$ and position $x$.
@@
 \end{align}
-    According to this, Fubini's theorem, \eqref{eq: N and characteristic exponent}, \eqref{eq: -v has positive real part} and the argument in Subsection \ref{sec: extension of branching mechanism}, we have $\mathbf Q^{(g,t)}_{x}$-a.s.ly,
+    According to this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-a.s.ly,
 \begin{align}
@@
 \end{align}
-    Therefore, according to \eqref{eq: derivative of characteristic exponent} and above, we have
+    Therefore, we have
 \begin{align}
     \frac{\partial}{\partial \theta} {U_t(\theta f)(x)}
-    =  \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ]
+    = \frac{\mathbf P_{\delta_x}[iX_t(f)e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
+    =  \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
 \end{align}
@@
     \big|\psi(\xi_s,- U_{t-s}f_n)\big|
-    \leq C_{\ref{eq: upper bound of psi'(v)}.1} P_{t-s}^\beta|f|(\xi_s)+C_{\ref{eq: upper bound of psi'(v)}.2} P_{t-s}^\beta|f|(\xi_s)^2.
+    \leq C_1 P_{t-s}^\beta|f|(\xi_s)+C_2 P_{t-s}^\beta|f|(\xi_s)^2.
 \end{align}

### 2019-01-31 supCLT.tex
supCLT.tex: 1207

@@
 %%%----Versions-----------------------------
+% supclt1207.tex 2018/12/07 by Renming
 % supCLT1204.tex 2018/12/04 by Zhenyao
@@
 %\date{}
-\maketitle
+%\maketitle
 %---Contents-----------------------
 \begin{abstract}
-    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$.
-For each testing function $f$ with polynomial growth, denote by $\kappa_f$ the order of $f$ in term of the spectral decomposition of $f$ with respect to the mean semigroup of $X$.
-Conditioned on no-extinction, we establish some spatial central limit theorem for $\langle f, X_t \rangle$ under three different regimes: In the small branching case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ convergences weakly.
-In the critical branching case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ convergences weakly.
-In the large branching case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ convergences a.s and in $L^{1+\gamma}$, with $\gamma \in (0,\beta)$.
+    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$. For each testing function $f$ 
+%    with polynomial growth, 
+of at most polynomial growth,
+    denote by $\kappa_f$ the order of $f$ in term of the spectral decomposition of $f$ 
+%    with respect to the mean semigroup of $X$. 
+in terms of the spectrum of the the mean semigroup of $X$. 
+    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$
+%    convergences weakly. 
+converges weakly.
+    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ 
+%    convergences weakly. 
+converges weakly.
+    In the large branching rate case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ 
+%   convergences a.s and in $L^{1+\gamma}$, with $\gamma \in (0,\beta)$.
+converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$.
 \end{abstract}
+\maketitle
 \section{Introduction}
@@
     %\deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
-    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
+    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator 
+%$L$ such that
 \begin{equation}
@@
 \end{equation}
-    where $\sigma>0$ and $b>0$.
+    where $\sigma>0$ and $b>0$ are constants.
     Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
-    Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
+    Let $\psi$ be the function on $\mathbb R_+:= [0,\infty)$ defined by
 \begin{equation}\label{mechanism}
@@
 \end{equation}
-	where $\alpha > 0$ and $\beta \in (0,1) $.
-    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite measures on $\mathbb{R}^d$.
-    For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
-    Put $\|\mu\|=\langle 1,\mu\rangle$ if it is well defined.
-    We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
+	where $\alpha > 0$ and $\beta \in (0,1) $ are constants.
+    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite Borel measures on $\mathbb{R}^d$.
+    For all Borel function $f$ and Borel measure $\mu$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
+    Put $\|\mu\|=\langle 1,\mu\rangle$.
+    We say an $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb{R}^d$, we have
 \begin{equation} \label{super}
@@
 
-	The existence of superprocesses are well known, see \cite{EB} for instance.
+	The existence of superprocesses is well known, see \cite{EB} for instance.
     According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
@@
 \subsection{OU semigroup}
-    In this subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
+    In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
     Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
@@
 \end{equation}
-    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
+    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
 \begin{equation}
@@
 \end{equation}
-    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
-    For each $k \in \mathbb Z_+$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
+    It is known that $(T_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
+    discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
+    For each $k \in \mathbb Z_+$, denote by $A_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
 \begin{equation}
@@
     Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
-    That is, for each $f\in L^2(\varphi)$,
+    Thus, for each $f\in L^2(\varphi)$,
 \begin{equation}\label{semicomp1}
@@
 \end{equation}
-    the order of function $f$ in $L^2(\varphi)$.
+    the order of the function $f$ in $L^2(\varphi)$.
     Note that $ \kappa_f\geq 0$.
     In particular, the order of any constant function is zero.
-    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ with
+    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
 \begin{equation}
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-    For each $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
+    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
 $
@@
     Let $X$ be the super OU-process discussed in the first subsection.
-    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
-    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
+    Its branching mechanism $\psi$ can be extended to $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$:
+ $$\psi(z) := -\alpha z + z^{1+\beta}, \quad z\in \mathbb C_+.$$
+%    According to the above analysis, 
+According to the analysis in Subsection A.1, 
+    $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
+    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
 \begin{equation}
@@
 \end{equation}
-    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
-    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
-    For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$ the value of the L\'evy exponent of infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
-    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ take values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
+    Write $\psi_0(z) := \psi(z) + \alpha z$. Then$\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
+    For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
+    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$, the value of the L\'evy exponent of the infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
+    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
 \begin{align}
@@
 
-In this subsection, we will give the main results of this paper. Let $\mu\in \mathcal M_c(\mathbb R_d)$ be a finite measure on $\mathbb R_d$ with compact support.
+In this subsection, we will give the main results of this paper. Suppose $\mu\in \mathcal M_c(\mathbb R_d)$ has compact support.
 \subsubsection{Large Branching Rate}
@@
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
-  For any $0<\gamma<\beta$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  \begin{thm}\label{Theorem11}
-     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then as $t\rightarrow \infty$,
-     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
-     for any $0<\gamma<\beta$.
-
-     Moreover, if $f$ is twice differentiable and its twice derivative $D^2 f$ satisfies $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
+     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for any $\gamma\in (0, \beta)$,
+     as $t\rightarrow \infty$,
+     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$
+
+     Moreover, if $f$ is twice differentiable and 
+%     its twice derivative $D^2 f$ satisfies $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
+all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
  \end{thm}
@@
  \begin{rem}
-    If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
+    If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},  for any $\gamma\in (0, \beta)$, as $t\rightarrow \infty$
      $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
-    for any $0<\gamma<\beta$. Moreover, if $f$ is twice differentiable and $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
+    Moreover, if $f$ is twice differentiable and 
+%    $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
+all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
  \end{rem}
@@
 \begin{thm}\label{Theorem12}
-Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
 $$\frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
-where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by
-$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\tilde{m}[\theta f]).$$
+where $\eta_1$ is a $(1+\beta)$-stable random variable with
+$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\tilde{m}[\theta f]), \quad \theta\in \mathbb R.$$
 \end{thm}
@@
     $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
-    where $\eta_2$ is a $(1+\beta)$-stable random variable with characteristic function given by
-    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(m[\theta f]).$$
+    where $\eta_2$ is a $(1+\beta)$-stable random variable with 
+    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
 \end{thm}
@@
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
-    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
-    We say $R$ is a monotonic operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for each $f, g \in \mathcal P^+$ with $f\leq g$.
-    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P^+$.
-    We say an operator $A$ is $\gamma$-controllable on $\mathcal D $ for some $\gamma \in \mathbb R$ if $A: \mathcal D \to \mathcal P^*$ and there  is a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
+    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for all $\theta \geq 0$ and $f \in \mathcal P^+$.
+    We say $R$ is a monotone operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for all $f, g \in \mathcal P^+$ with $f\leq g$.
+    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotone operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for all $f\in \mathcal P^+$.
+    We say an operator $A$ is $\gamma$-controllable on $\mathcal D \subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if $A: \mathcal D \to \mathcal P^*$ and there  is a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f| (\le S|f|)$ for all $f\in \mathcal D$.
     In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
     We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that, for each $s\in \Lambda$, $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$.
-    \begin{comment}
-
-\deleted{
-    The first reason for considering $\gamma$-controllable operators is the following:
-\begin{lem}
-    Suppose that operators $(A_\lambda)_{\lambda\in \Lambda}$ are uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$.
-    Then \added{for each $\kappa\geq0$,} there exists a $\gamma$-scalable operator $S$ such that
-\[
-    |A_\lambda T_t^\alpha f|
-    \leq e^{\gamma t (\alpha  - \added{\kappa} b)} S\added{Q_{\kappa}}f,
-    \quad \lambda \in \Lambda, t\geq 0, f\in \added{ \mathcal{D}\cap\mathcal{P}_{\kappa}}.
-\]
-\end{lem}
-
-\begin{proof}
-    Let $(R,S)$ be the $\gamma$-control-pair for $(A_\lambda)_{\lambda\in \Lambda}$.
-    Then
-\[
-    |A_\lambda T_t^\alpha f| \leq R|T_t^\alpha f|
-    \leq R (e^{\alpha t  - \kappa bt}Q_{\kappa}f)
-    \leq S (e^{\alpha t  - \kappa bt}Q_{\kappa}f)
-    \leq e^{\gamma t (\alpha  - \kappa b)} SQ_{\kappa}f.
-    \qedhere
-\]
-\end{proof}
-}
-\end{comment}
-	For two operators $A: \mathcal D_A \to \mathcal P^*$ and $B: \mathcal D_B \to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for each $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
-    Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for each $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
-    One of the reason for considering $\gamma$-controllable operators is that they have good algebra properties:
+
+	For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
+    Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
+    One of the reason for considering $\gamma$-controllable operators is that they have good algebraic properties:
 \begin{lem}
 \label{lem: property of controllable operators}
-    Let operators $(A_\lambda)_{\lambda\in \Lambda}$ be uniformly $\gamma$-controllable on $\mathcal D \subset \mathcal P^*$:
+%    Let operators $(A_\lambda)_{\lambda\in \Lambda}$ be uniformly $\gamma$-controllable on $\mathcal D \subset \mathcal P^*$:
+Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$.
+Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D$.
 \begin{itemize}
 \item[(1)]
-    Suppose that $(\Lambda, \mathscr F)$ is a measurable space.
-    Also suppose that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
-    For each probability measure $\mu$ on $(\Lambda, \mathscr F)$ write
+    Suppose that $(\Lambda, \mathscr F)$ is a measurable space
+    and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
+    For any probability measure $\mu$ on $(\Lambda, \mathscr F)$, write
 \[
@@
 \]
-    Then operators $\{A_\mu: \mu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ are uniformly $\gamma$-controllable on $\mathcal D$.
+    Then  $\{A_\mu: \mu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $\gamma$-controllable on $\mathcal D$.
 \item[(2)]
-    Suppose that operators $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$ for some $\beta \in \mathbb R$.
-    Also suppose that for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
-    Then operators $(B_\delta A_\lambda)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
+    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal P^*$.
+    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0$ for some $\beta \in \mathbb R$ and that, for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
+    Then  $(B_\delta A_\lambda)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
 \item[(3)]
-    Suppose that operators $(B_\delta)_{\delta \in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta\in \mathbb R$.
-    Then operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ are uniformly $(\gamma+\beta)$-controllable.
+ %   Suppose that operators $(B_\delta)_{\delta \in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta\in \mathbb R$.
+    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
+    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta \in \mathbb R$.
+    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma+\beta)$-controllable.
 \item[(4)]
     Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
-    Then operators $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ are uniformly $(a\gamma)$-controllable.
+    Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(a\gamma)$-controllable.
 \end{itemize}
@@
 \begin{proof}
-    Proof of (1): Let $(R,S)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$.
-For each $f \in \mathcal{D}$ and $\mu$ the probability measure on $(\Lambda, \mathscr F)$.
+    (1).
+Let $(R,S)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$.
+For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\mu$ on $(\Lambda, \mathscr F)$,
 \[
@@
 
-   	Proof of (2): Let $(R_A, S_A)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$ and $(R_B, S_B)$ be the $\beta$-control-pair of $(B_{\delta})_{\delta\in\Delta}$ on $\mathcal{D}_0$.
+   	(2).
+Let $(R_A, S_A)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$ and $(R_B, S_B)$ be the $\beta$-control-pair of $(B_{\delta})_{\delta\in\Delta}$ on $\mathcal{D}_0$.
 	Note that $(R_BR_A, S_BS_A)$ is a $\beta \gamma$-control-pair.
@@
 \end{itemize}
-	Finally, note that for each $\delta\in \Delta, \lambda\in\Lambda$ and $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|$ which says that operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ are uniformly $(\beta\gamma)$-controlled by $(R_BR_A,S_BS_A)$.
-
-   Proof of (3) and (4): Similar to the Proof of (2).
+	Finally, note that for each $\delta\in \Delta, \lambda\in\Lambda$ and $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|$ which says that $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(\beta\gamma)$-controlled by $(R_BR_A,S_BS_A)$.
+
+   The proofs of (3) and (4) are similar to that of (2).
 \end{proof}
 \subsection{}
-    For each $f \in \mathcal{P}$, $x\in \mathbb{R}^d$ and $t\geq 0$, define
+    For all $f \in \mathcal{P}$, $x\in \mathbb{R}^d$ and $t\geq 0$, define
 \begin{align}
@@
     \tilde U_t f(x)
-    &:= i T^\alpha_t f(x) + \int_0^t T^\alpha_{t-s} \Psi_0(-i T_s^{\alpha}f)(x)ds
+    &:= i T^\alpha_t f(x) + \int_0^t T^\alpha_{t-s} \Psi_0(-i T_s^{\alpha}f)(x)ds,
     \\Z_t f (x)
@@
 \label{lem: upper bound for usgx}
-The following statements are true for the super-OU process considered in this paper:
+The following statements are true for our super-OU process:
 \begin{itemize}
 \item[(1)]
-    Operators $(-U_t)_{0\leq t\leq 1}$ are uniformly $1$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
+   $(-U_t)_{0\leq t\leq 1}$ is uniformly $1$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
 \item[(2)]
-    Operators $(T^\alpha_t)_{0\leq t\leq 1}$ are uniformly $1$-controllable on $\mathcal P$.
+    $(T^\alpha_t)_{0\leq t\leq 1}$ is uniformly $1$-controllable on $\mathcal P$.
 \item[(3)]
-    Operator $\Psi_0$ is $(1+\beta)$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
+    $\Psi_0$ is $(1+\beta)$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
 \item[(4)]
-    Operators $(U_t- iT_t^{\alpha})_{0\leq t\leq 1}$ are uniformly $(1+\beta)$-controllable on $\mathcal P$.
+    $(U_t- iT_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(1+\beta)$-controllable on $\mathcal P$.
 \item[(5)]
-    Operators $\{\Psi_0(-U_t) - \Psi_0(-iT_t^\alpha): 0\leq t\leq 1\}$ are uniformly $(1+2\beta)$-controllable on $\mathcal P$.
+    $\{\Psi_0(-U_t) - \Psi_0(-iT_t^\alpha): 0\leq t\leq 1\}$ is uniformly $(1+2\beta)$-controllable on $\mathcal P$.
 \item[(6)]
-    Operator $(U_t-\tilde U_t)_{0\leq t\leq 1}$ are uniformly $(1+2\beta)$-controllable on $\mathcal P$.
+    $(U_t-\tilde U_t)_{0\leq t\leq 1}$ is uniformly $(1+2\beta)$-controllable on $\mathcal P$.
 \item[(7)]
-    Operators $(Z_t)_{0\leq t\leq 1}$ are uniformly $(1+\beta)$-controallable on $\mathcal P$.
+    $(Z_t)_{0\leq t\leq 1}$ is uniformly $(1+\beta)$-controallable on $\mathcal P$.
 \end{itemize}
@@
 \begin{proof}
-    Proof of (1): From \eqref{eq: upper bound for vf} in the appendix, we have for each $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
+    (1). It follows from \eqref{eq: upper bound for vf}, that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
 \[
@@
 \]
-    Note that $f\mapsto\sup_{0\leq u\leq 1}T^{\alpha}_u|f|$ is monotonic and $1$-scalable.
-
-    Proof of (2): Similar to the Proof of (1).
-
-    Proof of (3): According to Lemma \ref{lem: Lip of power function}, for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
+    Now note that $f\mapsto\sup_{0\leq u\leq 1}T^{\alpha}_u|f|$ is monotone and $1$-scalable.
+
+    (2). Similar to the proof of (1).
+
+    (3). According to Lemma \ref{lem: Lip of power function}, for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
 \[
@@
 \]
-    Also note that $f\mapsto |f|^{1+\beta}$ is monotonic and $(1+\beta)$-scalable.
-
-    Proof of (4): From (1), (2), (3) and Lemma \ref{lem: property of controllable operators}(2) we know that operators
+    Now note that $f\mapsto |f|^{1+\beta}$ is monotone and $(1+\beta)$-scalable.
+
+    (4). From (1), (2), (3) and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
 \[
@@
 \]
-    are uniformly $(1+\beta)$-controllable.
-    From \eqref{eq:chareq2}, Lemma \ref{lem: property of controllable operators}(1) and this we get the desired result.
-
-    Proof of (5): Notice that from Lemma \ref{lem: Lip of power function},
+    is uniformly $(1+\beta)$-controllable.
+    Combining this with \eqref{eq:chareq2} and Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.
+
+    (5).  Notice that from Lemma \ref{lem: Lip of power function},
 \[
@@
 \]
-    From (1), (2), (4) and Lemma \ref{lem: property of controllable operators} (3,4) we get the desired result.
-
-    Proof of (6): Note that
+    Now using (1), (2), (4) and Lemma \ref{lem: property of controllable operators}.(3)-(4), we get the desired result.
+
+    (6). Note that
 \[
@@
 \]
-    Then from (2), (5) and Lemma \ref{lem: property of controllable operators}(1,2) we get the desired result.
-
-    Proof of (7): Similar to the proof of (4).
+    Now using (2), (5) and Lemma \ref{lem: property of controllable operators}.(1)--(2), we get the desired result.
+
+    (7). The proof is similar to that of (4).
 \end{proof}
-\begin{comment}
-\textbf{ Zhenyao: I think the following Corollary is incorrect.
-In its proof, we seems used Jensen's inequality assuming $\mu$ is a probability measure (which is not the case).
-At first, I think I may find a way to fix this.
-But then I realize we don't really need this Corrollary to calculate $\|X_t(g)\|_{1+\gamma}$.
-So I didn't touch it.
-Yet, I'm not sure if this Corrollary is needed somewhere else in section 3.}
-
-\begin{cor}
-\label{cor: corollary1}
-    There exists an $R^g_3 \in \mathcal{P}$ such that for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$,$\theta \in \mathbb{R}$ and $0\leq s\leq 1$, we have
-\[
-    \mathbb P_{\mu}[e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}]
-    =1+\langle Z_{g_k}(s,\cdot,\theta),\mu\rangle+ err(k,\mu,\theta),
-\]
-    where $|err(k,\mu,\theta)| \leq (C_g|\theta e^{(\alpha-\kappa b)k}|^{2+2\beta} + C_g|\theta e^{(\alpha-\kappa b)k}|^{1+2\beta} )\langle R^g_3,\mu\rangle$.
-\end{cor}
-\begin{proof}
-    Let
-\begin{align}
-\label{eq: definition of varphi-mu-k-theta}
-    \varphi_{k,\mu,s}(\theta)
-    =\mathbb{P}_{\mu}[e^{i\theta(\langle g_k, X_s\rangle-\langle T_s^{\alpha}g_k,\mu \rangle)}]
-    =e^{(\langle v_{g_k}(s,\cdot,\theta),\mu \rangle-i\theta \langle T_s^{\alpha} g_k, \mu \rangle)},
-    \quad \theta \in \mathbb R.
-\end{align}
-    Then we have
-\begin{align*}
-    &|\varphi_{k,\mu,s}(\theta)-1-\langle Z_{g_k}(s,\cdot, \theta),\mu\rangle|\\
-    &\leq|\varphi_{\mu,k,s}(\theta)-1-\left( \langle v_{g_k}(s,\cdot,\theta), \mu \rangle-i\theta \langle T_s^{\alpha}g_k,\mu\rangle\right)| + |\langle v_{g_k}(s,\cdot,\theta)-\tilde{v}_{g_k}(s,\cdot,\theta),\mu \rangle|.
-\end{align*}
-    Let $R^g_1\in \mathcal P$ be the control function in Lemma \ref{lemma2}.
-    Let $\tilde R^g$ be the control function in \eqref{eq: Zineq}.
-    Notice that
+
+\subsection{}
+
+ In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
+Denote by $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite Borel measures on $\mathbb{R}^d$ with compact support.
+	For all $0 \leq a_1 \leq a_2 <\infty$ and  random variable $Y$ with finite mean, define
 $
-    \operatorname{Re} \big(v_{g_k}(s,x,\theta) - i\theta T_s^\alpha g_k(x)\big)
-    = \operatorname{Re} v_{g_k}(s,x,\theta)
-    \leq 0,
-$
-    (see \eqref{eq: -v has positive real part} in the appendix); and if $ \operatorname{Re} z\leq 0$, we have $|e^z-1-z|\leq |z|^2$, (see Lemma \ref{lem: estimate of exponential remaining} in the appendix).
-    Therefore, for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, $k \in \mathbb{N}$, $\theta \in \mathbb{R}$ and $0\leq s\leq1$, using Jensen's inequality,
-\begin{align*}
-    &|\varphi_{k,\mu,s}(\theta)-1- \langle Z_{g_k}(s,\cdot, \theta),\mu\rangle|\\
-    &\leq |\langle v_{g_k}(s,\cdot,\theta)-i\theta T_s^{\alpha}g_k, \mu \rangle|^2 + \langle |v_{g_k}(s,\cdot,\theta)-\tilde{v}_{g_k}(s,\cdot,\theta)|, \mu \rangle
-    \\&\leq \langle |v_{g_k}(s,\cdot,\theta)-i\theta T_s^{\alpha}g_k|^2, \mu \rangle + \langle |v_{g_k}(s,\cdot,\theta)-\tilde{v}_{g_k}(s,\cdot,\theta)|, \mu \rangle
-    \\&\leq e^{2\alpha}|C_g\theta e^{(\alpha-\kappa b)k+\alpha}|^{2+2\beta}\langle (\tilde R^g)^2,\mu\rangle + |C_g\theta e^{(\alpha-\kappa b)k}|^{1+2\beta}\langle R^g_1,\mu\rangle.
-    \qedhere
-\end{align*}
-\end{proof}
-\end{comment}
-
-\subsection{}
-
- In this subsection, for any $\gamma \in (0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$.
-Denote $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite measures on $\mathbb{R}^d$ with compact support.
-	For each $0 \leq a \leq b <\infty$ and  random variable $Y \in$ with finite mean, define random variable
-$
-   	\mathcal I_a^b Y
-    := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
+   	\mathcal I_{a_1}^{a_2} Y
+    := \mathbb P[Y|\mathscr F_{a_2}] - \mathbb P[Y|\mathscr F_{a_1}].
 $
@@
 \label{lem: control pair for P(M>lambda)}
-    There is an $(1+\beta)$-control-pair $(R,S)$ such that for each $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$ we have
+    There is a $(1+\beta)$-control-pair $(R,S)$ such that for all $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we have
 \[
@@
 \begin{proof}
-    Denote by $(R,S)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}(4).
-    Using Lemma \ref{lem: estimate of exponential remaining} and the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, we have
+    Denote by $(R,S)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}.(4).
+    Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
 \begin{align}
@@
 \begin{lem}\label{lem: temp}
-	For each $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb{R}^d)$ there exist a constant $C \geq 0$ such that for each $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
+	For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb{R}^d)$, there exist a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
 \[
@@
     Suppose that $g\in \mathcal P$ satisfies $Q_\kappa g \leq h$.
-    Using Markovian property of $(X_t)_{t\geq 0}$ we get
+    Using the Markov property of $(X_t)_{t\geq 0}$, we get
 \begin{align}
@@
 \label{lem: control of mgtrs}
-	For each $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exist a constant $C > 0$, such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
+	For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $\gamma\in (0, \beta)$, there exist a constant $C > 0$, such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
 \[
@@
 \begin{proof}
-	Fix $h \in \mathcal P$ and $\mu \in \mathcal M_c(\mathbb R^d)$. Let $C_0$ be the constant in the previous Lemma.
-    For each $\kappa \in \mathbb Z_+$, each $0\leq r\leq s\leq t$ with $s-r \leq 1$, each $g\in \mathcal P$ with $Q_{\kappa} g \leq h$ and each $c>0$, we have
+	Fix $h \in \mathcal P$ and $\mu \in \mathcal M_c(\mathbb R^d)$. Let $C_0$ be the constant in the Lemma \ref{lem: temp}.
+    For all $\kappa \in \mathbb Z_+$,  $0\leq r\leq s\leq t$ with $s-r \leq 1$,  $g\in \mathcal P$ with $Q_{\kappa} g \leq h$, and $c>0$, we have
 \begin{align}
@@
 \end{align}
-    Taking $c = e^{(t-s)(\alpha- \kappa b)}$ we have
+    Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
 \begin{align}
@@
 \label{lem: control moment}
-	For each $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$, $0<\gamma < \beta$ and $\kappa \in \mathbb Z_+$, there exist a constant $C > 0$, such that for each $t\geq 0$, we have
+	For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exist a constant $C > 0$ such that for each $t\geq 0$, we have
 \begin{itemize}
@@
     Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
-    Using the triangle inequality, for each $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$ we have
+    Using the triangle inequality, for all $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$, we have
 \begin{align}
@@
 \subsection{Martingales}
-    In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales with $0<\gamma<\beta$.
-Recall that $L$ is the infinitesimal generator of OU-process.
-Let $a\in \mathbb{R}$ and $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$ ,we define that
+    In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales for $\gamma\in (0, \beta)$.
+Recall that $L$ is the infinitesimal generator of the OU-process.
+Let $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ be such that $Lf \in \mathcal{P}$, and let $a\in \mathbb{R}$, we define that
 \begin{align}
@@
 \end{align}
-    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra $\{\mathscr{F}_t\}_{t\geq 0}$.
+    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $\{\mathscr{F}_t\}_{t\geq 0}$.
 \begin{lem}
 \label{lemma25}
-    Let $a\in \mathbb R$ and $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$. Then the process $(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.
+    Let $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ be such that $Lf \in \mathcal{P}$ and let $a\in \mathbb R$. Then the process $(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.
 \end{lem}
@@
 
-    Let $p=(p_1,...,p_d)\in \mathbb Z_+^d$, recall that $\phi_p$ is one of the eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
+    Let $p=(p_1,...,p_d)\in \mathbb Z_+^d$, recall that $\phi_p$ is an eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
 $$H_t^p:=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.$$
@@
 \begin{lem}\label{lemma26}
-    $(H^p_t)_{t\geq 0}$ is a martingale with respect to filtration $(\mathscr F_t)$.
-    Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $0< \gamma<\beta$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
+    $(H^p_t)_{t\geq 0}$ is a martingale with respect to $(\mathscr F_t)$.
+    Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $\gamma\in (0, \beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
 $$H_{\infty}^p:=\lim_{t\rightarrow \infty}H_t^p$$
@@
 \begin{proof}
-    According to Lemma \ref{lemma25}, we get $(H_t^p)_{t\geq 0}$ is a martingale.
-
-    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$.
-    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that, there exists a constant $C_{\gamma, \mu, p}>0$ (which depends on the choice of $\gamma$, $\mu$ and $p$)  such that
+   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a martingale.
+
+    There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
+    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that there exists a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$)  such that
  $$
@@
  $$
-    For any $0\leq\gamma<\gamma_0$, note that
+    For any $\gamma\in (0, \gamma_0)$, note that
 $$
@@
 
-    Hence, for each $\gamma \in (0,\beta)$, the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicates the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ and almost sure,
-    according to \cite[Theorem 5.4.5]{Durrett2010Probability}.
+    Hence, for each $\gamma \in (0,\beta)$, the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
 \end{proof}
 
-In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ convergences to $H_{\infty}$, $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
+In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+
 \begin{lem}\label{lem: control of Wt}
- %For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have
- For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for each $0\leq s<t$,
- $$\|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-\alpha s/2}.$$
+ For all $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for all $0\leq s<t$,
+ $$
+ \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq C 
+ %e^{-\alpha s/2}.
+ e^{-\frac{\alpha \gamma}{1+\gamma}s}.
+ $$
 \end{lem}
@@
 \begin{proof}
-%new added
      Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
- According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C_0>0$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
+ According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
     \begin{align}
@@
 	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
-	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
+%	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
+	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}.
     \qedhere
@@
 \label{lem: control of XT}
-	For each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for each function $f:[0,\infty)\to [1,\infty)$ and each $t\geq 0$ we have
+	For any $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for all $f:[0,\infty)\to [1,\infty)$ and $t\geq 0$, we have
 \begin{align}
@@
 \]
-    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
-    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
-    By \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
+    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
+%    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+    By \eqref{CSBP} and the Markov property we have for all $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
     $t\geq 0$,
@@
 
-By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
-
+By Chebyshev's inequality and \eqref{laplaceexpress}, we get
 \begin{align*}
@@
 \end{align*}
-	Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t}$ where $t\geq 0,\lambda\geq0$ then $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
+	Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t}$, then $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
 Note that
@@
 \end{align*}
-Therefore, for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for each non-negative function $f$ on $[0,\infty),$ each $\lambda \geq 0$ and each $t\geq 0$ we have
+Therefore, for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for all non-negative function $f$ on $[0,\infty)$, $\lambda \geq 0$ and $t\geq 0$, we have
 \begin{align}
@@
 \end{align*}
-Finally, taking $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.
+Finally, plugging $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.
 \end{proof}
@@
 \]
-    Accodting to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies that $\alpha\beta=\kappa_f b(1+\beta)$ then the following limit exists:
+    Accodting to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, then the following limit exists:
 \begin{align}
@@
 \]
-    According to \cite[Lemma 5.1]{MM}, if $f\in \mathcal{P}$ satisfies that $\alpha\beta<\kappa_fb(1+\beta)$, then we have that the following summation and integration are equal and absolutely convergence:
+    According to \cite[Lemma 5.1]{MM}, if $f\in \mathcal{P}$ satisfies that $\alpha\beta<\kappa_fb(1+\beta)$, then 
 \begin{align}
@@
     :=\sum_{k=0}^\infty m_k[f]
-    =\alpha e^{\alpha}\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx. \label{msmallcase}
-\end{align}
+    =\alpha e^{\alpha}\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx, \label{msmallcase}
+\end{align}
+and both the series and the integral converge absolutely.
 \begin{lem}
@@
 \begin{proof}
-    From the measure theory, there is a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
+    From measure theory, there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
 \[
@@
 \[
-    \int_{\mathbb R^d/\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
-\]
-    Then, according to \cite[Remark 14.4]{Sato1999Levy}, $\nu$ is the L\`evy measure of an $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is \[\hat \mu(\theta)=\exp\Big\{\int_{\mathbb R^d/\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\}.\]
-    The final step, we verify that
-\begin{align}
-    &\int_{\mathbb R^d/\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
+    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
+\]
+    Then, according to \cite[Remark 14.4]{Sato1999Levy}, $\nu$ is the L\`evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is \[\hat \mu(\theta)=\exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\}.\]
+Finally, 
+\begin{align}
+    &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
     = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}
@@
 \label{cor: alpha stable rv}
-	For each $t\geq 0$ and $f\in \mathcal P$, 
+	For all $t\geq 0$ and $f\in \mathcal P$, 
 \begin{enumerate}
@@
 \label{it: first stable}
-    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of an $(1+\beta)$-stable random variable.
+    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
 \item 
@@
 \begin{proof}
-    Proof of \eqref{it: first stable}: 
+    \eqref{it: first stable}: 
 	Fix $t\geq 0$ and $f\in \mathcal P$.
-	Note that $m_t[\theta f]$ can be rewritten as follows:
+	Note that $m_t[\theta f]$ can be rewritten as 
 \[
@@
 \]
-	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only have to show that
+	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
 \begin{equation}
@@
 \end{equation}
-	According to Lemma \ref{lem: upper bound for usgx}(2) and Lemma \ref{lem: property of controllable operators}(1,2,4) we know that
+	According to Lemma \ref{lem: upper bound for usgx}.(2), parts (1), (2) and (4) of Lemma \ref{lem: property of controllable operators},  we know that
 $
@@
 $
-	is an $(1+\beta)$-controallable operator on $\mathcal P$.
+	is a $(1+\beta)$-controallable operator on $\mathcal P$.
 	This implies that $x \mapsto \int_0^1 T_{1-s}^\alpha (|T_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
@@
 
-    Proof of \eqref{it: second stable} and \eqref{it: third stable}: Similar to the proof of \eqref{it: first stable}.
+    The proofs of \eqref{it: second stable} and \eqref{it: third stable} are similar to that of \eqref{it: first stable}.
 \end{proof}
@@
 In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
-\begin{comment}
-\begin{lem}\label{lemma32}
-    Write $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\},$ for each $\epsilon,t>0$.
-    Then for any $\epsilon>0$, we have
-\begin{align}
-    \lim_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=D^c, ~~\mathbb{P}_{\mu}\text{-}{\rm a.s}.
-\end{align}
-\end{lem}
-\begin{proof}
-    We just need to prove
-    \begin{align}
-        D^c \subset \liminf_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c,~~\mathbb{P}_{\mu}\text{-}{\rm a.s}.
-    \end{align}
-
-    On one hand, let $\omega\in D$. Then there exists $T(\omega)>0$, such that $\|X_t(\omega)\|=0,$ for each $t\geq T(\omega)$.
-    Thus $\omega\notin  \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=\cap_{s\geq 0}\cup_{t\geq s}\mathcal{A}_t(\epsilon)$.
-    This implies that $\limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c$.
-
-    On the other hand, let $\omega \in \{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}$.
-    Then, there exists $\delta>0$ such that $H_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$ and there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq H_t(\omega)\leq 2\delta$.
-    Taking $S_2>0$ such that for any $t>S_2$, $\|\mu\|e^{-\epsilon t}<\frac{\delta}{2}$ and $\|\mu\|e^{\epsilon t}>2\delta$.
-    Then $\omega\in \mathcal{A}_t(\epsilon),$ for each $t>S:=\max\{S_1,S_2\}$.
-    This implies that $\omega \in \liminf_{t\rightarrow \infty}\mathcal{A}_t(\epsilon):=\cup_{s>0}\cap_{t\geq s}\mathcal{A}_t(\epsilon)$.
-    According to \cite{LSR}, $D^c=\{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}, \mathbb{P}_{\mu}$-a.s.. Using this we get the desired result.
-\end{proof}
-\end{comment}
+
 \begin{lem}\label{lem: mainlemma}
-
 Let $f\in \mathcal{P}$.
 Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
-Then for any $k\geq 0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+Then for all $k\geq 0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
  \begin{align}
@@
  \begin{proof}
-	We only have to show that
+	We only need to show that
 \begin{align}
@@
 \end{align}
-	In fact, once we proved this, we can replace $f$ with $\theta f$ where $\theta \in \mathbb R$ is arbitrary and get the desired result.
+	In fact, once we prove this, we can replace $f$ by $\theta f$, with $\theta \in \mathbb R$ being  arbitrary,  to get the desired result.
 	In the rest of the proof we fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and an $f\in \mathcal P$.
-	Define events
+	Define 
 \[
@@
 
-	Step 1. We will show that for each $\epsilon > 0, k\geq 0$, and $t>k+1$ we have
+	Step 1. We will show that for all $\epsilon > 0, k\geq 0$ and $t>k+1$, we have
 \begin{align}
@@
 	J_1(t,k,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle U_1(\theta_{t,k}T_k^{\alpha}f)-\tilde U_1(\theta_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big]
+	&:= \mathbb{P}_{\mu}\big[|\langle U_1(\theta_{t,k}T_k^{\alpha}f)-\tilde U_1(\theta_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
 	\\ J_2(t,k,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|; A_{t-k-1}(\epsilon)\big]
+	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|; A_{t-k-1}(\epsilon)\big],
 	\\ J_3(t,k, \epsilon)
@@
 \end{align}
-In fact, from the definition of $U_1, \tilde U_1$ and $Z_1$, we have
+In fact, from the definitions of $U_1, \tilde U_1$ and $Z_1$, we have
 \begin{align}
@@
 \end{equation}
-    According to the definition of $\tilde U_1$ and $Z_1$, \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
+    According to the definitions of $\tilde U_1$ and $Z_1$, \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
 \[
@@
 \]
-	we verify that
+	we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
     \\& \leq \mathbb{P}_{\mu}\big[|\langle (U_1 - i T_1^\alpha)(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
-    \\&\leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon),
-    \quad k\geq 0, t\geq k+1, \epsilon> 0.
-\end{align}
-
-Step 2.  We will show that there exists a $C>0$, such that,
+    \\&\leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon).
+\end{align}
+
+Step 2.  We will show that there exists a $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
     \begin{align}
     \label{lemma31q}
-      J_1(k,t,\epsilon)\leq C\exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
-      \quad k \geq 0, t\geq k+1, \epsilon > 0.
-    \end{align}
-	In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6).
-	Then, we can verify that
+      J_1(k,t,\epsilon)\leq C\exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\}.
+    \end{align}
+	In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}. (6).
+	Then, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
    \\&=\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}}e^{\frac{1+2\beta}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf
-   \\&\leq\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf,
-   \quad k\geq 0, t\geq k+1, \epsilon > 0.
-\end{align}
-Thus
+   \\&\leq\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf.
+\end{align}
+Thus for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
      \leq \|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}\mathbb{P}_{\mu}[\langle SQf,X_{t-k-1}\rangle]\\
-     & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
-     \\ &&\mathllap {k\geq 0, t\geq k+1, \epsilon > 0.}
+     & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\}.
 \end{align}
 	Step 3.
-	Fix a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-	Then there exists a constant $C > 0$ such that
+	Fix a $\gamma\in(0,\beta)$ small enough so that $\alpha \gamma < b < (1+\gamma)b$.
+	Then there exists a constant $C > 0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
     J_2(t,k,\epsilon)
-    \leq C \exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big),
-    \quad k\geq 0, t\geq k+1, \epsilon >0.
-\end{align}
-    In fact, according to the definition of $Z_1$ and $m_t$ we have
+    \leq C \exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big).
+\end{align}
+    In fact, according to the definitions of $Z_1$ and $m_t$, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
     \begin{align}
@@
           \\&= \theta_{t,k}^{1+\beta} \langle Z_1T_k^{\alpha}f,X_{t-k-1}\rangle - e^{-\alpha k}\langle  Z_1T_k^{\alpha}f,\varphi\rangle
-          \\&=e^{-\alpha k}\Big(\frac{\langle Z_1T_k^{\alpha}f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1T_k^{\alpha}f ,\varphi\rangle\Big),
-          \quad k\in \mathbb Z_+, t\geq k+1.
-    \end{align}
-Therefore,
+          \\&=e^{-\alpha k}\Big(\frac{\langle Z_1T_k^{\alpha}f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1T_k^{\alpha}f ,\varphi\rangle\Big).
+    \end{align}
+Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
     &\leq \|\mu\|^{-1} e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
-    \\& &\mathllap{k\in \mathbb Z_+, t\geq k+1, \epsilon > 0,}
 \end{align}
@@
 \]
-According to \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$, such that
+According to \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$ such that
 \[
@@
 \]
- 	This implies that,
+ 	This implies that
  \[
@@
  \]
-	Recall that $\gamma\in(0,\beta)$ is chosen small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-	According to Lemma \ref{lem: control moment} (3) (with $\kappa$ being $1$), there exist $C>0$ such that
+	Recall that $\gamma\in(0,\beta)$ is chosen small enough so that $\alpha \gamma < b < (1+\gamma)b$.
+	According to Lemma \ref{lem: control moment}.(3) (with $\kappa=1$), there exists $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
     \leq \|\langle \operatorname{Re} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}}
-    \\& \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma}
-    \\&\leq C e^{\frac{\alpha t}{1+\gamma}},\quad k \in \mathbb Z_+, t\geq 0.
-\end{align}
-Therefore, according to \eqref{eq: prevJ2}, we have
+    \\& \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C e^{\frac{\alpha t}{1+\gamma}}.
+\end{align}
+Therefore, according to \eqref{eq: prevJ2}, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
 	\\&= \|\mu\|^{-1}C e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
-	\\&\leq \|\mu\|^{-1}C e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}, \quad k \in \mathbb Z_+, t\geq k+1, \epsilon > 0,
+	\\&\leq \|\mu\|^{-1}C e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)},
 \end{align}
@@
 
-	Step 4. We will show that for each $\epsilon\leq \alpha$ there exist $C,\delta>0$ such that
+	Step 4. We will show that for each $\epsilon\in (0,  \alpha]$ there exist $C,\delta>0$ such that
 \begin{align}\label{ineq: control of J3}
@@
 	\\&= \mathbb P_\mu[e^{-\alpha^*\|X_t\|};A_t(\epsilon)]
-	\leq \exp({-\alpha^* e^{(\alpha - \epsilon)t}}),\quad t\geq 0, \epsilon >0,
-\end{align}
-	and, according to Lemma \ref{lem: control of XT}, there is a constant $C>0$ such that
+	\leq \exp({-\alpha^* e^{(\alpha - \epsilon)t}}),\quad t\geq 0, \epsilon >0.
+\end{align}
+According to Lemma \ref{lem: control of XT}, there is a constant $C>0$ such that
 \begin{align}
@@
 \end{align}
-	Combine those we get the desired result in step 4.
-
-	Final step, combine the result in Step 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ convergence to $0$ exponentially fast while $t\rightarrow\infty$.
-	This gives the desired result.
+	Combining these, we get the desired result in step 4.
+
+	Step 5.  Combining the results in Step 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$, 
+we immediately get the desired result.
 \end{proof}
 
-	It turns out that we need to evaluate the previous Lemma into the following:
+%	It turns out that we need to evaluate the previous Lemma into the following:
 
@@
 Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
-Then there exist $C>0$ and $\delta>0$ such that for each $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
+Then there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
 \begin{align}
@@
 	Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal P$.
-    According to \eqref{eq: inequality that will used later} we have
+    According to \eqref{eq: inequality that will used later},  we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
     &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-    \\&\leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon),
-    \quad \theta\in \mathbb R, k\geq 0, t\geq k+1, \epsilon> 0.
-\end{align}
-	According to \eqref{eq: estimate of J1}, we have
+    \\&\leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
+\end{align}
+	According to \eqref{eq: estimate of J1}, we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
      \\& = |\theta|^{1+2\beta} \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
-     \\ &\qquad \theta \in \mathbb R^d, k\geq 0, t\geq k+1, \epsilon > 0,
-\end{align}
-	where $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6).
-	From the definition of $Z_1$ and $m_t$ we can verify that
+\end{align}
+	where $(R,S)$ is the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}.(6).
+	From the definitions of $Z_1$ and $m_t$ we get that
 \[
@@
 \]
-	According to this and the Step 3 in the proof of the previous Lemma, we have that there exists a constant $C > 0$ such that
-\begin{align}
-\label{eq:31step3}
+	According to this and Step 3 in the proof of the previous lemma, we have that there exists a constant $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+\begin{align}
+\label{eq:31step3b}
     J^{\theta f}_2(t,k,\epsilon)
-    \leq C |\theta|^{1+\beta}\exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big),
-    \quad \theta \in \mathbb R, k\geq 0, t\geq k+1, \epsilon >0.
-\end{align}
-	Finally, according to those estimation of $J^{\theta f}_{i}, i = 1,2$ and the estimation of $J_3$ in the Step 4 of the proof of the previous Lemma, we get the desired result by chosing $\epsilon$ small enough.
+    \leq C |\theta|^{1+\beta}\exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big).
+\end{align}
+	Finally, using the estimates of $J^{\theta f}_{i}, i = 1,2$ and the estimate of $J_3$ in Step 4 of the proof of the previous lemma, we get the desired result by choosing $\epsilon$ small enough.
 \end{proof}
@@
 Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$.
-Then there exists $C,\delta>0$ such that for any $T\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
+Then there exist $C,\delta>0$ such that for all $T\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
 \begin{align}
@@
 \begin{proof}
-	Let $C,\delta > 0$ be the constant in Corollary \ref{cor: used in next corollary}.
+	Let $C,\delta > 0$ be the constants in Corollary \ref{cor: used in next corollary}.
     Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
@@
     For each $k\in\{-1,...,n\}$, we define
-    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big)\]
+    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big)\],
      where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
@@
         \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
-        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big]
-    \end{align*}
-    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$, we have
+        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
+    \end{align*}
+    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$ we have
     \begin{align*}
@@
 \label{sec: proof of thm 1.3}
-    Fix an $f\in\mathcal{P}$. 
-    Chose a $t_0 > 0$ large enough such that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
+    Fix $f\in\mathcal{P}$. 
+    Chose $t_0 > 0$ large enough so that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
     Write
@@
     \end{align*}
-    Denote by
+    Define
 \[
@@
     Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb{R}$.
-Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we have that there exists $C,\delta>0$ such that,
+Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get that there exist $C,\delta>0$ such that,
 \begin{align*}
@@
 \end{align*}
-    According to \eqref{para: critical case}, we obtain that $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\eta_1$ with respect to $\tilde {\mathbb P}_\mu$.
-    Therefore, we only need to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I_i(t)\xrightarrow[t\to \infty]{d} 0$ for $i = 2,3$ with respect to $\tilde {\mathbb P}_\mu$.
-
-    In order to show
+    According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\eta_1$ under $\tilde {\mathbb P}_\mu$.
+    Therefore, we only need to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I_i(t)\xrightarrow[t\to \infty]{d} 0$ for $i = 2,3$ under $\tilde {\mathbb P}_\mu$.
+
+   We first show that
 \begin{align}
     |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
-    \xrightarrow[t\to \infty]{} 0,
-\end{align}
-	we use \cite[Lemma 3.4.3.]{Durrett2010Probability} and get that
+    \xrightarrow[t\to \infty]{} 0.
+\end{align}
+By\cite[Lemma 3.4.3.]{Durrett2010Probability},
 \begin{align}\label{ineq: control of I1t}
@@
 \end{align}
-    where
+    where for all $k \geq 0$ and $t\geq k+1$,
 \begin{align*}
     Y_{t,k}
-    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big),
-    \quad k \geq 0 , t\geq k+1.
-\end{align*}
-    Define
+    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big).
+\end{align*}
+    Define for all $k \geq 0$ and $t\geq k+1$,
 \begin{align}
 \label{def: Dtk}
-    \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, H_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\},
-    \\ &&\mathllap{ k\geq 0, t\geq k+1.}
-\end{align}
-
-    Step 1. We will show that there exists a $C>0$ such that,
+    \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, H_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\}.
+\end{align}
+
+    Step 1. We will show that there exists a $C>0$ such that for all $k \geq 0$ and $t\geq k+1$,
 \begin{align}
@@
     \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\big]
-    \leq C e^{-\frac{\alpha\beta}{32}(t-k-1)},
-    \quad k\geq 0, t\geq k+1.
+    \leq C e^{-\frac{\alpha\beta}{32}(t-k-1)}.
 \end{align}
     Fix a $\gamma \in (0,\beta)$.
-    Let $C_1$ be the constant in  Lemma \ref{lem: control of Wt} corresponding to this $\gamma_0$ and $C_2$ be the constant in Lemma \ref{lem: control of XT}. 
-    By Chebyshev inequality, there exist $C>0$, such that
+    Let $C_1$ be the constant in  Lemma \ref{lem: control of Wt} corresponding to this $\gamma$ and $C_2$ be the constant in Lemma \ref{lem: control of XT}. 
+    ({\bf The next display needs to be revised because of the corrected statement of Lemma 2.9.
+    The whole proof needs to be changed accordingly.})
+    By Chebyshev's inequality, there exists $C>0$ such that for all $k \geq 0$ and $t\geq k+1$,
 \begin{align}
@@
     \\&\leq C_1  \mathbb{P}_{\mu}(D^c)^{-1} \|\mu\|^{-1} e^{-\frac{\alpha}{4}(t-k-1)}+C_2\|\mu\|^{\beta}e^{-\frac{\alpha\beta}{32}(t-k-1)}
-    \\&\leq Ce^{-\frac{\alpha\beta}{32}(t-k-1)},
-    \quad k\geq 0, t\geq k+1.
+    \leq Ce^{-\frac{\alpha\beta}{32}(t-k-1)}.
 \end{align}
@@
 
-    Step 2. We will show that there exists constant $C > 0$ such that
+    Step 2. We will show that there exists constant $C > 0$ such that for all 
+    $0\leq k\leq t-\ln t$ with $t$ large enough,
 \begin{align}
@@
      \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-     \leq  C e^{-\frac{\alpha}{16}(t-k)}, \quad 0\leq k\leq t-\ln t, t\text{ large enough.}
-\end{align}
-    In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for each $x,y\in \mathbb R$, we have
+     \leq  C e^{-\frac{\alpha}{16}(t-k)}.
+\end{align}
+    In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \geq 0$ and $t\geq k+1$,
 \begin{align}
@@
         \\&=|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
-        \quad k\geq 0, t\geq k+1,
 \end{align}
@@
     K_{t,k}
-    :=\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}},
-    \quad k\geq 0, t\geq k+1.
-\end{equation}
-    Note that for each $0 < x< y$, we have
+    :=\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}.
+\end{equation}
+    Note that for all $0 < x< y$, we have for $t$ large enough,
 \[
@@
     \geq e^{-xt},
-    \quad t \text{ large enough,}
 \]
@@
     Therefore, by taking $x= \frac{\alpha}{32}$ and $y= \frac{\alpha}{4}$, we have 
+    for $t$ large enough,
 \[
@@
     \geq e^{- \frac{\alpha t}{16}},
-    \quad t \text{ large enough.}
-\]
-    We can then verify that
+\]
+Thus for $0\leq k\leq t-\ln t$ with $t$ large enough,
 \begin{align*}
@@
     \\&\geq \|\mu\| e^{-\frac{\alpha}{16}(t-k-1)},
-    \quad \text{ on } \mathcal D_{t,k}, 
-    \quad 0 \leq k \leq t - \ln t, t \text{ large enough}.
-\end{align*}
-    Therefore,
+    \quad \text{ on } \mathcal D_{t,k}.
+\end{align*}
+    Therefore, for $0\leq k\leq t-\ln t$ with $t$ large enough,
 \begin{align*}
@@
     &=\frac{1}{1+\beta}\|\mu\|^{\frac{1}{1+\beta}}  e^{-\frac{3\alpha}{16}(t-k-1)},
-    \\ && \mathllap{ \text{ on } \mathcal D_{t,k}, \quad 0 \leq k \leq t - \ln t, t \text{ large enouph,} }
+    \quad \text{ on } \mathcal D_{t,k}, 
 \end{align*}
@@
     \geq \|\mu\|^{\frac{2}{1+\beta}} e^{-\frac{3\alpha}{32}(t-k-1)},
-    \\ && \mathllap{ \text{ on } \mathcal D_{t,k}, \quad 0 \leq k \leq t - \ln t, t \text{ large enouph.} }
-\end{align*}
-    Thus, there is a constant $C\geq 0$ such that 
+    \quad \text{ on } \mathcal D_{t,k}.
+\end{align*}
+    Thus, there is a constant $C\geq 0$ such that  for $0\leq k\leq t-\ln t$ with $t$ large enough,
 \begin{align}
@@
      K_{t,k}
-     \leq C e^{-\frac{3\alpha}{32}(t-k-1)},
-    \quad 0 \leq k \leq t - \ln t, t \text{ large enouph.} 
-\end{align}
-    Now fix a $\gamma \in (0, \beta)$ close enough to $\beta$ such that 
+     \leq C e^{-\frac{3\alpha}{32}(t-k-1)}.
+\end{align}
+    Now fix $\gamma \in (0, \beta)$ close enough to $\beta$ so that 
 \[
@@
 \]
-    From the condition $\alpha\beta=\kappa_f(1+\beta)b$, we can verify that 
+    From the condition $\alpha\beta=\kappa_f(1+\beta)b$, we get that 
 \begin{align}
@@
 \end{align}
-    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt}, \eqref{ineq: control of Kkt} and the above, there exists constants $C,C'>0$, such that
+    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt}, \eqref{ineq: control of Kkt} and the above, there exist constants $C,C'>0$ such that  for $0\leq k\leq t-\ln t$ with $t$ large enough,
 \begin{align}
@@
     \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k)}\\&= C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}
-    \\&\leq C' e^{-\frac{\alpha}{16}(t-k)},
-    \quad 0\leq k\leq t-\ln t, t\text{ large enough,}
-\end{align}
-    as required in Step 2.
-
-    Step 3. We will show that there exists $C, \delta> 0$ such that
+    \leq C' e^{-\frac{\alpha}{16}(t-k)},
+\end{align}
+    as required in this step.
+
+    Step 3. We will show that there exist $C, \delta> 0$ such that for $t$ large enough,
 \[
     |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
-    \leq C t^{-\delta}, 
-    \quad t \text{ large enough}.
-\]
-    In fact, according to \eqref{thm121} and \eqref{thm122}, there exists $C,\delta > 0$ such that
+    \leq C t^{-\delta}.
+\]
+    In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C,\delta > 0$ such that
+    for $0\leq k\leq t-\ln t$ with $t$ large enough,
 \[
     \tilde{\mathbb P}_\mu\big[|Y_{t,k}|\big] 
-    \leq C e^{-\delta(t-k)},
-    \quad 0\leq k\leq t-\ln t, t\text{ large enough.}
-\]
-    Therefore, there exists $C, \delta > 0$ and $C'$ such that 
+    \leq C e^{-\delta(t-k)}.
+\]
+    Therefore, there exist $C, \delta > 0$ and $C'$ such that for $t$ large enough,
 \begin{align}
@@
     = C'\frac{1}{t^{\delta}},
-    \quad t \text{ large enough,}
-\end{align}
-    as required in Step 3.
+\end{align}
+    as required in this step.
 
@@
 \end{align*}
-	From this and \eqref{Theorem123}, we get the required result in Step 4.
+	From this and \eqref{Theorem123}, we get the required result in this step.
 
@@
 
-	Finally, according to Step 3,4 and 5, we complete the proof of Theorem \ref{Theorem12}.
+	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{Theorem12}.
 
 \subsection{Proof of Theorem \ref{Theorem11}}
-	%For any $f\in \mathcal{P}$, we rewrite
-	Fix a $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$.
+	Fix  $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$.
 	Fix $\mu \in \mathcal M_c(\mathbb R^d)$.
@@
 \end{align}
-%	where $\tilde{f}=\sum_{|p|> \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p$. 
-	Therefore
+	Then
 \begin{align*}
     &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
-    %e^{-(\alpha-\kappa_fb)t}\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle.
     \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle,
@@
 	According to Lemma \ref{lemma26}, 
-	%we easily get that,  for any $0< \gamma<\beta$,
 	we have
@@
 \label{as convergence}
-     %e^{-(\alpha-\kappa_fb)t}\sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \langle \phi_p,X_t\rangle 
      \sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p
-     %\rightarrow \sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,  \quad  t\rightarrow \infty,
      \xrightarrow[t\to \infty]{} \sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
 \end{align}
-	in $\mathbb{P}_{\mu}$-a.s. and in $L_{1+\gamma}(\mathbb{P}_{\mu})$ with arbitrary $\gamma\in(0,\beta)$.
-%	$\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. 
+$\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
 	Therefore, it is suffice to show that
@@
 \end{align}
-	%It suffices to show that $\lim_{t\rightarrow \infty}J_t=0$, $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
-	convergence in $L_{1+\gamma}(\mathbb{P}_{\mu})$ with arbitrary $\gamma\in(0,\beta)$, and convergence a.s.ly provided $f\in C^2(\mathbb R^d)$.
+	converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$.
 
 	Step 1. Let $g\in \mathcal P$. 
-	Let $a > 0$ satisfies that $a< \kappa_g$ and $a < \frac{\alpha \beta}{b(1+\beta)}$. 
-	We will show that for each $\gamma\in (0,\beta)$ there exists constants $C,\delta > 0$ such that
+	Let $a > 0$ be such that $a< \kappa_g$ and $a < \frac{\alpha \beta}{b(1+\beta)}$. 
+	We will show that for each $\gamma\in (0,\beta)$ there exist constants $C,\delta > 0$ such that
 \[
@@
 	In order to do this, we choice a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, for each $\gamma \in [\gamma_0, \beta)$, we have $a < \frac{\alpha\gamma}{b(1+\gamma)}$.
-	Then, according to Lemma \ref{lem: control moment}, we verify that, for each $\gamma \in (0,\beta)$,
+	Then, according to Lemma \ref{lem: control moment}, we have, for each $\gamma \in (0,\beta)$,
 \begin{enumerate}
 \item 
-	%When $\alpha\gamma>\kappa_{\tilde{f}}(1+\gamma)b$
 	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
@@
     \leq C  e^{-(\kappa_g - a)bt},
-    \quad t\geq 0.
+    \quad t\geq 0;
 \]
@@
      = C t e^{-(\frac{\alpha \gamma}{1+\gamma} - ab)t},
-     \quad t\geq 0.
-\]
-\item 
-	%When $\alpha\gamma>\kappa_{\tilde{f}}(1+\gamma)b\geq (\kappa_f+1)(1+\gamma)b$
+     \quad t\geq 0;
+\]
+\item 
 	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
@@
      = C  e^{-(\frac{\alpha \gamma}{1+\gamma} - ab)t},
-     \quad t\geq 0.
-\]
-\item
-	if $\gamma \in (0,\gamma_0)$ then, thanks to the above (1-3), and the fact that $\|J_t\|_{\mathbb{P}_{\mu};1+\gamma} 
-	\leq \|J_t\|_{\mathbb{P}_{\mu};1+\gamma_0}$, there exists $C, \delta >0$ such that
+     \quad t\geq 0;
+\]
+\item
+	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above, and the fact that $\|J_t\|_{\mathbb{P}_{\mu};1+\gamma} 
+	\leq \|J_t\|_{\mathbb{P}_{\mu};1+\gamma_0}$, there exist $C, \delta >0$ such that
 \[
@@
 \end{enumerate}
-	Thus, we get the desired conclusion in Step 1. 
-	In particular, by taking $g = \tilde f$ and $a = \kappa_f$, this implies that $J_t$ convergence to $0$ in $L_{1+\gamma}(\mathbb{P}_{\mu})$ with arbitrary $\gamma\in(0,\beta)$.
+	Thus, the desired conclusion in this step is valid. 
+	In particular, by taking $g = \tilde f$ and $a = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
 
 	Step 2.
-	Further assume that $f\in C^2(\mathbb R^d)$, we will show that $J_t$ convergence to $0$ as surely.
+	Further assume that $f\in C^2(\mathbb R^d)$, we will show that $J_t$ converges to $0$ almost surely.
 	Define
@@
 \end{align}
-	Now choice $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enouph to $\kappa_f$ such that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$. 
+	Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$. 
 	According to \eqref{defmartingale}, we have
@@
 \end{align*}
-	So we only have to show that
+	So we only need to show that
 \begin{align*}
@@
 	Notice that $\kappa_{(L+a_0 b)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
-	So according to Step 1, for an arbitrary fixed $\gamma\in (0,\beta)$, there exists $C, \delta>0$ such that for each $t\geq 0$,
+	So according to Step 1, for an arbitrary fixed $\gamma\in (0,\beta)$, there exist $C, \delta>0$ such that for each $t\geq 0$,
 \begin{align}
@@
 \end{align}
-	Now, by triangle inequality, for each $t\geq 0$,
+	Now, by the triangle inequality, for each $t\geq 0$,
 \begin{align*}
@@
 \end{align*}
-	Noticing that $Y_t^{\tilde{f},a_0}$ is increasing with $t$, so it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-	As a consequence, as surely we have
+Since $Y_t^{\tilde{f},a_0}$ is increasing in $t$, so it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+	As a consequence, almost surely we have
 \begin{align*}
@@
 \end{align*}
-	This implies that the martingale convergence as surely. 
+	This implies that the martingale converges almost surely. 
 	As a consequence, 
@@
 
-	The proof is completed.
+	The proof is now complete.
+
 \subsection{Proof of Theorem \ref{Theorem13}}
-	Let $f\in \mathcal P$ satisfy that $\alpha \beta < \kappa_f b(1+\beta)$. 
-	Let $t_0 > 1$ be large enough such that 
+	Let $f\in \mathcal P$ be such that $\alpha \beta < \kappa_f b(1+\beta)$. 
+	Let $t_0 > 1$ be large enough so that 
 \[
@@
     Let $\theta\in \mathbb{R}$. 
-    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get that there exists $C,\delta > 0$ such that
+    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get that there exist $C,\delta > 0$ such that
 \begin{align*}
@@
 \end{align*}
-    Hence, according to \eqref{msmallcase}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \eta_2$ with respect to $\tilde {\mathbb P}_\mu$.
-    So we only have to prove that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3$ with respect to $\tilde {\mathbb P}_\mu$.
+    Hence, according to \eqref{msmallcase}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \eta_2$ under $\tilde {\mathbb P}_\mu$.
+    So we only need to prove that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3,$ under $\tilde {\mathbb P}_\mu$.
 
     Step 1. We will show that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
-    Define
+    Define for $k\geq 0$ and $t\geq k+1$,
 \begin{align*}
     Y'_{t,k}
-    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big),
-    \quad k\geq 0, t\geq k+1.
+    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big).
 \end{align*}
@@
 \begin{align}
-\label{ineq: control of I1t}
+\label{ineq: control of I1tb}
     |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}] - \mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}'_1(t)}]|
@@
 \end{align}
-	Let $\gamma\in (0,\beta)$ be close enouph to $\beta$ such that
+	Let $\gamma\in (0,\beta)$ be close enough to $\beta$ so that
 \[
@@
 \]
-	Define $\mathcal D_{t,k}$ and $K_{t,k}$ using \eqref{def: Dtk} and \eqref{def: Ktk} respectively.
-	According to \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and the similar arguement in \eqref{eq: control of Ykt} we have that there exists $C,C'>0$ such that
+	Define $\mathcal D_{t,k}$ and $K_{t,k}$ as in \eqref{def: Dtk} and \eqref{def: Ktk} respectively.
+	Using \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and an argument similar to that used in proving \eqref{eq: control of Ykt}, we get that there exist $C,C'>0$ such that for $0 \leq k \leq t - \ln t$ with $t$ large enough,
 \begin{align*}
@@
     \\& \leq C e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-\frac{3\alpha}{32}(t-k)} + Ce^{-\frac{\alpha \beta}{32}(t-k)}
-    \\& \leq C'( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)}),
-    \\&& \mathllap{\quad 0 \leq k \leq t - \ln t, t \text{ large enough}.}
-\end{align*}
-	Note that $\alpha\beta<\kappa_f(1+\beta)b$, so we have  
+    \\& \leq C'( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)}).
+\end{align*}
+Since $\alpha\beta<\kappa_f(1+\beta)b$,  we have  
 \begin{align}
@@
 \end{align}
-	Using this, we have that there exists $C > 0$ such that
+	Using this, we have that there exists $C > 0$ such that for $0 \leq k \leq t - \ln t$ with $t$ large enough,
 \begin{align*}
@@
     \\& \leq C( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)})
-    \\& \leq C( e^{-\frac{\alpha}{16}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)}),
-    \quad 0 \leq k \leq t - \ln t, t \text{ large enough}.
-\end{align*}
-	Then we can prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ using same arguement in the Step 3 in Section \ref{sec: proof of thm 1.3}.
+    \\& \leq C( e^{-\frac{\alpha}{16}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)}).
+\end{align*}
+Now we can use the same argument as in Step 3 in Section \ref{sec: proof of thm 1.3} to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
 
@@
 	Let $\gamma \in (0,\beta)$.
-	According to \eqref{eq: condition for supercritical}, we can choice $\epsilon > 0$ small enough such that
+	According to \eqref{eq: condition for supercritical}, we can choose $\epsilon > 0$ small enough so that
 \[
@@
 	According to Lemma \ref{lem: control of XT}, there exists
-	$C>0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal E_t^c)\leq C e^{-\epsilon \beta t},~t\geq 0$.
+	$C>0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal E_t^c)\leq C e^{-\epsilon \beta t}$
+	for all $t\geq 0$.
 	Therefore, there exists $C>0$ such that
@@
 \end{align}
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that for all
+	$t\ge t_0$, 
 \begin{align*}
@@
     &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{qt} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-qk}\\
-    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\\
-    &\leq C'' e^{-\frac{\epsilon}{1+\beta} t} t^q,
-    \quad t\geq t_0.
-\end{align*}
-	Therefore, we get the required result in Step 2.
+    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\leq C'' e^{-\frac{\epsilon}{1+\beta} t} t^q.
+\end{align*}
+	Therefore, we get the required result in this step.
 
@@
 \end{align}
-	The proof is compeleted.
+	The proof is complete.
 
@@
 \subsection{}
-    In this subsection, we present some analytic fasts that will be useful.
+    In this subsection, we present some analytic facts that will be useful.
 \begin{lem}
 \label{lem: estimate of exponential remaining}
-    Suppose that $z\in \mathbb C_+:= \{x+iy: x \in [0,\infty), y \in \mathbb R\}$. Then
+    Suppose that $z\in \mathbb C_+$. Then
 \begin{equation}
@@
     Notice that $|e^{-z}| = e^{- \operatorname{Re} z} \leq 1$.
-    Therefore, according to \cite[Theorem 7.20.]{Rudin1987Real},
+    Therefore, according to \cite[Theorem 7.20]{Rudin1987Real},
 \begin{equation}
@@
     Also, notice that $|e^{-z} - 1| \leq |e^{-z}|+1 \leq 2$.
-    So we have \eqref{eq: estimate of exponential remaining} is true when $n = 0$.
+    Thus \eqref{eq: estimate of exponential remaining} is true when $n = 0$.
     Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb Z_+$.
-    According to \cite[Theorem 7.20.]{Rudin1987Real},
+    According to \cite[Theorem 7.20]{Rudin1987Real},
 \begin{align}
@@
     which says that \eqref{eq: estimate of exponential remaining} is true for $n = m + 1$.
-    Finally, use induction.
+    The proof is complete.
 \end{proof}
@@
 \label{lem: extension lemma for branching mechanism}
-    Suppose that  $\nu$ is a measure on $(0,\infty)$ such that $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$. Then the following function $h: \mathbb C_+ \to \mathbb C$ is well defined:
-\begin{equation}
-    h (z) = \int_{(0,\infty)} (e^{-zu} - 1 + zu) \nu(du), \quad z \in \mathbb C_+.
-\end{equation}
-    Moreover, $h$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}$ with deriavative
-\begin{equation}
-\label{eq: deriavetive of the Poission part}
+    Suppose that  $\nu$ is a measure on $(0,\infty)$ such that $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$. Then 
+\begin{equation}
+    h (z) = \int_{(0,\infty)} (e^{-zu} - 1 + zu) \nu(du), \quad z \in \mathbb C_+,
+\end{equation}
+is well defined.
+    Moreover, $h$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with 
+\begin{equation}
+\label{eq: deriavetive of the Poission partb}
     h'(z) = \int_{(0,\infty)}(1- e^{-uz})u \nu(du).
@@
     According to \cite[Theorem 3.2.
-\& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, \eqref{eq: deriavetive of the Poission part} defines a continuous function $h'$ on $\mathbb C_+$ which is holomorphic on $\mathbb C_+^0$.
+\& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, \eqref{eq: deriavetive of the Poission partb} defines a continuous function $h'$ on $\mathbb C_+$ which is holomorphic on $\mathbb C_+^0$.
     Let $z_0, z \in \mathbb C_+$.
@@
 \end{align}
-    Therefore, according to Fubini's theorem and \cite[Theorem 7.20.]{Rudin1987Real},
+    Therefore, according to Fubini's theorem and \cite[Theorem 7.20]{Rudin1987Real},
 \begin{align}
@@
 \end{align}
-    The rest of the proof follows the arguement in \cite[Section 10.14]{Rudin1987Real}.
+    The rest of the proof follows the argument in \cite[Section 10.14]{Rudin1987Real} and we omit the details.
 \end{proof}
 
-	For each $z\in \mathbb C\setminus (-\infty,0]$ define
-\[
-	\log z := \log |z| + i \arg z
+	For each $z\in \mathbb C\setminus (-\infty,0]$, define
+\[
+	\log z := \log |z| + i \arg z,
 \]
@@
 \] 	
-	For each $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$ define
+	For all $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$, define
 \[
@@
 \]
-	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, $z\mapsto \log z$ is holomophic on $\mathbb C\setminus (-\infty,0]$.
-	Therefore, so is $z\mapsto z^\gamma$, for each $\gamma \in \mathbb C$.
-	For convention, define $0^\gamma := \mathbf 1_{\gamma = 0}$ for each $\gamma \in \mathbb C$.
-    From this definition we can verify that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
-
-    Recall $\Gamma$ the Gamma function defined by
+	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, $z\mapsto \log z$ is holomorphic on $\mathbb C\setminus (-\infty,0]$.
+	Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic on $\mathbb C\setminus (-\infty,0]$.
+(We use the convention tha  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
+    From this definition we can show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
+
+    Recall that $\Gamma$ the Gamma function defined by
 \begin{equation}
@@
 \end{equation}
-	It is known, see \cite[Theorem 6.1.3 and its following remark]{SteinShakarchi2003Complex} for example, function $\Gamma$ has an unique analytic extension on $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
+	It is known, see \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it for example, the function $\Gamma$ has an unique analytic extension on $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
 \[
@@
 \]
-	Using this recursively, one can verify that
+	Using this recursively, one get that
 \begin{align}
@@
     Fix a $\beta \in (0,1)$.
-    Using the uniqueness of holomorphic extension and \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that
+    Using the uniqueness of holomorphic extension and \cite[Theorem 3.2 \& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, we get that
 \begin{equation}
@@
 \end{itemize}
-    Similarly, using Lemma \ref{lem: extension lemma for branching mechanism} in the Appendix, we can verify that
+    Similarly, using Lemma \ref{lem: extension lemma for branching mechanism}, we get that
 \begin{equation}
@@
 \end{align}
-    This also verifies that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
+    This also shows that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
 \begin{lem}
 \label{lem: Lip of power function}
-    There is a constant $(1+\beta)$ such that for any $z_0,z_1 \in \mathbb C_+$,
+    There is a constant $(1+\beta)$ such that for all $z_0,z_1 \in \mathbb C_+$,
 \begin{equation}
@@
 	Then according to \cite[Lemma 7.6]{Sato1999Levy}, there is a unique continuous function $f(\theta)$ from $\mathbb R$ into $\mathbb C$ such that $f(0) = 0$ and $e^{f(\theta)} = \varphi(\theta)$. 
-	Such function $f$ is called the distinguished logarithm of function $\varphi$ and is denoted as $\operatorname{Log} \varphi(\theta)$.
-	In particular, let $\varphi$ be the characteristic function of an infinitely divisible random variable $Y$, then $h$ is called the Levy exponent of $Y$. 
+	Such a function $f$ is called the distinguished logarithm of the function $\varphi$ and is denoted as $\operatorname{Log} \varphi(\theta)$.
+	In particular, let $\varphi$ be the characteristic function of an infinitely divisible random variable $Y$, then $h$ is called the L\'evy exponent of $Y$. 
 	This distinguished logarithm should not be confused with the $\log$ function defined on $\mathbb C\setminus (-\infty, 0]$.
@@
     Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact seperable metric space $E$.
-    %For brevity, for each $0< s< t< \infty$ and each bounded complex valued measurable function $\rho$ on $[0,\infty) \times E$, we write
     Fix a time $t >0$.
-    For each $0< s< t$ and each bounded complex valued measurable function $\rho$ on $[0,t) \times E$, we write
+    For all $s\in (0,  t)$ and  bounded complex valued Borel function $\rho$ on $[0,t) \times E$, we write
 \begin{equation}
@@
 \end{equation}
-    %Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,\infty) \times E$; $F$ is a complex valued bounded measurable function on $E$.
-    Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,t) \times E$; $F$ is a complex valued bounded measurable function on $E$.
-%delete
-    %Fix a time $t >0$.
-%end delete
+    Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,t) \times E$ and that  $F$ is a complex valued bounded measurable function on $E$.
     Define
@@
 \end{align}
-    Therefore, from the Markov property of $\xi$ and Fubini's theorem we can verify that
+    Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
 \begin{align}
@@
 \label{sec: definition of superprocess}
-    We say $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a $(\xi,\psi)$-superprocess if
+Let $E$ be locally compact separable metric space. Denote by $\mathcal M_E^1$ the collection of all the finite measures on $E$ equipped with weak topology.
+    Recall that $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is said to be a $(\xi,\psi)$-superprocess if
 \begin{itemize}
 \item
-    The sample space $E$ is a locally compact separable metric space.
-    Denote by $\mathcal M_E^1$ the collection of all the finite measures on $E$ equipped with weak topology.
-\item
     The spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$.
 \item
-    %the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
     The branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
@@
 \item
-    $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is an $\mathcal M^1_E$-valued Hunt process with is transition probability determined by
+    $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is an $\mathcal M^1_E$-valued Hunt process with transition probability determined by
 \begin{align}
@@
 
-    Notice that, the branching mechanism $\psi$ can be extended as a map from $E \times \mathbb C_+$ to $\mathbb C$ using \eqref{eq: branching mechanism}.
+    Notice that, the branching mechanism $\psi$ can be extended into a map from $E \times \mathbb C_+$ to $\mathbb C$ using \eqref{eq: branching mechanism}.
     Define
@@
 \end{itemize}
-    We refer to $(\mathbb N_x)_{x\in E}$ the Kuznetsov measures of $X$.
+    We refer to $(\mathbb N_x)_{x\in E}$ as the Kuznetsov measures of $X$.
 \subsection{}
@@
     Assume that the superprocess $X$ is non-presistent with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
-    It is know from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for any $t > 0$, $\mu \in \mathcal M_E^1$ and $f\in b\mathscr B^+_E$,
+    It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M_E^1$ and $f\in b\mathscr B^+_E$,
 \begin{equation}
@@
     Let $f\in L_1(\xi), t >0$ and $x\in E$.
-    Evaluating \eqref{eq: mean formula for superprocesses} by monotonicity and linearity, we have
+    Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
 \begin{equation}
@@
     Notice that, from the branching property of the superprocess $X$, $\{X_t(f); \mathbf P_{\delta_x}\}$ is an infinitely divisible random variable with finite moment.
-    Denote by $U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}]$  the charateristic exponent of random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
+({\bf Do you want to say mean or higher moment?})
+    Denote by $U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}]$  the charateristic exponent of the random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
     According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, for each $\theta \in \mathbb R$,
@@
 \]
-    is well defined. Firstly, we only assume that $f\in L^1(\xi)$.
+    is well defined. First, we only assume that $f\in L^1(\xi)$.
     Noticing that
@@
 \end{equation}
-%new added
-    Therefore, it is legal to talk about $\psi(x,-U_tf)$since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
+    Therefore, we can talk about $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
     According to Lemma \ref{lem: estimate of exponential remaining}, we have that
@@
     From the dominate convergence theorem, we can verify that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
-    In another words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
+    In other words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
     According to this and \eqref{eq: path integration representation of h}, we can write
@@
 \\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty  P^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\beta_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
-\\ &=: C_1 + C_2(P^\beta_t |f|)(x).
+\\ &=: C_1 + C_2(P^\beta_t |f|)(x),
 \end{split}
 \end{equation}
-    where $C_1, C_2$ are constants not dependent on $f,x$ and $t$.
+    where $C_1, C_2$ are constants independent on $f,x$ and $t$.
     Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have
@@
 \end{align}
-	As a consequence, expectation
+	As a consequence, the expectation
 \[
@@
 	Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}. 
-	In this subsection, we will proof the following:
+	In this subsection, we will prove the following:
 	\begin{prop}
 \label{prop: complex FKPP-equation}
-    Let $f\in L_2(\xi)$. Then for each $t\geq 0$ and $x\in E$,
+    If $f\in L_2(\xi)$,  then for all $t\geq 0$ and $x\in E$,
 \begin{equation}
@@
     U_tf(x) - \Pi_x \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f\big) ds \Big]
-    \\= i \Pi_x [f(\xi_t)],
+    \\= i \Pi_x [f(\xi_t)]
 \end{equation}
@@
 
-    To do this, we will need the generalized spine decomposition theorem for the superprocesses \cite{RenSongSun2017Spine} which we now recall.
+    To prove this, we will need the generalized spine decomposition theorem from \cite{RenSongSun2017Spine} which we now recall.
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
@@
 \end{itemize}
-    According to the spine decomposition theorem \cite{RenSongSun2017Spine}, we have that
+    According to the spine decomposition theorem in \cite{RenSongSun2017Spine}, we have that
 \begin{align}
@@
     Assume that $f\in b\mathscr B_E$.
-    Set $t>0, r\in [0,t), x\in E$ and $g\in b\mathscr B_E^{++}$.
-    Denoted by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
-    %Given $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$.
+    Fix $t>0, r\in [0,t), x\in E$ and $g\in b\mathscr B_E^{++}$.
+    Denote by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
     Conditioned on $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$ in \eqref{eq: conditional intensity}.
     Denote by $\Pi_{r,x}$ the probability of Hunt process $\{\xi; \Pi\}$ initiated at time $r$ and position $x$.
-    From Lemma \ref{lem: estimate of exponential remaining}, we have $\mathbf Q^{(g,t)}_{x}$-a.s.ly
+    From Lemma \ref{lem: estimate of exponential remaining}, we have $\mathbf Q^{(g,t)}_{x}$-almost surely
 \begin{align}
@@
 \end{align}
-    According to this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-a.s.ly,
+    AUsing this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-almost surely,
 \begin{align}
@@
 \end{equation}
-    Using \eqref{eq: N to Pi} and above, we have
+    Using \eqref{eq: N to Pi} and the above, we have
 \begin{align}
@@
     Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
-
 \[
     \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]
-    = \Pi_{r,x} [i f(\xi_t)],
+    = \Pi_{r,x} [i f(\xi_t)]
 \]
@@
 \begin{align}
-    \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]
-    = \Pi_{r,x} [i e^{\int_r^t \beta(\xi_s)ds}f(\xi_t)].
-\end{align}
-    Integrating the aboves with respect to $\theta$  on [0,1], using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we have
-
+    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
+    &= \Pi_{r,x} [i e^{\int_r^t \beta(\xi_s)ds}f(\xi_t)].
+\end{align}
+    Integrating the two displays above with respect to $\theta$  on [0,1], using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get
 \begin{equation}
     U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-U_{t-s}f\big) ~ds\Big]
-    = i\theta \Pi_{r,x} [f(\xi_t)],
-\end{equation}
-    and similarly,
+    = i\theta \Pi_{r,x} [f(\xi_t)]
+\end{equation}
+    and 
 \begin{equation}
@@
 \end{equation}
-    Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} is true if $f\in b\mathscr B_E$.
-
-    %Now assume that $f\in L_2(\xi)$.
+    Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} are true if $f\in b\mathscr B_E$.
+
     The rest of the proof is to evaluate \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} for all $f\in L_2(\xi)$.
 We only do this for \eqref{eq: complex FKPP-equation} since the argument for \eqref{eq: complex FKPP-equation with FK-transform} is similar.
-    Set $n \in \mathbb N$.
-    Writing $f_n := (f^+ \wedge n) - (f^- \wedge n)$, then $f_n \xrightarrow[n\to \infty]{} f$ pointwisely.
+    Let $n \in \mathbb N$.
+    Writing $f_n := (f^+ \wedge n) - (f^- \wedge n)$, then $f_n \xrightarrow[n\to \infty]{} f$ pointwise.
     From what we have proved, we have
@@
 \item
-     $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$ due to \eqref{eq: N and characteristic exponent}, dominated convergence theorem and the fact that
+     $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$ due to \eqref{eq: N and characteristic exponent}, the dominated convergence theorem and the fact that
 \[
@@
 \item
-     $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to donimated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
+     $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
 \begin{align}
@@
 \end{itemize}
-    Using the above arguements, letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
+    Using the above arguments, letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
 \end{proof}
-%end new add
 

### 2019-01-31 supCLT.tex
supCLT1209.tex

@@
 %%%----Versions-----------------------------
+% supclt1209.tex 2018/12/07 by Zhenyao
 % supclt1207.tex 2018/12/07 by Renming
@@
 %\subjclass[2010]{60J80, 60F05}
-%\keywords{}
+%\keywords{}p
 %\date{}
@@
 \begin{abstract}
-    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$. For each testing function $f$ 
-%    with polynomial growth, 
-of at most polynomial growth,
-    denote by $\kappa_f$ the order of $f$ in term of the spectral decomposition of $f$ 
-%    with respect to the mean semigroup of $X$. 
-in terms of the spectrum of the the mean semigroup of $X$. 
-    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$
-%    convergences weakly. 
-converges weakly.
-    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ 
-%    convergences weakly. 
-converges weakly.
-    In the large branching rate case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ 
-%   convergences a.s and in $L^{1+\gamma}$, with $\gamma \in (0,\beta)$.
-converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$.
+    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$.
+For each testing function $f$ of at most polynomial growth,
+    denote by $\kappa_f$ the order of $f$ in term of the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 
+    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
+    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.
+    In the large branching rate case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$.
 \end{abstract}
@@
     Let $d \in \mathbb N:= \{1,2,\dots\}$ and
-    %\deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
     $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator 
-%$L$ such that
 \begin{equation}
@@
 
-	The existence of superprocesses is well known, see \cite{EB} for instance.
+	The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.
     According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
@@
     Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
-\begin{comment}
-
-	\deleted{
-	For each $\kappa\geq0$, define $\mathcal{P}_{\kappa}$ by
-	\begin{align}
-	     \mathcal{P}_{\kappa}
-    :=\big \{f\in \mathcal{P}:\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ \sup_{t\geq0}e^{\kappa b t}|T_tf(x)|\leq C(1+|x|)^n\big\}.
-	\end{align}
-	and an operator $Q_{\kappa}:\mathcal{P}_{\kappa}\mapsto\mathcal{P}\cap\mathscr{B}(\mathbb{R}^d,\mathbb{R}_+)$ by $Q_{\kappa}f=\sup_{t\geq0}e^{\kappa b t}|T_tf|$.
-	Then
-	\begin{itemize}
-	    \item For each $\kappa_1\geq \kappa_2$, $\mathcal{P}_{\kappa_1}\subset\mathcal{P}_{\kappa_2}$, and $\mathcal{P}=\cup_{\kappa\geq 0}\mathcal{P}_{\kappa}$.
-	    \item for each $f\in \mathcal{P}$, then $f\in \mathcal{P}_{\kappa_f}$, and $Q_{\kappa}f\leq Qf:=Q_{\kappa_f}f$, $\kappa\leq \kappa_f$.
-
-	\end{itemize}
-	}
-\end{comment}
 \subsection{}
@@
  $$\psi(z) := -\alpha z + z^{1+\beta}, \quad z\in \mathbb C_+.$$ 
-%    According to the above analysis, 
     According to the analysis in Subsection A.1, 
@@
 
-     Moreover, if $f$ is twice differentiable and 
-%     its twice derivative $D^2 f$ satisfies $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
-all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
+     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence. 
  \end{thm}
@@
      $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
-    Moreover, if $f$ is twice differentiable and 
-%    $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
-all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
+    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
  \end{rem}
@@
     For $f\in \mathcal{P}$, define
-$$\tilde{m}[f]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
+\[
+    \tilde{m}[f]
+    := \langle(-i\phi)^{1+\beta},\varphi\rangle
+\]
     where
-$$\phi(x)=\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).$$
+\[
+    \phi(x)
+    =\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).
+\]
     Denote by $D$ the extinction event of the super OU-process.
-\begin{thm}\label{Theorem12}
+\begin{thm}
+\label{Theorem12}
     If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-$$\frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
+\[
+    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
+    \xrightarrow{d} \eta_1, 
+    \quad t\rightarrow \infty,
+\]
     where $\eta_1$ is a $(1+\beta)$-stable random variable with
-$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\tilde{m}[\theta f]), \quad \theta\in \mathbb R.$$
+\[
+    \mathbb{E} [e^{i\theta \eta_1}]
+    =\exp(\tilde{m}[\theta f]), 
+    \quad \theta\in \mathbb R.
+\]
 \end{thm}
@@
 For $f\in \mathcal{P}$, define
-$$m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx$$
-\begin{thm}\label{Theorem13}
+\[
+    m[f]
+    :=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx
+\]
+\begin{thm}
+\label{Theorem13}
     If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
@@
 \section{Preliminaries}
-\begin{comment}
-
-\deleted{	
-	In this case we have
-\begin{align}
-    I_a^b[\langle g,X_t\rangle]
-    = I_a^b\big[\mathbb P[\langle g,X_t\rangle|\mathscr F_b]\big]
-    = I_a^b[ \langle T_{t-b}^\alpha g, X_b \rangle ].
-\end{align}
-}
-\end{comment}
 
@@
 \label{lem: property of controllable operators}
-%    Let operators $(A_\lambda)_{\lambda\in \Lambda}$ be uniformly $\gamma$-controllable on $\mathcal D \subset \mathcal P^*$:
     Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$.
@@
 \item[(3)]
- %   Suppose that operators $(B_\delta)_{\delta \in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta\in \mathbb R$.
     Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
@@
     Let $p=(p_1,...,p_d)\in \mathbb Z_+^d$, recall that $\phi_p$ is an eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
-$$H_t^p:=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.$$
+\[
+    H_t^p
+    :=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.
+\]
 
@@
     Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $\gamma\in (0, \beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
-$$H_{\infty}^p:=\lim_{t\rightarrow \infty}H_t^p$$
+\[
+    H_{\infty}^p
+    :=\lim_{t\rightarrow \infty}H_t^p
+\]
 exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
@@
     Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that there exists a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$)  such that
- $$
+\[
  	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
@@
     =C_{\gamma, \mu, p}, \quad t\geq 0.
- $$
+\]
     For any $\gamma\in (0, \gamma_0)$, note that
-$$
+\[
 	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
@@
 	\quad t\geq 0.
-$$
+\]
 
@@
  For all $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for all $0\leq s<t$,
- $$
- \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq C 
- %e^{-\alpha s/2}.
- e^{-\frac{\alpha \gamma}{1+\gamma}s}.
- $$
+\[
+    \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C e^{-\frac{\alpha \gamma}{1+\gamma}s}.
+\]
 \end{lem}
@@
     Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
-%    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
     By \eqref{CSBP} and the Markov property we have for all $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
@@
 \end{proof}
-
-%	It turns out that we need to evaluate the previous Lemma into the following:
 
@@
 
-   We first show that
-\begin{align}
-    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
-    \xrightarrow[t\to \infty]{} 0.
-\end{align}
-By\cite[Lemma 3.4.3.]{Durrett2010Probability},
+By \cite[Lemma 3.4.3.]{Durrett2010Probability},
 \begin{align}\label{ineq: control of I1t}
@@
 \end{align*}
+    Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
+\[
+    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
+\]
+    Fix this $\gamma$, then chose $\eta_0,\eta_1>0$ such that
+\[
+    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
+\]
     Define for all $k \geq 0$ and $t\geq k+1$,
@@
 \label{def: Dtk}
-    \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, H_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\}.
-\end{align}
-
-    Step 1. We will show that there exists a $C>0$ such that for all $k \geq 0$ and $t\geq k+1$,
+    %\mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, H_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\}.
+    \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
+\end{align}
+
+    Step 1. We will show that there exists a $C,\delta >0$ such that for all $k \geq 0$ and $t\geq k+1$,
 \begin{align}
@@
     \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\big]
-    \leq C e^{-\frac{\alpha\beta}{32}(t-k-1)}.
-\end{align}
-    Fix a $\gamma \in (0,\beta)$.
-    Let $C_1$ be the constant in  Lemma \ref{lem: control of Wt} corresponding to this $\gamma$ and $C_2$ be the constant in Lemma \ref{lem: control of XT}. 
-    ({\bf The next display needs to be revised because of the corrected statement of Lemma 2.9.
-    The whole proof needs to be changed accordingly.})
+    \leq C e^{-\delta (t-k)}.
+\end{align}
+    In fact, let $C_1$ be the constant in  Lemma \ref{lem: control of Wt} corresponding to the fixed $\gamma$ and $C_2$ be the constant in Lemma \ref{lem: control of XT}. 
     By Chebyshev's inequality, there exists $C>0$ such that for all $k \geq 0$ and $t\geq k+1$,
@@
     &\mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
-    \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}|\geq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq \|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}),
-    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}\|\mu\|^{-1}e^{\frac{\alpha}{4}(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]+\mathbb{\tilde{P}}(H_{t-k-1}\leq\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)})
-    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1} \|\mu\|^{-1} e^{\frac{\alpha}{4}(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}+\mathbb{\tilde{P}}(H_{t-k-1}\leq\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)})
-    \\&\leq C_1  \mathbb{P}_{\mu}(D^c)^{-1} \|\mu\|^{-1} e^{-\frac{\alpha}{4}(t-k-1)}+C_2\|\mu\|^{\beta}e^{-\frac{\alpha\beta}{32}(t-k-1)}
-    \leq Ce^{-\frac{\alpha\beta}{32}(t-k-1)}.
-\end{align}
-    This implies the desired result in Step 1.
-
-    Step 2. We will show that there exists constant $C > 0$ such that for all 
-    $0\leq k\leq t-\ln t$ with $t$ large enough,
+    \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}),
+    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]+\mathbb{\tilde{P}}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
+    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}+\mathbb{\tilde{P}}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
+    \\&\leq C_1  \mathbb{P}_{\mu}(D^c)^{-1}  e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C_2 e^{-\eta_1\beta(t-k-1)}.
+\end{align}
+    This implies the desired result in Step 1, since $|Y_{t,k}| \leq 2$ a.s..
+
+    Step 2. We will show that there exists constant $C,\delta > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
 \begin{align}
@@
      \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-     \leq  C e^{-\frac{\alpha}{16}(t-k)}.
+     \leq  C e^{-\delta (t-k)}.
 \end{align}
@@
         \\&\leq|\theta|t^{-\frac{1}{1+\beta}} \mathbb{\tilde{P}}_{\mu}\bigg[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot\Big|\frac{1}{(e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\bigg]
-        \\&=|\theta|t^{-\frac{1}{1+\beta}}e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
+        \\&\leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
 \end{align}
@@
 \end{equation}
-    Note that for all $0 < x< y$, we have for $t$ large enough,
-\[
-    1-e^{-(y-x)t} 
-    \geq e^{-xt},
-\]
-    since the left side converges to $1$ and the right side converges to $0$.
-    Therefore, by taking $x= \frac{\alpha}{32}$ and $y= \frac{\alpha}{4}$, we have 
-    for $t$ large enough,
-\[
-    e^{-\frac{\alpha t}{32} } - e^{-\frac{\alpha t}{4}}
-    \geq e^{- \frac{\alpha t}{32}}(1 - e^{-(\frac{1}{4} - \frac{1}{32})\alpha t})
-    \geq e^{- \frac{\alpha t}{16}},
-\]
-Thus for $0\leq k\leq t-\ln t$ with $t$ large enough,
+    Note that, since $\eta_1 < \eta_0$, we have
 \begin{align*}
     H_t
-    &\geq H_{t-k-1}-\|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}
-    \geq\|\mu\|\left(e^{-\frac{\alpha}{32}(t-k-1)}-e^{-\frac{\alpha}{4}(t-k-1)}\right)
-    \\&\geq \|\mu\| e^{-\frac{\alpha}{16}(t-k-1)},
+    &\geq H_{t-k-1}- e^{-\eta_0(t-k-1)}
+    \geq 2e^{-\eta_1(t-k-1)}-e^{-\eta_0(t-k-1)}
+    \\&\geq e^{-\eta_1(t-k-1)},
     \quad \text{ on } \mathcal D_{t,k}.
 \end{align*}
-    Therefore, for $0\leq k\leq t-\ln t$ with $t$ large enough,
+    Therefore, for each $k \geq 0$ and $t\geq k+1$,
 \begin{align*}
-     \left|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\right|
+     \Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
      &\leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
-    \\&\leq \frac{1}{1+\beta}\|\mu\|^{\frac{1}{1+\beta}} \max\left\{e^{\frac{\alpha}{16}(t-k-1)}, e^{\frac{\alpha}{32}(t-k-1)}\right\}e^{-\frac{\alpha}{4}(t-k-1)}\\
-    &=\frac{1}{1+\beta}\|\mu\|^{\frac{1}{1+\beta}}  e^{-\frac{3\alpha}{16}(t-k-1)},
+    \\&\leq \frac{1}{1+\beta} \max\{e^{\eta_1 (t-k-1)}, \frac{1}{2}e^{\eta_1(t-k-1)}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0(t-k-1)}
+    \\&\leq \frac{1}{1+\beta} e^{\eta_1 (t-k-1)} e^{-\eta_0(t-k-1)}
+    =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)},
     \quad \text{ on } \mathcal D_{t,k}, 
@@
     |H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}|
-    \geq \|\mu\|^{\frac{2}{1+\beta}} e^{-\frac{3\alpha}{32}(t-k-1)},
+    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1(t-k-1)},
     \quad \text{ on } \mathcal D_{t,k}.
 \end{align*}
-    Thus, there is a constant $C\geq 0$ such that  for $0\leq k\leq t-\ln t$ with $t$ large enough,
+    Thus, there is a constant $C\geq 0$ such that,
 \begin{align}
@@
      K_{t,k}
-     \leq C e^{-\frac{3\alpha}{32}(t-k-1)}.
-\end{align}
-    Now fix $\gamma \in (0, \beta)$ close enough to $\beta$ so that 
-\[
-    \frac{1}{1+\gamma} - \frac{1}{1+\beta} 
-    \leq \frac{1}{32}.
-\]
-    From the condition $\alpha\beta=\kappa_f(1+\beta)b$, we get that 
-\begin{align}
-    &\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}
-    = -\alpha(1-\frac{1}{1+\gamma}) + \alpha(1-\frac{1}{1+\beta})
-    \\&= -\frac{\gamma \alpha}{1+\gamma} + k_f b
-    =-\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
-\end{align}
-    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt}, \eqref{ineq: control of Kkt} and the above, there exist constants $C,C'>0$ such that  for $0\leq k\leq t-\ln t$ with $t$ large enough,
+     \leq C e^{-(\eta_0 - 3\eta_1)(t-k-1)},
+     \quad k \geq 0, t\geq k+1.
+\end{align}
+    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt}, \eqref{ineq: control of Kkt}, there exist constants $C,C'>0$ such that  for all $k\geq 0$ and $t\geq k+1$,
 \begin{align}
@@
     &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \leq C|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
-    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-\frac{3\alpha}{32}(t-k-1)}
-    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-\frac{3\alpha}{32}(t-k)}
-    \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k)}\\&= C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k-1)}
-    \leq C' e^{-\frac{\alpha}{16}(t-k)},
-\end{align}
-    as required in this step.
+    \leq C|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
+    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
+    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta_0 - 3\eta_1)(t-k - 1)}
+    \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}\\&= C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k-1)},
+\end{align}
+    as required in step 2. 
+    In the last equality, we used the fact that
+\[
+    -(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})
+    = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta})
+    = \frac{\gamma \alpha}{1+\gamma} - k_f b
+    =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
+\]
 
@@
     In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C,\delta > 0$ such that
-    for $0\leq k\leq t-\ln t$ with $t$ large enough,
+    for all $k \geq 0$ and $t\geq k+1$ we have,
 \[
@@
 \]
-    Therefore, there exist $C, \delta > 0$ and $C'$ such that for $t$ large enough,
+    Therefore, there exist $C, \delta > 0$ and $C'$ such that for all $t \geq 1$,
 \begin{align}
@@
 
-    Step 4. We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$.
+    Step 4. We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\tilde{P}}_{\mu}$.
     In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Lemma \ref{lem: control of XT}, there exists $C>0$ such that
@@
 \end{align}
-	Let $\gamma\in (0,\beta)$ be close enough to $\beta$ so that
-\[
-	\frac{1}{1+\gamma} - \frac{1}{1+\beta} \leq \frac{1}{32}.
+    Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
+\[
+    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
+\]
+    Fix this $\gamma$, then chose $\eta_0,\eta_1>0$ such that
+\[
+    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
 \]
 	Define $\mathcal D_{t,k}$ and $K_{t,k}$ as in \eqref{def: Dtk} and \eqref{def: Ktk} respectively.
-	Using \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and an argument similar to that used in proving \eqref{eq: control of Ykt}, we get that there exist $C,C'>0$ such that for $0 \leq k \leq t - \ln t$ with $t$ large enough,
+	Using Lemma \ref{lem: control of mgtrs}, \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and an argument similar to that used in proving \eqref{eq: control of Ykt}, we get that there exist $C,C',\delta>0$ such that for $k\geq 0$ and $t\geq k+1$,
 \begin{align*}
@@
     \\& \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\tilde{P}}_{\mu}( \mathcal D_{t,k}^c )
-    \\& \leq C e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-\frac{3\alpha}{32}(t-k)} + Ce^{-\frac{\alpha \beta}{32}(t-k)}
-    \\& \leq C'( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-\frac{3\alpha}{32}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)}).
+    \\& \leq C e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-(\eta_0 - 3\eta_1)(t-k)} + Ce^{-\delta(t-k)}
+    \\& \leq C'( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta(t-k)}).
 \end{align*}
@@
 \end{align}
-	Using this, we have that there exists $C > 0$ such that for $0 \leq k \leq t - \ln t$ with $t$ large enough,
+	Using this, we have that there exists $C,C',
+    \delta > 0$ such that for $k\geq 0$ and $t\geq k+1$,
 \begin{align*}
     &\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
-    \\& \leq C( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-\frac{3\alpha}{32}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)})
-    \\& \leq C( e^{-\frac{\alpha}{16}(t-k)}+ e^{-\frac{\alpha \beta}{32}(t-k)}).
+    \\& \leq C( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta(t-k)})
+    \\& \leq C'e^{-\delta (t-k)}.
 \end{align*}
@@
 	\mathcal E_t
-	:=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon )t}\},
+	:=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
 	\quad t\geq 0.
@@
     &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
-    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
+    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
     \\&\leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
@@
 \end{align}
-	The proof is complete.
+	The proof is completed.
 
@@
 
-\subsection{}
+\subsection{Analytic facts}
     In this subsection, we present some analytic facts that will be useful.
@@
     Notice that $|e^{-z}| = e^{- \operatorname{Re} z} \leq 1$.
-    Therefore, according to \cite[Theorem 7.20]{Rudin1987Real},
+    %Therefore, according to \cite[Theorem 7.20]{Rudin1987Real},
+    Therefore,
 \begin{equation}
@@
     Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb Z_+$.
-    According to \cite[Theorem 7.20]{Rudin1987Real},
+    %According to \cite[Theorem 7.20]{Rudin1987Real},
+    We have
 \begin{align}
@@
     = \Big| \int_0^1\Big(e^{-\theta z} - \sum_{k=0}^m \frac{(-\theta z)^k}{k!} \Big) z d\theta \Big|
-    %\\&\quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} z d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} z d\theta\Big)
     \\&\quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} |z| d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} |z| d\theta\Big)
@@
 \label{lem: extension lemma for branching mechanism}
-    Suppose that  $\nu$ is a measure on $(0,\infty)$ such that $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$. Then 
-\begin{equation}
-    h (z) = \int_{(0,\infty)} (e^{-zu} - 1 + zu) \nu(du), \quad z \in \mathbb C_+,
-\end{equation}
-is well defined.
-    Moreover, $h$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with 
+%%%
+%Suppose that  $\nu$ is a measure on $(0,\infty)$ such that $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$. Then 
+%\begin{equation}
+%    h (z) = \int_{(0,\infty)} (e^{-zu} - 1 + zu) \nu(du), \quad z \in \mathbb C_+,
+%\end{equation}
+%is well defined.
+%    Moreover, $h$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with 
+%\begin{equation}
+%\label{eq: deriavetive of the Poission partb}
+%    h'(z) = \int_{(0,\infty)}(1- e^{-uz})u \nu(du).
+%\end{equation}
+    Suppose that  $\nu$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$. 
+    Then functions
+\begin{equation}
+    h (z) = \int_{(0,\infty)} (e^{-zu} - 1 + zu) \nu(du), \quad z \in \mathbb C_+
+\end{equation}
+and
 \begin{equation}
 \label{eq: deriavetive of the Poission partb}
-    h'(z) = \int_{(0,\infty)}(1- e^{-uz})u \nu(du).
-\end{equation}
+    h'(z) = \int_{(0,\infty)}(1- e^{-uz})u \nu(du), \quad z \in \mathbb C_+
+\end{equation}
+    are well defined, continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
+    Moreover, 
+\[
+    \frac{h(z)-h(z_0)}{z-z_0} \xrightarrow[\mathbb C_+\ni z \to z_0]{} h'(z_0),\quad z_0 \in \mathbb C_+.
+\] %%
 \end{lem}
 \begin{proof}
-    From Lemma \ref{lem: estimate of exponential remaining}, we know that $h$ is well defined on $\mathbb C_+$.
-    According to \cite[Theorem 3.2.
+    %From Lemma \ref{lem: estimate of exponential remaining}, we know that $h$ is well defined on $\mathbb C_+$.
+    From Lemma \ref{lem: estimate of exponential remaining}, we know that $h$ and $h'$ are well defined on $\mathbb C_+$. %%
+    %According to \cite[Theorem 3.2.
 \& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, \eqref{eq: deriavetive of the Poission partb} defines a continuous function $h'$ on $\mathbb C_+$ which is holomorphic on $\mathbb C_+^0$.
-    Let $z_0, z \in \mathbb C_+$.
-    Let $\gamma: [0,1]\mapsto \mathbb C_+$ be a $C^1$ path with $\gamma(0) = z_0$ and $\gamma(1) = z$.
-    Notice that, according to Lemma \ref{lem: estimate of exponential remaining},
-\begin{align}
-    &\int_0^1 \int_0^\infty |1-e^{-u\gamma(\theta)}|u~\nu(du)~d\theta
-    \\ &= \int_0^1~d\theta~ \Big( \int_0^1 |1-e^{-u\gamma(\theta)}|u~\nu(du) + \int_1^\infty |1-e^{-u\gamma(\theta)}|u~\nu(du) \Big)
-    \\ &\leq \int_0^1~d\theta~ \Big( |\gamma(\theta)|\int_0^1 u^2~\nu(du) + 2\int_1^\infty u~\nu(du) \Big)
-    < \infty.
-\end{align}
-    Therefore, according to Fubini's theorem and \cite[Theorem 7.20]{Rudin1987Real},
-\begin{align}
-\label{eq: path integration representation of h}
-    \int_\gamma h'(z)dz
-    &=\int_0^1 h'(\gamma(\theta))\gamma'(\theta) ~d\theta
-    = \int_0^1 \int_0^\infty (1-e^{-u\gamma(
-    \theta)}) u~\nu(du)~ \gamma'(\theta) ~d\theta
-    \\&= \int_0^\infty \int_0^1 (1-e^{-u\gamma(
-    \theta)})~ \gamma'(\theta) u ~d\theta~ \nu(du)
-    = h(z) - h(z_0).
-\end{align}
-    The rest of the proof follows the argument in \cite[Section 10.14]{Rudin1987Real} and we omit the details.
+    According to \cite[Theorem 3.2. \& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
+
+%    Let $z_0, z \in \mathbb C_+$.
+%    Let $\gamma: [0,1]\mapsto \mathbb C_+$ be a $C^1$ path with $\gamma(0) = z_0$ and $\gamma(1) = z$.
+%    Notice that, according to Lemma \ref{lem: estimate of exponential remaining},
+%\begin{align}
+%    &\int_0^1 \int_0^\infty |1-e^{-u\gamma(\theta)}|u~\nu(du)~d\theta
+%    \\ &= \int_0^1~d\theta~ \Big( \int_0^1 |1-e^{-u\gamma(\theta)}|u~\nu(du) + \int_1^\infty |1-e^{-u\gamma(\theta)}|u~\nu(du) \Big)
+%    \\ &\leq \int_0^1~d\theta~ \Big( |\gamma(\theta)|\int_0^1 u^2~\nu(du) + 2\int_1^\infty u~\nu(du) \Big)
+%    < \infty.
+%\end{align}
+%    Therefore, according to Fubini's theorem and \cite[Theorem 7.20]{Rudin1987Real},
+    From Lemma \ref{lem: estimate of exponential remaining}, for each $z_0 \in \mathbb C_+$, we have that there exists $C>0$ such that
+\begin{align}
+    &\Big| \frac{e^{-zu} - e^{-z_0u}+(z-z_0) u}{z-z_0} \Big|
+    = \frac{1}{|z-z_0|}\Big| \int_0^1 \big(-ue^{-(\theta z+(1-\theta)z_0)u}+u\big)(z-z_0)d\theta\Big|
+    \\ &\leq u\int_0^1 |1-e^{-(\theta z +(1-\theta)z_0)u}| d\theta 
+    \leq (2u) \wedge\Big( u^2\int_0^1|\theta z+(1-\theta)z_0|d\theta\Big)
+    \\ &\leq C(u\wedge u^2),
+    \quad z \in \mathbb C_+ \text{ close enough to } z_0, u>0.
+\end{align}
+    Using this and dominated convergence theorem, we have
+\begin{align}
+    &\frac{h(z)-h(z_0)}{z-z_0} = \int_{(0,\infty)} \frac{e^{-zu}+zu -(e^{-z_0u}+z_0u)}{z-z_0}  \nu(du) 
+    \\&\xrightarrow[\mathbb C_+\ni z\to z_0]{} \int_{(0,\infty)}(1 - e^{-z_0u} )u\nu(du) = h'(z_0),
+\end{align}
+    which says that $h$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
 \end{proof}
@@
 	For each $z\in \mathbb C\setminus (-\infty,0]$, define
-\[
-	\log z := \log |z| + i \arg z,
-\]
+$
+	\log z := \log |z| + i \arg z
+$
 	where $\arg z \in (-\pi,\pi)$ is uniquely determined by
-\[
+$
 	z = |z|e^{i \arg z}.
-\] 	
+$ 	
 	For all $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$, define
-\[
+$
 	z^\gamma := e^{\gamma \log z}.
-\]
+$
 	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, $z\mapsto \log z$ is holomorphic on $\mathbb C\setminus (-\infty,0]$.
@@
     Fix a $\beta \in (0,1)$.
-    Using the uniqueness of holomorphic extension and \cite[Theorem 3.2 \& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, we get that
+    %Using the uniqueness of holomorphic extension and \cite[Theorem 3.2 \& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, we get that
+    Using the uniqueness of holomorphic extension and Lemma \ref{lem: extension lemma for branching mechanism}, we get that
 \begin{equation}
@@
 \item
-    are extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
+    %are extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
+    are extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
 \item
-    are holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$;
+    %are holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$;
+    are holomorphic on $\mathbb C_+^0$;
 \item
-    are continuous on $\mathbb C_+ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}$.
+    %are continuous on $\mathbb C_+ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}$.
+    are continuous on $\mathbb C_+$.
 \end{itemize}
-    Similarly, using Lemma \ref{lem: extension lemma for branching mechanism}, we get that
+    %Similarly, using Lemma \ref{lem: extension lemma for branching mechanism}, we get that
+    Similarly, we get that
 \begin{equation}
@@
 \end{equation}
-    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\to \mathbb C_+$ ,
-\begin{align}
-\label{eq: integration formula for 1+beta-th power of z}
-    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta}
-    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
-    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}}
-    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
-\end{align}
-    This also shows that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
+%    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\to \mathbb C_+$ ,
+%\begin{align}
+%\label{eq: integration formula for 1+beta-th power of z}
+%    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta}
+%    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
+%    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}}
+%    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
+%\end{align}
+%    This also shows that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
+    Lemma \ref{lem: extension lemma for branching mechanism} also says that the derivative of $z^{1+\beta}$ is $(1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
 \begin{lem}
 \label{lem: Lip of power function}
-    There is a constant $(1+\beta)$ such that for all $z_0,z_1 \in \mathbb C_+$,
+    %There is a constant $(1+\beta)$ such that for all $z_0,z_1 \in \mathbb C_+$,
+    For each $z_0,z_1 \in \mathbb C_+$, we have
 \begin{equation}
@@
 \begin{proof}
+%added
+    Since $z^{1+\beta}$ is continuous on $\mathbb C_+$, we only have to proof the Lemma assuming $z_0,z_1 \in \mathbb C^0_+$.
+%end added
     Notice that
@@
 \end{align}
-    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
+    %Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
+    Define a path $\gamma: [0,1] \to \mathbb C^0_+$ such that
 \[
@@
 \]
-    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
+    %Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
+    Then, we have
 \begin{align}
@@
 
-\subsection{}
+\subsection{Feynman-Kac formula with complex values}
 \label{seq: complex Feynman-Kac transform}
-%new added
     In this subsection we give a version of the Feynman-Kac formula with complex values.
-%end new added
     Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact seperable metric space $E$.
-    Fix a time $t >0$.
-    For all $s\in (0,  t)$ and  bounded complex valued Borel function $\rho$ on $[0,t) \times E$, we write
-\begin{equation}
-    H^{(\rho)}_{(s,t)}:= \exp\Big\{\int_s^t \rho(u,\xi_u) du\Big\}.
-\end{equation}
+%    Fix a time $t >0$.
+%    For all $s\in (0,  t)$ and  bounded complex valued Borel function $\rho$ on $[0,t) \times E$, we write
+%\begin{equation}
+%    H^{(\rho)}_{(s,t)}:= \exp\Big\{\int_s^t \rho(u,\xi_u) du\Big\}.
+%\end{equation}
+    Write
+\begin{equation}
+    H^{(h)}_{(s,t)}
+    := \exp\Big\{\int_s^t h(u,\xi_u) du\Big\},
+    \quad 0 \leq s \leq t, h \in \mathcal B_b([0,t] \times E,\mathbb C).
+\end{equation}
+%deleted
+%    Notice that
+%\begin{equation}
+%\label{eq: crucial for Feynman-Kac}
+%    \frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
+%    \quad s\in (0,t).
+%\end{equation}
+%end deleted
+%    Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,t) \times E$ and that $F$ is a complex valued bounded measurable function on $E$.
+%    Define
+%\begin{equation}
+%    g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\beta+\rho)} F(\xi_t)],\quad r \in [0,t), x\in E.
+%\end{equation}
+\begin{lem}
+    Let $t \geq 0$. Suppose that $\beta,\rho\in \mathcal B_b([0,t] \times E, \mathbb C)$ and $f\in \mathcal B_b(E, \mathbb C)$.
+    Then 
+\begin{equation}
+    g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\beta+\rho)} f(\xi_t)],\quad r \in [0,t], x\in E,
+\end{equation}
+    is the unique solution to the equation
+\[
+    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\beta)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\beta)}\rho(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
+\]
+\end{lem}
+%    Notice that
+%\begin{align}
+%    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} F(\xi_t)| ~ds \Big]
+%    \leq  \int_r^t e^{(t-r)\|\beta\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|F\|_\infty ~ds
+%    < \infty.
+%\end{align}
+%    Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
+%\begin{align}
+%    &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\beta)}~(\rho g)(s,\xi_s)~ds \Big]
+%    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\beta)}\rho(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\beta+\rho)} F(\xi_t)]~ds \Big]
+%    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} F(\xi_t) ~ds \Big]
+%    = \Pi_{r,x} [ H_{(r,t)}^{(\beta)}F(\xi_t)(H_{(r,t)}^{(\rho)} - 1)]
+%    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\beta)} F(\xi_t)].
+%\end{align}
+\begin{proof}
+    The proof is similar to the proof of \cite[Lemma A.1.5]{Dynkin1993Superprocesses}. We included it for the sake of completeness.
     Notice that
+\begin{align}
+    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t)| ~ds \Big]
+    \leq  \int_r^t e^{(t-r)\|\beta\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|f\|_\infty ~ds
+    < \infty.
+\end{align}
+    Also notice that
 \begin{equation}
@@
     \frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
-    %\quad s> 0.
     \quad s\in (0,t).
 \end{equation}
-    Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,t) \times E$ and that  $F$ is a complex valued bounded measurable function on $E$.
-    Define
-\begin{equation}
-    g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\beta+\rho)} F(\xi_t)],\quad r \in [0,t), x\in E.
-\end{equation}
-    Notice that
-\begin{align}
-    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} F(\xi_t)| ~ds \Big]
-    \leq  \int_r^t e^{(t-r)\|\beta\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|F\|_\infty ~ds
-    < \infty.
-\end{align}
     Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
@@
     &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\beta)}~(\rho g)(s,\xi_s)~ds \Big]
-    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\beta)}\rho(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\beta+\rho)} F(\xi_t)]~ds \Big]
-    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} F(\xi_t) ~ds \Big]
-    = \Pi_{r,x} [ H_{(r,t)}^{(\beta)}F(\xi_t)(H_{(r,t)}^{(\rho)} - 1)]
-    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\beta)} F(\xi_t)].
-\end{align}
-
-\subsection{}
+    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\beta)}\rho(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\beta+\rho)} f(\xi_t)]~ds \Big]
+    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t) ~ds \Big]
+    = \Pi_{r,x} [ H_{(r,t)}^{(\beta)}f(\xi_t)(H_{(r,t)}^{(\rho)} - 1)]
+    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\beta)} f(\xi_t)].
+\end{align}
+%added
+    For the uniqueness, suppose that $\tilde g$ is another solution. Writting $h(r) = \sup_{x\in E}|g(r,x) - \tilde g(r,x)|$, we have
+\[
+    h(r) \leq e^{t\|\beta\|_\infty}\|\rho\|_\infty \int_r^t h(s)ds,
+    \quad r\le t.
+\]
+    According to \cite[Lemma A.1.5]{Dynkin1993Superprocesses}, this says that $h(r) =  0$ for $r\in [0,t]$.
+%end added
+\end{proof}
+
+\subsection{Superprocesses}
 \label{sec: definition of superprocess}
+%added
+    In this subsection, we will give the definition of the superprocesses that are considered in this Appendix.
+%end added
 Let $E$ be locally compact separable metric space. Denote by $\mathcal M_E^1$ the collection of all the finite measures on $E$ equipped with weak topology.
@@
 \end{align}
-    where for each $f\in b\mathscr B_E$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
+    where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
 \begin{align}\label{eq:FKPP_in_definition}
@@
 \end{itemize}
-    We refer to $(\mathbb N_x)_{x\in E}$ as the Kuznetsov measures of $X$.
-\subsection{}
+    We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
+\subsection{{Semigroups for superprocesses}}
 \label{sec: definition of vf}
-    Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.
+    %Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.
+    %Assume that the superprocess $X$ is non-presistent with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
+    Let $X$ be the non-presistent superprocess defined in Subsection \ref{sec: definition of superprocess} with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
     Define the mean semigroup
@@
     := \Pi_{x}[e^{\int_0^t \beta(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
-    \quad t\geq 0, x\in E, f\in b\mathscr B^+_E.
-\end{equation}
-    Assume that the superprocess $X$ is non-presistent with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
-    It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M_E^1$ and $f\in b\mathscr B^+_E$,
+    \quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
+\end{equation}
+    It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M_E^1$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
 \begin{equation}
@@
 \end{equation}
+
     Define
@@
     L_1(\xi)
-    &:= \{f\in \mathscr B_E: \forall x\in E, t\geq 0, \quad \Pi_x[|f(\xi_t)|]< \infty\},
+    &:= \{f\in \mathcal B(E): \forall x\in E, t\geq 0, \quad \Pi_x[|f(\xi_t)|]< \infty\},
     \\L_2(\xi)
-    &:= \{f \in \mathscr B_E: |f|^2 \in L_1(\xi)\}.
-\end{align}
-    Let $f\in L_1(\xi), t >0$ and $x\in E$.
+    &:= \{f \in \mathcal B(E): |f|^2 \in L_1(\xi)\}.
+\end{align}
+    %Let $f\in L_1(\xi), t >0$ and $x\in E$.
     Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
@@
     \mathbb N_x[W_t(f)]
-    =\mathbf P_{\delta_x}[X_t(f)]=P^\beta_t f(x) \in \mathbb R.
-\end{equation}
-    Notice that, from the branching property of the superprocess $X$, $\{X_t(f); \mathbf P_{\delta_x}\}$ is an infinitely divisible random variable with finite moment.
-({\bf Do you want to say mean or higher moment?})
-    Denote by $U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}]$  the charateristic exponent of the random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
-    According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, for each $\theta \in \mathbb R$,
-$   \mathbf P_{\delta_x} [e^{i\theta X_t(f)}]
-    = \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]).
-$
-    Notice that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function.
-    Also notice that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$.
-    Therefore, according to \cite[Lemma 7.6]{Sato1999Levy}, we have
+    =\mathbf P_{\delta_x}[X_t(f)]=P^\beta_t f(x) \in \mathbb R,
+%added
+    \quad f\in L_1(\xi), t > 0,x\in E.
+%end added
+\end{equation}
+%added
+    This says that random variables $X_t(f)$ are well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
+%end added
+    %Notice that, from the branching property of the superprocess $X$, $\{X_t(f); \mathbf P_{\delta_x}\}$ is an infinitely divisible random variable with finite moment.
+%({\bf Do you want to say mean or higher moment?})
+    According to the branching property of the superprocess, they are infinitely divisible random variables.
+    %Denote by $U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}]$  the charateristic exponent of the random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
+    Therefore, we can write 
+\[
+    U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}],
+%added    
+    \quad t\geq 0, f\in L_1(\xi), \theta \in \mathbb R, x\in E,
+%end added
+\] 
+    %the charateristic exponent of the random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
+    as their charateristic exponent.
+    %According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, for each $\theta \in \mathbb R$,
+%$   \mathbf P_{\delta_x} [e^{i\theta X_t(f)}]
+%    = \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]).
+%$
+    According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
+\[   
+    \mathbf P_{\delta_x} [e^{i\theta X_t(f)}]
+    = \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]),
+    \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
+\]
+    %Notice that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function.
+    %Also notice that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$.
+    %Therefore, according to \cite[Lemma 7.6]{Sato1999Levy}, we have
+    Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato1999Levy}, we have
 \begin{equation}
 \label{eq: N and characteristic exponent}
-    U_tf(x) = \mathbb N_x[e^{i W_t(f)} - 1]
-    \quad t \geq 0.
-\end{equation}
-
-    We claim that if $f\in L^2(\xi)$ then the following expectation
-\[
-    \Pi_x\Big[\int_0^t \psi(\xi_s,- U_{t-s}f)ds\Big]
-    \in \mathbb C
-\]
-    is well defined. First, we only assume that $f\in L^1(\xi)$.
+    %U_tf(x) = \mathbb N_x[e^{i W_t(f)} - 1],
+    U_t(\theta f)(x) = \mathbb N_x[e^{i W_t(\theta f)} - 1],
+    %\quad t \geq 0.
+    \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
+\end{equation}
+
+%added
+\begin{lem}
+    There exists constants $C_1, C_2\geq 0$ such that for each $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
+\begin{align}
+\label{eq: upper bound of psi(v)}
+    \big|\psi\big(x,-U_tf\big)\big|
+    \leq C_1 P^\beta_t |f|(x)+C_2 P^\beta_t |f| (x)^2.
+\end{align}
+\end{lem}
+\begin{proof}
      Noticing that
@@
     \mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
-    \leq \mathbb N_x[|W_t(f)|] \leq (P^\beta_t |f|)(x) < \infty.
+    \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta| \leq (P^\beta_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
 \end{equation}
@@
     In other words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
-    According to this and \eqref{eq: path integration representation of h}, we can write
+    According to this, we have
 \begin{equation}
@@
     where $C_1, C_2$ are constants independent on $f,x$ and $t$.
-    Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have
-
-\begin{align}
-\label{eq: upper bound of psi(v)}
-    \big|\psi\big(x,-U_tf\big)\big|
-    \leq C_1 P^\beta_t |f|(x)+C_2 P^\beta_t |f| (x)^2.
-\end{align}
-    Now assume that $f \in L_2(\xi) \subset L_1(\xi)$.
-    Then, using Jensen's inequality and the above, we have that
+    Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have get the desired result.
+\end{proof}
+%end added
+
+    %We claim that if $f\in L^2(\xi)$ then the following expectations
+    This Lemma also says that if $f\in L^2(\xi)$ then the following expectations
+\[
+    \Pi_x\Big[\int_0^t \psi(\xi_s,- U_{t-s}f)ds\Big]
+    \in \mathbb C,
+%added
+    \quad x\in E, t\geq 0.
+%end added
+\]
+    are well defined. 
+%    First, we only assume that $f\in L^1(\xi)$.
+%    Noticing that
+%\[
+%     e^{\operatorname{Re} U_tf(x)}
+%    = |e^{U_tf(x)}|
+%    = |\mathbf P_{\delta_x}[e^{i X_t(f)}]|
+%    \leq 1,
+%\]
+%    we have
+%\begin{equation}
+%\label{eq: -v has positive real part}
+% \operatorname{Re} U_tf(x)
+%    \leq 0.
+%\end{equation}
+%    Therefore, we can talk about $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
+%    According to Lemma \ref{lem: estimate of exponential remaining}, we have that
+%\begin{equation}
+%\label{eq: upper bound for vf}
+%    |U_tf(x)| \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
+%    \leq \mathbb N_x[|i W_t(f)|]
+%    \leq (P^\beta_t |f|)(x).
+%\end{equation}
+%    Notice that, for any compact $K \subset \mathbb R$,
+%\begin{equation}
+%\label{eq: estimate of deriavetive of v(theta)}
+%    \mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
+%    \leq \mathbb N_x[|W_t(f)|] \leq (P^\beta_t |f|)(x) < \infty.
+%\end{equation}
+%    Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability},
+%    $U_t(\theta f)(x)$ is differentiable in $\theta \in \mathbb R$ with
+%\[
+%    \frac{\partial}{\partial \theta} U_t(\theta f)(x)
+%    = i\mathbb N_x[W_t(f)e^{i\theta W_t(f)}],
+%    \quad \theta \in \mathbb R.
+%\]
+%    Moreover, from the above, it is clear that
+%\begin{equation}
+%\label{eq: upper bounded for derivative of v(theta)}
+%    \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
+%    \leq ( P^\beta_t |f|)(x).
+%\end{equation}
+%    From the dominate convergence theorem, we can verify that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
+%    In other words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
+%    According to this and \eqref{eq: path integration representation of h}, we can write
+%\begin{equation}
+%\label{eq: path integration representation of psi(v)}
+%    \psi(x,-U_tf) = -\int_0^1 \psi'\big(x,-U_t(\theta f)\big) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
+%\end{equation}
+%    Notice that
+%\begin{equation}
+%\label{eq: upper bound of psi'(v)}
+%\begin{split}
+%    &|\psi'(x, -U_tf)|
+%    \\&= \Big| -\beta(x)- 2\alpha(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
+%    \\&= \Big| - \beta(x)- 2\alpha(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi%(x,dy) \Big|
+%\\ &\leq \|\beta\|_\infty + 2\alpha(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
+%\\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty  P^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\beta_t |f|(x) + 2%\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
+%\\ &=: C_1 + C_2(P^\beta_t |f|)(x),
+%\end{split}
+%\end{equation}
+%    where $C_1, C_2$ are constants independent on $f,x$ and $t$.
+%    Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have
+%\begin{align}
+%\label{eq: upper bound of psi(v)}
+%    \big|\psi\big(x,-U_tf\big)\big|
+%    \leq C_1 P^\beta_t |f|(x)+C_2 P^\beta_t |f| (x)^2.
+%\end{align}
+%    Now assume that $f \in L_2(\xi) \subset L_1(\xi)$.
+    In fact, using Jensen's inequality and the markovian property, we have 
 \begin{align}
@@
 \end{align}
-	As a consequence, the expectation
-\[
-     \Pi_x\Big[\int_0^t \psi(\xi_s,-U_{t-s}f)ds\Big]
-    \in \mathbb C
-\]
-    is well defined for all $f\in L_2(\xi)$.
+%deleted
+%	As a consequence, the expectation
+%\[
+%     \Pi_x\Big[\int_0^t \psi(\xi_s,-U_{t-s}f)ds\Big]
+%    \in \mathbb C
+%\]
+%    is well defined for all $f\in L_2(\xi)$.
+%end deleted
 
@@
     Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
-    Let $f\in b\mathscr B_E^{++}$, $T >0$ and $x\in E$.
-    The fact that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^\beta_T f(x) \in (0,\infty)$ allows us to define the following probability transforms:
+    Let $f\in \mathcal B_b(E,\mathbb R_+)$, $T >0$ and $x\in E$.
+    Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^\beta_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
 \begin{equation}
@@
     \mathbf m(\xi,ds,dw)
-    %:= 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
     := 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
@@
 \begin{proof}[Proof of Proposition \ref{prop: complex FKPP-equation}]
-    Assume that $f\in b\mathscr B_E$.
-    Fix $t>0, r\in [0,t), x\in E$ and $g\in b\mathscr B_E^{++}$.
+    Assume that $f\in \mathcal B_b(E)$.
+    Fix $t>0, r\in [0,t), x\in E$ and $g\in \mathcal B_b(E)^{++}$.
     Denote by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
@@
 \end{align}
-    AUsing this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-almost surely,
+    Using this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-almost surely,
 \begin{align}
@@
 \end{equation}
-    Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} are true if $f\in b\mathscr B_E$.
+    Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} are true if $f\in \mathcal B_b(E)$.
 
@@
 
-\bibitem{EB}
+\bibitem{Dynkin1993Superprocesses}
 Dynkin,~E.B.

### 2019-01-31 supCLT.tex
supCLT.tex: 1213

@@
 %%%----Versions-----------------------------
+% supclt1213.tex 2018/12/13 by Renming
 % supclt1209.tex 2018/12/07 by Zhenyao
@@
 \address
+   {Renming Song\\
+   Department of Mathematics\\
+   University of Illinois\\
+   Urbana, IL 61801, USA}
+   \email{rsong@illinois.edu}
+   \thanks{The research of Renming Song is supported in part by a grant from the Simons Foundation (\# 429343, Renming Song)}
+\address
     {Zhenyao Sun\\
@@
 For each testing function $f$ of at most polynomial growth,
-    denote by $\kappa_f$ the order of $f$ in term of the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 
+    denote by $\kappa_f$ the order of $f$ in 
+%term of the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 
+the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 
     Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
@@
 \section{Introduction}
-\subsection{Model}
+%\subsection{Model}
+\subsection{Model}\label{ss:1.1}
     Let $d \in \mathbb N:= \{1,2,\dots\}$ and
@@
 
-\subsection{OU semigroup}
+\subsection{OU Semigroup}
     In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
@@
 $
-	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
+	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|
 $
@@
 \subsection{}
-    Let $X$ be the super OU-process discussed in the first subsection.
+    Let $X$ be the super OU-process discussed in Subsection \ref{ss:1.1}.
     Its branching mechanism $\psi$ can be extended to $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$:
@@
 \end{equation}
-    Write $\psi_0(z) := \psi(z) + \alpha z$. Then$\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
+    Write $\psi_0(z) := \psi(z) + \alpha z$. Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
     For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
@@
 \subsection{Main Result}
-
-In this subsection, we will give the main results of this paper. Suppose $\mu\in \mathcal M_c(\mathbb R_d)$ has compact support.
-\subsubsection{Large Branching Rate}
+We will use $\mathcal M_c(\mathbb R_d)$ to denote the space of all
+finite Borel measures of compact support on $\mathbb R^d$.
+In this subsection, we will give the main results of this paper. 
+%Suppose $\mu\in \mathcal M_c(\mathbb R_d)$ has compact support.
+\subsubsection{Large branching rate}
 
@@
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
-  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in 
+%  $L^{1+\gamma}(\mathbb{P}_{\mu})$, 
+$L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\mu\in \mathcal M_c(\mathbb R_d)$,
+  thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  \begin{thm}\label{Theorem11}
-     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for any $\gamma\in (0, \beta)$,
+     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for 
+%     any $\gamma\in (0, \beta)$,
+any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$,
      as $t\rightarrow \infty$,
@@
 For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s.
-and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$.
  \begin{rem}
-    If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},  for any $\gamma\in (0, \beta)$, as $t\rightarrow \infty$
+%    If $\kappa_f=0$, 
+Let $f \in \mathcal{P}$.  If $\kappa_f=0$, 
+    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},  
+%    for any $\gamma\in (0, \beta)$, as $t\rightarrow \infty$
+for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$, as $t\rightarrow \infty$,
      $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
@@
 
-\subsubsection{Critical Branching Rate}
+\subsubsection{Critical branching rate}
     For $f\in \mathcal{P}$, define
@@
 \label{Theorem12}
-    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, 
+%    then, under 
+   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under 
+    $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
 \[
@@
 
-\subsubsection{Small Branching Rate}
+\subsubsection{Small branching rate}
 
@@
 \label{Theorem13}
-    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, 
+%    then, under 
+   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under 
+    $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
     $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
@@
 	For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
-    Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
+    For any $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
     One of the reason for considering $\gamma$-controllable operators is that they have good algebraic properties:
@@
     and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
-    For any probability measure $\mu$ on $(\Lambda, \mathscr F)$, write
-\[
-    A_\mu f(x):= \int_{\Lambda} A_\lambda f (x)~\mu(d\lambda), \quad f\in \mathcal D, x\in \mathbb R^d.
-\]
-    Then  $\{A_\mu: \mu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $\gamma$-controllable on $\mathcal D$.
+    For any probability measure $\nu$ on $(\Lambda, \mathscr F)$, write
+\[
+    A_\nu f(x):= \int_{\Lambda} A_\lambda f (x)~\nu(d\lambda), \quad f\in \mathcal D, x\in \mathbb R^d.
+\]
+    Then  $\{A_\nu: \nu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $\gamma$-controllable on $\mathcal D$.
 \item[(2)]
@@
 Let $(R,S)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$.
-For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\mu$ on $(\Lambda, \mathscr F)$,
-\[
-   |A_{\mu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\mu(d\lambda) \leq \int_{\Lambda}R|f|(x)\mu(d\lambda) \leq R|f|(x).
+For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
+\[
+   |A_{\nu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\nu(d\lambda) \leq \int_{\Lambda}R|f|(x)\nu(d\lambda) \leq R|f|(x).
 \]
@@
 \begin{proof}
-    (1). It follows from \eqref{eq: upper bound for vf}, that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
+    (1). It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
 \[
@@
 \]
-    is uniformly $(1+\beta)$-controllable.
+    are uniformly $(1+\beta)$-controllable.
     Combining this with \eqref{eq:chareq2} and Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.
@@
  In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$. 
-Denote by $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite Borel measures on $\mathbb{R}^d$ with compact support.
+ %Denote by $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite Borel measures on $\mathbb{R}^d$ with compact support.
 	For all $0 \leq a_1 \leq a_2 <\infty$ and  random variable $Y$ with finite mean, define
@@
 \begin{lem}\label{lem: temp}
-	For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb{R}^d)$, there exist a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
+	For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb{R}^d)$, there exists a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
 \[
@@
     Suppose that $g\in \mathcal P$ satisfies $Q_\kappa g \leq h$.
-    Using the Markov property of $(X_t)_{t\geq 0}$, we get
+    Using the Markov property of $X$, we get
 \begin{align}
@@
 \label{lem: control of mgtrs}
-	For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $\gamma\in (0, \beta)$, there exist a constant $C > 0$, such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
+	For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
 \[
@@
 \label{lem: control moment}
-	For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exist a constant $C > 0$ such that for each $t\geq 0$, we have
+	For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
 \begin{itemize}
@@
 \end{align}
-    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $\{\mathscr{F}_t\}_{t\geq 0}$.
+    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
 \begin{lem}
 \label{lemma25}
-    Let $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ be such that $Lf \in \mathcal{P}$ and let $a\in \mathbb R$. Then the process $(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.
+    Let $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ be such that $Lf \in \mathcal{P}$ and let $a\in \mathbb R$. 
+%    Then the process $(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.
+Then, for any $\mu\in \mathcal M_c(\mathbb{R}^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
 \end{lem}
@@
 \begin{lem}\label{lemma26}
-    $(H^p_t)_{t\geq 0}$ is a martingale with respect to $(\mathscr F_t)$.
+%    $(H^p_t)_{t\geq 0}$ is a martingale with respect to $(\mathscr F_t)$.
+    For any $\mu\in \mathcal M_c(\mathbb{R}^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
     Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $\gamma\in (0, \beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
@@
 \begin{proof}
-   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a martingale.
+%   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a martingale.
+  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb{R}^d)$.
 
     There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
-    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that there exists a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$)  such that
+    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, 
+%    we get that there exists 
+   we get, for $\gamma\in [\gamma_0, \beta)$, that there exists 
+    a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$)  such that
 \[
@@
 \]
-    For any $\gamma\in (0, \gamma_0)$, note that
+%    For any $\gamma\in (0, \gamma_0)$, note that
+   For any $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb{R}^d)$, note that
 \[
@@
 
-    Hence, for each $\gamma \in (0,\beta)$, the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
+%    Hence, for each $\gamma \in (0,\beta)$, 
+   Hence, for each $\gamma \in (0,\beta)$ and any $\mu\in \mathcal M_c(\mathbb{R}^d)$, 
+    the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
 \end{proof}
 
-In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$  for any $\mu\in \mathcal M_c(\mathbb{R}^d)$.
 
@@
     \end{align}
-    Then there is a $C>0$, for any $0\leq s<t$,
+    Thus there is a $C>0$ for any $0\leq s<t$,
 \begin{align}
@@
 	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
-%	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
 	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}.
@@
 
-Write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+%Write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
+From now on, we write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
 \begin{lem}
@@
 \]
-    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
-    By \eqref{CSBP} and the Markov property we have for all $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
+    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger root of $\psi(z)=0$.
+    By \eqref{CSBP} and the Markov property, we have for all $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
     $t\geq 0$,
@@
 \]
-    Accodting to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, then the following limit exists:
+    According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, then the following limit exists:
 \begin{align}
@@
 \label{it: first stable}
-    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable;
 \item 
 \label{it: second stable}
-    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$.
+    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
 \item 
@@
 \end{equation}
-	According to Lemma \ref{lem: upper bound for usgx}.(2), parts (1), (2) and (4) of Lemma \ref{lem: property of controllable operators},  we know that
+	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),  we know that
 $
@@
 \end{align}
-In fact, from the definitions of $U_1, \tilde U_1$ and $Z_1$, we have
+In fact, from the definitions of $U_1, \tilde U_1$ and $Z_1$, we have that for all 
+$k\geq 0, t\geq k+1$, 
 \begin{align}
@@
     \\&=e^{\langle (U_1 - iT_{1}^{\alpha}) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle}
-    \\&=e^{\langle (U_1 - \tilde U_1+Z_1) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle},
-    \quad k\geq 0, t\geq k+1.
+    =e^{\langle (U_1 - \tilde U_1+Z_1) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle}.
 \end{align}
@@
     \end{align}
-	In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}. (6).
+	In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}.(6).
 	Then, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
@@
 
-	Step 4. We will show that for each $\epsilon\in (0,  \alpha]$ there exist $C,\delta>0$ such that
+	Step 4. We will show that, for each $\epsilon\in (0,  \alpha]$, there exist $C,\delta>0$ such that for all $k\geq0, t\geq k+1$,
 \begin{align}\label{ineq: control of J3}
-    J_3(k,t,\epsilon)\leq Ce^{-\delta (t-k-1)}\quad k\geq0, t\geq k+1.
-\end{align}
-	In fact, we have
+    J_3(k,t,\epsilon)\leq Ce^{-\delta (t-k-1)}.
+\end{align}
+	In fact, we have that for all $t\geq 0, \epsilon >0$,
 \begin{align}
@@
 	\\&= \mathbb P_\mu[e^{-\alpha^*\|X_t\|};A_t(\epsilon)]
-	\leq \exp({-\alpha^* e^{(\alpha - \epsilon)t}}),\quad t\geq 0, \epsilon >0.
+	\leq \exp({-\alpha^* e^{(\alpha - \epsilon)t}}).
 \end{align}
 According to Lemma \ref{lem: control of XT}, there is a constant $C>0$ such that
-\begin{align}
-	\mathbb P_\mu(A_t(\epsilon)^c,D^c) = \mathbb P_\mu(D^c) \tilde{\mathbb P}_\mu(\|X_t\|\leq e^{(\alpha - \epsilon) t}) \leq \mathbb P_\mu(D^c)C e^{-\epsilon \beta t},\quad t\geq 0, \epsilon >0.
+for all $t\geq 0, \epsilon >0$,
+\begin{align}
+	\mathbb P_\mu(A_t(\epsilon)^c,D^c) = \mathbb P_\mu(D^c) \tilde{\mathbb P}_\mu(\|X_t\|\leq e^{(\alpha - \epsilon) t}) \leq \mathbb P_\mu(D^c)C e^{-\epsilon \beta t}.
 \end{align}
@@
 
-	Step 5.  Combining the results in Step 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$, 
+	Step 5.  Combining the results in Steps 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$, 
 we immediately get the desired result.
@@
 \begin{cor}\label{cor: used in next corollary}
-Let $f\in \mathcal{P}$ and $\Theta >0$.
+%Let $f\in \mathcal{P}$ and $\Theta >0$.
+Let $f\in \mathcal{P}$, and $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
 Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
@@
 	where $(R,S)$ is the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}.(6).
-	From the definitions of $Z_1$ and $m_t$ we get that
-\[
-	Z_1( \pm \theta g) = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[\pm g],\quad g\in \mathcal P, \theta \geq 0, t\geq 0.
-\]
-	Therefore, we have
+	From the definitions of $Z_1$ and $m_t$ we get that for all $g\in \mathcal P, \theta \geq 0, t\geq 0$, 
+\[
+	Z_1( \pm \theta g) = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[\pm g].
+\]
+	Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$, 
 \[
 J^{\pm \theta f}_2(t,k,\epsilon)
-	:= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon), \quad \theta >0, k \geq 0, t\geq k+1, \epsilon > 0.
+	:= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon).
 \]
@@
 \begin{prop}\label{corollary31}
-Let $f\in \mathcal{P}$ and $\Theta>0$.
+%Let $f\in \mathcal{P}$ and $\Theta>0$. 
+Let $f\in \mathcal{P}$, and $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
 Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$.
@@
     For each $k\in\{-1,...,n\}$, we define
-    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big)\],
+    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),\]
      where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
@@
     \end{align*}
-    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$ we have
+    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$, we have
     \begin{align*}
@@
 
-By \cite[Lemma 3.4.3.]{Durrett2010Probability},
+By \cite[Lemma 3.4.3]{Durrett2010Probability},
 \begin{align}\label{ineq: control of I1t}
@@
 \]
-    Fix this $\gamma$, then chose $\eta_0,\eta_1>0$ such that
+    Fix this $\gamma$, then choose $\eta_0,\eta_1>0$ such that
 \[
@@
 \label{def: Dtk}
-    %\mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq \|\mu\| e^{-\frac{\alpha}{4}(t-k-1)}, H_{t-k-1}>\|\mu\|e^{-\frac{\alpha}{32}(t-k-1)}\right\}.
     \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
@@
 
-    Step 1. We will show that there exists a $C,\delta >0$ such that for all $k \geq 0$ and $t\geq k+1$,
+    Step 1. We will show that there exist $C,\delta >0$ such that for all $k \geq 0$ and $t\geq k+1$,
 \begin{align}
@@
 \end{align}
-    In fact, let $C_1$ be the constant in  Lemma \ref{lem: control of Wt} corresponding to the fixed $\gamma$ and $C_2$ be the constant in Lemma \ref{lem: control of XT}. 
+    In fact, let $C_1$ be the constant in  Lemma \ref{lem: control of Wt} corresponding to this fixed $\gamma$ and $C_2$ be the constant in Lemma \ref{lem: control of XT}. 
     By Chebyshev's inequality, there exists $C>0$ such that for all $k \geq 0$ and $t\geq k+1$,
@@
 \end{align}
-    This implies the desired result in Step 1, since $|Y_{t,k}| \leq 2$ a.s..
-
-    Step 2. We will show that there exists constant $C,\delta > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
+    This implies the desired result in this step, since $|Y_{t,k}| \leq 2$ a.s..
+
+    Step 2. We will show that there exist constant $C,\delta > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
 \begin{align}
@@
 \begin{align*}
-     \Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
-     &\leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
+     &\Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
+     \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
     \\&\leq \frac{1}{1+\beta} \max\{e^{\eta_1 (t-k-1)}, \frac{1}{2}e^{\eta_1(t-k-1)}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0(t-k-1)}
@@
 \end{align}
-    as required in step 2. 
+    as desired in this step. 
     In the last equality, we used the fact that
@@
 \end{align}
-    as required in this step.
+    giving the desired result in this step.
 
@@
 \end{align}
-    Chose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})\leq \frac{1}{2(1+\beta)}$.
+    Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})\leq \frac{1}{2(1+\beta)}$.
 	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that
@@
 \end{align*}
-	From this and \eqref{Theorem123}, we get the required result in this step.
+	From this and \eqref{Theorem123}, we get the desired result in this step.
 
@@
     =\sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
-    %=
     =:
@@
 	Further assume that $f\in C^2(\mathbb R^d)$, we will show that $J_t$ converges to $0$ almost surely.
-	Define
+	Define for $a \geq 0$ and $ t\geq 0$,
 \begin{align}
 	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,
-	\quad g\in \mathcal P\cap C^2(\mathbb R^d), a \geq 0, t\geq 0,
+	\quad g\in \mathcal P\cap C^2(\mathbb R^d),
 \end{align}
@@
     :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds, 
-    \quad g\in \mathcal P\cap C^2(\mathbb R^d), a \geq 0, t\geq 0.
+    \quad g\in \mathcal P\cap C^2(\mathbb R^d).
 \end{align}
@@
 \end{align*}
-Since $Y_t^{\tilde{f},a_0}$ is increasing in $t$, so it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+Since $Y_t^{\tilde{f},a_0}$ is increasing in $t$, it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 	As a consequence, almost surely we have
@@
  \]
-    Let $\theta\in \mathbb{R}$. 
+    Let $\theta\in \mathbb{R}$ and $\mu\in \mathcal M_c(\mathbb R^d)$. 
     Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get that there exist $C,\delta > 0$ such that
@@
 \end{align}
-	Using this, we have that there exists $C,C',
+	Using this, we have that there exist $C,C',
     \delta > 0$ such that for $k\geq 0$ and $t\geq k+1$,
@@
 \end{align*}
-	Therefore, we get the required result in this step.
+	Therefore, we get the desired result in this step.
 
@@
 \end{align}
-	The proof is completed.
+	The proof is complete.
 
@@
 \subsection{Analytic facts}
-    In this subsection, we present some analytic facts that will be useful.
+    In this subsection, we present some some analytic facts.
 \begin{lem}
@@
     Notice that $|e^{-z}| = e^{- \operatorname{Re} z} \leq 1$.
-    %Therefore, according to \cite[Theorem 7.20]{Rudin1987Real},
     Therefore,
@@
     Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb Z_+$.
-    %According to \cite[Theorem 7.20]{Rudin1987Real},
     We have
@@
 \label{lem: extension lemma for branching mechanism}
-%%%
-%Suppose that  $\nu$ is a measure on $(0,\infty)$ such that $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$. Then 
-%\begin{equation}
-%    h (z) = \int_{(0,\infty)} (e^{-zu} - 1 + zu) \nu(du), \quad z \in \mathbb C_+,
-%\end{equation}
-%is well defined.
-%    Moreover, $h$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with 
-%\begin{equation}
-%\label{eq: deriavetive of the Poission partb}
-%    h'(z) = \int_{(0,\infty)}(1- e^{-uz})u \nu(du).
-%\end{equation}
     Suppose that  $\nu$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$. 
@@
     \frac{h(z)-h(z_0)}{z-z_0} \xrightarrow[\mathbb C_+\ni z \to z_0]{} h'(z_0),\quad z_0 \in \mathbb C_+.
-\] %%
+\] 
 \end{lem}
 \begin{proof}
-    %From Lemma \ref{lem: estimate of exponential remaining}, we know that $h$ is well defined on $\mathbb C_+$.
-    From Lemma \ref{lem: estimate of exponential remaining}, we know that $h$ and $h'$ are well defined on $\mathbb C_+$. %%
-    %According to \cite[Theorem 3.2.
-\& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, \eqref{eq: deriavetive of the Poission partb} defines a continuous function $h'$ on $\mathbb C_+$ which is holomorphic on $\mathbb C_+^0$.
+    From Lemma \ref{lem: estimate of exponential remaining}, we know that $h$ and $h'$ are well defined on $\mathbb C_+$. 
     According to \cite[Theorem 3.2. \& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
 
-%    Let $z_0, z \in \mathbb C_+$.
-%    Let $\gamma: [0,1]\mapsto \mathbb C_+$ be a $C^1$ path with $\gamma(0) = z_0$ and $\gamma(1) = z$.
-%    Notice that, according to Lemma \ref{lem: estimate of exponential remaining},
-%\begin{align}
-%    &\int_0^1 \int_0^\infty |1-e^{-u\gamma(\theta)}|u~\nu(du)~d\theta
-%    \\ &= \int_0^1~d\theta~ \Big( \int_0^1 |1-e^{-u\gamma(\theta)}|u~\nu(du) + \int_1^\infty |1-e^{-u\gamma(\theta)}|u~\nu(du) \Big)
-%    \\ &\leq \int_0^1~d\theta~ \Big( |\gamma(\theta)|\int_0^1 u^2~\nu(du) + 2\int_1^\infty u~\nu(du) \Big)
-%    < \infty.
-%\end{align}
-%    Therefore, according to Fubini's theorem and \cite[Theorem 7.20]{Rudin1987Real},
-    From Lemma \ref{lem: estimate of exponential remaining}, for each $z_0 \in \mathbb C_+$, we have that there exists $C>0$ such that
+    From Lemma \ref{lem: estimate of exponential remaining}, for each $z_0 \in \mathbb C_+$, we have that there exists $C>0$ such that for $z \in \mathbb C_+$ close enough to $z_0$ and any
+    $u>0$,
 \begin{align}
@@
     \leq (2u) \wedge\Big( u^2\int_0^1|\theta z+(1-\theta)z_0|d\theta\Big)
-    \\ &\leq C(u\wedge u^2),
-    \quad z \in \mathbb C_+ \text{ close enough to } z_0, u>0.
-\end{align}
-    Using this and dominated convergence theorem, we have
+    \leq C(u\wedge u^2).
+\end{align}
+    Using this and the dominated convergence theorem, we have
 \begin{align}
@@
     Fix a $\beta \in (0,1)$.
-    %Using the uniqueness of holomorphic extension and \cite[Theorem 3.2 \& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, we get that
     Using the uniqueness of holomorphic extension and Lemma \ref{lem: extension lemma for branching mechanism}, we get that
@@
 \item
-    %are extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
     are extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
 \item
-    %are holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$;
     are holomorphic on $\mathbb C_+^0$;
 \item
-    %are continuous on $\mathbb C_+ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}$.
     are continuous on $\mathbb C_+$.
 \end{itemize}
-    %Similarly, using Lemma \ref{lem: extension lemma for branching mechanism}, we get that
     Similarly, we get that
@@
 \end{equation}
-%    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\to \mathbb C_+$ ,
-%\begin{align}
-%\label{eq: integration formula for 1+beta-th power of z}
-%    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta}
-%    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
-%    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}}
-%    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
-%\end{align}
-%    This also shows that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
     Lemma \ref{lem: extension lemma for branching mechanism} also says that the derivative of $z^{1+\beta}$ is $(1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
@@
 \label{lem: Lip of power function}
-    %There is a constant $(1+\beta)$ such that for all $z_0,z_1 \in \mathbb C_+$,
     For each $z_0,z_1 \in \mathbb C_+$, we have
@@
 \begin{proof}
-%added
-    Since $z^{1+\beta}$ is continuous on $\mathbb C_+$, we only have to proof the Lemma assuming $z_0,z_1 \in \mathbb C^0_+$.
-%end added
+    Since $z^{1+\beta}$ is continuous on $\mathbb C_+$, we only need to prove the lemma assuming $z_0,z_1 \in \mathbb C^0_+$.
     Notice that
@@
 \end{align}
-    %Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
     Define a path $\gamma: [0,1] \to \mathbb C^0_+$ such that
@@
 \]
-    %Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
     Then, we have
@@
     Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact seperable metric space $E$.
-%    Fix a time $t >0$.
-%    For all $s\in (0,  t)$ and  bounded complex valued Borel function $\rho$ on $[0,t) \times E$, we write
-%\begin{equation}
-%    H^{(\rho)}_{(s,t)}:= \exp\Big\{\int_s^t \rho(u,\xi_u) du\Big\}.
-%\end{equation}
     Write
@@
 \end{equation}
-%deleted
-%    Notice that
-%\begin{equation}
-%\label{eq: crucial for Feynman-Kac}
-%    \frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
-%    \quad s\in (0,t).
-%\end{equation}
-%end deleted
-%    Suppose that $\beta$, $\rho$ are complex valued bounded measurable functions on $[0,t) \times E$ and that $F$ is a complex valued bounded measurable function on $E$.
-%    Define
-%\begin{equation}
-%    g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\beta+\rho)} F(\xi_t)],\quad r \in [0,t), x\in E.
-%\end{equation}
+
 \begin{lem}
@@
 \end{lem}
-%    Notice that
-%\begin{align}
-%    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} F(\xi_t)| ~ds \Big]
-%    \leq  \int_r^t e^{(t-r)\|\beta\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|F\|_\infty ~ds
-%    < \infty.
-%\end{align}
-%    Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
-%\begin{align}
-%    &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\beta)}~(\rho g)(s,\xi_s)~ds \Big]
-%    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\beta)}\rho(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\beta+\rho)} F(\xi_t)]~ds \Big]
-%    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} F(\xi_t) ~ds \Big]
-%    = \Pi_{r,x} [ H_{(r,t)}^{(\beta)}F(\xi_t)(H_{(r,t)}^{(\rho)} - 1)]
-%    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\beta)} F(\xi_t)].
-%\end{align}
+
 \begin{proof}
-    The proof is similar to the proof of \cite[Lemma A.1.5]{Dynkin1993Superprocesses}. We included it for the sake of completeness.
+    The proof is similar to the proof of \cite[Lemma A.1.5]{Dynkin1993Superprocesses}. We include it here for the sake of completeness.
     Notice that
@@
 \end{align}
-%added
     For the uniqueness, suppose that $\tilde g$ is another solution. Writting $h(r) = \sup_{x\in E}|g(r,x) - \tilde g(r,x)|$, we have
@@
     According to \cite[Lemma A.1.5]{Dynkin1993Superprocesses}, this says that $h(r) =  0$ for $r\in [0,t]$.
-%end added
 \end{proof}
@@
 \label{sec: definition of superprocess}
-%added
-    In this subsection, we will give the definition of the superprocesses that are considered in this Appendix.
-%end added
+    In this subsection, we will give the definition of the superprocesses considered in this Appendix.
 Let $E$ be locally compact separable metric space. Denote by $\mathcal M_E^1$ the collection of all the finite measures on $E$ equipped with weak topology.
@@
 \label{sec: definition of vf}
-    %Let $X$ be the superprocess defined in Subsection \ref{sec: definition of superprocess}.
-    %Assume that the superprocess $X$ is non-presistent with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
     Let $X$ be the non-presistent superprocess defined in Subsection \ref{sec: definition of superprocess} with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
@@
 \end{align}
-    %Let $f\in L_1(\xi), t >0$ and $x\in E$.
     Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
@@
     =\mathbf P_{\delta_x}[X_t(f)]=P^\beta_t f(x) \in \mathbb R,
-%added
     \quad f\in L_1(\xi), t > 0,x\in E.
-%end added
-\end{equation}
-%added
+\end{equation}
     This says that random variables $X_t(f)$ are well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
-%end added
-    %Notice that, from the branching property of the superprocess $X$, $\{X_t(f); \mathbf P_{\delta_x}\}$ is an infinitely divisible random variable with finite moment.
-%({\bf Do you want to say mean or higher moment?})
     According to the branching property of the superprocess, they are infinitely divisible random variables.
-    %Denote by $U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}]$  the charateristic exponent of the random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
     Therefore, we can write 
@@
     U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}],
-%added    
     \quad t\geq 0, f\in L_1(\xi), \theta \in \mathbb R, x\in E,
-%end added
-\] 
-    %the charateristic exponent of the random variable $\{X_t(f); \mathbf P_{\delta_x}\}$.
-    as their charateristic exponent.
-    %According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, for each $\theta \in \mathbb R$,
-%$   \mathbf P_{\delta_x} [e^{i\theta X_t(f)}]
-%    = \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]).
-%$
+\] 
+    as their characteristic exponent.
     According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
@@
 \]
-    %Notice that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function.
-    %Also notice that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$.
-    %Therefore, according to \cite[Lemma 7.6]{Sato1999Levy}, we have
     Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato1999Levy}, we have
@@
 \label{eq: N and characteristic exponent}
-    %U_tf(x) = \mathbb N_x[e^{i W_t(f)} - 1],
     U_t(\theta f)(x) = \mathbb N_x[e^{i W_t(\theta f)} - 1],
-    %\quad t \geq 0.
     \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
@@
 
-%added
 \begin{lem}
@@
 \end{proof}
-%end added
-
-    %We claim that if $f\in L^2(\xi)$ then the following expectations
+
     This Lemma also says that if $f\in L^2(\xi)$ then the following expectations
@@
     \in \mathbb C,
-%added
     \quad x\in E, t\geq 0.
-%end added
 \]
     are well defined.
-%    First, we only assume that $f\in L^1(\xi)$.
-%    Noticing that
-%\[
-%     e^{\operatorname{Re} U_tf(x)}
-%    = |e^{U_tf(x)}|
-%    = |\mathbf P_{\delta_x}[e^{i X_t(f)}]|
-%    \leq 1,
-%\]
-%    we have
-%\begin{equation}
-%\label{eq: -v has positive real part}
-% \operatorname{Re} U_tf(x)
-%    \leq 0.
-%\end{equation}
-%    Therefore, we can talk about $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
-%    According to Lemma \ref{lem: estimate of exponential remaining}, we have that
-%\begin{equation}
-%\label{eq: upper bound for vf}
-%    |U_tf(x)| \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
-%    \leq \mathbb N_x[|i W_t(f)|]
-%    \leq (P^\beta_t |f|)(x).
-%\end{equation}
-%    Notice that, for any compact $K \subset \mathbb R$,
-%\begin{equation}
-%\label{eq: estimate of deriavetive of v(theta)}
-%    \mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
-%    \leq \mathbb N_x[|W_t(f)|] \leq (P^\beta_t |f|)(x) < \infty.
-%\end{equation}
-%    Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability},
-%    $U_t(\theta f)(x)$ is differentiable in $\theta \in \mathbb R$ with
-%\[
-%    \frac{\partial}{\partial \theta} U_t(\theta f)(x)
-%    = i\mathbb N_x[W_t(f)e^{i\theta W_t(f)}],
-%    \quad \theta \in \mathbb R.
-%\]
-%    Moreover, from the above, it is clear that
-%\begin{equation}
-%\label{eq: upper bounded for derivative of v(theta)}
-%    \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
-%    \leq ( P^\beta_t |f|)(x).
-%\end{equation}
-%    From the dominate convergence theorem, we can verify that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
-%    In other words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
-%    According to this and \eqref{eq: path integration representation of h}, we can write
-%\begin{equation}
-%\label{eq: path integration representation of psi(v)}
-%    \psi(x,-U_tf) = -\int_0^1 \psi'\big(x,-U_t(\theta f)\big) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
-%\end{equation}
-%    Notice that
-%\begin{equation}
-%\label{eq: upper bound of psi'(v)}
-%\begin{split}
-%    &|\psi'(x, -U_tf)|
-%    \\&= \Big| -\beta(x)- 2\alpha(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
-%    \\&= \Big| - \beta(x)- 2\alpha(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi%(x,dy) \Big|
-%\\ &\leq \|\beta\|_\infty + 2\alpha(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
-%\\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty  P^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\beta_t |f|(x) + 2%\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
-%\\ &=: C_1 + C_2(P^\beta_t |f|)(x),
-%\end{split}
-%\end{equation}
-%    where $C_1, C_2$ are constants independent on $f,x$ and $t$.
-%    Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have
-%\begin{align}
-%\label{eq: upper bound of psi(v)}
-%    \big|\psi\big(x,-U_tf\big)\big|
-%    \leq C_1 P^\beta_t |f|(x)+C_2 P^\beta_t |f| (x)^2.
-%\end{align}
-%    Now assume that $f \in L_2(\xi) \subset L_1(\xi)$.
-    In fact, using Jensen's inequality and the markovian property, we have 
+
+    In fact, using Jensen's inequality and the Markov property, we have 
 \begin{align}
@@
 \end{align}
-%deleted
-%	As a consequence, the expectation
-%\[
-%     \Pi_x\Big[\int_0^t \psi(\xi_s,-U_{t-s}f)ds\Big]
-%    \in \mathbb C
-%\]
-%    is well defined for all $f\in L_2(\xi)$.
-%end deleted
 

### 2019-01-31 supCLT.tex
supCLT.tex: 1214

@@
 %%%----Versions-----------------------------
+% supclt1213.tex 2018/12/13 by Yanxia
 % supclt1213.tex 2018/12/13 by Renming
@@
     denote by $\kappa_f$ the order of $f$ in
-%term of the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 
 the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
@@
 \section{Introduction}
-%\subsection{Model}
 \subsection{Model}\label{ss:1.1}
@@
      Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+ %   For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$,
+  For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
+    let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
     The Hermite polynomials are defined by
@@
     :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
-    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
+    \quad x\in \mathbb R^d,
+    %p \in \mathbb{N}_0^{d}.
+    p \in \mathbb{Z}_+^{d}.
 \end{equation}
@@
     For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-$
-	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|
-$
+%$
+%	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|
+%$
+\begin{equation}\label{Q_k}
+Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
+\end{equation}
 and
-$
+%$
+%	Q f:= Q_{\kappa_f}f.
+%$
+\begin{equation}\label{Q}
 Q f:= Q_{\kappa_f}f.
-$
+\end{equation}
+
     Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
@@
 \end{equation}
-    Write $\psi_0(z) := \psi(z) + \alpha z$. Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
+   % Write $\psi_0(z) := \psi(z) + \alpha z$.
+   Write $\psi_0(z) := \psi(z) + \alpha z=z^{1+\beta}$.
+  %  Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
+   Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}=(1+\beta)z^\beta$.
     For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
@@
 In this subsection, we will give the main results of this paper.
-%Suppose $\mu\in \mathcal M_c(\mathbb R_d)$ has compact support.
 \subsubsection{Large branching rate}
 
-For each $p\in \mathbb{N}_+^d$, we define
+%For each $p\in \mathbb{N}_+^d$, we define
+For each $p\in \mathbb{Z}_+^d$, we define
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
   For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
-%  $L^{1+\gamma}(\mathbb{P}_{\mu})$, 
    $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\mu\in \mathcal M_c(\mathbb R_d)$,
@@
      If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for
-%     any $\gamma\in (0, \beta)$,
 any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$,
@@
  \begin{rem}
-%    If $\kappa_f=0$, 
 Let $f \in \mathcal{P}$.  If $\kappa_f=0$,
     $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},
-%    for any $\gamma\in (0, \beta)$, as $t\rightarrow \infty$
 for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$, as $t\rightarrow \infty$,
@@
     If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$,
-%    then, under 
-   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under 
+   then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under
     $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
@@
     m[f]
-    :=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx
+    :=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx.
 \]
@@
     If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$,
-%    then, under 
    then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under
@@
  In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
- %Denote by $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite Borel measures on $\mathbb{R}^d$ with compact support.
 	For all $0 \leq a_1 \leq a_2 <\infty$ and  random variable $Y$ with finite mean, define
-$
+%$
+%  	\mathcal I_{a_1}^{a_2} Y
+%   := \mathbb P[Y|\mathscr F_{a_2}] - \mathbb P[Y|\mathscr F_{a_1}].
+%$
+$$
 	\mathcal I_{a_1}^{a_2} Y
-    := \mathbb P[Y|\mathscr F_{a_2}] - \mathbb P[Y|\mathscr F_{a_1}].
-$
+  := \mathbb P_\mu[Y|\mathscr F_{a_2}] - \mathbb P_\mu[Y|\mathscr F_{a_1}].
+$$
+
 \begin{lem}
@@
     \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    \leq \frac{ C}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r}.
-\]
+    \leq \frac{ C}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r},
+\]
+%new added
+where $Q_kg$ is defined by \eqref{Q_k} with $f$ replaced by $g$.
+%end new
 \end{lem}
@@
     &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    \\ &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-k-1}^{t-k}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
+    % k is replaced by l to avoide confusing between k and \kappa.
+    \\ &\leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
     + |\langle T^\alpha_t g,\mu\rangle|
-    \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} k} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle. 
+    \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
 \end{align}
@@
     Let $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ be such that $Lf \in \mathcal{P}$ and let $a\in \mathbb R$.
-%    Then the process $(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.
 Then, for any $\mu\in \mathcal M_c(\mathbb{R}^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
@@
 \begin{lem}\label{lemma26}
-%    $(H^p_t)_{t\geq 0}$ is a martingale with respect to $(\mathscr F_t)$.
     For any $\mu\in \mathcal M_c(\mathbb{R}^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
@@
 \begin{proof}
-%   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a martingale.
   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb{R}^d)$.
@@
     Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$,
-%    we get that there exists 
    we get, for $\gamma\in [\gamma_0, \beta)$, that there exists
@@
 \]
-%    For any $\gamma\in (0, \gamma_0)$, note that
    For any $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb{R}^d)$, note that
@@
 
-%    Hence, for each $\gamma \in (0,\beta)$, 
    Hence, for each $\gamma \in (0,\beta)$ and any $\mu\in \mathcal M_c(\mathbb{R}^d)$,
@@
      Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
- According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
+% According to Lemma \ref{lem: control of mgtrs},
+Using Lemma \ref{lem: control of mgtrs} with $g=1$ and $k=0$,
+ there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
     \begin{align}
@@
 
-%Write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
 From now on, we write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
@@
 \end{align*}
-Finally, plugging $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.
+Finally, plugging
+%$\lambda = f(t)^{-1} \in [0,1]$
+$\lambda = f(t)^{-1} \in (0,1]$
+back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.
 \end{proof}
@@
 \[
-    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi)
+    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi).
 \]
@@
     \label{lemma31q}
-      J_1(k,t,\epsilon)\leq C\exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\}.
+      %J_1(k,t,\epsilon)
+      J_1(t,k,\epsilon)
+      \leq C\exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\}.
     \end{align}
@@
    \\&=\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}}e^{\frac{1+2\beta}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf
-   \\&\leq\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf.
-\end{align}
+   \\&\leq\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf,
+\end{align}
+%new added
+where $Q$ is defined by \eqref{Q}.
+%end new
 Thus for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
@@
 \label{eq: estimate of J1}
-     J_1(k,t,\epsilon)&
+     %J_1(k,t,\epsilon)&
+     J_1(t,k,\epsilon)&
      \leq \|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}\mathbb{P}_{\mu}[\langle SQf,X_{t-k-1}\rangle]\\
-     & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\}.
-\end{align}
+     & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
+\end{align}
+%new added
+where $Q_0$ is defined by \eqref{Q_k} with $k=0$.
+%end new
+
 	Step 3.
@@
 \label{eq: prevJ2}
-&J_2(k,t,\epsilon)
-	\\&= \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]
+%&J_2(k,t,\epsilon)\\&=
+J_2(t,k,\epsilon)&
+	= \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]
     \\&=e^{-\alpha k}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1T^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1T^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
@@
 \begin{align}
-	&J_2(k,t,\epsilon)
+%	&J_2(k,t,\epsilon)
+	J_2(t,k, \epsilon)&
 \leq  \|\mu\|^{-1}e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
@@
 \begin{align}\label{ineq: control of J3}
-    J_3(k,t,\epsilon)\leq Ce^{-\delta (t-k-1)}.
+ %   J_3(k,t,\epsilon)\leq Ce^{-\delta (t-k-1)}.
+ J_3(t,k,\epsilon)\leq Ce^{-\delta (t-k-1)}.
 \end{align}
@@
 	\\&= \mathbb P_\mu[e^{-\alpha^*\|X_t\|};A_t(\epsilon)]
-	\leq \exp({-\alpha^* e^{(\alpha - \epsilon)t}}).
+%	\leq \exp({-\alpha^* e^{(\alpha - \epsilon)t}}).
+\leq \exp({-\alpha^* \|\mu\|e^{(\alpha - \epsilon)t}}).
 \end{align}
@@
 \begin{cor}\label{cor: used in next corollary}
-%Let $f\in \mathcal{P}$ and $\Theta >0$.
-Let $f\in \mathcal{P}$, and $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
+Let $f\in \mathcal{P}$, $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
 Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
@@
 \begin{prop}\label{corollary31}
-%Let $f\in \mathcal{P}$ and $\Theta>0$. 
 Let $f\in \mathcal{P}$, and $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$.
-Then there exist $C,\delta>0$ such that for all $T\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$, we have
+Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then there exist $C,\delta>0$ such that
+%for all $T\geq 0$,
+for all $t\geq 0$,
+%$n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$
+$n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb{R}^{n+1}$
+satisfying $|\theta_i|\leq \Theta$, we have
 \begin{align}
@@
     Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
-    Fix $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ satisfying $|\theta_i|\leq \Theta$.
+    %Fix $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ 
+    Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb{R}^{n+1}$ 
+    satisfying $|\theta_i|\leq \Theta$.
     For each $k\in\{-1,...,n\}$, we define
@@
     \end{align*}
-    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$, we have
+    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any 
+    % $k\in\{0,1,...,n\}$, we have
+    $k\in\{0, 1, \cdots, n\}$, we have
     \begin{align*}
@@
         &(t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle
-        \\ &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big) + \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
+        \\ &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big) +
+     %   \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
+         \frac{\langle T^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
         \\&=:I_1(t)+I_2(t) + I_3(t),
@@
 \]
-    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb{R}$.
-Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get that there exist $C,\delta>0$ such that,
+    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb{R}$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ 
+    %in Corollary \ref{corollary31},
+    in Proposition \ref{corollary31},
+    we get that there exist $C,\delta>0$ such that,
 \begin{align*}
@@
     According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\eta_1$ under $\tilde {\mathbb P}_\mu$.
-    Therefore, we only need to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I_i(t)\xrightarrow[t\to \infty]{d} 0$ for $i = 2,3$ under $\tilde {\mathbb P}_\mu$.
+    Therefore, we only need to prove
+  %   $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0$
+ \begin{equation}\label{toprove-1}|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0,
+ \end{equation}
+      and 
+      %$I_i(t)\xrightarrow[t\to \infty]{d} 0$ for $i = 2,3$ under $\tilde {\mathbb P}_\mu$.
+     \begin{equation}\label{toprove-2}
+     I_i(t)\xrightarrow[t\to \infty]{d} 0,\quad i = 2,3,  \mbox{ under } \tilde {\mathbb P}_\mu.\end{equation}
 
 By \cite[Lemma 3.4.3]{Durrett2010Probability},
-\begin{align}\label{ineq: control of I1t}
+%\begin{align}\label{ineq: control of I1t}
+\begin{equation}\label{ineq: control of I1t}
     |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]|
@@
     \quad t\geq t_0,
-\end{align}
+%\end{align}
+\end{equation}
     where for all $k \geq 0$ and $t\geq k+1$,
@@
 \end{align}
-    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt}, \eqref{ineq: control of Kkt}, there exist constants $C,C'>0$ such that  for all $k\geq 0$ and $t\geq k+1$,
+   % According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt}, \eqref{ineq: control of Kkt}, 
+   According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and  \eqref{ineq: control of Kkt}, 
+    there exist constants $C,C'>0$ such that  for all $k\geq 0$ and $t\geq k+1$,
 \begin{align}
@@
     Step 3. We will show that there exist $C, \delta> 0$ such that for $t$ large enough,
-\[
+%\[
+\begin{equation}\label{domi-difference of Is}
     |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
     \leq C t^{-\delta}.
-\]
+%\]
+\end{equation}
     In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C,\delta > 0$ such that
@@
 \end{align}
-    giving the desired result in this step.
+%    giving the desired result in this step.
+which implies \eqref{domi-difference of Is}  by \eqref{ineq: control of I1t}.
+
+    %new added
+    Letting $t\to\infty$ in \eqref{domi-difference of Is}, we get \eqref{toprove-1}.
+
+    %end new
 
@@
 	Step 5. We will show that $I_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
-	In fact, we can write
+	%In fact, we can write
+In fact, we have
 \begin{align}
 	&|I_3(t)|
-	\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
+	%\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
+\leq \frac{\langle |T^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
 	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(te^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
@@
 \]
-	In order to do this, we choice a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, for each $\gamma \in [\gamma_0, \beta)$, we have $a < \frac{\alpha\gamma}{b(1+\gamma)}$.
+	In order to do this, 
+%we choice a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, 
+we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, 
+for each $\gamma \in [\gamma_0, \beta)$, we have $a < \frac{\alpha\gamma}{b(1+\gamma)}$.
 	Then, according to Lemma \ref{lem: control moment}, we have, for each $\gamma \in (0,\beta)$,
@@
 \]
+{\bf Question: $J_t$ should be $e^{-(\alpha - ab)t} \langle g, X_t\rangle$, right?}
 \item
@@
 \]
+{\bf Question: the above $J_t$ should be replaced by $e^{-(\alpha - ab)t} \langle g, X_t\rangle$, right?}
 \end{enumerate}
@@
 	&\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-	\\&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+ \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big) + \frac{\langle P_t^\alpha f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+	\\&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+ \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big) +
+%\frac{\langle P_t^\alpha f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+\frac{\langle T_t^\alpha f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
 	\\&=:I'_1(t)+I'_2(t)+I'_3(t),
@@
     Let $\theta\in \mathbb{R}$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Corollary \ref{corollary31}, we get that there exist $C,\delta > 0$ such that
+    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in 
+  %  Corollary \ref{corollary31}, 
+  Proposition \ref{corollary31},
+    we get that there exist $C,\delta > 0$ such that
 \begin{align*}
@@
 	Step 3. We will show that $I'_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
-	In fact, we can write
+%	In fact, we can write
+In fact, we have
 \begin{align}
 	&|I'_3(t)|
-	\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+	%\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+     \leq \frac{\langle |T^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
 	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
@@
 
-    Recall that $\Gamma$ the Gamma function defined by
+%    Recall that $\Gamma$ the Gamma function defined by
+ Recall that the Gamma function  $\Gamma$ is defined by
 \begin{equation}
@@
 \]
-	Using this recursively, one get that
+	Using this recursively, one gets that
 \begin{align}
@@
 \begin{equation}
-    P_t^\beta f(x)
+   % P_t^\beta f(x)
+   T_t^\beta f(x)
     := \Pi_{x}[e^{\int_0^t \beta(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
@@
     \mathbb N_{\mu}[W_t(f)]
-    =\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_t f).
+    =\mathbf P_{\mu}[X_t(f)]=
+    %\mu(P^\beta_t f).
+    \mu(T^\beta_t f).
 \end{equation}
@@
     \big|\psi\big(x,-U_tf\big)\big|
-    \leq C_1 P^\beta_t |f|(x)+C_2 P^\beta_t |f| (x)^2.
+    \leq C_1 P^\beta_t |f|(x)+
+    %C_2 P^\beta_t |f| (x)^2.
+     C_2 (T^\beta_t |f| (x))^2.
 \end{align}
@@
     \leq \mathbb N_x[|i W_t(f)|]
-    \leq (P^\beta_t |f|)(x).
+ %   \leq (P^\beta_t |f|)(x).
+  \leq (T^\beta_t |f|)(x).
 \end{equation}
@@
     \mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
-    \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta| \leq (P^\beta_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
+    \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta| 
+    %\leq (P^\beta_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
+    \leq (T^\beta_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
 \end{equation}
@@
     \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
-    \leq ( P^\beta_t |f|)(x).
+    %\leq ( P^\beta_t |f|)(x).
+    \leq ( T^\beta_t |f|)(x).
 \end{equation}
@@
 \\ &\leq \|\beta\|_\infty + 2\alpha(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
-\\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty  P^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\beta_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
-\\ &=: C_1 + C_2(P^\beta_t |f|)(x),
+\\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty 
+% P^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\beta_t |f|(x)
+T^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~T^\beta_t |f|(x)
+  + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
+%\\ &=: C_1 + C_2(P^\beta_t |f|)(x),
+\\ &=: C_1 + C_2(T^\beta_t |f|)(x),
 \end{split}
@@
     U_tf(x) -  \int_0^t P_{t-s}^{\beta} \psi_0\big(\cdot,-U_sf\big) (x)~ds
-    \\= iP_t^\beta f(x).
+   % \\= iP_t^\beta f(x).
+   \\= iT_t^\beta f(x).
 \end{equation}
@@
 \end{equation}
+({\bf Remark: I changed $P^\beta$ to $T^\beta$ above. But I find that is it not good to make this kind of changes is not good for above equation. So, I stop to make changes. Should we use $P^\beta$?})
     Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{W_T(f)}$ if

### 2019-01-31 supCLT.tex
supCLT.tex: 1231

@@
 %---The preamble----------------------
-\documentclass[12pt]{amsart}
+\documentclass[12pt,a4paper]{amsart}
+	\setlength{\textwidth}{\paperwidth}
+	\addtolength{\textwidth}{-2in}
+	\calclayout
 \usepackage[utf8]{inputenc}
-\usepackage{geometry}
-\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
 \usepackage{mathtools}
 	\mathtoolsset{showonlyrefs}
-\usepackage{amsthm}
 \usepackage{stackrel}
+\usepackage{mathrsfs}
 \usepackage[backref=section]{hyperref}
@@
 	\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
-\usepackage{mathrsfs}
-\usepackage{color}
 \usepackage{comment}
+\usepackage{amsthm}
 	\theoremstyle{plain}
@@
 	\allowdisplaybreaks
-\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
-%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}
 
@@
     [CLT for Super-OU processes]
-    {CLT for Super-OU Processes with stable Branching}
+    {\large CLT for Super-OU Processes with stable Branching}
 \author
@@
 \email{zhaojianjie@pku.edu.cn}
-%\begin{abstract}
-%\end{abstract}
-%\subjclass[2010]{60J80, 60F05}
-%\keywords{}p
-%\date{}
-%\maketitle
-%---Contents-----------------------
 \begin{abstract}
-    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$.
-For each testing function $f$ of at most polynomial growth,
-    denote by $\kappa_f$ the order of $f$ in
-the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
-    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
-    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.
+    %Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$. 
+    Consider a super-OU process $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, where $\alpha >0$ and $\beta\in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
+$
+    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}). 
+$
+    For each testing function $f$ of at most polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
+    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: 
+    %In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
+    In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly.
+    %In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.
+    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly.
     In the large branching rate case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$.
 \end{abstract}
+%\subjclass[2010]{60J80, 60F05}
+%\keywords{}
+%\date{}
 \maketitle
 \section{Introduction}
-\subsection{Model}\label{ss:1.1}
-    Let $d \in \mathbb N:= \{1,2,\dots\}$ and
-    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator
+\subsection{Model}
+\label{ss:1.1}
+	%Let $d \in \mathbb N:= \{1,2,\dots\}$ and
+	Let $d \in \mathbb N:= \{1,2,\dots\}$. 
+    %$\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator
+    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with generator
 \begin{equation}
@@
         \quad  x\in \mathbb R^d,
-        f \in C^2(\mathbb{R}^d),
-\end{equation}
-    where $\sigma>0$ and $b>0$ are constants.
-    Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
-    Let $\psi$ be the function on $\mathbb R_+:= [0,\infty)$ defined by
-\begin{equation}\label{mechanism}
-    \psi(z)
-    := - \alpha z + z^{1+\beta},
+        f \in C^2(\mathbb R^d),
+\end{equation}
+    %where $a>0$ and $b>0$ are constants.
+    where $a>0$ and $b>0$.
+    %Denote by $(P_t^\alpha)_{t\geq 0}$ the transition semigroup of $\xi$.
+    Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
+    Let $\psi$ be the function on $\mathbb R_+$ defined by
+\begin{equation}
+\label{mechanism}
+    %\psi(z)
+    %:= - \alpha z + z^{1+\beta},
+    \psi(x,z)=
+    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy).
     \quad  z \in \mathbb R_+,
 \end{equation}
-	where $\alpha > 0$ and $\beta \in (0,1) $ are constants.
-    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite Borel measures on $\mathbb{R}^d$.
-    For all Borel function $f$ and Borel measure $\mu$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
+	%where $\alpha > 0$ and $\beta \in (0,1) $ are constants.
+	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
+    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
+%added%
+    Denote by $\mathcal B(\mathbb R^d)$ the space of all real-valued Borel measurable functions on $\mathbb R^d$.
+%%end added%
+	%For all Borel function $f$ and Borel measure $\mu$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
+	For each $f\in \mathcal B(\mathbb R^d)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
     Put $\|\mu\|=\langle 1,\mu\rangle$.
-    We say an $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb{R}^d$, we have
+
+    We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
 \begin{equation} \label{super}
@@
 \end{equation}	
-
-	The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.
+    The existence of superprocesses are well known, see \cite{Dynkin1993Superprocesses} for instance.
+
+    According to the Subsection A.1, the branching mechanism $\psi$ can be extended on $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
+ \[\psi(x,z)=
+    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
+    \quad  z \in \mathbb C_+,\]
+    which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
+    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
+\begin{equation}
+\label{eq: deriavetive of the Poission part}
+    \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
+    \quad z\in \mathbb C_+.
+\end{equation}
+
+    \begin{asp}
+\label{asp: branching mechanism}
+    The branching mechanism takes the form of 
+\[
+    \psi(z) = -\alpha z + \eta z^{1+\gamma} + \psi_1(z),\quad z\in \mathbb C_+,
+\]
+    where $\eta > 0$, $\gamma \in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
+\[
+    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}),\quad z\in \mathbb C_+.
+\]
+\end{asp}
+
+\begin{lem}
+    Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e.
+there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+    Also, $\psi$ satisfies the $L \log L$ critierion  i.e. 
+\[
+    \int_1^\infty y \log y~\pi(dr)< \infty.
+\]
+\end{lem}
+\begin{proof}
+    {\bf Need a proof.}
+\end{proof}
+
     According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
@@
     \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
-    = e^{-\alpha^* \|\mu\|},
-\end{equation}
-    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
+    = e^{-\bar v \|\mu\|},
+\end{equation}
+    where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
     Define
 \begin{equation}\label{meansemigroup}
-    T^{\alpha}_t f(x)
+    P^{\alpha}_t f(x)
     :=
-    e^{\alpha t} T_t f(x) =
+    e^{\alpha t} P_t f(x) =
     \Pi_x [e^{\alpha t}f(\xi_t)],
-    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
-\end{equation}
-    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
+    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
+\end{equation}
+    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
 \begin{equation}\label{eq:meanformula}
     \mathbb{P}_{\mu}[\langle f, X_t \rangle]
-    = \langle T_t^\alpha f, \mu \rangle,
+    = \langle P^\alpha_t f, \mu \rangle,
     \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
@@
     =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
-    \quad x\in \mathbb{R}^d.
-\end{equation}
-    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
+    \quad x\in \mathbb R^d.
+\end{equation}
+    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
 \begin{equation}
     \langle f_1, f_2 \rangle_{\varphi}
-    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
+    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
 \end{equation}
      Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
- %   For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$,
      For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
-    let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+    let $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
     The Hermite polynomials are defined by
@@
     \quad x\in \mathbb R^d,
-    %p \in \mathbb{N}_0^{d}.
     p \in \mathbb{Z}_+^{d}.
 \end{equation}
-    It is known that $(T_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
-    discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
+    It is known that $(P_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
+    discrete spectrum $a(L)= \{-bk: k \in \mathbb Z_+\}$.
     For each $k \in \mathbb Z_+$, denote by $A_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
@@
     \phi_p(x)
-    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
-    \quad x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
+    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{a}x \Big),
+    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
 \end{equation}
@@
 \begin{equation}\label{semigroupformula}
-    T_t\phi_p(x)
+    P_t\phi_p(x)
     =e^{-b|p|t}\phi_p(x),
-    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
+    \quad t\geq 0, x\in \mathbb R^d, p\in \mathbb Z_+^d.
 \end{equation}
@@
     \mathcal{P}
-    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+    :=\big \{f\in \mathscr B(\mathbb R^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
 \end{equation}
@@
     For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-%$
-%	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|
-%$
 \begin{equation}\label{Q_k}
-Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
+Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|P_t f|,
 \end{equation}
 and
-%$
-%	Q f:= Q_{\kappa_f}f.
-%$
 \begin{equation}\label{Q}
@@
 \end{equation}
-
     Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
-\subsection{}
-    Let $X$ be the super OU-process discussed in Subsection \ref{ss:1.1}.
-    Its branching mechanism $\psi$ can be extended to $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$:
- $$\psi(z) := -\alpha z + z^{1+\beta}, \quad z\in \mathbb C_+.$$
-    According to the analysis in Subsection A.1,
-    $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
-    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
-\begin{equation}
-\label{eq: deriavetive of the Poission part}
-    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
-    \quad z\in \mathbb C_+.
-\end{equation}
-   % Write $\psi_0(z) := \psi(z) + \alpha z$.
-   Write $\psi_0(z) := \psi(z) + \alpha z=z^{1+\beta}$.
-  %  Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
-   Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}=(1+\beta)z^\beta$.
+
+\subsection{complex valued FKPP equations}
+    Let $X$ be the super OU-process introduced in Subsection \ref{ss:1.1}.    
+   Write $\psi_0(z) := \psi(z) + \alpha z$,
+   %Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}=(1+\beta)z^\beta$.
+   and $\psi'_0(z) = \psi'(z) + \alpha$ for each $z\in \mathbb C_+$.
     For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
@@
     From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq:chareq2}
-    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
-    =i T^{\alpha}_t f(x),
+    U_tf(x)-\int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
+    =i P^{\alpha}_t f(x),
     \quad t\in [0,\infty), x\in E, f\in \mathcal P.
-\end{align}
+\end{split}\end{equation}
 
@@
 
-%For each $p\in \mathbb{N}_+^d$, we define
 For each $p\in \mathbb{Z}_+^d$, we define
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
-  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
-   $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\mu\in \mathcal M_c(\mathbb R_d)$,
-  thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+  For any $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
+   $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+  Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  \begin{thm}\label{Theorem11}
@@
      Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
+({\bf In the proof of this theorem, where do we need the condition that $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$ ?})
  \end{thm}
-For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s.
+For any $t\geq 0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s.
 and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$.
@@
     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
+({\bf This result should be refered as the SLLN, right?})
  \end{rem}
@@
     \tilde{m}[f]
-    := \langle(-i\phi)^{1+\beta},\varphi\rangle
+    := \langle \eta (-i\phi)^{1+\beta},\varphi\rangle
 \]
@@
 For $f\in \mathcal{P}$, define
+
 \[
      m[f]
-    :=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx.
+    =\alpha e^{\alpha}\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds, \label{msmallcase}
 \]
@@
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
-    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for all $\theta \geq 0$ and $f \in \mathcal P^+$.
-    We say $R$ is a monotone operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for all $f, g \in \mathcal P^+$ with $f\leq g$.
-    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotone operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for all $f\in \mathcal P^+$.
-    We say an operator $A$ is $\gamma$-controllable on $\mathcal D \subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if $A: \mathcal D \to \mathcal P^*$ and there  is a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f| (\le S|f|)$ for all $f\in \mathcal D$.
-    In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
-    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that, for each $s\in \Lambda$, $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$.
-
-	For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
-    For any $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
-    One of the reason for considering $\gamma$-controllable operators is that they have good algebraic properties:
+    For each function $h: [0,\infty) \to [0,\infty)$, we say an operator $R$ is an $h$-controller if
+\begin{itemize}
+\item
+    $R: \mathcal P^+ \to \mathcal P^+$;
+\item
+    $f, g\in \mathcal P^+$ and $f\leq g$ implies that $Rf \leq Rg$; and
+\item
+    $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ implies that $ R (\theta f)\leq h(\theta) Rf$.
+\end{itemize} 
+    For each function $h: [0,\infty) \to [0,\infty)$ and $\mathcal D \subset \mathcal P^*$, we say $A$ is an \emph{$h$-controllable} operator on $\mathcal D$ if 
+\begin{itemize}
+\item
+    $A : \mathcal D \to \mathcal P^*$;
+\item
+    There exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
+\end{itemize}
+    We also say operator $A$ is \emph{$h$-controlled by $R$ on $\mathcal D$} in this case.
+    We say a family of operators $(A_s)_{s\in \Lambda}$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by operator $R$ on $\mathcal D$.
+    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in E$.
+    For any $a \in \mathbb R$, suppose that $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
+
 \begin{lem}
@@
     Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$.
-Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D$.
+Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
 \begin{itemize}
@@
 \]
-    Then  $\{A_\nu: \nu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $\gamma$-controllable on $\mathcal D$.
+    Then  $\{A_\nu: \nu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $h$-controllable on $\mathcal D$.
 \item[(2)]
-    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal P^*$.
-    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0$ for some $\beta \in \mathbb R$ and that, for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
-    Then  $(B_\delta A_\lambda)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
+    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$.
+    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D_0$ for some function $g: [0,\infty) \to [0,\infty)$.
+    Then  $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$.
 \item[(3)]
     Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
-    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta \in \mathbb R$.
-    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma+\beta)$-controllable.
+    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D$ for some function $g: [0,\infty) \to [0,\infty)$.
+    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$, and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$.
 \item[(4)]
-    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
-    Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(a\gamma)$-controllable.
+    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal B(\mathbb R^d, \mathbb C_+)$.
+    Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable.
 \end{itemize}
@@
     (1).
-Let $(R,S)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$.
+Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
 For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
@@
 
-   	(2).
-Let $(R_A, S_A)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$ and $(R_B, S_B)$ be the $\beta$-control-pair of $(B_{\delta})_{\delta\in\Delta}$ on $\mathcal{D}_0$.
-	Note that $(R_BR_A, S_BS_A)$ is a $\beta \gamma$-control-pair.
-	In fact:
+    (2). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by  an$h$-controller $R_A$ on $\mathcal D$. 
+    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controalled by $g$-controller $R_B$ on $\mathcal D_0$. 
+    We verify the following:
 \begin{itemize}
 \item
-	For each $f,g \in \mathcal P^+$ with $f\leq g$, since $R_Af \leq R_A g$ we have $R_B(R_A f)\leq R_B(R_A g)$.
-\item
-	For each $f\in \mathcal{P}^+$ and $\theta \geq 0$, we have $S_BS_A(\theta f)=S_B(\theta^{\gamma}S_Af)=\theta^{\beta\gamma}S_BS_Af$.
-\item
-	For each $f,g \in \mathcal P^+$ with $f\leq g$, we have $R_B R_A f \leq R_B S_A f \leq S_BS_A f$.
+    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, we have $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
+\item
+    If $f,g \in \mathcal D_0$ with $|f|\leq |g|$, then $R_AR_B|f| \leq R_A R_B |g|$.
+\item
+    If $f \in \mathcal D_0$ and $\theta \in [0,\infty)$, then $R_AR_B|\theta f| \leq R_A(g(\theta) R_B|f|) \leq (h\circ g)(\theta) R_A R_B |f| $.
 \end{itemize}
-	Finally, note that for each $\delta\in \Delta, \lambda\in\Lambda$ and $f\in \mathcal D$, $|B_{\delta}A_{\lambda}f|\leq R_B|A_{\lambda}f|\leq R_BR_A|f|$ which says that $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(\beta\gamma)$-controlled by $(R_BR_A,S_BS_A)$.
-
-   The proofs of (3) and (4) are similar to that of (2).
+    Therefore $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$.
+
+    (3). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R_A$ on $\mathcal D$. 
+    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controalled by a $g$-controller $R_B$ on $\mathcal D$.
+
+    We verify the following:
+\begin{itemize}
+\item
+    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
+\item
+    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R_A\times R_B|f| \leq R_A\times R_B |g|$.
+\item
+    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R_A\times R_B|\theta f| \leq h(\theta) g(\theta) (R_A \times R_B) |f| $.
+\end{itemize}
+    Therefore $(A_\lambda \times B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \times g)$-controllable on $\mathcal D$.
+
+    We also verify the following:
+\begin{itemize}
+\item
+    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
+\item
+    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $(R_A + R_B)|f| \leq (R_A + R_B) |g|$.
+\item
+    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $(R_A + R_B) |\theta f| \leq h(\theta) R_A|f| + g(\theta) R_B|f| \leq (h(\theta) \vee g(\theta)) (R_A+R_B)|f| $.
+\end{itemize}
+    Therefore $(A_\lambda + B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \vee g)$-controllable on $\mathcal D$.
+
+    (4). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
+    We verify the following:  
+\begin{itemize}
+\item
+    For each $\lambda \in \Lambda$, $f\in \mathcal D$, we have $|A_\lambda^{\times a} f| = |A_\lambda f|^a  \leq R^{\times a} |f|$.
+\item
+    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R^{\times a}|f| \leq R^{\times a} |g|$.
+\item
+    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R^{\times a}|\theta f| \leq (h(\theta) R |f|)^a = h(\theta)^a R^{\times a}|f|$.
+\end{itemize}
+    Therefore $(A_\lambda^{\times a})_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable on $\mathcal D$.
 \end{proof}
-\subsection{}
-    For all $f \in \mathcal{P}$, $x\in \mathbb{R}^d$ and $t\geq 0$, define
-\begin{align}
+
+\subsection{Control the Operators for super-OU process}
+    Denote by $\psi_0(z) = \psi(z) + \alpha z$ for each $z\in \mathbb C_+$, and define operators on $\mathcal B(\mathbb R^d, \mathbb C_+)$ by
+\begin{equation}\begin{split}
+    \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
+    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x)
+    \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big), 
+    \quad  f\in \mathcal B(\mathbb R^d, \mathbb C_+), x\in \mathbb R^d.
+\end{split}\end{equation}   
+    Define
+\begin{equation}\begin{split}
 \label{eq: def of Zf}
-    \tilde U_t f(x)
-    &:= i T^\alpha_t f(x) + \int_0^t T^\alpha_{t-s} \Psi_0(-i T_s^{\alpha}f)(x)ds,
-    \\Z_t f (x)
-    &:= \int_0^t T^\alpha_{t-s} \Psi_0(-i T_s^{\alpha}f)(x)ds.
-\end{align}
+    Z_t f 
+    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,
+    \\ Z'_t f
+    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,
+    \\ Z''_t f
+    &:= \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
+    \\ K_t f
+    &:= (Z'_t - Z_t+ Z''_t)f.
+\end{split}\end{equation}
+    Then we have that
+\[
+    U_t - i P^\alpha_t 
+    = Z'_t + Z''_t 
+    = Z_t+ (Z'_t - Z_t) + Z''_t
+    = Z_t+K_t.
+\]
 
@@
 \label{lem: upper bound for usgx}
-The following statements are true for our super-OU process:
+    Under Assumption \ref{asp: branching mechanism}, the following statements are true:
 \begin{itemize}
 \item[(1)]
-   $(-U_t)_{0\leq t\leq 1}$ is uniformly $1$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
+   $(-U_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
 \item[(2)]
-    $(T^\alpha_t)_{0\leq t\leq 1}$ is uniformly $1$-controllable on $\mathcal P$.
+    $(P^\alpha_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable on $\mathcal P^*$.
 \item[(3)]
-    $\Psi_0$ is $(1+\beta)$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
+    $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
 \item[(4)]
-    $(U_t- iT_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(1+\beta)$-controllable on $\mathcal P$.
+    $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P$.
 \item[(5)]
-    $\{\Psi_0(-U_t) - \Psi_0(-iT_t^\alpha): 0\leq t\leq 1\}$ is uniformly $(1+2\beta)$-controllable on $\mathcal P$.
+    $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
 \item[(6)]
-    $(U_t-\tilde U_t)_{0\leq t\leq 1}$ is uniformly $(1+2\beta)$-controllable on $\mathcal P$.
+    There is a constant $\delta > 0$ such that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
 \item[(7)]
-    $(Z_t)_{0\leq t\leq 1}$ is uniformly $(1+\beta)$-controallable on $\mathcal P$.
+    There is a constant $\delta > 0$ such that $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
 \end{itemize}
@@
 \begin{proof}
-    (1). It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
+    (1). According to \eqref{eq: -v has positive real part}, $U_t: \mathcal P \to \mathcal B(\mathbb R^d, \mathbb C_+)$. 
+    It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
 \[
     |U_t g(x)|
-    \leq \sup_{0\leq u\leq 1}T_u^\alpha |g| (x).
-\]
-    Now note that $f\mapsto\sup_{0\leq u\leq 1}T^{\alpha}_u|f|$ is monotone and $1$-scalable.
+    \leq \sup_{0\leq u\leq 1}P_u^\alpha |g| (x).
+\]
+    Note that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.
 
@@
 
-    (3). According to Lemma \ref{lem: Lip of power function}, for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
-\[
-    |\Psi_0 f(x)| = |f(x)^{1+\beta}| = |f(x)|^{1+\beta}.
-\]
-    Now note that $f\mapsto |f|^{1+\beta}$ is monotone and $(1+\beta)$-scalable.
+    (3). Let $C>0$ and $\delta > 0$ be the constant in Assumption \ref{asp: branching mechanism}. 
+    For each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
+\begin{equation}\begin{split}
+    &|\Psi_0 f| 
+    \leq \eta |f|^{1+\beta} + |\Psi_1 f|
+    \leq \eta |f|^{1+\beta} + C|f|^2+ C|f|^{1+\beta + \delta}
+\end{split}\end{equation}
+    Note that 
+\[
+    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta},\quad f\in \mathcal P^+
+\]
+     is a $(\theta^2 \vee \theta^{1+\beta})$-controller.
 
@@
     f
-    \mapsto T^{\alpha}_{t-s}\Psi_0(-U_sf)(x),
+    \mapsto P^\alpha_{t-s}\Psi_0(-U_sf)(x),
     \quad 0\leq s\leq t\leq 1
 \]
-    are uniformly $(1+\beta)$-controllable.
+    are uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable.
     Combining this with \eqref{eq:chareq2} and Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.
@@
 \[
-    |\Psi_0(-U_t f) - \Psi_0(-iT_t^\alpha f) |
-    \leq  (1+\beta) |U_u f-iT_u^{\alpha}f|(|U_u f|^{\beta}+|i T_u^{\alpha}f|^{\beta}).
-\]
-    Now using (1), (2), (4) and Lemma \ref{lem: property of controllable operators}.(3)-(4), we get the desired result.
-
-    (6). Note that
-\[
-    U_sf - \tilde U_sf
-    = \int_0^s T_{s-u}^{\alpha}\big(\Psi_0(-U_t f)-\Psi_0(-i T_t^{\alpha}f)\big)~du.
-\]
-    Now using (2), (5) and Lemma \ref{lem: property of controllable operators}.(1)--(2), we get the desired result.
-
-    (7). The proof is similar to that of (4).
+    |(-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta} |
+    \leq  (1+\beta) |U_t f-iP^\alpha_t f|(|U_t f|^{\beta}+|i P^\alpha_t f|^{\beta}).
+\]
+    Now using (1), (2), (4) and Lemma \ref{lem: property of controllable operators}.(3)-(4), we get that
+\[
+    f \mapsto (-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta},\quad 0\leq t\leq 1
+\]
+    are unifromly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable.
+    As a consequence of this, Lemma \ref{lem: property of controllable operators}.(1)-(2), and 
+\begin{equation}\begin{split}
+    (Z'_t - Z_t)f = \int_0^t P^\alpha_{t-s}\Big( \eta \big((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} \big)\Big)ds,
+    \quad 0\leq t\leq 1, f\in \mathcal P,
+\end{split}\end{equation}
+    we get the desired result.
+
+    (6). Suppose that $C>0, \delta>0$ are constants in Assumption \ref{asp: branching mechanism}. 
+    Noticing that 
+\[
+    |\Psi_1(f)| 
+    \le C(|f|^2+|f|^{1+\beta+ \delta}), 
+    \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)
+\]
+    and that
+\[
+    f\mapsto C(f^2+f^{1+\beta+\delta}), 
+    \quad f\in \mathcal P^+
+\]
+    is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllor, we have that $\Psi_1$ is $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
+    According to this, (1), (2), and Lemma \ref{lem: property of controllable operators} (1)-(2), we have that
+\[
+    f
+    \mapsto Z_t'' f
+    = \int_0^t P_{t-s}^\alpha \Psi_1(-U_sf)ds,
+    \quad 0\leq t\leq 1,
+\] 
+    are uniformly $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+
+    (7). A consequence of (5), (6), Lemma \ref{lem: property of controllable operators}(3) and that $K_t = (Z'_t-Z_t)+Z''_t$.
 \end{proof}
 
-\subsection{}
+\subsection{$(1+\gamma)$-moments for the super-OU process}
 
  In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
-	For all $0 \leq a_1 \leq a_2 <\infty$ and  random variable $Y$ with finite mean, define
-%$
-%  	\mathcal I_{a_1}^{a_2} Y
-%   := \mathbb P[Y|\mathscr F_{a_2}] - \mathbb P[Y|\mathscr F_{a_1}].
-%$
+    For all $0 \leq s \leq t <\infty$ and  random variable $Y$ with finite mean, write
 $$
-	\mathcal I_{a_1}^{a_2} Y
-  := \mathbb P_\mu[Y|\mathscr F_{a_2}] - \mathbb P_\mu[Y|\mathscr F_{a_1}].
+    \mathcal I_s^t Y
+  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s].
 $$
@@
 \label{lem: control pair for P(M>lambda)}
-    There is a $(1+\beta)$-control-pair $(R,S)$ such that for all $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we have
+    There is a $(\theta^2\vee\theta^{1+\beta})$-controller $R$ such that for all $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we have
 \[
@@
 \begin{proof}
-    Denote by $(R,S)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}.(4).
+    Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller for Lemma \ref{lem: upper bound for usgx}.(4).
     Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
-\begin{align}
+\begin{equation}\begin{split}
     &\big|\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)\big|
-    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^t\langle g,X_t\rangle]})d\theta\Big|
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}|d\theta
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iT_t^\alpha(\theta g)|,\mu\rangle d\theta
+    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^t\langle g,X_t\rangle}])d\theta\Big|
+    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iP^\alpha_t (\theta g),\mu \rangle}|d\theta
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iP^\alpha_t(\theta g)|,\mu\rangle d\theta
     \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
       \qedhere
-\end{align}
+\end{split}\end{equation}
 \end{proof}
@@
 \begin{lem}\label{lem: temp}
-	For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb{R}^d)$, there exists a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
+    For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
 \[
     \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    \leq \frac{ C}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r},
-\]
-%new added
-where $Q_kg$ is defined by \eqref{Q_k} with $f$ replaced by $g$.
-%end new
+    %\leq \frac{ C}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r},
+    \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg).
+\]
+    %where $Q_kg$ is defined by \eqref{Q_k} with $f$ replaced by $g$.
 \end{lem}
 \begin{proof}
-    Denote by $(R,S)$ the $(1+\beta)$-control-pair in Lemma \ref{lem: control pair for P(M>lambda)}.
-    Let $h \in \mathcal P^+$, $\mu \in \mathcal M_c(\mathbb{R}^d)$, $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t$ with $s-r \leq 1$.
+    Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: control pair for P(M>lambda)}.
+    Fix $h \in \mathcal P^+$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t < \infty$ with $s-r \leq 1$.
     Suppose that $g\in \mathcal P$ satisfies $Q_\kappa g \leq h$.
     Using the Markov property of $X$, we get
-\begin{align}
+\begin{equation}\begin{split}
     &\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    = \mathbb P_\mu \big[\mathbb P_\mu[|\langle T_{t-s}^\alpha g, X_{s}\rangle - \langle T_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r]\big]
-    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle T_{t-s}^\alpha g, X_{s-r}\rangle - \langle T_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
-    = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle T_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
-    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
+    = \mathbb P_\mu \big[\mathbb P_\mu[|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r]\big]
+    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle P_{t-s}^\alpha g, X_{s-r}\rangle - \langle P_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
+    = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
+    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
     \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
-	\\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
-    = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \mathbb P_\mu [ \langle Sh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
-    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa b)} \langle T_r^\alpha Sh,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
-    \\&\leq e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r} \langle Q_0 Sh,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}.
-\end{align}
-    Therefore the desired result is true with
-\[
-    C := \frac{2^{2+\beta}}{2+\beta}\langle Q_0Sh, \mu\rangle.
+    \\&\leq \mathbb P_\mu [ \langle Rh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
+    \\& =  \langle P_r^\alpha Rh,\mu\rangle \bigg(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\bigg)
+    \\ & \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg),
+\end{split}\end{equation}
+    where the constatn $C$ is chosen as
+\[
+    C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big)\langle Q_0Rh, \mu\rangle.
     \qedhere
@@
 \label{lem: control of mgtrs}
-	For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
+    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
 \[
@@
     For all $\kappa \in \mathbb Z_+$,  $0\leq r\leq s\leq t$ with $s-r \leq 1$,  $g\in \mathcal P$ with $Q_{\kappa} g \leq h$, and $c>0$, we have
-\begin{align}
+\begin{equation}\begin{split}
 &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
@@
     \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^s\langle g, X_t\rangle|> \lambda) d\lambda
-    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r} C_0  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
-    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r} C_0   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
-\end{align}
+    \\& \leq c^{1+\gamma} + C_0  e^{\alpha r}(1+\gamma)\int_c^\infty \bigg(\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta}+\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2}\bigg)\lambda^{\gamma}d\lambda
+    \\&\leq c^{1+\gamma} e^{\alpha r} + C_0e^{\alpha r}(1+\gamma)\Big(  \frac{e^{(1+\beta)(t-s)(\alpha- \kappa b)}}{(\beta - \gamma)c^{\beta - \gamma}}  + \frac{e^{2(t-s)(\alpha- \kappa b)}}{(1 - \gamma)c^{1 - \gamma}} \Big).
+\end{split}\end{equation}
     Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
-\begin{align}
+\begin{equation}\begin{split}
     &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
-    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}\Big).
-\end{align}
+    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
+\end{split}\end{equation}
     Note that
-\[
-    (1+\gamma)(t-s)(\alpha- \kappa b) + \alpha r
-    \leq t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b).
-\]
+\begin{equation}\begin{split}
+    &(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r
+    = (t-s)\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b)
+    \\&\leq t\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b).
+\end{split}\end{equation}
     So the desired result is true with
 \[
-	C := \Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}\Big).
+    C := 1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}.
     \qedhere
@@
 \label{lem: control moment}
-	For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
+    For any $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
 \begin{itemize}
@@
     Using the triangle inequality, for all $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$, we have
-\begin{align}
+\begin{equation}\begin{split}
     &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
@@
     \\ &\leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
-    + |\langle T^\alpha_t g,\mu\rangle|
+    + |\langle P^\alpha_t g,\mu\rangle|
     \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
-\end{align}
+\end{split}\end{equation}
     By calculating the sum on the right, we get the desired result.
@@
 \subsection{Martingales}
-    In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales for $\gamma\in (0, \beta)$.
+    In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family martingales for $\gamma\in (0, \beta)$.
 Recall that $L$ is the infinitesimal generator of the OU-process.
-Let $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ be such that $Lf \in \mathcal{P}$, and let $a\in \mathbb{R}$, we define that
-\begin{align}
+Let $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ be such that $Lf \in \mathcal{P}$, and let $a\in \mathbb R$, we define that
+\begin{equation}\begin{split}
 \label{defmartingale}
     M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds.
-\end{align}
+\end{split}\end{equation}
     The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
@@
 \label{lemma25}
-    Let $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ be such that $Lf \in \mathcal{P}$ and let $a\in \mathbb R$.
-Then, for any $\mu\in \mathcal M_c(\mathbb{R}^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
+    Let $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ be such that $Lf \in \mathcal{P}$ and let $a\in \mathbb R$.
+Then, for any $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
 \end{lem}
@@
     Write $\bar{f}=(L+ab)f$. According to \cite[Theorem A.55]{Li2011Measure-valued}, we have
-\begin{align}\label{Theorem55}
-    T_t^{ab}f(x)= f(x)+\int_0^t T_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb{R}^d.
-\end{align}
+\begin{equation}\begin{split}\label{Theorem55}
+    P_t^{ab}f(x)= f(x)+\int_0^t T_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d.
+\end{split}\end{equation}
 Let $0\leq s\leq t$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{martingale1}
     &\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
-    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
-    \\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du -\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
-\end{align}
+    \\&=e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
+    \\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du 
+    \\&\quad -\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
+\end{split}\end{equation}
     Using \eqref{Theorem55} and Fubini's theorem, we have
-\begin{align}
+\begin{equation}\begin{split}
     &\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle T_{u-s}^{ab}\bar{f},X_s\rangle~du\\
@@
     f,X_s\rangle.
-\end{align}
+\end{split}\end{equation}
    Using this and \eqref{martingale1}, we get the desired result.
@@
 \begin{lem}\label{lemma26}
-    For any $\mu\in \mathcal M_c(\mathbb{R}^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
+    For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
     Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $\gamma\in (0, \beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
@@
 \begin{proof}
-  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb{R}^d)$.
+  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb R^d)$.
 
@@
 \]
-   For any $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb{R}^d)$, note that
+   For any $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, note that
 \[
@@
 
-   Hence, for each $\gamma \in (0,\beta)$ and any $\mu\in \mathcal M_c(\mathbb{R}^d)$,
+   Hence, for each $\gamma \in (0,\beta)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$,
     the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
@@
 
-In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$  for any $\mu\in \mathcal M_c(\mathbb{R}^d)$.
+In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$  for any $\mu\in \mathcal M_c(\mathbb R^d)$.
 
@@
      Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-% According to Lemma \ref{lem: control of mgtrs},
-Using Lemma \ref{lem: control of mgtrs} with $g=1$ and $k=0$,
- there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
-    \begin{align}
+     Using Lemma \ref{lem: control of mgtrs} with $g=1$ and $k=0$, there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
+    \begin{equation}\begin{split}
         \mathbb{P}_{\mu}\big[\big|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\|\big|^{1+\gamma}\big]
         \leq C_0e^{\alpha t+(t-s)\alpha\gamma}.
-    \end{align}
+    \end{split}\end{equation}
     Dividing both sides by $e^{\alpha t(1+\gamma)}$, we get
-    \begin{align}
+    \begin{equation}\begin{split}
         \mathbb{P}_{\mu}\big[|H_s-H_r|^{1+\gamma}\big]\leq  C_0 e^{-\alpha \gamma s}.
-    \end{align}
+    \end{split}\end{equation}
     Thus there is a $C>0$ for any $0\leq s<t$,
-\begin{align}
+\begin{equation}\begin{split}
 	& \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}
@@
     \qedhere
-\end{align}	
+\end{split}\end{equation}	
 \end{proof}
 
+\begin{comment}
 From now on, we write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
@@
 	For any $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for all $f:[0,\infty)\to [1,\infty)$ and $t\geq 0$, we have
-\begin{align}
+\begin{equation}\begin{split}
     \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)\leq C \Big(\frac{f(t)}{e^{\alpha t}}\Big)^{\beta}.
-\end{align}
+\end{split}\end{equation}
 \end{lem}
@@
     Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
-\begin{align}\label{CSBP}
+\begin{equation}\begin{split}\label{CSBP}
     \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
@@
     \quad \lambda \geq 0, t\geq 0,
-\end{align}
+\end{split}\end{equation}
     where
@@
 \]
-    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger root of $\psi(z)=0$.
+    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\bar v\|\mu\|}$, where $\bar v=\alpha^{1/\beta}$ is the larger root of $\psi(z)=0$.
     By \eqref{CSBP} and the Markov property, we have for all $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
@@
 
-\begin{align}
+\begin{equation}\begin{split}
     \label{laplaceexpress}
@@
     &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
-    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\alpha^*\|X_t\|})] }{\mathbb P_\mu(D^c)}
-    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}
-    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
-\end{align}
+    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\bar v\|X_t\|})] }{\mathbb P_\mu(D^c)}
+    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\bar v)}}{1-e^{-\|\mu\|\bar v}}
+    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\bar v}}\left|v_t(\lambda)-v_t(\lambda+\bar v)\right|.
+\end{split}\end{equation}
 
@@
     \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]\\
-    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
+    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\bar v}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\bar v)\right|.
 \end{align*}
@@
 \begin{align*}
-    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta} \left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right| \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
-    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
-    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
+    \left|v_t(\lambda)-v_t(\lambda+\bar v)\right|&\leq\frac {\alpha^{1/\beta}}{\beta} \left|w_t(\lambda)-w_t(\lambda+\bar v)\right| \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}\\
+    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\bar v)^{\beta}}\right|e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}\\
+    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}.
 \end{align*}
 Therefore, for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for all non-negative function $f$ on $[0,\infty)$, $\lambda \geq 0$ and $t\geq 0$, we have
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: inequality before take lambda}
     \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)
-    \leq C_0e^{\lambda f(t)}\frac{1}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
-\end{align}
+    \leq C_0e^{\lambda f(t)}\frac{1}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}.
+\end{split}\end{equation}
 
@@
 \begin{align*}
-    \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}
-    &\leq\sup_{s\in [\lambda,\lambda+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
-    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}} =: C_1.
+    \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}
+    &\leq\sup_{s\in [\lambda,\lambda+\bar v]}\frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
+    &\leq \frac{(1+\bar v)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}} =: C_1.
 \end{align*}
-Finally, plugging
-%$\lambda = f(t)^{-1} \in [0,1]$
-$\lambda = f(t)^{-1} \in (0,1]$
+Finally, plugging $\lambda = f(t)^{-1} \in (0,1]$
 back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.
 \end{proof}
+\end{comment}
+
+\subsection{Small value probability}
+    In this subsection, we digress briefly from super-OU process and consider a supercritical continuous-state branching process (CSBP) $(Y_t)$.
+Our goal is to determing how fast the probability $P_x(0<e^{-\alpha t}Y_t \leq k_t)$ convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
+    Let branching mechanism corresponding to the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ be denoted as
+\[
+    \psi(z)
+    := -\alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z\geq 0,
+\]
+    where $\alpha > 0$, $\rho \geq 0$ and $\pi$ is a measure on $(0,\infty)$ satisfying $\int_{(0,\infty)} (y \wedge y^2) \pi(dy) < \infty$.
+    Suppose that the Grey's condition is satisfied, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$. 
+    Also suppose that the $L \log L$ critierion is satisfied, i.e. 
+\[
+    \int_1^\infty y \log y~\pi(dr)< \infty.
+\]
+    Write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
+\begin{prop}
+\label{lem: control of XT}
+    Suppose that $t\mapsto k_t$ is a strictly positive map on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$. 
+    Then, for each $x\geq 0$, there are constants $C,\delta>0$ such that
+\[
+    \mathbf P_x(0<W_t\leq k_t) \leq C(k_t^\delta + e^{-\delta t}), \quad t\geq 0.
+\]
+\end{prop}
+\begin{proof}
+    \emph{Step 1}. We recall some known facts about the CSBP $(Y_t)$. 
+    For each $\lambda \geq 0$, denote by $t\mapsto v_t(\lambda)$ the unique positive solution of 
+\[
+    v_t(\lambda) 
+    = \lambda - \int_0^t \psi(v_s(\lambda))ds,\quad t\geq 0.
+\]
+    Then according to the definition of CSBP, we have
+\[
+    \mathbf P_x[e^{-\lambda Y_t}] = e^{-xv_t(\lambda)}, \quad t\geq 0, \lambda \geq 0, x\geq 0.
+\]
+    Taking $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
+\begin{equation}
+\label{eq: svp1}
+    \mathbf P_x(Y_t = 0)=e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
+\end{equation}
+    It is known, see \cite[Theorem 3.5-3.8]{Li2011Measure-valued} for example, that under the Grey's condition, the following statements are true:
+\begin{itemize}
+\item
+    $0\leq \bar v_t < \infty$ for all $t>0$.
+\item 
+    $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
+\end{itemize}
+    Taking $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
+\[
+    \mathbf P_x(\exists t \geq 0, Y_t = 0) 
+    = e^{-x\bar v}, \quad x\geq 0.
+\]
+
+    Note that $\psi$ has derivative 
+\[
+    \psi'(z) 
+    = -\alpha + 2\beta z + \int_{(0,\infty)}(1-e^{-zy})y\pi(dy),\quad z\geq 0,
+\]
+    which is increasing in $z$. 
+    This says that $\psi$ is a convex function. 
+    Also notice that $\psi'(0+)=-\alpha <0$ and that there exists $z>0$ such that $\psi(z)>0$. 
+    So, we can verify that the following are true: 
+\begin{itemize}
+\item
+    $\bar v > 0$ , 
+\item
+    $\psi(z) < 0$ on $z\in (0,\bar v)$, 
+\item
+    $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
+\end{itemize}
+    It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that
+\begin{itemize}
+\item
+    if $\lambda \in (0,\bar v)$ then $0<\lambda \leq v_t(\lambda)<\bar v $, and that
+\[
+    \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0.
+\]
+\item
+    if $\lambda \in (\bar v, \infty)$ then $\bar v < v_t(\lambda)\leq \lambda< \infty $, and that
+\[
+  \int_{v_t(\lambda)}^\lambda\frac{dz}{\psi(z)} = t, \quad t\geq 0.
+\]
+\end{itemize}
+    By monotonicity, we have that
+\begin{equation}
+\label{eq:svp2}
+    \int_{\bar v_t}^\infty \frac{dz}{\psi(z)} = t, \quad t\geq 0.
+\end{equation}
+
+    Step 2. We will show that, for each $x \geq 0$ there exists a constant $C>0$ such that
+\[
+    \mathbf P_{x}(0< W_t\leq k_t)
+    \leq C\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
+    \quad t\geq 0.
+\]
+In fact, for each $x\geq 0$ and $t\geq 0$ we have
+\begin{equation}\begin{split}
+    &\mathbf P_{x}(0<W_t \leq k_t)
+    = \mathbf P_{x}( e^{-k_t^{-1}W_t}\geq e^{-1},W_t > 0)
+    \\&\leq e \mathbf P_{x}[e^{-k_t^{-1} W_t};W_t > 0]
+    =  e\big(\mathbf P_x[e^{-k_t^{-1} W_t}]-\mathbf P_x(W_t = 0)\big)
+    \\ &= e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
+    \\&\leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big)
+\end{split}\end{equation}
+    as required in this step.
+
+    Step 3. We will show that there exists constants $c, \delta, t_0 > 0$ such that 
+\[
+    |\bar v_t-\bar v| 
+    \leq ce^{-\delta t}, 
+    \quad t\geq t_0.
+\]
+    In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$, and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
+    According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
+\[
+    t_0 
+    := \int^\infty_{z_0} \frac{dz}{\psi(z)} < \infty.
+\]
+    For each $t > t_0$, according to the \eqref{eq:svp2}, we have
+\begin{equation}\begin{split}
+    &t-t_0 = \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)} 
+    =\int_{\bar v_t}^{z_0} \frac{dz}{\psi(z)}
+    \\ &\leq \int_{\bar v_t}^{z_0} \frac{dz}{(z-\bar v)\tau} 
+    = \frac{1}{\tau} \big(\log (z_0-\bar v) - \log(\bar v_t-\bar v)\big).
+\end{split}\end{equation}
+    Rearrange this, we have
+\[
+    \bar v_t - \bar v \leq (z_0 - \bar v)e^{-\tau(t-t_0)},
+    \quad t\geq t_0.
+\] 
+    This implies the desired result in this step.
+
+    Step 4: We will show that there exists constant $C, \delta,t_0>0$ such that
+\[
+    |\bar v - v_t(k_t^{-1} e^{-\alpha t})|\leq Ck_t^\delta, \quad t\geq t_0.
+\]
+    Define 
+\[
+    \rho_t := 1+ \frac{\log k_t}{t\alpha}, \quad t\geq 0.
+\]
+    According to the fact that
+\[
+    k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}, \quad t\geq 0,
+\]
+    and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
+    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$ where the martingale limit $W_\infty$ is a non-degenerate random variable.
+This implies that
+\[
+    v_t(e^{-\alpha t}) = -\log \mathbf P_1[e^{-W_t}]\xrightarrow[t\to \infty]{} - \log \mathbf P_{1}[e^{-W_\infty}] =: z^* \in (0,\infty).
+\]
+    The $L \log L$ critierioin also garuntees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.ly in $\mathbf P_1$.
+This and the non-degeneracy of $W_\infty$ implies that
+\[
+    z^*=-\log \mathbf P_1[e^{-W_\infty}] < -\log \mathbf P_1(W_\infty = 0) = \bar v.
+\]
+
+    Fix an arbitrary $\epsilon \in (0,\tau)$.
+    According to the fact that $\tau=\psi'(\bar v)>0$ , there exists $z_0 \in (0,\bar v)$ such that for all $z\in (z_0, \bar v)$, we have $-\psi(z)\geq (\bar v - z)(\tau- \epsilon)$.
+    Fix this $z_0$. For $t$ large enough, according to the fact that $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$, we can verify the following:
+\begin{equation}\begin{split}
+    &t =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
+    \\&= \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)}
+     \\&= \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
+\end{split}\end{equation} 
+    where we used the fact that
+\[
+    \int_{v_{\rho_t t}(e^{-\alpha \rho_tt})}^{z_0} \frac{dz}{-\psi(z)} \xrightarrow[t\to \infty] {}\int_{z^*}^{z_0} \frac{dz}{-\psi(z)}.
+\]
+    Now we have, for $t$ large enough,
+\begin{equation}\begin{split}
+    &t\leq  \rho_t t + O(1)+ \int_{z_0}^{v_t(k_t^{-1}e^{-\alpha t})} \frac{dz}{(\bar v-z)(\tau - \epsilon)}
+    \\&=  \rho_t t +O(1)- \frac{1}{\tau-\epsilon}\Big( \log \big(\bar v-v_t(e^{-\alpha \rho_t t})\big) - \log(\bar v-z_0)\Big).
+\end{split}\end{equation}
+    Rearrange this, we have, for $t$ large enough,
+\[
+    e^{-t(\tau - \epsilon)} \geq e^{-\rho_t t(\tau - \epsilon)+O(1)}(\bar v - v_t(e^{-\alpha \rho_t t})).
+\]
+    Therefore, there exists constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$, 
+\[
+    \bar v - v_t(k_t^{-1} e^{-\alpha t}) \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
+    \leq Ck_t^{\frac{\tau - \epsilon}{\alpha}}.
+\]
+    This implies the required result in this step.
+
+    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exists constant $C, \delta, t_0 > 0$ such that
+\[
+    \mathbf P_{x}(0< W_t\leq k_t) \leq C(k_t^{\delta}+e^{-\delta t}),\quad t\geq t_0.
+\]
+Note that the left side is always bounded by $1$, so if we can take $t_0 =0$ in the above statement. 
+\end{proof}
+\begin{comment}
+
+\end{comment}
 
@@
     Define
- \begin{align}
+ \begin{equation}\begin{split}
  \label{parameter_mk}
       m_t[f]
-      :=e^{-\alpha (t+1)}\int_{\mathbb R^d} (Z_1T_t^{\alpha}f)(x)\varphi(x)dx,\quad t\geq 0, f\in \mathcal P.
- \end{align}
+      :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
+ \end{split}\end{equation}
     According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
@@
     According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, then the following limit exists:
-\begin{align}
+\begin{equation}\begin{split}
 \label{para: critical case}
-    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\Psi_0(-i\phi),\varphi\rangle,
-\end{align}
+    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
+\end{split}\end{equation}
     where
@@
     According to \cite[Lemma 5.1]{MM}, if $f\in \mathcal{P}$ satisfies that $\alpha\beta<\kappa_fb(1+\beta)$, then
-\begin{align}
+\begin{equation}\begin{split}
     m[f]
     :=\sum_{k=0}^\infty m_k[f]
-    =\alpha e^{\alpha}\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx, \label{msmallcase}
-\end{align}
-and both the series and the integral converge absolutely.
+    =\alpha e^{\alpha}\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds \label{msmallcase}
+\end{split}\end{equation}
+is well defined.
 \begin{lem}
@@
     Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
-    Then $$\theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\}$$
-    is the characteristic function of a $(1+\beta)$-stable random variable.
+    Then $$\theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},\quad \theta \in \mathbb R^d$$
+    is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
 \end{lem}
@@
 	Finally,
-\begin{align}
+\begin{equation}\begin{split}
     &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
@@
 \qedhere
-\end{align}
+\end{split}\end{equation}
 \end{proof}
@@
 $
-	is a $(1+\beta)$-controallable operator on $\mathcal P$.
+	is a $(1+\beta)$-controllable operator on $\mathcal P$.
 	This implies that $x \mapsto \int_0^1 T_{1-s}^\alpha (|T_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
@@
 Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
-Then for all $k\geq 0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
- \begin{align}
+Then for all $k\geq 0$ and $\mu \in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+ \begin{equation}\begin{split}
       \gamma_{t,k}:=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
- \end{align}
+ \end{split}\end{equation}
  where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
@@
     We only need to show that
-\begin{align}
+\begin{equation}\begin{split}
     \mathbb{P}_{\mu}[\exp(i\gamma_{t,k}); D^c]
@@
     \quad \mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0.
-\end{align}
+\end{split}\end{equation}
     In fact, once we prove this, we can replace $f$ by $\theta f$, with $\theta \in \mathbb R$ being  arbitrary,  to get the desired result.
@@
 \[
-	A_t(\epsilon):=\{ \|X_t\| \geq \|\mu\|e^{(\alpha - \epsilon)t} \},\quad t\geq 0, \epsilon > 0.
+    A_t(\epsilon):=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \},\quad t\geq 0, \epsilon > 0.
 \]
@@
     Step 1. We will show that for all $\epsilon > 0, k\geq 0$ and $t>k+1$, we have
-\begin{align}
+\begin{equation}\begin{split}
     \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
     \leq J_1(t,k,\epsilon)+J_2(t,k,\epsilon)+J_3(t,k,\epsilon)
-\end{align}
+\end{split}\end{equation}
     where
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: Def of Ji}
     J_1(t,k,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle U_1(\theta_{t,k}T_k^{\alpha}f)-\tilde U_1(\theta_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
+    &:= \mathbb{P}_{\mu}\big[|\langle K_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
     \\ J_2(t,k,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|; A_{t-k-1}(\epsilon)\big],
+    &:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|; A_{t-k-1}(\epsilon)\big],
     \\ J_3(t,k, \epsilon)
@@
     &:= (e^{\alpha k}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
-\end{align}
-In fact, from the definitions of $U_1, \tilde U_1$ and $Z_1$, we have that for all
+\end{split}\end{equation}
+In fact, from the definitions of $K_1$ and $Z_1$, we have that for all
 $k\geq 0, t\geq k+1$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: need1}
     &\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}|\mathscr{F}_{t-k-1}]
-    =\mathbb{P}_{\mu}[e^{i\theta_{t,k}\langle T_k^{\alpha}f,X_{t-k}\rangle-i\theta_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle}|\mathscr{F}_{t-k-1}]
-    \\&=e^{\langle (U_1 - iT_{1}^{\alpha}) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle}
-    =e^{\langle (U_1 - \tilde U_1+Z_1) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle}.
-\end{align}
+    =\mathbb{P}_{\mu}[e^{i\theta_{t,k}\langle P^\alpha_k f,X_{t-k}\rangle-i\theta_{t,k}\langle P^\alpha_{k+1} f, X_{t-k-1}\rangle}|\mathscr{F}_{t-k-1}]
+    \\&=e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}
+    =e^{\langle (Z_1 + K_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
+\end{split}\end{equation}
     From Corollary \ref{cor: alpha stable rv}, we have
@@
 \end{equation}
-    According to the definitions of $\tilde U_1$ and $Z_1$, \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
+    According to \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
 \[
@@
     we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: inequality that will used later}
@@
     \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{e^{\alpha}m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon)
-    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (U_1 - iT_{1}^{\alpha}) (\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
-    \\& \leq \mathbb{P}_{\mu}\big[|\langle (U_1 - i T_1^\alpha)(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    \\& \leq \mathbb{P}_{\mu}\big[|\langle (U_1 - i T_1^\alpha)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
     \\&\leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon).
-\end{align}
-
-Step 2.  We will show that there exists a $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-    \begin{align}
+\end{split}\end{equation}
+
+Step 2.  We will show that for each $\epsilon>0$ small enough, there exists constants $C, \delta>0$ such that
+    \begin{equation}\begin{split}
     \label{lemma31q}
-      %J_1(k,t,\epsilon)
       J_1(t,k,\epsilon)
-      \leq C\exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\}.
-    \end{align}
-	In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}.(6).
+      \leq Ce^{-\delta (t-k)},
+      \quad k\geq 0, t\geq k+1.
+    \end{split}\end{equation}
+    In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
     Then, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
-   & |(U_1 - \tilde U_1)(\theta_{t,k}T_k^{\alpha}f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
-   \leq R(|\theta_{t,k}T_k^{\alpha}f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
-   \\&\leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
-    \leq S \Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}Qf\Big)
-   \\&\leq \Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+2\beta}SQf
-   \\&=\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}}e^{\frac{1+2\beta}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf
-   \\&\leq\|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}SQf,
-\end{align}
-%new added
+\begin{equation}\begin{split}
+   & |Y_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
+   \leq R(|\theta_{t,k}P^\alpha_k f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
+   \\&\leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha k}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
+   \\&\leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf
+   \\&=\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
+   \\&\leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
+\end{split}\end{equation}
 where $Q$ is defined by \eqref{Q}.
-%end new
 Thus for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: estimate of J1}
-     %J_1(k,t,\epsilon)&
      J_1(t,k,\epsilon)&
-     \leq \|\mu\|^{-\frac{(1+2\beta)}{(1+\beta)}} e^{-\frac{(\alpha-\epsilon)(1+2\beta)(t-k-1)}{1+\beta}}\mathbb{P}_{\mu}[\langle SQf,X_{t-k-1}\rangle]\\
-     & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
-\end{align}
-%new added
+     \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}\mathbb{P}_{\mu}[\langle RQf,X_{t-k-1}\rangle]\\
+     & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)},
+\end{split}\end{equation}
 where $Q_0$ is defined by \eqref{Q_k} with $k=0$.
-%end new
+    By taking $\epsilon>0$ small enough, we get the desired result in this step.
 
     Step 3.
-	Fix a $\gamma\in(0,\beta)$ small enough so that $\alpha \gamma < b < (1+\gamma)b$.
-	Then there exists a constant $C > 0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
+    We will show that for $\epsilon>0$ small enough, there exists constants $C, \delta>0$ such that
+    \begin{equation}\begin{split}
     \label{eq:31step3}
       J_2(t,k,\epsilon)
-    \leq C \exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big).
-\end{align}
+      \leq Ce^{-\delta (t-k)},
+      \quad k\geq 0, t\geq k+1.
+    \end{split}\end{equation}
     In fact, according to the definitions of $Z_1$ and $m_t$, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-    \begin{align}
-          &\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]
-          \\&= \theta_{t,k}^{1+\beta} \langle Z_1T_k^{\alpha}f,X_{t-k-1}\rangle - e^{-\alpha k}\langle  Z_1T_k^{\alpha}f,\varphi\rangle
-          \\&=e^{-\alpha k}\Big(\frac{\langle Z_1T_k^{\alpha}f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1T_k^{\alpha}f ,\varphi\rangle\Big).
-    \end{align}
+    \begin{equation}\begin{split}
+          &\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]
+          \\&= \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha k}\langle  Z_1P^\alpha_k f,\varphi\rangle
+          \\&=e^{-\alpha k}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big).
+    \end{split}\end{equation}
 Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: prevJ2}
-%&J_2(k,t,\epsilon)\\&=
 J_2(t,k,\epsilon)&
-	= \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]
-    \\&=e^{-\alpha k}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1T^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1T^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
-    &\leq \|\mu\|^{-1} e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
-\end{align}
+    = \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]
+    \\&=e^{-\alpha k}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1P^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
+    &\leq e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
+\end{split}\end{equation}
 where
@@
 g_k
-	:= \frac{Z_1 T^{\alpha}_k f-\langle  Z_1T^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)k}},
+    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)k}},
     \quad k \in \mathbb Z_+.
@@
 \[
-     |T_t g_k|\leq e^{-bt}h,
+     |P_t g_k|\leq e^{-bt}h,
      \quad k\geq 0,t\geq 0.
@@
     \text{ and } Q_1 (\operatorname{Im} g_k)\leq h,
- 	\quad k \geq 0.
- \]
-	Recall that $\gamma\in(0,\beta)$ is chosen small enough so that $\alpha \gamma < b < (1+\gamma)b$.
-	According to Lemma \ref{lem: control moment}.(3) (with $\kappa=1$), there exists $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
+    \quad k \geq 0,
+ \]
+    where $Q_1$ is defined by \eqref{Q_k} with $k=1$.
+
+    Chose a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
+    According to Lemma \ref{lem: control moment}.(3) (with $\kappa=1$), there exists $C>0$ such that for all $t\geq 0$ and $k\geq 0$,
+\begin{equation}\begin{split}
     &\mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t}\rangle\right|\right]
@@
     \\& \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C e^{\frac{\alpha t}{1+\gamma}}.
-\end{align}
-Therefore, according to \eqref{eq: prevJ2}, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
-%	&J_2(k,t,\epsilon)
+\end{split}\end{equation}
+Therefore, according to \eqref{eq: prevJ2}, we have there exists constant $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+\begin{equation}\begin{split}
+\label{eq: right bound for J2}
     J_2(t,k, \epsilon)&
-\leq  \|\mu\|^{-1}e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
-	\\&\leq \|\mu\|^{-1}C e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)}
-	\\&= \|\mu\|^{-1}C e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
-	\\&\leq \|\mu\|^{-1}C e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)},
-\end{align}
-	as desired.
-
-	Step 4. We will show that, for each $\epsilon\in (0,  \alpha]$, there exist $C,\delta>0$ such that for all $k\geq0, t\geq k+1$,
-\begin{align}\label{ineq: control of J3}
- %   J_3(k,t,\epsilon)\leq Ce^{-\delta (t-k-1)}.
- J_3(t,k,\epsilon)\leq Ce^{-\delta (t-k-1)}.
-\end{align}
+\leq  e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
+    \\&\leq C e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)}
+    \\&= C e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
+    \\&\leq C e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
+\end{split}\end{equation}
+    By taking $\epsilon >0$ small enough, we get the required result in this step.
+
+    Step 4. We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C,\delta>0$ such that for all $k\geq0, t\geq k+1$,
+\begin{equation}\begin{split}\label{ineq: control of J3}
+ J_3(t,k,\epsilon)\leq Ce^{-\delta (t-k)}.
+\end{split}\end{equation}
     In fact, we have that for all $t\geq 0, \epsilon >0$,
-\begin{align}
+\begin{equation}\begin{split}
     &\mathbb P_{\mu}(A_{t}(\epsilon), D) = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
-	\\&= \mathbb P_\mu[e^{-\alpha^*\|X_t\|};A_t(\epsilon)]
-%	\leq \exp({-\alpha^* e^{(\alpha - \epsilon)t}}).
-\leq \exp({-\alpha^* \|\mu\|e^{(\alpha - \epsilon)t}}).
-\end{align}
-According to Lemma \ref{lem: control of XT}, there is a constant $C>0$ such that
-for all $t\geq 0, \epsilon >0$,
-\begin{align}
-	\mathbb P_\mu(A_t(\epsilon)^c,D^c) = \mathbb P_\mu(D^c) \tilde{\mathbb P}_\mu(\|X_t\|\leq e^{(\alpha - \epsilon) t}) \leq \mathbb P_\mu(D^c)C e^{-\epsilon \beta t}.
-\end{align}
-	Combining these, we get the desired result in step 4.
-
-	Step 5.  Combining the results in Steps 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$,
+    \\&= \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
+    \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
+\end{split}\end{equation}
+According to Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there are constants $C, \delta>0$ such that
+for all $t\geq 0$,
+\begin{equation}\begin{split}
+    \mathbb P_\mu(A_t(\epsilon)^c,D^c) \leq   \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\|\leq e^{ - \epsilon t}) \leq C (e^{-\epsilon \delta t}+e^{-\delta t}).
+\end{split}\end{equation}
+    Combining these results, we get the desired result in step 4.
+
+    Finally, combining the results in Steps 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$,
 we immediately get the desired result.
@@
 Then there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
-\begin{align}
-    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]\leq Ce^{-\delta(t-k-1)}.
-\end{align}
+\begin{equation}\begin{split}
+    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]\leq Ce^{-\delta(t-k)}.
+\end{split}\end{equation}
 \end{cor}
 \begin{proof}
-	Define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as $J_1, J_2$ and $J_3$ in \eqref{eq: Def of Ji}.
-	Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal P$.
+	For each $f\in \mathcal P$, define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as $J_1, J_2$ and $J_3$ in \eqref{eq: Def of Ji}.
+	Now, fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and an $f\in \mathcal P$.
     According to \eqref{eq: inequality that will used later},  we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
+\begin{equation}\begin{split}
     &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
     \\&\leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
-\end{align}
+\end{split}\end{equation}
+
+    Let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
 	According to \eqref{eq: estimate of J1}, we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
-	J^{\theta f}_1(k,t,\epsilon)
-     & \leq \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQ (\theta f), \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\}
-     \\& = |\theta|^{1+2\beta} \|\mu\|^{-\frac{1+2\beta}{1+\beta}} \langle Q_0 SQf, \mu \rangle \exp\Big\{-\Big(\alpha\frac{\beta}{1+\beta}-\epsilon\frac{1+2\beta}{1+\beta}\Big)(t-k-1)\Big\},
-\end{align}
-	where $(R,S)$ is the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}.(6).
+\begin{equation}\begin{split}
+	&J^{\theta f}_1(k,t,\epsilon)
+     \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}
+     \\& \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}.
+\end{split}\end{equation}
 	From the definitions of $Z_1$ and $m_t$ we get that for all $g\in \mathcal P, \theta \geq 0, t\geq 0$,
@@
 \]
-	According to this and Step 3 in the proof of the previous lemma, we have that there exists a constant $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
+	According to this and \eqref{eq: right bound for J2} in the Step 3 in the proof of the previous lemma, we have that there exists a constant $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+\begin{equation}\begin{split}
 \label{eq:31step3b}
@@
     \leq C |\theta|^{1+\beta}\exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big).
-\end{align}
-	Finally, using the estimates of $J^{\theta f}_{i}, i = 1,2$ and the estimate of $J_3$ in Step 4 of the proof of the previous lemma, we get the desired result by choosing $\epsilon$ small enough.
+\end{split}\end{equation}
+	Finally, noticing that $|\theta| < \Theta$, using the estimates of $J^{\theta f}_{i}, i = 1,2$ and the estimate of $J_3$ in Step 4 of the proof of the previous lemma, we get the desired result by choosing $\epsilon$ small enough.
 \end{proof}
@@
 Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then there exist $C,\delta>0$ such that
-%for all $T\geq 0$,
 for all $t\geq 0$,
-%$n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$
-$n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb{R}^{n+1}$
+$n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$
 satisfying $|\theta_i|\leq \Theta$, we have
-\begin{align}
+\begin{equation}\begin{split}
 \label{32corollary}
     \Big|\mathbb{\tilde{P}}_{\mu}\Big[\prod_{k=0}^n\exp\Big(i\theta_k \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}}\Big)-\prod_{k=0}^n\exp(e^{\alpha}m_k[\theta_k f])\Big]\Big|\leq C e^{-\delta(t-n)}.
-\end{align}
+\end{split}\end{equation}
 \end{prop}
@@
     Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
-    %Fix $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ 
-    Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb{R}^{n+1}$ 
+    %Fix $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb R^{n+1}$ 
+    Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$ 
     satisfying $|\theta_i|\leq \Theta$.
@@
         \\&\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
-        \\& \leq C e^{-\delta(t-k-1)}.
+        \\& \leq C e^{-\delta(t-k)}.
     \end{align*}
 Therefore,
-\begin{align}
+\begin{equation}\begin{split}
     \text{LHS of \eqref{32corollary}}&= \left|a_{-1}-a_n\right|
     \leq\sum_{k=0}^n\left|a_{k-1}-a_k\right|
-    \leq \sum_{k=0}^n C e^{-\delta(t-k-1)}.
-\end{align}
-	Recall that $C, \delta>0$ are independent of the choice of $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb{R}^{n+1}$ with $|\theta_i|\leq \Theta$.
+    \leq \sum_{k=0}^n C e^{-\delta(t-k)}.
+\end{split}\end{equation}
+	Recall that $C, \delta>0$ are independent of the choice of $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb R^{n+1}$ with $|\theta_i|\leq \Theta$.
+    This implies the desired result.
 \end{proof}
@@
      %   \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
-         \frac{\langle T^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
+         \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
         \\&=:I_1(t)+I_2(t) + I_3(t),
@@
 \]
-    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb{R}$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ 
+    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb R$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ 
     %in Corollary \ref{corollary31},
@@
 By \cite[Lemma 3.4.3]{Durrett2010Probability},
-%\begin{align}\label{ineq: control of I1t}
+%\begin{equation}\begin{split}\label{ineq: control of I1t}
 \begin{equation}\label{ineq: control of I1t}
@@
     \quad t\geq t_0,
-%\end{align}
+%\end{split}\end{equation}
 \end{equation}
@@
     Define for all $k \geq 0$ and $t\geq k+1$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{def: Dtk}
     \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
-\end{align}
+\end{split}\end{equation}
 
     Step 1. We will show that there exist $C,\delta >0$ such that for all $k \geq 0$ and $t\geq k+1$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{thm121}
-    \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}^c_{t,k}}\big]
+    \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|;\mathcal{D}^c_{t,k}\big]
     \leq C e^{-\delta (t-k)}.
-\end{align}
-    In fact, let $C_1$ be the constant in  Lemma \ref{lem: control of Wt} corresponding to this fixed $\gamma$ and $C_2$ be the constant in Lemma \ref{lem: control of XT}.
-    By Chebyshev's inequality, there exists $C>0$ such that for all $k \geq 0$ and $t\geq k+1$,
-\begin{align}
+\end{split}\end{equation}
+    Then according to Lemma \ref{lem: control of Wt}, Proposition \ref{lem: control of XT} and Chebyshev's inequality, there exists $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
+\begin{equation}\begin{split}
 \label{eq: prob of Dtkc}
@@
     \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}),
-    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]+\mathbb{\tilde{P}}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
-    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}+\mathbb{\tilde{P}}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
-    \\&\leq C_1  \mathbb{P}_{\mu}(D^c)^{-1}  e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C_2 e^{-\eta_1\beta(t-k-1)}.
-\end{align}
+    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]
+    \\&\quad +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
+    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}
+    \\&\quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
+    \\&\leq C e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C e^{-\delta(t-k-1)}.
+\end{split}\end{equation}
     This implies the desired result in this step, since $|Y_{t,k}| \leq 2$ a.s..
@@
     Step 2. We will show that there exist constant $C,\delta > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{thm122}
@@
      \leq  C e^{-\delta (t-k)}.
-\end{align}
+\end{split}\end{equation}
     In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \geq 0$ and $t\geq k+1$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: control of Ykt}
@@
         \\&\leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
-\end{align}
+\end{split}\end{equation}
     where
@@
     Thus, there is a constant $C\geq 0$ such that,
-\begin{align}
+\begin{equation}\begin{split}
 \label{ineq: control of Kkt}
@@
      \quad k \geq 0, t\geq k+1.
-\end{align}
-   % According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt}, \eqref{ineq: control of Kkt}, 
+\end{split}\end{equation}
    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and  \eqref{ineq: control of Kkt}, 
     there exist constants $C,C'>0$ such that  for all $k\geq 0$ and $t\geq k+1$,
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: Y in D}
@@
     \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}\\&= C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k-1)},
-\end{align}
+\end{split}\end{equation}
     as desired in this step.
@@
     Step 3. We will show that there exist $C, \delta> 0$ such that for $t$ large enough,
-%\[
 \begin{equation}\label{domi-difference of Is}
@@
     \leq C t^{-\delta}.
-%\]
 \end{equation}
@@
     Therefore, there exist $C, \delta > 0$ and $C'$ such that for all $t \geq 1$,
-\begin{align}
+\begin{equation}\begin{split}
     &\sum_{k=0}^{\lfloor t-\ln t \rfloor} \tilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
@@
     \\&\leq C' e^{-\delta t}e^{\delta (t-\ln t)}
-    = C'\frac{1}{t^{\delta}},
-\end{align}
-%    giving the desired result in this step.
-which implies \eqref{domi-difference of Is}  by \eqref{ineq: control of I1t}.
-
-    %new added
+    = C'\frac{1}{t^{\delta}}.
+\end{split}\end{equation}
     Letting $t\to\infty$ in \eqref{domi-difference of Is}, we get \eqref{toprove-1}.
 
-    %end new
-
     Step 4. We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\tilde{P}}_{\mu}$.
-    In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Lemma \ref{lem: control of XT}, there exists $C>0$ such that
-\begin{align}
-    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C t^{-\frac{\beta}{2}}, \quad t\geq0.
-\end{align}
-    Therefore, there exists $C>0$ such that
-\begin{align}\label{Theorem123}
+    In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exists $C, \delta>0$ such that
+\begin{equation}\begin{split}
+    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C t^{-\delta}, \quad t\geq0.
+\end{split}\end{equation}
+    Therefore, there exists $C, \delta>0$ such that
+\begin{equation}\begin{split}\label{Theorem123}
     |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
-    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ct^{-\frac{\beta}{2}},
+    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ct^{-\delta},
     \quad t\geq t_0.
-\end{align}
+\end{split}\end{equation}
     Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})\leq \frac{1}{2(1+\beta)}$.
@@
 	Step 5. We will show that $I_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
-	%In fact, we can write
 In fact, we have
-\begin{align}
+\begin{equation}\begin{split}
 	&|I_3(t)|
-	%\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
-\leq \frac{\langle |T^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
+\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
 	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(te^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
@@
 	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
-\end{align}
+\end{split}\end{equation}
 
@@
 	Write
-\begin{align}
+\begin{equation}\begin{split}
     f
@@
     \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f}.
-\end{align}
+\end{split}\end{equation}
 	Then
@@
 	we have
-\begin{align}
+\begin{equation}\begin{split}
 \label{as convergence}
@@
      \xrightarrow[t\to \infty]{} \sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
-\end{align}
+\end{split}\end{equation}
 $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
 	Therefore, it is suffice to show that
-\begin{align}
+\begin{equation}\begin{split}
     J_t
@@
     \quad t\geq 0,
-\end{align}
+\end{split}\end{equation}
 	converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$.
@@
 	Step 1. Let $g\in \mathcal P$.
-	Let $a > 0$ be such that $a< \kappa_g$ and $a < \frac{\alpha \beta}{b(1+\beta)}$.
-	We will show that for each $\gamma\in (0,\beta)$ there exist constants $C,\delta > 0$ such that
-\[
-	\|e^{-(\alpha - ab)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+	Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa < \frac{\alpha \beta}{b(1+\beta)}$.
+	We will show that for each $\gamma \in (0,\beta)$ there exist constants $C,\delta > 0$ such that
+\[
+	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
 	\leq C e^{-\delta t},
@@
 	In order to do this, 
-%we choice a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, 
 we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, 
-for each $\gamma \in [\gamma_0, \beta)$, we have $a < \frac{\alpha\gamma}{b(1+\gamma)}$.
+for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
 	Then, according to Lemma \ref{lem: control moment}, we have, for each $\gamma \in (0,\beta)$,
@@
 \[
-    \|e^{-(\alpha - ab)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    \leq C e^{-(\alpha-ab)t}e^{(\alpha-\kappa_g b)t}
-    \leq C  e^{-(\kappa_g - a)bt},
+    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+    \leq C e^{-(\alpha-\kappa b)t}e^{(\alpha-\kappa_g b)t}
+    \leq C  e^{-(\kappa_g - \kappa )bt},
     \quad t\geq 0;
@@
 \[
-     \|e^{-(\alpha - ab)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-     \leq C t e^{-(\alpha - a b)t}e^{\frac{\alpha}{1+\gamma}t}
-     = C t e^{-(\frac{\alpha \gamma}{1+\gamma} - ab)t},
+     \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+     \leq C t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
+     = C t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
      \quad t\geq 0;
@@
 \[
-    \|J_t\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C  e^{-(\alpha - a b)t}e^{\frac{\alpha}{1+\gamma}t}
-     = C  e^{-(\frac{\alpha \gamma}{1+\gamma} - ab)t},
+    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
+     = C  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
      \quad t\geq 0;
 \]
-{\bf Question: $J_t$ should be $e^{-(\alpha - ab)t} \langle g, X_t\rangle$, right?}
-\item
-	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above, and the fact that $\|J_t\|_{\mathbb{P}_{\mu};1+\gamma}
-	\leq \|J_t\|_{\mathbb{P}_{\mu};1+\gamma_0}$, there exist $C, \delta >0$ such that
-\[
-	\|J_t\|_{\mathbb{P}_{\mu};1+\gamma}
+\item
+	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above, and the fact that \[\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+	\leq \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C, \delta >0$ such that
+\[
+	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
 	\leq Ce^{-\delta t},
@@
 \]
-{\bf Question: the above $J_t$ should be replaced by $e^{-(\alpha - ab)t} \langle g, X_t\rangle$, right?}
 \end{enumerate}
 	Thus, the desired conclusion in this step is valid.
-	In particular, by taking $g = \tilde f$ and $a = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
+	In particular, by taking $g = \tilde f$ and $\kappa = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
 
@@
 	Define for $a \geq 0$ and $ t\geq 0$,
-\begin{align}
+\begin{equation}\begin{split}
 	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,
 	\quad g\in \mathcal P\cap C^2(\mathbb R^d),
-\end{align}
+\end{split}\end{equation}
 and
-\begin{align}
+\begin{equation}\begin{split}
     Y_t^{g,a}
@@
     \quad g\in \mathcal P\cap C^2(\mathbb R^d).
-\end{align}
+\end{split}\end{equation}
 	Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$.
@@
 	So according to Step 1, for an arbitrary fixed $\gamma\in (0,\beta)$, there exist $C, \delta>0$ such that for each $t\geq 0$,
-\begin{align}
+\begin{equation}\begin{split}
     \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
@@
     \leq C e^{-\delta t}.
-\end{align}
+\end{split}\end{equation}
 	Now, by the triangle inequality, for each $t\geq 0$,
@@
 
-	The proof is now complete.
+	The proof is now completed.
 
@@
 	\\&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+ \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big) +
-%\frac{\langle P_t^\alpha f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-\frac{\langle T_t^\alpha f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+\frac{\langle P^\alpha_t f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
 	\\&=:I'_1(t)+I'_2(t)+I'_3(t),
@@
  \]
-    Let $\theta\in \mathbb{R}$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in 
-  %  Corollary \ref{corollary31}, 
-  Proposition \ref{corollary31},
+    Let $\theta\in \mathbb R$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
+    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{corollary31},
     we get that there exist $C,\delta > 0$ such that
@@
 	Then we have
-\begin{align}
+\begin{equation}\begin{split}
 \label{ineq: control of I1tb}
@@
     \quad t\geq t_0,
-\end{align}
+\end{split}\end{equation}
     Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
@@
 Since $\alpha\beta<\kappa_f(1+\beta)b$,  we have
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: condition for supercritical}
@@
     =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
-\end{align}
+\end{split}\end{equation}
 	Using this, we have that there exist $C,C',
@@
 \]
-	According to Lemma \ref{lem: control of XT}, there exists
+	According to Proposition \ref{lem: control of XT}, there exists
 	$C>0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal E_t^c)\leq C e^{-\epsilon \beta t}$
@@
 	Therefore, there exists $C>0$ such that
-\begin{align}
+\begin{equation}\begin{split}
     |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{\mathcal{E}^{c}_t}]|
@@
     \quad t\geq t_0.
-\end{align}
+\end{split}\end{equation}
 	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that for all
@@
 	Step 3. We will show that $I'_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
-%	In fact, we can write
 In fact, we have
-\begin{align}
+\begin{equation}\begin{split}
 	&|I'_3(t)|
-	%\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-     \leq \frac{\langle |T^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+     \leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
 	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
@@
 	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
-\end{align}
+\end{split}\end{equation}
 	The proof is complete.
@@
 \subsection{Analytic facts}
-    In this subsection, we present some some analytic facts.
 \begin{lem}
@@
     We have
-\begin{align}
+\begin{equation}\begin{split}
     &\Big|e^{-z} - \sum_{k=0}^{m+1} \frac{(-z)^k}{k!}\Big|
@@
     = \frac{|z|^{m+2}}{(m+2)!} \wedge \frac{2|z|^{m+1}}{(m+1)!},
-\end{align}
+\end{split}\end{equation}
     which says that \eqref{eq: estimate of exponential remaining} is true for $n = m + 1$.
@@
 \label{lem: extension lemma for branching mechanism}
-    Suppose that  $\nu$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)} (u \wedge u^2) \nu(du)< \infty$.
+    Suppose that  $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)} (y \wedge y^2) \pi(dy)< \infty$.
     Then functions
 \begin{equation}
-    h (z) = \int_{(0,\infty)} (e^{-zu} - 1 + zu) \nu(du), \quad z \in \mathbb C_+
+    h (z) = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+
 \end{equation}
@@
 \label{eq: deriavetive of the Poission partb}
-    h'(z) = \int_{(0,\infty)}(1- e^{-uz})u \nu(du), \quad z \in \mathbb C_+
+    h'(z) = \int_{(0,\infty)}(1- e^{-zy})y \pi(dy), \quad z \in \mathbb C_+
 \end{equation}
@@
     From Lemma \ref{lem: estimate of exponential remaining}, for each $z_0 \in \mathbb C_+$, we have that there exists $C>0$ such that for $z \in \mathbb C_+$ close enough to $z_0$ and any
-    $u>0$,
-\begin{align}
-    &\Big| \frac{e^{-zu} - e^{-z_0u}+(z-z_0) u}{z-z_0} \Big|
-    = \frac{1}{|z-z_0|}\Big| \int_0^1 \big(-ue^{-(\theta z+(1-\theta)z_0)u}+u\big)(z-z_0)d\theta\Big|
-    \\ &\leq u\int_0^1 |1-e^{-(\theta z +(1-\theta)z_0)u}| d\theta
-    \leq (2u) \wedge\Big( u^2\int_0^1|\theta z+(1-\theta)z_0|d\theta\Big)
-    \leq C(u\wedge u^2).
-\end{align}
+    $y>0$,
+\begin{equation}\begin{split}
+    &\Big| \frac{e^{-zy} - e^{-z_0 y}+(z-z_0) y}{z-z_0} \Big|
+    = \frac{1}{|z-z_0|}\Big| \int_0^1 \big(-y e^{-(\theta z+(1-\theta)z_0)y}+y\big)(z-z_0)d\theta\Big|
+    \\ &\leq y\int_0^1 |1-e^{-(\theta z +(1-\theta)z_0)y}| d\theta
+    \leq (2y) \wedge\Big( y^2\int_0^1|\theta z+(1-\theta)z_0|d\theta\Big)
+    \leq C(y\wedge y^2).
+\end{split}\end{equation}
     Using this and the dominated convergence theorem, we have
-\begin{align}
-    &\frac{h(z)-h(z_0)}{z-z_0} = \int_{(0,\infty)} \frac{e^{-zu}+zu -(e^{-z_0u}+z_0u)}{z-z_0}  \nu(du)
-    \\&\xrightarrow[\mathbb C_+\ni z\to z_0]{} \int_{(0,\infty)}(1 - e^{-z_0u} )u\nu(du) = h'(z_0),
-\end{align}
+\begin{equation}\begin{split}
+    &\frac{h(z)-h(z_0)}{z-z_0} = \int_{(0,\infty)} \frac{e^{-zy}+zy -(e^{-z_0 y}+z_0 y)}{z-z_0}  \pi(dy)
+    \\&\xrightarrow[\mathbb C_+\ni z\to z_0]{} \int_{(0,\infty)}(1 - e^{-z_0 y} )y\pi(dy) = h'(z_0),
+\end{split}\end{equation}
     which says that $h$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
@@
 
-%    Recall that $\Gamma$ the Gamma function defined by
  Recall that the Gamma function  $\Gamma$ is defined by
@@
 	Using this recursively, one gets that
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: definition of Gamma function}
@@
     \quad -n< x< -n+1, n\in \mathbb N.
-\end{align}
+\end{split}\end{equation}
 
@@
     Notice that
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: upper bound for beta power of z}
@@
 	\quad z \in \mathbb C\setminus (-\infty, 0].
-\end{align}
+\end{split}\end{equation}
     Define a path $\gamma: [0,1] \to \mathbb C^0_+$ such that
@@
     Then, we have
-\begin{align}
+\begin{equation}\begin{split}
     |z_0^{1+\beta} - z_1^{1+\beta}|
@@
     \qedhere
-\end{align}
+\end{split}\end{equation}
 \end{proof}
@@
 	Such a function $f$ is called the distinguished logarithm of the function $\varphi$ and is denoted as $\operatorname{Log} \varphi(\theta)$.
-	In particular, let $\varphi$ be the characteristic function of an infinitely divisible random variable $Y$, then $h$ is called the L\'evy exponent of $Y$.
+	In particular, let $\varphi$ be the characteristic function of an infinitely divisible random variable $Y$, then $\operatorname{Log} \varphi(\theta)$ is called the L\'evy exponent of $Y$.
  	This distinguished logarithm should not be confused with the $\log$ function defined on $\mathbb C\setminus (-\infty, 0]$.
@@
 \begin{lem}
-    Let $t \geq 0$. Suppose that $\beta,\rho\in \mathcal B_b([0,t] \times E, \mathbb C)$ and $f\in \mathcal B_b(E, \mathbb C)$.
+    Let $t \geq 0$. Suppose that $\alpha,\rho\in \mathcal B_b([0,t] \times E, \mathbb C)$ and $f\in \mathcal B_b(E, \mathbb C)$.
     Then
 \begin{equation}
-    g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\beta+\rho)} f(\xi_t)],\quad r \in [0,t], x\in E,
+    g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\alpha+\rho)} f(\xi_t)],\quad r \in [0,t], x\in E,
 \end{equation}
@@
 \[
-    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\beta)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\beta)}\rho(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
+    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\alpha)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\alpha)}\rho(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
 \]
@@
     Notice that
-\begin{align}
-    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t)| ~ds \Big]
-    \leq  \int_r^t e^{(t-r)\|\beta\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|f\|_\infty ~ds
+\begin{equation}\begin{split}
+    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\alpha)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t)| ~ds \Big]
+    \leq  \int_r^t e^{(t-r)\|\alpha\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|f\|_\infty ~ds
     < \infty.
-\end{align}
+\end{split}\end{equation}
     Also notice that
@@
     Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
-\begin{align}
-    &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\beta)}~(\rho g)(s,\xi_s)~ds \Big]
-    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\beta)}\rho(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\beta+\rho)} f(\xi_t)]~ds \Big]
-    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\beta)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t) ~ds \Big]
-    = \Pi_{r,x} [ H_{(r,t)}^{(\beta)}f(\xi_t)(H_{(r,t)}^{(\rho)} - 1)]
-    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\beta)} f(\xi_t)].
-\end{align}
+\begin{equation}\begin{split}
+    &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\alpha)}~(\rho g)(s,\xi_s)~ds \Big]
+    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\alpha)}\rho(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\alpha+\rho)} f(\xi_t)]~ds \Big]
+    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\alpha)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t) ~ds \Big]
+    = \Pi_{r,x} [ H_{(r,t)}^{(\alpha)}f(\xi_t)(H_{(r,t)}^{(\rho)} - 1)]
+    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\alpha)} f(\xi_t)].
+\end{split}\end{equation}
     For the uniqueness, suppose that $\tilde g$ is another solution. Writting $h(r) = \sup_{x\in E}|g(r,x) - \tilde g(r,x)|$, we have
 \[
-    h(r) \leq e^{t\|\beta\|_\infty}\|\rho\|_\infty \int_r^t h(s)ds,
+    h(r) \leq e^{t\|\alpha\|_\infty}\|\rho\|_\infty \int_r^t h(s)ds,
     \quad r\le t.
@@
     In this subsection, we will give the definition of the superprocesses considered in this Appendix.
-Let $E$ be locally compact separable metric space. Denote by $\mathcal M_E^1$ the collection of all the finite measures on $E$ equipped with weak topology.
-    Recall that $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is said to be a $(\xi,\psi)$-superprocess if
+Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with weak topology.
+    Recall that $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
 \begin{itemize}
@@
     \psi(x,z)=
-    - \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
-\end{equation}
-    where $\beta \in \mathcal B_b(E)$, $\alpha \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
-\item
-    $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is an $\mathcal M^1_E$-valued Hunt process with transition probability determined by
-\begin{align}
+    - \alpha(x) z + \rho (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
+\end{equation}
+    where $\alpha \in \mathcal B_b(E)$, $\rho \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+\item
+    $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
+\begin{equation}\begin{split}
     \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
-    \quad t\geq 0, \mu \in \mathcal M_E^1, f\in \mathscr B^+_b(E),
-\end{align}
+    \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
+\end{split}\end{equation}
     where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
-\begin{align}\label{eq:FKPP_in_definition}
+\begin{equation}\begin{split}\label{eq:FKPP_in_definition}
     V_tf(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi(\xi_s,V_{t-s}f)ds \Big]
@@
     \quad t \geq 0, x \in E.
-\end{align}
+\end{split}\end{equation}
 \end{itemize}
     We refer our reader to \cite{Li2011Measure-valued} for more discussion about the definition and the existence of superprocesses.
-    To avoid triviality, we assume that $\psi(x,z)\neq -\beta(x)z$ for some $x \in E$ and $z \geq 0$.
+    To avoid triviality, we assume that $\psi(x,z)\neq -\alpha(x)z$ for some $x \in E$ and $z \geq 0$.
 
@@
 \begin{equation}
-    \psi'(x,z):= - \beta(x) + 2\alpha(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
+    \psi'(x,z):= - \alpha(x) + 2\rho(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
     \quad x\in E, z\in \mathbb C_+.
@@
     Then according to Lemma \ref{lem: extension lemma for branching mechanism}, for each $x \in E$, $z \mapsto \psi(x,z)$ is a holomorphic function on $\mathbb C_+^0$ with deriavetive $z \mapsto \psi'(x,z)$.
-    Define $\psi_0(x,z) := \psi(x,z)+ \beta(x)z $ and $\psi'_0(x,z) := \psi'(x,z) + \beta(x)$.
-
-    Denote by $\mathbb W$ the space of $\mathcal M_E^1$-valued c\`{a}dl\`{a}g paths with its conanical path denoted by $(W_t)_{t\geq 0}$.
+    Define $\psi_0(x,z) := \psi(x,z)+ \alpha(x)z $ and $\psi'_0(x,z) := \psi'(x,z) + \alpha(x)$.
+
+    Denote by $\mathbb W$ the space of $\mathcal M(E)$-valued c\`{a}dl\`{a}g paths with its conanical path denoted by $(W_t)_{t\geq 0}$.
     We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
@@
 \item
-    For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure defined on some probability space
+    For any $\mu \in \mathcal M(E)$, if $\mathcal N$ is a Poisson random measure defined on some probability space
     with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
@@
 \begin{equation}
-   % P_t^\beta f(x)
-   T_t^\beta f(x)
-    := \Pi_{x}[e^{\int_0^t \beta(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
+   % P_t^\alpha f(x)
+   P_t^\alpha f(x)
+    := \Pi_{x}[e^{\int_0^t \alpha(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
     \quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
 \end{equation}
-    It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M_E^1$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
+    It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M(E)$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
 \begin{equation}
@@
     =\mathbf P_{\mu}[X_t(f)]=
-    %\mu(P^\beta_t f).
-    \mu(T^\beta_t f).
+    %\mu(P^\alpha_t f).
+    \mu(P^\alpha_t f).
 \end{equation}
@@
     Define
-\begin{align}
+\begin{equation}\begin{split}
     L_1(\xi)
@@
     &:= \{f \in \mathcal B(E): |f|^2 \in L_1(\xi)\}.
-\end{align}
+\end{split}\end{equation}
     Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
@@
     \mathbb N_x[W_t(f)]
-    =\mathbf P_{\delta_x}[X_t(f)]=P^\beta_t f(x) \in \mathbb R,
+    =\mathbf P_{\delta_x}[X_t(f)]=P^\alpha_t f(x) \in \mathbb R,
     \quad f\in L_1(\xi), t > 0,x\in E.
@@
 \begin{lem}
-    There exists constants $C_1, C_2\geq 0$ such that for each $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
-\begin{align}
+    There exists constants $C\geq 0$ such that for each $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
+\begin{equation}\begin{split}
 \label{eq: upper bound of psi(v)}
     \big|\psi\big(x,-U_tf\big)\big|
-    \leq C_1 P^\beta_t |f|(x)+
-    %C_2 P^\beta_t |f| (x)^2.
-     C_2 (T^\beta_t |f| (x))^2.
-\end{align}
+    \leq C P^\alpha_t |f|(x)+
+    %C_2 P^\alpha_t |f| (x)^2.
+     C (P^\alpha_t |f| (x))^2.
+\end{split}\end{equation}
 \end{lem}
@@
     \leq \mathbb N_x[|i W_t(f)|]
- %   \leq (P^\beta_t |f|)(x).
-  \leq (T^\beta_t |f|)(x).
+ %   \leq (P^\alpha_t |f|)(x).
+  \leq (P^\alpha_t |f|)(x).
 \end{equation}
@@
     \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta| 
-    %\leq (P^\beta_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
-    \leq (T^\beta_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
-\end{equation}
-    Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability},
+    %\leq (P^\alpha_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
+    \leq (P^\alpha_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
+\end{equation}
+    Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent},
     $U_t(\theta f)(x)$ is differentiable in $\theta \in \mathbb R$ with
@@
     \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
-    %\leq ( P^\beta_t |f|)(x).
-    \leq ( T^\beta_t |f|)(x).
+    %\leq ( P^\alpha_t |f|)(x).
+    \leq ( P^\alpha_t |f|)(x).
 \end{equation}
@@
     &|\psi'(x, -U_tf)|
-    \\&= \Big| -\beta(x)- 2\alpha(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
-    \\&= \Big| - \beta(x)- 2\alpha(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi(x,dy) \Big|
-\\ &\leq \|\beta\|_\infty + 2\alpha(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
-\\ &\leq \|\beta\|_\infty + 2\|\alpha\|_\infty 
-% P^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\beta_t |f|(x)
-T^\beta_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~T^\beta_t |f|(x)
+    \\&= \Big| -\alpha(x)- 2\rho(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
+    \\&= \Big| - \alpha(x)- 2\rho(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi(x,dy) \Big|
+\\ &\leq \|\alpha\|_\infty + 2\rho(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
+\\ &\leq \|\alpha\|_\infty + 2\|\rho\|_\infty 
+% P^\alpha_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\alpha_t |f|(x)
+P^\alpha_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\alpha_t |f|(x)
   + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
-%\\ &=: C_1 + C_2(P^\beta_t |f|)(x),
-\\ &=: C_1 + C_2(T^\beta_t |f|)(x),
+%\\ &=: C_1 + C_2(P^\alpha_t |f|)(x),
+\\ &=: C_1 + C_2(P^\alpha_t |f|)(x),
 \end{split}
@@
     are well defined. 
-
     In fact, using Jensen's inequality and the Markov property, we have
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: domination of psi(v)}
     &\Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
-    \\&\leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^\beta|f|(\xi_s)+C_2 P_{t-s}^\beta|f|(\xi_s)^2\big)ds\Big]
-    \\ &\leq \int_0^t \big(C_1 e^{t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\beta\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
-    \\ &\leq \int_0^t (C_1 e^{t\|\beta\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\beta\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
-\end{align}
+    \\&\leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^\alpha|f|(\xi_s)+C_2 P_{t-s}^\alpha|f|(\xi_s)^2\big)ds\Big]
+    \\ &\leq \int_0^t \big(C_1 e^{t\|\alpha\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\alpha\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
+    \\ &\leq \int_0^t (C_1 e^{t\|\alpha\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\alpha\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
+\end{split}\end{equation}
 
@@
 \label{eq: complex FKPP-equation with FK-transform}
-    U_tf(x) -  \int_0^t P_{t-s}^{\beta} \psi_0\big(\cdot,-U_sf\big) (x)~ds
-   % \\= iP_t^\beta f(x).
-   \\= iT_t^\beta f(x).
+    U_tf(x) -  \int_0^t P_{t-s}^{\alpha} \psi_0\big(\cdot,-U_sf\big) (x)~ds
+   % \\= iP_t^\alpha f(x).
+   \\= iP_t^\alpha f(x).
 \end{equation}
@@
     Let $f\in \mathcal B_b(E,\mathbb R_+)$, $T >0$ and $x\in E$.
-    Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^\beta_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
+    Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^\alpha_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
 \begin{equation}
     d\mathbf P_{\delta_x}^{X_T(f)}
-   := \frac{X_T(f)}{P_T^\beta f(x)} d\mathbf P_{\delta_x};
+   := \frac{X_T(f)}{P_T^\alpha f(x)} d\mathbf P_{\delta_x};
     \quad d\mathbb N_x^{W_T(f)}
-    :=  \frac{W_T(f)}{P_T^\beta f(x)} d\mathbb N_x.
-\end{equation}
-({\bf Remark: I changed $P^\beta$ to $T^\beta$ above. But I find that is it not good to make this kind of changes is not good for above equation. So, I stop to make changes. Should we use $P^\beta$?})
+    :=  \frac{W_T(f)}{P_T^\alpha f(x)} d\mathbb N_x.
+\end{equation}
     Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{W_T(f)}$ if
@@
 \begin{equation}
-    d\Pi_x^{(f,T)} := \frac{f(\xi_T)e^{\int_0^T \beta(\xi_s)ds}}{P^\beta_T f(x)} d \Pi_x;
+    d\Pi_x^{(f,T)} := \frac{f(\xi_T)e^{\int_0^T \alpha(\xi_s)ds}}{P^\alpha_T f(x)} d \Pi_x;
 \end{equation}
@@
     Given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure $\{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
-\begin{align}
+\begin{equation}
 \label{eq: conditional intensity}
     \mathbf m(\xi,ds,dw)
-    := 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-\end{align}
-\item
-    $\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M^1_E$-valued process defined by
-\begin{align}
+    := 2 \rho(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
+\end{equation}
+\item
+    $\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M(E)$-valued process defined by
+\begin{equation}\begin{split}
     Y_t
@@
     \quad 0 \leq t\leq T.
-\end{align}
+\end{split}\end{equation}
 \end{itemize}
     According to the spine decomposition theorem in \cite{RenSongSun2017Spine}, we have that
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: Spine decomposition 1}
@@
     \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{W_T(f)} \}
-\end{align}
+\end{split}\end{equation}
     and
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: Spine decomposition 2}
@@
     \overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
-\end{align}
+\end{split}\end{equation}
 
@@
     From Lemma \ref{lem: estimate of exponential remaining}, we have $\mathbf Q^{(g,t)}_{x}$-almost surely
-\begin{align}
+\begin{equation}\begin{split}
 &\int_{[0,t]\times \mathbb W}|e^{i w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
     \leq \int_{[0,t]\times \mathbb W}\big(| w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
-    \\&\leq \int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[ X_{t-s}(|f|)] \pi(\xi_s,dy)
+    \\&\leq \int_0^t \Big(2\rho(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[ X_{t-s}(|f|)] \pi(\xi_s,dy)
     \\&\qquad\qquad+ 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
-     \\&\leq \int_0^t (P_{t-s}^\beta |f|)(\xi_s)\Big(2\alpha(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
-    \\&\leq \Big(2\|\alpha\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\beta\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+     \\&\leq \int_0^t (P_{t-s}^\alpha |f|)(\xi_s)\Big(2\rho(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+    \\&\leq \Big(2\|\rho\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\alpha\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
     < \infty.
-\end{align}
+\end{split}\end{equation}
     Using this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-almost surely,
-\begin{align}
+\begin{equation}\begin{split}
     &\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
-    \\&=\int_0^t \Big(2\alpha(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
-    \\&=\int_0^t \Big( 2\alpha(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
+    \\&=\int_0^t \Big(2\rho(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
+    \\&=\int_0^t \Big( 2\rho(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
     \\&= -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
-\end{align}
+\end{split}\end{equation}
     Therefore, according to \eqref{eq: Spine decomposition 2}, Campbell's formula and above, we have that
-\begin{align}
+\begin{equation}\begin{split}
 \label{eq: N to Pi}
@@
     \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
-    \\&= \frac{1}{T_t^\beta g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
-\end{align}
+    \\&= \frac{1}{P_t^\alpha g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
+\end{split}\end{equation}
     Let $\epsilon >0$.
-    Define $f^+ = (f \vee 0) + \epsilon$ and $f^- = (-f) \vee 0 + \epsilon$, then $f^\pm \in b\mathscr B^{++}_E$ and $f = f^+ - f^-$.
+    Define $f^+ = (f \vee 0) + \epsilon$ and $f^- = (-f) \vee 0 + \epsilon$, then $f^\pm \in \mathcal B_b(E)^{++}$ and $f = f^+ - f^-$.
     According to \eqref{eq: Spine decomposition 1}, we have that
@@
     Using \eqref{eq: N to Pi} and the above, we have
-\begin{align}
+\begin{equation}\begin{split}
     \frac{\mathbf P_{\delta_x}[X_t(f)e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
@@
     \\& = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
-\end{align}
+\end{split}\end{equation}
     Therefore, we have
-\begin{align}
+\begin{equation}\begin{split}
     \frac{\partial}{\partial \theta} {U_t(\theta f)(x)}
@@
     =  \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
-\end{align}
+\end{split}\end{equation}
     Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
 
-\begin{align}
+\begin{equation}\begin{split}
     &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)( x)
@@
     = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -U_{t-s}(\theta f)) ds} ].
-\end{align}
+\end{split}\end{equation}
 
@@
     and
-\begin{align}
-    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
-    &= \Pi_{r,x} [i e^{\int_r^t \beta(\xi_s)ds}f(\xi_t)].
-\end{align}
+\begin{equation}\begin{split}
+    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \alpha(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
+    &= \Pi_{r,x} [i e^{\int_r^t \alpha(\xi_s)ds}f(\xi_t)].
+\end{split}\end{equation}
     Integrating the two displays above with respect to $\theta$  on [0,1], using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get
@@
 \begin{equation}
-    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \beta(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
-    = i\Pi_{r,x} [e^{\int_r^t\beta(\xi_u)du}f(\xi_t)].
+    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \alpha(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
+    = i\Pi_{r,x} [e^{\int_r^t\alpha(\xi_u)du}f(\xi_t)].
 \end{equation}
@@
     |e^{i W_t(f_n)} - 1| \leq W_t(|f|);
-    \quad \mathbb N_x[W_t(|f|)] = (P_t^\beta |f|)(x) < \infty.
+    \quad \mathbb N_x[W_t(|f|)] = (P_t^\alpha |f|)(x) < \infty.
 \]
@@
      $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
-\begin{align}
+\begin{equation}\begin{split}
     \big|\psi(\xi_s,- U_{t-s}f_n)\big|
-    \leq C_1 P_{t-s}^\beta|f|(\xi_s)+C_2 P_{t-s}^\beta|f|(\xi_s)^2.
-\end{align}
+    \leq C_1 P_{t-s}^\alpha|f|(\xi_s)+C_2 P_{t-s}^\alpha|f|(\xi_s)^2.
+\end{split}\end{equation}
 \end{itemize}
@@
 
+\bibitem{LiuRenSong2009Llog}
+Liu, R.-L., Ren, Y.-X. and Song, R.:
+\emph{{$LlogL$} criterion for a class of superdiffusions.}  
+J. Appl. Probab. \textbf{46} (2009), no. 2, 479–496.
+
 \bibitem{MM}
@@
 \end{thebibliography}
-
 \end{document}

### 2019-01-31 supCLT.tex
supCLT.tex: 0107

@@
-%%%----Versions-----------------------------
-% supclt1213.tex 2018/12/13 by Yanxia
-% supclt1213.tex 2018/12/13 by Renming
-% supclt1209.tex 2018/12/07 by Zhenyao
-% supclt1207.tex 2018/12/07 by Renming
+%%----Versions-----------------------------
+% supCLT0107.tex 2018/01/07 by Jianjie
 % supCLT1204.tex 2018/12/04 by Zhenyao
@@
 	\allowdisplaybreaks
+%\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
+%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}
 
@@
     [CLT for Super-OU processes]
-    {\large CLT for Super-OU Processes with stable Branching}
+    {CLT for Super-OU Processes with stable Branching}
 \author
@@
 \thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
-\address
-   {Renming Song\\
-   Department of Mathematics\\
-   University of Illinois\\
-   Urbana, IL 61801, USA}
-   \email{rsong@illinois.edu}
-   \thanks{The research of Renming Song is supported in part by a grant from the Simons Foundation (\# 429343, Renming Song)}
 \address
@@
 \email{zhaojianjie@pku.edu.cn}
+%\begin{abstract}
+%\end{abstract}
+%\subjclass[2010]{60J80, 60F05}
+%\keywords{}
+%\date{}
+\maketitle
+%---Contents-----------------------
 \begin{abstract}
@@
     %where $a>0$ and $b>0$ are constants.
-    where $a>0$ and $b>0$.
+    where $\sigma>0$ and $b>0$.
     %Denote by $(P_t^\alpha)_{t\geq 0}$ the transition semigroup of $\xi$.
@@
     %:= - \alpha z + z^{1+\beta},
-    \psi(x,z)=
+    \psi(z)=
     - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy).
@@
     According to the Subsection A.1, the branching mechanism $\psi$ can be extended on $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
- \[\psi(x,z)=
+ \[\psi(z)=
     - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
@@
 \end{equation}
-
+{ \bf
 \begin{asp}
@@
 \[
-    \psi(z) = -\alpha z + \eta z^{1+\gamma} + \psi_1(z),\quad z\in \mathbb C_+,
+    \psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
 \]
@@
 \[
-    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}),\quad z\in \mathbb C_+.
+    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
 \]
 \end{asp}
-
 \begin{lem}
@@
 \begin{proof}
-    {\bf Need a proof.}
+    { Need a proof.}
 \end{proof}
-
+}
     According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
@@
     discrete spectrum $a(L)= \{-bk: k \in \mathbb Z_+\}$.
-    For each $k \in \mathbb Z_+$, denote by $A_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
-\begin{equation}
-    A_k
+    For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
+\begin{equation}
+    \mathcal{A}_k
     = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-\begin{equation}\label{Q_k}
-Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|P_t f|,
-\end{equation}
-and
-\begin{equation}\label{Q}
-Q f:= Q_{\kappa_f}f.
-\end{equation}
-    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
-
-\subsection{complex valued FKPP equations}
-    Let $X$ be the super OU-process introduced in Subsection \ref{ss:1.1}.    
-   Write $\psi_0(z) := \psi(z) + \alpha z$,
-   %Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}=(1+\beta)z^\beta$.
-   and $\psi'_0(z) = \psi'(z) + \alpha$ for each $z\in \mathbb C_+$.
-    For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
-    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$, the value of the L\'evy exponent of the infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
-    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
-\begin{equation}\begin{split}
-\label{eq:chareq2}
-    U_tf(x)-\int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
-    =i P^{\alpha}_t f(x),
-    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
-\end{split}\end{equation}
-
 \subsection{Main Result}
 We will use $\mathcal M_c(\mathbb R_d)$ to denote the space of all
-finite Borel measures of compact support on $\mathbb R^d$.
+finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of super-OU process.
 In this subsection, we will give the main results of this paper.
@@
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
-  For any $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
-   $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+  For all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, on the condition $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
+   $L^{1+\gamma}(\mathbb{P}_{\mu})$ (see Lemma \ref{lemma26}).
   Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  \begin{thm}\label{Theorem11}
-     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for
-any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$,
+     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for
+any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$,
      as $t\rightarrow \infty$,
@@
      Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence. 
-({\bf In the proof of this theorem, where do we need the condition that $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$ ?})
  \end{thm}
@@
     $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},
-for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$, as $t\rightarrow \infty$,
+for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
      $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
-({\bf This result should be refered as the SLLN, right?})
  \end{rem}
@@
 \subsubsection{Critical branching rate}
-    For $f\in \mathcal{P}$, define
+    For $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
 \[
@@
     \phi(x)
-    =\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).
-\]
-    Denote by $D$ the extinction event of the super OU-process.
+    =\sum_{|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x).
+\]
+
 \begin{thm}
@@
     \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
-    \xrightarrow{d} \eta_1,
+    \xrightarrow{d} \tilde{\zeta},
     \quad t\rightarrow \infty,
 \]
-    where $\eta_1$ is a $(1+\beta)$-stable random variable with
-\[
-    \mathbb{E} [e^{i\theta \eta_1}]
+    where $\tilde{\zeta}$ is a $(1+\beta)$-stable random variable with
+\[
+    \mathbb{E} [e^{i\theta \tilde{\zeta}}]
     =\exp(\tilde{m}[\theta f]),
@@
 
-For $f\in \mathcal{P}$, define
+For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_f b(1+\beta)$, define
 
@@
      m[f]
-    =\alpha e^{\alpha}\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds, \label{msmallcase}
-\]
+    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds, \label{msmallcase}
+\]
+According to \cite[Lemma 5.1]{MM}, $m[f]$ is well-defined.
 \begin{thm}
@@
     If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$,
-   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under
+   then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under
     $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
-    where $\eta_2$ is a $(1+\beta)$-stable random variable with
-    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
+    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \zeta, \quad t\rightarrow \infty,$$
+    where $\zeta$ is a $(1+\beta)$-stable random variable with
+    $$\mathbb{E} [e^{i\theta \zeta}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
 \end{thm}
 
+\subsubsection{further results in the large branching rate case}
+Define
+\begin{align}
+   \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}, 
+\end{align}
+and
+\begin{align}
+    \mathcal{C}_l:=\Big\{f(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
+\end{align}
+Fixed $f\in \mathcal{C}_l$, $f$ can be expressed by
+\begin{align}\label{discompose}
+    f(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x),\quad x\in \mathbb{R}^d,
+\end{align}
+where $a_p=\langle f, \phi_p\rangle_{\varphi}$. Let
+\begin{align}
+    I_tf(x):=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d. 
+\end{align}
+It is easy to get that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$. Denote
+\begin{align}
+    \bar{m}[f]:=\int_{0}^{\infty} e^{\alpha s}\langle \eta(iI_sf)^{1+\beta},\varphi\rangle ds.
+\end{align}
+According to Lemma \ref{lem: control of mn}, $\bar{m}[f]$ is well-defined.
+\begin{thm}\label{theorem 1.6}
+For each $f\in\mathcal{C}_l$ expressed by \eqref{discompose} and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$ it holds that,
+\begin{align}\label{thm: large rate}
+    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}a_pe^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow{d}\bar{\zeta},\quad t\rightarrow\infty,
+\end{align}
+where $\bar{\zeta}$ is an $(1+\beta)$-stable random variable with characteristic function
+\begin{align}
+    \mathbb{E}[e^{i\theta\bar{\zeta}}]=\exp[\bar{m}[\theta g]],\quad \theta\in \mathbb{R}.
+\end{align}
+\end{thm}
+
 \section{Preliminaries}
-
+\subsection{~~operators}
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
@@
     We say a family of operators $(A_s)_{s\in \Lambda}$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by operator $R$ on $\mathcal D$.
-    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in E$.
+    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
     For any $a \in \mathbb R$, suppose that $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
@@
 
-    (2). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by  an$h$-controller $R_A$ on $\mathcal D$. 
-    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controalled by $g$-controller $R_B$ on $\mathcal D_0$. 
+    (2). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by  an $h$-controller $R_A$ on $\mathcal D$.
+    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by $g$-controller $R_B$ on $\mathcal D_0$.
     We verify the following:
@@
     (3). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R_A$ on $\mathcal D$.
-    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controalled by a $g$-controller $R_B$ on $\mathcal D$.
+    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
 
@@
 
-\subsection{Control the Operators for super-OU process}
-    Denote by $\psi_0(z) = \psi(z) + \alpha z$ for each $z\in \mathbb C_+$, and define operators on $\mathcal B(\mathbb R^d, \mathbb C_+)$ by
+\subsection{Control the operators for super-OU process.} Let $X$ be the super-OU process introduced in subsection 1.1.
+Write $\psi_0(z)=\psi(z)+\alpha z$, for each $z\in \mathbb{C}_+$, and define operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$ by
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-    Define
+For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$, the value of the L\'evy exponent of the infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
+    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
+\begin{equation}\begin{split}
+\label{eq:chareq2}
+    U_tf(x)-\int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
+    =i P^{\alpha}_t f(x),
+    \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
+\end{split}\end{equation}
+If let 
 \begin{equation}\begin{split}
@@
     \\ K_t f
-    &:= (Z'_t - Z_t+ Z''_t)f.
+    &:= (Z'_t - Z_t+ Z''_t)f,
 \end{split}\end{equation}
@@
     = Z_t+ (Z'_t - Z_t) + Z''_t
-    = Z_t+K_t.
+    = Z_t+K_t, \quad t\geq 0.
 \]
@@
 \end{proof}
-
+\section{Tail probability}
+In this section, we will introduce a small value probability result of supercritical continuous-state branching process with general branching mechanism and control $(1+\gamma)$-moments for the super-OU process.
+
+\subsection{Small value probability}
+    In this subsection, we digress briefly from super-OU process and consider a supercritical continuous-state branching process (CSBP) $(Y_t)$.
+Our goal is to determing how fast the probability $P_x(0<e^{-\alpha t}Y_t \leq k_t)$ convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
+    Let branching mechanism corresponding to the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ be denoted as
+\[
+    \psi(z)
+    := -\alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z\geq 0,
+\]
+    where $\alpha > 0$, $\rho \geq 0$ and $\pi$ is a measure on $(0,\infty)$ satisfying $\int_{(0,\infty)} (y \wedge y^2) \pi(dy) < \infty$.
+    Suppose that the Grey's condition is satisfied, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+    Also suppose that the $L \log L$ critierion is satisfied, i.e.
+\[
+    \int_1^\infty y \log y~\pi(dr)< \infty.
+\]
+    Write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
+\begin{prop}
+\label{lem: control of XT}
+    Suppose that $t\mapsto k_t$ is a strictly positive map on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
+    Then, for each $x\geq 0$, there are constants $C,\delta>0$ such that
+\[
+    \mathbf P_x(0<W_t\leq k_t) \leq C(k_t^\delta + e^{-\delta t}), \quad t\geq 0.
+\]
+\end{prop}
+\begin{proof}
+    \emph{Step 1}. We recall some known facts about the CSBP $(Y_t)$.
+    For each $\lambda \geq 0$, denote by $t\mapsto v_t(\lambda)$ the unique positive solution of
+\[
+    v_t(\lambda)
+    = \lambda - \int_0^t \psi(v_s(\lambda))ds,\quad t\geq 0.
+\]
+    Then according to the definition of CSBP, we have
+\[
+    \mathbf P_x[e^{-\lambda Y_t}] = e^{-xv_t(\lambda)}, \quad t\geq 0, \lambda \geq 0, x\geq 0.
+\]
+    Taking $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
+\begin{equation}
+\label{eq: svp1}
+    \mathbf P_x(Y_t = 0)=e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
+\end{equation}
+    It is known, see \cite[Theorem 3.5-3.8]{Li2011Measure-valued} for example, that under the Grey's condition, the following statements are true:
+\begin{itemize}
+\item
+    $0\leq \bar v_t < \infty$ for all $t>0$.
+\item
+    $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
+\end{itemize}
+    Taking $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
+\[
+    \mathbf P_x(\exists t \geq 0, Y_t = 0)
+    = e^{-x\bar v}, \quad x\geq 0.
+\]
+
+    Note that $\psi$ has derivative
+\[
+    \psi'(z)
+    = -\alpha + 2\rho z + \int_{(0,\infty)}(1-e^{-zy})y\pi(dy),\quad z\geq 0,
+\]
+    which is increasing in $z$.
+    This says that $\psi$ is a convex function.
+    Also notice that $\psi'(0+)=-\alpha <0$ and that there exists $z>0$ such that $\psi(z)>0$.
+    So, we can verify that the following are true:
+\begin{itemize}
+\item
+    $\bar v > 0$ ,
+\item
+    $\psi(z) < 0$ on $z\in (0,\bar v)$,
+\item
+    $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
+\end{itemize}
+    It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that
+\begin{itemize}
+\item
+    if $\lambda \in (0,\bar v)$ then $0<\lambda \leq v_t(\lambda)<\bar v $, and that
+\begin{align}
+\label{CSBP: int}
+    \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0. 
+\end{align}
+\item
+    if $\lambda \in (\bar v, \infty)$ then $\bar v < v_t(\lambda)\leq \lambda< \infty $, and that
+\[
+  \int_{v_t(\lambda)}^\lambda\frac{dz}{\psi(z)} = t, \quad t\geq 0.
+\]
+\end{itemize}
+    By monotonicity, we have that
+\begin{equation}
+\label{eq:svp2}
+    \int_{\bar v_t}^\infty \frac{dz}{\psi(z)} = t, \quad t\geq 0.
+\end{equation}
+
+    Step 2. We will show that, for each $x \geq 0$ there exists a constant $C>0$ such that
+\[
+    \mathbf P_{x}(0< W_t\leq k_t)
+    \leq C\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
+    \quad t\geq 0.
+\]
+In fact, for each $x\geq 0$ and $t\geq 0$ we have
+\begin{equation}\begin{split}
+    &\mathbf P_{x}(0<W_t \leq k_t)
+    = \mathbf P_{x}( e^{-k_t^{-1}W_t}\geq e^{-1},W_t > 0)
+    \\&\leq e \mathbf P_{x}[e^{-k_t^{-1} W_t};W_t > 0]
+    =  e\big(\mathbf P_x[e^{-k_t^{-1} W_t}]-\mathbf P_x(W_t = 0)\big)
+    \\ &= e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
+    \\&\leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big)
+\end{split}\end{equation}
+    as required in this step.
+
+    Step 3. We will show that there exists constants $c, \delta, t_0 > 0$ such that
+\[
+    |\bar v_t-\bar v|
+    \leq ce^{-\delta t},
+    \quad t\geq t_0.
+\]
+    In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$, and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
+    According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
+\[
+    t_0
+    := \int^\infty_{z_0} \frac{dz}{\psi(z)} < \infty.
+\]
+    For each $t > t_0$, according to \eqref{eq:svp2}, we have
+\begin{equation}\begin{split}
+    &t-t_0 = \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)}
+    =\int_{\bar v_t}^{z_0} \frac{dz}{\psi(z)}
+    \\ &\leq \int_{\bar v_t}^{z_0} \frac{dz}{(z-\bar v)\tau}
+    = \frac{1}{\tau} \big(\log (z_0-\bar v) - \log(\bar v_t-\bar v)\big).
+\end{split}\end{equation}
+    Rearrange this, we have
+\[
+    \bar v_t - \bar v \leq (z_0 - \bar v)e^{-\tau(t-t_0)},
+    \quad t\geq t_0.
+\]
+    This implies the desired result in this step.
+
+    Step 4: We will show that there exists constant $C, \delta,t_0>0$ such that
+\[
+    |\bar v - v_t(k_t^{-1} e^{-\alpha t})|\leq Ck_t^\delta, \quad t\geq t_0.
+\]
+    Define
+\[
+    \rho_t := 1+ \frac{\log k_t}{t\alpha}, \quad t\geq 0.
+\]
+    According to the fact that
+\[
+    k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}, \quad t\geq 0,
+\]
+    and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
+    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$ where the martingale limit $W_\infty$ is a non-degenerate random variable.
+This implies that
+\[
+    v_t(e^{-\alpha t}) = -\log \mathbf P_1[e^{-W_t}]\xrightarrow[t\to \infty]{} - \log \mathbf P_{1}[e^{-W_\infty}] =: z^* \in (0,\infty).
+\]
+    The $L \log L$ critierioin also garuntees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.ly in $\mathbf P_1$.
+This and the non-degeneracy of $W_\infty$ implies that
+\[
+    z^*=-\log \mathbf P_1[e^{-W_\infty}] < -\log \mathbf P_1(W_\infty = 0) = \bar v.
+\]
+
+    Fix an arbitrary $\epsilon \in (0,\tau)$.
+    According to the fact that $\tau=\psi'(\bar v)>0$ , there exists $z_0 \in (0,\bar v)$ such that for all $z\in (z_0, \bar v)$, we have $-\psi(z)\geq (\bar v - z)(\tau- \epsilon)$.
+    Fix this $z_0$. For $t$ large enough, according to \eqref{CSBP: int} and the fact that $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$, we can verify the following:
+\begin{equation}\begin{split}
+    &t =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
+    \\&= \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)}
+     \\&= \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
+\end{split}\end{equation}
+    where we used the fact that
+\[
+    \int_{v_{\rho_t t}(e^{-\alpha \rho_tt})}^{z_0} \frac{dz}{-\psi(z)} \xrightarrow[t\to \infty] {}\int_{z^*}^{z_0} \frac{dz}{-\psi(z)}.
+\]
+    Now we have, for $t$ large enough,
+\begin{equation}\begin{split}
+    &t\leq  \rho_t t + O(1)+ \int_{z_0}^{v_t(k_t^{-1}e^{-\alpha t})} \frac{dz}{(\bar v-z)(\tau - \epsilon)}
+    \\&=  \rho_t t +O(1)- \frac{1}{\tau-\epsilon}\Big( \log \big(\bar v-v_t(e^{-\alpha \rho_t t})\big) - \log(\bar v-z_0)\Big).
+\end{split}\end{equation}
+    Rearrange this, we have, for $t$ large enough,
+\[
+    e^{-t(\tau - \epsilon)} \geq e^{-\rho_t t(\tau - \epsilon)+O(1)}(\bar v - v_t(e^{-\alpha \rho_t t})).
+\]
+    Therefore, there exists constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$,
+\[
+    \bar v - v_t(k_t^{-1} e^{-\alpha t}) \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
+    \leq Ck_t^{\frac{\tau - \epsilon}{\alpha}}.
+\]
+    This implies the required result in this step.
+
+    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exists constant $C, \delta, t_0 > 0$ such that
+\[
+    \mathbf P_{x}(0< W_t\leq k_t) \leq C(k_t^{\delta}+e^{-\delta t}),\quad t\geq t_0.
+\]
+Note that the left side is always bounded by $1$, so if we can take $t_0 =0$ in the above statement.
+\end{proof}
 \subsection{$(1+\gamma)$-moments for the super-OU process}
@@
 \end{proof}
-
+    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
+\begin{equation}\label{Q_k}
+Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|P_t f|,
+\end{equation}
+and
+\begin{equation}\label{Q}
+Q f:= Q_{\kappa_f}f.
+\end{equation}
+    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
 \begin{lem}\label{lem: temp}
@@
 \end{proof}
-
-\subsection{Martingales}
-    In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family martingales for $\gamma\in (0, \beta)$.
+\section{Proof of main results}
+In this section, we will prove the main results of this paper.
+Recall that $\mathcal{M}_c(\mathbb{R}^d)$ is the space of all finite Borel measures of compact support on $\mathbb{R}^d$.
+Denote  $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in the following section.
+\subsection{The large rate case.} To prove Theorem \ref{Theorem11}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family martingales for $\gamma\in (0, \beta)$.
 Recall that $L$ is the infinitesimal generator of the OU-process.
-Let $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ be such that $Lf \in \mathcal{P}$, and let $a\in \mathbb R$, we define that
+Let $f\in \mathcal{P}\cap C^2(\mathbb R^d)$, and let $a\in \mathbb R$, we define that
 \begin{equation}\begin{split}
@@
 \label{lemma25}
-    Let $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ be such that $Lf \in \mathcal{P}$ and let $a\in \mathbb R$.
+    For each $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and $a\in \mathbb R$.
 Then, for any $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
@@
 \begin{equation}\begin{split}\label{Theorem55}
-    P_t^{ab}f(x)= f(x)+\int_0^t T_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d.
+    P_t^{ab}f(x)= f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d.
 \end{split}\end{equation}
@@
     \\&=e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
-    \\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du 
-    \\&\quad -\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
+    \\&=e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du
+    \\&\quad -\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
 \end{split}\end{equation}
@@
 \begin{equation}\begin{split}
-    &\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle T_{u-s}^{ab}\bar{f},X_s\rangle~du\\
-    &=e^{-(\alpha-ab)s}\Big\langle\int_0^{t-s}T_{u}^{ab}\bar{f}~du,X_s\Big\rangle=e^{-(\alpha-ab)s}\left(\langle T_{t-s}^{ab}f,X_s\rangle-\langle
+    &\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle P_{u-s}^{ab}\bar{f},X_s\rangle~du\\
+    &=e^{-(\alpha-ab)s}\Big\langle\int_0^{t-s}P_{u}^{ab}\bar{f}~du,X_s\Big\rangle=e^{-(\alpha-ab)s}\left(\langle P_{t-s}^{ab}f,X_s\rangle-\langle
     f,X_s\rangle\right)\\
-    &=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-e^{-(\alpha-ab)s}\langle
+    &=e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-e^{-(\alpha-ab)s}\langle
     f,X_s\rangle.
@@
     For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
-    Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $\gamma\in (0, \beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
+Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
 \[
@@
 
-\begin{lem}\label{lem: control of Wt}
- For all $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for all $0\leq s<t$,
-\[
-    \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C e^{-\frac{\alpha \gamma}{1+\gamma}s}.
+\begin{lem}\label{lem: control of wt} For all $\gamma\in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for all $0\leq s<t$,
+\[
+    \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C e^{-\frac{ 1}{1+\gamma}(\alpha\gamma-|p|b(1+\gamma))s}.
 \]
@@
 \begin{proof}
-     Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-     Using Lemma \ref{lem: control of mgtrs} with $g=1$ and $k=0$, there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
-    \begin{equation}\begin{split}
-        \mathbb{P}_{\mu}\big[\big|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\|\big|^{1+\gamma}\big]
-        \leq C_0e^{\alpha t+(t-s)\alpha\gamma}.
-    \end{split}\end{equation}
-    Dividing both sides by $e^{\alpha t(1+\gamma)}$, we get
-    \begin{equation}\begin{split}
-        \mathbb{P}_{\mu}\big[|H_s-H_r|^{1+\gamma}\big]\leq  C_0 e^{-\alpha \gamma s}.
-    \end{split}\end{equation}
+     Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
+% According to Lemma \ref{lem: control of mgtrs},
+Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,
+ there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
+    \begin{align}
+        \mathbb{P}_{\mu}\big[\big|e^{(\alpha-|p|b)(t-s)}\langle\phi_p, X_s\rangle-e^{(\alpha-|p|b)(t-r)}\langle\phi_p, X_r\rangle\big|^{1+\gamma}\big]
+        \leq C_0e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b\gamma}.
+    \end{align}
+    Dividing both sides by $e^{(\alpha-|p|b) t(1+\gamma)}$, we get
+    \begin{align}
+        \mathbb{P}_{\mu}\big[|H^p_s-H^p_r|^{1+\gamma}\big]\leq  C_0 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
+    \end{align}
     Thus there is a $C>0$ for any $0\leq s<t$,
-\begin{equation}\begin{split}
-	& \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}
-	\\&\leq \|H_{\lfloor s \rfloor+1}-H_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H_{k+1}-H_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H_t-H_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
-	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
-	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}.
+\begin{align}
+	& \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
+	\\&\leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
+	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
+	\leq Ce^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
     \qedhere
-\end{split}\end{equation}	
+\end{align}	
 \end{proof}
 
-\begin{comment}
-From now on, we write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
-\begin{lem}
-\label{lem: control of XT}
-	For any $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for all $f:[0,\infty)\to [1,\infty)$ and $t\geq 0$, we have
-\begin{equation}\begin{split}
-    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)\leq C \Big(\frac{f(t)}{e^{\alpha t}}\Big)^{\beta}.
-\end{split}\end{equation}
-\end{lem}
-
-\begin{proof}
-    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
-\begin{equation}\begin{split}\label{CSBP}
-    \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
-    =e^{-\|\mu\|v_t(\lambda)},
-    \quad \lambda \geq 0, t\geq 0,
-\end{split}\end{equation}
-    where
-\[
-    v_t(\lambda)=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
-\]
-    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\bar v\|\mu\|}$, where $\bar v=\alpha^{1/\beta}$ is the larger root of $\psi(z)=0$.
-    By \eqref{CSBP} and the Markov property, we have for all $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
-    $t\geq 0$,
-
-\begin{equation}\begin{split}
-    \label{laplaceexpress}
-    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]
-    &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
-    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\bar v\|X_t\|})] }{\mathbb P_\mu(D^c)}
-    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\bar v)}}{1-e^{-\|\mu\|\bar v}}
-    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\bar v}}\left|v_t(\lambda)-v_t(\lambda+\bar v)\right|.
-\end{split}\end{equation}
-
-By Chebyshev's inequality and \eqref{laplaceexpress}, we get
+\subsubsection{Proof of Theorem \ref{Theorem11}}.
+	Fix  $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$.
+	Fix $\mu \in \mathcal M_c(\mathbb R^d)$.
+	Write
+\begin{equation}\begin{split}
+    f
+    =\sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
+    =:
+    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f}.
+\end{split}\end{equation}
+	Then
 \begin{align*}
-    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]\\
-    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\bar v}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\bar v)\right|.
+    &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
+    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle,
+    \quad t\geq 0.
 \end{align*}
-	Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t}$, then $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
-Note that
+	According to Lemma \ref{lemma26},
+	we have
+\begin{equation}\begin{split}
+\label{as convergence}
+     \sum_{p\in \mathbb{Z}_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p
+     \xrightarrow[t\to \infty]{} \sum_{p\in \mathbb{Z}_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
+\end{split}\end{equation}
+$\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
+	Therefore, it is suffice to show that
+\begin{equation}\begin{split}
+    J_t
+    :=e^{-(\alpha-\kappa_fb)t}\langle \tilde{f},X_t\rangle,
+    \quad t\geq 0,
+\end{split}\end{equation}
+	converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$ satisfying $D^2f\in \mathcal{P}$.
+
+	Step 1. Let $g\in \mathcal P$.
+	Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa < \frac{\alpha \beta}{b(1+\beta)}$.
+	We will show that for each $\gamma \in (0,\beta)$ there exist constants $C,\delta > 0$ such that
+\[
+	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+	\leq C e^{-\delta t},
+	\quad t\geq 0.
+\]
+	In order to do this,
+we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that,
+for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
+	Then, according to Lemma \ref{lem: control moment}, we have, for each $\gamma \in (0,\beta)$,
+\begin{enumerate}
+\item
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
+\[
+    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+    \leq C e^{-(\alpha-\kappa b)t}e^{(\alpha-\kappa_g b)t}
+    \leq C  e^{-(\kappa_g - \kappa )bt},
+    \quad t\geq 0;
+\]
+\item
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C>0$ such that
+\[
+     \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+     \leq C t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
+     = C t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
+     \quad t\geq 0;
+\]
+\item
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
+\[
+    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
+     = C  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
+     \quad t\geq 0;
+\]
+\item
+	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above, and the fact that \[\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+	\leq \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C, \delta >0$ such that
+\[
+	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+	\leq Ce^{-\delta t},
+	\quad t\geq 0.
+\]
+\end{enumerate}
+	Thus, the desired conclusion in this step is valid.
+	In particular, by taking $g = \tilde f$ and $\kappa = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
+
+	Step 2.
+	Further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$, we will show that $J_t$ converges to $0$ almost surely.
+	For $a \geq 0$ and $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, define
+\begin{equation}\begin{split}
+	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,
+\end{split}\end{equation}
+and
+\begin{equation}\begin{split}
+    Y_t^{g,a}
+    :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
+\end{split}\end{equation}
+	Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$.
+	According to \eqref{defmartingale}, we have
 \begin{align*}
-    \left|v_t(\lambda)-v_t(\lambda+\bar v)\right|&\leq\frac {\alpha^{1/\beta}}{\beta} \left|w_t(\lambda)-w_t(\lambda+\bar v)\right| \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}\\
-    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\bar v)^{\beta}}\right|e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}\\
-    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}.
+    J_t
+    =e^{-(a_0-\kappa_f)bt} (M_t^{\tilde{f}, a_0}+L_t^{\tilde{f}, a_0}),
+    \quad t\geq 0.
 \end{align*}
-Therefore, for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for all non-negative function $f$ on $[0,\infty)$, $\lambda \geq 0$ and $t\geq 0$, we have
-\begin{equation}\begin{split}
-\label{eq: inequality before take lambda}
-    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)
-    \leq C_0e^{\lambda f(t)}\frac{1}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}.
-\end{split}\end{equation}
-
-Notice that
+	So we only need to show that
 \begin{align*}
-    w_t(s)^{-1/\beta-1}&\leq \frac{1}{(\alpha s^{-\beta}e^{-\alpha \beta t})^{1/
-    \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
-    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.
+    e^{-(a_0-\kappa_f)b t}M_t^{\tilde{f},a_0}
+    \xrightarrow[t\to \infty]{} 0,
+    \quad e^{-(a_0-\kappa_f)b t}L_t^{\tilde{f},a_0}
+    \xrightarrow[t\to \infty]{} 0
+    \quad \mathbb{P}_{\mu}\text{-a.s.}
 \end{align*}
-Therefore, for each $\lambda \in [0,1]$,
+	Notice that $\kappa_{(L+a_0 b)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
+	So according to Step 1, for an arbitrary fixed $\gamma\in (0,\beta)$, there exist $C, \delta>0$ such that for each $t\geq 0$,
+\begin{equation}\begin{split}
+    \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C e^{-\delta t},
+    \quad \|e^{-(\alpha-a_0 b)t}\langle L\tilde{f}+a_0 b\tilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C e^{-\delta t}.
+\end{split}\end{equation}
+	Now, by the triangle inequality, for each $t\geq 0$,
 \begin{align*}
-    \sup_{s\in [\lambda,\lambda+\bar v]}w_t(s)^{-1/\beta-1}
-    &\leq\sup_{s\in [\lambda,\lambda+\bar v]}\frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
-    &\leq \frac{(1+\bar v)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}} =: C_1.
+    &\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq\|Y_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\tilde{f}+a_0 b\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
 \end{align*}
-Finally, plugging $\lambda = f(t)^{-1} \in (0,1]$
-back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.
-\end{proof}
-\end{comment}
-
-\subsection{Small value probability}
-    In this subsection, we digress briefly from super-OU process and consider a supercritical continuous-state branching process (CSBP) $(Y_t)$.
-Our goal is to determing how fast the probability $P_x(0<e^{-\alpha t}Y_t \leq k_t)$ convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
-    Let branching mechanism corresponding to the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ be denoted as
-\[
-    \psi(z)
-    := -\alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z\geq 0,
-\]
-    where $\alpha > 0$, $\rho \geq 0$ and $\pi$ is a measure on $(0,\infty)$ satisfying $\int_{(0,\infty)} (y \wedge y^2) \pi(dy) < \infty$.
-    Suppose that the Grey's condition is satisfied, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$. 
-    Also suppose that the $L \log L$ critierion is satisfied, i.e. 
-\[
-    \int_1^\infty y \log y~\pi(dr)< \infty.
-\]
-    Write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
-\begin{prop}
-\label{lem: control of XT}
-    Suppose that $t\mapsto k_t$ is a strictly positive map on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$. 
-    Then, for each $x\geq 0$, there are constants $C,\delta>0$ such that
-\[
-    \mathbf P_x(0<W_t\leq k_t) \leq C(k_t^\delta + e^{-\delta t}), \quad t\geq 0.
-\]
-\end{prop}
-\begin{proof}
-    \emph{Step 1}. We recall some known facts about the CSBP $(Y_t)$. 
-    For each $\lambda \geq 0$, denote by $t\mapsto v_t(\lambda)$ the unique positive solution of 
-\[
-    v_t(\lambda) 
-    = \lambda - \int_0^t \psi(v_s(\lambda))ds,\quad t\geq 0.
-\]
-    Then according to the definition of CSBP, we have
-\[
-    \mathbf P_x[e^{-\lambda Y_t}] = e^{-xv_t(\lambda)}, \quad t\geq 0, \lambda \geq 0, x\geq 0.
-\]
-    Taking $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
-\begin{equation}
-\label{eq: svp1}
-    \mathbf P_x(Y_t = 0)=e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
-\end{equation}
-    It is known, see \cite[Theorem 3.5-3.8]{Li2011Measure-valued} for example, that under the Grey's condition, the following statements are true:
-\begin{itemize}
-\item
-    $0\leq \bar v_t < \infty$ for all $t>0$.
-\item 
-    $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
-\end{itemize}
-    Taking $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
-\[
-    \mathbf P_x(\exists t \geq 0, Y_t = 0) 
-    = e^{-x\bar v}, \quad x\geq 0.
-\]
-
-    Note that $\psi$ has derivative 
-\[
-    \psi'(z) 
-    = -\alpha + 2\beta z + \int_{(0,\infty)}(1-e^{-zy})y\pi(dy),\quad z\geq 0,
-\]
-    which is increasing in $z$. 
-    This says that $\psi$ is a convex function. 
-    Also notice that $\psi'(0+)=-\alpha <0$ and that there exists $z>0$ such that $\psi(z)>0$. 
-    So, we can verify that the following are true: 
-\begin{itemize}
-\item
-    $\bar v > 0$ , 
-\item
-    $\psi(z) < 0$ on $z\in (0,\bar v)$, 
-\item
-    $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
-\end{itemize}
-    It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that
-\begin{itemize}
-\item
-    if $\lambda \in (0,\bar v)$ then $0<\lambda \leq v_t(\lambda)<\bar v $, and that
-\[
-    \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0.
-\]
-\item
-    if $\lambda \in (\bar v, \infty)$ then $\bar v < v_t(\lambda)\leq \lambda< \infty $, and that
-\[
-  \int_{v_t(\lambda)}^\lambda\frac{dz}{\psi(z)} = t, \quad t\geq 0.
-\]
-\end{itemize}
-    By monotonicity, we have that
-\begin{equation}
-\label{eq:svp2}
-    \int_{\bar v_t}^\infty \frac{dz}{\psi(z)} = t, \quad t\geq 0.
-\end{equation}
-
-    Step 2. We will show that, for each $x \geq 0$ there exists a constant $C>0$ such that
-\[
-    \mathbf P_{x}(0< W_t\leq k_t)
-    \leq C\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
-    \quad t\geq 0.
-\]
-In fact, for each $x\geq 0$ and $t\geq 0$ we have
-\begin{equation}\begin{split}
-    &\mathbf P_{x}(0<W_t \leq k_t)
-    = \mathbf P_{x}( e^{-k_t^{-1}W_t}\geq e^{-1},W_t > 0)
-    \\&\leq e \mathbf P_{x}[e^{-k_t^{-1} W_t};W_t > 0]
-    =  e\big(\mathbf P_x[e^{-k_t^{-1} W_t}]-\mathbf P_x(W_t = 0)\big)
-    \\ &= e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
-    \\&\leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big)
-\end{split}\end{equation}
-    as required in this step.
-
-    Step 3. We will show that there exists constants $c, \delta, t_0 > 0$ such that 
-\[
-    |\bar v_t-\bar v| 
-    \leq ce^{-\delta t}, 
-    \quad t\geq t_0.
-\]
-    In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$, and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
-    According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
-\[
-    t_0 
-    := \int^\infty_{z_0} \frac{dz}{\psi(z)} < \infty.
-\]
-    For each $t > t_0$, according to the \eqref{eq:svp2}, we have
-\begin{equation}\begin{split}
-    &t-t_0 = \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)} 
-    =\int_{\bar v_t}^{z_0} \frac{dz}{\psi(z)}
-    \\ &\leq \int_{\bar v_t}^{z_0} \frac{dz}{(z-\bar v)\tau} 
-    = \frac{1}{\tau} \big(\log (z_0-\bar v) - \log(\bar v_t-\bar v)\big).
-\end{split}\end{equation}
-    Rearrange this, we have
-\[
-    \bar v_t - \bar v \leq (z_0 - \bar v)e^{-\tau(t-t_0)},
-    \quad t\geq t_0.
-\] 
-    This implies the desired result in this step.
-
-    Step 4: We will show that there exists constant $C, \delta,t_0>0$ such that
-\[
-    |\bar v - v_t(k_t^{-1} e^{-\alpha t})|\leq Ck_t^\delta, \quad t\geq t_0.
-\]
-    Define 
-\[
-    \rho_t := 1+ \frac{\log k_t}{t\alpha}, \quad t\geq 0.
-\]
-    According to the fact that
-\[
-    k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}, \quad t\geq 0,
-\]
-    and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
-    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$ where the martingale limit $W_\infty$ is a non-degenerate random variable.
-This implies that
-\[
-    v_t(e^{-\alpha t}) = -\log \mathbf P_1[e^{-W_t}]\xrightarrow[t\to \infty]{} - \log \mathbf P_{1}[e^{-W_\infty}] =: z^* \in (0,\infty).
-\]
-    The $L \log L$ critierioin also garuntees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.ly in $\mathbf P_1$.
-This and the non-degeneracy of $W_\infty$ implies that
-\[
-    z^*=-\log \mathbf P_1[e^{-W_\infty}] < -\log \mathbf P_1(W_\infty = 0) = \bar v.
-\]
-
-    Fix an arbitrary $\epsilon \in (0,\tau)$.
-    According to the fact that $\tau=\psi'(\bar v)>0$ , there exists $z_0 \in (0,\bar v)$ such that for all $z\in (z_0, \bar v)$, we have $-\psi(z)\geq (\bar v - z)(\tau- \epsilon)$.
-    Fix this $z_0$. For $t$ large enough, according to the fact that $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$, we can verify the following:
-\begin{equation}\begin{split}
-    &t =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
-    \\&= \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)}
-     \\&= \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
-\end{split}\end{equation} 
-    where we used the fact that
-\[
-    \int_{v_{\rho_t t}(e^{-\alpha \rho_tt})}^{z_0} \frac{dz}{-\psi(z)} \xrightarrow[t\to \infty] {}\int_{z^*}^{z_0} \frac{dz}{-\psi(z)}.
-\]
-    Now we have, for $t$ large enough,
-\begin{equation}\begin{split}
-    &t\leq  \rho_t t + O(1)+ \int_{z_0}^{v_t(k_t^{-1}e^{-\alpha t})} \frac{dz}{(\bar v-z)(\tau - \epsilon)}
-    \\&=  \rho_t t +O(1)- \frac{1}{\tau-\epsilon}\Big( \log \big(\bar v-v_t(e^{-\alpha \rho_t t})\big) - \log(\bar v-z_0)\Big).
-\end{split}\end{equation}
-    Rearrange this, we have, for $t$ large enough,
-\[
-    e^{-t(\tau - \epsilon)} \geq e^{-\rho_t t(\tau - \epsilon)+O(1)}(\bar v - v_t(e^{-\alpha \rho_t t})).
-\]
-    Therefore, there exists constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$, 
-\[
-    \bar v - v_t(k_t^{-1} e^{-\alpha t}) \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
-    \leq Ck_t^{\frac{\tau - \epsilon}{\alpha}}.
-\]
-    This implies the required result in this step.
-
-    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exists constant $C, \delta, t_0 > 0$ such that
-\[
-    \mathbf P_{x}(0< W_t\leq k_t) \leq C(k_t^{\delta}+e^{-\delta t}),\quad t\geq t_0.
-\]
-Note that the left side is always bounded by $1$, so if we can take $t_0 =0$ in the above statement. 
-\end{proof}
-\begin{comment}
-
-\end{comment}
-
-\subsection{Parameters}
-    Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}.
-    Define
- \begin{equation}\begin{split}
- \label{parameter_mk}
-      m_t[f]
-      :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
- \end{split}\end{equation}
-    According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
-\[
-    |m_t[f]|
-    \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
-    \quad t\geq 0.
-\]
-    According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, then the following limit exists:
-\begin{equation}\begin{split}
-\label{para: critical case}
-    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
-\end{split}\end{equation}
-    where
-\[
-    \phi
-    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
-\]
-    According to \cite[Lemma 5.1]{MM}, if $f\in \mathcal{P}$ satisfies that $\alpha\beta<\kappa_fb(1+\beta)$, then
-\begin{equation}\begin{split}
-    m[f]
-    :=\sum_{k=0}^\infty m_k[f]
-    =\alpha e^{\alpha}\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds \label{msmallcase}
-\end{split}\end{equation}
-is well defined.
+Since $Y_t^{\tilde{f},a_0}$ is increasing in $t$, it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+	As a consequence, almost surely we have
+\begin{align*}
+    \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\tilde{f},a_0}|
+    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\tilde{f},a_0}|=0.
+\end{align*}
+	On the other hand, the martingale $M_t^{\tilde{f},a_0}$ satisfies
+\begin{align*}
+    \|M_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),\quad t\geq 0.
+\end{align*}
+	This implies that the martingale converges almost surely.
+	As a consequence,
+\[
+	\lim_{t\rightarrow\infty} e^{-(a_0-\kappa_f)bt}M_t^{\tilde{f},a_0}
+	=0,
+	\quad \mathbb P_\mu\text{-a.s.}
+\]
+
+	The proof is now completed.
+\subsection{The critical rate case.} First we introduce an criterion of $(1+\beta)$-stable distribution.
 \begin{lem}
@@
 \]
-    Define another measure $\lambda_0$ on $S$ by
+Recall the definition of $\Gamma$ function in \eqref{eq: definition of Gamma function}, and define another measure $\lambda_0$ on $S$ by
 \[
@@
 \end{proof}
-
+ Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}.
+    Define
+ \begin{equation}\begin{split}
+ \label{parameter_mk}
+      m_t[f]
+      :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
+ \end{split}\end{equation}
+    According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
+\[
+    |m_t[f]|
+    \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
+    \quad t\geq 0.
+\]
+    According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, the following limit exists:
+\begin{equation}\begin{split}
+\label{para: critical case}
+    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
+\end{split}\end{equation}
+    where
+\[
+    \phi
+    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
+\]
 \begin{cor}
@@
     $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
-\item
-\label{it: third stable}
-    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
 \end{enumerate}
@@
 \[
-    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 T_{1-s}^\alpha (-i\theta T_{s+t}^\alpha f)^{1+\beta}(x)~ds,
+    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
     \quad \theta \in \mathbb R.
@@
 \label{eq: what I want to proof}
-	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 T_{1-s}^\alpha (|T_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
+	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
 \end{equation}
@@
 $
-	g \mapsto \int_0^1 T_{1-s}^\alpha (|T_{s}^\alpha g|^{1+\beta})~ds
+	g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds
 $
 	is a $(1+\beta)$-controllable operator on $\mathcal P$.
-	This implies that $x \mapsto \int_0^1 T_{1-s}^\alpha (|T_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
+	This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
 	Therefore \eqref{eq: what I want to proof} is true.
 
-    The proofs of \eqref{it: second stable} and \eqref{it: third stable} are similar to that of \eqref{it: first stable}.
+    The proofs of \eqref{it: second stable} is similar to that of \eqref{it: first stable}.
 \end{proof}
-
-\section{Proof of main results}
-
-In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
-
 \begin{lem}\label{lem: mainlemma}
@@
 \begin{equation}\begin{split}
-   & |Y_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
+   & |K_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
    \leq R(|\theta_{t,k}P^\alpha_k f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
@@
      \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}
-     \\& \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}.
+     \\& \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}.
 \end{split}\end{equation}
@@
 \end{proof}
-\subsection{Proof of Theorem \ref{Theorem12}}
+We now present the proof of Theorem \ref{Theorem12}
+\subsubsection{Proof of Theorem \ref{Theorem12}}
 \label{sec: proof of thm 1.3}
@@
         \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq C \frac{1}{t^{\delta}},
-        \quad t\geq t_0.
+        \quad t\geq t_0,
 \end{align*}
-    According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\eta_1$ under $\tilde {\mathbb P}_\mu$.
+    Where $\mathcal{\mathbb{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$. According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\zeta$ under $\tilde {\mathbb P}_\mu$.
     Therefore, we only need to prove
@@
 \end{split}\end{equation}
-    Then according to Lemma \ref{lem: control of Wt}, Proposition \ref{lem: control of XT} and Chebyshev's inequality, there exists $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
+    Then according to Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality, there exists $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
 \begin{equation}\begin{split}
@@
 \begin{equation}\begin{split}
-    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C t^{-\delta}, \quad t\geq0.
+    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<t^{-1/2})\leq C( t^{-\delta}+e^{-\delta t}), \quad t\geq0.
 \end{split}\end{equation}
@@
     |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
-    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ct^{-\delta},
+    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C(t^{-\delta}+e^{-\delta t}),
     \quad t\geq t_0.
@@
 	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{Theorem12}.
-
-\subsection{Proof of Theorem \ref{Theorem11}}
-	Fix  $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$.
-	Fix $\mu \in \mathcal M_c(\mathbb R^d)$.
-	Write
-\begin{equation}\begin{split}
-    f
-    =\sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
-    =:
-    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f}.
-\end{split}\end{equation}
-	Then
-\begin{align*}
-    &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
-    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle,
-    \quad t\geq 0.
-\end{align*}
-	According to Lemma \ref{lemma26},
-	we have
-\begin{equation}\begin{split}
-\label{as convergence}
-     \sum_{|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p
-     \xrightarrow[t\to \infty]{} \sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
-\end{split}\end{equation}
-$\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
-	Therefore, it is suffice to show that
-\begin{equation}\begin{split}
-    J_t
-    :=e^{-(\alpha-\kappa_fb)t}\langle \tilde{f},X_t\rangle,
-    \quad t\geq 0,
-\end{split}\end{equation}
-	converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$.
-
-	Step 1. Let $g\in \mathcal P$.
-	Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa < \frac{\alpha \beta}{b(1+\beta)}$.
-	We will show that for each $\gamma \in (0,\beta)$ there exist constants $C,\delta > 0$ such that
-\[
-	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-	\leq C e^{-\delta t},
-	\quad t\geq 0.
-\]
-	In order to do this, 
-we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, 
-for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
-	Then, according to Lemma \ref{lem: control moment}, we have, for each $\gamma \in (0,\beta)$,
-\begin{enumerate}
-\item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
-\[
-    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    \leq C e^{-(\alpha-\kappa b)t}e^{(\alpha-\kappa_g b)t}
-    \leq C  e^{-(\kappa_g - \kappa )bt},
-    \quad t\geq 0;
-\]
-\item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C>0$ such that
-\[
-     \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-     \leq C t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-     = C t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
-     \quad t\geq 0;
-\]
-\item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
-\[
-    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-     = C  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
-     \quad t\geq 0;
-\]
-\item
-	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above, and the fact that \[\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-	\leq \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C, \delta >0$ such that
-\[
-	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-	\leq Ce^{-\delta t},
-	\quad t\geq 0.
-\]
-\end{enumerate}
-	Thus, the desired conclusion in this step is valid.
-	In particular, by taking $g = \tilde f$ and $\kappa = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
-
-	Step 2.
-	Further assume that $f\in C^2(\mathbb R^d)$, we will show that $J_t$ converges to $0$ almost surely.
-	Define for $a \geq 0$ and $ t\geq 0$,
-\begin{equation}\begin{split}
-	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,
-	\quad g\in \mathcal P\cap C^2(\mathbb R^d),
-\end{split}\end{equation}
-and
-\begin{equation}\begin{split}
-    Y_t^{g,a}
-    :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds,
-    \quad g\in \mathcal P\cap C^2(\mathbb R^d).
-\end{split}\end{equation}
-	Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$.
-	According to \eqref{defmartingale}, we have
-\begin{align*}
-    J_t
-    =e^{-(a_0-\kappa_f)bt} (M_t^{\tilde{f}, a_0}+L_t^{\tilde{f}, a_0}),
-    \quad t\geq 0.
-\end{align*}
-	So we only need to show that
-\begin{align*}
-    e^{-(a_0-\kappa_f)b t}M_t^{\tilde{f},a_0}
-    \xrightarrow[t\to \infty]{} 0,
-    \quad e^{-(a_0-\kappa_f)b t}L_t^{\tilde{f},a_0}
-    \xrightarrow[t\to \infty]{} 0
-    \quad \mathbb{P}_{\mu}\text{-a.s.}
-\end{align*}
-	Notice that $\kappa_{(L+a_0 b)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
-	So according to Step 1, for an arbitrary fixed $\gamma\in (0,\beta)$, there exist $C, \delta>0$ such that for each $t\geq 0$,
-\begin{equation}\begin{split}
-    \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C e^{-\delta t},
-    \quad \|e^{-(\alpha-a_0 b)t}\langle L\tilde{f}+a_0 b\tilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C e^{-\delta t}.
-\end{split}\end{equation}
-	Now, by the triangle inequality, for each $t\geq 0$,
-\begin{align*}
-    &\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq\|Y_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\tilde{f}+a_0 b\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
-\end{align*}
-Since $Y_t^{\tilde{f},a_0}$ is increasing in $t$, it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-	As a consequence, almost surely we have
-\begin{align*}
-    \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\tilde{f},a_0}|
-    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\tilde{f},a_0}|=0.
-\end{align*}
-	On the other hand, the martingale $M_t^{\tilde{f},a}$ satisfies
-\begin{align*}
-    \|M_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),\quad t\geq 0.
-\end{align*}
-	This implies that the martingale converges almost surely.
-	As a consequence,
-\[
-	\lim_{t\rightarrow\infty} e^{-(a_0-\kappa_f)bt}M_t^{\tilde{f},a}
-	=0,
-	\quad \mathbb P_\mu\text{-a.s.}
-\]
-
-	The proof is now completed.
-
-\subsection{Proof of Theorem \ref{Theorem13}}
+\subsection{The small rate case.}
+     For each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$, let
+\begin{equation}\begin{split}
+    m[f]
+    :=\sum_{k=0}^\infty m_k[f]
+    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds. 
+\end{split}\end{equation}
+According to \cite[Lemma 5.1]{MM}, $m[f]$
+is well defined, i.e. $|m[f]|<\infty$.
+\begin{cor}
+	For all $t\geq 0$ and $f\in \mathcal P$ satisfying $\alpha\beta < \kappa_f b(1+\beta)$, 
+    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+\end{cor}
+\begin{proof}
+Similar to the proof of corollary \ref{cor: alpha stable rv}.
+\end{proof}
+\subsubsection{Proof of Theorem \ref{Theorem13}}
 	Let $f\in \mathcal P$ be such that $\alpha \beta < \kappa_f b(1+\beta)$.
@@
  	:=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
- 	\quad t > t_0,
+ 	\quad t > t_0.
  \]
@@
 \end{align*}
-    Hence, according to \eqref{msmallcase}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \eta_2$ under $\tilde {\mathbb P}_\mu$.
+    Hence, according to \eqref{msmallcase}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
     So we only need to prove that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3,$ under $\tilde {\mathbb P}_\mu$.
@@
     \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big],
-    \quad t\geq t_0,
+    \quad t\geq t_0.
 \end{split}\end{equation}
@@
 \]
-	Let
-\[
-	\mathcal E_t
+	Recall that
+\[
+	 A_t(\epsilon)
 	:=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
@@
 \]
-	According to Proposition \ref{lem: control of XT}, there exists
-	$C>0$ such that  $\mathbb{\tilde{P}}_{\mu}(\mathcal E_t^c)\leq C e^{-\epsilon \beta t}$
-	for all $t\geq 0$.
+	According to \eqref{lem: control of XT}, there exists
+	$C,\delta>0$ such that  
 	Therefore, there exists $C>0$ such that
 \begin{equation}\begin{split}
-    |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{\mathcal{E}^{c}_t}]|
-    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq Ce^{-\epsilon \beta t},
+    &|\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
+    \leq 2\mathbb{\tilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<e^{-\epsilon t})
+    \\&\leq C(e^{-\epsilon\delta t}+e^{-\delta t}).
     \quad t\geq t_0.
@@
 \begin{align*}
-    &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
-    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
+    &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
+    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)^c}\big]
     \\&\leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
@@
 	The proof is complete.
-
+\subsection{Further results for large rate case.}
+Recall that
+\begin{align}
+   \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}, 
+\end{align}
+and
+\begin{align}
+    \mathcal{C}_l=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
+\end{align}
+For each $g\in \mathcal{C}_l$ expressed by
+    $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$,
+where $x\in \mathbb{R}^d$. Let
+\begin{align}
+    I_tg(x):=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d. 
+\end{align}
+and define 
+\begin{align}
+    K:=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
+\end{align}
+
+\begin{lem}\label{lem: control of Isg}
+ There exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
+\begin{align}
+    |I_tg(x)|\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
+\end{align}
+\end{lem}
+\begin{proof}
+Let $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
+\begin{align}
+    |I_tg(x)|=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|\leq e^{-(\alpha-Kb)t}h(x),\quad t\geq 0,x\in \mathbb{R}^d.
+\end{align}
+\end{proof}
+For each  $n\geq 1$, let 
+\begin{align}
+    \bar{m}_n[g]:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds,
+\end{align}
+therefore,
+\begin{align}
+    \bar{m}[g]=\sum_{n=1}^{\infty}\bar{m}_n[g].
+\end{align}
+\begin{lem}\label{lem: control of mn}
+There exists $C>0$ such that
+ \begin{align}
+     |\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1.
+ \end{align}
+Then $|\bar{m}[g]|<\infty$.
+\end{lem}
+\begin{proof}
+Let $h$ be the control function in Lemma \ref{lem: control of Isg}.
+\begin{align}
+    &|\bar{m}_n[g]|\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
+    &\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle 
+    \leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
+\end{align}
+By the fact $\alpha\beta>K(1+\beta)b$, we easily get $|\bar{m}[g]|<\infty$.
+\end{proof}
+\begin{cor}
+\label{cor: alpha stable rv 1}
+	For all $n\geq 0$ and $g\in \mathcal C_l$ expressed by \eqref{discompose},
+\begin{enumerate}
+\item
+\label{it: first stable}
+    $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable;
+\item
+\label{it: second stable}
+    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+\end{enumerate}
+\end{cor}
+\begin{proof}
+Similar to the proof of corollary \ref{cor: alpha stable rv}.
+\end{proof}
+Moreover, by fubini's theorem, we get
+\begin{align}\label{equ: transform of mn}
+    &\bar{m}_n[g]=e^{\alpha(n-1)}\int_0^1 e^{\alpha s}\langle \eta(iI_{s+n-1}g)^{1+\beta}, \varphi\rangle ds\\
+    &=e^{\alpha(n-1)}\langle \int_0^1 P_s^{\alpha}\langle \eta(iI_{s+n-1}g)^{1+\beta}ds, \varphi\rangle\\
+    &=e^{\alpha(n-1)}\langle \int_0^1 P_{1-s}^{\alpha}\langle \eta(iI_{n-s}g)^{1+\beta}ds, \varphi\rangle=e^{\alpha(n-1)}\langle Z_1(-I_ng), \varphi\rangle.
+\end{align}
+\begin{comment}
+
+For each $p\in \mathbb{N}_0$ and $t\geq 0$, recall that $H ^p_t=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle$ is a martingale corresponding to the $\sigma$-algebra $\{\mathscr{F}_t\}_{t\geq 0}$.
+According to Lemma 2.8, we get
+\begin{align}
+    \lim_{u\rightarrow \infty}\langle I_ug,X_{t+u} \rangle=\sum_{k:\alpha\beta>k(1+\beta)b}e^{(\alpha-kb)t}\sum_{|p|=k}H_{\infty}^p, \quad \mathbb{P}_{\mu}\text{-a.s}. 
+\end{align}
+\end{comment}
+
+Recall that $\Big\{\{H^p_t, \mathscr{F}_t\}_{t\geq 0};p\in \mathbb{Z}_+^d\Big\}$ is a family of martingale defined in Lemma \ref{lemma26}.
+
+\begin{lem}
+    For each $n>0$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$,
+    \begin{align}
+        \bar{\gamma}_{t,n}:=\sum_{p\in\mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\bar{\zeta}_n,
+    \end{align}
+    where $\bar{\zeta}_n$ is an $(1+\beta)$-stable random variable with characteristic function
+    \begin{align}
+        \mathbb{E}[e^{i\theta \bar{\zeta}_n}]=\exp[\bar{m}_n[\theta g]],\quad \theta\in \mathbb{R}.
+    \end{align}
+\end{lem}
+\begin{proof}
+We only have to show that
+\begin{align}
+    \mathbb{P}_{\mu}[\exp(i\bar{\gamma}_{t,n}); D^c]
+    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(\bar{m}_n[g]),
+    \quad \mu \in \mathcal M_c(\mathbb R^d), n \geq 0.
+\end{align}
+Let $\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$, we easily get 
+\begin{align}
+    \bar{\gamma}_{t,n}=\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p, X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle).
+\end{align}
+
+	Step 1. We will show that for each $\epsilon > 0, n\geq 0$, and $t\geq 0$ we have
+\begin{align}
+    \big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
+    \leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon)
+\end{align}
+	where
+\begin{align}
+\label{eq: Def of JJ1}
+	J'_1(t,n,\epsilon)
+	&:= \mathbb{P}_{\mu}\big[|\langle K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p, X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big]
+	\\ J'_2(t,n,\epsilon)
+	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big]
+	\\ J'_3(t,n, \epsilon)
+	&:=2\mathbb{P}_{\mu}(A_{t+n-1}(\epsilon)\Delta D^c).
+\end{align}
+ From the definition of $K_1$ and $Z_1$, we have
+\begin{align}
+\label{eq: need11}
+    &\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}|\mathscr{F}_{t+n-1}]
+    =\mathbb{P}_{\mu}[e^{i\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p,X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle)}|\mathscr{F}_{t+n-1}]
+    \\&=e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
+\end{align}
+
+ According to \eqref{eq: need11} and the fact that
+\[
+	|e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
+\]
+	we verify that
+\begin{align}
+\label{eq: inequality that will used later1}
+    &\big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
+    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]
+    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; A_{t+n-1}(\epsilon)| \mathscr F_{t+n-1}]\big| + 2\mathbb P_\mu(A_{t+n-1}(\epsilon) \Delta D^c| \mathscr F_{t+n-1})\Big]
+    \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}| \mathscr F_{t+n-1}]-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big] + J'_3(t,n,\epsilon)
+    \\&=\mathbb{P}_{\mu}\Big[\big|e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
+    \\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (k_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
+    \\&\leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon)
+    \quad n\geq 0, t\geq 0, \epsilon> 0.
+\end{align}
+
+Step 2.  We will show that for each $\epsilon$ small enough, there exists constant $C,\delta>0$ such that,
+    \begin{align}
+    \label{eq:large rate J1}
+      J'_1(t,n,\epsilon)\leq C e^{-\delta(t+n)}, n\geq 1, t\geq 0.
+    \end{align}
+	In fact, let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the $(\theta^{1+\beta}\vee \theta^{1+\beta+\delta_0})$-controller. Then we have, 
+\begin{align}
+   & |K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
+   \leq R(|\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p|)\mathbf{1}_{A_{t+n-1}(\epsilon)}
+   \\&\leq R \Big(\frac{\sum_{p\in\mathcal{N}}|a_p|e^{-(\alpha-|p|b)n}|\phi_p|}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)
+   \\&\leq \sum_{\rho\in\{\delta_0,1\}}\Big(\frac{e^{-(\alpha-Kb)n}}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)^{1+\beta+\rho}R|h|
+   \\&=\sum_{\rho\in\{\delta_0,1\}}e^{-\alpha\frac{1+\beta+\rho}{1+\beta}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha\beta-K(1+\beta)b)n}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}S|h|
+   \\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|,
+   \quad n\geq 0, t\geq 0, \epsilon > 0,
+\end{align}
+where $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
+Thus for each $n\geq 0, t\geq 0, \epsilon > 0$
+\begin{align}
+\label{eq: estimate of J11}
+     J'_1(t,n,\epsilon)&
+     \leq  \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle R|h|,X_{t+n-1}\rangle]\\
+     & \leq C\sum_{\rho\in\{\delta_0,1\}}\exp\Big\{-\Big(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta}\Big)(t+n-1)\Big\}.
+     \end{align}
+
+Step 3.
+	We will show that for each $\epsilon$ small enough, there exists constant $C,\delta>0$ such that,
+\begin{align}
+\label{eq:31step31}
+    J'_2(t,n,\epsilon)
+    \leq C e^{-\delta(t+n)},
+    \quad n\geq 1, t\geq 0.
+\end{align}
+
+In fact, according to the definition of $Z_1$, $\bar{m}_n$ and \eqref{equ: transform of mn}, we have
+\begin{align}
+    &\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\\
+    &=e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big),\\
+    & t\geq 0, n\geq1.
+\end{align}
+Therefore,
+\begin{align}
+    &J'_2(t,n,\epsilon)
+	= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big]\\
+	&\leq e^{\alpha(n-1)}\mathbb{P}_{\mu}\Big[\big|\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\big|;A_{t+n-1}(\epsilon)\Big]\\
+	&\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle g_p, X_{t+n-1}\rangle],
+	\quad t\geq 0, n\geq 1.
+\end{align}
+Where
+\begin{align}
+    g_n=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
+\end{align}
+Similar to proof of \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$, such that
+\[
+     |T_t g_n|\leq e^{-bt}h,
+     \quad t\geq 0, n\geq 1.
+\]
+
+ Chose $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$. According to Lemma \ref{lem: control moment} (3) with $\kappa=1$, there exists $C>0$ such that 
+\begin{align}
+    \mathbb{P}_{\mu}[\langle g_n, X_{t+n-1}\rangle]\leq Ce^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
+\end{align}
+Therefore, 
+\begin{align}
+    &J'_2(t,n,\epsilon)\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle g_n, X_{t+n-1}\rangle]\\
+    &\leq C e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)}\\
+    &=Ce^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}\\&\leq Ce^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)},\quad t\geq 0,n\geq 1.
+\end{align}
+	Step 4. We will show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
+\begin{align}\label{ineq: control of J31}
+    J'_3(t,n,\epsilon)\leq Ce^{-\delta (t+n)}\quad t\geq0, n\geq 1.
+\end{align}
+	Similar to the proof of step 4 in Lemma \ref{lem: mainlemma}
+
+	Final step, combine the result in Step 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ convergence to $0$ exponentially fast while $t\rightarrow\infty$.
+	This gives the desired result.
+\end{proof}
+
+\begin{lem}\label{lem:lemma03}
+    For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for any $t\geq 0$, $m\in\mathbb{N}$, we have
+    \begin{align}\label{ineq: next we will need}
+        \Big|\tilde{\mathbb{P}}_{\mu}\Big[\prod_{n=1}^m\exp(i\theta\bar{\gamma}_{t,n})-\prod_{n=1}^m\exp(\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t}.
+    \end{align}
+\end{lem}
+\begin{proof}
+Step 1.
+Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  For each  $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for any $t\geq 0$, $n\geq 1$, we have
+\begin{align}
+    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]\leq Ce^{-\delta(t+n-1)}.
+\end{align}
+Step 2.   Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$, 
+    For each $n=1,...,m$, we define
+    \[\tilde{a}_n:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big)\]
+     where by convention the product is $1$ for $n=0$. Then we get for each $n > 0$,
+    \begin{align*}
+        &\tilde{a}_{n-1} - \tilde{a}_n
+        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\Big(e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}}\Big);D^c\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
+        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
+    \end{align*}
+    According to step 1 and corollary \ref{cor: alpha stable rv 1} there exist $C,\delta>0$ such that for any $n=1,..m$ and $t\geq0$, we have
+    \begin{align*}
+        &|\tilde{a}_{n-1}- \tilde{a}_n|
+        \\&\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
+        \\& \leq C e^{-\delta(t+n-1)}.
+    \end{align*}
+Therefore,
+\begin{align}
+    \text{LHS of \eqref{ineq: next we will need}}&= \left|\tilde{a}_{0}-\tilde{a}_m\right|
+    \leq\sum_{n=1}^m\left|\tilde{a}_{n-1}-\tilde{a}_n\right|
+    \leq \sum_{n=1}^m C e^{-\delta(t+n-1)}.
+\end{align}
+	Notice that $C, \delta>0$ are independent of the choice of $t\geq 0$, $m\in \mathbb{N}$.
+\end{proof}
+Now let
+\begin{align}
+    \tilde{\gamma}_{t,n}:=\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_{t}\|^{\frac{1}{1+\beta}}},\quad t\geq 0, n\geq 1.
+\end{align}
+\begin{lem}\label{lem: lemma04}
+     For each $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$
+such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
+\begin{align}
+    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq C m e^{-\delta t}.
+\end{align}
+\end{lem}
+\begin{proof}
+According to \cite[Lemma 3.4.3]{Durrett2010Probability}
+\begin{align}\label{ineq: used next 3}
+    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq \sum_{n=1}^m\tilde{\mathbb{P}}_{\mu}[|Y''_{t,n}|],
+\end{align}
+where 
+\begin{align}
+    Y''_{t,n}:=e^{i\theta\tilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},\quad t\geq 0, n\geq 1, \theta\in \mathbb{R}.
+\end{align}
+    Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
+\[
+    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0,
+\]
+and 
+\[
+   \alpha\gamma>K(1+\gamma)b.
+  \]
+  Fix this $\gamma$, then choose $\eta_0,\eta_1>0$ such that
+\[
+    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
+\]
+    Define for all $n \geq 1$ and $t\geq 0$,
+\begin{align}
+\label{def: Dtk1}
+    \mathcal{D}_{t,n}&:=\left\{|H_t-H_{t+n-1}|\leq  e^{-\eta_0 t}, H_{t}> 2e^{-\eta_1t}\right\}.
+\end{align}
+Step 1. Similar to the proof of step 1 in section \ref{sec: proof of thm 1.3}, we can show that there exist $C,\delta >0$ such that for all $n \geq 1$ and $t\geq 0$,
+\begin{align}
+\label{thm12111}
+    \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}^c_{t,n}}\big]
+    \leq C e^{-\delta t}.
+\end{align}
+\begin{comment}
+
+    In fact, let $C_1$ be the constant in  Lemma 2.9 corresponding to this fixed $\gamma$ and $C_2$ be the constant in Lemma 2.10.
+    By Chebyshev's inequality, there exists $C>0$ such that for all $n \geq 1$ and $t\geq 0$,
+\begin{align}
+\label{eq: prob of Dtkc11}
+    &\mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,n}^c)
+    \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t+n-1}| > e^{-\eta_0 t})+\mathbb{\tilde{P}}_{\mu}(H_{t}\leq 2e^{-\eta_1 t}),
+    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0 t}\mathbb{P}_{\mu}[|H_t-H_{t+n-1}|]+\mathbb{\tilde{P}}(H_t\leq 2e^{-\eta_1 t})
+    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0 t}\|H_t - H_{t+n-1}\|_{\mathbb P_\mu; 1+\gamma}+\mathbb{\tilde{P}}(H_{t}\leq 2e^{-\eta_1t})
+    \\&\leq C_1  \mathbb{P}_{\mu}(D^c)^{-1}  e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)t}+C_2 e^{-\eta_1\beta t}.
+\end{align}
+    This implies the desired result in this step, since $|Y_{t,k}| \leq 2$ a.s..
+\end{comment}
+    Step 2. We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constant $C,\delta > 0$, such that for all $n\geq 1$ and $t\geq 0$,
+\begin{align}
+\label{thm12211}
+     \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq Ce^{-\delta t}.
+\end{align}
+    In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $t \geq 0$ and $n\geq 1$,
+    \begin{align}\label{large: used next}
+        &\tilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\\
+        &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}\tilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot\Big|\frac{1}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}\Big]\\
+        &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}\tilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot K'_{t,n}\Big],
+    \end{align}
+    where
+    \begin{align}
+        K'_{t,n}
+    :=\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t+n-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t+n-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}.
+    \end{align}
+\begin{comment}
+
+     Note that, since $\eta_1 < \eta_0$, we have
+\begin{align*}
+    H_{t+n-1}
+    &\geq H_{t}- e^{-\eta_0 t}
+    \geq 2e^{-\eta_1t}-e^{-\eta_0 t}
+    \\&\geq e^{-\eta_1 t},
+    \quad \text{ on } \mathcal D_{t,n}.
+\end{align*}
+    Therefore, for each $t \geq 0$ and $n\geq 1$,
+\begin{align*}
+     &\Big|H_t^{\frac{1}{1+\beta}}-H_{t+n-1}^{\frac{1}{1+\beta}}\Big|
+     \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t+n-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t+n-1}\right|,
+    \\&\leq \frac{1}{1+\beta} \max\{e^{\eta_1 t}, \frac{1}{2}e^{\eta_1 t}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0 t}
+    \\&\leq \frac{1}{1+\beta} e^{\eta_1 t} e^{-\eta_0 t}
+    =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1) t},
+    \quad \text{ on } \mathcal D_{t,n},
+\end{align*}
+    and
+\begin{align*}
+    |H_t^{\frac{1}{1+\beta}}H_{t+n-1}^{\frac{1}{1+\beta}}|
+    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1t},
+    \quad \text{ on } \mathcal D_{t,n}.
+\end{align*}
+\end{comment}
+Since $\eta_1 < \eta_0$,  Similar to the proof of step 2 in section \ref{sec: proof of thm 1.3}, we can show that, there is a constant $C\geq 0$ such that,
+\begin{align}
+\label{ineq: control of Kkt1}
+     K'_{t,n}
+     \leq C e^{-(\eta_0 - 3\eta_1) t},
+     \quad t \geq 0, n\geq 1.
+\end{align}
+   According to Lemma \ref{lem: control of wt},
+    there exist constants $C,C',C''>0$ such that  for all $t\geq 0$ and $n\geq 1$,
+    \begin{align}\label{ineq:used next 2}
+        &\tilde{\mathbb{P}}_{\mu}\big[|Y_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq \frac{C}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\mathbb{P}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\Big]\\
+        &\leq \frac{C}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}
+        \\&\leq C' |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
+        &=C'|\theta|\sum_{p\in\mathcal{N}}|a_p|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}\cdot e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(n-1)}.\\
+        &\leq C''|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}.
+    \end{align}
+    We get \eqref{thm12211} since $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}<\eta_0-3\eta_1$ and $\alpha\gamma>Kb(1+\gamma)\geq |p|b(1+\gamma)$.
+\begin{comment}
+
+ Step 3. We will show that there exist $C, \delta> 0$ such that
+    \begin{align}
+    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq Cm e^{-\delta t},\quad m\in \mathbb{N}, t\geq 0.
+    \end{align}
+\end{comment}
+
+    Combine \eqref{ineq: used next 3}, Step 1 and Step 2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
+\end{proof}
+\begin{comment}
+
+Let 
+\begin{align}
+    \gamma_t:=\frac{H_t^p-H_{\infty}^p}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}},\quad t\geq 0, p\in \mathbb{N}_0^d.
+\end{align}
+\end{comment}
+\begin{lem}\label{lem: lemma05}
+For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta_1,\delta_2>0$ such that 
+\begin{align}
+  \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 m}),\quad m\in \mathbb{N}, t\geq 0.
+\end{align}
+\end{lem}
+\begin{proof}
+In fact, recall that $A_t(\epsilon):=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to proposition \ref{lem: control of XT}, there exists
+	$C,\delta>0$ such that for all $t\geq 0$
+\begin{align}\label{ineq: control of gamma_t on dc}
+     \Big|\tilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]\leq 2\tilde{P}_{\mu}(A_t(\epsilon)^c)\leq C e^{-\delta t}.
+\end{align}
+	 Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ satisfying $\alpha\gamma>Kb(1+\gamma)$, According to Lemma \ref{lem: control of wt}, there exist $C,C'>0$ such that
+\begin{align}\label{ineq: control of gamma_t on d}
+  &\Big|\tilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)}\Big]\Big|\\
+  &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{n=m}^{\infty}\sum_{p\in \mathcal{N}}|a_p|\mathbb{P}_{\mu}\Big[\frac{|H_{t+n-1}^p-H_{t+n}^p|}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}\mathbf{1}_{A_t(\epsilon)}\Big]\\
+  &\leq  \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}\\
+  &\leq C|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
+  &\leq C'|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m}.\\
+  & \theta\in\mathbb{R}, m\in \mathbb{N}, \epsilon>0, t\geq 0.
+\end{align}
+Combining with \eqref{ineq: control of gamma_t on dc} and \eqref{ineq: control of gamma_t on d}, we complete the proof.
+\end{proof}
+Now we are ready to prove Theorem \ref{theorem 1.6}.
+\subsubsection{Proof of Theorem \ref{theorem 1.6}}
+
+Let $\delta_0$ be the control parameter in Lemma \ref{lem: lemma04} and fixed $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$, notice that
+\begin{align}
+    \text{LHS of \eqref{thm: large rate}}=\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\tilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\tilde{\gamma}_{t,n},\quad t\geq 0.
+\end{align}
+According to Lemma \ref{lem:lemma03}, there exists $C,\delta>0$ such that
+\begin{align}\label{ineq: last1}
+    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t},\quad t\geq 0,\theta\in\mathbb{R}.
+\end{align}
+According to Lemma \ref{lem: lemma04}, there exists $C>0$ such that
+\begin{align}
+    \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C  e^{-\frac{\delta_0}{2} t},\quad t\geq 0, \theta\in \mathbb{R}.
+ \end{align}
+ According to Lemma \ref{lem: lemma05}, there exists $C,\delta_1,\delta_2>0$ such that
+ \begin{align}
+  \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 e^{\frac{\delta_0}{2}t}}),\quad t\geq 0, \theta\in \mathbb{R}.
+\end{align}
+we complete the proof by letting $t\rightarrow\infty$.
 \appendix
@@
 \end{thebibliography}
+
 \end{document}

### 2019-01-31 supCLT.tex
supCLT.tex 0114

@@
 %%----Versions-----------------------------
+% supCLT0109.tex 2018/01/14 by Yanxia
 % supCLT0107.tex 2018/01/07 by Jianjie
+% supclt1231.tex 2018/12/14 by Zhenyao
+% supclt1213.tex 2018/12/14 by Yanxia
+% supclt1213.tex 2018/12/13 by Renming
+% supclt1209.tex 2018/12/07 by Zhenyao
+% supclt1207.tex 2018/12/07 by Renming
 % supCLT1204.tex 2018/12/04 by Zhenyao
@@
     [CLT for Super-OU processes]
-    {CLT for Super-OU Processes with stable Branching}
+ %   {CLT for Super-OU Processes with stable Branching}
+ {Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with Stable Branching}
 \author
@@
     {Yan-Xia Ren\\
-    School of Mathematical Sciences\\
+    LMAM School of Mathematical Sciences \& Center for
+Statistical Science\\
     Peking University\\
@@
     %Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$.
-    Consider a super-OU process $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, where $\alpha >0$ and $\beta\in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
+    Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, where $\alpha >0$ and $\beta\in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
 $
@@
     %In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
-    In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly.
+    In the small branching rate case  $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
     %In the critical branching rate case,  $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.
-    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly.
-    In the large branching rate case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$.
+    In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
+    In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$,
+    %new added
+    we first prove that
+    %end new
+    $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$,
+    %new added
+   and then established a central limit theorem, which say that after proper centering and scaling, we get a $(1+\beta)$-stable random variable again.
+    %end new
 \end{abstract}
@@
     %where $a>0$ and $b>0$ are constants.
-    where $\sigma>0$ and $b>0$.
-    %Denote by $(P_t^\alpha)_{t\geq 0}$ the transition semigroup of $\xi$.
+    where $\sigma$ and $b$ are positive constants.
     Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
@@
 \label{mechanism}
-    %\psi(z)
-    %:= - \alpha z + z^{1+\beta},
        \psi(z)=
@@
 
-    According to the Subsection A.1, the branching mechanism $\psi$ can be extended on $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
+  %  According to the Subsection A.1, the branching mechanism $\psi$ can be extended on
+   According to  Subsection A.1, the branching mechanism $\psi$ can be extended to
+    $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
  \[\psi(z)=
@@
     \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
-    \quad z\in \mathbb C_+.
+    %\quad z\in \mathbb C_+.
+    \quad z\in \mathbb C^0_+.
 \end{equation}
@@
     \kappa_f
-    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
+    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \},
 \end{equation}
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-\subsection{Main Result}
-We will use $\mathcal M_c(\mathbb R_d)$ to denote the space of all
+%\subsection{Main Result}
+\subsection{Main Results}
+We will use $\mathcal M_c(\mathbb R^d)$ to denote the space of all
 finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of super-OU process.
@@
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
-  For all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, on the condition $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
+  For all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
+  % on the condition
+  under the condition
+   $\alpha\beta>|p|b(1+\beta)$,
+   $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
    $L^{1+\gamma}(\mathbb{P}_{\mu})$ (see Lemma \ref{lemma26}).
@@
  \end{thm}
-For any $t\geq 0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s.
-and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$.
+For any $t\geq 0$, let $H_t:=e^{-\alpha t}\|X_t\|$.
+Then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s.
+and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
  \begin{rem}
@@
 for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
-     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
+     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$
     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
@@
     For $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
-\[
-    \tilde{m}[f]
+%\[
+\begin{equation}\label{tilde-m}
+%\tilde{m} is changed to \widetilde{m} withput marking.
+    \widetilde{m}[f]
     := \langle \eta (-i\phi)^{1+\beta},\varphi\rangle
-\]
+%\]
+\end{equation}
     where
@@
     \mathbb{E} [e^{i\theta \tilde{\zeta}}]
-    =\exp(\tilde{m}[\theta f]),
-    \quad \theta\in \mathbb R.
-\]
+    =\exp(\widetilde{m}[\theta f]),
+    \quad \theta\in \mathbb R,
+\]
+%new added
+where $\widetilde{m}$ is defined by \eqref{tilde-m}.
+%end new
 \end{thm}
@@
 For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_f b(1+\beta)$, define
-
-\[
+%\[
+\begin{equation}
      m[f]
     =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds, \label{msmallcase}
-\]
-According to \cite[Lemma 5.1]{MM}, $m[f]$ is well-defined.
+%\]
+\end{equation}
+%According to \cite[Lemma 5.1]{MM}, $m[f]$ is well-defined.
+According to Lemmd \ref{Lemma2.7} below, $m[f]$ is well-defined.
 \begin{thm}
@@
     where $\zeta$ is a $(1+\beta)$-stable random variable with
-    $$\mathbb{E} [e^{i\theta \zeta}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
+    $$\mathbb{E} [e^{i\theta \zeta}]=\exp(m[\theta f]), \quad \theta\in \mathbb R,$$
+    %new added
+    where $m$ is defined by \eqref{msmallcase}.
+    %end new
 \end{thm}
 
-\subsubsection{further results in the large branching rate case}
+\subsubsection{Further results in the large branching rate case}
 Define
@@
 \end{align}
-Fixed $f\in \mathcal{C}_l$, $f$ can be expressed by
+%Fixed $f\in \mathcal{C}_l$, $f$ can be expressed by
+For each fixed $f\in \mathcal{C}_l$, $f$ can be expressed as
 \begin{align}\label{discompose}
@@
 \end{align}
-It is easy to get that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$. Denote
-\begin{align}
+It is easy to get that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$.
+
+%Denote
+Define
+\begin{align}\label{bar-m}
    \bar{m}[f]:=\int_{0}^{\infty} e^{\alpha s}\langle \eta(iI_sf)^{1+\beta},\varphi\rangle ds.
 \end{align}
-According to Lemma \ref{lem: control of mn}, $\bar{m}[f]$ is well-defined.
+According to Lemma \ref{lem: control of mn} in Subsection 4, $\bar{m}[f]$ is well-defined.
 \begin{thm}\label{theorem 1.6}
-For each $f\in\mathcal{C}_l$ expressed by \eqref{discompose} and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$ it holds that,
+For each $f\in\mathcal{C}_l$ expressed by \eqref{discompose} and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$ it holds that, as $t\to\infty$,
 \begin{align}\label{thm: large rate}
-    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}a_pe^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow{d}\bar{\zeta},\quad t\rightarrow\infty,
+    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}a_pe^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow{d}\bar{\zeta},
+    %\quad t\rightarrow\infty,
 \end{align}
@@
 \begin{align}
-    \mathbb{E}[e^{i\theta\bar{\zeta}}]=\exp[\bar{m}[\theta g]],\quad \theta\in \mathbb{R}.
-\end{align}
+    \mathbb{E}[e^{i\theta\bar{\zeta}}]=\exp[\bar{m}[\theta f]],\quad \theta\in \mathbb{R},
+\end{align}
+%new added
+where $\bar{m}$ is defined by \eqref{bar-m}.
+%end new
 \end{thm}
@@
 \section{Preliminaries}
-\subsection{~~operators}
+%\subsection{~~operators}
+\subsection{Definition of $h$-controller}
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
@@
 
-\subsection{Control the operators for super-OU process.} Let $X$ be the super-OU process introduced in subsection 1.1.
-Write $\psi_0(z)=\psi(z)+\alpha z$, for each $z\in \mathbb{C}_+$, and define operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$ by
+%\subsection{Control the operators for super-OU process.}
+\subsection{h-controller  for super-OU process.}
+Let $X$ be the super-OU process introduced in Subsection 1.1. Write $\psi_0(z)=\psi(z)+\alpha z$, for each $z\in \mathbb{C}_+$, and define operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$ by
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$, the value of the L\'evy exponent of the infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
+For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$,
+%the value of the L\'evy exponent of the infinite divisible random variable
+the value of the characteristic exponent of the infinite divisible random variable
+$\langle f, X_t\rangle$ at $1$.
     From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
@@
 \[
-    f \mapsto (-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta},\quad 0\leq t\leq 1
+    f \mapsto (-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta},\quad 0\leq t\leq 1,
 \]
@@
 
-    (7). A consequence of (5), (6), Lemma \ref{lem: property of controllable operators}(3) and that $K_t = (Z'_t-Z_t)+Z''_t$.
+%    (7). A consequence of (5), (6), Lemma \ref{lem: property of controllable operators}(3) and that $K_t = (Z'_t-Z_t)+Z''_t$.
+(7). Since $K_t = (Z'_t-Z_t)+Z''_t$, we get the desired result from (5), (6), Lemma \ref{lem: property of controllable operators}(3).
 \end{proof}
+
+%new added
+\subsection{Parameters of the stable limits}
+%end new
+%The following is moved from below with modification.
+   Define
+ \begin{equation}\begin{split}
+ \label{parameter_mk}
+      m_t[f]
+      :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
+ \end{split}\end{equation}
+
+ We first collect some lemmas of \cite{MM}, which will be used in this paper.
+%   According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
+ \begin{lem}(\cite[Lemma 2.7]{MM})\label{Lemma2.7} For each $f\in\mathcal{P}$, there is a constant $C>0$ such that
+%\[
+\begin{equation}\label{domi-m}
+    |m_t[f]|
+    \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
+    \quad t\geq 0.
+%\]
+\end{equation}
+\end{lem}
+  %new added
+ Recall the definition of $\widetilde{m}$ in \eqref{tilde-m}.
+  %end new
+  \begin{lem}(\cite[Lemma 4.2]{MM})
+   % According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
+    %the following limit exists:
+    If $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
+    we have
+\begin{equation}\begin{split}
+\label{para: critical case}
+ %   \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
+ \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle=\widetilde{m}[f],
+\end{split}\end{equation}
+    where
+\[
+    \phi
+    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
+\]
+\end{lem}
+%\begin{cor}
+\begin{prop}
+\label{cor: alpha stable rv}
+	For all $t\geq 0$ and $f\in \mathcal P$,
+\begin{enumerate}
+\item
+\label{it: first stable}
+ $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable;
+ \item
+\label{it: second stable}
+%    $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
+If $\alpha\beta=\kappa_f b(1+\beta)$,  $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+\end{enumerate}
+%\end{cor}
+\end{prop}
+\begin{proof}
+    \eqref{it: first stable}:
+	Fix $t\geq 0$ and $f\in \mathcal P$.
+	Note that $m_t[\theta f]$ can be rewritten as
+\[
+    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
+    \quad \theta \in \mathbb R.
+\]
+	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
+\begin{equation}
+\label{eq: what I want to proof}
+	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
+\end{equation}
+	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),  we know that
+$
+	g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds
+$
+	is a $(1+\beta)$-controllable operator on $\mathcal P$.
+	This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
+	Therefore \eqref{eq: what I want to proof} is true.
+
+    The proofs of \eqref{it: second stable} is similar to that of \eqref{it: first stable}.
+\end{proof}
+
+ For each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
+     %let
+%\begin{equation}\begin{split}
+%    m[f]
+%    :=\sum_{k=0}^\infty m_k[f]
+ %   =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
+%\end{split}\end{equation}
+%According to \cite[Lemma 5.1]{MM}, $m[f]$
+%is well defined, i.e. $|m[f]|<\infty$.
+According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
+\begin{equation}\label{sum-m}
+m[f]
+    =\sum_{k=0}^\infty m_k[f]
+    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
+\end{equation}
+%\begin{cor}
+\begin{prop}
+	For all $t\geq 0$ and $f\in \mathcal P$ satisfying $\alpha\beta < \kappa_f b(1+\beta)$,
+    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+%\end{cor}
+\end{prop}
+\begin{proof}
+%Similar to the proof of corollary \ref{cor: alpha stable rv}.
+The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
+\end{proof}
+
+Recall that
+\begin{align}
+   \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
+\end{align}
+and
+\begin{align}
+    \mathcal{C}_l=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
+\end{align}
+%For each $g\in \mathcal{C}_l$ expressed by
+For each $g\in \mathcal{C}_l$ we have the following expression:
+    $$g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.$$
+%where $x\in \mathbb{R}^d$.
+%Let
+Also recall that the definition of $I_tg(x)$:
+\begin{align}
+    I_tg(x)=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
+\end{align}
+%and define
+Define
+\begin{align}
+    K=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
+\end{align}
+
+\begin{lem}\label{lem: control of Isg}
+ %There exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
+ For each $g\in \mathcal{C}_l$, there exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
+\begin{align}
+    |I_tg(x)|\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
+\end{align}
+\end{lem}
+\begin{proof}
+%Let $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
+Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  Put  $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
+\begin{align}
+    |I_tg(x)|=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|\leq e^{-(\alpha-Kb)t}h(x),\quad t\geq 0,x\in \mathbb{R}^d.
+\end{align}
+\end{proof}
+For each  $n\geq 1$, let
+\begin{align}
+    \bar{m}_n[g]:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds.
+\end{align}
+%therefore,
+%\begin{align}
+%   \bar{m}[g]=\sum_{n=1}^{\infty}\bar{m}_n[g].
+%\end{align}
+\begin{lem}\label{lem: control of mn}
+%There exists $C>0$ such that
+For each $g\in \mathcal{C}_l$,  there exists constant $C>0$ such that
+ \begin{align}
+     |\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1,
+ \end{align}
+%Then $|\bar{m}[g]|<\infty$.
+which implies that
+\begin{equation}\label{sum-bar-m}\bar{m}[g]=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g]\end{equation}
+is well-defined.
+\end{lem}
+\begin{proof}
+Let $h$ be the control function in Lemma \ref{lem: control of Isg}.
+\begin{align}
+    &|\bar{m}_n[g]|\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
+    &\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle
+    \leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
+\end{align}
+By the fact that $\alpha\beta>K(1+\beta)b$, we easily get
+%$|\bar{m}[g]|<\infty$.
+$\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
+\end{proof}
+%\begin{cor}
+\begin{prop}
+\label{cor: alpha stable rv 1}
+%	For all $n\geq 0$ and $g\in \mathcal C_l$
+%expressed by \eqref{discompose},
+For any $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
+\begin{enumerate}
+\item
+\label{it: first stable}
+    $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable;
+\item
+\label{it: second stable}
+    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+\end{enumerate}
+%\end{cor}
+\end{prop}
+\begin{proof}
+%Similar to the proof of corollary \ref{cor: alpha stable rv}.
+The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
+\end{proof}
+
 \section{Tail probability}
-In this section, we will introduce a small value probability result of supercritical continuous-state branching process with general branching mechanism and control $(1+\gamma)$-moments for the super-OU process.
+In this section, we will introduce a small value probability result of supercritical continuous-state branching process with general branching mechanism and %control
+$(1+\gamma)$-moments for the super-OU process. These will be needed to prove our main results.
 
 \subsection{Small value probability}
-    In this subsection, we digress briefly from super-OU process and consider a supercritical continuous-state branching process (CSBP) $(Y_t)$.
-Our goal is to determing how fast the probability $P_x(0<e^{-\alpha t}Y_t \leq k_t)$ convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
-    Let branching mechanism corresponding to the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ be denoted as
-\[
-    \psi(z)
-    := -\alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z\geq 0,
-\]
-    where $\alpha > 0$, $\rho \geq 0$ and $\pi$ is a measure on $(0,\infty)$ satisfying $\int_{(0,\infty)} (y \wedge y^2) \pi(dy) < \infty$.
+    In this subsection, we digress briefly from super-OU process and consider a supercritical continuous-state branching process (CSBP)
+    %$(Y_t)$.
+    $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
+    Our goal is to determing how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
+  %  Let branching mechanism corresponding to the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ be denoted as
+  %\[
+  %  \psi(z)
+  %  := -\alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z\geq 0,
+  %\]
+  %  where $\alpha > 0$, $\rho \geq 0$ and $\pi$ is a measure on $(0,\infty)$ satisfying $\int_{(0,\infty)} (y \wedge y^2) \pi(dy) < \infty$.
+  Assume that the branching mechanism of the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is given by \eqref{mechanism}.
     Suppose that the Grey's condition is satisfied, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
@@
 \begin{proof}
-    \emph{Step 1}. We recall some known facts about the CSBP $(Y_t)$.
+    Step 1. We recall some known facts about the CSBP $(Y_t)$.
     For each $\lambda \geq 0$, denote by $t\mapsto v_t(\lambda)$ the unique positive solution of
@@
     According to the fact that $\tau=\psi'(\bar v)>0$ , there exists $z_0 \in (0,\bar v)$ such that for all $z\in (z_0, \bar v)$, we have $-\psi(z)\geq (\bar v - z)(\tau- \epsilon)$.
-    Fix this $z_0$. For $t$ large enough, according to \eqref{CSBP: int} and the fact that $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$, we can verify the following:
+Fix this $z_0$.
+    %For $t$ large enough, according to \eqref{CSBP: int} and the fact that $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$, we can verify the following:
+    For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$. Then  using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have
 \begin{equation}\begin{split}
@@
 \]
-Note that the left side is always bounded by $1$, so if we can take $t_0 =0$ in the above statement.
+Note that the left side is always bounded by $1$, so we can take $t_0 =0$ in the above statement.
 \end{proof}
@@
 Denote  $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in the following section.
-\subsection{The large rate case.} To prove Theorem \ref{Theorem11}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family martingales for $\gamma\in (0, \beta)$.
+
+%\subsection{The large rate case.}
+\subsection{The large rate case: $\alpha \beta > \kappa_f b (1+\beta)$}
+%new added
+
+In this subsection, we prove Theorem \ref{Theorem11}. We will be back to the large branching rate case in Subsection \ref{large rate again} to prove Theorem \ref{theorem 1.6}.
+%end new
+To prove Theorem \ref{Theorem11}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family martingales for $\gamma\in (0, \beta)$.
 Recall that $L$ is the infinitesimal generator of the OU-process.
@@
 \]
+%new added
+Moreover, letting $t\to\infty$ in above inequality, we have
+\[
+    \|H^p_\infty-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq C e^{-\frac{ 1}{1+\gamma}(\alpha\gamma-|p|b(1+\gamma))s},\quad s\geq 0.
+\]
+%end new
 \end{lem}
@@
 
-\subsubsection{Proof of Theorem \ref{Theorem11}}.
+%\subsubsection{Proof of Theorem \ref{Theorem11}}.
+{\it Proof of Theorem \ref{Theorem11}.}\quad
 	Fix  $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$.
@@
 	The proof is now completed.
-\subsection{The critical rate case.} First we introduce an criterion of $(1+\beta)$-stable distribution.
+%\subsection{The critical rate case.}
+\subsection{The critical rate case: $\alpha\beta=\kappa_fb(1+\beta)$}
+First we introduce an criterion of $(1+\beta)$-stable distribution.
 \begin{lem}
@@
 \end{proof}
- Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}.
-    Define
- \begin{equation}\begin{split}
- \label{parameter_mk}
-      m_t[f]
-      :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
- \end{split}\end{equation}
-    According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
-\[
-    |m_t[f]|
-    \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
-    \quad t\geq 0.
-\]
-    According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, the following limit exists:
-\begin{equation}\begin{split}
-\label{para: critical case}
-    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
-\end{split}\end{equation}
-    where
-\[
-    \phi
-    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
-\]
-\begin{cor}
-\label{cor: alpha stable rv}
-	For all $t\geq 0$ and $f\in \mathcal P$,
-\begin{enumerate}
-\item
-\label{it: first stable}
-    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable;
-\item
-\label{it: second stable}
-    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
-\end{enumerate}
-\end{cor}
-\begin{proof}
-    \eqref{it: first stable}:
-	Fix $t\geq 0$ and $f\in \mathcal P$.
-	Note that $m_t[\theta f]$ can be rewritten as
-\[
-    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
-    \quad \theta \in \mathbb R.
-\]
-	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
-\begin{equation}
-\label{eq: what I want to proof}
-	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
-\end{equation}
-	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),  we know that
-$
-	g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds
-$
-	is a $(1+\beta)$-controllable operator on $\mathcal P$.
-	This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
-	Therefore \eqref{eq: what I want to proof} is true.
-
-    The proofs of \eqref{it: second stable} is similar to that of \eqref{it: first stable}.
-\end{proof}
+%The following is moved forward
+%Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}.
+%    Define
+% \begin{equation}\begin{split}
+ %\label{parameter_mk}
+  %    m_t[f]
+   %   :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
+ %\end{split}\end{equation}
+  %  According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
+%%\[
+%\begin{equation}\label{domi-m}
+ %   |m_t[f]|
+  %  \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
+   % \quad t\geq 0.
+%%\]
+%\end{equation}
+%  %new added
+% Recall the definition of $\widetilde{m}$ in \eqref{tilde-m}.
+%  %end new
+%    According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
+    %the following limit exists:
+%    we have
+%\begin{equation}\begin{split}
+%\label{para: critical case}
+ %%   \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
+ %\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle=\widetilde{m}[f],
+%\end{split}\end{equation}
+ %   where
+%\[
+ %   \phi
+%    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
+%\]
+%%\begin{cor}
+%\begin{prop}
+%\label{cor: alpha stable rv}
+%	For all $t\geq 0$ and $f\in \mathcal P$,
+%\begin{enumerate}
+%\item
+%\label{it: first stable}
+ %$\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable;
+ %\item
+%\label{it: second stable}
+%%    $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
+%If $\alpha\beta=\kappa_f b(1+\beta)$,  $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random %variable.
+%\end{enumerate}
+%%\end{cor}
+%\end{prop}
+%\begin{proof}
+ %   \eqref{it: first stable}:
+	%Fix $t\geq 0$ and $f\in \mathcal P$.
+	%Note that $m_t[\theta f]$ can be rewritten as
+%\[
+ %   m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
+  %  \quad \theta \in \mathbb R.
+%\]
+%	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
+%\begin{equation}
+%\label{eq: what I want to proof}
+%	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
+%\end{equation}
+%	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),  we know that
+%$
+%	g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds
+%$
+%	is a $(1+\beta)$-controllable operator on $\mathcal P$.
+%	This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
+%	Therefore \eqref{eq: what I want to proof} is true.
+
+ %   The proofs of \eqref{it: second stable} is similar to that of \eqref{it: first stable}.
+%\end{proof}
+%end move
 \begin{lem}\label{lem: mainlemma}
@@
 \end{split}\end{equation}
-    From Corollary \ref{cor: alpha stable rv}, we have
+    %From Corollary \ref{cor: alpha stable rv}, we have
+    From Proposition \ref{cor: alpha stable rv}, we have
 \begin{equation}
@@
 According to \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$ such that
+{\bf( Remark: State \cite[Lemma 2.8]{MM} as a Lemma in our paper)}
 \[
@@
 \begin{cor}\label{cor: used in next corollary}
-Let $f\in \mathcal{P}$, $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
-Then there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
+%Let $f\in \mathcal{P}$, $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
+%Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
+Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq \kappa_fb(1+\beta)$.
+%Then
+Then for any $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
+there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
 \begin{equation}\begin{split}
@@
 \begin{prop}\label{corollary31}
-Let $f\in \mathcal{P}$, and $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then there exist $C,\delta>0$ such that
+%Let $f\in \mathcal{P}$, and $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
+%Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then there exist $C,\delta>0$ such that
+Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then for any $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
+there exist constants $C,\delta>0$ such that
 for all $t\geq 0$,
@@
     \end{align*}
-    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any
+ %   According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary},
+  According to Proposition \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary},
+    there exist $C,\delta>0$ such that for any
     % $k\in\{0,1,...,n\}$, we have
@@
 \end{proof}
-We now present the proof of Theorem \ref{Theorem12}
-\subsubsection{Proof of Theorem \ref{Theorem12}}
-\label{sec: proof of thm 1.3}
-    Fix $f\in\mathcal{P}$.
+We now present the proof of Theorem \ref{Theorem12}.
+\bigskip
+%\subsubsection{Proof of Theorem \ref{Theorem12}}
+%\label{sec: proof of thm 1.3}
+
+{\it Proof of Theorem \ref{Theorem12}.}\quad
+  %  Fix $f\in\mathcal{P}$.
+  According to our assumption, $f\in\mathcal{P}$ is fixed and that  $\alpha\beta=\kappa_fb(1+\beta)$.
     Chose $t_0 > 0$ large enough so that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
@@
 	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{Theorem12}.
-\subsection{The small rate case.}
-     For each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$, let
-\begin{equation}\begin{split}
-    m[f]
-    :=\sum_{k=0}^\infty m_k[f]
-    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds. 
-\end{split}\end{equation}
-According to \cite[Lemma 5.1]{MM}, $m[f]$
-is well defined, i.e. $|m[f]|<\infty$.
-\begin{cor}
-	For all $t\geq 0$ and $f\in \mathcal P$ satisfying $\alpha\beta < \kappa_f b(1+\beta)$, 
-    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\end{cor}
-\begin{proof}
-Similar to the proof of corollary \ref{cor: alpha stable rv}.
-\end{proof}
-\subsubsection{Proof of Theorem \ref{Theorem13}}
-	Let $f\in \mathcal P$ be such that $\alpha \beta < \kappa_f b(1+\beta)$.
+%\subsection{The small rate case.}
+\subsection{The small rate case: $\alpha\beta<\kappa_fb(1+\beta)$}
+
+%The following is moved forward
+% %    For each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
+     %let
+%%\begin{equation}\begin{split}
+%%    m[f]
+%%    :=\sum_{k=0}^\infty m_k[f]
+ %%   =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
+%%\end{split}\end{equation}
+%%According to \cite[Lemma 5.1]{MM}, $m[f]$
+%%is well defined, i.e. $|m[f]|<\infty$.
+%According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
+%\begin{equation}\label{sum-m}
+%m[f]
+%    =\sum_{k=0}^\infty m_k[f]
+%    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
+%\end{equation}
+%\begin{cor}
+%\begin{prop}
+%	For all $t\geq 0$ and $f\in \mathcal P$ satisfying $\alpha\beta < \kappa_f b(1+\beta)$,
+%    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+%\end{cor}
+%\end{prop}
+%\begin{proof}
+%Similar to the proof of corollary \ref{cor: alpha stable rv}.
+%The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
+%\end{proof}
+
+%\subsubsection{Proof of Theorem \ref{Theorem13}}
+{\it Proof of Theorem \ref{Theorem13}.}\quad
+%	Let $f\in \mathcal P$ be such that $\alpha \beta < \kappa_f b(1+\beta)$.
+According to our assumption, $f\in \mathcal P$  is fixed  and  that $\alpha \beta < \kappa_f b(1+\beta)$.
 	Let $t_0 > 1$ be large enough so that
@@
 \end{align*}
-    Hence, according to \eqref{msmallcase}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
+%Hence, according to \eqref{msmallcase}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
+Hence, according to \eqref{sum-m}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
    So we only need to prove that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3,$ under $\tilde {\mathbb P}_\mu$.
@@
 \end{align*}
-Now we can use the same argument as in Step 3 in Section \ref{sec: proof of thm 1.3} to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
+%Now we can use the same argument as in Step 3 in Section \ref{sec: proof of thm 1.3}
+Now we can  use the  same argument used in the proof of Theorem \ref{Theorem12}
+to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
 
@@
 	The proof is complete.
-\subsection{Further results for large rate case.}
-Recall that
-\begin{align}
-   \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}, 
-\end{align}
-and
-\begin{align}
-    \mathcal{C}_l=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
-\end{align}
-For each $g\in \mathcal{C}_l$ expressed by
-    $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$,
-where $x\in \mathbb{R}^d$. Let
-\begin{align}
-    I_tg(x):=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d. 
-\end{align}
-and define 
-\begin{align}
-    K:=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
-\end{align}
-
-\begin{lem}\label{lem: control of Isg}
- There exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
-\begin{align}
-    |I_tg(x)|\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
-\end{align}
-\end{lem}
-\begin{proof}
-Let $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-\begin{align}
-    |I_tg(x)|=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|\leq e^{-(\alpha-Kb)t}h(x),\quad t\geq 0,x\in \mathbb{R}^d.
-\end{align}
-\end{proof}
-For each  $n\geq 1$, let 
-\begin{align}
-    \bar{m}_n[g]:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds,
-\end{align}
-therefore,
-\begin{align}
-    \bar{m}[g]=\sum_{n=1}^{\infty}\bar{m}_n[g].
-\end{align}
-\begin{lem}\label{lem: control of mn}
-There exists $C>0$ such that
- \begin{align}
-     |\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1.
- \end{align}
-Then $|\bar{m}[g]|<\infty$.
-\end{lem}
-\begin{proof}
-Let $h$ be the control function in Lemma \ref{lem: control of Isg}.
-\begin{align}
-    &|\bar{m}_n[g]|\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
-    &\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle 
-    \leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
-\end{align}
-By the fact $\alpha\beta>K(1+\beta)b$, we easily get $|\bar{m}[g]|<\infty$.
-\end{proof}
-\begin{cor}
-\label{cor: alpha stable rv 1}
-	For all $n\geq 0$ and $g\in \mathcal C_l$ expressed by \eqref{discompose},
-\begin{enumerate}
-\item
-\label{it: first stable}
-    $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable;
-\item
-\label{it: second stable}
-    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\end{enumerate}
-\end{cor}
-\begin{proof}
-Similar to the proof of corollary \ref{cor: alpha stable rv}.
-\end{proof}
-Moreover, by fubini's theorem, we get
+%\subsection{Further results for large rate case.}
+\subsection{Proof of Theorem \ref{theorem 1.6}}\label{large rate again}
+%new added
+In this subsection, we are back to the large branching rate case, and aim to prove Theorem \ref{theorem 1.6}. 
+%end new
+%The following is moved forward
+%Recall that
+%\begin{align}
+ %  \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
+%\end{align}
+%and
+%\begin{align}
+ %   \mathcal{C}_l=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
+%\end{align}
+%%For each $g\in \mathcal{C}_l$ expressed by
+%For each $g\in \mathcal{C}_l$ we have the following expression:
+%    $$g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.$$
+%%where $x\in \mathbb{R}^d$.
+%%Let
+%Also recall that the definition of $I_tg(x)$:
+%\begin{align}
+ %   I_tg(x)=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
+%\end{align}
+%Define
+%\begin{align}
+%    K=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
+%\end{align}
+
+%\begin{lem}\label{lem: control of Isg}
+% %There exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
+% For each $g\in \mathcal{C}_l$, there exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
+%\begin{align}
+ %   |I_tg(x)|\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
+%\end{align}
+%\end{lem}
+%\begin{proof}
+%%Let $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
+%Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  Put  $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
+%\begin{align}
+ %   |I_tg(x)|=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|\leq e^{-(\alpha-Kb)t}h(x),\quad t\geq 0,x\in \mathbb{R}^d.
+%\end{align}
+%\end{proof}
+%For each  $n\geq 1$, let
+%\begin{align}
+ %   \bar{m}_n[g]:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds.
+%\end{align}
+%%therefore,
+%%\begin{align}
+%%   \bar{m}[g]=\sum_{n=1}^{\infty}\bar{m}_n[g].
+%%\end{align}
+%\begin{lem}\label{lem: control of mn}
+%%There exists $C>0$ such that
+%For each $g\in \mathcal{C}_l$,  there exists constant $C>0$ such that
+% \begin{align}
+%     |\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1,
+% \end{align}
+%%Then $|\bar{m}[g]|<\infty$.
+%which implies that
+%\begin{equation}\label{sum-bar-m}\bar{m}[g]=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g]\end{equation}
+%is well-defined.
+%\end{lem}
+%\begin{proof}
+%Let $h$ be the control function in Lemma \ref{lem: control of Isg}.
+%\begin{align}
+%    &|\bar{m}_n[g]|\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
+ %   &\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle
+%    \leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
+%\end{align}
+%By the fact that $\alpha\beta>K(1+\beta)b$, we easily get
+%%$|\bar{m}[g]|<\infty$.
+%$\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle %ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
+%\end{proof}
+%%\begin{cor}
+%\begin{prop}
+%\label{cor: alpha stable rv 1}
+%For any $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
+%\begin{enumerate}
+%\item
+%\label{it: first stable}
+ %   $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable;
+%\item
+%\label{it: second stable}
+%    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+%\end{enumerate}
+%%\end{cor}
+%\end{prop}
+%\begin{proof}
+%The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
+%\end{proof}
+%end move
+%Moreover, by fubini's theorem, we get
+By Fubini's theorem, we get
 \begin{align}\label{equ: transform of mn}
@@
 \begin{proof}
-We only have to show that
+%We only have to show that
+We only need to show that
 \begin{align}
@@
 \end{align}
-Let $\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$, we easily get 
+%Let
+Put
+$\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
+%, we easily get
+We get that
 \begin{align}
@@
 
-	Step 1. We will show that for each $\epsilon > 0, n\geq 0$, and $t\geq 0$ we have
+	Step 1. We will show that for any $\epsilon > 0, n\geq 0$, and $t\geq 0$, we have
 \begin{align}
     \big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
-    \leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon)
+    \leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon),
 \end{align}
@@
 	J'_1(t,n,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p, X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big]
+	&:= \mathbb{P}_{\mu}\big[|\langle K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p, X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big],
 	\\ J'_2(t,n,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big]
+	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big],\quad\mbox{and}
 	\\ J'_3(t,n, \epsilon)
@@
 \end{align}
- From the definition of $K_1$ and $Z_1$, we have
+ From the definitions of $K_1$ and $Z_1$, we have
 \begin{align}
 \label{eq: need11}
-    &\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}|\mathscr{F}_{t+n-1}]
+    &\displaystyle\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}|\mathscr{F}_{t+n-1}]
     =\mathbb{P}_{\mu}[e^{i\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p,X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle)}|\mathscr{F}_{t+n-1}]
-    \\&=e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
+    \\&=\displaystyle e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
 \end{align}
@@
 \]
-	we verify that
+we have
 \begin{align}
@@
 
-Step 2.  We will show that for each $\epsilon$ small enough, there exists constant $C,\delta>0$ such that,
+Step 2.  We will show that for each $\epsilon$ small enough, there exist constants $C,\delta>0$ such that,
     \begin{align}
     \label{eq:large rate J1}
-      J'_1(t,n,\epsilon)\leq C e^{-\delta(t+n)}, n\geq 1, t\geq 0.
+      J'_1(t,n,\epsilon)\leq C e^{-\delta(t+n)},\quad n\geq 1, \, t\geq 0.
     \end{align}
@@
 where $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-Thus for each $n\geq 0, t\geq 0, \epsilon > 0$
+Thus for each $n\geq 0,  t\geq 0, \epsilon > 0$,
 \begin{align}
@@
 
-In fact, according to the definition of $Z_1$, $\bar{m}_n$ and \eqref{equ: transform of mn}, we have
+In fact, according to the definitions of $Z_1$ and $\bar{m}_n$, and \eqref{equ: transform of mn}, we have
 \begin{align}
@@
 	&\leq e^{\alpha(n-1)}\mathbb{P}_{\mu}\Big[\big|\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\big|;A_{t+n-1}(\epsilon)\Big]\\
-	&\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle g_p, X_{t+n-1}\rangle],
-	\quad t\geq 0, n\geq 1.
-\end{align}
-Where
-\begin{align}
-    g_n=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
+	&\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}
+%[\langle g_p, X_{t+n-1}\rangle],
+[\langle g_n, X_{t+n-1}\rangle],
+	\quad t\geq 0, n\geq 1,
+\end{align}
+where we set
+\begin{align}
+    g_n:=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
 \end{align}
@@
 \]
-
- Chose $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$. According to Lemma \ref{lem: control moment} (3) with $\kappa=1$, there exists $C>0$ such that 
+{\bf Remark: State the above result as a Lemma}
+ Choose $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
+ %According to Lemma \ref{lem: control moment} (3) with $\kappa=1$,
+ Using Lemma \ref{lem: control moment} (3) with $\kappa=1$,
+ there exists $C>0$ such that
 \begin{align}
@@
 \end{align}
-	Step 4. We will show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
+	Step 4. %We will show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
+Using similar arguments in the proof of step 4 of Lemma \ref{lem: mainlemma}, we can show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
 \begin{align}\label{ineq: control of J31}
@@
 \end{align}
-	Similar to the proof of step 4 in Lemma \ref{lem: mainlemma}
-
-	Final step, combine the result in Step 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ convergence to $0$ exponentially fast while $t\rightarrow\infty$.
+%	Similar to the proof of step 4 in Lemma \ref{lem: mainlemma}
+
+%	Final step, combine the result in Step 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ convergence to $0$ exponentially fast while $t\rightarrow\infty$.
+%This gives the desired result.
+
+Finally, combining the results in steps 1-4.
+and noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$, converge to $0$ exponentially fast while $t\rightarrow\infty$, we get the desired result.
 	This gives the desired result.
@@
 \begin{lem}\label{lem:lemma03}
-    For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for any $t\geq 0$, $m\in\mathbb{N}$, we have
+    For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
     \begin{align}\label{ineq: next we will need}
@@
 Step 1.
-Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  For each  $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for any $t\geq 0$, $n\geq 1$, we have
+Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  for any  $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that, for any $t\geq 0$, $n\geq 1$, we have
 \begin{align}
@@
 \end{align}
-Step 2.   Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$, 
-    For each $n=1,...,m$, we define
-    \[\tilde{a}_n:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big)\]
+Step 2.   Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$.
+    For each $n=1,\cdots,m$, we define
+    \[\tilde{a}_n:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big),\]
      where by convention the product is $1$ for $n=0$. Then we get for each $n > 0$,
@@
         \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\Big(e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}}\Big);D^c\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
-        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
+        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
     \end{align*}
-    According to step 1 and corollary \ref{cor: alpha stable rv 1} there exist $C,\delta>0$ such that for any $n=1,..m$ and $t\geq0$, we have
+    %According to step 1 and corollary \ref{cor: alpha stable rv 1}
+   According to step 1 and Proposition \ref{cor: alpha stable rv 1},
+    there exist $C,\delta>0$ such that for any $n=1,\cdots, m$ and $t\geq0$, we have
     \begin{align*}
@@
 \begin{lem}\label{lem: lemma04}
-     For each $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$
+     For each $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$
 such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
@@
 \begin{proof}
-According to \cite[Lemma 3.4.3]{Durrett2010Probability}
+According to \cite[Lemma 3.4.3]{Durrett2010Probability},
 \begin{align}\label{ineq: used next 3}
@@
   \]
-  Fix this $\gamma$, then choose $\eta_0,\eta_1>0$ such that
+  Fix this $\gamma$, and then choose $\eta_0,\eta_1>0$ such that
 \[
@@
 \end{align}
-Step 1. Similar to the proof of step 1 in section \ref{sec: proof of thm 1.3}, we can show that there exist $C,\delta >0$ such that for all $n \geq 1$ and $t\geq 0$,
+%Step 1. Similar to the proof of step 1 in section \ref{sec: proof of thm 1.3},
+
+Step 1. Similar to step 1 in the proof of Theorem \ref{Theorem12},
+we can show that there exist constants $C,\delta >0$ such that for all $n \geq 1$ and $t\geq 0$,
 \begin{align}
@@
 \end{comment}
-    Step 2. We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constant $C,\delta > 0$, such that for all $n\geq 1$ and $t\geq 0$,
+
+    Step 2. We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta > 0$, such that for all $n\geq 1$ and $t\geq 0$,
 \begin{align}
@@
 \end{align}
-    In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $t \geq 0$ and $n\geq 1$,
+    In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have, for all $t \geq 0$ and $n\geq 1$,
     \begin{align}\label{large: used next}
@@
 \end{comment}
-Since $\eta_1 < \eta_0$,  Similar to the proof of step 2 in section \ref{sec: proof of thm 1.3}, we can show that, there is a constant $C\geq 0$ such that,
+%Since $\eta_1 < \eta_0$,  Similar to the proof of step 2 in section \ref{sec: proof of thm 1.3},
+Since $\eta_1 < \eta_0$,  using similar arguments used in  step 2 of the proof of Theorem \ref{Theorem12},
+we can show that, there is a constant $C\geq 0$ such that,
 \begin{align}
@@
 
-    Combine \eqref{ineq: used next 3}, Step 1 and Step 2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
+  %  Combine \eqref{ineq: used next 3}, Step 1 and Step 2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
+  Combinning \eqref{ineq: used next 3}, Steps 1-2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
 \end{proof}
@@
 \begin{lem}\label{lem: lemma05}
-For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta_1,\delta_2>0$ such that 
+For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta_1,\delta_2>0$ such that
 \begin{align}
@@
 \begin{proof}
-In fact, recall that $A_t(\epsilon):=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to proposition \ref{lem: control of XT}, there exists
+Recall that $A_t(\epsilon):=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to Proposition \ref{lem: control of XT}, there exists
 	$C,\delta>0$ such that for all $t\geq 0$
@@
 \end{align}
-	 Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ satisfying $\alpha\gamma>Kb(1+\gamma)$, According to Lemma \ref{lem: control of wt}, there exist $C,C'>0$ such that
+	 Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ satisfying $\alpha\gamma>Kb(1+\gamma)$.  According to Lemma \ref{lem: control of wt}, there exist $C,C'>0$ such that
 \begin{align}\label{ineq: control of gamma_t on d}
@@
   &\leq C'|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m}.\\
-  & \theta\in\mathbb{R}, m\in \mathbb{N}, \epsilon>0, t\geq 0.
+  & \qquad\theta\in\mathbb{R}, m\in \mathbb{N}, \epsilon>0, t\geq 0.
 \end{align}
@@
 Now we are ready to prove Theorem \ref{theorem 1.6}.
-\subsubsection{Proof of Theorem \ref{theorem 1.6}}
-
-Let $\delta_0$ be the control parameter in Lemma \ref{lem: lemma04} and fixed $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$, notice that
-\begin{align}
+\bigskip
+%\subsubsection{Proof of Theorem \ref{theorem 1.6}}
+
+{\it Proof of Theorem \ref{theorem 1.6}.}\quad
+Let $\delta_0$ be the control parameter in Lemma \ref{lem: lemma04}.  Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$. First note that
+\begin{align}\label{decompose}
     \text{LHS of \eqref{thm: large rate}}=\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\tilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\tilde{\gamma}_{t,n},\quad t\geq 0.
@@
 According to Lemma \ref{lem: lemma04}, there exists $C>0$ such that
-\begin{align}
+\begin{align}\label{ineq: last2}
     \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C  e^{-\frac{\delta_0}{2} t},\quad t\geq 0, \theta\in \mathbb{R}.
@@
  According to Lemma \ref{lem: lemma05}, there exists $C,\delta_1,\delta_2>0$ such that
- \begin{align}
+ \begin{align}\label{ineq: last3}
   \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 e^{\frac{\delta_0}{2}t}}),\quad t\geq 0, \theta\in \mathbb{R}.
 \end{align}
-we complete the proof by letting $t\rightarrow\infty$.
+%new addedd
+Also note that $\sum_{n=1}^\infty\bar{m}_n[\theta g]=\bar{m}[\theta g]$, see \eqref{sum-bar-m}.
+%end new
+Combining \eqref{decompose},\eqref{ineq: last1}, \eqref{ineq: last2} and \eqref{ineq: last3}, and letting $t\to\infty$, we get the desired result of Theorem \ref{theorem 1.6}.
 \appendix

### 2019-01-31 supCLT.tex
supCLT.tex: 0124

@@
 %%----Versions-----------------------------
+% supCLT0124.tex 2018/01/24 by Jianjie
 % supCLT0109.tex 2018/01/14 by Yanxia
@@
 \usepackage{mathrsfs}
+\usepackage{cite}
 \usepackage[backref=section]{hyperref}
@@
 \label{ss:1.1}
-	%Let $d \in \mathbb N:= \{1,2,\dots\}$ and
 	Let $d \in \mathbb N:= \{1,2,\dots\}$.
-    %$\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator
     Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with generator
@@
 
-  %  According to the Subsection A.1, the branching mechanism $\psi$ can be extended on
    According to  Subsection A.1, the branching mechanism $\psi$ can be extended to
@@
     \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
-    %\quad z\in \mathbb C_+.
     \quad z\in \mathbb C^0_+.
@@
 \end{equation}
-
+ %new added
+ In this paper, we will establish some spatial central limit theorems for the super-OU process with stable branching mechanism. Precisely, we want to find $F_t$ and $G_t$ such that
+ $$\frac{\langle f, X_t \rangle -G_t}{F_t}$$ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$.
+It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition.
+
+ There are many papers studying central limit behavior for branching processes, branching diffusions and superprocesses.
+See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes under some certain conditions.
+In \cite{ARMP}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{MP2012} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a forth moment condition.
+In this two paper, Milo\'s with his coauthor pictured connection between CLT and what they call branching rate regimes.
+In \cite{RSZ}, Yanxia Ren, Renming Song and Rui Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
+Moverover, Compare with the results in \cite{ARMP,MP2012}, the limit distributions in \cite{RSZ} are non-degenerate.
+In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, They also establish a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
+
+ All the results described above hold for systems with branching mechanisms satisfying finite variance.
+It's a natural step to establish counterparts of the central limit theorems for super processes with infinite variance.
+In \cite{MM}, Marks and Milo\'s have considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
+They established some central limit theorems on the small and critical branching rate cases but no large rate case.
+In this paper, we consider a class of super-OU processes with more general stable branching mechanisms.
+On small and critical branching cases, we obtained similar central limit theorems.
+Moreover, on large rate case, we not only show an almost sure convergent result, but also establish the corresponding central limit theorem, which is not appeared in \cite{MM}.
+
+ Except for the main results proved in section 4, there are some other significative results in our paper.
+In appendix, we show that the characteristic exponent of supercritical general super processes $U_t f(x)=-{\rm Log} \mathbb{P}_{\delta_x}e^{i\theta X_t(f)}$ can be defined by corresponding equation by using Spain Decomposition.
+In section 3, we establish a small value probability estimation of supercritical continuous-state branching processes with branching mechanism satisfying Grey's condition and $L\log L$ critierion.
+This all results are necessary for us to prove the central limit theorems.
+
+ % end new
 \subsection{OU Semigroup}
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-%\subsection{Main Result}
 \subsection{Main Results}
@@
   For all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
-  % on the condition
   under the condition
@@
     For $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
-%\[
 \begin{equation}\label{tilde-m}
-%\tilde{m} is changed to \widetilde{m} withput marking.
     \widetilde{m}[f]
     := \langle \eta (-i\phi)^{1+\beta},\varphi\rangle
-%\]
 \end{equation}
@@
 \]
-%new added
 where $\widetilde{m}$ is defined by \eqref{tilde-m}.
-%end new
 \end{thm}
@@
 For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_f b(1+\beta)$, define
-%\[
 \begin{equation}
@@
     =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds, \label{msmallcase}
-%\]
-\end{equation}
-%According to \cite[Lemma 5.1]{MM}, $m[f]$ is well-defined.
+\end{equation}
 According to Lemmd \ref{Lemma2.7} below, $m[f]$ is well-defined.
@@
     $$\mathbb{E} [e^{i\theta \zeta}]=\exp(m[\theta f]), \quad \theta\in \mathbb R,$$
-    %new added
     where $m$ is defined by \eqref{msmallcase}.
-    %end new
 \end{thm}
@@
 \end{align}
-%Fixed $f\in \mathcal{C}_l$, $f$ can be expressed by
 For each fixed $f\in \mathcal{C}_l$, $f$ can be expressed as
@@
 where $a_p=\langle f, \phi_p\rangle_{\varphi}$. Let
-\begin{align}
+\begin{align}\label{definition of Itf}
     I_tf(x):=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
@@
 
-%Denote
 Define
@@
     \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}a_pe^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow{d}\bar{\zeta},
-    %\quad t\rightarrow\infty,
 \end{align}
@@
 \end{align}
-%new added
 where $\bar{m}$ is defined by \eqref{bar-m}.
-%end new
 \end{thm}
@@
 \section{Preliminaries}
-%\subsection{~~operators}
 \subsection{Definition of $h$-controller}
@@
 
-%\subsection{Control the operators for super-OU process.}
 \subsection{h-controller  for super-OU process.}
@@
 
-%    (7). A consequence of (5), (6), Lemma \ref{lem: property of controllable operators}(3) and that $K_t = (Z'_t-Z_t)+Z''_t$.
 (7). Since $K_t = (Z'_t-Z_t)+Z''_t$, we get the desired result from (5), (6), Lemma \ref{lem: property of controllable operators}(3).
@@
 
-%new added
 \subsection{Parameters of the stable limits}
-%end new
-%The following is moved from below with modification.
    Define
@@
  We first collect some lemmas of \cite{MM}, which will be used in this paper.
-%   According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
  \begin{lem}(\cite[Lemma 2.7]{MM})\label{Lemma2.7} For each $f\in\mathcal{P}$, there is a constant $C>0$ such that
-%\[
 \begin{equation}\label{domi-m}
@@
     \quad t\geq 0.
-%\]
 \end{equation}
 \end{lem}
-  %new added
  Recall the definition of $\widetilde{m}$ in \eqref{tilde-m}.
-  %end new
   \begin{lem}(\cite[Lemma 4.2]{MM})
-   % According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
-    %the following limit exists:
     If $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
@@
 \label{para: critical case}
- %   \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
- \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle=\widetilde{m}[f],
+ \widetilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
 \end{split}\end{equation}
@@
 \end{lem}
-%\begin{cor}
+
+Further, for each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
+According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
+\begin{equation}\label{sum-m}
+m[f]
+    :=\sum_{k=0}^\infty m_k[f]
+    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
+\end{equation}
+% new added
+% I move ahead the follow lemma used in prop 2.6.
+Next lemma is an criterion of $(1+\beta)$-stable distribution.
+\begin{lem}
+\label{lem: charactreisticfunction}
+    Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
+    Then $$\theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},\quad \theta \in \mathbb R^d$$
+    is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
+\end{lem}
+\begin{proof}
+    From measure theory, there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
+\[
+    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
+    f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+\]
+Recall the definition of $\Gamma$ function in \eqref{eq: definition of Gamma function}, and define another measure $\lambda_0$ on $S$ by
+\[
+    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi).
+\]
+    Then $\lambda_0$ is a non-zero finite measure, since
+\[
+    \lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt)
+    = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
+\]
+    Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
+\[
+    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
+\]
+    Then, according to \cite[Remark 14.4]{Sato1999Levy}, $\nu$ is the L\`evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is \[\hat \mu(\theta)=\exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\}.\]
+	Finally,
+\begin{equation}\begin{split}
+    &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
+    = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}
+\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt)
+\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
+= \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)
+\\&\quad = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
+\qedhere
+\end{split}\end{equation}
+\end{proof}
+% added end
 \begin{prop}
@@
 \label{it: second stable}
-%    $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
-If $\alpha\beta=\kappa_f b(1+\beta)$,  $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
+\item
+\label{it: third stable}
+    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
 \end{enumerate}
-%\end{cor}
 \end{prop}
@@
 
-    The proofs of \eqref{it: second stable} is similar to that of \eqref{it: first stable}.
+    The proofs of \eqref{it: second stable} and \eqref{it: third stable}  is similar to that of \eqref{it: first stable}.
 \end{proof}
-
- For each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
-     %let
-%\begin{equation}\begin{split}
-%    m[f]
-%    :=\sum_{k=0}^\infty m_k[f]
- %   =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
-%\end{split}\end{equation}
-%According to \cite[Lemma 5.1]{MM}, $m[f]$
-%is well defined, i.e. $|m[f]|<\infty$.
-According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
-\begin{equation}\label{sum-m}
-m[f]
-    =\sum_{k=0}^\infty m_k[f]
-    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
-\end{equation}
-%\begin{cor}
-\begin{prop}
-	For all $t\geq 0$ and $f\in \mathcal P$ satisfying $\alpha\beta < \kappa_f b(1+\beta)$,
-    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-%\end{cor}
-\end{prop}
-\begin{proof}
-%Similar to the proof of corollary \ref{cor: alpha stable rv}.
-The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
-\end{proof}
-
 Recall that
@@
 \end{align}
-%For each $g\in \mathcal{C}_l$ expressed by
+
 For each $g\in \mathcal{C}_l$ we have the following expression:
     $$g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.$$
-%where $x\in \mathbb{R}^d$.
-%Let
+
 Also recall that the definition of $I_tg(x)$:
@@
 \end{align}
-%and define
 Define
@@
 \begin{lem}\label{lem: control of Isg}
- %There exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
  For each $g\in \mathcal{C}_l$, there exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
@@
 \begin{proof}
-%Let $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
 Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  Put  $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
@@
 \end{align}
-%therefore,
-%\begin{align}
-%   \bar{m}[g]=\sum_{n=1}^{\infty}\bar{m}_n[g].
-%\end{align}
 \begin{lem}\label{lem: control of mn}
-%There exists $C>0$ such that
 For each $g\in \mathcal{C}_l$,  there exists constant $C>0$ such that
@@
  \end{align}
-%Then $|\bar{m}[g]|<\infty$.
 which implies that
-\begin{equation}\label{sum-bar-m}\bar{m}[g]=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g]\end{equation}
+\begin{equation}\label{sum-bar-m}\bar{m}[g]:=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g]\end{equation}
 is well-defined.
@@
 By the fact that $\alpha\beta>K(1+\beta)b$, we easily get
-%$|\bar{m}[g]|<\infty$.
 $\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
 \end{proof}
-%\begin{cor}
 \begin{prop}
 \label{cor: alpha stable rv 1}
-%	For all $n\geq 0$ and $g\in \mathcal C_l$
-%expressed by \eqref{discompose},
 For any $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
@@
 \end{enumerate}
-%\end{cor}
 \end{prop}
 \begin{proof}
-%Similar to the proof of corollary \ref{cor: alpha stable rv}.
 The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
@@
 
-%\subsection{The large rate case.}
 \subsection{The large rate case: $\alpha \beta > \kappa_f b (1+\beta)$}
-%new added
 
 In this subsection, we prove Theorem \ref{Theorem11}. We will be back to the large branching rate case in Subsection \ref{large rate again} to prove Theorem \ref{theorem 1.6}.
-%end new
+
 To prove Theorem \ref{Theorem11}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family martingales for $\gamma\in (0, \beta)$.
@@
 \]
-%new added
 Moreover, letting $t\to\infty$ in above inequality, we have
@@
 \]
-%end new
 \end{lem}
@@
      Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-% According to Lemma \ref{lem: control of mgtrs},
 Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,
@@
 
-%\subsubsection{Proof of Theorem \ref{Theorem11}}.
 {\it Proof of Theorem \ref{Theorem11}.}\quad
@@
 	The proof is now completed.
-%\subsection{The critical rate case.}
+
 \subsection{The critical rate case: $\alpha\beta=\kappa_fb(1+\beta)$}
-First we introduce an criterion of $(1+\beta)$-stable distribution.
-\begin{lem}
-\label{lem: charactreisticfunction}
-    Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
-    Then $$\theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},\quad \theta \in \mathbb R^d$$
-    is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
+% new added
+\begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MM})
+    For each $f\in \mathcal{P}$, let
+    \begin{align}
+        g_k
+    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
+    \quad k \geq 0.
+    \end{align}
+    There exist $h\in \mathcal{P}$ such that
+    \begin{align}
+        |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
+    \end{align}
 \end{lem}
-\begin{proof}
-    From measure theory, there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
-\[
-    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
-    f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
-\]
-Recall the definition of $\Gamma$ function in \eqref{eq: definition of Gamma function}, and define another measure $\lambda_0$ on $S$ by
-\[
-    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi).
-\]
-    Then $\lambda_0$ is a non-zero finite measure, since
-\[
-    \lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt)
-    = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
-\]
-    Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
-\[
-    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
-\]
-    Then, according to \cite[Remark 14.4]{Sato1999Levy}, $\nu$ is the L\`evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is \[\hat \mu(\theta)=\exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\}.\]
-	Finally,
-\begin{equation}\begin{split}
-    &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
-    = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}
-\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt)
-\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
-= \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)
-\\&\quad = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
-\qedhere
-\end{split}\end{equation}
-\end{proof}
-%The following is moved forward
-%Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}.
-%    Define
-% \begin{equation}\begin{split}
- %\label{parameter_mk}
-  %    m_t[f]
-   %   :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
- %\end{split}\end{equation}
-  %  According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that
-%%\[
-%\begin{equation}\label{domi-m}
- %   |m_t[f]|
-  %  \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
-   % \quad t\geq 0.
-%%\]
-%\end{equation}
-%  %new added
-% Recall the definition of $\widetilde{m}$ in \eqref{tilde-m}.
-%  %end new
-%    According to \cite[Lemma 4.2]{MM}, if $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
-    %the following limit exists:
-%    we have
-%\begin{equation}\begin{split}
-%\label{para: critical case}
- %%   \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
- %\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle=\widetilde{m}[f],
-%\end{split}\end{equation}
- %   where
-%\[
- %   \phi
-%    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
-%\]
-%%\begin{cor}
-%\begin{prop}
-%\label{cor: alpha stable rv}
-%	For all $t\geq 0$ and $f\in \mathcal P$,
-%\begin{enumerate}
-%\item
-%\label{it: first stable}
- %$\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable;
- %\item
-%\label{it: second stable}
-%%    $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
-%If $\alpha\beta=\kappa_f b(1+\beta)$,  $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random %variable.
-%\end{enumerate}
-%%\end{cor}
-%\end{prop}
-%\begin{proof}
- %   \eqref{it: first stable}:
-	%Fix $t\geq 0$ and $f\in \mathcal P$.
-	%Note that $m_t[\theta f]$ can be rewritten as
-%\[
- %   m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
-  %  \quad \theta \in \mathbb R.
-%\]
-%	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
-%\begin{equation}
-%\label{eq: what I want to proof}
-%	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
-%\end{equation}
-%	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),  we know that
-%$
-%	g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds
-%$
-%	is a $(1+\beta)$-controllable operator on $\mathcal P$.
-%	This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
-%	Therefore \eqref{eq: what I want to proof} is true.
-
- %   The proofs of \eqref{it: second stable} is similar to that of \eqref{it: first stable}.
-%\end{proof}
-%end move
+% end new
 \begin{lem}\label{lem: mainlemma}
@@
 g_k
-    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)k}},
-    \quad k \in \mathbb Z_+.
-\]
-According to \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$ such that
-{\bf( Remark: State \cite[Lemma 2.8]{MM} as a Lemma in our paper)}
-\[
-     |P_t g_k|\leq e^{-bt}h,
-     \quad k\geq 0,t\geq 0.
-\]
-    This implies that
+    = \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)k}},
+    \quad k \geq 0.
+\]
+%According to \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$ such that
+%\[
+%     |P_t g_k|\leq e^{-bt}h,
+%     \quad k\geq 0,t\geq 0.
+%\]
+%   This implies that
+
+%new
+According to Lemma \ref{lem: control of gk}, we get there exists $h\in \mathcal{P}$ such that
+% new end
  \[
@@
 \begin{cor}\label{cor: used in next corollary}
-%Let $f\in \mathcal{P}$, $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-%Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
 Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq \kappa_fb(1+\beta)$.
@@
 \begin{prop}\label{corollary31}
-%Let $f\in \mathcal{P}$, and $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-%Assume that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then there exist $C,\delta>0$ such that
 Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then for any $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
@@
     \end{align*}
- %   According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary},
   According to Proposition \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary},
@@
 \bigskip
-%\subsubsection{Proof of Theorem \ref{Theorem12}}
-%\label{sec: proof of thm 1.3}
 
@@
         \\ &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big) +
-     %   \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
          \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
@@
     Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb R$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$
-    %in Corollary \ref{corollary31},
     in Proposition \ref{corollary31},
@@
     Therefore, we only need to prove
-  %   $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0$
  \begin{equation}\label{toprove-1}|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0,
@@
       and
-      %$I_i(t)\xrightarrow[t\to \infty]{d} 0$ for $i = 2,3$ under $\tilde {\mathbb P}_\mu$.
      \begin{equation}\label{toprove-2}
@@
 By \cite[Lemma 3.4.3]{Durrett2010Probability},
-%\begin{equation}\begin{split}\label{ineq: control of I1t}
 \begin{equation}\label{ineq: control of I1t}
@@
     \quad t\geq t_0,
-%\end{split}\end{equation}
 \end{equation}
@@
 
-%The following is moved forward
-% %    For each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
-     %let
-%%\begin{equation}\begin{split}
-%%    m[f]
-%%    :=\sum_{k=0}^\infty m_k[f]
- %%   =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
-%%\end{split}\end{equation}
-%%According to \cite[Lemma 5.1]{MM}, $m[f]$
-%%is well defined, i.e. $|m[f]|<\infty$.
-%According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
-%\begin{equation}\label{sum-m}
-%m[f]
-%    =\sum_{k=0}^\infty m_k[f]
-%    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
-%\end{equation}
-%\begin{cor}
-%\begin{prop}
-%	For all $t\geq 0$ and $f\in \mathcal P$ satisfying $\alpha\beta < \kappa_f b(1+\beta)$,
-%    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-%\end{cor}
-%\end{prop}
-%\begin{proof}
-%Similar to the proof of corollary \ref{cor: alpha stable rv}.
-%The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
-%\end{proof}
-
-%\subsubsection{Proof of Theorem \ref{Theorem13}}
 {\it Proof of Theorem \ref{Theorem13}.}\quad
-%	Let $f\in \mathcal P$ be such that $\alpha \beta < \kappa_f b(1+\beta)$.
+
 According to our assumption, $f\in \mathcal P$  is fixed  and  that $\alpha \beta < \kappa_f b(1+\beta)$.
@@
 \end{align*}
-%Hence, according to \eqref{msmallcase}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
 Hence, according to \eqref{sum-m}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
@@
 \end{align*}
-%Now we can use the same argument as in Step 3 in Section \ref{sec: proof of thm 1.3}
 Now we can  use the  same argument used in the proof of Theorem \ref{Theorem12}
@@
 	The proof is complete.
-%\subsection{Further results for large rate case.}
 \subsection{Proof of Theorem \ref{theorem 1.6}}\label{large rate again}
-%new added
 In this subsection, we are back to the large branching rate case, and aim to prove Theorem \ref{theorem 1.6}.
-%end new
-%The following is moved forward
-%Recall that
-%\begin{align}
- %  \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
-%\end{align}
-%and
-%\begin{align}
- %   \mathcal{C}_l=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
-%\end{align}
-%%For each $g\in \mathcal{C}_l$ expressed by
-%For each $g\in \mathcal{C}_l$ we have the following expression:
-%    $$g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.$$
-%%where $x\in \mathbb{R}^d$.
-%%Let
-%Also recall that the definition of $I_tg(x)$:
-%\begin{align}
- %   I_tg(x)=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
-%\end{align}
-%Define
-%\begin{align}
-%    K=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
-%\end{align}
-
-%\begin{lem}\label{lem: control of Isg}
-% %There exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
-% For each $g\in \mathcal{C}_l$, there exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
-%\begin{align}
- %   |I_tg(x)|\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
-%\end{align}
-%\end{lem}
-%\begin{proof}
-%%Let $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-%Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  Put  $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-%\begin{align}
- %   |I_tg(x)|=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|\leq e^{-(\alpha-Kb)t}h(x),\quad t\geq 0,x\in \mathbb{R}^d.
-%\end{align}
-%\end{proof}
-%For each  $n\geq 1$, let
-%\begin{align}
- %   \bar{m}_n[g]:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds.
-%\end{align}
-%%therefore,
-%%\begin{align}
-%%   \bar{m}[g]=\sum_{n=1}^{\infty}\bar{m}_n[g].
-%%\end{align}
-%\begin{lem}\label{lem: control of mn}
-%%There exists $C>0$ such that
-%For each $g\in \mathcal{C}_l$,  there exists constant $C>0$ such that
-% \begin{align}
-%     |\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1,
-% \end{align}
-%%Then $|\bar{m}[g]|<\infty$.
-%which implies that
-%\begin{equation}\label{sum-bar-m}\bar{m}[g]=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g]\end{equation}
-%is well-defined.
-%\end{lem}
-%\begin{proof}
-%Let $h$ be the control function in Lemma \ref{lem: control of Isg}.
-%\begin{align}
-%    &|\bar{m}_n[g]|\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
- %   &\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle
-%    \leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
-%\end{align}
-%By the fact that $\alpha\beta>K(1+\beta)b$, we easily get
-%%$|\bar{m}[g]|<\infty$.
-%$\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle %ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
-%\end{proof}
-%%\begin{cor}
-%\begin{prop}
-%\label{cor: alpha stable rv 1}
-%For any $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
-%\begin{enumerate}
-%\item
-%\label{it: first stable}
- %   $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable;
-%\item
-%\label{it: second stable}
-%    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-%\end{enumerate}
-%%\end{cor}
-%\end{prop}
-%\begin{proof}
-%The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
-%\end{proof}
-%end move
-%Moreover, by fubini's theorem, we get
+
+For each $g\in \mathcal{C}_l$, recall the definition of $I_tg$ in \eqref{definition of Itf}.
 By Fubini's theorem, we get
@@
 \end{align}
-\begin{comment}
-
-For each $p\in \mathbb{N}_0$ and $t\geq 0$, recall that $H ^p_t=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle$ is a martingale corresponding to the $\sigma$-algebra $\{\mathscr{F}_t\}_{t\geq 0}$.
-According to Lemma 2.8, we get
-\begin{align}
-    \lim_{u\rightarrow \infty}\langle I_ug,X_{t+u} \rangle=\sum_{k:\alpha\beta>k(1+\beta)b}e^{(\alpha-kb)t}\sum_{|p|=k}H_{\infty}^p, \quad \mathbb{P}_{\mu}\text{-a.s}.
-\end{align}
-\end{comment}
-
+%new added
+\begin{lem}\label{control of gn}
+    Let
+    \begin{align}
+        \bar{g}_t:=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0, g\in \mathcal{C}_l.
+    \end{align}
+    There exists $h\in \mathcal{P}$ such that
+    \begin{align}
+        |P_s\bar{g}_t|\leq e^{-bs}h,\quad s\geq 0, t\geq 0.
+    \end{align}
+\end{lem}
+\begin{proof}
+    Similar to the proof of \cite[Lemma 2.8]{MM}.
+\end{proof}
+% end new
 Recall that $\Big\{\{H^p_t, \mathscr{F}_t\}_{t\geq 0};p\in \mathbb{Z}_+^d\Big\}$ is a family of martingale defined in Lemma \ref{lemma26}.
@@
 \begin{proof}
-%We only have to show that
 We only need to show that
@@
 \end{align}
-%Let
 Put
 $\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
-%, we easily get
 We get that
@@
 	&\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}
-%[\langle g_p, X_{t+n-1}\rangle],
-[\langle g_n, X_{t+n-1}\rangle],
+[\langle \bar {g}_n, X_{t+n-1}\rangle],
 	\quad t\geq 0, n\geq 1,
 \end{align}
-where we set
-\begin{align}
-    g_n:=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
-\end{align}
-Similar to proof of \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$, such that
-\[
-     |T_t g_n|\leq e^{-bt}h,
-     \quad t\geq 0, n\geq 1.
-\]
-{\bf Remark: State the above result as a Lemma}
+where
+\begin{align}
+    \bar{g}_n:=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
+\end{align}
+%Similar to proof of \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$, such that
+%\[
+%     |P_t g_n|\leq e^{-bt}h,
+%     \quad t\geq 0, n\geq 1.
+%\]
+%{\bf Remark: State the above result as a Lemma}
  Choose $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
- %According to Lemma \ref{lem: control moment} (3) with $\kappa=1$,
- Using Lemma \ref{lem: control moment} (3) with $\kappa=1$,
+% Using  Lemma \ref{lem: control moment} (3) with $\kappa=1$,
+% there exists $C>0$ such that
+Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment} (3) with $\kappa=1$,
  there exists $C>0$ such that
 \begin{align}
-    \mathbb{P}_{\mu}[\langle g_n, X_{t+n-1}\rangle]\leq Ce^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
+    \mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]\leq Ce^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
 \end{align}
@@
 \begin{align}
-    &J'_2(t,n,\epsilon)\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle g_n, X_{t+n-1}\rangle]\\
+    &J'_2(t,n,\epsilon)\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]\\
     &\leq C e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)}\\
@@
 \end{align}
-	Step 4. %We will show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
-Using similar arguments in the proof of step 4 of Lemma \ref{lem: mainlemma}, we can show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
+	Step 4. Using similar arguments in the proof of step 4 of Lemma \ref{lem: mainlemma}, we can show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
 \begin{align}\label{ineq: control of J31}
@@
 \end{align}
-%	Similar to the proof of step 4 in Lemma \ref{lem: mainlemma}
-
-%	Final step, combine the result in Step 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$ convergence to $0$ exponentially fast while $t\rightarrow\infty$.
-%This gives the desired result.
-
 Finally, combining the results in steps 1-4.
@@
     \end{align*}
-    %According to step 1 and corollary \ref{cor: alpha stable rv 1}
    According to step 1 and Proposition \ref{cor: alpha stable rv 1},
@@
 \end{align}
-%Step 1. Similar to the proof of step 1 in section \ref{sec: proof of thm 1.3},
 
@@
 \end{comment}
-%Since $\eta_1 < \eta_0$,  Similar to the proof of step 2 in section \ref{sec: proof of thm 1.3},
+
 Since $\eta_1 < \eta_0$,  using similar arguments used in  step 2 of the proof of Theorem \ref{Theorem12},
@@
     We get \eqref{thm12211} since $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}<\eta_0-3\eta_1$ and $\alpha\gamma>Kb(1+\gamma)\geq |p|b(1+\gamma)$.
-\begin{comment}
-
- Step 3. We will show that there exist $C, \delta> 0$ such that
-    \begin{align}
-    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq Cm e^{-\delta t},\quad m\in \mathbb{N}, t\geq 0.
-    \end{align}
-\end{comment}
-
-  %  Combine \eqref{ineq: used next 3}, Step 1 and Step 2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
   Combinning \eqref{ineq: used next 3}, Steps 1-2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
 \end{proof}
-\begin{comment}
-
-Let
-\begin{align}
-    \gamma_t:=\frac{H_t^p-H_{\infty}^p}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}},\quad t\geq 0, p\in \mathbb{N}_0^d.
-\end{align}
-\end{comment}
 \begin{lem}\label{lem: lemma05}
@@
 \bigskip
-%\subsubsection{Proof of Theorem \ref{theorem 1.6}}
 
@@
 \end{align}
-%new addedd
 Also note that $\sum_{n=1}^\infty\bar{m}_n[\theta g]=\bar{m}[\theta g]$, see \eqref{sum-bar-m}.
-%end new
+
 Combining \eqref{decompose},\eqref{ineq: last1}, \eqref{ineq: last2} and \eqref{ineq: last3}, and letting $t\to\infty$, we get the desired result of Theorem \ref{theorem 1.6}.
@@
 
+\bibitem{ARMP}
+Adamczak, RR. Milo\'s, P.:
+\emph{CLT for Ornstein-Uhlenbeck branching particle system.}
+Electron. J. Probab. 20 (2015), no.42, 1-35.
+
+\bibitem{ASHH}
+Asmussen, S. Hering, H.:
+\emph{Branching Processes.}
+Birkh auser, Boston, 1983.
+
 \bibitem{BAM}
@@
 
+\bibitem{KBA1}
+Kyprianou, A. E.:
+\emph{Limit theorems for multitype continuous time Markov branching processes I: the case of an eigenvector linear functional.}
+Z. Wahrs. Verw. Gebiete 12 (1969), 320-332.
+
+\bibitem{KBA2}
+Kyprianou, A. E.:
+\emph{Limit theorems for multitype continuous time Markov branching processes II: the case of an arbitrary linear functional.}
+Z. Wahrs. Verw. Gebiete 12 (1969), 204-214.
+
+\bibitem{KBA3}
+Kyprianou, A. E.:
+\emph{Some redinements in the theory of supercritical multitype Markov branching processes.}
+Z. Wahrs. Verw. Gebiete 12 (1971), 47-57.
+
+\bibitem{HKBPS1}
+Kesten, H. Stigum, B. P.:
+\emph{A limit theorem for multidimensional Galton-Watson processes.}
+Ann. Math. Statist. 37 (1966), 1221-1223.
+
+\bibitem{HKBPS2}
+Kesten, H. Stigum, B. P.:
+\emph{Additional limit theorems for indecomposable multidimensional Galton-Watson processes.}
+Ann. Math. Statist. 37 (1966), 1463-1481.
+
 \bibitem{Li2011Measure-valued}
@@
 Linde, W.:
-\emph{Probability in Banach spaces—stable and infinitely divisible distributions.}
+\emph{Probability in Banach spaces-stable and infinitely divisible distributions.}
 Second edition. A Wiley-Interscience Publication. John Wiley \& Sons, Ltd., Chichester, 1986.
@@
 \bibitem{LiuRenSong2009Llog}
-Liu, R.-L., Ren, Y.-X. and Song, R.:
-\emph{{$LlogL$} criterion for a class of superdiffusions.}
-J. Appl. Probab. \textbf{46} (2009), no. 2, 479–496.
+Liu, R., Ren, Y.-X., Song, R.:
+\emph{{$L log L$} criterion for a class of Superdiffusions.}
+J. Appl. Probab. \textbf{46} (2009), no. 2, 479-496.
+
+\bibitem{MP2012}
+Milo\'s, P.:
+\emph{Spatial CLT for the supercritical Ornstein-Uhlenbeck superprocess.}
+Preprint, 2012. arXiv:1203:6661
 
 \bibitem{MM}
-Marks, R., Mil\'{o}s, P.:
-\newblock {\em CLT for supercritical branching processes with heavy-tailed branching law}.
-\ARXIV{1803.05491}
+Marks,R., Milo\'s, P.:
+\emph{CLT for supercritical branching processes with heavy-tailed branching law.}
+\ARXIV{183.05491}
 
 \bibitem{GD}
-Metafune,~G., Pallara,D.
-\newblock {\em Specturm of Ornstein-Uhlenbeck operators in $\mathcal{L}^p$ space with respect to invariant measures}. J. Funct. Anal. 196, 40-60(2002)
+Metafune,~G., Pallara, D.:
+\emph{Specturm of Ornstein-Uhlenbeck operators in $\mathcal{L}^p$ space with respect to invariant measures.}
+J. Funct. Anal. 196,40-60(2002)
 
@@
 Ren, Y.-X., Song, R., Zhang, R.:
-\newblock {\em Central limit theorems for super Ornstein-Uhlenbeck processes}, Acta Appl. Math. 130(2014)9-49.
+\emph{Central limit theorems for super Ornstein-Uhlenbeck processes.}
+Acta Appl. Math. 130(2014)9-49.
+
+\bibitem{RSZ1}
+Ren, Y.-X., Song, R., Zhang, R.:
+\emph{Central limit theorems for supercritical branching Markov processes.}
+J. Funct. Anal. 266(2014): 1716-1756.
+
+\bibitem{RSZ2}
+Ren, Y.-X., Song, R., Zhang, R.:
+\emph{Central limit theorems for supercritical superprocesses.}
+Stochastic Processes and Their Applications, 125(2015) 428-457.
+
+\bibitem{RSZ3}
+Ren, Y.-X., Song, R., Zhang, R.:
+\emph{Central limit theorems for supercritical branching nonsymmetric Markov processes.}
+Ann. Probab., 45(1)(2017): 564-623.
+
+\bibitem{RSZ4}
+Ren, Y.-X., Song, R., Zhang, R.:
+\emph{Functional central limit theorems for supercritical superprocesses.}
+Acta Applicandae Mathematicae 147(1)(2017): 137-175.
 
@@
 Ren, Y.-X., Song, R., Sun, Z.:
-\newblock{\em Spine decompositions and limit theorems for a class of critical superpeocesses,} arXiv preprint arXiv:1711.09188(2017).
+\emph{ Spine decompositions and limit theorems for a class of critical superpeocesses.}
+arXiv preprint arXiv: 1711. 09188(2017).
 
@@
 Sato, K.:
-\emph{Lévy processes and infinitely divisible distributions.}
+\emph{L\'evy proesses and infinitely divisible distributions.}
 Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.
@@
 \bibitem{SteinShakarchi2003Complex}
-Stein, E. M. and Shakarchi, Rami:
+Stein, E. M and Shakarchi, Rami.:
 \emph{Complex analysis.}
@@
 
-\bibitem{LSR}
-Liu, R.,  Ren, Y.-X., Song, R.:
-\emph{ L Log L Criterion for a Class of Superdiffusions.}
-Journal of Applied Probability, 46(2), 479-496. 2009.
-
 \end{thebibliography}

### 2019-01-31 supCLT.tex
supCLT.tex: 0127

@@
 %%----Versions-----------------------------
+% supCLT0127.tex 2018/01/27 by Yanxia
 % supCLT0124.tex 2018/01/24 by Jianjie
-% supCLT0109.tex 2018/01/14 by Yanxia
+% supCLT0114.tex 2018/01/14 by Yanxia
 % supCLT0107.tex 2018/01/07 by Jianjie
@@
 \end{equation}
- %new added
+
  In this paper, we will establish some spatial central limit theorems for the super-OU process with stable branching mechanism. Precisely, we want to find $F_t$ and $G_t$ such that
@@
 
- There are many papers studying central limit behavior for branching processes, branching diffusions and superprocesses.
+ There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses.
 See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes under some certain conditions.
@@
 In this two paper, Milo\'s with his coauthor pictured connection between CLT and what they call branching rate regimes.
-In \cite{RSZ}, Yanxia Ren, Renming Song and Rui Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
+In \cite{RSZ}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
 Moverover, Compare with the results in \cite{ARMP,MP2012}, the limit distributions in \cite{RSZ} are non-degenerate.
@@
  All the results described above hold for systems with branching mechanisms satisfying finite variance.
-It's a natural step to establish counterparts of the central limit theorems for super processes with infinite variance.
-In \cite{MM}, Marks and Milo\'s have considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
-They established some central limit theorems on the small and critical branching rate cases but no large rate case.
+It's a natural  to ask that how to establish counterparts of the central limit theorems for branching Markov processes and superprocesses with infinite variance.
+In \cite{MM}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
+They established some central limit theorems for small and critical branching rate cases,  but leave the central limit result unsolved for large rate case.
 In this paper, we consider a class of super-OU processes with more general stable branching mechanisms.
-On small and critical branching cases, we obtained similar central limit theorems.
-Moreover, on large rate case, we not only show an almost sure convergent result, but also establish the corresponding central limit theorem, which is not appeared in \cite{MM}.
-
- Except for the main results proved in section 4, there are some other significative results in our paper.
+For small and critical branching cases, we obtained central limit theorems which are similar to corresponding results for branching Ornstein-Uhlenbeck processes in Marks and Milo\'s \cite{MM}.
+For large rate case, we first establish  an almost sure convergent result, and then establish a central limit theorem, which has no corresponds in \cite{MM}.
+
+ %Except for the main results proved in section 4, there are some other significative results in our paper.
 In appendix, we show that the characteristic exponent of supercritical general super processes $U_t f(x)=-{\rm Log} \mathbb{P}_{\delta_x}e^{i\theta X_t(f)}$ can be defined by corresponding equation by using Spain Decomposition.
@@
 
- % end new
 \subsection{OU Semigroup}
@@
 For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$,
-%the value of the L\'evy exponent of the infinite divisible random variable
 the value of the characteristic exponent of the infinite divisible random variable
@@
 
-Further, for each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
-According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
-\begin{equation}\label{sum-m}
-m[f]
-    :=\sum_{k=0}^\infty m_k[f]
-    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
-\end{equation}
-% new added
-% I move ahead the follow lemma used in prop 2.6.
+%moved from below
+\begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MM})
+    For each $f\in \mathcal{P}$, let
+    \begin{align}
+        g_k
+    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
+    \quad k \geq 0.
+    \end{align}
+    There exist $h\in \mathcal{P}$ such that
+    \begin{align}
+        |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
+    \end{align}
+\end{lem}
+% end move
+%moved from below
+\begin{lem}\label{control of gn} Suppose that $g\in \mathcal{C}_l$.
+    Put
+    \begin{align}
+        \bar{g}_t:=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
+    \end{align}
+    There exists $h\in \mathcal{P}$ such that
+    \begin{align}
+        |P_s\bar{g}_t|\leq e^{-bs}h,\quad s\geq 0, t\geq 0.
+    \end{align}
+\end{lem}
+\begin{proof}
+    The proof  is similar to that of \cite[Lemma 2.8]{MM}.
+\end{proof}
+% end move
+
 Next lemma is an criterion of $(1+\beta)$-stable distribution.
+
 \begin{lem}
@@
 \end{proof}
-% added end
+
+For each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
+According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
+\begin{equation}\label{sum-m}
+m[f]
+    :=\sum_{k=0}^\infty m_k[f]
+    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
+\end{equation}
+
 \begin{prop}
@@
 \section{Tail probability}
-In this section, we will introduce a small value probability result of supercritical continuous-state branching process with general branching mechanism and %control
+In this section, we will introduce a small value probability result of supercritical continuous-state branching process with general branching mechanism and
 $(1+\gamma)$-moments for the super-OU process. These will be needed to prove our main results.
@@
     In this subsection, we digress briefly from super-OU process and consider a supercritical continuous-state branching process (CSBP)
-    %$(Y_t)$.
         $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
-    Our goal is to determing how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
-  %  Let branching mechanism corresponding to the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ be denoted as
-  %\[
-  %  \psi(z)
-  %  := -\alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z\geq 0,
-  %\]
-  %  where $\alpha > 0$, $\rho \geq 0$ and $\pi$ is a measure on $(0,\infty)$ satisfying $\int_{(0,\infty)} (y \wedge y^2) \pi(dy) < \infty$.
+    Our goal is to determining how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
    Assume that the branching mechanism of the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is given by \eqref{mechanism}.
@@
 Fix this $z_0$.
-    %For $t$ large enough, according to \eqref{CSBP: int} and the fact that $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$, we can verify the following:
     For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$. Then  using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have
@@
     \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    %\leq \frac{ C}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa b)+ \alpha r},
        \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg).
 \]
-    %where $Q_kg$ is defined by \eqref{Q_k} with $f$ replaced by $g$.
    \end{lem}
@@
     &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    % k is replaced by l to avoide confusing between k and \kappa.
         \\ &\leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
@@
 \end{proof}
+
 \section{Proof of main results}
+
 In this section, we will prove the main results of this paper.
@@
 \subsection{The critical rate case: $\alpha\beta=\kappa_fb(1+\beta)$}
-% new added
-\begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MM})
-    For each $f\in \mathcal{P}$, let
-    \begin{align}
-        g_k
-    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
-    \quad k \geq 0.
-    \end{align}
-    There exist $h\in \mathcal{P}$ such that
-    \begin{align}
-        |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
-    \end{align}
-\end{lem}
-% end new
+
 \begin{lem}\label{lem: mainlemma}
@@
 \end{split}\end{equation}
-    %From Corollary \ref{cor: alpha stable rv}, we have
        From Proposition \ref{cor: alpha stable rv}, we have
@@
 \]
-%According to \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$ such that
-%\[
-%     |P_t g_k|\leq e^{-bt}h,
-%     \quad k\geq 0,t\geq 0.
-%\]
-%   This implies that
-
-%new
 According to Lemma \ref{lem: control of gk}, we get there exists $h\in \mathcal{P}$ such that
-% new end
  \[
@@
 Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq \kappa_fb(1+\beta)$.
-%Then
 Then for any $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
@@
     Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
-    %Fix $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb R^{n+1}$
         Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$
@@
     there exist $C,\delta>0$ such that for any
-    % $k\in\{0,1,...,n\}$, we have
         $k\in\{0, 1, \cdots, n\}$, we have
@@
 {\it Proof of Theorem \ref{Theorem12}.}\quad
-  %  Fix $f\in\mathcal{P}$.
     According to our assumption, $f\in\mathcal{P}$ is fixed and that  $\alpha\beta=\kappa_fb(1+\beta)$.
@@
 	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{Theorem12}.
-%\subsection{The small rate case.}
+
 \subsection{The small rate case: $\alpha\beta<\kappa_fb(1+\beta)$}
+ In this subsection, we prove the central limit theorem for the small rate case.
 
 {\it Proof of Theorem \ref{Theorem13}.}\quad
-
 According to our assumption, $f\in \mathcal P$  is fixed  and  that $\alpha \beta < \kappa_f b(1+\beta)$.
@@
 \end{align}
-%new added
-\begin{lem}\label{control of gn}
-    Let
-    \begin{align}
-        \bar{g}_t:=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0, g\in \mathcal{C}_l.
-    \end{align}
-    There exists $h\in \mathcal{P}$ such that
-    \begin{align}
-        |P_s\bar{g}_t|\leq e^{-bs}h,\quad s\geq 0, t\geq 0.
-    \end{align}
-\end{lem}
-\begin{proof}
-    Similar to the proof of \cite[Lemma 2.8]{MM}.
-\end{proof}
-% end new
+
 Recall that $\Big\{\{H^p_t, \mathscr{F}_t\}_{t\geq 0};p\in \mathbb{Z}_+^d\Big\}$ is a family of martingale defined in Lemma \ref{lemma26}.
@@
 \end{align}
-%Similar to proof of \cite[Lemma 2.8]{MM}, there exists $h \in \mathcal P$, such that
-%\[
-%     |P_t g_n|\leq e^{-bt}h,
-%     \quad t\geq 0, n\geq 1.
-%\]
-%{\bf Remark: State the above result as a Lemma}
- Choose $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-% Using  Lemma \ref{lem: control moment} (3) with $\kappa=1$,
-% there exists $C>0$ such that
 Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment} (3) with $\kappa=1$,
@@
 \begin{equation}
-   % P_t^\alpha f(x)
        P_t^\alpha f(x)
@@
     =\mathbf P_{\mu}[X_t(f)]=
-    %\mu(P^\alpha_t f).
        \mu(P^\alpha_t f).
@@
     \leq C P^\alpha_t |f|(x)+
-    %C_2 P^\alpha_t |f| (x)^2.
          C (P^\alpha_t |f| (x))^2.
@@
     \leq \mathbb N_x[|i W_t(f)|]
- %   \leq (P^\alpha_t |f|)(x).
      \leq (P^\alpha_t |f|)(x).
@@
     \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta|
-    %\leq (P^\alpha_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
         \leq (P^\alpha_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
@@
     \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
-    %\leq ( P^\alpha_t |f|)(x).
          \leq ( P^\alpha_t |f|)(x).
@@
 \\ &\leq \|\alpha\|_\infty + 2\|\rho\|_\infty
-% P^\alpha_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\alpha_t |f|(x)
   P^\alpha_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\alpha_t |f|(x)
   + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
-%\\ &=: C_1 + C_2(P^\alpha_t |f|)(x),
  \\ &=: C_1 + C_2(P^\alpha_t |f|)(x),
@@
     U_tf(x) -  \int_0^t P_{t-s}^{\alpha} \psi_0\big(\cdot,-U_sf\big) (x)~ds
-   % \\= iP_t^\alpha f(x).
       \\= iP_t^\alpha f(x).

### 2019-01-31 supCLT.tex
supCLT.tex: 0128

@@
 %%----Versions-----------------------------
+% supCLT0128.tex 2018/01/28 by Renming
 % supCLT0127.tex 2018/01/27 by Yanxia
@@
  %   {CLT for Super-OU Processes with stable Branching}
- {Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with Stable Branching}
+% {Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with Stable Branching}
+{Stable Central Limit Theorems for Super OU Processes with Stable Branching}
 \author
@@
 \thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
+%new
+\address
+{Renming Sond\\
+Department of Mathematics\\
+University of Illinois of Illinois at Urbana-Champaign\\
+Urbana, IL 61801, USA}
+\email{rsong@illinois.edu}
+\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
+%end new
 \address
@@
 \email{zhaojianjie@pku.edu.cn}
+\begin{abstract}
+ Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, 
+ where $\alpha >0$ and $\beta\in (0,1)$ and 
+% that there exists $C >0$ and $\delta >0$ such that
+$psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
+$
+    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).
+$
+    For each testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
+    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
+    In the small branching rate case  $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
+    In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
+ In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$,
+we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$,
+and then established a central limit theorem, 
+%which say that after proper centering and scaling, we get a $(1+\beta)$-stable random variable again.
+which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges
+weakly to a $(1+\beta)$-stable random variable.
+\end{abstract}
 %\begin{abstract}
@@
 %---Contents-----------------------
-\begin{abstract}
-    %Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$.
-    Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, where $\alpha >0$ and $\beta\in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
-$
-    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).
-$
-    For each testing function $f$ of at most polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
-    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
-    %In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
-    In the small branching rate case  $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
-    %In the critical branching rate case,  $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.
-    In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
-    In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$,
-    %new added
-    we first prove that
-    %end new
-    $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$,
-    %new added
-   and then established a central limit theorem, which say that after proper centering and scaling, we get a $(1+\beta)$-stable random variable again.
-    %end new
-\end{abstract}
+
+%\maketitle
+%\end{abstract}
 %\subjclass[2010]{60J80, 60F05}
@@
 %\date{}
-\maketitle
+
 \section{Introduction}
@@
 \end{equation}
-    %where $a>0$ and $b>0$ are constants.
     where $\sigma$ and $b$ are positive constants.
@@
        \psi(z)=
-    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy).
+    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
     \quad  z \in \mathbb R_+,
 \end{equation}
-	%where $\alpha > 0$ and $\beta \in (0,1) $ are constants.
 	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
-    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-%added%
-    Denote by $\mathcal B(\mathbb R^d)$ the space of all real-valued Borel measurable functions on $\mathbb R^d$.
-%%end added%
-	%For all Borel function $f$ and Borel measure $\mu$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
-	For each $f\in \mathcal B(\mathbb R^d)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
-    Put $\|\mu\|=\langle 1,\mu\rangle$.
+%    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
+%    Denote by $\mathcal B(\mathbb R^d)$ the space of all real-valued Borel measurable functions on $\mathbb R^d$.
+We use $B(\mathbb R^d, \mathbb R)$ to denote   the space of all real-valued Borel measurable functions on $\mathbb R^d$ and use $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
+	For $f\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, we write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
+ We aslo use the notation $\|\mu\|=\langle 1,\mu\rangle$. For $f, g\in \mathcal B(\mathbb R^d, \mathbb R)$, we also write $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
 
@@
 \end{equation}	
-    The existence of superprocesses are well known, see \cite{Dynkin1993Superprocesses} for instance.
+    The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.
 
@@
 \]
-    where $\eta > 0$, $\gamma \in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
+%    where $\eta > 0$, $\gamma \in (0,1)$ and 
+   where $\alpha>0$, $\eta > 0$, $\beta \in (0,1)$ and 
+    %that there exists $C >0$ and $\delta >0$ such that
+    and $\psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
 \[
@@
 there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-    Also, $\psi$ satisfies the $L \log L$ critierion  i.e.
+    Also, $\psi$ satisfies the $L \log L$ criterion  i.e.,
 \[
@@
 }
-    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
+    According to \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations}, we have
 \begin{equation}
@@
 
- In this paper, we will establish some spatial central limit theorems for the super-OU process with stable branching mechanism. Precisely, we want to find $F_t$ and $G_t$ such that
+ In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
  $$\frac{\langle f, X_t \rangle -G_t}{F_t}$$ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$.
-It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition.
+It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral
+ %decomposition.
+ decomposition in terms of the spectrum of $L$.
 
  There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses.
-See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes under some certain conditions.
-In \cite{ARMP}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{MP2012} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a forth moment condition.
-In this two paper, Milo\'s with his coauthor pictured connection between CLT and what they call branching rate regimes.
+See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes
+% under some certain conditions. 
+ under certain conditions. 
+ In \cite{ARMP}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{MP2012} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+% In this two paper, Milo\'s with his coauthor pictured connection 
+These two papers made connections
+ between CLT and what they call branching rate regimes.
 In \cite{RSZ}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
-Moverover, Compare with the results in \cite{ARMP,MP2012}, the limit distributions in \cite{RSZ} are non-degenerate.
-In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, They also establish a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
-
- All the results described above hold for systems with branching mechanisms satisfying finite variance.
-It's a natural  to ask that how to establish counterparts of the central limit theorems for branching Markov processes and superprocesses with infinite variance.
+% Moverover, Compare with the results in \cite{ARMP,MP2012}, 
+ Moverover, compared with the results in \cite{ARMP,MP2012}, 
+ the limit distributions in \cite{RSZ} are non-degenerate. 
+% In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, They also establish 
+ In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, Ren, Song and Zhang also established
+ a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
+
+ All the results described above hold for systems with branching mechanisms with finite variance. %It's a natural  to ask that how to establish 
+It is natural to ask whether there are 
+counterparts of the central limit theorems for branching Markov processes and superprocesses %with infinite variance.  
+with branching mechanisms of infinite variance.
  In \cite{MM}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
-They established some central limit theorems for small and critical branching rate cases,  but leave the central limit result unsolved for large rate case.
+They established some central limit theorems in small and critical branching rate cases,
+%but leave the central limit result unsolved for large rate case. 
+but \cite{MM} contained no central limit result in the branching rate case.
 In this paper, we consider a class of super-OU processes with more general stable branching mechanisms.
-For small and critical branching cases, we obtained central limit theorems which are similar to corresponding results for branching Ornstein-Uhlenbeck processes in Marks and Milo\'s \cite{MM}.
-For large rate case, we first establish  an almost sure convergent result, and then establish a central limit theorem, which has no corresponds in \cite{MM}.
-
- %Except for the main results proved in section 4, there are some other significative results in our paper.
-In appendix, we show that the characteristic exponent of supercritical general super processes $U_t f(x)=-{\rm Log} \mathbb{P}_{\delta_x}e^{i\theta X_t(f)}$ can be defined by corresponding equation by using Spain Decomposition.
-In section 3, we establish a small value probability estimation of supercritical continuous-state branching processes with branching mechanism satisfying Grey's condition and $L\log L$ critierion.
-This all results are necessary for us to prove the central limit theorems.
+For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MM}.
+For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit
+%theorem, which has no corresponds in \cite{MM}.
+theorem, which has no counterpart in \cite{MM}.
 
 \subsection{OU Semigroup}
-    In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
+   In this subsection, we recall 
+%   some results on the spectral properties of the OU operator $L$ from \cite{GD}.
+   some spectral properties of the OU operator $L$ from \cite{GD}.
     Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
@@
 \end{equation}
-    It is known that $(P_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
+    It is known that $(P_t)$ is a strongly continuous semigroup in $L^2(\varphi)$ and $L$ has
     discrete spectrum $a(L)= \{-bk: k \in \mathbb Z_+\}$.
@@
 \end{equation}
-    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
+    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete 
+    %orthogonal basis for $L^2(\varphi)$.
+    orthonormal basis for $L^2(\varphi)$.
     Thus, for each $f\in L^2(\varphi)$,
@@
 \end{equation}
-    the order of the function $f$ in $L^2(\varphi)$.
+%    the order of the function $f$ in $L^2(\varphi)$.
+   the order of the function in spectral decomposition \eqref{semicomp1}.
     Note that $ \kappa_f\geq 0$.
@@
 We will use $\mathcal M_c(\mathbb R^d)$ to denote the space of all
-finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of super-OU process.
+finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of the super-OU process.
 In this subsection, we will give the main results of this paper.
-\subsubsection{Large branching rate}
+%new
+The results are stated in three separate cases: the large branching rate case,
+critical  branching rate case and small  branching rate case.
+%end new
+
+\subsubsection{Large branching rate case}
 
@@
 $$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
-  For all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
-  under the condition
-   $\alpha\beta>|p|b(1+\beta)$,
+%  For all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
+%  under the condition
+%   $\alpha\beta>|p|b(1+\beta)$,
+If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
    $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
@@
      If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for
-any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$,
+all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
      as $t\rightarrow \infty$,
      $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$
-
 Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
@@
 Let $f \in \mathcal{P}$.  If $\kappa_f=0$,
-    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},
-for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
+    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f, 1\rangle_\phi=\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},
+for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
      $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$
@@
 
-\subsubsection{Critical branching rate}
-    For $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
+\subsubsection{Critical branching rate case}
+    For $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, we define
 \begin{equation}\label{tilde-m}
     \widetilde{m}[f]
-    := \langle \eta (-i\phi)^{1+\beta},\varphi\rangle
+%    := \langle \eta (-i\phi)^{1+\beta},\varphi\rangle
+    := \langle \eta (-if_0)^{1+\beta},\varphi\rangle
 \end{equation}
     where
-\[
-    \phi(x)
+%\[
+\begin{equation}\label{phif}
+%    \phi(x)
+    f_0(x)
     =\sum_{|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x).
-\]
+%\]
+\end{equation}
 
@@
     =\exp(\widetilde{m}[\theta f]),
-    \quad \theta\in \mathbb R,
-\]
-where $\widetilde{m}$ is defined by \eqref{tilde-m}.
+%    \quad \theta\in \mathbb R,
+   \quad \theta\in \mathbb R.
+\]
+%where $\widetilde{m}$ is defined by \eqref{tilde-m}.
 \end{thm}
 
-\subsubsection{Small branching rate}
-
-For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_f b(1+\beta)$, define
+\subsubsection{Small branching rate case}
+
+For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_f b(1+\beta)$, we define
 \begin{equation}
      m[f]
-    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds, \label{msmallcase}
-\end{equation}
-According to Lemmd \ref{Lemma2.7} below, $m[f]$ is well-defined.
+    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds. \label{msmallcase}
+\end{equation}
+According to Lemma \ref{Lemma2.7} below, $m[f]$ is well-defined.
 \begin{thm}
@@
     where $\zeta$ is a $(1+\beta)$-stable random variable with
-    $$\mathbb{E} [e^{i\theta \zeta}]=\exp(m[\theta f]), \quad \theta\in \mathbb R,$$
-    where $m$ is defined by \eqref{msmallcase}.
+    $$\mathbb{E} [e^{i\theta \zeta}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
+%    where $m$ is defined by \eqref{msmallcase}.
 \end{thm}
@@
 \begin{align}
-   \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
+   \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
 \end{align}
@@
 \end{align}
-For each fixed $f\in \mathcal{C}_l$, $f$ can be expressed as
+%For each fixed $f\in \mathcal{C}_l$, $f$ can be expressed as
+Each $f\in \mathcal{C}_l$ can be expressed as
 \begin{align}\label{discompose}
@@
 \end{align}
-It is easy to get that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$.
+It is easy to see that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$.
 
@@
 \end{align}
-According to Lemma \ref{lem: control of mn} in Subsection 4, $\bar{m}[f]$ is well-defined.
+According to Lemma \ref{lem: control of mn} below, $\bar{m}[f]$ is well-defined.
 \begin{thm}\label{theorem 1.6}
-For each $f\in\mathcal{C}_l$ expressed by \eqref{discompose} and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$ it holds that, as $t\to\infty$,
+For $f\in\mathcal{C}_l$ given by \eqref{discompose} and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that, as $t\to\infty$,
 \begin{align}\label{thm: large rate}
@@
 \begin{align}
-    \mathbb{E}[e^{i\theta\bar{\zeta}}]=\exp[\bar{m}[\theta f]],\quad \theta\in \mathbb{R},
-\end{align}
-where $\bar{m}$ is defined by \eqref{bar-m}.
+    \mathbb{E}[e^{i\theta\bar{\zeta}}]=\exp[\bar{m}[\theta f]],\quad \theta\in \mathbb{R}.
+\end{align}
+%where $\bar{m}$ is defined by \eqref{bar-m}.
 \end{thm}
 
+%RS We should collect our commonly used notation at the end of this section.
+
 \section{Preliminaries}
-\subsection{Definition of $h$-controller}
+%\subsection{Definition of $h$-controller}
+\subsection{Definition of controller}
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
-    For each function $h: [0,\infty) \to [0,\infty)$, we say an operator $R$ is an $h$-controller if
+    For any function $h: [0,\infty) \to [0,\infty)$, we say an operator 
+%   $R$ is an $h$-controller if
+ $R: \mathcal P^+ \to \mathcal P^+$  is an $h$-controller if
 \begin{itemize}
-\item
-    $R: \mathcal P^+ \to \mathcal P^+$;
-\item
-    $f, g\in \mathcal P^+$ and $f\leq g$ implies that $Rf \leq Rg$; and
-\item
-    $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ implies that $ R (\theta f)\leq h(\theta) Rf$.
+%\item
+%    $R: \mathcal P^+ \to \mathcal P^+$;
+\item
+%    $f, g\in \mathcal P^+$ and $f\leq g$ implies that $Rf \leq Rg$; and
+   $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and
+\item
+    $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ 
+%    implies that $ R (\theta f)\leq h(\theta) Rf$.
+    imply that $ R (\theta f)\leq h(\theta) Rf$.
 \end{itemize}
-    For each function $h: [0,\infty) \to [0,\infty)$ and $\mathcal D \subset \mathcal P^*$, we say $A$ is an \emph{$h$-controllable} operator on $\mathcal D$ if
-\begin{itemize}
-\item
-    $A : \mathcal D \to \mathcal P^*$;
-\item
-    There exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
-\end{itemize}
-    We also say operator $A$ is \emph{$h$-controlled by $R$ on $\mathcal D$} in this case.
-    We say a family of operators $(A_s)_{s\in \Lambda}$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by operator $R$ on $\mathcal D$.
-    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
-    For any $a \in \mathbb R$, suppose that $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
+
+    For any function $h: [0,\infty) \to [0,\infty)$ and $\mathcal D \subset \mathcal P^*$, 
+%    we say $A$ is an \emph{$h$-controllable} operator on $\mathcal D$ if
+we say that $A : \mathcal D \to \mathcal P^*$ is an \emph{$h$-controllable} operator on $\mathcal D$ if
+%\begin{itemize}
+%\item
+%    $A : \mathcal D \to \mathcal P^*$;
+%\item
+%    There exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
+%\end{itemize}
+there exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
+    We also say the operator $A$ is \emph{$h$-controlled by $R$ on $\mathcal D$} in this case.
+
+%    We say a family of operators $(A_s)_{s\in \Lambda}$
+   We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$
+     is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
+
+    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, we define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
+
+%    For any $a \in \mathbb R$, suppose that 
+    For any $a \in \mathbb R$ and any operator
+    $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, we define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
 
@@
     and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
-    For any probability measure $\nu$ on $(\Lambda, \mathscr F)$, write
+    For any probability measure $\nu$ on $(\Lambda, \mathscr F)$,  we write
 \[
@@
 \item[(4)]
-    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal B(\mathbb R^d, \mathbb C_+)$.
+    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
     Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable.
@@
     (2). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by  an $h$-controller $R_A$ on $\mathcal D$.
-    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by $g$-controller $R_B$ on $\mathcal D_0$.
-    We verify the following:
+    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D_0$.
+%    We verify the following:
+Then we have
 \begin{itemize}
@@
     Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
-
-    We verify the following:
+%
+%    We verify the following:
+Then we have
 \begin{itemize}
@@
 
-    We also verify the following:
+%    We also verify the following:
+    We also have the following:
 \begin{itemize}
@@
     (4). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
-    We verify the following:
+%    We verify the following:
+then we have the following:
 \begin{itemize}
@@
 
-\subsection{h-controller  for super-OU process.}
-Let $X$ be the super-OU process introduced in Subsection 1.1. Write $\psi_0(z)=\psi(z)+\alpha z$, for each $z\in \mathbb{C}_+$, and define operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$ by
+\subsection{h-controller  for super-OU processes}
+Let $X$ be the super-OU process introduced in Subsection 1.1.
+We define $\psi_0(z)=\psi(z)+\alpha z$, $z\in \mathbb{C}_+$, and define the following operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$:
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$,
-the value of the characteristic exponent of the infinite divisible random variable
+For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, 
+%recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$,
+let $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$ be 
+the value of the characteristic exponent of the infinitely divisible random variable
 $\langle f, X_t\rangle$ at $1$.
@@
 \end{split}\end{equation}
-If let
+If we  let
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-    Then we have that
+    then we have that
 \[
@@
 \begin{proof}
-    (1). According to \eqref{eq: -v has positive real part}, $U_t: \mathcal P \to \mathcal B(\mathbb R^d, \mathbb C_+)$.
+    (1). According to \eqref{eq: -v has positive real part}, 
+%    $U_t: \mathcal P \to \mathcal B(\mathbb R^d, \mathbb C_+)$.
+   $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
     It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
@@
 
-    (3). Let $C>0$ and $\delta > 0$ be the constant in Assumption \ref{asp: branching mechanism}.
+    (3). Let $C>0$ and $\delta > 0$ be the constants in Assumption \ref{asp: branching mechanism}.
     For each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
@@
     \leq \eta |f|^{1+\beta} + |\Psi_1 f|
-    \leq \eta |f|^{1+\beta} + C|f|^2+ C|f|^{1+\beta + \delta}
+    \leq \eta |f|^{1+\beta} + C|f|^2+ C|f|^{1+\beta + \delta}.
 \end{split}\end{equation}
@@
 
-    (4). From (1), (2), (3) and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
+%    (4). From (1), (2), (3) 
+        (4). From parts (1)--(3) of this lemma 
+    and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
 \[
@@
 \]
-    Now using (1), (2), (4) and Lemma \ref{lem: property of controllable operators}.(3)-(4), we get that
+%    Now using (1), (2), (4) 
+   Now using parts (1), (2) and  (4) of this lemma, 
+    and Lemma \ref{lem: property of controllable operators}.(3)--(4), we get that
 \[
@@
 
-    (6). Suppose that $C>0, \delta>0$ are constants in Assumption \ref{asp: branching mechanism}.
+    (6). Suppose that $C>0, \delta>0$ are the constants in Assumption \ref{asp: branching mechanism}.
     Noticing that
@@
     is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllor, we have that $\Psi_1$ is $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-    According to this, (1), (2), and Lemma \ref{lem: property of controllable operators} (1)-(2), we have that
+    According to this, parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we have that
 \[
@@
 
-(7). Since $K_t = (Z'_t-Z_t)+Z''_t$, we get the desired result from (5), (6), Lemma \ref{lem: property of controllable operators}(3).
+(7). Since $K_t = (Z'_t-Z_t)+Z''_t$, we get the desired result from parts (5) and  (6) of this lemma,  and Lemma \ref{lem: property of controllable operators}.(3).
 \end{proof}
@@
 
- We first collect some lemmas of \cite{MM}, which will be used in this paper.
+ We first collect some lemmas from \cite{MM}, which will be used in this paper.
  \begin{lem}(\cite[Lemma 2.7]{MM})\label{Lemma2.7} For each $f\in\mathcal{P}$, there is a constant $C>0$ such that
@@
     If $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
-    we have
+    then
 \begin{equation}\begin{split}
 \label{para: critical case}
- \widetilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
-\end{split}\end{equation}
-    where
-\[
-    \phi
-    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
-\]
+% \widetilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
+\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=
+ \widetilde{m}[f].
+\end{split}\end{equation}
+%    where
+%\[
+%    \phi
+%    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
+%\]
 \end{lem}
 
-%moved from below
 \begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MM})
@@
     \end{align}
-    There exist $h\in \mathcal{P}$ such that
+    Then there exists $h\in \mathcal{P}$ such that
     \begin{align}
@@
 \end{lem}
-% end move
-%moved from below
+
 \begin{lem}\label{control of gn} Suppose that $g\in \mathcal{C}_l$.
@@
     \end{align}
-    There exists $h\in \mathcal{P}$ such that
+    Then there exists $h\in \mathcal{P}$ such that
     \begin{align}
@@
 \end{proof}
-% end move
-
-Next lemma is an criterion of $(1+\beta)$-stable distribution.
+
+The next lemma is a criterion of $(1+\beta)$-stable distribution.
 
@@
 \begin{proof}
-    From measure theory, there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
+%    From measure theory, 
+It follows from measure theory that
+    there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
 \[
@@
 \]
-Recall the definition of $\Gamma$ function in \eqref{eq: definition of Gamma function}, and define another measure $\lambda_0$ on $S$ by
-\[
-    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi).
-\]
+%Recall the definition of $\Gamma$ function in \eqref{eq: definition of Gamma function}, and define another measure $\lambda_0$ on $S$ by
+We define another measure $\lambda_0$ on $S$ by
+\[
+    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi)
+\]
+where $\Gamma$ is the $\Gamma$ function, see eqref{eq: definition of Gamma function}.
     Then $\lambda_0$ is a non-zero finite measure, since
@@
 
-For each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
-According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
+For  $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
+according to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  thus
 \begin{equation}\label{sum-m}
@@
 \label{it: first stable}
-    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable;
+    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
 \item
 \label{it: second stable}
-    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
+    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
 \item
 \label{it: third stable}
-    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
+    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
 \end{enumerate}
@@
 \[
-    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
+    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)
+%    \int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
+   \int_0^1 P_{1-s}^\alpha \left(\eta(-i\theta P_{s+t}^\alpha f)^{1+\beta}\right)(x)~ds,
     \quad \theta \in \mathbb R.
@@
 
-    The proofs of \eqref{it: second stable} and \eqref{it: third stable}  is similar to that of \eqref{it: first stable}.
+    The proofs of \eqref{it: second stable} and \eqref{it: third stable} are similar to that of \eqref{it: first stable}.
 \end{proof}
@@
 \begin{align}
-   \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
+   \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
 \end{align}
@@
     $$g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.$$
-
-Also recall that the definition of $I_tg(x)$:
+%Also recall that the definition of $I_tg(x)$:
+Also recall that $I_tg(x)$ is defined by
 \begin{align}
@@
 \begin{proof}
-Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  Put  $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
+Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  Put  $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$. Then
 \begin{align}
@@
 \begin{proof}
-Let $h$ be the control function in Lemma \ref{lem: control of Isg}.
+Let $h$ be the function in Lemma \ref{lem: control of Isg}. Then
 \begin{align}
@@
 \end{align}
-By the fact that $\alpha\beta>K(1+\beta)b$, we easily get
+Using  the fact that $\alpha\beta>K(1+\beta)b$, we easily get
 $\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
@@
 \label{cor: alpha stable rv 1}
-For any $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
+For all $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
 \begin{enumerate}
 \item
-\label{it: first stable}
-    $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable;
-\item
-\label{it: second stable}
-    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+\label{it: first stableb}
+    $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
+\item
+\label{it: second stableb}
+    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable.
 \end{enumerate}
@@
 
-\section{Tail probability}
-In this section, we will introduce a small value probability result of supercritical continuous-state branching process with general branching mechanism and
-$(1+\gamma)$-moments for the super-OU process. These will be needed to prove our main results.
+%\section{Tail probability}
+\section{Preliminary results}
+
+In this section, we will give a small value probability result for supercritical continuous-state branching processes with general branching mechanisms and
+%$(1+\gamma)$-moments for the super-OU process. 
+give some estimates on the $(1+\gamma)$-moments for our super-OU process.
+These will be needed to prove our main results.
 
 \subsection{Small value probability}
-    In this subsection, we digress briefly from super-OU process and consider a supercritical continuous-state branching process (CSBP)
+    In this subsection, we digress briefly from our super-OU process and consider a supercritical continuous-state branching process (CSBP)
         $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
-    Our goal is to determining how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
-   Assume that the branching mechanism of the CSBP $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is given by \eqref{mechanism}.
-    Suppose that the Grey's condition is satisfied, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-    Also suppose that the $L \log L$ critierion is satisfied, i.e.
+    Our goal is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ 
+%    convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
+   converges to $0$, where $k_t \to 0$ as $t\to \infty$.
+   Assume that the branching mechanism of  $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is given by \eqref{mechanism}.
+    Suppose that Grey's condition is satisfied, i.e., there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+    Also suppose that the $L \log L$ critierion is satisfied, i.e.,
 \[
@@
 \]
-    Write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
+    We write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
 \begin{prop}
 \label{lem: control of XT}
-    Suppose that $t\mapsto k_t$ is a strictly positive map on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
+    Suppose that $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
     Then, for each $x\geq 0$, there are constants $C,\delta>0$ such that
@@
     Step 1. We recall some known facts about the CSBP $(Y_t)$.
-    For each $\lambda \geq 0$, denote by $t\mapsto v_t(\lambda)$ the unique positive solution of
+    For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of
 \[
@@
 \]
-    Taking $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
+    letting $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
 \begin{equation}
@@
 \end{equation}
-    It is known, see \cite[Theorem 3.5-3.8]{Li2011Measure-valued} for example, that under the Grey's condition, the following statements are true:
+    It is known, see \cite[Theorem 3.5-3.8]{Li2011Measure-valued} for example, that under Grey's condition, the following statements are true:
 \begin{itemize}
@@
 \end{itemize}
-    Taking $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
+    Letting $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
 \[
@@
     Also notice that $\psi'(0+)=-\alpha <0$ and that there exists $z>0$ such that $\psi(z)>0$.
-    So, we can verify that the following are true:
+%    So, we can verify that the following are true:
+    Therefore we have
 \begin{itemize}
@@
 \item
-    if $\lambda \in (0,\bar v)$ then $0<\lambda \leq v_t(\lambda)<\bar v $, and that
+    if $\lambda \in (0,\bar v)$ then $0<\lambda \leq v_t(\lambda)<\bar v $ and 
 \begin{align}
@@
 \item
-    if $\lambda \in (\bar v, \infty)$ then $\bar v < v_t(\lambda)\leq \lambda< \infty $, and that
+    if $\lambda \in (\bar v, \infty)$ then $\bar v < v_t(\lambda)\leq \lambda< \infty $ and 
 \[
@@
 \]
-In fact, for each $x\geq 0$ and $t\geq 0$ we have
+In fact, for all $x\geq 0$ and $t\geq 0$, we have
 \begin{equation}\begin{split}
@@
     \\ &= e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
-    \\&\leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big)
-\end{split}\end{equation}
-    as required in this step.
-
-    Step 3. We will show that there exists constants $c, \delta, t_0 > 0$ such that
+    \\&\leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big),
+\end{split}\end{equation}
+%    as required in this step.
+   as desired in this step.
+
+    Step 3. We will show that there exist constants $c, \delta, t_0 > 0$ such that
 \[
@@
 \]
-    In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$, and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
+    In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
     According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
@@
 \end{split}\end{equation}
-    Rearrange this, we have
+%    Rearrange this, we have
+Rearranging this, we get
 \[
@@
 
-    Step 4: We will show that there exists constant $C, \delta,t_0>0$ such that
+    Step 4: We will show that there exist constant $C, \delta,t_0>0$ such that
 \[
@@
     and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
-    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$ where the martingale limit $W_\infty$ is a non-degenerate random variable.
+    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate random variable.
 This implies that
@@
 \]
-    The $L \log L$ critierioin also garuntees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.ly in $\mathbf P_1$.
-This and the non-degeneracy of $W_\infty$ implies that
+    The $L \log L$ critierioin also garuntees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.
+in $\mathbf P_1$.
+This and the non-degeneracy of $W_\infty$ imply that
 \[
@@
 \end{split}\end{equation}
-    Rearrange this, we have, for $t$ large enough,
+    Rearranging this, we get, for $t$ large enough,
 \[
@@
 \]
-    Therefore, there exists constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$,
+    Therefore, there exist constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$,
 \[
@@
 \]
-    This implies the required result in this step.
-
-    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exists constant $C, \delta, t_0 > 0$ such that
+    This implies the desired result in this step.
+
+    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exist constant $C, \delta, t_0 > 0$ such that
 \[
@@
 \end{proof}
-\subsection{$(1+\gamma)$-moments for the super-OU process}
+%\subsection{$(1+\gamma)$-moments for the super-OU process}
+\subsection{moments estimates  for super-OU processes}
 
  In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
-    For all $0 \leq s \leq t <\infty$ and  random variable $Y$ with finite mean, write
-$$
+    For all $0 \leq s \leq t <\infty$ and  random variable $Y$ with finite mean, we write
+%$$
+\begin{equation}\label{Ist}
     \mathcal I_s^t Y
   := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s].
-$$
+%$$
+\end{equation}
 
@@
 \begin{proof}
-    Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller for Lemma \ref{lem: upper bound for usgx}.(4).
-    Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
+    Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: upper bound for usgx}.(4).
+    Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof of \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
 \begin{equation}\begin{split}
@@
 \begin{equation}\label{Q_k}
-Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|P_t f|,
+Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|P_t f|
 \end{equation}
@@
 \label{lem: control moment}
-    For any $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
+    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
 \begin{itemize}
@@
 
-\section{Proof of main results}
+\section{Proofs of main results}
 
@@
 
-\subsection{The large rate case: $\alpha \beta > \kappa_f b (1+\beta)$}
-
-In this subsection, we prove Theorem \ref{Theorem11}. We will be back to the large branching rate case in Subsection \ref{large rate again} to prove Theorem \ref{theorem 1.6}.
-
-To prove Theorem \ref{Theorem11}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family martingales for $\gamma\in (0, \beta)$.
+%\subsection{The large rate case: $\alpha \beta > \kappa_f b (1+\beta)$}
+\subsection{The large rate case}
+
+In this subsection, we prove Theorem \ref{Theorem11}. 
+%We will be back to the large branching rate case 
+We will return to the large branching rate case 
+in Subsection \ref{large rate again} to prove Theorem \ref{theorem 1.6}.
+
+To prove Theorem \ref{Theorem11}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
 Recall that $L$ is the infinitesimal generator of the OU-process.
-Let $f\in \mathcal{P}\cap C^2(\mathbb R^d)$, and let $a\in \mathbb R$, we define that
+For $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and  $a\in \mathbb R$, we define
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
+%    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
+Let $(\mathscr{F}_t)_{t\geq 0}$ be the natural filtration of $X$.  The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
 \begin{lem}
 \label{lemma25}
-    For each $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and $a\in \mathbb R$.
-Then, for any $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
+    For all $f\in \mathcal{P}\cap C^2(\mathbb R^d)$, $a\in \mathbb R$
+and $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
 \end{lem}
 \begin{proof}
-    Write $\bar{f}=(L+ab)f$. According to \cite[Theorem A.55]{Li2011Measure-valued}, we have
+    We write $\bar{f}=(L+ab)f$. According to \cite[Theorem A.55]{Li2011Measure-valued}, we have
 \begin{equation}\begin{split}\label{Theorem55}
@@
 \end{split}\end{equation}
-Let $0\leq s\leq t$,
+For $0\leq s\leq t$, we have
 \begin{equation}\begin{split}
@@
   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb R^d)$.
-
     There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
     Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$,
-   we get, for $\gamma\in [\gamma_0, \beta)$, that there exists
+   we get that, for $\gamma\in [\gamma_0, \beta)$, there exists
     a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$)  such that
@@
 \]
-   For any $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, note that
+   For all $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, we have 
 \[
@@
 
-   Hence, for each $\gamma \in (0,\beta)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$,
+   Hence, for all $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
     the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
@@
 \]
-Moreover, letting $t\to\infty$ in above inequality, we have
+Moreover, 
+%letting $t\to\infty$ in above inequality, 
+we have
 \[
@@
 \begin{proof}
+%new
+The second assertion follows immediately from the first, so we only first the first assertion.
+%ene new
      Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,
+It follows from Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$ that
  there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
@@
     \end{align}
-    Thus there is a $C>0$ for any $0\leq s<t$,
+    Thus there is a $C>0$ such that for any $0\leq s<t$,
 \begin{align}
@@
 {\it Proof of Theorem \ref{Theorem11}.}\quad
-	Fix  $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$.
-	Fix $\mu \in \mathcal M_c(\mathbb R^d)$.
+	Fix  $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
 	Write
@@
 $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
-	Therefore, it is suffice to show that
+	Therefore, it suffices to show that
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-	converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$ satisfying $D^2f\in \mathcal{P}$.
+	converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$ satisfies $D^2f\in \mathcal{P}$.
 
@@
 	Step 2.
-	Further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$, we will show that $J_t$ converges to $0$ almost surely.
-	For $a \geq 0$ and $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, define
+	We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$, we will show that $J_t$ converges to $0$ almost surely.
+	For $a \geq 0$ and $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
 \begin{equation}\begin{split}
@@
 
-	The proof is now completed.
-
-\subsection{The critical rate case: $\alpha\beta=\kappa_fb(1+\beta)$}
+	The proof is now complete.
+
+%\subsection{The critical rate case: $\alpha\beta=\kappa_fb(1+\beta)$}
+\subsection{The critical rate case}
+
+%new
+Recall that $I_s^t$ is defined in \eqref{Ist}.
+%end new
 
@@
  \begin{proof}
-    We only need to show that
+%    We only need to show that
+   We only need to show that for all $\mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0$, 
 \begin{equation}\begin{split}
     \mathbb{P}_{\mu}[\exp(i\gamma_{t,k}); D^c]
-    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[f]),
-    \quad \mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0.
+    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[f]).
+%    \quad \mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0.
 \end{split}\end{equation}
@@
     \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
-    \leq J_1(t,k,\epsilon)+J_2(t,k,\epsilon)+J_3(t,k,\epsilon)
+    \leq J_1(t,k,\epsilon)+J_2(t,k,\epsilon)+J_3(t,k,\epsilon),
 \end{split}\end{equation}
@@
 \end{split}\end{equation}
-In fact, from the definitions of $K_1$ and $Z_1$, we have that for all
+In fact, 
+%from the definitions of $K_1$ and $Z_1$, we have 
+it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$, 
+that for all
 $k\geq 0, t\geq k+1$,
@@
 
-Step 2.  We will show that for each $\epsilon>0$ small enough, there exists constants $C, \delta>0$ such that
+Step 2.  We will show that for each $\epsilon>0$ small enough, there exist constants $C, \delta>0$ such that
     \begin{equation}\begin{split}
@@
     Step 3.
-    We will show that for $\epsilon>0$ small enough, there exists constants $C, \delta>0$ such that
+    We will show that for $\epsilon>0$ small enough, there exist constants $C, \delta>0$ such that
     \begin{equation}\begin{split}
@@
 \]
-According to Lemma \ref{lem: control of gk}, we get there exists $h\in \mathcal{P}$ such that
+%According to Lemma \ref{lem: control of gk}, we get there exists $h\in \mathcal{P}$ such that
+It follows from Lemma \ref{lem: control of gk} that there exists $h\in \mathcal{P}$ such that
  \[
@@
 \end{split}\end{equation}
-Therefore, according to \eqref{eq: prevJ2}, we have there exists constant $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+%Therefore, according to \eqref{eq: prevJ2}, we have 
+Therefore, it follows from \eqref{eq: prevJ2} that
+there exists constant $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-    In fact, we have that for all $t\geq 0, \epsilon >0$,
+    In fact, we have  for all $t\geq 0, \epsilon >0$,
 \begin{equation}\begin{split}
@@
 
-    Finally, combining the results in Steps 1-4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$,
+    Finally, combining the results in Steps 1--4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$,
 we immediately get the desired result.
@@
 Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq \kappa_fb(1+\beta)$.
-Then for any $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
+Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
 there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
@@
 \begin{proof}
-	For each $f\in \mathcal P$, define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as $J_1, J_2$ and $J_3$ in \eqref{eq: Def of Ji}.
+	For  $f\in \mathcal P$, define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as the $J_1, J_2$ and $J_3$ in \eqref{eq: Def of Ji}.
 	Now, fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and an $f\in \mathcal P$.
@@
 \]
-	According to this and \eqref{eq: right bound for J2} in the Step 3 in the proof of the previous lemma, we have that there exists a constant $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+%	According to this and \eqref{eq: right bound for J2} in the Step 3 in the proof of the previous lemma, 
+		According to this and \eqref{eq: right bound for J2}, 
+	we have that there exists a constant $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{equation}\begin{split}
@@
 \begin{prop}\label{corollary31}
-Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then for any $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
+Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
 there exist constants $C,\delta>0$ such that
@@
     \begin{align*}
-        &|a_{k-1}- a_k|
-        \\&\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
+        |a_{k-1}- a_k|
+        &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
         \\& \leq C e^{-\delta(t-k)}.
@@
 {\it Proof of Theorem \ref{Theorem12}.}\quad
-    According to our assumption, $f\in\mathcal{P}$ is fixed and that  $\alpha\beta=\kappa_fb(1+\beta)$.
+   By assumption, $f\in\mathcal{P}$ and  $\alpha\beta=\kappa_fb(1+\beta)$.
     Chose $t_0 > 0$ large enough so that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
-    Write
+    We write
     \begin{align*}
@@
         \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq C \frac{1}{t^{\delta}},
-        \quad t\geq t_0,
+        \quad t\geq t_0.
 \end{align*}
-    Where $\mathcal{\mathbb{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$. According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\zeta$ under $\tilde {\mathbb P}_\mu$.
+%    Where $\mathcal{\mathbb{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$. 
+    According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\zeta$ under $\tilde {\mathbb P}_\mu$.
     Therefore, we only need to prove
- \begin{equation}\label{toprove-1}|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0,
+ \begin{equation}\label{toprove-1}|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0
  \end{equation}
@@
 \end{split}\end{equation}
-    Then according to Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality, there exists $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
+%    Then according to 
+   According to 
+    Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality, there exist $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
 \begin{equation}\begin{split}
@@
 \end{equation}
-    Note that, since $\eta_1 < \eta_0$, we have
+    Note that, since $\eta_1 < \eta_0$, we have on $\mathcal D_{t,k}$, 
 \begin{align*}
@@
     \geq 2e^{-\eta_1(t-k-1)}-e^{-\eta_0(t-k-1)}
-    \\&\geq e^{-\eta_1(t-k-1)},
-    \quad \text{ on } \mathcal D_{t,k}.
+    \geq e^{-\eta_1(t-k-1)}.
+ %   \quad \text{ on } \mathcal D_{t,k}.
 \end{align*}
-    Therefore, for each $k \geq 0$ and $t\geq k+1$,
+    Therefore, for each $k \geq 0$ and $t\geq k+1$,  on $\mathcal D_{t,k}$, 
 \begin{align*}
@@
     =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)},
-    \quad \text{ on } \mathcal D_{t,k},
+%    \quad \text{ on } \mathcal D_{t,k},
 \end{align*}
@@
     |H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}|
-    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1(t-k-1)},
-    \quad \text{ on } \mathcal D_{t,k}.
+    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1(t-k-1)}.
+%    \quad \text{ on } \mathcal D_{t,k}.
 \end{align*}
-    Thus, there is a constant $C\geq 0$ such that,
+    Thus, there is a constant $C\geq 0$ such that for all $k \geq 0, t\geq k+1$, 
 \begin{equation}\begin{split}
@@
      K_{t,k}
-     \leq C e^{-(\eta_0 - 3\eta_1)(t-k-1)},
-     \quad k \geq 0, t\geq k+1.
+     \leq C e^{-(\eta_0 - 3\eta_1)(t-k-1)}.
+ %    \quad k \geq 0, t\geq k+1.
 \end{split}\end{equation}
@@
     Step 4. We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\tilde{P}}_{\mu}$.
-    In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exists $C, \delta>0$ such that
+    In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C, \delta>0$ such that
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-    Therefore, there exists $C, \delta>0$ such that
+    Therefore, there exist $C, \delta>0$ such that
 \begin{equation}\begin{split}\label{Theorem123}
@@
 
-\subsection{The small rate case: $\alpha\beta<\kappa_fb(1+\beta)$}
+%\subsection{The small rate case: $\alpha\beta<\kappa_fb(1+\beta)$}
+\subsection{The small rate case}
+
  In this subsection, we prove the central limit theorem for the small rate case.
@@
 {\it Proof of Theorem \ref{Theorem13}.}\quad
-According to our assumption, $f\in \mathcal P$  is fixed  and  that $\alpha \beta < \kappa_f b(1+\beta)$.
+%According to our assumption, $f\in \mathcal P$  is fixed  and  that $\alpha \beta < \kappa_f b(1+\beta)$.
+By assumption, $f\in \mathcal P$  and $\alpha \beta < \kappa_f b(1+\beta)$.
 	Let $t_0 > 1$ be large enough so that
@@
 \]
-	Write
+	We write
 \begin{align*}
@@
 \begin{align*}
-    &\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
-    \\& \leq C( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta(t-k)})
+    \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
+    & \leq C( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta(t-k)})
     \\& \leq C'e^{-\delta (t-k)}.
@@
 	 A_t(\epsilon)
-	:=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
+	=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
 	\quad t\geq 0.
 \]
-	According to \eqref{lem: control of XT}, there exists
+	According to \eqref{lem: control of XT}, there exist
 	$C,\delta>0$ such that
@@
 \subsection{Proof of Theorem \ref{theorem 1.6}}\label{large rate again}
-In this subsection, we are back to the large branching rate case, and aim to prove Theorem \ref{theorem 1.6}.
-
-For each $g\in \mathcal{C}_l$, recall the definition of $I_tg$ in \eqref{definition of Itf}.
-By Fubini's theorem, we get
+In this subsection, 
+%we are back to the large branching rate case, and aim to prove Theorem \ref{theorem 1.6}.
+we revisit the large branching rate case and prove Theorem \ref{theorem 1.6}.
+
+For $g\in \mathcal{C}_l$, recall the definition of $I_tg$ in \eqref{definition of Itf}.
+By Fubini's theorem, we have
 \begin{align}\label{equ: transform of mn}
@@
 
-Recall that $\Big\{\{H^p_t, \mathscr{F}_t\}_{t\geq 0};p\in \mathbb{Z}_+^d\Big\}$ is a family of martingale defined in Lemma \ref{lemma26}.
+Recall that $\Big\{\{H^p_t, \mathscr{F}_t\}_{t\geq 0};p\in \mathbb{Z}_+^d\Big\}$ is a family of martingales defined in Lemma \ref{lemma26}.
 
 \begin{lem}
-    For each $n>0$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$,
+    For all $n>0$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$,
     \begin{align}
@@
     \end{align}
-    where $\bar{\zeta}_n$ is an $(1+\beta)$-stable random variable with characteristic function
+    where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function
     \begin{align}
@@
 $\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
-We get that
+We have
 \begin{align}
@@
 \end{align}
- From the definitions of $K_1$ and $Z_1$, we have
+% From the definitions of $K_1$ and $Z_1$, we have
+It follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$ that
 \begin{align}
@@
 \]
-we have
+we have for all $n\geq 0, t\geq 0, \epsilon> 0$, 
 \begin{align}
@@
     \\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (k_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
-    \\&\leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon)
-    \quad n\geq 0, t\geq 0, \epsilon> 0.
-\end{align}
-
-Step 2.  We will show that for each $\epsilon$ small enough, there exist constants $C,\delta>0$ such that,
+    \\&\leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon).
+%    \quad n\geq 0, t\geq 0, \epsilon> 0.
+\end{align}
+
+Step 2.  We will show that for each $\epsilon$ small enough, there exist constants $C,\delta>0$ such that for all $n\geq 1, \, t\geq 0$, 
     \begin{align}
     \label{eq:large rate J1}
-      J'_1(t,n,\epsilon)\leq C e^{-\delta(t+n)},\quad n\geq 1, \, t\geq 0.
-    \end{align}
-	In fact, let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the $(\theta^{1+\beta}\vee \theta^{1+\beta+\delta_0})$-controller. Then we have,
+      J'_1(t,n,\epsilon)\leq C e^{-\delta(t+n)}. %\quad n\geq 1, \, t\geq 0.
+    \end{align}
+	In fact, let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the $(\theta^{1+\beta}\vee \theta^{1+\beta+\delta_0})$-controller. Then we have
+	for all $n\geq 0, t\geq 0, \epsilon > 0$, 
 \begin{align}
@@
    \\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|,
-   \quad n\geq 0, t\geq 0, \epsilon > 0,
+ %  \quad n\geq 0, t\geq 0, \epsilon > 0,
 \end{align}
 where $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-Thus for each $n\geq 0,  t\geq 0, \epsilon > 0$,
+Thus for all $n\geq 0,  t\geq 0, \epsilon > 0$,
 \begin{align}
@@
 Step 3.
-	We will show that for each $\epsilon$ small enough, there exists constant $C,\delta>0$ such that,
+	We will show that for each $\epsilon$ small enough, there exist constant $C,\delta>0$ such that for all $n\geq 1, t\geq 0$, 
 \begin{align}
@@
     J'_2(t,n,\epsilon)
-    \leq C e^{-\delta(t+n)},
-    \quad n\geq 1, t\geq 0.
-\end{align}
-
-In fact, according to the definitions of $Z_1$ and $\bar{m}_n$, and \eqref{equ: transform of mn}, we have
+    \leq C e^{-\delta(t+n)}.
+%    \quad n\geq 1, t\geq 0.
+\end{align}
+In fact, according to the definitions of $Z_1$ and $\bar{m}_n$, and \eqref{equ: transform of mn}, we have for all $t\geq 0, n\geq1$, 
 \begin{align}
     &\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\\
-    &=e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big),\\
-    & t\geq 0, n\geq1.
-\end{align}
-Therefore,
+    &=e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
+%    & t\geq 0, n\geq1.
+\end{align}
+Therefore, for all $t\geq 0, n\geq1$, 
 \begin{align}
@@
 	&\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}
-[\langle \bar {g}_n, X_{t+n-1}\rangle],
-	\quad t\geq 0, n\geq 1,
+[\langle \bar {g}_n, X_{t+n-1}\rangle].
+%	\quad t\geq 0, n\geq 1,
 \end{align}
@@
 \end{align}
-Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment} (3) with $\kappa=1$,
+Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment}.(3) with $\kappa=1$,
  there exists $C>0$ such that
@@
 \end{align}
-Therefore,
+Therefore, for all $t\geq 0, n\geq1$, 
 \begin{align}
@@
     &\leq C e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)}\\
-    &=Ce^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}\\&\leq Ce^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)},\quad t\geq 0,n\geq 1.
-\end{align}
-	Step 4. Using similar arguments in the proof of step 4 of Lemma \ref{lem: mainlemma}, we can show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
+    &=Ce^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}\\&\leq Ce^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}.
+%    ,\quad t\geq 0,n\geq 1.
+\end{align}
+	Step 4. Using an argument similar to that used in Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we can show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
 \begin{align}\label{ineq: control of J31}
@@
 \end{align}
-Finally, combining the results in steps 1-4.
-and noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$, converge to $0$ exponentially fast while $t\rightarrow\infty$, we get the desired result.
-	This gives the desired result.
+
+Finally, combining the results in Steps 1--4.
+and noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$, converge to $0$ exponentially fast when $t\rightarrow\infty$, we get the desired result.
+%	This gives the desired result.
 \end{proof}
@@
 \begin{lem}\label{lem:lemma03}
-    For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
+    For all $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
     \begin{align}\label{ineq: next we will need}
@@
 Step 1.
-Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  for any  $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that, for any $t\geq 0$, $n\geq 1$, we have
+Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  for all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that, for any $t\geq 0$, $n\geq 1$, we have
 \begin{align}
@@
     \end{align*}
-   According to step 1 and Proposition \ref{cor: alpha stable rv 1},
+   According to Step 1 and Proposition \ref{cor: alpha stable rv 1},
     there exist $C,\delta>0$ such that for any $n=1,\cdots, m$ and $t\geq0$, we have
     \begin{align*}
-        &|\tilde{a}_{n-1}- \tilde{a}_n|
-        \\&\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
+        |\tilde{a}_{n-1}- \tilde{a}_n|
+        &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
         \\& \leq C e^{-\delta(t+n-1)}.
@@
 \end{proof}
-Now let
+Now we define
 \begin{align}
@@
 \begin{lem}\label{lem: lemma04}
-     For each $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$
+     For all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$
 such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
@@
 \[
-    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0,
+    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0
 \]
@@
 
-Step 1. Similar to step 1 in the proof of Theorem \ref{Theorem12},
+Step 1. Similar to Step 1 in the proof of Theorem \ref{Theorem12},
 we can show that there exist constants $C,\delta >0$ such that for all $n \geq 1$ and $t\geq 0$,
@@
 
-    Step 2. We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta > 0$, such that for all $n\geq 1$ and $t\geq 0$,
+    Step 2. We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta > 0$ such that for all $n\geq 1$ and $t\geq 0$,
 \begin{align}
@@
     \end{align}
-    We get \eqref{thm12211} since $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}<\eta_0-3\eta_1$ and $\alpha\gamma>Kb(1+\gamma)\geq |p|b(1+\gamma)$.
-  Combinning \eqref{ineq: used next 3}, Steps 1-2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
+    \eqref{thm12211} now follows  since $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}<\eta_0-3\eta_1$ and $\alpha\gamma>Kb(1+\gamma)\geq |p|b(1+\gamma)$.
+
+ Combining \eqref{ineq: used next 3} with Steps 1-2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
 \end{proof}
@@
 \begin{proof}
-Recall that $A_t(\epsilon):=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to Proposition \ref{lem: control of XT}, there exists
+Recall that $A_t(\epsilon)=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to Proposition \ref{lem: control of XT}, there exist
 	$C,\delta>0$ such that for all $t\geq 0$
@@
 \end{align}
-	 Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ satisfying $\alpha\gamma>Kb(1+\gamma)$.  According to Lemma \ref{lem: control of wt}, there exist $C,C'>0$ such that
+	 Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ with $\alpha\gamma>Kb(1+\gamma)$.  According to Lemma \ref{lem: control of wt}, there exist $C,C'>0$ such that
 \begin{align}\label{ineq: control of gamma_t on d}
@@
 \end{align}
-Combining with \eqref{ineq: control of gamma_t on dc} and \eqref{ineq: control of gamma_t on d}, we complete the proof.
+Combining \eqref{ineq: control of gamma_t on dc} and \eqref{ineq: control of gamma_t on d}, we complete the proof.
 \end{proof}
@@
 {\it Proof of Theorem \ref{theorem 1.6}.}\quad
-Let $\delta_0$ be the control parameter in Lemma \ref{lem: lemma04}.  Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$. First note that
+Let $\delta_0$ be the constant $\delta$ in Lemma \ref{lem: lemma04}.  Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$. First note that for $t\ge 0$,
 \begin{align}\label{decompose}
-    \text{LHS of \eqref{thm: large rate}}=\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\tilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\tilde{\gamma}_{t,n},\quad t\geq 0.
-\end{align}
-According to Lemma \ref{lem:lemma03}, there exists $C,\delta>0$ such that
+    \text{LHS of \eqref{thm: large rate}}=\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\tilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\tilde{\gamma}_{t,n}.
+    %\quad t\geq 0.
+\end{align}
+According to Lemma \ref{lem:lemma03}, there exist $C,\delta>0$ such that for all
+$t\geq 0,\theta\in\mathbb{R}$, 
 \begin{align}\label{ineq: last1}
-    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t},\quad t\geq 0,\theta\in\mathbb{R}.
-\end{align}
-According to Lemma \ref{lem: lemma04}, there exists $C>0$ such that
+    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t}.
+    %\quad t\geq 0,\theta\in\mathbb{R}.
+\end{align}
+According to Lemma \ref{lem: lemma04}, there exists $C>0$ such that for all
+$t\geq 0,\theta\in\mathbb{R}$, 
 \begin{align}\label{ineq: last2}
-    \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C  e^{-\frac{\delta_0}{2} t},\quad t\geq 0, \theta\in \mathbb{R}.
- \end{align}
- According to Lemma \ref{lem: lemma05}, there exists $C,\delta_1,\delta_2>0$ such that
+    \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C  e^{-\frac{\delta_0}{2} t}.
+    %\quad t\geq 0, \theta\in \mathbb{R}.
+ \end{align}
+ According to Lemma \ref{lem: lemma05}, there exist $C,\delta_1,\delta_2>0$ such that
+ for all
+$t\geq 0,\theta\in\mathbb{R}$, 
  \begin{align}\label{ineq: last3}
-  \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 e^{\frac{\delta_0}{2}t}}),\quad t\geq 0, \theta\in \mathbb{R}.
+  \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 e^{\frac{\delta_0}{2}t}}).
+  %\quad t\geq 0, \theta\in \mathbb{R}.
 \end{align}
@@
 \subsection{Analytic facts}
+
+%new
+In this subsection, we collect some useful analytic facts.
+%end new
 \begin{lem}
 \label{lem: estimate of exponential remaining}
-    Suppose that $z\in \mathbb C_+$. Then
+ For  $z\in \mathbb C_+$,  we have
 \begin{equation}
@@
     Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb Z_+$.
-    We have
+ Then
 \begin{equation}\begin{split}
@@
     Suppose that  $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)} (y \wedge y^2) \pi(dy)< \infty$.
-    Then functions
+    Then the functions
 \begin{equation}
@@
 \begin{proof}
-    From Lemma \ref{lem: estimate of exponential remaining}, we know that $h$ and $h'$ are well defined on $\mathbb C_+$.
-    According to \cite[Theorem 3.2. \& Theorem 3.5]{SchillingSongVondracek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
-
-    From Lemma \ref{lem: estimate of exponential remaining}, for each $z_0 \in \mathbb C_+$, we have that there exists $C>0$ such that for $z \in \mathbb C_+$ close enough to $z_0$ and any
+    It follows from Lemma \ref{lem: estimate of exponential remaining} that $h$ and $h'$ are well defined on $\mathbb C_+$.
+    According to \cite[Theorems 3.2. \& 3.5]{SchillingSongVondracek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
+
+    It follows from Lemma \ref{lem: estimate of exponential remaining} that, for each $z_0 \in \mathbb C_+$,  there exists $C>0$ such that for $z \in \mathbb C_+$ close enough to $z_0$ and any
     $y>0$,
@@
 
-	For each $z\in \mathbb C\setminus (-\infty,0]$, define
+	For each $z\in \mathbb C\setminus (-\infty,0]$, we define
 $
@@
 $ 	
-	For all $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$, define
+	For all $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$, we define
 $
@@
 $
-	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, $z\mapsto \log z$ is holomorphic on $\mathbb C\setminus (-\infty,0]$.
-	Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic on $\mathbb C\setminus (-\infty,0]$.
-(We use the convention tha  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
-    From this definition we can show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
+	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, that $z\mapsto \log z$ is holomorphic in $\mathbb C\setminus (-\infty,0]$.
+	Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic in $\mathbb C\setminus (-\infty,0]$.
+(We use the convention that  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
+   Using  the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
 
@@
 \end{equation}
-	It is known, see \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it for example, the function $\Gamma$ has an unique analytic extension on $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
+	It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
 \[
@@
 \label{lem: Lip of power function}
-    For each $z_0,z_1 \in \mathbb C_+$, we have
+    For all $z_0,z_1 \in \mathbb C_+$, we have
 \begin{equation}
@@
 	Such a function $f$ is called the distinguished logarithm of the function $\varphi$ and is denoted as $\operatorname{Log} \varphi(\theta)$.
-	In particular, let $\varphi$ be the characteristic function of an infinitely divisible random variable $Y$, then $\operatorname{Log} \varphi(\theta)$ is called the L\'evy exponent of $Y$.
+	In particular, when $\varphi$ is the characteristic function of an infinitely divisible random variable $Y$,  $\operatorname{Log} \varphi(\theta)$ is called the L\'evy exponent of $Y$.
  	This distinguished logarithm should not be confused with the $\log$ function defined on $\mathbb C\setminus (-\infty, 0]$.
 
-\subsection{Feynman-Kac formula with complex values}
+\subsection{Feynman-Kac formula with complex valued functions}
 \label{seq: complex Feynman-Kac transform}
-    In this subsection we give a version of the Feynman-Kac formula with complex values.
+    In this subsection we give a version of the Feynman-Kac formula with complex valued functions.
     Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact seperable metric space $E$.
-    Write
+    We write
 \begin{equation}
@@
 \begin{lem}
-    Let $t \geq 0$. Suppose that $\alpha,\rho\in \mathcal B_b([0,t] \times E, \mathbb C)$ and $f\in \mathcal B_b(E, \mathbb C)$.
+    Let $t \geq 0$. Suppose that 
+%    $\alpha,\rho\in \mathcal B_b([0,t] \times E, \mathbb C)$ 
+   $\rho_1, \rho_2\in \mathcal B_b([0,t] \times E, \mathbb C)$ 
+    and $f\in \mathcal B_b(E, \mathbb C)$.
     Then
 \begin{equation}
-    g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\alpha+\rho)} f(\xi_t)],\quad r \in [0,t], x\in E,
+ %   g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\alpha+\rho)} f(\xi_t)],\quad r \in [0,t], x\in E,
+   g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
 \end{equation}
@@
 \[
-    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\alpha)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\alpha)}\rho(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
+%    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\alpha)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\alpha)}\rho(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
+    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
 \]
@@
 \begin{equation}\begin{split}
-    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\alpha)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t)| ~ds \Big]
-    \leq  \int_r^t e^{(t-r)\|\alpha\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|f\|_\infty ~ds
+%    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\alpha)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t)| ~ds \Big]
+%    \leq  \int_r^t e^{(t-r)\|\alpha\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|f\|_\infty ~ds
+%    < \infty.
+   \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t)| ~ds \Big]
+    \leq  \int_r^t e^{(t-r)\|\rho_1\|_\infty}e^{(t-s)\|\rho_2\|_\infty}\|\rho_2\|_\infty\|f\|_\infty ~ds
     < \infty.
@@
 \label{eq: crucial for Feynman-Kac}
-    \frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
+%    \frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
+   \frac{\partial}{\partial s} H^{(\rho_2)}_{(s,t)}= -H^{(\rho_2)}_{(s,t)}\rho_2(s,\xi_s),
     \quad s\in (0,t).
@@
 \begin{equation}\begin{split}
-    &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\alpha)}~(\rho g)(s,\xi_s)~ds \Big]
-    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\alpha)}\rho(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\alpha+\rho)} f(\xi_t)]~ds \Big]
-    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\alpha)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t) ~ds \Big]
-    = \Pi_{r,x} [ H_{(r,t)}^{(\alpha)}f(\xi_t)(H_{(r,t)}^{(\rho)} - 1)]
-    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\alpha)} f(\xi_t)].
-\end{split}\end{equation}
-    For the uniqueness, suppose that $\tilde g$ is another solution. Writting $h(r) = \sup_{x\in E}|g(r,x) - \tilde g(r,x)|$, we have
+    &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}~(\rho_2 g)(s,\xi_s)~ds \Big]
+    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\rho_1+\rho_2)} f(\xi_t)]~ds \Big]
+    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t) ~ds \Big]
+    = \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)}f(\xi_t)(H_{(r,t)}^{(\rho_2)} - 1)]
+    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\rho_2)} f(\xi_t)].
+\end{split}\end{equation}
+    For uniqueness, suppose  $\tilde g$ is another solution. Put $h(r) = \sup_{x\in E}|g(r,x) - \tilde g(r,x)|$. Then 
 \[
@@
 \label{sec: definition of superprocess}
-    In this subsection, we will give the definition of the superprocesses considered in this Appendix.
-Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with weak topology.
-    Recall that $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
+    In this subsection, we will give the definition of a general superprocess.
+Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the weak topology.
+    A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
 \begin{itemize}
@@
     \psi(x,z)=
-    - \alpha(x) z + \rho (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
-\end{equation}
-    where $\alpha \in \mathcal B_b(E)$, $\rho \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+%    - \alpha(x) z + \rho (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
+   - \rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
+\end{equation}
+    where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
 \item
@@
 \end{itemize}
-    We refer our reader to \cite{Li2011Measure-valued} for more discussion about the definition and the existence of superprocesses.
-    To avoid triviality, we assume that $\psi(x,z)\neq -\alpha(x)z$ for some $x \in E$ and $z \geq 0$.
-
-    Notice that, the branching mechanism $\psi$ can be extended into a map from $E \times \mathbb C_+$ to $\mathbb C$ using \eqref{eq: branching mechanism}.
+    We refer our reader to \cite{Li2011Measure-valued} for more discussions about the definition and the existence of superprocesses.
+    To avoid triviality, we assume that 
+   %$\psi(x,z)\neq -\alpha(x)z$ for some $x \in E$ and $z \geq 0$.
+   $\psi(x,z)$ is not identically equal to $-\rho_1(x)z$.
+
+    Notice that the branching mechanism $\psi$ can be extended into a map from $E \times \mathbb C_+$ to $\mathbb C$ using \eqref{eq: branching mechanism}.
     Define
 \begin{equation}
-    \psi'(x,z):= - \alpha(x) + 2\rho(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
+%    \psi'(x,z):= - \alpha(x) + 2\rho(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
+   \psi'(x,z):= - \rho_(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
     \quad x\in E, z\in \mathbb C_+.
 \end{equation}
-    Then according to Lemma \ref{lem: extension lemma for branching mechanism}, for each $x \in E$, $z \mapsto \psi(x,z)$ is a holomorphic function on $\mathbb C_+^0$ with deriavetive $z \mapsto \psi'(x,z)$.
-    Define $\psi_0(x,z) := \psi(x,z)+ \alpha(x)z $ and $\psi'_0(x,z) := \psi'(x,z) + \alpha(x)$.
-
-    Denote by $\mathbb W$ the space of $\mathcal M(E)$-valued c\`{a}dl\`{a}g paths with its conanical path denoted by $(W_t)_{t\geq 0}$.
+    Then according to Lemma \ref{lem: extension lemma for branching mechanism}, for each $x \in E$, $z \mapsto \psi(x,z)$ is a holomorphic function on $\mathbb C_+^0$ with derivative $z \mapsto \psi'(x,z)$.
+    Define $\psi_0(x,z) := \psi(x,z)+ \rho_1(x)z $ and $\psi'_0(x,z) := \psi'(x,z) + \rho_1(x)$.
+
+    Denote by $\mathbb W$ the space of $\mathcal M(E)$-valued c\`{a}dl\`{a}g paths with its canonical path denoted by $(W_t)_{t\geq 0}$.
     We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
@@
 \label{sec: definition of vf}
-    Let $X$ be the non-presistent superprocess defined in Subsection \ref{sec: definition of superprocess} with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
-    Define the mean semigroup
-\begin{equation}
-       P_t^\alpha f(x)
-    := \Pi_{x}[e^{\int_0^t \alpha(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
+    Let $X$ be a non-presistent superprocess 
+%    defined in Subsection \ref{sec: definition of superprocess} 
+    with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
+    We define the mean semigroup
+\begin{equation}
+ %      P_t^\alpha f(x)
+%    := \Pi_{x}[e^{\int_0^t \alpha(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
+       P_t^{\rho_1} f(x)
+    := \Pi_{x}[e^{\int_0^t \rho_1(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
     \quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
@@
     =\mathbf P_{\mu}[X_t(f)]=
-       \mu(P^\alpha_t f).
+       \mu(P^{\rho_1}_t f).
 \end{equation}
@@
     \mathbb N_x[W_t(f)]
-    =\mathbf P_{\delta_x}[X_t(f)]=P^\alpha_t f(x) \in \mathbb R,
+    =\mathbf P_{\delta_x}[X_t(f)]=P^{\rho_1}_t f(x) \in \mathbb R,
     \quad f\in L_1(\xi), t > 0,x\in E.
 \end{equation}
-    This says that random variables $X_t(f)$ are well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
-    According to the branching property of the superprocess, they are infinitely divisible random variables.
+    This says that the random variable $X_t(f)$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
+    According to the branching property of the superprocess, its is an infinitely divisible random variable.
     Therefore, we can write
@@
 \]
-    as their characteristic exponent.
+    as its characteristic exponent.
     According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
@@
 \begin{lem}
-    There exists constants $C\geq 0$ such that for each $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
+    There exists constants $C\geq 0$ such that for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
 \begin{equation}\begin{split}
@@
     \big|\psi\big(x,-U_tf\big)\big|
-    \leq C P^\alpha_t |f|(x)+
-         C (P^\alpha_t |f| (x))^2.
+    \leq C P^{\rho_1}_t |f|(x)+
+         C (P^{\rho_1}_t |f| (x))^2.
 \end{split}\end{equation}
@@
 \end{equation}
-    Therefore, we can talk about $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
+    Therefore, we can speak of $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
     According to Lemma \ref{lem: estimate of exponential remaining}, we have that
@@
     \leq \mathbb N_x[|i W_t(f)|]
-     \leq (P^\alpha_t |f|)(x).
+     \leq (P^{\rho_1}_t |f|)(x).
 \end{equation}
@@
     \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta|
-        \leq (P^\alpha_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
+        \leq (P^{\rho_1}_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
 \end{equation}
@@
     \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
-         \leq ( P^\alpha_t |f|)(x).
-\end{equation}
-    From the dominate convergence theorem, we can verify that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
+         \leq ( P^{\rho_1}_t |f|)(x).
+\end{equation}
+    It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
     In other words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
-    According to this, we have
+Thus,
 \begin{equation}
@@
     &|\psi'(x, -U_tf)|
-    \\&= \Big| -\alpha(x)- 2\rho(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
-    \\&= \Big| - \alpha(x)- 2\rho(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi(x,dy) \Big|
-\\ &\leq \|\alpha\|_\infty + 2\rho(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
-\\ &\leq \|\alpha\|_\infty + 2\|\rho\|_\infty
-  P^\alpha_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^\alpha_t |f|(x)
+    \\&= \Big| -\rho_1(x)- 2\rho_2(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
+    \\&= \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi(x,dy) \Big|
+\\ &\leq \|\rho_1\|_\infty + 2\rho(x)_2\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
+\\ &\leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty
+  P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x)
   + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
- \\ &=: C_1 + C_2(P^\alpha_t |f|)(x),
+ \\ &=: C_1 + C_2(P^{\rho_1}_t |f|)(x),
 \end{split}
@@
     where $C_1, C_2$ are constants independent on $f,x$ and $t$.
-    Now, using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we have get the desired result.
+    Now, ucombining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we get the desired result.
 \end{proof}
 
-    This Lemma also says that if $f\in L^2(\xi)$ then the following expectations
+    This lemma also says that if $f\in L^2(\xi)$ then 
 \[
@@
 \]
-    are well defined.
+    is well defined.
     In fact, using Jensen's inequality and the Markov property, we have
@@
     &\Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
-    \\&\leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^\alpha|f|(\xi_s)+C_2 P_{t-s}^\alpha|f|(\xi_s)^2\big)ds\Big]
-    \\ &\leq \int_0^t \big(C_1 e^{t\|\alpha\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\alpha\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
-    \\ &\leq \int_0^t (C_1 e^{t\|\alpha\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\alpha\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
+    \\&\leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big]
+    \\ &\leq \int_0^t \big(C_1 e^{t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
+    \\ &\leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\rho_1\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
 \end{split}\end{equation}
@@
 \subsection{}
-    Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
+    Let $X$ be a non-persistent superprocess.
+    % discussed in Subsection \ref{sec: definition of vf}.
     In this subsection, we will prove the following:
@@
 \label{eq: complex FKPP-equation with FK-transform}
-    U_tf(x) -  \int_0^t P_{t-s}^{\alpha} \psi_0\big(\cdot,-U_sf\big) (x)~ds
-      \\= iP_t^\alpha f(x).
+    U_tf(x) -  \int_0^t P_{t-s}^{\rho_1} \psi_0\big(\cdot,-U_sf\big) (x)~ds
+      \\= iP_t^{\rho_1} f(x).
 \end{equation}
@@
     To prove this, we will need the generalized spine decomposition theorem from \cite{RenSongSun2017Spine} which we now recall.
-    Let $X$ be the non-persistent superprocess discussed in Subsection \ref{sec: definition of vf}.
+    Let $X$ be the non-persistent superprocess.
+    % discussed in Subsection \ref{sec: definition of vf}.
     Let $f\in \mathcal B_b(E,\mathbb R_+)$, $T >0$ and $x\in E$.
-    Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^\alpha_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
+    Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
 \begin{equation}
     d\mathbf P_{\delta_x}^{X_T(f)}
-   := \frac{X_T(f)}{P_T^\alpha f(x)} d\mathbf P_{\delta_x};
+   := \frac{X_T(f)}{P_T^{\rho_1} f(x)} d\mathbf P_{\delta_x};
     \quad d\mathbb N_x^{W_T(f)}
-    :=  \frac{W_T(f)}{P_T^\alpha f(x)} d\mathbb N_x.
+    :=  \frac{W_T(f)}{P_T^{\rho_1} f(x)} d\mathbb N_x.
 \end{equation}
@@
 \begin{equation}
-    d\Pi_x^{(f,T)} := \frac{f(\xi_T)e^{\int_0^T \alpha(\xi_s)ds}}{P^\alpha_T f(x)} d \Pi_x;
+    d\Pi_x^{(f,T)} := \frac{f(\xi_T)e^{\int_0^T \rho_1(\xi_s)ds}}{P^{\rho_1}_T f(x)} d \Pi_x;
 \end{equation}
@@
     \mathbf m(\xi,ds,dw)
-    := 2 \rho(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
+    := 2 \rho_2(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
 \end{equation}
@@
     \leq \int_{[0,t]\times \mathbb W}\big(| w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
-    \\&\leq \int_0^t \Big(2\rho(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[ X_{t-s}(|f|)] \pi(\xi_s,dy)
+    \\&\leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[ X_{t-s}(|f|)] \pi(\xi_s,dy)
     \\&\qquad\qquad+ 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
-     \\&\leq \int_0^t (P_{t-s}^\alpha |f|)(\xi_s)\Big(2\rho(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
-    \\&\leq \Big(2\|\rho\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\alpha\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+     \\&\leq \int_0^t (P_{t-s}^{\rho_1} |f|)(\xi_s)\Big(2\rho_2(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+    \\&\leq \Big(2\|\rho_2\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\rho_1\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
     < \infty.
@@
     &\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
-    \\&=\int_0^t \Big(2\rho(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
-    \\&=\int_0^t \Big( 2\rho(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
+    \\&=\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
+    \\&=\int_0^t \Big( 2\rho_2(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
     \\&= -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
@@
     \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
-    \\&= \frac{1}{P_t^\alpha g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
+    \\&= \frac{1}{P_t^{\rho_1} g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
 \end{split}\end{equation}
@@
 \begin{equation}\begin{split}
-    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \alpha(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
-    &= \Pi_{r,x} [i e^{\int_r^t \alpha(\xi_s)ds}f(\xi_t)].
+    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
+    &= \Pi_{r,x} [i e^{\int_r^t \rho_1(\xi_s)ds}f(\xi_t)].
 \end{split}\end{equation}
@@
 \begin{equation}
-    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \alpha(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
-    = i\Pi_{r,x} [e^{\int_r^t\alpha(\xi_u)du}f(\xi_t)].
+    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
+    = i\Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
 \end{equation}
@@
     |e^{i W_t(f_n)} - 1| \leq W_t(|f|);
-    \quad \mathbb N_x[W_t(|f|)] = (P_t^\alpha |f|)(x) < \infty.
+    \quad \mathbb N_x[W_t(|f|)] = (P_t^{\rho_1} |f|)(x) < \infty.
 \]
@@
     \big|\psi(\xi_s,- U_{t-s}f_n)\big|
-    \leq C_1 P_{t-s}^\alpha|f|(\xi_s)+C_2 P_{t-s}^\alpha|f|(\xi_s)^2.
+    \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2.
 \end{split}\end{equation}

### 2019-02-11 supCLT.tex
supCLT.tex: 0211
supCLT.tex: deleted %


supCLT.tex: 0131


working

@@
 \usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage{mathtools}
@@
 \usepackage{mathrsfs}
-\usepackage{cite}
-\usepackage[backref=section]{hyperref}
-	\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
-	\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
+%\usepackage[backref=section]{hyperref}
+\usepackage{hyperref}
 \usepackage{comment}
+%\usepackage[nobysame]{amsrefs}
 \usepackage{amsthm}
@@
 	\allowdisplaybreaks
-%\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
-%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}
-
 %---Top matter------------------------------
@@
     [CLT for Super-OU processes]
- %   {CLT for Super-OU Processes with stable Branching}
-% {Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with Stable Branching}
     {Stable Central Limit Theorems for Super OU Processes with Stable Branching}
@@
 \address
-    {Yan-Xia Ren\\
-    LMAM School of Mathematical Sciences \& Center for
-Statistical Science\\
-    Peking University\\
-    Beijing, P. R. China, 100871}
+    {Yan-Xia Ren
+    \\ LMAM School of Mathematical Sciences \& Center for Statistical Science
+    \\ Peking University
+    \\ Beijing, P. R. China, 100871}
 \email{yxren@math.pku.edu.cn}
 \thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
-%new
 \address
-{Renming Sond\\
-Department of Mathematics\\
-University of Illinois of Illinois at Urbana-Champaign\\
-Urbana, IL 61801, USA}
+    %{Renming Sond\\
+    {Renming Song
+    \\ Department of Mathematics
+    \\ University of Illinois of Illinois at Urbana-Champaign
+    \\ Urbana, IL 61801, USA}
 \email{rsong@illinois.edu}
 \thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
-%end new
 \address
-    {Zhenyao Sun\\
-    School of Mathematical Sciences\\
-    Peking University\\
-    Beijing, P. R. China, 100871}
+    {Zhenyao Sun
+    \\ School of Mathematical Sciences
+    \\ Peking University
+    \\ Beijing, P. R. China, 100871}
 \email{zhenyao.sun@pku.edu.cn}
 \address
-    {Jianjie Zhao\\
-    School of Mathematical Sciences\\
-    Peking University\\
-    Beijing, P. R. China, 100871}
+    {Jianjie Zhao
+    \\ School of Mathematical Sciences
+    \\ Peking University
+    \\ Beijing, P. R. China, 100871}
 \email{zhaojianjie@pku.edu.cn}
 \begin{abstract}
- Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, 
- where $\alpha >0$ and $\beta\in (0,1)$ and 
-% that there exists $C >0$ and $\delta >0$ such that
-$psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
-$
-    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).
-$
+    Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z),$ where $\alpha >0$ and $\beta\in (0,1)$ and $psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that $|\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).$
     For each testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
@@
     In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
- In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$,
-we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$,
-and then established a central limit theorem, 
-%which say that after proper centering and scaling, we get a $(1+\beta)$-stable random variable again.
-which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges
-weakly to a $(1+\beta)$-stable random variable.
+    In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$, we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$, and then established a central limit theorem, which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges weakly to a $(1+\beta)$-stable random variable.
 \end{abstract}
-%\begin{abstract}
-%\end{abstract}
 %\subjclass[2010]{60J80, 60F05}
@@
 %---Contents-----------------------
-
-%\maketitle
-%\end{abstract}
-%\subjclass[2010]{60J80, 60F05}
-%\keywords{}
-%\date{}
-
 \section{Introduction}
-\subsection{Model}
-\label{ss:1.1}
+%Moved and modified from below
+\subsection{Motivation}
+\label{sec: Motivation}
+In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
+\[
+    \frac{\langle f, X_t \rangle -G_t}{F_t}
+\] 
+    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. 
+    It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
+
+    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. 
+    See \cite{KestenStigum1966A-limit,KestenStigum1966Additional} for supercritical multi-type Galton-Waston processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
+    In \cite{AdamczakMilos2015CLT}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+    These two papers made connections between CLT and what they call branching rate regimes. 
+    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
+    Moverover, compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate. 
+    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central,RenSongZhang2017Functional}, Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
+    All the results described above hold for systems with branching mechanisms with finite variance. 
+    It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
+    In \cite{MarksMilos2018CLT}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
+They established some central limit theorems in small and critical branching rate cases, but \cite{MarksMilos2018CLT} contained no central limit result in the branching rate case.
+    In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. 
+    For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}.
+    For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit theorem, which has no counterpart in \cite{MarksMilos2018CLT}.
+
+%Added
+    {\bf ZS: I think this subsection should be extended with more literatures like: 
+    \cite{AdamczakMilos2014U-statistics}, 
+    \cite{EckhoffKyprianouWinkel2015Spines},
+    \cite{EnglanderHarrisKyprianou2010Strong},
+    \cite{IksanovKabluchko2016A-central}, 
+    \cite{LiuRenSong2013Strong}, 
+    \cite{Wang2018Central},
+    \cite{IksanovKoleskoMeiners2018Stable-like},
+    \cite{IksanovKoleskoMeiners2018Fluctuations},
+    \cite{GrubelKabluchko2016A-functional},
+    \cite{Heyde1970A-rate}, 
+    \cite{Heyde1971Some}, 
+    \cite{HeydeBrown1871An-invariance}, 
+    \cite{HeydeLeslie1971Improved}, 
+    \cite{BansayeDelmasMarsalleTran2011Limit}, 
+    \cite{EnglanderWinter2006Law}, 
+    \cite{Englander2009Law}, 
+    \cite{Janson2004Functional}, 
+    \cite{ChenRenWang2008An-almost}, 
+    \cite{Wang2010An-almost}, 
+    \cite{HartungKlimovsky2018The-phase}, 
+    \cite{BansayeDelmasMarsalleTran2011Limit}, 
+    \cite{Le2019Long}.
+}
+%end and modified from below
+%\subsection{Model}\label{sec: main results}
+\subsection{Main results}
+\label{sec: main results}{}
 	Let $d \in \mathbb N:= \{1,2,\dots\}$.
-    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with generator
-\begin{equation}
-\label{eq: OU generator}
+%moved and modifeid from below 
+    Let $\mathbb R_+:= [0,\infty)$.
+    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
+    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
+    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
+    For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
+    For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
+%deletd
+    %Write $\|\mu\|=\langle 1,\mu\rangle$ for each $\mu \in \mathcal M(\mathbb R^d)$. 
+%end deleted
+    We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have 
+\[
+    \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
+\]
+%end moved from below
+    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
+\begin{equation}
     Lf(x)
     = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
-        \quad  x\in \mathbb R^d,
-        f \in C^2(\mathbb R^d),
+    \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
 \end{equation}
     where $\sigma$ and $b$ are positive constants.
-    Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
-    Let $\psi$ be the function on $\mathbb R_+$ defined by
-\begin{equation}
-\label{mechanism}
+%deleted
+    %Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
+%end deleted
+    %Let $\psi$ be the function on $\mathbb R_+$ defined by
+    Let the \emph{branching mechanism} $\psi$ be a function on $\mathbb R_+$ which takes the form of
+\begin{equation} \label{eq: honogeneou branching mechanism}
     \psi(z)=
@@
 	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
-%    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-%    Denote by $\mathcal B(\mathbb R^d)$ the space of all real-valued Borel measurable functions on $\mathbb R^d$.
-We use $B(\mathbb R^d, \mathbb R)$ to denote   the space of all real-valued Borel measurable functions on $\mathbb R^d$ and use $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-	For $f\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, we write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
- We aslo use the notation $\|\mu\|=\langle 1,\mu\rangle$. For $f, g\in \mathcal B(\mathbb R^d, \mathbb R)$, we also write $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
-
-    We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
-\begin{equation} \label{super}
+%new added
+	It is known that $\alpha, \rho$ and $\pi$ are uniquelly determined by function $\psi$. 
+	We refer to $\pi$ the \emph{L\'evy measure} of the branching mechanism $\psi$.
+%end new added
+%moved above
+    %We use $\mathcal B(\mathbb R^d, \mathbb R)$ to denote   the space of all real-valued Borel measurable functions on $\mathbb R^d$ and use $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
+	%For $f\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, we write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
+    %We aslo use the notation $\|\mu\|=\langle 1,\mu\rangle$. 
+    %For $f, g\in \mathcal B(\mathbb R^d, \mathbb R)$, we also write $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
+%end moved above
+    %We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+    We say an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+\begin{equation} 
+%\label{super}
     \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
@@
 	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
-\begin{equation}\label{eq1}
-	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
+\begin{equation} 
+%\label{eq1}
+	%V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
+    V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(V_{t-s}f(\xi_s)\big)~ds\Big]
 	= \Pi_x [f(\xi_t)],
@@
 \end{equation}	
-    The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.
-
-   According to  Subsection A.1, the branching mechanism $\psi$ can be extended to
-    $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
- \[\psi(z)=
-    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
-    \quad  z \in \mathbb C_+,\]
-    which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
-    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
-\begin{equation}
-\label{eq: deriavetive of the Poission part}
-    \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
-    \quad z\in \mathbb C^0_+.
-\end{equation}
-{ \bf
+    %The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.
+    The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
+%Added
+
+	Denote by $\Gamma$ the gamma function. 
+	In this paper, we will always assume that the following Assumption holds.
+%End added
+
+%Deleted
+    %According to Subsection A.1, the branching mechanism $\psi$ can be extended to
+    %$\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
+ %\[
+    %\psi(z)=
+    %- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
+    %\quad  z \in \mathbb C_+,
+%\]
+    %which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
+    %\{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
+%\begin{equation}
+%\label{eq: deriavetive of the Poission part}
+    %\psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
+    %\quad z\in \mathbb C^0_+.
+%\end{equation}
+
+%\begin{asp}
+%\label{asp: branching mechanism}
+    %The branching mechanism takes the form of
+%\[
+    %\psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
+%\]
+    %where $\alpha>0$, $\eta > 0$, $\beta \in (0,1)$ and $\psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
+%\[
+    %|\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
+%\]
+%\end{asp}
+%end Deleted
+%added
 \begin{asp}
 \label{asp: branching mechanism}
-    The branching mechanism takes the form of
-\[
-    \psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
-\]
-%    where $\eta > 0$, $\gamma \in (0,1)$ and 
-   where $\alpha>0$, $\eta > 0$, $\beta \in (0,1)$ and 
-    %that there exists $C >0$ and $\delta >0$ such that
-    and $\psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
-\[
-    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
-\]
+    There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
+\begin{equation}
+\label{eq: asp of branching mechanism}
+    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
+\end{equation}
+	for some $\delta > 0$.
 \end{asp}
-\begin{lem}
-    Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e.
+
+	It will be showed in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquelly determined by the L\'evy measure $\pi$.
+	In the reminder of the paper, we will always write $\eta,\beta$ for the constants corresponding to $\pi$.
+\begin{rem}
+\label{rem: small enough delta}
+	Note that $\delta$ is not uniquelly determined by $\pi$. 
+	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
+	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statements: There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
+\end{rem}
+
+    Assumption \ref{asp: branching mechanism} says that there exists a constatn $\eta>0$ and $\beta > 0$ such that the Levy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
+    In particular, if $\pi(dy)$ equals to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of a stable branching
+	$-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
+	It will be proved in Lemma \ref{lem: LlogL criterion} that under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ criteria, i.e. 
+\[
+	\int_{(1,\infty)} y\log y~\pi(dy) < \infty.
+\]
+
+	In this paper, we will also assume the following:
+\begin{asp}
+\label{asp: Greys condition}
+	The branching mechanism satisfies the Grey's condition, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+\end{asp}
+%end added
+%moved to the nexe section
+%\begin{lem}
+    %Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e.
 there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-    Also, $\psi$ satisfies the $L \log L$ criterion  i.e.,
-\[
-    \int_1^\infty y \log y~\pi(dr)< \infty.
-\]
-\end{lem}
-\begin{proof}
-    { Need a proof.}
-\end{proof}
-}
-    According to \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations}, we have
-\begin{equation}
-    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
+    %Also, $\psi$ satisfies the $L \log L$ criterion  i.e.,
+%\[
+    %\int_1^\infty y \log y~\pi(dr)< \infty.
+%\]
+%\end{lem}
+%\begin{proof}
+    %{ Need a proof.}
+%\end{proof}
+%end moved to the next section
+
+%Deleted
+    %According to \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations}, we have
+%\begin{equation}
+    %\mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
+    %= e^{-\bar v \|\mu\|},
+%\end{equation}
+    %where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
+%End Deleted
+%Added
+	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{distinguish event} $D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has a positive probability, with respect to each $\mathbb P_\mu$ with $\mu \in \mathcal M(\mathbb R^d)$.
+    In fact,
+\begin{equation}
+    \mathbb{P}_{\mu} (D)
     = e^{-\bar v \|\mu\|},
-\end{equation}
-    where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
+    \quad \mu\in \mathcal M(\mathbb R^d),
+\end{equation}
+    where 
+\[
+	\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
+\]
+	is the largest root of $\psi$.
+%End added
+
 	Define
-\begin{equation}\label{meansemigroup}
+\begin{equation}
+\label{eq: meansemigroup}
     P^{\alpha}_t f(x)
@@
     It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
-\begin{equation}\label{eq:meanformula}
+\begin{equation}
+%\label{eq:meanformula}
     \mathbb{P}_{\mu}[\langle f, X_t \rangle]
@@
 \end{equation}
-
- In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
- $$\frac{\langle f, X_t \rangle -G_t}{F_t}$$ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$.
-It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral
- %decomposition.
- decomposition in terms of the spectrum of $L$.
-
- There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses.
-See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes
-% under some certain conditions. 
- under certain conditions. 
- In \cite{ARMP}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{MP2012} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
-% In this two paper, Milo\'s with his coauthor pictured connection 
-These two papers made connections
- between CLT and what they call branching rate regimes.
-In \cite{RSZ}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
-% Moverover, Compare with the results in \cite{ARMP,MP2012}, 
- Moverover, compared with the results in \cite{ARMP,MP2012}, 
- the limit distributions in \cite{RSZ} are non-degenerate. 
-% In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, They also establish 
- In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, Ren, Song and Zhang also established
- a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
-
- All the results described above hold for systems with branching mechanisms with finite variance. %It's a natural  to ask that how to establish 
-It is natural to ask whether there are 
-counterparts of the central limit theorems for branching Markov processes and superprocesses %with infinite variance.  
-with branching mechanisms of infinite variance.
- In \cite{MM}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
-They established some central limit theorems in small and critical branching rate cases,
-%but leave the central limit result unsolved for large rate case. 
-but \cite{MM} contained no central limit result in the branching rate case.
-In this paper, we consider a class of super-OU processes with more general stable branching mechanisms.
-For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MM}.
-For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit
-%theorem, which has no corresponds in \cite{MM}.
-theorem, which has no counterpart in \cite{MM}.
-
-\subsection{OU Semigroup}
-   In this subsection, we recall 
-%   some results on the spectral properties of the OU operator $L$ from \cite{GD}.
-   some spectral properties of the OU operator $L$ from \cite{GD}.
-    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
-    It is known that $\xi$ has an invariant measure
+%Moved to the first Subsection
+    %In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
+%\[
+    %\frac{\langle f, X_t \rangle -G_t}{F_t}
+%\] 
+    %converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. 
+    %It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
+    %There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. 
+    %See \cite{KestenStigum1966A-limit,KestenStigum1966Additional} for supercritical multi-type Galton-Waston processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
+    %In \cite{AdamczakMilos2015CLT}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+    %These two papers made connections between CLT and what they call branching rate regimes. 
+    %In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
+    %Moverover, compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate. 
+    %In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central,RenSongZhang2017Functional}, Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
+    %All the results described above hold for systems with branching mechanisms with finite variance. 
+    %It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
+    %In \cite{MarksMilos2018CLT}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
+They established some central limit theorems in small and critical branching rate cases, but \cite{MarksMilos2018CLT} contained no central limit result in the branching rate case.
+    %In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. 
+    %For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}.
+    %For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit theorem, which has no counterpart in \cite{MarksMilos2018CLT}.
+%End moved to the first subsection
+%Deleted
+%\subsection{OU Semigroup}
+%End Deleted
+    %In this subsection, we recall some spectral properties of the OU operator $L$ from \cite{MetafunePallaraPriola2002Spectrum}.
+    %Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
+    The limiting behavior of the super-OU process is closly related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, on the property of the OU semigoup $(P_t)_{t\geq 0}$.
+
+    We now recall some basic spectral properties of $(P_t)_{t\geq 0}$ from \cite{MetafunePallaraPriola2002Spectrum}.
+    %It is known that $\xi$ has an invariant measure
+    It is known that the OU process $\xi$ has an invariant measure
 \begin{equation}
@@
     \varphi(x)dx
-    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
+    :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
     \quad x\in \mathbb R^d.
 \end{equation}
-    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
+    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. 
+    %$L^2(\varphi)$ is a Hilbert space with inner product
+    Then, $L^2(\varphi)$ is a Hilbert space with inner product
 \begin{equation}
@@
 \end{equation}
-     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-     For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
-    let $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
-    The Hermite polynomials are defined by
+    %Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
+    Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
+    For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+    The \emph{Hermite polynomials} are defined by
 \begin{equation}
@@
 \end{equation}
-    It is known that $(P_t)$ is a strongly continuous semigroup in $L^2(\varphi)$ and $L$ has
-    discrete spectrum $a(L)= \{-bk: k \in \mathbb Z_+\}$.
+    %It is known that $(P_t)$ is a strongly continuous semigroup in $L^2(\varphi)$ and $L$ has discrete spectrum 
+    It is known that the transition semigroup $(P_t)_{t\geq 0}$ of the OU process $\xi$ is a strongly continuous semigroup in $L^2(\varphi)$, and its corresponding generator $L$ has discrete spectrum 
+    %$a(L)= \{-bk: k \in \mathbb Z_+\}$.
+    $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
     For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
-\begin{equation}
+$
     \mathcal{A}_k
     = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
-\end{equation}
+$
     where
@@
     \phi_p(x)
-    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{a}x \Big),
+    %:= \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{a}x \Big),
+    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
     \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
 \end{equation}
-    It is known that
-\begin{equation}\label{semigroupformula}
+    %It is known that
+    In another word,
+\begin{equation}
     P_t\phi_p(x)
@@
 \end{equation}
-    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete 
-    %orthogonal basis for $L^2(\varphi)$.
-    orthonormal basis for $L^2(\varphi)$.
-    Thus, for each $f\in L^2(\varphi)$,
+    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis for $L^2(\varphi)$.
+    Thus, for each $f\in L^2(\varphi)$, we have
 \begin{equation}\label{semicomp1}
     f
-    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
+    %=\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
+    =\sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
     \quad \text{in~} L^2(\varphi).
@@
     Denote by
-\begin{equation}\label{order}
+\begin{equation}
+%\label{order}
     \kappa_f
@@
 \end{equation}
-%    the order of the function $f$ in $L^2(\varphi)$.
-   the order of the function in spectral decomposition \eqref{semicomp1}.
+    %the order of the function in spectral decomposition \eqref{semicomp1}.
+    the order of the function $f$ in its spectral decomposition \eqref{semicomp1}.
     Note that $ \kappa_f\geq 0$.
@@
 \begin{equation}
+\label{eq: polynomial growth function}
     \mathcal{P}
@@
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-\subsection{Main Results}
-We will use $\mathcal M_c(\mathbb R^d)$ to denote the space of all
-finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of the super-OU process.
-In this subsection, we will give the main results of this paper.
-%new
-The results are stated in three separate cases: the large branching rate case,
-critical  branching rate case and small  branching rate case.
-%end new
+%Deleted
+%\subsection{Main Results}
+    %We will use $\mathcal M_c(\mathbb R^d)$ to denote the space of all finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of the super-OU process.
+%End Deleted
+    %In this subsection, we will give the main results of this paper.
+    In this paper, we are mainly interested in the asmptotic behavior of $\langle f, X_t\rangle$ with $f\in \mathcal P$ under the following three cases:
+    %The results are stated in three separate cases: the large branching rate case, critical  branching rate case and small  branching rate case.
+\begin{itemize}
+\item
+    The large branching rate case: $\alpha\beta>\kappa_fb(1+\beta)$;
+\item
+    The critical branching rate case: $\alpha\beta=\kappa_fb(1+\beta)$;
+\item
+    The small branching rate case: $\alpha\beta<\kappa_fb(1+\beta)$.
+\end{itemize}
 
 \subsubsection{Large branching rate case}
-
-For each $p\in \mathbb{Z}_+^d$, we define
-$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
-%  For all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
-%  under the condition
-%   $\alpha\beta>|p|b(1+\beta)$,
+%Added
+    Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
+%End Added
+    For each $p\in \mathbb{Z}_+^d$, define
+\[
+    H_t^p
+    := e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,
+    \quad t\geq 0.
+\]
     If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, 
-   $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
-   $L^{1+\gamma}(\mathbb{P}_{\mu})$ (see Lemma \ref{lemma26}).
+    %$H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ (see Lemma \ref{lemma26}).
+    it will be proved in Lemma \ref{lemma26} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
     Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  \begin{thm}\label{Theorem11}
-     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for
-all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
-     as $t\rightarrow \infty$,
-     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$
+     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, %as $t\rightarrow \infty$,
+\[
+    e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle 
+    %\rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p 
+    \xrightarrow[t\to \infty]{}\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p
+    \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).
+\]
     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
 \end{thm}
+\begin{comment}
     For any $t\geq 0$, let $H_t:=e^{-\alpha t}\|X_t\|$. 
@@
 \begin{rem}
-Let $f \in \mathcal{P}$.  If $\kappa_f=0$,
-    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f, 1\rangle_\phi=\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},
-for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
-     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$
+    Let $f \in \mathcal{P}$.  If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f, 1\rangle_\phi=\langle f,\varphi\rangle$. 
+    Hence by Theorem \ref{Theorem11}, for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
+\[
+    e^{-\alpha t}\langle f, X_t\rangle 
+    \rightarrow \langle f, \varphi\rangle H_{\infty} 
+    \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).
+\]
     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
  \end{rem}
+\end{comment}
+%Moved and modified from below
+Define
+\begin{equation}
+\label{eq: def of N}
+    \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
+\end{equation}
+    and
+\begin{equation}
+\label{eq: def of Cl}
+    \mathcal{C}_l:=\Big\{f\in \mathcal P: f(x)=\sum_{p\in\mathcal{N}}\langle f, \phi_p\rangle_{\varphi}\phi_p(x)\Big\}.
+\end{equation}
+    Define an operator $(I_t)_{t\geq 0}$ on $\mathcal{C}_l$ such that
+\begin{align}\label{definition of Itf}
+    I_tf(x)
+    :=\sum_{p\in \mathcal{N}}\langle f, \phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x), 
+    \quad t\geq 0, x\in \mathbb{R}^d, f\in \mathcal C_l.
+\end{align}
+    It is easy to see that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$.
+    Define
+\begin{align}\label{bar-m}
+   \bar{m}[f]
+   :=\eta \int_{0}^{\infty} e^{\alpha s}~ds \int_{\mathbb R^d} \big(iI_sf(x)\big)^{1+\beta}\varphi(x)~dx,
+   \quad f\in \mathcal C_l.
+\end{align}
+    It will be showed in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$.
+    It will also be proved in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp(\theta \bar m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
+\begin{thm}
+\label{thm: large clt}
+    For $f\in\mathcal{C}_l$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that,
+\begin{align}\label{thm: large rate}
+    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow[t\to \infty]{d}\bar{\zeta},
+\end{align}
+    where $\bar{\zeta}$ is an $(1+\beta)$-stable random variable with characteristic function
+\begin{align}
+    \mathbf{E}[e^{i\theta\bar{\zeta}}]=\exp(\bar{m}[\theta f]),\quad \theta\in \mathbb{R}.
+\end{align}
+\end{thm}
+%End moved from below
 
 \subsubsection{Critical branching rate case}
-    For $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, we define
+    For each $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
 \begin{equation}\label{tilde-m}
-    \widetilde{m}[f]
-%    := \langle \eta (-i\phi)^{1+\beta},\varphi\rangle
-    := \langle \eta (-if_0)^{1+\beta},\varphi\rangle
-\end{equation}
-    where
-%\[
-\begin{equation}\label{phif}
-%    \phi(x)
-    f_0(x)
-    =\sum_{|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x).
-%\]
-\end{equation}
-
+    %\widetilde{m}[f]
+    \tilde{m}[f]
+    %:= \langle \eta (-if_0)^{1+\beta},\varphi\rangle
+    := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
+\end{equation}
+%Deleted
+    %where
+%\begin{equation}\label{phif}
+    %f_0(x)
+    %=\sum_{|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x).
+%\end{equation}
+%End Deleted
+%Added
+    It will be proved in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp(\theta \tilde m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
+%End added
 \begin{thm}
-\label{Theorem12}
-    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$,
-   then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under
-    $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+\label{thm: critical clt}
+    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$, %under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, 
+    under $\mathbb{P}_{\mu}(\cdot|D^c)$, 
+    it holds that
 \[
     \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
-    \xrightarrow{d} \tilde{\zeta},
-    \quad t\rightarrow \infty,
+    %\xrightarrow{d} \tilde{\zeta},
+    %\quad t\rightarrow \infty,
+    \xrightarrow[t\to \infty]{d} \tilde{\zeta},
 \]
     where $\tilde{\zeta}$ is a $(1+\beta)$-stable random variable with
-\[
-    \mathbb{E} [e^{i\theta \tilde{\zeta}}]
+%Added
+    characteristic funciton
+%End Added
+\[
+    %\mathbb{E} [e^{i\theta \tilde{\zeta}}]
+    \mathbf E [e^{i\theta \tilde{\zeta}}]
     =\exp(\widetilde{m}[\theta f]),
-%    \quad \theta\in \mathbb R,
     \quad \theta\in \mathbb R.
 \]
-%where $\widetilde{m}$ is defined by \eqref{tilde-m}.
 \end{thm}
@@
 \subsubsection{Small branching rate case}
-
+\label{msmallcase}
 	For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_f b(1+\beta)$, we define
@@
     m[f]
-    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds. \label{msmallcase}
-\end{equation}
-According to Lemma \ref{Lemma2.7} below, $m[f]$ is well-defined.
+    %=\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds 
+    =\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
+\end{equation}
+	According to Lemma \ref{lem: def of all m} below, $m[f]$ is well-defined.
+%Added
+	It will also be proved in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp(\theta m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
+%End ADDEd
 \begin{thm}
-\label{Theorem13}
-    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$,
-   then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under
-    $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \zeta, \quad t\rightarrow \infty,$$
+\label{thm: small clt}
+    If $f\in\mathcal{P}$ satisfies $\alpha\beta<\kappa_f b(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+\[
+    %\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \zeta, \quad t\rightarrow \infty,
+    \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow[t\rightarrow \infty]{d} \zeta,
+\]
     where $\zeta$ is a $(1+\beta)$-stable random variable with
-    $$\mathbb{E} [e^{i\theta \zeta}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
-%    where $m$ is defined by \eqref{msmallcase}.
+\[
+    %\mathbb{E} [e^{i\theta \zeta}]
+    \mathbf E[e^{i\theta \zeta}]
+    =\exp(m[\theta f]), 
+    \quad \theta\in \mathbb R.
+\]
 \end{thm}
-
-\subsubsection{Further results in the large branching rate case}
+%Deleted
+%\subsubsection{Further results in the large branching rate case}
+%End Deleted
+%Moved to above
+\begin{comment}
     Define
@@
 \end{align}
-%For each fixed $f\in \mathcal{C}_l$, $f$ can be expressed as
     Each $f\in \mathcal{C}_l$ can be expressed as
 \begin{align}\label{discompose}
-    f(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x),\quad x\in \mathbb{R}^d,
+    f(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x),
+    \quad x\in \mathbb{R}^d,
 \end{align}
@@
 \begin{align}\label{definition of Itf}
-    I_tf(x):=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
+    I_tf(x)
+    :=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), 
+    \quad t\geq 0, x\in \mathbb{R}^d.
 \end{align}
@@
 \begin{align}\label{bar-m}
-   \bar{m}[f]:=\int_{0}^{\infty} e^{\alpha s}\langle \eta(iI_sf)^{1+\beta},\varphi\rangle ds.
+   \bar{m}[f]
+   :=\int_{0}^{\infty} e^{\alpha s}\langle \eta(iI_sf)^{1+\beta},\varphi\rangle ds.
 \end{align}
     According to Lemma \ref{lem: control of mn} below, $\bar{m}[f]$ is well-defined.
-\begin{thm}\label{theorem 1.6}
+\begin{thm}\label{thm: large clt}
     For $f\in\mathcal{C}_l$ given by \eqref{discompose} and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that, as $t\to\infty$,
@@
 \end{align}
-%where $\bar{m}$ is defined by \eqref{bar-m}.
 \end{thm}
-
-%RS We should collect our commonly used notation at the end of this section.
+\end{comment}
+%End moved to above
+
+    %{\bf (RS We should collect our commonly used notation at the end of this section.)}
 
 \section{Preliminaries}
-%\subsection{Definition of $h$-controller}
+%Moved and modified from the first section
+\subsection{Branching mechanism}
+\label{sec: branching mechanism}
+	Let $\psi$ be the branching mechanism given by \eqref{eq: honogeneou branching mechanism}. 
+	Suppose that Assumption \ref{asp: branching mechanism} holds. 
+	In this Subsection, we give some preliminary results about the branching mechanism $\psi$.
+	Recall that $\eta$ and $\beta$ are the constants appread in Assumption \ref{asp: branching mechanism}.
+	For each $z\in \mathbb R_+$, define
+\begin{align}
+	\psi_1(z) 
+	&:= \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big)
+	\\&= \int_{(0,\infty)}(e^{-yz}-1+yz) \pi(dy) -  \eta z^{1+\beta}.
+\end{align}
+	Let $\mathbb C_+:= \{x+iy: x\in \mathbb R_+, y \in \mathbb R\}$ and $\mathbb C^0_+:= \{x+iy: x\in (0,\infty), y \in \mathbb R\}$.
+\begin{lem}
+\label{lem: complex extension for psi1}
+	Function $\psi_1$ on $\mathbb R_+$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomophic on $\mathbb C^0_+$. 
+	%Moreover, there exist constants $c,\delta >0$ such that for each $z\in \mathbb C_+$, we have
+	Moreover, for each $\delta > 0$ small enough, there exist constant $c>0$ such that for each $z\in \mathbb C_+$, we have
+$
+	|\psi_1(z)| \leq c |z|^{1+\beta+\delta} + c|z|^2.
+$
+\end{lem}
+\begin{proof}
+	For each $\sigma$-finite signed measure $\mu$, denote by $|\mu|$ the total variation measure of $\mu$.	
+	According to Lemma \ref{lem: extension lemma for branching mechanism} and the identity theorem for holomorphic functions, we have that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomophic on $\mathbb C^0_+$.
+	The extended $\psi_1$ has the following form:
+\[
+	\psi_1(z)= \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big),
+	\quad z\in \mathbb C_+.
+\]
+	Now, according to  Assumption \ref{asp: branching mechanism} and Remark \ref{rem: small enough delta}, for each small enough $\delta > 0$, we have
+\begin{align}
+	|\psi_1(z)| 
+	&\leq \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|
+	\\&\leq  |z|^2\int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| 
+	\\&\quad + |z|^{1+\beta +\delta}\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|,
+\end{align}
+	as desired.
+\end{proof}
+
+	We then give a Lemma which says that the constants $\eta, \beta$ appread in Asumption \ref{asp: branching mechanism} is uniquelly determined by the L\'evy measure $\pi$.
+\begin{lem}
+\label{lem: unique of beta and eta}
+	Suppose that there are constants $\eta'>0, \beta'\in (0,1)$ and $\delta' > 0$ such that
+\[
+	 \int_{(1,\infty)}y^{1+\beta' +\delta'}~\Big|\pi(dy)-\frac{\eta'~dy}{\Gamma(-1-\beta)y^{2+\beta'}}\Big| <\infty.
+\]
+	Then $\eta'= \eta$ and $\beta ' = \beta$.
+\end{lem}
+\begin{proof}
+	Let $\delta> 0$ be the constant appread in Assumption \ref{asp: branching mechanism}.
+	Without loss of generality, we assume that $\beta+\delta \leq \beta'+ \delta'$.
+	According to the fact that $y^{1+\beta+ \delta} \leq y^{1+\beta'+\delta'}$ with $y \geq 1$, we have
+\[
+	\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy)-\frac{\eta'~dy}{\Gamma(-1-\beta)y^{2+\beta'}}\Big| <\infty.
+\]
+	Compare this to Assumption \ref{asp: branching mechanism}, we have
+\[
+	\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}-\frac{\eta'~dy}{\Gamma(-1-\beta)y^{2+\beta'}}\Big| <\infty.
+\]
+	In another word, if we denote by $\tilde \pi(dy)$ the measure $\eta' \Gamma(-1-\beta)^{-1} y^{-2-\beta'} dy$, then $\tilde \pi$ is a L\'evy measure which satisfies the Assumption \ref{asp: branching mechanism}.
+	Applying Lemma \ref{lem: complex extension for psi1} to this measure $\tilde \pi$, we have that there exists $c>0$ such that
+\[
+	|\eta z^{1+\beta} - \eta' z^{1+\beta'} | 
+	\leq cz^{1+\beta+ \delta}+cz^2,
+	\quad z \in \mathbb R_+.
+\]
+	Dividing each side by $z^{1+\beta}$ we have
+\[
+	|\eta - \eta' z^{1+\beta' - \beta} | 
+	\leq cz^{\delta}+cz^{1-\beta},
+	\quad z \in \mathbb R_+.
+\]
+	This implies that
+\[
+	\eta' z^{1+\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0.
+\]
+	So we must have $\beta'= \beta$ and $\eta'= \eta$.
+\end{proof}
+
+	We also have the following result:
+\begin{lem}
+\label{lem: LlogL criterion}
+    $\psi$ satisfies the $L \log L$ criterion, i.e.
+\[
+    \int_{(1,\infty)} y \log y~\pi(dy)< \infty.
+\]
+\end{lem}
+\begin{proof}
+	According to Assumption \ref{asp: branching mechanism} and the fact that $y\log y \leq y^{1+\beta+\delta}$ for $y$ large enough, we have
+\[
+	\int_{(1,\infty)}y\log y~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty.
+\]
+	Therefore, we have
+\[
+	\int_{(1,\infty)}y\log y~\Big(\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big) < \infty.
+\]
+	Noticing that
+\[
+	\int_{(1,\infty)}\frac{\eta \log y~dy}{\Gamma(-1-\beta)y^{1+\beta}} < \infty,
+\]
+	so we have the desired result.
+\end{proof}
+%End moved and modified from the first section
 \subsection{Definition of controller}
+%New added
+	Denote by $\mathcal B(\mathbb R^d, \mathbb C)$ the space of all $\mathbb C$-valued Borel measurable functions on $\mathbb R^d$.
+	Recall that $\mathcal P$ is given by \eqref{eq: polynomial growth function}.
+%End new added
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
-    For any function $h: [0,\infty) \to [0,\infty)$, we say an operator 
-%   $R$ is an $h$-controller if
- $R: \mathcal P^+ \to \mathcal P^+$  is an $h$-controller if
+    For any function $h: [0,\infty) \to [0,\infty)$, we say an operator $R: \mathcal P^+ \to \mathcal P^+$ is an \emph{$h$-controller} if
 \begin{itemize}
-%\item
-%    $R: \mathcal P^+ \to \mathcal P^+$;
-\item
-%    $f, g\in \mathcal P^+$ and $f\leq g$ implies that $Rf \leq Rg$; and
+\item
     $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and
 \item
-    $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ 
-%    implies that $ R (\theta f)\leq h(\theta) Rf$.
-    imply that $ R (\theta f)\leq h(\theta) Rf$.
+    $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
 \end{itemize}
-
-    For any function $h: [0,\infty) \to [0,\infty)$ and $\mathcal D \subset \mathcal P^*$, 
-%    we say $A$ is an \emph{$h$-controllable} operator on $\mathcal D$ if
-we say that $A : \mathcal D \to \mathcal P^*$ is an \emph{$h$-controllable} operator on $\mathcal D$ if
-%\begin{itemize}
-%\item
-%    $A : \mathcal D \to \mathcal P^*$;
-%\item
-%    There exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
-%\end{itemize}
-there exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
-    We also say the operator $A$ is \emph{$h$-controlled by $R$ on $\mathcal D$} in this case.
-
-%    We say a family of operators $(A_s)_{s\in \Lambda}$
-   We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$
-     is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
-
-    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, we define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
-
-%    For any $a \in \mathbb R$, suppose that 
-    For any $a \in \mathbb R$ and any operator
-    $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, we define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
-
-\begin{lem}
-    \label{lem: property of controllable operators}
-    Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$.
+    %For any function $h: [0,\infty) \to [0,\infty)$ and $\mathcal D \subset \mathcal P^*$, we say that $A : \mathcal D \to \mathcal P^*$ is an \emph{$h$-controllable} operator on $\mathcal D$ if there exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
+    %We also say the operator $A$ is \emph{$h$-controlled by $R$ on $\mathcal D$} in this case.
+    For a subset $\mathcal D$ of $\mathcal P^*$ and an $h$-controller $R$, we say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controlled by $R$ on $\mathcal D$} if $|Af| \leq R|f|$ for each $f\in \mathcal D$.
+    We say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controllable} if there exists an $h$-controller $R$ such that $A$ is $h$-controlled by it.
+     We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
+
+    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
+    For any $a \in \mathbb R$ and any operator $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
+\begin{lem}\label{lem: property of controllable operators}
+    %Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$. 
+    Suppose that $\Lambda$ is an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$. 
     Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
@@
 \item[(1)]
-    Suppose that $(\Lambda, \mathscr F)$ is a measurable space
-    and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
+    Suppose that $(\Lambda, \mathscr F)$ is a measurable space and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
     For any probability measure $\nu$ on $(\Lambda, \mathscr F)$,  we write
 \[
-    A_\nu f(x):= \int_{\Lambda} A_\lambda f (x)~\nu(d\lambda), \quad f\in \mathcal D, x\in \mathbb R^d.
+    A_\nu f(x)
+    := \int_{\Lambda} A_\lambda f (x)~\nu(d\lambda), 
+    \quad f\in \mathcal D, x\in \mathbb R^d.
 \]
@@
 \item[(4)]
-    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
+    Let $a>0$. 
+    Suppose that, for each $\lambda \in \Lambda$, $A_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
     Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable.
@@
 \begin{proof}
-    (1).
-Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
+    (1). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$. 
     For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
@@
     Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D_0$.
-%    We verify the following:
     Then we have
@@
 \item
-    If $f,g \in \mathcal D_0$ with $|f|\leq |g|$, then $R_AR_B|f| \leq R_A R_B |g|$.
-\item
-    If $f \in \mathcal D_0$ and $\theta \in [0,\infty)$, then $R_AR_B|\theta f| \leq R_A(g(\theta) R_B|f|) \leq (h\circ g)(\theta) R_A R_B |f| $.
+    %If $f,g \in \mathcal D_0$ with $|f|\leq |g|$, then $R_AR_B|f| \leq R_A R_B |g|$.
+    If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_AR_Bf \leq R_A R_B g$.
+\item
+    %If $f \in \mathcal D_0$ and $\theta \in [0,\infty)$, then $R_AR_B|\theta f| \leq R_A(g(\theta) R_B|f|) \leq (h\circ g)(\theta) R_A R_B |f| $.
+    If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_AR_B(\theta f) \leq R_A(g(\theta) R_Bf) \leq (h\circ g)(\theta) R_A R_B f $.
 \end{itemize}
@@
     Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
-%
-%    We verify the following:
+
     Then we have
@@
 \item
-    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R_A\times R_B|f| \leq R_A\times R_B |g|$.
-\item
-    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R_A\times R_B|\theta f| \leq h(\theta) g(\theta) (R_A \times R_B) |f| $.
+    %If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R_A\times R_B|f| \leq R_A\times R_B |g|$.
+    If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_A\times R_Bf \leq R_A\times R_B g$.
+\item
+    %If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R_A\times R_B|\theta f| \leq h(\theta) g(\theta) (R_A \times R_B) |f| $.
+    If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_A\times R_B (\theta f) \leq h(\theta) g(\theta) (R_A \times R_B) f $.
 \end{itemize}
@@
 
-%    We also verify the following:
     We also have the following:
@@
 \item
-    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $(R_A + R_B)|f| \leq (R_A + R_B) |g|$.
-\item
-    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $(R_A + R_B) |\theta f| \leq h(\theta) R_A|f| + g(\theta) R_B|f| \leq (h(\theta) \vee g(\theta)) (R_A+R_B)|f| $.
+    %If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $(R_A + R_B)|f| \leq (R_A + R_B) |g|$.
+    If $f,g \in \mathcal P^+$ with $f\leq g$, then $(R_A + R_B)f \leq (R_A + R_B) g$.
+\item
+    %If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $(R_A + R_B) |\theta f| \leq h(\theta) R_A|f| + g(\theta) R_B|f| \leq (h(\theta) \vee g(\theta)) (R_A+R_B)|f| $.
+    If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $(R_A + R_B) (\theta f) \leq h(\theta) R_Af + g(\theta) R_Bf \leq (h(\theta) \vee g(\theta)) (R_A+R_B)f $.
 \end{itemize}
@@
     (4). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
-%    We verify the following:
     then we have the following:
@@
 \item
-    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R^{\times a}|f| \leq R^{\times a} |g|$.
-\item
-    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R^{\times a}|\theta f| \leq (h(\theta) R |f|)^a = h(\theta)^a R^{\times a}|f|$.
+    %If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R^{\times a}|f| \leq R^{\times a} |g|$.
+    If $f,g \in \mathcal P^+$ with $f\leq g$, then $R^{\times a}f \leq R^{\times a} g$.
+\item
+    %If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R^{\times a}|\theta f| \leq (h(\theta) R |f|)^a = h(\theta)^a R^{\times a}|f|$.
+    If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R^{\times a}(\theta f) \leq (h(\theta) R f)^a = h(\theta)^a R^{\times a}f$.
 \end{itemize}
@@
 \subsection{h-controller  for super-OU processes}
-Let $X$ be the super-OU process introduced in Subsection 1.1.
-We define $\psi_0(z)=\psi(z)+\alpha z$, $z\in \mathbb{C}_+$, and define the following operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$:
+    %Let $X$ be the super-OU process introduced in Subsection 1.1. 
+    Let $X$ be the super-OU process introduced in Subsection \ref{sec: main results} with its branching mechanism $\psi$ satisfying \ref{asp: branching mechanism} and \ref{asp: Greys condition}. 
+%Added
+	In this subsection, we will give several operators and their properties that will be used in this paper.
+%End added
+
+    %We define $\psi_0(z)=\psi(z)+\alpha z$ for each $z\in \mathbb{C}_+$, and define the following operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$: 
+    Define $\psi_0(z)=\psi(z)+\alpha z$ for each $z\in \mathbb{R}_+$. 
+%Added
+    According to a similar arguement to Lemma \ref{lem: complex extension for psi1}, similar to function $\psi_1$, both functions $\psi$, $\psi_0$ can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomophic on $\mathbb C^0_+$.
+%End added
+    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define 
 \begin{equation}\begin{split}
@@
     \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x)
-    \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big),
-    \quad  f\in \mathcal B(\mathbb R^d, \mathbb C_+), x\in \mathbb R^d.
-\end{split}\end{equation}
-For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, 
-%recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$,
-let $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$ be 
-the value of the characteristic exponent of the infinitely divisible random variable
-$\langle f, X_t\rangle$ at $1$.
+    %\\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big),
+    %\quad  f\in \mathcal B(\mathbb R^d, \mathbb C_+), x\in \mathbb R^d.
+    \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big).
+\end{split}\end{equation}
+    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let \[U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}\] be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
     From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
@@
 \end{split}\end{equation}
-If we  let
+    %If we let
+    For each $t\geq 0$ and $f\in \mathcal P$, define
 \begin{equation}\begin{split}
@@
     \\ K_t f
-    &:= (Z'_t - Z_t+ Z''_t)f,
-\end{split}\end{equation}
-    then we have that
+    &:= (Z'_t - Z_t+ Z''_t)f.
+\end{split}\end{equation}
+    %then we have that
+    Then we have that
 \[
@@
     = Z'_t + Z''_t
-    = Z_t+ (Z'_t - Z_t) + Z''_t
+%Deleted
+    %= Z_t+ (Z'_t - Z_t) + Z''_t
+%End deleted
     = Z_t+K_t, \quad t\geq 0.
 \]
+%Moved and modified from below
+	For all $k \in \mathbb Z_+$ and $f\in \mathcal P$, define
+\begin{equation}\label{Q_k}
+    Q_k f 
+    := \sup_{t\geq 0} e^{k b t}|P_t f|
+\end{equation}
+    and
+\begin{equation}\label{Q}
+    Q f:= Q_{\kappa_f}f.
+\end{equation}
+    Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
+%End moved and modified from below
 
@@
 \label{lem: upper bound for usgx}
-    Under Assumption \ref{asp: branching mechanism}, the following statements are true:
+    %Under Assumption \ref{asp: branching mechanism}, the following statements are true:
+    Under Assumption \ref{asp: branching mechanism} and \ref{asp: Greys condition}, the following statements are true:
 \begin{itemize}
@@
 \item[(3)]
-    $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
+    %$\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
+    $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
 \item[(4)]
@@
 \item[(5)]
-    $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+    %$(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+    $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable on $\mathcal P$.
 \item[(6)]
-    There is a constant $\delta > 0$ such that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+    %There is a constant $\delta > 0$ such that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+    For each $\delta > 0$ small enough, we have $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
 \item[(7)]
-    There is a constant $\delta > 0$ such that $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+    %There is a constant $\delta > 0$ such that $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+    For each $\delta > 0$ small enough, we have $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
 \end{itemize}
@@
 \begin{proof}
-    (1). According to \eqref{eq: -v has positive real part}, 
-%    $U_t: \mathcal P \to \mathcal B(\mathbb R^d, \mathbb C_+)$.
-   $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
+    (1). According to \eqref{eq: -v has positive real part}, $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
     It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
@@
 \]
-    Note that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.
+%Added
+    Note that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a map from $\mathcal P^+$ to $\mathcal P^+$, since if $f\in \mathcal P^+$, there exists constant $c>0$ such that
+\[
+	0
+	\leq \sup_{0\leq u\leq 1}P^{\alpha}_u f
+	\leq \sup_{0\leq u\leq 1} P_u (e^{\alpha u} e^{-\kappa_f u} e^{\kappa_f u} f )
+	\leq c \sup_{0\leq u\leq 1} (e^{\kappa_fu}P_u f) \leq c Qf \in \mathcal P.
+\]
+%End added
+	%Note that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.
+	It is also clear that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.
 
@@
 
-    (3). Let $C>0$ and $\delta > 0$ be the constants in Assumption \ref{asp: branching mechanism}.
-    For each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
+    (3). 
+    %Let $C>0$ and $\delta > 0$ be the constants in Assumption \ref{asp: branching mechanism}.
+    %For each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
+    According to Lemma \ref{lem: complex extension for psi1}, there exist constants $C, \delta >0$ with $1+\beta+\delta< 2$, such that for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
 \begin{equation}\begin{split}
@@
     \leq \eta |f|^{1+\beta} + |\Psi_1 f|
-    \leq \eta |f|^{1+\beta} + C|f|^2+ C|f|^{1+\beta + \delta}.
+    \leq \eta |f|^{1+\beta} + C|f|^2+ C |f|^{1+\beta + \delta}.
 \end{split}\end{equation}
@@
 
-%    (4). From (1), (2), (3) 
-        (4). From parts (1)--(3) of this lemma 
-    and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
+    (4). From parts (1)--(3) of this lemma and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
 \[
     f
-    \mapsto P^\alpha_{t-s}\Psi_0(-U_sf)(x),
+    %\mapsto P^\alpha_{t-s}\Psi_0(-U_sf)(x),
+    \mapsto P^\alpha_{t-s}\Psi_0(-U_sf),
     \quad 0\leq s\leq t\leq 1
@@
 \]
-%    Now using (1), (2), (4) 
-   Now using parts (1), (2) and  (4) of this lemma, 
-    and Lemma \ref{lem: property of controllable operators}.(3)--(4), we get that
+    Now using parts (1), (2) and  (4) of this lemma, and Lemma \ref{lem: property of controllable operators}.(3)--(4), we get that operators
 \[
@@
 
-    (6). Suppose that $C>0, \delta>0$ are the constants in Assumption \ref{asp: branching mechanism}.
-    Noticing that
+    (6). %Suppose that $C>0, \delta>0$ are the constants in Assumption \ref{asp: branching mechanism}.
+    %Noticing that
+    According to Lemma \ref{lem: complex extension for psi1}, for each $\delta > 0$ small enough, there exists a constant $C>0$ such that
 \[
@@
     \le C(|f|^2+|f|^{1+\beta+ \delta}),
-    \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)
-\]
-    and that
+    \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+).
+\]
+    %and that
+    Note that, for each $\delta, C>0$,
 \[
@@
 \]
-    is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllor, we have that $\Psi_1$ is $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-    According to this, parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we have that
+    %is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllor, we have that $\Psi_1$ is $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
+    is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllor. 
+    Therefore, for each $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
+    %According to this, parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we have that
+    According to this, parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we have that, for each $\delta > 0$ small enough, operators
 \[
@@
 
-\subsection{Parameters of the stable limits}
-   Define
- \begin{equation}\begin{split}
- \label{parameter_mk}
+%\subsection{Parameters of the stable limits}
+\subsection{Stable distributions}
+%Deleted    
+    %Define
+%\begin{equation}\label{parameter_mk}\begin{split}
+    %m_t[f]
+    %:=e^{-\alpha (t+1)} \int_{\mathbb R^d}(Z_1P^\alpha_t f)(x)\cdot \varphi(x)~dx,
+    %\quad t\geq 0, f\in \mathcal P.
+%\end{split}\end{equation}
+
+    %We first collect some lemmas from \cite{MarksMilos2018CLT}, which will be used in this paper.
+%\begin{lem}{\cite[Lemma 2.7]{MarksMilos2018CLT}}\label{lem: def of all m} 
+    %For each $f\in\mathcal{P}$, there is a constant $C>0$ such that
+%\begin{equation}\label{domi-m}
+    %|m_t[f]|
+    %\leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
+    %\quad t\geq 0.
+%\end{equation}
+%\end{lem}
+%End Deleted
+%Added
+    In this subsection, we will show that the $(1+\beta)$-stable random variables appreared in Theorem \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
+
+    In the following Lemma, recall that $(P^\alpha_t)_{t\geq 0}$ is given by \eqref{eq: meansemigroup}, $\mathcal P$ is given by \eqref{eq: polynomial growth function}, $\mathcal N$ is given by \eqref{eq: def of N} and $\mathcal C_l$ is given by \eqref{eq: def of Cl}.
+\begin{lem}
+\label{lem: def of all m} 
+\begin{enumerate}
+\item 
+	Suppose that $f\in\mathcal{P}$. Then the following integrals are well defined:
+\[
 	m_t[f]
-      :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
- \end{split}\end{equation}
-
- We first collect some lemmas from \cite{MM}, which will be used in this paper.
- \begin{lem}(\cite[Lemma 2.7]{MM})\label{Lemma2.7} For each $f\in\mathcal{P}$, there is a constant $C>0$ such that
+    %:=e^{-\alpha (t+1)} \int_{\mathbb R^d}(Z_1P^\alpha_t f)(x)\cdot \varphi(x)~dx,
+    := \eta \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} (-iP_{s}^\alpha f(x))^{1+\beta} \varphi(x)~dx, 
+    \quad t\geq 0.
+\]
+	Furthermore, there exists a constant $C>0$ such that
 \begin{equation}\label{domi-m}
@@
 \end{equation}
+\item 
+    Suppose that $f\in\mathcal C_l$. Then the following integrals are well defined:
+\[
+    \bar{m}_t[f]
+    := \eta \int_{t}^{t+1} e^{\alpha s}~ds \int_{\mathbb R^d}\big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx.
+\]
+    Furthermore, there exists a constant $C>0$ such that
+\begin{equation}
+    |\bar{m}_t[f]| \leq C e^{-(\alpha\beta-K(1+\beta)b)t}, \quad t\geq 0.
+\end{equation}
+\item
+    Suppose that $f \in \mathcal C_l$. 
+    Then the following integral is well defined:
+\[
+    \bar{m}[f]
+   :=\eta \int_{0}^{\infty} e^{\alpha s}~ds \int_{\mathbb R^d} \big(iI_sf(x)\big)^{1+\beta}\varphi(x)~dx.
+\]
+    Furthermore, we have
+\[
+    \bar{m}[f]
+    =\sum_{n=0}^{\infty}\bar{m}_n[f].
+\]
+\item
+	Suppose that $f \in \mathcal{P}$ satisfies that $\alpha\beta=\kappa_f b(1+\beta)$. Then the following integral is well defined:
+\[
+	\tilde{m}[f]
+    := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
+\]
+	Furthermore, we have
+\[
+	\widetilde{m}[f] = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
+\]
+\item
+	Suppose that $f\in \mathcal{P}$ satisfies $\alpha\beta<\kappa_fb(1+\beta)$. 
+	Then the following integral is well defined:
+\[
+    m[f]
+    :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
+\]
+	Furthermore, we have
+\[    
+	m[f]
+    =\sum_{k=0}^\infty m_k[f].
+\]
+\end{enumerate}
 \end{lem}
- Recall the definition of $\widetilde{m}$ in \eqref{tilde-m}.
-  \begin{lem}(\cite[Lemma 4.2]{MM})
-    If $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
-    then
-\begin{equation}\begin{split}
-\label{para: critical case}
-% \widetilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
-\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=
- \widetilde{m}[f].
-\end{split}\end{equation}
-%    where
+\begin{proof}
+    (1). See \cite[Lemma 2.7]{MarksMilos2018CLT}.
+
+    (2). We first cliam that there exists $h\in \mathcal{P}$ such that for each $t\geq 0$,
+\[
+    |I_tf(x)|
+    \leq e^{-(\alpha-Kb)t}h(x),
+    \quad t\geq 0, x\in \mathbb{R}^d.
+\]
+    In fact, put $h:= \sum_{p\in \mathcal N} |\langle f,\phi_p\rangle_{\varphi}\phi_p|$, then
+\[
+    |I_tf(x)|
+    =\Big|\sum_{p\in\mathcal{N}} \langle f,\phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x)\Big|
+    \leq e^{-(\alpha-Kb)t}h(x),
+    \quad t\geq 0,x\in \mathbb{R}^d.
+\]
+    Therefore, there exists constant $C>0$ such that
+\begin{align}
+    &|\bar{m}_t[f]|
+    \leq \eta \int_{t}^{t+1} e^{\alpha s}~ds \int_{\mathbb R^d} | I_sf(x)|^{1+\beta}\varphi(x)~dx
+    \\&\leq \int_{t}^{t+1} e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}~ds\int_{\mathbb R^d} h(x)^{1+\beta}\varphi(x)~dx
+    \\&\leq C e^{-(\alpha\beta-K(1+\beta)b)t},
+    \quad t\geq 0.
+\end{align}
+
+    (3). This is obvious from (2), noticing that $\alpha\beta>K(1+\beta)b$.
+
+    (4). See \cite[Lemma 4.2]{MarksMilos2018CLT}.
+
+    (5). This is obvious from (1).
+\end{proof}
+%End added
+%Deleted
+    %Recall the definition of $\widetilde{m}$ in \eqref{tilde-m}.
+%\begin{lem}(\cite[Lemma 4.2]{MarksMilos2018CLT})
+    %If $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, then
+%\begin{equation}\begin{split} \label{para: critical case}
+    %\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]
+    %=\widetilde{m}[f].
+%\end{split}\end{equation}
+%\end{lem}
+%End Deleted
+%Moved and modified from below
+    The following proposition says that $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\bar m[f]$ and $\tilde m[f]$ are all related to some $(1+\beta)$-stable distribution. 
+\begin{prop}
+\label{prop: alpha stable rv}
+    For all $t\geq 0$ and $f\in \mathcal P$,
+\begin{enumerate}
+\item
+\label{item: stable 1}
+    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable;
+\item 
+\label{item: stable 2}
+    $\theta \mapsto \exp(\bar{m}_t[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$.
+\item 
+\label{item: stable 3}
+    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$.
+\item
+\label{item: stable 4}
+    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
+\item
+\label{item: stable 5}
+    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
+\end{enumerate}
+\end{prop}
+%End moved and modified from below
+%Moved below
+%\begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MarksMilos2018CLT})
+    %For each $f\in \mathcal{P}$, let
+%\begin{align}
+    %g_k
+    %:= \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
+    %\quad k \geq 0.
+%\end{align}
+    %Then there exists $h\in \mathcal{P}$ such that
+%\begin{align}
+    %|P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
+%\end{align}
+%\end{lem}
+%
+%\begin{lem}\label{control of gn} Suppose that $g\in \mathcal{C}_l$.
+    %Put
+%\begin{align}
+    %\bar{g}_t
+    %:=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
+%\end{align}
+    %Then there exists $h\in \mathcal{P}$ such that
+%\begin{align}
+    %|P_s\bar{g}_t|
+    %\leq e^{-bs}h,\quad s\geq 0, t\geq 0.
+%\end{align}
+%\end{lem}
+%\begin{proof}
+    %The proof  is similar to that of \cite[Lemma 2.8]{MarksMilos2018CLT}.
+%\end{proof}
+%End moved below
+    %The next lemma is a criterion of $(1+\beta)$-stable distribution.
+    This proposition says that the $(1+\beta)$-stable random variables appreared in Theorem \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined. 
+    The proof of this proposition relies on the following lemma:
+\begin{lem}
+\label{lem: charactreisticfunction}
+    Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
+    Then 
+\[
+    \theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},
+    \quad \theta \in \mathbb R^d
+\]
+    is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
+\end{lem}
+\begin{proof}
+    It follows from measure theory that there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
+\[
+    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
+    f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+\]
+    We define another measure $\lambda_0$ on $S$ by
+\[
+    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi)
+\]
+    %where $\Gamma$ is the $\Gamma$ function, see eqref{eq: definition of Gamma function}.
+    where $\Gamma$ is the Gamma function.
+    Then $\lambda_0$ is a non-zero finite measure, since
+\begin{align}
+    &\lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt)
+    \\&= \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
+\end{align}
+    Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
+\[
+    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
+\]
+    %Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\`evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is 
+    Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\'evy measure of an $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is
+\[
+    \hat \mu(\theta)
+    =\exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\},
+%added
+    \quad \theta \in \mathbb R.
+%End added
+\]
+	%Finally,
+    Fimally, according to \eqref{eq: stable branching on C+}, we have
+\begin{equation}\begin{split}
+    &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
+    = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}
+    \\& = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt)
+    \\& = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
+    = \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)
+    \\& = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
+    \qedhere
+\end{split}\end{equation}
+\end{proof}
+%Deleted
+    %For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$, according to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and thus
+%\begin{equation}\label{sum-m}
+    %m[f]
+    %:=\sum_{k=0}^\infty m_k[f]
+    %=\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
+%\end{equation}
+%End Deleted
+%Moved and modified above
+%\begin{prop}
+%\label{prop: alpha stable rv}
+	%For all $t\geq 0$ and $f\in \mathcal P$,
+%\begin{enumerate}
+%\item
+%\label{item: stable 1}
+    %$\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
+%\item
+%\label{item: stable 4}
+    %$\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
+%\item
+%\label{item: stable 5}
+    %$\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
+%\end{enumerate}
+%\end{prop}
+%End moved and modified above
+\begin{proof}[Proof of Proposition \ref{prop: alpha stable rv}]
+    \eqref{item: stable 1}.
+	Fix $t\geq 0$ and $f\in \mathcal P$.
+	Note that $m_t[\theta f]$ can be rewritten as
+\[
+    m_t[\theta f]
+    %= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x) \int_0^1 P_{1-s}^\alpha \left(\eta(-i\theta P_{s+t}^\alpha f)^{1+\beta}\right)(x)~ds,
+    = \eta \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} \big(-i\theta (P_{s}^\alpha f)(x)\big)^{1+\beta} \varphi(x)~dx,
+    \quad \theta \in \mathbb R.
+\]
+	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
+\begin{equation}
+\label{eq: what I want to proof}
+	%\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds
+    \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} | P_{s}^\alpha f(x)|^{1+\beta} \varphi(x)~dx
+    < \infty.
+\end{equation}
+	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),  
+    %we know that $ g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds$ is a $(1+\beta)$-controllable operator on $\mathcal P$.
+    we know that \[ g \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f|^{1+\beta}~ds\] is a $(1+\beta)$-controllable operator on $\mathcal P$.
+	%This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
+    This implies that \[ x \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f(x)|^{1+\beta}~ds\] is an element of $\mathcal P$.
+	Therefore \eqref{eq: what I want to proof} is true.
+
+    %The proofs of \eqref{item: stable 4} and \eqref{item: stable 5} are similar to that of \eqref{item: stable 1}.
+    The proofs of \eqref{item: stable 2}, \eqref{item: stable 3}, \eqref{item: stable 4} and \eqref{item: stable 5} are similar to that of \eqref{item: stable 1}.
+\end{proof}
+%Moved and modified above
+    %Recall that
+%\begin{align}
+    %\mathcal{N}
+    %=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
+%\end{align}
+    %and
+%\begin{align}
+    %\mathcal{C}_l
+    %=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
+%\end{align}
+%
+    %For each $g\in \mathcal{C}_l$ we have the following expression:
 %\[
-%    \phi
-%    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
+    %g(x)
+    %=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.
 %\]
-\end{lem}
-
-\begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MM})
+    %Also recall that $I_tg(x)$ is defined by
+%\begin{align}
+    %I_tg(x)
+    %=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
+%\end{align}
+    %Define
+%\begin{align}
+    %K=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
+%\end{align}
+%End moved and modified above
+%Deleted
+%\begin{lem}\label{lem: control of Isg}
+    %For each $g\in \mathcal{C}_l$, there exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
+%\begin{align}
+    %|I_tg(x)|
+    %\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
+%\end{align}
+%\end{lem}
+%\begin{proof}
+    %Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  
+    %Put $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$. 
+    %Then
+%\begin{align}
+    %|I_tg(x)|
+    %=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|
+    %\leq e^{-(\alpha-Kb)t}h(x),
+    %\quad t\geq 0,x\in \mathbb{R}^d.
+%\end{align}
+%\end{proof}
+%End Deleted
+%Deleted
+    %For each  $n\geq 1$, let
+%\begin{align}
+    %\bar{m}_n[g]
+    %:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds.
+%\end{align}
+%\begin{lem}\label{lem: control of mn}
+    %For each $g\in \mathcal{C}_l$,  there exists constant $C>0$ such that
+%\begin{align}
+    %|\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1,
+%\end{align}
+    %which implies that
+%\begin{equation}\label{sum-bar-m}
+    %\bar{m}[g]
+    %:=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds
+    %=\sum_{n=1}^{\infty}\bar{m}_n[g]
+%\end{equation}
+    %is well-defined.
+%\end{lem}
+%\begin{proof}
+    %Let $h$ be the function in Lemma \ref{lem: control of Isg}. Then
+%\begin{align}
+    %&|\bar{m}_n[g]|
+    %\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds
+    %\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
+    %&\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle
+    %\leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
+%\end{align}
+    %Using  the fact that $\alpha\beta>K(1+\beta)b$, we easily get $\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
+%\end{proof}
+%End Deleted
+%Deleted
+%\begin{prop}\label{cor: alpha stable rv 1}
+    %For all $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
+%\begin{enumerate}
+%\item \label{item: stable 2}
+    %$\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
+%\item \label{item: stable 3}
+    %$\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable.
+%\end{enumerate}
+%\end{prop}
+%\begin{proof}
+    %The proof is similar to that of Proposition \ref{prop: alpha stable rv}. We omit the details here.
+%\end{proof}
+%End Deleted
+%Moved and modified from above
+%Added
+    Before we end this subsection, we also give the following two lemmas which are useful:
+%End Added
+\begin{lem}{\cite[Lemma 2.8]{MarksMilos2018CLT}}\label{lem: control of gk}
     For each $f\in \mathcal{P}$, let
@@
 \begin{align}
-        \bar{g}_t:=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
+    \bar{g}_t
+    :=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
 \end{align}
@@
 \begin{align}
-        |P_s\bar{g}_t|\leq e^{-bs}h,\quad s\geq 0, t\geq 0.
+    |P_s\bar{g}_t|
+    \leq e^{-bs}h,\quad s\geq 0, t\geq 0.
 \end{align}
@@
 \begin{proof}
-    The proof  is similar to that of \cite[Lemma 2.8]{MM}.
+    The proof  is similar to that of \cite[Lemma 2.8]{MarksMilos2018CLT}.
+    {\bf ZS: Jianjie says he will give more details about this.}
 \end{proof}
-
-The next lemma is a criterion of $(1+\beta)$-stable distribution.
-
-\begin{lem}
-\label{lem: charactreisticfunction}
-    Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
-    Then $$\theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},\quad \theta \in \mathbb R^d$$
-    is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
-\end{lem}
-\begin{proof}
-%    From measure theory, 
-It follows from measure theory that
-    there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
-\[
-    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
-    f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
-\]
-%Recall the definition of $\Gamma$ function in \eqref{eq: definition of Gamma function}, and define another measure $\lambda_0$ on $S$ by
-We define another measure $\lambda_0$ on $S$ by
-\[
-    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi)
-\]
-where $\Gamma$ is the $\Gamma$ function, see eqref{eq: definition of Gamma function}.
-    Then $\lambda_0$ is a non-zero finite measure, since
-\[
-    \lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt)
-    = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
-\]
-    Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
-\[
-    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
-\]
-    Then, according to \cite[Remark 14.4]{Sato1999Levy}, $\nu$ is the L\`evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is \[\hat \mu(\theta)=\exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\}.\]
-	Finally,
-\begin{equation}\begin{split}
-    &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
-    = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}
-\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt)
-\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
-= \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)
-\\&\quad = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
-\qedhere
-\end{split}\end{equation}
-\end{proof}
-
-For  $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
-according to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  thus
-\begin{equation}\label{sum-m}
-m[f]
-    :=\sum_{k=0}^\infty m_k[f]
-    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
-\end{equation}
-
-\begin{prop}
-\label{cor: alpha stable rv}
-	For all $t\geq 0$ and $f\in \mathcal P$,
-\begin{enumerate}
-\item
-\label{it: first stable}
-    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
-\item
-\label{it: second stable}
-    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
-\item
-\label{it: third stable}
-    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
-\end{enumerate}
-\end{prop}
-\begin{proof}
-    \eqref{it: first stable}:
-	Fix $t\geq 0$ and $f\in \mathcal P$.
-	Note that $m_t[\theta f]$ can be rewritten as
-\[
-    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)
-%    \int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
-   \int_0^1 P_{1-s}^\alpha \left(\eta(-i\theta P_{s+t}^\alpha f)^{1+\beta}\right)(x)~ds,
-    \quad \theta \in \mathbb R.
-\]
-	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
-\begin{equation}
-\label{eq: what I want to proof}
-	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
-\end{equation}
-	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),  we know that
-$
-	g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds
-$
-	is a $(1+\beta)$-controllable operator on $\mathcal P$.
-	This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
-	Therefore \eqref{eq: what I want to proof} is true.
-
-    The proofs of \eqref{it: second stable} and \eqref{it: third stable} are similar to that of \eqref{it: first stable}.
-\end{proof}
-Recall that
-\begin{align}
-   \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
-\end{align}
-and
-\begin{align}
-    \mathcal{C}_l=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
-\end{align}
-
-For each $g\in \mathcal{C}_l$ we have the following expression:
-    $$g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.$$
-%Also recall that the definition of $I_tg(x)$:
-Also recall that $I_tg(x)$ is defined by
-\begin{align}
-    I_tg(x)=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
-\end{align}
-Define
-\begin{align}
-    K=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
-\end{align}
-
-\begin{lem}\label{lem: control of Isg}
- For each $g\in \mathcal{C}_l$, there exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
-\begin{align}
-    |I_tg(x)|\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
-\end{align}
-\end{lem}
-\begin{proof}
-Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  Put  $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$. Then
-\begin{align}
-    |I_tg(x)|=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|\leq e^{-(\alpha-Kb)t}h(x),\quad t\geq 0,x\in \mathbb{R}^d.
-\end{align}
-\end{proof}
-For each  $n\geq 1$, let
-\begin{align}
-    \bar{m}_n[g]:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds.
-\end{align}
-\begin{lem}\label{lem: control of mn}
-For each $g\in \mathcal{C}_l$,  there exists constant $C>0$ such that
- \begin{align}
-     |\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1,
- \end{align}
-which implies that
-\begin{equation}\label{sum-bar-m}\bar{m}[g]:=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g]\end{equation}
-is well-defined.
-\end{lem}
-\begin{proof}
-Let $h$ be the function in Lemma \ref{lem: control of Isg}. Then
-\begin{align}
-    &|\bar{m}_n[g]|\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
-    &\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle
-    \leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
-\end{align}
-Using  the fact that $\alpha\beta>K(1+\beta)b$, we easily get
-$\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
-\end{proof}
-\begin{prop}
-\label{cor: alpha stable rv 1}
-For all $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
-\begin{enumerate}
-\item
-\label{it: first stableb}
-    $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
-\item
-\label{it: second stableb}
-    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable.
-\end{enumerate}
-\end{prop}
-\begin{proof}
-The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
-\end{proof}
-
-%\section{Tail probability}
-\section{Preliminary results}
-
-In this section, we will give a small value probability result for supercritical continuous-state branching processes with general branching mechanisms and
-%$(1+\gamma)$-moments for the super-OU process. 
-give some estimates on the $(1+\gamma)$-moments for our super-OU process.
-These will be needed to prove our main results.
+%End moved and modified from above
+
+%Deleted
+%\section{Preliminary results}
+    %In this section, we will give a small value probability result for supercritical continuous-state branching processes with general branching mechanisms and give some estimates on the $(1+\gamma)$-moments for our super-OU process.
+    %These will be needed to prove our main results.
+%End Deleted
 
 \subsection{Small value probability}
-    In this subsection, we digress briefly from our super-OU process and consider a supercritical continuous-state branching process (CSBP)
-        $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
-    Our goal is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ 
-%    convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
-   converges to $0$, where $k_t \to 0$ as $t\to \infty$.
-   Assume that the branching mechanism of  $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is given by \eqref{mechanism}.
+    %In this subsection, we digress briefly from our super-OU process and consider a supercritical continuous-state branching process (CSBP) $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
+    In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}.
+%Added
+    Such process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying that
+\[
+    \mathbf P_x[e^{-\lambda Y_t}] = e^{- x v_t(\lambda)},
+    \quad x\in \mathbb R^+, t\geq 0, \lambda \in \mathbb R^+,
+\] 
+    where for each $\lambda\geq 0$, $t\mapsto v_t(\lambda)$ is the unique positive solution to the equation
+\begin{equation}
+\label{eq: fkpp equation for CSBP}
+    v_t(\lambda) - \int_0^t \psi(v_s(\lambda))~ds = \lambda,
+    \quad t\geq 0.
+\end{equation}
+    It can be varified that for each $\mu \in \mathcal M(\mathbb R^d)$ with $x = \| \mu \|$, we have
+\[
+    \{(\|X_t\|)_{t\geq 0}; \mathbb P_\mu\} 
+    \overset{\text{law}}{=} \{(Y_t)_{t\geq 0}; \mathbf P_x\}.
+\]
+%End added
+
+    Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$ where $k_t \to 0$ as $t\to \infty$.
+%Deleted    
+    %Assume that the branching mechanism of  $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is given by \eqref{eq: honogeneou branching mechanism}.
+%End deleted
     Suppose that Grey's condition is satisfied, i.e., there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
@@
 \[
-    \int_1^\infty y \log y~\pi(dr)< \infty.
+    \int_1^\infty y \log y~\pi(dr)
+    < \infty.
 \]
@@
 \[
-    \mathbf P_x(0<W_t\leq k_t) \leq C(k_t^\delta + e^{-\delta t}), \quad t\geq 0.
+    \mathbf P_x(0<W_t\leq k_t) 
+    \leq C(k_t^\delta + e^{-\delta t}), \quad t\geq 0.
 \]
@@
     Step 1. We recall some known facts about the CSBP $(Y_t)$.
-    For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of
-\[
-    v_t(\lambda)
-    = \lambda - \int_0^t \psi(v_s(\lambda))ds,\quad t\geq 0.
-\]
-    Then according to the definition of CSBP, we have
-\[
-    \mathbf P_x[e^{-\lambda Y_t}] = e^{-xv_t(\lambda)}, \quad t\geq 0, \lambda \geq 0, x\geq 0.
-\]
-    letting $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
+    %For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of
+    For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of \eqref{eq: fkpp equation for CSBP}. 
+%Deleted
+%\[
+    %v_t(\lambda)
+    %= \lambda - \int_0^t \psi(v_s(\lambda))ds,\quad t\geq 0.
+%\]
+    %Then according to the definition of CSBP, we have
+%\[
+    %\mathbf P_x[e^{-\lambda Y_t}] = e^{-xv_t(\lambda)}, \quad t\geq 0, \lambda \geq 0, x\geq 0.
+%\]
+%End deleted
+    %letting $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
+    Letting $\lambda \to \infty$ in \eqref{eq: fkpp equation for CSBP}, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
 \begin{equation}
@@
     Also notice that $\psi'(0+)=-\alpha <0$ and that there exists $z>0$ such that $\psi(z)>0$.
-%    So, we can verify that the following are true:
     Therefore we have
@@
 \end{split}\end{equation}
-%    as required in this step.
     as desired in this step.
@@
 \]
-    In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
+    %In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
+    In fact, since $\psi$ is a convex function, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for each $z\geq \bar v$.
     According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
@@
 \end{split}\end{equation}
-%    Rearrange this, we have
     Rearranging this, we get
@@
     and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
-    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate random variable.
+    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate positive random variable.
 This implies that
@@
     Fix an arbitrary $\epsilon \in (0,\tau)$.
-    According to the fact that $\tau=\psi'(\bar v)>0$ , there exists $z_0 \in (0,\bar v)$ such that for all $z\in (z_0, \bar v)$, we have $-\psi(z)\geq (\bar v - z)(\tau- \epsilon)$.
+    According to the fact that $\tau=\psi'(\bar v)>0$, there exists $z_0 \in (0,\bar v)$ such that for all $z\in (z_0, \bar v)$, we have $-\psi(z)\geq (\bar v - z)(\tau- \epsilon)$.
 Fix this $z_0$.
-    For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$. Then  using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have
+    For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$. 
+    %Then using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have
+    Then using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have for $t>0$ large enough, 
 \begin{equation}\begin{split}
@@
 \end{proof}
-%\subsection{$(1+\gamma)$-moments for the super-OU process}
-\subsection{moments estimates  for super-OU processes}
-
- In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
-    For all $0 \leq s \leq t <\infty$ and  random variable $Y$ with finite mean, we write
-%$$
+%\subsection{moments estimates  for super-OU processes}
+\subsection{Moments for the super-OU processes}
+
+    %In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
+    In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: branching mechanism} and \ref{asp: Greys condition}.
+    %For all $0 \leq s \leq t <\infty$ and  random variable $Y$ with finite mean, we write
+    With respect to a probability $\mathbb P_\mu$ with $\mu\in \mathcal M(\mathbb R^d)$, for each $0 \leq s \leq t <\infty$ and a random variable $Y$ with finite mean, we write
 \begin{equation}\label{Ist}
     \mathcal I_s^t Y
-  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s].
-%$$
-\end{equation}
+    := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s]
+\end{equation}
+%Added
+    where $(\mathscr F_t)_{t\geq 0}$ is the natural filtration of the super OU process $X$.
+%End added
 
@@
 \end{proof}
-    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-\begin{equation}\label{Q_k}
-Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|P_t f|
-\end{equation}
-and
-\begin{equation}\label{Q}
-Q f:= Q_{\kappa_f}f.
-\end{equation}
-    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
+%moved above
+    %For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
+%\begin{equation}\label{Q_k}
+    %Q_\kappa f 
+    %:= \sup_{t\geq 0} e^{\kappa b t}|P_t f|
+%\end{equation}
+    %and
+%\begin{equation}\label{Q}
+    %Q f:= Q_{\kappa_f}f.
+%\end{equation}
+    %Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
+%End moved above
 \begin{lem}\label{lem: temp}
-    For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
+    For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists a constant $C > 0$ such that 
+    %for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
+    for all $\kappa \in \mathbb Z_+ $, $\lambda > 0$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
 \[
@@
     Using the Markov property of $X$, we get
-\begin{equation}\begin{split}
+\begin{align}
     &\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    = \mathbb P_\mu \big[\mathbb P_\mu[|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r]\big]
+    = \mathbb P_\mu \Big[\mathbb P_\mu\big[|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r\big]\Big]
     \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle P_{t-s}^\alpha g, X_{s-r}\rangle - \langle P_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
-    = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
+    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
     \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
-    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
+    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
     \\&\leq \mathbb P_\mu [ \langle Rh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
@@
     \\ & \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg),
-\end{split}\end{equation}
-    where the constatn $C$ is chosen as
+\end{align}
+    where the constant $C>0$ above is chosen as
 \[
@@
 \[
-    C := 1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}.
+    C 
+    := 1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}.
     \qedhere
@@
 \section{Proofs of main results}
-
     In this section, we will prove the main results of this paper.
@@
 
-%\subsection{The large rate case: $\alpha \beta > \kappa_f b (1+\beta)$}
 \subsection{The large rate case}
@@
     In this subsection, we prove Theorem \ref{Theorem11}. 
-%We will be back to the large branching rate case 
-We will return to the large branching rate case 
-in Subsection \ref{large rate again} to prove Theorem \ref{theorem 1.6}.
+    We will return to the large branching rate case in Subsection \ref{large rate again} to prove Theorem \ref{thm: large clt}.
+    {\bf (ZS: Jianjie, can you bring the proofs related to the large branching together? I mean you can move subsection 3.4 just after this subsection.)}
 
@@
 \label{defmartingale}
-    M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds.
-\end{split}\end{equation}
-%    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
+    M_t^{f,a}
+    :=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds.
+\end{split}\end{equation}
     Let $(\mathscr{F}_t)_{t\geq 0}$ be the natural filtration of $X$.  The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
@@
 \label{lemma25}
-    For all $f\in \mathcal{P}\cap C^2(\mathbb R^d)$, $a\in \mathbb R$
-and $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
+    For all $f\in \mathcal{P}\cap C^2(\mathbb R^d)$, $a\in \mathbb R$ and $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
 \end{lem}
@@
     There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
-    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$,
-   we get that, for $\gamma\in [\gamma_0, \beta)$, there exists
-    a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$)  such that
+    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that, for $\gamma\in [\gamma_0, \beta)$, there exists a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$) such that
 \[
@@
 
-   Hence, for all $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
-    the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
+    Hence, for all $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
 \end{proof}
@@
 
-\begin{lem}\label{lem: control of wt} For all $\gamma\in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for all $0\leq s<t$,
+\begin{lem}\label{lem: control of wt} 
+    For all $\gamma\in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for all $0\leq s<t$,
 \[
@@
 \]
-Moreover, 
-%letting $t\to\infty$ in above inequality, 
-we have
+    Moreover, we have
 \[
@@
 \begin{proof}
-%new
     The second assertion follows immediately from the first, so we only first the first assertion.
-%ene new
     Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-It follows from Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$ that
- there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
+    It follows from Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$ that there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
 \begin{align}
@@
 \begin{align}
-        \mathbb{P}_{\mu}\big[|H^p_s-H^p_r|^{1+\gamma}\big]\leq  C_0 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
+    \mathbb{P}_{\mu}\big[|H^p_s-H^p_r|^{1+\gamma}\big]
+    \leq  C_0 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
 \end{align}
@@
 	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
-	\leq Ce^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
+	\\&\leq Ce^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
     \qedhere
@@
 \]
-	In order to do this,
-we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that,
-for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
+	In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
 	Then, according to Lemma \ref{lem: control moment}, we have, for each $\gamma \in (0,\beta)$,
@@
 \begin{align*}
-    \|M_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),\quad t\geq 0.
+    \|M_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),
+    \quad t\geq 0.
 \end{align*}
@@
 
-%\subsection{The critical rate case: $\alpha\beta=\kappa_fb(1+\beta)$}
 \subsection{The critical rate case}
 
-%new
     Recall that $I_s^t$ is defined in \eqref{Ist}.
-%end new
-
 \begin{lem}\label{lem: mainlemma}
@@
 \begin{equation}\begin{split}
-      \gamma_{t,k}:=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
+    \gamma_{t,k}
+    :=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{split}\end{equation}
     where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
- $$\mathbb{E}(e^{i\theta\zeta_k})=\exp(e^{\alpha}m_k[\theta f]),\quad \theta \in \mathbb R.$$
+\[
+    \mathbb{E}(e^{i\theta\zeta_k})
+    =\exp(e^{\alpha}m_k[\theta f]),\quad \theta \in \mathbb R.
+\]
 \end{lem}
 \begin{proof}
-%    We only need to show that
     We only need to show that for all $\mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0$, 
@@
     \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[f]).
-%    \quad \mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0.
 \end{split}\end{equation}
@@
 \[
-    A_t(\epsilon):=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \},\quad t\geq 0, \epsilon > 0.
+    A_t(\epsilon)
+    :=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \},
+    \quad t\geq 0, \epsilon > 0.
 \]
@@
 \end{split}\end{equation}
-In fact, 
-%from the definitions of $K_1$ and $Z_1$, we have 
-it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$, 
-that for all
-$k\geq 0, t\geq k+1$,
+    In fact, it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-       From Proposition \ref{cor: alpha stable rv}, we have
+    From Proposition \ref{prop: alpha stable rv}, we have
 \begin{equation}
@@
 \]
-%According to Lemma \ref{lem: control of gk}, we get there exists $h\in \mathcal{P}$ such that
     It follows from Lemma \ref{lem: control of gk} that there exists $h\in \mathcal{P}$ such that
@@
 \end{split}\end{equation}
-%Therefore, according to \eqref{eq: prevJ2}, we have 
-Therefore, it follows from \eqref{eq: prevJ2} that
-there exists constant $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+    Therefore, it follows from \eqref{eq: prevJ2} that there exists constant $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{equation}\begin{split}
@@
 
-    Step 4. We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C,\delta>0$ such that for all $k\geq0, t\geq k+1$,
+    Step 4. 
+    We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C,\delta>0$ such that for all $k\geq0, t\geq k+1$,
 \begin{equation}\begin{split}\label{ineq: control of J3}
@@
 \end{split}\end{equation}
-According to Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there are constants $C, \delta>0$ such that
-for all $t\geq 0$,
+    According to Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there are constants $C, \delta>0$ such that for all $t\geq 0$,
 \begin{equation}\begin{split}
@@
 
-    Finally, combining the results in Steps 1--4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$,
-we immediately get the desired result.
+    Finally, combining the results in Steps 1--4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$, we immediately get the desired result.
 \end{proof}
@@
     Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq \kappa_fb(1+\beta)$.
-Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
-there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
-\begin{equation}\begin{split}
-    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]\leq Ce^{-\delta(t-k)}.
+    Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
+\begin{equation}\begin{split}
+    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+    \leq Ce^{-\delta(t-k)}.
 \end{split}\end{equation}
@@
 \]
-%	According to this and \eqref{eq: right bound for J2} in the Step 3 in the proof of the previous lemma, 
 	According to this and \eqref{eq: right bound for J2}, 
@@
 \begin{prop}\label{corollary31}
-Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
-there exist constants $C,\delta>0$ such that
-for all $t\geq 0$,
-$n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$
-satisfying $|\theta_i|\leq \Theta$, we have
+    Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq\kappa_fb(1+\beta)$. 
+    Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$satisfying $|\theta_i|\leq \Theta$, we have
 \begin{equation}\begin{split}
@@
     Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
-        Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$
-    satisfying $|\theta_i|\leq \Theta$.
+    Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$satisfying $|\theta_i|\leq \Theta$.
     For each $k\in\{-1,...,n\}$, we define
-    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),\]
+\[
+    a_k
+    :=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
+\]
     where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
@@
 \end{align*}
-  According to Proposition \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary},
-    there exist $C,\delta>0$ such that for any
-        $k\in\{0, 1, \cdots, n\}$, we have
+    According to Proposition \ref{prop: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
 \begin{align*}
@@
 \end{proof}
-We now present the proof of Theorem \ref{Theorem12}.
+    We now present the proof of Theorem \ref{thm: critical clt}.
 \bigskip
 
-{\it Proof of Theorem \ref{Theorem12}.}\quad
+{\it Proof of Theorem \ref{thm: critical clt}.}\quad
     By assumption, $f\in\mathcal{P}$ and  $\alpha\beta=\kappa_fb(1+\beta)$.
@@
 \]
-    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb R$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$
-    in Proposition \ref{corollary31},
+    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb R$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{corollary31},
     we get that there exist $C,\delta>0$ such that,
@@
 \end{align*}
-%    Where $\mathcal{\mathbb{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$. 
     According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\zeta$ under $\tilde {\mathbb P}_\mu$.
     Therefore, we only need to prove
- \begin{equation}\label{toprove-1}|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0
+ \begin{equation}\label{toprove-1}
+    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
+    \xrightarrow[t\to \infty]{} 0
  \end{equation}
@@
 \begin{equation}\label{toprove-2}
-     I_i(t)\xrightarrow[t\to \infty]{d} 0,\quad i = 2,3,  \mbox{ under } \tilde {\mathbb P}_\mu.\end{equation}
+    I_i(t)\xrightarrow[t\to \infty]{d} 0,
+    \quad i = 2,3,  
+    \mbox{ under } \tilde {\mathbb P}_\mu.
+\end{equation}
 
@@
 \end{split}\end{equation}
-%    Then according to 
-   According to 
-    Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality, there exist $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
+    According to Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality, there exist $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
 \begin{equation}\begin{split}
@@
     \geq e^{-\eta_1(t-k-1)}.
- %   \quad \text{ on } \mathcal D_{t,k}.
 \end{align*}
@@
     =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)},
-%    \quad \text{ on } \mathcal D_{t,k},
 \end{align*}
@@
     \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1(t-k-1)}.
-%    \quad \text{ on } \mathcal D_{t,k}.
 \end{align*}
@@
      \leq C e^{-(\eta_0 - 3\eta_1)(t-k-1)}.
- %    \quad k \geq 0, t\geq k+1.
-\end{split}\end{equation}
-   According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and  \eqref{ineq: control of Kkt},
-    there exist constants $C,C'>0$ such that  for all $k\geq 0$ and $t\geq k+1$,
+\end{split}\end{equation}
+    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and \eqref{ineq: control of Kkt}, there exist constants $C,C'>0$ such that for all $k\geq 0$ and $t\geq k+1$,
 \begin{equation}\begin{split}
@@
 
-    Step 3. We will show that there exist $C, \delta> 0$ such that for $t$ large enough,
+    Step 3. 
+    We will show that there exist $C, \delta> 0$ such that for $t$ large enough,
 \begin{equation}\label{domi-difference of Is}
@@
 
-    Step 4. We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\tilde{P}}_{\mu}$.
+    Step 4. 
+    We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\tilde{P}}_{\mu}$.
     In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C, \delta>0$ such that
@@
 
-	Step 5. We will show that $I_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+	Step 5. 
+    We will show that $I_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
     In fact, we have
@@
 
-	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{Theorem12}.
-
-%\subsection{The small rate case: $\alpha\beta<\kappa_fb(1+\beta)$}
+	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{thm: critical clt}.
+
 \subsection{The small rate case}
@@
 
-{\it Proof of Theorem \ref{Theorem13}.}\quad
-%According to our assumption, $f\in \mathcal P$  is fixed  and  that $\alpha \beta < \kappa_f b(1+\beta)$.
+{\it Proof of Theorem \ref{thm: small clt}.}\quad
     By assumption, $f\in \mathcal P$  and $\alpha \beta < \kappa_f b(1+\beta)$.
@@
 
-    Step 1. We will show that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
+    Step 1. 
+    We will show that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
     Define for $k\geq 0$ and $t\geq k+1$,
@@
 \end{align*}
-Now we can  use the  same argument used in the proof of Theorem \ref{Theorem12}
-to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
+    Now we can  use the  same argument used in the proof of Theorem \ref{thm: critical clt} to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
 
@@
 	The proof is complete.
-\subsection{Proof of Theorem \ref{theorem 1.6}}\label{large rate again}
-In this subsection, 
-%we are back to the large branching rate case, and aim to prove Theorem \ref{theorem 1.6}.
-we revisit the large branching rate case and prove Theorem \ref{theorem 1.6}.
-
+\subsection{Proof of Theorem \ref{thm: large clt}}\label{large rate again}
+    In this subsection, we revisit the large branching rate case and prove Theorem \ref{thm: large clt}.
     For $g\in \mathcal{C}_l$, recall the definition of $I_tg$ in \eqref{definition of Itf}.
@@
 \end{align}
-Put
-$\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
+    Put $\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
     We have
@@
 \end{align}
-% From the definitions of $K_1$ and $Z_1$, we have
     It follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$ that
@@
     \\&\leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon).
-%    \quad n\geq 0, t\geq 0, \epsilon> 0.
-\end{align}
-
-Step 2.  We will show that for each $\epsilon$ small enough, there exist constants $C,\delta>0$ such that for all $n\geq 1, \, t\geq 0$, 
-    \begin{align}
-    \label{eq:large rate J1}
+\end{align}
+
+    Step 2.  
+    We will show that for each $\epsilon$ small enough, there exist constants $C,\delta>0$ such that for all $n\geq 1, \, t\geq 0$, 
+\begin{align}\label{eq:large rate J1}
     J'_1(t,n,\epsilon)\leq C e^{-\delta(t+n)}. %\quad n\geq 1, \, t\geq 0.
@@
     \\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|,
- %  \quad n\geq 0, t\geq 0, \epsilon > 0,
 \end{align}
@@
     \leq C e^{-\delta(t+n)}.
-%    \quad n\geq 1, t\geq 0.
 \end{align}
@@
     &=e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
-%    & t\geq 0, n\geq1.
 \end{align}
@@
     [\langle \bar {g}_n, X_{t+n-1}\rangle].
-%	\quad t\geq 0, n\geq 1,
 \end{align}
@@
 \begin{align}
-    \bar{g}_n:=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
-\end{align}
-Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment}.(3) with $\kappa=1$,
- there exists $C>0$ such that
-\begin{align}
-    \mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]\leq Ce^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
+    \bar{g}_n
+    :=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
+\end{align}
+    Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment}.(3) with $\kappa=1$, there exists $C>0$ such that
+\begin{align}
+    \mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]
+    \leq Ce^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
 \end{align}
@@
     &=Ce^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}\\&\leq Ce^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}.
-%    ,\quad t\geq 0,n\geq 1.
 \end{align}
@@
 and noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$, converge to $0$ exponentially fast when $t\rightarrow\infty$, we get the desired result.
-%	This gives the desired result.
 \end{proof}
@@
 \end{align}
-Step 2.   Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$.
+
+    Step 2.   
+    Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$.
     For each $n=1,\cdots,m$, we define
-    \[\tilde{a}_n:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big),\]
-     where by convention the product is $1$ for $n=0$. Then we get for each $n > 0$,
+    \[\tilde{a}_n:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big),\] where by convention the product is $1$ for $n=0$.
+Then we get for each $n > 0$,
 \begin{align*}
@@
 \end{align*}
-   According to Step 1 and Proposition \ref{cor: alpha stable rv 1},
-    there exist $C,\delta>0$ such that for any $n=1,\cdots, m$ and $t\geq0$, we have
+    According to Step 1 and Proposition \ref{cor: alpha stable rv 1}, there exist $C,\delta>0$ such that for any $n=1,\cdots, m$ and $t\geq0$, we have
 \begin{align*}
@@
 \begin{align}
-    \text{LHS of \eqref{ineq: next we will need}}&= \left|\tilde{a}_{0}-\tilde{a}_m\right|
+    \text{LHS of \eqref{ineq: next we will need}}
+    &= \left|\tilde{a}_{0}-\tilde{a}_m\right|
     \leq\sum_{n=1}^m\left|\tilde{a}_{n-1}-\tilde{a}_n\right|
@@
 \begin{align}
-    \tilde{\gamma}_{t,n}:=\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_{t}\|^{\frac{1}{1+\beta}}},\quad t\geq 0, n\geq 1.
+    \tilde{\gamma}_{t,n}
+    :=\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_{t}\|^{\frac{1}{1+\beta}}},
+    \quad t\geq 0, n\geq 1.
 \end{align}
 \begin{lem}\label{lem: lemma04}
-     For all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$
-such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
-\begin{align}
-    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq C m e^{-\delta t}.
+    For all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
+\begin{align}
+    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^m e^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|
+    \leq C m e^{-\delta t}.
 \end{align}
@@
 \begin{align}
-    Y''_{t,n}:=e^{i\theta\tilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},\quad t\geq 0, n\geq 1, \theta\in \mathbb{R}.
+    Y''_{t,n}
+    :=e^{i\theta\tilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},\quad t\geq 0, n\geq 1, \theta\in \mathbb{R}.
 \end{align}
@@
 \[
-    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0
+    \frac{\alpha \gamma}{1+\gamma} 
+    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0
 \]
@@
 \[
-   \alpha\gamma>K(1+\gamma)b.
+    \alpha\gamma
+    >K(1+\gamma)b.
 \]
@@
 \[
-    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
+    \frac{\alpha \gamma}{1+\gamma} 
+    > \eta_0 
+    > \eta_0 - 3\eta_1 
+    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} 
+    > 0.
 \]
@@
 \label{def: Dtk1}
-    \mathcal{D}_{t,n}&:=\left\{|H_t-H_{t+n-1}|\leq  e^{-\eta_0 t}, H_{t}> 2e^{-\eta_1t}\right\}.
-\end{align}
-
-Step 1. Similar to Step 1 in the proof of Theorem \ref{Theorem12},
-we can show that there exist constants $C,\delta >0$ such that for all $n \geq 1$ and $t\geq 0$,
+    \mathcal{D}_{t,n}
+    &:=\left\{|H_t-H_{t+n-1}|\leq  e^{-\eta_0 t}, H_{t}> 2e^{-\eta_1t}\right\}.
+\end{align}
+
+    Step 1. Similar to Step 1 in the proof of Theorem \ref{thm: critical clt}, we can show that there exist constants $C,\delta >0$ such that for all $n \geq 1$ and $t\geq 0$,
 \begin{align}
@@
 \begin{comment}
-
     In fact, let $C_1$ be the constant in  Lemma 2.9 corresponding to this fixed $\gamma$ and $C_2$ be the constant in Lemma 2.10.
@@
 
-Since $\eta_1 < \eta_0$,  using similar arguments used in  step 2 of the proof of Theorem \ref{Theorem12},
-we can show that, there is a constant $C\geq 0$ such that,
+    Since $\eta_1 < \eta_0$,  using similar arguments used in  step 2 of the proof of Theorem \ref{thm: critical clt}, we can show that, there is a constant $C\geq 0$ such that,
 \begin{align}
@@
 \begin{align}
-  \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 m}),\quad m\in \mathbb{N}, t\geq 0.
+    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|
+    \leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 m}),
+    \quad m\in \mathbb{N}, t\geq 0.
 \end{align}
@@
 \begin{proof}
-Recall that $A_t(\epsilon)=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to Proposition \ref{lem: control of XT}, there exist
-	$C,\delta>0$ such that for all $t\geq 0$
+    Recall that $A_t(\epsilon)=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C,\delta>0$ such that for all $t\geq 0$
 \begin{align}\label{ineq: control of gamma_t on dc}
-     \Big|\tilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]\leq 2\tilde{P}_{\mu}(A_t(\epsilon)^c)\leq C e^{-\delta t}.
+    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]
+    \leq 2\tilde{P}_{\mu}(A_t(\epsilon)^c)
+    \leq C e^{-\delta t}.
 \end{align}
@@
 \end{proof}
-Now we are ready to prove Theorem \ref{theorem 1.6}.
+    Now we are ready to prove Theorem \ref{thm: large clt}.
 \bigskip
-
-{\it Proof of Theorem \ref{theorem 1.6}.}\quad
-Let $\delta_0$ be the constant $\delta$ in Lemma \ref{lem: lemma04}.  Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$. First note that for $t\ge 0$,
+{\it Proof of Theorem \ref{thm: large clt}.}\quad
+    Let $\delta_0$ be the constant $\delta$ in Lemma \ref{lem: lemma04}.  Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$. 
+    First note that for $t\ge 0$,
 \begin{align}\label{decompose}
-    \text{LHS of \eqref{thm: large rate}}=\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\tilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\tilde{\gamma}_{t,n}.
-    %\quad t\geq 0.
-\end{align}
-According to Lemma \ref{lem:lemma03}, there exist $C,\delta>0$ such that for all
-$t\geq 0,\theta\in\mathbb{R}$, 
+    \text{LHS of \eqref{thm: large rate}}
+    =\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\tilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\tilde{\gamma}_{t,n}.
+\end{align}
+    According to Lemma \ref{lem:lemma03}, there exist $C,\delta>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$, 
 \begin{align}\label{ineq: last1}
-    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t}.
-    %\quad t\geq 0,\theta\in\mathbb{R}.
-\end{align}
-According to Lemma \ref{lem: lemma04}, there exists $C>0$ such that for all
-$t\geq 0,\theta\in\mathbb{R}$, 
+    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]
+    \Big|\leq C e^{-\delta t}.
+\end{align}
+    According to Lemma \ref{lem: lemma04}, there exists $C>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$, 
 \begin{align}\label{ineq: last2}
     \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C  e^{-\frac{\delta_0}{2} t}.
-    %\quad t\geq 0, \theta\in \mathbb{R}.
- \end{align}
- According to Lemma \ref{lem: lemma05}, there exist $C,\delta_1,\delta_2>0$ such that
- for all
-$t\geq 0,\theta\in\mathbb{R}$, 
+ \end{align}
+    According to Lemma \ref{lem: lemma05}, there exist $C,\delta_1,\delta_2>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$, 
 \begin{align}\label{ineq: last3}
     \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 e^{\frac{\delta_0}{2}t}}).
-  %\quad t\geq 0, \theta\in \mathbb{R}.
 \end{align}
@@
 
-Combining \eqref{decompose},\eqref{ineq: last1}, \eqref{ineq: last2} and \eqref{ineq: last3}, and letting $t\to\infty$, we get the desired result of Theorem \ref{theorem 1.6}.
+    Combining \eqref{decompose},\eqref{ineq: last1}, \eqref{ineq: last2} and \eqref{ineq: last3}, and letting $t\to\infty$, we get the desired result of Theorem \ref{thm: large clt}.
 \appendix
@@
 \subsection{Analytic facts}
-
-%new
     In this subsection, we collect some useful analytic facts.
-%end new
 \begin{lem}
@@
 \begin{equation}
-    |e^{-z} - 1| = \Big| \int_0^1 e^{-\theta z} z d\theta\Big|
+    |e^{-z} - 1| 
+    = \Big| \int_0^1 e^{-\theta z} z d\theta\Big|
     \leq |z|.
@@
     It follows from Lemma \ref{lem: estimate of exponential remaining} that $h$ and $h'$ are well defined on $\mathbb C_+$.
-    According to \cite[Theorems 3.2. \& 3.5]{SchillingSongVondracek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
+    According to \cite[Theorems 3.2. \& 3.5]{SchillingSongVondravcek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
 
@@
 	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, that $z\mapsto \log z$ is holomorphic in $\mathbb C\setminus (-\infty,0]$.
-	Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic in $\mathbb C\setminus (-\infty,0]$.
-(We use the convention that  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
+	Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic in $\mathbb C\setminus (-\infty,0]$. (We use the convention that  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
     Using  the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
@@
 	Suppose that $\varphi(\theta)$ is a continuous function from $\mathbb R$ into $\mathbb C$ such that $\varphi(0) = 1$ and $\varphi(\theta) \neq 0$ for all $\theta \in \mathbb R$.
-	Then according to \cite[Lemma 7.6]{Sato1999Levy}, there is a unique continuous function $f(\theta)$ from $\mathbb R$ into $\mathbb C$ such that $f(0) = 0$ and $e^{f(\theta)} = \varphi(\theta)$.
+	Then according to \cite[Lemma 7.6]{Sato2013Levy}, there is a unique continuous function $f(\theta)$ from $\mathbb R$ into $\mathbb C$ such that $f(0) = 0$ and $e^{f(\theta)} = \varphi(\theta)$.
 	Such a function $f$ is called the distinguished logarithm of the function $\varphi$ and is denoted as $\operatorname{Log} \varphi(\theta)$.
@@
     Let $t \geq 0$. Suppose that 
-%    $\alpha,\rho\in \mathcal B_b([0,t] \times E, \mathbb C)$ 
     $\rho_1, \rho_2\in \mathcal B_b([0,t] \times E, \mathbb C)$ 
@@
 \begin{equation}
- %   g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\alpha+\rho)} f(\xi_t)],\quad r \in [0,t], x\in E,
     g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
@@
 \[
-%    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\alpha)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\alpha)}\rho(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
     g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
@@
 \begin{equation}\begin{split}
-%    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\alpha)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t)| ~ds \Big]
-%    \leq  \int_r^t e^{(t-r)\|\alpha\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|f\|_\infty ~ds
-%    < \infty.
    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t)| ~ds \Big]
@@
 \label{eq: crucial for Feynman-Kac}
-%    \frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
     \frac{\partial}{\partial s} H^{(\rho_2)}_{(s,t)}= -H^{(\rho_2)}_{(s,t)}\rho_2(s,\xi_s),
@@
     \psi(x,z)=
-%    - \alpha(x) z + \rho (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
-   - \rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
+    -rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
 \end{equation}
@@
     To avoid triviality, we assume that 
-   %$\psi(x,z)\neq -\alpha(x)z$ for some $x \in E$ and $z \geq 0$.
     $\psi(x,z)$ is not identically equal to $-\rho_1(x)z$.
@@
 \begin{equation}
-%    \psi'(x,z):= - \alpha(x) + 2\rho(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
     \psi'(x,z):= - \rho_(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
@@
 \label{sec: definition of vf}
-    Let $X$ be a non-presistent superprocess 
-%    defined in Subsection \ref{sec: definition of superprocess} 
-    with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
+    Let $X$ be a non-presistent superprocess with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
     We define the mean semigroup
 \begin{equation}
- %      P_t^\alpha f(x)
-%    := \Pi_{x}[e^{\int_0^t \alpha(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
     P_t^{\rho_1} f(x)
@@
 \]
-    Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato1999Levy}, we have
+    Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
 \begin{equation}
@@
 \label{eq: path integration representation of psi(v)}
-    \psi(x,-U_tf) = -\int_0^1 \psi'\big(x,-U_t(\theta f)\big) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
+    \psi(x,-U_tf) 
+    = -\int_0^1 \psi'\big(x,-U_t(\theta f)\big) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
 \end{equation}
@@
     \\ &\leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty
-  P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x)
-  + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
+    P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
     \\ &=: C_1 + C_2(P^{\rho_1}_t |f|)(x),
@@
     Let $X$ be a non-persistent superprocess.
-    % discussed in Subsection \ref{sec: definition of vf}.
     In this subsection, we will prove the following:
@@
     Let $X$ be the non-persistent superprocess.
-    % discussed in Subsection \ref{sec: definition of vf}.
     Let $f\in \mathcal B_b(E,\mathbb R_+)$, $T >0$ and $x\in E$.
@@
 
-\begin{thebibliography} {10}
-
-\bibitem{ARMP}
-Adamczak, RR. Milo\'s, P.:
-\emph{CLT for Ornstein-Uhlenbeck branching particle system.}
-Electron. J. Probab. 20 (2015), no.42, 1-35.
-
-\bibitem{ASHH}
-Asmussen, S. Hering, H.:
-\emph{Branching Processes.}
-Birkh auser, Boston, 1983.
-
-\bibitem{BAM}
-Berestycki, J., Kyrianou, A.E., Murillo-Salas, A
-\newblock{\em The prolific backbone for supercritical superprocesses}. Stoch. Proc. Appl. 121, 1315-1331(2011)
-
-\bibitem{Cuppens1975Decomposition}
-Cuppens, R.:
-\emph{Decomposition of multivariate probabilities.}
-Probability and Mathematical Statistics, Vol. 29. Academic Press [Harcourt Brace Jovanovich, Publishers], New York-London, 1975.
-\MR{0517412}
+%\bibliographystyle{amsplain}
+%\bibliography{bib.bib}
+
+\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
+\begin{thebibliography}{10}
+%ZS: Changes made for the bibliographies are not marked by %
+
+\bibitem{AdamczakMilos2014U-statistics}
+R.~Adamczak and P.~Mi{\l}o\'{s}, \emph{{$U$}-statistics of
+  {O}rnstein-{U}hlenbeck branching particle system}, J. Theoret. Probab.
+  \textbf{27} (2014), no.~4, 1071--1111.
+
+\bibitem{AdamczakMilos2015CLT}
+\bysame, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
+  Electron. J. Probab. \textbf{20} (2015), no.~42, 35 pp.
+
+\bibitem{AsmussenHering1983Branching}
+S.~Asmussen and H.~Hering, \emph{Branching processes}, Progress in Probability
+  and Statistics, vol.~3, Birkh\"{a}user Boston, Inc., Boston, MA, 1983.
+
+\bibitem{Athreya1969Limit}
+K.~B. Athreya, \emph{Limit theorems for multitype continuous time {M}arkov
+  branching processes. {I}. {T}he case of an eigenvector linear functional}, Z.
+  Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{12} (1969), 320--332.
+
+\bibitem{Athreya1969LimitB}
+\bysame, \emph{Limit theorems for multitype continuous time {M}arkov branching
+  processes. {II}. {T}he case of an arbitrary linear functional}, Z.
+  Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{13} (1969), 204--214.
+
+\bibitem{Athreya1971Some}
+\bysame, \emph{Some refinements in the theory of supercritical multitype
+  {M}arkov branching processes}, Z. Wahrscheinlichkeitstheorie und Verw.
+  Gebiete \textbf{20} (1971), 47--57.
+
+\bibitem{BansayeDelmasMarsalleTran2011Limit}
+V.~Bansaye, J.~Delmas, L.~Marsalle, and V.~C. Tran, \emph{Limit theorems for
+  {M}arkov processes indexed by continuous time {G}alton-{W}atson trees}, Ann.
+  Appl. Probab. \textbf{21} (2011), no.~6, 2263--2314. \MR{2895416}
+
+\bibitem{ChenRenWang2008An-almost}
+Z.-Q. Chen, Y.-X. Ren, and H.~Wang, \emph{An almost sure scaling limit theorem
+  for {D}awson-{W}atanabe superprocesses}, J. Funct. Anal. \textbf{254} (2008),
+  no.~7, 1988--2019.
 
 \bibitem{Durrett2010Probability}
-Durrett, R.:
-\emph{Probability: theory and examples.}
-Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
-\MR{2722836}
+R.~Durrett, \emph{Probability: theory and examples}, 4 ed., Cambridge Series in
+  Statistical and Probabilistic Mathematics, vol.~31, Cambridge University
+  Press, Cambridge, 2010.
 
 \bibitem{Dynkin1993Superprocesses}
-Dynkin,~E.B.
-\newblock {\em Superprocesses and partial differential equations}, Ann. Probab (1993): 1185-1262.
-
-\bibitem{DK}
-Dynkin, E. B., Kuznetsov, S. E.:
-\newblock {\em $\mathbb{N}$-measure  for branching exit Markov system and their applications to differential equations}, Probab. Theory Related Fields 130(2004) 135-150
+E.~B. Dynkin, \emph{Superprocesses and partial differential equations}, Ann.
+  Probab. \textbf{21} (1993), no.~3, 1185--1262.
+
+\bibitem{EckhoffKyprianouWinkel2015Spines}
+M.~Eckhoff, A.~E. Kyprianou, and M.~Winkel, \emph{Spines, skeletons and the
+  strong law of large numbers for superdiffusions}, Ann. Probab. \textbf{43}
+  (2015), no.~5, 2545--2610.
+
+\bibitem{Englander2009Law}
+J.~Engl\"{a}nder, \emph{Law of large numbers for superdiffusions: the
+  non-ergodic case}, Ann. Inst. Henri Poincar\'{e} Probab. Stat. \textbf{45}
+  (2009), no.~1, 1--6.
+
+\bibitem{EnglanderHarrisKyprianou2010Strong}
+J.~Engl\"{a}nder, S.~C. Harris, and A.~E. Kyprianou, \emph{Strong law of large
+  numbers for branching diffusions}, Ann. Inst. Henri Poincar\'{e} Probab.
+  Stat. \textbf{46} (2010), no.~1, 279--298.
+
+\bibitem{EnglanderWinter2006Law}
+J.~Engl\"{a}nder and A.~Winter, \emph{Law of large numbers for a class of
+  superdiffusions}, Ann. Inst. H. Poincar\'{e} Probab. Statist. \textbf{42}
+  (2006), no.~2, 171--185.
+
+\bibitem{GrubelKabluchko2016A-functional}
+R.~Gr\"{u}bel and Z.~Kabluchko, \emph{A functional central limit theorem for
+  branching random walks, almost sure weak convergence and applications to
+  random trees}, Ann. Appl. Probab. \textbf{26} (2016), no.~6, 3659--3698.
+
+\bibitem{HartungKlimovsky2018The-phase}
+L.~Hartung and A.~Klimovsky, \emph{The phase diagram of the complex branching
+  brownian motion energy model}, Electron. J. Probab. \textbf{23} (2018).
+
+\bibitem{Heyde1970A-rate}
+C.~C. Heyde, \emph{A rate of convergence result for the super-critical
+  {G}alton-{W}atson process}, J. Appl. Probability \textbf{7} (1970), 451--454.
+
+\bibitem{Heyde1971Some}
+\bysame, \emph{Some central limit analogues for supercritical {G}alton-{W}atson
+  processes}, J. Appl. Probability \textbf{8} (1971), 52--59.
+
+\bibitem{HeydeBrown1871An-invariance}
+C.~C. Heyde and B.~M. Brown, \emph{An invariance principle and some convergence
+  rate results for branching processes}, Z. Wahrscheinlichkeitstheorie und
+  Verw. Gebiete \textbf{20} (1971), 271--278.
+
+\bibitem{HeydeLeslie1971Improved}
+C.~C. Heyde and J.~R. Leslie, \emph{Improved classical limit analogues for
+  {G}alton-{W}atson processes with or without immigration}, Bull. Austral.
+  Math. Soc. \textbf{5} (1971), 145--155.
+
+\bibitem{IksanovKabluchko2016A-central}
+A.~Iksanov and Z.~Kabluchko, \emph{A central limit theorem and a law of the
+  iterated logarithm for the {B}iggins martingale of the supercritical
+  branching random walk}, J. Appl. Probab. \textbf{53} (2016), no.~4,
+  1178--1192.
+
+\bibitem{IksanovKoleskoMeiners2018Fluctuations}
+A.~Iksanov, K.~Kolesko, and M.~Meiners, \emph{Fluctuations of biggins'
+  martingales at complex parameters}, arXiv:1806.09943, 2018.
+
+\bibitem{IksanovKoleskoMeiners2018Stable-like}
+\bysame, \emph{Stable-like fluctuations of biggins' martingales}, Stochastic
+  Process. Appl. (2018).
+
+\bibitem{Janson2004Functional}
+S.~Janson, \emph{Functional limit theorems for multitype branching processes
+  and generalized {P}\'{o}lya urns}, Stochastic Process. Appl. \textbf{110}
+  (2004), no.~2, 177--245.
+
+\bibitem{KestenStigum1966Additional}
+H.~Kesten and B.~P. Stigum, \emph{Additional limit theorems for indecomposable
+  multidimensional {G}alton-{W}atson processes}, Ann. Math. Statist.
+  \textbf{37} (1966), 1463--1481.
+
+\bibitem{KestenStigum1966A-limit}
+\bysame, \emph{A limit theorem for multidimensional {G}alton-{W}atson
+  processes}, Ann. Math. Statist. \textbf{37} (1966), 1211--1223.
 
 \bibitem{Kyprianou2014Fluctuations}
-Kyprianou, A. E.:
-\emph{Fluctuations of L\'{e}vy processes with applications.}
-Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
-\MR{3155252}
-
-\bibitem{KBA1}
-Kyprianou, A. E.:
-\emph{Limit theorems for multitype continuous time Markov branching processes I: the case of an eigenvector linear functional.}
-Z. Wahrs. Verw. Gebiete 12 (1969), 320-332.
-
-\bibitem{KBA2}
-Kyprianou, A. E.:
-\emph{Limit theorems for multitype continuous time Markov branching processes II: the case of an arbitrary linear functional.}
-Z. Wahrs. Verw. Gebiete 12 (1969), 204-214.
-
-\bibitem{KBA3}
-Kyprianou, A. E.:
-\emph{Some redinements in the theory of supercritical multitype Markov branching processes.}
-Z. Wahrs. Verw. Gebiete 12 (1971), 47-57.
-
-\bibitem{HKBPS1}
-Kesten, H. Stigum, B. P.:
-\emph{A limit theorem for multidimensional Galton-Watson processes.}
-Ann. Math. Statist. 37 (1966), 1221-1223.
-
-\bibitem{HKBPS2}
-Kesten, H. Stigum, B. P.:
-\emph{Additional limit theorems for indecomposable multidimensional Galton-Watson processes.}
-Ann. Math. Statist. 37 (1966), 1463-1481.
+A.~E. Kyprianou, \emph{Fluctuations of {L}\'{e}vy processes with applications},
+  2 ed., Universitext, Springer, Heidelberg, 2014.
+
+\bibitem{Le2019Long}
+K.~L\^{e}, \emph{Long-time asymptotic of stable {D}awson-{W}atanabe processes
+  in supercritical regimes}, Acta Math. Sci. \textbf{39} (2019), no.~1, 37--45.
 
 \bibitem{Li2011Measure-valued}
-Li, Z.:
-\emph{Measure-valued branching Markov processes.}
-Probability and its Applications (New York), Springer, Heidelberg, 2011.
-\MR{2060602}
-
-\bibitem{Linde1986Probability}
-Linde, W.:
-\emph{Probability in Banach spaces-stable and infinitely divisible distributions.}
-Second edition. A Wiley-Interscience Publication. John Wiley \& Sons, Ltd., Chichester, 1986.
+Z.~Li, \emph{Measure-valued branching {M}arkov processes}, Probability and its
+  Applications (New York), Springer, Heidelberg, 2011.
 
 \bibitem{LiuRenSong2009Llog}
-Liu, R., Ren, Y.-X., Song, R.:
-\emph{{$L log L$} criterion for a class of Superdiffusions.}
-J. Appl. Probab. \textbf{46} (2009), no. 2, 479-496.
-
-\bibitem{MP2012}
-Milo\'s, P.:
-\emph{Spatial CLT for the supercritical Ornstein-Uhlenbeck superprocess.}
-Preprint, 2012. arXiv:1203:6661
-
-\bibitem{MM}
-Marks,R., Milo\'s, P.:
-\emph{CLT for supercritical branching processes with heavy-tailed branching law.}
-\ARXIV{183.05491}
-
-\bibitem{GD}
-Metafune,~G., Pallara, D.:
-\emph{Specturm of Ornstein-Uhlenbeck operators in $\mathcal{L}^p$ space with respect to invariant measures.}
-J. Funct. Anal. 196,40-60(2002)
-
-\bibitem{RSZ}
-Ren, Y.-X., Song, R., Zhang, R.:
-\emph{Central limit theorems for super Ornstein-Uhlenbeck processes.}
-Acta Appl. Math. 130(2014)9-49.
-
-\bibitem{RSZ1}
-Ren, Y.-X., Song, R., Zhang, R.:
-\emph{Central limit theorems for supercritical branching Markov processes.}
-J. Funct. Anal. 266(2014): 1716-1756.
-
-\bibitem{RSZ2}
-Ren, Y.-X., Song, R., Zhang, R.:
-\emph{Central limit theorems for supercritical superprocesses.}
-Stochastic Processes and Their Applications, 125(2015) 428-457.
-
-\bibitem{RSZ3}
-Ren, Y.-X., Song, R., Zhang, R.:
-\emph{Central limit theorems for supercritical branching nonsymmetric Markov processes.}
-Ann. Probab., 45(1)(2017): 564-623.
-
-\bibitem{RSZ4}
-Ren, Y.-X., Song, R., Zhang, R.:
-\emph{Functional central limit theorems for supercritical superprocesses.}
-Acta Applicandae Mathematicae 147(1)(2017): 137-175.
+R.~Liu, Y.-X. Ren, and R.~Song, \emph{{$L\log L$} criterion for a class of
+  superdiffusions}, J. Appl. Probab. \textbf{46} (2009), no.~2, 479--496.
+
+\bibitem{LiuRenSong2013Strong}
+\bysame, \emph{Strong law of large numbers for a
+  class of superdiffusions}, Acta Appl. Math. \textbf{123} (2013), 73--97.
+
+\bibitem{MarksMilos2018CLT}
+R.~Marks and P.~Mi{\l}o{\'s}, \emph{C{LT} for supercritical branching processes
+  with heavy-tailed branching law}, arXiv:1803.05491, 2018.
+
+\bibitem{MetafunePallaraPriola2002Spectrum}
+G.~Metafune, D.~Pallara, and E.~Priola, \emph{Spectrum of
+  {O}rnstein-{U}hlenbeck operators in {$L^p$} spaces with respect to invariant
+  measures}, J. Funct. Anal. \textbf{196} (2002), no.~1, 40--60.
+
+\bibitem{Milos2012Spatial}
+P.~Mi{\l}o{\'s}, \emph{Spatial {CLT} for the supercritical
+  {O}rnstein-{U}hlenbeck superprocess}, arXiv:1203.6661, 2012.
 
 \bibitem{RenSongSun2017Spine}
-Ren, Y.-X., Song, R., Sun, Z.:
-\emph{ Spine decompositions and limit theorems for a class of critical superpeocesses.}
-arXiv preprint arXiv: 1711. 09188(2017).
-
-\bibitem{Rudin1987Real}
-Rudin, W.:
-\emph{Real and complex analysis.}
-Third edition. McGraw-Hill Book Co., New York, 1987.
-\MR{0924157}
-
-\bibitem{SchillingSongVondracek2010Bernstein}
-Schilling, R., Song, R., Vondra\v{c}ek, Z.:
-\emph{Bernstein functions. Theory and applications.}
-De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2010.
-\MR{2598208}
-
-\bibitem{Sato1999Levy}
-Sato, K.:
-\emph{L\'evy proesses and infinitely divisible distributions.}
-Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.
+Y.-X. Ren, R.~Song, and Z.~Sun, \emph{Spine decompositions and limit theorems
+  for a class of critical superprocesses}, arXiv:1711.09188, 2017.
+
+\bibitem{RenSongZhang2014Central}
+Y.-X. Ren, R.~Song, and R.~Zhang, \emph{Central limit theorems for super
+  {O}rnstein-{U}hlenbeck processes}, Acta Appl. Math. \textbf{130} (2014),
+  9--49.
+
+\bibitem{RenSongZhang2014CentralB}
+\bysame, \emph{Central limit theorems for supercritical branching {M}arkov
+  processes}, J. Funct. Anal. \textbf{266} (2014), no.~3, 1716--1756.
+
+\bibitem{RenSongZhang2015Central}
+\bysame, \emph{Central limit theorems for supercritical superprocesses},
+  Stochastic Process. Appl. \textbf{125} (2015), no.~2, 428--457.
+
+\bibitem{RenSongZhang2017Central}
+\bysame, \emph{Central limit theorems for supercritical branching nonsymmetric
+  {M}arkov processes}, Ann. Probab. \textbf{45} (2017), no.~1, 564--623.
+
+\bibitem{RenSongZhang2017Functional}
+\bysame, \emph{Functional central limit theorems for supercritical
+  superprocesses}, Acta Appl. Math. \textbf{147} (2017), 137--175.
+
+\bibitem{Sato2013Levy}
+K.~Sato, \emph{L{\'e}vy processes and infinitely divisible distributions},
+  Cambridge Studies in Advanced Mathematics, vol.~68, Cambridge University
+  Press, Cambridge, 2013.
+
+\bibitem{SchillingSongVondravcek2010Bernstein}
+R.~L. Schilling, R.~Song, and Z.~Vondra\v{c}ek, \emph{Bernstein functions}, De
+  Gruyter Studies in Mathematics, vol.~37, Walter de Gruyter \& Co., Berlin,
+  2010.
 
 \bibitem{SteinShakarchi2003Complex}
-Stein, E. M and Shakarchi, Rami.:
-\emph{Complex analysis.}
-Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.
+E.~M. Stein and R.~Shakarchi, \emph{Complex analysis}, Princeton Lectures in
+  Analysis, vol.~2, Princeton University Press, Princeton, NJ, 2003.
+
+\bibitem{Wang2010An-almost}
+L.~Wang, \emph{An almost sure limit theorem for super-{B}rownian motion}, J.
+  Theoret. Probab. \textbf{23} (2010), no.~2, 401--416.
+
+\bibitem{Wang2018Central}
+\bysame, \emph{Central limit theorems for supercritical superprocesses with
+  immigration}, J. Theoret. Probab. \textbf{31} (2018), no.~2, 984--1012.
 
 \end{thebibliography}
+%\end{comment}
 

### 2019-03-06 supCLT.tex
supCLT.tex: 0303
0305

@@
 %%----Versions-----------------------------
-% supCLT0128.tex 2018/01/28 by Renming
-% supCLT0127.tex 2018/01/27 by Yanxia
-% supCLT0124.tex 2018/01/24 by Jianjie
-% supCLT0114.tex 2018/01/14 by Yanxia
-% supCLT0107.tex 2018/01/07 by Jianjie
+% supclt0220.tex 2019/02/20 by Jianjie
+% supclt0217.tex 2019/02/14 by Renming
+% supclt0214.tex 2019/02/14 by Yanxia
+% supclt0211.tex 2019/02/11 by Zhenyao
+% supCLT0128.tex 2019/01/28 by Renming
+% supCLT0127.tex 2019/01/27 by Yanxia
+% supCLT0124.tex 2019/01/24 by Jianjie
+% supCLT0114.tex 2019/01/14 by Yanxia
+% supCLT0107.tex 2019/01/07 by Jianjie
 % supclt1231.tex 2018/12/14 by Zhenyao
@@
 \usepackage{mathrsfs}
-%\usepackage[backref=section]{hyperref}
-\usepackage{hyperref}
+\usepackage[backref=section]{hyperref}
+%\usepackage{hyperref}
 \usepackage{comment}
@@
 \title
-    [CLT for Super-OU processes]
-    {Stable Central Limit Theorems for Super OU Processes with Stable Branching}
+    %[CLT for Super-OU processes]
+    [stable CLT for super-OU processes]
+    %{Stable Central Limit Theorems for Super OU Processes with Stable Branching}
+    {Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
 \author
@@
 \email{yxren@math.pku.edu.cn}
-\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
+\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}
 \address
@@
 \email{zhaojianjie@pku.edu.cn}
+\thanks{Jianjie Zhao is the corresponding author}
+%ZS: I changed all "branching rate regime" to "branching rate regime" below.
 \begin{abstract}
-    Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z),$ where $\alpha >0$ and $\beta\in (0,1)$ and $psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that $|\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).$
-    For each testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
-    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
-    In the small branching rate case $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
-    In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
-    In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$, we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$, and then established a central limit theorem, which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges weakly to a $(1+\beta)$-stable random variable.
+	%Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism 
+    Consider a $(\xi, \psi)$-superprocess $(X_t)_{t\geq 0}$ where the spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$  which has generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ with $\sigma, b >0$, and the
+    branching mechanism $\psi$ takes the form close to
+	$\psi(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$ in some sense.
+    For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$.
+    %Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: 
+    Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
+    %In the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
+    %In the critical branching rate regime  $\alpha\beta= \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
+    %In the large branching rate regime  $\alpha\beta> \kappa_f b(1+\beta)$, we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$, and then established a central limit theorem, which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges weakly to a $(1+\beta)$-stable random variable.
+    the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
 \end{abstract}
-%\subjclass[2010]{60J80, 60F05}
-%\keywords{}
+\subjclass[2010]{60J68, 60F05}
+\keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}
 %\date{}
@@
 \section{Introduction}
-%Moved and modified from below
 \subsection{Motivation}
 \label{sec: Motivation}
-In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
-\[
-    \frac{\langle f, X_t \rangle -G_t}{F_t}
-\] 
-    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. 
-    It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
-
-    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. 
-    See \cite{KestenStigum1966A-limit,KestenStigum1966Additional} for supercritical multi-type Galton-Waston processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-    In \cite{AdamczakMilos2015CLT}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
-    These two papers made connections between CLT and what they call branching rate regimes. 
-    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
-    Moverover, compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate. 
-    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central,RenSongZhang2017Functional}, Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
-    All the results described above hold for systems with branching mechanisms with finite variance. 
-    It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
-    In \cite{MarksMilos2018CLT}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
-They established some central limit theorems in small and critical branching rate cases, but \cite{MarksMilos2018CLT} contained no central limit result in the branching rate case.
-    In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. 
-    For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}.
-    For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit theorem, which has no counterpart in \cite{MarksMilos2018CLT}.
-
-%Added
-    {\bf ZS: I think this subsection should be extended with more literatures like: 
-    \cite{AdamczakMilos2014U-statistics}, 
-    \cite{EckhoffKyprianouWinkel2015Spines},
-    \cite{EnglanderHarrisKyprianou2010Strong},
-    \cite{IksanovKabluchko2016A-central}, 
-    \cite{LiuRenSong2013Strong}, 
-    \cite{Wang2018Central},
-    \cite{IksanovKoleskoMeiners2018Stable-like},
-    \cite{IksanovKoleskoMeiners2018Fluctuations},
-    \cite{GrubelKabluchko2016A-functional},
-    \cite{Heyde1970A-rate}, 
-    \cite{Heyde1971Some}, 
-    \cite{HeydeBrown1871An-invariance}, 
-    \cite{HeydeLeslie1971Improved}, 
-    \cite{BansayeDelmasMarsalleTran2011Limit}, 
-    \cite{EnglanderWinter2006Law}, 
-    \cite{Englander2009Law}, 
-    \cite{Janson2004Functional}, 
-    \cite{ChenRenWang2008An-almost}, 
-    \cite{Wang2010An-almost}, 
-    \cite{HartungKlimovsky2018The-phase}, 
-    \cite{BansayeDelmasMarsalleTran2011Limit}, 
-    \cite{Le2019Long}.
-}
-%end and modified from below
-%\subsection{Model}\label{sec: main results}
-\subsection{Main results}
-\label{sec: main results}{}
-	Let $d \in \mathbb N:= \{1,2,\dots\}$.
-%moved and modifeid from below 
-    Let $\mathbb R_+:= [0,\infty)$.
-    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
-    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
-    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-    For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
-    For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
-%deletd
-    %Write $\|\mu\|=\langle 1,\mu\rangle$ for each $\mu \in \mathcal M(\mathbb R^d)$. 
-%end deleted
-    We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have 
-\[
-    \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
-\]
-%end moved from below
+	Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
+%MOVED BELOW
+    %Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
+    %Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
+    %Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
+    %For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
+    %For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
+    %We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have
+%\[
+    %\sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
+%\]
+%END MOVED BELOW
     Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
@@
 \end{equation}
-    where $\sigma$ and $b$ are positive constants.
-%deleted
-    %Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
-%end deleted
-    %Let $\psi$ be the function on $\mathbb R_+$ defined by
+    %where $\sigma$ and $b$ are positive constants.
+    where $\sigma > 0$ and $b > 0$ are constants.
         Let the \emph{branching mechanism} $\psi$ be a function on $\mathbb R_+$ which takes the form of
@@
 \end{equation}
-	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
-%new added
-	It is known that $\alpha, \rho$ and $\pi$ are uniquelly determined by function $\psi$. 
+	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty$.
+%DELETED
+	%It is known that $\alpha, \rho$ and $\pi$ are uniquely determined by the function $\psi$.
+%END DELETED
 	We refer to $\pi$ the \emph{L\'evy measure} of the branching mechanism $\psi$.
-%end new added
-%moved above
-    %We use $\mathcal B(\mathbb R^d, \mathbb R)$ to denote   the space of all real-valued Borel measurable functions on $\mathbb R^d$ and use $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-	%For $f\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, we write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
-    %We aslo use the notation $\|\mu\|=\langle 1,\mu\rangle$. 
-    %For $f, g\in \mathcal B(\mathbb R^d, \mathbb R)$, we also write $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
-%end moved above
-    %We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
-    We say an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
-\begin{equation} 
-%\label{super}
+%MOVED FROM ABOVE
+    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
+    For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
+    We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have
+\[
+    \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
+\]
+%END MOVED FROM ABOVE
+       We say an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ 
+on a measurable space $(\Omega, \mathcal{F})$       
+       is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+\begin{equation}
+\label{eq: def of V_t}
     \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
@@
 \begin{equation}
-%\label{eq1}
-	%V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
 	    V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(V_{t-s}f(\xi_s)\big)~ds\Big]
@@
 \end{equation}	
-    %The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.
     The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
-%Added
-
+
+    Recently, there have been quite a few papers on laws of large numbers for superdiffusions.
+In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established.
+The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost},
+    %followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost}. 
+    %The setups of the papers mentioned above are  different. 
+    followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost} under different settings.
+    For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.
+
+    %In this paper, we focus on limit results for the super-OU process $X$.
+    %The strong law of large numbers of $X$ can be stated as follows: 
+    The strong law of large numbers of the above super-OU process $X$ can be stated as follows: 
+    Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our assumptions 1 and 2, below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$,
+    %for every Lebesgue-almost everywhere continuous bounded $f\in\mathcal B(\mathbb R^d, \mathbb R_+)$,
+    for every Lebesgue-almost everywhere continuous bounded non-negative function $f$ on $\mathbb R^d$, 
+    we have
+    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f,\phi_0\varphi\rangle $, 
+    %where  $H_\infty=\lim_{t\to\infty}e^{-\alpha t}\|X_t\|$, and the convergence also holds in $L^1(\mathbb P_\mu)$, see \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
+    where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\phi_0$, $\varphi$ are functions which will be introduced in  \eqref{eigenfunction} and \eqref{invariantdensity} below.
+    See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
+
+    %In this paper, we will establish some spatial central limit theorems for the super-OU process $X$ above.  
+    In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above. 
+%NEW ADDED
+    Our key assumption is that the corresponding branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$ where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$ in some sense.
+%END ADDED
+    %More precisely, we want to find 
+    We want to find
+    %$F_t$ and $G_t$ such that
+    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
+\[
+    \frac{\langle f, X_t \rangle -G_t}{F_t}
+\]
+    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, 
+    %for some test functions $f$.
+    for some testing functions $f$.
+    %It turns out that the normalization $F_t$ depends on the branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
+    It turns out that there are three regimes of different behavior of this CLT depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
+Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
+%ADDED
+    Note that, under the settings of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
+%END ADDED
+
+    %There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses.
+    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under finite second moment condition.
+    See
+    \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes, 
+    %see \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Waston processes, 
+    \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Watson processes,
+    \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
+    In \cite{AdamczakMilos2015CLT}, 
+    %Adamcazk and Milo\'s 
+    Adamczak and Milo\'s 
+    proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+    These two papers made connections between CLT and what they call branching rate regimes.
+    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
+    %Moverover, 
+    Moreover,
+    compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
+    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central},
+    Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
+    The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
+
+    %All central limit results described above hold for systems with branching mechanisms with finite variance.
+    %It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
+    There are also many limiting theory for branching processes and branching Markov processes with branching mechanisms of infinite second moments.
+    Heyde \cite{Heyde1971Some} established a central limit type  theorem for Galton-Watson process 
+when the offspring distribution
+    %belongs to the domain of a stable law of index $\alpha\in (1, 2]$, 
+    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
+    and   proved that the limit law is  a stable law. Similar results  for supercritical multi-type Galton-Watson processes and supercritical  continuous time branching processes,  
+under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
+    were given in Asmussen \cite{Asmussen76Convergence}.
+    Recently,   Marks and Milo\'s \cite{MarksMilos2018CLT}
+    considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. 
+    %They established some central limit theorems in small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
+    They established some central limit theorems in small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
+%NEW ADDED
+    We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered the stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.
+%END NEW ADDED
+
+%NEW ADDED
+    As far as we know, this paper is the first one in the literature on establishing CLT for supercritical superprocesses without the second moment condition.
+%END added
+%DELETED
+    %In this paper, we consider a class of super-OU processes with a general stable branching mechanism.
+    %For small and critical branching rate regimes, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}.
+    %For large branching rate regime, we not only prove an almost sure convergence result as in \cite{MarksMilos2018CLT}, we also prove a central limit theorem type result.
+%END DELETED
+
+%DELETED    
+    %For recent works on limit results (strong law of large numbers and central limit theorems) for branching diffusions and general branching Markov processes, we refer to \cite{BansayeDelmasMarsalleTran2011Limit, ChenRenSongZhang2017Law, EnglanderHarrisKyprianou2010Strong, GrubelKabluchko2016A-functional, RenSongZhang2015Central} and references there in.
+%END DELETED
+
+%    {\bf ZS: I think this subsection should be extended with more literatures like:
+%    \cite{AdamczakMilos2014U-statistics},
+ %   \cite{EckhoffKyprianouWinkel2015Spines},
+%    \cite{EnglanderHarrisKyprianou2010Strong},
+%    \cite{IksanovKabluchko2016A-central},
+%    \cite{LiuRenSong2013Strong},
+%    \cite{Wang2018Central},
+%    \cite{IksanovKoleskoMeiners2018Stable-like},
+%    \cite{IksanovKoleskoMeiners2018Fluctuations},
+%    \cite{GrubelKabluchko2016A-functional},
+%    \cite{Heyde1970A-rate},
+%    \cite{Heyde1971Some},
+%    \cite{HeydeBrown1871An-invariance},
+%    \cite{HeydeLeslie1971Improved},
+%    \cite{BansayeDelmasMarsalleTran2011Limit},
+%    \cite{EnglanderWinter2006Law},
+%    \cite{Englander2009Law},
+%    \cite{Janson2004Functional},
+%    \cite{ChenRenWang2008An-almost},
+%    \cite{Wang2010An-almost},
+%    \cite{HartungKlimovsky2018The-phase},
+%    \cite{BansayeDelmasMarsalleTran2011Limit},
+%    \cite{Le2019Long}.
+%
+ %   YX: I have added some parts which are related to references listed above.
+But I did not cite  \cite{AdamczakMilos2014U-statistics}, \cite{HartungKlimovsky2018The-phase} and \cite{Wang2018Central} since these are not closely related to our paper.
+I did not cite \cite{HeydeLeslie1971Improved}--\cite{IksanovKoleskoMeiners2018Stable-like} since these are about central limit theorems for Biggin's martingales.
+%}
+\subsection{Main results}
+\label{sec: main results}{}
+
+%MOVED BELOW	
+	%Denote by $\Gamma$ the gamma function.
+%For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
+%END MOVED BELOW
+	We will always assume that the following Assumption holds.
+\begin{asp}
+\label{asp: Greys condition}
+	The branching mechanism satisfies the Grey's condition, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+\end{asp}
+%MOVED FROM ABOVE
+    For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
+%END MOVED FROM ABOVE
+	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, 
+	the \emph{extinction event} 
+	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has a positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
+    In fact,
+\begin{equation}
+    \mathbb{P}_{\mu} (D)
+    = e^{-\bar v \|\mu\|},
+    \quad \mu\in \mathcal M(\mathbb R^d),
+\end{equation}
+    where
+\[
+	\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
+\]
+	is the largest root of $\psi$.
+
+%MOVED FROM ABOVE
     Denote by $\Gamma$ the gamma function.
-	In this paper, we will always assume that the following Assumption holds.
-%End added
-
-%Deleted
-    %According to Subsection A.1, the branching mechanism $\psi$ can be extended to
-    %$\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
- %\[
-    %\psi(z)=
-    %- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
-    %\quad  z \in \mathbb C_+,
-%\]
-    %which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
-    %\{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
-%\begin{equation}
-%\label{eq: deriavetive of the Poission part}
-    %\psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
-    %\quad z\in \mathbb C^0_+.
-%\end{equation}
-
-%\begin{asp}
-%\label{asp: branching mechanism}
-    %The branching mechanism takes the form of
-%\[
-    %\psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
-%\]
-    %where $\alpha>0$, $\eta > 0$, $\beta \in (0,1)$ and $\psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
-%\[
-    %|\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
-%\]
-%\end{asp}
-%end Deleted
-%added
+For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
+%END MOVED FROM ABOVE    
+    In this paper, we will also assume the following:
 \begin{asp}
@@
 \end{asp}
-
-	It will be showed in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquelly determined by the L\'evy measure $\pi$.
-	In the reminder of the paper, we will always write $\eta,\beta$ for the constants corresponding to $\pi$.
+    %{\bf Jianjie: do we need to emphasize that $\delta\in (0,1-\beta)$ such that $1+\beta+\delta<2$.}
+    %ZS: It is done by Remark 1.1. 
+	We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
+	In the reminder of the paper, we will always use $\eta,\beta$ to denote the constants corresponding to $\pi$.
 \begin{rem}
 \label{rem: small enough delta}
-	Note that $\delta$ is not uniquelly determined by $\pi$. 
+	Note that $\delta$ is not uniquely determined by $\pi$.
 	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
@@
 
-    Assumption \ref{asp: branching mechanism} says that there exists a constatn $\eta>0$ and $\beta > 0$ such that the Levy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
-    In particular, if $\pi(dy)$ equals to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of a stable branching
+    Assumption \ref{asp: branching mechanism} says that 
+ there exist constants $\eta>0$ and $\beta > 0$ 
+    such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
+    In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$
+    takes the form of
 	$-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
-	It will be proved in Lemma \ref{lem: LlogL criterion} that under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ criteria, i.e. 
+	It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ criteria, i.e.,
 \[
@@
 \]
-
-	In this paper, we will also assume the following:
-\begin{asp}
-\label{asp: Greys condition}
-	The branching mechanism satisfies the Grey's condition, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-\end{asp}
-%end added
-%moved to the nexe section
-%\begin{lem}
-    %Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e.
-there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-    %Also, $\psi$ satisfies the $L \log L$ criterion  i.e.,
-%\[
-    %\int_1^\infty y \log y~\pi(dr)< \infty.
-%\]
-%\end{lem}
-%\begin{proof}
-    %{ Need a proof.}
-%\end{proof}
-%end moved to the next section
-
-%Deleted
-    %According to \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations}, we have
-%\begin{equation}
-    %\mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
-    %= e^{-\bar v \|\mu\|},
-%\end{equation}
-    %where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
-%End Deleted
-%Added
-	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{distinguish event} $D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has a positive probability, with respect to each $\mathbb P_\mu$ with $\mu \in \mathcal M(\mathbb R^d)$.
-    In fact,
-\begin{equation}
-    \mathbb{P}_{\mu} (D)
-    = e^{-\bar v \|\mu\|},
-    \quad \mu\in \mathcal M(\mathbb R^d),
-\end{equation}
-    where 
-\[
-	\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
-\]
-	is the largest root of $\psi$.
-%End added
-
+%NEW ADDED
+    This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate. 
+%END NEW ADDED
+
+%MOVED FROM ABOVE
+    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
+    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
+%END MOVED FROM ABOVE
+    We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
     Define
@@
 \end{equation}
-    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
-\begin{equation}
-%\label{eq:meanformula}
+    It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
+\begin{equation}
     \mathbb{P}_{\mu}[\langle f, X_t \rangle]
@@
 \end{equation}
-%Moved to the first Subsection
-    %In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
-%\[
-    %\frac{\langle f, X_t \rangle -G_t}{F_t}
-%\] 
-    %converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. 
-    %It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
-    %There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. 
-    %See \cite{KestenStigum1966A-limit,KestenStigum1966Additional} for supercritical multi-type Galton-Waston processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-    %In \cite{AdamczakMilos2015CLT}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
-    %These two papers made connections between CLT and what they call branching rate regimes. 
-    %In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
-    %Moverover, compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate. 
-    %In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central,RenSongZhang2017Functional}, Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
-    %All the results described above hold for systems with branching mechanisms with finite variance. 
-    %It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
-    %In \cite{MarksMilos2018CLT}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
-They established some central limit theorems in small and critical branching rate cases, but \cite{MarksMilos2018CLT} contained no central limit result in the branching rate case.
-    %In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. 
-    %For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}.
-    %For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit theorem, which has no counterpart in \cite{MarksMilos2018CLT}.
-%End moved to the first subsection
-%Deleted
-%\subsection{OU Semigroup}
-%End Deleted
-    %In this subsection, we recall some spectral properties of the OU operator $L$ from \cite{MetafunePallaraPriola2002Spectrum}.
-    %Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
-    The limiting behavior of the super-OU process is closly related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, on the property of the OU semigoup $(P_t)_{t\geq 0}$.
+        The limiting behavior of the super-OU process is closely related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.
 
     We now recall some basic spectral properties of $(P_t)_{t\geq 0}$ from \cite{MetafunePallaraPriola2002Spectrum}.
-    %It is known that $\xi$ has an invariant measure
         It is known that the OU process $\xi$ has an invariant measure
@@
     Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$.
-    %$L^2(\varphi)$ is a Hilbert space with inner product
         Then, $L^2(\varphi)$ is a Hilbert space with inner product
@@
 \end{equation}
-    %Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
        Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-    For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+    For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
     The \emph{Hermite polynomials} are defined by
@@
 \end{equation}
-    %It is known that $(P_t)$ is a strongly continuous semigroup in $L^2(\varphi)$ and $L$ has discrete spectrum 
        It is known that the transition semigroup $(P_t)_{t\geq 0}$ of the OU process $\xi$ is a strongly continuous semigroup in $L^2(\varphi)$, and its corresponding generator $L$ has discrete spectrum
-    %$a(L)= \{-bk: k \in \mathbb Z_+\}$.
         $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
@@
     \phi_p(x)
-    %:= \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{a}x \Big),
         := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
@@
 \end{equation}
-    %It is known that
-    In another word,
+       In other words,
 \begin{equation}
@@
     f
-    %=\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
          =\sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
@@
 \end{equation}
-    Denote by
-\begin{equation}
-%\label{order}
+    %Denote by
+    For each function $f\in L^2(\varphi)$, denote by
+\begin{equation}
     \kappa_f
@@
 \end{equation}
-    %the order of the function in spectral decomposition \eqref{semicomp1}.
     the order of the function $f$ in its spectral decomposition \eqref{semicomp1}.
-    Note that $ \kappa_f\geq 0$.
-    In particular, the order of any constant function is zero.
+    Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
+    In particular, the order of any constant non-zero function is zero.
     Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
@@
     \mathcal{P}
-    :=\big \{f\in \mathscr B(\mathbb R^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+    :=\big \{f\in \mathscr B(\mathbb R^d, \mathbb R):\exists~ C>0, n \in \mathbb Z_+, {\rm such  \, \, that \, } \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
 \end{equation}
     It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-%Deleted
-%\subsection{Main Results}
-    %We will use $\mathcal M_c(\mathbb R^d)$ to denote the space of all finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of the super-OU process.
-%End Deleted
-    %In this subsection, we will give the main results of this paper.
-    In this paper, we are mainly interested in the asmptotic behavior of $\langle f, X_t\rangle$ with $f\in \mathcal P$ under the following three cases:
-    %The results are stated in three separate cases: the large branching rate case, critical  branching rate case and small  branching rate case.
+    In this paper, we are mainly interested in the asymptotic behavior of $\langle f, X_t\rangle$ 
+    %for $f\in \mathcal P$. 
+    for non-trivial $f\in \mathcal P$.
+    The asymptotic behavior varies with the following three regimes:
     \begin{itemize}
 \item
-    The large branching rate case: $\alpha\beta>\kappa_fb(1+\beta)$;
-\item
-    The critical branching rate case: $\alpha\beta=\kappa_fb(1+\beta)$;
-\item
-    The small branching rate case: $\alpha\beta<\kappa_fb(1+\beta)$.
+    The large branching rate regime: $\alpha\beta>\kappa_fb(1+\beta)$;
+\item
+    The critical branching rate regime: $\alpha\beta=\kappa_fb(1+\beta)$;
+\item
+    The small branching rate regime: $\alpha\beta<\kappa_fb(1+\beta)$.
 \end{itemize}
-
-\subsubsection{Large branching rate case}
-%Added
+%DELETED
+    %Note that in the large and critical branching rate regimes, $f$ is non-trivial.
+%END DELETED
+
+\subsubsection{Large branching rate regime}
     Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
-%End Added
     For each $p\in \mathbb{Z}_+^d$, define
@@
     If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
-    %$H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ (see Lemma \ref{lemma26}).
-    it will be proved in Lemma \ref{lemma26} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+      we will prove in Lemma \ref{lemma26} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
     Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
- \begin{thm}\label{Theorem11}
-     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, %as $t\rightarrow \infty$,
+ \begin{thm}
+ \label{thm: law of large number}
+     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then
+   for all
+     $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
 \[
     e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle
-    %\rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p 
        \xrightarrow[t\to \infty]{}\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p
@@
 \end{thm}
-\begin{comment}
-    For any $t\geq 0$, let $H_t:=e^{-\alpha t}\|X_t\|$. 
-    Then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s.
-and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
 \begin{rem}
-    Let $f \in \mathcal{P}$.  If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f, 1\rangle_\phi=\langle f,\varphi\rangle$. 
-    Hence by Theorem \ref{Theorem11}, for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
+   If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
+    %Hence by Theorem \ref{thm: law of large number}, 
+    Hence, Theorem \ref{thm: law of large number} says that
+    for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
 \[
@@
     \rightarrow \langle f, \varphi\rangle H_{\infty}
-    \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).
-\]
-    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
+    \quad \mbox{in } L^{1+\gamma}(\mathbb{P}_{\mu}).
+\]
+    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have the almost sure convergence.
+    %In fact, to get the almost sure convergence for bounded test functions $f$, we do not need $f$ to be twice differentiable.
+$f$ being bounded and Lebesgue-almost every where continuous is enough for the almost sure convergence, see \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
+    However, to get the almost sure convergence for bounded, non-negative, and Lebesgue-almost every where continuous testing functions $f$, we do not need $f$ to be twice differentiable.
+See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
 \end{rem}
-\end{comment}
-%Moved and modified from below
+\begin{rem} 
+    %For general test functions $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} says that the correct scaling for $\langle f, X_t\rangle$ is $e^{-(\alpha-\kappa_fb)t}$.
+%Theorem \ref{thm: law of large number} gives a strong law of large numbers for general test functions $f$ in the large branching rate regime, and it extends the strong laws of large numbers in  \cite{ChenRenYang2019Skeleton} and \cite{EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
+    For general test functions $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers in  \cite{ChenRenYang2019Skeleton} and \cite{EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
+%DELETED 
+    %For any $f \in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} gives an expansions of $e^{-\alpha t} \langle f, X_t\rangle$ in the following sense:
+    %\[
+    %e^{-\alpha t}\langle f, X_t\rangle=
+    %\sum_{p\in \mathbb Z_+^d:|p|\leq\kappa_f} e^{-|p|t}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p+o(e^{-\kappa_ft}),
+    %\]
+    %where $\lim_{t\to\infty}e^{\kappa_ft}o(e^{-\kappa_ft})=0$ in   $L^{1+\gamma}(\mathbb{P}_{\mu})$.  
+%END DELETED
+    When the generator of the 
+Ornstein-Uhlenbeck process is replaced by $-(-\Delta)^{\frac{p}{2}}$ with $p\in(0,2]$, similar results have been obtained by L\^{e} \cite{Le2019Long}.    
+    \end{rem}
+
+    The fluctuation result associated to the law of large numbers are given in the following Theorem \ref{thm: large clt}.
 Define
@@
 \label{eq: def of N}
-    \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
+    \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
+%ADDED
+    \quad K : = \sup\{|p|: p \in \mathcal N\}.
+%END ADDED
 \end{equation}
@@
 \end{equation}
-    Define an operator $(I_t)_{t\geq 0}$ on $\mathcal{C}_l$ such that
+    For each $t\ge 0$, we define an operator $I_t$ on $\mathcal{C}_l$ by
 \begin{align}\label{definition of Itf}
@@
     :=\sum_{p\in \mathcal{N}}\langle f, \phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x),
-    \quad t\geq 0, x\in \mathbb{R}^d, f\in \mathcal C_l.
+   \quad x\in \mathbb{R}^d, f\in \mathcal C_l.
 \end{align}
@@
 \end{align}
-    It will be showed in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$.
-    It will also be proved in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp(\theta \bar m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
+    %We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$.
+    %We will show that, when $f\in \mathcal{P}$ is non-trivial, $\theta \mapsto \exp(\theta \bar m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
+    We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; and in Lemma \ref{prop: alpha stable rv} that that, when $f\in \mathcal{P}$ is non-trivial, $\theta \mapsto \exp(\theta \bar m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
 \begin{thm}
 \label{thm: large clt}
-    For $f\in\mathcal{C}_l$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that,
+    %For $f\in\mathcal{C}_l$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that,
+    For non-trivial $f\in\mathcal{C}_l$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that,
 \begin{align}\label{thm: large rate}
@@
 \end{thm}
-%End moved from below
-
-\subsubsection{Critical branching rate case}
+
+\subsubsection{Critical branching rate regime}
     For each $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
 \begin{equation}\label{tilde-m}
-    %\widetilde{m}[f]
-    \tilde{m}[f]
-    %:= \langle \eta (-if_0)^{1+\beta},\varphi\rangle
+    \widetilde{m}[f]
         := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
 \end{equation}
-%Deleted
-    %where
-%\begin{equation}\label{phif}
-    %f_0(x)
-    %=\sum_{|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x).
-%\end{equation}
-%End Deleted
-%Added
-    It will be proved in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp(\theta \tilde m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
-%End added
+%ADDED
+    According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
+%END ADDED
+   We will prove in Lemma \ref{prop: alpha stable rv} that
+   $\theta \mapsto \exp(\theta \widetilde m[f])$
+    is a characteristic function of an $(1+\beta)$-stable random variable.
 \begin{thm}
 \label{thm: critical clt}
-    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$, %under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, 
+    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$,
     under $\mathbb{P}_{\mu}(\cdot|D^c)$,
@@
     \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
-    %\xrightarrow{d} \tilde{\zeta},
-    %\quad t\rightarrow \infty,
         \xrightarrow[t\to \infty]{d} \tilde{\zeta},
@@
     where $\tilde{\zeta}$ is a $(1+\beta)$-stable random variable with
-%Added
-    characteristic funciton
-%End Added
-\[
-    %\mathbb{E} [e^{i\theta \tilde{\zeta}}]
+    characteristic function
+\[
      \mathbf E [e^{i\theta \tilde{\zeta}}]
@@
 
-\subsubsection{Small branching rate case}
+\subsubsection{Small branching rate regime}
 \label{msmallcase}
-	For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_f b(1+\beta)$, we define
+	If $f\in \mathcal{P}$ is non-trivial and satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, 
+	we define
 \begin{equation}
     m[f]
-    %=\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds 
-    =\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
+    :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
 \end{equation}
 	According to Lemma \ref{lem: def of all m} below, $m[f]$ is well-defined.
-%Added
-	It will also be proved in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp(\theta m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
-%End ADDEd
+	We will prove  in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp(\theta m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
 \begin{thm}
 \label{thm: small clt}
-    If $f\in\mathcal{P}$ satisfies $\alpha\beta<\kappa_f b(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-\[
-    %\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \zeta, \quad t\rightarrow \infty,
+       If $f\in\mathcal{P}$ is non-trivial and satisfies $\alpha\beta<\kappa_f b(1+\beta)$, 
+    then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+\[
         \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow[t\rightarrow \infty]{d} \zeta,
@@
 \[
-    %\mathbb{E} [e^{i\theta \zeta}]
        \mathbf E[e^{i\theta \zeta}]
@@
 \end{thm}
-%Deleted
-%\subsubsection{Further results in the large branching rate case}
-%End Deleted
-%Moved to above
-\begin{comment}
-    Define
-\begin{align}
-   \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
-\end{align}
+%ADDED
+\subsection{Some words before the proofs}
+%END ADDEd
+Let us give some intuition about the central limit theorems above before we move to proofs.  
+The mains ideas are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
+For any $\mu\in  \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
+\begin{equation}\label{Ist}
+    \mathcal I_s^t Y:=\mathcal I_s^t [Y, \mu]
+    := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s],\quad 0 \leq s \leq t <\infty.
+\end{equation}
+    We will use the shorter notation $\mathcal I_s^t Y$ when there is no danger of confusion. 
+    %Then for any $f\in \mathcal{P}$, we have 
+    For each $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
+\begin{align}
+       \langle f,X_t\rangle
+        %= &\sum_{k=0}^{\lfloor t \rfloor-1} \left(\mathbb P_\mu[\langle f ,X_t\rangle|\mathscr F_{t-k}] - \mathbb P_\mu[\langle f ,X_t\rangle|\mathscr F_{t-k-1}]\right)+\\
+        %&\left(\mathbb P_\mu[\langle f ,X_t\rangle|\mathscr F_{{t-\lfloor t \rfloor}}] - \mathbb P_\mu[\langle f ,X_t\rangle|\mathscr F_{0}]\right)+ \langle P^\alpha_tf,X_0\rangle\\
+        :=\sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle+\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle +
+         \langle P^\alpha_tf,X_0\rangle,
+               \quad t\geq 0.
+\end{align}
+   %Therefore, to find the normalized limit of  $\langle f,X_t\rangle$, we need to look at each term $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$.
+   To find the fluctuation of $\langle f,X_t\rangle$, we will investigate the fluctuation of each term $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$.
+%DELETED
+ %Note that $$
+ %\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle=\langle P^\alpha_kf, X_{t-k}\rangle-\mathbb P_\mu[\langle P^\alpha_kf, X_{t-k}\rangle|\mathscr F_{t-k-1}]
+ %$$
+%END DELETED
+
+%ADDED
+    Suppose that $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions
+\[
+    \mathbf E[e^{i\theta \zeta_k}] = \exp(e^\alpha m_k[\theta f]),\quad k \in \mathbb N
+\]   
+    where $m_k[f]$ is given by Lemma \ref{lem: def of all m} below.
+    Recall that $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
+    Lemma \ref{lem: mainlemma} and Corollary \ref{cor: indepedent of the limit zeta for critical and small} below actually says that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
+\[
+    \bigg(\frac{\mathcal I^{t-k}_{t-k-1}\langle f,X_t\rangle}{(e^{-\alpha}\|X_t\|)^{\frac{1}{1+\beta}}}\bigg)_{k=1}^n 
+    \xrightarrow [t\to \infty]{d} (\zeta_k)_{k=1}^n.
+\]
+    So if $f$ lives in the small branching rate regime, i.e. $\alpha \beta < \kappa_f b(1+\beta)$, we have roughly that
+\[
+    \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}e^{-\frac{\alpha}{1+\beta}}\sum_{k=0}^\infty \zeta_k
+\]
+    where $\zeta$ is an $(1+\beta)$-stable random variable with characteristic function
+\[
+    \mathbf E[e^{i\theta \zeta}] = \exp(m[\theta f]),\quad \theta \in \mathbb R.
+\]
+    with $m[\theta f]$ given by Lemma \ref{lem: def of all m} below. 
+    In this intuition, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined,
+\begin{equation}
+\label{eq: equatlity for mf for small rate}
+    m[f] =  \sum_{k=0}^\infty m_k[ f],
+\end{equation}
     and 
-\begin{align}
-    \mathcal{C}_l:=\Big\{f(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
-\end{align}
-    Each $f\in \mathcal{C}_l$ can be expressed as
-\begin{align}\label{discompose}
-    f(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x),
-    \quad x\in \mathbb{R}^d,
-\end{align}
-    where $a_p=\langle f, \phi_p\rangle_{\varphi}$. Let
-\begin{align}\label{definition of Itf}
-    I_tf(x)
-    :=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), 
-    \quad t\geq 0, x\in \mathbb{R}^d.
-\end{align}
-    It is easy to see that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$.
-
-    Define
-\begin{align}\label{bar-m}
-   \bar{m}[f]
-   :=\int_{0}^{\infty} e^{\alpha s}\langle \eta(iI_sf)^{1+\beta},\varphi\rangle ds.
-\end{align}
-    According to Lemma \ref{lem: control of mn} below, $\bar{m}[f]$ is well-defined.
-\begin{thm}\label{thm: large clt}
-    For $f\in\mathcal{C}_l$ given by \eqref{discompose} and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that, as $t\to\infty$,
-\begin{align}\label{thm: large rate}
-    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}a_pe^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow{d}\bar{\zeta},
-\end{align}
-    where $\bar{\zeta}$ is an $(1+\beta)$-stable random variable with characteristic function
-\begin{align}
-    \mathbb{E}[e^{i\theta\bar{\zeta}}]=\exp[\bar{m}[\theta f]],\quad \theta\in \mathbb{R}.
-\end{align}
-\end{thm}
-\end{comment}
-%End moved to above
-
-    %{\bf (RS We should collect our commonly used notation at the end of this section.)}
+\[
+    m[\theta f] = \theta^{1+\beta} m[f], \quad \theta \geq 0.
+\]
+    All of this facts well be made clear in Subsection \ref{sec: stable distributions} below.
+
+    If $f$ lives in the critical branching rate regime, i.e. $\alpha \beta = \kappa_f b(1+\beta)$, then \eqref{eq: equatlity for mf for small rate} doesn't hold anymore. 
+    Instead, see Lemma \ref{lem: def of all m} below, there is another quantity $\widetilde m[f]$ satisfying that
+\[
+    \widetilde{m}[f] = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
+\]
+    In this situation, we roughly have that
+\[
+    \frac{\langle f,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}} \overset{d}{\approx} \frac{1}{t^{\frac{1}{1+\beta}}} \sum_{k=0}^{\lfloor t\rfloor} e^{- \frac{\alpha}{1+\beta}} \zeta_k \xrightarrow[t\to \infty]{d} \widetilde \zeta
+\]
+    where $\widetilde \zeta$ is an $(1+\beta)$-stable random variable with characteristic function
+\[
+    \mathbf E[e^{i\theta \widetilde \zeta}] = \exp(\widetilde m[\theta f]),\quad \theta \in \mathbb R.
+\]
+
+    For the testing function $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
+Taking $f = \phi_p$ with $\alpha \beta > |p|b(1+\beta)$ as an example, we do the following decomposition:
+\[
+    H^p_t-H^p_\infty=\sum^{\infty}_{n=1}(H^p_{t+n-1}-H^p_{t+n}).
+\]
+    The fluctuation behaviors of each terms $H_{t+n-1}^p - H_{t+n}^p$ and their asymptotic independence will be established in Lemma \ref{large-central} and \ref{lem: independency for large rate} below, respectively.
+    These lemmas will eventually lead us to the fluctuation result for the large branching rate regime.
+%END ADDED
+
+ %DELETED
+ %By \eqref{lem: control of mgtrs}, we roughly have
+%\begin{enumerate}
+%\item If  $f$ is non-trivial and $\alpha\beta<\kappa_f b(1+\beta)$, the normalization is $F_t=\|X_t\|^{\frac{1}{1+\beta}}$, and only those $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$ with small $k$, normalized by $\|X_t\|^{\frac{1}{1+\beta}}$,  contribute  to the limit of $\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}$.
+Lemma \ref{lem: mainlemma} below gives the contribution of each term.
+Also, we will prove that the contributions from different time intervals are independent, and thus $\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}$ has $(1+\beta)$-stable limit as $t\to\infty$.
+
+%\item If  $\alpha\beta=\kappa_f b(1+\beta)$, then Lemma \ref{lem: mainlemma} below says that for each $k<t$,  $\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}$ has a $(1+\beta)$-stable limit.
+But the summation of these terms will diverge.
+In this case, the correct normalization is $F_t=(t\|X_t\|)^{\frac{1}{1+\beta}}$.
+%\item 
+    %If  $\alpha\beta>\kappa_f b(1+\beta)$,  by Theorem \ref{thm: law of large number}, $e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle$ has an almost sure limit.  
+%In this case, we further consider a central limit type result for $\langle f, X_t\rangle$ when
+%$f\in \mathcal{C}_l$. 
+%Since each $f\in \mathcal{C}_l$ can be expressed as
+%\begin{align}
+    %f(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x),\quad x\in \mathbb{R}^d,
+%\end{align}
+%where $a_p=\langle f, \phi_p\rangle_{\varphi}$, and $\mathcal{N}$ is a finite set, we only need to consider the special case of $f=\phi$.
+Therefore, we only need to consider the martingale central limit result for $H^p_t, t\geq 0.$
+%The correct normalization for each $H_{t+n-1}^p-H^p_{t+n}$ is $e^{-(\alpha-b|p|)t}e^{\frac{\alpha t}{1+\beta}}$.
+%Since $\alpha\beta> |p|b(1+\beta)$, only those $H_{t+n-1}^p-H^p_{t+n}$  with small $n$, normalized by $e^{-(\alpha-b|p|)t}\|X_t\|^{\frac{1}{1+\beta}}$,  contribute  to the normalized limit of $H^p_t-H^p_\infty$.
+In Lemma \ref{large-central}, we will prove that for each $n$, $\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p| b)t}\|X_t\|^{\frac{1}{1+\beta}}}$ has a $(1+\beta)$-stable limit as $t\to\infty$.
+The limits are independent for different intervals.
+%END DELETED
+
+    For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$, where $$f_l=\sum_{p\in \mathcal{N}}a_p\phi_p(x)\in \mathcal{C}_l,\quad x\in \mathbb{R}^d,$$
+ and $f_c=\langle f, \phi_p\rangle_{\varphi} \phi_p(x)$  with $p=\frac{\alpha\beta}{b(1+\beta)}$. Note that there may be no $p$ such that $p=\frac{\alpha\beta}{b(1+\beta)}$. In this case $f_c=0$. 
+Our main results above give central limit type results for $\langle f_l, X_t\rangle$, $\langle f_c, X_t\rangle$ and $\langle f_s, X_t\rangle$, respectively.
+ We conjecture that the limits of these three terms, normalized properly, are independent, because intuitively these limits come from small time intervals, intermediate time intervals and large time intervals, respectively.
+ If this is valid, we can get a central limit type result for $\langle f, X_t\rangle$ for general $f\in\mathcal{P}$. 
+ This independence was proved under the second moment condition, see \cite{RenSongZhang2015Central}. 
+ We leave the question of independence for stable branching mechanism to a future project.
+%\end{enumerate}
+
+%This paper is our first attempt to study central limit type theorems for general superprocesses with general branching mechanism. 
+    This paper is our first attempt on the stable CLT for superprocesses. 
+    There are still many open questions. 
+    For example, the spatial motion in this paper is an Ornstein-Uhlenbeck process. 
+    %We would be interested in more general motions. 
+    If the branching mechanism has finite second moment, we established some central limit theorems in \cite{RenSongZhang2015Central} for a class of superprocesses with general motions. 
+    We hope to prove stable CLT for superprocesses with general motions in a future project.
+
+    %Recall that we assume that the the branching mechanism satisfies Assumption \ref{asp: branching mechanism}. 
+    Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z + \rho z^2+\eta z^{1+\beta}$ plus a small perturbation 
+    %For each $z\in \mathbb R_+$, define
+\begin{align}
+\label{eq: psi 1}
+	\psi_1(z)
+	&:= \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big)
+\end{align}
+    where $\psi_1$ satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
+%DELETED
+%Then the branching mechanism can be rewritten as
+%\begin{equation}\label{decom-branchingMechanism}
+    %\psi(z) = -\alpha z + \rho z^2+\eta z^{1+\beta} + \psi_1(z),\quad  z \in \mathbb R_+,
+%\end{equation}
+%where $\alpha, \eta>0$, $\rho\geq 0$, $\beta\in(0,1)$. 
+%Assumption \ref{asp: branching mechanism} is equivalent to that the branching mechanism is given in the form of \eqref{decom-branchingMechanism} with $\psi_1=\psi^+_1-\psi^-_1$, where $\psi^+_1=\int_{(0,\infty)}(e^{-yz}-1+yz)\nu^+(dy)$, and $\psi^-_1=\int_{(0,\infty)}(e^{-yz}-1+yz)\nu^-(dy)$ with $\nu^+$ and $\nu^+$ being measures on $(0,\infty)$ such that
+%$$\int_{(0,\infty)}(y^{1+\beta +\delta}\wedge y^2)(\nu^++\nu^-)(dy)<\infty$$ for sufficient small $\delta>0$. 
+%Basically, our  Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z + \rho z^2+\eta z^{1+\beta}$ plus a a small perturbation $\psi_1$.
+    It would be interesting to consider more general branching mechanism.
+
+%DELETED
+%Our results show that he behavior of $\psi(z)+\alpha z$ near $z= 0$ plays the dominating role. 
+%The limit and the normalization only depend on $\eta z^{1+\beta}$. It is interesting to consider more general branching mechanism.
+%END DELETED
+
+%We wend this section with some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
+    Some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism} are the following:
+    %If $\varphi$ is a complete Bernstein function which is regularly varying at 0 with index
+    If $h$ is a complete Bernstein function which is regularly varying at 0 with index
+$\beta_1\in (\beta, 1)$, then 
+$$
+%\psi(z):=-\alpha z + \rho z^2+\eta z^{1+\beta}+z\varphi(z), \qquad z>0
+    \psi(z):=-\alpha z + \rho z^2+\eta z^{1+\beta}+zh(z), \qquad z>0
+$$
+satisfies Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
+If $\beta_1\in (\beta, 1)$, $c_1\in (0, \eta/\Gamma(-1-\beta))$ and $c_2\ge 1$, then
+$$
+\psi(z):=-\alpha z + \rho z^2+\eta z^{1+\beta}-\int^\infty_{c_2}
+(e^{-yz}-1+yz)\frac{c_1dy}{y^{1+\beta_1}}, \qquad z\in \mathbb R_+
+$$
+satisfies Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
+
+%NEW ADDED
+    The rest of the paper is organized as follows: In Subsection \ref{sec: branching mechanism} we will give some preliminary results for our branching mechanism $\psi$.
+    In Subsection \ref{sec: controller} and \ref{sec: h-controller} we will give several estimations for the operators related to the super-OU process $X$ that will be used in our proofs.
+    In Subsection \ref{sec: stable distributions} we will give the definition of all the $(1+\beta)$-stable random variables involved in this paper. 
+    In Subsection \ref{sec: Small value probability} we will give estimations for the small value probability of continuous state branching processes.
+In Subsection \ref{sec: Moments for super-OU processes} we will give upper bounds for the $(1+\gamma)$-moments for our superprocesses.
+    These estimations and upper bounds will be crucial in the later proofs.
+    In Subsection \ref{sec: large rate lln}, we will give the proof of Theorem \ref{thm: law of large number}.
+    In Subsection \ref{sec:critical}, we will give the proof of Theorem \ref{thm: critical clt}.
+    In Subsection \ref{sec: small rate}, we will give the proof of Theorem \ref{thm: small clt}.
+    In Subsection \ref{sec: large rate clt}, we will give the proof of Theorem \ref{thm: large clt}.
+    In the Appendix, we consider a general superprocess $(X_t)_{t\geq 0}$, and we prove there that the characteristic exponent of $\langle f,X_t\rangle$ will satisfy a complex-valued non-linear integral equation.
+    This fact will be used at several places in this paper, and we think it should be of independent interests.
+
+    We end this section with a list of frequently used notations:
+\begin{itemize}
+\item
+    $\varphi$ and $\phi_p$ are given by \eqref{invariantdensity} and \eqref{eigenfunction}, respectively.
+\item
+    $P_t$, $P^\alpha_t$, $V_t$ and $U_t$ are given by \eqref{eq: meansemigroup}, \eqref{eq: meansemigroup}, \eqref{eq: def of V_t}, \eqref{eq: def of U_t}, respectively.
+\item
+    $\mathcal N$, $K$, $\mathcal C_l$ and $I_t$ are given by \eqref{eq: def of N}, \eqref{eq: def of N},  \eqref{eq: def of Cl} and \eqref{definition of Itf}, respectively.
+\item
+    $\psi$, $\psi_1$ and $\psi_0$ are given by \eqref{eq: honogeneou branching mechanism}, \eqref{eq: psi 1} and \eqref{eq: psi 0}, respectively.
+\item
+    $\Psi$, $\Psi_1$ and $\Psi_0$ are given by \eqref{eq: def of operator Psi}.
+\item
+    $Z_t$, $Z'_t$, $Z''_t$ and $Z'''_t$ are given by \eqref{eq: def of Zf}.
+\item
+    $Q_\kappa$ and $Q$ are given by \eqref{Q_k} and \eqref{Q}, respectively.
+\item
+    $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\tilde m[f]$ and $\bar m[f]$ are given by Lemma \ref{lem: def of all m}.
+\end{itemize}
+%END NEW ADDED
 
 \section{Preliminaries}
-%Moved and modified from the first section
 \subsection{Branching mechanism}
@@
 	Let $\psi$ be the branching mechanism given by \eqref{eq: honogeneou branching mechanism}.
-	Suppose that Assumption \ref{asp: branching mechanism} holds. 
-	In this Subsection, we give some preliminary results about the branching mechanism $\psi$.
-	Recall that $\eta$ and $\beta$ are the constants appread in Assumption \ref{asp: branching mechanism}.
-	For each $z\in \mathbb R_+$, define
-\begin{align}
-	\psi_1(z) 
-	&:= \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big)
-	\\&= \int_{(0,\infty)}(e^{-yz}-1+yz) \pi(dy) -  \eta z^{1+\beta}.
-\end{align}
+	Suppose that Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism} hold.
+	In this subsection, we give some preliminary results about the branching mechanism $\psi$.
+	Recall that $\eta$ and $\beta$ are the constants in Assumption \ref{asp: branching mechanism}.
 	Let $\mathbb C_+:= \{x+iy: x\in \mathbb R_+, y \in \mathbb R\}$ and $\mathbb C^0_+:= \{x+iy: x\in (0,\infty), y \in \mathbb R\}$.
@@
 \label{lem: complex extension for psi1}
-	Function $\psi_1$ on $\mathbb R_+$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomophic on $\mathbb C^0_+$. 
-	%Moreover, there exist constants $c,\delta >0$ such that for each $z\in \mathbb C_+$, we have
-	Moreover, for each $\delta > 0$ small enough, there exist constant $c>0$ such that for each $z\in \mathbb C_+$, we have
+	The function $\psi_1$ on $\mathbb R_+$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
+		Moreover, for each $\delta > 0$ small enough, there exists a  constant $C>0$ such that for each $z\in \mathbb C_+$, we have
 $
-	|\psi_1(z)| \leq c |z|^{1+\beta+\delta} + c|z|^2.
+	|\psi_1(z)| \leq C |z|^{1+\beta+\delta} + C|z|^2.
 $
@@
 \begin{proof}
-	For each $\sigma$-finite signed measure $\mu$, denote by $|\mu|$ the total variation measure of $\mu$.	
-	According to Lemma \ref{lem: extension lemma for branching mechanism} and the identity theorem for holomorphic functions, we have that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomophic on $\mathbb C^0_+$.
+According to Lemma \ref{lem: extension lemma for branching mechanism} below and 
+the uniqueness of holomorphic extensions, 
+	we have that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
 	The extended $\psi_1$ has the following form:
@@
 	\\&\quad + |z|^{1+\beta +\delta}\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|,
+%ADDED
+    \quad z \in \mathbb C_+,
+%END ADDED
 \end{align}
@@
 
-	We then give a Lemma which says that the constants $\eta, \beta$ appread in Asumption \ref{asp: branching mechanism} is uniquelly determined by the L\'evy measure $\pi$.
+The following lemma says that the constants $\eta, \beta$ in Assumption \ref{asp: branching mechanism} are uniquely determined by the L\'evy measure $\pi$.
 \begin{lem}
 \label{lem: unique of beta and eta}
+Suppose that Assumption  \ref{asp: branching mechanism} holds.
 	Suppose that there are constants $\eta'>0, \beta'\in (0,1)$ and $\delta' > 0$ such that
@@
 \begin{proof}
-	Let $\delta> 0$ be the constant appread in Assumption \ref{asp: branching mechanism}.
 	Without loss of generality, we assume that $\beta+\delta \leq \beta'+ \delta'$.
-	According to the fact that $y^{1+\beta+ \delta} \leq y^{1+\beta'+\delta'}$ with $y \geq 1$, we have
+	Using  the fact that $y^{1+\beta+ \delta} \leq y^{1+\beta'+\delta'}$ with $y \geq 1$, we get
 \[
@@
 \]
-	Compare this to Assumption \ref{asp: branching mechanism}, we have
+	Comparing this with Assumption \ref{asp: branching mechanism}, we get
 \[
@@
 \]
-	In another word, if we denote by $\tilde \pi(dy)$ the measure $\eta' \Gamma(-1-\beta)^{-1} y^{-2-\beta'} dy$, then $\tilde \pi$ is a L\'evy measure which satisfies the Assumption \ref{asp: branching mechanism}.
+	In other words, if we denote by $\tilde \pi(dy)$ the measure $\eta' \Gamma(-1-\beta)^{-1} y^{-2-\beta'} dy$, then $\tilde \pi$ is a L\'evy measure which satisfies Assumption \ref{asp: branching mechanism}.
 	Applying Lemma \ref{lem: complex extension for psi1} to this measure $\tilde \pi$, we have that there exists $c>0$ such that
@@
 \]
-	Dividing each side by $z^{1+\beta}$ we have
-\[
-	|\eta - \eta' z^{1+\beta' - \beta} | 
+Dividing both sides by $z^{1+\beta}$ we have
+\[
+	|\eta - \eta' z^{\beta' - \beta} |
 	\leq cz^{\delta}+cz^{1-\beta},
@@
 \[
-	\eta' z^{1+\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0.
+	\eta' z^{\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0.
 \]
@@
 \label{lem: LlogL criterion}
-    $\psi$ satisfies the $L \log L$ criterion, i.e.
+If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies the $L \log L$ criterion, i.e.,
 \[
@@
 \begin{proof}
-	According to Assumption \ref{asp: branching mechanism} and the fact that $y\log y \leq y^{1+\beta+\delta}$ for $y$ large enough, we have
+	Using  Assumption \ref{asp: branching mechanism} and the fact that $y\log y \leq y^{1+\beta+\delta}$ for $y$ large enough, we get
 \[
@@
 \]
-	Noticing that
+Combining this with
 \[
@@
 \]
-	so we have the desired result.
+we immediately get the desired result.
 \end{proof}
-%End moved and modified from the first section
 \subsection{Definition of controller}
-%New added
+\label{sec: controller}
 	Denote by $\mathcal B(\mathbb R^d, \mathbb C)$ the space of all $\mathbb C$-valued Borel measurable functions on $\mathbb R^d$.
 	Recall that $\mathcal P$ is given by \eqref{eq: polynomial growth function}.
-%End new added
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
@@
 \end{itemize}
-    %For any function $h: [0,\infty) \to [0,\infty)$ and $\mathcal D \subset \mathcal P^*$, we say that $A : \mathcal D \to \mathcal P^*$ is an \emph{$h$-controllable} operator on $\mathcal D$ if there exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
-    %We also say the operator $A$ is \emph{$h$-controlled by $R$ on $\mathcal D$} in this case.
        For a subset $\mathcal D$ of $\mathcal P^*$ and an $h$-controller $R$, we say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controlled by $R$ on $\mathcal D$} if $|Af| \leq R|f|$ for each $f\in \mathcal D$.
-    We say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controllable} if there exists an $h$-controller $R$ such that $A$ is $h$-controlled by it.
+    We say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controllable} if there exists an $h$-controller $R$ such that $A$ is $h$-controlled by $R$.
      We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
 
-    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
+    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, we define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
     For any $a \in \mathbb R$ and any operator $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
 \begin{lem}\label{lem: property of controllable operators}
-    %Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$. 
-    Suppose that $\Lambda$ is an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$. 
+Suppose that $\Lambda$ is an index set and $(A_\lambda)_{\lambda\in \Lambda}$ is a 
+family of operators from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$.
     Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
@@
     Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D$ for some function $g: [0,\infty) \to [0,\infty)$.
-    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$, and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$.
+    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$ and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$.
 \item[(4)]
@@
 \item
-    %If $f,g \in \mathcal D_0$ with $|f|\leq |g|$, then $R_AR_B|f| \leq R_A R_B |g|$.
         If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_AR_Bf \leq R_A R_B g$.
 \item
-    %If $f \in \mathcal D_0$ and $\theta \in [0,\infty)$, then $R_AR_B|\theta f| \leq R_A(g(\theta) R_B|f|) \leq (h\circ g)(\theta) R_A R_B |f| $.
        If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_AR_B(\theta f) \leq R_A(g(\theta) R_Bf) \leq (h\circ g)(\theta) R_A R_B f $.
@@
     Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
-
     Then we have
@@
 \item
-    %If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R_A\times R_B|f| \leq R_A\times R_B |g|$.
        If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_A\times R_Bf \leq R_A\times R_B g$.
 \item
-    %If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R_A\times R_B|\theta f| \leq h(\theta) g(\theta) (R_A \times R_B) |f| $.
         If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_A\times R_B (\theta f) \leq h(\theta) g(\theta) (R_A \times R_B) f $.
@@
 \item
-    %If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $(R_A + R_B)|f| \leq (R_A + R_B) |g|$.
         If $f,g \in \mathcal P^+$ with $f\leq g$, then $(R_A + R_B)f \leq (R_A + R_B) g$.
 \item
-    %If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $(R_A + R_B) |\theta f| \leq h(\theta) R_A|f| + g(\theta) R_B|f| \leq (h(\theta) \vee g(\theta)) (R_A+R_B)|f| $.
         If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $(R_A + R_B) (\theta f) \leq h(\theta) R_Af + g(\theta) R_Bf \leq (h(\theta) \vee g(\theta)) (R_A+R_B)f $.
@@
 \item
-    %If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R^{\times a}|f| \leq R^{\times a} |g|$.
         If $f,g \in \mathcal P^+$ with $f\leq g$, then $R^{\times a}f \leq R^{\times a} g$.
 \item
-    %If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R^{\times a}|\theta f| \leq (h(\theta) R |f|)^a = h(\theta)^a R^{\times a}|f|$.
         If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R^{\times a}(\theta f) \leq (h(\theta) R f)^a = h(\theta)^a R^{\times a}f$.
@@
 \subsection{h-controller  for super-OU processes}
-    %Let $X$ be the super-OU process introduced in Subsection 1.1. 
-    Let $X$ be the super-OU process introduced in Subsection \ref{sec: main results} with its branching mechanism $\psi$ satisfying \ref{asp: branching mechanism} and \ref{asp: Greys condition}. 
-%Added
-	In this subsection, we will give several operators and their properties that will be used in this paper.
-%End added
-
-    %We define $\psi_0(z)=\psi(z)+\alpha z$ for each $z\in \mathbb{C}_+$, and define the following operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$: 
-    Define $\psi_0(z)=\psi(z)+\alpha z$ for each $z\in \mathbb{R}_+$. 
-%Added
-    According to a similar arguement to Lemma \ref{lem: complex extension for psi1}, similar to function $\psi_1$, both functions $\psi$, $\psi_0$ can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomophic on $\mathbb C^0_+$.
-%End added
-    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define 
-\begin{equation}\begin{split}
+\label{sec: h-controller}
+   Let $X$ be the super-OU process introduced in Subsection \ref{sec: Motivation}
+    with branching mechanism $\psi$ satisfying 
+    Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
+	In this subsection, we will define several operators and study their properties that will be used in this paper.
+
+     Define 
+\begin{equation}
+\label{eq: psi 0}
+    \psi_0(z)=\psi(z)+\alpha z,\quad z\in \mathbb{R}_+
+\end{equation}
+  Using an argument similar to the proof  of Lemma \ref{lem: complex extension for psi1},
+    both functions $\psi$, $\psi_0$ can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C^0_+$.
+    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, we define
+\begin{align}
+\label{eq: def of operator Psi}
     \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
-    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x)
-    %\\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big),
-    %\quad  f\in \mathcal B(\mathbb R^d, \mathbb C_+), x\in \mathbb R^d.
+    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x),
     \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big).
-\end{split}\end{equation}
-    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let \[U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}\] be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
-    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
-\begin{equation}\begin{split}
+\end{align}
+    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let 
+\begin{equation}\label{eq: def of U_t}
+    U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}
+\end{equation} 
+    be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
+    It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
+\begin{align}
 \label{eq:chareq2}
@@
     \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
-\end{split}\end{equation}
-    %If we let
-    For each $t\geq 0$ and $f\in \mathcal P$, define
-\begin{equation}\begin{split}
+\end{align}
+       For each $t\geq 0$ and $f\in \mathcal P$, we define
+\begin{align}
 \label{eq: def of Zf}
@@
     &:= \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
-    \\ K_t f
+    %\\ K_t f
+    \\ Z'''_t f
     &:= (Z'_t - Z_t+ Z''_t)f.
-\end{split}\end{equation}
-    %then we have that
+\end{align}
     Then we have that
-\[
+\begin{equation}
+\label{eq: key equality}
     U_t - i P^\alpha_t
     = Z'_t + Z''_t
-%Deleted
-    %= Z_t+ (Z'_t - Z_t) + Z''_t
-%End deleted
-    = Z_t+K_t, \quad t\geq 0.
-\]
-%Moved and modified from below
-	For all $k \in \mathbb Z_+$ and $f\in \mathcal P$, define
+    %= Z_t+K_t, \quad t\geq 0.
+    = Z_t+Z'''_t, \quad t\geq 0.
+\end{equation}
+	For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
 \begin{equation}\label{Q_k}
-    Q_k f 
-    := \sup_{t\geq 0} e^{k b t}|P_t f|
+    Q_\kappa f
+    := \sup_{t\geq 0} e^{\kappa b t}|P_t f|
 \end{equation}
@@
     Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
-%End moved and modified from below
 
@@
 \label{lem: upper bound for usgx}
-    %Under Assumption \ref{asp: branching mechanism}, the following statements are true:
-    Under Assumption \ref{asp: branching mechanism} and \ref{asp: Greys condition}, the following statements are true:
+        Under Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}, the following statements are true:
 \begin{itemize}
@@
 \item[(3)]
-    %$\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
        $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
@@
 \item[(5)]
-    %$(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
         $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable on $\mathcal P$.
 \item[(6)]
-    %There is a constant $\delta > 0$ such that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-    For each $\delta > 0$ small enough, we have $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
+        For any $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
 \item[(7)]
-    %There is a constant $\delta > 0$ such that $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-    For each $\delta > 0$ small enough, we have $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
+       %For any $\delta > 0$ small enough, we have that $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
+       For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
 \end{itemize}
@@
 \]
-%Added
-    Note that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a map from $\mathcal P^+$ to $\mathcal P^+$, since if $f\in \mathcal P^+$, there exists constant $c>0$ such that
+  We claim that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a map from $\mathcal P^+$ to $\mathcal P^+$. In fact, if $f\in \mathcal P^+$, there exists constant $c>0$ such that
 \[
@@
 \]
-%End added
-	%Note that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.
-	It is also clear that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.
+	It is clear that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.
 
@@
     (3).
-    %Let $C>0$ and $\delta > 0$ be the constants in Assumption \ref{asp: branching mechanism}.
-    %For each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
-    According to Lemma \ref{lem: complex extension for psi1}, there exist constants $C, \delta >0$ with $1+\beta+\delta< 2$, such that for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
-\begin{equation}\begin{split}
+        According to Lemma \ref{lem: complex extension for psi1},
+         there exist constants $C, \delta >0$ such that  $1+\beta+\delta< 2$, and for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
+\begin{align}
     &|\Psi_0 f|
@@
     \leq \eta |f|^{1+\beta} + C|f|^2+ C |f|^{1+\beta + \delta}.
-\end{split}\end{equation}
+\end{align}
     Note that
 \[
-    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta},\quad f\in \mathcal P^+
+    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta},\quad f\in \mathcal P^+,
 \]
@@
 \[
-    f
-    %\mapsto P^\alpha_{t-s}\Psi_0(-U_sf)(x),
-    \mapsto P^\alpha_{t-s}\Psi_0(-U_sf),
-    \quad 0\leq s\leq t\leq 1
+    f\mapsto P^\alpha_{t-s}\Psi_0(-U_sf),
+    \quad 0\leq s\leq t\leq 1,
 \]
@@
 \]
-    are unifromly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable.
-    As a consequence of this, Lemma \ref{lem: property of controllable operators}.(1)-(2), and
-\begin{equation}\begin{split}
+    are uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable.
+    Combining this with Lemma \ref{lem: property of controllable operators}.(1)-(2), and
+\begin{equation}
     (Z'_t - Z_t)f = \int_0^t P^\alpha_{t-s}\Big( \eta \big((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} \big)\Big)ds,
     \quad 0\leq t\leq 1, f\in \mathcal P,
-\end{split}\end{equation}
+\end{equation}
     we get the desired result.
 
-    (6). %Suppose that $C>0, \delta>0$ are the constants in Assumption \ref{asp: branching mechanism}.
-    %Noticing that
-    According to Lemma \ref{lem: complex extension for psi1}, for each $\delta > 0$ small enough, there exists a constant $C>0$ such that
+    (6).  According to Lemma \ref{lem: complex extension for psi1}, for any $\delta > 0$ small enough, there exists a constant $C>0$ such that
 \[
@@
 \]
-    %and that
-    Note that, for each $\delta, C>0$,
+        Note that, for all $\delta, C>0$,
 \[
@@
 \]
-    %is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllor, we have that $\Psi_1$ is $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-    is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllor. 
-    Therefore, for each $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-    %According to this, parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we have that
-    According to this, parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we have that, for each $\delta > 0$ small enough, operators
+        is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controller.
+    Therefore, for any $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
+        Combining  this with parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we get that, for any $\delta > 0$ small enough, the operators
 \[
@@
 
-    (7). Since $K_t = (Z'_t-Z_t)+Z''_t$, we get the desired result from parts (5) and  (6) of this lemma,  and Lemma \ref{lem: property of controllable operators}.(3).
+    %(7). Since $K_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from parts (5)-- (6) of this lemma  and Lemma \ref{lem: property of controllable operators}.(3).
+    (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from parts (5)-- (6) of this lemma  and Lemma \ref{lem: property of controllable operators}.(3).
 \end{proof}
 
-%\subsection{Parameters of the stable limits}
 \subsection{Stable distributions}
-%Deleted    
-    %Define
-%\begin{equation}\label{parameter_mk}\begin{split}
-    %m_t[f]
-    %:=e^{-\alpha (t+1)} \int_{\mathbb R^d}(Z_1P^\alpha_t f)(x)\cdot \varphi(x)~dx,
-    %\quad t\geq 0, f\in \mathcal P.
-%\end{split}\end{equation}
-
-    %We first collect some lemmas from \cite{MarksMilos2018CLT}, which will be used in this paper.
-%\begin{lem}{\cite[Lemma 2.7]{MarksMilos2018CLT}}\label{lem: def of all m} 
-    %For each $f\in\mathcal{P}$, there is a constant $C>0$ such that
-%\begin{equation}\label{domi-m}
-    %|m_t[f]|
-    %\leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
-    %\quad t\geq 0.
-%\end{equation}
-%\end{lem}
-%End Deleted
-%Added
-    In this subsection, we will show that the $(1+\beta)$-stable random variables appreared in Theorem \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
-
-    In the following Lemma, recall that $(P^\alpha_t)_{t\geq 0}$ is given by \eqref{eq: meansemigroup}, $\mathcal P$ is given by \eqref{eq: polynomial growth function}, $\mathcal N$ is given by \eqref{eq: def of N} and $\mathcal C_l$ is given by \eqref{eq: def of Cl}.
+\label{sec: stable distributions}
+
+    In this subsection, we will show that the $(1+\beta)$-stable random variables in Theorem \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
+
+   Recall that
+    $(P^\alpha_t)_{t\geq 0}$ is given by \eqref{eq: meansemigroup}, $\mathcal P$ is given by \eqref{eq: polynomial growth function}, $\mathcal N$ is given by \eqref{eq: def of N} and $\mathcal C_l$ is given by \eqref{eq: def of Cl}.
 \begin{lem}
@@
 	m_t[f]
-    %:=e^{-\alpha (t+1)} \int_{\mathbb R^d}(Z_1P^\alpha_t f)(x)\cdot \varphi(x)~dx,
         := \eta \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} (-iP_{s}^\alpha f(x))^{1+\beta} \varphi(x)~dx,
@@
     \bar{m}_t[f]
-    := \eta \int_{t}^{t+1} e^{\alpha s}~ds \int_{\mathbb R^d}\big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx.
+    %:= \eta \int_{t}^{t+1} e^{\alpha s}~ds \int_{\mathbb R^d}\big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx, \quad t\geq 0.
+    := \eta \int_{t-1}^{t} e^{\alpha s}~ds \int_{\mathbb R^d}\big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx, \quad t\geq 1.
 \]
@@
 \begin{equation}
-    |\bar{m}_t[f]| \leq C e^{-(\alpha\beta-K(1+\beta)b)t}, \quad t\geq 0.
-\end{equation}
+    |\bar{m}_t[f]| \leq C e^{-(\alpha\beta-K(1+\beta)b)t}, \quad t\geq 0,
+\end{equation}
+	where $K:=\sup\{k\in \mathbb N : \alpha\beta>k(1+\beta)b\}$.
 \item
@@
     Furthermore, we have
-\[
+\begin{equation}\label{sum-bar-m}
     \bar{m}[f]
-    =\sum_{n=0}^{\infty}\bar{m}_n[f].
-\]
-\item
-	Suppose that $f \in \mathcal{P}$ satisfies that $\alpha\beta=\kappa_f b(1+\beta)$. Then the following integral is well defined:
+    %=\sum_{n=0}^{\infty}\bar{m}_n[f].
+    =\sum_{n=1}^{\infty}\bar{m}_n[f].
+\end{equation}
+\item
+	Suppose that $f \in \mathcal{P}$ satisfies  $\alpha\beta=\kappa_f b(1+\beta)$. Then the following integral is well defined:
 \[
@@
 	Furthermore, we have
-\[
+\begin{equation}
+\label{para: critical case}
 	\widetilde{m}[f] = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
-\]
+\end{equation}
 \item
@@
 	Furthermore, we have
-\[    
+\begin{equation}\label{sum-m}
 	m[f]
     =\sum_{k=0}^\infty m_k[f].
-\]
+\end{equation}
 \end{enumerate}
@@
 
-    (2). We first cliam that there exists $h\in \mathcal{P}$ such that for each $t\geq 0$,
-\[
+    (2). We first claim that there exists $h\in \mathcal{P}$ such that,
+\[
+    \label{ineq: control of Itg}
     |I_tf(x)|
@@
 \]
-    In fact, put $h:= \sum_{p\in \mathcal N} |\langle f,\phi_p\rangle_{\varphi}\phi_p|$, then
-\[
+    In fact, if we put $h:= \sum_{p\in \mathcal N} |\langle f,\phi_p\rangle_{\varphi}\phi_p|$, then
+\begin{equation}
+\label{eq: supper for Itf}
     |I_tf(x)|
@@
     \quad t\geq 0,x\in \mathbb{R}^d.
-\]
+\end{equation}
     Therefore, there exists constant $C>0$ such that
@@
     \leq \eta \int_{t}^{t+1} e^{\alpha s}~ds \int_{\mathbb R^d} | I_sf(x)|^{1+\beta}\varphi(x)~dx
-    \\&\leq \int_{t}^{t+1} e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}~ds\int_{\mathbb R^d} h(x)^{1+\beta}\varphi(x)~dx
+    \\&\leq \eta \int_{t}^{t+1} e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}~ds\int_{\mathbb R^d} h(x)^{1+\beta}\varphi(x)~dx
     \\&\leq C e^{-(\alpha\beta-K(1+\beta)b)t},
@@
 \end{proof}
-%End added
-%Deleted
-    %Recall the definition of $\widetilde{m}$ in \eqref{tilde-m}.
-%\begin{lem}(\cite[Lemma 4.2]{MarksMilos2018CLT})
-    %If $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, then
-%\begin{equation}\begin{split} \label{para: critical case}
-    %\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]
-    %=\widetilde{m}[f].
-%\end{split}\end{equation}
-%\end{lem}
-%End Deleted
-%Moved and modified from below
-    The following proposition says that $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\bar m[f]$ and $\tilde m[f]$ are all related to some $(1+\beta)$-stable distribution. 
+    The following proposition says that $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\bar m[f]$ and $\tilde m[f]$ are all related to $(1+\beta)$-stable distributions.
 \begin{prop}
 \label{prop: alpha stable rv}
-    For all $t\geq 0$ and $f\in \mathcal P$,
+%   For all $t\geq 0$ and $f\in \mathcal P$,
+	For all $t\geq 0$ and non-trivial $f\in \mathcal P$,
 \begin{enumerate}
@@
 \label{item: stable 3}
-    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$.
+   $\theta \mapsto \exp(\bar m[\theta f])$
+    is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$.
 \item
@@
 \end{prop}
-%End moved and modified from below
-%Moved below
-%\begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MarksMilos2018CLT})
-    %For each $f\in \mathcal{P}$, let
-%\begin{align}
-    %g_k
-    %:= \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
-    %\quad k \geq 0.
-%\end{align}
-    %Then there exists $h\in \mathcal{P}$ such that
-%\begin{align}
-    %|P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
-%\end{align}
-%\end{lem}
-%
-%\begin{lem}\label{control of gn} Suppose that $g\in \mathcal{C}_l$.
-    %Put
-%\begin{align}
-    %\bar{g}_t
-    %:=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
-%\end{align}
-    %Then there exists $h\in \mathcal{P}$ such that
-%\begin{align}
-    %|P_s\bar{g}_t|
-    %\leq e^{-bs}h,\quad s\geq 0, t\geq 0.
-%\end{align}
-%\end{lem}
-%\begin{proof}
-    %The proof  is similar to that of \cite[Lemma 2.8]{MarksMilos2018CLT}.
-%\end{proof}
-%End moved below
-    %The next lemma is a criterion of $(1+\beta)$-stable distribution.
-    This proposition says that the $(1+\beta)$-stable random variables appreared in Theorem \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined. 
+    This proposition says that the $(1+\beta)$-stable random variables  in Theorem \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
     The proof of this proposition relies on the following lemma:
@@
 \label{lem: charactreisticfunction}
-    Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
+    Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with
+    $\int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty)$.
     Then
@@
 \begin{proof}
-    It follows from measure theory that there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
+    It follows from disintegration that there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
 \[
@@
 \[
-    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi)
-\]
-    %where $\Gamma$ is the $\Gamma$ function, see eqref{eq: definition of Gamma function}.
+    \lambda_0(d\xi) := \frac1{\Gamma(-1-\beta)}\int_0^\infty t^{1+\beta}k(\xi,dt) \lambda (d\xi),
+\]
         where $\Gamma$ is the Gamma function.
@@
 \]
-    %Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\`evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is 
         Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\'evy measure of an $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is
@@
     =\exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\},
-%added
     \quad \theta \in \mathbb R.
-%End added
-\]
-	%Finally,
-    Fimally, according to \eqref{eq: stable branching on C+}, we have
-\begin{equation}\begin{split}
+\]
+	    Finally, according to \eqref{eq: stable branching on C+}, we have
+\begin{align}
     &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
@@
     \qedhere
-\end{split}\end{equation}
+\end{align}
 \end{proof}
-%Deleted
-    %For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$, according to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and thus
-%\begin{equation}\label{sum-m}
-    %m[f]
-    %:=\sum_{k=0}^\infty m_k[f]
-    %=\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
-%\end{equation}
-%End Deleted
-%Moved and modified above
-%\begin{prop}
-%\label{prop: alpha stable rv}
-	%For all $t\geq 0$ and $f\in \mathcal P$,
-%\begin{enumerate}
-%\item
-%\label{item: stable 1}
-    %$\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
-%\item
-%\label{item: stable 4}
-    %$\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
-%\item
-%\label{item: stable 5}
-    %$\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
-%\end{enumerate}
-%\end{prop}
-%End moved and modified above
 \begin{proof}[Proof of Proposition \ref{prop: alpha stable rv}]
@@
     m_t[\theta f]
-    %= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x) \int_0^1 P_{1-s}^\alpha \left(\eta(-i\theta P_{s+t}^\alpha f)^{1+\beta}\right)(x)~ds,
        = \eta \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} \big(-i\theta (P_{s}^\alpha f)(x)\big)^{1+\beta} \varphi(x)~dx,
@@
 \label{eq: what I want to proof}
-	%\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds
 	 \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} | P_{s}^\alpha f(x)|^{1+\beta} \varphi(x)~dx
-    < \infty.
+	\in (0, \infty).
 \end{equation}
 	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),
-    %we know that $ g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds$ is a $(1+\beta)$-controllable operator on $\mathcal P$.
-    we know that \[ g \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f|^{1+\beta}~ds\] is a $(1+\beta)$-controllable operator on $\mathcal P$.
-	%This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
+      we know that 
+      \[ 
+      f \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f|^{1+\beta}~ds
+      \] 
+      is a $(1+\beta)$-controllable operator on $\mathcal P$.
 	    This implies that \[ x \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f(x)|^{1+\beta}~ds\] is an element of $\mathcal P$.
-	Therefore \eqref{eq: what I want to proof} is true.
-
-    %The proofs of \eqref{item: stable 4} and \eqref{item: stable 5} are similar to that of \eqref{item: stable 1}.
-    The proofs of \eqref{item: stable 2}, \eqref{item: stable 3}, \eqref{item: stable 4} and \eqref{item: stable 5} are similar to that of \eqref{item: stable 1}.
+	Therefore the integral on the left-hand side of \eqref{eq: what I want to proof} is finite.
+	Since $f$ is non-trivial, 
+%DELETED
+    %by \cite[(2.24)]{RenSongZhang2014Central}, 
+%END DELETED
+    the integral on the left-hand side of \eqref{eq: what I want to proof} is positive.
+
+The proofs of \eqref{item: stable 2}, \eqref{item: stable 3}, \eqref{item: stable 4} and \eqref{item: stable 5} are similar to that of \eqref{item: stable 1}. We omit the details here.
 \end{proof}
-%Moved and modified above
-    %Recall that
-%\begin{align}
-    %\mathcal{N}
-    %=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
-%\end{align}
-    %and
-%\begin{align}
-    %\mathcal{C}_l
-    %=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
-%\end{align}
-%
-    %For each $g\in \mathcal{C}_l$ we have the following expression:
-%\[
-    %g(x)
-    %=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.
-%\]
-    %Also recall that $I_tg(x)$ is defined by
-%\begin{align}
-    %I_tg(x)
-    %=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
-%\end{align}
-    %Define
-%\begin{align}
-    %K=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
-%\end{align}
-%End moved and modified above
-%Deleted
-%\begin{lem}\label{lem: control of Isg}
-    %For each $g\in \mathcal{C}_l$, there exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
-%\begin{align}
-    %|I_tg(x)|
-    %\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
-%\end{align}
-%\end{lem}
-%\begin{proof}
-    %Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  
-    %Put $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$. 
-    %Then
-%\begin{align}
-    %|I_tg(x)|
-    %=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|
-    %\leq e^{-(\alpha-Kb)t}h(x),
-    %\quad t\geq 0,x\in \mathbb{R}^d.
-%\end{align}
-%\end{proof}
-%End Deleted
-%Deleted
-    %For each  $n\geq 1$, let
-%\begin{align}
-    %\bar{m}_n[g]
-    %:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds.
-%\end{align}
-%\begin{lem}\label{lem: control of mn}
-    %For each $g\in \mathcal{C}_l$,  there exists constant $C>0$ such that
-%\begin{align}
-    %|\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1,
-%\end{align}
-    %which implies that
-%\begin{equation}\label{sum-bar-m}
-    %\bar{m}[g]
-    %:=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds
-    %=\sum_{n=1}^{\infty}\bar{m}_n[g]
-%\end{equation}
-    %is well-defined.
-%\end{lem}
-%\begin{proof}
-    %Let $h$ be the function in Lemma \ref{lem: control of Isg}. Then
-%\begin{align}
-    %&|\bar{m}_n[g]|
-    %\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds
-    %\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
-    %&\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle
-    %\leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
-%\end{align}
-    %Using  the fact that $\alpha\beta>K(1+\beta)b$, we easily get $\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
-%\end{proof}
-%End Deleted
-%Deleted
-%\begin{prop}\label{cor: alpha stable rv 1}
-    %For all $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
-%\begin{enumerate}
-%\item \label{item: stable 2}
-    %$\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
-%\item \label{item: stable 3}
-    %$\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable.
-%\end{enumerate}
-%\end{prop}
-%\begin{proof}
-    %The proof is similar to that of Proposition \ref{prop: alpha stable rv}. We omit the details here.
-%\end{proof}
-%End Deleted
-%Moved and modified from above
-%Added
-    Before we end this subsection, we also give the following two lemmas which are useful:
-%End Added
+
+ Before we end this subsection, we  give  two more lemmas which will be used in the proofs of our main results in Section \ref{proofs of main results}.
+
 \begin{lem}{\cite[Lemma 2.8]{MarksMilos2018CLT}}\label{lem: control of gk}
@@
 \begin{proof}
-    The proof  is similar to that of \cite[Lemma 2.8]{MarksMilos2018CLT}.
-    {\bf ZS: Jianjie says he will give more details about this.}
+    First we claim that there exists $h_1\in \mathcal P$ such that
+\begin{align}
+\label{ineq: control of partial derivative of Itg}
+    \Big|\frac{\partial}{\partial x_i}I_tg(x)\Big| \leq e^{-(\alpha-Kb)t}h_1(x),
+    \quad  t\geq 0, x\in \mathbb R^d.
+\end{align}
+	%In fact, if we put $h_1(x)=\Big|\sum_{p\in \mathcal N}\langle g, \phi_p\rangle_\varphi\frac{\partial}{\partial x_i}\phi_p(x)\Big| \in \mathcal P$, then
+    In fact, if we put $h_1(x)=\sum_{p\in \mathcal N}|\langle g, \phi_p\rangle_\varphi\frac{\partial \phi_p}{\partial x_i}(x)| \in \mathcal P$, then
+\begin{align}
+    \Big|\frac{\partial}{\partial x_i}I_tg(x)\Big| = 
+    \Big|\sum_{p\in \mathcal N}\langle g, \phi_p\rangle_\varphi e^{-(\alpha-|p|b)t} \frac{\partial}{\partial x_i}\phi_p(x)\Big|
+     \leq e^{-(\alpha-Kb)t}h_1(x),
+    \quad t\geq 0, x\in \mathbb R^d.
+\end{align}
+%NEW ADDED
+    We have the following well-known results for the OU semigroup: 
+\[
+    P_t f(x) = \int_{\mathbb R^d} f\big(x e^{-bt} + y \sqrt{1-e^{-2bt}}\big) \varphi(y) dy,
+    \quad t\geq 0, x\in \mathbb R^d, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
+\]
+    It is clear that the above equality also holds for each $f\in \mathcal P$.
+    From this, it can be checked that for each $f \in \mathcal P$ such that $f$ is differentiable with $|\nabla  f| \in \mathcal P$, we have
+\[
+    \frac{\partial P_t^\alpha f(x)}{\partial x_i} = e^{-bt} P_t^\alpha\Big(\frac{\partial f}{\partial x_i}\Big)(x), \quad t\geq 0, x\in \mathbb R^d.
+\]
+    Note that if $g \in \mathcal C_l$, then we do have $g^{1+\beta}\in \mathcal P$ and $|\nabla (g^{1+\beta})| \in \mathcal P$.
+    Therefore, 
+\begin{align}
+    &\frac{\partial}{\partial x_i} P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta} 
+    = \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s} g)^{1+\beta} 
+    = e^{-b(1-s)} P_{1-s}^\alpha \frac{\partial}{\partial x_i} (I_{t-s}g)^{1+\beta}
+    \\&=(1+\beta)e^{-b(1-s)} P_{1-s}^\alpha \Big( (I_{t-s}g)^\beta \times \frac{\partial}{\partial x_i} (I_{t-s}g) \Big),\quad s\in [0,1], t\geq 0.
+\end{align}
+    Using \eqref{eq: supper for Itf}, \eqref{ineq: control of partial derivative of Itg} and above, we have that there exists a bounded function $a$ on $[0,1]$ and an $h_2 \in \mathcal P$ such that
+\begin{equation}
+\label{eq: key estimation for partial}
+    \Big|\frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| \leq a(s) e^{-(\alpha - Kb)(1+\beta)t}h_2(x),\quad s\in [0,1],t\geq 0, x\in \mathbb R^d.
+\end{equation}
+    Therefore, for each compact subset $A \subset \mathbb R^d$, we have
+\[
+    \int_0^1 \sup_{x\in A} \Big|\frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| ds < \infty,\quad t\geq 0.
+\] 
+    According to this and \cite[Theorem A.5.2.]{Durrett2010Probability} we have
+\[
+    \frac{\partial}{\partial x_i} Z_1(-I_tg)
+    = \eta i^{1+\beta}  \frac{\partial}{\partial x_i} \int_0^1 P_{1-s}^\alpha (I_{t-s}g)^{1+\beta} ds
+    = \eta i^{1+\beta}  \int_0^1  \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s}g)^{1+\beta} ds.
+\]
+    Therefore, using \eqref{eq: key estimation for partial} and above, there exists a constant $C> 0$ such that for all $t\geq 0$, 
+\begin{align}
+    &\Big|\frac{\partial}{\partial x_i}\bar{g}_t(x)\Big| 
+    = e^{(\alpha-Kb)(1+\beta)t}\Big|\frac{\partial}{\partial x_i}Z_1(-I_tg)\Big| \leq C h_2(x),
+    \quad x\in \mathbb R^d.
+\end{align}
+%END NEW ADDED
+%DELETED
+    %According to \eqref{ineq: control of Itg} and \eqref{ineq: control of partial derivative of Itg}, we easily get there exists $h_2 \in \mathcal P$ such that for all $t\geq 0$,
+%\begin{align}
+    %&\Big|\frac{\partial}{\partial x_i}\bar{g}_t(x)\Big| 
+    %= e^{(\alpha-Kb)(1+\beta)t}\Big|\frac{\partial}{\partial x_i}Z_1(-I_tg)\Big| \\
+    %& = (1+\beta) \eta e^{(\alpha-Kb)(1+\beta)t}\Big |\int_0^1 P_{1-s}^{\alpha}\Big((iP_s^{\alpha} I_tg)^{\beta}\cdot i P_s^{\alpha}(\frac{\partial}{\partial x_i}I_tg(x))\Big)~ds\Big| \\
+    %& \leq (1+\beta) \eta  e^{(\alpha-Kb)(1+\beta)t}
+    %\int_0^1 P_{1-s}^{\alpha}\Big((P_s^{\alpha} |I_tg|)^{\beta}\cdot P_s^{\alpha}(\big|\frac{\partial}{\partial x_i}I_tg(x)\big|)\Big)~ds \\
+    %& \leq h_2(x).
+%\end{align}
+%END DELETED
+%Therefore, there exists $h_3 \in \mathcal P$, such that
+Therefore, there exists constants $c,n>0$ such that 
+\begin{align}\label{ineq: control of sup gt}
+    %\sup |\nabla \bar g_t (z)| \leq h_3(x)+h_3(y),
+    %\quad t\geq 0,~ x,y \in \mathbb R^d,
+    |\nabla \bar g_t (z)| 
+    \leq c(1+|z|)^n,
+    \quad t\geq 0, z\in \mathbb R^d.
+\end{align}
+%NEW ADDED
+    Denote by
+\[
+    D(x,y):= \{ax+by: a,b\in [0,1]\},\quad x, y \in \mathbb R^d.
+\]
+    Then for each $x,y\in \mathbb R^d$, $D(x,y)$ is a convex set on $\mathbb R^d$. 
+    In particular, it contains the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$ for each $s\geq 0$.
+    Also, observe that 
+\[
+    |\sqrt {1-\theta} - 1| \leq \theta, \quad \theta\in [0,1],
+\]
+and
+\[
+    1+\theta + \lambda \leq (1+\theta)(1+\lambda), \quad \theta ,\lambda \geq 0.
+\]
+    By the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we may now write for each $s,t\geq 0, x\in \mathbb R^d$
+\begin{align}
+    &|P_s\bar{g}_t(x)| 
+    = \Big|\int_{\mathbb R^d} \big(\bar {g}_t(xe^{-bs}+y\sqrt{1-e^{-2bs}})-\bar {g}_t (y)\big) \varphi(y)~dy \Big| \\
+    & \leq \int_{\mathbb R^d} \sup_{z\in D(x,y)} |\nabla \bar g_t (z)|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy \\
+    & \leq e^{-bs}\int_{\mathbb R^d} c(1+|x|+|y|)^n (|x|+|y|) \varphi(y)~dy
+    \\& \leq ce^{-bs}(1+|x|)^n\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y)dy + \int_{\mathbb R^d}(1+|y|)^n|y|\varphi(y)dy\Big).
+    \qedhere
+\end{align}
+%END NEW ADDED
+%Deleted
+%where supermum is taken over $z$ in the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$.
+%By the fact $\langle \bar{g}_t,\varphi\rangle = 0$, we may write
+%\begin{align}
+    %&|P_s\bar{g}_t| = \Big|\int_{\mathbb R^d} \big(\bar {g}_t(xe^{-bs}+y\sqrt{1-e^{-2bs}})-\bar {g}_t (y)\big) \varphi(y)~dy \Big| \\
+    %& \leq \int_{\mathbb R^d} \sup |\bigtriangledown \bar g_t (z)|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy \\
+    %& \leq \int_{\mathbb R^d} ( h_3(x)+h_3(y))|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy.
+%\end{align}
+ %We get the conclusion by the fact that there exists $h_4 \in \mathcal P$ such that
+%\begin{align}
+    %\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big|\leq e^{-bs}(h_4(x)+h_4(y)),
+    %\quad s\geq 0,~x,y \in \mathbb R^d.
+%\end{align}
 \end{proof}
-%End moved and modified from above
-
-%Deleted
-%\section{Preliminary results}
-    %In this section, we will give a small value probability result for supercritical continuous-state branching processes with general branching mechanisms and give some estimates on the $(1+\gamma)$-moments for our super-OU process.
-    %These will be needed to prove our main results.
-%End Deleted
 
 \subsection{Small value probability}
-    %In this subsection, we digress briefly from our super-OU process and consider a supercritical continuous-state branching process (CSBP) $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
+\label{sec: Small value probability}
     In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}.
-%Added
-    Such process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying that
+    Such a process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying that
 \[
@@
 \end{equation}
-    It can be varified that for each $\mu \in \mathcal M(\mathbb R^d)$ with $x = \| \mu \|$, we have
+    It can be verified that for each $\mu \in \mathcal M(\mathbb R^d)$ with $x = \| \mu \|$, we have
 \[
@@
 \]
-%End added
-
-    Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$ where $k_t \to 0$ as $t\to \infty$.
-%Deleted    
-    %Assume that the branching mechanism of  $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is given by \eqref{eq: honogeneou branching mechanism}.
-%End deleted
+
+    Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$ 
+    when $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
     Suppose that Grey's condition is satisfied, i.e., there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-    Also suppose that the $L \log L$ critierion is satisfied, i.e.,
+    Also suppose that the $L \log L$ criterion is satisfied, i.e.,
 \[
@@
     Suppose that $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
-    Then, for each $x\geq 0$, there are constants $C,\delta>0$ such that
+    Then, for each $x\geq 0$, there exist constants $C,\delta>0$ such that
 \[
@@
     Step 1. We recall some known facts about the CSBP $(Y_t)$.
-    %For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of
        For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of \eqref{eq: fkpp equation for CSBP}.
-%Deleted
-%\[
-    %v_t(\lambda)
-    %= \lambda - \int_0^t \psi(v_s(\lambda))ds,\quad t\geq 0.
-%\]
-    %Then according to the definition of CSBP, we have
-%\[
-    %\mathbf P_x[e^{-\lambda Y_t}] = e^{-xv_t(\lambda)}, \quad t\geq 0, \lambda \geq 0, x\geq 0.
-%\]
-%End deleted
-    %letting $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
     Letting $\lambda \to \infty$ in \eqref{eq: fkpp equation for CSBP}, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
@@
 \end{equation}
-    It is known, see \cite[Theorem 3.5-3.8]{Li2011Measure-valued} for example, that under Grey's condition, the following statements are true:
+    It is known, see \cite[Theorems 3.5-3.8]{Li2011Measure-valued} for example, that under Grey's condition, the following statements are true:
 \begin{itemize}
@@
     In fact, for all $x\geq 0$ and $t\geq 0$, we have
-\begin{equation}\begin{split}
+\begin{align}
     &\mathbf P_{x}(0<W_t \leq k_t)
@@
     \\&\leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big),
-\end{split}\end{equation}
+\end{align}
     as desired in this step.
@@
 \]
-    %In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
         In fact, since $\psi$ is a convex function, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for each $z\geq \bar v$.
@@
     For each $t > t_0$, according to \eqref{eq:svp2}, we have
-\begin{equation}\begin{split}
+\begin{align}
     &t-t_0 = \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)}
@@
     = \frac{1}{\tau} \big(\log (z_0-\bar v) - \log(\bar v_t-\bar v)\big).
-\end{split}\end{equation}
-    Rearranging this, we get
+\end{align}
+    Rearranging, we get
 \[
@@
 \]
-    The $L \log L$ critierioin also garuntees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.
+    The $L \log L$ criterion also guarantees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.
 in $\mathbf P_1$.
@@
     For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$.
-    %Then using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have
         Then using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have for $t>0$ large enough,
-\begin{equation}\begin{split}
+\begin{align}
     &t =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
@@
      \\&= \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
-\end{split}\end{equation}
+\end{align}
     where we used the fact that
@@
     Now we have, for $t$ large enough,
-\begin{equation}\begin{split}
+\begin{align}
     &t\leq  \rho_t t + O(1)+ \int_{z_0}^{v_t(k_t^{-1}e^{-\alpha t})} \frac{dz}{(\bar v-z)(\tau - \epsilon)}
     \\&=  \rho_t t +O(1)- \frac{1}{\tau-\epsilon}\Big( \log \big(\bar v-v_t(e^{-\alpha \rho_t t})\big) - \log(\bar v-z_0)\Big).
-\end{split}\end{equation}
-    Rearranging this, we get, for $t$ large enough,
+\end{align}
+    Rearranging, we get, for $t$ large enough,
 \[
@@
 \end{proof}
-%\subsection{moments estimates  for super-OU processes}
-\subsection{Moments for the super-OU processes}
-
-    %In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
-    In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: branching mechanism} and \ref{asp: Greys condition}.
-    %For all $0 \leq s \leq t <\infty$ and  random variable $Y$ with finite mean, we write
-    With respect to a probability $\mathbb P_\mu$ with $\mu\in \mathcal M(\mathbb R^d)$, for each $0 \leq s \leq t <\infty$ and a random variable $Y$ with finite mean, we write
-\begin{equation}\label{Ist}
-    \mathcal I_s^t Y
-    := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s]
-\end{equation}
-%Added
-    where $(\mathscr F_t)_{t\geq 0}$ is the natural filtration of the super OU process $X$.
-%End added
+
+\subsection{Moments for super-OU processes}
+\label{sec: Moments for super-OU processes}
+    In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
+    Recall that the operator $\mathcal{I}^t_s$ is defined in \ref{Ist}.
 
@@
     Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof of \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
-\begin{equation}\begin{split}
+\begin{align}
     &\big|\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)\big|
@@
       \qedhere
-\end{split}\end{equation}
+\end{align}
 \end{proof}
-%moved above
-    %For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-%\begin{equation}\label{Q_k}
-    %Q_\kappa f 
-    %:= \sup_{t\geq 0} e^{\kappa b t}|P_t f|
-%\end{equation}
-    %and
-%\begin{equation}\label{Q}
-    %Q f:= Q_{\kappa_f}f.
-%\end{equation}
-    %Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
-%End moved above
 \begin{lem}\label{lem: temp}
     For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists a constant $C > 0$ such that
-    %for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
        for all $\kappa \in \mathbb Z_+ $, $\lambda > 0$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
@@
     Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: control pair for P(M>lambda)}.
-    Fix $h \in \mathcal P^+$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t < \infty$ with $s-r \leq 1$.
+    Fix $h \in \mathcal P^+$, $\mu \in \mathcal M_c(\mathbb R^d)$ $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t < \infty$ with $s-r \leq 1$.
     Suppose that $g\in \mathcal P$ satisfies $Q_\kappa g \leq h$.
@@
 \label{lem: control of mgtrs}
-    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
+    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
 \[
@@
     For all $\kappa \in \mathbb Z_+$,  $0\leq r\leq s\leq t$ with $s-r \leq 1$,  $g\in \mathcal P$ with $Q_{\kappa} g \leq h$, and $c>0$, we have
-\begin{equation}\begin{split}
+\begin{align}
     &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
@@
     \\&\leq c^{1+\gamma} e^{\alpha r} + C_0e^{\alpha r}(1+\gamma)\Big(  \frac{e^{(1+\beta)(t-s)(\alpha- \kappa b)}}{(\beta - \gamma)c^{\beta - \gamma}}  + \frac{e^{2(t-s)(\alpha- \kappa b)}}{(1 - \gamma)c^{1 - \gamma}} \Big).
-\end{split}\end{equation}
+\end{align}
     Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
-\begin{equation}\begin{split}
+\begin{align}
     &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
     \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
-\end{split}\end{equation}
+\end{align}
     Note that
-\begin{equation}\begin{split}
+\begin{align}
     &(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r
@@
     \\&\leq t\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b).
-\end{split}\end{equation}
+\end{align}
     So the desired result is true with
@@
 \end{proof}
-
+    %ADDED
+    For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write its $L_p$-norm as
+\[
+    \|Y\|_{\mathbb P;p}:= E[|Y|^p]^{1/p}.
+\]
+    %END ADDED
 \begin{lem}
@@
     Using the triangle inequality, for all $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$, we have
-\begin{equation}\begin{split}
+\begin{align}
     &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
@@
     \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
-\end{split}\end{equation}
+\end{align}
     By calculating the sum on the right, we get the desired result.
@@
 
-\section{Proofs of main results}
-    In this section, we will prove the main results of this paper.
-Recall that $\mathcal{M}_c(\mathbb{R}^d)$ is the space of all finite Borel measures of compact support on $\mathbb{R}^d$.
-Denote  $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in the following section.
-
-\subsection{The large rate case}
-
-    In this subsection, we prove Theorem \ref{Theorem11}. 
-    We will return to the large branching rate case in Subsection \ref{large rate again} to prove Theorem \ref{thm: large clt}.
-    {\bf (ZS: Jianjie, can you bring the proofs related to the large branching together? I mean you can move subsection 3.4 just after this subsection.)}
-
-    To prove Theorem \ref{Theorem11}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
+\section{Proofs of main results}\label{proofs of main results}
+    In this section, we will prove the main results of this paper. Recall that $\mathcal{M}_c(\mathbb{R}^d)$ is the space of all finite Borel measures of compact support on $\mathbb{R}^d$. 
+    For simplicity, we will write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$
+    in this section.
+
+%\subsection{The large rate regime}
+\subsection{The large rate regime: law of large numbers}
+\label{sec: large rate lln}
+
+    In this subsection, we prove Theorem \ref{thm: law of large number}.
+    We will return to the large branching rate regime in Subsection \ref{sec: large rate clt} to prove Theorem \ref{thm: large clt}.
+
+    To prove Theorem \ref{thm: law of large number}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
 Recall that $L$ is the infinitesimal generator of the OU-process.
 For $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and  $a\in \mathbb R$, we define
-\begin{equation}\begin{split}
+\begin{align}
 \label{defmartingale}
@@
     :=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds.
-\end{split}\end{equation}
+\end{align}
     Let $(\mathscr{F}_t)_{t\geq 0}$ be the natural filtration of $X$.  The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
@@
 \begin{proof}
-    We write $\bar{f}=(L+ab)f$. According to \cite[Theorem A.55]{Li2011Measure-valued}, we have
-\begin{equation}\begin{split}\label{Theorem55}
-    P_t^{ab}f(x)= f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d.
-\end{split}\end{equation}
+    Put$\bar{f}:=(L+ab)f$. 
+    It follows easily from the Ito formula that
+\begin{equation}\label{Theorem55}
+    P_t^{ab}f(x)= f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d,
+\end{equation}
+%ADDED
+    where $P_t^{ab} := e^{abt}P_t$.
+%END ADDED
     For $0\leq s\leq t$, we have
-\begin{equation}\begin{split}
+\begin{align}
 \label{martingale1}
@@
     \\&\quad -\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
-\end{split}\end{equation}
+\end{align}
     Using \eqref{Theorem55} and Fubini's theorem, we have
-\begin{equation}\begin{split}
+\begin{align}
     &\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle P_{u-s}^{ab}\bar{f},X_s\rangle~du\\
@@
     f,X_s\rangle.
-\end{split}\end{equation}
+\end{align}
     Using this and \eqref{martingale1}, we get the desired result.
@@
 
-    Let $p=(p_1,...,p_d)\in \mathbb Z_+^d$, recall that $\phi_p$ is an eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
+    Recall that, for $p=(p_1,...,p_d)\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
 \[
@@
     For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
-Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
+Moreover, if $\alpha\beta>|p|b(1+\beta)$, then, for all $\gamma\in (0, \beta)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
 \[
@@
     It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb R^d)$.
-    There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
+    %There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
+    There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, we have $\alpha\gamma>|p|(1+\gamma)b$.
     Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that, for $\gamma\in [\gamma_0, \beta)$, there exists a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$) such that
@@
 \begin{lem}\label{lem: control of wt}
-    For all $\gamma\in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for all $0\leq s<t$,
+    %For all $\gamma\in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists $C> 0$ such that for all $0\leq s<t$,
+    Let $\mu\in \mathcal M_c(\mathbb R^d)$. 
+    For each $\gamma\in (0,\beta)$ and $p\in \mathbb{Z}_+^d$ with $\alpha \gamma > |p|b(1+\gamma)$, there exists $C> 0$ such that for all $0\leq s<t$,
 \[
@@
 \begin{proof}
-    The second assertion follows immediately from the first, so we only first the first assertion.
+    The second assertion follows immediately from the first, so we only prove the first assertion.
     Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-    It follows from Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$ that there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
-\begin{align}
-    \mathbb{P}_{\mu}\big[\big|e^{(\alpha-|p|b)(t-s)}\langle\phi_p, X_s\rangle-e^{(\alpha-|p|b)(t-r)}\langle\phi_p, X_r\rangle\big|^{1+\gamma}\big]
-    \leq C_0e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b\gamma}.
+    It follows from Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$ that there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
+\begin{align}
+    \mathbb{P}_{\mu}\Big[\big|e^{(\alpha-|p|b)(t-s)}\langle\phi_p, X_s\rangle-e^{(\alpha-|p|b)(t-r)}\langle\phi_p, X_r\rangle\big|^{1+\gamma}\Big]
+    %\leq C_1e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b\gamma}.
+    \leq C_1e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b)}.
 \end{align}
@@
     \mathbb{P}_{\mu}\big[|H^p_s-H^p_r|^{1+\gamma}\big]
-    \leq  C_0 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
-\end{align}
-    Thus there is a $C>0$ such that for any $0\leq s<t$,
+    \leq  C_1 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
+\end{align}
+    Thus there exists $C_2>0$ such that for any $0\leq s<t$,
 \begin{align}
@@
 	\\&\leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
-	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
-	\\&\leq Ce^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
+	\\& \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
+	\\&\leq C_2e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
     \qedhere
@@
 
-    {\it Proof of Theorem \ref{Theorem11}.}\quad
+    %{\it Proof of Theorem \ref{thm: law of large number}.}\quad
+\begin{proof}[Proof of Theorem \ref{thm: law of large number}]
 	Fix  $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
 	Write
-\begin{equation}\begin{split}
+\begin{equation}
     f
@@
     \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f}.
-\end{split}\end{equation}
+\end{equation}
 	Then
-\begin{align*}
+\begin{align}
     &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
@@
     \quad t\geq 0.
-\end{align*}
+\end{align}
 	According to Lemma \ref{lemma26},
 	we have
-\begin{equation}\begin{split}
+\begin{equation}
 \label{as convergence}
@@
     \xrightarrow[t\to \infty]{} \sum_{p\in \mathbb{Z}_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
-\end{split}\end{equation}
+\end{equation}
     $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
 	Therefore, it suffices to show that
-\begin{equation}\begin{split}
+\begin{equation}
     J_t
@@
     \quad t\geq 0,
-\end{split}\end{equation}
+\end{equation}
 	converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$ satisfies $D^2f\in \mathcal{P}$.
@@
 	Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa < \frac{\alpha \beta}{b(1+\beta)}$.
-	We will show that for each $\gamma \in (0,\beta)$ there exist constants $C,\delta > 0$ such that
+	We will show that for each $\gamma \in (0,\beta)$ there exist 
+	constants $C_1,\delta_1 > 0$ such that
 \[
 	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-	\leq C e^{-\delta t},
+%	\leq C e^{-\delta t},
+	\leq C_1 e^{-\delta_1 t},
 	\quad t\geq 0.
@@
 \item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C_2>0$ such that
 \[
     \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    \leq C e^{-(\alpha-\kappa b)t}e^{(\alpha-\kappa_g b)t}
-    \leq C  e^{-(\kappa_g - \kappa )bt},
+    \leq C_2 e^{-(\alpha-\kappa b)t}e^{(\alpha-\kappa_g b)t}
+    \leq C_2  e^{-(\kappa_g - \kappa )bt},
     \quad t\geq 0;
@@
 \item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C>0$ such that
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C_3>0$ such that
 \[
     \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-    \leq C t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-    = C t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
+    \leq C_3 t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
+    = C_3 t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
     \quad t\geq 0;
@@
 \item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C_4>0$ such that
 \[
     \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-    = C  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
+    \leq C_4  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
+    = C_4  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
     \quad t\geq 0;
@@
 	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above, and the fact that \[\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-	\leq \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C, \delta >0$ such that
+	\leq \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C_5, \delta_2 >0$ such that
 \[
 	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-	\leq Ce^{-\delta t},
+	\leq C_5e^{-\delta_2 t},
 	\quad t\geq 0.
@@
 	Step 2.
-	We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$, we will show that $J_t$ converges to $0$ almost surely.
+	%We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$, we will show that $J_t$ converges to $0$ almost surely.
+    We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$. 
+    We will show that $J_t$ converges to $0$ almost surely.
 	For $a \geq 0$ and $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
-\begin{equation}\begin{split}
-	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,
-\end{split}\end{equation}
+\begin{equation}
+	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds
+\end{equation}
     and
-\begin{equation}\begin{split}
+\begin{equation}
     Y_t^{g,a}
     :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
-\end{split}\end{equation}
+\end{equation}
 	Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$.
 	According to \eqref{defmartingale}, we have
-\begin{align*}
+\begin{align}
     J_t
@@
     \quad t\geq 0.
-\end{align*}
+\end{align}
 	So we only need to show that
-\begin{align*}
+\begin{align}
     e^{-(a_0-\kappa_f)b t}M_t^{\tilde{f},a_0}
@@
     \quad \mathbb{P}_{\mu}\text{-a.s.}
-\end{align*}
-	Notice that $\kappa_{(L+a_0 b)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
-	So according to Step 1, for an arbitrary fixed $\gamma\in (0,\beta)$, there exist $C, \delta>0$ such that for each $t\geq 0$,
-\begin{equation}\begin{split}
+\end{align}
+	%Notice that $\kappa_{(L+a_0 b)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
+    Notice that $\kappa_{(L+a_0 b)\tilde{f}}\geq \kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
+By Step 1, for any fixed $\gamma\in (0,\beta)$, there exist $C_6, \delta_3>0$ such that for each $t\geq 0$,
+\begin{equation}
     \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C e^{-\delta t},
+    \leq C_6 e^{-\delta_3 t},
     \quad \|e^{-(\alpha-a_0 b)t}\langle L\tilde{f}+a_0 b\tilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C e^{-\delta t}.
-\end{split}\end{equation}
+    \leq C_6 e^{-\delta_3 t}.
+\end{equation}
 	Now, by the triangle inequality, for each $t\geq 0$,
-\begin{align*}
+\begin{align}
     &\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq\|Y_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\tilde{f}+a_0 b\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
-\end{align*}
+    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\tilde{f}+a_0 b\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
+\end{align}
     Since $Y_t^{\tilde{f},a_0}$ is increasing in $t$, it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-	As a consequence, almost surely we have
-\begin{align*}
+Consequently,  we have
+\begin{align}
     \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\tilde{f},a_0}|
-    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\tilde{f},a_0}|=0.
-\end{align*}
+    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\tilde{f},a_0}|=0, \quad
+     \mathbb P_\mu\text{-a.s.}
+\end{align}
 	On the other hand, the martingale $M_t^{\tilde{f},a_0}$ satisfies
-\begin{align*}
+\begin{align}
     \|M_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),
+    \leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    %\leq C(e^{-\delta t}+\frac{1}{\delta}),
+    \leq C_6(e^{-\delta_3 t}+\frac{1}{\delta_3}),
     \quad t\geq 0.
-\end{align*}
+\end{align}
 	This implies that the martingale converges almost surely.
-	As a consequence,
+	Consequently,
 \[
@@
 	=0,
-	\quad \mathbb P_\mu\text{-a.s.}
-\]
-
-	The proof is now complete.
-
-\subsection{The critical rate case}
-
-    Recall that $I_s^t$ is defined in \eqref{Ist}.
+	\quad \mathbb P_\mu\text{-a.s.}.
+    \qedhere
+\]
+\end{proof}
+
+\subsection{The critical rate regime}
+\label{sec:critical}
+
+    Recall that $\mathcal I_s^t$ is defined in \eqref{Ist}.
+
 \begin{lem}\label{lem: mainlemma}
-    Let $f\in \mathcal{P}$. 
-    Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
+Let $f\in \mathcal{P}$ be non-trivial and satisfy $\alpha\beta\leq \kappa_fb(1+\beta)$.
     Then for all $k\geq 0$ and $\mu \in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
-\begin{equation}\begin{split}
+\begin{equation}
     \gamma_{t,k}
     :=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
-\end{split}\end{equation}
+\end{equation}
     where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 \[
-    \mathbb{E}(e^{i\theta\zeta_k})
+    \mathbf{E}(e^{i\theta\zeta_k})
     =\exp(e^{\alpha}m_k[\theta f]),\quad \theta \in \mathbb R.
@@
     We only need to show that for all $\mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0$,
-\begin{equation}\begin{split}
+\begin{equation}
     \mathbb{P}_{\mu}[\exp(i\gamma_{t,k}); D^c]
     \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[f]).
-\end{split}\end{equation}
+\end{equation}
     In fact, once we prove this, we can replace $f$ by $\theta f$, with $\theta \in \mathbb R$ being  arbitrary,  to get the desired result.
@@
     Step 1. We will show that for all $\epsilon > 0, k\geq 0$ and $t>k+1$, we have
-\begin{equation}\begin{split}
+\begin{equation}
     \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
     \leq J_1(t,k,\epsilon)+J_2(t,k,\epsilon)+J_3(t,k,\epsilon),
-\end{split}\end{equation}
+\end{equation}
     where
-\begin{equation}\begin{split}
+\begin{align}
 \label{eq: Def of Ji}
     J_1(t,k,\epsilon)
-    &:= \mathbb{P}_{\mu}\big[|\langle K_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
+    %&:= \mathbb{P}_{\mu}\big[|\langle K_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
+    &:= \mathbb{P}_{\mu}\big[|\langle Z'''_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
     \\ J_2(t,k,\epsilon)
@@
     &:= (e^{\alpha k}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
-\end{split}\end{equation}
-    In fact, it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
-\begin{equation}\begin{split}
+\end{align}
+    %In fact, it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
+    %In fact, it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $Z'''_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
+    In fact, it follows from \eqref{eq: key equality}, the definitions of $U_1$, $Z'''_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
+\begin{align}
 \label{eq: need1}
@@
     \\&=e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}
-    =e^{\langle (Z_1 + K_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
-\end{split}\end{equation}
-    From Proposition \ref{prop: alpha stable rv}, we have
+    %=e^{\langle (Z_1 + K_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
+    =e^{\langle (Z_1 + Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
+\end{align}
+    From Proposition \ref{prop: alpha stable rv}.(1), we have
 \begin{equation}
@@
 \end{equation}
-    According to \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
+  Using \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
 \[
@@
     we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
+\begin{align}
 \label{eq: inequality that will used later}
@@
     \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{e^{\alpha}m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon)
-    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
-    \\& \leq \mathbb{P}_{\mu}\big[|\langle (U_1 - i T_1^\alpha)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    %\\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (Z_1+Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    %\\& \leq \mathbb{P}_{\mu}\big[|\langle (U_1 - i T_1^\alpha)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    \\& \leq \mathbb{P}_{\mu}\big[|\langle (Z_1+Z'''_1)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
     \\&\leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon).
-\end{split}\end{equation}
-
-Step 2. We will show that for each $\epsilon>0$ small enough, there exist constants $C, \delta>0$ such that
-\begin{equation}\begin{split}
+\end{align}
+
+Step 2. We will show that for each $\epsilon>0$ small enough, there exist constants $C_1, \delta_1>0$ such that
+\begin{equation}
 \label{lemma31q}
     J_1(t,k,\epsilon)
-    \leq Ce^{-\delta (t-k)},
+    \leq C_1e^{-\delta_1 (t-k)},
     \quad k\geq 0, t\geq k+1.
-\end{split}\end{equation}
+\end{equation}
     In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
     Then, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
-    & |K_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
+\begin{align}
+    %& |K_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
+    & |Z'''_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
     \leq R(|\theta_{t,k}P^\alpha_k f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
@@
     \\&\leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
-\end{split}\end{equation}
+\end{align}
     where $Q$ is defined by \eqref{Q}.
     Thus for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
+\begin{align}
 \label{eq: estimate of J1}
@@
     & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)},
-\end{split}\end{equation}
+\end{align}
     where $Q_0$ is defined by \eqref{Q_k} with $k=0$.
@@
     Step 3.
-    We will show that for $\epsilon>0$ small enough, there exist constants $C, \delta>0$ such that
-\begin{equation}\begin{split}
+    We will show that for $\epsilon>0$ small enough, there exist constants $C_2, \delta_2>0$ such that
+\begin{equation}
 \label{eq:31step3}
     J_2(t,k,\epsilon)
-    \leq Ce^{-\delta (t-k)},
+    \leq C_2e^{-\delta_2 (t-k)},
     \quad k\geq 0, t\geq k+1.
-\end{split}\end{equation}
+\end{equation}
     In fact, according to the definitions of $Z_1$ and $m_t$, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
+\begin{align}
     &\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]
@@
     \\&=e^{-\alpha k}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big).
-\end{split}\end{equation}
+\end{align}
     Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
+\begin{align}
 \label{eq: prevJ2}
@@
     &\leq e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
-\end{split}\end{equation}
+\end{align}
 where
@@
  \]
-    where $Q_1$ is defined by \eqref{Q_k} with $k=1$.
+    where $Q_1$ is defined by \eqref{Q_k} with $\kappa=1$.
 
     Chose a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-    According to Lemma \ref{lem: control moment}.(3) (with $\kappa=1$), there exists $C>0$ such that for all $t\geq 0$ and $k\geq 0$,
-\begin{equation}\begin{split}
+    According to Lemma \ref{lem: control moment}.(3) (with $\kappa=1$), there exists $C_3>0$ such that for all $t\geq 0$ and $k\geq 0$,
+\begin{align}
     &\mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t}\rangle\right|\right]
     \leq \|\langle \operatorname{Re} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}}
-    \\& \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C e^{\frac{\alpha t}{1+\gamma}}.
-\end{split}\end{equation}
-    Therefore, it follows from \eqref{eq: prevJ2} that there exists constant $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
+    \\& \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_3 e^{\frac{\alpha t}{1+\gamma}}.
+\end{align}
+    %Therefore, it follows from \eqref{eq: prevJ2} that there exists constant $C_3>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+    Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$, we have
+\begin{align}
 \label{eq: right bound for J2}
@@
     \leq  e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
-    \\&\leq C e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)}
-    \\&= C e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
-    \\&\leq C e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
-\end{split}\end{equation}
+    \\&\leq C_3 e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)}
+    \\&= C_3 e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
+    \\&\leq C_3 e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
+\end{align}
     By taking $\epsilon >0$ small enough, we get the required result in this step.
@@
     Step 4.
-    We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C,\delta>0$ such that for all $k\geq0, t\geq k+1$,
-\begin{equation}\begin{split}\label{ineq: control of J3}
-    J_3(t,k,\epsilon)\leq Ce^{-\delta (t-k)}.
-\end{split}\end{equation}
+    We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_3>0$ such that for all $k\geq0, t\geq k+1$,
+\begin{equation}\label{ineq: control of J3}
+    J_3(t,k,\epsilon)\leq C_4e^{-\delta_3 (t-k)}.
+\end{equation}
     In fact, we have  for all $t\geq 0, \epsilon >0$,
-\begin{equation}\begin{split}
+\begin{align}
     &\mathbb P_{\mu}(A_{t}(\epsilon), D) = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
@@
     \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
-\end{split}\end{equation}
-    According to Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there are constants $C, \delta>0$ such that for all $t\geq 0$,
-\begin{equation}\begin{split}
-    \mathbb P_\mu(A_t(\epsilon)^c,D^c) \leq   \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\|\leq e^{ - \epsilon t}) \leq C (e^{-\epsilon \delta t}+e^{-\delta t}).
-\end{split}\end{equation}
+\end{align}
+    According to Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_5, \delta_4>0$ such that for all $t\geq 0$,
+\begin{equation}
+    \mathbb P_\mu(A_t(\epsilon)^c,D^c) \leq   \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\|\leq e^{ - \epsilon t}) \leq C_5 (e^{-\epsilon \delta_4 t}+e^{-\delta_4 t}).
+\end{equation}
     Combining these results, we get the desired result in step 4.
@@
 \begin{cor}\label{cor: used in next corollary}
-    Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq \kappa_fb(1+\beta)$.
+   Suppose that $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq \kappa_fb(1+\beta)$.
     Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
-\begin{equation}\begin{split}
+\begin{equation}
     \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
     \leq Ce^{-\delta(t-k)}.
-\end{split}\end{equation}
+\end{equation}
 \end{cor}
@@
     According to \eqref{eq: inequality that will used later},  we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
+\begin{align}
     &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
     \\&\leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
-\end{split}\end{equation}
+\end{align}
 
@@
 	According to \eqref{eq: estimate of J1}, we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
+\begin{align}
     &J^{\theta f}_1(k,t,\epsilon)
@@
     \\& \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}.
-\end{split}\end{equation}
+\end{align}
 	From the definitions of $Z_1$ and $m_t$ we get that for all $g\in \mathcal P, \theta \geq 0, t\geq 0$,
@@
 	we have that there exists a constant $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}\begin{split}
+\begin{equation}
 \label{eq:31step3b}
@@
     \leq C |\theta|^{1+\beta}\exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big).
-\end{split}\end{equation}
+\end{equation}
 	Finally, noticing that $|\theta| < \Theta$, using the estimates of $J^{\theta f}_{i}, i = 1,2$ and the estimate of $J_3$ in Step 4 of the proof of the previous lemma, we get the desired result by choosing $\epsilon$ small enough.
@@
 
-\begin{prop}\label{corollary31}
-    Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq\kappa_fb(1+\beta)$. 
+\begin{prop}\label{cor: indepedent of the limit zeta for critical and small}
+   Suppose that $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq\kappa_fb(1+\beta)$.
     Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$satisfying $|\theta_i|\leq \Theta$, we have
-\begin{equation}\begin{split}
+\begin{equation}
 \label{32corollary}
     \Big|\mathbb{\tilde{P}}_{\mu}\Big[\prod_{k=0}^n\exp\Big(i\theta_k \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}}\Big)-\prod_{k=0}^n\exp(e^{\alpha}m_k[\theta_k f])\Big]\Big|\leq C e^{-\delta(t-n)}.
-\end{split}\end{equation}
+\end{equation}
 \end{prop}
 \begin{proof}
-	Let $C,\delta > 0$ be the constants in Corollary \ref{cor: used in next corollary}.
     Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
@@
     a_k
-    :=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
-\]
-    where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
-\begin{align*}
+    %:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
+    :=\Big(\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\Big) \times \mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
+\]
+    %where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
+    where by convention the first product is $1$ for $k=-1$. Then we get for each $k > -1$,
+\begin{align}
     &a_{k-1} - a_k
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
-\end{align*}
-    According to Proposition \ref{prop: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
-\begin{align*}
+    %\\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
+    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
+    \\&=\mathbb{P}_{\mu}(D^c)^{-1} \Big(\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
+\end{align}
+    %According to Proposition \ref{prop: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
+    According to Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
+\begin{align}
     |a_{k-1}- a_k|
@@
     \\& \leq C e^{-\delta(t-k)}.
-\end{align*}
+\end{align}
     Therefore,
-\begin{equation}\begin{split}
+\begin{align}
     \text{LHS of \eqref{32corollary}}&= \left|a_{-1}-a_n\right|
@@
     \leq \sum_{k=0}^n C e^{-\delta(t-k)}.
-\end{split}\end{equation}
+\end{align}
 	Recall that $C, \delta>0$ are independent of the choice of $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb R^{n+1}$ with $|\theta_i|\leq \Theta$.
@@
 
-{\it Proof of Theorem \ref{thm: critical clt}.}\quad
-    By assumption, $f\in\mathcal{P}$ and  $\alpha\beta=\kappa_fb(1+\beta)$.
+%{\it Proof of Theorem \ref{thm: critical clt}.}\quad
+\begin{proof}[Proof of Theorem \ref{thm: critical clt}]
+   By assumption, $f\in\mathcal{P}$ is non-trivial and satisfies $\alpha\beta=\kappa_fb(1+\beta)$.
+   Fix $\mu \in \mathcal M_c(\mathbb R^d)$.
     Chose $t_0 > 0$ large enough so that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
     We write
-\begin{align*}
+\begin{align}
     &(t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle
@@
     \quad t\geq t_0.
-\end{align*}
+\end{align}
     Define
@@
 \]
-    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb R$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{corollary31},
-    we get that there exist $C,\delta>0$ such that,
-\begin{align*}
-    \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq C \frac{1}{t^{\delta}},
+Fix $\theta\in \mathbb R$. 
+    Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small},
+    we get that there exist $C_1,\delta_1>0$ such that,
+\begin{align}
+    \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq \frac{C_1}{t^{\delta_1}},
     \quad t\geq t_0.
-\end{align*}
-    According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\zeta$ under $\tilde {\mathbb P}_\mu$.
+\end{align}
+    %According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\zeta$ under $\tilde {\mathbb P}_\mu$.
+    According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\tilde \zeta$ under $\tilde {\mathbb P}_\mu$.
     Therefore, we only need to prove
@@
     where for all $k \geq 0$ and $t\geq k+1$,
-\begin{align*}
+\begin{align}
     Y_{t,k}
     :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big).
-\end{align*}
+\end{align}
     Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
@@
 \]
+%ADDED
+    Recall that $H_t := e^{-\alpha t}\|X_t\|$.
+%END ADDED
     Define for all $k \geq 0$ and $t\geq k+1$,
-\begin{equation}\begin{split}
+\begin{equation}
 \label{def: Dtk}
-    \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
-\end{split}\end{equation}
-
-    Step 1. We will show that there exist $C,\delta >0$ such that for all $k \geq 0$ and $t\geq k+1$,
-\begin{equation}\begin{split}
+    \mathcal{D}_{t,k}:=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
+\end{equation}
+
+    Step 1. We will show that there exist $C_2,\delta_2 >0$ such that for all $k \geq 0$ and $t\geq k+1$,
+\begin{equation}
 \label{thm121}
     \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|;\mathcal{D}^c_{t,k}\big]
-    \leq C e^{-\delta (t-k)}.
-\end{split}\end{equation}
-    According to Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality, there exist $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
-\begin{equation}\begin{split}
+    \leq C_2 e^{-\delta_2 (t-k)}.
+\end{equation}
+    It follows from Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality that there exist $C_3, \delta_3>0$ such that for all $k \geq 0$ and $t\geq k+1$,
+\begin{align}
 \label{eq: prob of Dtkc}
@@
     \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]
-    \\&\quad +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
+    %\\&\quad +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
+    \\&\quad +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
     \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}
-    \\&\quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
-    \\&\leq C e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C e^{-\delta(t-k-1)}.
-\end{split}\end{equation}
+    %\\&\quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
+    \\&\quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
+    \\&\leq C_3 e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C_3 e^{-\delta_3(t-k-1)}.
+\end{align}
     This implies the desired result in this step, since $|Y_{t,k}| \leq 2$ a.s..
 
-    Step 2. We will show that there exist constant $C,\delta > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
-\begin{equation}\begin{split}
+    Step 2. We will show that there exist constant $C_4,\delta_4 > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
+\begin{equation}
 \label{thm122}
     \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \leq  C e^{-\delta (t-k)}.
-\end{split}\end{equation}
+    \leq  C_4 e^{-\delta_4 (t-k)}.
+\end{equation}
     In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \geq 0$ and $t\geq k+1$,
-\begin{equation}\begin{split}
+\begin{align}
 \label{eq: control of Ykt}
@@
     \\&\leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
-\end{split}\end{equation}
+\end{align}
     where
@@
     Note that, since $\eta_1 < \eta_0$, we have on $\mathcal D_{t,k}$,
-\begin{align*}
+\begin{align}
     H_t
@@
     \geq e^{-\eta_1(t-k-1)}.
-\end{align*}
+\end{align}
     Therefore, for each $k \geq 0$ and $t\geq k+1$,  on $\mathcal D_{t,k}$,
-\begin{align*}
+\begin{align}
     &\Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
-    \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
+    %\leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
+    \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|
     \\&\leq \frac{1}{1+\beta} \max\{e^{\eta_1 (t-k-1)}, \frac{1}{2}e^{\eta_1(t-k-1)}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0(t-k-1)}
     \\&\leq \frac{1}{1+\beta} e^{\eta_1 (t-k-1)} e^{-\eta_0(t-k-1)}
-    =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)},
-\end{align*}
+    =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)}
+\end{align}
     and
-\begin{align*}
+\begin{align}
     |H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}|
     \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1(t-k-1)}.
-\end{align*}
-    Thus, there is a constant $C\geq 0$ such that for all $k \geq 0, t\geq k+1$, 
-\begin{equation}\begin{split}
+\end{align}
+    Thus, there exists  $C_5> 0$ such that for all $k \geq 0, t\geq k+1$,
+\begin{equation}
 \label{ineq: control of Kkt}
      K_{t,k}
-     \leq C e^{-(\eta_0 - 3\eta_1)(t-k-1)}.
-\end{split}\end{equation}
-    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and \eqref{ineq: control of Kkt}, there exist constants $C,C'>0$ such that for all $k\geq 0$ and $t\geq k+1$,
-\begin{equation}\begin{split}
+     \leq C_5 e^{-(\eta_0 - 3\eta_1)(t-k-1)}.
+\end{equation}
+    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and \eqref{ineq: control of Kkt}, 
+    there exist constant $C_6>0$ such that for all $k\geq 0$ and $t\geq k+1$,
+\begin{align}
 \label{eq: Y in D}
     &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \leq C|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
-    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
-    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta_0 - 3\eta_1)(t-k - 1)}
-    \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}\\&= C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k-1)},
-\end{split}\end{equation}
+    \leq C_5|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
+    \\&\leq \frac{C_5}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
+    \\&\leq \frac{C_5}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta_0 - 3\eta_1)(t-k - 1)}
+    \\&\leq C_6 e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}
+    %\\&= C_6 e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k-1)},
+    \\&= C_6 e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)},
+\end{align}
     as desired in this step.
@@
     Step 3.
-    We will show that there exist $C, \delta> 0$ such that for $t$ large enough,
+    We will show that there exist $C_7, \delta_5> 0$ such that for $t$ large enough,
 \begin{equation}\label{domi-difference of Is}
     |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
-    \leq C t^{-\delta}.
-\end{equation}
-    In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C,\delta > 0$ such that
+    \leq C_7 t^{-\delta_5}.
+\end{equation}
+    In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C_8,\delta_6 > 0$ such that
     for all $k \geq 0$ and $t\geq k+1$ we have,
@@
     \tilde{\mathbb P}_\mu\big[|Y_{t,k}|\big]
-    \leq C e^{-\delta(t-k)}.
-\]
-    Therefore, there exist $C, \delta > 0$ and $C'$ such that for all $t \geq 1$,
-\begin{equation}\begin{split}
+    \leq C_8 e^{-\delta_6(t-k)}.
+\]
+   Therefore, there exists $C_9> 0$  such that for all $t \geq 1$,
+\begin{align}
     &\sum_{k=0}^{\lfloor t-\ln t \rfloor} \tilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
-    \leq C\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{-\delta(t-k)}
-    = C e^{-\delta t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta k}
-    \\&\leq C' e^{-\delta t}e^{\delta (t-\ln t)}
-    = C'\frac{1}{t^{\delta}}.
-\end{split}\end{equation}
+    \leq C_8\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{-\delta_6(t-k)}
+    %= C_8 e^{-\delta t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta_6 k}
+    = C_8 e^{-\delta_6 t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta_6 k}
+    %\\&\leq C_9 e^{-\delta t}e^{\delta_6 (t-\ln t)}
+    \\&\leq C_9 e^{-\delta_6 t}e^{\delta_6 (t-\ln t)}
+    = \frac{C_9}{t^{\delta_6}}.
+\end{align}
     Letting $t\to\infty$ in \eqref{domi-difference of Is}, we get \eqref{toprove-1}.
@@
     We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\tilde{P}}_{\mu}$.
-    In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C, \delta>0$ such that
-\begin{equation}\begin{split}
-    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<t^{-1/2})\leq C( t^{-\delta}+e^{-\delta t}), \quad t\geq0.
-\end{split}\end{equation}
-    Therefore, there exist $C, \delta>0$ such that
-\begin{equation}\begin{split}\label{Theorem123}
+    In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C_{10}, \delta_7>0$ such that
+\begin{equation}
+    %\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t}), \quad t\geq0.
+    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t}), \quad t\geq0.
+\end{equation}
+    Therefore, 
+\begin{equation}\label{Theorem123}
     |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
-    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C(t^{-\delta}+e^{-\delta t}),
+    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C_{10}(t^{-\delta_7}+e^{-\delta_7 t}),
     \quad t\geq t_0.
-\end{split}\end{equation}
+\end{equation}
     Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})\leq \frac{1}{2(1+\beta)}$.
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that
-\begin{align*}
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C_{11},C_{12},C_{13}>0$ such that
+\begin{align}
     &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
@@
     \\&\leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
-    \\& \leq C |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
-    \\ &\leq C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    &= C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})k}\\
-    &\leq C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})j}\\
-    &\leq C''|\theta| t^{-\frac{1}{2(1+\beta)}}t^{(\frac{\alpha}{1+\gamma}- \frac{\alpha}{1+\beta})},
+    \\& \leq C_{11} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
+    \\ &\leq C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    &= C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})k}\\
+    &\leq C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})j}\\
+    &\leq C_{13}|\theta| t^{-\frac{1}{2(1+\beta)}}t^{(\frac{\alpha}{1+\gamma}- \frac{\alpha}{1+\beta})},
     \quad t\geq t_0.
-\end{align*}
+\end{align}
 	From this and \eqref{Theorem123}, we get the desired result in this step.
@@
     In fact, we have
-\begin{equation}\begin{split}
+\begin{align}
 	&|I_3(t)|
@@
 	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
-\end{split}\end{equation}
+\end{align}
 
 	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{thm: critical clt}.
-
-\subsection{The small rate case}
-
-    In this subsection, we prove the central limit theorem for the small rate case.
-
-{\it Proof of Theorem \ref{thm: small clt}.}\quad
-    By assumption, $f\in \mathcal P$  and $\alpha \beta < \kappa_f b(1+\beta)$.
+\end{proof}
+
+\subsection{The small rate regime}
+\label{sec: small rate}
+
+    In this subsection, we prove the central limit theorem for the small rate regime.
+
+%{\it Proof of Theorem \ref{thm: small clt}.}\quad
+\begin{proof}[Proof of Theorem \ref{thm: small clt}]
+ By assumption, $f\in \mathcal P$ is non-trivial and satisfies $\alpha \beta < \kappa_f b(1+\beta)$.
 	Let $t_0 > 1$ be large enough so that
@@
 \]
-	We write
-\begin{align*}
+Fix $\mu\in \mathcal M_c(\mathbb R^d)$ and write
+\begin{align}
 	&\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
@@
 	\quad t\geq t_0.
-\end{align*}
+\end{align}
 	Define
@@
 \]
-    Let $\theta\in \mathbb R$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{corollary31},
-    we get that there exist $C,\delta > 0$ such that
-\begin{align*}
+    %Let $\theta\in \mathbb R$.
+    Fix a $\theta\in \mathbb R$.
+    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small},
+    we get that there exist $C_1,\delta_1 > 0$ such that
+\begin{align}
     \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde I'_1(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|
-    \leq C e^{-\delta(t - \lfloor t - \ln t\rfloor)}
-    \leq C \frac{1}{t^{\delta}},
+    \leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}
+    \leq \frac{C_1}{t^{\delta_1}},
     \quad t\geq 0.
-\end{align*}
+\end{align}
     Hence, according to \eqref{sum-m}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
@@
     Define for $k\geq 0$ and $t\geq k+1$,
-\begin{align*}
+\begin{align}
     Y'_{t,k}
     :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big).
-\end{align*}
+\end{align}
 	Then we have
-\begin{equation}\begin{split}
+\begin{equation}
 \label{ineq: control of I1tb}
@@
     \quad t\geq t_0.
-\end{split}\end{equation}
+\end{equation}
     Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
@@
 	Define $\mathcal D_{t,k}$ and $K_{t,k}$ as in \eqref{def: Dtk} and \eqref{def: Ktk} respectively.
-	Using Lemma \ref{lem: control of mgtrs}, \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and an argument similar to that used in proving \eqref{eq: control of Ykt}, we get that there exist $C,C',\delta>0$ such that for $k\geq 0$ and $t\geq k+1$,
-\begin{align*}
+	Using Lemma \ref{lem: control of mgtrs}, \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and an argument similar to that used in proving \eqref{eq: control of Ykt}, we get that there exist $C_2,C_3,\delta_2>0$ such that for $k\geq 0$ and $t\geq k+1$,
+\begin{align}
     &\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
@@
     \\& \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\tilde{P}}_{\mu}( \mathcal D_{t,k}^c )
-    \\& \leq C e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-(\eta_0 - 3\eta_1)(t-k)} + Ce^{-\delta(t-k)}
-    \\& \leq C'( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta(t-k)}).
-\end{align*}
+    \\& \leq C_2 e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-(\eta_0 - 3\eta_1)(t-k)} + Ce^{-\delta_2(t-k)}
+    \\& \leq C_3( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)}).
+\end{align}
     Since $\alpha\beta<\kappa_f(1+\beta)b$,  we have
-\begin{equation}\begin{split}
+\begin{align}
 \label{eq: condition for supercritical}
@@
     = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta})
+    %= \alpha(1-\frac{\gamma}{1+\gamma}) - \alpha(1-\frac{\beta}{1+\beta})
     \\&> \frac{\gamma \alpha}{1+\gamma} - k_f b
     =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
-\end{split}\end{equation}
-	Using this, we have that there exist $C,C',
-    \delta > 0$ such that for $k\geq 0$ and $t\geq k+1$,
-\begin{align*}
+\end{align}
+Using this, we have that there exist $C_4,
+    \delta_3 > 0$ such that for $k\geq 0$ and $t\geq k+1$,
+\begin{align}
     \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
-    & \leq C( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta(t-k)})
-    \\& \leq C'e^{-\delta (t-k)}.
-\end{align*}
+    & \leq C_3( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)})
+    \\& \leq C_4e^{-\delta_3 (t-k)}.
+\end{align}
     Now we can  use the  same argument used in the proof of Theorem \ref{thm: critical clt} to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
@@
 	A_t(\epsilon)
-	=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
+	%=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
+    :=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
 	\quad t\geq 0.
@@
 	According to \eqref{lem: control of XT}, there exist
-	$C,\delta>0$ such that
-	Therefore, there exists $C>0$ such that
-\begin{equation}\begin{split}
+$C_5,\delta_4>0$ such that
+\begin{align}
     &|\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
-    \leq 2\mathbb{\tilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<e^{-\epsilon t})
-    \\&\leq C(e^{-\epsilon\delta t}+e^{-\delta t}).
+    %\leq 2\mathbb{\tilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<e^{-\epsilon t})
+    \leq 2\mathbb{\tilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})
+    %\\&\leq C_5(e^{-\epsilon\delta_4 t}+e^{-\delta_4 t}).
+    \\&\leq C_5(e^{-\epsilon\delta_4 t}+e^{-\delta_4 t}),
     \quad t\geq t_0.
-\end{split}\end{equation}
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that for all
+\end{align}
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C_6,C_7,C_8>0$ such that for all
 	$t\ge t_0$,
-\begin{align*}
-    &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
-    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)^c}\big]
+\begin{align}
+    %&|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
+    &\big|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)}]\big|
+    %\leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)^c}\big]
+    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)}\big]
     \\&\leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
-    \\& \leq C  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
-    \\ &\leq C'  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta} + \frac{2\epsilon}{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{qt} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-qk}\\
-    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\leq C'' e^{-\frac{\epsilon}{1+\beta} t} t^q.
-\end{align*}
+    \\& \leq C_6  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
+    \\ &\leq C_7  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    &\leq C_7 e^{-\frac{\epsilon}{1+\beta} t}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta} + \frac{2\epsilon}{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    &\leq C_7 e^{-\frac{\epsilon}{1+\beta} t} e^{qt} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-qk}\\
+    &\leq C_7 e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\leq C_8 e^{-\frac{\epsilon}{1+\beta} t} t^q.
+\end{align}
 	Therefore, we get the desired result in this step.
@@
     In fact, we have
-\begin{equation}\begin{split}
+\begin{align}
 	&|I'_3(t)|
@@
 	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
-\end{split}\end{equation}
-	The proof is complete.
-\subsection{Proof of Theorem \ref{thm: large clt}}\label{large rate again}
-    In this subsection, we revisit the large branching rate case and prove Theorem \ref{thm: large clt}.
+    \qedhere
+\end{align}
+	%The proof is complete.
+\end{proof}
+%\subsection{Proof of Theorem \ref{thm: large clt}}
+\subsection{The large rate regime: CLT}
+\label{sec: large rate clt}
+    In this subsection, we revisit the large branching rate regime and prove Theorem \ref{thm: large clt}.
     For $g\in \mathcal{C}_l$, recall the definition of $I_tg$ in \eqref{definition of Itf}.
@@
 
-    Recall that $\Big\{\{H^p_t, \mathscr{F}_t\}_{t\geq 0};p\in \mathbb{Z}_+^d\Big\}$ is a family of martingales defined in Lemma \ref{lemma26}.
-
-\begin{lem}
-    For all $n>0$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$,
-\begin{align}
-    \bar{\gamma}_{t,n}:=\sum_{p\in\mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\bar{\zeta}_n,
-\end{align}
-    where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function
-\begin{align}
-    \mathbb{E}[e^{i\theta \bar{\zeta}_n}]=\exp[\bar{m}_n[\theta g]],\quad \theta\in \mathbb{R}.
+    %Recall that $\{H^p_t, \mathscr{F}_t\}_{t\geq 0}, p\in \mathbb{Z}_+^d,$ are defined before Lemma \ref{lemma26}.
+    Recall that $H^p_t$ are defined before Lemma \ref{lemma26}. We write $a_p:= \langle \phi_p, g\rangle_\varphi$ for each $p \in \mathbb Z_+^d$.
+
+\begin{lem}\label{large-central}
+    For all $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$,
+\begin{align}
+    \bar{\gamma}_{t,n}:=\sum_{p\in\mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}
+    %\xrightarrow{d}\bar{\zeta}_n,
+    \xrightarrow[t\to \infty]{d}\bar{\zeta}_n,
+\end{align}
+    %where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function
+    where $\bar{\zeta}_n$ is an $(1+\beta)$-stable random variable with characteristic function
+\begin{align}
+    %\mathbf{E}[e^{i\theta \bar{\zeta}_n}]=\exp[\bar{m}_n[\theta g]],\quad \theta\in \mathbb{R}.
+    \mathbf{E}[e^{i\theta \bar{\zeta}_n}]=\exp(\bar{m}_n[\theta g]),\quad \theta\in \mathbb{R}.
 \end{align}
@@
 \begin{proof}
+    %We fix $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$.
+    Fix $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$.
     We only need to show that
@@
     \mathbb{P}_{\mu}[\exp(i\bar{\gamma}_{t,n}); D^c]
-    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(\bar{m}_n[g]),
-    \quad \mu \in \mathcal M_c(\mathbb R^d), n \geq 0.
-\end{align}
-    Put $\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
+    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(\bar{m}_n[g]).
+\end{align}
+    Put $\theta_{t,p,n}:=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and 
+    %$A_t(\epsilon):=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
+    $A_t(\epsilon):=\{\|X_t\| > e^{(\alpha-\epsilon)t}\}$.
     We have
@@
 
-	Step 1. We will show that for any $\epsilon > 0, n\geq 0$, and $t\geq 0$, we have
+	Step 1. We will show that for all $\epsilon > 0, n\geq 1$, and $t\geq 0$, we have
 \begin{align}
@@
 	J'_1(t,n,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p, X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big],
+	%&:= \mathbb{P}_{\mu}\big[|\langle K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big],
+    &:= \mathbb{P}_{\mu}\big[|\langle Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big],
 	\\ J'_2(t,n,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big],\quad\mbox{and}
+	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big],
 	\\ J'_3(t,n, \epsilon)
@@
 \end{align}
-    It follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$ that
+    %It follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$ that
+    In fact, it follows from \eqref{eq: key equality} that
 \begin{align}
@@
     =\mathbb{P}_{\mu}[e^{i\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p,X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle)}|\mathscr{F}_{t+n-1}]
-    \\&=\displaystyle e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
+    %\\&=\displaystyle e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
+    \\&=\displaystyle e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
 \end{align}
@@
 \]
-    we have for all $n\geq 0, t\geq 0, \epsilon> 0$, 
+    %we have for all $n\geq 1, t\geq 0, \epsilon> 0$,
+    we have for all $n\geq 1, t\geq 0$ and $\epsilon> 0$,
 \begin{align}
@@
     \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}| \mathscr F_{t+n-1}]-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big] + J'_3(t,n,\epsilon)
-    \\&=\mathbb{P}_{\mu}\Big[\big|e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
-    \\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (k_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
+    %\\&=\mathbb{P}_{\mu}\Big[\big|e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
+    \\&=\mathbb{P}_{\mu}\Big[\big|e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
+    %\\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}
+    \\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}
+ \theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
     \\&\leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon).
@@
     Step 2.
-    We will show that for each $\epsilon$ small enough, there exist constants $C,\delta>0$ such that for all $n\geq 1, \, t\geq 0$, 
+    %We will show that for $\epsilon>0$ small enough, there exist constants $C_1,\delta_1>0$ such that for all $n\geq 1, \, t\geq 0$,
+    We will show that for $\epsilon>0$ small enough, there exist constants $C_1,\delta_1>0$ such that for all $n\geq 1$ and $t\geq 0$,
 \begin{align}\label{eq:large rate J1}
-    J'_1(t,n,\epsilon)\leq C e^{-\delta(t+n)}. %\quad n\geq 1, \, t\geq 0.
-\end{align}
-	In fact, let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the $(\theta^{1+\beta}\vee \theta^{1+\beta+\delta_0})$-controller. Then we have
-	for all $n\geq 0, t\geq 0, \epsilon > 0$, 
-\begin{align}
-    & |K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
+    J'_1(t,n,\epsilon)\leq C_1 e^{-\delta_1(t+n)}.
+\end{align}
+	%Let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the $(\theta^{1+\beta}\vee \theta^{1+\beta+\delta_0})$-controller. 
+    Let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
+    Then we have for all $n\geq 1, t\geq 0, \epsilon > 0$,
+\begin{align}
+    %& |K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
+    & |Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
     \leq R(|\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p|)\mathbf{1}_{A_{t+n-1}(\epsilon)}
     \\&\leq R \Big(\frac{\sum_{p\in\mathcal{N}}|a_p|e^{-(\alpha-|p|b)n}|\phi_p|}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)
-    \\&\leq \sum_{\rho\in\{\delta_0,1\}}\Big(\frac{e^{-(\alpha-Kb)n}}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)^{1+\beta+\rho}R|h|
-    \\&=\sum_{\rho\in\{\delta_0,1\}}e^{-\alpha\frac{1+\beta+\rho}{1+\beta}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha\beta-K(1+\beta)b)n}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}S|h|
-    \\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|,
+    %\\&\leq \sum_{\rho\in\{\delta_0,1\}}\Big(\frac{e^{-(\alpha-Kb)n}}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)^{1+\beta+\rho}R|h|
+    \\&\leq \sum_{\rho\in\{\delta_0,1\}}\Big(\frac{e^{-(\alpha-Kb)n}}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)^{1+\beta+\rho}Rh
+    %\\&=\sum_{\rho\in\{\delta_0,1\}}e^{-\alpha\frac{1+\beta+\rho}{1+\beta}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha\beta-K(1+\beta)b)n}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|
+    \\&=\sum_{\rho\in\{\delta_0,1\}}e^{-\alpha\frac{1+\beta+\rho}{1+\beta}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha\beta-K(1+\beta)b)n}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}Rh
+    %\\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|,
+    \\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}Rh,
 \end{align}
     where $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-    Thus for all $n\geq 0,  t\geq 0, \epsilon > 0$,
+    %Thus for all $n\geq 1,  t\geq 0, \epsilon > 0$,
+    Thus, there exists constant $C_3>0$ such that for all $n\geq 1,  t\geq 0$ and $\epsilon > 0$,
 \begin{align}
@@
      \leq  \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle R|h|,X_{t+n-1}\rangle]\\
-     & \leq C\sum_{\rho\in\{\delta_0,1\}}\exp\Big\{-\Big(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta}\Big)(t+n-1)\Big\}.
-\end{align}
+     & \leq C_1\sum_{\rho\in\{\delta_0,1\}}\exp\Big\{-\Big(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta}\Big)(t+n-1)\Big\}.
+\end{align}
+%ADDED
+    By choosing $\epsilon>0$ small enough, we get the desired result in this step.
+%END ADDED
 
     Step 3.
-	We will show that for each $\epsilon$ small enough, there exist constant $C,\delta>0$ such that for all $n\geq 1, t\geq 0$, 
+	%We will show that for each $\epsilon$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$,
+    We will show that for each $\epsilon > 0$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$,
 \begin{align}
@@
     J'_2(t,n,\epsilon)
-    \leq C e^{-\delta(t+n)}.
+    \leq C_2 e^{-\delta_2(t+n)}.
 \end{align}
@@
 \end{align}
-Therefore, for all $t\geq 0, n\geq1$, 
+    %Therefore, for all $t\geq 0, n\geq1$,
+    Therefore, for all $t\geq 0, n\geq1$ and $\epsilon > 0$,
 \begin{align}
@@
 \end{align}
-    Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment}.(3) with $\kappa=1$, there exists $C>0$ such that
+%ADDED
+    Fix a $\gamma>0$ small enough such that $\alpha \gamma < (1+\gamma)b$.
+%END ADDED
+    Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment}.(3) with $\kappa=1$, there exists $C_3>0$ such that
 \begin{align}
     \mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]
-    \leq Ce^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
-\end{align}
-    Therefore, for all $t\geq 0, n\geq1$, 
+    %\leq C_3e^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
+    \leq C_3e^{\frac{\alpha}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
+\end{align}
+    %Therefore, for all $t\geq 0, n\geq1$,
+    Therefore, for all $t\geq 0, n\geq1$ and $\epsilon >0$,
 \begin{align}
     &J'_2(t,n,\epsilon)\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]\\
-    &\leq C e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)}\\
-    &=Ce^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}\\&\leq Ce^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}.
-\end{align}
-	Step 4. Using an argument similar to that used in Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we can show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
+    &\leq C_3 e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)}\\
+    &=C_3e^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}\\&\leq C_3e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}.
+\end{align}
+%ADDED
+    Now, by choosing $\epsilon >0$ small enough, we get the desired result in this step.
+%END ADDED
+
+	%Step 4. Using an argument similar to that used in Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we can show that for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that
+    Step 4. According to the Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that
 \begin{align}\label{ineq: control of J31}
-    J'_3(t,n,\epsilon)\leq Ce^{-\delta (t+n)}\quad t\geq0, n\geq 1.
+    J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}\quad t\geq0, n\geq 1.
 \end{align}
@@
 
-\begin{lem}\label{lem:lemma03}
+\begin{lem}\label{lem: independency for large rate}
     For all $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
 \begin{align}\label{ineq: next we will need}
-    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\prod_{n=1}^m\exp(i\theta\bar{\gamma}_{t,n})-\prod_{n=1}^m\exp(\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t}.
+    %\Big|\tilde{\mathbb{P}}_{\mu}\Big[\prod_{n=1}^m\exp(i\theta\bar{\gamma}_{t,n})-\prod_{n=1}^m\exp(\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t}.
+    \bigg|\tilde{\mathbb{P}}_{\mu}\Big[\prod_{l=1}^m\exp(i\theta\bar{\gamma}_{t,l})-\prod_{l=1}^m\exp(\bar{m}_l[\theta g])\Big]\bigg|\leq C e^{-\delta t}.
 \end{align}
@@
 \begin{proof}
-    Step 1.
-Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  for all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that, for any $t\geq 0$, $n\geq 1$, we have
-\begin{align}
-    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]\leq Ce^{-\delta(t+n-1)}.
+    %Step 1. 
+    Step 1. Fix $\theta \in \mathbb R$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
+    Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  for all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C_1,\delta_1>0$ such that, for any $t\geq 0$, $n\geq 1$, we have
+\begin{align}
+    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]\leq C_1e^{-\delta_1(t+n-1)}.
 \end{align}
@@
     Step 2.
-    Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$.
-    For each $n=1,\cdots,m$, we define
-    \[\tilde{a}_n:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big),\] where by convention the product is $1$ for $n=0$.
-Then we get for each $n > 0$,
-\begin{align*}
+    %Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$.
+    Fix $t\geq 0$ and $m\in \mathbb{N}$.
+    %For each $n=1,\cdots,m$, we define
+    For each $n=0,\cdots,m$, we define
+\[
+    \tilde{a}_n
+    %:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big),
+    :=\mathbb{\tilde{P}}_{\mu}\Big[\prod_{l=0}^{n}\exp(i\theta\bar{\gamma}_{t,l})\Big] \times \prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g]),
+\] 
+    %where by convention the product is $1$ for $n=0$. Then we get for each $n \ge 1$,
+    where by convention the first product is $1$ for $n=0$. Then we get for each $n \ge 1$,
+\begin{align}
     &\tilde{a}_{n-1} - \tilde{a}_n
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\Big(e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}}\Big);D^c\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
-\end{align*}
-    According to Step 1 and Proposition \ref{cor: alpha stable rv 1}, there exist $C,\delta>0$ such that for any $n=1,\cdots, m$ and $t\geq0$, we have
-\begin{align*}
+    %\\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\Big(e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}}\Big);D^c\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
+    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times (e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}});D^c\Big] \times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
+    %\\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
+    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times \mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
+\end{align}
+    According to Step 1 and Proposition \ref{prop: alpha stable rv},
+    there exist $C_2>0$ such that for any $n=1,\cdots, m$ and $t\geq0$, we have
+\begin{align}
     |\tilde{a}_{n-1}- \tilde{a}_n|
     &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
-    \\& \leq C e^{-\delta(t+n-1)}.
-\end{align*}
+    \\& \leq C_2 e^{-\delta_1(t+n-1)}.
+\end{align}
     Therefore,
@@
     \leq\sum_{n=1}^m\left|\tilde{a}_{n-1}-\tilde{a}_n\right|
-    \leq \sum_{n=1}^m C e^{-\delta(t+n-1)}.
-\end{align}
-	Notice that $C, \delta>0$ are independent of the choice of $t\geq 0$, $m\in \mathbb{N}$.
+    \leq \sum_{n=1}^m C_2 e^{-\delta_1(t+n-1)}.
+\end{align}
+	Notice that $C_2, \delta_1>0$ are independent of the choice of $t\geq 0$, $m\in \mathbb{N}$.
 \end{proof}
@@
 \begin{proof}
+%ADDED
+    Fix a $\theta \in \mathbb R$ and a $\mu \in \mathcal M_c(\mathbb R^d)$.
+%END ADDED
     According to \cite[Lemma 3.4.3]{Durrett2010Probability},
@@
     Y''_{t,n}
-    :=e^{i\theta\tilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},\quad t\geq 0, n\geq 1, \theta\in \mathbb{R}.
+    :=e^{i\theta\tilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},
+    %\quad t\geq 0, n\geq 1, \theta\in \mathbb{R}.
+    \quad t\geq 0, n\geq 1.
 \end{align}
@@
     \alpha\gamma
-    >K(1+\gamma)b.
-\]
+    >K(1+\gamma)b,
+\]
+	where $K=\sup\{k\in \mathbb N:~\alpha\beta>k(1+\beta)b\}$.
     Fix this $\gamma$, and then choose $\eta_0,\eta_1>0$ such that
@@
 
-    Step 1. Similar to Step 1 in the proof of Theorem \ref{thm: critical clt}, we can show that there exist constants $C,\delta >0$ such that for all $n \geq 1$ and $t\geq 0$,
+    Step 1. Similar to Step 1 in the proof of Theorem \ref{thm: critical clt}, we can show that there exist $C_1,\delta_1 >0$ such that for all $n \geq 1$ and $t\geq 0$,
 \begin{align}
@@
     \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}^c_{t,n}}\big]
-    \leq C e^{-\delta t}.
-\end{align}
-\begin{comment}
-    In fact, let $C_1$ be the constant in  Lemma 2.9 corresponding to this fixed $\gamma$ and $C_2$ be the constant in Lemma 2.10.
-    By Chebyshev's inequality, there exists $C>0$ such that for all $n \geq 1$ and $t\geq 0$,
-\begin{align}
-\label{eq: prob of Dtkc11}
-    &\mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,n}^c)
-    \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t+n-1}| > e^{-\eta_0 t})+\mathbb{\tilde{P}}_{\mu}(H_{t}\leq 2e^{-\eta_1 t}),
-    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0 t}\mathbb{P}_{\mu}[|H_t-H_{t+n-1}|]+\mathbb{\tilde{P}}(H_t\leq 2e^{-\eta_1 t})
-    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0 t}\|H_t - H_{t+n-1}\|_{\mathbb P_\mu; 1+\gamma}+\mathbb{\tilde{P}}(H_{t}\leq 2e^{-\eta_1t})
-    \\&\leq C_1  \mathbb{P}_{\mu}(D^c)^{-1}  e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)t}+C_2 e^{-\eta_1\beta t}.
-\end{align}
-    This implies the desired result in this step, since $|Y_{t,k}| \leq 2$ a.s..
-\end{comment}
-
-    Step 2. We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta > 0$ such that for all $n\geq 1$ and $t\geq 0$,
+    \leq C_1 e^{-\delta_1 t}.
+\end{align}
+
+    Step 2.
+    %We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C_2,\delta_2 > 0$ such that for all $n\geq 1$ and $t\geq 0$,
+    We will show that there exist $C_2,\delta_2 > 0$ such that for all $n\geq 1$ and $t\geq 0$,
 \begin{align}
 \label{thm12211}
-    \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq Ce^{-\delta t}.
+    \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq C_1e^{-\delta_2 t}.
 \end{align}
@@
 \end{align}
-\begin{comment}
-
-     Note that, since $\eta_1 < \eta_0$, we have
-\begin{align*}
-    H_{t+n-1}
-    &\geq H_{t}- e^{-\eta_0 t}
-    \geq 2e^{-\eta_1t}-e^{-\eta_0 t}
-    \\&\geq e^{-\eta_1 t},
-    \quad \text{ on } \mathcal D_{t,n}.
-\end{align*}
-    Therefore, for each $t \geq 0$ and $n\geq 1$,
-\begin{align*}
-     &\Big|H_t^{\frac{1}{1+\beta}}-H_{t+n-1}^{\frac{1}{1+\beta}}\Big|
-     \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t+n-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t+n-1}\right|,
-    \\&\leq \frac{1}{1+\beta} \max\{e^{\eta_1 t}, \frac{1}{2}e^{\eta_1 t}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0 t}
-    \\&\leq \frac{1}{1+\beta} e^{\eta_1 t} e^{-\eta_0 t}
-    =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1) t},
-    \quad \text{ on } \mathcal D_{t,n},
-\end{align*}
-    and
-\begin{align*}
-    |H_t^{\frac{1}{1+\beta}}H_{t+n-1}^{\frac{1}{1+\beta}}|
-    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1t},
-    \quad \text{ on } \mathcal D_{t,n}.
-\end{align*}
-\end{comment}
-
-    Since $\eta_1 < \eta_0$,  using similar arguments used in  step 2 of the proof of Theorem \ref{thm: critical clt}, we can show that, there is a constant $C\geq 0$ such that,
+Since $\eta_1 < \eta_0$,  using similar arguments used in  step 2 of the proof of Theorem \ref{thm: critical clt}, we can show that, there is a constant $C_3> 0$ such that,
 \begin{align}
@@
      K'_{t,n}
-     \leq C e^{-(\eta_0 - 3\eta_1) t},
+     \leq C_3 e^{-(\eta_0 - 3\eta_1) t},
      \quad t \geq 0, n\geq 1.
 \end{align}
-    According to Lemma \ref{lem: control of wt},
-    there exist constants $C,C',C''>0$ such that  for all $t\geq 0$ and $n\geq 1$,
+    %According to Lemma \ref{lem: control of wt}, there exist constants $C_4,C_5>0$ such that  for all $t\geq 0$ and $n\geq 1$,
+    According to Lemma \ref{lem: control of wt}, there exist constants $C_4>0$ such that  for all $t\geq 0$ and $n\geq 1$,
 \begin{align}\label{ineq:used next 2}
-    &\tilde{\mathbb{P}}_{\mu}\big[|Y_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq \frac{C}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\mathbb{P}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\Big]\\
-    &\leq \frac{C}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}
-    \\&\leq C' |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
-    &=C'|\theta|\sum_{p\in\mathcal{N}}|a_p|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}\cdot e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(n-1)}.\\
-    &\leq C''|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}.
+    &\tilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]
+    \leq \frac{C_3}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\mathbb{P}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\Big]\\
+    &\leq \frac{C_3}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}
+    \\&\leq C_4|\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
+    &=C_4|\theta|\sum_{p\in\mathcal{N}}|a_p|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}\cdot e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(n-1)}.
+ %DELETED   
+    %\\&\leq C_5|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}.
+%END DELETED
 \end{align}
@@
 
-    Combining \eqref{ineq: used next 3} with Steps 1-2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
+    Combining \eqref{ineq: used next 3} with Steps 1-2, we get the result immediately. Notice that $\delta$ is independent of $m$ and $t$.
 \end{proof}
@@
 \begin{proof}
-    Recall that $A_t(\epsilon)=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C,\delta>0$ such that for all $t\geq 0$
+%ADDED
+    Fix $\theta \in \mathbb R$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\epsilon \in (0,\alpha)$ and $\gamma \in (0,\beta)$ with $\alpha \gamma > Kb(1+\gamma)$.
+%END ADDED
+    %Recall that $A_t(\epsilon)=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. 
+    Recall that $A_t(\epsilon):=\{\|X_t\|> e^{(\alpha-\epsilon) t}\}$. 
+    According to Proposition \ref{lem: control of XT}, there exist $C_1,\delta>0$ such that for all $t\geq 0$ and $m\in \mathbb N$,
 \begin{align}\label{ineq: control of gamma_t on dc}
@@
     \leq 2\tilde{P}_{\mu}(A_t(\epsilon)^c)
-    \leq C e^{-\delta t}.
-\end{align}
-    Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ with $\alpha\gamma>Kb(1+\gamma)$.  According to Lemma \ref{lem: control of wt}, there exist $C,C'>0$ such that
+    \leq C_1 e^{-\delta t}.
+\end{align}
+%DELETED
+    %Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ with $\alpha\gamma>Kb(1+\gamma)$.  
+%END DELETED
+    According to Lemma \ref{lem: control of wt}, there exist $C_2,C_3>0$ such that
 \begin{align}\label{ineq: control of gamma_t on d}
@@
     &\leq  \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}\\
-    &\leq C|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
-    &\leq C'|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m}.\\
-    & \qquad\theta\in\mathbb{R}, m\in \mathbb{N}, \epsilon>0, t\geq 0.
+    &\leq C_2|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
+    &\leq C_3|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m},
+    %& \qquad\theta\in\mathbb{R}, m\in \mathbb{N}, \epsilon>0, t\geq 0.
+    \qquad m\in \mathbb{N}, t\geq 0.
 \end{align}
@@
 \bigskip
-{\it Proof of Theorem \ref{thm: large clt}.}\quad
-    Let $\delta_0$ be the constant $\delta$ in Lemma \ref{lem: lemma04}.  Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$. 
+
+%{\it Proof of Theorem \ref{thm: large clt}.}\quad
+\begin{proof}[Proof of Theorem \ref{thm: large clt}]
+%ADDED
+    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta \in \mathbb R$.
+%END ADDED
+    Let $\delta_0$ be the constant $\delta$ in Lemma \ref{lem: lemma04}.  
+    Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$.
     First note that for $t\ge 0$,
@@
 \end{align}
-    According to Lemma \ref{lem:lemma03}, there exist $C,\delta>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$, 
+    %According to Lemma \ref{lem: independency for large rate}, there exist $C_1,\delta_1>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$,
+    According to Lemma \ref{lem: independency for large rate}, there exist $C_1,\delta_1>0$ such that for all $t\geq 0$,
 \begin{align}\label{ineq: last1}
     \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]
-    \Big|\leq C e^{-\delta t}.
-\end{align}
-    According to Lemma \ref{lem: lemma04}, there exists $C>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$, 
+    \Big|\leq C_1 e^{-\delta_1 t}.
+\end{align}
+    %According to Lemma \ref{lem: lemma04}, there exists $C_2>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$,
+    According to Lemma \ref{lem: lemma04}, there exists $C_2>0$ such that for all $t\geq 0$,
 \begin{align}\label{ineq: last2}
-    \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C  e^{-\frac{\delta_0}{2} t}.
- \end{align}
-    According to Lemma \ref{lem: lemma05}, there exist $C,\delta_1,\delta_2>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$, 
+    \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C_2  e^{-\frac{\delta_0}{2} t}.
+ \end{align}
+    %According to Lemma \ref{lem: lemma05}, there exist $C_3,\delta_2,\delta_3>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$,
+    According to Lemma \ref{lem: lemma05}, there exist $C_3,\delta_2,\delta_3>0$ such that for all $t\geq 0$,
 \begin{align}\label{ineq: last3}
-    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 e^{\frac{\delta_0}{2}t}}).
+    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C_3(e^{-\delta_2 t}+e^{\delta_2 t}e^{-\delta_3 e^{\frac{\delta_0}{2}t}}).
 \end{align}
@@
     Combining \eqref{decompose},\eqref{ineq: last1}, \eqref{ineq: last2} and \eqref{ineq: last3}, and letting $t\to\infty$, we get the desired result of Theorem \ref{thm: large clt}.
+\end{proof}
+
 \appendix
-\section{}
+\section{ }
 
@@
     Then
-\begin{equation}\begin{split}
+\begin{align}
     &\Big|e^{-z} - \sum_{k=0}^{m+1} \frac{(-z)^k}{k!}\Big|
@@
     = \frac{|z|^{m+2}}{(m+2)!} \wedge \frac{2|z|^{m+1}}{(m+1)!},
-\end{split}\end{equation}
+\end{align}
     which says that \eqref{eq: estimate of exponential remaining} is true for $n = m + 1$.
-    The proof is complete.
+%DELETED    
+    %The proof is complete.
+%END DELETED
 \end{proof}
@@
     It follows from Lemma \ref{lem: estimate of exponential remaining} that $h$ and $h'$ are well defined on $\mathbb C_+$.
-    According to \cite[Theorems 3.2. \& 3.5]{SchillingSongVondravcek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
+   According to \cite[Theorems 3.2. \& Proposition 3.6]{SchillingSongVondravcek2010Bernstein}, 
+    $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
 
@@
     $y>0$,
-\begin{equation}\begin{split}
+\begin{align}
     &\Big| \frac{e^{-zy} - e^{-z_0 y}+(z-z_0) y}{z-z_0} \Big|
@@
     \leq C(y\wedge y^2).
-\end{split}\end{equation}
+\end{align}
     Using this and the dominated convergence theorem, we have
-\begin{equation}\begin{split}
+\begin{align}
     &\frac{h(z)-h(z_0)}{z-z_0} = \int_{(0,\infty)} \frac{e^{-zy}+zy -(e^{-z_0 y}+z_0 y)}{z-z_0}  \pi(dy)
     \\&\xrightarrow[\mathbb C_+\ni z\to z_0]{} \int_{(0,\infty)}(1 - e^{-z_0 y} )y\pi(dy) = h'(z_0),
-\end{split}\end{equation}
+\end{align}
     which says that $h$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
@@
 	Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic in $\mathbb C\setminus (-\infty,0]$. (We use the convention that  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
-    Using  the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
+    %Using  the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
+    Using the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg (z_1) + \arg(z_0)$.
 
@@
 	Using this recursively, one gets that
-\begin{equation}\begin{split}
+\begin{equation}
 \label{eq: definition of Gamma function}
@@
     \quad -n< x< -n+1, n\in \mathbb N.
-\end{split}\end{equation}
+\end{equation}
 
@@
     Notice that
-\begin{equation}\begin{split}
+\begin{equation}
 \label{eq: upper bound for beta power of z}
@@
 	\quad z \in \mathbb C\setminus (-\infty, 0].
-\end{split}\end{equation}
+\end{equation}
     Define a path $\gamma: [0,1] \to \mathbb C^0_+$ such that
@@
     Then, we have
-\begin{equation}\begin{split}
+\begin{align}
     |z_0^{1+\beta} - z_1^{1+\beta}|
@@
     \qedhere
-\end{split}\end{equation}
+\end{align}
 \end{proof}
@@
  	This distinguished logarithm should not be confused with the $\log$ function defined on $\mathbb C\setminus (-\infty, 0]$.
+ 	See the paragraph immediately after \cite[Lemma 7.6]{Sato2013Levy}.
 
@@
     In this subsection we give a version of the Feynman-Kac formula with complex valued functions.
-    Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact seperable metric space $E$.
+    Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact separable metric space $E$.
     We write
@@
 \begin{lem}
+\label{eq: complex FK}
     Let $t \geq 0$. Suppose that
@@
 \begin{equation}
+\label{eq: expresion of g}
     g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
 \end{equation}
-    is the unique solution to the equation
+    %is the unique solution to the equation
+    is the unique locally bounded solution to the equation
 \[
@@
 \begin{proof}
-    The proof is similar to the proof of \cite[Lemma A.1.5]{Dynkin1993Superprocesses}. We include it here for the sake of completeness.
+    The proof is similar to that of \cite[Lemma A.1.5]{Dynkin1993Superprocesses}. We include it here for the sake of completeness.
+%ADDED
+    We first verify that \eqref{eq: expresion of g} is a solution.
+%END ADDED
     Notice that
-\begin{equation}\begin{split}
+\begin{equation}
    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t)| ~ds \Big]
@@
     < \infty.
-\end{split}\end{equation}
+\end{equation}
     Also notice that
@@
     Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
-\begin{equation}\begin{split}
+\begin{align}
     &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}~(\rho_2 g)(s,\xi_s)~ds \Big]
@@
     \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\rho_2)} f(\xi_t)].
-\end{split}\end{equation}
+\end{align}
     For uniqueness, suppose  $\tilde g$ is another solution. Put $h(r) = \sup_{x\in E}|g(r,x) - \tilde g(r,x)|$. Then
 \[
-    h(r) \leq e^{t\|\alpha\|_\infty}\|\rho\|_\infty \int_r^t h(s)ds,
+   h(r) \leq e^{t\|\rho_1\|_\infty}\|\rho_2\|_\infty \int_r^t h(s)ds,
     \quad r\le t.
 \]
-    According to \cite[Lemma A.1.5]{Dynkin1993Superprocesses}, this says that $h(r) =  0$ for $r\in [0,t]$.
+Applying Gronwall's inequality, we get that $h(r) =  0$ for $r\in [0,t]$.
 \end{proof}
@@
     Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the weak topology.
+%ADDED
+    For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$, we use the following convention in this subsection:
+\[
+    F(x,f):= F(x,f(x)),\quad x\in E.
+\]
+%END ADDED
     A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
@@
     \psi(x,z)=
-    -rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
+    -\rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
 \end{equation}
@@
     $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
-\begin{equation}\begin{split}
+\begin{equation}
     \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
     \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
-\end{split}\end{equation}
+\end{equation}
     where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
-\begin{equation}\begin{split}\label{eq:FKPP_in_definition}
+\begin{equation}\label{eq:FKPP_in_definition}
     V_tf(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi(\xi_s,V_{t-s}f)ds \Big]
@@
     \quad t \geq 0, x \in E.
-\end{split}\end{equation}
+\end{equation}
 \end{itemize}
-    We refer our reader to \cite{Li2011Measure-valued} for more discussions about the definition and the existence of superprocesses.
+    We refer our readers to \cite{Li2011Measure-valued} for more discussions about the definition and the existence of superprocesses.
     To avoid triviality, we assume that
@@
 \begin{equation}
-    \psi'(x,z):= - \rho_(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
+    %\psi'(x,z):= - \rho_(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
+    \psi'(x,z):= - \rho_1(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
     \quad x\in E, z\in \mathbb C_+.
@@
 \item
-    $\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$;
+    %$\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$;
+    $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
 \item
@@
 \label{sec: definition of vf}
-    Let $X$ be a non-presistent superprocess with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
+    Let $X$ be a non-persistent superprocess with its Kuznetsov measure denoted by $(\mathbb N_x)_{x\in E}$.
     We define the mean semigroup
@@
 \label{eq: mean formula for superprocesses}
-    \mathbb N_{\mu}[W_t(f)]
-    =\mathbf P_{\mu}[X_t(f)]=
-       \mu(P^{\rho_1}_t f).
+   \mathbb N_{\mu}[\langle W_t, f\rangle]    
+   =\mathbf P_{\mu}[\langle X_t, f\rangle]
+   =\mu(P^{\rho_1}_t f).
 \end{equation}
@@
     Define
-\begin{equation}\begin{split}
+\begin{align}
     L_1(\xi)
@@
     &:= \{f \in \mathcal B(E): |f|^2 \in L_1(\xi)\}.
-\end{split}\end{equation}
+\end{align}
     Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
 \begin{equation}
-    \mathbb N_x[W_t(f)]
-    =\mathbf P_{\delta_x}[X_t(f)]=P^{\rho_1}_t f(x) \in \mathbb R,
+   \mathbb N_x[\langle W_t, f\rangle]   
+    %=\mathbf P_{\delta_x}[X_t(f)]
+    =\mathbf P_{\delta_x}[\langle f, X_t\rangle]
+    =P^{\rho_1}_t f(x) \in \mathbb R,
     \quad f\in L_1(\xi), t > 0,x\in E.
 \end{equation}
-    This says that the random variable $X_t(f)$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
-    According to the branching property of the superprocess, its is an infinitely divisible random variable.
+    This says that the random variable $\langle X_t, f\rangle$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
+    By the branching property of the superprocess, $\langle X_t, f\rangle$ is an infinitely divisible random variable.
     Therefore, we can write
 \[
-    U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}],
+    U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta \langle X_t, f\rangle}],
     \quad t\geq 0, f\in L_1(\xi), \theta \in \mathbb R, x\in E,
@@
 \[
-    \mathbf P_{\delta_x} [e^{i\theta X_t(f)}]
-    = \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]),
+    \mathbf P_{\delta_x} [e^{i\theta \langle X_t, f\rangle}]
+    = \exp(\mathbb N_x[ e^{i\theta \langle W_t, f\rangle} - 1]),
     \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
 \]
-    Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
+    Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta \langle W_t, f\rangle} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
 \begin{equation}
 \label{eq: N and characteristic exponent}
-    U_t(\theta f)(x) = \mathbb N_x[e^{i W_t(\theta f)} - 1],
+    U_t(\theta f)(x) = \mathbb N_x[e^{i \langle W_t, \theta f\rangle} - 1],
     \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
@@
     There exists constants $C\geq 0$ such that for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
-\begin{equation}\begin{split}
+\begin{equation}
 \label{eq: upper bound of psi(v)}
@@
          C (P^{\rho_1}_t |f| (x))^2.
-\end{split}\end{equation}
+\end{equation}
 \end{lem}
@@
     = |e^{U_tf(x)}|
-    = |\mathbf P_{\delta_x}[e^{i X_t(f)}]|
+    = |\mathbf P_{\delta_x}[e^{i \langle X_t, f\rangle}]|
     \leq 1,
@@
 \label{eq: upper bound for vf}
-    |U_tf(x)| \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
-    \leq \mathbb N_x[|i W_t(f)|]
+    |U_tf(x)| \leq \mathbb N_x[|e^{i \langle W_t, f\rangle} - 1|]
+    \leq \mathbb N_x[|i \langle W_t, f\rangle|]
     \leq (P^{\rho_1}_t |f|)(x).
@@
 \label{eq: estimate of deriavetive of v(theta)}
-    \mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
-    \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta|
+    \mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta \langle W_t, f\rangle} - 1) \Big|\Big]
+    \leq \mathbb N_x[|\langle W_t, f\rangle|] \sup_{\theta \in K}|\theta|
     \leq (P^{\rho_1}_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
 \end{equation}
-    Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent},
+    Therefore, according to \cite[Theorem A.5.2]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent},
     $U_t(\theta f)(x)$ is differentiable in $\theta \in \mathbb R$ with
@@
     \frac{\partial}{\partial \theta} U_t(\theta f)(x)
-    = i\mathbb N_x[W_t(f)e^{i\theta W_t(f)}],
+    = i\mathbb N_x[\langle W_t, f\rangle e^{i\theta \langle W_t, f\rangle}],
     \quad \theta \in \mathbb R.
@@
 \end{equation}
-    It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
+    %It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
+    It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_t(\theta f)(x)$ is continuous in $\theta$.
     In other words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
@@
     Notice that
-\begin{equation}
+\begin{align}
 \label{eq: upper bound of psi'(v)}
-\begin{split}
     &|\psi'(x, -U_tf)|
     \\&= \Big| -\rho_1(x)- 2\rho_2(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
-    \\&= \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi(x,dy) \Big|
-    \\ &\leq \|\rho_1\|_\infty + 2\rho(x)_2\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
+    \\&= \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i \langle W_t, f\rangle} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i \langle X_t, f\rangle}] \pi(x,dy) \Big|
+    %\\ &\leq \|\rho_1\|_\infty + 2\rho(x)_2\mathbb N_x[\langle W_t, |f|\rangle]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge \langle X_t, |f|\rangle] \pi(x,dy)
+    \\ &\leq \|\rho_1\|_\infty + 2\rho_2(x)\mathbb N_x[\langle W_t, |f|\rangle]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge \langle X_t, |f|\rangle] \pi(x,dy)
     \\ &\leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty
@@
     \\ &=: C_1 + C_2(P^{\rho_1}_t |f|)(x),
-\end{split}
-\end{equation}
+\end{align}
     where $C_1, C_2$ are constants independent on $f,x$ and $t$.
-    Now, ucombining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we get the desired result.
+    Now, combining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we get the desired result.
 \end{proof}
@@
     In fact, using Jensen's inequality and the Markov property, we have
-\begin{equation}\begin{split}
+\begin{align}
 \label{eq: domination of psi(v)}
@@
     \\ &\leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\rho_1\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
-\end{split}\end{equation}
-
-\subsection{}
+\end{align}
+
+\subsection{A complex-valued non-linear integral equation}
     Let $X$ be a non-persistent superprocess.
@@
 
-    To prove this, we will need the generalized spine decomposition theorem from \cite{RenSongSun2017Spine} which we now recall.
-    Let $X$ be the non-persistent superprocess.
+    To prove this, we will need the generalized spine decomposition theorem from \cite{RenSongSun2017Spine}. 
     Let $f\in \mathcal B_b(E,\mathbb R_+)$, $T >0$ and $x\in E$.
-    Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
-\begin{equation}
-    d\mathbf P_{\delta_x}^{X_T(f)}
-    := \frac{X_T(f)}{P_T^{\rho_1} f(x)} d\mathbf P_{\delta_x};
-    \quad d\mathbb N_x^{W_T(f)}
-    :=  \frac{W_T(f)}{P_T^{\rho_1} f(x)} d\mathbb N_x.
-\end{equation}
-    Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{W_T(f)}$ if
+    Suppose that $\mathbf P_{\delta_x}[\langle X_T, f\rangle] = \mathbb N_x[\langle W_T, f\rangle] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
+\begin{equation}
+    d\mathbf P_{\delta_x}^{\langle X_T, f\rangle}
+    := \frac{\langle X_T, f\rangle}{P_T^{\rho_1} f(x)} d\mathbf P_{\delta_x};
+    \quad d\mathbb N_x^{\langle W_T, f\rangle}
+    :=  \frac{\langle W_T, f\rangle}{P_T^{\rho_1} f(x)} d\mathbb N_x.
+\end{equation}
+    Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{\langle W_T, f\rangle}$ if
 \begin{itemize}
@@
     $\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M(E)$-valued process defined by
-\begin{equation}\begin{split}
+\begin{equation}
     Y_t
@@
     \quad 0 \leq t\leq T.
-\end{split}\end{equation}
+\end{equation}
 \end{itemize}
     According to the spine decomposition theorem in \cite{RenSongSun2017Spine}, we have that
-\begin{equation}\begin{split}
+\begin{equation}
 \label{eq: Spine decomposition 1}
-    \{(X_s)_{s \geq 0};\mathbf P_{\delta_x}^{X_T(f)}\}
-    \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{W_T(f)} \}
-\end{split}\end{equation}
+    \{(X_s)_{s \geq 0};\mathbf P_{\delta_x}^{\langle X_T, f\rangle}\}
+    \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{\langle W_T, f\rangle} \}
+\end{equation}
     and
-\begin{equation}\begin{split}
+\begin{equation}
 \label{eq: Spine decomposition 2}
-    \{(W_s)_{0\leq s\leq T};\mathbb N_x^{W_T(f)}\}
+    \{(W_s)_{0\leq s\leq T};\mathbb N_x^{\langle W_T, f\rangle}\}
     \overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
-\end{split}\end{equation}
+\end{equation}
 
@@
     Assume that $f\in \mathcal B_b(E)$.
-    Fix $t>0, r\in [0,t), x\in E$ and $g\in \mathcal B_b(E)^{++}$.
-    Denote by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
+    Fix $t>0, r\in [0,t), x\in E$ and a strictly positive $g\in \mathcal B_b(E)$.
+    Denote by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{\langle W_t, g\rangle}$.
     Conditioned on $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$ in \eqref{eq: conditional intensity}.
@@
     From Lemma \ref{lem: estimate of exponential remaining}, we have $\mathbf Q^{(g,t)}_{x}$-almost surely
-\begin{equation}\begin{split}
-    &\int_{[0,t]\times \mathbb W}|e^{i w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
-    \leq \int_{[0,t]\times \mathbb W}\big(| w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
-    \\&\leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[ X_{t-s}(|f|)] \pi(\xi_s,dy)
+\begin{align}
+    &\int_{[0,t]\times \mathbb W}|e^{i \langle w_{t-s}, f\rangle} - 1| \mathbf m(\xi, ds,dw)
+    \leq \int_{[0,t]\times \mathbb W}\big(| \langle w_{t-s}, f\rangle| \wedge 2\big) \mathbf m(\xi, ds,dw)
+    \\&\leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( \langle W_{t-s}, |f|\rangle\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[\langle X_{t-s}, |f|\rangle] \pi(\xi_s,dy)
     \\&\qquad\qquad+ 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
@@
     < \infty.
-\end{split}\end{equation}
+\end{align}
     Using this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-almost surely,
-\begin{equation}\begin{split}
-    &\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
-    \\&=\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
+\begin{align}
+    &\int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)
+    \\&=\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i \langle W_{t-s}, f\rangle} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i \langle X_{t-s}, f\rangle} - 1] \pi(\xi_s,dy)\Big) ds
     \\&=\int_0^t \Big( 2\rho_2(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
     \\&= -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
-\end{split}\end{equation}
+\end{align}
     Therefore, according to \eqref{eq: Spine decomposition 2}, Campbell's formula and above, we have that
-\begin{equation}\begin{split}
+\begin{align}
 \label{eq: N to Pi}
-    \mathbb N_x^{W_t(g)}[e^{i W_t(f)}]
-    &=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
+    \mathbb N_x^{\langle W_{t}, g\rangle}[e^{i \langle W_t, f\rangle}]
+    &=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
     \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
     \\&= \frac{1}{P_t^{\rho_1} g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
-\end{split}\end{equation}
+\end{align}
     Let $\epsilon >0$.
-    Define $f^+ = (f \vee 0) + \epsilon$ and $f^- = (-f) \vee 0 + \epsilon$, then $f^\pm \in \mathcal B_b(E)^{++}$ and $f = f^+ - f^-$.
+    Define $f^+ = (f \vee 0) + \epsilon$ and $f^- = (-f) \vee 0 + \epsilon$, then $f^\pm$ are strictly positive and $f = f^+ - f^-$.
     According to \eqref{eq: Spine decomposition 1}, we have that
 \begin{equation}
-    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]}
-    = \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i X_t(f)}].
+    %\frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]}
+    \frac{\mathbf P_{\delta_x}[\langle X_t,f^{\pm}\rangle e^{i \langle X_t,f\rangle}]}{\mathbf P_{\delta_x}[\langle X_t,f^{\pm}\rangle ]}
+    %= \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i X_t(f)}].
+    = \mathbf P_{\delta_x}[e^{i \langle X_t,f\rangle}] \mathbb N_x^{\langle W_t,f^{\pm}\rangle}[e^{i \langle X_t,f\rangle}].
 \end{equation}
     Using \eqref{eq: N to Pi} and the above, we have
-\begin{equation}\begin{split}
-    \frac{\mathbf P_{\delta_x}[X_t(f)e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
-    &= \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i X_t(f)}]
+\begin{align}
+    \frac{\mathbf P_{\delta_x}[\langle X_t, f\rangle e^{i \langle X_t, f\rangle}] }{\mathbf P_{\delta_x}[e^{i \langle X_t, f\rangle}]}
+    &= \mathbf P_{\delta_x}[\langle X_t, f^+\rangle] \mathbb N_x^{\langle W_t, f^+\rangle} [e^{i \langle X_t, f\rangle}] - \mathbf P_{\delta_x}[\langle X_t, f^-\rangle]\mathbb N_x^{\langle W_t, f^-\rangle}[e^{i \langle X_t, f\rangle}]
     \\& = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
-\end{split}\end{equation}
+\end{align}
     Therefore, we have
-\begin{equation}\begin{split}
+\begin{equation}
     \frac{\partial}{\partial \theta} {U_t(\theta f)(x)}
-    = \frac{\mathbf P_{\delta_x}[iX_t(f)e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
+    = \frac{\mathbf P_{\delta_x}[i\langle X_t, f\rangle e^{i \langle X_t, f\rangle}] }{\mathbf P_{\delta_x}[e^{i \langle X_t, f\rangle}]}
     =  \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
-\end{split}\end{equation}
+\end{equation}
     Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
 
-\begin{equation}\begin{split}
+\begin{align}
     &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)( x)
@@
     = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -U_{t-s}(\theta f)) ds} ].
-\end{split}\end{equation}
+\end{align}
 
     From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
-    Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
+    %Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
+    Therefore, we can apply Lemma \ref{eq: complex FK} and get that
 \[
@@
     and
-\begin{equation}\begin{split}
+\begin{align}
     &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
     &= \Pi_{r,x} [i e^{\int_r^t \rho_1(\xi_s)ds}f(\xi_t)].
-\end{split}\end{equation}
+\end{align}
     Integrating the two displays above with respect to $\theta$  on [0,1], using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get
@@
 \[
-    |e^{i W_t(f_n)} - 1| \leq W_t(|f|);
-    \quad \mathbb N_x[W_t(|f|)] = (P_t^{\rho_1} |f|)(x) < \infty.
+    |e^{i W_t(f_n)} - 1| \leq \langle W_t, |f|\rangle;
+    \quad \mathbb N_x[\langle W_t, |f|\rangle] = (P_t^{\rho_1} |f|)(x) < \infty.
 \]
@@
     $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
-\begin{equation}\begin{split}
+\begin{equation}
     \big|\psi(\xi_s,- U_{t-s}f_n)\big|
     \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2.
-\end{split}\end{equation}
+\end{equation}
 \end{itemize}
@@
 
-%\bibliographystyle{amsplain}
-%\bibliography{bib.bib}
-
 \providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
 \begin{thebibliography}{10}
-%ZS: Changes made for the bibliographies are not marked by %
-
-\bibitem{AdamczakMilos2014U-statistics}
-R.~Adamczak and P.~Mi{\l}o\'{s}, \emph{{$U$}-statistics of
-  {O}rnstein-{U}hlenbeck branching particle system}, J. Theoret. Probab.
-  \textbf{27} (2014), no.~4, 1071--1111.
+
+%\bibitem{AdamczakMilos2014U-statistics}
+%R.~Adamczak and P.~Mi{\l}o\'{s}, \emph{{$U$}-statistics of
+  %{O}rnstein-{U}hlenbeck branching particle system}, J. Theoret. Probab.
+  %\textbf{27} (2014), no.~4, 1071--1111.
 
 \bibitem{AdamczakMilos2015CLT}
-\bysame, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
+R.~Adamczak and P.~Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
   Electron. J. Probab. \textbf{20} (2015), no.~42, 35 pp.
+
+ \bibitem{Asmussen76Convergence}
+  S.~Asmussen, \emph{Convergence rates for branching processes}, Ann.
+  Probab.  \textbf{4} (1976), no.~1, 139--146.
 
@@
 
-\bibitem{BansayeDelmasMarsalleTran2011Limit}
-V.~Bansaye, J.~Delmas, L.~Marsalle, and V.~C. Tran, \emph{Limit theorems for
-  {M}arkov processes indexed by continuous time {G}alton-{W}atson trees}, Ann.
-  Appl. Probab. \textbf{21} (2011), no.~6, 2263--2314. \MR{2895416}
+%\bibitem{BansayeDelmasMarsalleTran2011Limit}
+%V.~Bansaye, J.~Delmas, L.~Marsalle, and V.~C. Tran, \emph{Limit theorems for
+  %{M}arkov processes indexed by continuous time {G}alton-{W}atson trees}, Ann.
+  %Appl. Probab. \textbf{21} (2011), no.~6, 2263--2314. \MR{2895416}
 
@@
 
+ \bibitem{ChenRenSongZhang2015Strong-law} Z.-Q. Chen, Y.-X. Ren, R. Song, and R. Zhang,
+ \emph{Strong law of large numbers for supercritical superprocesses under second moment condition}, Front. Math. China \textbf{10} (2015), no.~4, 807--838.
+
+ %\bibitem{ChenRenSongZhang2017Law} Z.-Q.
+Chen, Y.-X.
+Ren,  and T.
+Yang, \emph{Law of large numbers for branching symmetric Hunt processes with measure-valued branching rates},  J.
+Theoret.
+Probab.
+\text{30} (2017), no.~3, 898--931.
+
+ \bibitem{ChenRenYang2019Skeleton} Z.-Q. Chen, Y.-X. Ren,  and T. Yang,
+ \emph{Skeleton decomposition and law of large numbers for supercritical superprocesses}, Acta Appl. Math. \textbf{159} (2019), no.~1, 225--285.
+
 \bibitem{Durrett2010Probability}
@@
 
-\bibitem{EnglanderHarrisKyprianou2010Strong}
-J.~Engl\"{a}nder, S.~C. Harris, and A.~E. Kyprianou, \emph{Strong law of large
-  numbers for branching diffusions}, Ann. Inst. Henri Poincar\'{e} Probab.
-  Stat. \textbf{46} (2010), no.~1, 279--298.
+%\bibitem{EnglanderHarrisKyprianou2010Strong}
+%J.~Engl\"{a}nder, S.~C. Harris, and A.~E. Kyprianou, \emph{Strong law of large
+  %numbers for branching diffusions}, Ann. Inst. Henri Poincar\'{e} Probab.
+  %Stat. \textbf{46} (2010), no.~1, 279--298.
 
@@
 
-\bibitem{GrubelKabluchko2016A-functional}
-R.~Gr\"{u}bel and Z.~Kabluchko, \emph{A functional central limit theorem for
-  branching random walks, almost sure weak convergence and applications to
-  random trees}, Ann. Appl. Probab. \textbf{26} (2016), no.~6, 3659--3698.
-
-\bibitem{HartungKlimovsky2018The-phase}
-L.~Hartung and A.~Klimovsky, \emph{The phase diagram of the complex branching
-  brownian motion energy model}, Electron. J. Probab. \textbf{23} (2018).
+\bibitem{EnglanderTuraev2002A-scaling}
+J.~Engl\"{a}nder and  D. ~Turaev, \emph{A scaling limit theorem for a class of superdiffusions}. Ann Probab., \textbf{30} (2002),  683--722.
+
+%\bibitem{GrubelKabluchko2016A-functional}
+%R.~Gr\"{u}bel and Z.~Kabluchko, \emph{A functional central limit theorem for
+  %branching random walks, almost sure weak convergence and applications to
+  %random trees}, Ann. Appl. Probab. \textbf{26} (2016), no.~6, 3659--3698.
+
+%\bibitem{HartungKlimovsky2018The-phase}
+%L.~Hartung and A.~Klimovsky, \emph{The phase diagram of the complex branching
+  %brownian motion energy model}, Electron. J. Probab. \textbf{23} (2018).
 
@@
 
-\bibitem{IksanovKabluchko2016A-central}
-A.~Iksanov and Z.~Kabluchko, \emph{A central limit theorem and a law of the
-  iterated logarithm for the {B}iggins martingale of the supercritical
-  branching random walk}, J. Appl. Probab. \textbf{53} (2016), no.~4,
-  1178--1192.
-
-\bibitem{IksanovKoleskoMeiners2018Fluctuations}
-A.~Iksanov, K.~Kolesko, and M.~Meiners, \emph{Fluctuations of biggins'
-  martingales at complex parameters}, arXiv:1806.09943, 2018.
+%\bibitem{IksanovKabluchko2016A-central}
+%A.~Iksanov and Z.~Kabluchko, \emph{A central limit theorem and a law of the
+  %iterated logarithm for the {B}iggins martingale of the supercritical
+  %branching random walk}, J. Appl. Probab. \textbf{53} (2016), no.~4,
+  %1178--1192.
+
+%\bibitem{IksanovKoleskoMeiners2018Fluctuations}
+%A.~Iksanov, K.~Kolesko, and M.~Meiners, \emph{Fluctuations of biggins'
+  %martingales at complex parameters}, arXiv:1806.09943, 2018.
 
 \bibitem{IksanovKoleskoMeiners2018Stable-like}
-\bysame, \emph{Stable-like fluctuations of biggins' martingales}, Stochastic
+A.~Iksanov, K.~Kolesko, and M.~Meiners, \emph{Stable-like fluctuations of {B}iggins' martingales}, Stochastic
   Process. Appl. (2018).
@@
 
+ \bibitem{KouritzinRen2014A-strong}
+ M. ~A. ~ Kouritzin, and  Y.-X. Ren,  \emph{A strong law of large numbers for super-stable Processes},  Stochastic Process. Appl.  \textbf{121} (2014),  505--521.
+
 \bibitem{Kyprianou2014Fluctuations}
@@
 Y.-X. Ren, R.~Song, and Z.~Sun, \emph{Spine decompositions and limit theorems
-  for a class of critical superprocesses}, arXiv:1711.09188, 2017.
+  for a class of critical superprocesses}, 
+  To appear in Acta Appl. Math.
+
+\bibitem{RenSongSun2018Limit}
+\bysame, \emph{Limit theorems for a class of critical superprocesses with stable branching},
+    arXiv:1807.02837, 2018.
 
@@
 \bibitem{SchillingSongVondravcek2010Bernstein}
-R.~L. Schilling, R.~Song, and Z.~Vondra\v{c}ek, \emph{Bernstein functions}, De
-  Gruyter Studies in Mathematics, vol.~37, Walter de Gruyter \& Co., Berlin,
-  2010.
+R.~L. Schilling, R.~Song, and Z.~Vondra\v{c}ek, 
+\emph{Bernstein functions: Theory and applications. Second edition.}
+de  Gruyter Studies in Mathematics, vol.~37, Walter de Gruyter \& Co., Berlin,
+  2012.
 
@@
 
-\bibitem{Wang2018Central}
-\bysame, \emph{Central limit theorems for supercritical superprocesses with
-  immigration}, J. Theoret. Probab. \textbf{31} (2018), no.~2, 984--1012.
+%\bibitem{Wang2018Central}
+%\bysame, \emph{Central limit theorems for supercritical superprocesses with
+  %immigration}, J. Theoret. Probab. \textbf{31} (2018), no.~2, 984--1012.
 
 \end{thebibliography}
-%\end{comment}
 

### 2019-03-06 supCLT.tex
supCLT.tex: 0306

@@
 %%----Versions-----------------------------
+%supCLT-2.tex 2019/03/05 by Renming
+%supCLT.tex 2019/03/04 by Zhenyao
 % supclt0220.tex 2019/02/20 by Jianjie
@@
 \title
-    %[CLT for Super-OU processes]
     [stable CLT for super-OU processes]
-    %{Stable Central Limit Theorems for Super OU Processes with Stable Branching}
     {Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
@@
 \address
-    %{Renming Sond\\
     {Renming Song
@@
 \thanks{Jianjie Zhao is the corresponding author}
-%ZS: I changed all "branching rate regime" to "branching rate regime" below.
 \begin{abstract}
-	%Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism 
-    Consider a $(\xi, \psi)$-superprocess $(X_t)_{t\geq 0}$ where the spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$  which has generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ with $\sigma, b >0$, and the
-    branching mechanism $\psi$ takes the form close to
-	$\psi(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$ in some sense.
+  %  Consider a $(\xi, \psi)$-superprocess $(X_t)_{t\geq 0}$ where the spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$  which has generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ with $\sigma, b >0$, and the
+%    branching mechanism $\psi$ takes the form close to
+%	$\psi(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$ in some sense.
+Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$. 
+Let $\psi$ be a branching mechanism which is close to a function of the form
+$\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense. In this paper, we study asymptotic behaviors of 
+$(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$.
     For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$.
-    %Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: 
     Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
-    %In the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
-    %In the critical branching rate regime  $\alpha\beta= \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
-    %In the large branching rate regime  $\alpha\beta> \kappa_f b(1+\beta)$, we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$, and then established a central limit theorem, which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges weakly to a $(1+\beta)$-stable random variable.
     the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
@@
 	Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
-%MOVED BELOW
-    %Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
-    %Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
-    %Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-    %For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
-    %For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
-    %We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have
-%\[
-    %\sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
-%\]
-%END MOVED BELOW
     Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
@@
 \end{equation}
-    %where $\sigma$ and $b$ are positive constants.
     where $\sigma > 0$ and $b > 0$ are constants.
@@
 	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty$.
-%DELETED
-	%It is known that $\alpha, \rho$ and $\pi$ are uniquely determined by the function $\psi$.
-%END DELETED
-	We refer to $\pi$ the \emph{L\'evy measure} of the branching mechanism $\psi$.
-%MOVED FROM ABOVE
+	We refer to $\pi$ as the \emph{L\'evy measure} of the branching mechanism $\psi$.
     Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
     For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
-    We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have
+    We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have
 \[
@@
 \]
-%END MOVED FROM ABOVE
-       We say an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ 
+       We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ 
 on a measurable space $(\Omega, \mathcal{F})$       
@@
 The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost},
-    %followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost}. 
-    %The setups of the papers mentioned above are  different. 
     followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost} under different settings.
@@
 
-    %In this paper, we focus on limit results for the super-OU process $X$.
-    %The strong law of large numbers of $X$ can be stated as follows: 
-    The strong law of large numbers of the above super-OU process $X$ can be stated as follows: 
-    Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our assumptions 1 and 2, below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$,
-    %for every Lebesgue-almost everywhere continuous bounded $f\in\mathcal B(\mathbb R^d, \mathbb R_+)$,
+%    The strong law of large numbers of the above super-OU process $X$ can be stated as follows: 
+   The strong law of large numbers for the super-OU process $X$ can be stated as follows:
+    Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$,
     for every Lebesgue-almost everywhere continuous bounded non-negative function $f$ on $\mathbb R^d$, 
     we have
-    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f,\phi_0\varphi\rangle $, 
-    %where  $H_\infty=\lim_{t\to\infty}e^{-\alpha t}\|X_t\|$, and the convergence also holds in $L^1(\mathbb P_\mu)$, see \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
-    where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\phi_0$, $\varphi$ are functions which will be introduced in  \eqref{eigenfunction} and \eqref{invariantdensity} below.
+%    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f,\phi_0\varphi\rangle $, 
+    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f, \varphi\rangle $, 
+    where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and 
+%    $\phi_0$, $\varphi$ are functions which will be introduced in  \eqref{eigenfunction} and \eqref{invariantdensity} below.
+$\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
     See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
 
-    %In this paper, we will establish some spatial central limit theorems for the super-OU process $X$ above.  
     In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above. 
-%NEW ADDED
-    Our key assumption is that the corresponding branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$ where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$ in some sense.
-%END ADDED
-    %More precisely, we want to find 
+    Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
     We want to find
-    %$F_t$ and $G_t$ such that
     $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
@@
     converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, 
-    %for some test functions $f$.
     for some testing functions $f$.
-    %It turns out that the normalization $F_t$ depends on the branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
-    It turns out that there are three regimes of different behavior of this CLT depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
+%    It turns out that there are three regimes of different behavior of this CLT 
+    It turns out that the statements of the CLT are different in three regimes
+    depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
 Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
-%ADDED
-    Note that, under the settings of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
-%END ADDED
-
-    %There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses.
-    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under finite second moment condition.
+    Note that, in the setting of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
+
+    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
     See
     \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes, 
-    %see \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Waston processes, 
     \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Watson processes,
@@
     In \cite{AdamczakMilos2015CLT}, 
-    %Adamcazk and Milo\'s 
     Adamczak and Milo\'s 
     proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
-    These two papers made connections between CLT and what they call branching rate regimes.
+    These two papers made connections between the CLT and 
+    %what they call branching rate regimes.
+    the branching rate regimes
     In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
-    %Moverover, 
     Moreover,
-    compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
+    compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
     In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central},
@@
 
-    %All central limit results described above hold for systems with branching mechanisms with finite variance.
-    %It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
     There are also many limiting theory for branching processes and branching Markov processes with branching mechanisms of infinite second moments.
@@
 when the offspring distribution
-    %belongs to the domain of a stable law of index $\alpha\in (1, 2]$, 
     belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
@@
     considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. 
-    %They established some central limit theorems in small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
-    They established some central limit theorems in small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
-%NEW ADDED
-    We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered the stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.
-%END NEW ADDED
-
-%NEW ADDED
-    As far as we know, this paper is the first one in the literature on establishing CLT for supercritical superprocesses without the second moment condition.
-%END added
-%DELETED
-    %In this paper, we consider a class of super-OU processes with a general stable branching mechanism.
-    %For small and critical branching rate regimes, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}.
-    %For large branching rate regime, we not only prove an almost sure convergence result as in \cite{MarksMilos2018CLT}, we also prove a central limit theorem type result.
-%END DELETED
-
-%DELETED    
-    %For recent works on limit results (strong law of large numbers and central limit theorems) for branching diffusions and general branching Markov processes, we refer to \cite{BansayeDelmasMarsalleTran2011Limit, ChenRenSongZhang2017Law, EnglanderHarrisKyprianou2010Strong, GrubelKabluchko2016A-functional, RenSongZhang2015Central} and references there in.
-%END DELETED
-
-%    {\bf ZS: I think this subsection should be extended with more literatures like:
-%    \cite{AdamczakMilos2014U-statistics},
- %   \cite{EckhoffKyprianouWinkel2015Spines},
-%    \cite{EnglanderHarrisKyprianou2010Strong},
-%    \cite{IksanovKabluchko2016A-central},
-%    \cite{LiuRenSong2013Strong},
-%    \cite{Wang2018Central},
-%    \cite{IksanovKoleskoMeiners2018Stable-like},
-%    \cite{IksanovKoleskoMeiners2018Fluctuations},
-%    \cite{GrubelKabluchko2016A-functional},
-%    \cite{Heyde1970A-rate},
-%    \cite{Heyde1971Some},
-%    \cite{HeydeBrown1871An-invariance},
-%    \cite{HeydeLeslie1971Improved},
-%    \cite{BansayeDelmasMarsalleTran2011Limit},
-%    \cite{EnglanderWinter2006Law},
-%    \cite{Englander2009Law},
-%    \cite{Janson2004Functional},
-%    \cite{ChenRenWang2008An-almost},
-%    \cite{Wang2010An-almost},
-%    \cite{HartungKlimovsky2018The-phase},
-%    \cite{BansayeDelmasMarsalleTran2011Limit},
-%    \cite{Le2019Long}.
-%
- %   YX: I have added some parts which are related to references listed above.
-But I did not cite  \cite{AdamczakMilos2014U-statistics}, \cite{HartungKlimovsky2018The-phase} and \cite{Wang2018Central} since these are not closely related to our paper.
-I did not cite \cite{HeydeLeslie1971Improved}--\cite{IksanovKoleskoMeiners2018Stable-like} since these are about central limit theorems for Biggin's martingales.
-%}
+%    They established some central limit theorems in small and critical branching rate regimes, 
+   They established some central limit theorems in the small and critical branching rate regimes, 
+    but they did not prove any central limit theorem type result in the large branching rate regime.
+    We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.
+
+    As far as we know, this paper is the 
+%    first one in the literature on establishing CLT 
+   first to study spatial central limit theorems
+    for supercritical superprocesses without the second moment condition.
+
 \subsection{Main results}
@@
 
-%MOVED BELOW	
-	%Denote by $\Gamma$ the gamma function.
-%For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
-%END MOVED BELOW
 	We will always assume that the following Assumption holds.
@@
 \label{asp: Greys condition}
-	The branching mechanism satisfies the Grey's condition, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+	The branching mechanism satisfies Grey's condition, i.e. there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
 \end{asp}
-%MOVED FROM ABOVE
     For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
-%END MOVED FROM ABOVE
 	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, 
 	the \emph{extinction event} 
-	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has a positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
+	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
     In fact,
@@
 
-%MOVED FROM ABOVE
     Denote by $\Gamma$ the gamma function.
 For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$. 
-%END MOVED FROM ABOVE    
     In this paper, we will also assume the following:
@@
 \end{asp}
-    %{\bf Jianjie: do we need to emphasize that $\delta\in (0,1-\beta)$ such that $1+\beta+\delta<2$.}
-    %ZS: It is done by Remark 1.1. 
 	We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
@@
 	$-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
-	It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ criteria, i.e.,
+	It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption 
+	\ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the 
+	%$L \log L$ criteria, i.e.,
+	$L \log L$ condition, i.e.,
 \[
@@
 \]
-%NEW ADDED
     This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
-%END NEW ADDED
-
-%MOVED FROM ABOVE
-    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
-    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
-%END MOVED FROM ABOVE
+
+    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
+    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel functions on $\mathbb R^d$.
     We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
@@
     We now recall some basic spectral properties of $(P_t)_{t\geq 0}$ from \cite{MetafunePallaraPriola2002Spectrum}.
-        It is known that the OU process $\xi$ has an invariant measure
+%        It is known that the OU process $\xi$ has an invariant measure
+       It is known that the OU process $\xi$ has an invariant density
 \begin{equation}
@@
     Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$.
-        Then, $L^2(\varphi)$ is a Hilbert space with inner product
+        Then $L^2(\varphi)$ is a Hilbert space with inner product
 \begin{equation}
@@
        Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-    For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+    For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, 
+    %$p!:= \prod_{k= 1}^d p_k$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+    $p!:= \prod_{k= 1}^d p_k!$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
     The \emph{Hermite polynomials} are defined by
@@
 \end{equation}
-       It is known that the transition semigroup $(P_t)_{t\geq 0}$ of the OU process $\xi$ is a strongly continuous semigroup in $L^2(\varphi)$, and its corresponding generator $L$ has discrete spectrum
+%       It is known that the transition semigroup $(P_t)_{t\geq 0}$ of the OU process $\xi$ 
+It is known that $(P_t)_{t\geq 0}$ 
+       is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum
         $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
@@
 \end{equation}
-    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis for $L^2(\varphi)$.
-    Thus, for each $f\in L^2(\varphi)$, we have
+    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
+    Thus for each $f\in L^2(\varphi)$, we have
 \begin{equation}\label{semicomp1}
@@
 \end{equation}
-    %Denote by
     For each function $f\in L^2(\varphi)$, denote by
@@
 \end{equation}
-    the order of the function $f$ in its spectral decomposition \eqref{semicomp1}.
+    the order of the function $f$ in the spectral decomposition \eqref{semicomp1}.
     Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
@@
     In this paper, we are mainly interested in the asymptotic behavior of $\langle f, X_t\rangle$ 
-    %for $f\in \mathcal P$. 
     for non-trivial $f\in \mathcal P$.
@@
 \end{itemize}
-%DELETED
-    %Note that in the large and critical branching rate regimes, $f$ is non-trivial.
-%END DELETED
 
@@
    If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
-    %Hence by Theorem \ref{thm: law of large number}, 
     Hence, Theorem \ref{thm: law of large number} says that
@@
 \]
-    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have the almost sure convergence.
-    %In fact, to get the almost sure convergence for bounded test functions $f$, we do not need $f$ to be twice differentiable.
-$f$ being bounded and Lebesgue-almost every where continuous is enough for the almost sure convergence, see \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
-    However, to get the almost sure convergence for bounded, non-negative, and Lebesgue-almost every where continuous testing functions $f$, we do not need $f$ to be twice differentiable.
+    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence. 
+    However, to get  almost sure convergence for bounded, non-negative, and Lebesgue-almost everywhere continuous testing functions $f$, we do not need $f$ to be twice differentiable.
 See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
@@
 \begin{rem} 
-    %For general test functions $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} says that the correct scaling for $\langle f, X_t\rangle$ is $e^{-(\alpha-\kappa_fb)t}$.
-%Theorem \ref{thm: law of large number} gives a strong law of large numbers for general test functions $f$ in the large branching rate regime, and it extends the strong laws of large numbers in  \cite{ChenRenYang2019Skeleton} and \cite{EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
-    For general test functions $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers in  \cite{ChenRenYang2019Skeleton} and \cite{EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
-%DELETED 
-    %For any $f \in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} gives an expansions of $e^{-\alpha t} \langle f, X_t\rangle$ in the following sense:
-    %\[
-    %e^{-\alpha t}\langle f, X_t\rangle=
-    %\sum_{p\in \mathbb Z_+^d:|p|\leq\kappa_f} e^{-|p|t}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p+o(e^{-\kappa_ft}),
-    %\]
-    %where $\lim_{t\to\infty}e^{\kappa_ft}o(e^{-\kappa_ft})=0$ in   $L^{1+\gamma}(\mathbb{P}_{\mu})$.  
-%END DELETED
+    For general test functions $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton} and \cite{EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
     When the generator of the 
@@
 
-    The fluctuation result associated to the law of large numbers are given in the following Theorem \ref{thm: large clt}.
+%    The fluctuation result associated to the law of large numbers are 
+   The fluctuation result associated to the law of large numbers in this case is
+    given in Theorem \ref{thm: large clt} below.
 Define
@@
     \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
-%ADDED
-    \quad K : = \sup\{|p|: p \in \mathcal N\}.
-%END ADDED
+    \quad K : = \sup\{|p|: p \in \mathcal N\}
 \end{equation}
@@
 \end{align}
-    %We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$.
-    %We will show that, when $f\in \mathcal{P}$ is non-trivial, $\theta \mapsto \exp(\theta \bar m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
-    We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; and in Lemma \ref{prop: alpha stable rv} that that, when $f\in \mathcal{P}$ is non-trivial, $\theta \mapsto \exp(\theta \bar m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
+    We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; and in Lemma \ref{prop: alpha stable rv} that that, when $f\in \mathcal{P}$ is non-trivial,
+%    $\theta \mapsto \exp(\theta \bar m[f])$ is a characteristic 
+    $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic 
+    function of a $(1+\beta)$-stable random variable.
 \begin{thm}
 \label{thm: large clt}
-    %For $f\in\mathcal{C}_l$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that,
     For non-trivial $f\in\mathcal{C}_l$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that,
@@
 \end{align}
-    where $\bar{\zeta}$ is an $(1+\beta)$-stable random variable with characteristic function
+    where $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function
 \begin{align}
@@
 \end{equation}
-%ADDED
     According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
-%END ADDED
    We will prove in Lemma \ref{prop: alpha stable rv} that
-   $\theta \mapsto \exp(\theta \widetilde m[f])$
-    is a characteristic function of an $(1+\beta)$-stable random variable.
+%   $\theta \mapsto \exp(\theta \widetilde m[f])$ is a characteristic function of an 
+   $\theta \mapsto \exp( \widetilde m[\theta f])$ is a characteristic function of a
+    $(1+\beta)$-stable random variable.
 \begin{thm}
@@
 	According to Lemma \ref{lem: def of all m} below, $m[f]$ is well-defined.
-	We will prove  in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp(\theta m[f])$ is a characteristic function of an $(1+\beta)$-stable random variable.
+	We will prove  in Lemma \ref{prop: alpha stable rv} that 
+%	$\theta \mapsto \exp(\theta m[f])$ is a characteristic function of an
+	$\theta \mapsto \exp( m[\theta f])$ is a characteristic function of a
+	 $(1+\beta)$-stable random variable.
 \begin{thm}
@@
 \end{thm}
-%ADDED
-\subsection{Some words before the proofs}
-%END ADDEd
-Let us give some intuition about the central limit theorems above before we move to proofs.  
+%\subsection{Some words before the proofs}
+\subsection{Some intuitive explanation}
+%Let us give some intuition about the central limit theorems above before we move to proofs.  
+Here we give some intuitive explanation of the central limit theorems above.
 The mains ideas are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
@@
     We will use the shorter notation $\mathcal I_s^t Y$ when there is no danger of confusion. 
-    %Then for any $f\in \mathcal{P}$, we have 
     For each $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
@@
        \langle f,X_t\rangle
-        %= &\sum_{k=0}^{\lfloor t \rfloor-1} \left(\mathbb P_\mu[\langle f ,X_t\rangle|\mathscr F_{t-k}] - \mathbb P_\mu[\langle f ,X_t\rangle|\mathscr F_{t-k-1}]\right)+\\
-        %&\left(\mathbb P_\mu[\langle f ,X_t\rangle|\mathscr F_{{t-\lfloor t \rfloor}}] - \mathbb P_\mu[\langle f ,X_t\rangle|\mathscr F_{0}]\right)+ \langle P^\alpha_tf,X_0\rangle\\
         :=\sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle+\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle +
@@
 \end{align}
-   %Therefore, to find the normalized limit of  $\langle f,X_t\rangle$, we need to look at each term $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$.
-   To find the fluctuation of $\langle f,X_t\rangle$, we will investigate the fluctuation of each term $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$.
-%DELETED
- %Note that $$
- %\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle=\langle P^\alpha_kf, X_{t-k}\rangle-\mathbb P_\mu[\langle P^\alpha_kf, X_{t-k}\rangle|\mathscr F_{t-k-1}]
- %$$
-%END DELETED
-
-%ADDED
+   To find the fluctuation of $\langle f,X_t\rangle$, we will investigate the fluctuation of 
+   %each term $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$.
+   each term on the right hand side above.
+
     Suppose that $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions
 \[
-    \mathbf E[e^{i\theta \zeta_k}] = \exp(e^\alpha m_k[\theta f]),\quad k \in \mathbb N
-\]   
-    where $m_k[f]$ is given by Lemma \ref{lem: def of all m} below.
+    \mathbf E[e^{i\theta \zeta_k}] = \exp(e^\alpha m_k[\theta f]),\quad k \in \mathbb N,
+\]   
+    where $m_k[f]$ is given in Lemma \ref{lem: def of all m} below.
     Recall that $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
-    Lemma \ref{lem: mainlemma} and Corollary \ref{cor: indepedent of the limit zeta for critical and small} below actually says that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
+    Lemma \ref{lem: mainlemma} and Corollary \ref{cor: indepedent of the limit zeta for critical and small} below imply that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
 \[
@@
 \]
-    So if $f$ lives in the small branching rate regime, i.e. $\alpha \beta < \kappa_f b(1+\beta)$, we have roughly that
-\[
-    \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}e^{-\frac{\alpha}{1+\beta}}\sum_{k=0}^\infty \zeta_k
+    So if $f$ is in the small branching rate regime, i.e., $\alpha \beta < \kappa_f b(1+\beta)$, we have roughly that
+\[
+    \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}e^{-\frac{\alpha}{1+\beta}}\sum_{k=0}^\infty \zeta_k,
 \]
@@
 \]
-    with $m[\theta f]$ given by Lemma \ref{lem: def of all m} below. 
-    In this intuition, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined,
+    with $m[\theta f]$ given in Lemma \ref{lem: def of all m} below. 
+    In explanation above, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined,
 \begin{equation}
@@
 \]
-    All of this facts well be made clear in Subsection \ref{sec: stable distributions} below.
-
-    If $f$ lives in the critical branching rate regime, i.e. $\alpha \beta = \kappa_f b(1+\beta)$, then \eqref{eq: equatlity for mf for small rate} doesn't hold anymore. 
+    All of this facts will be made clear in Subsection \ref{sec: stable distributions} below.
+
+    If $f$ is in the critical branching rate regime, i.e., $\alpha \beta = \kappa_f b(1+\beta)$, 
+    %then \eqref{eq: equatlity for mf for small rate} doesn't hold anymore. 
+    then the right hand side of \eqref{eq: equatlity for mf for small rate} may not converge. 
     Instead, see Lemma \ref{lem: def of all m} below, there is another quantity $\widetilde m[f]$ satisfying that
@@
 \]
-    In this situation, we roughly have that
+    In this case, we roughly have that
 \[
@@
 
-    For the testing function $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
+    For  testing functions $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
 Taking $f = \phi_p$ with $\alpha \beta > |p|b(1+\beta)$ as an example, we do the following decomposition:
@@
 \]
-    The fluctuation behaviors of each terms $H_{t+n-1}^p - H_{t+n}^p$ and their asymptotic independence will be established in Lemma \ref{large-central} and \ref{lem: independency for large rate} below, respectively.
-    These lemmas will eventually lead us to the fluctuation result for the large branching rate regime.
-%END ADDED
-
- %DELETED
- %By \eqref{lem: control of mgtrs}, we roughly have
-%\begin{enumerate}
-%\item If  $f$ is non-trivial and $\alpha\beta<\kappa_f b(1+\beta)$, the normalization is $F_t=\|X_t\|^{\frac{1}{1+\beta}}$, and only those $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$ with small $k$, normalized by $\|X_t\|^{\frac{1}{1+\beta}}$,  contribute  to the limit of $\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}$.
-Lemma \ref{lem: mainlemma} below gives the contribution of each term.
-Also, we will prove that the contributions from different time intervals are independent, and thus $\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}$ has $(1+\beta)$-stable limit as $t\to\infty$.
-
-%\item If  $\alpha\beta=\kappa_f b(1+\beta)$, then Lemma \ref{lem: mainlemma} below says that for each $k<t$,  $\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}$ has a $(1+\beta)$-stable limit.
-But the summation of these terms will diverge.
-In this case, the correct normalization is $F_t=(t\|X_t\|)^{\frac{1}{1+\beta}}$.
-%\item 
-    %If  $\alpha\beta>\kappa_f b(1+\beta)$,  by Theorem \ref{thm: law of large number}, $e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle$ has an almost sure limit.  
-%In this case, we further consider a central limit type result for $\langle f, X_t\rangle$ when
-%$f\in \mathcal{C}_l$. 
-%Since each $f\in \mathcal{C}_l$ can be expressed as
-%\begin{align}
-    %f(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x),\quad x\in \mathbb{R}^d,
-%\end{align}
-%where $a_p=\langle f, \phi_p\rangle_{\varphi}$, and $\mathcal{N}$ is a finite set, we only need to consider the special case of $f=\phi$.
-Therefore, we only need to consider the martingale central limit result for $H^p_t, t\geq 0.$
-%The correct normalization for each $H_{t+n-1}^p-H^p_{t+n}$ is $e^{-(\alpha-b|p|)t}e^{\frac{\alpha t}{1+\beta}}$.
-%Since $\alpha\beta> |p|b(1+\beta)$, only those $H_{t+n-1}^p-H^p_{t+n}$  with small $n$, normalized by $e^{-(\alpha-b|p|)t}\|X_t\|^{\frac{1}{1+\beta}}$,  contribute  to the normalized limit of $H^p_t-H^p_\infty$.
-In Lemma \ref{large-central}, we will prove that for each $n$, $\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p| b)t}\|X_t\|^{\frac{1}{1+\beta}}}$ has a $(1+\beta)$-stable limit as $t\to\infty$.
-The limits are independent for different intervals.
-%END DELETED
+    The fluctuation behaviors of each of the terms $H_{t+n-1}^p - H_{t+n}^p$ and their asymptotic independence will be established in Lemma \ref{large-central} and \ref{lem: independency for large rate} below, respectively.
+    These lemmas will eventually lead us to the fluctuation result in the large branching rate regime.
 
@@
  We leave the question of independence for stable branching mechanism to a future project.
-%\end{enumerate}
-
-%This paper is our first attempt to study central limit type theorems for general superprocesses with general branching mechanism. 
+
     This paper is our first attempt on the stable CLT for superprocesses. 
     There are still many open questions. 
-    For example, the spatial motion in this paper is an Ornstein-Uhlenbeck process. 
-    %We would be interested in more general motions. 
-    If the branching mechanism has finite second moment, we established some central limit theorems in \cite{RenSongZhang2015Central} for a class of superprocesses with general motions. 
-    We hope to prove stable CLT for superprocesses with general motions in a future project.
-
-    %Recall that we assume that the the branching mechanism satisfies Assumption \ref{asp: branching mechanism}. 
+%    For example, the spatial motion in this paper is an Ornstein-Uhlenbeck process. 
+%    If the branching mechanism has finite second moment, we established some central limit theorems in \cite{RenSongZhang2015Central} for a class of superprocesses with general motions. 
+We have established some central limit theorems in \cite{RenSongZhang2015Central} for a class of superprocesses with general motions under the assumption that the branching mechanisms
+satisfy a second moment condition.
+    We hope to prove stable CLT's for superprocesses with general motions in a future project.
+
     Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z + \rho z^2+\eta z^{1+\beta}$ plus a small perturbation 
-    %For each $z\in \mathbb R_+$, define
 \begin{align}
@@
     where $\psi_1$ satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
-%DELETED
-%Then the branching mechanism can be rewritten as
-%\begin{equation}\label{decom-branchingMechanism}
-    %\psi(z) = -\alpha z + \rho z^2+\eta z^{1+\beta} + \psi_1(z),\quad  z \in \mathbb R_+,
-%\end{equation}
-%where $\alpha, \eta>0$, $\rho\geq 0$, $\beta\in(0,1)$. 
-%Assumption \ref{asp: branching mechanism} is equivalent to that the branching mechanism is given in the form of \eqref{decom-branchingMechanism} with $\psi_1=\psi^+_1-\psi^-_1$, where $\psi^+_1=\int_{(0,\infty)}(e^{-yz}-1+yz)\nu^+(dy)$, and $\psi^-_1=\int_{(0,\infty)}(e^{-yz}-1+yz)\nu^-(dy)$ with $\nu^+$ and $\nu^+$ being measures on $(0,\infty)$ such that
-%$$\int_{(0,\infty)}(y^{1+\beta +\delta}\wedge y^2)(\nu^++\nu^-)(dy)<\infty$$ for sufficient small $\delta>0$. 
-%Basically, our  Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z + \rho z^2+\eta z^{1+\beta}$ plus a a small perturbation $\psi_1$.
     It would be interesting to consider more general branching mechanism.
 
-%DELETED
-%Our results show that he behavior of $\psi(z)+\alpha z$ near $z= 0$ plays the dominating role. 
-%The limit and the normalization only depend on $\eta z^{1+\beta}$. It is interesting to consider more general branching mechanism.
-%END DELETED
-
-%We wend this section with some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-    Some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism} are the following:
-    %If $\varphi$ is a complete Bernstein function which is regularly varying at 0 with index
+%    Some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism} are the following:
+Here are some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}:
     If $h$ is a complete Bernstein function which is regularly varying at 0 with index
@@
 $$
-%\psi(z):=-\alpha z + \rho z^2+\eta z^{1+\beta}+z\varphi(z), \qquad z>0
     \psi(z):=-\alpha z + \rho z^2+\eta z^{1+\beta}+zh(z), \qquad z>0
@@
 
-%NEW ADDED
     The rest of the paper is organized as follows: In Subsection \ref{sec: branching mechanism} we will give some preliminary results for our branching mechanism $\psi$.
-    In Subsection \ref{sec: controller} and \ref{sec: h-controller} we will give several estimations for the operators related to the super-OU process $X$ that will be used in our proofs.
-    In Subsection \ref{sec: stable distributions} we will give the definition of all the $(1+\beta)$-stable random variables involved in this paper. 
-    In Subsection \ref{sec: Small value probability} we will give estimations for the small value probability of continuous state branching processes.
+    In Subsections \ref{sec: controller} and \ref{sec: h-controller} we will give some estimates for some operators related to the super-OU process $X$ that will be used in our proofs.
+    In Subsection \ref{sec: stable distributions} we will give the definitions of all the $(1+\beta)$-stable random variables involved in this paper. 
+    In Subsection \ref{sec: Small value probability} we will give some estimates for the small value probability of continuous state branching processes.
 In Subsection \ref{sec: Moments for super-OU processes} we will give upper bounds for the $(1+\gamma)$-moments for our superprocesses.
-    These estimations and upper bounds will be crucial in the later proofs.
+    These estimates and upper bounds will be crucial in the proofs of our main results.
     In Subsection \ref{sec: large rate lln}, we will give the proof of Theorem \ref{thm: law of large number}.
@@
     In Subsection \ref{sec: large rate clt}, we will give the proof of Theorem \ref{thm: large clt}.
-    In the Appendix, we consider a general superprocess $(X_t)_{t\geq 0}$, and we prove there that the characteristic exponent of $\langle f,X_t\rangle$ will satisfy a complex-valued non-linear integral equation.
-    This fact will be used at several places in this paper, and we think it should be of independent interests.
+    In the Appendix, we consider a general superprocess $(X_t)_{t\geq 0}$, and we prove there that the characteristic exponent of $\langle f,X_t\rangle$ satisfies a complex-valued non-linear integral equation.
+    This fact will be used at several places in this paper, and we think it is of independent interest.
 
@@
 \end{itemize}
-%END NEW ADDED
 
@@
 \label{sec: branching mechanism}
-	Let $\psi$ be the branching mechanism given by \eqref{eq: honogeneou branching mechanism}.
+	Let $\psi$ be the branching mechanism given in \eqref{eq: honogeneou branching mechanism}.
 	Suppose that Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism} hold.
@@
 the uniqueness of holomorphic extensions, 
-	we have that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
+	we know that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
 	The extended $\psi_1$ has the following form:
@@
 	\\&\quad + |z|^{1+\beta +\delta}\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|,
-%ADDED
     \quad z \in \mathbb C_+,
-%END ADDED
 \end{align}
@@
 \label{lem: LlogL criterion}
-If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies the $L \log L$ criterion, i.e.,
+If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies 
+%the $L \log L$ criterion, i.e.,
+the $L \log L$ condition, i.e.,
 \[
@@
 \]
-	Therefore, we have
+	Therefore we have
 \[
@@
 \label{sec: controller}
-	Denote by $\mathcal B(\mathbb R^d, \mathbb C)$ the space of all $\mathbb C$-valued Borel measurable functions on $\mathbb R^d$.
-	Recall that $\mathcal P$ is given by \eqref{eq: polynomial growth function}.
+	Denote by $\mathcal B(\mathbb R^d, \mathbb C)$ the space of all $\mathbb C$-valued Borel functions on $\mathbb R^d$.
+	Recall that $\mathcal P$ is defined in \eqref{eq: polynomial growth function}.
     Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
@@
     (4). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
-    then we have the following:
+%    then we have the following:
+Then we have the following:
 \begin{itemize}
@@
     both functions $\psi$, $\psi_0$ can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C^0_+$.
-    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, we define
+    For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, we define
 \begin{align}
@@
 \end{align}
-       For each $t\geq 0$ and $f\in \mathcal P$, we define
+       For all $t\geq 0$ and $f\in \mathcal P$, we define
 \begin{align}
@@
     &:= \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
-    %\\ K_t f
     \\ Z'''_t f
@@
     = Z'_t + Z''_t
-    %= Z_t+K_t, \quad t\geq 0.
     = Z_t+Z'''_t, \quad t\geq 0.
@@
 \label{lem: upper bound for usgx}
-        Under Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}, the following statements are true:
+        Under Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}, the following statements are true:
 \begin{itemize}
@@
 \item[(7)]
-       %For any $\delta > 0$ small enough, we have that $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
        For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
@@
 
-    %(7). Since $K_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from parts (5)-- (6) of this lemma  and Lemma \ref{lem: property of controllable operators}.(3).
     (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from parts (5)-- (6) of this lemma  and Lemma \ref{lem: property of controllable operators}.(3).
@@
    Recall that
-    $(P^\alpha_t)_{t\geq 0}$ is given by \eqref{eq: meansemigroup}, $\mathcal P$ is given by \eqref{eq: polynomial growth function}, $\mathcal N$ is given by \eqref{eq: def of N} and $\mathcal C_l$ is given by \eqref{eq: def of Cl}.
+    $(P^\alpha_t)_{t\geq 0}$ is defined in \eqref{eq: meansemigroup}, $\mathcal P$ is defined in \eqref{eq: polynomial growth function}, $\mathcal N$ is given by \eqref{eq: def of N} and $\mathcal C_l$ is defined in \eqref{eq: def of Cl}.
 \begin{lem}
@@
 \item
-	Suppose that $f\in\mathcal{P}$. Then the following integrals are well defined:
+%	Suppose that $f\in\mathcal{P}$. Then the following integrals are well defined:
+If $f\in\mathcal{P}$, then the following integrals are well defined:
 \[
@@
 \item
-    Suppose that $f\in\mathcal C_l$. Then the following integrals are well defined:
+%    Suppose that $f\in\mathcal C_l$. Then the following integrals are well defined:
+If $f\in\mathcal C_l$, then the following integrals are well defined:
 \[
     \bar{m}_t[f]
-    %:= \eta \int_{t}^{t+1} e^{\alpha s}~ds \int_{\mathbb R^d}\big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx, \quad t\geq 0.
     := \eta \int_{t-1}^{t} e^{\alpha s}~ds \int_{\mathbb R^d}\big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx, \quad t\geq 1.
@@
 \end{equation}
-	where $K:=\sup\{k\in \mathbb N : \alpha\beta>k(1+\beta)b\}$.
-\item
-    Suppose that $f \in \mathcal C_l$.
-    Then the following integral is well defined:
+%	where $K:=\sup\{k\in \mathbb N : \alpha\beta>k(1+\beta)b\}$.
+where $K$ is defined in \eqref{eq: def of N}.
+\item
+%    Suppose that $f \in \mathcal C_l$.
+%    Then the following integral is well defined:
+If $f \in \mathcal C_l$, then the following integral is well defined:
 \[
@@
     \bar{m}[f]
-    %=\sum_{n=0}^{\infty}\bar{m}_n[f].
     =\sum_{n=1}^{\infty}\bar{m}_n[f].
@@
 \item
-	Suppose that $f \in \mathcal{P}$ satisfies  $\alpha\beta=\kappa_f b(1+\beta)$. Then the following integral is well defined:
+%	Suppose that $f \in \mathcal{P}$ satisfies  $\alpha\beta=\kappa_f b(1+\beta)$. Then the following integral is well defined:
+If $f \in \mathcal{P}$ satisfies  $\alpha\beta=\kappa_f b(1+\beta)$, then the following integral is well defined:
 \[
@@
 \item
-	Suppose that $f\in \mathcal{P}$ satisfies $\alpha\beta<\kappa_fb(1+\beta)$.
-	Then the following integral is well defined:
+%	Suppose that $f\in \mathcal{P}$ satisfies $\alpha\beta<\kappa_fb(1+\beta)$.
+%	Then the following integral is well defined:
+If $f\in \mathcal{P}$ satisfies $\alpha\beta<\kappa_fb(1+\beta)$, then the following integral is well defined:
 \[
@@
 
-    (2). We first claim that there exists $h\in \mathcal{P}$ such that,
+    (2). We first claim that there exists $h\in \mathcal{P}$ such that
 \[
@@
 \end{equation}
-    Therefore, there exists constant $C>0$ such that
+    Therefore there exists a constant $C>0$ such that
 \begin{align}
@@
 \label{prop: alpha stable rv}
-%   For all $t\geq 0$ and $f\in \mathcal P$,
 	For all $t\geq 0$ and non-trivial $f\in \mathcal P$,
@@
 \end{prop}
-    This proposition says that the $(1+\beta)$-stable random variables  in Theorem \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
+    This proposition says that the $(1+\beta)$-stable random variables  in Theorems \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
     The proof of this proposition relies on the following lemma:
@@
       \] 
-      is a $(1+\beta)$-controllable operator on $\mathcal P$.
+%      is a $(1+\beta)$-controllable operator on $\mathcal P$.
+ is a $\theta^{1+\beta}$-controllable operator on $\mathcal P$.
 	    This implies that \[ x \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f(x)|^{1+\beta}~ds\] is an element of $\mathcal P$.
@@
 	Since $f$ is non-trivial, 
-%DELETED
-    %by \cite[(2.24)]{RenSongZhang2014Central}, 
-%END DELETED
     the integral on the left-hand side of \eqref{eq: what I want to proof} is positive.
@@
 \end{align}
-	%In fact, if we put $h_1(x)=\Big|\sum_{p\in \mathcal N}\langle g, \phi_p\rangle_\varphi\frac{\partial}{\partial x_i}\phi_p(x)\Big| \in \mathcal P$, then
     In fact, if we put $h_1(x)=\sum_{p\in \mathcal N}|\langle g, \phi_p\rangle_\varphi\frac{\partial \phi_p}{\partial x_i}(x)| \in \mathcal P$, then
@@
 \end{align}
-%NEW ADDED
-    We have the following well-known results for the OU semigroup: 
+%    We have the following well-known results for the OU semigroup: 
+It is well known that
 \[
@@
     It is clear that the above equality also holds for each $f\in \mathcal P$.
-    From this, it can be checked that for each $f \in \mathcal P$ such that $f$ is differentiable with $|\nabla  f| \in \mathcal P$, we have
+%    From this, it can be checked that for each $f \in \mathcal P$ such that $f$ is differentiable with $|\nabla  f| \in \mathcal P$, we have
+From this, one can easily check that for each differential $f \in \mathcal P$ with $|\nabla  f| \in \mathcal P$, we have
 \[
@@
 \]
-    Note that if $g \in \mathcal C_l$, then we do have $g^{1+\beta}\in \mathcal P$ and $|\nabla (g^{1+\beta})| \in \mathcal P$.
+    Note that if $g \in \mathcal C_l$, then $g^{1+\beta}\in \mathcal P$ and $|\nabla (g^{1+\beta})| \in \mathcal P$.
     Therefore, 
@@
 \end{align}
-    Using \eqref{eq: supper for Itf}, \eqref{ineq: control of partial derivative of Itg} and above, we have that there exists a bounded function $a$ on $[0,1]$ and an $h_2 \in \mathcal P$ such that
+    Using \eqref{eq: supper for Itf}, \eqref{ineq: control of partial derivative of Itg} and the above, we have that there exist a bounded function $a$ on $[0,1]$ and an $h_2 \in \mathcal P$ such that
 \begin{equation}
@@
 \] 
-    According to this and \cite[Theorem A.5.2.]{Durrett2010Probability} we have
+%    According to this and \cite[Theorem A.5.2.]{Durrett2010Probability} we have
+Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, we can get
 \[
@@
 \]
-    Therefore, using \eqref{eq: key estimation for partial} and above, there exists a constant $C> 0$ such that for all $t\geq 0$, 
+    Therefore, using \eqref{eq: key estimation for partial} and the above, there exists a constant $C> 0$ such that for all $t\geq 0$, 
 \begin{align}
@@
 \end{align}
-%END NEW ADDED
-%DELETED
-    %According to \eqref{ineq: control of Itg} and \eqref{ineq: control of partial derivative of Itg}, we easily get there exists $h_2 \in \mathcal P$ such that for all $t\geq 0$,
-%\begin{align}
-    %&\Big|\frac{\partial}{\partial x_i}\bar{g}_t(x)\Big| 
-    %= e^{(\alpha-Kb)(1+\beta)t}\Big|\frac{\partial}{\partial x_i}Z_1(-I_tg)\Big| \\
-    %& = (1+\beta) \eta e^{(\alpha-Kb)(1+\beta)t}\Big |\int_0^1 P_{1-s}^{\alpha}\Big((iP_s^{\alpha} I_tg)^{\beta}\cdot i P_s^{\alpha}(\frac{\partial}{\partial x_i}I_tg(x))\Big)~ds\Big| \\
-    %& \leq (1+\beta) \eta  e^{(\alpha-Kb)(1+\beta)t}
-    %\int_0^1 P_{1-s}^{\alpha}\Big((P_s^{\alpha} |I_tg|)^{\beta}\cdot P_s^{\alpha}(\big|\frac{\partial}{\partial x_i}I_tg(x)\big|)\Big)~ds \\
-    %& \leq h_2(x).
-%\end{align}
-%END DELETED
-%Therefore, there exists $h_3 \in \mathcal P$, such that
-Therefore, there exists constants $c,n>0$ such that 
+Therefore there exist constants $c,n>0$ such that 
 \begin{align}\label{ineq: control of sup gt}
-    %\sup |\nabla \bar g_t (z)| \leq h_3(x)+h_3(y),
-    %\quad t\geq 0,~ x,y \in \mathbb R^d,
     |\nabla \bar g_t (z)| 
@@
 \end{align}
-%NEW ADDED
-    Denote by
+    Define
 \[
@@
 \]
-    Then for each $x,y\in \mathbb R^d$, $D(x,y)$ is a convex set on $\mathbb R^d$. 
+    Then for all $x,y\in \mathbb R^d$, $D(x,y)$ is a convex set on $\mathbb R^d$. 
     In particular, it contains the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$ for each $s\geq 0$.
-    Also, observe that 
+    Also, note that 
 \[
@@
 \]
-    By the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we may now write for each $s,t\geq 0, x\in \mathbb R^d$
+    By the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we get that for each $s,t\geq 0, x\in \mathbb R^d$,
 \begin{align}
@@
 \end{align}
-%END NEW ADDED
-%Deleted
-%where supermum is taken over $z$ in the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$.
-%By the fact $\langle \bar{g}_t,\varphi\rangle = 0$, we may write
-%\begin{align}
-    %&|P_s\bar{g}_t| = \Big|\int_{\mathbb R^d} \big(\bar {g}_t(xe^{-bs}+y\sqrt{1-e^{-2bs}})-\bar {g}_t (y)\big) \varphi(y)~dy \Big| \\
-    %& \leq \int_{\mathbb R^d} \sup |\bigtriangledown \bar g_t (z)|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy \\
-    %& \leq \int_{\mathbb R^d} ( h_3(x)+h_3(y))|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy.
-%\end{align}
- %We get the conclusion by the fact that there exists $h_4 \in \mathcal P$ such that
-%\begin{align}
-    %\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big|\leq e^{-bs}(h_4(x)+h_4(y)),
-    %\quad s\geq 0,~x,y \in \mathbb R^d.
-%\end{align}
 \end{proof}
@@
     Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$ 
-    when $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
+    when $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
     Suppose that Grey's condition is satisfied, i.e., there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-    Also suppose that the $L \log L$ criterion is satisfied, i.e.,
+%    Also suppose that the $L \log L$ criterion is satisfied, i.e.,
+    Also suppose that the $L \log L$ condition is satisfied, i.e.,
 \[
@@
 \label{lem: control of XT}
-    Suppose that $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
+    Suppose that $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
     Then, for each $x\geq 0$, there exist constants $C,\delta>0$ such that
@@
 \end{equation}
-    It is known, see \cite[Theorems 3.5-3.8]{Li2011Measure-valued} for example, that under Grey's condition, the following statements are true:
+    It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, the following statements are true:
 \begin{itemize}
@@
 \item
-    if $\lambda \in (0,\bar v)$ then $0<\lambda \leq v_t(\lambda)<\bar v $ and
+    if $\lambda \in (0,\bar v)$, then $0<\lambda \leq v_t(\lambda)<\bar v $ and
 \begin{align}
@@
 \item
-    if $\lambda \in (\bar v, \infty)$ then $\bar v < v_t(\lambda)\leq \lambda< \infty $ and
+    if $\lambda \in (\bar v, \infty)$, then $\bar v < v_t(\lambda)\leq \lambda< \infty $ and
 \[
@@
 
-    Step 2. We will show that, for each $x \geq 0$ there exists a constant $C>0$ such that
+    Step 2. We will show that, for each $x \geq 0$ there exists a constant 
+    %$C>0$ such that
+    $c_1>0$ such that
 \[
     \mathbf P_{x}(0< W_t\leq k_t)
-    \leq C\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
+%    \leq C\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
+     \leq c_1\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
     \quad t\geq 0.
@@
 
-    Step 3. We will show that there exist constants $c, \delta, t_0 > 0$ such that
+    Step 3. We will show that there exist constants 
+    %$c, \delta, t_0 > 0$ such that
+    $c_2, \delta_1, t_0 > 0$ such that
 \[
     |\bar v_t-\bar v|
-    \leq ce^{-\delta t},
-    \quad t\geq t_0.
+%    \leq ce^{-\delta t},    \quad t\geq t_0.
+    \leq c_2e^{-\delta_1 t},    \quad t\geq t_0.
 \]
@@
 \begin{align}
-    &t-t_0 = \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)}
+    &t-t_0 = 
+    \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)}
     =\int_{\bar v_t}^{z_0} \frac{dz}{\psi(z)}
@@
 
-    Step 4: We will show that there exist constant $C, \delta,t_0>0$ such that
-\[
-    |\bar v - v_t(k_t^{-1} e^{-\alpha t})|\leq Ck_t^\delta, \quad t\geq t_0.
+    Step 4: We will show that there exist 
+    %constant $C, \delta,t_0>0$ such that
+    constants $c_3, \delta_2, t_1>0$ such that
+\[
+    |\bar v - v_t(k_t^{-1} e^{-\alpha t})|\leq 
+    %Ck_t^\delta, \quad t\geq t_0.
+    c_3k_t^{\delta_2}, \quad t\geq t_1.
 \]
@@
 \]
-    and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
-    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate positive random variable.
-This implies that
+    and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, 
+    we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
+%    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for
+    Since the $L\log L$ condition is satisfied, we have (see \cite{LiuRenSong2009Llog} for
+ example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate positive random variable. This implies that
 \[
@@
 \]
-    The $L \log L$ criterion also guarantees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.
-in $\mathbf P_1$.
-This and the non-degeneracy of $W_\infty$ imply that
+%    The $L \log L$ criterion also guarantees that (see again \cite{LiuRenSong2009Llog} 
+    The $L \log L$ condition also guarantees that (see again \cite{LiuRenSong2009Llog} 
+    for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s. in $\mathbf P_1$. This and the non-degeneracy of $W_\infty$ imply that
 \[
@@
 \]
-    Therefore, there exist constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$,
+    Therefore, there exist 
+    %constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$,
+    constants $c_3>0$ and $t_1>0$ such that for all $t\geq t_1$,
 \[
     \bar v - v_t(k_t^{-1} e^{-\alpha t}) \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
-    \leq Ck_t^{\frac{\tau - \epsilon}{\alpha}}.
+%    \leq Ck_t^{\frac{\tau - \epsilon}{\alpha}}.
+   \leq c_3k_t^{\frac{\tau - \epsilon}{\alpha}}.
 \]
@@
 
-    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exist constant $C, \delta, t_0 > 0$ such that
-\[
-    \mathbf P_{x}(0< W_t\leq k_t) \leq C(k_t^{\delta}+e^{-\delta t}),\quad t\geq t_0.
-\]
-Note that the left side is always bounded by $1$, so we can take $t_0 =0$ in the above statement.
+    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exist 
+    %constant $C, \delta, t_0 > 0$ such that
+    constant $c_4, \delta_3, t_2 > 0$ such that
+\[
+    \mathbf P_{x}(0< W_t\leq k_t) \leq 
+    %C(k_t^{\delta}+e^{-\delta t}),\quad t\geq t_0.
+    c_4(k_t^{\delta_3}+e^{-\delta_3 t}),\quad t\geq t_2.
+\]
+Note that the left side is always bounded by $1$, so we can take $t_2 =0$ in the above statement.
 \end{proof}
@@
 \end{proof}
-    %ADDED
     For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write its $L_p$-norm as
@@
 \]
-    %END ADDED
 \begin{lem}
@@
 
-%\subsection{The large rate regime}
-\subsection{The large rate regime: law of large numbers}
+\subsection{The large branching rate regime: law of large numbers}
 \label{sec: large rate lln}
@@
 \end{equation}
-%ADDED
     where $P_t^{ab} := e^{abt}P_t$.
-%END ADDED
     For $0\leq s\leq t$, we have
@@
     It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb R^d)$.
-    %There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
     There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, we have $\alpha\gamma>|p|(1+\gamma)b$.
@@
 \begin{lem}\label{lem: control of wt}
-    %For all $\gamma\in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists $C> 0$ such that for all $0\leq s<t$,
     Let $\mu\in \mathcal M_c(\mathbb R^d)$. 
-    For each $\gamma\in (0,\beta)$ and $p\in \mathbb{Z}_+^d$ with $\alpha \gamma > |p|b(1+\gamma)$, there exists $C> 0$ such that for all $0\leq s<t$,
+    For all $\gamma\in (0,\beta)$ and $p\in \mathbb{Z}_+^d$ with $\alpha \gamma > |p|b(1+\gamma)$, there exists $C> 0$ such that for all $0\leq s<t$,
 \[
@@
     \mathbb{P}_{\mu}\Big[\big|e^{(\alpha-|p|b)(t-s)}\langle\phi_p, X_s\rangle-e^{(\alpha-|p|b)(t-r)}\langle\phi_p, X_r\rangle\big|^{1+\gamma}\Big]
-    %\leq C_1e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b\gamma}.
     \leq C_1e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b)}.
@@
 
-    %{\it Proof of Theorem \ref{thm: law of large number}.}\quad
 \begin{proof}[Proof of Theorem \ref{thm: law of large number}]
@@
 	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-%	\leq C e^{-\delta t},
 	\leq C_1 e^{-\delta_1 t},
@@
 \item
-	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above, and the fact that \[\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above and the fact that \[\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
 	\leq \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C_5, \delta_2 >0$ such that
@@
 	Step 2.
-	%We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$, we will show that $J_t$ converges to $0$ almost surely.
     We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$. 
@@
 \end{align}
-	%Notice that $\kappa_{(L+a_0 b)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
     Notice that $\kappa_{(L+a_0 b)\tilde{f}}\geq \kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
@@
     \leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    %\leq C(e^{-\delta t}+\frac{1}{\delta}),
     \leq C_6(e^{-\delta_3 t}+\frac{1}{\delta_3}),
@@
 
-\subsection{The critical rate regime}
+\subsection{The critical branching rate regime}
 \label{sec:critical}
@@
     J_1(t,k,\epsilon)
-    %&:= \mathbb{P}_{\mu}\big[|\langle K_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
     &:= \mathbb{P}_{\mu}\big[|\langle Z'''_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
@@
 \end{align}
-    %In fact, it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
-    %In fact, it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $Z'''_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
     In fact, it follows from \eqref{eq: key equality}, the definitions of $U_1$, $Z'''_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
@@
     \\&=e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}
-    %=e^{\langle (Z_1 + K_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
     =e^{\langle (Z_1 + Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
@@
     \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{e^{\alpha}m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon)
-    %\\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
     \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (Z_1+Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
-    %\\& \leq \mathbb{P}_{\mu}\big[|\langle (U_1 - i T_1^\alpha)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
     \\& \leq \mathbb{P}_{\mu}\big[|\langle (Z_1+Z'''_1)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
@@
 \begin{align}
-    %& |K_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
     & |Z'''_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
@@
 \end{align}
-    %Therefore, it follows from \eqref{eq: prevJ2} that there exists constant $C_3>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
     Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$, we have
@@
     a_k
-    %:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
     :=\Big(\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\Big) \times \mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
 \]
-    %where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
     where by convention the first product is $1$ for $k=-1$. Then we get for each $k > -1$,
@@
     &a_{k-1} - a_k
-    %\\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
     \\&=\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
@@
 \end{align}
-    %According to Proposition \ref{prop: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
     According to Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
@@
 
-%{\it Proof of Theorem \ref{thm: critical clt}.}\quad
 \begin{proof}[Proof of Theorem \ref{thm: critical clt}]
@@
     \\ &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big) +
-    \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
+    \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
     \\&=:I_1(t)+I_2(t) + I_3(t),
@@
 \end{align}
-    %According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\zeta$ under $\tilde {\mathbb P}_\mu$.
     According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\tilde \zeta$ under $\tilde {\mathbb P}_\mu$.
@@
 \]
-%ADDED
     Recall that $H_t := e^{-\alpha t}\|X_t\|$.
-%END ADDED
     Define for all $k \geq 0$ and $t\geq k+1$,
@@
     \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]
-    %\\&\quad +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
     \\&\quad +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
     \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}
-    %\\&\quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
     \\&\quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
@@
     &\Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
-    %\leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
     \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|
@@
     \\&\leq C_6 e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}
-    %\\&= C_6 e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k-1)},
     \\&= C_6 e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)},
@@
     \leq C_8\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{-\delta_6(t-k)}
-    %= C_8 e^{-\delta t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta_6 k}
     = C_8 e^{-\delta_6 t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta_6 k}
-    %\\&\leq C_9 e^{-\delta t}e^{\delta_6 (t-\ln t)}
     \\&\leq C_9 e^{-\delta_6 t}e^{\delta_6 (t-\ln t)}
@@
 \begin{equation}
-    %\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t}), \quad t\geq0.
     \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t}), \quad t\geq0.
@@
 
-\subsection{The small rate regime}
+\subsection{The small branching rate regime}
 \label{sec: small rate}
 
-    In this subsection, we prove the central limit theorem for the small rate regime.
-
-%{\it Proof of Theorem \ref{thm: small clt}.}\quad
+    In this subsection, we prove the central limit theorem for the small branching rate regime.
+
 \begin{proof}[Proof of Theorem \ref{thm: small clt}]
@@
 \]
-    %Let $\theta\in \mathbb R$.
     Fix a $\theta\in \mathbb R$.
@@
     = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta})
-    %= \alpha(1-\frac{\gamma}{1+\gamma}) - \alpha(1-\frac{\beta}{1+\beta})
     \\&> \frac{\gamma \alpha}{1+\gamma} - k_f b
@@
 	A_t(\epsilon)
-	%=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
     :=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
@@
     &|\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
-    %\leq 2\mathbb{\tilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<e^{-\epsilon t})
     \leq 2\mathbb{\tilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})
-    %\\&\leq C_5(e^{-\epsilon\delta_4 t}+e^{-\delta_4 t}).
     \\&\leq C_5(e^{-\epsilon\delta_4 t}+e^{-\delta_4 t}),
@@
 \begin{align}
-    %&|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
     &\big|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)}]\big|
-    %\leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)^c}\big]
     \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)}\big]
@@
 \end{align}
-	%The proof is complete.
 \end{proof}
-%\subsection{Proof of Theorem \ref{thm: large clt}}
-\subsection{The large rate regime: CLT}
+\subsection{The large branching rate regime: CLT}
 \label{sec: large rate clt}
@@
 
-    %Recall that $\{H^p_t, \mathscr{F}_t\}_{t\geq 0}, p\in \mathbb{Z}_+^d,$ are defined before Lemma \ref{lemma26}.
     Recall that $H^p_t$ are defined before Lemma \ref{lemma26}. We write $a_p:= \langle \phi_p, g\rangle_\varphi$ for each $p \in \mathbb Z_+^d$.
@@
     \bar{\gamma}_{t,n}:=\sum_{p\in\mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}
-    %\xrightarrow{d}\bar{\zeta}_n,
     \xrightarrow[t\to \infty]{d}\bar{\zeta}_n,
 \end{align}
-    %where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function
     where $\bar{\zeta}_n$ is an $(1+\beta)$-stable random variable with characteristic function
 \begin{align}
-    %\mathbf{E}[e^{i\theta \bar{\zeta}_n}]=\exp[\bar{m}_n[\theta g]],\quad \theta\in \mathbb{R}.
     \mathbf{E}[e^{i\theta \bar{\zeta}_n}]=\exp(\bar{m}_n[\theta g]),\quad \theta\in \mathbb{R}.
@@
 \begin{proof}
-    %We fix $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$.
     Fix $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$.
@@
     Put $\theta_{t,p,n}:=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and 
-    %$A_t(\epsilon):=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
     $A_t(\epsilon):=\{\|X_t\| > e^{(\alpha-\epsilon)t}\}$.
@@
 	J'_1(t,n,\epsilon)
-	%&:= \mathbb{P}_{\mu}\big[|\langle K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big],
     &:= \mathbb{P}_{\mu}\big[|\langle Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big],
@@
 \end{align}
-    %It follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$ that
     In fact, it follows from \eqref{eq: key equality} that
@@
     =\mathbb{P}_{\mu}[e^{i\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p,X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle)}|\mathscr{F}_{t+n-1}]
-    %\\&=\displaystyle e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
     \\&=\displaystyle e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
@@
 \]
-    %we have for all $n\geq 1, t\geq 0, \epsilon> 0$,
     we have for all $n\geq 1, t\geq 0$ and $\epsilon> 0$,
@@
     \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}| \mathscr F_{t+n-1}]-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big] + J'_3(t,n,\epsilon)
-    %\\&=\mathbb{P}_{\mu}\Big[\big|e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
     \\&=\mathbb{P}_{\mu}\Big[\big|e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
-    %\\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}
     \\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}
@@
     Step 2.
-    %We will show that for $\epsilon>0$ small enough, there exist constants $C_1,\delta_1>0$ such that for all $n\geq 1, \, t\geq 0$,
     We will show that for $\epsilon>0$ small enough, there exist constants $C_1,\delta_1>0$ such that for all $n\geq 1$ and $t\geq 0$,
@@
 \end{align}
-	%Let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the $(\theta^{1+\beta}\vee \theta^{1+\beta+\delta_0})$-controller. 
     Let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
@@
 \begin{align}
-    %& |K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
     & |Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
@@
     \\&\leq R \Big(\frac{\sum_{p\in\mathcal{N}}|a_p|e^{-(\alpha-|p|b)n}|\phi_p|}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)
-    %\\&\leq \sum_{\rho\in\{\delta_0,1\}}\Big(\frac{e^{-(\alpha-Kb)n}}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)^{1+\beta+\rho}R|h|
     \\&\leq \sum_{\rho\in\{\delta_0,1\}}\Big(\frac{e^{-(\alpha-Kb)n}}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)^{1+\beta+\rho}Rh
-    %\\&=\sum_{\rho\in\{\delta_0,1\}}e^{-\alpha\frac{1+\beta+\rho}{1+\beta}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha\beta-K(1+\beta)b)n}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|
     \\&=\sum_{\rho\in\{\delta_0,1\}}e^{-\alpha\frac{1+\beta+\rho}{1+\beta}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha\beta-K(1+\beta)b)n}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}Rh
-    %\\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|,
     \\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}Rh,
@@
     where $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-    %Thus for all $n\geq 1,  t\geq 0, \epsilon > 0$,
     Thus, there exists constant $C_3>0$ such that for all $n\geq 1,  t\geq 0$ and $\epsilon > 0$,
@@
 \end{align}
-%ADDED
     By choosing $\epsilon>0$ small enough, we get the desired result in this step.
-%END ADDED
 
     Step 3.
-	%We will show that for each $\epsilon$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$,
     We will show that for each $\epsilon > 0$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$,
@@
 \end{align}
-    %Therefore, for all $t\geq 0, n\geq1$,
     Therefore, for all $t\geq 0, n\geq1$ and $\epsilon > 0$,
@@
 	&\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}
-    [\langle \bar {g}_n, X_{t+n-1}\rangle].
+    [\langle \bar {g}_n, X_{t+n-1}\rangle],
 \end{align}
@@
 \end{align}
-%ADDED
     Fix a $\gamma>0$ small enough such that $\alpha \gamma < (1+\gamma)b$.
-%END ADDED
     Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment}.(3) with $\kappa=1$, there exists $C_3>0$ such that
@@
     \mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]
-    %\leq C_3e^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
     \leq C_3e^{\frac{\alpha}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
 \end{align}
-    %Therefore, for all $t\geq 0, n\geq1$,
     Therefore, for all $t\geq 0, n\geq1$ and $\epsilon >0$,
@@
 \end{align}
-%ADDED
     Now, by choosing $\epsilon >0$ small enough, we get the desired result in this step.
-%END ADDED
-
-	%Step 4. Using an argument similar to that used in Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we can show that for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that
+
     Step 4. According to the Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that
@@
 \begin{align}\label{ineq: next we will need}
-    %\Big|\tilde{\mathbb{P}}_{\mu}\Big[\prod_{n=1}^m\exp(i\theta\bar{\gamma}_{t,n})-\prod_{n=1}^m\exp(\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t}.
     \bigg|\tilde{\mathbb{P}}_{\mu}\Big[\prod_{l=1}^m\exp(i\theta\bar{\gamma}_{t,l})-\prod_{l=1}^m\exp(\bar{m}_l[\theta g])\Big]\bigg|\leq C e^{-\delta t}.
@@
 \begin{proof}
-    %Step 1. 
     Step 1. Fix $\theta \in \mathbb R$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
@@
     Step 2.
-    %Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$.
     Fix $t\geq 0$ and $m\in \mathbb{N}$.
-    %For each $n=1,\cdots,m$, we define
     For each $n=0,\cdots,m$, we define
@@
     \tilde{a}_n
-    %:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big),
     :=\mathbb{\tilde{P}}_{\mu}\Big[\prod_{l=0}^{n}\exp(i\theta\bar{\gamma}_{t,l})\Big] \times \prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g]),
 \] 
-    %where by convention the product is $1$ for $n=0$. Then we get for each $n \ge 1$,
     where by convention the first product is $1$ for $n=0$. Then we get for each $n \ge 1$,
@@
     &\tilde{a}_{n-1} - \tilde{a}_n
-    %\\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\Big(e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}}\Big);D^c\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
     \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times (e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}});D^c\Big] \times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
-    %\\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
     \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times \mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
@@
 \begin{proof}
-%ADDED
     Fix a $\theta \in \mathbb R$ and a $\mu \in \mathcal M_c(\mathbb R^d)$.
-%END ADDED
     According to \cite[Lemma 3.4.3]{Durrett2010Probability},
@@
     :=e^{i\theta\tilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},
-    %\quad t\geq 0, n\geq 1, \theta\in \mathbb{R}.
     \quad t\geq 0, n\geq 1.
@@
     Step 2.
-    %We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C_2,\delta_2 > 0$ such that for all $n\geq 1$ and $t\geq 0$,
     We will show that there exist $C_2,\delta_2 > 0$ such that for all $n\geq 1$ and $t\geq 0$,
@@
 \end{align}
-    %According to Lemma \ref{lem: control of wt}, there exist constants $C_4,C_5>0$ such that  for all $t\geq 0$ and $n\geq 1$,
     According to Lemma \ref{lem: control of wt}, there exist constants $C_4>0$ such that  for all $t\geq 0$ and $n\geq 1$,
@@
     &=C_4|\theta|\sum_{p\in\mathcal{N}}|a_p|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}\cdot e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(n-1)}.
- %DELETED   
-    %\\&\leq C_5|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}.
-%END DELETED
 \end{align}
@@
 \begin{proof}
-%ADDED
     Fix $\theta \in \mathbb R$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\epsilon \in (0,\alpha)$ and $\gamma \in (0,\beta)$ with $\alpha \gamma > Kb(1+\gamma)$.
-%END ADDED
-    %Recall that $A_t(\epsilon)=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. 
     Recall that $A_t(\epsilon):=\{\|X_t\|> e^{(\alpha-\epsilon) t}\}$. 
@@
 \end{align}
-%DELETED
-    %Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ with $\alpha\gamma>Kb(1+\gamma)$.  
-%END DELETED
-    According to Lemma \ref{lem: control of wt}, there exist $C_2,C_3>0$ such that
+    According to Lemma \ref{lem: control of wt}, there exist $C_2,C_3>0$ 
+    %such that
+    such that for all $m\in \mathbb{N}, t\geq$, 
 \begin{align}\label{ineq: control of gamma_t on d}
@@
     &\leq C_2|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
-    &\leq C_3|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m},
-    %& \qquad\theta\in\mathbb{R}, m\in \mathbb{N}, \epsilon>0, t\geq 0.
-    \qquad m\in \mathbb{N}, t\geq 0.
+    &\leq C_3|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}
+%    e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m},
+%    \qquad m\in \mathbb{N}, t\geq 0.
+    e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m}.
 \end{align}
@@
 
-%{\it Proof of Theorem \ref{thm: large clt}.}\quad
 \begin{proof}[Proof of Theorem \ref{thm: large clt}]
-%ADDED
     Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta \in \mathbb R$.
-%END ADDED
     Let $\delta_0$ be the constant $\delta$ in Lemma \ref{lem: lemma04}.  
@@
 \end{align}
-    %According to Lemma \ref{lem: independency for large rate}, there exist $C_1,\delta_1>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$,
     According to Lemma \ref{lem: independency for large rate}, there exist $C_1,\delta_1>0$ such that for all $t\geq 0$,
@@
 \end{align}
-    %According to Lemma \ref{lem: lemma04}, there exists $C_2>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$,
     According to Lemma \ref{lem: lemma04}, there exists $C_2>0$ such that for all $t\geq 0$,
@@
  \end{align}
-    %According to Lemma \ref{lem: lemma05}, there exist $C_3,\delta_2,\delta_3>0$ such that for all $t\geq 0,\theta\in\mathbb{R}$,
     According to Lemma \ref{lem: lemma05}, there exist $C_3,\delta_2,\delta_3>0$ such that for all $t\geq 0$,
@@
     which says that \eqref{eq: estimate of exponential remaining} is true for $n = m + 1$.
-%DELETED    
-    %The proof is complete.
-%END DELETED
 \end{proof}
@@
 	Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic in $\mathbb C\setminus (-\infty,0]$. (We use the convention that  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
-    %Using  the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.
     Using the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg (z_1) + \arg(z_0)$.
@@
 \end{equation}
-    %is the unique solution to the equation
     is the unique locally bounded solution to the equation
@@
     The proof is similar to that of \cite[Lemma A.1.5]{Dynkin1993Superprocesses}. We include it here for the sake of completeness.
-%ADDED
     We first verify that \eqref{eq: expresion of g} is a solution.
-%END ADDED
     Notice that
@@
     In this subsection, we will give the definition of a general superprocess.
-    Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the weak topology.
-%ADDED
+    Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the topology of weak convergence.
     For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$, we use the following convention in this subsection:
@@
 \]
-%END ADDED
     A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
@@
 \begin{equation}
-    %\psi'(x,z):= - \rho_(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
     \psi'(x,z):= - \rho_1(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
@@
 \item
-    %$\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$;
     $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
@@
    \mathbb N_x[\langle W_t, f\rangle]   
-    %=\mathbf P_{\delta_x}[X_t(f)]
     =\mathbf P_{\delta_x}[\langle f, X_t\rangle]
@@
 \end{equation}
-    %It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
     It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_t(\theta f)(x)$ is continuous in $\theta$.
@@
     \\&= \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i \langle W_t, f\rangle} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i \langle X_t, f\rangle}] \pi(x,dy) \Big|
-    %\\ &\leq \|\rho_1\|_\infty + 2\rho(x)_2\mathbb N_x[\langle W_t, |f|\rangle]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge \langle X_t, |f|\rangle] \pi(x,dy)
     \\ &\leq \|\rho_1\|_\infty + 2\rho_2(x)\mathbb N_x[\langle W_t, |f|\rangle]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge \langle X_t, |f|\rangle] \pi(x,dy)
@@
 \item
-    Given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure $\{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
+    Given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure 
+%    $\{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ 
+\[ \{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}\]
+    is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
 \begin{equation}
@@
 \begin{equation}
-    %\frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]}
     \frac{\mathbf P_{\delta_x}[\langle X_t,f^{\pm}\rangle e^{i \langle X_t,f\rangle}]}{\mathbf P_{\delta_x}[\langle X_t,f^{\pm}\rangle ]}
-    %= \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i X_t(f)}].
     = \mathbf P_{\delta_x}[e^{i \langle X_t,f\rangle}] \mathbb N_x^{\langle W_t,f^{\pm}\rangle}[e^{i \langle X_t,f\rangle}].
@@
     From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
-    %Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
     Therefore, we can apply Lemma \ref{eq: complex FK} and get that
@@
 
-%\bibitem{AdamczakMilos2014U-statistics}
-%R.~Adamczak and P.~Mi{\l}o\'{s}, \emph{{$U$}-statistics of
-  %{O}rnstein-{U}hlenbeck branching particle system}, J. Theoret. Probab.
-  %\textbf{27} (2014), no.~4, 1071--1111.
-
 \bibitem{AdamczakMilos2015CLT}
@@
 
-%\bibitem{BansayeDelmasMarsalleTran2011Limit}
-%V.~Bansaye, J.~Delmas, L.~Marsalle, and V.~C. Tran, \emph{Limit theorems for
-  %{M}arkov processes indexed by continuous time {G}alton-{W}atson trees}, Ann.
-  %Appl. Probab. \textbf{21} (2011), no.~6, 2263--2314. \MR{2895416}
-
 \bibitem{ChenRenWang2008An-almost}
@@
 
- %\bibitem{ChenRenSongZhang2017Law} Z.-Q.
-Chen, Y.-X.
-Ren,  and T.
-Yang, \emph{Law of large numbers for branching symmetric Hunt processes with measure-valued branching rates},  J.
-Theoret.
-Probab.
-\text{30} (2017), no.~3, 898--931.
-
  \bibitem{ChenRenYang2019Skeleton} Z.-Q. Chen, Y.-X. Ren,  and T. Yang,
@@
 
-%\bibitem{EnglanderHarrisKyprianou2010Strong}
-%J.~Engl\"{a}nder, S.~C. Harris, and A.~E. Kyprianou, \emph{Strong law of large
-  %numbers for branching diffusions}, Ann. Inst. Henri Poincar\'{e} Probab.
-  %Stat. \textbf{46} (2010), no.~1, 279--298.
-
 \bibitem{EnglanderWinter2006Law}
@@
 
-%\bibitem{GrubelKabluchko2016A-functional}
-%R.~Gr\"{u}bel and Z.~Kabluchko, \emph{A functional central limit theorem for
-  %branching random walks, almost sure weak convergence and applications to
-  %random trees}, Ann. Appl. Probab. \textbf{26} (2016), no.~6, 3659--3698.
-
-%\bibitem{HartungKlimovsky2018The-phase}
-%L.~Hartung and A.~Klimovsky, \emph{The phase diagram of the complex branching
-  %brownian motion energy model}, Electron. J. Probab. \textbf{23} (2018).
-
 \bibitem{Heyde1970A-rate}
@@
 
-%\bibitem{IksanovKabluchko2016A-central}
-%A.~Iksanov and Z.~Kabluchko, \emph{A central limit theorem and a law of the
-  %iterated logarithm for the {B}iggins martingale of the supercritical
-  %branching random walk}, J. Appl. Probab. \textbf{53} (2016), no.~4,
-  %1178--1192.
-
-%\bibitem{IksanovKoleskoMeiners2018Fluctuations}
-%A.~Iksanov, K.~Kolesko, and M.~Meiners, \emph{Fluctuations of biggins'
-  %martingales at complex parameters}, arXiv:1806.09943, 2018.
-
 \bibitem{IksanovKoleskoMeiners2018Stable-like}
@@
 \bibitem{Milos2012Spatial}
-P.~Mi{\l}o{\'s}, \emph{Spatial {CLT} for the supercritical
-  {O}rnstein-{U}hlenbeck superprocess}, arXiv:1203.6661, 2012.
+P.~Mi{\l}o{\'s}, 
+%\emph{Spatial {CLT} for the supercritical
+%  {O}rnstein-{U}hlenbeck superprocess}, arXiv:1203.6661, 2012.
+\emph{Spatial central limit theorem for supercritical superprocesses}, 
+ J. Theoret. Probab. \textbf{31} (2018), no.~1, 1--40.
 
@@
 
-%\bibitem{Wang2018Central}
-%\bysame, \emph{Central limit theorems for supercritical superprocesses with
-  %immigration}, J. Theoret. Probab. \textbf{31} (2018), no.~2, 984--1012.
-
 \end{thebibliography}

### 2019-03-09 supCLT.tex
supCLT.tex: 0309

@@
 %%----Versions-----------------------------
+%supCLT-8.tex 2019/03/08 by Zhenyao
+%supCLT-7.tex 2019/03/08 by Renming
+%supCLT-6.tex 2019/03/07 by Zhenyao
+%supCLT-5.tex 2019/03/07 by Jianjie
+%supCLT-4.tex 2019/03/07 by Yanxia
+%supCLT-3.tex 2019/03/06 by Jianjie
 %supCLT-2.tex 2019/03/05 by Renming
@@
 \usepackage{mathrsfs}
-\usepackage[backref=section]{hyperref}
-%\usepackage{hyperref}
+%\usepackage[backref=section]{hyperref}
+\usepackage{hyperref}
 \usepackage{comment}
@@
 \begin{abstract}
-  %  Consider a $(\xi, \psi)$-superprocess $(X_t)_{t\geq 0}$ where the spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$  which has generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ with $\sigma, b >0$, and the
-%    branching mechanism $\psi$ takes the form close to
-%	$\psi(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$ in some sense.
 Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$.
@@
 \keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}
-%\date{}
 \maketitle
@@
 
-%    The strong law of large numbers of the above super-OU process $X$ can be stated as follows: 
    The strong law of large numbers for the super-OU process $X$ can be stated as follows:
@@
     we have
-%    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f,\phi_0\varphi\rangle $, 
     $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f, \varphi\rangle $,
     where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and
-%    $\phi_0$, $\varphi$ are functions which will be introduced in  \eqref{eigenfunction} and \eqref{invariantdensity} below.
 $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
@@
 \]
-    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, 
-    for some testing functions $f$.
-%    It turns out that there are three regimes of different behavior of this CLT 
+    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of testing functions $f$.
     It turns out that the statements of the CLT are different in three regimes
@@
     In \cite{AdamczakMilos2015CLT},
-    Adamczak and Milo\'s 
-    proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
-    These two papers made connections between the CLT and 
-    %what they call branching rate regimes.
-    the branching rate regimes
-    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
+    Adamczak and Mi\l{}o\'s proved some spatial central limit theorems for 
+    supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} 
+    Mi\l{}o\'s proved some spatial central limit theorems for 
+    supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+    These two papers made connections between the CLT and  the branching rate regimes.
+    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some spatial central limit theorems for supercritical super-OU 
+    processes with branching mechanisms satisfying 
+    only a second moment condition.
     Moreover,
@@
     In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central},
-    Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
+    Ren, Song and Zhang also established a series of spatial central limit theorems for a large class of general 
+    supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
     The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
 
-    There are also many limiting theory for branching processes and branching Markov processes with branching mechanisms of infinite second moments.
-    Heyde \cite{Heyde1971Some} established a central limit type  theorem for Galton-Watson process 
-when the offspring distribution
+    There are also many limiting theorem type results 
+    for supercritical branching processes and branching Markov processes
+    with branching mechanisms of infinite second moments.
+    Heyde \cite{Heyde1971Some} established a central limit type  theorem 
+    for supercritical Galton-Watson process when the offspring distribution
     belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
-    and   proved that the limit law is  a stable law. Similar results  for supercritical multi-type Galton-Watson processes and supercritical  continuous time branching processes,  
-under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
+    and   proved that the limit law is  a stable law.
+Similar results  for supercritical multi-type Galton-Watson processes and supercritical  continuous time branching processes, under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
     were given in Asmussen \cite{Asmussen76Convergence}.
@@
     considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
-%    They established some central limit theorems in small and critical branching rate regimes, 
-   They established some central limit theorems in the small and critical branching rate regimes, 
+	They established some spatial central limit theorems in the small and critical branching rate regimes,
     but they did not prove any central limit theorem type result in the large branching rate regime.
@@
     As far as we know, this paper is the
-%    first one in the literature on establishing CLT 
    first to study spatial central limit theorems
@@
 
-	We will always assume that the following Assumption holds.
+We will always assume that the following assumption holds.
 \begin{asp}
 \label{asp: Greys condition}
-	The branching mechanism satisfies Grey's condition, i.e. there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+	The branching mechanism satisfies Grey's condition, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
 \end{asp}
@@
 	We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
-	In the reminder of the paper, we will always use $\eta,\beta$ to denote the constants corresponding to $\pi$.
+	In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
+
 \begin{rem}
@@
 	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
-	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statements: There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
+	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statement: 
+	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
 \end{rem}
@@
 	\ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the
-	%$L \log L$ criteria, i.e.,
 	$L \log L$ condition, i.e.,
@@
     We now recall some basic spectral properties of $(P_t)_{t\geq 0}$ from \cite{MetafunePallaraPriola2002Spectrum}.
-%        It is known that the OU process $\xi$ has an invariant measure
        It is known that the OU process $\xi$ has an invariant density
@@
     For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$,
-    %$p!:= \prod_{k= 1}^d p_k$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
     $p!:= \prod_{k= 1}^d p_k!$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
@@
 \end{equation}
-%       It is known that the transition semigroup $(P_t)_{t\geq 0}$ of the OU process $\xi$ 
 It is known that $(P_t)_{t\geq 0}$
@@
     For general test functions $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton} and \cite{EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
-    When the generator of the 
-Ornstein-Uhlenbeck process is replaced by $-(-\Delta)^{\frac{p}{2}}$ with $p\in(0,2]$, similar results have been obtained by L\^{e} \cite{Le2019Long}.    
     \end{rem}
 
-%    The fluctuation result associated to the law of large numbers are 
    The fluctuation result associated to the law of large numbers in this case is
@@
 \end{align}
-    We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; and in Lemma \ref{prop: alpha stable rv} that that, when $f\in \mathcal{P}$ is non-trivial,
-%    $\theta \mapsto \exp(\theta \bar m[f])$ is a characteristic 
+    We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; and in Lemma \ref{prop: alpha stable rv} that, 
+    when $f\in \mathcal C_l$ is non-trivial,
     $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic
@@
 \end{equation}
+%ZS: here and below, I changed all \wide to \widetilde without %
     According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
    We will prove in Lemma \ref{prop: alpha stable rv} that
-%   $\theta \mapsto \exp(\theta \widetilde m[f])$ is a characteristic function of an 
-   $\theta \mapsto \exp( \widetilde m[\theta f])$ is a characteristic function of a
-    $(1+\beta)$-stable random variable.
+   $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
 \begin{thm}
@@
     \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
-        \xrightarrow[t\to \infty]{d} \tilde{\zeta},
-\]
-    where $\tilde{\zeta}$ is a $(1+\beta)$-stable random variable with
+        \xrightarrow[t\to \infty]{d} \widetilde{\zeta},
+\]
+    where $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with
     characteristic function
 \[
-     \mathbf E [e^{i\theta \tilde{\zeta}}]
+     \mathbf E [e^{i\theta \widetilde{\zeta}}]
     =\exp(\widetilde{m}[\theta f]),
@@
 	According to Lemma \ref{lem: def of all m} below, $m[f]$ is well-defined.
-	We will prove  in Lemma \ref{prop: alpha stable rv} that 
-%	$\theta \mapsto \exp(\theta m[f])$ is a characteristic function of an
-	$\theta \mapsto \exp( m[\theta f])$ is a characteristic function of a
-	 $(1+\beta)$-stable random variable.
+	We will prove  in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp( m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
 \begin{thm}
@@
 \end{thm}
-%\subsection{Some words before the proofs}
 \subsection{Some intuitive explanation}
-%Let us give some intuition about the central limit theorems above before we move to proofs.  
 Here we give some intuitive explanation of the central limit theorems above.
-The mains ideas are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
+    The main ideas
+    are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
 For any $\mu\in  \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
@@
    To find the fluctuation of $\langle f,X_t\rangle$, we will investigate the fluctuation of
-   %each term $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$.
    each term on the right hand side above.
@@
 \[
-    \mathbf E[e^{i\theta \zeta_k}] = \exp(e^\alpha m_k[\theta f]),\quad k \in \mathbb N,
+     \mathbf E[e^{i\theta \zeta_k}] = \exp( m_k[\theta f]),\quad k \in \mathbb N,
 \]
@@
     Recall that $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
-    Lemma \ref{lem: mainlemma} and Corollary \ref{cor: indepedent of the limit zeta for critical and small} below imply that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
-\[
-    \bigg(\frac{\mathcal I^{t-k}_{t-k-1}\langle f,X_t\rangle}{(e^{-\alpha}\|X_t\|)^{\frac{1}{1+\beta}}}\bigg)_{k=1}^n 
+    Lemma \ref{lem: mainlemma} and 
+   Proposition \ref{cor: indepedent of the limit zeta for critical and small} below  
+    imply that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
+\[
+    \bigg(\frac{\mathcal I^{t-k}_{t-k-1}\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\bigg)_{k=1}^n
     \xrightarrow [t\to \infty]{d} (\zeta_k)_{k=1}^n.
@@
 \[
-    \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}e^{-\frac{\alpha}{1+\beta}}\sum_{k=0}^\infty \zeta_k,
-\]
-    where $\zeta$ is an $(1+\beta)$-stable random variable with characteristic function
+     \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}\sum_{k=0}^\infty \zeta_k,
+\]
+	where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function
 \[
@@
     with $m[\theta f]$ given in Lemma \ref{lem: def of all m} below.
-    In explanation above, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined,
+	In the explanation above, we have used the facts that 
+    $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined, and
 \begin{equation}
 \label{eq: equatlity for mf for small rate}
-    m[f] =  \sum_{k=0}^\infty m_k[ f],
-\end{equation}
-    and 
-\[
-    m[\theta f] = \theta^{1+\beta} m[f], \quad \theta \geq 0.
-\]
-    All of this facts will be made clear in Subsection \ref{sec: stable distributions} below.
+    m[f] =  \sum_{k=0}^\infty m_k[ f].
+\end{equation}
+    These facts will be made clear in Subsection \ref{sec: stable distributions} below.
 
     If $f$ is in the critical branching rate regime, i.e., $\alpha \beta = \kappa_f b(1+\beta)$,
-    %then \eqref{eq: equatlity for mf for small rate} doesn't hold anymore. 
     then the right hand side of \eqref{eq: equatlity for mf for small rate} may not converge.
@@
 \[
-    \frac{\langle f,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}} \overset{d}{\approx} \frac{1}{t^{\frac{1}{1+\beta}}} \sum_{k=0}^{\lfloor t\rfloor} e^{- \frac{\alpha}{1+\beta}} \zeta_k \xrightarrow[t\to \infty]{d} \widetilde \zeta
-\]
-    where $\widetilde \zeta$ is an $(1+\beta)$-stable random variable with characteristic function
+ 	\frac{\langle f,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}} \overset{d}{\approx} \frac{1}{t^{\frac{1}{1+\beta}}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{d} \widetilde \zeta
+\]
+	where $\widetilde \zeta$ is a $(1+\beta)$-stable random variable with characteristic function
 \[
@@
     There are still many open questions.
-%    For example, the spatial motion in this paper is an Ornstein-Uhlenbeck process. 
-%    If the branching mechanism has finite second moment, we established some central limit theorems in \cite{RenSongZhang2015Central} for a class of superprocesses with general motions. 
-We have established some central limit theorems in \cite{RenSongZhang2015Central} for a class of superprocesses with general motions under the assumption that the branching mechanisms
-satisfy a second moment condition.
-    We hope to prove stable CLT's for superprocesses with general motions in a future project.
+    Ren, Song and Zhang have established some spatial  central limit theorems in
+ \cite{RenSongZhang2015Central} 
+	for a class of superprocesses with general spatial motions under the assumption that the branching mechanisms satisfy a second moment condition.
+	We hope to prove spatial CLT's for superprocesses with general motions without the second moment assumption on the branching mechanism in a future project.
 
@@
     where $\psi_1$ satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
-    It would be interesting to consider more general branching mechanism.
-
-%    Some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism} are the following:
+    It would be interesting to consider more general branching mechanisms.
+
 Here are some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}:
@@
 \item
-    $\varphi$ and $\phi_p$ are given by \eqref{invariantdensity} and \eqref{eigenfunction}, respectively.
-\item
-    $P_t$, $P^\alpha_t$, $V_t$ and $U_t$ are given by \eqref{eq: meansemigroup}, \eqref{eq: meansemigroup}, \eqref{eq: def of V_t}, \eqref{eq: def of U_t}, respectively.
-\item
-    $\mathcal N$, $K$, $\mathcal C_l$ and $I_t$ are given by \eqref{eq: def of N}, \eqref{eq: def of N},  \eqref{eq: def of Cl} and \eqref{definition of Itf}, respectively.
-\item
-    $\psi$, $\psi_1$ and $\psi_0$ are given by \eqref{eq: honogeneou branching mechanism}, \eqref{eq: psi 1} and \eqref{eq: psi 0}, respectively.
-\item
-    $\Psi$, $\Psi_1$ and $\Psi_0$ are given by \eqref{eq: def of operator Psi}.
-\item
-    $Z_t$, $Z'_t$, $Z''_t$ and $Z'''_t$ are given by \eqref{eq: def of Zf}.
-\item
-    $Q_\kappa$ and $Q$ are given by \eqref{Q_k} and \eqref{Q}, respectively.
-\item
-    $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\tilde m[f]$ and $\bar m[f]$ are given by Lemma \ref{lem: def of all m}.
+    $\varphi$ and $\phi_p$ are given 
+    in \eqref{invariantdensity} and \eqref{eigenfunction}, respectively.
+\item
+    $P_t$, $P^\alpha_t$, $V_t$ and $U_t$ are given 
+   in \eqref{eq: meansemigroup}, \eqref{eq: meansemigroup}, 
+    \eqref{eq: def of V_t}, \eqref{eq: def of U_t}, respectively.
+\item
+    $\mathcal N$, $K$, $\mathcal C_l$ and $I_t$ are given 
+    in \eqref{eq: def of N}, \eqref{eq: def of N},  \eqref{eq: def of Cl} and 
+    \eqref{definition of Itf}, respectively.
+\item
+    $\psi$, $\psi_1$ and $\psi_0$ are given 
+    in \eqref{eq: honogeneou branching mechanism}, \eqref{eq: psi 1} and 
+    \eqref{eq: psi 0}, respectively.
+\item
+   $\Psi$, $\Psi_1$ and $\Psi_0$ are given in \eqref{eq: def of operator Psi}.
+\item
+    $Z_t$, $Z'_t$, $Z''_t$ and $Z'''_t$ are given in \eqref{eq: def of Zf}.
+\item
+    $Q_\kappa$ and $Q$ are given in \eqref{Q_k} and \eqref{Q}, respectively.
+\item
+    $m_t[f]$, $\bar m_t[f]$, $m[f]$, 
+   $\widetilde m[f]$ 
+   and $\bar m[f]$ are given in Lemma \ref{lem: def of all m}.
 \end{itemize}
@@
 	The function $\psi_1$ on $\mathbb R_+$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
-		Moreover, for each $\delta > 0$ small enough, there exists a  constant $C>0$ such that for each $z\in \mathbb C_+$, we have
+		Moreover, for each $\delta > 0$ small enough, there exists a  constant $C>0$ such that for all $z\in \mathbb C_+$, we have
 $
@@
 \]
-	In other words, if we denote by $\tilde \pi(dy)$ the measure $\eta' \Gamma(-1-\beta)^{-1} y^{-2-\beta'} dy$, then $\tilde \pi$ is a L\'evy measure which satisfies Assumption \ref{asp: branching mechanism}.
-	Applying Lemma \ref{lem: complex extension for psi1} to this measure $\tilde \pi$, we have that there exists $c>0$ such that
+	In other words, if we denote by $\widetilde \pi(dy)$ the measure $\eta' \Gamma(-1-\beta)^{-1} y^{-2-\beta'} dy$, then $\widetilde \pi$ is a L\'evy measure which satisfies Assumption \ref{asp: branching mechanism}.
+	Applying Lemma \ref{lem: complex extension for psi1} to this measure $\widetilde \pi$, we have that there exists $c>0$ such that
 \[
@@
 If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies
-%the $L \log L$ criterion, i.e.,
 the $L \log L$ condition, i.e.,
@@
     (4). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
-%    then we have the following:
 Then we have the following:
@@
         According to Lemma \ref{lem: complex extension for psi1},
-         there exist constants $C, \delta >0$ such that  $1+\beta+\delta< 2$, and for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
+         there exist constants $C, \delta >0$ 
+         satisfying $\beta+\delta< 1$ such that for all
+         $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
 \begin{align}
@@
    Recall that
-    $(P^\alpha_t)_{t\geq 0}$ is defined in \eqref{eq: meansemigroup}, $\mathcal P$ is defined in \eqref{eq: polynomial growth function}, $\mathcal N$ is given by \eqref{eq: def of N} and $\mathcal C_l$ is defined in \eqref{eq: def of Cl}.
+    $(P^\alpha_t)_{t\geq 0}$ is defined in \eqref{eq: meansemigroup}, $\mathcal P$ is defined in \eqref{eq: polynomial growth function}, $\mathcal N$ is given in \eqref{eq: def of N} and $\mathcal C_l$ is defined in \eqref{eq: def of Cl}.
 \begin{lem}
@@
 \item
-%	Suppose that $f\in\mathcal{P}$. Then the following integrals are well defined:
 If $f\in\mathcal{P}$, then the following integrals are well defined:
@@
 \item
-%    Suppose that $f\in\mathcal C_l$. Then the following integrals are well defined:
 If $f\in\mathcal C_l$, then the following integrals are well defined:
@@
 \begin{equation}
-    |\bar{m}_t[f]| \leq C e^{-(\alpha\beta-K(1+\beta)b)t}, \quad t\geq 0,
-\end{equation}
-%	where $K:=\sup\{k\in \mathbb N : \alpha\beta>k(1+\beta)b\}$.
+    |\bar{m}_t[f]| \leq C e^{-(\alpha\beta-K(1+\beta)b)t}, \quad t\geq 1,
+\end{equation}
 where $K$ is defined in \eqref{eq: def of N}.
 \item
-%    Suppose that $f \in \mathcal C_l$.
-%    Then the following integral is well defined:
 If $f \in \mathcal C_l$, then the following integral is well defined:
@@
 \item
-%	Suppose that $f \in \mathcal{P}$ satisfies  $\alpha\beta=\kappa_f b(1+\beta)$. Then the following integral is well defined:
 If $f \in \mathcal{P}$ satisfies  $\alpha\beta=\kappa_f b(1+\beta)$, then the following integral is well defined:
 \[
-	\tilde{m}[f]
+	\widetilde{m}[f]
     := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
@@
 \item
-%	Suppose that $f\in \mathcal{P}$ satisfies $\alpha\beta<\kappa_fb(1+\beta)$.
-%	Then the following integral is well defined:
 If $f\in \mathcal{P}$ satisfies $\alpha\beta<\kappa_fb(1+\beta)$, then the following integral is well defined:
@@
      &|\bar{m}_t[f]|
-    \leq \eta \int_{t}^{t+1} e^{\alpha s}~ds \int_{\mathbb R^d} | I_sf(x)|^{1+\beta}\varphi(x)~dx
-    \\&\leq \eta \int_{t}^{t+1} e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}~ds\int_{\mathbb R^d} h(x)^{1+\beta}\varphi(x)~dx
+    \leq \eta \int_{t-1}^{t} e^{\alpha s}~ds \int_{\mathbb R^d} | I_sf(x)|^{1+\beta}\varphi(x)~dx
+    \\&\leq \eta \int_{t-1}^{t} e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}~ds\int_{\mathbb R^d} h(x)^{1+\beta}\varphi(x)~dx
     \\&\leq C e^{-(\alpha\beta-K(1+\beta)b)t},
-    \quad t\geq 0.
+    \quad t\geq 1.
 \end{align}
@@
 \end{proof}
-    The following proposition says that $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\bar m[f]$ and $\tilde m[f]$ are all related to $(1+\beta)$-stable distributions.
+    The following proposition says that $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\bar m[f]$ and 
+    $\widetilde m[f]$ 
+    are all related to $(1+\beta)$-stable distributions.
 \begin{prop}
@@
 \label{item: stable 4}
-    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
+    $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
 \item
@@
       \]
-%      is a $(1+\beta)$-controllable operator on $\mathcal P$.
  is a $\theta^{1+\beta}$-controllable operator on $\mathcal P$.
@@
 \end{align}
-%    We have the following well-known results for the OU semigroup: 
 It is well known that
@@
     It is clear that the above equality also holds for each $f\in \mathcal P$.
-%    From this, it can be checked that for each $f \in \mathcal P$ such that $f$ is differentiable with $|\nabla  f| \in \mathcal P$, we have
 From this, one can easily check that for each differential $f \in \mathcal P$ with $|\nabla  f| \in \mathcal P$, we have
@@
 \]
-%    According to this and \cite[Theorem A.5.2.]{Durrett2010Probability} we have
 Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, we can get
@@
 \[
-    |\sqrt {1-\theta} - 1| \leq \theta, \quad \theta\in [0,1],
+    |\sqrt {1-\theta} - 1| \leq \theta, \quad \theta\in [0,1]
 \]
@@
 \]
-    By the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we get that for each $s,t\geq 0, x\in \mathbb R^d$,
+	Using the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, 
+    we get that for all $s,t\geq 0, x\in \mathbb R^d$,
 \begin{align}
@@
     In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}.
-    Such a process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying that
+    Such a process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying 
 \[
@@
     Suppose that Grey's condition is satisfied, i.e., there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-%    Also suppose that the $L \log L$ criterion is satisfied, i.e.,
     Also suppose that the $L \log L$ condition is satisfied, i.e.,
@@
 \label{CSBP: int}
-    \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0.
+    \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0;
 \end{align}
@@
     Step 2. We will show that, for each $x \geq 0$ there exists a constant
-    %$C>0$ such that
     $c_1>0$ such that
@@
     \mathbf P_{x}(0< W_t\leq k_t)
-%    \leq C\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
      \leq c_1\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
@@
     Step 3. We will show that there exist constants
-    %$c, \delta, t_0 > 0$ such that
     $c_2, \delta_1, t_0 > 0$ such that
@@
     |\bar v_t-\bar v|
-%    \leq ce^{-\delta t},    \quad t\geq t_0.
     \leq c_2e^{-\delta_1 t},    \quad t\geq t_0.
@@
     Step 4: We will show that there exist
-    %constant $C, \delta,t_0>0$ such that
     constants $c_3, \delta_2, t_1>0$ such that
@@
     |\bar v - v_t(k_t^{-1} e^{-\alpha t})|\leq
-    %Ck_t^\delta, \quad t\geq t_0.
     c_3k_t^{\delta_2}, \quad t\geq t_1.
@@
     we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
-%    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for
     Since the $L\log L$ condition is satisfied, we have (see \cite{LiuRenSong2009Llog} for
@@
 \]
-%    The $L \log L$ criterion also guarantees that (see again \cite{LiuRenSong2009Llog} 
     The $L \log L$ condition also guarantees that (see again \cite{LiuRenSong2009Llog}
@@
         Then using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have for $t>0$ large enough,
+
 \begin{align}
@@
     Therefore, there exist
-    %constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$,
     constants $c_3>0$ and $t_1>0$ such that for all $t\geq t_1$,
@@
     \bar v - v_t(k_t^{-1} e^{-\alpha t}) \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
-%    \leq Ck_t^{\frac{\tau - \epsilon}{\alpha}}.
    \leq c_3k_t^{\frac{\tau - \epsilon}{\alpha}}.
@@
     Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exist
-    %constant $C, \delta, t_0 > 0$ such that
     constant $c_4, \delta_3, t_2 > 0$ such that
@@
     \mathbf P_{x}(0< W_t\leq k_t) \leq
-    %C(k_t^{\delta}+e^{-\delta t}),\quad t\geq t_0.
     c_4(k_t^{\delta_3}+e^{-\delta_3 t}),\quad t\geq t_2.
@@
 \label{sec: Moments for super-OU processes}
-    In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
+    In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, 
+    where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
     Recall that the operator $\mathcal{I}^t_s$ is defined in \ref{Ist}.
@@
 \end{proof}
-    For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write its $L_p$-norm as
-\[
-    \|Y\|_{\mathbb P;p}:= E[|Y|^p]^{1/p}.
+    For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write
+\[
+    %\|Y\|_{\mathbb P;p}:= E[|Y|^p]^{1/p}.
+    \|Y\|_{\mathbb P;p}:= \mathbb P[|Y|^p]^{1/p}.
 \]
@@
     In this section, we will prove the main results of this paper. Recall that $\mathcal{M}_c(\mathbb{R}^d)$ is the space of all finite Borel measures of compact support on $\mathbb{R}^d$.
-    For simplicity, we will write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$
-    in this section.
+    For simplicity, we will write $\mathbb{\widetilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in this section.
 
@@
     Put$\bar{f}:=(L+ab)f$.
-    It follows easily from the Ito formula that
+    It follows easily from Ito's formula that
 \begin{equation}\label{Theorem55}
@@
     =\sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
-    =:
-    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f}.
+    =:\sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\widetilde{f}.
 \end{equation}
@@
     &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
-    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle,
+    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \widetilde{f},X_t\rangle,
     \quad t\geq 0.
@@
     J_t
-    :=e^{-(\alpha-\kappa_fb)t}\langle \tilde{f},X_t\rangle,
+    :=e^{-(\alpha-\kappa_fb)t}\langle \widetilde{f},X_t\rangle,
     \quad t\geq 0,
@@
 	Thus, the desired conclusion in this step is valid.
-	In particular, by taking $g = \tilde f$ and $\kappa = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
+	In particular, by taking $g = \widetilde f$ and $\kappa = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
 
@@
     We will show that $J_t$ converges to $0$ almost surely.
-	For $a \geq 0$ and $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
+	For $a \geq 0$, $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
 \begin{equation}
@@
     J_t
-    =e^{-(a_0-\kappa_f)bt} (M_t^{\tilde{f}, a_0}+L_t^{\tilde{f}, a_0}),
+    =e^{-(a_0-\kappa_f)bt} (M_t^{\widetilde{f}, a_0}+L_t^{\widetilde{f}, a_0}),
     \quad t\geq 0.
@@
 \begin{align}
-    e^{-(a_0-\kappa_f)b t}M_t^{\tilde{f},a_0}
+    e^{-(a_0-\kappa_f)b t}M_t^{\widetilde{f},a_0}
     \xrightarrow[t\to \infty]{} 0,
-    \quad e^{-(a_0-\kappa_f)b t}L_t^{\tilde{f},a_0}
+    \quad e^{-(a_0-\kappa_f)b t}L_t^{\widetilde{f},a_0}
     \xrightarrow[t\to \infty]{} 0
@@
 \end{align}
-    Notice that $\kappa_{(L+a_0 b)\tilde{f}}\geq \kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
+    Notice that $\kappa_{(L+a_0 b)\widetilde{f}}\geq \kappa_{\widetilde{f}}\geq \kappa_f+1 > a_0$.
 By Step 1, for any fixed $\gamma\in (0,\beta)$, there exist $C_6, \delta_3>0$ such that for each $t\geq 0$,
 \begin{equation}
-    \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
+    \|e^{-(\alpha-a_0 b)t}\langle \widetilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq C_6 e^{-\delta_3 t},
-    \quad \|e^{-(\alpha-a_0 b)t}\langle L\tilde{f}+a_0 b\tilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+    \quad \|e^{-(\alpha-a_0 b)t}\langle L\widetilde{f}+a_0 b\widetilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq C_6 e^{-\delta_3 t}.
@@
 \begin{align}
-    &\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq\|Y_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\tilde{f}+a_0 b\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
-\end{align}
-    Since $Y_t^{\tilde{f},a_0}$ is increasing in $t$, it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+    &\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq\|Y_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\widetilde{f}+a_0 b\widetilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
+\end{align}
+    Since $Y_t^{\widetilde{f},a_0}$ is increasing in $t$, it converges to some finite random variable $Y_{\infty}^{\widetilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 Consequently,  we have
 \begin{align}
-    \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\tilde{f},a_0}|
-    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\tilde{f},a_0}|=0, \quad
+    \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\widetilde{f},a_0}|
+    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\widetilde{f},a_0}|=0, \quad
      \mathbb P_\mu\text{-a.s.}
 \end{align}
-	On the other hand, the martingale $M_t^{\tilde{f},a_0}$ satisfies
-\begin{align}
-    \|M_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+	On the other hand, the martingale $M_t^{\widetilde{f},a_0}$ satisfies
+\begin{align}
+    \|M_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq  \|e^{-(\alpha-a_0 b)t}\langle \widetilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq C_6(e^{-\delta_3 t}+\frac{1}{\delta_3}),
@@
 \[
-	\lim_{t\rightarrow\infty} e^{-(a_0-\kappa_f)bt}M_t^{\tilde{f},a_0}
+	\lim_{t\rightarrow\infty} e^{-(a_0-\kappa_f)bt}M_t^{\widetilde{f},a_0}
 	=0,
@@
     \gamma_{t,k}
-    :=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
+    :=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha (k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{equation}
@@
     \mathbf{E}(e^{i\theta\zeta_k})
-    =\exp(e^{\alpha}m_k[\theta f]),\quad \theta \in \mathbb R.
+    =\exp(m_k[\theta f]),\quad \theta \in \mathbb R.
 \]
@@
     \mathbb{P}_{\mu}[\exp(i\gamma_{t,k}); D^c]
-    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[f]).
+    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(m_k[f]).
 \end{equation}
@@
 \begin{equation}
-    \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
+    \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c\big]\big|
     \leq J_1(t,k,\epsilon)+J_2(t,k,\epsilon)+J_3(t,k,\epsilon),
@@
     \\ J_2(t,k,\epsilon)
-    &:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|; A_{t-k-1}(\epsilon)\big],
+    &:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|; A_{t-k-1}(\epsilon)\big],
     \\ J_3(t,k, \epsilon)
@@
     \\\theta_{t,k}
-    &:= (e^{\alpha k}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
+    &:= (e^{\alpha( k+1)}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
 \end{align}
@@
 \label{eq: inequality that will used later}
-    &\big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
-    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; A_{t-k-1}(\epsilon)| \mathscr F_{t-k-1}]\big| + 2\mathbb P_\mu(A_{t-k-1}(\epsilon) \Delta D^c| \mathscr F_{t-k-1})\Big]
-    \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{e^{\alpha}m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon)
-    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (Z_1+Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
-    \\& \leq \mathbb{P}_{\mu}\big[|\langle (Z_1+Z'''_1)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    &\big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c\big]\big|
+    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; A_{t-k-1}(\epsilon)| \mathscr F_{t-k-1}]\big| + 2\mathbb P_\mu(A_{t-k-1}(\epsilon) \Delta D^c| \mathscr F_{t-k-1})\Big]
+    \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon)
+    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (Z_1+Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
+    \\& \leq \mathbb{P}_{\mu}\big[|\langle (Z_1+Z'''_1)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
     \\&\leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon).
@@
     \leq R(|\theta_{t,k}P^\alpha_k f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
-    \\&\leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha k}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
-    \\&\leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf
-    \\&=\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
+    \\&\leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
+    \\&\leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf
+    \\&\leq\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
     \\&\leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
@@
 \end{align}
-    where $Q_0$ is defined by \eqref{Q_k} with $k=0$.
+    where $Q$ is defined by \eqref{Q}.
     By taking $\epsilon>0$ small enough, we get the desired result in this step.
@@
 \end{equation}
-    In fact, according to the definitions of $Z_1$ and $m_t$, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
-    &\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]
-    \\&= \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha k}\langle  Z_1P^\alpha_k f,\varphi\rangle
-    \\&=e^{-\alpha k}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big).
-\end{align}
+
+ We first claim that for each $k\geq0$ and $g\in \mathcal P$, $m_k[g]=e^{-\alpha(k+1)}\langle Z_1P_k^{\alpha}g, \varphi \rangle$. 
+In fact, by Fubini's theorem and the definitions of $Z_1$ and $m_k$, we have for all $k\geq 0$ and $g\in \mathcal P$.
+\begin{align}
+	&m_k[g]
+        = \eta \int_k^{k+1}e^{-\alpha s}~ds\int_{\mathbb R^d} (-iP_{s}^\alpha g(x))^{1+\beta} \varphi(x)~dx\\
+       &=\eta \int_0^1e^{-\alpha (k+s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha g)^{1+\beta}\varphi(x)~dx\\
+       &=e^{-\alpha(k+1)} \cdot \eta \int_0^{1}e^{\alpha(1- s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha        g(x))^{1+\beta} \varphi(x)~dx\\
+      &=e^{-\alpha(k+1)}\langle \eta \int_0^1P_{1-s}^{\alpha}(-iP_{s+k}^\alpha g(x))^{1+\beta}~ds, \varphi \rangle\\
+      &=e^{-\alpha(k+1)}\langle Z_1(P_k^{\alpha}g), \varphi \rangle.
+\end{align}
+
 Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+\begin{align}
+    &\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]
+    \\&= \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha (k+1)}\langle  Z_1P^\alpha_k f,\varphi\rangle
+    \\&=e^{-\alpha (k+1)}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big),
+\end{align}
+and
 \begin{align}
@@
     J_2(t,k,\epsilon)&
-    = \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]
-    \\&=e^{-\alpha k}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1P^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
-    &\leq e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
+    = \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|;A_{t-k-1}(\epsilon)\big]
+    \\&=e^{-\alpha( k+1)}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1P^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
+    &\leq e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
 \end{align}
@@
     J_2(t,k, \epsilon)&
-    \leq  e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
+    \leq  e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
     \\&\leq C_3 e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)}
@@
 \begin{equation}
-    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
     \leq Ce^{-\delta(t-k)}.
@@
 \begin{align}
-    &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+    &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
     \\&\leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
@@
 \label{32corollary}
-    \Big|\mathbb{\tilde{P}}_{\mu}\Big[\prod_{k=0}^n\exp\Big(i\theta_k \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}}\Big)-\prod_{k=0}^n\exp(e^{\alpha}m_k[\theta_k f])\Big]\Big|\leq C e^{-\delta(t-n)}.
+    \Big|\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{k=0}^n\exp\Big(i\theta_k \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha (k+1)}\|X_{t-k-1}\|)^\frac{1}{1+\beta}}\Big)-\prod_{k=0}^n\exp(m_k[\theta_k f])\Big]\Big|\leq C e^{-\delta(t-n)}.
 \end{equation}
@@
 \begin{proof}
-    Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
+    Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha( k+1)}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
     Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$satisfying $|\theta_i|\leq \Theta$.
@@
     a_k
-    :=\Big(\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\Big) \times \mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
+    :=\Big(\prod_{l=0}^{k}\exp(m_l[\theta_lf])\Big) \times \mathbb{\widetilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
 \]
@@
     &a_{k-1} - a_k
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1} \Big(\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
+    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
+    \\&=\mathbb{P}_{\mu}(D^c)^{-1} \Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
 \end{align}
@@
     |a_{k-1}- a_k|
-    &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
+    &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
     \\& \leq C e^{-\delta(t-k)}.
@@
    Fix $\mu \in \mathcal M_c(\mathbb R^d)$.
-    Chose $t_0 > 0$ large enough so that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
+   Choose $t_0 > 0$ large enough so that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
     We write
@@
 \[
-    \tilde I_1(t)
+    \widetilde I_1(t)
     :=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
@@
 Fix $\theta\in \mathbb R$.
-    Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small},
+    Taking $\theta_k=t ^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small},
     we get that there exist $C_1,\delta_1>0$ such that,
 \begin{align}
-    \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq \frac{C_1}{t^{\delta_1}},
+    \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq \frac{C_1}{t^{\delta_1}},
     \quad t\geq t_0.
 \end{align}
-    According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\tilde \zeta$ under $\tilde {\mathbb P}_\mu$.
+    According to \eqref{para: critical case},  $\widetilde{I}_1(t)\xrightarrow[t\to \infty]{d}\widetilde \zeta$ under $\widetilde {\mathbb P}_\mu$.
     Therefore, we only need to prove
  \begin{equation}\label{toprove-1}
-    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
+    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde{I}_1(t)}]|
     \xrightarrow[t\to \infty]{} 0
@@
     \quad i = 2,3,
-    \mbox{ under } \tilde {\mathbb P}_\mu.
+    \mbox{ under } \widetilde {\mathbb P}_\mu.
 \end{equation}
@@
 \begin{equation}\label{ineq: control of I1t}
-    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]|
-    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\big],
+    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde{I}_1(t)}]|
+    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\big],
     \quad t\geq t_0,
@@
 \label{thm121}
-    \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|;\mathcal{D}^c_{t,k}\big]
+    \mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|;\mathcal{D}^c_{t,k}\big]
     \leq C_2 e^{-\delta_2 (t-k)}.
@@
 \label{eq: prob of Dtkc}
-    &\mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
-    \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}),
+    &\mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
+    \\&\leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}),
     \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]
@@
 \label{thm122}
-    \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
+    \mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
     \leq  C_4 e^{-\delta_4 (t-k)}.
@@
 \label{eq: control of Ykt}
-    &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \\&\leq|\theta|t^{-\frac{1}{1+\beta}} \mathbb{\tilde{P}}_{\mu}\bigg[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot\Big|\frac{1}{(e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\bigg]
-    \\&\leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
+    &\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
+    \\&\leq|\theta|t^{-\frac{1}{1+\beta}} \mathbb{\widetilde{P}}_{\mu}\bigg[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot\Big|\frac{1}{(e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\bigg]
+    \\&\leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
 \end{align}
@@
 \label{eq: Y in D}
-    &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \leq C_5|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
+    &\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
+    \leq C_5|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
     \\&\leq \frac{C_5}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
@@
 \begin{equation}\label{domi-difference of Is}
-    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
+    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde{I}_1(t)}]|
     \leq C_7 t^{-\delta_5}.
@@
 \[
-    \tilde{\mathbb P}_\mu\big[|Y_{t,k}|\big]
+    \widetilde{\mathbb P}_\mu\big[|Y_{t,k}|\big]
     \leq C_8 e^{-\delta_6(t-k)}.
@@
 \begin{align}
-    &\sum_{k=0}^{\lfloor t-\ln t \rfloor} \tilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
+    &\sum_{k=0}^{\lfloor t-\ln t \rfloor} \widetilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
     \leq C_8\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{-\delta_6(t-k)}
@@
     Step 4.
-    We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\tilde{P}}_{\mu}$.
+    We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\widetilde{P}}_{\mu}$.
     In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C_{10}, \delta_7>0$ such that
 \begin{equation}
-    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t}), \quad t\geq0.
+    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t}), \quad t\geq0.
 \end{equation}
@@
 \begin{equation}\label{Theorem123}
-    |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
-    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C_{10}(t^{-\delta_7}+e^{-\delta_7 t}),
+    |\mathbb{\widetilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
+    \leq 2\mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C_{10}(t^{-\delta_7}+e^{-\delta_7 t}),
     \quad t\geq t_0.
@@
 \begin{align}
-    &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
-    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
-    \\&\leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
+    &|\mathbb{\widetilde{P}}_{\mu} [ (e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
+    \leq |\theta| \mathbb{\widetilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
+    \\&\leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
     \\& \leq C_{11} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
@@
 	Step 5.
-    We will show that $I_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+    We will show that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
     In fact, we have
@@
 	\\& = t^{-\frac{1}{1+\beta}} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
-	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
+	\xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
 \end{align}
@@
 \[
- 	\tilde I'_1(t)
+ 	\widetilde I'_1(t)
  	:=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
@@
     Fix a $\theta\in \mathbb R$.
-    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small},
+    Taking $\theta_k=\theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small},
     we get that there exist $C_1,\delta_1 > 0$ such that
 \begin{align}
-    \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde I'_1(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|
+    \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde I'_1(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|
     \leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}
@@
 \end{align}
-    Hence, according to \eqref{sum-m}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
-    So we only need to prove that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3,$ under $\tilde {\mathbb P}_\mu$.
+    Hence, according to \eqref{sum-m}, we have $\widetilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\widetilde {\mathbb P}_\mu$.
+    So we only need to prove that $|\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3,$ under $\widetilde {\mathbb P}_\mu$.
 
     Step 1.
-    We will show that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
+    We will show that $|\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
     Define for $k\geq 0$ and $t\geq k+1$,
@@
 \label{ineq: control of I1tb}
-    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}] - \mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}'_1(t)}]|
-    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big],
+    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I'_1(t)}] - \mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde{I}'_1(t)}]|
+    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|\big],
     \quad t\geq t_0.
@@
 \begin{align}
-    &\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
-    = \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}\big] + \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}^c \big]
-    \\& \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\tilde{P}}_{\mu}( \mathcal D_{t,k}^c )
+    &\mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
+    = \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}\big] + \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}^c \big]
+    \\& \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\widetilde{P}}_{\mu}( \mathcal D_{t,k}^c )
     \\& \leq C_2 e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-(\eta_0 - 3\eta_1)(t-k)} + Ce^{-\delta_2(t-k)}
@@
 \begin{align}
-    \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
+    \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
     & \leq C_3( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)})
@@
 \end{align}
-    Now we can  use the  same argument used in the proof of Theorem \ref{thm: critical clt} to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
+    Now we can  use the  same argument used in the proof of Theorem \ref{thm: critical clt} to prove $|\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
 
@@
 \begin{align}
-    &|\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
-    \leq 2\mathbb{\tilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})
+    &|\mathbb{\widetilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
+    \leq 2\mathbb{\widetilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})
     \\&\leq C_5(e^{-\epsilon\delta_4 t}+e^{-\delta_4 t}),
@@
 \begin{align}
-    &\big|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)}]\big|
-    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)}\big]
-    \\&\leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
+    &\big|\mathbb{\widetilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)}]\big|
+    \leq |\theta| \mathbb{\widetilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)}\big]
+    \\&\leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
     \\& \leq C_6  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
@@
 
-	Step 3. We will show that $I'_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+	Step 3. We will show that $I'_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
     In fact, we have
@@
 	\\& = e^{(\frac{\beta \alpha }{1+\beta} - k_fb)t} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
-	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
+	\xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
     \qedhere
@@
     &=e^{\alpha(n-1)}\langle \int_0^1 P_s^{\alpha}\langle \eta(iI_{s+n-1}g)^{1+\beta}ds, \varphi\rangle\\
-    &=e^{\alpha(n-1)}\langle \int_0^1 P_{1-s}^{\alpha}\langle \eta(iI_{n-s}g)^{1+\beta}ds, \varphi\rangle=e^{\alpha(n-1)}\langle Z_1(-I_ng), \varphi\rangle.
+    &=e^{\alpha(n-1)}\langle \int_0^1 P_{1-s}^{\alpha}\langle \eta(iI_{n-s}g)^{1+\beta}ds, \varphi\rangle=e^{\alpha(n-1)}\langle Z_1(-I_ng),
+    \varphi\rangle,
+    \quad n\geq 1.
 \end{align}
@@
 \end{align}
-    where $\bar{\zeta}_n$ is an $(1+\beta)$-stable random variable with characteristic function
+	where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with
+    characteristic function
 \begin{align}
@@
      J'_1(t,n,\epsilon)&
-     \leq  \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle R|h|,X_{t+n-1}\rangle]\\
+       \leq  \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle Rh,X_{t+n-1}\rangle]\\
      & \leq C_1\sum_{\rho\in\{\delta_0,1\}}\exp\Big\{-\Big(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta}\Big)(t+n-1)\Big\}.
@@
 \begin{align}\label{ineq: next we will need}
-    \bigg|\tilde{\mathbb{P}}_{\mu}\Big[\prod_{l=1}^m\exp(i\theta\bar{\gamma}_{t,l})-\prod_{l=1}^m\exp(\bar{m}_l[\theta g])\Big]\bigg|\leq C e^{-\delta t}.
+    \bigg|\widetilde{\mathbb{P}}_{\mu}\Big[\prod_{l=1}^m\exp(i\theta\bar{\gamma}_{t,l})-\prod_{l=1}^m\exp(\bar{m}_l[\theta g])\Big]\bigg|\leq C e^{-\delta t}.
 \end{align}
@@
 \[
-    \tilde{a}_n
-    :=\mathbb{\tilde{P}}_{\mu}\Big[\prod_{l=0}^{n}\exp(i\theta\bar{\gamma}_{t,l})\Big] \times \prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g]),
+    \widetilde{a}_n
+    :=\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{l=0}^{n}\exp(i\theta\bar{\gamma}_{t,l})\Big] \times \prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g]),
 \]
@@
 \begin{align}
-    &\tilde{a}_{n-1} - \tilde{a}_n
+    &\widetilde{a}_{n-1} - \widetilde{a}_n
     \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times (e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}});D^c\Big] \times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
@@
 \end{align}
-    According to Step 1 and Proposition \ref{prop: alpha stable rv},
-    there exist $C_2>0$ such that for any $n=1,\cdots, m$ and $t\geq0$, we have
-\begin{align}
-    |\tilde{a}_{n-1}- \tilde{a}_n|
+    According to Step 1 and Proposition \ref{prop: alpha stable rv}, there exists $C_2>0$ such that for any $n=1,\cdots, m$ and $t\geq 0$, we have
+\begin{align}
+    |\widetilde{a}_{n-1}- \widetilde{a}_n|
     &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
@@
     \text{LHS of \eqref{ineq: next we will need}}
-    &= \left|\tilde{a}_{0}-\tilde{a}_m\right|
-    \leq\sum_{n=1}^m\left|\tilde{a}_{n-1}-\tilde{a}_n\right|
+    &= \left|\widetilde{a}_{0}-\widetilde{a}_m\right|
+    \leq\sum_{n=1}^m\left|\widetilde{a}_{n-1}-\widetilde{a}_n\right|
     \leq \sum_{n=1}^m C_2 e^{-\delta_1(t+n-1)}.
@@
 \begin{align}
-    \tilde{\gamma}_{t,n}
+    \widetilde{\gamma}_{t,n}
     :=\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_{t}\|^{\frac{1}{1+\beta}}},
@@
 \begin{align}
-    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^m e^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|
+    \Big|\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^m e^{i\theta \widetilde{\gamma}_{t,n}}]-\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|
     \leq C m e^{-\delta t}.
@@
 \begin{align}\label{ineq: used next 3}
-    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq \sum_{n=1}^m\tilde{\mathbb{P}}_{\mu}[|Y''_{t,n}|],
+    \Big|\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \widetilde{\gamma}_{t,n}}]-\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq \sum_{n=1}^m\widetilde{\mathbb{P}}_{\mu}[|Y''_{t,n}|],
 \end{align}
@@
     Y''_{t,n}
-    :=e^{i\theta\tilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},
+    :=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},
     \quad t\geq 0, n\geq 1.
@@
 \]
-	where $K=\sup\{k\in \mathbb N:~\alpha\beta>k(1+\beta)b\}$.
+		where $K$ is defined in \eqref{eq: def of N}.
     Fix this $\gamma$, and then choose $\eta_0,\eta_1>0$ such that
@@
 \label{thm12111}
-    \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}^c_{t,n}}\big]
+    \mathbb{\widetilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}^c_{t,n}}\big]
     \leq C_1 e^{-\delta_1 t}.
@@
 \label{thm12211}
-    \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq C_1e^{-\delta_2 t}.
+    \mathbb{\widetilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq C_1e^{-\delta_2 t}.
 \end{align}
@@
 \begin{align}\label{large: used next}
-    &\tilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\\
-    &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}\tilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot\Big|\frac{1}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}\Big]\\
-    &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}\tilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot K'_{t,n}\Big],
+    &\widetilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\\
+    &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}\widetilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot\Big|\frac{1}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}\Big]\\
+    &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}\widetilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot K'_{t,n}\Big],
 \end{align}
@@
 \end{align}
-Since $\eta_1 < \eta_0$,  using similar arguments used in  step 2 of the proof of Theorem \ref{thm: critical clt}, we can show that, there is a constant $C_3> 0$ such that,
+	Since $\eta_1 < \eta_0$, using an argument similar to that used in Step 2 of the proof of Theorem \ref{thm: critical clt}, we can show that, there is a constant $C_3> 0$ such that,
 \begin{align}
@@
 \end{align}
-    According to Lemma \ref{lem: control of wt}, there exist constants $C_4>0$ such that  for all $t\geq 0$ and $n\geq 1$,
+    According to Lemma \ref{lem: control of wt}, there exists a constant $C_4>0$ such that for all $t\geq 0$ and $n\geq 1$,
 \begin{align}\label{ineq:used next 2}
-    &\tilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]
+    &\widetilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]
     \leq \frac{C_3}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\mathbb{P}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\Big]\\
@@
 \begin{align}
-    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|
+    \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\Big]\Big|
     \leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 m}),
@@
 \begin{align}\label{ineq: control of gamma_t on dc}
-    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]
-    \leq 2\tilde{P}_{\mu}(A_t(\epsilon)^c)
+    \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]
+    \leq 2\widetilde{P}_{\mu}(A_t(\epsilon)^c)
     \leq C_1 e^{-\delta t}.
@@
     According to Lemma \ref{lem: control of wt}, there exist $C_2,C_3>0$
-    %such that
     such that for all $m\in \mathbb{N}, t\geq$,
 \begin{align}\label{ineq: control of gamma_t on d}
-    &\Big|\tilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)}\Big]\Big|\\
+    &\Big|\widetilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)}\Big]\Big|\\
     &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{n=m}^{\infty}\sum_{p\in \mathcal{N}}|a_p|\mathbb{P}_{\mu}\Big[\frac{|H_{t+n-1}^p-H_{t+n}^p|}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}\mathbf{1}_{A_t(\epsilon)}\Big]\\
@@
     &\leq C_3|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}
-%    e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m},
-%    \qquad m\in \mathbb{N}, t\geq 0.
     e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m}.
@@
     \text{LHS of \eqref{thm: large rate}}
-    =\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\tilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\tilde{\gamma}_{t,n}.
+    =\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\widetilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\widetilde{\gamma}_{t,n}.
 \end{align}
@@
 \begin{align}\label{ineq: last1}
-    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]
+    \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]
     \Big|\leq C_1 e^{-\delta_1 t}.
@@
 \begin{align}\label{ineq: last2}
-    \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C_2  e^{-\frac{\delta_0}{2} t}.
+    \Big|\widetilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \widetilde{\gamma}_{t,n}}]-\widetilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C_2  e^{-\frac{\delta_0}{2} t}.
  \end{align}
@@
 \begin{align}\label{ineq: last3}
-    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C_3(e^{-\delta_2 t}+e^{\delta_2 t}e^{-\delta_3 e^{\frac{\delta_0}{2}t}}).
+    \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\Big]\Big|\leq C_3(e^{-\delta_2 t}+e^{\delta_2 t}e^{-\delta_3 e^{\frac{\delta_0}{2}t}}).
 \end{align}
@@
 \end{align}
-    For uniqueness, suppose  $\tilde g$ is another solution. Put $h(r) = \sup_{x\in E}|g(r,x) - \tilde g(r,x)|$. Then
+    For uniqueness, suppose  $\widetilde g$ is another solution. Put $h(r) = \sup_{x\in E}|g(r,x) - \widetilde g(r,x)|$. Then
 \[
@@
 \item
-    The spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$.
-\item
-    The branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
+    %The spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$;
+    the spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$;
+\item
+    %The branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
+    the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
 \begin{equation}
@@
 \end{equation}
-    where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+    where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$;
 \item
@@
 \item
-    For any $\mu \in \mathcal M(E)$, if $\mathcal N$ is a Poisson random measure defined on some probability space
-    with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
+    %For any $\mu \in \mathcal M(E)$, 
+    for any $\mu \in \mathcal M(E)$, 
+    if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
     then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
@@
 \begin{lem}
-    There exists constants $C\geq 0$ such that for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
+    There exists a constant $C\geq 0$ such that
+    for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
 \begin{equation}
@@
 \item
-    The spine process $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$,
+     the spine process
+    $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$,
     where
@@
 \item
-    Given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure 
-%    $\{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ 
+    given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, 
+    the immigration measure
 \[ \{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}\]
@@
 
+\bigskip
+\noindent
+{\bf Acknowledgment:}
+	%We thank Zenghu Li for helpful conversations..
+	We thank Zenghu Li and Rui Zhang for helpful conversations.
+\bigskip
+
 \providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
@@
 
-\bibitem{Le2019Long}
-K.~L\^{e}, \emph{Long-time asymptotic of stable {D}awson-{W}atanabe processes
-  in supercritical regimes}, Acta Math. Sci. \textbf{39} (2019), no.~1, 37--45.
-
 \bibitem{Li2011Measure-valued}
@@
 P.~Mi{\l}o{\'s},
-%\emph{Spatial {CLT} for the supercritical
-%  {O}rnstein-{U}hlenbeck superprocess}, arXiv:1203.6661, 2012.
 \emph{Spatial central limit theorem for supercritical superprocesses},

### 2019-03-09 supCLT.tex
supCLT.tex: 0309 submitted version to EJP and arXiv

@@
-%%----Versions-----------------------------
-%supCLT-8.tex 2019/03/08 by Zhenyao
-%supCLT-7.tex 2019/03/08 by Renming
-%supCLT-6.tex 2019/03/07 by Zhenyao
-%supCLT-5.tex 2019/03/07 by Jianjie
-%supCLT-4.tex 2019/03/07 by Yanxia
-%supCLT-3.tex 2019/03/06 by Jianjie
-%supCLT-2.tex 2019/03/05 by Renming
-%supCLT.tex 2019/03/04 by Zhenyao
-% supclt0220.tex 2019/02/20 by Jianjie
-% supclt0217.tex 2019/02/14 by Renming
-% supclt0214.tex 2019/02/14 by Yanxia
-% supclt0211.tex 2019/02/11 by Zhenyao
-% supCLT0128.tex 2019/01/28 by Renming
-% supCLT0127.tex 2019/01/27 by Yanxia
-% supCLT0124.tex 2019/01/24 by Jianjie
-% supCLT0114.tex 2019/01/14 by Yanxia
-% supCLT0107.tex 2019/01/07 by Jianjie
-% supclt1231.tex 2018/12/14 by Zhenyao
-% supclt1213.tex 2018/12/14 by Yanxia
-% supclt1213.tex 2018/12/13 by Renming
-% supclt1209.tex 2018/12/07 by Zhenyao
-% supclt1207.tex 2018/12/07 by Renming
-% supCLT1204.tex 2018/12/04 by Zhenyao
-% supCLT1130.tex 2018/11/30 by Jianjie
-% supCLT1124.tex 2018/11/24 by Zhenyao
-% supCLT1115.tex 2018/11/15 by Jianjie
-% supCLT9.tex ......... by Zhenyao
-% supCLT8.tex ......... by Jianjie
-% supCLT7.tex ......... by Zhenyao
-% supCLT6.tex ......... by Jianjie
-% supCLT5.tex ......... by Zhenyao
-% supCLT4.tex ......... by Jianjie
-% supCLT3.tex 2018/8/25 by Zhenyao
-% supCLT2.tex 2018/8/13 by Jianjie
-% supCLT1.tex 2018/7/24 by Zhenyao
-% supCLT.tex 2018/6/29 by Jianjie
 %---The preamble----------------------
@@
     \\ Department of Mathematics
-    \\ University of Illinois of Illinois at Urbana-Champaign
+    \\ University of Illinois at Urbana-Champaign
     \\ Urbana, IL 61801, USA}
@@
 Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$.
-Let $\psi$ be a branching mechanism which is close to a function of the form
-$\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense. In this paper, we study asymptotic behaviors of
+Let $\psi$ be a branching mechanism which is close to a function of the form $\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense.
+In this paper, we study asymptotic behaviors of
 $(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$.
 For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$.
-    Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
-    the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
+Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
 \end{abstract}
@@
 \end{equation}
-%ZS: here and below, I changed all \wide to \widetilde without %
     According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
@@
 \[
-    %\|Y\|_{\mathbb P;p}:= E[|Y|^p]^{1/p}.
     \|Y\|_{\mathbb P;p}:= \mathbb P[|Y|^p]^{1/p}.
@@
 \item
-    %The spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$;
     the spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$;
 \item
-    %The branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
     the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
@@
 \item
-    %For any $\mu \in \mathcal M(E)$, 
     for any $\mu \in \mathcal M(E)$, 
@@
 {\bf Acknowledgment:}
-	%We thank Zenghu Li for helpful conversations..
 	We thank Zenghu Li and Rui Zhang for helpful conversations.

### 2019-06-09 representation/representation.tex
add representation.tex

\documentclass[9pt]{beamer}
\usepackage{lmodern}
\usepackage{mathrsfs}
\usepackage{mathtools}
	\mathtoolsset{showonlyrefs}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage[style=authoryear-icomp,maxbibnames=10,maxcitenames=10,uniquename=false]{biblatex}
\usepackage{comment}
\usetheme{Frankfurt}
\usecolortheme{seahorse}
\usecolortheme{rose}
\usefonttheme{serif}
\usefonttheme{structurebold}
\setbeamerfont{title}{shape=\itshape,family=\rmfamily}
\setbeamercolor{title}{fg=red!80!black,bg=red!20!white}
\title{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
\author{\bf Zhenyao Sun\inst{1}}
\institute{
	Based on a joint work with Yan-Xia Ren\inst{1,2}, Renming Song\inst{3} and Jianjie Zhao\inst{1}
\and
\inst{1}
	School of Mathematical Sciences, Peking University
\and
\inst{2}
	Center for Statistical Science, Peking University
\and
\inst{3}
	Department of Mathematics, University of Illinois at Urbana-Champaign
}
\date{
	Beijing Normal University,\\
	April, 2019}
\addbibresource{/Users/zhenyao/Repository/orggtd/bib.bib}
\begin{document}
\begin{frame}
  \titlepage
\end{frame}

\section{Background and Motivation}
\begin{frame}[allowframebreaks]{Model}
\begin{itemize}
\item
	In this talk, we consider a measure-valued Markov process $(X_t)_{t\geq 0}$ known as the superprocess.
\item
	Let $E$ be a locally compact separable metric space.
\item
	Let the spatial motion $(\xi_t)_{t\geq 0}$ be an $E$-valued Hunt process with transition semigroup $(P_t)_{t\geq 0}$. 
\item
	Let the branching mechanism $\psi\in \mathcal B(\mathbb R_+, \mathbb R)$ be given by 
\begin{equation} \label{eq: honogeneou branching mechanism}
    \psi(z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb R_+,
\end{equation}
	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with 
\[
	\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty.
\]
\item
	Denote by $\mathcal M(E)$ the space of all finite Borel measures on $E$ equipped with the weak convergence.
\item
	For each $f\in \mathcal B(E, \mathbb R)$ and $\mu \in \mathcal M(E)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral make sense.
\item
	We say a function $f\in \mathcal B(\mathbb R_+\times E, \mathbb R)$ is \emph{locally bounded} if
\[
    \sup_{s\in [0,t],x\in E} |f(s,x)|
    <\infty,
    \quad t\in \mathbb R_+.
\]
\end{itemize}
\begin{definition}[Superprocess, \cite{Dynkin1991Branching}]
	Say an $\mathcal M(E)$-valued Markov process $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu\in \mathcal M_f(E)}\}$ is a $(\xi,\psi)$-superprocess if for each $f\in \mathcal B_b(E, \mathbb R^+)$, we have
\begin{equation}
\label{eq: def of V_t}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(E),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{equation}
	V_tf(x) +  \int_0^t P_{t-s}(\psi \circ V_{t-s}f)(x)ds
	= P_tf(x),
    \quad x\in E, t\geq 0.
\end{equation}
\end{definition}
\begin{itemize}
\item
	When $E=\mathbb R^d$ and $\xi$ is a Brownian motion on $\mathbb R^d$, $X$ is called a super Brownian motion. 
	When $E=\mathbb R^d$ and $\xi$ is a diffusion process on $\mathbb R^d$, $X$ is called a super diffusion process. 
	When $E=\mathbb R^d$ and $\xi$ is an OU process on $\mathbb R^d$ with generator
\[
	Lf(x)=\frac{1}{2}\sigma^2\Delta f(x)-bx\cdot \nabla f(x)
\]
	with $b, \sigma$ being positive constants, $X$ is called a super OU process.
\item
	Superprocess are high-density limits of 
	{\color{red} branching particle systems} (\cite{Watanabe1968A-limit}, \cite{Dawson1975Stochastic}, \cite{Dynkin1991Branching}), 
	{\color{red} long-range contact process} (\cite{MullerTribe1995Stochastic}, \cite{DurrettPerkins1999Rescaled}), 
	{\color{red} voter model } (\cite{CoxDurrettPerkins2000Rescaled}), and 
	{\color{red} long range percolation} (\cite{LalleyZheng2010Spatial}). 
\end{itemize}
\begin{example}[\cite{Li2011Measure-valued}]
	Let $\alpha >0$ and $\beta \in (0,1)$.
	Consider a Branching OU-process with
\begin{itemize}
\item
	{\color{red} $k$} initial particles;
\item
	killing rate  $2{\color{red}k}^\beta$;
\item
	offspring generating function
\[
	F_k(x) =x +\frac{1}{2}(1-x)^{1+\beta} + \frac{-\alpha (1-x)}{2{\color{red}k}^\beta}.
\]
\end{itemize}
	Let $X^{({\color{red} k})}_t(A)$ be number of particles in a Borel set $A$ at time $t$. 
	Then,
\[
	\Big(\frac{1}{\color{red} k} X^{({\color{red} k})}_t(\cdot)\Big)_{t\geq 0}
	\xrightarrow[{\color{red}k}\to \infty]{w} (\xi,\Psi)\text{-superprocess}
\]
	with $\xi$ being an OU process and $\Psi(z) = -\alpha z + z^{1+\beta}$.
\end{example}
\end{frame}
\begin{frame}[allowframebreaks]{Background}
\begin{itemize}
\item
	There have been quite a few papers on laws of large numbers for superprocesses. 
\item
	\cite{Englander2009Law,EnglanderWinter2006Law,EnglanderTuraev2002A-scaling} established some {\color{red}weak laws of large numbers}.
\item
	\cite{ChenRenWang2008An-almost,Wang2010An-almost,LiuRenSong2013Strong,KouritzinRen2014A-strong,ChenRenSongZhang2015Strong,EckhoffKyprianouWinkel2015Spines,ChenRenYang2019Skeleton} established {\color{red}strong law of large numbers} for superprocesses under different settings.
\end{itemize}
\begin{example}[\cite{ChenRenYang2019Skeleton}]
	Suppose that $X$ is a super OU process with branching mechanism $\psi(z)=-\alpha z+ z^{1+\beta}$ with $\alpha>0$ and $\beta \in (0,1)$. Then, for each $\mu \in \mathcal M(\mathbb R^d)$ and each continuous bounded non-negative function $f$ on $\mathbb R^d$, we have
\[
	e^{-\alpha t} \langle f, X_t\rangle \xrightarrow[t\to \infty]{\mathbb P_\mu \text{-a.s.}, L^1(\mathbb P_\mu)} H_\infty \langle f, \varphi\rangle,
\]
	where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\varphi$ is the invariant density of the OU process $\xi$.
\end{example}
\begin{block}{Motivation}
	We are interested in the spatial central limit theorems (CLT) for superprocesses.
	More precisely, we want to find
    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
\[
    \frac{\langle f, X_t \rangle -G_t}{F_t}
\]
    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of superprocesses $(X_t)_{t\geq 0}$ and testing functions $f$.
\end{block}
\begin{itemize}
\item
	There are many papers studying CLT for branching processes, branching diffusions and superprocesses.
\item
	For CLT of supercritical {\color{red} Galton-Watson processes}, see \cite{Heyde1970A-rate,HeydeBrown1871An-invariance,HeydeLeslie1971Improved}.
\item 
	For CLT of supercritical  {\color{red} multi-type Galton-Watson processes}, see \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some}.
\item
	For CLT of some general supercritical {\color{red} branching Markov processes}, see \cite{AsmussenHering1983Branching}.
\item
	For CLT of supercritical {\color{red} branching OU processes} with {\color{red} binary branching} mechanism, see \cite{AdamczakMilos2015CLT}.
\item
	For CLT of some supercritical {\color{red} superprocesses} with branching mechanisms satisfying a {\color{red} fourth moment condition}, see \cite{Milos2018Spatial}.
\item
	For CLT of supercritical {\color{red} super OU processes} with branching mechanisms satisfying only a  {\color{red} second moment condition}, see \cite{RenSongZhang2014Central}.
\item
	For a series of CLT for a large class of general supercritical {\color{red} branching Markov processes} and {\color{red} superprocesses} with {\color{red} spatially dependent branching mechanisms} satisfying a {\color{red} second moment condition}, see \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
\item
    All CLTs described above hold for systems with branching mechanisms with finite variance. 
    It is natural to ask whether there are counterparts of CLTs for the cases when the branching mechanisms are of infinite variance.
\item
	For stable CLT for supercritical {\color{red} Galton-Watson process} whose {\color{red} offspring distribution
    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$}, see \cite{Heyde1971Some}.
\item
	For stable CLT for supercritical {\color{red} multi-type Galton-Watson process} and supercritical {\color{red} continuous time branching processes}, see \cite{Asmussen1976Convergence}.
\item
	Recently, some stable CLTs for supercritical {\color{red} branching OU processes} with offspring generating function
\[
    F(s)
    = ms -(m-1) +(m-1) (1-s)^{1+\beta},
    \quad |s|< 1
\]
	with $m>1$ and $\beta\in (0, 1)$ are established in \cite{MarksMilos2018CLT}.
\item
	Very recently, some stable fluctuation results of Biggins’ martingales in the context of {\color{red} branching random walks} are established in \cite{IksanovKoleskoMeiners2018Fluctuations}.
\end{itemize}
\end{frame}
\section{Results}
\begin{frame}[allowframebreaks]{Settings}
\begin{itemize}
\item
	Let $E= \mathbb R^d$.
\item
	Let $(\xi_t)_{t\geq 0}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck (OU) process with generator
\[
	Lf(x)
	=\frac{1}{2} \sigma^2 \Delta f(x)-bx\cdot\nabla f(x),
	\quad x\in \mathbb R^d, f\in C^2(\mathbb R^d),
\]
	where $\sigma,b>0$.
\end{itemize}
\begin{block}{Assumption 1. (Grey's condition)}
	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
\end{block}
\begin{itemize}
\item
	It is known  that, under Assumption 1, 
	the \emph{extinction event} 
	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
\item
	Denote by $\Gamma$ the gamma function.
	For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
\end{itemize}
\begin{block}{Assumption 2.}
	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{equation}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
\end{equation}
	for some $\delta \in (0,1-\beta)$.
\end{block}
\begin{itemize}
\item
	Assumption 2 says that 
 there exist constants $\eta>0$ and $\beta > 0$ 
    such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
\item
    In particular, if \[\pi(dy)=\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy,\] then the branching mechanism takes the form: \[\psi(z)=-\alpha z + \rho z^2 + \eta z^{1+\beta},\quad z\geq 0.\]
\end{itemize}
\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
	Suppose that Assumption  2 holds.
	Suppose that there are constants $\eta'>0, \beta'\in (0,1)$ and $\delta' \in (0, 1-\beta)$ such that
\[
	 \int_{(1,\infty)}y^{1+\beta' +\delta'}~\Big|\pi(dy)-\frac{\eta'~dy}{\Gamma(-1-\beta)y^{2+\beta'}}\Big| <\infty.
\]
	Then $\eta'= \eta$ and $\beta ' = \beta$.
\end{lemma}
\begin{itemize}
\item
	Therefore, $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
\end{itemize}
\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
	If $\psi$ satisfies Assumption  2, then $\psi$ satisfies the $L \log L$ condition, i.e.,
\[
    \int_{(1,\infty)} y \log y~\pi(dy)< \infty.
\]
\end{lemma}
\begin{itemize}
\item
	This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
\end{itemize}
\end{frame}
\begin{frame}[allowframebreaks]{OU semigroup}
\begin{itemize}
\item
	We use $(P_t)_{t\geq 0}$ to denote the transition semigroup of the OU process $\xi$.
\item
	Define
\[
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\]
	Then $(P^\alpha_t)_{t\geq 0}$ is the mean semigroup of the super OU process $X$, in the sense that
\[
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\]
\item
	The limiting behavior of the super OU process is closely related to the asymptotic property of its mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.
\item
    The OU process $(\xi_t)_{t\geq 0}$ has an invariant density
\begin{equation}
    \varphi(x)dx
    :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb R^d.
\end{equation}
\item
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$.
    Then $L^2(\varphi)$ is a Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
\item
    For each multi-index $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write 
\begin{equation}
	|p|:=\sum_{k=1}^d p_k;
	\quad p!:= \prod_{k= 1}^d p_k!;
	\quad \frac{\partial^p} {\partial x^p}:= \prod_{k = 1}^d\frac{\partial^{p_k}}{\partial x_k^{p_k}}.
\end{equation}
\item
    The \emph{Hermite polynomials} are given by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    p \in \mathbb{Z}_+^{d}.
\end{equation}
\begin{lemma}[\cite{MetafunePallaraPriola2002Spectrum}]
	$(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
\[
    \mathcal{A}_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\]
    where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
	Moreover, $\{\phi_p:p\in \mathbb Z_+^d\}$ forms a complete orthonormal basis for $L^2(\varphi)$.
\end{lemma}
\item
    For each function $f\in L^2(\varphi)$, denote by
\begin{equation}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \},
\end{equation}
    the order of the function $f$. 
\item
	We say a function $f\in \mathcal B(\mathbb R^d, \mathbb R)$ is of polynomial growth if there exists constants $C,n>0$ such that 
\[
	|f(x)|\leq C(1+|x|)^n,
	\quad \forall x\in \mathbb R^d.
\]
\item
    Let $\mathcal P \subset L^2(\varphi)$ the collection of all functions of polynomial growth.
\end{itemize}
\begin{block}{Goal in specific}
	Let $(X_t)_{t\geq 0}$ be the super OU process which satisfies Assumption 1 and 2.
	Let $f\in \mathcal P$ and $f\not \equiv 0$.
	We want to find
    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
\[
    \frac{\langle f, X_t \rangle -G_t}{F_t}
\]
    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$.
\end{block}
\begin{itemize}
\item
	It turns out that the statements of the results are different in three different regimes
    depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$.
\end{itemize}
\end{frame}
\begin{frame}{Small branching rate regime: $\alpha\beta < \kappa_f b (1+\beta)$}
\begin{lemma}[\cite{MarksMilos2018CLT}]
	Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta<\kappa_f b(1+\beta)$.
	Then the following integral is well defined:
\begin{equation}
    m[f]
    :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
\end{equation}
	Moreover, $\theta \mapsto \exp( m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
\end{lemma}
\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
    Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta<\kappa_f b(1+\beta)$.
    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    \|X_t\|^{-\frac{1}{1+\beta}} \langle f,X_t\rangle\xrightarrow[t\rightarrow \infty]{d} \zeta,
\]
    where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta \mapsto \exp( m[\theta f])$.
\end{theorem}
\end{frame}
\begin{frame}{Critical branching rate regime: $\alpha\beta = \kappa_f b (1+\beta)$}
\begin{lemma}[\cite{MarksMilos2018CLT}]
	Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta=\kappa_f b(1+\beta)$, then the following integral is well defined
\[
	\widetilde{m}[f]
    := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
\]
	Moreover, $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
\end{lemma}
\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
\label{thm: critical clt}
    Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta=\kappa_f b(1+\beta)$.
    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    (t\|X_t\|)^{-\frac{1}{1+\beta}} \langle f,X_t\rangle
        \xrightarrow[t\to \infty]{d} \widetilde{\zeta},
\]
    where $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with
    characteristic function $\theta \mapsto \exp( \widetilde m[\theta f])$.
\end{theorem}
\end{frame}
\begin{frame}[allowframebreaks]{Large branching rate regime: $\alpha\beta > \kappa_f b (1+\beta)$.}
\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
	For each multi-index $p\in \mathbb Z_+^d$ with $\alpha \beta > |p|b(1+\beta)$, each $\gamma \in (0,\beta)$ and each $\mu \in \mathcal M(\mathbb R^d)$ with compact support, the following martingale
\[
	H_t^p:= e^{-(\alpha-|p|b) t} \langle \phi_p, X_t\rangle, \quad t\geq 0,
\]
	is bounded in $L^{1+\gamma}(\mathbb P_\mu)$. 
	Thus the limit $H_\infty^p:= \lim_{t\to \infty} H_t^p$ exists $\mathbb P_\mu$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
\end{lemma}
\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
	Let $f \in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta>\kappa_fb(1+\beta)$. 
	Then for each $\gamma\in (0, \beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, it holds that
\[
    e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle
       \xrightarrow[t\to \infty]{}\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p
    \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).
\]
    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
\end{theorem}
\begin{itemize}
\item
	Define
\begin{align}
	\mathcal{N}_l
	&:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
	\quad \mathcal{C}_l
	:=Span\{\phi_p:p\in\mathcal N_l\}.
	\\\mathcal{N}_c
	&:=\{p\in \mathbb{Z}_+^d:  \alpha\beta=|p|(1+\beta)b\},
	\quad \mathcal{C}_c
	:=Span\{\phi_p:p\in\mathcal N_c\}.
	\\\mathcal{N}_s
	&:=\{p\in \mathbb{Z}_+^d:  \alpha\beta<|p|(1+\beta)b\},
	\quad \mathcal{C}_s
	:=\overline{Span}\{\phi_p:p\in\mathcal N_s\}.
\end{align}
\item
	For any $f\in \mathcal P\setminus\{0\}$, we have a unique decomposition: 
\[
	f := f_l + f_c + f_s
\]
	where $f_l \in \mathcal C_l, f_c\in \mathcal C_c$ and $f_s\in \mathcal C_s$.
\item
	Not that CLTs for $f_s$ and $f_c$ are already established.
\item
	For each $t\ge 0$, define an operator $I_t$ as the inverse of $P_t^\alpha$ on $\mathcal{C}_l$, i.e.
\begin{align}\label{definition of Itf}
    I_tf(x)
    :=\sum_{p\in \mathcal{N}}\langle f, \phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x),
   \quad x\in \mathbb{R}^d, f\in \mathcal C_l.
\end{align}
\end{itemize}
\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
	Let $f\in \mathcal{C}_l\setminus\{0\}$, then the following integral is well defined
\[
	\bar{m}[f]
    := \eta\int_0^\infty e^{\alpha s}~ds \int_{\mathbb R^d} \big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx,
    \quad f\in \mathcal C_l.
\]
	Moreover, $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
\end{lemma}
\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
\label{thm: large clt}
    Let $f\in \mathcal{C}_l\setminus\{0\}$.
    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. 
    Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\begin{align}\label{thm: large rate}
    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow[t\to \infty]{d}\bar{\zeta},
\end{align}
    where $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with
    characteristic function $\theta \mapsto \exp( \bar m[\theta f])$.
\end{theorem}
\end{frame}
\begin{frame}{Interpretation}
\begin{itemize}
\item
	A phase transition phenomenon for CLT of spatial Markovian branching systems is first observed by \cite{AdamczakMilos2015CLT} in the context of branching OU processes and by \cite{Milos2018Spatial} in the context of super OU processes. (Both assuming finite second moment.)
\item
	This phase transition phenomenon is due to an interplay of coarsening and smoothing. 
\item
	Coarsening means the increasing of the spatial inequalities. It is a consequence of branching: Simply an area with more particles will produce more offspring. The coarsening effect is quantified by the branching rate $\alpha$.
\item
	Smoothing means the decreasing of the spatial inequalities. 
	It is a consequence of the mixing property of the OU process. Imaging an offspring with birth position $x$. This OU particle will ``forget'' its initial position exponentially fast. This will reduce the spatial inequalities. 
	This smoothing effect is quantified by $b$ (the spectral gap of the OU semigroup).
\item
	Put $f\in \mathcal P$ with an order $\kappa_f \geq 1$. Consider an OU particle $\xi_t$. The expected value of $f(\xi_t)$ will decrease exponentially fast. This will also reduce the spatial inequality in the integration $\langle f,X_t\rangle$. 
	This smoothing effect is quantified by $\kappa_f$.
\end{itemize}
\end{frame}
\section{Methods}
\begin{frame}[allowframebreaks]{General Ideas}
\begin{itemize}
\item
	For any $\mu\in  \mathcal M(\mathbb R^d)$ and any random variable $Y$ with finite mean, define
\[
    \mathcal I_s^t Y:=\mathcal I_s^t [Y, \mu]
    := \mathbb P_\mu[Y|\mathcal F_t] - \mathbb P_\mu[Y|\mathcal F_s],\quad 0 \leq s \leq t <\infty.
\]
\item
	Then for any $f\in \mathcal{P}$, we have 
\[
    \langle f,X_t\rangle
    :=\sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle+\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle + \langle P^\alpha_tf,X_0\rangle,
    \quad t\geq 0.
\]
\item
	We can study the fluctuation of $\langle f,X_t\rangle$ by finding the fluctuation of each term $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$.
\item
	This idea can be traced back to the CLT of martingales. 
	Note that $(\mathbb P_\mu[\langle f,X_t\rangle|\mathscr F_s])_{0\leq s\leq t}$ is a martingale in $s$, therefore $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$ is simply the conditional increments of this martingale.
\item
	Taking $f = 1$ as an example. Note that, conditioned on $X_s = \mu$, the conditional distribution of $\mathcal I_s^{s+1}\langle 1, X_t\rangle$ is the same to the distribution of 
\[
	\langle 1, X_1\rangle - \|\mu\|
\]
	under probability $\mathbb P_{\mu}$.
\item
	Also note that, on the event of non-extinction, $\|X_s\|$ will grow exponentially.
	So from the branching property, if $s$ is very large, after some normalization, $\mathcal I_s^{s+1}\langle 1, X_t\rangle$ should distributed approximately like a stable random variable.
\item
	If the superprocess has finite second moment, then after some normalization $\mathcal I_s^{s+1}\langle 1, X_t\rangle$ will distributed like a Gaussian random variable. So we only need to calculate its variance.
\item
	However, under our settings, the superprocess has infinite second moment. So we need to develop new method to characterize the distribution of $\mathcal I_s^{s+1}\langle 1, X_t\rangle$.
\item
	If $\infty >\kappa_f \geq 1$ then $f$ must take both positive and negative values. 
	In this case, the Laplace transform of $\langle f,X_t\rangle$ may not exist.
\end{itemize}
\end{frame}
\begin{frame}[allowframebreaks]{Method}
\begin{itemize}
\item
	Note that $\langle f,X_t\rangle$ is an infinitely divisible random variable. Define its characteristic exponent as
	\[U_t(\theta f)(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}],
	\quad t\geq 0, \theta \in \mathbb R, x\in \mathbb R^d.\]
	It can be proved that $-U_t(\theta f)(x)$ always takes values in $\mathbb C_+:= \{x+iy:x\geq 0, y\in \mathbb R\}$.
\item
	Define
\[
	\psi_0(z) = \psi(z)+\alpha z = \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb R_+.
\]
	It can be proved that $\psi_0$ can be uniquely extended as a complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C_+^0:= \{x+iy: x>0, y\in \mathbb R\}$.
\end{itemize}
\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
    If $f\in \mathcal P$, then for all $t\geq 0$ and $x\in E$, we have
\begin{equation}
    U_tf(x) -  \int_0^t P_{t-s}^\alpha [\psi_0 \circ (- U_{s}f)](x)~ds
    = iP_t^{\alpha} f(x).
\end{equation}
\end{lemma}
\begin{itemize}
\item
	An analog of this Lemma for general non-persistent superprocesses with spatially dependent branching mechanisms is also developed in \cite{RenSongSunZhao2019Stable}.
\item
	Using the above Lemma and Assumption 2, we can derive:
\end{itemize}
\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
    For all $g \in \mathcal P$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C > 0$ such that for all $\lambda > 0$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
\[
    \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
    \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)({\color{red}\alpha - \kappa_g b})}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)({\color{red}\alpha - \kappa_g b})}}{\lambda}\Big)^{2} \bigg).
\]
\end{lemma}
\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
    For all $g \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for all $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
\[
    \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    \leq C e^{t\alpha+(t-s) (\gamma{\color{red}\alpha}- (1+\gamma){\color{red}\kappa_g b})}.
\]
\end{lemma}
\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
    For all $g \in \mathcal P$, $\mu \in \mathcal M(\mathbb R^d)$ with compact support and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
\begin{itemize}
\item
    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa_g b)t}$ provided {\color{red}$\alpha\gamma >  (1+\gamma)\kappa_gb$};
\item
    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided {\color{red}$\alpha\gamma = (1+\gamma)\kappa_gb$};
\item
    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided {\color{red}$\alpha\gamma < (1+\gamma)\kappa_g b$}.
\end{itemize}
\end{lemma}
\begin{lemma}[\cite{MarksMilos2018CLT}]
	Let $f\in \mathcal{P}\setminus\{0\}$.
	Then the following integral is well defined:
\begin{equation}
    m_t[f]
    := \eta \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} (-iP_{s}^\alpha f(x))^{1+\beta} \varphi(x)~dx,
    \quad t\geq 0.
\end{equation}
	Moreover, $\theta \mapsto \exp( m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
\end{lemma}
\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
\label{thm: small clt}
    Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta\leq \kappa_f b(1+\beta)$.
    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    \big(\|X_t\|^{-\frac{1}{1+\beta}}\mathcal I^{t-k}_{t-k-1}\langle f,X_t\rangle\big)_{k=1}^n
    \xrightarrow [t\to \infty]{d} (\zeta_k)_{k=1}^n.
\]
    where $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions
\[
     \mathbf E[e^{i\theta \zeta_k}] = \exp( m_k[\theta f]),\quad k \in \mathbb N.
\]
\end{theorem}
\begin{itemize}
\item
	For the small branching regime $\alpha \beta < \kappa_f b(1+\beta)$. The above Theorem roughly says that
\[
	\|X_t\|^{-\frac{1}{1+\beta}}\langle f,X_t\rangle \xrightarrow[t\to \infty]{d} \sum_{k=0}^\infty \zeta_k \overset{d}{=}: \zeta,
\]
	where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function
\[
	E[e^{i\theta \zeta}] = \exp(m[\theta f]) := \exp\Big(\sum_{k=0}^\infty m_k[\theta f]\Big).
\]
\item
	For the critical branching regime $\alpha \beta = \kappa_f b(1+\beta)$. The above Theorem roughly says that
\[
	(t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle \overset{d}{\approx} t^{-\frac{1}{1+\beta}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{d} \widetilde \zeta
\]
	where $\widetilde \zeta$ is a $(1+\beta)$-stable random variable with characteristic function
\[
	E[e^{i\theta \widetilde \zeta}] = \exp(\widetilde m[\theta f]) := \exp\Big(\lim_{t\to \infty} \frac{1}{t} \sum_{k=0}^{\lfloor t\rfloor} m_k[\theta f]\Big),\quad \theta \in \mathbb R.
\]
\item
	For  testing functions $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$. 
\item
	Taking $f = \phi_p$ with $\alpha \beta > |p|b(1+\beta)$ as an example, we do the following decomposition:
\[
    H^p_t-H^p_\infty=\sum^{\infty}_{n=1}(H^p_{t+n-1}-H^p_{t+n}).
\]
    We established the fluctuation behaviors of each terms.
\end{itemize}
\end{frame}
\begin{frame}[allowframebreaks]{Remarks}
\begin{itemize}
\item
	For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$ where $f_l \in \mathcal C_l$, $f_c \in \mathcal C_c$ and $f_s\in \mathcal C_s$.
	Our main results give CLT for $\langle f_l, X_t\rangle$, $\langle f_c, X_t\rangle$ and $\langle f_s, X_t\rangle$, respectively.
\item
	We conjecture that the limits of these three terms, normalized properly, are independent.
	If this is valid, we can get a CLT for $\langle f, X_t\rangle$ for general $f\in\mathcal{P}$.
\item
	This independence was proved under the second moment condition by \cite{RenSongZhang2015Central}.
\item
	We only considered a special case: Super OU with spatial independent branching mechanism. 
	It is interesting to ask whether stable CLTs are valid for general superprocesses with spatially dependent branching mechanism.
\end{itemize}
\end{frame}
\begin{frame}[allowframebreaks]
	\frametitle{References}
	\printbibliography
\end{frame}
\end{document}

### 2019-07-13 representation/representation.tex
change representation.tex
change representation.tex


change representation.tex

@@
-\documentclass[9pt]{beamer}
+% * Preamble
+\documentclass[xcolor=dvipsnames]{beamer}
+\synctex=1
+%\usepackage[UTF8,scheme=plain]{ctex}
+\usepackage{hyperref}
 \usepackage{lmodern}
 \usepackage{mathrsfs}
+\usepackage{graphicx}
+\usepackage[export]{adjustbox}
+\usepackage{comment}
 \usepackage{mathtools}
 \mathtoolsset{showonlyrefs}
-\usepackage{graphicx}
-\usepackage[export]{adjustbox}
-\usepackage[style=authoryear-icomp,maxbibnames=10,maxcitenames=10,uniquename=false]{biblatex}
-\usepackage{comment}
-\usetheme{Frankfurt}
+\usetheme{Madrid}
 \usecolortheme{seahorse}
@@
 \setbeamercolor{title}{fg=red!80!black,bg=red!20!white}
-\title{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
-\author{\bf Zhenyao Sun\inst{1}}
-\institute{
-	Based on a joint work with Yan-Xia Ren\inst{1,2}, Renming Song\inst{3} and Jianjie Zhao\inst{1}
+% * Top matter
+\title[Stable CLT for Super OU]{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
+\author[Z. Sun]{ 
+  {\bf \Large Zhenyao Sun\inst{1}}
+\\
+{\scriptsize  Joint work with {\bf Yan-Xia Ren\inst{1}}, {\bf Renming Song\inst{2}} and {\bf Jianjie Zhao\inst{1} } }
+}
+\institute[PKU]{
 \and
 \inst{1}
-	School of Mathematical Sciences, Peking University
+	Peking University
 \and
 \inst{2}
-	Center for Statistical Science, Peking University
-\and
-\inst{3}
-	Department of Mathematics, University of Illinois at Urbana-Champaign
+	University of Illinois at Urbana-Champaign
 }
-\date{
-	Beijing Normal University,\\
-	April, 2019}
-\addbibresource{/Users/zhenyao/Repository/orggtd/bib.bib}
+\date[SHNU, July, 2019]{
+	Shanghai Normal University,\\
+	July, 2019}
 \begin{document}
+
 \begin{frame}
@@
 
-\section{Background and Motivation}
-\begin{frame}[allowframebreaks]{Model}
+\section{Model}
+\subsection{Settings}
+\begin{frame}{Model/Settings}
 \begin{itemize}
 \item
-	In this talk, we consider a measure-valued Markov process $(X_t)_{t\geq 0}$ known as the superprocess.
+	$E$: a locally compact separable metric space.
 \item
-	Let $E$ be a locally compact separable metric space.
+	$(\xi_t)_{t\geq 0}$: an $E$-valued Hunt process with semigroup $(P_t)_{t\geq 0}$. 
 \item
-	Let the spatial motion $(\xi_t)_{t\geq 0}$ be an $E$-valued Hunt process with transition semigroup $(P_t)_{t\geq 0}$. 
-\item
-	Let the branching mechanism $\psi\in \mathcal B(\mathbb R_+, \mathbb R)$ be given by 
+	$\psi$: a function from $[0,\infty)$ to $\mathbb R$ given by 
 \begin{equation} \label{eq: honogeneou branching mechanism}
     \psi(z)=
-    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
-    \quad  z \in \mathbb R_+,
+    - {\color{red} \alpha} z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
+    \quad  z \geq 0,
 \end{equation}
-	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with 
+	where ${\color{red}\alpha} > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with 
 \[
@@
 \item
-	Denote by $\mathcal M(E)$ the space of all finite Borel measures on $E$ equipped with the weak convergence.
+  We call ${\color{red}\alpha}$ the {\color{red} branching rate}.
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Model/Settings}
+\begin{itemize}
 \item
-	For each $f\in \mathcal B(E, \mathbb R)$ and $\mu \in \mathcal M(E)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral make sense.
+	$\mathcal M(E)$: the space of all finite Borel measures on $E$ equipped with the weak topology.
 \item
-	We say a function $f\in \mathcal B(\mathbb R_+\times E, \mathbb R)$ is \emph{locally bounded} if
+  $\left\langle f,\mu \right\rangle$: the integration of function $f$ and measure $\mu$ whenever it make senses.
+\item
+	Say a function $f$ on $\mathbb R_+\times E$ is \emph{locally bounded} if
 \[
@@
 \end{itemize}
-\begin{definition}[Superprocess, \cite{Dynkin1991Branching}]
-	Say an $\mathcal M(E)$-valued Markov process $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu\in \mathcal M_f(E)}\}$ is a $(\xi,\psi)$-superprocess if for each $f\in \mathcal B_b(E, \mathbb R^+)$, we have
+\end{frame}
+
+\subsection{Superprocesses}
+\begin{frame}{Model/Superprocesses}
+\begin{definition}[Superprocess]
+	Say an $\mathcal M(E)$-valued Markov process $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu\in \mathcal M(E)}\}$ is a $(\xi,\psi)$-superprocess if for each bounded non-negative measurable function $f$ on $E$, we have
 \begin{equation}
@@
 \begin{equation}
-	V_tf(x) +  \int_0^t P_{t-s}(\psi \circ V_{t-s}f)(x)ds
+	V_tf(x) +  \int_0^t P_{t-s}(\psi \circ V_{s}f)(x)ds
 	= P_tf(x),
@@
 \end{definition}
-\begin{itemize}
-\item
-	When $E=\mathbb R^d$ and $\xi$ is a Brownian motion on $\mathbb R^d$, $X$ is called a super Brownian motion. 
-	When $E=\mathbb R^d$ and $\xi$ is a diffusion process on $\mathbb R^d$, $X$ is called a super diffusion process. 
-	When $E=\mathbb R^d$ and $\xi$ is an OU process on $\mathbb R^d$ with generator
-\[
-	Lf(x)=\frac{1}{2}\sigma^2\Delta f(x)-bx\cdot \nabla f(x)
-\]
-	with $b, \sigma$ being positive constants, $X$ is called a super OU process.
-\item
-	Superprocess are high-density limits of 
-	{\color{red} branching particle systems} (\cite{Watanabe1968A-limit}, \cite{Dawson1975Stochastic}, \cite{Dynkin1991Branching}), 
-	{\color{red} long-range contact process} (\cite{MullerTribe1995Stochastic}, \cite{DurrettPerkins1999Rescaled}), 
-	{\color{red} voter model } (\cite{CoxDurrettPerkins2000Rescaled}), and 
-	{\color{red} long range percolation} (\cite{LalleyZheng2010Spatial}). 
-\end{itemize}
-\begin{example}[\cite{Li2011Measure-valued}]
+\end{frame}
+
+\begin{frame}{Model/Superprocesses}
+\begin{example}
 	Let $\alpha >0$ and $\beta \in (0,1)$.
@@
 \[
-	F_k(x) =x +\frac{1}{2}(1-x)^{1+\beta} + \frac{-\alpha (1-x)}{2{\color{red}k}^\beta}.
+	F_{\color{red}k}(x) =x +\frac{1}{2}(1-x)^{1+\beta} + \frac{-\alpha (1-x)}{2{\color{red}k}^\beta}.
 \]
@@
 	\Big(\frac{1}{\color{red} k} X^{({\color{red} k})}_t(\cdot)\Big)_{t\geq 0}
-	\xrightarrow[{\color{red}k}\to \infty]{w} (\xi,\Psi)\text{-superprocess}
+	\xrightarrow[{\color{red}k}\to \infty]{w} (X_t)_{t\geq 0}
 \]
-	with $\xi$ being an OU process and $\Psi(z) = -\alpha z + z^{1+\beta}$.
+where $(X_t)_{t\geq 0}$ is a super OU process with branching mechanism \[\psi(z) = -\alpha z + z^{1+\beta}.\]
 \end{example}
 \end{frame}
-\begin{frame}[allowframebreaks]{Background}
+
+\section{Background}
+\subsection{Motivation}
+
+\begin{frame}{Background/Motivation}
+  \begin{block}{Motivation}
+    We are interested in the spatial laws of large numbers (LLNs) and central limit theorems (CLT) for superprocesses.
+    More precisely, we want to find
+    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
+    \[
+      \frac{\langle f, X_t \rangle -G_t}{F_t}
+    \]
 \begin{itemize}
 \item
-	There have been quite a few papers on laws of large numbers for superprocesses. 
+converges in probability or in $L^p$ to a non-degenerate random variable (weak LLNs);
 \item
-	\cite{Englander2009Law,EnglanderWinter2006Law,EnglanderTuraev2002A-scaling} established some {\color{red}weak laws of large numbers}.
+converges almost surely to a non-degenerate random variable (strong LLNs);
 \item
-	\cite{ChenRenWang2008An-almost,Wang2010An-almost,LiuRenSong2013Strong,KouritzinRen2014A-strong,ChenRenSongZhang2015Strong,EckhoffKyprianouWinkel2015Spines,ChenRenYang2019Skeleton} established {\color{red}strong law of large numbers} for superprocesses under different settings.
+converges weakly to some non-degenerate random variable (CLTs).
 \end{itemize}
-\begin{example}[\cite{ChenRenYang2019Skeleton}]
+  \end{block}
+\end{frame}
+
+\subsection{LLNs of superprocesses}
+\begin{frame}{Background/LLNs of superprocesses}
+\begin{itemize}
+\item
+{\color{red}Weak laws of large numbers} under different settings: Englander 2009, Englander and Winter 2006, Englander  and Turaev 2002.
+\item
+{\color{red}Strong law of large numbers} under different settings: Chen, Ren and Wang 2008, Wang 2010, Liu, Ren and Song 2013, Kouritzin and  Ren 2014, Chen, Ren, Song and Zhang 2015, Eckhoff, Kyprianou and Winkel 2015, Chen, Ren and Yang 2019.
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Background/LLNs of superprocesses}
+\begin{example}[Chen, Ren and Yang 2019]
 	Suppose that $X$ is a super OU process with branching mechanism $\psi(z)=-\alpha z+ z^{1+\beta}$ with $\alpha>0$ and $\beta \in (0,1)$.
@@
 \end{example}
-\begin{block}{Motivation}
-	We are interested in the spatial central limit theorems (CLT) for superprocesses.
-	More precisely, we want to find
-    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
-\[
-    \frac{\langle f, X_t \rangle -G_t}{F_t}
-\]
-    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of superprocesses $(X_t)_{t\geq 0}$ and testing functions $f$.
-\end{block}
+\end{frame}
+
+\subsection{CLTs for branching processes with 2rd moment conditions}
+\begin{frame}{Background/CLTs for branching processes with 2rd moment conditions}
 \begin{itemize}
 \item
-	There are many papers studying CLT for branching processes, branching diffusions and superprocesses.
+	For CLT of supercritical {\color{red} Galton-Watson processes}, see Heyde 1970, Heyde and Brown 1971, Heyde and Leslie 1971.
 \item 
-	For CLT of supercritical {\color{red} Galton-Watson processes}, see \cite{Heyde1970A-rate,HeydeBrown1871An-invariance,HeydeLeslie1971Improved}.
+	For CLT of supercritical  {\color{red} multi-type Galton-Watson processes}, see Athreya 1969, Athreya 1969, Athreya 1971.
 \item
-	For CLT of supercritical  {\color{red} multi-type Galton-Watson processes}, see \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some}.
+	For CLT of some general supercritical {\color{red} branching Markov processes}, see Asmussen and Hering 1983.
 \item
-	For CLT of some general supercritical {\color{red} branching Markov processes}, see \cite{AsmussenHering1983Branching}.
+	For CLT of supercritical {\color{red} branching OU processes} with {\color{red} binary branching} mechanism, see Adamczak and Milos 2015.
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Background/CLTs for Superprocesses with 2rd moment conditions}
+\begin{itemize}
 \item
-	For CLT of supercritical {\color{red} branching OU processes} with {\color{red} binary branching} mechanism, see \cite{AdamczakMilos2015CLT}.
+	For CLT of some supercritical {\color{red} superprocesses} with branching mechanisms satisfying a {\color{red} fourth moment condition}, see Milos 2018.
 \item
-	For CLT of some supercritical {\color{red} superprocesses} with branching mechanisms satisfying a {\color{red} fourth moment condition}, see \cite{Milos2018Spatial}.
+	For CLT of supercritical {\color{red} super OU processes} with branching mechanisms satisfying only a {\color{red} second moment condition}, see Ren, Song and Zhang 2014.
 \item
-	For CLT of supercritical {\color{red} super OU processes} with branching mechanisms satisfying only a  {\color{red} second moment condition}, see \cite{RenSongZhang2014Central}.
-\item
-	For a series of CLT for a large class of general supercritical {\color{red} branching Markov processes} and {\color{red} superprocesses} with {\color{red} spatially dependent branching mechanisms} satisfying a {\color{red} second moment condition}, see \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
-\item
-    All CLTs described above hold for systems with branching mechanisms with finite variance. 
-    It is natural to ask whether there are counterparts of CLTs for the cases when the branching mechanisms are of infinite variance.
+	For a series of CLT for a large class of general supercritical {\color{red} branching Markov processes} and {\color{red} superprocesses} with {\color{red} spatially dependent branching mechanisms} satisfying a {\color{red} second moment condition}, see Ren, Song and Zhang 2014, Ren, Song and Zhang 2015, Ren, Song and Zhang 2017.
+\end{itemize}
+\end{frame}
+
+\subsection{Stable CLTs without the 2rd moment condition}
+\begin{frame}{Background/Stable CLTs without the 2rd moment condition}
+\begin{itemize}
 \item
 	For stable CLT for supercritical {\color{red} Galton-Watson process} whose {\color{red} offspring distribution
-    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$}, see \cite{Heyde1971Some}.
+    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$}, see Heyde 1971.
 \item
-	For stable CLT for supercritical {\color{red} multi-type Galton-Watson process} and supercritical {\color{red} continuous time branching processes}, see \cite{Asmussen1976Convergence}.
+	For stable CLT for supercritical {\color{red} multi-type Galton-Watson process} and supercritical {\color{red} continuous time branching processes}, see Asmussen 1976.
 \item
@@
 \]
-	with $m>1$ and $\beta\in (0, 1)$ are established in \cite{MarksMilos2018CLT}.
+	with $m>1$ and $\beta\in (0, 1)$ are established in Marks and Milos 2018.
 \item
-	Very recently, some stable fluctuation results of Biggins’ martingales in the context of {\color{red} branching random walks} are established in \cite{IksanovKoleskoMeiners2018Fluctuations}.
+	Very recently, some stable fluctuation results of Biggins’ martingales in the context of {\color{red} branching random walks} are established in Iksanov, Kolesko and Meiners 2018.
 \end{itemize}
 \end{frame}
-\section{Results}
-\begin{frame}[allowframebreaks]{Settings}
+
+\section{Settings}
+\begin{frame}{Settings}
 \begin{itemize}
@@
 \end{itemize}
+\end{frame}
+
+\begin{frame}{Settings/Assumption 1}
+
 \begin{block}{Assumption 1. (Grey's condition)}
@@
 	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Settings/Assumption 2}
+\begin{itemize}
 \item
@@
 \end{block}
+\end{frame}
+
+\begin{frame}{Settings/Assumption 2}
 \begin{itemize}
@@
 \end{itemize}
-\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
-	Suppose that Assumption  2 holds.
-	Suppose that there are constants $\eta'>0, \beta'\in (0,1)$ and $\delta' \in (0, 1-\beta)$ such that
-\[
-	 \int_{(1,\infty)}y^{1+\beta' +\delta'}~\Big|\pi(dy)-\frac{\eta'~dy}{\Gamma(-1-\beta)y^{2+\beta'}}\Big| <\infty.
-\]
-	Then $\eta'= \eta$ and $\beta ' = \beta$.
-\end{lemma}
+\end{frame}
+
+\section{Preliminary}
+\begin{frame}{Preliminary/Invariant measure of OU semigroup}
 \begin{itemize}
 \item
-	Therefore, $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
-\end{itemize}
-\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
-	If $\psi$ satisfies Assumption  2, then $\psi$ satisfies the $L \log L$ condition, i.e.,
-\[
-    \int_{(1,\infty)} y \log y~\pi(dy)< \infty.
-\]
-\end{lemma}
-\begin{itemize}
+  Recall that $(P_t)_{t\geq 0}$ is the transition semigroup of the OU process $\xi$.
 \item
-	This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
-\end{itemize}
-\end{frame}
-\begin{frame}[allowframebreaks]{OU semigroup}
-\begin{itemize}
-\item
-	We use $(P_t)_{t\geq 0}$ to denote the transition semigroup of the OU process $\xi$.
-\item
-	Define
-\[
-    P^{\alpha}_t f(x)
-    :=
-    e^{\alpha t} P_t f(x) =
-    \Pi_x [e^{\alpha t}f(\xi_t)],
-    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
-\]
-	Then $(P^\alpha_t)_{t\geq 0}$ is the mean semigroup of the super OU process $X$, in the sense that
-\[
-    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
-    = \langle P^\alpha_t f, \mu \rangle,
-    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
-\]
-\item
-	The limiting behavior of the super OU process is closely related to the asymptotic property of its mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.
-\item
-    The OU process $(\xi_t)_{t\geq 0}$ has an invariant density
+  $(P_t)_{t\geq 0}$ has the invariant density
 \begin{equation}
@@
 \item
-    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$.
-    Then $L^2(\varphi)$ is a Hilbert space with inner product
+    Let $L^2(\varphi)$ be the Hilbert space with inner product
 \begin{equation}
     \langle f_1, f_2 \rangle_{\varphi}
-    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
+    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x).
 \end{equation}
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Preliminary/Hermite polynomials}
+\begin{itemize}
 \item
@@
     H_p(x)
-    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
+    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{p}}{\partial x^p} \exp(-|x|^2) ,
     \quad x\in \mathbb R^d,
@@
 \end{equation}
-\begin{lemma}[\cite{MetafunePallaraPriola2002Spectrum}]
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Preliminary/Spectrum of OU semigroup}
+
+\begin{lemma}[Metafune, Pallara and Priola 2002]
 	$(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
@@
 \end{lemma}
+\end{frame}
+
+\begin{frame}{Preliminary/Order of a testing function}
+\begin{itemize}
 \item
@@
 \item
-    Let $\mathcal P \subset L^2(\varphi)$ the collection of all functions of polynomial growth.
+    $\mathcal P$: the collection of all functions of polynomial growth.
 \end{itemize}
-\begin{block}{Goal in specific}
-	Let $(X_t)_{t\geq 0}$ be the super OU process which satisfies Assumption 1 and 2.
-	Let $f\in \mathcal P$ and $f\not \equiv 0$.
-	We want to find
-    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
-\[
-    \frac{\langle f, X_t \rangle -G_t}{F_t}
-\]
-    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$.
-\end{block}
+\end{frame}
+
+\section{Results}
+\begin{frame}{Results/Phase transition}
 \begin{itemize}
 \item
-	It turns out that the statements of the results are different in three different regimes
-    depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$.
+  Recall that $\alpha$ is the branching rate.
+\item
+	It turns out that the CLTs of $\left\langle f,X_t \right\rangle$ are different in three different regimes
+    depending on the sign of $\alpha-\frac{\kappa_f b (1+\beta)}{\beta}$:
+\begin{itemize}
+\item
+  small branching rate regime: $\alpha < \frac{\kappa_f b (1+\beta)}{\beta}$;
+\item
+  critical branching rate regime: $\alpha = \frac{\kappa_f b (1+\beta)}{\beta}$;
+\item
+  large branching rate regime: $\alpha > \frac{\kappa_f b (1+\beta)}{\beta}$.
+\end{itemize}
 \end{itemize}
 \end{frame}
-\begin{frame}{Small branching rate regime: $\alpha\beta < \kappa_f b (1+\beta)$}
-\begin{lemma}[\cite{MarksMilos2018CLT}]
-	Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta<\kappa_f b(1+\beta)$.
-	Then the following integral is well defined:
-\begin{equation}
-    m[f]
-    :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
-\end{equation}
-	Moreover, $\theta \mapsto \exp( m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\end{lemma}
-\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
+\begin{frame}{Results/Small branching rate regime/ CLT}
+\begin{theorem}[Ren, Song, S. and Zhao 2019+]
     Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta<\kappa_f b(1+\beta)$.
@@
 \[
-    \|X_t\|^{-\frac{1}{1+\beta}} \langle f,X_t\rangle\xrightarrow[t\rightarrow \infty]{d} \zeta,
+    \|X_t\|^{-\frac{1}{1+\beta}} \langle f,X_t\rangle\xrightarrow[t\rightarrow \infty]{d} \zeta.
 \]
-    where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta \mapsto \exp( m[\theta f])$.
+    Here, $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta \mapsto \exp( m[\theta f])$ with 
+    \begin{equation}
+      m[\theta f]
+      :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-i \theta P_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
+    \end{equation}
 \end{theorem}
 \end{frame}
-\begin{frame}{Critical branching rate regime: $\alpha\beta = \kappa_f b (1+\beta)$}
-\begin{lemma}[\cite{MarksMilos2018CLT}]
-	Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta=\kappa_f b(1+\beta)$, then the following integral is well defined
-\[
-	\widetilde{m}[f]
-    := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
-\]
-	Moreover, $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\end{lemma}
-\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
+
+\begin{frame}{Results/Critical branching rate regime/CLT}
+\begin{theorem}[Ren, Song, S. and Zhao 2019+]
 \label{thm: critical clt}
@@
     (t\|X_t\|)^{-\frac{1}{1+\beta}} \langle f,X_t\rangle
-        \xrightarrow[t\to \infty]{d} \widetilde{\zeta},
+        \xrightarrow[t\to \infty]{d} \widetilde{\zeta}.
 \]
-    where $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with
-    characteristic function $\theta \mapsto \exp( \widetilde m[\theta f])$.
+    Here, $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with
+    characteristic function $\theta \mapsto \exp( \widetilde m[\theta f])$ where
+    \[
+      \widetilde{m}[\theta f]
+      := \eta\int_{\mathbb R^d} \left(-i \theta \sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p(x)\right)^{1+\beta} \varphi(x)~dx.
+    \]
 \end{theorem}
 \end{frame}
-\begin{frame}[allowframebreaks]{Large branching rate regime: $\alpha\beta > \kappa_f b (1+\beta)$.}
-\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
+
+\begin{frame}{Results/Large branching rate regime/ Martingale limit}
+\begin{lemma}[Ren, Song, S. and Zhao 2019]
 	For each multi-index $p\in \mathbb Z_+^d$ with $\alpha \beta > |p|b(1+\beta)$, each $\gamma \in (0,\beta)$ and each $\mu \in \mathcal M(\mathbb R^d)$ with compact support, the following martingale
@@
 \end{lemma}
-\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
+\end{frame}
+
+\begin{frame}{Results/Large branching rate regime/LLNs}
+\begin{theorem}[Ren, Song, S. and Zhao 2019+]
 	Let $f \in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta>\kappa_fb(1+\beta)$. 
@@
 \end{theorem}
+\end{frame}
+
+\begin{frame}{Results/Spectrum decomposition}
 \begin{itemize}
@@
 \begin{align}
-	\mathcal{N}_l
-	&:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
-	\quad \mathcal{C}_l
-	:=Span\{\phi_p:p\in\mathcal N_l\}.
-	\\\mathcal{N}_c
-	&:=\{p\in \mathbb{Z}_+^d:  \alpha\beta=|p|(1+\beta)b\},
-	\quad \mathcal{C}_c
-	:=Span\{\phi_p:p\in\mathcal N_c\}.
-	\\\mathcal{N}_s
-	&:=\{p\in \mathbb{Z}_+^d:  \alpha\beta<|p|(1+\beta)b\},
-	\quad \mathcal{C}_s
-	:=\overline{Span}\{\phi_p:p\in\mathcal N_s\}.
+	&\mathcal{C}_l
+   :=\overline{Span}\{\phi_p: \alpha\beta>|p|(1+\beta)b \}.
+	\\ &\mathcal{C}_c
+  :=\overline{Span}\{\phi_p: \alpha\beta=|p|(1+\beta)b \}.
+	\\&\mathcal{C}_s
+  :=\overline{Span}\{\phi_p: \alpha\beta >|p|(1+\beta)b \}.
 \end{align}
 \item
-	For any $f\in \mathcal P\setminus\{0\}$, we have a unique decomposition: 
+	For any $f\in \mathcal P\setminus\{0\}$, there is a unique decomposition: 
 \[
@@
 \item
-	Not that CLTs for $f_s$ and $f_c$ are already established.
-\item
-	For each $t\ge 0$, define an operator $I_t$ as the inverse of $P_t^\alpha$ on $\mathcal{C}_l$, i.e.
-\begin{align}\label{definition of Itf}
-    I_tf(x)
-    :=\sum_{p\in \mathcal{N}}\langle f, \phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x),
-   \quad x\in \mathbb{R}^d, f\in \mathcal C_l.
-\end{align}
+	CLTs for $f_s$ and $f_c$ are already established.
 \end{itemize}
-\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
-	Let $f\in \mathcal{C}_l\setminus\{0\}$, then the following integral is well defined
-\[
-	\bar{m}[f]
-    := \eta\int_0^\infty e^{\alpha s}~ds \int_{\mathbb R^d} \big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx,
-    \quad f\in \mathcal C_l.
-\]
-	Moreover, $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\end{lemma}
-\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
+\end{frame}
+
+\begin{frame}{Results/Large branching rate regime/CLTs}
+\begin{theorem}[Ren, Song, S. and Zhao 2019+]
 \label{thm: large clt}
@@
 \begin{align}\label{thm: large rate}
-    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow[t\to \infty]{d}\bar{\zeta},
+    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow[t\to \infty]{d}\bar{\zeta}.
 \end{align}
-    where $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with
-    characteristic function $\theta \mapsto \exp( \bar m[\theta f])$.
+    Here $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function $\theta \mapsto \exp( \bar m[\theta f])$ where
+\[
+	\bar{m}[\theta f]
+  := \eta\int_0^\infty e^{\alpha s}~ds \int_{\mathbb R^d} \big(i\theta I_sf(x)\big)^{1+\beta} \varphi(x)~dx,
+  \quad f\in \mathcal C_l
+\]
+and $(I_t)_{t\geq 0}$ are the inverse operator of $(P_t^\alpha)_{t\geq 0}$ on $\mathcal{C}_l$.
 \end{theorem}
 \end{frame}
-\begin{frame}{Interpretation}
+
+\begin{frame}{Remark/Phase transition}
 \begin{itemize}
 \item
-	A phase transition phenomenon for CLT of spatial Markovian branching systems is first observed by \cite{AdamczakMilos2015CLT} in the context of branching OU processes and by \cite{Milos2018Spatial} in the context of super OU processes.
-(Both assuming finite second moment.)
+	Similar phase transition phenomenon in the context of branching OU processes is first observed by Adamczak and Milos 2015.
+
 \item
-	This phase transition phenomenon is due to an interplay of coarsening and smoothing. 
+	Coarsening effect (increasing of the spatial inequalities): A consequence of branching. Simply an area with more particles will produce more offspring.
 \item
-	Coarsening means the increasing of the spatial inequalities.
-It is a consequence of branching: Simply an area with more particles will produce more offspring.
-The coarsening effect is quantified by the branching rate $\alpha$.
+	Smoothing effect (decreasing of the spatial inequalities):  
+	A consequence of the mixing property of the OU process. Simply each OU particles will ``forget'' its initial position exponentially fast.
 \item
-	Smoothing means the decreasing of the spatial inequalities. 
-	It is a consequence of the mixing property of the OU process.
-Imaging an offspring with birth position $x$.
-This OU particle will ``forget'' its initial position exponentially fast.
-This will reduce the spatial inequalities.
-	This smoothing effect is quantified by $b$ (the spectral gap of the OU semigroup).
-\item
-	Put $f\in \mathcal P$ with an order $\kappa_f \geq 1$.
-Consider an OU particle $\xi_t$.
-The expected value of $f(\xi_t)$ will decrease exponentially fast.
-This will also reduce the spatial inequality in the integration $\langle f,X_t\rangle$.
-	This smoothing effect is quantified by $\kappa_f$.
+	The phase transition phenomenon is due to an interplay of the coarsening effect and the smoothing effect.
 \end{itemize}
 \end{frame}
-\section{Methods}
-\begin{frame}[allowframebreaks]{General Ideas}
-\begin{itemize}
-\item
-	For any $\mu\in  \mathcal M(\mathbb R^d)$ and any random variable $Y$ with finite mean, define
-\[
-    \mathcal I_s^t Y:=\mathcal I_s^t [Y, \mu]
-    := \mathbb P_\mu[Y|\mathcal F_t] - \mathbb P_\mu[Y|\mathcal F_s],\quad 0 \leq s \leq t <\infty.
-\]
-\item
-	Then for any $f\in \mathcal{P}$, we have 
-\[
-    \langle f,X_t\rangle
-    :=\sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle+\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle + \langle P^\alpha_tf,X_0\rangle,
-    \quad t\geq 0.
-\]
-\item
-	We can study the fluctuation of $\langle f,X_t\rangle$ by finding the fluctuation of each term $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$.
-\item
-	This idea can be traced back to the CLT of martingales. 
-	Note that $(\mathbb P_\mu[\langle f,X_t\rangle|\mathscr F_s])_{0\leq s\leq t}$ is a martingale in $s$, therefore $\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle$ is simply the conditional increments of this martingale.
-\item
-	Taking $f = 1$ as an example. Note that, conditioned on $X_s = \mu$, the conditional distribution of $\mathcal I_s^{s+1}\langle 1, X_t\rangle$ is the same to the distribution of 
-\[
-	\langle 1, X_1\rangle - \|\mu\|
-\]
-	under probability $\mathbb P_{\mu}$.
-\item
-	Also note that, on the event of non-extinction, $\|X_s\|$ will grow exponentially.
-	So from the branching property, if $s$ is very large, after some normalization, $\mathcal I_s^{s+1}\langle 1, X_t\rangle$ should distributed approximately like a stable random variable.
-\item
-	If the superprocess has finite second moment, then after some normalization $\mathcal I_s^{s+1}\langle 1, X_t\rangle$ will distributed like a Gaussian random variable.
-So we only need to calculate its variance.
-\item
-	However, under our settings, the superprocess has infinite second moment. So we need to develop new method to characterize the distribution of $\mathcal I_s^{s+1}\langle 1, X_t\rangle$.
-\item
-	If $\infty >\kappa_f \geq 1$ then $f$ must take both positive and negative values. 
-	In this case, the Laplace transform of $\langle f,X_t\rangle$ may not exist.
-\end{itemize}
+\begin{frame}
+  \centering \Large
+  \emph{Thanks!}
 \end{frame}
-\begin{frame}[allowframebreaks]{Method}
-\begin{itemize}
-\item
-	Note that $\langle f,X_t\rangle$ is an infinitely divisible random variable. Define its characteristic exponent as
-	\[U_t(\theta f)(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}],
-	\quad t\geq 0, \theta \in \mathbb R, x\in \mathbb R^d.\]
-	It can be proved that $-U_t(\theta f)(x)$ always takes values in $\mathbb C_+:= \{x+iy:x\geq 0, y\in \mathbb R\}$.
-\item
-	Define
-\[
-	\psi_0(z) = \psi(z)+\alpha z = \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
-    \quad  z \in \mathbb R_+.
-\]
-	It can be proved that $\psi_0$ can be uniquely extended as a complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C_+^0:= \{x+iy: x>0, y\in \mathbb R\}$.
-\end{itemize}
-\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
-    If $f\in \mathcal P$, then for all $t\geq 0$ and $x\in E$, we have
-\begin{equation}
-    U_tf(x) -  \int_0^t P_{t-s}^\alpha [\psi_0 \circ (- U_{s}f)](x)~ds
-    = iP_t^{\alpha} f(x).
-\end{equation}
-\end{lemma}
-\begin{itemize}
-\item
-	An analog of this Lemma for general non-persistent superprocesses with spatially dependent branching mechanisms is also developed in \cite{RenSongSunZhao2019Stable}.
-\item
-	Using the above Lemma and Assumption 2, we can derive:
-\end{itemize}
-\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
-    For all $g \in \mathcal P$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C > 0$ such that for all $\lambda > 0$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
-\[
-    \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)({\color{red}\alpha - \kappa_g b})}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)({\color{red}\alpha - \kappa_g b})}}{\lambda}\Big)^{2} \bigg).
-\]
-\end{lemma}
-\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
-    For all $g \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for all $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
-\[
-    \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
-    \leq C e^{t\alpha+(t-s) (\gamma{\color{red}\alpha}- (1+\gamma){\color{red}\kappa_g b})}.
-\]
-\end{lemma}
-\begin{lemma}[\cite{RenSongSunZhao2019Stable}]
-    For all $g \in \mathcal P$, $\mu \in \mathcal M(\mathbb R^d)$ with compact support and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
-\begin{itemize}
-\item
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa_g b)t}$ provided {\color{red}$\alpha\gamma >  (1+\gamma)\kappa_gb$};
-\item
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided {\color{red}$\alpha\gamma = (1+\gamma)\kappa_gb$};
-\item
-    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided {\color{red}$\alpha\gamma < (1+\gamma)\kappa_g b$}.
-\end{itemize}
-\end{lemma}
-\begin{lemma}[\cite{MarksMilos2018CLT}]
-	Let $f\in \mathcal{P}\setminus\{0\}$.
-	Then the following integral is well defined:
-\begin{equation}
-    m_t[f]
-    := \eta \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} (-iP_{s}^\alpha f(x))^{1+\beta} \varphi(x)~dx,
-    \quad t\geq 0.
-\end{equation}
-	Moreover, $\theta \mapsto \exp( m_t[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\end{lemma}
-\begin{theorem}[\cite{RenSongSunZhao2019Stable}]
-\label{thm: small clt}
-    Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta\leq \kappa_f b(1+\beta)$.
-    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-\[
-    \big(\|X_t\|^{-\frac{1}{1+\beta}}\mathcal I^{t-k}_{t-k-1}\langle f,X_t\rangle\big)_{k=1}^n
-    \xrightarrow [t\to \infty]{d} (\zeta_k)_{k=1}^n.
-\]
-    where $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions
-\[
-     \mathbf E[e^{i\theta \zeta_k}] = \exp( m_k[\theta f]),\quad k \in \mathbb N.
-\]
-\end{theorem}
-\begin{itemize}
-\item
-	For the small branching regime $\alpha \beta < \kappa_f b(1+\beta)$. The above Theorem roughly says that
-\[
-	\|X_t\|^{-\frac{1}{1+\beta}}\langle f,X_t\rangle \xrightarrow[t\to \infty]{d} \sum_{k=0}^\infty \zeta_k \overset{d}{=}: \zeta,
-\]
-	where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function
-\[
-	E[e^{i\theta \zeta}] = \exp(m[\theta f]) := \exp\Big(\sum_{k=0}^\infty m_k[\theta f]\Big).
-\]
-\item
-	For the critical branching regime $\alpha \beta = \kappa_f b(1+\beta)$. The above Theorem roughly says that
-\[
-	(t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle \overset{d}{\approx} t^{-\frac{1}{1+\beta}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{d} \widetilde \zeta
-\]
-	where $\widetilde \zeta$ is a $(1+\beta)$-stable random variable with characteristic function
-\[
-	E[e^{i\theta \widetilde \zeta}] = \exp(\widetilde m[\theta f]) := \exp\Big(\lim_{t\to \infty} \frac{1}{t} \sum_{k=0}^{\lfloor t\rfloor} m_k[\theta f]\Big),\quad \theta \in \mathbb R.
-\]
-\item
-	For  testing functions $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$. 
-\item
-	Taking $f = \phi_p$ with $\alpha \beta > |p|b(1+\beta)$ as an example, we do the following decomposition:
-\[
-    H^p_t-H^p_\infty=\sum^{\infty}_{n=1}(H^p_{t+n-1}-H^p_{t+n}).
-\]
-    We established the fluctuation behaviors of each terms.
-\end{itemize}
-\end{frame}
-\begin{frame}[allowframebreaks]{Remarks}
-\begin{itemize}
-\item
-	For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$ where $f_l \in \mathcal C_l$, $f_c \in \mathcal C_c$ and $f_s\in \mathcal C_s$.
-	Our main results give CLT for $\langle f_l, X_t\rangle$, $\langle f_c, X_t\rangle$ and $\langle f_s, X_t\rangle$, respectively.
-\item
-	We conjecture that the limits of these three terms, normalized properly, are independent.
-	If this is valid, we can get a CLT for $\langle f, X_t\rangle$ for general $f\in\mathcal{P}$.
-\item
-	This independence was proved under the second moment condition by \cite{RenSongZhang2015Central}.
-\item
-	We only considered a special case: Super OU with spatial independent branching mechanism. 
-	It is interesting to ask whether stable CLTs are valid for general superprocesses with spatially dependent branching mechanism.
-\end{itemize}
-\end{frame}
-\begin{frame}[allowframebreaks]
-	\frametitle{References}
-	\printbibliography
-\end{frame}
+
 \end{document}

### 2019-07-30 supCLT.tex
change supCLT.tex

@@
     where $\sigma > 0$ and $b > 0$ are constants.
-        Let the \emph{branching mechanism} $\psi$ be a function on $\mathbb R_+$ which takes the form of
+%        Let the \emph{branching mechanism} $\psi$ be a function on $\mathbb R_+$ which takes the form of
+ Let $\psi$ be a function on $\mathbb R_+$ of the form 
 \begin{equation} \label{eq: honogeneou branching mechanism}
@@
 	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty$.
-	We refer to $\pi$ as the \emph{L\'evy measure} of the branching mechanism $\psi$.
+%	We refer to $\pi$ as the \emph{L\'evy measure} of the branching mechanism $\psi$.
+$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure
+of $\psi$.
     Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
     For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
-    We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have
-\[
+    We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have
+%\[
+$
     \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
-\]
+%\]
+$
        We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
 on a measurable space $(\Omega, \mathcal{F})$
-       is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+       is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, 
+     or a $(\xi, \psi)$ superprocess,  
+       if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
 \begin{equation}
@@
     Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$,
-    for every Lebesgue-almost everywhere continuous bounded non-negative function $f$ on $\mathbb R^d$,
+    for every Lebesgue-a.\/e. continuous bounded non-negative function $f$ on $\mathbb R^d$,
     we have
     $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f, \varphi\rangle $,
-    where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and
+    where $H_\infty$ is the limit of the martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and
 $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
@@
     $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
-\[
-    \frac{\langle f, X_t \rangle -G_t}{F_t}
-\]
-    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of testing functions $f$.
-    It turns out that the statements of the CLT are different in three regimes
+%\[
+$
+ %   \frac{\langle f, X_t \rangle -G_t}{F_t}
+    (\langle f, X_t \rangle -G_t)/F_t
+%\]
+$
+    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
+    It turns out that the statements of the CLT's are different in three regimes
     depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
@@
     There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
-    See
-    \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes,
-    \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Watson processes,
+   See   \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for %supercritical Galton-Watson processes,
+   supercritical Galton-Watson processes (GW processes),
+    \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type %Galton-Watson processes,
+    GW processes
     \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-    In \cite{AdamczakMilos2015CLT},
-    Adamczak and Mi\l{}o\'s proved some spatial central limit theorems for 
-    supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} 
-    Mi\l{}o\'s proved some spatial central limit theorems for 
-    supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+%In \cite{AdamczakMilos2015CLT}, Adamczak and Mi\l{}o\'s proved some spatial central limit theorems for   supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Mi\l{}o\'s proved some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+Some spatial central limit theorems for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
     These two papers made connections between the CLT and  the branching rate regimes.
-    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some spatial central limit theorems for supercritical super-OU 
-    processes with branching mechanisms satisfying 
-    only a second moment condition.
-    Moreover,
-    compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
-    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central},
-    Ren, Song and Zhang also established a series of spatial central limit theorems for a large class of general 
-    supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
+%In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition.
+Some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition were established in \cite{RenSongZhang2014Central}.
+Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
+%In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}, Ren, Song and Zhang also established a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
+Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms
+were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
     The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
 
-    There are also many limiting theorem type results 
-    for supercritical branching processes and branching Markov processes
-    with branching mechanisms of infinite second moments.
+There are also many limiting theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moments.
 Heyde \cite{Heyde1971Some} established a central limit type  theorem 
-    for supercritical Galton-Watson process when the offspring distribution
+%for supercritical Galton-Watson process when the offspring distribution
+for supercritical GW processes when the offspring distribution
 belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
-    and   proved that the limit law is  a stable law.
-Similar results  for supercritical multi-type Galton-Watson processes and supercritical  continuous time branching processes, under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
+and   proved that the limit law is  a stable law. Similar results  for supercritical multi-type 
+%Galton-Watson processes and supercritical  continuous time branching processes, 
+GW processes and supercritical  continuous time branching processes, 
+under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
 were given in Asmussen \cite{Asmussen76Convergence}.
 Recently,   Marks and Milo\'s \cite{MarksMilos2018CLT}
-    considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law.
+%considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes 
+considered the limit behavior of supercritical branching OU processes
+with a special stable branching law.
 	They established some spatial central limit theorems in the small and critical branching rate regimes,
@@
     In fact,
-\begin{equation}
+%\begin{equation}
+$
     \mathbb{P}_{\mu} (D)
     = e^{-\bar v \|\mu\|},
-    \quad \mu\in \mathcal M(\mathbb R^d),
-\end{equation}
+%    \quad \mu\in \mathcal M(\mathbb R^d),
+%\end{equation}
+$ for $\mu\in \mathcal M(\mathbb R^d)$,
     where
-\[
+%\[
+$
 	\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
-\]
+%\]
+$
 	is the largest root of $\psi$.
@@
 	$L \log L$ condition, i.e.,
-\[
+%\[
+$
 	\int_{(1,\infty)} y\log y~\pi(dy) < \infty.
-\]
+%\]
+$
     This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
@@
     the order of the function $f$ in the spectral decomposition \eqref{semicomp1}.
+%new
+$\kappa_f$ corresponds to the lowest non-trivial frequency in the eigen-expansion of $f$.
+%end new    
     Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
@@
     The asymptotic behavior varies with the following three regimes:
-    \begin{itemize}
-\item
-    The large branching rate regime: $\alpha\beta>\kappa_fb(1+\beta)$;
-\item
-    The critical branching rate regime: $\alpha\beta=\kappa_fb(1+\beta)$;
-\item
-    The small branching rate regime: $\alpha\beta<\kappa_fb(1+\beta)$.
-\end{itemize}
+%    \begin{itemize}
+%\item
+%    The large branching rate regime: $\alpha\beta>\kappa_fb(1+\beta)$;
+%\item
+%    The critical branching rate regime: $\alpha\beta=\kappa_fb(1+\beta)$;
+%\item
+%    The small branching rate regime: $\alpha\beta<\kappa_fb(1+\beta)$.
+%\end{itemize}
+(1) the small branching rate regime where $\alpha\beta<\kappa_fb(1+\beta)$; (2) the 
+critical branching rate regime where $\alpha\beta=\kappa_fb(1+\beta)$; and
+(3) the large branching rate regime where $\alpha\beta>\kappa_fb(1+\beta)$.
 
@@
 \]
-    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
-    However, to get  almost sure convergence for bounded, non-negative, and Lebesgue-almost everywhere continuous testing functions $f$, we do not need $f$ to be twice differentiable.
+    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have a.\/s.\ convergence.
+    However, to get  a.\/s.\ convergence for bounded non-negative 
+    Lebesgue-a.\/e.\/\ continuous functions $f$, we do not need $f$ to be twice differentiable.
 See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
@@
 \begin{rem}
-    For general test functions $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton} and \cite{EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
+    For general $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which
+the first order asymptotic ($\kappa_f=0$) was identified.
     \end{rem}
@@
     where $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function
-\begin{align}
-    \mathbf{E}[e^{i\theta\bar{\zeta}}]=\exp(\bar{m}[\theta f]),\quad \theta\in \mathbb{R}.
-\end{align}
+%\begin{align}
+%    \mathbf{E}[e^{i\theta\bar{\zeta}}]=\exp(\bar{m}[\theta f]),\quad \theta\in \mathbb{R}.
+%\end{align}
+$\theta\mapsto \exp(\bar{m}[\theta f])$.
 \end{thm}
@@
     characteristic function
-\[
-     \mathbf E [e^{i\theta \widetilde{\zeta}}]
-    =\exp(\widetilde{m}[\theta f]),
-    \quad \theta\in \mathbb R.
-\]
+%\[
+%     \mathbf E [e^{i\theta \widetilde{\zeta}}]
+%    =\exp(\widetilde{m}[\theta f]),
+%    \quad \theta\in \mathbb R.
+%\]
+$\theta\mapsto \exp(\widetilde{m}[\theta f]$.
 \end{thm}
@@
     where $\zeta$ is a $(1+\beta)$-stable random variable with
-\[
-       \mathbf E[e^{i\theta \zeta}]
-    =\exp(m[\theta f]),
-    \quad \theta\in \mathbb R.
-\]
+%\[
+%       \mathbf E[e^{i\theta \zeta}]
+%    =\exp(m[\theta f]),
+%    \quad \theta\in \mathbb R.
+%\]
+characteristic function $\theta\mapsto \exp(m[\theta f])$.
 \end{thm}
@@
 
-    Suppose that $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions
-\[
-     \mathbf E[e^{i\theta \zeta_k}] = \exp( m_k[\theta f]),\quad k \in \mathbb N,
-\]
+    Suppose $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions
+%\[
+%     \mathbf E[e^{i\theta \zeta_k}] = \exp( m_k[\theta f]),\quad k \in \mathbb N,
+%\]
+$\theta\mapsto \exp( m_k[\theta f])$,
     where $m_k[f]$ is given in Lemma \ref{lem: def of all m} below.
-    Recall that $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
+    Recall $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
     Lemma \ref{lem: mainlemma} and 
@@
 	where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function
-\[
-    \mathbf E[e^{i\theta \zeta}] = \exp(m[\theta f]),\quad \theta \in \mathbb R.
-\]
+%\[
+%    \mathbf E[e^{i\theta \zeta}] = \exp(m[\theta f]),\quad \theta \in \mathbb R.
+%\]
+$\theta\mapsto \exp(m[\theta f])$,
     with $m[\theta f]$ given in Lemma \ref{lem: def of all m} below.
@@
 	where $\widetilde \zeta$ is a $(1+\beta)$-stable random variable with characteristic function
-\[
-    \mathbf E[e^{i\theta \widetilde \zeta}] = \exp(\widetilde m[\theta f]),\quad \theta \in \mathbb R.
-\]
-
-    For  testing functions $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
+%\[
+%    \mathbf E[e^{i\theta \widetilde \zeta}] = \exp(\widetilde m[\theta f]),\quad \theta \in \mathbb R.
+%\]
+$\theta\mapsto \exp(\widetilde m[\theta f])$.
+
+    For  $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
 Taking $f = \phi_p$ with $\alpha \beta > |p|b(1+\beta)$ as an example, we do the following decomposition:
@@
     This fact will be used at several places in this paper, and we think it is of independent interest.
-
+\begin{comment}
     We end this section with a list of frequently used notations:
@@
 \end{itemize}
+\end{comment}
 
@@
 	The function $\psi_1$ on $\mathbb R_+$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
-		Moreover, for each $\delta > 0$ small enough, there exists a  constant $C>0$ such that for all $z\in \mathbb C_+$, we have
+		Moreover, for each $\delta > 0$ small enough, there exists $C>0$ such that for all $z\in \mathbb C_+$, we have
 $
@@
 \label{lem: unique of beta and eta}
-Suppose that Assumption  \ref{asp: branching mechanism} holds.
-	Suppose that there are constants $\eta'>0, \beta'\in (0,1)$ and $\delta' > 0$ such that
+Suppose Assumption  \ref{asp: branching mechanism} holds. Suppose that there are $\eta', \delta'>0$ and $\beta'\in (0,1)$ such that
 \[
@@
 	This implies that
-\[
+%\[
+$
 	\eta' z^{\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0.
-\]
+%\]
+$
 	So we must have $\beta'= \beta$ and $\eta'= \eta$.
@@
 
-	We also have the following result:
+%	We also have the following result:
 \begin{lem}
@@
     For any function $h: [0,\infty) \to [0,\infty)$, we say an operator $R: \mathcal P^+ \to \mathcal P^+$ is an \emph{$h$-controller} if
-\begin{itemize}
-\item
-    $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and
-\item
-    $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
-\end{itemize}
+%\begin{itemize}
+%\item
+%    $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and
+%\item
+%    $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
+%\end{itemize}
+(1) $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and (2) $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
        For a subset $\mathcal D$ of $\mathcal P^*$ and an $h$-controller $R$, we say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controlled by $R$ on $\mathcal D$} if $|Af| \leq R|f|$ for each $f\in \mathcal D$.
@@
 Suppose that $\Lambda$ is an index set and $(A_\lambda)_{\lambda\in \Lambda}$ is a
-family of operators from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$.
-    Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
+%family of operators from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$.
+%    Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
+family of operators, from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$,
+which is uniformly 
+%$h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
+$h$-controlled by $R_A$ on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
+Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators, from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$,
+% which is  is uniformly $g$-controllable on $\mathcal D_0$ 
+which is  is uniformly $g$-controlled by $R_B$ on $\mathcal D_0$ 
+ for some function $g: [0,\infty) \to [0,\infty)$. Suppose that
+ $(C_\lambda)_{\lambda\in \Lambda} $ is a family of operators, from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$,
+% for each $\lambda \in \Lambda$, $C_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$. 
+which is  is uniformly $k$-controlled by $R_C$ on $\mathcal D_0$  
+for a given function $k:[0,\infty) \to [0, \infty)$.
+ Then 
 \begin{itemize}
 \item[(1)]
-    Suppose that $(\Lambda, \mathscr F)$ is a measurable space and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
+$(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$;
+\item[(2)]
+%    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$.
+%    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D_0$ for some function $g: [0,\infty) \to [0,\infty)$.
+$(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$ and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$;
+\item[(3)] For any $a>0$, $(C^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(k^a)$-controllable.
+%    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
+%    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D$ for some function $g: [0,\infty) \to [0,\infty)$.
+\item[(4)]
+ %   Let $a>0$.
+%    Suppose that, for each $\lambda \in \Lambda$, $A_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
+  Suppose further that $(\Lambda, \mathscr F)$ is a measurable space and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
     For any probability measure $\nu$ on $(\Lambda, \mathscr F)$,  we write
@@
     Then  $\{A_\nu: \nu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $h$-controllable on $\mathcal D$.
-\item[(2)]
-    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$.
-    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D_0$ for some function $g: [0,\infty) \to [0,\infty)$.
-    Then $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$.
-\item[(3)]
-    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
-    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D$ for some function $g: [0,\infty) \to [0,\infty)$.
-    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$ and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$.
-\item[(4)]
-    Let $a>0$.
-    Suppose that, for each $\lambda \in \Lambda$, $A_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
-    Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable.
 \end{itemize}
@@
 \begin{proof}
-    (1). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
+    (1). 
+%    Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by  an $h$-controller $R_A$ on $\mathcal D$.
+%    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D_0$.
+%    Then we have
+%\begin{itemize}
+%\item
+%    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, we have $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
+%\item
+%        If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_AR_Bf \leq R_A R_B g$.
+%\item
+%       If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_AR_B(\theta f) \leq R_A(g(\theta) R_Bf) \leq (h\circ g)(\theta) R_A R_B f $.
+%\end{itemize}
+If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, then $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
+ If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_AR_Bf \leq R_A R_B g$.
+ If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_AR_B(\theta f) \leq R_A(g(\theta) R_Bf) \leq (h\circ g)(\theta) R_A R_B f $.
+%    Therefore 
+Combining these, we get that
+    $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$.
+
+    (2). 
+    %Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R_A$ on $\mathcal D$.
+%    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
+%    Then we have
+%\begin{itemize}
+%\item
+%    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
+%\item
+%       If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_A\times R_Bf \leq R_A\times R_B g$.
+%\item
+%        If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_A\times R_B (\theta f) \leq h(\theta) g(\theta) (R_A \times R_B) f $.
+%\end{itemize}
+%    Therefore $(A_\lambda \times B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \times g)$-controllable on $\mathcal D$.
+If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, then $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
+If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_A\times R_Bf \leq R_A\times R_B g$.
+If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_A\times R_B (\theta f) \leq h(\theta) g(\theta) (R_A \times R_B) f $.
+Combining these, we get that $(A_\lambda \times B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \times g)$-controllable on $\mathcal D$.
+
+%    We also have the following:
+%\begin{itemize}
+%\item
+%    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
+%\item
+%        If $f,g \in \mathcal P^+$ with $f\leq g$, then $(R_A + R_B)f \leq (R_A + R_B) g$.
+%\item
+%        If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $(R_A + R_B) (\theta f) \leq h(\theta) R_Af + g(\theta) R_Bf \leq (h(\theta) \vee g(\theta)) (R_A+R_B)f $.
+%\end{itemize}
+%    Therefore $(A_\lambda + B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \vee g)$-controllable on $\mathcal D$.
+If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, then $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
+If $f,g \in \mathcal P^+$ with $f\leq g$, then $(R_A + R_B)f \leq (R_A + R_B) g$.
+If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $(R_A + R_B) (\theta f) \leq h(\theta) R_Af + g(\theta) R_Bf \leq (h(\theta) \vee g(\theta)) (R_A+R_B)f $.
+Combining these, we get that $(A_\lambda + B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \vee g)$-controllable on $\mathcal D$.
+
+    (3). 
+    %Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
+%Then we have the following:
+%\begin{itemize}
+%\item
+%    For each $\lambda \in \Lambda$, $f\in \mathcal D$, we have $|A_\lambda^{\times a} f| = |A_\lambda f|^a  \leq R^{\times a} |f|$.
+%\item
+%        If $f,g \in \mathcal P^+$ with $f\leq g$, then $R^{\times a}f \leq R^{\times a} g$.
+%\item
+%        If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R^{\times a}(\theta f) \leq (h(\theta) R f)^a = h(\theta)^a R^{\times a}f$.
+%\end{itemize}
+%    Therefore $(A_\lambda^{\times a})_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable on $\mathcal D$.
+If $\lambda \in \Lambda$, $f\in \mathcal D$, then $|C_\lambda^{\times a} f| = |C_\lambda f|^a  \leq R_C^{\times a} |f|$.
+If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_C^{\times a}f \leq R_C^{\times a} g$.
+If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_C^{\times a}(\theta f) \leq (k(\theta) R_C f)^a = k(\theta)^a R_C^{\times a}f$.
+Combining these, we get that $(C_\lambda^{\times a})_{\lambda \in \Lambda}$ is uniformly $(k^a)$-controllable on $\mathcal D$.
+
+    (4).     
+    %Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
     For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
 \[
-    |A_{\nu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\nu(d\lambda) \leq \int_{\Lambda}R|f|(x)\nu(d\lambda) \leq R|f|(x).
-\]
-
-    (2). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by  an $h$-controller $R_A$ on $\mathcal D$.
-    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D_0$.
-    Then we have
-\begin{itemize}
-\item
-    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, we have $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
-\item
-        If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_AR_Bf \leq R_A R_B g$.
-\item
-       If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_AR_B(\theta f) \leq R_A(g(\theta) R_Bf) \leq (h\circ g)(\theta) R_A R_B f $.
-\end{itemize}
-    Therefore $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$.
-
-    (3). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R_A$ on $\mathcal D$.
-    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
-    Then we have
-\begin{itemize}
-\item
-    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
-\item
-       If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_A\times R_Bf \leq R_A\times R_B g$.
-\item
-        If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_A\times R_B (\theta f) \leq h(\theta) g(\theta) (R_A \times R_B) f $.
-\end{itemize}
-    Therefore $(A_\lambda \times B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \times g)$-controllable on $\mathcal D$.
-
-    We also have the following:
-\begin{itemize}
-\item
-    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
-\item
-        If $f,g \in \mathcal P^+$ with $f\leq g$, then $(R_A + R_B)f \leq (R_A + R_B) g$.
-\item
-        If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $(R_A + R_B) (\theta f) \leq h(\theta) R_Af + g(\theta) R_Bf \leq (h(\theta) \vee g(\theta)) (R_A+R_B)f $.
-\end{itemize}
-    Therefore $(A_\lambda + B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \vee g)$-controllable on $\mathcal D$.
-
-    (4). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
-Then we have the following:
-\begin{itemize}
-\item
-    For each $\lambda \in \Lambda$, $f\in \mathcal D$, we have $|A_\lambda^{\times a} f| = |A_\lambda f|^a  \leq R^{\times a} |f|$.
-\item
-        If $f,g \in \mathcal P^+$ with $f\leq g$, then $R^{\times a}f \leq R^{\times a} g$.
-\item
-        If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R^{\times a}(\theta f) \leq (h(\theta) R f)^a = h(\theta)^a R^{\times a}f$.
-\end{itemize}
-    Therefore $(A_\lambda^{\times a})_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable on $\mathcal D$.
+    |A_{\nu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\nu(d\lambda) \leq \int_{\Lambda}R|f|(x)\nu(d\lambda) \leq R|f|(x). \qedhere
+\]
 \end{proof}
@@
   Using an argument similar to the proof  of Lemma \ref{lem: complex extension for psi1},
-    both functions $\psi$, $\psi_0$ can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C^0_+$.
+%    both functions $\psi$, $\psi_0$ 
+$\psi, \psi_1$ and $\psi_0$ 
+    can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C^0_+$.
     For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, we define
-\begin{align}
-\label{eq: def of operator Psi}
-    \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
-    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x),
-    \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big).
-\end{align}
+%\begin{align}
+%\label{eq: def of operator Psi}
+%    \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
+%    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x),
+%    \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big).
+%\end{align}
+$\Psi f (x) = -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big)$. $\Psi_1 f(x)$ and
+$Psi_0 f(x)$ are defined similarly.
     For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let
@@
     be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
+    %new
+    (See the paragraph after Lemma \ref{lem: Lip of power function}.)
+    %end new
     It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
@@
        For all $t\geq 0$ and $f\in \mathcal P$, we define
-\begin{align}
-\label{eq: def of Zf}
-    Z_t f
-    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,
-    \\ Z'_t f
-    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,
-    \\ Z''_t f
-    &:= \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
-    \\ Z'''_t f
-    &:= (Z'_t - Z_t+ Z''_t)f.
+\begin{align}\label{eq: def of Zf}
+   & Z_t f
+    := \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,
+%   \\ Z'_t f
+\qquad Z'_t f
+    := \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,\\
+ &  Z''_t f
+    := \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
+%    \\ Z'''_t f
+\qquad \qquad\  Z'''_t f
+    := (Z'_t - Z_t+ Z''_t)f.
 \end{align}
@@
     Q_\kappa f
-    := \sup_{t\geq 0} e^{\kappa b t}|P_t f|
-\end{equation}
-    and
-\begin{equation}\label{Q}
-    Q f:= Q_{\kappa_f}f.
-\end{equation}
+%    := \sup_{t\geq 0} e^{\kappa b t}|P_t f|
+    := \sup_{t\geq 0} e^{\kappa b t}|P_t f|, \qquad  Q f:= Q_{\kappa_f}f.
+\end{equation}
+%    and
+%\begin{equation}\label{Q}
+%    Q f:= Q_{\kappa_f}f.
+%\end{equation}
     Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
@@
     (3).
-        According to Lemma \ref{lem: complex extension for psi1},
-         there exist constants $C, \delta >0$ 
+        By Lemma \ref{lem: complex extension for psi1},
+         there exist $C, \delta >0$ 
          satisfying $\beta+\delta< 1$ such that for all
@@
 
-    (4). From parts (1)--(3) of this lemma and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
+    (4). 
+%    From parts (1)--(3) of this lemma and Lemma \ref{lem: property of controllable operators}.(2), 
+From (1)--(3) above and Lemma \ref{lem: property of controllable operators}.(1), 
+we know that the operators
 \[
@@
     are uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable.
-    Combining this with \eqref{eq:chareq2} and Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.
+    Combining this with \eqref{eq:chareq2} and 
+    %Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.
+    Lemma \ref{lem: property of controllable operators}.(4), we get the desired result.
 
@@
 \]
-    Now using parts (1), (2) and  (4) of this lemma, and Lemma \ref{lem: property of controllable operators}.(3)--(4), we get that operators
+%    Now using parts (1), (2) and  (4) of this lemma, and Lemma \ref{lem: property of controllable operators}.(3)--(4), we get that operators
+Now using (1), (2) and  (4) above, and Lemma \ref{lem: property of controllable operators}.(2)--(3), we get that the operators
 \[
@@
     are uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable.
-    Combining this with Lemma \ref{lem: property of controllable operators}.(1)-(2), and
+    Combining with Lemma \ref{lem: property of controllable operators}.(1) and (4), and
 \begin{equation}
@@
 
-    (6).  According to Lemma \ref{lem: complex extension for psi1}, for any $\delta > 0$ small enough, there exists a constant $C>0$ such that
+    (6).  By  Lemma \ref{lem: complex extension for psi1}, for any $\delta > 0$ small enough, there exists  $C>0$ such that
 \[
@@
     Therefore, for any $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-        Combining  this with parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we get that, for any $\delta > 0$ small enough, the operators
+        Combining  this  (1)--(2) above, and Lemma \ref{lem: property of controllable operators}.(1) and (4), we get that, for any $\delta > 0$ small enough, the operators
 \[
@@
 
-    (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from parts (5)-- (6) of this lemma  and Lemma \ref{lem: property of controllable operators}.(3).
+    (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from (5)-- (6) above and Lemma \ref{lem: property of controllable operators}.(2).
 \end{proof}
@@
 
-    In this subsection, we will show that the $(1+\beta)$-stable random variables in Theorem \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
+    In this subsection, we will show that the $(1+\beta)$-stable random variables in Theorems \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
 
@@
 \]
-	Furthermore, there exists a constant $C>0$ such that
+	Furthermore, there exists  $C>0$ such that
 \begin{equation}\label{domi-m}
@@
 \]
-    Furthermore, there exists a constant $C>0$ such that
+    Furthermore, there exists  $C>0$ such that
 \begin{equation}
@@
 \begin{proof}
-    (1). See \cite[Lemma 2.7]{MarksMilos2018CLT}.
-
-    (2). We first claim that there exists $h\in \mathcal{P}$ such that
+%    (1). See \cite[Lemma 2.7]{MarksMilos2018CLT}.
+(1) is  \cite[Lemma 2.7]{MarksMilos2018CLT} (3) is \cite[Lemma 4.2]{MarksMilos2018CLT}.
+ is obvious from (2), noticing that $\alpha\beta>K(1+\beta)b$. (5) is obvious from (1).
+So we only need to  (2). We first claim that there exists $h\in \mathcal{P}$ such that
 \[
@@
 \end{equation}
-    Therefore there exists a constant $C>0$ such that
+    Therefore there exists  $C>0$ such that
 \begin{align}
@@
 \end{align}
-
-    (3). This is obvious from (2), noticing that $\alpha\beta>K(1+\beta)b$.
-
-    (4). See \cite[Lemma 4.2]{MarksMilos2018CLT}.
-
-    (5). This is obvious from (1).
+%
+%    (3). This is obvious from (2), noticing that $\alpha\beta>K(1+\beta)b$.
+%
+%    (4). See \cite[Lemma 4.2]{MarksMilos2018CLT}.
+%
+%    (5). This is obvious from (1).
 \end{proof}
@@
 \label{item: stable 2}
-    $\theta \mapsto \exp(\bar{m}_t[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$.
+    $\theta \mapsto \exp(\bar{m}_t[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$;
 \item
@@
    $\theta \mapsto \exp(\bar m[\theta f])$
-    is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$.
+    is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$;
 \item
@@
 \]
-        Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\'evy measure of an $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is
+        Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\'evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is
 \[
@@
 
-The proofs of \eqref{item: stable 2}, \eqref{item: stable 3}, \eqref{item: stable 4} and \eqref{item: stable 5} are similar to that of \eqref{item: stable 1}. We omit the details here.
+The proofs of \eqref{item: stable 2}--\eqref{item: stable 5} are similar to that of \eqref{item: stable 1}. We omit the details here.
 \end{proof}
@@
     Then there exists $h\in \mathcal{P}$ such that
-\begin{align}
-    |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
-\end{align}
+%\begin{align}
+%    |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
+%\end{align}
+$|P_sg_k|\leq e^{-bs}h$ for all $s, k \geq 0.$
 \end{lem}
@@
     Then there exists $h\in \mathcal{P}$ such that
-\begin{align}
-    |P_s\bar{g}_t|
-    \leq e^{-bs}h,\quad s\geq 0, t\geq 0.
-\end{align}
+%\begin{align}
+%    |P_s\bar{g}_t|
+%    \leq e^{-bs}h,\quad s\geq 0, t\geq 0.
+%\end{align}
+$|P_s\bar{g}_t| \leq e^{-bs}h$ for all $s, t\geq 0.$
 \end{lem}
@@
 \]
-    Therefore, using \eqref{eq: key estimation for partial} and the above, there exists a constant $C> 0$ such that for all $t\geq 0$,
+    Therefore, using \eqref{eq: key estimation for partial} and the above, there exists  $C> 0$ such that for all $t\geq 0$,
 \begin{align}
@@
 \end{align}
-Therefore there exist constants $c,n>0$ such that
+Therefore there exist $c,n>0$ such that
 \begin{align}\label{ineq: control of sup gt}
@@
     In particular, it contains the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$ for each $s\geq 0$.
-    Also, note that
-\[
-    |\sqrt {1-\theta} - 1| \leq \theta, \quad \theta\in [0,1]
-\]
+%    Also, note that
+%\[
+%    |\sqrt {1-\theta} - 1| \leq \theta, \quad \theta\in [0,1]
+%\]
+$|\sqrt {1-\theta} - 1| \leq \theta$ for all $\theta\in [0,1]$,
 and
-\[
-    1+\theta + \lambda \leq (1+\theta)(1+\lambda), \quad \theta ,\lambda \geq 0.
-\]
+%\[
+%    1+\theta + \lambda \leq (1+\theta)(1+\lambda), \quad \theta ,\lambda \geq 0.
+%\]
+$1+\theta + \lambda \leq (1+\theta)(1+\lambda)$ for all $\theta ,\lambda \geq 0$.
 	Using the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, 
@@
     Suppose that $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
-    Then, for each $x\geq 0$, there exist constants $C,\delta>0$ such that
+    Then, for each $x\geq 0$, there exist $C,\delta>0$ such that
 \[
@@
 \end{equation}
-    It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, the following statements are true:
-\begin{itemize}
-\item
-    $0\leq \bar v_t < \infty$ for all $t>0$.
-\item
-    $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
-\end{itemize}
+    It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, 
+%the following statements are true:
+%\begin{itemize}
+%\item
+%    $0\leq \bar v_t < \infty$ for all $t>0$.
+%\item
+%    $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
+%\end{itemize}
+we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; and (ii) $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
     Letting $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
@@
     Therefore we have
-\begin{itemize}
-\item
-    $\bar v > 0$ ,
-\item
-    $\psi(z) < 0$ on $z\in (0,\bar v)$,
-\item
-    $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
-\end{itemize}
+%\begin{itemize}
+%\item
+%    $\bar v > 0$ ,
+%\item
+%    $\psi(z) < 0$ on $z\in (0,\bar v)$,
+%\item
+%    $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
+%\end{itemize}
+(i) $\bar v > 0$; (ii) $\psi(z) < 0$ on $z\in (0,\bar v)$; and (iii) $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
     It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that
@@
     if $\lambda \in (0,\bar v)$, then $0<\lambda \leq v_t(\lambda)<\bar v $ and
-\begin{align}
-\label{CSBP: int}
+\begin{align}\label{CSBP: int}
     \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0;
@@
     \\ &= e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
-    \\&\leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big),
+    \leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big),
 \end{align}
@@
 
-    Step 3. We will show that there exist constants
+    Step 3. We will show that there exist
     $c_2, \delta_1, t_0 > 0$ such that
@@
     According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
-\[
-   t_0
-    := \int^\infty_{z_0} \frac{dz}{\psi(z)} < \infty.
-\]
+%\[
+%   t_0
+%    := \int^\infty_{z_0} \frac{dz}{\psi(z)} < \infty.
+%\]
+$t_0 := \int^\infty_{z_0}\psi(z)^{-1}dz<\infty$.
 For each $t > t_0$, according to \eqref{eq:svp2}, we have
@@
     Rearranging, we get
-\[
+%\[
+$
     \bar v_t - \bar v \leq (z_0 - \bar v)e^{-\tau(t-t_0)},
-    \quad t\geq t_0.
-\]
+%    \quad t\geq t_0.
+$ for all $t\geq t_0$.
+%\]
     This implies the desired result in this step.
 
-    Step 4: We will show that there exist
-    constants $c_3, \delta_2, t_1>0$ such that
+    Step 4: We will show that there exist $c_3, \delta_2, t_1>0$ such that
 \[
@@
     Define
-\[
-    \rho_t := 1+ \frac{\log k_t}{t\alpha}, \quad t\geq 0.
-\]
-    According to the fact that
-\[
-    k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}, \quad t\geq 0,
-\]
+%\[
+%    \rho_t := 1+ \frac{\log k_t}{t\alpha}, \quad t\geq 0.
+%\]
+$\rho_t := 1+(\log k_t)/(t\alpha)$ for all $t\geq 0$.
+%    According to the fact that
+%\[
+%    k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}, \quad t\geq 0,
+%\]
+By the fact that $k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}$ for  all $t\geq 0$
     and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$,
@@
         Then using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have for $t>0$ large enough,
-
-\begin{align}
-    &t =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
-    \\&= \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)}
+\begin{align}
+    t& =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
+    = \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)}
      \\&= \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
@@
     Therefore, there exist
-    constants $c_3>0$ and $t_1>0$ such that for all $t\geq t_1$,
+    $c_3>0$ and $t_1>0$ such that for all $t\geq t_1$,
 \[
@@
 
-    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exist
-    constant $c_4, \delta_3, t_2 > 0$ such that
+    Finally, by Steps 2-4, we have for each $x\geq 0$, there exist
+     $c_4, \delta_3, t_2 > 0$ such that
 \[
@@
     where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-    Recall that the operator $\mathcal{I}^t_s$ is defined in \ref{Ist}.
+    Recall that the operator $\mathcal{I}^t_s$ is defined in \eqref{Ist}.
 
@@
 \begin{lem}\label{lem: temp}
-    For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists a constant $C > 0$ such that
+    For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists $C > 0$ such that
        for all $\kappa \in \mathbb Z_+ $, $\lambda > 0$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
@@
     \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
-    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
+%    \\&
+    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
     \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
@@
 \end{align}
-    where the constant $C>0$ above is chosen as
+    where the $C>0$ above is chosen as
 \[
@@
 \label{lem: control of mgtrs}
-    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
+    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists $C > 0$ such that for all $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
 \[
@@
     For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write
-\[
+%\[
+$
     \|Y\|_{\mathbb P;p}:= \mathbb P[|Y|^p]^{1/p}.
-\]
+%\]
+$
 \begin{lem}
@@
     &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-        \\ &\leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
+%        \\ &
+        \leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
     + |\langle P^\alpha_t g,\mu\rangle|
@@
 \label{martingale1}
-    &\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
-    \\&=e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
+    &\quad\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
+%    \\&
+    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
     \\&=e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du
-    \\&\quad -\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
+%    \\&\quad 
+    -\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
 \end{align}
@@
 
-    Recall that, for $p=(p_1,...,p_d)\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
+    Recall that, for $p=(p_1,...,p_d)\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$. Define
 \[
@@
 Moreover, if $\alpha\beta>|p|b(1+\beta)$, then, for all $\gamma\in (0, \beta)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
-\[
+%\[
+$
     H_{\infty}^p
     :=\lim_{t\rightarrow \infty}H_t^p
-\]
+%\]
+$
     exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
@@
     There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, we have $\alpha\gamma>|p|(1+\gamma)b$.
-    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that, for $\gamma\in [\gamma_0, \beta)$, there exists a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$) such that
+    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that, for $\gamma\in [\gamma_0, \beta)$, there exists $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$) such that
 \[
@@
     Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-    It follows from Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$ that there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
+    By Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$, there exists $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
 \begin{align}
@@
 	\\& \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
-	\\&\leq C_2e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
+%	\\&
+	\leq C_2e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
     \qedhere
@@
 	We will show that for each $\gamma \in (0,\beta)$ there exist
-	constants $C_1,\delta_1 > 0$ such that
+ $C_1,\delta_1 > 0$ such that
 \[
@@
 	For $a \geq 0$, $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
-\begin{equation}
-	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds
-\end{equation}
-    and
-\begin{equation}
+%\begin{equation}
+\begin{align*}
+	L_t^{g,a}&:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,\\
+%\end{equation}
+%    and
+%\begin{equation}
     Y_t^{g,a}
-    :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
-\end{equation}
+    &:=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
+%\end{equation}
+\end{align*}
 	Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$.
-	According to \eqref{defmartingale}, we have
+	According to \eqref{defmartingale}, 
 \begin{align}
@@
     \leq\|Y_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\widetilde{f}+a_0 b\widetilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
+    \\&
+    \leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\widetilde{f}+a_0 b\widetilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
 \end{align}
@@
     where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
-\[
-    \mathbf{E}(e^{i\theta\zeta_k})
-    =\exp(m_k[\theta f]),\quad \theta \in \mathbb R.
-\]
+%\[
+%    \mathbf{E}(e^{i\theta\zeta_k})
+%    =\exp(m_k[\theta f]),\quad \theta \in \mathbb R.
+%\]
+$\theta\mapsto \exp(m_k[\theta f])$.
 \end{lem}
@@
     From Proposition \ref{prop: alpha stable rv}.(1), we have
-\begin{equation}
-\label{eq: need2}
-    \operatorname {Re} m_t[f] < 0.
-\end{equation}
-  Using \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
-\[
-    |e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
-\]
+%\begin{equation}
+%\label{eq: need2}
+%    \operatorname {Re} m_t[f] < 0.
+%\end{equation}
+$\operatorname {Re} m_t[f] < 0$. 
+%  Using \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
+Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact
+%\[
+%    |e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
+%\]
+$|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$,
     we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
@@
     &\big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c\big]\big|
-    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+%    \\& 
+    \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
     \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; A_{t-k-1}(\epsilon)| \mathscr F_{t-k-1}]\big| + 2\mathbb P_\mu(A_{t-k-1}(\epsilon) \Delta D^c| \mathscr F_{t-k-1})\Big]
@@
 
-Step 2. We will show that for each $\epsilon>0$ small enough, there exist constants $C_1, \delta_1>0$ such that
+Step 2. We will show that for $\epsilon>0$ small enough, there exist  $C_1, \delta_1>0$ such that
 \begin{equation}
@@
     \leq R(|\theta_{t,k}P^\alpha_k f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
-    \\&\leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
+%    \\&
+    \leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
     \\&\leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf
     \\&\leq\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
-    \\&\leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
-\end{align}
-    where $Q$ is defined by \eqref{Q}.
+%    \\&
+    \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
+\end{align}
+%    where $Q$ is defined by \eqref{Q}.
+    where $Q$ is defined by \eqref{Q_k}.
     Thus for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
@@
 \end{align}
-    where $Q$ is defined by \eqref{Q}.
+%    where $Q$ is defined by \eqref{Q}.
+    where $Q$ is defined by \eqref{Q_k}.
     By taking $\epsilon>0$ small enough, we get the desired result in this step.
@@
     Step 3.
-    We will show that for $\epsilon>0$ small enough, there exist constants $C_2, \delta_2>0$ such that
-\begin{equation}
-\label{eq:31step3}
+    We will show that for $\epsilon>0$ small enough there exist $C_2, \delta_2>0$ such that
+%\begin{equation}\label{eq:31step3}
+$
     J_2(t,k,\epsilon)
@@
     \quad k\geq 0, t\geq k+1.
-\end{equation}
+%\end{equation}
+$
 
@@
        &=e^{-\alpha(k+1)} \cdot \eta \int_0^{1}e^{\alpha(1- s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha        g(x))^{1+\beta} \varphi(x)~dx\\
-      &=e^{-\alpha(k+1)}\langle \eta \int_0^1P_{1-s}^{\alpha}(-iP_{s+k}^\alpha g(x))^{1+\beta}~ds, \varphi \rangle\\
-      &=e^{-\alpha(k+1)}\langle Z_1(P_k^{\alpha}g), \varphi \rangle.
+      &=e^{-\alpha(k+1)}\langle \eta \int_0^1P_{1-s}^{\alpha}(-iP_{s+k}^\alpha g(x))^{1+\beta}~ds, \varphi \rangle
+%      \\&
+      =e^{-\alpha(k+1)}\langle Z_1(P_k^{\alpha}g), \varphi \rangle.
 \end{align}
@@
 \begin{align}
-    &\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]
-    \\&= \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha (k+1)}\langle  Z_1P^\alpha_k f,\varphi\rangle
+    \langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]
+%    \\&
+    &= \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha (k+1)}\langle  Z_1P^\alpha_k f,\varphi\rangle
     \\&=e^{-\alpha (k+1)}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big),
@@
 \label{eq: right bound for J2}
-    J_2(t,k, \epsilon)&
+   & J_2(t,k, \epsilon)
     \leq  e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
@@
     \\&= C_3 e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
-    \\&\leq C_3 e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
+%    \\&
+    \leq C_3 e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
 \end{align}
@@
     We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_3>0$ such that for all $k\geq0, t\geq k+1$,
-\begin{equation}\label{ineq: control of J3}
+%\begin{equation}\label{ineq: control of J3}
+$
     J_3(t,k,\epsilon)\leq C_4e^{-\delta_3 (t-k)}.
-\end{equation}
+%\end{equation}
+$
     In fact, we have  for all $t\geq 0, \epsilon >0$,
-\begin{align}
-    &\mathbb P_{\mu}(A_{t}(\epsilon), D) = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
-    \\&= \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
+%\begin{align}
+%    &
+\[   
+\mathbb P_{\mu}(A_{t}(\epsilon), D) = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
+%    \\&
+    = \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
     \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
-\end{align}
-    According to Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_5, \delta_4>0$ such that for all $t\geq 0$,
+%\end{align}
+\]
+    By Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_5, \delta_4>0$ such that for all $t\geq 0$,
 \begin{equation}
@@
 
-    Finally, combining the results in Steps 1--4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$, we immediately get the desired result.
+    Finally, combining the results in Steps 1--4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3,$ converge to $0$ exponentially fast as $t\rightarrow\infty$, we immediately get the desired result.
 \end{proof}
@@
 \begin{cor}\label{cor: used in next corollary}
-   Suppose that $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq \kappa_fb(1+\beta)$.
-    Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
+   Suppose $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq \kappa_fb(1+\beta)$.
+    Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C, \delta>0$ such that for $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
 \begin{equation}
@@
     &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-    \\&\leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
+%    \\&
+    \leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
 \end{align}
@@
 	Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$,
-\[
+%\[
+$
     J^{\pm \theta f}_2(t,k,\epsilon)
-	:= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon).
-\]
+	= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon).
+	$
+%\]
 	According to this and \eqref{eq: right bound for J2},
-	we have that there exists a constant $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+	we have that there exists $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{equation}
@@
    Suppose that $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq\kappa_fb(1+\beta)$.
-    Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$satisfying $|\theta_i|\leq \Theta$, we have
+    Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for all $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$satisfying $|\theta_i|\leq \Theta$, we have
 \begin{equation}
@@
     &a_{k-1} - a_k
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
+%    \\&
+    =\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
     \\&=\mathbb{P}_{\mu}(D^c)^{-1} \Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
 \end{align}
-    According to Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
+    By Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
 \begin{align}
@@
     &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
-    \\& \leq C e^{-\delta(t-k)}.
+%    \\& 
+    \leq C e^{-\delta(t-k)}.
 \end{align}
@@
     We now present the proof of Theorem \ref{thm: critical clt}.
-\bigskip
+\medskip
 
@@
     &\mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
-    \\&\leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}),
+%    \\&
+    \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
     \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]
-    \\&\quad +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
+    \\&\quad 
+    +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
     \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}
@@
 
-    Step 2. We will show that there exist constant $C_4,\delta_4 > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
+    Step 2. We will show that there exist $C_4,\delta_4 > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
 \begin{equation}
@@
 \end{equation}
-    According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and \eqref{ineq: control of Kkt},
-    there exist constant $C_6>0$ such that for all $k\geq 0$ and $t\geq k+1$,
+    By Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and \eqref{ineq: control of Kkt},
+    there exist $C_6>0$ such that for all $k\geq 0$ and $t\geq k+1$,
 \begin{align}
@@
     = C_8 e^{-\delta_6 t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta_6 k}
-    \\&\leq C_9 e^{-\delta_6 t}e^{\delta_6 (t-\ln t)}
+%    \\&
+    \leq C_9 e^{-\delta_6 t}e^{\delta_6 (t-\ln t)}
     = \frac{C_9}{t^{\delta_6}}.
@@
 	\\& = t^{-\frac{1}{1+\beta}} e^{\frac{\beta \alpha t}{1+\beta} - k_fbt} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
-	\\& = t^{-\frac{1}{1+\beta}} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
+%	\\& 
+	= t^{-\frac{1}{1+\beta}} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
 	\xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
@@
 	Let $t_0 > 1$ be large enough so that
-\[
-	\lceil t - \ln t\rceil
+%\[
+$	\lceil t - \ln t\rceil
 	\leq \lfloor t \rfloor - 1,
-	\quad t\geq t_0.
-\]
+%	\quad t\geq t_0.
+$ for all $t\geq t_0$.
+%\]
 Fix $\mu\in \mathcal M_c(\mathbb R^d)$ and write
@@
     & \leq C_3( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)})
-    \\& \leq C_4e^{-\delta_3 (t-k)}.
+%    \\& 
+    \leq C_4e^{-\delta_3 (t-k)}.
 \end{align}
@@
 	Recall that
-\[
-	A_t(\epsilon)
-    :=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
-	\quad t\geq 0.
-\]
-	According to \eqref{lem: control of XT}, there exist
+%\[
+%	A_t(\epsilon)
+%    :=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
+%	\quad t\geq 0.
+%\]
+$A_t(\epsilon)=\{\|X_t\|>e^{(\alpha-\epsilon )t}\}$.
+By \eqref{lem: control of XT}, there exist
 $C_5,\delta_4>0$ such that
@@
 	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
-	\\& = e^{(\frac{\beta \alpha }{1+\beta} - k_fb)t} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
+%	\\& 
+	= e^{(\frac{\beta \alpha }{1+\beta} - k_fb)t} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
 	\xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
@@
 \begin{align}\label{equ: transform of mn}
-    &\bar{m}_n[g]=e^{\alpha(n-1)}\int_0^1 e^{\alpha s}\langle \eta(iI_{s+n-1}g)^{1+\beta}, \varphi\rangle ds\\
-    &=e^{\alpha(n-1)}\langle \int_0^1 P_s^{\alpha}\langle \eta(iI_{s+n-1}g)^{1+\beta}ds, \varphi\rangle\\
+    &\bar{m}_n[g]=e^{\alpha(n-1)}\int_0^1 e^{\alpha s}\langle \eta(iI_{s+n-1}g)^{1+\beta}, \varphi\rangle ds
+    \\    &
+    =e^{\alpha(n-1)}\langle \int_0^1 P_s^{\alpha}\langle \eta(iI_{s+n-1}g)^{1+\beta}ds, \varphi\rangle\\
     &=e^{\alpha(n-1)}\langle \int_0^1 P_{1-s}^{\alpha}\langle \eta(iI_{n-s}g)^{1+\beta}ds, \varphi\rangle=e^{\alpha(n-1)}\langle Z_1(-I_ng),
@@
     characteristic function
-\begin{align}
-    \mathbf{E}[e^{i\theta \bar{\zeta}_n}]=\exp(\bar{m}_n[\theta g]),\quad \theta\in \mathbb{R}.
-\end{align}
+%\begin{align}
+%    \mathbf{E}[e^{i\theta \bar{\zeta}_n}]=\exp(\bar{m}_n[\theta g]),\quad \theta\in \mathbb{R}.
+%\end{align}
+$\theta\mapsto \exp(\bar{m}_n[\theta g])$.
 \end{lem}
@@
     According to \eqref{eq: need11} and the fact that
-\[
-	|e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
-\]
+%\[
+%	|e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
+%\]
+$|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$,
     we have for all $n\geq 1, t\geq 0$ and $\epsilon> 0$,
@@
     &\big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
-    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]
+%    \\& 
+    \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]
     \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; A_{t+n-1}(\epsilon)| \mathscr F_{t+n-1}]\big| + 2\mathbb P_\mu(A_{t+n-1}(\epsilon) \Delta D^c| \mathscr F_{t+n-1})\Big]
@@
     Step 2.
-    We will show that for $\epsilon>0$ small enough, there exist constants $C_1,\delta_1>0$ such that for all $n\geq 1$ and $t\geq 0$,
-\begin{align}\label{eq:large rate J1}
+    We will show that for $\epsilon>0$ small enough, there exist $C_1,\delta_1>0$ such that for all $n\geq 1$ and $t\geq 0$,
+%\begin{align}\label{eq:large rate J1}
+$
     J'_1(t,n,\epsilon)\leq C_1 e^{-\delta_1(t+n)}.
-\end{align}
+    $
+%\end{align}
     Let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
@@
     where $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-    Thus, there exists constant $C_3>0$ such that for all $n\geq 1,  t\geq 0$ and $\epsilon > 0$,
+    Thus there exists $C_3>0$ such that for $n\geq 1,  t\geq 0$ and $\epsilon > 0$,
 \begin{align}
@@
     We will show that for each $\epsilon > 0$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$,
-\begin{align}
-\label{eq:31step31}
+%\begin{align}
+%\label{eq:31step31}
+$
     J'_2(t,n,\epsilon)
     \leq C_2 e^{-\delta_2(t+n)}.
-\end{align}
+%\end{align}
+$
     In fact, according to the definitions of $Z_1$ and $\bar{m}_n$, and \eqref{equ: transform of mn}, we have for all $t\geq 0, n\geq1$,
 \begin{align}
-    &\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\\
-    &=e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
+    &\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]
+%    \\&
+    =e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
 \end{align}
@@
     &\leq C_3 e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)}\\
-    &=C_3e^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}\\&\leq C_3e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}.
+    &=C_3e^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}
+%    \\&
+    \leq C_3e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}.
 \end{align}
@@
     Step 4. According to the Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that
-\begin{align}\label{ineq: control of J31}
-    J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}\quad t\geq0, n\geq 1.
-\end{align}
+%\begin{align}\label{ineq: control of J31}
+ %   J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}\quad t\geq0, n\geq 1.
+%\end{align}
+$J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}$ for all $ t\geq0, n\geq 1$.
 
@@
 \begin{lem}\label{lem: independency for large rate}
-    For all $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
+    For all $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
 \begin{align}\label{ineq: next we will need}
@@
     &\widetilde{a}_{n-1} - \widetilde{a}_n
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times (e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}});D^c\Big] \times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
+%    \\&
+    =\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times (e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}});D^c\Big] \times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
     \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times \mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
@@
     &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
-    \\& \leq C_2 e^{-\delta_1(t+n-1)}.
+%    \\& 
+    \leq C_2 e^{-\delta_1(t+n-1)}.
 \end{align}
@@
 \begin{lem}\label{lem: lemma04}
-    For all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
+    For all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
 \begin{align}
@@
     where
-\begin{align}
-    Y''_{t,n}
-    :=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},
-    \quad t\geq 0, n\geq 1.
-\end{align}
+%\begin{align}
+ %   Y''_{t,n}
+%    :=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},  \quad t\geq 0, n\geq 1.
+%\end{align}
+$Y''_{t,n}:=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}}$.
     Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
@@
     \frac{\alpha \gamma}{1+\gamma}
-    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0
-\]
-    and
-\[
+    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0,
+%\]
+%    and
+%\[
+\qquad
     \alpha\gamma
@@
     Step 1. Similar to Step 1 in the proof of Theorem \ref{thm: critical clt}, we can show that there exist $C_1,\delta_1 >0$ such that for all $n \geq 1$ and $t\geq 0$,
-\begin{align}
-\label{thm12111}
+%\begin{align}
+%\label{thm12111}
+$
     \mathbb{\widetilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}^c_{t,n}}\big]
     \leq C_1 e^{-\delta_1 t}.
-\end{align}
+%\end{align}
+$
 
@@
 \end{align}
-    According to Lemma \ref{lem: control of wt}, there exists a constant $C_4>0$ such that for all $t\geq 0$ and $n\geq 1$,
+    According to Lemma \ref{lem: control of wt}, there exists $C_4>0$ such that for all $t\geq 0$ and $n\geq 1$,
 \begin{align}\label{ineq:used next 2}
@@
 \begin{lem}\label{lem: lemma05}
-    For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta_1,\delta_2>0$ such that
+    For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist  $C,\delta_1,\delta_2>0$ such that
 \begin{align}
@@
     Now we are ready to prove Theorem \ref{thm: large clt}.
-\bigskip
+\medskip
 
@@
     Then the functions
-\begin{equation}
+%\begin{equation}
+\begin{align*}
+&
     h (z) = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+
-\end{equation}
-    and
-\begin{equation}
-\label{eq: deriavetive of the Poission partb}
+%\end{equation}
+%    and
+%\begin{equation}
+%\label{eq: deriavetive of the Poission partb}
+\\&
     h'(z) = \int_{(0,\infty)}(1- e^{-zy})y \pi(dy), \quad z \in \mathbb C_+
-\end{equation}
+%\end{equation}
+\end{align*}
     are well defined, continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
@@
 
-    Recall that the Gamma function  $\Gamma$ is defined by
-\begin{equation}
-    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
-    \quad x>0.
-\end{equation}
+%    Recall that the Gamma function  $\Gamma$ is defined by
+%\begin{equation}
+%    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
+%    \quad x>0.
+%\end{equation}
 	It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
@@
 \end{equation}
-	by showing that the both sides
-\begin{itemize}
-\item
-    are extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
-\item
-    are holomorphic on $\mathbb C_+^0$;
-\item
-    are continuous on $\mathbb C_+$.
-\end{itemize}
+%	by showing that the both sides
+%\begin{itemize}
+%\item
+ %   are extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
+%\item
+%    are holomorphic on $\mathbb C_+^0$;
+%\item
+ %   are continuous on $\mathbb C_+$.
+%\end{itemize}
+are (i)  extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
+(ii) holomorphic on $\mathbb C_+^0$ and (iii) continuous on $\mathbb C_+$.
     Similarly, we get that
@@
     there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
-\begin{itemize}
-\item
-    $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
-\item
-    $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
-\item
-    for any $\mu \in \mathcal M(E)$, 
-    if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
-    then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
-\end{itemize}
+%\begin{itemize}
+%\item
+%    $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
+%\item
+%    $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
+%\item
+%    for any $\mu \in \mathcal M(E)$, 
+%    if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
+%    then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
+%\end{itemize}
+(i) $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$; (ii) $\mathbb N_x(\|W_0 \|\neq 0) = 0$
+and (iii) if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
+%    then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
     We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
@@
     where $C_1, C_2$ are constants independent on $f,x$ and $t$.
-    Now, combining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we get the desired result.
+    Now, 
+    %combining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, 
+    combining the display above with \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bounded for derivative of v(theta)}
+    we get the desired result.
 \end{proof}
@@
     &\Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
-    \\&\leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big]
+ %   \\&
+    \leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big]
     \\ &\leq \int_0^t \big(C_1 e^{t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
@@
     U_tf(x) - \Pi_x \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f\big) ds \Big]
-    \\= i \Pi_x [f(\xi_t)]
-\end{equation}
-    and
+    \\= i \Pi_x [f(\xi_t)].
+\end{equation}
+%    and
 \begin{equation}
@@
     \{(X_s)_{s \geq 0};\mathbf P_{\delta_x}^{\langle X_T, f\rangle}\}
-    \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{\langle W_T, f\rangle} \}
-\end{equation}
-    and
+    \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{\langle W_T, f\rangle} \},
+\end{equation}
+%    and
 \begin{equation}
@@
 \label{eq: N to Pi}
-    \mathbb N_x^{\langle W_{t}, g\rangle}[e^{i \langle W_t, f\rangle}]
-    &=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
+    &\mathbb N_x^{\langle W_{t}, g\rangle}[e^{i \langle W_t, f\rangle}]
+    =\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
     \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
-    \\&= \frac{1}{P_t^{\rho_1} g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
+%    \\&
+    = \frac{1}{P_t^{\rho_1} g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
 \end{align}
@@
 
-    From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
+%    From \eqref{eq: upper bound of psi'(v)},
+From the display below \eqref{eq: path integration representation of psi(v)},
+     we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
     Therefore, we can apply Lemma \ref{eq: complex FK} and get that
@@
 \end{align}
-    Integrating the two displays above with respect to $\theta$  on [0,1], using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get
+    Integrating the two displays above with respect to $\theta$  on [0,1], using 
+    %\eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get
+Fubini's theorem,   \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and the display below it, we get
 \begin{equation}
@@
 \end{equation}
-    Notice the following:
-\begin{itemize}
-\item
-    It is clear that $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$.
-\item
-    $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$ due to \eqref{eq: N and characteristic exponent}, the dominated convergence theorem and the fact that
+%    Notice the following:
+Note that 
+%\begin{itemize}
+%\item
+%    It is clear that $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$.
+%\item
+%    $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$ due to \eqref{eq: N and characteristic exponent}, the dominated convergence theorem and the fact that
+%\[
+%    |e^{i W_t(f_n)} - 1| \leq \langle W_t, |f|\rangle;
+ %   \quad \mathbb N_x[\langle W_t, |f|\rangle] = (P_t^{\rho_1} |f|)(x) < \infty.
+%\]
+%\item
+ %   $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
+%\begin{equation}
+%    \big|\psi(\xi_s,- U_{t-s}f_n)\big|
+%    \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2.
+%\end{equation}
+%\end{itemize}
+%    Using the above arguments, 
+(i) $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$;
+(ii) by \eqref{eq: N and characteristic exponent}, the dominated convergence theorem and the fact that
 \[
  |e^{i W_t(f_n)} - 1| \leq \langle W_t, |f|\rangle;
-    \quad \mathbb N_x[\langle W_t, |f|\rangle] = (P_t^{\rho_1} |f|)(x) < \infty.
-\]
-\item
-    $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
-\begin{equation}
-    \big|\psi(\xi_s,- U_{t-s}f_n)\big|
-    \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2.
-\end{equation}
-\end{itemize}
-    Using the above arguments, letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
+  \quad \mathbb N_x[\langle W_t, |f|\rangle] = (P_t^{\rho_1} |f|)(x) < \infty,
+\]
+we have $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$, and (iii) by the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
+\[
+big|\psi(\xi_s,- U_{t-s}f_n)\big|
+   \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2,
+\]
+we get that $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$.
+Using these, 
+    letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
 \end{proof}
 
-\bigskip
+\medskip
 \noindent
@@
 	We thank Zenghu Li and Rui Zhang for helpful conversations.
-\bigskip
+	%new
+	We also thank the referee for very helpful comments.
+	%end new
+\medskip
 

### 2019-08-02 supCLT.tex
change supCLT.tex

@@
-%---The preamble----------------------
+% * The preamble
 \documentclass[12pt,a4paper]{amsart}
@@
 \usepackage{mathrsfs}
-%\usepackage[backref=section]{hyperref}
 \usepackage{hyperref}
 \usepackage{comment}
-%\usepackage[nobysame]{amsrefs}
 \usepackage{amsthm}
@@
 \allowdisplaybreaks
-%---Top matter------------------------------
+% * Top matter
 \begin{document}
@@
 {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
-\address
-    {Yan-Xia Ren
-    \\ LMAM School of Mathematical Sciences \& Center for Statistical Science
-    \\ Peking University
-    \\ Beijing, P. R. China, 100871}
+\address{
+  Yan-Xia Ren \\
+  LMAM School of Mathematical Sciences \& Center for Statistical Science \\
+  Peking University \\
+  Beijing, P. R. China, 100871}
 \email{yxren@math.pku.edu.cn}
 \thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}
-\address
-    {Renming Song
-    \\ Department of Mathematics
-    \\ University of Illinois at Urbana-Champaign
-    \\ Urbana, IL 61801, USA}
+\address{
+  Renming Song \\
+  Department of Mathematics \\ 
+  University of Illinois at Urbana-Champaign \\ 
+  Urbana, IL 61801, USA}
 \email{rsong@illinois.edu}
 \thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
-\address
-    {Zhenyao Sun
-    \\ School of Mathematical Sciences
-    \\ Peking University
-    \\ Beijing, P. R. China, 100871}
+\address{
+  Zhenyao Sun \\ 
+  School of Mathematical Sciences \\ 
+  Peking University \\ 
+  Beijing, P. R. China, 100871}
 \email{zhenyao.sun@pku.edu.cn}
-\address
-    {Jianjie Zhao
-    \\ School of Mathematical Sciences
-    \\ Peking University
-    \\ Beijing, P. R. China, 100871}
+\address{
+  Jianjie Zhao \\ 
+  School of Mathematical Sciences \\ 
+  Peking University \\ 
+  Beijing, P. R. China, 100871}
 \email{zhaojianjie@pku.edu.cn}
@@
   Let $\psi$ be a branching mechanism which is close to a function of the form $\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-In this paper, we study asymptotic behaviors of
-$(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$.
+  In this paper, we study asymptotic behaviors of $(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$. 
   For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$. 
-Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
+  Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes: 
+  the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; 
+  the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; 
+  and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
 \end{abstract}
@@
 \maketitle
-%---Contents-----------------------
+% * Contents
 \section{Introduction}
+% ** Motivation
 \subsection{Motivation}
@@
 Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
-\begin{equation}
+\begin{align}
   Lf(x)
-    = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
-    \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
-\end{equation}
+  = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x)
+  , \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
+\end{align}
 where $\sigma > 0$ and $b > 0$ are constants.
@@
 Let $\psi$ be a function on $\mathbb R_+$ of the form 
-\begin{equation} \label{eq: honogeneou branching mechanism}
+\begin{align} 
+  \label{eq: honogeneou branching mechanism}
   \psi(z)=
-    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
-    \quad  z \in \mathbb R_+,
-\end{equation}
+  - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy)
+  , \quad  z \in \mathbb R_+,
+\end{align}
 where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty$.
 %	We refer to $\pi$ as the \emph{L\'evy measure} of the branching mechanism $\psi$.
-$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure
-of $\psi$.
+$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
 Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
@@
 $
-       We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
-on a measurable space $(\Omega, \mathcal{F})$
-       is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, 
-     or a $(\xi, \psi)$ superprocess,  
-       if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
-\begin{equation}
+We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ on a measurable space $(\Omega, \mathcal{F})$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$ superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+\begin{align}
   \label{eq: def of V_t}
   \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
-    = e^{-\langle V_tf, \mu \rangle},
-    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
-\end{equation}
+  = e^{-\langle V_tf, \mu \rangle}
+  , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
+\end{align}
 where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
-\begin{equation}
+\begin{align}
   V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(V_{t-s}f(\xi_s)\big)~ds\Big]
-	= \Pi_x [f(\xi_t)],
-    \quad x\in \mathbb R^d, t\geq 0.
-\end{equation}	
+	= \Pi_x [f(\xi_t)]
+  , \quad x\in \mathbb R^d, t\geq 0.
+\end{align}	
 The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
@@
 In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established. 
-The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost},
-    followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost} under different settings.
+The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
 For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.
@@
 The strong law of large numbers for the super-OU process $X$ can be stated as follows:
-    Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$,
-    for every Lebesgue-a.\/e. continuous bounded non-negative function $f$ on $\mathbb R^d$,
-    we have
-    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f, \varphi\rangle $,
-    where $H_\infty$ is the limit of the martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and
-$\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
+Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e.
+continuous bounded non-negative function $f$ on $\mathbb R^d$, we have $\lim_{t\to\infty} e^{-\alpha t} \langle f, X_t\rangle =H_\infty\langle f, \varphi\rangle $, where $H_\infty$ is the limit of the martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
 See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
@@
 Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-    We want to find
-    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
+We want to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
 %\[
@@
 (\langle f, X_t \rangle -G_t)/F_t
-%\]
+% \]
 $
 converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
-    It turns out that the statements of the CLT's are different in three regimes
-    depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
+It turns out that the statements of the CLT's are different in three regimes depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: 
+the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; 
+the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; 
+and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. 
 Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
@@
 \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-%In \cite{AdamczakMilos2015CLT}, Adamczak and Mi\l{}o\'s proved some spatial central limit theorems for   supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Mi\l{}o\'s proved some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+% In \cite{AdamczakMilos2015CLT}, Adamczak and Mi\l{}o\'s proved some spatial central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Mi\l{}o\'s proved some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
 Some spatial central limit theorems for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
 These two papers made connections between the CLT and  the branching rate regimes.
-%In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition.
+% In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition.
 Some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition were established in \cite{RenSongZhang2014Central}.
 Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
-%In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}, Ren, Song and Zhang also established a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
-Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms
-were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
+% In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}, Ren, Song and Zhang also established a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
+Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
 The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
@@
 Heyde \cite{Heyde1971Some} established a central limit type  theorem 
-%for supercritical Galton-Watson process when the offspring distribution
+% for supercritical Galton-Watson process when the offspring distribution
 for supercritical GW processes when the offspring distribution
-belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
-and   proved that the limit law is  a stable law. Similar results  for supercritical multi-type 
-%Galton-Watson processes and supercritical  continuous time branching processes, 
+belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit law is  a stable law. 
+Similar results  for supercritical multi-type 
+% Galton-Watson processes and supercritical  continuous time branching processes, 
 GW processes and supercritical  continuous time branching processes, 
-under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
-were given in Asmussen \cite{Asmussen76Convergence}.
+under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
 Recently, Marks and Milo\'s \cite{MarksMilos2018CLT}
-%considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes 
+% considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes 
 considered the limit behavior of supercritical branching OU processes
 with a special stable branching law.
-	They established some spatial central limit theorems in the small and critical branching rate regimes,
-    but they did not prove any central limit theorem type result in the large branching rate regime.
+They established some spatial central limit theorems in the small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
 We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.
 
-    As far as we know, this paper is the
-   first to study spatial central limit theorems
-    for supercritical superprocesses without the second moment condition.
-
+As far as we know, this paper is the first to study spatial central limit theorems for supercritical superprocesses without the second moment condition.
+
+% ** Main results
 \subsection{Main results}
 \label{sec: main results}{}
-
 We will always assume that the following assumption holds.
@@
 For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
-	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition},
-	the \emph{extinction event}
-	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
+It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event} $D :=\{\exists t\geq 0,~\text{s.t.}~ \|X_t\| =0 \}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
 In fact,
@@
 % \quad \mu\in \mathcal M(\mathbb R^d),
-%\end{equation}
-$ for $\mu\in \mathcal M(\mathbb R^d)$,
+% \end{equation}
+$ 
+for $\mu\in \mathcal M(\mathbb R^d)$,
 where
-%\[
+% \[
 $
 \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
-%\]
+% \]
 $
@@
   There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
-\begin{equation}
+  \begin{align}
     \label{eq: asp of branching mechanism}
     \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
-\end{equation}
+  \end{align}
 	for some $\delta > 0$.
@@
 
-    Assumption \ref{asp: branching mechanism} says that
- there exist constants $\eta>0$ and $\beta > 0$
-    such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
-    In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$
-    takes the form of
-	$-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
-	It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption
-	\ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the
-	$L \log L$ condition, i.e.,
+Assumption \ref{asp: branching mechanism} says that there exist constants $\eta>0$ and $\beta > 0$ such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
+In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of $-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
+It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ condition, i.e.,
 %\[
@@
 \int_{(1,\infty)} y\log y~\pi(dy) < \infty.
-%\]
+% \]
 $
@@
 Define
-\begin{equation}
+\begin{align}
   \label{eq: meansemigroup}
@@
   :=
-    e^{\alpha t} P_t f(x) =
-    \Pi_x [e^{\alpha t}f(\xi_t)],
-    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
-\end{equation}
+  e^{\alpha t} P_t f(x) 
+  = \Pi_x [e^{\alpha t}f(\xi_t)]
+  , \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
+\end{align}
 It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
@@
 It is known that the OU process $\xi$ has an invariant density
-\begin{equation}
+\begin{align}
 \label{invariantdensity}
@@
   \quad x\in \mathbb R^d.
-\end{equation}
+\end{align}
 Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$.
 Then $L^2(\varphi)$ is a Hilbert space with inner product
-\begin{equation}
+\begin{align}
   \langle f_1, f_2 \rangle_{\varphi}
   := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
-\end{equation}
+\end{align}
 Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-    For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$,
-    $p!:= \prod_{k= 1}^d p_k!$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
 The \emph{Hermite polynomials} are defined by
-\begin{equation}
+\begin{align}
   H_p(x)
-    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
-    \quad x\in \mathbb R^d,
-    p \in \mathbb{Z}_+^{d}.
-\end{equation}
-It is known that $(P_t)_{t\geq 0}$
-       is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum
-        $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
+  :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) 
+  , \quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
+\end{align}
+It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
 For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
@@
 where
-\begin{equation}\label{eigenfunction}
+\begin{align}
+  \label{eigenfunction}
   \phi_p(x)
-        := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
-    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
-\end{equation}
+  := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big)
+  , \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
+\end{align}
 In other words,
@@
 Thus for each $f\in L^2(\varphi)$, we have
-\begin{equation}\label{semicomp1}
+\begin{equation}
+\label{semicomp1}
 f
-         =\sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
-    \quad \text{in~} L^2(\varphi).
+=\sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
+, \quad \text{in~} L^2(\varphi).
 \end{equation}
@@
 the order of the function $f$ in the spectral decomposition \eqref{semicomp1}.
-%new
+% new
 $\kappa_f$ corresponds to the lowest non-trivial frequency in the eigen-expansion of $f$.
-%end new    
+% end new    
 Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
@@
 It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-    In this paper, we are mainly interested in the asymptotic behavior of $\langle f, X_t\rangle$
-    for non-trivial $f\in \mathcal P$.
+In this paper, we are mainly interested in the asymptotic behavior of $\langle f, X_t\rangle$ for non-trivial $f\in \mathcal P$.
 The asymptotic behavior varies with the following three regimes:
 % \begin{itemize}
-%\item
+% \item
 %   The large branching rate regime: $\alpha\beta>\kappa_fb(1+\beta)$;
-%\item
+% \item
 %   The critical branching rate regime: $\alpha\beta=\kappa_fb(1+\beta)$;
-%\item
+% \item
 %   The small branching rate regime: $\alpha\beta<\kappa_fb(1+\beta)$.
-%\end{itemize}
-(1) the small branching rate regime where $\alpha\beta<\kappa_fb(1+\beta)$; (2) the 
-critical branching rate regime where $\alpha\beta=\kappa_fb(1+\beta)$; and
+% \end{itemize}
+(1) the small branching rate regime where $\alpha\beta<\kappa_fb(1+\beta)$; 
+(2) the critical branching rate regime where $\alpha\beta=\kappa_fb(1+\beta)$; and
 (3) the large branching rate regime where $\alpha\beta>\kappa_fb(1+\beta)$.
 
+% *** Large branching rate regime
 \subsubsection{Large branching rate regime}
@@
 \]
-    If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
-      we will prove in Lemma \ref{lemma26} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lemma26} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
@@
   \label{thm: law of large number}
-     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then
-   for all
-     $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
+  If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
   \[
@@
   If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
-    Hence, Theorem \ref{thm: law of large number} says that
-    for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
+  Hence, Theorem \ref{thm: law of large number} says that for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
   \[
@@
 \begin{rem}
-    For general $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which
-the first order asymptotic ($\kappa_f=0$) was identified.
+  For general $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
 \end{rem}
 
-   The fluctuation result associated to the law of large numbers in this case is
-    given in Theorem \ref{thm: large clt} below.
+The fluctuation result associated to the law of large numbers in this case is given in Theorem \ref{thm: large clt} below.
 Define
-\begin{equation}
+\begin{align}
   \label{eq: def of N}
-    \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\},
+  \mathcal{N}
+  :=\{p\in \mathbb{Z}_+^d: \alpha\beta>|p|(1+\beta)b\},
   \quad K : = \sup\{|p|: p \in \mathcal N\}
-\end{equation}
+\end{align}
 and
@@
   \label{eq: def of Cl}
-    \mathcal{C}_l:=\Big\{f\in \mathcal P: f(x)=\sum_{p\in\mathcal{N}}\langle f, \phi_p\rangle_{\varphi}\phi_p(x)\Big\}.
+  \mathcal{C}_l
+  :=\Big\{f\in \mathcal P: f(x)=\sum_{p\in\mathcal{N}}\langle f, \phi_p\rangle_{\varphi}\phi_p(x)\Big\}.
 \end{equation}
 For each $t\ge 0$, we define an operator $I_t$ on $\mathcal{C}_l$ by
-\begin{align}\label{definition of Itf}
-    I_tf(x)
-    :=\sum_{p\in \mathcal{N}}\langle f, \phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x),
-   \quad x\in \mathbb{R}^d, f\in \mathcal C_l.
+\begin{align}
+  \label{definition of Itf}
+  I_t f(x)
+  := \sum_{p\in \mathcal{N}}\langle f, \phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x)
+  , \quad x\in \mathbb{R}^d, f\in \mathcal C_l.
 \end{align}
@@
 Define
-\begin{align}\label{bar-m}
+\begin{align}
+  \label{bar-m}
   \bar{m}[f]
@@
 \end{align}
-    We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; and in Lemma \ref{prop: alpha stable rv} that, 
-    when $f\in \mathcal C_l$ is non-trivial,
-    $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic
-    function of a $(1+\beta)$-stable random variable.
+We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; 
+and in Lemma \ref{prop: alpha stable rv} that, when $f\in \mathcal C_l$ is non-trivial, $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
 \begin{thm}
@@
   For non-trivial $f\in\mathcal{C}_l$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that,
-\begin{align}\label{thm: large rate}
-    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow[t\to \infty]{d}\bar{\zeta},
+  \begin{align}
+    \label{thm: large rate}
+    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}
+    \xrightarrow[t\to \infty]{d}\bar{\zeta},
   \end{align}
   where $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function
-%\begin{align}
+  % \begin{align}
   %   \mathbf{E}[e^{i\theta\bar{\zeta}}]=\exp(\bar{m}[\theta f]),\quad \theta\in \mathbb{R}.
-%\end{align}
+  % \end{align}
   $\theta\mapsto \exp(\bar{m}[\theta f])$.
@@
 
+% *** Critical branching rate regime
 \subsubsection{Critical branching rate regime}
 For each $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
-\begin{equation}\label{tilde-m}
+\begin{equation}
+  \label{tilde-m}
   \widetilde{m}[f]
@@
 According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
-   We will prove in Lemma \ref{prop: alpha stable rv} that
-   $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+We will prove in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
 \begin{thm}
   \label{thm: critical clt}
-    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$,
-    under $\mathbb{P}_{\mu}(\cdot|D^c)$,
-    it holds that
+  If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
   \[
@@
   characteristic function
-%\[
+  % \[
   %   \mathbf E [e^{i\theta \widetilde{\zeta}}]
@@
   %   \quad \theta\in \mathbb R.
-%\]
+  % \]
   $\theta\mapsto \exp(\widetilde{m}[\theta f]$.
@@
 
+% *** Small branching rate regime
 \subsubsection{Small branching rate regime}
 \label{msmallcase}
-	If $f\in \mathcal{P}$ is non-trivial and satisfies  $\alpha\beta<\kappa_f b(1+\beta)$,
-	we define
+If $f\in \mathcal{P}$ is non-trivial and satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, we define
 \begin{equation}
   m[f]
-    :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
+  := \eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
 \end{equation}
@@
   \label{thm: small clt}
-       If $f\in\mathcal{P}$ is non-trivial and satisfies $\alpha\beta<\kappa_f b(1+\beta)$,
-    then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+  If $f\in\mathcal{P}$ is non-trivial and satisfies $\alpha\beta<\kappa_f b(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
   \[
@@
   where $\zeta$ is a $(1+\beta)$-stable random variable with
-%\[
+  % \[
   %   \mathbf E[e^{i\theta \zeta}]
@@
   %   \quad \theta\in \mathbb R.
-%\]
+  % \]
   characteristic function $\theta\mapsto \exp(m[\theta f])$.
 \end{thm}
+
+% ** Some intuitive explanation
 \subsection{Some intuitive explanation}
 Here we give some intuitive explanation of the central limit theorems above.
-    The main ideas
-    are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
+The main ideas are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
 For any $\mu\in \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
-\begin{equation}\label{Ist}
-    \mathcal I_s^t Y:=\mathcal I_s^t [Y, \mu]
-    := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s],\quad 0 \leq s \leq t <\infty.
+\begin{equation}
+  \label{Ist}
+  \mathcal I_s^t Y
+  := \mathcal I_s^t [Y, \mu]
+  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s],
+  \quad 0 \leq s \leq t <\infty.
 \end{equation}
@@
   \langle f,X_t\rangle
-        :=\sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle+\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle +
-         \langle P^\alpha_tf,X_0\rangle,
+  := \sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle+\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle + \langle P^\alpha_tf,X_0\rangle,
   \quad t\geq 0.
 \end{align}
-   To find the fluctuation of $\langle f,X_t\rangle$, we will investigate the fluctuation of
-   each term on the right hand side above.
+To find the fluctuation of $\langle f,X_t\rangle$, we will investigate the fluctuation of each term on the right hand side above.
 
 Suppose $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions
-%\[
+% \[
 %   \mathbf E[e^{i\theta \zeta_k}] = \exp( m_k[\theta f]),\quad k \in \mathbb N,
-%\]
-$\theta\mapsto \exp( m_k[\theta f])$,
-    where $m_k[f]$ is given in Lemma \ref{lem: def of all m} below.
+% \]
+$\theta\mapsto \exp( m_k[\theta f])$, where $m_k[f]$ is given in Lemma \ref{lem: def of all m} below.
 Recall $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
-    Lemma \ref{lem: mainlemma} and 
-   Proposition \ref{cor: indepedent of the limit zeta for critical and small} below  
-    imply that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
-\[
-    \bigg(\frac{\mathcal I^{t-k}_{t-k-1}\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\bigg)_{k=1}^n
+Lemma \ref{lem: mainlemma} and Proposition \ref{cor: indepedent of the limit zeta for critical and small} below imply that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
+\[
+  \bigg(\frac{\mathcal I^{t-k}_{t-k-1} \langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \bigg)_{k=1}^n
   \xrightarrow [t\to \infty]{d} (\zeta_k)_{k=1}^n.
@@
 \[
-     \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}\sum_{k=0}^\infty \zeta_k,
+  \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} 
+  \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}\sum_{k=0}^\infty \zeta_k,
 \]
 where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function
-%\[
+% \[
 %   \mathbf E[e^{i\theta \zeta}] = \exp(m[\theta f]),\quad \theta \in \mathbb R.
-%\]
+% \]
 $\theta\mapsto \exp(m[\theta f])$,
 with $m[\theta f]$ given in Lemma \ref{lem: def of all m} below.
-	In the explanation above, we have used the facts that 
-    $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined, and
-\begin{equation}
+In the explanation above, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined, and
+\begin{align}
   \label{eq: equatlity for mf for small rate}
-    m[f] =  \sum_{k=0}^\infty m_k[ f].
-\end{equation}
+  m[f] 
+  = \sum_{k=0}^\infty m_k[ f].
+\end{align}
 These facts will be made clear in Subsection \ref{sec: stable distributions} below.
 
-    If $f$ is in the critical branching rate regime, i.e., $\alpha \beta = \kappa_f b(1+\beta)$,
-    then the right hand side of \eqref{eq: equatlity for mf for small rate} may not converge.
+If $f$ is in the critical branching rate regime, i.e., $\alpha \beta = \kappa_f b(1+\beta)$, then the right hand side of \eqref{eq: equatlity for mf for small rate} may not converge.
 Instead, see Lemma \ref{lem: def of all m} below, there is another quantity $\widetilde m[f]$ satisfying that
 \[
-    \widetilde{m}[f] = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
+  \widetilde{m}[f] 
+  = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
 \]
@@
 \[
- 	\frac{\langle f,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}} \overset{d}{\approx} \frac{1}{t^{\frac{1}{1+\beta}}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{d} \widetilde \zeta
+ 	\frac{\langle f,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}} 
+  \overset{d}{\approx} \frac{1}{t^{\frac{1}{1+\beta}}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k
+  \xrightarrow[t\to \infty]{d} \widetilde \zeta
 \]
 where $\widetilde \zeta$ is a $(1+\beta)$-stable random variable with characteristic function
-%\[
-%    \mathbf E[e^{i\theta \widetilde \zeta}] = \exp(\widetilde m[\theta f]),\quad \theta \in \mathbb R.
-%\]
+% \[
+%   \mathbf E[e^{i\theta \widetilde \zeta}] 
+%   = \exp(\widetilde m[\theta f]),\quad \theta \in \mathbb R.
+% \]
 $\theta\mapsto \exp(\widetilde m[\theta f])$.
@@
 \[
-    H^p_t-H^p_\infty=\sum^{\infty}_{n=1}(H^p_{t+n-1}-H^p_{t+n}).
+  H^p_t-H^p_\infty
+  =\sum^{\infty}_{n=1}(H^p_{t+n-1}-H^p_{t+n}).
 \]
@@
 
-    For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$, where $$f_l=\sum_{p\in \mathcal{N}}a_p\phi_p(x)\in \mathcal{C}_l,\quad x\in \mathbb{R}^d,$$
- and $f_c=\langle f, \phi_p\rangle_{\varphi} \phi_p(x)$  with $p=\frac{\alpha\beta}{b(1+\beta)}$. Note that there may be no $p$ such that $p=\frac{\alpha\beta}{b(1+\beta)}$. In this case $f_c=0$.
+For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$, where 
+\[
+  f_l
+  = \sum_{p\in \mathcal{N}}a_p\phi_p(x)\in \mathcal{C}_l
+  , \quad x\in \mathbb{R}^d,
+\]
+and $f_c=\langle f, \phi_p\rangle_{\varphi} \phi_p(x)$  with $p=\frac{\alpha\beta}{b(1+\beta)}$.
+Note that there may be no $p$ such that $p=\frac{\alpha\beta}{b(1+\beta)}$. In this case $f_c=0$.
 Our main results above give central limit type results for $\langle f_l, X_t\rangle$, $\langle f_c, X_t\rangle$ and $\langle f_s, X_t\rangle$, respectively.
@@
 There are still many open questions.
-    Ren, Song and Zhang have established some spatial  central limit theorems in
- \cite{RenSongZhang2015Central} 
-	for a class of superprocesses with general spatial motions under the assumption that the branching mechanisms satisfy a second moment condition.
+Ren, Song and Zhang have established some spatial  central limit theorems in \cite{RenSongZhang2015Central} for a class of superprocesses with general spatial motions under the assumption that the branching mechanisms satisfy a second moment condition.
 We hope to prove spatial CLT's for superprocesses with general motions without the second moment assumption on the branching mechanism in a future project.
@@
 	\psi_1(z)
-	&:= \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big)
+	& := \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta) y^{2+\beta}}\Big)
 \end{align}
@@
 Here are some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}:
-    If $h$ is a complete Bernstein function which is regularly varying at 0 with index
-$\beta_1\in (\beta, 1)$, then
-$$
-    \psi(z):=-\alpha z + \rho z^2+\eta z^{1+\beta}+zh(z), \qquad z>0
-$$
+If $h$ is a complete Bernstein function which is regularly varying at 0 with index $\beta_1\in (\beta, 1)$, then
+\[
+  \psi(z)
+  := -\alpha z + \rho z^2+\eta z^{1+\beta}+zh(z)
+  , \qquad z>0
+\]
 satisfies Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
 If $\beta_1\in (\beta, 1)$, $c_1\in (0, \eta/\Gamma(-1-\beta))$ and $c_2\ge 1$, then
-$$
-\psi(z):=-\alpha z + \rho z^2+\eta z^{1+\beta}-\int^\infty_{c_2}
-(e^{-yz}-1+yz)\frac{c_1dy}{y^{1+\beta_1}}, \qquad z\in \mathbb R_+
-$$
+\[
+  \psi(z)
+  :=-\alpha z + \rho z^2+\eta z^{1+\beta}-\int^\infty_{c_2} (e^{-yz}-1+yz)\frac{c_1dy}{y^{1+\beta_1}}
+  , \qquad z\in \mathbb R_+
+\]
 satisfies Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
 
-    The rest of the paper is organized as follows: In Subsection \ref{sec: branching mechanism} we will give some preliminary results for our branching mechanism $\psi$.
+The rest of the paper is organized as follows: 
+In Subsection \ref{sec: branching mechanism} we will give some preliminary results for our branching mechanism $\psi$.
 In Subsections \ref{sec: controller} and \ref{sec: h-controller} we will give some estimates for some operators related to the super-OU process $X$ that will be used in our proofs.
@@
   \item
-    $\varphi$ and $\phi_p$ are given 
-    in \eqref{invariantdensity} and \eqref{eigenfunction}, respectively.
+    $\varphi$ and $\phi_p$ are given in \eqref{invariantdensity} and \eqref{eigenfunction}, respectively.
   \item
-    $P_t$, $P^\alpha_t$, $V_t$ and $U_t$ are given 
-   in \eqref{eq: meansemigroup}, \eqref{eq: meansemigroup}, 
-    \eqref{eq: def of V_t}, \eqref{eq: def of U_t}, respectively.
+    $P_t$, $P^\alpha_t$, $V_t$ and $U_t$ are given in \eqref{eq: meansemigroup}, \eqref{eq: meansemigroup}, \eqref{eq: def of V_t}, \eqref{eq: def of U_t}, respectively.
   \item
-    $\mathcal N$, $K$, $\mathcal C_l$ and $I_t$ are given 
-    in \eqref{eq: def of N}, \eqref{eq: def of N},  \eqref{eq: def of Cl} and 
-    \eqref{definition of Itf}, respectively.
+    $\mathcal N$, $K$, $\mathcal C_l$ and $I_t$ are given in \eqref{eq: def of N}, \eqref{eq: def of N},  \eqref{eq: def of Cl} and \eqref{definition of Itf}, respectively.
   \item
-    $\psi$, $\psi_1$ and $\psi_0$ are given 
-    in \eqref{eq: honogeneou branching mechanism}, \eqref{eq: psi 1} and 
-    \eqref{eq: psi 0}, respectively.
+    $\psi$, $\psi_1$ and $\psi_0$ are given in \eqref{eq: honogeneou branching mechanism}, \eqref{eq: psi 1} and \eqref{eq: psi 0}, respectively.
   \item
@@
   \item
-    $m_t[f]$, $\bar m_t[f]$, $m[f]$, 
-   $\widetilde m[f]$ 
-   and $\bar m[f]$ are given in Lemma \ref{lem: def of all m}.
+    $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\widetilde m[f]$ and $\bar m[f]$ are given in Lemma \ref{lem: def of all m}.
   \end{itemize}
@@
 
+% ** Preliminaries
 \section{Preliminaries}
+% *** Branching mechanism
 \subsection{Branching mechanism}
@@
 \begin{proof}
-According to Lemma \ref{lem: extension lemma for branching mechanism} below and
-the uniqueness of holomorphic extensions,
+  According to Lemma \ref{lem: extension lemma for branching mechanism} below and the uniqueness of holomorphic extensions,
 	we know that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
@@
   \[
-	\psi_1(z)= \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big),
-	\quad z\in \mathbb C_+.
+    \psi_1(z)
+    = \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big)
+    , \quad z\in \mathbb C_+.
   \]
@@
     |\psi_1(z)|
-	&\leq \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|
-	\\&\leq  |z|^2\int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|
-	\\&\quad + |z|^{1+\beta +\delta}\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|,
+    & \leq \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
+    & \leq  |z|^2\int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
+    & \quad + |z|^{1+\beta +\delta}\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|,
       \quad z \in \mathbb C_+,
@@
 \end{proof}
-
 The following lemma says that the constants $\eta, \beta$ in Assumption \ref{asp: branching mechanism} are uniquely determined by the L\'evy measure $\pi$.
@@
   \[
-	 \int_{(1,\infty)}y^{1+\beta' +\delta'}~\Big|\pi(dy)-\frac{\eta'~dy}{\Gamma(-1-\beta)y^{2+\beta'}}\Big| <\infty.
+    \int_{(1,\infty)} y^{ 1 + \beta'  + \delta' }~ \Big| \pi(dy) - \frac {\eta' ~dy} {\Gamma (- 1 - \beta ) y^{2 + \beta'}} \Big| 
+    < \infty.
   \]
@@
   \[
-	\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy)-\frac{\eta'~dy}{\Gamma(-1-\beta)y^{2+\beta'}}\Big| <\infty.
+    \int_{(1, \infty)} y^{1 + \beta + \delta}   \Big| \pi(dy) - \frac {\eta' ~dy} {\Gamma( - 1 - \beta)y^{2 + \beta'}} \Big| 
+    < \infty .
   \]
@@
   \[
-	\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}-\frac{\eta'~dy}{\Gamma(-1-\beta)y^{2+\beta'}}\Big| <\infty.
+    \int_{(1,\infty)} y^{ 1 + \beta + \delta} \Big| \frac { \eta ~dy} {\Gamma (- 1 - \beta) y^{2 + \beta}} - \frac {\eta' ~dy} {\Gamma (- 1 - \beta) y^{2 + \beta'}} \Big| < \infty.
   \]
@@
   \[
-	|\eta z^{1+\beta} - \eta' z^{1+\beta'} |
-	\leq cz^{1+\beta+ \delta}+cz^2,
-	\quad z \in \mathbb R_+.
+    | \eta z^{ 1 + \beta } - \eta' z^{ 1 + \beta' } |
+    \leq c z^{ 1 + \beta + \delta } + c z^2
+    , \quad z \in \mathbb R_+.
   \]
@@
   \[
-	|\eta - \eta' z^{\beta' - \beta} |
-	\leq cz^{\delta}+cz^{1-\beta},
-	\quad z \in \mathbb R_+.
+    | \eta - \eta' z^{ \beta' - \beta } |
+    \leq cz^{\delta}+cz^{1-\beta}
+    ,	\quad z \in \mathbb R_+.
   \]
 	This implies that
-%\[
+  % \[
   $
 	\eta' z^{\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0.
-%\]
+  % \]
   $
@@
   \label{lem: LlogL criterion}
-If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies
-the $L \log L$ condition, i.e.,
-\[
-    \int_{(1,\infty)} y \log y~\pi(dy)< \infty.
+  If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies the $L \log L$ condition, i.e.,
+  \[
+    \int_{(1,\infty)} y \log y~\pi(dy)
+    < \infty.
   \]
@@
   \[
-	\int_{(1,\infty)}y\log y~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty.
+    \int_{(1,\infty)} y \log y ~\Big| \pi(dy) - \frac { \eta ~dy } { \Gamma ( - 1 - \beta ) y^{ 2 + \beta } } \Big| 
+    < \infty.
   \]
@@
   \[
-	\int_{(1,\infty)}y\log y~\Big(\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big) < \infty.
+    \int_{ ( 1, \infty ) } y \log y ~\Big( \pi(dy) - \frac { \eta ~dy } { \Gamma ( - 1 - \beta ) y^{ 2 + \beta } } \Big) 
+    < \infty.
   \]
@@
   \[
-	\int_{(1,\infty)}\frac{\eta \log y~dy}{\Gamma(-1-\beta)y^{1+\beta}} < \infty,
+    \int_{ ( 1, \infty ) } \frac { \eta \log y ~dy } { \Gamma ( - 1 - \beta ) y^{ 1 + \beta } } 
+    < \infty,
   \]
@@
 \end{proof}
+
+% ** Definition of controller
 \subsection{Definition of controller}
@@
 For any function $h: [0,\infty) \to [0,\infty)$, we say an operator $R: \mathcal P^+ \to \mathcal P^+$ is an \emph{$h$-controller} if
-%\begin{itemize}
-%\item
+% \begin{itemize}
+% \item
 %   $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and
-%\item
+% \item
 %   $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
-%\end{itemize}
+% \end{itemize}
 (1) $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and (2) $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
 For a subset $\mathcal D$ of $\mathcal P^*$ and an $h$-controller $R$, we say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controlled by $R$ on $\mathcal D$} if $|Af| \leq R|f|$ for each $f\in \mathcal D$.
-    We say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controllable} if there exists an $h$-controller $R$ such that $A$ is $h$-controlled by $R$.
+We say an operator $A : 
+\mathcal D \to \mathcal P^*$ is \emph{$h$-controllable} if there exists an $h$-controller $R$ such that $A$ is $h$-controlled by $R$.
 We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
@@
 For any $a \in \mathbb R$ and any operator $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
-\begin{lem}\label{lem: property of controllable operators}
+\begin{lem}
+  \label{lem: property of controllable operators}
   Suppose that $\Lambda$ is an index set and $(A_\lambda)_{\lambda\in \Lambda}$ is a
-%family of operators from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$.
+  % family of operators from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$.
   % Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
@@
   which is uniformly 
-%$h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
+  % $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
   $h$-controlled by $R_A$ on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
   Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators, from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$,
-% which is  is uniformly $g$-controllable on $\mathcal D_0$ 
-which is  is uniformly $g$-controlled by $R_B$ on $\mathcal D_0$ 
- for some function $g: [0,\infty) \to [0,\infty)$. Suppose that
- $(C_\lambda)_{\lambda\in \Lambda} $ is a family of operators, from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$,
+  % which is uniformly $g$-controllable on $\mathcal D_0$ 
+  which is uniformly $g$-controlled by $R_B$ on $\mathcal D_0$ 
+  for some function $g: [0,\infty) \to [0,\infty)$. 
+  Suppose that $(C_\lambda)_{\lambda\in \Lambda} $ is a family of operators, from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$,
   % for each $\lambda \in \Lambda$, $C_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$. 
-which is  is uniformly $k$-controlled by $R_C$ on $\mathcal D_0$  
-for a given function $k:[0,\infty) \to [0, \infty)$.
+  which is uniformly $k$-controlled by $R_C$ on $\mathcal D_0$ for a given function $k:[0,\infty) \to [0, \infty)$.
   Then 
@@
     $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$ and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$;
-\item[(3)] For any $a>0$, $(C^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(k^a)$-controllable.
+  \item[(3)] 
+    For any $a>0$, $(C^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(k^a)$-controllable.
     % Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
@@
   % Then we have
-%\begin{itemize}
-%\item
+  % \begin{itemize}
+  % \item
   %   For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, we have $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
-%\item
+  % \item
   %   If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_AR_Bf \leq R_A R_B g$.
-%\item
+  % \item
   %   If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_AR_B(\theta f) \leq R_A(g(\theta) R_Bf) \leq (h\circ g)(\theta) R_A R_B f $.
-%\end{itemize}
+  % \end{itemize}
   If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, then $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
@@
   (2). 
-    %Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R_A$ on $\mathcal D$.
+  % Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R_A$ on $\mathcal D$.
   % Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
   % Then we have
-%\begin{itemize}
-%\item
+  % \begin{itemize}
+  % \item
   %   For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
-%\item
+  % \item
   %   If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_A\times R_Bf \leq R_A\times R_B g$.
-%\item
+  % \item
   %   If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_A\times R_B (\theta f) \leq h(\theta) g(\theta) (R_A \times R_B) f $.
-%\end{itemize}
+  % \end{itemize}
   % Therefore $(A_\lambda \times B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \times g)$-controllable on $\mathcal D$.
@@
   % We also have the following:
-%\begin{itemize}
-%\item
+  % \begin{itemize}
+  % \item
   %   For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
-%\item
+  % \item
   %   If $f,g \in \mathcal P^+$ with $f\leq g$, then $(R_A + R_B)f \leq (R_A + R_B) g$.
-%\item
+  % \item
   %   If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $(R_A + R_B) (\theta f) \leq h(\theta) R_Af + g(\theta) R_Bf \leq (h(\theta) \vee g(\theta)) (R_A+R_B)f $.
-%\end{itemize}
+  % \end{itemize}
   % Therefore $(A_\lambda + B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \vee g)$-controllable on $\mathcal D$.
@@
   (3). 
-    %Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
-%Then we have the following:
-%\begin{itemize}
-%\item
+  % Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
+  % Then we have the following:
+  % \begin{itemize}
+  % \item
   %   For each $\lambda \in \Lambda$, $f\in \mathcal D$, we have $|A_\lambda^{\times a} f| = |A_\lambda f|^a  \leq R^{\times a} |f|$.
-%\item
+  % \item
   %   If $f,g \in \mathcal P^+$ with $f\leq g$, then $R^{\times a}f \leq R^{\times a} g$.
-%\item
+  % \item
   %   If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R^{\times a}(\theta f) \leq (h(\theta) R f)^a = h(\theta)^a R^{\times a}f$.
-%\end{itemize}
+  % \end{itemize}
   % Therefore $(A_\lambda^{\times a})_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable on $\mathcal D$.
@@
   (4).     
-    %Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
+  % Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
   For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
   \[
-    |A_{\nu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\nu(d\lambda) \leq \int_{\Lambda}R|f|(x)\nu(d\lambda) \leq R|f|(x). \qedhere
+    | A_{\nu}f(x) | 
+    \leq \int_{\Lambda} | A_{\lambda}f(x) | \nu(d\lambda) 
+    \leq \int_{\Lambda}R|f|(x)\nu(d\lambda) \leq R|f|(x). 
+    \qedhere
   \]
@@
 
+% ** h-controller for super-OU processes
 \subsection{h-controller for super-OU processes}
 \label{sec: h-controller}
-   Let $X$ be the super-OU process introduced in Subsection \ref{sec: Motivation}
-    with branching mechanism $\psi$ satisfying
+Let $X$ be the super-OU process introduced in Subsection \ref{sec: Motivation} with branching mechanism $\psi$ satisfying
 Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
@@
 Define
-\begin{equation}
+\begin{align}
   \label{eq: psi 0}
-    \psi_0(z)=\psi(z)+\alpha z,\quad z\in \mathbb{R}_+
-\end{equation}
+  \psi_0(z)
+  = \psi(z) + \alpha z
+  , \quad z\in \mathbb{R}_+
+\end{align}
 Using an argument similar to the proof  of Lemma \ref{lem: complex extension for psi1},
@@
 For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, we define
-%\begin{align}
-%\label{eq: def of operator Psi}
+% \begin{align}
+%   \label{eq: def of operator Psi}
 %   \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
-%    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x),
+%   \\ \Psi_0 f(x) &:= \Psi f(x) + \alpha f(x),
 %   \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big).
-%\end{align}
+% \end{align}
 $\Psi f (x) = -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big)$. $\Psi_1 f(x)$ and
@@
 For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let
-\begin{equation}\label{eq: def of U_t}
-    U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}
-\end{equation}
+\begin{align}
+  \label{eq: def of U_t}
+  U_tf(x) 
+  := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}
+\end{align}
 be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
-    %new
+% new
 (See the paragraph after Lemma \ref{lem: Lip of power function}.)
-    %end new
+% end new
 It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
@@
   \label{eq:chareq2}
-    U_tf(x)-\int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
-    =i P^{\alpha}_t f(x),
-    \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
+  U_tf(x) - \int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
+  = i P^{\alpha}_t f(x)
+  , \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
 \end{align}
 For all $t\geq 0$ and $f\in \mathcal P$, we define
-\begin{align}\label{eq: def of Zf}
+\begin{align}
+  \label{eq: def of Zf}
   & Z_t f
@@
   = Z'_t + Z''_t
-    = Z_t+Z'''_t, \quad t\geq 0.
+  = Z_t + Z'''_t
+  , \quad t\geq 0.
 \end{equation}
 For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-\begin{equation}\label{Q_k}
+\begin{equation}
+  \label{Q_k}
   Q_\kappa f
@@
 % and
-%\begin{equation}\label{Q}
+% \begin{equation}
+%   \label{Q}
 %   Q f:= Q_{\kappa_f}f.
-%\end{equation}
+% \end{equation}
 Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
@@
 
-    (3).
-        By Lemma \ref{lem: complex extension for psi1},
-         there exist $C, \delta >0$ 
-         satisfying $\beta+\delta< 1$ such that for all
-         $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
+  (3). By Lemma \ref{lem: complex extension for psi1}, there exist $C, \delta >0$ satisfying $\beta+\delta< 1$ such that for all $ f \in \mathcal P^* \cap \mathcal B( \mathbb R^d, \mathbb C_+ )$,
   \begin{align}
@@
   \[
-    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta},\quad f\in \mathcal P^+,
+    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta}
+    , \quad f\in \mathcal P^+,
   \]
@@
   % From parts (1)--(3) of this lemma and Lemma \ref{lem: property of controllable operators}.(2), 
-From (1)--(3) above and Lemma \ref{lem: property of controllable operators}.(1), 
-we know that the operators
-\[
-    f\mapsto P^\alpha_{t-s}\Psi_0(-U_sf),
-    \quad 0\leq s\leq t\leq 1,
+  From (1)--(3) above and Lemma \ref{lem: property of controllable operators}.(1), we know that the operators
+  \[
+    f \mapsto P^\alpha_{t-s}\Psi_0(-U_sf)
+    , \quad 0\leq s\leq t\leq 1,
   \]
@@
   Combining this with \eqref{eq:chareq2} and 
-    %Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.
+  % Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.
   Lemma \ref{lem: property of controllable operators}.(4), we get the desired result.
@@
   \begin{equation}
-    (Z'_t - Z_t)f = \int_0^t P^\alpha_{t-s}\Big( \eta \big((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} \big)\Big)ds,
-    \quad 0\leq t\leq 1, f\in \mathcal P,
+    (Z'_t - Z_t)f 
+    = \int_0^t P^\alpha_{t-s}\Big( \eta \big((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} \big)\Big)ds
+    , \quad 0\leq t\leq 1, f\in \mathcal P,
   \end{equation}
@@
     |\Psi_1(f)|
-    \le C(|f|^2+|f|^{1+\beta+ \delta}),
-    \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+).
+    \le C(|f|^2+|f|^{1+\beta+ \delta})
+    , \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+).
   \]
@@
   \[
-    f\mapsto C(f^2+f^{1+\beta+\delta}),
-    \quad f\in \mathcal P^+
+    f \mapsto C(f^2+f^{1+\beta+\delta})
+    , \quad f\in \mathcal P^+
   \]
@@
     \mapsto Z_t'' f
-    = \int_0^t P_{t-s}^\alpha \Psi_1(-U_sf)ds,
-    \quad 0\leq t\leq 1,
+    = \int_0^t P_{t-s}^\alpha \Psi_1(-U_sf)ds
+    , \quad 0\leq t\leq 1,
   \]
@@
 
+% *** Stable distributions
 \subsection{Stable distributions}
@@
 
-   Recall that
-    $(P^\alpha_t)_{t\geq 0}$ is defined in \eqref{eq: meansemigroup}, $\mathcal P$ is defined in \eqref{eq: polynomial growth function}, $\mathcal N$ is given in \eqref{eq: def of N} and $\mathcal C_l$ is defined in \eqref{eq: def of Cl}.
+Recall that $(P^\alpha_t)_{t\geq 0}$ is defined in \eqref{eq: meansemigroup}, $\mathcal P$ is defined in \eqref{eq: polynomial growth function}, $\mathcal N$ is given in \eqref{eq: def of N} and $\mathcal C_l$ is defined in \eqref{eq: def of Cl}.
 \begin{lem}
@@
 	Furthermore, there exists  $C>0$ such that
-\begin{equation}\label{domi-m}
+  \begin{equation}
+    \label{domi-m}
     |m_t[f]|
@@
   \begin{equation}
-    |\bar{m}_t[f]| \leq C e^{-(\alpha\beta-K(1+\beta)b)t}, \quad t\geq 1,
+    |\bar{m}_t[f]| 
+    \leq C e^{-(\alpha\beta-K(1+\beta)b)t}, \quad t\geq 1,
   \end{equation}
@@
     \bar{m}[f]
-   :=\eta \int_{0}^{\infty} e^{\alpha s}~ds \int_{\mathbb R^d} \big(iI_sf(x)\big)^{1+\beta}\varphi(x)~dx.
+    :=\eta \int_{0}^{\infty} e^{\alpha s}~ds \int_{\mathbb R^d} \big( iI_sf(x) \big)^{ 1 + \beta } \varphi( x ) ~dx.
   \]
   Furthermore, we have
-\begin{equation}\label{sum-bar-m}
+  \begin{equation}
+    \label{sum-bar-m}
     \bar{m}[f]
-    =\sum_{n=1}^{\infty}\bar{m}_n[f].
+    = \sum_{n=1}^{\infty} \bar{m}_n[f].
   \end{equation}
@@
     \label{para: critical case}
-	\widetilde{m}[f] = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
+    \widetilde{m}[f] 
+    = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
   \end{equation}
@@
     m[f]
-    :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
+    := \eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
   \]
 	Furthermore, we have
-\begin{equation}\label{sum-m}
+  \begin{equation}
+    \label{sum-m}
     m[f]
-    =\sum_{k=0}^\infty m_k[f].
+    = \sum_{k=0}^\infty m_k[f].
   \end{equation}
@@
   So we only need to  (2). We first claim that there exists $h\in \mathcal{P}$ such that
-\[
+  \begin{align}
     \label{ineq: control of Itg}
@@
     \quad t\geq 0, x\in \mathbb{R}^d.
-\]
+  \end{align}
   In fact, if we put $h:= \sum_{p\in \mathcal N} |\langle f,\phi_p\rangle_{\varphi}\phi_p|$, then
@@
 \begin{align}
-     &|\bar{m}_t[f]|
-    \leq \eta \int_{t-1}^{t} e^{\alpha s}~ds \int_{\mathbb R^d} | I_sf(x)|^{1+\beta}\varphi(x)~dx
-    \\&\leq \eta \int_{t-1}^{t} e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}~ds\int_{\mathbb R^d} h(x)^{1+\beta}\varphi(x)~dx
-    \\&\leq C e^{-(\alpha\beta-K(1+\beta)b)t},
-    \quad t\geq 1.
+  & |\bar{m}_t[f]|
+    \leq \eta \int_{t-1}^{t} e^{\alpha s}~ds \int_{\mathbb R^d} | I_sf(x)|^{1+\beta}\varphi(x)~dx \\
+  & \leq \eta \int_{t-1}^{t} e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}~ds\int_{\mathbb R^d} h(x)^{1+\beta}\varphi(x)~dx \\
+  & \leq C e^{-(\alpha\beta-K(1+\beta)b)t}
+    , \quad t\geq 1.
 \end{align}
@@
 \end{proof}
-    The following proposition says that $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\bar m[f]$ and 
-    $\widetilde m[f]$ 
-    are all related to $(1+\beta)$-stable distributions.
+The following proposition says that $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\bar m[f]$ and  $\widetilde m[f]$ are all related to $(1+\beta)$-stable distributions.
 \begin{prop}
@@
     \label{item: stable 3}
-   $\theta \mapsto \exp(\bar m[\theta f])$
-    is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$;
+    $\theta \mapsto \exp(\bar m[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$;
   \item
@@
   \[
-    \theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},
+    \theta 
+    \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},
     \quad \theta \in \mathbb R^d
@@
   \[
-    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
+    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) 
+    = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
     f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
@@
   \[
-    \lambda_0(d\xi) := \frac1{\Gamma(-1-\beta)}\int_0^\infty t^{1+\beta}k(\xi,dt) \lambda (d\xi),
+    \lambda_0(d\xi) 
+    := \frac1{\Gamma(-1-\beta)}\int_0^\infty t^{1+\beta}k(\xi,dt) \lambda (d\xi),
   \]
@@
   \begin{align}
-    &\lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt)
-    \\&= \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
+    &\lambda_0(S) 
+      = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt) \\
+    & = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
   \end{align}
@@
   \[
-    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
+    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)
+    = \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
   \]
@@
     \hat \mu(\theta)
-    =\exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\},
-    \quad \theta \in \mathbb R.
+    = \exp \Big \{ \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy) \Big \}
+    , \quad \theta \in \mathbb R.
   \]
@@
   \begin{align}
-    &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
-    = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}
-    \\& = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt)
-    \\& = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
-    = \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)
-    \\& = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
+    & \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
+      = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}} \\
+    & = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt) \\
+    & = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
+      = \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt) \\
+    & = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
       \qedhere
@@
     \label{eq: what I want to proof}
-	 \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} | P_{s}^\alpha f(x)|^{1+\beta} \varphi(x)~dx
+    \int_t^{t+1}e^{-\alpha s} ~ds\int_{\mathbb R^d} | P_{s}^\alpha f(x)|^{1+\beta} \varphi(x)~dx
     \in (0, \infty).
   \end{equation}
-	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),
-      we know that
-      \[
-      f \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f|^{1+\beta}~ds
+	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4), we know that
+  \[
+    f 
+    \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f|^{1+\beta}~ds
   \]
@@
 	Therefore the integral on the left-hand side of \eqref{eq: what I want to proof} is finite.
-	Since $f$ is non-trivial,
-    the integral on the left-hand side of \eqref{eq: what I want to proof} is positive.
-
-The proofs of \eqref{item: stable 2}--\eqref{item: stable 5} are similar to that of \eqref{item: stable 1}. We omit the details here.
+	Since $f$ is non-trivial, the integral on the left-hand side of \eqref{eq: what I want to proof} is positive.
+
+  The proofs of \eqref{item: stable 2}--\eqref{item: stable 5} are similar to that of \eqref{item: stable 1}. 
+  We omit the details here.
 \end{proof}
@@
   Then there exists $h\in \mathcal{P}$ such that
-%\begin{align}
+  % \begin{align}
   %   |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
-%\end{align}
+  % \end{align}
   $|P_sg_k|\leq e^{-bs}h$ for all $s, k \geq 0.$
@@
 
-\begin{lem}\label{control of gn} Suppose that $g\in \mathcal{C}_l$.
+\begin{lem}
+  \label{control of gn} 
+  Suppose that $g\in \mathcal{C}_l$.
   Put
@@
   Then there exists $h\in \mathcal{P}$ such that
-%\begin{align}
+  % \begin{align}
   %   |P_s\bar{g}_t|
   %   \leq e^{-bs}h,\quad s\geq 0, t\geq 0.
-%\end{align}
+  % \end{align}
   $|P_s\bar{g}_t| \leq e^{-bs}h$ for all $s, t\geq 0.$
@@
   \Big|\sum_{p\in \mathcal N}\langle g, \phi_p\rangle_\varphi e^{-(\alpha-|p|b)t} \frac{\partial}{\partial x_i}\phi_p(x)\Big|
-     \leq e^{-(\alpha-Kb)t}h_1(x),
-    \quad t\geq 0, x\in \mathbb R^d.
+  \leq e^{-(\alpha-Kb)t}h_1(x)
+  , \quad t\geq 0, x\in \mathbb R^d.
 \end{align}
@@
 \begin{align}
-    &\frac{\partial}{\partial x_i} P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}
+  & \frac{\partial}{\partial x_i} P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}
     = \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s} g)^{1+\beta}
-    = e^{-b(1-s)} P_{1-s}^\alpha \frac{\partial}{\partial x_i} (I_{t-s}g)^{1+\beta}
-    \\&=(1+\beta)e^{-b(1-s)} P_{1-s}^\alpha \Big( (I_{t-s}g)^\beta \times \frac{\partial}{\partial x_i} (I_{t-s}g) \Big),\quad s\in [0,1], t\geq 0.
+    = e^{-b(1-s)} P_{1-s}^\alpha \frac{\partial}{\partial x_i} (I_{t-s}g)^{1+\beta} \\
+  & =(1+\beta)e^{-b(1-s)} P_{1-s}^\alpha \Big( (I_{t-s}g)^\beta \times \frac{\partial}{\partial x_i} (I_{t-s}g) \Big),\quad s\in [0,1], t\geq 0.
 \end{align}
@@
   \label{eq: key estimation for partial}
-    \Big|\frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| \leq a(s) e^{-(\alpha - Kb)(1+\beta)t}h_2(x),\quad s\in [0,1],t\geq 0, x\in \mathbb R^d.
+  \Big| \frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| \leq a(s) e^{-(\alpha - Kb)(1+\beta)t}h_2(x),\quad s\in [0,1],t\geq 0, x\in \mathbb R^d.
 \end{equation}
@@
 \[
-    \int_0^1 \sup_{x\in A} \Big|\frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| ds < \infty,\quad t\geq 0.
+  \int_0^1 \sup_{x\in A} \Big|\frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| ds 
+  < \infty
+  , \quad t\geq 0.
 \]
@@
 \begin{align}
-    &\Big|\frac{\partial}{\partial x_i}\bar{g}_t(x)\Big|
+  & \Big|\frac{\partial}{\partial x_i}\bar{g}_t(x)\Big|
     = e^{(\alpha-Kb)(1+\beta)t}\Big|\frac{\partial}{\partial x_i}Z_1(-I_tg)\Big| \leq C h_2(x),
@@
 Therefore there exist $c,n>0$ such that
-\begin{align}\label{ineq: control of sup gt}
-    |\nabla \bar g_t (z)|
-    \leq c(1+|z|)^n,
-    \quad t\geq 0, z\in \mathbb R^d.
+\begin{align}
+  \label{ineq: control of sup gt}
+  | \nabla \bar g_t (z)|
+  \leq c(1+|z|)^n
+  , \quad t\geq 0, z\in \mathbb R^d.
 \end{align}
@@
 \[
-    D(x,y):= \{ax+by: a,b\in [0,1]\},\quad x, y \in \mathbb R^d.
+  D(x,y)
+  := \{ax+by: a,b\in [0,1]\}
+  , \quad x, y \in \mathbb R^d.
 \]
@@
 % Also, note that
-%\[
+% \[
 %   |\sqrt {1-\theta} - 1| \leq \theta, \quad \theta\in [0,1]
-%\]
-$|\sqrt {1-\theta} - 1| \leq \theta$ for all $\theta\in [0,1]$,
+% \]
+$ | \sqrt { 1 - \theta } - 1 | \leq \theta $ for all $ \theta \in [ 0, 1 ] $,
 and
-%\[
+% \[
 %   1+\theta + \lambda \leq (1+\theta)(1+\lambda), \quad \theta ,\lambda \geq 0.
-%\]
-$1+\theta + \lambda \leq (1+\theta)(1+\lambda)$ for all $\theta ,\lambda \geq 0$.
-	Using the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, 
-    we get that for all $s,t\geq 0, x\in \mathbb R^d$,
-\begin{align}
-    &|P_s\bar{g}_t(x)|
+% \]
+$ 1 + \theta + \lambda \leq ( 1 + \theta ) ( 1 + \lambda ) $ for all $ \theta, \lambda \geq 0$.
+Using the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we get that for all $s,t\geq 0, x\in \mathbb R^d$,
+\begin{align}
+  & |P_s\bar{g}_t(x)|
     = \Big|\int_{\mathbb R^d} \big(\bar {g}_t(xe^{-bs}+y\sqrt{1-e^{-2bs}})-\bar {g}_t (y)\big) \varphi(y)~dy \Big| \\
   & \leq \int_{\mathbb R^d} \sup_{z\in D(x,y)} |\nabla \bar g_t (z)|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy \\
-    & \leq e^{-bs}\int_{\mathbb R^d} c(1+|x|+|y|)^n (|x|+|y|) \varphi(y)~dy
-    \\& \leq ce^{-bs}(1+|x|)^n\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y)dy + \int_{\mathbb R^d}(1+|y|)^n|y|\varphi(y)dy\Big).
+  & \leq e^{-bs}\int_{\mathbb R^d} c(1+|x|+|y|)^n (|x|+|y|) \varphi(y)~dy \\
+  & \leq ce^{-bs}(1+|x|)^n\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y)dy + \int_{\mathbb R^d}(1+|y|)^n|y|\varphi(y)dy\Big).
   \qedhere
@@
 
+% * Working
 \subsection{Small value probability}

### 2019-08-03 supCLT.tex
change supCLT.tex
Clean the tex file

@@
 
-% * Working
+% *** small value probability
 \subsection{Small value probability}
@@
 
-    Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$
-    when $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
+Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$ when $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
 Suppose that Grey's condition is satisfied, i.e., there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
@@
   It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, 
-%the following statements are true:
-%\begin{itemize}
-%\item
+  % the following statements are true:
+  % \begin{itemize}
+  % \item
   %   $0\leq \bar v_t < \infty$ for all $t>0$.
-%\item
+  % \item
   %   $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
-%\end{itemize}
+  % \end{itemize}
   we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; and (ii) $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
@@
   Therefore we have
-%\begin{itemize}
-%\item
+  % \begin{itemize}
+  % \item
   %   $\bar v > 0$ ,
-%\item
+  % \item
   %   $\psi(z) < 0$ on $z\in (0,\bar v)$,
-%\item
+  % \item
   %   $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
-%\end{itemize}
+  % \end{itemize}
   (i) $\bar v > 0$; (ii) $\psi(z) < 0$ on $z\in (0,\bar v)$; and (iii) $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
@@
     if $\lambda \in (0,\bar v)$, then $0<\lambda \leq v_t(\lambda)<\bar v $ and
-\begin{align}\label{CSBP: int}
+    \begin{align}
+      \label{CSBP: int}
     \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0;
@@
 
-    Step 2. We will show that, for each $x \geq 0$ there exists a constant
-    $c_1>0$ such that
+  Step 2. We will show that, for each $x \geq 0$ there exists a constant $c_1>0$ such that
   \[
@@
   \begin{align}
-    &\mathbf P_{x}(0<W_t \leq k_t)
-    = \mathbf P_{x}( e^{-k_t^{-1}W_t}\geq e^{-1},W_t > 0)
-    \\&\leq e \mathbf P_{x}[e^{-k_t^{-1} W_t};W_t > 0]
-    =  e\big(\mathbf P_x[e^{-k_t^{-1} W_t}]-\mathbf P_x(W_t = 0)\big)
-    \\ &= e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
+    & \mathbf P_{x}(0<W_t \leq k_t)
+      = \mathbf P_{x}( e^{-k_t^{-1}W_t}\geq e^{-1},W_t > 0) \\
+    & \leq e \mathbf P_{x}[e^{-k_t^{-1} W_t};W_t > 0]
+      =  e\big(\mathbf P_x[e^{-k_t^{-1} W_t}]-\mathbf P_x(W_t = 0)\big) \\ 
+    & = e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
       \leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big),
@@
 
-    Step 3. We will show that there exist
-    $c_2, \delta_1, t_0 > 0$ such that
+  Step 3. We will show that there exist $c_2, \delta_1, t_0 > 0$ such that
   \[
     |\bar v_t-\bar v|
-    \leq c_2e^{-\delta_1 t},    \quad t\geq t_0.
+    \leq c_2e^{-\delta_1 t}
+    , \quad t\geq t_0.
   \]
@@
   According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
-%\[
+  % \[
   %   t_0
   %   := \int^\infty_{z_0} \frac{dz}{\psi(z)} < \infty.
-%\]
+  % \]
   $t_0 := \int^\infty_{z_0}\psi(z)^{-1}dz<\infty$.
@@
   \begin{align}
-    &t-t_0 =
+    & t - t_0 =
       \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)}
-    =\int_{\bar v_t}^{z_0} \frac{dz}{\psi(z)}
-    \\ &\leq \int_{\bar v_t}^{z_0} \frac{dz}{(z-\bar v)\tau}
+      = \int_{\bar v_t}^{z_0} \frac{dz}{\psi(z)} \\ 
+    & \leq \int_{\bar v_t}^{z_0} \frac{dz}{(z-\bar v)\tau}
       = \frac{1}{\tau} \big(\log (z_0-\bar v) - \log(\bar v_t-\bar v)\big).
@@
   Rearranging, we get
-%\[
+  % \[
   $
@@
   $ for all $t\geq t_0$.
-%\]
+  % \]
   This implies the desired result in this step.
 
-    Step 4: We will show that there exist $c_3, \delta_2, t_1>0$ such that
+  Step 4: 
+  We will show that there exist $c_3, \delta_2, t_1>0$ such that
   \[
@@
   Define
-%\[
+  % \[
   %   \rho_t := 1+ \frac{\log k_t}{t\alpha}, \quad t\geq 0.
-%\]
+  % \]
   $\rho_t := 1+(\log k_t)/(t\alpha)$ for all $t\geq 0$.
   % According to the fact that
-%\[
+  % \[
   %   k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}, \quad t\geq 0,
-%\]
-By the fact that $k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}$ for  all $t\geq 0$
-    and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$,
-    we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
-    Since the $L\log L$ condition is satisfied, we have (see \cite{LiuRenSong2009Llog} for
- example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate positive random variable. This implies that
-\[
-    v_t(e^{-\alpha t}) = -\log \mathbf P_1[e^{-W_t}]\xrightarrow[t\to \infty]{} - \log \mathbf P_{1}[e^{-W_\infty}] =: z^* \in (0,\infty).
-\]
-    The $L \log L$ condition also guarantees that (see again \cite{LiuRenSong2009Llog}
-    for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s. in $\mathbf P_1$. This and the non-degeneracy of $W_\infty$ imply that
-\[
-    z^*=-\log \mathbf P_1[e^{-W_\infty}] < -\log \mathbf P_1(W_\infty = 0) = \bar v.
+  % \]
+  By the fact that $k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}$ for  all $t\geq 0$ and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
+  Since the $L\log L$ condition is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate positive random variable.
+This implies that
+\[
+  v_t(e^{-\alpha t}) 
+  = -\log \mathbf P_1[e^{-W_t}]\xrightarrow[t\to \infty]{} - \log \mathbf P_{1}[e^{-W_\infty}] 
+  =: z^* \in (0,\infty).
+\]
+The $L \log L$ condition also guarantees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.
+in $\mathbf P_1$.
+This and the non-degeneracy of $W_\infty$ imply that
+\[
+  z^*
+  = -\log \mathbf P_1[e^{-W_\infty}] 
+  < -\log \mathbf P_1(W_\infty = 0) = \bar v.
 \]
@@
 \begin{align}
-    t& =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
-    = \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)}
-     \\&= \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
+  t 
+  & =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
+    = \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)} \\
+  & = \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
 \end{align}
@@
 \[
-    \int_{v_{\rho_t t}(e^{-\alpha \rho_tt})}^{z_0} \frac{dz}{-\psi(z)} \xrightarrow[t\to \infty] {}\int_{z^*}^{z_0} \frac{dz}{-\psi(z)}.
+  \int_{v_{\rho_t t}(e^{-\alpha \rho_tt})}^{z_0} \frac{dz}{-\psi(z)} 
+  \xrightarrow[t\to \infty] {} \int_{z^*}^{z_0} \frac{dz}{-\psi(z)}.
 \]
@@
 \begin{align}
-    &t\leq  \rho_t t + O(1)+ \int_{z_0}^{v_t(k_t^{-1}e^{-\alpha t})} \frac{dz}{(\bar v-z)(\tau - \epsilon)}
-    \\&=  \rho_t t +O(1)- \frac{1}{\tau-\epsilon}\Big( \log \big(\bar v-v_t(e^{-\alpha \rho_t t})\big) - \log(\bar v-z_0)\Big).
+  & t 
+    \leq  \rho_t t + O(1) + \int_{z_0}^{v_t(k_t^{-1}e^{-\alpha t})} \frac{dz}{(\bar v-z)(\tau - \epsilon)} \\
+  & =  \rho_t t +O(1)- \frac{1}{\tau-\epsilon}\Big( \log \big(\bar v-v_t(e^{-\alpha \rho_t t})\big) - \log(\bar v-z_0)\Big).
 \end{align}
@@
 \[
-    e^{-t(\tau - \epsilon)} \geq e^{-\rho_t t(\tau - \epsilon)+O(1)}(\bar v - v_t(e^{-\alpha \rho_t t})).
-\]
-    Therefore, there exist
-    $c_3>0$ and $t_1>0$ such that for all $t\geq t_1$,
-\[
-    \bar v - v_t(k_t^{-1} e^{-\alpha t}) \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
+  e^{-t(\tau - \epsilon)} 
+  \geq e^{-\rho_t t(\tau - \epsilon)+O(1)}(\bar v - v_t(e^{-\alpha \rho_t t})).
+\]
+Therefore, there exist $c_3>0$ and $t_1>0$ such that for all $t\geq t_1$,
+\[
+  \bar v - v_t(k_t^{-1} e^{-\alpha t}) 
+  \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
   \leq c_3k_t^{\frac{\tau - \epsilon}{\alpha}}.
@@
 
-    Finally, by Steps 2-4, we have for each $x\geq 0$, there exist
-     $c_4, \delta_3, t_2 > 0$ such that
-\[
-    \mathbf P_{x}(0< W_t\leq k_t) \leq
-    c_4(k_t^{\delta_3}+e^{-\delta_3 t}),\quad t\geq t_2.
+Finally, by Steps 2-4, we have for each $x\geq 0$, there exist $c_4, \delta_3, t_2 > 0$ such that
+\[
+  \mathbf P_{x}(0< W_t\leq k_t) 
+  \leq c_4(k_t^{\delta_3}+e^{-\delta_3 t})
+  , \quad t\geq t_2.
 \]
@@
 
+% ** Moments for super-OU processes
 \subsection{Moments for super-OU processes}
 \label{sec: Moments for super-OU processes}
-    In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, 
-    where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
+In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
 Recall that the operator $\mathcal{I}^t_s$ is defined in \eqref{Ist}.
@@
   \begin{align}
-    &\big|\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)\big|
-    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^t\langle g,X_t\rangle}])d\theta\Big|
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iP^\alpha_t (\theta g),\mu \rangle}|d\theta
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iP^\alpha_t(\theta g)|,\mu\rangle d\theta
-    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
+    & \big|\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)\big|
+      \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^t\langle g,X_t\rangle}])d\theta\Big| \\
+    & \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iP^\alpha_t (\theta g),\mu \rangle}|d\theta
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iP^\alpha_t(\theta g)|,\mu\rangle d\theta \\ 
+    & \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
       \qedhere
@@
 \end{proof}
-\begin{lem}\label{lem: temp}
-    For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists $C > 0$ such that
-       for all $\kappa \in \mathbb Z_+ $, $\lambda > 0$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
+\begin{lem}
+  \label{lem: temp}
+  For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists $C > 0$ such that for all $\kappa \in \mathbb Z_+ $, $\lambda > 0$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
   \[
@@
 \end{lem}
+
 \begin{proof}
@@
 \begin{align}
-    &\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    = \mathbb P_\mu \Big[\mathbb P_\mu\big[|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r\big]\Big]
-    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle P_{t-s}^\alpha g, X_{s-r}\rangle - \langle P_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
-    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
+  & \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
+    = \mathbb P_\mu \Big[\mathbb P_\mu\big[|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r\big]\Big] \\
+  & = \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle P_{t-s}^\alpha g, X_{s-r}\rangle - \langle P_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big] \\
+  & = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
   % \\&
-    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
-    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
-    \\&\leq \mathbb P_\mu [ \langle Rh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
-    \\& =  \langle P_r^\alpha Rh,\mu\rangle \bigg(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\bigg)
+  \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big] \\
+  & \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big] \\
+  & \leq \mathbb P_\mu [ \langle Rh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
+  \\ & =  \langle P_r^\alpha Rh,\mu\rangle \bigg(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\bigg)
   \\ & \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg),
@@
 \begin{align}
-    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
-    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda) d\lambda
-    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^s\langle g, X_t\rangle|> \lambda) d\lambda
-    \\& \leq c^{1+\gamma} + C_0  e^{\alpha r}(1+\gamma)\int_c^\infty \bigg(\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta}+\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2}\bigg)\lambda^{\gamma}d\lambda
-    \\&\leq c^{1+\gamma} e^{\alpha r} + C_0e^{\alpha r}(1+\gamma)\Big(  \frac{e^{(1+\beta)(t-s)(\alpha- \kappa b)}}{(\beta - \gamma)c^{\beta - \gamma}}  + \frac{e^{2(t-s)(\alpha- \kappa b)}}{(1 - \gamma)c^{1 - \gamma}} \Big).
+  & \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
+    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda) d\lambda \\ 
+  & \leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^s\langle g, X_t\rangle|> \lambda) d\lambda \\
+  & \leq c^{1+\gamma} + C_0  e^{\alpha r}(1+\gamma)\int_c^\infty \bigg(\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta}+\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2}\bigg)\lambda^{\gamma}d\lambda \\
+  & \leq c^{1+\gamma} e^{\alpha r} + C_0e^{\alpha r}(1+\gamma)\Big(  \frac{e^{(1+\beta)(t-s)(\alpha- \kappa b)}}{(\beta - \gamma)c^{\beta - \gamma}}  + \frac{e^{2(t-s)(\alpha- \kappa b)}}{(1 - \gamma)c^{1 - \gamma}} \Big).
 \end{align}
@@
 \begin{align}
-    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
+  & \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
     \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
@@
 \begin{align}
-    &(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r
-    = (t-s)\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b)
-    \\&\leq t\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b).
+  & (1+\beta)(t-s)(\alpha- \kappa b) + \alpha r
+    = (t-s)\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b) \\
+  & \leq t\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b).
 \end{align}
@@
 For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write
-%\[
+% \[
 $
-    \|Y\|_{\mathbb P;p}:= \mathbb P[|Y|^p]^{1/p}.
-%\]
+\|Y\|_{\mathbb P;p}
+:= \mathbb P[|Y|^p]^{1/p}.
+% \]
 $
@@
 \begin{align}
-    &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+  & \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
   % \\ &
-        \leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
-    + |\langle P^\alpha_t g,\mu\rangle|
-    \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
+         \leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma} + |\langle P^\alpha_t g,\mu\rangle|
+  \\ & \leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
 \end{align}
@@
 
-\section{Proofs of main results}\label{proofs of main results}
+% * Proofs of main results
+\section{Proofs of main results}
+\label{proofs of main results}
 In this section, we will prove the main results of this paper. Recall that $\mathcal{M}_c(\mathbb{R}^d)$ is the space of all finite Borel measures of compact support on $\mathbb{R}^d$.
@@
 
+% ** The large branching rate regime: law of large numbers
 \subsection{The large branching rate regime: law of large numbers}
@@
 \begin{proof}
-    Put$\bar{f}:=(L+ab)f$.
+  Put$\bar{f} :=(L+ab)f$.
   It follows easily from Ito's formula that
-\begin{equation}\label{Theorem55}
-    P_t^{ab}f(x)= f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d,
+\begin{equation}
+  \label{Theorem55}
+  P_t^{ab}f(x)
+  = f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d,
 \end{equation}
@@
   \label{martingale1}
-    &\quad\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
-%    \\&
-    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
-    \\&=e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du
+  & \quad\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
+  % \\ &
+         =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big] \\
+  & =e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du
   % \\&\quad 
-    -\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
+  - \int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
 \end{align}
@@
 \begin{align}
-    &\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle P_{u-s}^{ab}\bar{f},X_s\rangle~du\\
-    &=e^{-(\alpha-ab)s}\Big\langle\int_0^{t-s}P_{u}^{ab}\bar{f}~du,X_s\Big\rangle=e^{-(\alpha-ab)s}\left(\langle P_{t-s}^{ab}f,X_s\rangle-\langle
-    f,X_s\rangle\right)\\
-    &=e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-e^{-(\alpha-ab)s}\langle
+  & \int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle P_{u-s}^{ab}\bar{f},X_s\rangle~du\\
+  & = e^{ - ( \alpha - ab ) s } \Big \langle \int_0^{t-s} P_{u}^{ab} \bar{f}~ du, X_s \Big \rangle
+    = e^{-(\alpha-ab)s}\left(\langle P_{t-s}^{ab}f,X_s\rangle-\langle
+    f, X_s \rangle \right) \\
+  & = e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle - e^{ - ( \alpha - ab ) s} \langle
     f,X_s\rangle.
@@
 
-\begin{lem}\label{lemma26}
+\begin{lem}
+  \label{lemma26}
   For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
 Moreover, if $\alpha\beta>|p|b(1+\beta)$, then, for all $\gamma\in (0, \beta)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
-%\[
+  % \[
   $
   H_{\infty}^p
-    :=\lim_{t\rightarrow \infty}H_t^p
-%\]
+  := \lim_{t\rightarrow \infty}H_t^p
+  % \]
   $
@@
   \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
-    =C_{\gamma, \mu, p}, \quad t\geq 0.
+  = C_{\gamma, \mu, p}
+  , \quad t\geq 0.
 \]
@@
 \[
-	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
-	\leq\|H_t^p\|_{\mathbb P_\mu;1+\gamma_0}
-	<C_{\gamma_0, \mu, p},
+	\| H_t^p \|_{\mathbb P_\mu;1+\gamma}
+	\leq \| H_t^p \|_{\mathbb P_\mu;1+\gamma_0}
+  < C_{\gamma_0, \mu, p},
 	\quad t\geq 0.
@@
 
-\begin{lem}\label{lem: control of wt}
+\begin{lem}
+  \label{lem: control of wt}
   Let $\mu\in \mathcal M_c(\mathbb R^d)$.
@@
 	& \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
-	\\&\leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
-	\\& \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
-%	\\&
+	\\ & \leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
+	\\ & \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
+  %	\\ &
          \leq C_2e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
@@
     f
-    =\sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
-    =:\sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\widetilde{f}.
+    = \sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
+    =: \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\widetilde{f}.
   \end{equation}
@@
   \begin{align}
-    &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
+    & e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
       \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \widetilde{f},X_t\rangle,
@@
   \end{align}
-	According to Lemma \ref{lemma26},
-	we have
+	According to Lemma \ref{lemma26}, we have
 \begin{equation}
@@
 Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa < \frac{\alpha \beta}{b(1+\beta)}$.
-	We will show that for each $\gamma \in (0,\beta)$ there exist
- $C_1,\delta_1 > 0$ such that
+We will show that for each $\gamma \in (0,\beta)$ there exist $C_1,\delta_1 > 0$ such that
 \[
@@
 For $a \geq 0$, $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
-%\begin{equation}
-\begin{align*}
-	L_t^{g,a}&:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,\\
-%\end{equation}
+% \begin{equation}
+\begin{align}
+	L_t^{g,a}
+  & :=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,\\
+  % \end{equation}
   % and
-%\begin{equation}
+  % \begin{equation}
   Y_t^{g,a}
-    &:=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
-%\end{equation}
-\end{align*}
+  & :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
+  % \end{equation}
+\end{align}
 Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$.
@@
   J_t
-    =e^{-(a_0-\kappa_f)bt} (M_t^{\widetilde{f}, a_0}+L_t^{\widetilde{f}, a_0}),
+  = e^{-(a_0-\kappa_f)bt} (M_t^{\widetilde{f}, a_0}+L_t^{\widetilde{f}, a_0}),
   \quad t\geq 0.
@@
 \begin{equation}
-    \|e^{-(\alpha-a_0 b)t}\langle \widetilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
+  \| e^{-(\alpha-a_0 b)t}\langle \widetilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
   \leq C_6 e^{-\delta_3 t},
@@
 \begin{align}
-    &\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq\|Y_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \\&
-    \leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\widetilde{f}+a_0 b\widetilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
+  & \|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq\|Y_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma} \\
+  & \leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\widetilde{f}+a_0 b\widetilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
 \end{align}
@@
 	\lim_{t\rightarrow\infty} e^{-(a_0-\kappa_f)bt}M_t^{\widetilde{f},a_0}
-	=0,
+	= 0,
 	\quad \mathbb P_\mu\text{-a.s.}.
@@
 
+% *** The critical branching rate regime
 \subsection{The critical branching rate regime}
@@
 Recall that $\mathcal I_s^t$ is defined in \eqref{Ist}.
-
-\begin{lem}\label{lem: mainlemma}
+\begin{lem}
+  \label{lem: mainlemma}
   Let $f\in \mathcal{P}$ be non-trivial and satisfy $\alpha\beta\leq \kappa_fb(1+\beta)$.
@@
     \gamma_{t,k}
-    :=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha (k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
+    := \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha (k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{equation}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
-%\[
+% \[
 %   \mathbf{E}(e^{i\theta\zeta_k})
 %   =\exp(m_k[\theta f]),\quad \theta \in \mathbb R.
-%\]
+% \]
 $\theta\mapsto \exp(m_k[\theta f])$.
@@
   J_1(t,k,\epsilon)
-    &:= \mathbb{P}_{\mu}\big[|\langle Z'''_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
+  & := \mathbb{P}_{\mu}\big[|\langle Z'''_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
   \\ J_2(t,k,\epsilon)
-    &:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|; A_{t-k-1}(\epsilon)\big],
+  & := \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|; A_{t-k-1}(\epsilon)\big],
   \\ J_3(t,k, \epsilon)
-    &:=2\mathbb{P}_{\mu}(A_{t-k-1}(\epsilon)\Delta D^c),
-    \\\theta_{t,k}
-    &:= (e^{\alpha( k+1)}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
+  & :=2\mathbb{P}_{\mu}(A_{t-k-1}(\epsilon)\Delta D^c),
+  \\ \theta_{t,k}
+  & := (e^{\alpha( k+1)}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
 \end{align}
@@
   \label{eq: need1}
-    &\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}|\mathscr{F}_{t-k-1}]
-    =\mathbb{P}_{\mu}[e^{i\theta_{t,k}\langle P^\alpha_k f,X_{t-k}\rangle-i\theta_{t,k}\langle P^\alpha_{k+1} f, X_{t-k-1}\rangle}|\mathscr{F}_{t-k-1}]
-    \\&=e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}
+  & \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}|\mathscr{F}_{t-k-1}]
+    =\mathbb{P}_{\mu}[e^{i\theta_{t,k}\langle P^\alpha_k f,X_{t-k}\rangle-i\theta_{t,k}\langle P^\alpha_{k+1} f, X_{t-k-1}\rangle}|\mathscr{F}_{t-k-1}] \\
+  & =e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}
     =e^{\langle (Z_1 + Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
@@
 From Proposition \ref{prop: alpha stable rv}.(1), we have
-%\begin{equation}
-%\label{eq: need2}
+% \begin{equation}
+%   \label{eq: need2}
 %   \operatorname {Re} m_t[f] < 0.
-%\end{equation}
+% \end{equation}
 $\operatorname {Re} m_t[f] < 0$. 
@@
 Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact
-%\[
+% \[
 %   |e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
-%\]
-$|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$,
-    we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+% \]
+$|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
   \label{eq: inequality that will used later}
-    &\big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c\big]\big|
-%    \\& 
-    \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; A_{t-k-1}(\epsilon)| \mathscr F_{t-k-1}]\big| + 2\mathbb P_\mu(A_{t-k-1}(\epsilon) \Delta D^c| \mathscr F_{t-k-1})\Big]
-    \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon)
-    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (Z_1+Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
-    \\& \leq \mathbb{P}_{\mu}\big[|\langle (Z_1+Z'''_1)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
-    \\&\leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon).
+  & \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c\big]\big|
+  % \\ & 
+         \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big] \\
+  & \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; A_{t-k-1}(\epsilon)| \mathscr F_{t-k-1}]\big| + 2\mathbb P_\mu(A_{t-k-1}(\epsilon) \Delta D^c| \mathscr F_{t-k-1})\Big] \\
+  & = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon) \\
+  & \leq \mathbb{P}_{\mu}\big[|e^{\langle (Z_1+Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon) \\
+  & \leq \mathbb{P}_{\mu}\big[|\langle (Z_1+Z'''_1)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon) \\
+  & \leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon).
 \end{align}
@@
   \leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
-    \\&\leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf
-    \\&\leq\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
-%    \\&
+  \\ & \leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf
+  \\ & \leq\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
+  % \\ &
          \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
@@
   \label{eq: estimate of J1}
-    J_1(t,k,\epsilon)&
-    \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}\mathbb{P}_{\mu}[\langle RQf,X_{t-k-1}\rangle]\\
+  J_1(t,k,\epsilon)
+  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}\mathbb{P}_{\mu}[\langle RQf,X_{t-k-1}\rangle]\\
   & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)},
@@
 We will show that for $\epsilon>0$ small enough there exist $C_2, \delta_2>0$ such that
-%\begin{equation}\label{eq:31step3}
+% \begin{equation}\label{eq:31step3}
 $
@@
 \quad k\geq 0, t\geq k+1.
-%\end{equation}
+% \end{equation}
 $
@@
 \begin{align}
-	&m_k[g]
+	& m_k[g]
    = \eta \int_k^{k+1}e^{-\alpha s}~ds\int_{\mathbb R^d} (-iP_{s}^\alpha g(x))^{1+\beta} \varphi(x)~dx\\
-       &=\eta \int_0^1e^{-\alpha (k+s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha g)^{1+\beta}\varphi(x)~dx\\
-       &=e^{-\alpha(k+1)} \cdot \eta \int_0^{1}e^{\alpha(1- s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha        g(x))^{1+\beta} \varphi(x)~dx\\
-      &=e^{-\alpha(k+1)}\langle \eta \int_0^1P_{1-s}^{\alpha}(-iP_{s+k}^\alpha g(x))^{1+\beta}~ds, \varphi \rangle
+  & = \eta \int_0^1e^{-\alpha (k+s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha g)^{1+\beta}\varphi(x)~dx\\
+  & = e^{-\alpha(k+1)} \cdot \eta \int_0^{1}e^{\alpha(1- s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha        g(x))^{1+\beta} \varphi(x)~dx\\
+  & =e^{-\alpha(k+1)}\langle \eta \int_0^1P_{1-s}^{\alpha}(-iP_{s+k}^\alpha g(x))^{1+\beta}~ds, \varphi \rangle
   % \\&
@@
   \langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]
-%    \\&
-    &= \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha (k+1)}\langle  Z_1P^\alpha_k f,\varphi\rangle
-    \\&=e^{-\alpha (k+1)}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big),
+  % \\ &
+    & = \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha (k+1)}\langle  Z_1P^\alpha_k f,\varphi\rangle
+  \\ & =e^{-\alpha (k+1)}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big),
 \end{align}
@@
   \label{eq: prevJ2}
-    J_2(t,k,\epsilon)&
-    = \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|;A_{t-k-1}(\epsilon)\big]
-    \\&=e^{-\alpha( k+1)}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1P^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
-    &\leq e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
+  J_2(t,k,\epsilon)
+  & = \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|;A_{t-k-1}(\epsilon)\big] \\ 
+  & =e^{-\alpha( k+1)}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1P^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
+  & \leq e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
 \end{align}
@@
 \begin{align}
-    &\mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t}\rangle\right|\right]
-    \leq \|\langle \operatorname{Re} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}}
-    \\& \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_3 e^{\frac{\alpha t}{1+\gamma}}.
+  & \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t}\rangle\right|\right]
+    \leq \|\langle \operatorname{Re} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} \\
+  & \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_3 e^{\frac{\alpha t}{1+\gamma}}.
 \end{align}
@@
   & J_2(t,k, \epsilon)
-    \leq  e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
-    \\&\leq C_3 e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)}
-    \\&= C_3 e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
-%    \\&
+    \leq  e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right] \\
+  & \leq C_3 e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)} \\
+  & = C_3 e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
+  % \\ &
          \leq C_3 e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
@@
 We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_3>0$ such that for all $k\geq0, t\geq k+1$,
-%\begin{equation}\label{ineq: control of J3}
+% \begin{equation}\label{ineq: control of J3}
 $
 J_3(t,k,\epsilon)\leq C_4e^{-\delta_3 (t-k)}.
-%\end{equation}
+% \end{equation}
 $
 In fact, we have  for all $t\geq 0, \epsilon >0$,
-%\begin{align}
+% \begin{align}
 %   &
 \[   
-\mathbb P_{\mu}(A_{t}(\epsilon), D) = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
-%    \\&
+  \mathbb P_{\mu}(A_{t}(\epsilon), D) 
+  = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
+  % \\ &
   = \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
   \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
-%\end{align}
+  % \end{align}
 \]
@@
 \begin{equation}
-    \mathbb P_\mu(A_t(\epsilon)^c,D^c) \leq   \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\|\leq e^{ - \epsilon t}) \leq C_5 (e^{-\epsilon \delta_4 t}+e^{-\delta_4 t}).
+  \mathbb P_\mu(A_t(\epsilon)^c,D^c) 
+  \leq \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\| 
+  \leq e^{ - \epsilon t}) \leq C_5 (e^{-\epsilon \delta_4 t}+e^{-\delta_4 t}).
 \end{equation}
@@
   \begin{align}
-    &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+    & \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
       %     \\&
@@
   \begin{align}
-    &J^{\theta f}_1(k,t,\epsilon)
-    \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}
-    \\& \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}.
+    & J^{\theta f}_1(k,t,\epsilon)
+      \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)} \\
+    & \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{ - ( \alpha \frac{ \rho} {1 + \beta} - \epsilon \frac{ 1 + \beta + \rho}{ 1 + \beta}) (t-k-1)}.
 \end{align}
@@
 \[
-	Z_1( \pm \theta g) = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[\pm g].
+	Z_1( \pm \theta g) 
+  = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[\pm g].
 \]
 Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$,
-%\[
+% \[
 $
@@
 $
-%\]
+% \]
 According to this and \eqref{eq: right bound for J2},
@@
 
-\begin{prop}\label{cor: indepedent of the limit zeta for critical and small}
+\begin{prop}
+  \label{cor: indepedent of the limit zeta for critical and small}
   Suppose that $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq\kappa_fb(1+\beta)$.
@@
   \begin{align}
-    &a_{k-1} - a_k
+    & a_{k-1} - a_k
     % \\&
-    =\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1} \Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
+    =\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big] \\
+    & =\mathbb{P}_{\mu}(D^c)^{-1} \Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
   \end{align}
@@
   \begin{align}
-    |a_{k-1}- a_k|
-    &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
-%    \\& 
+    | a_{k-1} - a_k|
+    & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
+    % \\ & 
     \leq C e^{-\delta(t-k)}.
@@
   \begin{align}
-    \text{LHS of \eqref{32corollary}}&= \left|a_{-1}-a_n\right|
-    \leq\sum_{k=0}^n\left|a_{k-1}-a_k\right|
+    \text{LHS of \eqref{32corollary}}
+    & = \left|a_{-1}-a_n\right|
+    \leq \sum_{k=0}^n\left|a_{k-1}-a_k\right|
     \leq \sum_{k=0}^n C e^{-\delta(t-k)}.
@@
   \begin{align}
-    &(t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle
-    \\ &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big) +
-    \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
-    \\&=:I_1(t)+I_2(t) + I_3(t),
+    &(t\|X_t\|)^{-\frac{1}{1+\beta}} \langle f,X_t \rangle \\
+    & = \sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle} {(t\|X_t\|)^{\frac{1}{1+\beta}}} + \Big( \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac {\mathcal I_{t-k-1}^{t-k} \langle f, X_t\rangle} {(t\|X_t\|)^{\frac{1}{1+\beta}}} + \frac {\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle} {(t\|X_t\|)^{\frac{1}{1+\beta}}} \Big) + \frac {\langle P^\alpha_tf,X_0\rangle} { ( t \| X_t \| )^{ \frac { 1 } { 1 + \beta } } } \\
+    & =: I_1(t) + I_2(t) + I_3(t),
       \quad t\geq t_0.
@@
     \widetilde I_1(t)
-    :=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
+    := \sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k} \langle f ,X_t\rangle} {(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}} },
     \quad t\geq t_0.
@@
   Fix $\theta\in \mathbb R$.
-    Taking $\theta_k=t ^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small},
-    we get that there exist $C_1,\delta_1>0$ such that,
-\begin{align}
-    \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq \frac{C_1}{t^{\delta_1}},
+  Taking $\theta_k=t ^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small}, we get that there exist $C_1,\delta_1>0$ such that,
+  \begin{align}
+    \Big| \mathbb{\widetilde{P}}_{\mu}  [ e^{ i  \theta \widetilde{I}_1(t) } ] - \exp \Big( \frac { 1 } { t } \sum_{k=0}^{\lfloor t - \ln t \rfloor} m_k [ \theta f ] \Big) \Big| 
+    \leq \frac{C_1}{t^{\delta_1}},
     \quad t\geq t_0.
@@
   Therefore, we only need to prove
- \begin{equation}\label{toprove-1}
+  \begin{equation}
+    \label{toprove-1}
     |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde{I}_1(t)}]|
@@
   and
-\begin{equation}\label{toprove-2}
+  \begin{equation}
+    \label{toprove-2}
     I_i(t)\xrightarrow[t\to \infty]{d} 0,
@@
   By \cite[Lemma 3.4.3]{Durrett2010Probability},
-\begin{equation}\label{ineq: control of I1t}
+  \begin{equation}
+    \label{ineq: control of I1t}
     |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde{I}_1(t)}]|
@@
     \label{def: Dtk}
-    \mathcal{D}_{t,k}:=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
+    \mathcal{D}_{t,k}
+    :=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
   \end{equation}
@@
     \label{eq: prob of Dtkc}
-    &\mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
+    & \mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
       %     \\&
-    \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
-    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]
-    \\&\quad 
-    +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
-    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}
-    \\&\quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
-    \\&\leq C_3 e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C_3 e^{-\delta_3(t-k-1)}.
+    \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}) \\
+    & \leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|] \\
+    & \quad 
+      + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c) \\
+    & \leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma} \\
+    & \quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}) \\
+    & \leq C_3 e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C_3 e^{-\delta_3(t-k-1)}.
   \end{align}
@@
     \label{eq: control of Ykt}
-    &\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \\&\leq|\theta|t^{-\frac{1}{1+\beta}} \mathbb{\widetilde{P}}_{\mu}\bigg[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot\Big|\frac{1}{(e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\bigg]
-    \\&\leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
+    & \mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big] \\
+    & \leq|\theta|t^{-\frac{1}{1+\beta}} \mathbb{\widetilde{P}}_{\mu}\bigg[|\mathcal I_{t-k-1}^{t-k}\langle f , X_t\rangle | \cdot \Big| \frac {1} {(e^{\alpha(k+1)} \| X_{t-k-1}\| )^{ \frac {1} {1+\beta} } } - \frac {1} {\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\bigg] \\
+    & \leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
   \end{align}
@@
     K_{t,k}
-    :=\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}.
+    := \Big| \frac {H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}} {H_t^{\frac{1}{1+\beta}} H_{t-k-1}^{ \frac {1} {1+\beta} }} \Big| \mathbf{1}_{\mathcal{D}_{t,k}}.
   \end{equation}
@@
     H_t
-    &\geq H_{t-k-1}- e^{-\eta_0(t-k-1)}
+    & \geq H_{t-k-1}- e^{-\eta_0(t-k-1)}
       \geq 2e^{-\eta_1(t-k-1)}-e^{-\eta_0(t-k-1)}
@@
   \begin{align}
-    &\Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
-    \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|
-    \\&\leq \frac{1}{1+\beta} \max\{e^{\eta_1 (t-k-1)}, \frac{1}{2}e^{\eta_1(t-k-1)}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0(t-k-1)}
-    \\&\leq \frac{1}{1+\beta} e^{\eta_1 (t-k-1)} e^{-\eta_0(t-k-1)}
-    =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)}
+    & \Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
+      \leq \frac {1} {1+\beta} \max \Big \{ H_t^{-\frac{\beta}{1+\beta} }, H_{t-k-1}^{ -\frac{\beta}{1+\beta} } \Big\} \left| H_t - H_{t-k-1} \right| \\
+    & \leq \frac{1}{1+\beta} \max\{e^{\eta_1 (t-k-1)}, \frac{1}{2}e^{\eta_1(t-k-1)}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0(t-k-1)} \\
+    & \leq \frac{1}{1+\beta} e^{\eta_1 (t-k-1)} e^{-\eta_0(t-k-1)}
+    = \frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)}
   \end{align}
@@
   \end{equation}
-    By Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and \eqref{ineq: control of Kkt},
-    there exist $C_6>0$ such that for all $k\geq 0$ and $t\geq k+1$,
+  By Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and \eqref{ineq: control of Kkt}, there exist $C_6>0$ such that for all $k\geq 0$ and $t\geq k+1$,
   \begin{align}
     \label{eq: Y in D}
-    &\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \leq C_5|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
-    \\&\leq \frac{C_5}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
-    \\&\leq \frac{C_5}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta_0 - 3\eta_1)(t-k - 1)}
-    \\&\leq C_6 e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}
-    \\&= C_6 e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)},
+    & \mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
+    \leq C_5 | \theta | e^{-\frac{\alpha}{1+\beta}t} \mathbb{\widetilde{P}}_{\mu} \big[ | \mathcal{I}_{t-k-1}^{t-k}\langle f, X_t\rangle| \big] e^{-(\eta_0 - 3\eta_1)(t-k-1)} \\
+    & \leq  \frac{C_5} {\mathbb{P}_{\mu}(D^c)} | \theta | e^{-\frac{\alpha} {1+\beta}t}\mathbb{P}_{\mu} \big[ |\mathcal{I}_{t-k-1}^{t-k}\langle f, X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)} \\
+    & \leq \frac{C_5} {\mathbb{P}_{\mu}(D^c)} | \theta | e^{ - \frac{\alpha} {1 + \beta} t} \|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta_0 - 3\eta_1)(t-k - 1)} \\
+    & \leq C_6 e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)} \\
+    & = C_6 e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)},
   \end{align}
@@
   We will show that there exist $C_7, \delta_5> 0$ such that for $t$ large enough,
-\begin{equation}\label{domi-difference of Is}
-    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde{I}_1(t)}]|
+  \begin{equation}
+    \label{domi-difference of Is}
+    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\widetilde{P}}_{\mu} [ e^{ i \theta \widetilde{I}_1(t) } ] |
     \leq C_7 t^{-\delta_5}.
   \end{equation}
-    In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C_8,\delta_6 > 0$ such that
-    for all $k \geq 0$ and $t\geq k+1$ we have,
+  In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C_8,\delta_6 > 0$ such that for all $k \geq 0$ and $t\geq k+1$ we have,
   \[
@@
   \begin{align}
-    &\sum_{k=0}^{\lfloor t-\ln t \rfloor} \widetilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
+    & \sum_{k=0}^{\lfloor t-\ln t \rfloor} \widetilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
       \leq C_8\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{-\delta_6(t-k)}
       = C_8 e^{-\delta_6 t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta_6 k}
-%    \\&
+      % \\ &
              \leq C_9 e^{-\delta_6 t}e^{\delta_6 (t-\ln t)}
@@
   \begin{equation}
-    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t}), \quad t\geq0.
+    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
+    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t})
+    , \quad t\geq0.
   \end{equation}
   Therefore,
-\begin{equation}\label{Theorem123}
+  \begin{equation}
+    \label{Theorem123}
     |\mathbb{\widetilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
@@
   \begin{align}
-    &|\mathbb{\widetilde{P}}_{\mu} [ (e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
-    \leq |\theta| \mathbb{\widetilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
-    \\&\leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
-    \\& \leq C_{11} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
-    \\ &\leq C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    &= C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})k}\\
-    &\leq C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})j}\\
-    &\leq C_{13}|\theta| t^{-\frac{1}{2(1+\beta)}}t^{(\frac{\alpha}{1+\gamma}- \frac{\alpha}{1+\beta})},
+    & |\mathbb{\widetilde{P}}_{\mu} [ (e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
+      \leq |\theta| \mathbb{\widetilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big] \\
+    & \leq | \theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big) \\
+    & \leq C_{11} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big) \\
+    & \leq C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    & = C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})k}\\
+    & \leq C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})j}\\
+    & \leq C_{13}|\theta| t^{-\frac{1}{2(1+\beta)}}t^{(\frac{\alpha}{1+\gamma}- \frac{\alpha}{1+\beta})},
       \quad t\geq t_0.
@@
   \begin{align}
-	&|I_3(t)|
+    & |I_3(t)|
       \leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
-	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(te^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
-	\\& = t^{-\frac{1}{1+\beta}} e^{\frac{\beta \alpha t}{1+\beta} - k_fbt} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
+      \leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(te^{\alpha t} H_t)^{\frac{1}{1+\beta}}} \\
+    & = t^{-\frac{1}{1+\beta}} e^{\frac{\beta \alpha t}{1+\beta} - k_fbt} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
 %	\\& 
@@
 
+% *** The small branching rate regime
 \subsection{The small branching rate regime}
@@
 	Let $t_0 > 1$ be large enough so that
-%\[
+  % \[
   $	\lceil t - \ln t\rceil
@@
   $ for all $t\geq t_0$.
-%\]
+  % \]
   Fix $\mu\in \mathcal M_c(\mathbb R^d)$ and write
   \begin{align}
-	&\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-	\\&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+ \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big) +
+    & \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+    \\ & =\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+ \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big) +
 \frac{\langle P^\alpha_t f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-	\\&=:I'_1(t)+I'_2(t)+I'_3(t),
+    \\ & =:I'_1(t)+I'_2(t)+I'_3(t),
          \quad t\geq t_0.
@@
     \widetilde I'_1(t)
- 	:=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
+    := \sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
     \quad t > t_0.
@@
   Fix a $\theta\in \mathbb R$.
-    Taking $\theta_k=\theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small},
-    we get that there exist $C_1,\delta_1 > 0$ such that
+  Taking $\theta_k=\theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small}, we get that there exist $C_1,\delta_1 > 0$ such that
   \begin{align}
@@
   \[
-    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
+    \frac{\alpha \gamma}{1+\gamma} 
+    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} 
+    > 0.
   \]
@@
   \[
-    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
+    \frac{\alpha \gamma}{1+\gamma} 
+    > \eta_0 
+    > \eta_0 - 3\eta_1 
+    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} 
+    > 0.
   \]
@@
   \begin{align}
-    &\mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
-    = \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}\big] + \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}^c \big]
-    \\& \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\widetilde{P}}_{\mu}( \mathcal D_{t,k}^c )
-    \\& \leq C_2 e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-(\eta_0 - 3\eta_1)(t-k)} + Ce^{-\delta_2(t-k)}
-    \\& \leq C_3( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)}).
+    & \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
+      = \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}\big] + \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}^c \big] \\
+    & \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\widetilde{P}}_{\mu}( \mathcal D_{t,k}^c ) \\
+    & \leq C_2 e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-(\eta_0 - 3\eta_1)(t-k)} + Ce^{-\delta_2(t-k)} \\
+    & \leq C_3( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)}).
   \end{align}
@@
     \label{eq: condition for supercritical}
-	&-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})
-    = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta})
-    \\&> \frac{\gamma \alpha}{1+\gamma} - k_f b
+    & -(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})
+      = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta}) \\
+    & > \frac{\gamma \alpha}{1+\gamma} - k_f b
       =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
   \end{align}
-Using this, we have that there exist $C_4,
-    \delta_3 > 0$ such that for $k\geq 0$ and $t\geq k+1$,
+  Using this, we have that there exist $C_4, \delta_3 > 0$ such that for $k\geq 0$ and $t\geq k+1$,
   \begin{align}
@@
   \[
-	q:= - \frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}
+    q
+    := - \frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}
     > \frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta} + \frac{2\epsilon}{1+\beta} > 0.
@@
 	Recall that
-%\[
+  % \[
   %   A_t(\epsilon)
@@
   %   \quad t\geq 0.
-%\]
+  % \]
   $A_t(\epsilon)=\{\|X_t\|>e^{(\alpha-\epsilon )t}\}$.
-By \eqref{lem: control of XT}, there exist
-$C_5,\delta_4>0$ such that
-\begin{align}
-    &|\mathbb{\widetilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
-    \leq 2\mathbb{\widetilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})
-    \\&\leq C_5(e^{-\epsilon\delta_4 t}+e^{-\delta_4 t}),
+  By \eqref{lem: control of XT}, there exist $C_5,\delta_4>0$ such that
+  \begin{align}
+    & |\mathbb{\widetilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
+      \leq 2\mathbb{\widetilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t}) \\
+    & \leq C_5(e^{-\epsilon\delta_4 t}+e^{-\delta_4 t}),
       \quad t\geq t_0.
   \end{align}
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C_6,C_7,C_8>0$ such that for all
-	$t\ge t_0$,
-\begin{align}
-    &\big|\mathbb{\widetilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)}]\big|
-    \leq |\theta| \mathbb{\widetilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)}\big]
-    \\&\leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
-    \\& \leq C_6  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
-    \\ &\leq C_7  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    &\leq C_7 e^{-\frac{\epsilon}{1+\beta} t}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta} + \frac{2\epsilon}{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    &\leq C_7 e^{-\frac{\epsilon}{1+\beta} t} e^{qt} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-qk}\\
-    &\leq C_7 e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\leq C_8 e^{-\frac{\epsilon}{1+\beta} t} t^q.
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C_6,C_7,C_8>0$ such that for all $t\ge t_0$,
+  \begin{align}
+    & \big|\mathbb{\widetilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)}]\big|
+      \leq |\theta| \mathbb{\widetilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)}\big] \\
+    & \leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big) \\
+    & \leq C_6  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big) \\
+    & \leq C_7  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    & \leq C_7 e^{-\frac{\epsilon}{1+\beta} t}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta} + \frac{2\epsilon}{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
+    & \leq C_7 e^{-\frac{\epsilon}{1+\beta} t} e^{qt} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-qk}\\
+    & \leq C_7 e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\leq C_8 e^{-\frac{\epsilon}{1+\beta} t} t^q.
   \end{align}
@@
   \begin{align}
-	&|I'_3(t)|
+    & |I'_3(t)|
       \leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
@@
 \end{proof}
+
+% *** The large branching rate regime: CLT
 \subsection{The large branching rate regime: CLT}
@@
 By Fubini's theorem, we have
-\begin{align}\label{equ: transform of mn}
-    &\bar{m}_n[g]=e^{\alpha(n-1)}\int_0^1 e^{\alpha s}\langle \eta(iI_{s+n-1}g)^{1+\beta}, \varphi\rangle ds
-    \\    &
-    =e^{\alpha(n-1)}\langle \int_0^1 P_s^{\alpha}\langle \eta(iI_{s+n-1}g)^{1+\beta}ds, \varphi\rangle\\
-    &=e^{\alpha(n-1)}\langle \int_0^1 P_{1-s}^{\alpha}\langle \eta(iI_{n-s}g)^{1+\beta}ds, \varphi\rangle=e^{\alpha(n-1)}\langle Z_1(-I_ng),
-    \varphi\rangle,
+\begin{align}
+  \label{equ: transform of mn}
+  & \bar{m}_n[g]
+    = e^{\alpha(n-1)}\int_0^1 e^{\alpha s}\langle \eta(iI_{s+n-1}g)^{1+\beta}, \varphi\rangle ds \\   
+  & = e^{\alpha(n-1)}\langle \int_0^1 P_s^{\alpha}\langle \eta(iI_{s+n-1}g)^{1+\beta}ds, \varphi\rangle\\
+  & =e^{\alpha(n-1)}\langle \int_0^1 P_{1-s}^{\alpha}\langle \eta(iI_{n-s}g)^{1+\beta}ds, \varphi\rangle=e^{\alpha(n-1)}\langle Z_1(-I_ng), \varphi\rangle,
     \quad n\geq 1.
@@
 
-\begin{lem}\label{large-central}
+\begin{lem}
+  \label{large-central}
   For all $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$,
 \begin{align}
-    \bar{\gamma}_{t,n}:=\sum_{p\in\mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}
+  \bar{\gamma}_{t,n}
+  := \sum_{p\in\mathcal{N}} a_p \frac { H^p_{t+n-1} - H^p_{t+n} } { e^{ - ( \alpha - | p | b ) t } ( e^{ - \alpha ( n - 1 ) } \| X_{ t + n - 1 } \| )^{ \frac { 1 } { 1 + \beta } } }
   \xrightarrow[t\to \infty]{d}\bar{\zeta}_n,
 \end{align}
-	where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with
-    characteristic function
-%\begin{align}
+	where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function
+  % \begin{align}
   %   \mathbf{E}[e^{i\theta \bar{\zeta}_n}]=\exp(\bar{m}_n[\theta g]),\quad \theta\in \mathbb{R}.
-%\end{align}
+  % \end{align}
   $\theta\mapsto \exp(\bar{m}_n[\theta g])$.
@@
   \end{align}
-    Put $\theta_{t,p,n}:=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and
-    $A_t(\epsilon):=\{\|X_t\| > e^{(\alpha-\epsilon)t}\}$.
+  Put $ \theta_{ t, p, n} := a_p \frac { e^{ - ( \alpha - | p | b ) n } } { ( e^{ - \alpha ( n - 1 ) } \| X_{ t + n - 1 } \| )^{ \frac { 1 } { 1 + \beta } } } $ and $ A_t(\epsilon):=\{\|X_t\| > e^{(\alpha-\epsilon)t}\}$.
   We have
   \begin{align}
-    \bar{\gamma}_{t,n}=\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p, X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle).
+    \bar{\gamma}_{t,n}
+    =\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p, X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle).
   \end{align}
@@
     J'_1(t,n,\epsilon)
-    &:= \mathbb{P}_{\mu}\big[|\langle Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big],
-	\\ J'_2(t,n,\epsilon)
-	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big],
-	\\ J'_3(t,n, \epsilon)
-	&:=2\mathbb{P}_{\mu}(A_{t+n-1}(\epsilon)\Delta D^c).
+    & := \mathbb{P}_{\mu}\big[|\langle Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big], \\ 
+    J'_2(t,n,\epsilon)
+    & := \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big] \\
+    J'_3(t,n, \epsilon)
+    & := 2\mathbb{P}_{\mu}(A_{t+n-1}(\epsilon)\Delta D^c).
   \end{align}
@@
     \label{eq: need11}
-    &\displaystyle\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}|\mathscr{F}_{t+n-1}]
-    =\mathbb{P}_{\mu}[e^{i\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p,X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle)}|\mathscr{F}_{t+n-1}]
-    \\&=\displaystyle e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
+    & \displaystyle\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}|\mathscr{F}_{t+n-1}]
+      = \mathbb{P}_{\mu}[e^{i\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p,X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle)}|\mathscr{F}_{t+n-1}] \\
+    & = \displaystyle e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
   \end{align}
@@
   According to \eqref{eq: need11} and the fact that
-%\[
+  % \[
   %   |e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
-%\]
+  % \]
   $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$,
@@
     \label{eq: inequality that will used later1}
-    &\big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
+    & \big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
     % \\& 
-    \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]
-    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; A_{t+n-1}(\epsilon)| \mathscr F_{t+n-1}]\big| + 2\mathbb P_\mu(A_{t+n-1}(\epsilon) \Delta D^c| \mathscr F_{t+n-1})\Big]
-    \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}| \mathscr F_{t+n-1}]-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big] + J'_3(t,n,\epsilon)
-    \\&=\mathbb{P}_{\mu}\Big[\big|e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
-    \\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}
- \theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
-    \\&\leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon).
+    \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c | \mathscr F_{t+n-1}]\big|\Big] \\
+    & \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; A_{t+n-1}(\epsilon)| \mathscr F_{t+n-1}]\big| + 2\mathbb P_\mu(A_{t+n-1}(\epsilon) \Delta D^c| \mathscr F_{t+n-1})\Big] \\
+    & = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}| \mathscr F_{t+n-1}]-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big] + J'_3(t,n,\epsilon) \\
+    & = \mathbb{P}_{\mu}\Big[\big|e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon) \\
+    & \leq \mathbb{P}_{\mu}\Big[\big|\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}
+ \theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon) \\
+    & \leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon).
   \end{align}
@@
   We will show that for $\epsilon>0$ small enough, there exist $C_1,\delta_1>0$ such that for all $n\geq 1$ and $t\geq 0$,
-%\begin{align}\label{eq:large rate J1}
-$
-    J'_1(t,n,\epsilon)\leq C_1 e^{-\delta_1(t+n)}.
-    $
-%\end{align}
+  % \begin{align}\label{eq:large rate J1}
+  $ J'_1(t,n,\epsilon)\leq C_1 e^{-\delta_1(t+n)}. $
+  % \end{align}
   Let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
@@
     & |Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
-    \leq R(|\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p|)\mathbf{1}_{A_{t+n-1}(\epsilon)}
-    \\&\leq R \Big(\frac{\sum_{p\in\mathcal{N}}|a_p|e^{-(\alpha-|p|b)n}|\phi_p|}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)
-    \\&\leq \sum_{\rho\in\{\delta_0,1\}}\Big(\frac{e^{-(\alpha-Kb)n}}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)^{1+\beta+\rho}Rh
-    \\&=\sum_{\rho\in\{\delta_0,1\}}e^{-\alpha\frac{1+\beta+\rho}{1+\beta}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha\beta-K(1+\beta)b)n}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}Rh
-    \\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}Rh,
+      \leq R(|\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p|)\mathbf{1}_{A_{t+n-1}(\epsilon)} \\
+    & \leq R \Big( \frac{ \sum_{p\in\mathcal{N} } | a_p | e^{ - ( \alpha - | p | b ) n } | \phi_p | } { \big( e^{ - \alpha ( n - 1 ) } e^{ ( \alpha - \epsilon ) ( t + n - 1 ) } \big)^{ \frac { 1 } { 1 + \beta } } } \Big) \\
+    & \leq \sum_{ \rho \in \{ \delta_0, 1 \} } \Big( \frac { e^{ - ( \alpha - K b ) n } }  { \big( e^{ - \alpha ( n - 1 ) } e^{ ( \alpha - \epsilon ) ( t + n - 1 ) } \big)^{ \frac { 1 } { 1 + \beta } } } \Big)^{ 1 + \beta + \rho } R h \\
+    & = \sum_{ \rho \in \{ \delta_0, 1 \} } e^{ - \alpha \frac{ 1 + \beta + \rho } { 1 + \beta } } e^{ - \frac { 1 + \beta + \rho } { 1 + \beta } ( \alpha \beta - K ( 1 + \beta ) b ) n } e^{ - \frac{ 1 + \beta + \rho } { 1 + \beta } ( \alpha - \epsilon ) ( t + n - 1 ) } R h \\
+    & \leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}Rh,
   \end{align}
@@
     \label{eq: estimate of J11}
-     J'_1(t,n,\epsilon)&
-       \leq  \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle Rh,X_{t+n-1}\rangle]\\
-     & \leq C_1\sum_{\rho\in\{\delta_0,1\}}\exp\Big\{-\Big(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta}\Big)(t+n-1)\Big\}.
+    J'_1(t,n,\epsilon)
+    & \leq  \sum_{ \rho \in \{ \delta_0, 1\} } e^{ - \frac{ 1 + \beta + \rho } { 1 + \beta } ( \alpha - \epsilon ) ( t + n - 1 ) } \mathbb{ P }_{ \mu }[ \langle R h, X_{ t + n - 1 } \rangle] \\
+    & \leq C_1 \sum_{ \rho \in \{ \delta_0, 1\} } \exp \Big \{ - \Big( \alpha \frac{ \rho } { 1 + \beta } - \epsilon \frac{ 1 + \beta + \rho } { 1 + \beta } \Big) ( t + n - 1 ) \Big\}.
   \end{align}
@@
   We will show that for each $\epsilon > 0$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$,
-%\begin{align}
-%\label{eq:31step31}
-$
-    J'_2(t,n,\epsilon)
-    \leq C_2 e^{-\delta_2(t+n)}.
-%\end{align}
+  % \begin{align}
+  %   \label{eq:31step31}
+  $ J'_2(t,n,\epsilon) \leq C_2 e^{-\delta_2(t+n)}.
+  % \end{align}
   $
@@
   \begin{align}
-    &\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]
-%    \\&
-    =e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
+    & \langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]
+    % \\ &
+           = e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
   \end{align}
@@
   \begin{align}
-    &J'_2(t,n,\epsilon)
-	= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big]\\
-	&\leq e^{\alpha(n-1)}\mathbb{P}_{\mu}\Big[\big|\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\big|;A_{t+n-1}(\epsilon)\Big]\\
-	&\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}
-    [\langle \bar {g}_n, X_{t+n-1}\rangle],
+    & J'_2(t,n,\epsilon)
+      = \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big]
+    \\ & \leq e^{\alpha(n-1)}\mathbb{P}_{\mu}\Big[\big|\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\big|; A_{t+n-1}(\epsilon)\Big]
+    \\ & \leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu} [ \langle \bar {g}_n, X_{t+n-1} \rangle],
   \end{align}
@@
     \bar{g}_n
-    :=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
+    := \frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
   \end{align}
@@
   \begin{align}
-    &J'_2(t,n,\epsilon)\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]\\
-    &\leq C_3 e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)}\\
-    &=C_3e^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}
+    & J'_2(t,n,\epsilon)\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]
+    \\ & \leq C_3 e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)} \\
+   & = C_3 e^{-\alpha} e^{ - ( \alpha \beta - K ( 1 + \beta ) b ) n } e^{ - ( \frac{ \alpha \gamma } { 1 + \gamma } - \epsilon ) ( t + n - 1 ) }
    % \\&
-    \leq C_3e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}.
+    \leq C_3 e^{-( \frac{ \alpha \gamma } { 1 + \gamma } - \epsilon ) ( t + n - 1 ) }.
   \end{align}
@@
   Step 4. According to the Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that
-%\begin{align}\label{ineq: control of J31}
+  % \begin{align}\label{ineq: control of J31}
   %   J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}\quad t\geq0, n\geq 1.
-%\end{align}
-$J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}$ for all $ t\geq0, n\geq 1$.
+  % \end{align}
+  $ J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}$ for all $ t\geq0, n\geq 1$.
 
@@
 
-\begin{lem}\label{lem: independency for large rate}
+\begin{lem}
+  \label{lem: independency for large rate}
   For all $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
-\begin{align}\label{ineq: next we will need}
-    \bigg|\widetilde{\mathbb{P}}_{\mu}\Big[\prod_{l=1}^m\exp(i\theta\bar{\gamma}_{t,l})-\prod_{l=1}^m\exp(\bar{m}_l[\theta g])\Big]\bigg|\leq C e^{-\delta t}.
+  \begin{align}
+    \label{ineq: next we will need}
+    \bigg| \widetilde{ \mathbb{P} }_{ \mu } \Big[ \prod_{ l = 1 }^m \exp ( i \theta \bar{ \gamma }_{t, l} ) - \prod_{ l = 1 }^m \exp( \bar{m}_l[\theta g])\Big]\bigg|\leq C e^{-\delta t}.
   \end{align}
@@
     \widetilde{a}_n
-    :=\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{l=0}^{n}\exp(i\theta\bar{\gamma}_{t,l})\Big] \times \prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g]),
+    := \mathbb{\widetilde{P}}_{\mu}\Big[\prod_{l=0}^{n}\exp(i\theta\bar{\gamma}_{t,l})\Big] \times \prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g]),
   \]
@@
   \begin{align}
-    &\widetilde{a}_{n-1} - \widetilde{a}_n
+    & \widetilde{a}_{n-1} - \widetilde{a}_n
     % \\&
-    =\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times (e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}});D^c\Big] \times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
-    \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\Big(\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,l}}\Big)\times \mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
+     = \mathbb{P}_{ \mu } ( D^c )^{ - 1 } \mathbb{P}_{ \mu } \Big[ \Big( \prod_{ l=0 }^{n - 1 } e^{ i \theta \bar{ \gamma }_{ t, l} } \Big) \times ( e^{ \bar{m}_n [ \theta g ] } - e^{ i \theta \bar{ \gamma }_{t, n}}) ; D^c \Big] \times \prod_{ l = n + 1}^{ m } e^{\bar{ m }_l[ \theta g ] } \\
+    & = \mathbb{ P }_{ \mu }( D^c )^{ - 1 } \mathbb{P}_{ \mu } \Big[ \Big( \prod_{ l = 0 }^{n - 1} e^{ i \theta \bar{ \gamma }_{t, l} } \Big) \times \mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
   \end{align}
@@
   \begin{align}
-    |\widetilde{a}_{n-1}- \widetilde{a}_n|
-    &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
+    | \widetilde{a}_{n-1}- \widetilde{a}_n|
+    & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
     % \\& 
@@
     \text{LHS of \eqref{ineq: next we will need}}
-    &= \left|\widetilde{a}_{0}-\widetilde{a}_m\right|
+    & = \left|\widetilde{a}_{0}-\widetilde{a}_m\right|
       \leq\sum_{n=1}^m\left|\widetilde{a}_{n-1}-\widetilde{a}_n\right|
@@
   \widetilde{\gamma}_{t,n}
-    :=\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_{t}\|^{\frac{1}{1+\beta}}},
+  :=\sum_{p\in \mathcal{N} } a_p \frac { H^p_{t+n-1} - H^p_{t+n} } { e^{-(\alpha-|p|b)t} \| X_{t} \|^{ \frac{1}{1+\beta}}},
   \quad t\geq 0, n\geq 1.
 \end{align}
-\begin{lem}\label{lem: lemma04}
+\begin{lem}
+  \label{lem: lemma04}
   For all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
@@
   According to \cite[Lemma 3.4.3]{Durrett2010Probability},
-\begin{align}\label{ineq: used next 3}
+  \begin{align}
+    \label{ineq: used next 3}
     \Big|\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \widetilde{\gamma}_{t,n}}]-\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq \sum_{n=1}^m\widetilde{\mathbb{P}}_{\mu}[|Y''_{t,n}|],
@@
   where
-%\begin{align}
+  % \begin{align}
   %   Y''_{t,n}
   %   :=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},  \quad t\geq 0, n\geq 1.
-%\end{align}
+  % \end{align}
   $Y''_{t,n}:=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}}$.
@@
     > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0,
-%\]
+    % \]
     % and
-%\[
+    % \[
     \qquad
@@
     \mathcal{D}_{t,n}
-    &:=\left\{|H_t-H_{t+n-1}|\leq  e^{-\eta_0 t}, H_{t}> 2e^{-\eta_1t}\right\}.
+    & :=\left\{|H_t-H_{t+n-1}|\leq  e^{-\eta_0 t}, H_{t}> 2e^{-\eta_1t}\right\}.
   \end{align}
@@
   Step 1. Similar to Step 1 in the proof of Theorem \ref{thm: critical clt}, we can show that there exist $C_1,\delta_1 >0$ such that for all $n \geq 1$ and $t\geq 0$,
-%\begin{align}
-%\label{thm12111}
+  % \begin{align}
+  %   \label{thm12111}
   $
@@
   \leq C_1 e^{-\delta_1 t}.
-%\end{align}
+  % \end{align}
   $
@@
     \label{thm12211}
-    \mathbb{\widetilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq C_1e^{-\delta_2 t}.
+    \mathbb{\widetilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]
+    \leq C_1e^{-\delta_2 t}.
   \end{align}
   In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have, for all $t \geq 0$ and $n\geq 1$,
-\begin{align}\label{large: used next}
-    &\widetilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\\
-    &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}\widetilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot\Big|\frac{1}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}\Big]\\
-    &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}\widetilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot K'_{t,n}\Big],
+  \begin{align}
+    \label{large: used next}
+    & \widetilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\\
+    & \leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}\widetilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot\Big|\frac{1}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}\Big]\\
+    & \leq |\theta| \sum_{p\in\mathcal{N}} |a_p| e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}\widetilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot K'_{t,n}\Big],
   \end{align}
@@
     K'_{t,n}
-    :=\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t+n-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t+n-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}.
+    := \Big| \frac{ H_t^{ \frac { 1 } { 1 + \beta } } - H_{ t + n - 1 }^{ \frac { 1 }{ 1 + \beta } } } { H_t^{ \frac{ 1 }{ 1 + \beta }} H_{t+n-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}.
   \end{align}
@@
   According to Lemma \ref{lem: control of wt}, there exists $C_4>0$ such that for all $t\geq 0$ and $n\geq 1$,
-\begin{align}\label{ineq:used next 2}
-    &\widetilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]
-    \leq \frac{C_3}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\mathbb{P}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\Big]\\
-    &\leq \frac{C_3}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}
-    \\&\leq C_4|\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
-    &=C_4|\theta|\sum_{p\in\mathcal{N}}|a_p|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}\cdot e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(n-1)}.
+  \begin{align}
+    \label{ineq:used next 2}
+    & \widetilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]
+      \leq \frac{C_3}{\mathbb{P}_{\mu}(D^c)} |\theta| \sum_{ p \in \mathcal{N} } |a_p| e^{ ( \alpha - |p| b ) t } e^{ - \frac{ \alpha } { 1 + \beta } t } e^{ - ( \eta_0 - 3 \eta_1 ) t } \mathbb{ P }_{ \mu } \Big[ | H_{t+n-1}^p - H_{t+n}^p | \Big]\\
+    & \leq \frac{ C_3 }{ \mathbb{P}_{ \mu }( D^c ) } |\theta| \sum_{p\in\mathcal{N}}| a_p | e^{(\alpha-|p|b)t} e^{ - \frac{ \alpha } { 1 + \beta } t } e^{ - ( \eta_0 - 3 \eta_1 ) t } \| H_{ t + n - 1 }^p - H_{ t + n}^p \|_{ \mathbb{ P }_{ \mu }; 1 + \gamma} \\
+    & \leq C_4 | \theta | \sum_{ p \in \mathcal{N} } | a_p | e^{ ( \alpha - |p| b ) t} e^{ - \frac{ \alpha } { 1 + \beta } t } e^{ - ( \eta_0 - 3 \eta_1 )t  } e^{ - \frac{ 1 } { 1 + \gamma } ( \alpha \gamma - | p |(1+\gamma)b)(t+n-1)}\\
+    & = C_4 | \theta | \sum_{ p \in \mathcal{ N } } | a_p | \exp \Big \{ \Big( \frac { \alpha } { 1 + \gamma } - \frac{ \alpha } { 1 + \beta } - ( \eta_0 - 3 \eta_1 ) \Big) t \Big \} \cdot e^{ - \frac { 1 } { 1 + \gamma }( \alpha \gamma - | p | ( 1 + \gamma ) b ) ( n - 1 ) }.
   \end{align}
@@
 \end{proof}
-\begin{lem}\label{lem: lemma05}
+\begin{lem}
+  \label{lem: lemma05}
   For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist  $C,\delta_1,\delta_2>0$ such that
@@
   According to Proposition \ref{lem: control of XT}, there exist $C_1,\delta>0$ such that for all $t\geq 0$ and $m\in \mathbb N$,
-\begin{align}\label{ineq: control of gamma_t on dc}
-    \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]
-    \leq 2\widetilde{P}_{\mu}(A_t(\epsilon)^c)
+  \begin{align}
+    \label{ineq: control of gamma_t on dc}
+    \Big| \widetilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]
+    \leq 2 \widetilde{P}_{\mu}(A_t(\epsilon)^c)
     \leq C_1 e^{-\delta t}.
   \end{align}
-    According to Lemma \ref{lem: control of wt}, there exist $C_2,C_3>0$
-    such that for all $m\in \mathbb{N}, t\geq$,
-\begin{align}\label{ineq: control of gamma_t on d}
-    &\Big|\widetilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)}\Big]\Big|\\
-    &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{n=m}^{\infty}\sum_{p\in \mathcal{N}}|a_p|\mathbb{P}_{\mu}\Big[\frac{|H_{t+n-1}^p-H_{t+n}^p|}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}\mathbf{1}_{A_t(\epsilon)}\Big]\\
-    &\leq  \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}\\
-    &\leq C_2|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
-    &\leq C_3|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}
+  According to Lemma \ref{lem: control of wt}, there exist $C_2,C_3>0$ such that for all $m\in \mathbb{N}, t\geq$,
+  \begin{align}
+  \label{ineq: control of gamma_t on d}
+    & \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty} \widetilde{ \gamma }_{ t, n}) - 1 \big) \mathbf{1}_{ A_t( \epsilon ) } \Big] \Big| \\
+    & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{n=m}^{\infty}\sum_{p\in \mathcal{N}}|a_p|\mathbb{P}_{\mu}\Big[\frac{|H_{t+n-1}^p-H_{t+n}^p|}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}\mathbf{1}_{A_t(\epsilon)}\Big]\\
+    & \leq  \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}\\
+    & \leq C_2|\theta|\sum_{p\in \mathcal{N} } |a_p| e^{ ( \alpha - |p| b ) t} e^{- \frac{ \alpha - \epsilon } { 1 + \beta } t } \sum_{ n = m}^{ \infty } e^{ - \frac{ 1 }{ 1 +\ gamma} ( \alpha \gamma - | p | ( 1 + \gamma ) b ) ( t + n - 1 ) } \\
+    & \leq C_3 | \theta | \exp \Big\{ \Big( \frac { \alpha } { 1 + \gamma } - \frac { \alpha } { 1 + \beta } + \frac{ \epsilon } { 1 + \beta } \Big) t \Big\}
     e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m}.
@@
 Now we are ready to prove Theorem \ref{thm: large clt}.
-\medskip
 
@@
   According to Lemma \ref{lem: independency for large rate}, there exist $C_1,\delta_1>0$ such that for all $t\geq 0$,
-\begin{align}\label{ineq: last1}
-    \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]
+  \begin{align}
+    \label{ineq: last1}
+    \Big| \widetilde{ \mathbb{ P } }_{ \mu } \Big[ \exp( i \theta \sum_{ n = 1 }^m \gamma_{ t, n} ) - \exp( \sum_{ n = 1 }^m \bar{ m }_n [ \theta g ] ) \Big]
     \Big|\leq C_1 e^{-\delta_1 t}.
@@
   According to Lemma \ref{lem: lemma04}, there exists $C_2>0$ such that for all $t\geq 0$,
-\begin{align}\label{ineq: last2}
+  \begin{align}
+    \label{ineq: last2}
     \Big|\widetilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \widetilde{\gamma}_{t,n}}]-\widetilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C_2  e^{-\frac{\delta_0}{2} t}.
@@
   According to Lemma \ref{lem: lemma05}, there exist $C_3,\delta_2,\delta_3>0$ such that for all $t\geq 0$,
-\begin{align}\label{ineq: last3}
+  \begin{align}
+    \label{ineq: last3}
     \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\Big]\Big|\leq C_3(e^{-\delta_2 t}+e^{\delta_2 t}e^{-\delta_3 e^{\frac{\delta_0}{2}t}}).
@@
 
+% ** Appendix
 \appendix
 \section{ }
-
 \subsection{Analytic facts}
@@
   &\Big|e^{-z} - \sum_{k=0}^{m+1} \frac{(-z)^k}{k!}\Big|
-    = \Big| \int_0^1\Big(e^{-\theta z} - \sum_{k=0}^m \frac{(-\theta z)^k}{k!} \Big) z d\theta \Big|
-    \\&\quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} |z| d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} |z| d\theta\Big)
+    = \Big| \int_0^1\Big(e^{-\theta z} - \sum_{k=0}^m \frac{(-\theta z)^k}{k!} \Big) z d\theta \Big| \\
+  & \quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} |z| d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} |z| d\theta\Big)
     = \frac{|z|^{m+2}}{(m+2)!} \wedge \frac{2|z|^{m+1}}{(m+1)!},
@@
   Then the functions
-%\begin{equation}
-\begin{align*}
-&
-    h (z) = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+
-%\end{equation}
+  % \begin{equation}
+  \begin{align}
+    & h (z) 
+      = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+
+      % \end{equation}
       % and
-%\begin{equation}
-%\label{eq: deriavetive of the Poission partb}
-\\&
-    h'(z) = \int_{(0,\infty)}(1- e^{-zy})y \pi(dy), \quad z \in \mathbb C_+
-%\end{equation}
-\end{align*}
+      % \begin{equation}
+      %   \label{eq: deriavetive of the Poission partb}
+    \\ & h'(z) 
+         = \int_{(0,\infty)}(1- e^{-zy})y \pi(dy), \quad z \in \mathbb C_+
+         % \end{equation}
+  \end{align}
   are well defined, continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
@@
   \[
-    \frac{h(z)-h(z_0)}{z-z_0} \xrightarrow[\mathbb C_+\ni z \to z_0]{} h'(z_0),\quad z_0 \in \mathbb C_+.
+    \frac{h(z)-h(z_0)}{z-z_0} 
+    \xrightarrow[\mathbb C_+\ni z \to z_0]{} h'(z_0),\quad z_0 \in \mathbb C_+.
   \]
@@
   It follows from Lemma \ref{lem: estimate of exponential remaining} that $h$ and $h'$ are well defined on $\mathbb C_+$.
-   According to \cite[Theorems 3.2. \& Proposition 3.6]{SchillingSongVondravcek2010Bernstein},
-    $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
-
-    It follows from Lemma \ref{lem: estimate of exponential remaining} that, for each $z_0 \in \mathbb C_+$,  there exists $C>0$ such that for $z \in \mathbb C_+$ close enough to $z_0$ and any
-    $y>0$,
-\begin{align}
-    &\Big| \frac{e^{-zy} - e^{-z_0 y}+(z-z_0) y}{z-z_0} \Big|
-    = \frac{1}{|z-z_0|}\Big| \int_0^1 \big(-y e^{-(\theta z+(1-\theta)z_0)y}+y\big)(z-z_0)d\theta\Big|
-    \\ &\leq y\int_0^1 |1-e^{-(\theta z +(1-\theta)z_0)y}| d\theta
+  According to \cite[Theorems 3.2. \& Proposition 3.6]{SchillingSongVondravcek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
+
+  It follows from Lemma \ref{lem: estimate of exponential remaining} that, for each $z_0 \in \mathbb C_+$,  there exists $C>0$ such that for $z \in \mathbb C_+$ close enough to $z_0$ and any $y>0$,
+\begin{align}
+  & \Big| \frac{e^{-zy} - e^{-z_0 y}+(z-z_0) y}{z-z_0} \Big|
+    = \frac{1}{|z-z_0|}\Big| \int_0^1 \big(-y e^{-(\theta z+(1-\theta)z_0)y}+y\big)(z-z_0)d\theta\Big| \\ 
+  & \leq y\int_0^1 |1-e^{-(\theta z +(1-\theta)z_0)y}| d\theta
     \leq (2y) \wedge\Big( y^2\int_0^1|\theta z+(1-\theta)z_0|d\theta\Big)
@@
 \begin{align}
-    &\frac{h(z)-h(z_0)}{z-z_0} = \int_{(0,\infty)} \frac{e^{-zy}+zy -(e^{-z_0 y}+z_0 y)}{z-z_0}  \pi(dy)
-    \\&\xrightarrow[\mathbb C_+\ni z\to z_0]{} \int_{(0,\infty)}(1 - e^{-z_0 y} )y\pi(dy) = h'(z_0),
+  & \frac{h(z)-h(z_0)}{z-z_0} = \int_{(0,\infty)} \frac{e^{-zy}+zy -(e^{-z_0 y}+z_0 y)}{z-z_0}  \pi(dy) \\
+  & \xrightarrow[\mathbb C_+\ni z\to z_0]{} \int_{(0,\infty)}(1 - e^{-z_0 y} )y\pi(dy) = h'(z_0),
 \end{align}
@@
 % Recall that the Gamma function  $\Gamma$ is defined by
-%\begin{equation}
+% \begin{equation}
 %   \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
 %   \quad x>0.
-%\end{equation}
+% \end{equation}
 It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
@@
 % by showing that the both sides
-%\begin{itemize}
-%\item
+% \begin{itemize}
+% \item
 %   are extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
-%\item
+% \item
 %   are holomorphic on $\mathbb C_+^0$;
-%\item
+% \item
 %   are continuous on $\mathbb C_+$.
-%\end{itemize}
+% \end{itemize}
 are (i)  extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
@@
 \end{equation}
-
 \end{lem}
@@
   |z_0^{1+\beta} - z_1^{1+\beta}|
-    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
-    \leq (1+\beta)  \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
-    \\&\leq (1+\beta)  ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
+  & \leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
+    \leq (1+\beta)  \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0| \\
+  & \leq (1+\beta)  ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
     \qedhere
@@
 
+% *** Feynman-Kac formula with complex valued functions
 \subsection{Feynman-Kac formula with complex valued functions}
@@
 \end{equation}
-
 \begin{lem}
   \label{eq: complex FK}
-    Let $t \geq 0$. Suppose that
-    $\rho_1, \rho_2\in \mathcal B_b([0,t] \times E, \mathbb C)$
-    and $f\in \mathcal B_b(E, \mathbb C)$.
+  Let $t \geq 0$. Suppose that $\rho_1, \rho_2\in \mathcal B_b([0,t] \times E, \mathbb C)$ and $f\in \mathcal B_b(E, \mathbb C)$.
   Then
@@
   \label{eq: expresion of g}
-    g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
+  g(r,x) 
+  := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
 \end{equation}
@@
 \[
-    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
+  g(r,x)
+  = \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
 \]
@@
   \begin{align}
-    &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}~(\rho_2 g)(s,\xi_s)~ds \Big]
-    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\rho_1+\rho_2)} f(\xi_t)]~ds \Big]
-    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t) ~ds \Big]
-    = \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)}f(\xi_t)(H_{(r,t)}^{(\rho_2)} - 1)]
-    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\rho_2)} f(\xi_t)].
-\end{align}
-    For uniqueness, suppose  $\widetilde g$ is another solution. Put $h(r) = \sup_{x\in E}|g(r,x) - \widetilde g(r,x)|$. Then
-\[
-   h(r) \leq e^{t\|\rho_1\|_\infty}\|\rho_2\|_\infty \int_r^t h(s)ds,
+    & \Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}~(\rho_2 g)(s,\xi_s)~ds \Big]
+      =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\rho_1+\rho_2)} f(\xi_t)]~ds \Big] \\
+    & = \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t) ~ds \Big]
+      = \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)}f(\xi_t)(H_{(r,t)}^{(\rho_2)} - 1)] \\
+    & = g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\rho_2)} f(\xi_t)].
+  \end{align}
+  For uniqueness, suppose  $\widetilde g$ is another solution. Put $h(r) = \sup_{x\in E}|g(r,x) - \widetilde g(r,x)|$. 
+  Then
+  \[
+    h(r) 
+    \leq e^{t\|\rho_1\|_\infty}\|\rho_2\|_\infty \int_r^t h(s)ds,
     \quad r\le t.
@@
 
+% ** Superprocesses
 \subsection{Superprocesses}
@@
   where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
-\begin{equation}\label{eq:FKPP_in_definition}
+  \begin{equation}
+    \label{eq:FKPP_in_definition}
     V_tf(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi(\xi_s,V_{t-s}f)ds \Big]
@@
 We refer our readers to \cite{Li2011Measure-valued} for more discussions about the definition and the existence of superprocesses.
-    To avoid triviality, we assume that
-    $\psi(x,z)$ is not identically equal to $-\rho_1(x)z$.
+To avoid triviality, we assume that $\psi(x,z)$ is not identically equal to $-\rho_1(x)z$.
 
@@
 \begin{equation}
-    \psi'(x,z):= - \rho_1(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
+  \psi'(x,z)
+  := - \rho_1(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
   \quad x\in E, z\in \mathbb C_+.
@@
 We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
-    Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued},
-    there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
-%\begin{itemize}
-%\item
+Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued}, there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
+% \begin{itemize}
+% \item
 %   $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
-%\item
+% \item
 %   $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
-%\item
+% \item
 %   for any $\mu \in \mathcal M(E)$, 
@@
 %   then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
-%\end{itemize}
+% \end{itemize}
 (i) $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$; (ii) $\mathbb N_x(\|W_0 \|\neq 0) = 0$
@@
 We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
-\subsection{{Semigroups for superprocesses}}
+
+% ** Semigroup for superproccesses
+\subsection{Semigroups for superprocesses}
 \label{sec: definition of vf}
@@
   L_1(\xi)
-    &:= \{f\in \mathcal B(E): \forall x\in E, t\geq 0, \quad \Pi_x[|f(\xi_t)|]< \infty\},
-    \\L_2(\xi)
+  &:= \{f\in \mathcal B(E): \forall x\in E, t\geq 0, \quad \Pi_x[|f(\xi_t)|]< \infty\}, \\
+  L_2(\xi)
   &:= \{f \in \mathcal B(E): |f|^2 \in L_1(\xi)\}.
@@
   \mathbb N_x[\langle W_t, f\rangle]
-    =\mathbf P_{\delta_x}[\langle f, X_t\rangle]
-    =P^{\rho_1}_t f(x) \in \mathbb R,
+  = \mathbf P_{\delta_x}[\langle f, X_t\rangle]
+  = P^{\rho_1}_t f(x) \in \mathbb R,
   \quad f\in L_1(\xi), t > 0,x\in E.
@@
 \[
-    U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta \langle X_t, f\rangle}],
+  U_t(\theta f)(x) 
+  := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta \langle X_t, f\rangle}],
   \quad t\geq 0, f\in L_1(\xi), \theta \in \mathbb R, x\in E,
@@
   \label{eq: N and characteristic exponent}
-    U_t(\theta f)(x) = \mathbb N_x[e^{i \langle W_t, \theta f\rangle} - 1],
+  U_t(\theta f)(x) 
+  = \mathbb N_x[e^{i \langle W_t, \theta f\rangle} - 1],
   \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
@@
   \big|\psi\big(x,-U_tf\big)\big|
-    \leq C P^{\rho_1}_t |f|(x)+
-         C (P^{\rho_1}_t |f| (x))^2.
+  \leq C P^{\rho_1}_t |f|(x) + C (P^{\rho_1}_t |f| (x))^2.
 \end{equation}
@@
     \label{eq: upper bound for vf}
-    |U_tf(x)| \leq \mathbb N_x[|e^{i \langle W_t, f\rangle} - 1|]
+    |U_tf(x)| 
+    \leq \mathbb N_x[|e^{i \langle W_t, f\rangle} - 1|]
     \leq \mathbb N_x[|i \langle W_t, f\rangle|]
@@
     \label{eq: estimate of deriavetive of v(theta)}
-    \mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta \langle W_t, f\rangle} - 1) \Big|\Big]
+    \mathbb N_x \Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta \langle W_t, f\rangle} - 1) \Big|\Big]
     \leq \mathbb N_x[|\langle W_t, f\rangle|] \sup_{\theta \in K}|\theta|
@@
   \end{equation}
-    Therefore, according to \cite[Theorem A.5.2]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent},
-    $U_t(\theta f)(x)$ is differentiable in $\theta \in \mathbb R$ with
+  Therefore, according to \cite[Theorem A.5.2]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent}, $ U_t( \theta f)( x )$ is differentiable in $\theta \in \mathbb R$ with
   \[
@@
     \label{eq: upper bound of psi'(v)}
-    &|\psi'(x, -U_tf)|
-    \\&= \Big| -\rho_1(x)- 2\rho_2(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
-    \\&= \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i \langle W_t, f\rangle} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i \langle X_t, f\rangle}] \pi(x,dy) \Big|
-    \\ &\leq \|\rho_1\|_\infty + 2\rho_2(x)\mathbb N_x[\langle W_t, |f|\rangle]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge \langle X_t, |f|\rangle] \pi(x,dy)
-    \\ &\leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty
-    P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
-    \\ &=: C_1 + C_2(P^{\rho_1}_t |f|)(x),
+    & |\psi'(x, -U_tf)| \\
+    & = \Big| -\rho_1(x)- 2\rho_2(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big| \\
+    & = \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i \langle W_t, f\rangle} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i \langle X_t, f\rangle}] \pi(x,dy) \Big| \\ 
+    & \leq \|\rho_1\|_\infty + 2\rho_2(x)\mathbb N_x[\langle W_t, |f|\rangle]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge \langle X_t, |f|\rangle] \pi(x,dy) \\ 
+    & \leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty
+    P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy) \\ 
+    & =: C_1 + C_2(P^{\rho_1}_t |f|)(x),
   \end{align}
@@
   Now, 
-    %combining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, 
+  % combining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, 
   combining the display above with \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bounded for derivative of v(theta)}
@@
 \end{proof}
-
 This lemma also says that if $f\in L^2(\xi)$ then
@@
   \label{eq: domination of psi(v)}
-    &\Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
+  & \Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
   % \\&
-    \leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big]
-    \\ &\leq \int_0^t \big(C_1 e^{t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
-    \\ &\leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\rho_1\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
-\end{align}
-
+  \leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big] \\ 
+  & \leq \int_0^t \big(C_1 e^{t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds \\ 
+  & \leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\rho_1\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
+\end{align}
+
+% ** A complex-valued non-linear integral equation
 \subsection{A complex-valued non-linear integral equation}
@@
   U_tf(x) - \Pi_x \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f\big) ds \Big] 
-    \\= i \Pi_x [f(\xi_t)].
+  = i \Pi_x [f(\xi_t)].
 \end{equation}
@@
   U_tf(x) -  \int_0^t P_{t-s}^{\rho_1} \psi_0\big(\cdot,-U_sf\big) (x)~ds
-    \\= iP_t^{\rho_1} f(x).
+  = iP_t^{\rho_1} f(x).
 \end{equation}
@@
 \item
-     the spine process
-    $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$,
-    where
-\begin{equation}
-    d\Pi_x^{(f,T)} := \frac{f(\xi_T)e^{\int_0^T \rho_1(\xi_s)ds}}{P^{\rho_1}_T f(x)} d \Pi_x;
+  the spine process $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$, where
+  \begin{equation}
+    d\Pi_x^{(f,T)} 
+    := \frac{f(\xi_T)e^{\int_0^T \rho_1(\xi_s)ds}}{P^{\rho_1}_T f(x)} d \Pi_x;
   \end{equation}
 \item
-    given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, 
-    the immigration measure
-\[ \{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}\]
+  given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure
+\[ 
+  \{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}
+\]
 is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
@@
 \begin{align}
-    &\int_{[0,t]\times \mathbb W}|e^{i \langle w_{t-s}, f\rangle} - 1| \mathbf m(\xi, ds,dw)
-    \leq \int_{[0,t]\times \mathbb W}\big(| \langle w_{t-s}, f\rangle| \wedge 2\big) \mathbf m(\xi, ds,dw)
-    \\&\leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( \langle W_{t-s}, |f|\rangle\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[\langle X_{t-s}, |f|\rangle] \pi(\xi_s,dy)
-    \\&\qquad\qquad+ 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
-     \\&\leq \int_0^t (P_{t-s}^{\rho_1} |f|)(\xi_s)\Big(2\rho_2(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
-    \\&\leq \Big(2\|\rho_2\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\rho_1\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+  & \int_{[0,t]\times \mathbb W}|e^{i \langle w_{t-s}, f\rangle} - 1| \mathbf m(\xi, ds,dw)
+    \leq \int_{[0,t]\times \mathbb W}\big(| \langle w_{t-s}, f\rangle| \wedge 2\big) \mathbf m(\xi, ds,dw) \\ 
+  & \leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( \langle W_{t-s}, |f|\rangle\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[\langle X_{t-s}, |f|\rangle] \pi(\xi_s,dy) \\
+  & \qquad\qquad + 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
+  \\ & \leq \int_0^t (P_{t-s}^{\rho_1} |f|)(\xi_s)\Big(2\rho_2(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
+  \\ & \leq \Big(2\|\rho_2\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\rho_1\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
        < \infty.
@@
 \begin{align}
-    &\int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)
-    \\&=\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i \langle W_{t-s}, f\rangle} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i \langle X_{t-s}, f\rangle} - 1] \pi(\xi_s,dy)\Big) ds
-    \\&=\int_0^t \Big( 2\rho_2(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
-    \\&= -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
+  & \int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)
+  \\ & =\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i \langle W_{t-s}, f\rangle} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i \langle X_{t-s}, f\rangle} - 1] \pi(\xi_s,dy)\Big) ds
+  \\ & =\int_0^t \Big( 2\rho_2(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
+  \\ & = -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
 \end{align}
@@
   \label{eq: N to Pi}
-    &\mathbb N_x^{\langle W_{t}, g\rangle}[e^{i \langle W_t, f\rangle}]
-    =\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
-    \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
-%    \\&
+    & \mathbb N_x^{\langle W_{t}, g\rangle}[e^{i \langle W_t, f\rangle}]
+      = \mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
+    \\ & = \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
+    % \\ &
     = \frac{1}{P_t^{\rho_1} g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
@@
   \frac{\mathbf P_{\delta_x}[\langle X_t, f\rangle e^{i \langle X_t, f\rangle}] }{\mathbf P_{\delta_x}[e^{i \langle X_t, f\rangle}]}
-    &= \mathbf P_{\delta_x}[\langle X_t, f^+\rangle] \mathbb N_x^{\langle W_t, f^+\rangle} [e^{i \langle X_t, f\rangle}] - \mathbf P_{\delta_x}[\langle X_t, f^-\rangle]\mathbb N_x^{\langle W_t, f^-\rangle}[e^{i \langle X_t, f\rangle}]
-    \\& = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
+  & = \mathbf P_{\delta_x}[\langle X_t, f^+\rangle] \mathbb N_x^{\langle W_t, f^+\rangle} [e^{i \langle X_t, f\rangle}] - \mathbf P_{\delta_x}[\langle X_t, f^-\rangle]\mathbb N_x^{\langle W_t, f^-\rangle}[e^{i \langle X_t, f\rangle}]
+  \\ & = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
 \end{align}
@@
 Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
-
-\begin{align}
-    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)( x)
-    = \Pi_x[ i f(\xi_{t-r}) e^{-\int_0^{t-r} \psi'(\xi_s, -U_{t-r-s}(\theta f)) ds} ]
-    \\&= \Pi_{r,x}[i f(\xi_t)e^{-\int_0^{t-r} \psi'(\xi_{r+s}, -U_{t-r-s}(\theta f)) ds} ]
+\begin{align}
+  & \frac{\partial}{\partial \theta} U_{t-r}(\theta f)( x)
+    = \Pi_x[ i f(\xi_{t-r}) e^{-\int_0^{t-r} \psi'(\xi_s, -U_{t-r-s}(\theta f)) ds} ] \\ 
+  & = \Pi_{r,x}[i f(\xi_t)e^{-\int_0^{t-r} \psi'(\xi_{r+s}, -U_{t-r-s}(\theta f)) ds} ]
     = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -U_{t-s}(\theta f)) ds} ].
@@
 % From \eqref{eq: upper bound of psi'(v)},
-From the display below \eqref{eq: path integration representation of psi(v)},
-     we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
+From the display below \eqref{eq: path integration representation of psi(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e.
+bounded on $[0,T]\times E$ for each $T \geq 0$).
 Therefore, we can apply Lemma \ref{eq: complex FK} and get that
@@
 \begin{align}
-    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
-    &= \Pi_{r,x} [i e^{\int_r^t \rho_1(\xi_s)ds}f(\xi_t)].
+  & \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
+  & = \Pi_{r,x} [i e^{\int_r^t \rho_1(\xi_s)ds}f(\xi_t)].
 \end{align}
 Integrating the two displays above with respect to $\theta$  on [0,1], using 
-    %\eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get
-Fubini's theorem,   \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and the display below it, we get
+% \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get Fubini's theorem, \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and the display below it, we get
 \begin{equation}
   U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-U_{t-s}f\big) ~ds\Big]
-    = i\theta \Pi_{r,x} [f(\xi_t)]
+  = i \theta \Pi_{r,x} [f(\xi_t)]
 \end{equation}
@@
   U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
-    = i\Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
+  = i \Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
 \end{equation}
@@
 Note that 
-%\begin{itemize}
-%\item
+% \begin{itemize}
+% \item
 %   It is clear that $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$.
-%\item
+% \item
 %   $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$ due to \eqref{eq: N and characteristic exponent}, the dominated convergence theorem and the fact that
-%\[
+%   \[
 %     |e^{i W_t(f_n)} - 1| \leq \langle W_t, |f|\rangle;
 %     \quad \mathbb N_x[\langle W_t, |f|\rangle] = (P_t^{\rho_1} |f|)(x) < \infty.
-%\]
-%\item
+%   \]
+% \item
 %   $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
-%\begin{equation}
+%   \begin{equation}
 %     \big|\psi(\xi_s,- U_{t-s}f_n)\big|
 %     \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2.
-%\end{equation}
-%\end{itemize}
+%   \end{equation}
+% \end{itemize}
 % Using the above arguments, 
@@
 we get that $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$.
-Using these, 
-    letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
+Using these, letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
 \end{proof}
@@
 We thank Zenghu Li and Rui Zhang for helpful conversations.
-	%new
+% new
 We also thank the referee for very helpful comments.
-	%end new
+% end new
 \medskip

### 2019-08-04 supCLT.tex
change supCLT.tex
Agreeing to Song's changes

@@
   University of Illinois at Urbana-Champaign \\ 
-  Urbana, IL 61801, USA}
+  % Urbana, IL 61801, USA}
+  Urbana, IL, USA, 61801}
 \email{rsong@illinois.edu}
@@
   Zhenyao Sun \\ 
-  School of Mathematical Sciences \\ 
-  Peking University \\ 
-  Beijing, P. R. China, 100871}
-\email{zhenyao.sun@pku.edu.cn}
+  % School of Mathematical Sciences \\ 
+  School of Mathematics and Statistics\\ 
+  % Peking University \\ 
+  Wuhan University \\ 
+  % Beijing, P. R. China, 100871}
+  Hubei, P. R. China, 100871}
+% \email{zhenyao.sun@pku.edu.cn}
+\email{zhenyao.sun@gmail.com}
 \address{
@@
 where $\sigma > 0$ and $b > 0$ are constants.
-% Let the \emph{branching mechanism} $\psi$ be a function on $\mathbb R_+$ which takes the form of
 Let $\psi$ be a function on $\mathbb R_+$ of the form 
@@
 where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty$.
-%	We refer to $\pi$ as the \emph{L\'evy measure} of the branching mechanism $\psi$.
 $\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
@@
 For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
-We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have
-%\[
-$
-\sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
-%\]
+We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
 $
@@
 Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-We want to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
-%\[
-$
-% \frac{\langle f, X_t \rangle -G_t}{F_t}
-(\langle f, X_t \rangle -G_t)/F_t
-% \]
-$
-converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
+We want to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
 It turns out that the statements of the CLT's are different in three regimes depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: 
@@
 There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
-See   \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for %supercritical Galton-Watson processes,
-supercritical Galton-Watson processes (GW processes),
-\cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type %Galton-Watson processes,
-GW processes
-\cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-% In \cite{AdamczakMilos2015CLT}, Adamczak and Mi\l{}o\'s proved some spatial central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Mi\l{}o\'s proved some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
+See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
 Some spatial central limit theorems for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
 These two papers made connections between the CLT and  the branching rate regimes.
-% In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition.
-Some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition were established in \cite{RenSongZhang2014Central}.
+Some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only a second moment condition were established in \cite{RenSongZhang2014Central}.
 Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
-% In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}, Ren, Song and Zhang also established a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
 Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
@@
 There are also many limiting theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moments.
-Heyde \cite{Heyde1971Some} established a central limit type  theorem 
-% for supercritical Galton-Watson process when the offspring distribution
-for supercritical GW processes when the offspring distribution
-belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit law is  a stable law. 
-Similar results  for supercritical multi-type 
-% Galton-Watson processes and supercritical  continuous time branching processes, 
-GW processes and supercritical  continuous time branching processes, 
+Heyde \cite{Heyde1971Some} established a central limit type  theorem for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit law is  a stable law.
+Similar results  for supercritical multi-type GW processes and supercritical  continuous time branching processes, 
 under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
-Recently, Marks and Milo\'s \cite{MarksMilos2018CLT}
-% considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes 
-considered the limit behavior of supercritical branching OU processes
-with a special stable branching law.
+Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable branching law.
 They established some spatial central limit theorems in the small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
@@
 It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event} $D :=\{\exists t\geq 0,~\text{s.t.}~ \|X_t\| =0 \}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
-In fact,
-%\begin{equation}
-$
-\mathbb{P}_{\mu} (D)
-= e^{-\bar v \|\mu\|},
-% \quad \mu\in \mathcal M(\mathbb R^d),
-% \end{equation}
-$ 
-for $\mu\in \mathcal M(\mathbb R^d)$,
-where
-% \[
-$
-\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
-% \]
-$
-is the largest root of $\psi$.
+In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}, $ for $\mu\in \mathcal M(\mathbb R^d)$, where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
 
@@
 In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of $-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
-It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ condition, i.e.,
-%\[
-$
-\int_{(1,\infty)} y\log y~\pi(dy) < \infty.
-% \]
+It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y~\pi(dy) < \infty.
 $
@@
 the order of the function $f$ in the spectral decomposition \eqref{semicomp1}.
-% new
 $\kappa_f$ corresponds to the lowest non-trivial frequency in the eigen-expansion of $f$.
-% end new    
 Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
@@
 The asymptotic behavior varies with the following three regimes:
-% \begin{itemize}
-% \item
-%   The large branching rate regime: $\alpha\beta>\kappa_fb(1+\beta)$;
-% \item
-%   The critical branching rate regime: $\alpha\beta=\kappa_fb(1+\beta)$;
-% \item
-%   The small branching rate regime: $\alpha\beta<\kappa_fb(1+\beta)$.
-% \end{itemize}
 (1) the small branching rate regime where $\alpha\beta<\kappa_fb(1+\beta)$; 
@@
   \end{align}
-  where $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function
-  % \begin{align}
-  %   \mathbf{E}[e^{i\theta\bar{\zeta}}]=\exp(\bar{m}[\theta f]),\quad \theta\in \mathbb{R}.
-  % \end{align}
-  $\theta\mapsto \exp(\bar{m}[\theta f])$.
+  where $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(\bar{m}[\theta f])$.
 \end{thm}
@@
   \]
-  where $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with
-  characteristic function
-  % \[
-  %   \mathbf E [e^{i\theta \widetilde{\zeta}}]
-  %   =\exp(\widetilde{m}[\theta f]),
-  %   \quad \theta\in \mathbb R.
-  % \]
-  $\theta\mapsto \exp(\widetilde{m}[\theta f]$.
+  where $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(\widetilde{m}[\theta f])$.
 \end{thm}
@@
   \]
-  where $\zeta$ is a $(1+\beta)$-stable random variable with
-  % \[
-  %   \mathbf E[e^{i\theta \zeta}]
-  %   =\exp(m[\theta f]),
-  %   \quad \theta\in \mathbb R.
-  % \]
-  characteristic function $\theta\mapsto \exp(m[\theta f])$.
+  where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(m[\theta f])$.
 \end{thm}
@@
 
-Suppose $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions
-% \[
-%   \mathbf E[e^{i\theta \zeta_k}] = \exp( m_k[\theta f]),\quad k \in \mathbb N,
-% \]
-$\theta\mapsto \exp( m_k[\theta f])$, where $m_k[f]$ is given in Lemma \ref{lem: def of all m} below.
+Suppose $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions $\theta\mapsto \exp( m_k[\theta f])$, where $m_k[f]$ is given in Lemma \ref{lem: def of all m} below.
 Recall $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
@@
 \]
-where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function
-% \[
-%   \mathbf E[e^{i\theta \zeta}] = \exp(m[\theta f]),\quad \theta \in \mathbb R.
-% \]
-$\theta\mapsto \exp(m[\theta f])$,
-with $m[\theta f]$ given in Lemma \ref{lem: def of all m} below.
+where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(m[\theta f])$, with $m[\theta f]$ given in Lemma \ref{lem: def of all m} below.
 In the explanation above, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined, and
@@
 \]
-where $\widetilde \zeta$ is a $(1+\beta)$-stable random variable with characteristic function
-% \[
-%   \mathbf E[e^{i\theta \widetilde \zeta}] 
-%   = \exp(\widetilde m[\theta f]),\quad \theta \in \mathbb R.
-% \]
-$\theta\mapsto \exp(\widetilde m[\theta f])$.
+where $\widetilde \zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(\widetilde m[\theta f])$.
 
@@
   \]
-	This implies that
-  % \[
-  $
-	\eta' z^{\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0.
-  % \]
-  $
+	This implies that $ \eta' z^{\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0. $
 	So we must have $\beta'= \beta$ and $\eta'= \eta$.
 \end{proof}
-
-%	We also have the following result:
 \begin{lem}
@@
 Denote by $\mathcal B(\mathbb R^d, \mathbb C)$ the space of all $\mathbb C$-valued Borel functions on $\mathbb R^d$.
-Recall that $\mathcal P$ is defined in \eqref{eq: polynomial growth function}.
+Recall that $\mathcal P$ is given in \eqref{eq: polynomial growth function}.
 Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
-For any function $h: [0,\infty) \to [0,\infty)$, we say an operator $R: \mathcal P^+ \to \mathcal P^+$ is an \emph{$h$-controller} if
-% \begin{itemize}
-% \item
-%   $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and
-% \item
-%   $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
-% \end{itemize}
-(1) $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and (2) $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
-For a subset $\mathcal D$ of $\mathcal P^*$ and an $h$-controller $R$, we say an operator $A : \mathcal D \to \mathcal P^*$ is \emph{$h$-controlled by $R$ on $\mathcal D$} if $|Af| \leq R|f|$ for each $f\in \mathcal D$.
-We say an operator $A : 
-\mathcal D \to \mathcal P^*$ is \emph{$h$-controllable} if there exists an $h$-controller $R$ such that $A$ is $h$-controlled by $R$.
-We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
-
-For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, we define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
+
+% Modified
+% For any function $h: [0,\infty) \to [0,\infty)$, we say an operator $R: \mathcal P^+ \to \mathcal P^+$ is an \emph{$h$-controller} if
+% (1) $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and (2) $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
+% For a subset $\mathcal D$ of $\mathcal P^*$ and an $h$-controller $R$, we say an operator $A : \mathcal D \to \mathcal P^*$ is \eminnershapeph{$h$-controlled by $R$ on $\mathcal D$} if $|Af| \leq R|f|$ for each $f\in \mathcal D$.
+% We say an operator $A: \mathcal D \to \mathcal P^*$ is \emph{$h$-controllable} if there exists an $h$-controller $R$ such that $A$ is $h$-controlled by $R$.
+% We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
+
+In this paper, we say $R$ is a \emph{monotone} operator on $\mathcal P^+$ if $R:\mathcal P^+ \to \mathcal P^+$ satisfies that $Rf\leq Rg$ for each $f\leq g$ in $\mathcal P^+$.
+For a function $h: [0,\infty) \to [0,\infty)$, we say $R$ is an \emph{$h$-controller} if $R$ is a monotone operator on $\mathcal P^+$ and that $R(\theta f)\leq h(\theta) Rf$ for each $f\in \mathcal P^+$ and $\theta \in [0,\infty)$.
+For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and an operator $R$ on $\mathcal P^+$, we say an operator $A$ is \emph{controlled by $R$ from $\mathcal D$ to $\mathcal I$} if $A:\mathcal D \to \mathcal I$ and that $|Af| \leq R|f|$ for each $f\in \mathcal D$; say a family of operators $\mathscr O$ is \emph{uniformly controlled by $\mathcal R$ from $\mathcal D$ to $\mathcal I$} if for each $A\in \mathcal O$, $A$ is controlled by $R$ from $\mathcal D$ to $\mathcal I$.
+For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and a function $h:[0,\infty) \to [0,\infty)$, we say an operator $A$ (resp.
+a family of operators $\mathscr O$) is \emph{$h$-controllable} (resp.
+\emph{uniformly $h$-controllable}) from $\mathcal D$ to $\mathcal I$ if there exists an $h$-controller $R$ such that $A$ (resp.
+$\mathscr O$) is controlled (resp.
+uniformly controlled) by $R$ from $\mathcal D$ to $\mathcal I$.
+% End Modified
+
+For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
 For any $a \in \mathbb R$ and any operator $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
+
+% Modified
+\begin{comment}
 \begin{lem}
@@
   Suppose that $\Lambda$ is an index set and $(A_\lambda)_{\lambda\in \Lambda}$ is a
-  % family of operators from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$.
-  % Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
   family of operators, from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$,
   which is uniformly 
-  % $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
   $h$-controlled by $R_A$ on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
   Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators, from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$,
-  % which is uniformly $g$-controllable on $\mathcal D_0$ 
   which is uniformly $g$-controlled by $R_B$ on $\mathcal D_0$ 
@@
   Suppose that $(C_\lambda)_{\lambda\in \Lambda} $ is a family of operators, from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$,
-  % for each $\lambda \in \Lambda$, $C_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$. 
   which is uniformly $k$-controlled by $R_C$ on $\mathcal D_0$ for a given function $k:[0,\infty) \to [0, \infty)$.
@@
   \item[(2)]
-    % Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$.
-    % Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D_0$ for some function $g: [0,\infty) \to [0,\infty)$.
     $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$ and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$;
@@
     For any $a>0$, $(C^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(k^a)$-controllable.
-    % Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
-    % Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D$ for some function $g: [0,\infty) \to [0,\infty)$.
   \item[(4)]
-    % Let $a>0$.
-    % Suppose that, for each $\lambda \in \Lambda$, $A_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
     Suppose further that $(\Lambda, \mathscr F)$ is a measurable space and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
@@
 \end{lem}
+\end{comment}
+The following lemma is easy to verify.
+\begin{lem}
+  \label{lem: property of controllable operators}
+  For each $i \in \{0,1\}$, let $\mathscr O_i$ be a family of operators which is  uniformly controlled by an $h_i$-controller $R_i$ from $\mathcal D_i \subset \mathcal P^*$ to $ \mathcal I_i \subset \mathcal P^*$.
+  Then the followings hold: 
+  \begin{enumerate}
+  \item 
+    If $\mathcal I_0 \subset \mathcal D_1$, then $\{A_1A_0: A_i \in \mathscr O_i, i = 0,1\}$ is uniformly controlled by the $(h_1 \circ h_0)$-controller $R_1R_0$ from $\mathcal D_0$ to $\mathcal I_1$;
+  \item
+    $\{ A_1 \times A_0: A_i \in \mathscr O_i, i = 0,1\}$ is uniformly controlled by the $(h_1\times h_0)$-controller $R_1 \times R_0$ from $\mathcal D_0 \cap \mathcal D_1$ to $\mathcal P^*$.
+  \item
+    $\{ A_1 + A_0: A_i \in \mathscr O_i, i = 0,1\}$ is uniformly controlled by the $(h_1 \vee h_0)$-controller $R_1 + R_0$ from $\mathcal D_0 \cap \mathcal D_1$ to $\mathcal P^*$. 
+\item 
+    If $\mathcal I_0 \subset \mathcal B(\mathbb R^d, \mathbb C \setminus (\infty, 0])$ and $a>0$, then $\{A^{\times a} : A \in \mathscr O_0\}$ is uniformly controlled by the $(h_0^a)$-controller $R_0^{\times a}$ from $\mathcal D_0$ to $\mathcal P^*$.
+  \item
+    Suppose that $\mathcal O_0 = \{A_\theta: \theta \in \Theta \}$ where $\Theta$ is an index set. 
+    Further suppose that $(\Theta, \mathcal J )$ is a measurable space and that $(\theta,x) \mapsto A_\theta f(x)$ is $\mathcal J \otimes \mathcal B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
+    Then the following space of operators
+    \[
+      \Big\{ f \mapsto \int_{\Theta} A_\theta f~\nu(d\theta) : \nu \text{ is a probability measure on } (\Theta, \mathcal J) \Big\}
+    \] 
+    is uniformly controlled by $R_0$ from $\mathcal D_0$ to $\mathcal P^*$.
+\end{enumerate}  
+\end{lem}
+% END MODIFIED
+
+% DELETED
+\begin{comment}
 \begin{proof}
   (1). 
-  % Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by  an $h$-controller $R_A$ on $\mathcal D$.
-  % Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D_0$.
-  % Then we have
-  % \begin{itemize}
-  % \item
-  %   For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, we have $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
-  % \item
-  %   If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_AR_Bf \leq R_A R_B g$.
-  % \item
-  %   If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_AR_B(\theta f) \leq R_A(g(\theta) R_Bf) \leq (h\circ g)(\theta) R_A R_B f $.
-  % \end{itemize}
   If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, then $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
@@
   (2). 
-  % Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R_A$ on $\mathcal D$.
-  % Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
-  % Then we have
-  % \begin{itemize}
-  % \item
-  %   For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
-  % \item
-  %   If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_A\times R_Bf \leq R_A\times R_B g$.
-  % \item
-  %   If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_A\times R_B (\theta f) \leq h(\theta) g(\theta) (R_A \times R_B) f $.
-  % \end{itemize}
-  % Therefore $(A_\lambda \times B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \times g)$-controllable on $\mathcal D$.
   If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, then $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
@@
 
-  % We also have the following:
-  % \begin{itemize}
-  % \item
-  %   For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
-  % \item
-  %   If $f,g \in \mathcal P^+$ with $f\leq g$, then $(R_A + R_B)f \leq (R_A + R_B) g$.
-  % \item
-  %   If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $(R_A + R_B) (\theta f) \leq h(\theta) R_Af + g(\theta) R_Bf \leq (h(\theta) \vee g(\theta)) (R_A+R_B)f $.
-  % \end{itemize}
-  % Therefore $(A_\lambda + B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \vee g)$-controllable on $\mathcal D$.
   If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, then $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
@@
   (3). 
-  % Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
-  % Then we have the following:
-  % \begin{itemize}
-  % \item
-  %   For each $\lambda \in \Lambda$, $f\in \mathcal D$, we have $|A_\lambda^{\times a} f| = |A_\lambda f|^a  \leq R^{\times a} |f|$.
-  % \item
-  %   If $f,g \in \mathcal P^+$ with $f\leq g$, then $R^{\times a}f \leq R^{\times a} g$.
-  % \item
-  %   If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R^{\times a}(\theta f) \leq (h(\theta) R f)^a = h(\theta)^a R^{\times a}f$.
-  % \end{itemize}
-  % Therefore $(A_\lambda^{\times a})_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable on $\mathcal D$.
   If $\lambda \in \Lambda$, $f\in \mathcal D$, then $|C_\lambda^{\times a} f| = |C_\lambda f|^a  \leq R_C^{\times a} |f|$.
@@
   (4).     
-  % Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
   For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
@@
 \end{proof}
-
-% ** h-controller for super-OU processes
-\subsection{h-controller for super-OU processes}
+\end{comment}
+% END DELETED
+% ** h-controller for super-OU processes% \subsection{h-controller for super-OU processes}
+\subsection{Controllers for super-OU processes}
 \label{sec: h-controller}
@@
 
-Define
-\begin{align}
-  \label{eq: psi 0}
-  \psi_0(z)
-  = \psi(z) + \alpha z
-  , \quad z\in \mathbb{R}_+
-\end{align}
-Using an argument similar to the proof  of Lemma \ref{lem: complex extension for psi1},
-% both functions $\psi$, $\psi_0$ 
-$\psi, \psi_1$ and $\psi_0$ 
-can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C^0_+$.
-For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, we define
-% \begin{align}
-%   \label{eq: def of operator Psi}
-%   \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
-%   \\ \Psi_0 f(x) &:= \Psi f(x) + \alpha f(x),
-%   \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big).
-% \end{align}
-$\Psi f (x) = -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big)$. $\Psi_1 f(x)$ and
-$Psi_0 f(x)$ are defined similarly.
+Define $\psi_0(z) = \psi(z) + \alpha z$ for each $z\in \mathbb{R}_+$.
+% Using an argument similar to the proof of Lemma \ref{lem: complex extension for psi1}, $\psi, \psi_0$ and $\psi_1$ can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C^0_+$.
+According to Lemma \ref{lem: complex extension for psi1}, $\psi, \psi_1$ and $\psi_0$ can all be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are also holomorphic on $\mathbb C^0_+$.
+For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define
+$\Psi f (x) = \psi\circ f(x)$, $\Psi_0 f(x)= \psi_0 \circ f(x)$ and $\Psi_1 f(x)= \psi_1 \circ f(x)$.
+
 For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let
@@
 \end{align}
+
 For all $t\geq 0$ and $f\in \mathcal P$, we define
@@
   \label{eq: def of Zf}
-  & Z_t f
+  Z_t f
     := \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,
-    % \\ Z'_t f
-  \qquad Z'_t f
+    & \qquad Z'_t f
     := \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,\\
-  &  Z''_t f
+   Z''_t f
     := \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
-    % \\ Z'''_t f
-  \qquad \qquad\  Z'''_t f
+    &\qquad\  Z'''_t f
     := (Z'_t - Z_t+ Z''_t)f.
@@
   Q_\kappa f
-  % := \sup_{t\geq 0} e^{\kappa b t}|P_t f|
-  := \sup_{t\geq 0} e^{\kappa b t}|P_t f|, \qquad  Q f:= Q_{\kappa_f}f.
-\end{equation}
-% and
-% \begin{equation}
-%   \label{Q}
-%   Q f:= Q_{\kappa_f}f.
-% \end{equation}
+  := \sup_{t\geq 0} e^{\kappa b t}|P_t f|, 
+  \qquad  Q f
+  := Q_{\kappa_f}f.
+\end{equation}
 Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
@@
   (4). 
-  % From parts (1)--(3) of this lemma and Lemma \ref{lem: property of controllable operators}.(2), 
   From (1)--(3) above and Lemma \ref{lem: property of controllable operators}.(1), we know that the operators
@@
   Combining this with \eqref{eq:chareq2} and 
-  % Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.
   Lemma \ref{lem: property of controllable operators}.(4), we get the desired result.
@@
   \]
-  % Now using parts (1), (2) and  (4) of this lemma, and Lemma \ref{lem: property of controllable operators}.(3)--(4), we get that operators
   Now using (1), (2) and  (4) above, and Lemma \ref{lem: property of controllable operators}.(2)--(3), we get that the operators
@@
 \begin{proof}
-  % (1). See \cite[Lemma 2.7]{MarksMilos2018CLT}.
-  (1) is  \cite[Lemma 2.7]{MarksMilos2018CLT} (3) is \cite[Lemma 4.2]{MarksMilos2018CLT}.
-  is obvious from (2), noticing that $\alpha\beta>K(1+\beta)b$. (5) is obvious from (1).
-  So we only need to  (2). We first claim that there exists $h\in \mathcal{P}$ such that
+  (1) is  \cite[Lemma 2.7]{MarksMilos2018CLT}; (3) is obvious from (2) noticing that $\alpha\beta>K(1+\beta)b$; (4) is \cite[Lemma 4.2]{MarksMilos2018CLT}; and (5) is obvious from (1).
+  So we only need to show (2). 
+  We first claim that there exists $h\in \mathcal{P}$ such that
   \begin{align}
@@
 \end{align}
-%
-% (3). This is obvious from (2), noticing that $\alpha\beta>K(1+\beta)b$.
-% 
-% (4). See \cite[Lemma 4.2]{MarksMilos2018CLT}.
-% 
-% (5). This is obvious from (1).
 \end{proof}
@@
   \end{align}
-  Then there exists $h\in \mathcal{P}$ such that
-  % \begin{align}
-  %   |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
-  % \end{align}
-  $|P_sg_k|\leq e^{-bs}h$ for all $s, k \geq 0.$
+  Then there exists $h\in \mathcal{P}$ such that $|P_sg_k|\leq e^{-bs}h$ for all $s, k \geq 0.$
 \end{lem}
@@
   \end{align}
-  Then there exists $h\in \mathcal{P}$ such that
-  % \begin{align}
-  %   |P_s\bar{g}_t|
-  %   \leq e^{-bs}h,\quad s\geq 0, t\geq 0.
-  % \end{align}
-  $|P_s\bar{g}_t| \leq e^{-bs}h$ for all $s, t\geq 0.$
+  Then there exists $h\in \mathcal{P}$ such that $|P_s\bar{g}_t| \leq e^{-bs}h$ for all $s, t\geq 0.$
 \end{lem}
@@
 In particular, it contains the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$ for each $s\geq 0$.
-% Also, note that
-% \[
-%   |\sqrt {1-\theta} - 1| \leq \theta, \quad \theta\in [0,1]
-% \]
-$ | \sqrt { 1 - \theta } - 1 | \leq \theta $ for all $ \theta \in [ 0, 1 ] $,
-and
-% \[
-%   1+\theta + \lambda \leq (1+\theta)(1+\lambda), \quad \theta ,\lambda \geq 0.
-% \]
-$ 1 + \theta + \lambda \leq ( 1 + \theta ) ( 1 + \lambda ) $ for all $ \theta, \lambda \geq 0$.
+Also, note that $ | \sqrt { 1 - \theta } - 1 | \leq \theta $ for all $ \theta \in [ 0, 1 ] $, and that $ 1 + \theta + \lambda \leq ( 1 + \theta ) ( 1 + \lambda ) $ for all $ \theta, \lambda \geq 0$.
 Using the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we get that for all $s,t\geq 0, x\in \mathbb R^d$,
@@
   \end{equation}
-  It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, 
-  % the following statements are true:
-  % \begin{itemize}
-  % \item
-  %   $0\leq \bar v_t < \infty$ for all $t>0$.
-  % \item
-  %   $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
-  % \end{itemize}
-  we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; and (ii) $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
+  It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; and (ii) $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
   Letting $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
@@
   Also notice that $\psi'(0+)=-\alpha <0$ and that there exists $z>0$ such that $\psi(z)>0$.
-  Therefore we have
-  % \begin{itemize}
-  % \item
-  %   $\bar v > 0$ ,
-  % \item
-  %   $\psi(z) < 0$ on $z\in (0,\bar v)$,
-  % \item
-  %   $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
-  % \end{itemize}
-  (i) $\bar v > 0$; (ii) $\psi(z) < 0$ on $z\in (0,\bar v)$; and (iii) $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
+  Therefore we have (i) $\bar v > 0$; (ii) $\psi(z) < 0$ on $z\in (0,\bar v)$; and (iii) $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
   It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that
@@
   In fact, since $\psi$ is a convex function, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for each $z\geq \bar v$.
-  According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
-  % \[
-  %   t_0
-  %   := \int^\infty_{z_0} \frac{dz}{\psi(z)} < \infty.
-  % \]
-  $t_0 := \int^\infty_{z_0}\psi(z)^{-1}dz<\infty$.
+  According to Grey's condition, we can find a constant $z_0 >\bar v $ such that $t_0 := \int^\infty_{z_0}\psi(z)^{-1}dz<\infty$.
   For each $t > t_0$, according to \eqref{eq:svp2}, we have
@@
   \end{align}
-  Rearranging, we get
-  % \[
-  $
-  \bar v_t - \bar v \leq (z_0 - \bar v)e^{-\tau(t-t_0)},
-  % \quad t\geq t_0.
-  $ for all $t\geq t_0$.
-  % \]
+  Rearranging, we get $ \bar v_t - \bar v \leq (z_0 - \bar v)e^{-\tau(t-t_0)}, $ for all $t\geq t_0$.
   This implies the desired result in this step.
@@
   \]
-  Define
-  % \[
-  %   \rho_t := 1+ \frac{\log k_t}{t\alpha}, \quad t\geq 0.
-  % \]
-  $\rho_t := 1+(\log k_t)/(t\alpha)$ for all $t\geq 0$.
-  % According to the fact that
-  % \[
-  %   k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}, \quad t\geq 0,
-  % \]
+  Define $\rho_t := 1+(\log k_t)/(t\alpha)$ for all $t\geq 0$.
   By the fact that $k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}$ for  all $t\geq 0$ and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
@@
   & = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
-  % \\&
   \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big] \\
@@
 \end{proof}
-For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write
-% \[
-$
-\|Y\|_{\mathbb P;p}
-:= \mathbb P[|Y|^p]^{1/p}.
-% \]
-$
+For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write $ \|Y\|_{\mathbb P;p} := \mathbb P[|Y|^p]^{1/p}. $
 \begin{lem}
@@
   & \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-  % \\ &
-         \leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma} + |\langle P^\alpha_t g,\mu\rangle|
-  \\ & \leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
+    \leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma} + |\langle P^\alpha_t g,\mu\rangle| \\
+  & \leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
 \end{align}
@@
   & \quad\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
-  % \\ &
     =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big] \\
-  & =e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du
-  % \\&\quad 
-  - \int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
+  & =e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du - \int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
 \end{align}
@@
   For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
-Moreover, if $\alpha\beta>|p|b(1+\beta)$, then, for all $\gamma\in (0, \beta)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
-  % \[
-  $
-  H_{\infty}^p
-  := \lim_{t\rightarrow \infty}H_t^p
-  % \]
-  $
-  exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
+Moreover, if $\alpha\beta>|p|b(1+\beta)$, then, for all $\gamma\in (0, \beta)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $ exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
 \end{lem}
@@
 \begin{align}
-	& \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
-	\\ & \leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
-	\\ & \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
-  %	\\ &
+	& \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma} \\
+	& \leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma} \\
+	& \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
    \leq C_2e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
@@
 For $a \geq 0$, $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
-% \begin{equation}
 \begin{align}
@@
   & :=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,\\
-  % \end{equation}
-  % and
-  % \begin{equation}
   Y_t^{g,a}
   & :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
-  % \end{equation}
 \end{align}
@@
 \end{equation}
-where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
-% \[
-%   \mathbf{E}(e^{i\theta\zeta_k})
-%   =\exp(m_k[\theta f]),\quad \theta \in \mathbb R.
-% \]
-$\theta\mapsto \exp(m_k[\theta f])$.
+where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(m_k[\theta f])$.
 \end{lem}
@@
 \end{align}
-From Proposition \ref{prop: alpha stable rv}.(1), we have
-% \begin{equation}
-%   \label{eq: need2}
-%   \operatorname {Re} m_t[f] < 0.
-% \end{equation}
-$\operatorname {Re} m_t[f] < 0$. 
-% Using \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
-Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact
-% \[
-%   |e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
-% \]
-$|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+From Proposition \ref{prop: alpha stable rv}.(1), we have $\operatorname {Re} m_t[f] < 0$. 
+Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
 \begin{align}
@@
   & \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c\big]\big|
-  % \\ & 
     \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big] \\
@@
     \leq R(|\theta_{t,k}P^\alpha_k f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
-    % \\&
-  \leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
-  \\ & \leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf
-  \\ & \leq\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
-  % \\ &
+  \leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big) \\
+  & \leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf \\
+  & \leq\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
     \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
 \end{align}
-% where $Q$ is defined by \eqref{Q}.
 where $Q$ is defined by \eqref{Q_k}.
@@
 \end{align}
-% where $Q$ is defined by \eqref{Q}.
 where $Q$ is defined by \eqref{Q_k}.
@@
 Step 3.
-We will show that for $\epsilon>0$ small enough there exist $C_2, \delta_2>0$ such that
-% \begin{equation}\label{eq:31step3}
-$
-J_2(t,k,\epsilon)
-\leq C_2e^{-\delta_2 (t-k)},
-\quad k\geq 0, t\geq k+1.
-% \end{equation}
-$
+We will show that for $\epsilon>0$ small enough there exist $C_2, \delta_2>0$ such that $ J_2(t,k,\epsilon) \leq C_2e^{-\delta_2 (t-k)},$ for each $k\geq 0, t\geq k+1.$
 
@@
   & =e^{-\alpha(k+1)}\langle \eta \int_0^1P_{1-s}^{\alpha}(-iP_{s+k}^\alpha g(x))^{1+\beta}~ds, \varphi \rangle
-  % \\&
   =e^{-\alpha(k+1)}\langle Z_1(P_k^{\alpha}g), \varphi \rangle.
@@
   \langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]
-  % \\ &
     & = \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha (k+1)}\langle  Z_1P^\alpha_k f,\varphi\rangle
@@
   & = C_3 e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
-  % \\ &
     \leq C_3 e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
@@
 Step 4.
-We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_3>0$ such that for all $k\geq0, t\geq k+1$,
-% \begin{equation}\label{ineq: control of J3}
-$
+We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_3>0$ such that for all $k\geq0, t\geq k+1$, $
 J_3(t,k,\epsilon)\leq C_4e^{-\delta_3 (t-k)}.
@@
 In fact, we have  for all $t\geq 0, \epsilon >0$,
-% \begin{align}
-%   &
 \[   
@@
   = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
-  % \\ &
   = \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
   \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
-  % \end{align}
 \]
@@
     & \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-      %     \\&
     \leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
@@
 \]
-Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$,
-% \[
-$
-J^{\pm \theta f}_2(t,k,\epsilon)
-= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon).
-$
-% \]
+Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$, $ J^{\pm \theta f}_2(t,k,\epsilon)
+= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon). $
 According to this and \eqref{eq: right bound for J2},
@@
     & a_{k-1} - a_k
-    % \\&
     =\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big] \\
@@
     & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
-    % \\ & 
     \leq C e^{-\delta(t-k)}.
@@
     & \mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
-      %     \\&
     \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}) \\
@@
       = C_8 e^{-\delta_6 t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta_6 k}
-      % \\ &
       \leq C_9 e^{-\delta_6 t}e^{\delta_6 (t-\ln t)}
@@
     & = t^{-\frac{1}{1+\beta}} e^{\frac{\beta \alpha t}{1+\beta} - k_fbt} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
-%	\\& 
       = t^{-\frac{1}{1+\beta}} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
@@
   By assumption, $f\in \mathcal P$ is non-trivial and satisfies $\alpha \beta < \kappa_f b(1+\beta)$.
-	Let $t_0 > 1$ be large enough so that
-  % \[
-  $	\lceil t - \ln t\rceil
-	\leq \lfloor t \rfloor - 1,
-  % \quad t\geq t_0.
-  $ for all $t\geq t_0$.
-  % \]
+	Let $t_0 > 1$ be large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1, $ for all $t\geq t_0$.
   Fix $\mu\in \mathcal M_c(\mathbb R^d)$ and write
@@
     & \leq C_3( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)})
-    % \\& 
     \leq C_4e^{-\delta_3 (t-k)}.
@@
   \]
-	Recall that
-  % \[
-  %   A_t(\epsilon)
-  %   :=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
-  %   \quad t\geq 0.
-  % \]
-  $A_t(\epsilon)=\{\|X_t\|>e^{(\alpha-\epsilon )t}\}$.
+	Recall that $A_t(\epsilon)=\{\|X_t\|>e^{(\alpha-\epsilon )t}\}$.
   By \eqref{lem: control of XT}, there exist $C_5,\delta_4>0$ such that
@@
       \leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
-      % \\& 
       = e^{(\frac{\beta \alpha }{1+\beta} - k_fb)t} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
@@
 \end{align}
-	where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function
-  % \begin{align}
-  %   \mathbf{E}[e^{i\theta \bar{\zeta}_n}]=\exp(\bar{m}_n[\theta g]),\quad \theta\in \mathbb{R}.
-  % \end{align}
-  $\theta\mapsto \exp(\bar{m}_n[\theta g])$.
+	where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(\bar{m}_n[\theta g])$.
 \end{lem}
@@
 
-  According to \eqref{eq: need11} and the fact that
-  % \[
-  %   |e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
-  % \]
-  $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$,
+  According to \eqref{eq: need11} and the fact that $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$,
   we have for all $n\geq 1, t\geq 0$ and $\epsilon> 0$,
@@
     & \big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
-    % \\& 
     \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c | \mathscr F_{t+n-1}]\big|\Big] \\
@@
   Step 2.
-  We will show that for $\epsilon>0$ small enough, there exist $C_1,\delta_1>0$ such that for all $n\geq 1$ and $t\geq 0$,
-  % \begin{align}\label{eq:large rate J1}
-  $ J'_1(t,n,\epsilon)\leq C_1 e^{-\delta_1(t+n)}. $
-  % \end{align}
+  We will show that for $\epsilon>0$ small enough, there exist $C_1,\delta_1>0$ such that for all $n\geq 1$ and $t\geq 0$, $ J'_1(t,n,\epsilon)\leq C_1 e^{-\delta_1(t+n)}. $
   Let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
@@
   Step 3.
-  We will show that for each $\epsilon > 0$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$,
-  % \begin{align}
-  %   \label{eq:31step31}
-  $ J'_2(t,n,\epsilon) \leq C_2 e^{-\delta_2(t+n)}.
-  % \end{align}
-  $
+  We will show that for each $\epsilon > 0$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$, $ J'_2(t,n,\epsilon) \leq C_2 e^{-\delta_2(t+n)}.$
   In fact, according to the definitions of $Z_1$ and $\bar{m}_n$, and \eqref{equ: transform of mn}, we have for all $t\geq 0, n\geq1$,
@@
     & \langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]
-    % \\ &
       = e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
@@
    & = C_3 e^{-\alpha} e^{ - ( \alpha \beta - K ( 1 + \beta ) b ) n } e^{ - ( \frac{ \alpha \gamma } { 1 + \gamma } - \epsilon ) ( t + n - 1 ) }
-   % \\&
      \leq C_3 e^{-( \frac{ \alpha \gamma } { 1 + \gamma } - \epsilon ) ( t + n - 1 ) }.
@@
 
-  Step 4. According to the Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that
-  % \begin{align}\label{ineq: control of J31}
-  %   J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}\quad t\geq0, n\geq 1.
-  % \end{align}
-  $ J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}$ for all $ t\geq0, n\geq 1$.
+  Step 4.
+According to the Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that $ J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}$ for all $ t\geq0, n\geq 1$.
 
@@
     & \widetilde{a}_{n-1} - \widetilde{a}_n
-    % \\&
       = \mathbb{P}_{ \mu } ( D^c )^{ - 1 } \mathbb{P}_{ \mu } \Big[ \Big( \prod_{ l=0 }^{n - 1 } e^{ i \theta \bar{ \gamma }_{ t, l} } \Big) \times ( e^{ \bar{m}_n [ \theta g ] } - e^{ i \theta \bar{ \gamma }_{t, n}}) ; D^c \Big] \times \prod_{ l = n + 1}^{ m } e^{\bar{ m }_l[ \theta g ] } \\
@@
     & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
-    % \\& 
     \leq C_2 e^{-\delta_1(t+n-1)}.
@@
   \end{align}
-  where
-  % \begin{align}
-  %   Y''_{t,n}
-  %   :=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},  \quad t\geq 0, n\geq 1.
-  % \end{align}
-  $Y''_{t,n}:=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}}$.
+  where $Y''_{t,n}:=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}}$.
   Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
@@
     > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0,
-    % \]
-    % and
-    % \[
     \qquad
@@
 
-  Step 1. Similar to Step 1 in the proof of Theorem \ref{thm: critical clt}, we can show that there exist $C_1,\delta_1 >0$ such that for all $n \geq 1$ and $t\geq 0$,
-  % \begin{align}
-  %   \label{thm12111}
-  $
-  \mathbb{\widetilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}^c_{t,n}}\big]
-  \leq C_1 e^{-\delta_1 t}.
-  % \end{align}
+  Step 1. 
+  Similar to Step 1 in the proof of Theorem \ref{thm: critical clt}, we can show that there exist $C_1,\delta_1 >0$ such that for all $n \geq 1$ and $t\geq 0$, $ \mathbb{ \widetilde{ P } }_{ \mu } \big[ | Y''_{ t, n } | \mathbf{ 1 }_{ \mathcal{ D }^c_{t, n } } \big] \leq C_1 e^{-\delta_1 t}.
 $
@@
   Then the functions
-  % \begin{equation}
   \begin{align}
     & h (z) 
-      = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+
-      % \end{equation}
-      % and
-      % \begin{equation}
-      %   \label{eq: deriavetive of the Poission partb}
-    \\ & h'(z) 
+      = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+ \\ 
+    & h'(z) 
       = \int_{(0,\infty)}(1- e^{-zy})y \pi(dy), \quad z \in \mathbb C_+
-         % \end{equation}
   \end{align}
@@
 
-% Recall that the Gamma function  $\Gamma$ is defined by
-% \begin{equation}
-%   \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
-%   \quad x>0.
-% \end{equation}
-It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
+% It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
+It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the Gamma function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
 \[
@@
 \end{equation}
-% by showing that the both sides
-% \begin{itemize}
-% \item
-%   are extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
-% \item
-%   are holomorphic on $\mathbb C_+^0$;
-% \item
-%   are continuous on $\mathbb C_+$.
-% \end{itemize}
-are (i)  extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
-(ii) holomorphic on $\mathbb C_+^0$ and (iii) continuous on $\mathbb C_+$.
-Similarly, we get that
+% are (i)  extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$; (ii) holomorphic on $\mathbb C_+^0$ and (iii) continuous on $\mathbb C_+$.
+% Similarly, we get that
+and similarly that
 \begin{equation}
@@
 Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued}, there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
-% \begin{itemize}
-% \item
-%   $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
-% \item
-%   $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
-% \item
-%   for any $\mu \in \mathcal M(E)$, 
-%   if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
-%   then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
-% \end{itemize}
-(i) $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$; (ii) $\mathbb N_x(\|W_0 \|\neq 0) = 0$
-and (iii) if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
-% then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
+(i) $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$; 
+(ii) $\mathbb N_x(\|W_0 \|\neq 0) = 0$; 
+and (iii) if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
 We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
@@
   \begin{align}
-    \label{eq: upper bound of psi'(v)}
     & |\psi'(x, -U_tf)| \\
@@
     & \leq \|\rho_1\|_\infty + 2\rho_2(x)\mathbb N_x[\langle W_t, |f|\rangle]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge \langle X_t, |f|\rangle] \pi(x,dy) \\ 
-    & \leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty
-    P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy) \\ 
-    & =: C_1 + C_2(P^{\rho_1}_t |f|)(x),
+    & \leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy) \\ 
+    & =: C_1 + C_2(P^{\rho_1}_t |f|)(x), \label{eq: upper bound of psi'(v)}
   \end{align}
   where $C_1, C_2$ are constants independent on $f,x$ and $t$.
-  Now, 
-  % combining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, 
-  combining the display above with \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bounded for derivative of v(theta)}
+  Now, combining the display above with \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bounded for derivative of v(theta)}
   we get the desired result.
@@
   & \Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
-  % \\&
   \leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big] \\ 
@@
 \end{equation}
-% and
 \begin{equation}
@@
     \\ & = \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
-    % \\ &
     = \frac{1}{P_t^{\rho_1} g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
@@
 
-% From \eqref{eq: upper bound of psi'(v)},
-From the display below \eqref{eq: path integration representation of psi(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e.
-bounded on $[0,T]\times E$ for each $T \geq 0$).
+ From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
 Therefore, we can apply Lemma \ref{eq: complex FK} and get that
@@
 Integrating the two displays above with respect to $\theta$  on [0,1], using 
-% \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get Fubini's theorem, \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and the display below it, we get
+Fubini's theorem, \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bound of psi'(v)}, we get
 \begin{equation}
@@
 \end{equation}
-% Notice the following:
 Note that 
-% \begin{itemize}
-% \item
-%   It is clear that $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$.
-% \item
-%   $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$ due to \eqref{eq: N and characteristic exponent}, the dominated convergence theorem and the fact that
-%   \[
-%     |e^{i W_t(f_n)} - 1| \leq \langle W_t, |f|\rangle;
-%     \quad \mathbb N_x[\langle W_t, |f|\rangle] = (P_t^{\rho_1} |f|)(x) < \infty.
-%   \]
-% \item
-%   $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
-%   \begin{equation}
-%     \big|\psi(\xi_s,- U_{t-s}f_n)\big|
-%     \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2.
-%   \end{equation}
-% \end{itemize}
-% Using the above arguments, 
 (i) $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$;
@@
 
-\medskip
-\noindent
-{\bf Acknowledgment:}
+\subsection*{Acknowledgment}
 We thank Zenghu Li and Rui Zhang for helpful conversations.
-% new
 We also thank the referee for very helpful comments.
-% end new
-\medskip
-
-\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
+
 \begin{thebibliography}{10}
@@
 \bibitem{AdamczakMilos2015CLT}
-R.~Adamczak and P.~Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
-  Electron. J. Probab. \textbf{20} (2015), no.~42, 35 pp.
+  R. Adamczak and P. Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
+  Electron. J. Probab. \textbf{20} (2015), no. 42, 35 pp.
 
 \bibitem{Asmussen76Convergence}
-  S.~Asmussen, \emph{Convergence rates for branching processes}, Ann.
-  Probab.  \textbf{4} (1976), no.~1, 139--146.
+  S. Asmussen, \emph{Convergence rates for branching processes}, 
+  Ann. Probab.  \textbf{4} (1976), no. 1, 139--146.
 
 \bibitem{AsmussenHering1983Branching}
-S.~Asmussen and H.~Hering, \emph{Branching processes}, Progress in Probability
-  and Statistics, vol.~3, Birkh\"{a}user Boston, Inc., Boston, MA, 1983.
+  S. Asmussen and H. Hering, \emph{Branching processes}, 
+  Progress in Probability and Statistics, 3. Birkh\"{a}user Boston, Inc., Boston, MA, 1983.
 
 \bibitem{Athreya1969Limit}
-K.~B. Athreya, \emph{Limit theorems for multitype continuous time {M}arkov
-  branching processes. {I}. {T}he case of an eigenvector linear functional}, Z.
-  Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{12} (1969), 320--332.
+  K. B. Athreya,  
+  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {I}. {T}he case of an eigenvector linear functional}, 
+  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{12} (1969), 320--332.
 
 \bibitem{Athreya1969LimitB}
-\bysame, \emph{Limit theorems for multitype continuous time {M}arkov branching
-  processes. {II}. {T}he case of an arbitrary linear functional}, Z.
-  Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{13} (1969), 204--214.
+  K. B. Athreya, 
+  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {II}. {T}he case of an arbitrary linear functional}, 
+  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{13} (1969), 204--214.
 
 \bibitem{Athreya1971Some}
-\bysame, \emph{Some refinements in the theory of supercritical multitype
-  {M}arkov branching processes}, Z. Wahrscheinlichkeitstheorie und Verw.
-  Gebiete \textbf{20} (1971), 47--57.
+  K. B. Athreya, 
+  \emph{Some refinements in the theory of supercritical multitype {M}arkov branching processes}, 
+  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{20} (1971), 47--57.
 
 \bibitem{ChenRenWang2008An-almost}
-Z.-Q. Chen, Y.-X. Ren, and H.~Wang, \emph{An almost sure scaling limit theorem
-  for {D}awson-{W}atanabe superprocesses}, J. Funct. Anal. \textbf{254} (2008),
-  no.~7, 1988--2019.
-
- \bibitem{ChenRenSongZhang2015Strong-law} Z.-Q. Chen, Y.-X. Ren, R. Song, and R. Zhang,
- \emph{Strong law of large numbers for supercritical superprocesses under second moment condition}, Front. Math. China \textbf{10} (2015), no.~4, 807--838.
-
- \bibitem{ChenRenYang2019Skeleton} Z.-Q. Chen, Y.-X. Ren,  and T. Yang,
- \emph{Skeleton decomposition and law of large numbers for supercritical superprocesses}, Acta Appl. Math. \textbf{159} (2019), no.~1, 225--285.
+  Z.-Q. Chen, Y.-X. Ren, and H. Wang, 
+  \emph{An almost sure scaling limit theorem for {D}awson-{W}atanabe superprocesses}, 
+  J. Funct. Anal. \textbf{254} (2008), no. 7, 1988--2019.
+
+ \bibitem{ChenRenSongZhang2015Strong-law} 
+   Z.-Q. Chen, Y.-X. Ren, R. Song, and R. Zhang,
+   \emph{Strong law of large numbers for supercritical superprocesses under second moment condition}, 
+   Front. Math. China \textbf{10} (2015), no. 4, 807--838.
+
+ \bibitem{ChenRenYang2019Skeleton} 
+   Z.-Q. Chen, Y.-X. Ren, and T. Yang,
+   \emph{Skeleton decomposition and law of large numbers for supercritical superprocesses}, 
+   Acta Appl. Math. \textbf{159} (2019), 225--285.
 
  \bibitem{Durrett2010Probability}
-R.~Durrett, \emph{Probability: theory and examples}, 4 ed., Cambridge Series in
-  Statistical and Probabilistic Mathematics, vol.~31, Cambridge University
-  Press, Cambridge, 2010.
+   R. Durrett, 
+   \emph{Probability: theory and examples}, 
+   Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
 
 \bibitem{Dynkin1993Superprocesses}
-E.~B. Dynkin, \emph{Superprocesses and partial differential equations}, Ann.
-  Probab. \textbf{21} (1993), no.~3, 1185--1262.
+  E. B. Dynkin, 
+  \emph{Superprocesses and partial differential equations}, 
+  Ann. Probab. \textbf{21} (1993), no. 3, 1185--1262.
 
 \bibitem{EckhoffKyprianouWinkel2015Spines}
-M.~Eckhoff, A.~E. Kyprianou, and M.~Winkel, \emph{Spines, skeletons and the
-  strong law of large numbers for superdiffusions}, Ann. Probab. \textbf{43}
-  (2015), no.~5, 2545--2610.
+  M. Eckhoff, A. E. Kyprianou, and M. Winkel, 
+  \emph{Spines, skeletons and the strong law of large numbers for superdiffusions}, 
+  Ann. Probab. \textbf{43} (2015), no. 5, 2545--2610.
 
 \bibitem{Englander2009Law}
-J.~Engl\"{a}nder, \emph{Law of large numbers for superdiffusions: the
-  non-ergodic case}, Ann. Inst. Henri Poincar\'{e} Probab. Stat. \textbf{45}
-  (2009), no.~1, 1--6.
+  J. Engl\"{a}nder, 
+  \emph{Law of large numbers for superdiffusions: the non-ergodic case}, 
+  Ann. Inst. Henri Poincar\'{e} Probab. Stat. \textbf{45} (2009), no. 1, 1--6.
 
 \bibitem{EnglanderWinter2006Law}
-J.~Engl\"{a}nder and A.~Winter, \emph{Law of large numbers for a class of
-  superdiffusions}, Ann. Inst. H. Poincar\'{e} Probab. Statist. \textbf{42}
-  (2006), no.~2, 171--185.
+  J. Engl\"{a}nder and A. Winter, 
+  \emph{Law of large numbers for a class of superdiffusions}, 
+  Ann. Inst. H. Poincar\'{e} Probab. Statist. \textbf{42} (2006), no. 2, 171--185.
 
 \bibitem{EnglanderTuraev2002A-scaling}
-J.~Engl\"{a}nder and  D. ~Turaev, \emph{A scaling limit theorem for a class of superdiffusions}. Ann Probab., \textbf{30} (2002),  683--722.
+  J. Engl\"{a}nder and  D. Turaev, 
+  \emph{A scaling limit theorem for a class of superdiffusions}, 
+  Ann. Probab. \textbf{30} (2002), no. 2, 683--722.
 
 \bibitem{Heyde1970A-rate}
-C.~C. Heyde, \emph{A rate of convergence result for the super-critical
-  {G}alton-{W}atson process}, J. Appl. Probability \textbf{7} (1970), 451--454.
+  C. C. Heyde, 
+  \emph{A rate of convergence result for the super-critical {G}alton-{W}atson process}, 
+  J. Appl. Probability \textbf{7} (1970), 451--454.
 
 \bibitem{Heyde1971Some}
-\bysame, \emph{Some central limit analogues for supercritical {G}alton-{W}atson
-  processes}, J. Appl. Probability \textbf{8} (1971), 52--59.
+  C. C. Heyde, 
+  % \emph{some central limit analogues for supercritical {g}alton-{w}atson processes}, 
+  \emph{some central limit analogues for supercritical {G}alton-{W}atson processes}, 
+  J. Appl. Probability \textbf{8} (1971), 52--59.
 
 \bibitem{HeydeBrown1871An-invariance}
-C.~C. Heyde and B.~M. Brown, \emph{An invariance principle and some convergence
-  rate results for branching processes}, Z. Wahrscheinlichkeitstheorie und
-  Verw. Gebiete \textbf{20} (1971), 271--278.
+  C. C. Heyde and B. M. Brown, 
+  \emph{An invariance principle and some convergence rate results for branching processes}, 
+  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete, \textbf{20} (1971), 271--278.
 
 \bibitem{HeydeLeslie1971Improved}
-C.~C. Heyde and J.~R. Leslie, \emph{Improved classical limit analogues for
-  {G}alton-{W}atson processes with or without immigration}, Bull. Austral.
-  Math. Soc. \textbf{5} (1971), 145--155.
+  C. C. Heyde and J. R. Leslie, 
+  \emph{Improved classical limit analogues for {G}alton-{W}atson processes with or without immigration}, 
+  Bull. Austral. Math. Soc. \textbf{5} (1971), 145--155.
 
 \bibitem{IksanovKoleskoMeiners2018Stable-like}
-A.~Iksanov, K.~Kolesko, and M.~Meiners, \emph{Stable-like fluctuations of {B}iggins' martingales}, Stochastic
-  Process. Appl. (2018).
+  A. Iksanov, K. Kolesko, and M. Meiners, 
+  \emph{Stable-like fluctuations of {B}iggins' martingales}, 
+  Stochastic Process. Appl. (2018).
 
 \bibitem{Janson2004Functional}
-S.~Janson, \emph{Functional limit theorems for multitype branching processes
-  and generalized {P}\'{o}lya urns}, Stochastic Process. Appl. \textbf{110}
-  (2004), no.~2, 177--245.
+  S. Janson, 
+  \emph{Functional limit theorems for multitype branching processes and generalized {P}\'{o}lya urns}, 
+  Stochastic Process. Appl. \textbf{110} (2004), no. 2, 177--245.
 
 \bibitem{KestenStigum1966Additional}
-H.~Kesten and B.~P. Stigum, \emph{Additional limit theorems for indecomposable
-  multidimensional {G}alton-{W}atson processes}, Ann. Math. Statist.
-  \textbf{37} (1966), 1463--1481.
+  H. Kesten and B. P. Stigum, 
+  \emph{Additional limit theorems for indecomposable multidimensional {G}alton-{W}atson processes},
+  Ann. Math. Statist. \textbf{37} (1966), 1463--1481.
 
 \bibitem{KestenStigum1966A-limit}
-\bysame, \emph{A limit theorem for multidimensional {G}alton-{W}atson
-  processes}, Ann. Math. Statist. \textbf{37} (1966), 1211--1223.
+  H. Kesten and B. P. Stigum, 
+  \emph{A limit theorem for multidimensional {G}alton-{W}atson processes}, 
+  Ann. Math. Statist. \textbf{37} (1966), 1211--1223.
 
 \bibitem{KouritzinRen2014A-strong}
- M. ~A. ~ Kouritzin, and  Y.-X. Ren,  \emph{A strong law of large numbers for super-stable Processes},  Stochastic Process. Appl.  \textbf{121} (2014),  505--521.
+  M. A. Kouritzin, and Y.-X. Ren,  
+  \emph{A strong law of large numbers for super-stable processes},  
+  Stochastic Process. Appl. \textbf{121} (2014), no. 1, 505--521.
 
 \bibitem{Kyprianou2014Fluctuations}
-A.~E. Kyprianou, \emph{Fluctuations of {L}\'{e}vy processes with applications},
-  2 ed., Universitext, Springer, Heidelberg, 2014.
+  A. E. Kyprianou, 
+  \emph{Fluctuations of {L}\'{e}vy processes with applications},
+  % 2 ed., Universitext, Springer, Heidelberg, 2014.
+  Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
 
 \bibitem{Li2011Measure-valued}
-Z.~Li, \emph{Measure-valued branching {M}arkov processes}, Probability and its
-  Applications (New York), Springer, Heidelberg, 2011.
+  Z. Li, 
+  \emph{Measure-valued branching {M}arkov processes}, 
+  Probability and its Applications (New York). Springer, Heidelberg, 2011.
 
 \bibitem{LiuRenSong2009Llog}
-R.~Liu, Y.-X. Ren, and R.~Song, \emph{{$L\log L$} criterion for a class of
-  superdiffusions}, J. Appl. Probab. \textbf{46} (2009), no.~2, 479--496.
+  % R.~Liu, Y.-X. Ren, and R.~Song, 
+  R.-L. Liu, Y.-X. Ren, and R. Song, 
+  \emph{{$L\log L$} criterion for a class of superdiffusions}, 
+  J. Appl. Probab. \textbf{46} (2009), no. 2, 479--496.
 
 \bibitem{LiuRenSong2013Strong}
-\bysame, \emph{Strong law of large numbers for a
-  class of superdiffusions}, Acta Appl. Math. \textbf{123} (2013), 73--97.
+  % R.~Liu, Y.-X. Ren, and R.~Song, 
+  R.-L. Liu, Y.-X. Ren, and R. Song, 
+  \emph{Strong law of large numbers for a class of superdiffusions}, 
+  Acta Appl. Math. \textbf{123} (2013), 73--97.
 
 \bibitem{MarksMilos2018CLT}
-R.~Marks and P.~Mi{\l}o{\'s}, \emph{C{LT} for supercritical branching processes
-  with heavy-tailed branching law}, arXiv:1803.05491, 2018.
+  R. Marks and P. Mi{\l}o{\'s}, 
+  \emph{C{LT} for supercritical branching processes with heavy-tailed branching law}, 
+  arXiv:1803.05491.
 
 \bibitem{MetafunePallaraPriola2002Spectrum}
-G.~Metafune, D.~Pallara, and E.~Priola, \emph{Spectrum of
-  {O}rnstein-{U}hlenbeck operators in {$L^p$} spaces with respect to invariant
-  measures}, J. Funct. Anal. \textbf{196} (2002), no.~1, 40--60.
+  G. Metafune, D. Pallara, and E. Priola, 
+  \emph{Spectrum of {O}rnstein-{U}hlenbeck operators in {$L^p$} spaces with respect to invariant  measures}, 
+  J. Funct. Anal. \textbf{196} (2002), no. 1, 40--60.
 
 \bibitem{Milos2012Spatial}
-P.~Mi{\l}o{\'s},
+  P. Mi{\l}o{\'s},
   \emph{Spatial central limit theorem for supercritical superprocesses},
- J. Theoret. Probab. \textbf{31} (2018), no.~1, 1--40.
+  J. Theoret. Probab. \textbf{31} (2018), no. 1, 1--40.
 
 \bibitem{RenSongSun2017Spine}
-Y.-X. Ren, R.~Song, and Z.~Sun, \emph{Spine decompositions and limit theorems
-  for a class of critical superprocesses},
-  To appear in Acta Appl. Math.
+  Y.-X. Ren, R. Song, and Z. Sun, 
+  \emph{Spine decompositions and limit theorems for a class of critical superprocesses},
+  Acta Appl. Math. (2019).
 
 \bibitem{RenSongSun2018Limit}
-\bysame, \emph{Limit theorems for a class of critical superprocesses with stable branching},
-    arXiv:1807.02837, 2018.
+  Y.-X. Ren, R. Song, and Z. Sun, 
+  \emph{Limit theorems for a class of critical superprocesses with stable branching},
+  arXiv:1807.02837.
 
 \bibitem{RenSongZhang2014Central}
-Y.-X. Ren, R.~Song, and R.~Zhang, \emph{Central limit theorems for super
-  {O}rnstein-{U}hlenbeck processes}, Acta Appl. Math. \textbf{130} (2014),
-  9--49.
+  Y.-X. Ren, R. Song, and R. Zhang, 
+  \emph{Central limit theorems for super {O}rnstein-{U}hlenbeck processes}, 
+  Acta Appl. Math. \textbf{130} (2014), 9--49.
 
 \bibitem{RenSongZhang2014CentralB}
-\bysame, \emph{Central limit theorems for supercritical branching {M}arkov
-  processes}, J. Funct. Anal. \textbf{266} (2014), no.~3, 1716--1756.
+  Y.-X. Ren, R. Song, and R. Zhang, 
+  \emph{Central limit theorems for supercritical branching {M}arkov processes}, 
+  J. Funct. Anal. \textbf{266} (2014), no. 3, 1716--1756.
 
 \bibitem{RenSongZhang2015Central}
-\bysame, \emph{Central limit theorems for supercritical superprocesses},
-  Stochastic Process. Appl. \textbf{125} (2015), no.~2, 428--457.
+  Y.-X. Ren, R. Song, and R. Zhang, 
+  \emph{Central limit theorems for supercritical superprocesses},
+  Stochastic Process. Appl. \textbf{125} (2015), no. 2, 428--457.
 
 \bibitem{RenSongZhang2017Central}
-\bysame, \emph{Central limit theorems for supercritical branching nonsymmetric
-  {M}arkov processes}, Ann. Probab. \textbf{45} (2017), no.~1, 564--623.
+  Y.-X. Ren, R. Song, and R. Zhang, 
+  \emph{Central limit theorems for supercritical branching nonsymmetric {M}arkov processes}, 
+  Ann. Probab. \textbf{45} (2017), no. 1, 564--623.
 
 \bibitem{RenSongZhang2017Functional}
-\bysame, \emph{Functional central limit theorems for supercritical
-  superprocesses}, Acta Appl. Math. \textbf{147} (2017), 137--175.
+  Y.-X. Ren, R. Song, and R. Zhang, 
+  \emph{Functional central limit theorems for supercritical superprocesses}, 
+  Acta Appl. Math. \textbf{147} (2017), 137--175.
 
 \bibitem{Sato2013Levy}
-K.~Sato, \emph{L{\'e}vy processes and infinitely divisible distributions},
-  Cambridge Studies in Advanced Mathematics, vol.~68, Cambridge University
-  Press, Cambridge, 2013.
+  K. Sato, 
+  \emph{L{\'e}vy processes and infinitely divisible distributions},
+  % Cambridge Studies in Advanced Mathematics, vol.~68, Cambridge University Press, Cambridge, 2013.
+  Translated from the 1990 Japanese original. Revised by the author. Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.
 
 \bibitem{SchillingSongVondravcek2010Bernstein}
-R.~L. Schilling, R.~Song, and Z.~Vondra\v{c}ek,
-\emph{Bernstein functions: Theory and applications. Second edition.}
-de  Gruyter Studies in Mathematics, vol.~37, Walter de Gruyter \& Co., Berlin,
-  2012.
+  R. L. Schilling, R. Song, and Z. Vondra\v{c}ek,
+  \emph{Bernstein functions.}
+  Theory and applications. Second edition. De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2012.
 
 \bibitem{SteinShakarchi2003Complex}
-E.~M. Stein and R.~Shakarchi, \emph{Complex analysis}, Princeton Lectures in
-  Analysis, vol.~2, Princeton University Press, Princeton, NJ, 2003.
+  E. M. Stein and R. Shakarchi, \emph{Complex analysis}, 
+  Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.
 
 \bibitem{Wang2010An-almost}
-L.~Wang, \emph{An almost sure limit theorem for super-{B}rownian motion}, J.
-  Theoret. Probab. \textbf{23} (2010), no.~2, 401--416.
+  L. Wang, \emph{An almost sure limit theorem for super-{B}rownian motion}, 
+  J. Theoret. Probab. \textbf{23} (2010), no. 2, 401--416.
 
 \end{thebibliography}
-
 \end{document}

### 2019-08-11 representation/representation.tex
change representation.tex
temp


temp
stable representation.tex


fix representation.tex

@@
 % * Top matter
-\title[Stable CLT for Super OU]{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
-\author[Z. Sun]{ 
-  {\bf \Large Zhenyao Sun\inst{1}}
-\\
-{\scriptsize  Joint work with {\bf Yan-Xia Ren\inst{1}}, {\bf Renming Song\inst{2}} and {\bf Jianjie Zhao\inst{1} } }
+\title[Stable CLT for superprocesses]{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
+\author[Zhenyao Sun]{ 
+  {\bf \Large Zhenyao Sun  }
 }
-\institute[PKU]{
-\and
-\inst{1}
-	Peking University
-\and
-\inst{2}
-	University of Illinois at Urbana-Champaign
-}
-\date[SHNU, July, 2019]{
-	Shanghai Normal University,\\
-	July, 2019}
+\institute[WHU]{Wuhan University\\
+  Joint work with {\bf Yan-Xia Ren}, {\bf Renming Song} and {\bf Jianjie Zhao}}
+\date[]{
+	Peking University,
+ \\ August, 2019}
 \begin{document}
@@
 
+% * Presentation
+% ** Model
 \section{Model}
+% *** Settints
 \subsection{Settings}
@@
 	$\psi$: a function from $[0,\infty)$ to $\mathbb R$ given by
-\begin{equation} \label{eq: honogeneou branching mechanism}
-    \psi(z)=
-    - {\color{red} \alpha} z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
+
+  \[\psi(z)=
+  - {\color{red} \alpha} z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) {\color{blue}\pi(dy)},
   \quad  z \geq 0,
-\end{equation}
-	where ${\color{red}\alpha} > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with 
+  \]
+
+	where ${\color{red}\alpha > 0}$, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with
+
 \[
-	\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty.
+	\int_{(0,\infty)}(y\wedge y^2) {\color{blue}\pi(dy)}
+  < \infty.
 \]
+
 \item
-  We call ${\color{red}\alpha}$ the {\color{red} branching rate}.
+  We call ${\color{red}\alpha}$ the {\color{red} branching rate}; ${\color{blue} \pi(dy)}$ the {\color{blue} L\'evy measure}.
 \end{itemize}
@@
 \item
-  $\left\langle f,\mu \right\rangle$: the integration of function $f$ and measure $\mu$ whenever it make senses.
+  $\mu(f)$ and $\langle f, \mu\rangle$: the integration of function $f$ and measure $\mu$ whenever it make senses.
 \item
-	Say a function $f$ on $\mathbb R_+\times E$ is \emph{locally bounded} if
+	Say a function $f$ on $\mathbb R_+\times E$ is locally bounded if
 \[
@@
 
+% *** Superprocesses
 \subsection{Superprocesses}
@@
 \begin{example}
-	Let $\alpha >0$ and $\beta \in (0,1)$.
-	Consider a Branching OU-process with
+	Let $\alpha >0$ and ${\color{red} \beta} \in (0,1)$.
+	Consider a branching Ornstein-Uhlenbeck(OU) process with
 \begin{itemize}
 \item
-	{\color{red} $k$} initial particles;
+	{\color{blue} $k$} initial particles at the origin;
 \item
-	killing rate  $2{\color{red}k}^\beta$;
+	killing rate  $2{\color{blue} k}^{\color{red}\beta}$;
 \item
 	offspring generating function
-\[
-	F_{\color{red}k}(x) =x +\frac{1}{2}(1-x)^{1+\beta} + \frac{-\alpha (1-x)}{2{\color{red}k}^\beta}.
-\]
+\(
+	F_{\color{blue} k}(x) =x +\frac{1}{2}(1-x)^{1+{\color{red}\beta}} + \frac{-\alpha (1-x)}{2{\color{blue} k}^{\color{red}\beta}}.
+\)
 \end{itemize}
@@
 \[
-	\Big(\frac{1}{\color{red} k} X^{({\color{red} k})}_t(\cdot)\Big)_{t\geq 0}
-	\xrightarrow[{\color{red}k}\to \infty]{w} (X_t)_{t\geq 0}
+	\Big(\frac{1}{\color{blue} k} X^{({\color{blue} k})}_t(\cdot)\Big)_{t\geq 0}
+	\xrightarrow[{\color{blue} k}\to \infty]{d} (X_t)_{t\geq 0}
 \]
-where $(X_t)_{t\geq 0}$ is a super OU process with branching mechanism \[\psi(z) = -\alpha z + z^{1+\beta}.\]
+where $(X_t)_{t\geq 0}$ is a super-OU process with branching mechanism \[\psi(z) = -\alpha z + z^{1+{\color{red}\beta}}.\]
 \end{example}
@@
 
+% ** Background
 \section{Background}
+% *** Motivation
 \subsection{Motivation}
-
 \begin{frame}{Background/Motivation}
@@
     We are interested in the spatial laws of large numbers (LLNs) and central limit theorems (CLT) for superprocesses.
-    More precisely, we want to find
+    More precisely, for a testing function $f$, we want to find
     $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
@@
     \]
+
     \begin{itemize}
@@
 \end{frame}
-
+% *** LLNs of superprocesses
 \subsection{LLNs of superprocesses}
@@
 \item
-{\color{red}Weak laws of large numbers} under different settings: Englander 2009, Englander and Winter 2006, Englander  and Turaev 2002.
-\item
-{\color{red}Strong law of large numbers} under different settings: Chen, Ren and Wang 2008, Wang 2010, Liu, Ren and Song 2013, Kouritzin and  Ren 2014, Chen, Ren, Song and Zhang 2015, Eckhoff, Kyprianou and Winkel 2015, Chen, Ren and Yang 2019.
+  {\color{red}Weak LLNs of supercritical superprocesses} under different settings:
+
+  \mbox{ $\circ$ J. Engl\"{a}nder and D. Turaev 2002 (AP);}
+  \mbox{ $\circ$ J. Engl\"{a}nder and A. Winter 2006 (AIHPPS);}
+  \mbox{ $\circ$ J. Engl\"{a}nder 2009 (AIHPPS);} 
 \end{itemize}
+\let\thefootnote\relax\footnotetext{
+  \mbox{(AP) = Ann. Probab.;} 
+  \mbox{(AIHPPS) = Ann. Inst. H. Poincar\'e Probab. Statist.}
+}
 \end{frame}
@@
 \begin{frame}{Background/LLNs of superprocesses}
-\begin{example}[Chen, Ren and Yang 2019]
+\begin{itemize}
+\item
+  {\color{red} Strong LLNs of supercritical superprocesses} under different settings:
+
+  \mbox{ $\circ$ Z.-Q. Chen, Y.-X. Ren and H. Wang 2008 (JFA);} 
+  \mbox{ $\circ$ L. Wang 2010 (JTP);} 
+  \mbox{ $\circ$ R.-L. Liu, Y.-X. Ren and R. Song 2013 (AAM);} 
+  \mbox{ $\circ$ M. A. Kouritzin and Y.-X. Ren 2014 (SPA);} 
+  \mbox{ $\circ$ Z.-Q. Chen, Y.-X. Ren, R. Song and R. Zhang 2015 (FMC);} 
+  \mbox{ $\circ$ M. Eckhoff, A. E. Kyprianou and M. Winkel 2015 (AP);} 
+  \mbox{ $\circ$ Z.-Q. Chen, Y.-X. Ren and T. Yang 2019 (AAM).}
+\end{itemize}
+\let\thefootnote\relax\footnotetext{
+  \mbox{(JFA) = J. Funct. Anal.;}
+  \mbox{(JTP) = J. Theoret. Probab.;}
+  \mbox{(AAM) = Acta Appl. Math.;}
+  \mbox{(SPA) = Stochastic Process. Appl.;}
+  \mbox{(FMC) = Front. Math. China.}
+}
+\end{frame}
+
+\begin{frame}{Background/LLNs of superprocesses}
+\begin{example}
 	Suppose that $X$ is a super OU process with branching mechanism $\psi(z)=-\alpha z+ z^{1+\beta}$ with $\alpha>0$ and $\beta \in (0,1)$.
@@
 \[
-	e^{-\alpha t} \langle f, X_t\rangle \xrightarrow[t\to \infty]{\mathbb P_\mu \text{-a.s.}, L^1(\mathbb P_\mu)} H_\infty \langle f, \varphi\rangle,
+	e^{-\alpha t} X_t(f) \xrightarrow[t\to \infty]{\mathbb P_\mu \text{-a.s.}, L^1(\mathbb P_\mu)} H_\infty \int f(x) \varphi(x) dx,
 \]
-	where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\varphi$ is the invariant density of the OU process $\xi$.
+	where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\|X_t\|$ and $\varphi$ is the invariant probability density of the OU process $\xi$.
 \end{example}
@@
 
-\subsection{CLTs for branching processes with 2rd moment conditions}
+\subsection{CLTs for branching processes with the 2rd moment condition}
 \begin{frame}{Background/CLTs for branching processes with 2rd moment conditions}
@@
 \item
-	For CLT of supercritical {\color{red} Galton-Watson processes}, see Heyde 1970, Heyde and Brown 1971, Heyde and Leslie 1971.
+	{\color{red} CLT of supercritical Galton-Watson(GW) processes} with finite offspring variance:
+
+  \mbox{ $\circ$ C. C. Heyde 1970 (JAP);}
+  \mbox{ $\circ$ C. C. Heyde and B. M. Brown 1971 (ZWVG);}
+  \mbox{ $\circ$ C. C. Heyde and J. R. Leslie 1971 (BAMS).}
 \item 
-	For CLT of supercritical  {\color{red} multi-type Galton-Watson processes}, see Athreya 1969, Athreya 1969, Athreya 1971.
+	{\color{red} CLT of supercritical multi-type GW processes} with a 2rd moment condition:
+
+  \mbox{ $\circ$ K. B. Athreya 1969a (ZWVG);}
+  \mbox{ $\circ$ K. B. Athreya 1969b (ZWVG);} 
+  \mbox{ $\circ$ K. B. Athreya 1971 (ZWVG).}
+\end{itemize}
+\let\thefootnote\relax\footnotetext{
+  \mbox{(JAP) = J. Appl. Probability;}
+  \mbox{(ZWVG) = Z. Wahrsch. Verw. Gebiete;}
+  \mbox{(BAMS) = Bull. Austral. Math. Soc.}
+}
+\end{frame}
+
+\begin{frame}{Background/CLTs for branching processes with 2rd moment conditions}
+\begin{itemize} 
 \item
-	For CLT of some general supercritical {\color{red} branching Markov processes}, see Asmussen and Hering 1983.
+  {\color{red} CLT of supercritical branching OU processes} with binary branching:
+
+  \mbox{ $\circ$ R. Adamczak and P. Mi{\l}o{\'s} 2015 (EJP).}
 \item
-	For CLT of supercritical {\color{red} branching OU processes} with {\color{red} binary branching} mechanism, see Adamczak and Milos 2015.
+	{\color{red} CLT of some general supercritical branching Markov processes} with a 2rd moment condition:
+
+  \mbox{ $\circ$ S. Asmussen and H. Hering 1983 (book);}
+  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2014 (JFA);}
+  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2017 (AP).}
 \end{itemize}
+\let\thefootnote\relax\footnotetext{
+  \mbox{(EJP) = Electron. J. Probab.}
+}
 \end{frame}
@@
 \item
-	For CLT of some supercritical {\color{red} superprocesses} with branching mechanisms satisfying a {\color{red} fourth moment condition}, see Milos 2018.
+	{\color{red} CLT of supercritical superprocesses} with a fourth moment condition:
+
+  \mbox{ $\circ$ P. Mi{\l}o\'{s} 2018 (JTP).}
 \item
-	For CLT of supercritical {\color{red} super OU processes} with branching mechanisms satisfying only a {\color{red} second moment condition}, see Ren, Song and Zhang 2014.
+	{\color{red} CLT of supercritical super OU processes} with a 2rd moment condition:
+
+  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2014 (AAM).}
 \item
-	For a series of CLT for a large class of general supercritical {\color{red} branching Markov processes} and {\color{red} superprocesses} with {\color{red} spatially dependent branching mechanisms} satisfying a {\color{red} second moment condition}, see Ren, Song and Zhang 2014, Ren, Song and Zhang 2015, Ren, Song and Zhang 2017.
+	{\color{red} CLT for a large class of general supercritical superprocesses} with a 2rd moment condition:
+
+  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2015 (SPA);}
+  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2017 (AAM).}
 \end{itemize}
@@
 \item
-	For stable CLT for supercritical {\color{red} Galton-Watson process} whose {\color{red} offspring distribution
-    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$}, see Heyde 1971.
+	{\color{red} Stable CLT for supercritical GW processes:}
+
+  \mbox{ $\circ$ C. C. Heyde 1971 (JAP).}
 \item
-	For stable CLT for supercritical {\color{red} multi-type Galton-Watson process} and supercritical {\color{red} continuous time branching processes}, see Asmussen 1976.
+	{\color{red} Stable CLT for supercritical multi-type GW process:}
+
+  \mbox{ $\circ$ S. Asmussen 1976 (AP).}
 \item
-	Recently, some stable CLTs for supercritical {\color{red} branching OU processes} with offspring generating function
-\[
-    F(s)
+	{\color{red} Stable CLTs for supercritical branching OU processes} with offspring generating function
+
+\( \displaystyle
+    \qquad F(s)
     = ms -(m-1) +(m-1) (1-s)^{1+\beta},
     \quad |s|< 1
-\]
-	with $m>1$ and $\beta\in (0, 1)$ are established in Marks and Milos 2018.
+\)
+
+	where $m>1$ and $\beta\in (0, 1)$:
+
+  \mbox{ $\circ$ R. Marks and P. Mi{\l}o{\'s} 2018 (arXiv).}
 \item
-	Very recently, some stable fluctuation results of Biggins’ martingales in the context of {\color{red} branching random walks} are established in Iksanov, Kolesko and Meiners 2018.
+	{\color{red} Stable fluctuation results of Biggins’ martingales of branching random walks:}
+
+  \mbox{ $\circ$ A. Iksanov, K. Kolesko and M. Meiners 2018 (SPA).}
 \end{itemize}
@@
 \section{Settings}
-\begin{frame}{Settings}
+\begin{frame}{Settings/Assumption 1}
 \begin{itemize}
 \item
-	Let $E= \mathbb R^d$.
+	$E:= \mathbb R^d$.
 \item
-	Let $(\xi_t)_{t\geq 0}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck (OU) process with generator
-\[
+  $\xi = (\xi_t)_{t\geq 0}$, an $\mathbb R^d$-valued OU process with generator
+
+  \( \displaystyle \qquad
 	Lf(x)
@@
 	\quad x\in \mathbb R^d, f\in C^2(\mathbb R^d),
-\]
+  \)
+
 	where $\sigma,b>0$.
 \end{itemize}
-\end{frame}
-
-\begin{frame}{Settings/Assumption 1}
-
 \begin{block}{Assumption 1. (Grey's condition)}
-	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  
+  \centerline{ \( \displaystyle
+    \int_{z'}^\infty \psi(z)^{-1}dz 
+    < \infty.
+    \)}
 \end{block}
@@
 \item
-	It is known  that, under Assumption 1, 
-	the \emph{extinction event} 
-	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
+	Under Assumption 1, write $D := \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$, then
+
+  \centerline{ \( \displaystyle
+    \mathbb P_\mu(D)
+    > 0, 
+    \quad \mu \in \mathcal M(\mathbb R^d).
+  \)}
 \end{itemize}
@@
 \item
-	Denote by $\Gamma$ the gamma function.
-	For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
+	$\Gamma$: the gamma function.
+\item
+	$|\mu|$: the total variation measure of some measure $\mu$.
+\item
+  Recall that $\pi$ is the L\'evy measure of the branching mechanism $\psi$.
 \end{itemize}
 \begin{block}{Assumption 2.}
-	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
-\begin{equation}
-    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
-\end{equation}
-	for some $\delta \in (0,1-\beta)$.
+	There exist (unique) constants ${\color{red}\eta} > 0$ and ${\color{red}\beta} \in (0,1)$ such that for some $\delta \in (0, 1- {\color{red}\beta})$ it holds that
+  \centerline{ \( \displaystyle	
+    \int_{(1,\infty)}y^{1+{\color{red}\beta} +\delta}~\Big|\pi(dy)-\frac{{\color{red}\eta}~dy}{\Gamma(-1-{\color{red}\beta})y^{2+{\color{red}\beta}}}\Big| 
+    <\infty.
+    \)}
 \end{block}
-\end{frame}
-
-\begin{frame}{Settings/Assumption 2}
 \begin{itemize}
 \item
-	Assumption 2 says that 
- there exist constants $\eta>0$ and $\beta > 0$ 
-    such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
-\item
-    In particular, if \[\pi(dy)=\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy,\] then the branching mechanism takes the form: \[\psi(z)=-\alpha z + \rho z^2 + \eta z^{1+\beta},\quad z\geq 0.\]
+    In particular, if 
+    \( \displaystyle
+    \pi(dy)
+    =\frac{{\color{red}\eta} dy}{ \Gamma(-1-{\color{red}\beta})y^{2+{\color{red}\beta}}},
+    \) 
+    then the branching mechanism takes the form: 
+    \( 
+    \psi(z)
+    = -\alpha z + \rho z^2 + {\color{red}\eta} z^{1+{\color{red}\beta}}
+    ,\quad z\geq 0.
+    \)
 \end{itemize}
@@
 \section{Preliminary}
-\begin{frame}{Preliminary/Invariant measure of OU semigroup}
+\begin{frame}{Preliminary/Hermite polynomials}
 \begin{itemize}
@@
 \item
-  $(P_t)_{t\geq 0}$ has the invariant density
-\begin{equation}
-    \varphi(x)dx
-    :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
+  $(P_t)_{t\geq 0}$ has the invariant probability
+
+  \centerline{ \( \displaystyle	
+    \varphi(x)~dx
+    := \Big(\frac{b}{\pi \sigma^2} \Big)^{\frac{d}{2}} e^{-\frac{b}{\sigma^2}|x|^2}~dx,
     \quad x\in \mathbb R^d.
-\end{equation}
+    \)}
 \item
-    Let $L^2(\varphi)$ be the Hilbert space with inner product
-\begin{equation}
+  $L^2(\varphi)$: the Hilbert space with inner product
+
+  \centerline{ \( \displaystyle    
     \langle f_1, f_2 \rangle_{\varphi}
-    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x).
-\end{equation}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Preliminary/Hermite polynomials}
-\begin{itemize}
+    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x)~dx.
+    \)}
 \item
     For each multi-index $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write
-\begin{equation}
+
+    \centerline{ \( \displaystyle	
       |p|:=\sum_{k=1}^d p_k;
@@
       \quad \frac{\partial^p} {\partial x^p}:= \prod_{k = 1}^d\frac{\partial^{p_k}}{\partial x_k^{p_k}}.
-\end{equation}
+      \)}
 \item
-    The \emph{Hermite polynomials} are given by
-\begin{equation}
+    Define the \emph{Hermite polynomials} by
+
+    \centerline{ \( \displaystyle
       H_p(x)
-    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{p}}{\partial x^p} \exp(-|x|^2) ,
+      :=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{p}}{\partial x^p} e^{-|x|^2} ,
       \quad x\in \mathbb R^d,
       p \in \mathbb{Z}_+^{d}.
-\end{equation}
+      \)}
 \end{itemize}
@@
 \begin{frame}{Preliminary/Spectrum of OU semigroup}
+\begin{block}{Fact}
+	$(P_t)_{t\geq 0}$ is a strongly continuous semigroup on $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
+  For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
 
-\begin{lemma}[Metafune, Pallara and Priola 2002]
-	$(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
-    For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
   \[
@@
   \]
+
     where
-\begin{equation}\label{eigenfunction}
+
+    \[
     \phi_p(x)
@@
     \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
-\end{equation}
+    \]
+
     Moreover, $\{\phi_p:p\in \mathbb Z_+^d\}$ forms a complete orthonormal basis for $L^2(\varphi)$.
-\end{lemma}
+\end{block}
 \end{frame}
 
-\begin{frame}{Preliminary/Order of a testing function}
+\begin{frame}{Preliminary/Martingale limits}
+  \begin{lemma}
+    Write $\tilde u = \frac{u}{1+ u}$ for all $u \in (0,1)$.
+    For each $p\in \mathbb Z_+^d$ with $\alpha \tilde \beta > |p|b$, $\gamma \in (0,\beta)$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, the following martingale
+
+    \[  
+      H_t^p
+      := e^{-(\alpha-|p|b) t} \langle \phi_p, X_t\rangle
+      , \quad t\geq 0,
+    \]
+    is bounded in $L^{1+\gamma}(\mathbb P_\mu)$. 
+    Thus the limit $H_\infty^p:= \lim_{t\to \infty} H_t^p$ exists $\mathbb P_\mu$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
+  \end{lemma}
   \begin{itemize}
 \item
-    For each function $f\in L^2(\varphi)$, denote by
-\begin{equation}
-    \kappa_f
-    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \},
-\end{equation}
-    the order of the function $f$. 
+  Roughly speaking, for all $p \in \mathbb Z_+^d$ and $\gamma \in (0,\beta)$, we can estimate that
+
+  \centerline{ \( \displaystyle
+    \|H_{t+1}^p - H_t^p\|_{1+\gamma} 
+    \sim e^{- (\alpha\tilde\gamma - |p|b)t}.
+    \)}
+  So if $\alpha \tilde \beta < |p| b$ then there exists a $\gamma \in (0,\beta)$ such that $H_t^p$ is not a Cauchy sequence in $L^{1+\gamma}$. 
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Preliminary/Polynomial growth functions}
+\begin{itemize}
 \item
-	We say a function $f\in \mathcal B(\mathbb R^d, \mathbb R)$ is of polynomial growth if there exists constants $C,n>0$ such that 
+  $\mathcal P$: the collection of all functions of polynomial growth, i.e.
   \[
-	|f(x)|\leq C(1+|x|)^n,
-	\quad \forall x\in \mathbb R^d.
+    \mathcal P 
+    := \{f \in \mathcal B(\mathbb R^d, \mathbb R) : \exists C, n > 0 \text{ s.t. } \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n\}.
   \]
 \item
-    $\mathcal P$: the collection of all functions of polynomial growth.
+  Recall that $\alpha$ is the branching rate and write $\tilde \beta = \frac{\beta}{1+\beta}$. Define
+\begin{align}  
+    &\mathcal{C}_s
+    :=\mathcal P \cap \overline{Span}\{\phi_p: \alpha \tilde\beta < |p|b \}; \\
+    &\mathcal{C}_c
+    :=\mathcal P\cap\overline{Span}\{\phi_p: \alpha \tilde\beta=|p|b \}; \\
+    &\mathcal{C}_l
+    :=\mathcal P\cap \overline{Span}\{\phi_p: \alpha \tilde \beta >|p|b \}. 
+\end{align}
+\item
+  Then $\mathcal P = \mathcal C_s \oplus \mathcal C_c \oplus \mathcal C_l$, i.e.
+for each $f\in \mathcal P$ there exists unique $f_s\in \mathcal C_s, f_c\in \mathcal C_c, f_l\in \mathcal C_l$ such that
+  \( \displaystyle
+  f = f_s+f_c+f_l.
+  \) 
+\item
+  The asymptotic behaviors of $X_t(f_s), X_t(f_c)$ and $X_t(f_l)$ will be different. 
 \end{itemize}
@@
 \section{Results}
-\begin{frame}{Results/Phase transition}
-\begin{itemize}
-\item
-  Recall that $\alpha$ is the branching rate.
-\item
-	It turns out that the CLTs of $\left\langle f,X_t \right\rangle$ are different in three different regimes
-    depending on the sign of $\alpha-\frac{\kappa_f b (1+\beta)}{\beta}$:
-\begin{itemize}
-\item
-  small branching rate regime: $\alpha < \frac{\kappa_f b (1+\beta)}{\beta}$;
-\item
-  critical branching rate regime: $\alpha = \frac{\kappa_f b (1+\beta)}{\beta}$;
-\item
-  large branching rate regime: $\alpha > \frac{\kappa_f b (1+\beta)}{\beta}$.
-\end{itemize}
-\end{itemize}
-\end{frame}
-\begin{frame}{Results/Small branching rate regime/ CLT}
-\begin{theorem}[Ren, Song, S. and Zhao 2019+]
-    Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta<\kappa_f b(1+\beta)$.
-    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
+\begin{frame}{Results/LLNs}
+  \begin{theorem}
+    Suppose that $f \in \mathcal{P}$ satisfies $\alpha \beta > \kappa_f b ( 1 + \beta)$ where
     \[
-    \|X_t\|^{-\frac{1}{1+\beta}} \langle f,X_t\rangle\xrightarrow[t\rightarrow \infty]{d} \zeta.
+      \kappa_f :=\inf \{k \geq 0: \exists p \in \mathbb Z_+^d,\text{ s.t. }|p| = k \text{ and } \langle f, \phi_p\rangle_\varphi \neq 0\}.
     \]
-    Here, $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta \mapsto \exp( m[\theta f])$ with 
-    \begin{equation}
-      m[\theta f]
-      :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-i \theta P_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
-    \end{equation}
-\end{theorem}
-\end{frame}
-
-\begin{frame}{Results/Critical branching rate regime/CLT}
-\begin{theorem}[Ren, Song, S. and Zhao 2019+]
-\label{thm: critical clt}
-    Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta=\kappa_f b(1+\beta)$.
-    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-\[
-    (t\|X_t\|)^{-\frac{1}{1+\beta}} \langle f,X_t\rangle
-        \xrightarrow[t\to \infty]{d} \widetilde{\zeta}.
-\]
-    Here, $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with
-    characteristic function $\theta \mapsto \exp( \widetilde m[\theta f])$ where
-    \[
-      \widetilde{m}[\theta f]
-      := \eta\int_{\mathbb R^d} \left(-i \theta \sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p(x)\right)^{1+\beta} \varphi(x)~dx.
-    \]
-\end{theorem}
-\end{frame}
-
-\begin{frame}{Results/Large branching rate regime/ Martingale limit}
-\begin{lemma}[Ren, Song, S. and Zhao 2019]
-	For each multi-index $p\in \mathbb Z_+^d$ with $\alpha \beta > |p|b(1+\beta)$, each $\gamma \in (0,\beta)$ and each $\mu \in \mathcal M(\mathbb R^d)$ with compact support, the following martingale
-\[
-	H_t^p:= e^{-(\alpha-|p|b) t} \langle \phi_p, X_t\rangle, \quad t\geq 0,
-\]
-	is bounded in $L^{1+\gamma}(\mathbb P_\mu)$. 
-	Thus the limit $H_\infty^p:= \lim_{t\to \infty} H_t^p$ exists $\mathbb P_\mu$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
-\end{lemma}
-\end{frame}
-
-\begin{frame}{Results/Large branching rate regime/LLNs}
-\begin{theorem}[Ren, Song, S. and Zhao 2019+]
-	Let $f \in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta>\kappa_fb(1+\beta)$. 
-	Then for each $\gamma\in (0, \beta)$ and $\mu\in \mathcal M(\mathbb R^d)$ with compact support, it holds that
+Then for all $\gamma\in (0, \beta)$ and  $\mu \in \mathcal M_c(\mathbb R^d)$,
     \[
@@
 \end{frame}
-
-\begin{frame}{Results/Spectrum decomposition}
+\begin{frame}{Results/A Lemma}
+  \begin{lemma}
+    Define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
+    \centerline{ \( \displaystyle      
+T_tf 
+      := \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
+    \)}
+    and a family of $\mathbb C$-valued functionals $(m_t)_{t\geq 0}$ on $\mathcal P$ by
+   \centerline{ \( \displaystyle
+      m_t[f]
+      := \eta \int_t^{t+1} ~ds \int_{\mathbb R_d} \big(-iT_sf(x)\big)^{1+\beta} \varphi(x) ~dx ,
+    \)}
+    Then it holds that
     \begin{itemize}
     \item 
-	Define
-\begin{align}
-	&\mathcal{C}_l
-   :=\overline{Span}\{\phi_p: \alpha\beta>|p|(1+\beta)b \}.
-	\\ &\mathcal{C}_c
-  :=\overline{Span}\{\phi_p: \alpha\beta=|p|(1+\beta)b \}.
-	\\&\mathcal{C}_s
-  :=\overline{Span}\{\phi_p: \alpha\beta >|p|(1+\beta)b \}.
-\end{align}
+      $(T_t)_{t\geq 0}$ and $(m_t)_{t\geq 0}$ are both well defined;
     \item
-	For any $f\in \mathcal P\setminus\{0\}$, there is a unique decomposition: 
-\[
-	f := f_l + f_c + f_s
-\]
-	where $f_l \in \mathcal C_l, f_c\in \mathcal C_c$ and $f_s\in \mathcal C_s$.
+      if $f\in \mathcal C_s \oplus \mathcal C_l$, then
+      \( \displaystyle
+      m[f]
+      := \sum_{n \in \mathbb Z_+} m_n[f]
+      \in \mathbb C
+      \)
+      is well defined;
     \item
-	CLTs for $f_s$ and $f_c$ are already established.
+      if $f \in \mathcal C_c$, then
+      \( \displaystyle
+      \bar m[f]
+      := \lim_{t\to \infty}\frac{1}{t} \sum_{n=0}^t m_n[f]
+      \in \mathbb C
+      \)
+      is well defined.
     \end{itemize}
+  \end{lemma}
 \end{frame}
 
-\begin{frame}{Results/Large branching rate regime/CLTs}
-\begin{theorem}[Ren, Song, S. and Zhao 2019+]
-\label{thm: large clt}
-    Let $f\in \mathcal{C}_l\setminus\{0\}$.
-    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. 
-    Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-\begin{align}\label{thm: large rate}
-    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow[t\to \infty]{d}\bar{\zeta}.
-\end{align}
-    Here $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function $\theta \mapsto \exp( \bar m[\theta f])$ where
-\[
-	\bar{m}[\theta f]
-  := \eta\int_0^\infty e^{\alpha s}~ds \int_{\mathbb R^d} \big(i\theta I_sf(x)\big)^{1+\beta} \varphi(x)~dx,
-  \quad f\in \mathcal C_l
-\]
-and $(I_t)_{t\geq 0}$ are the inverse operator of $(P_t^\alpha)_{t\geq 0}$ on $\mathcal{C}_l$.
+\begin{frame}{Results/Stable CLT}
+\begin{theorem}
+    Let $\mu\in \mathcal M(\mathbb R^d)\setminus \{0\}$ have compact support. Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, the follows hold:
+\begin{itemize}
+\item
+  if $f_s\in \mathcal C_s\setminus\{0\}$, then 
+  \( \displaystyle  
+    \frac{X_t(f_s)}{\|X_t\|^{\frac{1}{1+\beta}}}
+    \xrightarrow[t\to \infty]{d} \zeta_s,\)
+    an $(1+\beta)$-stable law with characteristic function (ch.f.) $\theta \mapsto e^{m[\theta f_s]}$; 
+\item
+  if $f_c\in \mathcal C_c\setminus\{0\}$, then
+  \( \displaystyle
+    \frac{X_t(f_c)}{\|t X_t\|^{\frac{1}{1+\beta}}}
+    \xrightarrow[t\to \infty]{d} 
+    \zeta_c,
+    \)
+    an $(1+\beta)$-stable law with ch.f. $\theta \mapsto e^{\bar m[\theta f_c]}$;
+  \item
+    if $f_l\in \mathcal C_l\setminus\{0\}$, then
+    \centerline{ \( \displaystyle
+    \frac{X_t(f_l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>pb}\langle f_l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} }{\|X_t\|^{\frac{1}{1+\beta}}}
+    \xrightarrow[t\to \infty]{d}
+    \zeta_l,
+    \)}
+    an $(1+\beta)$-stable law with ch.f. $\theta \mapsto e^{m[- \theta f_l]}$.
+\end{itemize}
 \end{theorem}
@@
 
-\begin{frame}{Remark/Phase transition}
+\begin{frame}{Remark/Two effects}
 \begin{itemize}
 \item
-	Similar phase transition phenomenon in the context of branching OU processes is first observed by Adamczak and Milos 2015.
+	The phase transition phenomenon is due to an interplay of the {\color{red} coarsening effect} and the {\color{blue}smoothing effect}.
+  \mbox{ $\circ$ R. Adamczak and P. Mi{\l}o{\'s} 2015 (EJP).}
+\item
+	{\color{red}Coarsening effect} (increasing of the spatial inequality): 
+  A consequence of branching. 
+  An area with more particles will produce more offspring.
+\item
+	{\color{blue}Smoothing effect} (decreasing of the spatial inequality):  
+	A consequence of the mixing property of the OU process. 
+  Each OU particles will ``forget'' its initial position exponentially fast.   
+\item
+  Roughly speaking, for all $p \in \mathbb Z_+^d$ and $\gamma \in (0,\beta)$, we can estimate that
 
-\item
-	Coarsening effect (increasing of the spatial inequalities): A consequence of branching. Simply an area with more particles will produce more offspring.
-\item
-	Smoothing effect (decreasing of the spatial inequalities):  
-	A consequence of the mixing property of the OU process. Simply each OU particles will ``forget'' its initial position exponentially fast.
-\item
-	The phase transition phenomenon is due to an interplay of the coarsening effect and the smoothing effect.
+  \centerline{ \( \displaystyle
+    \|H_{t+1}^p - H_t^p\|_{1+\gamma} 
+    \sim e^{- ( {\color{red}\alpha\tilde\gamma} - {\color{blue}|p|b})t}.
+    \)} 
 \end{itemize}
 \end{frame}
+\begin{frame} {Methods}
+  \begin{enumerate}
+    \item
+      The characteristic exponent $U_t f(x):= \log \mathbb P_{\delta_x}[e^{i \langle f, X_t \rangle}]$ can be characterized by a complex valued integral equation.
+      \mbox{ $\circ$ N-measure of the superprocesses}, E.-B. Dykin and S. E. Kuznetsov 2004 (PTRF).
+
+\mbox{ $\circ$ Generalized spine decomposition theorem for superprocesses,} Y.-X. Ren, R. Song and S. 2019 (AAM).
+
+\mbox{ $\circ$ Discussions with Z. Li.}
+\item Some estimations of $|U_tf - iP_t^\alpha f|$ when $t\leq 1$.
+  \mbox{ $\circ$ Thanks to Assumption 2 and discussions with R. Zhang.}
+\item Tail probability estimation for random variable 
+  \(\mathbb P_\mu [\langle f, X_{T}\rangle | \mathscr F_t] - \mathbb P_\mu [\langle f, X_{T}\rangle | \mathscr F_{t+1}].\) 
+\item
+  CLT for $\langle f,X_T\rangle$.
+  \mbox{ $\circ$ Similar to the arguments in R. Marks and P. Mi{\l}o{\'s} 2018 (arXiv)} for branching OU processes. 
+  \mbox{ $\circ$ Ideas trace back to the CLT of martingales.}
+    \end{enumerate}
+
+\end{frame}
 \begin{frame}
-  \centering \Large
-  \emph{Thanks!}
+  \[ \text{ \it \Large Thanks!}\]
 \end{frame}

### 2019-08-23 supCLT.tex
change supCLT.tex
Stage the file
change supCLT.tex


change supCLT.tex


change supCLT.tex tep


change supCLT.tex

@@
 % * Contents
+% ** Introduction
 \section{Introduction}
-% ** Motivation
+% *** Motivation
 \subsection{Motivation}
-\label{sec: Motivation}
+\label{subsec:M}
 Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
@@
   \psi(z)=
-  - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy)
+  - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy)
   , \quad  z \in \mathbb R_+,
 \end{align}
-where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty$.
-$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
+where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)~\pi(dy)< \infty$.
+% $\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
+$\psi$ is referred to as the branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
 Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
+% For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
+For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)=\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
 We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
@@
 \end{align}
-where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
+% where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
+where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
 \begin{align}
@@
 
-The strong law of large numbers for the super-OU process $X$ can be stated as follows:
+% The strong law of large numbers for the super-OU process $X$ can be stated as follows:
+The strong law of large numbers for the super-OU process $X$ introduced at the beginning can be stated as follows:
 Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e.
@@
 
-In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above.
+% In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above.
+In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
+% Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
 Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-We want to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
-It turns out that the statements of the CLT's are different in three regimes depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: 
-the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; 
-the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; 
-and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. 
-Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
+% We want to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
+And the general goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
+% DELETED
+% It turns out that the statements of the CLT's are different in three regimes depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: 
+% the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; 
+% the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; 
+% and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. 
+% Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
+% END DELETED
 Note that, in the setting of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
 
-There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
-See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-Some spatial central limit theorems for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
-These two papers made connections between the CLT and  the branching rate regimes.
+% There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
+There are many papers studying CLTs for branching processes, branching diffusions and superprocesses under the second moment condition.
+See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
+% Some spatial central limit theorems for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
+Some spatial CLTs for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
+These two papers made connections between the CLTs and  the branching rate regimes.
 Some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only a second moment condition were established in \cite{RenSongZhang2014Central}.
@@
 
-% ** Main results
+% *** Main results
 \subsection{Main results}
-\label{sec: main results}{}
+\label{sec:I:R}
+% **** Assumption 1
 We will always assume that the following assumption holds.
@@
 It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event} $D :=\{\exists t\geq 0,~\text{s.t.}~ \|X_t\| =0 \}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
-In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}, $ for $\mu\in \mathcal M(\mathbb R^d)$, where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
-
+In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ for each $\mu\in \mathcal M(\mathbb R^d)$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
+
+% **** Assumption 2
 Denote by $\Gamma$ the gamma function.
@@
 
+% **** Mean semigroup
 Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
@@
 
+% **** Spectral Property
 We now recall some basic spectral properties of $(P_t)_{t\geq 0}$ from \cite{MetafunePallaraPriola2002Spectrum}.
@@
 Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+% For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
+For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial/\partial x_k^{p_k})$.
 The \emph{Hermite polynomials} are defined by
@@
   H_p(x)
-  :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) 
+  % :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) 
+  :=(-1)^{|p|}\exp(|x|^2) \partial_p \exp(-|x|^2) 
   , \quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
@@
 In particular, the order of any constant non-zero function is zero.
-Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
-\begin{equation}
-  \label{eq: polynomial growth function}
-  \mathcal{P}
-  :=\big \{f\in \mathscr B(\mathbb R^d, \mathbb R):\exists~ C>0, n \in \mathbb Z_+, {\rm such  \, \, that \, } \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
-\end{equation}
-It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-In this paper, we are mainly interested in the asymptotic behavior of $\langle f, X_t\rangle$ for non-trivial $f\in \mathcal P$.
-The asymptotic behavior varies with the following three regimes:
-(1) the small branching rate regime where $\alpha\beta<\kappa_fb(1+\beta)$; 
-(2) the critical branching rate regime where $\alpha\beta=\kappa_fb(1+\beta)$; and
-(3) the large branching rate regime where $\alpha\beta>\kappa_fb(1+\beta)$.
-
-% *** Large branching rate regime
-\subsubsection{Large branching rate regime}
+
+% **** Martingale limits
+% MOVED from below
   Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
@@
   \]
-If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lemma26} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+  If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lem:M:L:ML} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
   Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+% END MOVED
+
+% **** LLNs
+% ADDED
+We first present a law of large numbers for our model which extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
+% END ADDED
+Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
+\begin{equation}
+  \label{eq: polynomial growth function}
+  \mathcal{P}
+  % :=\big \{f\in \mathscr B(\mathbb R^d, \mathbb R):\exists~ C>0, n \in \mathbb Z_+, {\rm such  \, \, that \, } \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+  :=\big \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists~ C>0, n \in \mathbb Z_+, {\rm such  \, \, that \, } \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
+\end{equation}
+It is clear that $\mathcal{P} \subset L^2(\varphi)$.
+% MOVED FROM BELOW
 \begin{thm}
@@
 \end{thm}
+If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
+Hence, Theorem \ref{thm: law of large number} says that for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
+\[
+  e^{-\alpha t}\langle f, X_t\rangle
+  \rightarrow \langle f, \varphi\rangle H_{\infty}
+  \quad \mbox{in } L^{1+\gamma}(\mathbb{P}_{\mu}).
+\]
+Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have a.\/s.\ convergence.
+However, to get  a.\/s.\ convergence for bounded non-negative 
+Lebesgue-a.\/e.\/\ continuous functions $f$, we do not need $f$ to be twice differentiable.
+See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
+% DELETED
+%\begin{rem}
+%  For general $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
+%\end{rem}
+% END DELETED
+% END MOVED FROM BELOW
+
+% **** Stable CLT 
+% In this paper, we are mainly interested in the asymptotic behavior of $\langle f, X_t\rangle$ for non-trivial $f\in \mathcal P$.
+For the rest of this subsection, we focus on the central limit theorems of $\langle f, X_t\rangle$ for $f\in \mathcal P\setminus \{0\}$.
+% ADDED
+Write $\tilde u = \frac{u}{ 1+ u}$ for each $u \neq -1$.
+% END ADDED
+% The asymptotic behavior varies with the following three regimes:
+It turns out that the fluctuation behaviors vary with the following three cases:
+% (1) the small branching rate regime where $\alpha\beta<\kappa_fb(1+\beta)$; 
+% (2) the critical branching rate regime where $\alpha\beta=\kappa_fb(1+\beta)$; and
+% (3) the large branching rate regime where $\alpha\beta>\kappa_fb(1+\beta)$.
+\begin{enumerate}
+\item
+  the small branching rate case where $f \in \mathcal C_s   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta < |p| b \}$; 
+\item
+  the critical branching rate case where $f \in \mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $; and
+\item
+  the large branching rate case  where $f \in \mathcal C_l   := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
+\end{enumerate}
+% ADDED
+Here, the small (rspt.
+large) branching means that the branching rate $\alpha$ is relatively small (rspt.
+relatively large) and the critical branching means that the branching rate $\alpha$ is at a balanced value.
+% END ADDED
+% ADDED
+To present our result we need to define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
+    \begin{align}
+      \label{eq:I:R:1}
+      T_t f 
+      := \sum_{p \in \mathbb Z_+^d} e^{-| |p|b - \alpha \tilde \beta |t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
+      ,\quad t\geq 0, f\in \mathcal P, 
+    \end{align}
+    and a family of $\mathbb C$-valued functionals $(m_t)_{0 \leq s \leq t < \infty}$ on $\mathcal P$ by
+    \begin{align}
+      \label{eq:I:R:2}
+      m_t[f]
+      := \eta \int_0^t ~du \int_{\mathbb R^d} (-iT_u f(x))^{1+\beta} \varphi(x) ~dx 
+      , \quad 0 \leq t< \infty, f\in \mathcal P. 
+    \end{align}
+    For each $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below we will show that
+    \begin{align} 
+      \label{eq:I:R:3}
+      m[f]
+      := \begin{cases}
+        \lim_{t\to \infty} m_t[f], & f \in \mathcal C_s \oplus \mathcal C_l \setminus \{0\}\\
+        \lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_s \oplus \mathcal C_l
+        \end{cases}
+    \end{align}     
+    is well defined, and moreover, there exists an $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}$.
+    \begin{thm}
+      \label{thm:M}
+    Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$. 
+    Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, the follows hold:
+\begin{enumerate}
+\item
+  \label{thm:M:1}
+  if $f\in \mathcal C_s\setminus\{0\}$, then $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$;
+\item
+  \label{thm:M:2}
+  if $f\in \mathcal C_c\setminus\{0\}$, then
+  \(
+    \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f)
+    \xrightarrow[t\to \infty]{d} 
+    \zeta^f;
+    \)
+  \item
+    \label{thm:M:3}
+    if $f\in \mathcal C_l\setminus\{0\}$, then
+\[
+  \|X_t\|^{-\frac{1}{1+\beta}} \Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big) 
+    \xrightarrow[t\to \infty]{d}
+    \zeta^{-f}.
+\]    
+\end{enumerate}
+\end{thm}
+% END ADDED
+
+% **** (Martingale limits)
+% DELETED
+% \subsubsection{Large branching rate regime}
+% END DELETED
+% MOVED ABOVE
+\begin{comment}
+Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
+For each $p\in \mathbb{Z}_+^d$, define
+\[
+  H_t^p
+  := e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,
+  \quad t\geq 0.
+\]
+If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lem:M:L:ML} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+\end{comment}
+% END MOVED ABOVE
+
+% **** (Theorem of LLN)
+% MOVED ABOVE
+\begin{comment}
+\begin{thm}
+  \label{thm: law of large number}
+  If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
+  \[
+    e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle
+    \xrightarrow[t\to \infty]{}\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p
+    \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).
+  \]
+  Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
+\end{thm}
+
 \begin{rem}
@@
 \end{rem}
+
 \begin{rem}
@@
 \end{rem}
-
+\end{comment}
+% END MOVED ABOVE
+
+% **** (fluctuation result of large numbers)
+% DELETED
+\begin{comment}
 The fluctuation result associated to the law of large numbers in this case is given in Theorem \ref{thm: large clt} below.
@@
 We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; 
-and in Lemma \ref{prop: alpha stable rv} that, when $f\in \mathcal C_l$ is non-trivial, $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+and in Lemma \ref{prop:PL:S} that, when $f\in \mathcal C_l$ is non-trivial, $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
 \begin{thm}
@@
 \end{thm}
-
-% *** Critical branching rate regime
+\end{comment}
+% END DELETED
+% **** (Critical branching rate regime)
+% DELETED
+\begin{comment}
 \subsubsection{Critical branching rate regime}
@@
 According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
-We will prove in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+We will prove in Lemma \ref{prop:PL:S} that $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
 \begin{thm}
@@
 \end{thm}
-
-% *** Small branching rate regime
+\end{comment}
+% END DELETED
+% **** (Small branching rate regime)
+% DELETED
+\begin{comment}
 \subsubsection{Small branching rate regime}
@@
 According to Lemma \ref{lem: def of all m} below, $m[f]$ is well-defined.
-We will prove  in Lemma \ref{prop: alpha stable rv} that $\theta \mapsto \exp( m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
+We will prove  in Lemma \ref{prop:PL:S} that $\theta \mapsto \exp( m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
 \begin{thm}
@@
 \end{thm}
-
+\end{comment}
+% END DELETED
 % ** Some intuitive explanation
 \subsection{Some intuitive explanation}
+{\bf (Sun: I didn't revise this subsection yet.)}
 Here we give some intuitive explanation of the central limit theorems above.
@@
 Recall $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
-Lemma \ref{lem: mainlemma} and Proposition \ref{cor: indepedent of the limit zeta for critical and small} below imply that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
+Lemma \ref{lem:PR:LC} and Proposition \ref{cor:MI} below imply that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
 \[
@@
 
-Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z + \rho z^2+\eta z^{1+\beta}$ plus a small perturbation
+% Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z + \rho z^2+\eta z^{1+\beta}$ plus a small perturbation
+Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z +\eta z^{1+\beta}$ plus a small perturbation
 \begin{align}
@@
 	\psi_1(z)
-	& := \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta) y^{2+\beta}}\Big)
+	& := \rho z^2+ \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta) y^{2+\beta}}\Big)
 \end{align}
@@
   \item
-    $Q_\kappa$ and $Q$ are given in \eqref{Q_k} and \eqref{Q}, respectively.
+    $Q_\kappa$ and $Q$ are given in \eqref{eq:Q} and \eqref{Q}, respectively.
   \item
@@
   \label{lem: complex extension for psi1}
-	The function $\psi_1$ on $\mathbb R_+$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
+	% The function $\psi_1$ on $\mathbb R_+$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
+	The function $\psi_1$ given by \eqref{eq: psi 1} can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
   Moreover, for each $\delta > 0$ small enough, there exists $C>0$ such that for all $z\in \mathbb C_+$, we have
@@
     \psi_1(z)
-    = \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big)
+    % = \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big)
+    = \rho z^2 + \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big)
     , \quad z\in \mathbb C_+.
@@
     |\psi_1(z)|
-    & \leq \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
-    & \leq  |z|^2\int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
+    % & \leq \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
+    & \leq \rho |z|^2 + \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
+    % & \leq  |z|^2 \int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
+    & \leq  |z|^2 \Big(\rho + \int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|\Big) \\
     & \quad + |z|^{1+\beta +\delta}\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|,
@@
 
-% ** Definition of controller
+% *** Definition of controller
 \subsection{Definition of controller}
@@
 For a function $h: [0,\infty) \to [0,\infty)$, we say $R$ is an \emph{$h$-controller} if $R$ is a monotone operator on $\mathcal P^+$ and that $R(\theta f)\leq h(\theta) Rf$ for each $f\in \mathcal P^+$ and $\theta \in [0,\infty)$.
-For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and an operator $R$ on $\mathcal P^+$, we say an operator $A$ is \emph{controlled by $R$ from $\mathcal D$ to $\mathcal I$} if $A:\mathcal D \to \mathcal I$ and that $|Af| \leq R|f|$ for each $f\in \mathcal D$; say a family of operators $\mathscr O$ is \emph{uniformly controlled by $\mathcal R$ from $\mathcal D$ to $\mathcal I$} if for each $A\in \mathcal O$, $A$ is controlled by $R$ from $\mathcal D$ to $\mathcal I$.
+For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and an operator $R$ on $\mathcal P^+$, we say an operator $A$ is \emph{controlled by $R$ from $\mathcal D$ to $\mathcal I$} if $A:\mathcal D \to \mathcal I$ and that $|Af| \leq R|f|$ for each $f\in \mathcal D$;
+we say a family of operators $\mathscr O$ is \emph{uniformly controlled by $R$ from $\mathcal D$ to $\mathcal I$} if for each operator $A\in \mathscr O$, $A$ is controlled by $R$ from $\mathcal D$ to $\mathcal I$.
 For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and a function $h:[0,\infty) \to [0,\infty)$, we say an operator $A$ (resp.
@@
   \item
-    Suppose that $\mathcal O_0 = \{A_\theta: \theta \in \Theta \}$ where $\Theta$ is an index set. 
+    Suppose that $\mathscr O_0 = \{A_\theta: \theta \in \Theta \}$ where $\Theta$ is an index set. 
     Further suppose that $(\Theta, \mathcal J )$ is a measurable space and that $(\theta,x) \mapsto A_\theta f(x)$ is $\mathcal J \otimes \mathcal B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
@@
 % END DELETED
-% ** h-controller for super-OU processes% \subsection{h-controller for super-OU processes}
-\subsection{Controllers for super-OU processes}
+% *** h-controller for super-OU processes
+% \subsection{h-controller for super-OU processes}
+\subsection{Controllers for the super-OU processes}
 \label{sec: h-controller}
-Let $X$ be the super-OU process introduced in Subsection \ref{sec: Motivation} with branching mechanism $\psi$ satisfying
+Let $X$ be the super-OU process introduced in Subsection \ref{subsec:M} with branching mechanism $\psi$ satisfying
 Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
@@
 For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let
-\begin{align}
-  \label{eq: def of U_t}
+  \(
     U_tf(x) 
   := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}
-\end{align}
+\)
 be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
@@
 \begin{equation}
-  \label{Q_k}
+  \label{eq:Q}
   Q_\kappa f
@@
   \item[(3)]
-    $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
+    % $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
+    $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
   \item[(4)]
-    $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P$.
+    % $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P$.
+    $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
   \item[(5)]
-    $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable on $\mathcal P$.
+    % $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable on $\mathcal P$.
+    $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
   \item[(6)]
-    For any $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
+    % For any $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
+    For any $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
   \item[(7)]
-    For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
+    % For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
+    For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
   \end{itemize}
@@
   (1). According to \eqref{eq: -v has positive real part}, $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
-  It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
-  \[
+  It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$, we have
+  \(
     |U_t g(x)|
     \leq \sup_{0\leq u\leq 1}P_u^\alpha |g| (x).
-  \]
+  \)
   We claim that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a map from $\mathcal P^+$ to $\mathcal P^+$. In fact, if $f\in \mathcal P^+$, there exists constant $c>0$ such that
@@
 
-  (3). By Lemma \ref{lem: complex extension for psi1}, there exist $C, \delta >0$ satisfying $\beta+\delta< 1$ such that for all $ f \in \mathcal P^* \cap \mathcal B( \mathbb R^d, \mathbb C_+ )$,
-  \begin{align}
-    &|\Psi_0 f|
+  (3).
+By Lemma \ref{lem: complex extension for psi1}, there exist $C, \delta >0$ satisfying $\beta+\delta< 1$ such that for all $ f \in \mathcal P^* \cap \mathcal B( \mathbb R^d, \mathbb C_+ )$, it holds that
+\(    
+|\Psi_0 f|
       \leq \eta |f|^{1+\beta} + |\Psi_1 f|
       \leq \eta |f|^{1+\beta} + C|f|^2+ C |f|^{1+\beta + \delta}.
-  \end{align}
-  Note that
+\)
+  Note that operator
   \[
@@
     (Z'_t - Z_t)f 
-    = \int_0^t P^\alpha_{t-s}\Big( \eta \big((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} \big)\Big)ds
+    = \int_0^t P^\alpha_{t-s}\Big( \eta ((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} )\Big)ds
     , \quad 0\leq t\leq 1, f\in \mathcal P,
@@
   Therefore, for any $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-  Combining  this  (1)--(2) above, and Lemma \ref{lem: property of controllable operators}.(1) and (4), we get that, for any $\delta > 0$ small enough, the operators
+  % Combining  this  (1)--(2) above, 
+  Combining  this with  (1)--(2) above, 
+  and Lemma \ref{lem: property of controllable operators}.(1) and (4), we get that, for any $\delta > 0$ small enough, the operators
   \[
@@
 \end{proof}
-
-% *** Stable distributions
+% *** (Stable distributions)
+% DELETED
+\begin{comment}
 \subsection{Stable distributions}
 \label{sec: stable distributions}
-
 In this subsection, we will show that the $(1+\beta)$-stable random variables in Theorems \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
@@
 \begin{prop}
-  \label{prop: alpha stable rv}
+  \label{prop:PL:S}
 	For all $t\geq 0$ and non-trivial $f\in \mathcal P$,
@@
 \end{proof}
-\begin{proof}[Proof of Proposition \ref{prop: alpha stable rv}]
+\begin{proof}[Proof of Proposition \ref{prop:PL:S}]
   \eqref{item: stable 1}.
@@
 
-\begin{lem}{\cite[Lemma 2.8]{MarksMilos2018CLT}}\label{lem: control of gk}
+\begin{lem}{\cite[Lemma 2.8]{MarksMilos2018CLT}}\label{lem:P:R}
   For each $f\in \mathcal{P}$, let
@@
 \end{proof}
-
+\end{comment}
+% END DELETED
+% ADDED
+% *** Stable distributions
+\subsection{Stable distributions}
+\label{sec: stable distributions}
+% **** characteristic functions
+Recall that the operators $(T_t)_{t\geq 0}$ are given by \eqref{eq:I:R:1}, and functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
+\begin{lem}
+  \label{lem:m}
+      Operators $(T_t)_{t\geq 0}$, functionals $(m_{t})_{0\leq t< \infty}$ and functional $m$ are well defined. 
+\end{lem}
+\begin{proof}
+  \emph{Step 1.} We will show that for each $f \in \mathcal P$, there exists an $h \in \mathcal P$ such that
+\(      
+|T_tf| 
+      \leq  e^{- \delta t} h
+\)    
+for each $t\geq 0$,
+where 
+    \begin{align}
+      \label{eq:m:1}
+      \delta 
+      := \inf \big\{ |\tilde \beta \alpha - |p|b| : p \in \mathbb Z_+^d, \langle f, \phi_p\rangle_\varphi \neq 0 \big\}
+      \geq 0.
+    \end{align}
+    From this upper bound, it can be verified that $(T_t)_{t\geq 0}$ and $(m_{t})_{0 \leq t < \infty}$ are well defined.
+    In fact, we can write $f = f_0 + f_1$ with $f_0\in \mathcal C_s \oplus \mathcal C_c$ and $f_1 \in \mathcal C_l$.
+    According to \cite[Lemma 2.7]{MarksMilos2018CLT}, there exists an $h_0 \in \mathcal P$ such that for each $t\geq 0$,
+    \[
+      |T_t f_0| 
+      = \Big| \sum_{p \in  \mathbb Z_+^d: \tilde \beta \alpha \leq |p|b } e^{- ( |p| b - \tilde \beta \alpha ) t} \langle f, \phi_p \rangle \phi_p \Big|
+      = e^{\tilde \beta \alpha t} | P_t f_0 |
+      \leq e^{- ( \kappa_{(f_0)} b - \tilde \beta \alpha) t} h_0
+      \leq e^{- \delta t} h_0.
+    \]
+  On the other hand 
+  \[
+    |T_t f_1| 
+    \leq e^{- \sigma t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > p}
+    |\langle f, \phi_p \rangle \phi_p|
+    =: e^{- \delta t} h_1,
+    \quad t\geq 0.
+  \]
+  So the desired result in this step follows with $h := h_0 + h_1$.
+
+  \emph{Step 2.} We will show that if $f \in \mathcal C_s \oplus \mathcal C_l$, then $m[f]$ is well defined.
+  In fact, let $\delta$ be given by \eqref{eq:m:1}, then in this case $\delta > 0$. 
+  Now, according to Step 1 there exists an $h \in \mathcal P$ such that $|T_tf| \leq e^{- \delta t} h$ for each $t\geq 0$.
+  This exponential decay implies the desired result in this step.
+
+  \emph{Step 3.} We will show that if $f\in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$, then $m[f]$ is also well defined. 
+  In fact, $f$ can be decomposed as $f = f_c + f_{sl}$ where $f \in \mathcal C_c\setminus \{0\}$ and $f_{sl}\in \mathcal C_s \oplus \mathcal C_l$. 
+  Note that $T_t f_c = f_c$ for each $t\geq 0$. 
+  Also note that in step 2, we already show that there exists a $\delta > 0$ and an $h \in \mathcal P^+$ such that for each $t\geq 0$, we have $|T_t f_{sl}| \leq e^{- \delta t}h$.
+  Therefore, using Lemma \ref{lem: Lip of power function} we have 
+\begin{align}
+  &|(-iT_t f)^{1+\beta} - (-i f_c)^{1+\beta}|
+  \leq (1+\beta) ( |T_tf|^\beta + |f_c|^\beta) |T_tf_{sl}|
+  \\&\leq (1+\beta) ( |f_c + T_t f_{sl}|^\beta + |f_c|^\beta) e^{- \delta t} h
+  \\&\leq (1+\beta) ( (|f_c| + |h|)^\beta + |f_c|^\beta) e^{- \delta t} h
+  =: e^{- \delta t} g
+\end{align}
+where $g\in \mathcal P^+$.
+Therefore 
+\begin{align}
+  \label{eq:P:S:1}
+  &\Big| \frac{1}{t} m_t[f] - \langle (-if_c)^{1+\beta}, \varphi\rangle\Big|
+  = \Big| \frac{1}{t} \cdot t \int_0^1  \big\langle (-iT_{rt}f)^{1+\beta} - (-if_c)^{1+\beta}, \varphi\big \rangle ~dr \Big|\\
+  &\leq \int_0^1  \big\langle |(-iT_{rt}f)^{1+\beta} - (-if_c)^{1+\beta}|, \varphi\big \rangle ~dr = \langle g,\varphi\rangle\int_0^1 e^{-\delta rt} ~dr
+    \xrightarrow[t\to \infty]{} 0.
+    \qedhere
+\end{align}
+\end{proof}
+
+% **** Stable stable rvs
+\begin{prop}
+  \label{prop:PL:S}
+  For each $f \in \mathcal P\setminus \{0\}$, there exists a non-degenerate $(1+\beta)$-stable random variable $\zeta^f$ such that 
+\(
+  E[e^{i\theta\zeta^f}] = e^{m[\theta f]}
+\)
+for each $\theta \in \mathbb R$.
+\end{prop}
+
+The proof of the above proposition relies on the following lemma:
+\begin{lem}
+  \label{lem: charactreisticfunction}
+  Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with
+  $\int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty)$.
+  Then
+  \[
+    \theta 
+    \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},
+    \quad \theta \in \mathbb R^d
+  \]
+  is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
+\end{lem}
+\begin{proof}
+  It follows from disintegration that there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
+  \[
+    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) 
+    = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(\xi t)k(\xi,dt)
+,\quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+  \]
+  We define another measure $\lambda_0$ on $S$ by
+  \[
+    \lambda_0(d\xi) 
+    := \frac1{\Gamma(-1-\beta)}\int_0^\infty t^{1+\beta}k(\xi,dt) \lambda (d\xi),
+  \]
+  where $\Gamma$ is the Gamma function.
+  Then $\lambda_0$ is a non-zero finite measure, since
+  \begin{align}
+    &\lambda_0(S) 
+      = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt) \\
+    & = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
+  \end{align}
+  Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
+  \[
+    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)
+    = \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}}
+    ,\quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+  \]
+  Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\'evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is
+  \[
+    \hat \mu(\theta)
+    = \exp \Big \{ \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy) \Big \}
+    , \quad \theta \in \mathbb R.
+  \]
+  Finally, according to \eqref{eq: stable branching on C+}, we have
+  \begin{align}
+    & \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
+      = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}} \\
+    & = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt) \\
+    & = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
+      = \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt) \\
+    & = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
+      \qedhere
+  \end{align}
+\end{proof}
+\begin{proof}[Proof of Proposition \ref{prop:PL:S}]
+	Suppose that $f\in \mathcal C_s \oplus \mathcal C_l$.
+Note that $m[\theta f]$ can be written as
+  \begin{align}
+    \label{eq:PL:S:1}
+    m[\theta f]
+    = \eta \int_0^{\infty}~ds\int_{\mathbb R^d} \big(-i\theta T_s f(x)\big)^{1+\beta} \varphi(x)~dx,
+    \quad \theta \in \mathbb R.
+  \end{align}
+	Therefore, according to Lemma \ref{lem: charactreisticfunction}, in order to show that $\zeta^f$ is an $(1+\beta)$-stable random variable we only need to show that
+\[    
+\int_0^{\infty}~ds\int_{\mathbb R^d} | T_{s} f(x)|^{1+\beta} \varphi(x)~dx
+    \in (0, \infty).
+    \]
+  According to the Step 1 of the proof of Lemma \ref{lem:m}, we know that there exists a $\delta \geq 0$ and an $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta t} h$ for each $s\geq 0$.
+  The above then follows.
+
+  Suppose that $f \in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$, then $f$ can be written by $f = f_c +(f - f_c)$ where $f_c \in \mathcal C_c\setminus\{0\}$ and $f - f_c \in \mathcal C_s \oplus \mathcal C_l$.
+  According to \eqref{eq:P:S:1} we have that in this case $m[\theta f]$ also admits an integral representation
+  \begin{align}
+  \label{eq:PL:S:2}
+  m[\theta f] 
+  = \int_{\mathbb R^d} (-i\theta f_c(x))^{1+\beta} \varphi(x) ~dx,
+  \quad \theta \in \mathbb R.
+  \end{align}
+  Finally, according to Lemma \ref{lem: charactreisticfunction} and the fact that
+  \begin{equation}
+    \int_{\mathbb R^d} | f_c(x)|^{1+\beta} \varphi(x)~dx
+    \in (0, \infty),
+  \end{equation}
+We have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
+\end{proof}
+
+% **** Two more Lemmas (Revising)
+\subsection{A refined estimation for the OU semigroup}
+It turns out that our proof of the CLT for the super OU processes relies on the following refined estimation for the OU semigroup.
+
+\begin{lem}
+\label{lem:P:R}
+Suppose that $g \in \mathcal P$, then there exists an $h \in \mathcal P^+$ such that for each 
+\(
+f 
+\in \mathcal P_g
+:= \{\theta T_n g: n \in \mathbb Z_+, \theta \in [-1,1]\}
+\) 
+and $t\geq 0$, we have
+\(
+\big | P_t Z_1 f - \langle Z_1 f, \varphi \rangle \big|
+\leq e^{-bt} h.
+\)
+\end{lem}
+\begin{proof}
+  Fix the $g \in \mathcal P$.
+
+  \emph{Step 1.} We argue that we only have to proof the result for all $f \in \widetilde{\mathcal P}_g:= \{T_{n+1} g : n \in \mathbb Z_+\}$.
+  In fact, writing $q_f:=Z_1f - \langle Z_1f, \varphi \rangle \in \mathcal P^*$ for each $f\in \mathcal P$, then both $\operatorname{Re} q_g$ and $\operatorname{Im} q_g$ are functions in $\mathcal P$ of order $\geq 1$.
+Therefore, the result is valid for $f = T_0 g = g$. 
+Also, note that if the result is valid for some $f \in \mathcal P$, it is also valid for any $\theta f$ with $\theta \in [-1,1]$.
+
+\emph{Step 2.} We show that $\{T_s g: s> 0\} \subset C_\infty (\mathbb R^d) \cap \mathcal P$. 
+In fact, for each $s > 0$,
+\[ 
+  T_s g 
+  = T_s (g_0 + g_1) 
+  = e^{\alpha \tilde \beta s}P_s g_0 + \sum_{p \in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} \langle g_1, \phi_p \rangle e^{-(\alpha \tilde \beta - |p|b)s} \phi_p,
+\]
+where $g = g_0 +g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$. 
+Notice that the second term is in $C_\infty(\mathbb R^d)\cap \mathcal P$ since it is a finite summation of polynomials, and the first term is also in $C_\infty (\mathbb R^d) \cap \mathcal P$ according to \cite[Fact 1.1]{MarksMilos2018CLT}.
+
+\emph{Step 3.} We show that there exists an $h_3 \in \mathcal P^+$ such that for each $j \in \{1,\dots, d\}$ and $f \in \widetilde {\mathcal P}_g$, it holds that $|\partial_j f| \leq h_3$. 
+In fact, it is known that for $t\geq 0$ and $x\in \mathbb R^d$, the position of the OU process $\xi_t$ under $\mathbb P_x$ is a Gaussian random variable with mean $xe^{-bt}$ and variance $\frac{\sigma^2}{2b} (1- e^{-2bt})$.
+From this it can be verified that (see \cite{MetafunePallaraPriola2002Spectrum} for example)
+\begin{align}
+  \label{eq:P:R:3:-1}
+  P_t f(x) = \int_{\mathbb R^d} f\big(x e^{-bt} + y \sqrt{1-e^{-2bt}}\big) \varphi(y)~dy,
+  \quad t\geq 0, x\in \mathbb R^d, f\in \mathcal P.
+\end{align}
+For $f \in C_\infty(\mathbb R^d)\cap \mathcal P$ it can be verified from above that
+\begin{align}
+  \label{eq:P:R:3:1}
+ \partial_j P_t f = e^{-bt} P_t \partial_j f,
+ \quad t \geq 0, j \in \{1,\dots, d\}. 
+\end{align}
+Write $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$. Thanks to Step 2, $T_1 g_0 \in C_\infty(\mathbb R^d)\cap \mathcal P$. 
+According to \cite[Fact 1.3]{MarksMilos2018CLT} and the fact that $\alpha \tilde \beta \leq \kappa _{g_0} b$, we have for each $j \in \{1,\dots, d\}$, 
+\[
+  \kappa_{(\frac{\partial T_1 g_0}{\partial x_j})} 
+  \geq \kappa_{(T_1 g_0)} - 1
+  = \kappa_{g_0} - 1 
+  \geq \frac{\alpha \tilde \beta}{b} - 1.
+\]
+Therefore, there exists an $h'_3\in \mathcal P^+$ such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$, 
+\begin{align}
+  & | \partial_j T_{n+1}g_0 | 
+  = | \partial_j e^{\alpha \tilde \beta n}P_n T_1g_0 | 
+  = e^{\alpha \tilde \beta n-bn} |P_n \partial_j T_1 g_0| \\
+  & \leq e^{\alpha \tilde \beta n-bn} \exp\{-\kappa_{(\partial_j T_1 g_0)}bn\}Q \partial_j T_1g_0
+  \leq Q\partial_j T_1g_0
+    \leq h'_3.
+\end{align}
+On the other hand, there exists an $h_3''\in \mathcal P^+$ such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$, 
+\begin{align}
+  & |\partial_j T_{n+1}g_1 |
+  = \Big| \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} e^{- (\alpha \tilde \beta - |p|b)(n+1)} \langle g_1, \phi_p \rangle_\varphi \partial_j \phi_p \Big| \\
+  & \leq \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} |\langle g_1, \phi_p \rangle_\varphi \partial_j \phi_p | 
+    \leq h_3''.
+\end{align}
+The desired result in this step then follows.
+
+  \emph{Step 4.} We show that there exists an $h_{4} \in \mathcal P^+$ such that for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$, it holds that
+  \(
+    | \partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta} |
+    \leq h_4.
+  \) 
+  In fact, thanks to Step 2 and \eqref{eq:P:R:3:1}, for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde{\mathcal P}_g$, we have
+\begin{align}
+  & \partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta}
+  = e^{-(1-u)b} P_{1-u}^\alpha \partial_j (- i P_u^\alpha f)^{1+\beta}
+  \\ & = (1+\beta) e^{-(1-u)b} P_{1-u}^\alpha [ (- i P_u^\alpha f)^\beta \partial_j (- i P_u^\alpha f) ]
+  \\ & = -i(1+\beta) e^{-(1-u)b} P_{1-u}^\alpha[ (- i P_u^\alpha f)^\beta e^{-ub} P_u^\alpha \partial_j f] 
+  \\ & = -i(1+\beta) e^{-b} e^{(1-u)\alpha} e^{u\alpha (1+\beta)} P_{1-u} [ (- i P_u f)^\beta P_u \partial_j f ].
+\end{align}
+Recall from Step 1 of the proof of Lemma \ref{lem:m} there exists an $h'_4\in \mathcal P^+$ such that for each $f \in \{T_sg:s\geq 0\}$ it holds that $|f| \leq h'_4$.
+Therefore, using Step 3, we have for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$, 
+\begin{align}
+  & |\partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta}|
+  \leq (1+\beta) e^{\alpha (2+\beta)} P_{1-u} [  (P_u |f|)^\beta P_u |\partial_j f| ] 
+\\&    \leq (1+\beta) e^{\alpha (2+\beta)} P_{1-u} [  (P_u h'_4)^\beta P_u h_3 ] 
+   \leq (1+\beta) e^{\alpha (2+\beta)} Q_0 [  (Q_0 h_4')^\beta Q_0 h_3 ], 
+\end{align}
+where $Q_0$ is given by \eqref{eq:Q}. 
+This implies the desired result in this step.
+
+ \emph{Step 5.} We show that there exits an $h_5 \in \mathcal P^+$ such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
+In fact, according to Step 4, for each $j \in \{1,\dots, d\}$, $f \in \widetilde{\mathcal P}_g$ and compact $A \subset \mathbb R^d$, we have 
+\[
+  \int_0^1 \sup_{x\in A} | (\partial_j  P_{1-u}^\alpha (-i P_u^\alpha f)^{1+\beta}) (x) |~du 
+  \leq \sup_{x\in A} h_4(x) < \infty.
+\]
+Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, for each $j \in 
+\{1,\dots, d\}$, $f\in \widetilde {\mathcal P}_g$ and $x\in \mathbb R^d$, it holds that
+\[
+  | \partial_j Z_1 f(x)| 
+  =\Big| \int_0^1  ( \partial_jP_{1-u}^\alpha (-iP_u^\alpha f)^{1+\beta} ) (x) ~du  \Big| 
+  \leq h_4(x).
+\]
+Now, the desired result for this step is valid.
+
+\emph{Final step.} From Step 5, there are $c_5,n_5> 0$ such that for each $x\in \mathbb R^d$, $h_5(x) \leq c_5(1+|x|)^{n_5}$. 
+Note that for each $x, y \in \mathbb R^d$, $1+|x|+|y|\leq (1+|x|) (1+|y|)$;
+and that for each $\theta \in [0,1]$, $|\sqrt {1 - \theta} - 1| \leq \theta$.
+Write $q_f = Z_1f - \langle Z_1f, \varphi\rangle$ for each $f\in \mathcal P$; and $D_{x,y} = \{ax+by: a, b \in [0,1]\}$ for each $x, y \in \mathbb R^d$. 
+Using \eqref{eq:P:R:3:-1} and Step 5, there exists an $h_6 \in \mathcal P^+$ such that for each $t \geq 0$, $f \in \widetilde {\mathcal P}_g$ and $x \in \mathbb R^d$, we have
+  \begin{align}
+    & |P_t q_f(x)|
+      = \Big| \int_{\mathbb R^d} ( (Z_1f)(x e^{-bt}+ y \sqrt{1 - e^{-2bt}}) - Z_1 f (y) ) \varphi(y) ~dy \Big| \\
+    & \leq \int_{\mathbb R^d} \Big(\sup_{z\in D_{x,y}} |\nabla  (Z_1f) (z) |\Big) | x e^{-bt} + y \sqrt{1 - e^{-2bt}} - y | \varphi(y) ~dy \\
+    & \leq e^{-bt} \int_{\mathbb R^d} c_0(1+|x|+|y|)^{n_0} (|x|+|y|) \varphi(y) ~dy \\
+    & \leq c_0 e^{-bt}(1+|x|)^{n_0}\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y) ~dy + \int_{\mathbb R^d} (1+ |y|)^n |y| \varphi(y) ~dy \Big) \\
+    & \leq e^{-bt} h_6(x).
+      \qedhere
+  \end{align}
+\end{proof}
+% DELETED
+\begin{comment}
+\begin{lem}{\cite[Lemma 2.8]{MarksMilos2018CLT}}
+  For each $f\in \mathcal{P}$, let
+  \begin{align}
+    g_k
+    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
+    \quad k \geq 0.
+  \end{align}
+  Then there exists an $h\in \mathcal{P}$ such that $|P_sg_k|\leq e^{-bs}h$ for all $s, k \geq 0.$
+\end{lem}
+
+\begin{lem}
+  \label{control of gn} 
+  Suppose that $g\in \mathcal{C}_l$.
+  Put
+  \begin{align}
+    \bar{g}_t
+    :=\frac{Z_1(T_tg)-\langle Z_1(T_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
+  \end{align}
+  Then there exists an $h\in \mathcal{P}$ such that $|P_s\bar{g}_t| \leq e^{-bs}h$ for all $s, t\geq 0.$
+\end{lem}
+\begin{proof}
+  First we claim that there exists $h_1\in \mathcal P$ such that
+\begin{align}
+  \label{ineq: control of partial derivative of Itg}
+  \Big|\frac{\partial}{\partial x_i}T_tg(x)\Big| \leq e^{-(\alpha-Kb)t}h_1(x),
+  \quad  t\geq 0, x\in \mathbb R^d.
+\end{align}
+In fact, if we put $h_1(x)=\sum_{p\in \mathbb Z^d_+: \alpha \tilde \beta > |p|b }|\langle g, \phi_p\rangle_\varphi\frac{\partial \phi_p}{\partial x_i}(x)| \in \mathcal P$, then there exists a $\delta > 0$ such that
+\begin{align}
+  \Big|\frac{\partial}{\partial x_i}T_tg(x)\Big| =
+  \Big|\sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta > |p|b}\langle g, \phi_p\rangle_\varphi e^{-(\alpha\tilde \beta-|p|b)t} \frac{\partial}{\partial x_i}\phi_p(x)\Big|
+  \leq e^{-\delta t}h_1(x)
+  , \quad t\geq 0, x\in \mathbb R^d.
+\end{align}
+It is well known that
+\[
+  P_t f(x) = \int_{\mathbb R^d} f\big(x e^{-bt} + y \sqrt{1-e^{-2bt}}\big) \varphi(y) dy,
+  \quad t\geq 0, x\in \mathbb R^d, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
+\]
+It is clear that the above equality also holds for each $f\in \mathcal P$.
+From this, one can easily check that for each differential $f \in \mathcal P$ with $|\nabla  f| \in \mathcal P$, we have
+\[
+  \frac{\partial P_t^\alpha f(x)}{\partial x_i} = e^{-bt} P_t^\alpha\Big(\frac{\partial f}{\partial x_i}\Big)(x), \quad t\geq 0, x\in \mathbb R^d.
+\]
+Note that if $g \in \mathcal C_l$, then $g$ is a linear combination of polynomials.
+Therefore, $g^{1+\beta}\in \mathcal P$ and $|\nabla (g^{1+\beta})| \in \mathcal P$.
+Therefore,
+\begin{align}
+  & \frac{\partial}{\partial x_i} P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}
+    = \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s} g)^{1+\beta}
+    = e^{-b(1-s)} P_{1-s}^\alpha \frac{\partial}{\partial x_i} (I_{t-s}g)^{1+\beta} \\
+  & =(1+\beta)e^{-b(1-s)} P_{1-s}^\alpha \Big( (I_{t-s}g)^\beta \times \frac{\partial}{\partial x_i} (I_{t-s}g) \Big),\quad s\in [0,1], t\geq 0.
+\end{align}
+Using \eqref{eq: supper for Itf}, \eqref{ineq: control of partial derivative of Itg} and the above, we have that there exist a bounded function $a$ on $[0,1]$ and an $h_2 \in \mathcal P$ such that
+\begin{equation}
+  \label{eq: key estimation for partial}
+  \Big| \frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| \leq a(s) e^{-(\alpha - Kb)(1+\beta)t}h_2(x),\quad s\in [0,1],t\geq 0, x\in \mathbb R^d.
+\end{equation}
+Therefore, for each compact subset $A \subset \mathbb R^d$, we have
+\[
+  \int_0^1 \sup_{x\in A} \Big|\frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| ds 
+  < \infty
+  , \quad t\geq 0.
+\]
+Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, we can get
+\[
+  \frac{\partial}{\partial x_i} Z_1(T_tg)
+  = \eta i^{1+\beta}  \frac{\partial}{\partial x_i} \int_0^1 P_{1-s}^\alpha (I_{t-s}g)^{1+\beta} ds
+  = \eta i^{1+\beta}  \int_0^1  \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s}g)^{1+\beta} ds.
+\]
+Therefore, using \eqref{eq: key estimation for partial} and the above, there exists  $C> 0$ such that for all $t\geq 0$,
+\begin{align}
+  & \Big|\frac{\partial}{\partial x_i}\bar{g}_t(x)\Big|
+    = e^{(\alpha-Kb)(1+\beta)t}\Big|\frac{\partial}{\partial x_i}Z_1(-I_tg)\Big| \leq C h_2(x),
+    \quad x\in \mathbb R^d.
+\end{align}
+Therefore there exist $c,n>0$ such that
+\begin{align}
+  \label{ineq: control of sup gt}
+  | \nabla \bar g_t (z)|
+  \leq c(1+|z|)^n
+  , \quad t\geq 0, z\in \mathbb R^d.
+\end{align}
+Define
+\[
+  D(x,y)
+  := \{ax+by: a,b\in [0,1]\}
+  , \quad x, y \in \mathbb R^d.
+\]
+Then for all $x,y\in \mathbb R^d$, $D(x,y)$ is a convex set on $\mathbb R^d$.
+In particular, it contains the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$ for each $s\geq 0$.
+Also, note that $ | \sqrt { 1 - \theta } - 1 | \leq \theta $ for all $ \theta \in [ 0, 1 ] $, and that $ 1 + \theta + \lambda \leq ( 1 + \theta ) ( 1 + \lambda ) $ for all $ \theta, \lambda \geq 0$.
+Using the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we get that for all $s,t\geq 0, x\in \mathbb R^d$,
+\begin{align}
+  & |P_s\bar{g}_t(x)|
+    = \Big|\int_{\mathbb R^d} \big(\bar {g}_t(xe^{-bs}+y\sqrt{1-e^{-2bs}})-\bar {g}_t (y)\big) \varphi(y)~dy \Big| \\
+  & \leq \int_{\mathbb R^d} \sup_{z\in D(x,y)} |\nabla \bar g_t (z)|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy \\
+  & \leq e^{-bs}\int_{\mathbb R^d} c(1+|x|+|y|)^n (|x|+|y|) \varphi(y)~dy \\
+  & \leq ce^{-bs}(1+|x|)^n\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y)dy + \int_{\mathbb R^d}(1+|y|)^n|y|\varphi(y)dy\Big).
+  \qedhere
+\end{align}
+\end{proof}
+\end{comment}
+% END ADDED
 % *** small value probability
@@
 It can be verified that for each $\mu \in \mathcal M(\mathbb R^d)$ with $x = \| \mu \|$, we have
-\[
+\(
   \{(\|X_t\|)_{t\geq 0}; \mathbb P_\mu\}
   \overset{\text{law}}{=} \{(Y_t)_{t\geq 0}; \mathbf P_x\}.
-\]
+\)
 
@@
 
-% ** Moments for super-OU processes
+% *** Moments for super-OU processes
 \subsection{Moments for super-OU processes}
 \label{sec: Moments for super-OU processes}
-In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec: main results} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
+In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec:I:R} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
 Recall that the operator $\mathcal{I}^t_s$ is defined in \eqref{Ist}.
@@
 \begin{proof}
+% ADDED
+  It is elementary calculus (see the proof of \cite[Theorem 3.3.6]{Durrett2010Probability} for example) that for each $ux \neq 0$ in $\mathbb R$,
+  \[\frac{1}{u}\int_{-u}^u (1- e^{i\theta x})~d\theta = 2 - \frac{2\sin ux}{ux} \geq \mathbf 1_{ux>2}.\]
+% END ADDED
+  % Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof of \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
   Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: upper bound for usgx}.(4).
-  Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof of \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
-  \begin{align}
-    & \big|\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)\big|
+  Therefore, using Lemma \ref{lem: estimate of exponential remaining} we get
+  \begin{align}
+    & |\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)|
       \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^t\langle g,X_t\rangle}])d\theta\Big| \\
@@
     \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg).
+    \leq C e^{\alpha r} \Big(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \Big).
   \]
@@
   & \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-    = \mathbb P_\mu \Big[\mathbb P_\mu\big[|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r\big]\Big] \\
+    = \mathbb P_\mu \Big[\mathbb P_\mu [|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda | \mathscr F_r ]\Big] \\
   & = \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle P_{t-s}^\alpha g, X_{s-r}\rangle - \langle P_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big] \\
@@
   & \leq \mathbb P_\mu [ \langle Rh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
-  \\ & =  \langle P_r^\alpha Rh,\mu\rangle \bigg(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\bigg)
-  \\ & \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg),
+  \\ & =  \langle P_r^\alpha Rh,\mu\rangle \Big(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\Big)
+  \\ & \leq C e^{\alpha r} \Big(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \Big),
 \end{align}
@@
 
+For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write $ \|Y\|_{\mathbb P;p} := \mathbb P[|Y|^p]^{1/p}. $
 \begin{lem}
   \label{lem: control of mgtrs}
-  For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists $C > 0$ such that for all $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
-  \[
-    \sup_{g \in \mathcal P: Q_\kappa g\leq h} \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
-    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b)}.
+  For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists $C > 0$ such that for all $\kappa \in \mathbb Z_+$ and $0\leq r \leq s\leq t<\infty$ with $s-r \leq 1$, we have
+  \[
+    \sup_{g \in \mathcal P: Q_\kappa g \leq h} \|\mathcal I_r^s\langle g, X_t\rangle \|_{\mathbb P_\mu;1+\gamma}
+    \leq C e^{t\alpha (1- \tilde \gamma)+(t-s) (\alpha \tilde \gamma - \kappa b)}.
   \]
@@
 \begin{align}
-  & (1+\beta)(t-s)(\alpha- \kappa b) + \alpha r
-    = (t-s)\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b) \\
-  & \leq t\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b).
-\end{align}
-So the desired result is true with
-\[
-  C
-  := 1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}.
-  \qedhere
-\]
+  & (1+\gamma) (t-s) (\alpha- \kappa b) + \alpha r
+    = (t-s)\alpha+(t-s) (\gamma \alpha- (1+\gamma )\kappa b) \\
+  & \leq t\alpha+(t-s) (\gamma \alpha- (1+\gamma)\kappa b).
+\end{align}
+So the desired result is true.
 \end{proof}
-For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write $ \|Y\|_{\mathbb P;p} := \mathbb P[|Y|^p]^{1/p}. $
 \begin{lem}
-  \label{lem: control moment}
+  \label{lem:P:M:uc}
   For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
-  \begin{itemize}
-  \item[(1)]
+  \begin{enumerate}
+  \item
+    \label{item:P:M:uc:1}
     $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$;
-  \item[(2)]
+  \item
+    \label{item:P:M:uc:2}
     $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$;
-  \item[(3)]
+  \item
+    \label{item:P:M:uc:3}
     $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
-  \end{itemize}
+  \end{enumerate}
 \end{lem}
@@
 
-% * Proofs of main results
+% ** Proofs of main results
 \section{Proofs of main results}
@@
 
-% ** The large branching rate regime: law of large numbers
-\subsection{The large branching rate regime: law of large numbers}
+% *** The large branching rate regime: law of large numbers
+% \subsection{The large branching rate regime: law of large numbers}
+\subsection{Law of large numbers}
 \label{sec: large rate lln}
@@
 In this subsection, we prove Theorem \ref{thm: law of large number}.
-We will return to the large branching rate regime in Subsection \ref{sec: large rate clt} to prove Theorem \ref{thm: large clt}.
-
-To prove Theorem \ref{thm: law of large number}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
+% DELETED
+% We will return to the large branching rate regime in Subsection \ref{sec: large rate clt} to prove Theorem \ref{thm: large clt}.
+% END DELETED
+% To prove Theorem \ref{thm: law of large number}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
+Recall that $L$ is the infinitesimal generator of the OU-process.
+For $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and  $a\in \mathbb R$, we define
+In order to do this, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
 Recall that $L$ is the infinitesimal generator of the OU-process.
@@
 
-Recall that, for $p=(p_1,...,p_d)\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$. Define
-\[
+Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$. Define
+\(
   H_t^p
-  :=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.
-\]
+  :=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle
+\)
+for each $t\geq 0$.
 
 \begin{lem}
-  \label{lemma26}
-  For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
-Moreover, if $\alpha\beta>|p|b(1+\beta)$, then, for all $\gamma\in (0, \beta)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $ exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
+  \label{lem:M:L:ML}
+  % For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$. 
+  For each $\mu\in \mathcal M_c(\mathbb R^d)$ and $p \in \mathbb Z_+^d$, $(H^p_t)_{t\geq 0}$ is a martingale with respect to $\mathbb P_\mu$. 
+  % Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$, 
+  Moreover if $\alpha\tilde \beta>|p|b$, then the martingale is bounded in $L^{1+\gamma}(\mathbb P_\mu)$ for each $\gamma\in (0, \beta)$. 
+  % and $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $ exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
+  As a consequence, $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $ convergence almost surely and also in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
 \end{lem}
 \begin{proof}
-  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb R^d)$.
-  There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, we have $\alpha\gamma>|p|(1+\gamma)b$.
-  Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that, for $\gamma\in [\gamma_0, \beta)$, there exists $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$) such that
+  % It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb R^d)$.
+  Fix the measure $\mu \in \mathcal M_c(\mathbb R^d)$ and the multi-index $p \in \mathbb Z_+^d$.
+  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale.
+
+  % There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, we have $\alpha\gamma>|p|(1+\gamma)b$.
+  Further suppose that $\alpha \tilde \beta > |p| b$.
+  Then there exists a $\gamma_0 \in (0,\beta)$ which is close enough to $\beta$ so that $\alpha\tilde \gamma>|p|b$ for each $\gamma\in [\gamma_0, \beta)$.
+  % Using  Lemma \ref{lem:P:M:uc} and the fact $\kappa_{\phi_p}=|p|$, we get that, for each $\gamma\in [\gamma_0, \beta)$, there exists a $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$) such that
+  Using  Lemma \ref{lem:P:M:uc} and the fact $\kappa_{\phi_p}=|p|$, we get that, for each $\gamma\in [\gamma_0, \beta)$, there exists a constant $c>0$ such that
 \[
  	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
-  \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
-  = C_{\gamma, \mu, p}
+  % \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
+  \leq c e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
+  % = C_{\gamma, \mu, p}
+  = c
   , \quad t\geq 0.
 \]
-For all $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, we have
+% For all $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, we have
+For each $\gamma\in (0, \gamma_0)$ there exists a constant $c>0$, such that
 \[
@@
 	\leq \| H_t^p \|_{\mathbb P_\mu;1+\gamma_0}
-  < C_{\gamma_0, \mu, p},
+  % < C_{\gamma_0, \mu, p},
+  \leq c,
 	\quad t\geq 0.
 \]
-
-Hence, for all $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
+% Hence, for all $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
+Therefore, for each $\gamma \in (0,\beta)$, the martingale $(H_t^p)_{t\geq 0}$ is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \end{proof}
-
-In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$  for any $\mu\in \mathcal M_c(\mathbb R^d)$.
-
+% DELETED
+% In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$  for any $\mu\in \mathcal M_c(\mathbb R^d)$.
+% END DELETED
 \begin{lem}
   \label{lem: control of wt}
-  Let $\mu\in \mathcal M_c(\mathbb R^d)$.
-  For all $\gamma\in (0,\beta)$ and $p\in \mathbb{Z}_+^d$ with $\alpha \gamma > |p|b(1+\gamma)$, there exists $C> 0$ such that for all $0\leq s<t$,
+  % Let $\mu\in \mathcal M_c(\mathbb R^d)$.
+  Suppose that $\mu\in \mathcal M_c(\mathbb R^d)$ and that $p \in \mathbb Z_+^d$ satisfies $\alpha \tilde \beta > |p|b$.
+  % For all $\gamma\in (0,\beta)$ and $p\in \mathbb{Z}_+^d$ with $\alpha \gamma > |p|b(1+\gamma)$, there exists $C> 0$ such that for all $0\leq s<t$,
+  Then for each $\gamma \in (0,\beta)$ satisfying $\alpha \tilde \gamma > |p|b$, there exists a constant $C> 0$ such that,
 \[
   \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
-  \leq C e^{-\frac{ 1}{1+\gamma}(\alpha\gamma-|p|b(1+\gamma))s}.
-\]
-Moreover, we have
-\[
-  \|H^p_\infty-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
-  \leq C e^{-\frac{ 1}{1+\gamma}(\alpha\gamma-|p|b(1+\gamma))s},\quad s\geq 0.
-\]
+  \leq C e^{-(\alpha \tilde \gamma-|p|b)s},
+  \quad 0 \leq s < t \leq \infty.
+\]
+% DELETED
+% Moreover, we have
+% \[
+%  \|H^p_\infty-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
+%  \leq C e^{-\frac{ 1}{1+\gamma}(\alpha\gamma-|p|b(1+\gamma))s},\quad s\geq 0.
+% \]
+% END DELETED
 \end{lem}
@@
 \begin{proof}
-  The second assertion follows immediately from the first, so we only prove the first assertion.
-  Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-  By Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$, there exists $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
-\begin{align}
-  \mathbb{P}_{\mu}\Big[\big|e^{(\alpha-|p|b)(t-s)}\langle\phi_p, X_s\rangle-e^{(\alpha-|p|b)(t-r)}\langle\phi_p, X_r\rangle\big|^{1+\gamma}\Big]
-  \leq C_1e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b)}.
-\end{align}
-Dividing both sides by $e^{(\alpha-|p|b) t(1+\gamma)}$, we get
-\begin{align}
-  \mathbb{P}_{\mu}\big[|H^p_s-H^p_r|^{1+\gamma}\big]
-  \leq  C_1 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
+  % The second assertion follows immediately from the first, so we only prove the first assertion.
+  Thanks to Lemma \ref{lem:M:L:ML} we only have to proof this when $0\leq s < t<\infty$.
+  % Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
+  Fix the $p\in \mathbb{Z}_+^d$, $\mu\in \mathcal M_c(\mathbb R^d)$ and the $\gamma \in (0,\beta)$ with $\alpha \tilde \beta > |p|b$.
+  % By Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$, there exists $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
+  By Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$, there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$,
+  % DELETED
+  % \begin{align}
+  %   \mathbb{P}_{\mu}\Big[\big|e^{(\alpha-|p|b)(t-s)}\langle\phi_p, X_s\rangle-e^{(\alpha-|p|b)(t-r)}\langle\phi_p, X_r\rangle\big|^{1+\gamma}\Big]
+  %   \leq C_1e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b)}.
+  % \end{align}
+  % Dividing both sides by $e^{(\alpha-|p|b) t(1+\gamma)}$, we get
+  % END DELETED
+\begin{align}
+  % \mathbb{P}_{\mu}\big[|H^p_s-H^p_r|^{1+\gamma}\big]
+  % \leq  C_1 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
+  \|H^p_s-H^p_r\|_{\mathbb P_\mu; 1+\gamma}
+  \leq  C_1 e^{-(\alpha\tilde \gamma-|p|b)s}.
 \end{align}
@@
 	& \leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma} \\
-	& \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
-   \leq C_2e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
+	% & \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
+	& \leq C_1 \Big(e^{-(\alpha \tilde \gamma- |p|b) s}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor} e^{-(\alpha \tilde \gamma- |p|b) k} + e^{-(\alpha \tilde \gamma-|p|b) t}\Big)
+   \leq C_2e^{-(\alpha \tilde \gamma-|p|b)s}.
    \qedhere
@@
   \end{align}
-	According to Lemma \ref{lemma26}, we have
+	According to Lemma \ref{lem:M:L:ML}, we have
 \begin{equation}
@@
 \end{equation}
-$\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
+$\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma\in(0,\beta)$.
 Therefore, it suffices to show that
@@
 \end{equation}
-converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$ satisfies $D^2f\in \mathcal{P}$.
-
-Step 1. Let $g\in \mathcal P$.
-Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa < \frac{\alpha \beta}{b(1+\beta)}$.
+% converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$ satisfies $D^2f\in \mathcal{P}$.
+converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
+
+\emph{Step 1.} Let $g\in \mathcal P$.
+Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa b < \alpha \tilde \beta$.
 We will show that for each $\gamma \in (0,\beta)$ there exist $C_1,\delta_1 > 0$ such that
@@
 \]
-In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
-Then, according to Lemma \ref{lem: control moment}, we have, for each $\gamma \in (0,\beta)$,
+% In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
+In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, $\kappa b< \alpha \tilde \gamma$ for each $\gamma \in [\gamma_0, \beta)$.
+According to Lemma \ref{lem:P:M:uc}, we have for each $\gamma \in (0,\beta)$,
 \begin{enumerate}
 \item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C_2>0$ such that
+	% if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C_2>0$ such that
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma> \kappa_g b$, then there exists $C_2>0$ such that
   \[
@@
 \item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C_3>0$ such that
+	% if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C_3>0$ such that
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma=\kappa_g b$, then there exists $C_3>0$ such that
   \[
@@
     \leq C_3 t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-    = C_3 t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
+    % = C_3 t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
+    = C_3 t e^{-(\alpha \tilde \gamma - \kappa b)t},
     \quad t\geq 0;
@@
 \item
-	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C_4>0$ such that
+	% if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C_4>0$ such that
+	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma < \kappa_g b$, then there exists $C_4>0$ such that
   \[
@@
     \leq C_4  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-    = C_4  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
+    % = C_4  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
+    = C_4  e^{-(\alpha \tilde \gamma - \kappa b)t},
     \quad t\geq 0;
@@
 
-Step 2.
+\emph{Step 2.}
 We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$.
@@
 \end{align}
-Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$.
+Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 b < \alpha \tilde \beta$.
 According to \eqref{defmartingale}, 
@@
 
-% *** The critical branching rate regime
+% *** (The critical branching rate regime)
+% DELETED
+\begin{comment}
 \subsection{The critical branching rate regime}
@@
 \begin{lem}
-  \label{lem: mainlemma}
+  \label{lem:PR:LC}
   Let $f\in \mathcal{P}$ be non-trivial and satisfy $\alpha\beta\leq \kappa_fb(1+\beta)$.
@@
     \gamma_{t,k}
-    := \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha (k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
+    := \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha (k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{eq:PR:LC:1}
 \end{equation}
@@
 \end{align}
-From Proposition \ref{prop: alpha stable rv}.(1), we have $\operatorname {Re} m_t[f] < 0$. 
+From Proposition \ref{prop:PL:S}.(1), we have $\operatorname {Re} m_t[f] < 0$. 
 Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
@@
 \end{align}
-where $Q$ is defined by \eqref{Q_k}.
+where $Q$ is defined by \eqref{eq:Q}.
 Thus for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
@@
 \end{align}
-where $Q$ is defined by \eqref{Q_k}.
+where $Q$ is defined by \eqref{eq:Q}.
 By taking $\epsilon>0$ small enough, we get the desired result in this step.
@@
 \]
-It follows from Lemma \ref{lem: control of gk} that there exists $h\in \mathcal{P}$ such that
+It follows from Lemma \ref{lem:P:R} that there exists $h\in \mathcal{P}$ such that
 \[
@@
 \]
-where $Q_1$ is defined by \eqref{Q_k} with $\kappa=1$.
+where $Q_1$ is defined by \eqref{eq:Q} with $\kappa=1$.
 
 Chose a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-According to Lemma \ref{lem: control moment}.(3) (with $\kappa=1$), there exists $C_3>0$ such that for all $t\geq 0$ and $k\geq 0$,
+According to Lemma \ref{lem:P:M:uc}.(3) (with $\kappa=1$), there exists $C_3>0$ such that for all $t\geq 0$ and $k\geq 0$,
 \begin{align}
@@
 \begin{prop}
-  \label{cor: indepedent of the limit zeta for critical and small}
+  \label{cor:MI}
   Suppose that $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq\kappa_fb(1+\beta)$.
@@
   Fix $\theta\in \mathbb R$.
-  Taking $\theta_k=t ^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small}, we get that there exist $C_1,\delta_1>0$ such that,
+  Taking $\theta_k=t ^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor:MI}, we get that there exist $C_1,\delta_1>0$ such that,
   \begin{align}
@@
 \end{proof}
-
-% *** The small branching rate regime
-\subsection{The small branching rate regime}
-\label{sec: small rate}
-
-In this subsection, we prove the central limit theorem for the small branching rate regime.
-
-\begin{proof}[Proof of Theorem \ref{thm: small clt}]
-  By assumption, $f\in \mathcal P$ is non-trivial and satisfies $\alpha \beta < \kappa_f b(1+\beta)$.
-	Let $t_0 > 1$ be large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1, $ for all $t\geq t_0$.
-  Fix $\mu\in \mathcal M_c(\mathbb R^d)$ and write
-  \begin{align}
-    & \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-    \\ & =\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+ \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big) +
-\frac{\langle P^\alpha_t f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-    \\ & =:I'_1(t)+I'_2(t)+I'_3(t),
-         \quad t\geq t_0.
-  \end{align}
-	Define
-  \[
-    \widetilde I'_1(t)
-    := \sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
-    \quad t > t_0.
-  \]
-  Fix a $\theta\in \mathbb R$.
-  Taking $\theta_k=\theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor: indepedent of the limit zeta for critical and small}, we get that there exist $C_1,\delta_1 > 0$ such that
-  \begin{align}
-    \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde I'_1(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|
-    \leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}
-    \leq \frac{C_1}{t^{\delta_1}},
-    \quad t\geq 0.
-  \end{align}
-  Hence, according to \eqref{sum-m}, we have $\widetilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\widetilde {\mathbb P}_\mu$.
-  So we only need to prove that $|\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3,$ under $\widetilde {\mathbb P}_\mu$.
-
-  Step 1.
-  We will show that $|\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
-  Define for $k\geq 0$ and $t\geq k+1$,
-  \begin{align}
-    Y'_{t,k}
-    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big).
-  \end{align}
-	Then we have
-  \begin{equation}
-    \label{ineq: control of I1tb}
-    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I'_1(t)}] - \mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde{I}'_1(t)}]|
-    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|\big],
-    \quad t\geq t_0.
-  \end{equation}
-  Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
-  \[
-    \frac{\alpha \gamma}{1+\gamma} 
-    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} 
-    > 0.
-  \]
-  Fix this $\gamma$, then chose $\eta_0,\eta_1>0$ such that
-  \[
-    \frac{\alpha \gamma}{1+\gamma} 
-    > \eta_0 
-    > \eta_0 - 3\eta_1 
-    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} 
-    > 0.
-  \]
-	Define $\mathcal D_{t,k}$ and $K_{t,k}$ as in \eqref{def: Dtk} and \eqref{def: Ktk} respectively.
-	Using Lemma \ref{lem: control of mgtrs}, \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and an argument similar to that used in proving \eqref{eq: control of Ykt}, we get that there exist $C_2,C_3,\delta_2>0$ such that for $k\geq 0$ and $t\geq k+1$,
-  \begin{align}
-    & \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
-      = \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}\big] + \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}^c \big] \\
-    & \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\widetilde{P}}_{\mu}( \mathcal D_{t,k}^c ) \\
-    & \leq C_2 e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-(\eta_0 - 3\eta_1)(t-k)} + Ce^{-\delta_2(t-k)} \\
-    & \leq C_3( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)}).
-  \end{align}
-  Since $\alpha\beta<\kappa_f(1+\beta)b$,  we have
-  \begin{align}
-    \label{eq: condition for supercritical}
-    & -(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})
-      = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta}) \\
-    & > \frac{\gamma \alpha}{1+\gamma} - k_f b
-      =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
-  \end{align}
-  Using this, we have that there exist $C_4, \delta_3 > 0$ such that for $k\geq 0$ and $t\geq k+1$,
-  \begin{align}
-    \mathbb{\widetilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
-    & \leq C_3( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta_2(t-k)})
-    \leq C_4e^{-\delta_3 (t-k)}.
-  \end{align}
-  Now we can  use the  same argument used in the proof of Theorem \ref{thm: critical clt} to prove $|\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
-
-	Step 2.
-	We will show that $I'_2(t)\xrightarrow[t\to \infty]{d} 0$.
-	Let $\gamma \in (0,\beta)$.
-	According to \eqref{eq: condition for supercritical}, we can choose $\epsilon > 0$ small enough so that
-  \[
-    q
-    := - \frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}
-    > \frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta} + \frac{2\epsilon}{1+\beta} > 0.
-  \]
-	Recall that $A_t(\epsilon)=\{\|X_t\|>e^{(\alpha-\epsilon )t}\}$.
-  By \eqref{lem: control of XT}, there exist $C_5,\delta_4>0$ such that
-  \begin{align}
-    & |\mathbb{\widetilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
-      \leq 2\mathbb{\widetilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t}) \\
-    & \leq C_5(e^{-\epsilon\delta_4 t}+e^{-\delta_4 t}),
-      \quad t\geq t_0.
-  \end{align}
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C_6,C_7,C_8>0$ such that for all $t\ge t_0$,
-  \begin{align}
-    & \big|\mathbb{\widetilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)}]\big|
-      \leq |\theta| \mathbb{\widetilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)}\big] \\
-    & \leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big) \\
-    & \leq C_6  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big) \\
-    & \leq C_7  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    & \leq C_7 e^{-\frac{\epsilon}{1+\beta} t}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta} + \frac{2\epsilon}{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    & \leq C_7 e^{-\frac{\epsilon}{1+\beta} t} e^{qt} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-qk}\\
-    & \leq C_7 e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\leq C_8 e^{-\frac{\epsilon}{1+\beta} t} t^q.
-  \end{align}
-	Therefore, we get the desired result in this step.
-
-	Step 3. We will show that $I'_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
-  In fact, we have
-  \begin{align}
-    & |I'_3(t)|
-      \leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-      \leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
-      = e^{(\frac{\beta \alpha }{1+\beta} - k_fb)t} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
-      \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
-      \qedhere
-  \end{align}
+\end{comment}
+% END DELETED
+% *** Local central limit theorems
+% \subsection{The critical branching rate regime}
+\subsection{Local central limit theorems}
+\label{sec:critical}
+% ***** Local CLT for one interval for small and critical
+In this section, we will establish the following local central limit theorem for our super OU processes.
+\begin{thm}
+  \label{lem:PR:LC}
+  Let $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal{P}\setminus \{0\}$.
+  Then under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+  \begin{align}
+    \label{eq:PR:LC:1}
+    \Upsilon^f_t 
+    := \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}
+    \xrightarrow[t\to \infty]{d}\zeta^f_0, 
+  \end{align}
+  where $\zeta^f_0$ is an $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto e^{\langle Z_1(\theta f), \varphi\rangle}$.
+\end{thm}
+
+In fact, we can proof a stronger result:
+
+\begin{prop}
+  \label{thm:Key}
+  For each $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P \setminus \{0\}$, there exist $C,\delta>0$ such that 
+    for each $t\geq 1$ and $f \in \mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$, we have 
+    \[
+      \mathbb P_\mu 
+      \Big[  |\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  |\Big]
+      \leq C e^{- \delta t}.
+    \]
+\end{prop}
+\begin{proof}
+  Fix the $\mu \in \mathcal M_c(\mathbb R^d)$ and the $g \in \mathcal P\setminus \{0\}$.
+
+  \emph{Step 1.} Write $ A_t(\epsilon) :=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \} $ with $t\geq 0$ and $\epsilon > 0$. 
+  We will show that for each $f\in \mathcal P \setminus \{0\}$, $\epsilon > 0$ and $t\geq 0$, it holds that
+  \[  
+    \mathbb P_\mu \Big[ | \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1(\theta f), \varphi\rangle}; D^c | \mathscr F_t ]| \Big]
+    \leq J^f_1(t,\epsilon)+J^f_2(t,\epsilon)+J^f_3(t,\epsilon),
+  \]
+where
+\begin{align}
+\label{eq: Def of Ji}
+  J^f_1(t,\epsilon)
+  & := \mathbb{P}_{\mu} [ |\langle Z'''_1(\theta_t f), X_t\rangle |; A_t(\epsilon) ],
+  \\ J^f_2(t,\epsilon)
+  & := \mathbb{P}_{\mu}[|\langle Z_1(\theta_t f),X_t \rangle-\langle Z_1f, \varphi\rangle |; A_t(\epsilon)],
+  \\ J_3(t,\epsilon)
+  & :=2\mathbb{P}_{\mu}(A_t (\epsilon)\Delta D^c),
+  \\ \theta_t
+  & := \|X_t\|^{-(1 - \tilde \beta)}.
+\end{align}
+In fact, it follows from \eqref{eq: key equality}, the definitions of $U_1$, $Z'''_1$ and $Z_1$, that for all $t\geq 0$,
+\begin{align}
+  \label{eq: need1}
+  & \mathbb{P}_{\mu}[e^{i\Upsilon^f_t}|\mathscr{F}_t] 
+    = \mathbb{P}_{\mu}[\exp\{i\theta_t X_{t+1} (f) - i \theta_t X_t(P_1^\alpha f)\} |\mathscr{F}_{t}] \\
+  & = \exp\{\langle (U_1 - iP^\alpha_1 ) (\theta_t f),X_t\rangle\} 
+    = \exp\{\langle (Z_1 + Z'''_1) (\theta_t f),X_t\rangle\}.
+\end{align}
+From Proposition \ref{prop:PL:S}, we have $\operatorname{Re} \langle Z_1f, \varphi\rangle \leq 0$.
+Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get for each $t\geq 0$ and $\epsilon> 0$,
+\begin{align}
+  \label{eq: inequality that will used later}
+  & \mathbb{P}_\mu \Big[ |  \mathbb{P}_\mu [ e^{i\Upsilon^f_t} - e^{\langle Z_1f,\varphi \rangle} ; D^c | \mathscr F_{t}]   |\Big]  \\
+  &  \leq \mathbb{P}_\mu   \Big[ |    \mathbb{P}_\mu [ e^{i \Upsilon^f_t }-e^{\langle Z_1f, \varphi\rangle}; A_{t}(\epsilon) | \mathscr F_{t}] |  + 2\mathbb P_\mu ( A_{t}(\epsilon) \Delta D^c | \mathscr F_{t}) \Big] \\
+  & = \mathbb{P}_{\mu}\Big[ |\mathbb{P}_\mu [e^{i\Upsilon^f_t}| \mathscr F_{t}]-e^{\langle Z_1f, \varphi\rangle}| ; A_{t}(\epsilon) \Big] + J_3(t,\epsilon) \\
+  & \leq \mathbb{P}_\mu \Big[ |e^{\langle (Z_1+Z'''_1) (\theta_t f),X_{t} \rangle}-e^{\langle Z_1f, \varphi\rangle} | ; A_{t}(\epsilon) \Big]+  J_3(t,\epsilon) \\
+  & \leq \mathbb{P}_\mu \Big[ | \langle (Z_1+Z'''_1)(\theta_t f),X_{t} \rangle - \langle Z_1f, \varphi\rangle | ;A_{t}(\epsilon)\Big]+  J_3(t,\epsilon) \\
+  & \leq J^f_1(t,\epsilon) + J^f_2(t,\epsilon)+ J_3(t,\epsilon).
+\end{align}
+
+\emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for each $t\geq 1$ and $f \in \{\theta T_sg: s\geq 0,-1\leq \theta \leq 1\}$, we have
+\(
+  J^f_1(t,\epsilon)
+  \leq C_2e^{-\delta_2 t}.
+\)
+In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
+Acording to the step 1 of the proof of Lemma \ref{lem:m}, there exist $h_{20} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{20}$.
+Then, we have for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
+\begin{align}
+  & |Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
+    \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t-1}(\epsilon)}
+  \leq R \Big(\frac{h_{20}}{e^{(\alpha-\epsilon)(t-1)(1-\tilde \beta)}}\Big) \\
+   & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-1)}Rh_{20}.
+\end{align}
+Thus for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
+\begin{align}
+  \label{eq: estimate of J1}
+  J^f_1(t,\epsilon)
+  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[\langle Rh_0,X_{t-1}\rangle]\\
+  & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 R h_{20}, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
+\end{align}
+where $Q_0$ is defined by \eqref{eq:Q}.
+By taking $\epsilon>0$ small enough, we get the desired result in this step.
+
+\emph{Step 3.}
+We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for each $t \geq 1$ and $f\in \mathcal P_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.
+In fact, for all $t\geq 0$, and $f\in \mathcal P_g$,
+\begin{align}
+  & \langle Z_1(\theta_t f),X_{t}\rangle- \langle Z_1f, \varphi\rangle
+     = \theta_t^{1+\beta} \langle Z_1 f,X_t\rangle - \langle  Z_1 f,\varphi \rangle
+   =\Big\langle Z_1f - \langle  Z_1 f ,\varphi \rangle, \frac{X_{t-1}}{\|X_{t-1}\|}\Big\rangle,
+\end{align}
+and therefore,
+\begin{align}
+  \label{eq: prevJ2}
+  J^f_2(t,\epsilon)
+  & = \mathbb P_\mu\Big[\Big| \Big\langle Z_1f - \langle  Z_1 f ,\varphi \rangle, \frac{X_t}{\|X_t\|}\Big\rangle \Big|;A_t(\epsilon)\Big] 
+   \leq e^{-(\alpha-\epsilon)t} \mathbb{P}_{\mu}[| \langle q_f,X_t \rangle |].
+\end{align}
+where
+\(
+  q_f
+  = Z_1 f-\langle  Z_1 f,\varphi\rangle \in \mathcal P^*.
+\)
+It follows from Lemma \ref{lem:P:R} that there exists an $h_{30}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have
+\(
+  Q_1 (\operatorname{Re} q_f) \leq h_{30}
+  \text{ and } Q_1 (\operatorname{Im} q_f)\leq h_{30},
+\)
+where $Q_1$ is given by \eqref{eq:Q} with $\kappa=1$.
+In the rest of this step, fixing a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
+According to Lemma \ref{lem:P:M:uc}.(3) (with $\kappa=1$), there exists $C_{30}>0$ such that for all $t\geq 0$ and $f\in \mathcal P_g$,
+\begin{align}
+  & \mathbb{P}_{\mu}\left[\left|\langle q_f,X_{t}\rangle\right|\right]
+    \leq \|\langle \operatorname{Re} q_f, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} q_f, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} \\
+  & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{30}} \|\langle q, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_{30} e^{\frac{\alpha t}{1+\gamma}}.
+\end{align}
+Therefore, for all $t\geq 0, \epsilon > 0$ and $f \in \mathcal P_g$, we have
+\begin{align}
+  \label{eq: right bound for J2}
+   J^f_2(t, \epsilon)
+    \leq  C_3 e^{-(\alpha-\epsilon)t}e^{\frac{\alpha t}{1+\gamma}} 
+\leq C_{30} e^{-(\alpha\tilde \gamma -\epsilon)t}.
+\end{align}
+By taking $\epsilon >0$ small enough, we get the required result in this step.
+
+\emph{Step 4.}
+We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_4>0$ such that for all $t\geq 1$, $
+J_3(t,\epsilon)\leq C_4e^{-\delta_4 t}.
+$
+In fact, we have  for all $t\geq 0, \epsilon >0$,
+\[   
+  \mathbb P_{\mu}(A_{t}(\epsilon), D) 
+  = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
+  = \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
+  \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
+\]
+On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_{40}, \delta_{40}>0$ such that for all $t\geq 0$,
+\begin{equation}
+  \mathbb P_\mu(A_t(\epsilon)^c,D^c) 
+  \leq \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\| 
+  \leq e^{ - \epsilon t}) \leq C_{40} (e^{-\epsilon \delta_{40} t}+e^{-\delta_{40} t}).
+\end{equation}
+Combining these results, we get the desired result in step 4.
+
+\emph{Final step}, combining the results in Steps 1--4, we immediately get the desired result.
 \end{proof}
-
-% *** The large branching rate regime: CLT
-\subsection{The large branching rate regime: CLT}
-\label{sec: large rate clt}
+% ***** Local CLT
+
+% ***** local CLT one interval for large
+% DELETED
+\begin{comment}
 In this subsection, we revisit the large branching rate regime and prove Theorem \ref{thm: large clt}.
@@
 
-Recall that $H^p_t$ are defined before Lemma \ref{lemma26}. We write $a_p:= \langle \phi_p, g\rangle_\varphi$ for each $p \in \mathbb Z_+^d$.
+Recall that $H^p_t$ are defined before Lemma \ref{lem:M:L:ML}. We write $a_p:= \langle \phi_p, g\rangle_\varphi$ for each $p \in \mathbb Z_+^d$.
 
@@
   \label{large-central}
-  For all $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$,
-\begin{align}
-  \bar{\gamma}_{t,n}
-  := \sum_{p\in\mathcal{N}} a_p \frac { H^p_{t+n-1} - H^p_{t+n} } { e^{ - ( \alpha - | p | b ) t } ( e^{ - \alpha ( n - 1 ) } \| X_{ t + n - 1 } \| )^{ \frac { 1 } { 1 + \beta } } }
-  \xrightarrow[t\to \infty]{d}\bar{\zeta}_n,
-\end{align}
-	where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(\bar{m}_n[\theta g])$.
+  For all $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$, if $f \in \mathcal C_l$, then
+\begin{align}
+  \gamma^f_{t,n}
+  := \frac{X_{t+n+1}(P^\alpha_{-(n+1)}f) - X_{t+n}(P_{-n}^\alpha f)}{\|e^{- \alpha n}X_{t+n}\|^{1 - \tilde \beta}}
+  \xrightarrow[t\to \infty]{d}\zeta^f_{n,n+1}.
+\end{align}
 \end{lem}
 \begin{proof}
-  Fix $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$.
   We only need to show that
   \begin{align}
-    \mathbb{P}_{\mu}[\exp(i\bar{\gamma}_{t,n}); D^c]
-    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(\bar{m}_n[g]).
+    \mathbb{P}_{\mu}[\exp(i\gamma^f_{t,n}); D^c]
+    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(m_{n,n+1}[g]).
   \end{align}
@@
   Fix a $\gamma>0$ small enough such that $\alpha \gamma < (1+\gamma)b$.
-  Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment}.(3) with $\kappa=1$, there exists $C_3>0$ such that
+  Using Lemma \ref{control of gn} and Lemma \ref{lem:P:M:uc}.(3) with $\kappa=1$, there exists $C_3>0$ such that
   \begin{align}
@@
   Step 4.
-According to the Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that $ J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}$ for all $ t\geq0, n\geq 1$.
+According to the Step 4 of the proof of  Lemma \ref{lem:PR:LC}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that $ J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}$ for all $ t\geq0, n\geq 1$.
 
@@
 \end{proof}
-
+\end{comment}
+% END MOVED AND MODIFIED FROM BELOW
+% ***** LCLT for conditional one interval
+% DELETED
+\begin{comment}
+\begin{cor}
+\label{cor: used in next corollary}
+  Suppose $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq \kappa_fb(1+\beta)$.
+  Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C, \delta>0$ such that for $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
+\begin{equation}
+  \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma^f_{t,k}}-e^{m_{k,k+1}[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+  \leq Ce^{-\delta(t-k)}.
+\end{equation}
+\end{cor}
+\begin{proof}
+	Define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as in \eqref{eq: Def of Ji}.
+  According to \eqref{eq: inequality that will used later},  we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+  \begin{align}
+    & \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma^f_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
+    \leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
+  \end{align}
+
+  Let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
+	According to \eqref{eq: estimate of J1}, we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+  \begin{align}
+    & J^{\theta f}_1(k,t,\epsilon)
+      \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)} \\
+    & \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{ - ( \alpha \frac{ \rho} {1 + \beta} - \epsilon \frac{ 1 + \beta + \rho}{ 1 + \beta}) (t-k-1)}.
+\end{align}
+From the definitions of $Z_1$ and $m_{t,t+1}$ we get that for all $g\in \mathcal P, \theta \geq 0, t\geq 0$,
+\[
+	Z_1( \pm \theta g) 
+  = \theta^{1+\beta} Z_1(\pm g), \quad m_{t,t+1}[\pm \theta g] = \theta^{1+\beta} m_t[\pm g].
+\]
+Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$, $ J^{\pm \theta f}_2(t,k,\epsilon)
+= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon). $
+According to this and \eqref{eq: right bound for J2},
+we have that there exists $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
+\begin{equation}
+  \label{eq:31step3b}
+  J^{\theta f}_2(t,k,\epsilon)
+  \leq C |\theta|^{1+\beta}e^{-(\alpha \tilde \gamma - \epsilon)(t-k-1)}.
+\end{equation}
+Finally, noticing that $|\theta| < \Theta$, using the estimates of $J^{\theta f}_{i}, i = 1,2$ above and the estimate of $J_3$ in Step 4 of the proof of the previous lemma, we get the desired result by choosing $\epsilon$ small enough.
+\end{proof}
+\end{comment}
+% END DELETEd
+% ***** LCLT for Multiple interval
+The following corollary of Proposition \ref{thm:Key} will be used later in the proof of our main result Theorem \ref{thm:M}.
+\begin{cor}
+  \label{cor:MI}
+  Suppose that $g\in \mathcal{P}\setminus\{0\}$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
+  Then there exist $C,\delta>0$ such that for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$,
+\begin{equation}
+  \label{32corollary}
+  \Big|\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{k=l}^ne^{i \Upsilon^{f_k}_{k} }-\prod_{k=l}^n e^{\langle Z_1f_k, \varphi\rangle}\Big]\Big|\leq C e^{-\delta l}.
+\end{equation}
+\end{cor}
+\begin{proof}
+  For each $l\leq n$ in $\mathbb Z_+$, $k \in \{l,\dots,n\}$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, define
+  \[
+    a_k
+    :=  \mathbb{\widetilde{P}}_{\mu}\Big[\prod_{j=l}^{k} e^{i\Upsilon_j^{f_j}}\Big] \times \Big(\prod_{j=k+1}^{n} e^{ \langle Z_1f_j,\varphi \rangle} \Big).
+  \]
+  Then for each $l\leq n$ in $\mathbb Z_+$, $k \in \{l,\dots,n\}$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+  \begin{align}
+    & a_{k} - a_{k-1}
+      =\mathbb{P}_{\mu}(D^c)^{-1} \mathbb{P}_{\mu}\Big[(e^{i\Upsilon^{f_k}_k}-e^{\langle Z_1f_k, \varphi\rangle})\prod_{j=l}^{k-1} e^{i\Upsilon_j^{f_j}};D^c\Big] \Big(\prod_{j=k+1}^n e^{\langle Z_1f_j, \varphi\rangle}\Big)\\
+    & =\mathbb{P}_{\mu}(D^c)^{-1} \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c|\mathscr F_k] \prod_{j=l}^{k-1} e^{i\Upsilon_j^{f_j}}\Big] \Big(\prod_{j=k+1}^{n}e^{\langle Z_1f_j, \varphi\rangle}\Big).
+  \end{align}
+  By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that for each $l\leq n$ in $\mathbb Z_+$, each $k \in \{l,\dots , n\}$, and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+  \begin{align}
+    | a_{k} - a_{k-1}|
+    & \leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c | \mathscr{F}_k]\big|\Big]
+    \leq C_0 e^{-\delta_0 k}.
+  \end{align}
+  Therefore, there exist $C_1,\delta_1 >0$ such that for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+  \begin{align}
+    \text{LHS of \eqref{32corollary}}
+    & = \left|a_n-a_{l-1}\right|
+    \leq \sum_{k=l}^n\left|a_{k}-a_{k-1}\right|
+    \leq \sum_{k=l}^n C_0 e^{-\delta_0 k}
+      \leq C_1 e^{- \delta_1 l}.
+      \qedhere
+  \end{align}
+\end{proof}
+
+% ***** local CLT multiple interval for large branching rate
+% DELETED 
+\begin{comment}
 \begin{lem}
@@
   \end{align}
-  According to Step 1 and Proposition \ref{prop: alpha stable rv}, there exists $C_2>0$ such that for any $n=1,\cdots, m$ and $t\geq 0$, we have
+  According to Step 1 and Proposition \ref{prop:PL:S}, there exists $C_2>0$ such that for any $n=1,\cdots, m$ and $t\geq 0$, we have
   \begin{align}
@@
 \end{proof}
-Now we define
-\begin{align}
-  \widetilde{\gamma}_{t,n}
-  :=\sum_{p\in \mathcal{N} } a_p \frac { H^p_{t+n-1} - H^p_{t+n} } { e^{-(\alpha-|p|b)t} \| X_{t} \|^{ \frac{1}{1+\beta}}},
-  \quad t\geq 0, n\geq 1.
-\end{align}
-\begin{lem}
-  \label{lem: lemma04}
-  For all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
-  \begin{align}
-    \Big|\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^m e^{i\theta \widetilde{\gamma}_{t,n}}]-\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|
-    \leq C m e^{-\delta t}.
-  \end{align}
-\end{lem}
-\begin{proof}
-  Fix a $\theta \in \mathbb R$ and a $\mu \in \mathcal M_c(\mathbb R^d)$.
-  According to \cite[Lemma 3.4.3]{Durrett2010Probability},
-  \begin{align}
-    \label{ineq: used next 3}
-    \Big|\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \widetilde{\gamma}_{t,n}}]-\widetilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq \sum_{n=1}^m\widetilde{\mathbb{P}}_{\mu}[|Y''_{t,n}|],
-  \end{align}
-  where $Y''_{t,n}:=e^{i\theta\widetilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}}$.
-  Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
-  \[
-    \frac{\alpha \gamma}{1+\gamma}
-    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0,
-    \qquad
-    \alpha\gamma
-    >K(1+\gamma)b,
-  \]
-  where $K$ is defined in \eqref{eq: def of N}.
-  Fix this $\gamma$, and then choose $\eta_0,\eta_1>0$ such that
-  \[
-    \frac{\alpha \gamma}{1+\gamma}
-    > \eta_0
-    > \eta_0 - 3\eta_1
-    > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta}
-    > 0.
-  \]
-  Define for all $n \geq 1$ and $t\geq 0$,
-  \begin{align}
-    \label{def: Dtk1}
-    \mathcal{D}_{t,n}
-    & :=\left\{|H_t-H_{t+n-1}|\leq  e^{-\eta_0 t}, H_{t}> 2e^{-\eta_1t}\right\}.
-  \end{align}
-
-  Step 1. 
-  Similar to Step 1 in the proof of Theorem \ref{thm: critical clt}, we can show that there exist $C_1,\delta_1 >0$ such that for all $n \geq 1$ and $t\geq 0$, $ \mathbb{ \widetilde{ P } }_{ \mu } \big[ | Y''_{ t, n } | \mathbf{ 1 }_{ \mathcal{ D }^c_{t, n } } \big] \leq C_1 e^{-\delta_1 t}.
+\end{comment}
+% *** The small branching rate regime
+\subsection{Central limit theorem for $f\in \mathcal C_s$}
+\label{sec: small rate}
+
+\begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:1})]
+	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_s$ and $t_0 > 1$ be large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
+  For each $t\geq t_0$, in this proof we write $\theta_t = \|X_t\|^{\tilde \beta - 1}$, 
+  \begin{multline} 
+    \label{eq:PM:CLTS:1}
+    \theta_t  X_t(f)    
+    = I^f_1(t) + I^f_2(t) + I^f_3(t)
+    := \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \theta_t \mathcal I_{t-k-1}^{t-k} X_t(f) \Big)\\
+    + \Big( \theta_t \mathcal I_0^{t-\lfloor t \rfloor} X_t(f)   + \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \theta_t \mathcal I_{t-k-1}^{t-k} X_t(f) \Big) + (\theta_t X_0(P_t^\alpha f) ),
+\end{multline}
+and
+\(    
+ I^f_0(t)
+ := \sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f},
+\)  
+where $\tilde f:= e^{\alpha(\tilde \beta - 1)} f$.
+
+% ****** Step 1.
+  \emph{Step 1.} We show that $I^f_0(t) \xrightarrow[t\to \infty]{d} \zeta^f$. 
+  In fact, for each $k \in \mathbb Z_+$, we have  $T_{k} \tilde f \in \mathcal P_{\tilde f}:=\{\theta T_n \tilde f: n \in \mathbb Z_+, \theta \in [-1,1]\}$. 
+  Therefore from Proposition \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
+  \begin{align}
+    \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i I^f_0(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}\tilde f, \varphi\rangle \Big)\Big|
+    \leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)},
+    \quad t\geq t_0.
+  \end{align}
+  On the other hand, using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of semigroup $(P_t)$, we can verify that
+  \begin{align}
+    \label{eq:PM:CLTS:2}
+    & \sum_{k=0}^\infty \langle Z_1 T_{k} \tilde f, \varphi \rangle
+    = \sum_{k=0}^\infty \int_0^1 \langle P_u^\alpha ((-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle ~du
+    \\& = \sum_{k=0}^\infty \int_0^1 e^{\alpha u} \langle  (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle ~du
+    \\& = \sum_{k=0}^\infty \int_0^1 \langle  (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle~du
+    = \int_0^\infty \langle  (-iT_{u} f)^{1+\beta}, \varphi\rangle~du = m[f].
+  \end{align}
+  Therefore, we have $\mathbb{\widetilde{P}}_{\mu} [e^{i I^f_0(t)} ] \xrightarrow[t\to \infty]{} e^{m[f]}$.
+Since $I_0^f(t)$ is linear in $f$, we can replace $f$ with $\theta f$, $\theta \in \mathbb R$, and then the desired result in this step follows.
+
+% ****** Step 2.
+  \emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$.
+  In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we can write for each $t\geq t_0$ that
+\begin{align}    
+  \label{eq:PM:S:1}
+|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t) - I^f_0(t) ) }] - 1|
+    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\big],
+\end{align}
+where
+\(
+Y_{t,k}
+:= \exp(i \Upsilon_{t-k-1}^{T_{k} \tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1.
+\)
+We claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb Z_+$ and $t\geq k+1$.
+And therefore there exists $C_2'>0$ such that for each $t \geq t_0$, $|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]| \leq C_2't^{-\delta_1}$ which, combines with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
+
+We will show this claim in the following substep 2.1 and 2.2. 
+First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with
+\(
+\alpha \tilde \gamma
+>\eta
+> \eta - 3\eta' 
+> \alpha \tilde \beta - \alpha \tilde \gamma 
+> 0;
+\)
+and define for each $k \in \mathbb Z_+$ and $t\geq k+1$,
+\[  
+\mathcal{D}_{t,k}
+  :=\{|H_t-H_{t-k-1}|\leq  e^{-\eta (t-k-1)}, H_{t-k-1}> 2e^{-\eta' (t-k-1)}\},
+\]
+where $H_t := e^{-\alpha t}\|X_t\|$.
+
+% ******* Step 2.1
+  \emph{Substep 2.1.} We show that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq k+1$, $ \mathbb{\widetilde{P}}_{\mu} \big[ |Y_{t,k}| ;\mathcal{D}^c_{t,k} \big] \leq C_{2.1} e^{-\delta_{2.1} (t-k)}.$
+  In fact, it follows from Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality that there exist $C_{2.1}', \delta_{2.1}'>0$ such that for all $k \geq 0$ and $t\geq k+1$,
+  \begin{align}
+    \label{eq: prob of Dtkc}
+    & \mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
+    \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta'(t-k-1)}) \\
+    & \leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|] +  \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta'(t-k-1)}; D^c) \\
+    & \leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma} + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_{t-k-1}\leq 2e^{-\eta'(t-k-1)}) \\
+    & \leq C'_{2.1} e^{-(\alpha \tilde \gamma - \eta)(t-k-1)}+C'_{2.1} e^{-\delta'_{2.1}(t-k-1)}.
+  \end{align}
+  This implies the desired result in this substep, since $|Y_{t,k}| \leq 2$ a.s..
+
+% ******* Step 2.2 
+  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for each $k\in \mathbb Z_+$ and $t\geq k+1$, it holds that
+\(
+    \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}]
+    \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.
+\)
+  In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha $; and therefore for each $k\in \mathbb Z_+$ and $t \geq k + 1$, 
+  \[
+    \Upsilon_{t-k-1}^{T_{k} \tilde f} 
+    = \frac{X_{t-k}(T_{k} \tilde  f) - X_{t -k-1}(P_1^\alpha T_{k} \tilde f)}{\|X_{t-k-1}\|^{1-\tilde \beta}} 
+    = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f)}{\|e^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
+  \]
+  Since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \in \mathbb Z_+$ and $t\geq k+1$,
+  \begin{align}
+    \label{eq: control of Ykt}
+    & \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}] \\
+    & \leq \mathbb{\widetilde{P}}_{\mu}\Big[|\mathcal I_{t-k-1}^{t-k}\langle f , X_t\rangle | \cdot \Big| \| e^{\alpha(k+1)}X_{t-k-1}\| ^{ \tilde \beta - 1} - \|X_t\|^{ \tilde \beta - 1}\Big|; \mathcal D_{t,k}\Big] \\
+    & \leq  e^{\alpha(\tilde \beta - 1)t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}X_t(f)|\cdot K_{t,k}\big],
+  \end{align}
+  where
+\[    
+K_{t,k}
+    := \Big| \frac {H_t^{1- \tilde \beta} - H_{t-k-1}^{1 - \tilde \beta}} {H_t^{1 - \tilde \beta} H_{t-k-1}^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t,k}}.
+\]  
+Note that, since $\eta' < \eta$, we have almost surely on $\mathcal D_{t,k}$,
+  \begin{align}
+    H_t
+    & \geq H_{t-k-1}- e^{-\eta (t-k-1)}
+      \geq 2e^{-\eta'(t-k-1)}-e^{-\eta(t-k-1)}
+      \geq e^{-\eta'(t-k-1)}.
+  \end{align}
+  Therefore, for each $k \in \mathbb Z_+$ and $t\geq k+1$, almost surely  on $\mathcal D_{t,k}$,
+  \begin{align}
+    & \Big|H_t^{1- \tilde \beta}-H_{t-k-1}^{1- \tilde \beta}\Big|
+      \leq (1- \tilde \beta) \max \{ H_t^{-\tilde \beta }, H_{t-k-1}^{ -\tilde \beta} \} | H_t - H_{t-k-1} | \\
+    & \leq (1- \tilde \beta ) \max\{e^{\eta' (t-k-1)}, \frac{1}{2}e^{\eta'(t-k-1)}\}^{\tilde \beta} e^{-\eta(t-k-1)}  \leq (1- \tilde \beta) e^{-(\eta - \eta') (t-k-1)}
+  \end{align}
+  and
   $
-
-  Step 2.
-  We will show that there exist $C_2,\delta_2 > 0$ such that for all $n\geq 1$ and $t\geq 0$,
-  \begin{align}
-    \label{thm12211}
-    \mathbb{\widetilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]
-    \leq C_1e^{-\delta_2 t}.
-  \end{align}
-  In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have, for all $t \geq 0$ and $n\geq 1$,
-  \begin{align}
-    \label{large: used next}
-    & \widetilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\\
-    & \leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}\widetilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot\Big|\frac{1}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}\Big]\\
-    & \leq |\theta| \sum_{p\in\mathcal{N}} |a_p| e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}\widetilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot K'_{t,n}\Big],
+    |H_t^{1 - \tilde \beta} H_{t-k-1}^{ 1 - \tilde \beta}|
+    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta'(t-k-1)}.
+  $
+  Thus, there exists  $C_{2.2}'> 0$ such that for all $k \geq 0, t\geq k+1$, almost surely
+  \begin{equation}
+    \label{ineq: control of Kkt}
+    K_{t,k}
+    \leq C_{2.2}' e^{-(\eta - 3\eta')(t-k-1)}.
+  \end{equation}
+  Now, by Lemma \ref{lem: control of mgtrs}, there exist $C''_{2.2}>0$ such that for all $k\geq 0$ and $t\geq k+1$,
+  \begin{align}
+    \label{eq: Y in D}
+    & \mathbb{\widetilde{P}}_{\mu} [|Y_{t,k}| ; \mathcal{D}_{t,k} ]
+    \leq C_{2.2}' e^{\alpha (\tilde \beta - 1)t} \mathbb{\widetilde{P}}_{\mu} [ | \mathcal{I}_{t-k-1}^{t-k}X_t(f)| ] e^{-(\eta - 3\eta')(t-k-1)} \\
+    & \leq \frac{C_{2.2}' } {\mathbb{P}_{\mu}(D^c)} e^{ \alpha (\tilde \beta - 1)t} \|\mathcal{I}_{t-k-1}^{t-k} X_t(f)\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta - 3\eta')(t-k - 1)} \\
+    & \leq C_{2.2}'' e^{\alpha(\tilde \beta - \tilde \gamma)t} e^{ (\alpha \tilde \gamma - \kappa_f b)k} e^{-(\eta - 3\eta')(t-k)} 
+     \leq C_{2.2}'' e^{\alpha(\tilde \beta - \tilde \gamma)(t-k)} e^{-(\eta - 3\eta')(t-k)},
+  \end{align}
+  as desired in this step.
+  In the last inequality, we used the fact that $f\in \mathcal C_s$ and therefore $\alpha \tilde \beta < \kappa_f b$.
+
+% ****** Step 3  
+  \emph{Step 3.}
+  We show that $I^f_2(t)\xrightarrow[t\to \infty]{d} 0$.
+  First fix a $\gamma \in (0,\beta)$ in this step. 
+  From the fact that $\kappa_f b -\alpha \tilde \gamma > \alpha (\tilde \beta - \tilde \gamma)$, we can chose $\epsilon >0$ small enough such that $q:=\kappa_fb- \alpha \tilde \gamma  > \alpha (\tilde \beta - \tilde \gamma) + 2\epsilon (1 - \tilde \beta)$.
+  Now writing $\mathcal{E}_t:=\{\|X_t\|>e^{(\alpha-\epsilon) t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
+  \begin{equation}
+    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
+    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})\leq C_3e^{-\delta_3 t}
+    , \quad t\geq0.
+  \end{equation}
+  Therefore,
+  \begin{equation}
+    \label{Theorem123}
+    |\mathbb{\widetilde{P}}_{\mu}[e^{i I^f_2(t)}-1;\mathcal{E}^c_t]|
+    \leq 2\mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
+    \leq 2C_3e^{-\delta_3 t},
+    \quad t\geq t_0.
+  \end{equation}
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C_3',C_3'',C_3'''>0$ such that for each $t\geq t_0 >1$, 
+  \begin{align}
+    & |\mathbb{\widetilde{P}}_{\mu} [ (e^{i I^f_2(t)}-1);\mathcal{E}_t]|
+      \leq  \mathbb{\widetilde{P}}_{\mu} [ |I^f_2(t)|;\mathcal{E}_t] \\
+    & \leq  ( e^{(\alpha-\epsilon) t} )^{\tilde \beta - 1}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu} [| \mathcal{I}_{t-k-1}^{t-k} X_t(f) |] + \mathbb{\widetilde{P}}_{\mu}[| \mathcal{I}_{0}^{t-\lfloor t\rfloor} X_t(f)|]\Big) \\
+    & \leq ( e^{(\alpha-\epsilon) t} )^{\tilde \beta - 1}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k} X_t(f) \|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} X_t(f)\|_{\mathbb P_\mu;1+\gamma}\Big) \\
+    & \leq C_3' e^{\alpha (\tilde \beta - \tilde \gamma)t} e ^{\epsilon (1-\tilde \beta) t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{(\alpha\tilde \gamma-\kappa_f b)k}
+      \leq C_3' e^{q t}e^{-\epsilon ( 1 - \tilde \beta)t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{-q k}
+\\ 
+    & \leq C_3'' e^{q(t - \lceil t - \ln t\rceil)}e^{-\epsilon(1 - \tilde \beta) t}
+\leq C_3'' t^q e^{- \epsilon(1 - \tilde \beta) t}.
+  \end{align}
+  From this and \eqref{Theorem123}, we get that $\widetilde {\mathbb P}_\mu[e^{i I^f_2(t)}] \xrightarrow[t\to \infty]{} 1$. 
+  Note that $I^f_2(t)$ is linear in $f$ so we can replace $f$ with $\theta f$ for $\theta \in \mathbb R$ and get the desired result in this step.
+
+% ****** Step 4
+	\emph{Step 4.} We will show that $I^f_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+  In fact, we have
+  \begin{align}
+    & |I^f_3(t)|
+      \leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{1 - \tilde \beta }}
+      \leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{1 - \tilde \beta}}
+      = e^{(\alpha \tilde \beta - k_fb)t} H_t^{\tilde \beta - 1} \langle Qf,X_0\rangle
+      \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
+  \end{align}
+
+% ****** Final step
+ 	\emph{Final step}, combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:1}.
+\end{proof}
+
+% *** Critical branching rate regime
+\subsection{Central limit theorem for $f \in \mathcal C_c$}
+% ***** Proof of thm:M:2
+\begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:2})]
+  	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_c$ and $t_0 > 1$ large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
+    For each $t\geq t_0$, in this proof we write $\theta_t = \|t X_t\|^{\tilde \beta - 1}$; and we define $I_i^f(t)$ for $i = 1,2,3$ using \eqref{eq:PM:CLTS:1}, and set
+$
+    I^f_0(t)
+    := t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f}
+$
+where $\tilde f = e^{\alpha(\tilde \beta - 1)} f$
+
+% ****** Step 1.
+  \emph{Step 1.} We show that $I^f_0(t) \xrightarrow[t\to \infty]{d} \zeta^f$. 
+  In fact, for each $t \geq  t_0 > 1$ we have $t^{\tilde \beta - 1} < 1$; and therefore, for each $k \in \mathbb Z_+$, we have $t^{\tilde \beta - 1} T_{k+1} f \in \mathcal P_f:=\{\theta T_n f: n \in \mathbb Z_+, \theta \in [-1,1]\}$.
+  Therefore from Proposition \ref{cor:MI} and that $\tilde \beta - 1 = -\frac{1}{1+\beta}$ we get that there exist $C_1,\delta_1 > 0$ such that
+  \begin{align}
+    \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i I^f_0(t)} ]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}\tilde f, \varphi\rangle \Big)\Big|
+    \leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}
+    \leq \frac{C_1}{t^{\delta_1}},
+    \quad t\geq t_0.
+  \end{align}
+  Note that since $f \in \mathcal C_c\setminus \{0\}$, so $T_k \tilde f = \tilde f$ for each $k \in \mathbb Z_+$.
+  Similar to the argument in \eqref{eq:PM:CLTS:2} we have 
+  \[ 
+    \lim_{t\to \infty} \frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1 T_{k}\tilde f, \varphi\rangle
+    = \langle Z_1 \tilde f,\varphi \rangle
+    = \langle (-if)^{1+\beta}, \varphi \rangle
+    = m[f].
+  \]
+  Therefore $\mathbb {\widetilde P}_\mu[e^{i I^f_0(t)}] \xrightarrow[t\to \infty]{} e^{m[f]}$.
+  Noticing that $I_0^f(t)$ is linear in $f$, the desired result in this step follows.
+
+% ****** Step 2.
+  \emph{Step 2.} We show that $ I^f_1(t) - I^f_0 (t) \xrightarrow[t\to \infty]{d} 0$.
+  In fact, similar to the Step 2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we also have \eqref{eq:PM:S:1} is valid with
+\(
+    Y_{t,k}
+    := \exp(i t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k}\tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1.
+\)
+  We also claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb N$ and $t\geq k+1$; and similarly, the desired results in this step follows with this claim.
+
+  We will show this claim in the following substep 2.1 and 2.2. 
+  First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with
+  \(
+    \alpha \tilde \gamma
+    >\eta
+    > \eta - 3\eta' 
+    > \alpha \tilde \beta - \alpha \tilde \gamma 
+    > 0;
+  \)
+  and define for each $k \in \mathbb N$ and $t\geq k+1$ that
+\(    
+\mathcal{D}_{t,k}
+    :=\{|H_t-H_{t-k-1}|\leq  e^{-\eta (t-k-1)}, H_{t-k-1}> 2e^{-\eta' (t-k-1)}\}.
+\)
+
+% ******* subStep 2.1
+  \emph{Substep 2.1.} Similar to the substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$,
+  \(
+    \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}]
+    \leq C_{2.1} e^{-\delta_{2.1} (t-k)}.
+  \)
+  We omit the details.
+
+% ******* Step 2.2 
+  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for each $k\in \mathbb N$ and $t\geq k+1$,
+\(    
+\mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}]
+    \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.
+\)  
+In fact, noticing that for $f\in \mathcal C_c$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha $; and therefore for each $k\in \mathbb Z_+$ and $t \geq k + 1$, 
+  \[
+    t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k} \tilde f} 
+    = \frac{X_{t-k}(T_{k} \tilde f) - X_{t -k-1}(P_1^\alpha T_{k} \tilde f)}{\|t X_{t-k-1}\|^{1-\tilde \beta}} 
+    = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f)}{\|te^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
+  \]
+  The rest is similar to the substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:2}).
+  We omit the details.
+
+% ****** Step 3  
+  \emph{Step 3.}
+  We show that $ I^f_2(t)\xrightarrow[t\to \infty]{d} 0$.
+  In fact, writing $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
+  \begin{equation}
+    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
+    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_3( t^{-\delta_3}+e^{-\delta_3 t})
+    , \quad t\geq0.
+  \end{equation}
+  Therefore,
+  \begin{equation}
+    \label{Theorem123}
+    |\mathbb{\widetilde{P}}_{\mu}[e^{i I^f_2(t)}-1;\mathcal{E}^c_t]|
+    \leq 2\mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
+    \leq C_3(t^{-\delta_3}+e^{-\delta_3 t}),
+    \quad t\geq t_0.
+  \end{equation}
+  Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\tilde \beta - \tilde \gamma) \leq \frac{1}{2}(1- \tilde \beta)$.
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C_3',C_3'',C_3'''>0$ such that for each $t\geq t_0 >1$, 
+  \begin{align}
+    & |\mathbb{\widetilde{P}}_{\mu} [ (e^{i I^f_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
+      \leq  \mathbb{\widetilde{P}}_{\mu} [ |I^f_2(t)|\mathbf{1}_{\mathcal{E}_t}] \\
+    & \leq  (t^{\frac{1}{2}} e^{\alpha t} )^{\tilde \beta - 1}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu} [| \mathcal{I}_{t-k-1}^{t-k} X_t(f) |] + \mathbb{\widetilde{P}}_{\mu}[| \mathcal{I}_{0}^{t-\lfloor t\rfloor} X_t(f)|]\Big) \\
+    & \leq C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - 1)t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k} X_t(f) \|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} X_t(f)\|_{\mathbb P_\mu;1+\gamma}\Big) \\
+    & \leq C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{(\alpha\tilde \gamma-\kappa_f b)k}
+      = C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - \tilde \gamma) t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{-\alpha (\tilde \beta -\tilde \gamma) k}
+\\ 
+    & \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)(t - \lceil t - \ln t\rceil)}.
+      \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} t^{\alpha (\tilde \beta - \tilde \gamma)}.
+  \end{align}
+  From this and \eqref{Theorem123}, combined with the fact that $I^f_2(t)$ is linear in $f$, we get the desired result in this step.
+
+% ****** Step 4
+  \emph{Step 4.}
+  Similar to the Step 4 of the Proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+  We omit the details.
+
+% ****** Final step
+ 	\emph{Final step.} Combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:2}.
+\end{proof}
+
+% *** The large branching rate regime: CLT
+\subsection{Central limit theorem for $f\in \mathcal C_l$}
+\label{sec: large rate clt}
+% ***** Proof or the main result
+\begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:3})]
+Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $f \in \mathcal C_l$.
+Define $\mathcal N:= \{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b\}$.
+In this proof we write for each $t\geq 0$ that
+\begin{align}
+  & \frac{X_tf - \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta \geq |p|b} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}H_\infty^p}{\|X_t\|^{1- \tilde \beta}}
+    = \sum_{p\in \mathcal N}\frac{ \langle f,\phi_p\rangle_\varphi [X_t(\phi_p) - e^{(\alpha - |p|b)t}H_\infty^p]}{\|X_t\|^{1- \tilde \beta}}
+  \\& = \sum_{p \in \mathcal N} \frac{\langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}(H_t^p - H_\infty^p)}{\|X_t\|^{1- \tilde \beta}}
+   = \sum_{k=0}^\infty \sum_{p \in \mathcal N}  \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}
+  \\ & =: \sum_{k=0}^\infty \widetilde \Upsilon_{t,k} 
+  = \Big(\sum_{k = 0}^{\lfloor t^2 \rfloor}  \widetilde \Upsilon_{t,k} \Big) + \Big(\sum_{k = \lceil t^2 \rceil}^\infty  \widetilde \Upsilon_{t,k}\Big) 
+  = : I^f_1(t) + I^f_2(t),
+\end{align}
+and $I^f_0(t):= \sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f}$ where $\tilde f := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f, \phi_p \rangle_\varphi \phi_p$.
+
+\emph{Step 1.} We show that $I^f_0(t) \xrightarrow [t\to \infty]{d} \zeta^{-f}$.
+In fact, since $T_k\tilde f \in \mathcal P_{\tilde f}$ for each $k\in \mathbb Z_+$, from Corollary \ref{cor:MI} we have $\widetilde{ \mathbb P}_\mu[e^{i I_0^f(t)}]\xrightarrow[t\to \infty]{}\exp\{\sum_{k=0}^\infty \langle Z_1T_k(-\tilde f),\varphi\rangle\}$.
+Using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of semigroup $(P_t)_{t\geq 0}$ we can verify that
+\begin{align}
+  \label{eq:PM:CLTS:2}
+  & \sum_{k=0}^\infty \langle Z_1 T_{k} (-\tilde f), \varphi \rangle
+    = \sum_{k=0}^\infty \int_0^1 \langle P_u^\alpha ((iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle ~du
+  \\& = \sum_{k=0}^\infty \int_0^1 e^{\alpha u} \langle  (iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle ~du
+  \\& = \sum_{k=0}^\infty \int_0^1 \langle  (iT_{k+ u} f)^{1+\beta}, \varphi\rangle~du
+  = \int_0^\infty \langle  (iT_{u} f)^{1+\beta}, \varphi\rangle~du = m[-f].
+\end{align}
+Now, combining with the fact that $I_0^f(t)$ is linear in $f$ the result in this step follows.
+
+\emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$. 
+In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we can write for each $t\geq 0$ that $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq \sum_{k=0}^{\lfloor t^2 \rfloor} \widetilde {\mathbb {P}}_\mu[|Y_{t,k}|]$ where $Y_{t,k} := e^{i(\widetilde {\Upsilon}_{t,k} - \Upsilon_{t+k}^{-T_{k}\widetilde {f}})} - 1.
+$
+We claim that there exist $C_2, \delta_2>0$ such that $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|] \leq C_2e^{-\delta_2 t}$ for each $t\geq 0$ and $k \in \mathbb Z_+$. 
+And therefore $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq (t^2+1)C_2e^{-\delta_2 t}$ which, combined with the fact that $I_1^f(t) - I_0^f(t)$ is linear in $f$, completes this step.
+
+We will show this claim in the following substeps 2.1 and 2.2.
+First we chose $\gamma\in(0,\tilde \beta)$ close enough to $\beta$ so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$; and even closer so that there exists $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
+We also define $\mathcal{D}_{t,k} :=\{|H_t-H_{t+k}|\leq  e^{-\eta t}, H_{t}> 2e^{-\eta' t}\}$.
+
+% ******* subStep 2.1
+\emph{Substep 2.1.} Similar to the substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$,
+\(
+\mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}]
+\leq C_{2.1} e^{-\delta_{2.1} t}.
+\)
+We omit the details.
+
+\emph{Substep 2.2.} We show that there exist $C_{2.2}, \delta_{2.2}>0$ such that for each $k \in \mathbb Z_+$ and $t\geq 0$, we have $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|; \mathcal D_{t,k}]\leq C_{2.2}e^{- \delta_{2,2} t}$.
+In fact, it can be verified that for each $k \in \mathbb Z_+$ and $t\geq 0$, 
+\begin{align}
+& \Upsilon_{t+k}^{-T_k\tilde f} 
+  = \frac{X_{t+k}(P^\alpha_1T_k\tilde f) - X_{t+k+1}(T_k \tilde f)}{\|X_{t+k}\|^{1 - \tilde \beta}}
+  \\& = \sum_{p}\langle\tilde f,\phi_p\rangle_\varphi e^{-(\alpha \tilde \beta - |pb|)k}\frac{ X_{t+k}(P_1^\alpha \phi_p) - X_{t+k+1}(\phi_p)}{\|X_{t+k}\|^{1 - \tilde \beta}}
+  \\& = \sum_{p}\langle f,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t}\frac{H_{t+k}^p-H_{t+k+1}^p }{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}}. 
+\end{align}
+Therefore for all $k\in \mathbb Z_+$ and $t\geq 0$,
+\begin{align}
+  &|Y_{t,k}| \mathbf 1_{\mathcal D_{t,k}}
+  \leq \Big( \sum_{p\in \mathcal N}\langle f,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)\mathbf 1_{\mathcal D_{t,k}}.
+  \\ &= \Big( \sum_{p\in \mathcal N}\langle f,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big)e^{\alpha (\tilde \beta - 1)t} K_{t,k}
+  \\ &= \Big( \sum_{p\in \mathcal N}\langle f,\phi_p\rangle_\varphi  e^{(\alpha \tilde \beta  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) K_{t,k},
 \end{align}
 where
-  \begin{align}
-    K'_{t,n}
-    := \Big| \frac{ H_t^{ \frac { 1 } { 1 + \beta } } - H_{ t + n - 1 }^{ \frac { 1 }{ 1 + \beta } } } { H_t^{ \frac{ 1 }{ 1 + \beta }} H_{t+n-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}.
-  \end{align}
-	Since $\eta_1 < \eta_0$, using an argument similar to that used in Step 2 of the proof of Theorem \ref{thm: critical clt}, we can show that, there is a constant $C_3> 0$ such that,
-  \begin{align}
-    \label{ineq: control of Kkt1}
-    K'_{t,n}
-    \leq C_3 e^{-(\eta_0 - 3\eta_1) t},
-    \quad t \geq 0, n\geq 1.
-  \end{align}
-  According to Lemma \ref{lem: control of wt}, there exists $C_4>0$ such that for all $t\geq 0$ and $n\geq 1$,
-  \begin{align}
-    \label{ineq:used next 2}
-    & \widetilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]
-      \leq \frac{C_3}{\mathbb{P}_{\mu}(D^c)} |\theta| \sum_{ p \in \mathcal{N} } |a_p| e^{ ( \alpha - |p| b ) t } e^{ - \frac{ \alpha } { 1 + \beta } t } e^{ - ( \eta_0 - 3 \eta_1 ) t } \mathbb{ P }_{ \mu } \Big[ | H_{t+n-1}^p - H_{t+n}^p | \Big]\\
-    & \leq \frac{ C_3 }{ \mathbb{P}_{ \mu }( D^c ) } |\theta| \sum_{p\in\mathcal{N}}| a_p | e^{(\alpha-|p|b)t} e^{ - \frac{ \alpha } { 1 + \beta } t } e^{ - ( \eta_0 - 3 \eta_1 ) t } \| H_{ t + n - 1 }^p - H_{ t + n}^p \|_{ \mathbb{ P }_{ \mu }; 1 + \gamma} \\
-    & \leq C_4 | \theta | \sum_{ p \in \mathcal{N} } | a_p | e^{ ( \alpha - |p| b ) t} e^{ - \frac{ \alpha } { 1 + \beta } t } e^{ - ( \eta_0 - 3 \eta_1 )t  } e^{ - \frac{ 1 } { 1 + \gamma } ( \alpha \gamma - | p |(1+\gamma)b)(t+n-1)}\\
-    & = C_4 | \theta | \sum_{ p \in \mathcal{ N } } | a_p | \exp \Big \{ \Big( \frac { \alpha } { 1 + \gamma } - \frac{ \alpha } { 1 + \beta } - ( \eta_0 - 3 \eta_1 ) \Big) t \Big \} \cdot e^{ - \frac { 1 } { 1 + \gamma }( \alpha \gamma - | p | ( 1 + \gamma ) b ) ( n - 1 ) }.
-  \end{align}
-  \eqref{thm12211} now follows  since $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}<\eta_0-3\eta_1$ and $\alpha\gamma>Kb(1+\gamma)\geq |p|b(1+\gamma)$.
-
-  Combining \eqref{ineq: used next 3} with Steps 1-2, we get the result immediately. Notice that $\delta$ is independent of $m$ and $t$.
-\end{proof}
-\begin{lem}
-  \label{lem: lemma05}
-  For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist  $C,\delta_1,\delta_2>0$ such that
-  \begin{align}
-    \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\Big]\Big|
-    \leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 m}),
-    \quad m\in \mathbb{N}, t\geq 0.
-  \end{align}
-\end{lem}
-\begin{proof}
-  Fix $\theta \in \mathbb R$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\epsilon \in (0,\alpha)$ and $\gamma \in (0,\beta)$ with $\alpha \gamma > Kb(1+\gamma)$.
-  Recall that $A_t(\epsilon):=\{\|X_t\|> e^{(\alpha-\epsilon) t}\}$.
-  According to Proposition \ref{lem: control of XT}, there exist $C_1,\delta>0$ such that for all $t\geq 0$ and $m\in \mathbb N$,
-  \begin{align}
-    \label{ineq: control of gamma_t on dc}
-    \Big| \widetilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]
-    \leq 2 \widetilde{P}_{\mu}(A_t(\epsilon)^c)
-    \leq C_1 e^{-\delta t}.
-  \end{align}
-  According to Lemma \ref{lem: control of wt}, there exist $C_2,C_3>0$ such that for all $m\in \mathbb{N}, t\geq$,
-  \begin{align}
-  \label{ineq: control of gamma_t on d}
-    & \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty} \widetilde{ \gamma }_{ t, n}) - 1 \big) \mathbf{1}_{ A_t( \epsilon ) } \Big] \Big| \\
-    & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{n=m}^{\infty}\sum_{p\in \mathcal{N}}|a_p|\mathbb{P}_{\mu}\Big[\frac{|H_{t+n-1}^p-H_{t+n}^p|}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}\mathbf{1}_{A_t(\epsilon)}\Big]\\
-    & \leq  \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}\\
-    & \leq C_2|\theta|\sum_{p\in \mathcal{N} } |a_p| e^{ ( \alpha - |p| b ) t} e^{- \frac{ \alpha - \epsilon } { 1 + \beta } t } \sum_{ n = m}^{ \infty } e^{ - \frac{ 1 }{ 1 +\ gamma} ( \alpha \gamma - | p | ( 1 + \gamma ) b ) ( t + n - 1 ) } \\
-    & \leq C_3 | \theta | \exp \Big\{ \Big( \frac { \alpha } { 1 + \gamma } - \frac { \alpha } { 1 + \beta } + \frac{ \epsilon } { 1 + \beta } \Big) t \Big\}
-    e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m}.
-  \end{align}
-  Combining \eqref{ineq: control of gamma_t on dc} and \eqref{ineq: control of gamma_t on d}, we complete the proof.
-\end{proof}
-Now we are ready to prove Theorem \ref{thm: large clt}.
-
-\begin{proof}[Proof of Theorem \ref{thm: large clt}]
-  Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta \in \mathbb R$.
-  Let $\delta_0$ be the constant $\delta$ in Lemma \ref{lem: lemma04}.
-  Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$.
-  First note that for $t\ge 0$,
-  \begin{align}\label{decompose}
-    \text{LHS of \eqref{thm: large rate}}
-    =\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\widetilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\widetilde{\gamma}_{t,n}.
-  \end{align}
-  According to Lemma \ref{lem: independency for large rate}, there exist $C_1,\delta_1>0$ such that for all $t\geq 0$,
-  \begin{align}
-    \label{ineq: last1}
-    \Big| \widetilde{ \mathbb{ P } }_{ \mu } \Big[ \exp( i \theta \sum_{ n = 1 }^m \gamma_{ t, n} ) - \exp( \sum_{ n = 1 }^m \bar{ m }_n [ \theta g ] ) \Big]
-    \Big|\leq C_1 e^{-\delta_1 t}.
-  \end{align}
-  According to Lemma \ref{lem: lemma04}, there exists $C_2>0$ such that for all $t\geq 0$,
-  \begin{align}
-    \label{ineq: last2}
-    \Big|\widetilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \widetilde{\gamma}_{t,n}}]-\widetilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C_2  e^{-\frac{\delta_0}{2} t}.
-  \end{align}
-  According to Lemma \ref{lem: lemma05}, there exist $C_3,\delta_2,\delta_3>0$ such that for all $t\geq 0$,
-  \begin{align}
-    \label{ineq: last3}
-    \Big|\widetilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\widetilde{\gamma}_{t,n})-1\Big]\Big|\leq C_3(e^{-\delta_2 t}+e^{\delta_2 t}e^{-\delta_3 e^{\frac{\delta_0}{2}t}}).
-  \end{align}
-  Also note that $\sum_{n=1}^\infty\bar{m}_n[\theta g]=\bar{m}[\theta g]$, see \eqref{sum-bar-m}.
-
-  Combining \eqref{decompose},\eqref{ineq: last1}, \eqref{ineq: last2} and \eqref{ineq: last3}, and letting $t\to\infty$, we get the desired result of Theorem \ref{thm: large clt}.
+\[
+  K_{t,k}
+  := \Big| \frac {H_t^{1- \tilde \beta} - H_{t+k}^{1 - \tilde \beta}} {H_t^{1 - \tilde \beta} H_{t+k}^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t,k}}.
+\]
+Similar to the substep 2.2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that for all $k\in \mathbb Z_+$ and $t\geq 0$, almost surely $K_{t,k} \leq C_{2.2}'' e^{- (\eta - 3\eta')t}$.
+From this and Lemma \ref{lem: control of wt} we know that there exists $C'''_{2.2}$ for each $k\in \mathbb Z_+$ and $t\geq 0$,
+\begin{align}
+  & \widetilde{\mathbb P}_\mu[|Y_{t,k}|; \mathcal D_{t,k}]
+  \leq \mathbb P_\mu(D)^{-1}\mathbb P_\mu[ |Y_{t,k}| ;\mathcal D_{t,k} ]
+  \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} \langle f,\phi_p\rangle_\varphi  e^{(\alpha \tilde \beta  -|p|b)t} \mathbb P_\mu[| H_{t+k}^p-H_{t+k+1}^p |]
+  \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} \langle f,\phi_p\rangle_\varphi  e^{(\alpha \tilde \beta  -|p|b)t} \| H_{t+k}^p-H_{t+k+1}^p \|_{\mathbb P_\mu; 1+\gamma}
+  \\&\leq  \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal N} \langle f,\phi_p\rangle_\varphi  e^{(\alpha \tilde \beta  -|p|b)t} e^{-(\alpha \tilde \gamma - |p|b)(t+k)} \\
+  &  \leq  C_{2.2}''' e^{- (\eta - 3\eta') t} e^{(\alpha \tilde \beta - \alpha \tilde \gamma)t}, 
+\end{align} 
+as desired in this substep.
+
+\emph{Step 3.} We show that $I^f_2(t) \xrightarrow[t\to \infty]{d} 0$. 
+In order to do this, chose an $\epsilon \in (0,\alpha)$ and a $\gamma \in (0,\beta)$ close enough to $\beta$ such that for each $p\in \mathcal N$, it holds that $\alpha \tilde \gamma > |p|b$. 
+Define $\mathcal E_t:= \{\|X_t\| > e^{(\alpha - \epsilon)t}\}$.
+According to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3 > 0$ such that for each $t\geq 0$, $|\widetilde {\mathbb {P}}_\mu[e^{i I_2^f(t)} - 1; \mathcal E_t^c]|\leq 2\widetilde {\mathbb {P}}_\mu(\mathcal E_t^c) \leq C_3 e^{- \delta_3 t}$.
+On the other hand, according to Lemma \ref{lem: control of wt}, we know that there exist $C_3',C_3''>0$ and $\delta_3'>0$ such that
+\begin{align}
+	& |\widetilde {\mathbb {P}}_\mu[e^{i I_{2}^{f}(t)} - 1; \mathcal {E}_t]|
+   \leq  \widetilde {\mathbb {P}}_\mu[ | I_{2}^{f}(t)|; \mathcal {E}_t]
+   \leq \sum_{k = \lceil t^2\rceil}^\infty \widetilde {\mathbb {P}}_\mu[ |\widetilde {\Upsilon}_{t,k}|; \mathcal {E}_t]
+  \\ & \leq \mathbb P_\mu(D^c)^{-1} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\mathbb {P}_\mu\Big[\frac{ |H_{t+k}^p - H_{t+k+1}^p|}{\|X_t\|^{1- \tilde \beta}}; \mathcal E_t\Big]
+  \\ & \leq \mathbb P_\mu(D^c)^{-1} e^{(\alpha - \epsilon) (\tilde \beta - 1) t} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\|H_{t+k}^p - H_{t+k+1}^p\|_{\mathbb P_\mu; 1+\gamma}
+  \\ & \leq C_3' e^{(\alpha - \epsilon) (\tilde \beta - 1) t} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t} e^{- (\alpha \tilde \gamma - |p|b)(t+k)}
+  \\ & = C_3'' e^{ \alpha (\tilde \beta - \tilde \gamma) t } e^{ \epsilon (1 - \tilde \beta) t}e^{- \delta'_3 t^2}.
+\end{align}
+To sum up we have that $\widetilde {\mathbb P}_\mu[e^{iI_2^f(t)}] \xrightarrow[t\to \infty]{} 1$, which combined with the fact that $I_2^f(t)$ is linear in $f$, completes this step.
+
+\emph{Final step.} Combining Steps 1--3, we complete the proof of \ref{thm:M}.\eqref{thm:M:3}.
 \end{proof}
@@
   \label{eq: domination of psi(v)}
-  & \Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
+  & \Pi_x\Big[\int_0^t |\psi \big(\xi_s,-U_{t-s}f\big)|ds\Big]
   \leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big] \\ 
@@
   A. Iksanov, K. Kolesko, and M. Meiners, 
-  \emph{Stable-like fluctuations of {B}iggins' martingales}, 
+  \emph{Stable-like fluctuations of {B}gins' martingales}, 
   Stochastic Process. Appl. (2018).

### 2019-08-29 supCLT.tex
change supCLT.tex

@@
   Zhenyao Sun \\
-  % School of Mathematical Sciences \\ 
   School of Mathematics and Statistics\\
-  % Peking University \\ 
   Wuhan University \\
-  % Beijing, P. R. China, 100871}
   Hubei, P. R. China, 100871}
-% \email{zhenyao.sun@pku.edu.cn}
 \email{zhenyao.sun@gmail.com}
@@
 where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)~\pi(dy)< \infty$.
-% $\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
 $\psi$ is referred to as the branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
 Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-% For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
 For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)=\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
@@
 \end{align}
-% where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
 where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
@@
 
-% The strong law of large numbers for the super-OU process $X$ can be stated as follows:
 The strong law of large numbers for the super-OU process $X$ introduced at the beginning can be stated as follows:
@@
 
-% In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above.
 In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
-% Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
 Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-% We want to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
 And the general goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
-% DELETED
-% It turns out that the statements of the CLT's are different in three regimes depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: 
-% the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; 
-% the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; 
-% and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. 
-% Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
-% END DELETED
 Note that, in the setting of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
 
-% There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
 There are many papers studying CLTs for branching processes, branching diffusions and superprocesses under the second moment condition.
 See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-% Some spatial central limit theorems for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
 Some spatial CLTs for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
@@
 
-% *** Main results
 \subsection{Main results}
@@
 Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-% For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
 For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial/\partial x_k^{p_k})$.
@@
   H_p(x)
-  % :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) 
   :=(-1)^{|p|}\exp(|x|^2) \partial_p \exp(-|x|^2)
@@
 % **** Martingale limits
-% MOVED from below
   Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
@@
   Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-% END MOVED
-
-% **** LLNs
-% ADDED
+
 We first present a law of large numbers for our model which extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
-% END ADDED
 Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
@@
   \mathcal{P}
-  % :=\big \{f\in \mathscr B(\mathbb R^d, \mathbb R):\exists~ C>0, n \in \mathbb Z_+, {\rm such  \, \, that \, } \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
   :=\big \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists~ C>0, n \in \mathbb Z_+, {\rm such  \, \, that \, } \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
@@
 It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-% MOVED FROM BELOW
 \begin{thm}
@@
 See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
-% DELETED
-%\begin{rem}
-%  For general $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
-%\end{rem}
-% END DELETED
-% END MOVED FROM BELOW
 
 % **** Stable CLT
-% In this paper, we are mainly interested in the asymptotic behavior of $\langle f, X_t\rangle$ for non-trivial $f\in \mathcal P$.
 For the rest of this subsection, we focus on the central limit theorems of $\langle f, X_t\rangle$ for $f\in \mathcal P\setminus \{0\}$.
-% ADDED
 Write $\tilde u = \frac{u}{ 1+ u}$ for each $u \neq -1$.
-% END ADDED
-% The asymptotic behavior varies with the following three regimes:
 It turns out that the fluctuation behaviors vary with the following three cases:
-% (1) the small branching rate regime where $\alpha\beta<\kappa_fb(1+\beta)$; 
-% (2) the critical branching rate regime where $\alpha\beta=\kappa_fb(1+\beta)$; and
-% (3) the large branching rate regime where $\alpha\beta>\kappa_fb(1+\beta)$.
 \begin{enumerate}
@@
 \end{enumerate}
-% ADDED
 Here, the small (rspt.
@@
 relatively large) and the critical branching means that the branching rate $\alpha$ is at a balanced value.
-% END ADDED
-% ADDED
 To present our result we need to define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
@@
       := \begin{cases}
-        \lim_{t\to \infty} m_t[f], & f \in \mathcal C_s \oplus \mathcal C_l \setminus \{0\}\\
-        \lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_s \oplus \mathcal C_l
+        \lim_{t\to \infty} m_t[f], &
+    %YX f \in \mathcal C_s \oplus \mathcal C_l \setminus \{0\}\\
+        f \in \mathcal C_s \oplus \mathcal C_l, \\
+        \lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_s \oplus \mathcal C_l,
         \end{cases}
@@
 \end{thm}
-% END ADDED
-
-% **** (Martingale limits)
-% DELETED
-% \subsubsection{Large branching rate regime}
-% END DELETED
-% MOVED ABOVE
-\begin{comment}
-Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
-For each $p\in \mathbb{Z}_+^d$, define
-\[
-  H_t^p
-  := e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,
-  \quad t\geq 0.
-\]
-If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lem:M:L:ML} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-\end{comment}
-% END MOVED ABOVE
-
-% **** (Theorem of LLN)
-% MOVED ABOVE
-\begin{comment}
-\begin{thm}
-  \label{thm: law of large number}
-  If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
-  \[
-    e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle
-    \xrightarrow[t\to \infty]{}\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p
-    \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).
-  \]
-  Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
-\end{thm}
-
-\begin{rem}
-  If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
-  Hence, Theorem \ref{thm: law of large number} says that for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
-  \[
-    e^{-\alpha t}\langle f, X_t\rangle
-    \rightarrow \langle f, \varphi\rangle H_{\infty}
-    \quad \mbox{in } L^{1+\gamma}(\mathbb{P}_{\mu}).
-  \]
-  Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have a.\/s.\ convergence.
-  However, to get  a.\/s.\ convergence for bounded non-negative 
-  Lebesgue-a.\/e.\/\ continuous functions $f$, we do not need $f$ to be twice differentiable.
-See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
-\end{rem}
-
-\begin{rem}
-  For general $f\in \mathcal{P}$ with $\alpha\beta>\kappa_fb(1+\beta)$, Theorem \ref{thm: law of large number} extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
-\end{rem}
-\end{comment}
-% END MOVED ABOVE
-
-% **** (fluctuation result of large numbers)
-% DELETED
-\begin{comment}
-The fluctuation result associated to the law of large numbers in this case is given in Theorem \ref{thm: large clt} below.
-Define
-\begin{align}
-  \label{eq: def of N}
-  \mathcal{N}
-  :=\{p\in \mathbb{Z}_+^d: \alpha\beta>|p|(1+\beta)b\},
-  \quad K : = \sup\{|p|: p \in \mathcal N\}
-\end{align}
-and
-\begin{equation}
-  \label{eq: def of Cl}
-  \mathcal{C}_l
-  :=\Big\{f\in \mathcal P: f(x)=\sum_{p\in\mathcal{N}}\langle f, \phi_p\rangle_{\varphi}\phi_p(x)\Big\}.
-\end{equation}
-For each $t\ge 0$, we define an operator $I_t$ on $\mathcal{C}_l$ by
-\begin{align}
-  \label{definition of Itf}
-  I_t f(x)
-  := \sum_{p\in \mathcal{N}}\langle f, \phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x)
-  , \quad x\in \mathbb{R}^d, f\in \mathcal C_l.
-\end{align}
-It is easy to see that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$.
-Define
-\begin{align}
-  \label{bar-m}
-  \bar{m}[f]
-  :=\eta \int_{0}^{\infty} e^{\alpha s}~ds \int_{\mathbb R^d} \big(iI_sf(x)\big)^{1+\beta}\varphi(x)~dx,
-  \quad f\in \mathcal C_l.
-\end{align}
-We will show in Lemma \ref{lem: def of all m} that $\bar{m}[f]$ is well-defined for each $f\in \mathcal C_l$; 
-and in Lemma \ref{prop:PL:S} that, when $f\in \mathcal C_l$ is non-trivial, $\theta \mapsto \exp( \bar m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\begin{thm}
-  \label{thm: large clt}
-  For non-trivial $f\in\mathcal{C}_l$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that,
-  \begin{align}
-    \label{thm: large rate}
-    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}
-    \xrightarrow[t\to \infty]{d}\bar{\zeta},
-  \end{align}
-  where $\bar{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(\bar{m}[\theta f])$.
-\end{thm}
-\end{comment}
-% END DELETED
-% **** (Critical branching rate regime)
-% DELETED
-\begin{comment}
-\subsubsection{Critical branching rate regime}
-For each $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
-\begin{equation}
-  \label{tilde-m}
-  \widetilde{m}[f]
-  := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
-\end{equation}
-According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
-We will prove in Lemma \ref{prop:PL:S} that $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\begin{thm}
-  \label{thm: critical clt}
-  If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-  \[
-    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
-    \xrightarrow[t\to \infty]{d} \widetilde{\zeta},
-  \]
-  where $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(\widetilde{m}[\theta f])$.
-\end{thm}
-\end{comment}
-% END DELETED
-% **** (Small branching rate regime)
-% DELETED
-\begin{comment}
-\subsubsection{Small branching rate regime}
-\label{msmallcase}
-If $f\in \mathcal{P}$ is non-trivial and satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, we define
-\begin{equation}
-  m[f]
-  := \eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
-\end{equation}
-According to Lemma \ref{lem: def of all m} below, $m[f]$ is well-defined.
-We will prove  in Lemma \ref{prop:PL:S} that $\theta \mapsto \exp( m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
-\begin{thm}
-  \label{thm: small clt}
-  If $f\in\mathcal{P}$ is non-trivial and satisfies $\alpha\beta<\kappa_f b(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
-  \[
-    \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow[t\rightarrow \infty]{d} \zeta,
-  \]
-  where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(m[\theta f])$.
-\end{thm}
-\end{comment}
-% END DELETED
-% ** Some intuitive explanation
-\subsection{Some intuitive explanation}
-{\bf (Sun: I didn't revise this subsection yet.)}
+
+%\subsection{Some intuitive explanation}
+\subsection{An outline of the methodology}
 Here we give some intuitive explanation of the central limit theorems above.
@@
 
-Suppose $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions $\theta\mapsto \exp( m_k[\theta f])$, where $m_k[f]$ is given in Lemma \ref{lem: def of all m} below.
 Recall $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
-Lemma \ref{lem:PR:LC} and Proposition \ref{cor:MI} below imply that if $\alpha\beta \leq \kappa_f b(1+\beta) $ then
+Theorem \ref{lem:PR:LC}, Corollary \ref{cor:MI} and \eqref{eq:gammafunction11} below imply that if $\alpha \tilde \beta \leq \kappa_f b$ then
 \[
   \bigg(\frac{\mathcal I^{t-k}_{t-k-1} \langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \bigg)_{k=1}^n
-  \xrightarrow [t\to \infty]{d} (\zeta_k)_{k=1}^n.
-\]
-So if $f$ is in the small branching rate regime, i.e., $\alpha \beta < \kappa_f b(1+\beta)$, we have roughly that
+  \xrightarrow [t\to \infty]{d} (\zeta_k)_{k=1}^n,
+\]
+where $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions $\theta\mapsto \exp( \langle Z_1T_k\tilde f,\varphi  \rangle)$ and $\tilde f:=e^{\alpha(\tilde \beta -1)}f$.
+So if $f\in \mathcal C_s$, i.e., $\alpha \tilde \beta < \kappa_f b$, we have roughly that
 \[
@@
 \]
-where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(m[\theta f])$, with $m[\theta f]$ given in Lemma \ref{lem: def of all m} below.
+where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(m[\theta f])$, with $m[\theta f]$ given by \ref{eq:I:R:3}.
 In the explanation above, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined, and
@@
   m[f]
-  = \sum_{k=0}^\infty m_k[ f].
-\end{align}
-These facts will be made clear in Subsection \ref{sec: stable distributions} below.
-
-If $f$ is in the critical branching rate regime, i.e., $\alpha \beta = \kappa_f b(1+\beta)$, then the right hand side of \eqref{eq: equatlity for mf for small rate} may not converge.
-Instead, see Lemma \ref{lem: def of all m} below, there is another quantity $\widetilde m[f]$ satisfying that
-\[
-  \widetilde{m}[f] 
-  = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
+  = \sum_{k=0}^\infty \langle Z_1 T_k \tilde f,\varphi \rangle,\quad f\in\mathcal C_s.
+\end{align}
+These facts will be made clear in Lemma \ref{lem:m} and formula \eqref{eq:PM:CLTS:2}.
+
+If $f\in \mathcal C_c$, i.e., $\alpha \tilde \beta = \kappa_f b$,
+%YX then the right hand side of \eqref{eq: equatlity for mf for small rate} may not converge.
+%YX Instead, see \eqref{CLT:C:eq:m} below, there is another quantity $m[f]$ satisfying that
+then
+\[
+  m[f]
+  = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}\langle Z_1 T_k \tilde f,\varphi \rangle,\quad f\in \mathcal C_c.
 \]
@@
   \overset{d}{\approx} \frac{1}{t^{\frac{1}{1+\beta}}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k
-  \xrightarrow[t\to \infty]{d} \widetilde \zeta
-\]
-where $\widetilde \zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(\widetilde m[\theta f])$.
+  \xrightarrow[t\to \infty]{d} \zeta,
+\]
+%YX where $\zeta$ is another $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp( m[\theta f])$.
+where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp( m[\theta f])$.
 
 For $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
-Taking $f = \phi_p$ with $\alpha \beta > |p|b(1+\beta)$ as an example, we do the following decomposition:
+%Taking $f = \phi_p$ with $\alpha \beta > |p|b(1+\beta)$ as an example, we do the following decomposition:
+Taking $f = \phi_p$ with $\alpha \tilde \beta > |p|b$ as an example, we do the following decomposition:
 \[
@@
 \]
-The fluctuation behaviors of each of the terms $H_{t+n-1}^p - H_{t+n}^p$ and their asymptotic independence will be established in Lemma \ref{large-central} and \ref{lem: independency for large rate} below, respectively.
+The fluctuation behaviors of each of the terms $H_{t+n-1}^p - H_{t+n}^p$ and their asymptotic independence will also be established in Theorem \ref{lem:PR:LC} and Corollary \ref{cor:MI} below.
 These lemmas will eventually lead us to the fluctuation result in the large branching rate regime.
 
-For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$, where 
-\[
-  f_l
-  = \sum_{p\in \mathcal{N}}a_p\phi_p(x)\in \mathcal{C}_l
-  , \quad x\in \mathbb{R}^d,
-\]
-and $f_c=\langle f, \phi_p\rangle_{\varphi} \phi_p(x)$  with $p=\frac{\alpha\beta}{b(1+\beta)}$.
-Note that there may be no $p$ such that $p=\frac{\alpha\beta}{b(1+\beta)}$. In this case $f_c=0$.
+%YX For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$,
+For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$ with $f_l\in\mathcal C_l$, $f_c\in\mathcal C_c$ and $f_s\in\mathcal C_c$.
+Note that there may be no $p$ such that $|p|=\frac{\alpha \tilde\beta}{b}$. In this case $f_c=0$.
 Our main results above give central limit type results for $\langle f_l, X_t\rangle$, $\langle f_c, X_t\rangle$ and $\langle f_s, X_t\rangle$, respectively.
@@
 
-% Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z + \rho z^2+\eta z^{1+\beta}$ plus a small perturbation
 Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z +\eta z^{1+\beta}$ plus a small perturbation
@@
 In Subsection \ref{sec: large rate lln}, we will give the proof of Theorem \ref{thm: law of large number}.
-In Subsection \ref{sec:critical}, we will give the proof of Theorem \ref{thm: critical clt}.
-In Subsection \ref{sec: small rate}, we will give the proof of Theorem \ref{thm: small clt}.
-In Subsection \ref{sec: large rate clt}, we will give the proof of Theorem \ref{thm: large clt}.
+%YX In Subsection \ref{sec:critical}, we will give the proof of Theorem \ref{thm:M}.
+In Subsections \ref{sec:critical}--\ref{sec: large rate clt}, we will give the proof of Theorem \ref{thm:M}.
 In the Appendix, we consider a general superprocess $(X_t)_{t\geq 0}$, and we prove there that the characteristic exponent of $\langle f,X_t\rangle$ satisfies a complex-valued non-linear integral equation.
@@
 
-% ** Preliminaries
 \section{Preliminaries}
-% *** Branching mechanism
 \subsection{Branching mechanism}
@@
   \label{lem: complex extension for psi1}
-	% The function $\psi_1$ on $\mathbb R_+$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
 	The function $\psi_1$ given by \eqref{eq: psi 1} can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
@@
     \psi_1(z)
-    % = \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big)
     = \rho z^2 + \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big)
@@
     |\psi_1(z)|
-    % & \leq \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
     & \leq \rho |z|^2 + \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
-    % & \leq  |z|^2 \int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
     & \leq  |z|^2 \Big(\rho + \int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|\Big) \\
@@
 
-% *** Definition of controller
 \subsection{Definition of controller}
@@
 Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
-
-% Modified
-% For any function $h: [0,\infty) \to [0,\infty)$, we say an operator $R: \mathcal P^+ \to \mathcal P^+$ is an \emph{$h$-controller} if
-% (1) $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and (2) $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ imply that $ R (\theta f)\leq h(\theta) Rf$.
-% For a subset $\mathcal D$ of $\mathcal P^*$ and an $h$-controller $R$, we say an operator $A : \mathcal D \to \mathcal P^*$ is \eminnershapeph{$h$-controlled by $R$ on $\mathcal D$} if $|Af| \leq R|f|$ for each $f\in \mathcal D$.
-% We say an operator $A: \mathcal D \to \mathcal P^*$ is \emph{$h$-controllable} if there exists an $h$-controller $R$ such that $A$ is $h$-controlled by $R$.
-% We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$ is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
 
@@
 uniformly controlled) by $R$ from $\mathcal D$ to $\mathcal I$.
-% End Modified
 
@@
 
-% Modified
-\begin{comment}
-\begin{lem}
-  \label{lem: property of controllable operators}
-  Suppose that $\Lambda$ is an index set and $(A_\lambda)_{\lambda\in \Lambda}$ is a
-  family of operators, from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$,
-  which is uniformly 
-  $h$-controlled by $R_A$ on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
-  Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators, from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$,
-  which is uniformly $g$-controlled by $R_B$ on $\mathcal D_0$ 
-  for some function $g: [0,\infty) \to [0,\infty)$. 
-  Suppose that $(C_\lambda)_{\lambda\in \Lambda} $ is a family of operators, from $\mathcal D\subset \mathcal P^*$ to $ \mathcal P^*$,
-  which is uniformly $k$-controlled by $R_C$ on $\mathcal D_0$ for a given function $k:[0,\infty) \to [0, \infty)$.
-  Then 
-  \begin{itemize}
-  \item[(1)]
-    $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$;
-  \item[(2)]
-    $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$ and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$;
-  \item[(3)] 
-    For any $a>0$, $(C^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(k^a)$-controllable.
-  \item[(4)]
-    Suppose further that $(\Lambda, \mathscr F)$ is a measurable space and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
-    For any probability measure $\nu$ on $(\Lambda, \mathscr F)$,  we write
-    \[
-      A_\nu f(x)
-      := \int_{\Lambda} A_\lambda f (x)~\nu(d\lambda),
-      \quad f\in \mathcal D, x\in \mathbb R^d.
-    \]
-    Then  $\{A_\nu: \nu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $h$-controllable on $\mathcal D$.
-  \end{itemize}
-\end{lem}
-\end{comment}
 The following lemma is easy to verify.
@@
   \item
-    If $\mathcal I_0 \subset \mathcal D_1$, then $\{A_1A_0: A_i \in \mathscr O_i, i = 0,1\}$ is uniformly controlled by the $(h_1 \circ h_0)$-controller $R_1R_0$ from $\mathcal D_0$ to $\mathcal I_1$;
+    If $\mathcal I_0 \subset \mathcal D_1$, then $\{A_1A_0: A_i \in \mathscr O_i, i = 0,1\}$ is uniformly controlled by the $(h_1 \circ h_0)$-controller $R_1R_0$ from $\mathcal D_0$ to $\mathcal I_1$.
   \item
@@
 \end{lem}
-% END MODIFIED
-
-% DELETED
-\begin{comment}
-\begin{proof}
-  (1). 
-  If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, then $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
-  If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_AR_Bf \leq R_A R_B g$.
-  If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_AR_B(\theta f) \leq R_A(g(\theta) R_Bf) \leq (h\circ g)(\theta) R_A R_B f $.
-  % Therefore 
-  Combining these, we get that
-  $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$.
-
-  (2). 
-  If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, then $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
-  If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_A\times R_Bf \leq R_A\times R_B g$.
-  If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_A\times R_B (\theta f) \leq h(\theta) g(\theta) (R_A \times R_B) f $.
-  Combining these, we get that $(A_\lambda \times B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \times g)$-controllable on $\mathcal D$.
-
-  If $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, then $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
-  If $f,g \in \mathcal P^+$ with $f\leq g$, then $(R_A + R_B)f \leq (R_A + R_B) g$.
-  If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $(R_A + R_B) (\theta f) \leq h(\theta) R_Af + g(\theta) R_Bf \leq (h(\theta) \vee g(\theta)) (R_A+R_B)f $.
-  Combining these, we get that $(A_\lambda + B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \vee g)$-controllable on $\mathcal D$.
-
-  (3). 
-  If $\lambda \in \Lambda$, $f\in \mathcal D$, then $|C_\lambda^{\times a} f| = |C_\lambda f|^a  \leq R_C^{\times a} |f|$.
-  If $f,g \in \mathcal P^+$ with $f\leq g$, then $R_C^{\times a}f \leq R_C^{\times a} g$.
-  If $f \in \mathcal P^+$ and $\theta \in [0,\infty)$, then $R_C^{\times a}(\theta f) \leq (k(\theta) R_C f)^a = k(\theta)^a R_C^{\times a}f$.
-  Combining these, we get that $(C_\lambda^{\times a})_{\lambda \in \Lambda}$ is uniformly $(k^a)$-controllable on $\mathcal D$.
-
-  (4).     
-  For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
-  \[
-    | A_{\nu}f(x) | 
-    \leq \int_{\Lambda} | A_{\lambda}f(x) | \nu(d\lambda) 
-    \leq \int_{\Lambda}R|f|(x)\nu(d\lambda) \leq R|f|(x). 
-    \qedhere
-  \]
-\end{proof}
-\end{comment}
-% END DELETED
-% *** h-controller for super-OU processes
+
 % \subsection{h-controller for super-OU processes}
@@
 Define $\psi_0(z) = \psi(z) + \alpha z$ for each $z\in \mathbb{R}_+$.
-% Using an argument similar to the proof of Lemma \ref{lem: complex extension for psi1}, $\psi, \psi_0$ and $\psi_1$ can be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are holomorphic on $\mathbb C^0_+$.
 According to Lemma \ref{lem: complex extension for psi1}, $\psi, \psi_1$ and $\psi_0$ can all be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are also holomorphic on $\mathbb C^0_+$.
@@
 be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
-% new
 (See the paragraph after Lemma \ref{lem: Lip of power function}.)
-% end new
 It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
@@
   \item[(3)]
-    % $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
     $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
   \item[(4)]
-    % $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P$.
     $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
   \item[(5)]
-    % $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable on $\mathcal P$.
     $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
   \item[(6)]
-    % For any $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
     For any $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
   \item[(7)]
-    % For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable on $\mathcal P$.
     For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
@@
   Combining this with \eqref{eq:chareq2} and
-  Lemma \ref{lem: property of controllable operators}.(4), we get the desired result.
+%YX Lemma \ref{lem: property of controllable operators}.(4), we get the desired result.
+Lemma \ref{lem: property of controllable operators}.(3), we get the desired result.
 
@@
   Therefore, for any $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-  % Combining  this  (1)--(2) above, 
   Combining  this with  (1)--(2) above,
@@
 
-  (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from (5)-- (6) above and Lemma \ref{lem: property of controllable operators}.(2).
+     (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from (5)-- (6) above and Lemma \ref{lem: property of controllable operators}.(3).
 \end{proof}
-% *** (Stable distributions)
-% DELETED
-\begin{comment}
-\subsection{Stable distributions}
-\label{sec: stable distributions}
-In this subsection, we will show that the $(1+\beta)$-stable random variables in Theorems \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
-
-Recall that $(P^\alpha_t)_{t\geq 0}$ is defined in \eqref{eq: meansemigroup}, $\mathcal P$ is defined in \eqref{eq: polynomial growth function}, $\mathcal N$ is given in \eqref{eq: def of N} and $\mathcal C_l$ is defined in \eqref{eq: def of Cl}.
-\begin{lem}
-\label{lem: def of all m}
-\begin{enumerate}
-\item
-  If $f\in\mathcal{P}$, then the following integrals are well defined:
-  \[
-    m_t[f]
-    := \eta \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} (-iP_{s}^\alpha f(x))^{1+\beta} \varphi(x)~dx,
-    \quad t\geq 0.
-  \]
-	Furthermore, there exists  $C>0$ such that
-  \begin{equation}
-    \label{domi-m}
-    |m_t[f]|
-    \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
-    \quad t\geq 0.
-  \end{equation}
-\item
-  If $f\in\mathcal C_l$, then the following integrals are well defined:
-  \[
-    \bar{m}_t[f]
-    := \eta \int_{t-1}^{t} e^{\alpha s}~ds \int_{\mathbb R^d}\big(iI_sf(x)\big)^{1+\beta} \varphi(x)~dx, \quad t\geq 1.
-  \]
-  Furthermore, there exists  $C>0$ such that
-  \begin{equation}
-    |\bar{m}_t[f]| 
-    \leq C e^{-(\alpha\beta-K(1+\beta)b)t}, \quad t\geq 1,
-  \end{equation}
-  where $K$ is defined in \eqref{eq: def of N}.
-\item
-  If $f \in \mathcal C_l$, then the following integral is well defined:
-  \[
-    \bar{m}[f]
-    :=\eta \int_{0}^{\infty} e^{\alpha s}~ds \int_{\mathbb R^d} \big( iI_sf(x) \big)^{ 1 + \beta } \varphi( x ) ~dx.
-  \]
-  Furthermore, we have
-  \begin{equation}
-    \label{sum-bar-m}
-    \bar{m}[f]
-    = \sum_{n=1}^{\infty} \bar{m}_n[f].
-  \end{equation}
-\item
-  If $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$, then the following integral is well defined:
-  \[
-    \widetilde{m}[f]
-    := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
-  \]
-	Furthermore, we have
-  \begin{equation}
-    \label{para: critical case}
-    \widetilde{m}[f] 
-    = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f].
-  \end{equation}
-\item
-  If $f\in \mathcal{P}$ satisfies $\alpha\beta<\kappa_fb(1+\beta)$, then the following integral is well defined:
-  \[
-    m[f]
-    := \eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-iP_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
-  \]
-	Furthermore, we have
-  \begin{equation}
-    \label{sum-m}
-    m[f]
-    = \sum_{k=0}^\infty m_k[f].
-  \end{equation}
-\end{enumerate}
-\end{lem}
-\begin{proof}
-  (1) is  \cite[Lemma 2.7]{MarksMilos2018CLT}; (3) is obvious from (2) noticing that $\alpha\beta>K(1+\beta)b$; (4) is \cite[Lemma 4.2]{MarksMilos2018CLT}; and (5) is obvious from (1).
-  So we only need to show (2). 
-  We first claim that there exists $h\in \mathcal{P}$ such that
-  \begin{align}
-    \label{ineq: control of Itg}
-    |I_tf(x)|
-    \leq e^{-(\alpha-Kb)t}h(x),
-    \quad t\geq 0, x\in \mathbb{R}^d.
-  \end{align}
-  In fact, if we put $h:= \sum_{p\in \mathcal N} |\langle f,\phi_p\rangle_{\varphi}\phi_p|$, then
-\begin{equation}
-  \label{eq: supper for Itf}
-  |I_tf(x)|
-  =\Big|\sum_{p\in\mathcal{N}} \langle f,\phi_p\rangle_{\varphi} e^{-(\alpha-|p|b)t}\phi_p(x)\Big|
-  \leq e^{-(\alpha-Kb)t}h(x),
-  \quad t\geq 0,x\in \mathbb{R}^d.
-\end{equation}
-Therefore there exists  $C>0$ such that
-\begin{align}
-  & |\bar{m}_t[f]|
-    \leq \eta \int_{t-1}^{t} e^{\alpha s}~ds \int_{\mathbb R^d} | I_sf(x)|^{1+\beta}\varphi(x)~dx \\
-  & \leq \eta \int_{t-1}^{t} e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}~ds\int_{\mathbb R^d} h(x)^{1+\beta}\varphi(x)~dx \\
-  & \leq C e^{-(\alpha\beta-K(1+\beta)b)t}
-    , \quad t\geq 1.
-\end{align}
-\end{proof}
-The following proposition says that $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\bar m[f]$ and  $\widetilde m[f]$ are all related to $(1+\beta)$-stable distributions.
-\begin{prop}
-  \label{prop:PL:S}
-	For all $t\geq 0$ and non-trivial $f\in \mathcal P$,
-  \begin{enumerate}
-  \item
-    \label{item: stable 1}
-    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable;
-  \item
-    \label{item: stable 2}
-    $\theta \mapsto \exp(\bar{m}_t[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$;
-  \item
-    \label{item: stable 3}
-    $\theta \mapsto \exp(\bar m[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $f \in \mathcal C_l$;
-  \item
-    \label{item: stable 4}
-    $\theta \mapsto \exp(\widetilde m[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
-  \item
-    \label{item: stable 5}
-    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of an $\mathbb R$-valued $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
-  \end{enumerate}
-\end{prop}
-This proposition says that the $(1+\beta)$-stable random variables  in Theorems \ref{thm: large clt}, \ref{thm: critical clt} and \ref{thm: small clt} are all well defined.
-The proof of this proposition relies on the following lemma:
-\begin{lem}
-  \label{lem: charactreisticfunction}
-  Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with
-  $\int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty)$.
-  Then
-  \[
-    \theta 
-    \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},
-    \quad \theta \in \mathbb R^d
-  \]
-  is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
-\end{lem}
-\begin{proof}
-  It follows from disintegration that there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
-  \[
-    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) 
-    = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
-    f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
-  \]
-  We define another measure $\lambda_0$ on $S$ by
-  \[
-    \lambda_0(d\xi) 
-    := \frac1{\Gamma(-1-\beta)}\int_0^\infty t^{1+\beta}k(\xi,dt) \lambda (d\xi),
-  \]
-  where $\Gamma$ is the Gamma function.
-  Then $\lambda_0$ is a non-zero finite measure, since
-  \begin{align}
-    &\lambda_0(S) 
-      = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt) \\
-    & = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
-  \end{align}
-  Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
-  \[
-    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)
-    = \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
-  \]
-  Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\'evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is
-  \[
-    \hat \mu(\theta)
-    = \exp \Big \{ \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy) \Big \}
-    , \quad \theta \in \mathbb R.
-  \]
-  Finally, according to \eqref{eq: stable branching on C+}, we have
-  \begin{align}
-    & \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
-      = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}} \\
-    & = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt) \\
-    & = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
-      = \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt) \\
-    & = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
-      \qedhere
-  \end{align}
-\end{proof}
-\begin{proof}[Proof of Proposition \ref{prop:PL:S}]
-  \eqref{item: stable 1}.
-	Fix $t\geq 0$ and $f\in \mathcal P$.
-	Note that $m_t[\theta f]$ can be rewritten as
-  \[
-    m_t[\theta f]
-    = \eta \int_t^{t+1}e^{-\alpha s}~ds\int_{\mathbb R^d} \big(-i\theta (P_{s}^\alpha f)(x)\big)^{1+\beta} \varphi(x)~dx,
-    \quad \theta \in \mathbb R.
-  \]
-	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
-  \begin{equation}
-    \label{eq: what I want to proof}
-    \int_t^{t+1}e^{-\alpha s} ~ds\int_{\mathbb R^d} | P_{s}^\alpha f(x)|^{1+\beta} \varphi(x)~dx
-    \in (0, \infty).
-  \end{equation}
-	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4), we know that
-  \[
-    f 
-    \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f|^{1+\beta}~ds
-  \]
-  is a $\theta^{1+\beta}$-controllable operator on $\mathcal P$.
-  This implies that \[ x \mapsto \int_t^{t+1}e^{-\alpha s} |P_{s}^\alpha f(x)|^{1+\beta}~ds\] is an element of $\mathcal P$.
-	Therefore the integral on the left-hand side of \eqref{eq: what I want to proof} is finite.
-	Since $f$ is non-trivial, the integral on the left-hand side of \eqref{eq: what I want to proof} is positive.
-
-  The proofs of \eqref{item: stable 2}--\eqref{item: stable 5} are similar to that of \eqref{item: stable 1}. 
-  We omit the details here.
-\end{proof}
-
-Before we end this subsection, we  give  two more lemmas which will be used in the proofs of our main results in Section \ref{proofs of main results}.
-
-\begin{lem}{\cite[Lemma 2.8]{MarksMilos2018CLT}}\label{lem:P:R}
-  For each $f\in \mathcal{P}$, let
-  \begin{align}
-    g_k
-    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
-    \quad k \geq 0.
-  \end{align}
-  Then there exists $h\in \mathcal{P}$ such that $|P_sg_k|\leq e^{-bs}h$ for all $s, k \geq 0.$
-\end{lem}
-
-\begin{lem}
-  \label{control of gn} 
-  Suppose that $g\in \mathcal{C}_l$.
-  Put
-  \begin{align}
-    \bar{g}_t
-    :=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
-  \end{align}
-  Then there exists $h\in \mathcal{P}$ such that $|P_s\bar{g}_t| \leq e^{-bs}h$ for all $s, t\geq 0.$
-\end{lem}
-\begin{proof}
-  First we claim that there exists $h_1\in \mathcal P$ such that
-\begin{align}
-  \label{ineq: control of partial derivative of Itg}
-  \Big|\frac{\partial}{\partial x_i}I_tg(x)\Big| \leq e^{-(\alpha-Kb)t}h_1(x),
-  \quad  t\geq 0, x\in \mathbb R^d.
-\end{align}
-In fact, if we put $h_1(x)=\sum_{p\in \mathcal N}|\langle g, \phi_p\rangle_\varphi\frac{\partial \phi_p}{\partial x_i}(x)| \in \mathcal P$, then
-\begin{align}
-  \Big|\frac{\partial}{\partial x_i}I_tg(x)\Big| =
-  \Big|\sum_{p\in \mathcal N}\langle g, \phi_p\rangle_\varphi e^{-(\alpha-|p|b)t} \frac{\partial}{\partial x_i}\phi_p(x)\Big|
-  \leq e^{-(\alpha-Kb)t}h_1(x)
-  , \quad t\geq 0, x\in \mathbb R^d.
-\end{align}
-It is well known that
-\[
-  P_t f(x) = \int_{\mathbb R^d} f\big(x e^{-bt} + y \sqrt{1-e^{-2bt}}\big) \varphi(y) dy,
-  \quad t\geq 0, x\in \mathbb R^d, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
-\]
-It is clear that the above equality also holds for each $f\in \mathcal P$.
-From this, one can easily check that for each differential $f \in \mathcal P$ with $|\nabla  f| \in \mathcal P$, we have
-\[
-  \frac{\partial P_t^\alpha f(x)}{\partial x_i} = e^{-bt} P_t^\alpha\Big(\frac{\partial f}{\partial x_i}\Big)(x), \quad t\geq 0, x\in \mathbb R^d.
-\]
-Note that if $g \in \mathcal C_l$, then $g^{1+\beta}\in \mathcal P$ and $|\nabla (g^{1+\beta})| \in \mathcal P$.
-Therefore,
-\begin{align}
-  & \frac{\partial}{\partial x_i} P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}
-    = \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s} g)^{1+\beta}
-    = e^{-b(1-s)} P_{1-s}^\alpha \frac{\partial}{\partial x_i} (I_{t-s}g)^{1+\beta} \\
-  & =(1+\beta)e^{-b(1-s)} P_{1-s}^\alpha \Big( (I_{t-s}g)^\beta \times \frac{\partial}{\partial x_i} (I_{t-s}g) \Big),\quad s\in [0,1], t\geq 0.
-\end{align}
-Using \eqref{eq: supper for Itf}, \eqref{ineq: control of partial derivative of Itg} and the above, we have that there exist a bounded function $a$ on $[0,1]$ and an $h_2 \in \mathcal P$ such that
-\begin{equation}
-  \label{eq: key estimation for partial}
-  \Big| \frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| \leq a(s) e^{-(\alpha - Kb)(1+\beta)t}h_2(x),\quad s\in [0,1],t\geq 0, x\in \mathbb R^d.
-\end{equation}
-Therefore, for each compact subset $A \subset \mathbb R^d$, we have
-\[
-  \int_0^1 \sup_{x\in A} \Big|\frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| ds 
-  < \infty
-  , \quad t\geq 0.
-\]
-Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, we can get
-\[
-  \frac{\partial}{\partial x_i} Z_1(-I_tg)
-  = \eta i^{1+\beta}  \frac{\partial}{\partial x_i} \int_0^1 P_{1-s}^\alpha (I_{t-s}g)^{1+\beta} ds
-  = \eta i^{1+\beta}  \int_0^1  \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s}g)^{1+\beta} ds.
-\]
-Therefore, using \eqref{eq: key estimation for partial} and the above, there exists  $C> 0$ such that for all $t\geq 0$,
-\begin{align}
-  & \Big|\frac{\partial}{\partial x_i}\bar{g}_t(x)\Big|
-    = e^{(\alpha-Kb)(1+\beta)t}\Big|\frac{\partial}{\partial x_i}Z_1(-I_tg)\Big| \leq C h_2(x),
-    \quad x\in \mathbb R^d.
-\end{align}
-Therefore there exist $c,n>0$ such that
-\begin{align}
-  \label{ineq: control of sup gt}
-  | \nabla \bar g_t (z)|
-  \leq c(1+|z|)^n
-  , \quad t\geq 0, z\in \mathbb R^d.
-\end{align}
-Define
-\[
-  D(x,y)
-  := \{ax+by: a,b\in [0,1]\}
-  , \quad x, y \in \mathbb R^d.
-\]
-Then for all $x,y\in \mathbb R^d$, $D(x,y)$ is a convex set on $\mathbb R^d$.
-In particular, it contains the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$ for each $s\geq 0$.
-Also, note that $ | \sqrt { 1 - \theta } - 1 | \leq \theta $ for all $ \theta \in [ 0, 1 ] $, and that $ 1 + \theta + \lambda \leq ( 1 + \theta ) ( 1 + \lambda ) $ for all $ \theta, \lambda \geq 0$.
-Using the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we get that for all $s,t\geq 0, x\in \mathbb R^d$,
-\begin{align}
-  & |P_s\bar{g}_t(x)|
-    = \Big|\int_{\mathbb R^d} \big(\bar {g}_t(xe^{-bs}+y\sqrt{1-e^{-2bs}})-\bar {g}_t (y)\big) \varphi(y)~dy \Big| \\
-  & \leq \int_{\mathbb R^d} \sup_{z\in D(x,y)} |\nabla \bar g_t (z)|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy \\
-  & \leq e^{-bs}\int_{\mathbb R^d} c(1+|x|+|y|)^n (|x|+|y|) \varphi(y)~dy \\
-  & \leq ce^{-bs}(1+|x|)^n\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y)dy + \int_{\mathbb R^d}(1+|y|)^n|y|\varphi(y)dy\Big).
-  \qedhere
-\end{align}
-\end{proof}
-\end{comment}
-% END DELETED
-% ADDED
-% *** Stable distributions
+
 \subsection{Stable distributions}
@@
 % **** characteristic functions
-Recall that the operators $(T_t)_{t\geq 0}$ are given by \eqref{eq:I:R:1}, and functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
+%YX Recall that the operators $(T_t)_{t\geq 0}$ are given by \eqref{eq:I:R:1},
+Recall that the operators $(T_t)_{t\geq 0}$ are defined by \eqref{eq:I:R:1},
+ and functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
 \begin{lem}
@@
 \begin{proof}
-  \emph{Step 1.} We will show that for each $f \in \mathcal P$, there exists an $h \in \mathcal P$ such that
+  \emph{Step 1.} We will show that for each $f \in \mathcal P$,
+  %YX there exists an $h \in \mathcal P$ such that
+   there exists  $h \in \mathcal P$ such that
 \(
@@
     In fact, we can write $f = f_0 + f_1$ with $f_0\in \mathcal C_s \oplus \mathcal C_c$ and $f_1 \in \mathcal C_l$.
-    According to \cite[Lemma 2.7]{MarksMilos2018CLT}, there exists an $h_0 \in \mathcal P$ such that for each $t\geq 0$,
+    According to \cite[Lemma 2.7]{MarksMilos2018CLT},
+    %YX there exists an $h_0 \in \mathcal P$ such that for each $t\geq 0$,
+     there exists $h_0 \in \mathcal P$ such that for each $t\geq 0$,
     \[
@@
       |T_t f_1|
-    \leq e^{- \sigma t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > p}
+    \leq e^{- \delta t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > |p|b}
     |\langle f, \phi_p \rangle \phi_p|
@@
   In fact, let $\delta$ be given by \eqref{eq:m:1}, then in this case $\delta > 0$.
-  Now, according to Step 1 there exists an $h \in \mathcal P$ such that $|T_tf| \leq e^{- \delta t} h$ for each $t\geq 0$.
+  Now, according to Step 1 there exists
+ %YX  an $h \in \mathcal P$ such that
+    $h \in \mathcal P$ such that
+  $|T_tf| \leq e^{- \delta t} h$ for each $t\geq 0$.
   This exponential decay implies the desired result in this step.
@@
   Note that $T_t f_c = f_c$ for each $t\geq 0$.
-  Also note that in step 2, we already show that there exists a $\delta > 0$ and an $h \in \mathcal P^+$ such that for each $t\geq 0$, we have $|T_t f_{sl}| \leq e^{- \delta t}h$.
+ %YX Also note that in step 2, we already show that there exists a $\delta > 0$ and an $h \in \mathcal P^+$
+   Also note that in Step 2, we already have shown that there exist $\delta > 0$ and  $h \in \mathcal P^+$
+  such that for each $t\geq 0$, we have $|T_t f_{sl}| \leq e^{- \delta t}h$.
   Therefore, using Lemma \ref{lem: Lip of power function} we have
@@
 
-% **** Stable stable rvs
 \begin{prop}
@@
     \]
-  According to the Step 1 of the proof of Lemma \ref{lem:m}, we know that there exists a $\delta \geq 0$ and an $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta t} h$ for each $s\geq 0$.
+  According to the Step 1 of the proof of Lemma \ref{lem:m},
+%YX  we know that there exists a $\delta \geq 0$   and an $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta t} h$ for each $s\geq 0$.
+ we know that there exist $\delta> 0$ and $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta s} h$ for each $s\geq 0$.
   The above then follows.
 
-  Suppose that $f \in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$, then $f$ can be written by $f = f_c +(f - f_c)$ where $f_c \in \mathcal C_c\setminus\{0\}$ and $f - f_c \in \mathcal C_s \oplus \mathcal C_l$.
-  According to \eqref{eq:P:S:1} we have that in this case $m[\theta f]$ also admits an integral representation
+ %YX Suppose that $f \in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$,
+ If $f \in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$,
+  then $f$ can be written by $f = f_c +(f - f_c)$ where $f_c \in \mathcal C_c\setminus\{0\}$ and $f - f_c \in \mathcal C_s \oplus \mathcal C_l$.
+%YX  According to \eqref{eq:P:S:1} we have that in this case $m[\theta f]$ also admits an integral representation
+ In this case, according to \eqref{eq:P:S:1}, $m[\theta f]$ has an integral representation:
   \begin{align}
@@
 
-% **** Two more Lemmas (Revising)
 \subsection{A refined estimation for the OU semigroup}
+%YX Do we need this subsection?
 It turns out that our proof of the CLT for the super OU processes relies on the following refined estimation for the OU semigroup.
@@
 \label{lem:P:R}
-Suppose that $g \in \mathcal P$, then there exists an $h \in \mathcal P^+$ such that for each 
+Suppose that $g \in \mathcal P$, then there exists
+%YX an $h \in \mathcal P^+$ such that for each
+ $h \in \mathcal P^+$ such that for each
 \(
@@
 \(
-\big | P_t Z_1 f - \langle Z_1 f, \varphi \rangle \big|
+%YX \big | P_t Z_1 f - \langle Z_1 f, \varphi \rangle \big|
+%YX \leq e^{-bt} h.
+\big | P_t [ Z_1 f - \langle Z_1 f, \varphi \rangle ]\big|
  \leq e^{-bt} h.
@@
 \begin{proof}
-  Fix the $g \in \mathcal P$.
-
-  \emph{Step 1.} We argue that we only have to proof the result for all $f \in \widetilde{\mathcal P}_g:= \{T_{n+1} g : n \in \mathbb Z_+\}$.
-  In fact, writing $q_f:=Z_1f - \langle Z_1f, \varphi \rangle \in \mathcal P^*$ for each $f\in \mathcal P$, then both $\operatorname{Re} q_g$ and $\operatorname{Im} q_g$ are functions in $\mathcal P$ of order $\geq 1$.
-Therefore, the result is valid for $f = T_0 g = g$. 
+ %YX Fix the $g \in \mathcal P$.
+In the following $g \in \mathcal P$ is fixed.
+We write  $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$,  and $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
+We need  to prove that for each
+$f\in \mathcal P_g$,  there exists  $h \in \mathcal P^+$ such that for each $|P_tq_f| \leq e^{-bt} h.$
+
+  \emph{Step 1.}
+  %YX We argue that we only have to proof the result for all
+  We claim  that we only need to prove the result for all
+  $f \in \widetilde{\mathcal P}_g:= \{T_{n+1} g : n \in \mathbb Z_+\}$.
+%YX  In fact, writing $q_f:=Z_1f - \langle Z_1f, \varphi \rangle \in \mathcal P^*$ for each $f\in \mathcal P$, then both $\operatorname{Re} q_g$ and $\operatorname{Im} q_g$ are functions in $\mathcal P$ of order $\geq 1$.
+ In fact, both $\operatorname{Re} q_g$ and $\operatorname{Im} q_g$ are functions in $\mathcal P$ of order $\geq 1$.
+%YX Therefore, the result is valid for $f = T_0 g = g$.
+The result is valid for $f = T_0 g = g$ according to  \cite[Fact 1.2]{MarksMilos2018CLT}.
 Also, note that if the result is valid for some $f \in \mathcal P$, it is also valid for any $\theta f$ with $\theta \in [-1,1]$.
@@
   = T_s (g_0 + g_1)
-  = e^{\alpha \tilde \beta s}P_s g_0 + \sum_{p \in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} \langle g_1, \phi_p \rangle e^{-(\alpha \tilde \beta - |p|b)s} \phi_p,
-\]
-where $g = g_0 +g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$. 
+  = e^{\alpha \tilde \beta s}P_s g_0 + \sum_{p \in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} \langle g_1, \phi_p \rangle e^{-(\alpha \tilde \beta - |p|b)s} \phi_p.
+\]
+%YX where $g = g_0 +g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$.
 Notice that the second term is in $C_\infty(\mathbb R^d)\cap \mathcal P$ since it is a finite summation of polynomials, and the first term is also in $C_\infty (\mathbb R^d) \cap \mathcal P$ according to \cite[Fact 1.1]{MarksMilos2018CLT}.
 
-\emph{Step 3.} We show that there exists an $h_3 \in \mathcal P^+$ such that for each $j \in \{1,\dots, d\}$ and $f \in \widetilde {\mathcal P}_g$, it holds that $|\partial_j f| \leq h_3$. 
+\emph{Step 3.} We show that there exists
+%YX an $h_3 \in \mathcal P^+$ such that
+ $h_3 \in \mathcal P^+$ such that
+for each $j \in \{1,\dots, d\}$ and $f \in \widetilde {\mathcal P}_g$, it holds that $|\partial_j f| \leq h_3$.
 In fact, it is known that for $t\geq 0$ and $x\in \mathbb R^d$, the position of the OU process $\xi_t$ under $\mathbb P_x$ is a Gaussian random variable with mean $xe^{-bt}$ and variance $\frac{\sigma^2}{2b} (1- e^{-2bt})$.
@@
 \end{align}
-Write $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$. Thanks to Step 2, $T_1 g_0 \in C_\infty(\mathbb R^d)\cap \mathcal P$. 
+%YX Write $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$.
+ Thanks to Step 2, $T_1 g_0 \in C_\infty(\mathbb R^d)\cap \mathcal P$.
 According to \cite[Fact 1.3]{MarksMilos2018CLT} and the fact that $\alpha \tilde \beta \leq \kappa _{g_0} b$, we have for each $j \in \{1,\dots, d\}$,
@@
 \]
-Therefore, there exists an $h'_3\in \mathcal P^+$ such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$, 
+%YX Therefore, there exists an $h'_3\in \mathcal P^+$
+Therefore, there exists  $h'_3\in \mathcal P^+$
+such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
 \begin{align}
@@
 \end{align}
-On the other hand, there exists an $h_3''\in \mathcal P^+$ such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$, 
+On the other hand, there exists
+%YX an $h_3''\in \mathcal P^+$ such that
+ $h_3''\in \mathcal P^+$ such that
+for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
 \begin{align}
@@
 \end{align}
-The desired result in this step then follows.
-
-  \emph{Step 4.} We show that there exists an $h_{4} \in \mathcal P^+$ such that for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$, it holds that
+%YX The desired result in this step then follows.
+Then the desired result in this step follows.
+
+  \emph{Step 4.} We show that there exists
+  %YX an $h_{4} \in \mathcal P^+$
+   $h_{4} \in \mathcal P^+$
+  such that for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$, it holds that
   \(
@@
 \end{align}
-Recall from Step 1 of the proof of Lemma \ref{lem:m} there exists an $h'_4\in \mathcal P^+$ such that for each $f \in \{T_sg:s\geq 0\}$ it holds that $|f| \leq h'_4$.
+Recall from Step 1 of the proof of Lemma \ref{lem:m} there exists
+%YX an $h'_4\in \mathcal P^+$ such that
+ $h'_4\in \mathcal P^+$ such that
+for each $f \in \{T_sg:s\geq 0\}$ it holds that $|f| \leq h'_4$.
 Therefore, using Step 3, we have for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$,
@@
   & |\partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta}|
-  \leq (1+\beta) e^{\alpha (2+\beta)} P_{1-u} [  (P_u |f|)^\beta P_u |\partial_j f| ] 
-\\&    \leq (1+\beta) e^{\alpha (2+\beta)} P_{1-u} [  (P_u h'_4)^\beta P_u h_3 ] 
-   \leq (1+\beta) e^{\alpha (2+\beta)} Q_0 [  (Q_0 h_4')^\beta Q_0 h_3 ], 
-\end{align}
-where $Q_0$ is given by \eqref{eq:Q}. 
+%YX  \leq (1+\beta) e^{\alpha (2+\beta)} P_{1-u} [  (P_u |f|)^\beta P_u |\partial_j f| ]
+%YX \\&    \leq (1+\beta) e^{\alpha (2+\beta)} P_{1-u} [  (P_u h'_4)^\beta P_u h_3 ]
+%YX   \leq (1+\beta) e^{\alpha (2+\beta)} Q_0 [  (Q_0 h_4')^\beta Q_0 h_3 ],
+\leq (1+\beta) e^{\alpha (1+\beta)} P_{1-u} [  (P_u |f|)^\beta P_u |\partial_j f| ]
+\\&    \leq (1+\beta) e^{\alpha (1+\beta)} P_{1-u} [  (P_u h'_4)^\beta P_u h_3 ]
+     \leq (1+\beta) e^{\alpha (1+\beta)} Q_0 [  (Q_0 h_4')^\beta Q_0 h_3 ],
+\end{align}
+%YX where $Q_0$ is given by \eqref{eq:Q}.
+where $Q_0$ is defined by \eqref{eq:Q}.
 This implies the desired result in this step.
 
- \emph{Step 5.} We show that there exits an $h_5 \in \mathcal P^+$ such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
+ \emph{Step 5.} We show that there exits
+ %YX an $h_5 \in \mathcal P^+$
+  $h_5 \in \mathcal P^+$
+ such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
 In fact, according to Step 4, for each $j \in \{1,\dots, d\}$, $f \in \widetilde{\mathcal P}_g$ and compact $A \subset \mathbb R^d$, we have
@@
 
-\emph{Final step.} From Step 5, there are $c_5,n_5> 0$ such that for each $x\in \mathbb R^d$, $h_5(x) \leq c_5(1+|x|)^{n_5}$. 
+\emph{Final step.}
+%YX From Step 5, there are $c_5,n_5> 0$ such that for each $x\in \mathbb R^d$, $h_5(x) \leq c_5(1+|x|)^{n_5}$.
+Let $h_5$ be the function in Step 5. There are $c_0, n_0> 0$ such that for each $x\in \mathbb R^d$, $h_5(x) \leq c_0(1+|x|)^{n_0}$.
 Note that for each $x, y \in \mathbb R^d$, $1+|x|+|y|\leq (1+|x|) (1+|y|)$;
 and that for each $\theta \in [0,1]$, $|\sqrt {1 - \theta} - 1| \leq \theta$.
-Write $q_f = Z_1f - \langle Z_1f, \varphi\rangle$ for each $f\in \mathcal P$; and $D_{x,y} = \{ax+by: a, b \in [0,1]\}$ for each $x, y \in \mathbb R^d$. 
-Using \eqref{eq:P:R:3:-1} and Step 5, there exists an $h_6 \in \mathcal P^+$ such that for each $t \geq 0$, $f \in \widetilde {\mathcal P}_g$ and $x \in \mathbb R^d$, we have
+Write %YX $q_f = Z_1f - \langle Z_1f, \varphi\rangle$ for each $f\in \mathcal P$; and
+$D_{x,y} = \{ax+by: a, b \in [0,1]\}$ for each $x, y \in \mathbb R^d$.
+Using \eqref{eq:P:R:3:-1} and Step 5,
+%YX there exists an $h_6 \in \mathcal P^+$
+  there exists  $h_6 \in \mathcal P^+$
+such that for each $t \geq 0$, $f \in \widetilde {\mathcal P}_g$ and $x \in \mathbb R^d$, we have
   \begin{align}
@@
     & \leq e^{-bt} \int_{\mathbb R^d} c_0(1+|x|+|y|)^{n_0} (|x|+|y|) \varphi(y) ~dy \\
-    & \leq c_0 e^{-bt}(1+|x|)^{n_0}\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y) ~dy + \int_{\mathbb R^d} (1+ |y|)^n |y| \varphi(y) ~dy \Big) \\
+%YX & \leq c_0 e^{-bt}(1+|x|)^{n_0}\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y) ~dy + \int_{\mathbb R^d} (1+ |y|)^n |y| \varphi(y) ~dy \Big) \\
+    & \leq c_0 e^{-bt}(1+|x|)^{n_0}\Big(|x|\int_{\mathbb R^d} (1+|y|)^{n_0}\varphi(y) ~dy + \int_{\mathbb R^d} (1+ |y|)^{n_0} |y| \varphi(y) ~dy \Big) \\
     & \leq e^{-bt} h_6(x).
@@
 \end{proof}
-% DELETED
-\begin{comment}
-\begin{lem}{\cite[Lemma 2.8]{MarksMilos2018CLT}}
-  For each $f\in \mathcal{P}$, let
-  \begin{align}
-    g_k
-    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
-    \quad k \geq 0.
-  \end{align}
-  Then there exists an $h\in \mathcal{P}$ such that $|P_sg_k|\leq e^{-bs}h$ for all $s, k \geq 0.$
-\end{lem}
-
-\begin{lem}
-  \label{control of gn} 
-  Suppose that $g\in \mathcal{C}_l$.
-  Put
-  \begin{align}
-    \bar{g}_t
-    :=\frac{Z_1(T_tg)-\langle Z_1(T_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
-  \end{align}
-  Then there exists an $h\in \mathcal{P}$ such that $|P_s\bar{g}_t| \leq e^{-bs}h$ for all $s, t\geq 0.$
-\end{lem}
-\begin{proof}
-  First we claim that there exists $h_1\in \mathcal P$ such that
-\begin{align}
-  \label{ineq: control of partial derivative of Itg}
-  \Big|\frac{\partial}{\partial x_i}T_tg(x)\Big| \leq e^{-(\alpha-Kb)t}h_1(x),
-  \quad  t\geq 0, x\in \mathbb R^d.
-\end{align}
-In fact, if we put $h_1(x)=\sum_{p\in \mathbb Z^d_+: \alpha \tilde \beta > |p|b }|\langle g, \phi_p\rangle_\varphi\frac{\partial \phi_p}{\partial x_i}(x)| \in \mathcal P$, then there exists a $\delta > 0$ such that
-\begin{align}
-  \Big|\frac{\partial}{\partial x_i}T_tg(x)\Big| =
-  \Big|\sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta > |p|b}\langle g, \phi_p\rangle_\varphi e^{-(\alpha\tilde \beta-|p|b)t} \frac{\partial}{\partial x_i}\phi_p(x)\Big|
-  \leq e^{-\delta t}h_1(x)
-  , \quad t\geq 0, x\in \mathbb R^d.
-\end{align}
-It is well known that
-\[
-  P_t f(x) = \int_{\mathbb R^d} f\big(x e^{-bt} + y \sqrt{1-e^{-2bt}}\big) \varphi(y) dy,
-  \quad t\geq 0, x\in \mathbb R^d, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
-\]
-It is clear that the above equality also holds for each $f\in \mathcal P$.
-From this, one can easily check that for each differential $f \in \mathcal P$ with $|\nabla  f| \in \mathcal P$, we have
-\[
-  \frac{\partial P_t^\alpha f(x)}{\partial x_i} = e^{-bt} P_t^\alpha\Big(\frac{\partial f}{\partial x_i}\Big)(x), \quad t\geq 0, x\in \mathbb R^d.
-\]
-Note that if $g \in \mathcal C_l$, then $g$ is a linear combination of polynomials.
-Therefore, $g^{1+\beta}\in \mathcal P$ and $|\nabla (g^{1+\beta})| \in \mathcal P$.
-Therefore,
-\begin{align}
-  & \frac{\partial}{\partial x_i} P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}
-    = \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s} g)^{1+\beta}
-    = e^{-b(1-s)} P_{1-s}^\alpha \frac{\partial}{\partial x_i} (I_{t-s}g)^{1+\beta} \\
-  & =(1+\beta)e^{-b(1-s)} P_{1-s}^\alpha \Big( (I_{t-s}g)^\beta \times \frac{\partial}{\partial x_i} (I_{t-s}g) \Big),\quad s\in [0,1], t\geq 0.
-\end{align}
-Using \eqref{eq: supper for Itf}, \eqref{ineq: control of partial derivative of Itg} and the above, we have that there exist a bounded function $a$ on $[0,1]$ and an $h_2 \in \mathcal P$ such that
-\begin{equation}
-  \label{eq: key estimation for partial}
-  \Big| \frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| \leq a(s) e^{-(\alpha - Kb)(1+\beta)t}h_2(x),\quad s\in [0,1],t\geq 0, x\in \mathbb R^d.
-\end{equation}
-Therefore, for each compact subset $A \subset \mathbb R^d$, we have
-\[
-  \int_0^1 \sup_{x\in A} \Big|\frac{\partial P_{1-s}^\alpha  (P_s^\alpha I_t g)^{1+\beta}}{\partial x_i}  (x)\Big| ds 
-  < \infty
-  , \quad t\geq 0.
-\]
-Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, we can get
-\[
-  \frac{\partial}{\partial x_i} Z_1(T_tg)
-  = \eta i^{1+\beta}  \frac{\partial}{\partial x_i} \int_0^1 P_{1-s}^\alpha (I_{t-s}g)^{1+\beta} ds
-  = \eta i^{1+\beta}  \int_0^1  \frac{\partial}{\partial x_i} P_{1-s}^\alpha (I_{t-s}g)^{1+\beta} ds.
-\]
-Therefore, using \eqref{eq: key estimation for partial} and the above, there exists  $C> 0$ such that for all $t\geq 0$,
-\begin{align}
-  & \Big|\frac{\partial}{\partial x_i}\bar{g}_t(x)\Big|
-    = e^{(\alpha-Kb)(1+\beta)t}\Big|\frac{\partial}{\partial x_i}Z_1(-I_tg)\Big| \leq C h_2(x),
-    \quad x\in \mathbb R^d.
-\end{align}
-Therefore there exist $c,n>0$ such that
-\begin{align}
-  \label{ineq: control of sup gt}
-  | \nabla \bar g_t (z)|
-  \leq c(1+|z|)^n
-  , \quad t\geq 0, z\in \mathbb R^d.
-\end{align}
-Define
-\[
-  D(x,y)
-  := \{ax+by: a,b\in [0,1]\}
-  , \quad x, y \in \mathbb R^d.
-\]
-Then for all $x,y\in \mathbb R^d$, $D(x,y)$ is a convex set on $\mathbb R^d$.
-In particular, it contains the interval connecting $xe^{-bs}+y\sqrt{1-e^{-2bs}}$ with $y$ for each $s\geq 0$.
-Also, note that $ | \sqrt { 1 - \theta } - 1 | \leq \theta $ for all $ \theta \in [ 0, 1 ] $, and that $ 1 + \theta + \lambda \leq ( 1 + \theta ) ( 1 + \lambda ) $ for all $ \theta, \lambda \geq 0$.
-Using the fact that $\langle \bar{g}_t,\varphi\rangle = 0$, we get that for all $s,t\geq 0, x\in \mathbb R^d$,
-\begin{align}
-  & |P_s\bar{g}_t(x)|
-    = \Big|\int_{\mathbb R^d} \big(\bar {g}_t(xe^{-bs}+y\sqrt{1-e^{-2bs}})-\bar {g}_t (y)\big) \varphi(y)~dy \Big| \\
-  & \leq \int_{\mathbb R^d} \sup_{z\in D(x,y)} |\nabla \bar g_t (z)|\Big|xe^{-bs}+y\sqrt{1-e^{-2bs}}-y \Big| \varphi(y)~dy \\
-  & \leq e^{-bs}\int_{\mathbb R^d} c(1+|x|+|y|)^n (|x|+|y|) \varphi(y)~dy \\
-  & \leq ce^{-bs}(1+|x|)^n\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y)dy + \int_{\mathbb R^d}(1+|y|)^n|y|\varphi(y)dy\Big).
-  \qedhere
-\end{align}
-\end{proof}
-\end{comment}
-% END ADDED
-% *** small value probability
+
 \subsection{Small value probability}
@@
 
-% *** Moments for super-OU processes
 \subsection{Moments for super-OU processes}
@@
 \begin{proof}
-% ADDED
   It is elementary calculus (see the proof of \cite[Theorem 3.3.6]{Durrett2010Probability} for example) that for each $ux \neq 0$ in $\mathbb R$,
   \[\frac{1}{u}\int_{-u}^u (1- e^{i\theta x})~d\theta = 2 - \frac{2\sin ux}{ux} \geq \mathbf 1_{ux>2}.\]
-% END ADDED
-  % Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof of \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
   Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: upper bound for usgx}.(4).
@@
 
-For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write $ \|Y\|_{\mathbb P;p} := \mathbb P[|Y|^p]^{1/p}. $
+For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write $ \|Y\|_{\mathbb P;p} := \mathbb P[|Y|^p]^{1/p}$.
+%YX Recall that we also write $\tilde u = \frac{u}{1+u}$ for each $u\neq -1$.
+Recall that we write $\tilde u = \frac{u}{1+u}$ for each $u\neq -1$.
 \begin{lem}
@@
     \label{item:P:M:uc:1}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$;
+        $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha \tilde \gamma > \kappa b$;
   \item
     \label{item:P:M:uc:2}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$;
+        $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma = \kappa b$;
   \item
     \label{item:P:M:uc:3}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
+       $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma < \kappa b$.
   \end{enumerate}
@@
 
-% ** Proofs of main results
 \section{Proofs of main results}
@@
 In this subsection, we prove Theorem \ref{thm: law of large number}.
-% DELETED
-% We will return to the large branching rate regime in Subsection \ref{sec: large rate clt} to prove Theorem \ref{thm: large clt}.
-% END DELETED
-% To prove Theorem \ref{thm: law of large number}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
-Recall that $L$ is the infinitesimal generator of the OU-process.
-For $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and  $a\in \mathbb R$, we define
-In order to do this, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
+%YX In order to do this,
+For this purpose,
+we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
 Recall that $L$ is the infinitesimal generator of the OU-process.
@@
   \label{lem:M:L:ML}
-  % For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$. 
-  For each $\mu\in \mathcal M_c(\mathbb R^d)$ and $p \in \mathbb Z_+^d$, $(H^p_t)_{t\geq 0}$ is a martingale with respect to $\mathbb P_\mu$. 
-  % Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$, 
-  Moreover if $\alpha\tilde \beta>|p|b$, then the martingale is bounded in $L^{1+\gamma}(\mathbb P_\mu)$ for each $\gamma\in (0, \beta)$. 
-  % and $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $ exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
-  As a consequence, $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $ convergence almost surely and also in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
+   For each $\mu\in \mathcal M_c(\mathbb R^d)$ and $p \in \mathbb Z_+^d$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_{\mu}$-martingale with respect to
+%YX $(\mathcal F_t)$.
+    $(\mathscr F_t)_{t\geq 0}$.
+%YX Moreover if $\alpha\tilde \beta>|p|b$, the martingale is bounded in $L^{1+\gamma}(\mathbb P_\mu)$ for each $\gamma\in (0, \beta)$
+    Moreover if $\alpha\tilde \beta>|p|b$, the martingale is bounded in $L^{1+\gamma}(\mathbb P_\mu)$ for each $\gamma\in (0, \beta)$.
+%YX  As a consequence, $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $  convergence almost surely  and also in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
+  Thus the limit $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $  exists $\mathbb{P}_{\mu}$-a.s.
+   and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
 \end{lem}
 \begin{proof}
-  % It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb R^d)$.
   Fix the measure $\mu \in \mathcal M_c(\mathbb R^d)$ and the multi-index $p \in \mathbb Z_+^d$.
@@
 
-  % There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, we have $\alpha\gamma>|p|(1+\gamma)b$.
   Further suppose that $\alpha \tilde \beta > |p| b$.
   Then there exists a $\gamma_0 \in (0,\beta)$ which is close enough to $\beta$ so that $\alpha\tilde \gamma>|p|b$ for each $\gamma\in [\gamma_0, \beta)$.
-  % Using  Lemma \ref{lem:P:M:uc} and the fact $\kappa_{\phi_p}=|p|$, we get that, for each $\gamma\in [\gamma_0, \beta)$, there exists a $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$) such that
-  Using  Lemma \ref{lem:P:M:uc} and the fact $\kappa_{\phi_p}=|p|$, we get that, for each $\gamma\in [\gamma_0, \beta)$, there exists a constant $c>0$ such that
+  Using  Lemma \ref{lem:P:M:uc} and the fact $\kappa_{\phi_p}=|p|$, we get that, for each $\gamma\in [\gamma_0, \beta)$,
+  %YX there exists a constant $c>0$ such that
+  there exists a constant $C>0$ such that
 \[
  	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
-  % \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
   \leq c e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
-  % = C_{\gamma, \mu, p}
-  = c
+%YX = c
+    = C
   , \quad t\geq 0.
 \]
-% For all $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, we have
-For each $\gamma\in (0, \gamma_0)$ there exists a constant $c>0$, such that
+%YX For each $\gamma\in (0, \gamma_0)$ there exists a constant $c>0$, such that
+For each $\gamma\in (0, \gamma_0)$ there exists a constant $C>0$, such that
 \[
@@
 	\leq \| H_t^p \|_{\mathbb P_\mu;1+\gamma_0}
-  % < C_{\gamma_0, \mu, p},
-  \leq c,
+ %YX \leq c,
+    \leq C,
 	\quad t\geq 0.
 \]
-% Hence, for all $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
 Therefore, for each $\gamma \in (0,\beta)$, the martingale $(H_t^p)_{t\geq 0}$ is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \end{proof}
-% DELETED
-% In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$  for any $\mu\in \mathcal M_c(\mathbb R^d)$.
-% END DELETED
 \begin{lem}
   \label{lem: control of wt}
-  % Let $\mu\in \mathcal M_c(\mathbb R^d)$.
   Suppose that $\mu\in \mathcal M_c(\mathbb R^d)$ and that $p \in \mathbb Z_+^d$ satisfies $\alpha \tilde \beta > |p|b$.
-  % For all $\gamma\in (0,\beta)$ and $p\in \mathbb{Z}_+^d$ with $\alpha \gamma > |p|b(1+\gamma)$, there exists $C> 0$ such that for all $0\leq s<t$,
   Then for each $\gamma \in (0,\beta)$ satisfying $\alpha \tilde \gamma > |p|b$, there exists a constant $C> 0$ such that,
@@
 \]
-% DELETED
-% Moreover, we have
-% \[
-%  \|H^p_\infty-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
-%  \leq C e^{-\frac{ 1}{1+\gamma}(\alpha\gamma-|p|b(1+\gamma))s},\quad s\geq 0.
-% \]
-% END DELETED
 \end{lem}
@@
 \begin{proof}
-  % The second assertion follows immediately from the first, so we only prove the first assertion.
-  Thanks to Lemma \ref{lem:M:L:ML} we only have to proof this when $0\leq s < t<\infty$.
-  % Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-  Fix the $p\in \mathbb{Z}_+^d$, $\mu\in \mathcal M_c(\mathbb R^d)$ and the $\gamma \in (0,\beta)$ with $\alpha \tilde \beta > |p|b$.
-  % By Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$, there exists $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
-  By Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$, there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$,
-  % DELETED
-  % \begin{align}
-  %   \mathbb{P}_{\mu}\Big[\big|e^{(\alpha-|p|b)(t-s)}\langle\phi_p, X_s\rangle-e^{(\alpha-|p|b)(t-r)}\langle\phi_p, X_r\rangle\big|^{1+\gamma}\Big]
-  %   \leq C_1e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b)}.
-  % \end{align}
-  % Dividing both sides by $e^{(\alpha-|p|b) t(1+\gamma)}$, we get
-  % END DELETED
-\begin{align}
-  % \mathbb{P}_{\mu}\big[|H^p_s-H^p_r|^{1+\gamma}\big]
-  % \leq  C_1 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
+%YX   Thanks to Lemma \ref{lem:M:L:ML} we only have to proof this when $0\leq s < t<\infty$.
+ Thanks to Lemma \ref{lem:M:L:ML}, we only  need to prove the inequality  when $0\leq s < t<\infty$.
+%YX  Fix the $p\in \mathbb{Z}_+^d$, $\mu\in \mathcal M_c(\mathbb R^d)$ and the $\gamma \in (0,\beta)$ with $\alpha \tilde \gamma > |p|b$.
+ Suppose $p\in \mathbb{Z}_+^d$, $\mu\in \mathcal M_c(\mathbb R^d)$ and  $\gamma \in (0,\beta)$ with $\alpha \tilde \gamma > |p|b$ are fixed.
+ %YX By Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,
+ Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,  we know that
+ there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$,
+\begin{align}
   \|H^p_s-H^p_r\|_{\mathbb P_\mu; 1+\gamma}
@@
 	& \leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma} \\
-	% & \leq C_1^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
 	& \leq C_1 \Big(e^{-(\alpha \tilde \gamma- |p|b) s}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor} e^{-(\alpha \tilde \gamma- |p|b) k} + e^{-(\alpha \tilde \gamma-|p|b) t}\Big)
@@
 \end{equation}
-% converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$ satisfies $D^2f\in \mathcal{P}$.
 converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
@@
 \]
-% In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
 In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, $\kappa b< \alpha \tilde \gamma$ for each $\gamma \in [\gamma_0, \beta)$.
@@
 \item
-	% if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C_2>0$ such that
 	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma> \kappa_g b$, then there exists $C_2>0$ such that
@@
 \item
-	% if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C_3>0$ such that
 	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma=\kappa_g b$, then there exists $C_3>0$ such that
@@
     \leq C_3 t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-    % = C_3 t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
     = C_3 t e^{-(\alpha \tilde \gamma - \kappa b)t},
@@
 \item
-	% if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C_4>0$ such that
 	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma < \kappa_g b$, then there exists $C_4>0$ such that
@@
     \leq C_4  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-    % = C_4  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
     = C_4  e^{-(\alpha \tilde \gamma - \kappa b)t},
@@
 
-% *** (The critical branching rate regime)
-% DELETED
-\begin{comment}
-\subsection{The critical branching rate regime}
-\label{sec:critical}
-
-Recall that $\mathcal I_s^t$ is defined in \eqref{Ist}.
-\begin{lem}
-  \label{lem:PR:LC}
-  Let $f\in \mathcal{P}$ be non-trivial and satisfy $\alpha\beta\leq \kappa_fb(1+\beta)$.
-  Then for all $k\geq 0$ and $\mu \in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
-\begin{equation}
-    \gamma_{t,k}
-    := \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha (k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{eq:PR:LC:1}
-\end{equation}
-where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(m_k[\theta f])$.
-\end{lem}
-\begin{proof}
-  We only need to show that for all $\mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0$,
-\begin{equation}
-  \mathbb{P}_{\mu}[\exp(i\gamma_{t,k}); D^c]
-  \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(m_k[f]).
-\end{equation}
-In fact, once we prove this, we can replace $f$ by $\theta f$, with $\theta \in \mathbb R$ being  arbitrary,  to get the desired result.
-In the rest of the proof we fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and an $f\in \mathcal P$.
-Define
-\[
-  A_t(\epsilon)
-  :=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \},
-  \quad t\geq 0, \epsilon > 0.
-\]
-
-Step 1. We will show that for all $\epsilon > 0, k\geq 0$ and $t>k+1$, we have
-\begin{equation}
-  \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c\big]\big|
-  \leq J_1(t,k,\epsilon)+J_2(t,k,\epsilon)+J_3(t,k,\epsilon),
-\end{equation}
-where
-\begin{align}
-\label{eq: Def of Ji}
-  J_1(t,k,\epsilon)
-  & := \mathbb{P}_{\mu}\big[|\langle Z'''_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
-  \\ J_2(t,k,\epsilon)
-  & := \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|; A_{t-k-1}(\epsilon)\big],
-  \\ J_3(t,k, \epsilon)
-  & :=2\mathbb{P}_{\mu}(A_{t-k-1}(\epsilon)\Delta D^c),
-  \\ \theta_{t,k}
-  & := (e^{\alpha( k+1)}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
-\end{align}
-In fact, it follows from \eqref{eq: key equality}, the definitions of $U_1$, $Z'''_1$ and $Z_1$, that for all $k\geq 0, t\geq k+1$,
-\begin{align}
-  \label{eq: need1}
-  & \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}|\mathscr{F}_{t-k-1}]
-    =\mathbb{P}_{\mu}[e^{i\theta_{t,k}\langle P^\alpha_k f,X_{t-k}\rangle-i\theta_{t,k}\langle P^\alpha_{k+1} f, X_{t-k-1}\rangle}|\mathscr{F}_{t-k-1}] \\
-  & =e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}
-    =e^{\langle (Z_1 + Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
-\end{align}
-From Proposition \ref{prop:PL:S}.(1), we have $\operatorname {Re} m_t[f] < 0$. 
-Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
-  \label{eq: inequality that will used later}
-  & \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c\big]\big|
-    \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big] \\
-  & \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{m_k[f]}; A_{t-k-1}(\epsilon)| \mathscr F_{t-k-1}]\big| + 2\mathbb P_\mu(A_{t-k-1}(\epsilon) \Delta D^c| \mathscr F_{t-k-1})\Big] \\
-  & = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon) \\
-  & \leq \mathbb{P}_{\mu}\big[|e^{\langle (Z_1+Z'''_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon) \\
-  & \leq \mathbb{P}_{\mu}\big[|\langle (Z_1+Z'''_1)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon) \\
-  & \leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon).
-\end{align}
-
-Step 2. We will show that for $\epsilon>0$ small enough, there exist  $C_1, \delta_1>0$ such that
-\begin{equation}
-  \label{lemma31q}
-  J_1(t,k,\epsilon)
-  \leq C_1e^{-\delta_1 (t-k)},
-  \quad k\geq 0, t\geq k+1.
-\end{equation}
-In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-Then, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
-  & |Z'''_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
-    \leq R(|\theta_{t,k}P^\alpha_k f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
-  \leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big) \\
-  & \leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha (k+1)}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf \\
-  & \leq\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
-    \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
-\end{align}
-where $Q$ is defined by \eqref{eq:Q}.
-Thus for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
-  \label{eq: estimate of J1}
-  J_1(t,k,\epsilon)
-  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}\mathbb{P}_{\mu}[\langle RQf,X_{t-k-1}\rangle]\\
-  & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)},
-\end{align}
-where $Q$ is defined by \eqref{eq:Q}.
-By taking $\epsilon>0$ small enough, we get the desired result in this step.
-
-Step 3.
-We will show that for $\epsilon>0$ small enough there exist $C_2, \delta_2>0$ such that $ J_2(t,k,\epsilon) \leq C_2e^{-\delta_2 (t-k)},$ for each $k\geq 0, t\geq k+1.$
-
-We first claim that for each $k\geq0$ and $g\in \mathcal P$, $m_k[g]=e^{-\alpha(k+1)}\langle Z_1P_k^{\alpha}g, \varphi \rangle$. 
-In fact, by Fubini's theorem and the definitions of $Z_1$ and $m_k$, we have for all $k\geq 0$ and $g\in \mathcal P$.
-\begin{align}
-	& m_k[g]
-   = \eta \int_k^{k+1}e^{-\alpha s}~ds\int_{\mathbb R^d} (-iP_{s}^\alpha g(x))^{1+\beta} \varphi(x)~dx\\
-  & = \eta \int_0^1e^{-\alpha (k+s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha g)^{1+\beta}\varphi(x)~dx\\
-  & = e^{-\alpha(k+1)} \cdot \eta \int_0^{1}e^{\alpha(1- s)}~ds\int_{\mathbb R^d} (-iP_{s+k}^\alpha        g(x))^{1+\beta} \varphi(x)~dx\\
-  & =e^{-\alpha(k+1)}\langle \eta \int_0^1P_{1-s}^{\alpha}(-iP_{s+k}^\alpha g(x))^{1+\beta}~ds, \varphi \rangle
-  =e^{-\alpha(k+1)}\langle Z_1(P_k^{\alpha}g), \varphi \rangle.
-\end{align}
-
-Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{align}
-  \langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]
-    & = \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha (k+1)}\langle  Z_1P^\alpha_k f,\varphi\rangle
-  \\ & =e^{-\alpha (k+1)}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big),
-\end{align}
-and
-\begin{align}
-  \label{eq: prevJ2}
-  J_2(t,k,\epsilon)
-  & = \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-m_k[f]|;A_{t-k-1}(\epsilon)\big] \\ 
-  & =e^{-\alpha( k+1)}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1P^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
-  & \leq e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
-\end{align}
-where
-\[
-  g_k
-  = \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)k}},
-  \quad k \geq 0.
-\]
-It follows from Lemma \ref{lem:P:R} that there exists $h\in \mathcal{P}$ such that
-\[
-  Q_1 (\operatorname{Re} g_k) \leq h
-  \text{ and } Q_1 (\operatorname{Im} g_k)\leq h,
-  \quad k \geq 0,
-\]
-where $Q_1$ is defined by \eqref{eq:Q} with $\kappa=1$.
-
-Chose a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-According to Lemma \ref{lem:P:M:uc}.(3) (with $\kappa=1$), there exists $C_3>0$ such that for all $t\geq 0$ and $k\geq 0$,
-\begin{align}
-  & \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t}\rangle\right|\right]
-    \leq \|\langle \operatorname{Re} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} \\
-  & \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_3 e^{\frac{\alpha t}{1+\gamma}}.
-\end{align}
-Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$, we have
-\begin{align}
-  \label{eq: right bound for J2}
-  & J_2(t,k, \epsilon)
-    \leq  e^{-\alpha (k+1)}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right] \\
-  & \leq C_3 e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)} \\
-  & = C_3 e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
-    \leq C_3 e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
-\end{align}
-By taking $\epsilon >0$ small enough, we get the required result in this step.
-
-Step 4.
-We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_3>0$ such that for all $k\geq0, t\geq k+1$, $
-J_3(t,k,\epsilon)\leq C_4e^{-\delta_3 (t-k)}.
-% \end{equation}
-$
-In fact, we have  for all $t\geq 0, \epsilon >0$,
-\[   
-  \mathbb P_{\mu}(A_{t}(\epsilon), D) 
-  = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
-  = \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
-  \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
-\]
-By Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_5, \delta_4>0$ such that for all $t\geq 0$,
-\begin{equation}
-  \mathbb P_\mu(A_t(\epsilon)^c,D^c) 
-  \leq \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\| 
-  \leq e^{ - \epsilon t}) \leq C_5 (e^{-\epsilon \delta_4 t}+e^{-\delta_4 t}).
-\end{equation}
-Combining these results, we get the desired result in step 4.
-
-Finally, combining the results in Steps 1--4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3,$ converge to $0$ exponentially fast as $t\rightarrow\infty$, we immediately get the desired result.
-\end{proof}
-
-\begin{cor}\label{cor: used in next corollary}
-  Suppose $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq \kappa_fb(1+\beta)$.
-  Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C, \delta>0$ such that for $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
-\begin{equation}
-  \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-  \leq Ce^{-\delta(t-k)}.
-\end{equation}
-\end{cor}
-\begin{proof}
-	For $f\in \mathcal P$, define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as the $J_1, J_2$ and $J_3$ in \eqref{eq: Def of Ji}.
-	Now, fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and an $f\in \mathcal P$.
-  According to \eqref{eq: inequality that will used later},  we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-  \begin{align}
-    & \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-    \leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
-  \end{align}
-
-  Let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-	According to \eqref{eq: estimate of J1}, we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-  \begin{align}
-    & J^{\theta f}_1(k,t,\epsilon)
-      \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)} \\
-    & \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{ - ( \alpha \frac{ \rho} {1 + \beta} - \epsilon \frac{ 1 + \beta + \rho}{ 1 + \beta}) (t-k-1)}.
-\end{align}
-From the definitions of $Z_1$ and $m_t$ we get that for all $g\in \mathcal P, \theta \geq 0, t\geq 0$,
-\[
-	Z_1( \pm \theta g) 
-  = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[\pm g].
-\]
-Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$, $ J^{\pm \theta f}_2(t,k,\epsilon)
-= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon). $
-According to this and \eqref{eq: right bound for J2},
-we have that there exists $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}
-  \label{eq:31step3b}
-  J^{\theta f}_2(t,k,\epsilon)
-  \leq C |\theta|^{1+\beta}\exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big).
-\end{equation}
-Finally, noticing that $|\theta| < \Theta$, using the estimates of $J^{\theta f}_{i}, i = 1,2$ and the estimate of $J_3$ in Step 4 of the proof of the previous lemma, we get the desired result by choosing $\epsilon$ small enough.
-\end{proof}
-
-\begin{prop}
-  \label{cor:MI}
-  Suppose that $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq\kappa_fb(1+\beta)$.
-  Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for all $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$satisfying $|\theta_i|\leq \Theta$, we have
-\begin{equation}
-  \label{32corollary}
-  \Big|\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{k=0}^n\exp\Big(i\theta_k \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha (k+1)}\|X_{t-k-1}\|)^\frac{1}{1+\beta}}\Big)-\prod_{k=0}^n\exp(m_k[\theta_k f])\Big]\Big|\leq C e^{-\delta(t-n)}.
-\end{equation}
-\end{prop}
-\begin{proof}
-  Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha( k+1)}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
-  Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$satisfying $|\theta_i|\leq \Theta$.
-  For each $k\in\{-1,...,n\}$, we define
-  \[
-    a_k
-    :=\Big(\prod_{l=0}^{k}\exp(m_l[\theta_lf])\Big) \times \mathbb{\widetilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),
-  \]
-  where by convention the first product is $1$ for $k=-1$. Then we get for each $k > -1$,
-  \begin{align}
-    & a_{k-1} - a_k
-    =\mathbb{P}_{\mu}(D^c)^{-1}\Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big] \\
-    & =\mathbb{P}_{\mu}(D^c)^{-1} \Big(\prod_{l=0}^{k-1}e^{m_l[\theta_l f]}\Big) \times \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
-  \end{align}
-  By Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0, 1, \cdots, n\}$, we have
-  \begin{align}
-    | a_{k-1} - a_k|
-    & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
-    \leq C e^{-\delta(t-k)}.
-  \end{align}
-  Therefore,
-  \begin{align}
-    \text{LHS of \eqref{32corollary}}
-    & = \left|a_{-1}-a_n\right|
-    \leq \sum_{k=0}^n\left|a_{k-1}-a_k\right|
-    \leq \sum_{k=0}^n C e^{-\delta(t-k)}.
-  \end{align}
-	Recall that $C, \delta>0$ are independent of the choice of $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb R^{n+1}$ with $|\theta_i|\leq \Theta$.
-  This implies the desired result.
-\end{proof}
-We now present the proof of Theorem \ref{thm: critical clt}.
-\medskip
-
-\begin{proof}[Proof of Theorem \ref{thm: critical clt}]
-  By assumption, $f\in\mathcal{P}$ is non-trivial and satisfies $\alpha\beta=\kappa_fb(1+\beta)$.
-  Fix $\mu \in \mathcal M_c(\mathbb R^d)$.
-  Choose $t_0 > 0$ large enough so that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
-  We write
-  \begin{align}
-    &(t\|X_t\|)^{-\frac{1}{1+\beta}} \langle f,X_t \rangle \\
-    & = \sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle} {(t\|X_t\|)^{\frac{1}{1+\beta}}} + \Big( \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac {\mathcal I_{t-k-1}^{t-k} \langle f, X_t\rangle} {(t\|X_t\|)^{\frac{1}{1+\beta}}} + \frac {\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle} {(t\|X_t\|)^{\frac{1}{1+\beta}}} \Big) + \frac {\langle P^\alpha_tf,X_0\rangle} { ( t \| X_t \| )^{ \frac { 1 } { 1 + \beta } } } \\
-    & =: I_1(t) + I_2(t) + I_3(t),
-      \quad t\geq t_0.
-  \end{align}
-  Define
-  \[
-    \widetilde I_1(t)
-    := \sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k} \langle f ,X_t\rangle} {(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}} },
-    \quad t\geq t_0.
-  \]
-  Fix $\theta\in \mathbb R$.
-  Taking $\theta_k=t ^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{cor:MI}, we get that there exist $C_1,\delta_1>0$ such that,
-  \begin{align}
-    \Big| \mathbb{\widetilde{P}}_{\mu}  [ e^{ i  \theta \widetilde{I}_1(t) } ] - \exp \Big( \frac { 1 } { t } \sum_{k=0}^{\lfloor t - \ln t \rfloor} m_k [ \theta f ] \Big) \Big| 
-    \leq \frac{C_1}{t^{\delta_1}},
-    \quad t\geq t_0.
-  \end{align}
-  According to \eqref{para: critical case},  $\widetilde{I}_1(t)\xrightarrow[t\to \infty]{d}\widetilde \zeta$ under $\widetilde {\mathbb P}_\mu$.
-  Therefore, we only need to prove
-  \begin{equation}
-    \label{toprove-1}
-    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\widetilde{P}}_{\mu}[e^{i\theta\widetilde{I}_1(t)}]|
-    \xrightarrow[t\to \infty]{} 0
-  \end{equation}
-  and
-  \begin{equation}
-    \label{toprove-2}
-    I_i(t)\xrightarrow[t\to \infty]{d} 0,
-    \quad i = 2,3,
-    \mbox{ under } \widetilde {\mathbb P}_\mu.
-  \end{equation}
-
-  By \cite[Lemma 3.4.3]{Durrett2010Probability},
-  \begin{equation}
-    \label{ineq: control of I1t}
-    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\widetilde{P}}_{\mu} [e^{i\theta\widetilde{I}_1(t)}]|
-    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\big],
-    \quad t\geq t_0,
-  \end{equation}
-  where for all $k \geq 0$ and $t\geq k+1$,
-  \begin{align}
-    Y_{t,k}
-    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big).
-  \end{align}
-  Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
-  \[
-    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
-  \]
-  Fix this $\gamma$, then choose $\eta_0,\eta_1>0$ such that
-  \[
-    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
-  \]
-  Recall that $H_t := e^{-\alpha t}\|X_t\|$.
-  Define for all $k \geq 0$ and $t\geq k+1$,
-  \begin{equation}
-    \label{def: Dtk}
-    \mathcal{D}_{t,k}
-    :=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
-  \end{equation}
-
-  Step 1. We will show that there exist $C_2,\delta_2 >0$ such that for all $k \geq 0$ and $t\geq k+1$,
-  \begin{equation}
-    \label{thm121}
-    \mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|;\mathcal{D}^c_{t,k}\big]
-    \leq C_2 e^{-\delta_2 (t-k)}.
-  \end{equation}
-  It follows from Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality that there exist $C_3, \delta_3>0$ such that for all $k \geq 0$ and $t\geq k+1$,
-  \begin{align}
-    \label{eq: prob of Dtkc}
-    & \mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
-    \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}) \\
-    & \leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|] \\
-    & \quad 
-      + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c) \\
-    & \leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma} \\
-    & \quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}) \\
-    & \leq C_3 e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C_3 e^{-\delta_3(t-k-1)}.
-  \end{align}
-  This implies the desired result in this step, since $|Y_{t,k}| \leq 2$ a.s..
-
-  Step 2. We will show that there exist $C_4,\delta_4 > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
-  \begin{equation}
-    \label{thm122}
-    \mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \leq  C_4 e^{-\delta_4 (t-k)}.
-  \end{equation}
-  In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \geq 0$ and $t\geq k+1$,
-  \begin{align}
-    \label{eq: control of Ykt}
-    & \mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big] \\
-    & \leq|\theta|t^{-\frac{1}{1+\beta}} \mathbb{\widetilde{P}}_{\mu}\bigg[|\mathcal I_{t-k-1}^{t-k}\langle f , X_t\rangle | \cdot \Big| \frac {1} {(e^{\alpha(k+1)} \| X_{t-k-1}\| )^{ \frac {1} {1+\beta} } } - \frac {1} {\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\bigg] \\
-    & \leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
-  \end{align}
-  where
-  \begin{equation}
-    \label{def: Ktk}
-    K_{t,k}
-    := \Big| \frac {H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}} {H_t^{\frac{1}{1+\beta}} H_{t-k-1}^{ \frac {1} {1+\beta} }} \Big| \mathbf{1}_{\mathcal{D}_{t,k}}.
-  \end{equation}
-  Note that, since $\eta_1 < \eta_0$, we have on $\mathcal D_{t,k}$,
-  \begin{align}
-    H_t
-    & \geq H_{t-k-1}- e^{-\eta_0(t-k-1)}
-      \geq 2e^{-\eta_1(t-k-1)}-e^{-\eta_0(t-k-1)}
-      \geq e^{-\eta_1(t-k-1)}.
-  \end{align}
-  Therefore, for each $k \geq 0$ and $t\geq k+1$,  on $\mathcal D_{t,k}$,
-  \begin{align}
-    & \Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
-      \leq \frac {1} {1+\beta} \max \Big \{ H_t^{-\frac{\beta}{1+\beta} }, H_{t-k-1}^{ -\frac{\beta}{1+\beta} } \Big\} \left| H_t - H_{t-k-1} \right| \\
-    & \leq \frac{1}{1+\beta} \max\{e^{\eta_1 (t-k-1)}, \frac{1}{2}e^{\eta_1(t-k-1)}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0(t-k-1)} \\
-    & \leq \frac{1}{1+\beta} e^{\eta_1 (t-k-1)} e^{-\eta_0(t-k-1)}
-    = \frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)}
-  \end{align}
-  and
-  \begin{align}
-    |H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}|
-    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1(t-k-1)}.
-  \end{align}
-  Thus, there exists  $C_5> 0$ such that for all $k \geq 0, t\geq k+1$,
-  \begin{equation}
-    \label{ineq: control of Kkt}
-    K_{t,k}
-    \leq C_5 e^{-(\eta_0 - 3\eta_1)(t-k-1)}.
-  \end{equation}
-  By Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and \eqref{ineq: control of Kkt}, there exist $C_6>0$ such that for all $k\geq 0$ and $t\geq k+1$,
-  \begin{align}
-    \label{eq: Y in D}
-    & \mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
-    \leq C_5 | \theta | e^{-\frac{\alpha}{1+\beta}t} \mathbb{\widetilde{P}}_{\mu} \big[ | \mathcal{I}_{t-k-1}^{t-k}\langle f, X_t\rangle| \big] e^{-(\eta_0 - 3\eta_1)(t-k-1)} \\
-    & \leq  \frac{C_5} {\mathbb{P}_{\mu}(D^c)} | \theta | e^{-\frac{\alpha} {1+\beta}t}\mathbb{P}_{\mu} \big[ |\mathcal{I}_{t-k-1}^{t-k}\langle f, X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)} \\
-    & \leq \frac{C_5} {\mathbb{P}_{\mu}(D^c)} | \theta | e^{ - \frac{\alpha} {1 + \beta} t} \|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta_0 - 3\eta_1)(t-k - 1)} \\
-    & \leq C_6 e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)} \\
-    & = C_6 e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)},
-  \end{align}
-  as desired in this step.
-  In the last equality, we used the fact that
-  \[
-    -(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})
-    = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta})
-    = \frac{\gamma \alpha}{1+\gamma} - k_f b
-    =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
-  \]
-
-  Step 3.
-  We will show that there exist $C_7, \delta_5> 0$ such that for $t$ large enough,
-  \begin{equation}
-    \label{domi-difference of Is}
-    |\mathbb{\widetilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\widetilde{P}}_{\mu} [ e^{ i \theta \widetilde{I}_1(t) } ] |
-    \leq C_7 t^{-\delta_5}.
-  \end{equation}
-  In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C_8,\delta_6 > 0$ such that for all $k \geq 0$ and $t\geq k+1$ we have,
-  \[
-    \widetilde{\mathbb P}_\mu\big[|Y_{t,k}|\big]
-    \leq C_8 e^{-\delta_6(t-k)}.
-  \]
-  Therefore, there exists $C_9> 0$  such that for all $t \geq 1$,
-  \begin{align}
-    & \sum_{k=0}^{\lfloor t-\ln t \rfloor} \widetilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
-      \leq C_8\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{-\delta_6(t-k)}
-      = C_8 e^{-\delta_6 t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta_6 k}
-      \leq C_9 e^{-\delta_6 t}e^{\delta_6 (t-\ln t)}
-      = \frac{C_9}{t^{\delta_6}}.
-  \end{align}
-  Letting $t\to\infty$ in \eqref{domi-difference of Is}, we get \eqref{toprove-1}.
-
-  Step 4.
-  We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\widetilde{P}}_{\mu}$.
-  In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C_{10}, \delta_7>0$ such that
-  \begin{equation}
-    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
-    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_{10}( t^{-\delta_7}+e^{-\delta_7 t})
-    , \quad t\geq0.
-  \end{equation}
-  Therefore,
-  \begin{equation}
-    \label{Theorem123}
-    |\mathbb{\widetilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
-    \leq 2\mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C_{10}(t^{-\delta_7}+e^{-\delta_7 t}),
-    \quad t\geq t_0.
-  \end{equation}
-  Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})\leq \frac{1}{2(1+\beta)}$.
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C_{11},C_{12},C_{13}>0$ such that
-  \begin{align}
-    & |\mathbb{\widetilde{P}}_{\mu} [ (e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
-      \leq |\theta| \mathbb{\widetilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big] \\
-    & \leq | \theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\widetilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big) \\
-    & \leq C_{11} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big) \\
-    & \leq C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
-    & = C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})k}\\
-    & \leq C_{12} |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})j}\\
-    & \leq C_{13}|\theta| t^{-\frac{1}{2(1+\beta)}}t^{(\frac{\alpha}{1+\gamma}- \frac{\alpha}{1+\beta})},
-      \quad t\geq t_0.
-  \end{align}
-  From this and \eqref{Theorem123}, we get the desired result in this step.
-
-  Step 5.
-  We will show that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
-  In fact, we have
-  \begin{align}
-    & |I_3(t)|
-      \leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
-      \leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(te^{\alpha t} H_t)^{\frac{1}{1+\beta}}} \\
-    & = t^{-\frac{1}{1+\beta}} e^{\frac{\beta \alpha t}{1+\beta} - k_fbt} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
-      = t^{-\frac{1}{1+\beta}} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
-      \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
-  \end{align}
-
-	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{thm: critical clt}.
-\end{proof}
-\end{comment}
-% END DELETED
-% *** Local central limit theorems
-% \subsection{The critical branching rate regime}
-\subsection{Local central limit theorems}
+%YX \subsection{Local central limit theorems}
+\subsection{Central limit theorems for one unite time interval}
 \label{sec:critical}
 % ***** Local CLT for one interval for small and critical
-In this section, we will establish the following local central limit theorem for our super OU processes.
+%YX In this section, we will establish the following local central limit theorem for our super OU processes.
+In this subsection, we will establish the following  central limit theorem for our super OU processes.
 \begin{thm}
@@
 
-In fact, we can proof a stronger result:
+%YX In fact, we can proof a stronger result:
+In fact, we  prove a stronger result:
 
@@
 \end{align}
-From Proposition \ref{prop:PL:S}, we have $\operatorname{Re} \langle Z_1f, \varphi\rangle \leq 0$.
+%YX From Proposition \ref{prop:PL:S} and Lemma \ref{lem: charactreisticfunction}, we easily get $\theta\mapsto \langle Z_1(\theta f),\varphi\rangle$ is the characteristic function of some $(1+\beta)$-stable random variable.
+Therefore  $\operatorname{Re} \langle Z_1f, \varphi\rangle \leq 0$.
+ From Lemma \ref{lem: charactreisticfunction}, we  get that $\theta\mapsto \langle Z_1(\theta f),\varphi\rangle$ is the characteristic function of some $(1+\beta)$-stable random variable, and then  $\operatorname{Re} \langle Z_1f, \varphi\rangle \leq 0$.
 Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get for each $t\geq 0$ and $\epsilon> 0$,
@@
 
-\emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for each $t\geq 1$ and $f \in \{\theta T_sg: s\geq 0,-1\leq \theta \leq 1\}$, we have
+\emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for each $t\geq 1$ and
+$f \in \mathcal P_g$, we have
 \(
@@
 In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-Acording to the step 1 of the proof of Lemma \ref{lem:m}, there exist $h_{20} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{20}$.
+%YX Acording to the step 1 of the proof of Lemma \ref{lem:m},
+Acording to Step 1 of the proof of Lemma \ref{lem:m},
+%YX there exist $h_{20} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{20}$.
+    there exist $h_{2} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{2}$.
 Then, we have for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
@@
   & |Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
-    \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t-1}(\epsilon)}
-  \leq R \Big(\frac{h_{20}}{e^{(\alpha-\epsilon)(t-1)(1-\tilde \beta)}}\Big) \\
-   & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-1)}Rh_{20}.
+ %YX   \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t-1}(\epsilon)}
+ %YX \leq R \Big(\frac{h_{20}}{e^{(\alpha-\epsilon)(t-1)(1-\tilde \beta)}}\Big) \\
+ %YX  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-1)}Rh_{20}.
+     \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t}(\epsilon)}
+     \leq R \Big(\frac{h_{2}}{e^{(\alpha-\epsilon)t(1-\tilde \beta)}}\Big) \\
+      & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}Rh_{2}.
 \end{align}
@@
   J^f_1(t,\epsilon)
-  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[\langle Rh_0,X_{t-1}\rangle]\\
-  & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 R h_{20}, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
+%YX & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[\langle Rh_0,X_{t-1}\rangle]\\
+%YX  & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 R h_{20}, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
+& \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[\langle Rh_2,X_{t-1}\rangle]\\
+& \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 R h_{2}, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
 \end{align}
@@
 \emph{Step 3.}
-We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for each $t \geq 1$ and $f\in \mathcal P_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.
+We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for each $t \geq 0$ and $f\in \mathcal P_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.
 In fact, for all $t\geq 0$, and $f\in \mathcal P_g$,
@@
      = \theta_t^{1+\beta} \langle Z_1 f,X_t\rangle - \langle  Z_1 f,\varphi \rangle
-   =\Big\langle Z_1f - \langle  Z_1 f ,\varphi \rangle, \frac{X_{t-1}}{\|X_{t-1}\|}\Big\rangle,
+     =\Big\langle Z_1f - \langle  Z_1 f ,\varphi \rangle, \frac{X_{t}}{\|X_{t}\|}\Big\rangle,
 \end{align}
@@
 \)
-It follows from Lemma \ref{lem:P:R} that there exists an $h_{30}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have
+%YX It follows from Lemma \ref{lem:P:R} that there exists an $h_{30}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have
+It follows from Lemma \ref{lem:P:R} that there exists $h_{30}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have
+%YX why use index 30?
 \(
@@
 where $Q_1$ is given by \eqref{eq:Q} with $\kappa=1$.
-In the rest of this step, fixing a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-According to Lemma \ref{lem:P:M:uc}.(3) (with $\kappa=1$), there exists $C_{30}>0$ such that for all $t\geq 0$ and $f\in \mathcal P_g$,
+%YX In the rest of this step, fixing a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
+In the rest of this step, we  fix a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
+According to Lemma \ref{lem:P:M:uc}.(3) (with $\kappa=1$),
+%YX there exists $C_{30}>0$ such that for all $t\geq 0$ and $f\in \mathcal P_g$,
+there exists $C_{3}>0$ such that for all $t\geq 0$ and $f\in \mathcal P_g$,
 \begin{align}
@@
     \leq \|\langle \operatorname{Re} q_f, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} q_f, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} \\
-  & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{30}} \|\langle q, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_{30} e^{\frac{\alpha t}{1+\gamma}}.
+%YX  & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{30}} \|\langle q, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_{30} e^{\frac{\alpha t}{1+\gamma}}.
+ & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{3}} \|\langle q, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_{3} e^{\frac{\alpha t}{1+\gamma}}.
 \end{align}
@@
     \leq  C_3 e^{-(\alpha-\epsilon)t}e^{\frac{\alpha t}{1+\gamma}}
-\leq C_{30} e^{-(\alpha\tilde \gamma -\epsilon)t}.
+%YX \leq C_{30} e^{-(\alpha\tilde \gamma -\epsilon)t}.
+   \leq C_{3} e^{-(\alpha\tilde \gamma -\epsilon)t}.
 \end{align}
@@
 \]
-On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_{40}, \delta_{40}>0$ such that for all $t\geq 0$,
+On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$,
+%YX there exists  $C_{40}, \delta_{40}>0$ such that for all $t\geq 0$,
+there exists  $C_{4}, \delta_{4}>0$ such that for all $t\geq 0$,
 \begin{equation}
@@
   \leq \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\|
-  \leq e^{ - \epsilon t}) \leq C_{40} (e^{-\epsilon \delta_{40} t}+e^{-\delta_{40} t}).
-\end{equation}
-Combining these results, we get the desired result in step 4.
-
-\emph{Final step}, combining the results in Steps 1--4, we immediately get the desired result.
+%YX  \leq e^{ - \epsilon t}) \leq C_{40} (e^{-\epsilon \delta_{40} t}+e^{-\delta_{40} t}).
+     \leq e^{ - \epsilon t}) \leq C_{4} (e^{-\epsilon \delta_{4} t}+e^{-\delta_{4} t}).
+\end{equation}
+%YX Combining these results, we get the desired result in step 4.
+ Combining these results, we get the desired result in this step.
+
+%YX \emph{Final step}, combining the results in Steps 1--4, we immediately get the desired result.
+ \emph{Final step}. Combining the results in Steps 1--4, we immediately get the desired result.
 \end{proof}
@@
 % ***** local CLT one interval for large
-% DELETED
-\begin{comment}
-In this subsection, we revisit the large branching rate regime and prove Theorem \ref{thm: large clt}.
-For $g\in \mathcal{C}_l$, recall the definition of $I_tg$ in \eqref{definition of Itf}.
-By Fubini's theorem, we have
-\begin{align}
-  \label{equ: transform of mn}
-  & \bar{m}_n[g]
-    = e^{\alpha(n-1)}\int_0^1 e^{\alpha s}\langle \eta(iI_{s+n-1}g)^{1+\beta}, \varphi\rangle ds \\   
-  & = e^{\alpha(n-1)}\langle \int_0^1 P_s^{\alpha}\langle \eta(iI_{s+n-1}g)^{1+\beta}ds, \varphi\rangle\\
-  & =e^{\alpha(n-1)}\langle \int_0^1 P_{1-s}^{\alpha}\langle \eta(iI_{n-s}g)^{1+\beta}ds, \varphi\rangle=e^{\alpha(n-1)}\langle Z_1(-I_ng), \varphi\rangle,
-    \quad n\geq 1.
-\end{align}
-
-Recall that $H^p_t$ are defined before Lemma \ref{lem:M:L:ML}. We write $a_p:= \langle \phi_p, g\rangle_\varphi$ for each $p \in \mathbb Z_+^d$.
-
-\begin{lem}
-  \label{large-central}
-  For all $n\ge 1$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$, if $f \in \mathcal C_l$, then
-\begin{align}
-  \gamma^f_{t,n}
-  := \frac{X_{t+n+1}(P^\alpha_{-(n+1)}f) - X_{t+n}(P_{-n}^\alpha f)}{\|e^{- \alpha n}X_{t+n}\|^{1 - \tilde \beta}}
-  \xrightarrow[t\to \infty]{d}\zeta^f_{n,n+1}.
-\end{align}
-\end{lem}
-\begin{proof}
-  We only need to show that
-  \begin{align}
-    \mathbb{P}_{\mu}[\exp(i\gamma^f_{t,n}); D^c]
-    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(m_{n,n+1}[g]).
-  \end{align}
-  Put $ \theta_{ t, p, n} := a_p \frac { e^{ - ( \alpha - | p | b ) n } } { ( e^{ - \alpha ( n - 1 ) } \| X_{ t + n - 1 } \| )^{ \frac { 1 } { 1 + \beta } } } $ and $ A_t(\epsilon):=\{\|X_t\| > e^{(\alpha-\epsilon)t}\}$.
-  We have
-  \begin{align}
-    \bar{\gamma}_{t,n}
-    =\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p, X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle).
-  \end{align}
-
-	Step 1. We will show that for all $\epsilon > 0, n\geq 1$, and $t\geq 0$, we have
-  \begin{align}
-    \big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
-    \leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon),
-  \end{align}
-	where
-  \begin{align}
-    \label{eq: Def of JJ1}
-    J'_1(t,n,\epsilon)
-    & := \mathbb{P}_{\mu}\big[|\langle Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big], \\ 
-    J'_2(t,n,\epsilon)
-    & := \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big] \\
-    J'_3(t,n, \epsilon)
-    & := 2\mathbb{P}_{\mu}(A_{t+n-1}(\epsilon)\Delta D^c).
-  \end{align}
-  In fact, it follows from \eqref{eq: key equality} that
-  \begin{align}
-    \label{eq: need11}
-    & \displaystyle\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}|\mathscr{F}_{t+n-1}]
-      = \mathbb{P}_{\mu}[e^{i\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p,X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle)}|\mathscr{F}_{t+n-1}] \\
-    & = \displaystyle e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
-  \end{align}
-
-  According to \eqref{eq: need11} and the fact that $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$,
-  we have for all $n\geq 1, t\geq 0$ and $\epsilon> 0$,
-  \begin{align}
-    \label{eq: inequality that will used later1}
-    & \big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
-    \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c | \mathscr F_{t+n-1}]\big|\Big] \\
-    & \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; A_{t+n-1}(\epsilon)| \mathscr F_{t+n-1}]\big| + 2\mathbb P_\mu(A_{t+n-1}(\epsilon) \Delta D^c| \mathscr F_{t+n-1})\Big] \\
-    & = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}| \mathscr F_{t+n-1}]-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big] + J'_3(t,n,\epsilon) \\
-    & = \mathbb{P}_{\mu}\Big[\big|e^{\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon) \\
-    & \leq \mathbb{P}_{\mu}\Big[\big|\langle (Z'''_1+Z_1)(-\sum_{p\in \mathcal{N}}
- \theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon) \\
-    & \leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon).
-  \end{align}
-
-  Step 2.
-  We will show that for $\epsilon>0$ small enough, there exist $C_1,\delta_1>0$ such that for all $n\geq 1$ and $t\geq 0$, $ J'_1(t,n,\epsilon)\leq C_1 e^{-\delta_1(t+n)}. $
-  Let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-  Then we have for all $n\geq 1, t\geq 0, \epsilon > 0$,
-  \begin{align}
-    & |Z'''_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
-      \leq R(|\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p|)\mathbf{1}_{A_{t+n-1}(\epsilon)} \\
-    & \leq R \Big( \frac{ \sum_{p\in\mathcal{N} } | a_p | e^{ - ( \alpha - | p | b ) n } | \phi_p | } { \big( e^{ - \alpha ( n - 1 ) } e^{ ( \alpha - \epsilon ) ( t + n - 1 ) } \big)^{ \frac { 1 } { 1 + \beta } } } \Big) \\
-    & \leq \sum_{ \rho \in \{ \delta_0, 1 \} } \Big( \frac { e^{ - ( \alpha - K b ) n } }  { \big( e^{ - \alpha ( n - 1 ) } e^{ ( \alpha - \epsilon ) ( t + n - 1 ) } \big)^{ \frac { 1 } { 1 + \beta } } } \Big)^{ 1 + \beta + \rho } R h \\
-    & = \sum_{ \rho \in \{ \delta_0, 1 \} } e^{ - \alpha \frac{ 1 + \beta + \rho } { 1 + \beta } } e^{ - \frac { 1 + \beta + \rho } { 1 + \beta } ( \alpha \beta - K ( 1 + \beta ) b ) n } e^{ - \frac{ 1 + \beta + \rho } { 1 + \beta } ( \alpha - \epsilon ) ( t + n - 1 ) } R h \\
-    & \leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}Rh,
-  \end{align}
-  where $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
-  Thus there exists $C_3>0$ such that for $n\geq 1,  t\geq 0$ and $\epsilon > 0$,
-  \begin{align}
-    \label{eq: estimate of J11}
-    J'_1(t,n,\epsilon)
-    & \leq  \sum_{ \rho \in \{ \delta_0, 1\} } e^{ - \frac{ 1 + \beta + \rho } { 1 + \beta } ( \alpha - \epsilon ) ( t + n - 1 ) } \mathbb{ P }_{ \mu }[ \langle R h, X_{ t + n - 1 } \rangle] \\
-    & \leq C_1 \sum_{ \rho \in \{ \delta_0, 1\} } \exp \Big \{ - \Big( \alpha \frac{ \rho } { 1 + \beta } - \epsilon \frac{ 1 + \beta + \rho } { 1 + \beta } \Big) ( t + n - 1 ) \Big\}.
-  \end{align}
-  By choosing $\epsilon>0$ small enough, we get the desired result in this step.
-
-  Step 3.
-  We will show that for each $\epsilon > 0$ small enough, there exist $C_2,\delta_2>0$ such that for all $n\geq 1, t\geq 0$, $ J'_2(t,n,\epsilon) \leq C_2 e^{-\delta_2(t+n)}.$
-  In fact, according to the definitions of $Z_1$ and $\bar{m}_n$, and \eqref{equ: transform of mn}, we have for all $t\geq 0, n\geq1$,
-  \begin{align}
-    & \langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]
-      = e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
-  \end{align}
-  Therefore, for all $t\geq 0, n\geq1$ and $\epsilon > 0$,
-  \begin{align}
-    & J'_2(t,n,\epsilon)
-      = \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big]
-    \\ & \leq e^{\alpha(n-1)}\mathbb{P}_{\mu}\Big[\big|\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\big|; A_{t+n-1}(\epsilon)\Big]
-    \\ & \leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu} [ \langle \bar {g}_n, X_{t+n-1} \rangle],
-  \end{align}
-  where
-  \begin{align}
-    \bar{g}_n
-    := \frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
-  \end{align}
-  Fix a $\gamma>0$ small enough such that $\alpha \gamma < (1+\gamma)b$.
-  Using Lemma \ref{control of gn} and Lemma \ref{lem:P:M:uc}.(3) with $\kappa=1$, there exists $C_3>0$ such that
-  \begin{align}
-    \mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]
-    \leq C_3e^{\frac{\alpha}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
-  \end{align}
-  Therefore, for all $t\geq 0, n\geq1$ and $\epsilon >0$,
-  \begin{align}
-    & J'_2(t,n,\epsilon)\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]
-    \\ & \leq C_3 e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)} \\
-   & = C_3 e^{-\alpha} e^{ - ( \alpha \beta - K ( 1 + \beta ) b ) n } e^{ - ( \frac{ \alpha \gamma } { 1 + \gamma } - \epsilon ) ( t + n - 1 ) }
-     \leq C_3 e^{-( \frac{ \alpha \gamma } { 1 + \gamma } - \epsilon ) ( t + n - 1 ) }.
-  \end{align}
-  Now, by choosing $\epsilon >0$ small enough, we get the desired result in this step.
-
-  Step 4.
-According to the Step 4 of the proof of  Lemma \ref{lem:PR:LC}, we have for any $\epsilon\in (0,  \alpha)$ there exist $C_4,\delta_3>0$ such that $ J'_3(t,n,\epsilon)\leq C_4e^{-\delta_3 (t+n)}$ for all $ t\geq0, n\geq 1$.
-
-  Finally, combining the results in Steps 1--4.
-and noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$, converge to $0$ exponentially fast when $t\rightarrow\infty$, we get the desired result.
-\end{proof}
-\end{comment}
-% END MOVED AND MODIFIED FROM BELOW
-% ***** LCLT for conditional one interval
-% DELETED
-\begin{comment}
-\begin{cor}
-\label{cor: used in next corollary}
-  Suppose $f\in \mathcal{P}$ is non-trivial and satisfies $\alpha\beta\leq \kappa_fb(1+\beta)$.
-  Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C, \delta>0$ such that for $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
-\begin{equation}
-  \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma^f_{t,k}}-e^{m_{k,k+1}[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-  \leq Ce^{-\delta(t-k)}.
-\end{equation}
-\end{cor}
-\begin{proof}
-	Define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as in \eqref{eq: Def of Ji}.
-  According to \eqref{eq: inequality that will used later},  we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-  \begin{align}
-    & \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma^f_{t,k}}-e^{m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
-    \leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
-  \end{align}
-
-  Let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-	According to \eqref{eq: estimate of J1}, we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-  \begin{align}
-    & J^{\theta f}_1(k,t,\epsilon)
-      \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)} \\
-    & \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{ - ( \alpha \frac{ \rho} {1 + \beta} - \epsilon \frac{ 1 + \beta + \rho}{ 1 + \beta}) (t-k-1)}.
-\end{align}
-From the definitions of $Z_1$ and $m_{t,t+1}$ we get that for all $g\in \mathcal P, \theta \geq 0, t\geq 0$,
-\[
-	Z_1( \pm \theta g) 
-  = \theta^{1+\beta} Z_1(\pm g), \quad m_{t,t+1}[\pm \theta g] = \theta^{1+\beta} m_t[\pm g].
-\]
-Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$, $ J^{\pm \theta f}_2(t,k,\epsilon)
-= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon). $
-According to this and \eqref{eq: right bound for J2},
-we have that there exists $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
-\begin{equation}
-  \label{eq:31step3b}
-  J^{\theta f}_2(t,k,\epsilon)
-  \leq C |\theta|^{1+\beta}e^{-(\alpha \tilde \gamma - \epsilon)(t-k-1)}.
-\end{equation}
-Finally, noticing that $|\theta| < \Theta$, using the estimates of $J^{\theta f}_{i}, i = 1,2$ above and the estimate of $J_3$ in Step 4 of the proof of the previous lemma, we get the desired result by choosing $\epsilon$ small enough.
-\end{proof}
-\end{comment}
-% END DELETEd
+% ***** LCLT for conditional one intervald
 % ***** LCLT for Multiple interval
@@
   \end{align}
-  By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that for each $l\leq n$ in $\mathbb Z_+$, each $k \in \{l,\dots , n\}$, and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+  By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that
+  %YX for each $l\leq n$ in $\mathbb Z_+$, each $k \in \{l,\dots , n\}$, and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+   for each $l\leq n$ in $\mathbb Z_+$,  $k \in \{l,\dots , n\}$, and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
   \begin{align}
@@
   \end{align}
-  Therefore, there exist $C_1,\delta_1 >0$ such that for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+ %YX Therefore, there exist $C_1,\delta_1 >0$ such that
+    Therefore, there exist $C,\delta >0$ such that
+   for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+
   \begin{align}
@@
     \leq \sum_{k=l}^n C_0 e^{-\delta_0 k}
-      \leq C_1 e^{- \delta_1 l}.
+%YX      \leq C_1 e^{- \delta_1 l}.
+         \leq C e^{- \delta l}.
       \qedhere
@@
 % ***** local CLT multiple interval for large branching rate
-% DELETED 
-\begin{comment}
-\begin{lem}
-  \label{lem: independency for large rate}
-  For all $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
-  \begin{align}
-    \label{ineq: next we will need}
-    \bigg| \widetilde{ \mathbb{P} }_{ \mu } \Big[ \prod_{ l = 1 }^m \exp ( i \theta \bar{ \gamma }_{t, l} ) - \prod_{ l = 1 }^m \exp( \bar{m}_l[\theta g])\Big]\bigg|\leq C e^{-\delta t}.
-  \end{align}
-\end{lem}
-\begin{proof}
-  Step 1. Fix $\theta \in \mathbb R$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
-  Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  for all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist $C_1,\delta_1>0$ such that, for any $t\geq 0$, $n\geq 1$, we have
-  \begin{align}
-    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]\leq C_1e^{-\delta_1(t+n-1)}.
-  \end{align}
-
-  Step 2.
-  Fix $t\geq 0$ and $m\in \mathbb{N}$.
-  For each $n=0,\cdots,m$, we define
-  \[
-    \widetilde{a}_n
-    := \mathbb{\widetilde{P}}_{\mu}\Big[\prod_{l=0}^{n}\exp(i\theta\bar{\gamma}_{t,l})\Big] \times \prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g]),
-  \]
-  where by convention the first product is $1$ for $n=0$. Then we get for each $n \ge 1$,
-  \begin{align}
-    & \widetilde{a}_{n-1} - \widetilde{a}_n
-      = \mathbb{P}_{ \mu } ( D^c )^{ - 1 } \mathbb{P}_{ \mu } \Big[ \Big( \prod_{ l=0 }^{n - 1 } e^{ i \theta \bar{ \gamma }_{ t, l} } \Big) \times ( e^{ \bar{m}_n [ \theta g ] } - e^{ i \theta \bar{ \gamma }_{t, n}}) ; D^c \Big] \times \prod_{ l = n + 1}^{ m } e^{\bar{ m }_l[ \theta g ] } \\
-    & = \mathbb{ P }_{ \mu }( D^c )^{ - 1 } \mathbb{P}_{ \mu } \Big[ \Big( \prod_{ l = 0 }^{n - 1} e^{ i \theta \bar{ \gamma }_{t, l} } \Big) \times \mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\times \prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
-  \end{align}
-  According to Step 1 and Proposition \ref{prop:PL:S}, there exists $C_2>0$ such that for any $n=1,\cdots, m$ and $t\geq 0$, we have
-  \begin{align}
-    | \widetilde{a}_{n-1}- \widetilde{a}_n|
-    & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
-    \leq C_2 e^{-\delta_1(t+n-1)}.
-  \end{align}
-  Therefore,
-  \begin{align}
-    \text{LHS of \eqref{ineq: next we will need}}
-    & = \left|\widetilde{a}_{0}-\widetilde{a}_m\right|
-      \leq\sum_{n=1}^m\left|\widetilde{a}_{n-1}-\widetilde{a}_n\right|
-      \leq \sum_{n=1}^m C_2 e^{-\delta_1(t+n-1)}.
-  \end{align}
-	Notice that $C_2, \delta_1>0$ are independent of the choice of $t\geq 0$, $m\in \mathbb{N}$.
-\end{proof}
-\end{comment}
 % *** The small branching rate regime
@@
 \begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:1})]
-	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_s$ and $t_0 > 1$ be large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
+	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_s$
+%YX and $t_0 > 1$ be large enough
+    and $t_0 > 1$  large enough
+so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
   For each $t\geq t_0$, in this proof we write $\theta_t = \|X_t\|^{\tilde \beta - 1}$,
@@
   In fact, for each $k \in \mathbb Z_+$, we have  $T_{k} \tilde f \in \mathcal P_{\tilde f}:=\{\theta T_n \tilde f: n \in \mathbb Z_+, \theta \in [-1,1]\}$.
-  Therefore from Proposition \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
+%YX  Therefore from Proposition \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
+    Therefore from Corollary \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
   \begin{align}
@@
   \end{align}
-  On the other hand, using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of semigroup $(P_t)$, we can verify that
+  On the other hand, using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability
+  %YX of semigroup $(P_t)$, we can verify that
+  of the semigroup $(P_t)_{t\geq 0}$, we have
   \begin{align}
@@
   \emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$.
-  In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we can write for each $t\geq t_0$ that
+%YX  In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we can write for each $t\geq t_0$ that
+In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we have that for each $t\geq t_0$,
 \begin{align}
@@
 We claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb Z_+$ and $t\geq k+1$.
-And therefore there exists $C_2'>0$ such that for each $t \geq t_0$, $|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]| \leq C_2't^{-\delta_1}$ which, combines with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
-
-We will show this claim in the following substep 2.1 and 2.2. 
+And therefore there exists $C_2'>0$ such that for each $t \geq t_0$,
+%YX $|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]| \leq C_2't^{-\delta_1}$ which, combines with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
+$|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]-1| \leq C_2't^{-\delta_1}$  which, combining with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
+
+%YX We will show this claim in the following substep 2.1 and 2.2.
+We will show this claim in the following substeps 2.1 and 2.2.
 First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with
@@
 \)
-  In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha $; and therefore for each $k\in \mathbb Z_+$ and $t \geq k + 1$, 
-  \[
+  In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $; and therefore for each $k\in \mathbb Z_+$ and $t \geq k + 1$,
+ \begin{align}
+\label{eq:gammafunction11}
     \Upsilon_{t-k-1}^{T_{k} \tilde f}
@@
     = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f)}{\|e^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
-  \]
+\end{align}
   Since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \in \mathbb Z_+$ and $t\geq k+1$,
@@
 
-% ****** Final step
- 	\emph{Final step}, combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:1}.
+%YX	\emph{Final step}, combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:1}.
+\emph{Final step}. Combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:1}.
 \end{proof}
@@
   	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_c$ and $t_0 > 1$ large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
-    For each $t\geq t_0$, in this proof we write $\theta_t = \|t X_t\|^{\tilde \beta - 1}$; and we define $I_i^f(t)$ for $i = 1,2,3$ using \eqref{eq:PM:CLTS:1}, and set
+%YX    For each $t\geq t_0$, in this proof we write $\theta_t = \|t X_t\|^{\tilde \beta - 1}$; and we define $I_i^f(t)$ for $i = 1,2,3$ using \eqref{eq:PM:CLTS:1}, and set
+ For each $t\geq t_0$, in this proof we write $\theta_t = \|t X_t\|^{\tilde \beta - 1}$,  define $I_i^f(t)$ using \eqref{eq:PM:CLTS:1}  for $i = 1,2,3$, and set
 $
     I^f_0(t)
-    := t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f}
+    := t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f},
 $
-where $\tilde f = e^{\alpha(\tilde \beta - 1)} f$
+where $\tilde f = e^{\alpha(\tilde \beta - 1)} f$.
 
@@
   \end{align}
-  Note that since $f \in \mathcal C_c\setminus \{0\}$, so $T_k \tilde f = \tilde f$ for each $k \in \mathbb Z_+$.
+%YX  Note that since $f \in \mathcal C_c\setminus \{0\}$, so $T_k \tilde f = \tilde f$ for each $k \in \mathbb Z_+$.
+Since $f \in \mathcal C_c\setminus \{0\}$, we have $T_k \tilde f = \tilde f$ for each $k \in \mathbb Z_+$.
   Similar to the argument in \eqref{eq:PM:CLTS:2} we have
-  \[ 
+  \begin{align}
+    \label{CLT:C:eq:m}
     \lim_{t\to \infty} \frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1 T_{k}\tilde f, \varphi\rangle
@@
     = m[f].
-  \]
+  \end{align}
   Therefore $\mathbb {\widetilde P}_\mu[e^{i I^f_0(t)}] \xrightarrow[t\to \infty]{} e^{m[f]}$.
-  Noticing that $I_0^f(t)$ is linear in $f$, the desired result in this step follows.
+%  Noticing that $I_0^f(t)$ is linear in $f$, the desired result in this step follows.
+The desired result in this step follows.
 
@@
   \emph{Step 2.} We show that $ I^f_1(t) - I^f_0 (t) \xrightarrow[t\to \infty]{d} 0$.
-  In fact, similar to the Step 2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we also have \eqref{eq:PM:S:1} is valid with
+%YX  In fact, similar to the Step 2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we also have \eqref{eq:PM:S:1} is valid with
+In fact, similar to Step 2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we  have \eqref{eq:PM:S:1} is valid with
 \(
@@
 \)
-  We also claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb N$ and $t\geq k+1$; and similarly, the desired results in this step follows with this claim.
-
-  We will show this claim in the following substep 2.1 and 2.2. 
+%YX  We also claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb N$ and $t\geq k+1$; and similarly, the desired results in this step follows with this claim.
+Similarly, we claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb N$ and $t\geq k+1$, and  then the desired result in this step follows.
+
+%YX  We will show this claim in the following substep 2.1 and 2.2.
+We  will  show this claim in the following substeps 2.1 and 2.2.
   First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with
@@
 % ******* subStep 2.1
-  \emph{Substep 2.1.} Similar to the substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$,
+  \emph{Substep 2.1.}
+  %YX  Similar to the substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$,
+  Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$,
   \(
@@
   \]
-  The rest is similar to the substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:2}).
+%YX  The rest is similar to the substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:2}).
+The rest is similar to Substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:2}).
   We omit the details.
@@
 \\
-    & \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)(t - \lceil t - \ln t\rceil)}.
+    & \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)(t - \lceil t - \ln t\rceil)}
       \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} t^{\alpha (\tilde \beta - \tilde \gamma)}.
   \end{align}
-  From this and \eqref{Theorem123}, combined with the fact that $I^f_2(t)$ is linear in $f$, we get the desired result in this step.
+%YX  From this and \eqref{Theorem123}, combined with the fact that $I^f_2(t)$ is linear in $f$, we get the desired result in this step.
+From this and \eqref{Theorem123}, we get the desired result in this step.
 
@@
   \emph{Step 4.}
-  Similar to the Step 4 of the Proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+ %YX Similar to the Step 4 of the Proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+ Similar to Step 4 of the Proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
   We omit the details.
@@
 \begin{align}
-  & \frac{X_tf - \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta \geq |p|b} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}H_\infty^p}{\|X_t\|^{1- \tilde \beta}}
+  & \frac{X_t(f) - \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta \geq |p|b} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}H_\infty^p}{\|X_t\|^{1- \tilde \beta}}
     = \sum_{p\in \mathcal N}\frac{ \langle f,\phi_p\rangle_\varphi [X_t(\phi_p) - e^{(\alpha - |p|b)t}H_\infty^p]}{\|X_t\|^{1- \tilde \beta}}
@@
 In fact, since $T_k\tilde f \in \mathcal P_{\tilde f}$ for each $k\in \mathbb Z_+$, from Corollary \ref{cor:MI} we have $\widetilde{ \mathbb P}_\mu[e^{i I_0^f(t)}]\xrightarrow[t\to \infty]{}\exp\{\sum_{k=0}^\infty \langle Z_1T_k(-\tilde f),\varphi\rangle\}$.
-Using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of semigroup $(P_t)_{t\geq 0}$ we can verify that
+Using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability
+%YX of  semigroup $(P_t)_{t\geq 0}$ we can verify that
+of the semigroup $(P_t)_{t\geq 0}$ we have
 \begin{align}
@@
 \end{align}
-Now, combining with the fact that $I_0^f(t)$ is linear in $f$ the result in this step follows.
+%YX Now, combining with the fact that $I_0^f(t)$ is linear in $f$, the result in this step follows.
+The result in this step follows.
 
 \emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$.
-In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we can write for each $t\geq 0$ that $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq \sum_{k=0}^{\lfloor t^2 \rfloor} \widetilde {\mathbb {P}}_\mu[|Y_{t,k}|]$ where $Y_{t,k} := e^{i(\widetilde {\Upsilon}_{t,k} - \Upsilon_{t+k}^{-T_{k}\widetilde {f}})} - 1.
+%YX In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we can write for each $t\geq 0$ that
+    In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we have, for each $t\geq 0$, that
+ $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq \sum_{k=0}^{\lfloor t^2 \rfloor} \widetilde {\mathbb {P}}_\mu[|Y_{t,k}|]$ where $Y_{t,k} := e^{i(\widetilde {\Upsilon}_{t,k} - \Upsilon_{t+k}^{-T_{k}\widetilde {f}})} - 1.
 $
 We claim that there exist $C_2, \delta_2>0$ such that $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|] \leq C_2e^{-\delta_2 t}$ for each $t\geq 0$ and $k \in \mathbb Z_+$.
-And therefore $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq (t^2+1)C_2e^{-\delta_2 t}$ which, combined with the fact that $I_1^f(t) - I_0^f(t)$ is linear in $f$, completes this step.
-
-We will show this claim in the following substeps 2.1 and 2.2.
-First we chose $\gamma\in(0,\tilde \beta)$ close enough to $\beta$ so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$; and even closer so that there exists $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
+And therefore $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq (t^2+1)C_2e^{-\delta_2 t}$
+%YX which, combined with the fact that $I_1^f(t) - I_0^f(t)$ is linear in $f$, completes this step.
+which completes this step.
+
+%YX We will show this claim in the following substeps 2.1 and 2.2.
+ We will show this claim in the following Substeps 2.1 and 2.2.
+%YX First we chose $\gamma\in(0,\tilde \beta)$ close enough to $\beta$
+First we chose $\gamma\in(0, \beta)$ close enough to $\beta$
+so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$; and even closer so that there exists $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
 We also define $\mathcal{D}_{t,k} :=\{|H_t-H_{t+k}|\leq  e^{-\eta t}, H_{t}> 2e^{-\eta' t}\}$.
@@
   = \frac{X_{t+k}(P^\alpha_1T_k\tilde f) - X_{t+k+1}(T_k \tilde f)}{\|X_{t+k}\|^{1 - \tilde \beta}}
-  \\& = \sum_{p}\langle\tilde f,\phi_p\rangle_\varphi e^{-(\alpha \tilde \beta - |pb|)k}\frac{ X_{t+k}(P_1^\alpha \phi_p) - X_{t+k+1}(\phi_p)}{\|X_{t+k}\|^{1 - \tilde \beta}}
-  \\& = \sum_{p}\langle f,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t}\frac{H_{t+k}^p-H_{t+k+1}^p }{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}}. 
+ %YX \\& = \sum_{p}
+ \\& = \sum_{p\in \mathcal N}
+  \langle\tilde f,\phi_p\rangle_\varphi e^{-(\alpha \tilde \beta - |pb|)k}\frac{ X_{t+k}(P_1^\alpha \phi_p) - X_{t+k+1}(\phi_p)}{\|X_{t+k}\|^{1 - \tilde \beta}}
+%YX   \\& = \sum_{p}
+ \\& = \sum_{p\in \mathcal N}
+  \langle f,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t}\frac{H_{t+k}^p-H_{t+k+1}^p }{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}}.
 \end{align}
@@
  &|Y_{t,k}| \mathbf 1_{\mathcal D_{t,k}}
-  \leq \Big( \sum_{p\in \mathcal N}\langle f,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)\mathbf 1_{\mathcal D_{t,k}}.
-  \\ &= \Big( \sum_{p\in \mathcal N}\langle f,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big)e^{\alpha (\tilde \beta - 1)t} K_{t,k}
-  \\ &= \Big( \sum_{p\in \mathcal N}\langle f,\phi_p\rangle_\varphi  e^{(\alpha \tilde \beta  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) K_{t,k},
+  \leq \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)\mathbf 1_{\mathcal D_{t,k}}.
+    \\ &= \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big)e^{\alpha (\tilde \beta - 1)t} K_{t,k}
+  \\ &= \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) K_{t,k},
 \end{align}
@@
 \]
-Similar to the substep 2.2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that for all $k\in \mathbb Z_+$ and $t\geq 0$, almost surely $K_{t,k} \leq C_{2.2}'' e^{- (\eta - 3\eta')t}$.
-From this and Lemma \ref{lem: control of wt} we know that there exists $C'''_{2.2}$ for each $k\in \mathbb Z_+$ and $t\geq 0$,
+%YX Similar to the substep 2.2 of
+Similar to Substep 2.2 of
+the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that for all $k\in \mathbb Z_+$ and $t\geq 0$, almost surely $K_{t,k} \leq C_{2.2}'' e^{- (\eta - 3\eta')t}$.
+From this and Lemma \ref{lem: control of wt} we know that there exists $C'''_{2.2}$ such that for each $k\in \mathbb Z_+$ and $t\geq 0$,
 \begin{align}
@@
   \leq \mathbb P_\mu(D)^{-1}\mathbb P_\mu[ |Y_{t,k}| ;\mathcal D_{t,k} ]
-  \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} \langle f,\phi_p\rangle_\varphi  e^{(\alpha \tilde \beta  -|p|b)t} \mathbb P_\mu[| H_{t+k}^p-H_{t+k+1}^p |]
-  \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} \langle f,\phi_p\rangle_\varphi  e^{(\alpha \tilde \beta  -|p|b)t} \| H_{t+k}^p-H_{t+k+1}^p \|_{\mathbb P_\mu; 1+\gamma}
-  \\&\leq  \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal N} \langle f,\phi_p\rangle_\varphi  e^{(\alpha \tilde \beta  -|p|b)t} e^{-(\alpha \tilde \gamma - |p|b)(t+k)} \\
+  \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} |\langle f,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} \mathbb P_\mu[| H_{t+k}^p-H_{t+k+1}^p |]
+  \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} |\langle f,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} \| H_{t+k}^p-H_{t+k+1}^p \|_{\mathbb P_\mu; 1+\gamma}
+  \\&\leq  \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal N} |\langle f,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} e^{-(\alpha \tilde \gamma - |p|b)(t+k)} \\
   &  \leq  C_{2.2}''' e^{- (\eta - 3\eta') t} e^{(\alpha \tilde \beta - \alpha \tilde \gamma)t},
@@
    \leq \sum_{k = \lceil t^2\rceil}^\infty \widetilde {\mathbb {P}}_\mu[ |\widetilde {\Upsilon}_{t,k}|; \mathcal {E}_t]
-  \\ & \leq \mathbb P_\mu(D^c)^{-1} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\mathbb {P}_\mu\Big[\frac{ |H_{t+k}^p - H_{t+k+1}^p|}{\|X_t\|^{1- \tilde \beta}}; \mathcal E_t\Big]
-  \\ & \leq \mathbb P_\mu(D^c)^{-1} e^{(\alpha - \epsilon) (\tilde \beta - 1) t} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\|H_{t+k}^p - H_{t+k+1}^p\|_{\mathbb P_\mu; 1+\gamma}
-  \\ & \leq C_3' e^{(\alpha - \epsilon) (\tilde \beta - 1) t} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t} e^{- (\alpha \tilde \gamma - |p|b)(t+k)}
+  \\ & \leq \mathbb P_\mu(D^c)^{-1} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} |\langle f,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t}\mathbb {P}_\mu\Big[\frac{ |H_{t+k}^p - H_{t+k+1}^p|}{\|X_t\|^{1- \tilde \beta}}; \mathcal E_t\Big]
+  \\ & \leq \mathbb P_\mu(D^c)^{-1} e^{(\alpha - \epsilon) (\tilde \beta - 1) t} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} |\langle f,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t}\|H_{t+k}^p - H_{t+k+1}^p\|_{\mathbb P_\mu; 1+\gamma}
+  \\ & \leq C_3' e^{(\alpha - \epsilon) (\tilde \beta - 1) t} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} |\langle f,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t} e^{- (\alpha \tilde \gamma - |p|b)(t+k)}
   \\ & = C_3'' e^{ \alpha (\tilde \beta - \tilde \gamma) t } e^{ \epsilon (1 - \tilde \beta) t}e^{- \delta'_3 t^2}.
 \end{align}
-To sum up we have that $\widetilde {\mathbb P}_\mu[e^{iI_2^f(t)}] \xrightarrow[t\to \infty]{} 1$, which combined with the fact that $I_2^f(t)$ is linear in $f$, completes this step.
+To sum up we have that $\widetilde {\mathbb P}_\mu[e^{iI_2^f(t)}] \xrightarrow[t\to \infty]{} 1$,
+%YX which combined with the fact that $I_2^f(t)$ is linear in $f$, completes this step.
+which completes this step.
 
@@
   Therefore,
-\begin{equation}
+%YX \begin{equation}
+$
 |e^{-z} - 1|
@@
   \leq |z|.
-\end{equation}
+%YX \end{equation}
+$
 Also, notice that $|e^{-z} - 1| \leq |e^{-z}|+1 \leq 2$.
@@
 
-% It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
 It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the Gamma function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
@@
 \end{equation}
-% are (i)  extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$; (ii) holomorphic on $\mathbb C_+^0$ and (iii) continuous on $\mathbb C_+$.
-% Similarly, we get that
 and similarly that
@@
   C. C. Heyde,
-  % \emph{some central limit analogues for supercritical {g}alton-{w}atson processes}, 
     \emph{some central limit analogues for supercritical {G}alton-{W}atson processes},

### 2019-09-02 supCLT.tex
change supCLT.tex

@@
   University of Illinois at Urbana-Champaign \\
-  % Urbana, IL 61801, USA}
   Urbana, IL, USA, 61801}
@@
 \begin{abstract}
-  Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$.
-  Let $\psi$ be a branching mechanism which is close to a function of the form $\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-  In this paper, we study asymptotic behaviors of $(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$.
-  For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$.
-  Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
-  the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$;
-  the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$;
-  and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
+  % ADDED
+  In this paper, we study the asymptotic behaviors of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$
+  % Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$.
+  whose underlying spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ where $\sigma, b >0$;
+  % Let $\psi$ be a branching mechanism which is close to a function of the form $\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense.
+  and whose branching mechanism $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that, while $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
+  % In this paper, we study asymptotic behaviors of $(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$.
+  Some law of large numbers and $(1+\beta)$-stable central limit theorems are established for $(\langle f, X_t\rangle )_{t\geq 0}$ where the testing function $f$ is assumed to be of polynomial growth.
+  % Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
+  % the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$;
+  % the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$;
+  % and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
+  A phase transition arises for the central limit theorems in the sense that three different type of results can be obtained which correspond to whether the branching rate $\alpha$ is relatively small, large or at a critical balanced value.
 \end{abstract}
@@
   \label{eq: honogeneou branching mechanism}
-  \psi(z)=
-  - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy)
+  \psi(z)
+  =- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy)
   , \quad  z \in \mathbb R_+,
@@
 $
-We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ on a measurable space $(\Omega, \mathcal{F})$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$ superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ 
+% on a measurable space $(\Omega, \mathcal{F})$ 
+on a measurable space $(\Omega, \mathscr{F})$ 
+is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
 \begin{align}
@@
 In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
-Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-And the general goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
+% Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
+Our key assumption is that the branching mechanism $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that, while $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
+The general goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
 Note that, in the setting of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
@@
 Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
-Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
-The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
+Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
+The functional version of the CLTs was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
 
 There are also many limiting theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moments.
-Heyde \cite{Heyde1971Some} established a central limit type  theorem for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit law is  a stable law.
+Heyde \cite{Heyde1971Some} established some  CLTs for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit laws are stable laws.
 Similar results  for supercritical multi-type GW processes and supercritical continuous time branching processes,
@@
 Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable branching law.
-They established some spatial central limit theorems in the small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
+They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
 We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.
@@
 
+% *** Main results
 \subsection{Main results}
@@
 For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
-It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event} $D :=\{\exists t\geq 0,~\text{s.t.}~ \|X_t\| =0 \}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
-In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ for each $\mu\in \mathcal M(\mathbb R^d)$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
+It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event} $D :=\{\exists t\geq 0,~\text{s.t.}~ \|X_t\| =0 \}$ has positive probability with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
+% In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ for each $\mu\in \mathcal M(\mathbb R^d)$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
+In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
 
@@
 In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
-
-\begin{rem}
-  \label{rem: small enough delta}
 	Note that $\delta$ is not uniquely determined by $\pi$.
@@
 	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
+
+\begin{rem}
+  \label{rem:SP}
+% Assumption \ref{asp: branching mechanism} says that there exist constants $\eta>0$ and $\beta > 0$ such that the L\'evy measure $\pi(dy)$ is ``not too far away'' from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
+Roughly speaking, Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is ``not too far away from $\widetilde \psi(z) := - \alpha z + \eta z^{1+\beta}$ near $0$''.
+ % In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of $-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
+In fact, if we consider their differences
+\begin{align}
+  \label{eq:PB}
+  & \psi_1(z)
+  := \psi(z) - \widetilde \psi(z)
+  \\ &= \rho z^2+ \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta) y^{2+\beta}}\Big),
+  \quad z\geq 0,
+\end{align}
+then it can be verified that (see Lemma \ref{lem:CEP} below) $\psi_1(z)/z^{1+\beta} \xrightarrow[z\to 0]{} 0$.
+Therefore, we can write $ \psi(z)  = - \alpha z + z^{1+\beta}(\eta + o(1))$ as $z\to 0$.
+One can further write that $\psi(z) = - \alpha z + z^{1+\beta} l(z)$ where $l$ is a function on $[0,\infty)$ which is slowly varying at $0$.
+% END ADDED
 \end{rem}
 
-Assumption \ref{asp: branching mechanism} says that there exist constants $\eta>0$ and $\beta > 0$ such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
-In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of $-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
+\begin{rem}
 It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y~\pi(dy) < \infty.
@@
 This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
-
+\end{rem}
 % **** Mean semigroup
+% ADDED
+Let us introduce some notation in order to give a precise formulation of our main result.
+% END ADDED
 Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
@@
 Define
-\begin{align}
-  \label{eq: meansemigroup}
+\(  
 P^{\alpha}_t f(x)
-  :=
-  e^{\alpha t} P_t f(x)
+  := e^{\alpha t} P_t f(x)
   = \Pi_x [e^{\alpha t}f(\xi_t)]
-  , \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
-\end{align}
-It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
-\begin{equation}
+\)
+for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
+It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$ in the sense that
+\( 
   \mathbb{P}_{\mu}[\langle f, X_t \rangle]
   = \langle P^\alpha_t f, \mu \rangle,
-  \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
-\end{equation}
-The limiting behavior of the super-OU process is closely related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.
+\)
+for each $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
+% The limiting behavior of the super-OU process is closely related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.
 
 % **** Spectral Property
-We now recall some basic spectral properties of $(P_t)_{t\geq 0}$ from \cite{MetafunePallaraPriola2002Spectrum}.
-It is known that the OU process $\xi$ has an invariant density
+The limiting behavior of the super-OU process is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
+% It is known that the OU process $\xi$ has an invariant density
+It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
 \begin{align}
@@
   \varphi(x)dx
-  :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
-  \quad x\in \mathbb R^d.
-\end{align}
-Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$.
-Then $L^2(\varphi)$ is a Hilbert space with inner product
+  :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx
+  % \quad x\in \mathbb R^d.
+\end{align}
+which is a   symmetric multivariate Gaussian distribution.
+% Let \[L^2(\varphi):= \Big\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \Big\}.\]
+% Then $L^2(\varphi)$ is a Hilbert space with inner product
+Let $L^2(\varphi)$ be the Hilbert space with inner product
 \begin{align}
@@
 It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
-For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
-$
-\mathcal{A}_k
-= \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
-$
-where
+For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$, where
 \begin{align}
@@
 In other words,
-\begin{equation}
+\(  
   P_t\phi_p(x)
-  =e^{-b|p|t}\phi_p(x),
-  \quad t\geq 0, x\in \mathbb R^d, p\in \mathbb Z_+^d.
-\end{equation}
+  = e^{-b|p|t}\phi_p(x)
+\)
+for each $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
 Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
 Thus for each $f\in L^2(\varphi)$, we have
-\begin{equation}
+\begin{align}
   \label{semicomp1}
   f
-=\sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
+  = \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
   , \quad \text{in~} L^2(\varphi).
-\end{equation}
-For each function $f\in L^2(\varphi)$, denote by
-\begin{equation}
+\end{align}
+For each function $f\in L^2(\varphi)$, define the order of $f$ as
+\[
   \kappa_f
-  :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \},
-\end{equation}
-the order of the function $f$ in the spectral decomposition \eqref{semicomp1}.
-$\kappa_f$ corresponds to the lowest non-trivial frequency in the eigen-expansion of $f$.
+  := \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
+\]
+which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
 Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
@@
 For each $p\in \mathbb{Z}_+^d$, define
-  \[
+\(
   H_t^p
-    := e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,
-    \quad t\geq 0.
-  \]
+  := e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle
+\)
+with $t\geq 0$.
 If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lem:M:L:ML} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
@@
 Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
-\begin{equation}
+\begin{align}
   \label{eq: polynomial growth function}
   \mathcal{P}
-  :=\big \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists~ C>0, n \in \mathbb Z_+, {\rm such  \, \, that \, } \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
-\end{equation}
+  := \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
+\end{align}
 It is clear that $\mathcal{P} \subset L^2(\varphi)$.
@@
 Hence, Theorem \ref{thm: law of large number} says that for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
-\[
+\(
   e^{-\alpha t}\langle f, X_t\rangle
   \rightarrow \langle f, \varphi\rangle H_{\infty}
-  \quad \mbox{in } L^{1+\gamma}(\mathbb{P}_{\mu}).
-\]
-Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have a.\/s.\ convergence.
-However, to get  a.\/s.\ convergence for bounded non-negative
-Lebesgue-a.\/e.\/\ continuous functions $f$, we do not need $f$ to be twice differentiable.
+\)
+in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have a.s.\ convergence.
+However, to get a.s.\ convergence for bounded non-negative
+Lebesgue-a.e.\ continuous functions $f$, we do not need $f$ to be twice differentiable. 
 See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
@@
 % **** Stable CLT
-For the rest of this subsection, we focus on the central limit theorems of $\langle f, X_t\rangle$ for $f\in \mathcal P\setminus \{0\}$.
+% For the rest of this subsection, we focus on the central limit theorems of $\langle f, X_t\rangle$ for $f\in \mathcal P\setminus \{0\}$.
+For the rest of this subsection, we focus on the central limit theorems of $\langle f, X_t\rangle$ for some $f\in \mathcal P\setminus \{0\}$.
 Write $\tilde u = \frac{u}{ 1+ u}$ for each $u \neq -1$.
-It turns out that the fluctuation behaviors vary with the following three cases:
+It turns out that there is a phase transition in the sense that the results are different in the following three cases:
 \begin{enumerate}
@@
 large) branching means that the branching rate $\alpha$ is relatively small (rspt.
-relatively large) and the critical branching means that the branching rate $\alpha$ is at a balanced value.
-To present our result we need to define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
+relatively large); and the critical branching means that the branching rate $\alpha$ is at a critical balanced value.
+To present our result, let us define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
 \begin{align}
@@
     \lim_{t\to \infty} m_t[f], &
-    %YX f \in \mathcal C_s \oplus \mathcal C_l \setminus \{0\}\\
     f \in \mathcal C_s \oplus \mathcal C_l, \\
@@
 is well defined, and moreover, there exists an $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}$.
+Let us now give the main results of this paper.
+
 \begin{thm}
@@
   \label{thm:M:2}
-  if $f\in \mathcal C_c\setminus\{0\}$, then
-  \(
-    \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f)
-    \xrightarrow[t\to \infty]{d}
-    \zeta^f;
-    \)
+  if $f\in \mathcal C_c\setminus\{0\}$, then $ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$; 
 \item
@@
 
-%\subsection{Some intuitive explanation}
+% ADDED
+At this point, we should mention that the CLTs above did not cover for all polynomial growth testing functions $f\in \mathcal P$.
+Indeed, considering a general $f \in \mathcal P$ which can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c\setminus\{0\}$ and $f_l \in \mathcal C_l$, as a simple corollary of Theorem \ref{thm:M}, one can verify that
+\[
+  \|tX_t\|^{-\frac{1}{1+\beta}} \Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big)
+  \xrightarrow[t\to \infty]{d}
+  \zeta^{f_c}
+\]
+for each $\mathbb P_\mu(\cdot | D^c)$ with $\mu \in \mathcal M_c(\mathbb R^d)\setminus \{0\}$.
+However, in the case that $f_c\equiv 0$, $f_s\not \equiv 0$ and $f_l\not \equiv 0$, it seems hard to establish any non-trivial CLTs for $X_t(f)$ using the methodology of this paper.  
+In general, we conjecture that under the condition of Theorem \ref{thm:M} the random vector
+\begin{align}
+  \|X_t\|^{- \frac{1}{1+\beta}} \Big( X_t(f_s) ,t X_t(f_c),  X_t(f_l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} \Big)
+\end{align}
+convergences in distribution to $(\zeta^{f_s},\zeta^{f_c}, \zeta^{-f_l})$ where $\zeta^{f_s}$, $\zeta^{f_c}$ and $\zeta^{-f_l}$ are independent.
+Similar convergence has already been proved under the second moment condition, see \cite{RenSongZhang2015Central}.
+
+Let us now give some intuitive explanation of this phase transition. 
+First we mention that the super-OU process arises as the ``high density'' limit of the superposition of a sequence of branching-OU processes, see \cite{Li2011Measure-valued} for example.
+And similar phase transition have already been discussed in the context of branching-OU processes, see \cite{MarksMilos2018CLT}. 
+Though it is hard to describe rigorously, one can consider superprocess as a branching particle system with infinitely many infinitesimal particles, and we employ this particle picture only for the sake of this interpretation.
+It is believed that this phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing. 
+The coarsening effect corresponds to the increasing of the spatial inequality and is a consequence of the branching: simply an area with more particles will produce more offspring.
+The smoothing effect corresponds to the decreasing of the spatial inequality and is a consequence of the mixing property of the OU processes: each OU particles will ``forget'' its initial position exponentially fast.
+
+Let us consider $X_t(\phi_p)$ as an example, and discuss how parameters $\alpha, \beta, b$ and $|p|$
+influences those two effects:
+\begin{itemize}
+\item
+  The branching rate $\alpha$ captures the mean intensity of the branching in the system. 
+  Therefore, lager the branching rate $\alpha$, stronger the coarsening effect.
+\item
+  The tail index $\beta$ describes the heaviness of the tail of the offspring numbers which belongs to the attraction of some $(1+\beta)$-stable random variable. 
+When $\beta$ is smaller i.e. the tail is heavier, then it is more likely that an area with few particles can suddenly have a large amount of offspring. 
+In other words, larger the tail index $\beta$, stronger the coarsening effect. 
+\item
+  The drift parameter $b$ captures the level of the mixing property of the OU particles.
+  Larger the drift parameter $b$, faster the OU-particles forgetting their initial position, and therefore stronger the smoothing effect.
+\item
+  The order $|p|$ describes the ability of the testing function $\phi_p$ while capturing the mixing property of the OU particles. 
+  In particular, in the case that $|p| = 0$, no mixing property can be captured by $\phi_p \equiv 1$ since we are only considering the total mass $\|X_t\|$. 
+  In general, higher the order $|p|$, more mixing property can be captured by the testing function $\phi_p$, and therefore stronger the smoothing effect.
+\end{itemize} 
+We also discuss the role of other parameters $\rho, \eta$ and $\sigma$ in our model:
+\begin{itemize}
+\item
+  The coefficient $\rho$ dose not influences the results since the second term $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$ (See Remark \ref{rem:SP}). 
+\item
+  The coefficients $\eta$ and $\sigma$ are hidden in the definition of the functional $m[f]$, and therefore influence the actual distribution of the limiting $(1+\beta)$-stable random variable $\xi^f$.
+  Their role in the coarsening and smoothing effects are negligible compared to the four parameters $\alpha, \beta, b$ and $|p|$ mentioned above.
+\end{itemize}
+% END ADDED
+
+% *** An outline of the methodology
 \subsection{An outline of the methodology}
-Here we give some intuitive explanation of the central limit theorems above.
-The main ideas are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
+% Here we give some intuitive explanation of the central limit theorems above.
+Let us give some intuitive explanation of the methodology used in this paper.
+% Deleted
+% The main ideas are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
+% End delted
 For any $\mu\in \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
-\begin{equation}
-  \label{Ist}
+$
   \mathcal I_s^t Y
   := \mathcal I_s^t [Y, \mu]
-  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s],
-  \quad 0 \leq s \leq t <\infty.
-\end{equation}
+  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s]
+$
+  where $0 \leq s \leq t <\infty.$
 We will use the shorter notation $\mathcal I_s^t Y$ when there is no danger of confusion.
@@
 \begin{align}
-  \langle f,X_t\rangle
-  := \sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle+\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle + \langle P^\alpha_tf,X_0\rangle,
+  % \langle f,X_t\rangle
+  X_t(f)
+  := \sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k} X_t (f)+\mathcal I_0^{t-\lfloor t \rfloor} X_t(f) + X_0( P^\alpha_tf),
   \quad t\geq 0.
@@
 To find the fluctuation of $\langle f,X_t\rangle$, we will investigate the fluctuation of each term on the right hand side above.
-
-Recall $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
-Theorem \ref{lem:PR:LC}, Corollary \ref{cor:MI} and \eqref{eq:gammafunction11} below imply that if $\alpha \tilde \beta \leq \kappa_f b$ then
-\[
-  \bigg(\frac{\mathcal I^{t-k}_{t-k-1} \langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}} \bigg)_{k=1}^n
-  \xrightarrow [t\to \infty]{d} (\zeta_k)_{k=1}^n,
-\]
-where $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables with characteristic functions $\theta\mapsto \exp( \langle Z_1T_k\tilde f,\varphi  \rangle)$ and $\tilde f:=e^{\alpha(\tilde \beta -1)}f$.
-So if $f\in \mathcal C_s$, i.e., $\alpha \tilde \beta < \kappa_f b$, we have roughly that
-\[
-  \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-  \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}\sum_{k=0}^\infty \zeta_k,
-\]
-where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp(m[\theta f])$, with $m[\theta f]$ given by \ref{eq:I:R:3}.
+% DELETED
+% Recall $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
+% END DELETED
+The second term and third term are negligible after the rescaling, and for the first term we will establish some multi-variant unite-interval CLTs which says that
+\[
+  \Big( \|X_t\|^{-\frac{1}{1+\beta}}\mathcal I^{t-k}_{t-k-1} X_t(f) \Big)_{k=0}^n
+  \xrightarrow [t\to \infty]{d} (\zeta^f_k)_{k=0}^n,
+\]
+where $(\zeta_k)_{k \in \mathbb N}$ are some independent $(1+\beta)$-stable random variables.
+% So if $f\in \mathcal C_s$, i.e., $\alpha \tilde \beta < \kappa_f b$, we have roughly that
+% \[
+%  \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
+%  \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}\sum_{k=0}^\infty \zeta_k,
+% \]
+If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \xi^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have 
+\(
+  \|X_t\|^{-\frac{1}{1+\beta}}  X_t(f) 
+  \xrightarrow[t\to \infty]{d} \zeta^f.
+  \)
+If $f \in \mathcal C_c \setminus \{0\}$, then it can be argued that 
+\(
+t^{-\frac{1}{1+\beta}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{ d} \zeta^f
+\)
+and then intuitively we have 
+\(
+\|tX_t\|^{-\frac{1}{1+\beta}}  X_t(f) 
+\xrightarrow[t\to \infty]{d} \zeta^f.
+\)
+% DELETED
+\begin{comment}
 In the explanation above, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined, and
@@
 If $f\in \mathcal C_c$, i.e., $\alpha \tilde \beta = \kappa_f b$,
-%YX then the right hand side of \eqref{eq: equatlity for mf for small rate} may not converge.
-%YX Instead, see \eqref{CLT:C:eq:m} below, there is another quantity $m[f]$ satisfying that
 then
@@
   m[f]
-  = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}\langle Z_1 T_k \tilde f,\varphi \rangle,\quad f\in \mathcal C_c.
+  = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}\langle Z_1 T_k \tilde f,\varphi \rangle, \quad f\in \mathcal C_c.
 \]
@@
 \]
-%YX where $\zeta$ is another $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp( m[\theta f])$.
 where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp( m[\theta f])$.
-
-For $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
-%Taking $f = \phi_p$ with $\alpha \beta > |p|b(1+\beta)$ as an example, we do the following decomposition:
+\end{comment}
+% END DELETED
+% For $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
+If $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
+\begin{comment}
 Taking $f = \phi_p$ with $\alpha \tilde \beta > |p|b$ as an example, we do the following decomposition:
@@
 These lemmas will eventually lead us to the fluctuation result in the large branching rate regime.
-
-%YX For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$,
+\end{comment}
+
+\begin{comment}
 For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$ with $f_l\in\mathcal C_l$, $f_c\in\mathcal C_c$ and $f_s\in\mathcal C_c$.
@@
 We leave the question of independence for stable branching mechanism to a future project.
+\end{comment}
 
@@
 Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z +\eta z^{1+\beta}$ plus a small perturbation
-\begin{align}
-  \label{eq: psi 1}
-	\psi_1(z)
-	& := \rho z^2+ \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta) y^{2+\beta}}\Big)
-\end{align}
-where $\psi_1$ satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
+%\begin{align}
+%  \label{eq:PB}
+%	\psi_1(z)
+%	& := \rho z^2+ \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta) y^{2+\beta}}\Big)
+%\end{align}
+$\psi_1(z)$
+% where $\psi_1$ satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
+which satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
 It would be interesting to consider more general branching mechanisms.
@@
 In Subsection \ref{sec: large rate lln}, we will give the proof of Theorem \ref{thm: law of large number}.
-%YX In Subsection \ref{sec:critical}, we will give the proof of Theorem \ref{thm:M}.
 In Subsections \ref{sec:critical}--\ref{sec: large rate clt}, we will give the proof of Theorem \ref{thm:M}.
@@
 This fact will be used at several places in this paper, and we think it is of independent interest.
-\begin{comment}
-  We end this section with a list of frequently used notations:
-  \begin{itemize}
-  \item
-    $\varphi$ and $\phi_p$ are given in \eqref{invariantdensity} and \eqref{eigenfunction}, respectively.
-  \item
-    $P_t$, $P^\alpha_t$, $V_t$ and $U_t$ are given in \eqref{eq: meansemigroup}, \eqref{eq: meansemigroup}, \eqref{eq: def of V_t}, \eqref{eq: def of U_t}, respectively.
-  \item
-    $\mathcal N$, $K$, $\mathcal C_l$ and $I_t$ are given in \eqref{eq: def of N}, \eqref{eq: def of N},  \eqref{eq: def of Cl} and \eqref{definition of Itf}, respectively.
-  \item
-    $\psi$, $\psi_1$ and $\psi_0$ are given in \eqref{eq: honogeneou branching mechanism}, \eqref{eq: psi 1} and \eqref{eq: psi 0}, respectively.
-  \item
-    $\Psi$, $\Psi_1$ and $\Psi_0$ are given in \eqref{eq: def of operator Psi}.
-  \item
-    $Z_t$, $Z'_t$, $Z''_t$ and $Z'''_t$ are given in \eqref{eq: def of Zf}.
-  \item
-    $Q_\kappa$ and $Q$ are given in \eqref{eq:Q} and \eqref{Q}, respectively.
-  \item
-    $m_t[f]$, $\bar m_t[f]$, $m[f]$, $\widetilde m[f]$ and $\bar m[f]$ are given in Lemma \ref{lem: def of all m}.
-  \end{itemize}
-\end{comment}
-
+
+% ** Preliminaries
 \section{Preliminaries}
+% *** Branching mechanisms
 \subsection{Branching mechanism}
@@
 \begin{lem}
-  \label{lem: complex extension for psi1}
-	The function $\psi_1$ given by \eqref{eq: psi 1} can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
-  Moreover, for each $\delta > 0$ small enough, there exists $C>0$ such that for all $z\in \mathbb C_+$, we have
-  $
-	|\psi_1(z)| \leq C |z|^{1+\beta+\delta} + C|z|^2.
-  $
+  \label{lem:CEP}
+	The function $\psi_1$ given by \eqref{eq:PB} can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
+  Moreover, for each $\delta > 0$ small enough, there exists $C>0$ such that for all $z\in \mathbb C_+$, we have $|\psi_1(z)| \leq C |z|^{1+\beta+\delta} + C|z|^2.$
 \end{lem}
 \begin{proof}
-  According to Lemma \ref{lem: extension lemma for branching mechanism} below and the uniqueness of holomorphic extensions,
-	we know that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
+  According to Lemma \ref{lem: extension lemma for branching mechanism} below and the uniqueness of holomorphic extensions, we know that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
 	The extended $\psi_1$ has the following form:
@@
   \]
-	Now, according to  Assumption \ref{asp: branching mechanism} and Remark \ref{rem: small enough delta}, for each small enough $\delta > 0$, we have
+	% Now, according to  Assumption \ref{asp: branching mechanism} and Remark \ref{rem: small enough delta}, for each small enough $\delta > 0$, we have
+	Now, according to  Assumption \ref{asp: branching mechanism}, for each small enough $\delta > 0$, we have
   \begin{align}
@@
 	In other words, if we denote by $\widetilde \pi(dy)$ the measure $\eta' \Gamma(-1-\beta)^{-1} y^{-2-\beta'} dy$, then $\widetilde \pi$ is a L\'evy measure which satisfies Assumption \ref{asp: branching mechanism}.
-	Applying Lemma \ref{lem: complex extension for psi1} to this measure $\widetilde \pi$, we have that there exists $c>0$ such that
+	Applying Lemma \ref{lem:CEP} to this measure $\widetilde \pi$, we have that there exists $c>0$ such that
   \[
@@
 
+% *** Definition of controller 
 \subsection{Definition of controller}
@@
 
-% \subsection{h-controller for super-OU processes}
+% *** Controllers for the super-OU processes
 \subsection{Controllers for the super-OU processes}
@@
 Define $\psi_0(z) = \psi(z) + \alpha z$ for each $z\in \mathbb{R}_+$.
-According to Lemma \ref{lem: complex extension for psi1}, $\psi, \psi_1$ and $\psi_0$ can all be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are also holomorphic on $\mathbb C^0_+$.
-For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define
-$\Psi f (x) = \psi\circ f(x)$, $\Psi_0 f(x)= \psi_0 \circ f(x)$ and $\Psi_1 f(x)= \psi_1 \circ f(x)$.
-
-For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let
-  \(
-    U_tf(x)
-  := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}
-\)
-be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
+According to Lemma \ref{lem:CEP}, $\psi, \psi_1$ and $\psi_0$ can all be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are also holomorphic on $\mathbb C^0_+$.
+For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi f (x) = \psi\circ f(x)$, $\Psi_0 f(x)= \psi_0 \circ f(x)$ and $\Psi_1 f(x)= \psi_1 \circ f(x)$.
+
+For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let $ U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1} $ be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
 (See the paragraph after Lemma \ref{lem: Lip of power function}.)
@@
   & \qquad Z'_t f
-    := \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,\\
-   Z''_t f
+    := \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,
+  \\ Z''_t f
   := \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
-    &\qquad\  Z'''_t f
+  & \qquad\  Z'''_t f
     := (Z'_t - Z_t+ Z''_t)f.
@@
 Then we have that
-\begin{equation}
+\begin{align}
   \label{eq: key equality}
@@
   , \quad t\geq 0.
-\end{equation}
+\end{align}
 For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-\begin{equation}
+\begin{align}
   \label{eq:Q}
@@
   := Q_{\kappa_f}f.
-\end{equation}
+\end{align}
 Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
@@
   Under Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}, the following statements are true:
-  \begin{itemize}
-  \item[(1)]
+  \begin{enumerate}
+  \item
     $(-U_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
-  \item[(2)]
+  \item
     $(P^\alpha_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable on $\mathcal P^*$.
-  \item[(3)]
+  \item
     $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-  \item[(4)]
+  \item
     $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item[(5)]
+  \item
     $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item[(6)]
+  \item
     For any $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item[(7)]
+  \item
     For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \end{itemize}
+  \end{enumerate}
 \end{lem}
@@
   (1). According to \eqref{eq: -v has positive real part}, $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
-  It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$, we have
-  \(
-    |U_t g(x)|
-    \leq \sup_{0\leq u\leq 1}P_u^\alpha |g| (x).
-  \)
+  It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$, we have $ |U_t g(x)| \leq \sup_{0\leq u\leq 1}P_u^\alpha |g| (x). $
   We claim that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a map from $\mathcal P^+$ to $\mathcal P^+$. In fact, if $f\in \mathcal P^+$, there exists constant $c>0$ such that
@@
   (3).
-By Lemma \ref{lem: complex extension for psi1}, there exist $C, \delta >0$ satisfying $\beta+\delta< 1$ such that for all $ f \in \mathcal P^* \cap \mathcal B( \mathbb R^d, \mathbb C_+ )$, it holds that
-\(
-|\Psi_0 f|
-      \leq \eta |f|^{1+\beta} + |\Psi_1 f|
-      \leq \eta |f|^{1+\beta} + C|f|^2+ C |f|^{1+\beta + \delta}.
-\)
+By Lemma \ref{lem:CEP}, there exist $C, \delta >0$ satisfying $\beta+\delta< 1$ such that for all $ f \in \mathcal P^* \cap \mathcal B( \mathbb R^d, \mathbb C_+ )$, it holds that $ |\Psi_0 f| \leq \eta |f|^{1+\beta} + |\Psi_1 f| \leq \eta |f|^{1+\beta} + C|f|^2+ C |f|^{1+\beta + \delta}.$
   Note that operator
@@
 
-  (4).
-  From (1)--(3) above and Lemma \ref{lem: property of controllable operators}.(1), we know that the operators
+  (4). From (1)--(3) above and Lemma \ref{lem: property of controllable operators}.(1), we know that the operators
   \[
@@
   Combining this with \eqref{eq:chareq2} and
-%YX Lemma \ref{lem: property of controllable operators}.(4), we get the desired result.
-Lemma \ref{lem: property of controllable operators}.(3), we get the desired result.
+  % YX Lemma \ref{lem: property of controllable operators}.(4), we get the desired result.
+  % ZY Lemma \ref{lem: property of controllable operators}.(3), we get the desired result.
+  Lemma \ref{lem: property of controllable operators}.(5), we get the desired result.
 
@@
   Combining with Lemma \ref{lem: property of controllable operators}.(1) and (4), and
-  \begin{equation}
+  \[
     (Z'_t - Z_t)f
@@
     , \quad 0\leq t\leq 1, f\in \mathcal P,
-  \end{equation}
+  \]
   we get the desired result.
 
-  (6). By  Lemma \ref{lem: complex extension for psi1}, for any $\delta > 0$ small enough, there exists  $C>0$ such that
+  (6). By  Lemma \ref{lem:CEP}, for any $\delta > 0$ small enough, there exists  $C>0$ such that
   \[
@@
 
+% *** Stable distributions
 \subsection{Stable distributions}
 \label{sec: stable distributions}
-% **** characteristic functions
-%YX Recall that the operators $(T_t)_{t\geq 0}$ are given by \eqref{eq:I:R:1},
-Recall that the operators $(T_t)_{t\geq 0}$ are defined by \eqref{eq:I:R:1},
- and functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
+Recall that the operators $(T_t)_{t\geq 0}$ are defined by \eqref{eq:I:R:1}, and functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
 \begin{lem}
@@
 \begin{proof}
-  \emph{Step 1.} We will show that for each $f \in \mathcal P$,
-  %YX there exists an $h \in \mathcal P$ such that
-   there exists  $h \in \mathcal P$ such that
-\(
-|T_tf|
-      \leq  e^{- \delta t} h
-\)
-for each $t\geq 0$,
-where
+  \emph{Step 1.} We will show that for each $f \in \mathcal P$, there exists $h \in \mathcal P$ such that $ |T_tf| \leq  e^{- \delta t} h$ for each $t\geq 0$, where
   \begin{align}
@@
   In fact, we can write $f = f_0 + f_1$ with $f_0\in \mathcal C_s \oplus \mathcal C_c$ and $f_1 \in \mathcal C_l$.
-    According to \cite[Lemma 2.7]{MarksMilos2018CLT},
-    %YX there exists an $h_0 \in \mathcal P$ such that for each $t\geq 0$,
-     there exists $h_0 \in \mathcal P$ such that for each $t\geq 0$,
+  According to \cite[Lemma 2.7]{MarksMilos2018CLT}, there exists $h_0 \in \mathcal P$ such that for each $t\geq 0$,
   \[
@@
   In fact, let $\delta$ be given by \eqref{eq:m:1}, then in this case $\delta > 0$.
-  Now, according to Step 1 there exists
- %YX  an $h \in \mathcal P$ such that
-    $h \in \mathcal P$ such that
-  $|T_tf| \leq e^{- \delta t} h$ for each $t\geq 0$.
+  Now, according to Step 1 there exists $h \in \mathcal P$ such that $|T_tf| \leq e^{- \delta t} h$ for each $t\geq 0$.
   This exponential decay implies the desired result in this step.
@@
   Note that $T_t f_c = f_c$ for each $t\geq 0$.
- %YX Also note that in step 2, we already show that there exists a $\delta > 0$ and an $h \in \mathcal P^+$
-   Also note that in Step 2, we already have shown that there exist $\delta > 0$ and  $h \in \mathcal P^+$
-  such that for each $t\geq 0$, we have $|T_t f_{sl}| \leq e^{- \delta t}h$.
+  Also note that in Step 2, we already have shown that there exist $\delta > 0$ and $h \in \mathcal P^+$ such that for each $t\geq 0$, we have $|T_t f_{sl}| \leq e^{- \delta t}h$.
   Therefore, using Lemma \ref{lem: Lip of power function} we have
@@
   \label{prop:PL:S}
-  For each $f \in \mathcal P\setminus \{0\}$, there exists a non-degenerate $(1+\beta)$-stable random variable $\zeta^f$ such that
-\(
-  E[e^{i\theta\zeta^f}] = e^{m[\theta f]}
-\)
-for each $\theta \in \mathbb R$.
+  For each $f \in \mathcal P\setminus \{0\}$, there exists a non-degenerate $(1+\beta)$-stable random variable $\zeta^f$ such that $ E[e^{i\theta\zeta^f}] = e^{m[\theta f]}$ for each $\theta \in \mathbb R$.
 \end{prop}
@@
     = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(\xi t)k(\xi,dt)
-,\quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+    , \quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
   \]
@@
 \end{proof}
+
 \begin{proof}[Proof of Proposition \ref{prop:PL:S}]
@@
   \]
-  According to the Step 1 of the proof of Lemma \ref{lem:m},
-%YX  we know that there exists a $\delta \geq 0$   and an $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta t} h$ for each $s\geq 0$.
- we know that there exist $\delta> 0$ and $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta s} h$ for each $s\geq 0$.
+  According to the Step 1 of the proof of Lemma \ref{lem:m}, we know that there exist $\delta> 0$ and $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta s} h$ for each $s\geq 0$.
   The above then follows.
 
- %YX Suppose that $f \in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$,
- If $f \in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$,
-  then $f$ can be written by $f = f_c +(f - f_c)$ where $f_c \in \mathcal C_c\setminus\{0\}$ and $f - f_c \in \mathcal C_s \oplus \mathcal C_l$.
-%YX  According to \eqref{eq:P:S:1} we have that in this case $m[\theta f]$ also admits an integral representation
+  If $f \in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$, then $f$ can be written by $f = f_c +(f - f_c)$ where $f_c \in \mathcal C_c\setminus\{0\}$ and $f - f_c \in \mathcal C_s \oplus \mathcal C_l$.
   In this case, according to \eqref{eq:P:S:1}, $m[\theta f]$ has an integral representation:
@@
   Finally, according to Lemma \ref{lem: charactreisticfunction} and the fact that
-  \begin{equation}
+  \begin{align}
     \int_{\mathbb R^d} | f_c(x)|^{1+\beta} \varphi(x)~dx
     \in (0, \infty),
-  \end{equation}
+  \end{align}
   We have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
@@
 \subsection{A refined estimation for the OU semigroup}
-%YX Do we need this subsection?
+% YX Do we need this subsection?
 It turns out that our proof of the CLT for the super OU processes relies on the following refined estimation for the OU semigroup.
@@
   \label{lem:P:R}
-Suppose that $g \in \mathcal P$, then there exists
-%YX an $h \in \mathcal P^+$ such that for each
- $h \in \mathcal P^+$ such that for each
-\(
-f
-\in \mathcal P_g
-:= \{\theta T_n g: n \in \mathbb Z_+, \theta \in [-1,1]\}
-\)
-and $t\geq 0$, we have
-\(
-%YX \big | P_t Z_1 f - \langle Z_1 f, \varphi \rangle \big|
-%YX \leq e^{-bt} h.
-\big | P_t [ Z_1 f - \langle Z_1 f, \varphi \rangle ]\big|
- \leq e^{-bt} h.
-\)
+  Suppose that $g \in \mathcal P$, then there exists $h \in \mathcal P^+$ such that for each $ f \in \mathcal P_g := \{\theta T_n g: n \in \mathbb Z_+, \theta \in [-1,1]\} $ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
 \end{lem}
 \begin{proof}
- %YX Fix the $g \in \mathcal P$.
   In the following $g \in \mathcal P$ is fixed.
 We write  $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$,  and $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
-We need  to prove that for each
-$f\in \mathcal P_g$,  there exists  $h \in \mathcal P^+$ such that for each $|P_tq_f| \leq e^{-bt} h.$
-
-  \emph{Step 1.}
-  %YX We argue that we only have to proof the result for all
-  We claim  that we only need to prove the result for all
+  % ZY We need  to prove that for each $f\in \mathcal P_g$, there exists  $h \in \mathcal P^+$ such that for each $|P_tq_f| \leq e^{-bt} h.$
+  We need to prove that there exists $h \in \mathcal P^+$ such that for each $f\in \mathcal P_g$, $|P_tq_f| \leq e^{-bt} h$.
+
+  \emph{Step 1.} We claim  that we only need to prove the result for all
   $f \in \widetilde{\mathcal P}_g:= \{T_{n+1} g : n \in \mathbb Z_+\}$.
-%YX  In fact, writing $q_f:=Z_1f - \langle Z_1f, \varphi \rangle \in \mathcal P^*$ for each $f\in \mathcal P$, then both $\operatorname{Re} q_g$ and $\operatorname{Im} q_g$ are functions in $\mathcal P$ of order $\geq 1$.
   In fact, both $\operatorname{Re} q_g$ and $\operatorname{Im} q_g$ are functions in $\mathcal P$ of order $\geq 1$.
-%YX Therefore, the result is valid for $f = T_0 g = g$.
   The result is valid for $f = T_0 g = g$ according to \cite[Fact 1.2]{MarksMilos2018CLT}.
@@
   \]
-%YX where $g = g_0 +g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$.
   Notice that the second term is in $C_\infty(\mathbb R^d)\cap \mathcal P$ since it is a finite summation of polynomials, and the first term is also in $C_\infty (\mathbb R^d) \cap \mathcal P$ according to \cite[Fact 1.1]{MarksMilos2018CLT}.
 
-\emph{Step 3.} We show that there exists
-%YX an $h_3 \in \mathcal P^+$ such that
- $h_3 \in \mathcal P^+$ such that
-for each $j \in \{1,\dots, d\}$ and $f \in \widetilde {\mathcal P}_g$, it holds that $|\partial_j f| \leq h_3$.
+  \emph{Step 3.} We show that there exists $h_3 \in \mathcal P^+$ such that for each $j \in \{1,\dots, d\}$ and $f \in \widetilde {\mathcal P}_g$, it holds that $|\partial_j f| \leq h_3$.
   In fact, it is known that for $t\geq 0$ and $x\in \mathbb R^d$, the position of the OU process $\xi_t$ under $\mathbb P_x$ is a Gaussian random variable with mean $xe^{-bt}$ and variance $\frac{\sigma^2}{2b} (1- e^{-2bt})$.
@@
     \label{eq:P:R:3:-1}
-  P_t f(x) = \int_{\mathbb R^d} f\big(x e^{-bt} + y \sqrt{1-e^{-2bt}}\big) \varphi(y)~dy,
+    P_t f(x) 
+    = \int_{\mathbb R^d} f\big(x e^{-bt} + y \sqrt{1-e^{-2bt}}\big) \varphi(y)~dy,
     \quad t\geq 0, x\in \mathbb R^d, f\in \mathcal P.
@@
     \label{eq:P:R:3:1}
- \partial_j P_t f = e^{-bt} P_t \partial_j f,
+    \partial_j P_t f 
+    = e^{-bt} P_t \partial_j f,
     \quad t \geq 0, j \in \{1,\dots, d\}.
   \end{align}
-%YX Write $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$.
   Thanks to Step 2, $T_1 g_0 \in C_\infty(\mathbb R^d)\cap \mathcal P$.
@@
   \]
-%YX Therefore, there exists an $h'_3\in \mathcal P^+$
-Therefore, there exists  $h'_3\in \mathcal P^+$
-such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
+  Therefore, there exists  $h'_3\in \mathcal P^+$n such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
   \begin{align}
@@
   \end{align}
-On the other hand, there exists
-%YX an $h_3''\in \mathcal P^+$ such that
- $h_3''\in \mathcal P^+$ such that
-for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
+  On the other hand, there exists $h_3''\in \mathcal P^+$ such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
   \begin{align}
@@
   \end{align}
-%YX The desired result in this step then follows.
   Then the desired result in this step follows.
 
-  \emph{Step 4.} We show that there exists
-  %YX an $h_{4} \in \mathcal P^+$
-   $h_{4} \in \mathcal P^+$
-  such that for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$, it holds that
-  \(
-    | \partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta} |
-    \leq h_4.
-  \)
+  \emph{Step 4.} We show that there exists $h_{4} \in \mathcal P^+$ such that for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$, it holds that $ | \partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta} | \leq h_4$.
   In fact, thanks to Step 2 and \eqref{eq:P:R:3:1}, for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde{\mathcal P}_g$, we have
@@
   \end{align}
-Recall from Step 1 of the proof of Lemma \ref{lem:m} there exists
-%YX an $h'_4\in \mathcal P^+$ such that
- $h'_4\in \mathcal P^+$ such that
-for each $f \in \{T_sg:s\geq 0\}$ it holds that $|f| \leq h'_4$.
+  Recall from Step 1 of the proof of Lemma \ref{lem:m} there exists $h'_4\in \mathcal P^+$ such that for each $f \in \{T_sg:s\geq 0\}$ it holds that $|f| \leq h'_4$.
   Therefore, using Step 3, we have for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$,
@@
     & |\partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta}|
-%YX  \leq (1+\beta) e^{\alpha (2+\beta)} P_{1-u} [  (P_u |f|)^\beta P_u |\partial_j f| ]
-%YX \\&    \leq (1+\beta) e^{\alpha (2+\beta)} P_{1-u} [  (P_u h'_4)^\beta P_u h_3 ]
-%YX   \leq (1+\beta) e^{\alpha (2+\beta)} Q_0 [  (Q_0 h_4')^\beta Q_0 h_3 ],
     \leq (1+\beta) e^{\alpha (1+\beta)} P_{1-u} [  (P_u |f|)^\beta P_u |\partial_j f| ]
-\\&    \leq (1+\beta) e^{\alpha (1+\beta)} P_{1-u} [  (P_u h'_4)^\beta P_u h_3 ]
+    \\ & \leq (1+\beta) e^{\alpha (1+\beta)} P_{1-u} [  (P_u h'_4)^\beta P_u h_3 ]
     \leq (1+\beta) e^{\alpha (1+\beta)} Q_0 [  (Q_0 h_4')^\beta Q_0 h_3 ],
   \end{align}
-%YX where $Q_0$ is given by \eqref{eq:Q}.
   where $Q_0$ is defined by \eqref{eq:Q}.
@@
 
- \emph{Step 5.} We show that there exits
- %YX an $h_5 \in \mathcal P^+$
-  $h_5 \in \mathcal P^+$
- such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
+  \emph{Step 5.} We show that there exits $h_5 \in \mathcal P^+$ such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
   In fact, according to Step 4, for each $j \in \{1,\dots, d\}$, $f \in \widetilde{\mathcal P}_g$ and compact $A \subset \mathbb R^d$, we have
@@
   \]
-Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, for each $j \in
-\{1,\dots, d\}$, $f\in \widetilde {\mathcal P}_g$ and $x\in \mathbb R^d$, it holds that
+  Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, for each $j \in \{1,\dots, d\}$, $f\in \widetilde {\mathcal P}_g$ and $x\in \mathbb R^d$, it holds that
   \[
     | \partial_j Z_1 f(x)|
-  =\Big| \int_0^1  ( \partial_jP_{1-u}^\alpha (-iP_u^\alpha f)^{1+\beta} ) (x) ~du  \Big|
+    = \Big| \int_0^1  ( \partial_jP_{1-u}^\alpha (-iP_u^\alpha f)^{1+\beta} ) (x) ~du  \Big|
     \leq h_4(x).
@@
   \emph{Final step.}
-%YX From Step 5, there are $c_5,n_5> 0$ such that for each $x\in \mathbb R^d$, $h_5(x) \leq c_5(1+|x|)^{n_5}$.
-Let $h_5$ be the function in Step 5. There are $c_0, n_0> 0$ such that for each $x\in \mathbb R^d$, $h_5(x) \leq c_0(1+|x|)^{n_0}$.
-Note that for each $x, y \in \mathbb R^d$, $1+|x|+|y|\leq (1+|x|) (1+|y|)$;
-and that for each $\theta \in [0,1]$, $|\sqrt {1 - \theta} - 1| \leq \theta$.
-Write %YX $q_f = Z_1f - \langle Z_1f, \varphi\rangle$ for each $f\in \mathcal P$; and
-$D_{x,y} = \{ax+by: a, b \in [0,1]\}$ for each $x, y \in \mathbb R^d$.
-Using \eqref{eq:P:R:3:-1} and Step 5,
-%YX there exists an $h_6 \in \mathcal P^+$
-  there exists  $h_6 \in \mathcal P^+$
-such that for each $t \geq 0$, $f \in \widetilde {\mathcal P}_g$ and $x \in \mathbb R^d$, we have
+  Let $h_5$ be the function in Step 5. 
+  There are $c_0, n_0> 0$ such that for each $x\in \mathbb R^d$, $h_5(x) \leq c_0(1+|x|)^{n_0}$.
+  Note that for each $x, y \in \mathbb R^d$, $1+|x|+|y|\leq (1+|x|) (1+|y|)$; and that for each $\theta \in [0,1]$, $|\sqrt {1 - \theta} - 1| \leq \theta$.
+  Write $D_{x,y} = \{ax+by: a, b \in [0,1]\}$ for each $x, y \in \mathbb R^d$.
+  Using \eqref{eq:P:R:3:-1} and Step 5, there exists  $h_6 \in \mathcal P^+$ such that for each $t \geq 0$, $f \in \widetilde {\mathcal P}_g$ and $x \in \mathbb R^d$, we have
   \begin{align}
@@
     & \leq e^{-bt} \int_{\mathbb R^d} c_0(1+|x|+|y|)^{n_0} (|x|+|y|) \varphi(y) ~dy \\
-%YX & \leq c_0 e^{-bt}(1+|x|)^{n_0}\Big(|x|\int_{\mathbb R^d} (1+|y|)^n\varphi(y) ~dy + \int_{\mathbb R^d} (1+ |y|)^n |y| \varphi(y) ~dy \Big) \\
     & \leq c_0 e^{-bt}(1+|x|)^{n_0}\Big(|x|\int_{\mathbb R^d} (1+|y|)^{n_0}\varphi(y) ~dy + \int_{\mathbb R^d} (1+ |y|)^{n_0} |y| \varphi(y) ~dy \Big) \\
@@
 
+% *** Small value probability
 \subsection{Small value probability}
@@
 where for each $\lambda\geq 0$, $t\mapsto v_t(\lambda)$ is the unique positive solution to the equation
-\begin{equation}
+\begin{align}
   \label{eq: fkpp equation for CSBP}
@@
   \quad t\geq 0.
-\end{equation}
-It can be verified that for each $\mu \in \mathcal M(\mathbb R^d)$ with $x = \| \mu \|$, we have
-\(
-  \{(\|X_t\|)_{t\geq 0}; \mathbb P_\mu\}
-  \overset{\text{law}}{=} \{(Y_t)_{t\geq 0}; \mathbf P_x\}.
-\)
+\end{align}
+It can be verified that for each $\mu \in \mathcal M(\mathbb R^d)$ with $x = \| \mu \|$, we have $ \{(\|X_t\|)_{t\geq 0}; \mathbb P_\mu\} \overset{\text{law}}{=} \{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
 
@@
 We write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
+
 \begin{prop}
@@
 \end{prop}
+
 \begin{proof}
-  Step 1. We recall some known facts about the CSBP $(Y_t)$.
+  \emph{Step 1.} 
+  We recall some known facts about the CSBP $(Y_t)$.
   For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of \eqref{eq: fkpp equation for CSBP}.
   Letting $\lambda \to \infty$ in \eqref{eq: fkpp equation for CSBP}, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
-  \begin{equation}
+  \begin{align}
     \label{eq: svp1}
     \mathbf P_x(Y_t = 0)=e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
-  \end{equation}
-  It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; and (ii) $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
+  \end{align}
+  % It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; (ii) $t\mapsto \bar v_t$ is decreasing; and (iii) $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
+  % It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; (ii) $t\mapsto \bar v_t$ is decreasing; and (iii) $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi$ on $[0,\infty)$.
+  It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ exists and is the largest root of $\psi$ on $[0,\infty)$.
   Letting $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
@@
   \]
-
-  Note that $\psi$ has derivative
+  Note the derivative of $\psi$
   \[
@@
   \]
-  which is increasing in $z$.
+  is non-decreasing.
   This says that $\psi$ is a convex function.
@@
   Therefore we have (i) $\bar v > 0$; (ii) $\psi(z) < 0$ on $z\in (0,\bar v)$; and (iii) $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
-  It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that
-  \begin{itemize}
-  \item
-    if $\lambda \in (0,\bar v)$, then $0<\lambda \leq v_t(\lambda)<\bar v $ and
-    \begin{align}
-      \label{CSBP: int}
-    \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0;
-    \end{align}
-  \item
-    if $\lambda \in (\bar v, \infty)$, then $\bar v < v_t(\lambda)\leq \lambda< \infty $ and
-    \[
-      \int_{v_t(\lambda)}^\lambda\frac{dz}{\psi(z)} = t, \quad t\geq 0.
-    \]
-  \end{itemize}
-  By monotonicity, we have that
-  \begin{equation}
+  It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that (i) if $\lambda \in (0,\bar v)$, then $0<\lambda \leq v_t(\lambda)<\bar v $; (ii) if $\lambda \in (\bar v, \infty)$, then $\bar v < v_t(\lambda)\leq \lambda< \infty$; and (iii) for each $\lambda \in (0,\infty)\setminus \{\bar v\}$ and $t\geq 0$, we always have
+    \(
+      \int_{v_t(\lambda)}^\lambda  \psi(z)^{-1}dz = t.
+    \)
+  % By monotonicity, we have that
+  Taking $\lambda \to \infty$ and using monotone convergence theorem, we have that
+  \begin{align}
     \label{eq:svp2}
     \int_{\bar v_t}^\infty \frac{dz}{\psi(z)} = t, \quad t\geq 0.
-  \end{equation}
-
-  Step 2. We will show that, for each $x \geq 0$ there exists a constant $c_1>0$ such that
+  \end{align}
+
+  \emph{Step 2.} We will show that, for each $x \geq 0$ there exists a constant $c_1>0$ such that
   \[
@@
 
-  Step 3. We will show that there exist $c_2, \delta_1, t_0 > 0$ such that
+  \emph{Step 3.} We will show that there exist $c_2, \delta_1, t_0 > 0$ such that
   \[
@@
 
-  Step 4:
+  \emph{Step 4.}
   We will show that there exist $c_3, \delta_2, t_1>0$ such that
@@
   For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$.
-Then using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have for $t>0$ large enough,
+  % Then using \eqref{eq:svp2} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have for $t>0$ large enough,
+  Then we have for $t>0$ large enough,
   \begin{align}
@@
 
+% *** Moments for super-OU processes
 \subsection{Moments for super-OU processes}
@@
 In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec:I:R} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-Recall that the operator $\mathcal{I}^t_s$ is defined in \eqref{Ist}.
+% Recall that the operator $\mathcal{I}^t_s$ is defined in \eqref{Ist}.
 
@@
 \end{proof}
+
 \begin{lem}
@@
   \[
-  C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big)\langle Q_0Rh, \mu\rangle.
+    C 
+    := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big)\langle Q_0Rh, \mu\rangle.
     \qedhere
@@
 For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write $ \|Y\|_{\mathbb P;p} := \mathbb P[|Y|^p]^{1/p}$.
-%YX Recall that we also write $\tilde u = \frac{u}{1+u}$ for each $u\neq -1$.
 Recall that we write $\tilde u = \frac{u}{1+u}$ for each $u\neq -1$.
@@
 
+% ** Proofs of main results
 \section{Proofs of main results}
@@
 
-% *** The large branching rate regime: law of large numbers
-% \subsection{The large branching rate regime: law of large numbers}
+% *** law of large numbers
 \subsection{Law of large numbers}
@@
 In this subsection, we prove Theorem \ref{thm: law of large number}.
-%YX In order to do this,
-For this purpose,
-we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
+For this purpose, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
 Recall that $L$ is the infinitesimal generator of the OU-process.
@@
 Let $(\mathscr{F}_t)_{t\geq 0}$ be the natural filtration of $X$.  The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
+
 \begin{lem}
@@
   It follows easily from Ito's formula that
-\begin{equation}
+  \begin{align}
     \label{Theorem55}
@@
     = f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d,
-\end{equation}
+  \end{align}
   where $P_t^{ab} := e^{abt}P_t$.
@@
     & = e^{ - ( \alpha - ab ) s } \Big \langle \int_0^{t-s} P_{u}^{ab} \bar{f}~ du, X_s \Big \rangle
-    = e^{-(\alpha-ab)s}\left(\langle P_{t-s}^{ab}f,X_s\rangle-\langle
-    f, X_s \rangle \right) \\
-  & = e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle - e^{ - ( \alpha - ab ) s} \langle
-    f,X_s\rangle.
+      = e^{-(\alpha-ab)s}\left(\langle P_{t-s}^{ab}f,X_s\rangle - \langle f, X_s \rangle \right) \\
+    & = e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle - e^{ - ( \alpha - ab ) s} \langle f,X_s\rangle.
   \end{align}
@@
 
-Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$. Define
-\(
-  H_t^p
-  :=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle
-\)
-for each $t\geq 0$.
+Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$. 
+Define $ H_t^p :=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle$ for each $t\geq 0$.
 
@@
   \label{lem:M:L:ML}
-   For each $\mu\in \mathcal M_c(\mathbb R^d)$ and $p \in \mathbb Z_+^d$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_{\mu}$-martingale with respect to
-%YX $(\mathcal F_t)$.
-    $(\mathscr F_t)_{t\geq 0}$.
-%YX Moreover if $\alpha\tilde \beta>|p|b$, the martingale is bounded in $L^{1+\gamma}(\mathbb P_\mu)$ for each $\gamma\in (0, \beta)$
+   For each $\mu\in \mathcal M_c(\mathbb R^d)$ and $p \in \mathbb Z_+^d$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_{\mu}$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
     Moreover if $\alpha\tilde \beta>|p|b$, the martingale is bounded in $L^{1+\gamma}(\mathbb P_\mu)$ for each $\gamma\in (0, \beta)$.
-%YX  As a consequence, $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $  convergence almost surely  and also in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
-  Thus the limit $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $  exists $\mathbb{P}_{\mu}$-a.s.
-   and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
+  Thus the limit $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $  exists $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
 \end{lem}
+
 \begin{proof}
@@
   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale.
-
   Further suppose that $\alpha \tilde \beta > |p| b$.
   Then there exists a $\gamma_0 \in (0,\beta)$ which is close enough to $\beta$ so that $\alpha\tilde \gamma>|p|b$ for each $\gamma\in [\gamma_0, \beta)$.
-  Using  Lemma \ref{lem:P:M:uc} and the fact $\kappa_{\phi_p}=|p|$, we get that, for each $\gamma\in [\gamma_0, \beta)$,
-  %YX there exists a constant $c>0$ such that
-  there exists a constant $C>0$ such that
+  Using  Lemma \ref{lem:P:M:uc} and the fact $\kappa_{\phi_p}=|p|$, we get that, for each $\gamma\in [\gamma_0, \beta)$, there exists a constant $C>0$ such that
   \[
@@
     \leq c e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
-%YX = c
     = C
@@
   \]
-%YX For each $\gamma\in (0, \gamma_0)$ there exists a constant $c>0$, such that
-For each $\gamma\in (0, \gamma_0)$ there exists a constant $C>0$, such that
+  % For each $\gamma\in (0, \gamma_0)$ there exists a constant $C>0$, such that
+  For each $\gamma\in (0, \gamma_0)$ there exists a constant $C'>0$, such that
   \[
@@
     \leq \| H_t^p \|_{\mathbb P_\mu;1+\gamma_0}
- %YX \leq c,
-    \leq C,
+    % \leq C,
+    \leq C',
     \quad t\geq 0.
@@
 \begin{proof}
-%YX   Thanks to Lemma \ref{lem:M:L:ML} we only have to proof this when $0\leq s < t<\infty$.
   Thanks to Lemma \ref{lem:M:L:ML}, we only  need to prove the inequality  when $0\leq s < t<\infty$.
-%YX  Fix the $p\in \mathbb{Z}_+^d$, $\mu\in \mathcal M_c(\mathbb R^d)$ and the $\gamma \in (0,\beta)$ with $\alpha \tilde \gamma > |p|b$.
   Suppose $p\in \mathbb{Z}_+^d$, $\mu\in \mathcal M_c(\mathbb R^d)$ and  $\gamma \in (0,\beta)$ with $\alpha \tilde \gamma > |p|b$ are fixed.
- %YX By Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,
- Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,  we know that
- there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$,
+  Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,  we know that there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$,
   \begin{align}
@@
 	Write
-  \begin{equation}
+  \[  
     f
@@
     =: \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\widetilde{f}.
-  \end{equation}
+  \]
 	Then
@@
 	According to Lemma \ref{lem:M:L:ML}, we have
-\begin{equation}
+  \begin{align}
     \label{as convergence}
@@
     \xrightarrow[t\to \infty]{} \sum_{p\in \mathbb{Z}_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
-\end{equation}
+  \end{align}
   $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma\in(0,\beta)$.
   Therefore, it suffices to show that
-\begin{equation}
+  \begin{align}
     J_t
@@
     \quad t\geq 0,
-\end{equation}
+  \end{align}
   converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
@@
   By Step 1, for any fixed $\gamma\in (0,\beta)$, there exist $C_6, \delta_3>0$ such that for each $t\geq 0$,
-\begin{equation}
+  \[
     \| e^{-(\alpha-a_0 b)t}\langle \widetilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
@@
     \leq C_6 e^{-\delta_3 t}.
-\end{equation}
+  \]
   Now, by the triangle inequality, for each $t\geq 0$,
@@
     \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\widetilde{f},a_0}|
-  \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\widetilde{f},a_0}|=0, \quad
-  \mathbb P_\mu\text{-a.s.}
+    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\widetilde{f},a_0}|=0, 
+    \quad \mathbb P_\mu\text{-a.s.}
   \end{align}
@@
 
-%YX \subsection{Local central limit theorems}
-\subsection{Central limit theorems for one unite time interval}
+% **** Central limit theorems for one unite time interval
+\subsection{Central limit theorems for one unite time intervals}
 \label{sec:critical}
-% ***** Local CLT for one interval for small and critical
-%YX In this section, we will establish the following local central limit theorem for our super OU processes.
-In this subsection, we will establish the following  central limit theorem for our super OU processes.
+% ***** Local CLT for one interval 
+In this subsection, we will establish the following  central limit theorem for our super-OU processes.
 \begin{thm}
@@
 
-%YX In fact, we can proof a stronger result:
 In fact, we prove a stronger result:
@@
 \end{prop}
+
 \begin{proof}
@@
 \end{align}
-%YX From Proposition \ref{prop:PL:S} and Lemma \ref{lem: charactreisticfunction}, we easily get $\theta\mapsto \langle Z_1(\theta f),\varphi\rangle$ is the characteristic function of some $(1+\beta)$-stable random variable.
-Therefore  $\operatorname{Re} \langle Z_1f, \varphi\rangle \leq 0$.
 From Lemma \ref{lem: charactreisticfunction}, we  get that $\theta\mapsto \langle Z_1(\theta f),\varphi\rangle$ is the characteristic function of some $(1+\beta)$-stable random variable, and then  $\operatorname{Re} \langle Z_1f, \varphi\rangle \leq 0$.
@@
 \emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for each $t\geq 1$ and
-$f \in \mathcal P_g$, we have
-\(
-  J^f_1(t,\epsilon)
-  \leq C_2e^{-\delta_2 t}.
-\)
+$f \in \mathcal P_g$, we have $ J^f_1(t,\epsilon) \leq C_2e^{-\delta_2 t}$.
+
 In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-%YX Acording to the step 1 of the proof of Lemma \ref{lem:m},
-Acording to Step 1 of the proof of Lemma \ref{lem:m},
-%YX there exist $h_{20} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{20}$.
-    there exist $h_{2} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{2}$.
+Acording to Step 1 of the proof of Lemma \ref{lem:m}, there exist $h_{2} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{2}$.
 Then, we have for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
@@
   & |Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
- %YX   \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t-1}(\epsilon)}
- %YX \leq R \Big(\frac{h_{20}}{e^{(\alpha-\epsilon)(t-1)(1-\tilde \beta)}}\Big) \\
- %YX  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-1)}Rh_{20}.
     \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t}(\epsilon)}
@@
   J^f_1(t,\epsilon)
-%YX & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[\langle Rh_0,X_{t-1}\rangle]\\
-%YX  & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 R h_{20}, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
   & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[\langle Rh_2,X_{t-1}\rangle]\\
@@
 \end{align}
-where
-\(
-  q_f
-  = Z_1 f-\langle  Z_1 f,\varphi\rangle \in \mathcal P^*.
-\)
-%YX It follows from Lemma \ref{lem:P:R} that there exists an $h_{30}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have
-It follows from Lemma \ref{lem:P:R} that there exists $h_{30}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have
-%YX why use index 30?
-\(
-  Q_1 (\operatorname{Re} q_f) \leq h_{30}
-  \text{ and } Q_1 (\operatorname{Im} q_f)\leq h_{30},
-\)
-where $Q_1$ is given by \eqref{eq:Q} with $\kappa=1$.
-%YX In the rest of this step, fixing a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
+where $ q_f = Z_1 f-\langle  Z_1 f,\varphi\rangle \in \mathcal P^*$.
+It follows from Lemma \ref{lem:P:R} that there exists $h_{3}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have $Q_1 (\operatorname{Re} q_f) \leq h_{3} \text{ and } Q_1 (\operatorname{Im} q_f)\leq h_3$, where $Q_1$ is given by \eqref{eq:Q} with $\kappa=1$.
 In the rest of this step, we  fix a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-According to Lemma \ref{lem:P:M:uc}.(3) (with $\kappa=1$),
-%YX there exists $C_{30}>0$ such that for all $t\geq 0$ and $f\in \mathcal P_g$,
-there exists $C_{3}>0$ such that for all $t\geq 0$ and $f\in \mathcal P_g$,
+According to Lemma \ref{lem:P:M:uc}.(3) (with $\kappa=1$), there exists $C_{3}>0$ such that for all $t\geq 0$ and $f\in \mathcal P_g$,
 \begin{align}
@@
     \leq \|\langle \operatorname{Re} q_f, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} q_f, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} \\
-%YX  & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{30}} \|\langle q, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_{30} e^{\frac{\alpha t}{1+\gamma}}.
  & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{3}} \|\langle q, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_{3} e^{\frac{\alpha t}{1+\gamma}}.
@@
     \leq  C_3 e^{-(\alpha-\epsilon)t}e^{\frac{\alpha t}{1+\gamma}}
-%YX \leq C_{30} e^{-(\alpha\tilde \gamma -\epsilon)t}.
    \leq C_{3} e^{-(\alpha\tilde \gamma -\epsilon)t}.
@@
 \emph{Step 4.}
-We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_4>0$ such that for all $t\geq 1$, $
-J_3(t,\epsilon)\leq C_4e^{-\delta_4 t}.
-$
+We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_4>0$ such that for all $t\geq 1$, $J_3(t,\epsilon)\leq C_4e^{-\delta_4 t}.$
 In fact, we have  for all $t\geq 0, \epsilon >0$,
@@
 \]
-On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$,
-%YX there exists  $C_{40}, \delta_{40}>0$ such that for all $t\geq 0$,
-there exists  $C_{4}, \delta_{4}>0$ such that for all $t\geq 0$,
-\begin{equation}
+On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_{4}, \delta_{4}>0$ such that for all $t\geq 0$,
+\begin{align}
   \mathbb P_\mu(A_t(\epsilon)^c,D^c)
   \leq \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\|
-%YX  \leq e^{ - \epsilon t}) \leq C_{40} (e^{-\epsilon \delta_{40} t}+e^{-\delta_{40} t}).
   \leq e^{ - \epsilon t}) \leq C_{4} (e^{-\epsilon \delta_{4} t}+e^{-\delta_{4} t}).
-\end{equation}
-%YX Combining these results, we get the desired result in step 4.
+\end{align}
  Combining these results, we get the desired result in this step.
 
-%YX \emph{Final step}, combining the results in Steps 1--4, we immediately get the desired result.
  \emph{Final step}. Combining the results in Steps 1--4, we immediately get the desired result.
 \end{proof}
-% ***** Local CLT
-
-% ***** local CLT one interval for large
-% ***** LCLT for conditional one intervald
+
 % ***** LCLT for Multiple interval
@@
   Then there exist $C,\delta>0$ such that for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$,
-\begin{equation}
+\begin{align}
   \label{32corollary}
   \Big|\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{k=l}^ne^{i \Upsilon^{f_k}_{k} }-\prod_{k=l}^n e^{\langle Z_1f_k, \varphi\rangle}\Big]\Big|\leq C e^{-\delta l}.
-\end{equation}
+\end{align}
 \end{cor}
@@
   \end{align}
-  By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that
-  %YX for each $l\leq n$ in $\mathbb Z_+$, each $k \in \{l,\dots , n\}$, and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
-   for each $l\leq n$ in $\mathbb Z_+$,  $k \in \{l,\dots , n\}$, and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+  By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that for each $l\leq n$ in $\mathbb Z_+$,  $k \in \{l,\dots , n\}$, and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
   \begin{align}
@@
   \end{align}
- %YX Therefore, there exist $C_1,\delta_1 >0$ such that
-    Therefore, there exist $C,\delta >0$ such that
-   for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+  Therefore, there exist $C,\delta >0$ such that for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
 
@@
       \leq \sum_{k=l}^n C_0 e^{-\delta_0 k}
-%YX      \leq C_1 e^{- \delta_1 l}.
       \leq C e^{- \delta l}.
@@
 
-% ***** local CLT multiple interval for large branching rate
 % *** The small branching rate regime
@@
 \begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:1})]
-	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_s$
-%YX and $t_0 > 1$ be large enough
-    and $t_0 > 1$  large enough
-so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
+	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_s$ and $t_0 > 1$  large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
   For each $t\geq t_0$, in this proof we write $\theta_t = \|X_t\|^{\tilde \beta - 1}$,
@@
   \end{multline}
-and
-\(
- I^f_0(t)
- := \sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f},
-\)
-where $\tilde f:= e^{\alpha(\tilde \beta - 1)} f$.
+  and $ I^f_0(t) := \sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f},$ where $\tilde f:= e^{\alpha(\tilde \beta - 1)} f$.
 
@@
   In fact, for each $k \in \mathbb Z_+$, we have  $T_{k} \tilde f \in \mathcal P_{\tilde f}:=\{\theta T_n \tilde f: n \in \mathbb Z_+, \theta \in [-1,1]\}$.
-%YX  Therefore from Proposition \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
   Therefore from Corollary \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
@@
   \end{align}
-  On the other hand, using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability
-  %YX of semigroup $(P_t)$, we can verify that
-  of the semigroup $(P_t)_{t\geq 0}$, we have
+  On the other hand, using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of the semigroup $(P_t)_{t\geq 0}$, we have
   \begin{align}
@@
   \emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$.
-%YX  In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we can write for each $t\geq t_0$ that
   In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we have that for each $t\geq t_0$,
@@
   \end{align}
-where
-\(
-Y_{t,k}
-:= \exp(i \Upsilon_{t-k-1}^{T_{k} \tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1.
-\)
+  where $ Y_{t,k} := \exp(i \Upsilon_{t-k-1}^{T_{k} \tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1. $
   We claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb Z_+$ and $t\geq k+1$.
-And therefore there exists $C_2'>0$ such that for each $t \geq t_0$,
-%YX $|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]| \leq C_2't^{-\delta_1}$ which, combines with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
-$|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]-1| \leq C_2't^{-\delta_1}$  which, combining with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
-
-%YX We will show this claim in the following substep 2.1 and 2.2.
+  And therefore there exists $C_2'>0$ such that for each $t \geq t_0$, $|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]-1| \leq C_2't^{-\delta_1}$  which, combining with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
+
   We will show this claim in the following substeps 2.1 and 2.2.
-First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with
-\(
-\alpha \tilde \gamma
->\eta
-> \eta - 3\eta'
-> \alpha \tilde \beta - \alpha \tilde \gamma
-> 0;
-\)
-and define for each $k \in \mathbb Z_+$ and $t\geq k+1$,
+  First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with $ \alpha \tilde \gamma > \eta > \eta - 3\eta' > \alpha \tilde \beta - \alpha \tilde \gamma > 0;$ and define for each $k \in \mathbb Z_+$ and $t\geq k+1$,
   \[
@@
 % ******* Step 2.2
-  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for each $k\in \mathbb Z_+$ and $t\geq k+1$, it holds that
-\(
-    \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}]
-    \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.
-\)
+  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for each $k\in \mathbb Z_+$ and $t\geq k+1$, it holds that $ \mathbb{\widetilde{P}}_{\mu} [|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}$.
   In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $; and therefore for each $k\in \mathbb Z_+$ and $t \geq k + 1$,
@@
   \end{align}
-  and
-  $
-    |H_t^{1 - \tilde \beta} H_{t-k-1}^{ 1 - \tilde \beta}|
-    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta'(t-k-1)}.
-  $
+  and $ |H_t^{1 - \tilde \beta} H_{t-k-1}^{ 1 - \tilde \beta}| \geq 2^{\frac{1}{1+\beta}} e^{-2\eta'(t-k-1)}$.
   Thus, there exists $C_{2.2}'> 0$ such that for all $k \geq 0, t\geq k+1$, almost surely
-  \begin{equation}
-    \label{ineq: control of Kkt}
+  \begin{align}
     K_{t,k}
     \leq C_{2.2}' e^{-(\eta - 3\eta')(t-k-1)}.
-  \end{equation}
+  \end{align}
   Now, by Lemma \ref{lem: control of mgtrs}, there exist $C''_{2.2}>0$ such that for all $k\geq 0$ and $t\geq k+1$,
@@
   Now writing $\mathcal{E}_t:=\{\|X_t\|>e^{(\alpha-\epsilon) t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
-  \begin{equation}
+  \begin{align}
     \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
@@
     , \quad t\geq0.
-  \end{equation}
+  \end{align}
   Therefore,
-  \begin{equation}
+  \begin{align}
     \label{Theorem123}
@@
     \quad t\geq t_0.
-  \end{equation}
+  \end{align}
 	According to Lemma \ref{lem: control of mgtrs}, there exist $C_3',C_3'',C_3'''>0$ such that for each $t\geq t_0 >1$,
@@
       \leq C_3' e^{q t}e^{-\epsilon ( 1 - \tilde \beta)t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{-q k}
-\\
-    & \leq C_3'' e^{q(t - \lceil t - \ln t\rceil)}e^{-\epsilon(1 - \tilde \beta) t}
+    \\ & \leq C_3'' e^{q(t - \lceil t - \ln t\rceil)}e^{-\epsilon(1 - \tilde \beta) t}
          \leq C_3'' t^q e^{- \epsilon(1 - \tilde \beta) t}.
@@
 
-%YX	\emph{Final step}, combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:1}.
-\emph{Final step}. Combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:1}.
+% ****** Final Step
+  \emph{Final step.} Combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:1}.
 \end{proof}
@@
   Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_c$ and $t_0 > 1$ large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
-%YX    For each $t\geq t_0$, in this proof we write $\theta_t = \|t X_t\|^{\tilde \beta - 1}$; and we define $I_i^f(t)$ for $i = 1,2,3$ using \eqref{eq:PM:CLTS:1}, and set
- For each $t\geq t_0$, in this proof we write $\theta_t = \|t X_t\|^{\tilde \beta - 1}$,  define $I_i^f(t)$ using \eqref{eq:PM:CLTS:1}  for $i = 1,2,3$, and set
-$
-    I^f_0(t)
-    := t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f},
-$
-where $\tilde f = e^{\alpha(\tilde \beta - 1)} f$.
+  For each $t\geq t_0$, in this proof we write $\theta_t = \|t X_t\|^{\tilde \beta - 1}$,  define $I_i^f(t)$ using \eqref{eq:PM:CLTS:1}  for $i = 1,2,3$, and set $ I^f_0(t) := t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f}$, where $\tilde f = e^{\alpha(\tilde \beta - 1)} f$.
 
@@
   \end{align}
-%YX  Note that since $f \in \mathcal C_c\setminus \{0\}$, so $T_k \tilde f = \tilde f$ for each $k \in \mathbb Z_+$.
   Since $f \in \mathcal C_c\setminus \{0\}$, we have $T_k \tilde f = \tilde f$ for each $k \in \mathbb Z_+$.
@@
   Therefore $\mathbb {\widetilde P}_\mu[e^{i I^f_0(t)}] \xrightarrow[t\to \infty]{} e^{m[f]}$.
-%  Noticing that $I_0^f(t)$ is linear in $f$, the desired result in this step follows.
   The desired result in this step follows.
@@
   \emph{Step 2.} We show that $ I^f_1(t) - I^f_0 (t) \xrightarrow[t\to \infty]{d} 0$.
-%YX  In fact, similar to the Step 2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we also have \eqref{eq:PM:S:1} is valid with
-In fact, similar to Step 2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we  have \eqref{eq:PM:S:1} is valid with
-\(
-    Y_{t,k}
-    := \exp(i t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k}\tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1.
-\)
-%YX  We also claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb N$ and $t\geq k+1$; and similarly, the desired results in this step follows with this claim.
-Similarly, we claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb N$ and $t\geq k+1$, and  then the desired result in this step follows.
-
-%YX  We will show this claim in the following substep 2.1 and 2.2.
+  In fact, similar to Step 2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we  have \eqref{eq:PM:S:1} is valid with $ Y_{t,k} := \exp(i t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k}\tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1$.
+  Similarly, we claim that there exists $C_2, \delta_2>0$ such that $\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}$ for each $k\in \mathbb N$ and $t\geq k+1$, and  then the desired result in this step follows.
+
   We will show this claim in the following substeps 2.1 and 2.2.
-  First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with
-  \(
-    \alpha \tilde \gamma
-    >\eta
-    > \eta - 3\eta'
-    > \alpha \tilde \beta - \alpha \tilde \gamma
-    > 0;
-  \)
-  and define for each $k \in \mathbb N$ and $t\geq k+1$ that
-\(
-\mathcal{D}_{t,k}
-    :=\{|H_t-H_{t-k-1}|\leq  e^{-\eta (t-k-1)}, H_{t-k-1}> 2e^{-\eta' (t-k-1)}\}.
-\)
+  First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with $ \alpha \tilde \gamma > \eta > \eta - 3\eta' > \alpha \tilde \beta - \alpha \tilde \gamma > 0$; and define for each $k \in \mathbb N$ and $t\geq k+1$ that $ \mathcal{D}_{t,k} := \{|H_t-H_{t-k-1}| \leq  e^{-\eta (t-k-1)}, H_{t-k-1}> 2e^{-\eta' (t-k-1)}\}$.
 
@@
   \emph{Substep 2.1.}
-  %YX  Similar to the substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$,
-  Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$,
-  \(
-    \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}]
-    \leq C_{2.1} e^{-\delta_{2.1} (t-k)}.
-  \)
+  Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$, $\mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} (t-k)}$.
   We omit the details.
@@
 % ******* Step 2.2
-  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for each $k\in \mathbb N$ and $t\geq k+1$,
-\(
-\mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}]
-    \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.
-\)
+  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for each $k\in \mathbb N$ and $t\geq k+1$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.$
   In fact, noticing that for $f\in \mathcal C_c$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha $; and therefore for each $k\in \mathbb Z_+$ and $t \geq k + 1$,
@@
   \]
-%YX  The rest is similar to the substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:2}).
   The rest is similar to Substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:2}).
@@
   In fact, writing $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
-  \begin{equation}
+  \[
     \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
@@
     , \quad t\geq0.
-  \end{equation}
+  \]
   Therefore,
-  \begin{equation}
+  \begin{align}
     \label{Theorem123}
@@
     \quad t\geq t_0.
-  \end{equation}
+  \end{align}
   Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\tilde \beta - \tilde \gamma) \leq \frac{1}{2}(1- \tilde \beta)$.
@@
       = C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - \tilde \gamma) t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{-\alpha (\tilde \beta -\tilde \gamma) k}
-\\
-    & \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)(t - \lceil t - \ln t\rceil)}
+    \\ & \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)(t - \lceil t - \ln t\rceil)}
          \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} t^{\alpha (\tilde \beta - \tilde \gamma)}.
   \end{align}
-%YX  From this and \eqref{Theorem123}, combined with the fact that $I^f_2(t)$ is linear in $f$, we get the desired result in this step.
   From this and \eqref{Theorem123}, we get the desired result in this step.
@@
 % ****** Step 4
-  \emph{Step 4.}
- %YX Similar to the Step 4 of the Proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
- Similar to Step 4 of the Proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+  \emph{Step 4.} Similar to Step 4 of the Proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
   We omit the details.
@@
   In fact, since $T_k\tilde f \in \mathcal P_{\tilde f}$ for each $k\in \mathbb Z_+$, from Corollary \ref{cor:MI} we have $\widetilde{ \mathbb P}_\mu[e^{i I_0^f(t)}]\xrightarrow[t\to \infty]{}\exp\{\sum_{k=0}^\infty \langle Z_1T_k(-\tilde f),\varphi\rangle\}$.
-Using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability
-%YX of  semigroup $(P_t)_{t\geq 0}$ we can verify that
-of the semigroup $(P_t)_{t\geq 0}$ we have
+  Using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of the semigroup $(P_t)_{t\geq 0}$ we have
   \begin{align}
@@
   \end{align}
-%YX Now, combining with the fact that $I_0^f(t)$ is linear in $f$, the result in this step follows.
   The result in this step follows.
@@
   \emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$.
-%YX In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we can write for each $t\geq 0$ that
-    In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we have, for each $t\geq 0$, that
- $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq \sum_{k=0}^{\lfloor t^2 \rfloor} \widetilde {\mathbb {P}}_\mu[|Y_{t,k}|]$ where $Y_{t,k} := e^{i(\widetilde {\Upsilon}_{t,k} - \Upsilon_{t+k}^{-T_{k}\widetilde {f}})} - 1.
+  In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we have, for each $t\geq 0$, that $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq \sum_{k=0}^{\lfloor t^2 \rfloor} \widetilde {\mathbb {P}}_\mu[|Y_{t,k}|]$ where $Y_{t,k} := e^{i(\widetilde {\Upsilon}_{t,k} - \Upsilon_{t+k}^{-T_{k}\widetilde {f}})} - 1.
 $
   We claim that there exist $C_2, \delta_2>0$ such that $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|] \leq C_2e^{-\delta_2 t}$ for each $t\geq 0$ and $k \in \mathbb Z_+$.
-And therefore $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq (t^2+1)C_2e^{-\delta_2 t}$
-%YX which, combined with the fact that $I_1^f(t) - I_0^f(t)$ is linear in $f$, completes this step.
-which completes this step.
-
-%YX We will show this claim in the following substeps 2.1 and 2.2.
+  And therefore $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq (t^2+1)C_2e^{-\delta_2 t}$ which completes this step.
+
   We will show this claim in the following Substeps 2.1 and 2.2.
-%YX First we chose $\gamma\in(0,\tilde \beta)$ close enough to $\beta$
-First we chose $\gamma\in(0, \beta)$ close enough to $\beta$
-so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$; and even closer so that there exists $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
+  First we chose $\gamma\in(0, \beta)$ close enough to $\beta$ so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$; 
+  and even closer so that there exists $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
 We also define $\mathcal{D}_{t,k} :=\{|H_t-H_{t+k}|\leq  e^{-\eta t}, H_{t}> 2e^{-\eta' t}\}$.
@@
 % ******* subStep 2.1
-\emph{Substep 2.1.} Similar to the substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$,
-\(
-\mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}]
-\leq C_{2.1} e^{-\delta_{2.1} t}.
-\)
+  \emph{Substep 2.1.} Similar to the substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} t}$.
   We omit the details.
@@
       = \frac{X_{t+k}(P^\alpha_1T_k\tilde f) - X_{t+k+1}(T_k \tilde f)}{\|X_{t+k}\|^{1 - \tilde \beta}}
- %YX \\& = \sum_{p}
     \\& = \sum_{p\in \mathcal N}
     \langle\tilde f,\phi_p\rangle_\varphi e^{-(\alpha \tilde \beta - |pb|)k}\frac{ X_{t+k}(P_1^\alpha \phi_p) - X_{t+k+1}(\phi_p)}{\|X_{t+k}\|^{1 - \tilde \beta}}
-%YX   \\& = \sum_{p}
     \\& = \sum_{p\in \mathcal N}
@@
   \]
-%YX Similar to the substep 2.2 of
-Similar to Substep 2.2 of
-the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that for all $k\in \mathbb Z_+$ and $t\geq 0$, almost surely $K_{t,k} \leq C_{2.2}'' e^{- (\eta - 3\eta')t}$.
+  Similar to Substep 2.2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that for all $k\in \mathbb Z_+$ and $t\geq 0$, almost surely $K_{t,k} \leq C_{2.2}'' e^{- (\eta - 3\eta')t}$.
   From this and Lemma \ref{lem: control of wt} we know that there exists $C'''_{2.2}$ such that for each $k\in \mathbb Z_+$ and $t\geq 0$,
@@
   \end{align}
-To sum up we have that $\widetilde {\mathbb P}_\mu[e^{iI_2^f(t)}] \xrightarrow[t\to \infty]{} 1$,
-%YX which combined with the fact that $I_2^f(t)$ is linear in $f$, completes this step.
-which completes this step.
+  To sum up we have that $\widetilde {\mathbb P}_\mu[e^{iI_2^f(t)}] \xrightarrow[t\to \infty]{} 1$, which completes this step.
 
@@
   For $z\in \mathbb C_+$,  we have
-  \begin{equation}
+  \begin{align}
     \label{eq: estimate of exponential remaining}
@@
     \leq \frac{|z|^{n+1}}{(n+1)!} \wedge \frac{2|z|^{n}}{n!}, \quad n\in \mathbb Z_+.
-  \end{equation}
+  \end{align}
 \end{lem}
@@
   Notice that $|e^{-z}| = e^{- \operatorname{Re} z} \leq 1$.
-  Therefore,
-%YX \begin{equation}
-$
-|e^{-z} - 1|
-  = \Big| \int_0^1 e^{-\theta z} z d\theta\Big|
-  \leq |z|.
-%YX \end{equation}
-$
+  Therefore, $ |e^{-z} - 1| = \Big| \int_0^1 e^{-\theta z} z d\theta\Big| \leq |z|. $
   Also, notice that $|e^{-z} - 1| \leq |e^{-z}|+1 \leq 2$.
@@
 
-For each $z\in \mathbb C\setminus (-\infty,0]$, we define
-$
-\log z := \log |z| + i \arg z
-$
-where $\arg z \in (-\pi,\pi)$ is uniquely determined by
-$
-z = |z|e^{i \arg z}.
-$ 	
-For all $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$, we define
-$
-z^\gamma := e^{\gamma \log z}.
-$
+For each $z\in \mathbb C\setminus (-\infty,0]$, we define $ \log z := \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined by $ z = |z|e^{i \arg z}$. 	
+For all $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$, we define $ z^\gamma := e^{\gamma \log z}. $
 Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, that $z\mapsto \log z$ is holomorphic in $\mathbb C\setminus (-\infty,0]$.
@@
 \[
-	\Gamma(z+1) = z \Gamma(z),\quad z\in \mathbb C\setminus\{0, -1,-2,\dots\}.
+	\Gamma(z+1) 
+  = z \Gamma(z),\quad z\in \mathbb C\setminus\{0, -1,-2,\dots\}.
 \]
 Using this recursively, one gets that
-\begin{equation}
+\begin{align}
   \label{eq: definition of Gamma function}
@@
   \quad -n< x< -n+1, n\in \mathbb N.
-\end{equation}
+\end{align}
 
@@
 Using the uniqueness of holomorphic extension and Lemma \ref{lem: extension lemma for branching mechanism}, we get that
-\begin{equation}
+\begin{align}
   z^{\beta}
@@
   \quad z\in \mathbb C_+,
-\end{equation}
+\end{align}
 and similarly that
-\begin{equation}
+\begin{align}
   \label{eq: stable branching on C+}
@@
   \quad z\in \mathbb C_+.
-\end{equation}
+\end{align}
 Lemma \ref{lem: extension lemma for branching mechanism} also says that the derivative of $z^{1+\beta}$ is $(1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
@@
   For all $z_0,z_1 \in \mathbb C_+$, we have
-\begin{equation}
+\begin{align}
   \label{eq: Lip of power function}
@@
   \leq (1+\beta)(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
-\end{equation}
+\end{align}
 \end{lem}
@@
   Notice that
-\begin{equation}
+  \begin{align}
     \label{eq: upper bound for beta power of z}
@@
     \quad z \in \mathbb C\setminus (-\infty, 0].
-\end{equation}
+  \end{align}
   Define a path $\gamma: [0,1] \to \mathbb C^0_+$ such that
@@
 We write
-\begin{equation}
+\begin{align}
   H^{(h)}_{(s,t)}
@@
   \quad 0 \leq s \leq t, h \in \mathcal B_b([0,t] \times E,\mathbb C).
-\end{equation}
+\end{align}
+
 \begin{lem}
@@
   Then
-\begin{equation}
+  \begin{align}
     \label{eq: expresion of g}
@@
     := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
-\end{equation}
+  \end{align}
   is the unique locally bounded solution to the equation
@@
   Notice that
-  \begin{equation}
+  \begin{align}
     \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t)| ~ds \Big]
@@
     < \infty.
-  \end{equation}
+  \end{align}
   Also notice that
-  \begin{equation}
+  \begin{align}
     \label{eq: crucial for Feynman-Kac}
@@
     \quad s\in (0,t).
-  \end{equation}
+  \end{align}
   Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
@@
 \[
-  F(x,f):= F(x,f(x)),\quad x\in E.
+  F(x,f)
+  := F(x,f(x)),\quad x\in E.
 \]
@@
   the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
-\begin{equation}
+\begin{align}
   \label{eq: branching mechanism}
@@
   -\rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
-\end{equation}
+\end{align}
 where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$;
@@
   $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
-  \begin{equation}
+  \begin{align}
     \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
     \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
-  \end{equation}
+  \end{align}
   where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
-  \begin{equation}
+  \begin{align}
     \label{eq:FKPP_in_definition}
@@
     \quad t \geq 0, x \in E.
-  \end{equation}
+  \end{align}
 \end{itemize}
@@
 Define
-\begin{equation}
+\begin{align}
   \psi'(x,z)
@@
   \quad x\in E, z\in \mathbb C_+.
-\end{equation}
+\end{align}
 Then according to Lemma \ref{lem: extension lemma for branching mechanism}, for each $x \in E$, $z \mapsto \psi(x,z)$ is a holomorphic function on $\mathbb C_+^0$ with derivative $z \mapsto \psi'(x,z)$.
@@
 We define the mean semigroup
-\begin{equation}
+\begin{align}
   P_t^{\rho_1} f(x)
@@
   \quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
-\end{equation}
+\end{align}
 It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M(E)$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
-\begin{equation}
+\begin{align}
   \label{eq: mean formula for superprocesses}
@@
   =\mu(P^{\rho_1}_t f).
-\end{equation}
+\end{align}
 
@@
 Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
-\begin{equation}
+\begin{align}
   \mathbb N_x[\langle W_t, f\rangle]
@@
   \quad f\in L_1(\xi), t > 0,x\in E.
-\end{equation}
+\end{align}
 This says that the random variable $\langle X_t, f\rangle$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
@@
 Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta \langle W_t, f\rangle} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
-\begin{equation}
+\begin{align}
   \label{eq: N and characteristic exponent}
@@
   \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
-\end{equation}
+\end{align}
 
@@
   for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
-\begin{equation}
+  \begin{align}
     \label{eq: upper bound of psi(v)}
@@
     \leq C P^{\rho_1}_t |f|(x) + C (P^{\rho_1}_t |f| (x))^2.
-\end{equation}
+  \end{align}
 \end{lem}
+
 \begin{proof}
@@
   we have
-  \begin{equation}
+  \begin{align}
     \label{eq: -v has positive real part}
@@
     \leq 0.
-  \end{equation}
+  \end{align}
   Therefore, we can speak of $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
   According to Lemma \ref{lem: estimate of exponential remaining}, we have that
-  \begin{equation}
+  \begin{align}
     \label{eq: upper bound for vf}
@@
     \leq (P^{\rho_1}_t |f|)(x).
-  \end{equation}
+  \end{align}
   Notice that, for any compact $K \subset \mathbb R$,
-  \begin{equation}
+  \begin{align}
     \label{eq: estimate of deriavetive of v(theta)}
@@
     \leq (P^{\rho_1}_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
-  \end{equation}
+  \end{align}
   Therefore, according to \cite[Theorem A.5.2]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent}, $ U_t( \theta f)( x )$ is differentiable in $\theta \in \mathbb R$ with
@@
   Moreover, from the above, it is clear that
-  \begin{equation}
+  \begin{align}
     \label{eq: upper bounded for derivative of v(theta)}
@@
     \leq ( P^{\rho_1}_t |f|)(x).
-  \end{equation}
+  \end{align}
   It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_t(\theta f)(x)$ is continuous in $\theta$.
@@
   Thus,
-  \begin{equation}
+  \begin{align}
     \label{eq: path integration representation of psi(v)}
@@
     = -\int_0^1 \psi'\big(x,-U_t(\theta f)\big) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
-  \end{equation}
+  \end{align}
   Notice that
@@
   where $C_1, C_2$ are constants independent on $f,x$ and $t$.
-  Now, combining the display above with \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bounded for derivative of v(theta)}
-  we get the desired result.
+  Now, combining the display above with \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bounded for derivative of v(theta)} we get the desired result.
 \end{proof}
+
 This lemma also says that if $f\in L^2(\xi)$ then
@@
 In this subsection, we will prove the following:
+
 \begin{prop}
@@
   If $f\in L_2(\xi)$,  then for all $t\geq 0$ and $x\in E$,
-\begin{equation}
+\begin{align}
   \label{eq: complex FKPP-equation}
@@
   = i \Pi_x [f(\xi_t)].
-\end{equation}
-\begin{equation}
+\end{align}
+\begin{align}
   \label{eq: complex FKPP-equation with FK-transform}
@@
   = iP_t^{\rho_1} f(x).
-\end{equation}
+\end{align}
 \end{prop}
@@
 Suppose that $\mathbf P_{\delta_x}[\langle X_T, f\rangle] = \mathbb N_x[\langle W_T, f\rangle] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
-\begin{equation}
+\begin{align}
   d\mathbf P_{\delta_x}^{\langle X_T, f\rangle}
@@
   :=  \frac{\langle W_T, f\rangle}{P_T^{\rho_1} f(x)} d\mathbb N_x.
-\end{equation}
+\end{align}
 Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{\langle W_T, f\rangle}$ if
@@
   the spine process $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$, where
-  \begin{equation}
+  \begin{align}
     d\Pi_x^{(f,T)}
     := \frac{f(\xi_T)e^{\int_0^T \rho_1(\xi_s)ds}}{P^{\rho_1}_T f(x)} d \Pi_x;
-  \end{equation}
+  \end{align}
 \item
@@
 is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
-\begin{equation}
+\begin{align}
   \label{eq: conditional intensity}
@@
   := 2 \rho_2(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-\end{equation}
+\end{align}
 \item
   $\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M(E)$-valued process defined by
-  \begin{equation}
+  \begin{align}
     Y_t
@@
     \quad 0 \leq t\leq T.
-  \end{equation}
+  \end{align}
 \end{itemize}
 According to the spine decomposition theorem in \cite{RenSongSun2017Spine}, we have that
-\begin{equation}
+\begin{align}
   \label{eq: Spine decomposition 1}
@@
   \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{\langle W_T, f\rangle} \},
-\end{equation}
-\begin{equation}
+\end{align}
+\begin{align}
   \label{eq: Spine decomposition 2}
@@
   \overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
-\end{equation}
+\end{align}
 
@@
   According to \eqref{eq: Spine decomposition 1}, we have that
-\begin{equation}
+  \begin{align}
     \frac{\mathbf P_{\delta_x}[\langle X_t,f^{\pm}\rangle e^{i \langle X_t,f\rangle}]}{\mathbf P_{\delta_x}[\langle X_t,f^{\pm}\rangle ]}
     = \mathbf P_{\delta_x}[e^{i \langle X_t,f\rangle}] \mathbb N_x^{\langle W_t,f^{\pm}\rangle}[e^{i \langle X_t,f\rangle}].
-\end{equation}
+  \end{align}
   Using \eqref{eq: N to Pi} and the above, we have
@@
   Therefore, we have
-\begin{equation}
+  \begin{align}
     \frac{\partial}{\partial \theta} {U_t(\theta f)(x)}
@@
     = \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
-\end{equation}
+  \end{align}
   Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
@@
   Fubini's theorem, \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bound of psi'(v)}, we get
-\begin{equation}
+  \begin{align}
     U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-U_{t-s}f\big) ~ds\Big]
     = i \theta \Pi_{r,x} [f(\xi_t)]
-\end{equation}
+  \end{align}
   and
-\begin{equation}
+  \begin{align}
     U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
     = i \Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
-\end{equation}
+  \end{align}
   Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} are true if $f\in \mathcal B_b(E)$.
@@
   From what we have proved, we have
-\begin{equation}
+  \begin{align}
     \label{eq: complex FKPP-equation for fn}
@@
     = i \Pi_{x} [f_n(\xi_t)].
-\end{equation}
+  \end{align}
   Note that

### 2019-09-02 response.tex
add response.tex

% * The preamble
% ! This TeX file uses 'amsart' for its document class.
\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\calclayout
% ! 'amsmath', 'amsthm', 'amsfonts' package is automatically loaded by 'amsart' class.
% ! Below is the configuration of 'amsmath' package.
\numberwithin{equation}{section}
\allowdisplaybreaks
% ! Below is the configuration of 'amsthm' package.
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollaray}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\newtheorem{iss}{Issue}
\newtheorem{rem}[thm]{Remark}
\newtheorem*{ack}{Acknowledgment}
% ! 'inputenc' package is used to specify the set of characters allowed to input into this TeX file.
% \usepackage[utf8]{inputenc}
% ! 'foutenc' package is used to specify the set of characters allowed to output into the generated pdf file.
% \usepackage[T1]{fontenc}
% ! 'amssymb', 'mathrsfs' and 'mathtools' packages provide additional math symbols from the AMS default symbol fonts. They are compatible with the AMS class and is recommended to be used.
\usepackage{amssymb}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{mathrsfs}
% ! 'hyperref' package is used to handle cross-referencing in the generated pdf file.
\usepackage[backref]{hyperref}
% ! Other packages
\usepackage{xcolor}
\usepackage{comment}
% * Top matter
\begin{document}
\title
[Response]
{Response}
\maketitle
% * Document body
We are grateful to the referees for their helpful comments.
We have incorporated all the comments made by the referees.
Here are the specific changes in response to the comments of the referees.
\begin{enumerate}
\item
  P.2.L.-11. 
  Please provide an interpretation of the form of $\psi$. 
  If you were to approximate this superprocess by a branching particle system, what are the implications on the distribution of the number of off-springs? 
  Does the term $\psi_1$ imply that the offspring distribution is heavy tailed?

  \emph{We add an interpretation in Remark 1.1.}
\item
  P.2.L.-8. 
  Please provide an interpretation of the expression $\alpha\beta - \kappa f b(1+\beta)$?

\emph{We add some discussion about this in the middle of page 7.}.

  Perhaps it might be easier to interpret if you wrote the inequality $\alpha \beta > \kappa f b(1 + \beta)$ as $\alpha \frac{\beta}{1+\beta} > \kappa f b$.
  This way the parameters on the left are branching related, whereas the parameters on the right are related to the Ornstein-Uhlenbeck process.

  \emph{We now write it as $\alpha \tilde \beta > \kappa b$ where $\tilde \beta := \frac{\beta}{1+\beta}$.}

  Is there an intuitive explanation why $\rho$ doesn’t play a role? 
  Why does $b$ come into play but $\sigma$ does not?

  \emph{We added some discussion about this at the end of subsection 1.2}.
\item
  P.4.Equation.(1.5). 
  Please provide an interpretation of the form of the invariant density. 
  For example, you can mention that it has a mode at the origin, it is symmetric around the origin and $b$ determines the spread etc.

\emph{We mentioned there that it is symmetric Gaussian.}

  Please also give some intuition about the role of the $\sigma^2$ specific form of density in the results. 
  If the invariant density had different properties, would the results still hold?

  \emph{We added some discussion about this at the end of subsection 1.2}.
\item
  P.5.L.-9. 
  Please provide an interpretation of $\kappa_f$. 
  What does it mean for $\kappa_f$ to be large or small?

  \emph{We add some discussion about this in the middle of page 7.}.

\item
  P.5.L.-3. 
  Please explain why the three cases are referred to as large, critical and small branching rate regimes?

  \emph{We add some explanation at the beginning of page 6.}
\item
  P.6. 
  Why is Theorem 1.5 restricted to test functions in $\mathcal C_l$, whereas Theorem 1.6 and 1.7 allow $f$ to be in $\mathcal P$? 
  Is this a limitation of the methodology used or there is a more substantial reason? 
  Please explain.

  \emph{We added some explanation about this after Theorem 1.4.}
\item
  There is substantial repetition in the statements of Theorem 1.5, 1.6 and 1.7. 
  These can be combined into a single Theorem, and differences can be managed as different cases in the same proof.

  \emph{They are now unified in the new Theorem 1.4.}
\item
  P.8. 
  Definitions of $m(f ), \tilde m(f ), \bar m(f )$ can be combined into a single definition, and instead of using different notation $\tilde m, \bar m$, the definition of $m(f)$ can be extended to f in the critical and the large branching rate regimes by the formula given for $\tilde m$ and $\bar m$.

  \emph{Their definitions are now unified in (1.9).}
\item
  P.8.
  Instead of calling this section “some intuitive explanation”, it would be more appropriate to call it “an outline of the methodology”.

  \emph{Done as suggested.}
\item
  P.10.L.1.
  Please provide an interpretation of the examples for $\psi$?
  In which contexts do these examples arise?

  \emph{TBD.}
\item
  P.12. Lemma.2.4. 
  There is substantial repetition in statements 2 and 3, please combine these into one statement. 
  In fact, it would be even better if all the hypothesis on the operators, index sets , etc can be given at the beginning of the lemma, and then all the results can be listed without saying “Suppose that” each time. 
  Similarly assumptions don’t need to be restated in the proof. 
  There are duplications in the proof, these should be removed as well. 
  For example you can say, “If $f,g \in \mathcal P^+$ with $f \leq g$, then $R_AR_Bf \leq R_AR_Bg$, and $R_A \times R_B f \leq R_A \times R_B g$ and $R_A +R_B f \leq (R_A +R_B)g$, and ...”. 
  These should reduce the length of Lemma 2.4 and and its proof by half.

  \emph{The presentation of Lemma 2.4 is now rearranged and its proof is now omitted, since the results are easy to verify.}
\item
  P.16-17.Lemma 2.6., Proposition 2.7. 
  If you use a single notation $m_t(f)$, instead of $m_t, \bar m$ and $\tilde m$ , you can simply say that $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of ...” without repeating it 5 times. 
  No need to provide separate statements for $m_t$ and $m$, since $m$ can be considered as a special case of $m_t$ for a suitable value of $t$, (e.g. $t = \infty$, or $t = \Delta$.)

  \emph{We now uses the single notation $m_t[f]$. Now the presentation of Lemma 2.6 and Proposition 2.7 is much shorter.}
\item
  P.19.
  Combine Lemma 2.9 and 2.10 into a single Lemma.

  \emph{We now unify them in the new Lemma 2.9.}
\item
  P.20.L.3. 
  Please give a reference after the statement “It is well known that”.

  \emph{We add a new reference above equation (2.7) as suggested.}
\item
  P.22.L.8-12. 
  The argument given here is not clear. 
  Please provide more details.

  \emph{We rearranged that sentence. See the sentence right after (2.10).}
\item
  P.22. Equations. 2.18-2.19. 
  These equations can be stated in a single line. 
  For example, “if $0< \lambda \leq v_t(\lambda) < \bar v < v_t(\lambda^*)<\lambda^* < \infty$, then...”.

  \emph{We rearranged that sentence. See the last sentence of Page 18.}

\item
  P.24. 
  Please give more details about the argument from [10, Theorem 3.3.6].

  \emph{We added more details there. See the last display on page 20.}

\item
  P.27.Line.-2. 
  Typo. ``..is an eigenfunction of $L$, ...''.

  \emph{Corrected as suggested.}
\item
  Page 31. Lemma 3.4 and Lemma 3.7 are nearly duplicates of each other. 
  They should be written in a unifying way to cover both cases. Same applies to their proofs.

  \emph{We added a new subsection 3.2 which deals with the CLTs for one unite time intervals in a unified way.}
\item
  Proof of Lemma 3.4. Please indicate clearly where $\alpha \beta \leq \kappa f b(1 + \beta)$ is used. 
  Same goes for the case $\alpha beta > \kappa f b(1 + \beta)$.

  \emph{It turns out that the proof of Lemma 3.4 doesn't use this condition. In the new version, We added a new subsection 3.2 which deals with the CLTs for one unite time intervals in a unified way.}

\item
  P.40.
  The proof of Theorem 1.7 is very similar to the proof of Theorem 1.6 with the exception of Step 2. 
  Please combine these two proofs into one, and deal with differences as separate cases in the same proof (case 1: $\alpha \beta = \kappa f b(1 + \beta)$, case 2: $\alpha \beta < \kappa_f b(1 + \beta)$.)

  \emph{We agree that the structure of these two proofs are very similar. But there are differences lying in the details even out of the range of Step 2 which we believe is crucial. For example:  at the beginning, the scaling coefficient in case 1 is $\|tX_t\|^{\frac{1}{1+\beta}}$ but in case 2 is $\|X_t\|^{\frac{1}{1+\beta}}$; (ii) In Step 4, the exceptional event for case 1 is chosen as $\mathcal E_t = \{\|X_t\| > t^{-1/2} e^{\alpha t}\}$ but in case 2 is chosen as $ A_t(\epsilon) = \{\|X_t\|> e^{(\alpha - \epsilon )t}\}$. }

\emph{    
    Nonetheless, in the new version, the proof of CLTs for three different cases (Subsection 3.3, 3.4 and 3.5) are rearranged in such a way that (1) their structure can be clearly compared; and (2) trivial duplications are avoided as much as possible.
}

\item
  P.45. 
  The proof of Lemma 3.8. is very similar to the proof of Proposition 3.6, please revise Proposition 3.6 to cover the case in Lemma 3.8.

  \emph{They are now unified in the new Corollary 3.6.}

\item
  P.46.Lemma 3.9 and Lemma 3.10. should be stated before the proof of Theorem 1.6 in more general way, that they can be used in the proof of both cases of CLT $\alpha \beta \leq \kappa_f b(1 + \beta)$ and $\alpha \beta > \kappa_f b(1 + \beta).$

  \emph{These two lemmas are now deleted, and their proofs are moved into the new subsection 3.5. 
In the new version, the proof of CLTs for three different cases (Subsection 3.3, 3.4 and 3.5) are rearranged in such a way that (1) their structure can be clearly compared; and (2) trivial duplications are avoided as much as possible.}
\end{enumerate}
\end{document}

### 2019-09-07 supCLT.tex
change supCLT.tex

@@
 \begin{abstract}
-  % ADDED
-  In this paper, we study the asymptotic behaviors of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$
-  % Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$.
+  In this paper, we study the asymptotic behavior of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$
   whose underlying spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ where $\sigma, b >0$;
-  % Let $\psi$ be a branching mechanism which is close to a function of the form $\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-  and whose branching mechanism $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that, while $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
-  % In this paper, we study asymptotic behaviors of $(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$.
-  Some law of large numbers and $(1+\beta)$-stable central limit theorems are established for $(\langle f, X_t\rangle )_{t\geq 0}$ where the testing function $f$ is assumed to be of polynomial growth.
-  % Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
-  % the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$;
-  % the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$;
-  % and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.
-  A phase transition arises for the central limit theorems in the sense that three different type of results can be obtained which correspond to whether the branching rate $\alpha$ is relatively small, large or at a critical balanced value.
+  and whose branching mechanism $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that,
+ when $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
+  Some law of large numbers and $(1+\beta)$-stable central limit theorems are established for
+  $(X_t(f) )_{t\geq 0}$, where the function $f$ is
+  assumed to be of polynomial growth.
+Some phase transitions arise  for the central limit theorems in the sense that the forms of the central limit theorem are different in three different regimes corresponding the branching rate being relatively small, large or at a critical balanced value.
 \end{abstract}
@@
 where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)~\pi(dy)< \infty$.
-$\psi$ is referred to as the branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
+$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
 Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)=\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
+For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$,
+ write $\mu(f)= \int f(x)\mu(dx)$
+and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
 We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
@@
 We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
-% on a measurable space $(\Omega, \mathcal{F})$ 
-on a measurable space $(\Omega, \mathscr{F})$ 
+on  $(\Omega, \mathscr{F})$
 is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
@@
   \label{eq: def of V_t}
-  \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
-  = e^{-\langle V_tf, \mu \rangle}
+  \mathbb{P}_{\mu}[e^{-X_t(f)}]
+  = e^{-\mu(V_tf)}
   , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
@@
 
-The strong law of large numbers for the super-OU process $X$ introduced at the beginning can be stated as follows:
-Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e.
-continuous bounded non-negative function $f$ on $\mathbb R^d$, we have $\lim_{t\to\infty} e^{-\alpha t} \langle f, X_t\rangle =H_\infty\langle f, \varphi\rangle $, where $H_\infty$ is the limit of the martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
+The strong law of large numbers for the super-OU process $X$ above can be stated as follows:
+Under some conditions on $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below),
+there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e.
+continuous bounded non-negative function $f$ on $\mathbb R^d$, we have
+ $\lim_{t\to\infty} e^{-\alpha t} X_t(f) =H_\infty\langle f, \varphi\rangle $,
+where $H_\infty$ is the limit of the martingale $e^{-\alpha t}X_t(1)$
+and $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
 See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
@@
 In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
-% Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
-Our key assumption is that the branching mechanism $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that, while $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
-The general goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that $ (\langle f, X_t \rangle -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
-Note that, in the setting of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
-
-There are many papers studying CLTs for branching processes, branching diffusions and superprocesses under the second moment condition.
-See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
-These two papers made connections between the CLTs and the branching rate regimes.
-Some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only a second moment condition were established in \cite{RenSongZhang2014Central}.
+Our key assumption is that $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that,
+when  $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
+Our  goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that
+$ (X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
+Note that, in the setting of this paper, $X_t(f)$ typically have infinite second moment.
+
+There are many papers on CLTs for branching processes, branching diffusions and superprocesses under the second moment condition.
+See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes),
+\cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some}
+for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
+Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some
+spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
+These two papers made connections between CLTs and branching rate regimes.
+Some spatial CLTs  for supercritical super-OU  processes with branching mechanisms satisfying only a second moment condition were established in \cite{RenSongZhang2014Central}.
 Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
 Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
-The functional version of the CLTs was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
-
-There are also many limiting theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moments.
+The functional version of the CLT was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
+
+There are also many limit theorems for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment.
 Heyde \cite{Heyde1971Some} established some  CLTs for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit laws are stable laws.
@@
 under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
-Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable branching law.
-They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
-We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.
-
-As far as we know, this paper is the first to study spatial central limit theorems for supercritical superprocesses without the second moment condition.
+ Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable offspring distribution.
+They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any CLT type result in the large branching rate regime
+We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior
+of a class of critical superprocesses with spatially dependent stable branching mechanism.
+
+As far as we know, this paper is the first to study spatial CLTs for supercritical superprocesses without the second moment condition.
 
@@
   \label{asp: Greys condition}
-  The branching mechanism satisfies Grey's condition, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+  The branching mechanism $\psi$ satisfies Grey's condition, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
 \end{asp}
-For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
+For $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \mu(1)$.
 It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event} $D :=\{\exists t\geq 0,~\text{s.t.}~ \|X_t\| =0 \}$ has positive probability with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
-% In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ for each $\mu\in \mathcal M(\mathbb R^d)$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
 In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
@@
     \label{eq: asp of branching mechanism}
-    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
+    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
   \end{align}
@@
 	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statement:
-	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
+	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for all small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
 
@@
   \label{rem:SP}
-% Assumption \ref{asp: branching mechanism} says that there exist constants $\eta>0$ and $\beta > 0$ such that the L\'evy measure $\pi(dy)$ is ``not too far away'' from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
-Roughly speaking, Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is ``not too far away from $\widetilde \psi(z) := - \alpha z + \eta z^{1+\beta}$ near $0$''.
- % In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of $-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
-In fact, if we consider their differences
+Roughly speaking, Assumption \ref{asp: branching mechanism} says that $\psi$ is ``not too far away'' from $\widetilde \psi(z) := - \alpha z + \eta z^{1+\beta}$ near $0$.
+In fact, if we consider their difference
 \begin{align}
@@
 One can further write that $\psi(z) = - \alpha z + z^{1+\beta} l(z)$ where $l$ is a function on $[0,\infty)$ which is slowly varying at $0$.
-% END ADDED
 \end{rem}
@@
 \begin{rem}
-It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y~\pi(dy) < \infty.
-$
+It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism},
+ $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y~\pi(dy) < \infty. $
 This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
@@
 % **** Mean semigroup
-% ADDED
-Let us introduce some notation in order to give a precise formulation of our main result.
-% END ADDED
+Let us introduce some notation in order to give the precise formulation of our main result.
 Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
@@
 \(
-  \mathbb{P}_{\mu}[\langle f, X_t \rangle]
-  = \langle P^\alpha_t f, \mu \rangle,
+  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f),
 \)
 for each $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
-% The limiting behavior of the super-OU process is closely related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.
 
 % **** Spectral Property
-The limiting behavior of the super-OU process is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
-% It is known that the OU process $\xi$ has an invariant density
+The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
 It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
@@
   :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx
-  % \quad x\in \mathbb R^d.
 \end{align}
 which is a   symmetric multivariate Gaussian distribution.
-% Let \[L^2(\varphi):= \Big\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \Big\}.\]
-% Then $L^2(\varphi)$ is a Hilbert space with inner product
 Let $L^2(\varphi)$ be the Hilbert space with inner product
@@
 It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
-For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$, where
+For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$, where
 \begin{align}
@@
 \)
-for each $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
+for all $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
 Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
@@
 Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
-For each $p\in \mathbb{Z}_+^d$, define
+For $p\in \mathbb{Z}_+^d$, define
 \(
   H_t^p
-  := e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle
+  := e^{-(\alpha-|p|b)t}X_t(\phi_p)
 \)
-with $t\geq 0$.
+for all $t\geq 0$.
 If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lem:M:L:ML} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
@@
   \[
-    e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle
+    e^{-(\alpha-\kappa_fb)t}X_t(f)
     \xrightarrow[t\to \infty]{}\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p
@@
 \(
-  e^{-\alpha t}\langle f, X_t\rangle
+  e^{-\alpha t}X_t(f)
   \rightarrow \langle f, \varphi\rangle H_{\infty}
@@
 % **** Stable CLT
-% For the rest of this subsection, we focus on the central limit theorems of $\langle f, X_t\rangle$ for $f\in \mathcal P\setminus \{0\}$.
-For the rest of this subsection, we focus on the central limit theorems of $\langle f, X_t\rangle$ for some $f\in \mathcal P\setminus \{0\}$.
+For the rest of this subsection, we focus on the CLTs of $X_t(f)$ for a large collection of $f\in \mathcal P\setminus \{0\}$.
 Write $\tilde u = \frac{u}{ 1+ u}$ for each $u \neq -1$.
@@
 \item
-  the small branching rate case where $f \in \mathcal C_s := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta < |p| b \}$;
-\item
-  the critical branching rate case where $f \in \mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $; and
-\item
-  the large branching rate case  where $f \in \mathcal C_l   := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
+  the small branching rate case: where
+$f$ satisfies $\alpha \tilde \beta < \kappa_f b$;
+\item
+  the critical branching rate case: where
+$f$ satisfies $\alpha \tilde \beta = \kappa_f b$; and
+\item
+  the large branching rate case:  where
+$f$ satisfies $\alpha \tilde \beta > \kappa_f b$.
 \end{enumerate}
-Here, the small (rspt.
-large) branching means that the branching rate $\alpha$ is relatively small (rspt.
-relatively large); and the critical branching means that the branching rate $\alpha$ is at a critical balanced value.
-To present our result, let us define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
+Here, the small (resp. large) branching rate case means that the branching rate $\alpha$ is small (resp. large) compared to $\kappa_f$;
+ and the critical branching rate means that the branching rate $\alpha$ is at a critical balanced value compared to $\kappa_f$.
+To present our result, we define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
 \begin{align}
@@
   T_t f
-  := \sum_{p \in \mathbb Z_+^d} e^{-| |p|b - \alpha \tilde \beta |t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
+  := \sum_{p \in \mathbb Z_+^d} e^{-| |p|b - \alpha \tilde \beta |t} \langle f, \phi_p \rangle_{\varphi}  %\phi_p,
+\phi_p
   ,\quad t\geq 0, f\in \mathcal P,
 \end{align}
-and a family of $\mathbb C$-valued functionals $(m_t)_{0 \leq s \leq t < \infty}$ on $\mathcal P$ by
+and a family of $\mathbb C$-valued functionals 
+%Jianjie $(m_t)_{0 \leq s \leq t < \infty}$ on $\mathcal P$ 
+$(m_t)_{0 \leq t < \infty}$ on $\mathcal P$ 
+by
 \begin{align}
@@
 \end{align}
-For each $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below we will show that
+Define $ \mathcal C_s := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
+and $ \mathcal C_l   := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
+For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
 \begin{align}
@@
 \end{align}
-is well defined, and moreover, there exists an $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}$.
-Let us now give the main results of this paper.
+is well defined, and moreover, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}$.
+The main result of this paper is as follows.
 
@@
   \label{thm:M}
-  Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$.
-  Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, the follows hold:
+ If $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$, then under $\mathbb{P}_{\mu}(\cdot|D^c)$, the following hold:
 \begin{enumerate}
@@
 
-% ADDED
-At this point, we should mention that the CLTs above did not cover for all polynomial growth testing functions $f\in \mathcal P$.
-Indeed, considering a general $f \in \mathcal P$ which can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c\setminus\{0\}$ and $f_l \in \mathcal C_l$, as a simple corollary of Theorem \ref{thm:M}, one can verify that
-\[
-  \|tX_t\|^{-\frac{1}{1+\beta}} \Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big)
-  \xrightarrow[t\to \infty]{d}
-  \zeta^{f_c}
-\]
-for each $\mathbb P_\mu(\cdot | D^c)$ with $\mu \in \mathcal M_c(\mathbb R^d)\setminus \{0\}$.
-However, in the case that $f_c\equiv 0$, $f_s\not \equiv 0$ and $f_l\not \equiv 0$, it seems hard to establish any non-trivial CLTs for $X_t(f)$ using the methodology of this paper.  
-In general, we conjecture that under the condition of Theorem \ref{thm:M} the random vector
-\begin{align}
-  \|X_t\|^{- \frac{1}{1+\beta}} \Big( X_t(f_s) ,t X_t(f_c),  X_t(f_l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} \Big)
-\end{align}
-convergences in distribution to $(\zeta^{f_s},\zeta^{f_c}, \zeta^{-f_l})$ where $\zeta^{f_s}$, $\zeta^{f_c}$ and $\zeta^{-f_l}$ are independent.
-Similar convergence has already been proved under the second moment condition, see \cite{RenSongZhang2015Central}.
-
-Let us now give some intuitive explanation of this phase transition. 
-First we mention that the super-OU process arises as the ``high density'' limit of the superposition of a sequence of branching-OU processes, see \cite{Li2011Measure-valued} for example.
-And similar phase transition have already been discussed in the context of branching-OU processes, see \cite{MarksMilos2018CLT}. 
-Though it is hard to describe rigorously, one can consider superprocess as a branching particle system with infinitely many infinitesimal particles, and we employ this particle picture only for the sake of this interpretation.
-It is believed that this phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing. 
-The coarsening effect corresponds to the increasing of the spatial inequality and is a consequence of the branching: simply an area with more particles will produce more offspring.
-The smoothing effect corresponds to the decreasing of the spatial inequality and is a consequence of the mixing property of the OU processes: each OU particles will ``forget'' its initial position exponentially fast.
-
-Let us consider $X_t(\phi_p)$ as an example, and discuss how parameters $\alpha, \beta, b$ and $|p|$
-influences those two effects:
+At this point, we should mention that the theorem above does not cover all $f\in \mathcal P$.
+%Indeed, considering a general $f \in \mathcal P$ which can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c\setminus\{0\}$ and $f_l \in \mathcal C_l$, as a simple corollary of Theorem \ref{thm:M},
+%one can verify that
+%\[
+%  \|tX_t\|^{-\frac{1}{1+\beta}} \Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big)
+%  \xrightarrow[t\to \infty]{d}
+%  \zeta^{f_c}
+%\]
+%for each $\mathbb P_\mu(\cdot | D^c)$ with $\mu \in \mathcal M_c(\mathbb R^d)\setminus \{0\}$.
+Theorem \ref{thm:M}.(1) can be rephrased as if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$.
+Combining the first two parts of Theorem \ref{thm:M}, one can easily get that  if $f\in \mathcal P$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$,
+$ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
+A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c\setminus\{0\}$ and $f_l \in \mathcal C_l$. For $f\in  \mathcal P$
+satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ maybe non-trivial.
+In this case, we do not have a CLT yet.
+We conjecture that the limit random variables in Theorem \ref{thm:M} for $ f\in \mathcal C_s$, $f\in \mathcal C_c$ and $ f\in \mathcal C_l$ are independent. If this is valid, we can
+get a CLT for $ X_t(f)$ for all $f\in  \mathcal P$.
+This independence is valid  under the second moment condition, see \cite{RenSongZhang2015Central}.
+We leave the question of independence of the limit stable random variables to a future project.
+
+ We now give some intuitive explanation of the branching rate regimes and the  phase transition.
+Similar explanation has been given in the context of branching-OU processes, see \cite{MarksMilos2018CLT}.
+First we mention that a super-OU process arises as the ``high density'' limit of a sequence of branching-OU processes, see \cite{Li2011Measure-valued} for example.
+A superprocess can be thought of as a cloud of infinitesimal branching ``particles'' moving in space.
+The phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing.
+The coarsening effect corresponds to the increase of the spatial inequality and is a consequence of the branching: simply an area with more particles will produce more offspring.
+The smoothing effect corresponds to the decrease of the spatial inequality and is a consequence of the mixing property of the OU processes: each OU ``particle'' will ``forget'' its initial position exponentially fast.
+
+Let us consider $X_t(\phi_p)$ as an example and discuss how the parameters $\alpha, \beta, b$ and $|p|$
+influence those two effects:
 \begin{itemize}
@@
   The branching rate $\alpha$ captures the mean intensity of the branching in the system.
-  Therefore, lager the branching rate $\alpha$, stronger the coarsening effect.
-\item
-  The tail index $\beta$ describes the heaviness of the tail of the offspring numbers which belongs to the attraction of some $(1+\beta)$-stable random variable. 
-When $\beta$ is smaller i.e. the tail is heavier, then it is more likely that an area with few particles can suddenly have a large amount of offspring. 
-In other words, larger the tail index $\beta$, stronger the coarsening effect. 
-\item
-  The drift parameter $b$ captures the level of the mixing property of the OU particles.
-  Larger the drift parameter $b$, faster the OU-particles forgetting their initial position, and therefore stronger the smoothing effect.
-\item
-  The order $|p|$ describes the ability of the testing function $\phi_p$ while capturing the mixing property of the OU particles. 
+  Therefore, the lager the branching rate $\alpha$, the stronger the coarsening effect.
+\item
+  The tail index $\beta$ describes the heaviness of the tail of the offspring distribution which belongs to the domain of attraction of some $(1+\beta)$-stable random variable.
+When $\beta$ is smaller i.e. the tail is heavier, then it is more likely that 
+one particle can suddenly have a large amount of offspring.
+In other words, the larger the tail index $\beta$, the smaller the fluctuation of offspring number, and then the stronger the coarsening effect.
+\item
+ The drift parameter $b$ is related to the level of the mixing property of the OU particles.
+  The larger the drift parameter $b$, the faster the OU-particles forgetting their initial position, and therefore the stronger the smoothing effect.
+\item
+    The order $|p|$ is related to the capability of $\phi_p$ capturing the mixing property of the OU particles.
   In particular, in the case that $|p| = 0$, no mixing property can be captured by $\phi_p \equiv 1$ since we are only considering the total mass $\|X_t\|$.
-  In general, higher the order $|p|$, more mixing property can be captured by the testing function $\phi_p$, and therefore stronger the smoothing effect.
+  In general, the higher the order $|p|$, the more mixing property can be captured by $\phi_p$, and therefore the stronger the smoothing effect.
 \end{itemize}
-We also discuss the role of other parameters $\rho, \eta$ and $\sigma$ in our model:
+Here we discuss the role of the other parameters $\rho, \eta$ and $\sigma$ in our model:
 \begin{itemize}
 \item
-  The coefficient $\rho$ dose not influences the results since the second term $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$ (See Remark \ref{rem:SP}). 
+  The coefficient $\rho$ dose not influence the result since $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$
+  (see Remark \ref{rem:SP}).
 \item
@@
 \end{itemize}
-% END ADDED
 
@@
 \subsection{An outline of the methodology}
-% Here we give some intuitive explanation of the central limit theorems above.
 Let us give some intuitive explanation of the methodology used in this paper.
-% Deleted
-% The main ideas are similar to those given in \cite{MarksMilos2018CLT} for branching OU processes.
-% End delted
 For any $\mu\in \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
@@
 We will use the shorter notation $\mathcal I_s^t Y$ when there is no danger of confusion.
-For each $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
-\begin{align}
-  % \langle f,X_t\rangle
+For $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
+\begin{align}
   X_t(f)
@@
 \end{align}
-To find the fluctuation of $\langle f,X_t\rangle$, we will investigate the fluctuation of each term on the right hand side above.
-% DELETED
-% Recall $\|X_t\|\sim e^{\alpha t}$ as $t\to\infty$.
-% END DELETED
-The second term and third term are negligible after the rescaling, and for the first term we will establish some multi-variant unite-interval CLTs which says that
+To find the fluctuation of $X_t(f)$, we will investigate the fluctuation of each term on the right hand side above.
+The second term and third term are negligible after the rescaling, and for the first term we will establish
+a multi-variate unit interval CLT  which says that
 \[
@@
 \]
-where $(\zeta_k)_{k \in \mathbb N}$ are some independent $(1+\beta)$-stable random variables.
-% So if $f\in \mathcal C_s$, i.e., $\alpha \tilde \beta < \kappa_f b$, we have roughly that
-% \[
-%  \frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
-%  \xrightarrow[t\to \infty]{d} \zeta\overset{d}{=}\sum_{k=0}^\infty \zeta_k,
-% \]
+where $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables.
 If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \xi^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have
@@
 \)
-% DELETED
-\begin{comment}
-In the explanation above, we have used the facts that $(\zeta_k)_{k\in \mathbb N}$, $\zeta$ are all well defined, and
-\begin{align}
-  \label{eq: equatlity for mf for small rate}
-  m[f]
-  = \sum_{k=0}^\infty \langle Z_1 T_k \tilde f,\varphi \rangle,\quad f\in\mathcal C_s.
-\end{align}
-These facts will be made clear in Lemma \ref{lem:m} and formula \eqref{eq:PM:CLTS:2}.
-
-If $f\in \mathcal C_c$, i.e., $\alpha \tilde \beta = \kappa_f b$,
-then
-\[
-  m[f]
-  = \lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}\langle Z_1 T_k \tilde f,\varphi \rangle, \quad f\in \mathcal C_c.
-\]
-In this case, we roughly have that
-\[
- 	\frac{\langle f,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
-  \overset{d}{\approx} \frac{1}{t^{\frac{1}{1+\beta}}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k
-  \xrightarrow[t\to \infty]{d} \zeta,
-\]
-where $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto \exp( m[\theta f])$.
-\end{comment}
-% END DELETED
-% For $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
 If $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
-\begin{comment}
-Taking $f = \phi_p$ with $\alpha \tilde \beta > |p|b$ as an example, we do the following decomposition:
-\[
-  H^p_t-H^p_\infty
-  =\sum^{\infty}_{n=1}(H^p_{t+n-1}-H^p_{t+n}).
-\]
-The fluctuation behaviors of each of the terms $H_{t+n-1}^p - H_{t+n}^p$ and their asymptotic independence will also be established in Theorem \ref{lem:PR:LC} and Corollary \ref{cor:MI} below.
-These lemmas will eventually lead us to the fluctuation result in the large branching rate regime.
-\end{comment}
-
-\begin{comment}
-For a general $f$, we have a unique decomposition: $f=f_l+f_c+f_s$ with $f_l\in\mathcal C_l$, $f_c\in\mathcal C_c$ and $f_s\in\mathcal C_c$.
-Note that there may be no $p$ such that $|p|=\frac{\alpha \tilde\beta}{b}$. In this case $f_c=0$.
-Our main results above give central limit type results for $\langle f_l, X_t\rangle$, $\langle f_c, X_t\rangle$ and $\langle f_s, X_t\rangle$, respectively.
-We conjecture that the limits of these three terms, normalized properly, are independent, because intuitively these limits come from small time intervals, intermediate time intervals and large time intervals, respectively.
-If this is valid, we can get a central limit type result for $\langle f, X_t\rangle$ for general $f\in\mathcal{P}$.
-This independence was proved under the second moment condition, see \cite{RenSongZhang2015Central}.
-We leave the question of independence for stable branching mechanism to a future project.
-\end{comment}
-
-This paper is our first attempt on the stable CLT for superprocesses.
+
+This paper is our first attempt on stable CLTs for superprocesses.
 There are still many open questions.
-Ren, Song and Zhang have established some spatial  central limit theorems in \cite{RenSongZhang2015Central} for a class of superprocesses with general spatial motions under the assumption that the branching mechanisms satisfy a second moment condition.
-We hope to prove spatial CLT's for superprocesses with general motions without the second moment assumption on the branching mechanism in a future project.
+Ren, Song and Zhang have established some spatial  CLTs in \cite{RenSongZhang2015Central} for a class of superprocesses with general spatial motions under
+the assumption that the branching mechanisms satisfy a second moment condition.
+We hope to prove spatial CLTs for superprocesses with general motions without the second moment assumption on the branching mechanism in a future project.
 
 Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z +\eta z^{1+\beta}$ plus a small perturbation
-%\begin{align}
-%  \label{eq:PB}
-%	\psi_1(z)
-%	& := \rho z^2+ \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta) y^{2+\beta}}\Big)
-%\end{align}
 $\psi_1(z)$
-% where $\psi_1$ satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
 which satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
@@
 
-Here are some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}:
+The following correspondence between (sub)critical branching mechanisms and Bernstein functions is well known, see, for instance,
+\cite[Theorem VII.4(ii)]{Bertoin} and \cite[Proposition 7]{BRY}. Suppose that $f, g:(0, \infty)\to [0, \infty)$ are related by $f(x)=xg(x)$.
+Then $f$ is a (sub)critical branching mechanism with $\lim_{x\to 0}f(x)=0$ iff $g$ is a Bernstein function with a decreasing L\'evy density.
+We now use this correspondence to give some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
 If $h$ is a complete Bernstein function which is regularly varying at 0 with index $\beta_1\in (\beta, 1)$, then
@@
   := -\alpha z + \rho z^2+\eta z^{1+\beta}+zh(z)
-  , \qquad z>0
+  , \qquad z>0,
 \]
@@
   :=-\alpha z + \rho z^2+\eta z^{1+\beta}-\int^\infty_{c_2} (e^{-yz}-1+yz)\frac{c_1dy}{y^{1+\beta_1}}
-  , \qquad z\in \mathbb R_+
+  , \qquad z\in \mathbb R_+,
 \]
@@
 The rest of the paper is organized as follows:
-In Subsection \ref{sec: branching mechanism} we will give some preliminary results for our branching mechanism $\psi$.
-In Subsections \ref{sec: controller} and \ref{sec: h-controller} we will give some estimates for some operators related to the super-OU process $X$ that will be used in our proofs.
-In Subsection \ref{sec: stable distributions} we will give the definitions of all the $(1+\beta)$-stable random variables involved in this paper.
+In Subsection \ref{sec: branching mechanism} we will give some preliminary results for the branching mechanism $\psi$.
+In Subsections \ref{sec: controller} and \ref{sec: h-controller} we will give some estimates for some operators related to the super-OU process $X$.
+In Subsection \ref{sec: stable distributions} we will give the definitions of the $(1+\beta)$-stable random variables involved in this paper.
+In Subsection \ref{sc:refined} we will give some refined estimate for the OU semigroup.
 In Subsection \ref{sec: Small value probability} we will give some estimates for the small value probability of continuous state branching processes.
@@
 In Subsections \ref{sec:critical}--\ref{sec: large rate clt}, we will give the proof of Theorem \ref{thm:M}.
-In the Appendix, we consider a general superprocess $(X_t)_{t\geq 0}$, and we prove there that the characteristic exponent of $\langle f,X_t\rangle$ satisfies a complex-valued non-linear integral equation.
+In the Appendix, we consider a general superprocess $(X_t)_{t\geq 0}$ and we prove that the characteristic exponent of $X_t(f)$ satisfies a complex-valued non-linear integral equation.
 This fact will be used at several places in this paper, and we think it is of independent interest.
@@
 Suppose that Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism} hold.
-In this subsection, we give some preliminary results about the branching mechanism $\psi$.
+In this subsection, we give some preliminary results on $\psi$.
 Recall that $\eta$ and $\beta$ are the constants in Assumption \ref{asp: branching mechanism}.
@@
 	The function $\psi_1$ given by \eqref{eq:PB} can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
-  Moreover, for each $\delta > 0$ small enough, there exists $C>0$ such that for all $z\in \mathbb C_+$, we have $|\psi_1(z)| \leq C |z|^{1+\beta+\delta} + C|z|^2.$
+  Moreover, for all $\delta > 0$ small enough, there exists $C>0$ such that for all $z\in \mathbb C_+$, we have $|\psi_1(z)| \leq C |z|^{1+\beta+\delta} + C|z|^2.$
 \end{lem}
@@
   \]
-	% Now, according to  Assumption \ref{asp: branching mechanism} and Remark \ref{rem: small enough delta}, for each small enough $\delta > 0$, we have
-	Now, according to  Assumption \ref{asp: branching mechanism}, for each small enough $\delta > 0$, we have
+	Now, according to  Assumption \ref{asp: branching mechanism}, for all small enough $\delta > 0$, we have
   \begin{align}
@@
 	Without loss of generality, we assume that $\beta+\delta \leq \beta'+ \delta'$.
-	Using  the fact that $y^{1+\beta+ \delta} \leq y^{1+\beta'+\delta'}$ with $y \geq 1$, we get
+	Using  the fact that $y^{1+\beta+ \delta} \leq y^{1+\beta'+\delta'}$ for $y \geq 1$, we get
   \[
@@
 	In other words, if we denote by $\widetilde \pi(dy)$ the measure $\eta' \Gamma(-1-\beta)^{-1} y^{-2-\beta'} dy$, then $\widetilde \pi$ is a L\'evy measure which satisfies Assumption \ref{asp: branching mechanism}.
-	Applying Lemma \ref{lem:CEP} to this measure $\widetilde \pi$, we have that there exists $c>0$ such that
+	Applying Lemma \ref{lem:CEP} to $\widetilde \pi$, we have that there exists $c>0$ such that
   \[
@@
   Dividing both sides by $z^{1+\beta}$ we have
-  \[
+   $
    | \eta - \eta' z^{ \beta' - \beta } |
@@
     ,	\quad z \in \mathbb R_+.
-  \]
+ $
 	This implies that $ \eta' z^{\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0. $
@@
   If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies the $L \log L$ condition, i.e.,
-  \[
+   $
     \int_{(1,\infty)} y \log y~\pi(dy)
     < \infty.
-  \]
+ $
 \end{lem}
@@
   Combining this with
-  \[
+  $
   \int_{ ( 1, \infty ) } \frac { \eta \log y ~dy } { \Gamma ( - 1 - \beta ) y^{ 1 + \beta } }
     < \infty,
-  \]
+ $
   we immediately get the desired result.
@@
 
-In this paper, we say $R$ is a \emph{monotone} operator on $\mathcal P^+$ if $R:\mathcal P^+ \to \mathcal P^+$ satisfies that $Rf\leq Rg$ for each $f\leq g$ in $\mathcal P^+$.
-For a function $h: [0,\infty) \to [0,\infty)$, we say $R$ is an \emph{$h$-controller} if $R$ is a monotone operator on $\mathcal P^+$ and that $R(\theta f)\leq h(\theta) Rf$ for each $f\in \mathcal P^+$ and $\theta \in [0,\infty)$.
-For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and an operator $R$ on $\mathcal P^+$, we say an operator $A$ is \emph{controlled by $R$ from $\mathcal D$ to $\mathcal I$} if $A:\mathcal D \to \mathcal I$ and that $|Af| \leq R|f|$ for each $f\in \mathcal D$;
-we say a family of operators $\mathscr O$ is \emph{uniformly controlled by $R$ from $\mathcal D$ to $\mathcal I$} if for each operator $A\in \mathscr O$, $A$ is controlled by $R$ from $\mathcal D$ to $\mathcal I$.
+In this paper, we say $R$ is a \emph{monotone} operator on $\mathcal P^+$ if $R:\mathcal P^+ \to \mathcal P^+$ satisfies that $Rf\leq Rg$ for all $f\leq g$ in $\mathcal P^+$.
+For a function $h: [0,\infty) \to [0,\infty)$, we say $R$ is an \emph{$h$-controller} if $R$ is a monotone operator on $\mathcal P^+$ and that $R(\theta f)\leq h(\theta) Rf$ for all $f\in \mathcal P^+$ and $\theta \in [0,\infty)$.
+For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and an operator $R$ on $\mathcal P^+$, we say an operator $A$ is \emph{controlled by $R$ from $\mathcal D$ to $\mathcal I$} if $A:\mathcal D \to \mathcal I$ and that $|Af| \leq R|f|$ for all $f\in \mathcal D$;
+we say a family of operators $\mathscr O$ is \emph{uniformly controlled by $R$ from $\mathcal D$ to $\mathcal I$} if
+each operator $A\in \mathscr O$  is controlled by $R$ from $\mathcal D$ to $\mathcal I$.
 For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and a function $h:[0,\infty) \to [0,\infty)$, we say an operator $A$ (resp.
@@
 \label{sec: h-controller}
-Let $X$ be the super-OU process introduced in Subsection \ref{subsec:M} with branching mechanism $\psi$ satisfying
+Let $X$ be our super-OU process with branching mechanism $\psi$ satisfying
 Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-In this subsection, we will define several operators and study their properties that will be used in this paper.
-
-Define $\psi_0(z) = \psi(z) + \alpha z$ for each $z\in \mathbb{R}_+$.
+In this subsection, we will define several operators and study some of their properties that will be used in this paper.
+
+Define $\psi_0(z) = \psi(z) + \alpha z$ for $z\in \mathbb{R}_+$.
 According to Lemma \ref{lem:CEP}, $\psi, \psi_1$ and $\psi_0$ can all be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are also holomorphic on $\mathbb C^0_+$.
-For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi f (x) = \psi\circ f(x)$, $\Psi_0 f(x)= \psi_0 \circ f(x)$ and $\Psi_1 f(x)= \psi_1 \circ f(x)$.
-
-For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let $ U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1} $ be the value of the characteristic exponent of the infinitely divisible random variable $\langle f, X_t\rangle$ at $1$.
-(See the paragraph after Lemma \ref{lem: Lip of power function}.)
+For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi f (x) = \psi\circ f(x)$, $\Psi_0 f(x)= \psi_0 \circ f(x)$ and $\Psi_1 f(x)= \psi_1 \circ f(x)$.
+
+For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let 
+%Jianjie $ U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f,X_t\rangle}]|_{\theta = 1} $ 
+$ U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]|_{\theta = 1} $ 
+be the value of the characteristic exponent of the infinitely divisible random variable
+%jianjie $\langle f, X_t\rangle$ at $1$.
+$X_t(f)$
+(See the paragraph after Lemma \ref{lem: Lip of power function}).
 It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
@@
   \item
-    For any $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item
-    For any $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+    For all $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
+  \item
+    For all $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
   \end{enumerate}
@@
 By Lemma \ref{lem:CEP}, there exist $C, \delta >0$ satisfying $\beta+\delta< 1$ such that for all $ f \in \mathcal P^* \cap \mathcal B( \mathbb R^d, \mathbb C_+ )$, it holds that $ |\Psi_0 f| \leq \eta |f|^{1+\beta} + |\Psi_1 f| \leq \eta |f|^{1+\beta} + C|f|^2+ C |f|^{1+\beta + \delta}.$
-  Note that operator
+  Note that the operator
   \[
@@
   Combining this with \eqref{eq:chareq2} and
-  % YX Lemma \ref{lem: property of controllable operators}.(4), we get the desired result.
-  % ZY Lemma \ref{lem: property of controllable operators}.(3), we get the desired result.
   Lemma \ref{lem: property of controllable operators}.(5), we get the desired result.
@@
 
-  (6). By  Lemma \ref{lem:CEP}, for any $\delta > 0$ small enough, there exists  $C>0$ such that
+  (6). By  Lemma \ref{lem:CEP}, for all $\delta > 0$ small enough, there exists  $C>0$ such that
   \[
@@
   is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controller.
-  Therefore, for any $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
+  Therefore, for all $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
   Combining  this with  (1)--(2) above,
-  and Lemma \ref{lem: property of controllable operators}.(1) and (4), we get that, for any $\delta > 0$ small enough, the operators
+  and Lemma \ref{lem: property of controllable operators}.(1) and (4), we get that, for all $\delta > 0$ small enough, the operators
   \[
@@
 \label{sec: stable distributions}
-Recall that the operators $(T_t)_{t\geq 0}$ are defined by \eqref{eq:I:R:1}, and functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
+Recall that the operators $(T_t)_{t\geq 0}$ are defined by \eqref{eq:I:R:1}, and the functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
 \begin{lem}
   \label{lem:m}
-  Operators $(T_t)_{t\geq 0}$, functionals $(m_{t})_{0\leq t< \infty}$ and functional $m$ are well defined.
+$(T_t)_{t\geq 0}$,  $(m_{t})_{0\leq t< \infty}$ and  $m$ are well defined.
 \end{lem}
@@
     \\&\leq (1+\beta) ( |f_c + T_t f_{sl}|^\beta + |f_c|^\beta) e^{- \delta t} h
-    \\&\leq (1+\beta) ( (|f_c| + |h|)^\beta + |f_c|^\beta) e^{- \delta t} h
-    =: e^{- \delta t} g
+    \leq (1+\beta) ( (|f_c| + |h|)^\beta + |f_c|^\beta) e^{- \delta t} h
+    =: e^{- \delta t} g,
   \end{align}
@@
   \label{prop:PL:S}
-  For each $f \in \mathcal P\setminus \{0\}$, there exists a non-degenerate $(1+\beta)$-stable random variable $\zeta^f$ such that $ E[e^{i\theta\zeta^f}] = e^{m[\theta f]}$ for each $\theta \in \mathbb R$.
+  For each $f \in \mathcal P\setminus \{0\}$, there exists a non-degenerate $(1+\beta)$-stable random variable $\zeta^f$ such that $ E[e^{i\theta\zeta^f}] = e^{m[\theta f]}$ for all $\theta \in \mathbb R$.
 \end{prop}
@@
     \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},
-    \quad \theta \in \mathbb R^d
+    \quad \theta \in \mathbb R^d,
   \]
@@
   \begin{align}
-    &\lambda_0(S)
-      = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt) \\
-    & = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
+    \lambda_0(S)
+      = &\frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt) \\
+   =  & \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
   \end{align}
@@
   \end{align}
-	Therefore, according to Lemma \ref{lem: charactreisticfunction}, in order to show that $\zeta^f$ is an $(1+\beta)$-stable random variable we only need to show that
-  \[
+	Therefore, according to Lemma \ref{lem: charactreisticfunction}, in order to show that $\zeta^f$ is a $(1+\beta)$-stable random variable we only need to show that
+\begin{equation}\label{e:new}
     \int_0^{\infty}~ds\int_{\mathbb R^d} | T_{s} f(x)|^{1+\beta} \varphi(x)~dx
     \in (0, \infty).
-  \]
-  According to the Step 1 of the proof of Lemma \ref{lem:m}, we know that there exist $\delta> 0$ and $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta s} h$ for each $s\geq 0$.
-  The above then follows.
+\end{equation}
+  According to the Step 1 in the proof of Lemma \ref{lem:m}, we know that there exist $\delta> 0$ and $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta s} h$ for each $s\geq 0$.
+The claim \eqref{e:new} then follows.
 
@@
   Finally, according to Lemma \ref{lem: charactreisticfunction} and the fact that
-  \begin{align}
+ $
     \int_{\mathbb R^d} | f_c(x)|^{1+\beta} \varphi(x)~dx
     \in (0, \infty),
-  \end{align}
+  $
   We have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
@@
 
-\subsection{A refined estimation for the OU semigroup}
-% YX Do we need this subsection?
-It turns out that our proof of the CLT for the super OU processes relies on the following refined estimation for the OU semigroup.
+\subsection{A refined estimate for the OU semigroup}\label{sc:refined}
+It turns out that our proof of the CLT relies on the following refined estimate for the OU semigroup.
 
@@
   \label{lem:P:R}
-  Suppose that $g \in \mathcal P$, then there exists $h \in \mathcal P^+$ such that for each $ f \in \mathcal P_g := \{\theta T_n g: n \in \mathbb Z_+, \theta \in [-1,1]\} $ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
+  Suppose that $g \in \mathcal P$, then there exists $h \in \mathcal P^+$ such that for all $ f \in \mathcal P_g := \{\theta T_n g: n \in \mathbb Z_+, \theta \in [-1,1]\} $ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
 \end{lem}
 \begin{proof}
-  In the following $g \in \mathcal P$ is fixed.
+Fix a $g \in \mathcal P$.
 We write  $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$,  and $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
-  % ZY We need  to prove that for each $f\in \mathcal P_g$, there exists  $h \in \mathcal P^+$ such that for each $|P_tq_f| \leq e^{-bt} h.$
   We need to prove that there exists $h \in \mathcal P^+$ such that for each $f\in \mathcal P_g$, $|P_tq_f| \leq e^{-bt} h$.
@@
 
-  \emph{Step 3.} We show that there exists $h_3 \in \mathcal P^+$ such that for each $j \in \{1,\dots, d\}$ and $f \in \widetilde {\mathcal P}_g$, it holds that $|\partial_j f| \leq h_3$.
-  In fact, it is known that for $t\geq 0$ and $x\in \mathbb R^d$, the position of the OU process $\xi_t$ under $\mathbb P_x$ is a Gaussian random variable with mean $xe^{-bt}$ and variance $\frac{\sigma^2}{2b} (1- e^{-2bt})$.
-From this it can be verified that (see \cite{MetafunePallaraPriola2002Spectrum} for example)
+  \emph{Step 3.} We show that there exists $h_3 \in \mathcal P^+$ such that for all $j \in \{1,\dots, d\}$ and $f \in \widetilde {\mathcal P}_g$, it holds that $|\partial_j f| \leq h_3$.
+  In fact, it is known that  (see \cite{MetafunePallaraPriola2002Spectrum} for example)
   \begin{align}
@@
   \]
-  Therefore, there exists  $h'_3\in \mathcal P^+$n such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
+  Therefore, there exists  $h'_3\in \mathcal P^+$ such that for all $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
   \begin{align}
@@
   \end{align}
-  On the other hand, there exists $h_3''\in \mathcal P^+$ such that for each $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
+  On the other hand, there exists $h_3''\in \mathcal P^+$ such that for all $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
   \begin{align}
@@
 
-  \emph{Step 4.} We show that there exists $h_{4} \in \mathcal P^+$ such that for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$, it holds that $ | \partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta} | \leq h_4$.
-  In fact, thanks to Step 2 and \eqref{eq:P:R:3:1}, for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde{\mathcal P}_g$, we have
+  \emph{Step 4.} We show that there exists $h_{4} \in \mathcal P^+$ such that for all $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$, it holds that $ | \partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta} | \leq h_4$.
+  In fact, thanks to Step 2 and \eqref{eq:P:R:3:1}, for all $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde{\mathcal P}_g$, we have
   \begin{align}
@@
   \end{align}
-  Recall from Step 1 of the proof of Lemma \ref{lem:m} there exists $h'_4\in \mathcal P^+$ such that for each $f \in \{T_sg:s\geq 0\}$ it holds that $|f| \leq h'_4$.
-  Therefore, using Step 3, we have for each $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$,
+  Recall from Step 1 in the proof of Lemma \ref{lem:m} there exists $h'_4\in \mathcal P^+$ such that for each $f \in \{T_sg:s\geq 0\}$ it holds that $|f| \leq h'_4$.
+  Therefore, using Step 3, we have for all $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f \in \widetilde {\mathcal P}_g$,
   \begin{align}
@@
 
-  \emph{Step 5.} We show that there exits $h_5 \in \mathcal P^+$ such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
-  In fact, according to Step 4, for each $j \in \{1,\dots, d\}$, $f \in \widetilde{\mathcal P}_g$ and compact $A \subset \mathbb R^d$, we have
+  \emph{Step 5.}
+We show that there exists $h_5 \in \mathcal P^+$ such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
+  In fact, according to Step 4, for all $j \in \{1,\dots, d\}$, $f \in \widetilde{\mathcal P}_g$ and compact $A \subset \mathbb R^d$, we have
   \[
@@
   \]
-  Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, for each $j \in \{1,\dots, d\}$, $f\in \widetilde {\mathcal P}_g$ and $x\in \mathbb R^d$, it holds that
+  Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, for all $j \in \{1,\dots, d\}$, $f\in \widetilde {\mathcal P}_g$ and $x\in \mathbb R^d$, it holds that
   \[
@@
 
-  \emph{Final step.}
+  \emph{Step 6.}
   Let $h_5$ be the function in Step 5.
-  There are $c_0, n_0> 0$ such that for each $x\in \mathbb R^d$, $h_5(x) \leq c_0(1+|x|)^{n_0}$.
-  Note that for each $x, y \in \mathbb R^d$, $1+|x|+|y|\leq (1+|x|) (1+|y|)$; and that for each $\theta \in [0,1]$, $|\sqrt {1 - \theta} - 1| \leq \theta$.
-  Write $D_{x,y} = \{ax+by: a, b \in [0,1]\}$ for each $x, y \in \mathbb R^d$.
-  Using \eqref{eq:P:R:3:-1} and Step 5, there exists  $h_6 \in \mathcal P^+$ such that for each $t \geq 0$, $f \in \widetilde {\mathcal P}_g$ and $x \in \mathbb R^d$, we have
+  There are $c_0, n_0> 0$ such that for all $x\in \mathbb R^d$, $h_5(x) \leq c_0(1+|x|)^{n_0}$.
+  Note that for all $x, y \in \mathbb R^d$, $1+|x|+|y|\leq (1+|x|) (1+|y|)$; and that for all $\theta \in [0,1]$, $|\sqrt {1 - \theta} - 1| \leq \theta$.
+  Write $D_{x,y} = \{ax+by: a, b \in [0,1]\}$ fo $x, y \in \mathbb R^d$.
+  Using \eqref{eq:P:R:3:-1} and Step 5, there exists  $h_6 \in \mathcal P^+$ such that for all $t \geq 0$, $f \in \widetilde {\mathcal P}_g$ and $x \in \mathbb R^d$,
   \begin{align}
@@
 \label{sec: Small value probability}
-In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}.
+In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}
+%Jianjie add
+satisfying Grey's condition and $L \log L$ condition.
+%add end 
 Such a process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying
@@
 Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$ when $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
-Suppose that Grey's condition is satisfied, i.e., there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-Also suppose that the $L \log L$ condition is satisfied, i.e.,
-\[
-  \int_1^\infty y \log y~\pi(dr)
-  < \infty.
-\]
+%Suppose that Grey's condition is satisfied, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+%Also suppose that the $L \log L$ condition is satisfied, i.e.,
+%$
+%  \int_1^\infty y \log y~\pi(dr)
+% < \infty.
+%$
 We write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
@@
   \end{align}
-  % It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; (ii) $t\mapsto \bar v_t$ is decreasing; and (iii) $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
-  % It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition, we have (i) $0\leq \bar v_t < \infty$ for all $t>0$; (ii) $t\mapsto \bar v_t$ is decreasing; and (iii) $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi$ on $[0,\infty)$.
   It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ exists and is the largest root of $\psi$ on $[0,\infty)$.
@@
   \]
-  Note the derivative of $\psi$
+ Note the derivative of $\psi$, i.e.,
   \[
@@
     \)
-  % By monotonicity, we have that
-  Taking $\lambda \to \infty$ and using monotone convergence theorem, we have that
+  Taking $\lambda \to \infty$ and using the monotone convergence theorem, we have that
   \begin{align}
@@
   In fact, since $\psi$ is a convex function, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for each $z\geq \bar v$.
-  According to Grey's condition, we can find a constant $z_0 >\bar v $ such that $t_0 := \int^\infty_{z_0}\psi(z)^{-1}dz<\infty$.
+  According to Grey's condition, we can find $z_0 >\bar v $ such that $t_0 := \int^\infty_{z_0}\psi(z)^{-1}dz<\infty$.
   For each $t > t_0$, according to \eqref{eq:svp2}, we have
@@
   For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$.
-  % Then using \eqref{eq:svp2} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have for $t>0$ large enough,
   Then we have for $t>0$ large enough,
@@
   \]
-  Note that the left side is always bounded by $1$, so we can take $t_2 =0$ in the above statement.
+  Note that the left hand side is always bounded from above by $1$, so we can take $t_2 =0$ in the above statement.
 \end{proof}
@@
 \label{sec: Moments for super-OU processes}
-In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$, where $\gamma \in (0,\beta)$, $g\in \mathcal P$ and $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is the super OU process considered in Subsection \ref{sec:I:R} satisfying Assumption \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-% Recall that the operator $\mathcal{I}^t_s$ is defined in \eqref{Ist}.
+In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $X_t(g)$,
+where $\gamma \in (0,\beta)$ and $g\in \mathcal P$.
 
@@
   \[
-    \mathbb P_\mu ( |\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
+    \mathbb P_\mu ( |\mathcal{I}_0^tX_t(g)| > \lambda)
+    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\mu(R|\theta g|) d\theta.
   \]
@@
 \begin{proof}
-  It is elementary calculus (see the proof of \cite[Theorem 3.3.6]{Durrett2010Probability} for example) that for each $ux \neq 0$ in $\mathbb R$,
+  It is elementary calculus (see the proof of \cite[Theorem 3.3.6]{Durrett2010Probability} for example) that
+for $u>0$ and $x\neq0$,
   \[\frac{1}{u}\int_{-u}^u (1- e^{i\theta x})~d\theta = 2 - \frac{2\sin ux}{ux} \geq \mathbf 1_{ux>2}.\]
   Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: upper bound for usgx}.(4).
-  Therefore, using Lemma \ref{lem: estimate of exponential remaining} we get
-  \begin{align}
-    & |\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)|
-      \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^t\langle g,X_t\rangle}])d\theta\Big| \\
-    & \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iP^\alpha_t (\theta g),\mu \rangle}|d\theta
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iP^\alpha_t(\theta g)|,\mu\rangle d\theta \\
-    & \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
+  Then, using Lemma \ref{lem: estimate of exponential remaining} we get
+  \begin{align}
+    & |\mathbb P_\mu (|\mathcal{I}_0^tX_t(g)| > \lambda)|
+       \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^tX_t(g)}])d\theta\Big| \\
+     & \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\mu(U_t(\theta g)-iP^\alpha_t (\theta g))}|d\theta
+     \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\mu(|U_t(\theta g) - iP^\alpha_t(\theta g)|) d\theta \\
+     & \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\mu(R|\theta g|) d\theta.
       \qedhere
@@
   \[
-    \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
+     \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^sX_t(g)|>\lambda)
     \leq C e^{\alpha r} \Big(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \Big).
@@
   \begin{align}
-    & \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
-      = \mathbb P_\mu \Big[\mathbb P_\mu [|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda | \mathscr F_r ]\Big] \\
-    & = \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle P_{t-s}^\alpha g, X_{s-r}\rangle - \langle P_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big] \\
-    & = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
-      \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big] \\
-    & \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big] \\
-    & \leq \mathbb P_\mu [ \langle Rh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
-    \\ & =  \langle P_r^\alpha Rh,\mu\rangle \Big(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\Big)
+   & \mathbb P_{\mu}(|\mathcal I_r^sX_t(g)|>\lambda)
+      = \mathbb P_\mu \Big[\mathbb P_\mu [| X_{s}(P_{t-s}^\alpha g) -  X_{r}(P_{t-r}^\alpha g)|> \lambda | \mathscr F_r ]\Big] \\
+     & = \mathbb P_\mu \big[\mathbb P_{X_r}(| X_{s-r}(P_{t-s}^\alpha g) -  X_{0}(P_{t-r}^\alpha g)|> \lambda)\big] \\
+    & = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r} X_{s-r}( P_{t-s}^\alpha g) |> \lambda)\big]
+      \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}X_r(R|\theta P^\alpha_{t-s}g|) d\theta \Big] \\
+     & \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}X_r(R|\theta e^{(t-s)(\alpha- \kappa b)}h|) d\theta \Big] \\
+     & \leq \mathbb P_\mu [X_r(Rh) ]
+\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
+     \\ & =  \mu(P_r^\alpha Rh)
+\Big(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\Big)
     \\ & \leq C e^{\alpha r} \Big(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \Big),
@@
   where the $C>0$ above is chosen as
-  \[
+%Jianjie \[
+  $
     C
-    := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big)\langle Q_0Rh, \mu\rangle.
+     := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh).
     \qedhere
-  \]
+  $
+%Jianjie \]
 \end{proof}
@@
   \[
-    \sup_{g \in \mathcal P: Q_\kappa g \leq h} \|\mathcal I_r^s\langle g, X_t\rangle \|_{\mathbb P_\mu;1+\gamma}
+     \sup_{g \in \mathcal P: Q_\kappa g \leq h} \|\mathcal I_r^s X_t(g) \|_{\mathbb P_\mu;1+\gamma}
     \leq C e^{t\alpha (1- \tilde \gamma)+(t-s) (\alpha \tilde \gamma - \kappa b)}.
@@
   \begin{align}
-    & \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
-      = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda) d\lambda \\
-    & \leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^s\langle g, X_t\rangle|> \lambda) d\lambda \\
+     & \mathbb P_\mu\big[|\mathcal I_r^sX_t(g)|^{1+\gamma}\big]
+       = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^sX_t(g)|>\lambda) d\lambda \\
+     & \leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^sX_t(g)|> \lambda) d\lambda \\
     & \leq c^{1+\gamma} + C_0  e^{\alpha r}(1+\gamma)\int_c^\infty \bigg(\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta}+\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2}\bigg)\lambda^{\gamma}d\lambda \\
@@
   \begin{align}
-    & \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
+     & \mathbb P_\mu\big[|\mathcal I_r^s X_t(g)|^{1+\gamma}\big]
       \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
@@
   \label{lem:P:M:uc}
-  For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
+  For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for all $t\geq 0$, we have
   \begin{enumerate}
@@
     \label{item:P:M:uc:1}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha \tilde \gamma > \kappa b$;
+    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha \tilde \gamma > \kappa b$;
   \item
     \label{item:P:M:uc:2}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma = \kappa b$;
+    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma = \kappa b$;
   \item
     \label{item:P:M:uc:3}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma < \kappa b$.
+    $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma < \kappa b$.
   \end{enumerate}
@@
   \begin{align}
-    & \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
-      \leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma} + |\langle P^\alpha_t g,\mu\rangle| \\
-    & \leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
+    & \|X_t(g)\|_{\mathbb P_\mu;1+\gamma}
+      \leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}X_t(g) \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}X_t(g)  \big\|_{\mathbb P_\mu;1+\gamma} + |\mu(P^\alpha_t g)| \\
+    & \leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \mu(h).
   \end{align}
@@
 \label{proofs of main results}
-In this section, we will prove the main results of this paper. Recall that $\mathcal{M}_c(\mathbb{R}^d)$ is the space of all finite Borel measures of compact support on $\mathbb{R}^d$.
+In this section, we will prove the main results of this paper.
 For simplicity, we will write $\mathbb{\widetilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in this section.
@@
   M_t^{f,a}
-  :=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds.
+   :=e^{-(\alpha-ab)t}X_t(f)-\int_0^t e^{-(\alpha-ab)s} X_s((L+ab)f)~ ds.
 \end{align}
@@
     & \quad\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
-    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big] \\
-    & =e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du - \int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
+    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[X_t(f)|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}X_u(\bar{f})~ du\Big|\mathscr{F}_s\big] \\
+    & =e^{-(\alpha-ab)t} X_s(P_{t-s}^{\alpha}f)-\int_0^s e^{-(\alpha-ab)u} X_u(\bar{f})~ du - \int_s^t e^{-(\alpha-ab)u}X_s(P_{u-s}^{\alpha} \bar{f})~ du.
   \end{align}
@@
   \begin{align}
-    & \int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle P_{u-s}^{ab}\bar{f},X_s\rangle~du\\
-    & = e^{ - ( \alpha - ab ) s } \Big \langle \int_0^{t-s} P_{u}^{ab} \bar{f}~ du, X_s \Big \rangle
-      = e^{-(\alpha-ab)s}\left(\langle P_{t-s}^{ab}f,X_s\rangle - \langle f, X_s \rangle \right) \\
-    & = e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle - e^{ - ( \alpha - ab ) s} \langle f,X_s\rangle.
+    & \int_s^t e^{-(\alpha-ab)u}X_s(P_{u-s}^{\alpha} \bar{f})~ du=e^{-(\alpha-ab)s}\int_s^tX_s(P_{u-s}^{ab}\bar{f})~du\\
+    & = e^{ - ( \alpha - ab ) s } X_s\left( \int_0^{t-s} P_{u}^{ab} \bar{f}~ du\right)
+      = e^{-(\alpha-ab)s}\left(X_s(P_{t-s}^{ab}f) - X_s(f) \right) \\
+    & = e^{-(\alpha-ab)t} X_s( P_{t-s}^{\alpha}f) - e^{ - ( \alpha - ab ) s} X_s(f).
   \end{align}
@@
 
-Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$. 
-Define $ H_t^p :=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle$ for each $t\geq 0$.
+Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$ 
+%Jianjie Define $ H_t^p :=e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
+and $ H_t^p :=e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
 
@@
   \label{lem:M:L:ML}
-   For each $\mu\in \mathcal M_c(\mathbb R^d)$ and $p \in \mathbb Z_+^d$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_{\mu}$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
+   For all $\mu\in \mathcal M_c(\mathbb R^d)$ and $p \in \mathbb Z_+^d$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_{\mu}$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
     Moreover if $\alpha\tilde \beta>|p|b$, the martingale is bounded in $L^{1+\gamma}(\mathbb P_\mu)$ for each $\gamma\in (0, \beta)$.
@@
 \begin{proof}
-  Fix the measure $\mu \in \mathcal M_c(\mathbb R^d)$ and the multi-index $p \in \mathbb Z_+^d$.
+  Fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and a $p \in \mathbb Z_+^d$.
   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale.
@@
   \]
-  % For each $\gamma\in (0, \gamma_0)$ there exists a constant $C>0$, such that
-  For each $\gamma\in (0, \gamma_0)$ there exists a constant $C'>0$, such that
+  For each $\gamma\in (0, \gamma_0)$ there exists a constant $C'>0$ such that
   \[
@@
     \leq \| H_t^p \|_{\mathbb P_\mu;1+\gamma_0}
-    % \leq C,
     \leq C',
@@
   \end{align}
-  Thus there exists $C_2>0$ such that for any $0\leq s<t$,
+  Thus there exists $C_2>0$ such that for all $0\leq s<t$,
   \begin{align}
@@
   \begin{align}
-    & e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
-      \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \widetilde{f},X_t\rangle,
+    & e^{-(\alpha-\kappa_fb)t}X_t(f)=
+      \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} X_t(\widetilde{f}),
       \quad t\geq 0.
@@
     J_t
-    :=e^{-(\alpha-\kappa_fb)t}\langle \widetilde{f},X_t\rangle,
+    :=e^{-(\alpha-\kappa_fb)t}X_t( \widetilde{f}),
     \quad t\geq 0,
@@
   \[
-    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+    \|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb P_\mu;1+\gamma}
     \leq C_1 e^{-\delta_1 t},
@@
   \]
-  In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that, $\kappa b< \alpha \tilde \gamma$ for each $\gamma \in [\gamma_0, \beta)$.
+  In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that $\kappa b< \alpha \tilde \gamma$ for each $\gamma \in [\gamma_0, \beta)$.
   According to Lemma \ref{lem:P:M:uc}, we have for each $\gamma \in (0,\beta)$,
@@
     \[
-      \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+      \|e^{-(\alpha - \kappa b)t}  X_t(g)\|_{\mathbb P_\mu;1+\gamma}
       \leq C_2 e^{-(\alpha-\kappa b)t}e^{(\alpha-\kappa_g b)t}
@@
     \[
-      \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
+      \|e^{-(\alpha - \kappa b)t}  X_t(g)\|_{\mathbb P_\mu;1+\gamma}
       \leq C_3 t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
@@
     \[
-      \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+      \|e^{-(\alpha - \kappa b)t}  X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}
       \leq C_4  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
@@
   \item
-    if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above and the fact that \[\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
-      \leq \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C_5, \delta_2 >0$ such that
-    \[
-      \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+  if $\gamma \in (0,\gamma_0)$,  then
+    thanks to (1)--(3) above and the fact that \[\|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}
+      \leq \|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C_5, \delta_2 >0$ such that
+    \[
+      \|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}
       \leq C_5e^{-\delta_2 t},
@@
     L_t^{g,a}
-    & :=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,\\
+    & :=\int_0^t e^{-(\alpha-ab)s}X_s((L+ab)g) ds,
+    \quad
     Y_t^{g,a}
-    & :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
+    :=\int_0^t e^{-(\alpha-ab)s}|X_s((L+ab)g)|ds.
   \end{align}
@@
     \quad e^{-(a_0-\kappa_f)b t}L_t^{\widetilde{f},a_0}
-    \xrightarrow[t\to \infty]{} 0
+    \xrightarrow[t\to \infty]{} 0,
     \quad \mathbb{P}_{\mu}\text{-a.s.}
@@
   \[
-    \| e^{-(\alpha-a_0 b)t}\langle \widetilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
+    \| e^{-(\alpha-a_0 b)t}X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq C_6 e^{-\delta_3 t},
-    \quad \|e^{-(\alpha-a_0 b)t}\langle L\widetilde{f}+a_0 b\widetilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
+    \quad \|e^{-(\alpha-a_0 b)t}X_t(L\widetilde{f}+a_0 b\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq C_6 e^{-\delta_3 t}.
@@
       \leq\|Y_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma} \\
-    & \leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\widetilde{f}+a_0 b\widetilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
+    & \leq \int_0^t \|e^{-(\alpha-a_0 b)s}X_s( L\widetilde{f}+a_0 b\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
   \end{align}
@@
     \|M_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq \|e^{-(\alpha-a_0 b)t}\langle \widetilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq \|e^{-(\alpha-a_0 b)t}X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq C_6(e^{-\delta_3 t}+\frac{1}{\delta_3}),
@@
 % **** Central limit theorems for one unite time interval
-\subsection{Central limit theorems for one unite time intervals}
+\subsection{Central limit theorems for unit time intervals}
 \label{sec:critical}
 % ***** Local CLT for one interval
-In this subsection, we will establish the following  central limit theorem for our super-OU processes.
+In this subsection, we will establish the following CLT.
 \begin{thm}
   \label{lem:PR:LC}
-  Let $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal{P}\setminus \{0\}$.
-  Then under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+If  $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal{P}\setminus \{0\}$,
+then  under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
   \begin{align}
@@
   \end{align}
-  where $\zeta^f_0$ is an $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto e^{\langle Z_1(\theta f), \varphi\rangle}$.
+  where $\zeta^f_0$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto e^{\langle Z_1(\theta f), \varphi\rangle}$.
 \end{thm}
@@
   \label{thm:Key}
-  For each $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P \setminus \{0\}$, there exist $C,\delta>0$ such that
-  for each $t\geq 1$ and $f \in \mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$, we have
+  For all $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P \setminus \{0\}$, there exist $C,\delta>0$ such that
+  for all $t\geq 1$ and $f \in \mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$, we have
   \[
@@
 \begin{proof}
-  Fix the $\mu \in \mathcal M_c(\mathbb R^d)$ and the $g \in \mathcal P\setminus \{0\}$.
-
-  \emph{Step 1.} Write $ A_t(\epsilon) :=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \} $ with $t\geq 0$ and $\epsilon > 0$.
-  We will show that for each $f\in \mathcal P \setminus \{0\}$, $\epsilon > 0$ and $t\geq 0$, it holds that
+  Fix  $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P\setminus \{0\}$.
+
+  \emph{Step 1.} Write $ A_t(\epsilon) :=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \} $ for $t\geq 0$ and $\epsilon > 0$.
+  We will show that for all $f\in \mathcal P \setminus \{0\}$, $\epsilon > 0$ and $t\geq 0$, it holds that
   \[
@@
 \label{eq: Def of Ji}
-  J^f_1(t,\epsilon)
-  & := \mathbb{P}_{\mu} [ |\langle Z'''_1(\theta_t f), X_t\rangle |; A_t(\epsilon) ],
-  \\ J^f_2(t,\epsilon)
-  & := \mathbb{P}_{\mu}[|\langle Z_1(\theta_t f),X_t \rangle-\langle Z_1f, \varphi\rangle |; A_t(\epsilon)],
-  \\ J_3(t,\epsilon)
-  & :=2\mathbb{P}_{\mu}(A_t (\epsilon)\Delta D^c),
-  \\ \theta_t
-  & := \|X_t\|^{-(1 - \tilde \beta)}.
+  &J^f_1(t,\epsilon):= \mathbb{P}_{\mu} [ | X_t(Z'''_1(\theta_t f)) |; A_t(\epsilon) ],
+ \quad
+  J^f_2(t,\epsilon):= \mathbb{P}_{\mu}[|X_t( Z_1(\theta_t f))-\langle Z_1f, \varphi\rangle |; A_t(\epsilon)],
+  \\ & J_3(t,\epsilon):=2\mathbb{P}_{\mu}(A_t (\epsilon)\Delta D^c),
+ \quad
+   \theta_t := \|X_t\|^{-(1 - \tilde \beta)}.
 \end{align}
@@
     = \mathbb{P}_{\mu}[\exp\{i\theta_t X_{t+1} (f) - i \theta_t X_t(P_1^\alpha f)\} |\mathscr{F}_{t}] \\
-  & = \exp\{\langle (U_1 - iP^\alpha_1 ) (\theta_t f),X_t\rangle\}
-    = \exp\{\langle (Z_1 + Z'''_1) (\theta_t f),X_t\rangle\}.
+  & = \exp\{X_t((U_1 - iP^\alpha_1 ) (\theta_t f))\}
+    = \exp\{X_t((Z_1 + Z'''_1) (\theta_t f))\}.
 \end{align}
@@
   & = \mathbb{P}_{\mu}\Big[ |\mathbb{P}_\mu [e^{i\Upsilon^f_t}| \mathscr F_{t}]-e^{\langle Z_1f, \varphi\rangle}| ; A_{t}(\epsilon) \Big] + J_3(t,\epsilon) \\
-  & \leq \mathbb{P}_\mu \Big[ |e^{\langle (Z_1+Z'''_1) (\theta_t f),X_{t} \rangle}-e^{\langle Z_1f, \varphi\rangle} | ; A_{t}(\epsilon) \Big]+  J_3(t,\epsilon) \\
-  & \leq \mathbb{P}_\mu \Big[ | \langle (Z_1+Z'''_1)(\theta_t f),X_{t} \rangle - \langle Z_1f, \varphi\rangle | ;A_{t}(\epsilon)\Big]+  J_3(t,\epsilon) \\
+  & \leq \mathbb{P}_\mu \Big[ |e^{X_{t}((Z_1+Z'''_1) (\theta_t f))}-e^{\langle Z_1f, \varphi\rangle} | ; A_{t}(\epsilon) \Big]+  J_3(t,\epsilon) \\
+  & \leq \mathbb{P}_\mu \Big[ | X_{t} ( (Z_1+Z'''_1)(\theta_t f)) - \langle Z_1f, \varphi\rangle | ;A_{t}(\epsilon)\Big]+  J_3(t,\epsilon) \\
   & \leq J^f_1(t,\epsilon) + J^f_2(t,\epsilon)+ J_3(t,\epsilon).
@@
 
-\emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for each $t\geq 1$ and
+\emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for all $t\geq 1$ and
 $f \in \mathcal P_g$, we have $ J^f_1(t,\epsilon) \leq C_2e^{-\delta_2 t}$.
@@
 In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-Acording to Step 1 of the proof of Lemma \ref{lem:m}, there exist $h_{2} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{2}$.
+Acording to Step 1 in the proof of Lemma \ref{lem:m}, there exists $h_{2} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{2}$.
 Then, we have for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
@@
     \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t}(\epsilon)}
-    \leq R \Big(\frac{h_{2}}{e^{(\alpha-\epsilon)t(1-\tilde \beta)}}\Big) \\
-  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}Rh_{2}.
+    \leq R \Big(\frac{h_{2}}{e^{(\alpha-\epsilon)t(1-\tilde \beta)}}\Big)
+    \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}Rh_{2}.
 \end{align}
@@
   J^f_1(t,\epsilon)
-  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[\langle Rh_2,X_{t-1}\rangle]\\
-  & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 R h_{2}, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
+%Jianjie  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t-1}(Rh_2)]
+& \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
+  \leq \sum_{\rho \in \{\delta_0,1\}} \mu(Q_0 R h_{2}) e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
 \end{align}
@@
 \emph{Step 3.}
-We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for each $t \geq 0$ and $f\in \mathcal P_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.
+We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for all $t \geq 0$ and $f\in \mathcal P_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.
 In fact, for all $t\geq 0$, and $f\in \mathcal P_g$,
 \begin{align}
-  & \langle Z_1(\theta_t f),X_{t}\rangle- \langle Z_1f, \varphi\rangle
-     = \theta_t^{1+\beta} \langle Z_1 f,X_t\rangle - \langle  Z_1 f,\varphi \rangle
-     =\Big\langle Z_1f - \langle  Z_1 f ,\varphi \rangle, \frac{X_{t}}{\|X_{t}\|}\Big\rangle,
+  & X_{t}(Z_1(\theta_t f))- \langle Z_1f, \varphi\rangle
+     = \theta_t^{1+\beta} X_t(Z_1 f) - \langle  Z_1 f,\varphi \rangle
+     = \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle),
 \end{align}
@@
   J^f_2(t,\epsilon)
-  & = \mathbb P_\mu\Big[\Big| \Big\langle Z_1f - \langle  Z_1 f ,\varphi \rangle, \frac{X_t}{\|X_t\|}\Big\rangle \Big|;A_t(\epsilon)\Big]
-    \leq e^{-(\alpha-\epsilon)t} \mathbb{P}_{\mu}[| \langle q_f,X_t \rangle |].
+  & = \mathbb P_\mu\Big[\Big|  \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle) \Big|;A_t(\epsilon)\Big]
+    \leq e^{-(\alpha-\epsilon)t} \mathbb{P}_{\mu}[|X_t (q_f) |].
 \end{align}
@@
 \begin{align}
-  & \mathbb{P}_{\mu}\left[\left|\langle q_f,X_{t}\rangle\right|\right]
-    \leq \|\langle \operatorname{Re} q_f, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} q_f, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} \\
- & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{3}} \|\langle q, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C_{3} e^{\frac{\alpha t}{1+\gamma}}.
+  & \mathbb{P}_{\mu}\left[\left|X_{t}(q_f)\right|\right]
+    \leq \| X_{t}( \operatorname{Re} q_f)\|_{\mathbb{P}_{\mu,1+\gamma}} + \| X_{t}(\operatorname{Im} q_f)\|_{\mathbb{P}_{\mu,1+\gamma}} \\
+ & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{3}} \|X_t(q)\|_{\mathbb P_\mu; 1+\gamma} \leq C_{3} e^{\frac{\alpha t}{1+\gamma}}.
 \end{align}
@@
 
- \emph{Final step}. Combining the results in Steps 1--4, we immediately get the desired result.
+ \emph{Step 5.} Combining the results in Steps 1--4, we immediately get the desired result.
 \end{proof}
@@
 % ***** LCLT for Multiple interval
-The following corollary of Proposition \ref{thm:Key} will be used later in the proof of our main result Theorem \ref{thm:M}.
+The following corollary  will be used later in the proof of Theorem \ref{thm:M}.
 \begin{cor}
   \label{cor:MI}
-  Suppose that $g\in \mathcal{P}\setminus\{0\}$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
-  Then there exist $C,\delta>0$ such that for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$,
+If  $g\in \mathcal{P}\setminus\{0\}$ and $\mu\in \mathcal M_c(\mathbb R^d)$, then there exist $C,\delta>0$ such that for
+all $l\leq n$ in $\mathbb Z_+$ and  $(f_j)_{j=l}^n\subset \mathcal P_g$,
 \begin{align}
@@
 \begin{proof}
-  For each $l\leq n$ in $\mathbb Z_+$, $k \in \{l,\dots,n\}$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, define
+  For  $l\leq n$ in $\mathbb Z_+$, $k \in \{l,\dots,n\}$ and $(f_j)_{j=l}^n\subset \mathcal P_g$, define
   \[
@@
   \]
-  Then for each $l\leq n$ in $\mathbb Z_+$, $k \in \{l,\dots,n\}$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+  Then for all $l\leq n$ in $\mathbb Z_+$, $k \in \{l,\dots,n\}$ and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
   \begin{align}
@@
   \end{align}
-  By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that for each $l\leq n$ in $\mathbb Z_+$,  $k \in \{l,\dots , n\}$, and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
+  By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that for all $l\leq n$ in $\mathbb Z_+$,  $k \in \{l,\dots , n\}$, and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
   \begin{align}
@@
   \end{align}
-  Therefore, there exist $C,\delta >0$ such that for each $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
-
+  Therefore, there exist $C,\delta >0$ such that for all $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
   \begin{align}
@@
 \begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:1})]
-	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_s$ and $t_0 > 1$  large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
+	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_s$ and $t_0 > 1$  large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for all $t\geq t_0$.
   For each $t\geq t_0$, in this proof we write $\theta_t = \|X_t\|^{\tilde \beta - 1}$,
@@
   where $ Y_{t,k} := \exp(i \Upsilon_{t-k-1}^{T_{k} \tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1. $
-  We claim that there exists $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for each $k\in \mathbb Z_+$ and $t\geq k+1$.
-  And therefore there exists $C_2'>0$ such that for each $t \geq t_0$, $|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]-1| \leq C_2't^{-\delta_1}$  which, combining with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
-
-  We will show this claim in the following substeps 2.1 and 2.2.
-  First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with $ \alpha \tilde \gamma > \eta > \eta - 3\eta' > \alpha \tilde \beta - \alpha \tilde \gamma > 0;$ and define for each $k \in \mathbb Z_+$ and $t\geq k+1$,
+  We claim that there exist $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for all $k\in \mathbb Z_+$ and $t\geq k+1$.
+  Then  there exists $C_2'>0$ such that for each  $t \geq t_0$, $|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]-1| \leq C_2't^{-\delta_1}$  which, combined with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
+
+ We will show the claim above  in the following substeps 2.1 and 2.2.
+  First we choose $\gamma \in (0,\beta)$ close enough to $\beta$ so that there exist $\eta,\eta'>0$ with $ \alpha \tilde \gamma > \eta > \eta - 3\eta' > \alpha \tilde \beta - \alpha \tilde \gamma > 0;$ and define for  $k \in \mathbb Z_+$ and $t\geq k+1$,
   \[
@@
 % ******* Step 2.2
-  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for each $k\in \mathbb Z_+$ and $t\geq k+1$, it holds that $ \mathbb{\widetilde{P}}_{\mu} [|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}$.
-  In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $; and therefore for each $k\in \mathbb Z_+$ and $t \geq k + 1$,
+  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for all $k\in \mathbb Z_+$ and $t\geq k+1$, it holds that $ \mathbb{\widetilde{P}}_{\mu} [|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}$.
+  In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $; and therefore for all $k\in \mathbb Z_+$ and $t \geq k + 1$,
   \begin{align}
@@
     \label{eq: control of Ykt}
-    & \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}] \\
-    & \leq \mathbb{\widetilde{P}}_{\mu}\Big[|\mathcal I_{t-k-1}^{t-k}\langle f , X_t\rangle | \cdot \Big| \| e^{\alpha(k+1)}X_{t-k-1}\| ^{ \tilde \beta - 1} - \|X_t\|^{ \tilde \beta - 1}\Big|; \mathcal D_{t,k}\Big] \\
+    \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}]
+    & \leq \mathbb{\widetilde{P}}_{\mu}\Big[|\mathcal I_{t-k-1}^{t-k} X_t(f) | \cdot \Big| \| e^{\alpha(k+1)}X_{t-k-1}\| ^{ \tilde \beta - 1} - \|X_t\|^{ \tilde \beta - 1}\Big|; \mathcal D_{t,k}\Big] \\
     & \leq  e^{\alpha(\tilde \beta - 1)t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}X_t(f)|\cdot K_{t,k}\big],
@@
   \end{align}
-  Therefore, for each $k \in \mathbb Z_+$ and $t\geq k+1$, almost surely  on $\mathcal D_{t,k}$,
+  Therefore, for all $k \in \mathbb Z_+$ and $t\geq k+1$, almost surely  on $\mathcal D_{t,k}$,
   \begin{align}
@@
   \end{align}
-  Now, by Lemma \ref{lem: control of mgtrs}, there exist $C''_{2.2}>0$ such that for all $k\geq 0$ and $t\geq k+1$,
+  Now, by Lemma \ref{lem: control of mgtrs}, there exists $C''_{2.2}>0$ such that for all $k\geq 0$ and $t\geq k+1$,
   \begin{align}
@@
   First fix a $\gamma \in (0,\beta)$ in this step.
-  From the fact that $\kappa_f b -\alpha \tilde \gamma > \alpha (\tilde \beta - \tilde \gamma)$, we can chose $\epsilon >0$ small enough such that $q:=\kappa_fb- \alpha \tilde \gamma  > \alpha (\tilde \beta - \tilde \gamma) + 2\epsilon (1 - \tilde \beta)$.
+  From the fact that $\kappa_f b -\alpha \tilde \gamma > \alpha (\tilde \beta - \tilde \gamma)$, we can choose $\epsilon >0$ small enough so that $q:=\kappa_fb- \alpha \tilde \gamma  > \alpha (\tilde \beta - \tilde \gamma) + 2\epsilon (1 - \tilde \beta)$.
   Now writing $\mathcal{E}_t:=\{\|X_t\|>e^{(\alpha-\epsilon) t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
@@
     & |I^f_3(t)|
-      \leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{1 - \tilde \beta }}
-      \leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{1 - \tilde \beta}}
-      = e^{(\alpha \tilde \beta - k_fb)t} H_t^{\tilde \beta - 1} \langle Qf,X_0\rangle
+      \leq \frac{X_0(|P^\alpha_tf|)}{\|X_t\|^{1 - \tilde \beta }}
+      \leq \frac{e^{\alpha t - \kappa_f b t}X_0(Qf)}{(e^{\alpha t} H_t)^{1 - \tilde \beta}}
+      = e^{(\alpha \tilde \beta - k_fb)t} H_t^{\tilde \beta - 1} X_0(Qf)
       \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
@@
 % ****** Final Step
-  \emph{Final step.} Combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:1}.
+  \emph{Step 5.} Combining Steps 1--4, we complete the proof of Theorem  \ref{thm:M}.\eqref{thm:M:1}.
 \end{proof}
@@
 \subsection{Central limit theorem for $f \in \mathcal C_c$}
-% ***** Proof of thm:M:2
 \begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:2})]
@@
   \emph{Step 1.} We show that $I^f_0(t) \xrightarrow[t\to \infty]{d} \zeta^f$.
-  In fact, for each $t \geq  t_0 > 1$ we have $t^{\tilde \beta - 1} < 1$; and therefore, for each $k \in \mathbb Z_+$, we have $t^{\tilde \beta - 1} T_{k+1} f \in \mathcal P_f:=\{\theta T_n f: n \in \mathbb Z_+, \theta \in [-1,1]\}$.
+  In fact, for each $t \geq  t_0( > 1)$ we have $t^{\tilde \beta - 1} < 1$; and therefore, for each $k \in \mathbb Z_+$, we have $t^{\tilde \beta - 1} T_{k+1} f \in \mathcal P_f:=\{\theta T_n f: n \in \mathbb Z_+, \theta \in [-1,1]\}$.
   Therefore from Proposition \ref{cor:MI} and that $\tilde \beta - 1 = -\frac{1}{1+\beta}$ we get that there exist $C_1,\delta_1 > 0$ such that
@@
   \emph{Step 2.} We show that $ I^f_1(t) - I^f_0 (t) \xrightarrow[t\to \infty]{d} 0$.
-  In fact, similar to Step 2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we  have \eqref{eq:PM:S:1} is valid with $ Y_{t,k} := \exp(i t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k}\tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1$.
-  Similarly, we claim that there exists $C_2, \delta_2>0$ such that $\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}$ for each $k\in \mathbb N$ and $t\geq k+1$, and  then the desired result in this step follows.
-
-  We will show this claim in the following substeps 2.1 and 2.2.
-  First we chose $\gamma \in (0,\beta)$ close enough to $\beta$ such that there exists $\eta,\eta'>0$ with $ \alpha \tilde \gamma > \eta > \eta - 3\eta' > \alpha \tilde \beta - \alpha \tilde \gamma > 0$; and define for each $k \in \mathbb N$ and $t\geq k+1$ that $ \mathcal{D}_{t,k} := \{|H_t-H_{t-k-1}| \leq  e^{-\eta (t-k-1)}, H_{t-k-1}> 2e^{-\eta' (t-k-1)}\}$.
+  In fact, similar to Step 2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we  have \eqref{eq:PM:S:1} is valid with $ Y_{t,k} := \exp(i t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k}\tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1$.
+  Similarly, we claim that there exist $C_2, \delta_2>0$ such that $\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}$ for all $k\in \mathbb N$ and $t\geq k+1$, and  then the desired result in this step follows.
+
+  We will show the claim above in the following substeps 2.1 and 2.2.
+  First we choose $\gamma \in (0,\beta)$ close enough to $\beta$ so that there exist $\eta,\eta'>0$ with $ \alpha \tilde \gamma > \eta > \eta - 3\eta' > \alpha \tilde \beta - \alpha \tilde \gamma > 0$; and define, for  $k \in \mathbb N$ and $t\geq k+1$, $ \mathcal{D}_{t,k} := \{|H_t-H_{t-k-1}| \leq  e^{-\eta (t-k-1)}, H_{t-k-1}> 2e^{-\eta' (t-k-1)}\}$.
 
@@
 % ******* Step 2.2
-  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for each $k\in \mathbb N$ and $t\geq k+1$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.$
-  In fact, noticing that for $f\in \mathcal C_c$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha $; and therefore for each $k\in \mathbb Z_+$ and $t \geq k + 1$,
+  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for all $k\in \mathbb N$ and $t\geq k+1$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.$
+  In fact, noticing that for $f\in \mathcal C_c$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha $; and therefore for all $k\in \mathbb Z_+$ and $t \geq k + 1$,
   \[
@@
   \begin{align}
-    \label{Theorem123}
+   \label{Theorem123a}
     |\mathbb{\widetilde{P}}_{\mu}[e^{i I^f_2(t)}-1;\mathcal{E}^c_t]|
@@
   \end{align}
-  Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\tilde \beta - \tilde \gamma) \leq \frac{1}{2}(1- \tilde \beta)$.
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C_3',C_3'',C_3'''>0$ such that for each $t\geq t_0 >1$,
+  Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ so that $\alpha(\tilde \beta - \tilde \gamma) \leq \frac{1}{2}(1- \tilde \beta)$.
+	According to Lemma \ref{lem: control of mgtrs}, there exist $C_3',C_3'',C_3'''>0$ such that for each $t\geq t_0 (>1)$,
   \begin{align}
@@
   \end{align}
-  From this and \eqref{Theorem123}, we get the desired result in this step.
+  From this and \eqref{Theorem123a}, we get the desired result in this step.
 
 % ****** Step 4
-  \emph{Step 4.} Similar to Step 4 of the Proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
+  \emph{Step 4.} Similar to Step 4 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
   We omit the details.
@@
 % ****** Final step
- 	\emph{Final step.} Combining Steps 1--4, we complete the proof of \ref{thm:M}.\eqref{thm:M:2}.
+ 	\emph{Step 5.} Combining Steps 1--4, we complete the proof of Theorem \ref{thm:M}.\eqref{thm:M:2}.
 \end{proof}
@@
   Define $\mathcal N:= \{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b\}$.
-  In this proof we write for each $t\geq 0$ that
+  In this proof we write for each $t\geq 0$,
   \begin{align}
@@
   \begin{align}
-    \label{eq:PM:CLTS:2}
+    \label{eq:PM:CLTS:2a}
     & \sum_{k=0}^\infty \langle Z_1 T_{k} (-\tilde f), \varphi \rangle
@@
 $
-  We claim that there exist $C_2, \delta_2>0$ such that $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|] \leq C_2e^{-\delta_2 t}$ for each $t\geq 0$ and $k \in \mathbb Z_+$.
-  And therefore $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq (t^2+1)C_2e^{-\delta_2 t}$ which completes this step.
-
-  We will show this claim in the following Substeps 2.1 and 2.2.
-  First we chose $\gamma\in(0, \beta)$ close enough to $\beta$ so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$; 
-  and even closer so that there exists $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
+  We claim that there exist $C_2, \delta_2>0$ such that $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|] \leq C_2e^{-\delta_2 t}$ for all $t\geq 0$ and $k \in \mathbb Z_+$.
+  Then  $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq (t^2+1)C_2e^{-\delta_2 t}$ which completes this step.
+
+  We will show the claim above in the following substeps 2.1 and 2.2.
+  First we choose $\gamma\in(0, \beta)$ close enough to $\beta$ so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$;
+  and even closer so that there exist $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
 We also define $\mathcal{D}_{t,k} :=\{|H_t-H_{t+k}|\leq  e^{-\eta t}, H_{t}> 2e^{-\eta' t}\}$.
@@
 % ******* subStep 2.1
-  \emph{Substep 2.1.} Similar to the substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} t}$.
+  \emph{Substep 2.1.} Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} t}$.
   We omit the details.
 
-  \emph{Substep 2.2.} We show that there exist $C_{2.2}, \delta_{2.2}>0$ such that for each $k \in \mathbb Z_+$ and $t\geq 0$, we have $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|; \mathcal D_{t,k}]\leq C_{2.2}e^{- \delta_{2,2} t}$.
-  In fact, it can be verified that for each $k \in \mathbb Z_+$ and $t\geq 0$,
+  \emph{Substep 2.2.} We show that there exist $C_{2.2}, \delta_{2.2}>0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$, we have $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|; \mathcal D_{t,k}]\leq C_{2.2}e^{- \delta_{2,2} t}$.
+  In fact, it can be verified that for all $k \in \mathbb Z_+$ and $t\geq 0$,
   \begin{align}
@@
   \]
-  Similar to Substep 2.2 of the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that for all $k\in \mathbb Z_+$ and $t\geq 0$, almost surely $K_{t,k} \leq C_{2.2}'' e^{- (\eta - 3\eta')t}$.
-  From this and Lemma \ref{lem: control of wt} we know that there exists $C'''_{2.2}$ such that for each $k\in \mathbb Z_+$ and $t\geq 0$,
+  Similar to Substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that for all $k\in \mathbb Z_+$ and $t\geq 0$, almost surely $K_{t,k} \leq C_{2.2}'' e^{- (\eta - 3\eta')t}$.
+  From this and Lemma \ref{lem: control of wt} we know that there exists $C'''_{2.2}$ such that for all $k\in \mathbb Z_+$ and $t\geq 0$,
   \begin{align}
@@
   \emph{Step 3.} We show that $I^f_2(t) \xrightarrow[t\to \infty]{d} 0$.
-  In order to do this, chose an $\epsilon \in (0,\alpha)$ and a $\gamma \in (0,\beta)$ close enough to $\beta$ such that for each $p\in \mathcal N$, it holds that $\alpha \tilde \gamma > |p|b$.
+  In order to do this, choose an $\epsilon \in (0,\alpha)$ and a $\gamma \in (0,\beta)$ close enough to $\beta$ so that for each $p\in \mathcal N$, it holds that $\alpha \tilde \gamma > |p|b$.
   Define $\mathcal E_t:= \{\|X_t\| > e^{(\alpha - \epsilon)t}\}$.
@@
 
-  \emph{Final step.} Combining Steps 1--3, we complete the proof of \ref{thm:M}.\eqref{thm:M:3}.
+  \emph{Step 4.} Combining Steps 1--3, we complete the proof of Theorem \ref{thm:M}.\eqref{thm:M:3}.
 \end{proof}
@@
     & h (z)
-      = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+ \\
+      = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+, \\
     & h'(z)
@@
 Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the topology of weak convergence.
-For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$, we use the following convention in this subsection:
-\[
+For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$,
+we use the  convention:
+$
   F(x,f)
-  := F(x,f(x)),\quad x\in E.
-\]
+  := F(x,f(x)),
+  x\in E.
+$
 A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
@@
   \end{align}
-  where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
+  where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique %locally bounded positive solution to the equation
+locally bounded non-negative solution to the equation
   \begin{align}
@@
   \label{eq: mean formula for superprocesses}
-  \mathbb N_{\mu}[\langle W_t, f\rangle]
-  =\mathbf P_{\mu}[\langle X_t, f\rangle]
+  \mathbb N_{\mu}[W_t(f)]
+  =\mathbf P_{\mu}[X_t(f)]
   =\mu(P^{\rho_1}_t f).
@@
 \begin{align}
-  \mathbb N_x[\langle W_t, f\rangle]
-  = \mathbf P_{\delta_x}[\langle f, X_t\rangle]
+  \mathbb N_x[W_t(f)]
+  = \mathbf P_{\delta_x}[X_t(f)]
   = P^{\rho_1}_t f(x) \in \mathbb R,
@@
 This says that the random variable $\langle X_t, f\rangle$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
-By the branching property of the superprocess, $\langle X_t, f\rangle$ is an infinitely divisible random variable.
+By the branching property of the superprocess, $X_t(f)$ is an infinitely divisible random variable.
 Therefore, we can write
@@
   U_t(\theta f)(x)
-  := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta \langle X_t, f\rangle}],
+  := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t( f)}],
   \quad t\geq 0, f\in L_1(\xi), \theta \in \mathbb R, x\in E,
@@
 \[
-  \mathbf P_{\delta_x} [e^{i\theta \langle X_t, f\rangle}]
-  = \exp(\mathbb N_x[ e^{i\theta \langle W_t, f\rangle} - 1]),
+  \mathbf P_{\delta_x} [e^{i\theta X_t(f)}]
+  = \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]),
   \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
 \]
-Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta \langle W_t, f\rangle} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
+Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
 \begin{align}
@@
   U_t(\theta f)(x)
-  = \mathbb N_x[e^{i \langle W_t, \theta f\rangle} - 1],
+  = \mathbb N_x[e^{i W_t(\theta f)} - 1],
   \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
@@
   Noticing that
-  \[
+ $
      e^{\operatorname{Re} U_tf(x)}
     = |e^{U_tf(x)}|
-    = |\mathbf P_{\delta_x}[e^{i \langle X_t, f\rangle}]|
+    = |\mathbf P_{\delta_x}[e^{i X_t(f)}]|
     \leq 1,
-  \]
+$
   we have
@@
     |U_tf(x)|
-    \leq \mathbb N_x[|e^{i \langle W_t, f\rangle} - 1|]
-    \leq \mathbb N_x[|i \langle W_t, f\rangle|]
+    \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
+    \leq \mathbb N_x[|i W_t(f)|]
     \leq (P^{\rho_1}_t |f|)(x).
@@
     \label{eq: estimate of deriavetive of v(theta)}
-    \mathbb N_x \Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta \langle W_t, f\rangle} - 1) \Big|\Big]
-    \leq \mathbb N_x[|\langle W_t, f\rangle|] \sup_{\theta \in K}|\theta|
+    \mathbb N_x \Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
+    \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta|
     \leq (P^{\rho_1}_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
@@
     \frac{\partial}{\partial \theta} U_t(\theta f)(x)
-    = i\mathbb N_x[\langle W_t, f\rangle e^{i\theta \langle W_t, f\rangle}],
+    = i\mathbb N_x[W_t(f) e^{i\theta W_t(f)}],
     \quad \theta \in \mathbb R.
@@
     & = \Big| -\rho_1(x)- 2\rho_2(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big| \\
-    & = \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i \langle W_t, f\rangle} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i \langle X_t, f\rangle}] \pi(x,dy) \Big| \\
-    & \leq \|\rho_1\|_\infty + 2\rho_2(x)\mathbb N_x[\langle W_t, |f|\rangle]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge \langle X_t, |f|\rangle] \pi(x,dy) \\
+    & = \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i W_t(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_t(f)}] \pi(x,dy) \Big| \\
+    & \leq \|\rho_1\|_\infty + 2\rho_2(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy) \\
     & \leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy) \\
@@
   \end{align}
-  where $C_1, C_2$ are constants independent on $f,x$ and $t$.
+where $C_1, C_2$ are constants independent of $f,x$ and $t$.
   Now, combining the display above with \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bounded for derivative of v(theta)} we get the desired result.
@@
 
-This lemma also says that if $f\in L^2(\xi)$ then
-\[
+This lemma also says that if $f\in L^2(\xi)$, then
+$
   \Pi_x\Big[\int_0^t \psi(\xi_s,- U_{t-s}f)ds\Big]
   \in \mathbb C,
-  \quad x\in E, t\geq 0.
-\]
+ x\in E, t\geq 0,$
 is well defined.
@@
 Let $f\in \mathcal B_b(E,\mathbb R_+)$, $T >0$ and $x\in E$.
-Suppose that $\mathbf P_{\delta_x}[\langle X_T, f\rangle] = \mathbb N_x[\langle W_T, f\rangle] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
-\begin{align}
-  d\mathbf P_{\delta_x}^{\langle X_T, f\rangle}
-  := \frac{\langle X_T, f\rangle}{P_T^{\rho_1} f(x)} d\mathbf P_{\delta_x};
-  \quad d\mathbb N_x^{\langle W_T, f\rangle}
-  :=  \frac{\langle W_T, f\rangle}{P_T^{\rho_1} f(x)} d\mathbb N_x.
+Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[ W_T(f)] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
+\begin{align}
+  d\mathbf P_{\delta_x}^{ X_T(f)}
+  := \frac{X_T(f)}{P_T^{\rho_1} f(x)} d\mathbf P_{\delta_x};
+  \quad d\mathbb N_x^{W_T(f)}
+  :=  \frac{W_T(f)}{P_T^{\rho_1} f(x)} d\mathbb N_x.
 \end{align}
@@
   given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure
-\[
+$
   \{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}
-\]
+$
 is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
@@
   \label{eq: Spine decomposition 1}
-  \{(X_s)_{s \geq 0};\mathbf P_{\delta_x}^{\langle X_T, f\rangle}\}
-  \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{\langle W_T, f\rangle} \},
+  \{(X_s)_{s \geq 0};\mathbf P_{\delta_x}^{X_T(f)}\}
+  \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{W_T(f)} \},
 \end{align}
@@
   \label{eq: Spine decomposition 2}
-  \{(W_s)_{0\leq s\leq T};\mathbb N_x^{\langle W_T, f\rangle}\}
+  \{(W_s)_{0\leq s\leq T};\mathbb N_x^{W_T(f)}\}
   \overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
@@
   Fix $t>0, r\in [0,t), x\in E$ and a strictly positive $g\in \mathcal B_b(E)$.
-  Denote by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{\langle W_t, g\rangle}$.
+  Denote by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
   Conditioned on $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$ in \eqref{eq: conditional intensity}.
@@
   \begin{align}
-    & \int_{[0,t]\times \mathbb W}|e^{i \langle w_{t-s}, f\rangle} - 1| \mathbf m(\xi, ds,dw)
-      \leq \int_{[0,t]\times \mathbb W}\big(| \langle w_{t-s}, f\rangle| \wedge 2\big) \mathbf m(\xi, ds,dw) \\
-    & \leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( \langle W_{t-s}, |f|\rangle\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[\langle X_{t-s}, |f|\rangle] \pi(\xi_s,dy) \\
-    & \qquad\qquad + 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
+    & \int_{[0,t]\times \mathbb W}|e^{i w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
+      \leq \int_{[0,t]\times \mathbb W}\big(| w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw) \\
+    & \leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[X_{t-s}(|f|)] \pi(\xi_s,dy)
+   + 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
     \\ & \leq \int_0^t (P_{t-s}^{\rho_1} |f|)(\xi_s)\Big(2\rho_2(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
@@
   \begin{align}
-    & \int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)
-    \\ & =\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i \langle W_{t-s}, f\rangle} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i \langle X_{t-s}, f\rangle} - 1] \pi(\xi_s,dy)\Big) ds
+    & \int_{[0,t]\times \mathbb N}(e^{i  w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
+    \\ & =\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
     \\ & =\int_0^t \Big( 2\rho_2(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
@@
     \label{eq: N to Pi}
-    & \mathbb N_x^{\langle W_{t}, g\rangle}[e^{i \langle W_t, f\rangle}]
-      = \mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i \langle w_{t-s}, f\rangle} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
+    & \mathbb N_x^{ W_t( g)}[e^{i W_t(f)}]
+      = \mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
     \\ & = \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
@@
   \begin{align}
-    \frac{\mathbf P_{\delta_x}[\langle X_t,f^{\pm}\rangle e^{i \langle X_t,f\rangle}]}{\mathbf P_{\delta_x}[\langle X_t,f^{\pm}\rangle ]}
-    = \mathbf P_{\delta_x}[e^{i \langle X_t,f\rangle}] \mathbb N_x^{\langle W_t,f^{\pm}\rangle}[e^{i \langle X_t,f\rangle}].
+    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm}) e^{i X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm}) ]}
+    = \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{ W_t(f^{\pm})}[e^{i X_t(f)}].
   \end{align}
@@
   \begin{align}
-    \frac{\mathbf P_{\delta_x}[\langle X_t, f\rangle e^{i \langle X_t, f\rangle}] }{\mathbf P_{\delta_x}[e^{i \langle X_t, f\rangle}]}
-    & = \mathbf P_{\delta_x}[\langle X_t, f^+\rangle] \mathbb N_x^{\langle W_t, f^+\rangle} [e^{i \langle X_t, f\rangle}] - \mathbf P_{\delta_x}[\langle X_t, f^-\rangle]\mathbb N_x^{\langle W_t, f^-\rangle}[e^{i \langle X_t, f\rangle}]
+    \frac{\mathbf P_{\delta_x}[X_t(f) e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
+    & = \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i X_t(f)}]
     \\ & = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
@@
     \frac{\partial}{\partial \theta} {U_t(\theta f)(x)}
-    = \frac{\mathbf P_{\delta_x}[i\langle X_t, f\rangle e^{i \langle X_t, f\rangle}] }{\mathbf P_{\delta_x}[e^{i \langle X_t, f\rangle}]}
+    = \frac{\mathbf P_{\delta_x}[i X_t(f) e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
     = \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
@@
   \[
-    |e^{i W_t(f_n)} - 1| \leq \langle W_t, |f|\rangle;
-    \quad \mathbb N_x[\langle W_t, |f|\rangle] = (P_t^{\rho_1} |f|)(x) < \infty,
+     |e^{i W_t(f_n)} - 1| \leq W_t(|f|);
+    \quad \mathbb N_x[W_t(|f|)] = (P_t^{\rho_1} |f|)(x) < \infty,
  \]
@@
   \[
-    big|\psi(\xi_s,- U_{t-s}f_n)\big|
+    \big|\psi(\xi_s,- U_{t-s}f_n)\big|
     \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2,
@@
 
+\bibitem{Bertoin}
+J. Bertoin,
+\emph{L\'evy processes}.
+Cambridge Tracts in Mathematics, 121. Cambridge
+University Press, 1996.
+
+\bibitem{BRY}
+J. Bertoin, B. Roynette and M. Yor,
+\emph{Some connections between (sub)critical branching mechanisms and Bernstein functions}.
+arXiv:0412322.
+
 \bibitem{ChenRenWang2008An-almost}
@@
   \emph{Fluctuations of {L}\'{e}vy processes with applications},
-  % 2 ed., Universitext, Springer, Heidelberg, 2014.
     Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
@@
 \bibitem{LiuRenSong2009Llog}
-  % R.~Liu, Y.-X. Ren, and R.~Song,
   R.-L. Liu, Y.-X. Ren, and R. Song,
@@
 \bibitem{LiuRenSong2013Strong}
-  % R.~Liu, Y.-X. Ren, and R.~Song,
   R.-L. Liu, Y.-X. Ren, and R. Song,
@@
   \emph{L{\'e}vy processes and infinitely divisible distributions},
-  % Cambridge Studies in Advanced Mathematics, vol.~68, Cambridge University Press, Cambridge, 2013.
   Translated from the 1990 Japanese original. Revised by the author. Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.

### 2019-09-07 response.tex
change response.tex

@@
-% * The preamble
-% ! This TeX file uses 'amsart' for its document class.
+%%%----Documentstyles-----------------------
 \documentclass[12pt,a4paper]{amsart}
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-2in}
-\calclayout
-% ! 'amsmath', 'amsthm', 'amsfonts' package is automatically loaded by 'amsart' class.
-% ! Below is the configuration of 'amsmath' package.
-\numberwithin{equation}{section}
-\allowdisplaybreaks
-% ! Below is the configuration of 'amsthm' package.
-\theoremstyle{plain}
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollaray}
-\newtheorem{conj}[thm]{Conjecture}
-\theoremstyle{definition}
-\newtheorem{defi}[thm]{Definition}
-\newtheorem{exa}[thm]{Example}
-\newtheorem{asp}{Assumption}
-\newtheorem{iss}{Issue}
-\newtheorem{rem}[thm]{Remark}
-\newtheorem*{ack}{Acknowledgment}
-% ! 'inputenc' package is used to specify the set of characters allowed to input into this TeX file.
-% \usepackage[utf8]{inputenc}
-% ! 'foutenc' package is used to specify the set of characters allowed to output into the generated pdf file.
-% \usepackage[T1]{fontenc}
-% ! 'amssymb', 'mathrsfs' and 'mathtools' packages provide additional math symbols from the AMS default symbol fonts. They are compatible with the AMS class and is recommended to be used.
-\usepackage{amssymb}
+\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
+\usepackage{hyperref}
+\usepackage{comment}
 \usepackage{mathtools}
-\mathtoolsset{showonlyrefs}
-\usepackage{mathrsfs}
-% ! 'hyperref' package is used to handle cross-referencing in the generated pdf file.
-\usepackage[backref]{hyperref}
-% ! Other packages
-\usepackage{xcolor}
-\usepackage{comment}
-% * Top matter
+\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
+\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
+
+%%%----Environments------------------------
+%\newtheorem{thm}{Theorem}[section]
+%\newtheorem{lem}[thm]{Lemma}
+%\newtheorem{prop}[thm]{Proposition}
+%\numberwithin{equation}{section}
+
+%%%---------Top matter----------------
+%YX \title
+%YX [Response]
+\title[Response]{\large Response to the referee's comments}
+%%%----Main-------------------------------
 \begin{document}
-\title
-[Response]
-{Response}
 \maketitle	
-% * Document body
-We are grateful to the referees for their helpful comments.
-We have incorporated all the comments made by the referees.
-Here are the specific changes in response to the comments of the referees.
+	We are grateful to the referee for the very helpful comments.
+We have incorporated all the comments made by the referee.
+Here are the specific changes in response to the comments of the referee.
+
+There are many duplications in the current presentation, see the comments below for more details.
+With a more general formulation, these duplications can be removed reducing the number of pages
+dramatically. For example, it is realistic that the same content can be presented in 45 pages rather
+than 60 pages.
+
+\emph{We made a more general formulation. The paper has been rearranged and streamlined.
+See the details below. We were not able to reduce the length to 45 pages, but we are pretty close. The paper is now 46 pages.}
+
+Also, the authors should give stronger interpretations of the assumptions and the results. What
+do the the parameters $\alpha$, $\beta$, $\kappa_f$, $b$ represent, and why does the limit behavior change with these
+parameters? For example, what's the interpretation of the inequality $\alpha\beta > \kappa_f b(1 + \beta)$? Why is
+this referred to this as the large branching rate regime?
+
+\emph{We added some explanation about these at the end of Subsection 1.2.}
+
 \begin{enumerate}
@@
 
-  \emph{We add an interpretation in Remark 1.1.}
+  \emph{We added an interpretation in Remark 1.1.
+   See also the bullet point about $\beta$ on page 7.
+    }
 \item
   P.2.L.-8.
-  Please provide an interpretation of the expression $\alpha\beta - \kappa f b(1+\beta)$?
+  %Please provide an interpretation of the expression $\alpha\beta - \kappa f b(1+\beta)$?
+   Please provide an interpretation of the expression $\alpha\beta - \kappa_f b(1+\beta)$?
 
-\emph{We add some discussion about this in the middle of page 7.}.
+\emph{We added some discussion about this in the middle of page 7.}.
 
-  Perhaps it might be easier to interpret if you wrote the inequality $\alpha \beta > \kappa f b(1 + \beta)$ as $\alpha \frac{\beta}{1+\beta} > \kappa f b$.
+  Perhaps it might be easier to interpret if you wrote the inequality $\alpha \beta > \kappa_f b(1 + \beta)$ as $\alpha \frac{\beta}{1+\beta} > \kappa_f b$.
   This way the parameters on the left are branching related, whereas the parameters on the right are related to the Ornstein-Uhlenbeck process.
@@
 
-  Is there an intuitive explanation why $\rho$ doesn’t play a role? 
+  Is there an intuitive explanation why $\rho$ doesn't play a role?
   Why does $b$ come into play but $\sigma$ does not?
 
-  \emph{We added some discussion about this at the end of subsection 1.2}.
+  \emph{We added some discussion about this at the end of Subsection 1.2}.
 \item
@@
 
-  \emph{We added some discussion about this at the end of subsection 1.2}.
+  \emph{We added some discussion about this at the end of Subsection 1.2.
+We mentioned that we hope to prove spatial CLTs for superprocesses with general motions without the second moment assumption
+on the branching mechanism in a future project (see paragraph 2 of page 8)
+}.
 \item
@@
 
-  \emph{We add some discussion about this in the middle of page 7.}.
+  \emph{We added some discussion about this in the middle of page 7.}
 
@@
 
-  \emph{We add some explanation at the beginning of page 6.}
+  \emph{We added some explanation at the beginning of page 6.}
 \item
@@
 
-  \emph{Their definitions are now unified in (1.9).}
+  \emph{The definitions are now unified in (1.9).}
 \item
   P.8.
-  Instead of calling this section “some intuitive explanation”, it would be more appropriate to call it “an outline of the methodology”.
+  Instead of calling this section "some intuitive explanation", it would be more appropriate to call it "an outline of the methodology".
 
@@
 
-  \emph{TBD.}
+  \emph{We added some explanation and gave two new references before the example.}
+
 \item
@@
   There is substantial repetition in statements 2 and 3, please combine these into one statement.
-  In fact, it would be even better if all the hypothesis on the operators, index sets , etc can be given at the beginning of the lemma, and then all the results can be listed without saying “Suppose that” each time.
-  Similarly assumptions don’t need to be restated in the proof. 
+  In fact, it would be even better if all the hypothesis on the operators, index sets , etc can be given at the beginning of the lemma, and then all the results can be listed without saying "Suppose that" each time.
+  Similarly assumptions don't need to be restated in the proof.
   There are duplications in the proof, these should be removed as well.
-  For example you can say, “If $f,g \in \mathcal P^+$ with $f \leq g$, then $R_AR_Bf \leq R_AR_Bg$, and $R_A \times R_B f \leq R_A \times R_B g$ and $R_A +R_B f \leq (R_A +R_B)g$, and ...”. 
+  For example you can say, "If $f,g \in \mathcal P^+$ with $f \leq g$, then $R_AR_Bf \leq R_AR_Bg$, and $R_A \times R_B f \leq R_A \times R_B g$ and $R_A +R_B f \leq (R_A +R_B)g$, and ...".
   These should reduce the length of Lemma 2.4 and and its proof by half.
@@
   P.16-17.Lemma 2.6., Proposition 2.7.
-  If you use a single notation $m_t(f)$, instead of $m_t, \bar m$ and $\tilde m$ , you can simply say that $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of ...” without repeating it 5 times.
+  If you use a single notation $m_t(f)$, instead of $m_t, \bar m$ and $\tilde m$ , you can simply say that $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of ..." without repeating it 5 times.
   No need to provide separate statements for $m_t$ and $m$, since $m$ can be considered as a special case of $m_t$ for a suitable value of $t$, (e.g. $t = \infty$, or $t = \Delta$.)
 
-  \emph{We now uses the single notation $m_t[f]$. Now the presentation of Lemma 2.6 and Proposition 2.7 is much shorter.}
+  \emph{We now use the single notation $m_t[f]$. Now the presentation of Lemma 2.6 and Proposition 2.7 is much shorter.}
 \item
@@
   P.20.L.3.
-  Please give a reference after the statement “It is well known that”.
+  Please give a reference after the statement "It is well known that".
 
-  \emph{We add a new reference above equation (2.7) as suggested.}
+  \emph{We added a new reference above equation (2.7) as suggested.}
 \item
@@
   These equations can be stated in a single line.
-  For example, “if $0< \lambda \leq v_t(\lambda) < \bar v < v_t(\lambda^*)<\lambda^* < \infty$, then...”.
+  For example, if $0< \lambda \leq v_t(\lambda) < \bar v < v_t(\lambda^*)<\lambda^* < \infty$, then.
 
@@
 
-  \emph{We added a new subsection 3.2 which deals with the CLTs for one unite time intervals in a unified way.}
+  \emph{We added a new Subsection 3.2 which deals with the CLTs for unit time intervals in a unified way.}
 \item
+  %Proof of Lemma 3.4. Please indicate clearly where $\alpha \beta \leq \kappa f b(1 + \beta)$ is used.
+  %Same goes for the case $\alpha beta > \kappa f b(1 + \beta)$.
   Proof of Lemma 3.4. Please indicate clearly where $\alpha \beta \leq \kappa f b(1 + \beta)$ is used.
-  Same goes for the case $\alpha beta > \kappa f b(1 + \beta)$.
+  Same goes for the case $\alpha \beta > \kappa_f b(1 + \beta)$.
 
@@
 
-  \emph{We agree that the structure of these two proofs are very similar.
-But there are differences lying in the details even out of the range of Step 2 which we believe is crucial.
-For example:  at the beginning, the scaling coefficient in case 1 is $\|tX_t\|^{\frac{1}{1+\beta}}$ but in case 2 is $\|X_t\|^{\frac{1}{1+\beta}}$; (ii) In Step 4, the exceptional event for case 1 is chosen as $\mathcal E_t = \{\|X_t\| > t^{-1/2} e^{\alpha t}\}$ but in case 2 is chosen as $ A_t(\epsilon) = \{\|X_t\|> e^{(\alpha - \epsilon )t}\}$.
+  \emph{We agree that the structure of these two proofs are very similar. But there are
+differences lying in the details which we believe are pretty important:
+(i) the scaling coefficient in case 1 is $\|tX_t\|^{\frac{1}{1+\beta}}$ but in case 2 is $\|X_t\|^{\frac{1}{1+\beta}}$;
+ (ii) In Step 4, the exceptional event for case 1 is chosen as $\mathcal E_t = \{\|X_t\| > t^{-1/2} e^{\alpha t}\}$ but in case 2 is chosen as $ A_t(\epsilon) = \{\|X_t\|> e^{(\alpha - \epsilon )t}\}$.
 }
@@
 
-  \emph{These two lemmas are now deleted, and their proofs are moved into the new subsection 3.5. 
+  \emph{These two lemmas are now deleted, and their proofs are moved into the new Subsection 3.5.
 In the new version, the proof of CLTs for three different cases (Subsection 3.3, 3.4 and 3.5) are rearranged in such a way that (1) their structure can be clearly compared; and (2) trivial duplications are avoided as much as possible.}

### 2019-09-08 supCLT.tex
change supCLT.tex

@@
   assumed to be of polynomial growth.
-Some phase transitions arise  for the central limit theorems in the sense that the forms of the central limit theorem are different in three different regimes corresponding the branching rate being relatively small, large or at a critical balanced value.
+Some phase transitions arise  for the central limit theorems in the sense that the forms of the central limit theorem are different in three different regimes corresponding the branching rate % being relatively small, large or at a critical balanced value.
+being relatively small, large or critical at a balanced value.
 \end{abstract}
@@
 Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
-The functional version of the CLT was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
+% The functional version of the CLT was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
+The functional version of the CLTs were established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
 
@@
  Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable offspring distribution.
-They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any CLT type result in the large branching rate regime
+They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any CLT type result in the large branching rate regime.
 We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior
@@
 \(
-  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f),
+  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)
 \)
@@
 Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial/\partial x_k^{p_k})$.
+% For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial/\partial x_k^{p_k})$.
+For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
 The \emph{Hermite polynomials} are defined by
@@
 It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
-For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$, where
+For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
 \begin{align}
@@
   T_t f
-  := \sum_{p \in \mathbb Z_+^d} e^{-| |p|b - \alpha \tilde \beta |t} \langle f, \phi_p \rangle_{\varphi}  %\phi_p,
-\phi_p
+  := \sum_{p \in \mathbb Z_+^d} e^{-| |p|b - \alpha \tilde \beta |t} \langle f, \phi_p \rangle_{\varphi} \phi_p
   ,\quad t\geq 0, f\in \mathcal P,
 \end{align}
-and a family of $\mathbb C$-valued functionals 
-%Jianjie $(m_t)_{0 \leq s \leq t < \infty}$ on $\mathcal P$ 
-$(m_t)_{0 \leq t < \infty}$ on $\mathcal P$ 
-by
+and a family of $\mathbb C$-valued functionals $(m_t)_{0 \leq t < \infty}$ on $\mathcal P$ by
 \begin{align}
@@
 \end{align}
-Define $ \mathcal C_s := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
-and $ \mathcal C_l   := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
+% Define $ \mathcal C_s := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
+Define $ \mathcal C_s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
+% and $ \mathcal C_l   := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
+For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
+and $ \mathcal C_l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
 For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
@@
 At this point, we should mention that the theorem above does not cover all $f\in \mathcal P$.
-%Indeed, considering a general $f \in \mathcal P$ which can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c\setminus\{0\}$ and $f_l \in \mathcal C_l$, as a simple corollary of Theorem \ref{thm:M},
-%one can verify that
-%\[
-%  \|tX_t\|^{-\frac{1}{1+\beta}} \Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big)
-%  \xrightarrow[t\to \infty]{d}
-%  \zeta^{f_c}
-%\]
-%for each $\mathbb P_\mu(\cdot | D^c)$ with $\mu \in \mathcal M_c(\mathbb R^d)\setminus \{0\}$.
 Theorem \ref{thm:M}.(1) can be rephrased as if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$.
@@
 $ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
-A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c\setminus\{0\}$ and $f_l \in \mathcal C_l$. For $f\in  \mathcal P$
-satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ maybe non-trivial.
+% A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c\setminus\{0\}$ and $f_l \in \mathcal C_l$. 
+A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$. 
+For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ maybe non-trivial.
 In this case, we do not have a CLT yet.
@@
     \leq cz^{\delta}+cz^{1-\beta}
-    ,	\quad z \in \mathbb R_+.
+    ,	z \in \mathbb R_+.
  $
@@
 Recall that $\mathcal P$ is given in \eqref{eq: polynomial growth function}.
-Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
+Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P^+\}$.
 
@@
 
-For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let 
-%Jianjie $ U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f,X_t\rangle}]|_{\theta = 1} $ 
-$ U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]|_{\theta = 1} $ 
-be the value of the characteristic exponent of the infinitely divisible random variable
-%jianjie $\langle f, X_t\rangle$ at $1$.
-$X_t(f)$
-(See the paragraph after Lemma \ref{lem: Lip of power function}).
+For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let $ U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]|_{\theta = 1} $ be the value of the characteristic exponent of the infinitely divisible random variable $X_t(f)$ (See the paragraph after Lemma \ref{lem: Lip of power function}).
 It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
@@
 \begin{proof}
-  (1). According to \eqref{eq: -v has positive real part}, $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
+  % (1). According to \eqref{eq: -v has positive real part}, $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
+  (1). According to \eqref{eq: -v has positive real part}, $-U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
   It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$, we have $ |U_t g(x)| \leq \sup_{0\leq u\leq 1}P_u^\alpha |g| (x). $
@@
   \]
-  Now using (1), (2) and (4) above, and Lemma \ref{lem: property of controllable operators}.(2)--(3), we get that the operators
+  % Now using (1), (2) and (4) above, and Lemma \ref{lem: property of controllable operators}.(2)--(3), we get that the operators
+  Now using (1), (2) and (4) above, and Lemma \ref{lem: property of controllable operators}, we get that the operators
   \[
@@
   are uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable.
-  Combining with Lemma \ref{lem: property of controllable operators}.(1) and (4), and
+  % Combining with Lemma \ref{lem: property of controllable operators}.(1) and (4), and
+  Combining with Lemma \ref{lem: property of controllable operators}, and
   \[
@@
   Combining  this with  (1)--(2) above,
-  and Lemma \ref{lem: property of controllable operators}.(1) and (4), we get that, for all $\delta > 0$ small enough, the operators
+  % and Lemma \ref{lem: property of controllable operators}.(1) and (4), we get that, for all $\delta > 0$ small enough, the operators
+  and Lemma \ref{lem: property of controllable operators}, we get that, for all $\delta > 0$ small enough, the operators
   \[
@@
 
-  (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from (5)-- (6) above and Lemma \ref{lem: property of controllable operators}.(3).
+  (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from (5)--(6) above and Lemma \ref{lem: property of controllable operators}.(3).
 \end{proof}
@@
     |T_t f_0|
-    = \Big| \sum_{p \in  \mathbb Z_+^d: \tilde \beta \alpha \leq |p|b } e^{- ( |p| b - \tilde \beta \alpha ) t} \langle f, \phi_p \rangle \phi_p \Big|
+    % = \Big| \sum_{p \in  \mathbb Z_+^d: \tilde \beta \alpha \leq |p|b } e^{- ( |p| b - \tilde \beta \alpha ) t} \langle f, \phi_p \rangle \phi_p \Big|
+    = \Big| \sum_{p \in  \mathbb Z_+^d: \tilde \beta \alpha \leq |p|b } e^{- ( |p| b - \tilde \beta \alpha ) t} \langle f, \phi_p \rangle_\varphi \phi_p \Big|
     = e^{\tilde \beta \alpha t} | P_t f_0 |
@@
     |T_t f_1|
-    \leq e^{- \delta t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > |p|b}
-    |\langle f, \phi_p \rangle \phi_p|
+    % \leq e^{- \delta t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > |p|b} |\langle f, \phi_p \rangle \phi_p|
+    \leq e^{- \delta t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > |p|b} |\langle f, \phi_p \rangle_\varphi \phi_p|
     =: e^{- \delta t} h_1,
@@
       = \Big| \frac{1}{t} \cdot t \int_0^1  \big\langle (-iT_{rt}f)^{1+\beta} - (-if_c)^{1+\beta}, \varphi\big \rangle ~dr \Big|\\
-    &\leq \int_0^1  \big\langle |(-iT_{rt}f)^{1+\beta} - (-if_c)^{1+\beta}|, \varphi\big \rangle ~dr = \langle g,\varphi\rangle\int_0^1 e^{-\delta rt} ~dr
+    &\leq \int_0^1  \big\langle |(-iT_{rt}f)^{1+\beta} - (-if_c)^{1+\beta}|, \varphi\big \rangle ~dr 
+      % = \langle g,\varphi\rangle\int_0^1 e^{-\delta rt} ~dr
+      \leq \langle g,\varphi\rangle\int_0^1 e^{-\delta rt} ~dr
       \xrightarrow[t\to \infty]{} 0.
@@
     \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx)
-    = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(\xi t)k(\xi,dt)
+    % = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(\xi t)k(\xi,dt)
+    = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(t \xi)k(\xi,dt)
     , \quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
@@
 \begin{proof}
-Fix a $g \in \mathcal P$.
+% Fix a $g \in \mathcal P$.
+Fix the $g \in \mathcal P$.
 We write  $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$,  and $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
@@
   \[
-    \kappa_{(\frac{\partial T_1 g_0}{\partial x_j})}
+    % \kappa_{(\frac{\partial T_1 g_0}{\partial x_j})}
+    \kappa_{(\partial_j T_1 g_0)}
     \geq \kappa_{(T_1 g_0)} - 1
@@
 \label{sec: Small value probability}
-In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}
-%Jianjie add
-satisfying Grey's condition and $L \log L$ condition.
-%add end 
+In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}.
+% DELETED
+% satisfying Grey's condition and $L \log L$ condition.
+% END DELETED
 Such a process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying
@@
 Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$ when $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
-%Suppose that Grey's condition is satisfied, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-%Also suppose that the $L \log L$ condition is satisfied, i.e.,
-%$
-%  \int_1^\infty y \log y~\pi(dr)
-% < \infty.
-%$
+Suppose that Grey's condition is satisfied i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
+Also suppose that the $L \log L$ condition is satisfied i.e.,
+$
+  \int_1^\infty y \log y~\pi(dr)
+ < \infty.
+$
 We write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
@@
   \end{align}
-  where the $C>0$ above is chosen as
-%Jianjie \[
-  $
-    C
-     := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh).
-    \qedhere
-  $
-%Jianjie \]
+  % where the $C>0$ above is chosen as $ C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh).\qedhere $
+  where the $C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh)>0$.
 \end{proof}
@@
   \begin{align}
-     & \mathbb P_\mu\big[|\mathcal I_r^sX_t(g)|^{1+\gamma}\big]
+     & \mathbb P_\mu[|\mathcal I_r^sX_t(g)|^{1+\gamma}]
        = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^sX_t(g)|>\lambda) d\lambda \\
@@
 
-Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$ 
-%Jianjie Define $ H_t^p :=e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
-and $ H_t^p :=e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
+Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$ and $ H_t^p :=e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
 
@@
     \|H_t^p\|_{\mathbb P_\mu;1+\gamma}
-    \leq c e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
+    % \leq c e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
+    \leq C e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
     = C
@@
   \end{align}
-  converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
+  % converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
+  converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
 
@@
     \|M_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq \|e^{-(\alpha-a_0 b)t}X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    % \leq \|e^{-(\alpha-a_0 b)t}X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
+    \leq \|e^{-(\alpha-a_0 b)t}X_t(\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq C_6(e^{-\delta_3 t}+\frac{1}{\delta_3}),
@@
   J^f_1(t,\epsilon)
-%Jianjie  & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t-1}(Rh_2)]
 & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
@@
   \end{align}
-  where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique %locally bounded positive solution to the equation
-locally bounded non-negative solution to the equation
+  where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded non-negative solution to the equation
   \begin{align}

### 2019-09-08 response.tex
change response.tex

@@
 
+\begin{itemize}
+\item
 There are many duplications in the current presentation, see the comments below for more details.
@@
 
+\item
 Also, the authors should give stronger interpretations of the assumptions and the results. What
@@
 
+\end{itemize}
 \begin{enumerate}
@@
 
-\emph{We added some discussion about this in the middle of page 7.}.
+\emph{We added some discussion about this in the middle of page 7.}
 
@@
   P.8.
-  Instead of calling this section "some intuitive explanation", it would be more appropriate to call it "an outline of the methodology".
+  Instead of calling this section ``some intuitive explanation'', it would be more appropriate to call it ``an outline of the methodology''.
 
@@
   P.20.L.3.
-  Please give a reference after the statement "It is well known that".
+  Please give a reference after the statement ``It is well known that''.
 
-  \emph{We added a new reference above equation (2.7) as suggested.}
+  % \emph{We added a new reference above equation (2.7) as suggested.}
+  \emph{We added a new reference above equation (2.8) as suggested.}
 \item
@@
 
-  \emph{We rearranged that sentence. See the sentence right after (2.10).}
+  % \emph{We rearranged that sentence. See the sentence right after (2.10).}
+  \emph{We rearranged that sentence. See the sentence right after (2.11).}
 \item
@@
 
-  \emph{We rearranged that sentence. See the last sentence of Page 18.}
+  \emph{We rearranged that sentence. 
+% See the last sentence of Page 18.}
+See the paragraph before (2.12).}
 
@@
 
-  \emph{We added more details there. See the last display on page 20.}
+  \emph{We added more details there. 
+    % See the last display on page 20.}
+    See the first display of the proof of Theorem 2.11.}
 

### 2019-09-09 supCLT.tex
change supCLT.tex

@@
   assumed to be of polynomial growth.
-Some phase transitions arise  for the central limit theorems in the sense that the forms of the central limit theorem are different in three different regimes corresponding the branching rate % being relatively small, large or at a critical balanced value.
+%Some phase transitions arise  for the central limit theorems in the sense 
+A phase transition arises  for the central limit theorems in the sense 
+that the forms of the central limit theorem are different in three different regimes corresponding the branching rate 
 being relatively small, large or critical at a balanced value.
@@
 $ (X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
-Note that, in the setting of this paper, $X_t(f)$ typically have infinite second moment.
+%Note that, in the setting of this paper, $X_t(f)$ typically have infinite second moment.
+Note that, in the setting of this paper, $X_t(f)$ typically has infinite second moment.
 
@@
 Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
-% The functional version of the CLT was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
 The functional version of the CLTs were established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
@@
 \)
-for each $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
+for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
 
@@
 Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-% For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial/\partial x_k^{p_k})$.
 For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
@@
 \end{align}
-% Define $ \mathcal C_s := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
 Define $ \mathcal C_s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
-% and $ \mathcal C_l   := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
-For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
 and $ \mathcal C_l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$. 
+%new
+Note that $\mathcal C_s$ is an infinite dimensional space, $ \mathcal C_l$ and $\mathcal C_c$
+are finite dimensional spaces, and $\mathcal C_c$ might be empty.
+%end new
 For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
@@
 $ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
-% A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c\setminus\{0\}$ and $f_l \in \mathcal C_l$. 
 A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$. 
@@
 \begin{proof}
-  % (1). According to \eqref{eq: -v has positive real part}, $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
   (1). According to \eqref{eq: -v has positive real part}, $-U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
@@
   \]
-  % Now using (1), (2) and (4) above, and Lemma \ref{lem: property of controllable operators}.(2)--(3), we get that the operators
   Now using (1), (2) and (4) above, and Lemma \ref{lem: property of controllable operators}, we get that the operators
@@
   are uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable.
-  % Combining with Lemma \ref{lem: property of controllable operators}.(1) and (4), and
   Combining with Lemma \ref{lem: property of controllable operators}, and
@@
   Combining  this with  (1)--(2) above,
-  % and Lemma \ref{lem: property of controllable operators}.(1) and (4), we get that, for all $\delta > 0$ small enough, the operators
   and Lemma \ref{lem: property of controllable operators}, we get that, for all $\delta > 0$ small enough, the operators
@@
     |T_t f_0|
-    % = \Big| \sum_{p \in  \mathbb Z_+^d: \tilde \beta \alpha \leq |p|b } e^{- ( |p| b - \tilde \beta \alpha ) t} \langle f, \phi_p \rangle \phi_p \Big|
     = \Big| \sum_{p \in  \mathbb Z_+^d: \tilde \beta \alpha \leq |p|b } e^{- ( |p| b - \tilde \beta \alpha ) t} \langle f, \phi_p \rangle_\varphi \phi_p \Big|
@@
     |T_t f_1|
-    % \leq e^{- \delta t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > |p|b} |\langle f, \phi_p \rangle \phi_p|
     \leq e^{- \delta t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > |p|b} |\langle f, \phi_p \rangle_\varphi \phi_p|
@@
     &\leq \int_0^1  \big\langle |(-iT_{rt}f)^{1+\beta} - (-if_c)^{1+\beta}|, \varphi\big \rangle ~dr 
-      % = \langle g,\varphi\rangle\int_0^1 e^{-\delta rt} ~dr
       \leq \langle g,\varphi\rangle\int_0^1 e^{-\delta rt} ~dr
@@
     \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx)
-    % = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(\xi t)k(\xi,dt)
     = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(t \xi)k(\xi,dt)
@@
 \begin{proof}
-% Fix a $g \in \mathcal P$.
-Fix the $g \in \mathcal P$.
+%Fix the $g \in \mathcal P$.
+Fix $g \in \mathcal P$.
 We write  $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$,  and $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
@@
     = T_s (g_0 + g_1)
-    = e^{\alpha \tilde \beta s}P_s g_0 + \sum_{p \in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} \langle g_1, \phi_p \rangle e^{-(\alpha \tilde \beta - |p|b)s} \phi_p.
-  \]
-  Notice that the second term is in $C_\infty(\mathbb R^d)\cap \mathcal P$ since it is a finite summation of polynomials, and the first term is also in $C_\infty (\mathbb R^d) \cap \mathcal P$ according to \cite[Fact 1.1]{MarksMilos2018CLT}.
+    = e^{\alpha \tilde \beta s}P_s g_0 + \sum_{p \in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} 
+    %\langle g_1, \phi_p \rangle e^{-(\alpha \tilde \beta - |p|b)s} \phi_p.
+    \langle g_1, \phi_p \rangle_\varphi e^{-(\alpha \tilde \beta - |p|b)s} \phi_p.
+  \]
+  Notice that the second term is in $C_\infty(\mathbb R^d)\cap \mathcal P$ since it is a finite %summation of polynomials, 
+  sum of polynomials, 
+  and the first term is also in $C_\infty (\mathbb R^d) \cap \mathcal P$ according to \cite[Fact 1.1]{MarksMilos2018CLT}.
 
@@
   \[
-    % \kappa_{(\frac{\partial T_1 g_0}{\partial x_j})}
     \kappa_{(\partial_j T_1 g_0)}
@@
 In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}.
-% DELETED
-% satisfying Grey's condition and $L \log L$ condition.
-% END DELETED
 Such a process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying
@@
   \end{align}
-  % where the $C>0$ above is chosen as $ C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh).\qedhere $
-  where the $C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh)>0$.
+%  where the $C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh)>0$.
+where $C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh)>0$.
 \end{proof}
@@
 
-Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$ and $ H_t^p :=e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
+Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the %eigenvalue $-|p|b$ and $ H_t^p :=e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
+eigenvalue $-|p|b$ and $ H_t^p =e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
 
@@
     \|H_t^p\|_{\mathbb P_\mu;1+\gamma}
-    % \leq c e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
     \leq C e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
@@
   \end{align}
-  % converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
   converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
@@
     \|M_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    % \leq \|e^{-(\alpha-a_0 b)t}X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq \|e^{-(\alpha-a_0 b)t}X_t(\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}

### 2019-09-10 supCLT.tex
change supCLT.tex

@@
-% * The preamble
 \documentclass[12pt,a4paper]{amsart}
@@
 \allowdisplaybreaks
-% * Top matter
 \begin{document}
@@
   assumed to be of polynomial growth.
-%Some phase transitions arise  for the central limit theorems in the sense 
 A phase transition arises  for the central limit theorems in the sense 
@@
 \maketitle
-% * Contents
-% ** Introduction
 \section{Introduction}
-% *** Motivation
 \subsection{Motivation}
@@
 \begin{align}
-  V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(V_{t-s}f(\xi_s)\big)~ds\Big]
+  V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) )~ds\Big]
 	= \Pi_x [f(\xi_t)]
@@
 $ (X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
-%Note that, in the setting of this paper, $X_t(f)$ typically have infinite second moment.
 Note that, in the setting of this paper, $X_t(f)$ typically has infinite second moment.
@@
 
-% *** Main results
 \subsection{Main results}
 \label{sec:I:R}
-% **** Assumption 1
 We will always assume that the following assumption holds.
@@
 
-% **** Assumption 2
 Denote by $\Gamma$ the gamma function.
@@
 \end{rem}
-% **** Mean semigroup
 Let us introduce some notation in order to give the precise formulation of our main result.
@@
 
-% **** Spectral Property
 The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
@@
 
-% **** Martingale limits
 Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
@@
 for all $t\geq 0$.
-If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lem:M:L:ML} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+If $\alpha \tilde \beta>|p|b, \tilde \beta := \beta/(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lem:M:L:ML} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
@@
   \label{thm: law of large number}
-  If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
+  If $f \in \mathcal{P}$ satisfies $\alpha\tilde \beta>\kappa_f b$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
   \[
@@
 
-% **** Stable CLT
 For the rest of this subsection, we focus on the CLTs of $X_t(f)$ for a large collection of $f\in \mathcal P\setminus \{0\}$.
@@
 \item
-  the small branching rate case: where
+  the small branching rate case where
 $f$ satisfies $\alpha \tilde \beta < \kappa_f b$;
 \item
-  the critical branching rate case: where
+  the critical branching rate case where
 $f$ satisfies $\alpha \tilde \beta = \kappa_f b$; and
 \item
-  the large branching rate case:  where
+  the large branching rate case  where
 $f$ satisfies $\alpha \tilde \beta > \kappa_f b$.
@@
 and $ \mathcal C_l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$. 
-%new
 Note that $\mathcal C_s$ is an infinite dimensional space, $ \mathcal C_l$ and $\mathcal C_c$
 are finite dimensional spaces, and $\mathcal C_c$ might be empty.
-%end new
 For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
@@
 
-% *** An outline of the methodology
 \subsection{An outline of the methodology}
@@
 \]
-where $(\zeta_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables.
+where $(\zeta^f_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables.
 If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \xi^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have
@@
 
-% ** Preliminaries
 \section{Preliminaries}
-% *** Branching mechanisms
 \subsection{Branching mechanism}
@@
 
-% *** Controllers for the super-OU processes
 \subsection{Controllers for the super-OU processes}
@@
 
-% *** Stable distributions
 \subsection{Stable distributions}
@@
     m[\theta f]
-    = \eta \int_0^{\infty}~ds\int_{\mathbb R^d} \big(-i\theta T_s f(x)\big)^{1+\beta} \varphi(x)~dx,
+    = \eta \int_0^{\infty}~ds\int_{\mathbb R^d} (-i\theta T_s f(x))^{1+\beta} \varphi(x)~dx,
     \quad \theta \in \mathbb R.
@@
 \begin{proof}
-%Fix the $g \in \mathcal P$.
 Fix $g \in \mathcal P$.
@@
     = e^{\alpha \tilde \beta s}P_s g_0 + \sum_{p \in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} 
-    %\langle g_1, \phi_p \rangle e^{-(\alpha \tilde \beta - |p|b)s} \phi_p.
     \langle g_1, \phi_p \rangle_\varphi e^{-(\alpha \tilde \beta - |p|b)s} \phi_p.
   \]
-  Notice that the second term is in $C_\infty(\mathbb R^d)\cap \mathcal P$ since it is a finite %summation of polynomials, 
-  sum of polynomials, 
-  and the first term is also in $C_\infty (\mathbb R^d) \cap \mathcal P$ according to \cite[Fact 1.1]{MarksMilos2018CLT}.
+  Notice that the second term is in $C_\infty(\mathbb R^d)\cap \mathcal P$ since it is a finite sum of polynomials, and the first term is also in $C_\infty (\mathbb R^d) \cap \mathcal P$ according to \cite[Fact 1.1]{MarksMilos2018CLT}.
 
@@
 
-% *** Small value probability
 \subsection{Small value probability}
@@
   \end{align}
-%  where the $C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh)>0$.
 where $C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh)>0$.
@@
 
-% *** law of large numbers
 \subsection{Law of large numbers}
@@
 
-Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the %eigenvalue $-|p|b$ and $ H_t^p :=e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
-eigenvalue $-|p|b$ and $ H_t^p =e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
+Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$ and $ H_t^p =e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
 
@@
 
-% **** Central limit theorems for one unite time interval
 \subsection{Central limit theorems for unit time intervals}
 \label{sec:critical}
-% ***** Local CLT for one interval
 In this subsection, we will establish the following CLT.
@@
 
-% ***** LCLT for Multiple interval
 The following corollary  will be used later in the proof of Theorem \ref{thm:M}.
@@
 
-% *** The small branching rate regime
 \subsection{Central limit theorem for $f\in \mathcal C_s$}
@@
 
-% ****** Step 1.
   \emph{Step 1.} We show that $I^f_0(t) \xrightarrow[t\to \infty]{d} \zeta^f$.
@@
 
-% ****** Step 2.
   \emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$.
@@
 
-% ******* Step 2.1
   \emph{Substep 2.1.} We show that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq k+1$, $ \mathbb{\widetilde{P}}_{\mu} \big[ |Y_{t,k}| ;\mathcal{D}^c_{t,k} \big] \leq C_{2.1} e^{-\delta_{2.1} (t-k)}.$
@@
 
-% ******* Step 2.2
   \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for all $k\in \mathbb Z_+$ and $t\geq k+1$, it holds that $ \mathbb{\widetilde{P}}_{\mu} [|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}$.
@@
 
-% ****** Step 3
   \emph{Step 3.}
@@
 
-% ****** Step 4
 	\emph{Step 4.} We will show that $I^f_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
@@
 
-% ****** Final Step
   \emph{Step 5.} Combining Steps 1--4, we complete the proof of Theorem  \ref{thm:M}.\eqref{thm:M:1}.
@@
 
-% *** Critical branching rate regime
 \subsection{Central limit theorem for $f \in \mathcal C_c$}
@@
 
-% ****** Step 2.
   \emph{Step 2.} We show that $ I^f_1(t) - I^f_0 (t) \xrightarrow[t\to \infty]{d} 0$.
@@
 
-% ******* subStep 2.1
   \emph{Substep 2.1.}
@@
 
-% ******* Step 2.2
   \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for all $k\in \mathbb N$ and $t\geq k+1$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.$
@@
 
-% ****** Step 4
   \emph{Step 4.} Similar to Step 4 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
@@
 
-% ****** Final step
  	\emph{Step 5.} Combining Steps 1--4, we complete the proof of Theorem \ref{thm:M}.\eqref{thm:M:2}.
@@
 
-% *** The large branching rate regime: CLT
 \subsection{Central limit theorem for $f\in \mathcal C_l$}
 \label{sec: large rate clt}
-% ***** Proof or the main result
 \begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:3})]
@@
 
-% ******* subStep 2.1
   \emph{Substep 2.1.} Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} t}$.
@@
 
-% ** Appendix
 \appendix
@@
     & \Big| \frac{e^{-zy} - e^{-z_0 y}+(z-z_0) y}{z-z_0} \Big|
-      = \frac{1}{|z-z_0|}\Big| \int_0^1 \big(-y e^{-(\theta z+(1-\theta)z_0)y}+y\big)(z-z_0)d\theta\Big| \\
+      = \frac{1}{|z-z_0|}\Big| \int_0^1 (-y e^{-(\theta z+(1-\theta)z_0)y}+y)(z-z_0)d\theta\Big| \\
     & \leq y\int_0^1 |1-e^{-(\theta z +(1-\theta)z_0)y}| d\theta
@@
 
-% *** Feynman-Kac formula with complex valued functions
 \subsection{Feynman-Kac formula with complex valued functions}
@@
 
-% ** Superprocesses
 \subsection{Superprocesses}
@@
 
-% ** Semigroup for superproccesses
 \subsection{Semigroups for superprocesses}
@@
     \label{eq: upper bound of psi(v)}
-    \big|\psi\big(x,-U_tf\big)\big|
+    |\psi (x,-U_tf)|
     \leq C P^{\rho_1}_t |f|(x) + C (P^{\rho_1}_t |f| (x))^2.
@@
     \psi(x,-U_tf)
-    = -\int_0^1 \psi'\big(x,-U_t(\theta f)\big) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
+    = -\int_0^1 \psi' (x,-U_t(\theta f) ) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
   \end{align}
@@
   \label{eq: domination of psi(v)}
-  & \Pi_x\Big[\int_0^t |\psi \big(\xi_s,-U_{t-s}f\big)|ds\Big]
-  \leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big] \\
-  & \leq \int_0^t \big(C_1 e^{t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds \\
+  & \Pi_x\Big[\int_0^t |\psi (\xi_s,-U_{t-s}f )|ds\Big]
+  \leq \Pi_x\Big[\int_0^t (C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2 )ds\Big] \\
+  & \leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ \Pi_{\xi_s}[|f(\xi_{t-s})|] ]+C_2 e^{2t\|\rho_1\|}\Pi_x [ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 ] )~ds \\
   & \leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\rho_1\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
@@
 
-% ** A complex-valued non-linear integral equation
 \subsection{A complex-valued non-linear integral equation}
@@
   \label{eq: complex FKPP-equation}
-  U_tf(x) - \Pi_x \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f\big) ds \Big]
+  U_tf(x) - \Pi_x \Big[\int_0^t \psi (\xi_s, - U_{t-s}f ) ds \Big]
   = i \Pi_x [f(\xi_t)].
@@
   \label{eq: complex FKPP-equation with FK-transform}
-  U_tf(x) -  \int_0^t P_{t-s}^{\rho_1} \psi_0\big(\cdot,-U_sf\big) (x)~ds
+  U_tf(x) -  \int_0^t P_{t-s}^{\rho_1} \psi_0(\cdot,-U_sf) (x)~ds
   = iP_t^{\rho_1} f(x).
@@
     & \int_{[0,t]\times \mathbb W}|e^{i w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
-      \leq \int_{[0,t]\times \mathbb W}\big(| w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw) \\
-    & \leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[X_{t-s}(|f|)] \pi(\xi_s,dy)
+      \leq \int_{[0,t]\times \mathbb W} (| w_{t-s}(f)| \wedge 2 ) \mathbf m(\xi, ds,dw) \\
+    & \leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s} ( W_{t-s}(|f|) )  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[X_{t-s}(|f|)] \pi(\xi_s,dy)
    + 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
@@
     \\ & =\int_0^t \Big( 2\rho_2(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
-    \\ & = -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
+    \\ & = -\int_0^t \psi'_0 (\xi_s, -U_{t-s}f )ds.
   \end{align}
@@
   \[
-    \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]
+    \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t \psi' (\xi_s,- U_{t-s}(\theta f) )\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]
     = \Pi_{r,x} [i f(\xi_t)]
@@
   \begin{align}
-    & \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
+    & \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du}\psi_0' (\xi_s,- U_{t-s}(\theta f) )\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
     & = \Pi_{r,x} [i e^{\int_r^t \rho_1(\xi_s)ds}f(\xi_t)].
@@
   \begin{align}
-    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-U_{t-s}f\big) ~ds\Big]
+    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi (\xi_s,-U_{t-s}f ) ~ds\Big]
     = i \theta \Pi_{r,x} [f(\xi_t)]
@@
   \begin{align}
-    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
+    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du} \psi_0 (\xi_s,- U_{t-s}f ) ~ds\Big]
     = i \Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
@@
     \label{eq: complex FKPP-equation for fn}
-    U_tf_n(x) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f_n\big) ~ds\Big]
+    U_tf_n(x) - \Pi_{x} \Big[\int_0^t \psi (\xi_s, - U_{t-s}f_n ) ~ds\Big]
     = i \Pi_{x} [f_n(\xi_t)].
@@
   \[
-    \big|\psi(\xi_s,- U_{t-s}f_n)\big|
+    |\psi(\xi_s,- U_{t-s}f_n) |
     \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2,

### 2019-09-11 supCLT.tex
change supCLT.tex

@@
 where $(\zeta^f_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables.
-If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \xi^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have
+If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \zeta^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have
 \(

### 2019-11-18 EJP1903.tex
add EJP1903.tex

--- 2019-09-11 supCLT.tex
@@
-\documentclass[12pt,a4paper]{amsart}
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-2in}
-\calclayout
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% This is the sample.tex file for the ejpecp document class.    %%
+%% This file is for ejpecp version 1.0                           %%
+%% Please be sure that you are using the lastest version:        %%
+%%  http://mirror.ctan.org/macros/latex/contrib/ejpecp/          %%
+%%                                                               %%
+%% The ejpecp class works *only* with a pdflatex engine.         %%
+%% You need the ejpecp.cls in your current directory or in any   %%
+%% directory scanned for cls files by your pdflatex engine.      %%
+%%                                                               %%
+%% Manual inclusion of page layout commands is useless.          %%
+%%                                                               %%
+%% Note that any complex file will produce delayed publication!  %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Journal selection: ECP or EJP.                                %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[EJP]{ejpecp} % replace ECP by EJP if needed.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please uncomment and adapt to your encoding if needed:        %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please add here your own packages (be minimalistic please!):  %%
+%% Please avoid using exotic packages and keep things simple.    %%
+%% It is not necessary to include ams* and graphicx packages     %%
+%% since they are automatically included by the ejpecp class.    %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \usepackage{mathtools}
@@
 \usepackage{hyperref}
-\usepackage{comment}
-\usepackage{amsthm}
-\theoremstyle{plain}
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{conj}[thm]{Conjecture}
-\theoremstyle{definition}
-\newtheorem{defi}[thm]{Definition}
-\newtheorem{rem}[thm]{Remark}
-\newtheorem{exa}[thm]{Example}
-\newtheorem{asp}{Assumption}
-\numberwithin{equation}{section}
-\allowdisplaybreaks
-\begin{document}
-\title
-[stable CLT for super-OU processes]
-{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
-\author
-[Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
-{Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
-\address{
-  Yan-Xia Ren \\
-  LMAM School of Mathematical Sciences \& Center for Statistical Science \\
-  Peking University \\
-  Beijing, P. R. China, 100871}
-\email{yxren@math.pku.edu.cn}
-\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}
-\address{
-  Renming Song \\
-  Department of Mathematics \\
-  University of Illinois at Urbana-Champaign \\
-  Urbana, IL, USA, 61801}
-\email{rsong@illinois.edu}
-\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
-\address{
-  Zhenyao Sun \\
-  School of Mathematics and Statistics\\
-  Wuhan University \\
-  Hubei, P. R. China, 100871}
-\email{zhenyao.sun@gmail.com}
-\address{
-  Jianjie Zhao \\
-  School of Mathematical Sciences \\
-  Peking University \\
-  Beijing, P. R. China, 100871}
-\email{zhaojianjie@pku.edu.cn}
-\thanks{Jianjie Zhao is the corresponding author}
-\begin{abstract}
-  In this paper, we study the asymptotic behavior of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$
+%\usepackage{comment}
+%\usepackage{amsthm}
+%\usepackage{amssymb}
+%\usepackage{color}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Title (please edit and customize):                            %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\SHORTTITLE{stable CLT for super-OU processes}
+
+\TITLE{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes \thanks{Y-X Ren's research  is partially supported by NSFC (Grant Nos.
+11671017  and 11731009) and LMEQF.
+Renming Song's research is partially supported by the Simons Foundation (\#429343, Renming Song)}} % \thanks is optional.
+Insert line breaks with \\
+
+%\DEDICATORY{Dedicated to the memory of ...} % Optional
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Authors (please edit and customize):                          %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\AUTHORS{%
+  Y.-X. Ren
+    \footnote{Peking University, Beijing, P. R. China, 100871.
+    \EMAIL{yxren@math.pku.edu.cn}}
+  \and 
+  Renming Song
+    \footnote{University of Illinois at Urbana-Champaign, Urbana, IL, USA, 61801. 
+    \EMAIL{rsong@illinois.edu}}
+  \and
+  Zhenyao Sun
+    \footnote{ Wuhan University, Hubei, P. R. China, 430072.
+    \EMAIL{zhenyao.sun@gmail.com}}
+  \and
+  Jianjie Zhao
+    \footnote{ Peking University, Beijing, P. R. China, 100871.
+   \EMAIL{zhaojianjie@pku.edu.cn}}
+}%AUTHORS
+%% Type \and between all consecutive authors (not only before the last author).
+%% Note: you may use \BEMAIL to force a line break before e-mail display.
+
+%% Here is a compact example with two authors with same affiliation
+%% \AUTHORS{%
+%%  Michael~First\footnote{Some University. \EMAIL{mf,js@uni.edu}
+%%  \and 
+%%  John~Second\footnotemark[2]}%AUTHORS
+%% Note: The \footnotemark is the footnote number that you wish to reuse. Here
+%% it is [2] (we took into account the footnote generated by \thanks in title).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please edit and customize the following items:                %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\KEYWORDS{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime} % Separate items with ;
+
+\AMSSUBJ{60J68, 60F05} % Edit. Separate items with ;
+%\AMSSUBJSECONDARY{FIXME:} % Optional, separate items with ;
+
+\SUBMITTED{March 9, 2019} % Edit.
+\ACCEPTED{November 15, 2019} % Edit.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please uncomment and edit if you have an arXiv ID:            %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\ARXIVID{NNNN.NNNNvn} % Edit.
+%\HALID{hal-NNN} % Edit.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% The following items will be set by the Managing Editor.       %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\VOLUME{0}
+\YEAR{2012}
+\PAPERNUM{0}
+\DOI{vVOL-PID}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please edit and customize the abstract:                       %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\ABSTRACT{ In this paper, we study the asymptotic behavior of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$
   whose underlying spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ where $\sigma, b >0$;
@@
 that the forms of the central limit theorem are different in three different regimes corresponding the branching rate 
-being relatively small, large or critical at a balanced value.
-\end{abstract}
-\subjclass[2010]{60J68, 60F05}
-\keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}
+being relatively small, large or critical at a balanced value.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please add your own macros and environments below:            %%
+%%                                                               %%
+%% If possible, avoid using \def and use instead \newcommand     %%
+%% If possible, avoid defining your own environments, and use    %%
+%% instead the environments already defined by ejpecp:           %%
+%%  assumption, assumptions, claim, condition, conjecture,       %%
+%%  corollary, definition, definitions, example, exercise, fact, %%
+%%  facts, heuristics, hypothesis, hypotheses, lemma, notation,  %%
+%%  notations, problem, proposition, remark, theorem             %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\ABS}[1]{\left(#1\right)} % example of author macro
+\newcommand{\veps}{\varepsilon} % another example of author macro
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% No macro definitions below this line please!                  %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% No need for \maketitle.                                       %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please replace what follows by the body of your article       %%
+%% (up to the bibliography):                                     %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \maketitle
@@
 We will always assume that the following assumption holds.
-\begin{asp}
+\begin{assumption}
   \label{asp: Greys condition}
   The branching mechanism $\psi$ satisfies Grey's condition, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-\end{asp}
+\end{assumption}
 For $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \mu(1)$.
@@
 In this paper, we will also assume the following:
-\begin{asp}
+\begin{assumption}
   \label{asp: branching mechanism}
@@
 	for some $\delta > 0$.
-\end{asp}
+\end{assumption}
 We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
-In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
+%In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
+In the remainder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
 	Note that $\delta$ is not uniquely determined by $\pi$.
@@
 
-\begin{rem}
+\begin{remark}
   \label{rem:SP}
@@
 One can further write that $\psi(z) = - \alpha z + z^{1+\beta} l(z)$ where $l$ is a function on $[0,\infty)$ which is slowly varying at $0$.
-\end{rem}
-
-\begin{rem}
+\end{remark}
+
+\begin{remark}
 It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism},
@@
 This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
-\end{rem}
+\end{remark}
 Let us introduce some notation in order to give the precise formulation of our main result.
@@
 \]
-which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
-Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
+%which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
+which is the lowest non-zero frequency in the eigen-expansion \eqref{semicomp1}.
+%Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
+Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-constant, then $\kappa_f<\infty$.
 In particular, the order of any constant non-zero function is zero.
@@
 It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-\begin{thm}
+\begin{theorem}
   \label{thm: law of large number}
@@
   Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
-\end{thm}
+\end{theorem}
 If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
@@
 
-\begin{thm}
+\begin{theorem}
   \label{thm:M}
@@
 \end{enumerate}
-\end{thm}
+\end{theorem}
 
@@
 \item
-  The coefficient $\rho$ dose not influence the result since $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$
+  %The coefficient $\rho$ dose not influence the result since $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$
+  The coefficient $\rho$ does not influence the result since $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$
   (see Remark \ref{rem:SP}).
@@
 The second term and third term are negligible after the rescaling, and for the first term we will establish
-a multi-variate unit interval CLT  which says that
+a multi-variate unit interval CLT,  which says that
 \[
@@
 Let $\mathbb C_+:= \{x+iy: x\in \mathbb R_+, y \in \mathbb R\}$ and $\mathbb C^0_+:= \{x+iy: x\in (0,\infty), y \in \mathbb R\}$.
-\begin{lem}
+\begin{lemma}
   \label{lem:CEP}
@@
   Moreover, for all $\delta > 0$ small enough, there exists $C>0$ such that for all $z\in \mathbb C_+$, we have $|\psi_1(z)| \leq C |z|^{1+\beta+\delta} + C|z|^2.$
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
 The following lemma says that the constants $\eta, \beta$ in Assumption \ref{asp: branching mechanism} are uniquely determined by the L\'evy measure $\pi$.
-\begin{lem}
+\begin{lemma}
   \label{lem: unique of beta and eta}
@@
 	Then $\eta'= \eta$ and $\beta ' = \beta$.
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
 \end{proof}
-\begin{lem}
+\begin{lemma}
   \label{lem: LlogL criterion}
@@
  $
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
 The following lemma is easy to verify.
-\begin{lem}
+\begin{lemma}
   \label{lem: property of controllable operators}
   For each $i \in \{0,1\}$, let $\mathscr O_i$ be a family of operators which is  uniformly controlled by an $h_i$-controller $R_i$ from $\mathcal D_i \subset \mathcal P^*$ to $ \mathcal I_i \subset \mathcal P^*$.
-  Then the followings hold:
+  %Then the followings hold:
+  Then the following statements hold:
   \begin{enumerate}
@@
   \end{enumerate}
-\end{lem}
+\end{lemma}
 
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lem: upper bound for usgx}
@@
 Recall that the operators $(T_t)_{t\geq 0}$ are defined by \eqref{eq:I:R:1}, and the functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
-\begin{lem}
+\begin{lemma}
   \label{lem:m}
 $(T_t)_{t\geq 0}$,  $(m_{t})_{0\leq t< \infty}$ and  $m$ are well defined.
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
   \]
-  On the other hand
+  On the other hand,
   \[
@@
 
-\begin{prop}
+\begin{proposition}
   \label{prop:PL:S}
   For each $f \in \mathcal P\setminus \{0\}$, there exists a non-degenerate $(1+\beta)$-stable random variable $\zeta^f$ such that $ E[e^{i\theta\zeta^f}] = e^{m[\theta f]}$ for all $\theta \in \mathbb R$.
-\end{prop}
+\end{proposition}
 
 The proof of the above proposition relies on the following lemma:
-\begin{lem}
+\begin{lemma}
   \label{lem: charactreisticfunction}
@@
   is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lem:P:R}
   Suppose that $g \in \mathcal P$, then there exists $h \in \mathcal P^+$ such that for all $ f \in \mathcal P_g := \{\theta T_n g: n \in \mathbb Z_+, \theta \in [-1,1]\} $ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{prop}
+\begin{proposition}
   \label{lem: control of XT}
@@
   \]
-\end{prop}
+\end{proposition}
 
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lem: control pair for P(M>lambda)}
@@
   \]
-\end{lem}
+\end{lemma}
 
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lem: temp}
@@
 Recall that we write $\tilde u = \frac{u}{1+u}$ for each $u\neq -1$.
-\begin{lem}
+\begin{lemma}
   \label{lem: control of mgtrs}
@@
   Note that
+%  \begin{align}
+%    & (1+\gamma) (t-s) (\alpha- \kappa b) + \alpha r
+%      = (t-s)\alpha+(t-s) (\gamma \alpha- (1+\gamma )\kappa b) \\
+%    & \leq t\alpha+(t-s) (\gamma \alpha- (1+\gamma)\kappa b).
+%  \end{align}
   \begin{align}
     & (1+\gamma) (t-s) (\alpha- \kappa b) + \alpha r
-      = (t-s)\alpha+(t-s) (\gamma \alpha- (1+\gamma )\kappa b) \\
+      = (t-s)\alpha+(t-s) (\gamma \alpha- (1+\gamma )\kappa b)+\alpha r \\
     & \leq t\alpha+(t-s) (\gamma \alpha- (1+\gamma)\kappa b).
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lem:P:M:uc}
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lemma25}
   For all $f\in \mathcal{P}\cap C^2(\mathbb R^d)$, $a\in \mathbb R$ and $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
-\end{lem}
+\end{lemma}
 
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lem:M:L:ML}
@@
   Thus the limit $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $  exists $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
-\end{lem}
+\end{lemma}
 
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lem: control of wt}
@@
 In this subsection, we will establish the following CLT.
-\begin{thm}
+\begin{theorem}
   \label{lem:PR:LC}
@@
   where $\zeta^f_0$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto e^{\langle Z_1(\theta f), \varphi\rangle}$.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{prop}
+\begin{proposition}
   \label{thm:Key}
@@
   We will show that for all $f\in \mathcal P \setminus \{0\}$, $\epsilon > 0$ and $t\geq 0$, it holds that
-  \[
-    \mathbb P_\mu \Big[ | \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1(\theta f), \varphi\rangle}; D^c | \mathscr F_t ]| \Big]
+  %\[
+   % \mathbb P_\mu \Big[ | \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1(\theta f), \varphi\rangle}; D^c | \mathscr F_t ]| \Big]
+    %\leq J^f_1(t,\epsilon)+J^f_2(t,\epsilon)+J^f_3(t,\epsilon),
+  %\]
+  \[
+    \mathbb P_\mu \Big[ | \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1(f), \varphi\rangle}; D^c | \mathscr F_t ]| \Big]
     \leq J^f_1(t,\epsilon)+J^f_2(t,\epsilon)+J^f_3(t,\epsilon),
@@
 The following corollary  will be used later in the proof of Theorem \ref{thm:M}.
-\begin{cor}
+\begin{corollary}
   \label{cor:MI}
@@
 \end{align}
-\end{cor}
+\end{corollary}
 \begin{proof}
@@
 In this subsection, we collect some useful analytic facts.
-\begin{lem}
+\begin{lemma}
   \label{lem: estimate of exponential remaining}
@@
   \end{align}
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{lem}
+\begin{lemma}
   \label{lem: extension lemma for branching mechanism}
@@
   \]
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
 Lemma \ref{lem: extension lemma for branching mechanism} also says that the derivative of $z^{1+\beta}$ is $(1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
-\begin{lem}
+\begin{lemma}
   \label{lem: Lip of power function}
@@
 \end{align}
-\end{lem}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{lem}
+\begin{lemma}
   \label{eq: complex FK}
@@
 
-\begin{lem}
+\begin{lemma}
   There exists a constant $C\geq 0$ such that
@@
   \end{align}
-\end{lem}
+\end{lemma}
 
@@
 
-\begin{prop}
+\begin{proposition}
   \label{prop: complex FKPP-equation}
@@
 \end{align}
-\end{prop}
+\end{proposition}
 
@@
 
-\subsection*{Acknowledgment}
-We thank Zenghu Li and Rui Zhang for helpful conversations.
-We also thank the referee for very helpful comments.
-
 \begin{thebibliography}{10}
@@
 \end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% You may add acknowledgments (optional).                       %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\ACKNO{We thank Zenghu Li and Rui Zhang for helpful conversations. We also thank the referee for very helpful comments.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% You have reached the end of your document.                    %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% You may put below funny messages to the Managing Editor:      %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% EOF

### 2019-11-21 EJP1903.tex
change EJP1903.tex
delete some %
temp change EJP1930.tex

Changed some equation signs
temp change EJP1930.tex

Align all setted
temp change EJP1903.tex

commas, 
not finished
temp change EJP1903.tex

Changing some scripting
change EJP1903.tex

@@
 \mathtoolsset{showonlyrefs}
-\usepackage{stackrel}
+%DELETED
+%\usepackage{stackrel}
+%END DELETED
 \usepackage{mathrsfs}
 \usepackage{hyperref}
-%\usepackage{comment}
-%\usepackage{amsthm}
-%\usepackage{amssymb}
-%\usepackage{color}
 
@@
 
-\SHORTTITLE{stable CLT for super-OU processes}
-
-\TITLE{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes \thanks{Y-X Ren's research  is partially supported by NSFC (Grant Nos.
-11671017  and 11731009) and LMEQF.
-Renming Song's research is partially supported by the Simons Foundation (\#429343, Renming Song)}} % \thanks is optional.
-Insert line breaks with \\
+\SHORTTITLE{
+	stable CLT for super-OU processes
+}
+
+\TITLE{
+	Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes 
+\thanks{
+	%Y-X Ren's research  is partially supported by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF. 
+	Yan-Xia Ren's research is partially supported by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF. 
+	%
+	\newline
+	Renming Song's research is partially supported by the Simons Foundation 
+	%(\#429343, Renming Song)
+	(\#429343, Renming Song).
+}} 
+% \thanks is optional. Insert line breaks with \\
 
@@
 
+%\AUTHORS{%
+%	Y.-X. Ren
+%	\footnote{Peking University, Beijing, P. R. China, 100871.
+%		\EMAIL{yxren@math.pku.edu.cn}}
+%	\and 
+%	Renming Song
+%	\footnote{University of Illinois at Urbana-Champaign, Urbana, IL, USA, 61801. 
+%		\EMAIL{rsong@illinois.edu}}
+%	\and
+%	Zhenyao Sun
+%	\footnote{ Wuhan University, Hubei, P. R. China, 430072.
+%		\EMAIL{zhenyao.sun@gmail.com}}
+%	\and
+%	Jianjie Zhao
+%	\footnote{ Peking University, Beijing, P. R. China, 100871.
+%		\EMAIL{zhaojianjie@pku.edu.cn}}
+%}
+
 \AUTHORS{%
-  Y.-X. Ren
-    \footnote{Peking University, Beijing, P. R. China, 100871.
-    \EMAIL{yxren@math.pku.edu.cn}}
+	Yan-Xia Ren
+\footnote{
+	Peking University, Beijing 100871, P. R. China
+	\EMAIL{yxren@math.pku.edu.cn, zhenyao.sun@gmail.com, zhaojianjie@pku.edu.cn}
+}
 \and 
 	Renming Song
-    \footnote{University of Illinois at Urbana-Champaign, Urbana, IL, USA, 61801. 
-    \EMAIL{rsong@illinois.edu}}
+\footnote{
+	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA. 
+	\EMAIL{rsong@illinois.edu}
+}
 \and
 	Zhenyao Sun
-    \footnote{ Wuhan University, Hubei, P. R. China, 430072.
-    \EMAIL{zhenyao.sun@gmail.com}}
+\footnote{
+	Wuhan University, Wuhan, Hubei 430072, P. R. China.
+	\EMAIL{zhenyao.sun@gmail.com}
+}
+\footnote{
+	Technion Israel Instituteof Technology, Haifa 32000, Israel.
+	\EMAIL{zhenyao.sun@gmail.com}
+}
+\footnotemark[2]
 \and
 	Jianjie Zhao
-    \footnote{ Peking University, Beijing, P. R. China, 100871.
-   \EMAIL{zhaojianjie@pku.edu.cn}}
-}%AUTHORS
+\footnotemark[2]
+}
+%AUTHORS
 %% Type \and between all consecutive authors (not only before the last author).
@@
 
-\KEYWORDS{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime} % Separate items with ;
-
-\AMSSUBJ{60J68, 60F05} % Edit. Separate items with ;
+% \KEYWORDS{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime} 
+\KEYWORDS{
+	Superprocesses; 
+	Ornstein-Uhlenbeck processes; 
+	Stable distribution; 
+	Central limit theorem; 
+	% Law of large numbers; 
+	Law of large number;
+	Branching rate regime} 
+% Separate items with ;
+
+%\AMSSUBJ{60J68, 60F05} 
+\AMSSUBJ{
+	60J68; 
+	60F05
+} 
+% Edit. Separate items with ;
 %\AMSSUBJSECONDARY{FIXME:} % Optional, separate items with ;
@@
 
-\ABSTRACT{ In this paper, we study the asymptotic behavior of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$
-  whose underlying spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ where $\sigma, b >0$;
-  and whose branching mechanism $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that,
- when $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
-  Some law of large numbers and $(1+\beta)$-stable central limit theorems are established for
-  $(X_t(f) )_{t\geq 0}$, where the function $f$ is
-  assumed to be of polynomial growth.
-A phase transition arises  for the central limit theorems in the sense 
-that the forms of the central limit theorem are different in three different regimes corresponding the branching rate 
-being relatively small, large or critical at a balanced value.}
+\ABSTRACT{ 
+	In this paper, we study the asymptotic behavior of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$ whose underlying spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ where $\sigma, b >0$;
+	and whose branching mechanism $\psi$ satisfies Grey's condition and 
+	%some perturbation condition 
+	a perturbation condition 
+	which guarantees that, when $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
+	Some law of large numbers and $(1+\beta)$-stable central limit theorems are established for $(X_t(f) )_{t\geq 0}$, where the function $f$ is assumed to be of polynomial growth.
+	A phase transition arises  for the central limit theorems in the sense that the forms of the central limit theorem are different in three different regimes 
+	% corresponding 
+	corresponding to
+	the branching rate being relatively small, large or critical at a balanced value.
+}
 
@@
 
-\newcommand{\ABS}[1]{\left(#1\right)} % example of author macro
-\newcommand{\veps}{\varepsilon} % another example of author macro
+%\newcommand{\ABS}[1]{\left(#1\right)} % example of author macro
+%\newcommand{\veps}{\varepsilon} % another example of author macro
 
@@
 \maketitle
+
 \section{Introduction}
+
 \subsection{Motivation}
@@
 	Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
-\begin{align}
+% \begin{align}
+\[
 	Lf(x)
-  = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x)
-  , \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
-\end{align}
+	= \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x), 
+	\quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
+% \end{align}
+\]
 	where $\sigma > 0$ and $b > 0$ are constants.
 	Let $\psi$ be a function on $\mathbb R_+$ of the form
-\begin{align}
+% \begin{align}
+\begin{equation}
 \label{eq: honogeneou branching mechanism}
 	\psi(z)
-  =- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy)
-  , \quad  z \in \mathbb R_+,
-\end{align}
+	=- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy), 
+	\quad  z \in \mathbb R_+,
+% \end{align}
+\end{equation}
 	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)~\pi(dy)< \infty$.
@@
 	Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$,
- write $\mu(f)= \int f(x)\mu(dx)$
-and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
-We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
-$
-We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
-on  $(\Omega, \mathscr{F})$
-is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
-\begin{align}
+	For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)= \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
+	We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.$
+	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ on  $(\Omega, \mathscr{F})$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+%\begin{align}
+\begin{equation}
 \label{eq: def of V_t}
 	\mathbb{P}_{\mu}[e^{-X_t(f)}]
-  = e^{-\mu(V_tf)}
-  , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
-\end{align}
+	= e^{-\mu(V_tf)}, 
+	\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
+% \end{align}
+\end{equation}
 	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
-\begin{align}
+% \begin{align}
+\[
 	V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) )~ds\Big]
-	= \Pi_x [f(\xi_t)]
-  , \quad x\in \mathbb R^d, t\geq 0.
-\end{align}	
+	= \Pi_x [f(\xi_t)], 
+	\quad x\in \mathbb R^d, t\geq 0.
+% \end{align}
+\]	
 	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
@@
 	In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established.
-The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
+	The strong law of large numbers for superprocesses 
+	%was first 
+	were first 
+	studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
 	For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.
@@
 	The strong law of large numbers for the super-OU process $X$ above can be stated as follows:
-Under some conditions on $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below),
-there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e.
-continuous bounded non-negative function $f$ on $\mathbb R^d$, we have
- $\lim_{t\to\infty} e^{-\alpha t} X_t(f) =H_\infty\langle f, \varphi\rangle $,
-where $H_\infty$ is the limit of the martingale $e^{-\alpha t}X_t(1)$
-and $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
+	Under some conditions on $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e.
+continuous bounded non-negative function $f$ on $\mathbb R^d$, we have $\lim_{t\to\infty} e^{-\alpha t} X_t(f) =H_\infty\langle f, \varphi\rangle $, where $H_\infty$ is the limit of the martingale $e^{-\alpha t}X_t(1)$ and $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
 	See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
@@
 	In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
-Our key assumption is that $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that,
-when  $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
-Our  goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that
-$ (X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
+	Our key assumption is that $\psi$ satisfies Grey's condition 
+	and some perturbation condition 
+	% and a perturbation condition 
+	which guarantees that, when  $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
+	Our  goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that $(X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
 	Note that, in the setting of this paper, $X_t(f)$ typically has infinite second moment.
 
-There are many papers on CLTs for branching processes, branching diffusions and superprocesses under the second moment condition.
-See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes),
-\cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some}
-for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some
+	There are many papers on CLTs for branching processes, branching diffusions 
+	%and superprocesses under the second moment condition.
+	and superprocesses, under the second moment condition.
+	See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
+	Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved 
+	%in \cite{AdamczakMilos2015CLT} and some 
+	in \cite{AdamczakMilos2015CLT}, and some 
 	spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
@@
 	Heyde \cite{Heyde1971Some} established some  CLTs for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit laws are stable laws.
-Similar results  for supercritical multi-type GW processes and supercritical continuous time branching processes,
-under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
+	Similar results  for supercritical multi-type GW processes and supercritical continuous time branching processes, under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
 	Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable offspring distribution.
 	They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any CLT type result in the large branching rate regime.
-We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior
-of a class of critical superprocesses with spatially dependent stable branching mechanism.
+	We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of 
+	%branching random walks and \cite{RenSongSun2018Limit} considered 
+	branching random walks, and \cite{RenSongSun2018Limit} considered 
+	the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching mechanism.
 
@@
 	We will always assume that the following assumption holds.
+
 \begin{assumption}
@@
 \end{assumption}
+
 	For $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \mu(1)$.
@@
 	In this paper, we will also assume the following:
+
 \begin{assumption}
@@
 	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
-  \begin{align}
+%  \begin{align}
+\begin{equation}
 \label{eq: asp of branching mechanism}
     \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
-  \end{align}
+%  \end{align}
+\end{equation}  
 	for some $\delta > 0$.
 \end{assumption}
+
 	We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
-%In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
    	In the remainder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
@@
 \begin{remark}
-It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism},
- $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y~\pi(dy) < \infty. $
+	It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y~\pi(dy) < \infty.
+$
 	This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
 \end{remark}
+
 	Let us introduce some notation in order to give the precise formulation of our main result.
@@
 \(
-  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)
+  	\mathbb{P}_{\mu}[X_t (f)]  
+  	= \mu( P^\alpha_t f)
 \)
@@
 	It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{invariantdensity}
@@
 	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx
-\end{align}
+%\end{align}
+\end{equation}
 	which is a   symmetric multivariate Gaussian distribution.
 	Let $L^2(\varphi)$ be the Hilbert space with inner product
-\begin{align}
+% \begin{align}
+\[ 
   	\langle f_1, f_2 \rangle_{\varphi}
   	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
-\end{align}
+%\end{align}
+\]
 	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
@@
 	The \emph{Hermite polynomials} are defined by
-\begin{align}
+%\begin{align}
+\[
 	H_p(x)
-  :=(-1)^{|p|}\exp(|x|^2) \partial_p \exp(-|x|^2)
-  , \quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
-\end{align}
+	:=(-1)^{|p|}\exp(|x|^2) \partial_p \exp(-|x|^2), 
+	\quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
+%\end{align}
+\]
 	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
 	For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eigenfunction}
 	\phi_p(x)
-  := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big)
-  , \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
-\end{align}
+  	:= \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big), 
+  	\quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
+%\end{align}
+\end{equation}
 	In other words,
@@
 	Thus for each $f\in L^2(\varphi)$, we have
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{semicomp1}
   	f
-  = \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
-  , \quad \text{in~} L^2(\varphi).
-\end{align}
-For each function $f\in L^2(\varphi)$, define the order of $f$ as
+  	= \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p, 
+  	\quad \text{in~} L^2(\varphi).
+% \end{align}
+\end{equation}
+	For each function $f\in L^2(\varphi)$, define \emph{the order of $f$} as
 \[
@@
 \]
-%which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
 	which is the lowest non-zero frequency in the eigen-expansion \eqref{semicomp1}.
-%Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
-Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-constant, then $\kappa_f<\infty$.
+	Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is 
+	%non-constant, then $\kappa_f<\infty$.
+	non-zero, then $\kappa_f<\infty$.
 	In particular, the order of any constant non-zero function is zero.
@@
 	Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
-\begin{align}
+% \begin{align}
+\begin{equation}
 \label{eq: polynomial growth function}
@@
   	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
-\end{align}
+% \end{align}
+\end{equation}
 	It is clear that $\mathcal{P} \subset L^2(\varphi)$.
@@
 \end{theorem}
-If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
-Hence, Theorem \ref{thm: law of large number} says that for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
-\(
-  e^{-\alpha t}X_t(f)
-  \rightarrow \langle f, \varphi\rangle H_{\infty}
-\)
-in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
+	If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is 
+	%non-trivial and  bounded, then $\kappa_f=0$.
+	non-zero and  bounded, then $\kappa_f=0$.
+	Hence, Theorem \ref{thm: law of large number} says that for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$, $e^{-\alpha t}X_t(f) \rightarrow \langle f, \varphi\rangle H_{\infty}$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 	Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have a.s.\ convergence.
-However, to get a.s.\ convergence for bounded non-negative
-Lebesgue-a.e.\ continuous functions $f$, we do not need $f$ to be twice differentiable.
+	However, to get a.s.\ convergence for bounded non-negative Lebesgue-a.e.\ continuous functions $f$, we do not need $f$ to be twice differentiable.
 	See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
@@
 	Write $\tilde u = \frac{u}{ 1+ u}$ for each $u \neq -1$.
-It turns out that there is a phase transition in the sense that the results are different in the following three cases:
+	It turns out that there is a phase transition in the sense that the results are different in the following three 
+	%cases:
+	regimes:
 \begin{enumerate}
 \item
-  the small branching rate case where
-$f$ satisfies $\alpha \tilde \beta < \kappa_f b$;
+	%the small branching rate case 
+	the small branching rate regime 
+	where $f$ satisfies $\alpha \tilde \beta < \kappa_f b$;
 \item
-  the critical branching rate case where
-$f$ satisfies $\alpha \tilde \beta = \kappa_f b$; and
+  	%the critical branching rate case 
+  	the critical branching rate regime 
+  	where $f$ satisfies $\alpha \tilde \beta = \kappa_f b$; and
 \item
-  the large branching rate case  where
-$f$ satisfies $\alpha \tilde \beta > \kappa_f b$.
+	%the large branching rate case 
+	the large branching rate regime 
+	where $f$ satisfies $\alpha \tilde \beta > \kappa_f b$.
 \end{enumerate}
-Here, the small (resp. large) branching rate case means that the branching rate $\alpha$ is small (resp. large) compared to $\kappa_f$;
- and the critical branching rate means that the branching rate $\alpha$ is at a critical balanced value compared to $\kappa_f$.
+	Here, %the small (resp. large) branching rate case 
+	the small (resp. large) branching rate
+	means that the branching rate $\alpha$ is small (resp.
+large) compared to $\kappa_f$; and the critical branching rate means that the branching rate $\alpha$ is at a critical balanced value compared to $\kappa_f$.
 	To present our result, we define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
-\begin{align}
+% \begin{align}
+\begin{equation}
 \label{eq:I:R:1}
 	T_t f
-  := \sum_{p \in \mathbb Z_+^d} e^{-| |p|b - \alpha \tilde \beta |t} \langle f, \phi_p \rangle_{\varphi} \phi_p
+  	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p
 	,\quad t\geq 0, f\in \mathcal P,
-\end{align}
+% \end{align}
+\end{equation}
 	and a family of $\mathbb C$-valued functionals $(m_t)_{0 \leq t < \infty}$ on $\mathcal P$ by
-\begin{align}
+% \begin{align}
+\begin{equation}
 \label{eq:I:R:2}
   	m_t[f]
-  := \eta \int_0^t ~du \int_{\mathbb R^d} (-iT_u f(x))^{1+\beta} \varphi(x) ~dx
-  , \quad 0 \leq t< \infty, f\in \mathcal P.
-\end{align}
-Define $ \mathcal C_s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
-and $ \mathcal C_l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$. 
-Note that $\mathcal C_s$ is an infinite dimensional space, $ \mathcal C_l$ and $\mathcal C_c$
-are finite dimensional spaces, and $\mathcal C_c$ might be empty.
+  	:= \eta \int_0^t ~du \int_{\mathbb R^d} (-iT_u f(x))^{1+\beta} \varphi(x) ~dx, 
+  	\quad 0 \leq t< \infty, f\in \mathcal P.
+% \end{align}
+\end{equation}
+	Define $ \mathcal C_s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \}$ and $ \mathcal C_l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
+	Note that $\mathcal C_s$ is an infinite dimensional space, $ \mathcal C_l$ and $\mathcal C_c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
 	For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
-\begin{align}
+% \begin{align}
+\begin{equation}
 \label{eq:I:R:3}
 	m[f]
-  := \begin{cases}
+	:= 
+\begin{cases}
     \lim_{t\to \infty} m_t[f], &
@@
 \end{cases}
-\end{align}
+%\end{align}
+\end{equation}
 	is well defined, and moreover, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}$.
@@
 \begin{enumerate}
-\item
-  \label{thm:M:1}
+\item \label{thm:M:1}
   	if $f\in \mathcal C_s\setminus\{0\}$, then $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$;
-\item
-  \label{thm:M:2}
+\item \label{thm:M:2}
   	if $f\in \mathcal C_c\setminus\{0\}$, then $ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$;
-\item
-  \label{thm:M:3}
+\item \label{thm:M:3}
   	if $f\in \mathcal C_l\setminus\{0\}$, then
@@
 	Theorem \ref{thm:M}.(1) can be rephrased as if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$.
-Combining the first two parts of Theorem \ref{thm:M}, one can easily get that  if $f\in \mathcal P$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$,
-$ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
+	Combining the first two parts of Theorem \ref{thm:M}, one can easily get that  if $f\in \mathcal P$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
 	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$. 
-For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ maybe non-trivial.
+	For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ 
+	%maybe non-trivial.
+	maybe non-zero.
 	In this case, we do not have a CLT yet.
-We conjecture that the limit random variables in Theorem \ref{thm:M} for $ f\in \mathcal C_s$, $f\in \mathcal C_c$ and $ f\in \mathcal C_l$ are independent. If this is valid, we can
-get a CLT for $ X_t(f)$ for all $f\in  \mathcal P$.
+	We conjecture that the limit random variables in Theorem \ref{thm:M} for $ f\in \mathcal C_s$, $f\in \mathcal C_c$ and $ f\in \mathcal C_l$ are independent.
+If this is valid, we can get a CLT for $ X_t(f)$ for all $f\in  \mathcal P$.
 	This independence is valid  under the second moment condition, see \cite{RenSongZhang2015Central}.
@@
 	The phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing.
-The coarsening effect corresponds to the increase of the spatial inequality and is a consequence of the branching: simply an area with more particles will produce more offspring.
+%	The coarsening effect corresponds to the increase of the spatial inequality
+	The coarsening effect corresponds to the increase of the spatial inequality, and is a consequence of the branching: simply an area with more particles will produce more offspring.
 	The smoothing effect corresponds to the decrease of the spatial inequality and is a consequence of the mixing property of the OU processes: each OU ``particle'' will ``forget'' its initial position exponentially fast.
 
-Let us consider $X_t(\phi_p)$ as an example and discuss how the parameters $\alpha, \beta, b$ and $|p|$
-influence those two effects:
+	Let us consider $X_t(\phi_p)$ as an example and discuss how the parameters $\alpha, \beta, b$ and $|p|$ influence those two effects:
 \begin{itemize}
@@
   	The tail index $\beta$ describes the heaviness of the tail of the offspring distribution which belongs to the domain of attraction of some $(1+\beta)$-stable random variable.
-When $\beta$ is smaller i.e. the tail is heavier, then it is more likely that 
-one particle can suddenly have a large amount of offspring.
+	When $\beta$ is smaller i.e. the tail is heavier, then it is more likely that one particle can suddenly have a large amount of offspring.
 	In other words, the larger the tail index $\beta$, the smaller the fluctuation of offspring number, and then the stronger the coarsening effect.
@@
 \item
-  %The coefficient $\rho$ dose not influence the result since $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$
-  The coefficient $\rho$ does not influence the result since $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$
-  (see Remark \ref{rem:SP}).
+  	The coefficient $\rho$ does not influence the result since $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$ (see Remark \ref{rem:SP}).
 \item
@@
 	Let us give some intuitive explanation of the methodology used in this paper.
-For any $\mu\in \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
-$
-  \mathcal I_s^t Y
-  := \mathcal I_s^t [Y, \mu]
-  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s]
-$
-  where $0 \leq s \leq t <\infty.$
+	For any $\mu\in \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define $\mathcal I_s^t Y:= \mathcal I_s^t [Y, \mu] := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s]$ where $0 \leq s \leq t <\infty.$
 	We will use the shorter notation $\mathcal I_s^t Y$ when there is no danger of confusion.
 	For $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
-\begin{align}
+%\begin{align}
+\[
 	X_t(f)
@@
 	\quad t\geq 0.
-\end{align}
+%\end{align}
+\]
 	To find the fluctuation of $X_t(f)$, we will investigate the fluctuation of each term on the right hand side above.
-The second term and third term are negligible after the rescaling, and for the first term we will establish
-a multi-variate unit interval CLT,  which says that
+%	The second term and third term are negligible after the rescaling, and for the first term
+	The second term and third term are negligible after the rescaling, and for the first term, we will establish a multi-variate unit interval CLT,  which says that
 \[
@@
 \]
-where $(\zeta^f_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables.
-If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \zeta^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have
-\(
-  \|X_t\|^{-\frac{1}{1+\beta}}  X_t(f)
-  \xrightarrow[t\to \infty]{d} \zeta^f.
-  \)
-If $f \in \mathcal C_c \setminus \{0\}$, then it can be argued that
-\(
-t^{-\frac{1}{1+\beta}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{ d} \zeta^f
-\)
-and then intuitively we have
-\(
-\|tX_t\|^{-\frac{1}{1+\beta}}  X_t(f)
-\xrightarrow[t\to \infty]{d} \zeta^f.
-\)
+	where $(\zeta^f_k)_{k \in \mathbb N}$ 
+	%are independent 
+	are some independent 
+	$(1+\beta)$-stable random variables.
+	If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \zeta^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have $\|X_t\|^{-\frac{1}{1+\beta}}  X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f.$
+	If $f \in \mathcal C_c \setminus \{0\}$, then it can be argued that $ t^{-\frac{1}{1+\beta}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{ d} \zeta^f$ and then intuitively we have $\|tX_t\|^{-\frac{1}{1+\beta}}  X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f.$
 	If $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
@@
 	There are still many open questions.
-Ren, Song and Zhang have established some spatial  CLTs in \cite{RenSongZhang2015Central} for a class of superprocesses with general spatial motions under
-the assumption that the branching mechanisms satisfy a second moment condition.
+	Ren, Song and Zhang have established some spatial  CLTs in \cite{RenSongZhang2015Central} for a class of superprocesses with general spatial motions under the assumption that the branching mechanisms satisfy a second moment condition.
 	We hope to prove spatial CLTs for superprocesses with general motions without the second moment assumption on the branching mechanism in a future project.
 
-Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z +\eta z^{1+\beta}$ plus a small perturbation
-$\psi_1(z)$
-which satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
+	Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z +\eta z^{1+\beta}$ plus a small perturbation $\psi_1(z)$ which satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
 	It would be interesting to consider more general branching mechanisms.
 
-The following correspondence between (sub)critical branching mechanisms and Bernstein functions is well known, see, for instance,
-\cite[Theorem VII.4(ii)]{Bertoin} and \cite[Proposition 7]{BRY}. Suppose that $f, g:(0, \infty)\to [0, \infty)$ are related by $f(x)=xg(x)$.
+	The following correspondence between (sub)critical branching mechanisms and Bernstein functions is well known, see, for instance, \cite[Theorem VII.4(ii)]{Bertoin} and \cite[Proposition 7]{BRY}. 
+	Suppose that $f, g:(0, \infty)\to [0, \infty)$ are related by $f(x)=xg(x)$.
 	Then $f$ is a (sub)critical branching mechanism with $\lim_{x\to 0}f(x)=0$ iff $g$ is a Bernstein function with a decreasing L\'evy density.
@@
   	\psi(z)
-  := -\alpha z + \rho z^2+\eta z^{1+\beta}+zh(z)
-  , \qquad z>0,
+  	:= -\alpha z + \rho z^2+\eta z^{1+\beta}+zh(z), 
+  	\qquad z>0,
 \]
@@
   	\psi(z)
-  :=-\alpha z + \rho z^2+\eta z^{1+\beta}-\int^\infty_{c_2} (e^{-yz}-1+yz)\frac{c_1dy}{y^{1+\beta_1}}
-  , \qquad z\in \mathbb R_+,
+  	:=-\alpha z + \rho z^2+\eta z^{1+\beta}-\int^\infty_{c_2} (e^{-yz}-1+yz)\frac{c_1dy}{y^{1+\beta_1}}, 
+  	\qquad z\in \mathbb R_+,
 \]
@@
 	In Subsection \ref{sec: stable distributions} we will give the definitions of the $(1+\beta)$-stable random variables involved in this paper.
-In Subsection \ref{sc:refined} we will give some refined estimate for the OU semigroup.
+	In Subsection \ref{sc:refined} we will give 
+	%some refined estimate for the OU semigroup.
+	some refined estimates for the OU semigroup.
 	In Subsection \ref{sec: Small value probability} we will give some estimates for the small value probability of continuous state branching processes.
@@
 \section{Preliminaries}
+
 \subsection{Branching mechanism}
@@
 	Let $\mathbb C_+:= \{x+iy: x\in \mathbb R_+, y \in \mathbb R\}$ and $\mathbb C^0_+:= \{x+iy: x\in (0,\infty), y \in \mathbb R\}$.
+
 \begin{lemma}
@@
 \end{lemma}
+
 \begin{proof}
@@
     \psi_1(z)
-    = \rho z^2 + \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big)
-    , \quad z\in \mathbb C_+.
+    = \rho z^2 + \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big), 
+    \quad z\in \mathbb C_+.
 \]
@@
 \end{proof}
+
 	The following lemma says that the constants $\eta, \beta$ in Assumption \ref{asp: branching mechanism} are uniquely determined by the L\'evy measure $\pi$.
+
 \begin{lemma}
@@
 \[
-    \int_{(1,\infty)} y^{ 1 + \beta + \delta} \Big| \frac { \eta ~dy} {\Gamma (- 1 - \beta) y^{2 + \beta}} - \frac {\eta' ~dy} {\Gamma (- 1 - \beta) y^{2 + \beta'}} \Big| < \infty.
+    \int_{(1,\infty)} y^{ 1 + \beta + \delta} \Big| \frac { \eta ~dy} {\Gamma (- 1 - \beta) y^{2 + \beta}} - \frac {\eta' ~dy} {\Gamma (- 1 - \beta) y^{2 + \beta'}} \Big| 
+    < \infty.
 \]
@@
     | \eta z^{ 1 + \beta } - \eta' z^{ 1 + \beta' } |
-    \leq c z^{ 1 + \beta + \delta } + c z^2
-    , \quad z \in \mathbb R_+.
-  \]
-  Dividing both sides by $z^{1+\beta}$ we have
-   $
-   | \eta - \eta' z^{ \beta' - \beta } |
-    \leq cz^{\delta}+cz^{1-\beta}
-    ,	z \in \mathbb R_+.
- $
+    \leq c z^{ 1 + \beta + \delta } + c z^2, 
+    \quad z \in \mathbb R_+.
+\]
+	Dividing both sides by $z^{1+\beta}$ we have $| \eta - \eta' z^{ \beta' - \beta }| \leq cz^{\delta}+cz^{1-\beta}, z \in \mathbb R_+.$
 	This implies that $ \eta' z^{\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0. $
@@
 \end{proof}
+
 \begin{lemma}
 \label{lem: LlogL criterion}
-  If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies the $L \log L$ condition, i.e.,
-   $
-    \int_{(1,\infty)} y \log y~\pi(dy)
-    < \infty.
- $
+	If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y \log y~\pi(dy) < \infty.$
 \end{lemma}
+
 \begin{proof}
@@
 \]
-  Combining this with
-  $
-  \int_{ ( 1, \infty ) } \frac { \eta \log y ~dy } { \Gamma ( - 1 - \beta ) y^{ 1 + \beta } }
-    < \infty,
- $
-  we immediately get the desired result.
+  	Combining this with $\int_{ ( 1, \infty ) } \frac { \eta \log y ~dy } { \Gamma ( - 1 - \beta ) y^{ 1 + \beta } }< \infty$, we immediately get the desired result.
 \end{proof}
@@
 
-In this paper, we say $R$ is a \emph{monotone} operator on $\mathcal P^+$ if $R:\mathcal P^+ \to \mathcal P^+$ satisfies that $Rf\leq Rg$ for all $f\leq g$ in $\mathcal P^+$.
+	In this paper, we say $R$ is a \emph{monotone operator on $\mathcal P^+$} if $R:\mathcal P^+ \to \mathcal P^+$ satisfies that $Rf\leq Rg$ for all $f\leq g$ in $\mathcal P^+$.
 	For a function $h: [0,\infty) \to [0,\infty)$, we say $R$ is an \emph{$h$-controller} if $R$ is a monotone operator on $\mathcal P^+$ and that $R(\theta f)\leq h(\theta) Rf$ for all $f\in \mathcal P^+$ and $\theta \in [0,\infty)$.
 	For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and an operator $R$ on $\mathcal P^+$, we say an operator $A$ is \emph{controlled by $R$ from $\mathcal D$ to $\mathcal I$} if $A:\mathcal D \to \mathcal I$ and that $|Af| \leq R|f|$ for all $f\in \mathcal D$;
-we say a family of operators $\mathscr O$ is \emph{uniformly controlled by $R$ from $\mathcal D$ to $\mathcal I$} if
-each operator $A\in \mathscr O$  is controlled by $R$ from $\mathcal D$ to $\mathcal I$.
+	we say a family of operators $\mathscr O$ is \emph{uniformly controlled by $R$ from $\mathcal D$ to $\mathcal I$} if each operator $A\in \mathscr O$  is controlled by $R$ from $\mathcal D$ to $\mathcal I$.
 	For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and a function $h:[0,\infty) \to [0,\infty)$, we say an operator $A$ (resp.
@@
 	For each $i \in \{0,1\}$, let $\mathscr O_i$ be a family of operators which is  uniformly controlled by an $h_i$-controller $R_i$ from $\mathcal D_i \subset \mathcal P^*$ to $ \mathcal I_i \subset \mathcal P^*$.
-  %Then the followings hold:
 	Then the following statements hold:
@@
 	It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq:chareq2}
   	U_tf(x) - \int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
-  = i P^{\alpha}_t f(x)
-  , \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
-\end{align}
-
+  	= i P^{\alpha}_t f(x), 
+  	\quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
+%\end{align}
+\end{equation}
+%
 	For all $t\geq 0$ and $f\in \mathcal P$, we define
@@
 	Then we have that
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: key equality}
@@
   	= Z'_t + Z''_t
-  = Z_t + Z'''_t
-  , \quad t\geq 0.
-\end{align}
+  	= Z_t + Z'''_t, 
+  	\quad t\geq 0.
+%\end{align}
+\end{equation}
 	For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq:Q}
@@
   	:= Q_{\kappa_f}f.
-\end{align}
+%\end{align}
+\end{equation}
 	Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
@@
   Under Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}, the following statements are true:
-  \begin{enumerate}
-  \item
+  %\begin{enumerate}
+  \begin{itemize}
+  %\item
+  \item[(1)]
     $(-U_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
-  \item
+   %\item
+  \item[(2)]
     $(P^\alpha_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable on $\mathcal P^*$.
-  \item
+    %\item
+  \item[(3)]
     $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-  \item
+    %\item
+  \item[(4)]
     $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item
+    %\item
+  \item[(5)]
     $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item
+    %\item
+  \item[(6)]
     For all $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item
+    %\item
+  \item[(7)]
     For all $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \end{enumerate}
+%\end{enumerate}
+\end{itemize}
 \end{lemma}
@@
     \leq \sup_{0\leq u\leq 1}P^{\alpha}_u f
-    \leq \sup_{0\leq u\leq 1} P_u (e^{\alpha u} e^{-\kappa_f u} e^{\kappa_f u} f )
-    \leq c \sup_{0\leq u\leq 1} (e^{\kappa_fu}P_u f) \leq c Qf \in \mathcal P.
+    %\leq \sup_{0\leq u\leq 1} P_u (e^{\alpha u} e^{-\kappa_f u} e^{\kappa_f u} f )
+    \leq \sup_{0\leq u\leq 1} P_u (e^{\alpha u} e^{-\kappa_f b u} e^{\kappa_f b u} f )
+    %\leq c \sup_{0\leq u\leq 1} (e^{\kappa_fu}P_u f) \leq c Qf \in \mathcal P.
+    \leq c \sup_{0\leq u\leq 1} (e^{\kappa_f b u}P_u f) \leq c Qf \in \mathcal P.
 \]
@@
 \[
-    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta}
-    , \quad f\in \mathcal P^+,
+    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta}, 
+    \quad f\in \mathcal P^+,
 \]
@@
 \[
-    f \mapsto P^\alpha_{t-s}\Psi_0(-U_sf)
-    , \quad 0\leq s\leq t\leq 1,
+    f \mapsto P^\alpha_{t-s}\Psi_0(-U_sf), 
+    \quad 0\leq s\leq t\leq 1,
 \]
@@
 \[
-    f \mapsto (-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta},\quad 0\leq t\leq 1,
+    f 
+    \mapsto (-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta},
+    \quad 0\leq t\leq 1,
 \]
@@
     (Z'_t - Z_t)f
-    = \int_0^t P^\alpha_{t-s}\Big( \eta ((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} )\Big)ds
-    , \quad 0\leq t\leq 1, f\in \mathcal P,
+    %= \int_0^t P^\alpha_{t-s}\Big( \eta ((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} )\Big)ds, 
+       = \int_0^t P^\alpha_{t-s}\Big( \eta ((-U_s f)^{1+\beta} - (-iP_s^\alpha f)^{1+\beta} )\Big)ds, 
+    \quad 0\leq t\leq 1, f\in \mathcal P,
 \]
@@
     |\Psi_1(f)|
-    \le C(|f|^2+|f|^{1+\beta+ \delta})
-    , \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+).
+    \le C(|f|^2+|f|^{1+\beta+ \delta}), 
+    \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+).
 \]
@@
 \[
-    f \mapsto C(f^2+f^{1+\beta+\delta})
-    , \quad f\in \mathcal P^+
+    f \mapsto C(f^2+f^{1+\beta+\delta}), 
+    \quad f\in \mathcal P^+
 \]
@@
   	Therefore, for all $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-  Combining  this with  (1)--(2) above,
-  and Lemma \ref{lem: property of controllable operators}, we get that, for all $\delta > 0$ small enough, the operators
+	Combining  this with  (1)--(2) above, and Lemma \ref{lem: property of controllable operators}, we get that, for all $\delta > 0$ small enough, the operators
 \[
@@
   	\emph{Step 1.} We will show that for each $f \in \mathcal P$, there exists $h \in \mathcal P$ such that $ |T_tf| \leq  e^{- \delta t} h$ for each $t\geq 0$, where
-  \begin{align}
+%  \begin{align}
+\begin{equation}
 \label{eq:m:1}
     \delta
-    := \inf \big\{ |\tilde \beta \alpha - |p|b| : p \in \mathbb Z_+^d, \langle f, \phi_p\rangle_\varphi \neq 0 \big\}
+    := \inf \big\{ \big|\tilde \beta \alpha - |p|b\big| : p \in \mathbb Z_+^d, \langle f, \phi_p\rangle_\varphi \neq 0 \big\}
     \geq 0.
-  \end{align}
+%  \end{align}
+\end{equation}
 	From this upper bound, it can be verified that $(T_t)_{t\geq 0}$ and $(m_{t})_{0 \leq t < \infty}$ are well defined.
@@
 	The proof of the above proposition relies on the following lemma:
+
 \begin{lemma}
 \label{lem: charactreisticfunction}
-  Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with
-  $\int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty)$.
+  	Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty)$.
 Then
@@
     \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx)
-    = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(t \xi)k(\xi,dt)
-    , \quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+    = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(t \xi)k(\xi,dt), 
+    \quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
 \]
@@
     \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)
-    = \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}}
-    ,\quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
+    = \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}},
+    \quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
 \]
@@
     \hat \mu(\theta)
-    = \exp \Big \{ \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy) \Big \}
-    , \quad \theta \in \mathbb R.
+    = \exp \Big \{ \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy) \Big \}, 
+    \quad \theta \in \mathbb R.
 \]
@@
 	Note that $m[\theta f]$ can be written as
-  \begin{align}
+% \begin{align}
+\begin{equation}
     \label{eq:PL:S:1}
@@
     \quad \theta \in \mathbb R.
-  \end{align}
+% \end{align}
+\end{equation}
 	Therefore, according to Lemma \ref{lem: charactreisticfunction}, in order to show that $\zeta^f$ is a $(1+\beta)$-stable random variable we only need to show that
@@
 	In this case, according to \eqref{eq:P:S:1}, $m[\theta f]$ has an integral representation:
-  \begin{align}
+%\begin{align}
+\begin{equation}  
 \label{eq:PL:S:2}
@@
     \quad \theta \in \mathbb R.
-  \end{align}
-  Finally, according to Lemma \ref{lem: charactreisticfunction} and the fact that
- $
-    \int_{\mathbb R^d} | f_c(x)|^{1+\beta} \varphi(x)~dx
-    \in (0, \infty),
-  $
-  We have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
+%\end{align}
+\end{equation}
+	Finally, according to Lemma \ref{lem: charactreisticfunction} and the fact that $\int_{\mathbb R^d} | f_c(x)|^{1+\beta} \varphi(x)~dx \in (0, \infty),$ 
+	%We have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
+	we have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
 \end{proof}
@@
 	We write  $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$,  and $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
-  We need to prove that there exists $h \in \mathcal P^+$ such that for each $f\in \mathcal P_g$, $|P_tq_f| \leq e^{-bt} h$.
-
-  \emph{Step 1.} We claim  that we only need to prove the result for all
-  $f \in \widetilde{\mathcal P}_g:= \{T_{n+1} g : n \in \mathbb Z_+\}$.
+	%Deleted
+	%We need to prove that there exists $h \in \mathcal P^+$ such that for each $f\in \mathcal P_g$, $|P_tq_f| \leq e^{-bt} h$.
+	%End Deleted
+
+	\emph{Step 1.} We claim  that we only need to prove the result for all $f \in \widetilde{\mathcal P}_g:= \{T_{n+1} g : n \in \mathbb Z_+\}$.
   	In fact, both $\operatorname{Re} q_g$ and $\operatorname{Im} q_g$ are functions in $\mathcal P$ of order $\geq 1$.
@@
 	In fact, it is known that  (see \cite{MetafunePallaraPriola2002Spectrum} for example)
-  \begin{align}
+%\begin{align}
+\begin{equation}
     \label{eq:P:R:3:-1}
@@
     \quad t\geq 0, x\in \mathbb R^d, f\in \mathcal P.
-  \end{align}
+%\end{align}
+\end{equation}
 	For $f \in C_\infty(\mathbb R^d)\cap \mathcal P$ it can be verified from above that
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq:P:R:3:1}
@@
    \quad t \geq 0, j \in \{1,\dots, d\}.
-  \end{align}
+%\end{align}
+\end{equation}
 	Thanks to Step 2, $T_1 g_0 \in C_\infty(\mathbb R^d)\cap \mathcal P$.
@@
 
-  \emph{Step 5.}
-We show that there exists $h_5 \in \mathcal P^+$ such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
+  	\emph{Step 5.} We show that there exists $h_5 \in \mathcal P^+$ such that for each $f \in \widetilde {\mathcal P}_g$, we have $ |\nabla (Z_1f)| \leq h_5$.
   	In fact, according to Step 4, for all $j \in \{1,\dots, d\}$, $f \in \widetilde{\mathcal P}_g$ and compact $A \subset \mathbb R^d$, we have
@@
 
-  \emph{Step 6.}
-  Let $h_5$ be the function in Step 5.
+	\emph{Step 6.} Let $h_5$ be the function in Step 5. 
 	There are $c_0, n_0> 0$ such that for all $x\in \mathbb R^d$, $h_5(x) \leq c_0(1+|x|)^{n_0}$.
@@
 	where for each $\lambda\geq 0$, $t\mapsto v_t(\lambda)$ is the unique positive solution to the equation
-\begin{align}
+%\begin{align}
+\begin{equation}
 	\label{eq: fkpp equation for CSBP}
@@
 	\quad t\geq 0.
-\end{align}
+%\end{align}
+\end{equation}
 	It can be verified that for each $\mu \in \mathcal M(\mathbb R^d)$ with $x = \| \mu \|$, we have $ \{(\|X_t\|)_{t\geq 0}; \mathbb P_\mu\} \overset{\text{law}}{=} \{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
@@
 	Suppose that Grey's condition is satisfied i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-Also suppose that the $L \log L$ condition is satisfied i.e.,
-$
-  \int_1^\infty y \log y~\pi(dr)
- < \infty.
-$
+	Also suppose that the $L \log L$ condition is satisfied i.e., $ \int_1^\infty y \log y~\pi(dr) < \infty.$
 	We write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
@@
     \mathbf P_x(0<W_t\leq k_t)
-    \leq C(k_t^\delta + e^{-\delta t}), \quad t\geq 0.
+    \leq C(k_t^\delta + e^{-\delta t}), 
+    \quad t\geq 0.
 \]
@@
 \begin{proof}
-  \emph{Step 1.}
-  We recall some known facts about the CSBP $(Y_t)$.
+	\emph{Step 1.} We recall some known facts about the CSBP $(Y_t)$.
   	For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of \eqref{eq: fkpp equation for CSBP}.
   	Letting $\lambda \to \infty$ in \eqref{eq: fkpp equation for CSBP}, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: svp1}
-    \mathbf P_x(Y_t = 0)=e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
-  \end{align}
+    \mathbf P_x(Y_t = 0)
+    =e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
+%\end{align}
+\end{equation}
   	It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ exists and is the largest root of $\psi$ on $[0,\infty)$.
@@
   	Therefore we have (i) $\bar v > 0$; (ii) $\psi(z) < 0$ on $z\in (0,\bar v)$; and (iii) $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
-  It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that (i) if $\lambda \in (0,\bar v)$, then $0<\lambda \leq v_t(\lambda)<\bar v $; (ii) if $\lambda \in (\bar v, \infty)$, then $\bar v < v_t(\lambda)\leq \lambda< \infty$; and (iii) for each $\lambda \in (0,\infty)\setminus \{\bar v\}$ and $t\geq 0$, we always have
-    \(
-      \int_{v_t(\lambda)}^\lambda  \psi(z)^{-1}dz = t.
-    \)
+  	It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that (i) if $\lambda \in (0,\bar v)$, then $0<\lambda \leq v_t(\lambda)<\bar v $; (ii) if $\lambda \in (\bar v, \infty)$, then $\bar v < v_t(\lambda)\leq \lambda< \infty$; and (iii) for each $\lambda \in (0,\infty)\setminus \{\bar v\}$ and $t\geq 0$, we always have $\int_{v_t(\lambda)}^\lambda  \psi(z)^{-1}dz = t.$
   	Taking $\lambda \to \infty$ and using the monotone convergence theorem, we have that
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq:svp2}
-    \int_{\bar v_t}^\infty \frac{dz}{\psi(z)} = t, \quad t\geq 0.
-  \end{align}
+    \int_{\bar v_t}^\infty \frac{dz}{\psi(z)} 
+    = t, 
+    \quad t\geq 0.
+%\end{align}
+\end{equation}
 
@@
     |\bar v_t-\bar v|
-    \leq c_2e^{-\delta_1 t}
-    , \quad t\geq t_0.
+    \leq c_2e^{-\delta_1 t}, 
+    \quad t\geq t_0.
 \]
@@
     \mathbf P_{x}(0< W_t\leq k_t)
-    \leq c_4(k_t^{\delta_3}+e^{-\delta_3 t})
-    , \quad t\geq t_2.
+    \leq c_4(k_t^{\delta_3}+e^{-\delta_3 t}), 
+    \quad t\geq t_2.
 \]
@@
 \label{sec: Moments for super-OU processes}
-In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $X_t(g)$,
-where $\gamma \in (0,\beta)$ and $g\in \mathcal P$.
+	In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $X_t(g)$, where $\gamma \in (0,\beta)$ and $g\in \mathcal P$.
 
@@
 \begin{proof}
-  It is elementary calculus (see the proof of \cite[Theorem 3.3.6]{Durrett2010Probability} for example) that
-for $u>0$ and $x\neq0$,
-  \[\frac{1}{u}\int_{-u}^u (1- e^{i\theta x})~d\theta = 2 - \frac{2\sin ux}{ux} \geq \mathbf 1_{ux>2}.\]
+	It is elementary calculus (see the proof of \cite[Theorem 3.3.6]{Durrett2010Probability} for example) that for $u>0$ and $x\neq0$,
+\[
+	\frac{1}{u}\int_{-u}^u (1- e^{i\theta x})~d\theta 
+	= 2 - \frac{2\sin ux}{ux} \geq \mathbf 1_{ux>2}.
+\]
 	Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: upper bound for usgx}.(4).
@@
     & \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}X_r(R|\theta e^{(t-s)(\alpha- \kappa b)}h|) d\theta \Big] \\
-     & \leq \mathbb P_\mu [X_r(Rh) ]
-\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
-     \\ & =  \mu(P_r^\alpha Rh)
-\Big(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\Big)
+    & \leq \mathbb P_\mu [X_r(Rh) ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
+    \\ & =  \mu(P_r^\alpha Rh) \Big(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\Big)
     \\ & \leq C e^{\alpha r} \Big(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \Big),
@@
 	Recall that we write $\tilde u = \frac{u}{1+u}$ for each $u\neq -1$.
+
 \begin{lemma}
@@
 	Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
-  \begin{align}
-     & \mathbb P_\mu\big[|\mathcal I_r^s X_t(g)|^{1+\gamma}\big]
+	%\begin{align}
+\begin{equation}
+%   & \mathbb P_\mu\big[|\mathcal I_r^s X_t(g)|^{1+\gamma}\big]
+	\mathbb P_\mu\big[|\mathcal I_r^s X_t(g)|^{1+\gamma}\big]
   	\leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
-  \end{align}
+%\end{align}
+\end{equation}
 	Note that
-%  \begin{align}
-%    & (1+\gamma) (t-s) (\alpha- \kappa b) + \alpha r
-%      = (t-s)\alpha+(t-s) (\gamma \alpha- (1+\gamma )\kappa b) \\
-%    & \leq t\alpha+(t-s) (\gamma \alpha- (1+\gamma)\kappa b).
-%  \end{align}
 \begin{align}
@@
 \begin{enumerate}
-  \item
-    \label{item:P:M:uc:1}
+\item\label{item:P:M:uc:1}
     $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha \tilde \gamma > \kappa b$;
-  \item
-    \label{item:P:M:uc:2}
+\item \label{item:P:M:uc:2}
     $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma = \kappa b$;
-  \item
-    \label{item:P:M:uc:3}
+\item \label{item:P:M:uc:3}
     $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma < \kappa b$.
@@
 \label{sec: large rate lln}
-
 	In this subsection, we prove Theorem \ref{thm: law of large number}.
@@
 For $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and  $a\in \mathbb R$, we define
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{defmartingale}
@@
    	:=e^{-(\alpha-ab)t}X_t(f)-\int_0^t e^{-(\alpha-ab)s} X_s((L+ab)f)~ ds.
-\end{align}
+%\end{align}
+\end{equation}
 	Let $(\mathscr{F}_t)_{t\geq 0}$ be the natural filtration of $X$.  The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
@@
 \begin{proof}
-  Put$\bar{f} :=(L+ab)f$.
+  	Put $\bar{f} :=(L+ab)f$.
   	It follows easily from Ito's formula that
-  \begin{align}
+%\begin{align}
+\begin{equation}
     \label{Theorem55}
@@
     = f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d,
-  \end{align}
+%\end{align}
+\end{equation}
 	where $P_t^{ab} := e^{abt}P_t$.
@@
     \leq C e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
-    = C
-    , \quad t\geq 0.
+    = C, 
+    \quad t\geq 0.
 \]
@@
 	Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,  we know that there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$,
-  \begin{align}
+%\begin{align}
+\[
     \|H^p_s-H^p_r\|_{\mathbb P_\mu; 1+\gamma}
     \leq  C_1 e^{-(\alpha\tilde \gamma-|p|b)s}.
-  \end{align}
+%\end{align}
+\]
 	Thus there exists $C_2>0$ such that for all $0\leq s<t$,
@@
 	Then
-  \begin{align}
-    & e^{-(\alpha-\kappa_fb)t}X_t(f)=
+%  \begin{align}
+\[
+    %& e^{-(\alpha-\kappa_fb)t}X_t(f)=
+    e^{-(\alpha-\kappa_fb)t}X_t(f)=
       \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} X_t(\widetilde{f}),
       \quad t\geq 0.
-  \end{align}
+%  \end{align}
+\]
 	According to Lemma \ref{lem:M:L:ML}, we have
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{as convergence}
@@
     \xrightarrow[t\to \infty]{} \sum_{p\in \mathbb{Z}_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
-  \end{align}
+%\end{align}
+\end{equation}
 	$\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma\in(0,\beta)$.
 	Therefore, it suffices to show that
-  \begin{align}
+%  \begin{align}
+\[
     J_t
@@
     \quad t\geq 0,
-  \end{align}
+%\end{align}
+\]
 	converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
@@
 \item
-  if $\gamma \in (0,\gamma_0)$,  then
-    thanks to (1)--(3) above and the fact that \[\|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}
-      \leq \|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C_5, \delta_2 >0$ such that
+	if $\gamma \in (0,\gamma_0)$,  then thanks to (1)--(3) above and the fact that \[\|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma} \leq \|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C_5, \delta_2 >0$ such that
 \[
@@
 
-  \emph{Step 2.}
-  We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$.
+  	\emph{Step 2.} We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$.
   	We will show that $J_t$ converges to $0$ almost surely.
@@
 	According to \eqref{defmartingale},
-  \begin{align}
+%\begin{align}
+\[
     J_t
@@
     \quad t\geq 0.
-  \end{align}
+%\end{align}
+\]
 	So we only need to show that
-  \begin{align}
+%\begin{align}
+\[
     e^{-(a_0-\kappa_f)b t}M_t^{\widetilde{f},a_0}
@@
     \quad \mathbb{P}_{\mu}\text{-a.s.}
-  \end{align}
+%\end{align}
+\]
 	Notice that $\kappa_{(L+a_0 b)\widetilde{f}}\geq \kappa_{\widetilde{f}}\geq \kappa_f+1 > a_0$.
@@
 \[
-    \| e^{-(\alpha-a_0 b)t}X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}
+    %\| e^{-(\alpha-a_0 b)t} X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}
+    \| e^{-(\alpha-a_0 b)t} X_t(\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}
     \leq C_6 e^{-\delta_3 t},
@@
 	Consequently,  we have
-  \begin{align}
+%\begin{align}
+\[
     \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\widetilde{f},a_0}|
@@
     \quad \mathbb P_\mu\text{-a.s.}
-  \end{align}
+%\end{align}
+\]
 	On the other hand, the martingale $M_t^{\widetilde{f},a_0}$ satisfies
-  \begin{align}
+%\begin{align}
+\[
     \|M_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
@@
     \quad t\geq 0.
-  \end{align}
+%\end{align}
+\]
 	This implies that the martingale converges almost surely.
@@
 \label{lem:PR:LC}
-If  $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal{P}\setminus \{0\}$,
-then  under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
-  \begin{align}
+	If  $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal{P}\setminus \{0\}$, then  under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
+%  \begin{align}
+\begin{equation}
     \label{eq:PR:LC:1}
@@
     \xrightarrow[t\to \infty]{d}\zeta^f_0,
-  \end{align}
+%\end{align}
+\end{equation}
 	where $\zeta^f_0$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto e^{\langle Z_1(\theta f), \varphi\rangle}$.
@@
 \label{thm:Key}
-  For all $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P \setminus \{0\}$, there exist $C,\delta>0$ such that
-  for all $t\geq 1$ and $f \in \mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$, we have
+	For all $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P \setminus \{0\}$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$, we have
 \[
     \mathbb P_\mu
-    \Big[  |\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  |\Big]
+    \Big[  \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ] \big |\Big]
     \leq C e^{- \delta t}.
@@
 	We will show that for all $f\in \mathcal P \setminus \{0\}$, $\epsilon > 0$ and $t\geq 0$, it holds that
-  %\[
-   % \mathbb P_\mu \Big[ | \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1(\theta f), \varphi\rangle}; D^c | \mathscr F_t ]| \Big]
-    %\leq J^f_1(t,\epsilon)+J^f_2(t,\epsilon)+J^f_3(t,\epsilon),
-  %\]
-  \[
-    \mathbb P_\mu \Big[ | \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1(f), \varphi\rangle}; D^c | \mathscr F_t ]| \Big]
+\[
+   	\mathbb P_\mu \Big[ \big| \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1(f), \varphi\rangle}; D^c | \mathscr F_t ]\big| \Big]
    	\leq J^f_1(t,\epsilon)+J^f_2(t,\epsilon)+J^f_3(t,\epsilon),
@@
 \label{eq: Def of Ji}
-  &J^f_1(t,\epsilon):= \mathbb{P}_{\mu} [ | X_t(Z'''_1(\theta_t f)) |; A_t(\epsilon) ],
- \quad
+	& J^f_1(t,\epsilon):= \mathbb{P}_{\mu} [ | X_t(Z'''_1(\theta_t f)) |; A_t(\epsilon) ], \quad
 	J^f_2(t,\epsilon):= \mathbb{P}_{\mu}[|X_t( Z_1(\theta_t f))-\langle Z_1f, \varphi\rangle |; A_t(\epsilon)], 
-  \\ & J_3(t,\epsilon):=2\mathbb{P}_{\mu}(A_t (\epsilon)\Delta D^c),
- \quad
+	\\ & J_3(t,\epsilon):=2\mathbb{P}_{\mu}(A_t (\epsilon)\Delta D^c), \quad
 	\theta_t := \|X_t\|^{-(1 - \tilde \beta)}.
@@
 \label{eq: inequality that will used later}
-  & \mathbb{P}_\mu \Big[ |  \mathbb{P}_\mu [ e^{i\Upsilon^f_t} - e^{\langle Z_1f,\varphi \rangle} ; D^c | \mathscr F_{t}]   |\Big]  \\
-  &  \leq \mathbb{P}_\mu   \Big[ |    \mathbb{P}_\mu [ e^{i \Upsilon^f_t }-e^{\langle Z_1f, \varphi\rangle}; A_{t}(\epsilon) | \mathscr F_{t}] |  + 2\mathbb P_\mu ( A_{t}(\epsilon) \Delta D^c | \mathscr F_{t}) \Big] \\
-  & = \mathbb{P}_{\mu}\Big[ |\mathbb{P}_\mu [e^{i\Upsilon^f_t}| \mathscr F_{t}]-e^{\langle Z_1f, \varphi\rangle}| ; A_{t}(\epsilon) \Big] + J_3(t,\epsilon) \\
-  & \leq \mathbb{P}_\mu \Big[ |e^{X_{t}((Z_1+Z'''_1) (\theta_t f))}-e^{\langle Z_1f, \varphi\rangle} | ; A_{t}(\epsilon) \Big]+  J_3(t,\epsilon) \\
-  & \leq \mathbb{P}_\mu \Big[ | X_{t} ( (Z_1+Z'''_1)(\theta_t f)) - \langle Z_1f, \varphi\rangle | ;A_{t}(\epsilon)\Big]+  J_3(t,\epsilon) \\
+	& \mathbb{P}_\mu \Big[ \big|  \mathbb{P}_\mu [ e^{i\Upsilon^f_t} - e^{\langle Z_1f,\varphi \rangle} ; D^c | \mathscr F_{t}]   \big|\Big]  \\
+  	& \leq \mathbb{P}_\mu   \Big[ \big|    \mathbb{P}_\mu [ e^{i \Upsilon^f_t }-e^{\langle Z_1f, \varphi\rangle}; A_{t}(\epsilon) | \mathscr F_{t}] \big|  + 2\mathbb P_\mu ( A_{t}(\epsilon) \Delta D^c | \mathscr F_{t}) \Big] \\
+  	& = \mathbb{P}_{\mu}\Big[ \big| \mathbb{P}_\mu [e^{i\Upsilon^f_t}| \mathscr F_{t}]-e^{\langle Z_1f, \varphi\rangle} \big| ; A_{t}(\epsilon) \Big] + J_3(t,\epsilon) \\
+  	& \leq \mathbb{P}_\mu \Big[ \big|e^{X_{t}((Z_1+Z'''_1) (\theta_t f))}-e^{\langle Z_1f, \varphi\rangle} \big| ; A_{t}(\epsilon) \Big]+  J_3(t,\epsilon) \\
+  	& \leq \mathbb{P}_\mu \Big[ \big| X_{t} ( (Z_1+Z'''_1)(\theta_t f)) - \langle Z_1f, \varphi\rangle \big| ;A_{t}(\epsilon)\Big]+  J_3(t,\epsilon) \\
   	& \leq J^f_1(t,\epsilon) + J^f_2(t,\epsilon)+ J_3(t,\epsilon).
@@
 
-\emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for all $t\geq 1$ and
-$f \in \mathcal P_g$, we have $ J^f_1(t,\epsilon) \leq C_2e^{-\delta_2 t}$.
+	\emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for all $t\geq 1$ and $f \in \mathcal P_g$, we have $ J^f_1(t,\epsilon) \leq C_2e^{-\delta_2 t}$.
 
 	In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-Acording to Step 1 in the proof of Lemma \ref{lem:m}, there exists $h_{2} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{2}$.
+	%Acording to 
+	According to
+	Step 1 in the proof of Lemma \ref{lem:m}, there exists $h_{2} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{2}$.
 	Then, we have for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
-\begin{align}
-  & |Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
+	%\begin{align}
+\begin{equation}
+	% & |Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
+	|Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
     \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t}(\epsilon)}
@@
     \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}Rh_{2}.
-\end{align}
+%\end{align}
+\end{equation}
 	Thus for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
-\begin{align}
+%\begin{align}
+\begin{equation}
 	\label{eq: estimate of J1}
   	J^f_1(t,\epsilon)
-& \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
+% & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
+	\leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
 	\leq \sum_{\rho \in \{\delta_0,1\}} \mu(Q_0 R h_{2}) e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
-\end{align}
+%\end{align}
+\end{equation}
 	where $Q_0$ is defined by \eqref{eq:Q}.
@@
 
-\emph{Step 3.}
-We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for all $t \geq 0$ and $f\in \mathcal P_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.
+	\emph{Step 3.} We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for all $t \geq 0$ and $f\in \mathcal P_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.
 	In fact, for all $t\geq 0$, and $f\in \mathcal P_g$,
-\begin{align}
-  & X_{t}(Z_1(\theta_t f))- \langle Z_1f, \varphi\rangle
+% \begin{align}
+\[
+%  & X_{t}(Z_1(\theta_t f))- \langle Z_1f, \varphi\rangle
+	X_{t}(Z_1(\theta_t f))- \langle Z_1f, \varphi\rangle
    	= \theta_t^{1+\beta} X_t(Z_1 f) - \langle  Z_1 f,\varphi \rangle
    	= \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle),
-\end{align}
+%\end{align}
+\]
 	and therefore,
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: prevJ2}
 	J^f_2(t,\epsilon)
-  & = \mathbb P_\mu\Big[\Big|  \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle) \Big|;A_t(\epsilon)\Big]
+% 	& = \mathbb P_\mu\Big[\Big|  \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle) \Big|;A_t(\epsilon)\Big]
+	= \mathbb P_\mu\Big[\Big|  \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle) \Big|;A_t(\epsilon)\Big]
     \leq e^{-(\alpha-\epsilon)t} \mathbb{P}_{\mu}[|X_t (q_f) |].
-\end{align}
+%\end{align}
+\end{equation}
 	where $ q_f = Z_1 f-\langle  Z_1 f,\varphi\rangle \in \mathcal P^*$.
@@
 	Therefore, for all $t\geq 0, \epsilon > 0$ and $f \in \mathcal P_g$, we have
-\begin{align}
+% \begin{align}
+\begin{equation}
 	\label{eq: right bound for J2}
@@
    	\leq C_{3} e^{-(\alpha\tilde \gamma -\epsilon)t}.
-\end{align}
+%\end{align}
+\end{equation}
 	By taking $\epsilon >0$ small enough, we get the required result in this step.
 
-\emph{Step 4.}
-We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_4>0$ such that for all $t\geq 1$, $J_3(t,\epsilon)\leq C_4e^{-\delta_4 t}.$
+	\emph{Step 4.} We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_4>0$ such that for all $t\geq 1$, $J_3(t,\epsilon)\leq C_4e^{-\delta_4 t}.$
 	In fact, we have  for all $t\geq 0, \epsilon >0$,
@@
 	On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_{4}, \delta_{4}>0$ such that for all $t\geq 0$,
-\begin{align}
+%\begin{align}
+\[
   	\mathbb P_\mu(A_t(\epsilon)^c,D^c)
@@
   	\leq e^{ - \epsilon t}) \leq C_{4} (e^{-\epsilon \delta_{4} t}+e^{-\delta_{4} t}).
-\end{align}
+%\end{align}
+\]
  	Combining these results, we get the desired result in this step.
@@
 \label{cor:MI}
-If  $g\in \mathcal{P}\setminus\{0\}$ and $\mu\in \mathcal M_c(\mathbb R^d)$, then there exist $C,\delta>0$ such that for
-all $l\leq n$ in $\mathbb Z_+$ and  $(f_j)_{j=l}^n\subset \mathcal P_g$,
-\begin{align}
+	If  $g\in \mathcal{P}\setminus\{0\}$ and $\mu\in \mathcal M_c(\mathbb R^d)$, then there exist $C,\delta>0$ such that for all $l\leq n$ in $\mathbb Z_+$ and  $(f_j)_{j=l}^n\subset \mathcal P_g$,
+%\begin{align}
+\begin{equation}
   	\label{32corollary}
   	\Big|\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{k=l}^ne^{i \Upsilon^{f_k}_{k} }-\prod_{k=l}^n e^{\langle Z_1f_k, \varphi\rangle}\Big]\Big|\leq C e^{-\delta l}.
-\end{align}
+%\end{align}
+\end{equation}
 \end{corollary}
@@
 	By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that for all $l\leq n$ in $\mathbb Z_+$,  $k \in \{l,\dots , n\}$, and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
-  \begin{align}
+%  \begin{align}
+\[
 	| a_{k} - a_{k-1}|
-    & \leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c | \mathscr{F}_k]\big|\Big]
+% & \leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c | \mathscr{F}_k]\big|\Big]
+	\leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c | \mathscr{F}_k]\big|\Big]
     \leq C_0 e^{-\delta_0 k}.
-  \end{align}
-  Therefore, there exist $C,\delta >0$ such that for all $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
-  \begin{align}
+%  \end{align}
+\]
+	Therefore, there exist $C,\delta >0$ such that for all $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have%
+%  \begin{align}
+\[
     \text{LHS of \eqref{32corollary}}
-    & = \left|a_n-a_{l-1}\right|
+%  & = \left|a_n-a_{l-1}\right|
+	= \left|a_n-a_{l-1}\right|
    	\leq \sum_{k=l}^n\left|a_{k}-a_{k-1}\right|
@@
     \qedhere
-  \end{align}
+% \end{align}
+\]
 \end{proof}
@@
 	Therefore from Corollary \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
-  \begin{align}
+%\begin{align}
+\[
   	\Big|\mathbb{\widetilde{P}}_{\mu} [e^{i I^f_0(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}\tilde f, \varphi\rangle \Big)\Big|
@@
     \quad t\geq t_0.
-  \end{align}
+%\end{align}
+\]
 	On the other hand, using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of the semigroup $(P_t)_{t\geq 0}$, we have
@@
 	In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we have that for each $t\geq t_0$,
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq:PM:S:1}
@@
     \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\big],
-  \end{align}
+%  \end{align}
+\end{equation}
 	where $ Y_{t,k} := \exp(i \Upsilon_{t-k-1}^{T_{k} \tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1. $
@@
   	In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $; and therefore for all $k\in \mathbb Z_+$ and $t \geq k + 1$,
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq:gammafunction11}
@@
     = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f)}{\|e^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
-  \end{align}
+%\end{align}
+\end{equation}
 Since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \in \mathbb Z_+$ and $t\geq k+1$,
@@
 	Note that, since $\eta' < \eta$, we have almost surely on $\mathcal D_{t,k}$,
-  \begin{align}
+%  \begin{align}
+\[
  	H_t
-    & \geq H_{t-k-1}- e^{-\eta (t-k-1)}
+%	& \geq H_{t-k-1}- e^{-\eta (t-k-1)}
+	\geq H_{t-k-1}- e^{-\eta (t-k-1)}
    	\geq 2e^{-\eta'(t-k-1)}-e^{-\eta(t-k-1)}
    	\geq e^{-\eta'(t-k-1)}.
-  \end{align}
+%  \end{align}
+\]
   	Therefore, for all $k \in \mathbb Z_+$ and $t\geq k+1$, almost surely  on $\mathcal D_{t,k}$,
@@
 	Thus, there exists $C_{2.2}'> 0$ such that for all $k \geq 0, t\geq k+1$, almost surely
-  \begin{align}
+%  \begin{align}
+\[
     K_{t,k}
     \leq C_{2.2}' e^{-(\eta - 3\eta')(t-k-1)}.
-  \end{align}
+%\end{align}
+\]
  	Now, by Lemma \ref{lem: control of mgtrs}, there exists $C''_{2.2}>0$ such that for all $k\geq 0$ and $t\geq k+1$,
@@
 
-  \emph{Step 3.}
-  We show that $I^f_2(t)\xrightarrow[t\to \infty]{d} 0$.
+	\emph{Step 3.} We show that $I^f_2(t)\xrightarrow[t\to \infty]{d} 0$.
   	First fix a $\gamma \in (0,\beta)$ in this step.
@@
   	Now writing $\mathcal{E}_t:=\{\|X_t\|>e^{(\alpha-\epsilon) t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
-  \begin{align}
+  %\begin{align}
+\[
     \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
-    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})\leq C_3e^{-\delta_3 t}
-    , \quad t\geq0.
-  \end{align}
+    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})\leq C_3e^{-\delta_3 t}, 
+    \quad t\geq0.
+%  \end{align}
+\]
   	Therefore,
-  \begin{align}
+%  \begin{align}
+\begin{equation}
 \label{Theorem123}
@@
     \quad t\geq t_0.
-  \end{align}
+%\end{align}
+\end{equation}
 	According to Lemma \ref{lem: control of mgtrs}, there exist $C_3',C_3'',C_3'''>0$ such that for each $t\geq t_0 >1$,
@@
 	In fact, we have
-  \begin{align}
-    & |I^f_3(t)|
+%  \begin{align}
+\begin{equation}
+% & |I^f_3(t)|
+	|I^f_3(t)|
 	\leq \frac{X_0(|P^\alpha_tf|)}{\|X_t\|^{1 - \tilde \beta }}
@@
 	\xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
-  \end{align}
+%\end{align}
+\end{equation}
 
@@
 	Therefore from Proposition \ref{cor:MI} and that $\tilde \beta - 1 = -\frac{1}{1+\beta}$ we get that there exist $C_1,\delta_1 > 0$ such that
-  \begin{align}
+%  \begin{align}
+\[
     \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i I^f_0(t)} ]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}\tilde f, \varphi\rangle \Big)\Big|
@@
     \quad t\geq t_0.
-  \end{align}
+%  \end{align}
+\]
 	Since $f \in \mathcal C_c\setminus \{0\}$, we have $T_k \tilde f = \tilde f$ for each $k \in \mathbb Z_+$.
 	Similar to the argument in \eqref{eq:PM:CLTS:2} we have
-  \begin{align}
+%  \begin{align}
+\begin{equation}
 \label{CLT:C:eq:m}
@@
     = m[f].
-  \end{align}
+%  \end{align}
+\end{equation}
 	Therefore $\mathbb {\widetilde P}_\mu[e^{i I^f_0(t)}] \xrightarrow[t\to \infty]{} e^{m[f]}$.
@@
 
-  \emph{Substep 2.1.}
-  Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$, $\mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} (t-k)}$.
+	\emph{Substep 2.1.} Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$, $\mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} (t-k)}$.
   	We omit the details.
@@
 
-  \emph{Step 3.}
-  We show that $ I^f_2(t)\xrightarrow[t\to \infty]{d} 0$.
+	\emph{Step 3.} We show that $ I^f_2(t)\xrightarrow[t\to \infty]{d} 0$.
   	In fact, writing $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
@@
     \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
-    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_3( t^{-\delta_3}+e^{-\delta_3 t})
-    , \quad t\geq0.
+    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_3( t^{-\delta_3}+e^{-\delta_3 t}), 
+    \quad t\geq0.
 \]
 	Therefore,
-  \begin{align}
+%  \begin{align}
+\begin{equation}
 \label{Theorem123a}
@@
     \quad t\geq t_0.
-  \end{align}
+% \end{align}
+\end{equation}
 	Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ so that $\alpha(\tilde \beta - \tilde \gamma) \leq \frac{1}{2}(1- \tilde \beta)$.
@@
  	Using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of the semigroup $(P_t)_{t\geq 0}$ we have
-  \begin{align}
-    \label{eq:PM:CLTS:2a}
+\begin{align} \label{eq:PM:CLTS:2a}
     & \sum_{k=0}^\infty \langle Z_1 T_{k} (-\tilde f), \varphi \rangle
@@
  	&|Y_{t,k}| \mathbf 1_{\mathcal D_{t,k}}
-      \leq \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)\mathbf 1_{\mathcal D_{t,k}}.
+   	\leq \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)
+   	%\mathbf 1_{\mathcal D_{t,k}}.
+   	\mathbf 1_{\mathcal D_{t,k}}
     \\ &= \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big)e^{\alpha (\tilde \beta - 1)t} K_{t,k}
@@
 \appendix
-\section{ }
+%\section{}
+
+\section{Appedix}
+
 \subsection{Analytic facts}
 	In this subsection, we collect some useful analytic facts.
+
 \begin{lemma}
@@
 	For $z\in \mathbb C_+$,  we have
-  \begin{align}
+%  \begin{align}
+\begin{equation}
 \label{eq: estimate of exponential remaining}
@@
     \leq \frac{|z|^{n+1}}{(n+1)!} \wedge \frac{2|z|^{n}}{n!}, \quad n\in \mathbb Z_+.
-  \end{align}
+%\end{align}
+\end{equation}
 \end{lemma}
+
 \begin{proof}
   	Notice that $|e^{-z}| = e^{- \operatorname{Re} z} \leq 1$.
-  Therefore, $ |e^{-z} - 1| = \Big| \int_0^1 e^{-\theta z} z d\theta\Big| \leq |z|. $
+  	Therefore, $ |e^{-z} - 1| = | \int_0^1 e^{-\theta z} z d\theta | \leq |z|. $
   	Also, notice that $|e^{-z} - 1| \leq |e^{-z}|+1 \leq 2$.
@@
 	Using this recursively, one gets that
-\begin{align}
+%\begin{align}
+\[
   	\label{eq: definition of Gamma function}
@@
   	\quad -n< x< -n+1, n\in \mathbb N.
-\end{align}
+%\end{align}
+\]
 
@@
 	Using the uniqueness of holomorphic extension and Lemma \ref{lem: extension lemma for branching mechanism}, we get that
-\begin{align}
+%\begin{align}
+\[
 	z^{\beta}
@@
   	\quad z\in \mathbb C_+,
-\end{align}
+%\end{align}
+\]
 	and similarly that
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: stable branching on C+}
@@
   	\quad z\in \mathbb C_+.
-\end{align}
+%\end{align}
+\end{equation}
 	Lemma \ref{lem: extension lemma for branching mechanism} also says that the derivative of $z^{1+\beta}$ is $(1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
+
 \begin{lemma}
@@
 	For all $z_0,z_1 \in \mathbb C_+$, we have
-\begin{align}
+%\begin{align}
+\begin{equation}
 	\label{eq: Lip of power function}
@@
 	\leq (1+\beta)(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
-\end{align}
+%\end{align}
+\end{equation}
 \end{lemma}
+
 \begin{proof}
@@
 	Notice that
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: upper bound for beta power of z}
@@
     \quad z \in \mathbb C\setminus (-\infty, 0].
-  \end{align}
+%\end{align}
+\end{equation}
 Define a path $\gamma: [0,1] \to \mathbb C^0_+$ such that
@@
 	We write
-\begin{align}
+%\begin{align}
+\[
  	H^{(h)}_{(s,t)}
@@
  	\quad 0 \leq s \leq t, h \in \mathcal B_b([0,t] \times E,\mathbb C).
-\end{align}
+%\end{align}
+\]
 
@@
 	Then
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: expresion of g}
@@
     := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
-  \end{align}
+%\end{align}
+\end{equation}
 	is the unique locally bounded solution to the equation
@@
 	Notice that
-  \begin{align}
+%\begin{align}
+\[
     \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t)| ~ds \Big]
@@
     < \infty.
-  \end{align}
+%\end{align}
+\]
 	Also notice that
-  \begin{align}
+%  \begin{align}
+\begin{equation}
 \label{eq: crucial for Feynman-Kac}
@@
     \quad s\in (0,t).
-  \end{align}
+% \end{align}
+\end{equation}
 	Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
@@
 	Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the topology of weak convergence.
-For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$,
-we use the  convention:
-$
-  F(x,f)
-  := F(x,f(x)),
-  x\in E.
-$
+	For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$, we use the  convention: $ F(x,f) := F(x,f(x)), x\in E.$
 	A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
@@
   	the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: branching mechanism}
@@
   	-\rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
-\end{align}
+%\end{align}
+\end{equation}
 	where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$;
@@
   	$X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
-  \begin{align}
-    \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
+%\begin{align}
+\[
+    \mathbf P_\mu [e^{-X_t(f)}] 
+    = e^{-\mu(V_tf)},
     \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
-  \end{align}
+%\end{align}
+\]
  	where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded non-negative solution to the equation
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq:FKPP_in_definition}
@@
     \quad t \geq 0, x \in E.
-  \end{align}
+%\end{align}
+\end{equation}
 \end{itemize}
@@
 	Define
-\begin{align}
+%\begin{align}
+\[
   	\psi'(x,z)
@@
   	\quad x\in E, z\in \mathbb C_+.
-\end{align}
+%\end{align}
+\]
 	Then according to Lemma \ref{lem: extension lemma for branching mechanism}, for each $x \in E$, $z \mapsto \psi(x,z)$ is a holomorphic function on $\mathbb C_+^0$ with derivative $z \mapsto \psi'(x,z)$.
@@
 	We define the mean semigroup
-\begin{align}
+%\begin{align}
+\[
   	P_t^{\rho_1} f(x)
@@
   	\quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
-\end{align}
+%\end{align}
+\]
 	It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M(E)$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: mean formula for superprocesses}
@@
 	=\mu(P^{\rho_1}_t f).
-\end{align}
+%\end{align}
+\end{equation}
 
@@
 	Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
-\begin{align}
+%\begin{align}
+\[
 	\mathbb N_x[W_t(f)]
@@
 	\quad f\in L_1(\xi), t > 0,x\in E.
-\end{align}
+%\end{align}
+\]
 	This says that the random variable $\langle X_t, f\rangle$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
@@
 	Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: N and characteristic exponent}
@@
 	\quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
-\end{align}
+%\end{align}
+\end{equation}
 
 \begin{lemma}
-  There exists a constant $C\geq 0$ such that
-  for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
-  \begin{align}
+	There exists a constant $C\geq 0$ such that for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
+%\begin{align}
+\begin{equation}
 	\label{eq: upper bound of psi(v)}
@@
     \leq C P^{\rho_1}_t |f|(x) + C (P^{\rho_1}_t |f| (x))^2.
-  \end{align}
+%\end{align}
+\end{equation}
 \end{lemma}
@@
 \begin{proof}
-  Noticing that
- $
-     e^{\operatorname{Re} U_tf(x)}
-    = |e^{U_tf(x)}|
-    = |\mathbf P_{\delta_x}[e^{i X_t(f)}]|
-    \leq 1,
-$
-  we have
-  \begin{align}
+	Noticing that $ e^{\operatorname{Re} U_tf(x)} = |e^{U_tf(x)}| = |\mathbf P_{\delta_x}[e^{i X_t(f)}]| \leq 1$, we have
+%  \begin{align}
+\begin{equation}
 \label{eq: -v has positive real part}
@@
     \leq 0.
-  \end{align}
+% \end{align}
+\end{equation}
 	Therefore, we can speak of $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
 	According to Lemma \ref{lem: estimate of exponential remaining}, we have that
-  \begin{align}
+% \begin{align}
+\begin{equation}
 \label{eq: upper bound for vf}
@@
     \leq (P^{\rho_1}_t |f|)(x).
-  \end{align}
+% 	\end{align}
+\end{equation}
 Notice that, for any compact $K \subset \mathbb R$,
-  \begin{align}
+%	\begin{align}
+\begin{equation}
 \label{eq: estimate of deriavetive of v(theta)}
@@
     \leq (P^{\rho_1}_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
-  \end{align}
+%  \end{align}
+\end{equation}
 	Therefore, according to \cite[Theorem A.5.2]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent}, $ U_t( \theta f)( x )$ is differentiable in $\theta \in \mathbb R$ with
@@
 	Moreover, from the above, it is clear that
-  \begin{align}
+% \begin{align}
+\begin{equation}
 \label{eq: upper bounded for derivative of v(theta)}
@@
     \leq ( P^{\rho_1}_t |f|)(x).
-  \end{align}
+%\end{align}
+\end{equation}
 	It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_t(\theta f)(x)$ is continuous in $\theta$.
@@
 	Thus,
-  \begin{align}
+%  \begin{align}
+\begin{equation}
 \label{eq: path integration representation of psi(v)}
@@
     = -\int_0^1 \psi' (x,-U_t(\theta f) ) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
-  \end{align}
+%\end{align}
+\end{equation}
 	Notice that
@@
 
-This lemma also says that if $f\in L^2(\xi)$, then
-$
-  \Pi_x\Big[\int_0^t \psi(\xi_s,- U_{t-s}f)ds\Big]
-  \in \mathbb C,
- x\in E, t\geq 0,$
-is well defined.
+	This lemma also says that if $f\in L^2(\xi)$, then $\Pi_x\Big[\int_0^t \psi(\xi_s,- U_{t-s}f)ds\Big] \in \mathbb C, x\in E, t\geq 0,$ is well defined.
 	In fact, using Jensen's inequality and the Markov property, we have
@@
   	If $f\in L_2(\xi)$,  then for all $t\geq 0$ and $x\in E$,
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: complex FKPP-equation}
@@
   	= i \Pi_x [f(\xi_t)].
-\end{align}
-\begin{align}
+%\end{align}
+\end{equation}
+%\begin{align}
+\begin{equation}
 \label{eq: complex FKPP-equation with FK-transform}
@@
   	= iP_t^{\rho_1} f(x).
-\end{align}
+%\end{align}
+\end{equation}
 \end{proposition}
@@
 	Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[ W_T(f)] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
-\begin{align}
+%\begin{align}
+\[
 	d\mathbf P_{\delta_x}^{ X_T(f)}
@@
 	:=  \frac{W_T(f)}{P_T^{\rho_1} f(x)} d\mathbb N_x.
-\end{align}
+%\end{align}
+\]
 	Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{\langle W_T, f\rangle}$ if
@@
 	the spine process $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$, where
-  \begin{align}
+%\begin{align}
+\[
     d\Pi_x^{(f,T)}
     := \frac{f(\xi_T)e^{\int_0^T \rho_1(\xi_s)ds}}{P^{\rho_1}_T f(x)} d \Pi_x;
-  \end{align}
+%\end{align}
+\]
 \item
-  given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure
-$
-  \{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}
-$
-is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
-\begin{align}
+	given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure $\{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
+%\begin{align}
+\begin{equation}
 \label{eq: conditional intensity}
@@
  	:= 2 \rho_2(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-\end{align}
+%\end{align}
+\end{equation}
 \item
 	$\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M(E)$-valued process defined by
-  \begin{align}
+%\begin{align}
+\[
     Y_t
@@
     \quad 0 \leq t\leq T.
-  \end{align}
+%\end{align}
+\]
 \end{itemize}
 	According to the spine decomposition theorem in \cite{RenSongSun2017Spine}, we have that
-\begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: Spine decomposition 1}
@@
 	\overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{W_T(f)} \},
-\end{align}
-\begin{align}
+%\end{align}
+\end{equation}
+%\begin{align}
+\begin{equation}
 \label{eq: Spine decomposition 2}
@@
 	\overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
-\end{align}
+%\end{align}
+\end{equation}
 
@@
    	\leq \int_{[0,t]\times \mathbb W} (| w_{t-s}(f)| \wedge 2 ) \mathbf m(\xi, ds,dw) \\
-    & \leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s} ( W_{t-s}(|f|) )  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[X_{t-s}(|f|)] \pi(\xi_s,dy)
-   + 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
+    & \leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s} ( W_{t-s}(|f|) )  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[X_{t-s}(|f|)] \pi(\xi_s,dy) + 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
     \\ & \leq \int_0^t (P_{t-s}^{\rho_1} |f|)(\xi_s)\Big(2\rho_2(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
@@
 	According to \eqref{eq: Spine decomposition 1}, we have that
-  \begin{align}
+% \begin{align}
+\[
     \frac{\mathbf P_{\delta_x}[X_t(f^{\pm}) e^{i X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm}) ]}
     = \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{ W_t(f^{\pm})}[e^{i X_t(f)}].
-  \end{align}
+% \end{align}
+\]
 	Using \eqref{eq: N to Pi} and the above, we have
@@
 	Therefore, we have
-  \begin{align}
+% \begin{align}
+\[
     \frac{\partial}{\partial \theta} {U_t(\theta f)(x)}
@@
     = \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
-  \end{align}
+%\end{align}
+\]
 	Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
@@
 	Fubini's theorem, \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bound of psi'(v)}, we get
-  \begin{align}
+%\begin{align}
+\[
     U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi (\xi_s,-U_{t-s}f ) ~ds\Big]
     = i \theta \Pi_{r,x} [f(\xi_t)]
-  \end{align}
+%  \end{align}
+\]
 	and
-  \begin{align}
+%\begin{align}
+\[
     U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du} \psi_0 (\xi_s,- U_{t-s}f ) ~ds\Big]
     = i \Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
-  \end{align}
+%\end{align}
+\]
   	Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} are true if $f\in \mathcal B_b(E)$.
@@
   	From what we have proved, we have
-  \begin{align}
+%\begin{align}
+\begin{equation}
 \label{eq: complex FKPP-equation for fn}
@@
     = i \Pi_{x} [f_n(\xi_t)].
-  \end{align}
+%\end{align}
+\end{equation}
 	Note that
@@
      |e^{i W_t(f_n)} - 1| \leq W_t(|f|);
-    \quad \mathbb N_x[W_t(|f|)] = (P_t^{\rho_1} |f|)(x) < \infty,
+    \quad \mathbb N_x[W_t(|f|)] = (P_t^{\rho_1} |f|)(x) 
+    < \infty,
 \]
@@
 \bibitem{AdamczakMilos2015CLT}
-  R. Adamczak and P. Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
+  	R. Adamczak and P. Mi{\l}o\'{s}, 
+  	\emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
   	Electron. J. Probab. \textbf{20} (2015), no. 42, 35 pp.
@@
 \bibitem{Asmussen76Convergence}
-  S. Asmussen, \emph{Convergence rates for branching processes},
+  	S. Asmussen, 
+  	\emph{Convergence rates for branching processes},
   	Ann. Probab.  \textbf{4} (1976), no. 1, 139--146.
@@
 \bibitem{AsmussenHering1983Branching}
-  S. Asmussen and H. Hering, \emph{Branching processes},
+  	S. Asmussen and H. Hering, 
+  	\emph{Branching processes},
   	Progress in Probability and Statistics, 3. Birkh\"{a}user Boston, Inc., Boston, MA, 1983.
@@
 	\emph{Some connections between (sub)critical branching mechanisms and Bernstein functions}.
-arXiv:0412322.
+	%arXiv:0412322.
+	arXiv:0412322v1.
 
@@
   	\emph{C{LT} for supercritical branching processes with heavy-tailed branching law},
-  arXiv:1803.05491.
+  	%arXiv:1803.05491.
+  	 arXiv:1803.05491v2.
 
@@
   	\emph{Limit theorems for a class of critical superprocesses with stable branching},
-  arXiv:1807.02837.
+  	%arXiv:1807.02837.
+  	arxiv:1807.02837v2.
 
@@
 \bibitem{SteinShakarchi2003Complex}
-  E. M. Stein and R. Shakarchi, \emph{Complex analysis},
+  	E. M. Stein and R. Shakarchi, 
+  	\emph{Complex analysis},
   	Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.
@@
 \bibitem{Wang2010An-almost}
-  L. Wang, \emph{An almost sure limit theorem for super-{B}rownian motion},
+  	L. Wang, 
+  	\emph{An almost sure limit theorem for super-{B}rownian motion},
   	J. Theoret. Probab. \textbf{23} (2010), no. 2, 401--416.
@@
 
-\ACKNO{We thank Zenghu Li and Rui Zhang for helpful conversations. We also thank the referee for very helpful comments.}
+\ACKNO{
+	We thank Zenghu Li and Rui Zhang for helpful conversations. 
+	We also thank the referee for very helpful comments.
+}
 

### 2019-11-23 EJP396.tex
add EJP396.tex

--- 2019-11-21 EJP1903.tex
@@
 \mathtoolsset{showonlyrefs}
-%DELETED
-%\usepackage{stackrel}
-%END DELETED
 \usepackage{mathrsfs}
@@
 \thanks{
-	%Y-X Ren's research  is partially supported by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF. 
 	Yan-Xia Ren's research is partially supported by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.
-	%
 \newline
 	Renming Song's research is partially supported by the Simons Foundation
-	%(\#429343, Renming Song)
 	(\#429343, Renming Song).
+\newline
+	Jianjie Zhao is the corresponding author.
 }}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\AUTHORS{%
-%	Y.-X. Ren
-%	\footnote{Peking University, Beijing, P. R. China, 100871.
-%		\EMAIL{yxren@math.pku.edu.cn}}
-%	\and 
-%	Renming Song
-%	\footnote{University of Illinois at Urbana-Champaign, Urbana, IL, USA, 61801. 
-%		\EMAIL{rsong@illinois.edu}}
-%	\and
-%	Zhenyao Sun
-%	\footnote{ Wuhan University, Hubei, P. R. China, 430072.
-%		\EMAIL{zhenyao.sun@gmail.com}}
-%	\and
-%	Jianjie Zhao
-%	\footnote{ Peking University, Beijing, P. R. China, 100871.
-%		\EMAIL{zhaojianjie@pku.edu.cn}}
-%}
 
@@
 \footnote{
-	Peking University, Beijing 100871, P. R. China
-	\EMAIL{yxren@math.pku.edu.cn, zhenyao.sun@gmail.com, zhaojianjie@pku.edu.cn}
+Peking University, Beijing 100871, P. R. China.
+\EMAIL{yxren@math.pku.edu.cn,  zhaojianjie@pku.edu.cn}
 }
@@
 }
-\footnotemark[2]
 \and
@@
 %% Here is a compact example with two authors with same affiliation
-%% \AUTHORS{%
+% \AUTHORS{%
 %%  Michael~First\footnote{Some University. \EMAIL{mf,js@uni.edu}
@@
 
-% \KEYWORDS{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime} 
 \KEYWORDS{
@@
 	Central limit theorem;
-	% Law of large numbers; 
-	Law of large number;
+Law of large numbers;
 	Branching rate regime}
@@
 	and whose branching mechanism $\psi$ satisfies Grey's condition and
-	%some perturbation condition 
 	a perturbation condition
@@
 	A phase transition arises  for the central limit theorems in the sense that the forms of the central limit theorem are different in three different regimes
-	% corresponding 
 	corresponding to
@@
 	Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
-% \begin{align}
 \[
@@
 	\quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
-% \end{align}
 \]
@@
 	Let $\psi$ be a function on $\mathbb R_+$ of the form
-% \begin{align}
 \begin{equation}
@@
 	\quad  z \in \mathbb R_+,
-% \end{align}
 \end{equation}
@@
 	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ on  $(\Omega, \mathscr{F})$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
-%\begin{align}
 \begin{equation}
@@
 	\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
-% \end{align}
 \end{equation}
 	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
-% \begin{align}
 \[
@@
 	\quad x\in \mathbb R^d, t\geq 0.
-% \end{align}
 \]	
@@
 	In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established.
-	The strong law of large numbers for superprocesses 
-	%was first 
-	were first 
+	The strong law of large numbers for superprocesses  was first
 	studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
@@
 	and some perturbation condition
-	% and a perturbation condition 
 	which guarantees that, when  $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
@@
 	There are many papers on CLTs for branching processes, branching diffusions
-	%and superprocesses under the second moment condition.
 	and superprocesses, under the second moment condition.
@@
 	Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved
-	%in \cite{AdamczakMilos2015CLT} and some 
 	in \cite{AdamczakMilos2015CLT}, and some
@@
 	Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
-	The functional version of the CLTs were established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
+    Functional versions of the CLTs were established in \cite{Janson2004Functional}
+	for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
 
@@
 	We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of
-	%branching random walks and \cite{RenSongSun2018Limit} considered 
 	branching random walks, and \cite{RenSongSun2018Limit} considered
@@
 	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
-%  \begin{align}
 \begin{equation}
@@
     \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
-%  \end{align}
 \end{equation}
@@
 	It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
-%\begin{align}
 \begin{equation}
@@
 	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx
-%\end{align}
 \end{equation}
@@
 	Let $L^2(\varphi)$ be the Hilbert space with inner product
-% \begin{align}
 \[
@@
   	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
-%\end{align}
 \]
@@
 	The \emph{Hermite polynomials} are defined by
-%\begin{align}
 \[
@@
 	\quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
-%\end{align}
 \]
@@
 	For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
-%\begin{align}
 \begin{equation}
@@
   	\quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
-%\end{align}
 \end{equation}
@@
 	Thus for each $f\in L^2(\varphi)$, we have
-%\begin{align}
 \begin{equation}
@@
   	\quad \text{in~} L^2(\varphi).
-% \end{align}
 \end{equation}
@@
 	Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is
-	%non-constant, then $\kappa_f<\infty$.
 	non-zero, then $\kappa_f<\infty$.
-	In particular, the order of any constant non-zero function is zero.
+    In particular, the order of any non-zero constant function is zero.
 
@@
 	Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
-% \begin{align}
 \begin{equation}
@@
   	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
-% \end{align}
 \end{equation}
@@
 	If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is
-	%non-trivial and  bounded, then $\kappa_f=0$.
 	non-zero and  bounded, then $\kappa_f=0$.
@@
 	It turns out that there is a phase transition in the sense that the results are different in the following three
-	%cases:
 	regimes:
@@
 \item
-	%the small branching rate case 
 	the small branching rate regime
@@
 \item
-  	%the critical branching rate case 
   	the critical branching rate regime
@@
 \item
-	%the large branching rate case 
 	the large branching rate regime
@@
 \end{enumerate}
-	Here, %the small (resp. large) branching rate case 
-	the small (resp. large) branching rate
-	means that the branching rate $\alpha$ is small (resp.
-large) compared to $\kappa_f$; and the critical branching rate means that the branching rate $\alpha$ is at a critical balanced value compared to $\kappa_f$.
+	Here, small (resp. large) branching rate
+	means that the branching rate $\alpha$ is small (resp. large) compared to $\kappa_f$;
+    and critical branching rate means that the branching rate $\alpha$ is
+	at a critical balanced value compared to $\kappa_f$.
 	To present our result, we define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
-% \begin{align}
 \begin{equation}
@@
 	,\quad t\geq 0, f\in \mathcal P,
-% \end{align}
 \end{equation}
 	and a family of $\mathbb C$-valued functionals $(m_t)_{0 \leq t < \infty}$ on $\mathcal P$ by
-% \begin{align}
 \begin{equation}
@@
   	\quad 0 \leq t< \infty, f\in \mathcal P.
-% \end{align}
 \end{equation}
@@
 	For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
-% \begin{align}
 \begin{equation}
@@
 \end{cases}
-%\end{align}
 \end{equation}
@@
 	For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$
-	%maybe non-trivial.
 	maybe non-zero.
@@
 	This independence is valid  under the second moment condition, see \cite{RenSongZhang2015Central}.
-	We leave the question of independence of the limit stable random variables to a future project.
+	We leave the question of the independence of the limit stable random variables to a future project.
 
@@
 	Similar explanation has been given in the context of branching-OU processes, see \cite{MarksMilos2018CLT}.
-	First we mention that a super-OU process arises as the ``high density'' limit of a sequence of branching-OU processes, see \cite{Li2011Measure-valued} for example.
-A superprocess can be thought of as a cloud of infinitesimal branching ``particles'' moving in space.
+	First we mention that a super-OU process arises as the
+	``high intensity'' limit of a sequence of branching-OU processes,
+	see \cite{Li2011Measure-valued} for example. A superprocess can be thought of as a cloud of infinitesimal branching ``particles'' moving in space.
 	The phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing.
-%	The coarsening effect corresponds to the increase of the spatial inequality
 	The coarsening effect corresponds to the increase of the spatial inequality, and is a consequence of the branching: simply an area with more particles will produce more offspring.
@@
 	For $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
-%\begin{align}
 \[
@@
 	\quad t\geq 0.
-%\end{align}
 \]
 	To find the fluctuation of $X_t(f)$, we will investigate the fluctuation of each term on the right hand side above.
-%	The second term and third term are negligible after the rescaling, and for the first term
-	The second term and third term are negligible after the rescaling, and for the first term, we will establish a multi-variate unit interval CLT,  which says that
+    The second term and third term are negligible after rescaling,
+	and for the first term, we will establish a multi-variate unit interval CLT,  which says that
 \[
@@
 	where $(\zeta^f_k)_{k \in \mathbb N}$
-	%are independent 
 	are some independent
@@
 	In Subsection \ref{sc:refined} we will give
-	%some refined estimate for the OU semigroup.
 	some refined estimates for the OU semigroup.
@@
 	It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
-%\begin{align}
 \begin{equation}
@@
   	\quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
-%\end{align}
-\end{equation}
-%
+\end{equation}
 	For all $t\geq 0$ and $f\in \mathcal P$, we define
@@
 	Then we have that
-%\begin{align}
 \begin{equation}
@@
   	\quad t\geq 0.
-%\end{align}
 \end{equation}
 	For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-%\begin{align}
 \begin{equation}
@@
   	:= Q_{\kappa_f}f.
-%\end{align}
 \end{equation}
@@
   Under Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}, the following statements are true:
-  %\begin{enumerate}
   \begin{itemize}
-  %\item
   \item[(1)]
     $(-U_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
-   %\item
   \item[(2)]
     $(P^\alpha_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable on $\mathcal P^*$.
-    %\item
   \item[(3)]
     $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-    %\item
   \item[(4)]
     $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-    %\item
   \item[(5)]
     $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-    %\item
   \item[(6)]
     For all $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-    %\item
   \item[(7)]
     For all $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-%\end{enumerate}
 \end{itemize}
@@
     \leq \sup_{0\leq u\leq 1}P^{\alpha}_u f
-    %\leq \sup_{0\leq u\leq 1} P_u (e^{\alpha u} e^{-\kappa_f u} e^{\kappa_f u} f )
     \leq \sup_{0\leq u\leq 1} P_u (e^{\alpha u} e^{-\kappa_f b u} e^{\kappa_f b u} f )
-    %\leq c \sup_{0\leq u\leq 1} (e^{\kappa_fu}P_u f) \leq c Qf \in \mathcal P.
     \leq c \sup_{0\leq u\leq 1} (e^{\kappa_f b u}P_u f) \leq c Qf \in \mathcal P.
@@
     (Z'_t - Z_t)f
-    %= \int_0^t P^\alpha_{t-s}\Big( \eta ((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} )\Big)ds, 
        = \int_0^t P^\alpha_{t-s}\Big( \eta ((-U_s f)^{1+\beta} - (-iP_s^\alpha f)^{1+\beta} )\Big)ds,
@@
   	\emph{Step 1.} We will show that for each $f \in \mathcal P$, there exists $h \in \mathcal P$ such that $ |T_tf| \leq  e^{- \delta t} h$ for each $t\geq 0$, where
-%  \begin{align}
 \begin{equation}
@@
     \geq 0.
-%  \end{align}
 \end{equation}
@@
 	Note that $m[\theta f]$ can be written as
-% \begin{align}
 \begin{equation}
@@
     \quad \theta \in \mathbb R.
-% \end{align}
 \end{equation}
@@
 	In this case, according to \eqref{eq:P:S:1}, $m[\theta f]$ has an integral representation:
-%\begin{align}
 \begin{equation}
@@
     \quad \theta \in \mathbb R.
-%\end{align}
 \end{equation}
 	Finally, according to Lemma \ref{lem: charactreisticfunction} and the fact that $\int_{\mathbb R^d} | f_c(x)|^{1+\beta} \varphi(x)~dx \in (0, \infty),$
-	%We have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
 	we have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
@@
 	We write  $g = g_0 + g_1$ with $g_0 \in \mathcal C_s \oplus \mathcal C_c$ and $g_1 \in \mathcal C_l$,  and $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
-	%Deleted
-	%We need to prove that there exists $h \in \mathcal P^+$ such that for each $f\in \mathcal P_g$, $|P_tq_f| \leq e^{-bt} h$.
-	%End Deleted
 
@@
 	In fact, it is known that  (see \cite{MetafunePallaraPriola2002Spectrum} for example)
-%\begin{align}
 \begin{equation}
@@
     \quad t\geq 0, x\in \mathbb R^d, f\in \mathcal P.
-%\end{align}
 \end{equation}
 	For $f \in C_\infty(\mathbb R^d)\cap \mathcal P$ it can be verified from above that
-%\begin{align}
 \begin{equation}
@@
    \quad t \geq 0, j \in \{1,\dots, d\}.
-%\end{align}
 \end{equation}
@@
 	where for each $\lambda\geq 0$, $t\mapsto v_t(\lambda)$ is the unique positive solution to the equation
-%\begin{align}
 \begin{equation}
@@
 	\quad t\geq 0.
-%\end{align}
 \end{equation}
@@
   	Letting $\lambda \to \infty$ in \eqref{eq: fkpp equation for CSBP}, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
-%\begin{align}
 \begin{equation}
@@
     =e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
-%\end{align}
 \end{equation}
@@
   	Taking $\lambda \to \infty$ and using the monotone convergence theorem, we have that
-%\begin{align}
 \begin{equation}
@@
     \quad t\geq 0.
-%\end{align}
 \end{equation}
@@
 	Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
-	%\begin{align}
-\begin{equation}
-%   & \mathbb P_\mu\big[|\mathcal I_r^s X_t(g)|^{1+\gamma}\big]
+\begin{equation}
 	\mathbb P_\mu\big[|\mathcal I_r^s X_t(g)|^{1+\gamma}\big]
   	\leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
-%\end{align}
 \end{equation}
@@
 For $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and  $a\in \mathbb R$, we define
-%\begin{align}
 \begin{equation}
@@
    	:=e^{-(\alpha-ab)t}X_t(f)-\int_0^t e^{-(\alpha-ab)s} X_s((L+ab)f)~ ds.
-%\end{align}
 \end{equation}
@@
   	It follows easily from Ito's formula that
-%\begin{align}
 \begin{equation}
@@
     = f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d,
-%\end{align}
 \end{equation}
@@
 	Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,  we know that there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$,
-%\begin{align}
 \[
@@
     \leq  C_1 e^{-(\alpha\tilde \gamma-|p|b)s}.
-%\end{align}
 \]
@@
 	Then
-%  \begin{align}
-\[
-    %& e^{-(\alpha-\kappa_fb)t}X_t(f)=
+\[
     e^{-(\alpha-\kappa_fb)t}X_t(f)=
@@
       \quad t\geq 0.
-%  \end{align}
 \]
 	According to Lemma \ref{lem:M:L:ML}, we have
-%\begin{align}
 \begin{equation}
@@
     \xrightarrow[t\to \infty]{} \sum_{p\in \mathbb{Z}_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
-%\end{align}
 \end{equation}
@@
 	Therefore, it suffices to show that
-%  \begin{align}
 \[
@@
     \quad t\geq 0,
-%\end{align}
 \]
@@
 	According to \eqref{defmartingale},
-%\begin{align}
 \[
@@
     \quad t\geq 0.
-%\end{align}
 \]
 	So we only need to show that
-%\begin{align}
 \[
@@
     \quad \mathbb{P}_{\mu}\text{-a.s.}
-%\end{align}
 \]
@@
 \[
-    %\| e^{-(\alpha-a_0 b)t} X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}
     \| e^{-(\alpha-a_0 b)t} X_t(\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}
@@
 	Consequently,  we have
-%\begin{align}
 \[
@@
     \quad \mathbb P_\mu\text{-a.s.}
-%\end{align}
 \]
 	On the other hand, the martingale $M_t^{\widetilde{f},a_0}$ satisfies
-%\begin{align}
 \[
@@
     \quad t\geq 0.
-%\end{align}
 \]
@@
 	If  $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal{P}\setminus \{0\}$, then  under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
-%  \begin{align}
 \begin{equation}
@@
     \xrightarrow[t\to \infty]{d}\zeta^f_0,
-%\end{align}
 \end{equation}
@@
 	In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-	%Acording to 
 	According to
@@
 	Then, we have for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
-	%\begin{align}
-\begin{equation}
-	% & |Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
+\begin{equation}
 	|Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
@@
     \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}Rh_{2}.
-%\end{align}
 \end{equation}
 	Thus for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
-%\begin{align}
 \begin{equation}
@@
   	J^f_1(t,\epsilon)
-% & \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
 	\leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
 	\leq \sum_{\rho \in \{\delta_0,1\}} \mu(Q_0 R h_{2}) e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
-%\end{align}
 \end{equation}
@@
 	In fact, for all $t\geq 0$, and $f\in \mathcal P_g$,
-% \begin{align}
-\[
-%  & X_{t}(Z_1(\theta_t f))- \langle Z_1f, \varphi\rangle
+\[
 	X_{t}(Z_1(\theta_t f))- \langle Z_1f, \varphi\rangle
@@
    	= \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle),
-%\end{align}
 \]
 	and therefore,
-%\begin{align}
 \begin{equation}
@@
 	J^f_2(t,\epsilon)
-% 	& = \mathbb P_\mu\Big[\Big|  \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle) \Big|;A_t(\epsilon)\Big]
 	= \mathbb P_\mu\Big[\Big|  \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle) \Big|;A_t(\epsilon)\Big]
-    \leq e^{-(\alpha-\epsilon)t} \mathbb{P}_{\mu}[|X_t (q_f) |].
-%\end{align}
+    \leq e^{-(\alpha-\epsilon)t} \mathbb{P}_{\mu}[|X_t (q_f) |],
 \end{equation}
@@
 	Therefore, for all $t\geq 0, \epsilon > 0$ and $f \in \mathcal P_g$, we have
-% \begin{align}
 \begin{equation}
@@
    	\leq C_{3} e^{-(\alpha\tilde \gamma -\epsilon)t}.
-%\end{align}
 \end{equation}
@@
 \]
-	On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_{4}, \delta_{4}>0$ such that for all $t\geq 0$,
-%\begin{align}
+	On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$,
+there exist  $C_{4}, \delta_{4}>0$ such that for all $t\geq 0$,
 \[
@@
   	\leq e^{ - \epsilon t}) \leq C_{4} (e^{-\epsilon \delta_{4} t}+e^{-\delta_{4} t}).
-%\end{align}
 \]
@@
 	If  $g\in \mathcal{P}\setminus\{0\}$ and $\mu\in \mathcal M_c(\mathbb R^d)$, then there exist $C,\delta>0$ such that for all $l\leq n$ in $\mathbb Z_+$ and  $(f_j)_{j=l}^n\subset \mathcal P_g$,
-%\begin{align}
 \begin{equation}
@@
   	\Big|\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{k=l}^ne^{i \Upsilon^{f_k}_{k} }-\prod_{k=l}^n e^{\langle Z_1f_k, \varphi\rangle}\Big]\Big|\leq C e^{-\delta l}.
-%\end{align}
 \end{equation}
@@
 	By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that for all $l\leq n$ in $\mathbb Z_+$,  $k \in \{l,\dots , n\}$, and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
-%  \begin{align}
 \[
 	| a_{k} - a_{k-1}|
-% & \leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c | \mathscr{F}_k]\big|\Big]
 	\leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c | \mathscr{F}_k]\big|\Big]
     \leq C_0 e^{-\delta_0 k}.
-%  \end{align}
-\]
-	Therefore, there exist $C,\delta >0$ such that for all $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have%
-%  \begin{align}
+\]
+	Therefore, there exist $C,\delta >0$ such that for all $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
 \[
     \text{LHS of \eqref{32corollary}}
-%  & = \left|a_n-a_{l-1}\right|
 	= \left|a_n-a_{l-1}\right|
@@
     \qedhere
-% \end{align}
 \]
@@
 	Therefore from Corollary \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
-%\begin{align}
 \[
@@
     \quad t\geq t_0.
-%\end{align}
 \]
@@
 	In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we have that for each $t\geq t_0$,
-%\begin{align}
 \begin{equation}
@@
     \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\big],
-%  \end{align}
 \end{equation}
@@
   	In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $; and therefore for all $k\in \mathbb Z_+$ and $t \geq k + 1$,
-%\begin{align}
 \begin{equation}
@@
     = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f)}{\|e^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
-%\end{align}
 \end{equation}
@@
 	Note that, since $\eta' < \eta$, we have almost surely on $\mathcal D_{t,k}$,
-%  \begin{align}
 \[
  	H_t
-%	& \geq H_{t-k-1}- e^{-\eta (t-k-1)}
 	\geq H_{t-k-1}- e^{-\eta (t-k-1)}
@@
    	\geq e^{-\eta'(t-k-1)}.
-%  \end{align}
 \]
@@
 	Thus, there exists $C_{2.2}'> 0$ such that for all $k \geq 0, t\geq k+1$, almost surely
-%  \begin{align}
 \[
@@
     \leq C_{2.2}' e^{-(\eta - 3\eta')(t-k-1)}.
-%\end{align}
 \]
@@
   	Now writing $\mathcal{E}_t:=\{\|X_t\|>e^{(\alpha-\epsilon) t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
-  %\begin{align}
 \[
@@
     \quad t\geq0.
-%  \end{align}
 \]
   	Therefore,
-%  \begin{align}
 \begin{equation}
@@
     \quad t\geq t_0.
-%\end{align}
 \end{equation}
@@
 	In fact, we have
-%  \begin{align}
-\begin{equation}
-% & |I^f_3(t)|
+\begin{equation}
 	|I^f_3(t)|
@@
 	\xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
-%\end{align}
 \end{equation}
@@
 	Therefore from Proposition \ref{cor:MI} and that $\tilde \beta - 1 = -\frac{1}{1+\beta}$ we get that there exist $C_1,\delta_1 > 0$ such that
-%  \begin{align}
 \[
@@
     \quad t\geq t_0.
-%  \end{align}
 \]
@@
 	Similar to the argument in \eqref{eq:PM:CLTS:2} we have
-%  \begin{align}
 \begin{equation}
@@
     = m[f].
-%  \end{align}
 \end{equation}
@@
 	Therefore,
-%  \begin{align}
 \begin{equation}
@@
     \quad t\geq t_0.
-% \end{align}
 \end{equation}
@@
    	\leq \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)
-   	%\mathbf 1_{\mathcal D_{t,k}}.
    	\mathbf 1_{\mathcal D_{t,k}}
@@
 \appendix
-%\section{}
 
@@
 	For $z\in \mathbb C_+$,  we have
-%  \begin{align}
 \begin{equation}
@@
     \leq \frac{|z|^{n+1}}{(n+1)!} \wedge \frac{2|z|^{n}}{n!}, \quad n\in \mathbb Z_+.
-%\end{align}
 \end{equation}
@@
 	Using this recursively, one gets that
-%\begin{align}
 \[
@@
   	\quad -n< x< -n+1, n\in \mathbb N.
-%\end{align}
 \]
@@
 	Using the uniqueness of holomorphic extension and Lemma \ref{lem: extension lemma for branching mechanism}, we get that
-%\begin{align}
 \[
@@
   	\quad z\in \mathbb C_+,
-%\end{align}
 \]
 	and similarly that
-%\begin{align}
 \begin{equation}
@@
   	\quad z\in \mathbb C_+.
-%\end{align}
 \end{equation}
@@
 	For all $z_0,z_1 \in \mathbb C_+$, we have
-%\begin{align}
 \begin{equation}
@@
 	\leq (1+\beta)(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
-%\end{align}
 \end{equation}
@@
 	Notice that
-%\begin{align}
 \begin{equation}
@@
     \quad z \in \mathbb C\setminus (-\infty, 0].
-%\end{align}
 \end{equation}
@@
 	We write
-%\begin{align}
 \[
@@
  	\quad 0 \leq s \leq t, h \in \mathcal B_b([0,t] \times E,\mathbb C).
-%\end{align}
 \]
@@
 	Then
-%\begin{align}
 \begin{equation}
@@
     := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
-%\end{align}
 \end{equation}
@@
 	Notice that
-%\begin{align}
 \[
@@
     < \infty.
-%\end{align}
 \]
 	Also notice that
-%  \begin{align}
 \begin{equation}
@@
     \quad s\in (0,t).
-% \end{align}
 \end{equation}
@@
   	the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
-%\begin{align}
 \begin{equation}
@@
   	-\rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
-%\end{align}
 \end{equation}
@@
   	$X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
-%\begin{align}
 \[
@@
     \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
-%\end{align}
 \]
  	where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded non-negative solution to the equation
-%\begin{align}
 \begin{equation}
@@
     \quad t \geq 0, x \in E.
-%\end{align}
 \end{equation}
@@
 	Define
-%\begin{align}
 \[
@@
   	\quad x\in E, z\in \mathbb C_+.
-%\end{align}
 \]
@@
 	We define the mean semigroup
-%\begin{align}
 \[
@@
   	\quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
-%\end{align}
 \]
 	It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M(E)$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
-%\begin{align}
 \begin{equation}
@@
 	=\mu(P^{\rho_1}_t f).
-%\end{align}
 \end{equation}
@@
 	Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
-%\begin{align}
 \[
@@
 	\quad f\in L_1(\xi), t > 0,x\in E.
-%\end{align}
-\]
-	This says that the random variable $\langle X_t, f\rangle$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
+\]
+	This says that the random variable
+    $X_t(f)$ is well defined
+	under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
 	By the branching property of the superprocess, $X_t(f)$ is an infinitely divisible random variable.
@@
 	Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
-%\begin{align}
 \begin{equation}
@@
 	\quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
-%\end{align}
 \end{equation}
@@
 	There exists a constant $C\geq 0$ such that for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
-%\begin{align}
 \begin{equation}
@@
     \leq C P^{\rho_1}_t |f|(x) + C (P^{\rho_1}_t |f| (x))^2.
-%\end{align}
 \end{equation}
@@
 	Noticing that $ e^{\operatorname{Re} U_tf(x)} = |e^{U_tf(x)}| = |\mathbf P_{\delta_x}[e^{i X_t(f)}]| \leq 1$, we have
-%  \begin{align}
 \begin{equation}
@@
     \leq 0.
-% \end{align}
 \end{equation}
@@
 	According to Lemma \ref{lem: estimate of exponential remaining}, we have that
-% \begin{align}
 \begin{equation}
@@
     \leq (P^{\rho_1}_t |f|)(x).
-% 	\end{align}
 \end{equation}
 Notice that, for any compact $K \subset \mathbb R$,
-%	\begin{align}
 \begin{equation}
@@
     \leq (P^{\rho_1}_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
-%  \end{align}
 \end{equation}
@@
 	Moreover, from the above, it is clear that
-% \begin{align}
 \begin{equation}
@@
     \leq ( P^{\rho_1}_t |f|)(x).
-%\end{align}
 \end{equation}
@@
 	Thus,
-%  \begin{align}
 \begin{equation}
@@
     = -\int_0^1 \psi' (x,-U_t(\theta f) ) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
-%\end{align}
 \end{equation}
@@
   	If $f\in L_2(\xi)$,  then for all $t\geq 0$ and $x\in E$,
-%\begin{align}
 \begin{equation}
@@
   	= i \Pi_x [f(\xi_t)].
-%\end{align}
-\end{equation}
-%\begin{align}
+\end{equation}
 \begin{equation}
@@
   	= iP_t^{\rho_1} f(x).
-%\end{align}
 \end{equation}
@@
 	Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[ W_T(f)] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
-%\begin{align}
 \[
@@
 	:=  \frac{W_T(f)}{P_T^{\rho_1} f(x)} d\mathbb N_x.
-%\end{align}
 \]
@@
 	the spine process $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$, where
-%\begin{align}
 \[
@@
     := \frac{f(\xi_T)e^{\int_0^T \rho_1(\xi_s)ds}}{P^{\rho_1}_T f(x)} d \Pi_x;
-%\end{align}
 \]
@@
 	given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure $\{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
-%\begin{align}
 \begin{equation}
@@
  	:= 2 \rho_2(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-%\end{align}
 \end{equation}
@@
 	$\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M(E)$-valued process defined by
-%\begin{align}
 \[
@@
     \quad 0 \leq t\leq T.
-%\end{align}
 \]
@@
 	According to the spine decomposition theorem in \cite{RenSongSun2017Spine}, we have that
-%\begin{align}
 \begin{equation}
@@
 	\overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{W_T(f)} \},
-%\end{align}
-\end{equation}
-%\begin{align}
+\end{equation}
 \begin{equation}
@@
 	\overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
-%\end{align}
 \end{equation}
@@
 	According to \eqref{eq: Spine decomposition 1}, we have that
-% \begin{align}
 \[
@@
     = \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{ W_t(f^{\pm})}[e^{i X_t(f)}].
-% \end{align}
 \]
@@
 	Therefore, we have
-% \begin{align}
 \[
@@
     = \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
-%\end{align}
 \]
@@
 	Fubini's theorem, \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bound of psi'(v)}, we get
-%\begin{align}
 \[
@@
     = i \theta \Pi_{r,x} [f(\xi_t)]
-%  \end{align}
 \]
 	and
-%\begin{align}
 \[
@@
     = i \Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
-%\end{align}
 \]
@@
   	From what we have proved, we have
-%\begin{align}
 \begin{equation}
@@
     = i \Pi_{x} [f_n(\xi_t)].
-%\end{align}
 \end{equation}
@@
 	\emph{Some connections between (sub)critical branching mechanisms and Bernstein functions}.
-	%arXiv:0412322.
 	arXiv:0412322v1.
@@
   	\emph{C{LT} for supercritical branching processes with heavy-tailed branching law},
-  	%arXiv:1803.05491.
   	 arXiv:1803.05491v2.
@@
   	\emph{Limit theorems for a class of critical superprocesses with stable branching},
-  	%arXiv:1807.02837.
   	arxiv:1807.02837v2.

### 2020-05-17 supCLT-ind3a.tex
add supCLT-ind3a.tex

\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\calclayout
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title
[stable CLT for super-OU processes]
{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II}
\author
[Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
{Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address{
  Yan-Xia Ren \\
  LMAM School of Mathematical Sciences \& Center for Statistical Science \\
  Peking University \\
  Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}
\address{
  Renming Song \\
  Department of Mathematics \\
  University of Illinois at Urbana-Champaign \\
  Urbana, IL, USA, 61801}
\email{rsong@illinois.edu}
\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
\address{
  Zhenyao Sun \\
  School of Mathematics and Statistics\\
  Wuhan University \\
  Hubei, P. R. China, 100871}
\email{zhenyao.sun@gmail.com}
\address{
  Jianjie Zhao \\
  School of Mathematical Sciences \\
  Peking University \\
  Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}

\begin{abstract}
This paper is a continuation of our recent paper (Elect. J Probab., \textbf{24} (2019), no. 141)
and is devoted to the  asymptotic behavior of a supercritical super Ornstein-Uhlenbeck process $(X_t)_{t\geq 0}$
 whose branching mechanism $\psi$ satisfies some perturbation condition which guarantees that,
 when $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
In the aforementioned paper, we have proved $(1+\beta)$-stable central limit theorems
for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth.
As a consequence of the main result of this paper, we will have
$(1+\beta)$-stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
\end{abstract}
\subjclass[2010]{60J68, 60F05}
\keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}
\maketitle
\section{Introduction}
\subsection{Motivation}
\label{subsec:M}
Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
\begin{align}
  Lf(x)
  = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x)
  , \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
\end{align}
where $\sigma > 0$ and $b > 0$ are constants.
Let $\psi$ be a function on $\mathbb R_+$ of the form
\begin{align}
  \label{eq: honogeneou branching mechanism}
  \psi(z)
  =- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy)
  , \quad  z \in \mathbb R_+,
\end{align}
where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)~\pi(dy)< \infty$.
$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$,
 write $\mu(f)= \int f(x)\mu(dx)$
and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty. $
We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
on  $(\Omega, \mathscr{F})$
is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{align}
  \label{eq: def of V_t}
  \mathbb{P}_{\mu}[e^{-X_t(f)}]
  = e^{-\mu(V_tf)}
  , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{align}
where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{align}
  V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) )~ds\Big]
	= \Pi_x [f(\xi_t)]
  , \quad x\in \mathbb R^d, t\geq 0.
\end{align}	
The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.

Recently, there have been quite a few papers on laws of large numbers for superdiffusions.
In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established.
The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.

The strong law of large numbers for the super-OU process $X$ above can be stated as follows:
Under some conditions on $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below),
there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e. continuous bounded non-negative function $f$ on $\mathbb R^d$, we have
 $\lim_{t\to\infty} e^{-\alpha t} X_t(f) =H_\infty\langle f, \varphi\rangle $,
where $H_\infty$ is the limit of the martingale $e^{-\alpha t}X_t(1)$
and $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.

In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
Our key assumption is that $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that,
when  $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
Our  goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that
$ (X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
Note that, in the setting of this paper, $X_t(f)$ typically has infinite second moment.

There are many papers on CLTs for branching processes, branching diffusions and superprocesses under the second moment condition.
See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes),
\cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some}
for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some
spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
These two papers made connections between CLTs and branching rate regimes.
Some spatial CLTs  for supercritical super-OU  processes with branching mechanisms satisfying only a second moment condition were established in \cite{RenSongZhang2014Central}.
Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
The functional version of the CLTs were established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.

There are also many limit theorems for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment.
Heyde \cite{Heyde1971Some} established some  CLTs for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit laws are stable laws.
Similar results  for supercritical multi-type GW processes and supercritical continuous time branching processes,
under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
 Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable offspring distribution.
They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any CLT type result in the large branching rate regime.
We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior
of a class of critical superprocesses with spatially dependent stable branching mechanism.

As far as we know, this paper is the first to study spatial CLTs for supercritical superprocesses without the second moment condition.

\subsection{Main results}
\label{sec:I:R}
We will always assume that the following assumption holds.
\begin{asp}
  \label{asp: Greys condition}
  The branching mechanism $\psi$ satisfies Grey's condition, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
\end{asp}
For $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \mu(1)$.
It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
$$D :=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}$$
has positive probability with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.

Denote by $\Gamma$ the gamma function.
For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
In this paper, we will also assume the following:
\begin{asp}
  \label{asp: branching mechanism}
  There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
  \begin{align}
    \label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
  \end{align}
	for some $\delta > 0$.
\end{asp}

Roughly speaking, Assumption \ref{asp: branching mechanism} says that $\psi$ is ``not too far away'' from $\widetilde \psi(z) := - \alpha z + \eta z^{1+\beta}$ near $0$, see \cite[Remark 1.3]{RenSongSunZhao2019Stable}.
It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
In \cite[Lemma 2.3]{RenSongSunZhao2019Stable}, we have shown  that,
under Assumption \ref{asp: branching mechanism},
 $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y~\pi(dy) < \infty. $
%This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.

In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
	Note that $\delta$ is not uniquely determined by $\pi$.
	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statement:
	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for all small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.

Let us introduce some notation in order to give the precise formulation of our main result.
Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel functions on $\mathbb R^d$.
We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
Define
\(
P^{\alpha}_t f(x)
  := e^{\alpha t} P_t f(x)
  = \Pi_x [e^{\alpha t}f(\xi_t)]
\)
for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$ in the sense that
\(
  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)
\)
for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.

The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
\begin{align}
  \label{invariantdensity}
  \varphi(x)dx
  :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx
\end{align}
which is a   symmetric multivariate Gaussian distribution.
Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{align}
  \langle f_1, f_2 \rangle_{\varphi}
  := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{align}
Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
The \emph{Hermite polynomials} are defined by
\begin{align}
  H_p(x)
  :=(-1)^{|p|}\exp(|x|^2) \partial_p \exp(-|x|^2)
  , \quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
\end{align}
It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
\begin{align}
  \label{eigenfunction}
  \phi_p(x)
  := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big)
  , \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{align}
In other words,
\(
  P_t\phi_p(x)
  = e^{-b|p|t}\phi_p(x)
\)
for all $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
Thus for each $f\in L^2(\varphi)$, we have
\begin{align}
  \label{semicomp1}
  f
  = \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
  , \quad \text{in~} L^2(\varphi).
\end{align}
For each function $f\in L^2(\varphi)$, define the order of $f$ as
\[
  \kappa_f
  := \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\]
which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
In particular, the order of any constant non-zero function is zero.

Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
For $p\in \mathbb{Z}_+^d$, define
\[
  H_t^p
  := e^{-(\alpha-|p|b)t}X_t(\phi_p), \qquad t\geq 0.
\]
We will write $H^0_t$ as $H_t$ for simplicity.
For $u \neq -1$, we write $\tilde u = u/(1+ u)$.
We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that, (1) for any
$\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale; (2)
if $\alpha \tilde \beta>|p|b$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
Similar as before, we will write $H^0_\infty$ as $H_\infty$.

Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{align}
  \label{eq: polynomial growth function}
  \mathcal{P}
  := \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
\end{align}
It is clear that $\mathcal{P} \subset L^2(\varphi)$. The following law of large numbers is
\cite[Theorem 1.5]{RenSongSunZhao2019Stable}.
\begin{thm}
  \label{thm: law of large number}
  If $f \in \mathcal{P}$ satisfies $\alpha\tilde \beta>\kappa_f b$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
  \[
    e^{-(\alpha-\kappa_fb)t}X_t(f)
    \xrightarrow[t\to \infty]{}\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p
    \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).
  \]
  Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
\end{thm}
If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
Hence, Theorem \ref{thm: law of large number} says that for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
\(
  e^{-\alpha t}X_t(f)
  \rightarrow \langle f, \varphi\rangle H_{\infty}
\)
in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have a.s.\ convergence.
However, to get a.s.\ convergence for bounded non-negative
Lebesgue-a.e.\ continuous functions $f$, we do not need $f$ to be twice differentiable.
See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.

For the rest of this subsection, we focus on the CLTs of $X_t(f)$ for a large collection of $f\in \mathcal P\setminus \{0\}$.
Now we recall some notation and the CLT from \cite{RenSongSunZhao2019Stable}.
The CLT,  \cite[Theorem 1.6]{RenSongSunZhao2019Stable}, is stated  in the following three cases:
\begin{enumerate}
\item
  the small branching rate case where
$f$ satisfies $\alpha \tilde \beta < \kappa_f b$;
\item
  the critical branching rate case where
$f$ satisfies $\alpha \tilde \beta = \kappa_f b$; and
\item
  the large branching rate case  where
$f$ satisfies $\alpha \tilde \beta > \kappa_f b$.
\end{enumerate}
Here, the small (resp. large) branching rate case means that the branching rate $\alpha$ is small (resp. large) compared to $\kappa_f$;
 and the critical branching rate means that the branching rate $\alpha$ is at a critical balanced value compared to $\kappa_f$.
Define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
\begin{align}
  \label{eq:I:R:1}
  T_t f
  := \sum_{p \in \mathbb Z_+^d} e^{-| |p|b - \alpha \tilde \beta |t} \langle f, \phi_p \rangle_{\varphi} \phi_p
  ,\quad t\geq 0, f\in \mathcal P,
\end{align}
and a family of $\mathbb C$-valued functionals $(m_t)_{0 \leq t < \infty}$ on $\mathcal P$ by
\begin{align}
  \label{eq:I:R:2}
  m_t[f]
  := \eta \int_0^t ~du \int_{\mathbb R^d} (-iT_u f(x))^{1+\beta} \varphi(x) ~dx
  , \quad 0 \leq t< \infty, f\in \mathcal P.
\end{align}
Define $ \mathcal C_s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
and $ \mathcal C_l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
Note that $\mathcal C_s$ is an infinite dimensional space, $ \mathcal C_l$ and $\mathcal C_c$
are finite dimensional spaces, and $\mathcal C_c$ might be empty.
We have shown in \cite[Lemma 2.6 and Propsoition 2.7]{RenSongSunZhao2019Stable} that,
for $f\in \mathcal P\setminus \{0\}$,
\begin{align}
  \label{eq:I:R:3}
  m[f]
  := \begin{cases}
    \lim_{t\to \infty} m_t[f], &
    f \in \mathcal C_s \oplus \mathcal C_l, \\
    \lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_s \oplus \mathcal C_l,
  \end{cases}
\end{align}
is well defined, and moreover, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function
\begin{align}\label{eq: charac func11}
 \theta \mapsto e^{m[\theta f]}, \quad \theta \in \mathbb R.
\end{align}
The following result is \cite[Theorem 1.6]{RenSongSunZhao2019Stable}.

\begin{thm}
\label{thm:RSSZ}
	If $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$, then under $\mathbb{P}_{\mu}(\cdot|D^c)$, the following hold:
\begin{enumerate}
\item \label{thm:M:1}
  	if $f\in \mathcal C_s\setminus\{0\}$, then $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$;
\item \label{thm:M:2}
  	if $f\in \mathcal C_c\setminus\{0\}$, then $ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$;
\item \label{thm:M:3}
  	if $f\in \mathcal C_l\setminus\{0\}$, then
\[
    \|X_t\|^{-\frac{1}{1+\beta}} \Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big)
    \xrightarrow[t\to \infty]{d}
    \zeta^{-f}.
\]
\end{enumerate}
\end{thm}

The theorem above does not cover all $f\in \mathcal P$.
	Theorem \ref{thm:RSSZ}.(1) can be rephrased as if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$.
	Combining the first two parts of Theorem \ref{thm:RSSZ}, one can easily get that  if $f\in \mathcal P$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$.
	For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$
	maybe non-zero. In \cite{RenSongSunZhao2019Stable}, we were not able to
	establish a CLT in this case. We conjectured there that the limit random variables in Theorem \ref{thm:RSSZ} for $ f\in \mathcal C_s$, $f\in \mathcal C_c$ and $ f\in \mathcal C_l$ are independent. Once this asymptotic independence is established, a CLT for $ X_t(f)$ for all $f\in  \mathcal P$ would follow.

	The main purpose of this paper is to prove the asymptotic independence conjectured in
	\cite{RenSongSunZhao2019Stable} and prove a CLT for $ X_t(f)$ for all $f\in  \mathcal P$.

Let
\begin{align}
S(t):=\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_s)}{\|X_t\|^{\frac{1}{1+\beta}}},\frac{X_t(f_c)}{\|tX_t\|^{\frac{1}{1+\beta}}},\frac{ X_t(f_l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{\frac{1}{1+\beta}}}\Bigg).
\end{align}
The main result of this paper is as follows.

\begin{thm}
  \label{thm:M}
 If $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$,$f_s\in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$, then under $\mathbb{P}_{\mu}(\cdot|D^c)$,
% the following hold:
\begin{align}
%&\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_s)}{\|X_t\|^{\frac{1}{1+\beta}}},\frac{X_t(f_c)}{\|tX_t\|^{\frac{1}{1+\beta}}},\frac{ X_t(f_l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{\frac{1}{1+\beta}}}\Bigg)\\
%&
S(t)
\xrightarrow[t\rightarrow \infty]{d}(H^*,\zeta^{f_s},\zeta^{f_c},\zeta^{-f_l}),
\end{align}
where $H^*$ has the same distribution as $H_{\infty}$ conditioned on $D^c$, $\zeta^{f_s}$, $\zeta^{f_c}$ and $\zeta^{-f_l}$ are $(1+\beta)$-stable random varibales with characteristic functions described by \eqref{eq: charac func11}. Moreover, $H^*$,  $\zeta^{f_s}$, $\zeta^{f_c}$ and $\zeta^{-f_l}$ are independent.
\end{thm}

As a corollary of this theorem, we can get the following CLTs for all function $f\in \mathcal P$.

\begin{cor} Suppose $f\in \mathcal P\setminus\{0\}$. Let $F=f_s + f_c + f_l$ be the decomposition of $f$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$.
If $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$, then under $\mathbb{P}_{\mu}(\cdot|D^c)$, the following hold:
\begin{enumerate}
\item if $\alpha \tilde \beta < \kappa_f b$, then
\[
\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f;
\]
\item if $\alpha \tilde \beta = \kappa_f b$, then
\[
\|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^{f_c};
\]
\item  if $\alpha \tilde \beta > \kappa_f b$ and $f_c=0$, then
\[
   \|X_t\|^{-\frac{1}{1+\beta}} \Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big)
    \xrightarrow[t\to \infty]{d}
     \zeta^{f_s}+\zeta^{-f_l};
\]
\item  if $\alpha \tilde \beta > \kappa_f b$ and $f_c\neq0$, then
\[
 \|t X_t\|^{-\frac{1}{1+\beta}}\Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big)
    \xrightarrow[t\to \infty]{d}\zeta^{f_c}.
\]
\end{enumerate}
\end{cor}

There are still many open questions on stable central limit theorems for superprocesses.
Ren, Song and Zhang have established some spatial  CLTs in \cite{RenSongZhang2015Central} for a class of superprocesses with general spatial motions under
the assumption that the branching mechanisms satisfy a second moment condition.
We hope to prove spatial CLTs for superprocesses with general motions without the second moment assumption on the branching mechanism in a future project.

Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z +\eta z^{1+\beta}$ plus a small perturbation
$\psi_1(z)$
which satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
It would be interesting to consider more general branching mechanisms.

The rest of the paper is organized as follows:
In Subsection \ref{sec: main},
we will give the proof of Theorem \ref{thm:M}.

\section{Proofs of main results}
\label{proofs of main results}
In this section, we will prove the main result of this paper.
For simplicity, we will write $\mathbb{\widetilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in this section.

%\subsection{Central limit theorems for unit time intervals}
%\label{sec:critical}
%In this subsection, we will establish the following CLT.
%\begin{thm}
%  \label{lem:PR:LC}
%If  $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal{P}\setminus \{0\}$,
%then  under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
%  \begin{align}
%    \label{eq:PR:LC:1}
%    \Upsilon^f_t
%    := \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}
%    \xrightarrow[t\to \infty]{d}\zeta^f_0,
%  \end{align}
%  where $\zeta^f_0$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto e^{\langle Z_1(\theta f), \varphi\rangle}$.
%\end{thm}
\subsection{Preliminaries}

The following  elementary analysis result will play an important role in this paper.

\begin{lem}\label{ineq: analysis}
There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
\[
    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
\]
\end{lem}
\begin{proof}
   Note that
\[
  \lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
\]
using this and continuity, we get that there exists $C_1>0$ such that for all $|y|>1$,
\[
  |(1+y)^{1+\beta}-y^{1+\beta}-1|\leq C_1 |y|^{\beta}.
\]
Hence, when $|x|>|y|$ and $y\neq 0$, we have
\[
|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq |y|^{1+\beta}\Big(|(1+\frac{x}{y})^{1+\beta}-(\frac{x}{y})^{1+\beta}-1|\Big)\leq C_1|y||x|^{\beta};
\]
and when $|x|<|y|$ and $x\neq 0$, we have
\[
|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq |x|^{1+\beta}\Big(|(1+\frac{y}{x})^{1+\beta}-(\frac{y}{x})^{1+\beta}-1|\Big)\leq C_1|x||y|^{\beta}.
\]
Combining the above, we immediately get the desired conclusion.
\end{proof}

For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$. 	For all $t\geq 0$ and $f\in \mathcal P$, define
	\begin{align}
  	Z_t f
  	&:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,\\
  	\Upsilon^f_t
   & := \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
  	\end{align}
The following corollary to  \cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of Theorem \ref{thm:M}.

\begin{cor}
  \label{cor:MI}
For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for
all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$ and $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$, we have
\begin{align}
  \label{32corollary}
  \Big|\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{k=0}^{n_1}e^{i \Upsilon^{f_k}_{t-k-1}}\prod_{k=0}^{n_2}e^{i \Upsilon^{g_k}_{t+k} }\Big]-\prod_{k=0}^{n_1} e^{\langle Z_1f_k, \varphi\rangle}\prod_{k=0}^{n_2} e^{\langle Z_1g_k, \varphi\rangle}\Big|\leq C e^{-\delta (t-n_1)}.
\end{align}
\end{cor}
\begin{proof}
For $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$, $k_1 \in \{-1,0,\dots,n_1\}$ and $k_2 \in \{-1,0,\dots,n_2\}$,  define
  \[
    a_{k_1,k_2}
    :=  \mathbb{\widetilde{P}}_{\mu}\Big[\prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}}\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big] \times \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big),
  \]
 where by convention the product is 1 for $k_1=-1$ or $k_2 = -1$.
  Then for all  $k_2 \in \{0,\dots,n_2\}$, we have
  \begin{align}
    & a_{-1,k_2} - a_{-1,k_2-1}\\
     & =\mathbb{P}_{\mu}(D^c)^{-1} \mathbb{P}_{\mu}\Big[\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}(e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle});D^c\Big] \Big(\prod_{j=k_2+1}^n e^{\langle Z_1g_j, \varphi\rangle}\Big)\\
    & =\mathbb{P}_{\mu}(D^c)^{-1} \mathbb{P}_{\mu}\Big[\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}] \Big] \Big(\prod_{j=k_2+1}^{n}e^{\langle Z_1g_j, \varphi\rangle}\Big).
  \end{align}
%  By Lemma \ref{thm:Key},
It follows from \cite[Lemma 2.8 and Proposition 3.5]{RenSongSunZhao2019Stable} and the definition of $Z_t$ that
  there exist $C_0,\delta_0 >0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $k_2 \in \{0,\dots,n_2\}$ we have
\begin{align}
    | a_{-1,k_2} - a_{-1,k_2-1}|
    & \leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}]\big|\Big]
    \leq C_0 e^{-\delta_0 (t+k_2)}.
\end{align}
Similarly,  we also get that there exist $C_0',\delta_0' >0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $k_1 \in \{0,\dots,n_1\}$,
\begin{align}
    | a_{k_1-1,-1} - a_{k_1,-1}|
    & \leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{f_{k_1}}_{t-k_1-1}}-e^{\langle Z_1f_{k_1}, \varphi\rangle}; D^c|\mathscr F_{t-k_1-1}]\big|\Big]
    \leq C_0' e^{-\delta_0' (t-k_1)}.
\end{align}
  Therefore, there exist $C,\delta >0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$ and $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$, we have
  \begin{align}
    \text{LHS of \eqref{32corollary}}
 %   & = \left|a_{-1,n_2}-a_{n-1,-1}\right|
    & = \left|a_{-1,n_2}-a_{n_1,-1}\right|
      \leq \sum_{k=0}^{n_1}\left|a_{k-1,-1}-a_{k,-1}\right|+\sum_{k=0}^{n_2}\left|a_{-1,k}-a_{-1,k-1}\right|\\
     & \leq \sum_{k=0}^{n_1} C_0' e^{-\delta_0' (t-k)}+\sum_{k=0}^{n_2} C_0 e^{-\delta_0 (t+k)}
      \leq C e^{- \delta (t-n_1)}.
      \qedhere
  \end{align}
\end{proof}

\subsection{Proof of Theorem \ref{thm:M}}
\label{sec: main}
In this subsection, we always fix $\mu \in \mathcal M_c(\mathbb R^d)$, $f_s\in \mathcal C_s$,  $f_c\in \mathcal C_c$, $f_l\in \mathcal C_l$ and $t_0>1$ large enough, so that $\lceil t-\ln t\rceil \leq \lfloor t \rfloor - 1$ for all $t\geq t_0$.
	For any random variable $Y$ with finite mean, we define $\mathcal I_r^t Y:= \mathcal I_r^t [Y, \mu] := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_r]$ where $0 \leq r \leq t <\infty.$
	We will use the shorter notation $\mathcal I_r^t Y$ when there is no danger of confusion.
For each $t\geq t_0$, we have the following decomposition.
  \begin{multline}
    \label{eq:PM:CLTS:1}
     \|X_t\|^{\tilde \beta - 1}  X_t(f_s)
     = I^{f_s}_1(t) + I^{f_s}_2(t) + I^{f_s}_3(t)
    := \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}  \|X_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_s) \Big)\\
    + \Big(  \|X_t\|^{\tilde \beta - 1} \mathcal I_0^{t-\lfloor t \rfloor} X_t(f_s)   + \sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor-1} \|X_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_s) \Big) + ( \|X_t\|^{\tilde \beta - 1}X_0(P_t^\alpha f_s) ),
  \end{multline}
  \begin{multline}
    \label{eq:PM:CLTS:2}
     \|tX_t\|^{\tilde \beta - 1}  X_t(f_c)
     = I^{f_c}_1(t) + I^{f_c}_2(t) + I^{f_c}_3(t)
    := \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}  \|tX_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_c) \Big)\\
    + \Big(  \|tX_t\|^{\tilde \beta - 1} \mathcal I_0^{t-\lfloor t \rfloor} X_t(f_c)   + \sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor-1} \|tX_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_c) \Big) + ( \|tX_t\|^{\tilde \beta - 1}X_0(P_t^\alpha f_c) ),
  \end{multline}
and
 \begin{align}
    & \frac{X_t(f_l) - \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta \geq |p|b} \langle f_l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}H_\infty^p}{\|X_t\|^{1- \tilde \beta}}
      = \sum_{p\in \mathcal N}\frac{ \langle f_l,\phi_p\rangle_\varphi [X_t(\phi_p) - e^{(\alpha - |p|b)t}H_\infty^p]}{\|X_t\|^{1- \tilde \beta}}
    \\& = \sum_{p \in \mathcal N} \frac{\langle f_l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}(H_t^p - H_\infty^p)}{\|X_t\|^{1- \tilde \beta}}
    = \sum_{k=0}^\infty \sum_{p \in \mathcal N}  \langle f_l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}
    \\ &= \Big(\sum_{k = 0}^{\lfloor t^2 \rfloor}  +\sum_{k = \lfloor t^2 \rfloor+1}^\infty \Big)\Big(\sum_{p \in \mathcal N}  \langle f_l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}\Big)
         = : I^{f_l}_1(t) + I^{f_l}_2(t),
  \end{align}
where $\mathcal N:= \{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b\}$.
%Now for each $t\geq t_0$ and $i=1,2,3$, let
Define $I_3^{f_l}(t)=0$, $t\geq t_0$. For all $t\geq t_0$ and $j=1,2,3$, let
\(
%   U_i(t):=\big(I_i^{f_s}(t),I_i^{f_c}(t),I_i^{f_l}(t)\big),
%we should avoid using  as an index
   R_j(t):=\big(I_j^{f_s}(t),I_j^{f_c}(t),I_j^{f_l}(t)\big)
\)
%where we write $I_3^{f_l}(t)=0$, $t\geq t_0$. and Let
and
\begin{align}
    R_0(t)=(I_0^{f_s}(t),I_0^{f_c}(t),I_0^{f_l}(t)):=\big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_l}\big),
    %\quad t\geq t_0,
\end{align}
where $\tilde f_s:=e^{\alpha(\tilde \beta - 1)} f_s$, $\tilde f_c:=e^{\alpha(\tilde \beta - 1)} f_c$ and  $\tilde f_l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_l, \phi_p \rangle_\varphi \phi_p$.

Define
\begin{align}
R(t):=\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_s)}{\|X_t\|^{\frac{1}{1+\beta}}},\frac{X_t(f_c)}{\|tX_t\|^{\frac{1}{1+\beta}}},\frac{ X_t(f_l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{\frac{1}{1+\beta}}}\Bigg).
\end{align}
The following result is a special case of Theorem \ref{thm:M}.
%Having set this notation, we can establish the following CLT.
\begin{thm}\label{thm: II}
%Under $\mathbb P_{\mu}(\cdot|D^c)$,
Under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$,
%\begin{align}
% U(t)&:=\Big( \|X_t\|^{\tilde{\beta}-1}X_t(f_s), \|tX_t\|^{\tilde{\beta}-1}X_t(f_c),\\
%& \|X_t\|^{\tilde{\beta}-1}(X_t(f_l)-\sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}\langle f_l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)t}H_{\infty}^p \Big)\xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_s},\zeta^{f_c},\zeta^{-f_l}),
%\end{align}
\begin{align}
R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_s},\zeta^{f_c},\zeta^{-f_l}),
\end{align}
where $\zeta^{f_s},\zeta^{f_c}$ and $\zeta^{-f_l}$ are independent $(1+\beta)$-stable random variables with characteristic functions described by \eqref{eq: charac func11}.
\end{thm}
\begin{proof}

Note that for each $t>t_0$,
\[
R(t)=R_0(t)+(R_1(t)-R_0(t))+R_2(t)+R_3(t).
\]
% Then the outline of Theorem's proof follows:
\begin{itemize}
\item[(1)] In Lemma \ref{lem: U0T}, we will show that, under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, $R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_s},\zeta^{f_c},\zeta^{-f_l})$, where $\zeta^{f_s},\zeta^{f_c}$ and $\zeta^{-f_l}$ are independent $(1+\beta)$-stable random variables with characteristic function described by \eqref{eq: charac func11}.
\item[(2)] In Lemma \ref{lem: U1-U0T}, we will show that, under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, $R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d}0$.
\item[(3)] In Lemma \ref{lem: U2T}, we will show that, under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, $R_2(t)\xrightarrow[t\to \infty]{d}0$.
\item[(4)] In Lemma \ref{lem: U3T}, we will show that, under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, $R_3(t)\xrightarrow[t\to \infty]{d}0$.
\end{itemize}
%which will be given by Lemma \ref{lem: U0T}-Lemma \ref{lem: U3T}. Therefore, we get the desired result.
Combining these, we immediately get the conclusion of the theorem.
\end{proof}

\begin{lem}\label{lem: U0T}
% Under $\mathbb P_{\mu}(\cdot |D^c)$,
Under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$,
 $R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_s},\zeta^{f_c},\zeta^{-f_l})$, where $\zeta^{f_s},\zeta^{f_c}$ and $\zeta^{-f_l}$ are independent $(1+\beta)$-stable random variables with characteristic function described by \eqref{eq: charac func11}.
\end{lem}
\begin{proof}
%In fact, for each $t>0$, $\Upsilon_t^f$ is linear in $f$, this means
Since $\Upsilon_t^f$ is linear in $f$, we have
\begin{align}
&\Upsilon_t^{\theta f} = \theta \Upsilon_t^f, \quad \theta \in \mathbb R,\\
&\Upsilon_t^{f+g} = \Upsilon_t^f+\Upsilon_t^g,\quad f,g \in \mathcal P.
\end{align}
Therefore, for each $t>t_0$,
\[
\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
%\sum_{i=s,c,l}I_0^{f_i}(t)\Big)\Big]
\sum_{j=s,c,l}I_0^{f_j}(t)\Big)\Big]
= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}(\Upsilon_{t-k-1}^{(T_k(\tilde{f_s}+t^{\tilde{\beta}-1} \tilde{f}_c))})\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_l}\Big)\Big].
\]
Using Corollary \ref{cor:MI} with $f=\tilde{f_s}+t^{\tilde{\beta}-1} \tilde{f}_c$ and $g = -\tilde{f}_l$, we get that there exist $C_1,\delta_1 > 0$ such that
  \begin{align}
    &\Big|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
%    \sum_{i=s,c,l}I_0^{f_i}(t)\Big)\Big]
    \sum_{j=s,c,l}I_0^{f_j}(t)\Big)\Big]
    -\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_s+t^{\tilde{\beta}-1}\tilde{f}_c)), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_l),\varphi\rangle\Big)\Big|\\
    &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)},
    \quad t\geq t_0.
  \end{align}
Next, we claim that
\begin{align}
\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_s+t^{\tilde{\beta}-1}\tilde{f}_c)), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_l),\varphi\rangle\Big) =
%\prod_{i=s,c,l}\exp(m[f_i]).
\prod_{j=s,c,l}\exp(m[f_j]).
\end{align}
 Then we have
% $\mathbb{\widetilde{P}}_{\mu} [e^{i \sum_{i=s,c,l}I^{f^i}_0(t)} ]
 $\mathbb{\widetilde{P}}_{\mu} [e^{i \sum_{j=s,c,l}I^{f^j}_0(t)} ]
% \xrightarrow[t\to \infty]{}  \prod_{i=s,c,l}\exp(m[f_i])$.
 \xrightarrow[t\to \infty]{}  \prod_{j=s,c,l}\exp(m[f_j])$.
% For $i=s,c,l$, since $I_0^{f_i}(t)$ is linear in $f_i$, we can replace $f_i$ with $\theta_i f_i$, $\theta_i \in \mathbb R$, and then we get the desired result.
Since $I_0^{f_j}(t)$, $j=s,c,l$, is linear in $f_j$, replacing $f_j$ with $\theta_j f_j$, we immediately get the desired result.

Now we prove the above claim.
 Recall that  $\tilde f_l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_l, \phi_p \rangle_\varphi \phi_p$.
  Using \eqref{eq:I:R:2} and the fact that $\varphi(x)dx$ is the invariant distribution of the semigroup $(P_t)_{t\geq 0}$, we get that for each $n\in \mathbb Z_+$,
  \begin{align}
    \label{eq:PM:CLTS:2a}
    & \sum_{k=0}^n \langle Z_1 T_{k} (-\tilde f_l), \varphi \rangle
      = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha ((iP_{1 - u}^\alpha T_k \tilde f_l)^{1+\beta}), \varphi\rangle ~du
    \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle  (iP_{1 - u}^\alpha T_{k}\tilde f_l)^{1+\beta}, \varphi \rangle ~du
    \\& = \sum_{k=0}^n \int_0^1 \langle  (iT_{k+ u} f_l)^{1+\beta}, \varphi\rangle~du
    = \int_0^{n+1} \langle  (iT_{u} f_l)^{1+\beta}, \varphi\rangle~du = m_{n+1}[-f_l].
  \end{align}
Therefore, we have
\[
\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_l),\varphi\rangle\Big) = \lim_{t\rightarrow \infty}\exp(m_{\lfloor t^2 \rfloor+1}[-f])=\exp(m[-f]).
\]
Similarly, for each $f\in \mathcal C_s  \oplus \mathcal C_c$ and $n\in \mathbb Z_+$.
  \begin{align}
%    \label{eq:PM:CLTS:2}
    & \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
    = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha ((-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle ~du
    \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle  (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle ~du
    \\& = \sum_{k=0}^n \int_0^1 \langle  (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle~du
    = \int_0^{n+1} \langle  (-iT_{u} f)^{1+\beta}, \varphi\rangle~du = m_{n+1}[f],
  \end{align}
where $\tilde f=e^{\alpha(\tilde \beta - 1)} f$ .
Therefore, for any $t\geq t_0$,
\[
\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_s+t^{\tilde{\beta}-1}\tilde{f}_c)), \varphi\rangle \Big)=\int_0^{\lfloor t-\ln t \rfloor+1}\langle (-i(T_u(f_s+t^{\tilde{\beta}-1}f_c)))^{1+\beta},\varphi\rangle du.
\]
Note that for each $u>0$, $T_uf_c=f_c$. According to Step 1 in the proof
of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, for each $f\in \mathcal P$, there exist a constant $\delta\geq 0$ and $h\in \mathcal P$
 such that
 %for all $u\geq 0$, we have $|T_uf|\leq e^{-\delta u}h$, especially, when $f\in \mathcal C_s$, $\delta$ can be chosen strictly positive.
 $|T_uf|\leq e^{-\delta u}h$ for all $u\geq 0$. When $f\in \mathcal C_s$, $\delta$, we can take
 $\delta$ to be  strictly positive.
%Therefore, according to  Lemma \ref{lem:m} and
Combining this with
Lemma \ref{ineq: analysis}, we get that there exist constant $C_1,\delta>0$ and $h\in \mathcal P$ such that for all $u>0$,
\begin{align}
  &|(-i(T_uf_s+t^{\tilde{\beta}-1}T_uf_c))^{1+\beta}-(-iT_uf_s)^{1+\beta}-(-it^{\tilde{\beta}-1}T_uf_c)^{1+\beta}|\\
&\leq C_1(t^{-\frac{\beta}{1+\beta}}|T_uf_s||T_uf_c|^{\beta}+t^{-\frac{1}{1+\beta}}|T_uf_s|^{\beta}|T_uf_c|)\\
&\leq C_1(t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_c|),
\end{align}
which means that
\begin{align}
&\Big|\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_s+t^{\tilde{\beta}-1}\tilde{f}_c)), \varphi\rangle \Big)-m_{\lfloor t-\ln t \rfloor+1}[f_s]-\frac{1}{t}m_{\lfloor t-\ln t \rfloor+1}[f_c]\Big|\\
&\leq C_1\int_0^{\lfloor t-\ln t \rfloor+1}(t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_c|)du\xrightarrow{t\rightarrow \infty} 0.
\end{align}
Combining this with \eqref{eq:I:R:3}, we get that
\[
\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_s+t^{\tilde{\beta}-1}\tilde{f}_c)), \varphi\rangle \Big) = m[f_s]+m[f_c].
\]
%Now we complete the proof of claim.
Thus the claim is valid.
\end{proof}
\begin{lem}\label{lem: U1-U0T}
% Under $\mathbb P_{\mu}(\cdot |D^c)$,
Under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$,
 $R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d}0$.
\end{lem}
\begin{proof}
%In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we have, for each $t\geq t_0$, that
It follows from \cite[Lemma 3.4.3]{Durrett2010Probability} that for $t\geq t_0$,
\[
\Big|\widetilde {\mathbb P}_{\mu}\Big[\exp\Big(i
%\sum_{i=s,c,l}(I_{1}^{f_i}(t) - I_0^{f_i}(t))\Big)
\sum_{j=s,c,l}(I_{1}^{f_j}(t) - I_0^{f_j}(t))\Big)
 - 1\Big]\Big| \leq  \sum_{k=0}^{\lfloor t-\ln t \rfloor}(\widetilde {\mathbb {P}}_\mu[|Y^s_{t,k}|] + \widetilde {\mathbb {P}}_\mu[|Y^c_{t,k}|] )+ \sum_{k=0}^{\lfloor t^2 \rfloor} \widetilde {\mathbb {P}}_\mu[|Y^l_{t,k}|]
\]
 where
 \begin{align}
 &Y^s_{t,k} := \exp\Big(i(\|X_t\|^{\tilde{\beta}-1}\mathcal I_{t-k-1}^{t-k}X_t(f_s) - \Upsilon_{t-k-1}^{T_{k}\widetilde {f_s}})\Big) - 1, \\
 &Y^c_{t,k} := \exp\Big(i(\|tX_t\|^{\tilde{\beta}-1}\mathcal I_{t-k-1}^{t-k}X_t(f_c) - \Upsilon_{t-k-1}^{T_{k}\widetilde {f_c}})\Big) - 1,\\
&Y^l_{t,k} := \exp\Big(i(\widetilde{\Upsilon}_{t,k} - \Upsilon_{t+k}^{-T_{k}\widetilde {f_l}})\Big) - 1,\\
&\widetilde{\Upsilon}_{t,k}=\|X_t\|^{\tilde{\beta}-1}\Big( \sum_{p\in \mathcal N}\langle f_l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)t}(H_{t+k}^p-H_{t+k+1}^p)\Big).
\end{align}
  We claim that there exist $C_1, \delta_1>0$ such that
\begin{align}
% \widetilde {\mathbb {P}}_\mu[|Y^i_{t,k}|]
 \widetilde {\mathbb {P}}_\mu[|Y^j_{t,k}|]
 \leq C_1e^{-\delta_1 (t-k)}, \quad  t\geq t_0, k \in \mathbb Z_+ \text{~satisfying~} k\leq t-1,
%  i=s,c,
  j=s,c,
\end{align}
and
\[
 \widetilde {\mathbb {P}}_\mu[|Y^l_{t,k}|] \leq C_1e^{-\delta_1 t}, \quad t\geq t_0, k \in \mathbb Z_+.
\]
  Then there exists $C_2>0$ such that for all $t>t_0$, we have
%  $\|\widetilde {\mathbb P}_{\mu}[\exp(i\sum_{i=s,c,l}(I_{1}^{f_i}(t) - I_0^{f_i}(t))) - 1]| \leq C_2(t^{-\delta_1}+(1+t^2)e^{-\delta_1 t})$
$$
\big|\widetilde {\mathbb P}_{\mu}\left[\exp\left(i\sum_{j=s,c,l}(I_{1}^{f_j}(t) - I_0^{f_j}(t))\right) - 1\right]\big| \leq C_2(t^{-\delta_1}+(1+t^2)e^{-\delta_1 t})
$$
which, combined with the fact that
%for $i=s,c,l$, $I^{f_i}_1(t) - I^{f_i}_0(t)$  is linear in $f_i$, completes this Lemma.
$I^{f_j}_1(t) - I^{f_j}_0(t)$, $j=s,c,l$, is linear in $f_j$, completes the proof of this lemma.

  We now show the claim above in the following steps.
  First we choose $\gamma\in(0, \beta)$ close enough to $\beta$ so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$,
  and that there exist $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
  %For all $0<s<t$, we define
  %We should avoid using s in this proof.
  For all $0<r<t$, we define
\[
%\mathcal{D}_{t,s} :=\{|H_t-H_{s}|\leq  e^{-\eta s}, H_{s}> 2e^{-\eta' s}\}.
\mathcal{D}_{t,r} :=\{|H_t-H_{r}|\leq  e^{-\eta r}, H_{r}> 2e^{-\eta' r}\}.
\]
 \emph{Step 1.} We show that there exist $C_{1.1},\delta_{1.1} >0$ such that
% for all  $0<s<t$, $ \mathbb{\widetilde{P}}_{\mu} \big[ \mathcal{D}^c_{t,s} \big] \leq C_{1.1} e^{-\delta_{1.1} s}.$
$\mathbb{\widetilde{P}}_{\mu} \big[ \mathcal{D}^c_{t,r} \big] \leq C_{1.1} e^{-\delta_{1.1} r}$ for all $0<r<t$.

 It follows from \cite[Proposition 2.10 \& Lemma 3.3 with $|p|=0$]{RenSongSunZhao2019Stable} and Chebyshev's inequality that there exist $C_{1.1}', \delta_{1.1}'>0$ such that for all
  $0<r<t$,
  \begin{align}
    & \mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,r}^c)
    \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{r}| > e^{-\eta r})+\mathbb{\widetilde{P}}_{\mu}(H_{r}\leq 2e^{-\eta'r}) \\
    & \leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta r}\mathbb{P}_{\mu}[|H_t-H_r|] +  \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_r\leq 2e^{-\eta'r}; D^c) \\
    & \leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta r}\|H_t - H_r\|_{\mathbb P_\mu; 1+\gamma} + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_r\leq 2e^{-\eta'r}) \\
    & \leq C'_{1.1} e^{-(\alpha \tilde \gamma - \eta)r}+C'_{1.1} e^{-\delta'_{1.1}r}.
  \end{align}
  \emph{Step 2.} We show that there exist $C_{2.1},\delta_{2.1} > 0$ such that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, it holds that $ \mathbb{\widetilde{P}}_{\mu} [|Y^s_{t,k}|] \leq  C_{2.1} e^{-\delta_{2.1} (t-k)}$.

  Note that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $. Therefore for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$,
  \begin{align}
    \label{eq:gammafunction11}
    \Upsilon_{t-k-1}^{T_{k} \tilde f_s}
    = \frac{X_{t-k}(T_{k} \tilde  f_s) - X_{t -k-1}(P_1^\alpha T_{k} \tilde f_s)}{\|X_{t-k-1}\|^{1-\tilde \beta}}
    = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f_s)}{\|e^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
  \end{align}
  Since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have  for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$,
  \begin{align}
    \label{eq: control of Ykt}
    \mathbb{\widetilde{P}}_{\mu}[|Y^s_{t,k}|;\mathcal{D}_{t,t-k-1}]
    & \leq \mathbb{\widetilde{P}}_{\mu}\Big[|\mathcal I_{t-k-1}^{t-k} X_t(f_s) | \cdot \Big| \| e^{\alpha(k+1)}X_{t-k-1}\| ^{ \tilde \beta - 1} - \|X_t\|^{ \tilde \beta - 1}\Big|; \mathcal D_{t,t-k-1}\Big] \\
    & \leq  e^{\alpha(\tilde \beta - 1)t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}X_t(f_s)|\cdot K_{t,k}\big],
  \end{align}
  where
  \[
    K_{t,k}
%    := \Big| \frac {H_t^{1- \tilde \beta} - H_{t-k-1}^{1 - \tilde \beta}} {H_t^{1 - \tilde \beta} %H_{t-k-1}^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t,t-k-1}}.
   := \Big| \frac {(H_t)^{1- \tilde \beta} - (H_{t-k-1})^{1 - \tilde \beta}} {(H_t)^{1 - \tilde \beta}
   (H_{t-k-1})^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t,t-k-1}}.
  \]
  Note that, since $\eta' < \eta$, we have almost surely on $\mathcal D_{t,t-k-1}$,
  \begin{align}
    H_t
    & \geq H_{t-k-1}- e^{-\eta (t-k-1)}
      \geq 2e^{-\eta'(t-k-1)}-e^{-\eta(t-k-1)}
      \geq e^{-\eta'(t-k-1)}.
  \end{align}
  Therefore, for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, almost surely  on $\mathcal D_{t,t-k-1}$,
  \begin{align}
%    & \Big|H_t^{1- \tilde \beta}-H_{t-k-1}^{1- \tilde \beta}\Big|
%      \leq (1- \tilde \beta) \max \{ H_t^{-\tilde \beta }, H_{t-k-1}^{ -\tilde \beta} \} | H_t - H_{t-k-1} | \\
   & \Big|(H_t)^{1- \tilde \beta}-(H_{t-k-1})^{1- \tilde \beta}\Big|
      \leq (1- \tilde \beta) \max \{ (H_t)^{-\tilde \beta }, (H_{t-k-1})^{ -\tilde \beta} \} | H_t - H_{t-k-1} | \\
    & \leq (1- \tilde \beta ) \max\{e^{\eta' (t-k-1)}, \frac{1}{2}e^{\eta'(t-k-1)}\}^{\tilde \beta} e^{-\eta(t-k-1)}  \leq (1- \tilde \beta) e^{-(\eta - \eta') (t-k-1)}
  \end{align}
%  and $ |H_t^{1 - \tilde \beta} H_{t-k-1}^{ 1 - \tilde \beta}| \geq 2^{\frac{1}{1+\beta}} e^{-2\eta'(t-k-1)}$.
  and $ |(H_t)^{1 - \tilde \beta} (H_{t-k-1})^{ 1 - \tilde \beta}| \geq 2^{\frac{1}{1+\beta}} e^{-2\eta'(t-k-1)}$.
  Thus, there exists $C_{2.1}'> 0$ such that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, almost surely
  \begin{align}
    K_{t,k}
    \leq C_{2.1}' e^{-(\eta - 3\eta')(t-k-1)}.
  \end{align}
  Now, by \cite[Lemma 2.13]{RenSongSunZhao2019Stable}, there exists $C''_{2.1}>0$ such that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$,
  \begin{align}
    & \mathbb{\widetilde{P}}_{\mu} [|Y^s_{t,k}| ; \mathcal{D}_{t,t-k-1} ]
    \leq C_{2.1}' e^{\alpha (\tilde \beta - 1)t} \mathbb{\widetilde{P}}_{\mu} [ | \mathcal{I}_{t-k-1}^{t-k}X_t(f_s)| ] e^{-(\eta - 3\eta')(t-k-1)} \\
    & \leq \frac{C_{2.1}' } {\mathbb{P}_{\mu}(D^c)} e^{ \alpha (\tilde \beta - 1)t} \|\mathcal{I}_{t-k-1}^{t-k} X_t(f_s)\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta - 3\eta')(t-k - 1)} \\
    & \leq C_{2.1}'' e^{\alpha(\tilde \beta - \tilde \gamma)t} e^{ (\alpha \tilde \gamma - \kappa_f b)k} e^{-(\eta - 3\eta')(t-k)}
     \leq C_{2.1}'' e^{\alpha(\tilde \beta - \tilde \gamma)(t-k)} e^{-(\eta - 3\eta')(t-k)}.
  \end{align}
  In the last inequality, we used the fact that $\alpha \tilde \beta < \kappa_{f_s} b$. Combining the fact that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, $\mathbb{\widetilde{P}}_{\mu} [|Y^s_{t,k}| ; \mathcal{D}^c_{t,t-k-1} ]\leq 2\mathbb{\widetilde{P}}_{\mu} [ \mathcal{D}^c_{t,t-k-1} ]\leq 2 C_{1,1}e^{-\delta_{1.1}(t-k-1)}$, we get the desired result.

 \emph{Step 3.} We show that there exist $C_{3.1},\delta_{3.1} > 0$ such that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, $ \mathbb{\widetilde{P}}_{\mu}[|Y^c_{t,k}|] \leq  C_{3.1} e^{-\delta_{3.1} (t-k)}.$

  Note that for $f\in \mathcal C_c$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f$. Therefore for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$,
  \[
    t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k} \tilde f_c}
    = \frac{X_{t-k}(T_{k} \tilde f_c) - X_{t -k-1}(P_1^\alpha T_{k} \tilde f_c)}{\|t X_{t-k-1}\|^{1-\tilde \beta}}
    = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f_c)}{\|te^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
  \]
  The rest is similar to Step 2.
  We omit the details.

 \emph{Step 4.} We show that there exist $C_{4.1}, \delta_{4.1}>0$ such that for all $k \in \mathbb Z_+$ and $t\geq t_0$, we have $\widetilde {\mathbb {P}}_\mu[|Y^l_{t,k}|]\leq C_{4.1}e^{- \delta_{4.1} t}$.

 Note that for all $k \in \mathbb Z_+$ and $t\geq t_ 0$,
  \begin{align}
    & \Upsilon_{t+k}^{-T_k\tilde f_l}
      = \frac{X_{t+k}(P^\alpha_1T_k\tilde f_l) - X_{t+k+1}(T_k \tilde f_l)}{\|X_{t+k}\|^{1 - \tilde \beta}}
    \\& = \sum_{p\in \mathcal N}
    \langle\tilde f_l,\phi_p\rangle_\varphi e^{-(\alpha \tilde \beta - |pb|)k}\frac{ X_{t+k}(P_1^\alpha \phi_p) - X_{t+k+1}(\phi_p)}{\|X_{t+k}\|^{1 - \tilde \beta}}
    \\& = \sum_{p\in \mathcal N}
    \langle f_l,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t}\frac{H_{t+k}^p-H_{t+k+1}^p }{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}}.
  \end{align}
  Therefore for all $k\in \mathbb Z_+$ and $t\geq t_0$,
  \begin{align}
    &|Y^l_{t,k}| \mathbf 1_{\mathcal D_{t+k,t}}
      \leq \Big( \sum_{p\in \mathcal N}|\langle f_l,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)\mathbf 1_{\mathcal D_{t+k,t}}
    \\ &= \Big( \sum_{p\in \mathcal N}|\langle f_l,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big)e^{\alpha (\tilde \beta - 1)t} K'_{t,k}
    \\ &= \Big( \sum_{p\in \mathcal N}|\langle f_l,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) K'_{t,k},
  \end{align}
  where
  \[
    K'_{t,k}
%    := \Big| \frac {H_t^{1- \tilde \beta} - H_{t+k}^{1 - \tilde \beta}} {H_t^{1 - \tilde \beta} H_{t+k}^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t+k,t}}.
        := \Big| \frac {(H_t)^{1- \tilde \beta} - (H_{t+k})^{1 - \tilde \beta}} {(H_t)^{1 - \tilde \beta} (H_{t+k})^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t+k,t}}.
  \]
  Similar to Step 2, we can get that for all $k\in \mathbb Z_+$ and $t\geq t_0$, almost surely $K'_{t,k} \leq C_{4.1}'' e^{- (\eta - 3\eta')t}$.
  It follows from this and \cite[Lemma 3.3]{RenSongSunZhao2019Stable} that there exists $C'''_{4.1}>0$ such that for all $k\in \mathbb Z_+$ and $t\geq t_0$,
  \begin{align}
    & \widetilde{\mathbb P}_\mu[|Y^l_{t,k}|; \mathcal D_{t+k,t}]
      \leq \mathbb P_\mu(D)^{-1}\mathbb P_\mu[ |Y^l_{t,k}| ;\mathcal D_{t+k,t} ]
    \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{4.1}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} |\langle f_l,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} \mathbb P_\mu[| H_{t+k}^p-H_{t+k+1}^p |]
    \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{4.1}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} |\langle f_l,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} \| H_{t+k}^p-H_{t+k+1}^p \|_{\mathbb P_\mu; 1+\gamma}
    \\&\leq  \mathbb P_{\mu}(D)^{-1} C_{4.1}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal N} |\langle f_l,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} e^{-(\alpha \tilde \gamma - |p|b)(t+k)} \\
    &  \leq  C_{4.1}''' e^{- (\eta - 3\eta') t} e^{(\alpha \tilde \beta - \alpha \tilde \gamma)t}.
  \end{align}
 Combining this with the fact that, for all $t>t_0$ and $k\in \mathbb Z_+$,  $\mathbb{\widetilde{P}}_{\mu} [|Y^l_{t,k}| ; \mathcal{D}^c_{t+k,t} ]\leq 2\mathbb{\widetilde{P}}_{\mu} [ \mathcal{D}^c_{t+k,t} ]\leq 2 C_{1,1}e^{-\delta_{1.1}t}$, we get the desired result.
\end{proof}
\begin{lem}\label{lem: U2T}
%Under $\mathbb P_{\mu}(\cdot |D^c)$,
Under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$,
$R_2(t)\xrightarrow[t\to \infty]{d}0$.
\end{lem}
\begin{proof}
 Define $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to
 \cite[Proposition 2.10]{RenSongSunZhao2019Stable}, there exist $C_1, \delta_1>0$ such that
  \begin{align}
    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_1(t^{-\delta_1 t}+e^{-\delta_1 t})
    , \quad t\geq t_0.
  \end{align}
  Therefore,
  \begin{align}
    \label{Theorem123}
    |\mathbb{\widetilde{P}}_{\mu}[e^{i
%    \sum_{i=s,c,l}I^{f_i}_2(t)}-1;\mathcal{E}^c_t]|
    \sum_{j=s,c,l}I^{f_j}_2(t)}-1;\mathcal{E}^c_t]|
    \leq 2\mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
    \leq 2C_1(t^{-\delta_1}+e^{-\delta_1 t}),
    \quad t\geq t_0.
  \end{align}
On the other hand,
\[
   |\mathbb{\widetilde{P}}_{\mu} [ (e^{i
%   \sum_{i=s,c,l}I^{f_i}_2(t)}-1);\mathcal{E}_t]|
%   \leq \sum_{i=s,c,l}\widetilde{\mathbb P}_{\mu}[|I^{f_i}_2(t)|\mathcal{E}_t],
      \sum_{j=s,c,l}I^{f_j}_2(t)}-1);\mathcal{E}_t]|
    \leq \sum_{j=s,c,l}\widetilde{\mathbb P}_{\mu}[|I^{f_j}_2(t)|\mathcal{E}_t],
\quad t\geq t_0.
\]
%We claim that for $i=s,c,l$,  $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_i}_2(t)|;\mathcal{E}_t]=0$. Then combining \eqref{Theorem123}, we get $\lim_{t\rightarrow \infty}\mathbb{\widetilde{P}}_{\mu}[e^{i \sum_{i=s,c,l}I^{f_i}_2(t)}-1] = 0$. For $i =s,c,l$, since $I_2^{f_i}(t)$ is linear in $f_i$, we can replace $f_i$ with $\theta_i f_i$, $\theta_i \in \mathbb R$, and then the desired result in this step follows.
We claim  $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_j}_2(t)|;\mathcal{E}_t]=0$, $j=s,c,l$. Then combining this with \eqref{Theorem123}, we get $\lim_{t\rightarrow \infty}\mathbb{\widetilde{P}}_{\mu}[e^{i \sum_{j=s,c,l}I^{f_j}_2(t)}-1] = 0$.
Since $I_2^{f_j}(t)$, $j=s,c,l$, is linear in $f_j$, replacing $f_j$ with $\theta_j f_j$, $\theta_j \in \mathbb R$, we immediately get the desired result in this step.

   We now show the claim above in the following steps.
Fix a $\gamma \in (0,\beta)$ close enough to $\beta$ so that $\alpha(\tilde{\beta}-\tilde{\gamma})\leq \frac{1}{2}(1-\tilde{\beta})$ and $\alpha\tilde{\gamma}>|p|b$ for all $p\in \mathcal N$.

\emph{Step 1.} We show that $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_s}_2(t)|;\mathcal{E}_t]=0$.

  Since $\kappa_{f_s} b -\alpha \tilde \gamma > \alpha (\tilde \beta - \tilde \gamma)$, we can choose $\epsilon >0$ small enough so that $q:=\kappa_{f_s}b- \alpha \tilde \gamma  > \alpha (\tilde \beta - \tilde \gamma) + \epsilon $.

	According to \cite[Lemma 2.13]{RenSongSunZhao2019Stable}, there exist $C_2',C_2''>0$ such that for each $t\geq t_0 >1$,
  \begin{align}
    & \mathbb{\widetilde{P}}_{\mu} [ |I^{f_s}_2(t)|;\mathcal{E}_t] \\
    & \leq  ( t^{-1/2}e^{\alpha t} )^{\tilde \beta - 1}\Big(\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu} [| \mathcal{I}_{t-k-1}^{t-k} X_t(f_s) |] + \mathbb{\widetilde{P}}_{\mu}[| \mathcal{I}_{0}^{t-\lfloor t\rfloor} X_t(f_s)|]\Big) \\
    & \leq  ( t^{-1/2}e^{\alpha t} )^{\tilde \beta - 1}\Big(\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k} X_t(f_s) \|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} X_t(f_s)\|_{\mathbb P_\mu;1+\gamma}\Big) \\
    & \leq C_2't^{\frac{1-\tilde{\beta}}{2}} e^{\alpha (\tilde \beta - \tilde \gamma)t}\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor}  e^{(\alpha\tilde \gamma-\kappa_{f_s} b)k}
      \leq C_2''t^{\frac{1-\tilde{\beta}}{2}} e^{(q-\epsilon) t}\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor}  e^{-q k}
    \\ & \leq C_2'''t^{\frac{1-\tilde{\beta}}{2}} e^{q(t - \lfloor t - \ln t\rfloor-1)}e^{-\epsilon t}
         \leq C_2'''t^{\frac{1-\tilde{\beta}}{2}} t^q e^{- \epsilon t}.
  \end{align}
%  From this , we get that $ \mathbb{\widetilde{P}}_{\mu} [ |I^{f_s}_2(t)|;\mathcal{E}_t]\xrightarrow{t\rightarrow \infty} 0$ and get the desired result in this step.
The desired result in this step now follows immediately.

\emph{Step 2.} We show that $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_c}_2(t)|;\mathcal{E}_t]=0$.

It follows from \cite[Lemma 2.13]{RenSongSunZhao2019Stable} that there exist $C_3',C_3''>0$ such that for each $t\geq t_0$,
  \begin{align}
     &\mathbb{\widetilde{P}}_{\mu} [ |I^{f_c}_2(t);{\mathcal{E}_t}] \\
    & \leq  (t^{\frac{1}{2}} e^{\alpha t} )^{\tilde \beta - 1}\Big(\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu} [| \mathcal{I}_{t-k-1}^{t-k} X_t(f_c) |] + \mathbb{\widetilde{P}}_{\mu}[| \mathcal{I}_{0}^{t-\lfloor t\rfloor} X_t(f_c)|]\Big) \\
    & \leq C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - 1)t}\Big(\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k} X_t(f_c) \|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} X_t(f_c)\|_{\mathbb P_\mu;1+\gamma}\Big) \\
    & \leq C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)t}\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor}  e^{(\alpha\tilde \gamma-\kappa_{f_c} b)k}
      = C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - \tilde \gamma) t}\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor}  e^{-\alpha (\tilde \beta -\tilde \gamma) k}
    \\ & \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)(t - \lfloor t - \ln t\rfloor-1)}
         \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} t^{\alpha (\tilde \beta - \tilde \gamma)}.
  \end{align}
  From this, we immediately get the desired result in this step.

\emph{Step 3.} We will show that $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_l}_2(t)|;\mathcal{E}_t]=0$.

 It follows from \cite[Lemma 3.3]{RenSongSunZhao2019Stable} that there exist $C_4',C_4''>0$ and $\delta_3'>0$ such that
  \begin{align}
    &\widetilde {\mathbb {P}}_\mu[ | I_{2}^{f_l}(t)|; \mathcal {E}_t]
      \leq \sum_{k = \lfloor t^2\rfloor+1}^\infty \widetilde {\mathbb {P}}_\mu[ |\widetilde {\Upsilon}_{t,k}|; \mathcal {E}_t]
    \\ & \leq \mathbb P_\mu(D^c)^{-1} \sum_{k = \lfloor t^2\rfloor+1}^\infty \sum_{p \in \mathcal N} |\langle f_l,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t}\mathbb {P}_\mu\Big[\frac{ |H_{t+k}^p - H_{t+k+1}^p|}{\|X_t\|^{1- \tilde \beta}}; \mathcal E_t\Big]
    \\ & \leq \mathbb P_\mu(D^c)^{-1} (t^{-1/2}e^{\alpha t})^{\tilde{\beta}-1} \sum_{k = \lfloor t^2\rfloor+1}^\infty \sum_{p \in \mathcal N} |\langle f_l,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t}\|H_{t+k}^p - H_{t+k+1}^p\|_{\mathbb P_\mu; 1+\gamma}
    \\ & \leq C_4' (t^{-1/2}e^{\alpha t})^{\tilde{\beta}-1} \sum_{k = \lfloor t^2\rfloor+1}^\infty \sum_{p \in \mathcal N} |\langle f_l,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t} e^{- (\alpha \tilde \gamma - |p|b)(t+k)}
    \\ & = C_4''t^{\frac{1-\tilde{\beta}}{2}} e^{ \alpha (\tilde \beta - \tilde \gamma) t }e^{- \delta'_3 t^2},
  \end{align}
 which completes the proof of this step.
\end{proof}
\begin{lem}\label{lem: U3T}
 $R_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$..
\end{lem}
\begin{proof}
\emph{Step 1.} We claim that $I^{f_s}_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
  In fact, if for all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, we define
\begin{equation}
\label{eq:Q}
  	Q_\kappa f
  	:= \sup_{t\geq 0} e^{\kappa b t}|P_t f|,
  	\qquad  Q f
  	:= Q_{\kappa_f}f.
\end{equation}
	Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$. Thus,  we have
  \begin{align}
    & |I^{f_s}_3(t)|
      \leq \frac{X_0(|P^\alpha_tf_s|)}{\|X_t\|^{1 - \tilde \beta }}
      \leq \frac{e^{\alpha t - \kappa_{f_s} b t}X_0(Qf_s)}{(e^{\alpha t} H_t)^{1 - \tilde \beta}}
      = e^{(\alpha \tilde \beta - k_{f_s}b)t} H_t^{\tilde \beta - 1} X_0(Qf_s)
      \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
  \end{align}

  \emph{Step 2.} Similar to Step 1, we can show that $I^{f_c}_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
  We omit the details.
Since $I_3^{f_l}(t)=0$, the desired result follows immediately.
\end{proof}

%\subsection{Proof of Theorem \ref{thm:M}}
%\label{proofofthm1.4}
\begin{proof}[Proof of Theorem Theorem \ref{thm:M}]
 We first recall some facts about weak convergence which will be used later. For $f:\mathbb R^d\mapsto \mathbb R$, let
 $$
 \|f\|_L:=\sup_{x\neq y}\frac{|f(x)-f(y)|}{|x-y|}
 $$
 and $\|f\|_{BL}:= \|f\|_{\infty}+\|f\|_L. $
 For any distributions $\mu_1$ and $\mu_2$ on $\mathbb R^d$, define
\[
  d(\mu_1,\mu_2):=\sup\Big\{\Big|\int fd\mu_1-\int f d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
\]
Then $d$ is a metric. It follows from \cite[Theorem 11.3.3]{Dudley2002} that the topology generated by $d$ is equivalent to the weak convergence topology. Using the definition, we can easily see that, if $\mu_1$ and $\mu_2$ are the distributions of two $\mathbb R^d $-valued random variables $X$ and $Y$ respectively, then
\begin{align}\label{ineq: distribution control}
  d(\mu_1,\mu_2) \leq \mathbb E|X-Y|.
\end{align}
Recall that $S(t)$ is defined in the display before Theorem \ref{thm:M}.
Now for all $f_s\in \mathcal C_s $, $f_c \in \mathcal C_c$, $f_l \in \mathcal C_l$ and
%$s,t>0$, let
%We should avoid using s. s is repalced by r without marking
$r,t>0$, let
%\begin{align}
%  U(t):=\Big(e^{-\alpha t}\|X_t\|,& \|X_t\|^{\tilde{\beta}-1}X_t(f_s), \|tX_t\|^{\tilde{\beta}-1}X_t(f_c),\\
%& \|X_t\|^{\tilde{\beta}-1}(X_t(f_l)-\sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}\langle f_l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)t}H_{\infty}^p \Big);
%\end{align}
\begin{align}
  S(t,r):=\Big(e^{-\alpha t}\|X_t\|,& \|X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_s), \|(t+r)X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_c),\\
& \|X_{t+r}\|^{\tilde{\beta}-1}(X_{t+r}(f_l)-\sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}\langle f_l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)(t+r)}H_{\infty}^p )\Big),
\end{align}
and
\begin{align}
\widetilde{S}(t,r)= \Big(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0\Big).
\end{align}
Then $S(t+r)=S(t,r)+\widetilde{S}(t,r)$.

\emph{Step 1.} For each $\mu\in \mathcal M_c(\mathbb R^d)$, $f_s\in \mathcal C_s$,$f_c\in \mathcal C_c$ and $f_l\in \mathcal C_l$, under $\mathbb P_{\mu}(\cdot|D^c)$, we have
\[
S(t,r)\xrightarrow[r\rightarrow \infty]{d}\widetilde{S}(t):=\Big(e^{-\alpha t}\|X_t\|,\zeta^{f_s},\zeta^{f_c},\zeta^{-f_l}\Big),
\]
where $\zeta^{f_s},\zeta^{f_c}$ and $\zeta^{-f_l}$ are independent $(1+\beta)$-stable random variables with characteristic functions described by \eqref{eq: charac func11}. Moreover,  $\zeta^{f_s},\zeta^{f_c}$ and $\zeta^{-f_l}$ are independent of $e^{-\alpha t}\|X_t\|$.

For each $\theta,\theta_s,\theta_c,\theta_l\in \mathbb R$ and $r,t>0$, denote the characteristic function of  $S(t,r)$ under $\mathbb P_{\mu}(\cdot|D^c)$ by $k(\theta,\theta_s,\theta_c,\theta_l,r,t)$, then by the dominated convergence theorem, we have,
\begin{align}
   &k(\theta,\theta_s,\theta_c,\theta_l,r,t)\
   =\widetilde{\mathbb P}_{\mu}\Big[\exp\Big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_s,\theta_c,\theta_l,r,t,\infty)\Big)\Big]\\
  &=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_s,\theta_c,\theta_l,r,t,u)\Big);D^c\Big],
\end{align}
where
\begin{align}
 &A(\theta_s,\theta_c,\theta_l,r,t,u)=i\theta_s\|X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_s)+ i\theta_c \|(t+r)X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_c)\\
&+i\theta_l \|X_{t+r}\|^{\tilde{\beta}-1}\Big(X_{t+r}(f_l)-\sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}\langle f_l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)(t+r)}H_{u}^p\Big),\quad r+t<u\leq \infty.
\end{align}
Note that the non-extinction event $D^c=\{\|X_r\|>0, r\geq 0\}=D_{\leq t}\cup D_{\geq t}$, where $D_{\leq t}=\{\|X_r\|>0, 0\leq r\leq t\}$ and $D_{\geq t}=\{\|X_r\|>0, r\geq t\}$. By the Markov property and the dominated convergence theorem, we get
\begin{align}
  & k(\theta,\theta_s,\theta_c,\theta_l,r,t)\\
&=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big(i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}} \mathbb P_{\mu}\Big[\exp\Big(A(\theta_s,\theta_c,\theta_l,r,t,u)\Big)\mathbf 1_{D_{\geq t}}\Big|\mathscr F_t\Big]\Big]\\
&=\lim_{u\rightarrow\infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big( i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}}\mathbb P_{X_t}\Big[\exp\Big(A(\theta_s,\theta_c,\theta_l,r,0,u-t)\Big)\mathbf 1_{D^c}\Big]\Big]\\
&=\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big( i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}}\mathbb P_{X_t}(D^c)\widetilde{\mathbb P}_{X_t}\Big[\exp\Big(A(\theta_s,\theta_c,\theta_l,r,0,\infty)\Big)\Big]\Big]
\end{align}
It follows from Theorem \ref{thm: II} and the dominated convergence theorem,
\begin{align}
   k(\theta,\theta_s, \theta_c,\theta_l,r,t)& \xrightarrow{r\to \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big(i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}}\mathbb P_{X_t}(D^c)\Big]
%   \prod_{i=s,c,l}\exp\Big(m[\theta_i f_l]\Big)\\
   \prod_{j=s,c,l}\exp\Big(m[\theta_j f_j]\Big)\\
&=\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\theta e^{-\alpha t}\|X_t\|\Big)\Big]
%\prod_{i=s,c,l}\exp\Big(m[\theta_i f_i]\Big).
\prod_{j=s,c,l}\exp\Big(m[\theta_j f_j]\Big).
\end{align}
The desired result of this step now follows immediately.

\emph{Step 2.} For all $r,t>0$, let $\mathcal D(r)$ and $\mathcal D(r,t)$ be the distributions of $S(r)$ and $S(t,r)$ under $\mathbb P_{\mu}(\cdot|D^c)$, let $ \widetilde{\mathcal D}(t)$ and $\mathcal D$ be the distributions of $\widetilde{V}(t)$ and $(H^*,\zeta^{f_s},\zeta^{f_c},\zeta^{-f_l})$ under $\mathbb P_{\mu}(\cdot|D^c)$. Then using \eqref{ineq: distribution control} and \cite[Lemma 3.3]{RenSongSunZhao2019Stable}, we have that for each $\gamma\in (0,\beta)$, there exist constant $C>0$ such that,
\begin{align}
 \limsup_{r\rightarrow \infty}d(\mathcal D(t+r),\mathcal D)&\leq \limsup_{r\rightarrow \infty}[d(\mathcal D(t+r),\mathcal D(t,r))+d(\mathcal D(t,r),\widetilde{\mathcal D}(t))+d(\widetilde{\mathcal D}(t),\mathcal D)]\\
&\leq \limsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|e^{-\alpha t}\|X_t\|-e^{-\alpha (t+r)}\|X_{t+r}\||]+0+\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]\\
&\leq \limsup_{r\rightarrow \infty}\mathbb P_{\mu}(D^c)^{-1}(\|H_t-H_{t+r}\|_{\mathbb P_{\mu};1+\gamma}+\|H_t-H_{\infty}\|_{\mathbb P_{\mu};1+\gamma})\\
&\leq Ce^{-\frac{\gamma}{1+\gamma}t}.
\end{align}
Therefore, using the definition of $\limsup_{s\rightarrow \infty}$, we know that,
\begin{align}
 &\limsup_{r\rightarrow \infty}d(\mathcal D(r),\mathcal D) =  \limsup_{s\rightarrow \infty}d(\mathcal D(t+r),\mathcal D)
\leq \lim_{t\rightarrow \infty}Ce^{-\frac{\gamma}{1+\gamma}t} = 0.
\end{align}
The desired result now follows immediately.
\end{proof}

\subsection*{Acknowledgment}

\begin{thebibliography}{10}

\bibitem{AdamczakMilos2015CLT}
  R. Adamczak and P. Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
  Electron. J. Probab. \textbf{20} (2015), no. 42, 35 pp.

\bibitem{Asmussen76Convergence}
  S. Asmussen, \emph{Convergence rates for branching processes},
  Ann. Probab.  \textbf{4} (1976), no. 1, 139--146.

\bibitem{AsmussenHering1983Branching}
  S. Asmussen and H. Hering, \emph{Branching processes},
  Progress in Probability and Statistics, 3. Birkh\"{a}user Boston, Inc., Boston, MA, 1983.

\bibitem{Athreya1969Limit}
  K. B. Athreya,
  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {I}. {T}he case of an eigenvector linear functional},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{12} (1969), 320--332.

\bibitem{Athreya1969LimitB}
  K. B. Athreya,
  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {II}. {T}he case of an arbitrary linear functional},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{13} (1969), 204--214.

\bibitem{Athreya1971Some}
  K. B. Athreya,
  \emph{Some refinements in the theory of supercritical multitype {M}arkov branching processes},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{20} (1971), 47--57.

\bibitem{Bertoin}
J. Bertoin,
\emph{L\'evy processes}.
Cambridge Tracts in Mathematics, 121. Cambridge
University Press, 1996.

\bibitem{BRY}
J. Bertoin, B. Roynette and M. Yor,
\emph{Some connections between (sub)critical branching mechanisms and Bernstein functions}.
arXiv:0412322.

\bibitem{ChenRenWang2008An-almost}
  Z.-Q. Chen, Y.-X. Ren, and H. Wang,
  \emph{An almost sure scaling limit theorem for {D}awson-{W}atanabe superprocesses},
  J. Funct. Anal. \textbf{254} (2008), no. 7, 1988--2019.

 \bibitem{ChenRenSongZhang2015Strong-law}
   Z.-Q. Chen, Y.-X. Ren, R. Song, and R. Zhang,
   \emph{Strong law of large numbers for supercritical superprocesses under second moment condition},
   Front. Math. China \textbf{10} (2015), no. 4, 807--838.

 \bibitem{ChenRenYang2019Skeleton}
   Z.-Q. Chen, Y.-X. Ren, and T. Yang,
   \emph{Skeleton decomposition and law of large numbers for supercritical superprocesses},
   Acta Appl. Math. \textbf{159} (2019), 225--285.

\bibitem{Dudley2002}
  R. M. Dudley
\emph{Real Analysis and Probability},
  Cambridge University Press, 2002.

 \bibitem{Durrett2010Probability}
   R. Durrett,
   \emph{Probability: theory and examples},
   Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.

\bibitem{Dynkin1993Superprocesses}
  E. B. Dynkin,
  \emph{Superprocesses and partial differential equations},
  Ann. Probab. \textbf{21} (1993), no. 3, 1185--1262.

\bibitem{EckhoffKyprianouWinkel2015Spines}
  M. Eckhoff, A. E. Kyprianou, and M. Winkel,
  \emph{Spines, skeletons and the strong law of large numbers for superdiffusions},
  Ann. Probab. \textbf{43} (2015), no. 5, 2545--2610.

\bibitem{Englander2009Law}
  J. Engl\"{a}nder,
  \emph{Law of large numbers for superdiffusions: the non-ergodic case},
  Ann. Inst. Henri Poincar\'{e} Probab. Stat. \textbf{45} (2009), no. 1, 1--6.

\bibitem{EnglanderWinter2006Law}
  J. Engl\"{a}nder and A. Winter,
  \emph{Law of large numbers for a class of superdiffusions},
  Ann. Inst. H. Poincar\'{e} Probab. Statist. \textbf{42} (2006), no. 2, 171--185.

\bibitem{EnglanderTuraev2002A-scaling}
  J. Engl\"{a}nder and  D. Turaev,
  \emph{A scaling limit theorem for a class of superdiffusions},
  Ann. Probab. \textbf{30} (2002), no. 2, 683--722.

\bibitem{Heyde1970A-rate}
  C. C. Heyde,
  \emph{A rate of convergence result for the super-critical {G}alton-{W}atson process},
  J. Appl. Probability \textbf{7} (1970), 451--454.

\bibitem{Heyde1971Some}
  C. C. Heyde,
    \emph{some central limit analogues for supercritical {G}alton-{W}atson processes},
  J. Appl. Probability \textbf{8} (1971), 52--59.

\bibitem{HeydeBrown1871An-invariance}
  C. C. Heyde and B. M. Brown,
  \emph{An invariance principle and some convergence rate results for branching processes},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete, \textbf{20} (1971), 271--278.

\bibitem{HeydeLeslie1971Improved}
  C. C. Heyde and J. R. Leslie,
  \emph{Improved classical limit analogues for {G}alton-{W}atson processes with or without immigration},
  Bull. Austral. Math. Soc. \textbf{5} (1971), 145--155.

\bibitem{IksanovKoleskoMeiners2018Stable-like}
  A. Iksanov, K. Kolesko, and M. Meiners,
  \emph{Stable-like fluctuations of {B}gins' martingales},
  Stochastic Process. Appl. (2018).

\bibitem{Janson2004Functional}
  S. Janson,
  \emph{Functional limit theorems for multitype branching processes and generalized {P}\'{o}lya urns},
  Stochastic Process. Appl. \textbf{110} (2004), no. 2, 177--245.

\bibitem{KestenStigum1966Additional}
  H. Kesten and B. P. Stigum,
  \emph{Additional limit theorems for indecomposable multidimensional {G}alton-{W}atson processes},
  Ann. Math. Statist. \textbf{37} (1966), 1463--1481.

\bibitem{KestenStigum1966A-limit}
  H. Kesten and B. P. Stigum,
  \emph{A limit theorem for multidimensional {G}alton-{W}atson processes},
  Ann. Math. Statist. \textbf{37} (1966), 1211--1223.

\bibitem{KouritzinRen2014A-strong}
  M. A. Kouritzin, and Y.-X. Ren,
  \emph{A strong law of large numbers for super-stable processes},
  Stochastic Process. Appl. \textbf{121} (2014), no. 1, 505--521.

\bibitem{Kyprianou2014Fluctuations}
  A. E. Kyprianou,
  \emph{Fluctuations of {L}\'{e}vy processes with applications},
    Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.

\bibitem{Li2011Measure-valued}
  Z. Li,
  \emph{Measure-valued branching {M}arkov processes},
  Probability and its Applications (New York). Springer, Heidelberg, 2011.

\bibitem{LiuRenSong2009Llog}
  R.-L. Liu, Y.-X. Ren, and R. Song,
  \emph{{$L\log L$} criterion for a class of superdiffusions},
  J. Appl. Probab. \textbf{46} (2009), no. 2, 479--496.

\bibitem{LiuRenSong2013Strong}
  R.-L. Liu, Y.-X. Ren, and R. Song,
  \emph{Strong law of large numbers for a class of superdiffusions},
  Acta Appl. Math. \textbf{123} (2013), 73--97.

\bibitem{MarksMilos2018CLT}
  R. Marks and P. Mi{\l}o{\'s},
  \emph{C{LT} for supercritical branching processes with heavy-tailed branching law},
  arXiv:1803.05491.

\bibitem{MetafunePallaraPriola2002Spectrum}
  G. Metafune, D. Pallara, and E. Priola,
  \emph{Spectrum of {O}rnstein-{U}hlenbeck operators in {$L^p$} spaces with respect to invariant  measures},
  J. Funct. Anal. \textbf{196} (2002), no. 1, 40--60.

\bibitem{Milos2012Spatial}
  P. Mi{\l}o{\'s},
  \emph{Spatial central limit theorem for supercritical superprocesses},
  J. Theoret. Probab. \textbf{31} (2018), no. 1, 1--40.

\bibitem{RenSongSun2017Spine}
  Y.-X. Ren, R. Song, and Z. Sun,
  \emph{Spine decompositions and limit theorems for a class of critical superprocesses},
  Acta Appl. Math. (2019).

\bibitem{RenSongSun2018Limit}
  Y.-X. Ren, R. Song, and Z. Sun,
  \emph{Limit theorems for a class of critical superprocesses with stable branching},
  arXiv:1807.02837.

\bibitem{RenSongSunZhao2019Stable}
Y.-X. Ren, R. Song, Z. Sun and J. Zhao,
\emph{Stable central limit theorems for super Ornstein-Uhlenbeck processes},
Elect. J Probab., \textbf{24} (2019), no. 141, 1--42.

\bibitem{RenSongZhang2014Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for super {O}rnstein-{U}hlenbeck processes},
  Acta Appl. Math. \textbf{130} (2014), 9--49.

\bibitem{RenSongZhang2014CentralB}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical branching {M}arkov processes},
  J. Funct. Anal. \textbf{266} (2014), no. 3, 1716--1756.

\bibitem{RenSongZhang2015Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical superprocesses},
  Stochastic Process. Appl. \textbf{125} (2015), no. 2, 428--457.

\bibitem{RenSongZhang2017Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical branching nonsymmetric {M}arkov processes},
  Ann. Probab. \textbf{45} (2017), no. 1, 564--623.

\bibitem{RenSongZhang2017Functional}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Functional central limit theorems for supercritical superprocesses},
  Acta Appl. Math. \textbf{147} (2017), 137--175.

\bibitem{Sato2013Levy}
  K. Sato,
  \emph{L{\'e}vy processes and infinitely divisible distributions},
  Translated from the 1990 Japanese original. Revised by the author. Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.

\bibitem{SchillingSongVondravcek2010Bernstein}
  R. L. Schilling, R. Song, and Z. Vondra\v{c}ek,
  \emph{Bernstein functions.}
  Theory and applications. Second edition. De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2012.

\bibitem{SteinShakarchi2003Complex}
  E. M. Stein and R. Shakarchi, \emph{Complex analysis},
  Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.

\bibitem{Wang2010An-almost}
  L. Wang, \emph{An almost sure limit theorem for super-{B}rownian motion},
  J. Theoret. Probab. \textbf{23} (2010), no. 2, 401--416.

\end{thebibliography}
\end{document}

### 2020-05-17 supCLT-ind4.tex
add supCLT-ind4.tex

%supCLT-ind1.tex ?/?/? by Jianjie
%supCLT-ind2.tex ?/?/? by ?
%supCLT-ind3.tex 03/05/2020 by Renming
%supCLT-ind4.tex 11/05/2020 by Zhenyao 
\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\calclayout
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
\usepackage[backref]{hyperref}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title
[stable CLT for super-OU processes]
{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II}
\author
[Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
{Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address{
  Yan-Xia Ren \\
  LMAM School of Mathematical Sciences \& Center for Statistical Science \\
  Peking University \\
  Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}
\address{
  Renming Song \\
  Department of Mathematics \\
  University of Illinois at Urbana-Champaign \\
  Urbana, IL, USA, 61801}
\email{rsong@illinois.edu}
\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
\address{
  Zhenyao Sun \\
  School of Mathematics and Statistics\\
  Wuhan University \\
  Hubei, P. R. China, 100871}
\email{zhenyao.sun@gmail.com}
\address{
  Jianjie Zhao \\
  School of Mathematical Sciences \\
  Peking University \\
  Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}

\begin{abstract}
This paper is a continuation of our recent paper (Elect. J. Probab. \textbf{24} (2019), no. 141)
and is devoted to the  asymptotic behavior of a supercritical super Ornstein-Uhlenbeck process $(X_t)_{t\geq 0}$
 whose branching mechanism $\psi$ satisfies some perturbation condition which guarantees that,
 when $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
In the aforementioned paper, we have proved $(1+\beta)$-stable central limit theorems
for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth.
As a consequence of the main result of this paper, we will have
$(1+\beta)$-stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
\end{abstract}
\subjclass[2010]{60J68, 60F05}
\keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}
\maketitle
\section{Introduction}
\subsection{Main result}
\label{subsec:M}
Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
\begin{align}
  Lf(x)
  = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x)
  , \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
\end{align}
where $\sigma > 0$ and $b > 0$ are constants.
Let $\psi$ be a function on $\mathbb R_+$ of the form
\begin{align}
  \label{eq: honogeneou branching mechanism}
  \psi(z)
  =- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) {\color{red} \chi}(\mathrm dy)
  , \quad  z \in \mathbb R_+,
\end{align}
where $\alpha > 0 $, $\rho \geq0$ and {\color{red}$\chi$} is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)\chi(\mathrm dy)< \infty$.
$\psi$ is referred to as a branching mechanism and {\color{red}$\chi$} is referred to as the L\'evy measure of $\psi$.
Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$,
 write $\mu(f)= \int f(x)\mu(\mathrm dx)$
and $\langle f, g\rangle = \int f(x)g(x) \mathrm dx$ whenever the integrals make sense.
We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty. $
We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{align}
  \label{eq: def of V_t}
  \mathbb{P}_{\mu}[e^{-X_t(f)}]
  = e^{-\mu(V_tf)}
  , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{align}
where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{align}
  V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) ) \mathrm ds\Big]
	= \Pi_x [f(\xi_t)]
  , \quad x\in \mathbb R^d, t\geq 0.
\end{align}	
The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.

{\color{red}There have been a lot of papers on laws of large numbers and central limit theorems for branching Markov processes under different settings, including several superprocesses. Those papers can be traced via the references given in \cite{RenSongSunZhao2019Stable}. In this paper, we will be focusing on the asymptotic behavior of the super-OU process $X$ whose branching mechanism $\psi$ satisfies the following two additional assumptions.}

{\color{red}
\begin{asp}[Grey's condition]
	\label{asp: Greys condition}
	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1} \mathrm dz < \infty$.
\end{asp}
}
Denote by $\Gamma$ the gamma function.
For any $\sigma$-finite signed measure $\mu$, denote by $|\mu|$ the total variation measure of $\mu$.
\begin{asp}
  \label{asp: branching mechanism}
  There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
  \begin{align}
    \label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}\Big|\chi(\mathrm dy)-\frac{\eta \mathrm dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
  \end{align}
	for some $\delta > 0$.
\end{asp}

Let us give some comments on those Assumptions.
For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \mu(1)$.
It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
$$D :=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}$$
is non-trivial with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$.
In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$. 
For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c)$.
Assumption \ref{asp: branching mechanism} says that $\psi$ is ``not too far away'' from $\widetilde \psi(z) := - \alpha z + \eta z^{1+\beta}$ near $0$, see \cite[Remark 1.3]{RenSongSunZhao2019Stable}.
It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\chi$.
In \cite[Lemma 2.3]{RenSongSunZhao2019Stable}, we have shown  that,
under Assumption \ref{asp: branching mechanism},
 $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y \chi(\mathrm dy) < \infty. $
In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
	Note that $\delta$ is not uniquely determined by $\chi$.

The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel functions on $\mathbb R^d$.
We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
Define
\(
P^{\alpha}_t f(x)
  := e^{\alpha t} P_t f(x)
  = \Pi_x [e^{\alpha t}f(\xi_t)]
\)
for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$ in the sense that
\(
  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)
\)
for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
\begin{align}
  \label{invariantdensity}
  \varphi(x)\mathrm dx
  :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx
\end{align}
which is a   symmetric multivariate Gaussian distribution.
Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{align}
  \langle f_1, f_2 \rangle_{\varphi}
  := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) \mathrm dx, \quad f_1,f_2 \in L^2(\varphi).
\end{align}
Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
The \emph{Hermite polynomials} are defined by
\begin{align}
  {\color{red}\mathcal H}_p(x)
  :=(-1)^{|p|}e^{|x|^2} \partial_p e^{-|x|^2}
  , \quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
\end{align}
It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
\begin{align}
  \label{eigenfunction}
  \phi_p(x)
  := \frac{1}{\sqrt{ p! 2^{|p|} }} {\color{red}\mathcal H_p} \Big(\frac{ \sqrt{b} }{\sigma}x \Big)
  , \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{align}
In other words,
\(
  P_t\phi_p(x)
  = e^{-b|p|t}\phi_p(x)
\)
for all $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
Thus for each $f\in L^2(\varphi)$, we have
\begin{align}
  \label{semicomp1}
  f
  = \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
  , \quad \text{in~} L^2(\varphi).
\end{align}
For each function $f\in L^2(\varphi)$, define the order of $f$ as
\[
  \kappa_f
  := \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\]
which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
In particular, the order of any constant non-zero function is zero.
Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
For $p\in \mathbb{Z}_+^d$, define
\[
  H_t^p
  := e^{-(\alpha-|p|b)t}X_t(\phi_p), \qquad t\geq 0.
\]
We will write $H^0_t$ as $H_t$.
For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} the following. 
\begin{equation}\label{eq:Hinfty}
\begin{minipage}{0.9\textwidth}
	For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
	Futhermore, if $\alpha \tilde \beta>|p|b$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
\end{minipage}
\end{equation}
We will write $H^0_\infty$ as $H_\infty$.

{\color{red}Let us also recall some results from \cite{RenSongSunZhao2019Stable} before we formulate our main theorem.}
Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{align}
  \label{eq: polynomial growth function}
  \mathcal{P}
  := \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
\end{align}
It is clear that $\mathcal{P} \subset L^2(\varphi)$. 
Define 
\begin{equation}
\begin{minipage}{0.9\textwidth}
	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
	\\ and $ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
\end{minipage}
\end{equation}
Define a semigroup
\begin{align}
\label{eq:I:R:1}
T_t f
:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p
,\quad t\geq 0, f\in \mathcal P,
\end{align}
and a family of functional
\begin{align}
\label{eq:I:R:2}
m_t[f]
:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx
, \quad 0 \leq t< \infty, f\in \mathcal P.
\end{align}
We have shown in \cite[Lemma 2.6 and Propsoition 2.7]{RenSongSunZhao2019Stable} that,
\begin{equation} \label{eq:I:R:3}
\begin{minipage}{0.9\textwidth}
for each {\color{red}$f\in \mathcal P$}, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function
$
\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,
$
where
\begin{equation}
m[f]
:= \begin{cases}
\lim_{t\to \infty} m_t[f], &
f \in \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l, \\
\lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l.
\end{cases}
\end{equation}
\end{minipage}
\end{equation}
Furthermore, we proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
\begin{equation}\label{eq:oldResult}
\begin{minipage}{0.9\textwidth}
if $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_c\setminus\{0
\}$ and $f_\mathrm l \in \mathcal C_l\setminus\{0\}$, then under $\mathbb {\widetilde P}_\mu$,
\begin{equation}
\begin{split}
&e^{-\alpha t}\|X_t\| \xrightarrow[t\to \infty]{\text{a.s.}} H_\infty;
\quad \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s};
\quad \frac{X_t(f_\mathrm c)}{\|t X_t\|^{1-\tilde \beta} } \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm c}; 
\\&\frac{X_t(f_\mathrm l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{1-\tilde \beta}}
\xrightarrow[t\to \infty]{d}
\zeta^{-f_\mathrm l}.
\end{split}
\end{equation}
\end{minipage}
\end{equation}

	The main contribution of this note is to show that the convergences in \eqref{eq:oldResult} are \emph{asymptotic independent} in the following sense.

\begin{thm}
	\label{thm:M}
	If $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_c\setminus\{0
\}$ and $f_\mathrm l \in \mathcal C_l\setminus\{0\}$, then under $\mathbb {\widetilde P}_\mu$,
	\begin{align}
	&S(t):=\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{1-\tilde \beta}}\Bigg)
	\\&\xrightarrow[t\rightarrow \infty]{d}({\color{red}\widetilde H_\infty},\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
	\end{align}
	where ${\color{red}\widetilde H_\infty}$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$; $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are $(1+\beta)$-stable random variables given by \eqref{eq:I:R:3}; $\widetilde H_\infty$,  $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
\end{thm}

As a corollary of this theorem, we have {\color{red} central limit theorems for $X_t(f)$ for all $f\in \mathcal P$.}

\begin{cor} Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P\setminus\{0\}$. Let {\color{red} $f=f_\mathrm s + f_\mathrm c + f_\mathrm l$ be the unique decomposition of $f$} with $f_\mathrm s \in \mathcal C_s$, $f_\mathrm c \in \mathcal C_c$ and $f_\mathrm l \in \mathcal C_l$.
Then under $\widetilde {\mathbb{P}}_{\mu}$, it holds that
\begin{enumerate}
\item  {\color{red}if $f_\mathrm c=0$}, then
\[
    \frac{ X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} }{\|X_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d}
     \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l};
\]
\item  {\color{red}if $f_\mathrm c\neq0$}, then
\[
  \frac{ X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} }{\|tX_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d}\zeta^{f_\mathrm c}.
\]
\end{enumerate}
{\color{red} Here, $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent $(1+\beta)$-stable random variables given by \eqref{eq:I:R:3}.}
\end{cor}

\section{Proofs of main results}
\label{proofs of main results}
In this section, we will prove the main result of this paper.
For simplicity, we will write $\mathbb{\widetilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in this section.

\subsection{Preliminaries}

The following  elementary analysis result will play an important role in this paper.

\begin{lem}\label{ineq: analysis}
There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
\[
    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
\]
\end{lem}
\begin{proof}
   Note that
\[
  \lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
\]
{\color{red}Using} this and continuity, we get that there exists $C_1>0$ such that for all {\color{red}$|y|\geq 1$},
\[
  |(1+y)^{1+\beta}-y^{1+\beta}-1|\leq C_1 |y|^{\beta}.
\]
{\color{red} Note that if $x = 0$ or $y= 0$, then the desired result is trivial. So we only have to consider the case that $x \neq 0$ and $y \neq 0$.}
{\color{red} In this case}, {\color{red}if $|x|\geq |y|$}, we have
\[
|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq |y|^{1+\beta}\Big(|(1+\frac{x}{y})^{1+\beta}-(\frac{x}{y})^{1+\beta}-1|\Big)\leq C_1|y||x|^{\beta};
\]
and {\color{red} if $|x|\leq |y|$}, we have
\[
|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq |x|^{1+\beta}\Big(|(1+\frac{y}{x})^{1+\beta}-(\frac{y}{x})^{1+\beta}-1|\Big)\leq C_1|x||y|^{\beta}.
\]
Combining the above, we immediately get the desired conclusion.
\end{proof}

For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$. 	For all $t\geq 0$ and $f\in \mathcal P$, define
	\begin{align}
  	Z_t f
  	&:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,\\
  	\Upsilon^f_t
   & := \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-{\color{blue}\tilde \beta}}}.
  	\end{align}
The following corollary to  \cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of Theorem \ref{thm:M}.

\begin{cor}
  \label{cor:MI}
For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for
all $n_1,n_2 \in \mathbb Z_+$, {\color{red}$t\geq n_1+1$,} $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$ and $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$, we have 
\begin{equation}
  \label{32corollary}
  \Big|\mathbb{\widetilde{P}}_{\mu}\Big[  \Big(\prod_{k=0}^{n_1}e^{i \Upsilon^{f_k}_{t-k-1}}\Big)  \Big( \prod_{k=0}^{n_2}e^{i \Upsilon^{g_k}_{t+k} } \Big) \Big]  -  \Big(\prod_{k=0}^{n_1} e^{\langle Z_1f_k, \varphi\rangle}\Big) \Big(\prod_{k=0}^{n_2} e^{\langle Z_1g_k, \varphi\rangle}\Big) \Big|\leq C e^{-\delta (t-n_1)}.
\end{equation}
\end{cor}
\begin{proof}
	{\color{red} In this proof, let us fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $t\geq n_1 + 1$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$ and $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$.}
{\color{red} For any $k_1 \in \{-1,0,\dots,n_1\}$ and $k_2 \in \{-1,0,\dots,n_2\}$},  define
  \[
    a_{k_1,k_2}
    :=  \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big),
  \]
 where by convention {\color{red} any product with the form $\prod_{j=0}^{-1} x(j)$ takes value $1$.}
  Then for all  $k_2 \in \{0,\dots,n_2\}$, we have
\begin{align}
& \begin{multlined}
	a_{-1,k_2} - a_{-1,k_2-1}
	\color{red} = \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) 
	\\ \color{red} - \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2 - 1}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) ,
\end{multlined}
    \\ & =\frac{1}{\mathbb{P}_{\mu}(D^c)} \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big) \Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) (e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle});D^c\Big] \Big(\prod_{j=k_2+1}^{{\color{red} n_2}} e^{\langle Z_1g_j, \varphi\rangle}\Big)\\
    & = \frac{1}{\mathbb{P}_{\mu}(D^c)}  \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big)\Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) \mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}] \Big] \Big(\prod_{j=k_2+1}^{{\color{red} n_2}}e^{\langle Z_1g_j, \varphi\rangle}\Big).
\end{align}

It follows from {\color{red}\cite[Proposition 3.5]{RenSongSunZhao2019Stable}} that
  there exist $C_0,\delta_0 >0$, {\color{red} only depend on $\mu$ and $g$}, such that {\color{red} for each $k \in \{0, \dots, n_2 \}$,}
\begin{equation}
    | a_{-1,k_2} - a_{-1,k_2-1}|
    \leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}]\big|\Big]
    \leq C_0 e^{-\delta_0 (t+k_2)}.
\end{equation}
{\color{red} 
	Notice that, for any $k_1 \in \{0, \dots , n_1\}$,
	\begin{align}
	&a_{k_1-1,-1} - a_{k_1,-1}
	\\ & \begin{multlined}
	=  \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) - {}
	\\ \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
	\end{multlined}
	\\& =  \mathbb{\widetilde{P}}_{\mu}\Big[ \big(e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle} \big) \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
	\\& \begin{multlined}
	=  \frac{1}{\mathbb P_\mu(D^c)} \mathbb{P}_{\mu}\Big[ \mathbb P_\mu\big[\big(e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle} \big) ; D^c \big| \mathscr F_{t-k_1 - 1}\big] \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \times {}
	\\ \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
	\end{multlined}
	\end{align}
}
	Therefore,  there exist $C_1,\delta_1 >0$, {\color{red} only depend on $\mu$ and $f$, such that for any $k_1 \in \{0,\dots,n_1\}$,}
\begin{align}
    | a_{k_1-1,-1} - a_{k_1,-1}|
    & \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{f_{k_1}}_{t-k_1-1}}-e^{\langle Z_1f_{k_1}, \varphi\rangle}; D^c|\mathscr F_{t-k_1-1}]\big|\Big]
    \leq C_1 e^{-\delta_1 (t-k_1)}.
\end{align}

  Therefore, there exist $C,\delta >0$ {\color{red} only depend on $f,g$ and $\mu$, such that }
  \begin{align}
    \text{LHS of \eqref{32corollary}}
    & = \left|a_{-1,n_2}-a_{n_1,-1}\right|
      \leq \sum_{k=0}^{n_1}\left|a_{k-1,-1}-a_{k,-1}\right|+\sum_{k=0}^{n_2}\left|a_{-1,k}-a_{-1,k-1}\right|\\
     & \leq \sum_{k=0}^{n_1} C_1 e^{-\delta_1 (t-k)}+\sum_{k=0}^{n_2} C_0 e^{-\delta_0 (t+k)}
      \leq C e^{- \delta (t-n_1)}.
      \qedhere
  \end{align}
\end{proof}

\subsection{Proof of Theorem \ref{thm:M}}
\label{sec: main}
In this subsection, we always fix {\color{red} $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_s\setminus\{0\}$,  $f_\mathrm c\in \mathcal C_c\setminus\{0\}$, $f_\mathrm l\in \mathcal C_l\setminus\{0\}$} and $t_0>1$ large enough, so that $\lceil t-\ln t\rceil \leq \lfloor t \rfloor - 1$ for all $t\geq t_0$.
	For any random variable $Y$ with finite mean, we define $\mathcal I_r^t Y:= \mathcal I_r^t [Y, \mu] := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_r]$ where $0 \leq r \leq t <\infty.$
	For each $t\geq t_0$, we have the following decomposition.
		{\color{blue} \tt Maybe here we can simplify the notation, by allowing $r<0$, and by using $\lceil \cdot \rceil$.}
  \begin{multline}
    \label{eq:PM:CLTS:1}
     \|X_t\|^{\tilde \beta - 1}  X_t(f_\mathrm s)
     = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
    := \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}  \|X_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s) \Big)\\
    + \Big(  \|X_t\|^{\tilde \beta - 1} \mathcal I_0^{t-\lfloor t \rfloor} X_t(f_\mathrm s)   + \sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor-1} \|X_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s) \Big) + ( \|X_t\|^{\tilde \beta - 1}X_0(P_t^\alpha f_\mathrm s) ),
  \end{multline}
  \begin{multline}
    \label{eq:PM:CLTS:2}
     \|tX_t\|^{\tilde \beta - 1}  X_t(f_\mathrm c)
     = I^{f_\mathrm c}_1(t) + I^{f_\mathrm c}_2(t) + I^{f_\mathrm c}_3(t)
    := \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}  \|tX_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c) \Big)\\
    + \Big(  \|tX_t\|^{\tilde \beta - 1} \mathcal I_0^{t-\lfloor t \rfloor} X_t(f_\mathrm c)   + \sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor-1} \|tX_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c) \Big) + ( \|tX_t\|^{\tilde \beta - 1}X_0(P_t^\alpha f_\mathrm c) ),
  \end{multline}
and
 \begin{align}
    & \frac{X_t(f_\mathrm l) - \sum_{p\in \mathcal N} \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}H_\infty^p}{\|X_t\|^{1- \tilde \beta}}
      = \sum_{p\in \mathcal N}\frac{ \langle f_\mathrm l,\phi_p\rangle_\varphi [X_t(\phi_p) - e^{(\alpha - |p|b)t}H_\infty^p]}{\|X_t\|^{1- \tilde \beta}}
    \\& = \sum_{p \in \mathcal N} \frac{\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}(H_t^p - H_\infty^p)}{\|X_t\|^{1- \tilde \beta}}
    {\color{blue}=} \sum_{k=0}^\infty \sum_{p \in \mathcal N}  \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}
    \\ &= \Big(\sum_{k = 0}^{\lfloor t^2 \rfloor}  +\sum_{k = \lceil t^2 \rceil}^\infty \Big)\Big(\sum_{p \in \mathcal N}  \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}\Big)
         = : I^{f_\mathrm l}_1(t) + I^{f_\mathrm l}_2(t),
  \end{align}
where $\mathcal N:= \{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b\}$.

Define $I_3^{f_\mathrm l}(t)=0$, $t\geq t_0$. For all $t\geq t_0$ and $j=1,2,3$, let
\(
   R_j(t):=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big)
\)
and
\begin{align}
    R_0(t)=(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t))
    :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
\end{align}
where $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.

Define
\begin{align}
R(t):=\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_\mathrm s)}{\|X_t\|^{\frac{1}{1+\beta}}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{\frac{1}{1+\beta}}},\frac{ X_t(f_\mathrm l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{\frac{1}{1+\beta}}}\Bigg).
\end{align}
The following result is a special case of Theorem \ref{thm:M}.
\begin{thm}\label{thm: II}
Under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$,
\begin{align}
R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
\end{align}
where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent $(1+\beta)$-stable random variables with characteristic functions described by \eqref{eq: charac func11}.
\end{thm}
\begin{proof}

Note that for each $t\geq t_0$,
\[
R(t)=R_0(t)+(R_1(t)-R_0(t))+R_2(t)+R_3(t).
\]

\begin{itemize}
\item[(1)] In Lemma \ref{lem: U0T}, we will show that, under $\mathbb{\widetilde{P}}_{\mu}$, $R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$.
\item[(2)] In Lemma \ref{lem: U1-U0T}, we will show that, under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, $R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d} (0,0,0)$.
\item[(3)] In Lemma \ref{lem: U2T}, we will show that, under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, $R_2(t)\xrightarrow[t\to \infty]{d}(0,0,0)$.
\item[(4)] In Lemma \ref{lem: U3T}, we will show that, under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, $R_3(t)\xrightarrow[t\to \infty]{d}(0,0,0)$.
\end{itemize}

{\color{blue}\tt Do we have this kind of result?: If $(X_t)_{t\geq 0}$ and $(Y_t)_{t\geq 0}$ are defined in a same probability space such that $X_t\xrightarrow[t\to \infty]{d}0$ and $Y_t\xrightarrow[t\to \infty]{d} 0$. Then $(X_t,Y_t) \xrightarrow[t\to \infty]{d} (0,0)$. If we do, then maybe (2)-(4) above are trivial.}

Combining these, we immediately get the conclusion of the theorem. {\color{blue}\tt Maybe we want to mention Slutsky's theorem here?}
\end{proof}

\begin{lem}\label{lem: U0T}

Under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$,
 $R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent $(1+\beta)$-stable random variables with characteristic function described by \eqref{eq: charac func11}.
\end{lem}
\begin{proof}
Since $\Upsilon_t^f$ is linear in $f$, for each $t>t_0$,
\[
\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
\sum_{j=s,c,l}I_0^{f_j}(t)\Big)\Big]
= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_c)}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_l}\Big)\Big].
\]
Using Corollary \ref{cor:MI} with $f=\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_c$ and $g = -\tilde{f}_l$, we get that there exist $C_1,\delta_1 > 0$ such that
  \begin{align}
    &\Big|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
    \sum_{j=s,c,l}I_0^{f_j}(t)\Big)\Big]
    -\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c)), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_l),\varphi\rangle\Big)\Big|\\
    &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)},
    \quad t\geq t_0.
  \end{align}
Next, we claim that
\begin{align}
\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c)), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_l),\varphi\rangle\Big) =
\prod_{j=s,c,l}\exp(m[f_j]).
\end{align}
 Then we have
 $\mathbb{\widetilde{P}}_{\mu} [e^{i \sum_{j=s,c,l}I^{f^j}_0(t)} ]
 \xrightarrow[t\to \infty]{}  \prod_{j=s,c,l}\exp(m[f_j])$.
Since $I_0^{f_j}(t)$, $j=s,c,l$, is linear in $f_j$, replacing $f_j$ with $\theta_j f_j$, we immediately get the desired result.

Now we prove the above claim.

 Recall that  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
  Using \eqref{eq:I:R:2} and the fact that $\varphi(x)dx$ is the invariant distribution of the semigroup $(P_t)_{t\geq 0}$, we get that for each $n\in \mathbb Z_+$,
  \begin{align}
    \label{eq:PM:CLTS:2a}
    & \sum_{k=0}^n \langle Z_1 T_{k} (-\tilde f_\mathrm l), \varphi \rangle
      = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha ((iP_{1 - u}^\alpha T_k \tilde f_\mathrm l)^{1+\beta}), \varphi\rangle ~du
    \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle  (iP_{1 - u}^\alpha T_{k}\tilde f_\mathrm l)^{1+\beta}, \varphi \rangle ~du
    \\& = \sum_{k=0}^n \int_0^1 \langle  (iT_{k+ u} f_\mathrm l)^{1+\beta}, \varphi\rangle~du
    = \int_0^{n+1} \langle  (iT_{u} f_\mathrm l)^{1+\beta}, \varphi\rangle~du = m_{n+1}[-f_\mathrm l].
  \end{align}
Therefore, we have
\[
\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_l),\varphi\rangle\Big) = \lim_{t\rightarrow \infty}\exp(m_{\lfloor t^2 \rfloor+1}[-f])=\exp(m[-f]).
\]

Similarly, for each $f\in \mathcal C_s  \oplus \mathcal C_c$ and $n\in \mathbb Z_+$.
  \begin{align}
    & \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
    = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha ((-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle ~du
    \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle  (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle ~du
    \\& = \sum_{k=0}^n \int_0^1 \langle  (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle~du
    = \int_0^{n+1} \langle  (-iT_{u} f)^{1+\beta}, \varphi\rangle~du = m_{n+1}[f],
  \end{align}
where $\tilde f=e^{\alpha(\tilde \beta - 1)} f$.
Therefore, for any $t\geq t_0$,
\[
{\color{red}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle }
=\int_0^{\lceil t-\ln t \rceil}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle du.
\]
Note that for each {\color{red}$u\geq 0$}, $T_uf_\mathrm c=f_\mathrm c$. 
According to Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, {\color{red}there exist $\delta> 0$ and $h\in \mathcal P$, (only depend on $f_\mathrm s$), such that for each $u\geq 0$,}
 $|T_uf_\mathrm s|\leq e^{-\delta u}h$.

{\color{red}According to Lemma \ref{ineq: analysis}, there exist $C>0$, (independent of the chose of $f_\mathrm s$ and $f_\mathrm c$), such that for each $u\geq 0$ and $t\geq 0$,}
\begin{align}
  &|(-i(T_uf_\mathrm s+t^{\tilde{\beta}-1}T_uf_\mathrm c))^{1+\beta}-(-iT_uf_\mathrm s)^{1+\beta}-(-it^{\tilde{\beta}-1}T_uf_\mathrm c)^{1+\beta}|
  \\& \color{red} = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
  \\&\leq {\color{red} C}(t^{-\frac{\beta}{1+\beta}}|T_uf_\mathrm s||T_uf_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}|T_uf_\mathrm s|^{\beta}|T_uf_\mathrm c|)\\
&\leq {\color{red}C}(t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|),
\end{align}
which means that
\begin{align}
&\Big|{\color{red} \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)}-m_{\lceil t-\ln t \rceil}[f_\mathrm s]-\frac{1}{t}m_{\lceil t-\ln t \rceil}[f_\mathrm c]\Big|\\
&{\color{blue}\leq} C_1\int_0^{\lceil t-\ln t \rceil}(t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|)du {\color{blue}\xrightarrow{t\rightarrow \infty} 0.}
\end{align}
Combining this with \eqref{eq:I:R:3}, we get that
\[
\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big) {\color{red} = \exp\{ m[f_\mathrm s]+m[f_\mathrm c]\}.}
\]
Thus the claim is valid.
\end{proof}

\begin{lem}\label{lem: U1-U0T}
Under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$,
 $R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d}0$.
\end{lem}
\begin{proof}
It follows from \cite[Lemma 3.4.3]{Durrett2010Probability} that for $t\geq t_0$,
\[
\Big|\widetilde {\mathbb P}_{\mu}\Big[\exp\Big(i
\sum_{j=\mathrm s,\mathrm c,\mathrm l}(I_{1}^{f_j}(t) - I_0^{f_j}(t))\Big)
 - 1\Big]\Big| \leq  \sum_{k=0}^{\lfloor t-\ln t \rfloor}(\widetilde {\mathbb {P}}_\mu[|Y^s_{t,k}|] + \widetilde {\mathbb {P}}_\mu[|Y^c_{t,k}|] )+ \sum_{k=0}^{\lfloor t^2 \rfloor} \widetilde {\mathbb {P}}_\mu[|Y^l_{t,k}|]
\]
 where
 \begin{align}
 &Y^s_{t,k} := \exp\Big(i(\|X_t\|^{\tilde{\beta}-1}\mathcal I_{t-k-1}^{t-k}X_t(f_\mathrm s) - \Upsilon_{t-k-1}^{T_{k}\widetilde {f_\mathrm s}})\Big) - 1, \\
 &Y^c_{t,k} := \exp\Big(i(\|tX_t\|^{\tilde{\beta}-1}\mathcal I_{t-k-1}^{t-k}X_t(f_\mathrm c) - \Upsilon_{t-k-1}^{T_{k}\widetilde {f_\mathrm c}})\Big) - 1,\\
&Y^l_{t,k} := \exp\Big(i(\widetilde{\Upsilon}_{t,k} - \Upsilon_{t+k}^{-T_{k}\widetilde {f_\mathrm l}})\Big) - 1,\\
&\widetilde{\Upsilon}_{t,k}=\|X_t\|^{\tilde{\beta}-1}\Big( \sum_{p\in \mathcal N}\langle f_\mathrm l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)t}(H_{t+k}^p-H_{t+k+1}^p)\Big).
\end{align}
  We claim that there exist $C_1, \delta_1>0$ such that
\begin{align}
 \widetilde {\mathbb {P}}_\mu[|Y^j_{t,k}|]
 \leq C_1e^{-\delta_1 (t-k)}, \quad  t\geq t_0, k \in \mathbb Z_+ \text{~satisfying~} k\leq t-1,
  j=\mathrm s,\mathrm c,
\end{align}
and
\[
 \widetilde {\mathbb {P}}_\mu[|Y^l_{t,k}|] \leq C_1e^{-\delta_1 t}, \quad t\geq t_0, k \in \mathbb Z_+.
\]
  Then there exists $C_2>0$ such that for all $t>t_0$, we have
$$
\big|\widetilde {\mathbb P}_{\mu}\left[\exp\left(i\sum_{j=s,c,l}(I_{1}^{f_j}(t) - I_0^{f_j}(t))\right) - 1\right]\big| \leq C_2(t^{-\delta_1}+(1+t^2)e^{-\delta_1 t})
$$
which, combined with the fact that
$I^{f_j}_1(t) - I^{f_j}_0(t)$, $j=s,c,l$, is linear in $f_j$, completes the proof of this lemma.

  We now show the claim above in the following steps.
  First we choose $\gamma\in(0, \beta)$ close enough to $\beta$ so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$,
  and that there exist $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
  For all $0<r<t$, we define
\[
\mathcal{D}_{t,r} :=\{|H_t-H_{r}|\leq  e^{-\eta r}, H_{r}> 2e^{-\eta' r}\}.
\]
 \emph{Step 1.} We show that there exist $C_{1.1},\delta_{1.1} >0$ such that
$\mathbb{\widetilde{P}}_{\mu} \big[ \mathcal{D}^c_{t,r} \big] \leq C_{1.1} e^{-\delta_{1.1} r}$ for all $0<r<t$.

 It follows from \cite[Proposition 2.10 \& Lemma 3.3 with $|p|=0$]{RenSongSunZhao2019Stable} and Chebyshev's inequality that there exist $C_{1.1}', \delta_{1.1}'>0$ such that for all
  $0<r<t$,
  \begin{align}
    & \mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,r}^c)
    \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{r}| > e^{-\eta r})+\mathbb{\widetilde{P}}_{\mu}(H_{r}\leq 2e^{-\eta'r}) \\
    & \leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta r}\mathbb{P}_{\mu}[|H_t-H_r|] +  \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_r\leq 2e^{-\eta'r}; D^c) \\
    & \leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta r}\|H_t - H_r\|_{\mathbb P_\mu; 1+\gamma} + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_r\leq 2e^{-\eta'r}) \\
    & \leq C'_{1.1} e^{-(\alpha \tilde \gamma - \eta)r}+C'_{1.1} e^{-\delta'_{1.1}r}.
  \end{align}
  \emph{Step 2.} We show that there exist $C_{2.1},\delta_{2.1} > 0$ such that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, it holds that $ \mathbb{\widetilde{P}}_{\mu} [|Y^s_{t,k}|] \leq  C_{2.1} e^{-\delta_{2.1} (t-k)}$.

  Note that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $. Therefore for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$,
  \begin{align}
    \label{eq:gammafunction11}
    \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm s}
    = \frac{X_{t-k}(T_{k} \tilde  f_\mathrm s) - X_{t -k-1}(P_1^\alpha T_{k} \tilde f_\mathrm s)}{\|X_{t-k-1}\|^{1-\tilde \beta}}
    = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f_\mathrm s)}{\|e^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
  \end{align}
  Since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have  for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$,
  \begin{align}
    \label{eq: control of Ykt}
    \mathbb{\widetilde{P}}_{\mu}[|Y^s_{t,k}|;\mathcal{D}_{t,t-k-1}]
    & \leq \mathbb{\widetilde{P}}_{\mu}\Big[|\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s) | \cdot \Big| \| e^{\alpha(k+1)}X_{t-k-1}\| ^{ \tilde \beta - 1} - \|X_t\|^{ \tilde \beta - 1}\Big|; \mathcal D_{t,t-k-1}\Big] \\
    & \leq  e^{\alpha(\tilde \beta - 1)t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}X_t(f_\mathrm s)|\cdot K_{t,k}\big],
  \end{align}
  where
  \[
    K_{t,k}
   := \Big| \frac {(H_t)^{1- \tilde \beta} - (H_{t-k-1})^{1 - \tilde \beta}} {(H_t)^{1 - \tilde \beta}
   (H_{t-k-1})^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t,t-k-1}}.
  \]
  Note that, since $\eta' < \eta$, we have almost surely on $\mathcal D_{t,t-k-1}$,
  \begin{align}
    H_t
    & \geq H_{t-k-1}- e^{-\eta (t-k-1)}
      \geq 2e^{-\eta'(t-k-1)}-e^{-\eta(t-k-1)}
      \geq e^{-\eta'(t-k-1)}.
  \end{align}
  Therefore, for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, almost surely  on $\mathcal D_{t,t-k-1}$,
  \begin{align}
   & \Big|(H_t)^{1- \tilde \beta}-(H_{t-k-1})^{1- \tilde \beta}\Big|
      \leq (1- \tilde \beta) \max \{ (H_t)^{-\tilde \beta }, (H_{t-k-1})^{ -\tilde \beta} \} | H_t - H_{t-k-1} | \\
    & \leq (1- \tilde \beta ) \max\{e^{\eta' (t-k-1)}, \frac{1}{2}e^{\eta'(t-k-1)}\}^{\tilde \beta} e^{-\eta(t-k-1)}  \leq (1- \tilde \beta) e^{-(\eta - \eta') (t-k-1)}
  \end{align}
  and $ |(H_t)^{1 - \tilde \beta} (H_{t-k-1})^{ 1 - \tilde \beta}| \geq 2^{\frac{1}{1+\beta}} e^{-2\eta'(t-k-1)}$.
  Thus, there exists $C_{2.1}'> 0$ such that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, almost surely
  \begin{align}
    K_{t,k}
    \leq C_{2.1}' e^{-(\eta - 3\eta')(t-k-1)}.
  \end{align}
  Now, by \cite[Lemma 2.13]{RenSongSunZhao2019Stable}, there exists $C''_{2.1}>0$ such that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$,
  \begin{align}
    & \mathbb{\widetilde{P}}_{\mu} [|Y^s_{t,k}| ; \mathcal{D}_{t,t-k-1} ]
    \leq C_{2.1}' e^{\alpha (\tilde \beta - 1)t} \mathbb{\widetilde{P}}_{\mu} [ | \mathcal{I}_{t-k-1}^{t-k}X_t(f_\mathrm s)| ] e^{-(\eta - 3\eta')(t-k-1)} \\
    & \leq \frac{C_{2.1}' } {\mathbb{P}_{\mu}(D^c)} e^{ \alpha (\tilde \beta - 1)t} \|\mathcal{I}_{t-k-1}^{t-k} X_t(f_\mathrm s)\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta - 3\eta')(t-k - 1)} \\
    & \leq C_{2.1}'' e^{\alpha(\tilde \beta - \tilde \gamma)t} e^{ (\alpha \tilde \gamma - \kappa_f b)k} e^{-(\eta - 3\eta')(t-k)}
     \leq C_{2.1}'' e^{\alpha(\tilde \beta - \tilde \gamma)(t-k)} e^{-(\eta - 3\eta')(t-k)}.
  \end{align}
  In the last inequality, we used the fact that $\alpha \tilde \beta < \kappa_{f_\mathrm s} b$. Combining the fact that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, $\mathbb{\widetilde{P}}_{\mu} [|Y^s_{t,k}| ; \mathcal{D}^c_{t,t-k-1} ]\leq 2\mathbb{\widetilde{P}}_{\mu} [ \mathcal{D}^c_{t,t-k-1} ]\leq 2 C_{1,1}e^{-\delta_{1.1}(t-k-1)}$, we get the desired result.

 \emph{Step 3.} We show that there exist $C_{3.1},\delta_{3.1} > 0$ such that for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$, $ \mathbb{\widetilde{P}}_{\mu}[|Y^c_{t,k}|] \leq  C_{3.1} e^{-\delta_{3.1} (t-k)}.$

  Note that for $f\in \mathcal C_c$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f$. Therefore for all $t>t_0$ and $k\in \mathbb Z_+$ satisfying $k\leq t-1$,
  \[
    t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c}
    = \frac{X_{t-k}(T_{k} \tilde f_\mathrm c) - X_{t -k-1}(P_1^\alpha T_{k} \tilde f_\mathrm c)}{\|t X_{t-k-1}\|^{1-\tilde \beta}}
    = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f_\mathrm c)}{\|te^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
  \]
  The rest is similar to Step 2.
  We omit the details.

 \emph{Step 4.} We show that there exist $C_{4.1}, \delta_{4.1}>0$ such that for all $k \in \mathbb Z_+$ and $t\geq t_0$, we have $\widetilde {\mathbb {P}}_\mu[|Y^l_{t,k}|]\leq C_{4.1}e^{- \delta_{4.1} t}$.

 Note that for all $k \in \mathbb Z_+$ and $t\geq t_ 0$,
  \begin{align}
    & \Upsilon_{t+k}^{-T_k\tilde f_\mathrm l}
      = \frac{X_{t+k}(P^\alpha_1T_k\tilde f_\mathrm l) - X_{t+k+1}(T_k \tilde f_\mathrm l)}{\|X_{t+k}\|^{1 - \tilde \beta}}
    \\& = \sum_{p\in \mathcal N}
    \langle\tilde f_\mathrm l,\phi_p\rangle_\varphi e^{-(\alpha \tilde \beta - |pb|)k}\frac{ X_{t+k}(P_1^\alpha \phi_p) - X_{t+k+1}(\phi_p)}{\|X_{t+k}\|^{1 - \tilde \beta}}
    \\& = \sum_{p\in \mathcal N}
    \langle f_\mathrm l,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t}\frac{H_{t+k}^p-H_{t+k+1}^p }{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}}.
  \end{align}
  Therefore for all $k\in \mathbb Z_+$ and $t\geq t_0$,
  \begin{align}
    &|Y^l_{t,k}| \mathbf 1_{\mathcal D_{t+k,t}}
      \leq \Big( \sum_{p\in \mathcal N}|\langle f_\mathrm l,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)\mathbf 1_{\mathcal D_{t+k,t}}
    \\ &= \Big( \sum_{p\in \mathcal N}|\langle f_\mathrm l,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big)e^{\alpha (\tilde \beta - 1)t} K'_{t,k}
    \\ &= \Big( \sum_{p\in \mathcal N}|\langle f_\mathrm l,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) K'_{t,k},
  \end{align}
  where
  \[
    K'_{t,k}
        := \Big| \frac {(H_t)^{1- \tilde \beta} - (H_{t+k})^{1 - \tilde \beta}} {(H_t)^{1 - \tilde \beta} (H_{t+k})^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t+k,t}}.
  \]
  Similar to Step 2, we can get that for all $k\in \mathbb Z_+$ and $t\geq t_0$, almost surely $K'_{t,k} \leq C_{4.1}'' e^{- (\eta - 3\eta')t}$.
  It follows from this and \cite[Lemma 3.3]{RenSongSunZhao2019Stable} that there exists $C'''_{4.1}>0$ such that for all $k\in \mathbb Z_+$ and $t\geq t_0$,
  \begin{align}
    & \widetilde{\mathbb P}_\mu[|Y^l_{t,k}|; \mathcal D_{t+k,t}]
      \leq \mathbb P_\mu(D)^{-1}\mathbb P_\mu[ |Y^l_{t,k}| ;\mathcal D_{t+k,t} ]
    \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{4.1}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} |\langle f_\mathrm l,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} \mathbb P_\mu[| H_{t+k}^p-H_{t+k+1}^p |]
    \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{4.1}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} |\langle f_\mathrm l,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} \| H_{t+k}^p-H_{t+k+1}^p \|_{\mathbb P_\mu; 1+\gamma}
    \\&\leq  \mathbb P_{\mu}(D)^{-1} C_{4.1}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal N} |\langle f_\mathrm l,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} e^{-(\alpha \tilde \gamma - |p|b)(t+k)} \\
    &  \leq  C_{4.1}''' e^{- (\eta - 3\eta') t} e^{(\alpha \tilde \beta - \alpha \tilde \gamma)t}.
  \end{align}
 Combining this with the fact that, for all $t>t_0$ and $k\in \mathbb Z_+$,  $\mathbb{\widetilde{P}}_{\mu} [|Y^l_{t,k}| ; \mathcal{D}^c_{t+k,t} ]\leq 2\mathbb{\widetilde{P}}_{\mu} [ \mathcal{D}^c_{t+k,t} ]\leq 2 C_{1,1}e^{-\delta_{1.1}t}$, we get the desired result.
\end{proof}

\begin{lem}\label{lem: U2T}
Under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$,
$R_2(t)\xrightarrow[t\to \infty]{d}0$.
\end{lem}
\begin{proof}
 Define $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to
 \cite[Proposition 2.10]{RenSongSunZhao2019Stable}, there exist $C_1, \delta_1>0$ such that
  \begin{align}
    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_1(t^{-\delta_1 t}+e^{-\delta_1 t})
    , \quad t\geq t_0.
  \end{align}
  Therefore,
  \begin{align}
    \label{Theorem123}
    |\mathbb{\widetilde{P}}_{\mu}[e^{i
    \sum_{j=s,c,l}I^{f_j}_2(t)}-1;\mathcal{E}^c_t]|
    \leq 2\mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
    \leq 2C_1(t^{-\delta_1}+e^{-\delta_1 t}),
    \quad t\geq t_0.
  \end{align}
On the other hand,
\[
   |\mathbb{\widetilde{P}}_{\mu} [ (e^{i
      \sum_{j=s,c,l}I^{f_j}_2(t)}-1);\mathcal{E}_t]|
    \leq \sum_{j=s,c,l}\widetilde{\mathbb P}_{\mu}[|I^{f_j}_2(t)|\mathcal{E}_t],
\quad t\geq t_0.
\]
We claim  $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_j}_2(t)|;\mathcal{E}_t]=0$, $j=s,c,l$. Then combining this with \eqref{Theorem123}, we get $\lim_{t\rightarrow \infty}\mathbb{\widetilde{P}}_{\mu}[e^{i \sum_{j=s,c,l}I^{f_j}_2(t)}-1] = 0$.
Since $I_2^{f_j}(t)$, $j=s,c,l$, is linear in $f_j$, replacing $f_j$ with $\theta_j f_j$, $\theta_j \in \mathbb R$, we immediately get the desired result in this step.

   We now show the claim above in the following steps.
Fix a $\gamma \in (0,\beta)$ close enough to $\beta$ so that $\alpha(\tilde{\beta}-\tilde{\gamma})\leq \frac{1}{2}(1-\tilde{\beta})$ and $\alpha\tilde{\gamma}>|p|b$ for all $p\in \mathcal N$.

\emph{Step 1.} We show that $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_\mathrm s}_2(t)|;\mathcal{E}_t]=0$.

  Since $\kappa_{f_\mathrm s} b -\alpha \tilde \gamma > \alpha (\tilde \beta - \tilde \gamma)$, we can choose $\epsilon >0$ small enough so that $q:=\kappa_{f_\mathrm s}b- \alpha \tilde \gamma  > \alpha (\tilde \beta - \tilde \gamma) + \epsilon $.

	According to \cite[Lemma 2.13]{RenSongSunZhao2019Stable}, there exist $C_2',C_2''>0$ such that for each $t\geq t_0 >1$,
  \begin{align}
    & \mathbb{\widetilde{P}}_{\mu} [ |I^{f_\mathrm s}_2(t)|;\mathcal{E}_t] \\
    & \leq  ( t^{-1/2}e^{\alpha t} )^{\tilde \beta - 1}\Big(\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu} [| \mathcal{I}_{t-k-1}^{t-k} X_t(f_\mathrm s) |] + \mathbb{\widetilde{P}}_{\mu}[| \mathcal{I}_{0}^{t-\lfloor t\rfloor} X_t(f_\mathrm s)|]\Big) \\
    & \leq  ( t^{-1/2}e^{\alpha t} )^{\tilde \beta - 1}\Big(\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k} X_t(f_\mathrm s) \|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} X_t(f_\mathrm s)\|_{\mathbb P_\mu;1+\gamma}\Big) \\
    & \leq C_2't^{\frac{1-\tilde{\beta}}{2}} e^{\alpha (\tilde \beta - \tilde \gamma)t}\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor}  e^{(\alpha\tilde \gamma-\kappa_{f_\mathrm s} b)k}
      \leq C_2''t^{\frac{1-\tilde{\beta}}{2}} e^{(q-\epsilon) t}\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor}  e^{-q k}
    \\ & \leq C_2'''t^{\frac{1-\tilde{\beta}}{2}} e^{q(t - \lfloor t - \ln t\rfloor-1)}e^{-\epsilon t}
         \leq C_2'''t^{\frac{1-\tilde{\beta}}{2}} t^q e^{- \epsilon t}.
  \end{align}
The desired result in this step now follows immediately.

\emph{Step 2.} We show that $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_\mathrm c}_2(t)|;\mathcal{E}_t]=0$.

It follows from \cite[Lemma 2.13]{RenSongSunZhao2019Stable} that there exist $C_3',C_3''>0$ such that for each $t\geq t_0$,
  \begin{align}
     &\mathbb{\widetilde{P}}_{\mu} [ |I^{f_\mathrm c}_2(t);{\mathcal{E}_t}] \\
    & \leq  (t^{\frac{1}{2}} e^{\alpha t} )^{\tilde \beta - 1}\Big(\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu} [| \mathcal{I}_{t-k-1}^{t-k} X_t(f_\mathrm c) |] + \mathbb{\widetilde{P}}_{\mu}[| \mathcal{I}_{0}^{t-\lfloor t\rfloor} X_t(f_\mathrm c)|]\Big) \\
    & \leq C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - 1)t}\Big(\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k} X_t(f_\mathrm c) \|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} X_t(f_\mathrm c)\|_{\mathbb P_\mu;1+\gamma}\Big) \\
    & \leq C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)t}\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor}  e^{(\alpha\tilde \gamma-\kappa_{f_\mathrm c} b)k}
      = C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - \tilde \gamma) t}\sum_{k=\lfloor t-\ln t \rfloor+1}^{\lfloor t \rfloor}  e^{-\alpha (\tilde \beta -\tilde \gamma) k}
    \\ & \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)(t - \lfloor t - \ln t\rfloor-1)}
         \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} t^{\alpha (\tilde \beta - \tilde \gamma)}.
  \end{align}
  From this, we immediately get the desired result in this step.

\emph{Step 3.} We will show that $\lim_{t\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|I^{f_\mathrm l}_2(t)|;\mathcal{E}_t]=0$.

 It follows from \cite[Lemma 3.3]{RenSongSunZhao2019Stable} that there exist $C_4',C_4''>0$ and $\delta_3'>0$ such that
  \begin{align}
    &\widetilde {\mathbb {P}}_\mu[ | I_{2}^{f_\mathrm l}(t)|; \mathcal {E}_t]
      \leq \sum_{k = \lfloor t^2\rfloor+1}^\infty \widetilde {\mathbb {P}}_\mu[ |\widetilde {\Upsilon}_{t,k}|; \mathcal {E}_t]
    \\ & \leq \mathbb P_\mu(D^c)^{-1} \sum_{k = \lfloor t^2\rfloor+1}^\infty \sum_{p \in \mathcal N} |\langle f_\mathrm l,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t}\mathbb {P}_\mu\Big[\frac{ |H_{t+k}^p - H_{t+k+1}^p|}{\|X_t\|^{1- \tilde \beta}}; \mathcal E_t\Big]
    \\ & \leq \mathbb P_\mu(D^c)^{-1} (t^{-1/2}e^{\alpha t})^{\tilde{\beta}-1} \sum_{k = \lfloor t^2\rfloor+1}^\infty \sum_{p \in \mathcal N} |\langle f_\mathrm l,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t}\|H_{t+k}^p - H_{t+k+1}^p\|_{\mathbb P_\mu; 1+\gamma}
    \\ & \leq C_4' (t^{-1/2}e^{\alpha t})^{\tilde{\beta}-1} \sum_{k = \lfloor t^2\rfloor+1}^\infty \sum_{p \in \mathcal N} |\langle f_\mathrm l,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t} e^{- (\alpha \tilde \gamma - |p|b)(t+k)}
    \\ & = C_4''t^{\frac{1-\tilde{\beta}}{2}} e^{ \alpha (\tilde \beta - \tilde \gamma) t }e^{- \delta'_3 t^2},
  \end{align}
 which completes the proof of this step.
\end{proof}

\begin{lem}\label{lem: U3T}
 $R_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$..
\end{lem}
\begin{proof}
\emph{Step 1.} We claim that $I^{f_\mathrm s}_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
  In fact, if for all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, we define
\begin{equation}
\label{eq:Q}
  	Q_\kappa f
  	:= \sup_{t\geq 0} e^{\kappa b t}|P_t f|,
  	\qquad  Q f
  	:= Q_{\kappa_f}f.
\end{equation}
	Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$. Thus,  we have
  \begin{align}
    & |I^{f_\mathrm s}_3(t)|
      \leq \frac{X_0(|P^\alpha_tf_\mathrm s|)}{\|X_t\|^{1 - \tilde \beta }}
      \leq \frac{e^{\alpha t - \kappa_{f_\mathrm s} b t}X_0(Qf_\mathrm s)}{(e^{\alpha t} H_t)^{1 - \tilde \beta}}
      = e^{(\alpha \tilde \beta - k_{f_\mathrm s}b)t} H_t^{\tilde \beta - 1} X_0(Qf_\mathrm s)
      \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
  \end{align}

  \emph{Step 2.} Similar to Step 1, we can show that $I^{f_\mathrm c}_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
  We omit the details.
Since $I_3^{f_\mathrm l}(t)=0$, the desired result follows immediately.
\end{proof}

\begin{proof}[Proof of Theorem Theorem \ref{thm:M}]
 We first recall some facts about weak convergence which will be used later. For $f:\mathbb R^d\mapsto \mathbb R$, let
 $$
 \|f\|_L:=\sup_{x\neq y}\frac{|f(x)-f(y)|}{|x-y|}
 $$
 and $\|f\|_{BL}:= \|f\|_{\infty}+\|f\|_L. $
 For any {\color{red}probability distributions} $\mu_1$ and $\mu_2$ on $\mathbb R^d$, define
\[
  d(\mu_1,\mu_2):=\sup\Big\{\Big|\int fd\mu_1-\int f d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
\]
Then $d$ is a metric. It follows from \cite[Theorem 11.3.3]{Dudley2002} that the topology generated by $d$ is equivalent to the weak convergence topology.

Using the definition, we can easily see that, if $\mu_1$ and $\mu_2$ are the distributions of two $\mathbb R^d $-valued random variables $X$ and $Y$ respectively, {\color{red} defined in same probability space} then
\begin{align}\label{ineq: distribution control}
  d(\mu_1,\mu_2) \leq \mathbb E|X-Y|.
\end{align}
Recall that $S(t)$ is defined in {\color{blue}the display before Theorem \ref{thm:M}.}
Now for all $f_\mathrm s\in \mathcal C_s $, $f_\mathrm c \in \mathcal C_c$, $f_\mathrm l \in \mathcal C_l$ and
$r,t>0$, let

\begin{align}
  S(t,r):=\Big(e^{-\alpha t}\|X_t\|,& \|X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_\mathrm s), \|(t+r)X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_\mathrm c),\\
& \|X_{t+r}\|^{\tilde{\beta}-1}(X_{t+r}(f_\mathrm l)-\sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}\langle f_\mathrm l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)(t+r)}H_{\infty}^p )\Big),
\end{align}
and
\begin{align}
\widetilde{S}(t,r)= \Big(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0\Big).
\end{align}
Then $S(t+r)=S(t,r)+\widetilde{S}(t,r)$.

\emph{Step 1.} For each $\mu\in \mathcal M_c(\mathbb R^d)$, $f_\mathrm s\in \mathcal C_s$,$f_\mathrm c\in \mathcal C_c$ and $f_\mathrm l\in \mathcal C_l$, under $\mathbb P_{\mu}(\cdot|D^c)$, we have
\[
S(t,r)\xrightarrow[r\rightarrow \infty]{d}\widetilde{S}(t):=\Big(e^{-\alpha t}\|X_t\|,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}\Big),
\]
where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent $(1+\beta)$-stable random variables with characteristic functions described by \eqref{eq: charac func11}. Moreover,  $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent of $e^{-\alpha t}\|X_t\|$.

For each $\theta,\theta_s,\theta_c,\theta_l\in \mathbb R$ and $r,t>0$, denote the characteristic function of  $S(t,r)$ under $\mathbb P_{\mu}(\cdot|D^c)$ by $k(\theta,\theta_s,\theta_c,\theta_l,r,t)$, {\color{red}then by \eqref{eq:Hinfty} and bounded convergence theorem} we have,
\begin{align}
   &k(\theta,\theta_s,\theta_c,\theta_l,r,t)\
   =\widetilde{\mathbb P}_{\mu}\Big[\exp\Big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_s,\theta_c,\theta_l,r,t,\infty)\Big)\Big]\\
  &=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_s,\theta_c,\theta_l,r,t,u)\Big);D^c\Big],
\end{align}
where
\begin{align}
 &A(\theta_s,\theta_c,\theta_l,r,t,u)=i\theta_s\|X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_\mathrm s)+ i\theta_c \|(t+r)X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_\mathrm c)\\
&+i\theta_l \|X_{t+r}\|^{\tilde{\beta}-1}\Big(X_{t+r}(f_\mathrm l)-\sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}\langle f_\mathrm l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)(t+r)}H_{u}^p\Big),\quad r+t<u\leq \infty.
\end{align}
Note that the non-extinction event $D^c=\{\|X_r\|>0, r\geq 0\}=D_{\leq t}\cup D_{\geq t}$, where $D_{\leq t}=\{\|X_r\|>0, 0\leq r\leq t\}$ and $D_{\geq t}=\{\|X_r\|>0, r\geq t\}$. 
{\color{blue} \tt Maybe we want to mention $\mathbf 1_{D^c} = \mathbf 1_{D\leq t} \mathbf 1_{D\geq t}$ here?}
By the Markov property and the dominated convergence theorem, we get
\begin{align}
  & k(\theta,\theta_s,\theta_c,\theta_l,r,t)\\
&=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big(i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}} \mathbb P_{\mu}\Big[\exp\Big(A(\theta_s,\theta_c,\theta_l,r,t,u)\Big)\mathbf 1_{D_{\geq t}}\Big|\mathscr F_t\Big]\Big]\\
&=\lim_{u\rightarrow\infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big( i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}}\mathbb P_{X_t}\Big[\exp\Big(A(\theta_s,\theta_c,\theta_l,r,0,u-t)\Big)\mathbf 1_{D^c}\Big]\Big]\\
&=\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big( i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}}\mathbb P_{X_t}(D^c)\widetilde{\mathbb P}_{X_t}\Big[\exp\Big(A(\theta_s,\theta_c,\theta_l,r,0,\infty)\Big)\Big]\Big]
\end{align}
It follows from Theorem \ref{thm: II} and the {\color{red}bounded convergence theorem,}
\begin{align}
   k(\theta,\theta_s, \theta_c,\theta_l,r,t)& \xrightarrow{r\to \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big(i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}}\mathbb P_{X_t}(D^c)\Big]
   \prod_{j=s,c,l}\exp\Big(m[\theta_j f_j]\Big)\\
&=\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\theta e^{-\alpha t}\|X_t\|\Big)\Big]
\prod_{j=s,c,l}\exp\Big(m[\theta_j f_j]\Big).
\end{align}
The desired result of this step now follows immediately. {\color{blue} \tt Maybe we can use linearity to simplify the argument here?}

\emph{Step 2.} For all $r,t>0$, let $\mathcal D(r)$ and $\mathcal D(r,t)$ be the distributions of $S(r)$ and $S(t,r)$ under $\mathbb P_{\mu}(\cdot|D^c)$, let $ \widetilde{\mathcal D}(t)$ and $\mathcal D$ be the distributions of {\color{red}$\widetilde{S}(t)$} and $(H^*,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$ under $\mathbb P_{\mu}(\cdot|D^c)$. Then using \eqref{ineq: distribution control} and \cite[Lemma 3.3]{RenSongSunZhao2019Stable}, we have that for each $\gamma\in (0,\beta)$, there exist constant $C>0$ such that,
\begin{align}
 \varlimsup_{r\rightarrow \infty}d(\mathcal D(t+r),\mathcal D)&\leq \varlimsup_{r\rightarrow \infty}[d(\mathcal D(t+r),\mathcal D(t,r))+d(\mathcal D(t,r),\widetilde{\mathcal D}(t))+d(\widetilde{\mathcal D}(t),\mathcal D)]\\
&\leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|e^{-\alpha t}\|X_t\|-e^{-\alpha (t+r)}\|X_{t+r}\||]+0+\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]\\
&\leq \varlimsup_{r\rightarrow \infty}\mathbb P_{\mu}(D^c)^{-1}(\|H_t-H_{t+r}\|_{\mathbb P_{\mu};1+\gamma}+\|H_t-H_{\infty}\|_{\mathbb P_{\mu};1+\gamma})\\
&\leq Ce^{-\frac{\gamma}{1+\gamma}t}.
\end{align}
Therefore, using the definition of $\varlimsup_{s\rightarrow \infty}$, we know that,
\begin{align}
 &\varlimsup_{r\rightarrow \infty}d(\mathcal D(r),\mathcal D) 
 = {\color{red} \varlimsup_{t\to \infty}}\varlimsup_{r\rightarrow \infty}d(\mathcal D(t+r),\mathcal D)
\leq \varlimsup_{t\rightarrow \infty}Ce^{-\frac{\gamma}{1+\gamma}t} = 0.
\end{align}
The desired result now follows immediately.
\end{proof}
{\tt\color{red} Maybe we should cleanup the references?}

\begin{thebibliography}{10}

\bibitem{AdamczakMilos2015CLT}
  R. Adamczak and P. Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
  Electron. J. Probab. \textbf{20} (2015), no. 42, 35 pp.

\bibitem{Asmussen76Convergence}
  S. Asmussen, \emph{Convergence rates for branching processes},
  Ann. Probab.  \textbf{4} (1976), no. 1, 139--146.

\bibitem{AsmussenHering1983Branching}
  S. Asmussen and H. Hering, \emph{Branching processes},
  Progress in Probability and Statistics, 3. Birkh\"{a}user Boston, Inc., Boston, MA, 1983.

\bibitem{Athreya1969Limit}
  K. B. Athreya,
  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {I}. {T}he case of an eigenvector linear functional},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{12} (1969), 320--332.

\bibitem{Athreya1969LimitB}
  K. B. Athreya,
  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {II}. {T}he case of an arbitrary linear functional},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{13} (1969), 204--214.

\bibitem{Athreya1971Some}
  K. B. Athreya,
  \emph{Some refinements in the theory of supercritical multitype {M}arkov branching processes},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{20} (1971), 47--57.

\bibitem{Bertoin}
J. Bertoin,
\emph{L\'evy processes}.
Cambridge Tracts in Mathematics, 121. Cambridge
University Press, 1996.

\bibitem{BRY}
J. Bertoin, B. Roynette and M. Yor,
\emph{Some connections between (sub)critical branching mechanisms and Bernstein functions}.
arXiv:0412322.

\bibitem{ChenRenWang2008An-almost}
  Z.-Q. Chen, Y.-X. Ren, and H. Wang,
  \emph{An almost sure scaling limit theorem for {D}awson-{W}atanabe superprocesses},
  J. Funct. Anal. \textbf{254} (2008), no. 7, 1988--2019.

 \bibitem{ChenRenSongZhang2015Strong-law}
   Z.-Q. Chen, Y.-X. Ren, R. Song, and R. Zhang,
   \emph{Strong law of large numbers for supercritical superprocesses under second moment condition},
   Front. Math. China \textbf{10} (2015), no. 4, 807--838.

 \bibitem{ChenRenYang2019Skeleton}
   Z.-Q. Chen, Y.-X. Ren, and T. Yang,
   \emph{Skeleton decomposition and law of large numbers for supercritical superprocesses},
   Acta Appl. Math. \textbf{159} (2019), 225--285.

\bibitem{Dudley2002}
  R. M. Dudley
\emph{Real Analysis and Probability},
  Cambridge University Press, 2002.

 \bibitem{Durrett2010Probability}
   R. Durrett,
   \emph{Probability: theory and examples},
   Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.

\bibitem{Dynkin1993Superprocesses}
  E. B. Dynkin,
  \emph{Superprocesses and partial differential equations},
  Ann. Probab. \textbf{21} (1993), no. 3, 1185--1262.

\bibitem{EckhoffKyprianouWinkel2015Spines}
  M. Eckhoff, A. E. Kyprianou, and M. Winkel,
  \emph{Spines, skeletons and the strong law of large numbers for superdiffusions},
  Ann. Probab. \textbf{43} (2015), no. 5, 2545--2610.

\bibitem{Englander2009Law}
  J. Engl\"{a}nder,
  \emph{Law of large numbers for superdiffusions: the non-ergodic case},
  Ann. Inst. Henri Poincar\'{e} Probab. Stat. \textbf{45} (2009), no. 1, 1--6.

\bibitem{EnglanderWinter2006Law}
  J. Engl\"{a}nder and A. Winter,
  \emph{Law of large numbers for a class of superdiffusions},
  Ann. Inst. H. Poincar\'{e} Probab. Statist. \textbf{42} (2006), no. 2, 171--185.

\bibitem{EnglanderTuraev2002A-scaling}
  J. Engl\"{a}nder and  D. Turaev,
  \emph{A scaling limit theorem for a class of superdiffusions},
  Ann. Probab. \textbf{30} (2002), no. 2, 683--722.

\bibitem{Heyde1970A-rate}
  C. C. Heyde,
  \emph{A rate of convergence result for the super-critical {G}alton-{W}atson process},
  J. Appl. Probability \textbf{7} (1970), 451--454.

\bibitem{Heyde1971Some}
  C. C. Heyde,
    \emph{some central limit analogues for supercritical {G}alton-{W}atson processes},
  J. Appl. Probability \textbf{8} (1971), 52--59.

\bibitem{HeydeBrown1871An-invariance}
  C. C. Heyde and B. M. Brown,
  \emph{An invariance principle and some convergence rate results for branching processes},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete, \textbf{20} (1971), 271--278.

\bibitem{HeydeLeslie1971Improved}
  C. C. Heyde and J. R. Leslie,
  \emph{Improved classical limit analogues for {G}alton-{W}atson processes with or without immigration},
  Bull. Austral. Math. Soc. \textbf{5} (1971), 145--155.

\bibitem{IksanovKoleskoMeiners2018Stable-like}
  A. Iksanov, K. Kolesko, and M. Meiners,
  \emph{Stable-like fluctuations of {B}gins' martingales},
  Stochastic Process. Appl. (2018).

\bibitem{Janson2004Functional}
  S. Janson,
  \emph{Functional limit theorems for multitype branching processes and generalized {P}\'{o}lya urns},
  Stochastic Process. Appl. \textbf{110} (2004), no. 2, 177--245.

\bibitem{KestenStigum1966Additional}
  H. Kesten and B. P. Stigum,
  \emph{Additional limit theorems for indecomposable multidimensional {G}alton-{W}atson processes},
  Ann. Math. Statist. \textbf{37} (1966), 1463--1481.

\bibitem{KestenStigum1966A-limit}
  H. Kesten and B. P. Stigum,
  \emph{A limit theorem for multidimensional {G}alton-{W}atson processes},
  Ann. Math. Statist. \textbf{37} (1966), 1211--1223.

\bibitem{KouritzinRen2014A-strong}
  M. A. Kouritzin, and Y.-X. Ren,
  \emph{A strong law of large numbers for super-stable processes},
  Stochastic Process. Appl. \textbf{121} (2014), no. 1, 505--521.

\bibitem{Kyprianou2014Fluctuations}
  A. E. Kyprianou,
  \emph{Fluctuations of {L}\'{e}vy processes with applications},
    Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.

\bibitem{Li2011Measure-valued}
  Z. Li,
  \emph{Measure-valued branching {M}arkov processes},
  Probability and its Applications (New York). Springer, Heidelberg, 2011.

\bibitem{LiuRenSong2009Llog}
  R.-L. Liu, Y.-X. Ren, and R. Song,
  \emph{{$L\log L$} criterion for a class of superdiffusions},
  J. Appl. Probab. \textbf{46} (2009), no. 2, 479--496.

\bibitem{LiuRenSong2013Strong}
  R.-L. Liu, Y.-X. Ren, and R. Song,
  \emph{Strong law of large numbers for a class of superdiffusions},
  Acta Appl. Math. \textbf{123} (2013), 73--97.

\bibitem{MarksMilos2018CLT}
  R. Marks and P. Mi{\l}o{\'s},
  \emph{C{LT} for supercritical branching processes with heavy-tailed branching law},
  arXiv:1803.05491.

\bibitem{MetafunePallaraPriola2002Spectrum}
  G. Metafune, D. Pallara, and E. Priola,
  \emph{Spectrum of {O}rnstein-{U}hlenbeck operators in {$L^p$} spaces with respect to invariant  measures},
  J. Funct. Anal. \textbf{196} (2002), no. 1, 40--60.

\bibitem{Milos2012Spatial}
  P. Mi{\l}o{\'s},
  \emph{Spatial central limit theorem for supercritical superprocesses},
  J. Theoret. Probab. \textbf{31} (2018), no. 1, 1--40.

\bibitem{RenSongSun2017Spine}
  Y.-X. Ren, R. Song, and Z. Sun,
  \emph{Spine decompositions and limit theorems for a class of critical superprocesses},
  Acta Appl. Math. (2019).

\bibitem{RenSongSun2018Limit}
  Y.-X. Ren, R. Song, and Z. Sun,
  \emph{Limit theorems for a class of critical superprocesses with stable branching},
  arXiv:1807.02837.

\bibitem{RenSongSunZhao2019Stable}
Y.-X. Ren, R. Song, Z. Sun and J. Zhao,
\emph{Stable central limit theorems for super Ornstein-Uhlenbeck processes},
Elect. J Probab., \textbf{24} (2019), no. 141, 1--42.

\bibitem{RenSongZhang2014Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for super {O}rnstein-{U}hlenbeck processes},
  Acta Appl. Math. \textbf{130} (2014), 9--49.

\bibitem{RenSongZhang2014CentralB}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical branching {M}arkov processes},
  J. Funct. Anal. \textbf{266} (2014), no. 3, 1716--1756.

\bibitem{RenSongZhang2015Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical superprocesses},
  Stochastic Process. Appl. \textbf{125} (2015), no. 2, 428--457.

\bibitem{RenSongZhang2017Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical branching nonsymmetric {M}arkov processes},
  Ann. Probab. \textbf{45} (2017), no. 1, 564--623.

\bibitem{RenSongZhang2017Functional}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Functional central limit theorems for supercritical superprocesses},
  Acta Appl. Math. \textbf{147} (2017), 137--175.

\bibitem{Sato2013Levy}
  K. Sato,
  \emph{L{\'e}vy processes and infinitely divisible distributions},
  Translated from the 1990 Japanese original. Revised by the author. Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.

\bibitem{SchillingSongVondravcek2010Bernstein}
  R. L. Schilling, R. Song, and Z. Vondra\v{c}ek,
  \emph{Bernstein functions.}
  Theory and applications. Second edition. De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2012.

\bibitem{SteinShakarchi2003Complex}
  E. M. Stein and R. Shakarchi, \emph{Complex analysis},
  Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.

\bibitem{Wang2010An-almost}
  L. Wang, \emph{An almost sure limit theorem for super-{B}rownian motion},
  J. Theoret. Probab. \textbf{23} (2010), no. 2, 401--416.

\end{thebibliography}
\end{document}

### 2020-05-23 supCLT-ind8.tex
add supCLT-ind8.tex

%supCLT-ind1.tex ?/?/? by Jianjie
%supCLT-ind2.tex ?/?/? by ?
%supCLT-ind3.tex 03/05/2020 by Renming
%supCLT-ind4.tex 11/05/2020 by Zhenyao
%supCLT-ind5.tex 14/05/2020 by Yanxia
%supCLT-ind6.tex 16/05/2020 by JianJie
%supCLT-ind7.tex 17/05/2020 by Renming
%supCLT-ind8.tex 20/05/2020 by Zhenyao
\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-1.5in}
\calclayout
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
%\usepackage[backref]{hyperref}
\usepackage{hyperref}
%\usepackage[inline]{showlabels}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title
[stable CLT for super-OU processes]
{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II}
\author
[Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
{Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address{
  Yan-Xia Ren \\
  LMAM School of Mathematical Sciences \& Center for Statistical Science \\
  Peking University \\
  Beijing 100871, P. R. China}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}
\address{
  Renming Song \\
  Department of Mathematics \\
  University of Illinois at Urbana-Champaign \\
  Urbana, IL 61801, USA}
\email{rsong@illinois.edu}
\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
\address{
  Zhenyao Sun \\
  Faculty of Industrial Engineering and Management\\
  Technion, Israel Institute of Technology \\
  Haifa 3200003, Israel}
\email{zhenyao.sun@gmail.com}
\address{
  Jianjie Zhao \\
  School of Mathematical Sciences \\
  Peking University \\
  Beijing 100871, P. R. China}
\email{zhaojianjie@pku.edu.cn}

\begin{abstract}
This paper is a continuation of our recent paper (Elect. J. Probab. \textbf{24} (2019), no. 141)
and is devoted to the  asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth
in three different regimes. However, we were not able to prove 
%a central limit theorem for
central limit theorems for
$X_t(f) $ for {\it all} functions $f$ of polynomial growth. 
In this note, we show that the limit stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
\end{abstract}
\subjclass[2010]{60J68, 60F05}
\keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}
\maketitle
%\section{Introduction}
\section{Introduction and main result}
%\subsection{Main result}
\label{subsec:M}
Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
\begin{align}
  Lf(x)
  = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x)
  , \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
\end{align}
where $\sigma > 0$ and $b > 0$ are constants.
Let $\psi$ be a function on $\mathbb R_+$ of the form
\begin{align}
  \psi(z)
  =- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(\mathrm dy)
  , \quad  z \in \mathbb R_+,
\end{align}
where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)\pi(\mathrm dy)< \infty$.
$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
Denote by $\mathcal M(\mathbb R^d)$ 
($\mathcal M_c(\mathbb R^d)$)
the space of all finite Borel measures (of compact support) on $\mathbb R^d$.
Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ 
($\mathcal B(\mathbb R^d, \mathbb R_+)$)
the space of all $\mathbb R$-valued 
($\mathbb R_+$-valued)
Borel functions on $\mathbb R^d$.
For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$,
 write $\mu(f)= \int f(x)\mu(\mathrm dx)$
and $\langle f, g\rangle = \int f(x)g(x) \mathrm dx$ whenever the integrals make sense.
We say a real-valued Borel function 
%$f:(t,x)\mapsto f(t,x)$ 
$f$
on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty. $
For any $\mu \in \mathcal M(\mathbb R^d)$, we write $\|\mu\| = \mu(1)$.
For any $\sigma$-finite signed measure $\mu$, denote by $|\mu|$ the total variation measure of $\mu$.

We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a \emph{$(\xi, \psi)$-superprocess}, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{align}
  \label{eq: def of V_t}
  \mathbb{P}_{\mu}[e^{-X_t(f)}]
  = e^{-\mu(V_tf)}
  , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{align}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{align}
  V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) ) \mathrm ds\Big]
	= \Pi_x [f(\xi_t)]
  , \quad x\in \mathbb R^d, t\geq 0.
\end{align}	
	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.

	There have been many central limit theorem type results for branching processes, branching diffusions and superprocesses, under the second moment condition.
	See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
	Some spatial central limit theorems for supercritical branching OU processes with binary branching mechanism were proved 
	in \cite{AdamczakMilos2015CLT}, and some 
	spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
	These two papers made connections between central limit theorems and branching rate regimes.
	The results of \cite{Milos2012Spatial} were extended and refined in \cite{RenSongZhang2014Central}.
		Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.

There are also  central  limit theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment. For earlier
papers, \cite{Heyde1971Some, Asmussen76Convergence}. 	Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} established some spatial central limit theorems in the small and critical branching rate regimes, for 
some supercritical branching OU processes with a special stable offspring distribution.
In \cite{RenSongSunZhao2019Stable}, we
established stable central limit theorems for 
super-OU processes $X$ with branching mechanisms $\psi$ satisfying the following two assumptions.

\begin{asp}[Grey's condition]
	\label{asp: Greys condition}
	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1} \mathrm dz < \infty$.
\end{asp}

\begin{asp}
	\label{asp: branching mechanism}
  There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
  \begin{align}
    \int_{(1,\infty)}y^{1+\beta +\delta}\Big|\pi(\mathrm dy)-\frac{\eta \mathrm dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
  \end{align}
for some $\delta > 0$.
\end{asp}

It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
$$D :=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}$$
is non-trivial with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$.
In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$, where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
Assumption \ref{asp: branching mechanism} says that $\psi$ is ``not too far away'' from $\widetilde \psi(z) := - \alpha z + \eta z^{1+\beta}$ near $0$, see \cite[Remark 1.3]{RenSongSunZhao2019Stable}.
It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
In \cite[Lemma 2.3]{RenSongSunZhao2019Stable}, we have shown  that,
under Assumption \ref{asp: branching mechanism},
 $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y \pi(\mathrm dy) < \infty. $
In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
	Note that $\delta$ is not uniquely determined by $\pi$.

The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (see \cite{MetafunePallaraPriola2002Spectrum} for more details).
We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
Define
\(
P^{\alpha}_t f(x)
  := e^{\alpha t} P_t f(x)
  = \Pi_x [e^{\alpha t}f(\xi_t)]
\)
for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$ in the sense that
\(
  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)
\)
for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
\begin{align}
  \varphi(x)\mathrm dx
  :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx
\end{align}
which is a   symmetric multivariate Gaussian distribution.
Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{align}
  \langle f_1, f_2 \rangle_{\varphi}
  := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) \mathrm dx, \quad f_1,f_2 \in L^2(\varphi).
\end{align}
Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
The \emph{Hermite polynomials} are defined by
\begin{align}
  \mathcal H_p(x)
  :=(-1)^{|p|}e^{|x|^2} \partial_p e^{-|x|^2}
  , \quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
\end{align}
It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
\begin{align}
  \phi_p(x)
  := \frac{1}{\sqrt{ p! 2^{|p|} }} \mathcal H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big)
  , \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{align}
In other words,
\(
  P_t\phi_p(x)
  = e^{-b|p|t}\phi_p(x)
\)
for all $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
Thus for each $f\in L^2(\varphi)$, we have
\begin{align}
  \label{semicomp1}
  f
  = \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
  , \quad \text{in~} L^2(\varphi).
\end{align}
For each function $f\in L^2(\varphi)$, define the order of $f$ as
\[
  \kappa_f
  := \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\]
which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
In particular, the order of any constant non-zero function is zero.
For $p\in \mathbb{Z}_+^d$, define
\[
  H_t^p
  := e^{-(\alpha-|p|b)t}X_t(\phi_p), \qquad t\geq 0.
\]
We will write $H^0_t$ as $H_t$.
For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} the following.
\begin{equation}\label{eq:Hinfty}
\begin{minipage}{0.9\textwidth}
	For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
	Futhermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
\end{minipage}
\end{equation}
We will write $H^0_\infty$ as $H_\infty$.

Let us also recall some results from \cite{RenSongSunZhao2019Stable} before we formulate our main theorem.
Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{align}
  \mathcal{P}
  := \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
\end{align}
It is clear that $\mathcal{P} \subset L^2(\varphi)$.
Define
\begin{equation}
\begin{minipage}{0.9\textwidth}
	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}, \quad \mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
	\\ $ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
\end{minipage}
\end{equation}
Define a semigroup
\begin{align}
T_t f
:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p
,\quad t\geq 0, f\in \mathcal P,
\end{align}
and a family of functionals
\begin{align}\label{eq:M.13}
m_t[f]
:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx
, \quad 0 \leq t< \infty, f\in \mathcal P.
\end{align}
For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write
$\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
We have shown in \cite[Lemma 2.6 and Propsoition 2.7]{RenSongSunZhao2019Stable} that,
\begin{equation} \label{eq:I:R:3}
\begin{minipage}{0.9\textwidth}
for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function
$
\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,
$
where
\begin{equation}
m[f]
:= \begin{cases}
\lim_{t\to \infty} m_t[f], &
f \in \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l, \\
\lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l.
\end{cases}
\end{equation}
\end{minipage}
\end{equation}
Furthermore, we proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
\begin{equation}\label{eq:oldResult}
\begin{minipage}{0.9\textwidth}
if $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_\mathrm c\setminus\{0
\}$ and $f_\mathrm l \in \mathcal C_\mathrm l\setminus\{0\}$, then under $\mathbb {\widetilde P}_\mu$,
\[
\begin{split}
&e^{-\alpha t}\|X_t\| \xrightarrow[t\to \infty]{\text{a.s.}} H_\infty;
\quad \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s};
\\&\frac{X_t(f_\mathrm c)}{\|t X_t\|^{1-\tilde \beta} } \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm c};
\quad\frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
\xrightarrow[t\to \infty]{d}
\zeta^{-f_\mathrm l},
\end{split}
\]
where $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$
are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; and
\[
\mathrm x_t(f) : = \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty},\quad t\geq 0, f\in \mathcal P.
\]
\end{minipage}
\end{equation}
	% The above result implies that if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f,$ and if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$,\\
	%The above result implies that if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta < \kappa_f b$, then  under $\widetilde {\mathbb P}_{\mu}$, 
%\[
	%\frac{X_t(f)}{\|X_t\|^{1-\tilde \beta} } \xrightarrow[t\to \infty]{d} \zeta^f,
%\] 
	%and if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta = \kappa_f b$,
	% then under $\mathbb{P}_{\mu}(\cdot|D^c)$,\\ 
	% $\|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^{f_c}$.
	%then under $\widetilde{\mathbb P}_\mu $, 
%\[
	%\frac{X_t(f)}{\|t X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_c}.
%\]
	The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$. 
	%A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$.
	%For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ maybe non-zero. 
	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$; and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero. 
	In \cite{RenSongSunZhao2019Stable}, we were not able to
	establish a central limit theorem in this case. We conjectured there that the limit random variables in \eqref{eq:oldResult} 
	%for $ f\in \mathcal C_\mathrm s$, $f\in \mathcal C_\mathrm c$ and $ f\in \mathcal C_\mathrm l$ are independent. 
	for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent. 
	Once this asymptotic independence is established, a central limit theorem  for $ X_t(f)$ for all $f\in  \mathcal P$ would follow.

	The main purpose of this note is to show that 
	the limit  random variables in \eqref{eq:oldResult} are independent.

\begin{thm}
	\label{thm:M}
	If $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l \in \mathcal C_\mathrm l\setminus\{0\}$, then under $\mathbb {\widetilde P}_\mu$,
	\begin{align} \label{eq:M.1}
	&S(t):=
	\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},
	%\frac{ X_t(f_\mathrm l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{1-\tilde \beta}}
	\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
	\Bigg)
	\\&\xrightarrow[t\rightarrow \infty]{d}(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
	\end{align}
	where $\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$; $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; $\widetilde H_\infty$,  $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
\end{thm}

As a corollary of this theorem, we get  central limit theorems for $X_t(f)$ for all $f\in \mathcal P$.

\begin{cor} Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P\setminus\{0\}$. Let  $f=f_\mathrm s + f_\mathrm c + f_\mathrm l$ be the unique decomposition of $f$ with $f_\mathrm s \in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$.
Then under $\widetilde {\mathbb{P}}_{\mu}$, it holds that
\begin{enumerate}
\item  if $f_\mathrm c=0$, then
\[
    %\frac{ X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} }{\|X_t\|^{1-\tilde \beta}}
    \frac{ X_t(f) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d}
    %\zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l};
     \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l},
\]
%
	where $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$  are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are independent;
\item if $f_\mathrm c\neq0$, then
\[
  %\frac{ X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} }{\|tX_t\|^{1-\tilde \beta}}
  \frac{ X_t(f) - \mathrm x_t(f)}{\|tX_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d}\zeta^{f_\mathrm c}.
\]
%
	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}.
\end{enumerate}
%Here, $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are 
%the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}.
\end{cor}

%\section{Proofs of main results}
\section{Proofs of main result}
\label{proofs of main results}

%\subsection{Preliminaries}
\subsection{A key result}
\begin{comment}
\begin{lem}\label{ineq: analysis}
There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
\[
    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
\]
\end{lem}
\begin{proof}
   Note that
\[
  \lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
\]
Using this and continuity, we get that there exists {\color{blue}$C_1>0$} such that for all $|y|\geq 1$,
\[
  |(1+y)^{1+\beta}-y^{1+\beta}-1|\leq C_1 |y|^{\beta}.
\]
 Note that if $x = 0$ or $y= 0$, then the desired result is trivial.
So we only need to consider
 the case that $x \neq 0$ and $y \neq 0$.
 In this case, if $|x|\geq |y|$, we have
\[
|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)\leq C_1|y||x|^{\beta};
\]
and  if $|x|\leq |y|$, we have
\[
	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
	\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)\leq C_1|x||y|^{\beta}.
\]
Combining the above, we immediately get the desired result.
\end{proof}
\end{comment}

% For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$. %
For every $t\geq 0$ and $f\in \mathcal P$, define
\[
  	Z_t f
  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,\quad
  	\Upsilon^f_t
   := \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
\]
Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is 
% the characteristic exponent of the limit of $\Upsilon^f_t$.
 the asymptotic characteristic exponent of $\Upsilon^f_t$.
The following corollary to  \cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of Theorem \ref{thm:M}.
%
For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$.

\begin{cor}
  \label{cor:MI}
For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for
all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1+1$, we have
\begin{equation}
  \label{32corollary}
  \Big|\mathbb{\widetilde{P}}_{\mu}\Big[  \Big(\prod_{k=0}^{n_1}e^{i \Upsilon^{f_k}_{t-k-1}}\Big)  \Big( \prod_{k=0}^{n_2}e^{i \Upsilon^{g_k}_{t+k} } \Big) \Big]  -  \Big(\prod_{k=0}^{n_1} e^{\langle Z_1f_k, \varphi\rangle}\Big) \Big(\prod_{k=0}^{n_2} e^{\langle Z_1g_k, \varphi\rangle}\Big) \Big|\leq C e^{-\delta (t-n_1)}.
\end{equation}
\end{cor}
\begin{proof}
	In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1 + 1$.
 For any $k_1 \in \{-1,0,\dots,n_1\}$ and $k_2 \in \{-1,0,\dots,n_2\}$,  define
  \[
    a_{k_1,k_2}
    :=  \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big),
  \]
where we used the convention that 
$\prod_{j=0}^{-1} =1.$
  Then for all  $k_2 \in \{0,\dots,n_2\}$, we have
\begin{align}
&a_{-1,k_2} - a_{-1,k_2-1}
\\& \begin{multlined}
	=\mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
	\\- \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2 - 1}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
\end{multlined}
	\\& \begin{multlined}
	= \frac{1}{\mathbb{P}_{\mu}(D^c)} \Big(\prod_{j=k_2+1}^{ n_2} e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
	\\ \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big) \Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) (e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle});D^c\Big] 
	\end{multlined}
	\\ \label{eq:MI.1}& \begin{multlined} 
	= \frac{1}{\mathbb{P}_{\mu}(D^c)}  \Big(\prod_{j=k_2+1}^{n_2}e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
	\\ \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big)\Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) \mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}] \Big].
	\end{multlined}
\end{align}
% It follows from \cite[Proposition 3.5]{RenSongSunZhao2019Stable} that there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$, 
	Therefore, there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$, 
  such that  for each $k_2 \in \{0, \dots, n_2 \}$,
\begin{align}
    &| a_{-1,k_2} - a_{-1,k_2-1}|
    \overset{\eqref{eq:MI.1}}\leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}]\big|\Big]
    \\&\label{eq:MI.15}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_0 e^{-\delta_0 (t+k_2)}.
\end{align}
	Notice that, for any $k_1 \in \{0, \dots , n_1\}$,
	\begin{align}
	&a_{k_1-1,-1} - a_{k_1,-1}
	\\ & \begin{multlined}
	=  \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) - {}
	\\ \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
	\end{multlined}
	\\& =  \mathbb{\widetilde{P}}_{\mu}\Big[ \big(e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle} \big) \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
	\\& \label{eq:MI.2}\begin{multlined}
	=  \frac{1}{\mathbb P_\mu(D^c)} \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) \times {}
	\\ \mathbb{P}_{\mu}\Big[ \mathbb P_\mu\big[e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle}  ; D^c \big| \mathscr F_{t-k_1 - 1}\big] \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] .
	\end{multlined}
	\end{align}
	Therefore,  there exist $C_1,\delta_1 >0$, depending only on $\mu$ and $f$, 
	such that for any $k_1 \in \{0,\dots,n_1\}$,
\begin{align}
    &| a_{k_1-1,-1} - a_{k_1,-1}|
    \overset{\eqref{eq:MI.2}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{f_{k_1}}_{t-k_1-1}}-e^{\langle Z_1f_{k_1}, \varphi\rangle}; D^c|\mathscr F_{t-k_1-1}]\big|\Big]
    \\&\label{eq:MI.25}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_1 e^{-\delta_1 (t-k_1)}.
\end{align}
  Therefore, there exist $C,\delta >0$, depending only on $f,g$ and $\mu$, such that
  \begin{align}
    &\text{LHS of \eqref{32corollary}}
    = \left|a_{-1,n_2}-a_{n_1,-1}\right|
      \leq \sum_{k=0}^{n_1}\left|a_{k-1,-1}-a_{k,-1}\right|+\sum_{k=0}^{n_2}\left|a_{-1,k}-a_{-1,k-1}\right|\\
     & \overset{\eqref{eq:MI.15},\eqref{eq:MI.25}}\leq \sum_{k=0}^{n_1} C_1 e^{-\delta_1 (t-k)}+\sum_{k=0}^{n_2} C_0 e^{-\delta_0 (t+k)}
      \leq C e^{- \delta (t-n_1)}.
      \qedhere
  \end{align}
\end{proof}

\subsection{Proof of Theorem \ref{thm:M}}
\label{sec: main}
% In this subsection, we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$,  $f_\mathrm c\in \mathcal C_\mathrm c\setminus\{0\}$, $f_\mathrm l\in \mathcal C_\mathrm l\setminus\{0\}$ and $t_0>1$ large enough, so that $\lceil t-\ln t\rceil \leq \lfloor t \rfloor - 1$ for all $t\geq t_0$.
In this subsection, we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$,  $f_\mathrm c\in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l\in \mathcal C_\mathrm l\setminus\{0\}$.
	% For any random variable $Y$ with finite mean, we define 
	 For any random variable $Y$ with finite mean under $\mathbb P_\mu$, we define 
\begin{align}
	% \mathcal I_r^t Y&:= \mathcal I_r^t [Y, \mu] := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_r], \quad 0 \leq r \leq t <\infty,
	\mathcal I_r^t Y := \mathbb P_\mu[Y|\mathscr F_{t\wedge 0}] - \mathbb P_\mu[Y|\mathscr F_{r\wedge 0}], \quad -\infty < r, t <\infty.
	%\\\mathcal I_r^t Y&:= \mathcal I_0^t [Y, \mu] := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_0], \quad r<0 \leq t <\infty.
\end{align}
	% For each $t\geq t_0$, 
	For each $t\geq 1$,
	we have the following decomposition.
  \begin{align} 
   %&\frac{X_t(f_\mathrm s)}{\|X_t\|^{1- \tilde \beta }} = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
   I^{f_\mathrm s}(t) &:= \frac{X_t(f_\mathrm s)}{\|X_t\|^{1- \tilde \beta }}  = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
    %\\ := & \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}  \|X_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s) \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]}\|X_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)   \Big)
    \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}  \Big)
   % \\& + ( \|X_t\|^{\tilde \beta - 1}X_0(P_t^\alpha f_\mathrm s) ),
   + \Big( \frac{X_0(P_t^\alpha f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}\Big),
     % & \frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}} = I^{f_\mathrm c}_1(t) + I^{f_\mathrm c}_2(t) + I^{f_\mathrm c}_3(t)
    \\ I^{f_\mathrm c}(t)&:=\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}} = I^{f_\mathrm c}_1(t) + I^{f_\mathrm c}_2(t) + I^{f_\mathrm c}_3(t)
    % \\:= &\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}  \|tX_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c) \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]}\|tX_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)\Big)\\
    % &+ ( \|tX_t\|^{\tilde \beta - 1}X_0(P_t^\alpha f_\mathrm c) ),
        \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}  \Big)    + \Big( \frac{X_0(P_t^\alpha f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}\Big),
 %\begin{align}
    %& \frac{X_t(f_\mathrm l) - \sum_{p\in \mathcal N} \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}H_\infty^p}{\|X_t\|^{1- \tilde \beta}}
      %= \sum_{p\in \mathcal N}\frac{ \langle f_\mathrm l,\phi_p\rangle_\varphi [X_t(\phi_p) - e^{(\alpha - |p|b)t}H_\infty^p]}{\|X_t\|^{1- \tilde \beta}}
    %\\& = \sum_{p \in \mathcal N} \frac{\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}(H_t^p - H_\infty^p)}{\|X_t\|^{1- \tilde \beta}}
    %= \sum_{k=0}^\infty \sum_{p \in \mathcal N}  \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}
    % \\ &= \Big(\sum_{k = 0}^{\lfloor t^2 \rfloor}  + \sum_{k = \lfloor t^2 \rfloor+1}^\infty \Big)
    %\\ &= \Big(\sum_{k\in \mathbb N \cap [0,t^2]}  + \sum_{k\in \mathbb N \cap (t^2,\infty)}   \Big)
    %\Big(\sum_{p \in \mathcal N}  \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}\Big)
     %= : I^{f_\mathrm l}_1(t) + I^{f_\mathrm l}_2(t),
  %\end{align}
  \\ I^{f_\mathrm l}(t) &:= \frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}
  = I^{f_\mathrm l}_1(t) + I^{f_\mathrm l}_2(t) + I^{f_\mathrm l}_3(t)
  \\& := \Big(\sum_{k\in \mathbb N \cap [0,t^2]} \frac{ \mathcal I_{t+k+1}^{t+k}\mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}\Big) + \Big(\sum_{k\in \mathbb N \cap (t^2,\infty)}  \frac{ \mathcal I_{t+k+1}^{t+k}\mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}\Big)+0.
  \end{align}
  %where $\mathcal N:= \{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b\}$.

	% Define $I_3^{f_\mathrm l}(t)=0$, $t\geq t_0$. 
	For every $t\geq 1$, define 
	% For all $t\geq t_0$ and $j=1,2,3$, let
	%$R_j(t):=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big)$
	%and
\begin{align}
	%
	R_j(t)&:=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big), \quad j = 1,2,3,
	\\ R(t)&:=\Bigg( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}\Bigg),
    \\R_0(t)&=(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t))
    % :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
    \\&:=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
\end{align}
where $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.

%Define
%\begin{align}
%R(t):=\Bigg( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{1-\tilde \beta}}\Bigg).
%\end{align}
%The following result is a special case of Theorem \ref{thm:M}.
%%
\begin{thm}\label{thm: II}
Under $\mathbb{\widetilde{P}}_{\mu}$,
$
R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
$
where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are
the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
\end{thm}
\begin{proof}

%Note that for each $t\geq t_0$,
Note that for each $t\geq 1$,
\[
%R(t)=R_0(t)+(R_1(t)-R_0(t))+R_2(t)+R_3(t),
R(t)=R_0(t)+(R_1(t)-R_0(t))+R_2(t)+R_3(t).
\]
%where 
Note that
$$
(R_1(t)-R_0(t))=(I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t), I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t), I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)).
$$
%$$
%R_2(t)=(I_2^{f_\mathrm s}(t), I_2^{f_\mathrm c}(t), I_2^{f_\mathrm l}(t)), \mbox{ and }R_2(t)=(I_3^{f_\mathrm s}(t), I_3^{f_\mathrm c}(t), 0).
%$$
In the proof of Theorem 1.6(1) in \cite{RenSongSunZhao2019Stable}, we proved that 
$I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
 In the proof of Theorem 1.6(2) in \cite{RenSongSunZhao2019Stable}, we proved that 
 $I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$ 
In the proof of Theorem 1.6(3) in \cite{RenSongSunZhao2019Stable}, we proved that 
$I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$ and  $I_2^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$.
Thus we have %under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, 
$R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d} (0,0,0)$, $R_2(t)\xrightarrow[t\to \infty]{d}(0,0,0)$ and
$R_3(t)\xrightarrow[t\to \infty]{d}(0,0,0)$. 
Combining the above results and using Slutsky's theorem, we only need to  show that, under $\mathbb{\widetilde{P}}_{\mu}$, 
\begin{equation}
\label{lem:UOT}R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
\end{equation} 
%\end{proof}
%
%\begin{lem}\label{lem: U0T}
%Under $\mathbb{\widetilde{P}}_{\mu}$,
 %$R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are 
%the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
%\end{lem}
%
%\begin{proof}
\\
\paragraph{\it Proof of \eqref{lem:UOT}}
Since $\Upsilon_t^f$ is linear in $f$, for each $t\geq 1$,
\[
\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
\]
Using Corollary \ref{cor:MI} with $f=\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c}$ and $g = -\tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that
% for $t>t_0$,
for every $t\geq 1$,
  \begin{align}
    &\Big|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
    -\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\Big|\\
    &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
  \end{align}
Next, we claim that
\begin{equation} \label{eq:UOT.1}
\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c)), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big) =
\prod_{j=\mathrm s,\mathrm c,\mathrm l}\exp(m[f_j]).
\end{equation}
 Then we have
\[
	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
	\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
	 \xrightarrow[t\to \infty]{} 
	 \prod_{j=\mathrm s,\mathrm c,\mathrm l}\exp(m[f_j]).
\]
% Since $I_0^{f_j}(t), j=\mathrm s,\mathrm c,\mathrm l$, is linear in $f_j$, replacing $f_j$ with $\theta_j f_j$, we immediately get the desired result.
 Since $I_0^{f_j}(t)$ are linear in $f_j\in \mathcal C_j$, replacing $f_j$ with $\theta_j f_j$, we immediately get the desired result.
%Now we prove the above claim.
\\
\paragraph*{\it Proof of \eqref{eq:UOT.1}} 
 %Recall that  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
 %Using \eqref{eq:I:R:2} and the fact that $\varphi(x)dx$ is the invariant distribution of the semigroup $(P_t)_{t\geq 0}$, we get that for each $n\in \mathbb Z_+$,
  %\begin{align}
  %\label{eq:PM:CLTS:2a}
   % & \sum_{k=0}^n \langle Z_1 T_{k} (-\tilde f_\mathrm l), \varphi \rangle
     % = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha ((iP_{1 - u}^\alpha T_k \tilde f_\mathrm l)^{1+\beta}), \varphi\rangle ~du
  %  \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle  (iP_{1 - u}^\alpha T_{k}\tilde f_\mathrm l)^{1+\beta}, \varphi \rangle ~du
  %  \\& = \sum_{k=0}^n \int_0^1 \langle  (iT_{k+ u} f_\mathrm l)^{1+\beta}, \varphi\rangle~du
 %   = \int_0^{n+1} \langle  (iT_{u} f_\mathrm l)^{1+\beta}, \varphi\rangle~du = m_{n+1}[-f_\mathrm l].
  %\end{align}
%Therefore, we have
%\[
%\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_l),\varphi\rangle\Big) = \lim_{t\rightarrow \infty}\exp(m_{\lfloor t^2 \rfloor+1}[-f])=\exp(m[-f]).
%\]
%%	
%Similarly, for all $f\in \mathcal C_\mathrm s  \oplus \mathcal C_\mathrm c$ and $n\in \mathbb Z_+$.
For every $f\in \mathcal C_\mathrm s  \oplus \mathcal C_\mathrm c$ and $n\in \mathbb Z_+$,
%  \begin{align}
 %   & \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
   % = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha ((-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle \mathrm du
    %\\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle  (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle \mathrm du
   % \\& = \sum_{k=0}^n \int_0^1 \langle  (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle \mathrm du
   % = \int_0^{n+1} \langle  (-iT_{u} f)^{1+\beta}, \varphi\rangle \mathrm du = m_{n+1}[f],
 % \end{align}
 \begin{align}
  & \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
  = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha (\eta(-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle \mathrm du
 \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle \eta (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle \mathrm du
 \\& = \sum_{k=0}^n \int_0^1 \langle \eta (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle \mathrm du
 = \int_0^{n+1} \langle  \eta (-iT_{u} f)^{1+\beta}, \varphi\rangle \mathrm du = m_{n+1}[f],
 \end{align}
where $\tilde f=e^{\alpha(\tilde \beta - 1)} f$.
% Therefore, for any $t\geq t_0$,
Therefore, for any $t\geq 1$,
\begin{equation} \label{eq:UOT.15}
\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c), \varphi\rangle
=\eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du.
\end{equation}
Note that for each $u\geq 0$, $T_uf_\mathrm c=f_\mathrm c$.
%According to
 Also note that according to
 Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, there exist $\delta> 0$ and
$h\in \mathcal P$ (depending only on $f_\mathrm s$)
such that for each $u\geq 0$,
 $|T_uf_\mathrm s|\leq e^{-\delta u}h$.
%
Let us claim the following analytical fact:
\begin{equation}\label{eq:UOT.2}
\begin{minipage}{0.9\textwidth}
	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
	\[
	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
	\]
\end{minipage}
\end{equation}
%According to Lemma \ref{ineq: analysis}, there exists $C>0$ (independent of the choices of $f_\mathrm s$ and $f_\mathrm c$)
Now for this $C>0$ it holds that for all $u\geq 0$ and $t\geq 0$,
\begin{align}
  &|(-i(T_uf_\mathrm s+t^{\tilde{\beta}-1}T_uf_\mathrm c))^{1+\beta}-(-iT_uf_\mathrm s)^{1+\beta}-(-it^{\tilde{\beta}-1}T_uf_\mathrm c)^{1+\beta}|
  \\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
  \\&\overset{\eqref{eq:UOT.2}}\leq  C(t^{-\frac{\beta}{1+\beta}}|T_uf_\mathrm s||T_uf_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}|T_uf_\mathrm s|^{\beta}|T_uf_\mathrm c|)
  \\&\label{eq:UOT.21}\leq C(t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|).
\end{align}
% which means that
This means that there exists $C_1 >0$ such that for all $t\geq 1$,
\begin{align}
&\Big|\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)-m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm s]-\frac{1}{t}m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm c]\Big|
%
\\& \begin{multlined} 
\overset{\eqref{eq:UOT.15},\eqref{eq:M.13}}\leq\Big| \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du - {}
\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du - \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|
\end{multlined}
\\ & \overset{\eqref{eq:UOT.21}}\leq C_1\int_0^{\lfloor t-\ln t \rfloor+1}\langle t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|, \varphi \rangle \mathrm du 
\\& \leq C_1 t^{-\frac{\beta}{1+\beta}} \langle h|f_\mathrm c|^{\beta},\varphi \rangle \int_0^\infty e^{-\delta u} \mathrm du + C_1 t^{-\frac{1}{1+\beta}} \langle h^\beta|f_\mathrm c|,\varphi \rangle \int_0^\infty e^{-\delta \beta u} \mathrm du
\\& \xrightarrow[t\rightarrow \infty]{} 0.
\end{align}
Combining this with \eqref{eq:I:R:3}, we get that
\begin{equation} \label{eq:UOT.4}
\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)  = \exp( m[f_\mathrm s]+m[f_\mathrm c]).
\end{equation}
%
Also note that according to the Step 1 in the Proof of Theorem 1.6.(3) in \cite{RenSongSunZhao2019Stable}, we have
\begin{equation}\label{eq:UOT.5}
\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big) =\exp(m[-f_\mathrm l]).
\end{equation}
% Thus the claim is valid.
Thus the desired claim follows from \eqref{eq:UOT.4} and \eqref{eq:UOT.5}.
%
\\
\paragraph{\it Proof of \eqref{eq:UOT.2}}
   Note that
\[
\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
\]
Using this and continuity, we get that there exists $C_1>0$ such that for all $|y|\geq 1$,
\[
|(1+y)^{1+\beta}-y^{1+\beta}-1|\leq C_1 |y|^{\beta}.
\]
Note that if $x = 0$ or $y= 0$, then the desired result is trivial.
So we only need to consider
the case that $x \neq 0$ and $y \neq 0$.
In this case, if $|x|\geq |y|$, we have
\[
|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)\leq C_1|y||x|^{\beta};
\]
and  if $|x|\leq |y|$, we have
\[
|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)\leq C_1|x||y|^{\beta}.
\]
Combining the above, we immediately get the desired result.
\end{proof}

\begin{proof}[Proof of Theorem Theorem \ref{thm:M}]
 We first recall some facts about weak convergence which will be used later. For $f:\mathbb R^d\mapsto \mathbb R$, let
 $$
 \|f\|_L:=\sup_{x\neq y}\frac{|f(x)-f(y)|}{|x-y|}
 $$
 and $\|f\|_{BL}:= \|f\|_{\infty}+\|f\|_L. $
 For any probability distributions $\mu_1$ and $\mu_2$ on $\mathbb R^d$, define
\[
  d(\mu_1,\mu_2):=\sup\Big\{\Big|\int fd\mu_1-\int f d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
\]
Then $d$ is a metric. It follows from \cite[Theorem 11.3.3]{Dudley2002} that the topology generated by $d$ is equivalent to the weak convergence topology.
Using the definition, we can easily see that, if $\mu_1$ and $\mu_2$ are the distributions of two $\mathbb R^d $-valued random variables $X$ and $Y$ respectively,
defined on same probability space then
\begin{align}\label{ineq: distribution control}
  d(\mu_1,\mu_2) \leq \mathbb E|X-Y|.
\end{align}
% Recall that $S(t)$ is defined in the display before Theorem \ref{thm:M}.
In this proof, let us fix $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l \in \mathcal C_\mathrm l\setminus\{0\}$.
Recall that $S(t)~(t\geq 0)$ is given by \eqref{eq:M.1}.
% Now for all $f_\mathrm s\in \mathcal C_\mathrm s $, $f_\mathrm c \in \mathcal C_\mathrm c$, $f_\mathrm l \in \mathcal C_\mathrm l$ and $r,t>0$, let
For every $r,t> 0$, let
\begin{align}
  %S(t,r):=\Big(e^{-\alpha t}\|X_t\|,& \|X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_\mathrm s), \|(t+r)X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_\mathrm c),\\
%& \|X_{t+r}\|^{\tilde{\beta}-1}(X_{t+r}(f_\mathrm l)-\sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}\langle f_\mathrm l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)(t+r)}H_{\infty}^p )\Big),
S(t,r):=\Big(e^{-\alpha t}\|X_t\|,& \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm c)}{\|(t+r)X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm l)-\mathrm x_{t+r}(f_\mathrm l) }{\|X_{t+r}\|^{1-\tilde{\beta}}}\Big),
\end{align}
and
\begin{align}
\widetilde{S}(t,r)= \Big(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0\Big).
\end{align}
Then $S(t+r)=S(t,r)+\widetilde{S}(t,r)$.
%
%\emph{Step 1.} For all $\mu\in \mathcal M_c(\mathbb R^d)$, $f_\mathrm s\in \mathcal C_\mathrm s$,$f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$, under $\mathbb P_{\mu}(\cdot|D^c)$, we have
%\[
%S(t,r)\xrightarrow[r\rightarrow \infty]{d}\widetilde{S}(t):=\Big(e^{-\alpha t}\|X_t\|,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}\Big),
%\]
%{\color{blue} where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
%Moreover,  $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent of the limit of $e^{-\alpha t}\|X_t\|$.}
Let us claim that
\begin{equation}\label{eq:M.3}
\begin{minipage}{0.9\textwidth}
	for each $t> 0$, under $\widetilde{\mathbb P}_{\mu}$, we have
	\[
	S(t,r)\xrightarrow[r\rightarrow \infty]{d} (\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
	\]
	where $\widetilde H_t$ has the distribution of $\{e^{-\alpha t} \|X_t\|; \widetilde {\mathbb P}_\mu\}$ and is independent of $(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$.
\end{minipage}
\end{equation}
%For all $r,t>0$, let $\mathcal D(r)$ and $\mathcal D(r,t)$ be the distributions of $S(r)$ and $S(t,r)$ under $\mathbb P_{\mu}(\cdot|D^c)$ respectively, 
For every $r,t\geq 0$, let $\mathcal D(r)$ and $\mathcal D(r,t)$ be the distributions of $S(r)$ and $S(t,r)$ under $\widetilde{\mathbb P}_{\mu}$ respectively;
%let $ \widetilde{\mathcal D}(t)$ and $\mathcal D$ be the distributions of $\widetilde{S}(t)$ and $(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$ under $\mathbb P_{\mu}(\cdot|D^c)$ respectively.
let $\widetilde{\mathcal D}(t)$ and $\mathcal D$ be the distributions of $(\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$ and $(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, respectively.
 Then for each $\gamma\in (0,\beta)$, there exist constant $C>0$
 %such that,
 such that for every $t > 0$,
\begin{align}
 &\varlimsup_{r\rightarrow \infty}d(\mathcal D(t+r),\mathcal D)
 \\& \overset{\rm Triangle~inequality}\leq \varlimsup_{r\rightarrow \infty}\Big( d\big(\mathcal D(t+r),\mathcal D(t,r)\big)+d\big(\mathcal D(t,r),\widetilde{\mathcal D}(t)\big)+d\big(\widetilde{\mathcal D}(t),\mathcal D\big)\Big)
 %
 \\&\overset{\eqref{ineq: distribution control}} \leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|S(t+r) - S(t,r)|]+ \varlimsup_{r\rightarrow \infty} d\big(\mathcal D(t,r),\widetilde{\mathcal D}(t)\big) +\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]
% \\&\leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|e^{-\alpha t}\|X_t\|-e^{-\alpha (t+r)}\|X_{t+r}\||]+0+\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]
\\&\overset{\eqref{eq:M.3}}\leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|H_t - H_{t+r}|]+\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]
 %\\&\leq \varlimsup_{r\rightarrow \infty}\mathbb P_{\mu}(D^c)^{-1}(\|H_t-H_{t+r}\|_{\mathbb P_{\mu};1+\gamma}+\|H_t-H_{\infty}\|_{\mathbb P_{\mu};1+\gamma})
 \\&\overset{\text{H\"older inequality}}\leq \varlimsup_{r\rightarrow \infty}\mathbb P_{\mu}(D^c)^{-1}(\|H_t-H_{t+r}\|_{L_{1+\gamma} (\mathbb P_\mu)}+\|H_t-H_{\infty}\|_{L_{1+\gamma} (\mathbb P_\mu)})
 %\\&\leq Ce^{-\frac{\gamma}{1+\gamma}t}.
\\&\label{eq:M.4}\overset{\text{\cite[Lemma 3.3]{RenSongSunZhao2019Stable}}}\leq C e^{-\alpha \tilde \gamma t}.
\end{align}
Therefore, 
%using the definition of $\varlimsup_{s\rightarrow \infty}$, we know that,
%%
\begin{align}
 &\varlimsup_{r\rightarrow \infty}d\big(\mathcal D(r),\mathcal D\big)
 =\varlimsup_{t\to \infty}\varlimsup_{r\rightarrow \infty}d\big(\mathcal D(t+r),\mathcal D\big)
% \leq \varlimsup_{t\rightarrow \infty}Ce^{-\frac{\gamma}{1+\gamma}t} = 0.
\overset{\eqref{eq:M.4}}\leq \varlimsup_{t\rightarrow \infty}Ce^{-\alpha \tilde \gamma t} = 0.
\end{align}
The desired result now follows immediately.
\\
\paragraph{\it Proof of \eqref{eq:M.3}}
%For all $\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l\in \mathbb R$ and $r,t>0$, denote the characteristic function of  $S(t,r)$ under $\mathbb P_{\mu}(\cdot|D^c)$ by $k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)$,
For every $r,t >0 0$, let 
\[
\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l\in \mathbb R \mapsto k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
\]
be the characteristic function of  $S(t,r)$ under $\widetilde{\mathbb P}_{\mu}$.
% then by \eqref{eq:Hinfty} and the bounded convergence theorem we have,
Then for each $\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l\in \mathbb R$ and $r,t> 0$,
\begin{align}
&k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
=\widetilde{\mathbb P}_{\mu}\big[\exp\big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,\infty)\big)\big]\\
&\label{eq:M.5}\overset{\text{Bounded convergence}}=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\big[\exp\big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\big);D^c\big],
\end{align}
where for each $u\in [0,\infty]$,
\begin{align}
&A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)
\\&:=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + i\theta_\mathrm c \frac{X_{t+r}(f_\mathrm c)}{\|(t+r)X_{t+r}\|^{1-\tilde{\beta}}} + i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l)- \mathbb P_\mu[\mathrm x_{t+r}(f_\mathrm l)|\mathscr F_u]}{\|X_{t+r}\|^{1-\tilde{\beta}}}
\\&\label{eq:M.6}\begin{multlined}
\overset{\eqref{eq:Hinfty}}=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + \frac{i\theta_\mathrm c}{(t+r)^{1-\tilde{\beta}}} \frac{X_{t+r}(f_\mathrm c)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + {}
\\ i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l) - \sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b} e^{(\alpha - |p|b)(t+r)} e^{-(\alpha - |p|b)u}X_u(\phi_p) }{\|X_{t+r}\|^{1-\tilde{\beta}}}.
\end{multlined}
\end{align}
%Note that $D^c=\{\|X_r\|>0, r\geq 0\}=D_{\leq t}\cap D_{> t}$,
%where $D_{\leq t}=\{\|X_r\|>0, 0\leq r\leq t\}$ and $D_{> t}=\{\|X_r\|>0, r> t\}$.
%%
Now for each $t>0$, we get
\begin{align}
& \lim_{r\to \infty}k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
%\\&=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big(i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}} \mathbb P_{\mu}\Big[\exp\Big(A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\Big)\mathbf 1_{D_{> t}}\Big|\mathscr F_t\Big]\Big]
\\&\overset{\eqref{eq:M.5}}=\lim_{r\to \infty}\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\big[\exp\{i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0} \mathbb P_{\mu}[\exp\{A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\}\mathbf 1_{D^c}|\mathscr F_t]\big]
\\&\begin{multlined}
\overset{\text{\eqref{eq:M.6}, Markov property}}=\lim_{r\to \infty}\lim_{u\rightarrow\infty}\frac{1}{\mathbb P_{\mu}(D^c)} \mathbb P_{\mu}\Bigg[\exp\{ i\theta e^{-\alpha t}\|X_t\|\}\mathbf 1_{\|X_t\|>0} \times {}
\\ \mathbb P_{X_t}\bigg[\exp\bigg\{A\bigg(\theta_\mathrm s,\theta_\mathrm c\Big(\frac{r}{t+r}\Big)^{1-\tilde \beta},\theta_\mathrm l,r,0,u-t\bigg)\bigg\}\mathbf 1_{D^c}\bigg]\Bigg]
\end{multlined}
\\&\begin{multlined}\overset{\text{Bounded convergence}}=\lim_{r\to \infty} \mathbb P_{\mu}\Bigg[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \times {}
\\\widetilde{\mathbb P}_{X_t}\bigg[\exp\bigg\{A\bigg(\theta_\mathrm s,\theta_\mathrm c\Big(\frac{r}{t+r}\Big)^{1-\tilde \beta},\theta_\mathrm l,r,0,\infty\bigg)\bigg\}\bigg]\Bigg].
\end{multlined}
\\& \overset{\text{Theorem \ref{thm: II}}}=  \mathbb P_{\mu}\Big[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \Big]\prod_{j=\mathrm s,\mathrm c,\mathrm l}\exp\{m[\theta_j f_j]\}
\\&=\widetilde{\mathbb P}_{\mu}[\exp\{i\theta e^{-\alpha t}\|X_t\|\}]
\prod_{j=\mathrm s,\mathrm c,\mathrm l}\exp\{m[\theta_j f_j]\}.
\qedhere
\end{align}
\end{proof}

\begin{thebibliography}{10}

\bibitem{AdamczakMilos2015CLT}
  R. Adamczak and P. Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
  Electron. J. Probab. \textbf{20} (2015), no. 42, 35 pp.

\bibitem{Asmussen76Convergence}
  S. Asmussen, \emph{Convergence rates for branching processes},
  Ann. Probab.  \textbf{4} (1976), no. 1, 139--146.

\bibitem{AsmussenHering1983Branching}
  S. Asmussen and H. Hering, \emph{Branching processes},
  Progress in Probability and Statistics, 3. Birkh\"{a}user Boston, Inc., Boston, MA, 1983.

\bibitem{Athreya1969Limit}
  K. B. Athreya,
  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {I}. {T}he case of an eigenvector linear functional},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{12} (1969), 320--332.

\bibitem{Athreya1969LimitB}
  K. B. Athreya,
  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {II}. {T}he case of an arbitrary linear functional},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{13} (1969), 204--214.

\bibitem{Athreya1971Some}
  K. B. Athreya,
  \emph{Some refinements in the theory of supercritical multitype {M}arkov branching processes},
  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{20} (1971), 47--57.

%
%\bibitem{Bertoin}
%J. Bertoin,
%\emph{L\'evy processes}.
%Cambridge Tracts in Mathematics, 121. Cambridge
%University Press, 1996.
%
%\bibitem{BRY}
%J. Bertoin, B. Roynette and M. Yor,
%\emph{Some connections between (sub)critical branching mechanisms and Bernstein functions}.
%arXiv:0412322.
%
%
%\bibitem{ChenRenWang2008An-almost}
%  Z.-Q. Chen, Y.-X. Ren, and H. Wang,
%  \emph{An almost sure scaling limit theorem for {D}awson-{W}atanabe superprocesses},
%  J. Funct. Anal. \textbf{254} (2008), no. 7, 1988--2019.
%
% \bibitem{ChenRenSongZhang2015Strong-law}
%   Z.-Q. Chen, Y.-X. Ren, R. Song, and R. Zhang,
%   \emph{Strong law of large numbers for supercritical superprocesses under second moment condition},
%   Front. Math. China \textbf{10} (2015), no. 4, 807--838.
%
% \bibitem{ChenRenYang2019Skeleton}
%   Z.-Q. Chen, Y.-X. Ren, and T. Yang,
%   \emph{Skeleton decomposition and law of large numbers for supercritical superprocesses},
%   Acta Appl. Math. \textbf{159} (2019), 225--285.
%
\bibitem{Dudley2002}
  R. M. Dudley
\emph{Real Analysis and Probability},
  Cambridge University Press, 2002.

% \bibitem{Durrett2010Probability}
%   R. Durrett,
%   \emph{Probability: theory and examples},
%   Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.

%\bibitem{Dynkin1993Superprocesses}
  %E. B. Dynkin,
  %\emph{Superprocesses and partial differential equations},
  %Ann. Probab. \textbf{21} (1993), no. 3, 1185--1262.
%
%\bibitem{EckhoffKyprianouWinkel2015Spines}
%  M. Eckhoff, A. E. Kyprianou, and M. Winkel,
%  \emph{Spines, skeletons and the strong law of large numbers for superdiffusions},
%  Ann. Probab. \textbf{43} (2015), no. 5, 2545--2610.
%
%\bibitem{Englander2009Law}
%  J. Engl\"{a}nder,
%  \emph{Law of large numbers for superdiffusions: the non-ergodic case},
%  Ann. Inst. Henri Poincar\'{e} Probab. Stat. \textbf{45} (2009), no. 1, 1--6.
%
%\bibitem{EnglanderWinter2006Law}
%  J. Engl\"{a}nder and A. Winter,
%  \emph{Law of large numbers for a class of superdiffusions},
%  Ann. Inst. H. Poincar\'{e} Probab. Statist. \textbf{42} (2006), no. 2, 171--185.
%
%\bibitem{EnglanderTuraev2002A-scaling}
%  J. Engl\"{a}nder and  D. Turaev,
%  \emph{A scaling limit theorem for a class of superdiffusions},
%  Ann. Probab. \textbf{30} (2002), no. 2, 683--722.
%
\bibitem{Heyde1970A-rate}
C. C. Heyde,
 \emph{A rate of convergence result for the super-critical {G}alton-{W}atson process},
  J. Appl. Probability \textbf{7} (1970), 451--454.

\bibitem{Heyde1971Some}
  C. C. Heyde,
    \emph{some central limit analogues for supercritical {G}alton-{W}atson processes},
  J. Appl. Probability \textbf{8} (1971), 52--59.

\bibitem{HeydeBrown1871An-invariance}
  C. C. Heyde and B. M. Brown,
  \emph{An invariance principle and some convergence rate results for branching processes},
 Z. Wahrscheinlichkeitstheorie und Verw. Gebiete, \textbf{20} (1971), 271--278.

\bibitem{HeydeLeslie1971Improved}
  C. C. Heyde and J. R. Leslie,
  \emph{Improved classical limit analogues for {G}alton-{W}atson processes with or without immigration},
  Bull. Austral. Math. Soc. \textbf{5} (1971), 145--155.

%\bibitem{IksanovKoleskoMeiners2018Stable-like}
%  A. Iksanov, K. Kolesko, and M. Meiners,
%  \emph{Stable-like fluctuations of {B}gins' martingales},
%  Stochastic Process. Appl. (2018).
%
%\bibitem{Janson2004Functional}
%  S. Janson,
%  \emph{Functional limit theorems for multitype branching processes and generalized {P}\'{o}lya urns},
%  Stochastic Process. Appl. \textbf{110} (2004), no. 2, 177--245.

\bibitem{KestenStigum1966Additional}
  H. Kesten and B. P. Stigum,
  \emph{Additional limit theorems for indecomposable multidimensional {G}alton-{W}atson processes},
  Ann. Math. Statist. \textbf{37} (1966), 1463--1481.

\bibitem{KestenStigum1966A-limit}
  H. Kesten and B. P. Stigum,
  \emph{A limit theorem for multidimensional {G}alton-{W}atson processes},
  Ann. Math. Statist. \textbf{37} (1966), 1211--1223.

%\bibitem{KouritzinRen2014A-strong}
%  M. A. Kouritzin, and Y.-X. Ren,
%  \emph{A strong law of large numbers for super-stable processes},
%  Stochastic Process. Appl. \textbf{121} (2014), no. 1, 505--521.
%
\bibitem{Kyprianou2014Fluctuations}
  A. E. Kyprianou,
  \emph{Fluctuations of {L}\'{e}vy processes with applications},
    Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.

\bibitem{Li2011Measure-valued}
  Z. Li,
  \emph{Measure-valued branching {M}arkov processes},
  Probability and its Applications (New York). Springer, Heidelberg, 2011.

%\bibitem{LiuRenSong2009Llog}
%  R.-L. Liu, Y.-X. Ren, and R. Song,
%  \emph{{$L\log L$} criterion for a class of superdiffusions},
%  J. Appl. Probab. \textbf{46} (2009), no. 2, 479--496.
%
%\bibitem{LiuRenSong2013Strong}
%  R.-L. Liu, Y.-X. Ren, and R. Song,
%  \emph{Strong law of large numbers for a class of superdiffusions},
%  Acta Appl. Math. \textbf{123} (2013), 73--97.

\bibitem{MarksMilos2018CLT}
  R. Marks and P. Mi{\l}o{\'s},
  \emph{C{LT} for supercritical branching processes with heavy-tailed branching law},
  arXiv:1803.05491.

\bibitem{MetafunePallaraPriola2002Spectrum}
  G. Metafune, D. Pallara, and E. Priola,
  \emph{Spectrum of {O}rnstein-{U}hlenbeck operators in {$L^p$} spaces with respect to invariant  measures},
  J. Funct. Anal. \textbf{196} (2002), no. 1, 40--60.

\bibitem{Milos2012Spatial}
  P. Mi{\l}o{\'s},
  \emph{Spatial central limit theorem for supercritical superprocesses},
  J. Theoret. Probab. \textbf{31} (2018), no. 1, 1--40.

%\bibitem{RenSongSun2017Spine}
%  Y.-X. Ren, R. Song, and Z. Sun,
%  \emph{Spine decompositions and limit theorems for a class of critical superprocesses},
%  Acta Appl. Math. (2019).
%
%\bibitem{RenSongSun2018Limit}
%  Y.-X. Ren, R. Song, and Z. Sun,
%  \emph{Limit theorems for a class of critical superprocesses with stable branching},
%  arXiv:1807.02837.
%
\bibitem{RenSongSunZhao2019Stable}
Y.-X. Ren, R. Song, Z. Sun and J. Zhao,
\emph{Stable central limit theorems for super Ornstein-Uhlenbeck processes},
Elect. J Probab., \textbf{24} (2019), no. 141, 1--42.

\bibitem{RenSongZhang2014Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for super {O}rnstein-{U}hlenbeck processes},
  Acta Appl. Math. \textbf{130} (2014), 9--49.

\bibitem{RenSongZhang2014CentralB}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical branching {M}arkov processes},
  J. Funct. Anal. \textbf{266} (2014), no. 3, 1716--1756.

\bibitem{RenSongZhang2015Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical superprocesses},
  Stochastic Process. Appl. \textbf{125} (2015), no. 2, 428--457.

\bibitem{RenSongZhang2017Central}
  Y.-X. Ren, R. Song, and R. Zhang,
  \emph{Central limit theorems for supercritical branching nonsymmetric {M}arkov processes},
  Ann. Probab. \textbf{45} (2017), no. 1, 564--623.

%\bibitem{RenSongZhang2017Functional}
%  Y.-X. Ren, R. Song, and R. Zhang,
%  \emph{Functional central limit theorems for supercritical superprocesses},
%  Acta Appl. Math. \textbf{147} (2017), 137--175.
%
%\bibitem{Sato2013Levy}
%  K. Sato,
%  \emph{L{\'e}vy processes and infinitely divisible distributions},
%  Translated from the 1990 Japanese original. Revised by the author. Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.
%
%\bibitem{SchillingSongVondravcek2010Bernstein}
%  R. L. Schilling, R. Song, and Z. Vondra\v{c}ek,
%  \emph{Bernstein functions.}
%  Theory and applications. Second edition. De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2012.
%
%\bibitem{SteinShakarchi2003Complex}
%  E. M. Stein and R. Shakarchi, \emph{Complex analysis},
%  Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.
%
%\bibitem{Wang2010An-almost}
%  L. Wang, \emph{An almost sure limit theorem for super-{B}rownian motion},
%  J. Theoret. Probab. \textbf{23} (2010), no. 2, 401--416.

\end{thebibliography}
\end{document}

### 2020-05-23 supCLT-ind11.tex
add supCLT-ind11.tex

--- 2020-05-23 supCLT-ind8.tex
@@
 %supCLT-ind8.tex 20/05/2020 by Zhenyao
+%supCLT-ind9.tex 21/05/2020 by Yanxia
+%%supCLT-ind10.tex 22/05/2020 by Jianjie
+%%supCLT-ind11.tex 22/05/2020 by Renming
+%%supCLT-ind12.tex 23/05/2020 by Zhenyao
 \documentclass[12pt,a4paper]{amsart}
 \setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.5in}
+\addtolength{\textwidth}{-2in}
 \calclayout
@@
 \mathtoolsset{showonlyrefs}
-\usepackage{stackrel}
 \usepackage{mathrsfs}
@@
 \usepackage{comment}
-\usepackage{xcolor}
+%\usepackage{xcolor}
 \usepackage{amsthm}
@@
 \email{yxren@math.pku.edu.cn}
-\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}
+\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF}
 \address{
@@
 in three different regimes. However, we were not able to prove
-%a central limit theorem for
 central limit theorems for
@@
 \maketitle
-%\section{Introduction}
+
 \section{Introduction and main result}
-%\subsection{Main result}
 \label{subsec:M}
@@
 and $\langle f, g\rangle = \int f(x)g(x) \mathrm dx$ whenever the integrals make sense.
-We say a real-valued Borel function 
-%$f:(t,x)\mapsto f(t,x)$ 
-$f$
+We say a real-valued Borel function $f$
 on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty. $
@@
   \mathbb{P}_{\mu}[e^{-X_t(f)}]
-  = e^{-\mu(V_tf)}
-  , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
+  = e^{-\mu(V_tf)},
+   \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
 \end{align}
@@
 For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
-We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} the following.
+We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} the following:
 \begin{equation}\label{eq:Hinfty}
@@
 \end{equation}
+Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$
+are finite dimensional spaces, and $\mathcal C_c$ might be empty.
 Define a semigroup
@@
 \begin{split}
-&e^{-\alpha t}\|X_t\| \xrightarrow[t\to \infty]{\text{a.s.}} H_\infty;
+&e^{-\alpha t}\|X_t\| \xrightarrow[t\to \infty]{\text{a.s.}} \widetilde{H}_\infty;
 \quad \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s};
@@
 \]
-where $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$
+where 
+$\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
+$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$
 are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; and
@@
 \end{equation}
-	% The above result implies that if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f,$ and if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$,\\
-	%The above result implies that if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta < \kappa_f b$, then  under $\widetilde {\mathbb P}_{\mu}$, 
-%\[
-	%\frac{X_t(f)}{\|X_t\|^{1-\tilde \beta} } \xrightarrow[t\to \infty]{d} \zeta^f,
-%\] 
-	%and if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta = \kappa_f b$,
-	% then under $\mathbb{P}_{\mu}(\cdot|D^c)$,\\ 
-	% $\|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^{f_c}$.
-	%then under $\widetilde{\mathbb P}_\mu $, 
-%\[
-	%\frac{X_t(f)}{\|t X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_c}.
-%\]
 	The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
-	%A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$.
-	%For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ maybe non-zero. 
-	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$; and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero.
+A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$; and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$,
+then $f_\mathrm c$ and $f_\mathrm l$ maybe non-zero.
 	In \cite{RenSongSunZhao2019Stable}, we were not able to
 	establish a central limit theorem in this case. We conjectured there that the limit random variables in \eqref{eq:oldResult}
-	%for $ f\in \mathcal C_\mathrm s$, $f\in \mathcal C_\mathrm c$ and $ f\in \mathcal C_\mathrm l$ are independent. 
 	for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
@@
 	\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},
-	%\frac{ X_t(f_\mathrm l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{1-\tilde \beta}}
 	\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
@@
 	\end{align}
-	where $\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$; $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; $\widetilde H_\infty$,  $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
+	where 
+$\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$;
+$\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$; $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; $\widetilde H_\infty$,  $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
 \end{thm}
@@
 \[
-    %\frac{ X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} }{\|X_t\|^{1-\tilde \beta}}
     \frac{ X_t(f) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}
     \xrightarrow[t\to \infty]{d}
-    %\zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l};
        \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l},
 \]
-%
 	where $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$  are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are independent;
@@
 \[
-  %\frac{ X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty} }{\|tX_t\|^{1-\tilde \beta}}
     \frac{ X_t(f) - \mathrm x_t(f)}{\|tX_t\|^{1-\tilde \beta}}
@@
 \]
-%
 	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}.
 \end{enumerate}
-%Here, $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are 
-%the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}.
+Here $\mathrm x_t(f)$ is defined in \eqref{eq:oldResult}.
 \end{cor}
 
-%\section{Proofs of main results}
-\section{Proofs of main result}
+\section{Proof of main result}
 \label{proofs of main results}
 
-%\subsection{Preliminaries}
-\subsection{A key result}
-\begin{comment}
-\begin{lem}\label{ineq: analysis}
-There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
-\[
-    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
-\]
-\end{lem}
-\begin{proof}
-   Note that
-\[
-  \lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
-\]
-Using this and continuity, we get that there exists {\color{blue}$C_1>0$} such that for all $|y|\geq 1$,
-\[
-  |(1+y)^{1+\beta}-y^{1+\beta}-1|\leq C_1 |y|^{\beta}.
-\]
- Note that if $x = 0$ or $y= 0$, then the desired result is trivial.
-So we only need to consider
- the case that $x \neq 0$ and $y \neq 0$.
- In this case, if $|x|\geq |y|$, we have
-\[
-|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)\leq C_1|y||x|^{\beta};
-\]
-and  if $|x|\leq |y|$, we have
-\[
-	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
-	\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)\leq C_1|x||y|^{\beta}.
-\]
-Combining the above, we immediately get the desired result.
-\end{proof}
-\end{comment}
-
-% For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$. %
+We first make some preparations before proving Theorem \ref{thm:M}.
 For every $t\geq 0$ and $f\in \mathcal P$, define
@@
   	Z_t f
-  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,\quad
+  	%:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,\quad
+  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,\quad
   	\Upsilon^f_t
@@
 \]
-Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is 
-% the characteristic exponent of the limit of $\Upsilon^f_t$.
- the asymptotic characteristic exponent of $\Upsilon^f_t$.
-The following corollary to  \cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of Theorem \ref{thm:M}.
-%
+Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of the limit of $\Upsilon^f_t$.
 For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$.
+The following generalization of
+\cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of  Theorem \ref{thm: II}, a special case of Theorem \ref{thm:M}.
 
-\begin{cor}
+\begin{prop}
   \label{cor:MI}
@@
 \end{equation}
-\end{cor}
+\end{prop}
 \begin{proof}
@@
 \end{align}
-% It follows from \cite[Proposition 3.5]{RenSongSunZhao2019Stable} that there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$, 
 	Therefore, there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$,
@@
 	=  \frac{1}{\mathbb P_\mu(D^c)} \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) \times {}
-	\\ \mathbb{P}_{\mu}\Big[ \mathbb P_\mu\big[e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle}  ; D^c \big| \mathscr F_{t-k_1 - 1}\big] \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] .
+	\\ \qquad \mathbb{P}_{\mu}\Big[ \mathbb P_\mu\big[e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle}  ; D^c \big| \mathscr F_{t-k_1 - 1}\big] \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] .
 	\end{multlined}
@@
 
-\subsection{Proof of Theorem \ref{thm:M}}
-\label{sec: main}
-% In this subsection, we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$,  $f_\mathrm c\in \mathcal C_\mathrm c\setminus\{0\}$, $f_\mathrm l\in \mathcal C_\mathrm l\setminus\{0\}$ and $t_0>1$ large enough, so that $\lceil t-\ln t\rceil \leq \lfloor t \rfloor - 1$ for all $t\geq t_0$.
-In this subsection, we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$,  $f_\mathrm c\in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l\in \mathcal C_\mathrm l\setminus\{0\}$.
-	% For any random variable $Y$ with finite mean, we define 
-	 For any random variable $Y$ with finite mean under $\mathbb P_\mu$, we define 
-\begin{align}
-	% \mathcal I_r^t Y&:= \mathcal I_r^t [Y, \mu] := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_r], \quad 0 \leq r \leq t <\infty,
-	\mathcal I_r^t Y := \mathbb P_\mu[Y|\mathscr F_{t\wedge 0}] - \mathbb P_\mu[Y|\mathscr F_{r\wedge 0}], \quad -\infty < r, t <\infty.
-	%\\\mathcal I_r^t Y&:= \mathcal I_0^t [Y, \mu] := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_0], \quad r<0 \leq t <\infty.
-\end{align}
-	% For each $t\geq t_0$, 
-	For each $t\geq 1$,
-	we have the following decomposition.
-  \begin{align} 
-   %&\frac{X_t(f_\mathrm s)}{\|X_t\|^{1- \tilde \beta }} = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
-   I^{f_\mathrm s}(t) &:= \frac{X_t(f_\mathrm s)}{\|X_t\|^{1- \tilde \beta }}  = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
-    %\\ := & \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}  \|X_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s) \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]}\|X_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)   \Big)
-    \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}  \Big)
-   % \\& + ( \|X_t\|^{\tilde \beta - 1}X_0(P_t^\alpha f_\mathrm s) ),
-   + \Big( \frac{X_0(P_t^\alpha f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}\Big),
-     % & \frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}} = I^{f_\mathrm c}_1(t) + I^{f_\mathrm c}_2(t) + I^{f_\mathrm c}_3(t)
-    \\ I^{f_\mathrm c}(t)&:=\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}} = I^{f_\mathrm c}_1(t) + I^{f_\mathrm c}_2(t) + I^{f_\mathrm c}_3(t)
-    % \\:= &\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}  \|tX_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c) \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]}\|tX_t\|^{\tilde \beta - 1} \mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)\Big)\\
-    % &+ ( \|tX_t\|^{\tilde \beta - 1}X_0(P_t^\alpha f_\mathrm c) ),
-        \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}  \Big)    + \Big( \frac{X_0(P_t^\alpha f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}\Big),
- %\begin{align}
-    %& \frac{X_t(f_\mathrm l) - \sum_{p\in \mathcal N} \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}H_\infty^p}{\|X_t\|^{1- \tilde \beta}}
-      %= \sum_{p\in \mathcal N}\frac{ \langle f_\mathrm l,\phi_p\rangle_\varphi [X_t(\phi_p) - e^{(\alpha - |p|b)t}H_\infty^p]}{\|X_t\|^{1- \tilde \beta}}
-    %\\& = \sum_{p \in \mathcal N} \frac{\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}(H_t^p - H_\infty^p)}{\|X_t\|^{1- \tilde \beta}}
-    %= \sum_{k=0}^\infty \sum_{p \in \mathcal N}  \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}
-    % \\ &= \Big(\sum_{k = 0}^{\lfloor t^2 \rfloor}  + \sum_{k = \lfloor t^2 \rfloor+1}^\infty \Big)
-    %\\ &= \Big(\sum_{k\in \mathbb N \cap [0,t^2]}  + \sum_{k\in \mathbb N \cap (t^2,\infty)}   \Big)
-    %\Big(\sum_{p \in \mathcal N}  \langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}\Big)
-     %= : I^{f_\mathrm l}_1(t) + I^{f_\mathrm l}_2(t),
-  %\end{align}
-  \\ I^{f_\mathrm l}(t) &:= \frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}
-  = I^{f_\mathrm l}_1(t) + I^{f_\mathrm l}_2(t) + I^{f_\mathrm l}_3(t)
-  \\& := \Big(\sum_{k\in \mathbb N \cap [0,t^2]} \frac{ \mathcal I_{t+k+1}^{t+k}\mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}\Big) + \Big(\sum_{k\in \mathbb N \cap (t^2,\infty)}  \frac{ \mathcal I_{t+k+1}^{t+k}\mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}\Big)+0.
-  \end{align}
-  %where $\mathcal N:= \{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b\}$.
-
-	% Define $I_3^{f_\mathrm l}(t)=0$, $t\geq t_0$. 
-	For every $t\geq 1$, define 
-	% For all $t\geq t_0$ and $j=1,2,3$, let
-	%$R_j(t):=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big)$
-	%and
-\begin{align}
-	%
-	R_j(t)&:=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big), \quad j = 1,2,3,
-	\\ R(t)&:=\Bigg( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}\Bigg),
-    \\R_0(t)&=(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t))
-    % :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
-    \\&:=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
-\end{align}
-where $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
-
-%Define
-%\begin{align}
-%R(t):=\Bigg( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f_\mathrm l,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^{1-\tilde \beta}}\Bigg).
-%\end{align}
-%The following result is a special case of Theorem \ref{thm:M}.
-%%
-\begin{thm}\label{thm: II}
-Under $\mathbb{\widetilde{P}}_{\mu}$,
-$
-R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
-$
-where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are
-the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
-\end{thm}
-\begin{proof}
-
-%Note that for each $t\geq t_0$,
-Note that for each $t\geq 1$,
-\[
-%R(t)=R_0(t)+(R_1(t)-R_0(t))+R_2(t)+R_3(t),
-R(t)=R_0(t)+(R_1(t)-R_0(t))+R_2(t)+R_3(t).
-\]
-%where 
-Note that
-$$
-(R_1(t)-R_0(t))=(I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t), I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t), I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)).
-$$
-%$$
-%R_2(t)=(I_2^{f_\mathrm s}(t), I_2^{f_\mathrm c}(t), I_2^{f_\mathrm l}(t)), \mbox{ and }R_2(t)=(I_3^{f_\mathrm s}(t), I_3^{f_\mathrm c}(t), 0).
-%$$
-In the proof of Theorem 1.6(1) in \cite{RenSongSunZhao2019Stable}, we proved that 
-$I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
- In the proof of Theorem 1.6(2) in \cite{RenSongSunZhao2019Stable}, we proved that 
- $I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
-In the proof of Theorem 1.6(3) in \cite{RenSongSunZhao2019Stable}, we proved that 
-$I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$ and  $I_2^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$.
-Thus we have %under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$, 
-$R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d} (0,0,0)$, $R_2(t)\xrightarrow[t\to \infty]{d}(0,0,0)$ and
-$R_3(t)\xrightarrow[t\to \infty]{d}(0,0,0)$. 
-Combining the above results and using Slutsky's theorem, we only need to  show that, under $\mathbb{\widetilde{P}}_{\mu}$, 
-\begin{equation}
-\label{lem:UOT}R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
-\end{equation} 
-%\end{proof}
-%
-%\begin{lem}\label{lem: U0T}
-%Under $\mathbb{\widetilde{P}}_{\mu}$,
- %$R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are 
-%the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
-%\end{lem}
-%
-%\begin{proof}
-\\
-\paragraph{\it Proof of \eqref{lem:UOT}}
-Since $\Upsilon_t^f$ is linear in $f$, for each $t\geq 1$,
-\[
-\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
-\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
-= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
-\]
-Using Corollary \ref{cor:MI} with $f=\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c}$ and $g = -\tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that
-% for $t>t_0$,
-for every $t\geq 1$,
-  \begin{align}
-    &\Big|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
-    -\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\Big|\\
-    &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
-  \end{align}
-Next, we claim that
-\begin{equation} \label{eq:UOT.1}
-\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c)), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big) =
-\prod_{j=\mathrm s,\mathrm c,\mathrm l}\exp(m[f_j]).
-\end{equation}
- Then we have
-\[
-	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
-	\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
-	 \xrightarrow[t\to \infty]{} 
-	 \prod_{j=\mathrm s,\mathrm c,\mathrm l}\exp(m[f_j]).
-\]
-% Since $I_0^{f_j}(t), j=\mathrm s,\mathrm c,\mathrm l$, is linear in $f_j$, replacing $f_j$ with $\theta_j f_j$, we immediately get the desired result.
- Since $I_0^{f_j}(t)$ are linear in $f_j\in \mathcal C_j$, replacing $f_j$ with $\theta_j f_j$, we immediately get the desired result.
-%Now we prove the above claim.
-\\
-\paragraph*{\it Proof of \eqref{eq:UOT.1}} 
- %Recall that  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
- %Using \eqref{eq:I:R:2} and the fact that $\varphi(x)dx$ is the invariant distribution of the semigroup $(P_t)_{t\geq 0}$, we get that for each $n\in \mathbb Z_+$,
-  %\begin{align}
-  %\label{eq:PM:CLTS:2a}
-   % & \sum_{k=0}^n \langle Z_1 T_{k} (-\tilde f_\mathrm l), \varphi \rangle
-     % = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha ((iP_{1 - u}^\alpha T_k \tilde f_\mathrm l)^{1+\beta}), \varphi\rangle ~du
-  %  \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle  (iP_{1 - u}^\alpha T_{k}\tilde f_\mathrm l)^{1+\beta}, \varphi \rangle ~du
-  %  \\& = \sum_{k=0}^n \int_0^1 \langle  (iT_{k+ u} f_\mathrm l)^{1+\beta}, \varphi\rangle~du
- %   = \int_0^{n+1} \langle  (iT_{u} f_\mathrm l)^{1+\beta}, \varphi\rangle~du = m_{n+1}[-f_\mathrm l].
-  %\end{align}
-%Therefore, we have
-%\[
-%\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_l),\varphi\rangle\Big) = \lim_{t\rightarrow \infty}\exp(m_{\lfloor t^2 \rfloor+1}[-f])=\exp(m[-f]).
-%\]
-%%	
-%Similarly, for all $f\in \mathcal C_\mathrm s  \oplus \mathcal C_\mathrm c$ and $n\in \mathbb Z_+$.
-For every $f\in \mathcal C_\mathrm s  \oplus \mathcal C_\mathrm c$ and $n\in \mathbb Z_+$,
-%  \begin{align}
- %   & \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
-   % = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha ((-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle \mathrm du
-    %\\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle  (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle \mathrm du
-   % \\& = \sum_{k=0}^n \int_0^1 \langle  (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle \mathrm du
-   % = \int_0^{n+1} \langle  (-iT_{u} f)^{1+\beta}, \varphi\rangle \mathrm du = m_{n+1}[f],
- % \end{align}
- \begin{align}
-  & \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
-  = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha (\eta(-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle \mathrm du
- \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle \eta (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle \mathrm du
- \\& = \sum_{k=0}^n \int_0^1 \langle \eta (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle \mathrm du
- = \int_0^{n+1} \langle  \eta (-iT_{u} f)^{1+\beta}, \varphi\rangle \mathrm du = m_{n+1}[f],
- \end{align}
-where $\tilde f=e^{\alpha(\tilde \beta - 1)} f$.
-% Therefore, for any $t\geq t_0$,
-Therefore, for any $t\geq 1$,
-\begin{equation} \label{eq:UOT.15}
-\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c), \varphi\rangle
-=\eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du.
-\end{equation}
-Note that for each $u\geq 0$, $T_uf_\mathrm c=f_\mathrm c$.
-%According to
- Also note that according to
- Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, there exist $\delta> 0$ and
-$h\in \mathcal P$ (depending only on $f_\mathrm s$)
-such that for each $u\geq 0$,
- $|T_uf_\mathrm s|\leq e^{-\delta u}h$.
-%
-Let us claim the following analytical fact:
-\begin{equation}\label{eq:UOT.2}
-\begin{minipage}{0.9\textwidth}
+The following elementary result will also be used in the proof of Theorem \ref{thm: II}.
+\begin{lem}\label{ineq: analysis}
 There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
@@
 \]
-\end{minipage}
-\end{equation}
-%According to Lemma \ref{ineq: analysis}, there exists $C>0$ (independent of the choices of $f_\mathrm s$ and $f_\mathrm c$)
-Now for this $C>0$ it holds that for all $u\geq 0$ and $t\geq 0$,
-\begin{align}
-  &|(-i(T_uf_\mathrm s+t^{\tilde{\beta}-1}T_uf_\mathrm c))^{1+\beta}-(-iT_uf_\mathrm s)^{1+\beta}-(-it^{\tilde{\beta}-1}T_uf_\mathrm c)^{1+\beta}|
-  \\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
-  \\&\overset{\eqref{eq:UOT.2}}\leq  C(t^{-\frac{\beta}{1+\beta}}|T_uf_\mathrm s||T_uf_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}|T_uf_\mathrm s|^{\beta}|T_uf_\mathrm c|)
-  \\&\label{eq:UOT.21}\leq C(t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|).
-\end{align}
-% which means that
-This means that there exists $C_1 >0$ such that for all $t\geq 1$,
-\begin{align}
-&\Big|\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)-m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm s]-\frac{1}{t}m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm c]\Big|
-%
-\\& \begin{multlined} 
-\overset{\eqref{eq:UOT.15},\eqref{eq:M.13}}\leq\Big| \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du - {}
-\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du - \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|
-\end{multlined}
-\\ & \overset{\eqref{eq:UOT.21}}\leq C_1\int_0^{\lfloor t-\ln t \rfloor+1}\langle t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|, \varphi \rangle \mathrm du
-\\& \leq C_1 t^{-\frac{\beta}{1+\beta}} \langle h|f_\mathrm c|^{\beta},\varphi \rangle \int_0^\infty e^{-\delta u} \mathrm du + C_1 t^{-\frac{1}{1+\beta}} \langle h^\beta|f_\mathrm c|,\varphi \rangle \int_0^\infty e^{-\delta \beta u} \mathrm du
-\\& \xrightarrow[t\rightarrow \infty]{} 0.
-\end{align}
-Combining this with \eqref{eq:I:R:3}, we get that
-\begin{equation} \label{eq:UOT.4}
-\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)  = \exp( m[f_\mathrm s]+m[f_\mathrm c]).
-\end{equation}
-%
-Also note that according to the Step 1 in the Proof of Theorem 1.6.(3) in \cite{RenSongSunZhao2019Stable}, we have
-\begin{equation}\label{eq:UOT.5}
-\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big) =\exp(m[-f_\mathrm l]).
-\end{equation}
-% Thus the claim is valid.
-Thus the desired claim follows from \eqref{eq:UOT.4} and \eqref{eq:UOT.5}.
-%
-\\
-\paragraph{\it Proof of \eqref{eq:UOT.2}}
+\end{lem}
+\begin{proof}
    Note that
@@
 \]
+% Using this and continuity, we get that there exists {\color{blue}$C_1>0$} such that for all $|y|\geq 1$,
 Using this and continuity, we get that there exists $C_1>0$ such that for all $|y|\geq 1$,
@@
 
-\begin{proof}[Proof of Theorem Theorem \ref{thm:M}]
+In the remainder of this section,
+we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$,  $f_\mathrm c\in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l\in \mathcal C_\mathrm l\setminus\{0\}$.
+For any random variable $Y$ with finite mean under $\mathbb P_\mu$, we define
+\begin{align}
+\mathcal I_r^t Y := \mathbb P_\mu[Y|\mathscr F_{t\vee 0}] - \mathbb P_\mu[Y|\mathscr F_{r\vee 0}], \quad -\infty < r, t <\infty.
+\end{align}
+	For each $t\geq 1$,
+	we have the following decomposition.
+  \begin{align}
+     I^{f_\mathrm s}(t) &:= \frac{X_t(f_\mathrm s)}{\|X_t\|^{1- \tilde \beta }}  = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
+        \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}  \Big)
+    + \Big( \frac{X_0(P_t^\alpha f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}\Big),
+       \\ I^{f_\mathrm c}(t)&:=\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}} = I^{f_\mathrm c}_1(t) + I^{f_\mathrm c}_2(t) + I^{f_\mathrm c}_3(t)
+    \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}  \Big)    + \Big( \frac{X_0(P_t^\alpha f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}\Big),
+   \\ I^{f_\mathrm l}(t) &:= \frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}
+  = I^{f_\mathrm l}_1(t) + I^{f_\mathrm l}_2(t) + I^{f_\mathrm l}_3(t)
+  \\& := \Big(\sum_{k\in \mathbb N \cap [0,t^2]} \frac{ \mathcal I_{t+k+1}^{t+k}\mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}\Big) + \Big(\sum_{k\in \mathbb N \cap (t^2,\infty)}  \frac{ \mathcal I_{t+k+1}^{t+k}\mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}\Big)+0,
+  \end{align}
+ where $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
+	For every $t\geq 1$, define
+	\begin{align}
+	R_j(t)&:=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big), \quad j = 1,2,3,
+	\\ R(t)&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
+    \\R_0(t)&=\big(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t)\big)
+       \\&:=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
+\end{align}
+where 
+ $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
+$\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
+The following result is a special case of Theorem \ref{thm:M}.
+
+\begin{thm}\label{thm: II}
+Under $\mathbb{\widetilde{P}}_{\mu}$,
+$
+R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
+$
+where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are
+the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
+\end{thm}
+\begin{proof}
+%In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$.
+In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
+Note that for each $t\geq 1$,
+\[
+R(t)=R_0(t)+\big(R_1(t)-R_0(t)\big)+R_2(t)+R_3(t).
+\]
+Note that
+$$
+(R_1(t)-R_0(t))=(I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t), I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t), I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)).
+$$
+In the proof of Theorem 1.6(1) in \cite{RenSongSunZhao2019Stable}, we proved that
+$I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
+ In the proof of Theorem 1.6(2) in \cite{RenSongSunZhao2019Stable}, we proved that
+ $I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
+In the proof of Theorem 1.6(3) in \cite{RenSongSunZhao2019Stable}, we proved that
+$I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$ and  $I_2^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$.
+Thus we have 
+$R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d} (0,0,0)$, $R_2(t)\xrightarrow[t\to \infty]{d}(0,0,0)$ and
+$R_3(t)\xrightarrow[t\to \infty]{d}(0,0,0)$.
+Combining the above results and using Slutsky's theorem, we only need to  show that, under $\mathbb{\widetilde{P}}_{\mu}$,
+\begin{equation}
+\label{lem:UOT}R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
+\end{equation}
+
+Now we prove \eqref{lem:UOT}.
+Since $\Upsilon_t^f$ is linear in $f$, for each $t\geq 1$,
+\[
+\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
+\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
+= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
+\]
+%Using Corollary \ref{cor:MI} 
+Using Proposition \ref{cor:MI} 
+with $f=\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c}$ and $g = -\tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that
+for every $t\geq 1$,
+  \begin{align}
+    &\Big|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
+    -\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\Big|\\
+    &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
+  \end{align}
+%Next, we claim that
+We claim that
+\begin{align} \label{eq:UOT.1}
+&\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c)), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big)\\
+& =\exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
+\end{align}
+Given this claim, we have
+\[
+	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
+	\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
+	 \xrightarrow[t\to \infty]{}
+	 \exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
+\]
+ Since $I_0^{f_j}(t)$ are linear in 
+     $f_j\in \mathcal C_j (j=\mathrm s,\mathrm c,\mathrm l)$,
+ replacing $f_j$ with $\theta_j f_j$, we immediately get 
+ \eqref{lem:UOT}.
+
+Now we prove the claim \eqref{eq:UOT.1}.
+For every $f\in \mathcal C_\mathrm s  \oplus \mathcal C_\mathrm c$ and $n\in \mathbb Z_+$,
+ \begin{align}
+  & \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
+  = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha (\eta(-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle \mathrm du
+ \\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle \eta (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle \mathrm du
+ \\& = \sum_{k=0}^n \int_0^1 \langle \eta (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle \mathrm du
+ = \int_0^{n+1} \langle  \eta (-iT_{u} f)^{1+\beta}, \varphi\rangle \mathrm du = m_{n+1}[f],
+ \end{align}
+where $\tilde f=e^{\alpha(\tilde \beta - 1)} f$.
+Therefore, for any $t\geq 1$,
+\begin{equation} \label{eq:UOT.15}
+\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c), \varphi\rangle
+=\eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du.
+\end{equation}
+Note that for each $u\geq 0$, $T_uf_\mathrm c=f_\mathrm c$.
+ Also note that according to
+ Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, there exist $\delta> 0$ and
+$h\in \mathcal P$ (depending only on $f_\mathrm s$)
+such that for each $u\geq 0$,
+ $|T_u f_\mathrm s|\leq e^{-\delta u}h$.
+It follows from Lemma \ref{ineq: analysis} that there exists $C>0$ such that for all $u\geq 0$ and $t\geq 0$,
+\begin{align}
+  &|(-i(T_uf_\mathrm s+t^{\tilde{\beta}-1}T_uf_\mathrm c))^{1+\beta}-(-iT_uf_\mathrm s)^{1+\beta}-(-it^{\tilde{\beta}-1}T_uf_\mathrm c)^{1+\beta}|
+  \\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
+  % \\&\overset{Lemma \ \ref{ineq: analysis}}
+  \\&\overset{\text{Lemma \ref{ineq: analysis}}}
+  \leq  C(t^{-\frac{\beta}{1+\beta}}|T_uf_\mathrm s||T_uf_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}|T_uf_\mathrm s|^{\beta}|T_uf_\mathrm c|)
+  \\&\label{eq:UOT.21}\leq C(t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|).
+\end{align}
+This means that there exists $C_1 >0$ such that for all $t\geq 1$,
+\begin{align}
+&\Big|\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)-m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm s]-\frac{1}{t}m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm c]\Big|
+\\& \begin{multlined}
+\overset{\eqref{eq:UOT.15},\eqref{eq:M.13}}\leq\Big| \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du - {}
+\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du - \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|
+\end{multlined}
+\\ & \overset{\eqref{eq:UOT.21}}\leq C_1\int_0^{\lfloor t-\ln t \rfloor+1}\langle t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|, \varphi \rangle \mathrm du
+\\& \leq C_1 t^{-\frac{\beta}{1+\beta}} \langle h|f_\mathrm c|^{\beta},\varphi \rangle \int_0^\infty e^{-\delta u} \mathrm du + C_1 t^{-\frac{1}{1+\beta}} \langle h^\beta|f_\mathrm c|,\varphi \rangle \int_0^\infty e^{-\delta \beta u} \mathrm du
+\\& \xrightarrow[t\rightarrow \infty]{} 0.
+\end{align}
+Combining this with \eqref{eq:I:R:3}, we get that
+\begin{equation} \label{eq:UOT.4}
+\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)  = \exp( m[f_\mathrm s]+m[f_\mathrm c]).
+\end{equation}
+Also note that according to the Step 1 in the Proof of Theorem 1.6.(3) in \cite{RenSongSunZhao2019Stable}, we have
+\begin{equation}\label{eq:UOT.5}
+\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big) =\exp(m[-f_\mathrm l]).
+\end{equation}
+Thus the desired claim follows from \eqref{eq:UOT.4} and \eqref{eq:UOT.5}.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{thm:M}]
  We first recall some facts about weak convergence which will be used later. For $f:\mathbb R^d\mapsto \mathbb R$, let
@@
 \[
-  d(\mu_1,\mu_2):=\sup\Big\{\Big|\int fd\mu_1-\int f d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
+  d(\mu_1,\mu_2)
+  %:=\sup\Big\{\Big|\int fd\mu_1-\int f d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
+  :=\sup\Big\{\Big|\int f \mathrm d\mu_1-\int f \mathrm d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
 \]
@@
 \end{align}
-% Recall that $S(t)$ is defined in the display before Theorem \ref{thm:M}.
 In this proof, let us fix $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l \in \mathcal C_\mathrm l\setminus\{0\}$.
 Recall that $S(t)~(t\geq 0)$ is given by \eqref{eq:M.1}.
-% Now for all $f_\mathrm s\in \mathcal C_\mathrm s $, $f_\mathrm c \in \mathcal C_\mathrm c$, $f_\mathrm l \in \mathcal C_\mathrm l$ and $r,t>0$, let
 For every $r,t> 0$, let
 \begin{align}
-  %S(t,r):=\Big(e^{-\alpha t}\|X_t\|,& \|X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_\mathrm s), \|(t+r)X_{t+r}\|^{\tilde{\beta}-1}X_{t+r}(f_\mathrm c),\\
-%& \|X_{t+r}\|^{\tilde{\beta}-1}(X_{t+r}(f_\mathrm l)-\sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}\langle f_\mathrm l,\phi_p\rangle_{\varphi}e^{(\alpha-|p|b)(t+r)}H_{\infty}^p )\Big),
  S(t,r):=\Big(e^{-\alpha t}\|X_t\|,& \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm c)}{\|(t+r)X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm l)-\mathrm x_{t+r}(f_\mathrm l) }{\|X_{t+r}\|^{1-\tilde{\beta}}}\Big),
@@
 \begin{align}
-\widetilde{S}(t,r)= \Big(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0\Big).
+\widetilde{S}(t,r)= \Big(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0\Big),
 \end{align}
+where, for any $t>0$, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
 Then $S(t+r)=S(t,r)+\widetilde{S}(t,r)$.
-%
-%\emph{Step 1.} For all $\mu\in \mathcal M_c(\mathbb R^d)$, $f_\mathrm s\in \mathcal C_\mathrm s$,$f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$, under $\mathbb P_{\mu}(\cdot|D^c)$, we have
-%\[
-%S(t,r)\xrightarrow[r\rightarrow \infty]{d}\widetilde{S}(t):=\Big(e^{-\alpha t}\|X_t\|,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}\Big),
-%\]
-%{\color{blue} where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
-%Moreover,  $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent of the limit of $e^{-\alpha t}\|X_t\|$.}
-Let us claim that
+%Let us claim that
+We claim that
 \begin{equation}\label{eq:M.3}
@@
 	\]
-	where $\widetilde H_t$ has the distribution of $\{e^{-\alpha t} \|X_t\|; \widetilde {\mathbb P}_\mu\}$ and is independent of $(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$.
+	where $\widetilde H_t$ has the distribution of $\{e^{-\alpha t} \|X_t\|; \widetilde {\mathbb P}_\mu\}$,
+	$\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, 
+	%and $\widetilde H_t$ is independent of $(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$.
+	and $\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent of each other.
 \end{minipage}
 \end{equation}
-%For all $r,t>0$, let $\mathcal D(r)$ and $\mathcal D(r,t)$ be the distributions of $S(r)$ and $S(t,r)$ under $\mathbb P_{\mu}(\cdot|D^c)$ respectively, 
+
 For every $r,t\geq 0$, let $\mathcal D(r)$ and $\mathcal D(r,t)$ be the distributions of $S(r)$ and $S(t,r)$ under $\widetilde{\mathbb P}_{\mu}$ respectively;
-%let $ \widetilde{\mathcal D}(t)$ and $\mathcal D$ be the distributions of $\widetilde{S}(t)$ and $(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$ under $\mathbb P_{\mu}(\cdot|D^c)$ respectively.
 let $\widetilde{\mathcal D}(t)$ and $\mathcal D$ be the distributions of $(\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$ and $(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, respectively.
  Then for each $\gamma\in (0,\beta)$, there exist constant $C>0$
- %such that,
  such that for every $t > 0$,
@@
  &\varlimsup_{r\rightarrow \infty}d(\mathcal D(t+r),\mathcal D)
- \\& \overset{\rm Triangle~inequality}\leq \varlimsup_{r\rightarrow \infty}\Big( d\big(\mathcal D(t+r),\mathcal D(t,r)\big)+d\big(\mathcal D(t,r),\widetilde{\mathcal D}(t)\big)+d\big(\widetilde{\mathcal D}(t),\mathcal D\big)\Big)
- %
+ \\& \overset{\rm triangle~inequality}\leq \varlimsup_{r\rightarrow \infty}\Big( d\big(\mathcal D(t+r),\mathcal D(t,r)\big)+d\big(\mathcal D(t,r),\widetilde{\mathcal D}(t)\big)+d\big(\widetilde{\mathcal D}(t),\mathcal D\big)\Big)
   \\&\overset{\eqref{ineq: distribution control}} \leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|S(t+r) - S(t,r)|]+ \varlimsup_{r\rightarrow \infty} d\big(\mathcal D(t,r),\widetilde{\mathcal D}(t)\big) +\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]
-% \\&\leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|e^{-\alpha t}\|X_t\|-e^{-\alpha (t+r)}\|X_{t+r}\||]+0+\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]
 \\&\overset{\eqref{eq:M.3}}\leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|H_t - H_{t+r}|]+\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]
- %\\&\leq \varlimsup_{r\rightarrow \infty}\mathbb P_{\mu}(D^c)^{-1}(\|H_t-H_{t+r}\|_{\mathbb P_{\mu};1+\gamma}+\|H_t-H_{\infty}\|_{\mathbb P_{\mu};1+\gamma})
   \\&\overset{\text{H\"older inequality}}\leq \varlimsup_{r\rightarrow \infty}\mathbb P_{\mu}(D^c)^{-1}(\|H_t-H_{t+r}\|_{L_{1+\gamma} (\mathbb P_\mu)}+\|H_t-H_{\infty}\|_{L_{1+\gamma} (\mathbb P_\mu)})
- %\\&\leq Ce^{-\frac{\gamma}{1+\gamma}t}.
 \\&\label{eq:M.4}\overset{\text{\cite[Lemma 3.3]{RenSongSunZhao2019Stable}}}\leq C e^{-\alpha \tilde \gamma t}.
@@
 Therefore,
-%using the definition of $\varlimsup_{s\rightarrow \infty}$, we know that,
-%%
 \begin{align}
@@
  =\varlimsup_{t\to \infty}\varlimsup_{r\rightarrow \infty}d\big(\mathcal D(t+r),\mathcal D\big)
-% \leq \varlimsup_{t\rightarrow \infty}Ce^{-\frac{\gamma}{1+\gamma}t} = 0.
 \overset{\eqref{eq:M.4}}\leq \varlimsup_{t\rightarrow \infty}Ce^{-\alpha \tilde \gamma t} = 0.
@@
 The desired result now follows immediately.
-\\
-\paragraph{\it Proof of \eqref{eq:M.3}}
-%For all $\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l\in \mathbb R$ and $r,t>0$, denote the characteristic function of  $S(t,r)$ under $\mathbb P_{\mu}(\cdot|D^c)$ by $k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)$,
-For every $r,t >0 0$, let 
+
+Now we prove the claim \eqref{eq:M.3}.
+For every $r,t >0$, let
 \[
@@
 be the characteristic function of  $S(t,r)$ under $\widetilde{\mathbb P}_{\mu}$.
-% then by \eqref{eq:Hinfty} and the bounded convergence theorem we have,
 Then for each $\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l\in \mathbb R$ and $r,t> 0$,
@@
 =\widetilde{\mathbb P}_{\mu}\big[\exp\big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,\infty)\big)\big]\\
-&\label{eq:M.5}\overset{\text{Bounded convergence}}=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\big[\exp\big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\big);D^c\big],
+&\label{eq:M.5}\overset{\text{bounded convergence}}=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\big[\exp\big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\big);D^c\big],
 \end{align}
@@
 \overset{\eqref{eq:Hinfty}}=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + \frac{i\theta_\mathrm c}{(t+r)^{1-\tilde{\beta}}} \frac{X_{t+r}(f_\mathrm c)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + {}
-\\ i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l) - \sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b} e^{(\alpha - |p|b)(t+r)} e^{-(\alpha - |p|b)u}X_u(\phi_p) }{\|X_{t+r}\|^{1-\tilde{\beta}}}.
+\\\quad  i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l) - \sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b} e^{(\alpha - |p|b)(t+r)} e^{-(\alpha - |p|b)u}X_u(\phi_p) }{\|X_{t+r}\|^{1-\tilde{\beta}}}.
 \end{multlined}
 \end{align}
-%Note that $D^c=\{\|X_r\|>0, r\geq 0\}=D_{\leq t}\cap D_{> t}$,
-%where $D_{\leq t}=\{\|X_r\|>0, 0\leq r\leq t\}$ and $D_{> t}=\{\|X_r\|>0, r> t\}$.
-%%
 Now for each $t>0$, we get
@@
 & \lim_{r\to \infty}k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
-%\\&=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\Big(i\theta e^{-\alpha t}\|X_t\|\Big)\mathbf 1_{D_{\leq t}} \mathbb P_{\mu}\Big[\exp\Big(A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\Big)\mathbf 1_{D_{> t}}\Big|\mathscr F_t\Big]\Big]
 \\&\overset{\eqref{eq:M.5}}=\lim_{r\to \infty}\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\big[\exp\{i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0} \mathbb P_{\mu}[\exp\{A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\}\mathbf 1_{D^c}|\mathscr F_t]\big]
@@
 \end{multlined}
-\\&\begin{multlined}\overset{\text{Bounded convergence}}=\lim_{r\to \infty} \mathbb P_{\mu}\Bigg[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \times {}
+\\&\begin{multlined}\overset{\text{bounded convergence}}=\lim_{r\to \infty} \mathbb P_{\mu}\Bigg[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \times {}
 \\\widetilde{\mathbb P}_{X_t}\bigg[\exp\bigg\{A\bigg(\theta_\mathrm s,\theta_\mathrm c\Big(\frac{r}{t+r}\Big)^{1-\tilde \beta},\theta_\mathrm l,r,0,\infty\bigg)\bigg\}\bigg]\Bigg].
 \end{multlined}
-\\& \overset{\text{Theorem \ref{thm: II}}}=  \mathbb P_{\mu}\Big[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \Big]\prod_{j=\mathrm s,\mathrm c,\mathrm l}\exp\{m[\theta_j f_j]\}
+\\& \overset{\text{Theorem \ref{thm: II}}}=  \mathbb P_{\mu}\Big[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \Big]\Big(\prod_{j=\mathrm s,\mathrm c}\exp\{m[\theta_j f_j]\}\Big)\exp\{m[-\theta_\mathrm l f_\mathrm l]\}
+%\\&=\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\mathbb P_{\mu}(D^c|\mathscr F_t) \Big]\Big(\prod_{j=\mathrm s,\mathrm c}\exp\{m[\theta_j f_j]\}\Big)\exp\{m[-\theta_\mathrm l f_\mathrm l]\}
 \\&=\widetilde{\mathbb P}_{\mu}[\exp\{i\theta e^{-\alpha t}\|X_t\|\}]
-\prod_{j=\mathrm s,\mathrm c,\mathrm l}\exp\{m[\theta_j f_j]\}.
+\Big(\prod_{j=\mathrm s,\mathrm c}\exp\{m[\theta_j f_j]\}\Big)\exp\{m[-\theta_\mathrm l f_\mathrm l]\}.
 \qedhere
@@
 
-%
-%\bibitem{Bertoin}
-%J. Bertoin,
-%\emph{L\'evy processes}.
-%Cambridge Tracts in Mathematics, 121. Cambridge
-%University Press, 1996.
-%
-%\bibitem{BRY}
-%J. Bertoin, B. Roynette and M. Yor,
-%\emph{Some connections between (sub)critical branching mechanisms and Bernstein functions}.
-%arXiv:0412322.
-%
-%
-%\bibitem{ChenRenWang2008An-almost}
-%  Z.-Q. Chen, Y.-X. Ren, and H. Wang,
-%  \emph{An almost sure scaling limit theorem for {D}awson-{W}atanabe superprocesses},
-%  J. Funct. Anal. \textbf{254} (2008), no. 7, 1988--2019.
-%
-% \bibitem{ChenRenSongZhang2015Strong-law}
-%   Z.-Q. Chen, Y.-X. Ren, R. Song, and R. Zhang,
-%   \emph{Strong law of large numbers for supercritical superprocesses under second moment condition},
-%   Front. Math. China \textbf{10} (2015), no. 4, 807--838.
-%
-% \bibitem{ChenRenYang2019Skeleton}
-%   Z.-Q. Chen, Y.-X. Ren, and T. Yang,
-%   \emph{Skeleton decomposition and law of large numbers for supercritical superprocesses},
-%   Acta Appl. Math. \textbf{159} (2019), 225--285.
-%
 \bibitem{Dudley2002}
-  R. M. Dudley
+  R. M. Dudley,
 \emph{Real Analysis and Probability},
@@
 
-% \bibitem{Durrett2010Probability}
-%   R. Durrett,
-%   \emph{Probability: theory and examples},
-%   Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
+\bibitem{Dynkin1993Superprocesses}
+  E. B. Dynkin,
+  \emph{Superprocesses and partial differential equations},
+  Ann. Probab. \textbf{21} (1993), no. 3, 1185--1262.
 
-%\bibitem{Dynkin1993Superprocesses}
-  %E. B. Dynkin,
-  %\emph{Superprocesses and partial differential equations},
-  %Ann. Probab. \textbf{21} (1993), no. 3, 1185--1262.
-%
-%\bibitem{EckhoffKyprianouWinkel2015Spines}
-%  M. Eckhoff, A. E. Kyprianou, and M. Winkel,
-%  \emph{Spines, skeletons and the strong law of large numbers for superdiffusions},
-%  Ann. Probab. \textbf{43} (2015), no. 5, 2545--2610.
-%
-%\bibitem{Englander2009Law}
-%  J. Engl\"{a}nder,
-%  \emph{Law of large numbers for superdiffusions: the non-ergodic case},
-%  Ann. Inst. Henri Poincar\'{e} Probab. Stat. \textbf{45} (2009), no. 1, 1--6.
-%
-%\bibitem{EnglanderWinter2006Law}
-%  J. Engl\"{a}nder and A. Winter,
-%  \emph{Law of large numbers for a class of superdiffusions},
-%  Ann. Inst. H. Poincar\'{e} Probab. Statist. \textbf{42} (2006), no. 2, 171--185.
-%
-%\bibitem{EnglanderTuraev2002A-scaling}
-%  J. Engl\"{a}nder and  D. Turaev,
-%  \emph{A scaling limit theorem for a class of superdiffusions},
-%  Ann. Probab. \textbf{30} (2002), no. 2, 683--722.
-%
 \bibitem{Heyde1970A-rate}
@@
   C. C. Heyde,
-    \emph{some central limit analogues for supercritical {G}alton-{W}atson processes},
+   \emph{Some central limit analogues for supercritical {G}alton-{W}atson processes},
   J. Appl. Probability \textbf{8} (1971), 52--59.
@@
 
-%\bibitem{IksanovKoleskoMeiners2018Stable-like}
-%  A. Iksanov, K. Kolesko, and M. Meiners,
-%  \emph{Stable-like fluctuations of {B}gins' martingales},
-%  Stochastic Process. Appl. (2018).
-%
-%\bibitem{Janson2004Functional}
-%  S. Janson,
-%  \emph{Functional limit theorems for multitype branching processes and generalized {P}\'{o}lya urns},
-%  Stochastic Process. Appl. \textbf{110} (2004), no. 2, 177--245.
-
 \bibitem{KestenStigum1966Additional}
@@
 
-%\bibitem{KouritzinRen2014A-strong}
-%  M. A. Kouritzin, and Y.-X. Ren,
-%  \emph{A strong law of large numbers for super-stable processes},
-%  Stochastic Process. Appl. \textbf{121} (2014), no. 1, 505--521.
-%
 \bibitem{Kyprianou2014Fluctuations}
@@
   Probability and its Applications (New York). Springer, Heidelberg, 2011.
-
-%\bibitem{LiuRenSong2009Llog}
-%  R.-L. Liu, Y.-X. Ren, and R. Song,
-%  \emph{{$L\log L$} criterion for a class of superdiffusions},
-%  J. Appl. Probab. \textbf{46} (2009), no. 2, 479--496.
-%
-%\bibitem{LiuRenSong2013Strong}
-%  R.-L. Liu, Y.-X. Ren, and R. Song,
-%  \emph{Strong law of large numbers for a class of superdiffusions},
-%  Acta Appl. Math. \textbf{123} (2013), 73--97.
 
@@
 
-%\bibitem{RenSongSun2017Spine}
-%  Y.-X. Ren, R. Song, and Z. Sun,
-%  \emph{Spine decompositions and limit theorems for a class of critical superprocesses},
-%  Acta Appl. Math. (2019).
-%
-%\bibitem{RenSongSun2018Limit}
-%  Y.-X. Ren, R. Song, and Z. Sun,
-%  \emph{Limit theorems for a class of critical superprocesses with stable branching},
-%  arXiv:1807.02837.
-%
 \bibitem{RenSongSunZhao2019Stable}
@@
 
-%\bibitem{RenSongZhang2017Functional}
-%  Y.-X. Ren, R. Song, and R. Zhang,
-%  \emph{Functional central limit theorems for supercritical superprocesses},
-%  Acta Appl. Math. \textbf{147} (2017), 137--175.
-%
-%\bibitem{Sato2013Levy}
-%  K. Sato,
-%  \emph{L{\'e}vy processes and infinitely divisible distributions},
-%  Translated from the 1990 Japanese original. Revised by the author. Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.
-%
-%\bibitem{SchillingSongVondravcek2010Bernstein}
-%  R. L. Schilling, R. Song, and Z. Vondra\v{c}ek,
-%  \emph{Bernstein functions.}
-%  Theory and applications. Second edition. De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2012.
-%
-%\bibitem{SteinShakarchi2003Complex}
-%  E. M. Stein and R. Shakarchi, \emph{Complex analysis},
-%  Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.
-%
-%\bibitem{Wang2010An-almost}
-%  L. Wang, \emph{An almost sure limit theorem for super-{B}rownian motion},
-%  J. Theoret. Probab. \textbf{23} (2010), no. 2, 401--416.
-
 \end{thebibliography}

### 2020-05-28 supCLT-ind-ECP.tex
add supCLT-ind-ECP.tex

--- 2020-05-23 supCLT-ind11.tex
@@
-%supCLT-ind1.tex ?/?/? by Jianjie
-%supCLT-ind2.tex ?/?/? by ?
-%supCLT-ind3.tex 03/05/2020 by Renming
-%supCLT-ind4.tex 11/05/2020 by Zhenyao
-%supCLT-ind5.tex 14/05/2020 by Yanxia
-%supCLT-ind6.tex 16/05/2020 by JianJie
-%supCLT-ind7.tex 17/05/2020 by Renming
-%supCLT-ind8.tex 20/05/2020 by Zhenyao
-%supCLT-ind9.tex 21/05/2020 by Yanxia
-%%supCLT-ind10.tex 22/05/2020 by Jianjie
-%%supCLT-ind11.tex 22/05/2020 by Renming
-%%supCLT-ind12.tex 23/05/2020 by Zhenyao
 \documentclass[12pt,a4paper]{amsart}
@@
 \usepackage{mathrsfs}
-%\usepackage[backref]{hyperref}
 \usepackage{hyperref}
-%\usepackage[inline]{showlabels}
-\usepackage{comment}
-%\usepackage{xcolor}
 \usepackage{amsthm}
@@
 \title
-[stable CLT for super-OU processes]
+[stable CLT for super-OU processes, II]
 {Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II}
@@
 \email{zhenyao.sun@gmail.com}
+\thanks{Zhenyao Sun is the corresponding author}
 \address{
@@
 \begin{abstract}
-This paper is a continuation of our recent paper (Elect. J. Probab. \textbf{24} (2019), no. 141)
-and is devoted to the  asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
-In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth
-in three different regimes. However, we were not able to prove
-central limit theorems for
-$X_t(f) $ for {\it all} functions $f$ of polynomial growth.
+This paper is a continuation of our recent paper (Elect.
+J.
+Probab.
+\textbf{24} (2019), no.
+141) and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
+In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth in three different regimes.
+However, we were not able to prove central limit theorems for $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
 In this note, we show that the limit stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
@@
 
-There are also  central  limit theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment. For earlier
-papers, \cite{Heyde1971Some, Asmussen76Convergence}.
+There are also  central  limit theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment. 
+For earlier papers, see \cite{Asmussen76Convergence, Heyde1971Some}. 	
 Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} established some spatial central limit theorems in the small and critical branching rate regimes, for
@@
   	Z_t f
-  	%:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,\quad
   	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,\quad
@@
 \]
-% Using this and continuity, we get that there exists {\color{blue}$C_1>0$} such that for all $|y|\geq 1$,
 Using this and continuity, we get that there exists $C_1>0$ such that for all $|y|\geq 1$,
@@
 \begin{proof}
-%In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}(\cdot)$.
 In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
@@
 \]
-%Using Corollary \ref{cor:MI} 
 Using Proposition \ref{cor:MI} 
@@
   \end{align}
-%Next, we claim that
 We claim that
@@
   \\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
-  % \\&\overset{Lemma \ \ref{ineq: analysis}}
   \\&\overset{\text{Lemma \ref{ineq: analysis}}}
@@
   d(\mu_1,\mu_2)
-  %:=\sup\Big\{\Big|\int fd\mu_1-\int f d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
   :=\sup\Big\{\Big|\int f \mathrm d\mu_1-\int f \mathrm d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
@@
 Then $S(t+r)=S(t,r)+\widetilde{S}(t,r)$.
-%Let us claim that
 We claim that
@@
 	$\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, 
-	%and $\widetilde H_t$ is independent of $(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$.
-	and $\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent of each other.
+	and $\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
 \end{minipage}
@@
 \\& \overset{\text{Theorem \ref{thm: II}}}=  \mathbb P_{\mu}\Big[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \Big]\Big(\prod_{j=\mathrm s,\mathrm c}\exp\{m[\theta_j f_j]\}\Big)\exp\{m[-\theta_\mathrm l f_\mathrm l]\}
-%\\&=\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\Big[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\mathbb P_{\mu}(D^c|\mathscr F_t) \Big]\Big(\prod_{j=\mathrm s,\mathrm c}\exp\{m[\theta_j f_j]\}\Big)\exp\{m[-\theta_\mathrm l f_\mathrm l]\}
 \\&=\widetilde{\mathbb P}_{\mu}[\exp\{i\theta e^{-\alpha t}\|X_t\|\}]

### 2020-09-05 supCLT-ind-ECP.tex
Update subCLT-ind-ECP.tex

@@
 Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of the limit of $\Upsilon^f_t$.
-For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$.
+%{
+%For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$.
+For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ such that $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$.
+%}
 The following generalization of
@@
 
-\begin{prop}
-  \label{cor:MI}
+\begin{prop} \label{cor:MI}
+%{
+	% For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1+1$, we have
 	For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for
-all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1+1$, we have
+	all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1+1$, we have
+%}
 \begin{equation}
@@
 \begin{proof}
-	In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1 + 1$.
+%{
+	% In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1 + 1$.
+	In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1 + 1$.
+%}
  	For any $k_1 \in \{-1,0,\dots,n_1\}$ and $k_2 \in \{-1,0,\dots,n_2\}$,  define
@@
     \overset{\eqref{eq:MI.1}}\leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}]\big|\Big]
-    \\&\label{eq:MI.15}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_0 e^{-\delta_0 (t+k_2)}.
+%{
+    %\\&\label{eq:MI.15}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_0 e^{-\delta_0 (t+k_2)}.
+    \\&\label{eq:MI.15}\overset{\text{Proposition \ref{thm:Key}}}\leq C_0 e^{-\delta_0 (t+k_2)}.
+%}
 \end{align}
@@
     \overset{\eqref{eq:MI.2}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{f_{k_1}}_{t-k_1-1}}-e^{\langle Z_1f_{k_1}, \varphi\rangle}; D^c|\mathscr F_{t-k_1-1}]\big|\Big]
-    \\&\label{eq:MI.25}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_1 e^{-\delta_1 (t-k_1)}.
+    %{ \\&\label{eq:MI.25}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_1 e^{-\delta_1 (t-k_1)}.
+    \\&\label{eq:MI.25}\overset{\text{Proposition \ref{thm:Key}}}\leq C_1 e^{-\delta_1 (t-k_1)}.
+    %}
 \end{align}
@@
 \]
-Using Proposition \ref{cor:MI} 
-with $f=\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c}$ and $g = -\tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that
-for every $t\geq 1$,
+%{
+	% Using Proposition \ref{cor:MI} with $f=\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c}$ and $g = -\tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that for every $t\geq 1$,
+	Using Proposition \ref{cor:MI} with $f=\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g = \tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that for every $t\geq 1$, 
   \begin{align}
@@
 
+%{
+\appendix
+\section{}
+\begin{lem}
+	\label{lem:P:R}
+	Suppose that $g = g_\mathrm s + g_\mathrm c + g_\mathrm l$ such that $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$. 
+	Then there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g := \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
+\end{lem}
+\begin{proof}
+	We write $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
+	We need to prove that there exists $h \in \mathcal P^+$ such that for each $f\in \overline{\mathcal P}_g$, $|P_tq_f| \leq e^{-bt} h$.
+
+	\emph{Step 1. We show that $\overline {\mathcal P}_g \subset C_\infty (\mathbb R^d) \cap \mathcal P$.}
+	In fact, for each $f \in \overline {\mathcal P}_g$, there exists $n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]$ such that
+	\[
+	f
+	= \theta_\mathrm s e^{\alpha \tilde \beta n}P_n g_\mathrm s +  \theta_\mathrm c e^{\alpha \tilde \beta n}P_n g_\mathrm c + \theta_\mathrm l \sum_{p \in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} \langle g_\mathrm l, \phi_p \rangle_\varphi e^{-(\alpha \tilde \beta - |p|b)s} \phi_p.
+	\]
+	Notice that the third term is in $C_\infty(\mathbb R^d)\cap \mathcal P$ since it is a finite sum of polynomials, and the first two terms are also in $C_\infty (\mathbb R^d) \cap \mathcal P$ according to \cite[Fact 1.1]{MarksMilos2018CLT}.
+
+	\emph{Step 2. We show that there exists $h_2 \in \mathcal P^+$ such that for any $j\in \{1,\dots, d\}$ and $f\in \overline{\mathcal P}_g$ it holds that $|\partial_j f| \leq h_2$.}
+	In fact, it is known that  (see \cite{MetafunePallaraPriola2002Spectrum} for example)
+	\begin{align}
+	\label{eq:P:R:3:-1}
+	P_t f(x)
+	= \int_{\mathbb R^d} f\big(x e^{-bt} + y \sqrt{1-e^{-2bt}}\big) \varphi(y)~dy,
+	\quad t\geq 0, x\in \mathbb R^d, f\in \mathcal P.
+	\end{align}
+	For $f\in C_\infty(\mathbb R^d)\cap \mathcal P$ it can be verified from above that
+	\begin{align}
+	\label{eq:P:R:3:1}
+	\partial_j P_t f
+	= e^{-bt} P_t \partial_j f,
+	\quad t \geq 0, j \in \{1,\dots, d\}.
+	\end{align}
+	Thanks to Step 1, $T_1 g_\mathrm s \in C_\infty(\mathbb R^d)\cap \mathcal P$.
+	According to \cite[Fact 1.3]{MarksMilos2018CLT} and the fact that $\alpha \tilde \beta \leq \kappa _{g_\mathrm s} b$, we have for each $j \in \{1,\dots, d\}$,
+	\[
+	\kappa_{(\partial_j T_1 g_\mathrm s)}
+	\geq \kappa_{(T_1 g_\mathrm s)} - 1
+	= \kappa_{g_\mathrm s} - 1
+	\geq \frac{\alpha \tilde \beta}{b} - 1.
+	\]
+	Therefore, there exists  $h'_2\in \mathcal P^+$ such that for all $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
+	\begin{align}
+	& | \partial_j T_{n+1}g_\mathrm s |
+	= | \partial_j e^{\alpha \tilde \beta n}P_n T_1g_\mathrm s |
+	= e^{\alpha \tilde \beta n-bn} |P_n \partial_j T_1 g_\mathrm s| \\
+	& \leq e^{\alpha \tilde \beta n-bn} \exp\{-\kappa_{(\partial_j T_1 g_\mathrm s)}bn\}Q \partial_j T_1g_\mathrm s
+	\leq Q\partial_j T_1g_\mathrm s
+	\leq h'_2,
+	\end{align}
+	where operator $Q$ is given by \cite[(2.3)]{RenSongSunZhao2019Stable}.
+	With the exact same reason there exists $h''_2 \in \mathcal P^+$ such that for all $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
+\[
+	| \partial_j T_{n+1}g_\mathrm c| \leq h''_2
+\]
+	On the other hand, there exists $h_2'''\in \mathcal P^+$ such that for all $n \in \mathbb Z_+$ and $j\in \{1,\dots,d\}$,
+	\begin{align}
+	& |\partial_j T_{n+1}g_\mathrm l |
+	= \Big| \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} e^{- (\alpha \tilde \beta - |p|b)(n+1)} \langle g_\mathrm l, \phi_p \rangle_\varphi \partial_j \phi_p \Big| \\
+	& \leq \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b} |\langle g_\mathrm l, \phi_p \rangle_\varphi \partial_j \phi_p |
+	\leq h_2'''.
+	\end{align}
+	Then the desired result in this step follows.
+
+	\emph{Step 3.
+We show that there exists $h_3 \in \mathcal P^+$ such that for all $j \in \{1,\dots, d\}$, $u \in [0, 1]$ and $f\in \overline{\mathcal P}_g$, it holds that $ | \partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta} | \leq h_3$.
+}
+	In fact, thanks to Step 2 and \eqref{eq:P:R:3:1}, for all $j \in \{1,\dots, d\}, u \in [0, 1]$ and $f\in \overline{\mathcal P}_g$, we have
+	\begin{align}
+	& \partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta}
+	= e^{-(1-u)b} P_{1-u}^\alpha \partial_j (- i P_u^\alpha f)^{1+\beta}
+	\\ & = (1+\beta) e^{-(1-u)b} P_{1-u}^\alpha [ (- i P_u^\alpha f)^\beta \partial_j (- i P_u^\alpha f) ]
+	\\ & = -i(1+\beta) e^{-(1-u)b} P_{1-u}^\alpha[ (- i P_u^\alpha f)^\beta e^{-ub} P_u^\alpha \partial_j f]
+	\\ & = -i(1+\beta) e^{-b} e^{(1-u)\alpha} e^{u\alpha (1+\beta)} P_{1-u} [ (- i P_u f)^\beta P_u \partial_j f ].
+	\end{align}
+	Recall from Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable} there exists $h'_3\in \mathcal P^+$ such that for all $f\in \overline{\mathcal P}_g$ we have $|f| \leq h'_3$.
+	Therefore, using Step 2, we have for all $j \in \{1,\dots, d\}$ and $u \in [0, 1]$,
+	\begin{align}
+	& |\partial_j  P_{1-u}^\alpha (- i P_u^\alpha f)^{1+\beta}|
+	\leq (1+\beta) e^{\alpha (1+\beta)} P_{1-u} [  (P_u |f|)^\beta P_u |\partial_j f| ]
+	\\ & \leq (1+\beta) e^{\alpha (1+\beta)} P_{1-u} [  (P_u h'_3)^\beta P_u h_2 ]
+	\leq (1+\beta) e^{\alpha (1+\beta)} Q_0 [  (Q_0 h'_3)^\beta Q_0 h_2 ],
+	\end{align}
+	where $Q_0$ is defined by \cite[(2.3)]{RenSongSunZhao2019Stable}.
+	This implies the desired result in this step.
+
+	\emph{Step 4. We show that there exists $h_4 \in \mathcal P^+$ such that for any $f \in \overline {\mathcal P}_g$ we have $ |\nabla (Z_1f)| \leq h_4$.}
+	In fact, according to Step 3, for all $j \in \{1,\dots, d\}$ and compact $A \subset \mathbb R^d$, we have
+	\[
+	\int_0^1 \sup_{x\in A} | (\partial_j  P_{1-u}^\alpha (-i P_u^\alpha f)^{1+\beta}) (x) |~du
+	\leq \sup_{x\in A} h_3(x) < \infty.
+	\]
+	Using this and \cite[Theorem A.5.2]{Durrett2010Probability}, for all $j \in \{1,\dots, d\}$ and $x\in \mathbb R^d$, it holds that
+	\[
+	| \partial_j Z_1 f(x)|
+	= \Big| \int_0^1  ( \partial_jP_{1-u}^\alpha (-iP_u^\alpha f)^{1+\beta} ) (x) ~du  \Big|
+	\leq h_3(x).
+	\]
+	Now, the desired result for this step is valid.
+
+	\emph{Step 5. We finish the proof.}
+	Note that there are $c_0, n_0> 0$ such that for all $x\in \mathbb R^d$, $h_4(x) \leq c_0(1+|x|)^{n_0}$.
+	Also note that for all $x, y \in \mathbb R^d$, $1+|x|+|y|\leq (1+|x|) (1+|y|)$; and that for all $\theta \in [0,1]$, $|\sqrt {1 - \theta} - 1| \leq \theta$.
+	Write $D_{x,y} = \{ax+by: a, b \in [0,1]\}$ fo $x, y \in \mathbb R^d$.
+	Using \eqref{eq:P:R:3:-1} and Step 4, there exists  $h_5 \in \mathcal P^+$ such that for all $f\in \overline {\mathcal P}_g$, $t \geq 0$ and $x \in \mathbb R^d$,
+	\begin{align}
+	& |P_t q_f(x)|
+	= \Big| \int_{\mathbb R^d}\big ( (Z_1f)(x e^{-bt}+ y \sqrt{1 - e^{-2bt}}) - (Z_1 f) (y) \big) \varphi(y) ~dy \Big| \\
+	& \leq \int_{\mathbb R^d} \Big(\sup_{z\in D_{x,y}} |\nabla  (Z_1f) (z) |\Big) | x e^{-bt} + y \sqrt{1 - e^{-2bt}} - y | \varphi(y) ~dy \\
+	& \leq e^{-bt} \int_{\mathbb R^d} c_0(1+|x|+|y|)^{n_0} (|x|+|y|) \varphi(y) ~dy \\
+	& \leq c_0 e^{-bt}(1+|x|)^{n_0}\Big(|x|\int_{\mathbb R^d} (1+|y|)^{n_0}\varphi(y) ~dy + \int_{\mathbb R^d} (1+ |y|)^{n_0} |y| \varphi(y) ~dy \Big) \\
+	& \leq e^{-bt} h_5(x).
+	\qedhere
+	\end{align}
+\end{proof}
+
+\begin{prop}
+	\label{thm:Key}
+	For all $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P \setminus \{0\}$, there exist $C,\delta>0$ such that
+	for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
+	\[
+	\mathbb P_\mu
+	\Big[  \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  \big|\Big]
+	\leq C e^{- \delta t}.
+	\]
+\end{prop}
+
+\begin{proof}
+	Fix  $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P\setminus \{0\}$.
+
+	\emph{Step 1. Write $ A_t(\epsilon) :=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \} $ for $t\geq 0$ and $\epsilon > 0$.
+	We will show that for all $f\in \mathcal P \setminus \{0\}$, $\epsilon > 0$ and $t\geq 0$, it holds that
+	\[
+	\mathbb P_\mu \Big[ | \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]| \Big]
+	\leq J^f_1(t,\epsilon)+J^f_2(t,\epsilon)+J^f_3(t,\epsilon),
+	\]
+	where
+	\begin{align}
+	\label{eq: Def of Ji}
+	&J^f_1(t,\epsilon):= \mathbb{P}_{\mu} [ | X_t(Z'''_1(\theta_t f)) |; A_t(\epsilon) ],
+	\quad
+	J^f_2(t,\epsilon):= \mathbb{P}_{\mu}[|X_t( Z_1(\theta_t f))-\langle Z_1f, \varphi\rangle |; A_t(\epsilon)],
+	\\ & J_3(t,\epsilon):=2\mathbb{P}_{\mu}(A_t (\epsilon)\Delta D^c),
+	\quad
+	\theta_t := \|X_t\|^{-(1 - \tilde \beta)}.
+	\end{align}
+}
+	In fact, it follows from \cite[(2.2)]{RenSongSunZhao2019Stable}, the definitions of $U_1$, $Z'''_1$ and $Z_1$, that for all $t\geq 0$,
+\begin{align}
+	\label{eq: need1}
+	& \mathbb{P}_{\mu}[e^{i\Upsilon^f_t}|\mathscr{F}_t]
+	= \mathbb{P}_{\mu}[\exp\{i\theta_t X_{t+1} (f) - i \theta_t X_t(P_1^\alpha f)\} |\mathscr{F}_{t}] \\
+	& = \exp\{X_t((U_1 - iP^\alpha_1 ) (\theta_t f))\}
+	= \exp\{X_t((Z_1 + Z'''_1) (\theta_t f))\}.
+\end{align}
+	From Lemma \cite[Lemma 2.8]{RenSongSunZhao2019Stable}, we  get that $\theta\mapsto \langle Z_1(\theta f),\varphi\rangle$ is the characteristic function of some $(1+\beta)$-stable random variable, and then  $\operatorname{Re} \langle Z_1f, \varphi\rangle \leq 0$.
+	Using this, \eqref{eq: need1}, the fact that $\operatorname{Re} U_tf \leq 0$, and that $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get for each $t\geq 0$ and $\epsilon> 0$,
+	\begin{align}
+	\label{eq: inequality that will used later}
+	& \mathbb{P}_\mu \Big[ \big|  \mathbb{P}_\mu [ e^{i\Upsilon^f_t} - e^{\langle Z_1f,\varphi \rangle} ; D^c | \mathscr F_{t}]  \big |\Big]  \\
+	&  \leq \mathbb{P}_\mu   \Big[ \big|    \mathbb{P}_\mu [ e^{i \Upsilon^f_t }-e^{\langle Z_1f, \varphi\rangle}; A_{t}(\epsilon) | \mathscr F_{t}] \big|  + 2\mathbb P_\mu ( A_{t}(\epsilon) \Delta D^c | \mathscr F_{t}) \Big] \\
+	& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_\mu [e^{i\Upsilon^f_t} | \mathscr F_{t}]-e^{\langle Z_1f, \varphi\rangle}\big| ; A_{t}(\epsilon) \Big] + J_3(t,\epsilon) \\
+	& \leq \mathbb{P}_\mu \Big[ |e^{X_{t}((Z_1+Z'''_1) (\theta_t f))}-e^{\langle Z_1f, \varphi\rangle} | ; A_{t}(\epsilon) \Big]+  J_3(t,\epsilon) \\
+	& \leq \mathbb{P}_\mu \Big[ | X_{t} ( (Z_1+Z'''_1)(\theta_t f)) - \langle Z_1f, \varphi\rangle | ;A_{t}(\epsilon)\Big]+  J_3(t,\epsilon) \\
+	& \leq J^f_1(t,\epsilon) + J^f_2(t,\epsilon)+ J_3(t,\epsilon).
+	\end{align}
+
+	\emph{Step 2. We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for all $t\geq 1$ and
+	$f \in \overline{\mathcal P}_g$, we have $ J^f_1(t,\epsilon) \leq C_2e^{-\delta_2 t}$.}	
+	In fact, let $\delta_0 >0$ be the constant in \cite[Lemma 2.5.(7)]{RenSongSunZhao2019Stable} and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
+	Acording to Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, there exists $h_{2} \in \mathcal P^+$ such that for each $f \in \overline{\mathcal P}_g$ it holds that $|f| \leq h_{2}$.
+	Then, we have for all $t\geq 0$, $\epsilon> 0$ and $f\in \overline{\mathcal P}_g$,
+	\begin{align}
+	& |Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
+	\leq R(|\theta_{t} f|)\mathbf{1}_{A_{t}(\epsilon)}
+	\leq R \Big(\frac{h_{2}}{e^{(\alpha-\epsilon)t(1-\tilde \beta)}}\Big)
+	\leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}Rh_{2}.
+	\end{align}
+	Thus for all $t\geq 0$, $\epsilon> 0$ and $f\in \overline{\mathcal P}_g$,
+	\begin{align}
+	\label{eq: estimate of J1}
+	J^f_1(t,\epsilon)
+	& \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
+	\leq \sum_{\rho \in \{\delta_0,1\}} \mu(Q_0 R h_{2}) e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
+	\end{align}
+	where $Q_0$ is defined by \cite[(2.3)]{RenSongSunZhao2019Stable}.
+	By taking $\epsilon>0$ small enough, we get the desired result in this step.
+
+	\emph{Step 3.
+	We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for all $t \geq 0$ and $f\in \overline{\mathcal P}_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.}
+	In fact, for all $t\geq 0$, and $f\in \overline{\mathcal P}_g$,
+	\begin{align}
+	& X_{t}(Z_1(\theta_t f))- \langle Z_1f, \varphi\rangle
+	= \theta_t^{1+\beta} X_t(Z_1 f) - \langle  Z_1 f,\varphi \rangle
+	= \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle),
+	\end{align}
+	and therefore,
+	\begin{align}
+	\label{eq: prevJ2}
+	J^f_2(t,\epsilon)
+	& = \mathbb P_\mu\Big[\Big|  \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle) \Big|;A_t(\epsilon)\Big]
+	\leq e^{-(\alpha-\epsilon)t} \mathbb{P}_{\mu}[|X_t (q_f) |].
+	\end{align}
+	where $ q_f = Z_1 f-\langle  Z_1 f,\varphi\rangle \in \mathcal P^*$.
+	It follows from Lemma \ref{lem:P:R} that there exists $h_{3}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have $Q_1 (\operatorname{Re} q_f) \leq h_{3} \text{ and } Q_1 (\operatorname{Im} q_f)\leq h_3$, where $Q_1$ is given by \cite[(2.3)]{RenSongSunZhao2019Stable} with $\kappa=1$.
+	In the rest of this step, we  fix a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
+	According to \cite[Lemma 2.14.(3)]{RenSongSunZhao2019Stable} (with $\kappa=1$), there exists $C_{3}>0$ such that for all $t\geq 0$ and $f\in \overline{\mathcal P}_g$,
+	\begin{align}
+	& \mathbb{P}_{\mu}\left[\left|X_{t}(q_f)\right|\right]
+	\leq \| X_{t}( \operatorname{Re} q_f)\|_{\mathbb{P}_{\mu,1+\gamma}} + \| X_{t}(\operatorname{Im} q_f)\|_{\mathbb{P}_{\mu,1+\gamma}} \\
+	& \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{3}} \|X_t(q)\|_{\mathbb P_\mu; 1+\gamma} \leq C_{3} e^{\frac{\alpha t}{1+\gamma}}.
+	\end{align}
+	Therefore, for all $t\geq 0, \epsilon > 0$ and $f \in \overline{\mathcal P}_g$, we have
+	\begin{align}
+	\label{eq: right bound for J2}
+	J^f_2(t, \epsilon)
+	\leq  C_3 e^{-(\alpha-\epsilon)t}e^{\frac{\alpha t}{1+\gamma}}
+	\leq C_{3} e^{-(\alpha\tilde \gamma -\epsilon)t}.
+	\end{align}
+	By taking $\epsilon >0$ small enough, we get the required result in this step.
+
+	\emph{Step 4. We finish the proof.}
+	Note that, from Step 4 of the proof of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, we have for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_4>0$ such that for all $t\geq 1$, $J_3(t,\epsilon)\leq C_4e^{-\delta_4 t}.$
+	Now combine this with the results in Step 1--3, we  immediately get the desired result.
+\end{proof}
+%}
+
 \begin{thebibliography}{10}
@@
   Cambridge University Press, 2002.
+
+  \bibitem{Durrett2010Probability}
+ R. Durrett,
+ \emph{Probability: theory and examples},
+ Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
 

### 2020-09-12 supCLT-ind-ECP-3.tex
update subCLT-ind-ECP-3.tex

--- 2020-09-05 supCLT-ind-ECP.tex
@@
 \usepackage{amsthm}
+\usepackage{comment}
 \theoremstyle{plain}
@@
 However, we were not able to prove central limit theorems for $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
-In this note, we show that the limit stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
+%{
+	%In this note, we show that the limit stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
+	In this note, we show that the limiting stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
+%}
 \end{abstract}
@@
  $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y \pi(\mathrm dy) < \infty. $
-In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
+%{
+	% In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
+	In the remainder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
+%}
 	Note that $\delta$ is not uniquely determined by $\pi$.
@@
 	For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
-	Futhermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
+%{	
+	% Futhermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
+	Furthermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
+%}
 	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
@@
 \end{align}
-For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write
-$\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
-We have shown in \cite[Lemma 2.6 and Propsoition 2.7]{RenSongSunZhao2019Stable} that,
+	For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
+%{
+	% We have shown in \cite[Lemma 2.6 and Propsoition 2.7]{RenSongSunZhao2019Stable} that,
+	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
+%}
 \begin{equation} \label{eq:I:R:3}
 \begin{minipage}{0.9\textwidth}
-for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function
-$
-\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,
-$
-where
+	for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,$ where
 \begin{equation}
@@
 \]
-	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}.
+%{	
+	% where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}.
+	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variable described in \eqref{eq:I:R:3}.
+%}
 \end{enumerate}
@@
 Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of the limit of $\Upsilon^f_t$.
-%{
-%For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$.
 For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ such that $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$.
-%}
 The following generalization of
@@
 \begin{prop} \label{cor:MI} 
-%{
-	% For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1+1$, we have
 	For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for
 	all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1+1$, we have
-%}
 \begin{equation}
@@
 \begin{proof}
-%{
-	% In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1 + 1$.
 	In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1 + 1$.
-%}
  	For any $k_1 \in \{-1,0,\dots,n_1\}$ and $k_2 \in \{-1,0,\dots,n_2\}$,  define
@@
   Then for all  $k_2 \in \{0,\dots,n_2\}$, we have
-\begin{align}
-&a_{-1,k_2} - a_{-1,k_2-1}
-\\& \begin{multlined}
-	=\mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
-	\\- \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2 - 1}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
-\end{multlined}
-	\\& \begin{multlined}
-	= \frac{1}{\mathbb{P}_{\mu}(D^c)} \Big(\prod_{j=k_2+1}^{ n_2} e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
-	\\ \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big) \Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) (e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle});D^c\Big]
-	\end{multlined}
-	\\ \label{eq:MI.1}& \begin{multlined}
-	= \frac{1}{\mathbb{P}_{\mu}(D^c)}  \Big(\prod_{j=k_2+1}^{n_2}e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
+%{
+%\begin{align}
+\begin{equation}
+	%& a_{-1,k_2} - a_{-1,k_2-1}
+%\\& \begin{multlined}
+	%=\mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
+	%\\- \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2 - 1}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
+%\end{multlined}
+	%\\& \begin{multlined}
+	%= \frac{1}{\mathbb{P}_{\mu}(D^c)} \Big(\prod_{j=k_2+1}^{ n_2} e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
+	%\\ \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big) \Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) (e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle});D^c\Big]
+	%\end{multlined}
+	\label{eq:MI.1} \begin{multlined}
+	 a_{-1,k_2} - a_{-1,k_2-1} = \frac{1}{\mathbb{P}_{\mu}(D^c)}  \Big(\prod_{j=k_2+1}^{n_2}e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
 	\\ \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big)\Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) \mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}] \Big].
 	\end{multlined}
-\end{align}
-	Therefore, there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$,
-  such that  for each $k_2 \in \{0, \dots, n_2 \}$,
+%\end{align}
+\end{equation}
+%}
+%{
+	% Therefore, there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$, such that  for each $k_2 \in \{0, \dots, n_2 \}$,
+	By Proposition \ref{thm:Key}, there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$, such that  for each $k_2 \in \{0, \dots, n_2 \}$,
+%}
 \begin{align}
@@
 %{ 
-    %\\&\label{eq:MI.15}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_0 e^{-\delta_0 (t+k_2)}.
-    \\&\label{eq:MI.15}\overset{\text{Proposition \ref{thm:Key}}}\leq C_0 e^{-\delta_0 (t+k_2)}.
-%}
-\end{align}
-	Notice that, for any $k_1 \in \{0, \dots , n_1\}$,
-	\begin{align}
-	&a_{k_1-1,-1} - a_{k_1,-1}
-	\\ & \begin{multlined}
-	=  \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) - {}
-	\\ \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
-	\end{multlined}
-	\\& =  \mathbb{\widetilde{P}}_{\mu}\Big[ \big(e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle} \big) \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
-	\\& \label{eq:MI.2}\begin{multlined}
+    %\\&\label{eq:MI.15}\overset{\text{Proposition \ref{thm:Key}}}\leq C_0 e^{-\delta_0 (t+k_2)}. 
+    \\&\label{eq:MI.15} \leq C_0 e^{-\delta_0 (t+k_2)}. 
+%}
+\end{align}
+%{
+	%Notice that, for any $k_1 \in \{0, \dots , n_1\}$,
+	Similarly, for any $k_1 \in \{0, \dots , n_1\}$,
+%}
+%{
+%\begin{align}
+\begin{equation}
+	% &a_{k_1-1,-1} - a_{k_1,-1}
+	%\\ & \begin{multlined}
+	%=  \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) - {}
+	%\\ \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
+	%\end{multlined}
+	%\\& =  \mathbb{\widetilde{P}}_{\mu}\Big[ \big(e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle} \big) \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
+	%\\& \label{eq:MI.2}
+	\label{eq:MI.2}
+	\begin{multlined}
+	a_{k_1-1,-1} - a_{k_1,-1}
 	=  \frac{1}{\mathbb P_\mu(D^c)} \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) \times {}
@@
 	\end{multlined}
-	\end{align}
-	Therefore,  there exist $C_1,\delta_1 >0$, depending only on $\mu$ and $f$,
-	such that for any $k_1 \in \{0,\dots,n_1\}$,
+%\end{align}
+\end{equation}
+%}
+%{
+	% Therefore,  there exist $C_1,\delta_1 >0$, depending only on $\mu$ and $f$, such that for any $k_1 \in \{0,\dots,n_1\}$,
+	By proposition \ref{thm:Key}, there exist $C_1,\delta_1 >0$, depending only on $\mu$ and $f$, such that for any $k_1 \in \{0,\dots,n_1\}$,
+%}
 \begin{align}
@@
     \overset{\eqref{eq:MI.2}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{f_{k_1}}_{t-k_1-1}}-e^{\langle Z_1f_{k_1}, \varphi\rangle}; D^c|\mathscr F_{t-k_1-1}]\big|\Big]
-    %{ \\&\label{eq:MI.25}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_1 e^{-\delta_1 (t-k_1)}.
-    \\&\label{eq:MI.25}\overset{\text{Proposition \ref{thm:Key}}}\leq C_1 e^{-\delta_1 (t-k_1)}.
-    %}
+    \\&\label{eq:MI.25} \leq C_1 e^{-\delta_1 (t-k_1)}.
 \end{align}
@@
 	we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$,  $f_\mathrm c\in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l\in \mathcal C_\mathrm l\setminus\{0\}$.
+%{
+\begin{comment}
 	For any random variable $Y$ with finite mean under $\mathbb P_\mu$, we define
@@
 \begin{align}
-     I^{f_\mathrm s}(t) &:= \frac{X_t(f_\mathrm s)}{\|X_t\|^{1- \tilde \beta }}  = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
-        \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}  \Big)
-    + \Big( \frac{X_0(P_t^\alpha f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}\Big),
+	I^{f_\mathrm s}(t) 
+	&:= \frac{X_t(f_\mathrm s)}{\|X_t\|^{1- \tilde \beta }}  = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
+    \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}  \Big) + \Big( \frac{X_0(P_t^\alpha f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}\Big),
     \\ I^{f_\mathrm c}(t)&:=\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}} = I^{f_\mathrm c}_1(t) + I^{f_\mathrm c}_2(t) + I^{f_\mathrm c}_3(t)
@@
 	where $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
+\end{comment}
 	For every $t\geq 1$, define
 \begin{align}
-	R_j(t)&:=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big), \quad j = 1,2,3,
-	\\ R(t)&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
-    \\R_0(t)&=\big(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t)\big)
+	%R_j(t)
+	%&:=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big), \quad j = 1,2,3,
+	%\\ 
+	R(t)
+	&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
+    \\R_0(t)
+    &=\big(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t)\big)
     \\&:=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
 \end{align}
-where 
- $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
-$\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
+	where $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
 	The following result is a special case of Theorem \ref{thm:M}.
@@
 In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
+%{
+\begin{comment}
 	Note that for each $t\geq 1$,
 \[
-R(t)=R_0(t)+\big(R_1(t)-R_0(t)\big)+R_2(t)+R_3(t).
+	R(t)
+	= R_0(t) + \big( R_1(t)-R_0(t) \big) + R_2(t) + R_3(t).
 \]
 	Note that
-$$
-(R_1(t)-R_0(t))=(I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t), I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t), I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)).
-$$
-In the proof of Theorem 1.6(1) in \cite{RenSongSunZhao2019Stable}, we proved that
-$I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
- In the proof of Theorem 1.6(2) in \cite{RenSongSunZhao2019Stable}, we proved that
- $I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
-In the proof of Theorem 1.6(3) in \cite{RenSongSunZhao2019Stable}, we proved that
-$I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$ and  $I_2^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$.
-Thus we have 
-$R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d} (0,0,0)$, $R_2(t)\xrightarrow[t\to \infty]{d}(0,0,0)$ and
-$R_3(t)\xrightarrow[t\to \infty]{d}(0,0,0)$.
+\[
+	(R_1(t)-R_0(t))
+	=(I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t), I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t), I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)).
+\]
+	In the proof of Theorem 1.6(1) in \cite{RenSongSunZhao2019Stable}, we proved that $I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
+	In the proof of Theorem 1.6(2) in \cite{RenSongSunZhao2019Stable}, we proved that $I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
+	In the proof of Theorem 1.6(3) in \cite{RenSongSunZhao2019Stable}, we proved that $I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$ and  $I_2^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$.
+	Thus we have $R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d} (0,0,0)$, $R_2(t)\xrightarrow[t\to \infty]{d}(0,0,0)$ and $R_3(t)\xrightarrow[t\to \infty]{d}(0,0,0)$.
 	Combining the above results and using Slutsky's theorem, we only need to  show that, under $\mathbb{\widetilde{P}}_{\mu}$,
-\begin{equation}
-\label{lem:UOT}R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
-\end{equation}
+\begin{equation} \label{lem:UOT}
+	R_0(t) 
+	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
+\end{equation}
+\end{comment}
+	According to the proof of Theorem 1.6 in \cite{RenSongSunZhao2019Stable}, and the fact that the convergence in probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
+\[
+	R(t)-R_0(t) \xrightarrow[t\to \infty]{\text{in probability}} 0.
+\]
+	With the help of Slutsky's theorem, what is left to show is that,
+\begin{equation} \label{lem:UOT}
+	R_0(t) 
+	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
+\end{equation}
+%}
 
@@
 \[
-\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
-\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
+	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
 	= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
@@
 %{
-	% Using Proposition \ref{cor:MI} with $f=\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c}$ and $g = -\tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that for every $t\geq 1$,
-	Using Proposition \ref{cor:MI} with $f=\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g = \tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that for every $t\geq 1$, 
+	Note that $\{T_k(\tilde f_\mathrm s + t^{\tilde\beta - 1}\tilde f_{\mathrm c}):k\in \mathbb Z_+, t\geq 1\}\subset \overline{\mathcal P}_{\tilde f_\mathrm s + \tilde f_{\mathrm c}}$ and $\{-T_k\tilde{f}_{\mathrm l}: k\in \mathbb Z_+\}\subset \overline{\mathcal P}_{\tilde f_\mathrm l}$.
+	%Using Proposition \ref{cor:MI} with $f=\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g = \tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that for every $t\geq 1$, 
+	Therefore, we can use Proposition \ref{cor:MI} with $f$ taking as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taking as $\tilde{f}_{\mathrm l}$, and get that there exist $C_1,\delta_1 > 0$ such that for every $t\geq \lfloor t - \ln t\rfloor +1$,
+%}
   \begin{align}
@@
 \[
-	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
-	\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
+	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
 	 \xrightarrow[t\to \infty]{}
@@
 \]
- Since $I_0^{f_j}(t)$ are linear in 
-     $f_j\in \mathcal C_j (j=\mathrm s,\mathrm c,\mathrm l)$,
- replacing $f_j$ with $\theta_j f_j$, we immediately get 
- \eqref{lem:UOT}.
+	Since $I_0^{f_j}(t)$ are linear in $f_j \in \mathcal C_j~(j=\mathrm s,\mathrm c,\mathrm l)$, replacing $f_j$ with $\theta_j f_j$, we immediately get \eqref{lem:UOT}.
 
@@
 \begin{proof}[Proof of Theorem \ref{thm:M}]
- We first recall some facts about weak convergence which will be used later. For $f:\mathbb R^d\mapsto \mathbb R$, let
- $$
- \|f\|_L:=\sup_{x\neq y}\frac{|f(x)-f(y)|}{|x-y|}
- $$
+ We first recall some facts about weak convergence which will be used later. 
+%{
+	% For $f:\mathbb R^d\mapsto \mathbb R$, let
+	For any bounded Lipschitz function $f:\mathbb R^d\mapsto \mathbb R$, let
+\[
+	\|f\|_L
+	:=\sup_{x\neq y}\frac{|f(x)-f(y)|}{|x-y|}
+\]
 	and $\|f\|_{BL}:= \|f\|_{\infty}+\|f\|_L. $
+%}
 For any probability distributions $\mu_1$ and $\mu_2$ on $\mathbb R^d$, define
@@
 
-%{
 \appendix
@@
 \begin{proof}
+	This can be proved using a similar argument used in the proof of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}.
+\end{proof}
+%{
+\begin{comment}
+\begin{proof}
 	We write $q_f:=Z_1f - \langle Z_1f, \varphi \rangle\in \mathcal P^*$ for each $f\in \mathcal P$.
@@
 \end{proof}
+\end{comment}
+%}
 
@@
 \end{prop}
-
+%{
+\begin{proof}
+	This can be proved by Lemma \ref{lem:P:R} and a similar argument used in the proof of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}.
+\end{proof}
+%}
+%{
+\begin{comment}
 \begin{proof}
@@
 \end{proof}
+\end{comment}
 %}

### 2020-09-25 note.tex
add note.tex

--- 2019-09-10 supCLT.tex
@@
-\documentclass[12pt,a4paper]{amsart}
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-2in}
-\calclayout
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{mathtools}
-\mathtoolsset{showonlyrefs}
-\usepackage{stackrel}
-\usepackage{mathrsfs}
+\documentclass[a4paper,12pt, reqno]{amsart}
+\usepackage{amssymb,amsmath,latexsym}
+\usepackage{color}%cyan,red;magenta,green;yellow,blue
+\usepackage{comment}
+\oddsidemargin 0in
+\evensidemargin 0in
+\topmargin -0.2in
+\textwidth 6.6in
+\textheight 9.6in
+%\def\doublespace{\baselineskip=16pt}
+\def\doublespace{\baselineskip=14pt}
+%\usepackage{hyperref}
+%\usepackage{showkeys}
+\allowdisplaybreaks
+%\def\singlespace{\baselineskip=12pt}
+\def\singlespace{\baselineskip=10pt}
+\newcommand{\red}{\color{red}}
+\newcommand{\blue}{\color{blue}}
+\newcommand{\magenta}{\color{magenta}}
+\newcommand{\normal}{\color{black}}
+\newcommand{\bk}{\color{black}}
+
+%\begin{doublespace}
+
+\def\1{{\bf 1}}
+\def\ind{{\bf 1}}
+\def\nn{\nonumber}
+\def\bee{\begin{equation}}
+\def\eee{\end{equation}}
+\def\sA {{\mathcal A}} \def\sB {{\mathcal B}} \def\sC {{\mathcal C}}
+\def\sD {{\mathcal D}} \def\sE {{\mathcal E}} \def\sF {{\mathcal F}}
+\def\sG {{\mathcal G}} \def\sH {{\mathcal H}} \def\sI {{\mathcal I}}
+\def\sJ {{\mathcal J}} \def\sK {{\mathcal K}} \def\sL {{\mathcal L}}
+\def\sM {{\mathcal M}} \def\sN {{\mathcal N}} \def\sO {{\mathcal O}}
+\def\sP {{\mathcal P}} \def\sQ {{\mathcal Q}} \def\sR {{\mathcal R}}
+\def\sV {{\mathcal V}} \def\sW {{\mathcal W}} \def\sX {{\mathcal X}}
+\def\sY {{\mathcal Y}} \def\sZ {{\mathcal Z}}
+
+\def\bA {{\mathbb A}} \def\bB {{\mathbb B}} \def\bC {{\mathbb C}}
+\def\bD {{\mathbb D}} \def\bE {{\mathbb E}} \def\bF {{\mathbb F}}
+\def\bG {{\mathbb G}} \def\bH {{\mathbb H}} \def\bI {{\mathbb I}}
+\def\bJ {{\mathbb J}} \def\bK {{\mathbb K}} \def\bL {{\mathbb L}}
+\def\bM {{\mathbb M}} \def\bN {{\mathbb N}} \def\bO {{\mathbb O}}
+\def\bP {{\mathbb P}} \def\bQ {{\mathbb Q}} \def\bR {{\mathbb R}}
+\def\bS {{\mathbb S}} \def\bT {{\mathbb T}}
+\def\bV {{\mathbb V}} \def\bW {{\mathbb W}} \def\bX {{\mathbb X}}
+\def\bY {{\mathbb Y}} \def\bZ {{\mathbb Z}}
+\def\R {{\mathbb R}} \def\RR {{\mathbb R}} \def\H {{\mathbb H}}
+\def\n{{\bf n}} \def\Z {{\mathbb Z}}
+
+\def\supp{{\mathop {{\rm supp\, }}}}
+\def\esssup{{\mathop{\rm ess \; sup \, }}}
+\def\essinf{{\mathop{\rm ess \; inf \, }}}
+\def\essosc{{\mathop{\rm ess \; osc \, }}}
+
+\newcommand{\expr}[1]{\left( #1 \right)}
+\newcommand{\cl}[1]{\overline{#1}}
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{lemma}[thm]{Lemma}
+\newtheorem{defn}[thm]{Definition}
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{corollary}[thm]{Corollary}
+\newtheorem{remark}[thm]{Remark}
+\newtheorem{example}[thm]{Example}
+\numberwithin{equation}{section}
+\def\ee{\varepsilon}
+\def\qed{{\hfill $\Box$ \bigskip}}
+\def\NN{{\mathcal N}}
+\def\AA{{\mathcal A}}
+\def\MM{{\mathcal M}}
+\def\BB{{\mathcal B}}
+\def\CC{{\mathcal C}}
+\def\LL{{\mathcal L}}
+\def\DD{{\mathcal D}}
+\def\FF{{\mathcal F}}
+\def\EE{{\mathcal E}}
+\def\QQ{{\mathcal Q}}
+\def\SS{{\mathcal S}}
+\def\RR{{\mathbb R}}
+\def\R{{\mathbb R}}
+\def\L{{\bf L}}
+\def\K{{\bf K}}
+\def\S{{\bf S}}
+\def\A{{\bf A}}
+\def\E{{\mathbb E}}
+\def\F{{\bf F}}
+\def\P{{\mathbb P}}
+\def\N{{\mathbb N}}
+\def\eps{\varepsilon}
+\def\wh{\widehat}
+\def\wt{\widetilde}
+\def\pf{\noindent{\bf Proof.} }
+\def\pff{\noindent{\bf Proof} }
+\def\cp{\mathrm{Cap}}
 \usepackage{hyperref}
-\usepackage{comment}
-\usepackage{amsthm}
-\theoremstyle{plain}
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{conj}[thm]{Conjecture}
-\theoremstyle{definition}
-\newtheorem{defi}[thm]{Definition}
-\newtheorem{rem}[thm]{Remark}
-\newtheorem{exa}[thm]{Example}
-\newtheorem{asp}{Assumption}
-\numberwithin{equation}{section}
-\allowdisplaybreaks
+%\bibliographystyle{plain}
 \begin{document}
-\title
-[stable CLT for super-OU processes]
-{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
-\author
-[Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
-{Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
-\address{
-  Yan-Xia Ren \\
-  LMAM School of Mathematical Sciences \& Center for Statistical Science \\
-  Peking University \\
-  Beijing, P. R. China, 100871}
-\email{yxren@math.pku.edu.cn}
-\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}
-\address{
-  Renming Song \\
-  Department of Mathematics \\
-  University of Illinois at Urbana-Champaign \\
-  Urbana, IL, USA, 61801}
-\email{rsong@illinois.edu}
-\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
-\address{
-  Zhenyao Sun \\
-  School of Mathematics and Statistics\\
-  Wuhan University \\
-  Hubei, P. R. China, 100871}
-\email{zhenyao.sun@gmail.com}
-\address{
-  Jianjie Zhao \\
-  School of Mathematical Sciences \\
-  Peking University \\
-  Beijing, P. R. China, 100871}
-\email{zhaojianjie@pku.edu.cn}
-\thanks{Jianjie Zhao is the corresponding author}
-\begin{abstract}
-  In this paper, we study the asymptotic behavior of a supercritical $(\xi,\psi)$-superprocess $(X_t)_{t\geq 0}$
-  whose underlying spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ where $\sigma, b >0$;
-  and whose branching mechanism $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that,
- when $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
-  Some law of large numbers and $(1+\beta)$-stable central limit theorems are established for
-  $(X_t(f) )_{t\geq 0}$, where the function $f$ is
-  assumed to be of polynomial growth.
-A phase transition arises  for the central limit theorems in the sense 
-that the forms of the central limit theorem are different in three different regimes corresponding the branching rate 
-being relatively small, large or critical at a balanced value.
-\end{abstract}
-\subjclass[2010]{60J68, 60F05}
-\keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}
+\title[]{Notes}
+\author{}
+
+ \date{}
+
+%\begin{abstract}
+
+%\end{abstract}
 \maketitle
-\section{Introduction}
-\subsection{Motivation}
-\label{subsec:M}
-Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
-Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
-\begin{align}
-  Lf(x)
-  = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x)
-  , \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
-\end{align}
-where $\sigma > 0$ and $b > 0$ are constants.
-Let $\psi$ be a function on $\mathbb R_+$ of the form
-\begin{align}
-  \label{eq: honogeneou branching mechanism}
-  \psi(z)
-  =- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy)~\pi(dy)
-  , \quad  z \in \mathbb R_+,
-\end{align}
-where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)~\pi(dy)< \infty$.
-$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
-Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
-For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$,
- write $\mu(f)= \int f(x)\mu(dx)$
-and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
-We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
-$
-We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
-on  $(\Omega, \mathscr{F})$
-is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$-superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
-\begin{align}
-  \label{eq: def of V_t}
-  \mathbb{P}_{\mu}[e^{-X_t(f)}]
-  = e^{-\mu(V_tf)}
-  , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
-\end{align}
-where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
-\begin{align}
-  V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) )~ds\Big]
-	= \Pi_x [f(\xi_t)]
-  , \quad x\in \mathbb R^d, t\geq 0.
-\end{align}	
-The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
 
-Recently, there have been quite a few papers on laws of large numbers for superdiffusions.
-In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established.
-The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
-For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.
+%\bigskip
+%\noindent {\bf AMS 2010 Mathematics Subject Classification}:
 
-The strong law of large numbers for the super-OU process $X$ above can be stated as follows:
-Under some conditions on $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below),
-there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e.
-continuous bounded non-negative function $f$ on $\mathbb R^d$, we have
- $\lim_{t\to\infty} e^{-\alpha t} X_t(f) =H_\infty\langle f, \varphi\rangle $,
-where $H_\infty$ is the limit of the martingale $e^{-\alpha t}X_t(1)$
-and $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
-See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
+%\bigskip\noindent
+%{\bf Keywords and phrases}:
 
-In this paper, we will establish some spatial central limit theorems (CLTs) for the super-OU process $X$ above.
-Our key assumption is that $\psi$ satisfies Grey's condition and some perturbation condition which guarantees that,
-when  $z\to 0$, $\psi(z)=-\alpha z + \eta z^{1+\beta} (1+o(1))$ with $\alpha > 0$, $\eta>0$ and $\beta\in (0, 1)$.
-Our  goal is to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ so that
-$ (X_t(f) -G_t)/F_t $ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
-Note that, in the setting of this paper, $X_t(f)$ typically has infinite second moment.
+\smallskip
 
-There are many papers on CLTs for branching processes, branching diffusions and superprocesses under the second moment condition.
-See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes),
-\cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some}
-for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-Some spatial CLTs for supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some
-spatial CLTs for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
-These two papers made connections between CLTs and branching rate regimes.
-Some spatial CLTs  for supercritical super-OU  processes with branching mechanisms satisfying only a second moment condition were established in \cite{RenSongZhang2014Central}.
-Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
-Since then, a series of spatial CLTs for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
-The functional version of the CLTs were established in \cite{Janson2004Functional} for supercritical multitype branching processes, and in \cite{RenSongZhang2017Functional} for supercritical superprocesses.
+The following statement, corresponding to Step 1 in the proof of Lemma 2.6 of the EJP paper, is correct, by looking at things separately.
 
-There are also many limit theorems for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment.
-Heyde \cite{Heyde1971Some} established some  CLTs for supercritical GW processes when the offspring distribution belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit laws are stable laws.
-Similar results  for supercritical multi-type GW processes and supercritical continuous time branching processes,
-under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
- Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} considered the limit behavior of supercritical branching OU processes with a special stable offspring distribution.
-They established some spatial CLTs in the small and critical branching rate regimes, but they did not prove any CLT type result in the large branching rate regime.
-We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior
-of a class of critical superprocesses with spatially dependent stable branching mechanism.
+If  $f(x)=f_1(x)+t^{\widetilde{\beta}-1}f_2(x)$ with
+$f_1, f_2\in\mathcal P$, then there exists $h\in \mathcal P$ such that 
+$|T_tf|\le e^{-\delta t}h$ for all $t\ge 1$, where
+$$
+\delta=(\inf\{|\tilde \beta\alpha-|p|b|: p\in\mathbb Z^d_+, \langle f_1, \phi_p\rangle\neq 0\})
+\wedge (\inf\{|\tilde \beta\alpha-|p|b|: p\in\mathbb Z^d_+, \langle f_2, \phi_p\rangle\neq 0\}).
+$$
 
-As far as we know, this paper is the first to study spatial CLTs for supercritical superprocesses without the second moment condition.
+The statement of Lemma 2.9 of the EJP paper can be changed to the following form
+with proof basically unchanged.
 
-\subsection{Main results}
-\label{sec:I:R}
-We will always assume that the following assumption holds.
-\begin{asp}
-  \label{asp: Greys condition}
-  The branching mechanism $\psi$ satisfies Grey's condition, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-\end{asp}
-For $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \mu(1)$.
-It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event} $D :=\{\exists t\geq 0,~\text{s.t.}~ \|X_t\| =0 \}$ has positive probability with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
-In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$ where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
+{\bf Lemma 2.9} Suppose that $g(x)=g_1(x)+t^{\tilde{\beta}-1}g_2(x)$ with
+$g_1, g_2\in\mathcal P$. Then there exists $h\in\mathcal P^+$ such that for all
+$f\in \mathcal P_g=\{\theta_nT_ng: n\in \mathbb Z_+, \theta\in [-1, 1]\}$ and $t\ge 1$, we have $|P_t(Z_1f-\langle Z_1f, \varphi\rangle)|\le e^{-b t}h$.
 
-Denote by $\Gamma$ the gamma function.
-For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
-In this paper, we will also assume the following:
-\begin{asp}
-  \label{asp: branching mechanism}
-  There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
-  \begin{align}
-    \label{eq: asp of branching mechanism}
-    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
-  \end{align}
-	for some $\delta > 0$.
-\end{asp}
-We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
-In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
-	Note that $\delta$ is not uniquely determined by $\pi$.
-	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
-	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statement:
-	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for all small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
+I am proposing to change the statement of Proposition 3.5 to the following form:
 
-\begin{rem}
-  \label{rem:SP}
-Roughly speaking, Assumption \ref{asp: branching mechanism} says that $\psi$ is ``not too far away'' from $\widetilde \psi(z) := - \alpha z + \eta z^{1+\beta}$ near $0$.
-In fact, if we consider their difference
-\begin{align}
-  \label{eq:PB}
-  & \psi_1(z)
-  := \psi(z) - \widetilde \psi(z)
-  \\ &= \rho z^2+ \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta) y^{2+\beta}}\Big),
-  \quad z\geq 0,
-\end{align}
-then it can be verified that (see Lemma \ref{lem:CEP} below) $\psi_1(z)/z^{1+\beta} \xrightarrow[z\to 0]{} 0$.
-Therefore, we can write $ \psi(z)  = - \alpha z + z^{1+\beta}(\eta + o(1))$ as $z\to 0$.
-One can further write that $\psi(z) = - \alpha z + z^{1+\beta} l(z)$ where $l$ is a function on $[0,\infty)$ which is slowly varying at $0$.
-\end{rem}
+{\bf Proposition 3.5} Fro all $\mu\in\mathcal M_c(\mathbb R^d)$ and $g(x)=g_1(x)+t^{\tilde{\beta}-1}g_2(x)$ with
+$g_1, g_2\in\mathcal P$, there exist $C, \delta>0$ such that for all $t\ge 1$ and $f\in \mathcal P_g:=\{\theta T_ng: n\in \mathbb Z_+, \theta\in [-1, 1]\}$, we have
+$$
+\mathbb P_\mu\left[|\mathbb P_\mu[e^{i\upsilon^f_t}-e^{\langle Z_1f, \varphi\rangle}; D^c|\mathcal F_t|\right]\le C e^{-\delta t}.
+$$
 
-\begin{rem}
-It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism},
- $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y~\pi(dy) < \infty. $
-This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.
-\end{rem}
-Let us introduce some notation in order to give the precise formulation of our main result.
-Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
-Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel functions on $\mathbb R^d$.
-We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
-Define
-\(
-P^{\alpha}_t f(x)
-  := e^{\alpha t} P_t f(x)
-  = \Pi_x [e^{\alpha t}f(\xi_t)]
-\)
-for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
-It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$ in the sense that
-\(
-  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)
-\)
-for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
-
-The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (See \cite{MetafunePallaraPriola2002Spectrum} for more details).
-It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
-\begin{align}
-  \label{invariantdensity}
-  \varphi(x)dx
-  :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx
-\end{align}
-which is a   symmetric multivariate Gaussian distribution.
-Let $L^2(\varphi)$ be the Hilbert space with inner product
-\begin{align}
-  \langle f_1, f_2 \rangle_{\varphi}
-  := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
-\end{align}
-Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
-The \emph{Hermite polynomials} are defined by
-\begin{align}
-  H_p(x)
-  :=(-1)^{|p|}\exp(|x|^2) \partial_p \exp(-|x|^2)
-  , \quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
-\end{align}
-It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
-For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
-\begin{align}
-  \label{eigenfunction}
-  \phi_p(x)
-  := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big)
-  , \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
-\end{align}
-In other words,
-\(
-  P_t\phi_p(x)
-  = e^{-b|p|t}\phi_p(x)
-\)
-for all $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
-Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
-Thus for each $f\in L^2(\varphi)$, we have
-\begin{align}
-  \label{semicomp1}
-  f
-  = \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
-  , \quad \text{in~} L^2(\varphi).
-\end{align}
-For each function $f\in L^2(\varphi)$, define the order of $f$ as
-\[
-  \kappa_f
-  := \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
-\]
-which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
-Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
-In particular, the order of any constant non-zero function is zero.
-
-Denote by $\mathcal M_c(\mathbb R^d)$ the space of all finite Borel measures of compact support on $\mathbb R^d$.
-For $p\in \mathbb{Z}_+^d$, define
-\(
-  H_t^p
-  := e^{-(\alpha-|p|b)t}X_t(\phi_p)
-\)
-for all $t\geq 0$.
-If $\alpha \tilde \beta>|p|b, \tilde \beta := \beta/(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we will prove in Lemma \ref{lem:M:L:ML} that $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-
-We first present a law of large numbers for our model which extends the strong laws of large numbers of \cite{ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines} in which the first order asymptotic ($\kappa_f=0$) was identified.
-Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
-\begin{align}
-  \label{eq: polynomial growth function}
-  \mathcal{P}
-  := \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
-\end{align}
-It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-\begin{thm}
-  \label{thm: law of large number}
-  If $f \in \mathcal{P}$ satisfies $\alpha\tilde \beta>\kappa_f b$, then for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
-  \[
-    e^{-(\alpha-\kappa_fb)t}X_t(f)
-    \xrightarrow[t\to \infty]{}\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p
-    \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).
-  \]
-  Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
-\end{thm}
-If $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$ is non-trivial and  bounded, then $\kappa_f=0$.
-Hence, Theorem \ref{thm: law of large number} says that for any $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
-\(
-  e^{-\alpha t}X_t(f)
-  \rightarrow \langle f, \varphi\rangle H_{\infty}
-\)
-in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have a.s.\ convergence.
-However, to get a.s.\ convergence for bounded non-negative
-Lebesgue-a.e.\ continuous functions $f$, we do not need $f$ to be twice differentiable.
-See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
-
-For the rest of this subsection, we focus on the CLTs of $X_t(f)$ for a large collection of $f\in \mathcal P\setminus \{0\}$.
-Write $\tilde u = \frac{u}{ 1+ u}$ for each $u \neq -1$.
-It turns out that there is a phase transition in the sense that the results are different in the following three cases:
-\begin{enumerate}
-\item
-  the small branching rate case where
-$f$ satisfies $\alpha \tilde \beta < \kappa_f b$;
-\item
-  the critical branching rate case where
-$f$ satisfies $\alpha \tilde \beta = \kappa_f b$; and
-\item
-  the large branching rate case  where
-$f$ satisfies $\alpha \tilde \beta > \kappa_f b$.
-\end{enumerate}
-Here, the small (resp. large) branching rate case means that the branching rate $\alpha$ is small (resp. large) compared to $\kappa_f$;
- and the critical branching rate means that the branching rate $\alpha$ is at a critical balanced value compared to $\kappa_f$.
-To present our result, we define a family of operators $(T_t)_{t\geq 0}$ on $\mathcal P$ by
-\begin{align}
-  \label{eq:I:R:1}
-  T_t f
-  := \sum_{p \in \mathbb Z_+^d} e^{-| |p|b - \alpha \tilde \beta |t} \langle f, \phi_p \rangle_{\varphi} \phi_p
-  ,\quad t\geq 0, f\in \mathcal P,
-\end{align}
-and a family of $\mathbb C$-valued functionals $(m_t)_{0 \leq t < \infty}$ on $\mathcal P$ by
-\begin{align}
-  \label{eq:I:R:2}
-  m_t[f]
-  := \eta \int_0^t ~du \int_{\mathbb R^d} (-iT_u f(x))^{1+\beta} \varphi(x) ~dx
-  , \quad 0 \leq t< \infty, f\in \mathcal P.
-\end{align}
-Define $ \mathcal C_s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}$, $\mathcal C_c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $
-and $ \mathcal C_l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$. 
-Note that $\mathcal C_s$ is an infinite dimensional space, $ \mathcal C_l$ and $\mathcal C_c$
-are finite dimensional spaces, and $\mathcal C_c$ might be empty.
-For $f\in \mathcal P\setminus \{0\}$, in Lemma \ref{lem:m} and Proposition \ref{prop:PL:S} below, we will show that
-\begin{align}
-  \label{eq:I:R:3}
-  m[f]
-  := \begin{cases}
-    \lim_{t\to \infty} m_t[f], &
-    f \in \mathcal C_s \oplus \mathcal C_l, \\
-    \lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_s \oplus \mathcal C_l,
-  \end{cases}
-\end{align}
-is well defined, and moreover, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}$.
-The main result of this paper is as follows.
-
-\begin{thm}
-  \label{thm:M}
- If $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$, then under $\mathbb{P}_{\mu}(\cdot|D^c)$, the following hold:
-\begin{enumerate}
-\item
-  \label{thm:M:1}
-  if $f\in \mathcal C_s\setminus\{0\}$, then $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$;
-\item
-  \label{thm:M:2}
-  if $f\in \mathcal C_c\setminus\{0\}$, then $ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$;
-\item
-  \label{thm:M:3}
-  if $f\in \mathcal C_l\setminus\{0\}$, then
-  \[
-    \|X_t\|^{-\frac{1}{1+\beta}} \Big( X_t(f) - \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty}\Big)
-    \xrightarrow[t\to \infty]{d}
-    \zeta^{-f}.
-  \]
-\end{enumerate}
-\end{thm}
-
-At this point, we should mention that the theorem above does not cover all $f\in \mathcal P$.
-Theorem \ref{thm:M}.(1) can be rephrased as if $f\in \mathcal P\setminus\{0\}$ satisfies   $\alpha \tilde \beta < \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$, $\|X_t\|^{- \frac{1}{1+\beta}} X_t(f)  \xrightarrow[t\to \infty]{d} \zeta^f$.
-Combining the first two parts of Theorem \ref{thm:M}, one can easily get that  if $f\in \mathcal P$ satisfies   $\alpha \tilde \beta = \kappa_f b$, then  under $\mathbb{P}_{\mu}(\cdot|D^c)$,
-$ \|t X_t\|^{-\frac{1}{1+\beta}} X_t(f) \xrightarrow[t\to \infty]{d} \zeta^f$.
-A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_s$, $f_c \in \mathcal C_c$ and $f_l \in \mathcal C_l$. 
-For $f\in  \mathcal P$ satisfying $\alpha \tilde \beta > \kappa_f b$, $f_s$ and $f_c$ maybe non-trivial.
-In this case, we do not have a CLT yet.
-We conjecture that the limit random variables in Theorem \ref{thm:M} for $ f\in \mathcal C_s$, $f\in \mathcal C_c$ and $ f\in \mathcal C_l$ are independent. If this is valid, we can
-get a CLT for $ X_t(f)$ for all $f\in  \mathcal P$.
-This independence is valid  under the second moment condition, see \cite{RenSongZhang2015Central}.
-We leave the question of independence of the limit stable random variables to a future project.
-
- We now give some intuitive explanation of the branching rate regimes and the  phase transition.
-Similar explanation has been given in the context of branching-OU processes, see \cite{MarksMilos2018CLT}.
-First we mention that a super-OU process arises as the ``high density'' limit of a sequence of branching-OU processes, see \cite{Li2011Measure-valued} for example.
-A superprocess can be thought of as a cloud of infinitesimal branching ``particles'' moving in space.
-The phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing.
-The coarsening effect corresponds to the increase of the spatial inequality and is a consequence of the branching: simply an area with more particles will produce more offspring.
-The smoothing effect corresponds to the decrease of the spatial inequality and is a consequence of the mixing property of the OU processes: each OU ``particle'' will ``forget'' its initial position exponentially fast.
-
-Let us consider $X_t(\phi_p)$ as an example and discuss how the parameters $\alpha, \beta, b$ and $|p|$
-influence those two effects:
-\begin{itemize}
-\item
-  The branching rate $\alpha$ captures the mean intensity of the branching in the system.
-  Therefore, the lager the branching rate $\alpha$, the stronger the coarsening effect.
-\item
-  The tail index $\beta$ describes the heaviness of the tail of the offspring distribution which belongs to the domain of attraction of some $(1+\beta)$-stable random variable.
-When $\beta$ is smaller i.e. the tail is heavier, then it is more likely that 
-one particle can suddenly have a large amount of offspring.
-In other words, the larger the tail index $\beta$, the smaller the fluctuation of offspring number, and then the stronger the coarsening effect.
-\item
- The drift parameter $b$ is related to the level of the mixing property of the OU particles.
-  The larger the drift parameter $b$, the faster the OU-particles forgetting their initial position, and therefore the stronger the smoothing effect.
-\item
-    The order $|p|$ is related to the capability of $\phi_p$ capturing the mixing property of the OU particles.
-  In particular, in the case that $|p| = 0$, no mixing property can be captured by $\phi_p \equiv 1$ since we are only considering the total mass $\|X_t\|$.
-  In general, the higher the order $|p|$, the more mixing property can be captured by $\phi_p$, and therefore the stronger the smoothing effect.
-\end{itemize}
-Here we discuss the role of the other parameters $\rho, \eta$ and $\sigma$ in our model:
-\begin{itemize}
-\item
-  The coefficient $\rho$ dose not influence the result since $\rho z^2$ in the branching mechanism $\psi$ is a part of the small perturbation $\psi_1$
-  (see Remark \ref{rem:SP}).
-\item
-  The coefficients $\eta$ and $\sigma$ are hidden in the definition of the functional $m[f]$, and therefore influence the actual distribution of the limiting $(1+\beta)$-stable random variable $\xi^f$.
-  Their role in the coarsening and smoothing effects are negligible compared to the four parameters $\alpha, \beta, b$ and $|p|$ mentioned above.
-\end{itemize}
-
-\subsection{An outline of the methodology}
-Let us give some intuitive explanation of the methodology used in this paper.
-For any $\mu\in \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
-$
-  \mathcal I_s^t Y
-  := \mathcal I_s^t [Y, \mu]
-  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s]
-$
-  where $0 \leq s \leq t <\infty.$
-We will use the shorter notation $\mathcal I_s^t Y$ when there is no danger of confusion.
-For $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
-\begin{align}
-  X_t(f)
-  := \sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k} X_t (f)+\mathcal I_0^{t-\lfloor t \rfloor} X_t(f) + X_0( P^\alpha_tf),
-  \quad t\geq 0.
-\end{align}
-To find the fluctuation of $X_t(f)$, we will investigate the fluctuation of each term on the right hand side above.
-The second term and third term are negligible after the rescaling, and for the first term we will establish
-a multi-variate unit interval CLT  which says that
-\[
-  \Big( \|X_t\|^{-\frac{1}{1+\beta}}\mathcal I^{t-k}_{t-k-1} X_t(f) \Big)_{k=0}^n
-  \xrightarrow [t\to \infty]{d} (\zeta^f_k)_{k=0}^n,
-\]
-where $(\zeta^f_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables.
-If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \xi^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have
-\(
-  \|X_t\|^{-\frac{1}{1+\beta}}  X_t(f)
-  \xrightarrow[t\to \infty]{d} \zeta^f.
-  \)
-If $f \in \mathcal C_c \setminus \{0\}$, then it can be argued that
-\(
-t^{-\frac{1}{1+\beta}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{ d} \zeta^f
-\)
-and then intuitively we have
-\(
-\|tX_t\|^{-\frac{1}{1+\beta}}  X_t(f)
-\xrightarrow[t\to \infty]{d} \zeta^f.
-\)
-If $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
-
-This paper is our first attempt on stable CLTs for superprocesses.
-There are still many open questions.
-Ren, Song and Zhang have established some spatial  CLTs in \cite{RenSongZhang2015Central} for a class of superprocesses with general spatial motions under
-the assumption that the branching mechanisms satisfy a second moment condition.
-We hope to prove spatial CLTs for superprocesses with general motions without the second moment assumption on the branching mechanism in a future project.
-
-Recall that our Assumption \ref{asp: branching mechanism} says that the branching mechanism $\psi$ is $-\alpha z +\eta z^{1+\beta}$ plus a small perturbation
-$\psi_1(z)$
-which satisfies \eqref{eq: asp of branching mechanism} with some $\delta>0$.
-It would be interesting to consider more general branching mechanisms.
-
-The following correspondence between (sub)critical branching mechanisms and Bernstein functions is well known, see, for instance,
-\cite[Theorem VII.4(ii)]{Bertoin} and \cite[Proposition 7]{BRY}. Suppose that $f, g:(0, \infty)\to [0, \infty)$ are related by $f(x)=xg(x)$.
-Then $f$ is a (sub)critical branching mechanism with $\lim_{x\to 0}f(x)=0$ iff $g$ is a Bernstein function with a decreasing L\'evy density.
-We now use this correspondence to give some examples of branching mechanisms satisfying Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-If $h$ is a complete Bernstein function which is regularly varying at 0 with index $\beta_1\in (\beta, 1)$, then
-\[
-  \psi(z)
-  := -\alpha z + \rho z^2+\eta z^{1+\beta}+zh(z)
-  , \qquad z>0,
-\]
-satisfies Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-If $\beta_1\in (\beta, 1)$, $c_1\in (0, \eta/\Gamma(-1-\beta))$ and $c_2\ge 1$, then
-\[
-  \psi(z)
-  :=-\alpha z + \rho z^2+\eta z^{1+\beta}-\int^\infty_{c_2} (e^{-yz}-1+yz)\frac{c_1dy}{y^{1+\beta_1}}
-  , \qquad z\in \mathbb R_+,
-\]
-satisfies Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-
-The rest of the paper is organized as follows:
-In Subsection \ref{sec: branching mechanism} we will give some preliminary results for the branching mechanism $\psi$.
-In Subsections \ref{sec: controller} and \ref{sec: h-controller} we will give some estimates for some operators related to the super-OU process $X$.
-In Subsection \ref{sec: stable distributions} we will give the definitions of the $(1+\beta)$-stable random variables involved in this paper.
-In Subsection \ref{sc:refined} we will give some refined estimate for the OU semigroup.
-In Subsection \ref{sec: Small value probability} we will give some estimates for the small value probability of continuous state branching processes.
-In Subsection \ref{sec: Moments for super-OU processes} we will give upper bounds for the $(1+\gamma)$-moments for our superprocesses.
-These estimates and upper bounds will be crucial in the proofs of our main results.
-In Subsection \ref{sec: large rate lln}, we will give the proof of Theorem \ref{thm: law of large number}.
-In Subsections \ref{sec:critical}--\ref{sec: large rate clt}, we will give the proof of Theorem \ref{thm:M}.
-In the Appendix, we consider a general superprocess $(X_t)_{t\geq 0}$ and we prove that the characteristic exponent of $X_t(f)$ satisfies a complex-valued non-linear integral equation.
-This fact will be used at several places in this paper, and we think it is of independent interest.
-
-\section{Preliminaries}
-\subsection{Branching mechanism}
-\label{sec: branching mechanism}
-Let $\psi$ be the branching mechanism given in \eqref{eq: honogeneou branching mechanism}.
-Suppose that Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism} hold.
-In this subsection, we give some preliminary results on $\psi$.
-Recall that $\eta$ and $\beta$ are the constants in Assumption \ref{asp: branching mechanism}.
-Let $\mathbb C_+:= \{x+iy: x\in \mathbb R_+, y \in \mathbb R\}$ and $\mathbb C^0_+:= \{x+iy: x\in (0,\infty), y \in \mathbb R\}$.
-\begin{lem}
-  \label{lem:CEP}
-	The function $\psi_1$ given by \eqref{eq:PB} can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
-  Moreover, for all $\delta > 0$ small enough, there exists $C>0$ such that for all $z\in \mathbb C_+$, we have $|\psi_1(z)| \leq C |z|^{1+\beta+\delta} + C|z|^2.$
-\end{lem}
-\begin{proof}
-  According to Lemma \ref{lem: extension lemma for branching mechanism} below and the uniqueness of holomorphic extensions, we know that $\psi_1$ can be uniquely extended as a complex-valued continuous function on $\mathbb C_+$ which is holomorphic on $\mathbb C^0_+$.
-	The extended $\psi_1$ has the following form:
-  \[
-    \psi_1(z)
-    = \rho z^2 + \int_{(0,\infty)}(e^{-yz}-1+yz) \Big(\pi(dy) - \frac {\eta~dy} {\Gamma(-1-\beta)y^{2+\beta}} \Big)
-    , \quad z\in \mathbb C_+.
-  \]
-	Now, according to  Assumption \ref{asp: branching mechanism}, for all small enough $\delta > 0$, we have
-  \begin{align}
-    |\psi_1(z)|
-    & \leq \rho |z|^2 + \int_{(0,\infty)} (|yz|\wedge |yz|^2) \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| \\
-    & \leq  |z|^2 \Big(\rho + \int_{(0,1)} y^2 \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|\Big) \\
-    & \quad + |z|^{1+\beta +\delta}\int_{(1,\infty)} y^{1+\beta + \delta} \Big|\pi(dy) - \frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big|,
-      \quad z \in \mathbb C_+,
-  \end{align}
-	as desired.
-\end{proof}
-The following lemma says that the constants $\eta, \beta$ in Assumption \ref{asp: branching mechanism} are uniquely determined by the L\'evy measure $\pi$.
-\begin{lem}
-  \label{lem: unique of beta and eta}
-  Suppose Assumption  \ref{asp: branching mechanism} holds. Suppose that there are $\eta', \delta'>0$ and $\beta'\in (0,1)$ such that
-  \[
-    \int_{(1,\infty)} y^{ 1 + \beta'  + \delta' }~ \Big| \pi(dy) - \frac {\eta' ~dy} {\Gamma (- 1 - \beta ) y^{2 + \beta'}} \Big|
-    < \infty.
-  \]
-	Then $\eta'= \eta$ and $\beta ' = \beta$.
-\end{lem}
-\begin{proof}
-	Without loss of generality, we assume that $\beta+\delta \leq \beta'+ \delta'$.
-	Using  the fact that $y^{1+\beta+ \delta} \leq y^{1+\beta'+\delta'}$ for $y \geq 1$, we get
-  \[
-    \int_{(1, \infty)} y^{1 + \beta + \delta}   \Big| \pi(dy) - \frac {\eta' ~dy} {\Gamma( - 1 - \beta)y^{2 + \beta'}} \Big|
-    < \infty .
-  \]
-	Comparing this with Assumption \ref{asp: branching mechanism}, we get
-  \[
-    \int_{(1,\infty)} y^{ 1 + \beta + \delta} \Big| \frac { \eta ~dy} {\Gamma (- 1 - \beta) y^{2 + \beta}} - \frac {\eta' ~dy} {\Gamma (- 1 - \beta) y^{2 + \beta'}} \Big| < \infty.
-  \]
-	In other words, if we denote by $\widetilde \pi(dy)$ the measure $\eta' \Gamma(-1-\beta)^{-1} y^{-2-\beta'} dy$, then $\widetilde \pi$ is a L\'evy measure which satisfies Assumption \ref{asp: branching mechanism}.
-	Applying Lemma \ref{lem:CEP} to $\widetilde \pi$, we have that there exists $c>0$ such that
-  \[
-    | \eta z^{ 1 + \beta } - \eta' z^{ 1 + \beta' } |
-    \leq c z^{ 1 + \beta + \delta } + c z^2
-    , \quad z \in \mathbb R_+.
-  \]
-  Dividing both sides by $z^{1+\beta}$ we have
-   $
-   | \eta - \eta' z^{ \beta' - \beta } |
-    \leq cz^{\delta}+cz^{1-\beta}
-    ,	z \in \mathbb R_+.
- $
-	This implies that $ \eta' z^{\beta' - \beta} \xrightarrow[\mathbb R^+\ni z\to 0]{} \eta >0. $
-	So we must have $\beta'= \beta$ and $\eta'= \eta$.
-\end{proof}
-\begin{lem}
-  \label{lem: LlogL criterion}
-  If $\psi$ satisfies Assumption  \ref{asp: branching mechanism}, then $\psi$ satisfies the $L \log L$ condition, i.e.,
-   $
-    \int_{(1,\infty)} y \log y~\pi(dy)
-    < \infty.
- $
-\end{lem}
-\begin{proof}
-	Using  Assumption \ref{asp: branching mechanism} and the fact that $y\log y \leq y^{1+\beta+\delta}$ for $y$ large enough, we get
-  \[
-    \int_{(1,\infty)} y \log y ~\Big| \pi(dy) - \frac { \eta ~dy } { \Gamma ( - 1 - \beta ) y^{ 2 + \beta } } \Big|
-    < \infty.
-  \]
-	Therefore we have
-  \[
-    \int_{ ( 1, \infty ) } y \log y ~\Big( \pi(dy) - \frac { \eta ~dy } { \Gamma ( - 1 - \beta ) y^{ 2 + \beta } } \Big)
-    < \infty.
-  \]
-  Combining this with
-  $
-  \int_{ ( 1, \infty ) } \frac { \eta \log y ~dy } { \Gamma ( - 1 - \beta ) y^{ 1 + \beta } }
-    < \infty,
- $
-  we immediately get the desired result.
-\end{proof}
-
-\subsection{Definition of controller}
-\label{sec: controller}
-Denote by $\mathcal B(\mathbb R^d, \mathbb C)$ the space of all $\mathbb C$-valued Borel functions on $\mathbb R^d$.
-Recall that $\mathcal P$ is given in \eqref{eq: polynomial growth function}.
-Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P^+\}$.
-
-In this paper, we say $R$ is a \emph{monotone} operator on $\mathcal P^+$ if $R:\mathcal P^+ \to \mathcal P^+$ satisfies that $Rf\leq Rg$ for all $f\leq g$ in $\mathcal P^+$.
-For a function $h: [0,\infty) \to [0,\infty)$, we say $R$ is an \emph{$h$-controller} if $R$ is a monotone operator on $\mathcal P^+$ and that $R(\theta f)\leq h(\theta) Rf$ for all $f\in \mathcal P^+$ and $\theta \in [0,\infty)$.
-For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and an operator $R$ on $\mathcal P^+$, we say an operator $A$ is \emph{controlled by $R$ from $\mathcal D$ to $\mathcal I$} if $A:\mathcal D \to \mathcal I$ and that $|Af| \leq R|f|$ for all $f\in \mathcal D$;
-we say a family of operators $\mathscr O$ is \emph{uniformly controlled by $R$ from $\mathcal D$ to $\mathcal I$} if
-each operator $A\in \mathscr O$  is controlled by $R$ from $\mathcal D$ to $\mathcal I$.
-For subsets $\mathcal D, \mathcal I\subset \mathcal P^*$ and a function $h:[0,\infty) \to [0,\infty)$, we say an operator $A$ (resp.
-a family of operators $\mathscr O$) is \emph{$h$-controllable} (resp.
-\emph{uniformly $h$-controllable}) from $\mathcal D$ to $\mathcal I$ if there exists an $h$-controller $R$ such that $A$ (resp.
-$\mathscr O$) is controlled (resp.
-uniformly controlled) by $R$ from $\mathcal D$ to $\mathcal I$.
-
-For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
-For any $a \in \mathbb R$ and any operator $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
-
-The following lemma is easy to verify.
-\begin{lem}
-  \label{lem: property of controllable operators}
-  For each $i \in \{0,1\}$, let $\mathscr O_i$ be a family of operators which is  uniformly controlled by an $h_i$-controller $R_i$ from $\mathcal D_i \subset \mathcal P^*$ to $ \mathcal I_i \subset \mathcal P^*$.
-  Then the followings hold:
-  \begin{enumerate}
-  \item
-    If $\mathcal I_0 \subset \mathcal D_1$, then $\{A_1A_0: A_i \in \mathscr O_i, i = 0,1\}$ is uniformly controlled by the $(h_1 \circ h_0)$-controller $R_1R_0$ from $\mathcal D_0$ to $\mathcal I_1$.
-  \item
-    $\{ A_1 \times A_0: A_i \in \mathscr O_i, i = 0,1\}$ is uniformly controlled by the $(h_1\times h_0)$-controller $R_1 \times R_0$ from $\mathcal D_0 \cap \mathcal D_1$ to $\mathcal P^*$.
-  \item
-    $\{ A_1 + A_0: A_i \in \mathscr O_i, i = 0,1\}$ is uniformly controlled by the $(h_1 \vee h_0)$-controller $R_1 + R_0$ from $\mathcal D_0 \cap \mathcal D_1$ to $\mathcal P^*$.
-  \item
-    If $\mathcal I_0 \subset \mathcal B(\mathbb R^d, \mathbb C \setminus (\infty, 0])$ and $a>0$, then $\{A^{\times a} : A \in \mathscr O_0\}$ is uniformly controlled by the $(h_0^a)$-controller $R_0^{\times a}$ from $\mathcal D_0$ to $\mathcal P^*$.
-  \item
-    Suppose that $\mathscr O_0 = \{A_\theta: \theta \in \Theta \}$ where $\Theta$ is an index set.
-    Further suppose that $(\Theta, \mathcal J )$ is a measurable space and that $(\theta,x) \mapsto A_\theta f(x)$ is $\mathcal J \otimes \mathcal B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
-    Then the following space of operators
-    \[
-      \Big\{ f \mapsto \int_{\Theta} A_\theta f~\nu(d\theta) : \nu \text{ is a probability measure on } (\Theta, \mathcal J) \Big\}
-    \]
-    is uniformly controlled by $R_0$ from $\mathcal D_0$ to $\mathcal P^*$.
-  \end{enumerate}
-\end{lem}
-
-\subsection{Controllers for the super-OU processes}
-\label{sec: h-controller}
-Let $X$ be our super-OU process with branching mechanism $\psi$ satisfying
-Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}.
-In this subsection, we will define several operators and study some of their properties that will be used in this paper.
-
-Define $\psi_0(z) = \psi(z) + \alpha z$ for $z\in \mathbb{R}_+$.
-According to Lemma \ref{lem:CEP}, $\psi, \psi_1$ and $\psi_0$ can all be uniquely extended as complex-valued continuous functions on $\mathbb C_+$ which are also holomorphic on $\mathbb C^0_+$.
-For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi f (x) = \psi\circ f(x)$, $\Psi_0 f(x)= \psi_0 \circ f(x)$ and $\Psi_1 f(x)= \psi_1 \circ f(x)$.
-
-For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, let $ U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]|_{\theta = 1} $ be the value of the characteristic exponent of the infinitely divisible random variable $X_t(f)$ (See the paragraph after Lemma \ref{lem: Lip of power function}).
-It follows from \eqref{eq: -v has positive real part} that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
-\begin{align}
-  \label{eq:chareq2}
-  U_tf(x) - \int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
-  = i P^{\alpha}_t f(x)
-  , \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
-\end{align}
-
-For all $t\geq 0$ and $f\in \mathcal P$, we define
-\begin{align}
-  \label{eq: def of Zf}
-  Z_t f
-  := \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,
-  & \qquad Z'_t f
-    := \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,
-  \\ Z''_t f
-  := \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
-  & \qquad\  Z'''_t f
-    := (Z'_t - Z_t+ Z''_t)f.
-\end{align}
-Then we have that
-\begin{align}
-  \label{eq: key equality}
-  U_t - i P^\alpha_t
-  = Z'_t + Z''_t
-  = Z_t + Z'''_t
-  , \quad t\geq 0.
-\end{align}
-For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
-\begin{align}
-  \label{eq:Q}
-  Q_\kappa f
-  := \sup_{t\geq 0} e^{\kappa b t}|P_t f|,
-  \qquad  Q f
-  := Q_{\kappa_f}f.
-\end{align}
-Then according to \cite[Fact 1.2]{MarksMilos2018CLT}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
-
-\begin{lem}
-  \label{lem: upper bound for usgx}
-  Under Assumptions \ref{asp: Greys condition} and \ref{asp: branching mechanism}, the following statements are true:
-  \begin{enumerate}
-  \item
-    $(-U_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
-  \item
-    $(P^\alpha_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable on $\mathcal P^*$.
-  \item
-    $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-  \item
-    $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item
-    $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item
-    For all $\delta > 0$ small enough, we have that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \item
-    For all $\delta > 0$ small enough, we have that $(Z'''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-  \end{enumerate}
-\end{lem}
-
-\begin{proof}
-  (1). According to \eqref{eq: -v has positive real part}, $-U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
-  It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$, we have $ |U_t g(x)| \leq \sup_{0\leq u\leq 1}P_u^\alpha |g| (x). $
-  We claim that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a map from $\mathcal P^+$ to $\mathcal P^+$. In fact, if $f\in \mathcal P^+$, there exists constant $c>0$ such that
-  \[
-    0
-    \leq \sup_{0\leq u\leq 1}P^{\alpha}_u f
-    \leq \sup_{0\leq u\leq 1} P_u (e^{\alpha u} e^{-\kappa_f u} e^{\kappa_f u} f )
-    \leq c \sup_{0\leq u\leq 1} (e^{\kappa_fu}P_u f) \leq c Qf \in \mathcal P.
-  \]
-	It is clear that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.
-
-  (2). Similar to the proof of (1).
-
-  (3).
-By Lemma \ref{lem:CEP}, there exist $C, \delta >0$ satisfying $\beta+\delta< 1$ such that for all $ f \in \mathcal P^* \cap \mathcal B( \mathbb R^d, \mathbb C_+ )$, it holds that $ |\Psi_0 f| \leq \eta |f|^{1+\beta} + |\Psi_1 f| \leq \eta |f|^{1+\beta} + C|f|^2+ C |f|^{1+\beta + \delta}.$
-  Note that the operator
-  \[
-    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta}
-    , \quad f\in \mathcal P^+,
-  \]
-  is a $(\theta^2 \vee \theta^{1+\beta})$-controller.
-
-  (4). From (1)--(3) above and Lemma \ref{lem: property of controllable operators}.(1), we know that the operators
-  \[
-    f \mapsto P^\alpha_{t-s}\Psi_0(-U_sf)
-    , \quad 0\leq s\leq t\leq 1,
-  \]
-  are uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable.
-  Combining this with \eqref{eq:chareq2} and
-  Lemma \ref{lem: property of controllable operators}.(5), we get the desired result.
-
-  (5). Notice that from Lemma \ref{lem: Lip of power function},
-  \[
-    |(-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta} |
-    \leq  (1+\beta) |U_t f-iP^\alpha_t f|(|U_t f|^{\beta}+|i P^\alpha_t f|^{\beta}).
-  \]
-  Now using (1), (2) and (4) above, and Lemma \ref{lem: property of controllable operators}, we get that the operators
-  \[
-    f \mapsto (-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta},\quad 0\leq t\leq 1,
-  \]
-  are uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable.
-  Combining with Lemma \ref{lem: property of controllable operators}, and
-  \[
-    (Z'_t - Z_t)f
-    = \int_0^t P^\alpha_{t-s}\Big( \eta ((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} )\Big)ds
-    , \quad 0\leq t\leq 1, f\in \mathcal P,
-  \]
-  we get the desired result.
-
-  (6). By  Lemma \ref{lem:CEP}, for all $\delta > 0$ small enough, there exists  $C>0$ such that
-  \[
-    |\Psi_1(f)|
-    \le C(|f|^2+|f|^{1+\beta+ \delta})
-    , \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+).
-  \]
-  Note that, for all $\delta, C>0$,
-  \[
-    f \mapsto C(f^2+f^{1+\beta+\delta})
-    , \quad f\in \mathcal P^+
-  \]
-  is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controller.
-  Therefore, for all $\delta > 0$ small enough, we have that $\Psi_1$ is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable operator from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
-  Combining  this with  (1)--(2) above,
-  and Lemma \ref{lem: property of controllable operators}, we get that, for all $\delta > 0$ small enough, the operators
-  \[
-    f
-    \mapsto Z_t'' f
-    = \int_0^t P_{t-s}^\alpha \Psi_1(-U_sf)ds
-    , \quad 0\leq t\leq 1,
-  \]
-  are uniformly $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
-
-  (7). Since $Z'''_t = (Z'_t-Z_t)+Z''_t$, the desired result follows from (5)--(6) above and Lemma \ref{lem: property of controllable operators}.(3).
-\end{proof}
-
-\subsection{Stable distributions}
-\label{sec: stable distributions}
-Recall that the operators $(T_t)_{t\geq 0}$ are defined by \eqref{eq:I:R:1}, and the functionals $(m_{t})_{0\leq t< \infty}$ and $m$ are given by \eqref{eq:I:R:2} and \eqref{eq:I:R:3} respectively.
-\begin{lem}
-  \label{lem:m}
-$(T_t)_{t\geq 0}$,  $(m_{t})_{0\leq t< \infty}$ and  $m$ are well defined.
-\end{lem}
-\begin{proof}
-  \emph{Step 1.} We will show that for each $f \in \mathcal P$, there exists $h \in \mathcal P$ such that $ |T_tf| \leq  e^{- \delta t} h$ for each $t\geq 0$, where
-  \begin{align}
-    \label{eq:m:1}
-    \delta
-    := \inf \big\{ |\tilde \beta \alpha - |p|b| : p \in \mathbb Z_+^d, \langle f, \phi_p\rangle_\varphi \neq 0 \big\}
-    \geq 0.
-  \end{align}
-  From this upper bound, it can be verified that $(T_t)_{t\geq 0}$ and $(m_{t})_{0 \leq t < \infty}$ are well defined.
-  In fact, we can write $f = f_0 + f_1$ with $f_0\in \mathcal C_s \oplus \mathcal C_c$ and $f_1 \in \mathcal C_l$.
-  According to \cite[Lemma 2.7]{MarksMilos2018CLT}, there exists $h_0 \in \mathcal P$ such that for each $t\geq 0$,
-  \[
-    |T_t f_0|
-    = \Big| \sum_{p \in  \mathbb Z_+^d: \tilde \beta \alpha \leq |p|b } e^{- ( |p| b - \tilde \beta \alpha ) t} \langle f, \phi_p \rangle_\varphi \phi_p \Big|
-    = e^{\tilde \beta \alpha t} | P_t f_0 |
-    \leq e^{- ( \kappa_{(f_0)} b - \tilde \beta \alpha) t} h_0
-    \leq e^{- \delta t} h_0.
-  \]
-  On the other hand
-  \[
-    |T_t f_1|
-    \leq e^{- \delta t}\sum_{p \in \mathbb Z_+^d : \tilde \beta \alpha > |p|b} |\langle f, \phi_p \rangle_\varphi \phi_p|
-    =: e^{- \delta t} h_1,
-    \quad t\geq 0.
-  \]
-  So the desired result in this step follows with $h := h_0 + h_1$.
-
-  \emph{Step 2.} We will show that if $f \in \mathcal C_s \oplus \mathcal C_l$, then $m[f]$ is well defined.
-  In fact, let $\delta$ be given by \eqref{eq:m:1}, then in this case $\delta > 0$.
-  Now, according to Step 1 there exists $h \in \mathcal P$ such that $|T_tf| \leq e^{- \delta t} h$ for each $t\geq 0$.
-  This exponential decay implies the desired result in this step.
-
-  \emph{Step 3.} We will show that if $f\in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$, then $m[f]$ is also well defined.
-  In fact, $f$ can be decomposed as $f = f_c + f_{sl}$ where $f \in \mathcal C_c\setminus \{0\}$ and $f_{sl}\in \mathcal C_s \oplus \mathcal C_l$.
-  Note that $T_t f_c = f_c$ for each $t\geq 0$.
-  Also note that in Step 2, we already have shown that there exist $\delta > 0$ and $h \in \mathcal P^+$ such that for each $t\geq 0$, we have $|T_t f_{sl}| \leq e^{- \delta t}h$.
-  Therefore, using Lemma \ref{lem: Lip of power function} we have
-  \begin{align}
-    &|(-iT_t f)^{1+\beta} - (-i f_c)^{1+\beta}|
-      \leq (1+\beta) ( |T_tf|^\beta + |f_c|^\beta) |T_tf_{sl}|
-    \\&\leq (1+\beta) ( |f_c + T_t f_{sl}|^\beta + |f_c|^\beta) e^{- \delta t} h
-    \leq (1+\beta) ( (|f_c| + |h|)^\beta + |f_c|^\beta) e^{- \delta t} h
-    =: e^{- \delta t} g,
-  \end{align}
-  where $g\in \mathcal P^+$.
-  Therefore
-  \begin{align}
-    \label{eq:P:S:1}
-    &\Big| \frac{1}{t} m_t[f] - \langle (-if_c)^{1+\beta}, \varphi\rangle\Big|
-      = \Big| \frac{1}{t} \cdot t \int_0^1  \big\langle (-iT_{rt}f)^{1+\beta} - (-if_c)^{1+\beta}, \varphi\big \rangle ~dr \Big|\\
-    &\leq \int_0^1  \big\langle |(-iT_{rt}f)^{1+\beta} - (-if_c)^{1+\beta}|, \varphi\big \rangle ~dr 
-      \leq \langle g,\varphi\rangle\int_0^1 e^{-\delta rt} ~dr
-      \xrightarrow[t\to \infty]{} 0.
-      \qedhere
-  \end{align}
-\end{proof}
-
-\begin{prop}
-  \label{prop:PL:S}
-  For each $f \in \mathcal P\setminus \{0\}$, there exists a non-degenerate $(1+\beta)$-stable random variable $\zeta^f$ such that $ E[e^{i\theta\zeta^f}] = e^{m[\theta f]}$ for all $\theta \in \mathbb R$.
-\end{prop}
-
-The proof of the above proposition relies on the following lemma:
-\begin{lem}
-  \label{lem: charactreisticfunction}
-  Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with
-  $\int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty)$.
-  Then
-  \[
-    \theta
-    \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},
-    \quad \theta \in \mathbb R^d,
-  \]
-  is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
-\end{lem}
-\begin{proof}
-  It follows from disintegration that there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
-  \[
-    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx)
-    = \int_S \lambda(d\xi) \int_{\mathbb R_+} f(t \xi)k(\xi,dt)
-    , \quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
-  \]
-  We define another measure $\lambda_0$ on $S$ by
-  \[
-    \lambda_0(d\xi)
-    := \frac1{\Gamma(-1-\beta)}\int_0^\infty t^{1+\beta}k(\xi,dt) \lambda (d\xi),
-  \]
-  where $\Gamma$ is the Gamma function.
-  Then $\lambda_0$ is a non-zero finite measure, since
-  \begin{align}
-    \lambda_0(S)
-      = &\frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt) \\
-   =  & \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
-  \end{align}
-  Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
-  \[
-    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)
-    = \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}}
-    ,\quad f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
-  \]
-  Then, according to \cite[Remark 14.4]{Sato2013Levy}, $\nu$ is the L\'evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is
-  \[
-    \hat \mu(\theta)
-    = \exp \Big \{ \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy) \Big \}
-    , \quad \theta \in \mathbb R.
-  \]
-  Finally, according to \eqref{eq: stable branching on C+}, we have
-  \begin{align}
-    & \int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
-      = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}} \\
-    & = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt) \\
-    & = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
-      = \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt) \\
-    & = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
-      \qedhere
-  \end{align}
-\end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop:PL:S}]
-	Suppose that $f\in \mathcal C_s \oplus \mathcal C_l$.
-Note that $m[\theta f]$ can be written as
-  \begin{align}
-    \label{eq:PL:S:1}
-    m[\theta f]
-    = \eta \int_0^{\infty}~ds\int_{\mathbb R^d} (-i\theta T_s f(x))^{1+\beta} \varphi(x)~dx,
-    \quad \theta \in \mathbb R.
-  \end{align}
-	Therefore, according to Lemma \ref{lem: charactreisticfunction}, in order to show that $\zeta^f$ is a $(1+\beta)$-stable random variable we only need to show that
-\begin{equation}\label{e:new}
-    \int_0^{\infty}~ds\int_{\mathbb R^d} | T_{s} f(x)|^{1+\beta} \varphi(x)~dx
-    \in (0, \infty).
-\end{equation}
-  According to the Step 1 in the proof of Lemma \ref{lem:m}, we know that there exist $\delta> 0$ and $h \in \mathcal P$ such that $|T_sf| \leq e^{- \delta s} h$ for each $s\geq 0$.
-The claim \eqref{e:new} then follows.
-
-  If $f \in \mathcal P \setminus (\mathcal C_s \oplus \mathcal C_l)$, then $f$ can be written by $f = f_c +(f - f_c)$ where $f_c \in \mathcal C_c\setminus\{0\}$ and $f - f_c \in \mathcal C_s \oplus \mathcal C_l$.
-  In this case, according to \eqref{eq:P:S:1}, $m[\theta f]$ has an integral representation:
-  \begin{align}
-    \label{eq:PL:S:2}
-    m[\theta f]
-    = \int_{\mathbb R^d} (-i\theta f_c(x))^{1+\beta} \varphi(x) ~dx,
-    \quad \theta \in \mathbb R.
-  \end{align}
-  Finally, according to Lemma \ref{lem: charactreisticfunction} and the fact that
- $
-    \int_{\mathbb R^d} | f_c(x)|^{1+\beta} \varphi(x)~dx
-    \in (0, \infty),
-  $
-  We have that $\zeta^f$ is a non-degenerate $(1+\beta)$-stable random variable.
-\end{proof}
-
-\subsection{A refined estimate for the OU semigroup}\label{sc:refined}
-It turns out that our proof of the CLT relies on the following refined estimate for the OU semigroup.
+I think that the proof stays the same.
 
@@
 
-\subsection{Small value probability}
-\label{sec: Small value probability}
-In this subsection, we digress briefly from our super-OU process and consider a (supercritical) \emph{continuous-state branching process (CSBP)} $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ with branching mechanism $\psi$ given by \eqref{eq: honogeneou branching mechanism}.
-Such a process $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is defined as an $\mathbb R^+$-valued Hunt process satisfying
-\[
-  \mathbf P_x[e^{-\lambda Y_t}] = e^{- x v_t(\lambda)},
-  \quad x\in \mathbb R^+, t\geq 0, \lambda \in \mathbb R^+,
-\]
-where for each $\lambda\geq 0$, $t\mapsto v_t(\lambda)$ is the unique positive solution to the equation
-\begin{align}
-  \label{eq: fkpp equation for CSBP}
-  v_t(\lambda) - \int_0^t \psi(v_s(\lambda))~ds = \lambda,
-  \quad t\geq 0.
-\end{align}
-It can be verified that for each $\mu \in \mathcal M(\mathbb R^d)$ with $x = \| \mu \|$, we have $ \{(\|X_t\|)_{t\geq 0}; \mathbb P_\mu\} \overset{\text{law}}{=} \{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
+%\end{doublespace}
 
-Our goal in this subsection is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ converges to $0$ when $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
-Suppose that Grey's condition is satisfied i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
-Also suppose that the $L \log L$ condition is satisfied i.e.,
-$
-  \int_1^\infty y \log y~\pi(dr)
- < \infty.
-$
-We write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
-
-\begin{prop}
-  \label{lem: control of XT}
-  Suppose that $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ such that $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
-  Then, for each $x\geq 0$, there exist $C,\delta>0$ such that
-  \[
-    \mathbf P_x(0<W_t\leq k_t)
-    \leq C(k_t^\delta + e^{-\delta t}), \quad t\geq 0.
-  \]
-\end{prop}
-
-\begin{proof}
-  \emph{Step 1.}
-  We recall some known facts about the CSBP $(Y_t)$.
-  For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of \eqref{eq: fkpp equation for CSBP}.
-  Letting $\lambda \to \infty$ in \eqref{eq: fkpp equation for CSBP}, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
-  \begin{align}
-    \label{eq: svp1}
-    \mathbf P_x(Y_t = 0)=e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
-  \end{align}
-  It is known, see \cite[Theorems 3.5--3.8]{Li2011Measure-valued} for example, that under Grey's condition $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ exists and is the largest root of $\psi$ on $[0,\infty)$.
-  Letting $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
-  \[
-    \mathbf P_x(\exists t \geq 0, Y_t = 0)
-    = e^{-x\bar v}, \quad x\geq 0.
-  \]
- Note the derivative of $\psi$, i.e.,
-  \[
-    \psi'(z)
-    = -\alpha + 2\rho z + \int_{(0,\infty)}(1-e^{-zy})y\pi(dy),\quad z\geq 0,
-  \]
-  is non-decreasing.
-  This says that $\psi$ is a convex function.
-  Also notice that $\psi'(0+)=-\alpha <0$ and that there exists $z>0$ such that $\psi(z)>0$.
-  Therefore we have (i) $\bar v > 0$; (ii) $\psi(z) < 0$ on $z\in (0,\bar v)$; and (iii) $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
-  It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that (i) if $\lambda \in (0,\bar v)$, then $0<\lambda \leq v_t(\lambda)<\bar v $; (ii) if $\lambda \in (\bar v, \infty)$, then $\bar v < v_t(\lambda)\leq \lambda< \infty$; and (iii) for each $\lambda \in (0,\infty)\setminus \{\bar v\}$ and $t\geq 0$, we always have
-    \(
-      \int_{v_t(\lambda)}^\lambda  \psi(z)^{-1}dz = t.
-    \)
-  Taking $\lambda \to \infty$ and using the monotone convergence theorem, we have that
-  \begin{align}
-    \label{eq:svp2}
-    \int_{\bar v_t}^\infty \frac{dz}{\psi(z)} = t, \quad t\geq 0.
-  \end{align}
-
-  \emph{Step 2.} We will show that, for each $x \geq 0$ there exists a constant $c_1>0$ such that
-  \[
-    \mathbf P_{x}(0< W_t\leq k_t)
-    \leq c_1\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
-    \quad t\geq 0.
-  \]
-  In fact, for all $x\geq 0$ and $t\geq 0$, we have
-  \begin{align}
-    & \mathbf P_{x}(0<W_t \leq k_t)
-      = \mathbf P_{x}( e^{-k_t^{-1}W_t}\geq e^{-1},W_t > 0) \\
-    & \leq e \mathbf P_{x}[e^{-k_t^{-1} W_t};W_t > 0]
-      =  e\big(\mathbf P_x[e^{-k_t^{-1} W_t}]-\mathbf P_x(W_t = 0)\big) \\
-    & = e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
-      \leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big),
-  \end{align}
-  as desired in this step.
-
-  \emph{Step 3.} We will show that there exist $c_2, \delta_1, t_0 > 0$ such that
-  \[
-    |\bar v_t-\bar v|
-    \leq c_2e^{-\delta_1 t}
-    , \quad t\geq t_0.
-  \]
-  In fact, since $\psi$ is a convex function, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for each $z\geq \bar v$.
-  According to Grey's condition, we can find $z_0 >\bar v $ such that $t_0 := \int^\infty_{z_0}\psi(z)^{-1}dz<\infty$.
-  For each $t > t_0$, according to \eqref{eq:svp2}, we have
-  \begin{align}
-    & t - t_0 =
-      \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)}
-      = \int_{\bar v_t}^{z_0} \frac{dz}{\psi(z)} \\
-    & \leq \int_{\bar v_t}^{z_0} \frac{dz}{(z-\bar v)\tau}
-      = \frac{1}{\tau} \big(\log (z_0-\bar v) - \log(\bar v_t-\bar v)\big).
-  \end{align}
-  Rearranging, we get $ \bar v_t - \bar v \leq (z_0 - \bar v)e^{-\tau(t-t_0)}, $ for all $t\geq t_0$.
-  This implies the desired result in this step.
-
-  \emph{Step 4.}
-  We will show that there exist $c_3, \delta_2, t_1>0$ such that
-  \[
-    |\bar v - v_t(k_t^{-1} e^{-\alpha t})|\leq
-    c_3k_t^{\delta_2}, \quad t\geq t_1.
-  \]
-  Define $\rho_t := 1+(\log k_t)/(t\alpha)$ for all $t\geq 0$.
-  By the fact that $k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}$ for  all $t\geq 0$ and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
-  Since the $L\log L$ condition is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate positive random variable.
-  This implies that
-  \[
-    v_t(e^{-\alpha t})
-    = -\log \mathbf P_1[e^{-W_t}]\xrightarrow[t\to \infty]{} - \log \mathbf P_{1}[e^{-W_\infty}]
-    =: z^* \in (0,\infty).
-  \]
-  The $L \log L$ condition also guarantees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s.
-in $\mathbf P_1$.
-This and the non-degeneracy of $W_\infty$ imply that
-  \[
-    z^*
-    = -\log \mathbf P_1[e^{-W_\infty}]
-    < -\log \mathbf P_1(W_\infty = 0) = \bar v.
-  \]
-
-  Fix an arbitrary $\epsilon \in (0,\tau)$.
-  According to the fact that $\tau=\psi'(\bar v)>0$, there exists $z_0 \in (0,\bar v)$ such that for all $z\in (z_0, \bar v)$, we have $-\psi(z)\geq (\bar v - z)(\tau- \epsilon)$.
-  Fix this $z_0$.
-  For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$.
-  Then we have for $t>0$ large enough,
-  \begin{align}
-    t
-    & =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
-      = \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)} \\
-    & = \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
-  \end{align}
-  where we used the fact that
-  \[
-    \int_{v_{\rho_t t}(e^{-\alpha \rho_tt})}^{z_0} \frac{dz}{-\psi(z)}
-    \xrightarrow[t\to \infty] {} \int_{z^*}^{z_0} \frac{dz}{-\psi(z)}.
-  \]
-  Now we have, for $t$ large enough,
-  \begin{align}
-    & t
-      \leq  \rho_t t + O(1) + \int_{z_0}^{v_t(k_t^{-1}e^{-\alpha t})} \frac{dz}{(\bar v-z)(\tau - \epsilon)} \\
-    & =  \rho_t t +O(1)- \frac{1}{\tau-\epsilon}\Big( \log \big(\bar v-v_t(e^{-\alpha \rho_t t})\big) - \log(\bar v-z_0)\Big).
-  \end{align}
-  Rearranging, we get, for $t$ large enough,
-  \[
-    e^{-t(\tau - \epsilon)}
-    \geq e^{-\rho_t t(\tau - \epsilon)+O(1)}(\bar v - v_t(e^{-\alpha \rho_t t})).
-  \]
-  Therefore, there exist $c_3>0$ and $t_1>0$ such that for all $t\geq t_1$,
-  \[
-    \bar v - v_t(k_t^{-1} e^{-\alpha t})
-    \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
-    \leq c_3k_t^{\frac{\tau - \epsilon}{\alpha}}.
-  \]
-  This implies the desired result in this step.
-
-  Finally, by Steps 2-4, we have for each $x\geq 0$, there exist $c_4, \delta_3, t_2 > 0$ such that
-  \[
-    \mathbf P_{x}(0< W_t\leq k_t)
-    \leq c_4(k_t^{\delta_3}+e^{-\delta_3 t})
-    , \quad t\geq t_2.
-  \]
-  Note that the left hand side is always bounded from above by $1$, so we can take $t_2 =0$ in the above statement.
-\end{proof}
-
-\subsection{Moments for super-OU processes}
-\label{sec: Moments for super-OU processes}
-In this subsection,  we want to find some upper bound for the $(1+\gamma)$-th moment of $X_t(g)$,
-where $\gamma \in (0,\beta)$ and $g\in \mathcal P$.
-
-\begin{lem}
-  \label{lem: control pair for P(M>lambda)}
-  There is a $(\theta^2\vee\theta^{1+\beta})$-controller $R$ such that for all $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we have
-  \[
-    \mathbb P_\mu ( |\mathcal{I}_0^tX_t(g)| > \lambda)
-    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\mu(R|\theta g|) d\theta.
-  \]
-\end{lem}
-
-\begin{proof}
-  It is elementary calculus (see the proof of \cite[Theorem 3.3.6]{Durrett2010Probability} for example) that
-for $u>0$ and $x\neq0$,
-  \[\frac{1}{u}\int_{-u}^u (1- e^{i\theta x})~d\theta = 2 - \frac{2\sin ux}{ux} \geq \mathbf 1_{ux>2}.\]
-  Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: upper bound for usgx}.(4).
-  Then, using Lemma \ref{lem: estimate of exponential remaining} we get
-  \begin{align}
-    & |\mathbb P_\mu (|\mathcal{I}_0^tX_t(g)| > \lambda)|
-       \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^tX_t(g)}])d\theta\Big| \\
-     & \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\mu(U_t(\theta g)-iP^\alpha_t (\theta g))}|d\theta
-     \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\mu(|U_t(\theta g) - iP^\alpha_t(\theta g)|) d\theta \\
-     & \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\mu(R|\theta g|) d\theta.
-      \qedhere
-  \end{align}
-\end{proof}
-
-\begin{lem}
-  \label{lem: temp}
-  For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists $C > 0$ such that for all $\kappa \in \mathbb Z_+ $, $\lambda > 0$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
-  \[
-     \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^sX_t(g)|>\lambda)
-    \leq C e^{\alpha r} \Big(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \Big).
-  \]
-\end{lem}
-
-\begin{proof}
-  Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: control pair for P(M>lambda)}.
-  Fix $h \in \mathcal P^+$, $\mu \in \mathcal M_c(\mathbb R^d)$ $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t < \infty$ with $s-r \leq 1$.
-  Suppose that $g\in \mathcal P$ satisfies $Q_\kappa g \leq h$.
-  Using the Markov property of $X$, we get
-  \begin{align}
-   & \mathbb P_{\mu}(|\mathcal I_r^sX_t(g)|>\lambda)
-      = \mathbb P_\mu \Big[\mathbb P_\mu [| X_{s}(P_{t-s}^\alpha g) -  X_{r}(P_{t-r}^\alpha g)|> \lambda | \mathscr F_r ]\Big] \\
-     & = \mathbb P_\mu \big[\mathbb P_{X_r}(| X_{s-r}(P_{t-s}^\alpha g) -  X_{0}(P_{t-r}^\alpha g)|> \lambda)\big] \\
-    & = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r} X_{s-r}( P_{t-s}^\alpha g) |> \lambda)\big]
-      \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}X_r(R|\theta P^\alpha_{t-s}g|) d\theta \Big] \\
-     & \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}X_r(R|\theta e^{(t-s)(\alpha- \kappa b)}h|) d\theta \Big] \\
-     & \leq \mathbb P_\mu [X_r(Rh) ]
-\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
-     \\ & =  \mu(P_r^\alpha Rh)
-\Big(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\Big)
-    \\ & \leq C e^{\alpha r} \Big(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \Big),
-  \end{align}
-where $C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big) \mu(Q_0Rh)>0$.
-\end{proof}
-
-For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write $ \|Y\|_{\mathbb P;p} := \mathbb P[|Y|^p]^{1/p}$.
-Recall that we write $\tilde u = \frac{u}{1+u}$ for each $u\neq -1$.
-\begin{lem}
-  \label{lem: control of mgtrs}
-  For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists $C > 0$ such that for all $\kappa \in \mathbb Z_+$ and $0\leq r \leq s\leq t<\infty$ with $s-r \leq 1$, we have
-  \[
-     \sup_{g \in \mathcal P: Q_\kappa g \leq h} \|\mathcal I_r^s X_t(g) \|_{\mathbb P_\mu;1+\gamma}
-    \leq C e^{t\alpha (1- \tilde \gamma)+(t-s) (\alpha \tilde \gamma - \kappa b)}.
-  \]
-\end{lem}
-
-\begin{proof}
-  Fix $h \in \mathcal P$ and $\mu \in \mathcal M_c(\mathbb R^d)$. Let $C_0$ be the constant in the Lemma \ref{lem: temp}.
-  For all $\kappa \in \mathbb Z_+$,  $0\leq r\leq s\leq t$ with $s-r \leq 1$,  $g\in \mathcal P$ with $Q_{\kappa} g \leq h$, and $c>0$, we have
-  \begin{align}
-     & \mathbb P_\mu[|\mathcal I_r^sX_t(g)|^{1+\gamma}]
-       = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^sX_t(g)|>\lambda) d\lambda \\
-     & \leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^sX_t(g)|> \lambda) d\lambda \\
-    & \leq c^{1+\gamma} + C_0  e^{\alpha r}(1+\gamma)\int_c^\infty \bigg(\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta}+\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2}\bigg)\lambda^{\gamma}d\lambda \\
-    & \leq c^{1+\gamma} e^{\alpha r} + C_0e^{\alpha r}(1+\gamma)\Big(  \frac{e^{(1+\beta)(t-s)(\alpha- \kappa b)}}{(\beta - \gamma)c^{\beta - \gamma}}  + \frac{e^{2(t-s)(\alpha- \kappa b)}}{(1 - \gamma)c^{1 - \gamma}} \Big).
-  \end{align}
-  Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
-  \begin{align}
-     & \mathbb P_\mu\big[|\mathcal I_r^s X_t(g)|^{1+\gamma}\big]
-      \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
-  \end{align}
-  Note that
-  \begin{align}
-    & (1+\gamma) (t-s) (\alpha- \kappa b) + \alpha r
-      = (t-s)\alpha+(t-s) (\gamma \alpha- (1+\gamma )\kappa b) \\
-    & \leq t\alpha+(t-s) (\gamma \alpha- (1+\gamma)\kappa b).
-  \end{align}
-  So the desired result is true.
-\end{proof}
-
-\begin{lem}
-  \label{lem:P:M:uc}
-  For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for all $t\geq 0$, we have
-  \begin{enumerate}
-  \item
-    \label{item:P:M:uc:1}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha \tilde \gamma > \kappa b$;
-  \item
-    \label{item:P:M:uc:2}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma = \kappa b$;
-  \item
-    \label{item:P:M:uc:3}
-    $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha \tilde \gamma < \kappa b$.
-  \end{enumerate}
-\end{lem}
-
-\begin{proof}
-  Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
-  Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
-  Using the triangle inequality, for all $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$, we have
-  \begin{align}
-    & \|X_t(g)\|_{\mathbb P_\mu;1+\gamma}
-      \leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}X_t(g) \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}X_t(g)  \big\|_{\mathbb P_\mu;1+\gamma} + |\mu(P^\alpha_t g)| \\
-    & \leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \mu(h).
-  \end{align}
-  By calculating the sum on the right, we get the desired result.
-\end{proof}
-
-\section{Proofs of main results}
-\label{proofs of main results}
-In this section, we will prove the main results of this paper.
-For simplicity, we will write $\mathbb{\widetilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in this section.
-
-\subsection{Law of large numbers}
-\label{sec: large rate lln}
-
-In this subsection, we prove Theorem \ref{thm: law of large number}.
-For this purpose, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$.
-Recall that $L$ is the infinitesimal generator of the OU-process.
-For $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and  $a\in \mathbb R$, we define
-\begin{align}
-  \label{defmartingale}
-  M_t^{f,a}
-   :=e^{-(\alpha-ab)t}X_t(f)-\int_0^t e^{-(\alpha-ab)s} X_s((L+ab)f)~ ds.
-\end{align}
-Let $(\mathscr{F}_t)_{t\geq 0}$ be the natural filtration of $X$.  The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
-
-\begin{lem}
-  \label{lemma25}
-  For all $f\in \mathcal{P}\cap C^2(\mathbb R^d)$, $a\in \mathbb R$ and $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
-\end{lem}
-
-\begin{proof}
-  Put$\bar{f} :=(L+ab)f$.
-  It follows easily from Ito's formula that
-  \begin{align}
-    \label{Theorem55}
-    P_t^{ab}f(x)
-    = f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d,
-  \end{align}
-  where $P_t^{ab} := e^{abt}P_t$.
-  For $0\leq s\leq t$, we have
-  \begin{align}
-    \label{martingale1}
-    & \quad\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
-    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[X_t(f)|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}X_u(\bar{f})~ du\Big|\mathscr{F}_s\big] \\
-    & =e^{-(\alpha-ab)t} X_s(P_{t-s}^{\alpha}f)-\int_0^s e^{-(\alpha-ab)u} X_u(\bar{f})~ du - \int_s^t e^{-(\alpha-ab)u}X_s(P_{u-s}^{\alpha} \bar{f})~ du.
-  \end{align}
-  Using \eqref{Theorem55} and Fubini's theorem, we have
-  \begin{align}
-    & \int_s^t e^{-(\alpha-ab)u}X_s(P_{u-s}^{\alpha} \bar{f})~ du=e^{-(\alpha-ab)s}\int_s^tX_s(P_{u-s}^{ab}\bar{f})~du\\
-    & = e^{ - ( \alpha - ab ) s } X_s\left( \int_0^{t-s} P_{u}^{ab} \bar{f}~ du\right)
-      = e^{-(\alpha-ab)s}\left(X_s(P_{t-s}^{ab}f) - X_s(f) \right) \\
-    & = e^{-(\alpha-ab)t} X_s( P_{t-s}^{\alpha}f) - e^{ - ( \alpha - ab ) s} X_s(f).
-  \end{align}
-  Using this and \eqref{martingale1}, we get the desired result.
-\end{proof}
-
-Recall that, for $p\in \mathbb Z_+^d$,  $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-|p|b$ and $ H_t^p =e^{-(\alpha-|p|b)t}X_t(\phi_p)$ for each $t\geq 0$.
-
-\begin{lem}
-  \label{lem:M:L:ML}
-   For all $\mu\in \mathcal M_c(\mathbb R^d)$ and $p \in \mathbb Z_+^d$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_{\mu}$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
-    Moreover if $\alpha\tilde \beta>|p|b$, the martingale is bounded in $L^{1+\gamma}(\mathbb P_\mu)$ for each $\gamma\in (0, \beta)$.
-  Thus the limit $ H_{\infty}^p := \lim_{t\rightarrow \infty}H_t^p $  exists $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma \in (0,\beta)$.
-\end{lem}
-
-\begin{proof}
-  Fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and a $p \in \mathbb Z_+^d$.
-  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale.
-  Further suppose that $\alpha \tilde \beta > |p| b$.
-  Then there exists a $\gamma_0 \in (0,\beta)$ which is close enough to $\beta$ so that $\alpha\tilde \gamma>|p|b$ for each $\gamma\in [\gamma_0, \beta)$.
-  Using  Lemma \ref{lem:P:M:uc} and the fact $\kappa_{\phi_p}=|p|$, we get that, for each $\gamma\in [\gamma_0, \beta)$, there exists a constant $C>0$ such that
-  \[
-    \|H_t^p\|_{\mathbb P_\mu;1+\gamma}
-    \leq C e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
-    = C
-    , \quad t\geq 0.
-  \]
-  For each $\gamma\in (0, \gamma_0)$ there exists a constant $C'>0$ such that
-  \[
-    \| H_t^p \|_{\mathbb P_\mu;1+\gamma}
-    \leq \| H_t^p \|_{\mathbb P_\mu;1+\gamma_0}
-    \leq C',
-    \quad t\geq 0.
-  \]
-  Therefore, for each $\gamma \in (0,\beta)$, the martingale $(H_t^p)_{t\geq 0}$ is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-\end{proof}
-
-\begin{lem}
-  \label{lem: control of wt}
-  Suppose that $\mu\in \mathcal M_c(\mathbb R^d)$ and that $p \in \mathbb Z_+^d$ satisfies $\alpha \tilde \beta > |p|b$.
-  Then for each $\gamma \in (0,\beta)$ satisfying $\alpha \tilde \gamma > |p|b$, there exists a constant $C> 0$ such that,
-  \[
-    \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C e^{-(\alpha \tilde \gamma-|p|b)s},
-    \quad 0 \leq s < t \leq \infty.
-  \]
-\end{lem}
-
-\begin{proof}
-  Thanks to Lemma \ref{lem:M:L:ML}, we only  need to prove the inequality  when $0\leq s < t<\infty$.
-  Suppose $p\in \mathbb{Z}_+^d$, $\mu\in \mathcal M_c(\mathbb R^d)$ and  $\gamma \in (0,\beta)$ with $\alpha \tilde \gamma > |p|b$ are fixed.
-  Using Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$,  we know that there exists a constant $C_1>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$,
-  \begin{align}
-    \|H^p_s-H^p_r\|_{\mathbb P_\mu; 1+\gamma}
-    \leq  C_1 e^{-(\alpha\tilde \gamma-|p|b)s}.
-  \end{align}
-  Thus there exists $C_2>0$ such that for all $0\leq s<t$,
-  \begin{align}
-    & \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma} \\
-    & \leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma} \\
-    & \leq C_1 \Big(e^{-(\alpha \tilde \gamma- |p|b) s}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor} e^{-(\alpha \tilde \gamma- |p|b) k} + e^{-(\alpha \tilde \gamma-|p|b) t}\Big)
-      \leq C_2e^{-(\alpha \tilde \gamma-|p|b)s}.
-      \qedhere
-  \end{align}	
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{thm: law of large number}]
-	Fix $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
-	Write
-  \[
-    f
-    = \sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
-    =: \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\widetilde{f}.
-  \]
-	Then
-  \begin{align}
-    & e^{-(\alpha-\kappa_fb)t}X_t(f)=
-      \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} X_t(\widetilde{f}),
-      \quad t\geq 0.
-  \end{align}
-	According to Lemma \ref{lem:M:L:ML}, we have
-  \begin{align}
-    \label{as convergence}
-    \sum_{p\in \mathbb{Z}_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p
-    \xrightarrow[t\to \infty]{} \sum_{p\in \mathbb{Z}_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
-  \end{align}
-  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for each $\gamma\in(0,\beta)$.
-  Therefore, it suffices to show that
-  \begin{align}
-    J_t
-    :=e^{-(\alpha-\kappa_fb)t}X_t( \widetilde{f}),
-    \quad t\geq 0,
-  \end{align}
-  converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges almost surely provided $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$.
-
-  \emph{Step 1.} Let $g\in \mathcal P$.
-  Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa b < \alpha \tilde \beta$.
-  We will show that for each $\gamma \in (0,\beta)$ there exist $C_1,\delta_1 > 0$ such that
-  \[
-    \|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb P_\mu;1+\gamma}
-    \leq C_1 e^{-\delta_1 t},
-    \quad t\geq 0.
-  \]
-  In order to do this, we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that $\kappa b< \alpha \tilde \gamma$ for each $\gamma \in [\gamma_0, \beta)$.
-  According to Lemma \ref{lem:P:M:uc}, we have for each $\gamma \in (0,\beta)$,
-  \begin{enumerate}
-  \item
-    if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma> \kappa_g b$, then there exists $C_2>0$ such that
-    \[
-      \|e^{-(\alpha - \kappa b)t}  X_t(g)\|_{\mathbb P_\mu;1+\gamma}
-      \leq C_2 e^{-(\alpha-\kappa b)t}e^{(\alpha-\kappa_g b)t}
-      \leq C_2  e^{-(\kappa_g - \kappa )bt},
-      \quad t\geq 0;
-    \]
-  \item
-    if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma=\kappa_g b$, then there exists $C_3>0$ such that
-    \[
-      \|e^{-(\alpha - \kappa b)t}  X_t(g)\|_{\mathbb P_\mu;1+\gamma}
-      \leq C_3 t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-      = C_3 t e^{-(\alpha \tilde \gamma - \kappa b)t},
-      \quad t\geq 0;
-    \]
-  \item
-    if $\gamma \in [\gamma_0, \beta)$ and $\alpha\tilde \gamma < \kappa_g b$, then there exists $C_4>0$ such that
-    \[
-      \|e^{-(\alpha - \kappa b)t}  X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}
-      \leq C_4  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
-      = C_4  e^{-(\alpha \tilde \gamma - \kappa b)t},
-      \quad t\geq 0;
-    \]
-  \item
-  if $\gamma \in (0,\gamma_0)$,  then
-    thanks to (1)--(3) above and the fact that \[\|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}
-      \leq \|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C_5, \delta_2 >0$ such that
-    \[
-      \|e^{-(\alpha - \kappa b)t} X_t(g)\|_{\mathbb{P}_{\mu};1+\gamma}
-      \leq C_5e^{-\delta_2 t},
-      \quad t\geq 0.
-    \]
-  \end{enumerate}
-  Thus, the desired conclusion in this step is valid.
-  In particular, by taking $g = \widetilde f$ and $\kappa = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
-
-  \emph{Step 2.}
-  We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$.
-  We will show that $J_t$ converges to $0$ almost surely.
-  For $a \geq 0$, $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
-  \begin{align}
-    L_t^{g,a}
-    & :=\int_0^t e^{-(\alpha-ab)s}X_s((L+ab)g) ds,
-    \quad
-    Y_t^{g,a}
-    :=\int_0^t e^{-(\alpha-ab)s}|X_s((L+ab)g)|ds.
-  \end{align}
-  Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 b < \alpha \tilde \beta$.
-  According to \eqref{defmartingale},
-  \begin{align}
-    J_t
-    = e^{-(a_0-\kappa_f)bt} (M_t^{\widetilde{f}, a_0}+L_t^{\widetilde{f}, a_0}),
-    \quad t\geq 0.
-  \end{align}
-  So we only need to show that
-  \begin{align}
-    e^{-(a_0-\kappa_f)b t}M_t^{\widetilde{f},a_0}
-    \xrightarrow[t\to \infty]{} 0,
-    \quad e^{-(a_0-\kappa_f)b t}L_t^{\widetilde{f},a_0}
-    \xrightarrow[t\to \infty]{} 0,
-    \quad \mathbb{P}_{\mu}\text{-a.s.}
-  \end{align}
-  Notice that $\kappa_{(L+a_0 b)\widetilde{f}}\geq \kappa_{\widetilde{f}}\geq \kappa_f+1 > a_0$.
-  By Step 1, for any fixed $\gamma\in (0,\beta)$, there exist $C_6, \delta_3>0$ such that for each $t\geq 0$,
-  \[
-    \| e^{-(\alpha-a_0 b)t}X_t(\widetilde{f}))\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C_6 e^{-\delta_3 t},
-    \quad \|e^{-(\alpha-a_0 b)t}X_t(L\widetilde{f}+a_0 b\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C_6 e^{-\delta_3 t}.
-  \]
-  Now, by the triangle inequality, for each $t\geq 0$,
-  \begin{align}
-    & \|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-      \leq\|Y_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma} \\
-    & \leq \int_0^t \|e^{-(\alpha-a_0 b)s}X_s( L\widetilde{f}+a_0 b\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C_6 \int_0^t e^{-\delta_3 s}ds\leq\frac{C_6}{\delta_3}.
-  \end{align}
-  Since $Y_t^{\widetilde{f},a_0}$ is increasing in $t$, it converges to some finite random variable $Y_{\infty}^{\widetilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
-  Consequently,  we have
-  \begin{align}
-    \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\widetilde{f},a_0}|
-    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\widetilde{f},a_0}|=0,
-    \quad \mathbb P_\mu\text{-a.s.}
-  \end{align}
-  On the other hand, the martingale $M_t^{\widetilde{f},a_0}$ satisfies
-  \begin{align}
-    \|M_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq \|e^{-(\alpha-a_0 b)t}X_t(\widetilde{f})\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\widetilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
-    \leq C_6(e^{-\delta_3 t}+\frac{1}{\delta_3}),
-    \quad t\geq 0.
-  \end{align}
-  This implies that the martingale converges almost surely.
-  Consequently,
-  \[
-    \lim_{t\rightarrow\infty} e^{-(a_0-\kappa_f)bt}M_t^{\widetilde{f},a_0}
-    = 0,
-    \quad \mathbb P_\mu\text{-a.s.}.
-    \qedhere
-  \]
-\end{proof}
-
-\subsection{Central limit theorems for unit time intervals}
-\label{sec:critical}
-In this subsection, we will establish the following CLT.
-\begin{thm}
-  \label{lem:PR:LC}
-If  $\mu \in \mathcal M_c(\mathbb R^d)$ and $f\in \mathcal{P}\setminus \{0\}$,
-then  under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
-  \begin{align}
-    \label{eq:PR:LC:1}
-    \Upsilon^f_t
-    := \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}
-    \xrightarrow[t\to \infty]{d}\zeta^f_0,
-  \end{align}
-  where $\zeta^f_0$ is a $(1+\beta)$-stable random variable with characteristic function $\theta\mapsto e^{\langle Z_1(\theta f), \varphi\rangle}$.
-\end{thm}
-
-In fact, we prove a stronger result:
-
-\begin{prop}
-  \label{thm:Key}
-  For all $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P \setminus \{0\}$, there exist $C,\delta>0$ such that
-  for all $t\geq 1$ and $f \in \mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$, we have
-  \[
-    \mathbb P_\mu
-    \Big[  |\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  |\Big]
-    \leq C e^{- \delta t}.
-  \]
-\end{prop}
-
-\begin{proof}
-  Fix  $\mu \in \mathcal M_c(\mathbb R^d)$ and $g \in \mathcal P\setminus \{0\}$.
-
-  \emph{Step 1.} Write $ A_t(\epsilon) :=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \} $ for $t\geq 0$ and $\epsilon > 0$.
-  We will show that for all $f\in \mathcal P \setminus \{0\}$, $\epsilon > 0$ and $t\geq 0$, it holds that
-  \[
-    \mathbb P_\mu \Big[ | \mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1(\theta f), \varphi\rangle}; D^c | \mathscr F_t ]| \Big]
-    \leq J^f_1(t,\epsilon)+J^f_2(t,\epsilon)+J^f_3(t,\epsilon),
-  \]
-where
-\begin{align}
-\label{eq: Def of Ji}
-  &J^f_1(t,\epsilon):= \mathbb{P}_{\mu} [ | X_t(Z'''_1(\theta_t f)) |; A_t(\epsilon) ],
- \quad
-  J^f_2(t,\epsilon):= \mathbb{P}_{\mu}[|X_t( Z_1(\theta_t f))-\langle Z_1f, \varphi\rangle |; A_t(\epsilon)],
-  \\ & J_3(t,\epsilon):=2\mathbb{P}_{\mu}(A_t (\epsilon)\Delta D^c),
- \quad
-   \theta_t := \|X_t\|^{-(1 - \tilde \beta)}.
-\end{align}
-In fact, it follows from \eqref{eq: key equality}, the definitions of $U_1$, $Z'''_1$ and $Z_1$, that for all $t\geq 0$,
-\begin{align}
-  \label{eq: need1}
-  & \mathbb{P}_{\mu}[e^{i\Upsilon^f_t}|\mathscr{F}_t]
-    = \mathbb{P}_{\mu}[\exp\{i\theta_t X_{t+1} (f) - i \theta_t X_t(P_1^\alpha f)\} |\mathscr{F}_{t}] \\
-  & = \exp\{X_t((U_1 - iP^\alpha_1 ) (\theta_t f))\}
-    = \exp\{X_t((Z_1 + Z'''_1) (\theta_t f))\}.
-\end{align}
-From Lemma \ref{lem: charactreisticfunction}, we  get that $\theta\mapsto \langle Z_1(\theta f),\varphi\rangle$ is the characteristic function of some $(1+\beta)$-stable random variable, and then  $\operatorname{Re} \langle Z_1f, \varphi\rangle \leq 0$.
-Using this, \eqref{eq: need1}, \eqref{eq: -v has positive real part} and the fact $|e^{-x} - e^{-y}| \leq |x-y|$ for all $x,y \in \mathbb C_+$, we get for each $t\geq 0$ and $\epsilon> 0$,
-\begin{align}
-  \label{eq: inequality that will used later}
-  & \mathbb{P}_\mu \Big[ |  \mathbb{P}_\mu [ e^{i\Upsilon^f_t} - e^{\langle Z_1f,\varphi \rangle} ; D^c | \mathscr F_{t}]   |\Big]  \\
-  &  \leq \mathbb{P}_\mu   \Big[ |    \mathbb{P}_\mu [ e^{i \Upsilon^f_t }-e^{\langle Z_1f, \varphi\rangle}; A_{t}(\epsilon) | \mathscr F_{t}] |  + 2\mathbb P_\mu ( A_{t}(\epsilon) \Delta D^c | \mathscr F_{t}) \Big] \\
-  & = \mathbb{P}_{\mu}\Big[ |\mathbb{P}_\mu [e^{i\Upsilon^f_t}| \mathscr F_{t}]-e^{\langle Z_1f, \varphi\rangle}| ; A_{t}(\epsilon) \Big] + J_3(t,\epsilon) \\
-  & \leq \mathbb{P}_\mu \Big[ |e^{X_{t}((Z_1+Z'''_1) (\theta_t f))}-e^{\langle Z_1f, \varphi\rangle} | ; A_{t}(\epsilon) \Big]+  J_3(t,\epsilon) \\
-  & \leq \mathbb{P}_\mu \Big[ | X_{t} ( (Z_1+Z'''_1)(\theta_t f)) - \langle Z_1f, \varphi\rangle | ;A_{t}(\epsilon)\Big]+  J_3(t,\epsilon) \\
-  & \leq J^f_1(t,\epsilon) + J^f_2(t,\epsilon)+ J_3(t,\epsilon).
-\end{align}
-
-\emph{Step 2.} We will show that for $\epsilon>0$ small enough, there exist  $C_2, \delta_2>0$ such that for all $t\geq 1$ and
-$f \in \mathcal P_g$, we have $ J^f_1(t,\epsilon) \leq C_2e^{-\delta_2 t}$.
-
-In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
-Acording to Step 1 in the proof of Lemma \ref{lem:m}, there exists $h_{2} \in \mathcal P^+$ such that for each $f \in \mathcal P_g$ it holds that $|f| \leq h_{2}$.
-Then, we have for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
-\begin{align}
-  & |Z'''_1(\theta_t f)|\mathbf{1}_{A_{t}(\epsilon)}
-    \leq R(|\theta_{t} f|)\mathbf{1}_{A_{t}(\epsilon)}
-    \leq R \Big(\frac{h_{2}}{e^{(\alpha-\epsilon)t(1-\tilde \beta)}}\Big)
-    \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}Rh_{2}.
-\end{align}
-Thus for all $t\geq 0$, $\epsilon> 0$ and $f\in \mathcal P_g$,
-\begin{align}
-  \label{eq: estimate of J1}
-  J^f_1(t,\epsilon)
-& \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)t}\mathbb{P}_{\mu}[X_{t}(Rh_2)]
-  \leq \sum_{\rho \in \{\delta_0,1\}} \mu(Q_0 R h_{2}) e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})t},
-\end{align}
-where $Q_0$ is defined by \eqref{eq:Q}.
-By taking $\epsilon>0$ small enough, we get the desired result in this step.
-
-\emph{Step 3.}
-We will show that for $\epsilon>0$ small enough there exist $C_3, \delta_3 > 0$ such that for all $t \geq 0$ and $f\in \mathcal P_g$,  we have $ J^f_2(t,\epsilon) \leq C_3 e^{-\delta_3 t}$.
-In fact, for all $t\geq 0$, and $f\in \mathcal P_g$,
-\begin{align}
-  & X_{t}(Z_1(\theta_t f))- \langle Z_1f, \varphi\rangle
-     = \theta_t^{1+\beta} X_t(Z_1 f) - \langle  Z_1 f,\varphi \rangle
-     = \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle),
-\end{align}
-and therefore,
-\begin{align}
-  \label{eq: prevJ2}
-  J^f_2(t,\epsilon)
-  & = \mathbb P_\mu\Big[\Big|  \frac{1}{\|X_{t}\|}X_t(Z_1f - \langle  Z_1 f ,\varphi \rangle) \Big|;A_t(\epsilon)\Big]
-    \leq e^{-(\alpha-\epsilon)t} \mathbb{P}_{\mu}[|X_t (q_f) |].
-\end{align}
-where $ q_f = Z_1 f-\langle  Z_1 f,\varphi\rangle \in \mathcal P^*$.
-It follows from Lemma \ref{lem:P:R} that there exists $h_{3}\in \mathcal{P}$ such that for each $ f\in \mathcal P_g$, we have $Q_1 (\operatorname{Re} q_f) \leq h_{3} \text{ and } Q_1 (\operatorname{Im} q_f)\leq h_3$, where $Q_1$ is given by \eqref{eq:Q} with $\kappa=1$.
-In the rest of this step, we  fix a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
-According to Lemma \ref{lem:P:M:uc}.(3) (with $\kappa=1$), there exists $C_{3}>0$ such that for all $t\geq 0$ and $f\in \mathcal P_g$,
-\begin{align}
-  & \mathbb{P}_{\mu}\left[\left|X_{t}(q_f)\right|\right]
-    \leq \| X_{t}( \operatorname{Re} q_f)\|_{\mathbb{P}_{\mu,1+\gamma}} + \| X_{t}(\operatorname{Im} q_f)\|_{\mathbb{P}_{\mu,1+\gamma}} \\
- & \leq 2\sup_{q\in \mathcal P: Q_1 q\leq h_{3}} \|X_t(q)\|_{\mathbb P_\mu; 1+\gamma} \leq C_{3} e^{\frac{\alpha t}{1+\gamma}}.
-\end{align}
-Therefore, for all $t\geq 0, \epsilon > 0$ and $f \in \mathcal P_g$, we have
-\begin{align}
-  \label{eq: right bound for J2}
-   J^f_2(t, \epsilon)
-    \leq  C_3 e^{-(\alpha-\epsilon)t}e^{\frac{\alpha t}{1+\gamma}}
-   \leq C_{3} e^{-(\alpha\tilde \gamma -\epsilon)t}.
-\end{align}
-By taking $\epsilon >0$ small enough, we get the required result in this step.
-
-\emph{Step 4.}
-We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C_4,\delta_4>0$ such that for all $t\geq 1$, $J_3(t,\epsilon)\leq C_4e^{-\delta_4 t}.$
-In fact, we have  for all $t\geq 0, \epsilon >0$,
-\[
-  \mathbb P_{\mu}(A_{t}(\epsilon), D)
-  = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
-  = \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
-  \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
-\]
-On the other hand, by Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there exists  $C_{4}, \delta_{4}>0$ such that for all $t\geq 0$,
-\begin{align}
-  \mathbb P_\mu(A_t(\epsilon)^c,D^c)
-  \leq \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\|
-  \leq e^{ - \epsilon t}) \leq C_{4} (e^{-\epsilon \delta_{4} t}+e^{-\delta_{4} t}).
-\end{align}
- Combining these results, we get the desired result in this step.
-
- \emph{Step 5.} Combining the results in Steps 1--4, we immediately get the desired result.
-\end{proof}
-
-The following corollary  will be used later in the proof of Theorem \ref{thm:M}.
-\begin{cor}
-  \label{cor:MI}
-If  $g\in \mathcal{P}\setminus\{0\}$ and $\mu\in \mathcal M_c(\mathbb R^d)$, then there exist $C,\delta>0$ such that for
-all $l\leq n$ in $\mathbb Z_+$ and  $(f_j)_{j=l}^n\subset \mathcal P_g$,
-\begin{align}
-  \label{32corollary}
-  \Big|\mathbb{\widetilde{P}}_{\mu}\Big[\prod_{k=l}^ne^{i \Upsilon^{f_k}_{k} }-\prod_{k=l}^n e^{\langle Z_1f_k, \varphi\rangle}\Big]\Big|\leq C e^{-\delta l}.
-\end{align}
-\end{cor}
-\begin{proof}
-  For  $l\leq n$ in $\mathbb Z_+$, $k \in \{l,\dots,n\}$ and $(f_j)_{j=l}^n\subset \mathcal P_g$, define
-  \[
-    a_k
-    :=  \mathbb{\widetilde{P}}_{\mu}\Big[\prod_{j=l}^{k} e^{i\Upsilon_j^{f_j}}\Big] \times \Big(\prod_{j=k+1}^{n} e^{ \langle Z_1f_j,\varphi \rangle} \Big).
-  \]
-  Then for all $l\leq n$ in $\mathbb Z_+$, $k \in \{l,\dots,n\}$ and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
-  \begin{align}
-    & a_{k} - a_{k-1}
-      =\mathbb{P}_{\mu}(D^c)^{-1} \mathbb{P}_{\mu}\Big[(e^{i\Upsilon^{f_k}_k}-e^{\langle Z_1f_k, \varphi\rangle})\prod_{j=l}^{k-1} e^{i\Upsilon_j^{f_j}};D^c\Big] \Big(\prod_{j=k+1}^n e^{\langle Z_1f_j, \varphi\rangle}\Big)\\
-    & =\mathbb{P}_{\mu}(D^c)^{-1} \mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c|\mathscr F_k] \prod_{j=l}^{k-1} e^{i\Upsilon_j^{f_j}}\Big] \Big(\prod_{j=k+1}^{n}e^{\langle Z_1f_j, \varphi\rangle}\Big).
-  \end{align}
-  By Lemma \ref{thm:Key}, there exist $C_0,\delta_0 >0$ such that for all $l\leq n$ in $\mathbb Z_+$,  $k \in \{l,\dots , n\}$, and $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
-  \begin{align}
-    | a_{k} - a_{k-1}|
-    & \leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon_k^{f_k}}-e^{\langle Z_1f_k, \varphi \rangle}; D^c | \mathscr{F}_k]\big|\Big]
-    \leq C_0 e^{-\delta_0 k}.
-  \end{align}
-  Therefore, there exist $C,\delta >0$ such that for all $l\leq n$ in $\mathbb Z_+$ and each $(f_j)_{j=l}^n\subset \mathcal P_g$, we have
-  \begin{align}
-    \text{LHS of \eqref{32corollary}}
-    & = \left|a_n-a_{l-1}\right|
-      \leq \sum_{k=l}^n\left|a_{k}-a_{k-1}\right|
-      \leq \sum_{k=l}^n C_0 e^{-\delta_0 k}
-      \leq C e^{- \delta l}.
-      \qedhere
-  \end{align}
-\end{proof}
-
-\subsection{Central limit theorem for $f\in \mathcal C_s$}
-\label{sec: small rate}
-
-\begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:1})]
-	Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_s$ and $t_0 > 1$  large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for all $t\geq t_0$.
-  For each $t\geq t_0$, in this proof we write $\theta_t = \|X_t\|^{\tilde \beta - 1}$,
-  \begin{multline}
-    \label{eq:PM:CLTS:1}
-    \theta_t  X_t(f)
-    = I^f_1(t) + I^f_2(t) + I^f_3(t)
-    := \Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \theta_t \mathcal I_{t-k-1}^{t-k} X_t(f) \Big)\\
-    + \Big( \theta_t \mathcal I_0^{t-\lfloor t \rfloor} X_t(f)   + \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \theta_t \mathcal I_{t-k-1}^{t-k} X_t(f) \Big) + (\theta_t X_0(P_t^\alpha f) ),
-  \end{multline}
-  and $ I^f_0(t) := \sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f},$ where $\tilde f:= e^{\alpha(\tilde \beta - 1)} f$.
-
-  \emph{Step 1.} We show that $I^f_0(t) \xrightarrow[t\to \infty]{d} \zeta^f$.
-  In fact, for each $k \in \mathbb Z_+$, we have  $T_{k} \tilde f \in \mathcal P_{\tilde f}:=\{\theta T_n \tilde f: n \in \mathbb Z_+, \theta \in [-1,1]\}$.
-  Therefore from Corollary \ref{cor:MI} we get that there exist $C_1,\delta_1 > 0$ such that
-  \begin{align}
-    \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i I^f_0(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}\tilde f, \varphi\rangle \Big)\Big|
-    \leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)},
-    \quad t\geq t_0.
-  \end{align}
-  On the other hand, using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of the semigroup $(P_t)_{t\geq 0}$, we have
-  \begin{align}
-    \label{eq:PM:CLTS:2}
-    & \sum_{k=0}^\infty \langle Z_1 T_{k} \tilde f, \varphi \rangle
-    = \sum_{k=0}^\infty \int_0^1 \langle P_u^\alpha ((-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle ~du
-    \\& = \sum_{k=0}^\infty \int_0^1 e^{\alpha u} \langle  (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle ~du
-    \\& = \sum_{k=0}^\infty \int_0^1 \langle  (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle~du
-    = \int_0^\infty \langle  (-iT_{u} f)^{1+\beta}, \varphi\rangle~du = m[f].
-  \end{align}
-  Therefore, we have $\mathbb{\widetilde{P}}_{\mu} [e^{i I^f_0(t)} ] \xrightarrow[t\to \infty]{} e^{m[f]}$.
-Since $I_0^f(t)$ is linear in $f$, we can replace $f$ with $\theta f$, $\theta \in \mathbb R$, and then the desired result in this step follows.
-
-  \emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$.
-  In fact,  by \cite[Lemma 3.4.3]{Durrett2010Probability} we have that for each $t\geq t_0$,
-  \begin{align}
-    \label{eq:PM:S:1}
-    |\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t) - I^f_0(t) ) }] - 1|
-    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\widetilde{P}}_{\mu}\big[|Y_{t,k}|\big],
-  \end{align}
-  where $ Y_{t,k} := \exp(i \Upsilon_{t-k-1}^{T_{k} \tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1. $
-  We claim that there exist $C_2, \delta_2>0$ such that \(\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}\) for all $k\in \mathbb Z_+$ and $t\geq k+1$.
-  Then  there exists $C_2'>0$ such that for each  $t \geq t_0$, $|\mathbb{\widetilde{P}}_{\mu}[e^{i (I^f_1(t)- I^f_0(t))}]-1| \leq C_2't^{-\delta_1}$  which, combined with the fact that $I^f_1(t) - I^f_0(t)$ is linear in $f$, completes this step.
-
- We will show the claim above  in the following substeps 2.1 and 2.2.
-  First we choose $\gamma \in (0,\beta)$ close enough to $\beta$ so that there exist $\eta,\eta'>0$ with $ \alpha \tilde \gamma > \eta > \eta - 3\eta' > \alpha \tilde \beta - \alpha \tilde \gamma > 0;$ and define for  $k \in \mathbb Z_+$ and $t\geq k+1$,
-  \[
-    \mathcal{D}_{t,k}
-    :=\{|H_t-H_{t-k-1}|\leq  e^{-\eta (t-k-1)}, H_{t-k-1}> 2e^{-\eta' (t-k-1)}\},
-  \]
-  where $H_t := e^{-\alpha t}\|X_t\|$.
-
-  \emph{Substep 2.1.} We show that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq k+1$, $ \mathbb{\widetilde{P}}_{\mu} \big[ |Y_{t,k}| ;\mathcal{D}^c_{t,k} \big] \leq C_{2.1} e^{-\delta_{2.1} (t-k)}.$
-  In fact, it follows from Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality that there exist $C_{2.1}', \delta_{2.1}'>0$ such that for all $k \geq 0$ and $t\geq k+1$,
-  \begin{align}
-    \label{eq: prob of Dtkc}
-    & \mathbb{\widetilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
-    \leq \mathbb{\widetilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta (t-k-1)})+\mathbb{\widetilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta'(t-k-1)}) \\
-    & \leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|] +  \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(H_{t-k-1}\leq 2e^{-\eta'(t-k-1)}; D^c) \\
-    & \leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma} + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P_\mu(0<H_{t-k-1}\leq 2e^{-\eta'(t-k-1)}) \\
-    & \leq C'_{2.1} e^{-(\alpha \tilde \gamma - \eta)(t-k-1)}+C'_{2.1} e^{-\delta'_{2.1}(t-k-1)}.
-  \end{align}
-  This implies the desired result in this substep, since $|Y_{t,k}| \leq 2$ a.s..
-
-  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for all $k\in \mathbb Z_+$ and $t\geq k+1$, it holds that $ \mathbb{\widetilde{P}}_{\mu} [|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}$.
-  In fact, noticing that for $f\in \mathcal C_s$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha f $; and therefore for all $k\in \mathbb Z_+$ and $t \geq k + 1$,
-  \begin{align}
-    \label{eq:gammafunction11}
-    \Upsilon_{t-k-1}^{T_{k} \tilde f}
-    = \frac{X_{t-k}(T_{k} \tilde  f) - X_{t -k-1}(P_1^\alpha T_{k} \tilde f)}{\|X_{t-k-1}\|^{1-\tilde \beta}}
-    = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f)}{\|e^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
-  \end{align}
-  Since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \in \mathbb Z_+$ and $t\geq k+1$,
-  \begin{align}
-    \label{eq: control of Ykt}
-    \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}]
-    & \leq \mathbb{\widetilde{P}}_{\mu}\Big[|\mathcal I_{t-k-1}^{t-k} X_t(f) | \cdot \Big| \| e^{\alpha(k+1)}X_{t-k-1}\| ^{ \tilde \beta - 1} - \|X_t\|^{ \tilde \beta - 1}\Big|; \mathcal D_{t,k}\Big] \\
-    & \leq  e^{\alpha(\tilde \beta - 1)t}\mathbb{\widetilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}X_t(f)|\cdot K_{t,k}\big],
-  \end{align}
-  where
-  \[
-    K_{t,k}
-    := \Big| \frac {H_t^{1- \tilde \beta} - H_{t-k-1}^{1 - \tilde \beta}} {H_t^{1 - \tilde \beta} H_{t-k-1}^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t,k}}.
-  \]
-  Note that, since $\eta' < \eta$, we have almost surely on $\mathcal D_{t,k}$,
-  \begin{align}
-    H_t
-    & \geq H_{t-k-1}- e^{-\eta (t-k-1)}
-      \geq 2e^{-\eta'(t-k-1)}-e^{-\eta(t-k-1)}
-      \geq e^{-\eta'(t-k-1)}.
-  \end{align}
-  Therefore, for all $k \in \mathbb Z_+$ and $t\geq k+1$, almost surely  on $\mathcal D_{t,k}$,
-  \begin{align}
-    & \Big|H_t^{1- \tilde \beta}-H_{t-k-1}^{1- \tilde \beta}\Big|
-      \leq (1- \tilde \beta) \max \{ H_t^{-\tilde \beta }, H_{t-k-1}^{ -\tilde \beta} \} | H_t - H_{t-k-1} | \\
-    & \leq (1- \tilde \beta ) \max\{e^{\eta' (t-k-1)}, \frac{1}{2}e^{\eta'(t-k-1)}\}^{\tilde \beta} e^{-\eta(t-k-1)}  \leq (1- \tilde \beta) e^{-(\eta - \eta') (t-k-1)}
-  \end{align}
-  and $ |H_t^{1 - \tilde \beta} H_{t-k-1}^{ 1 - \tilde \beta}| \geq 2^{\frac{1}{1+\beta}} e^{-2\eta'(t-k-1)}$.
-  Thus, there exists $C_{2.2}'> 0$ such that for all $k \geq 0, t\geq k+1$, almost surely
-  \begin{align}
-    K_{t,k}
-    \leq C_{2.2}' e^{-(\eta - 3\eta')(t-k-1)}.
-  \end{align}
-  Now, by Lemma \ref{lem: control of mgtrs}, there exists $C''_{2.2}>0$ such that for all $k\geq 0$ and $t\geq k+1$,
-  \begin{align}
-    \label{eq: Y in D}
-    & \mathbb{\widetilde{P}}_{\mu} [|Y_{t,k}| ; \mathcal{D}_{t,k} ]
-    \leq C_{2.2}' e^{\alpha (\tilde \beta - 1)t} \mathbb{\widetilde{P}}_{\mu} [ | \mathcal{I}_{t-k-1}^{t-k}X_t(f)| ] e^{-(\eta - 3\eta')(t-k-1)} \\
-    & \leq \frac{C_{2.2}' } {\mathbb{P}_{\mu}(D^c)} e^{ \alpha (\tilde \beta - 1)t} \|\mathcal{I}_{t-k-1}^{t-k} X_t(f)\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta - 3\eta')(t-k - 1)} \\
-    & \leq C_{2.2}'' e^{\alpha(\tilde \beta - \tilde \gamma)t} e^{ (\alpha \tilde \gamma - \kappa_f b)k} e^{-(\eta - 3\eta')(t-k)}
-     \leq C_{2.2}'' e^{\alpha(\tilde \beta - \tilde \gamma)(t-k)} e^{-(\eta - 3\eta')(t-k)},
-  \end{align}
-  as desired in this step.
-  In the last inequality, we used the fact that $f\in \mathcal C_s$ and therefore $\alpha \tilde \beta < \kappa_f b$.
-
-  \emph{Step 3.}
-  We show that $I^f_2(t)\xrightarrow[t\to \infty]{d} 0$.
-  First fix a $\gamma \in (0,\beta)$ in this step.
-  From the fact that $\kappa_f b -\alpha \tilde \gamma > \alpha (\tilde \beta - \tilde \gamma)$, we can choose $\epsilon >0$ small enough so that $q:=\kappa_fb- \alpha \tilde \gamma  > \alpha (\tilde \beta - \tilde \gamma) + 2\epsilon (1 - \tilde \beta)$.
-  Now writing $\mathcal{E}_t:=\{\|X_t\|>e^{(\alpha-\epsilon) t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
-  \begin{align}
-    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
-    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq e^{-\epsilon t})\leq C_3e^{-\delta_3 t}
-    , \quad t\geq0.
-  \end{align}
-  Therefore,
-  \begin{align}
-    \label{Theorem123}
-    |\mathbb{\widetilde{P}}_{\mu}[e^{i I^f_2(t)}-1;\mathcal{E}^c_t]|
-    \leq 2\mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
-    \leq 2C_3e^{-\delta_3 t},
-    \quad t\geq t_0.
-  \end{align}
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C_3',C_3'',C_3'''>0$ such that for each $t\geq t_0 >1$,
-  \begin{align}
-    & |\mathbb{\widetilde{P}}_{\mu} [ (e^{i I^f_2(t)}-1);\mathcal{E}_t]|
-      \leq  \mathbb{\widetilde{P}}_{\mu} [ |I^f_2(t)|;\mathcal{E}_t] \\
-    & \leq  ( e^{(\alpha-\epsilon) t} )^{\tilde \beta - 1}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu} [| \mathcal{I}_{t-k-1}^{t-k} X_t(f) |] + \mathbb{\widetilde{P}}_{\mu}[| \mathcal{I}_{0}^{t-\lfloor t\rfloor} X_t(f)|]\Big) \\
-    & \leq ( e^{(\alpha-\epsilon) t} )^{\tilde \beta - 1}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k} X_t(f) \|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} X_t(f)\|_{\mathbb P_\mu;1+\gamma}\Big) \\
-    & \leq C_3' e^{\alpha (\tilde \beta - \tilde \gamma)t} e ^{\epsilon (1-\tilde \beta) t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{(\alpha\tilde \gamma-\kappa_f b)k}
-      \leq C_3' e^{q t}e^{-\epsilon ( 1 - \tilde \beta)t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{-q k}
-    \\ & \leq C_3'' e^{q(t - \lceil t - \ln t\rceil)}e^{-\epsilon(1 - \tilde \beta) t}
-         \leq C_3'' t^q e^{- \epsilon(1 - \tilde \beta) t}.
-  \end{align}
-  From this and \eqref{Theorem123}, we get that $\widetilde {\mathbb P}_\mu[e^{i I^f_2(t)}] \xrightarrow[t\to \infty]{} 1$.
-  Note that $I^f_2(t)$ is linear in $f$ so we can replace $f$ with $\theta f$ for $\theta \in \mathbb R$ and get the desired result in this step.
-
-	\emph{Step 4.} We will show that $I^f_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
-  In fact, we have
-  \begin{align}
-    & |I^f_3(t)|
-      \leq \frac{X_0(|P^\alpha_tf|)}{\|X_t\|^{1 - \tilde \beta }}
-      \leq \frac{e^{\alpha t - \kappa_f b t}X_0(Qf)}{(e^{\alpha t} H_t)^{1 - \tilde \beta}}
-      = e^{(\alpha \tilde \beta - k_fb)t} H_t^{\tilde \beta - 1} X_0(Qf)
-      \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0.
-  \end{align}
-
-  \emph{Step 5.} Combining Steps 1--4, we complete the proof of Theorem  \ref{thm:M}.\eqref{thm:M:1}.
-\end{proof}
-
-\subsection{Central limit theorem for $f \in \mathcal C_c$}
-\begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:2})]
-  Fix $\mu\in \mathcal M_c(\mathbb R^d)$, $f\in \mathcal C_c$ and $t_0 > 1$ large enough so that $ \lceil t - \ln t\rceil \leq \lfloor t \rfloor - 1$ for each $t\geq t_0$.
-  For each $t\geq t_0$, in this proof we write $\theta_t = \|t X_t\|^{\tilde \beta - 1}$,  define $I_i^f(t)$ using \eqref{eq:PM:CLTS:1}  for $i = 1,2,3$, and set $ I^f_0(t) := t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f}$, where $\tilde f = e^{\alpha(\tilde \beta - 1)} f$.
-
-  \emph{Step 1.} We show that $I^f_0(t) \xrightarrow[t\to \infty]{d} \zeta^f$.
-  In fact, for each $t \geq  t_0( > 1)$ we have $t^{\tilde \beta - 1} < 1$; and therefore, for each $k \in \mathbb Z_+$, we have $t^{\tilde \beta - 1} T_{k+1} f \in \mathcal P_f:=\{\theta T_n f: n \in \mathbb Z_+, \theta \in [-1,1]\}$.
-  Therefore from Proposition \ref{cor:MI} and that $\tilde \beta - 1 = -\frac{1}{1+\beta}$ we get that there exist $C_1,\delta_1 > 0$ such that
-  \begin{align}
-    \Big|\mathbb{\widetilde{P}}_{\mu} [e^{i I^f_0(t)} ]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}\tilde f, \varphi\rangle \Big)\Big|
-    \leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}
-    \leq \frac{C_1}{t^{\delta_1}},
-    \quad t\geq t_0.
-  \end{align}
-  Since $f \in \mathcal C_c\setminus \{0\}$, we have $T_k \tilde f = \tilde f$ for each $k \in \mathbb Z_+$.
-  Similar to the argument in \eqref{eq:PM:CLTS:2} we have
-  \begin{align}
-    \label{CLT:C:eq:m}
-    \lim_{t\to \infty} \frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1 T_{k}\tilde f, \varphi\rangle
-    = \langle Z_1 \tilde f,\varphi \rangle
-    = \langle (-if)^{1+\beta}, \varphi \rangle
-    = m[f].
-  \end{align}
-  Therefore $\mathbb {\widetilde P}_\mu[e^{i I^f_0(t)}] \xrightarrow[t\to \infty]{} e^{m[f]}$.
-  The desired result in this step follows.
-
-  \emph{Step 2.} We show that $ I^f_1(t) - I^f_0 (t) \xrightarrow[t\to \infty]{d} 0$.
-  In fact, similar to Step 2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we  have \eqref{eq:PM:S:1} is valid with $ Y_{t,k} := \exp(i t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k}\tilde f} - i\theta_t \mathcal I_{t-k-1}^{t-k} X_t(f)) - 1$.
-  Similarly, we claim that there exist $C_2, \delta_2>0$ such that $\widetilde {\mathbb P}_\mu [|Y_{t,k}|] \leq C_2 e^{-\delta_2 (t-k-1)}$ for all $k\in \mathbb N$ and $t\geq k+1$, and  then the desired result in this step follows.
-
-  We will show the claim above in the following substeps 2.1 and 2.2.
-  First we choose $\gamma \in (0,\beta)$ close enough to $\beta$ so that there exist $\eta,\eta'>0$ with $ \alpha \tilde \gamma > \eta > \eta - 3\eta' > \alpha \tilde \beta - \alpha \tilde \gamma > 0$; and define, for  $k \in \mathbb N$ and $t\geq k+1$, $ \mathcal{D}_{t,k} := \{|H_t-H_{t-k-1}| \leq  e^{-\eta (t-k-1)}, H_{t-k-1}> 2e^{-\eta' (t-k-1)}\}$.
-
-  \emph{Substep 2.1.}
-  Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb N$ and $t\geq k+1$, $\mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} (t-k)}$.
-  We omit the details.
-
-  \emph{Substep 2.2.} We will show that there exist $C_{2.2},\delta_{2.2} > 0$ such that for all $k\in \mathbb N$ and $t\geq k+1$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}_{t,k}] \leq  C_{2.2} e^{-\delta_{2.2} (t-k)}.$
-  In fact, noticing that for $f\in \mathcal C_c$ and $k\in \mathbb Z_+$, we have $T_kf = e^{\alpha (\tilde \beta - 1 )k}P_k^\alpha $; and therefore for all $k\in \mathbb Z_+$ and $t \geq k + 1$,
-  \[
-    t^{\tilde \beta - 1} \Upsilon_{t-k-1}^{T_{k} \tilde f}
-    = \frac{X_{t-k}(T_{k} \tilde f) - X_{t -k-1}(P_1^\alpha T_{k} \tilde f)}{\|t X_{t-k-1}\|^{1-\tilde \beta}}
-    = \frac{\mathcal I_{t - k - 1}^{t - k} X_t(f)}{\|te^{\alpha (k+1)}X_{t-k-1} \|^{1 -\tilde \beta}}.
-  \]
-  The rest is similar to Substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:2}).
-  We omit the details.
-
-  \emph{Step 3.}
-  We show that $ I^f_2(t)\xrightarrow[t\to \infty]{d} 0$.
-  In fact, writing $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$, according to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3>0$ such that
-  \[
-    \mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
-    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|\leq t^{-1/2})\leq C_3( t^{-\delta_3}+e^{-\delta_3 t})
-    , \quad t\geq0.
-  \]
-  Therefore,
-  \begin{align}
-   \label{Theorem123a}
-    |\mathbb{\widetilde{P}}_{\mu}[e^{i I^f_2(t)}-1;\mathcal{E}^c_t]|
-    \leq 2\mathbb{\widetilde{P}}_{\mu}(\mathcal{E}^c_t)
-    \leq C_3(t^{-\delta_3}+e^{-\delta_3 t}),
-    \quad t\geq t_0.
-  \end{align}
-  Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ so that $\alpha(\tilde \beta - \tilde \gamma) \leq \frac{1}{2}(1- \tilde \beta)$.
-	According to Lemma \ref{lem: control of mgtrs}, there exist $C_3',C_3'',C_3'''>0$ such that for each $t\geq t_0 (>1)$,
-  \begin{align}
-    & |\mathbb{\widetilde{P}}_{\mu} [ (e^{i I^f_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
-      \leq  \mathbb{\widetilde{P}}_{\mu} [ |I^f_2(t)|\mathbf{1}_{\mathcal{E}_t}] \\
-    & \leq  (t^{\frac{1}{2}} e^{\alpha t} )^{\tilde \beta - 1}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\widetilde{P}}_{\mu} [| \mathcal{I}_{t-k-1}^{t-k} X_t(f) |] + \mathbb{\widetilde{P}}_{\mu}[| \mathcal{I}_{0}^{t-\lfloor t\rfloor} X_t(f)|]\Big) \\
-    & \leq C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - 1)t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k} X_t(f) \|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} X_t(f)\|_{\mathbb P_\mu;1+\gamma}\Big) \\
-    & \leq C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{(\alpha\tilde \gamma-\kappa_f b)k}
-      = C_3' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha(\tilde \beta - \tilde \gamma) t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}  e^{-\alpha (\tilde \beta -\tilde \gamma) k}
-    \\ & \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} e^{\alpha (\tilde \beta - \tilde \gamma)(t - \lceil t - \ln t\rceil)}
-         \leq C_3'' t^{\frac{1}{2}(\tilde \beta - 1)} t^{\alpha (\tilde \beta - \tilde \gamma)}.
-  \end{align}
-  From this and \eqref{Theorem123a}, we get the desired result in this step.
-
-  \emph{Step 4.} Similar to Step 4 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that $I_3(t) \xrightarrow[t\to \infty]{\widetilde {\mathbb P}_\mu \text{-} a.s.} 0$.
-  We omit the details.
-
- 	\emph{Step 5.} Combining Steps 1--4, we complete the proof of Theorem \ref{thm:M}.\eqref{thm:M:2}.
-\end{proof}
-
-\subsection{Central limit theorem for $f\in \mathcal C_l$}
-\label{sec: large rate clt}
-\begin{proof}[Proof of Theorem \ref{thm:M}.(\ref{thm:M:3})]
-  Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $f \in \mathcal C_l$.
-  Define $\mathcal N:= \{p\in \mathbb Z_+^d: \alpha \tilde \beta > |p|b\}$.
-  In this proof we write for each $t\geq 0$,
-  \begin{align}
-    & \frac{X_t(f) - \sum_{p\in \mathbb Z_+^d: \alpha \tilde \beta \geq |p|b} \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}H_\infty^p}{\|X_t\|^{1- \tilde \beta}}
-      = \sum_{p\in \mathcal N}\frac{ \langle f,\phi_p\rangle_\varphi [X_t(\phi_p) - e^{(\alpha - |p|b)t}H_\infty^p]}{\|X_t\|^{1- \tilde \beta}}
-    \\& = \sum_{p \in \mathcal N} \frac{\langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}(H_t^p - H_\infty^p)}{\|X_t\|^{1- \tilde \beta}}
-    = \sum_{k=0}^\infty \sum_{p \in \mathcal N}  \langle f,\phi_p\rangle_\varphi e^{(\alpha - |p|b)t}\frac{ H_{t+k}^p - H_{t+k+1}^p}{\|X_t\|^{1- \tilde \beta}}
-    \\ & =: \sum_{k=0}^\infty \widetilde \Upsilon_{t,k}
-         = \Big(\sum_{k = 0}^{\lfloor t^2 \rfloor}  \widetilde \Upsilon_{t,k} \Big) + \Big(\sum_{k = \lceil t^2 \rceil}^\infty  \widetilde \Upsilon_{t,k}\Big)
-         = : I^f_1(t) + I^f_2(t),
-  \end{align}
-  and $I^f_0(t):= \sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f}$ where $\tilde f := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f, \phi_p \rangle_\varphi \phi_p$.
-
-  \emph{Step 1.} We show that $I^f_0(t) \xrightarrow [t\to \infty]{d} \zeta^{-f}$.
-  In fact, since $T_k\tilde f \in \mathcal P_{\tilde f}$ for each $k\in \mathbb Z_+$, from Corollary \ref{cor:MI} we have $\widetilde{ \mathbb P}_\mu[e^{i I_0^f(t)}]\xrightarrow[t\to \infty]{}\exp\{\sum_{k=0}^\infty \langle Z_1T_k(-\tilde f),\varphi\rangle\}$.
-  Using \eqref{eq:PL:S:1} and the fact that $\varphi(x)dx$ is the invariant probability of the semigroup $(P_t)_{t\geq 0}$ we have
-  \begin{align}
-    \label{eq:PM:CLTS:2a}
-    & \sum_{k=0}^\infty \langle Z_1 T_{k} (-\tilde f), \varphi \rangle
-      = \sum_{k=0}^\infty \int_0^1 \langle P_u^\alpha ((iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle ~du
-    \\& = \sum_{k=0}^\infty \int_0^1 e^{\alpha u} \langle  (iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle ~du
-    \\& = \sum_{k=0}^\infty \int_0^1 \langle  (iT_{k+ u} f)^{1+\beta}, \varphi\rangle~du
-    = \int_0^\infty \langle  (iT_{u} f)^{1+\beta}, \varphi\rangle~du = m[-f].
-  \end{align}
-  The result in this step follows.
-
-  \emph{Step 2.} We show that $I^f_1(t) - I^f_0(t) \xrightarrow[t\to \infty]{d} 0$.
-  In fact, by \cite[Lemma 3.4.3]{Durrett2010Probability} we have, for each $t\geq 0$, that $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq \sum_{k=0}^{\lfloor t^2 \rfloor} \widetilde {\mathbb {P}}_\mu[|Y_{t,k}|]$ where $Y_{t,k} := e^{i(\widetilde {\Upsilon}_{t,k} - \Upsilon_{t+k}^{-T_{k}\widetilde {f}})} - 1.
-$
-  We claim that there exist $C_2, \delta_2>0$ such that $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|] \leq C_2e^{-\delta_2 t}$ for all $t\geq 0$ and $k \in \mathbb Z_+$.
-  Then  $|\widetilde {\mathbb P}_{\mu}[e^{i(I_{1}^{f}(t) - I_0^f(t))} - 1]| \leq (t^2+1)C_2e^{-\delta_2 t}$ which completes this step.
-
-  We will show the claim above in the following substeps 2.1 and 2.2.
-  First we choose $\gamma\in(0, \beta)$ close enough to $\beta$ so that $\alpha \tilde \gamma > |p|b$ for each $p\in \mathcal N$;
-  and even closer so that there exist $\eta,\eta'>0$ satisfying $\alpha \tilde \gamma > \eta>\eta - 3\eta'> \alpha (\tilde \beta - \tilde \gamma)>0$.
-We also define $\mathcal{D}_{t,k} :=\{|H_t-H_{t+k}|\leq  e^{-\eta t}, H_{t}> 2e^{-\eta' t}\}$.
-
-  \emph{Substep 2.1.} Similar to Substep 2.1 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we have that there exist $C_{2.1},\delta_{2.1} >0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$, $ \mathbb{\widetilde{P}}_{\mu}[|Y_{t,k}|;\mathcal{D}^c_{t,k}] \leq C_{2.1} e^{-\delta_{2.1} t}$.
-  We omit the details.
-
-  \emph{Substep 2.2.} We show that there exist $C_{2.2}, \delta_{2.2}>0$ such that for all $k \in \mathbb Z_+$ and $t\geq 0$, we have $\widetilde {\mathbb {P}}_\mu[|Y_{t,k}|; \mathcal D_{t,k}]\leq C_{2.2}e^{- \delta_{2,2} t}$.
-  In fact, it can be verified that for all $k \in \mathbb Z_+$ and $t\geq 0$,
-  \begin{align}
-    & \Upsilon_{t+k}^{-T_k\tilde f}
-      = \frac{X_{t+k}(P^\alpha_1T_k\tilde f) - X_{t+k+1}(T_k \tilde f)}{\|X_{t+k}\|^{1 - \tilde \beta}}
-    \\& = \sum_{p\in \mathcal N}
-    \langle\tilde f,\phi_p\rangle_\varphi e^{-(\alpha \tilde \beta - |pb|)k}\frac{ X_{t+k}(P_1^\alpha \phi_p) - X_{t+k+1}(\phi_p)}{\|X_{t+k}\|^{1 - \tilde \beta}}
-    \\& = \sum_{p\in \mathcal N}
-    \langle f,\phi_p\rangle_\varphi  e^{(\alpha  -|p|b)t}\frac{H_{t+k}^p-H_{t+k+1}^p }{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}}.
-  \end{align}
-  Therefore for all $k\in \mathbb Z_+$ and $t\geq 0$,
-  \begin{align}
-    &|Y_{t,k}| \mathbf 1_{\mathcal D_{t,k}}
-      \leq \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) \Big( \frac{1}{\|X_t\|^{1 - \tilde \beta}} - \frac{1}{\|e^{-\alpha k}X_{t+k}\|^{1 - \tilde \beta}} \Big)\mathbf 1_{\mathcal D_{t,k}}.
-    \\ &= \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big)e^{\alpha (\tilde \beta - 1)t} K_{t,k}
-    \\ &= \Big( \sum_{p\in \mathcal N}|\langle f,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} | H_{t+k}^p-H_{t+k+1}^p |\Big) K_{t,k},
-  \end{align}
-  where
-  \[
-    K_{t,k}
-    := \Big| \frac {H_t^{1- \tilde \beta} - H_{t+k}^{1 - \tilde \beta}} {H_t^{1 - \tilde \beta} H_{t+k}^{ 1- \tilde \beta }} \Big| \mathbf{1}_{\mathcal{D}_{t,k}}.
-  \]
-  Similar to Substep 2.2 in the proof of Theorem \ref{thm:M}.(\ref{thm:M:1}), we can verify that for all $k\in \mathbb Z_+$ and $t\geq 0$, almost surely $K_{t,k} \leq C_{2.2}'' e^{- (\eta - 3\eta')t}$.
-  From this and Lemma \ref{lem: control of wt} we know that there exists $C'''_{2.2}$ such that for all $k\in \mathbb Z_+$ and $t\geq 0$,
-  \begin{align}
-    & \widetilde{\mathbb P}_\mu[|Y_{t,k}|; \mathcal D_{t,k}]
-      \leq \mathbb P_\mu(D)^{-1}\mathbb P_\mu[ |Y_{t,k}| ;\mathcal D_{t,k} ]
-    \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} |\langle f,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} \mathbb P_\mu[| H_{t+k}^p-H_{t+k+1}^p |]
-    \\ & \leq \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal {N}} |\langle f,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} \| H_{t+k}^p-H_{t+k+1}^p \|_{\mathbb P_\mu; 1+\gamma}
-    \\&\leq  \mathbb P_{\mu}(D)^{-1} C_{2.2}'' e^{- (\eta - 3\eta') t}\sum_{p\in \mathcal N} |\langle f,\phi_p\rangle_\varphi|  e^{(\alpha \tilde \beta  -|p|b)t} e^{-(\alpha \tilde \gamma - |p|b)(t+k)} \\
-    &  \leq  C_{2.2}''' e^{- (\eta - 3\eta') t} e^{(\alpha \tilde \beta - \alpha \tilde \gamma)t},
-  \end{align}
-  as desired in this substep.
-
-  \emph{Step 3.} We show that $I^f_2(t) \xrightarrow[t\to \infty]{d} 0$.
-  In order to do this, choose an $\epsilon \in (0,\alpha)$ and a $\gamma \in (0,\beta)$ close enough to $\beta$ so that for each $p\in \mathcal N$, it holds that $\alpha \tilde \gamma > |p|b$.
-  Define $\mathcal E_t:= \{\|X_t\| > e^{(\alpha - \epsilon)t}\}$.
-  According to Proposition \ref{lem: control of XT}, there exist $C_3, \delta_3 > 0$ such that for each $t\geq 0$, $|\widetilde {\mathbb {P}}_\mu[e^{i I_2^f(t)} - 1; \mathcal E_t^c]|\leq 2\widetilde {\mathbb {P}}_\mu(\mathcal E_t^c) \leq C_3 e^{- \delta_3 t}$.
-  On the other hand, according to Lemma \ref{lem: control of wt}, we know that there exist $C_3',C_3''>0$ and $\delta_3'>0$ such that
-  \begin{align}
-    & |\widetilde {\mathbb {P}}_\mu[e^{i I_{2}^{f}(t)} - 1; \mathcal {E}_t]|
-      \leq  \widetilde {\mathbb {P}}_\mu[ | I_{2}^{f}(t)|; \mathcal {E}_t]
-      \leq \sum_{k = \lceil t^2\rceil}^\infty \widetilde {\mathbb {P}}_\mu[ |\widetilde {\Upsilon}_{t,k}|; \mathcal {E}_t]
-    \\ & \leq \mathbb P_\mu(D^c)^{-1} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} |\langle f,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t}\mathbb {P}_\mu\Big[\frac{ |H_{t+k}^p - H_{t+k+1}^p|}{\|X_t\|^{1- \tilde \beta}}; \mathcal E_t\Big]
-    \\ & \leq \mathbb P_\mu(D^c)^{-1} e^{(\alpha - \epsilon) (\tilde \beta - 1) t} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} |\langle f,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t}\|H_{t+k}^p - H_{t+k+1}^p\|_{\mathbb P_\mu; 1+\gamma}
-    \\ & \leq C_3' e^{(\alpha - \epsilon) (\tilde \beta - 1) t} \sum_{k = \lceil t^2\rceil}^\infty \sum_{p \in \mathcal N} |\langle f,\phi_p\rangle_\varphi| e^{(\alpha - |p|b)t} e^{- (\alpha \tilde \gamma - |p|b)(t+k)}
-    \\ & = C_3'' e^{ \alpha (\tilde \beta - \tilde \gamma) t } e^{ \epsilon (1 - \tilde \beta) t}e^{- \delta'_3 t^2}.
-  \end{align}
-  To sum up we have that $\widetilde {\mathbb P}_\mu[e^{iI_2^f(t)}] \xrightarrow[t\to \infty]{} 1$, which completes this step.
-
-  \emph{Step 4.} Combining Steps 1--3, we complete the proof of Theorem \ref{thm:M}.\eqref{thm:M:3}.
-\end{proof}
-
-\appendix
-\section{ }
-\subsection{Analytic facts}
-In this subsection, we collect some useful analytic facts.
-\begin{lem}
-  \label{lem: estimate of exponential remaining}
-  For $z\in \mathbb C_+$,  we have
-  \begin{align}
-    \label{eq: estimate of exponential remaining}
-    \Big|e^{-z} - \sum_{k=0}^n \frac{(-z)^k}{k!} \Big|
-    \leq \frac{|z|^{n+1}}{(n+1)!} \wedge \frac{2|z|^{n}}{n!}, \quad n\in \mathbb Z_+.
-  \end{align}
-\end{lem}
-\begin{proof}
-  Notice that $|e^{-z}| = e^{- \operatorname{Re} z} \leq 1$.
-  Therefore, $ |e^{-z} - 1| = \Big| \int_0^1 e^{-\theta z} z d\theta\Big| \leq |z|. $
-  Also, notice that $|e^{-z} - 1| \leq |e^{-z}|+1 \leq 2$.
-  Thus \eqref{eq: estimate of exponential remaining} is true when $n = 0$.
-  Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb Z_+$.
-  Then
-  \begin{align}
-    &\Big|e^{-z} - \sum_{k=0}^{m+1} \frac{(-z)^k}{k!}\Big|
-      = \Big| \int_0^1\Big(e^{-\theta z} - \sum_{k=0}^m \frac{(-\theta z)^k}{k!} \Big) z d\theta \Big| \\
-    & \quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} |z| d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} |z| d\theta\Big)
-      = \frac{|z|^{m+2}}{(m+2)!} \wedge \frac{2|z|^{m+1}}{(m+1)!},
-  \end{align}
-  which says that \eqref{eq: estimate of exponential remaining} is true for $n = m + 1$.
-\end{proof}
-
-\begin{lem}
-  \label{lem: extension lemma for branching mechanism}
-  Suppose that  $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)} (y \wedge y^2) \pi(dy)< \infty$.
-  Then the functions
-  \begin{align}
-    & h (z)
-      = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+, \\
-    & h'(z)
-      = \int_{(0,\infty)}(1- e^{-zy})y \pi(dy), \quad z \in \mathbb C_+
-  \end{align}
-  are well defined, continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
-  Moreover,
-  \[
-    \frac{h(z)-h(z_0)}{z-z_0}
-    \xrightarrow[\mathbb C_+\ni z \to z_0]{} h'(z_0),\quad z_0 \in \mathbb C_+.
-  \]
-\end{lem}
-\begin{proof}
-  It follows from Lemma \ref{lem: estimate of exponential remaining} that $h$ and $h'$ are well defined on $\mathbb C_+$.
-  According to \cite[Theorems 3.2. \& Proposition 3.6]{SchillingSongVondravcek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
-
-  It follows from Lemma \ref{lem: estimate of exponential remaining} that, for each $z_0 \in \mathbb C_+$,  there exists $C>0$ such that for $z \in \mathbb C_+$ close enough to $z_0$ and any $y>0$,
-  \begin{align}
-    & \Big| \frac{e^{-zy} - e^{-z_0 y}+(z-z_0) y}{z-z_0} \Big|
-      = \frac{1}{|z-z_0|}\Big| \int_0^1 (-y e^{-(\theta z+(1-\theta)z_0)y}+y)(z-z_0)d\theta\Big| \\
-    & \leq y\int_0^1 |1-e^{-(\theta z +(1-\theta)z_0)y}| d\theta
-      \leq (2y) \wedge\Big( y^2\int_0^1|\theta z+(1-\theta)z_0|d\theta\Big)
-      \leq C(y\wedge y^2).
-  \end{align}
-  Using this and the dominated convergence theorem, we have
-  \begin{align}
-    & \frac{h(z)-h(z_0)}{z-z_0} = \int_{(0,\infty)} \frac{e^{-zy}+zy -(e^{-z_0 y}+z_0 y)}{z-z_0}  \pi(dy) \\
-    & \xrightarrow[\mathbb C_+\ni z\to z_0]{} \int_{(0,\infty)}(1 - e^{-z_0 y} )y\pi(dy) = h'(z_0),
-  \end{align}
-  which says that $h$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
-\end{proof}
-
-For each $z\in \mathbb C\setminus (-\infty,0]$, we define $ \log z := \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined by $ z = |z|e^{i \arg z}$. 	
-For all $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$, we define $ z^\gamma := e^{\gamma \log z}. $
-Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, that $z\mapsto \log z$ is holomorphic in $\mathbb C\setminus (-\infty,0]$.
-Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic in $\mathbb C\setminus (-\infty,0]$. (We use the convention that  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
-Using the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg (z_1) + \arg(z_0)$.
-
-It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the Gamma function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
-\[
-	\Gamma(z+1)
-  = z \Gamma(z),\quad z\in \mathbb C\setminus\{0, -1,-2,\dots\}.
-\]
-Using this recursively, one gets that
-\begin{align}
-  \label{eq: definition of Gamma function}
-  \Gamma(x)
-  := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
-  \quad -n< x< -n+1, n\in \mathbb N.
-\end{align}
-
-Fix a $\beta \in (0,1)$.
-Using the uniqueness of holomorphic extension and Lemma \ref{lem: extension lemma for branching mechanism}, we get that
-\begin{align}
-  z^{\beta}
-	= \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}},
-  \quad z\in \mathbb C_+,
-\end{align}
-and similarly that
-\begin{align}
-  \label{eq: stable branching on C+}
-  z^{1+\beta}
-  = \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
-  \quad z\in \mathbb C_+.
-\end{align}
-Lemma \ref{lem: extension lemma for branching mechanism} also says that the derivative of $z^{1+\beta}$ is $(1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
-\begin{lem}
-  \label{lem: Lip of power function}
-  For all $z_0,z_1 \in \mathbb C_+$, we have
-\begin{align}
-  \label{eq: Lip of power function}
-  |z_0^{1+\beta} - z_1^{1+\beta}|
-  \leq (1+\beta)(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
-\end{align}
-\end{lem}
-\begin{proof}
-  Since $z^{1+\beta}$ is continuous on $\mathbb C_+$, we only need to prove the lemma assuming $z_0,z_1 \in \mathbb C^0_+$.
-  Notice that
-  \begin{align}
-    \label{eq: upper bound for beta power of z}
-    |z^\beta|
-    = |e^{\beta \log |z| +i\beta \operatorname {arg}z}| = e^{\beta \log |z|} = |z|^\beta,
-    \quad z \in \mathbb C\setminus (-\infty, 0].
-  \end{align}
-  Define a path $\gamma: [0,1] \to \mathbb C^0_+$ such that
-  \[
-    \gamma(\theta)
-    = z_0 (1-\theta) + \theta z_1,
-    \quad \theta \in [0,1].
-  \]
-  Then, we have
-  \begin{align}
-    |z_0^{1+\beta} - z_1^{1+\beta}|
-    & \leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
-      \leq (1+\beta)  \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0| \\
-    & \leq (1+\beta)  ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
-      \qedhere
-  \end{align}
-\end{proof}
-
-Suppose that $\varphi(\theta)$ is a continuous function from $\mathbb R$ into $\mathbb C$ such that $\varphi(0) = 1$ and $\varphi(\theta) \neq 0$ for all $\theta \in \mathbb R$.
-Then according to \cite[Lemma 7.6]{Sato2013Levy}, there is a unique continuous function $f(\theta)$ from $\mathbb R$ into $\mathbb C$ such that $f(0) = 0$ and $e^{f(\theta)} = \varphi(\theta)$.
-Such a function $f$ is called the distinguished logarithm of the function $\varphi$ and is denoted as $\operatorname{Log} \varphi(\theta)$.
-In particular, when $\varphi$ is the characteristic function of an infinitely divisible random variable $Y$,  $\operatorname{Log} \varphi(\theta)$ is called the L\'evy exponent of $Y$.
-This distinguished logarithm should not be confused with the $\log$ function defined on $\mathbb C\setminus (-\infty, 0]$.
-See the paragraph immediately after \cite[Lemma 7.6]{Sato2013Levy}.
-
-\subsection{Feynman-Kac formula with complex valued functions}
-\label{seq: complex Feynman-Kac transform}
-In this subsection we give a version of the Feynman-Kac formula with complex valued functions.
-Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact separable metric space $E$.
-We write
-\begin{align}
-  H^{(h)}_{(s,t)}
-  := \exp\Big\{\int_s^t h(u,\xi_u) du\Big\},
-  \quad 0 \leq s \leq t, h \in \mathcal B_b([0,t] \times E,\mathbb C).
-\end{align}
-
-\begin{lem}
-  \label{eq: complex FK}
-  Let $t \geq 0$. Suppose that $\rho_1, \rho_2\in \mathcal B_b([0,t] \times E, \mathbb C)$ and $f\in \mathcal B_b(E, \mathbb C)$.
-  Then
-  \begin{align}
-    \label{eq: expresion of g}
-    g(r,x)
-    := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
-  \end{align}
-  is the unique locally bounded solution to the equation
-  \[
-    g(r,x)
-    = \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
-  \]
-\end{lem}
-
-\begin{proof}
-  The proof is similar to that of \cite[Lemma A.1.5]{Dynkin1993Superprocesses}. We include it here for the sake of completeness.
-  We first verify that \eqref{eq: expresion of g} is a solution.
-  Notice that
-  \begin{align}
-    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t)| ~ds \Big]
-    \leq  \int_r^t e^{(t-r)\|\rho_1\|_\infty}e^{(t-s)\|\rho_2\|_\infty}\|\rho_2\|_\infty\|f\|_\infty ~ds
-    < \infty.
-  \end{align}
-  Also notice that
-  \begin{align}
-    \label{eq: crucial for Feynman-Kac}
-    \frac{\partial}{\partial s} H^{(\rho_2)}_{(s,t)}= -H^{(\rho_2)}_{(s,t)}\rho_2(s,\xi_s),
-    \quad s\in (0,t).
-  \end{align}
-  Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
-  \begin{align}
-    & \Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}~(\rho_2 g)(s,\xi_s)~ds \Big]
-      =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\rho_1+\rho_2)} f(\xi_t)]~ds \Big] \\
-    & = \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t) ~ds \Big]
-      = \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)}f(\xi_t)(H_{(r,t)}^{(\rho_2)} - 1)] \\
-    & = g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\rho_2)} f(\xi_t)].
-  \end{align}
-  For uniqueness, suppose  $\widetilde g$ is another solution. Put $h(r) = \sup_{x\in E}|g(r,x) - \widetilde g(r,x)|$.
-  Then
-  \[
-    h(r)
-    \leq e^{t\|\rho_1\|_\infty}\|\rho_2\|_\infty \int_r^t h(s)ds,
-    \quad r\le t.
-  \]
-  Applying Gronwall's inequality, we get that $h(r) =  0$ for $r\in [0,t]$.
-\end{proof}
-
-\subsection{Superprocesses}
-\label{sec: definition of superprocess}
-In this subsection, we will give the definition of a general superprocess.
-Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the topology of weak convergence.
-For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$,
-we use the  convention:
-$
-  F(x,f)
-  := F(x,f(x)),
-  x\in E.
-$
-A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
-\begin{itemize}
-\item
-  the spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$;
-\item
-  the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
-\begin{align}
-  \label{eq: branching mechanism}
-  \psi(x,z)=
-  -\rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
-\end{align}
-where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$;
-\item
-  $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
-  \begin{align}
-    \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
-    \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
-  \end{align}
-  where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded non-negative solution to the equation
-  \begin{align}
-    \label{eq:FKPP_in_definition}
-    V_tf(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi(\xi_s,V_{t-s}f)ds \Big]
-    = \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
-    \quad t \geq 0, x \in E.
-  \end{align}
-\end{itemize}
-We refer our readers to \cite{Li2011Measure-valued} for more discussions about the definition and the existence of superprocesses.
-To avoid triviality, we assume that $\psi(x,z)$ is not identically equal to $-\rho_1(x)z$.
-
-Notice that the branching mechanism $\psi$ can be extended into a map from $E \times \mathbb C_+$ to $\mathbb C$ using \eqref{eq: branching mechanism}.
-Define
-\begin{align}
-  \psi'(x,z)
-  := - \rho_1(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
-  \quad x\in E, z\in \mathbb C_+.
-\end{align}
-Then according to Lemma \ref{lem: extension lemma for branching mechanism}, for each $x \in E$, $z \mapsto \psi(x,z)$ is a holomorphic function on $\mathbb C_+^0$ with derivative $z \mapsto \psi'(x,z)$.
-Define $\psi_0(x,z) := \psi(x,z)+ \rho_1(x)z $ and $\psi'_0(x,z) := \psi'(x,z) + \rho_1(x)$.
-
-Denote by $\mathbb W$ the space of $\mathcal M(E)$-valued c\`{a}dl\`{a}g paths with its canonical path denoted by $(W_t)_{t\geq 0}$.
-We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
-Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued}, there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
-(i) $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
-(ii) $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
-and (iii) if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
-We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
-
-\subsection{Semigroups for superprocesses}
-\label{sec: definition of vf}
-Let $X$ be a non-persistent superprocess with its Kuznetsov measure denoted by $(\mathbb N_x)_{x\in E}$.
-We define the mean semigroup
-\begin{align}
-  P_t^{\rho_1} f(x)
-  := \Pi_{x}[e^{\int_0^t \rho_1(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
-  \quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
-\end{align}
-It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M(E)$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
-\begin{align}
-  \label{eq: mean formula for superprocesses}
-  \mathbb N_{\mu}[W_t(f)]
-  =\mathbf P_{\mu}[X_t(f)]
-  =\mu(P^{\rho_1}_t f).
-\end{align}
-
-Define
-\begin{align}
-  L_1(\xi)
-  &:= \{f\in \mathcal B(E): \forall x\in E, t\geq 0, \quad \Pi_x[|f(\xi_t)|]< \infty\}, \\
-  L_2(\xi)
-  &:= \{f \in \mathcal B(E): |f|^2 \in L_1(\xi)\}.
-\end{align}
-Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
-\begin{align}
-  \mathbb N_x[W_t(f)]
-  = \mathbf P_{\delta_x}[X_t(f)]
-  = P^{\rho_1}_t f(x) \in \mathbb R,
-  \quad f\in L_1(\xi), t > 0,x\in E.
-\end{align}
-This says that the random variable $\langle X_t, f\rangle$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
-By the branching property of the superprocess, $X_t(f)$ is an infinitely divisible random variable.
-Therefore, we can write
-\[
-  U_t(\theta f)(x)
-  := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t( f)}],
-  \quad t\geq 0, f\in L_1(\xi), \theta \in \mathbb R, x\in E,
-\]
-as its characteristic exponent.
-According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
-\[
-  \mathbf P_{\delta_x} [e^{i\theta X_t(f)}]
-  = \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]),
-  \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
-\]
-Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato2013Levy}, we have
-\begin{align}
-  \label{eq: N and characteristic exponent}
-  U_t(\theta f)(x)
-  = \mathbb N_x[e^{i W_t(\theta f)} - 1],
-  \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
-\end{align}
-
-\begin{lem}
-  There exists a constant $C\geq 0$ such that
-  for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
-  \begin{align}
-    \label{eq: upper bound of psi(v)}
-    |\psi (x,-U_tf)|
-    \leq C P^{\rho_1}_t |f|(x) + C (P^{\rho_1}_t |f| (x))^2.
-  \end{align}
-\end{lem}
-
-\begin{proof}
-  Noticing that
- $
-     e^{\operatorname{Re} U_tf(x)}
-    = |e^{U_tf(x)}|
-    = |\mathbf P_{\delta_x}[e^{i X_t(f)}]|
-    \leq 1,
-$
-  we have
-  \begin{align}
-    \label{eq: -v has positive real part}
-    \operatorname{Re} U_tf(x)
-    \leq 0.
-  \end{align}
-  Therefore, we can speak of $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
-  According to Lemma \ref{lem: estimate of exponential remaining}, we have that
-  \begin{align}
-    \label{eq: upper bound for vf}
-    |U_tf(x)|
-    \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
-    \leq \mathbb N_x[|i W_t(f)|]
-    \leq (P^{\rho_1}_t |f|)(x).
-  \end{align}
-  Notice that, for any compact $K \subset \mathbb R$,
-  \begin{align}
-    \label{eq: estimate of deriavetive of v(theta)}
-    \mathbb N_x \Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
-    \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta|
-    \leq (P^{\rho_1}_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
-  \end{align}
-  Therefore, according to \cite[Theorem A.5.2]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent}, $ U_t( \theta f)( x )$ is differentiable in $\theta \in \mathbb R$ with
-  \[
-    \frac{\partial}{\partial \theta} U_t(\theta f)(x)
-    = i\mathbb N_x[W_t(f) e^{i\theta W_t(f)}],
-    \quad \theta \in \mathbb R.
-  \]
-  Moreover, from the above, it is clear that
-  \begin{align}
-    \label{eq: upper bounded for derivative of v(theta)}
-    \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
-    \leq ( P^{\rho_1}_t |f|)(x).
-  \end{align}
-  It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_t(\theta f)(x)$ is continuous in $\theta$.
-  In other words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
-  Thus,
-  \begin{align}
-    \label{eq: path integration representation of psi(v)}
-    \psi(x,-U_tf)
-    = -\int_0^1 \psi' (x,-U_t(\theta f) ) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
-  \end{align}
-  Notice that
-  \begin{align}
-    & |\psi'(x, -U_tf)| \\
-    & = \Big| -\rho_1(x)- 2\rho_2(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big| \\
-    & = \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i W_t(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_t(f)}] \pi(x,dy) \Big| \\
-    & \leq \|\rho_1\|_\infty + 2\rho_2(x)\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy) \\
-    & \leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x) + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy) \\
-    & =: C_1 + C_2(P^{\rho_1}_t |f|)(x), \label{eq: upper bound of psi'(v)}
-  \end{align}
-where $C_1, C_2$ are constants independent of $f,x$ and $t$.
-  Now, combining the display above with \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bounded for derivative of v(theta)} we get the desired result.
-\end{proof}
-
-This lemma also says that if $f\in L^2(\xi)$, then
-$
-  \Pi_x\Big[\int_0^t \psi(\xi_s,- U_{t-s}f)ds\Big]
-  \in \mathbb C,
- x\in E, t\geq 0,$
-is well defined.
-In fact, using Jensen's inequality and the Markov property, we have
-\begin{align}
-  \label{eq: domination of psi(v)}
-  & \Pi_x\Big[\int_0^t |\psi (\xi_s,-U_{t-s}f )|ds\Big]
-  \leq \Pi_x\Big[\int_0^t (C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2 )ds\Big] \\
-  & \leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ \Pi_{\xi_s}[|f(\xi_{t-s})|] ]+C_2 e^{2t\|\rho_1\|}\Pi_x [ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 ] )~ds \\
-  & \leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\rho_1\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
-\end{align}
-
-\subsection{A complex-valued non-linear integral equation}
-Let $X$ be a non-persistent superprocess.
-In this subsection, we will prove the following:
-
-\begin{prop}
-  \label{prop: complex FKPP-equation}
-  If $f\in L_2(\xi)$,  then for all $t\geq 0$ and $x\in E$,
-\begin{align}
-  \label{eq: complex FKPP-equation}
-  U_tf(x) - \Pi_x \Big[\int_0^t \psi (\xi_s, - U_{t-s}f ) ds \Big]
-  = i \Pi_x [f(\xi_t)].
-\end{align}
-\begin{align}
-  \label{eq: complex FKPP-equation with FK-transform}
-  U_tf(x) -  \int_0^t P_{t-s}^{\rho_1} \psi_0(\cdot,-U_sf) (x)~ds
-  = iP_t^{\rho_1} f(x).
-\end{align}
-\end{prop}
-
-To prove this, we will need the generalized spine decomposition theorem from \cite{RenSongSun2017Spine}.
-Let $f\in \mathcal B_b(E,\mathbb R_+)$, $T >0$ and $x\in E$.
-Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[ W_T(f)] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
-\begin{align}
-  d\mathbf P_{\delta_x}^{ X_T(f)}
-  := \frac{X_T(f)}{P_T^{\rho_1} f(x)} d\mathbf P_{\delta_x};
-  \quad d\mathbb N_x^{W_T(f)}
-  :=  \frac{W_T(f)}{P_T^{\rho_1} f(x)} d\mathbb N_x.
-\end{align}
-Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{\langle W_T, f\rangle}$ if
-\begin{itemize}
-\item
-  the spine process $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$, where
-  \begin{align}
-    d\Pi_x^{(f,T)}
-    := \frac{f(\xi_T)e^{\int_0^T \rho_1(\xi_s)ds}}{P^{\rho_1}_T f(x)} d \Pi_x;
-  \end{align}
-\item
-  given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure
-$
-  \{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}
-$
-is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
-\begin{align}
-  \label{eq: conditional intensity}
-  \mathbf m(\xi,ds,dw)
-  := 2 \rho_2(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-\end{align}
-\item
-  $\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M(E)$-valued process defined by
-  \begin{align}
-    Y_t
-    := \int_{(0,t] \times \mathbb W} w_{t-s} \mathbf n(\xi,ds,dw),
-    \quad 0 \leq t\leq T.
-  \end{align}
-\end{itemize}
-According to the spine decomposition theorem in \cite{RenSongSun2017Spine}, we have that
-\begin{align}
-  \label{eq: Spine decomposition 1}
-  \{(X_s)_{s \geq 0};\mathbf P_{\delta_x}^{X_T(f)}\}
-  \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{W_T(f)} \},
-\end{align}
-\begin{align}
-  \label{eq: Spine decomposition 2}
-  \{(W_s)_{0\leq s\leq T};\mathbb N_x^{W_T(f)}\}
-  \overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
-\end{align}
-
-\begin{proof}[Proof of Proposition \ref{prop: complex FKPP-equation}]
-  Assume that $f\in \mathcal B_b(E)$.
-  Fix $t>0, r\in [0,t), x\in E$ and a strictly positive $g\in \mathcal B_b(E)$.
-  Denote by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
-  Conditioned on $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$ in \eqref{eq: conditional intensity}.
-  Denote by $\Pi_{r,x}$ the probability of Hunt process $\{\xi; \Pi\}$ initiated at time $r$ and position $x$.
-  From Lemma \ref{lem: estimate of exponential remaining}, we have $\mathbf Q^{(g,t)}_{x}$-almost surely
-  \begin{align}
-    & \int_{[0,t]\times \mathbb W}|e^{i w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
-      \leq \int_{[0,t]\times \mathbb W} (| w_{t-s}(f)| \wedge 2 ) \mathbf m(\xi, ds,dw) \\
-    & \leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s} ( W_{t-s}(|f|) )  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[X_{t-s}(|f|)] \pi(\xi_s,dy)
-   + 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
-    \\ & \leq \int_0^t (P_{t-s}^{\rho_1} |f|)(\xi_s)\Big(2\rho_2(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
-    \\ & \leq \Big(2\|\rho_2\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\rho_1\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
-         < \infty.
-  \end{align}
-  Using this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-almost surely,
-  \begin{align}
-    & \int_{[0,t]\times \mathbb N}(e^{i  w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
-    \\ & =\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
-    \\ & =\int_0^t \Big( 2\rho_2(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
-    \\ & = -\int_0^t \psi'_0 (\xi_s, -U_{t-s}f )ds.
-  \end{align}
-  Therefore, according to \eqref{eq: Spine decomposition 2}, Campbell's formula and above, we have that
-  \begin{align}
-    \label{eq: N to Pi}
-    & \mathbb N_x^{ W_t( g)}[e^{i W_t(f)}]
-      = \mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
-    \\ & = \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
-    = \frac{1}{P_t^{\rho_1} g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
-  \end{align}
-  Let $\epsilon >0$.
-  Define $f^+ = (f \vee 0) + \epsilon$ and $f^- = (-f) \vee 0 + \epsilon$, then $f^\pm$ are strictly positive and $f = f^+ - f^-$.
-  According to \eqref{eq: Spine decomposition 1}, we have that
-  \begin{align}
-    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm}) e^{i X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm}) ]}
-    = \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{ W_t(f^{\pm})}[e^{i X_t(f)}].
-  \end{align}
-  Using \eqref{eq: N to Pi} and the above, we have
-  \begin{align}
-    \frac{\mathbf P_{\delta_x}[X_t(f) e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
-    & = \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i X_t(f)}]
-    \\ & = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
-  \end{align}
-  Therefore, we have
-  \begin{align}
-    \frac{\partial}{\partial \theta} {U_t(\theta f)(x)}
-    = \frac{\mathbf P_{\delta_x}[i X_t(f) e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
-    = \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
-  \end{align}
-  Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have
-  \begin{align}
-    & \frac{\partial}{\partial \theta} U_{t-r}(\theta f)( x)
-      = \Pi_x[ i f(\xi_{t-r}) e^{-\int_0^{t-r} \psi'(\xi_s, -U_{t-r-s}(\theta f)) ds} ] \\
-    & = \Pi_{r,x}[i f(\xi_t)e^{-\int_0^{t-r} \psi'(\xi_{r+s}, -U_{t-r-s}(\theta f)) ds} ]
-      = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -U_{t-s}(\theta f)) ds} ].
-  \end{align}
-
-  From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
-  Therefore, we can apply Lemma \ref{eq: complex FK} and get that
-  \[
-    \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t \psi' (\xi_s,- U_{t-s}(\theta f) )\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]
-    = \Pi_{r,x} [i f(\xi_t)]
-  \]
-  and
-  \begin{align}
-    & \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du}\psi_0' (\xi_s,- U_{t-s}(\theta f) )\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
-    & = \Pi_{r,x} [i e^{\int_r^t \rho_1(\xi_s)ds}f(\xi_t)].
-  \end{align}
-  Integrating the two displays above with respect to $\theta$  on [0,1], using
-  Fubini's theorem, \eqref{eq: upper bounded for derivative of v(theta)}, \eqref{eq: path integration representation of psi(v)} and \eqref{eq: upper bound of psi'(v)}, we get
-  \begin{align}
-    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi (\xi_s,-U_{t-s}f ) ~ds\Big]
-    = i \theta \Pi_{r,x} [f(\xi_t)]
-  \end{align}
-  and
-  \begin{align}
-    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du} \psi_0 (\xi_s,- U_{t-s}f ) ~ds\Big]
-    = i \Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
-  \end{align}
-  Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} are true if $f\in \mathcal B_b(E)$.
-
-  The rest of the proof is to evaluate \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} for all $f\in L_2(\xi)$.
-We only do this for \eqref{eq: complex FKPP-equation} since the argument for \eqref{eq: complex FKPP-equation with FK-transform} is similar.
-  Let $n \in \mathbb N$.
-  Writing $f_n := (f^+ \wedge n) - (f^- \wedge n)$, then $f_n \xrightarrow[n\to \infty]{} f$ pointwise.
-  From what we have proved, we have
-  \begin{align}
-    \label{eq: complex FKPP-equation for fn}
-    U_tf_n(x) - \Pi_{x} \Big[\int_0^t \psi (\xi_s, - U_{t-s}f_n ) ~ds\Big]
-    = i \Pi_{x} [f_n(\xi_t)].
-  \end{align}
-  Note that
-  (i) $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$;
-  (ii) by \eqref{eq: N and characteristic exponent}, the dominated convergence theorem and the fact that
-  \[
-     |e^{i W_t(f_n)} - 1| \leq W_t(|f|);
-    \quad \mathbb N_x[W_t(|f|)] = (P_t^{\rho_1} |f|)(x) < \infty,
- \]
-  we have $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$, and (iii) by the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
-  \[
-    |\psi(\xi_s,- U_{t-s}f_n) |
-    \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2,
-  \]
-  we get that $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$.
-  Using these, letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
-\end{proof}
-
-\subsection*{Acknowledgment}
-We thank Zenghu Li and Rui Zhang for helpful conversations.
-We also thank the referee for very helpful comments.
-
-\begin{thebibliography}{10}
-
-\bibitem{AdamczakMilos2015CLT}
-  R. Adamczak and P. Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
-  Electron. J. Probab. \textbf{20} (2015), no. 42, 35 pp.
-
-\bibitem{Asmussen76Convergence}
-  S. Asmussen, \emph{Convergence rates for branching processes},
-  Ann. Probab.  \textbf{4} (1976), no. 1, 139--146.
-
-\bibitem{AsmussenHering1983Branching}
-  S. Asmussen and H. Hering, \emph{Branching processes},
-  Progress in Probability and Statistics, 3. Birkh\"{a}user Boston, Inc., Boston, MA, 1983.
-
-\bibitem{Athreya1969Limit}
-  K. B. Athreya,
-  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {I}. {T}he case of an eigenvector linear functional},
-  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{12} (1969), 320--332.
-
-\bibitem{Athreya1969LimitB}
-  K. B. Athreya,
-  \emph{Limit theorems for multitype continuous time {M}arkov branching processes. {II}. {T}he case of an arbitrary linear functional},
-  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{13} (1969), 204--214.
-
-\bibitem{Athreya1971Some}
-  K. B. Athreya,
-  \emph{Some refinements in the theory of supercritical multitype {M}arkov branching processes},
-  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{20} (1971), 47--57.
-
-\bibitem{Bertoin}
-J. Bertoin,
-\emph{L\'evy processes}.
-Cambridge Tracts in Mathematics, 121. Cambridge
-University Press, 1996.
-
-\bibitem{BRY}
-J. Bertoin, B. Roynette and M. Yor,
-\emph{Some connections between (sub)critical branching mechanisms and Bernstein functions}.
-arXiv:0412322.
-
-\bibitem{ChenRenWang2008An-almost}
-  Z.-Q. Chen, Y.-X. Ren, and H. Wang,
-  \emph{An almost sure scaling limit theorem for {D}awson-{W}atanabe superprocesses},
-  J. Funct. Anal. \textbf{254} (2008), no. 7, 1988--2019.
-
- \bibitem{ChenRenSongZhang2015Strong-law}
-   Z.-Q. Chen, Y.-X. Ren, R. Song, and R. Zhang,
-   \emph{Strong law of large numbers for supercritical superprocesses under second moment condition},
-   Front. Math. China \textbf{10} (2015), no. 4, 807--838.
-
- \bibitem{ChenRenYang2019Skeleton}
-   Z.-Q. Chen, Y.-X. Ren, and T. Yang,
-   \emph{Skeleton decomposition and law of large numbers for supercritical superprocesses},
-   Acta Appl. Math. \textbf{159} (2019), 225--285.
-
- \bibitem{Durrett2010Probability}
-   R. Durrett,
-   \emph{Probability: theory and examples},
-   Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
-
-\bibitem{Dynkin1993Superprocesses}
-  E. B. Dynkin,
-  \emph{Superprocesses and partial differential equations},
-  Ann. Probab. \textbf{21} (1993), no. 3, 1185--1262.
-
-\bibitem{EckhoffKyprianouWinkel2015Spines}
-  M. Eckhoff, A. E. Kyprianou, and M. Winkel,
-  \emph{Spines, skeletons and the strong law of large numbers for superdiffusions},
-  Ann. Probab. \textbf{43} (2015), no. 5, 2545--2610.
-
-\bibitem{Englander2009Law}
-  J. Engl\"{a}nder,
-  \emph{Law of large numbers for superdiffusions: the non-ergodic case},
-  Ann. Inst. Henri Poincar\'{e} Probab. Stat. \textbf{45} (2009), no. 1, 1--6.
-
-\bibitem{EnglanderWinter2006Law}
-  J. Engl\"{a}nder and A. Winter,
-  \emph{Law of large numbers for a class of superdiffusions},
-  Ann. Inst. H. Poincar\'{e} Probab. Statist. \textbf{42} (2006), no. 2, 171--185.
-
-\bibitem{EnglanderTuraev2002A-scaling}
-  J. Engl\"{a}nder and  D. Turaev,
-  \emph{A scaling limit theorem for a class of superdiffusions},
-  Ann. Probab. \textbf{30} (2002), no. 2, 683--722.
-
-\bibitem{Heyde1970A-rate}
-  C. C. Heyde,
-  \emph{A rate of convergence result for the super-critical {G}alton-{W}atson process},
-  J. Appl. Probability \textbf{7} (1970), 451--454.
-
-\bibitem{Heyde1971Some}
-  C. C. Heyde,
-    \emph{some central limit analogues for supercritical {G}alton-{W}atson processes},
-  J. Appl. Probability \textbf{8} (1971), 52--59.
-
-\bibitem{HeydeBrown1871An-invariance}
-  C. C. Heyde and B. M. Brown,
-  \emph{An invariance principle and some convergence rate results for branching processes},
-  Z. Wahrscheinlichkeitstheorie und Verw. Gebiete, \textbf{20} (1971), 271--278.
-
-\bibitem{HeydeLeslie1971Improved}
-  C. C. Heyde and J. R. Leslie,
-  \emph{Improved classical limit analogues for {G}alton-{W}atson processes with or without immigration},
-  Bull. Austral. Math. Soc. \textbf{5} (1971), 145--155.
-
-\bibitem{IksanovKoleskoMeiners2018Stable-like}
-  A. Iksanov, K. Kolesko, and M. Meiners,
-  \emph{Stable-like fluctuations of {B}gins' martingales},
-  Stochastic Process. Appl. (2018).
-
-\bibitem{Janson2004Functional}
-  S. Janson,
-  \emph{Functional limit theorems for multitype branching processes and generalized {P}\'{o}lya urns},
-  Stochastic Process. Appl. \textbf{110} (2004), no. 2, 177--245.
-
-\bibitem{KestenStigum1966Additional}
-  H. Kesten and B. P. Stigum,
-  \emph{Additional limit theorems for indecomposable multidimensional {G}alton-{W}atson processes},
-  Ann. Math. Statist. \textbf{37} (1966), 1463--1481.
-
-\bibitem{KestenStigum1966A-limit}
-  H. Kesten and B. P. Stigum,
-  \emph{A limit theorem for multidimensional {G}alton-{W}atson processes},
-  Ann. Math. Statist. \textbf{37} (1966), 1211--1223.
-
-\bibitem{KouritzinRen2014A-strong}
-  M. A. Kouritzin, and Y.-X. Ren,
-  \emph{A strong law of large numbers for super-stable processes},
-  Stochastic Process. Appl. \textbf{121} (2014), no. 1, 505--521.
-
-\bibitem{Kyprianou2014Fluctuations}
-  A. E. Kyprianou,
-  \emph{Fluctuations of {L}\'{e}vy processes with applications},
-    Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
-
-\bibitem{Li2011Measure-valued}
-  Z. Li,
-  \emph{Measure-valued branching {M}arkov processes},
-  Probability and its Applications (New York). Springer, Heidelberg, 2011.
-
-\bibitem{LiuRenSong2009Llog}
-  R.-L. Liu, Y.-X. Ren, and R. Song,
-  \emph{{$L\log L$} criterion for a class of superdiffusions},
-  J. Appl. Probab. \textbf{46} (2009), no. 2, 479--496.
-
-\bibitem{LiuRenSong2013Strong}
-  R.-L. Liu, Y.-X. Ren, and R. Song,
-  \emph{Strong law of large numbers for a class of superdiffusions},
-  Acta Appl. Math. \textbf{123} (2013), 73--97.
-
-\bibitem{MarksMilos2018CLT}
-  R. Marks and P. Mi{\l}o{\'s},
-  \emph{C{LT} for supercritical branching processes with heavy-tailed branching law},
-  arXiv:1803.05491.
-
-\bibitem{MetafunePallaraPriola2002Spectrum}
-  G. Metafune, D. Pallara, and E. Priola,
-  \emph{Spectrum of {O}rnstein-{U}hlenbeck operators in {$L^p$} spaces with respect to invariant  measures},
-  J. Funct. Anal. \textbf{196} (2002), no. 1, 40--60.
-
-\bibitem{Milos2012Spatial}
-  P. Mi{\l}o{\'s},
-  \emph{Spatial central limit theorem for supercritical superprocesses},
-  J. Theoret. Probab. \textbf{31} (2018), no. 1, 1--40.
-
-\bibitem{RenSongSun2017Spine}
-  Y.-X. Ren, R. Song, and Z. Sun,
-  \emph{Spine decompositions and limit theorems for a class of critical superprocesses},
-  Acta Appl. Math. (2019).
-
-\bibitem{RenSongSun2018Limit}
-  Y.-X. Ren, R. Song, and Z. Sun,
-  \emph{Limit theorems for a class of critical superprocesses with stable branching},
-  arXiv:1807.02837.
-
-\bibitem{RenSongZhang2014Central}
-  Y.-X. Ren, R. Song, and R. Zhang,
-  \emph{Central limit theorems for super {O}rnstein-{U}hlenbeck processes},
-  Acta Appl. Math. \textbf{130} (2014), 9--49.
-
-\bibitem{RenSongZhang2014CentralB}
-  Y.-X. Ren, R. Song, and R. Zhang,
-  \emph{Central limit theorems for supercritical branching {M}arkov processes},
-  J. Funct. Anal. \textbf{266} (2014), no. 3, 1716--1756.
-
-\bibitem{RenSongZhang2015Central}
-  Y.-X. Ren, R. Song, and R. Zhang,
-  \emph{Central limit theorems for supercritical superprocesses},
-  Stochastic Process. Appl. \textbf{125} (2015), no. 2, 428--457.
-
-\bibitem{RenSongZhang2017Central}
-  Y.-X. Ren, R. Song, and R. Zhang,
-  \emph{Central limit theorems for supercritical branching nonsymmetric {M}arkov processes},
-  Ann. Probab. \textbf{45} (2017), no. 1, 564--623.
-
-\bibitem{RenSongZhang2017Functional}
-  Y.-X. Ren, R. Song, and R. Zhang,
-  \emph{Functional central limit theorems for supercritical superprocesses},
-  Acta Appl. Math. \textbf{147} (2017), 137--175.
-
-\bibitem{Sato2013Levy}
-  K. Sato,
-  \emph{L{\'e}vy processes and infinitely divisible distributions},
-  Translated from the 1990 Japanese original. Revised by the author. Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.
-
-\bibitem{SchillingSongVondravcek2010Bernstein}
-  R. L. Schilling, R. Song, and Z. Vondra\v{c}ek,
-  \emph{Bernstein functions.}
-  Theory and applications. Second edition. De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2012.
-
-\bibitem{SteinShakarchi2003Complex}
-  E. M. Stein and R. Shakarchi, \emph{Complex analysis},
-  Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.
-
-\bibitem{Wang2010An-almost}
-  L. Wang, \emph{An almost sure limit theorem for super-{B}rownian motion},
-  J. Theoret. Probab. \textbf{23} (2010), no. 2, 401--416.
-
-\end{thebibliography}
 \end{document}

### 2020-09-25 supCLT-ind-ECP-Re.tex
add supCLT-ind-ECP-Re.tex

--- 2020-05-28 supCLT-ind-ECP.tex
@@
 \email{yxren@math.pku.edu.cn}
-\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF}
+\thanks{Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF}
 \address{
@@
 \email{rsong@illinois.edu}
-\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
+\thanks{Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
 \address{
@@
 However, we were not able to prove central limit theorems for $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
-In this note, we show that the limit stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
+	In this note, we show that the limiting stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
 \end{abstract}
 \subjclass[2010]{60J68, 60F05}
-\keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}
+\keywords{superprocesses, Ornstein-Uhlenbeck processes, stable distribution, central limit theorem, law of large numbers, branching rate regime}
 \maketitle
@@
   	Lf(x)
-  = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x)
-  , \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
+  	= \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x), 
+  	\quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
 \end{align}
@@
   	\psi(z)
-  =- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(\mathrm dy)
-  , \quad  z \in \mathbb R_+,
+  	=- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(\mathrm dy), 
+  	\quad  z \in \mathbb R_+,
 \end{align}
@@
 	$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
-Denote by $\mathcal M(\mathbb R^d)$
-($\mathcal M_c(\mathbb R^d)$)
-the space of all finite Borel measures (of compact support) on $\mathbb R^d$.
-Denote by $\mathcal B(\mathbb R^d, \mathbb R)$
-($\mathcal B(\mathbb R^d, \mathbb R_+)$)
-the space of all $\mathbb R$-valued
-($\mathbb R_+$-valued)
+	Denote by $\mathcal M(\mathbb R^d)$ ($\mathcal M_c(\mathbb R^d)$) the space of all finite Borel measures (of compact support) on $\mathbb R^d$.
+	Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ ($\mathcal B(\mathbb R^d, \mathbb R_+)$) the space of all $\mathbb R$-valued ($\mathbb R_+$-valued)
 	Borel functions on $\mathbb R^d$.
-For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$,
- write $\mu(f)= \int f(x)\mu(\mathrm dx)$
-and $\langle f, g\rangle = \int f(x)g(x) \mathrm dx$ whenever the integrals make sense.
-We say a real-valued Borel function $f$
-on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty. $
+	For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)= \int f(x)\mu(\mathrm dx)$ and $\langle f, g\rangle = \int f(x)g(x) \mathrm dx$ whenever the integrals make sense.
+	We say a real-valued Borel function $f$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty. $
 	For any $\mu \in \mathcal M(\mathbb R^d)$, we write $\|\mu\| = \mu(1)$.
@@
 
-We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
-is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a \emph{$(\xi, \psi)$-superprocess}, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a \emph{$(\xi, \psi)$-superprocess}, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
 \begin{align}
@@
   	V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) ) \mathrm ds\Big]
-	= \Pi_x [f(\xi_t)]
-  , \quad x\in \mathbb R^d, t\geq 0.
+	= \Pi_x [f(\xi_t)], 
+	\quad x\in \mathbb R^d, t\geq 0.
 \end{align}	
-	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
+	%{The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
+	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses,Li2011Measure-valued} for instance.
 
 	There have been many central limit theorem type results for branching processes, branching diffusions and superprocesses, under the second moment condition.
-	See \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes (GW processes), \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type GW processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
-	Some spatial central limit theorems for supercritical branching OU processes with binary branching mechanism were proved
-	in \cite{AdamczakMilos2015CLT}, and some
-	spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
-	These two papers made connections between central limit theorems and branching rate regimes.
-	The results of \cite{Milos2012Spatial} were extended and refined in \cite{RenSongZhang2014Central}.
-		Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
-
+	See \cite{AdamczakMilos2015CLT, AsmussenHering1983Branching, Athreya1969Limit,Athreya1969LimitB,Athreya1971Some, Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved, KestenStigum1966Additional,KestenStigum1966A-limit,Milos2012Spatial,RenSongZhang2014Central,RenSongZhang2014CentralB, RenSongZhang2015Central,RenSongZhang2017Central}.
+	For a detailed literature review, see \cite[Section 1.1]{RenSongSunZhao2019Stable}.
 	There are also  central  limit theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment.
 	For earlier papers, see \cite{Asmussen76Convergence, Heyde1971Some}. 	
-Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} established some spatial central limit theorems in the small and critical branching rate regimes, for
-some supercritical branching OU processes with a special stable offspring distribution.
-In \cite{RenSongSunZhao2019Stable}, we
-established stable central limit theorems for
-super-OU processes $X$ with branching mechanisms $\psi$ satisfying the following two assumptions.
+	Recently, Marks and Milo\'s \cite{MarksMilos2018CLT} established some spatial central limit theorems for supercritical branching OU processes with a special stable offspring distribution.
+	In \cite{RenSongSunZhao2019Stable}, we established stable central limit theorems for super-OU processes $X$ with branching mechanisms $\psi$ satisfying the following two assumptions.
 
@@
 	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
-$$D :=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}$$
+%{\[
+$
+	D 
+	:=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}
+%\]
+$ %}
 	is non-trivial with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$.
-In fact, $ \mathbb{P}_{\mu} (D) = e^{-\bar v \|\mu\|}$, where $ \bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty) $ is the largest root of $\psi$.
-Assumption \ref{asp: branching mechanism} says that $\psi$ is ``not too far away'' from $\widetilde \psi(z) := - \alpha z + \eta z^{1+\beta}$ near $0$, see \cite[Remark 1.3]{RenSongSunZhao2019Stable}.
 	It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
-In \cite[Lemma 2.3]{RenSongSunZhao2019Stable}, we have shown  that,
-under Assumption \ref{asp: branching mechanism},
- $\psi$ satisfies the $L \log L$ condition, i.e., $ \int_{(1,\infty)} y\log y \pi(\mathrm dy) < \infty. $
-In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.
-	Note that $\delta$ is not uniquely determined by $\pi$.
 
-The limit behavior of $X$  is closely related to the spectral property of the OU semigroup $(P_t)_{t\geq 0}$ which we now recall (see \cite{MetafunePallaraPriola2002Spectrum} for more details).
+	We now recall some notation and basic facts from \cite{RenSongSunZhao2019Stable}.
 	We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
-Define
-\(
-P^{\alpha}_t f(x)
-  := e^{\alpha t} P_t f(x)
-  = \Pi_x [e^{\alpha t}f(\xi_t)]
-\)
-for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
-It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$ in the sense that
-\(
-  \mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)
-\)
-for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
-It is known that the OU process $\xi$ has an invariant probability on $\mathbb R^d$
+	Define $P^{\alpha}_t f(x) := e^{\alpha t} P_t f(x) = \Pi_x [e^{\alpha t}f(\xi_t)]$ for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
+	It is known that $\mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)$ for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
+	The OU process $\xi$ has an invariant probability on $\mathbb R^d$:
 \begin{align}
   	\varphi(x)\mathrm dx
-  :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx
+  	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx.
 \end{align}
-which is a symmetric multivariate Gaussian distribution.
 	Let $L^2(\varphi)$ be the Hilbert space with inner product
@@
 	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
-The \emph{Hermite polynomials} are defined by
-\begin{align}
-  \mathcal H_p(x)
-  :=(-1)^{|p|}e^{|x|^2} \partial_p e^{-|x|^2}
-  , \quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
-\end{align}
+%{
 	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
-For $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then $ \mathcal{A}_k = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\}$ where
-\begin{align}
-  \phi_p(x)
-  := \frac{1}{\sqrt{ p! 2^{|p|} }} \mathcal H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big)
-  , \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
-\end{align}
-In other words,
-\(
-  P_t\phi_p(x)
-  = e^{-b|p|t}\phi_p(x)
-\)
-for all $t\geq 0$, $x\in \mathbb R^d$ and $p\in \mathbb Z_+^d$.
-Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
-Thus for each $f\in L^2(\varphi)$, we have
-\begin{align}
-  \label{semicomp1}
-  f
-  = \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p
-  , \quad \text{in~} L^2(\varphi).
-\end{align}
+	%For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
+	%The \emph{Hermite polynomials} are defined by
+%\begin{align}
+  	%\mathcal H_p(x)
+  	%:=(-1)^{|p|}e^{|x|^2} \partial_p e^{-|x|^2}, 
+  	%\quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
+%\end{align}
+	The eigenfunctions of $L$ consists a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$. 
+	And for each $p\in \mathbb Z_+^d$, $\phi_p$ corresponding to eigenvalue $-b|p|$ where $|p|:= \sum_{k=1}^d p_k$.
+	% It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
+	%For each $p\in \mathbb Z_+^d$,
+%\begin{align}
+  	%\phi_p(x)
+  	%:= \frac{1}{\sqrt{ p! 2^{|p|} }} \mathcal H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big), 
+  	%\quad x\in \mathbb R^d,
+%\end{align}
+	%is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$.
+	%Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
+	%Thus for each $f\in L^2(\varphi)$, we have
+%\begin{align}
+%\label{semicomp1}
+	%f
+  	%= \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p, 
+  	%\quad \text{in~} L^2(\varphi).
+%\end{align}
+%}
 	For each function $f\in L^2(\varphi)$, define the order of $f$ as
-\[
+%{
+%\[
+$
   	\kappa_f
-  := \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
-\]
-which is the lowest non-trivial frequency in the eigen-expansion \eqref{semicomp1}.
-Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
-In particular, the order of any constant non-zero function is zero.
+  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}.
+$
+%\]
+%{
+	%Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
+	%In particular, the order of any constant non-zero function is zero.
+%}
+
 	For $p\in \mathbb{Z}_+^d$, define
-\[
+%{\[
+$
   	H_t^p
-  := e^{-(\alpha-|p|b)t}X_t(\phi_p), \qquad t\geq 0.
-\]
-We will write $H^0_t$ as $H_t$.
+  	%:= e^{-(\alpha-|p|b)t}X_t(\phi_p), \qquad t\geq 0.
+  	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.
+%\]
+$
+%}
+%{	We will write $H^0_t$ as $H_t$. %}
 	For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
-We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} the following:
-\begin{equation}\label{eq:Hinfty}
-\begin{minipage}{0.9\textwidth}
-	For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
-	Futhermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
+%{
+	%We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} the following:
+	We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that
+%\begin{equation}\label{eq:Hinfty}
+%\begin{minipage}{0.9\textwidth}
+	%For any
+	for any 
+	$\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
+	Furthermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
 	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
-\end{minipage}
-\end{equation}
-We will write $H^0_\infty$ as $H_\infty$.
+%\end{minipage}
+%\end{equation}
+%}
+%{
+	%We will write $H^0_\infty$ as $H_\infty$.
+	We will write $H^0_t$ and $H^0_\infty$ as $H^0_t$ and $H_\infty$.
+%}
 
-Let us also recall some results from \cite{RenSongSunZhao2019Stable} before we formulate our main theorem.
-Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
-\begin{align}
+%{Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
+	Denote by $\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
+%\begin{align}
+$
   	\mathcal{P}
   	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
-\end{align}
-It is clear that $\mathcal{P} \subset L^2(\varphi)$.
+$
+%\end{align}
+	%It is clear that $\mathcal{P} \subset L^2(\varphi)$.
+%}
+%{	
 	Define
-\begin{equation}
-\begin{minipage}{0.9\textwidth}
-	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}, \quad \mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
-	\\ $ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
-\end{minipage}
-\end{equation}
-Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$
-are finite dimensional spaces, and $\mathcal C_c$ might be empty.
+%\begin{equation}
+%\begin{minipage}{0.9\textwidth}
+	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \}, 
+	%\quad 
+	~
+	\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
+	%\\ 
+	$ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
+%\end{minipage}
+%\end{equation}
+	Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
 	Define a semigroup
-\begin{align}
+\begin{align}\label{e:Tt}
 	T_t f
-:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p
-,\quad t\geq 0, f\in \mathcal P,
+	%{:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
+	:= \sum_{p \in \mathbb Z_+^d} \exp\{-\big| |p|b - \alpha \tilde \beta \big|t\} \langle f, \phi_p \rangle_{\varphi} \phi_p,
+	\quad t\geq 0, f\in \mathcal P,
 \end{align}
@@
 	m_t[f]
-:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx
-, \quad 0 \leq t< \infty, f\in \mathcal P.
+	:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx, 
+	\quad 0 \leq t< \infty, f\in \mathcal P.
 \end{align}
-For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write
-$\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
-We have shown in \cite[Lemma 2.6 and Propsoition 2.7]{RenSongSunZhao2019Stable} that,
+%{	For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$ %}
+	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
 \begin{equation} \label{eq:I:R:3}
 \begin{minipage}{0.9\textwidth}
-for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function
-$
-\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,
-$
-where
+	for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,$ where
 \begin{equation}
 	m[f]
-:= \begin{cases}
+	:= 
+\begin{cases}
 	\lim_{t\to \infty} m_t[f], &
@@
 \end{equation}
-Furthermore, we proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
+	%{Furthermore, we proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
+	For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$ 
+	We also proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that 
+	%}
 \begin{equation}\label{eq:oldResult}
 \begin{minipage}{0.9\textwidth}
-if $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_\mathrm c\setminus\{0
-\}$ and $f_\mathrm l \in \mathcal C_\mathrm l\setminus\{0\}$, then under $\mathbb {\widetilde P}_\mu$,
+	if $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb {\widetilde P}_\mu$,
 \[
@@
 	\quad\frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
-\xrightarrow[t\to \infty]{d}
-\zeta^{-f_\mathrm l},
+	\xrightarrow[t\to \infty]{d} \zeta^{-f_\mathrm l},
 \end{split}
 \]
-where 
-$\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
-$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$
-are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; and
+	where $\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
+	$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; and
 \[
-\mathrm x_t(f) : = \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty},\quad t\geq 0, f\in \mathcal P.
+	\mathrm x_t(f) 
+	:= \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty},
+	\quad t\geq 0, f\in \mathcal P.
 \]
@@
 	The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
-A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$; and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$,
-then $f_\mathrm c$ and $f_\mathrm l$ maybe non-zero.
-	In \cite{RenSongSunZhao2019Stable}, we were not able to
-	establish a central limit theorem in this case. We conjectured there that the limit random variables in \eqref{eq:oldResult}
-	for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
+	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$; 
+%{and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm c$ and $f_\mathrm l$ maybe non-zero.
+	and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero while $f_\mathrm c \equiv 0$.
+%}
+	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem in this case.
+We conjectured there that the limit random variables in \eqref{eq:oldResult} for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
 	Once this asymptotic independence is established, a central limit theorem  for $ X_t(f)$ for all $f\in  \mathcal P$ would follow.
 
-	The main purpose of this note is to show that
-	the limit  random variables in \eqref{eq:oldResult} are independent.
+	%{The main purpose of this note is to show that the limit  random variables in \eqref{eq:oldResult} are independent.
+	The main purpose of this note is to confirm this conjecture. %}
 
@@
 \label{thm:M}
-	If $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l \in \mathcal C_\mathrm l\setminus\{0\}$, then under $\mathbb {\widetilde P}_\mu$,
+	If $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb {\widetilde P}_\mu$,
 \begin{align} \label{eq:M.1}
 	&S(t):=
-	\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},
-	\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
+	\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}, \frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
 	\Bigg)
@@
 \end{align}
-	where 
-$\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$;
-$\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$; $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; $\widetilde H_\infty$,  $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
+	where $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$;
+	$\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$; 
+	$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; 
+	$\widetilde H_\infty$,  $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
 \end{thm}
@@
 
-\begin{cor} Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P\setminus\{0\}$.
+\begin{cor} 
+	Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P$.
 	Let  $f=f_\mathrm s + f_\mathrm c + f_\mathrm l$ be the unique decomposition of $f$ with $f_\mathrm s \in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$.
@@
 \begin{enumerate}
-\item  if $f_\mathrm c=0$, then
+\item  
+%{ if $f_\mathrm c=0$, then
+	if $f_\mathrm c\equiv 0$, then
+%}
 \[
     \frac{ X_t(f) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}
-    \xrightarrow[t\to \infty]{d}
-       \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l},
+    \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l},
 \]
 	where $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are independent;
-\item if $f_\mathrm c\neq0$, then
+\item 
+%{	if $f_\mathrm c\neq0$, then
+if $f_\mathrm c\not\equiv 0$, then%}
 \[
@@
 \]
-	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}.
+	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variable described in \eqref{eq:I:R:3}.
 \end{enumerate}
-Here $\mathrm x_t(f)$ is defined in \eqref{eq:oldResult}.
 \end{cor}
@@
 \label{proofs of main results}
-
 	We first make some preparations before proving Theorem \ref{thm:M}.
@@
   	Z_t f
-  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,\quad
-  	\Upsilon^f_t
+  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
+  	\quad \Upsilon^f_t
    	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
@@
 	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of the limit of $\Upsilon^f_t$.
-For $g\in \mathcal P$, define $\mathcal P_g:= \{\theta T_ng:n \in \mathbb Z_+, \theta \in [-1,1]\}$.
-The following generalization of
-\cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of  Theorem \ref{thm: II}, a special case of Theorem \ref{thm:M}.
+	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
+	The following Lemma \ref{lem:P:R} can be proved using a similar argument used in the proof of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
+\begin{lem}
+\label{lem:P:R}
+	%{Suppose that $g = g_\mathrm s + g_\mathrm c + g_\mathrm l$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$.
+	%Then there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
+	For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
+\end{lem}
 
+	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable} 
+	%{with using Lemma \ref{lem:P:R} instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
+	with using Lemma \ref{lem:P:R} above instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
+	Let $(\mathscr F_t)_{t\geq 0}$ be the natural filtration of $X$.
+	%}
 \begin{prop}
-  \label{cor:MI}
-For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for
-all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1+1$, we have
+\label{thm:Key}
+	For each $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
+\[
+	\mathbb P_\mu
+	\Big[ \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  \big|\Big]
+	\leq C e^{- \delta t}.
+\]
+\end{prop}
+
+	The following generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of  Theorem \ref{thm: II}, a special case of Theorem \ref{thm:M}.
+	Note that the constants $C$ and $\delta$ in the next result depend only on $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, do not depend on $n_1, n_2, f_j, g_j$ and $t$ (as long as $t\geq n_1+1$).
+
+\begin{prop} \label{cor:MI}
+	For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1+1$, we have
 \begin{equation}
 \label{32corollary}
-  \Big|\mathbb{\widetilde{P}}_{\mu}\Big[  \Big(\prod_{k=0}^{n_1}e^{i \Upsilon^{f_k}_{t-k-1}}\Big)  \Big( \prod_{k=0}^{n_2}e^{i \Upsilon^{g_k}_{t+k} } \Big) \Big]  -  \Big(\prod_{k=0}^{n_1} e^{\langle Z_1f_k, \varphi\rangle}\Big) \Big(\prod_{k=0}^{n_2} e^{\langle Z_1g_k, \varphi\rangle}\Big) \Big|\leq C e^{-\delta (t-n_1)}.
+	\Big|\mathbb{\widetilde{P}}_{\mu}\Big[  \Big(\prod_{k=0}^{n_1}e^{i \Upsilon^{f_k}_{t-k-1}}\Big)  \Big( \prod_{k=0}^{n_2}e^{i \Upsilon^{g_k}_{t+k} } \Big) \Big]  -  \Big(\prod_{k=0}^{n_1} e^{\langle Z_1f_k, \varphi\rangle}\Big) \Big(\prod_{k=0}^{n_2} e^{\langle Z_1g_k, \varphi\rangle}\Big) \Big|
+	\leq C e^{-\delta (t-n_1)}.
 \end{equation}
@@
 \begin{proof}
-	In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \mathcal P_f$, $(g_j)_{j=0}^{n_2}\subset \mathcal P_g$ and $t\geq n_1 + 1$.
+	In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1 + 1$.
  	For any $k_1 \in \{-1,0,\dots,n_1\}$ and $k_2 \in \{-1,0,\dots,n_2\}$,  define
@@
 \]
-where we used the convention that
-$\prod_{j=0}^{-1} =1.$
+	where we used the convention that $\prod_{j=0}^{-1} =1.$
+%{Let $(\mathscr F_t)_{t\ge 0}$ be the natural filtration of $X$. %}
   	Then for all  $k_2 \in \{0,\dots,n_2\}$, we have
-\begin{align}
-&a_{-1,k_2} - a_{-1,k_2-1}
-\\& \begin{multlined}
-	=\mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
-	\\- \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=0}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2 - 1}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=k_2}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
-\end{multlined}
-	\\& \begin{multlined}
-	= \frac{1}{\mathbb{P}_{\mu}(D^c)} \Big(\prod_{j=k_2+1}^{ n_2} e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
-	\\ \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big) \Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) (e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle});D^c\Big]
-	\end{multlined}
-	\\ \label{eq:MI.1}& \begin{multlined}
+\begin{equation}
+\label{eq:MI.1} 
+\begin{multlined}
+	 a_{-1,k_2} - a_{-1,k_2-1} 
 	 = \frac{1}{\mathbb{P}_{\mu}(D^c)}  \Big(\prod_{j=k_2+1}^{n_2}e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
@@
 \end{multlined}
-\end{align}
-	Therefore, there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$,
-  such that  for each $k_2 \in \{0, \dots, n_2 \}$,
+\end{equation}
+	By Proposition \ref{thm:Key}, there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$, such that  for each $k_2 \in \{0, \dots, n_2 \}$,
 \begin{align}
@@
     \overset{\eqref{eq:MI.1}}\leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}]\big|\Big]
-    \\&\label{eq:MI.15}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_0 e^{-\delta_0 (t+k_2)}.
+    \\&\label{eq:MI.15} \leq C_0 e^{-\delta_0 (t+k_2)}.
 \end{align}
-	Notice that, for any $k_1 \in \{0, \dots , n_1\}$,
-	\begin{align}
-	&a_{k_1-1,-1} - a_{k_1,-1}
-	\\ & \begin{multlined}
-	=  \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) - {}
-	\\ \mathbb{\widetilde{P}}_{\mu}\Big[ \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
-	\end{multlined}
-	\\& =  \mathbb{\widetilde{P}}_{\mu}\Big[ \big(e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle} \big) \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big)
-	\\& \label{eq:MI.2}\begin{multlined}
+	Similarly, for any $k_1 \in \{0, \dots , n_1\}$,
+\begin{equation}
+\label{eq:MI.2}
+\begin{multlined}
+	a_{k_1-1,-1} - a_{k_1,-1}
 	=  \frac{1}{\mathbb P_\mu(D^c)} \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) \times {}
@@
 \end{multlined}
-	\end{align}
-	Therefore,  there exist $C_1,\delta_1 >0$, depending only on $\mu$ and $f$,
-	such that for any $k_1 \in \{0,\dots,n_1\}$,
+\end{equation}
+	By Proposition \ref{thm:Key}, there exist $C_1,\delta_1 >0$, depending only on $\mu$ and $f$, such that for any $k_1 \in \{0,\dots,n_1\}$,
 \begin{align}
@@
     \overset{\eqref{eq:MI.2}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{f_{k_1}}_{t-k_1-1}}-e^{\langle Z_1f_{k_1}, \varphi\rangle}; D^c|\mathscr F_{t-k_1-1}]\big|\Big]
-    \\&\label{eq:MI.25}\overset{\text{\cite[Proposition 3.5]{RenSongSunZhao2019Stable}}}\leq C_1 e^{-\delta_1 (t-k_1)}.
+    \\&\label{eq:MI.25} \leq C_1 e^{-\delta_1 (t-k_1)}.
 \end{align}
@@
     = \left|a_{-1,n_2}-a_{n_1,-1}\right|
-      \leq \sum_{k=0}^{n_1}\left|a_{k-1,-1}-a_{k,-1}\right|+\sum_{k=0}^{n_2}\left|a_{-1,k}-a_{-1,k-1}\right|\\
-     & \overset{\eqref{eq:MI.15},\eqref{eq:MI.25}}\leq \sum_{k=0}^{n_1} C_1 e^{-\delta_1 (t-k)}+\sum_{k=0}^{n_2} C_0 e^{-\delta_0 (t+k)}
+    \leq \sum_{k=0}^{n_1}\left|a_{k-1,-1}-a_{k,-1}\right|+\sum_{k=0}^{n_2}\left|a_{-1,k}-a_{-1,k-1}\right|
+    \\& \overset{\eqref{eq:MI.15},\eqref{eq:MI.25}}\leq \sum_{k=0}^{n_1} C_1 e^{-\delta_1 (t-k)}+\sum_{k=0}^{n_2} C_0 e^{-\delta_0 (t+k)}
   	\leq C e^{- \delta (t-n_1)}.
@@
 
-The following elementary result will also be used in the proof of Theorem \ref{thm: II}.
-\begin{lem}\label{ineq: analysis}
+	%{The following elementary result will also be used in the proof of Theorem \ref{thm: II}.
+	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
+	%}
+\begin{lem}
+\label{ineq: analysis}
 	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
 \[
-    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
+    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
+    \leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
 \]
 \end{lem}
+\begin{comment}
 \begin{proof}
@@
 \[
-  \lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
+  	\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}
+  	=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}
+  	=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
 \]
@@
 \[
-  |(1+y)^{1+\beta}-y^{1+\beta}-1|\leq C_1 |y|^{\beta}.
+  	|(1+y)^{1+\beta}-y^{1+\beta}-1|
+  	\leq C_1 |y|^{\beta}.
 \]
  	Note that if $x = 0$ or $y= 0$, then the desired result is trivial.
-So we only need to consider
- the case that $x \neq 0$ and $y \neq 0$.
+	So we only need to consider the case that $x \neq 0$ and $y \neq 0$.
  	In this case, if $|x|\geq |y|$, we have
 \[
-|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)\leq C_1|y||x|^{\beta};
+	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
+	\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)
+	\leq C_1|y||x|^{\beta};
 \]
@@
 	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
-	\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)\leq C_1|x||y|^{\beta}.
+	\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)
+	\leq C_1|x||y|^{\beta}.
 \]
@@
 \end{proof}
+\end{comment}
 
-In the remainder of this section,
-we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$,  $f_\mathrm c\in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l\in \mathcal C_\mathrm l\setminus\{0\}$.
-For any random variable $Y$ with finite mean under $\mathbb P_\mu$, we define
-\begin{align}
-\mathcal I_r^t Y := \mathbb P_\mu[Y|\mathscr F_{t\vee 0}] - \mathbb P_\mu[Y|\mathscr F_{r\vee 0}], \quad -\infty < r, t <\infty.
-\end{align}
-	For each $t\geq 1$,
-	we have the following decomposition.
-  \begin{align}
-     I^{f_\mathrm s}(t) &:= \frac{X_t(f_\mathrm s)}{\|X_t\|^{1- \tilde \beta }}  = I^{f_\mathrm s}_1(t) + I^{f_\mathrm s}_2(t) + I^{f_\mathrm s}_3(t)
-        \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}  \Big)
-    + \Big( \frac{X_0(P_t^\alpha f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}}\Big),
-       \\ I^{f_\mathrm c}(t)&:=\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}} = I^{f_\mathrm c}_1(t) + I^{f_\mathrm c}_2(t) + I^{f_\mathrm c}_3(t)
-    \\&:=  \Big(\sum_{k\in \mathbb N \cap [0,t-\ln t]}  \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta} } \Big) + \Big(\sum_{k\in\mathbb{N}\cap(t-\ln t, t]} \frac{\mathcal I_{t-k-1}^{t-k} X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}  \Big)    + \Big( \frac{X_0(P_t^\alpha f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}\Big),
-   \\ I^{f_\mathrm l}(t) &:= \frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}
-  = I^{f_\mathrm l}_1(t) + I^{f_\mathrm l}_2(t) + I^{f_\mathrm l}_3(t)
-  \\& := \Big(\sum_{k\in \mathbb N \cap [0,t^2]} \frac{ \mathcal I_{t+k+1}^{t+k}\mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}\Big) + \Big(\sum_{k\in \mathbb N \cap (t^2,\infty)}  \frac{ \mathcal I_{t+k+1}^{t+k}\mathrm x_t(f_\mathrm l)}{\|X_t\|^{1- \tilde \beta}}\Big)+0,
-  \end{align}
- where $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
+	In the remainder of this section, we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$,  $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$.
 	For every $t\geq 1$, define
 \begin{align}
-	R_j(t)&:=\big(I_j^{f_\mathrm s}(t),I_j^{f_\mathrm c}(t),I_j^{f_\mathrm l}(t)\big), \quad j = 1,2,3,
-	\\ R(t)&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
-    \\R_0(t)&=\big(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t)\big)
-       \\&:=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
+	R(t)
+	&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
+    %{ \\R_0(t)
+    %&=\big(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t)\big)
+    \\R'(t)
+    &=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
+    %}
+    \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
 \end{align}
-where 
- $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
-$\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and  $\tilde f_\mathrm l := \sum_{p\in \mathcal N} e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
+%{
+	%where $T_k$ is the operator defined in \eqref{e:Tt} and $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
+	where $T_k$ is the operator defined in \eqref{e:Tt}, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
+%}
 	The following result is a special case of Theorem \ref{thm:M}.
-
 \begin{thm}\label{thm: II}
-Under $\mathbb{\widetilde{P}}_{\mu}$,
-$
-R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
-$
-where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are
-the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
+	Under $\mathbb{\widetilde{P}}_{\mu}$, $R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
 \end{thm}
@@
 	In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
-Note that for each $t\geq 1$,
+	According to the proof of Theorem 1.6 in \cite{RenSongSunZhao2019Stable}, and the fact that the convergence in probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
 \[
-R(t)=R_0(t)+\big(R_1(t)-R_0(t)\big)+R_2(t)+R_3(t).
+	%{R(t)-R_0(t) 
+	R(t)-R'(t)
+	%} 
+	\xrightarrow[t\to \infty]{\text{in probability}} 0.
 \]
-Note that
-$$
-(R_1(t)-R_0(t))=(I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t), I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t), I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)).
-$$
-In the proof of Theorem 1.6(1) in \cite{RenSongSunZhao2019Stable}, we proved that
-$I_1^{f_\mathrm s}(t)-I_0^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm s}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
- In the proof of Theorem 1.6(2) in \cite{RenSongSunZhao2019Stable}, we proved that
- $I_1^{f_\mathrm c}(t)-I_0^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$, $I_2^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{d} 0$ and $I_3^{f_\mathrm c}(t)\xrightarrow[t\to \infty]{\mathbb{\widetilde{P}}_{\mu}-a.s.} 0.$
-In the proof of Theorem 1.6(3) in \cite{RenSongSunZhao2019Stable}, we proved that
-$I_1^{f_\mathrm l}(t)-I_0^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$ and  $I_2^{f_\mathrm l}(t)\xrightarrow[t\to \infty]{d} 0$.
-Thus we have 
-$R_1(t)-R_0(t)\xrightarrow[t\to \infty]{d} (0,0,0)$, $R_2(t)\xrightarrow[t\to \infty]{d}(0,0,0)$ and
-$R_3(t)\xrightarrow[t\to \infty]{d}(0,0,0)$.
-Combining the above results and using Slutsky's theorem, we only need to  show that, under $\mathbb{\widetilde{P}}_{\mu}$,
-\begin{equation}
-\label{lem:UOT}R_0(t) \xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
+	With the help of Slutsky's theorem, what is left to show is that,
+\begin{equation} \label{lem:UOT}
+	%{R_0(t)
+	R'(t)%}
+	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
 \end{equation}
@@
 \[
-\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
-\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
+	%{\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
+	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R_j(t)\Big)\Big] %}
 	= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
 \]
-Using Proposition \ref{cor:MI} 
-with $f=\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c}$ and $g = -\tilde{f}_{\mathrm l}$, we get that there exist $C_1,\delta_1 > 0$ such that
-for every $t\geq 1$,
+	Note that $\{T_k(\tilde f_\mathrm s + t^{\tilde\beta - 1}\tilde f_{\mathrm c}):k\in \mathbb Z_+, t\geq 1\}\subset \overline{\mathcal P}_{\tilde f_\mathrm s + \tilde f_{\mathrm c}}$ and $\{-T_k\tilde{f}_{\mathrm l}: k\in \mathbb Z_+\}\subset \overline{\mathcal P}_{\tilde f_\mathrm l}$.
+	Therefore, we can use Proposition \ref{cor:MI} with $f$ taking as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taking as $\tilde{f}_{\mathrm l}$, and get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
 \begin{align}
-    &\Big|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
-    -\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\Big|\\
-    &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
+    %{&\Big|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big] -\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\Big|
+    &\begin{multlined} 
+  	\bigg|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}R'_j(t)\Big)\Big] - {}
+  	\\ \exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \big\langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})\big), \varphi \big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\bigg|
+  	\end{multlined}
+  	%}
+    \\ &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
 \end{align}
 	We claim that
-\begin{align} \label{eq:UOT.1}
-&\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c)), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big)\\
-& =\exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
+\begin{align} 
+\label{eq:UOT.1}
+	&\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}\big \langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c)\big), \varphi\big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big)
+	\\& =\exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
 \end{align}
@@
 \[
-	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i
-	\sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
-	 \xrightarrow[t\to \infty]{}
-	 \exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
+	%{\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
+	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_{j}(t)\Big)\Big] %}
+	\xrightarrow[t\to \infty]{} \exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
 \]
- Since $I_0^{f_j}(t)$ are linear in 
-     $f_j\in \mathcal C_j (j=\mathrm s,\mathrm c,\mathrm l)$,
- replacing $f_j$ with $\theta_j f_j$, we immediately get 
- \eqref{lem:UOT}.
+	%{Since $I_0^{f_j}(t)$ are linear
+	Since $R'_{j}(t)$ are linear %}
+	 in $f_j \in \mathcal C_j~(j=\mathrm s,\mathrm c,\mathrm l)$, replacing $f_j$ with $\theta_j f_j$, we immediately get \eqref{lem:UOT}.
 
@@
   	& \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
-  = \sum_{k=0}^n \int_0^1 \langle P_u^\alpha (\eta(-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}), \varphi\rangle \mathrm du
+  	= \sum_{k=0}^n \int_0^1 \big\langle P_u^\alpha \big(\eta(-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}\big), \varphi\big\rangle \mathrm du
  	\\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle \eta (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle \mathrm du
- \\& = \sum_{k=0}^n \int_0^1 \langle \eta (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle \mathrm du
- = \int_0^{n+1} \langle  \eta (-iT_{u} f)^{1+\beta}, \varphi\rangle \mathrm du = m_{n+1}[f],
+ 	= \sum_{k=0}^n \int_0^1 \langle \eta (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle \mathrm du
+ 	\\&= \int_0^{n+1} \langle  \eta (-iT_{u} f)^{1+\beta}, \varphi\rangle \mathrm du 
+ 	= m_{n+1}[f],
 \end{align}
@@
 	\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c), \varphi\rangle
-=\eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du.
+	= \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du.
 \end{equation}
@@
 	Also note that according to
- Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, there exist $\delta> 0$ and
-$h\in \mathcal P$ (depending only on $f_\mathrm s$)
-such that for each $u\geq 0$,
- $|T_u f_\mathrm s|\leq e^{-\delta u}h$.
+ 	Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, there exist $\delta> 0$ and $h\in \mathcal P$ (depending only on $f_\mathrm s$) such that for each $u\geq 0$, $|T_u f_\mathrm s|\leq e^{-\delta u}h$.
 	It follows from Lemma \ref{ineq: analysis} that there exists $C>0$ such that for all $u\geq 0$ and $t\geq 0$,
@@
 	&\Big|\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)-m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm s]-\frac{1}{t}m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm c]\Big|
-\\& \begin{multlined}
+	\\& 
+\begin{multlined}
 	\overset{\eqref{eq:UOT.15},\eqref{eq:M.13}}\leq\Big| \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du - {}
@@
 	Combining this with \eqref{eq:I:R:3}, we get that
-\begin{equation} \label{eq:UOT.4}
+\begin{equation} 
+\label{eq:UOT.4}
 	\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)  = \exp( m[f_\mathrm s]+m[f_\mathrm c]).
@@
 	Also note that according to the Step 1 in the Proof of Theorem 1.6.(3) in \cite{RenSongSunZhao2019Stable}, we have
-\begin{equation}\label{eq:UOT.5}
+\begin{equation}
+\label{eq:UOT.5}
 	\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big) =\exp(m[-f_\mathrm l]).
@@
 \begin{proof}[Proof of Theorem \ref{thm:M}]
- We first recall some facts about weak convergence which will be used later. For $f:\mathbb R^d\mapsto \mathbb R$, let
- $$
- \|f\|_L:=\sup_{x\neq y}\frac{|f(x)-f(y)|}{|x-y|}
- $$
- and $\|f\|_{BL}:= \|f\|_{\infty}+\|f\|_L. $
+ 	We first recall some facts about weak convergence which will be used later.
+	For any bounded Lipschitz function $f:\mathbb R^d\mapsto \mathbb R$, let
+\[
+	\|f\|_L
+	:=\sup_{x\neq y}\frac{|f(x)-f(y)|}{|x-y|}
+\]
+	and $\|f\|_{BL}:= \|f\|_{\infty}+\|f\|_L.$
 	For any probability distributions $\mu_1$ and $\mu_2$ on $\mathbb R^d$, define
@@
 	Then $d$ is a metric. It follows from \cite[Theorem 11.3.3]{Dudley2002} that the topology generated by $d$ is equivalent to the weak convergence topology.
-Using the definition, we can easily see that, if $\mu_1$ and $\mu_2$ are the distributions of two $\mathbb R^d $-valued random variables $X$ and $Y$ respectively,
-defined on same probability space then
-\begin{align}\label{ineq: distribution control}
-  d(\mu_1,\mu_2) \leq \mathbb E|X-Y|.
+	Using the definition, we can easily see that, if $\mu_1$ and $\mu_2$ are the distributions of two $\mathbb R^d $-valued random variables $X$ and $Y$ respectively, defined on same probability space, then
+\begin{align}
+\label{ineq: distribution control}
+  	d(\mu_1,\mu_2) 
+  	\leq \mathbb E|X-Y|.
 \end{align}
-In this proof, let us fix $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s\setminus\{0\}$, $f_\mathrm c \in \mathcal C_\mathrm c\setminus\{0\}$ and $f_\mathrm l \in \mathcal C_\mathrm l\setminus\{0\}$.
+	In this proof, let us fix $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$.
 	Recall that $S(t)~(t\geq 0)$ is given by \eqref{eq:M.1}.
@@
 \begin{align}
- S(t,r):=\Big(e^{-\alpha t}\|X_t\|,& \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm c)}{\|(t+r)X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm l)-\mathrm x_{t+r}(f_\mathrm l) }{\|X_{t+r}\|^{1-\tilde{\beta}}}\Big),
+	S(t,r)
+	:=\Big(e^{-\alpha t}\|X_t\|,& \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm c)}{\|(t+r)X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm l)-\mathrm x_{t+r}(f_\mathrm l) }{\|X_{t+r}\|^{1-\tilde{\beta}}}\Big),
 \end{align}
@@
 \begin{align}
-\widetilde{S}(t,r)= \Big(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0\Big),
+	\widetilde{S}(t,r)
+	= (e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0),
 \end{align}
@@
 	We claim that
-\begin{equation}\label{eq:M.3}
+\begin{equation}
+\label{eq:M.3}
 \begin{minipage}{0.9\textwidth}
@@
 \[
-	S(t,r)\xrightarrow[r\rightarrow \infty]{d} (\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
+	S(t,r)
+	\xrightarrow[r\rightarrow \infty]{d} (\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
 \]
-	where $\widetilde H_t$ has the distribution of $\{e^{-\alpha t} \|X_t\|; \widetilde {\mathbb P}_\mu\}$,
-	$\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, 
-	and $\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
+	where $\widetilde H_t$ has the distribution of $\{e^{-\alpha t} \|X_t\|; \widetilde {\mathbb P}_\mu\}$, $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, 	and $\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
 \end{minipage}
@@
 	let $\widetilde{\mathcal D}(t)$ and $\mathcal D$ be the distributions of $(\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$ and $(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, respectively.
- Then for each $\gamma\in (0,\beta)$, there exist constant $C>0$
- such that for every $t > 0$,
+	Then for each $\gamma\in (0,\beta)$, there exist constant $C>0$ such that for every $t > 0$,
 \begin{align}
@@
 \[
-\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l\in \mathbb R \mapsto k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
+	\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l \in \mathbb R 
+	\mapsto k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
 \]
@@
 	\\&:=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + i\theta_\mathrm c \frac{X_{t+r}(f_\mathrm c)}{\|(t+r)X_{t+r}\|^{1-\tilde{\beta}}} + i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l)- \mathbb P_\mu[\mathrm x_{t+r}(f_\mathrm l)|\mathscr F_u]}{\|X_{t+r}\|^{1-\tilde{\beta}}}
-\\&\label{eq:M.6}\begin{multlined}
-\overset{\eqref{eq:Hinfty}}=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + \frac{i\theta_\mathrm c}{(t+r)^{1-\tilde{\beta}}} \frac{X_{t+r}(f_\mathrm c)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + {}
+	\\&\label{eq:M.6}
+\begin{multlined}
+	%{\overset{\eqref{eq:Hinfty}}%}
+	=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + \frac{i\theta_\mathrm c}{(t+r)^{1-\tilde{\beta}}} \frac{X_{t+r}(f_\mathrm c)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + {}
 	\\\quad  i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l) - \sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b} e^{(\alpha - |p|b)(t+r)} e^{-(\alpha - |p|b)u}X_u(\phi_p) }{\|X_{t+r}\|^{1-\tilde{\beta}}}.
@@
 	\\&\overset{\eqref{eq:M.5}}=\lim_{r\to \infty}\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\big[\exp\{i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0} \mathbb P_{\mu}[\exp\{A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\}\mathbf 1_{D^c}|\mathscr F_t]\big]
-\\&\begin{multlined}
+	\\&
+\begin{multlined}
 	\overset{\text{\eqref{eq:M.6}, Markov property}}=\lim_{r\to \infty}\lim_{u\rightarrow\infty}\frac{1}{\mathbb P_{\mu}(D^c)} \mathbb P_{\mu}\Bigg[\exp\{ i\theta e^{-\alpha t}\|X_t\|\}\mathbf 1_{\|X_t\|>0} \times {}
@@
 \bibitem{AdamczakMilos2015CLT}
-  R. Adamczak and P. Mi{\l}o\'{s}, \emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
+	R. Adamczak and P. Mi{\l}o\'{s}, 
+	\emph{C{LT} for {O}rnstein-{U}hlenbeck branching particle system},
 	Electron. J. Probab. \textbf{20} (2015), no. 42, 35 pp.
@@
 \bibitem{Asmussen76Convergence}
-  S. Asmussen, \emph{Convergence rates for branching processes},
+	S. Asmussen, 
+	\emph{Convergence rates for branching processes},
 	Ann. Probab.  \textbf{4} (1976), no. 1, 139--146.
@@
 \bibitem{AsmussenHering1983Branching}
-  S. Asmussen and H. Hering, \emph{Branching processes},
+	S. Asmussen and H. Hering, 
+	\emph{Branching processes},
 	Progress in Probability and Statistics, 3. Birkh\"{a}user Boston, Inc., Boston, MA, 1983.
@@
   	Cambridge University Press, 2002.
+
+%{\bibitem{Durrett2010Probability}
+ 	%R. Durrett,
+ 	%\emph{Probability: theory and examples},
+ 	%Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
+%}
 
@@
 
-\bibitem{MetafunePallaraPriola2002Spectrum}
-  G. Metafune, D. Pallara, and E. Priola,
-  \emph{Spectrum of {O}rnstein-{U}hlenbeck operators in {$L^p$} spaces with respect to invariant  measures},
-  J. Funct. Anal. \textbf{196} (2002), no. 1, 40--60.
-
 \bibitem{Milos2012Spatial}

### 2020-09-25 supCLT-ind-JAP.tex
Update supCLT-ind-ECP-Re

--- 2020-09-25 supCLT-ind-ECP-Re.tex
@@
 \end{align}	
-	%{The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
 	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses,Li2011Measure-valued} for instance.
@@
 	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
-%{\[
 $
 	D
-	:=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}
-%\]
-$ %}
+	:=\{\exists t\geq 0~\text{such that}~ \|X_t\| =0 \}
+$ 
 	is non-trivial with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$.
@@
 	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
-%{
 	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
-	%For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
-	%The \emph{Hermite polynomials} are defined by
-%\begin{align}
-  	%\mathcal H_p(x)
-  	%:=(-1)^{|p|}e^{|x|^2} \partial_p e^{-|x|^2}, 
-  	%\quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
-%\end{align}
 		The eigenfunctions of $L$ consists a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
-	And for each $p\in \mathbb Z_+^d$, $\phi_p$ corresponding to eigenvalue $-b|p|$ where $|p|:= \sum_{k=1}^d p_k$.
-	% It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
-	%For each $p\in \mathbb Z_+^d$,
-%\begin{align}
-  	%\phi_p(x)
-  	%:= \frac{1}{\sqrt{ p! 2^{|p|} }} \mathcal H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big), 
-  	%\quad x\in \mathbb R^d,
-%\end{align}
-	%is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$.
-	%Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
-	%Thus for each $f\in L^2(\varphi)$, we have
-%\begin{align}
-%\label{semicomp1}
-	%f
-  	%= \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p, 
-  	%\quad \text{in~} L^2(\varphi).
-%\end{align}
-%}
+%	And for each $p\in \mathbb Z_+^d$, 
+For each $p\in \mathbb Z_+^d$, 
+$\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$, where $|p|:= \sum_{k=1}^d p_k$.
 	For each function $f\in L^2(\varphi)$, define the order of $f$ as
-%{
-%\[
-$
-  	\kappa_f
-  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}.
-$
-%\]
-%{
-	%Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
-	%In particular, the order of any constant non-zero function is zero.
-%}
+$\kappa_f
+  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}$
+with the convention that $\inf\emptyset=\infty.$
 
 	For $p\in \mathbb{Z}_+^d$, define
-%{\[
-$
-  	H_t^p
-  	%:= e^{-(\alpha-|p|b)t}X_t(\phi_p), \qquad t\geq 0.
-  	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.
-%\]
-$
-%}
-%{	We will write $H^0_t$ as $H_t$. %}
+$H_t^p
+    	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.$
 	For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
-%{
-	%We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} the following:
 	We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that
-%\begin{equation}\label{eq:Hinfty}
-%\begin{minipage}{0.9\textwidth}
-	%For any
 	for any
@@
 	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
-%\end{minipage}
-%\end{equation}
-%}
-%{
-	%We will write $H^0_\infty$ as $H_\infty$.
-	We will write $H^0_t$ and $H^0_\infty$ as $H^0_t$ and $H_\infty$.
-%}
+%We will write $H^0_t$ and $H^0_\infty$ as $H^0_t$ and $H_\infty$, respectively.
+We will write $H^0_t$ and $H^0_\infty$ as $H_t$ and $H_\infty$, respectively.
 
-%{Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
 	Denote by $\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
-%\begin{align}
-$
-  	\mathcal{P}
-  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
-$
-%\end{align}
-	%It is clear that $\mathcal{P} \subset L^2(\varphi)$.
-%}
-%{	
+$\mathcal{P}
+  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.$
 	Define
-%\begin{equation}
-%\begin{minipage}{0.9\textwidth}
 	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \},
-	%\quad 
 		~
 	\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
-	%\\ 
 	$ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
-%\end{minipage}
-%\end{equation}
 	Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
@@
 	T_t f
-	%{:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
-	:= \sum_{p \in \mathbb Z_+^d} \exp\{-\big| |p|b - \alpha \tilde \beta \big|t\} \langle f, \phi_p \rangle_{\varphi} \phi_p,
+	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
 	\quad t\geq 0, f\in \mathcal P,
@@
 \end{align}
-%{	For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$ %}
 	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
@@
 \end{equation}
-	%{Furthermore, we proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
 		For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
 	We also proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
-	%}
 	\begin{equation}\label{eq:oldResult}
@@
 	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$;
-%{and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm c$ and $f_\mathrm l$ maybe non-zero.
   and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero while $f_\mathrm c \equiv 0$.
-%}
 	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem in this case.
@@
 
-	%{The main purpose of this note is to show that the limit  random variables in \eqref{eq:oldResult} are independent.
-	The main purpose of this note is to confirm this conjecture. %}
+	The main purpose of this note is to show that the limit  random variables in \eqref{eq:oldResult} are independent.
 
@@
 \end{align}
-	where $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$;
+	where $\mathrm x_t(f_\mathrm l)$ is defined in 
+	\eqref{eq:oldResult} 
+	with $f$ replaced with $f_\mathrm l$;
 	$\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
@@
 \item
-%{ if $f_\mathrm c=0$, then
 	if $f_\mathrm c\equiv 0$, then
-%}
 \[
@@
 \item
-%{	if $f_\mathrm c\neq0$, then
-if $f_\mathrm c\not\equiv 0$, then%}
+if $f_\mathrm c\not\equiv 0$, then
 \[
@@
 \]
-	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of the limit of $\Upsilon^f_t$.
+	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
+%	the limit of $\Upsilon^f_t$.
+the weak limit of $\Upsilon^f_t$.
 	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
-	The following Lemma \ref{lem:P:R} can be proved using a similar argument used in the proof of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
+	The following Lemma \ref{lem:P:R} can be proved using 
+%	a similar argument used in the proof of 
+an argument similar to that used in the proof of 
+	\cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
 \begin{lem}
 \label{lem:P:R}
-	%{Suppose that $g = g_\mathrm s + g_\mathrm c + g_\mathrm l$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$.
-	%Then there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
 	For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
@@
 
-	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable} 
-	%{with using Lemma \ref{lem:P:R} instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
-	with using Lemma \ref{lem:P:R} above instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
+	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable},
+%		with using Lemma \ref{lem:P:R} above instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
+with Lemma \ref{lem:P:R} replacing the role of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}.
 	Let $(\mathscr F_t)_{t\geq 0}$ be the natural filtration of $X$.
-	%}
 	\begin{prop}
 \label{thm:Key}
-	For each $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
+	For any $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
 \[
@@
 \begin{prop} \label{cor:MI}
-	For each  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1+1$, we have
+	For any  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1+1$, we have
 \begin{equation}
@@
 	where we used the convention that $\prod_{j=0}^{-1} =1.$
-%{Let $(\mathscr F_t)_{t\ge 0}$ be the natural filtration of $X$. %}
   	Then for all  $k_2 \in \{0,\dots,n_2\}$, we have
@@
 
-	%{The following elementary result will also be used in the proof of Theorem \ref{thm: II}.
 	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
-	%}
 	\begin{lem}
@@
 
-	In the remainder of this section, we always fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$,  $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$.
+	In the remainder of this section, we  fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$,  $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$.
 	For every $t\geq 1$, define
@@
 	&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
-    %{ \\R_0(t)
-    %&=\big(I_0^{f_\mathrm s}(t),I_0^{f_\mathrm c}(t),I_0^{f_\mathrm l}(t)\big)
         \\R'(t)
     &=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
-    %}
         \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
 \end{align}
-%{
-	%where $T_k$ is the operator defined in \eqref{e:Tt} and $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
-	where $T_k$ is the operator defined in \eqref{e:Tt}, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
-%}
+where $T_k$ is the operator defined in 
+%\eqref{e:Tt} and $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
+\eqref{e:Tt}, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
+with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
 	The following result is a special case of Theorem \ref{thm:M}.
@@
 	In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
-	According to the proof of Theorem 1.6 in \cite{RenSongSunZhao2019Stable}, and the fact that the convergence in probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
+	According to the proof of 
+%	Theorem 1.6 in \cite{RenSongSunZhao2019Stable}, and the fact that the convergence in
+\cite[Theorem 1.6]{RenSongSunZhao2019Stable} and the fact that the convergence in
+ probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
 \[
-	%{R(t)-R_0(t) 
 	R(t)-R'(t)
-	%} 
 	\xrightarrow[t\to \infty]{\text{in probability}} 0.
@@
 \begin{equation} \label{lem:UOT}
-	%{R_0(t)
-	R'(t)%}
+	R'(t)
 	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
@@
 \[
-	%{\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
-	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R_j(t)\Big)\Big] %}
+        \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_j(t)\Big)\Big]
 	= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
@@
 	Note that $\{T_k(\tilde f_\mathrm s + t^{\tilde\beta - 1}\tilde f_{\mathrm c}):k\in \mathbb Z_+, t\geq 1\}\subset \overline{\mathcal P}_{\tilde f_\mathrm s + \tilde f_{\mathrm c}}$ and $\{-T_k\tilde{f}_{\mathrm l}: k\in \mathbb Z_+\}\subset \overline{\mathcal P}_{\tilde f_\mathrm l}$.
-	Therefore, we can use Proposition \ref{cor:MI} with $f$ taking as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taking as $\tilde{f}_{\mathrm l}$, and get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
+	Therefore, we can use Proposition \ref{cor:MI} with $f$ 
+%	taking as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taking as 
+taken as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taken as
+	$\tilde{f}_{\mathrm l}$
+	%, and get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
+	to get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
 \begin{align}
-    %{&\Big|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big] -\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})), \varphi\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\Big|
        &\begin{multlined}
-  	\bigg|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}R'_j(t)\Big)\Big] - {}
+  	\bigg|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}R'_j(t)\Big)\Big] - 
   	\\ \exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \big\langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})\big), \varphi \big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\bigg|
   	\end{multlined}
-  	%}
       \\ &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
@@
 \[
-	%{\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}I_0^{f_j}(t)\Big)\Big]
-	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_{j}(t)\Big)\Big] %}
+	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_{j}(t)\Big)\Big]
 	\xrightarrow[t\to \infty]{} \exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
 \]
-	%{Since $I_0^{f_j}(t)$ are linear
-	Since $R'_{j}(t)$ are linear %}
+	Since $R'_{j}(t)$ are linear 
 	 in $f_j \in \mathcal C_j~(j=\mathrm s,\mathrm c,\mathrm l)$, replacing $f_j$ with $\theta_j f_j$, we immediately get \eqref{lem:UOT}.
@@
 \begin{multlined}
-	%{\overset{\eqref{eq:Hinfty}}%}
 	=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + \frac{i\theta_\mathrm c}{(t+r)^{1-\tilde{\beta}}} \frac{X_{t+r}(f_\mathrm c)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + {}
@@
   	Cambridge University Press, 2002.
-
-%{\bibitem{Durrett2010Probability}
- 	%R. Durrett,
- 	%\emph{Probability: theory and examples},
- 	%Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
-%}
 

### 2020-09-25 supCLT-ind-JAP.tex
Update supCLT-ind-JAP.tex

@@
 		The eigenfunctions of $L$ consists a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
-%	And for each $p\in \mathbb Z_+^d$, 
 For each $p\in \mathbb Z_+^d$, 
@@
 	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
-%We will write $H^0_t$ and $H^0_\infty$ as $H^0_t$ and $H_\infty$, respectively.
 We will write $H^0_t$ and $H^0_\infty$ as $H_t$ and $H_\infty$, respectively.
@@
 	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
-%	the limit of $\Upsilon^f_t$.
 the weak limit of $\Upsilon^f_t$.
@@
 	The following Lemma \ref{lem:P:R} can be proved using 
-%	a similar argument used in the proof of 
 an argument similar to that used in the proof of 
@@
 	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable},
-%		with using Lemma \ref{lem:P:R} above instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
 with Lemma \ref{lem:P:R} replacing the role of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}.
@@
 where $T_k$ is the operator defined in 
-%\eqref{e:Tt} and $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
 \eqref{e:Tt}, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
@@
 	According to the proof of 
-%	Theorem 1.6 in \cite{RenSongSunZhao2019Stable}, and the fact that the convergence in
 \cite[Theorem 1.6]{RenSongSunZhao2019Stable} and the fact that the convergence in
@@
 	Therefore, we can use Proposition \ref{cor:MI} with $f$ 
-%	taking as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taking as 
 taken as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taken as
 	$\tilde{f}_{\mathrm l}$
-	%, and get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
 	to get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
@@
        &\begin{multlined}
-  	\bigg|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}R'_j(t)\Big)\Big] - 
+  	\bigg|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}R'_j(t)\Big)\Big] - {}
   	\\ \exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \big\langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})\big), \varphi \big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\bigg|

### 2020-10-04 representation/oneworld20.tex
Update oneworld20.tex

\documentclass[xcolor=dvipsnames]{beamer}
\synctex=1
%\usepackage[UTF8,scheme=plain]{ctex}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{comment}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usetheme{Madrid}
\usecolortheme{seahorse}
\usecolortheme{rose}
\usefonttheme{serif}
\usefonttheme{structurebold}
\setbeamerfont{title}{shape=\itshape,family=\rmfamily}
\setbeamercolor{title}{fg=red!80!black,bg=red!20!white}

\title[Stable CLT for superprocesses]{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
\author[Zhenyao Sun]{ 
	{\bf \Large Zhenyao Sun  }
}
\institute[]{Joint work with {\bf Yan-Xia Ren}, {\bf Renming Song} and {\bf Jianjie Zhao}}
\date[]{
	Branching structure,
	\\ August, 2020}

\AtBeginSection[]{\frame{\frametitle{Outline}\tableofcontents[current]}}

\begin{document}

\frame{\titlepage}

%\part{Main Part}
\begin{frame}
	\vfill This talk is based on the following two papers:

	\vfill [1] Y.-X. Ren, R. Song Z. Sun and J. Zhao: 
	Stable central limit theorems for super Ornstein-Uhlenbeck processes. 
	{\it Elect. J. Probab.}, \textbf{24} (2019), No. 141, 1--42

	\vfill [2] Y.-X. Ren, R. Song Z. Sun and J. Zhao: 
	Y.-X. Ren, R. Song, Z, Sun and J. Zhao Stable central limit theorems for super 
	Ornstein-Uhlenbeck processes, II. https://arxiv.org/pdf/2005.11731.pdf
\end{frame}

\section{Background}

\begin{frame}{Background/CLT with finite second moment}
\begin{block}{}<1-2>
There have been many {\color{Bittersweet}central limit theorem} type results for {\color{blue} branching processes}, {\color{blue} branching Markov processes} and {\color{blue} superprocesses}, under the {\color{PineGreen} second moment condition}.
\end{block}

\begin{block}{}<2>
	Some {\color{Bittersweet}spatial central limit theorems} for {\color{PineGreen}supercritical} {\color{blue}branching OU processes} with {\color{PineGreen} binary branching} were proved in Adamczak-Milos (EJP, 2015), and some {\color{Bittersweet}spatial central limit theorems} for {\color{PineGreen} supercritical} {\color{blue} super-processes} were proved in Milos (JTP, 2018). 
	These two papers made connections between {\color{Bittersweet}spatial central limit theorems} and {\color{Bittersweet}branching rate regimes}. The results of these two papers have been refined and generalized in a series of papers by Ren-Song-Zhang.
\end{block}
\end{frame}

\begin{frame}{Background/CLT with infinite second moment}
\begin{block}{}<1-3>
There are also {\color{Bittersweet}central limit theorem} type results for {\color{PineGreen} supercritical} {\color{blue}branching processes}
and {\color{blue} branching Markov processes} with branching mechanisms of {\color{PineGreen} infinite second moment}.
For earlier papers, see Asmussen, (AOP, 1976) and Heyde (JAP, 1971).
\end{block}

\begin{block}{}<2-3>
In a recent paper (arXiv:1803.05491) Marks and Milos established some {\color{Bittersweet}spatial central limit theorems} in the {\color{PineGreen} small and critical branching rate regimes}, for some {\color{PineGreen} supercritical} {\color{blue} branching OU processes} with a {\color{PineGreen} special stable offspring distribution.}
\end{block}

\begin{block}{}<3>
Our {\color{red}goal} is to establish {\color{Bittersweet}stable central limit theorems} for {\color{blue}super-OU processes} with {\color{PineGreen} general stable branching mechanisms.}
\end{block}  
\end{frame}

\section{Model}

\begin{frame}{Model/Parameters}
\begin{block}{}<1-2>
Suppose ${\color{blue}\xi}=\{({\color{blue}\xi}_t)_{t\ge 0}, (\Pi_x)_{x\in \mathbb R^d}\}$ is an OU process on $\mathbb R^d$ with generator
$$
Lf(x)=\frac12\sigma^2\Delta f(x)-{\color{red} b}x\cdot \nabla f(x)
$$
with ${\color{red}b}, \sigma$ being positive constants.
\end{block}

\begin{block}{}<2>
Suppose that ${\color{blue}\psi}$ is a branching mechanism of the form
$$
{\color{blue}\psi} (z)=-{\color{red}\alpha} z + \rho z^2 +\int_{(0, \infty)}(e^{-zy}-1+zy) \pi(dy)
$$
where ${\color{red}\alpha}>0$ and $\rho\ge 0$ and $\pi$ is a measure on $(0, \infty)$ with
$\int_{(0, \infty)}(y\wedge y^2)\pi(dy)<\infty$.
We call ${\color{red}\alpha}$ the branching rate.
\end{block}
\end{frame}

\begin{frame}{Model/Assumptions}
\begin{block}{Assumption 1}<1-3>
	The branching mechanism satisfies Grey's condition, i.e. there is some constant $z' > 0$ such that ${\color{blue}\psi}(z) > 0$ for all $z>z'$ and that $\int_{z'}^\infty {\color{blue}\psi}(z)^{-1}dz < \infty$.
\end{block}
\begin{block}{Assumption 2}<2-3>
There exist constants $\eta > 0$ and ${\color{red}\beta} \in (0,1)$ such that
$$
    \int_{(1,\infty)}y^{1+ {\color{red} \beta} +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-{\color{red}\beta})y^{2+{\color{red}\beta}}}\Big| <\infty,
$$
	for some $\delta \in (0, 1-{\color{red}\beta})$.
\end{block}
\begin{block}{}<3>
Roughly speaking, Assumption 2 says that ${\color{blue}\psi}$ is ``not too far away'' from
$\widetilde \psi(z)= -{\color{red}\alpha} z+\eta z^{1+{\color{red}\beta}}$ near 0.
\end{block}
\end{frame}

\begin{frame}{Model/Superprocess}
\begin{block}{}<1-2>
Denote by $\mathcal M(\mathbb R^d)$ ($\mathcal M_c(\mathbb R^d)$, resp.) the space of all finite Borel measures (of compact support, resp.) on $\mathbb R^d$. We suppose that $X=\{(X_t)_{t\ge 0}, 
(\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a superprocess with spatial motion ${\color{blue}\xi}$ and branching mechanism ${\color{blue}\psi}$, i.e., a super-OU process.
\end{block}
\begin{block}{}<2>
	In other word, for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
	\begin{align}
		\label{eq: def of V_t}
		\mathbb{P}_{\mu}[e^{-X_t(f)}]
		= e^{-\mu(V_tf)},
		\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
	\end{align}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
	\begin{align}
		V_tf(x) + \Pi_x \Big[ \int_0^t {\color{blue}\psi} (V_{t-s}f({\color{blue}\xi}_s) ) \mathrm ds\Big]
		= \Pi_x [f({\color{blue}\xi}_t)],
		\quad x\in \mathbb R^d, t\geq 0.
	\end{align}	
\end{block}
\end{frame}

\section{Main Result}
\begin{frame}{Main Result/Preliminary}
\begin{block}{}<1-2>
The OU process ${\color{blue}\xi}$ has an invariant distribution
$$
    {\color{blue}\varphi(x)}dx
    :=\Big (\frac{{\color{red}b}}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{{\color{red}b}}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb R^d.
$$
    Let ${\color{blue}L^2(\varphi)}:= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 {\color{blue}\varphi(x)} dx < \infty \right\}$.
        Then, ${\color{blue}L^2(\varphi)}$ is a Hilbert space with inner product $\langle \cdot, \cdot \rangle_{\color{blue}\varphi}$.
\end{block}

\begin{block}{}<2>
The OU operator $L$ has discrete spectrum
$\color{red}\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
The eigenfunctions of $L$ consists a family of polynomials $\color{red}\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of ${\color{blue}L^2(\varphi)}$.
For each $\color{red}p\in \mathbb Z_+^d$, 
${\color{red}\phi_p}$ is an eigenfunction of $L$ corresponding to the eigenvalue ${\color{red}b}{\color{red}|p|}$, where $\color{red}|p|:= \sum_{k=1}^d p_k$. 
\end{block}
\end{frame}

\begin{frame} {Main Result/Preliminary}
	\begin{block}{}<1-4>
		For $p\in \mathbb{Z}_+^d$, define a martingale
		$
		\color{blue}H_t^p
		:= e^{-(\alpha-|p|b)t}X_t({\color{blue}\phi_p}), t\geq 0.
		$
	\end{block}

	\begin{block}{}<2-4>
		For any $u \neq -1$, we write $\color{red}\tilde u = u/(1+ u)$.
	\end{block}

	\begin{block}{Lemma 1}<3-4>
		For any $\mu\in \mathcal M_c(\mathbb R^d)$, $\color{blue}(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
		Furthermore, if $\color{red}\alpha  \tilde \beta>|p|b$, then for any $\gamma\in (0, {\color{red}\beta})$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $\color{blue}(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
		thus $\color{blue}H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
	\end{block}
	\begin{block}{}<4>
		Fixing $\color{red}\beta\in (0,1)$, $\color{red}p\in \mathbb Z_+^d$ and $\color{red}b>0$, if the branching rate $\color{red} \alpha$ is large enough so that $\color{red}\alpha  \tilde \beta>|p|b$ then we say we are in the large branching rate regime; if $\color{red}\alpha \tilde \beta= |p|b$ then we are in the critical branching rate regime;
		if $\color{red}\alpha \tilde \beta< |p|b$ then we are in the small branching rate regime.
	\end{block}
\end{frame}

\begin{frame}{Main Result/Preliminary}
\begin{block}{}<1-3>
	Denote by $\color{blue}\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$:
	$$
	\left\{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists~ C>0, n \in \mathbb Z_+ {\rm\,  s. t. \, } \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\right\}.
	$$
\end{block}
\begin{block}{}<2-3>
	Then we have the decomposition ${\color{blue}\mathcal P} = {\color{red}\mathcal C_\mathrm s} \otimes {\color{red}\mathcal C_\mathrm c} \otimes {\color{red}\mathcal C_\mathrm l}$ where
\begin{align*}
	{\color{red}\mathcal C_\mathrm s} &:= \mathcal P \cap \overline{\operatorname{Span}} \{ {\color{blue}\phi_p}: {\color{red}\alpha \tilde \beta < |p| b} \}\\
 	{\color{red}\mathcal C_\mathrm c}   &:= \mathcal P \cap \operatorname{Span} \{ {\color{blue}\phi_p} : {\color{red}\alpha \tilde \beta = |p| b} \} \\
	{\color{red}\mathcal C_\mathrm l} &  := \mathcal P \cap \operatorname{Span} \{ {\color{blue}\phi_p}: {\color{red}\alpha \tilde \beta > |p| b} \}.
\end{align*}
\end{block}

\begin{block}{}<3>
Note that $\color{red}\mathcal C_\mathrm s$ is an infinite dimensional space, ${\color{red}\mathcal C_\mathrm l}$ and ${\color{red}\mathcal C_\mathrm c}$
are finite dimensional spaces, and ${\color{red}\mathcal C_\mathrm c}$ might be empty.
\end{block}
\end{frame}

\begin{frame}{Main Result/Preliminary}

\begin{block}{}<1-2>
Define a semigroup
\begin{align*}
{\color{blue}T_t} f
:= \sum_{p \in \mathbb Z_+^d} e^{\color{red}-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p
,\quad t\geq 0, f\in \mathcal P,
\end{align*}
and a family of functionals
$$
{\color{blue}m_t}[f]
:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-i {\color{blue}T_u} f(x)\big)^{1+{\color{red}\beta}} \varphi(x) \mathrm dx
, \quad 0 \leq t< \infty, f\in \mathcal P.
$$
\end{block}

\begin{block}{Proposition 2}<2>   
For each $f\in \mathcal P$, there exists a $(1+{\color{red}\beta})$-stable random variable ${\color{red}\zeta^f}$ with characteristic function
$
\theta \mapsto e^{\color{red}m[\theta f]}, \theta \in \mathbb R,
$
where
$$
{\color{red}m[f]}
:= \begin{cases}
\lim_{t\to \infty} {\color{blue}m_t}[f], &
f \in {\color{red}\mathcal C_\mathrm s \oplus \mathcal C_\mathrm l}, \\
\lim_{t\to \infty} {\color{red}\frac{1}{t}} {\color{blue}m_t}[f], & f\in {\color{red}\mathcal P \setminus (\mathcal C_\mathrm s \oplus \mathcal C_\mathrm l)}.
\end{cases}
$$
\end{block}
\end{frame}

\begin{frame}{Main Result/Preliminary}

\begin{block}{}<1-2>
For $f\in \mathcal P$, note that
	$$
	{\color{blue}\mathrm X_t(f)} = \sum_{p\in \mathbb Z^d_+}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}{\color{blue}H^p_{t}}, \quad t\ge 0.
	$$ 
Define the centering 
$$
{\color{blue}\mathrm x_t(f)} : = \sum_{p\in \mathbb Z^d_+:{\color{red}\alpha} {\color{red}\tilde \beta>|p|b}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}{\color{blue}H^p_{B\infty}}, \quad t\ge 0.
$$ 
\end{block}
\begin{block}{}<2>
	Let $D :=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}$
	be the extinction event. 
\end{block}
\end{frame}

\begin{frame}{Main Result}

\begin{block}{Theorem 3 (Ren, Song, S. and Zhao, arXiv:2005.11731)}<1>
If $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus\{0\}$, $\color{red}f_\mathrm s\in \mathcal C_\mathrm s$, $\color{red}f_\mathrm c\in \mathcal C_\mathrm c$ and $\color{red}f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb P_\mu(\cdot | D^c)$,
	\begin{align*} 
	&S(t):=
	\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t({\color{red}f_\mathrm s})}{\|X_t\|^{{\color{blue}1-\tilde \beta}}},\frac{X_t({\color{red}f_\mathrm c)}}{\|{\color{blue}t}X_t\|^{{\color{blue}1-\tilde \beta}}}, \frac{ X_t({\color{red}f_\mathrm l}) - \mathrm x_t({\color{red}f_\mathrm l})}{\|X_t\|^{{\color{blue}1-\tilde \beta}}} \Bigg)
	\\&\xrightarrow[t\rightarrow \infty]{d}({\color{blue}\widetilde H_\infty},{\color{red}\zeta^{f_\mathrm s}},{\color{red}\zeta^{f_\mathrm c}},{\color{red}\zeta^{-f_\mathrm l}}),
	\end{align*}
	where 
${\color{red}\widetilde H_\infty}$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$; $\color{red}\zeta^{f_\mathrm s}$, $\color{red}\zeta^{f_\mathrm c}$ and $\color{red}\zeta^{-f_\mathrm l}$ are the $\color{blue}(1+\beta)$-stable random variables described in Proposition 2; $\color{blue}\widetilde H_\infty$,  $\color{red}\zeta^{f_\mathrm s}$, $\color{red}\zeta^{f_\mathrm c}$ and $\color{red}\zeta^{-f_\mathrm l}$ are independent.
\end{block}
\end{frame}

\begin{frame}{Main Result}
\begin{block}{Corollary 4}<1>
Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P$ with $\color{red}f=f_\mathrm s + f_\mathrm c+ f_\mathrm l$ where $\color{red}f_\mathrm s \in \mathcal C_\mathrm s$, $\color{red}f_\mathrm c\in \mathcal C_\mathrm c$ and $\color{red}f_\mathrm l \in \mathcal C_\mathrm l$.
Then under $\mathbb{P}_{\mu}(\cdot| D^c)$, it holds that
\begin{enumerate}
\item  if $\color{red}f_\mathrm c\equiv 0$, then
\[
    \frac{ X_t(f) - \mathrm x_t(f)} {\|X_t\|^{{\color{blue}1-\tilde \beta}}}
    \xrightarrow[t\to \infty]{d}
       {\color{red}\zeta^{f_\mathrm s}}+{\color{red}\zeta^{-f_\mathrm l}},
\]
	where $\color{red}\zeta^{f_\mathrm s}$ and $\color{red}\zeta^{-f_\mathrm l}$  are the $\color{blue}(1+\beta)$-stable random variables described in Proposition 2, $\color{red}\zeta^{f_\mathrm s}$ and $\color{red}\zeta^{-f_\mathrm l}$ are independent;
\item if $\color{red}f_\mathrm c\not \equiv 0$, then
\[
    \frac{ X_t(f) - \mathrm x_t(f)}{\|{\color{blue}t}X_t\|^{{\color{blue}1-\tilde \beta}}}
    \xrightarrow[t\to \infty]{d}{\color{red}\zeta^{f_\mathrm c}}.
\]
	where $\color{red}\zeta^{f_\mathrm c}$ is the $\color{blue}(1+\beta)$-stable random variable described in Proposition 2.
\end{enumerate}
\end{block}
\end{frame}

\section{Intuitive explanation}

\begin{frame}{Intuitive explanation}
\begin{block}{}<1-3>
	The central limit theorem for $\color{blue}X_t(\phi_p)$ takes different forms depending on whether it's in the large branching regime (${\color{red}\alpha \tilde \beta > {\color{red}|p|}  b}$), or in the critical branching regime (${\color{red}\alpha \tilde \beta = {\color{red}|p|}  b}$), or in the small branching regime (${\color{red}\alpha \tilde \beta < {\color{red}|p|}  b}$).
	We now give some intuitive explanation of this phase transition.
\end{block}

\begin{block}{}<2-3>
	A superprocess can be thought of as a cloud of infinitesimal branching ``particles'' moving in space.
\end{block}

\begin{block}{}<3>
	The phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing.
	The coarsening effect corresponds to the increase of the spatial inequality and is a consequence of the branching.
	The smoothing effect corresponds to the decrease of the spatial inequality and is a consequence of the mixing property of the OU processes.
\end{block}

\end{frame}

\begin{frame}{Intuitive explanation}
\begin{block}{}<1-3>
	Let us discuss how the parameters $\color{red}\alpha, \beta, b$ and ${\color{red}|p|}$
	influence those two effects:
\end{block}
\begin{block}{}<2-3>
		The branching rate $\color{red}\alpha$ captures the mean intensity of the branching in the system.
		Therefore, the lager the branching rate $\color{red}\alpha$, the stronger the coarsening effect.
\end{block}
\begin{block}{}<3>
		The tail index $\color{red}\beta$ describes the heaviness of the tail of the offspring distribution which belongs to the domain of attraction of some $\color{red}(1+\beta)$-stable random variable.
		When $\color{red}\beta$ is smaller i.e. the tail is heavier, then it is more likely that 
		one particle can suddenly have a large amount of offspring.
		In other words, the larger the tail index $\color{red}\beta$, the smaller the fluctuation of offspring number, and then the stronger the coarsening effect.
\end{block}
\end{frame}

\begin{frame}{Intuitive explanation}
\begin{block}{}<1-2>
	The drift parameter $\color{red}b$ is related to the level of the mixing property of the OU particles.
		The larger the drift parameter $\color{red}b$, the faster the OU-particles forgetting their initial position, and therefore the stronger the smoothing effect.
\end{block}
\begin{block}{}<2>
		The order ${\color{red}|p|}$ is related to the capability of $\color{blue}\phi_p$ capturing the mixing property of the OU particles.
		In particular, in the case that $\color{red}|p| = 0$, no mixing property can be captured. (Since $\color{blue}\phi_p \equiv 1$, we are only considering the total mass $\color{blue}\|X_t\|$).
		In general, the higher the order ${\color{red}|p|}$, the more mixing property can be captured by $\color{blue}\phi_p$, and therefore the stronger the smoothing effect.
\end{block}
\end{frame}

\begin{frame}
\begin{center}
\Huge{Thank you!}
\end{center}
\begin{center}
\end{center}
\end{frame}
\end{document}

### 2021-02-06 supCLT-ind-AMSE.tex
add supCLT-ind-AMSE.tex

--- 2020-09-25 supCLT-ind-JAP.tex
@@
   	Zhenyao Sun \\
+  	School of Mathematics and Statistics\\
+  	Wuhan University\\
+  	Wuhan, Hubei 430072, P. R. China. }
+\address{
   	Faculty of Industrial Engineering and Management\\

### 2021-02-06 representation/Zhenyao2020Oct.tex

--- 2020-10-04 representation/oneworld20.tex
@@
 \date[]{
-	Branching structure,
-	\\ August, 2020}
+	The 6th workshop on branching processes and related topics,
+	\\ Octorber, 2020}
 
@@
 \end{block}
-
 \begin{block}{}<2>
@@
 \end{block}
-
 \begin{block}{}<2-3>
@@
 \end{block}
-
 \begin{block}{}<3>
@@
 \begin{block}{}<1-2>
-Suppose ${\color{blue}\xi}=\{({\color{blue}\xi}_t)_{t\ge 0}, (\Pi_x)_{x\in \mathbb R^d}\}$ is an OU process on $\mathbb R^d$ with generator
+Suppose {\color{PineGreen} spatial motion} ${\color{blue}\xi}=\{({\color{blue}\xi}_t)_{t\ge 0}, (\Pi_x)_{x\in \mathbb R^d}\}$ is an {\color{PineGreen}OU process} on $\mathbb R^d$ with generator
 $$
@@
 \end{block}
-
 \begin{block}{}<2>
-Suppose that ${\color{blue}\psi}$ is a branching mechanism of the form
+Suppose that ${\color{blue}\psi}$ is a {\color{PineGreen}branching mechanism} of the form
 $$
@@
 $\int_{(0, \infty)}(y\wedge y^2)\pi(dy)<\infty$.
-We call ${\color{red}\alpha}$ the branching rate.
+We call ${\color{red}\alpha}$ the {\color{PineGreen}branching rate}.
 \end{block}
@@
 Denote by $\mathcal M(\mathbb R^d)$ ($\mathcal M_c(\mathbb R^d)$, resp.) the space of all finite Borel measures (of compact support, resp.) on $\mathbb R^d$. We suppose that $X=\{(X_t)_{t\ge 0}, 
-(\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a superprocess with spatial motion ${\color{blue}\xi}$ and branching mechanism ${\color{blue}\psi}$, i.e., a super-OU process.
+(\mathbb P_\mu)_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a {\color{PineGreen}superprocess} with {\color{PineGreen}spatial motion} ${\color{blue}\xi}$ and {\color{PineGreen}branching mechanism} ${\color{blue}\psi}$, i.e., a {\color{PineGreen} super-OU process}.
 \end{block}
 \begin{block}{}<2>
-	In other word, for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+	For each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
 	\begin{align}
@@
 \begin{block}{}<1-2>
-The OU process ${\color{blue}\xi}$ has an invariant distribution
+The OU process ${\color{blue}\xi}$ has an {\color{PineGreen} invariant distribution}
 $$
@@
 $\color{red}\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
-The eigenfunctions of $L$ consists a family of polynomials $\color{red}\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of ${\color{blue}L^2(\varphi)}$.
+The eigenfunctions of $L$ consists a family of polynomials $\color{red}\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a {\color{PineGreen}complete orthonormal basis} of ${\color{blue}L^2(\varphi)}$.
 For each $\color{red}p\in \mathbb Z_+^d$, 
@@
 	\end{block}
-
 	\begin{block}{Lemma 1}<3-4>
@@
 	\begin{block}{}<4>
-		Fixing $\color{red}\beta\in (0,1)$, $\color{red}p\in \mathbb Z_+^d$ and $\color{red}b>0$, if the branching rate $\color{red} \alpha$ is large enough so that $\color{red}\alpha  \tilde \beta>|p|b$ then we say we are in the large branching rate regime; if $\color{red}\alpha \tilde \beta= |p|b$ then we are in the critical branching rate regime;
-		if $\color{red}\alpha \tilde \beta< |p|b$ then we are in the small branching rate regime.
+		Fixing $\color{red}\beta\in (0,1)$, $\color{red}p\in \mathbb Z_+^d$ and $\color{red}b>0$, if the {\color{PineGreen} branching rate} $\color{red} \alpha$ is large enough so that $\color{red}\alpha  \tilde \beta>|p|b$ then we say we are in {\color{PineGreen} the large branching rate regime}; if $\color{red}\alpha \tilde \beta= |p|b$ then we are in {\color{PineGreen} the critical branching rate regime};
+		if $\color{red}\alpha \tilde \beta< |p|b$ then we are in {\color{PineGreen} the small branching rate regime}.
 	\end{block}
 \end{frame}
-
 \begin{frame}{Main Result/Preliminary}
 \begin{block}{}<1-3>
-	Denote by $\color{blue}\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$:
+	Denote by $\color{blue}\mathcal P \subset L^2(\varphi)$ the class of {\color{PineGreen}functions of polynomial growth} on $\mathbb R^d$:
 	$$
@@
 \end{block}
-
 \begin{block}{}<3>
-Note that $\color{red}\mathcal C_\mathrm s$ is an infinite dimensional space, ${\color{red}\mathcal C_\mathrm l}$ and ${\color{red}\mathcal C_\mathrm c}$
-are finite dimensional spaces, and ${\color{red}\mathcal C_\mathrm c}$ might be empty.
+Note that $\color{red}\mathcal C_\mathrm s$ is an {\color{PineGreen} infinite dimensional space}, ${\color{red}\mathcal C_\mathrm l}$ and ${\color{red}\mathcal C_\mathrm c}$
+are {\color{PineGreen} finite dimensional spaces}, and ${\color{red}\mathcal C_\mathrm c}$ {\color{PineGreen} might be empty}.
 \end{block}
@@
 \begin{frame}{Main Result/Preliminary}
-
 \begin{block}{}<1-2>
@@
 {\color{blue}m_t}[f]
-:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-i {\color{blue}T_u} f(x)\big)^{1+{\color{red}\beta}} \varphi(x) \mathrm dx
+:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-i {\color{blue}T_u} f(x)\big)^{{\color{red}1+\beta}} \varphi(x) \mathrm dx
 , \quad 0 \leq t< \infty, f\in \mathcal P.
@@
 \end{block}
-
 \begin{block}{Proposition 2}<2>   
-For each $f\in \mathcal P$, there exists a $(1+{\color{red}\beta})$-stable random variable ${\color{red}\zeta^f}$ with characteristic function
+For each $f\in \mathcal P$, there exists a $({\color{red}1+\beta})$-{\color{PineGreen}stable random variable} ${\color{red}\zeta^f}$ with characteristic function
 $
@@
 $$
-{\color{blue}\mathrm x_t(f)} : = \sum_{p\in \mathbb Z^d_+:{\color{red}\alpha} {\color{red}\tilde \beta>|p|b}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}{\color{blue}H^p_{B\infty}}, \quad t\ge 0.
+{\color{blue}\mathrm x_t(f)} : = \sum_{p\in \mathbb Z^d_+:{\color{red}\alpha} {\color{red}\tilde \beta>|p|b}}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}{\color{blue}H^p_{\infty}}, \quad t\ge 0.
 $$ 
@@
 	Let $D :=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}$
-	be the extinction event. 
+	be the {\color{PineGreen}extinction event}. 
 \end{block}
@@
 \begin{frame}{Main Result}
-
 \begin{block}{Theorem 3 (Ren, Song, S. and Zhao, arXiv:2005.11731)}<1>
@@
 	where 
-${\color{red}\widetilde H_\infty}$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$; $\color{red}\zeta^{f_\mathrm s}$, $\color{red}\zeta^{f_\mathrm c}$ and $\color{red}\zeta^{-f_\mathrm l}$ are the $\color{blue}(1+\beta)$-stable random variables described in Proposition 2; $\color{blue}\widetilde H_\infty$,  $\color{red}\zeta^{f_\mathrm s}$, $\color{red}\zeta^{f_\mathrm c}$ and $\color{red}\zeta^{-f_\mathrm l}$ are independent.
+${\color{blue}\widetilde H_\infty}$ has the distribution of $\color{blue}\{H^0_{\infty}; \widetilde {\mathbb P}_\mu\}$; $\color{red}\zeta^{f_\mathrm s}$, $\color{red}\zeta^{f_\mathrm c}$ and $\color{red}\zeta^{-f_\mathrm l}$ are the $\color{blue}(1+\beta)$-{\color{PineGreen}stable random variables} described in Proposition 2; $\color{blue}\widetilde H_\infty$,  $\color{red}\zeta^{f_\mathrm s}$, $\color{red}\zeta^{f_\mathrm c}$ and $\color{red}\zeta^{-f_\mathrm l}$ are independent.
 \end{block}
@@
 \]
-	where $\color{red}\zeta^{f_\mathrm s}$ and $\color{red}\zeta^{-f_\mathrm l}$  are the $\color{blue}(1+\beta)$-stable random variables described in Proposition 2, $\color{red}\zeta^{f_\mathrm s}$ and $\color{red}\zeta^{-f_\mathrm l}$ are independent;
+	where $\color{red}\zeta^{f_\mathrm s}$ and $\color{red}\zeta^{-f_\mathrm l}$  are the $\color{blue}(1+\beta)$-{\color{PineGreen}stable random variables} described in Proposition 2, $\color{red}\zeta^{f_\mathrm s}$ and $\color{red}\zeta^{-f_\mathrm l}$ are independent;
 \item if $\color{red}f_\mathrm c\not \equiv 0$, then
@@
 \]
-	where $\color{red}\zeta^{f_\mathrm c}$ is the $\color{blue}(1+\beta)$-stable random variable described in Proposition 2.
+	where $\color{red}\zeta^{f_\mathrm c}$ is the $\color{blue}(1+\beta)$-{\color{PineGreen}stable random variable} described in Proposition 2.
 \end{enumerate}
@@
 
-\section{Intuitive explanation}
+\section{Intuition}
 
-\begin{frame}{Intuitive explanation}
+\begin{frame}{Intuition}
 \begin{block}{}<1-3>
-	The central limit theorem for $\color{blue}X_t(\phi_p)$ takes different forms depending on whether it's in the large branching regime (${\color{red}\alpha \tilde \beta > {\color{red}|p|}  b}$), or in the critical branching regime (${\color{red}\alpha \tilde \beta = {\color{red}|p|}  b}$), or in the small branching regime (${\color{red}\alpha \tilde \beta < {\color{red}|p|}  b}$).
+	The central limit theorem for $\color{blue}X_t(\phi_p)$ takes different forms depending on whether it's in the {\color{PineGreen}large branching regime} (${\color{red}\alpha \tilde \beta > {\color{red}|p|}  b}$), or in the {\color{PineGreen}critical branching regime} (${\color{red}\alpha \tilde \beta = {\color{red}|p|}  b}$), or in the {\color{PineGreen}small branching regime} (${\color{red}\alpha \tilde \beta < {\color{red}|p|}  b}$).
 	We now give some intuitive explanation of this phase transition.
 \end{block}
-
 \begin{block}{}<2-3>
@@
 \end{block}
-
 \begin{block}{}<3>
-	The phase transition is due to an interplay of two competing effects in the system: coarsening and smoothing.
-	The coarsening effect corresponds to the increase of the spatial inequality and is a consequence of the branching.
-	The smoothing effect corresponds to the decrease of the spatial inequality and is a consequence of the mixing property of the OU processes.
-\end{block}
-
-\end{frame}
-
-\begin{frame}{Intuitive explanation}
-\begin{block}{}<1-3>
-	Let us discuss how the parameters $\color{red}\alpha, \beta, b$ and ${\color{red}|p|}$
-	influence those two effects:
-\end{block}
-\begin{block}{}<2-3>
-		The branching rate $\color{red}\alpha$ captures the mean intensity of the branching in the system.
-		Therefore, the lager the branching rate $\color{red}\alpha$, the stronger the coarsening effect.
-\end{block}
-\begin{block}{}<3>
-		The tail index $\color{red}\beta$ describes the heaviness of the tail of the offspring distribution which belongs to the domain of attraction of some $\color{red}(1+\beta)$-stable random variable.
-		When $\color{red}\beta$ is smaller i.e. the tail is heavier, then it is more likely that 
-		one particle can suddenly have a large amount of offspring.
-		In other words, the larger the tail index $\color{red}\beta$, the smaller the fluctuation of offspring number, and then the stronger the coarsening effect.
+	The phase transition is due to an interplay of two competing effects in the system: {\color{PineGreen}coarsening} and {\color{PineGreen}smoothing}.
+	The {\color{PineGreen}coarsening effect} corresponds to the increase of the spatial inequality and is a consequence of the branching.
+	The {\color{PineGreen}smoothing effect} corresponds to the decrease of the spatial inequality and is a consequence of the mixing property of the OU processes.
 \end{block}
@@
 
-\begin{frame}{Intuitive explanation}
+\begin{frame}{Intuition}
+\begin{block}{}<1-3>
+	Let us discuss how the parameters $\color{red}\alpha, \beta, b$ and ${\color{red}|p|}$
+	influence those two effects for $\color{blue}X_t(\phi_p)$:
+\end{block}
+\begin{block}{}<2-3>
+		The {\color{PineGreen}branching rate} $\color{red}\alpha$ captures the mean intensity of the branching in the system.
+		Therefore, the {\color{PineGreen}lager the branching rate} $\color{red}\alpha$, the {\color{PineGreen}stronger the coarsening effect}.
+\end{block}
+\begin{block}{}<3>
+		The {\color{PineGreen}tail index} $\color{red}\beta$ describes the heaviness of the tail of the offspring distribution.
+		When $\color{red}\beta$ is smaller i.e. the tail is heavier, then it is more likely that 
+		one particle can suddenly have a large amount of offspring.
+		In other words, the {\color{PineGreen} larger the tail index} $\color{red}\beta$, the smaller the fluctuation of offspring number, and then the {\color{PineGreen} stronger the coarsening effect}.
+\end{block}
+\end{frame}
+
+\begin{frame}{Intuition}
 \begin{block}{}<1-2>
-	The drift parameter $\color{red}b$ is related to the level of the mixing property of the OU particles.
-		The larger the drift parameter $\color{red}b$, the faster the OU-particles forgetting their initial position, and therefore the stronger the smoothing effect.
+	The {\color{PineGreen}drift parameter} $\color{red}b$ is related to the level of the mixing property of the OU particles.
+		The {\color{PineGreen}larger the drift parameter} $\color{red}b$, the faster the OU-particles forgetting their initial position, and therefore the {\color{PineGreen}stronger the smoothing effect}.
 \end{block}
 \begin{block}{}<2>
-		The order ${\color{red}|p|}$ is related to the capability of $\color{blue}\phi_p$ capturing the mixing property of the OU particles.
-		In particular, in the case that $\color{red}|p| = 0$, no mixing property can be captured. (Since $\color{blue}\phi_p \equiv 1$, we are only considering the total mass $\color{blue}\|X_t\|$).
-		In general, the higher the order ${\color{red}|p|}$, the more mixing property can be captured by $\color{blue}\phi_p$, and therefore the stronger the smoothing effect.
+		The {\color{PineGreen}order} ${\color{red}|p|}$ is related to the capability of $\color{blue}\phi_p$ capturing the mixing property of the OU particles.
+		In particular, in the case that $\color{red}|p| = 0$, no mixing property can be captured.
+(Since $\color{blue}\phi_0 \equiv 1$, we are only considering the total mass $\color{blue}X_t(\phi_0)=\|X_t\|$).
+		In general, the {\color{PineGreen}higher the order} ${\color{red}|p|}$, the more mixing property can be captured by $\color{blue}\phi_p$, and therefore the {\color{PineGreen}stronger the smoothing effect}.
 \end{block}

### 2021-02-06 supCLT-ind.tex
add supCLT-ind.tex

--- 2021-02-06 supCLT-ind-AMSE.tex
@@
 \end{align}
+%{
+{\bf Zhenyao: give definition for this non-integer power here.}
+%}
 	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
@@
 	The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
+%{
+{\bf ZS: page 4 line 1. I think that “$\leq$” should be “$>$”}
+%}
 	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$;
@@
 
+%{
+{\bf ZS: add some comments about the second Assumption here about its limitation. Why we are not generalizing it to the slowly varying case.}
+%}
+
 \section{Proof of main result}
@@
 \end{lem}
+
+%{
+{\bf ZS: Give the definition of $\mathcal P^+$ here.}
+%}
 
@@
 	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
-	\begin{lem}
-\label{ineq: analysis}
+\begin{lem} \label{ineq: analysis}
 	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
@@
 \end{lem}
+%{
+	{\bf ZS: Give the definition of $x^\beta$ for negative numbers.}
+%}
 \begin{comment}
@@
 \end{align}
+%{
+{\bf ZS: In the second line of (2.9), change ’$T_uf$’ into ’$T_uf_s$’.}
+%}
 	This means that there exists $C_1 >0$ such that for all $t\geq 1$,
@@
 \end{align}
+%{
+{\bf ZS: there is a $1/t$ missed in the above inequality.}
+%}
 	Combining this with \eqref{eq:I:R:3}, we get that

### 2021-02-06 supCLT-ind.tex
update supCLT-ind.tex

--- 2021-02-06 supCLT-ind-AMSE.tex
@@
 \end{align}
+%{
+{\bf Zhenyao: give definition for this non-integer power here. Check page 32 of our EJP paper.}
+%}
 	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
@@
 	The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
+%{
+{\bf (ZS: One reviewer think here that “$\alpha \tilde \beta \leq \kappa_f b$” should be “$\alpha \tilde \beta > \kappa_f b$”. But I think it should be “$\alpha \tilde \beta \leq \kappa_f b$”.)}
+%}
 	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$;
@@
 
+%{
+{\bf ZS: We can add some comments about the second Assumption here about its limitation. 
+	We can also think about why we can't easily generalize our result to slowly varying case. 
+	From remark 1.3 of our EJP paper, $\eta$ is an key parameter there. 
+	What is the role of $\eta$ in our end result? If we replace $\eta + o(1)$ by slowly varying functions, we might loss this parameter, and the result might not hold.
+}
+%}
+
 \section{Proof of main result}
@@
 \end{lem}
+
+%{
+{\bf ZS: Give the definition of $\mathcal P^+$ here. $\mathcal P^+$ is the non-negative element in $\mathcal P$. See the original definition in our EJP paper page 10.}
+%}
 
@@
 \end{lem}
+%{
+	{\bf ZS: Here the non-integer power of negative number should be avoided. When we are applying it in (2.9) below, however, we don't have to use the non-negative values. }
+%}
 \begin{comment}
@@
 \end{align}
+%{
+{\bf ZS: Let's change the second equal sign above as $:=$.}
+%}
 where $T_k$ is the operator defined in 
@@
 \end{align}
+%{
+{\bf ZS: there is a $1/t$ missed in the above inequality. Indeed before the third integration on the right of the first inequality. This is only a typo.}
+%}
 	Combining this with \eqref{eq:I:R:3}, we get that
@@
 \end{align}
+%{
+{\bf ZS: Here $=$ should be $:=$.}
+%}
 	where, for any $t>0$, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
@@
 \end{align}
+%{
+{\bf ZS: Above $\langle f_l, \phi_p\rangle_\varphi$ is missing. This is only a typo.}
+%}
 	Now for each $t>0$, we get

### 2021-02-08 supCLT-ind.tex

--- 2021-02-06 supCLT-ind-AMSE.tex
@@
 \end{align}
+%{
+	Let us explain the non-integer power of the complex numbers used above. 
+	For each $z\in \mathbb C\setminus (-\infty, 0]$, we define $\log z : = \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined so that $z = |z|e^{i \arg z}$. 
+	For each $z\in \mathbb C\setminus (-\infty, 0]$ and $\gamma \in \mathbb R$, we define $z^\gamma := e^{\gamma \log z}$.
+	For each $\gamma \geq 0$, we define $0^\gamma := \lim_{z\to 0, z\in \mathbb C\setminus (-\infty,0]} z^\gamma=\mathbf 1_{\gamma = 0}$.
+%}
+
 	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
@@
 \end{equation}
-	The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
-	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$;
-  and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero while $f_\mathrm c \equiv 0$.
-	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem in this case.
+%{
+	%The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
+	%A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$;
+  %and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero while $f_\mathrm c \equiv 0$.
+	%In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem in this case. 
+	Any  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$. 
+	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem for $f$ if  $\|f_\mathrm s\|_{L^2(\varphi)}> 0, \|f_\mathrm c\|_{L^2(\varphi)} = 0$ and $\|f_\mathrm l\|_{L^2(\varphi)}> 0$.
+%}	
 	We conjectured there that the limit random variables in \eqref{eq:oldResult} for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
@@
 
+%{
+\begin{rem}
+	We mention here that  the branching mechanism $\psi$ considered in this paper can be written in a form of $\psi(z)= -\alpha z + z^{1+\beta} (\eta + \epsilon(z))$ where $\epsilon (z) \to 0$ as $z \to 0$ (See \cite[Remark 1.3]{RenSongSunZhao2019Stable}).
+	It would be interesting to consider the more general cases $\psi(z)= -\alpha z + z^{1+\beta}l(z)$ where $l(z)$ is only assumed to be a slowly varying function. 
+	Note that in this case if $l$ blows up at $0$ (for example $l(z) = \log z$) our result can not hold anymore. 
+	This is simply because the limiting $\alpha$-stable random variable $\zeta^f$ described in \eqref{eq:I:R:3} will cease to make sense. 
+\end{rem}
+
+%}
+
 \section{Proof of main result}
@@
 \label{lem:P:R}
-	For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
+	%{
+	%For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
+	For any $g\in \mathcal P$ there exists non-negative $h \in \mathcal P$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
+	%}
 \end{lem}
@@
 	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
-	\begin{lem}
-\label{ineq: analysis}
+\begin{lem} \label{ineq: analysis}
 	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
 \[
-    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
+%{
+	%|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
+    |(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
     \leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
+    %}
 \]
 \end{lem}
-\begin{comment}
+%{
 \begin{proof}
-   	Note that
+   	Note the desired result holds if $x =0$ or $y = 0$.
+   	So, we can assume $|x|>0$ and $|y|>0$.
+   	Noticing also the symmetry between $x$ and $y$, we can assume without loss of generality that $|x|\geq |y|$.
+   	Also note that $\overline{ z^{1+\beta}} = \overline z^{1+\beta}$ for each $z \in \mathbb C \setminus (-\infty, 0)$ where $\bar z$ represents the conjugation of $z$.
+   	So by taking conjugation, we can verify that 
 \[
-  	\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}
-  	=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}
-  	=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
+	|(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
+	= |(-ix-iy)^{1+\beta}-(-ix)^{1+\beta}-(-iy)^{1+\beta}|.
 \]
-	Using this and continuity, we get that there exists $C_1>0$ such that for all $|y|\geq 1$,
+	This allows us to further assume without loss of generality that $y>0$.
+	Now let us calculate that for each $z\in \mathbb C$, 
+\begin{align}
+  	&\lim_{r \to \infty, r>0}\frac{(r\pm 1)^{1+\beta}-r^{1+\beta} - z}{r^{\beta}}
+  	=\lim_{r\to \infty, r > 0}\frac{(r\pm1)^{1+\beta}-r^{1+\beta}}{r^{\beta}}
+  	\\&=\lim_{r\to \infty,r>0}\big((1\pm r^{-1})^{1+\beta}-1\big)r = \pm(1+\beta).
+\end{align}
+	Taking absolute value and using continuity, we get that for each $z\in \mathbb C$ there exists $C(z)>0$ such that for each $r\geq 1$,
 \[
-  	|(1+y)^{1+\beta}-y^{1+\beta}-1|
-  	\leq C_1 |y|^{\beta}.
+  	|(r\pm 1)^{1+\beta}-r^{1+\beta} - z|
+  	\leq C(z) |r|^{\beta}.
 \]
- 	Note that if $x = 0$ or $y= 0$, then the desired result is trivial.
-	So we only need to consider the case that $x \neq 0$ and $y \neq 0$.
- 	In this case, if $|x|\geq |y|$, we have
+	For any $u\in \mathbb R\setminus\{0\}, r>0$ and $\gamma \geq 0$, from the fact that $\arg (iu r) = \arg(iu)+ \arg(r)$ we can verify $(iur)^{\gamma} = (iu)^{\gamma} r^{\gamma}$.
+Therefore for each $r\geq 1$ we have
+\begin{align}
+	&\big|\big(i(1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big|
+	= \big|i^{1+\beta} \big((r+1)^{1+\beta} - r^{1+\beta} - 1\big)\big|
+	\\&= |(r+1)^{1+\beta}-r^{1+\beta}-1|
+	\leq C(1) |r|^{\beta};
+\end{align}
+and for each $r\leq -1$ we have
+\begin{align}
+	&\big|\big( i (1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big|
+	= \big|(-i)^{1+\beta} \big((-r - 1)^{1+\beta} - (-r)^{1+\beta} - i^{2+2\beta}\big)\big|
+	\\&= |(-r-1)^{1+\beta}-(-r)^{1+\beta}  - i^{2+2\beta}|
+	\leq C(i^{2+2\beta}) |r|^{\beta}.
+\end{align}
+	To summarize, there exists a $C_1>0$ such that for each $r\in \mathbb R$ with $|r|\geq 1$,
 \[
-	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
-	\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)
-	\leq C_1|y||x|^{\beta};
+	\big|\big( i(1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big| \leq C_1 |r|^\beta.
 \]
-	and  if $|x|\leq |y|$, we have
-\[
-	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
-	\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)
-	\leq C_1|x||y|^{\beta}.
-\]
-	Combining the above, we immediately get the desired result.
+	Now we can verify that
+\begin{align}
+	&|(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
+	= \big|y^{1+\beta}\big(i(1+x/y)^{1+\beta}-(ix/y)^{1+\beta}- i^{1+\beta}\big)\big|
+	\\&= |y|^{1+\beta}\big|\big(i(1+x/y)\big)^{1+\beta}-(ix/y)^{1+\beta}-i^{1+\beta}\big|
+	\leq C_1|y||x|^{\beta}.
+	\qedhere
+\end{align}
 \end{proof}
-\end{comment}
+%}
 
@@
         \\R'(t)
-    &=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
+    %{
+    %&=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
+    &:=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
+    %}
         \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
@@
   	&|(-i(T_uf_\mathrm s+t^{\tilde{\beta}-1}T_uf_\mathrm c))^{1+\beta}-(-iT_uf_\mathrm s)^{1+\beta}-(-it^{\tilde{\beta}-1}T_uf_\mathrm c)^{1+\beta}|
-  	\\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
+%{
+  	%\\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
+%}
   	\\&\overset{\text{Lemma \ref{ineq: analysis}}}
@@
 	\overset{\eqref{eq:UOT.15},\eqref{eq:M.13}}\leq\Big| \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du - {}
-	\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du - \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|
+%{
+	\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du
+	%- \eta 
+	- \frac{1}{t} \eta 
+	\int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|
+%}
 \end{multlined}
@@
 	\widetilde{S}(t,r)
-	= (e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0),
+	%{
+	%= 
+	:=
+	(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0),
+	%}
 \end{align}
@@
 	=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + \frac{i\theta_\mathrm c}{(t+r)^{1-\tilde{\beta}}} \frac{X_{t+r}(f_\mathrm c)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + {}
-	\\\quad  i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l) - \sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b} e^{(\alpha - |p|b)(t+r)} e^{-(\alpha - |p|b)u}X_u(\phi_p) }{\|X_{t+r}\|^{1-\tilde{\beta}}}.
+	\\\quad  i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l) - \sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b} 
+	%{
+		%e^{(\alpha - |p|b)(t+r)} e^{-(\alpha - |p|b)u}X_u(\phi_p) 
+		\langle f_\mathrm l, \phi_p\rangle_\varphi e^{(\alpha - |p|b)(t+r)} H_u^p 
+	%}
+	}{\|X_{t+r}\|^{1-\tilde{\beta}}}.
 \end{multlined}

### 2021-02-10 response-ind.tex
add response-ind.tex

\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage{hyperref}
\usepackage{comment}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\title[Response]{\large Response to the referee's comments}
\begin{document}
	\maketitle	
	We are grateful to the referee for the very helpful comments.
	We have incorporated all the comments made by the referee.
	Here are the changes in response to the comments of the first referee.

	\begin{itemize}
		\item ``It is, however, a pity that the branching mechanisms they deal with are not general enough(Assumption 2).''

	\end{itemize}
\begin{enumerate}
	\item ``Page 3: give clearly definition of $z^{1+\beta}$.''

	\item ``Page 5: In Lemma 2.1, introduce the notation $\mathcal P^+$;''

	\item ``page 6, Lemma 2.4: The same as above: define $x^{1+\beta}$, when $x$ is negative.''

	\item ``page 8: change `$T_uf$' into `$T_uf_s$'.''

	\item ``page 8: In the first inequality below (2.9), the last part missed $t^{-1}$.''

\end{enumerate}
	Here are the changes in response to the comments of the second reviewer.
	\begin{enumerate}
		\item ``Page 4. line 1. I think that `$\alpha \widetilde \beta \leq \kappa_f b$' should be `$\alpha \tilde \beta > \kappa_f b$'. ''

		\item ``Page 4, line 3. Correspondingly, `$\alpha \tilde \beta > \kappa_f b$' should be `$\alpha \tilde \beta \leq \kappa_f b$'. ''

		\item ``Page 9, line 15. `$=$' should be `:='.''

		\item ``Page 10, line 16. The term `$\langle f, \phi_p\rangle_{\varphi}$' was missed.''

	\end{enumerate}
\end{document}

### 2021-02-10 supCLT-ind.tex
update supCLT-ind.tex

@@
 	It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
+	%{ new
+    Throughout this paper, $\beta$ and  $\eta$ always stand for the constants in 
+     Assumption \ref{asp: branching mechanism}.
+ %}
 
@@
 	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
-		The eigenfunctions of $L$ consists a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
+		The eigenfunctions of $L$ 
+%{		
+		%consists 
+		consists of 
+		%}
+		a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
 For each $p\in \mathbb Z_+^d$, 
@@
 %{
-	Let us explain the non-integer power of the complex numbers used above. 
+%	Let us explain the non-integer power of the complex numbers used above. 
+	The non-integer power of the complex numbers above is has its usual meaning. For the reader's convenience, we recall the its definition here.
+%}	
 	For each $z\in \mathbb C\setminus (-\infty, 0]$, we define $\log z : = \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined so that $z = |z|e^{i \arg z}$. 
@@
 	For each $\gamma \geq 0$, we define $0^\gamma := \lim_{z\to 0, z\in \mathbb C\setminus (-\infty,0]} z^\gamma=\mathbf 1_{\gamma = 0}$.
-%}
 
@@
 \end{equation}
+	Any  $f \in \mathcal P$ can be decomposed as 
 %{	
-	%The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
-	%A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$;
-  %and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero while $f_\mathrm c \equiv 0$.
-	%In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem in this case. 
-	Any  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$. 
+%$f_s + f_c + f_l$ 
+	$f=f_s + f_c + f_l$ 
+%}	
+	with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$. 
 	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem for $f$ if  $\|f_\mathrm s\|_{L^2(\varphi)}> 0, \|f_\mathrm c\|_{L^2(\varphi)} = 0$ and $\|f_\mathrm l\|_{L^2(\varphi)}> 0$.
-%}	
 	We conjectured there that the limit random variables in \eqref{eq:oldResult} for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
@@
     \frac{ X_t(f) - \mathrm x_t(f)}{\|tX_t\|^{1-\tilde \beta}}
-    \xrightarrow[t\to \infty]{d}\zeta^{f_\mathrm c}.
+    \xrightarrow[t\to \infty]{d}
+    %{
+   % \zeta^{f_\mathrm c}.
+   \zeta^{f_\mathrm c},
+   %}
 \]
@@
 
-%{
 \begin{rem}
@@
 	It would be interesting to consider the more general cases $\psi(z)= -\alpha z + z^{1+\beta}l(z)$ where $l(z)$ is only assumed to be a slowly varying function. 
-	Note that in this case if $l$ blows up at $0$ (for example $l(z) = \log z$) our result can not hold anymore. 
-	This is simply because the limiting $\alpha$-stable random variable $\zeta^f$ described in \eqref{eq:I:R:3} will cease to make sense. 
+%{	
+%Note that in this case if $l$ blows up at $0$ (for example $l(z) = \log z$) our result can not hold anymore. 
+%	This is simply because the limiting $\alpha$-stable random variable $\zeta^f$ described in \eqref{eq:I:R:3} will cease to make sense. 
+For this more general case, the arguments of \cite{RenSongSunZhao2019Stable} and this paper no longer work. It seems that new idea and treatment are needed.
+%}
 \end{rem}
-
-%}
 
@@
 \]
-	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
+%{	
+%Form 
+From
+%}
+	\cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
 the weak limit of $\Upsilon^f_t$.
@@
 \label{lem:P:R}
-	%{
-	%For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
 	For any $g\in \mathcal P$ there exists non-negative $h \in \mathcal P$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
-	%}
 \end{lem}
@@
 \begin{lem} \label{ineq: analysis}
-	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
+	There exists a constant $C>0$ such that for any $x,y \in \mathbb R$,
 \[
-%{
-	%|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
     |(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
     \leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
-    %}
 \]
 \end{lem}
-%{
 \begin{proof}
@@
    	Noticing also the symmetry between $x$ and $y$, we can assume without loss of generality that $|x|\geq |y|$.
-   	Also note that $\overline{ z^{1+\beta}} = \overline z^{1+\beta}$ for each $z \in \mathbb C \setminus (-\infty, 0)$ where $\bar z$ represents the conjugation of $z$.
-   	So by taking conjugation, we can verify that 
+   	Also note that $\overline{ z^{1+\beta}} = \overline z^{1+\beta}$ for each $z \in \mathbb C \setminus (-\infty, 0)$ 
+   	%{
+%   	where $\bar z$ represents the conjugation of $z$.
+   	where $\bar z$ is the complex conjugate of $z$.
+ %  	So by taking conjugation, we can verify that 
+ It is easy is see that
+ %}
 \[
@@
 \]
-	This allows us to further assume without loss of generality that $y>0$.
-	Now let us calculate that for each $z\in \mathbb C$, 
+%{
+%	This allows us to further assume without loss of generality that $y>0$.
+Thus we can further assume without loss of generality that $y>0$.
+%	Now let us calculate that for each $z\in \mathbb C$, 
+	Note that for any $z\in \mathbb C$, 
+	%}
 \begin{align}
@@
 \end{align}
-	Taking absolute value and using continuity, we get that for each $z\in \mathbb C$ there exists $C(z)>0$ such that for each $r\geq 1$,
+%{
+%	Taking absolute value and using continuity, 
+Combining the above with continuity, 
+	%}
+	we get that for each $z\in \mathbb C$ there exists $C(z)>0$ such that for each $r\geq 1$,
 \[
@@
 \]
-	For any $u\in \mathbb R\setminus\{0\}, r>0$ and $\gamma \geq 0$, from the fact that $\arg (iu r) = \arg(iu)+ \arg(r)$ we can verify $(iur)^{\gamma} = (iu)^{\gamma} r^{\gamma}$.
+%{
+%	For any $u\in \mathbb R\setminus\{0\}, r>0$ and $\gamma \geq 0$, from the fact that $\arg (iu r) = \arg(iu)+ \arg(r)$ we can verify $(iur)^{\gamma} = (iu)^{\gamma} r^{\gamma}$.
+One can easily check by definition that $(iur)^{\gamma} = (iu)^{\gamma} r^{\gamma}$ for  any $u\in \mathbb R\setminus\{0\}, r>0$ and $\gamma \geq 0$.
+	%}
 Therefore for each $r\geq 1$ we have
@@
 \end{align}
-	To summarize, there exists a $C_1>0$ such that for each $r\in \mathbb R$ with $|r|\geq 1$,
+%{
+%	To summarize, 
+Summarizing, we have that 	
+%}	
+	there exists a $C_1>0$ such that for each $r\in \mathbb R$ with $|r|\geq 1$,
 \[
@@
 \]
-	Now we can verify that
+%{	
+%Now we can verify that
+Now it follows immediately that
+%}
 \begin{align}
 	&|(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
-	= \big|y^{1+\beta}\big(i(1+x/y)^{1+\beta}-(ix/y)^{1+\beta}- i^{1+\beta}\big)\big|
+	= \big|y^{1+\beta}\big(
+	%{
+	%i(1+x/y)^{1+\beta}
+	(i(1+x/y))^{1+\beta}
+	%}
+	-(ix/y)^{1+\beta}- i^{1+\beta}\big)\big|
 	\\&= |y|^{1+\beta}\big|\big(i(1+x/y)\big)^{1+\beta}-(ix/y)^{1+\beta}-i^{1+\beta}\big|
@@
 \end{proof}
-%}
 
@@
         \\R'(t)
-    %{
-    %&=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
     &:=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
-    %}
         \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
@@
   	&|(-i(T_uf_\mathrm s+t^{\tilde{\beta}-1}T_uf_\mathrm c))^{1+\beta}-(-iT_uf_\mathrm s)^{1+\beta}-(-it^{\tilde{\beta}-1}T_uf_\mathrm c)^{1+\beta}|
-%{
-  	%\\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
-%}
   	\\&\overset{\text{Lemma \ref{ineq: analysis}}}
@@
 	\overset{\eqref{eq:UOT.15},\eqref{eq:M.13}}\leq\Big| \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du - {}
-%{
 	\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du
-	%- \eta 
 	- \frac{1}{t} \eta 
 	\int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|
-%}
 \end{multlined}
@@
 	\widetilde{S}(t,r)
-	%{
-	%= 
 	:=
 	(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0),
-	%}
 \end{align}
@@
 	\\\quad  i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l) - \sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b} 
-	%{
-		%e^{(\alpha - |p|b)(t+r)} e^{-(\alpha - |p|b)u}X_u(\phi_p) 
 		\langle f_\mathrm l, \phi_p\rangle_\varphi e^{(\alpha - |p|b)(t+r)} H_u^p 
-	%}
 	}{\|X_{t+r}\|^{1-\tilde{\beta}}}.
@@
 
+%{ new
+\bigskip
+\noindent
+
+{\bf Acknowledgments:}  We thank the referees for the very helpful comments.
+%
 \begin{thebibliography}{10}

### 2021-02-10 supCLT-ind.tex
update supCLT-ind.tex

@@
 	It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
-	%{ new
     Throughout this paper, $\beta$ and  $\eta$ always stand for the constants in 
      Assumption \ref{asp: branching mechanism}.
- %}
 
@@
 		The eigenfunctions of $L$ 
-%{		
-		%consists 
 		consists of 
-		%}
 		a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
@@
 	The non-integer power of the complex numbers above is has its usual meaning. For the reader's convenience, we recall the its definition here.
+	{\bf This definition is not that common.}
 %}	
@@
 	Any  $f \in \mathcal P$ can be decomposed as 
-%{	
-%$f_s + f_c + f_l$ 
 	$f=f_s + f_c + f_l$ 
-%}	
 	with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$. 
@@
     \xrightarrow[t\to \infty]{d}
-    %{
-   % \zeta^{f_\mathrm c}.
    \zeta^{f_\mathrm c},
-   %}
 \]
@@
 	It would be interesting to consider the more general cases $\psi(z)= -\alpha z + z^{1+\beta}l(z)$ where $l(z)$ is only assumed to be a slowly varying function. 
-%{	
-%Note that in this case if $l$ blows up at $0$ (for example $l(z) = \log z$) our result can not hold anymore. 
-%	This is simply because the limiting $\alpha$-stable random variable $\zeta^f$ described in \eqref{eq:I:R:3} will cease to make sense. 
 For this more general case, the arguments of \cite{RenSongSunZhao2019Stable} and this paper no longer work. It seems that new idea and treatment are needed.
-%}
 \end{rem}
@@
 \]
-%{	
-%Form 
 From
-%}
 	\cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
@@
    	Also note that $\overline{ z^{1+\beta}} = \overline z^{1+\beta}$ for each $z \in \mathbb C \setminus (-\infty, 0)$ 
-   	%{
-%   	where $\bar z$ represents the conjugation of $z$.
    	where $\bar z$ is the complex conjugate of $z$.
- %  	So by taking conjugation, we can verify that 
  It is easy is see that
- %}
 \[
@@
 \]
-%{
-%	This allows us to further assume without loss of generality that $y>0$.
 Thus we can further assume without loss of generality that $y>0$.
-%	Now let us calculate that for each $z\in \mathbb C$, 
 	Note that for any $z\in \mathbb C$, 
-	%}
 \begin{align}
@@
 \end{align}
-%{
-%	Taking absolute value and using continuity, 
-Combining the above with continuity, 
-	%}
-	we get that for each $z\in \mathbb C$ there exists $C(z)>0$ such that for each $r\geq 1$,
+	Combining the above with continuity, we get that for each $z\in \mathbb C$ there exists $C(z)>0$ such that for each $r\geq 1$,
 \[
@@
 \]
-%{
-%	For any $u\in \mathbb R\setminus\{0\}, r>0$ and $\gamma \geq 0$, from the fact that $\arg (iu r) = \arg(iu)+ \arg(r)$ we can verify $(iur)^{\gamma} = (iu)^{\gamma} r^{\gamma}$.
 	One can easily check by definition that $(iur)^{\gamma} = (iu)^{\gamma} r^{\gamma}$ for  any $u\in \mathbb R\setminus\{0\}, r>0$ and $\gamma \geq 0$.
-	%}
 	Therefore for each $r\geq 1$ we have
@@
 \end{align}
-%{
-%	To summarize, 
-Summarizing, we have that 	
-%}	
-	there exists a $C_1>0$ such that for each $r\in \mathbb R$ with $|r|\geq 1$,
+Summarizing, we have that there exists a $C_1>0$ such that for each $r\in \mathbb R$ with $|r|\geq 1$,
 \[
@@
 \]
-%{	
-%Now we can verify that
 Now it follows immediately that
-%}
 \begin{align}
@@
 	= \big|y^{1+\beta}\big(
-	%{
-	%i(1+x/y)^{1+\beta}
 	(i(1+x/y))^{1+\beta}
-	%}
 	-(ix/y)^{1+\beta}- i^{1+\beta}\big)\big|
@@
 
-%{ new
+{\bf Lets change the form of Acknowledgments here.}
 \bigskip
@@
 {\bf Acknowledgments:}  We thank the referees for the very helpful comments.
-%
 \begin{thebibliography}{10}

### 2021-02-10 supCLT-ind.tex

@@
 %{
-%	Let us explain the non-integer power of the complex numbers used above. 
-	The non-integer power of the complex numbers above is has its usual meaning. For the reader's convenience, we recall the its definition here.
-	{\bf This definition is not that common.}
+%	The non-integer power of the complex numbers above is has its usual meaning. For the reader's convenience, we recall the its definition here.
+	Let us recall the definition of the non-integer power of complex numbers here.
 %}	
@@
 
-{\bf Lets change the form of Acknowledgments here.}
-\bigskip
-\noindent
-
-{\bf Acknowledgments:}  We thank the referees for the very helpful comments.
+%{
+%\bigskip
+%\noindent
+% {\bf Acknowledgments:}  
+\subsection*{Acknowledgment}
+We thank the referees for the very helpful comments.
+%}
 \begin{thebibliography}{10}

### 2021-02-10 response-ind.tex
update response-ind.tex

@@
 
+		\emph{We agree. We addressed this in the Remark 1.3.}
+
 	\end{itemize}
@@
 
+	\emph{We added the definition of $z^{1+\beta}$ after equation (1.2).}
+
 	\item ``Page 5: In Lemma 2.1, introduce the notation $\mathcal P^+$;''
+
+	\emph{We replaced ``$h\in \mathcal P^+$'' with ``non-negative $f\in \mathcal P$'' in the Lemma 2.1.}
 
@@
 
+	\emph{In this paper, the non-integer power for negative numbers are not defined. We changed our statement in Lemma 2.4 and added a proof.}
+
 	\item ``page 8: change `$T_uf$' into `$T_uf_s$'.''
 
+	\emph{Changed as suggested.}
+
 	\item ``page 8: In the first inequality below (2.9), the last part missed $t^{-1}$.''
+
+	\emph{This is a typo. We added $t^{-1}$ back.}
 
@@
 
+		\emph{We changed our statement there to resolve this ambiguity. See lines 9-11 on page 4.}
+
 		\item ``Page 4, line 3. Correspondingly, `$\alpha \tilde \beta > \kappa_f b$' should be `$\alpha \tilde \beta \leq \kappa_f b$'. ''
+
+		\emph{Similar to the previous one.}
 
@@
 
+		\emph{Changed as suggested.}
+
 		\item ``Page 10, line 16. The term `$\langle f, \phi_p\rangle_{\varphi}$' was missed.''
+
+		\emph{This is a typo. We added it back.}
 

### 2021-02-11 supCLT-ind.tex
add supCLT-ind.tex

@@
 \email{yxren@math.pku.edu.cn}
-\thanks{Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF}
+\thanks{Yan-Xia Ren is supported in part by NSFC 
+%YX (Grant Nos. 11671017  and 11731009) 
+(Grant Nos. 11731009 and 12071011) 
+and LMEQF}
 \address{
@@
 \begin{abstract}
-	This paper is a continuation of our recent paper (Elect.
-J.
-Probab.
-\textbf{24} (2019), no.
-141) and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
+	This paper is a continuation of our recent paper 
+%YX (Elect. J. Probab. \textbf{24} (2019), no. 141) 
+(Electron. J. Probab. \textbf{24} (2019), no. 141)
+and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
 	In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth in three different regimes.
@@
 	\emph{Stable central limit theorems for super Ornstein-Uhlenbeck processes},
-	Elect. J Probab., \textbf{24} (2019), no. 141, 1--42.
+%YX	Elect. J Probab., 
+ Electron. J. Probab.,
+\textbf{24} (2019), no. 141, 1--42.
 

### 2021-02-11 supCLT-ind.tex
update supCLT-ind.tex

--- 2021-02-10 supCLT-ind.tex
@@
 \email{yxren@math.pku.edu.cn}
-\thanks{Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF}
+\thanks{Yan-Xia Ren is supported in part by NSFC 
+(Grant Nos. 11731009 and 12071011) 
+and LMEQF}
 \address{
@@
 \begin{abstract}
-	This paper is a continuation of our recent paper (Elect.
-J.
-Probab.
-\textbf{24} (2019), no.
-141) and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
+	This paper is a continuation of our recent paper 
+(Electron. J. Probab. \textbf{24} (2019), no. 141)
+and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
 	In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth in three different regimes.
@@
 \end{align}
-%{
-%	The non-integer power of the complex numbers above is has its usual meaning. For the reader's convenience, we recall the its definition here.
 	Let us recall the definition of the non-integer power of complex numbers here.
-%}	
 	For each $z\in \mathbb C\setminus (-\infty, 0]$, we define $\log z : = \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined so that $z = |z|e^{i \arg z}$.
@@
 
-%{
-%\bigskip
-%\noindent
-% {\bf Acknowledgments:}  
 \subsection*{Acknowledgment}
 We thank the referees for the very helpful comments.
-%}
 \begin{thebibliography}{10}
@@
 	\emph{Stable central limit theorems for super Ornstein-Uhlenbeck processes},
-	Elect. J Probab., \textbf{24} (2019), no. 141, 1--42.
+ Electron. J. Probab.,
+\textbf{24} (2019), no. 141, 1--42.
 

### 2021-02-11 response-ind.tex
update response-ind.tex

@@
 
-\title[Response]{\large Response to the referee's comments}
+\title[Response]{\large Response to the referees' comments}
 \begin{document}
 	\maketitle	
-	We are grateful to the referee for the very helpful comments.
-	We have incorporated all the comments made by the referee.
+	We are grateful to the referees for the very helpful comments.
+	We have incorporated all the comments made by the referees.
 	Here are the changes in response to the comments of the first referee.
@@
 
-		\emph{We agree. We addressed this in the Remark 1.3.}
+		\emph{We agree. We addressed this in  Remark 1.3.}
 
@@
 
-	\emph{In this paper, the non-integer power for negative numbers are not defined. We changed our statement in Lemma 2.4 and added a proof.}
+	\emph{In this paper, 
+	the non-integer power for negative numbers is not defined. 
+	We changed our statement in Lemma 2.4 and added a proof.}
 
@@
 \end{enumerate}
-	Here are the changes in response to the comments of the second reviewer.
+	Here are the changes in response to the comments of the second referee.
 	\begin{enumerate}
@@
 
-		\emph{This is a typo. We added it back.}
+		\emph{This is a typo. We added it.}
 

### 2021-04-23 Proof_AMSE/supCLT-ind-AMSE3.tex
add supCLT-ind-AMSE3.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%            NOTE: The content in this template, including title, authors' name and affiliation, and etc.
%%                 is ONLY a sample for the author's guidance.
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{amse-new}

\numberwithin{equation}{section} %%% Equations numbered by section. If you don't want it, please delete it.

\begin{document}

 \PageNum{1}
 \Volume{201x}{Sep.}{x}{x}
 \OnlineTime{August 15, 201x}
 \DOI{0000000000000000}
 \EditorNote{Received x x, 201x, accepted x x, 201x}

\abovedisplayskip 6pt plus 2pt minus 2pt \belowdisplayskip 6pt
plus 2pt minus 2pt
%%%%%%%%%%%%%%%%
\def\vsp{\vspace{1mm}}
\def\th#1{\vspace{1mm}\noindent{\bf #1}\quad}
\def\proof{\vspace{1mm}\noindent{\it Proof}\quad}
\def\no{\nonumber}
\newenvironment{prof}[1][Proof]{\noindent\textit{#1}\quad }
{\hfill $\Box$\vspace{0.7mm}}
\def\q{\quad} \def\qq{\qquad}
\allowdisplaybreaks[4]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%-------------------       Beginning of  Author's Definitions       -------------------%%
%%                     Note: You may add your own definitions here.

%%-------------------         the end of  Author's Definitions           -------------------%%

\AuthorMark{Surname1 F1. and Surname2 F2. }                             %%%  appear on the head of even pages  %%%

\TitleMark{A Template for Journal}  %%% Running Title, appear on the head of odd pages  %%%

\title{A Template for Journal        %%%   Main Title of your paper  %%%
\footnote{Supported by \ldots (Grant No. \ldots)}}                  %%%   the Fund which you are supported by  %%%

\author{Firstname1 \uppercase{Surname1}}             %%%  1st Author's information   %%%
    {Address\\
    E-mail\,$:$ }

\author{Firstname2 SURNAME2}     %%%  2nd Author's info, if exists, or you may delete this part directly  %%%
    {Address\\
    E-mail\,$:$  }

\maketitle%

\Abstract{Please make sure NO reference number in your Abstract since it is misunderstood independent of full text.}      % the abstract

\Keywords{Aaaa, bbbb, cccc}        % the keywords

\MRSubClass{05B05, 05B25, 20B25}      % MR(2000) Subject Classification

%\baselineskip 15pt

\section{Introduction}

\subsection{A Subsection}

Please make sure that your paper contains correct reference
sequence (please resort them according to its {\it alphabetical
order} and make sure that each bibliographical item is labelled
and that these items are recalled using the command
\verb|\cite{...}|, such as \cite{LT}, and \cite{HB,T1,T2,T3})

All equations, theorems, definitions, lemmas, propositions,
corollaries, examples, remarks etc. would be better to be numbered
consecutively and unrepeatedly within each section. For example,
Definition 2.1, Lemma 2.2, Theorem 2.3 \ldots.

Use \verb|\label| and \verb|\ref| or \verb|\eqref| to
automatically cross-reference sections, equations, theorems and
theorem-like environments, tables, figures, etc.

\begin{theorem}[\cite{HB}]\label{th:1.1} %Theorem 1.1 could be recalled by using Theorem \ref{th:1.1}
The statements of theorems, lemmas, definitions, propositions,
corollaries, conjectures, etc. are set in italics, by using
\begin{verbatim}
\begin{theorem/lemma/definition/proposition/corollary/conjecture}
\end{theorem/lemma/definition/proposition/corollary/conjecture}.
\end{verbatim}
\end{theorem}

\begin{prof}  %you can also use the environment \begin{proof}\end{proof}
Observe that
\begin{align}\label{E:1.1}
AAAAAAAAAA &= BBBBBBBBBBB\nonumber \\
           &\quad + CCCCCCCCCC\nonumber \\
           &= DDDDDDDDDDDDD.
\end{align}
Now apply induction on $n$ to \eqref{E:1.1}\ldots
\end{prof}

\begin{remark}\label{re:1.2}
Remarks, examples, problems, etc. are set in roman type.
\end{remark}

\subsection{Table}

\begin{table}
\begin{tabular}{|c|c|c|l|c|}
\hline $P(x)$ & $i$& $(e(1),e(2),e(4))$ & $(e(3),e(6),e(12),e(24))$ & $T(E)$ \\
\hline $P_1$  &    & & &$\emptyset$ \\
\hline $P_2$  & 4  & & $(1,1,1,0)\rightarrow(0,0,0,1)$ &2\\
\hline $P_3$  & 2  & &$(1,1,1,0)\rightarrow(0,0,2,0)$ &1\\
\hline $P_4$  & 2  & $(0,1,1)\rightarrow(1,2,0)$ & &1\\
\hline $P_5$  & 2  & $(0,1,1)\rightarrow(1,2,0)$ &$(1,1,1,0)\rightarrow(0,0,0,1)$ &$1,2$\\
\hline $P_6$  & 6  & $(0,1,1)\rightarrow(1,2,0)$ &$(1,1,1,0)\rightarrow(2,2,0,0)$ &1\\
\hline $P_7$  & 3  & $(0,1,1)\rightarrow(1,0,1)$ &$(1,1,1,0)\rightarrow(2,0,1,0)$ &0\\
\hline $P_8$  & 3  & $(0,1,1)\rightarrow(2,1,0)$ &$(1,1,1,0)\rightarrow(2,0,1,0) \rightarrow(3,1,0,0)$ &$0,1$\\
\hline
\end{tabular}
\caption{Aaa bbb ccc\label{tab}}
\end{table}

\subsection{Figure}

%\centerline{\includegraphics[scale=1.2]{actmark.eps}}
%\centerline{\small Figure 1\quad Journal mark}

\acknowledgements{\rm We thank the referees for their time and
comments. }

\begin{thebibliography}{99}

\bibitem{HB} %% Books %% surname(s), initial(s), title, publisher, place of publication, year
Huppert, B., Blackburn, N.: Finite Groups II, Springer-Verlag, New
York, 1982

\bibitem{LT} %% Journals %% surname(s), initial(s), article, journal, volume, relevant page numbers, year
Lorenzini, D., Tucker, T. J.: The equations and the method of
Chabauty--Coleman. \emph{Invent. Math.}, \textbf{148}, 1--46
(2002)

\bibitem{T1}
Test

\bibitem{T2}
Test

\bibitem{T3}
Test

\end{thebibliography}

\end{document}

### 2021-04-23 Proof_AMSE/supCLT-ind-AMSE3.tex

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%
-%%            NOTE: The content in this template, including title, authors' name and affiliation, and etc.
-%%                 is ONLY a sample for the author's guidance.
-%%
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \documentclass{amse-new}
-
-\numberwithin{equation}{section} %%% Equations numbered by section. If you don't want it, please delete it.
-
+%%---------- Beginning of Author's packages --------%%
+\usepackage{mathtools}
+\mathtoolsset{showonlyrefs}
+%%---------- the end of Author's packages ----------%%
+\numberwithin{equation}{section}
 \begin{document}
-
  \PageNum{1}
@@
  \EditorNote{Received x x, 201x, accepted x x, 201x}
-
 \abovedisplayskip 6pt plus 2pt minus 2pt \belowdisplayskip 6pt
 plus 2pt minus 2pt
-%%%%%%%%%%%%%%%%
 \def\vsp{\vspace{1mm}}
@@
 \allowdisplaybreaks[4]
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%-------------------       Beginning of  Author's Definitions       -------------------%%
-%%                     Note: You may add your own definitions here.
-
+\theoremstyle{definition}
+\newtheorem{asp}{Assumption}
 %%-------------------         the end of  Author's Definitions           -------------------%%
 
-\AuthorMark{Surname1 F1. and Surname2 F2. }                             %%%  appear on the head of even pages  %%%
+\AuthorMark{Ren Y.-X., Song R., Sun Z. and Zhao J.}
+\TitleMark{Stable CLT for super-OU processes, II}
 
-\TitleMark{A Template for Journal}  %%% Running Title, appear on the head of odd pages  %%%
+\title{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II
+\footnote{Yan-Xia Ren is supported in part by NSFC (Grant Nos.
+11731009 and 12071011) and LMEQF.
+Renming Song is supported in part by Simons Foundation (\#429343, Renming Song).
+Zhenyao Sun is the corresponding author.}}
 
-\title{A Template for Journal        %%%   Main Title of your paper  %%%
-\footnote{Supported by \ldots (Grant No. \ldots)}}                  %%%   the Fund which you are supported by  %%%
+\author{Yan-Xia \uppercase{Ren}}             %%%  1st Author's information   %%%
+    {LMAM School of Mathematical Sciences \& Center for Statistical Science, Peking University, \\
+	    Beijing 100871, P. R. China \\
+    E-mail\,$:$ yxren@math.pku.edu.cn}
 
-\author{Firstname1 \uppercase{Surname1}}             %%%  1st Author's information   %%%
-    {Address\\
-    E-mail\,$:$ }
+    \author{Renming \uppercase{Song}} 
+    {Department of Mathematics, University of Illinois at Urbana-Champaign, \\
+  	Urbana, IL 61801, USA\\
+    E-mail\,$:$ rsong@illinois.edu}
 
-\author{Firstname2 SURNAME2}     %%%  2nd Author's info, if exists, or you may delete this part directly  %%%
-    {Address\\
-    E-mail\,$:$  }
+    \author{Zhenyao \uppercase{Sun}} 
+    {School of Mathematics and Statistics, Wuhan University, \\
+  	Wuhan, Hubei 430072, P. R. China \\
+	Faculty of Industrial Engineering and Management, Technion, \\
+	Haifa 3200003, Israel\\
+    E-mail\,$:$ zhenyao.sun@gmail.com}
+
+    \author{Jianjie \uppercase{Zhao}} 
+    {School of Mathematical Sciences, Peking University,\\
+  	Beijing 100871, P. R. China\\
+    E-mail\,$:$ zhaojianjie@pku.edu.cn}
 
@@
 
-\Abstract{Please make sure NO reference number in your Abstract since it is misunderstood independent of full text.}      % the abstract
+\Abstract{
+	This paper is a continuation of our recent paper (Electron.
+J.
+Probab.
+\textbf{24} (2019), no.
+141) and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
+	In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth in three different regimes.
+	However, we were not able to prove central limit theorems for $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
+	In this note, we show that the limiting stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
+}
 
-\Keywords{Aaaa, bbbb, cccc}        % the keywords
+\Keywords{Superprocesses, Ornstein-Uhlenbeck processes, stable distribution, central limit theorem, law of large numbers, branching rate regime}
 
-\MRSubClass{05B05, 05B25, 20B25}      % MR(2000) Subject Classification
+\MRSubClass{60J68, 60F05}
 
@@
 
-\section{Introduction}
+\section{Introduction and main result}
+\label{subsec:M}
+	Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
+	Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
+\begin{align}
+  	Lf(x)
+  	= \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
+  	\quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
+\end{align}
+	where $\sigma > 0$ and $b > 0$ are constants.
+	Let $\psi$ be a function on $\mathbb R_+$ of the form
+\begin{align}
+  	\psi(z)
+  	=- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(\mathrm dy),
+  	\quad  z \in \mathbb R_+,
+\end{align}
+	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)\pi(\mathrm dy)< \infty$.
+	$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
+	Denote by $\mathcal M(\mathbb R^d)$ ($\mathcal M_c(\mathbb R^d)$) the space of all finite Borel measures (of compact support) on $\mathbb R^d$.
+	Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ ($\mathcal B(\mathbb R^d, \mathbb R_+)$) the space of all $\mathbb R$-valued ($\mathbb R_+$-valued)
+	Borel functions on $\mathbb R^d$.
+	For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)= \int f(x)\mu(\mathrm dx)$ and $\langle f, g\rangle = \int f(x)g(x) \mathrm dx$ whenever the integrals make sense.
+	We say a real-valued Borel function $f$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty. $
+	For any $\mu \in \mathcal M(\mathbb R^d)$, we write $\|\mu\| = \mu(1)$.
+	For any $\sigma$-finite signed measure $\mu$, denote by $|\mu|$ the total variation measure of $\mu$.
 
-\subsection{A Subsection}
+	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a \emph{$(\xi, \psi)$-superprocess}, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
+\begin{align}
+  	\label{eq: def of V_t}
+  	\mathbb{P}_{\mu}[e^{-X_t(f)}]
+  	= e^{-\mu(V_tf)},
+   	\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
+\end{align}
+	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
+\begin{align}
+  	V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) ) \mathrm ds\Big]
+	= \Pi_x [f(\xi_t)],
+	\quad x\in \mathbb R^d, t\geq 0.
+\end{align}	
+	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses,Li2011Measure-valued} for instance.
 
-Please make sure that your paper contains correct reference
-sequence (please resort them according to its {\it alphabetical
-order} and make sure that each bibliographical item is labelled
-and that these items are recalled using the command
-\verb|\cite{...}|, such as \cite{LT}, and \cite{HB,T1,T2,T3})
+	There have been many central limit theorem type results for branching processes, branching diffusions and superprocesses, under the second moment condition.
+	See \cite{AdamczakMilos2015CLT, AsmussenHering1983Branching, Athreya1969Limit,Athreya1969LimitB,Athreya1971Some, Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved, KestenStigum1966Additional,KestenStigum1966A-limit,Milos2012Spatial,RenSongZhang2014Central,RenSongZhang2014CentralB, RenSongZhang2015Central,RenSongZhang2017Central}.
+	For a detailed literature review, see \cite[Section 1.1]{RenSongSunZhao2019Stable}.
+	There are also  central  limit theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment.
+	For earlier papers, see \cite{Asmussen76Convergence, Heyde1971Some}. 	
+	Recently, Marks and 
+	%Milo\'s
+	Mi{\l}o\'s
+	\cite{MarksMilos2018CLT} established some spatial central limit theorems for supercritical branching OU processes with a special stable offspring distribution.
+	In \cite{RenSongSunZhao2019Stable}, we established stable central limit theorems for super-OU processes $X$ with branching mechanisms $\psi$ satisfying the following two assumptions.
 
-All equations, theorems, definitions, lemmas, propositions,
-corollaries, examples, remarks etc. would be better to be numbered
-consecutively and unrepeatedly within each section. For example,
-Definition 2.1, Lemma 2.2, Theorem 2.3 \ldots.
+\begin{asp}[Grey's condition]
+\label{asp: Greys condition}
+	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1} \mathrm dz < \infty$.
+\end{asp}
 
-Use \verb|\label| and \verb|\ref| or \verb|\eqref| to
-automatically cross-reference sections, equations, theorems and
-theorem-like environments, tables, figures, etc.
+\begin{asp}
+\label{asp: branching mechanism}
+  	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
+\begin{align}
+    \int_{(1,\infty)}y^{1+\beta +\delta}\Big|\pi(\mathrm dy)-\frac{\eta \mathrm dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
+\end{align}
+	for some $\delta > 0$.
+\end{asp}
 
-\begin{theorem}[\cite{HB}]\label{th:1.1} %Theorem 1.1 could be recalled by using Theorem \ref{th:1.1}
-The statements of theorems, lemmas, definitions, propositions,
-corollaries, conjectures, etc. are set in italics, by using
-\begin{verbatim}
-\begin{theorem/lemma/definition/proposition/corollary/conjecture}
-\end{theorem/lemma/definition/proposition/corollary/conjecture}.
-\end{verbatim}
+	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
+$
+	D
+	:=\{\exists t\geq 0~\text{such that}~ \|X_t\| =0 \}
+$
+	is non-trivial with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$.
+	It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
+    Throughout this paper, $\beta$ and  $\eta$ always stand for the constants in
+     Assumption \ref{asp: branching mechanism}.
+
+	We now recall some notation and basic facts from \cite{RenSongSunZhao2019Stable}.
+	We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
+	Define $P^{\alpha}_t f(x) := e^{\alpha t} P_t f(x) = \Pi_x [e^{\alpha t}f(\xi_t)]$ for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
+	It is known that $\mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)$ for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
+	The OU process $\xi$ has an invariant probability on $\mathbb R^d$:
+\begin{align}
+  	\varphi(x)\mathrm dx
+  	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx.
+\end{align}
+	Let $L^2(\varphi)$ be the Hilbert space with inner product
+\begin{align}
+  	\langle f_1, f_2 \rangle_{\varphi}
+  	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) \mathrm dx, \quad f_1,f_2 \in L^2(\varphi).
+\end{align}
+	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
+	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
+		The eigenfunctions of $L$
+		consists of
+		a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
+For each $p\in \mathbb Z_+^d$,
+$\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$, where $|p|:= \sum_{k=1}^d p_k$.
+	For each function $f\in L^2(\varphi)$, define the order of $f$ as
+$\kappa_f
+  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}$
+with the convention that $\inf\emptyset=\infty.$
+
+	For $p\in \mathbb{Z}_+^d$, define
+$H_t^p
+    	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.$
+	For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
+	We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that
+	for any
+	$\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
+	Furthermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
+	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
+We will write $H^0_t$ and $H^0_\infty$ as $H_t$ and $H_\infty$, respectively.
+
+	Denote by $\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
+$\mathcal{P}
+  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.$
+	Define
+	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \},
+		~
+	\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
+	$ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
+	Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
+	Define a semigroup
+\begin{align}\label{e:Tt}
+	T_t f
+	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
+	\quad t\geq 0, f\in \mathcal P,
+\end{align}
+	and a family of functionals
+\begin{align}\label{eq:M.13}
+	m_t[f]
+	:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx,
+	\quad 0 \leq t< \infty, f\in \mathcal P.
+\end{align}
+	Let us recall the definition of the non-integer power of complex numbers here.
+	For each $z\in \mathbb C\setminus (-\infty, 0]$, we define $\log z : = \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined so that $z = |z|e^{i \arg z}$.
+	For each $z\in \mathbb C\setminus (-\infty, 0]$ and $\gamma \in \mathbb R$, we define $z^\gamma := e^{\gamma \log z}$.
+	For each $\gamma \geq 0$, we define $0^\gamma := \lim_{z\to 0, z\in \mathbb C\setminus (-\infty,0]} z^\gamma=\mathbf 1_{\gamma = 0}$.
+
+	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
+\begin{equation} \label{eq:I:R:3}
+\begin{minipage}{0.9\textwidth}
+	for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,$ where
+\begin{equation}
+	m[f]
+	:=
+\begin{cases}
+	\lim_{t\to \infty} m_t[f], &
+	f \in \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l, \\
+	\lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l.
+\end{cases}
+\end{equation}
+\end{minipage}
+\end{equation}
+		For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
+	We also proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
+\begin{equation}\label{eq:oldResult}
+\begin{minipage}{0.9\textwidth}
+	if $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb {\widetilde P}_\mu$,
+\[
+\begin{split}
+	&e^{-\alpha t}\|X_t\| \xrightarrow[t\to \infty]{\text{a.s.}} \widetilde{H}_\infty;
+	\quad \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s};
+	\\&\frac{X_t(f_\mathrm c)}{\|t X_t\|^{1-\tilde \beta} } \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm c};
+	\quad\frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
+	\xrightarrow[t\to \infty]{d} \zeta^{-f_\mathrm l},
+\end{split}
+\]
+	where $\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
+	$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; and
+\[
+	\mathrm x_t(f)
+	:= \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty},
+	\quad t\geq 0, f\in \mathcal P.
+\]
+\end{minipage}
+\end{equation}
+	Any  $f \in \mathcal P$ can be decomposed as
+	$f=f_s + f_c + f_l$
+	with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$.
+	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem for $f$ if  $\|f_\mathrm s\|_{L^2(\varphi)}> 0, \|f_\mathrm c\|_{L^2(\varphi)} = 0$ and $\|f_\mathrm l\|_{L^2(\varphi)}> 0$.
+	We conjectured there that the limit random variables in \eqref{eq:oldResult} for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
+	Once this asymptotic independence is established, a central limit theorem  for $ X_t(f)$ for all $f\in  \mathcal P$ would follow.
+
+	The main purpose of this note is to show that the limit  random variables in \eqref{eq:oldResult} are independent.
+
+\begin{theorem}
+\label{thm:M}
+	If $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb {\widetilde P}_\mu$,
+\begin{align} \label{eq:M.1}
+	&S(t):=
+	\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}, \frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
+	\Bigg)
+	\\&\xrightarrow[t\rightarrow \infty]{d}(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
+\end{align}
+	where $\mathrm x_t(f_\mathrm l)$ is defined in
+	\eqref{eq:oldResult}
+	with $f$ replaced with $f_\mathrm l$;
+	$\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
+	$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3};
+	$\widetilde H_\infty$,  $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
 \end{theorem}
 
-\begin{prof}  %you can also use the environment \begin{proof}\end{proof}
-Observe that
-\begin{align}\label{E:1.1}
-AAAAAAAAAA &= BBBBBBBBBBB\nonumber \\
-           &\quad + CCCCCCCCCC\nonumber \\
-           &= DDDDDDDDDDDDD.
+	As a corollary of this theorem, we get  central limit theorems for $X_t(f)$ for all $f\in \mathcal P$.
+
+\begin{corollary}
+	Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P$.
+	Let  $f=f_\mathrm s + f_\mathrm c + f_\mathrm l$ be the unique decomposition of $f$ with $f_\mathrm s \in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$.
+	Then under $\widetilde {\mathbb{P}}_{\mu}$, it holds that
+\begin{enumerate}
+\item
+	if $f_\mathrm c\equiv 0$, then
+\[
+    \frac{ X_t(f) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}
+    \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l},
+\]
+	where $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are independent;
+\item
+if $f_\mathrm c\not\equiv 0$, then
+\[
+    \frac{ X_t(f) - \mathrm x_t(f)}{\|tX_t\|^{1-\tilde \beta}}
+    \xrightarrow[t\to \infty]{d}
+   \zeta^{f_\mathrm c},
+\]
+	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variable described in \eqref{eq:I:R:3}.
+\end{enumerate}
+\end{corollary}
+
+\begin{remark}
+	We mention here that  the branching mechanism $\psi$ considered in this paper can be written in a form of $\psi(z)= -\alpha z + z^{1+\beta} (\eta + \epsilon(z))$ where $\epsilon (z) \to 0$ as $z \to 0$ (See \cite[Remark 1.3]{RenSongSunZhao2019Stable}).
+	It would be interesting to consider the more general cases $\psi(z)= -\alpha z + z^{1+\beta}l(z)$ where $l(z)$ is only assumed to be a slowly varying function.
+For this more general case, the arguments of \cite{RenSongSunZhao2019Stable} and this paper no longer work. It seems that new idea and treatment are needed.
+\end{remark}
+
+\section{Proof of main result}
+\label{proofs of main results}
+	We first make some preparations before proving Theorem \ref{thm:M}.
+	For every $t\geq 0$ and $f\in \mathcal P$, define
+\[
+  	Z_t f
+  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
+  	\quad \Upsilon^f_t
+   	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
+\]
+From
+	\cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of
+the weak limit of $\Upsilon^f_t$.
+	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
+	The following Lemma \ref{lem:P:R} can be proved using
+an argument similar to that used in the proof of
+	\cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
+\begin{lemma}
+\label{lem:P:R}
+	For any $g\in \mathcal P$ there exists non-negative $h \in \mathcal P$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
+\end{lemma}
+
+	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable},
+with Lemma \ref{lem:P:R} replacing the role of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}.
+	Let $(\mathscr F_t)_{t\geq 0}$ be the natural filtration of $X$.
+	\begin{proposition}
+\label{thm:Key}
+	For any $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
+\[
+	\mathbb P_\mu
+	\Big[ \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  \big|\Big]
+	\leq C e^{- \delta t}.
+\]
+\end{proposition}
+
+	The following generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of  Theorem \ref{thm: II}, a special case of Theorem \ref{thm:M}.
+	Note that the constants $C$ and $\delta$ in the next result depend only on $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, do not depend on $n_1, n_2, f_j, g_j$ and $t$ (as long as $t\geq n_1+1$).
+
+\begin{proposition} \label{cor:MI}
+	For any  $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exist $C,\delta>0$ such that for all $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1+1$, we have
+\begin{equation}
+\label{32corollary}
+	\Big|\mathbb{\widetilde{P}}_{\mu}\Big[  \Big(\prod_{k=0}^{n_1}e^{i \Upsilon^{f_k}_{t-k-1}}\Big)  \Big( \prod_{k=0}^{n_2}e^{i \Upsilon^{g_k}_{t+k} } \Big) \Big]  -  \Big(\prod_{k=0}^{n_1} e^{\langle Z_1f_k, \varphi\rangle}\Big) \Big(\prod_{k=0}^{n_2} e^{\langle Z_1g_k, \varphi\rangle}\Big) \Big|
+	\leq C e^{-\delta (t-n_1)}.
+\end{equation}
+\end{proposition}
+\begin{prof}
+	In this proof, we fix $f,g\in \mathcal P$, $\mu\in \mathcal M_c(\mathbb R^d)$, $n_1,n_2 \in \mathbb Z_+$, $(f_j)_{j=0}^{n_1}\subset \overline{\mathcal P}_f$, $(g_j)_{j=0}^{n_2}\subset \overline{\mathcal P}_g$ and $t\geq n_1 + 1$.
+ 	For any $k_1 \in \{-1,0,\dots,n_1\}$ and $k_2 \in \{-1,0,\dots,n_2\}$,  define
+\[
+    a_{k_1,k_2}
+    :=  \mathbb{\widetilde{P}}_{\mu}\Big[ \Big(\prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big)  \Big(\prod_{j=0}^{k_2}e^{i\Upsilon_{t+j}^{g_j}}\Big) \Big] \Big(\prod_{j=0}^{k_1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=k_2+1}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big),
+\]
+	where we used the convention that $\prod_{j=0}^{-1} =1.$
+  	Then for all  $k_2 \in \{0,\dots,n_2\}$, we have
+\begin{equation}
+\label{eq:MI.1}
+\begin{multlined}
+	 a_{-1,k_2} - a_{-1,k_2-1}
+	 = \frac{1}{\mathbb{P}_{\mu}(D^c)}  \Big(\prod_{j=k_2+1}^{n_2}e^{\langle Z_1g_j, \varphi\rangle}\Big) \times {}
+	\\ \mathbb{P}_{\mu}\Big[\Big(\prod_{j=0}^{n_1}e^{i\Upsilon_{t-j-1}^{f_j}}\Big)\Big(\prod_{j=0}^{k_2-1} e^{i\Upsilon_{t+j}^{g_j}}\Big) \mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}] \Big].
+\end{multlined}
+\end{equation}
+	By Proposition \ref{thm:Key}, there exist $C_0,\delta_0 >0$,  depending only on $\mu$ and $g$, such that  for each $k_2 \in \{0, \dots, n_2 \}$,
+\begin{align}
+    &| a_{-1,k_2} - a_{-1,k_2-1}|
+    \overset{\eqref{eq:MI.1}}\leq \mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{g_{k_2}}_{t+k_2}}-e^{\langle Z_1g_{k_2}, \varphi\rangle}; D^c|\mathscr F_{t+k_2}]\big|\Big]
+    \\&\label{eq:MI.15} \leq C_0 e^{-\delta_0 (t+k_2)}.
 \end{align}
-Now apply induction on $n$ to \eqref{E:1.1}\ldots
+	Similarly, for any $k_1 \in \{0, \dots , n_1\}$,
+\begin{equation}
+\label{eq:MI.2}
+\begin{multlined}
+	a_{k_1-1,-1} - a_{k_1,-1}
+	=  \frac{1}{\mathbb P_\mu(D^c)} \Big(\prod_{j=0}^{k_1-1}e^{\langle Z_1 f_j, \varphi\rangle}\Big) \Big(\prod_{j=0}^{n_2} e^{ \langle Z_1g_j,\varphi \rangle} \Big) \times {}
+	\\ \qquad \mathbb{P}_{\mu}\Big[ \mathbb P_\mu\big[e^{i\Upsilon_{t-k_1-1}^{f_{k_1}}} -e^{\langle Z_1 f_{k_1}, \varphi\rangle}  ; D^c \big| \mathscr F_{t-k_1 - 1}\big] \prod_{j=k_1+1}^{n_1} e^{i\Upsilon_{t-j-1}^{f_j}} \Big] .
+\end{multlined}
+\end{equation}
+	By Proposition \ref{thm:Key}, there exist $C_1,\delta_1 >0$, depending only on $\mu$ and $f$, such that for any $k_1 \in \{0,\dots,n_1\}$,
+\begin{align}
+    &| a_{k_1-1,-1} - a_{k_1,-1}|
+    \overset{\eqref{eq:MI.2}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\Upsilon^{f_{k_1}}_{t-k_1-1}}-e^{\langle Z_1f_{k_1}, \varphi\rangle}; D^c|\mathscr F_{t-k_1-1}]\big|\Big]
+    \\&\label{eq:MI.25} \leq C_1 e^{-\delta_1 (t-k_1)}.
+\end{align}
+	Therefore, there exist $C,\delta >0$, depending only on $f,g$ and $\mu$, such that
+\begin{align}
+    &\text{LHS of \eqref{32corollary}}
+    = \left|a_{-1,n_2}-a_{n_1,-1}\right|
+    \leq \sum_{k=0}^{n_1}\left|a_{k-1,-1}-a_{k,-1}\right|+\sum_{k=0}^{n_2}\left|a_{-1,k}-a_{-1,k-1}\right|
+    \\& \overset{\eqref{eq:MI.15},\eqref{eq:MI.25}}\leq \sum_{k=0}^{n_1} C_1 e^{-\delta_1 (t-k)}+\sum_{k=0}^{n_2} C_0 e^{-\delta_0 (t+k)}
+  	\leq C e^{- \delta (t-n_1)}.
+    \qedhere
+\end{align}
 \end{prof}
 
-\begin{remark}\label{re:1.2}
-Remarks, examples, problems, etc. are set in roman type.
-\end{remark}
+	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
+\begin{lemma} \label{ineq: analysis}
+	There exists a constant $C>0$ such that for any $x,y \in \mathbb R$,
+\[
+    |(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
+    \leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
+\]
+\end{lemma}
+\begin{prof}
+   	Note the desired result holds if $x =0$ or $y = 0$.
+   	So, we can assume $|x|>0$ and $|y|>0$.
+   	Noticing also the symmetry between $x$ and $y$, we can assume without loss of generality that $|x|\geq |y|$.
+   	Also note that $\overline{ z^{1+\beta}} = \overline z^{1+\beta}$ for each $z \in \mathbb C \setminus (-\infty, 0)$
+   	where $\bar z$ is the complex conjugate of $z$.
+% It is easy is see that
+It is easy to see that
+\[
+	|(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
+	= |(-ix-iy)^{1+\beta}-(-ix)^{1+\beta}-(-iy)^{1+\beta}|.
+\]
+Thus we can further assume without loss of generality that $y>0$.
+	Note that for any $z\in \mathbb C$,
+\begin{align}
+  	&\lim_{r \to \infty, r>0}\frac{(r\pm 1)^{1+\beta}-r^{1+\beta} - z}{r^{\beta}}
+  	=\lim_{r\to \infty, r > 0}\frac{(r\pm1)^{1+\beta}-r^{1+\beta}}{r^{\beta}}
+  	\\&=\lim_{r\to \infty,r>0}\big((1\pm r^{-1})^{1+\beta}-1\big)r = \pm(1+\beta).
+\end{align}
+	Combining the above with continuity, we get that for each $z\in \mathbb C$ there exists $C(z)>0$ such that for each $r\geq 1$,
+\[
+  	|(r\pm 1)^{1+\beta}-r^{1+\beta} - z|
+  	\leq C(z) |r|^{\beta}.
+\]
+	One can easily check by definition that $(iur)^{\gamma} = (iu)^{\gamma} r^{\gamma}$ for  any $u\in \mathbb R\setminus\{0\}, r>0$ and $\gamma \geq 0$.
+	Therefore for each $r\geq 1$ we have
+\begin{align}
+	&\big|\big(i(1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big|
+	= \big|i^{1+\beta} \big((r+1)^{1+\beta} - r^{1+\beta} - 1\big)\big|
+	\\&= |(r+1)^{1+\beta}-r^{1+\beta}-1|
+	\leq C(1) |r|^{\beta};
+\end{align}
+and for each $r\leq -1$ we have
+\begin{align}
+	&\big|\big( i (1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big|
+	= \big|(-i)^{1+\beta} \big((-r - 1)^{1+\beta} - (-r)^{1+\beta} - i^{2+2\beta}\big)\big|
+	\\&= |(-r-1)^{1+\beta}-(-r)^{1+\beta}  - i^{2+2\beta}|
+	\leq C(i^{2+2\beta}) |r|^{\beta}.
+\end{align}
+Summarizing, we have that there exists a $C_1>0$ such that for each $r\in \mathbb R$ with $|r|\geq 1$,
+\[
+	\big|\big( i(1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big| \leq C_1 |r|^\beta.
+\]
+Now it follows immediately that
+\begin{align}
+	&|(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
+	= \big|y^{1+\beta}\big(
+	(i(1+x/y))^{1+\beta}
+	-(ix/y)^{1+\beta}- i^{1+\beta}\big)\big|
+	\\&= |y|^{1+\beta}\big|\big(i(1+x/y)\big)^{1+\beta}-(ix/y)^{1+\beta}-i^{1+\beta}\big|
+	\leq C_1|y||x|^{\beta}.
+	\qedhere
+\end{align}
+\end{prof}
 
-\subsection{Table}
+	In the remainder of this section, we  fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$,  $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$.
+	For every $t\geq 1$, define
+\begin{align}
+	R(t)
+	&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
+        \\R'(t)
+    &:=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
+        \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
+\end{align}
+where $T_k$ is the operator defined in
+\eqref{e:Tt}, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult}
+with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
+	The following result is a special case of Theorem \ref{thm:M}.
+\begin{theorem}\label{thm: II}
+	Under $\mathbb{\widetilde{P}}_{\mu}$, $R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
+\end{theorem}
+\begin{prof}
+	In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
+	According to the proof of
+\cite[Theorem 1.6]{RenSongSunZhao2019Stable} and the fact that the convergence in
+ probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
+\[
+	R(t)-R'(t)
+	\xrightarrow[t\to \infty]{\text{in probability}} 0.
+\]
+	With the help of Slutsky's theorem, what is left to show is that,
+\begin{equation} \label{lem:UOT}
+	R'(t)
+	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
+\end{equation}
 
-\begin{table}
-\begin{tabular}{|c|c|c|l|c|}
-\hline $P(x)$ & $i$& $(e(1),e(2),e(4))$ & $(e(3),e(6),e(12),e(24))$ & $T(E)$ \\
-\hline $P_1$  &    & & &$\emptyset$ \\
-\hline $P_2$  & 4  & & $(1,1,1,0)\rightarrow(0,0,0,1)$ &2\\
-\hline $P_3$  & 2  & &$(1,1,1,0)\rightarrow(0,0,2,0)$ &1\\
-\hline $P_4$  & 2  & $(0,1,1)\rightarrow(1,2,0)$ & &1\\
-\hline $P_5$  & 2  & $(0,1,1)\rightarrow(1,2,0)$ &$(1,1,1,0)\rightarrow(0,0,0,1)$ &$1,2$\\
-\hline $P_6$  & 6  & $(0,1,1)\rightarrow(1,2,0)$ &$(1,1,1,0)\rightarrow(2,2,0,0)$ &1\\
-\hline $P_7$  & 3  & $(0,1,1)\rightarrow(1,0,1)$ &$(1,1,1,0)\rightarrow(2,0,1,0)$ &0\\
-\hline $P_8$  & 3  & $(0,1,1)\rightarrow(2,1,0)$ &$(1,1,1,0)\rightarrow(2,0,1,0) \rightarrow(3,1,0,0)$ &$0,1$\\
-\hline
-\end{tabular}
-\caption{Aaa bbb ccc\label{tab}}
-\end{table}
+	Now we prove \eqref{lem:UOT}.
+	Since $\Upsilon_t^f$ is linear in $f$, for each $t\geq 1$,
+\[
+        \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_j(t)\Big)\Big]
+	= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
+\]
+	Note that $\{T_k(\tilde f_\mathrm s + t^{\tilde\beta - 1}\tilde f_{\mathrm c}):k\in \mathbb Z_+, t\geq 1\}\subset \overline{\mathcal P}_{\tilde f_\mathrm s + \tilde f_{\mathrm c}}$ and $\{-T_k\tilde{f}_{\mathrm l}: k\in \mathbb Z_+\}\subset \overline{\mathcal P}_{\tilde f_\mathrm l}$.
+	Therefore, we can use Proposition \ref{cor:MI} with $f$
+taken as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taken as
+	$\tilde{f}_{\mathrm l}$
+	to get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
+\begin{align}
+       &\begin{multlined}
+  	\bigg|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}R'_j(t)\Big)\Big] - {}
+  	\\ \exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \big\langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})\big), \varphi \big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\bigg|
+  	\end{multlined}
+      \\ &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
+\end{align}
+	We claim that
+\begin{align}
+\label{eq:UOT.1}
+	&\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}\big \langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c)\big), \varphi\big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big)
+	\\& =\exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
+\end{align}
+	Given this claim, we have
+\[
+	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_{j}(t)\Big)\Big]
+	\xrightarrow[t\to \infty]{} \exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
+\]
+	Since $R'_{j}(t)$ are linear
+	 in $f_j \in \mathcal C_j~(j=\mathrm s,\mathrm c,\mathrm l)$, replacing $f_j$ with $\theta_j f_j$, we immediately get \eqref{lem:UOT}.
 
-\subsection{Figure}
+	Now we prove the claim \eqref{eq:UOT.1}.
+	For every $f\in \mathcal C_\mathrm s  \oplus \mathcal C_\mathrm c$ and $n\in \mathbb Z_+$,
+ \begin{align}
+  	& \sum_{k=0}^n \langle Z_1 T_{k} \tilde f, \varphi \rangle
+  	= \sum_{k=0}^n \int_0^1 \big\langle P_u^\alpha \big(\eta(-iP_{1 - u}^\alpha T_k \tilde f)^{1+\beta}\big), \varphi\big\rangle \mathrm du
+ 	\\& = \sum_{k=0}^n \int_0^1 e^{\alpha u} \langle \eta (-iP_{1 - u}^\alpha T_{k}\tilde f)^{1+\beta}, \varphi \rangle \mathrm du
+ 	= \sum_{k=0}^n \int_0^1 \langle \eta (-iT_{k+1 - u} f)^{1+\beta}, \varphi\rangle \mathrm du
+ 	\\&= \int_0^{n+1} \langle  \eta (-iT_{u} f)^{1+\beta}, \varphi\rangle \mathrm du
+ 	= m_{n+1}[f],
+\end{align}
+	where $\tilde f=e^{\alpha(\tilde \beta - 1)} f$.
+	Therefore, for any $t\geq 1$,
+\begin{equation} \label{eq:UOT.15}
+	\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c), \varphi\rangle
+	= \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du.
+\end{equation}
+	Note that for each $u\geq 0$, $T_uf_\mathrm c=f_\mathrm c$.
+	Also note that according to
+ 	Step 1 in the proof of \cite[Lemma 2.6]{RenSongSunZhao2019Stable}, there exist $\delta> 0$ and $h\in \mathcal P$ (depending only on $f_\mathrm s$) such that for each $u\geq 0$, $|T_u f_\mathrm s|\leq e^{-\delta u}h$.
+	It follows from Lemma \ref{ineq: analysis} that there exists $C>0$ such that for all $u\geq 0$ and $t\geq 0$,
+\begin{align}
+  	&|(-i(T_uf_\mathrm s+t^{\tilde{\beta}-1}T_uf_\mathrm c))^{1+\beta}-(-iT_uf_\mathrm s)^{1+\beta}-(-it^{\tilde{\beta}-1}T_uf_\mathrm c)^{1+\beta}|
+  	\\&\overset{\text{Lemma \ref{ineq: analysis}}}
+  	\leq  C(t^{-\frac{\beta}{1+\beta}}|T_uf_\mathrm s||T_uf_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}|T_uf_\mathrm s|^{\beta}|T_uf_\mathrm c|)
+  	\\&\label{eq:UOT.21}\leq C(t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|).
+\end{align}
+	This means that there exists $C_1 >0$ such that for all $t\geq 1$,
+\begin{align}
+	&\Big|\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)-m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm s]-\frac{1}{t}m_{\lfloor t-\ln t \rfloor+1}[f_\mathrm c]\Big|
+	\\&
+\begin{multlined}
+	\overset{\eqref{eq:UOT.15},\eqref{eq:M.13}}\leq\Big| \eta \int_0^{\lfloor t-\ln t \rfloor+1}\big\langle \big(-iT_u(f_\mathrm s+t^{\tilde{\beta}-1}f_\mathrm c)\big)^{1+\beta},\varphi \big\rangle \mathrm du - {}
+	\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du
+	- \frac{1}{t} \eta
+	\int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|
+\end{multlined}
+	\\ & \overset{\eqref{eq:UOT.21}}\leq C_1\int_0^{\lfloor t-\ln t \rfloor+1}\langle t^{-\frac{\beta}{1+\beta}}e^{-\delta u}h|f_\mathrm c|^{\beta}+t^{-\frac{1}{1+\beta}}e^{-\delta\beta u}h^{\beta}|f_\mathrm c|, \varphi \rangle \mathrm du
+	\\& \leq C_1 t^{-\frac{\beta}{1+\beta}} \langle h|f_\mathrm c|^{\beta},\varphi \rangle \int_0^\infty e^{-\delta u} \mathrm du + C_1 t^{-\frac{1}{1+\beta}} \langle h^\beta|f_\mathrm c|,\varphi \rangle \int_0^\infty e^{-\delta \beta u} \mathrm du
+	\\& \xrightarrow[t\rightarrow \infty]{} 0.
+\end{align}
+	Combining this with \eqref{eq:I:R:3}, we get that
+\begin{equation}
+\label{eq:UOT.4}
+	\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \langle Z_1T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_c), \varphi\rangle \Big)  = \exp( m[f_\mathrm s]+m[f_\mathrm c]).
+\end{equation}
+	Also note that according to the Step 1 in the Proof of Theorem 1.6.(3) in \cite{RenSongSunZhao2019Stable}, we have
+\begin{equation}
+\label{eq:UOT.5}
+	\lim_{t\rightarrow \infty}\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big) =\exp(m[-f_\mathrm l]).
+\end{equation}
+	Thus the desired claim follows from \eqref{eq:UOT.4} and \eqref{eq:UOT.5}.
+\end{prof}
 
-%\centerline{\includegraphics[scale=1.2]{actmark.eps}}
-%\centerline{\small Figure 1\quad Journal mark}
+\begin{prof}[Proof of Theorem \ref{thm:M}]
+ 	We first recall some facts about weak convergence which will be used later.
+	For any bounded Lipschitz function $f:\mathbb R^d\mapsto \mathbb R$, let
+\[
+	\|f\|_L
+	:=\sup_{x\neq y}\frac{|f(x)-f(y)|}{|x-y|}
+\]
+	and $\|f\|_{BL}:= \|f\|_{\infty}+\|f\|_L.$
+	For any probability distributions $\mu_1$ and $\mu_2$ on $\mathbb R^d$, define
+\[
+	d(\mu_1,\mu_2)
+  	:=\sup\Big\{\Big|\int f \mathrm d\mu_1-\int f \mathrm d\mu_2\Big|:\|f\|_{BL}\leq 1\Big\}.
+\]
+	Then $d$ is a metric. It follows from \cite[Theorem 11.3.3]{Dudley2002} that the topology generated by $d$ is equivalent to the weak convergence topology.
+	Using the definition, we can easily see that, if $\mu_1$ and $\mu_2$ are the distributions of two $\mathbb R^d $-valued random variables $X$ and $Y$ respectively, defined on same probability space, then
+\begin{align}
+\label{ineq: distribution control}
+  	d(\mu_1,\mu_2)
+  	\leq \mathbb E|X-Y|.
+\end{align}
+	In this proof, let us fix $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$.
+	Recall that $S(t)~(t\geq 0)$ is given by \eqref{eq:M.1}.
+	For every $r,t> 0$, let
+\begin{align}
+	S(t,r)
+	:=\Big(e^{-\alpha t}\|X_t\|,& \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm c)}{\|(t+r)X_{t+r}\|^{1-\tilde{\beta}}}, \frac{X_{t+r}(f_\mathrm l)-\mathrm x_{t+r}(f_\mathrm l) }{\|X_{t+r}\|^{1-\tilde{\beta}}}\Big),
+\end{align}
+	and
+\begin{align}
+	\widetilde{S}(t,r)
+	:=
+	(e^{-\alpha (t+r)}\|X_{t+r}\|-e^{-\alpha t}\|X_t\|,0,0,0),
+\end{align}
+	where, for any $t>0$, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} with $f$ replaced with $f_\mathrm l$.
+	Then $S(t+r)=S(t,r)+\widetilde{S}(t,r)$.
+	We claim that
+\begin{equation}
+\label{eq:M.3}
+\begin{minipage}{0.9\textwidth}
+	for each $t> 0$, under $\widetilde{\mathbb P}_{\mu}$, we have
+\[
+	S(t,r)
+	\xrightarrow[r\rightarrow \infty]{d} (\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
+\]
+	where $\widetilde H_t$ has the distribution of $\{e^{-\alpha t} \|X_t\|; \widetilde {\mathbb P}_\mu\}$, $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, 	and $\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
+\end{minipage}
+\end{equation}
 
-\acknowledgements{\rm We thank the referees for their time and
-comments. }
+	For every $r,t\geq 0$, let $\mathcal D(r)$ and $\mathcal D(r,t)$ be the distributions of $S(r)$ and $S(t,r)$ under $\widetilde{\mathbb P}_{\mu}$ respectively;
+	let $\widetilde{\mathcal D}(t)$ and $\mathcal D$ be the distributions of $(\widetilde H_t,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$ and $(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, respectively.
+	Then for each $\gamma\in (0,\beta)$, there exist constant $C>0$ such that for every $t > 0$,
+\begin{align}
+ 	&\varlimsup_{r\rightarrow \infty}d(\mathcal D(t+r),\mathcal D)
+ 	\\& \overset{\rm triangle~inequality}\leq \varlimsup_{r\rightarrow \infty}\Big( d\big(\mathcal D(t+r),\mathcal D(t,r)\big)+d\big(\mathcal D(t,r),\widetilde{\mathcal D}(t)\big)+d\big(\widetilde{\mathcal D}(t),\mathcal D\big)\Big)
+ 	\\&\overset{\eqref{ineq: distribution control}} \leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|S(t+r) - S(t,r)|]+ \varlimsup_{r\rightarrow \infty} d\big(\mathcal D(t,r),\widetilde{\mathcal D}(t)\big) +\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]
+	\\&\overset{\eqref{eq:M.3}}\leq \varlimsup_{r\rightarrow \infty}\widetilde{\mathbb P}_{\mu}[|H_t - H_{t+r}|]+\widetilde{\mathbb P}_{\mu}[|H_t-H_{\infty}|]
+  	\\&\overset{\text{H\"older inequality}}\leq \varlimsup_{r\rightarrow \infty}\mathbb P_{\mu}(D^c)^{-1}(\|H_t-H_{t+r}\|_{L_{1+\gamma} (\mathbb P_\mu)}+\|H_t-H_{\infty}\|_{L_{1+\gamma} (\mathbb P_\mu)})
+	\\&\label{eq:M.4}\overset{\text{\cite[Lemma 3.3]{RenSongSunZhao2019Stable}}}\leq C e^{-\alpha \tilde \gamma t}.
+\end{align}
+	Therefore,
+\begin{align}
+ 	&\varlimsup_{r\rightarrow \infty}d\big(\mathcal D(r),\mathcal D\big)
+ 	=\varlimsup_{t\to \infty}\varlimsup_{r\rightarrow \infty}d\big(\mathcal D(t+r),\mathcal D\big)
+	\overset{\eqref{eq:M.4}}\leq \varlimsup_{t\rightarrow \infty}Ce^{-\alpha \tilde \gamma t} = 0.
+\end{align}
+	The desired result now follows immediately.
+
+	Now we prove the claim \eqref{eq:M.3}.
+	For every $r,t >0$, let
+\[
+	\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l \in \mathbb R
+	\mapsto k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
+\]
+	be the characteristic function of  $S(t,r)$ under $\widetilde{\mathbb P}_{\mu}$.
+	Then for each $\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l\in \mathbb R$ and $r,t> 0$,
+\begin{align}
+	&k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
+	=\widetilde{\mathbb P}_{\mu}\big[\exp\big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,\infty)\big)\big]\\
+	&\label{eq:M.5}\overset{\text{bounded convergence}}=\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\big[\exp\big( i\theta e^{-\alpha t}\|X_t\|+A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\big);D^c\big],
+\end{align}
+	where for each $u\in [0,\infty]$,
+\begin{align}
+	&A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)
+	\\&:=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + i\theta_\mathrm c \frac{X_{t+r}(f_\mathrm c)}{\|(t+r)X_{t+r}\|^{1-\tilde{\beta}}} + i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l)- \mathbb P_\mu[\mathrm x_{t+r}(f_\mathrm l)|\mathscr F_u]}{\|X_{t+r}\|^{1-\tilde{\beta}}}
+	\\&\label{eq:M.6}
+\begin{multlined}
+	=i\theta_\mathrm s \frac{X_{t+r}(f_\mathrm s)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + \frac{i\theta_\mathrm c}{(t+r)^{1-\tilde{\beta}}} \frac{X_{t+r}(f_\mathrm c)}{\|X_{t+r}\|^{1-\tilde{\beta}}} + {}
+	\\\quad  i\theta_\mathrm l  \frac{ X_{t+r}(f_\mathrm l) - \sum_{p\in \mathbb Z_+^d:\alpha\tilde{\beta}>|p|b}
+		\langle f_\mathrm l, \phi_p\rangle_\varphi e^{(\alpha - |p|b)(t+r)} H_u^p
+	}{\|X_{t+r}\|^{1-\tilde{\beta}}}.
+\end{multlined}
+\end{align}
+	Now for each $t>0$, we get
+\begin{align}
+	& \lim_{r\to \infty}k(\theta,\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t)
+	\\&\overset{\eqref{eq:M.5}}=\lim_{r\to \infty}\lim_{u\rightarrow \infty}\frac{1}{\mathbb P_{\mu}(D^c)}\mathbb P_{\mu}\big[\exp\{i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0} \mathbb P_{\mu}[\exp\{A(\theta_\mathrm s,\theta_\mathrm c,\theta_\mathrm l,r,t,u)\}\mathbf 1_{D^c}|\mathscr F_t]\big]
+	\\&
+\begin{multlined}
+	\overset{\text{\eqref{eq:M.6}, Markov property}}=\lim_{r\to \infty}\lim_{u\rightarrow\infty}\frac{1}{\mathbb P_{\mu}(D^c)} \mathbb P_{\mu}\Bigg[\exp\{ i\theta e^{-\alpha t}\|X_t\|\}\mathbf 1_{\|X_t\|>0} \times {}
+	\\ \mathbb P_{X_t}\bigg[\exp\bigg\{A\bigg(\theta_\mathrm s,\theta_\mathrm c\Big(\frac{r}{t+r}\Big)^{1-\tilde \beta},\theta_\mathrm l,r,0,u-t\bigg)\bigg\}\mathbf 1_{D^c}\bigg]\Bigg]
+\end{multlined}
+	\\&\begin{multlined}\overset{\text{bounded convergence}}=\lim_{r\to \infty} \mathbb P_{\mu}\Bigg[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \times {}
+	\\\widetilde{\mathbb P}_{X_t}\bigg[\exp\bigg\{A\bigg(\theta_\mathrm s,\theta_\mathrm c\Big(\frac{r}{t+r}\Big)^{1-\tilde \beta},\theta_\mathrm l,r,0,\infty\bigg)\bigg\}\bigg]\Bigg].
+\end{multlined}
+	\\& \overset{\text{Theorem \ref{thm: II}}}=  \mathbb P_{\mu}\Big[\exp\{ i\theta e^{-\alpha t}\|X_t\|\} \mathbf 1_{\|X_t\|>0}\frac{\mathbb P_{X_t}(D^c)}{\mathbb P_{\mu}(D^c)} \Big]\Big(\prod_{j=\mathrm s,\mathrm c}\exp\{m[\theta_j f_j]\}\Big)\exp\{m[-\theta_\mathrm l f_\mathrm l]\}
+	\\&=\widetilde{\mathbb P}_{\mu}[\exp\{i\theta e^{-\alpha t}\|X_t\|\}]
+	\Big(\prod_{j=\mathrm s,\mathrm c}\exp\{m[\theta_j f_j]\}\Big)\exp\{m[-\theta_\mathrm l f_\mathrm l]\}.
+	\qedhere
+\end{align}
+\end{prof}
+
+\acknowledgements{\rm We thank the referees for the very helpful comments.}
 
@@
 
-\bibitem{HB} %% Books %% surname(s), initial(s), title, publisher, place of publication, year
-Huppert, B., Blackburn, N.: Finite Groups II, Springer-Verlag, New
-York, 1982
+\bibitem{AdamczakMilos2015CLT}
+	Adamczak, R., Mi{\l}o\'{s}, P.:
+	C{LT} for {O}rnstein-{U}hlenbeck branching particle system.
+	\emph{Electron. J. Probab.}, \textbf{20}, no. 42, 35 pp. (2015)
 
-\bibitem{LT} %% Journals %% surname(s), initial(s), article, journal, volume, relevant page numbers, year
-Lorenzini, D., Tucker, T. J.: The equations and the method of
-Chabauty--Coleman. \emph{Invent. Math.}, \textbf{148}, 1--46
-(2002)
+\bibitem{Asmussen76Convergence}
+	Asmussen, S.: 
+	Convergence rates for branching processes.
+	\emph{Ann. Probab.}, \textbf{4}, no. 1, 139--146 (1976)
 
-\bibitem{T1}
-Test
+\bibitem{AsmussenHering1983Branching}
+	Asmussen, S., Hering, H.: 
+	Branching processes,
+	Progress in Probability and Statistics, 3. Birkh\"{a}user Boston, Inc., Boston, MA, 1983.
 
-\bibitem{T2}
-Test
+\bibitem{Athreya1969Limit}
+	Athreya, K. B.: 
+	Limit theorems for multitype continuous time {M}arkov branching processes. {I}. {T}he case of an eigenvector linear functional.
+	\emph{Z. Wahrscheinlichkeitstheorie und Verw. Gebiete}, \textbf{12}, 320--332 (1969)
 
-\bibitem{T3}
-Test
+\bibitem{Athreya1969LimitB}
+  	Athreya, K. B.: 
+  	Limit theorems for multitype continuous time {M}arkov branching processes. {II}. {T}he case of an arbitrary linear functional.
+	\emph{Z. Wahrscheinlichkeitstheorie und Verw. Gebiete}, \textbf{13}, 204--214 (1969)
+
+\bibitem{Athreya1971Some}
+  	Athreya, K. B.: 
+  	Some refinements in the theory of supercritical multitype {M}arkov branching processes.
+	\emph{Z. Wahrscheinlichkeitstheorie und Verw. Gebiete}, \textbf{20}, 47--57 (1971)
+
+\bibitem{Dudley2002}
+  	Dudley, R. M.: 
+	Real Analysis and Probability. 
+	Revised reprint of the 1989 original. 
+	Cambridge Studies in Advanced Mathematics, 74.
+  	Cambridge University Press, Cambridge, 2002.
+
+\bibitem{Dynkin1993Superprocesses}
+  	Dynkin, E. B.: 
+  	Superprocesses and partial differential equations.
+	\emph{Ann. Probab.}, \textbf{21}, no. 3, 1185--1262 (1993)
+
+\bibitem{Heyde1970A-rate}
+	Heyde, C. C.: 
+ 	A rate of convergence result for the super-critical {G}alton-{W}atson process.
+	\emph{J. Appl. Probability}, \textbf{7}, 451--454 (1970)
+
+\bibitem{Heyde1971Some}
+  	Heyde, C. C.: 
+   	Some central limit analogues for supercritical {G}alton-{W}atson processes.
+	\emph{J. Appl. Probability}, \textbf{8}, 52--59 (1971)
+
+\bibitem{HeydeBrown1871An-invariance}
+  	Heyde, C. C., Brown, B. M.: 
+  	An invariance principle and some convergence rate results for branching processes.
+	\emph{Z. Wahrscheinlichkeitstheorie und Verw. Gebiete}, \textbf{20}, 271--278 (1971)
+
+\bibitem{HeydeLeslie1971Improved}
+	Heyde, C. C., Leslie, J. R.: 
+  	Improved classical limit analogues for {G}alton-{W}atson processes with or without immigration.
+	\emph{Bull. Austral. Math. Soc.}, \textbf{5}, 145--155 (1971)
+
+\bibitem{KestenStigum1966A-limit}
+ 	Kesten, H., Stigum, B. P.: 
+  	A limit theorem for multidimensional {G}alton-{W}atson processes.
+	\emph{Ann. Math. Statist.}, \textbf{37}, 1211--1223 (1966)
+
+\bibitem{KestenStigum1966Additional}
+  	Kesten, H., Stigum, B. P.: 
+  	Additional limit theorems for indecomposable multidimensional {G}alton-{W}atson processes.
+	\emph{Ann. Math. Statist.}, \textbf{37}, 1463--1481 (1966)
+
+\bibitem{Kyprianou2014Fluctuations}
+  	Kyprianou, A. E.: 
+  	Fluctuations of {L}\'{e}vy processes with applications.
+	Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
+
+\bibitem{Li2011Measure-valued}
+  	Li, Z.: 
+  	Measure-valued branching {M}arkov processes.
+  	Probability and its Applications (New York). Springer, Heidelberg, 2011.
+
+\bibitem{MarksMilos2018CLT}
+  	Marks, R., Mi{\l}o{\'s}, P.: 
+  	C{LT} for supercritical branching processes with heavy-tailed branching law.
+  	arXiv:1803.05491.
+
+\bibitem{Milos2012Spatial}
+  	Mi{\l}o{\'s}, P.: 
+  	Spatial central limit theorem for supercritical superprocesses.
+	\emph{J. Theoret. Probab.}, \textbf{31}, no. 1, 1--40 (2018)
+
+\bibitem{RenSongSunZhao2019Stable}
+	Ren, Y.-X., Song, R., Sun, Z., Zhao, J.: 
+	Stable central limit theorems for super Ornstein-Uhlenbeck processes.
+	\emph{Electron. J. Probab.}, \textbf{24}, no. 141, 1--42 (2019)
+
+\bibitem{RenSongZhang2014Central}
+  	Ren, Y.-X., Song, R., Zhang, R.: 
+  	Central limit theorems for super {O}rnstein-{U}hlenbeck processes.
+	\emph{Acta Appl. Math.}, \textbf{130}, 9--49 (2014)
+
+\bibitem{RenSongZhang2014CentralB}
+  	Ren, Y.-X., Song, R., Zhang, R.: 
+  	Central limit theorems for supercritical branching {M}arkov processes.
+	\emph{J. Funct. Anal.}, \textbf{266}, no. 3, 1716--1756 (2014)
+
+\bibitem{RenSongZhang2017Central}
+  	Ren, Y.-X., Song, R., Zhang, R.: 
+  	Central limit theorems for supercritical branching nonsymmetric {M}arkov processes.
+	\emph{Ann. Probab.}, \textbf{45}, no. 1, 564--623 (2017)
+
+\bibitem{RenSongZhang2015Central}
+  	Ren, Y.-X., Song, R., Zhang, R.: 
+  	Central limit theorems for supercritical superprocesses.
+	\emph{Stochastic Process. Appl.}, \textbf{125}, no. 2, 428--457 (2015)
 
 \end{thebibliography}
-
 \end{document}
